### 2015-11-16 DQC3.tex
Initial ShareLaTeX Import

%% Discrete Quantum Computing/Discrete Quantum Theory
%%  - third paper, focusing on how fundamental aspects needed by
%% all quantum mechanical theories (as treated in Asher Peres's book)
%% have to be approached in a quantum theory based on Galois groups,
%% via COMPUTABLE integer number fields with finite characteristic.

\documentclass[english,12pt]{article}
\usepackage{mathrsfs}
\usepackage{fullpage}
% \documentclass[english,prl,aps,showpacs,preprint,floatfix,superscriptaddress]{revtex4-1} 
%\usepackage[T1]{fontenc}
% \usepackage[latin9]{inputenc}
% \setcounter{secnumdepth}{3}
\usepackage{url}
\usepackage{times}

\usepackage{amsthm}
\usepackage{amsmath}

\input{Qcircuit}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\usepackage{enumitem}		% customizable list environments
% \newlength{\lyxlabelwidth}      % auxiliary length

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{amsfonts}
\usepackage{color}
\usepackage{stmaryrd}\usepackage{dsfont}
\usepackage[usenames,dvipsnames]{xcolor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% these went missing?
% \newcommand{\bra}[1]{\left\langle{#1}\right|}
% \newcommand{\ket}[1]{\left|{#1}\right\rangle}
% \newcommand{\mathscr}[1]{{\cal #1}}
%\renewcommand{\author}[1]{\bf #1 \/}
\newcommand{\affiliation}[1]{\parbox{5.5in}{\small{\it #1 \/}}}
\newcommand{\pacs}[1]{\bf #1 \/}

\newcommand{\cardp}[2]{#1 \,\sslash\, #2}
\newcommand{\braket}[2]{\langle{#1}|{#2}\rangle} 
\newcommand{\uf}{U_{\!f}}
\def\image {\rm Image~}
\def\ker{\rm ker~}
\def\coker{\rm coker~}
\def\ker{\rm ker~}
\def\dr{\smash{\downharpoonright}}
\def\ad{{\rm ad~}}
\def\Q{{\mathbb{Q}}}
\def\R{{\mathbb{R}}}
\def\N{{\mathbb{N}}}
\def\C{{\mathbb{C}}}
\def\Z{{\mathbb{Z}}}
\def\del{\partial}
\def\grad{\nabla}
\def\proof{{\em Proof:  }}
\def\ra{\rangle}
\def\la{\langle}
\def\rl{\rangle \langle}
\def\openone{\leavevmode\hbox{\small1\kern-3.8pt\normalsize1}}
\def\RR{{\rm I\kern-.2emR}}
\def\tr{{\rm tr}\; }
\def\fu{\mathfrak{u}}
\def\fa{\mathfrak{a}}
\def\fd{\mathfrak{d}}
\def\fb{\mathfrak{b}}
\def\fj{\mathfrak{j}}
\def\fg{\mathfrak{g}}
\def\fh{\mathfrak{h}}
\def\fk{\mathfrak{k}}
\def\fs{\mathfrak{s}}
\def\fgl{\mathfrak{gl}}
\def\fsl{\mathfrak{sl}}
\def\fsu{\mathfrak{su}}
\def\fsp{\mathfrak{sp}}
\def\fso{\mathfrak{so}}
\def\proof{{\em Proof:  }}
\def\tphi{\tilde{\Phi}}
\def\ra{\rangle}
\def\la{\langle}
\def\rl{\rangle \langle}
\def\openone{\leavevmode\hbox{\small1\kern-3.8pt\normalsize1}}
\def\RR{{\rm I\kern-.2emR}}
\def\tr{{\rm tr}\; }
\def\ce{{\cal E}}
\def\cl{{\cal L}}
\def\cg{{\cal G}}
\def\cd{{\cal D}}
\def\cb{{\cal B}}
\def\cn{{\cal N}}
\def\ch{{\cal H}}
\def\cs{{\cal S}}
\def\ct{{\cal T}}
\def\cp{{\cal P}}
\def\cm{{\cal M}}
\def\cf{{\cal F}}
\def\ci{{\cal I}}
\def\ca{{\cal A}}
\def\calr{{\cal R}}
\def\cv{{\cal V}}
\def\cc{{\cal C}}
\def\rhon{\rho^{\otimes n}}
\def\on{^{\otimes n}}
\def\pn{^{(n)}}
\def\pnp{^{(n)'}}
\def\id{\frac{I}{d}}
\def\pthang{\frac{P}{\sqrt{d \tr P^2}}}
\def\Psirq{\Psi^{RQ}}
\def\d{^\dagger}
\def\union{\cup}
\def\intersection{\cap}
\newcommand{\QED}{\hspace*{\fill}\mbox{\rule[0pt]{1.5ex}{1.5ex}}}
\providecommand{\ignore}[1]{}

\newcommand{\scalarZ}{0}
\newcommand{\scalarO}{1}
\newcommand{\scalarPlus}{+}
\newcommand{\scalarTimes}{*}
\newcommand{\ip}[2]{\langle #1 ~|~ #2 \rangle}
\newcommand{\usat}{\texttt{UNIQUE-SAT}}
\newcommand{\boolt}{\textsf{Bool}} 
\newcommand{\bfalse}{\texttt{\textbf{false}}}
\newcommand{\btrue}{\texttt{\textbf{true}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\ffz}[1]{{\mathbb{F}^{\ast}_{#1}}}
%% \newcommand{\ffzd}[1]{\mathbb{F^{d}}_{#1}^{*}}
%%\newcommand{\ffzd}[1]{{\mathbb{F}^{d}_{#1}}^{\ast}}
%%\newcommand{\ffzd}[1]{{\mathbb{F}^{d\,\ast}_{#1}}}
\newcommand{\ffd}[1]{{\mathbb{F}^{d}_{#1}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
%% \newcommand{\dotprod}{quadratic Hermitian form}}
\newcommand{\dotprod}{dot product}
\newcommand{\todo}[1]{\textbf{TODO.~#1}}

\newcommand{\p}[1]{^{(#1)}}

\def\gbar{\overline{\gamma}}
\def\rev{{\cal R}_{\ca,\rho}}

\def\imod#1{\allowbreak\mkern8mu({\operator@font mod}\,\,#1)}

\newcommand{\half}{\mbox{$\textstyle \frac{1}{2}$} }
\newcommand{\proj}[1]{\ket{#1}\! \bra{#1}}
\newcommand{\outerp}[2]{\ket{#1}\! \bra{#2}}
\newcommand{\inner}[2]{ \langle #1 | #2 \rangle}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\benum}{\begin{enumerate}}
\newcommand{\eenum}{\end{enumerate}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqa}{\begin{eqnarray}}
\newcommand{\eeqa}{\end{eqnarray}}
\newtheorem{definition}{Definition}
\newtheorem{assertion}{Assertion}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{axiom}{Axiom}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{property}{Property}
\newtheorem{fact}{Fact}
\newtheorem{remark}{Remark}
\newcommand{\bproof}{\begin{proof}}
\newcommand{\eproof}{\end{proof}}
\newcommand{\bprop}{\begin{proposition}}
\newcommand{\eprop}{\end{\proposition}}
\newcommand{\bdef}{\begin{definition}}
\newcommand{\zls}{{\mathbb Z}}
%%% This is our own symbol for "discrete probability"
%%    - originally "g", try "\pi" for now.
\newcommand{\dpr}{{\pi}}
\newcommand{\dpt}{{\tilde{\pi}}}
\def\round{\mathop{\rm round}\nolimits}

\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{red}{Amr says: #1}\end{minipage}}}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}

\newcommand{\ComplexI}{\text{i}}
\allowdisplaybreaks
\newcommand{\fnorm}[1]{\mathsf{N}(#1)}

\makeatother

\usepackage{babel}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Contextuality and Nonlocality in \\ Discrete Quantum Theory}

\author{John Gardiner\\
 \affiliation{College of Physical and Mathematical Sciences, Brigham
  Young University, Provo, UT 84602, U.S.A}\\[.2in]
%% \author
Andrew J. Hanson\\
\affiliation{School of Informatics and Computing, Indiana University,
  Bloomington, IN 47405, U.S.A}\\[.2in]
%%\author
Gerardo Ortiz \\
\affiliation{Department of Physics, Indiana University, Bloomington, IN 47405,
U.S.A}\\[.2in]
%%\author
Amr Sabry\\
\affiliation{School of Informatics and Computing, Indiana University,
  Bloomington, IN 47405, U.S.A}\\[.2in]
%%\author
Yu-Tsung Tai\\
\affiliation{Department of Mathematics, Indiana University,
  Bloomington, IN 47405, U.S.A}\\
\affiliation{School of Informatics and Computing, Indiana University,
  Bloomington, IN 47405, U.S.A}}

\maketitle

%\date{\today}

\pacs{03.65.-w, 03.65.Ud, 03.65.Ta, 02.10.De}

\maketitle

\rm \normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Theories of quantum mechanics based on finite complexified fields can
provide novel insights into subtle issues of nonclassical theories.  While
the study of such discrete quantum theories is motivated by the desire
to restrict our physical theories to computable numbers, all such
theories are handicapped by the absence of naturally ordered
quantities that can be associated with traditional probabilities.

\gerardo{This paper is about the measurement process in Discrete 
  Quantum Theories, that is, the process by which one extracts 
  information from a physical system in a hypothetical world 
  characterized by a finite number of resources, albeit arbitrarily 
  large.}

\amr{I would also start with a statement along the following lines and
  then using Gerardo's paragraph: Whether Nature is continuous or
  discrete, any \emph{representation} of a physical system in a
  computer or in a laboratory must use finite resources. In the realm
  of quantum computing, these finite resources must arguably be
  founded on vector spaces over finite fields that have as many
  properties of the conventional Hilbert spaces. This paper is about
  the measurement process in Discrete Quantum Theories, that is, the
  process by which one extracts information from a physical system in
  a hypothetical world characterized by a finite number of resources,
  albeit arbitrarily large.}

Having investigated the geometrical implications and properties of
discrete quantum theories in previous
work~\cite{geometry2013,DQT2014}, we turn here to the study of the
measurement process within such theories.  Our goal is to rediscover
properties of the foundations of standard axiomatic quantum mechanics,
including Gleason's theorem, the Kochen-Specker theorem, and Bell's
theorem, consistent within the discrete-field context, even while
lacking ordered probabilities in the number system.  We find for
example, that the discrete version of Gleason's theorem motivates a
corresponding Born rule.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fundamentals}

Measurement, considered as the process by which one extracts
information from a physical system in a world with finite resources,
is a fundamental property of quantum mechanics in our discrete field
context that we will study in this paper.

\andy{This section needs a clear treatment of {\it contextuality\/},
  and a mention of the issues for measurement with possibly illegal
  intermediate states, and degenerate eigenvalues as troublesome
  special cases.}

\gerardo{Add a statement ``Here we concentrate on a discrete quantum
  theory that uses the number systems, but not the cardinal
  probability adaptation, that we introduced in our previous
  paper~\cite{DQT2014}, that used partially transitively-ordered sets
  to address the question of probabilities.''}

In quantum mechanics, measurement is contextual, meaning that the
outcome of an experiment depends not only on the system being measured
and the choice of the measured observable, but also on the details of
the measurement process. It is also nonlocal, meaning that
correlations exist that are inconsistent with causal influences.
Classical physics, on the other hand, seems to be local and
independent of the context.  The introduction of hidden variables,
along with several important results proving their inconsistency, have
been motivated from the very early days of quantum mechanics by the
classical intuition that some (partially unknown) local context might
influence the outcome of experiments and thus invalidate traditional
quantum theory.

\paragraph{The Concept of Contextuality and its Role in the Properties
  of Candidates for Quantum Theories.}
Quantum Physics is contextual, meaning that the outcome of a
measurement (or a set of measurements) depends not only on the choice
of the measured observable(s) and on the system being measured, but
also on the details of the measurement process.  To be more precise,
as noted by Peres~\cite{peres1995quantum} and
Mermin~\cite{MerminPRL1990}, the result of measuring an observable in
a physical system must not depend on whether we measure the observable
alone, or along with arbitrary sets of mutually commuting observables.

Classical Physics, on the other hand, is usually agreed to be
independent of the context; that is, we presume that every physical
variable has a predetermined value.  The motivation for studying the
possibility that the probabilistic features of quantum mechanics can
be explained by hidden variables is the possibility that a (partially
unknown but complete) context influences the outcome of experiments.

\paragraph{Basic Features We Expect in Quantum Theories.}
To understand how much of conventional measurement theory we can
maintain in discrete quantum theories without ordered probabilities,
along with the possibility of non-trivial null-norm states, we must
critically address three pillars at the foundation of traditional
quantum theories. Many of these issues are treated in detail, e.g., in
Peres~\cite{peres1995quantum}.  The issues we shall consider are:

\begin{itemize}

\item {\it Gleason's theorem\/} tells us that for Hilbert spaces of
  dimension $>2$, the Born Rule is the \emph{only} way to assign
  consistent probabilities to the statistical prediction of a quantum
  measurement~\cite{gleason1957}.  This result excludes a very general
  class of hidden variable theories using continuity and
  probabilities.  In the conventional quantum formalism the Born rule
  provides the link between the formalism of quantum mechanics and the
  potential results of experimental observations.  In order to achieve
  similar results with finite fields, we must find a way around the
  dependence on continuity and ordered probabilities.  Replacing
  continuous-valued probabilities with discrete interval-valued
  probabilities (e.g., possible and impossible measurement outcomes)
  provides one route to the desired outcomes.

\item {\it The Kochen-Specker theorem\/} in its classical form employs
  a complicated array of measurements on a single system along with
  geometric arguments to exclude additional wide classes of hidden
  variable theories~\cite{kochenspecker1967}.  The Kochen-Specker
  theorem does not depend on statistical averages, and it is geometric
  in spirit.  (More succinct approaches can be found, e.g., in
  Peres~\cite{peres1995quantum}.)  The freedom from statistical
  averages in the Kochen-Specker methods suggests that important parts
  of the result could be independent of ordered probabilities and thus
  in fact might possess suitable analogs in finite fields.  The key is
  to understand the implications of contextuality, and here we find
  that the possibility of valid null intermediate states in discrete
  quantum theory can disrupt what would seem to be trivial
  contextuality.  To deal with this, we are compelled to explicitly
  consider, not only the initial and final resources needed to
  represent the system and the final measurement outcome, but also the
  resources needed to represent the intermediate steps in a series of
  experiments. We find that, to preserve the spirit of the
  Kochen-Specker theorem, we have to explicitly introduce and propagate
  \emph{error states} whose representation requires more than the
  available resources.

\item {\it Bell's theorem\/} reveals the intrinsic non-local nature of
  correlations in quantum physics, i.e., the nature of entanglement,
  which has no classical analog~\cite{BellBook1987}.  Bell's original
  arguments depended on continuity and probability to produce
  inequalities satisfied by any local realistic theories, as broadly
  defined by Einstein, thus quantifying nonlocality.  Since then, many
  Bell-type inequalities have been derived for different observable
  quantities, refined by the incorporation of particular experimental
  setups.  In addition, it was later
  realized~\cite{GHZ1990,CabelloPRL.86.2001} that one can derive
  Bell-type equalities encoding non-local correlations and, as we will
  see, it is this version of Bell's theorem that is generalizable to
  Discrete Quantum Theories.

\end{itemize}

All of these basic insights into the structure of traditional quantum
mechanics rely on {\it contextuality\/} and {\it nonlocality\/}: We
will argue in our conclusions that, in discrete quantum theory, we can
consistently employ both contextuality, the statement that measurement
of a quantum observable does not depend on any given second observable
provided it commutes with the first observable, and, nonlocality,
which says that spatially separated measurements in a quantum theory
can in fact be correlated, counter to classical intuitions.

\andy{
\section*{Internal note: Structure Outline}
\begin{itemize} 
\item {\bf Critical analysis of measurement in conventional theory.} 
\item {\bf Discrete Vector Space.}  $\ffd{p^2} \to \ffzd{p^2}$.
\item {\bf No go theorem.} Cannot use Real numbers in $[0,1]$.
\item {\bf Post measurement issues.} Requires explicit error states.
\item {\bf Show contextuality works.} Prove Gleason, Bell, and
  Kochen-Specker to conclude that DQT with interval-valued
  probabilities and explicit error states is sufficient to retain a
  quantum theory with contextuality and absence of local hidden
  variables.
\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Critical Analysis of the Measurement Process in CQT}

Before discussing the measurement process and the manifestations of
nonlocality and contextuality in discrete quantum mechanics, we first
review various notations brought forward from conventional quantum
theory.  Assume that a physical system is represented by a state
$\ket{\Psi}$, and that we wish to measure a physical quantity
${\cal O}$ of this system, with corresponding observable
${\mathbf O}$, whose eigenspectrum is given by
\[ {\mathbf O} \left|i\right\rangle = \lambda_{i} \left|i\right\rangle
\ . \]
Then Born's rule of CQT tells us that the probability of obtaining the
eigenvalue $\lambda_{i}$ as an outcome of the measurement is given by
\begin{eqnarray}
\begin{array}{rcccl}
{\cal P}_{\Psi}\left(\lambda_{i}\right) & = &
\displaystyle{\frac{\langle\Psi |{P}_{i} |  \Psi\rangle}
{\ip{\Psi}{\Psi}}}
& = &
\displaystyle{
\frac{\ip{\Psi}{i}\ip{i}{\Psi}}{\ip{\Psi}{\Psi}\ip{i}{i}} }
\end{array}
\ ,
 \label{prob1.eq}   
\end{eqnarray}
where ${P}_{i}$ is the projector onto the subspace generated by the
eigenvector $\left|i\right\rangle$.  We have until now assumed
non-degenerate eigenvalues.  If, for some set of states $\{k\}$, the
eigenvalue $\lambda$ is degenerate, we account for that by replacing
the simple expression for the projector $P_{i}$ by
\[ P_{\lambda} = \sum_{k=1}^{K_{\lambda}}
\frac{ \left|k\right\rangle  \left\langle k\right|}
{ \ip{k}{k}} \ ,
\]
where $K_{\lambda}$ is the degeneracy of the eigenvalue $\lambda$.

% We will assume in the following that this is taken into
% account, except for particular cases where degeneracy is explicitly
% involved in distinguishing the behavior of DQT from CQT.

One other issue that will confront us in the transition from CQT to
DQT is the presence of post-measurement states.  In CQT, the Von
Neumann projective measurement state, immediately after the
measurement of ${\cal O}$, is given in general by
\[
  \frac{P_{\lambda} \ket{\Psi}}
       {\sqrt{\langle\Psi |{P}_{\lambda} | \Psi\rangle}} \ ,
\]
where for the non-degenerate case, $P_{\lambda} \to {P}_{i}$, and so
the resulting state is just $\ket{i}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  Here we look at the theorem that says a MIXED MODE
%%%  probability theory, with discrete vectors but
%%%  real-valued probabilities, is not consistent.
\section{States, Observables, and Probability in DQT}

Following the development in the previous section, we need to
carefully define a few notions in order to describe the measurement
process in DQT. In the following, we will briefly introduce discrete
quantum theory (DQT), as defined in~\cite{geometry2013,DQT2014}, and
will highlight the main differences and contrasts with conventional
quantum theory (CQT). We will start by definining states and
observables and then spend the remainder of the section investigating
the proper notion of probability in DQT.

%%%%%%%%%%%%%%%%%
\subsection{States in DQT}

Our fundamental divergence from CQT is to replace continuous complex
amplitudes in the field of complex numbers $\C$ by discrete fields
$\ff{p^{2}}$.  If we restrict ourselves to odd primes with
$p\equiv 3\mod 4$, the fields $\ff{p}$ are exactly those for which
$x^2+1$ has no root in the field, and we can adjoin $\ComplexI$ as a
root of $x^2+1$ to the field $\ff{p}$.  For a given element
$\alpha \in \ff{p^2}$, we define the equivalent of complex conjugation
as the map $\alpha\mapsto\alpha^p$, which we may write as
$\alpha^*=\alpha^p$. The resulting extended field is isomorphic to
$\ff{p^2}$ and is a realization of discrete complex numbers suitable
for quantum mechanical calculations.

Let us start by defining a vector space $\ffd{p^{2}}$ of
$d$-dimensional vectors with elements in $\ff{p^{2}}$, where the
conjugate transpose is defined in the natural way giving us the notion
of a dual vector $\bra{\Psi}$ for every vector
$\ket{\Psi}\in\ffd{p^2}$ as well as unitary operators.  Next we
propose the Hermitian dot product defined as the map from
$\ffd{p^2}\times\ffd{p^2}$ to $\ff{p^2}$ given by
$(\ket{\Psi},\ket{\Phi})\longmapsto \braket{\Phi}{\Psi}$.  Notice that
this product is technically not an inner product because there are
vectors $\ket{\Psi}$ other than the zero vector whose ``norm''
$\braket{\Psi}{\Psi}$ vanishes.  We therefore exclude such cases by
moving to the domain $\ffzd{p^{2}}$, where the ${}^{*}$ indicates the
exclusion of null vectors; that is we consider
$\ket{\Psi}\in\ffzd{p^{2}}$, where
\[\ffzd{p^{2}}=\left\{
  \ket{\Psi}\in\ffd{p^{2}}\mid\ip{\Psi}{\Psi}\ne 0\right\} \ . \]

\amr{we want to emphasize that it is not sufficient to remove these
  null vectors once and for all at the beginning of time; it is
  possible to wrap around during calculation (unitary evolution as
  well as projection to post-measurement state) and produce a null
  state from a well-defined state. In the rest of the paper (say where
  exactly) we will arrange for such invalid operations to be detected
  and dealt with properly.}

\gerardo{1) When the eigenvalues are non-degenerate there is never a
  problem; 2) The problem is a manifestation of the lack of
  resources. Had we used a larger p from the start, this situation
  would have been avoided.}

\andy{I definitely agree. Gerardo and I discussed at length whether
  the decision to "fix the p in advance" could be relaxed, and, though
  that is very complicated, I think that we make a very good
  connection to the previous paper if we emphasize the role of the
  size of p and the RESOURCES.  Without changing p in the measurement
  PROCESS, it is still legitimate to state that a glitch in the
  PROCESS can arguably come directly from the RESOURCES allocated.
  Then our overall story is that DQT permits the splitting-apart of
  "computability" in quantum theories into state-representation and
  measurement resources.  So I'd say, if anything, such an
  interpretation needs to be expanded and made very clear.  Then the
  readers of the sequence of papers know exactly who we are and what
  our narrative implies about computability and quantum theory in
  general.}

\amr{Long discussion about whether to allow zero norm states as
  intermediate values. Also discussion about whether we are computing
  with states or equivalence classes of states; in the latter case,
  all zero-norm states should be equivalent.}

%%%%%%%%%%%%%%%%%
\subsection{Unitary and Hermitian operators in DQT}

After we define the state vectors and the Hermitian dot product, we
are ready to define unitary and Hermitian operators representing time
evolutions and observables, respectively. All unitary operators can
represent time-evolution operators. Because a unitary operator~$\mathbf{U}$
preserves norm, a physical state~$\ket{\Psi}$ always evolves to
another physical state~$\mathbf{U}\ket{\Psi}$ according to $\mathbf{U}$.\footnote{Although some unitary operators might not be induced by a Hamiltonian,
we might discuss further in our upcoming papers.}

The situation for observables is more delicate. As discussed in section
3, the measurement result of an observable~$\mathbf{O}$ is a real
number and a eigenvalue of $\mathbf{O}$; the post-measurment state
is a physical state as well as an eigenvector of $\mathbf{O}$. However,
a Hermitian operator~$\mathbf{H}$ over $\ff{p^{2}}$ may not be
qualified for an observable because $\mathbf{H}$ may not have suitable
eigenvalues and eigenvectors to define the measurement precess, or
equavalently $\mathbf{H}$ is not unitarily diagonalizable, for the
following reasons:
\begin{enumerate}
\item \label{enu:eigenvalueCount}$\mathbf{H}$ may lack of eigenvalues.
\\
\yutsung{No eigenvalue is a problem, but how to clearly say why no
enough eigenvalue is a problem?}\\
Formally, the total multiplicity of eigenvalues of $\mathbf{H}$ in
$\ff{p^{2}}$ may be less than $d$, where the multiplicity of an
eigenvalue $\lambda$ is $K_{\lambda}$ means that $\left(x-\lambda\right)^{K_{\lambda}}$
is a factor of the characteristic polynomial 
\begin{equation}
\det\left(\mathbf{A}-x\mathds{1}\right)\textrm{ ,}\label{eq:characteristic}
\end{equation}
while $\left(x-\lambda\right)^{K_{\lambda}+1}$ is not a factor of
the characteristic polynomial. This happens because $\ff{p^{2}}$
is not algebraically closed~\cite{DummitFoote2004} so that the solutions
of the characteristic polynomial may be in an proper extension field
of $\ff{p^{2}}$. For example, consider a Hermitian matrix 
\[
\mathbf{H}_{1}=\begin{pmatrix}-1 & -\ComplexI & 0\\
\ComplexI & 1 & -\ComplexI\\
0 & \ComplexI & 1
\end{pmatrix}
\]
whose characteristic polynomials over $\ff{9}$ are
\begin{eqnarray*}
\det\left(\mathbf{H}_{1}-x\mathds{1}\right) & = & 2x^{3}+x^{2}+2
\end{eqnarray*}
which have no solution in $\ff{9}$ so that their total multiplicities
are 0 less than 3. In this case, $\mathbf{H}_{1}$ should not be an
observable because there is no eigenvalue as any measurement result. 
\item \label{enu:degeneracy}\yutsung{The same. How to say clearly why
no enough eigenvector is a problem?}\\
The dimension of an eigenspace may be less than the multiplicity of
its eigenvalue. For example, consider a Hermitian matrix 
\[
\mathbf{H}_{2}=\begin{pmatrix}-1 & -1-\ComplexI\\
-1+\ComplexI & 0
\end{pmatrix}
\]
Over $\ff{9}$, its only eigenvalue is $1$ of multiplicity $2$.
The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\begin{pmatrix}1\\
-1+\ComplexI
\end{pmatrix}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$
are not diagonalizable over $\ff{9}$. If $\mathbf{H}_{2}$ were an
observable, $\mathbf{H}_{2}$ would always have the outcome of measurement
$1$ with the post-measurement state $\begin{pmatrix}1\\
-1+\ComplexI
\end{pmatrix}$. However, only operator always producing $1$ is the identity operator
which change no state. Therefore, $\mathbf{H}_{2}$ may not be intuitively
as an observable.\\
In order to understand this non-diagonalability, we can diagonalize
them in $\C$. The eigenvalues of $\mathbf{H}_{2}$ in $\C$ are $1$
and $-2$. 
\begin{eqnarray*}
-2 & \equiv & 1\left(\bmod p\right)
\end{eqnarray*}
In another word, two eigenvalues in $\C$ map to only one eigenvalue
of multiplicity $2$ in $\ff{9}$, and the corresponding two eigenspaces
with dimension $1$ in $\C$ map to one eigenspace still with dimension
$1$ in $\ff{9}$. 
\item \label{enu:orthonormal}Some eigenvectors are zero-norm so that $\mathbf{H}$
may be diagonalizable, but not unitarily diagonalizable. In this case,
the corresponding eigenvalue~$\lambda$ of a Hermitian matrix may
not be in $\ff{p}$.\\
For example, consider a Hermitian matrix~$\mathbf{H}_{3}$ 
\[
\mathbf{H}_{3}=\begin{pmatrix}-1 & -1-\ComplexI\\
-1+\ComplexI & 1-
\end{pmatrix}
\]
Over $\ff{9}$, the eigenvalues and eigenvectors of $\mathbf{H}_{3}$
are $-1-\ComplexI$ with $\begin{pmatrix}1\\
-1-\ComplexI
\end{pmatrix}$ and $-1+\ComplexI$ with $\begin{pmatrix}1\\
1+\ComplexI
\end{pmatrix}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the
eigenvectors are all zero-normed.\\
If we diagonalize $\mathbf{H}_{3}$ in $\C$, we have the eigenvalues
of $\mathbf{H}_{3}$ in $\C$ are $-1\pm\sqrt{2}$. If we extend the
modulo $p$ to algebraic number by 
\[
a\equiv b\left(\bmod p\right)\Leftrightarrow\pm\sqrt{a}\equiv\pm\sqrt{b}\left(\bmod p\right)
\]
then 
\begin{eqnarray*}
-1\pm\sqrt{2} & \equiv & -1\pm\ComplexI\left(\bmod p\right)
\end{eqnarray*}
In another word, although the extended modulo $p$ operation respects
any field operations and roots, it does not respect the complex conjugate
so that any definition depend on the complex conjugate may not be
preserved when we map them into finite fields.
\end{enumerate}
As long as there exists a non-zero-norm eigenbasis of $\mathbf{H}$,
$\mathbf{H}$ has an orthonormal eigenbasis~\cite{grove2002classical}.
Therefore, these are the only reasons that $\mathbf{H}$ may not be
unitarily diagonalizable, or an observable. Besides, some unitary
operators are not unitarily diagonalizable as well although they are
still time-evolution operators.

\yutsung{
I don't know whether there is a relation between the occurrence of
zero norm post-measurement states and anomalies in the list of possible
observables, especially we have already required any observables must
be unitarily diagonalizable.

I am sure I have asked Prof. Lunts ``what we can say for the eigenvalues
of Hermitian matrices over finite fields,'' and he seems not sure.
I guess I also asked Prof. Thurston the same question, but I am not
sure...
}

\andy{We want to see where the argument of {\em compatible observables}
  fits in.}

%%%%%%%%%%%%%%%%%
\subsection{Considering Continuous Probabilities}

As seen in the previous section, the CQT Born rule gives a physical
meaning to the state vectors, which can be seen as holding the
information regarding outcomes of measurements.  Given a state
$\ket{\Psi}$, the measurement of a physical quantity will result in
one of some number of mutually exclusive outcomes $\lambda$.

It is worth asking whether the state vectors in DQT can contain
probabilistic information about measurement outcomes.  When the Born
rule is literally translated directly into the finite field framework,
i.e., so the quantity ${\cal P}_{\Psi}(\lambda)$ is in the field
$\ff{p}$, then ${\cal P}$ can no longer be considered as a probability
because it cannot be interpreted as a real number in the interval
$[0,1]$, or as any other transitively ordered set.  Thus in order to
get a rule in DQT for extracting information from the state vectors,
the Born rule must be modified.

Thus we are led first to consider the most obvious extension, which is
to postulate the existence of a consistent function $\dpt$ with
outcomes compatible with CQT, that is
\[\dpt\colon \ffzd{p^2}\times \ffzd{p^2}
\longrightarrow [0,1]\ . \]

For the outcomes of this new rule to truly be interpreted as
probabilities, the rule $\dpt$ must satisfy certain properties.
First, probabilities must satisfy a normalization requirement:
\begin{description}
\item[(i)]  For any orthonormal basis $\{\ket{i}\}$ and any state
  $\ket{\Psi}$, $\displaystyle \sum_{i=0}^{d-1} \dpt(\ket{\Psi},\ket{i})=1$.
\end{description}
That is, the sum of probabilities for a complete set of mutually
exclusive outcomes must be 1.  To motivate the next requirement,
consider the state $\alpha\ket{0}+\beta\ket{1}$ in the vector space
spanned by $\ket{0}$ and $\ket{1}$.  We can embed this vector subspace
in the larger $d$-dimensional space spanned by $\ket{0}$, $\ket{1}$,
\ldots, $\ket{d-1}$ and view our state in the larger vector space,
i.e., view $\alpha\ket{0}+\beta\ket{1}$ as
$\alpha\ket{0}+\beta\ket{1} + 0\ket{2} + \cdots+ 0\ket{d-1}$.  The
probabilities corresponding to outcomes $\ket{0}$ and $\ket{1}$ should
not depend on whether we are viewing the state in the original
two-dimensional subspace or the larger one. Thus, in light of property
({\bf i}), the probabilities corresponding to outcomes $\ket{2}$,
\ldots, $\ket{d-1}$ should all be zero. This suggests the following
necessary condition:
\begin{description}
\item[(ii)]
If $\braket{\Phi}{\Psi}=0$ then $\dpt(\ket{\Psi},\ket{\Phi})=0$.
\end{description}
The final property we require of a rule for deriving probabilities is
that it be basis independent:
\begin{description}
\item[(iii)]
$\dpt(U\ket{\Phi},U\ket{\Psi})=\dpt(\ket{\Phi},\ket{\Psi})$ 
where $U$ is any unitary map.
\end{description}

In CQT, Gleason's theorem~\cite{gleason1957} shows that properties
similar to these are sufficient to uniquely identify the Born rule as
the only consistent rule for defining probabilities from states when
$d>2$.  If we adopt the natural conditions ({\bf i}), ({\bf ii}), and
({\bf iii}) in DQT, we find from the following theorem that a map
$\dpt$ satisfying these conditions does not exist.

%%%%%%%%%%%%%%%%%
\subsection{A No-Go Theorem}

We will fill out our arguments by introducing a no-go theorem that
explains why it is impossible in DQT to incorporate into Born's rule a
continuous real probability in the interval $[0,1]$.

\begin{theorem}
\label{theorem1}
There is no map $\dpt\colon \ffzd{p^2}\times \ffzd{p^2}
\longrightarrow [0,1]$ satisfying properties ({\bf i}), ({\bf ii}),
and ({\bf iii}) when $d> 3$.
\end{theorem}
%
\begin{proof}
  Assume such a map $\dpt$ satisfying all three properties exists.
  Consider the state
\[
\ket{\Psi}=\alpha\big(\ket{0} + \ket{1} + \ket{2} + \beta\ket{3}\big)
\]
expressed in terms of orthonormal vectors, where $\beta\in \ff{p^2}$
is chosen so that $\left|\beta\right|^2=p-1$ and $\alpha\in\ff{p^2}$
is a constant such that $\ket{\Psi}$ is normalized.  Let
$\ket{\Phi}= \ket{1} + \ket{2} + \beta\ket{3}$. Note that $\ket{\Phi}$
is normalized in $\ff{p}$.  We can write our original state
$\ket{\Psi}$ as $\ket{\Psi}=\alpha\big(\ket{0}+\ket{\Phi}\big)$ The
vectors $\ket{0}$ and $\ket{\Phi}$ are orthonormal and so are part of
some larger orthonormal basis. Thus by properties ({\bf i}) and ({\bf
  ii}) we have
\begin{equation}
1= \dpt\big(\ket{\Psi},\ket{0}\big) +  \dpt\big(\ket{\Psi},\ket{\Phi}\big). \label{prob1}
\end{equation}
Let $U$ be the unitary map that simply permutes the orthonormal
vectors $\ket{0}$ and $\ket{\Phi}$.  Note that $\ket{\Psi}$ is
invariant under $U$, so invoking property ({\bf iii}), we have
\[
\dpt\big(\ket{\Psi},\ket{0}\big)=\dpt\big(U\ket{\Psi},U\ket{0}\big) = 
   \dpt\big(\ket{\Psi},\ket{\Phi}\big) \ .
\]
This along with equation (\ref{prob1}) gives
\[
1= \dpt\big(\ket{\Psi},\ket{0}\big) +  \dpt\big(\ket{\Psi},\ket{0}\big),
\]
so
\begin{equation}
\label{prob2}
\dpt\big(\ket{\Psi},\ket{0}\big)=\dpt\big(\ket{\Psi},
   \ket{\Phi}\big)=\frac{1}{2} \in [0,1] \ .
\end{equation}

For $i=0,1,2$ let $U_i$ be the unitary map that permutes the basis
vectors $\ket{0}$ and $\ket{i}$ and acts as the identity for the rest.
Note that $\ket{\Psi}$ is invariant under $U_i$. So again by property
({\bf iii}) we have
\[
\dpt\big(\ket{\Psi},\ket{i}\big) =\dpt\big(U_i\ket{\Psi},U_i\ket{0}\big)=
\dpt\big(\ket{\Psi},\ket{0}\big) = \frac{1}{2}
\]
for $i=0,1,2$.  These probability assignments are inconsistent with
the requirement that the probabilities for orthogonal outcomes add up
to 1. By property ({\bf i})
\begin{align*}
  1&=\dpt\big(\ket{\Psi},\ket{0}\big)+ \dpt\big(\ket{\Psi},\ket{1}\big) + 
     \dpt\big(\ket{\Psi},\ket{2}\big)+ \dpt \big(\ket{\Psi},\ket{3}\big)\\
  &=\frac{1}{2}+\frac{1}{2}+\frac{1}{2}+\dpt\big(\ket{\Psi},\ket{3}\big)\\
  &\geq \frac{3}{2},
\end{align*}
so we have a contradiction. The assumption of a satisfactory map
$\dpt$ is thus false. $\Box$
\end{proof}
(It should be pointed out that the argument above explicitly uses
states from a vector space of four dimensions or larger, and thus does
not hold if the largest vector space one can consider has dimension
$d\le 3$.  But it does hold for any system that, for example, contains
more than a single qubit.)

What are the implications of this theorem?  Intuitively one might
think that the lack of an order on the field elements is the main
obstacle to extracting probabilities from DQT, but the above result
shows that this is not the case.  Even supplementing the field
elements with an ordering does not allow for a rule that satisfies the
three properties above.  And any other scheme for extracting
probabilities from quantum mechanics over a finite field will violate
one of the three properties above.

We next observe that one way out of this dilemma is to define a
framework for quantum measurement in DQT that is based not upon
probabilities but upon discrete interval-valued probabilities.

\gerardo{There is a paper by Mermin, Quantum Mysteries
  Revisited~\cite{MerminPRL1990}, that could be used profitably in the
  next arguments.  See also John's paper, section ``GHZ
  Experiment.''}

%%%%%%%%%%%%%%%%%
\subsection{Interval-Valued Probabilities for DQT}

\yutsung{
It seems that almost everything currently in this section should move to Section 5, because they are already focus on the measurement process in DQT, especially $\dpr \left(\ket{\Psi},\ket{\Phi}\right)$ should be intuitively corresponding to ${\cal P}_{\Psi}\left(\lambda_{i}\right)$ in CQT. Or we may combine Section 4.5 and Section 5.1 into one section.

If we want to keep Section 4.5 and Section 5.1 separately, we may try to focus on the definition of Interval-Valued Probabilities and these algebraic relation, like =, 0, 1, and +. However, the readers may not know why they need these algebraic relation before we define the measurement process...
}

In order to write down the analog of the CQT Born rule and
quantum measurement process for DQT, we must explicitly define a
corresponding discrete measurement framework.  To this end, consider
an orthogonal basis $\{\left|i\right\rangle\}$ of $\ffzd{p^2}$.  In
this basis, two arbitrary vectors can be written in the form
\begin{equation}
\ket{\Psi}=\sum_{i=0}^{d-1}~\alpha_{i}\left|i\right\rangle \ ,\
\ket{\Phi}=\sum_{i=0}^{d-1}~\beta_{i}\left|i\right\rangle , 
\end{equation}
with $\alpha_{i}$ and $\beta_{i}$ elements of the field $\ff{p^{2}}$.
The Hermitian product in our discrete number system is thus 
reducible to the form
 \begin{equation}
   \ip{\Phi}{\Psi}=\sum_{i=0}^{d-1}~{\beta_{i}}^{p}~\alpha_{i}^{\;}
     \ .
\label{innerprod}  
\end{equation}

%% Needed?? ~\cite{DQT2014}.. ~\cite{grove2002classical}

These issues are all crucial for DQT because in the discrete domain we
do not have transitive ordered probabilities defined on the real
numbers.  Furthermore, although the physical state $\ket{\Psi}$ before
the measurement belongs to $\ffzd{p^2}$, the post-measurement state
may not belong to $\ffzd{p^2}$ in the case of {\it degenerate
  eigenvalues\/}.

This leads us to introduce a modified Born's rule, with
values in discrete interval-valued probabilities, for the study of the
properties that DQT shares with CQT but not with classical theories.
It will turn out that in order to accommodate the anomalous situation
where post-measurement states do not belong to $\ffzd{p^2}$, we
explicitly detect such invalid intermediate states and cause them to
halt the entire computation immediately.

\amr{I think the previous two paragraphs could be even more clear if
  we said the following. First we talk about the no-go theorem and say
  that we must go to ``interval-valued probabilities.'' Then say we
  will use two intervals {\it (possible, impossible) \/}. Then explain
  that a measurement operation is a \emph {partial function } that
  takes a current state (non-null vector) and an observable ${\cal O}$
  and as explained next produces \emph{three} things when defined.
  Generally if we measure observable ${\cal O}$ of quantum state
  $\ket{\phi}$, then (i) with interval-value probability $p_i$, (ii)
  the result of the measurement will be eigenvalue $\lambda_i$, and
  (iii) the quantum state will collapse to the state
  $\ket{\psi}_i$. In the case the post-measurement state would be null
  because of wrapping around that might occur with degenerate
  observables the entire measurement operation is
  \emph{undefined}. Otherwise the result is the triple of probability,
  eigenvalue, and post-measurement state.  Note that composition of
  measurement operations is only defined if both measurement
  operations are defined. In particular, if is possible that two
  commuting observables ${\cal O}_1$ and ${\cal O}_2$ could be
  measured in one order but not the order if one of the intermediate
  steps is undefined.}

 Since discrete quantum theories do not have orderable fields, and thus
lack orderable probabilities, we must discover a way to understand how
Born's rule could manifest itself in a consistent discrete theory.

To begin our study of discrete theory, we define a map $\dpr $ that
will play the role of a discrete Born rule, with the replacement of
real-valued probabilities by the two tags 'impossible' and 'possible':
\[\dpr :\ffzd{p^{2}}\times\ffzd{p^{2}}\rightarrow\mathscr{L}_{2} = \left\{
\text{impossible},\text{possible}\right\} , \]
Thus $\dpr $ can be defined in the possibility field $\mathscr{L}_{2}$ 
as
\begin{equation}
\dpr \left(\ket{\Psi},\ket{\Phi}\right)=
\left\{ \begin{array}{r@{\textrm{, if }}l}
\textrm{possible} & \ip{\Psi}{\Phi}\ne 0\\
\textrm{impossible} & \ip{\Psi}{\Phi}=0
\end{array} \right. \ .
\label{eq:modality}
\end{equation}

% \begin{equation}
% \dpr \left(\ket{\Psi},\ket{\Phi}\right)=\begin{cases}
% \text{possible} & \textrm{, if }\ip{\Psi}{\Phi}\ne 0\\
% \text{impossible} & \textrm{, if }\ip{\Psi}{\Phi}=0
% \end{cases} \ .
% %\label{eq:modality}
% \end{equation}

% {\bf Remark}: The natural occurrence of null-norm intermediate states
% in examples of two-operator measurement systems used to test
% contextuality will lead us to the requirement for a three-valued
% logic, $\mathscr{L}_{3}$, with a possibility of the value
% $\text{inconsistent}$.  For clarity of exposition, we employ the
% two-valued modal logic $\mathscr{L}_{2}$ until absolutely necessary.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Measurement Process in DQT}

%%%%%%%%%%%%%%%%%
\subsection{Basic Measurement}

\amr{Adapt the following to DQT}

Assume that a physical system is represented by a state $\ket{\Psi}$,
and that we wish to measure a physical quantity ${\cal O}$ of this
system, with corresponding observable ${\mathbf O}$, whose
eigenspectrum is given by
\[ {\mathbf O} \left|i\right\rangle = \lambda_{i} \left|i\right\rangle
\ . \]
Then Born's rule of CQT tells us that the probability of obtaining the
eigenvalue $\lambda_{i}$ as an outcome of the measurement is given by
\begin{eqnarray}
\begin{array}{rcccl}
{\cal P}_{\Psi}\left(\lambda_{i}\right) & = &
\displaystyle{\frac{\langle\Psi |{P}_{i} |  \Psi\rangle}
{\ip{\Psi}{\Psi}}}
& = &
\displaystyle{
\frac{\ip{\Psi}{i}\ip{i}{\Psi}}{\ip{\Psi}{\Psi}\ip{i}{i}} }
\end{array}
\ ,
 \label{prob1.eq}   
\end{eqnarray}
where ${P}_{i}$ is the projector onto the subspace generated by the
eigenvector $\left|i\right\rangle$.  We have until now assumed
non-degenerate eigenvalues.  If, for some set of states $\{k\}$, the
eigenvalue $\lambda$ is degenerate, we account for that by replacing
the simple expression for the projector $P_{i}$ by
\[ P_{\lambda} = \sum_{k=1}^{K_{\lambda}}
\frac{ \left|k\right\rangle  \left\langle k\right|}
{ \ip{k}{k}} \ ,
\]
where $K_{\lambda}$ is the degeneracy of the eigenvalue $\lambda$.

%%%%%%%%%%%%%%%%%
\subsection{Degeneracy and Post-Measurement States}

\amr{Explain that problem and need to deal with errors}

% We will assume in the following that this is taken into
% account, except for particular cases where degeneracy is explicitly
% involved in distinguishing the behavior of DQT from CQT.

One other issue that will confront us in the transition from CQT to
DQT is the presence of post-measurement states.  In CQT, the Von
Neumann projective measurement state, immediately after the
measurement of ${\cal O}$, is given in general by
\[
  \frac{P_{\lambda} \ket{\Psi}}
       {\sqrt{\langle\Psi |{P}_{\lambda} | \Psi\rangle}} \ ,
\]
where for the non-degenerate case, $P_{\lambda} \to {P}_{i}$, and so
the resulting state is just $\ket{i}$.

\amr{
Assume O1 and O2 are compatible:
f([O1.O2],psi) = f([O2.O1],psi)

In CQT,
f(O1,f(O2,psi)) = f([O1.O2],psi) = f([O2.O1],psi) = f(O2,f(O1,psi))

In DQT, it is possible that:
f(O1,f(O2,psi)) /= f(O2,f(O1,psi))
because one of them, say f(O1,psi) wraps in the field
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Now we need to look at the DQT measurement process
%%%  and whether we can get around the limitations.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Gleason's Theorem and the Born Rule, etc.
\section{Contextuality and Non-Locality in DQT}

%%%%%%%%%%%%%%%%%
\subsection{Gleason's Theorem in DQT} The Born rule is the \emph{only}
way to assign a probability in conventional quantum theory because of
Gleason's theorem.  We now show that $\dpr $ defined in
Eq. (\ref{eq:modality}) is an example of a properly defined Born rule
in the discrete theory because $\dpr $ also satisfies the closest
analog of Gleason's Theorem that we can construct.

Following the standard axioms for Gleason's
theorem~\cite{peres1995quantum}, we introduce discrete axioms that
differ in only one significant instance from the classical ones:
\begin{eqnarray}
 & \bullet & \textrm{For any orthogonal basis }\left\{
  \left| n \right\rangle \right\}
  _{n=0}^{d-1}\subset\ffzd{p^{2}}\textrm{, and
  }\label{enu:total-probability-DQT(I)}\\ & &
  \ket{\Psi}\in\ffzd{p^{2}}\textrm{, at least one of\ }
  \dpr \left(\ket{\Psi},\ket{n}\right) = \text{possible.}\nonumber \\ &
  \bullet & \textrm{For any orthogonal basis }
\left\{  \left| n \right\rangle
\right\}_{n=0}^{d-1}\subset\ffzd{p^{2}}\nonumber \\ & &
 \textrm{and a particular\ }\ket{n'}\in\left\{ \left| n \right\rangle \right\}
  _{n=0}^{d-1}\textrm{, }\nonumber \\ & &
  \dpr\big(\ket{n'},\ket{n'}\big)=\text{possible and\ }
   \label{enu:particular-vector-DQT(I)}\\ & &
  \dpr\big(\ket{n'},\ket{n}\big)=\text{impossible for any }n\ne  n'
   \textrm{. }\nonumber \\ & \bullet & \textrm{For any vector  }
   \ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}
  \textrm{, and  }\gamma\in\ff{p^{2}}\backslash\left\{ 0\right\} 
  \textrm{, }\nonumber
  \\ & &
  \dpr (\ket{\Psi},\ket{\Phi})=\dpr (\gamma\ket{\Psi},\ket{\Phi}) = 
    \dpr (\ket{\Psi},\gamma\ket{\Phi}) \textrm{. }
  \label{enu:parallel-DQT(I)}\\
 & \bullet & \textrm{For any vector
  }\ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}
  \textrm{, }\nonumber \\ & &
  \textrm{and }U\textrm{ is a }d\textrm{-by-}d
  \textrm{ unitary matrix over }\ff{p^{2}}\textrm{, }
  \label{enu:unitary-DQT(I)}\\ & &
  \textrm{i.e. , }U^{\dagger}U=I\textrm{, then  }
   \dpr (\ket{\Psi},\ket{\Phi})=\dpr (U\ket{\Psi},U\ket{\Phi})\textrm{. }\nonumber
\end{eqnarray}
Because there is no possibility for continuity in the discrete theory,
we have substituted the condition (\ref{enu:unitary-DQT(I)}) for the
conventional continuity axiom in Gleason's Theorem.

%%%%%%%%%%%%%%%%%
\subsection {The Kochen-Specker Theorem in DQT}
The essence of the Kochen-Specker theorem is to ask if it is possible,
for a fixed $\ket{\Psi}\in\ffzd{p^{2}}$, to have another function
$v\left(\ket{\Phi}\right)$ playing the role of
$\dpr \left(\ket{\Psi},\ket{\Phi}\right)$ but failing to satisfy any
single one of the conditions in the set
(\ref{enu:total-probability-DQT(I)},\ref{enu:particular-vector-DQT(I)},
\ref{enu:parallel-DQT(I)},\ref{enu:unitary-DQT(I)}) and to show that
this cannot be true.

% \begin{description} 
{\bf The Theorem \/}: For $d \ge 3$, there is
  no function $v:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$ such that
\begin{eqnarray}
 & \bullet & \textrm{For any orthogonal basis }\left\{
  \left|n\right\rangle \right\}
  _{n=0}^{d-1}\subset\ffzd{p^{2}}\textrm{, }\nonumber \\ & &
  \textrm{exactly one of }\left\{ v\left(\left|n\right\rangle
  \right)\right\} _{n=0}^{d-1}
  \text{ is possible.}
  \label{enu:total-probability-DQT(I)-KS}
\end{eqnarray}
%\end{description}

\begin{table*}
\begin{tabular}{|c|c|c|c|c|c|}
\hline Possible & \multicolumn{4}{c|}{Impossible} & The first vector
is possible because of\tabularnewline \hline $001$ & $100$ & $010$ &
$110$ & $1\bar{1}0$ & arbitrary choice of $z$ axis\tabularnewline
\hline $101$ & $\bar{1}01$ & $010$ & & & arbitrary choice of $x$ vs
$-x$\tabularnewline \hline $011$ & $0\bar{1}1$ & $100$ & & & arbitrary
choice of $y$ vs $-y$\tabularnewline \hline $1\bar{1}{-}$ &
$\bar{1}1{-}$ & $110$ & ${+}0\bar{1}$ & $0{+}1$ & arbitrary choice of
$x$ vs $y$\tabularnewline \hline $10{-}$ & ${+}0\bar{1}$ & $010$ &
${+}\bar{1}\bar{1}$ & & orthogonality to 2nd and 3rd
vectors\tabularnewline \hline ${+}11$ & $0\bar{1}1$ &
${+}\bar{1}\bar{1}$ & $\bar{1}0{-}$ & & orthogonality to 2nd and 3rd
vectors\tabularnewline \hline ${+}01$ & $010$ & $\bar{1}0{-}$ &
$\bar{1}\bar{1}{-}$ & & orthogonality to 2nd and 3rd
vectors\tabularnewline \hline $11{-}$ & $1\bar{1}0$ &
$\bar{1}\bar{1}{-}$ & $0{+}\bar{1}$ & & orthogonality to 2nd and 3rd
vectors\tabularnewline \hline $01{-}$ & $100$ & $0{+}\bar{1}$ &
$\bar{1}{+}\bar{1}$ & & orthogonality to 2nd and 3rd
vectors\tabularnewline \hline $1{+}1$ & $\bar{1}01$ &
$\bar{1}{+}\bar{1}$ & $0\bar{1}{-}$ & & orthogonality to 2nd and 3rd
vectors\tabularnewline \hline
\end{tabular}\protect\caption{\label{tab:proof-of-K-S}Proof of the Kochen-Specker theorem in DQT(I)(I)
in 3 dimensions.}
\end{table*}

\begin{proof}

  Following the general structure in~\cite{peres1995quantum}, we will
  prove by contradiction that the theorem holds for primes (with
  $p \equiv 3 \mod 4$) with $p > 3$ ~\footnote{\label{fn:p>3}When
    $p=3$, the Kochen-Specker theorem still holds, but the proof is
    longer.}. Suppose $v$ exists, and consider the set of all vectors
  with entries in $\left\{ 0,\pm1,\pm1\pm\ComplexI\right\} $. Then the
  steps in the proof can be read off from Table
  \ref{tab:proof-of-K-S}.  In each cell in Table
  \ref{tab:proof-of-K-S}, the string $xyz$ represents a state vector,
  where $x$, $y$, and $z$ can be \{ $0$, $1$, $\bar{1}\equiv -1,$
  ${+} \equiv (1+\ComplexI)$, ${-} \equiv (1-\ComplexI)$ \}, and
\[
v\left( xyz \right)= \{\textrm{possible}\, \mbox{\it or\/}\,
\textrm{impossible} \ , \]
depending on its column.  Examining the table from top to the bottom,
we will eventually get a contradiction.  The set of vectors are
invariant under interchanges of the $x$, $y$, and $z$ axess.  Hence,
we can assume
$v\left(100\right)=v\left(010\right)=\textrm{impossible}$ and
$v\left(001\right)=\textrm{possible}$.  Furthermore, $110$ and
$1\bar{1}0$ are orthogonal to $001$, so that
$v\left(110\right)=v\left(1\bar{1}0\right)=\textrm{impossible}$.  A
similar argument may be used to construct the second, third, and
fourth rows.  After we know enough values of
$v\left(\ket{\Psi}\right)$, we can find that $10{-}$, ${+}0\bar{1}$,
and $010$ is an orthogonal basis, and we already know that
$v\left({+}0\bar{1}\right)=v\left(010\right)=\textrm{impossible}$, so
$v\left(10{-}\right)=\textrm{possible}$.  Following a similar
procedure, we can continue evaluating the entire content of Table
\ref{tab:proof-of-K-S}.  We can see that $100$, $0{+}1$, and
$0\bar{1}{-}$ form an orthogonal basis, but we already know
$v\left(100\right)=v\left(0{+}1\right)=v\left(0\bar{1}{-}\right)
=\textrm{impossible}$.
This contradicts our initial assumptions. Therefore, there is no
function $v$ satisfying the conditions.
\end{proof}
Notice that this proof applies for almost all $p$, and, despite
the exclusive appearance of integers in $\ff{p^{2}}$ throughout the
computation, there are no occurrences of wrapping back to zero in the
number field.

%%%%%%%%%%%%%%%%%
\subsection {Bell's Theorem in DQT}

We conclude with a discrete quantum theory version of Bell's theorem,
showing that non-locality persists in the discrete theory, and no
hidden variable theories are consistent with our modal-logic-valued
operations.  We exploit methods such as those of Greenberger, Horne,
and Zeilinger~\cite{GHZ1990} that do not rely on inequalities, and so
allow us to escape the disadvantages of lack of orderability of
discrete field values (see, e.g, \cite{MerminPRL1990,peres1995quantum}).

First, let $\mathbb{O}_{p^{2}}^{d}$ be the set of all observables for
$\ff{p^{2}}^{d}$, and let $\Delta\left(\mathcal{O}\right)$ be the set
of eigenvalues of an observable~$\mathcal{O}$. Then, the Born rule in
DQT(I) $\dpr $ asserts that given $\ket{\Psi}\in\ffzd{p^{2}}$ and an
observable~$\mathcal{O}\in\mathbb{O}_{p^{2}}^{d}$ whether a
eigenvalue~$\lambda\in\Delta\left(\mathcal{O}\right)$ is a possible
measurement result or not. Hence, a hidden variable theories
consistent with $\dpr $ can be described by a function~$w$ giving
directly the measurement result~$\lambda=w(\ket{\Psi},\mathcal{O})$
and satisfying condition (\ref{eq:consistent}).
\begin{eqnarray}
 & \bullet & \textrm{For any }\ket{\Psi}\in\ffzd{p^{2}}\textrm{, }\mathcal{O}\in\mathbb{O}_{p^{2}}^{d}\textrm{, }\nonumber \\
 &  & w(\ket{\Psi},\mathcal{O})\in\Delta\left(\mathcal{O}\right)\textrm{. Moreover, }\nonumber \\
 &  & \textrm{if }\mathcal{H}\textrm{ is an eigenspace of }\mathcal{O}\textrm{ corresponding to }w\left(\ket{\Psi},\mathcal{O}\right)\textrm{, }\nonumber \\
 &  & \textrm{then }\dpr \left(\ket{\Psi},\mathcal{H}\right)=\textrm{possible .}\label{eq:consistent}
\end{eqnarray}

Second, local observables $\mathcal{O}'$ and $\mathcal{O}''$ are
represented by the observables in subspace $\mathbb{O}_{p^{2}}^{d'}$
and $\mathbb{O}_{p^{2}}^{d''}$ and be considered as observables in the
whole space by applying tensor product, $\mathcal{O}'\otimes Id_{d''}$
and $Id_{d'}\otimes\mathcal{O}''$. Then, condition (\ref{eq:locality})
\begin{eqnarray}
 & \bullet & \textrm{For any }d',d''\in\N\textrm{, }d=d'd''\textrm{, }\mathcal{O}'\in\mathbb{O}_{p^{2}}^{d'}\textrm{, }\mathcal{O}''\in\mathbb{O}_{p^{2}}^{d''}\textrm{. }\nonumber \\
 &  & \textrm{If }\mathcal{H}'\textrm{ is an eigenspace of }\mathcal{O}'\otimes Id_{d''}\textrm{, }\nonumber \\
 &  & \textrm{and }\mathcal{H}''\textrm{ is an eigenspace of }Id_{d'}\otimes\mathcal{O}''\textrm{, }\nonumber \\
 &  & \textrm{and }\dpr \left(\ket{\Psi},\mathcal{H}'\right)=\textrm{possible ,}\nonumber \\
 &  & \textrm{then }w\left(\ket{\Psi},\mathcal{H}''\right)=w\left(\hat{P}_{\mathcal{H}'}\ket{\Psi},\mathcal{H}''\right)\textrm{. }\label{eq:locality}
\end{eqnarray}
represents locality because we require the measurement result of $Id_{d'}\otimes\mathcal{O}''$
should be the same no matter whether we apply the other observable
$\mathcal{O}'\otimes Id_{d''}$ which may be far away from $Id_{d'}\otimes\mathcal{O}''$.
\begin{description}
\item [{Theorem}] For $8\mid d$, there is no function $w:\ffzd{p^{2}}\times\mathbb{O}_{p^{2}}^{d}\rightarrow\ff{p}$
satisfying condition (\ref{eq:consistent}) and (\ref{eq:locality}).
\end{description}
\begin{proof}Suppose the function $w$ exists, we are going to construct
a contradiction form a (non-normalized) GHZ state~$\ket{\Psi_{4}}=4\ket{000}-4\ket{111}$,
where $\ket{xyz}$ are a three qubit state $\ket{x}\otimes\ket{y}\otimes\ket{y}$,
$x$, $y$, $z\in\left\{ 0,1\right\} $. Then we consider observables
representing the $j$-th experimenter measuring the spin along the
$\mu$-axis, the Pauli operators acting on the $j$-th spin~$\sigma_{\mu}^{j}$,
where $\mu=x,y$, and 
\begin{equation}
\sigma_{\mu}^{j}=\overbrace{\mathds{1}\otimes\mathds{1}\otimes\cdots\otimes\underbrace{\sigma_{\mu}}_{j^{th}\ \mbox{factor}}\otimes\cdots\otimes\mathds{1}}^{n\ \mbox{factors}}\;,\label{pauli3}
\end{equation}
with 
\[
\sigma_{x}=\left(\begin{array}{cc}
0 & 1\\
1 & 0
\end{array}\right),\sigma_{y}=\left(\begin{array}{cc}
0 & -i\\
i & 0
\end{array}\right).
\]

Suppose the first experimenter perform measurement on the first qubit
along the $x$-axis, and the other experiments perform measurement on
the other qubits along the $y$-axis, their measurements are actually
associated with observables $\sigma_{x}^{1}$, $\sigma_{y}^{2}$, and
$\sigma_{y}^{3}$. Because $\sigma_{x}^{1}$, $\sigma_{y}^{2}$, and
$\sigma_{y}^{3}$ are commuting, the product
observables~$\sigma_{x}^{1}\sigma_{y}^{2}\sigma_{y}^{3}$ used to be
considered in the proof in CQT~\cite{MerminPRL1990,peres1995quantum}.
However, as we discussed, we may not guarantee commuting observables
are compatible and can be measured simultaneously. Therefore, if we
want to consider the product of measurement result
$\sigma_{x}^{1}\sigma_{y}^{2}\sigma_{y}^{3}$, it is better to consider
$3!=6$ possible orders of measurements, to do these measurements
sequentially, and to multiply the measurement results after the
measurement process complete.

Assume the first experimenter measures first, and so on. By the
definition of $\dpr $ and the von Neumann measurement postulate, we
can represent the whole process in Figure
\ref{fig:possible-worlds-graph-2}, where each
arrow~$\ket{\Psi}\overset{\lambda}{\rightarrow}\ket{\Psi'}$ is from a
pre-measurement state~$\ket{\Psi}$ to a possible post-measurement
state~$\ket{\Psi'}$, labeled by the measurement result
eigenvalue~$\lambda$ on the row labeled by the observable
$\mathcal{O}$. By the von Neumann measurement postulate, the possible
post-measurement state~$\ket{\Psi'}$ is
$\hat{P}_{\mathcal{O}=\lambda}\ket{\Psi}$, where
$\hat{P}_{\mathcal{O}=\lambda}$ is the projector on the eigenspace of
$\lambda$. By the condition (\ref{eq:consistent}), the existence of
arrow~$\ket{\Psi}\overset{\lambda}{\rightarrow}\ket{\Psi'}$ implies
that $w\left(\ket{\Psi},\mathcal{O}\right)=\lambda$ is possible;
conversely, we must have
$w\left(\ket{\Psi},\mathcal{O}\right)\ne\lambda$ if there is no
arrow~$\ket{\Psi}\overset{\lambda}{\rightarrow}\ket{\Psi'}$.

\begin{figure*}
$\xymatrix@R=0pt{ &  &  &  & \ket{\Psi_{4}}\ar[ddll]_{1}\ar[ddrr]^{-1}\\
\sigma_{x}^{1}\\
 &  & \ket{\Psi_{+}}\ar[ddl]_{1}\ar[ddr]^{-1} &  &  &  & \ket{\Psi_{-}}\ar[ddl]_{-1}\ar[ddr]^{1}\\
\sigma_{y}^{2}\\
 & \ket{\Psi_{++}}\ar[dd]^{1} &  & \ket{\Psi_{+-}}\ar[dd]^{-1} &  & \ket{\Psi_{--}}\ar[dd]^{1} &  & \ket{\Psi_{-+}}\ar[dd]^{-1}\\
\sigma_{y}^{3}\\
 & \ket{\Psi_{+++}} &  & \ket{\Psi_{+--}} &  & \ket{\Psi_{--+}} &  & \ket{\Psi_{-+-}}
}
$

\begin{eqnarray*}
\ket{\Psi_{+}} & = & \hat{P}_{\sigma_{x}^{1}=1}\ket{\Psi_{4}}\\
\ket{\Psi_{-}} & = & \hat{P}_{\sigma_{x}^{1}=-1}\ket{\Psi_{4}}\\
\ket{\Psi_{++}} & = & \hat{P}_{\sigma_{y}^{2}=1}\hat{P}_{\sigma_{x}^{1}=1}\ket{\Psi_{4}}\\
\ket{\Psi_{+-}} & = & \hat{P}_{\sigma_{y}^{2}=-1}\hat{P}_{\sigma_{x}^{1}=1}\ket{\Psi_{4}}\\
\ket{\Psi_{-+}} & = & \hat{P}_{\sigma_{y}^{2}=1}\hat{P}_{\sigma_{x}^{1}=-1}\ket{\Psi_{4}}\\
\ket{\Psi_{--}} & = & \hat{P}_{\sigma_{y}^{2}=-1}\hat{P}_{\sigma_{x}^{1}=-1}\ket{\Psi_{4}}\\
\ket{\Psi_{+++}} & = & \hat{P}_{\sigma_{y}^{3}=1}\hat{P}_{\sigma_{y}^{2}=1}\hat{P}_{\sigma_{x}^{1}=1}\ket{\Psi_{4}}\\
\ket{\Psi_{+--}} & = & \hat{P}_{\sigma_{y}^{3}=-1}\hat{P}_{\sigma_{y}^{2}=-1}\hat{P}_{\sigma_{x}^{1}=1}\ket{\Psi_{4}}\\
\ket{\Psi_{-+-}} & = & \hat{P}_{\sigma_{y}^{3}=-1}\hat{P}_{\sigma_{y}^{2}=1}\hat{P}_{\sigma_{x}^{1}=-1}\ket{\Psi_{4}}\\
\ket{\Psi_{--+}} & = & \hat{P}_{\sigma_{y}^{3}=1}\hat{P}_{\sigma_{y}^{2}=-1}\hat{P}_{\sigma_{x}^{1}=-1}\ket{\Psi_{4}}
\end{eqnarray*}
\protect\caption{\label{fig:possible-worlds-graph-2}A measurement series start from
a (non-normalized) GHZ state $\ket{\Psi_{4}}$, and perform measurement
associated with observables $\sigma_{x}^{1}$, $\sigma_{y}^{2}$,
and $\sigma_{y}^{3}$ consecutively. }
\end{figure*}
After we draw Figure \ref{fig:possible-worlds-graph-2}, by the locality
condition (\ref{eq:locality}), we know 
\[
w\left(\ket{\Psi_{4}},\sigma_{y}^{2}\right)=w\left(\hat{P}_{\sigma_{x}^{1}=1}\ket{\Psi_{4}},\sigma_{y}^{2}\right)
\]
and so on. Therefore, no matter what measurement results are in Figure
\ref{fig:possible-worlds-graph-2}, the product of measurement results
always satisfies 
\begin{equation}
w\left(\ket{\Psi_{4}},\sigma_{x}^{1}\right)w\left(\ket{\Psi_{4}},\sigma_{y}^{2}\right)w\left(\ket{\Psi_{4}},\sigma_{y}^{3}\right)=1\label{eq:xyy}
\end{equation}
By the same reason, no matter which measurement order among $\sigma_{x}^{1}$,
$\sigma_{y}^{2}$, and $\sigma_{y}^{3}$, the product of measurement
result is always $1$. If we apply the similar method on other triad
observables, we can get 
\begin{eqnarray}
w\left(\ket{\Psi_{4}},\sigma_{y}^{1}\right)w\left(\ket{\Psi_{4}},\sigma_{x}^{2}\right)w\left(\ket{\Psi_{4}},\sigma_{y}^{3}\right) & = & 1\label{eq:yxy}\\
w\left(\ket{\Psi_{4}},\sigma_{y}^{1}\right)w\left(\ket{\Psi_{4}},\sigma_{y}^{2}\right)w\left(\ket{\Psi_{4}},\sigma_{x}^{3}\right) & = & 1\label{eq:yyx}\\
w\left(\ket{\Psi_{4}},\sigma_{x}^{1}\right)w\left(\ket{\Psi_{4}},\sigma_{x}^{2}\right)w\left(\ket{\Psi_{4}},\sigma_{x}^{3}\right) & = & -1\label{eq:xxx}
\end{eqnarray}
However, there is no way to assign $w\left(\ket{\Psi_{4}},\sigma_{\mu}^{j}\right)=1$
or $-1$ to satisfying the equation (\ref{eq:xyy}), (\ref{eq:yxy}),
(\ref{eq:yyx}), and (\ref{eq:xxx}). Therefore, there is no function
$w$.\end{proof}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

We have shown that by replacing state vectors and continuous probabilities
introduced in the conventional quantum mechanical arguments for
Gleason's theorem and related theorems invalidating hidden variable
theories by vectors in the discrete field $\ffzd{p^{2}}$ and a modal
logic-valued Born Rule, all the basic properties needed for a quantum
theory that is distinct from classical theory, forbidding hidden
variables, can be recovered.

\andy{Need to close with an assessment of the Mayer-Mermin discussion
  about the validity of the KS theorem in a world with finite
  resources and precision.}

\bibliographystyle{plain}
\bibliography{discreteGBKS}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{enumerate}
\item Possible or impossible needed, if then inconsistent requires extends. 
\item At first assume non-degenerate for clarity, but degenerate state will
play an important rule in final analysis.
\item Review of CQT notation with pointers to DQT glitches. 
\end{enumerate}
\item Elementary tests, e.g., yes/no questions, are represented by projectors
in a complex vector space <cite Peres>
\begin{equation}
\hat{P}_{\mathcal{H}_{n}}\equiv\sum_{g_{n}=0}^{d_{n}-1}\frac{\left|n^{g_{n}}\right\rangle \bra{n^{g_{n}}}}{\ip{n^{g_{n}}}{n^{g_{n}}}}\textrm{ ,}\label{eq:projection-1}
\end{equation}
where 
\begin{equation}
{\cal O}\,\left|n^{g_{n}}\right\rangle =\lambda_{n}\left|n^{g_{n}}\right\rangle \textrm{ .}
\end{equation}
 allow degenerate extension to 
\begin{equation}
{\cal O}\,\left|n\right\rangle =\lambda_{n}\left|n\right\rangle \textrm{ .}
\end{equation}
where the set labeled by $\dpr _{n}$ has same eigenvalue $\lambda_{n}$.\end{itemize}

### 2015-11-17 DQC3.tex
DQC3.tex compiled in iopart class

@@
 
-\documentclass[english,12pt]{article}
+\documentclass[english,12pt]{iopart}
 \usepackage{mathrsfs}
 \usepackage{fullpage}
-% \documentclass[english,prl,aps,showpacs,preprint,floatfix,superscriptaddress]{revtex4-1} 
-%\usepackage[T1]{fontenc}
-% \usepackage[latin9]{inputenc}
-% \setcounter{secnumdepth}{3}
 \usepackage{url}
 \usepackage{times}
-
+\usepackage{amstext}
+\usepackage{amssymb}
 \usepackage{amsthm}
-\usepackage{amsmath}
+\usepackage{iopams}
+\usepackage{setstack}
 
@@
 \newcommand{\affiliation}[1]{\parbox{5.5in}{\small{\it #1 \/}}}
-\newcommand{\pacs}[1]{\bf #1 \/}
 
@@
 \newcommand{\ComplexI}{\text{i}}
-\allowdisplaybreaks
 \newcommand{\fnorm}[1]{\mathsf{N}(#1)}
+\newcommand{\mod}{\mbox{mod }}
 
@@
   Bloomington, IN 47405, U.S.A}}
-
-\maketitle
-
-%\date{\today}
 
@@
 $p\equiv 3\mod 4$, the fields $\ff{p}$ are exactly those for which
-$x^2+1$ has no root in the field, and we can adjoin $\ComplexI$ as a
+$x^2+1$ has no root in the field, and we can adjoin $\rmi$ as a
 root of $x^2+1$ to the field $\ff{p}$.  For a given element
@@
 \[
-\mathbf{H}_{1}=\begin{pmatrix}-1 & -\ComplexI & 0\\
-\ComplexI & 1 & -\ComplexI\\
-0 & \ComplexI & 1
-\end{pmatrix}
+\mathbf{H}_{1}=\left(\begin{array}{ccc}
+-1 & -\rmi & 0\\
+\rmi & 1 & -\rmi\\
+0 & \rmi & 1
+\end{array}\right)
 \]
@@
 \[
-\mathbf{H}_{2}=\begin{pmatrix}-1 & -1-\ComplexI\\
--1+\ComplexI & 0
-\end{pmatrix}
+\mathbf{H}_{2}=\left(\begin{array}{cc}
+-1 & -1-\rmi\\
+-1+\rmi & 0
+\end{array}\right)
 \]
@@
 The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\begin{pmatrix}1\\
--1+\ComplexI
+-1+\rmi
 \end{pmatrix}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$
@@
 $1$ with the post-measurement state $\begin{pmatrix}1\\
--1+\ComplexI
+-1+\rmi
 \end{pmatrix}$. However, only operator always producing $1$ is the identity operator
@@
 \[
-\mathbf{H}_{3}=\begin{pmatrix}-1 & -1-\ComplexI\\
--1+\ComplexI & 1-
-\end{pmatrix}
+\mathbf{H}_{3}=\left(\begin{array}{cc}
+-1 & -1-\rmi\\
+-1+\rmi & 1-
+\end{array}\right)
 \]
 Over $\ff{9}$, the eigenvalues and eigenvectors of $\mathbf{H}_{3}$
-are $-1-\ComplexI$ with $\begin{pmatrix}1\\
--1-\ComplexI
-\end{pmatrix}$ and $-1+\ComplexI$ with $\begin{pmatrix}1\\
-1+\ComplexI
+are $-1-\rmi$ with $\begin{pmatrix}1\\
+-1-\rmi
+\end{pmatrix}$ and $-1+\rmi$ with $\begin{pmatrix}1\\
+1+\rmi
 \end{pmatrix}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the
@@
 \begin{eqnarray*}
--1\pm\sqrt{2} & \equiv & -1\pm\ComplexI\left(\bmod p\right)
+-1\pm\sqrt{2} & \equiv & -1\pm\rmi\left(\bmod p\right)
 \end{eqnarray*}
@@
 to 1. By property ({\bf i})
-\begin{align*}
-  1&=\dpt\big(\ket{\Psi},\ket{0}\big)+ \dpt\big(\ket{\Psi},\ket{1}\big) + 
-     \dpt\big(\ket{\Psi},\ket{2}\big)+ \dpt \big(\ket{\Psi},\ket{3}\big)\\
-  &=\frac{1}{2}+\frac{1}{2}+\frac{1}{2}+\dpt\big(\ket{\Psi},\ket{3}\big)\\
-  &\geq \frac{3}{2},
-\end{align*}
+\begin{eqnarray*}
+1 & = & \dpt\big(\ket{\Psi},\ket{0}\big)+\dpt\big(\ket{\Psi},\ket{1}\big)+\dpt\big(\ket{\Psi},\ket{2}\big)+\dpt\big(\ket{\Psi},\ket{3}\big)\\
+ & = & \frac{1}{2}+\frac{1}{2}+\frac{1}{2}+\dpt\big(\ket{\Psi},\ket{3}\big)\\
+ & \geq & \frac{3}{2},
+\end{eqnarray*}
 so we have a contradiction. The assumption of a satisfactory map
@@
     longer.}. Suppose $v$ exists, and consider the set of all vectors
-  with entries in $\left\{ 0,\pm1,\pm1\pm\ComplexI\right\} $. Then the
+  with entries in $\left\{ 0,\pm1,\pm1\pm\rmi\right\} $. Then the
   steps in the proof can be read off from Table
@@
   where $x$, $y$, and $z$ can be \{ $0$, $1$, $\bar{1}\equiv -1,$
-  ${+} \equiv (1+\ComplexI)$, ${-} \equiv (1-\ComplexI)$ \}, and
+  ${+} \equiv (1+\rmi)$, ${-} \equiv (1-\rmi)$ \}, and
 \[

### 2015-11-18 DQC3.tex
Update title and reference according to IOPLaTeXGuildines

@@
 
-\author{John Gardiner\\
- \affiliation{College of Physical and Mathematical Sciences, Brigham
-  Young University, Provo, UT 84602, U.S.A}\\[.2in]
-%% \author
-Andrew J. Hanson\\
-\affiliation{School of Informatics and Computing, Indiana University,
-  Bloomington, IN 47405, U.S.A}\\[.2in]
-%%\author
-Gerardo Ortiz \\
-\affiliation{Department of Physics, Indiana University, Bloomington, IN 47405,
-U.S.A}\\[.2in]
-%%\author
-Amr Sabry\\
-\affiliation{School of Informatics and Computing, Indiana University,
-  Bloomington, IN 47405, U.S.A}\\[.2in]
-%%\author
-Yu-Tsung Tai\\
-\affiliation{Department of Mathematics, Indiana University,
-  Bloomington, IN 47405, U.S.A}\\
-\affiliation{School of Informatics and Computing, Indiana University,
-  Bloomington, IN 47405, U.S.A}}
+\author{John Gardiner$^{1}$, Andrew J. Hanson$^{2}$, Gerardo Ortiz$^{3}$,
+Amr Sabry$^{1}$, Yu-Tsung Tai$^{42}$}
+
+\address{$^{1}$ College of Physical and Mathematical Sciences, Brigham Young
+University, Provo, UT 84602, U.S.A}
+
+\address{$^{2}$ School of Informatics and Computing, Indiana University,
+Bloomington, IN 47405, U.S.A}
+
+\address{$^{3}$ Department of Physics, Indiana University, Bloomington, IN
+47405, U.S.A}
+
+\address{$^{4}$ Department of Mathematics, Indiana University, Bloomington,
+IN 47405, U.S.A}
+
+\ead{ortizg@indiana.edu}
 
 \pacs{03.65.-w, 03.65.Ud, 03.65.Ta, 02.10.De}
+
+\submitto{\jpa}
 
@@
 
-\bibliographystyle{plain}
+\section*{References}
+
+\bibliographystyle{iopart-num}
 \bibliography{discreteGBKS}

### 2015-11-21 DQC3.tex
Re: Yu-Tsung Tai wants to share "Erratum: Geometry of discrete...
From: JOHN GOLDEN GARDINER [mailto:johngardiner@ucla.edu] 
Sent: Friday, November 20, 2015 22:51
To: Tai, Yu-Tsung <yuttai@indiana.edu>
Subject: Re: Yu-Tsung Tai wants to share "Erratum: Geometry of discrete
quantum computing" with you

I think

Department of Physics and Astronomy, University of California, Los
Angeles, CA 90095, USA

would be better to use.

Thanks,
John

On Fri, Nov 20, 2015 at 6:49 PM, Tai, Yu-Tsung <yuttai@indiana.edu>
wrote:
Dear all, 
 
I changed it to “unentangled states,” and I am about to submit our
Err

@@
 
-\address{$^{1}$ College of Physical and Mathematical Sciences, Brigham Young
-University, Provo, UT 84602, U.S.A}
+\address{$^{1}$ Department of Physics and Astronomy, University of California,
+Los Angeles, CA 90095, USA}
 
 \address{$^{2}$ School of Informatics and Computing, Indiana University,
-Bloomington, IN 47405, U.S.A}
+Bloomington, IN 47405, USA}
 
 \address{$^{3}$ Department of Physics, Indiana University, Bloomington, IN
-47405, U.S.A}
+47405, USA}
 
 \address{$^{4}$ Department of Mathematics, Indiana University, Bloomington,
-IN 47405, U.S.A}
+IN 47405, USA}
 

### 2015-11-22 DQC3.tex
Replace \ComplexI by \rmi because of IOPLaTeXGuidelines
Add the date to title page, and fix some obverious bugs...

@@
 
-\newcommand{\ComplexI}{\text{i}}
 \newcommand{\fnorm}[1]{\mathsf{N}(#1)}
@@
 
-\title{Contextuality and Nonlocality in \\ Discrete Quantum Theory}
+\title{Contextuality and Nonlocality in Discrete Quantum Theory}
 
@@
 \ead{ortizg@indiana.edu}
+\begin{abstract}
+\today
+\end{abstract}
 
 \pacs{03.65.-w, 03.65.Ud, 03.65.Ta, 02.10.De}
+
+\noindent{\it Keywords\/}: {contextuality, nonlocality, measurement process, Gleason's theorem,
+Bell's theorem, the Kochen-Specker theorem}
 
@@
 no enough eigenvector is a problem?}\\
-The dimension of an eigenspace may be less than the multiplicity of
-its eigenvalue. For example, consider a Hermitian matrix 
+ The dimension of an eigenspace may be less than the multiplicity
+of its eigenvalue. For example, consider a Hermitian matrix 
 \[
@@
 Over $\ff{9}$, its only eigenvalue is $1$ of multiplicity $2$.
-The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\begin{pmatrix}1\\
--1+\rmi
-\end{pmatrix}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$
+The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\left(\begin{array}{cc}
+1 & -1+\rmi\end{array}\right)^{T}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$
 are not diagonalizable over $\ff{9}$. If $\mathbf{H}_{2}$ were an
 observable, $\mathbf{H}_{2}$ would always have the outcome of measurement
-$1$ with the post-measurement state $\begin{pmatrix}1\\
--1+\rmi
-\end{pmatrix}$. However, only operator always producing $1$ is the identity operator
+$1$ with the post-measurement state $\left(\begin{array}{cc}
+1 & -1+\rmi\end{array}\right)^{T}$. However, only operator always producing $1$ is the identity operator
 which change no state. Therefore, $\mathbf{H}_{2}$ may not be intuitively
@@
 -1 & -1-\rmi\\
--1+\rmi & 1-
+-1+\rmi & -1
 \end{array}\right)
@@
 Over $\ff{9}$, the eigenvalues and eigenvectors of $\mathbf{H}_{3}$
-are $-1-\rmi$ with $\begin{pmatrix}1\\
--1-\rmi
-\end{pmatrix}$ and $-1+\rmi$ with $\begin{pmatrix}1\\
-1+\rmi
-\end{pmatrix}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the
+are $-1-\rmi$ with $\left(\begin{array}{cc}
+1 & -1-\rmi\end{array}\right)^{T}$ and $-1+\rmi$ with $\left(\begin{array}{cc}
+1 & 1+\rmi\end{array}\right)^{T}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the
 eigenvectors are all zero-normed.\\
@@
 so that any definition depend on the complex conjugate may not be
-preserved when we map them into finite fields.
+preserved when we map them into finite fields. \yutsung{Although
+may not need to type it down, need to check the definition of the
+map, passing congruence into square root, and partial homomorphism...
+etc.}
 \end{enumerate}

### 2015-11-24 DQC3.tex
Fix a typo in the title page...
Adding comments since "The Concept of Contextuality and its Role in ..."

@@
 \author{John Gardiner$^{1}$, Andrew J. Hanson$^{2}$, Gerardo Ortiz$^{3}$,
-Amr Sabry$^{1}$, Yu-Tsung Tai$^{42}$}
+Amr Sabry$^{2}$, Yu-Tsung Tai$^{4,2}$}
 
@@
 
+\yutsung{Does the sentences in this paragraph contradict to each
+other? I think Peres~\cite{peres1995quantum} means: If we think
+the measurement process as a quantum system by the Born rule, the
+measurement result does not depend on simultaneously measuring commuting
+observables. On the other hand, if we want to think the measurement
+process classically, i.e., to assign the measurement result for each
+observable, we cannot make the assignment prior to any measurement,
+and assume that measuring commuting observables does not change the
+assigned measurement result. <- This long sentence means contextuality.}
+
 Classical Physics, on the other hand, is usually agreed to be
@@
 unknown but complete) context influences the outcome of experiments.
+
+\yutsung{I don't understand the last sentence...}
 

### 2015-11-25 DQC3.tex
Adding more comments on "The Concept of Contextuality and its..."

@@
 \yutsung{Does the sentences in this paragraph contradict to each
-other? I think Peres~\cite{peres1995quantum} means: If we think
-the measurement process as a quantum system by the Born rule, the
-measurement result does not depend on simultaneously measuring commuting
-observables. On the other hand, if we want to think the measurement
-process classically, i.e., to assign the measurement result for each
-observable, we cannot make the assignment prior to any measurement,
-and assume that measuring commuting observables does not change the
-assigned measurement result. <- This long sentence means contextuality.}
+other? Besides, are we talking about CQT or DQT here? The paragraph
+make sense because we can simultaneously measuring commuting observables
+in CQT. However, if $J_{z}$ and $J_{z}^{2}$ cannot measure simultaneously,
+then I doubt whether any observables can measure simultaneously. Furthermore,
+the definition of contextuality is based on simultaneously measurement
+in CQT so that we must be very careful to re-define the contextuality
+in DQT to bypass the simultaneously measurement...
+
+I think Peres~\cite{peres1995quantum} means: If we think the measurement
+process as a quantum system by the Born rule, the measurement result
+does not depend on simultaneously measuring commuting observables.
+On the other hand, if we want to think the measurement process classically,
+i.e., to assign the measurement result for each observable, we cannot
+make the assignment prior to any measurement, and assume that measuring
+commuting observables does not change the assigned measurement result.
+<- This long sentence means contextuality.}
 

### 2015-11-26 DQC3.tex
Keep adding comments on "The Concept of Contextuality and its..."

--- 2015-11-22 DQC3.tex
@@
 
+\yutsung{Does the sentences in this paragraph contradict to each
+other? Besides, are we talking about CQT or DQT here? The paragraph
+only make sense if we can simultaneously measuring commuting observables
+in CQT so that we could implement an observable in many different
+measurement processes. For example, in CQT, we could implement $J_{z}$
+in two different measurement processes: measuring $J_{z}$ directly,
+or measuring $J_{z}^{2}$ and then $J_{z}$. These two processes are
+the same because $J_{z}$ and $J_{z}^{2}$ are commuting, and can
+measure simultaneously. However, these two processes are not the same
+in DQT because the first always success, but the second one may produce
+a zero-norm state in the middle. In general, observables cannot measure
+simultaneously in DQT. Because the definition of contextuality is
+based on simultaneously measurement in CQT, we must redefine the contextuality
+in DQT to address this issue.
+
+What does contextuality mean in CQT? Assume:
+\begin{enumerate}
+\item The quantum system were actually classical, i.e., we could assign
+each observable~$\mathbf{O}$ a measurement result~$v\left(\mathbf{O}\right)$
+before we do any measurement.
+\end{enumerate}
+Because whether measuring commuting observables of $\mathbf{O}$ or
+not doesn't change the measurement result of $\mathbf{O}$, it is
+nature to hope this property still hold if the quantum system were
+actually classical. Therefore, we assume:
+\begin{enumerate}[resume]
+\item \label{enu:contextuality}The preassigned measurement result~$v\left(\mathbf{O}\right)$
+of an observable~$\mathbf{O}$ is not changed if we measure the system
+by any other observable commuting to $\mathbf{O}$. (page 207 in~\cite{peres1995quantum})
+\end{enumerate}
+Then, we have the premise of the Kochen-Specker theorem
+\begin{enumerate}[resume]
+\item \label{enu:premise}For a set of commuting projection operator $\proj{n}$,
+if $\left\{ \ket{n}\right\} $ forms a basis, then $\sum_{n}v\left(\proj{n}\right)=1$.
+(page 196 in~\cite{peres1995quantum}).
+\end{enumerate}
+The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
+to be satisfied, so that Assumption (\ref{enu:contextuality}) cannot
+be true.
+
+Schumacher and Westmoreland\cite{2010arXiv1010.5452S} uses Premise
+(\ref{enu:premise}) as the definition of contextuality because it
+seems impossible to discuss the commuting observables in their theory.
+Our paper may do better and use Assumption (\ref{enu:contextuality})
+as contextuality. However, it is not that surprising if Assumption
+(\ref{enu:contextuality}) is false because commuting observables
+cannot be measured simultaneously in DQT anyway. }
+
 Classical Physics, on the other hand, is usually agreed to be

### 2015-11-26 DQC3.tex
Keep editing comments on "The Concept of Contextuality and its..."

--- 2015-11-24 DQC3.tex
@@
 \yutsung{Does the sentences in this paragraph contradict to each
-other? I think Peres~\cite{peres1995quantum} means: If we think
-the measurement process as a quantum system by the Born rule, the
-measurement result does not depend on simultaneously measuring commuting
-observables. On the other hand, if we want to think the measurement
-process classically, i.e., to assign the measurement result for each
-observable, we cannot make the assignment prior to any measurement,
-and assume that measuring commuting observables does not change the
-assigned measurement result. <- This long sentence means contextuality.}
+other? According to the postulates in page 206 and 207 in Peres~\cite{peres1995quantum},
+this paragraph should read ``Quantum Physics is contextual, meaning
+that if we predetermine definite outcomes for any measurement, then
+the predetermined outcomes depend not only on the choice of the measured
+observable(s) and on the system being measured, but also on the details
+of the measurement process. To be more precise, as noted by Peres~\cite{peres1995quantum}
+and Mermin~\cite{MerminPRL1990}, the result of measuring an observable
+in a physical system must not depend on whether we measure the observable
+alone, or along with arbitrary sets of mutually commuting observables.
+However, if we try to predetermine definite measurement outcomes for
+all observables on a system, the predetermined outcome of an observable
+$\mathbf{O}$ will be changed by measuring other observables commuting
+to $\mathbf{O}$.''}
+
+\yutsung{Personal note about the reason why the quantum physics is
+contextuality, and a bit of literature review. Don't know whether
+or where to put them in our paper through.
+
+In order to prove by contradiction, assume the quantum physics is
+non-contextuality, i.e., 
+\begin{enumerate}
+\item \label{enu:non-contextuality}Given an observable $\mathbf{O}$, the
+predetermined definite outcome $v\left(\mathbf{O}\right)$ does not
+depend on the choice of compatible observables that may be preformed
+together with it. (postulate I in page 207 in \cite{peres1995quantum}).
+\end{enumerate}
+This leads to the premise of the Kochen-Specker theorem
+\begin{enumerate}[resume]
+\item \label{enu:premise}For a set of commuting projection operator $\proj{n}$,
+if $\left\{ \ket{n}\right\} $ forms a basis, then $\sum_{n}v\left(\proj{n}\right)=1$.
+(page 196 in \cite{peres1995quantum}).
+\end{enumerate}
+The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
+to be satisfied so that postulate (\ref{enu:non-contextuality}) fails,
+and the quantum theory is contextual .
+
+Schumacher and Westmoreland~\cite{2010arXiv1010.5452S} uses Premise
+(\ref{enu:premise}) instead of Postulate (\ref{enu:non-contextuality})
+as the definition of non-contextuality because lack of commuting observables
+in their theory. Our paper can do better and use Assumption (\ref{enu:non-contextuality})
+as non-contextuality.
+
+There is no solid reason why people assume Postulate (\ref{enu:non-contextuality})
+as a postulate. Peres gives a ``psychological reason'' that Postulate
+(\ref{enu:non-contextuality}) is true when the measurement outcome
+is predictable. Another ``psychological reason'' might be: because
+Postulate (\ref{enu:non-contextuality}) is true when we replace the
+``predetermined definite outcome'' by the usual ``measurement result''
+in CQT. However, in DQT, because commuting observables cannot be measured
+simultaneously, it may not be surprising that Postulate (\ref{enu:non-contextuality})
+is false.}
 

### 2015-11-29 DQC3.tex
Keep updating comments on "The Concept of Contextuality and its..."

@@
 \begin{enumerate}
-\item \label{enu:non-contextuality}Given an observable $\mathbf{O}$, the
-predetermined definite outcome $v\left(\mathbf{O}\right)$ does not
-depend on the choice of compatible observables that may be preformed
-together with it. (postulate I in page 207 in \cite{peres1995quantum}).
+\item \label{enu:non-contextuality}Given an observable $\mathbf{O}$, we
+can predetermine a definite measurement outcome $v\left(\mathbf{O}\right)$
+not depending on the choice of compatible observables that may be
+preformed together with it. (postulate I in page 207 in \cite{peres1995quantum}).
 \end{enumerate}
@@
 \begin{enumerate}[resume]
-\item \label{enu:premise}For a set of commuting projection operator $\proj{n}$,
-if $\left\{ \ket{n}\right\} $ forms a basis, then $\sum_{n}v\left(\proj{n}\right)=1$.
+\item \label{enu:premise}We can also define $v$ on states by $v\left(\ket{n}\right)=v\left(\proj{n}\right)$.
+If $\left\{ \ket{n}\right\} $ forms a orthonormal basis, then $\sum_{n}v\left(\ket{n}\right)=1$.
 (page 196 in \cite{peres1995quantum}).
@@
 The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
-to be satisfied so that postulate (\ref{enu:non-contextuality}) fails,
+to be satisfied so that Postulate (\ref{enu:non-contextuality}) fails,
 and the quantum theory is contextual .
 
-Schumacher and Westmoreland~\cite{2010arXiv1010.5452S} uses Premise
-(\ref{enu:premise}) instead of Postulate (\ref{enu:non-contextuality})
-as the definition of non-contextuality because lack of commuting observables
-in their theory. Our paper can do better and use Assumption (\ref{enu:non-contextuality})
-as non-contextuality.
+Because lack of commuting observables in their theory, Schumacher
+and Westmoreland~\cite{2010arXiv1010.5452S} uses ``$v$ is well-defined
+on states'' instead of Postulate (\ref{enu:non-contextuality}) as
+the definition of non-contextuality. However, comparing to Postulate
+(\ref{enu:non-contextuality}), it is less clear why ``$v$ is well-defined
+on states'' should be a postulate or not.
 

### 2015-11-29 DQC3-article.tex
Simplify comments on "The Concept of Contextuality and its..."
Because I think I understand a little bit more about contextuality
maybe...

--- 2015-11-26 DQC3.tex
@@
 
-\documentclass[english,12pt]{iopart}
+\documentclass[english,12pt]{article}
 \usepackage{mathrsfs}
 \usepackage{fullpage}
+% \documentclass[english,prl,aps,showpacs,preprint,floatfix,superscriptaddress]{revtex4-1} 
+%\usepackage[T1]{fontenc}
+% \usepackage[latin9]{inputenc}
+% \setcounter{secnumdepth}{3}
 \usepackage{url}
 \usepackage{times}
-\usepackage{amstext}
-\usepackage{amssymb}
+
 \usepackage{amsthm}
-\usepackage{iopams}
-\usepackage{setstack}
+\usepackage{amsmath}
 
@@
 \newcommand{\affiliation}[1]{\parbox{5.5in}{\small{\it #1 \/}}}
+\newcommand{\pacs}[1]{\bf #1 \/}
 
@@
 
+\newcommand{\ComplexI}{\text{i}}
+\allowdisplaybreaks
 \newcommand{\fnorm}[1]{\mathsf{N}(#1)}
-\newcommand{\mod}{\mbox{mod }}
 
@@
 
-\title{Contextuality and Nonlocality in Discrete Quantum Theory}
-
-\author{John Gardiner$^{1}$, Andrew J. Hanson$^{2}$, Gerardo Ortiz$^{3}$,
-Amr Sabry$^{2}$, Yu-Tsung Tai$^{4,2}$}
-
-\address{$^{1}$ Department of Physics and Astronomy, University of California,
-Los Angeles, CA 90095, USA}
-
-\address{$^{2}$ School of Informatics and Computing, Indiana University,
-Bloomington, IN 47405, USA}
-
-\address{$^{3}$ Department of Physics, Indiana University, Bloomington, IN
-47405, USA}
-
-\address{$^{4}$ Department of Mathematics, Indiana University, Bloomington,
-IN 47405, USA}
-
-\ead{ortizg@indiana.edu}
-\begin{abstract}
-\today
-\end{abstract}
+\title{Contextuality and Nonlocality in \\ Discrete Quantum Theory}
+
+\author{John Gardiner\\
+ \affiliation{College of Physical and Mathematical Sciences, Brigham
+  Young University, Provo, UT 84602, U.S.A}\\[.2in]
+%% \author
+Andrew J. Hanson\\
+\affiliation{School of Informatics and Computing, Indiana University,
+  Bloomington, IN 47405, U.S.A}\\[.2in]
+%%\author
+Gerardo Ortiz \\
+\affiliation{Department of Physics, Indiana University, Bloomington, IN 47405,
+U.S.A}\\[.2in]
+%%\author
+Amr Sabry\\
+\affiliation{School of Informatics and Computing, Indiana University,
+  Bloomington, IN 47405, U.S.A}\\[.2in]
+%%\author
+Yu-Tsung Tai\\
+\affiliation{Department of Mathematics, Indiana University,
+  Bloomington, IN 47405, U.S.A}\\
+\affiliation{School of Informatics and Computing, Indiana University,
+  Bloomington, IN 47405, U.S.A}}
+
+\maketitle
+
+%\date{\today}
 
 \pacs{03.65.-w, 03.65.Ud, 03.65.Ta, 02.10.De}
-
-\noindent{\it Keywords\/}: {contextuality, nonlocality, measurement process, Gleason's theorem,
-Bell's theorem, the Kochen-Specker theorem}
-
-\submitto{\jpa}
 
@@
 
-\yutsung{Does the sentences in this paragraph contradict to each
-other? Besides, are we talking about CQT or DQT here? The paragraph
-only make sense if we can simultaneously measuring commuting observables
-in CQT so that we could implement an observable in many different
-measurement processes. For example, in CQT, we could implement $J_{z}$
-in two different measurement processes: measuring $J_{z}$ directly,
-or measuring $J_{z}^{2}$ and then $J_{z}$. These two processes are
-the same because $J_{z}$ and $J_{z}^{2}$ are commuting, and can
-measure simultaneously. However, these two processes are not the same
-in DQT because the first always success, but the second one may produce
-a zero-norm state in the middle. In general, observables cannot measure
-simultaneously in DQT. Because the definition of contextuality is
-based on simultaneously measurement in CQT, we must redefine the contextuality
-in DQT to address this issue.
-
-What does contextuality mean in CQT? Assume:
-\begin{enumerate}
-\item The quantum system were actually classical, i.e., we could assign
-each observable~$\mathbf{O}$ a measurement result~$v\left(\mathbf{O}\right)$
-before we do any measurement.
-\end{enumerate}
-Because whether measuring commuting observables of $\mathbf{O}$ or
-not doesn't change the measurement result of $\mathbf{O}$, it is
-nature to hope this property still hold if the quantum system were
-actually classical. Therefore, we assume:
-\begin{enumerate}[resume]
-\item \label{enu:contextuality}The preassigned measurement result~$v\left(\mathbf{O}\right)$
-of an observable~$\mathbf{O}$ is not changed if we measure the system
-by any other observable commuting to $\mathbf{O}$. (page 207 in~\cite{peres1995quantum})
-\end{enumerate}
-Then, we have the premise of the Kochen-Specker theorem
-\begin{enumerate}[resume]
-\item \label{enu:premise}For a set of commuting projection operator $\proj{n}$,
-if $\left\{ \ket{n}\right\} $ forms a basis, then $\sum_{n}v\left(\proj{n}\right)=1$.
-(page 196 in~\cite{peres1995quantum}).
-\end{enumerate}
-The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
-to be satisfied, so that Assumption (\ref{enu:contextuality}) cannot
-be true.
-
-Schumacher and Westmoreland\cite{2010arXiv1010.5452S} uses Premise
-(\ref{enu:premise}) as the definition of contextuality because it
-seems impossible to discuss the commuting observables in their theory.
-Our paper may do better and use Assumption (\ref{enu:contextuality})
-as contextuality. However, it is not that surprising if Assumption
-(\ref{enu:contextuality}) is false because commuting observables
-cannot be measured simultaneously in DQT anyway. }
-
 Classical Physics, on the other hand, is usually agreed to be
@@
 unknown but complete) context influences the outcome of experiments.
-
-\yutsung{I don't understand the last sentence...}
 
@@
 $p\equiv 3\mod 4$, the fields $\ff{p}$ are exactly those for which
-$x^2+1$ has no root in the field, and we can adjoin $\rmi$ as a
+$x^2+1$ has no root in the field, and we can adjoin $\ComplexI$ as a
 root of $x^2+1$ to the field $\ff{p}$.  For a given element
@@
 \[
-\mathbf{H}_{1}=\left(\begin{array}{ccc}
--1 & -\rmi & 0\\
-\rmi & 1 & -\rmi\\
-0 & \rmi & 1
-\end{array}\right)
+\mathbf{H}_{1}=\begin{pmatrix}-1 & -\ComplexI & 0\\
+\ComplexI & 1 & -\ComplexI\\
+0 & \ComplexI & 1
+\end{pmatrix}
 \]
@@
 no enough eigenvector is a problem?}\\
- The dimension of an eigenspace may be less than the multiplicity
-of its eigenvalue. For example, consider a Hermitian matrix 
+The dimension of an eigenspace may be less than the multiplicity of
+its eigenvalue. For example, consider a Hermitian matrix 
 \[
-\mathbf{H}_{2}=\left(\begin{array}{cc}
--1 & -1-\rmi\\
--1+\rmi & 0
-\end{array}\right)
+\mathbf{H}_{2}=\begin{pmatrix}-1 & -1-\ComplexI\\
+-1+\ComplexI & 0
+\end{pmatrix}
 \]
 Over $\ff{9}$, its only eigenvalue is $1$ of multiplicity $2$.
-The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\left(\begin{array}{cc}
-1 & -1+\rmi\end{array}\right)^{T}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$
+The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\begin{pmatrix}1\\
+-1+\ComplexI
+\end{pmatrix}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$
 are not diagonalizable over $\ff{9}$. If $\mathbf{H}_{2}$ were an
 observable, $\mathbf{H}_{2}$ would always have the outcome of measurement
-$1$ with the post-measurement state $\left(\begin{array}{cc}
-1 & -1+\rmi\end{array}\right)^{T}$. However, only operator always producing $1$ is the identity operator
+$1$ with the post-measurement state $\begin{pmatrix}1\\
+-1+\ComplexI
+\end{pmatrix}$. However, only operator always producing $1$ is the identity operator
 which change no state. Therefore, $\mathbf{H}_{2}$ may not be intuitively
@@
 \[
-\mathbf{H}_{3}=\left(\begin{array}{cc}
--1 & -1-\rmi\\
--1+\rmi & -1
-\end{array}\right)
+\mathbf{H}_{3}=\begin{pmatrix}-1 & -1-\ComplexI\\
+-1+\ComplexI & 1-
+\end{pmatrix}
 \]
 Over $\ff{9}$, the eigenvalues and eigenvectors of $\mathbf{H}_{3}$
-are $-1-\rmi$ with $\left(\begin{array}{cc}
-1 & -1-\rmi\end{array}\right)^{T}$ and $-1+\rmi$ with $\left(\begin{array}{cc}
-1 & 1+\rmi\end{array}\right)^{T}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the
+are $-1-\ComplexI$ with $\begin{pmatrix}1\\
+-1-\ComplexI
+\end{pmatrix}$ and $-1+\ComplexI$ with $\begin{pmatrix}1\\
+1+\ComplexI
+\end{pmatrix}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the
 eigenvectors are all zero-normed.\\
@@
 \begin{eqnarray*}
--1\pm\sqrt{2} & \equiv & -1\pm\rmi\left(\bmod p\right)
+-1\pm\sqrt{2} & \equiv & -1\pm\ComplexI\left(\bmod p\right)
 \end{eqnarray*}
@@
 so that any definition depend on the complex conjugate may not be
-preserved when we map them into finite fields. \yutsung{Although
-may not need to type it down, need to check the definition of the
-map, passing congruence into square root, and partial homomorphism...
-etc.}
+preserved when we map them into finite fields.
 \end{enumerate}
@@
 to 1. By property ({\bf i})
-\begin{eqnarray*}
-1 & = & \dpt\big(\ket{\Psi},\ket{0}\big)+\dpt\big(\ket{\Psi},\ket{1}\big)+\dpt\big(\ket{\Psi},\ket{2}\big)+\dpt\big(\ket{\Psi},\ket{3}\big)\\
- & = & \frac{1}{2}+\frac{1}{2}+\frac{1}{2}+\dpt\big(\ket{\Psi},\ket{3}\big)\\
- & \geq & \frac{3}{2},
-\end{eqnarray*}
+\begin{align*}
+  1&=\dpt\big(\ket{\Psi},\ket{0}\big)+ \dpt\big(\ket{\Psi},\ket{1}\big) + 
+     \dpt\big(\ket{\Psi},\ket{2}\big)+ \dpt \big(\ket{\Psi},\ket{3}\big)\\
+  &=\frac{1}{2}+\frac{1}{2}+\frac{1}{2}+\dpt\big(\ket{\Psi},\ket{3}\big)\\
+  &\geq \frac{3}{2},
+\end{align*}
 so we have a contradiction. The assumption of a satisfactory map
@@
     longer.}. Suppose $v$ exists, and consider the set of all vectors
-  with entries in $\left\{ 0,\pm1,\pm1\pm\rmi\right\} $. Then the
+  with entries in $\left\{ 0,\pm1,\pm1\pm\ComplexI\right\} $. Then the
   steps in the proof can be read off from Table
@@
   where $x$, $y$, and $z$ can be \{ $0$, $1$, $\bar{1}\equiv -1,$
-  ${+} \equiv (1+\rmi)$, ${-} \equiv (1-\rmi)$ \}, and
+  ${+} \equiv (1+\ComplexI)$, ${-} \equiv (1-\ComplexI)$ \}, and
 \[
@@
 
-\section*{References}
-
-\bibliographystyle{iopart-num}
+\bibliographystyle{plain}
 \bibliography{discreteGBKS}
@@
 \end{equation}
-where the set labeled by $\dpr _{n}$ has same eigenvalue $\lambda_{n}$.\end{itemize}
+where the set labeled by $\dpr _{n}$ has same eigenvalue $\lambda_{n}$.

### 2015-11-29 DQC3.tex
Simplify comments on "The Concept of Contextuality and its..."
Because I think I understand a little bit more about contextuality
maybe...

--- 2015-11-26 DQC3.tex
@@
 \yutsung{Does the sentences in this paragraph contradict to each
-other? Besides, are we talking about CQT or DQT here? The paragraph
-only make sense if we can simultaneously measuring commuting observables
-in CQT so that we could implement an observable in many different
-measurement processes. For example, in CQT, we could implement $J_{z}$
-in two different measurement processes: measuring $J_{z}$ directly,
-or measuring $J_{z}^{2}$ and then $J_{z}$. These two processes are
-the same because $J_{z}$ and $J_{z}^{2}$ are commuting, and can
-measure simultaneously. However, these two processes are not the same
-in DQT because the first always success, but the second one may produce
-a zero-norm state in the middle. In general, observables cannot measure
-simultaneously in DQT. Because the definition of contextuality is
-based on simultaneously measurement in CQT, we must redefine the contextuality
-in DQT to address this issue.
-
-What does contextuality mean in CQT? Assume:
-\begin{enumerate}
-\item The quantum system were actually classical, i.e., we could assign
-each observable~$\mathbf{O}$ a measurement result~$v\left(\mathbf{O}\right)$
-before we do any measurement.
-\end{enumerate}
-Because whether measuring commuting observables of $\mathbf{O}$ or
-not doesn't change the measurement result of $\mathbf{O}$, it is
-nature to hope this property still hold if the quantum system were
-actually classical. Therefore, we assume:
-\begin{enumerate}[resume]
-\item \label{enu:contextuality}The preassigned measurement result~$v\left(\mathbf{O}\right)$
-of an observable~$\mathbf{O}$ is not changed if we measure the system
-by any other observable commuting to $\mathbf{O}$. (page 207 in~\cite{peres1995quantum})
-\end{enumerate}
-Then, we have the premise of the Kochen-Specker theorem
-\begin{enumerate}[resume]
-\item \label{enu:premise}For a set of commuting projection operator $\proj{n}$,
-if $\left\{ \ket{n}\right\} $ forms a basis, then $\sum_{n}v\left(\proj{n}\right)=1$.
-(page 196 in~\cite{peres1995quantum}).
-\end{enumerate}
-The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
-to be satisfied, so that Assumption (\ref{enu:contextuality}) cannot
-be true.
-
-Schumacher and Westmoreland\cite{2010arXiv1010.5452S} uses Premise
-(\ref{enu:premise}) as the definition of contextuality because it
-seems impossible to discuss the commuting observables in their theory.
-Our paper may do better and use Assumption (\ref{enu:contextuality})
-as contextuality. However, it is not that surprising if Assumption
-(\ref{enu:contextuality}) is false because commuting observables
-cannot be measured simultaneously in DQT anyway. }
+other? According to the postulates in page 207 in Peres~\cite{peres1995quantum},
+the last sentence should be ``To be more precise, as noted by Peres~\cite{peres1995quantum}
+and Mermin~\cite{MerminPRL1990}, it is impossible to predetermine
+definite measurement outcomes for all observables on a system, such
+that the predetermined outcome of any observable does not depend on
+whether we measure the observable alone, or along with arbitrary sets
+of mutually commuting observables.''
+
+Let $v\left(\mathbf{O}\right)$ be the predetermined definite outcome
+of an observable $\mathbf{O}$, then we can define $v'$ on states
+by their projector $v'\left(\ket{n}\right)=v\left(\proj{n}\right)$.
+Because lack of commuting observables in Schumacher and Westmoreland~\cite{2010arXiv1010.5452S},
+they use ``$v'$ is well-defined'' as the definition of non-contextuality.
+
+Besides, if the result of measuring an observable depends on simultaneously
+measuring commuting observables, then the usual slogan ``two commuting
+operators can be simultaneously measured'' is just confusing... }
 
@@
   quantum theory can disrupt what would seem to be trivial
-  contextuality.  To deal with this, we are compelled to explicitly
-  consider, not only the initial and final resources needed to
+  contextuality. \yutsung{I don't understand this sentence...} To deal with
+  this, we are compelled to explicitly consider, not only the initial and final resources needed to
   represent the system and the final measurement outcome, but also the
@@
 of a quantum observable does not depend on any given second observable
-provided it commutes with the first observable, and, nonlocality,
+provided it commutes with the first observable, \yutsung{Should
+be ``contextuality, the statement that the predetermined measurement
+outcome of a quantum observable depends on any given second observable
+although it may commute with the first observable''} and, nonlocality,
 which says that spatially separated measurements in a quantum theory

### 2015-11-30 DQC3.tex
Further remove useless comments on "The Concept of Contextuality and..."

@@
 
-\yutsung{Does the sentences in this paragraph contradict to each
-other? According to the postulates in page 207 in Peres~\cite{peres1995quantum},
+\yutsung{According to the postulates in page 207 in Peres~\cite{peres1995quantum},
 the last sentence should be ``To be more precise, as noted by Peres~\cite{peres1995quantum}
@@
 whether we measure the observable alone, or along with arbitrary sets
-of mutually commuting observables.''
-
-Let $v\left(\mathbf{O}\right)$ be the predetermined definite outcome
-of an observable $\mathbf{O}$, then we can define $v'$ on states
-by their projector $v'\left(\ket{n}\right)=v\left(\proj{n}\right)$.
-Because lack of commuting observables in Schumacher and Westmoreland~\cite{2010arXiv1010.5452S},
-they use ``$v'$ is well-defined'' as the definition of non-contextuality.
-
-Besides, if the result of measuring an observable depends on simultaneously
-measuring commuting observables, then the usual slogan ``two commuting
-operators can be simultaneously measured'' is just confusing... }
+of mutually commuting observables.''}
 

### 2015-12-16 DQC3.tex
Clean up comments in 4.2 Unitary and Hermitian operators in DQT

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Critical Analysis of the Measurement Process in CQT}
+\section{\label{sec:Critical-Analysis-CQT}Critical Analysis of the Measurement
+Process in CQT}
 
@@
 are ready to define unitary and Hermitian operators representing time
-evolutions and observables, respectively. All unitary operators can
+evolution and observables, respectively. All unitary operators can
 represent time-evolution operators. Because a unitary operator~$\mathbf{U}$
@@
 The situation for observables is more delicate. As discussed in section
-3, the measurement result of an observable~$\mathbf{O}$ is a real
-number and a eigenvalue of $\mathbf{O}$; the post-measurment state
-is a physical state as well as an eigenvector of $\mathbf{O}$. However,
-a Hermitian operator~$\mathbf{H}$ over $\ff{p^{2}}$ may not be
-qualified for an observable because $\mathbf{H}$ may not have suitable
-eigenvalues and eigenvectors to define the measurement precess, or
-equavalently $\mathbf{H}$ is not unitarily diagonalizable, for the
-following reasons:
+\ref{sec:Critical-Analysis-CQT}, the measurement result of an observable~$\mathbf{O}$
+is a real eigenvalue of $\mathbf{O}$; the post-measurment state is
+a physical eigenstate of $\mathbf{O}$. However, a Hermitian operator~$\mathbf{H}$
+over $\ff{p^{2}}$ may not be qualified for an observable because
+$\mathbf{H}$ may not have suitable eigenvalues and eigenvectors to
+define the measurement process, or equivalently $\mathbf{H}$ is not
+unitarily diagonalizable, for the following reasons: 
 \begin{enumerate}
-\item \label{enu:eigenvalueCount}$\mathbf{H}$ may lack of eigenvalues.
-\\
-\yutsung{No eigenvalue is a problem, but how to clearly say why no
-enough eigenvalue is a problem?}\\
-Formally, the total multiplicity of eigenvalues of $\mathbf{H}$ in
-$\ff{p^{2}}$ may be less than $d$, where the multiplicity of an
-eigenvalue $\lambda$ is $K_{\lambda}$ means that $\left(x-\lambda\right)^{K_{\lambda}}$
+\item \label{enu:eigenvalueCount}$\mathbf{H}$ may lack eigenvalues. More
+precisely, the total multiplicity of eigenvalues of $\mathbf{H}$
+in $\ff{p^{2}}$ may be less than $d$, where $K_{\lambda}$ is the
+multiplicity of an eigenvalue $\lambda$ means that $\left(x-\lambda\right)^{K_{\lambda}}$
 is a factor of the characteristic polynomial 
 \begin{equation}
-\det\left(\mathbf{A}-x\mathds{1}\right)\textrm{ ,}\label{eq:characteristic}
+\det\left(\mathbf{H}-x\mathds{1}\right)\textrm{ ,}\label{eq:characteristic}
 \end{equation}
 while $\left(x-\lambda\right)^{K_{\lambda}+1}$ is not a factor of
-the characteristic polynomial. This happens because $\ff{p^{2}}$
-is not algebraically closed~\cite{DummitFoote2004} so that the solutions
-of the characteristic polynomial may be in an proper extension field
-of $\ff{p^{2}}$. For example, consider a Hermitian matrix 
+the characteristic polynomial. In another word, $\ff{p^{2}}$ is not
+algebraically closed~\cite{DummitFoote2004}. For example, consider
+a Hermitian matrix 
 \[
@@
 \end{eqnarray*}
-which have no solution in $\ff{9}$ so that their total multiplicities
-are 0 less than 3. In this case, $\mathbf{H}_{1}$ should not be an
-observable because there is no eigenvalue as any measurement result. 
-\item \label{enu:degeneracy}\yutsung{The same. How to say clearly why
-no enough eigenvector is a problem?}\\
- The dimension of an eigenspace may be less than the multiplicity
-of its eigenvalue. For example, consider a Hermitian matrix 
+which have no solution in $\ff{9}$ so that the total multiplicities
+is 0 less than 3. Hence, $\mathbf{H}_{1}$ should not be an observable
+because there is no eigenvalue as any measurement result. 
+\item \label{enu:degeneracy}The dimension of an eigenspace may be less
+than the multiplicity of its eigenvalue. For example, consider a Hermitian
+matrix 
 \[
@@
 The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\left(\begin{array}{cc}
-1 & -1+\rmi\end{array}\right)^{T}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$
+1 & -1+\rmi\end{array}\right)^{T}$. The dimension of the eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$
 are not diagonalizable over $\ff{9}$. If $\mathbf{H}_{2}$ were an
-observable, $\mathbf{H}_{2}$ would always have the outcome of measurement
+observable, $\mathbf{H}_{2}$ would always have the measurement result
 $1$ with the post-measurement state $\left(\begin{array}{cc}
-1 & -1+\rmi\end{array}\right)^{T}$. However, only operator always producing $1$ is the identity operator
-which change no state. Therefore, $\mathbf{H}_{2}$ may not be intuitively
-as an observable.\\
- In order to understand this non-diagonalability, we can diagonalize
-them in $\C$. The eigenvalues of $\mathbf{H}_{2}$ in $\C$ are $1$
-and $-2$. 
+1 & -1+\rmi\end{array}\right)^{T}$. In another word, if we measured $\mathbf{H}_{2}$ by the Stern-Gerlach
+experiment, we would always produce a $\left(\begin{array}{cc}
+1 & -1+\rmi\end{array}\right)^{T}$ beam without even splitting the input beam. This violates our intuitively
+of quantum measurement. Therefore, $\mathbf{H}_{2}$ should not be
+an observable.\\
+In order to understand the reason why $\mathbf{H}_{2}$ is not diagonalizable,
+we can diagonalize $\mathbf{H}_{2}$ in $\C$. The eigenvalues of
+$\mathbf{H}_{2}$ in $\C$ are $1$ and $-2$. 
 \begin{eqnarray*}
--2 & \equiv & 1\left(\bmod p\right)
+-2 & \equiv & 1\left(\bmod3\right)
 \end{eqnarray*}
@@
 of multiplicity $2$ in $\ff{9}$, and the corresponding two eigenspaces
-with dimension $1$ in $\C$ map to one eigenspace still with dimension
-$1$ in $\ff{9}$. 
+with dimension $1$ in $\C$ map to the same eigenspace still with
+dimension $1$ in $\ff{9}$. 
 \item \label{enu:orthonormal}Some eigenvectors are zero-norm so that $\mathbf{H}$
@@
 Over $\ff{9}$, the eigenvalues and eigenvectors of $\mathbf{H}_{3}$
-are $-1-\rmi$ with $\left(\begin{array}{cc}
-1 & -1-\rmi\end{array}\right)^{T}$ and $-1+\rmi$ with $\left(\begin{array}{cc}
-1 & 1+\rmi\end{array}\right)^{T}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the
+are $-1+\rmi$ with $\left(\begin{array}{cc}
+1 & 1+\rmi\end{array}\right)^{T}$ and $-1-\rmi$ with $\left(\begin{array}{cc}
+1 & -1-\rmi\end{array}\right)^{T}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the
 eigenvectors are all zero-normed.\\
- If we diagonalize $\mathbf{H}_{3}$ in $\C$, we have the eigenvalues
-of $\mathbf{H}_{3}$ in $\C$ are $-1\pm\sqrt{2}$. If we extend the
-modulo $p$ to algebraic number by 
+If we diagonalize $\mathbf{H}_{3}$ in $\C$, $\mathbf{H}_{3}$ has
+the eigenvalues $-1\pm\sqrt{2}$. If we extend the modulo $p$ to
+some algebraic numbers by 
 \[
-a\equiv b\left(\bmod p\right)\Leftrightarrow\pm\sqrt{a}\equiv\pm\sqrt{b}\left(\bmod p\right)
+a\equiv b\left(\bmod p\right)\Leftrightarrow\pm\sqrt{a}\equiv\pm\sqrt{b}\left(\bmod p\right)\textrm{ ,}
 \]
@@
 \begin{eqnarray*}
--1\pm\sqrt{2} & \equiv & -1\pm\rmi\left(\bmod p\right)
+-1\pm\sqrt{2} & \equiv & -1\pm\rmi\left(\bmod3\right)\textrm{ ,}
 \end{eqnarray*}
-In another word, although the extended modulo $p$ operation respects
-any field operations and roots, it does not respect the complex conjugate
-so that any definition depend on the complex conjugate may not be
-preserved when we map them into finite fields. \yutsung{Although
-may not need to type it down, need to check the definition of the
-map, passing congruence into square root, and partial homomorphism...
-etc.}
+This means the real eigenvalues in $\C$ may be corresponding to the
+complex eigenvalues in $\ff{p^{2}}$. The complex eigenvalues in $\ff{p^{2}}$
+is further related to the zero-norm eigenstates because if an eigenstate
+is not zero-normed, its corresponding eigenvalue must be in $\ff{p}$.\\
+\yutsung{Although may not need to type it down, need to check the
+definition of the map, passing congruence into square root, and partial
+homomorphism... etc.}
 \end{enumerate}
@@
 still time-evolution operators.
-
-\yutsung{
-I don't know whether there is a relation between the occurrence of
-zero norm post-measurement states and anomalies in the list of possible
-observables, especially we have already required any observables must
-be unitarily diagonalizable.
-
-I am sure I have asked Prof. Lunts ``what we can say for the eigenvalues
-of Hermitian matrices over finite fields,'' and he seems not sure.
-I guess I also asked Prof. Thurston the same question, but I am not
-sure...
-}
 

### 2015-12-22 DQC3.tex
Typed the proof when d = 3 for 4.4 A No-Go Theorem

@@
 \usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{enumitem}		% customizable list environments
+\newlength{\lyxlabelwidth}      % auxiliary length 
+\theoremstyle{plain}
+\newtheorem{thm}{\protect\theoremname}
+\ifx\proof\undefined
+\newenvironment{proof}[1][\protect\proofname]{\par
+\normalfont\topsep6\p@\@plus6\p@\relax
+\trivlist
+\itemindent\parindent
+\item[\hskip\labelsep\scshape #1]\ignorespaces
+}{%
+\endtrivlist\@endpefalse
+}
+\providecommand{\proofname}{Proof}
+\fi
 
@@
 \usepackage{babel}
+\providecommand{\theoremname}{Theorem}
 
@@
 
-\begin{theorem}
-\label{theorem1}
-There is no map $\dpt\colon \ffzd{p^2}\times \ffzd{p^2}
-\longrightarrow [0,1]$ satisfying properties ({\bf i}), ({\bf ii}),
-and ({\bf iii}) when $d> 3$.
-\end{theorem}
+\begin{thm}
+\label{theorem1} There is no map $\dpt\colon\ffzd{p^{2}}\times\ffzd{p^{2}}\longrightarrow[0,1]$
+satisfying properties ({\bf i}), ({\bf ii}), and ({\bf iii})
+when $d>3$. \end{thm}
 %
@@
 \[
-\ket{\Psi}=\alpha\big(\ket{0} + \ket{1} + \ket{2} + \beta\ket{3}\big)
+\ket{\Psi}=\alpha\big(\ket{0}+\ket{1}+\ket{2}+\beta\ket{3}\big)
 \]
-expressed in terms of orthonormal vectors, where $\beta\in \ff{p^2}$
-is chosen so that $\left|\beta\right|^2=p-1$ and $\alpha\in\ff{p^2}$
-is a constant such that $\ket{\Psi}$ is normalized.  Let
-$\ket{\Phi}= \ket{1} + \ket{2} + \beta\ket{3}$. Note that $\ket{\Phi}$
-is normalized in $\ff{p}$.  We can write our original state
-$\ket{\Psi}$ as $\ket{\Psi}=\alpha\big(\ket{0}+\ket{\Phi}\big)$ The
-vectors $\ket{0}$ and $\ket{\Phi}$ are orthonormal and so are part of
-some larger orthonormal basis. Thus by properties ({\bf i}) and ({\bf
-  ii}) we have
+expressed in terms of orthonormal vectors, where $\beta\in\ff{p^{2}}$
+is chosen so that $\left|\beta\right|^{2}=p-1$ and $\alpha\in\ff{p^{2}}$
+is a constant such that $\ket{\Psi}$ is normalized. Let $\ket{\Phi}=\ket{1}+\ket{2}+\beta\ket{3}$.
+Note that $\ket{\Phi}$ is normalized in $\ff{p}$. We can write our
+original state $\ket{\Psi}$ as $\ket{\Psi}=\alpha\big(\ket{0}+\ket{\Phi}\big)$
+The vectors $\ket{0}$ and $\ket{\Phi}$ are orthonormal and so are
+part of some larger orthonormal basis. Thus by properties ({\bf
+i}) and ({\bf ii}) we have 
 \begin{equation}
-1= \dpt\big(\ket{\Psi},\ket{0}\big) +  \dpt\big(\ket{\Psi},\ket{\Phi}\big). \label{prob1}
+1=\dpt\big(\ket{\Psi},\ket{0}\big)+\dpt\big(\ket{\Psi},\ket{\Phi}\big).\label{prob1}
 \end{equation}
-Let $U$ be the unitary map that simply permutes the orthonormal
-vectors $\ket{0}$ and $\ket{\Phi}$.  Note that $\ket{\Psi}$ is
-invariant under $U$, so invoking property ({\bf iii}), we have
+Let $U$ be the unitary map that simply permutes the orthonormal vectors
+$\ket{0}$ and $\ket{\Phi}$. Note that $\ket{\Psi}$ is invariant
+under $U$, so invoking property ({\bf iii}), we have 
 \[
-\dpt\big(\ket{\Psi},\ket{0}\big)=\dpt\big(U\ket{\Psi},U\ket{0}\big) = 
-   \dpt\big(\ket{\Psi},\ket{\Phi}\big) \ .
+\dpt\big(\ket{\Psi},\ket{0}\big)=\dpt\big(U\ket{\Psi},U\ket{0}\big)=\dpt\big(\ket{\Psi},\ket{\Phi}\big)\ .
 \]
@@
 \[
-1= \dpt\big(\ket{\Psi},\ket{0}\big) +  \dpt\big(\ket{\Psi},\ket{0}\big),
+1=\dpt\big(\ket{\Psi},\ket{0}\big)+\dpt\big(\ket{\Psi},\ket{0}\big),
 \]
@@
 \begin{equation}
-\label{prob2}
-\dpt\big(\ket{\Psi},\ket{0}\big)=\dpt\big(\ket{\Psi},
-   \ket{\Phi}\big)=\frac{1}{2} \in [0,1] \ .
+\dpt\big(\ket{\Psi},\ket{0}\big)=\dpt\big(\ket{\Psi},\ket{\Phi}\big)=\frac{1}{2}\in[0,1]\ .\label{prob2}
 \end{equation}
-
-For $i=0,1,2$ let $U_i$ be the unitary map that permutes the basis
-vectors $\ket{0}$ and $\ket{i}$ and acts as the identity for the rest.
-Note that $\ket{\Psi}$ is invariant under $U_i$. So again by property
-({\bf iii}) we have
+\par For $i=0,1,2$ let $U_{i}$ be the unitary map that permutes
+the basis vectors $\ket{0}$ and $\ket{i}$ and acts as the identity
+for the rest. Note that $\ket{\Psi}$ is invariant under $U_{i}$.
+So again by property ({\bf iii}) we have 
 \[
-\dpt\big(\ket{\Psi},\ket{i}\big) =\dpt\big(U_i\ket{\Psi},U_i\ket{0}\big)=
-\dpt\big(\ket{\Psi},\ket{0}\big) = \frac{1}{2}
+\dpt\big(\ket{\Psi},\ket{i}\big)=\dpt\big(U_{i}\ket{\Psi},U_{i}\ket{0}\big)=\dpt\big(\ket{\Psi},\ket{0}\big)=\frac{1}{2}
 \]
 for $i=0,1,2$. These probability assignments are inconsistent with
-the requirement that the probabilities for orthogonal outcomes add up
-to 1. By property ({\bf i})
+the requirement that the probabilities for orthogonal outcomes add
+up to 1. By property ({\bf i}) 
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-so we have a contradiction. The assumption of a satisfactory map
-$\dpt$ is thus false. $\Box$
+so we have a contradiction. The assumption of a satisfactory map $\dpt$
+is thus false. 
 \end{proof}
@@
 more than a single qubit.)
+
+\yutsung{I am going to prove a no-go theorem for $d=3$ here with
+an extra property
+\begin{description}
+\item [{(iv)}] $\dpt(\ket{\Phi},\ket{\Psi})=\dpt(\lambda\ket{\Phi},\ket{\Psi})=\dpt(\ket{\Phi},\lambda\ket{\Psi})$
+where $\lambda\in\ff{p^{2}}^{*}$. 
+\end{description}
+This property means that the phase difference and normalization will
+not effect the probability assignment. Although this property will
+not be used explicitly, considering non-normalized states may simplify
+the proof. 
+\begin{thm}
+\label{theorem1-1} There is no map $\dpt\colon\ffzd{p^{2}}\times\ffzd{p^{2}}\longrightarrow[0,1]$
+satisfying properties ({\bf i}), ({\bf ii}), ({\bf iii}),
+and ({\bf iv}) when $d\ge3$ and $p>3$.\end{thm}
+}
+
+\yutsung{
+\begin{proof}
+Assume such a map $\dpt$ satisfying all four properties exists. Consider
+the orthonormal basis and the non-normalized state 
+\begin{eqnarray*}
+\ket{0} & = & \left(\begin{array}{ccc}
+1 & 0 & 0\end{array}\right)^{T}\\
+\ket{1} & = & \left(\begin{array}{ccc}
+0 & 1 & 0\end{array}\right)^{T}\\
+\ket{2} & = & \left(\begin{array}{ccc}
+0 & 0 & 1\end{array}\right)^{T}\\
+\ket{+} & = & \ket{0}+\ket{1}+\ket{2}\textrm{ ,}
+\end{eqnarray*}
+where $\ket{+}$ is not zero-normed when $p>3$. For $i=1,2$, let
+$\mathbf{U}_{i}$ be the unitary map that permutes the basis vectors
+$\ket{0}$ and $\ket{i}$ and acts as the identity for the rest. Note
+that $\ket{+}$ is invariant under $\mathbf{U}_{i}$. So by property
+({\bf iii}) we have 
+\[
+\dpt\big(\ket{+},\ket{i}\big)=\dpt\big(\mathbf{U}_{i}\ket{+},\mathbf{U}_{i}\ket{0}\big)=\dpt\big(\ket{+},\ket{0}\big)
+\]
+for $i=1,2$. By property ({\bf i}) 
+\begin{eqnarray*}
+\dpt\big(\ket{+},\ket{0}\big)+\dpt\big(\ket{+},\ket{1}\big)+\dpt\big(\ket{+},\ket{2}\big) & = & 1
+\end{eqnarray*}
+so 
+\begin{equation}
+\dpt\big(\ket{+},\ket{i}\big)=\frac{1}{3}\in[0,1]\textrm{ .}\label{prob2-1-1}
+\end{equation}
+
+Let 
+\begin{eqnarray*}
+\mathbf{U}' & = & \left(\begin{array}{ccc}
+\alpha & \alpha & 0\\
+-\alpha & \alpha & 0\\
+0 & 0 & 1
+\end{array}\right)\\
+\ket{\Phi} & = & 2\alpha\ket{0}+\ket{2}=\mathbf{U}'\ket{+}
+\end{eqnarray*}
+where $\alpha\in\ff{p^{2}}$ is chosen so that $2\alpha^{*}\alpha=1$.
+Thus by property ({\bf iii}), we have
+\begin{eqnarray*}
+\dpt\big(\ket{\Phi},\ket{2}\big) & = & \dpt\big(\mathbf{U}'\ket{+},\mathbf{U}'\ket{2}\big)=\dpt\big(\ket{+},\ket{2}\big)\textrm{ .}
+\end{eqnarray*}
+Also, properties ({\bf i}) and ({\bf ii}) imply 
+\begin{eqnarray*}
+1 & = & \dpt\big(\ket{\Phi},\ket{0}\big)+\dpt\big(\ket{\Phi},\ket{2}\big)\textrm{ .}
+\end{eqnarray*}
+This along with equation (\ref{prob2-1-1}) gives 
+\begin{equation}
+\dpt\big(\ket{\Phi},\ket{0}\big)=\frac{2}{3}\in[0,1]\textrm{ .}\label{eq:prob23}
+\end{equation}
+
+\end{proof}
+}
+
+\yutsung{
+\begin{proof}
+Finally, consider 
+\begin{eqnarray*}
+\mathbf{U}'' & = & \left(\begin{array}{ccc}
+1 & 0 & 0\\
+0 & \beta^{*} & 2\alpha\\
+0 & 2\alpha^{*} & \beta
+\end{array}\right)\\
+\ket{\Psi} & = & 2\alpha\left(\ket{0}+\ket{1}\right)+\beta\ket{2}=\mathbf{U}''\ket{\Phi}\textrm{ ,}
+\end{eqnarray*}
+where $\beta\in\ff{p^{2}}$ is chosen so that $\beta^{*}\beta=-1$.
+Because $\ket{\Psi}$ is invariant under $\mathbf{U}_{1}$, invoking
+property ({\bf iii}) with equation (\ref{eq:prob23}), we have
+\begin{eqnarray*}
+ &  & \dpt\big(\ket{\Psi},\ket{1}\big)=\dpt\big(\mathbf{U}_{1}\ket{\Psi},\mathbf{U}_{1}\ket{1}\big)\\
+ & = & \dpt\big(\ket{\Psi},\ket{0}\big)=\dpt\big(\mathbf{U}''\ket{\Phi},\mathbf{U}''\ket{0}\big)\\
+ & = & \dpt\big(\ket{\Phi},\ket{0}\big)=\frac{2}{3}
+\end{eqnarray*}
+These probability assignments are inconsistent with the requirement
+that the probabilities for orthogonal outcomes add up to 1. By property
+({\bf i}) 
+\begin{eqnarray*}
+1 & = & \dpt\big(\ket{\Psi},\ket{0}\big)+\dpt\big(\ket{\Psi},\ket{1}\big)+\dpt\big(\ket{\Psi},\ket{2}\big)\\
+ & = & \frac{2}{3}+\frac{2}{3}+\dpt\big(\ket{\Psi},\ket{2}\big)\\
+ & \geq & \frac{4}{3}\textrm{ ,}
+\end{eqnarray*}
+so we have a contradiction. The assumption of a satisfactory map $\dpt$
+is thus false. 
+\end{proof}
+}
 

### 2016-01-17 DQC3.tex
Review Gleason's Theorem in CQT in "6.1 Gleason's Theorem in DQT"

@@
 \fi
+\theoremstyle{definition}
+\newtheorem{problem}[thm]{\protect\problemname}
 
@@
 %%%%%%%%%%%%%%%%%
-\subsection{Gleason's Theorem in DQT} The Born rule is the \emph{only}
+\subsection{Gleason's Theorem in DQT}
+
+Recall the measurement process discussed in section \ref{sec:Critical-Analysis-CQT}.
+Given a physical system represented by a state $\ket{\Psi}$, and
+an observable ${\mathbf{O}}$, whose eigenspectrum is given by 
+\[
+{\mathbf{O}}\left|i\right\rangle =\lambda_{i}\left|i\right\rangle \ .
+\]
+Then the Born rule of CQT tells us that the probability of obtaining
+the eigenvalue $\lambda_{i}$ as an outcome of the measurement is
+given by 
+\begin{eqnarray}
+\begin{array}{rcccl}
+{\cal P}_{\Psi}\left(\ket{i}\right)={\cal P}_{\Psi}\left(\lambda_{i}\right) & = & {\displaystyle {\frac{\langle\Psi|{P}_{i}|\Psi\rangle}{\ip{\Psi}{\Psi}}}} & = & {\displaystyle {\frac{\ip{\Psi}{i}\ip{i}{\Psi}}{\ip{\Psi}{\Psi}\ip{i}{i}}}}=\Tr\left(\frac{\proj{i}}{\ip{i}{i}}\frac{\proj{\Psi}}{\ip{\Psi}{\Psi}}\right)\end{array}\ ,\label{prob1.eq-6}
+\end{eqnarray}
+If the system is a mixed state represented by a density matrix 
+\[
+\rho=\sum_{j}p_{j}\frac{\proj{\Psi_{j}}}{\ip{\Psi_{j}}{\Psi_{j}}}\textrm{ ,}
+\]
+equation (\ref{prob1.eq-6}) can be extended to 
+\begin{eqnarray}
+{\cal P}_{\rho}\left(\ket{i}\right)={\cal P}_{\rho}\left(\lambda_{i}\right) & = & \Tr\left(\frac{\proj{i}}{\ip{i}{i}}\sum_{j}p_{j}\frac{\proj{\Psi_{j}}}{\ip{\Psi_{j}}{\Psi_{j}}}\right)=\sum_{i}p_{i}\frac{\ip{\Psi_{j}}{i}\ip{i}{\Psi_{j}}}{\ip{\Psi_{j}}{\Psi_{j}}\ip{i}{i}}\label{prob1.eq-2}
+\end{eqnarray}
+Let $\C^{d*}=\left\{ \ket{\Psi}\in\C^{d}\mid\ip{\Psi}{\Psi}\ne0\right\} $,
+then ${\cal P}_{\rho}:\C^{d*}\rightarrow\left[0,1\right]$ defines
+a probability which means ${\cal P}_{\rho}$ satisfies 
+\begin{description}
+\item [{(i')}] For any orthonormal basis $\{\ket{i}\}$ and any state $\ket{\Psi}$,
+${\displaystyle \sum_{i=0}^{d-1}{\cal P}_{\rho}\left(\ket{i}\right)=1}$. 
+\end{description}
+Conversely, if an assignment ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$
+is a probability, i.e., satisfying ({\bf i'}), we can identify
+${\cal P}$ to a mixed state $\rho$ by Gleason's theorem~\cite{Redhead1987-REDINA,gleason1957}\footnote{In order to simplify the statement, we consider consider the probability
+on the state vectors instead of the projectors or closed subspaces
+as in the Gleason's original paper.}.
+\begin{thm}
+(Gleason's Theorem) For $d\ge3$, for any probability ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$,
+there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$.
+\end{thm}
+Consequently, the Born rule is the only reasonable probability assignment,
+and can be deduced by other reasonable axioms~\cite{peres1995quantum}.
+
+Let's move on to Gleason's Theorem in DQT.
+\begin{problem}
+Can we recover Gleason's Theorem in DQT? or more precisely: 
+\begin{enumerate}
+\item Given an assignment $\hat{{\cal P}}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
+in DQT, if $\hat{{\cal P}}$ is a probability, i.e., for any orthonormal
+basis $\{\ket{i}\}$, ${\displaystyle \sum_{i=0}^{d-1}\hat{{\cal P}}\left(\ket{i}\right)=1}$,
+can we say something about $\hat{{\cal P}}$?
+\item Can we induce the Born rule by some reasonable axioms?
+\end{enumerate}
+\end{problem}
+In order to answer the first problem, we need to define the mixed
+state in DQT.
+
+\yutsung{The Born rule is the \emph{only}
 way to assign a probability in conventional quantum theory because of
@@
 we have substituted the condition (\ref{enu:unitary-DQT(I)}) for the
-conventional continuity axiom in Gleason's Theorem.
+conventional continuity axiom in Gleason's Theorem.}
 

### 2016-01-18 DQC3.tex
Update "6.1 Gleason's Theorem in DQT"...

@@
 \theoremstyle{definition}
-\newtheorem{problem}[thm]{\protect\problemname}
+\newtheorem{problem}[thm]{Problem}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{sec:Critical-Analysis-CQT}Critical Analysis of the Measurement
-Process in CQT}
+\section{\label{sec:Critical-Analysis-CQT}Critical
+Analysis of the Measurement Process in CQT}
 
@@
 %%%%%%%%%%%%%%%%%
-\subsection{A No-Go Theorem}
+\subsection{\label{sub:A-No-Go-Theorem}A No-Go Theorem}
 
@@
 \begin{description}
-\item [{(iv)}] $\dpt(\ket{\Phi},\ket{\Psi})=\dpt(\lambda\ket{\Phi},\ket{\Psi})=\dpt(\ket{\Phi},\lambda\ket{\Psi})$
-where $\lambda\in\ff{p^{2}}^{*}$. 
+\item [{(iv)}] $\dpt(\ket{\Phi},\ket{\Psi})=\dpt(\gamma\ket{\Phi},\ket{\Psi})=\dpt(\ket{\Phi},\gamma\ket{\Psi})$
+where $\gamma\in\ff{p^{2}}^{*}$. 
 \end{description}
@@
 %%%%%%%%%%%%%%%%%
-\subsection{Interval-Valued Probabilities for DQT}
+\subsection{\label{sub:Interval-Valued-Probabilities-DQT}Interval-Valued
+Probabilities for DQT}
 
@@
 \]
-equation (\ref{prob1.eq-6}) can be extended to 
+the Born rule (\ref{prob1.eq-6}) can be extended to 
 \begin{eqnarray}
@@
 a probability which means ${\cal P}_{\rho}$ satisfies 
-\begin{description}
-\item [{(i')}] For any orthonormal basis $\{\ket{i}\}$ and any state $\ket{\Psi}$,
-${\displaystyle \sum_{i=0}^{d-1}{\cal P}_{\rho}\left(\ket{i}\right)=1}$. 
-\end{description}
+\begin{equation}
+\textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ and any state }\ket{\Psi}\textrm{ , }{\displaystyle \sum_{i=0}^{d-1}{\cal P}_{\rho}\left(\ket{i}\right)=1}\label{eq:total-probability}
+\end{equation}
+
 Conversely, if an assignment ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$
-is a probability, i.e., satisfying ({\bf i'}), we can identify
-${\cal P}$ to a mixed state $\rho$ by Gleason's theorem~\cite{Redhead1987-REDINA,gleason1957}\footnote{In order to simplify the statement, we consider consider the probability
+is a probability, i.e., satisfying equation (\ref{eq:total-probability}),
+we can identify ${\cal P}$ to a mixed state $\rho$ by Gleason's
+theorem.
+\begin{thm}
+(Gleason's Theorem) 
+\begin{enumerate}
+\item For $d\ge3$, for any probability ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$,
+there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$~\cite{Redhead1987-REDINA,gleason1957}.\footnote{In order to simplify the statement, we consider consider the probability
 on the state vectors instead of the projectors or closed subspaces
-as in the Gleason's original paper.}.
+as in the Gleason's original paper.}
+\item Consequently, the Born rule (\ref{prob1.eq-6}) is the only reasonable
+probability assignment, and can be deduced by other reasonable axioms~\cite{peres1995quantum}. 
+\end{enumerate}
+\end{thm}
+Let's move on to Gleason's Theorem in DQT. Can we recover Gleason's
+Theorem in DQT? or more precisely: 
+\begin{problem}
+Given an assignment $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
+in DQT, if $\hat{\pi}$ is a probability, i.e., 
+\begin{equation}
+\textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \bigvee_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}\textrm{possible , }\label{eq:total-probability-DQT}
+\end{equation}
+can we say something about $\hat{\pi}$?
+\end{problem}
+The answer is no, and the reasons are simple. First, compare the following
+arithmetic equation and Boolean equation.
+\begin{eqnarray}
+p_{1}+p_{2}+p_{3} & = & 1\label{eq:arithmetic}\\
+\pi_{1}\vee\pi_{2}\vee\pi_{3} & = & \text{possible}\label{eq:Boolean}
+\end{eqnarray}
+When $p_{1}=\frac{1}{2}$, we still have an equality $p_{2}+p_{3}=1$
+for $p_{2}$ and $p_{3}$ because $\left(\mathbb{R},0,+\right)$ is
+a group. In contrast, when $\pi_{1}=\text{possible}$, we know nothing
+about $\pi_{2}$ and $\pi_{3}$ because the semigroup$\left(\mathscr{L}_{2},\text{impossible},\vee\right)$
+is not cancellative, i.e., $a\vee c=b\vee c$ does not imply $a=b$.
+This suggests to study the range of the probability. Consider the
+range has the structure $\left(\underline{\mathscr{L}},\mathscr{L},0,1,\oplus,<\right)$,
+where $\left(\underline{\mathscr{L}},0,\oplus,<\right)$ is the underlying
+commutative ordered semigroup~\cite{clifford1958}, $\mathscr{L}\subseteq\underline{\mathscr{L}}$
+is the allowed range value, $1\in\mathscr{L}'\subseteq\mathscr{L}$
+is another special value, and for all $x\in\mathscr{L}$, we have
+$0<x<1$. For example, $\left(\mathscr{L}_{2},\mathscr{L}_{2},\text{impossible},\text{possible},\vee,<\right)$
+and $\left(\mathbb{R},\left[0,1\right],0,1,+,<\right)$ are two possible
+range of the probability, but we cannot pick $\underline{\mathscr{L}}=\ff{p^{2}}$
+because we cannot define an inequality such that $\left(\ff{p^{2}},0,+,<\right)$
+be an ordered semigroup.
+
+Second, Gleason's theorem relies a lot on the continuous probability~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum},
+but continuity doesn't even make sense in DQT. This fact implies that
+the structure of the domain of the probability, $\ffzd{p^{2}}$, is
+also too weak. In order to think which structure we need, let's check
+which the reasonable property ${\cal P}_{\Psi}:\C^{d*}\rightarrow\left[0,1\right]$
+should have. Despite the total probability is one, ${\cal P}_{\Psi}$
+must have 
+\begin{eqnarray}
+{\cal P}_{\Psi}\left(\ket{i}\right) & = & 0\textrm{ if }\ip{\Psi}{i}=0\label{prob1.eq-6-1}\\
+{\cal P}_{\Psi}\left(\ket{i}\right) & = & {\cal P}_{\Psi}\left(\gamma\ket{i}\right)\textrm{ ,}
+\end{eqnarray}
+where $\gamma\in\C^{*}$. Moreover, the probability must be invariant
+under any rotation, i.e., 
+\begin{equation}
+{\cal P}_{U\Psi}\left(U\ket{i}\right)={\cal P}_{\Psi}\left(\ket{i}\right)\label{eq:rotation}
+\end{equation}
+for any unitary matrix $U$. Because we consider ${\cal P}_{\Psi}$
+and ${\cal P}_{U\Psi}$ together, the first part of Gleason's theorem
+doesn't really make sense, but we can still ask whether there is an
+unique ``Born rule'' satisfying all the conditions. If we add these
+three conditions, our problem becomes
+\begin{problem}
+\label{prob:Gleason's}Is there a structure $\left(\underline{\mathscr{L}},\mathscr{L},0,1,\oplus,<\right)$
+such that $\tilde{\pi}:\ffzd{p^{2}}\times\ffzd{p^{2}}\rightarrow\mathscr{L}$
+satisfying the following conditions is unique for $d\ge3$ and infinitely
+many for $d=2$? 
+\begin{eqnarray}
+ & \bullet & \textrm{For any orthonormal basis }\left\{ \ket{i}\right\} _{n=0}^{d-1}\subset\ffzd{p^{2}}\textrm{, }\label{enu:total-probability-DQT(I)}\\
+ &  & \textrm{ \ensuremath{{\displaystyle \bigoplus_{i=0}^{d-1}\tilde{\pi}\left(\ket{\Psi},\ket{i}\right)=1}} .}\nonumber \\
+ & \bullet & \textrm{If }\braket{\Psi}{i}=0\textrm{ ,}\nonumber \\
+ &  & \textrm{then }\tilde{\pi}\left(\ket{\Psi},\ket{i}\right)=0\textrm{ .}\label{enu:particular-vector-DQT(I)}\\
+ & \bullet & \textrm{For any vector }\ket{\Psi},\ket{i}\in\ffzd{p^{2}}\textrm{, }\nonumber \\
+ &  & \textrm{and }U\textrm{ is a }d\textrm{-by-}d\textrm{ unitary matrix over }\ff{p^{2}}\textrm{, }\label{enu:unitary-DQT(I)}\\
+ &  & \textrm{i.e. , }U^{\dagger}U=I\textrm{, then }\tilde{\pi}(\ket{\Psi},\ket{i})=\tilde{\pi}(U\ket{\Psi},U\ket{i})\textrm{. }\nonumber \\
+ & \bullet & \textrm{For any vector }\ket{\Psi},\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{, }\nonumber \\
+ &  & \dpr(\ket{\Psi},\ket{\Phi})=\dpr(\gamma\ket{\Psi},\ket{\Phi})=\dpr(\ket{\Psi},\gamma\ket{\Phi})\textrm{. }\label{enu:parallel-DQT(I)}
+\end{eqnarray}
+
+\end{problem}
+The no-go theorem in section \ref{sub:A-No-Go-Theorem} said the if
+$\left(\underline{\mathscr{L}},\mathscr{L},0,1,\oplus,<\right)=\left(\mathbb{R},\left[0,1\right],0,1,+,<\right)$,
+there is no $\tilde{\pi}:\ffzd{p^{2}}\times\ffzd{p^{2}}\rightarrow\mathscr{L}$
+for $d\ge3$. It is easy to extend the no-go theorem and prove 
 \begin{thm}
-(Gleason's Theorem) For $d\ge3$, for any probability ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$,
-there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$.
+If $\left(\underline{\mathscr{L}},0,\oplus,<\right)$ is a ordered
+group, then there is no $\tilde{\pi}:\ffzd{p^{2}}\times\ffzd{p^{2}}\rightarrow\mathscr{L}$
+satisfying all conditions in problem \ref{prob:Gleason's} for $d\ge3$.
 \end{thm}
-Consequently, the Born rule is the only reasonable probability assignment,
-and can be deduced by other reasonable axioms~\cite{peres1995quantum}.
-
-Let's move on to Gleason's Theorem in DQT.
-\begin{problem}
-Can we recover Gleason's Theorem in DQT? or more precisely: 
-\begin{enumerate}
-\item Given an assignment $\hat{{\cal P}}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
-in DQT, if $\hat{{\cal P}}$ is a probability, i.e., for any orthonormal
-basis $\{\ket{i}\}$, ${\displaystyle \sum_{i=0}^{d-1}\hat{{\cal P}}\left(\ket{i}\right)=1}$,
-can we say something about $\hat{{\cal P}}$?
-\item Can we induce the Born rule by some reasonable axioms?
-\end{enumerate}
-\end{problem}
-In order to answer the first problem, we need to define the mixed
-state in DQT.
-
-\yutsung{The Born rule is the \emph{only}
-way to assign a probability in conventional quantum theory because of
-Gleason's theorem.  We now show that $\dpr $ defined in
-Eq. (\ref{eq:modality}) is an example of a properly defined Born rule
-in the discrete theory because $\dpr $ also satisfies the closest
-analog of Gleason's Theorem that we can construct.
-
-Following the standard axioms for Gleason's
-theorem~\cite{peres1995quantum}, we introduce discrete axioms that
-differ in only one significant instance from the classical ones:
-\begin{eqnarray}
- & \bullet & \textrm{For any orthogonal basis }\left\{
-  \left| n \right\rangle \right\}
-  _{n=0}^{d-1}\subset\ffzd{p^{2}}\textrm{, and
-  }\label{enu:total-probability-DQT(I)}\\ & &
-  \ket{\Psi}\in\ffzd{p^{2}}\textrm{, at least one of\ }
-  \dpr \left(\ket{\Psi},\ket{n}\right) = \text{possible.}\nonumber \\ &
-  \bullet & \textrm{For any orthogonal basis }
-\left\{  \left| n \right\rangle
-\right\}_{n=0}^{d-1}\subset\ffzd{p^{2}}\nonumber \\ & &
- \textrm{and a particular\ }\ket{n'}\in\left\{ \left| n \right\rangle \right\}
-  _{n=0}^{d-1}\textrm{, }\nonumber \\ & &
-  \dpr\big(\ket{n'},\ket{n'}\big)=\text{possible and\ }
-   \label{enu:particular-vector-DQT(I)}\\ & &
-  \dpr\big(\ket{n'},\ket{n}\big)=\text{impossible for any }n\ne  n'
-   \textrm{. }\nonumber \\ & \bullet & \textrm{For any vector  }
-   \ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}
-  \textrm{, and  }\gamma\in\ff{p^{2}}\backslash\left\{ 0\right\} 
-  \textrm{, }\nonumber
-  \\ & &
-  \dpr (\ket{\Psi},\ket{\Phi})=\dpr (\gamma\ket{\Psi},\ket{\Phi}) = 
-    \dpr (\ket{\Psi},\gamma\ket{\Phi}) \textrm{. }
-  \label{enu:parallel-DQT(I)}\\
- & \bullet & \textrm{For any vector
-  }\ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}
-  \textrm{, }\nonumber \\ & &
-  \textrm{and }U\textrm{ is a }d\textrm{-by-}d
-  \textrm{ unitary matrix over }\ff{p^{2}}\textrm{, }
-  \label{enu:unitary-DQT(I)}\\ & &
-  \textrm{i.e. , }U^{\dagger}U=I\textrm{, then  }
-   \dpr (\ket{\Psi},\ket{\Phi})=\dpr (U\ket{\Psi},U\ket{\Phi})\textrm{. }\nonumber
-\end{eqnarray}
-Because there is no possibility for continuity in the discrete theory,
-we have substituted the condition (\ref{enu:unitary-DQT(I)}) for the
-conventional continuity axiom in Gleason's Theorem.}
+When we consider $\left(\mathscr{L}_{2},\mathscr{L}_{2},\text{impossible},\text{possible},\vee,<\right)$,
+$\dpr$ defined in section \ref{sub:Interval-Valued-Probabilities-DQT}
+satisfies all conditions, but $\dpr$ is not the unique solution because
+of lack of cancellation law. It is still an open question whether
+problem \ref{prob:Gleason's} is true or false in general.
 

### 2016-01-26 DQC3.tex
Update "6.1 Gleason's Theorem in DQT"...

--- 2015-12-22 DQC3.tex
@@
 \fi
+\theoremstyle{definition}
+\newtheorem{problem}[thm]{Problem}
 
@@
 %%%%%%%%%%%%%%%%%
-\subsection{Gleason's Theorem in DQT} The Born rule is the \emph{only}
-way to assign a probability in conventional quantum theory because of
-Gleason's theorem.  We now show that $\dpr $ defined in
-Eq. (\ref{eq:modality}) is an example of a properly defined Born rule
-in the discrete theory because $\dpr $ also satisfies the closest
-analog of Gleason's Theorem that we can construct.
-
-Following the standard axioms for Gleason's
-theorem~\cite{peres1995quantum}, we introduce discrete axioms that
-differ in only one significant instance from the classical ones:
+\subsection{Gleason's Theorem in DQT}
+
+Recall the measurement process discussed in section \ref{sec:Critical-Analysis-CQT}.
+Given a physical system represented by a state $\ket{\Psi}$, and
+an observable ${\mathbf{O}}$, whose eigenspectrum is given by ${\mathbf{O}}\left|i\right\rangle =\lambda_{i}\left|i\right\rangle $.
+Then the Born rule of CQT tells us that the probability of obtaining
+the eigenvalue $\lambda_{i}$ as an outcome of the measurement is
+given by 
 \begin{eqnarray}
- & \bullet & \textrm{For any orthogonal basis }\left\{
-  \left| n \right\rangle \right\}
-  _{n=0}^{d-1}\subset\ffzd{p^{2}}\textrm{, and
-  }\label{enu:total-probability-DQT(I)}\\ & &
-  \ket{\Psi}\in\ffzd{p^{2}}\textrm{, at least one of\ }
-  \dpr \left(\ket{\Psi},\ket{n}\right) = \text{possible.}\nonumber \\ &
-  \bullet & \textrm{For any orthogonal basis }
-\left\{  \left| n \right\rangle
-\right\}_{n=0}^{d-1}\subset\ffzd{p^{2}}\nonumber \\ & &
- \textrm{and a particular\ }\ket{n'}\in\left\{ \left| n \right\rangle \right\}
-  _{n=0}^{d-1}\textrm{, }\nonumber \\ & &
-  \dpr\big(\ket{n'},\ket{n'}\big)=\text{possible and\ }
-   \label{enu:particular-vector-DQT(I)}\\ & &
-  \dpr\big(\ket{n'},\ket{n}\big)=\text{impossible for any }n\ne  n'
-   \textrm{. }\nonumber \\ & \bullet & \textrm{For any vector  }
-   \ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}
-  \textrm{, and  }\gamma\in\ff{p^{2}}\backslash\left\{ 0\right\} 
-  \textrm{, }\nonumber
-  \\ & &
-  \dpr (\ket{\Psi},\ket{\Phi})=\dpr (\gamma\ket{\Psi},\ket{\Phi}) = 
-    \dpr (\ket{\Psi},\gamma\ket{\Phi}) \textrm{. }
-  \label{enu:parallel-DQT(I)}\\
- & \bullet & \textrm{For any vector
-  }\ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}
-  \textrm{, }\nonumber \\ & &
-  \textrm{and }U\textrm{ is a }d\textrm{-by-}d
-  \textrm{ unitary matrix over }\ff{p^{2}}\textrm{, }
-  \label{enu:unitary-DQT(I)}\\ & &
-  \textrm{i.e. , }U^{\dagger}U=I\textrm{, then  }
-   \dpr (\ket{\Psi},\ket{\Phi})=\dpr (U\ket{\Psi},U\ket{\Phi})\textrm{. }\nonumber
+\begin{array}{rcccl}
+{\cal P}_{\Psi}\left(\ket{i}\right) & = & {\cal P}_{\Psi}\left(\lambda_{i}\right) & = & \frac{\ip{\Psi}{i}\ip{i}{\Psi}}{\ip{\Psi}{\Psi}\ip{i}{i}}\end{array}\ ,\label{prob1.eq-6}
 \end{eqnarray}
-Because there is no possibility for continuity in the discrete theory,
-we have substituted the condition (\ref{enu:unitary-DQT(I)}) for the
-conventional continuity axiom in Gleason's Theorem.
+If the system is a mixed state represented by a density matrix 
+\[
+\rho=\sum_{j}p_{j}\frac{\proj{\Psi_{j}}}{\ip{\Psi_{j}}{\Psi_{j}}}\textrm{ ,}
+\]
+we can extend the Born rule (\ref{prob1.eq-6}) and get 
+\begin{eqnarray}
+{\cal P}_{\rho}\left(\ket{i}\right)={\cal P}_{\rho}\left(\lambda_{i}\right) & = & \sum_{i}p_{i}\frac{\ip{\Psi_{j}}{i}\ip{i}{\Psi_{j}}}{\ip{\Psi_{j}}{\Psi_{j}}\ip{i}{i}}\label{prob1.eq-2}
+\end{eqnarray}
+
+Let $\C^{*}=\C\backslash\left\{ 0\right\} $ and $\C^{d*}=\left\{ \ket{\Psi}\in\C^{d}\mid\ip{\Psi}{\Psi}\ne0\right\} $
+be the set of non-zero vectors. Because normalization and global phase
+gives the same state, and ${\cal P}_{\rho}:\C^{d*}\rightarrow\left[0,1\right]$
+should be a state-function, we should have 
+\begin{equation}
+\textrm{For any vector }\ket{i}\in\C^{d*}\textrm{, and }\gamma\in\C^{*}\textrm{ , }{\cal P}_{\rho}(\ket{i})={\cal P}_{\rho}(\gamma\ket{i})\textrm{ .}\label{eq:parallel-DQT(I)}
+\end{equation}
+More importantly, ${\cal P}_{\rho}$ defines a probability which means
+\begin{equation}
+\textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \sum_{i=0}^{d-1}{\cal P}_{\rho}\left(\ket{i}\right)=1}\textrm{ .}\label{eq:total-probability}
+\end{equation}
+Conversely, if a state-function ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$
+is a probability, i.e., satisfying equation (\ref{eq:parallel-DQT(I)})
+and (\ref{eq:total-probability}), we can identify ${\cal P}$ to
+a mixed state $\rho$ by Gleason's theorem.
+\begin{thm}
+(Gleason's Theorem) 
+\begin{enumerate}
+\item For $d\ge3$, for any state-function ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$,
+if ${\cal P}$ is a probability, there is a density matrix $\rho$
+such that ${\cal P}={\cal P}_{\rho}$~\cite{Redhead1987-REDINA,gleason1957}.\footnote{In order to simplify the statement, we consider consider the probability
+on the state vectors instead of the projectors or closed subspaces
+as in the Gleason's original paper.}
+\item Consequently, the Born rule (\ref{prob1.eq-6}) is the only reasonable
+probability assignment, and can be deduced by other reasonable axioms~\cite{peres1995quantum}. 
+\end{enumerate}
+\end{thm}
+Notice that every state is an equivalence class of $\C^{d*}$, but
+we cannot really get them directly by a physical measurement. All
+we can get from a physical measurement is the probability ${\cal P}$.
+An important meaning of Gleason's theorem is that the state space
+is sufficient enough to produce every probability. Hence, we don't
+have to introduce a new state to explain the probability got from
+a measurement. This may be analog to the fact that every algebraic
+equation over $\C$ can be solved in $\C$ so that we don't have to
+introduce new numbers to solve an equation. The other important meaning
+of Gleason's theorem is that it implies the Born rule (\ref{prob1.eq-6}).
+This is even more important for building a discrete quantum theory.
+If we plug in vectors over $\ff{p^{2}}$ into the usual Born rule
+(\ref{prob1.eq-6}), it gives an elements in $\ff{p}$ which has no
+way interpreted as a probability. Everyone who tried to build a quantum
+theory over finite fields struggled on how to define a reasonable
+probability. If Gleason's theorem works in any sense over finite fields,
+we can have a reasonable way to induce the Born rule over finite fields.
+
+A naive way to extend Gleason's Theorem in DQT may be as follow.
+\begin{problem}
+Given a state-function $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
+which is also a probability, i.e., 
+\begin{eqnarray}
+ &  & \textrm{For any vector }\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{ , }\hat{\pi}(\ket{i})=\hat{\pi}(\gamma\ket{i})\textrm{ . }\label{eq:parallel-DQT}\\
+ &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \bigvee_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}\textrm{possible . }\label{eq:total-probability-DQT}
+\end{eqnarray}
+Can we say something about $\hat{\pi}$?
+\end{problem}
+The answer is no, and the reasons are simple. First, compare the following
+arithmetic equation and Boolean equation.
+\begin{eqnarray}
+p_{1}+p_{2}+p_{3} & = & 1\label{eq:arithmetic}\\
+\pi_{1}\vee\pi_{2}\vee\pi_{3} & = & \text{possible}\label{eq:Boolean}
+\end{eqnarray}
+When $p_{1}=\frac{1}{2}$, we still have an equality $p_{2}+p_{3}=1$
+for $p_{2}$ and $p_{3}$ because $\left(\mathbb{R},0,+\right)$ is
+a group. In contrast, when $\pi_{1}=\text{possible}$, we know nothing
+about $\pi_{2}$ and $\pi_{3}$ because $\left(\mathscr{L}_{2},\text{impossible},\vee\right)$
+is a semigroup without cancellative, i.e., $a\vee c=b\vee c$ does
+not imply $a=b$. The difference between $\left(\mathbb{R},0,+\right)$
+and $\left(\mathscr{L}_{2},\text{impossible},\vee\right)$ suggests
+us to study the range of the probability. A reasonable range should
+have the structure $\left(\mathscr{L},0,1,\oplus,<\right)$, where
+$\left(\mathscr{L},0,\oplus,<\right)$ is the underlying commutative
+ordered semigroup~\cite{clifford1958} because the condition (\ref{eq:total-probability})
+and (\ref{eq:total-probability-DQT}) suggests the value of the range
+should be able to add together. $1\in\mathscr{L}$ is another special
+value to indicate the total probability. For example, $\left(\mathscr{L}_{2},\text{impossible},\text{possible},\vee,<\right)$
+and $\left(\mathbb{R},0,1,+,<\right)$ are two possible range of the
+probability, but we cannot pick $\mathscr{L}=\ff{p^{2}}$ because
+we cannot define an inequality such that $\left(\ff{p^{2}},0,+,<\right)$
+be an ordered semigroup.
+
+Second, Gleason's theorem relies a lot on the continuous probability~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.
+However, continuity doesn't even make sense in DQT. This fact implies
+that the structure of the domain of the probability, $\ffzd{p^{2}}$,
+is also too weak. In order to think which structure we need, we can
+check which the reasonable property ${\cal P}_{\Psi}:\C^{d*}\rightarrow\left[0,1\right]$
+should have. Despite the total probability is one, ${\cal P}_{\Psi}$
+must have 
+\begin{eqnarray}
+{\cal P}_{\Psi}\left(\ket{i}\right) & = & 0\textrm{ if }\ip{\Psi}{i}=0\label{prob1.eq-6-1}
+\end{eqnarray}
+where $\gamma\in\C^{*}$. Moreover, the probability must be invariant
+under any rotation, i.e., 
+\begin{equation}
+{\cal P}_{U\Psi}\left(U\ket{i}\right)={\cal P}_{\Psi}\left(\ket{i}\right)\label{eq:rotation}
+\end{equation}
+for any unitary matrix $U$. Because we consider the probability of
+two different state ${\cal P}_{\Psi}$ and ${\cal P}_{U\Psi}$ together,
+it may be more reasonable to ask whether there is an unique ``Born
+rule'' satisfying all the conditions, and our problem becomes
+\begin{problem}
+\label{prob:Gleason's}Is there a structure $\left(\mathscr{L},0,1,\oplus,<\right)$
+such that $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\left(\ffzd{p^{2}}\rightarrow\left\{ x\in\mathscr{L}\middle|0\le x\le1\right\} \right)$
+satisfying the following conditions is unique for $d\ge3$ and infinitely
+many for $d=2$?\footnote{Instead of equation (\ref{enu:particular-vector-DQT(I)}), another
+reasonable condition is $\braket{\Psi}{i}=0\Leftrightarrow\tilde{\pi}_{\Psi}\left(\ket{i}\right)=0$.
+However, when the underlying group $\mathscr{L}=\mathscr{L}_{2}$,
+this condition implies an unique solution for $d=2$. This is too
+strong and is not what we want. } 
+\begin{eqnarray}
+ & \bullet & \textrm{For any orthonormal basis }\left\{ \ket{i}\right\} _{n=0}^{d-1}\subset\ffzd{p^{2}}\textrm{, }\label{enu:total-probability-DQT(I)}\\
+ &  & \textrm{ \ensuremath{{\displaystyle \bigoplus_{i=0}^{d-1}\tilde{\pi}_{\Psi}\left(\ket{i}\right)=1}} .}\nonumber \\
+ & \bullet & \textrm{If }\braket{\Psi}{i}=0\textrm{ ,}\textrm{then }\tilde{\pi}_{\Psi}\left(\ket{i}\right)=0\textrm{ .}\label{enu:particular-vector-DQT(I)}\\
+ & \bullet & \textrm{For any vector }\ket{\Psi},\ket{i}\in\ffzd{p^{2}}\textrm{, }\nonumber \\
+ &  & \textrm{and }U\textrm{ is a }d\textrm{-by-}d\textrm{ unitary matrix over }\ff{p^{2}}\textrm{, }\label{enu:unitary-DQT(I)}\\
+ &  & \textrm{i.e. , }U^{\dagger}U=I\textrm{, then }\tilde{\pi}_{\Psi}(\ket{i})=\tilde{\pi}_{U\Psi}(U\ket{i})\textrm{. }\nonumber \\
+ & \bullet & \textrm{For any vector }\ket{\Psi},\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{, }\nonumber \\
+ &  & \tilde{\pi}_{\Psi}(\ket{i})=\tilde{\pi}_{\Psi}(\gamma\ket{i})\textrm{. }\label{enu:parallel-DQT(I)}
+\end{eqnarray}
+
+\end{problem}
+The no-go theorem in section \ref{sub:A-No-Go-Theorem} said the if
+$\left(\mathscr{L},0,1,\oplus,<\right)=\left(\mathbb{R},0,1,+,<\right)$,
+there is no $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\ffzd{p^{2}}\rightarrow\mathscr{L}$
+for $d\ge3$. It is easy to extend the no-go theorem and prove 
+\begin{thm}
+If $\left(\mathscr{L},0,\oplus,<\right)$ is a ordered group, then
+there is no $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\ffzd{p^{2}}\rightarrow\mathscr{L}$
+satisfying all conditions in problem \ref{prob:Gleason's} for $d\ge3$.
+\end{thm}
+When we consider $\left(\mathscr{L}_{2},\text{impossible},\text{possible},\vee,<\right)$,
+$\dpr$ defined in section \ref{sub:Interval-Valued-Probabilities-DQT}
+satisfies all conditions, but $\dpr$ is not the unique solution because
+of lack of cancellation law. It is still an open question whether
+problem \ref{prob:Gleason's} is true or false in general.
+
+\yutsung{Is that all probability value should be distinct be an reasonable
+condition?}
 

### 2016-01-27 DQC3.tex
Update "6.1 Gleason's Theorem in DQT"...

@@
 \item Consequently, the Born rule (\ref{prob1.eq-6}) is the only reasonable
-probability assignment, and can be deduced by other reasonable axioms~\cite{peres1995quantum}. 
+probability assignment, and can be deduced by other reasonable axioms~\cite{peres1995quantum,inun.606849520040101}. 
 \end{enumerate}
 \end{thm}
-Notice that every state is an equivalence class of $\C^{d*}$, but
-we cannot really get them directly by a physical measurement. All
-we can get from a physical measurement is the probability ${\cal P}$.
 An important meaning of Gleason's theorem is that the state space
-is sufficient enough to produce every probability. Hence, we don't
-have to introduce a new state to explain the probability got from
-a measurement. This may be analog to the fact that every algebraic
-equation over $\C$ can be solved in $\C$ so that we don't have to
-introduce new numbers to solve an equation. The other important meaning
-of Gleason's theorem is that it implies the Born rule (\ref{prob1.eq-6}).
-This is even more important for building a discrete quantum theory.
-If we plug in vectors over $\ff{p^{2}}$ into the usual Born rule
-(\ref{prob1.eq-6}), it gives an elements in $\ff{p}$ which has no
-way interpreted as a probability. Everyone who tried to build a quantum
-theory over finite fields struggled on how to define a reasonable
-probability. If Gleason's theorem works in any sense over finite fields,
-we can have a reasonable way to induce the Born rule over finite fields.
+is sufficient enough to produce every possible probability we get
+from an experiment. Hence, we don't have to worry about whether there
+is a chance that the probability got from a measurement cannot be
+explained by a state, and we need to introduce a new state. This may
+be analog to the fact that every algebraic equation over $\C$ can
+be solved in $\C$ so that we don't have to introduce new numbers
+to solve an equation. The other important meaning of Gleason's theorem
+is that it implies the Born rule (\ref{prob1.eq-6}). This is even
+more important for building a discrete quantum theory. If we plug
+in vectors over $\ff{p^{2}}$ into the usual Born rule (\ref{prob1.eq-6}),
+it gives an elements in $\ff{p}$ which has no way interpreted as
+a probability. Everyone who tried to build a quantum theory over finite
+fields struggled on how to define a reasonable probability. If Gleason's
+theorem works in any sense over finite fields, we can have a reasonable
+way to induce the Born rule over finite fields.
 

### 2016-01-27 DQC3.tex
"6.1 Gleason's Theorem in DQT" Updated...

@@
 \item Consequently, the Born rule (\ref{prob1.eq-6}) is the only reasonable
-probability assignment, and can be deduced by other reasonable axioms~\cite{peres1995quantum,inun.606849520040101}. 
+probability assignment, and can be deduced by other reasonable axioms~\cite{peres1995quantum}. 
 \end{enumerate}
@@
 it gives an elements in $\ff{p}$ which has no way interpreted as
-a probability. Everyone who tried to build a quantum theory over finite
-fields struggled on how to define a reasonable probability. If Gleason's
-theorem works in any sense over finite fields, we can have a reasonable
-way to induce the Born rule over finite fields.
+a probability. Hence, everyone who tried to build a quantum theory
+over finite fields struggled on how to define a reasonable probability.
+If Gleason's theorem works in any sense over finite fields, we can
+have a reasonable way to induce the Born rule over finite fields.
 

### 2016-01-28 DQC3.tex
Type something in "6.1 Gleason's Theorem in DQT"...

@@
 \begin{eqnarray}
-{\cal P}_{\rho}\left(\ket{i}\right)={\cal P}_{\rho}\left(\lambda_{i}\right) & = & \sum_{i}p_{i}\frac{\ip{\Psi_{j}}{i}\ip{i}{\Psi_{j}}}{\ip{\Psi_{j}}{\Psi_{j}}\ip{i}{i}}\label{prob1.eq-2}
+{\cal P}_{\rho}\left(\ket{i}\right)={\cal P}_{\rho}\left(\lambda_{i}\right) & = & \sum_{j}p_{j}{\cal P}_{\Psi_{j}}\left(\ket{i}\right)\label{prob1.eq-2}
 \end{eqnarray}
@@
 Conversely, if a state-function ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$
-is a probability, i.e., satisfying equation (\ref{eq:parallel-DQT(I)})
-and (\ref{eq:total-probability}), we can identify ${\cal P}$ to
-a mixed state $\rho$ by Gleason's theorem.
+is a probability, we can identify ${\cal P}$ to a mixed state $\rho$
+by Gleason's theorem.
 \begin{thm}
 (Gleason's Theorem)
-\begin{enumerate}
-\item For $d\ge3$, for any state-function ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$,
-if ${\cal P}$ is a probability, there is a density matrix $\rho$
-such that ${\cal P}={\cal P}_{\rho}$~\cite{Redhead1987-REDINA,gleason1957}.\footnote{In order to simplify the statement, we consider consider the probability
+
+For $d\ge3$, for any ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$,
+if ${\cal P}$ is a state-function and probability, i.e.,
+\begin{eqnarray}
+ &  & \textrm{For any vector }\ket{i}\in\C^{d*}\textrm{, and }\gamma\in\C^{*}\textrm{ , }{\cal P}(\ket{i})={\cal P}(\gamma\ket{i})\textrm{ ,}\label{eq:parallel-DQT(I)-1}\\
+ &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \sum_{i=0}^{d-1}{\cal P}\left(\ket{i}\right)=1}\textrm{ ,}\label{eq:total-probability-1}
+\end{eqnarray}
+there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.\footnote{In order to simplify the statement, we consider consider the probability
 on the state vectors instead of the projectors or closed subspaces
 as in the Gleason's original paper.}
-\item Consequently, the Born rule (\ref{prob1.eq-6}) is the only reasonable
-probability assignment, and can be deduced by other reasonable axioms~\cite{peres1995quantum}. 
-\end{enumerate}
 \end{thm}
+In contrast, when $d=2$, consider the discontinuous function ${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$
+by 
+\[
+{\cal P}
+\left(\begin{array}{c} \alpha_{0}\\ \alpha_{1} \end{array}\right)=
+\cases{ 
+1 & , if $\alpha_{0}\alpha_{1}>0$\\
+\frac{1}{2} & , if $\alpha_{0}\alpha_{1}=0$\\
+0 & , if $\alpha_{0}\alpha_{1}<0$ } 
+\]
+${\cal P}$ satisfies equation (\ref{eq:parallel-DQT(I)-1}) and (\ref{eq:total-probability-1})
+because no matter the sign of $\alpha_{0}\alpha_{1}$, we always have
+\[
+{\cal P}\left(\begin{array}{c}
+\alpha_{0}\\
+\alpha_{1}
+\end{array}\right)+{\cal P}\left(\begin{array}{c}
+-\alpha_{1}\\
+\alpha_{0}
+\end{array}\right)=1\textrm{ .}
+\]
+However, ${\cal P}_{\rho}$ is always continuous. Therefore, we can
+never find a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$.
+
 An important meaning of Gleason's theorem is that the state space
@@
 to solve an equation. The other important meaning of Gleason's theorem
-is that it implies the Born rule (\ref{prob1.eq-6}). This is even
-more important for building a discrete quantum theory. If we plug
-in vectors over $\ff{p^{2}}$ into the usual Born rule (\ref{prob1.eq-6}),
-it gives an elements in $\ff{p}$ which has no way interpreted as
-a probability. Hence, everyone who tried to build a quantum theory
-over finite fields struggled on how to define a reasonable probability.
-If Gleason's theorem works in any sense over finite fields, we can
-have a reasonable way to induce the Born rule over finite fields.
+is that it implies the Born rule (\ref{prob1.eq-6})~\cite{peres1995quantum,inun.606849520040101}.
+This is even more important for building a discrete quantum theory.
+If we plug in vectors over $\ff{p^{2}}$ into the usual Born rule
+(\ref{prob1.eq-6}), it gives an elements in $\ff{p}$ which has no
+way interpreted as a probability. Hence, everyone who tried to build
+a quantum theory over finite fields struggled on how to define a reasonable
+probability. If Gleason's theorem works in any sense over finite fields,
+we can have a reasonable way to induce the Born rule over finite fields.
 

### 2016-01-29 DQC3.tex
"6.1 Gleason's Theorem in DQT" Updated....

@@
 \fi
-\theoremstyle{definition}
-\newtheorem{problem}[thm]{Problem}
+\def\casename{Case. }
+ \newlist{casenv}{enumerate}{4}
+ \setlist[casenv]{leftmargin=*,align=left,widest={iiii}}
+ \setlist[casenv,1]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
+ \setlist[casenv,2]{label={{\itshape\ \casename} \roman*.},ref=\roman*}
+ \setlist[casenv,3]{label={{\itshape\ \casename\ \alph*.}},ref=\alph*}
+ \setlist[casenv,4]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
 
@@
 \end{thm}
-In contrast, when $d=2$, consider the discontinuous function ${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$
-by 
+In contrast, when $d=2$, consider ${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$
+such that if we restrict ${\cal P}$ on the real unit circle, we will
+have a discontinuous function 
 \[
 {\cal P}
-\left(\begin{array}{c} \alpha_{0}\\ \alpha_{1} \end{array}\right)=
+\left(\begin{array}{c} \cos\theta\\ \sin\theta \end{array}\right)=
 \cases{ 
-1 & , if $\alpha_{0}\alpha_{1}>0$\\
-\frac{1}{2} & , if $\alpha_{0}\alpha_{1}=0$\\
-0 & , if $\alpha_{0}\alpha_{1}<0$ } 
+0 & , if $0 \le \theta < \frac{\pi}{2}$\\
+1 & , if $\frac{\pi}{2} \le \theta < \pi$ } 
 \]
 ${\cal P}$ satisfies equation (\ref{eq:parallel-DQT(I)-1}) and (\ref{eq:total-probability-1})
-because no matter the sign of $\alpha_{0}\alpha_{1}$, we always have
+because we have 
 \[
 {\cal P}\left(\begin{array}{c}
-\alpha_{0}\\
-\alpha_{1}
+\cos\theta\\
+\sin\theta
 \end{array}\right)+{\cal P}\left(\begin{array}{c}
--\alpha_{1}\\
-\alpha_{0}
+-\sin\theta\\
+\cos\theta
+\end{array}\right)={\cal P}\left(\begin{array}{c}
+\cos\theta\\
+\sin\theta
+\end{array}\right)+{\cal P}\left(\begin{array}{c}
+\cos\left(\theta+\frac{\pi}{2}\right)\\
+\sin\left(\theta+\frac{\pi}{2}\right)
 \end{array}\right)=1\textrm{ .}
@@
 
-An important meaning of Gleason's theorem is that the state space
-is sufficient enough to produce every possible probability we get
-from an experiment. Hence, we don't have to worry about whether there
-is a chance that the probability got from a measurement cannot be
-explained by a state, and we need to introduce a new state. This may
-be analog to the fact that every algebraic equation over $\C$ can
-be solved in $\C$ so that we don't have to introduce new numbers
-to solve an equation. The other important meaning of Gleason's theorem
-is that it implies the Born rule (\ref{prob1.eq-6})~\cite{peres1995quantum,inun.606849520040101}.
-This is even more important for building a discrete quantum theory.
-If we plug in vectors over $\ff{p^{2}}$ into the usual Born rule
-(\ref{prob1.eq-6}), it gives an elements in $\ff{p}$ which has no
-way interpreted as a probability. Hence, everyone who tried to build
-a quantum theory over finite fields struggled on how to define a reasonable
-probability. If Gleason's theorem works in any sense over finite fields,
-we can have a reasonable way to induce the Born rule over finite fields.
-
-A naive way to extend Gleason's Theorem in DQT may be as follow.
-\begin{problem}
-Given a state-function $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
-which is also a probability, i.e., 
+Although the situation is different between $d=2$ and $d\ge3$ in
+CQT, we may not identify a state from a probability in DQT no matter
+the dimension of the system. In order to clearly state the theorem,
+we define $\dpr_{\Psi}\left(\ket{i}\right)=\dpr\left(\ket{\Psi},\ket{i}\right)$.
+Then, 
+\begin{thm}
+\label{thm:GleasonDQT}There exists $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
+which is a state-function and a probability, i.e., 
 \begin{eqnarray}
@@
 \end{eqnarray}
-Can we say something about $\hat{\pi}$?
-\end{problem}
-The answer is no, and the reasons are simple. First, compare the following
-arithmetic equation and Boolean equation.
+such that for any $\ket{\Psi}\in\ffzd{p^{2}},\dpr_{\Psi}\ne\hat{\pi}$.\end{thm}
+\begin{proof}
+Fix a basis $\{\ket{i}\}_{i=0}^{d-1}$. Consider 
+\[
+{\hat{\pi}}\left(\ket{\Phi}\right)=
+\cases{ 
+\textrm{impossible} & , if $\ip{\Phi}{0} = 0$ or $\ip{\Phi}{0} = \ldots = \ip{\Phi}{d-1}\ne 0$ ; \\
+\textrm{possible} & , otherwise. } 
+\]
+It is easy to verify that equation (\ref{eq:parallel-DQT}) hold as
+follow. 
+\begin{eqnarray*}
+ &  & \hat{\pi}\left(\ket{\Phi}\right)=\textrm{impossible}\\
+ & \Leftrightarrow & \ip{\Phi}{0}=0\textrm{ or }\ip{\Phi}{0}=\ldots=\ip{\Phi}{d-1}\ne0\\
+ & \Leftrightarrow & \gamma\ip{\Phi}{0}=0\textrm{ or }\gamma\ip{\Phi}{0}=\ldots=\gamma\ip{\Phi}{d-1}\ne0\\
+ & \Leftrightarrow & \hat{\pi}\left(\gamma\ket{\Phi}\right)=\textrm{impossible}
+\end{eqnarray*}
+For equation (\ref{eq:total-probability-DQT}), because 
+\[
+\textrm{impossible}\lor\textrm{possible}=\textrm{possible ,}
+\]
+it is sufficient to prove for any $\ket{\Phi}\in\ffzd{p^{2}}$ such
+that $\hat{\pi}\left(\ket{\Phi}\right)=\textrm{impossible}$, there
+is a $\ket{\Psi}\in\ffzd{p^{2}}$ such that $\ip{\Phi}{\Psi}=0$ and
+$\hat{\pi}\left(\ket{\Psi}\right)=\textrm{possible}$.
+\begin{casenv}
+\item When $\ip{\Phi}{0}=0$, $\ket{0}$ is what we want because $\ip{0}{0}=1\ne0$
+implies $\hat{\pi}\left(\ket{0}\right)=\textrm{possible}$.
+\item When $\ip{\Phi}{0}=\ldots=\ip{\Phi}{d-1}\ne0$, let $\alpha=\ip{\Phi}{0}$,
+and consider the state 
+\[
+\ket{\Psi}=\left(\begin{array}{ccccc}
+\alpha & -\alpha & 0 & \ldots & 0\end{array}\right)^{T}\textrm{ .}
+\]
+Then, $\ip{\Phi}{\Psi}=\alpha^{*}\alpha-\alpha^{*}\alpha=0$. Moreover,
+$\ket{\Psi}{0}=\alpha^{*}\ne0$ and $\ket{\Psi}{0}=\alpha^{*}\ne-\alpha^{*}=\ket{\Psi}{1}$
+implies $\hat{\pi}\left(\ket{\Psi}\right)=\textrm{possible}$.
+\end{casenv}
+Therefore, equation (\ref{eq:total-probability-DQT}) holds.
+
+The last part of the theorem is to prove that for any $\ket{\Psi}\in\ffzd{p^{2}},\dpr_{\Psi}\ne\hat{\pi}$.
+This part can be established by counting states. For any $\ket{\Psi}\in\ffzd{p^{2}}$,
+\begin{eqnarray*}
+ &  & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\dpr_{\Psi}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|\\
+ & = & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\ip{\Psi}{i}=0\right\} \right|\\
+ & < & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\hat{\pi}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|
+\end{eqnarray*}
+$\QED$
+\end{proof}
+There are reasons why there is no Gleason's theorem in DQT. First,
+given ${\cal P}$ in CQT, we search for a mixed state $\rho$ such
+that ${\cal P}={\cal P}_{\rho}$, but given $\hat{\pi}$ in DQT, we
+only search for a pure state $\ket{\Psi}$ such that $\dpr_{\Psi}=\hat{\pi}$.
+Notice that there are much more mixed states than pure states so that
+it is likely we cannot find any pure state $\ket{\Psi}$ satisfying
+$\dpr_{\Psi}=\hat{\pi}$ in DQT. Although this reason is important,
+theorem \ref{thm:GleasonDQT} still hold even if we define a mixed
+state. Assume $\rho$ is a mixed state between $\ket{\Psi_{1}}$ and
+$\ket{\Psi_{2}}$, then we still have 
+\begin{eqnarray*}
+ &  & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\dpr_{\rho}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|\\
+ & \le & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\dpr_{\Psi_{1}}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|\\
+ & < & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\hat{\pi}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|
+\end{eqnarray*}
+Therefore, no matter how we define the mixed state, theorem \ref{thm:GleasonDQT}
+still hold, and there are some other reasons why theorem \ref{thm:GleasonDQT}
+hold.
+
+Second, compare the following arithmetic equation and Boolean equation.
 \begin{eqnarray}
-p_{1}+p_{2}+p_{3} & = & 1\label{eq:arithmetic}\\
-\pi_{1}\vee\pi_{2}\vee\pi_{3} & = & \text{possible}\label{eq:Boolean}
+{\cal P}\left(\ket{0}\right)+{\cal P}\left(\ket{1}\right)+{\cal P}\left(\ket{2}\right) & = & 1\label{eq:arithmetic}\\
+\hat{\pi}\left(\ket{0}\right)\vee\hat{\pi}\left(\ket{1}\right)\vee\hat{\pi}\left(\ket{2}\right) & = & \text{possible}\label{eq:Boolean}
 \end{eqnarray}
-When $p_{1}=\frac{1}{2}$, we still have an equality $p_{2}+p_{3}=1$
-for $p_{2}$ and $p_{3}$ because $\left(\mathbb{R},0,+\right)$ is
-a group. In contrast, when $\pi_{1}=\text{possible}$, we know nothing
-about $\pi_{2}$ and $\pi_{3}$ because $\left(\mathscr{L}_{2},\text{impossible},\vee\right)$
-is a semigroup without cancellative, i.e., $a\vee c=b\vee c$ does
-not imply $a=b$. The difference between $\left(\mathbb{R},0,+\right)$
-and $\left(\mathscr{L}_{2},\text{impossible},\vee\right)$ suggests
-us to study the range of the probability. A reasonable range should
-have the structure $\left(\mathscr{L},0,1,\oplus,<\right)$, where
-$\left(\mathscr{L},0,\oplus,<\right)$ is the underlying commutative
-ordered semigroup~\cite{clifford1958} because the condition (\ref{eq:total-probability})
-and (\ref{eq:total-probability-DQT}) suggests the value of the range
-should be able to add together. $1\in\mathscr{L}$ is another special
-value to indicate the total probability. For example, $\left(\mathscr{L}_{2},\text{impossible},\text{possible},\vee,<\right)$
-and $\left(\mathbb{R},0,1,+,<\right)$ are two possible range of the
-probability, but we cannot pick $\mathscr{L}=\ff{p^{2}}$ because
-we cannot define an inequality such that $\left(\ff{p^{2}},0,+,<\right)$
-be an ordered semigroup.
-
-Second, Gleason's theorem relies a lot on the continuous probability~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.
-However, continuity doesn't even make sense in DQT. This fact implies
-that the structure of the domain of the probability, $\ffzd{p^{2}}$,
-is also too weak. In order to think which structure we need, we can
-check which the reasonable property ${\cal P}_{\Psi}:\C^{d*}\rightarrow\left[0,1\right]$
-should have. Despite the total probability is one, ${\cal P}_{\Psi}$
-must have 
-\begin{eqnarray}
-{\cal P}_{\Psi}\left(\ket{i}\right) & = & 0\textrm{ if }\ip{\Psi}{i}=0\label{prob1.eq-6-1}
-\end{eqnarray}
-where $\gamma\in\C^{*}$. Moreover, the probability must be invariant
-under any rotation, i.e., 
-\begin{equation}
-{\cal P}_{U\Psi}\left(U\ket{i}\right)={\cal P}_{\Psi}\left(\ket{i}\right)\label{eq:rotation}
-\end{equation}
-for any unitary matrix $U$. Because we consider the probability of
-two different state ${\cal P}_{\Psi}$ and ${\cal P}_{U\Psi}$ together,
-it may be more reasonable to ask whether there is an unique ``Born
-rule'' satisfying all the conditions, and our problem becomes
-\begin{problem}
-\label{prob:Gleason's}Is there a structure $\left(\mathscr{L},0,1,\oplus,<\right)$
-such that $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\left(\ffzd{p^{2}}\rightarrow\left\{ x\in\mathscr{L}\middle|0\le x\le1\right\} \right)$
-satisfying the following conditions is unique for $d\ge3$ and infinitely
-many for $d=2$?\footnote{Instead of equation (\ref{enu:particular-vector-DQT(I)}), another
-reasonable condition is $\braket{\Psi}{i}=0\Leftrightarrow\tilde{\pi}_{\Psi}\left(\ket{i}\right)=0$.
-However, when the underlying group $\mathscr{L}=\mathscr{L}_{2}$,
-this condition implies an unique solution for $d=2$. This is too
-strong and is not what we want. } 
-\begin{eqnarray}
- & \bullet & \textrm{For any orthonormal basis }\left\{ \ket{i}\right\} _{n=0}^{d-1}\subset\ffzd{p^{2}}\textrm{, }\label{enu:total-probability-DQT(I)}\\
- &  & \textrm{ \ensuremath{{\displaystyle \bigoplus_{i=0}^{d-1}\tilde{\pi}_{\Psi}\left(\ket{i}\right)=1}} .}\nonumber \\
- & \bullet & \textrm{If }\braket{\Psi}{i}=0\textrm{ ,}\textrm{then }\tilde{\pi}_{\Psi}\left(\ket{i}\right)=0\textrm{ .}\label{enu:particular-vector-DQT(I)}\\
- & \bullet & \textrm{For any vector }\ket{\Psi},\ket{i}\in\ffzd{p^{2}}\textrm{, }\nonumber \\
- &  & \textrm{and }U\textrm{ is a }d\textrm{-by-}d\textrm{ unitary matrix over }\ff{p^{2}}\textrm{, }\label{enu:unitary-DQT(I)}\\
- &  & \textrm{i.e. , }U^{\dagger}U=I\textrm{, then }\tilde{\pi}_{\Psi}(\ket{i})=\tilde{\pi}_{U\Psi}(U\ket{i})\textrm{. }\nonumber \\
- & \bullet & \textrm{For any vector }\ket{\Psi},\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{, }\nonumber \\
- &  & \tilde{\pi}_{\Psi}(\ket{i})=\tilde{\pi}_{\Psi}(\gamma\ket{i})\textrm{. }\label{enu:parallel-DQT(I)}
-\end{eqnarray}
-
-\end{problem}
-The no-go theorem in section \ref{sub:A-No-Go-Theorem} said the if
-$\left(\mathscr{L},0,1,\oplus,<\right)=\left(\mathbb{R},0,1,+,<\right)$,
-there is no $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\ffzd{p^{2}}\rightarrow\mathscr{L}$
-for $d\ge3$. It is easy to extend the no-go theorem and prove 
-\begin{thm}
-If $\left(\mathscr{L},0,\oplus,<\right)$ is a ordered group, then
-there is no $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\ffzd{p^{2}}\rightarrow\mathscr{L}$
-satisfying all conditions in problem \ref{prob:Gleason's} for $d\ge3$.
-\end{thm}
-When we consider $\left(\mathscr{L}_{2},\text{impossible},\text{possible},\vee,<\right)$,
-$\dpr$ defined in section \ref{sub:Interval-Valued-Probabilities-DQT}
-satisfies all conditions, but $\dpr$ is not the unique solution because
-of lack of cancellation law. It is still an open question whether
-problem \ref{prob:Gleason's} is true or false in general.
-
-\yutsung{Is that all probability value should be distinct be an reasonable
-condition?}
-
+When ${\cal P}\left(\ket{0}\right)=\frac{1}{2}$, we still have an
+equality ${\cal P}\left(\ket{1}\right)+{\cal P}\left(\ket{2}\right)=1$
+for ${\cal P}\left(\ket{1}\right)$ and ${\cal P}\left(\ket{2}\right)$
+because $\left(\mathbb{R},0,+\right)$ is a group. In contrast, when
+$\hat{\pi}\left(\ket{0}\right)=\text{possible}$, we know nothing
+about $\hat{\pi}\left(\ket{1}\right)$ and $\hat{\pi}\left(\ket{2}\right)$
+because $\left(\mathscr{L}_{2},\text{impossible},\vee\right)$ is
+a semigroup without cancellative, i.e., $a\vee c=b\vee c$ does not
+imply $a=b$.
+
+Third, even if we require the range of $\hat{\pi}$ has a group structure,
+we still may not find $\dpr_{\Psi}=\hat{\pi}$.
 %%%%%%%%%%%%%%%%%

### 2016-02-08 DQC3.tex
"6.1 Gleason's Theorem in DQT" Typed something...

@@
  \setlist[casenv,4]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
+\newtheorem{problem}[thm]{Problem}
 
@@
 
-Third, even if we require the range of $\hat{\pi}$ has a group structure,
-we still may not find $\dpr_{\Psi}=\hat{\pi}$.
+If the problem is that the range of $\hat{\pi}$ is only a semigroup,
+we may want to consider the range of $\hat{\pi}$ to be a group.
+\begin{problem}
+\label{thm:GleasonDQT-group}Is there a group $\left(\mathscr{L},0,\oplus\right)$
+with a special element $1\in\mathscr{L}$ and $1\ne0$ satisfying
+the following statement? 
+\begin{itemize}
+\item There is a way to define a mixed state $\rho$ and a corresponding
+Born rule $\tilde{\pi}_{\rho}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
+in a sense of equation (\ref{prob.mixed}).
+\item For $d\ge3$, for any $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
+satisfying 
+\begin{eqnarray}
+ &  & \textrm{For any vector }\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{ , }\hat{\pi}(\ket{i})=\hat{\pi}(\gamma\ket{i})\textrm{ . }\label{eq:parallel-DQT-1}\\
+ &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \bigoplus_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}1\textrm{ .}\label{eq:total-probability-DQT-1}
+\end{eqnarray}
+There is a mixed state $\rho$ such that $\hat{\pi}=\tilde{\pi}_{\rho}$.
+\end{itemize}
+\end{problem}
+When $d=3$ and $p=7$, we have verified that we no longer have the
+freedom to assign impossible more than any reasonable probability
+assignment. Therefore, we cannot find a similar counterexample for
+problem \ref{thm:GleasonDQT-group}. However, even if there is a group
+$\left(\mathscr{L},0,\oplus\right)$ satisfying problem \ref{thm:GleasonDQT-group},
+the corresponding Born rule $\tilde{\pi}_{\rho}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
+is not basis independent, i.e., we will not have 
+\begin{equation}
+\tilde{\pi}_{U\rho}\left(U\ket{i}\right)=\tilde{\pi}_{\rho}\left(\ket{i}\right)\label{eq:rotation-1}
+\end{equation}
+for all unitary matrix $U$, mixed state $\rho$, and pure state $\ket{i}\in\ffzd{p^{2}}$,
+and the proof is similar to the one of the no-go theorem in section
+\ref{sub:A-No-Go-Theorem}.
+
+In summary, there are some difficulties to establish corresponding
+Gleason's theorem in DQT no matter how we set the conditions. However,
+Gleason's theorem gives an idea how to fine ``the'' reasonable Born
+rule in a discrete quantum theory, and we hope we may find one in
+the future.
+
 %%%%%%%%%%%%%%%%%

### 2016-02-08 DQC3.tex
"6.1 Gleason's Theorem in DQT" Start editing...

@@
 Recall the measurement process discussed in section \ref{sec:Critical-Analysis-CQT}.
-Given a physical system represented by a state $\ket{\Psi}$, and
-an observable ${\mathbf{O}}$, whose eigenspectrum is given by ${\mathbf{O}}\left|i\right\rangle =\lambda_{i}\left|i\right\rangle $.
-Then the Born rule of CQT tells us that the probability of obtaining
-the eigenvalue $\lambda_{i}$ as an outcome of the measurement is
-given by 
+Given an observable ${\mathbf{O}}$ whose eigenspectrum is given by
+${\mathbf{O}}\left|i\right\rangle =\lambda_{i}\left|i\right\rangle $,
+when we measure ${\mathbf{O}}$ on a system in a state $\ket{\Psi}$,
+the probability is given by the Born rule of CQT 
 \begin{eqnarray}
@@
 \end{eqnarray}
-If the system is a mixed state represented by a density matrix 
+If the system is in a mixed state represented by a density matrix
 \[
@@
 \]
-we can extend the Born rule (\ref{prob1.eq-6}) and get 
+the Born rule (\ref{prob1.eq-6}) can be extended to 
 \begin{eqnarray}
-{\cal P}_{\rho}\left(\ket{i}\right)={\cal P}_{\rho}\left(\lambda_{i}\right) & = & \sum_{j}p_{j}{\cal P}_{\Psi_{j}}\left(\ket{i}\right)\label{prob1.eq-2}
+{\cal P}_{\rho}\left(\ket{i}\right)={\cal P}_{\rho}\left(\lambda_{i}\right) & = & \sum_{j}p_{j}{\cal P}_{\Psi_{j}}\left(\ket{i}\right)\textrm{ ,}\label{prob1.eq-2}
 \end{eqnarray}
 
-Let $\C^{*}=\C\backslash\left\{ 0\right\} $ and $\C^{d*}=\left\{ \ket{\Psi}\in\C^{d}\mid\ip{\Psi}{\Psi}\ne0\right\} $
-be the set of non-zero vectors. Because normalization and global phase
-gives the same state, and ${\cal P}_{\rho}:\C^{d*}\rightarrow\left[0,1\right]$
-should be a state-function, we should have 
-\begin{equation}
-\textrm{For any vector }\ket{i}\in\C^{d*}\textrm{, and }\gamma\in\C^{*}\textrm{ , }{\cal P}_{\rho}(\ket{i})={\cal P}_{\rho}(\gamma\ket{i})\textrm{ .}\label{eq:parallel-DQT(I)}
-\end{equation}
-More importantly, ${\cal P}_{\rho}$ defines a probability which means
-\begin{equation}
-\textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \sum_{i=0}^{d-1}{\cal P}_{\rho}\left(\ket{i}\right)=1}\textrm{ .}\label{eq:total-probability}
-\end{equation}
-Conversely, if a state-function ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$
-is a probability, we can identify ${\cal P}$ to a mixed state $\rho$
-by Gleason's theorem.
-\begin{thm}
-(Gleason's Theorem)
-
-For $d\ge3$, for any ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$,
-if ${\cal P}$ is a state-function and probability, i.e.,
+There are two important properties ${\cal P}_{\rho}:\C^{d*}\rightarrow\left[0,1\right]$
+should have. First, if we normalize a vector or multiply it by a constant
+factor, it still represents the same state, and ${\cal P}_{\rho}$
+is a function of state. Thus, we have ${\cal P}_{\rho}(\ket{i})={\cal P}_{\rho}(\gamma\ket{i})$
+for any $\gamma\in\C^{*}$ and $\ket{i}\in\C^{d*}$, where $\C^{*}=\C\backslash\left\{ 0\right\} $
+and $\C^{d*}=\left\{ \ket{\Psi}\in\C^{d}\mid\ip{\Psi}{\Psi}\ne0\right\} $
+is the set of non-zero vectors. Second, ${\cal P}_{\rho}$ defines
+a probability, and the total probability should be one, i.e., ${\displaystyle \sum_{i=0}^{d-1}{\cal P}_{\rho}\left(\ket{i}\right)=1}$
+for any orthonormal basis $\left\{ \ket{i}\right\} $.
+
+Conversely, if ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$ is a
+function of state and defines a probability, ${\cal P}$ can be identified
+to a mixed state $\rho$ by Gleason's theorem.
+\begin{thm}[Gleason's]
+For $d\ge3$, if ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$ is
+a function of state and defines a probability, i.e.,
 \begin{eqnarray}
- &  & \textrm{For any vector }\ket{i}\in\C^{d*}\textrm{, and }\gamma\in\C^{*}\textrm{ , }{\cal P}(\ket{i})={\cal P}(\gamma\ket{i})\textrm{ ,}\label{eq:parallel-DQT(I)-1}\\
- &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \sum_{i=0}^{d-1}{\cal P}\left(\ket{i}\right)=1}\textrm{ ,}\label{eq:total-probability-1}
+ &  & {\cal P}(\ket{i})={\cal P}(\gamma\ket{i})\textrm{ for any vector }\ket{i}\in\C^{d*}\textrm{, and }\gamma\in\C^{*}\textrm{ ,}\label{eq:parallel-DQT(I)-1}\\
+ &  & {\displaystyle \sum_{i=0}^{d-1}{\cal P}\left(\ket{i}\right)=1}\textrm{ for any orthonormal basis }\{\ket{i}\}\textrm{ ,}\label{eq:total-probability-1}
 \end{eqnarray}
-there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.\footnote{In order to simplify the statement, we consider consider the probability
-on the state vectors instead of the projectors or closed subspaces
-as in the Gleason's original paper.}
+there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.\footnote{In order to simplify the statement, we consider the probability on
+the state vectors instead of the projectors or closed subspaces as
+in the Gleason's original paper.}
 \end{thm}
-In contrast, when $d=2$, consider ${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$
-such that if we restrict ${\cal P}$ on the real unit circle, we will
-have a discontinuous function 
+Gleason's theorem requires $d\ge3$ because different orthonormal
+bases may share their vectors. For example, $\left\{ \ket{0},\ket{1},\ket{2}\right\} $
+and $\left\{ \ket{0},\frac{1}{\sqrt{2}}\left(\ket{1}+\ket{2}\right),\frac{1}{\sqrt{2}}\left(\ket{1}-\ket{2}\right)\right\} $
+share the vector $\ket{0}$. This implies ${\cal P}$ should be continuous
+and further proves the theorem. In contrast, when $d=2$, there is
+only one state orthogonal to a given state. Hence, every equation
+(\ref{eq:total-probability-1}) is either identical or share no common
+${\cal P}\left(\ket{i}\right)$. Therefore, when we solve the system
+of linear equation (\ref{eq:total-probability-1}), we can actually
+solve them individually and get a discontinuous function. For example,
+${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$ such that if we restrict
+${\cal P}$ on the real unit circle 
 \[

### 2016-02-08 DQC3.tex
"6.1 Gleason's Theorem in DQT" Update by old-to-new information...

@@
 There are two important properties ${\cal P}_{\rho}:\C^{d*}\rightarrow\left[0,1\right]$
-should have. First, if we normalize a vector or multiply it by a constant
-factor, it still represents the same state, and ${\cal P}_{\rho}$
-is a function of state. Thus, we have ${\cal P}_{\rho}(\ket{i})={\cal P}_{\rho}(\gamma\ket{i})$
-for any $\gamma\in\C^{*}$ and $\ket{i}\in\C^{d*}$, where $\C^{*}=\C\backslash\left\{ 0\right\} $
-and $\C^{d*}=\left\{ \ket{\Psi}\in\C^{d}\mid\ip{\Psi}{\Psi}\ne0\right\} $
-is the set of non-zero vectors. Second, ${\cal P}_{\rho}$ defines
-a probability, and the total probability should be one, i.e., ${\displaystyle \sum_{i=0}^{d-1}{\cal P}_{\rho}\left(\ket{i}\right)=1}$
+should have, where $\C^{d*}=\left\{ \ket{\Psi}\in\C^{d}\mid\ip{\Psi}{\Psi}\ne0\right\} $
+is the set of non-zero vectors. First, ${\cal P}_{\rho}$ is invariant
+under scalar multiplication because a vector still represents the
+same state if we normalize it or multiply it by a constant factor.
+Second, ${\cal P}_{\rho}$ defines a probability, and the total probability
+should be one, i.e., ${\displaystyle \sum_{i=0}^{d-1}{\cal P}_{\rho}\left(\ket{i}\right)=1}$
 for any orthonormal basis $\left\{ \ket{i}\right\} $.
 
-Conversely, if ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$ is a
-function of state and defines a probability, ${\cal P}$ can be identified
+Conversely, if any ${\cal P}$ with these two properties can be identified
 to a mixed state $\rho$ by Gleason's theorem.
@@
 For $d\ge3$, if ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$ is
-a function of state and defines a probability, i.e.,
+invariant under scalar multiplication and defines a probability, i.e.,
 \begin{eqnarray}

### 2016-02-08 DQC3.tex
"6.1 Gleason's Theorem in DQT" Check a quick diagnosis...

@@
 
-Recall the measurement process discussed in section \ref{sec:Critical-Analysis-CQT}.
-Given an observable ${\mathbf{O}}$ whose eigenspectrum is given by
-${\mathbf{O}}\left|i\right\rangle =\lambda_{i}\left|i\right\rangle $,
-when we measure ${\mathbf{O}}$ on a system in a state $\ket{\Psi}$,
-the probability is given by the Born rule of CQT 
+Recall the measurement process in CQT discussed in section \ref{sec:Critical-Analysis-CQT}.
+When we measure an observable ${\mathbf{O}}$ with ${\mathbf{O}}\left|i\right\rangle =\lambda_{i}\left|i\right\rangle $
+on a system in a state $\ket{\Psi}$, the probability is given by
+the Born rule of CQT 
 \begin{eqnarray}
@@
 If the system is in a mixed state represented by a density matrix
-\[
+\begin{equation}
 \rho=\sum_{j}p_{j}\frac{\proj{\Psi_{j}}}{\ip{\Psi_{j}}{\Psi_{j}}}\textrm{ ,}
-\]
+\end{equation}
 the Born rule (\ref{prob1.eq-6}) can be extended to 
@@
 There are two important properties ${\cal P}_{\rho}:\C^{d*}\rightarrow\left[0,1\right]$
-should have, where $\C^{d*}=\left\{ \ket{\Psi}\in\C^{d}\mid\ip{\Psi}{\Psi}\ne0\right\} $
+have, where $\C^{d*}=\left\{ \ket{\Psi}\in\C^{d}\mid\ip{\Psi}{\Psi}\ne0\right\} $
 is the set of non-zero vectors. First, ${\cal P}_{\rho}$ is invariant
@@
 
-Conversely, if any ${\cal P}$ with these two properties can be identified
+Conversely, any ${\cal P}$ with these two properties can be identified
 to a mixed state $\rho$ by Gleason's theorem.
@@
 and $\left\{ \ket{0},\frac{1}{\sqrt{2}}\left(\ket{1}+\ket{2}\right),\frac{1}{\sqrt{2}}\left(\ket{1}-\ket{2}\right)\right\} $
-share the vector $\ket{0}$. This implies ${\cal P}$ should be continuous
-and further proves the theorem. In contrast, when $d=2$, there is
-only one state orthogonal to a given state. Hence, every equation
-(\ref{eq:total-probability-1}) is either identical or share no common
-${\cal P}\left(\ket{i}\right)$. Therefore, when we solve the system
-of linear equation (\ref{eq:total-probability-1}), we can actually
-solve them individually and get a discontinuous function. For example,
-${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$ such that if we restrict
-${\cal P}$ on the real unit circle 
+share the vector $\ket{0}$. In contrast, when $d=2$, there is only
+one state orthogonal to a given state. Hence, every equation (\ref{eq:total-probability-1})
+is either identical or share no common ${\cal P}\left(\ket{i}\right)$.
+Therefore, when we solve the system of linear equation (\ref{eq:total-probability-1}),
+we can actually solve them individually and get a discontinuous function.
+For example, ${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$ such that
+if we restrict ${\cal P}$ on the real unit circle 
 \[

### 2016-02-09 DQC3.tex
"6.1 Gleason's Theorem in DQT" keep your topics short and consistent

@@
 under scalar multiplication because a vector still represents the
-same state if we normalize it or multiply it by a constant factor.
-Second, ${\cal P}_{\rho}$ defines a probability, and the total probability
-should be one, i.e., ${\displaystyle \sum_{i=0}^{d-1}{\cal P}_{\rho}\left(\ket{i}\right)=1}$
-for any orthonormal basis $\left\{ \ket{i}\right\} $.
+same state if we normalize it or multiply it by a global phase. Second,
+${\cal P}_{\rho}$ is a probability, and the total probability should
+be one.
 
 Conversely, any ${\cal P}$ with these two properties can be identified
-to a mixed state $\rho$ by Gleason's theorem.
+with a mixed state $\rho$ by Gleason's theorem~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}\footnote{In order to simplify the statement, we consider the probability on
+the state vectors instead of the projectors or closed subspaces as
+in the Gleason's original paper.}.
 \begin{thm}[Gleason's]
 For $d\ge3$, if ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$ is
-invariant under scalar multiplication and defines a probability, i.e.,
+invariant under scalar multiplication and is a probability, i.e.,
 \begin{eqnarray}
@@
 \end{eqnarray}
-there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.\footnote{In order to simplify the statement, we consider the probability on
-the state vectors instead of the projectors or closed subspaces as
-in the Gleason's original paper.}
+there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$.
 \end{thm}
@@
 and $\left\{ \ket{0},\frac{1}{\sqrt{2}}\left(\ket{1}+\ket{2}\right),\frac{1}{\sqrt{2}}\left(\ket{1}-\ket{2}\right)\right\} $
-share the vector $\ket{0}$. In contrast, when $d=2$, there is only
-one state orthogonal to a given state. Hence, every equation (\ref{eq:total-probability-1})
-is either identical or share no common ${\cal P}\left(\ket{i}\right)$.
-Therefore, when we solve the system of linear equation (\ref{eq:total-probability-1}),
-we can actually solve them individually and get a discontinuous function.
-For example, ${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$ such that
-if we restrict ${\cal P}$ on the real unit circle 
+share the vector $\ket{0}$. In contrast, when $d=2$, two orthonormal
+bases are either identical or completely different after we use equation
+(\ref{eq:parallel-DQT(I)-1}) to identify ${\cal P}\left(\ket{i}\right)$
+and ${\cal P}(\gamma\ket{i})$. Therefore, when we solve the system
+of linear equation (\ref{eq:total-probability-1}), we actually solve
+them individually and may get a discontinuous solution. For example,
+consider 
 \[
 {\cal P}
-\left(\begin{array}{c} \cos\theta\\ \sin\theta \end{array}\right)=
+\left(\begin{array}{c} \cos\theta\\ \sin\theta\rme^{\rmi\gamma} \end{array}\right)=
 \cases{ 
@@
 because we have 
-\[
-{\cal P}\left(\begin{array}{c}
+\begin{eqnarray*}
+ &  & {\cal P}\left(\begin{array}{c}
 \cos\theta\\
-\sin\theta
+\sin\theta\rme^{\rmi\gamma}
 \end{array}\right)+{\cal P}\left(\begin{array}{c}
--\sin\theta\\
+-\sin\theta\rme^{-\rmi\gamma}\\
 \cos\theta
-\end{array}\right)={\cal P}\left(\begin{array}{c}
+\end{array}\right)\\
+ & = & {\cal P}\left(\begin{array}{c}
 \cos\theta\\
-\sin\theta
+\sin\theta\rme^{\rmi\gamma}
 \end{array}\right)+{\cal P}\left(\begin{array}{c}
 \cos\left(\theta+\frac{\pi}{2}\right)\\
-\sin\left(\theta+\frac{\pi}{2}\right)
+\sin\left(\theta+\frac{\pi}{2}\right)\rme^{\rmi\gamma}
 \end{array}\right)=1\textrm{ .}
-\]
-However, ${\cal P}_{\rho}$ is always continuous. Therefore, we can
-never find a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$.
+\end{eqnarray*}
+However, ${\cal P}_{\rho}$ is always continuous. Therefore, no density
+matrix $\rho$ satisfies ${\cal P}={\cal P}_{\rho}$.
 
 Although the situation is different between $d=2$ and $d\ge3$ in
-CQT, we may not identify a state from a probability in DQT no matter
+CQT, a probability in DQT cannot be identified with a state despite
 the dimension of the system. In order to clearly state the theorem,
-we define $\dpr_{\Psi}\left(\ket{i}\right)=\dpr\left(\ket{\Psi},\ket{i}\right)$.
-Then, 
+the discrete Born rule $\dpr\left(\ket{\Psi},\ket{i}\right)$ will
+be written in the curried form $\dpr_{\Psi}\left(\ket{i}\right)$.
+Then, we have 
 \begin{thm}
-\label{thm:GleasonDQT}There exists $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
-which is a state-function and a probability, i.e., 
+\label{thm:GleasonDQT}For any $d\ge2$, there exists $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
+which is invariant under scalar multiplication and is a probability,
+i.e., 
 \begin{eqnarray}
- &  & \textrm{For any vector }\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{ , }\hat{\pi}(\ket{i})=\hat{\pi}(\gamma\ket{i})\textrm{ . }\label{eq:parallel-DQT}\\
- &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \bigvee_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}\textrm{possible . }\label{eq:total-probability-DQT}
+ &  & \hat{\pi}(\ket{i})=\hat{\pi}(\gamma\ket{i})\textrm{ for any vector }\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{ ,}\label{eq:parallel-DQT}\\
+ &  & {\displaystyle \bigvee_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}\textrm{possible for any orthonormal basis }\{\ket{i}\}\textrm{ , }\label{eq:total-probability-DQT}
 \end{eqnarray}
-such that for any $\ket{\Psi}\in\ffzd{p^{2}},\dpr_{\Psi}\ne\hat{\pi}$.\end{thm}
+such that $\dpr_{\Psi}\ne\hat{\pi}$ for any $\ket{\Psi}\in\ffzd{p^{2}}$.\end{thm}
 \begin{proof}
@@
 \]
-It is easy to verify that equation (\ref{eq:parallel-DQT}) hold as
-follow. 
+$\hat{\pi}$ satisfies equation (\ref{eq:parallel-DQT}) because we
+have 
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-For equation (\ref{eq:total-probability-DQT}), because 
-\[
-\textrm{impossible}\lor\textrm{possible}=\textrm{possible ,}
-\]
+for any $\gamma\in\ff{p^{2}}^{*}$. For equation (\ref{eq:total-probability-DQT}),
+because $\textrm{impossible}\lor\textrm{possible}=\textrm{possible}$,
 it is sufficient to prove for any $\ket{\Phi}\in\ffzd{p^{2}}$ such

### 2016-02-09 DQC3.tex
"6.1 Gleason's Theorem in DQT" S-7 Parallelism

@@
 \begin{eqnarray}
- &  & {\cal P}(\ket{i})={\cal P}(\gamma\ket{i})\textrm{ for any vector }\ket{i}\in\C^{d*}\textrm{, and }\gamma\in\C^{*}\textrm{ ,}\label{eq:parallel-DQT(I)-1}\\
+ &  & {\cal P}(\ket{i})={\cal P}(\gamma\ket{i})\textrm{ for any vector }\ket{i}\in\C^{d*}\textrm{, and }\gamma\in\C^{*}=\C\backslash\left\{ 0\right\} \textrm{ ,}\label{eq:parallel-DQT(I)-1}\\
  &  & {\displaystyle \sum_{i=0}^{d-1}{\cal P}\left(\ket{i}\right)=1}\textrm{ for any orthonormal basis }\{\ket{i}\}\textrm{ ,}\label{eq:total-probability-1}
@@
 CQT, a probability in DQT cannot be identified with a state despite
-the dimension of the system. In order to clearly state the theorem,
-the discrete Born rule $\dpr\left(\ket{\Psi},\ket{i}\right)$ will
-be written in the curried form $\dpr_{\Psi}\left(\ket{i}\right)$.
-Then, we have 
+the dimension of the system. 
 \begin{thm}
@@
 \end{eqnarray}
-such that $\dpr_{\Psi}\ne\hat{\pi}$ for any $\ket{\Psi}\in\ffzd{p^{2}}$.\end{thm}
+such that $\dpr_{\Psi}\ne\hat{\pi}$ for any $\ket{\Psi}\in\ffzd{p^{2}}$,
+where $\dpr_{\Psi}\left(\ket{i}\right)=\dpr\left(\ket{\Psi},\ket{i}\right)$
+is the discrete Born rule (\ref{eq:modality}).\end{thm}
 \begin{proof}
@@
 because $\textrm{impossible}\lor\textrm{possible}=\textrm{possible}$,
-it is sufficient to prove for any $\ket{\Phi}\in\ffzd{p^{2}}$ such
-that $\hat{\pi}\left(\ket{\Phi}\right)=\textrm{impossible}$, there
-is a $\ket{\Psi}\in\ffzd{p^{2}}$ such that $\ip{\Phi}{\Psi}=0$ and
-$\hat{\pi}\left(\ket{\Psi}\right)=\textrm{possible}$.
+it is sufficient to prove the following claim.
+\begin{description}
+\item [{Claim}] For any $\ket{\Phi}\in\ffzd{p^{2}}$ such that $\hat{\pi}\left(\ket{\Phi}\right)=\textrm{impossible}$,
+there is a $\ket{\Psi}\in\ffzd{p^{2}}$ such that $\ip{\Phi}{\Psi}=0$
+and $\hat{\pi}\left(\ket{\Psi}\right)=\textrm{possible}$.\end{description}
 \begin{casenv}
 \item When $\ip{\Phi}{0}=0$, $\ket{0}$ is what we want because $\ip{0}{0}=1\ne0$
-implies $\hat{\pi}\left(\ket{0}\right)=\textrm{possible}$.
+and $\ip{0}{d-1}=0$ implies $\hat{\pi}\left(\ket{0}\right)=\textrm{possible}$.
 \item When $\ip{\Phi}{0}=\ldots=\ip{\Phi}{d-1}\ne0$, let $\alpha=\ip{\Phi}{0}$,

### 2016-02-10 GleasonDQT.d_3.p_3.m
Correctly convert .nb to .m...

@@ -1,0 +1,869 @@
+(* ::Package:: *)
+
+(* ::Section:: *)
+(*I. Introduction*)
+
+
+(* ::Section:: *)
+(*II. Fundamentals of Finite Fields*)
+
+
+cModOffset[p_Integer]:=-((p-1)/2);
+cLogOffset[p_Integer]:=-((p^2-1)/2)+1;
+
+
+cMod[x_,0]:=cMod[x,0]=ToRadicals[FullSimplify[x]]
+GaussianIntegerQ[x_]:=GaussianIntegerQ[x]=IntegerQ[Re[x]]\[And]IntegerQ[Im[x]]
+cMod[x_?GaussianIntegerQ,p_Integer]:=cMod[x,p]=Mod[Re[x],p,cModOffset[p]]+I Mod[Im[x],p,cModOffset[p]]
+SetAttributes[cMod,Listable]
+cBasis[p_Integer]:=cBasis[p]=Flatten[Table[x+I y,{x,cModOffset[p],cModOffset[p]+p-1},{y,cModOffset[p],cModOffset[p]+p-1}]]
+cBasis::usage="List all elements in \!\(\*SubscriptBox[\[DoubleStruckCapitalF], SuperscriptBox[\(p\), \(2\)]]\)";
+cBasis[3]
+
+
+(* ::Text:: *)
+(*Galois generator list:*)
+
+
+cFindGens[p_Integer]:=cFindGens[p]=Module[{base=Complement[cBasis[p],{0}],test,out={}},Do[test=Table[cMod[b^k,p],{k,1,p^2-1}];
+If[Sort[base]==Sort[test],AppendTo[out,b]],{b,base}];
+out]
+
+
+(* ::Text:: *)
+(*and the number of generators is EulerPhi[p^2-1].*)
+
+
+defaultGenerators[p_Integer]:=defaultGenerators[p]=Switch[p,0,Indeterminate,3,1-I,7,3+I,11,5+4I,19,9+6 I,23,11+10I,31,15+13 I,43,21+19 I]
+
+
+(* ::Text:: *)
[…]

### 2016-02-10 GleasonDQT.d_3.p_3.m
GleasonDQT.d_3.p_3.m Fixed the output...

@@ -848,7 +848,7 @@ position=Position[Most[row],Except[0],{1},Heads->False];
 If[position=={},
 If[Last[row]==0,Break[],AppendTo[output,\!\(TraditionalForm\`0 == Last[row]\)]],
 AppendTo[output,
-Row[Join[{\!\(TraditionalForm\`row[\([position[\([1, 1]\)]]\)] \[Pi]\ MatrixForm[unitNormVectorsRepresentative[\([position[\([1, 1]\)]]\)]]\)},Flatten[{Switch[row[[#[[1]]]],1,"+",-1,"-",_,NumberForm[row[[#[[1]]]],0,NumberSigns->{"-","+"}]],\!\(TraditionalForm\`\[Pi]\ MatrixForm[unitNormVectorsRepresentative[\([#[\([1]\)]]\)]]\)}&/@Rest[position]],{"\[Equal]",Last[row]}]]]],
+Row[Join[{\!\(TraditionalForm\`row[\([position[\([1, 1]\)]]\)] \[Pi]\ MatrixForm[unitNormVectorsRepresentative[\([position[\([1, 1]\)]]\)]]\)},Flatten[{Switch[row[[#[[1]]]],1,"\"+\"",-1,"\"-\"",_,NumberForm[row[[#[[1]]]],0,NumberSigns->{"\"-\"","\"+\""}]],\!\(TraditionalForm\`\[Pi]\ MatrixForm[unitNormVectorsRepresentative[\([#[\([1]\)]]\)]]\)}&/@Rest[position]],{"\"\[Equal]\"",Last[row]}]]]],
 {row,reducedForm}];
 output]
 Column[cGleasonPrint[cGleasonAbelianGroup[3,2],3,2]]
@@ -867,3 +867,4 @@ Print[AbsoluteTiming[MatrixRank[cGleasonAbelianGroup[p,3]]]];
 Print[AbsoluteTiming[cPossibleZeroCount[p,3]]];
 Print[AbsoluteTiming[cMaxZeroCount[p,3]]];
 Print[Column[cGleasonPrint[cGleasonAbelianGroup[p,3],p,3]]]];
+Print[];

### 2016-02-10 GleasonDQT.d_3.p_11.m
Prepared the files for big red 2...

@@ -1,0 +1,870 @@
+(* ::Package:: *)
+
+(* ::Section:: *)
+(*I. Introduction*)
+
+
+(* ::Section:: *)
+(*II. Fundamentals of Finite Fields*)
+
+
+cModOffset[p_Integer]:=-((p-1)/2);
+cLogOffset[p_Integer]:=-((p^2-1)/2)+1;
+
+
+cMod[x_,0]:=cMod[x,0]=ToRadicals[FullSimplify[x]]
+GaussianIntegerQ[x_]:=GaussianIntegerQ[x]=IntegerQ[Re[x]]\[And]IntegerQ[Im[x]]
+cMod[x_?GaussianIntegerQ,p_Integer]:=cMod[x,p]=Mod[Re[x],p,cModOffset[p]]+I Mod[Im[x],p,cModOffset[p]]
+SetAttributes[cMod,Listable]
+cBasis[p_Integer]:=cBasis[p]=Flatten[Table[x+I y,{x,cModOffset[p],cModOffset[p]+p-1},{y,cModOffset[p],cModOffset[p]+p-1}]]
+cBasis::usage="List all elements in \!\(\*SubscriptBox[\[DoubleStruckCapitalF], SuperscriptBox[\(p\), \(2\)]]\)";
+cBasis[3]
+
+
+(* ::Text:: *)
+(*Galois generator list:*)
+
+
+cFindGens[p_Integer]:=cFindGens[p]=Module[{base=Complement[cBasis[p],{0}],test,out={}},Do[test=Table[cMod[b^k,p],{k,1,p^2-1}];
+If[Sort[base]==Sort[test],AppendTo[out,b]],{b,base}];
+out]
+
+
+(* ::Text:: *)
+(*and the number of generators is EulerPhi[p^2-1].*)
+
+
+defaultGenerators[p_Integer]:=defaultGenerators[p]=Switch[p,0,Indeterminate,3,1-I,7,3+I,11,5+4I,19,9+6 I,23,11+10I,31,15+13 I,43,21+19 I]
+
+
+(* ::Text:: *)
[…]

### 2016-02-10 GleasonDQT.d_3.p_11.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+module load mathematica
+cd "/N/u/yuttai/BigRed2/201401-05.M800/BigRed2.new"
+math -script GleasonDQT.d_3.p_11.m 5 >> GleasonDQT.d_3.p_11.txt

### 2016-02-10 GleasonDQT.d_3.p_19.m

@@ -1,0 +1,870 @@
+(* ::Package:: *)
+
+(* ::Section:: *)
+(*I. Introduction*)
+
+
+(* ::Section:: *)
+(*II. Fundamentals of Finite Fields*)
+
+
+cModOffset[p_Integer]:=-((p-1)/2);
+cLogOffset[p_Integer]:=-((p^2-1)/2)+1;
+
+
+cMod[x_,0]:=cMod[x,0]=ToRadicals[FullSimplify[x]]
+GaussianIntegerQ[x_]:=GaussianIntegerQ[x]=IntegerQ[Re[x]]\[And]IntegerQ[Im[x]]
+cMod[x_?GaussianIntegerQ,p_Integer]:=cMod[x,p]=Mod[Re[x],p,cModOffset[p]]+I Mod[Im[x],p,cModOffset[p]]
+SetAttributes[cMod,Listable]
+cBasis[p_Integer]:=cBasis[p]=Flatten[Table[x+I y,{x,cModOffset[p],cModOffset[p]+p-1},{y,cModOffset[p],cModOffset[p]+p-1}]]
+cBasis::usage="List all elements in \!\(\*SubscriptBox[\[DoubleStruckCapitalF], SuperscriptBox[\(p\), \(2\)]]\)";
+cBasis[3]
+
+
+(* ::Text:: *)
+(*Galois generator list:*)
+
+
+cFindGens[p_Integer]:=cFindGens[p]=Module[{base=Complement[cBasis[p],{0}],test,out={}},Do[test=Table[cMod[b^k,p],{k,1,p^2-1}];
+If[Sort[base]==Sort[test],AppendTo[out,b]],{b,base}];
+out]
+
+
+(* ::Text:: *)
+(*and the number of generators is EulerPhi[p^2-1].*)
+
+
+defaultGenerators[p_Integer]:=defaultGenerators[p]=Switch[p,0,Indeterminate,3,1-I,7,3+I,11,5+4I,19,9+6 I,23,11+10I,31,15+13 I,43,21+19 I]
+
+
+(* ::Text:: *)
[…]

### 2016-02-10 GleasonDQT.d_3.p_19.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+module load mathematica
+cd "/N/u/yuttai/BigRed2/201401-05.M800/BigRed2.new"
+math -script GleasonDQT.d_3.p_19.m 5 >> GleasonDQT.d_3.p_19.txt

### 2016-02-10 DQC3.tex
"6.1 Gleason's Theorem in DQT" Updates new results...

@@
 \end{proof}
-There are reasons why there is no Gleason's theorem in DQT. First,
-given ${\cal P}$ in CQT, we search for a mixed state $\rho$ such
-that ${\cal P}={\cal P}_{\rho}$, but given $\hat{\pi}$ in DQT, we
-only search for a pure state $\ket{\Psi}$ such that $\dpr_{\Psi}=\hat{\pi}$.
+It is easy to identify the reasons why theorem \ref{thm:GleasonDQT}
+is different from Gleason's theorem in CQT, but it is hard to find
+the correct conditions to get the corresponding Gleason's theorem
+in DQT. Given ${\cal P}$ in CQT, we search for a mixed state $\rho$
+such that ${\cal P}={\cal P}_{\rho}$, but given $\hat{\pi}$ in DQT,
+we only search for a pure state $\ket{\Psi}$ such that $\dpr_{\Psi}=\hat{\pi}$.
 Notice that there are much more mixed states than pure states so that
 it is likely we cannot find any pure state $\ket{\Psi}$ satisfying
-$\dpr_{\Psi}=\hat{\pi}$ in DQT. Although this reason is important,
-theorem \ref{thm:GleasonDQT} still hold even if we define a mixed
-state. Assume $\rho$ is a mixed state between $\ket{\Psi_{1}}$ and
-$\ket{\Psi_{2}}$, then we still have 
-\begin{eqnarray*}
- &  & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\dpr_{\rho}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|\\
- & \le & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\dpr_{\Psi_{1}}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|\\
- & < & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\hat{\pi}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|
-\end{eqnarray*}
-Therefore, no matter how we define the mixed state, theorem \ref{thm:GleasonDQT}
-still hold, and there are some other reasons why theorem \ref{thm:GleasonDQT}
-hold.
-
-Second, compare the following arithmetic equation and Boolean equation.
+$\dpr_{\Psi}=\hat{\pi}$ in DQT.
+
+Lacking the notion of mixed state is not the only reason why theorem
+\ref{thm:GleasonDQT} is hold. Even if we find a way to define a mixed
+state, if $\rho$ is a mixed state between $\ket{\Psi_{1}}$ and $\ket{\Psi_{2}}$,
+then we still have 
+\[
+\left|\dpr_{\rho}^{-1}\left(\left\{ \textrm{impossible}\right\} \right)\right|\le\left|\dpr_{\Psi_{1}}^{-1}\left(\left\{ \textrm{impossible}\right\} \right)\right|<\left|\hat{\pi}^{-1}\left(\left\{ \textrm{impossible}\right\} \right)\right|\textrm{ .}
+\]
+We can always pick $\hat{\pi}$ such that $\left|\hat{\pi}^{-1}\left(\left\{ \textrm{impossible}\right\} \right)\right|$
+is larger because we have $x\lor\textrm{possible}=\textrm{possible}$
+no matter whether $x$ is possible or impossible. More precisely,
+compare the following arithmetic equation and Boolean equation.
 \begin{eqnarray}
@@
 because $\left(\mathscr{L}_{2},\text{impossible},\vee\right)$ is
-a semigroup without cancellative, i.e., $a\vee c=b\vee c$ does not
-imply $a=b$.
-
-If the problem is that the range of $\hat{\pi}$ is only a semigroup,
-we may want to consider the range of $\hat{\pi}$ to be a group.
+a commutative semigroup without cancellative, i.e., $a\vee c=b\vee c$
+does not imply $a=b$.
+
+If the problem is that the range of $\hat{\pi}$ is only a commutative
+semigroup, we may want to consider $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
+, and $\left(\mathscr{L},0,\uplus\right)$ is an abelian group. By
+the fundamental theorem of abelian group~\cite{DummitFoote2004},
+$\mathscr{L}$ must be isomorphic to $\mathbb{Z}_{d_{1}}\oplus\ldots\oplus\mathbb{Z}_{d_{k}}\oplus\mathbb{Z}^{b}$,
+where $\mathbb{Z}_{d_{1}},\ldots,\mathbb{Z}_{d_{k}}$ are finite cyclic
+subgroups, $\mathbb{Z}^{b}$ is the free abelian group with rank $b$,
+and $\oplus$ is the direct sum of the abelian groups. Moreover, we
+want $\left(\mathscr{L},0,\uplus\right)$ to have a sense of probability. 
 \begin{problem}

### 2016-02-10 DQC3.tex
"6.1 Gleason's Theorem in DQT" Updates new results...

@@
 semigroup, we may want to consider $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
-, and $\left(\mathscr{L},0,\uplus\right)$ is an abelian group. By
-the fundamental theorem of abelian group~\cite{DummitFoote2004},
-$\mathscr{L}$ must be isomorphic to $\mathbb{Z}_{d_{1}}\oplus\ldots\oplus\mathbb{Z}_{d_{k}}\oplus\mathbb{Z}^{b}$,
+, and $\left(\mathscr{L},0,\oplus\right)$ is an abelian group. By
+the fundamental theorem of finitely generated abelian group~\cite{DummitFoote2004},
+$\mathscr{L}$ must be isomorphic to $\mathbb{Z}_{d_{1}}\times\ldots\times\mathbb{Z}_{d_{k}}\times\mathbb{Z}^{b}$,
 where $\mathbb{Z}_{d_{1}},\ldots,\mathbb{Z}_{d_{k}}$ are finite cyclic
 subgroups, $\mathbb{Z}^{b}$ is the free abelian group with rank $b$,
-and $\oplus$ is the direct sum of the abelian groups. Moreover, we
-want $\left(\mathscr{L},0,\uplus\right)$ to have a sense of probability. 
+and $\times$ is the direct product of the abelian groups. However,
+if $\mathscr{L}$ has any finite cyclic subgroups, we may have $\hat{\pi}\left(\ket{0}\right)\ne0$,
+but $d_{1}\hat{\pi}\left(\ket{0}\right)=0$. This contradicts the
+idea that $\hat{\pi}$ can be understood as a probability. Therefore,
+we must have $\mathscr{L}\cong\mathbb{Z}^{b}$.
 \begin{problem}
-\label{thm:GleasonDQT-group}Is there a group $\left(\mathscr{L},0,\oplus\right)$
+\label{thm:GleasonDQT-group}Is there a group $\left(\mathscr{L},0,\oplus\right)\cong\mathbb{Z}^{b}$
 with a special element $1\in\mathscr{L}$ and $1\ne0$ satisfying
@@
 in a sense of equation (\ref{prob.mixed}).
-\item For $d\ge3$, for any $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
-satisfying 
+\item $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}$ satisfies 
 \begin{eqnarray}
- &  & \textrm{For any vector }\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{ , }\hat{\pi}(\ket{i})=\hat{\pi}(\gamma\ket{i})\textrm{ . }\label{eq:parallel-DQT-1}\\
- &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \bigoplus_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}1\textrm{ .}\label{eq:total-probability-DQT-1}
+ &  & \hat{\pi}(\ket{i})=\hat{\pi}(\gamma\ket{i})\textrm{ for any vector }\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{ , }\label{eq:parallel-DQT-1}\\
+ &  & {\displaystyle \bigoplus_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}1\textrm{ for any orthonormal basis }\{\ket{i}\}\textrm{ . }\label{eq:total-probability-DQT-1}
 \end{eqnarray}
-There is a mixed state $\rho$ such that $\hat{\pi}=\tilde{\pi}_{\rho}$.
+For $d\ge3$, there is a mixed state $\rho$ such that $\hat{\pi}=\tilde{\pi}_{\rho}$;
+for $d=2$, there is a $\hat{\pi}$ corresponding to no mixed state
+$\rho$.
 \end{itemize}
 \end{problem}
-When $d=3$ and $p=7$, we have verified that we no longer have the
-freedom to assign impossible more than any reasonable probability
-assignment. Therefore, we cannot find a similar counterexample for
-problem \ref{thm:GleasonDQT-group}. However, even if there is a group
-$\left(\mathscr{L},0,\oplus\right)$ satisfying problem \ref{thm:GleasonDQT-group},
-the corresponding Born rule $\tilde{\pi}_{\rho}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
-is not basis independent, i.e., we will not have 
-\begin{equation}
-\tilde{\pi}_{U\rho}\left(U\ket{i}\right)=\tilde{\pi}_{\rho}\left(\ket{i}\right)\label{eq:rotation-1}
-\end{equation}
-for all unitary matrix $U$, mixed state $\rho$, and pure state $\ket{i}\in\ffzd{p^{2}}$,
-and the proof is similar to the one of the no-go theorem in section
-\ref{sub:A-No-Go-Theorem}.
-
-In summary, there are some difficulties to establish corresponding
-Gleason's theorem in DQT no matter how we set the conditions. However,
-Gleason's theorem gives an idea how to fine ``the'' reasonable Born
-rule in a discrete quantum theory, and we hope we may find one in
-the future.
+For $d=2$, we can easily construct a $\hat{\pi}$ satisfying equation
+(\ref{eq:zero-count}) and corresponding to no mixed state $\rho$.
+When $d=3$ and $p=7$, we have verified the only $\hat{\pi}$ is
+$\hat{\pi}\left(\ket{i}\right)=\hat{\pi}\left(\ket{j}\right)$ and
+$3\hat{\pi}\left(\ket{i}\right)=1$ for all $\ket{i},\ket{j}\in\ffzd{p^{2}}$.
+Therefore, we don't have enough $\hat{\pi}$ to corresponding to even
+pure states. We believe the same situation happens for other $d\ge3$
+and $p\ge7$.
+
+We don't know whether $\mathscr{L}$ can be a non-Boolean commutative
+semigroup, but not yet a group. In summary, there are some difficulties
+to establish corresponding Gleason's theorem in DQT no matter how
+we set the conditions.
 

### 2016-04-06 Gleason.tex
Revert "The merged files have never been pulled to ShareLaTeX..."
This reverts commit 9446d0dbf0f9bf458d1329c0126bd5b65461c00b.

%% LyX 2.1.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,english]{iopart}
\usepackage[latin9]{inputenc}
\usepackage{calc}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\usepackage{iopams}
\usepackage{setstack}
\usepackage{enumitem}		% customizable list environments
\newlength{\lyxlabelwidth}      % auxiliary length 
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
  \theoremstyle{plain}
  \newtheorem{cor}[thm]{\protect\corollaryname}
 \newlist{casenv}{enumerate}{4}
 \setlist[casenv]{leftmargin=*,align=left,widest={iiii}}
 \setlist[casenv,1]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
 \setlist[casenv,2]{label={{\itshape\ \casename} \roman*.},ref=\roman*}
 \setlist[casenv,3]{label={{\itshape\ \casename\ \alph*.}},ref=\alph*}
 \setlist[casenv,4]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
  \theoremstyle{definition}
  \newtheorem{example}[thm]{\protect\examplename}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%% Discrete Quantum Computing/Discrete Quantum Theory
%%  - third paper, focusing on how fundamental aspects needed by
%% all quantum mechanical theories (as treated in Asher Peres's book)
%% have to be approached in a quantum theory based on Galois groups,
%% via COMPUTABLE integer number fields with finite characteristic.

\usepackage{mathrsfs}
\usepackage{fullpage}
\usepackage{url}
\usepackage{times}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{iopams}
\usepackage{setstack}

\input{Qcircuit}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\usepackage{enumitem}% customizable list environments
% \newlength{\lyxlabelwidth}      % auxiliary length

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{amsfonts}
\usepackage{color}
\usepackage{dsfont}
\usepackage[usenames,dvipsnames]{xcolor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% these went missing?
% \newcommand{\bra}[1]{\left\langle{#1}\right|}
% \newcommand{\ket}[1]{\left|{#1}\right\rangle}
% \newcommand{\mathscr}[1]{{\cal #1}}
%\renewcommand{\author}[1]{\bf #1 \/}
\newcommand{\affiliation}[1]{\parbox{5.5in}{\small{\it #1 \/}}}

\newcommand{\cardp}[2]{#1 \,\sslash\, #2}
\newcommand{\braket}[2]{\langle{#1}|{#2}\rangle} 
\newcommand{\uf}{U_{\!f}}
\def\image {\rm Image~}
\def\ker{\rm ker~}
\def\coker{\rm coker~}
\def\ker{\rm ker~}
\def\dr{\smash{\downharpoonright}}
\def\ad{{\rm ad~}}
\def\Q{{\mathbb{Q}}}
\def\R{{\mathbb{R}}}
\def\N{{\mathbb{N}}}
\def\C{{\mathbb{C}}}
\def\Z{{\mathbb{Z}}}
\def\del{\partial}
\def\grad{\nabla}
\def\proof{{\em Proof:  }}
\def\ra{\rangle}
\def\la{\langle}
\def\rl{\rangle \langle}
\def\openone{\leavevmode\hbox{\small1\kern-3.8pt\normalsize1}}
\def\RR{{\rm I\kern-.2emR}}
\def\tr{{\rm tr}\; }
\def\fu{\mathfrak{u}}
\def\fa{\mathfrak{a}}
\def\fd{\mathfrak{d}}
\def\fb{\mathfrak{b}}
\def\fj{\mathfrak{j}}
\def\fg{\mathfrak{g}}
\def\fh{\mathfrak{h}}
\def\fk{\mathfrak{k}}
\def\fs{\mathfrak{s}}
\def\fgl{\mathfrak{gl}}
\def\fsl{\mathfrak{sl}}
\def\fsu{\mathfrak{su}}
\def\fsp{\mathfrak{sp}}
\def\fso{\mathfrak{so}}
\def\proof{{\em Proof:  }}
\def\tphi{\tilde{\Phi}}
\def\ra{\rangle}
\def\la{\langle}
\def\rl{\rangle \langle}
\def\openone{\leavevmode\hbox{\small1\kern-3.8pt\normalsize1}}
\def\RR{{\rm I\kern-.2emR}}
\def\tr{{\rm tr}\; }
\def\ce{{\cal E}}
\def\cl{{\cal L}}
\def\cg{{\cal G}}
\def\cd{{\cal D}}
\def\cb{{\cal B}}
\def\cn{{\cal N}}
\def\ch{{\cal H}}
\def\cs{{\cal S}}
\def\ct{{\cal T}}
\def\cp{{\cal P}}
\def\cm{{\cal M}}
\def\cf{{\cal F}}
\def\ci{{\cal I}}
\def\ca{{\cal A}}
\def\calr{{\cal R}}
\def\cv{{\cal V}}
\def\cc{{\cal C}}
\def\rhon{\rho^{\otimes n}}
\def\on{^{\otimes n}}
\def\pn{^{(n)}}
\def\pnp{^{(n)'}}
\def\id{\frac{I}{d}}
\def\pthang{\frac{P}{\sqrt{d \tr P^2}}}
\def\Psirq{\Psi^{RQ}}
\def\d{^\dagger}
\def\union{\cup}
\def\intersection{\cap}
\newcommand{\QED}{\hspace*{\fill}\mbox{\rule[0pt]{1.5ex}{1.5ex}}}
\providecommand{\ignore}[1]{}

\newcommand{\scalarZ}{0}
\newcommand{\scalarO}{1}
\newcommand{\scalarPlus}{+}
\newcommand{\scalarTimes}{*}
\newcommand{\ip}[2]{\langle #1 ~|~ #2 \rangle}
\newcommand{\usat}{\texttt{UNIQUE-SAT}}
\newcommand{\boolt}{\textsf{Bool}} 
\newcommand{\bfalse}{\texttt{\textbf{false}}}
\newcommand{\btrue}{\texttt{\textbf{true}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\ffz}[1]{{\mathbb{F}^{\ast}_{#1}}}
%% \newcommand{\ffzd}[1]{\mathbb{F^{d}}_{#1}^{*}}
%%\newcommand{\ffzd}[1]{{\mathbb{F}^{d}_{#1}}^{\ast}}
%%\newcommand{\ffzd}[1]{{\mathbb{F}^{d\,\ast}_{#1}}}
\newcommand{\ffd}[1]{{\mathbb{F}^{d}_{#1}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
%% \newcommand{\dotprod}{quadratic Hermitian form}}
\newcommand{\dotprod}{dot product}
\newcommand{\todo}[1]{\textbf{TODO.~#1}}

\newcommand{\p}[1]{^{(#1)}}

\def\gbar{\overline{\gamma}}
\def\rev{{\cal R}_{\ca,\rho}}

\def\imod#1{\allowbreak\mkern8mu({\operator@font mod}\,\,#1)}

\newcommand{\half}{\mbox{$\textstyle \frac{1}{2}$} }
\newcommand{\proj}[1]{\ket{#1}\! \bra{#1}}
\newcommand{\outerp}[2]{\ket{#1}\! \bra{#2}}
\newcommand{\inner}[2]{ \langle #1 | #2 \rangle}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\benum}{\begin{enumerate}}
\newcommand{\eenum}{\end{enumerate}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqa}{\begin{eqnarray}}
\newcommand{\eeqa}{\end{eqnarray}}
\newtheorem{definition}{}\newtheorem{assertion}{}\newtheorem{theorem}{}\newtheorem{proposition}{}\newtheorem{axiom}{}\newtheorem{lemma}{}\newtheorem{corollary}{}\newtheorem{conjecture}{}\newtheorem{property}{}\newtheorem{fact}{}\newtheorem{remark}{}\newcommand{\bproof}{\begin{proof}}
\newcommand{\eproof}{\end{proof}}
\newcommand{\bprop}{\begin{proposition}}
\newcommand{\eprop}{\end{\proposition}}
\newcommand{\bdef}{\begin{definition}}
\newcommand{\zls}{{\mathbb Z}}
%%% This is our own symbol for "discrete probability"
%%    - originally "g", try "\pi" for now.
\newcommand{\dpr}{{\pi}}
\newcommand{\dpt}{{\tilde{\pi}}}
\def\round{\mathop{\rm round}\nolimits}

\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{red}{Amr says: #1}\end{minipage}}}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}

\newcommand{\fnorm}[1]{\mathsf{N}(#1)}
\newcommand{\mod}{\mbox{mod }}

\usepackage{babel}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeatother

\usepackage{babel}
  \providecommand{\corollaryname}{Corollary}
  \providecommand{\examplename}{Example}
 \providecommand{\casename}{Case}
\providecommand{\theoremname}{Theorem}

\begin{document}

\title{Discretization and Gleason's Theorem}

\author{John Gardiner$^{1}$, Andrew J. Hanson$^{2}$, Gerardo Ortiz$^{3}$,
Amr Sabry$^{2}$, Yu-Tsung Tai$^{4,2}$}

\address{$^{1}$ Department of Physics and Astronomy, University of California,
Los Angeles, CA 90095, USA}

\address{$^{2}$ School of Informatics and Computing, Indiana University,
Bloomington, IN 47405, USA}

\address{$^{3}$ Department of Physics, Indiana University, Bloomington, IN
47405, USA}

\address{$^{4}$ Department of Mathematics, Indiana University, Bloomington,
IN 47405, USA}

\ead{ortizg@indiana.edu}
\begin{abstract}
\today
\end{abstract}

\pacs{03.65.-w, 03.65.Ud, 03.65.Ta, 02.10.De}

\noindent{\it Keywords\/}: {Finite precision measurement, the Born rule, Gleason's theorem, interval-valued
probability, discrete quantum theory}

\submitto{\jpa}

\maketitle
\tableofcontents{}

\section{Introduction}

Any physical measurement can only be realized as finite precision
measurement~\cite{BirkhoffVonNeumann1936,PhysRevLett.83.3751,Mermin1999}
which may impact the validity of an idealized theorem based on uncountable
complex numbers, for example, the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,PhysRevLett.83.3751,Kent1999,CliftonKent2000}.
If the idea of finite precision measurement is formulated by discretizing
a quantum theory, then we found an analog of the Kochen-Specker theorem
is still hold in discrete quantum theory (DQT), and the discrete Kochen-Specker
theorem could really establish that DQT cannot be simulated by a contextual
classical theory because there is no dense subset hidden in finite
number of states. We further found that Gleason's theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}
has no discretized analog no matter how we discretize probability
or state space. The interaction between discretization and Gleason's
theorem is particularly interesting, not only because Gleason's theorem
together with the Kochen-Specker theorem and Bell's theorem~\cite{BellBook1987,peres1995quantum}
highlights the difference between quantum and classical, but also
because Gleason's theorem justifies that the Born rule~\cite{Born1984,Mermin2007}
is the only reasonable way to correspond mixed states and probabilities
bijectively.

We first focus on discretizing the probability. A discretized probability
with only impossible, $\left\{ 0\right\} $, and possible, $\left(0,1\right]$,
is sufficient to prove Bell's theorem in conventional quantum theory
(CQT)~\cite{MerminPRL1990,CabelloPRL.86.2001}. Actually, the impossible
and possible discretized probability is a special case of set-valued
probability measure~\cite{Artstein1972,PuriRalescu1983}. In section~\ref{sec:CQT-Interval-Valued-2},
a kind of set-valued probability measure is considered with only finite
number of intervals contained in $\left[0,1\right]$ called interval-valued
probability. We show that there is an interval-valued probability
which cannot correspond to any mixed state, and there is no analog
of Gleason's theorem with interval probability in CQT. Another idea
to discretize the probability is to only consider a finite set of
probability values. In this case, the Kochen-Specker theorem shows
there is no $\left\{ 0,1\right\} $-valued probability, and Gleason's
theorem rules out almost all finite value probabilities in general
in section~\ref{sec:CQT-Variants}. Therefore, we have no one-to-one
correspondence between finite value probabilities and mixed states
as well.

There is a long debate whether finite precision measurement nullifies
the Kochen-Specker theorem or not~\cite{PhysRevLett.83.3751,Kent1999,Mermin1999,CliftonKent2000,Peres2003,BarrettKent2004}
because CQT is based on uncountable complex numbers. When the Kochen-Specker
theorem are experimental verified, this finite precision problem also
requires physicists to consider some supplemental continuous conditions~\cite{MazurekPuseyKunjwalEtAl2015}.
In contrast, if the states space in reality is discrete with an enormous
large prime as described in our previous papers~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013},
then every state and observable can be realized theoretically. There
is no dense subset hidden in finite number of states, and the Kochen-Specker
theorem may be experimental verified without extra continuous conditions.
In section~\ref{sec:DQT-Finite-Value-Probability}, we prove a DQT
version of the Kochen-Specker theorem which implies that not only
DQT cannot be simulated by a non-contextual classical theory, but
also no one-to-one correspondence between $\left\{ 0,1\right\} $-valued
probabilities and mixed states in DQT no matter how mixed states are
defined. Notice that because the difficulty to define mixed states
in DQT, when we say ``no correspondence between ... and mixed states
in DQT,'' we always means ``no correspondence between ... and mixed
states in DQT no matter how mixed states are defined'' in the following
discussion.

It is not hard to imagine there is no analog of Gleason's theorem
$\left\{ 0,1\right\} $-valued probabilities and mixed states in DQT
because finite value probabilities cannot bijectively correspond to
mixed states in CQT as well. In section~\ref{sec:DQT-probability},
we try to investigate possible Gleason's theorem in DQT with $\left[0,1\right]$-valued
probability. We found that there is a basis-independent $\left[0,1\right]$-valued
Born rule when $p=d=3$ in DQT, but there still exists a $\left[0,1\right]$-valued
probability which cannot correspond to any mixed states. Except $p=d=3$,
there is always some difficulty to define a $\left[0,1\right]$-valued
Born rule. First, we proved that if there is a $\left[0,1\right]$-valued
Born rule in DQT, it must be basis-dependent when $d\ge3$. Second,
when $p=7$ and $d=3$, we also numerically verified that there is
an unique $\left[0,1\right]$-valued probability so that most of the
states do not have a corresponding probability, and eliminate any
possible $\left[0,1\right]$-valued Born rule.

Because of the difficulty to have the Born rule in previous cases,
we consider the Born rule with the simplest interval-valued probability:
impossible and possible in section~\ref{sec:DQT-interval-valued}.
Although the interval-valued Born rule can be defined intuitively,
there is still an interval-valued probability corresponding to no
mixed state. Therefore, we can conclude that there is no one-to-one
correspondence between probabilities and mixed states no matter how
we discretize probability or state space.

\section{\label{sec:probability}Classical and Quantum Probability}

We can better understand quantum probability by comparing it with
classical probability~\cite{inun.425605319950101}. In classical
probability~\cite{rohatgi2011introduction,GrahamKnuthPatashnik1994},
when $\Omega$ is a finite set $\left\{ \omega_{0},\omega_{1},\ldots,\omega_{d-1}\right\} $,
it is sufficient to define a classical probability distribution $\mathcal{Q}:\Omega\rightarrow\left[0,1\right]$
by assigning each element $\omega$ a number $\mathcal{Q}\left(\omega\right)$
with 
\begin{equation}
1=\sum_{i=0}^{d-1}\mathcal{Q}\left(\omega_{i}\right)\textrm{ .}\label{eq:total-probability-classical}
\end{equation}
Because disjoint events can be always tested together without interfering
with each other, the probability of an event $A\subseteq\Omega$ is
the sum $\sum_{\omega\in A}\mathcal{Q}\left(\omega\right)$. For example,
when we toss a coin, the outcome is $\left\{ H,T\right\} $, and the
classical probability distribution can be given by $\mathcal{Q}_{q}\left(H\right)=q$
and $\mathcal{Q}_{q}\left(T\right)=1-q$ for any $q\in\left[0,1\right]$.
Although $\mathcal{Q}'\left(H\right)=\mathcal{Q}'\left(T\right)=1$
is also a function from $\Omega$ to $\left[0,1\right]$, $\mathcal{Q}'\left(H\right)+\mathcal{Q}'\left(T\right)=2\ne1$
implies that $\mathcal{Q}'$ is not a probability distribution.

The classical probability can be extended to a different range as
long as the extended probability still has an analog of total probability
one. To have an analog of the right hand side of equation (\ref{eq:total-probability-classical}),
we want our probability values~$\mathscr{L}$ together with an associative
and commutative addition~$\oplus$, i.e., $\left(\mathscr{L},\oplus\right)$
is a commutative semigroup~\cite{Jacobson1951,clifford1958,Wechler1992}.
Next, the whole set of $\mathscr{L}$ may be too big to consider as
probability values. For example, the minimal commutative semigroup
containing $\left[0,1\right]$ is $\left(\left[0,\infty\right),+\right)$,
but not every number in $\left[0,\infty\right)$ is a reasonable probability
value. Hence, we consider $\tilde{{\cal \mathscr{L}}}\subseteq\mathscr{L}$
as the set of allowed probability values. Finally, to represent ``the
total probability one,'' we need a predicate~$P$~\cite{PurdomBrown1995,Pierce2002,Voevodskyothers2013}.
If $\mathscr{L}$ is a numerical value, the predicate is usually ``$1=$
the sum of the probability values'' denoted by $P_{=}$. If $\mathscr{L}$
is a set of intervals, a special case of set-valued probability~\cite{Artstein1972,PuriRalescu1983},
the predicate is formulated by ``$1\in$ the sum of the interval-valued
probabilities'' denoted by $P_{\in}$.

When $\tilde{{\cal \mathscr{L}}}$ is a finite set, probability distribution
is called finite value probability distribution. The easiest example
is to consider $\left(\mathscr{L},\oplus\right)=\left(\R,+\right)$
as usual, but the allowed probability~$\tilde{{\cal \mathscr{L}}}$
is $\left\{ 0,1\right\} $. Then, the coin-tossing becomes deterministic
because the only two $\left\{ 0,1\right\} $-valued probability distributions
are $\check{\mathcal{Q}}_{0}\left(H\right)=0,\check{\mathcal{Q}}_{0}\left(T\right)=1$
and $\check{\mathcal{Q}}_{1}\left(H\right)=1,\check{\mathcal{Q}}_{1}\left(T\right)=0$.

If the allowed value~$\tilde{{\cal \mathscr{L}}}$ is a partition
of $\left[0,1\right]$~\cite{Artin1991,Wechler1992,PurdomBrown1995,DummitFoote2004},
like, $\hat{\mathscr{L}}_{n}=\left\{ \left\{ 0\right\} \right\} \cup\left\{ \left(\frac{k-1}{n},\frac{k}{n}\right]\middle|k=1,\ldots,n\right\} $
with the natural addition 
\begin{eqnarray}
I_{1}+I_{2} & = & \left\{ a+b\middle|a\in I_{1},b\in I_{2}\right\} \cap\left[0,1\right]\textrm{ .}\label{eq:interval-add}
\end{eqnarray}
Because the addition now may loss precision, the minimal semigroup
containing $\hat{\mathscr{L}}_{n}$ is $\left(\mathscr{L}_{n},+\right)$,
where $\mathscr{L}_{n}=\left\{ \left\{ 0\right\} ,\textrm{Ø}\right\} \cup\left\{ \left(\frac{k}{n},\frac{k'}{n}\right]\middle|k,k'=0,\ldots,n\textrm{ and }k<k'\right\} $.
$\hat{\mathscr{L}}_{n}$ is a partition of $\left[0,1\right]$ also
suggests that many $\left[0,1\right]$-valued statements may have
their counterpart by applying the natural subjective map~$\iota_{n}:\left[0,1\right]\rightarrow\hat{\mathscr{L}}_{n}$
\begin{equation} 
\iota_{n}\left(x\right)
=\cases{
	\left(\frac{\left\lceil n x\right\rceil - 1}{n},\frac{\left\lceil n x\right\rceil}{n}\right] &, if $x \ne 0$\\ 
	\left\{ 0\right\}  &, if $x = 0$  
}\textrm{ ,} \label{eq:iota}
\end{equation}
where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
is the smallest integer not less than $x$. For example, $\iota_{n}$
sends every $\left[0,1\right]$-valued probability distribution to
a $\hat{\mathscr{L}}_{n}$-valued probability distribution. More concretely,
when $n=1$, ${\cal \mathscr{L}}_{1}=\hat{\mathscr{L}}_{1}=\left\{ \left\{ 0\right\} ,\left(0,1\right]\right\} $,
there are three interval-valued probability distributions for coin-tossing:
$\hat{\mathcal{Q}}_{0}\left(H\right)=\left\{ 0\right\} ,\hat{\mathcal{Q}}_{0}\left(T\right)=\left(0,1\right]$;
$\hat{\mathcal{Q}}_{1}\left(H\right)=\left(0,1\right],\hat{\mathcal{Q}}_{1}\left(T\right)=\left\{ 0\right\} $;
and $\hat{\mathcal{Q}}_{2}\left(H\right)=\left(0,1\right],\hat{\mathcal{Q}}_{2}\left(T\right)=\left(0,1\right]$.
They are all induced by $\left[0,1\right]$-valued probability distributions
since $\hat{\mathcal{Q}}_{0}=\iota_{1}\circ\mathcal{Q}_{0}$; $\hat{\mathcal{Q}}_{1}=\iota_{1}\circ\mathcal{Q}_{1}$;
and $\hat{\mathcal{Q}}_{2}=\iota_{1}\circ\mathcal{Q}_{q}$ for $0<q<1$,
where $\circ$ is the function composition. Also notice that $\left\{ 0,1\right\} $
and $\left\{ \left\{ 0\right\} ,\left(0,1\right]\right\} $ both have
two possible values, but the number of probability distributions they
have are different, because the rule of addition is different.

We can similarly define a quantum probability distribution with a
given probability values~$\tilde{{\cal \mathscr{L}}}\subseteq{\cal \mathscr{L}}$
when the dimension of a Hilbert space is finite~\cite{Redhead1987-REDINA,inun.425605319950101}.
For each non-zero vector $\ket{\Phi}\in\C^{d*}=\left\{ \ket{\Phi}\in\C^{d}\middle|\ip{\Phi}{\Phi}\ne0\right\} $,
a $\tilde{{\cal \mathscr{L}}}$-valued quantum probability distribution
$\mathcal{P}:\C^{d*}\rightarrow\tilde{{\cal \mathscr{L}}}$ gives
a number ${\cal P}\left(\ket{\Phi}\right)\in\tilde{{\cal \mathscr{L}}}$
satisfying the following conditions: 
\begin{eqnarray}
 &  & {\displaystyle P\left(\sum_{i=0}^{d-1}{\cal P}\left(\ket{i}\right)\right)}\textrm{ for any orthonormal basis }\left\{ \ket{i}\right\} _{i=0}^{d-1}\textrm{ ;}\label{eq:total-probability-CQT}\\
 &  & {\cal P}\left(\ket{\Phi}\right)={\cal P}\left(\lambda\ket{\Phi}\right)\textrm{ for }\lambda\in\C^{*}=\C\backslash\left\{ 0\right\} \textrm{ ,}\label{eq:parallel-CQT}
\end{eqnarray}
where $P$ is the predicate for total probability one. Without a classical
counterpart, equation (\ref{eq:parallel-CQT}) holds because parallel
vectors always in the same linear subspace, and a linear subspace
is what can be tested in a quantum theory analog to a classical event.
Furthermore, two linear subspaces $V$ and $W$ can be tested together
if they are orthogonal of where orthogonality is defined by $\ip{\Psi}{\Phi}=0$
for all $\ket{\Psi}\in V$ and $\ket{\Phi}\in W$. Therefore, the
probability of a linear subspace $V$ is the sum $\sum_{i=0}^{d'-1}{\cal P}\left(\ket{i}\right)$,
where $\left\{ \ket{i}\right\} _{i=0}^{d'-1}$ is a orthonormal basis
of $V$. Because of the essential rule of $\mathcal{P}$, when there
is no confusion, we may call $\mathcal{P}$ simply a $\tilde{{\cal \mathscr{L}}}$-valued
probability\footnote{$\mathcal{P}$ is also called a frame function if we restrict the
domain to the unit sphere and $\tilde{{\cal \mathscr{L}}}=\left[0,1\right]$~\cite{gleason1957,peres1995quantum}.}.

In the same way as $\left[0,1\right]$-valued classical probabilities,
on a given Hilbert space, there are many $\left[0,1\right]$-valued
quantum probability assignments. Given a two dimensional Hilbert space,
a vector $\ket{\Phi}$ can be normalized and written in $\left(\begin{array}{c}
\cos\theta\\
\rme^{\rmi\gamma}\sin\theta
\end{array}\right)$. Consider 
\begin{equation}
{\cal P}_{1}
\left(\begin{array}{c} \cos\theta\\ \rme^{\rmi\gamma}\sin\theta \end{array}\right)=
\cases{ 
0 & , if $0 \le \theta < \frac{\pi}{2}$\\
1 & , if $\frac{\pi}{2} \le \theta < \pi$ } 
\end{equation}
We can extend the domain of ${\cal P}_{1}$ to the whole $\C^{d*}$
by equation (\ref{eq:parallel-CQT}), and get a $\left[0,1\right]$-valued
and $\left\{ 0,1\right\} $-valued probability. Similar to the classical
case, $\iota_{n}\left({\cal P}_{1}\right)$ gives a $\hat{\mathscr{L}}_{n}$-valued
probability.

In section \ref{sec:DQT-interval-valued}, we are going to replace
complex numbers~$\C$ by finite fields~$\ff{p^{2}}$, and define
a discrete quantum theory (DQT)~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
Probability in DQT is exactly the same as we defined in previous paragraphs
except replacing every $\C$ by $\ff{p^{2}}$, and $\left[0,1\right]$-valued,
finite value, and interval-valued probability can all be defined as
we expect.

\section{\label{sec:Conventional-Quantum-Theory}Gleason's Theorem in Conventional
Quantum Theory}

We can define another $\left[0,1\right]$-valued probability assignment
$\tilde{{\cal P}}_{\Psi}:\C^{d*}\rightarrow\left[0,1\right]$ by means
of the Born rule~\cite{Born1984,Mermin2007} 
\begin{equation}
\tilde{{\cal P}}_{\Psi}\left(\ket{\Phi}\right)=\frac{\ip{\Psi}{\Phi}\ip{\Phi}{\Psi}}{\ip{\Psi}{\Psi}\ip{\Phi}{\Phi}}\label{BornRule.pure}
\end{equation}
for any pure state $\ket{\Psi}\in\C^{d*}$. We can also consider the
system in a mixed state represented by a density matrix $\rho=\sum_{j}q_{j}\frac{\proj{\Psi_{j}}}{\ip{\Psi_{j}}{\Psi_{j}}}$,
where $q_{j}$ is a $\left[0,1\right]$-valued classical probability
distribution, i.e., $\Tr\left(\rho\right)=1$. The Born rule can be
extended to define a $\left[0,1\right]$-valued probability for $\rho$
by 
\begin{eqnarray}
\tilde{{\cal P}}_{\rho}\left(\ket{\Phi}\right) & = & \Tr\left(\rho\frac{\proj{\Phi}}{\ip{\Phi}{\Phi}}\right)=\sum_{j}q_{j}\tilde{{\cal P}}_{\Psi_{j}}\left(\ket{\Phi}\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

Not only the Born rule gives a $\left[0,1\right]$-valued probability
for a mixed state, but all $\left[0,1\right]$-valued probabilities
for $d\ge3$ comes from this way by Gleason's theorem~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.
\begin{thm}[Gleason's]
\label{thm:Gleason's}For $d\ge3$, if ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$
is a $\left[0,1\right]$-valued probability, there is an unique density
matrix $\rho$ such that ${\cal P}=\tilde{{\cal P}}_{\rho}$.
\end{thm}
\noindent Although for $d\ge3$ there is a one-to-one correspondence
between mixed states and probabilities, when $d=2$, the example ${\cal P}_{1}$
cannot correspond to any mixed state. One reason is that ${\cal P}_{1}$
not continuous, but the probabilities induces by the Born rule is
always continuous. Another reason is that the zeros of ${\cal P}_{1}$,
$\left\{ \ket{\Phi}\in\C^{d*}\middle|{\cal P}_{1}\left(\ket{\Phi}\right)=0\right\} $,
is not contained in a $\left(d-1\right)$-dimensional subspace, but
the zeros of $\tilde{{\cal P}}_{\rho}$, $\left\{ \ket{\Phi}\in\C^{d*}\middle|\tilde{{\cal P}}_{\rho}\left(\ket{\Phi}\right)=0\right\} $,
is always a subset of a $\left(d-1\right)$-dimensional subspace.
The second reason will be used over and over again to prove a variant
of probability is not induced by an analog of the Born rule in this
paper.

\section{\label{sec:CQT-Variants}Variants of Conventional Quantum Theory}

In contrasts of existing many finite value probability distributions
in classical case, we proved there is no $\left\{ 0,1\right\} $-valued
quantum probability distribution in theorem \ref{thm:Kochen-Specker}.
In general~\cite{Redhead1987-REDINA}, Gleason's theorem asserts
that a quantum probability distribution must be a continuous function
in CQT. Therefore, if there is a finite value quantum probability
distribution in CQT, it must be constant function.
\begin{cor}
\label{cor:Finite-Value-Probility}For $d\ge3$, if $\frac{1}{d}\in\check{\mathscr{L}}$,
the only $\check{\mathscr{L}}$-valued probability $\check{\mathcal{P}}_{0}:\C^{d*}\rightarrow\check{\mathscr{L}}$
is $\check{\mathcal{P}}_{0}\left(\ket{\Phi}\right)=\frac{1}{d}$ for
all $\ket{\Phi}\in\C^{d*}$; otherwise, there is no $\check{\mathscr{L}}$-valued
probability $\check{\mathcal{P}}:\C^{d*}\rightarrow\check{\mathscr{L}}$.
\end{cor}
In contrast of finite value probability, we do not have to worry about
lacking interval-valued probability. Given any $\left[0,1\right]$-valued
probability~${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$, every
$\iota_{n}:\left[0,1\right]\rightarrow\hat{\mathscr{L}}_{n}$ induces
a $\hat{\mathscr{L}}_{n}$-valued probability~$\iota_{n}\left({\cal P}\right)$.
Furthermore, given any mixed state $\rho$, the interval-valued Born
rule of $\ket{\Phi}\in\C^{d*}$ is given by 
\begin{equation}
\bar{{\cal P}}_{\rho}\left(\ket{\Phi}\right)=\iota\left(\tilde{{\cal P}}_{\rho}\left(\ket{\Phi}\right)\right)\textrm{ .}\label{eq:interval-valued-Born-rule}
\end{equation}
However, an analog of Gleason's theorem does not hold because interval-valued
probability gives us more freedom to assign probability values, and
we can assign probability zero to some states which should not be
probability zero according to the Born rule. Given an interval-valued
probability~$\bar{{\cal P}}_{\Psi}$ for a pure state~$\ket{\Psi}\in\C^{d*}$,
the zeros of $\bar{{\cal P}}_{\Psi}$ is a $\left(d-1\right)$-dimensional
subspace, i.e., 
\begin{eqnarray}
 &  & \ip{\Psi}{\Phi}=0\Leftrightarrow\bar{{\cal P}}_{\Psi}\left(\ket{\Phi}\right)=\left\{ 0\right\} \textrm{ ,}\label{eq:modality-CQT-2}
\end{eqnarray}
and the zeros of general $\bar{{\cal P}}_{\rho}$ should be always
contained in a $\left(d-1\right)$-dimensional subspace. Consider
$\hat{{\cal P}}_{1}:\C^{d*}\rightarrow\hat{\mathscr{L}}_{n}$ 
\begin{equation}
\hat{{\cal P}}_{1}\left(\ket{\Phi}\right)=\cases{ 
	\left\{ 0\right\}  & , if $\ket{\Phi} = \lambda\ket{\Phi_{0}}$ ; \\
	\bar{{\cal P}}_{\ket{0}}\left(\ket{\Phi}\right)  & , otherwise; 
}\label{eq:hatcalP1}
\end{equation}
where $d\ge2$, $\lambda\in\C^{*}$, $\ket{\Phi_{0}}=\ket{0}+\sqrt{2n-1}\ket{1}$,
and $\left\{ \ket{0},\ket{1},\ldots,\ket{d-1}\right\} \subset\C^{d*}$
is a fixed orthonormal basis. $\hat{{\cal P}}_{1}$ is an interval-valued
probability which cannot correspond to any mixed states because the
zeros of $\hat{{\cal P}}_{1}$ is not contained in a $\left(d-1\right)$-dimensional
subspace as proved in theorem \ref{thm:NotGleason-1}.

\section{\label{sec:DQT-Born-Rule}Discrete Quantum Theory and the Born Rule}

Our fundamental divergence from CQT is to replace continuous complex
amplitudes in the field of complex numbers $\C$ by discrete fields
$\ff{p^{2}}$. If we restrict ourselves to odd primes with $p\equiv3\mod4$,
the fields $\ff{p}$ are exactly those for which $x^{2}+1$ has no
root in the field, and we can adjoin $\rmi$ as a root of $x^{2}+1$
to the field $\ff{p}$. For a given element $\alpha\in\ff{p^{2}}$,
we define the equivalent of complex conjugation as the map $\alpha\mapsto\alpha^{p}$,
which we may write as $\alpha^{*}=\alpha^{p}$. The resulting extended
field is isomorphic to $\ff{p^{2}}$ and is a realization of discrete
complex numbers suitable for quantum mechanical calculations.

Let us start by defining a vector space $\ffd{p^{2}}$ of $d$-dimensional
vectors with elements in $\ff{p^{2}}$, where the conjugate transpose
is defined in the natural way giving us the notion of a dual vector
$\bra{\Psi}$ for every vector $\ket{\Psi}\in\ffd{p^{2}}$. If we
consider an orthogonal basis $\{\left|i\right\rangle \}$ of $\ffd{p^{2}}$,
and write two arbitrary vectors in the form 
\begin{equation}
\ket{\Psi}=\sum_{i=0}^{d-1}~\alpha_{i}\left|i\right\rangle \ ,\ \ket{\Phi}=\sum_{i=0}^{d-1}~\beta_{i}\left|i\right\rangle ,
\end{equation}
with $\alpha_{i}$ and $\beta_{i}$ elements of the field $\ff{p^{2}}$.
The Hermitian product in our discrete number system is thus reducible
to the form 
\begin{equation}
\ip{\Phi}{\Psi}=\sum_{i=0}^{d-1}~{\beta_{i}}^{p}~\alpha_{i}^{\;}\ .\label{innerprod}
\end{equation}
Notice that this product is technically not an inner product because
there are vectors $\ket{\Psi}$ other than the zero vector whose ``norm''
$\braket{\Psi}{\Psi}$ vanishes. We therefore exclude such cases by
moving to the domain $\ffzd{p^{2}}$, where the $^{*}$ indicates
the exclusion of null vectors; that is, we consider $\ket{\Psi}\in\ffzd{p^{2}}$,
where 
\begin{equation}
\ffzd{p^{2}}=\left\{ \ket{\Psi}\in\ffd{p^{2}}\mid\ip{\Psi}{\Psi}\ne0\right\} \ .
\end{equation}

As described in the end of section \ref{sec:probability}, given a
set of probability values~$\tilde{{\cal \mathscr{L}}}$ within a
semigroup~$\left(\mathscr{L},\oplus\right)$, we can define $\tilde{{\cal \mathscr{L}}}$-valued
probability by replacing every $\C$ by $\ff{p^{2}}$ in equation
(\ref{eq:total-probability-CQT}) and (\ref{eq:parallel-CQT}). As
in CQT, theorem \ref{thm:Kochen-Specker} shows there is no $\left\{ 0,1\right\} $-valued
probability in DQT for $d\ge3$. Therefore, we will focus on $\left[0,1\right]$-Valued
Probability and interval-valued probability later.

Although $\tilde{{\cal \mathscr{L}}}$-valued probability may be defined
as we expect, it is not obvious how to define the $\tilde{{\cal \mathscr{L}}}$-valued
Born rule because the Born rule in CQT (\ref{BornRule.pure}) will
yield a value in $\ff{p}$ which has no way to interpreted as a probability.
Furthermore, as in CQT, the $\left[0,1\right]$-valued Born rule can
be justified by Gleason's theorem, while the interval-valued Born
rule cannot. We may not expect a Born rule in DQT can always be justified
by an analog of Gleason's theorem. Hence, it may be a better strategy
to find a Born rule in DQT independently.

First, given a pure state $\ket{\Psi}\in\ffzd{p^{2}}$, a $\tilde{{\cal \mathscr{L}}}$-valued
Born-rule~$\tilde{\pi}:\ffzd{p^{2}}\rightarrow\left(\ffzd{p^{2}}\rightarrow\left[0,1\right]\right)$
should give a $\tilde{{\cal \mathscr{L}}}$-valued probability~$\tilde{\pi}_{\Psi}$.

Second, a $\tilde{{\cal \mathscr{L}}}$-valued Born-rule should also
satisfy 
\begin{equation}
\ip{\Psi}{\Phi}=0\Leftrightarrow\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{0}\textrm{ ,}\label{eq:zero}
\end{equation}
where $\tilde{0}=0$ for $\tilde{{\cal \mathscr{L}}}=\left[0,1\right]$
and $\tilde{0}=\left\{ 0\right\} $ for $\tilde{{\cal \mathscr{L}}}=\hat{\mathscr{L}}_{n}$.
To motivate equation (\ref{eq:zero}), consider the state $\alpha\ket{0}+\beta\ket{1}$
in the vector space spanned by $\ket{0}$ and $\ket{1}$. We can embed
this vector subspace in the larger $d$-dimensional space spanned
by $\ket{0}$, $\ket{1}$, \ldots{}, $\ket{d-1}$ and view our state
in the larger vector space, i.e., view $\alpha\ket{0}+\beta\ket{1}$
as $\alpha\ket{0}+\beta\ket{1}+0\ket{2}+\cdots+0\ket{d-1}$. The probabilities
corresponding to outcomes $\ket{0}$ and $\ket{1}$ should not depend
on whether we are viewing the state in the original two-dimensional
subspace or the larger one. Thus, in light of equation (\ref{eq:total-probability-DQT}),
the probabilities corresponding to outcomes $\ket{2}$, \ldots{},
$\ket{d-1}$ should all be zero. Conversely, if the probabilities
of non-orthogonal pairs are zero, we may get too many information
from measurement which may even contradict to each other, and hence
unrealistic. For example, when $d=2$ and $\tilde{{\cal \mathscr{L}}}=\left[0,1\right]$,
if there are two non parallel orthonormal basis $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{0'},\ket{1'}\right\} $ both have $\tilde{\pi}_{\Psi}\left(\ket{0}\right)=\tilde{\pi}_{\Psi}\left(\ket{0'}\right)=0$,
then $\tilde{\pi}_{\Psi}\left(\ket{1}\right)=\tilde{\pi}_{\Psi}\left(\ket{1'}\right)=1$
which cannot help us to identify the pre-measurement state because
pre-measurement state cannot be both $\ket{1}$ and $\ket{1'}$ at
the same time.

The above two conditions are sufficient to discuss whether there is
a $\tilde{{\cal \mathscr{L}}}$-valued Born-rule or not in some cases.
However, when these two conditions are not enough, we may consider
another desirable property of a Born-rule in DQT called basis-independent:
\begin{equation}
\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{\pi}_{\mathbf{U}\ket{\Psi}}\left(\mathbf{U}\ket{\Phi}\right)\textrm{ ,}\label{eq:basis-independent}
\end{equation}
where $\ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}$ and $\mathbf{U}$ is
any unitary map, which means the quantum theory remains the same no
matter which orthonormal basis we represent the states and observables.

Finally, although we have not defined mixed states in discrete quantum
theory, no matter how a mixed state~$\rho$ is defined, $\rho$ must
be an ensemble among some pure states. Let $\ket{\Psi}$ be a part
of the ensemble for $\rho$. For any $\ket{\Phi}\in\ffzd{p^{2}}$,
when $\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)\ne\tilde{0}$, we
must have $\tilde{\pi}_{\rho}\left(\ket{\Phi}\right)\ne\tilde{0}$.
Moreover, the zeros of $\tilde{\pi}_{\Psi}$, $\left\{ \ket{\Phi}\in\C^{d*}\middle|\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{0}\right\} $
form a $\left(d-1\right)$-dimensional subspace as in equation (\ref{eq:zero}).
Therefore, the zeros of $\tilde{\pi}_{\rho}$, $\left\{ \ket{\Phi}\in\C^{d*}\middle|\tilde{\pi}_{\rho}\left(\ket{\Phi}\right)=\tilde{0}\right\} $
must be a subset of a $\left(d-1\right)$-dimensional subspace no
matter how a mixed state~$\rho$ is defined.

\section{\label{sec:DQT-probability}Discrete Quantum Theory with $\left[0,1\right]$-Valued
Probability}

We want to consider DQT with conventional probability $\left[0,1\right]$
for two reasons. First, because it is an conventional probability,
if we could build a discrete quantum theory with it, we do not have
to worry about how to interpret the meaning of probability. Second,
if we can find any $\left[0,1\right]$-valued probabilities and Born
rules, $\iota_{n}:\left[0,1\right]\rightarrow\hat{\mathscr{L}}_{n}$
will induce a corresponding interval-valued probabilities and Born
rules, but not vice visa.

In order to define a $\left[0,1\right]$-valued Born rules in DQT,
we first need to consider the formula for conventional Born rule in
DQT~$c:\left(\ff{p^{2}}^{d}\times\ff{p^{2}}^{d}\right)\rightarrow\ff{p}$
\begin{equation}
c\left(\Psi,\Phi\right)=\frac{\ip{\Psi}{\Phi}\ip{\Phi}{\Psi}}{\ip{\Psi}{\Psi}\ip{\Phi}{\Phi}}\label{eq:cosine_square}
\end{equation}
The notation~$c$ is used to indicate that the conventional Born
rule is the square of the cosine of the angle between two states,
and is called the cross when we consider trigonometry over finite
fields~\cite{Wildberger2005}. Although the cross itself cannot give
us a Born rule in DQT, any following Born rules in DQT are based on
it.

When $d=2$, given any sequence of number $\left\{ q_{2},\ldots,q_{\frac{p-1}{2}}\right\} \subset\left(0,1\right)$,
we can define a basis-independent $\left[0,1\right]$-valued Born
rule~$\tilde{\pi}:\ff{p^{2}}^{2*}\rightarrow\left(\ff{p^{2}}^{2*}\rightarrow\left[0,1\right]\right)$
as follow. 
\begin{equation}
\tilde{\pi}_{\ket{\Psi}}\left(\ket{\Phi}\right)=\cases{ 
	0 & , if $c\left(\Psi,\Phi\right) = 0$ ; \\
	1 & , if $c\left(\Psi,\Phi\right) = 1$ ; \\
	1/2 & , if $c\left(\Psi,\Phi\right) = \frac{1-p}{2}$ ; \\
	q_{j} & , if $c\left(\Psi,\Phi\right) = j$ for $j = 2, \ldots, \frac{p-1}{2}$ ; \\
	1 - q_{j} & , if $c\left(\Psi,\Phi\right) = 1 - j$ for $j = 2, \ldots, \frac{p-1}{2}$ .
}\label{eq:tildepi2}
\end{equation}
Notice that the fourth and fifth cases never happens when $p=3$.
This yields an unique basis-independent $\left[0,1\right]$-valued
Born rule. When $p>3$, there is infinitely many basis-independent
$\left[0,1\right]$-valued Born rule. It is also easy to get a $\left[0,1\right]$-valued
probability~$\pi_{1}:\ff{p^{2}}^{2*}\rightarrow\left[0,1\right]$

\begin{equation}
\pi_{1}\left(\ket{\Phi}\right)=\cases{ 
	1/2 & , if $c\left(\ket{0},\Phi\right) = \frac{1-p}{2}$ ; \\
	1 & , if $c\left(\ket{0},\Phi\right) = j$ for $j = 1, \ldots, \frac{p-1}{2}$ ; \\
	0 & , if $c\left(\ket{0},\Phi\right) = 1 - j$ for $j = 1, \ldots, \frac{p-1}{2}$ .
}\label{eq:pi1}
\end{equation}
which cannot correspond to any mixed state no matter how to define
mixed states because the zeros of $\pi_{1}$ is not contained in a
$1$-dimensional linear subspace\footnote{When $p=3$, there is still a $\left[0,1\right]$-valued probability
which cannot correspond to any mixed state. However, it is more messy
because it does not come from a $\left[0,1\right]$-valued Born rule,
and we omit it here.}.

For $d\ge3$, we will discuss $d=p=3$ first because it is a special
case. There is an unique basis-independent $\left[0,1\right]$-valued
Born-rule on DQT~$\tilde{\pi}:\ff{3^{2}}^{3*}\rightarrow\left(\ff{3^{2}}^{3*}\rightarrow\left[0,1\right]\right)$
\begin{equation}
\tilde{\pi}_{\ket{\Psi}}\left(\ket{\Phi}\right)=\cases{ 
	0 & , if $c\left(\Psi,\Phi\right) = 0$ ; \\
	1 & , if $\ket{\Psi}=\lambda\ket{\Phi}$ for $\lambda\in\ff{3^{2}}$; \\
	1/2 & , if $c\left(\Psi,\Phi\right) = -1$ ; \\
	1/4 & , otherwise . \\
}\label{eq:tildepi3}
\end{equation}
Moreover, there is a $\left[0,1\right]$-valued probability~$\pi_{2}:\ff{3^{2}}^{3*}\rightarrow\left[0,1\right]$
defined in example \ref{exa:tildepi} which does not correspond to
any mixed state.

For $d\ge3$ except $d=p=3$, there is no basis-independent $\left[0,1\right]$-valued
Born-rule as shown in theorem \ref{thm:NotGleasonDQT-group}. We have
also numerical verified the unique $\left[0,1\right]$-valued probabilities
is $\pi_{0}\left(\ket{\Phi}\right)=\frac{1}{3}$ for all $\ket{\Phi}\in\ff{p^{2}}^{3*}$
when $d=3$ and $p=7$. In this case, there is no $\left[0,1\right]$-valued
Born-rule even basis-dependent. In general, we conjecture the constant
function~$\pi_{0}$ is the unique $\left[0,1\right]$-valued probabilities
for $d\ge3$ except $d=p=3$, and there is no $\left[0,1\right]$-valued
Born-rule.

\section{\label{sec:DQT-interval-valued}Discrete Quantum Theory with Interval-Valued
Probability}

Although we have some difficulty to find a $\left[0,1\right]$-valued
Born rule, the same task can be finished easily if we consider the
simplest interval probability value~${\cal \mathscr{L}}_{1}=\hat{\mathscr{L}}_{1}=\left\{ \left\{ 0\right\} ,\left(0,1\right]\right\} $.
The unique $\hat{\mathscr{L}}_{1}$-valued Born rule for pure states
$\bar{\pi}_{\Psi}:\ffzd{p^{2}}\rightarrow\hat{\mathscr{L}}_{1}$ is
defined as
\begin{equation}
\bar{\pi}_{\Psi}\left(\ket{\Phi}\right)=\cases{ 
	\{0\}              & , if $\ip{\Psi}{\Phi} = 0$ ; \\
	\left(0,1\right] & , otherwise; 
}\label{eq:barpi}
\end{equation}
 which is basis-independent as well.

Similar to CQT, in theorem \ref{thm:NotGleason}, we proved that any
mixed state cannot correspond to a $\hat{\mathscr{L}}_{1}$-valued
probability~$\hat{\pi}_{1}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
which is defined as follow: 
\begin{equation}
\hat{\pi}_{1}\left(\ket{\Phi}\right)=\cases{ 
	\{0\} & , if $\ket{\Phi} = \lambda\ket{\Phi_{0}}$ ; \\
	\bar{\pi}_{\ket{0}}\left(\ket{\Phi}\right) & , otherwise; 
}\label{eq:hatpi1}
\end{equation}
where $d\ge2$, $\lambda\in\C^{*}$, $\ket{\Phi_{0}}=\ket{0}+\ket{1}$,
and $\left\{ \ket{0},\ket{1},\ldots,\ket{d-1}\right\} \subset\ffzd{p^{2}}$
is a fixed orthonormal basis.

\section*{References}

\bibliographystyle{iopart-num}
\addcontentsline{toc}{section}{\refname}\bibliography{discreteGBKS}

\appendix

\section{\label{sec:Proofs}Proofs}
\begin{thm}
\label{thm:Kochen-Specker}For $d\ge3$, there is no $\left\{ 0,1\right\} $-valued
probability~$\check{{\cal P}}:\mathbb{F}^{d*}\rightarrow\left\{ 0,1\right\} $,
where $\mathbb{F}$ is $\C$ or $\ff{p^{2}}$.\end{thm}
\begin{proof}
\begin{table*}
\center{%
\begin{tabular}{c|cccc|c}
\hline 
$\check{{\cal P}}\left(\ket{\Phi}\right)=1$  & \multicolumn{4}{c|}{$\check{{\cal P}}\left(\ket{\Phi}\right)=0$} & $\check{{\cal P}}$ of the first vector is $1$ because of\tabularnewline
\hline 
$001$  & %
\fbox{$100$}  & $010$  & $110$  & $1\bar{1}0$  & arbitrary choice of $z$ axis\tabularnewline
$101$  & $\bar{1}01$  & $010$  &  &  & arbitrary choice of $x$ vs $-x$\tabularnewline
$011$  & $0\bar{1}1$  & $100$  &  &  & arbitrary choice of $y$ vs $-y$\tabularnewline
$1\bar{1}\beta$  & $\bar{1}1\beta$  & $110$  & $\alpha0\bar{1}$  & %
\fbox{$0\alpha1$}  & arbitrary choice of $x$ vs $y$\tabularnewline
$10\beta$  & $\alpha0\bar{1}$  & $010$  & $\alpha\bar{1}\bar{1}$  &  & orthogonality to 2nd and 3rd vectors\tabularnewline
$\alpha11$  & $0\bar{1}1$  & $\alpha\bar{1}\bar{1}$  & $\bar{1}0\beta$  &  & orthogonality to 2nd and 3rd vectors\tabularnewline
$\alpha01$  & $010$  & $\bar{1}0\beta$  & $\bar{1}\bar{1}\beta$  &  & orthogonality to 2nd and 3rd vectors\tabularnewline
$11\beta$  & $1\bar{1}0$  & $\bar{1}\bar{1}\beta$  & $0\alpha\bar{1}$  &  & orthogonality to 2nd and 3rd vectors\tabularnewline
$01\beta$  & $100$  & $0\alpha\bar{1}$  & $\bar{1}\alpha\bar{1}$  &  & orthogonality to 2nd and 3rd vectors\tabularnewline
$1\alpha1$  & $\bar{1}01$  & $\bar{1}\alpha\bar{1}$  & %
\fbox{$0\bar{1}\beta$}  &  & orthogonality to 2nd and 3rd vectors\tabularnewline
\hline 
\end{tabular}}\caption{\label{tab:proof-of-K-S}Proof of theorem~\ref{thm:Kochen-Specker}}
\end{table*}
\footnote{The following proof assume $p\ge7$, and there is a longer proof for
$p=3$.} Our proof is almost the same as the proof of the similar statement
in \cite{Peres1991} and in section 7-3 of \cite{peres1995quantum}.
Except we consider Gaussian integers instead of $\sqrt{2}$, because
$\sqrt{2}$ may not be in $\ff{p^{2}}$. Suppose $\check{{\cal P}}$
exists, and consider the set of all vectors with entries in $\left\{ 0,1,-1,1+\rmi,1-\rmi,-1+\rmi,-1-\rmi\right\} $.
In order to represents these vectors in a more condense form, we use
$0$, $1$, $\bar{1}$, $\alpha$, and $\beta$ to represents $0$,
$1$,$-1$, $1+\rmi$, and $1-\rmi$, and write in a three character
string. For example, $\left(\begin{array}{c}
0\\
-1\\
1-\rmi
\end{array}\right)$ is represented by $0\bar{1}\beta$. Then, we write these vectors
in different columns in table \ref{tab:proof-of-K-S} depending on
$\check{{\cal P}}\left(\ket{\Phi}\right)=1$ or $\check{{\cal P}}\left(\ket{\Phi}\right)=0$.
Examining the table from top to the bottom, we will eventually get
a contradiction. The set of vectors are invariant under interchanges
of the $x$, $y$, and $z$ axes. Hence, we can assume $\check{{\cal P}}\left(100\right)=\check{{\cal P}}\left(010\right)=0$
and $\check{{\cal P}}\left(001\right)=1$. Furthermore, $110$ and
$1\bar{1}0$ are orthogonal to $001$, so that $\check{{\cal P}}\left(110\right)=\check{{\cal P}}\left(1\bar{1}0\right)=0$.
A similar argument can be used to construct the second, third, and
fourth rows. After we know enough values of $\check{{\cal P}}\left(\ket{\Phi}\right)$,
we find that $10\beta$, $\alpha0\bar{1}$, and $010$ is an orthogonal
basis, and we already know that $\check{{\cal P}}\left(\alpha0\bar{1}\right)=\check{{\cal P}}\left(010\right)=0$,
so $\check{{\cal P}}\left(10\beta\right)=1$. Following a similar
procedure, we can continue evaluating the entire content of table
\ref{tab:proof-of-K-S}. Finally, we can see that the boxed vectors~$100$,
$0\alpha1$, and $0\bar{1}\beta$ form an orthogonal basis, but we
already know $\check{{\cal P}}\left(100\right)=\check{{\cal P}}\left(0\alpha1\right)=\check{{\cal P}}\left(0\bar{1}\beta\right)=0$.
This contradicts equation (\ref{eq:total-finite-value-probability-DQT}).
Therefore, there is no $\left\{ 0,1\right\} $-valued probability.$\QED$\end{proof}
\begin{thm}
\label{thm:NotGleason-1}$\hat{{\cal P}}_{1}:\C^{d*}\rightarrow\hat{\mathscr{L}}_{n}$
is an interval-valued probability, but $\bar{{\cal P}}_{\rho}\ne\hat{{\cal P}}_{1}$
for any mixed state $\rho$.\end{thm}
\begin{proof}
Following are some familiar fact which will be used in the proof:
\begin{eqnarray}
\left\lceil x+y\right\rceil  & \le & \left\lceil x\right\rceil +\left\lceil y\right\rceil \label{eq:ceiling-add}\\
\max\left(I_{1}+I_{2}\right) & = & \min\left\{ 1,\max I_{1}+\max I_{2}\right\} \label{eq:interval-add-right}
\end{eqnarray}
for $x,y\in\left[0,1\right]$ and $I_{1},I_{2}\in\mathscr{L}_{n}$~\cite{GrahamKnuthPatashnik1994}.

To be an interval-valued probability, $\hat{{\cal P}}_{1}$ needs
to satisfy equation (\ref{eq:total-probability-CQT}) and (\ref{eq:parallel-CQT}).
Equation (\ref{eq:parallel-CQT}) is trivial. For equation (\ref{eq:total-probability-CQT}),
we want to prove that for any orthonormal basis $\left\{ \ket{i'}\right\} _{i=0}^{d-1}$,
\begin{equation}
1\in{\displaystyle \sum_{i=0}^{d-1}\hat{{\cal P}}_{1}\left(\ket{i'}\right)}\textrm{ .}\label{eq:total-probability-hatcalP1}
\end{equation}

\begin{casenv}
\item If $\ket{\Phi_{0}}$ does not parallel to any vector in $\left\{ \ket{i'}\right\} _{i=0}^{d-1}$,
then 
\begin{equation}
1\in{\displaystyle \sum_{i=0}^{d-1}\bar{{\cal P}}_{\ket{0}}\left(\ket{i'}\right)}\overset{\left(\ref{eq:hatcalP1}\right)}{=}{\displaystyle \sum_{i=0}^{d-1}\hat{{\cal P}}_{1}\left(\ket{i'}\right)}\textrm{ .}
\end{equation}

\item If $\ket{\Phi_{0}}$ parallels to a vector in $\left\{ \ket{i'}\right\} _{i=0}^{d-1}$,
WLOG, let $\ket{0'}=\lambda_{0}\ket{\Phi_{0}}$. In order to prove
equation (\ref{eq:total-probability-hatcalP1}), we are going to prove
the right end of the interval $\sum_{i=0}^{d-1}\hat{{\cal P}}_{1}\left(\ket{i'}\right)$
is $1$ as following. 
\begin{eqnarray}
 &  & \max{\displaystyle \sum_{i=0}^{d-1}\hat{{\cal P}}_{1}\left(\ket{i'}\right)}\\
 & \overset{\left(\ref{eq:hatcalP1}\right)}{=} & \max{\displaystyle \sum_{i=1}^{d-1}\bar{{\cal P}}_{\ket{0}}\left(\ket{i'}\right)}\\
 & \overset{\left(\ref{eq:interval-add-right}\right)}{=} & \min\left\{ 1,\sum_{i=1}^{d-1}\max\bar{{\cal P}}_{\ket{0}}\left(\ket{i'}\right)\right\} \\
 & \overset{\left(\ref{eq:iota}\right)}{=} & \min\left\{ 1,\sum_{i=1}^{d-1}\frac{1}{n}\left\lceil n\tilde{{\cal P}}_{\ket{0}}\left(\ket{i'}\right)\right\rceil \right\} \\
 & = & 1\textrm{ .}
\end{eqnarray}
The last equality holds because
\begin{eqnarray}
 &  & \sum_{i=1}^{d-1}\frac{1}{n}\left\lceil n\tilde{{\cal P}}_{\ket{0}}\left(\ket{i'}\right)\right\rceil \\
 & \overset{\left(\ref{eq:ceiling-add}\right)}{\ge} & \frac{1}{n}\left\lceil n\sum_{i=1}^{d-1}\tilde{{\cal P}}_{\ket{0}}\left(\ket{i'}\right)\right\rceil \\
 & \overset{\left(\ref{eq:total-probability-CQT}\right)}{=} & \frac{1}{n}\left\lceil n\left(1-\tilde{{\cal P}}_{\ket{0}}\left(\ket{0'}\right)\right)\right\rceil \\
 & \overset{\left(\ref{BornRule.pure}\right)}{=} & \frac{1}{n}\left\lceil n\left(1-\frac{\ip{0}{\Phi_{0}}\ip{\Phi_{0}}{0}}{\ip{0}{0}\ip{\Phi_{0}}{\Phi_{0}}}\right)\right\rceil \\
 & \overset{\left(\ref{eq:hatcalP1}\right)}{=} & \frac{1}{n}\left\lceil n-\frac{1}{2}\right\rceil =1\textrm{ .}
\end{eqnarray}

\end{casenv}
We will prove $\bar{{\cal P}}_{\rho}\ne\hat{{\cal P}}_{1}$ for any
mixed state $\rho$ by comparing the zeros of $\bar{{\cal P}}_{\rho}$,
$\left\{ \ket{\Phi}\in\C^{d*}\middle|\bar{{\cal P}}_{\rho}\left(\ket{\Phi}\right)=\left\{ 0\right\} \right\} $,
and the zeros of $\hat{{\cal P}}_{1}$, $\left\{ \ket{\Phi}\in\C^{d*}\middle|\hat{{\cal P}}_{1}\left(\ket{\Phi}\right)=\left\{ 0\right\} \right\} $.
Let $\ket{\Psi}$ be any pure state which is a part of the ensemble
for $\rho$, then we have
\[
\left\{ \ket{\Phi}\in\C^{d*}\middle|\bar{{\cal P}}_{\rho}\left(\ket{\Phi}\right)=\left\{ 0\right\} \right\} \subseteq\left\{ \ket{\Phi}\in\C^{d*}\middle|\ip{\Psi}{\Phi}=0\right\} \textrm{ ,}
\]
i.e., the zeros of $\bar{{\cal P}}_{\rho}$ is a subset of a $\left(d-1\right)$-dimensional
hyper-plane. However, the zeros of $\hat{{\cal P}}_{1}$ is a proper
superset of a $\left(d-1\right)$-dimensional hyper-plane, i.e., 
\[
\left\{ \ket{\Phi}\in\C^{d*}\middle|\ip{0}{\Phi}=0\right\} \subsetneq\left\{ \ket{\Phi}\in\C^{d*}\middle|\bar{{\cal P}}_{\Psi}\left(\ket{\Phi}\right)=\left\{ 0\right\} \right\} 
\]
Therefore, $\bar{{\cal P}}_{\rho}\ne\hat{{\cal P}}_{1}$ for any mixed
state $\rho$.$\QED$\end{proof}
\begin{example}
\label{exa:tildepi}A $\left[0,1\right]$-valued probability~$\pi_{2}:\ff{3^{2}}^{3*}\rightarrow\left[0,1\right]$
is defined as follow. Notice that we list parallel vector only once
because of equation (\ref{eq:parallel-CQT}). To simplify the notation,
we extend the notation in the proof of theorem \ref{thm:Kochen-Specker},
and represent $0$, $1$, $-1$, $\rmi$, $-\rmi$,$1+\rmi$, $1-\rmi$,
$-1+\rmi$, and $-1-\rmi$ by $0$, $1$, $\bar{1}$, $\rmi$, $\bar{\rmi}$,
$\alpha$, $\beta$, $\bar{\beta}$, and $\bar{\alpha}$, respectively,
and write in a three character string.

When $\ket{\Phi}$ is one of $\bar{\alpha}\bar{\alpha}0$, $\bar{\alpha}\bar{\rmi}\rmi$,
$\bar{\alpha}0\bar{\alpha}$, $\bar{\alpha}0\bar{\beta}$, $\bar{\alpha}\rmi\bar{1}$,
$\bar{\alpha}\rmi\bar{\rmi}$, $\bar{\alpha}\rmi1$, $\bar{\alpha}\beta0$,
$\bar{\alpha}1\bar{\rmi}$, $\bar{\alpha}1\rmi$, $1\alpha\rmi$,
$1\alpha\bar{\rmi}$, $11\beta$, $11\bar{\beta}$, $1\beta1$, $1\rmi\alpha$,
$1\rmi\beta$, $1\rmi\bar{\beta}$, $1\rmi\bar{\alpha}$, $1\bar{\rmi}\bar{\beta}$,
$1\bar{\rmi}\bar{\alpha}$, $1\bar{\beta}1$, $1\bar{\beta}\rmi$,
$1\bar{\beta}\bar{1}$, $1\bar{1}\bar{\beta}$, $1\bar{1}\bar{\alpha}$,
$1\bar{\alpha}\bar{\rmi}$, $1\bar{\alpha}\bar{1}$, $0\bar{\alpha}\bar{\beta}$,
$0\bar{\alpha}\beta$, $010$, and $001$, we have $\pi_{2}\left(\ket{\Phi}\right)=0$;
when $\ket{\Phi}$ is one of $\bar{\alpha}\bar{1}\bar{1}$, $\bar{\alpha}\bar{1}\bar{\rmi}$,
$\bar{\alpha}\bar{1}\rmi$, $\bar{\alpha}\bar{\beta}0$, $\bar{\alpha}\bar{\rmi}\bar{1}$,
$\bar{\alpha}\bar{\rmi}\bar{\rmi}$, $\bar{\alpha}\bar{\rmi}1$, $\bar{\alpha}0\beta$,
$\bar{\alpha}0\alpha$, $\bar{\alpha}\rmi\rmi$, $\bar{\alpha}1\bar{1}$,
$\bar{\alpha}11$, $\bar{\alpha}\alpha0$, $1\alpha1$, $1\alpha\bar{1}$,
$11\bar{\alpha}$, $1\beta\rmi$, $1\beta\bar{1}$, $100$, $1\bar{\rmi}\alpha$,
$1\bar{\rmi}\beta$, $1\bar{\beta}\bar{\rmi}$, $1\bar{1}\alpha$,
$1\bar{1}\beta$, $1\bar{\alpha}\rmi$, and $0\bar{\alpha}\bar{\ensuremath{\alpha}}$,
we have $\pi_{2}\left(\ket{\Phi}\right)=\frac{1}{2}$; when $\ket{\Phi}$
is one of $\bar{\alpha}\bar{1}1$, $11\alpha$, $1\beta\bar{\rmi}$,
$1\bar{\alpha}1$, and $0\bar{\alpha}\alpha$, we have $\pi_{2}\left(\ket{\Phi}\right)=1$.\end{example}
\begin{thm}
\label{thm:NotGleasonDQT-group}For $d\ge3$ except $p=d=3$, there
is no $\left[0,1\right]$-valued basis-independent Born rule $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\left(\ffzd{p^{2}}\rightarrow\left[0,1\right]\right)$
for pure states.\end{thm}
\begin{proof}
\footnote{The following proof assume $p\ge7$, and there is a simpler proof
for $d\ge4$ applying to $p=3$ case.} Assume such a map $\tilde{\pi}$ satisfying all properties exists.
Consider the orthonormal basis and the non-normalized state 
\begin{eqnarray}
\ket{0} & = & \left(\begin{array}{c}
1\\
0\\
0
\end{array}\right),\ket{1}=\left(\begin{array}{c}
0\\
1\\
0
\end{array}\right),\ket{2}=\left(\begin{array}{c}
0\\
0\\
1
\end{array}\right)\\
\ket{+} & = & \ket{0}+\ket{1}+\ket{2}\textrm{ ,}
\end{eqnarray}
where $\ket{+}$ is not zero-normed when $p\ge7$. For $\rmi=1,2$,
let $\mathbf{U}_{i}$ be the unitary map that permutes the basis vectors
$\ket{0}$ and $\ket{i}$ and acts as the identity for the rest. Note
that $\ket{+}$ is invariant under $\mathbf{U}_{i}$. So by property
(\ref{eq:basis-independent}), we have $\tilde{\pi}_{\ket{+}}\big(\ket{i}\big)=\tilde{\pi}_{\mathbf{U}_{i}\ket{+}}\big(\mathbf{U}_{i}\ket{0}\big)=\tilde{\pi}_{\ket{+}}\big(\ket{0}\big)$
for $i=1,2$. By property (\ref{eq:total-probability-CQT}), $\tilde{\pi}_{\ket{+}}\big(\ket{0}\big)+\tilde{\pi}_{\ket{+}}\big(\ket{1}\big)+\tilde{\pi}_{\ket{+}}\big(\ket{2}\big)=1$
so 
\begin{equation}
\tilde{\pi}_{\ket{+}}\big(\ket{i}\big)=\frac{1}{3}\textrm{ .}\label{prob2-1-1}
\end{equation}

Let 
\begin{eqnarray}
\mathbf{U}' & = & \left(\begin{array}{ccc}
\alpha & \alpha & 0\\
-\alpha & \alpha & 0\\
0 & 0 & 1
\end{array}\right)\\
\ket{\Phi} & = & 2\alpha\ket{0}+\ket{2}=\mathbf{U}'\ket{+}
\end{eqnarray}
where $\alpha\in\ff{p^{2}}$ is chosen so that $2\alpha^{*}\alpha=1$.
Thus by property (\ref{eq:basis-independent}), we have $\tilde{\pi}_{\Phi}\big(\ket{2}\big)=\tilde{\pi}_{\mathbf{U}'\ket{+}}\big(\mathbf{U}'\ket{2}\big)=\tilde{\pi}_{\ket{+}}\big(\ket{2}\big)$.
Also, properties (\ref{eq:total-probability-CQT}) and (\ref{eq:zero})
imply $1=\tilde{\pi}_{\Phi}\big(\ket{0}\big)+\tilde{\pi}_{\Phi}\big(\ket{2}\big)$.
This along with equation (\ref{prob2-1-1}) gives 
\begin{equation}
\tilde{\pi}_{\Phi}\big(\ket{0}\big)=\frac{2}{3}\textrm{ .}\label{eq:prob23}
\end{equation}

Finally, consider 
\begin{eqnarray}
\mathbf{U}'' & = & \left(\begin{array}{ccc}
1 & 0 & 0\\
0 & \beta^{*} & 2\alpha\\
0 & 2\alpha^{*} & \beta
\end{array}\right)\\
\ket{\Psi} & = & 2\alpha\left(\ket{0}+\ket{1}\right)+\beta\ket{2}=\mathbf{U}''\ket{\Phi}\textrm{ ,}
\end{eqnarray}
where $\beta\in\ff{p^{2}}$ is chosen so that $\beta^{*}\beta=-1$.
Because $\ket{\Psi}$ is invariant under $\mathbf{U}_{1}$, invoking
property (\ref{eq:basis-independent}) with equation (\ref{eq:prob23}),
we have 
\begin{equation}
\tilde{\pi}_{\Psi}\big(\ket{1}\big)=\tilde{\pi}_{\mathbf{U}_{1}\ket{\Psi}}\big(\mathbf{U}_{1}\ket{1}\big)=\tilde{\pi}_{\Psi}\big(\ket{0}\big)=\tilde{\pi}_{\mathbf{U}''\ket{\Phi}}\big(\mathbf{U}''\ket{0}\big)=\tilde{\pi}_{\Phi}\big(\ket{0}\big)=\frac{2}{3}\textrm{ .}
\end{equation}
These probability assignments are inconsistent with the requirement
that the probabilities for orthogonal outcomes add up to $1$. By
property (\ref{eq:total-probability-CQT}), 
\begin{equation}
1=\tilde{\pi}_{\Psi}\big(\ket{0}\big)+\tilde{\pi}_{\Psi}\big(\ket{1}\big)+\tilde{\pi}_{\Psi}\big(\ket{2}\big)=\frac{2}{3}+\frac{2}{3}+\tilde{\pi}_{\Psi}\big(\ket{2}\big)>\frac{4}{3}
\end{equation}
The assumption of a satisfactory map $\tilde{\pi}$ is thus false.
$\QED$\end{proof}
\begin{thm}
\label{thm:NotGleason}$\hat{\pi}_{1}$ is an interval-valued probability,
but $\bar{\pi}_{\rho}\ne\hat{\pi}_{1}$ for any mixed state $\rho$.\end{thm}
\begin{proof}
To be an interval-valued probability, $\hat{\pi}_{1}$ needs to satisfy
equation (\ref{eq:total-probability-CQT}) and (\ref{eq:parallel-CQT}).
Equation (\ref{eq:parallel-CQT}) is trivial. For equation (\ref{eq:total-probability-CQT}),
we want to prove that for any orthonormal basis $\left\{ \ket{i'}\right\} _{i=0}^{d-1}$,
\begin{equation}
\left(0,1\right]={\displaystyle \sum_{i=0}^{d-1}\hat{\pi}_{1}\left(\ket{i'}\right)}\textrm{ .}\label{eq:total-probability-hatcalpi1}
\end{equation}

\begin{casenv}
\item If $\ket{\Phi_{0}}$ does not parallel to any vector in $\left\{ \ket{i'}\right\} _{i=0}^{d-1}$,
then 
\begin{equation}
\left(0,1\right]={\displaystyle \sum_{i=0}^{d-1}\bar{\pi}_{\ket{0}}\left(\ket{i'}\right)}\overset{\left(\ref{eq:hatpi1}\right)}{=}{\displaystyle \sum_{i=0}^{d-1}\hat{\pi}_{1}\left(\ket{i'}\right)}\textrm{ .}
\end{equation}

\item If $\ket{\Phi_{0}}$ parallels to a vector in $\left\{ \ket{i'}\right\} _{i=0}^{d-1}$,
WLOG, let $\ket{0'}=\lambda_{0}\ket{\Phi_{0}}$. We want to prove
by contradiction. Assume ${\displaystyle \sum_{i=0}^{d-1}\hat{\pi}_{1}\left(\ket{i'}\right)}=\left\{ 0\right\} $.
Let $\ket{0}^{\bot}=\left\{ \ket{\Phi}\in\ffd{p^{2}}\middle|\ip{\Phi}{0}=0\right\} $
which is a $d-1$ dimensional linear subspace. By the definition of
$\hat{\pi}_{1}$, $\left\{ \ket{i'}\right\} _{i=1}^{d-1}\subset\ket{0}^{\bot}$.
Moreover, $\left\{ \ket{i'}\right\} _{i=1}^{d-1}$ is a orthonormal
set with $d-1$ elements. Hence, $\left\{ \ket{i'}\right\} _{i=1}^{d-1}$
is a orthonormal basis of the linear subspace $\ket{0}^{\bot}$. Therefore,
$\ket{\Phi_{0}}$ parallel to $\ket{0'}$ parallel to $\ket{0}$.
A contradiction!
\end{casenv}
By following the exactly the same proof in theorem \ref{thm:NotGleason-1},
we can prove $\bar{\pi}_{\rho}\ne\hat{\pi}_{1}$ for any mixed state
$\rho$. $\QED$
\end{proof}

\end{document}

### 2016-04-07 prob.tex
From: Sabry, Amr A. Sent: Thursday, April 07, 2016 6:16 To: Tai, Yu-Tsung <yuttai@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu> Subject: Re: This Wednesday
Here is the source. Can you please change the quantum sample space,
quantum events, and quantum probability to be consistent with Mermin’s
example of the three detectors.

\documentclass{article}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{amsthm}

\theoremstyle{remark}
\newtheorem{example}{Example}

\begin{document}
\title{Probability}
\author{}
\date{\today}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Classical Conventional Probability Spaces}

Textbook probability theory is defined using the notions of
\emph{sample spaces}, \emph{events}, and \emph{measures}.

%%%%%
\subsection{Sample Space $\Omega$}

In this paper, we will only consider \textbf{finite} sample spaces. We
therefore define a sample space $\Omega$ as a non-empty finite set.

\begin{example}[A Classical Sample Space.]
Consider an experiment that tosses three coins. A possible outcome of
the experiment is $HHT$ which means that the fist and second coins
landed with ``heads'' as the face-up side and that the third coin
landed with ``tails'' as the face-up side. There are clearly a total
of eight possible outcomes, and this collection constitutes the sample
space:
\[
\Omega_C = \{ HHH, HHT, HTH, HTT, THH, THT, TTH, TTT \}
\]
\end{example}

\begin{example}[A Quantum Sample Space.]
Consider a quantum system composed of three electrons. By the
postulates of quantum mechanics, an experiment designed to measure
whether the spin of each electron along the $x$ axis is left ($L$) or
right ($R$) can only result in one of eight outcomes:
\[
\Omega_H = \{ LLL, LLR, LRL, LRR, RLL, RLR, RRL, RRR \}
\]
\end{example}

%%%%%
\subsection{Events $\mathcal{F}$}

The space of events $\mathcal{F}$ associated with a sample space
$\Omega$ is $2^\Omega$, the power set of $\Omega$. In other words,
every subset of $\Omega$ is a possible event.

\begin{example}[Some classical events.] 
The following are events associated with $\Omega_C$:
\begin{itemize}
\item $E_0$, exactly zero coins are $H$, is the set $\{ TTT \}$.
\item $E_1$, exactly one coin is $H$, is the set $\{ HTT, THT, TTH \}$. 
\item $E_2$, exactly two coins are $H$, is the set $\{ HHT, HTH, THH \}$.
\item $E_3$, exactly three coins are $H$, is the set $\{ HHH \}$. 
\item $E_{>0}$, at least one coin is $H$, is the set $\{ HHH, HHT, HTH, HTT, THH, THT, TTH \}$. 
\end{itemize}
As the examples illustrate, events are \emph{indirect} questions. Also
note that some events may be disjoint and that some events may be
expressed as combinations of other events. For example, we have
$E_{>0} = E_1 \cup E_2 \cup E_3$ and each of these four events is
disjoint from event $E_0$.
\end{example}

\begin{example}[Some quantum events.] 
The following are events associated with $\Omega_H$:
\begin{itemize}
\item $F_0$, exactly zero electrons are spinning $L$, is the set $\{ RRR \}$.
\item $F_1$, exactly one electron is spinning $L$, is the set $\{ LRR, RLR, RRL \}$. 
\item $F_2$, exactly two electrons are spinning $L$, is the set $\{ LLR, LRL, RLL \}$.
\item $F_3$, exactly three electrons are spinning $L$, is the set $\{ LLL \}$. 
\item $F_{>0}$, at least one electron is spinning $L$, is the set $\{ LLL, LLR, LRL, LRR, RLL, RLR, RRL \}$. 
\end{itemize}
As the examples illustrate, quantum events are, at first glance,
similar to classical events. There are however some subtle
differences that we point out in the next section.
\end{example}

%%%%%
\subsection{Measures $\mathbb{P}$}

The last ingredient of a probability space is a probability measure
$\mathbb{P} : \mathcal{F} \rightarrow [0,1]$ that assigns to each
event a real number in the closed interval $[0,1]$ subject to the
following conditions:
\begin{itemize}
\item $\mathbb{P}(\Omega) = 1$, and 
\item For any collection of pairwise disjoint events $A_i$, we have 
$\mathbb{P}(\bigcup_i A_i) = \Sigma_i ~\mathbb{P}(A_i)$.
\end{itemize}

\begin{example}[Classical probability measure]
There are $2^8$ events associated with $\Omega_C$. A possible probability measure for
these events is:
\[\begin{array}{c}
\mathbb{P}(E) = \left\{ \begin{array}{ll} 
  1 & \mbox{if}~E = \Omega \\
  0 & \mbox{otherwise} 
  \end{array}\right.
\end{array}\]
A more interesting measure is defined recursively as follows:
\renewcommand\arraystretch{1.4}
\[\begin{array}{rcl}
\mathbb{P}(\emptyset) &=& 0 \\
\mathbb{P}(\{ HHH \} \cup E) &=& \frac{1}{5} + \mathbb{P}(E) \\
\mathbb{P}(\{ HHT \} \cup E) &=& \mathbb{P}(E) \\
\mathbb{P}(\{ HTH \} \cup E) &=& \frac{3}{10} + \mathbb{P}(E) \\
\mathbb{P}(\{ HTT \} \cup E) &=& \mathbb{P}(E) \\
\mathbb{P}(\{ THH \} \cup E) &=& \frac{1}{5} + \mathbb{P}(E) \\
\mathbb{P}(\{ THT \} \cup E) &=& \mathbb{P}(E) \\
\mathbb{P}(\{ TTH \} \cup E) &=& \frac{3}{10} + \mathbb{P}(E) \\
\mathbb{P}(\{ TTT \} \cup E) &=& \mathbb{P}(E) 
\end{array}\]
Because this is a \emph{classical} situation, the probability
assignments can be understood \emph{locally} and
\emph{non-contextually}. In other words, we can reason about each coin
separately and perform experiments on it ignoring the rest of the
context. If we were to perform such experiments we may find that for
the first coin with sample space, the probability of either outcome
$H$ or $T$ is $\frac{1}/{2}$; for coin two, the probabilities are
skewed a little with the probability of outcome $H$ being
$\frac{2}{5}$ and the probability of outcome $T$ being $\frac{3}{5}$;
coin 3 is a fake double-headed coin and hence the probability of
outcome $H$ is 1 and the probability of outcome $T$ is 0. The reader
may check that these local observations are consistent with the
probability measure above. 
\end{example}

\begin{example}[Quantum probability measure]
Like in the classical case, there are $2^8$ events. But as Mermin
explains in a simple example (Quantum Mysteries Revisited), here is a
possible probability measure: 
\[\begin{array}{rcl}
\mathbb{P}(S) &=& \left.\{ \begin{array}{ll}
  1/8 & \mbox{if there is an odd number of $L$} \\
  \ldots
  \end{array}\right.
\end{array}\]
Interestingly and paradoxically, it is \emph{not} possible to analyze
each electron independently and assign a consistent probability to
each one locally and non-contextually. 
\end{example}

%%%%
\subsection{Finite Precision of Measurements}

In a laboratory setting or a computational setting, there are neither
uncountable entities nor uncomputable entities. We are thus looking at
alternative probability spaces which do not depend on the real numbers
and revisit the mysteries of quantum mechanics in that
setting. Following previous work on probability, we will replace the
closed interval $[0,1]$ by the \emph{finite set} $S = \{
\textbf{possible}, \textbf{impossible}$ and adapt the definition of
probability measure as follows:

A set-valued probability mesure $\mathbb{P} : \mathcal{F} \rightarrow
S$ assigns to each event either the tag \textbf{possible} or the tag
\textbf{impossible} subject to the following conditions:
\begin{itemize}
\item $\mathbb{P}(\Omega) = \textbf{possible}$, and 
\item For any collection of pairwise disjoint events $A_i$, we have 
$\mathbb{P}(\bigcup_i A_i) = \textbf{possible}$ if any event $A_i$ is
\textbf{possible} and \textbf{impossible} otherwise. 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

Probability space (restricted to finite sample spaces)

* Sample space Ω (arbitrary finite non-empty set)
* Set of events F: pick 2^Ω
* Probability measure (real-valued): P : F → [0,1] such that:
  * For any collection of pairwise disjoint Aᵢ ∈ F, we have P ( ∪ᵢ Aᵢ) = ∑ᵢ P(Aᵢ) 
  * P(Ω) = 1

Set-value probability measures. Change the last bullet to:
* P : F → 2^(ℝⁿ) such that: ...

### 2016-04-08 prob.tex

@@
 \newtheorem{example}{Example}
+\newcommand{\pmeas}{\ensuremath{\mathbb{P}}}
 
@@
 The space of events $\mathcal{F}$ associated with a sample space
-$\Omega$ is $2^\Omega$, the power set of $\Omega$. In other words,
+$\Omega$ is $2^\Omega$, the powerset of $\Omega$. In other words,
 every subset of $\Omega$ is a possible event.
@@
 \end{itemize}
-As the examples illustrate, events are \emph{indirect} questions. Also
+As the examples illustrate, events are \emph{indirect} questions built from elementary elements of the sample space using logical connectives. Also
 note that some events may be disjoint and that some events may be
@@
 context. If we were to perform such experiments we may find that for
-the first coin with sample space, the probability of either outcome
-$H$ or $T$ is $\frac{1}/{2}$; for coin two, the probabilities are
+the first coin, the probability of either outcome
+$H$ or $T$ is $\frac{1}{2}$; for coin two, the probabilities are
 skewed a little with the probability of outcome $H$ being
-$\frac{2}{5}$ and the probability of outcome $T$ being $\frac{3}{5}$;
-coin 3 is a fake double-headed coin and hence the probability of
+$\frac{2}{5}$ and the probability of outcome $T$ being $\frac{3}{5}$; and that
+coin 3 is a fake double-headed coin where the probability of
 outcome $H$ is 1 and the probability of outcome $T$ is 0. The reader
@@
 and revisit the mysteries of quantum mechanics in that
-setting. Following previous work on probability, we will replace the
+setting. In other words, is it possible that at least part of the quantum mysteries related to probability and measurement are due to the reliance on uncomputable probability values?
+
+Following previous work on probability, we will replace the
 closed interval $[0,1]$ by the \emph{finite set} $S = \{
-\textbf{possible}, \textbf{impossible}$ and adapt the definition of
-probability measure as follows:
+\textbf{possible}, \textbf{impossible} \}$ and adapt the definition of
+probability measure as follows.
 
-A set-valued probability mesure $\mathbb{P} : \mathcal{F} \rightarrow
+A set-valued probability measure $\mathbb{P} : \mathcal{F} \rightarrow
 S$ assigns to each event either the tag \textbf{possible} or the tag
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conventional Quantum Mechanics}
+
+Attempting to modify the probability measure to be set-valued, while keeping the rest of the mathematical framework of quantum mechanics intact leads to a contradiction.
+More precisely, it is not possible to maintain
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2016-04-08 prob.tex

@@
 Attempting to modify the probability measure to be set-valued, while keeping the rest of the mathematical framework of quantum mechanics intact leads to a contradiction.
-More precisely, it is not possible to maintain
+More precisely, it is not possible to maintain infinite precision probability amplitudes in the presence of set-valued probabilities without violating essential aspects of quantum theory.
+
+\ldots explain and give theorem
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discrete Quantum Theory}
+
+The next question to ask is therefore whether the infinite precision of probability amplitudes is itself justified.
+If all measurements are finite and all probabilities are computable, then it is plausible that the internal mathematical representation of quantum states should also be based on countable computable entities.
+
+\ldots
 

### 2016-04-08 prob.tex
Start adding comments...

@@
 \newcommand{\pmeas}{\ensuremath{\mathbb{P}}}
+
+\usepackage{color}
+\usepackage[usenames,dvipsnames]{xcolor}
+\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
 
@@
 \end{array}\]
+\yutsung{ Actually, the above $\mathbb{P}$ is not a probability
+because 
+\[
+\mathbb{P}\left(\Omega\right)=1\ne0+0=\mathbb{P}\left(\left\{ HHH\right\} \right)+\mathbb{P}\left(\Omega\backslash\left\{ HHH\right\} \right)
+\]
+} \\
 A more interesting measure is defined recursively as follows:
@@
 \end{array}\]
+\yutsung{It seems more clear to write like this: 
+\[
+\begin{array}{rcl}
+\mathbb{P}(\{HHH\}) & = & \frac{1}{5}\\
+\mathbb{P}(\{HHT\}) & = & 0\\
+\mathbb{P}(\{HTH\}) & = & \frac{3}{10}\\
+\mathbb{P}(\{HTT\}) & = & 0\\
+\mathbb{P}(\{THH\}) & = & \frac{1}{5}\\
+\mathbb{P}(\{THT\}) & = & 0\\
+\mathbb{P}(\{TTH\}) & = & \frac{3}{10}\\
+\mathbb{P}(\{TTT\}) & = & 0\\
+\mathbb{P}(E) & = & \sum_{\omega\in E}\mathbb{P}(\left\{ \omega\right\} )
+\end{array}
+\]
+} \\
 Because this is a \emph{classical} situation, the probability

### 2016-04-08 prob.tex
prob.tex "Example 6. [Quantum probability measure]" update, but bibtex cannot work in TeXclipse so far...

@@
 
-\begin{example}[Quantum probability measure]
-Like in the classical case, there are $2^8$ events. But as Mermin
-explains in a simple example (Quantum Mysteries Revisited), here is a
-possible probability measure: 
-\[\begin{array}{rcl}
-\mathbb{P}(S) &=& \left.\{ \begin{array}{ll}
-  1/8 & \mbox{if there is an odd number of $L$} \\
-  \ldots
-  \end{array}\right.
-\end{array}\]
+\begin{example}{[}Quantum probability measure{]} Like in the classical
+case, there are $2^{8}$ events. But as Mermin explains in a simple
+example~\cite{MerminPRL1990}, here is a possible probability measure:
+\[
+\begin{array}{rcl}
+\mathbb{P}(\{LLL\}) & = & \frac{1}{4}\\
+\mathbb{P}(\{LLR\}) & = & 0\\
+\mathbb{P}(\{LRL\}) & = & 0\\
+\mathbb{P}(\{LRR\}) & = & \frac{1}{4}\\
+\mathbb{P}(\{RLL\}) & = & 0\\
+\mathbb{P}(\{RLR\}) & = & \frac{1}{4}\\
+\mathbb{P}(\{RRL\}) & = & \frac{1}{4}\\
+\mathbb{P}(\{RRR\}) & = & 0\\
+\mathbb{P}(E) & = & \sum_{\omega\in E}\mathbb{P}(\left\{ \omega\right\} )
+\end{array}
+\]
+In contrast with the classical example previously, the probability
+of each electron is not independent~\cite{GrahamKnuthPatashnik1994,inun.425605319950101,rohatgi2011introduction},
+i.e., we cannot find three probability space for each subsystem such
+that 
+\[
+\mathbb{P}(\{abc\})=\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
+\]
+Correlated variables are also common in the classical world. For example,
+if the first coin is head or tail decided by whether the temperature
+is higher than a particular degree and the second coin is decided
+by whether Coca Cola is sold more than a particular amount, then we
+know these two coins are correlated. Einstein, Podolsky, and Rosen~\cite{EPR1935}
+suggested any correlated quantum probability results may be interpreted
+classically. For example, maybe the natural actually rolls an tetrahedron
+die with $\{LLL,LRR,RLR,RRL\}$ in its four faces, and this tetrahedron
+die could not be accessed by human for some reasons so that we think
+we are handling three electrons.
+
+The interesting part is that three electrons cannot be measured the
+spin only along the $x$ axis, but also along the $y$ axis with the
+result down ($D$) or up ($U$).
+
 Interestingly and paradoxically, it is \emph{not} possible to analyze
@@
 * P : F → 2^(ℝⁿ) such that: ...
+
+\bibliographystyle{plain}
+\bibliography{discreteGBKS}

### 2016-04-09 prob.tex
prob.tex Fix a bug about the location of BibTeX...
prob.tex "Example 6. [Quantum probability measure]" update

@@
 \begin{array}{rcl}
-\mathbb{P}(\{LLL\}) & = & \frac{1}{4}\\
-\mathbb{P}(\{LLR\}) & = & 0\\
-\mathbb{P}(\{LRL\}) & = & 0\\
-\mathbb{P}(\{LRR\}) & = & \frac{1}{4}\\
-\mathbb{P}(\{RLL\}) & = & 0\\
-\mathbb{P}(\{RLR\}) & = & \frac{1}{4}\\
-\mathbb{P}(\{RRL\}) & = & \frac{1}{4}\\
-\mathbb{P}(\{RRR\}) & = & 0\\
-\mathbb{P}(E) & = & \sum_{\omega\in E}\mathbb{P}(\left\{ \omega\right\} )
+\mathbb{P}_{xxx}(\{LLL\}) & = & \frac{1}{4}\\
+\mathbb{P}_{xxx}(\{LLR\}) & = & 0\\
+\mathbb{P}_{xxx}(\{LRL\}) & = & 0\\
+\mathbb{P}_{xxx}(\{LRR\}) & = & \frac{1}{4}\\
+\mathbb{P}_{xxx}(\{RLL\}) & = & 0\\
+\mathbb{P}_{xxx}(\{RLR\}) & = & \frac{1}{4}\\
+\mathbb{P}_{xxx}(\{RRL\}) & = & \frac{1}{4}\\
+\mathbb{P}_{xxx}(\{RRR\}) & = & 0\\
+\mathbb{P}_{xxx}(E) & = & \sum_{\omega\in E}\mathbb{P}_{xxx}(\left\{ \omega\right\} )
 \end{array}
@@
 \[
-\mathbb{P}(\{abc\})=\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
+\mathbb{P}_{xxx}(\{abc\})=\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
 \]
@@
 by whether Coca Cola is sold more than a particular amount, then we
-know these two coins are correlated. Einstein, Podolsky, and Rosen~\cite{EPR1935}
-suggested any correlated quantum probability results may be interpreted
-classically. For example, maybe the natural actually rolls an tetrahedron
-die with $\{LLL,LRR,RLR,RRL\}$ in its four faces, and this tetrahedron
-die could not be accessed by human for some reasons so that we think
-we are handling three electrons.
+know these two coins are correlated. Einstein, Podolsky, and Rosen
+(EPR)~\cite{EPR1935} suggested any correlated quantum probability
+results may be interpreted classically. For example, maybe the nature
+actually rolls an tetrahedron die with $\{LLL,LRR,RLR,RRL\}$ in its
+four faces, and this tetrahedron die could not be accessed by human
+for some reasons so that we think we are handling three electrons.
+
+In order to verify EPR's idea, we need to analysis the idea of probability
+more carefully. Imagining somebody tosses a coin behind a veil, we
+heard the coin is tossed, but cannot see the result. Although the
+probability for us is still $\mathbb{P}(\{H\})=\mathbb{P}(\{T\})=\frac{1}{2}$,
+we know the coin behind the veil must be either head or tail face-up.
+
+In classical probability, there is no difference between the coins
+have not been tossed or the coins have been tossed but we do not know.
+However, there is a difference when we consider the quantum probability.
+Because the three electrons can be specially separated, and each electron
+can be measured along the $x$ axis separately, if the nature actually
+rolled the tetrahedron die, this die should be rolled before the electrons
+are separated and measured. In another word, there should be a period
+that the human observer would not know the measurement results for
+each electron along the $x$ axis, but the nature should know. The
+result for $j$-th electron is denoted by $w\left(\sigma_{x}^{j}\right)$
+so that $w\left(\sigma_{x}^{1}\right)w\left(\sigma_{x}^{2}\right)w\left(\sigma_{x}^{3}\right)\in\{LLL,LRR,RLR,RRL\}$,
+i.e., the number of $L$ in $w\left(\sigma_{x}^{1}\right)$, $w\left(\sigma_{x}^{2}\right)$,
+and $w\left(\sigma_{x}^{3}\right)$ must be odd.
 
@@
 spin only along the $x$ axis, but also along the $y$ axis with the
-result down ($D$) or up ($U$).
+result down ($D$) or up ($U$). We only consider to measure even
+number of electrons along the $y$ axis, and the measure of non-singleton
+set should be computed by $\mathbb{P}_{ijk}(E)=\sum_{\omega\in E}\mathbb{P}_{ijk}(\left\{ \omega\right\} )$.
+\begin{eqnarray*}
+\begin{array}{rcl}
+\mathbb{P}_{xyy}(\{LDD\}) & = & 0\\
+\mathbb{P}_{xyy}(\{LDU\}) & = & \frac{1}{4}\\
+\mathbb{P}_{xyy}(\{LUD\}) & = & \frac{1}{4}\\
+\mathbb{P}_{xyy}(\{LUU\}) & = & 0\\
+\mathbb{P}_{xyy}(\{RDD\}) & = & \frac{1}{4}\\
+\mathbb{P}_{xyy}(\{RDU\}) & = & 0\\
+\mathbb{P}_{xyy}(\{RUD\}) & = & 0\\
+\mathbb{P}_{xyy}(\{RUU\}) & = & \frac{1}{4}
+\end{array} & \begin{array}{rcl}
+\mathbb{P}_{yxy}(\{DLD\}) & = & 0\\
+\mathbb{P}_{yxy}(\{DLU\}) & = & \frac{1}{4}\\
+\mathbb{P}_{yxy}(\{DRD\}) & = & \frac{1}{4}\\
+\mathbb{P}_{yxy}(\{DRU\}) & = & 0\\
+\mathbb{P}_{yxy}(\{ULD\}) & = & \frac{1}{4}\\
+\mathbb{P}_{yxy}(\{ULU\}) & = & 0\\
+\mathbb{P}_{yxy}(\{URD\}) & = & 0\\
+\mathbb{P}_{yxy}(\{URU\}) & = & \frac{1}{4}
+\end{array} & \begin{array}{rcl}
+\mathbb{P}_{yyx}(\{DDL\}) & = & 0\\
+\mathbb{P}_{yyx}(\{DDR\}) & = & \frac{1}{4}\\
+\mathbb{P}_{yyx}(\{DUL\}) & = & \frac{1}{4}\\
+\mathbb{P}_{yyx}(\{DUR\}) & = & 0\\
+\mathbb{P}_{yyx}(\{UDL\}) & = & \frac{1}{4}\\
+\mathbb{P}_{yyx}(\{UDR\}) & = & 0\\
+\mathbb{P}_{yyx}(\{UUL\}) & = & 0\\
+\mathbb{P}_{yyx}(\{UUR\}) & = & \frac{1}{4}
+\end{array}
+\end{eqnarray*}
+Similarly, there would be predetermined $w\left(\sigma_{x}^{j}\right)$
+and $w\left(\sigma_{y}^{j}\right)$ for these probabilities. Notice
+that the nature should predetermine the same values of $w\left(\sigma_{x}^{j}\right)$
+and $w\left(\sigma_{y}^{j}\right)$ no matter we measure along $x$
+axes or $y$ axes because the nature does not know which axes we are
+going to measure.
 
@@
 
+\bibliographystyle{plain}
+\bibliography{discreteGBKS}
+
 \end{document}
@@
 * P : F → 2^(ℝⁿ) such that: ...
-
-\bibliographystyle{plain}
-\bibliography{discreteGBKS}

### 2016-04-09 prob.tex
prob.tex "Example 6. [Quantum probability measure]" update...

@@
 Consider an experiment that tosses three coins. A possible outcome of
-the experiment is $HHT$ which means that the fist and second coins
+the experiment is $HHT$ which means that the first and second coins
 landed with ``heads'' as the face-up side and that the third coin
@@
 \end{array}\]
-\yutsung{It seems more clear to write like this: 
+\yutsung{Should write like
+\[
+\begin{array}{rcl}
+\mathbb{P}(\emptyset) & = & 0\\
+\mathbb{P}(\{HHH\}\cup E) & = & \frac{1}{5}+\mathbb{P}(E)\textrm{, if }HHH\notin E\\
+\mathbb{P}(\{HHT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }HHT\notin E\\
+\mathbb{P}(\{HTH\}\cup E) & = & \frac{3}{10}+\mathbb{P}(E)\textrm{, if }HTH\notin E\\
+\mathbb{P}(\{HTT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }HTT\notin E\\
+\mathbb{P}(\{THH\}\cup E) & = & \frac{1}{5}+\mathbb{P}(E)\textrm{, if }THH\notin E\\
+\mathbb{P}(\{THT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }THT\notin E\\
+\mathbb{P}(\{TTH\}\cup E) & = & \frac{3}{10}+\mathbb{P}(E)\textrm{, if }TTH\notin E\\
+\mathbb{P}(\{TTT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }TTT\notin E
+\end{array}
+\]
+However, many if clauses seems confusing, and it seems easier to write
+like this: 
 \[
@@
 i.e., the number of $L$ in $w\left(\sigma_{x}^{1}\right)$, $w\left(\sigma_{x}^{2}\right)$,
-and $w\left(\sigma_{x}^{3}\right)$ must be odd.
+and $w\left(\sigma_{x}^{3}\right)$ should be odd.
 
@@
 Similarly, there would be predetermined $w\left(\sigma_{x}^{j}\right)$
-and $w\left(\sigma_{y}^{j}\right)$ for these probabilities. Notice
-that the nature should predetermine the same values of $w\left(\sigma_{x}^{j}\right)$
-and $w\left(\sigma_{y}^{j}\right)$ no matter we measure along $x$
-axes or $y$ axes because the nature does not know which axes we are
-going to measure.
-
-Interestingly and paradoxically, it is \emph{not} possible to analyze
-each electron independently and assign a consistent probability to
-each one locally and non-contextually. 
-\end{example}
+and $w\left(\sigma_{y}^{j}\right)$ for these probabilities. The number
+of $L$ or $D$ in $\left\{ w\left(\sigma_{x}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
+$\left\{ w\left(\sigma_{y}^{1}\right),w\left(\sigma_{x}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
+and $\left\{ w\left(\sigma_{y}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{x}^{3}\right)\right\} $
+should be even. If we look these 9 letters carefully, we can find
+every $w\left(\sigma_{x}^{j}\right)$ appear once and every $w\left(\sigma_{y}^{j}\right)$
+appear twice. Hence, the number of $L$ in $w\left(\sigma_{x}^{1}\right)$,
+$w\left(\sigma_{x}^{2}\right)$, and $w\left(\sigma_{x}^{3}\right)$
+should be even. This contradict to the conclusion in our last paragraph.
+Therefore, EPR's assumption is wrong and the correlation of quantum
+probability cannot be interpreted by a classical probability. \end{example}
 

### 2016-04-09 prob.tex
prob.tex Modify a little bit...

@@
 Textbook probability theory is defined using the notions of
-\emph{sample spaces}, \emph{events}, and \emph{measures}.
+\emph{sample spaces}, \emph{events}, and
+\emph{measures}~\cite{GrahamKnuthPatashnik1994,inun.425605319950101,rohatgi2011introduction}.
 
@@
 \yutsung{ Actually, the above $\mathbb{P}$ is not a probability
-because 
+measure because 
 \[
-\mathbb{P}\left(\Omega\right)=1\ne0+0=\mathbb{P}\left(\left\{ HHH\right\} \right)+\mathbb{P}\left(\Omega\backslash\left\{ HHH\right\} \right)
+\mathbb{P}\left(\Omega\right)=1\ne0+0=\mathbb{P}\left(E_{0}\right)+\mathbb{P}\left(E_{>0}\right)
 \]
@@
 In contrast with the classical example previously, the probability
-of each electron is not independent~\cite{GrahamKnuthPatashnik1994,inun.425605319950101,rohatgi2011introduction},
-i.e., we cannot find three probability space for each subsystem such
-that 
+of each electron is not independent, i.e., we cannot find three probability
+space for each subsystem such that 
 \[
@@
 (EPR)~\cite{EPR1935} suggested any correlated quantum probability
-results may be interpreted classically. For example, maybe the nature
-actually rolls an tetrahedron die with $\{LLL,LRR,RLR,RRL\}$ in its
-four faces, and this tetrahedron die could not be accessed by human
-for some reasons so that we think we are handling three electrons.
+results may be interpreted classically. For example, the nature might
+roll an tetrahedron die with $\{LLL,LRR,RLR,RRL\}$ in its four faces.
+If $LRR$ were face-down, the measurement result for three electrons
+would be $L$, $R$, and $R$, respectively. Furthermore, this tetrahedron
+die might not be accessed by human for some reasons so that we think
+we are handling a system constituting three electrons.
 

### 2016-04-09 prob.tex
Copy Programs/DQC3.nb from 201408-12.M800\DQC3.nb @ revision 3876

@@
 \end{array}\]
-\yutsung{Should write like
+\yutsung{Because $\mathbb{P}(\bigcup_{i}A_{i})=\Sigma_{i}~\mathbb{P}(A_{i})$
+requires disjoint events, the above formula should write like:
 \[
@@
 \]
-However, many if clauses seems confusing, and it seems easier to write
-like this: 
+Or add a sentence ``where the element in the singleton set is not
+belong to $E$ for each equation.'' We may also write like this:
 \[

### 2016-04-10 prob.tex
prob.tex "Example 6. [Quantum probability measure]" update...

@@
 In contrast with the classical example previously, the probability
-of each electron is not independent, i.e., we cannot find three probability
-space for each subsystem such that 
+measure of the space cannot be expressed as the product of the probability
+measure of each electron, i.e., 
 \[
-\mathbb{P}_{xxx}(\{abc\})=\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
+\mathbb{P}_{xxx}(\{abc\})\ne\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
 \]

### 2016-04-11 prob.tex
prob.tex [Quantum probability measure] updated....

@@
 \]
-In contrast with the classical example previously, the probability
-measure of the space cannot be expressed as the product of the probability
-measure of each electron, i.e., 
+In contrast with the classical example previously, the event of different
+electrons are not independent or correlated. More precisely, consider
+the event for each electron separately:
+\begin{eqnarray*}
+F_{1,L} & = & \left\{ LLL,LLR,LRL,LRR\right\} \\
+F_{2,L} & = & \left\{ LLL,LLR,RLL,RLR\right\} \\
+F_{3,L} & = & \left\{ LLL,LRL,RLL,RRL\right\} 
+\end{eqnarray*}
+They are correlated means 
 \[
-\mathbb{P}_{xxx}(\{abc\})\ne\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
+\mathbb{P}_{xxx}(F_{1,L}\cap F_{2,L}\cap F_{3,L})=\mathbb{P}_{xxx}(\{LLL\})=\frac{1}{4}\ne\frac{1}{8}=\mathbb{P}_{xxx}(F_{1,L})\mathbb{P}_{xxx}(F_{2,L})\mathbb{P}_{xxx}(F_{3,L})\textrm{ .}
 \]
-Correlated variables are also common in the classical world. For example,
-if the first coin is head or tail decided by whether the temperature
-is higher than a particular degree and the second coin is decided
-by whether Coca Cola is sold more than a particular amount, then we
-know these two coins are correlated. Einstein, Podolsky, and Rosen
-(EPR)~\cite{EPR1935} suggested any correlated quantum probability
-results may be interpreted classically. For example, the nature might
-roll an tetrahedron die with $\{LLL,LRR,RLR,RRL\}$ in its four faces.
-If $LRR$ were face-down, the measurement result for three electrons
-would be $L$, $R$, and $R$, respectively. Furthermore, this tetrahedron
-die might not be accessed by human for some reasons so that we think
-we are handling a system constituting three electrons.
 
-In order to verify EPR's idea, we need to analysis the idea of probability
-more carefully. Imagining somebody tosses a coin behind a veil, we
-heard the coin is tossed, but cannot see the result. Although the
-probability for us is still $\mathbb{P}(\{H\})=\mathbb{P}(\{T\})=\frac{1}{2}$,
-we know the coin behind the veil must be either head or tail face-up.
+Classical events may also be correlated even they come from different
+sources. A typical example is events defined by the temperature is
+highly likely correlated to the event related to how Coca Cola is
+sold. Another example are the same events we discussed in coin-tossing.
+However, this time the coins are tossed behind a veil, and somebody
+tosses the three coins for you. Because she tosses the coins behind
+a veil, she might actually roll an tetrahedron die with $\{HHH,HTT,THT,TTH\}$
+in its four faces. If $HTT$ were face-down, she places three coins
+with $H$, $T$, and $T$ face-up, respectively. Then, she uncovers
+the veil, and claims she has tossed the coins. Then, the result of
+coin-tossing is correlated, and we will never see $TTT$ if the coins
+are tossed in this way.
 
-In classical probability, there is no difference between the coins
-have not been tossed or the coins have been tossed but we do not know.
-However, there is a difference when we consider the quantum probability.
+Because we do not know how nature decides the spin of an electron,
+Einstein, Podolsky, and Rosen (EPR)~\cite{EPR1935} suggested the
+nature might give us the probability measure~$\mathbb{P}_{xxx}$
+because she rolled an tetrahedron die or performed other classical
+and deterministic process behind the veil. This claim is convincing
+if $\mathbb{P}_{xxx}$ is the only probability measure we have, but
+will lead to a contradiction if we consider other probability measures
+all together. Notice that after the coins are placed before uncovering
+the veil, which face of a coin is up is decided although we do not
+know. This would be also true for the quantum probability measure.
 Because the three electrons can be specially separated, and each electron
-can be measured along the $x$ axis separately, if the nature actually
-rolled the tetrahedron die, this die should be rolled before the electrons
-are separated and measured. In another word, there should be a period
-that the human observer would not know the measurement results for
-each electron along the $x$ axis, but the nature should know. The
-result for $j$-th electron is denoted by $w\left(\sigma_{x}^{j}\right)$
-so that $w\left(\sigma_{x}^{1}\right)w\left(\sigma_{x}^{2}\right)w\left(\sigma_{x}^{3}\right)\in\{LLL,LRR,RLR,RRL\}$,
+can be measured along the $x$ axis separately, if the nature rolled
+the tetrahedron die, this die should be rolled before the electrons
+are separated and measured, and she should know the result of measurement.
+Let the result of the $j$-th electron measured along the $x$ axis
+be $w\left(\sigma_{x}^{j}\right)$ so that $w\left(\sigma_{x}^{1}\right)w\left(\sigma_{x}^{2}\right)w\left(\sigma_{x}^{3}\right)\in\{LLL,LRR,RLR,RRL\}$,
 i.e., the number of $L$ in $w\left(\sigma_{x}^{1}\right)$, $w\left(\sigma_{x}^{2}\right)$,
@@
 result down ($D$) or up ($U$). We only consider to measure even
-number of electrons along the $y$ axis, and the measure of non-singleton
-set should be computed by $\mathbb{P}_{ijk}(E)=\sum_{\omega\in E}\mathbb{P}_{ijk}(\left\{ \omega\right\} )$.
+number of electrons along the $y$ axis, and the probability measure
+of non-singleton set should be computed by $\mathbb{P}_{ijk}(E)=\sum_{\omega\in E}\mathbb{P}_{ijk}(\left\{ \omega\right\} )$.
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-Similarly, there would be predetermined $w\left(\sigma_{x}^{j}\right)$
-and $w\left(\sigma_{y}^{j}\right)$ for these probabilities. The number
-of $L$ or $D$ in $\left\{ w\left(\sigma_{x}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
+Similarly, the nature should predetermine $w\left(\sigma_{x}^{j}\right)$
+and $w\left(\sigma_{y}^{j}\right)$ for these probabilities. Furthermore,
+because she do not know along which axis we are going to measure,
+she should predetermine the same $w\left(\sigma_{x}^{j}\right)$ and
+$w\left(\sigma_{y}^{j}\right)$ for all different probabilities. Notice
+that the number of $L$ or $D$ in $\left\{ w\left(\sigma_{x}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
 $\left\{ w\left(\sigma_{y}^{1}\right),w\left(\sigma_{x}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
@@
 should be even. This contradict to the conclusion in our last paragraph.
-Therefore, EPR's assumption is wrong and the correlation of quantum
-probability cannot be interpreted by a classical probability. \end{example}
+Therefore, EPR's assumption is wrong, and it is not always true that
+the nature can predetermine the measurement result before we perform
+the measurement. \end{example}
 

### 2016-04-11 prob.tex
prob.lyx "1.3 Measures \mathbb{P}" Updated...

@@
 Or add a sentence ``where the element in the singleton set is not
-belong to $E$ for each equation.'' We may also write like this:
+belong to $E$ for each equation.'' Or write like: 
 \[
@@
 In contrast with the classical example previously, the event of different
-electrons are not independent or correlated. More precisely, consider
-the event for each electron separately:
+electrons are not independent. More precisely, consider the event
+for each electron separately:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-They are correlated means 
+They are not independent means 
 \[
@@
 
-Classical events may also be correlated even they come from different
-sources. A typical example is events defined by the temperature is
-highly likely correlated to the event related to how Coca Cola is
-sold. Another example are the same events we discussed in coin-tossing.
-However, this time the coins are tossed behind a veil, and somebody
-tosses the three coins for you. Because she tosses the coins behind
-a veil, she might actually roll an tetrahedron die with $\{HHH,HTT,THT,TTH\}$
-in its four faces. If $HTT$ were face-down, she places three coins
-with $H$, $T$, and $T$ face-up, respectively. Then, she uncovers
-the veil, and claims she has tossed the coins. Then, the result of
-coin-tossing is correlated, and we will never see $TTT$ if the coins
-are tossed in this way.
+Classical events may also not be independent even if they seems unrelated.
+For example, events defined by the temperature is usually not independent
+to ones defined by how much Coca Cola is sold. Another example can
+be formulated by tossing three coins as we discussed previously. However,
+this time the coins are tossed behind a veil where someone tosses
+the coins for you. Because we cannot see how she tosses the coins,
+she might actually roll an tetrahedron die with $\{HHH,HTT,THT,TTH\}$
+in its four faces. If $HTT$ is face-down, she faces $H$, $T$, and
+$T$ up by hand, respectively. Then, she uncovers the veil, and claims
+she has tossed the coins. If the coins are tossed in this way, the
+result of coin-tossing is correlated, and we will never see $TTT$
+no matter how many times we toss these coins.
 
@@
 because she rolled an tetrahedron die or performed other classical
-and deterministic process behind the veil. This claim is convincing
+and deterministic process behind the veil. This claim may be convincing
 if $\mathbb{P}_{xxx}$ is the only probability measure we have, but
 will lead to a contradiction if we consider other probability measures
-all together. Notice that after the coins are placed before uncovering
-the veil, which face of a coin is up is decided although we do not
-know. This would be also true for the quantum probability measure.
-Because the three electrons can be specially separated, and each electron
-can be measured along the $x$ axis separately, if the nature rolled
-the tetrahedron die, this die should be rolled before the electrons
-are separated and measured, and she should know the result of measurement.
-Let the result of the $j$-th electron measured along the $x$ axis
-be $w\left(\sigma_{x}^{j}\right)$ so that $w\left(\sigma_{x}^{1}\right)w\left(\sigma_{x}^{2}\right)w\left(\sigma_{x}^{3}\right)\in\{LLL,LRR,RLR,RRL\}$,
+as well. Notice that after the coins are placed by hand and before
+uncovering the veil, which side up has already been decided although
+we do not know. This would be also true for the quantum probability
+measure. Because the three electrons can be spacially separated, and
+each electron can be measured along the $x$ axis separately, if the
+nature rolled a tetrahedron die, this die should be rolled before
+the electrons are separated and measured, and she should know the
+result of measurement. Let the result of the $j$-th electron measured
+along the $x$ axis be $w\left(\sigma_{x}^{j}\right)$. Because 
+\[
+\mathbb{P}_{xxx}(\{LLR\})=\mathbb{P}_{xxx}(\{LRL\})=\mathbb{P}_{xxx}(\{RLL\})=\mathbb{P}_{xxx}(\{RRR\})=0\textrm{ ,}
+\]
+we have $w\left(\sigma_{x}^{1}\right)w\left(\sigma_{x}^{2}\right)w\left(\sigma_{x}^{3}\right)\in\{LLL,LRR,RLR,RRL\}$,
 i.e., the number of $L$ in $w\left(\sigma_{x}^{1}\right)$, $w\left(\sigma_{x}^{2}\right)$,
@@
 number of electrons along the $y$ axis, and the probability measure
-of non-singleton set should be computed by $\mathbb{P}_{ijk}(E)=\sum_{\omega\in E}\mathbb{P}_{ijk}(\left\{ \omega\right\} )$.
+of non-singleton set could be defined by 
 \begin{eqnarray*}
@@
 \end{eqnarray*}
+with $\mathbb{P}_{ijk}(E)=\sum_{\omega\in E}\mathbb{P}_{ijk}(\left\{ \omega\right\} )$.
 Similarly, the nature should predetermine $w\left(\sigma_{x}^{j}\right)$
@@
 she should predetermine the same $w\left(\sigma_{x}^{j}\right)$ and
-$w\left(\sigma_{y}^{j}\right)$ for all different probabilities. Notice
-that the number of $L$ or $D$ in $\left\{ w\left(\sigma_{x}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
+$w\left(\sigma_{y}^{j}\right)$ for all different probability measures.
+Notice that the number of $L$ or $D$ in $\left\{ w\left(\sigma_{x}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
 $\left\{ w\left(\sigma_{y}^{1}\right),w\left(\sigma_{x}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,

### 2016-04-11 prob.tex
prob.tex "Example 6. [Quantum probability measure]" modifying words...

@@
 \]
-In contrast with the classical example previously, the event of different
+In contrast with the previous classical example, the event of different
 electrons are not independent. More precisely, consider the event
@@
 For example, events defined by the temperature is usually not independent
-to ones defined by how much Coca Cola is sold. Another example can
+to ones defined by how much Coca-Cola is sold. Another example can
 be formulated by tossing three coins as we discussed previously. However,
@@
 the coins for you. Because we cannot see how she tosses the coins,
-she might actually roll an tetrahedron die with $\{HHH,HTT,THT,TTH\}$
-in its four faces. If $HTT$ is face-down, she faces $H$, $T$, and
-$T$ up by hand, respectively. Then, she uncovers the veil, and claims
-she has tossed the coins. If the coins are tossed in this way, the
-result of coin-tossing is correlated, and we will never see $TTT$
-no matter how many times we toss these coins.
+she might actually roll a four-sided tetrahedral die with $\{HHH,HTT,THT,TTH\}$
+in its four faces. If $HTT$ is on the downward face, she places $H$,
+$T$, and $T$ as the face-up sides of of the three coins by hand,
+respectively. Then, she uncovers the veil, and claims she has tossed
+the coins. If the coins are tossed in this way, the result of coin-tossing
+is correlated, and we will never see $TTT$ no matter how many times
+we toss these coins.
 
-Because we do not know how nature decides the spin of an electron,
-Einstein, Podolsky, and Rosen (EPR)~\cite{EPR1935} suggested the
-nature might give us the probability measure~$\mathbb{P}_{xxx}$
-because she rolled an tetrahedron die or performed other classical
-and deterministic process behind the veil. This claim may be convincing
-if $\mathbb{P}_{xxx}$ is the only probability measure we have, but
-will lead to a contradiction if we consider other probability measures
-as well. Notice that after the coins are placed by hand and before
-uncovering the veil, which side up has already been decided although
-we do not know. This would be also true for the quantum probability
-measure. Because the three electrons can be spacially separated, and
-each electron can be measured along the $x$ axis separately, if the
-nature rolled a tetrahedron die, this die should be rolled before
-the electrons are separated and measured, and she should know the
-result of measurement. Let the result of the $j$-th electron measured
+Because we do not know how the spin of an electron is decided, Einstein,
+Podolsky, and Rosen (EPR)~\cite{EPR1935} suggested the nature might
+give us the probability measure~$\mathbb{P}_{xxx}$ because she rolled
+a tetrahedral die or performed other classical and deterministic process
+behind the veil. This claim may be convincing if $\mathbb{P}_{xxx}$
+is the only probability measure we have, but will lead to a contradiction
+if we consider other probability measures as well. Notice that after
+the coins are placed by hand and before uncovering the veil, which
+side up has already been decided although we do not know. This would
+be also true for the quantum probability measure. Because the three
+electrons can be spacially separated, and each electron can be measured
+along the $x$ axis separately, if the nature rolled a tetrahedral
+die, this die should be rolled before the electrons are separated
+and measured, and she should know the result of measurement before
+we measure the electrons. Let the result of the $j$-th electron measured
 along the $x$ axis be $w\left(\sigma_{x}^{j}\right)$. Because 
@@
 
-The interesting part is that three electrons cannot be measured the
-spin only along the $x$ axis, but also along the $y$ axis with the
-result down ($D$) or up ($U$). We only consider to measure even
-number of electrons along the $y$ axis, and the probability measure
-of non-singleton set could be defined by 
+The three electrons cannot be measured the spin only along the $x$
+axis, but also along the $y$ axis with the result down ($D$) or
+up ($U$). We only consider to measure even number of electrons along
+the $y$ axis, and the probability measures could be defined by 
 \begin{eqnarray*}
@@
 Similarly, the nature should predetermine $w\left(\sigma_{x}^{j}\right)$
-and $w\left(\sigma_{y}^{j}\right)$ for these probabilities. Furthermore,
-because she do not know along which axis we are going to measure,
-she should predetermine the same $w\left(\sigma_{x}^{j}\right)$ and
-$w\left(\sigma_{y}^{j}\right)$ for all different probability measures.
-Notice that the number of $L$ or $D$ in $\left\{ w\left(\sigma_{x}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
+and $w\left(\sigma_{y}^{j}\right)$ for them. Furthermore, because
+she do not know along which axis we are going to measure, she should
+predetermine the same $w\left(\sigma_{x}^{j}\right)$ and $w\left(\sigma_{y}^{j}\right)$
+for all different probability measures. By the same reason as above,
+the number of $L$ or $D$ in $\left\{ w\left(\sigma_{x}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
 $\left\{ w\left(\sigma_{y}^{1}\right),w\left(\sigma_{x}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
@@
 should be even. If we look these 9 letters carefully, we can find
-every $w\left(\sigma_{x}^{j}\right)$ appear once and every $w\left(\sigma_{y}^{j}\right)$
-appear twice. Hence, the number of $L$ in $w\left(\sigma_{x}^{1}\right)$,
-$w\left(\sigma_{x}^{2}\right)$, and $w\left(\sigma_{x}^{3}\right)$
-should be even. This contradict to the conclusion in our last paragraph.
-Therefore, EPR's assumption is wrong, and it is not always true that
-the nature can predetermine the measurement result before we perform
-the measurement. \end{example}
+that every $w\left(\sigma_{x}^{j}\right)$ appears once and every
+$w\left(\sigma_{y}^{j}\right)$ appears twice. Hence, the number of
+$L$ in $w\left(\sigma_{x}^{1}\right)$, $w\left(\sigma_{x}^{2}\right)$,
+and $w\left(\sigma_{x}^{3}\right)$ should be even. This contradict
+to the conclusion in our last paragraph. Therefore, EPR's assumption
+is wrong, and it is not always true that the nature can predetermine
+the measurement result before we perform the measurement. \end{example}
 

### 2016-04-13 prob.tex
prob

@@
 \usepackage{fullpage}
+\usepackage{bbm}
 \usepackage{amssymb}
 \usepackage{amsthm}
+\usepackage{multicol}
 
@@
 \newtheorem{example}{Example}
-\newcommand{\pmeas}{\ensuremath{\mathbb{P}}}
+\newcommand{\events}{\ensuremath{\mathcal{F}}}
+\newcommand{\qevents}{\ensuremath{\mathcal{A}}}
+\newcommand{\pmeas}{\ensuremath{\mu}}
+\newcommand{\Hilb}{\mathcal{H}}
+\newcommand{\pr}[2]{\langle #1, #2 \rangle}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Classical Conventional Probability Spaces}
+\section{Probability Spaces}
 
-Textbook probability theory is defined using the notions of
-\emph{sample spaces}, \emph{events}, and
-\emph{measures}~\cite{GrahamKnuthPatashnik1994,inun.425605319950101,rohatgi2011introduction}.
+%%%%%
+\subsection{Classical Probability Spaces}
+
+Textbook probability
+theory~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
+is defined using the notions of a \emph{sample space} $\Omega$, a
+space of \emph{events}~$\events$, and a \emph{probability
+  measure}~$\pmeas$. In this paper, we will only consider
+\emph{finite} sample spaces: we therefore define a sample space
+$\Omega$ as an arbitrary non-empty finite set and the space of events
+$\events$ as, $2^\Omega$, the powerset of $\Omega$. A \emph{probability
+measure} is a function $\pmeas : \events \rightarrow [0,1]$ such that:
+\begin{itemize}
+\item $\pmeas(\Omega) = 1$, and 
+\item for a collection of pairwise disjoint events $E_i$, we have
+  $\pmeas(\bigcup E_i) = \sum \pmeas(E_i)$. 
+\end{itemize}
+
+\begin{example}[Two coin experiment] Consider an experiment that
+  tosses two coins. We have four possible outcomes that constitute the
+  sample space $\Omega = \{ HH, HT, TH, TT \}$. The event that the
+  first coin is ``heads'' is $\{ HH, HT \}$; the event that the two
+  coins land on opposite sides is $\{ HT, TH \}$; the event that at
+  least one coin is tails is $\{ HT, TH, TT\}$. Depending on the
+  assumptions regarding the coins, we can define several probability
+  measures. Here is a possible one:
+\[\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) &=& 0 \\
+\pmeas(\{ HH \}) &=& 1/3 \\
+\pmeas(\{ HT \}) &=& 0 \\
+\pmeas(\{ TH \}) &=& 2/3 \\
+\pmeas(\{ TT \}) &=& 0 \\
+\pmeas(\{  HH, HT \}) &=& 1/3 \\
+\pmeas(\{  HH, TH \}) &=& 1 \\
+\pmeas(\{  HH , TT \}) &=& 1/3 
+\end{array} & \begin{array}{rcl}
+\pmeas(\{  HT, TH \}) &=& 2/3 \\
+\pmeas(\{  HT , TT \}) &=& 0 \\
+\pmeas(\{  TH , TT \}) &=& 2/3 \\
+\pmeas(\{  HH, HT, TH \}) &=& 1 \\
+\pmeas(\{  HH, HT, TT \}) &=& 1/3 \\
+\pmeas(\{  HH, TH, TT \}) &=& 1 \\
+\pmeas(\{  HT, TH, TT \}) &=& 2/3 \\
+\pmeas(\{  HH, HT, TH, TT \}) &=& 1
+\end{array}
+\end{array}\]
+\end{example}
+
+%%%%%
+\subsection{Quantum Probability Spaces}
+
+A classical model decides the occurrence or non-occurence of all
+events simultaneously which is inconsistent with quantum
+mechanics. Indeed, in the quantum world, there are (non-commuting)
+events which cannot happen simultaneously. To accommodate this
+situation, we completely abandon the sample space $\Omega$ and define
+and reason directly about events. Thus a quantum probability space
+will consist of just two components: a set of events $\qevents$ and a
+probability measure $\phi : \qevents \rightarrow [0,1]$. These
+components are defined as follows.
+
+We first assume an ambient Hilbert space $\Hilb$ and define the set of
+events $\qevents$ as \emph{projections} on $\Hilb$. Similarly to the
+classical case, a probability measure is a function
+$\phi : \qevents \rightarrow [0,1]$ satisfying:
+\begin{itemize}
+\item $\phi(\mathbbm{1}) = 1$, and
+\item for all $A \in \qevents$, we have $\phi(A^*A) \geq 0$.
+\end{itemize}
+
+As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
+projections on $\Hilb$ with sum $\mathbbm{1}$ and define the event
+space $\qevents$ to be the linear span of these operators:
+\[
+\qevents = \{ \sum_{j=1}^k \lambda_jP_j ~|~ \lambda_i, \ldots, \lambda_k \in \mathbb{C} \}. 
+\]
+Each state $\psi$ of the Hilbert space induces a probability measure
+$\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
+\[
+\phi_\psi(A) = \langle \psi ~|~ A\psi \rangle
+\]
+
+%%%%%
+\subsection{Plan}
+
+We see that a quantum probability space embeds several infinite
+precision assumptions, both in the Hilbert space itself and in the
+range of the probability measure. We will now study the consequences
+of restricting each occurrence of $\mathbb{R}$ or $\mathbb{C}$ to some
+finite structure.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliographystyle{plain}
+\bibliography{discreteGBKS}
+
+\end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Probability space (restricted to finite sample spaces)
+
+* Sample space Ω (arbitrary finite non-empty set)
+* Set of events F: pick 2^Ω
+* Probability measure (real-valued): P : F → [0,1] such that:
+  * For any collection of pairwise disjoint Aᵢ ∈ F, we have P ( ∪ᵢ Aᵢ) = ∑ᵢ P(Aᵢ) 
+  * P(Ω) = 1
+
+Set-value probability measures. Change the last bullet to:
+* P : F → 2^(ℝⁿ) such that: ...
 
@@
 
+We begin by reviewing the conventional presentation of classical
+probability spaces and then give an alternative formulation that is
+``quantum-like'' but still classical. We conclude this section with a
+definition of quantum probability spaces given as a modest
+generalization of the alternative classical definition.
+
+%%%%%
+\subsection{Conventional Classical Probability Spaces}
+
+Textbook probability
+theory~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
+is defined using the notions of a \emph{sample space} $\Omega$, a
+space of \emph{events}~$\events$, and a \emph{probability
+  measure}~$\pmeas$. In this paper, we will only consider
+\emph{finite} sample spaces: we therefore define a sample space
+$\Omega$ as an arbitrary non-empty finite set and the space of events
+$\events$ as, $2^\Omega$, the powerset of $\Omega$. A \emph{probability
+measure} is a function $\pmeas : \events \rightarrow [0,1]$ such that:
+\begin{itemize}
+\item $\pmeas(\Omega) = 1$, and 
+\item for a collection of pairwise disjoint events $E_i$, we have
+  $\pmeas(\bigcup E_i) = \sum \pmeas(E_i)$. 
+\end{itemize}
+
+\begin{example}[Two coin experiment] Consider an experiment that
+  tosses two coins. We have four possible outcomes that constitute the
+  sample space $\Omega = \{ HH, HT, TH, TT \}$. The event that the
+  first coin is ``heads'' is $\{ HH, HT \}$; the event that the two
+  coins land on opposite sides is $\{ HT, TH \}$; the event that at
+  least one coin is tails is $\{ HT, TH, TT\}$. Depending on the
+  assumptions regarding the coins, we can define several probability
+  measures. Here is a possible one:
+\[\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) &=& 0 \\
+\pmeas(\{ HH \}) &=& 1/3 \\
+\pmeas(\{ HT \}) &=& 0 \\
+\pmeas(\{ TH \}) &=& 2/3 \\
+\pmeas(\{ TT \}) &=& 0 \\
+\pmeas(\{  HH, HT \}) &=& 1/3 \\
+\pmeas(\{  HH, TH \}) &=& 1 \\
+\pmeas(\{  HH , TT \}) &=& 1/3 
+\end{array} & \begin{array}{rcl}
+\pmeas(\{  HT, TH \}) &=& 2/3 \\
+\pmeas(\{  HT , TT \}) &=& 0 \\
+\pmeas(\{  TH , TT \}) &=& 2/3 \\
+\pmeas(\{  HH, HT, TH \}) &=& 1 \\
+\pmeas(\{  HH, HT, TT \}) &=& 1/3 \\
+\pmeas(\{  HH, TH, TT \}) &=& 1 \\
+\pmeas(\{  HT, TH, TT \}) &=& 2/3 \\
+\pmeas(\{  HH, HT, TH, TT \}) &=& 1
+\end{array}
+\end{array}\]
+\end{example}
+
+%%%%%
+\subsection{Alternative Definition of Classical Probability Spaces}
+
+In the conventional presentation, we have viewed the space of events
+$2^\Omega$ are the powerset of $\Omega$. We can equivalently view
+$2^\Omega$ as the space of functions from $\Omega$ to the set
+$2 = \{0,1\}$. For example, the event $\{HT,TH\}$ is the function $e$
+such that:
+\[
+e (HH) = 0, \quad e (HT) = 1, \quad e (TH) = 1, \quad e (TT) = 0 
+\]
+We will in fact do a sweeping generalization and view events as
+functions from $\Omega$ to $\mathbb{C}$, the set of complex
+numbers. This accommodates the previous events such as $e$ and allows
+many more events such as event $e'$ below:
+\[
+e' (HH) = \sqrt{2} + i \sqrt{3}, \quad e' (HT) = 1, \quad e' (TH) = \pi, \quad e' (TT) = 0 
+\]
+The events are not going to be completely arbitrary functions,
+however. We will insist on some conditions:...
+
+This generalization
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 If all measurements are finite and all probabilities are computable, then it is plausible that the internal mathematical representation of quantum states should also be based on countable computable entities.
-
-\ldots
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{plain}
-\bibliography{discreteGBKS}
-
-\end{document}
-
-Probability space (restricted to finite sample spaces)
-
-* Sample space Ω (arbitrary finite non-empty set)
-* Set of events F: pick 2^Ω
-* Probability measure (real-valued): P : F → [0,1] such that:
-  * For any collection of pairwise disjoint Aᵢ ∈ F, we have P ( ∪ᵢ Aᵢ) = ∑ᵢ P(Aᵢ) 
-  * P(Ω) = 1
-
-Set-value probability measures. Change the last bullet to:
-* P : F → 2^(ℝⁿ) such that: ...

### 2016-04-14 prob.tex
[4] JM Swart. Introduction to quantum probability. Lecture Notes, 2013.

@@
 \]
+\yutsung{If we want to follow Swart~\cite{Swart2013}... Maybe we
+should define the set of projection and the }\\
 Each state $\psi$ of the Hilbert space induces a probability measure

### 2016-04-14 prob.tex
outline of example

--- 2016-04-13 prob.tex
@@
 \newcommand{\pr}[2]{\langle #1, #2 \rangle}
+\newcommand{\ket}[1]{|#1\rangle}
+\newcommand{\bra}[1]{\langle#1|}
+\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
+\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
 
@@
 \]
-Each state $\psi$ of the Hilbert space induces a probability measure
-$\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
+Each state $\ket{\psi}$ of the Hilbert space induces a probability
+measure $\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
 \[
-\phi_\psi(A) = \langle \psi ~|~ A\psi \rangle
+\phi_\psi(A) = \ip{\psi}{A\ket{\psi}}
 \]
+
+Concrete example: consider the two qubit Hilbert space with
+computational bases $\ket{0}$ and $\ket{1}$ and consider
+the following families of projections:
+\begin{itemize}
+\item Family I: $\proj{0}$, $\proj{1}$
+\item Family II: $\proj{+}$, $\proj{-}$
+\end{itemize}
+and consider the two states \ldots
 

### 2016-04-15 prob.tex
plan outline

@@
 \[
-\phi_\psi(A) = \ip{\psi}{A\ket{\psi}}
+\phi_\psi(A) = \ip{\psi}{A\psi}
 \]
+
+%% If we want to follow Swart~\cite{Swart2013} 
+%% I am following sec 4 of https://www.math.ru.nl/~maassen/lectures/Trieste.pdf
 
@@
 
-We see that a quantum probability space embeds several infinite
-precision assumptions, both in the Hilbert space itself and in the
-range of the probability measure. We will now study the consequences
-of restricting each occurrence of $\mathbb{R}$ or $\mathbb{C}$ to some
-finite structure.
+Several assumptions are woven in the definition of a quantum probability space:
+\begin{itemize}
+\item the Hilbert space $\Hilb$;
+\item the real interval $[0,1]$; 
+\item the fact that each state induces a probability measure, i.e., the Born rule;
+\item the fact that every probability measure is induced by a state,
+  i.e., Gleason's theorem
+\end{itemize}
+
+In the remainder of the paper, we examine each of these assumptions
+and consider variations motivated by computation in a world with
+limited resources. In particular, we will consider a variant of the
+Hilbert space over finite fields; we will consider set-valued
+probability measures; we will consider ways other than the Born rule
+in which a state can induce a probability measure, and we will consider
+probability measures that may come from information beyond the quantum
+states.
 
@@
 be also true for the quantum probability measure. Because the three
-electrons can be spacially separated, and each electron can be measured
+electrons can be spatially separated, and each electron can be measured
 along the $x$ axis separately, if the nature rolled a tetrahedral

### 2016-04-18 prob.tex
Start adding comments...

@@
 probability measure $\phi : \qevents \rightarrow [0,1]$. These
-components are defined as follows.
+components are defined as follows~\cite{Maassen2010,Swart2013}.
 
@@
 \end{itemize}
-
+\yutsung{If we follow \cite{Maassen2010,Swart2013}, then we also
+need 
+\begin{itemize}
+\item $\phi$ can be extended to a linear functional~$\phi:alg\left(\qevents\right)\rightarrow\mathbb{C}$,
+where $alg\left(\qevents\right)$ is the minimal $*$-algebra generated
+by $\qevents$.
+\end{itemize}
+}\\
 As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
@@
 \]
+\yutsung{$\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{i},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
+is the minimal $*$-algebra generated by $P_{1},P_{2},\ldots,P_{k}$,
+but it contains all possible observables $P_{1},P_{2},\ldots,P_{k}$
+can generate (and something more) not just projections. For example,
+$2\mathbbm{1}\in\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{i},\ldots,\lambda_{k}\in\mathbb{C}\right\} $.}\\
 Each state $\ket{\psi}$ of the Hilbert space induces a probability
@@
 \]
-
-%% If we want to follow Swart~\cite{Swart2013} 
-%% I am following sec 4 of https://www.math.ru.nl/~maassen/lectures/Trieste.pdf
+\yutsung{So $\phi_{\psi}$ maps the projections generated by $P_{1},P_{2},\ldots,P_{k}$
+to $[0,1]$, and maps $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{i},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
+to $\mathbb{C}$...}\\
 

### 2016-04-18 prob.tex
I don't know why ShareLaTeX believed I modified a PDF file in it... Hope this time git merge works...

--- 2016-04-15 prob.tex
@@
 \end{itemize}
-
+\yutsung{If we follow \cite{Maassen2010,Swart2013}, then we also
+need 
+\begin{itemize}
+\item $\phi$ can be extended to a linear functional~$\phi:alg\left(\qevents\right)\rightarrow\mathbb{C}$,
+where $alg\left(\qevents\right)$ is the minimal $*$-algebra generated
+by $\qevents$.
+\end{itemize}
+Also, 
+\begin{itemize}
+\item for all $A\in\qevents$, we have $\phi(A^{*}A)\geq0$. 
+\end{itemize}
+should be 
+\begin{itemize}
+\item for all $A\in alg\left(\qevents\right)$, we have $\phi(A^{*}A)\geq0$. 
+\end{itemize}
+because we have $\phi(A^{*}A)=\phi(A^{2})=\phi(A)$ if $A$ is a projection.}\\
 As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
@@
 \[
-\qevents = \{ \sum_{j=1}^k \lambda_jP_j ~|~ \lambda_i, \ldots, \lambda_k \in \mathbb{C} \}. 
+\qevents=\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} .
 \]
+\yutsung{$\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
+is the minimal $*$-algebra generated by $P_{1},P_{2},\ldots,P_{k}$,
+but it contains all possible observables $P_{1},P_{2},\ldots,P_{k}$
+can generate (and something more) not just projections. For example,
+$2\mathbbm{1}\in\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $.}\\
 Each state $\ket{\psi}$ of the Hilbert space induces a probability
@@
 \]
+\yutsung{So $\phi_{\psi}$ maps the projections generated by $P_{1},P_{2},\ldots,P_{k}$
+to $[0,1]$, and maps $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
+to $\mathbb{C}$...}\\
 
-%% If we want to follow Swart~\cite{Swart2013} 
-%% I am following sec 4 of https://www.math.ru.nl/~maassen/lectures/Trieste.pdf
-
-Concrete example: consider the two qubit Hilbert space with
-computational bases $\ket{0}$ and $\ket{1}$ and consider
-the following families of projections:
+Concrete example: consider the two qubit Hilbert space with computational
+bases $\ket{0}$ and $\ket{1}$. First, consider the two states 
+\[
+\ket{+}=\frac{\ket{0}+\ket{1}}{\sqrt{2}},\ket{-}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}
+\]
+and consider the following families of projections: 
 \begin{itemize}
@@
 \end{itemize}
-and consider the two states \ldots
+In family I, all operators can be expressed as $\left\{ \lambda_{1}\proj{0}+\lambda_{2}\proj{1}~\middle|~\lambda_{1},\lambda_{2}\in\mathbb{C}\right\} $.
+In order to identify projectors among them, we need to solve the following
+two equations.
+\begin{eqnarray*}
+\lambda_{1}\proj{0}+\lambda_{2}\proj{1} & = & \left(\lambda_{1}\proj{0}+\lambda_{2}\proj{1}\right)^{*}=\lambda_{1}^{*}\proj{0}+\lambda_{2}^{*}\proj{1}\\
+\lambda_{1}\proj{0}+\lambda_{2}\proj{1} & = & \left(\lambda_{1}\proj{0}+\lambda_{2}\proj{1}\right)^{2}=\lambda_{1}^{2}\proj{0}+\lambda_{2}^{2}\proj{1}
+\end{eqnarray*}
+Therefore, we actually have $\lambda_{1},\lambda_{2}\in\left\{ 0,1\right\} $,
+and there are only four projections: $0$, $\proj{0}$, $\proj{1}$,
+and $\mathbbm{1}=\proj{0}+\proj{1}$. Then, $\phi_{\ket{+}}$ and
+$\phi_{\ket{-}}$ of each projections are 
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\phi_{\ket{+}}(0) & = & 0\\
+\phi_{\ket{+}}(\proj{0}) & = & 1/2\\
+\phi_{\ket{+}}(\proj{1}) & = & 1/2\\
+\phi_{\ket{+}}(\mathbbm{1}) & = & 1
+\end{array} & \begin{array}{rcl}
+\phi_{\ket{-}}(0) & = & 0\\
+\phi_{\ket{-}}(\proj{0}) & = & 1/2\\
+\phi_{\ket{-}}(\proj{1}) & = & 1/2\\
+\phi_{\ket{-}}(\mathbbm{1}) & = & 1
+\end{array}\end{array}
+\]
+Similarly, $\phi_{\ket{+}}$ and $\phi_{\ket{-}}$ gives two probability
+for family II as well.
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\phi_{\ket{+}}(0) & = & 0\\
+\phi_{\ket{+}}(\proj{+}) & = & 1\\
+\phi_{\ket{+}}(\proj{-}) & = & 0\\
+\phi_{\ket{+}}(\mathbbm{1}) & = & 1
+\end{array} & \begin{array}{rcl}
+\phi_{\ket{-}}(0) & = & 0\\
+\phi_{\ket{-}}(\proj{+}) & = & 0\\
+\phi_{\ket{-}}(\proj{-}) & = & 1\\
+\phi_{\ket{-}}(\mathbbm{1}) & = & 1
+\end{array}\end{array}
+\]
 

### 2016-04-18 prob.tex
restructure quantum prob

--- 2016-04-15 prob.tex
@@
 \usepackage{bbm}
+\usepackage{bbold}
 \usepackage{amssymb}
@@
 \newtheorem{example}{Example}
-\newcommand{\events}{\ensuremath{\mathcal{F}}}
+\newcommand{\events}{\ensuremath{\mathcal{A}}}
 \newcommand{\qevents}{\ensuremath{\mathcal{A}}}
@@
 \newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
+\newcommand{\ps}{\texttt{+}}
+\newcommand{\ms}{\texttt{-}}
 
@@
 
-A classical model decides the occurrence or non-occurence of all
-events simultaneously which is inconsistent with quantum
-mechanics. Indeed, in the quantum world, there are (non-commuting)
-events which cannot happen simultaneously. To accommodate this
-situation, we completely abandon the sample space $\Omega$ and define
-and reason directly about events. Thus a quantum probability space
-will consist of just two components: a set of events $\qevents$ and a
-probability measure $\phi : \qevents \rightarrow [0,1]$. These
-components are defined as follows.
+The mathematical framework above assumes that one has complete
+knowledge of the events and their relationships. But even in many
+classical situations, the structure of the event space is only
+partially known and the precise dependence of two events on each other
+cannot be determined with certainty. In the quantum case, this partial
+knowledge is compounded by the fact that not all quantum events can be
+observed simultaneously.  Indeed, in the quantum world, there are
+non-commuting events which cannot even happen simultaneously. To
+accommodate these more complex situations, we completely abandon the
+sample space~$\Omega$ and define and reason directly about
+events. Thus a quantum probability space will consist of just two
+components: a set of events $\qevents$ and a probability measure
+$\mu : \qevents \rightarrow [0,1]$. We give an example before giving
+the formal definition.
 
-We first assume an ambient Hilbert space $\Hilb$ and define the set of
-events $\qevents$ as \emph{projections} on $\Hilb$. Similarly to the
-classical case, a probability measure is a function
-$\phi : \qevents \rightarrow [0,1]$ satisfying:
+Consider the two-qubit Hilbert space with computational basis
+$\ket{0}$ and $\ket{1}$ and states:
+\[
+\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}, \qquad\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.
+\]
+A possible space of events is the set
+$\{ \mathbb{0}, \proj{0}, \proj{1}, \mathbb{1}\}$ consisting of the
+projection operators $\proj{0}$ and $\proj{1}$ as well as the empty
+projection $\mathbb{0}$ and the unit projection
+$\mathbb{1} = \proj{0}+\proj{1}$. Each event is interpreted as a
+possible post-measurement of a quantum system as follows: given some
+arbitrary current quantum $\ket{\psi}$ to be measured, the event
+$\proj{0}$ states that the post-measurement state will be $\ket{0}$;
+the event $\proj{1}$ states that the post-measurement state will be
+$\ket{1}$; the event $\mathbb{1}$ states that the post-measurement
+state will be a linear combination of $\ket{0}$ and $\ket{1}$; and the
+event $\mathbb{0}$ states that the post-measurement state will be the
+empty state. Clearly irrespective of the current state $\ket{\psi}$
+and irrespective of the particular experiment, the probability of
+event $\mathbb{0}$ will always be 0 (it is an impossible event) and
+the probability of event $\mathbb{1}$ will always be 1 (it is a
+certain event). The probabilities attached to other events will depend
+on the particular state in question. If the state is $\ket{0}$, the
+probability of event $\proj{0}$ is 1 and the probability of event
+$\proj{1}$ is 0. If the state is $\ket{\ps}$, the probability of both
+events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$. The same
+Hilbert space setup admits other possible spaces of events. For
+example, another space of events could be
+$\{ \mathbb{0}, \proj{\ps}, \proj{\ms}, \mathbb{1}\}$. Using that
+space of events, the state $\ket{0}$ maps both events $\proj{\ps}$ and
+$\proj{\ms}$ to the probability $\frac{1}{2}$.
+
+% \begin{itemize}
+% \item Family I: $\proj{0}$, $\proj{1}$ 
+% \item Family II: $\proj{\ps}$, $\proj{\ms}$
+% \end{itemize}
+% In family I, all operators can be expressed as $\left\{ \lambda_{1}\proj{0}+\lambda_{2}\proj{1}~\middle|~\lambda_{1},\lambda_{2}\in\mathbb{C}\right\} $.
+% In order to identify projectors among them, we need to solve the following
+% two equations.
+% \begin{eqnarray*}
+% \lambda_{1}\proj{0}+\lambda_{2}\proj{1} & = & \left(\lambda_{1}\proj{0}+\lambda_{2}\proj{1}\right)^{*}=\lambda_{1}^{*}\proj{0}+\lambda_{2}^{*}\proj{1}\\
+% \lambda_{1}\proj{0}+\lambda_{2}\proj{1} & = & \left(\lambda_{1}\proj{0}+\lambda_{2}\proj{1}\right)^{2}=\lambda_{1}^{2}\proj{0}+\lambda_{2}^{2}\proj{1}
+% \end{eqnarray*}
+% Therefore, we actually have $\lambda_{1},\lambda_{2}\in\left\{ 0,1\right\} $,
+% and there are only four projections: $0$, $\proj{0}$, $\proj{1}$,
+% and $\mathbb{1}=\proj{0}+\proj{1}$. Then, $\mu_{\ket{\ps}}$ and
+% $\mu_{\ket{\ms}}$ of each projections are 
+% \[
+% \begin{array}{c@{\qquad\qquad}c}
+% \begin{array}{rcl}
+% \mu_{\ket{\ps}}(0) & = & 0\\
+% \mu_{\ket{\ps}}(\proj{0}) & = & 1/2\\
+% \mu_{\ket{\ps}}(\proj{1}) & = & 1/2\\
+% \mu_{\ket{\ps}}(\mathbb{1}) & = & 1
+% \end{array} & \begin{array}{rcl}
+% \mu_{\ket{\ms}}(0) & = & 0\\
+% \mu_{\ket{\ms}}(\proj{0}) & = & 1/2\\
+% \mu_{\ket{\ms}}(\proj{1}) & = & 1/2\\
+% \mu_{\ket{\ms}}(\mathbb{1}) & = & 1
+% \end{array}\end{array}
+% \]
+% Similarly, $\mu_{\ket{\ps}}$ and $\mu_{\ket{\ms}}$ gives two probability
+% for family II as well.
+% \[
+% \begin{array}{c@{\qquad\qquad}c}
+% \begin{array}{rcl}
+% \mu_{\ket{\ps}}(0) & = & 0\\
+% \mu_{\ket{\ps}}(\proj{+}) & = & 1\\
+% \mu_{\ket{\ps}}(\proj{\ms}) & = & 0\\
+% \mu_{\ket{\ps}}(\mathbb{1}) & = & 1
+% \end{array} & \begin{array}{rcl}
+% \mu_{\ket{\ms}}(0) & = & 0\\
+% \mu_{\ket{\ms}}(\proj{\ps}) & = & 0\\
+% \mu_{\ket{\ms}}(\proj{\ms}) & = & 1\\
+% \mu_{\ket{\ms}}(\mathbb{1}) & = & 1
+% \end{array}\end{array}
+% \]
+
+We now formalize a \emph{quantum probability space} as
+follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
+Hilbert space $\Hilb$ and define the set of events $\qevents$ as all
+linear combinations of \emph{projections} on $\Hilb$. Specifically,
+let $P_1, P_2, \ldots, P_k$ be mutually orthogonal projections on
+$\Hilb$ with sum $\mathbb{1}$ and define the event space $\qevents$ to
+be the linear span of these operators:
+\[
+\qevents=\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} .
+\]
+Each quantum state $\ket{\psi}$ induces a probability measure
+$\mu_\psi : \qevents \rightarrow [0,1]$ on the space of events
+defined as follows:
+\[
+\mu_\psi(A) = \ip{\psi}{A\psi}
+\]
+Similarlly to the classical case, this probability measure satisfies:
 \begin{itemize}
-\item $\phi(\mathbbm{1}) = 1$, and
-\item for all $A \in \qevents$, we have $\phi(A^*A) \geq 0$.
+\item $\mu(\mathbb{1}) = 1$, and
+\item for all $A \in \qevents$, we have $\mu(A^*A) \geq 0$.
 \end{itemize}
 
-As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
-projections on $\Hilb$ with sum $\mathbbm{1}$ and define the event
-space $\qevents$ to be the linear span of these operators:
-\[
-\qevents = \{ \sum_{j=1}^k \lambda_jP_j ~|~ \lambda_i, \ldots, \lambda_k \in \mathbb{C} \}. 
-\]
-Each state $\ket{\psi}$ of the Hilbert space induces a probability
-measure $\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
-\[
-\phi_\psi(A) = \ip{\psi}{A\psi}
-\]
+% \yutsung{If we follow \cite{Maassen2010,Swart2013}, then we also
+% need 
+% \begin{itemize}
+% \item $\mu$ can be extended to a linear functional~$\mu:alg\left(\qevents\right)\rightarrow\mathbb{C}$,
+% where $alg\left(\qevents\right)$ is the minimal $*$-algebra generated
+% by $\qevents$.
+% \end{itemize}
+% Also, 
+% \begin{itemize}
+% \item for all $A\in\qevents$, we have $\mu(A^{*}A)\geq0$. 
+% \end{itemize}
+% should be 
+% \begin{itemize}
+% \item for all $A\in alg\left(\qevents\right)$, we have $\mu(A^{*}A)\geq0$. 
+% \end{itemize}
+% because we have $\mu(A^{*}A)=\mu(A^{2})=\mu(A)$ if $A$ is a projection.}\\
 
-%% If we want to follow Swart~\cite{Swart2013} 
-%% I am following sec 4 of https://www.math.ru.nl/~maassen/lectures/Trieste.pdf
+% \yutsung{$\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
+% is the minimal $*$-algebra generated by $P_{1},P_{2},\ldots,P_{k}$,
+% but it contains all possible observables $P_{1},P_{2},\ldots,P_{k}$
+% can generate (and something more) not just projections. For example,
+% $2\mathbb{1}\in\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $.}\\
 
-Concrete example: consider the two qubit Hilbert space with
-computational bases $\ket{0}$ and $\ket{1}$ and consider
-the following families of projections:
-\begin{itemize}
-\item Family I: $\proj{0}$, $\proj{1}$
-\item Family II: $\proj{+}$, $\proj{-}$
-\end{itemize}
-and consider the two states \ldots
+% \yutsung{So $\mu_{\psi}$ maps the projections generated by $P_{1},P_{2},\ldots,P_{k}$
+% to $[0,1]$, and maps $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
+% to $\mathbb{C}$...}\\
 

### 2016-04-18 prob.tex
prob.tex \subsection{Plan} updated...

--- 2016-04-18 prob.tex
@@
 \newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
+\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
 
@@
 In the remainder of the paper, we examine each of these assumptions
-and consider variations motivated by computation in a world with
-limited resources. In particular, we will consider a variant of the
-Hilbert space over finite fields; we will consider set-valued
-probability measures; we will consider ways other than the Born rule
-in which a state can induce a probability measure, and we will consider
-probability measures that may come from information beyond the quantum
-states.
+and consider variations motivated by computation in a world with limited
+resources. In particular, we will consider a variant of the Hilbert
+space over finite fields~$\mathbb{F}_{p^{2}}^{d}$. Instead of $\left[0,1\right]$,
+we will consider set-valued probability measures, in particular $\left\{ 0\right\} $,
+impossible, and $\left(0,\infty\right)$, possible. Surprisingly,
+some combinations of space and probability will result in no probability
+measure or an unique probability measure. In these cases, there is
+no need to discuss whether there is a Born rule, because we do not
+have enough probability to correspond to every state.
+
+If there may be more than one probability measure, we will discuss
+whether there is a Born rule to generate a probability measure from
+a state. When the space is $\mathbb{C}^{d}$, we will try to induced
+a Born rule from the conventional Born rule; when the space is $\mathbb{F}_{p^{2}}^{d}$,
+there is no natural way to induce a probability measure from a state,
+so we will set some conditions a Born~$\tilde{\pi}$ should have:
+\begin{itemize}
+\item Given a pure state $\ket{\Psi}\in\ffzd{p^{2}}$, a Born-rule~$\tilde{\pi}$
+should give a probability~$\tilde{\pi}_{\Psi}$;
+\item $\ip{\Psi}{\Phi}=0\Leftrightarrow\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{0}$,
+where $\tilde{0}$ is $0$ while considering $\left[0,1\right]$ and
+$\tilde{0}$ is impossible while considering $\left\{ \textrm{impossible},\textrm{possible}\right\} $.
+\item $\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{\pi}_{\mathbf{U}\ket{\Psi}}\left(\mathbf{U}\ket{\Phi}\right)\textrm{ ,}$where
+$\ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}$ and $\mathbf{U}$ is any unitary
+map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbbm{1}$. 
+\end{itemize}
+Notice that when the space is $\mathbb{C}^{d}$, every Born rule we
+consider will satisfy these three conditions.
+
+Finally, if there is a Born rule, we will see whether every probability
+measure is induced by a state, and establish Gleason's theorem.
 

### 2016-04-18 prob.tex
typos

--- 2016-04-18 prob.tex
@@
 $\mathbb{1} = \proj{0}+\proj{1}$. Each event is interpreted as a
-possible post-measurement of a quantum system as follows: given some
+possible post-measurement state of a quantum system as follows: given some
 arbitrary current quantum $\ket{\psi}$ to be measured, the event
@@
 follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
-Hilbert space $\Hilb$ and define the set of events $\qevents$ as all
-linear combinations of \emph{projections} on $\Hilb$. Specifically,
+Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
+linear combinations of \emph{projections} on~$\Hilb$. Specifically,
 let $P_1, P_2, \ldots, P_k$ be mutually orthogonal projections on

### 2016-04-18 prob.tex
prob.tex "\subsection{Quantum Probability Spaces}" add comments...

@@
 event $\mathbb{0}$ states that the post-measurement state will be the
-empty state. Clearly irrespective of the current state $\ket{\psi}$
+empty state. \\
+\yutsung{How about replacing the above sentence by something like: 
+\begin{quote}
+Each event is interpreted as a possible post-measurement state of
+a quantum system if that event occurs as follows~\cite{Abramsky2013}:
+...... and the event $\mathbb{0}$ does not to state the post-measurement
+state because it never occurs. 
+\end{quote}
+}\\
+Clearly irrespective of the current state $\ket{\psi}$
 and irrespective of the particular experiment, the probability of

### 2016-04-18 prob.tex
prob.tex \subsection{Plan} Add table...

@@
 \usepackage{multicol}
+\usepackage{array}
+\usepackage{mathrsfs}
 
@@
 \newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
+\def\C{{\mathbb{C}}}
+\newcommand{\ff}[1]{\mathbb{F}_{#1}}
 
@@
 \item the real interval $[0,1]$; 
-\item the fact that each state induces a probability measure, i.e., the Born rule;
-\item the fact that every probability measure is induced by a state,
-  i.e., Gleason's theorem
+\item the fact that each state induces a probability measure, i.e., the
+Born rule~\cite{Born1984,Mermin2007}; 
+\item the fact that every probability measure is induced by a state, i.e.,
+Gleason's theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}. 
 \end{itemize}
-
 In the remainder of the paper, we examine each of these assumptions
@@
 resources. In particular, we will consider a variant of the Hilbert
-space over finite fields~$\mathbb{F}_{p^{2}}^{d}$. Instead of $\left[0,1\right]$,
-we will consider set-valued probability measures, in particular $\left\{ 0\right\} $,
+space over finite fields~$\mathbb{F}_{p^{2}}^{d}$~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
+Instead of $\left[0,1\right]$, we will consider set-valued probability
+measures~\cite{Artstein1972,PuriRalescu1983}, in particular $\left\{ 0\right\} $,
 impossible, and $\left(0,\infty\right)$, possible. Surprisingly,
@@
 \item $\ip{\Psi}{\Phi}=0\Leftrightarrow\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{0}$,
-where $\tilde{0}$ is $0$ while considering $\left[0,1\right]$ and
-$\tilde{0}$ is impossible while considering $\left\{ \textrm{impossible},\textrm{possible}\right\} $.
+where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
+is impossible for $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $. 
 \item $\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{\pi}_{\mathbf{U}\ket{\Psi}}\left(\mathbf{U}\ket{\Phi}\right)\textrm{ ,}$where
@@
 Finally, if there is a Born rule, we will see whether every probability
-measure is induced by a state, and establish Gleason's theorem.
+measure is induced by a state, and establish Gleason's theorem. Notice
+that Gleason's theorem only hold when $d\ge3$ in CQT so that we may
+expect the situation for $d\ge3$ and $d=2$ are different.
+
+The results can be summarized in the following table:\\
+\begin{tabular}{>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}}
+\hline 
+State space $\Hilb$ & Probability values & How many probability measure?
+& Is there a nature Born rule?
+& How many possible Born rule if there is no nature one?
+& How many probability measure not come from any possible Born rules?\tabularnewline
+\hline 
+\hline 
+$\C^{2*}$ & $\left[0,1\right]$  & $\ge2$ & Yes &  & $\ge1$\tabularnewline
+\hline 
+$\C^{d*}$ for $d\ge3$ & $\left[0,1\right]$  & $\ge2$ & Yes &  & $0$\tabularnewline
+\hline 
+$\C^{d*}$ & $\mathscr{L}_{2}$ & $\ge2$ & Yes &  & $\ge1$\tabularnewline
+\hline 
+$\ff{3^{2}}^{d*}$ for $3\ge d\ge2$ & $\left[0,1\right]$  & $\ge2$ & No & $1$ & $\ge1$\tabularnewline
+\hline 
+$\ff{p^{2}}^{2*}$ for $p\ge7$ & $\left[0,1\right]$  & $\ge2$ & No & $\infty$ & $\ge1$\tabularnewline
+\hline 
+$\ff{7^{2}}^{3*}$ & $\left[0,1\right]$  & $1$ & No & $0$ & \tabularnewline
+\hline 
+$\ffzd{p^{2}}$for $d\ge3$ except $d=p=3$ & $\left[0,1\right]$  & $\ge1$ & No & $0$ & \tabularnewline
+\hline 
+$\ffzd{p^{2}}$ & $\mathscr{L}_{2}$ & $\ge2$ & No & $1$ & $\ge1$\tabularnewline
+\hline 
+\end{tabular}
 

### 2016-04-19 prob.tex
From: Tai, Yu-Tsung Sent: Monday, April 18, 2016 23:55 To: Sabry, Amr A. <sabry@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu> Subject: RE: probability in the quantum case
Dear Prof. Sabry, 

I have updated the plan section, and I updated my comment so that it may
be clearer than previously... We may meet and discuss if it is still not
clear enough...

About Prof. Ellerman’s paper, it seems interested, although his bra and
the probability he defined is basis dependent… I would be really
interested if he could build a probability model on a basis inde

@@
 \usepackage{mathrsfs}
+\usepackage[all]{xy}
 
@@
 \]
-Similarlly to the classical case, this probability measure satisfies:
+Similarly to the classical case, this probability measure satisfies: 
 \begin{itemize}
-\item $\mu(\mathbb{1}) = 1$, and
-\item for all $A \in \qevents$, we have $\mu(A^*A) \geq 0$.
+\item $\mu(\mathbb{1})=1$, and 
+\item for all $A\in\qevents$, we have $\mu(A^{*}A)\geq0$. 
 \end{itemize}
+\yutsung{The following is the diagram for quantum probability objects
+and their corresponding physical meaning (in parentheses):
+\[
+\xymatrix{\textrm{projections (\textrm{events})}\ar[d]^{\mu_{\psi}\textrm{(probability)}} & \subsetneq & \textrm{Hermitian operators (observables)}\ar[d]^{\mu_{\psi}\textrm{(expectation value)}} & \subsetneq & \textrm{all operators in a }*\textrm{-algebra(?)}\ar[d]^{\mu_{\psi}\textrm{(?)}}\\
+\left[0,1\right] & \subsetneq & \mathbb{R} & \subsetneq & \mathbb{C}
+}
+\]
+Although the above paragraph claimed $\qevents$ is a set of events,
+``all linear combinations of \emph{projections}'' and $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
+gives all operators in a $*$-algebra. Therefore, I got confused you
+want $\qevents$ be ``the set of all events'' or ``the set of all
+operators in a $*$-algebra''...}
 
@@
 space over finite fields~$\mathbb{F}_{p^{2}}^{d}$~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
-Instead of $\left[0,1\right]$, we will consider set-valued probability
-measures~\cite{Artstein1972,PuriRalescu1983}, in particular $\left\{ 0\right\} $,
-impossible, and $\left(0,\infty\right)$, possible. Surprisingly,
-some combinations of space and probability will result in no probability
-measure or an unique probability measure. In these cases, there is
-no need to discuss whether there is a Born rule, because we do not
-have enough probability to correspond to every state.
+
+For the probability values, we will consider set-valued probability
+measures~\cite{Artstein1972,PuriRalescu1983}, in particular $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $,
+where impossible is a singleton set,$\left\{ 0\right\} $, and possible
+is an open interval, $\left(0,\infty\right)$. Surprisingly, some
+combinations of space and probability will result in an unique probability
+measure. In these cases, there is no need to discuss whether there
+is a Born rule, because we do not have enough probability to correspond
+to every state.
 
@@
 a state. When the space is $\mathbb{C}^{d}$, we will try to induced
-a Born rule from the conventional Born rule; when the space is $\mathbb{F}_{p^{2}}^{d}$,
+a Born rule from the conventional Born rule. When the space is $\mathbb{F}_{p^{2}}^{d}$,
 there is no natural way to induce a probability measure from a state,
-so we will set some conditions a Born~$\tilde{\pi}$ should have: 
+so we will set some conditions for a Born rule~$\tilde{\pi}$: 
 \begin{itemize}
@@
 \hline 
-$\C^{2*}$ & $\left[0,1\right]$  & $\ge2$ & Yes &  & $\ge1$\tabularnewline
+$\C^{2}$ & $\left[0,1\right]$  & $\ge2$ & Yes &  & $\ge1$\tabularnewline
 \hline 
-$\C^{d*}$ for $d\ge3$ & $\left[0,1\right]$  & $\ge2$ & Yes &  & $0$\tabularnewline
+$\C^{d}$ for $d\ge3$ & $\left[0,1\right]$  & $\ge2$ & Yes &  & $0$\tabularnewline
 \hline 
-$\C^{d*}$ & $\mathscr{L}_{2}$ & $\ge2$ & Yes &  & $\ge1$\tabularnewline
+$\C^{d}$ & $\mathscr{L}_{2}$ & $\ge2$ & Yes &  & $\ge1$\tabularnewline
 \hline 
-$\ff{3^{2}}^{d*}$ for $3\ge d\ge2$ & $\left[0,1\right]$  & $\ge2$ & No & $1$ & $\ge1$\tabularnewline
+$\ff{3^{2}}^{d}$ for $3\ge d\ge2$ & $\left[0,1\right]$  & $\ge2$ & No & $1$ & $\ge1$\tabularnewline
 \hline 
-$\ff{p^{2}}^{2*}$ for $p\ge7$ & $\left[0,1\right]$  & $\ge2$ & No & $\infty$ & $\ge1$\tabularnewline
+$\ff{p^{2}}^{2}$ for $p\ge7$ & $\left[0,1\right]$  & $\ge2$ & No & $\infty$ & $\ge1$\tabularnewline
 \hline 
-$\ff{7^{2}}^{3*}$ & $\left[0,1\right]$  & $1$ & No & $0$ & \tabularnewline
+$\ff{7^{2}}^{3}$ & $\left[0,1\right]$  & $1$ & No & $0$ & \tabularnewline
 \hline 
-$\ffzd{p^{2}}$for $d\ge3$ except $d=p=3$ & $\left[0,1\right]$  & $\ge1$ & No & $0$ & \tabularnewline
+$\ffzd{p^{2}}$for $d\ge3$ except $d=p=3$ & $\left[0,1\right]$  & $\ge1$
+
+(Whether $\ge2$ or $1$?) & No & $0$ & \tabularnewline
 \hline 

### 2016-04-19 prob.tex
fixed prob space

@@
 \newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
+\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
 \newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
@@
 \]
-A possible space of events is the set
-$\{ \mathbb{0}, \proj{0}, \proj{1}, \mathbb{1}\}$ consisting of the
-projection operators $\proj{0}$ and $\proj{1}$ as well as the empty
-projection $\mathbb{0}$ and the unit projection
-$\mathbb{1} = \proj{0}+\proj{1}$. Each event is interpreted as a
-possible post-measurement state of a quantum system as follows: given some
-arbitrary current quantum $\ket{\psi}$ to be measured, the event
-$\proj{0}$ states that the post-measurement state will be $\ket{0}$;
-the event $\proj{1}$ states that the post-measurement state will be
-$\ket{1}$; the event $\mathbb{1}$ states that the post-measurement
-state will be a linear combination of $\ket{0}$ and $\ket{1}$; and the
-event $\mathbb{0}$ states that the post-measurement state will be the
-empty state. \\
-\yutsung{How about replacing the above sentence by something like: 
-\begin{quote}
-Each event is interpreted as a possible post-measurement state of
-a quantum system if that event occurs as follows~\cite{Abramsky2013}:
-...... and the event $\mathbb{0}$ does not to state the post-measurement
-state because it never occurs. 
-\end{quote}
-}\\
-Clearly irrespective of the current state $\ket{\psi}$
-and irrespective of the particular experiment, the probability of
-event $\mathbb{0}$ will always be 0 (it is an impossible event) and
-the probability of event $\mathbb{1}$ will always be 1 (it is a
-certain event). The probabilities attached to other events will depend
-on the particular state in question. If the state is $\ket{0}$, the
-probability of event $\proj{0}$ is 1 and the probability of event
-$\proj{1}$ is 0. If the state is $\ket{\ps}$, the probability of both
-events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$. The same
-Hilbert space setup admits other possible spaces of events. For
-example, another space of events could be
-$\{ \mathbb{0}, \proj{\ps}, \proj{\ms}, \mathbb{1}\}$. Using that
-space of events, the state $\ket{0}$ maps both events $\proj{\ps}$ and
-$\proj{\ms}$ to the probability $\frac{1}{2}$.
+The set of events associated with this Hilbert space consists of all
+projections including the empty projection $\mathbb{0}$ and the unit
+projection $\mathbb{1} = \proj{0}+\proj{1}$:
+\[ 
+\{ \mathbb{0}, \proj{0}, \proj{1}, \proj{\ps}, \proj{\ms}, \ldots, \mathbb{1}\}
+\]
+Each event is interpreted as a possible post post-measurement state of
+a quantum system as follows: given some arbitrary current quantum
+$\ket{\psi}$ to be measured, the event $\proj{0}$ states that the
+post-measurement state will be $\ket{0}$; the event $\proj{1}$ states
+that the post-measurement state will be $\ket{1}$; the event
+$\proj{\ps}$ states that the post-measurement state will be
+$\ket{\ps}$; the event $\proj{\ms}$ states that the post-measurement
+state will be $\ket{\ms}$; the event $\mathbb{1}$ states that the
+post-measurement state will be a linear combination of $\ket{0}$ and
+$\ket{1}$; and the event $\mathbb{0}$ states that the post-measurement
+state will be the empty state.
+
+Clearly irrespective of the current state $\ket{\psi}$ and
+irrespective of the particular experiment, the probability of event
+$\mathbb{0}$ will always be 0 (it is an impossible event) and the
+probability of event $\mathbb{1}$ will always be 1 (it is a certain
+event). The probabilities attached to other events will depend on the
+particular state in question. If the state is $\ket{0}$, the
+probability of event $\proj{0}$ is 1; the probability of event
+$\proj{1}$ is 0; the probability of event $\proj{\ps}$ is
+$\frac{1}{2}$; and the probability of event $\proj{\ms}$ is
+$\frac{1}{2}$. If the state is $\ket{\ps}$, the probability of both
+events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$; the
+probability of event $\proj{\ps}$ is 1; and the probability of event
+$\proj{\ms}$ is 0.
 
@@
 Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
-linear combinations of \emph{projections} on~$\Hilb$. Specifically,
-let $P_1, P_2, \ldots, P_k$ be mutually orthogonal projections on
-$\Hilb$ with sum $\mathbb{1}$ and define the event space $\qevents$ to
-be the linear span of these operators:
-\[
-\qevents=\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} .
-\]
-Each quantum state $\ket{\psi}$ induces a probability measure
-$\mu_\psi : \qevents \rightarrow [0,1]$ on the space of events
-defined as follows:
+\emph{projections} on~$\Hilb$. Each quantum state $\ket{\psi}$ induces
+a probability measure $\mu_\psi : \qevents \rightarrow [0,1]$ on the
+space of events defined as follows:
 \[
@@
 \]
-Similarly to the classical case, this probability measure satisfies: 
+Similarly to the classical case, this probability measure must satisfy:
 \begin{itemize}
 \item $\mu(\mathbb{1})=1$, and 
-\item for all $A\in\qevents$, we have $\mu(A^{*}A)\geq0$. 
+\item for a collection of pairwise orthogonal $A_i$, we have
+  $\mu(\sum_i A_i) = \sum_i \mu(A_i)$.
+
+\amr{CHECK because sum of
+    projections may not be a projection}
 \end{itemize}
+
 \yutsung{The following is the diagram for quantum probability objects

### 2016-04-20 prob.tex
prob.tex "\subsection{Quantum Probability Spaces}" Add a proof...

@@
     projections may not be a projection}
+
+\yutsung{I am going to verify if $\proj{\psi_{1}}+\proj{\psi_{2}}$
+is a projection, then they are orthogonal. Given any state $\ket{\phi}=a\ket{\psi_{1}}+b\ket{\psi_{2}}$,
+if $\proj{\psi_{1}}+\proj{\psi_{2}}$ is a projection, then 
+\begin{eqnarray*}
+\ket{\phi} & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\ket{\phi}\\
+ & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\left(a\ket{\psi_{1}}+b\ket{\psi_{2}}\right)\\
+ & = & a\ket{\psi_{1}}+b\ket{\psi_{2}}+a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
+\end{eqnarray*}
+Therefore, we have 
+\begin{eqnarray*}
+0 & = & a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
+\end{eqnarray*}
+However, $a$ and $b$ can be any numbers. Therefore, we must have
+$0=\ip{\psi_{2}}{\psi_{1}}=\ip{\psi_{1}}{\psi_{2}}$.}
 \end{itemize}
-
 \yutsung{The following is the diagram for quantum probability objects
@@
 \[
-\xymatrix{\textrm{projections (\textrm{events})}\ar[d]^{\mu_{\psi}\textrm{(probability)}} & \subsetneq & \textrm{Hermitian operators (observables)}\ar[d]^{\mu_{\psi}\textrm{(expectation value)}} & \subsetneq & \textrm{all operators in a }*\textrm{-algebra(?)}\ar[d]^{\mu_{\psi}\textrm{(?)}}\\
+\xymatrix{\textrm{projections (events)}\ar[d]^{\mu_{\psi}\textrm{(probability)}} & \subsetneq & \textrm{Hermitian operators (observables)}\ar[d]^{\mu_{\psi}\textrm{(expectation value)}} & \subsetneq & \textrm{all operators in a }*\textrm{-algebra(?)}\ar[d]^{\mu_{\psi}\textrm{(?)}}\\
 \left[0,1\right] & \subsetneq & \mathbb{R} & \subsetneq & \mathbb{C}
@@
 \]
-Although the above paragraph claimed $\qevents$ is a set of events,
-``all linear combinations of \emph{projections}'' and $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
-gives all operators in a $*$-algebra. Therefore, I got confused you
-want $\qevents$ be ``the set of all events'' or ``the set of all
-operators in a $*$-algebra''...}
+}
 

### 2016-04-20 prob.tex
Merge Andy's comments by hand to prob.tex...

@@
 
-Textbook probability
+Probability
 theory~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
@@
 \emph{finite} sample spaces: we therefore define a sample space
-$\Omega$ as an arbitrary non-empty finite set and the space of events
-$\events$ as, $2^\Omega$, the powerset of $\Omega$. A \emph{probability
-measure} is a function $\pmeas : \events \rightarrow [0,1]$ such that:
+$\Omega$ as an arbitrary non-empty finite set, the space of events
+$\events$ as $2^\Omega$, the powerset of $\Omega$, and the \emph{probability
+measure} as a function $\pmeas : \events \rightarrow [0,1]$ such that:
 \begin{itemize}
 \item $\pmeas(\Omega) = 1$, and 
-\item for a collection of pairwise disjoint events $E_i$, we have
-  $\pmeas(\bigcup E_i) = \sum \pmeas(E_i)$. 
+\item for a collection of pairwise disjoint events $E_i$, the probability
+measures are additive $\pmeas(\bigcup E_i) = \sum \pmeas(E_i)$. 
 \end{itemize}
 
-\begin{example}[Two coin experiment] Consider an experiment that
-  tosses two coins. We have four possible outcomes that constitute the
+\emph{Example of a problem on a finite sample space} (Two coin experiment)
+Consider an experiment that tosses two coins. We have four possible outcomes that constitute the
   sample space $\Omega = \{ HH, HT, TH, TT \}$. The event that the
@@
 \end{array}\]
-\end{example}
+Note that the probability measure for disjoint events such as $\{ HT \}$ and
+$\{ TH \}$ do indeed add.
 
@@
 non-commuting events which cannot even happen simultaneously. To
-accommodate these more complex situations, we completely abandon the
+accommodate these more complex situations, we abandon the
 sample space~$\Omega$ and define and reason directly about
-events. Thus a quantum probability space will consist of just two
+events. A quantum probability space consist of just two
 components: a set of events $\qevents$ and a probability measure
@@
 Each event is interpreted as a possible post post-measurement state of
-a quantum system as follows: given some arbitrary current quantum
+a quantum system as follows: given some arbitrary current quantum state
 $\ket{\psi}$ to be measured, the event $\proj{0}$ states that the
@@
 
-Clearly irrespective of the current state $\ket{\psi}$ and
+Irrespective of the current state $\ket{\psi}$ and
 irrespective of the particular experiment, the probability of event
@@
 $\frac{1}{2}$; and the probability of event $\proj{\ms}$ is
-$\frac{1}{2}$. If the state is $\ket{\ps}$, the probability of both
-events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$; the
+$\frac{1}{2}$. If the state is $\ket{\ps}$, the probability of each
+event $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$; the
 probability of event $\proj{\ps}$ is 1; and the probability of event
@@
 Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
-\emph{projections} on~$\Hilb$. Each quantum state $\ket{\psi}$ induces
+\emph{projections} on~$\Hilb$. Each quantum state $\ket{\psi}\in\Hilb$ induces
 a probability measure $\mu_\psi : \qevents \rightarrow [0,1]$ on the
-space of events defined as follows:
+space of events defined for any event $A\in\qevents$ as follows:
 \[
@@
 In the remainder of the paper, we examine each of these assumptions
-and consider variations motivated by computation in a world with limited
-resources. In particular, we will consider a variant of the Hilbert
+and consider variations motivated by computation of numerical quantities in a
+world with limited resources. In particular, we will consider a variant of the Hilbert
 space over finite fields~$\mathbb{F}_{p^{2}}^{d}$~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.

### 2016-04-21 prob.tex
prob.tex Change variable name from A to E in order to: 1. Clearly express that E is an event; 2. Avoid confusing with the whole *-algebra in the literature, bucause we are not using the full algebra...

@@
 \newtheorem{example}{Example}
-\newcommand{\events}{\ensuremath{\mathcal{A}}}
-\newcommand{\qevents}{\ensuremath{\mathcal{A}}}
+\newcommand{\events}{\ensuremath{\mathcal{E}}}
+\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
 \newcommand{\pmeas}{\ensuremath{\mu}}
@@
 a probability measure $\mu_\psi : \qevents \rightarrow [0,1]$ on the
-space of events defined for any event $A\in\qevents$ as follows:
+space of events defined for any event $E\in\qevents$ as follows:
 \[
-\mu_\psi(A) = \ip{\psi}{A\psi}
+\mu_\psi(E) = \ip{\psi}{E\psi}
 \]
@@
 \item $\mu(\mathbb{1})=1$, and 
-\item for a collection of pairwise orthogonal $A_i$, we have
-  $\mu(\sum_i A_i) = \sum_i \mu(A_i)$.
+\item for a collection of pairwise orthogonal $E_i$, we have
+  $\mu(\sum_i E_i) = \sum_i \mu(E_i)$.
 

### 2016-04-21 prob.tex
prob.tex "\subsection{Quantum Probability Spaces}" resolve domain...

@@
 
-We now formalize a \emph{quantum probability space} as
-follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
-Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
-\emph{projections} on~$\Hilb$. Each quantum state $\ket{\psi}\in\Hilb$ induces
-a probability measure $\mu_\psi : \qevents \rightarrow [0,1]$ on the
-space of events defined for any event $E\in\qevents$ as follows:
+We now formalize a \emph{quantum probability space} as follows~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}.
+We first assume an ambient Hilbert space~$\Hilb$ and define the
+set of events $\qevents$ as all \emph{projections} on~$\Hilb$.
+Each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
+induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
+on the space of events defined for any event $E\in\qevents$ as follows\footnote{Recently, people extend the domain of $\mu_{\psi}$ to all operators~$\mathcal{A}$
+on $\Hilb$ and consider $\mu_{\psi}:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
+When an operator $A\in\mathcal{A}$ is Hermitian, $\mu_{\psi}\left(A\right)$
+is the expectation value of $A$. We does not take this approach because
+we want to focus only on probability. }: 
 \[
-\mu_\psi(E) = \ip{\psi}{E\psi}
+\mu_{\psi}(E)=\frac{\ip{\psi}{E\psi}}{\ip{\psi}{\psi}}
 \]
@@
 \end{itemize}
-\yutsung{The following is the diagram for quantum probability objects
-and their corresponding physical meaning (in parentheses): 
-\[
-\xymatrix{\textrm{projections (events)}\ar[d]^{\mu_{\psi}\textrm{(probability)}} & \subsetneq & \textrm{Hermitian operators (observables)}\ar[d]^{\mu_{\psi}\textrm{(expectation value)}} & \subsetneq & \textrm{all operators in a }*\textrm{-algebra(?)}\ar[d]^{\mu_{\psi}\textrm{(?)}}\\
-\left[0,1\right] & \subsetneq & \mathbb{R} & \subsetneq & \mathbb{C}
-}
-\]
-}
 

### 2016-04-21 prob.tex
removed comment
Still cannot prove if projections sum up to projections, they are orthogonal... Decide to leave it there for a while...

@@
 
-\amr{CHECK because sum of
-    projections may not be a projection}
-
-\yutsung{I am going to verify if $\proj{\psi_{1}}+\proj{\psi_{2}}$
-is a projection, then they are orthogonal. Given any state $\ket{\phi}=a\ket{\psi_{1}}+b\ket{\psi_{2}}$,
-if $\proj{\psi_{1}}+\proj{\psi_{2}}$ is a projection, then 
+\yutsung{Claim: If $\sum_{i}\proj{\psi_{i}}$ is a projection, then
+they are orthogonal. \\
+Proof: If $\sum_{i}\proj{\psi_{i}}$ is a projection, then 
 \begin{eqnarray*}
-\ket{\phi} & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\ket{\phi}\\
- & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\left(a\ket{\psi_{1}}+b\ket{\psi_{2}}\right)\\
- & = & a\ket{\psi_{1}}+b\ket{\psi_{2}}+a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
+\ket{\psi_{j}} & = & \left(\sum_{i}\proj{\psi_{i}}\right)\ket{\psi_{j}}\\
+ & = & \sum_{i}\ket{\psi_{i}}\ip{\psi_{i}}{\psi_{j}}
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-0 & = & a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
+0 & = & \sum_{i\ne j}\ket{\psi_{i}}\ip{\psi_{i}}{\psi_{j}}
 \end{eqnarray*}
-However, $a$ and $b$ can be any numbers. Therefore, we must have
-$0=\ip{\psi_{2}}{\psi_{1}}=\ip{\psi_{1}}{\psi_{2}}$.}
+} 
 \end{itemize}

### 2016-04-22 prob.tex
prob.tex "\subsection{Plan}" updated...

@@
 we want to focus only on probability. }: 
-\[
-\mu_{\psi}(E)=\frac{\ip{\psi}{E\psi}}{\ip{\psi}{\psi}}
-\]
+\begin{equation}
+\mu_{\psi}(E)=\frac{\ip{\psi}{E\psi}}{\ip{\psi}{\psi}}\label{eq:Born}
+\end{equation}
 Similarly to the classical case, this probability measure must satisfy:
@@
 \item the fact that each state induces a probability measure, i.e., the
-Born rule~\cite{Born1984,Mermin2007}; 
+Born rule (\ref{eq:Born})~\cite{Born1984,Mermin2007}; 
 \item the fact that every probability measure is induced by a state, i.e.,
@@
 In the remainder of the paper, we examine each of these assumptions
-and consider variations motivated by computation of numerical quantities in a
-world with limited resources. In particular, we will consider a variant of the Hilbert
-space over finite fields~$\mathbb{F}_{p^{2}}^{d}$~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
+and consider variations motivated by computation of numerical quantities
+in a world with limited resources. In particular, we will consider
+a variant of the Hilbert space over finite fields~$\mathbb{F}_{p^{2}}^{d}$~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
 
@@
 where impossible is a singleton set,$\left\{ 0\right\} $, and possible
-is an open interval, $\left(0,\infty\right)$. Surprisingly, some
-combinations of space and probability will result in an unique probability
-measure. In these cases, there is no need to discuss whether there
-is a Born rule, because we do not have enough probability to correspond
-to every state.
+is an open interval, $\left(0,\infty\right)$.
 
 If there may be more than one probability measure, we will discuss
-whether there is a Born rule to generate a probability measure from
-a state. When the space is $\mathbb{C}^{d}$, we will try to induced
-a Born rule from the conventional Born rule. When the space is $\mathbb{F}_{p^{2}}^{d}$,
-there is no natural way to induce a probability measure from a state,
-so we will set some conditions for a Born rule~$\tilde{\pi}$: 
+whether we will keep using the Born rule (\ref{eq:Born}) or there
+is another formula $\tilde{\mu}$ such that $\tilde{\mu}_{\psi}$
+is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
+
+Then, Gleason's theorem states given a probability measure $\mu$
+there is a mixed state $\ket{\psi}$ such that $\mu=\mu_{\psi}$,
+i.e., the Born rule is surjective\footnote{If we extend the domain of $\mu_{\psi}$ including the mixed states.}.
+For any other formula~$\tilde{\mu}$, we can ask whether $\tilde{\mu}$
+is surjective as well.
+
+Obveriously, we don't want arbirarily assign a state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
+with a proabability measure $\tilde{\mu}_{\psi}$, for example, assigning
+every state to the same probability measure. We want $\tilde{\mu}_{\psi}$
+satisfying the following properties with some physical meaning:
 \begin{itemize}
-\item Given a pure state $\ket{\Psi}\in\ffzd{p^{2}}$, a Born-rule~$\tilde{\pi}$
-should give a probability~$\tilde{\pi}_{\Psi}$; 
-\item $\ip{\Psi}{\Phi}=0\Leftrightarrow\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{0}$,
+\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
 where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
 is impossible for $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $. 
-\item $\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{\pi}_{\mathbf{U}\ket{\Psi}}\left(\mathbf{U}\ket{\Phi}\right)\textrm{ ,}$where
-$\ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}$ and $\mathbf{U}$ is any unitary
-map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbbm{1}$. 
+\item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
+$\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
+map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
 \end{itemize}
-Notice that when the space is $\mathbb{C}^{d}$, every Born rule we
-consider will satisfy these three conditions.
-
-Finally, if there is a Born rule, we will see whether every probability
-measure is induced by a state, and establish Gleason's theorem. Notice
-that Gleason's theorem only hold when $d\ge3$ in CQT so that we may
-expect the situation for $d\ge3$ and $d=2$ are different.
-
-The results can be summarized in the following table:\\
-\begin{tabular}{>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}>{\raggedright}m{0.15\columnwidth}}
+And the results can be summarized in the following table:\\
+\center{ %
+\begin{tabular}{>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}}
 \hline 
-State space $\Hilb$ & Probability values & How many probability measure?
-& Is there a nature Born rule?
-& How many possible Born rule if there is no nature one?
-& How many probability measure not come from any possible Born rules?\tabularnewline
+State space $\Hilb$  & Probability values  & Is there a $\tilde{\mu}$ satisfying the given conditions?  & Is the $\tilde{\mu}$ surjective?\tabularnewline
 \hline 
 \hline 
-$\C^{2}$ & $\left[0,1\right]$  & $\ge2$ & Yes &  & $\ge1$\tabularnewline
+$\C^{d}$ for $d\ge3$  & $\left[0,1\right]$  & Yes  & Yes\tabularnewline
 \hline 
-$\C^{d}$ for $d\ge3$ & $\left[0,1\right]$  & $\ge2$ & Yes &  & $0$\tabularnewline
+$\C^{d}$  & $\mathscr{L}_{2}$  & Yes  & No\tabularnewline
 \hline 
-$\C^{d}$ & $\mathscr{L}_{2}$ & $\ge2$ & Yes &  & $\ge1$\tabularnewline
+$\ffzd{p^{2}}$for $d\ge3$ except $d=p=3$  & $\left[0,1\right]$  & No  & \tabularnewline
 \hline 
-$\ff{3^{2}}^{d}$ for $3\ge d\ge2$ & $\left[0,1\right]$  & $\ge2$ & No & $1$ & $\ge1$\tabularnewline
+$\ffzd{p^{2}}$  & $\mathscr{L}_{2}$  & Yes & No\tabularnewline
 \hline 
-$\ff{p^{2}}^{2}$ for $p\ge7$ & $\left[0,1\right]$  & $\ge2$ & No & $\infty$ & $\ge1$\tabularnewline
-\hline 
-$\ff{7^{2}}^{3}$ & $\left[0,1\right]$  & $1$ & No & $0$ & \tabularnewline
-\hline 
-$\ffzd{p^{2}}$for $d\ge3$ except $d=p=3$ & $\left[0,1\right]$  & $\ge1$
-
-(Whether $\ge2$ or $1$?) & No & $0$ & \tabularnewline
-\hline 
-$\ffzd{p^{2}}$ & $\mathscr{L}_{2}$ & $\ge2$ & No & $1$ & $\ge1$\tabularnewline
-\hline 
-\end{tabular}
+\end{tabular}}
 

### 2016-04-22 prob.tex
plan

@@
 \begin{equation}
-\mu_{\psi}(E)=\frac{\ip{\psi}{E\psi}}{\ip{\psi}{\psi}}\label{eq:Born}
+\mu_{\psi}(E)= \ip{\psi}{E\psi} \label{eq:Born}
 \end{equation}
@@
 
-Several assumptions are woven in the definition of a quantum probability space:
+In the remainder of the paper, we consider variations of quantum
+probability spaces motivated by computation of numerical quantities in
+a world with limited resources:
 \begin{itemize}
-\item the Hilbert space $\Hilb$;
-\item the real interval $[0,1]$; 
-\item the fact that each state induces a probability measure, i.e., the
-Born rule (\ref{eq:Born})~\cite{Born1984,Mermin2007}; 
-\item the fact that every probability measure is induced by a state, i.e.,
-Gleason's theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}. 
+\item Instead of the Hilbert space $\Hilb$ (constructed over the
+  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
+  consider variants constructed over finite
+  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
+\item Instead of real-valued probability measures producing results in
+  the uncountable and uncomputable interval $[0,1]$, we will consider
+  set-valued probablitity measures~\cite{Artstein1972,PuriRalescu1983}.
 \end{itemize}
-In the remainder of the paper, we examine each of these assumptions
-and consider variations motivated by computation of numerical quantities
-in a world with limited resources. In particular, we will consider
-a variant of the Hilbert space over finite fields~$\mathbb{F}_{p^{2}}^{d}$~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
+We will then ask if it is possible to construct variants of quantum
+probability spaces under these conditions. The main question is
+related to the definition of probability measures: is it possible to
+still define a probability measure as a function that depends on a
+single state? Specifically,
+\begin{itemize}
+\item given a state $\ket{\psi}$, is there a probability measure
+  mapping events to probabilities that only depends on $\ket{\psi}$?
+  In the conventional quantum probability space, the answer is yes by
+  the Born rule~\cite{Born1984,Mermin2007} and the map is given by:
+  $E \mapsto \ip{\psi}{E\psi}$.
+\item given a probability measure $\mu$
+  mapping each event $E$
+  to a probability, is there is a \emph{unique} state $\psi$
+  such that $\mu(E)
+  =
+  \ip{\psi}{E\psi}$. In the conventional case, the answer is yes by
+  Gleason's
+  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
+\end{itemize}
 
-For the probability values, we will consider set-valued probability
-measures~\cite{Artstein1972,PuriRalescu1983}, in particular $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $,
-where impossible is a singleton set,$\left\{ 0\right\} $, and possible
-is an open interval, $\left(0,\infty\right)$.
+\amr{The rest is NO NO NO. We are inventing some other conditions on
+  probability measures that are not part of the framework !!! }
 

### 2016-04-22 prob.tex
plan

@@
   the uncountable and uncomputable interval $[0,1]$, we will consider
-  set-valued probablitity measures~\cite{Artstein1972,PuriRalescu1983}.
+  finite set-valued probablitity measures~\cite{Artstein1972,PuriRalescu1983}.
 \end{itemize}
@@
 
-\amr{The rest is NO NO NO. We are inventing some other conditions on
-  probability measures that are not part of the framework !!! }
+% If there may be more than one probability measure, we will discuss
+% whether we will keep using the Born rule (\ref{eq:Born}) or there
+% is another formula $\tilde{\mu}$ such that $\tilde{\mu}_{\psi}$
+% is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
 
-If there may be more than one probability measure, we will discuss
-whether we will keep using the Born rule (\ref{eq:Born}) or there
-is another formula $\tilde{\mu}$ such that $\tilde{\mu}_{\psi}$
-is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
+% Then, Gleason's theorem states given a probability measure $\mu$
+% there is a mixed state $\ket{\psi}$ such that $\mu=\mu_{\psi}$,
+% i.e., the Born rule is surjective\footnote{If we extend the domain of $\mu_{\psi}$ including the mixed states.}.
+% For any other formula~$\tilde{\mu}$, we can ask whether $\tilde{\mu}$
+% is surjective as well.
 
-Then, Gleason's theorem states given a probability measure $\mu$
-there is a mixed state $\ket{\psi}$ such that $\mu=\mu_{\psi}$,
-i.e., the Born rule is surjective\footnote{If we extend the domain of $\mu_{\psi}$ including the mixed states.}.
-For any other formula~$\tilde{\mu}$, we can ask whether $\tilde{\mu}$
-is surjective as well.
+% Obveriously, we don't want arbirarily assign a state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
+% with a proabability measure $\tilde{\mu}_{\psi}$, for example, assigning
+% every state to the same probability measure. We want $\tilde{\mu}_{\psi}$
+% satisfying the following properties with some physical meaning:
+% \begin{itemize}
+% \item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
+% where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
+% is impossible for $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $. 
+% \item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
+% $\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
+% map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
+% \end{itemize}
+% And the results can be summarized in the following table:\\
+% \center{ %
+% \begin{tabular}{>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}}
+% \hline 
+% State space $\Hilb$  & Probability values  & Is there a $\tilde{\mu}$ satisfying the given conditions?  & Is the $\tilde{\mu}$ surjective?\tabularnewline
+% \hline 
+% \hline 
+% $\C^{d}$ for $d\ge3$  & $\left[0,1\right]$  & Yes  & Yes\tabularnewline
+% \hline 
+% $\C^{d}$  & $\mathscr{L}_{2}$  & Yes  & No\tabularnewline
+% \hline 
+% $\ffzd{p^{2}}$for $d\ge3$ except $d=p=3$  & $\left[0,1\right]$  & No  & \tabularnewline
+% \hline 
+% $\ffzd{p^{2}}$  & $\mathscr{L}_{2}$  & Yes & No\tabularnewline
+% \hline 
+% \end{tabular}}
 
-Obveriously, we don't want arbirarily assign a state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
-with a proabability measure $\tilde{\mu}_{\psi}$, for example, assigning
-every state to the same probability measure. We want $\tilde{\mu}_{\psi}$
-satisfying the following properties with some physical meaning:
-\begin{itemize}
-\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
-where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
-is impossible for $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $. 
-\item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
-$\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
-map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
-\end{itemize}
-And the results can be summarized in the following table:\\
-\center{ %
-\begin{tabular}{>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}}
-\hline 
-State space $\Hilb$  & Probability values  & Is there a $\tilde{\mu}$ satisfying the given conditions?  & Is the $\tilde{\mu}$ surjective?\tabularnewline
-\hline 
-\hline 
-$\C^{d}$ for $d\ge3$  & $\left[0,1\right]$  & Yes  & Yes\tabularnewline
-\hline 
-$\C^{d}$  & $\mathscr{L}_{2}$  & Yes  & No\tabularnewline
-\hline 
-$\ffzd{p^{2}}$for $d\ge3$ except $d=p=3$  & $\left[0,1\right]$  & No  & \tabularnewline
-\hline 
-$\ffzd{p^{2}}$  & $\mathscr{L}_{2}$  & Yes & No\tabularnewline
-\hline 
-\end{tabular}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{All Continuous or All Discrete}
+
+Before we turn to the main part of the paper, we quickly dismiss the
+possibility of having one but not the other of the discrete
+variations. Speficially, it is impossible to maintain the Hllbert
+space and have a finite set-valued probability measure and it is also
+impossible to have a vector space constructed over a finite field with
+a real-valued probability measure.
+
+%%%
+\subsection{HIlbert Space with Finite Set-Valued Probability Measure}
+
+%%%
+\subsection{Discrete Vector Space with Real-Valued Probability Measure}
 

### 2016-04-22 prob.tex
prob.tex \subsection{Plan} fix a typo...
prob.tex \subsection{HIlbert Space with Finite Set-Valued Probability Measure} updated...

@@
 \usepackage[all]{xy}
+\usepackage{amsmath}
 
@@
   mapping each event $E$
-  to a probability, is there is a \emph{unique} state $\psi$
+  to a probability, is there a \emph{unique} state $\psi$
   such that $\mu(E)
@@
 \subsection{HIlbert Space with Finite Set-Valued Probability Measure}
+
+In order to simplify the discussion, we will focus on $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $
+where impossible and possible means $\left\{ 0\right\} $ and $\left(0,1\right]$
+respectively while our result can be easily extend to other values
+with the form $\left\{ \left\{ 0\right\} ,\left(0,\frac{1}{n}\right],\ldots,\left(\frac{n-1}{n},1\right]\right\} $.
+
+Because $\mathscr{L}_{2}$ is a partition of $\left[0,1\right]$~\cite{Artin1991,Wechler1992,PurdomBrown1995,DummitFoote2004},
+there is a natural surjective map~$\iota:\left[0,1\right]\rightarrow\mathscr{L}_{2}$
+defined by $\iota\left(0\right)=\textrm{impossible}$ and $\iota\left(x\right)=\textrm{possible}$
+for $x\ne0$. By applying $\iota$, we can define the corresponding
+Born rule~$\bar{\mu}$ by $\bar{\mu}_{\psi}(E)=\iota\left(\mu_{\psi}(E)\right)$,
+and the corresponding probability measure~$\hat{\mu}$ should satisfy: 
+\begin{itemize}
+\item $\hat{\mu}(\mathbb{1})=\textrm{possible}$, and 
+\item for a collection of pairwise orthogonal $E_{i}$, we have $\hat{\mu}(\sum_{i}E_{i})=\bigvee_{i}\hat{\mu}(E_{i})$,
+where $x\vee y=\textrm{impossible}$ if and only if $x=y=\textrm{impossible}$.
+\end{itemize}
+However, there is a $\mathscr{L}_{2}$-valued probability measure
+\[
+\hat{\mu}_{1}\left(E\right)=\begin{cases}
+\textrm{impossible} & \textrm{, if }E=\proj{+};\\
+\bar{\mu}_{0}(E) & \textrm{, otherwise.}
+\end{cases}
+\]
+such that $\hat{\mu}_{1}\ne\bar{\mu}_{\psi}$ for all mixed state
+$\ket{\psi}$.
 

### 2016-04-22 prob.tex
prob.tex "\subsection{Quantum Probability Spaces}" update comments...

@@
   $\mu(\sum_i E_i) = \sum_i \mu(E_i)$. 
+\end{itemize}
+\yutsung{There are three ways to charactize a quantum probability:
+\begin{enumerate}
+\item The above two conditions as Gleason did.
+\item As a linear functional on a {*} algebra.
+\item As induced by a state vector by the Born rule (\ref{eq:Born}).
+\end{enumerate}
+According to equation (37) in section 4 Quantum Probability in \cite{Maassen2010},
+the equalivance between 1. and 2. only hold for $d\ge3$ because of
+Gleason' theorem. Therefore, it seems hard to get insight for how
+to handle Gleason's theorem by {*}-algebra formulism...
 
-\yutsung{Claim: If $\sum_{i}\proj{\psi_{i}}$ is a projection, then
-they are orthogonal. \\
-Proof: If $\sum_{i}\proj{\psi_{i}}$ is a projection, then 
-\begin{eqnarray*}
-\ket{\psi_{j}} & = & \left(\sum_{i}\proj{\psi_{i}}\right)\ket{\psi_{j}}\\
- & = & \sum_{i}\ket{\psi_{i}}\ip{\psi_{i}}{\psi_{j}}
-\end{eqnarray*}
-Therefore, we have 
-\begin{eqnarray*}
-0 & = & \sum_{i\ne j}\ket{\psi_{i}}\ip{\psi_{i}}{\psi_{j}}
-\end{eqnarray*}
-} 
-\end{itemize}
+The equalivance between 2. and 3. can be found
+in Proposition 4.1.1 in \cite{Swart2013}. Notice that this proposition
+holds for every dimension... So it is not exactly Gleason's theorem,
+or at least not the main part of the Gleason's theorem...}
 

### 2016-04-23 prob.tex
prob.tex \subsection{Quantum Probability Spaces} Add examples...

@@
 \end{equation}
+We may verify our previous examples. When events are orthogonal and
+commutative, they can be measured together and their probability is
+additive: 
+\[
+\mu_{0}(\proj{0})+\mu_{0}(\proj{1})=\mu_{0}(\proj{+})+\mu_{0}(\proj{-})=1=\mu_{0}(\mathbb{1})\textrm{ .}
+\]
+On the other hand, $\proj{0}$ and $\proj{-}$ are non-commutative,
+and their total probabilities are not a probability of an event
+\begin{eqnarray*}
+\mu_{0}(\proj{0})+\mu_{0}(\proj{-}) & = & \frac{3}{2}>1\textrm{ .}
+\end{eqnarray*}
 Similarly to the classical case, this probability measure must satisfy:
@@
   =
-  \ip{\psi}{E\psi}$. In the conventional case, the answer is yes by
+  \ip{\psi}{E\psi}$? In the conventional case, the answer is yes by
   Gleason's
@@
 %%%
-\subsection{HIlbert Space with Finite Set-Valued Probability Measure}
+\subsection{Hilbert Space with Finite Set-Valued Probability Measure}
 

### 2016-04-23 prob.tex
prob.tex \subsection{Quantum Probability Spaces} updated...

@@
 \end{equation}
-We may verify our previous examples. When events are orthogonal and
-commutative, they can be measured together and their probability is
-additive: 
+which is called the Born rule~\cite{Born1984,Mermin2007}.\\
+\yutsung{One small thing is whether we should say
+\begin{quote}
+for each normalized state~$\ket{\psi}$...$\mu_{\psi}(E)=\ip{\psi}{E\psi}$
+\end{quote}
+as in Mermin~\cite{Mermin2007} and Maassen~\cite{Maassen2010}
+or
+\begin{quote}
+for each state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $...$\mu_{\psi}(E)=\frac{\ip{\psi}{E\psi}}{\ip{\psi}{\psi}}$
+\end{quote}
+as in Abramsky~\cite{DBLP:journals/corr/abs-0910-2393}. Personally,
+I prefer Abramsky's approach, because normalizing a state in DQT is
+messier than in CQT, and we have already considered states whose norm
+is not one in our previous paper~\cite{DQT2014}.}\\
+Our previous examples can be verified in terms of $\mu_{\psi}$. Because
+$\proj{0}$ and $\proj{-}$ are non-commutative, their total probabilities
+are not a probability of an event
+\begin{eqnarray*}
+\mu_{0}(\proj{0})+\mu_{0}(\proj{-}) & = & \frac{3}{2}>1\textrm{ .}
+\end{eqnarray*}
+When events are orthogonal, i.e., commutative, they can be measured
+together and their probability is additive: 
 \[
@@
 \]
-On the other hand, $\proj{0}$ and $\proj{-}$ are non-commutative,
-and their total probabilities are not a probability of an event
-\begin{eqnarray*}
-\mu_{0}(\proj{0})+\mu_{0}(\proj{-}) & = & \frac{3}{2}>1\textrm{ .}
-\end{eqnarray*}
-Similarly to the classical case, this probability measure must satisfy:
+Similarly to the classical case, the total probability is one and
+the orthogonal additivity can be summarized into the following two
+rules:
 \begin{itemize}
 \item $\mu(\mathbb{1})=1$, and 
-\item for a collection of pairwise orthogonal $E_i$, we have
-  $\mu(\sum_i E_i) = \sum_i \mu(E_i)$. 
+\item for a collection of pairwise orthogonal $E_{i}$, we have $\mu(\sum_{i}E_{i})=\sum_{i}\mu(E_{i})$.
 \end{itemize}
+These two conditions define quantum probability measures. Recall that
+the Born rule (\ref{eq:Born}) induces a probability measure from
+a state. Naturally, we may ask: is every probability measure induced
+from a state by the Born rule? The answer is yes by Gleason's theorem
+when the dimension~$\ge3$~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
+
 \yutsung{There are three ways to charactize a quantum probability:

### 2016-04-23 prob.tex
moved set valued to classical

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Probability Spaces}
+\section{Classical Probability Spaces}
 
-%%%%%
-\subsection{Classical Probability Spaces}
-
-Probability
-theory~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
-is defined using the notions of a \emph{sample space} $\Omega$, a
-space of \emph{events}~$\events$, and a \emph{probability
+A \emph{probability
+  space}~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
+collects necessary conditions for reasoning coherently about
+collections of uncertain events. It consists of a \emph{sample space}
+$\Omega$, a space of \emph{events}~$\events$, and a \emph{probability
   measure}~$\pmeas$. In this paper, we will only consider
-\emph{finite} sample spaces: we therefore define a sample space
-$\Omega$ as an arbitrary non-empty finite set, the space of events
-$\events$ as $2^\Omega$, the powerset of $\Omega$, and the \emph{probability
-measure} as a function $\pmeas : \events \rightarrow [0,1]$ such that:
+\emph{finite} sets of events: we therefore define a sample space
+$\Omega$ as an arbitrary non-empty finite set and the space of events
+$\events$ as $2^\Omega$, the powerset of $\Omega$. Given the set of
+events $\events$, the \emph{probability measure} is a function
+$\pmeas : \events \rightarrow [0,1]$ such that:
 \begin{itemize}
 \item $\pmeas(\Omega) = 1$, and 
-\item for a collection of pairwise disjoint events $E_i$, the probability
-measures are additive $\pmeas(\bigcup E_i) = \sum \pmeas(E_i)$. 
+\item for a collection $E_i$,  of pairwise disjoint events, 
+  $\pmeas(\bigcup E_i) = \sum \pmeas(E_i)$.
 \end{itemize}
 
-\emph{Example of a problem on a finite sample space} (Two coin experiment)
-Consider an experiment that tosses two coins. We have four possible outcomes that constitute the
-  sample space $\Omega = \{ HH, HT, TH, TT \}$. The event that the
-  first coin is ``heads'' is $\{ HH, HT \}$; the event that the two
-  coins land on opposite sides is $\{ HT, TH \}$; the event that at
-  least one coin is tails is $\{ HT, TH, TT\}$. Depending on the
-  assumptions regarding the coins, we can define several probability
+\begin{example}[Two-coin probability space]
+  Consider an experiment that tosses two coins. We have four possible
+  outcomes that constitute the sample space
+  $\Omega = \{ HH, HT, TH, TT \}$. The event that the first coin is
+  ``heads'' is $\{ HH, HT \}$; the event that the two coins land on
+  opposite sides is $\{ HT, TH \}$; the event that at least one coin
+  is tails is $\{ HT, TH, TT\}$. Depending on the assumptions
+  regarding the coins, we can define several probability
   measures. Here is a possible one:
@@
 \end{array}\]
-Note that the probability measure for disjoint events such as $\{ HT \}$ and
-$\{ TH \}$ do indeed add.
+The assignment satisfies the two constraints for probability measures:
+the probability of the entire sample space is 1, and the probability
+of every collection of disjoint events (e.g.,
+$\{ HT \} \cup \{ TH \}$) is the sum of the individual probabilities.
+\end{example}
 
-%%%%%
-\subsection{Quantum Probability Spaces}
+In a strict computational or experimental setting, one may question
+the reliance of the definition of probability space on the uncountable
+and uncomputable real interval $[0,1]$. This interval includes numbers
+like $0.h_1h_2h_3\ldots$ where $h_i$ is 1 or 0 depending on whether
+Turing machine $M_i$ halts or not. Such numbers cannot be
+computed. This interval also includes numbers like $\frac{\pi}{4}$
+which can be computed but with increasingly large resources as the
+precision increases. Therefore it is more appropriate in such
+situations to consider probability measures mapping events to a finite
+set of elements computable with a fixed set of
+resources~\cite{Artin1991,Wechler1992,PurdomBrown1995,DummitFoote2004}. The
+simplest such set, and the one we will consider exclusively in this
+paper, is the set
+$\mathscr{L}_{2}=\left\{
+  \textrm{impossible},\textrm{possible}\right\}$
+together with the operation $\vee$ where
+$x \vee y=\textrm{impossible}$ if and only if
+$x=y=\textrm{impossible}$. In relation to the first definition, one
+can interpret impossible as the closed interval $[0]$, possible as the
+open interval $(0,1]$, and $\vee$ as the union of intervals. The
+definition of a probability measure in this case is modifed as being a
+function $\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
+\begin{itemize}
+\item $\pmeas(\Omega) = \textrm{possible}$, and 
+\item for a collection $E_i$,  of pairwise disjoint events, $\pmeas(\bigcup E_i) = \bigvee \pmeas(E_i)$.
+\end{itemize}
+
+\begin{example}[Two-coin probability space with finite set-valued
+  probability measure.] Under the new set-valued requirement, the
+  probability measure in the first example becomes:
+\[\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) &=& \textrm{impossible} \\
+\pmeas(\{ HH \}) &=& \textrm{possible} \\
+\pmeas(\{ HT \}) &=& \textrm{impossible} \\
+\pmeas(\{ TH \}) &=& \textrm{possible} \\
+\pmeas(\{ TT \}) &=& \textrm{impossible} \\
+\pmeas(\{  HH, HT \}) &=& \textrm{possible} \\
+\pmeas(\{  HH, TH \}) &=& \textrm{possible} \\
+\pmeas(\{  HH , TT \}) &=& \textrm{possible} \\
+\end{array} & \begin{array}{rcl}
+\pmeas(\{  HT, TH \}) &=& \textrm{possible} \\
+\pmeas(\{  HT , TT \}) &=& \textrm{impossible} \\
+\pmeas(\{  TH , TT \}) &=& \textrm{possible} \\
+\pmeas(\{  HH, HT, TH \}) &=& \textrm{possible} \\
+\pmeas(\{  HH, HT, TT \}) &=& \textrm{possible} \\
+\pmeas(\{  HH, TH, TT \}) &=& \textrm{possible} \\
+\pmeas(\{  HT, TH, TT \}) &=& \textrm{possible} \\
+\pmeas(\{  HH, HT, TH, TT \}) &=& \textrm{possible} 
+\end{array}
+\end{array}\]
+\end{example}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Quantum Probability Spaces}
 
@@
 
-In order to simplify the discussion, we will focus on $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $
-where impossible and possible means $\left\{ 0\right\} $ and $\left(0,1\right]$
-respectively while our result can be easily extend to other values
-with the form $\left\{ \left\{ 0\right\} ,\left(0,\frac{1}{n}\right],\ldots,\left(\frac{n-1}{n},1\right]\right\} $.
-
-Because $\mathscr{L}_{2}$ is a partition of $\left[0,1\right]$~\cite{Artin1991,Wechler1992,PurdomBrown1995,DummitFoote2004},
-there is a natural surjective map~$\iota:\left[0,1\right]\rightarrow\mathscr{L}_{2}$
-defined by $\iota\left(0\right)=\textrm{impossible}$ and $\iota\left(x\right)=\textrm{possible}$
-for $x\ne0$. By applying $\iota$, we can define the corresponding
-Born rule~$\bar{\mu}$ by $\bar{\mu}_{\psi}(E)=\iota\left(\mu_{\psi}(E)\right)$,
-and the corresponding probability measure~$\hat{\mu}$ should satisfy: 
-\begin{itemize}
-\item $\hat{\mu}(\mathbb{1})=\textrm{possible}$, and 
-\item for a collection of pairwise orthogonal $E_{i}$, we have $\hat{\mu}(\sum_{i}E_{i})=\bigvee_{i}\hat{\mu}(E_{i})$,
-where $x\vee y=\textrm{impossible}$ if and only if $x=y=\textrm{impossible}$.
-\end{itemize}
 However, there is a $\mathscr{L}_{2}$-valued probability measure

### 2016-04-24 prob.tex
prob.tex \section{Quantum Probability Spaces} fix a typo(?)
prob.tex "Classical Probability Spaces" Fix citation and math symbols(?)

@@
 set of elements computable with a fixed set of
-resources~\cite{Artin1991,Wechler1992,PurdomBrown1995,DummitFoote2004}. The
+resources~\cite{Artstein1972,PuriRalescu1983}. The
 simplest such set, and the one we will consider exclusively in this
@@
 $x=y=\textrm{impossible}$. In relation to the first definition, one
-can interpret impossible as the closed interval $[0]$, possible as the
-open interval $(0,1]$, and $\vee$ as the union of intervals. The
+can interpret impossible as the closed interval $[0,0]$, possible as the
+open interval $(0,1]$, and $\vee$ as the addition of intervals. The
 definition of a probability measure in this case is modifed as being a
@@
 from a state by the Born rule? The answer is yes by Gleason's theorem
-when the dimension~$\ge3$~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
+when the dimension~$\ge3$ and extend the domain of the Born rule
+to mixed state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
 

### 2016-04-24 prob.tex
prob.tex \section{Quantum Probability Spaces} update comments...

@@
 
-The equalivance between 2. and 3. can be found
-in Proposition 4.1.1 in \cite{Swart2013}. Notice that this proposition
-holds for every dimension... So it is not exactly Gleason's theorem,
-or at least not the main part of the Gleason's theorem...}
+The equalivance between 2. and 3. can be found in Proposition 4.1.1
+in \cite{Swart2013}. Here, the Born rule~$\mu_{\psi}(E)$ is replaced
+by a faithful pseudotrace $\tau$ and $\mu_{\psi}(E)=\tau\left(\proj{\psi}E\right)$.
+The faithful pseudotrace is defined in section 5.2 Decomposition of
+algebra with a list of conditions. The problem is:
+\begin{itemize}
+\item Lemma 5.2.1 proved there exists a faith pseudotrace, but said nothing
+about uniqueness. Therefore, these conditions may not uniquely determine
+the Born rule?
+\item We don't formulate thing in algrebra... So although we may have an
+analog or something, we cannot quite sure our conditions will be exactly
+the same as theirs. 
+\end{itemize}
+If we admit the above, then the condition (a) to (c) and $\tau\left(AB\right)=\tau\left(BA\right)$
+implies 
+\begin{itemize}
+\item Our map $\tilde{\mu}:\Hilb\rightarrow\qevents\rightarrow[0,1]$ should
+satisfy $\tilde{\mu}_{\psi}$ is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
+\end{itemize}
+The condition (a) and (d) implies
+\begin{itemize}
+\item Our map $\tilde{\mu}$ satisfy $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
+where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
+is impossible for $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $. 
+\end{itemize}
+$\tau\left(AB\right)=\tau\left(BA\right)$ also implies
+\begin{itemize}
+\item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
+$\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
+map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
+\end{itemize}
+Besides, the condition (a) also gives the probability of mixed states
+form pure states... OK... it seems that I know what I am going to
+type for DQT, but I think I need to sort them out before type them...}
 

### 2016-04-24 prob.tex
prob.tex \section{Quantum Probability Spaces} update...

@@
 
-Consider the two-qubit Hilbert space with computational basis
+Consider the one-qubit Hilbert space with computational basis
 $\ket{0}$ and $\ket{1}$ and states:
@@
 \]
-Each event is interpreted as a possible post post-measurement state of
+Each event is interpreted as a possible post-measurement state of
 a quantum system as follows: given some arbitrary current quantum state
@@
 
-Irrespective of the current state $\ket{\psi}$ and
-irrespective of the particular experiment, the probability of event
-$\mathbb{0}$ will always be 0 (it is an impossible event) and the
-probability of event $\mathbb{1}$ will always be 1 (it is a certain
-event). The probabilities attached to other events will depend on the
-particular state in question. If the state is $\ket{0}$, the
-probability of event $\proj{0}$ is 1; the probability of event
-$\proj{1}$ is 0; the probability of event $\proj{\ps}$ is
-$\frac{1}{2}$; and the probability of event $\proj{\ms}$ is
-$\frac{1}{2}$. If the state is $\ket{\ps}$, the probability of each
-event $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$; the
-probability of event $\proj{\ps}$ is 1; and the probability of event
-$\proj{\ms}$ is 0.
+In classical probability space, two particular coins can define a
+probability measure on every event. Similarly, a quantum system can
+define a quantum probability measure on its event. The difference
+is that only orthogonal events can test together. For example, asking
+whether event~$\mathbb{1}$ occurs is the same as asking whether
+event~$\proj{0}$ or event~$\proj{1}$ occurs simultaniously. However,
+we can never ask whether event~$\proj{0}$ or event~$\proj{-}$
+occurs simultaniously. Similarly to the classical case, a \emph{quantum
+probability space}~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}
+can be summarized into the following two rules\footnote{Recently, people extend the domain of $\mu$ to all operators~$\mathcal{A}$
+on $\Hilb$ and consider $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
+When an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$
+is the expectation value of $A$. We does not take this approach because
+we want to focus only on probability. }: 
+\begin{itemize}
+\item $\mu(\mathbb{1})=1$, and 
+\item for a collection of pairwise orthogonal $E_{i}$, we have $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$. 
+\end{itemize}
+\begin{example}{[}One-qubit Hilbert space{]} Consider an experiment
+that with a qubit. The events are discribed previously. Depending on
+the systems, we can define different quantum probability measures.
+Here is a possible one: 
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\mu_{0}\left(\mathbb{0}\right) & = & 0\\
+\mu_{0}\left(\proj{0}\right) & = & 1\\
+\mu_{0}\left(\proj{1}\right) & = & 0\\
+ & \vdots
+\end{array} & \begin{array}{rcl}
+\mu_{0}\left(\mathbb{1}\right) & = & 1\\
+\mu_{0}\left(\proj{\ps}\right) & = & 1/2\\
+\mu_{0}\left(\proj{\ms}\right) & = & 1/2\\
+ & \vdots
+\end{array}\end{array}
+\]
+The assignment satisfies the two constraints for quantum probability
+measures: the probability of $\mathbb{1}$ is 1, and the probability
+of every summation of orthogonal events (e.g., $\proj{0}+\proj{1}$)
+is the sum of the individual probabilities. \end{example}
 
@@
 is not one in our previous paper~\cite{DQT2014}.}\\
-Our previous examples can be verified in terms of $\mu_{\psi}$. Because
-$\proj{0}$ and $\proj{-}$ are non-commutative, their total probabilities
-are not a probability of an event
-\begin{eqnarray*}
-\mu_{0}(\proj{0})+\mu_{0}(\proj{-}) & = & \frac{3}{2}>1\textrm{ .}
-\end{eqnarray*}
-When events are orthogonal, i.e., commutative, they can be measured
-together and their probability is additive: 
-\[
-\mu_{0}(\proj{0})+\mu_{0}(\proj{1})=\mu_{0}(\proj{+})+\mu_{0}(\proj{-})=1=\mu_{0}(\mathbb{1})\textrm{ .}
-\]
-Similarly to the classical case, the total probability is one and
-the orthogonal additivity can be summarized into the following two
-rules:
-\begin{itemize}
-\item $\mu(\mathbb{1})=1$, and 
-\item for a collection of pairwise orthogonal $E_{i}$, we have $\mu(\sum_{i}E_{i})=\sum_{i}\mu(E_{i})$.
-\end{itemize}
 These two conditions define quantum probability measures. Recall that

### 2016-04-25 prob.tex
prob.tex \section{Quantum Probability Spaces} updated...

@@
 \newcommand{\ff}[1]{\mathbb{F}_{#1}}
+\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
 
@@
 
-We now formalize a \emph{quantum probability space} as follows~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}.
-We first assume an ambient Hilbert space~$\Hilb$ and define the
-set of events $\qevents$ as all \emph{projections} on~$\Hilb$.
-Each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
+Although it seems that we need an infinite long table to specify the
+quantum probability measure~$\mu_{0}$, our $\mu_{0}$ is actually
+given by a simple formula~$\melement{0}{E}$. In general, Born discovered
+each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
 induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
-on the space of events defined for any event $E\in\qevents$ as follows\footnote{Recently, people extend the domain of $\mu_{\psi}$ to all operators~$\mathcal{A}$
-on $\Hilb$ and consider $\mu_{\psi}:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
-When an operator $A\in\mathcal{A}$ is Hermitian, $\mu_{\psi}\left(A\right)$
-is the expectation value of $A$. We does not take this approach because
-we want to focus only on probability. }: 
+on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
 \begin{equation}
-\mu_{\psi}(E)= \ip{\psi}{E\psi} \label{eq:Born}
+\mu_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
 \end{equation}
-which is called the Born rule~\cite{Born1984,Mermin2007}.\\
-\yutsung{One small thing is whether we should say
-\begin{quote}
-for each normalized state~$\ket{\psi}$...$\mu_{\psi}(E)=\ip{\psi}{E\psi}$
-\end{quote}
-as in Mermin~\cite{Mermin2007} and Maassen~\cite{Maassen2010}
-or
-\begin{quote}
-for each state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $...$\mu_{\psi}(E)=\frac{\ip{\psi}{E\psi}}{\ip{\psi}{\psi}}$
-\end{quote}
-as in Abramsky~\cite{DBLP:journals/corr/abs-0910-2393}. Personally,
-I prefer Abramsky's approach, because normalizing a state in DQT is
-messier than in CQT, and we have already considered states whose norm
-is not one in our previous paper~\cite{DQT2014}.}\\
-These two conditions define quantum probability measures. Recall that
-the Born rule (\ref{eq:Born}) induces a probability measure from
-a state. Naturally, we may ask: is every probability measure induced
-from a state by the Born rule? The answer is yes by Gleason's theorem
-when the dimension~$\ge3$ and extend the domain of the Born rule
-to mixed state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
+Naturally, we may ask: is every probability measure induced from a
+state by the Born rule? The answer is yes by Gleason's theorem when
+the dimension~$\ge3$ and extend the domain of the Born rule to mixed
+state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
 

### 2016-04-25 prob.tex
prob.tex \section{Quantum Probability Spaces} updated?

@@
 \newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
+\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
 
@@
 each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
-induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
+induces a probability measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$
 on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
 \begin{equation}
-\mu_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
+\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
 \end{equation}
+The Born rule satisfies the following properties:
+\begin{itemize}
+\item It can be extend to mixed states. Given a mixed state represented
+by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
+where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
+the Born rule can be extended to $\rho$ by 
+\begin{eqnarray}
+\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\end{eqnarray}
+Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
+is a classical probability space. Therefore, when we discretize the
+Hilbert space later, we may need to discretize this probability space
+as well.\yutsung{Check!!!}
+\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
+\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
+\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
+$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
+\end{itemize}
+\yutsung{...I think I need to check these properties identify an
+unique Born rule in CQT or something...}
+
 Naturally, we may ask: is every probability measure induced from a

### 2016-04-25 prob.tex
clean up first section

@@
 \usepackage{amsmath}
+\usepackage{wesa}
+\usepackage[T1]{fontenc}
 
@@
 \newtheorem{example}{Example}
+\newtheorem{definition}{Definition}
 \newcommand{\events}{\ensuremath{\mathcal{E}}}
@@
 \newcommand{\ms}{\texttt{-}}
+\newcommand{\poss}{{\mbox{\wesa{possible}}}}
+\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
 
@@
   space}~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
-collects necessary conditions for reasoning coherently about
+specifies the necessary conditions for reasoning coherently about
 collections of uncertain events. It consists of a \emph{sample space}
@@
 $\events$ as $2^\Omega$, the powerset of $\Omega$. Given the set of
-events $\events$, the \emph{probability measure} is a function
+events $\events$, a \emph{probability measure} is a function
 $\pmeas : \events \rightarrow [0,1]$ such that:
@@
   outcomes that constitute the sample space
-  $\Omega = \{ HH, HT, TH, TT \}$. The event that the first coin is
-  ``heads'' is $\{ HH, HT \}$; the event that the two coins land on
-  opposite sides is $\{ HT, TH \}$; the event that at least one coin
-  is tails is $\{ HT, TH, TT\}$. Depending on the assumptions
-  regarding the coins, we can define several probability
-  measures. Here is a possible one:
+  $\Omega = \{ HH, HT, TH, TT \}$. There are 16 total events including
+  for example the event $\{ HH, HT \}$ that the first coin is
+  ``heads,'' the event $\{ HT, TH \}$ that the two coins land on
+  opposite sides, and the event $\{ HT, TH, TT\}$ that at least one
+  coin is tails. Here is a possible probability measure for these
+  events:
 \[\begin{array}{c@{\qquad\qquad}c}
@@
 of every collection of disjoint events (e.g.,
-$\{ HT \} \cup \{ TH \}$) is the sum of the individual probabilities.
+$\{ HT, TH \} = \{ HT \} \cup \{ TH \}$) is the sum of the individual
+probabilities. The probability of collections of non-disjoint events
+(e.g., $\{ HT, TH, TT \} = \{ HT, TH \} \cup \{ TH , TT \}$) may add
+to something different than the probabilities of the individual
+events. It is useful to think that this probability measure is
+completely induced by the two coins and their characteristics in the
+sense that each pair of coins induces a measure, and each measure must
+correspond to some pair of coins.
 \end{example}
@@
 computed. This interval also includes numbers like $\frac{\pi}{4}$
-which can be computed but with increasingly large resources as the
-precision increases. Therefore it is more appropriate in such
-situations to consider probability measures mapping events to a finite
-set of elements computable with a fixed set of
-resources~\cite{Artstein1972,PuriRalescu1983}. The
-simplest such set, and the one we will consider exclusively in this
-paper, is the set
-$\mathscr{L}_{2}=\left\{
-  \textrm{impossible},\textrm{possible}\right\}$
-together with the operation $\vee$ where
-$x \vee y=\textrm{impossible}$ if and only if
-$x=y=\textrm{impossible}$. In relation to the first definition, one
-can interpret impossible as the closed interval $[0,0]$, possible as the
-open interval $(0,1]$, and $\vee$ as the addition of intervals. The
-definition of a probability measure in this case is modifed as being a
-function $\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
+which can only be computed with increasingly large resources as the
+precision increases. Therefore, in a resource-aware setting, it is
+more appropriate to consider probability measures that map events to a
+finite set of elements computable with a fixed set of
+resources~\cite{Artstein1972,PuriRalescu1983}. The simplest such set,
+and the one we will consider exclusively in this paper, is the set
+$\mathscr{L}_{2}=\left\{ \imposs, \poss\right\}$ together with the
+operation $\vee$ where $x \vee y=\imposs$ if and only if
+$x=y=\imposs$. In relation to the first definition, one can interpret
+\imposs\ as the closed interval $[0,0]$, \poss\ as the open interval
+$(0,1]$, and $\vee$ as the addition of intervals. The definition of a
+probability measure in this case is modified as being a function
+$\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
 \begin{itemize}
-\item $\pmeas(\Omega) = \textrm{possible}$, and 
+\item $\pmeas(\Omega) = \poss$, and
 \item for a collection $E_i$,  of pairwise disjoint events, $\pmeas(\bigcup E_i) = \bigvee \pmeas(E_i)$.
@@
 \begin{example}[Two-coin probability space with finite set-valued
-  probability measure.] Under the new set-valued requirement, the
+  probability measure] Under the new set-valued requirement, the
   probability measure in the first example becomes:
@@
 \begin{array}{rcl}
-\pmeas(\emptyset) &=& \textrm{impossible} \\
-\pmeas(\{ HH \}) &=& \textrm{possible} \\
-\pmeas(\{ HT \}) &=& \textrm{impossible} \\
-\pmeas(\{ TH \}) &=& \textrm{possible} \\
-\pmeas(\{ TT \}) &=& \textrm{impossible} \\
-\pmeas(\{  HH, HT \}) &=& \textrm{possible} \\
-\pmeas(\{  HH, TH \}) &=& \textrm{possible} \\
-\pmeas(\{  HH , TT \}) &=& \textrm{possible} \\
+\pmeas(\emptyset) &=& \imposs \\
+\pmeas(\{ HH \}) &=& \poss \\
+\pmeas(\{ HT \}) &=& \imposs \\
+\pmeas(\{ TH \}) &=& \poss \\
+\pmeas(\{ TT \}) &=& \imposs \\
+\pmeas(\{  HH, HT \}) &=& \poss \\
+\pmeas(\{  HH, TH \}) &=& \poss \\
+\pmeas(\{  HH , TT \}) &=& \poss \\
 \end{array} & \begin{array}{rcl}
-\pmeas(\{  HT, TH \}) &=& \textrm{possible} \\
-\pmeas(\{  HT , TT \}) &=& \textrm{impossible} \\
-\pmeas(\{  TH , TT \}) &=& \textrm{possible} \\
-\pmeas(\{  HH, HT, TH \}) &=& \textrm{possible} \\
-\pmeas(\{  HH, HT, TT \}) &=& \textrm{possible} \\
-\pmeas(\{  HH, TH, TT \}) &=& \textrm{possible} \\
-\pmeas(\{  HT, TH, TT \}) &=& \textrm{possible} \\
-\pmeas(\{  HH, HT, TH, TT \}) &=& \textrm{possible} 
+\pmeas(\{  HT, TH \}) &=& \poss \\
+\pmeas(\{  HT , TT \}) &=& \imposs \\
+\pmeas(\{  TH , TT \}) &=& \poss \\
+\pmeas(\{  HH, HT, TH \}) &=& \poss \\
+\pmeas(\{  HH, HT, TT \}) &=& \poss \\
+\pmeas(\{  HH, TH, TT \}) &=& \poss \\
+\pmeas(\{  HT, TH, TT \}) &=& \poss \\
+\pmeas(\{  HH, HT, TH, TT \}) &=& \poss 
 \end{array}
@@
 The mathematical framework above assumes that one has complete
-knowledge of the events and their relationships. But even in many
-classical situations, the structure of the event space is only
+knowledge of the events and their relationships. However, in many
+practical situations, the structure of the event space is only
 partially known and the precise dependence of two events on each other
-cannot be determined with certainty. In the quantum case, this partial
-knowledge is compounded by the fact that not all quantum events can be
-observed simultaneously.  Indeed, in the quantum world, there are
-non-commuting events which cannot even happen simultaneously. To
-accommodate these more complex situations, we abandon the
-sample space~$\Omega$ and define and reason directly about
-events. A quantum probability space consist of just two
-components: a set of events $\qevents$ and a probability measure
+cannot, a priori, be determined with certainty. In the quantum case,
+this partial knowledge is compounded by the fact that there exist
+non-commuting events which cannot happen simultaneously. To
+accommodate these more complex situations, we abandon the sample
+space~$\Omega$ and reason directly about events. A quantum probability
+space therefore consist of just two components: a set of events
+$\qevents$ and a probability measure
 $\mu : \qevents \rightarrow [0,1]$. We give an example before giving
@@
 
-Consider the one-qubit Hilbert space with computational basis
-$\ket{0}$ and $\ket{1}$ and states:
-\[
-\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}, \qquad\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.
-\]
-The set of events associated with this Hilbert space consists of all
-projections including the empty projection $\mathbb{0}$ and the unit
-projection $\mathbb{1} = \proj{0}+\proj{1}$:
-\[ 
-\{ \mathbb{0}, \proj{0}, \proj{1}, \proj{\ps}, \proj{\ms}, \ldots, \mathbb{1}\}
-\]
-Each event is interpreted as a possible post-measurement state of
-a quantum system as follows: given some arbitrary current quantum state
-$\ket{\psi}$ to be measured, the event $\proj{0}$ states that the
-post-measurement state will be $\ket{0}$; the event $\proj{1}$ states
-that the post-measurement state will be $\ket{1}$; the event
-$\proj{\ps}$ states that the post-measurement state will be
-$\ket{\ps}$; the event $\proj{\ms}$ states that the post-measurement
-state will be $\ket{\ms}$; the event $\mathbb{1}$ states that the
-post-measurement state will be a linear combination of $\ket{0}$ and
-$\ket{1}$; and the event $\mathbb{0}$ states that the post-measurement
-state will be the empty state.
+\begin{example}[One-qubit quantum probability space] 
+  Consider a one-qubit Hilbert space with states
+  $\alpha \ket{0} + \beta \ket{1}$ such that
+  $|\alpha|^2 + |\beta|^2 = 1$. The set of events associated with this
+  Hilbert space consists of the empty projection~$\mathbb{0}$ together 
+  with projection operators $\proj{\psi}$ for each state $\ket{\psi}$.
+  Each event is interpreted as a possible post-measurement state of a
+  quantum system in current state $\ket{\phi}$. For example, the event
+  $\proj{0}$ indicates that the post-measurement state will
+  be~$\ket{0}$; the event $\proj{1}$ indicates that the
+  post-measurement state will be~$\ket{1}$; the event $\proj{\ps}$
+  where $\ket{\ps} = \frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$ indicates
+  that the post-measurement state will be $\ket{\ps}$; the event
+  $\mathbb{1} = \proj{0}+\proj{1}$ indicates that the post-measurement
+  state will be a linear combination of $\ket{0}$ and $\ket{1}$; and
+  the event $\mathbb{0}$ states that the post-measurement state will
+  be the empty state. As in the classical case, a probability measure
+  maps events to $[0,1]$: here is a partial specification of a
+  possible measure:
+\[\begin{array}{rcl}
+\mu\left(\mathbb{0}\right) = 0, \quad
+\mu\left(\mathbb{1}\right) =  1, \quad
+\mu\left(\proj{0}\right) = 1, \quad
+\mu\left(\proj{1}\right) = 0, \quad
+\mu\left(\proj{\ps}\right) = 1/2, \ldots
+\end{array}\]
+Note that, similarly to the classical case, the probability of
+$\mathbb{1}$ is 1 and the probability of collections of orthogonal
+events (e.g., $\proj{0}+\proj{1}$) is the sum of the individual
+probabilities. In contrast, a collection of non-orthogonal events
+(e.g., $\proj{0}$ and $\proj{\ps}$) is not itself an event.
+In the classical example, we argued that each probability measure is
+uniquely determined by two actual coins. A similar (but much more
+subtle) argument is valid also in the quantum case. By postulates of
+quantum mechanics and Gleason's theorem, it turns out that for large
+enough quantum systems, each probability measure is uniquely
+determined by an actual quantum state.
+\end{example}
 
-In classical probability space, two particular coins can define a
-probability measure on every event. Similarly, a quantum system can
-define a quantum probability measure on its event. The difference
-is that only orthogonal events can test together. For example, asking
-whether event~$\mathbb{1}$ occurs is the same as asking whether
-event~$\proj{0}$ or event~$\proj{1}$ occurs simultaniously. However,
-we can never ask whether event~$\proj{0}$ or event~$\proj{-}$
-occurs simultaniously. Similarly to the classical case, a \emph{quantum
-probability space}~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}
-can be summarized into the following two rules\footnote{Recently, people extend the domain of $\mu$ to all operators~$\mathcal{A}$
-on $\Hilb$ and consider $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
-When an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$
-is the expectation value of $A$. We does not take this approach because
-we want to focus only on probability. }: 
+To properly explain the previous example and generalize to arbitrary
+quantum systems, we formally define a quantum probability space as
+follows.
+
+\begin{definition}[Quantum Probability Space~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}]
+  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
+  consists of a set of events $\events$ and a probability measure
+  $\mu$ such that:\footnote {It is possible to define a more general
+    space of events consisting of all operators~$\mathcal{A}$ on
+    $\Hilb$ and consider
+    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
+    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
+    the expectation value of $A$. We does not take this approach
+    because we want to focus only on probability. }
 \begin{itemize}
+\item The set of events contains the empty projection $\mathbb{0}$
+  together with projection operators $\proj{\psi}$ for each state
+  $\ket{\psi}$,
 \item $\mu(\mathbb{1})=1$, and 
-\item for a collection of pairwise orthogonal $E_{i}$, we have $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$. 
+\item for projections expressible as sums $\sum_{i}E_{i}$ of
+  necessarily orthogonal events $E_i$, we have
+  $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$.
 \end{itemize}
-\begin{example}{[}One-qubit Hilbert space{]} Consider an experiment
-that with a qubit. The events are discribed previously. Depending on
-the systems, we can define different quantum probability measures.
-Here is a possible one: 
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\mu_{0}\left(\mathbb{0}\right) & = & 0\\
-\mu_{0}\left(\proj{0}\right) & = & 1\\
-\mu_{0}\left(\proj{1}\right) & = & 0\\
- & \vdots
-\end{array} & \begin{array}{rcl}
-\mu_{0}\left(\mathbb{1}\right) & = & 1\\
-\mu_{0}\left(\proj{\ps}\right) & = & 1/2\\
-\mu_{0}\left(\proj{\ms}\right) & = & 1/2\\
- & \vdots
-\end{array}\end{array}
-\]
-The assignment satisfies the two constraints for quantum probability
-measures: the probability of $\mathbb{1}$ is 1, and the probability
-of every summation of orthogonal events (e.g., $\proj{0}+\proj{1}$)
-is the sum of the individual probabilities. \end{example}
+\end{definition}
+
+\newpage
+\amr{the rest needs cleaning up and perhaps does not even belong in
+  this section}
+
+Although it seems that we need an infinite
+long table to specify the quantum probability measure~$\mu$, our $\mu$
+is actually given by a simple formula~$\melement{0}{E}$. In general,
+Born discovered each quantum state
+$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $ induces a probability
+measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$ on the space of
+events defined for any event $E\in\qevents$ as
+follows~\cite{Born1984,Mermin2007}:
+\begin{equation}
+\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
+\end{equation}
+The Born rule satisfies the following properties:
+\begin{itemize}
+\item It can be extend to mixed states. Given a mixed state represented
+by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
+where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
+the Born rule can be extended to $\rho$ by 
+\begin{eqnarray}
+\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\end{eqnarray}
+Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
+is a classical probability space. Therefore, when we discretize the
+Hilbert space later, we may need to discretize this probability space
+as well.\yutsung{Check!!!}
+\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
+\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
+\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
+$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
+\end{itemize}
+\yutsung{...I think I need to check these properties identify an
+unique Born rule in CQT or something...}
 
@@
 Although it seems that we need an infinite long table to specify the
-quantum probability measure~$\mu_{0}$, our $\mu_{0}$ is actually
+quantum probability measure~$\mu$, our $\mu$ is actually
 given by a simple formula~$\melement{0}{E}$. In general, Born discovered
@@
 
-\yutsung{There are three ways to charactize a quantum probability: 
+\yutsung{There are three ways to characterize a quantum probability: 
 \begin{enumerate}
@@
 According to equation (37) in section 4 Quantum Probability in \cite{Maassen2010},
-the equalivance between 1. and 2. only hold for $d\ge3$ because of
+the equivalence between 1. and 2. only hold for $d\ge3$ because of
 Gleason' theorem. Therefore, it seems hard to get insight for how
-to handle Gleason's theorem by {*}-algebra formulism...
+to handle Gleason's theorem by {*}-algebra formalism...
 
-The equalivance between 2. and 3. can be found in Proposition 4.1.1
+The equivalence between 2. and 3. can be found in Proposition 4.1.1
 in \cite{Swart2013}. Here, the Born rule~$\mu_{\psi}(E)$ is replaced
@@
 the Born rule?
-\item We don't formulate thing in algrebra... So although we may have an
+\item We don't formulate thing in algebra... So although we may have an
 analog or something, we cannot quite sure our conditions will be exactly
@@
 where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
-is impossible for $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $. 
+is impossible for $\mathscr{L}_{2}=\left\{ \imposs,\poss\right\} $. 
 \end{itemize}
@@
 
+\amr{give example non-commuting events}
+
 %%%%%
@@
   the uncountable and uncomputable interval $[0,1]$, we will consider
-  finite set-valued probablitity measures~\cite{Artstein1972,PuriRalescu1983}.
+  finite set-valued probability measures~\cite{Artstein1972,PuriRalescu1983}.
 \end{itemize}
@@
 
-% Obveriously, we don't want arbirarily assign a state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
-% with a proabability measure $\tilde{\mu}_{\psi}$, for example, assigning
+% Obviously, we don't want arbitrarily assign a state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
+% with a probability measure $\tilde{\mu}_{\psi}$, for example, assigning
 % every state to the same probability measure. We want $\tilde{\mu}_{\psi}$
@@
 % where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
-% is impossible for $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $. 
+% is impossible for $\mathscr{L}_{2}=\left\{ \imposs,\poss\right\} $. 
 % \item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
@@
 possibility of having one but not the other of the discrete
-variations. Speficially, it is impossible to maintain the Hllbert
+variations. Specifically, it is impossible to maintain the Hilbert
 space and have a finite set-valued probability measure and it is also
@@
 \hat{\mu}_{1}\left(E\right)=\begin{cases}
-\textrm{impossible} & \textrm{, if }E=\proj{+};\\
-\bar{\mu}_{0}(E) & \textrm{, otherwise.}
+\imposs & \textrm{, if }E=\proj{+};\\
+\bar{\mu}(E) & \textrm{, otherwise.}
 \end{cases}

### 2016-04-25 prob.tex
measures

@@
 \usepackage{fullpage}
+\usepackage{url}
 \usepackage{bbm}
@@
 
-\theoremstyle{remark}
+\makeatletter
+\newtheoremstyle{indented}
+  {3pt}% space before
+  {3pt}% space after
+  {\addtolength{\@totalleftmargin}{3.5em}
+   \addtolength{\linewidth}{-3.5em}
+   \parshape 1 3.5em \linewidth}% body font
+  {}% indent
+  {\bfseries}% header font
+  {.}% punctuation
+  {.5em}% after theorem header
+  {}% header specification (empty for default)
+\makeatother
+\theoremstyle{indented}
+%% \theoremstyle{remark}
 \newtheorem{example}{Example}
@@
 \newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
+\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
 \newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
@@
 correspond to some pair of coins.
-\end{example}
+\qed\end{example}
 
@@
 \end{array}\]
-\end{example}
+\qed\end{example}
+
+We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
 
@@
 \mu\left(\proj{1}\right) = 0, \quad
-\mu\left(\proj{\ps}\right) = 1/2, \ldots
+\mu\left(\proj{\ps}\right) = 1/2, \quad \ldots
 \end{array}\]
@@
 determined by an actual quantum state.
-\end{example}
+\qed\end{example}
 
@@
   consists of a set of events $\events$ and a probability measure
-  $\mu$ such that:\footnote {It is possible to define a more general
-    space of events consisting of all operators~$\mathcal{A}$ on
-    $\Hilb$ and consider
+  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
+    possible to define a more general space of events consisting of
+    all operators~$\mathcal{A}$ on $\Hilb$ and consider
     $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
@@
 \begin{itemize}
-\item The set of events contains the empty projection $\mathbb{0}$
+\item The set of events consists of the empty projection $\mathbb{0}$
   together with projection operators $\proj{\psi}$ for each state
@@
 \end{itemize}
-\end{definition}
+\qed\end{definition}
+
+%%%%%
+\subsection{Quantum Probability Measures}
+
+For a given set of events $\events$, there are many possible
+probability measures $\mu : \events \rightarrow [0,1]$. The Born rule,
+a postulate of quantum mechanics, states that each quantum state
+$\ket{\phi}$ induces a probability measure $\mu_\phi$ as follows:
+\[ 
+\mu_\phi(E) = \ip{\phi}{E\phi}
+\]
+Conversely, Gleason's theorem states that given a probability measure
+$\mu$, there exist a quantum state $\ket{phi}$ that induces such a
+measure using the Born rule. The theorem is only valid in Hilbert
+spaces with dimension $d \geq 3$. It is instructive to study
+counterexamples in $d=2$, i.e., the case of a one-qubit
+system. Consider five states $\ket{\psi_0}$ to $\ket{\psi_4}$ that
+form five orthogonal bases $\{ \ket{\psi_0}, \ket{\psi_1} \}$,
+$\{ \ket{\psi_1}, \ket{\psi_2} \}$,
+$\{ \ket{\psi_2}, \ket{\psi_3} \}$,
+$\{ \ket{\psi_3}, \ket{\psi_4} \}$, and
+$\{ \ket{\psi_4}, \ket{\psi_0} \}$ and consider the probability
+measure defined as follows. For all $i \in \{0,1,2,3,4\}$, we have
+$\mu_X(\proj{\psi_i}) = 1/2$. For each orthogonal basis, the
+probability is 1 as desired and yet it is impossible to find a single
+quantum state that realizes such a probability
+measure (see \url{http://tph.tuwien.ac.at/~svozil/publ/2006-gleason.pdf})
 

### 2016-04-25 prob.tex
prob.tex several quick fix and comments...

@@
 which can only be computed with increasingly large resources as the
-precision increases. Therefore, in a resource-aware setting, it is
+precision increases. \\
+\yutsung{Check the meaning of the ``computing $\frac{\pi}{4}$'', because
+Bailey Borwein Plouffe formula can computing the $n$th binary digit of $\pi$ 
+using base 16 directly.}\\
+Therefore, in a resource-aware setting, it is
 more appropriate to consider probability measures that map events to a
@@
 $x=y=\imposs$. In relation to the first definition, one can interpret
-\imposs\ as the closed interval $[0,0]$, \poss\ as the open interval
+\imposs\ as the closed interval $[0,0]$, \poss\ as the half-open interval
 $(0,1]$, and $\vee$ as the addition of intervals. The definition of a
@@
   together with projection operators $\proj{\psi}$ for each state
-  $\ket{\psi}$,
+  $\ket{\psi}$,\\
+  \yutsung{and the sum of the orthogonal events recursively.}
 \item $\mu(\mathbb{1})=1$, and 
@@
 Conversely, Gleason's theorem states that given a probability measure
-$\mu$, there exist a quantum state $\ket{phi}$ that induces such a
+$\mu$, there exist a quantum state $\ket{\phi}$ that induces such a
 measure using the Born rule. The theorem is only valid in Hilbert
@@
 \amr{give example non-commuting events}
+
+\yutsung{Isn't $\proj{0}$ and $\proj{\ps}$ an example in the example of
+One-qubit quantum probability space.}
 

### 2016-04-25 prob.tex
prob.tex \subsection{Quantum Probability Measures} delete before typing

@@
 
-Although it seems that we need an infinite
-long table to specify the quantum probability measure~$\mu$, our $\mu$
-is actually given by a simple formula~$\melement{0}{E}$. In general,
-Born discovered each quantum state
-$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $ induces a probability
-measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$ on the space of
-events defined for any event $E\in\qevents$ as
-follows~\cite{Born1984,Mermin2007}:
-\begin{equation}
-\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
-\end{equation}
-The Born rule satisfies the following properties:
-\begin{itemize}
-\item It can be extend to mixed states. Given a mixed state represented
-by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
-where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
-the Born rule can be extended to $\rho$ by 
-\begin{eqnarray}
-\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
-\end{eqnarray}
-Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
-is a classical probability space. Therefore, when we discretize the
-Hilbert space later, we may need to discretize this probability space
-as well.\yutsung{Check!!!}
-\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
-\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
-\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
-$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
-\end{itemize}
-\yutsung{...I think I need to check these properties identify an
-unique Born rule in CQT or something...}
-
-% \begin{itemize}
-% \item Family I: $\proj{0}$, $\proj{1}$ 
-% \item Family II: $\proj{\ps}$, $\proj{\ms}$
-% \end{itemize}
-% In family I, all operators can be expressed as $\left\{ \lambda_{1}\proj{0}+\lambda_{2}\proj{1}~\middle|~\lambda_{1},\lambda_{2}\in\mathbb{C}\right\} $.
-% In order to identify projectors among them, we need to solve the following
-% two equations.
-% \begin{eqnarray*}
-% \lambda_{1}\proj{0}+\lambda_{2}\proj{1} & = & \left(\lambda_{1}\proj{0}+\lambda_{2}\proj{1}\right)^{*}=\lambda_{1}^{*}\proj{0}+\lambda_{2}^{*}\proj{1}\\
-% \lambda_{1}\proj{0}+\lambda_{2}\proj{1} & = & \left(\lambda_{1}\proj{0}+\lambda_{2}\proj{1}\right)^{2}=\lambda_{1}^{2}\proj{0}+\lambda_{2}^{2}\proj{1}
-% \end{eqnarray*}
-% Therefore, we actually have $\lambda_{1},\lambda_{2}\in\left\{ 0,1\right\} $,
-% and there are only four projections: $0$, $\proj{0}$, $\proj{1}$,
-% and $\mathbb{1}=\proj{0}+\proj{1}$. Then, $\mu_{\ket{\ps}}$ and
-% $\mu_{\ket{\ms}}$ of each projections are 
-% \[
-% \begin{array}{c@{\qquad\qquad}c}
-% \begin{array}{rcl}
-% \mu_{\ket{\ps}}(0) & = & 0\\
-% \mu_{\ket{\ps}}(\proj{0}) & = & 1/2\\
-% \mu_{\ket{\ps}}(\proj{1}) & = & 1/2\\
-% \mu_{\ket{\ps}}(\mathbb{1}) & = & 1
-% \end{array} & \begin{array}{rcl}
-% \mu_{\ket{\ms}}(0) & = & 0\\
-% \mu_{\ket{\ms}}(\proj{0}) & = & 1/2\\
-% \mu_{\ket{\ms}}(\proj{1}) & = & 1/2\\
-% \mu_{\ket{\ms}}(\mathbb{1}) & = & 1
-% \end{array}\end{array}
-% \]
-% Similarly, $\mu_{\ket{\ps}}$ and $\mu_{\ket{\ms}}$ gives two probability
-% for family II as well.
-% \[
-% \begin{array}{c@{\qquad\qquad}c}
-% \begin{array}{rcl}
-% \mu_{\ket{\ps}}(0) & = & 0\\
-% \mu_{\ket{\ps}}(\proj{+}) & = & 1\\
-% \mu_{\ket{\ps}}(\proj{\ms}) & = & 0\\
-% \mu_{\ket{\ps}}(\mathbb{1}) & = & 1
-% \end{array} & \begin{array}{rcl}
-% \mu_{\ket{\ms}}(0) & = & 0\\
-% \mu_{\ket{\ms}}(\proj{\ps}) & = & 0\\
-% \mu_{\ket{\ms}}(\proj{\ms}) & = & 1\\
-% \mu_{\ket{\ms}}(\mathbb{1}) & = & 1
-% \end{array}\end{array}
-% \]
-
 Although it seems that we need an infinite long table to specify the
@@
 Hilbert space later, we may need to discretize this probability space
-as well.\yutsung{Check!!!}
+as well.
 \item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
@@
 \end{itemize}
-\yutsung{...I think I need to check these properties identify an
-unique Born rule in CQT or something...}
 
@@
 state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
-
-\yutsung{There are three ways to characterize a quantum probability: 
-\begin{enumerate}
-\item The above two conditions as Gleason did. 
-\item As a linear functional on a {*} algebra. 
-\item As induced by a state vector by the Born rule (\ref{eq:Born}). 
-\end{enumerate}
-According to equation (37) in section 4 Quantum Probability in \cite{Maassen2010},
-the equivalence between 1. and 2. only hold for $d\ge3$ because of
-Gleason' theorem. Therefore, it seems hard to get insight for how
-to handle Gleason's theorem by {*}-algebra formalism...
-
-The equivalence between 2. and 3. can be found in Proposition 4.1.1
-in \cite{Swart2013}. Here, the Born rule~$\mu_{\psi}(E)$ is replaced
-by a faithful pseudotrace $\tau$ and $\mu_{\psi}(E)=\tau\left(\proj{\psi}E\right)$.
-The faithful pseudotrace is defined in section 5.2 Decomposition of
-algebra with a list of conditions. The problem is:
-\begin{itemize}
-\item Lemma 5.2.1 proved there exists a faith pseudotrace, but said nothing
-about uniqueness. Therefore, these conditions may not uniquely determine
-the Born rule?
-\item We don't formulate thing in algebra... So although we may have an
-analog or something, we cannot quite sure our conditions will be exactly
-the same as theirs. 
-\end{itemize}
-If we admit the above, then the condition (a) to (c) and $\tau\left(AB\right)=\tau\left(BA\right)$
-implies 
-\begin{itemize}
-\item Our map $\tilde{\mu}:\Hilb\rightarrow\qevents\rightarrow[0,1]$ should
-satisfy $\tilde{\mu}_{\psi}$ is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
-\end{itemize}
-The condition (a) and (d) implies
-\begin{itemize}
-\item Our map $\tilde{\mu}$ satisfy $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
-where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
-is impossible for $\mathscr{L}_{2}=\left\{ \imposs,\poss\right\} $. 
-\end{itemize}
-$\tau\left(AB\right)=\tau\left(BA\right)$ also implies
-\begin{itemize}
-\item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
-$\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
-map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
-\end{itemize}
-Besides, the condition (a) also gives the probability of mixed states
-form pure states... OK... it seems that I know what I am going to
-type for DQT, but I think I need to sort them out before type them...}
-
-% \yutsung{If we follow \cite{Maassen2010,Swart2013}, then we also
-% need 
-% \begin{itemize}
-% \item $\mu$ can be extended to a linear functional~$\mu:alg\left(\qevents\right)\rightarrow\mathbb{C}$,
-% where $alg\left(\qevents\right)$ is the minimal $*$-algebra generated
-% by $\qevents$.
-% \end{itemize}
-% Also, 
-% \begin{itemize}
-% \item for all $A\in\qevents$, we have $\mu(A^{*}A)\geq0$. 
-% \end{itemize}
-% should be 
-% \begin{itemize}
-% \item for all $A\in alg\left(\qevents\right)$, we have $\mu(A^{*}A)\geq0$. 
-% \end{itemize}
-% because we have $\mu(A^{*}A)=\mu(A^{2})=\mu(A)$ if $A$ is a projection.}\\
-
-% \yutsung{$\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
-% is the minimal $*$-algebra generated by $P_{1},P_{2},\ldots,P_{k}$,
-% but it contains all possible observables $P_{1},P_{2},\ldots,P_{k}$
-% can generate (and something more) not just projections. For example,
-% $2\mathbb{1}\in\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $.}\\
-
-% \yutsung{So $\mu_{\psi}$ maps the projections generated by $P_{1},P_{2},\ldots,P_{k}$
-% to $[0,1]$, and maps $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
-% to $\mathbb{C}$...}\\
 

### 2016-04-25 prob.tex
prob.tex Add a corollary, and a little bit proof...

@@
 \newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
+\theoremstyle{plain}
+\newtheorem{thm}{\protect\theoremname}
+\theoremstyle{plain}
+\newtheorem{cor}[thm]{Corollary}
 
@@
 state by the Born rule? The answer is yes by Gleason's theorem when
-the dimension~$\ge3$ and extend the domain of the Born rule to mixed
-state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
+the dimension~$\ge3$~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
+Furthermore, a simple corollary of Gleason's theorem can show the
+Born rule is the unique function satisfying conditions 1. to 3.
+\begin{cor}
+The Born rule is the unique function satisfying conditions 1. to 3.
+\end{cor}
+\begin{proof}
+Assume there is another function $\tilde{\mu}'$ such that $\tilde{\mu}'_{\rho}$
+is a quantum probability measure for all mixed state~$\rho$. We
+are going to prove $\tilde{\mu}'=\tilde{\mu}$.
+
+Fix a pure normalized state $\phi$, $\tilde{\mu}'_{\phi}$ is a quantum
+probability measure by condition 2. By Gleason's theorem, there is
+a mixed state ~$\rho'$, such that $\tilde{\mu}'_{\phi}\left(E\right)=\Tr\left(\rho'E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\psi_{j}}\left(E\right)$
+for all event $E$.
+
+Consider the event $E'=\mathbb{1}-\proj{\phi}$, we have 
+\begin{eqnarray*}
+0 & \overset{\textrm{Condition 3}}{=} & \tilde{\mu}_{\phi}\left(E'\right)\\
+ & = & \sum_{j=1}^{N}q_{j}\tilde{\mu}_{\psi_{j}}\left(E'\right)
+\end{eqnarray*}
+Because $q_{j}>0$, we have $\tilde{\mu}_{\psi_{j}}\left(E\right)=0$,
+i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $E'$.
+However, the only subspace orthogonal to $E'$ is span by $\ket{\phi}$.
+Hence, $\tilde{\mu}'_{\phi}=\tilde{\mu}_{\phi}$.
+\end{proof}
 

### 2016-04-25 prob.tex
projections

@@
 which can only be computed with increasingly large resources as the
-precision increases. \\
-\yutsung{Check the meaning of the ``computing $\frac{\pi}{4}$'', because
-Bailey Borwein Plouffe formula can computing the $n$th binary digit of $\pi$ 
-using base 16 directly.}\\
-Therefore, in a resource-aware setting, it is
-more appropriate to consider probability measures that map events to a
-finite set of elements computable with a fixed set of
+precision increases.
+% \yutsung{Check the meaning of the ``computing $\frac{\pi}{4}$'', because
+% Bailey Borwein Plouffe formula can computing the $n$th binary digit of $\pi$ 
+% using base 16 directly.}
+Therefore, in a resource-aware setting, it is more appropriate to
+consider probability measures that map events to a finite set of
+elements computable with a fixed set of
 resources~\cite{Artstein1972,PuriRalescu1983}. The simplest such set,
@@
 $x=y=\imposs$. In relation to the first definition, one can interpret
-\imposs\ as the closed interval $[0,0]$, \poss\ as the half-open interval
-$(0,1]$, and $\vee$ as the addition of intervals. The definition of a
-probability measure in this case is modified as being a function
-$\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
+\imposs\ as the closed interval $[0,0]$, \poss\ as the half-open
+interval $(0,1]$, and $\vee$ as the addition of intervals. The
+definition of a probability measure in this case is modified as being
+a function $\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
 \begin{itemize}
@@
 To properly explain the previous example and generalize to arbitrary
-quantum systems, we formally define a quantum probability space as
-follows.
+quantum systems, we formally discuss projection operators and then
+define a quantum probability space.
+
+\amr{
+
+  Projections include $\mathbb{0}, \proj{\psi}$ and $P_1 + P_2$ and
+  $P_1 . P_2$ if $P_1$ and $P_2$ commute.
+
+  When we write an event as $\sum E_i$ we are implicitly assuming they
+  are commutative.
+
+  Orthogonal implies commutative but not vice-versa
+}
 
@@
 \begin{itemize}
-\item The set of events consists of the empty projection $\mathbb{0}$
-  together with projection operators $\proj{\psi}$ for each state
-  $\ket{\psi}$,\\
-  \yutsung{and the sum of the orthogonal events recursively.}
+\item The set of events consists of all projections. This set includes
+  the empty projection, projection operators $\proj{\psi}$ for each
+  state $\ket{\psi}$, and sums of \emph{commuting} projections, 
 \item $\mu(\mathbb{1})=1$, and 
-\item for projections expressible as sums $\sum_{i}E_{i}$ of
-  necessarily orthogonal events $E_i$, we have
+\item for mutually orthogonal projections $E_i$, we have
   $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$.
@@
 \qed\end{definition}
+
+%% See http://math.stackexchange.com/questions/1146893/on-the-sum-of-projection-operators
+% Two properties: E1 orthogonal to E2 or not
+%                          E1 commutative with E2 or not
+
+% the empty projection $\mathbb{0}$
+
+%   \yutsung{and the sum of the orthogonal events recursively.}
 

### 2016-04-26 prob.tex
prob.tex \section{Quantum Probability Spaces} Add a comment...
projections cleaned up

@@
 \newtheorem{definition}{Definition}
+\newtheorem{cor}{Corollary}
 \newcommand{\events}{\ensuremath{\mathcal{E}}}
@@
 \newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
-\theoremstyle{plain}
-\newtheorem{thm}{\protect\theoremname}
-\theoremstyle{plain}
-\newtheorem{cor}[thm]{Corollary}
 
@@
 events. It is useful to think that this probability measure is
-completely induced by the two coins and their characteristics in the
-sense that each pair of coins induces a measure, and each measure must
-correspond to some pair of coins.
+completely induced by the two coins in question and their
+characteristics in the sense that each pair of coins induces a
+measure, and each measure must correspond to some pair of coins.
 \qed\end{example}
@@
   $|\alpha|^2 + |\beta|^2 = 1$. The set of events associated with this
-  Hilbert space consists of the empty projection~$\mathbb{0}$ together 
-  with projection operators $\proj{\psi}$ for each state $\ket{\psi}$.
-  Each event is interpreted as a possible post-measurement state of a
-  quantum system in current state $\ket{\phi}$. For example, the event
-  $\proj{0}$ indicates that the post-measurement state will
-  be~$\ket{0}$; the event $\proj{1}$ indicates that the
-  post-measurement state will be~$\ket{1}$; the event $\proj{\ps}$
-  where $\ket{\ps} = \frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$ indicates
-  that the post-measurement state will be $\ket{\ps}$; the event
+  Hilbert space consists of all projection operators. Each event is
+  interpreted as a possible post-measurement state of a quantum system
+  in current state $\ket{\phi}$. For example, the event $\proj{0}$
+  indicates that the post-measurement state will be~$\ket{0}$; the
+  event $\proj{1}$ indicates that the post-measurement state will
+  be~$\ket{1}$; the event $\proj{\ps}$ where
+  $\ket{\ps} = \frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$ indicates that the
+  post-measurement state will be $\ket{\ps}$; the event
   $\mathbb{1} = \proj{0}+\proj{1}$ indicates that the post-measurement
   state will be a linear combination of $\ket{0}$ and $\ket{1}$; and
-  the event $\mathbb{0}$ states that the post-measurement state will
-  be the empty state. As in the classical case, a probability measure
-  maps events to $[0,1]$: here is a partial specification of a
-  possible measure:
+  the empty event $\mathbb{0}$ states that the post-measurement state
+  will be the empty state. As in the classical case, a probability
+  measure is a function that maps events to $[0,1]$: here is a partial
+  specification of a possible probability measure:
 \[\begin{array}{rcl}
@@
 
-\amr{
+\begin{definition}[Projection Operators; Orthogonality; Commutativity]
+  Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear
+  transformation from $\Hilb$ to itself such that $P^2 = P$. An
+  orthogonal projection furthermore satisfies $P = P^*$. Projection
+  operators have the following properties:
+\begin{itemize}
+\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
+  P_2P_1 = \mathbb{0}$;
+\item Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
+  P_2P_1$;
+\item If the projections $P_1$ and $P_2$ are orthogonal then f $P_1 +
+  P_2$ is also a projection;
+\item If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
+  a projection; it is not sufficient in this case for $P_1$ and $P_2$
+  to be orthogonal. 
+\end{itemize}
+\end{definition}
 
-  Projections include $\mathbb{0}, \proj{\psi}$ and $P_1 + P_2$ and
-  $P_1 . P_2$ if $P_1$ and $P_2$ commute.
-
-  When we write an event as $\sum E_i$ we are implicitly assuming they
-  are commutative.
-
-  Orthogonal implies commutative but not vice-versa
-}
+% \amr{ 
+%   Projections include $\mathbb{0}, \proj{\psi}$ and $P_1 + P_2$ and
+%   $P_1 . P_2$ if $P_1$ and $P_2$ commute.
+%   When we write an event as $\sum E_i$ we are implicitly assuming they
+%   are commutative.
+%   Orthogonal implies commutative but not vice-versa
+% }
+% \yutsung{
+%   I checked \\
+%   \url{http://math.stackexchange.com/questions/1146893/on-the-sum-of-projection-operators}.\\
+%   Actually, they said $P_1 P_2 = P_2 P_1 = 0$, and the last $= 0$ is orthogonal.
+% }
 
@@
   the empty projection, projection operators $\proj{\psi}$ for each
-  state $\ket{\psi}$, and sums of \emph{commuting} projections, 
+  state $\ket{\psi}$, sums of \emph{orthogonal} projections, and
+  products of \emph{commuting} projections; 
 \item $\mu(\mathbb{1})=1$, and 
@@
 \qed\end{definition}
-
-%% See http://math.stackexchange.com/questions/1146893/on-the-sum-of-projection-operators
-% Two properties: E1 orthogonal to E2 or not
-%                          E1 commutative with E2 or not
-
-% the empty projection $\mathbb{0}$
-
-%   \yutsung{and the sum of the orthogonal events recursively.}
 

### 2016-04-27 prob.tex
prob.tex Updating definition of Projection Operators...

@@
 
-\begin{definition}[Projection Operators; Orthogonality; Commutativity]
-  Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear
-  transformation from $\Hilb$ to itself such that $P^2 = P$. An
-  orthogonal projection furthermore satisfies $P = P^*$. Projection
-  operators have the following properties:
+\begin{definition}[Projection Operators; Orthogonality;
+Commutativity~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
+Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear transformation from $\Hilb$
+to itself such that $P^2 = P^{\dagger} = P$. Projection operators have the
+following properties:\footnote {``Projection'' is sometimes called
+``orthogonal projection" or ``self-adjoint projection" to
+emphasis $P^{\dagger} = P$~\cite{Maassen2010}.}
 \begin{itemize}

### 2016-04-27 prob.tex
typos

--- 2016-04-26 prob.tex
@@
 space~$\Omega$ and reason directly about events. A quantum probability
-space therefore consist of just two components: a set of events
+space therefore consists of just two components: a set of events
 $\qevents$ and a probability measure
@@
 
-\begin{definition}[Projection Operators; Orthogonality; Commutativity]
-  Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear
-  transformation from $\Hilb$ to itself such that $P^2 = P$. An
-  orthogonal projection furthermore satisfies $P = P^*$. Projection
-  operators have the following properties:
+\begin{definition}[Projection Operators; Orthogonality;
+Commutativity~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
+Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear transformation from $\Hilb$
+to itself such that $P^2 = P = P^{\dagger}$. Projection operators have the
+following properties:\footnote {``Projection'' is sometimes called
+``orthogonal projection" or ``self-adjoint projection" to
+emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
 \begin{itemize}
@@
   P_2P_1$;
-\item If the projections $P_1$ and $P_2$ are orthogonal then f $P_1 +
+\item If the projections $P_1$ and $P_2$ are orthogonal then $P_1 +
   P_2$ is also a projection;

### 2016-04-27 prob.tex
prob.tex \subsection{Quantum Probability Measures} updated...

@@
 \newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
+
+% The following copy from `iopart.cls'
 \newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
+\newcommand{\rmi}{\mathrm{i}}
+\newcommand{\rme}{\mathrm{e}}
 
@@
 
-\begin{example}[One-qubit quantum probability space] 
-  Consider a one-qubit Hilbert space with states
+\begin{example}\label{One-qubit-quantum-probability}[One-qubit quantum
+probability space] Consider a one-qubit Hilbert space with states
   $\alpha \ket{0} + \beta \ket{1}$ such that
@@
 
-For a given set of events $\events$, there are many possible
-probability measures $\mu : \events \rightarrow [0,1]$. The Born rule,
-a postulate of quantum mechanics, states that each quantum state
-$\ket{\phi}$ induces a probability measure $\mu_\phi$ as follows:
+For a given set of events~$\events$, there are many possible probability
+measures~$\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1984,Mermin2007},
+a postulate of quantum mechanics, states that each pure quantum state
+$\ket{\phi}\in\Hilb\backslash\left\{ 0\right\} $ induces a probability
+measure~$\mu_{\phi}$ as follows: 
 \[
-\mu_\phi(E) = \ip{\phi}{E\phi}
+\mu_{\phi}(E)=\frac{\ip{\phi}{E\phi}}{\ip{\phi}{\phi}}
 \]
-Conversely, Gleason's theorem states that given a probability measure
-$\mu$, there exist a quantum state $\ket{\phi}$ that induces such a
-measure using the Born rule. The theorem is only valid in Hilbert
-spaces with dimension $d \geq 3$. It is instructive to study
-counterexamples in $d=2$, i.e., the case of a one-qubit
-system. Consider five states $\ket{\psi_0}$ to $\ket{\psi_4}$ that
-form five orthogonal bases $\{ \ket{\psi_0}, \ket{\psi_1} \}$,
-$\{ \ket{\psi_1}, \ket{\psi_2} \}$,
-$\{ \ket{\psi_2}, \ket{\psi_3} \}$,
-$\{ \ket{\psi_3}, \ket{\psi_4} \}$, and
-$\{ \ket{\psi_4}, \ket{\psi_0} \}$ and consider the probability
-measure defined as follows. For all $i \in \{0,1,2,3,4\}$, we have
-$\mu_X(\proj{\psi_i}) = 1/2$. For each orthogonal basis, the
-probability is 1 as desired and yet it is impossible to find a single
-quantum state that realizes such a probability
-measure (see \url{http://tph.tuwien.ac.at/~svozil/publ/2006-gleason.pdf})
+This Born rule can be extended to mixed quantum states~$\rho$ by
+\begin{eqnarray}
+\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\psi_{j}}\left(E\right)\textrm{ ,}\label{BornRule.mixed}
+\end{eqnarray}
+where $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$
+is a density matrix, and $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$.
+It is easy to verify that given a mixed state, the Born rule also
+induces a probability measure. Conversely, Gleason's theorem states
+that given a probability measure~$\mu$, there exist a mixed quantum
+states~$\rho$ that induces such a measure using the Born rule. The
+theorem is only valid in Hilbert spaces with dimension $d\geq3$.
+It is instructive to study counterexamples in $d=2$, i.e., the case
+of a one-qubit system. As in example~\ref{One-qubit-quantum-probability},
+the set of events associated with it contains $\mathbb{0}$, $\mathbb{1}$,
+and one-dimensional projection operators which can be expressed as
+$\proj{\phi}$, where $\ket{\phi}=\left(\begin{array}{c}
+\cos\theta\\
+\rme^{\rmi\gamma}\sin\theta
+\end{array}\right)$. Then, we can define a probability measure as follow.
+\begin{eqnarray*}
+\mu\left(\mathbb{0}\right) & = & 0\textrm{;}\\
+\mu\left(\mathbb{1}\right) & = & 1\textrm{;}\\
+\mu\left(\proj{\phi}\right) & = & \begin{cases}
+0 & \textrm{, if }0\le\theta<\frac{\pi}{2}\textrm{;}\\
+1 & \textrm{, if }\frac{\pi}{2}\le\theta<\pi\textrm{.}
+\end{cases}
+\end{eqnarray*}
+$\mu$ is a probability measure, but not induced by the Born rule
+because $\mu$ not continuous, but the probabilities induces by the
+Born rule are always continuous.
+
+\yutsung{Rieder and Svozil~\cite{RiederSvozil2007} didn't provide
+enough details to construct an example. It seems that the full details
+in written in Svozil's book~\cite{Svozil1998}. Hence, I have recommended
+the library to purchase this book and sent an interlibrary loan request
+as well.}
 
@@
 The Born rule satisfies the following properties:
-\begin{itemize}
+\begin{enumerate}
 \item It can be extend to mixed states. Given a mixed state represented
@@
 where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
-the Born rule can be extended to $\rho$ by 
+the Born rule can be extended to 
 \begin{eqnarray}
-\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\psi_{j}}\left(E\right)\textrm{ ,}\label{BornRule.mixed-1}
 \end{eqnarray}
+where $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$
+is a density matrix, and $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$.
+\\
 Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
@@
 $\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
-\end{itemize}
-
+\end{enumerate}
 Naturally, we may ask: is every probability measure induced from a

### 2016-04-27 prob.tex
def comm proj
prob.tex "Classical Probability Spaces" Add small things from meeting...

--- 2016-04-27 prob.tex
@@
 \newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
+\newcommand{\likely}{{\mbox{\wesa{likely}}}}
+\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
 
@@
 \item for a collection $E_i$,  of pairwise disjoint events, 
-  $\pmeas(\bigcup E_i) = \sum \pmeas(E_i)$.
+  $\pmeas(\bigcup_i E_i) = \sum_i \pmeas(E_i)$.
 \end{itemize}
@@
 measure, and each measure must correspond to some pair of coins.
+In this example, the probability measure is induced by a weighted first coin and
+a double-headed second coin.
 \qed\end{example}
@@
 \item $\pmeas(\Omega) = \poss$, and
-\item for a collection $E_i$,  of pairwise disjoint events, $\pmeas(\bigcup E_i) = \bigvee \pmeas(E_i)$.
+\item for a collection $E_i$,  of pairwise disjoint events, $\pmeas(\bigcup_i
+E_i) = \bigvee_i \pmeas(E_i)$.
 \end{itemize}
@@
 \end{array}\]
+Compare to the first example, we can still get the information that the second
+coin is double-headed, although we loss the information that the first coin is
+weighted.
 \qed\end{example}
+
+If we consider set with more values, the probability measure may give us more
+information about the coins.
 
@@
 \item If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
-  a projection; it is not sufficient in this case for $P_1$ and $P_2$
-  to be orthogonal. 
+  a projection.
 \end{itemize}

### 2016-04-28 prob.tex
prob.tex "Classical Probability Spaces" Add the third example...

@@
 \newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
+\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
 
@@
 
-If we consider set with more values, the probability measure may give us more
-information about the coins.
+If we consider set with more values, the probability measure may give
+us more information about the coins. For example, despite $\imposs$
+and $\poss$, we may also adopt three more values: $\unlikely$\ as
+the interval~$\left(0,\frac{1}{2}\right]$, $\likely$\ as the interval~$\left(\frac{1}{2},1\right]$,
+and $\overflow$\ as the empty set~$\emptyset$ which means the
+total probability may be excessed than one. In particular, $\likely\vee\likely=\overflow$
+because the probability of two disjoint events should not both bigger
+than $\frac{1}{2}$. The complete rule for operator~$\vee$ on $\mathscr{L}_{5}=\left\{ \imposs,\poss,\unlikely,\likely,\overflow\right\} $
+is defined in table~\ref{tab:The-operator-on}, or more abstractly,
+we define $(a,b]\vee(c,d]=(a+c,b+d]\cap[0,1]$. The definition of
+a probability measure can be modified as a function $\pmeas:\events\rightarrow\mathscr{L}_{5}$
+such that: 
+\begin{itemize}
+\item $\pmeas(\Omega)\in\left\{ \poss,\likely\right\} $ or equivalently
+$1\in\pmeas(\Omega)$, and 
+\item for a collection $E_{i}$, of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\bigvee_{i}\pmeas(E_{i})$. 
+\end{itemize}
+\begin{table}
+\center{%
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline 
+$\vee$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
+\hline 
+\hline 
+$\imposs$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
+\hline 
+$\poss$ & $\poss$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
+\hline 
+$\unlikely$ & $\unlikely$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
+\hline 
+$\likely$ & $\likely$ & $\likely$ & $\likely$ & $\overflow$ & $\overflow$\tabularnewline
+\hline 
+$\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$\tabularnewline
+\hline 
+\end{tabular}}
+
+\caption{\label{tab:The-operator-on}The operator~$\vee$ on $\mathscr{L}_{5}=\left\{ \imposs,\poss,\unlikely,\likely,\overflow\right\} $}
+\end{table}
+\begin{example}{[}Two-coin probability space with $\mathscr{L}_{5}$-valued
+probability measure{]} Under the new $\mathscr{L}_{5}$-valued requirement,
+the probability measure in the first example becomes: 
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) & = & \imposs\\
+\pmeas(\{HH\}) & = & \unlikely\\
+\pmeas(\{HT\}) & = & \imposs\\
+\pmeas(\{TH\}) & = & \likely\\
+\pmeas(\{TT\}) & = & \imposs\\
+\pmeas(\{HH,HT\}) & = & \unlikely\\
+\pmeas(\{HH,TH\}) & = & \likely\\
+\pmeas(\{HH,TT\}) & = & \unlikely
+\end{array} & \begin{array}{rcl}
+\pmeas(\{HT,TH\}) & = & \likely\\
+\pmeas(\{HT,TT\}) & = & \imposs\\
+\pmeas(\{TH,TT\}) & = & \likely\\
+\pmeas(\{HH,HT,TH\}) & = & \likely\\
+\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
+\pmeas(\{HH,TH,TT\}) & = & \likely\\
+\pmeas(\{HT,TH,TT\}) & = & \likely\\
+\pmeas(\{HH,HT,TH,TT\}) & = & \likely
+\end{array}\end{array}
+\]
+In this example, we can get the information that the first coin is
+weighted and the second coin is double-headed. \qed\end{example}
 

### 2016-04-28 prob.tex
import Amr's question from email to prepare a respond with formulas...

@@
 weighted and the second coin is double-headed. \qed\end{example}
+
+\amr{Look at the first few pages of \cite{JamisonLodwick2004}. This
+is consistent with some of the other things I have read. The way you
+assign probability in this imprecise world is something like this:
+
+- define some intervals
+
+- the probability of an event is in $[x,y]$ where $x$ is some kind
+of necessity and $y$ is some of belief.
+
+So $[\frac{1}{2},1]$ would mean that the event must at least have
+probability $\frac{1}{2}$ but I have reasons to believe it might
+be certain. What is important I think is that two such events when
+combined would combine to $[1,1]$ because the belief gets adjusted
+based on the actual probabilities.
+
+So perhaps we just need to adjust the intervals we choose for L5 and
+change the $\vee$ operation to reflect this understanding and it
+would be more intuitive?
+
+\textemdash Amr
+
+> On Apr 28, 2016, at 12:35 AM, Sabry, Amr A. <sabry@indiana.edu>
+wrote:
+
+>
+
+> A quick thought. I don\textquoteright t like that the probability
+of the entire space is $\likely$ and I don\textquoteright t like
+the $\overflow$. I am absolutely sure other people have worked out
+similar examples in possibility theory, dempster-shafer, Look at \textquotedblleft See
+Also\textquotedblright{} near the end of \textquotedbl{}https://en.wikipedia.org/wiki/Dempster\textendash Shafer\_theory\textquotedblright .
+I think there must be a way a simpler way of choosing the subsets
+(intervals) to make things more intuitive. \textemdash Amr
+
+> }
 

### 2016-04-29 prob.tex
interval

--- 2016-04-28 prob.tex
@@
 \newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
+\newcommand{\necess}{{\mbox{\wesa{necessary}}}}
 \newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
@@
 characteristics in the sense that each pair of coins induces a
-measure, and each measure must correspond to some pair of coins.
-In this example, the probability measure is induced by a weighted first coin and
-a double-headed second coin.
+measure, and each measure must correspond to some pair of coins.  In
+this example, the first coin is twice as likely to be tails than heads
+and the second coin is double-headed.  
 \qed\end{example}
@@
 consider probability measures that map events to a finite set of
-elements computable with a fixed set of
-resources~\cite{Artstein1972,PuriRalescu1983}. The simplest such set,
+elements computable with a fixed set of resources. We will consider
+two approaches: set-valued probability
+measures~\cite{Artstein1972,PuriRalescu1983} and interval-valued
+probability measures~\cite{JamisonLodwick2004,Weichselberger2000}.
+
+\paragraph*{Set-valued Probability Measures.} The simplest such set,
 and the one we will consider exclusively in this paper, is the set
@@
 operation $\vee$ where $x \vee y=\imposs$ if and only if
-$x=y=\imposs$. In relation to the first definition, one can interpret
-\imposs\ as the closed interval $[0,0]$, \poss\ as the half-open
-interval $(0,1]$, and $\vee$ as the addition of intervals. The
-definition of a probability measure in this case is modified as being
-a function $\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
+$x=y=\imposs$. In relation to the conventional definition, one can
+interpret \imposs\ as the closed interval $[0,0]$, \poss\ as the
+half-open interval $(0,1]$, and $\vee$ as the addition of
+intervals. The definition of a probability measure in this case is
+modified as being a function
+$\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
 \begin{itemize}
@@
 \end{array}\]
-Compare to the first example, we can still get the information that the second
-coin is double-headed, although we loss the information that the first coin is
-weighted.
+Despite the fact that we lost all numeric information, the probability
+measure still reveals that the second coin is double-headed. We have
+however lost the information regarding the bias in the first
+coin. This information can be recovered with a more refined
+probability measure as we show next. 
 \qed\end{example}
 
-If we consider set with more values, the probability measure may give
-us more information about the coins. For example, despite $\imposs$
-and $\poss$, we may also adopt three more values: $\unlikely$\ as
-the interval~$\left(0,\frac{1}{2}\right]$, $\likely$\ as the interval~$\left(\frac{1}{2},1\right]$,
-and $\overflow$\ as the empty set~$\emptyset$ which means the
-total probability may be excessed than one. In particular, $\likely\vee\likely=\overflow$
-because the probability of two disjoint events should not both bigger
-than $\frac{1}{2}$. The complete rule for operator~$\vee$ on $\mathscr{L}_{5}=\left\{ \imposs,\poss,\unlikely,\likely,\overflow\right\} $
-is defined in table~\ref{tab:The-operator-on}, or more abstractly,
-we define $(a,b]\vee(c,d]=(a+c,b+d]\cap[0,1]$. The definition of
-a probability measure can be modified as a function $\pmeas:\events\rightarrow\mathscr{L}_{5}$
-such that: 
+\paragraph*{Interval-valued probability measures.} In this case, we
+split the $[0,1]$ interval into a collection of closed sub-intervals
+obeying certain restrictions to be described at the end of the
+section. To illustrate the main ideas, we first consider a simple
+example.
+
+\begin{example}[Two-coin probability space with four intervals]
+We split the interval in the following four closed sub-intervals:
+\begin{itemize}
+\item $[0,0]$ which we call \imposs, 
+\item $[0,\frac{1}{2}]$ which we call \unlikely, 
+\item $[\frac{1}{2},1]$ which we call \likely, and 
+\item $[1,1]$ which we call \necess.
+\end{itemize}
+The probability measure in this case becomes:
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) & = & \imposs\\
+\pmeas(\{HH\}) & = & \unlikely\\
+\pmeas(\{HT\}) & = & \imposs\\
+\pmeas(\{TH\}) & = & \likely\\
+\pmeas(\{TT\}) & = & \imposs\\
+\pmeas(\{HH,HT\}) & = & \unlikely\\
+\pmeas(\{HH,TH\}) & = & \necess\\
+\pmeas(\{HH,TT\}) & = & \unlikely
+\end{array} & \begin{array}{rcl}
+\pmeas(\{HT,TH\}) & = & \likely\\
+\pmeas(\{HT,TT\}) & = & \imposs\\
+\pmeas(\{TH,TT\}) & = & \likely\\
+\pmeas(\{HH,HT,TH\}) & = & \necess\\
+\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
+\pmeas(\{HH,TH,TT\}) & = & \necess\\
+\pmeas(\{HT,TH,TT\}) & = & \likely\\
+\pmeas(\{HH,HT,TH,TT\}) & = & \necess
+\end{array}\end{array}
+\]
+Not only does this probability measure reveal that the second coin is
+double-headed but it also reveals that the first coin is more likely
+to be heads than tails, despite the absence of numeric information.
+\qed\end{example}
+
+\newpage
+
+We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
+
+\[\begin{array}{rclrcll}
+\imposs \vee x &=& x \vee \imposs &=& x \\
+\necess \vee x &=& x \vee \necess  &=& \necess \\
+\unlikely \vee \likely &=& \likely \vee \unlikely &=& \necess
+\end{array}\]
+
+If we consider set
+with more values, the probability measure may give us more information
+about the coins. For example, despite $\imposs$ and $\poss$, we may
+also adopt three more values: $\unlikely$\ as the
+interval~$\left(0,\frac{1}{2}\right]$, $\likely$\ as the
+interval~$\left(\frac{1}{2},1\right]$, and $\overflow$\ as the empty
+set~$\emptyset$ which means the total probability may be excessed than
+one. In particular, $\likely\vee\likely=\overflow$ because the
+probability of two disjoint events should not both bigger than
+$\frac{1}{2}$. The complete rule for operator~$\vee$ on
+$\mathscr{L}_{5}=\left\{
+  \imposs,\poss,\unlikely,\likely,\overflow\right\} $
+is defined in table~\ref{tab:The-operator-on}, or more abstractly, we
+define $(a,b]\vee(c,d]=(a+c,b+d]\cap[0,1]$. The definition of a
+probability measure can be modified as a function
+$\pmeas:\events\rightarrow\mathscr{L}_{5}$ such that:
 \begin{itemize}
@@
 \end{table}
-\begin{example}{[}Two-coin probability space with $\mathscr{L}_{5}$-valued
-probability measure{]} Under the new $\mathscr{L}_{5}$-valued requirement,
-the probability measure in the first example becomes: 
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\pmeas(\emptyset) & = & \imposs\\
-\pmeas(\{HH\}) & = & \unlikely\\
-\pmeas(\{HT\}) & = & \imposs\\
-\pmeas(\{TH\}) & = & \likely\\
-\pmeas(\{TT\}) & = & \imposs\\
-\pmeas(\{HH,HT\}) & = & \unlikely\\
-\pmeas(\{HH,TH\}) & = & \likely\\
-\pmeas(\{HH,TT\}) & = & \unlikely
-\end{array} & \begin{array}{rcl}
-\pmeas(\{HT,TH\}) & = & \likely\\
-\pmeas(\{HT,TT\}) & = & \imposs\\
-\pmeas(\{TH,TT\}) & = & \likely\\
-\pmeas(\{HH,HT,TH\}) & = & \likely\\
-\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
-\pmeas(\{HH,TH,TT\}) & = & \likely\\
-\pmeas(\{HT,TH,TT\}) & = & \likely\\
-\pmeas(\{HH,HT,TH,TT\}) & = & \likely
-\end{array}\end{array}
-\]
-In this example, we can get the information that the first coin is
-weighted and the second coin is double-headed. \qed\end{example}
-
-We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
 

### 2016-04-30 prob.tex
prob.tex \paragraph*{Interval-valued probability measures.} update...

@@
 
+We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
+
 \paragraph*{Interval-valued probability measures.} In this case, we
@@
 
-\newpage
-
-We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
-
-\[\begin{array}{rclrcll}
-\imposs \vee x &=& x \vee \imposs &=& x \\
-\necess \vee x &=& x \vee \necess  &=& \necess \\
-\unlikely \vee \likely &=& \likely \vee \unlikely &=& \necess
-\end{array}\]
-
-If we consider set
-with more values, the probability measure may give us more information
-about the coins. For example, despite $\imposs$ and $\poss$, we may
-also adopt three more values: $\unlikely$\ as the
-interval~$\left(0,\frac{1}{2}\right]$, $\likely$\ as the
-interval~$\left(\frac{1}{2},1\right]$, and $\overflow$\ as the empty
-set~$\emptyset$ which means the total probability may be excessed than
-one. In particular, $\likely\vee\likely=\overflow$ because the
-probability of two disjoint events should not both bigger than
-$\frac{1}{2}$. The complete rule for operator~$\vee$ on
-$\mathscr{L}_{5}=\left\{
-  \imposs,\poss,\unlikely,\likely,\overflow\right\} $
-is defined in table~\ref{tab:The-operator-on}, or more abstractly, we
-define $(a,b]\vee(c,d]=(a+c,b+d]\cap[0,1]$. The definition of a
-probability measure can be modified as a function
-$\pmeas:\events\rightarrow\mathscr{L}_{5}$ such that:
-\begin{itemize}
-\item $\pmeas(\Omega)\in\left\{ \poss,\likely\right\} $ or equivalently
-$1\in\pmeas(\Omega)$, and 
-\item for a collection $E_{i}$, of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\bigvee_{i}\pmeas(E_{i})$. 
-\end{itemize}
-\begin{table}
-\center{%
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline 
-$\vee$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
-\hline 
-\hline 
-$\imposs$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
-\hline 
-$\poss$ & $\poss$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
-\hline 
-$\unlikely$ & $\unlikely$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
-\hline 
-$\likely$ & $\likely$ & $\likely$ & $\likely$ & $\overflow$ & $\overflow$\tabularnewline
-\hline 
-$\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$\tabularnewline
-\hline 
-\end{tabular}}
-
-\caption{\label{tab:The-operator-on}The operator~$\vee$ on $\mathscr{L}_{5}=\left\{ \imposs,\poss,\unlikely,\likely,\overflow\right\} $}
-\end{table}
+In interval-valued probability measures, if $\mu\left(E\right)=\left[a,b\right]$,
+the left-endpoint~$a$ called belief denotes the strength of the
+evidence that $E$ happens, and the right-endpoint~$b$ called plausibility
+denotes the strength of the evidence that contradicts $E$. If we
+define $1-\left[a,b\right]=\left[1-b,1-a\right]$, then we intuitively
+have 
+\begin{eqnarray*}
+\pmeas\left(\emptyset\right) & = & \imposs\\
+\pmeas\left(\Omega\right) & = & \necess\\
+\pmeas\left(\Omega\backslash E\right) & = & 1-\pmeas\left(E\right)
+\end{eqnarray*}
+Next, if we define $\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$,
+then 
+\begin{itemize}
+\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
+\end{itemize}
+Notice that the equality may not hold in general This statement says
+that the evidences of $\bigcup_{i}E_{i}$ is at least as strong as
+putting all the evidences of $E_{i}$ together, but some evidence
+may only be acquired for $\bigcup_{i}E_{i}$ as the whole. Therefore,
+$\pmeas\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\pmeas\left(E_{i}\right)$,
+but may not equal. In our example, 
+\begin{eqnarray*}
+ &  & \pmeas(\{HH,TH\})=\necess=[1,1]\\
+ & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\pmeas(\{HH\})+\pmeas(\{TH\})\textrm{ .}
+\end{eqnarray*}
+However, $\pmeas(\{HH,TH\})$ is a proper subset of $\pmeas(\{HH\})+\pmeas(\{TH\})$
+because if we check the complement of $\{HH,TH\}$, we have 
+\begin{eqnarray*}
+ &  & \pmeas(\{HH,TH\})=1-\pmeas(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
+\end{eqnarray*}
+and $\pmeas(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
+of $\{HH\}$ and $\{TH\}$ individually.
+
+\yutsung{Although this is clearer than the previous one, I keep some
+intervals instead write everything in \imposs, \unlikely, \likely,
+and \necess. The biggest point is the addition rule~$\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$:
+\begin{itemize}
+\item This rule without \overflow will be push complexity to ``we may abort
+computing probability when....''
+\item It seems more concisely than a table among \imposs, \unlikely, \likely,
+and \necess.
+\end{itemize}
+However, if you prefer as less interval as possible, I may try to
+replace them by \imposs, \unlikely, \likely, and \necess...}
 

### 2016-04-30 prob.tex
small comments

@@
 
-We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
-
 \paragraph*{Interval-valued probability measures.} In this case, we
-split the $[0,1]$ interval into a collection of closed sub-intervals
-obeying certain restrictions to be described at the end of the
-section. To illustrate the main ideas, we first consider a simple
-example.
+split the $[0,1]$ interval into a collection of overlapping closed
+sub-intervals obeying certain restrictions to be described at the end
+of the section. To illustrate the main ideas, we first consider a
+simple example.
 
@@
 \end{itemize}
-The probability measure in this case becomes:
+Using these new values, the probability measure becomes:
 \[
@@
 double-headed but it also reveals that the first coin is more likely
-to be heads than tails, despite the absence of numeric information.
+to be tails than heads, despite the absence of numeric information.
 \qed\end{example}
@@
 replace them by \imposs, \unlikely, \likely, and \necess...}
+\amr{I like this. We just might need to rewrite a little but overall
+  it's good.}
 
@@
 \end{definition}
+
+\amr{Here it would be good to refer to the notion of ``quantum test''
+  and define events as sums of quantum tests. This will automatically
+  include everything except the products of commutative projections
+  which we will have to explain that they can be expressed as sums of
+  orthogonal projections.}
 

### 2016-04-30 prob.tex
Add citation, but need to verify the material...

@@
 measures~\cite{Artstein1972,PuriRalescu1983} and interval-valued
-probability measures~\cite{JamisonLodwick2004,Weichselberger2000}.
+probability measures~\cite{Dempster1967,Weichselberger2000,JamisonLodwick2004}.
 
@@
 \end{itemize}
-Notice that the equality may not hold in general This statement says
+Notice that the equality may not hold in general. This statement says
 that the evidences of $\bigcup_{i}E_{i}$ is at least as strong as
@@
 of $\{HH\}$ and $\{TH\}$ individually.
-
-\yutsung{Although this is clearer than the previous one, I keep some
-intervals instead write everything in \imposs, \unlikely, \likely,
-and \necess. The biggest point is the addition rule~$\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$:
-\begin{itemize}
-\item This rule without \overflow will be push complexity to ``we may abort
-computing probability when....''
-\item It seems more concisely than a table among \imposs, \unlikely, \likely,
-and \necess.
-\end{itemize}
-However, if you prefer as less interval as possible, I may try to
-replace them by \imposs, \unlikely, \likely, and \necess...}
-\amr{I like this. We just might need to rewrite a little but overall
-  it's good.}
 
@@
 
-\amr{give example non-commuting events}
-
-\yutsung{Isn't $\proj{0}$ and $\proj{\ps}$ an example in the example of
-One-qubit quantum probability space.}
-
 %%%%%
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{discreteGBKS}

### 2016-04-30 prob.tex
a little cleanup; still not happy with interval prob

@@
 \begin{document}
-\title{Probability}
+\title{Discrete Probability for Discrete Quantum Computing}
 \author{}
@@
 \item $\pmeas(\Omega) = 1$, and 
-\item for a collection $E_i$,  of pairwise disjoint events, 
+\item for a collection $E_i$ of pairwise disjoint events, 
   $\pmeas(\bigcup_i E_i) = \sum_i \pmeas(E_i)$.
@@
 
-\begin{example}[Two-coin probability space]
+\begin{example}[Two-coin probability space]\label{ex1}
   Consider an experiment that tosses two coins. We have four possible
@@
   $\Omega = \{ HH, HT, TH, TT \}$. There are 16 total events including
-  for example the event $\{ HH, HT \}$ that the first coin is
-  ``heads,'' the event $\{ HT, TH \}$ that the two coins land on
-  opposite sides, and the event $\{ HT, TH, TT\}$ that at least one
-  coin is tails. Here is a possible probability measure for these
-  events:
+  for example the event $\{ HH, HT \}$ that the first coin lands heads
+  up, the event $\{ HT, TH \}$ that the two coins land on opposite
+  sides, and the event $\{ HT, TH, TT\}$ that at least one coin lands
+  tails up. Here is a possible probability measure for these events:
 \[\begin{array}{c@{\qquad\qquad}c}
@@
 characteristics in the sense that each pair of coins induces a
-measure, and each measure must correspond to some pair of coins.  In
-this example, the first coin is twice as likely to be tails than heads
-and the second coin is double-headed.  
+measure, and each measure must correspond to some pair of coins.  The
+measure above is induced by two coins such that the first coin is
+twice as likely to land tails up than heads up and the second coin is
+double-headed.  
 \qed\end{example}
@@
 
-\paragraph*{Set-valued Probability Measures.} The simplest such set,
-and the one we will consider exclusively in this paper, is the set
-$\mathscr{L}_{2}=\left\{ \imposs, \poss\right\}$ together with the
-operation $\vee$ where $x \vee y=\imposs$ if and only if
+\paragraph*{Set-valued Probability Measures.} The simplest such set is
+the set $\mathscr{L}_{2}=\left\{ \imposs, \poss\right\}$ together with
+the operation $\vee$ where $x \vee y=\imposs$ if and only if
 $x=y=\imposs$. In relation to the conventional definition, one can
@@
 intervals. The definition of a probability measure in this case is
-modified as being a function
-$\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
+modified to a function $\pmeas : \events \rightarrow \mathscr{L}_{2}$
+such that:
 \begin{itemize}
 \item $\pmeas(\Omega) = \poss$, and
-\item for a collection $E_i$,  of pairwise disjoint events, $\pmeas(\bigcup_i
+\item for a collection $E_i$ of pairwise disjoint events, $\pmeas(\bigcup_i
 E_i) = \bigvee_i \pmeas(E_i)$.
@@
 \begin{example}[Two-coin probability space with finite set-valued
-  probability measure] Under the new set-valued requirement, the
-  probability measure in the first example becomes:
+  probability measure] \label{ex2} Under the new set-valued
+  requirement, the probability measure in the first example becomes:
 \[\begin{array}{c@{\qquad\qquad}c}
@@
 \end{array}\]
-Despite the fact that we lost all numeric information, the probability
-measure still reveals that the second coin is double-headed. We have
-however lost the information regarding the bias in the first
-coin. This information can be recovered with a more refined
-probability measure as we show next. 
+Despite the fact that we have lost all numeric information, the
+probability measure still reveals that the second coin is
+double-headed. We have however lost the information regarding the bias
+in the first coin. This information can be recovered with a more
+refined probability measure as we show next.  
 \qed\end{example}
@@
 sub-intervals obeying certain restrictions to be described at the end
-of the section. To illustrate the main ideas, we first consider a
-simple example.
+of the section. First we illustrate the main ideas using a simple
+example.
 
-\begin{example}[Two-coin probability space with four intervals]
-We split the interval in the following four closed sub-intervals:
+\begin{example}[Two-coin probability space with four intervals] \label{ex3}
+We split the unit interval $[0,1]$ in the following four closed sub-intervals:
 \begin{itemize}
@@
 Not only does this probability measure reveal that the second coin is
-double-headed but it also reveals that the first coin is more likely
-to be tails than heads, despite the absence of numeric information.
+double-headed but it also reveals the bias in the first coin, again despite
+the absence of any numeric information.  
 \qed\end{example}
 
-In interval-valued probability measures, if $\mu\left(E\right)=\left[a,b\right]$,
-the left-endpoint~$a$ called belief denotes the strength of the
-evidence that $E$ happens, and the right-endpoint~$b$ called plausibility
-denotes the strength of the evidence that contradicts $E$. If we
-define $1-\left[a,b\right]=\left[1-b,1-a\right]$, then we intuitively
-have 
+The probability measure above can be understood in reference to
+Ex.~\ref{ex1} by mapping each numeric value to the smallest interval
+containing it. The probability measure appears quite intuitive from
+that perspective. However, if we attempt to understand the probability
+measure independently of Ex.~\ref{ex1} we would hard pressed to
+justify the following assignments:
+\[ 
+\pmeas(\{HH\}) = \unlikely, \quad\pmeas(\{TH\}) = \likely, \quad
+\pmeas(\{HH\}\cup\{TH\}) = \necess 
+\]
+which assert that an \unlikely-event whose probability is in the range
+$[0,\frac{1}{2}]$ and a \likely-event whose probability is in the
+range $[\frac{1}{2},1]$ combine to a \necess-event whose probability
+is in the range $[1,1]$! To understand this mystery, it is important
+to investigate the mathematical definition of interval-valued
+probabilities in detail.
+
+In interval-valued probability measures, if the probability of an
+event $E$ is $[a,b]$, we think of the left-endpoint~$a$ as
+representing the strength of the evidence that supports $E$, and the
+right-endpoint~$b$ as the strength of the evidence that contradicts
+$E$. If we define $1-\left[a,b\right]=\left[1-b,1-a\right]$, then we
+intuitively have
 \begin{eqnarray*}
@@
   sample space $\Omega = \{ HH, HT, TH, TT \}$. The event that the
-  first coin is ``heads'' is $\{ HH, HT \}$; the event that the two
+  first coin lands heads up is $\{ HH, HT \}$; the event that the two
   coins land on opposite sides is $\{ HT, TH \}$; the event that at
-  least one coin is tails is $\{ HT, TH, TT\}$. Depending on the
+  least one coin lands tails up is $\{ HT, TH, TT\}$. Depending on the
   assumptions regarding the coins, we can define several probability

### 2016-04-30 prob.tex
example dempster shafer

@@
 containing it. The probability measure appears quite intuitive from
-that perspective. However, if we attempt to understand the probability
-measure independently of Ex.~\ref{ex1} we would hard pressed to
-justify the following assignments:
+that perspective. However, we also must be able to understand the
+probability measure independently of Ex.~\ref{ex1} and in particular
+justify how combinations such as
 \[ 
@@
 range $[\frac{1}{2},1]$ combine to a \necess-event whose probability
-is in the range $[1,1]$! To understand this mystery, it is important
-to investigate the mathematical definition of interval-valued
-probabilities in detail.
+is in the range $[1,1]$! To understand this mystery, we look at
+another more general example and then give the formal mathematical
+definition of interval-valued probabilities.
+
+\amr{See A Simple View of the Dempster-Shafer Theory of Evidence and 
+  its Implication for the Rule of Combination Lotfi A. Zadeh, AAAI,
+  1986}
+
+\begin{example}[Dempster-Shafer Theory of Evidence] We have five
+  employees whose precise age is not known. All is give is a range for
+  each employee:
+\[\begin{array}{rcl}
+\textrm{Age}(M_1) &=& [22,26] \\
+\textrm{Age}(M_2) &=& [20,22] \\
+\textrm{Age}(M_3) &=& [30,35] \\
+\textrm{Age}(M_4) &=& [20,22] \\
+\textrm{Age}(M_5) &=& [28,30] 
+\end{array}\]
+What is the probability that an employee's age is in the range
+$[20,25]$. Looking at the data, it is \emph{possible} for $M_1$'s age
+to be within the range, it is \emph{not possible} for $M_3$'s age to
+be within the range, and it is \emph{certain} or \emph{necessary} that
+$M_4$'s age is in the range. Clearly saying that an event is
+\emph{necessary} is equivalent to saying that its complement is
+\emph{not possible}. Aggregating the results for the five employees,
+we can calculate that is necessary that 2 employees have their ages
+within the range, and it is possible that 3 employees have their ages
+within the range. We express this formally as saying that the
+probability of the event is $[0.4,0.6]$. Now consider another event
+asking whether the ages are some other disjoint range
+$[26,40]$. Reasoning in a similar way we calculate that the
+probability for this event is $[0.4,0.6]$. Now let's take the two events
+together and ask about the possibility of the ages to be in the range
+$[20,40]$. Clearly that probability must be $[1,1]$ as every
+employee's age is in that range. The way to calculate this probability
+from the individual probabilities of the events is as follows: 
+\begin{itemize}
+\item \amr{can you try to fix this... perhaps it is not consistent
+    with the interval-valued formalization but it is really nice if we
+    can make it work}
+\end{itemize}
+\qed\end{example}
 
@@
 right-endpoint~$b$ as the strength of the evidence that contradicts
-$E$. If we define $1-\left[a,b\right]=\left[1-b,1-a\right]$, then we
-intuitively have
+$E$.
+
+Thus if we have an event $E$ with probability $[a,b]$ where
+$a=0.1$ and $b=0.7$, we have that:
+\begin{itemize}
+\item the strength of evidence supporting $E$ is 0.1; since either $E$
+  or its complement must happen, we conclude that there is 0.9
+  evidence supporting the complement of $E$; 
+\item the strength of evidence contradicting $E$ is 0.7; again since
+  either $E$ or its complement must happen, we conclude that there is
+  0.3 evidence contradicting the complement of $E$.
+\end{itemize}
+
+Turning things around, the strength of evidence that contradicts
+$E$ is evidence supporting the complement of $E$
+
+The complement of $E$ must therefore have probability
+$\left[1-b,1-a\right]$ which we abbreviate $1-\left[a,b\right]$:
+
 \begin{eqnarray*}

### 2016-04-30 prob.tex
Briefly read through and fix some typos...

@@
 \begin{example}[Dempster-Shafer Theory of Evidence] We have five
-  employees whose precise age is not known. All is give is a range for
+  employees whose precise age is not known. All is given is a range for
   each employee:
@@
 What is the probability that an employee's age is in the range
-$[20,25]$. Looking at the data, it is \emph{possible} for $M_1$'s age
+$[20,25]$? Looking at the data, it is \emph{possible} for $M_1$'s age
 to be within the range, it is \emph{not possible} for $M_3$'s age to
@@
 asking whether the ages are some other disjoint range
-$[26,40]$. Reasoning in a similar way we calculate that the
+$(25,40]$. Reasoning in a similar way we calculate that the
 probability for this event is $[0.4,0.6]$. Now let's take the two events
@@
 
+\yutsung{Do we use the law of excluded middle here? You remind me Agda : ) Did
+Homotopy Type Theory people said anything about the probability?}
+
 Turning things around, the strength of evidence that contradicts
-$E$ is evidence supporting the complement of $E$
-
-The complement of $E$ must therefore have probability
-$\left[1-b,1-a\right]$ which we abbreviate $1-\left[a,b\right]$:
+$E$ is evidence supporting the complement of $E$. The complement of $E$ must
+therefore have probability $\left[1-b,1-a\right]$ which we abbreviate $1-\left[a,b\right]$:
 

### 2016-04-30 prob.tex
Add the cited document...

@@
 measures~\cite{Artstein1972,PuriRalescu1983} and interval-valued
-probability measures~\cite{Dempster1967,Weichselberger2000,JamisonLodwick2004}.
+probability
+measures~\cite{Dempster1967,Zadeh1986,Weichselberger2000,JamisonLodwick2004}.
 
@@
 \[\begin{array}{rcl}
-\textrm{Age}(M_1) &=& [22,26] \\
-\textrm{Age}(M_2) &=& [20,22] \\
-\textrm{Age}(M_3) &=& [30,35] \\
-\textrm{Age}(M_4) &=& [20,22] \\
-\textrm{Age}(M_5) &=& [28,30] 
+\textrm{Age}(M_1) &\in& [22,26] \\
+\textrm{Age}(M_2) &\in& [20,22] \\
+\textrm{Age}(M_3) &\in& [30,35] \\
+\textrm{Age}(M_4) &\in& [20,22] \\
+\textrm{Age}(M_5) &\in& [28,30] 
 \end{array}\]
@@
 asking whether the ages are some other disjoint range
-$(25,40]$. Reasoning in a similar way we calculate that the
+$[26,40]$. Reasoning in a similar way we calculate that the
 probability for this event is $[0.4,0.6]$. Now let's take the two events

### 2016-05-03 prob.tex
prob.tex \begin{example}[Dempster-Shafer Theory of Evidence] updates...

@@
 \[\begin{array}{rcl}
-\textrm{Age}(M_1) &\in& [22,26] \\
-\textrm{Age}(M_2) &\in& [20,22] \\
-\textrm{Age}(M_3) &\in& [30,35] \\
-\textrm{Age}(M_4) &\in& [20,22] \\
-\textrm{Age}(M_5) &\in& [28,30] 
+\textrm{Age}(M_{1}) & \in & [22,26]=D_{1}\\
+\textrm{Age}(M_{2}) & \in & [20,22]=D_{2}\\
+\textrm{Age}(M_{3}) & \in & [30,35]=D_{3}\\
+\textrm{Age}(M_{4}) & \in & [20,22]=D_{4}\\
+\textrm{Age}(M_{5}) & \in & [28,30]=D_{5}
 \end{array}\]
@@
     can make it work}
+\item Because ages are all integers, and we only consider ages from 20 to
+40. Hence, the sample space~$\Omega$ can be $\left\{ 20,21,\ldots,39,40\right\} $,
+and the set of events are $2^{\Omega}$ as usual.\\
+\yutsung{I have numerically verified if we set $\Omega=\left\{ 20,22,25,26,28,30,35,40\right\} $,
+and the answer should be the same as $\left\{ 20,21,\ldots,39,40\right\} $
+because only end-points should matter in the question... I will numerically
+verify $\left\{ 20,21,\ldots,39,40\right\} $, or prove they are the
+same later...} 
+\item Given a event~$E\subseteq\Omega$, the probability of $E$ can be
+defined by 
+\[
+\pmeas(E)=\left[\frac{1}{5}\left|\left\{ i\middle|D_{i}\cap E\ne\emptyset\right\} \right|,\frac{1}{5}\left|\left\{ i\middle|D_{i}\subseteq E\right\} \right|\right]\textrm{ ,}
+\]
+where $\left|A\right|$ is the number of elements in $A$. Then, we
+can verify that $\pmeas$ in an interval-value probability measure.
 \end{itemize}

### 2016-05-03 prob.tex
small changes to first page

@@
 
+We review the conventional presentation of probability spaces and then
+discuss several variations that avoid using the real interval $[0,1]$.
+
+%%%
+\subsection{Real-Valued Probability Spaces}
+
 A \emph{probability
@@
   of every collection of disjoint events (e.g.,
-$\{ HT, TH \} = \{ HT \} \cup \{ TH \}$) is the sum of the individual
+  $\{ HT \} \cup \{ TH \} = \{ HT, TH \}$) is the sum of the individual
   probabilities. The probability of collections of non-disjoint events
-(e.g., $\{ HT, TH, TT \} = \{ HT, TH \} \cup \{ TH , TT \}$) may add
+  (e.g., $\{ HT, TH \} \cup \{ TH , TT \} = \{ HT, TH, TT \}$) may add
   to something different than the probabilities of the individual
@@
 
-\paragraph*{Set-valued Probability Measures.} The simplest such set is
-the set $\mathscr{L}_{2}=\left\{ \imposs, \poss\right\}$ together with
-the operation $\vee$ where $x \vee y=\imposs$ if and only if
-$x=y=\imposs$. In relation to the conventional definition, one can
-interpret \imposs\ as the closed interval $[0,0]$, \poss\ as the
-half-open interval $(0,1]$, and $\vee$ as the addition of
-intervals. The definition of a probability measure in this case is
-modified to a function $\pmeas : \events \rightarrow \mathscr{L}_{2}$
-such that:
+%%%%%
+\subsection{Set-valued Probability Measures}
+
+Instead of using every point in the real interval $[0,1]$ we can
+partition the interval into disjoint sets and only consider
+probability measures up to set membership. The simplest such situation
+is to partition the interval $[0,1]$ into $\{0\}$ (which we will call
+$\imposs$) and the half-open interval $(0,1]$ (which we will call
+$\poss$). The addition that was used to aggregate probabilities is now
+abstracted to $\vee$ such that $x \vee y=\imposs$ if and only if
+$x=y=\imposs$. We will call the resulting set
+$\left\{ \imposs, \poss\right\}$ together with the with associated
+operation $\vee$, the set $\mathscr{L}_{2}$. The definition of a
+probability measure in this case is modified to a function
+$\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
 \begin{itemize}
@@
 
-\paragraph*{Interval-valued probability measures.} In this case, we
-split the $[0,1]$ interval into a collection of overlapping closed
-sub-intervals obeying certain restrictions to be described at the end
-of the section. First we illustrate the main ideas using a simple
-example.
+%%%%%
+\subsection{Interval-valued probability measures}
+
+In this case, we split the $[0,1]$ interval into a collection of
+overlapping closed sub-intervals obeying certain restrictions to be
+described at the end of the section. First we illustrate the main
+ideas using a simple example.
 

### 2016-05-04 prob.tex
mess

@@
 
-In this case, we split the $[0,1]$ interval into a collection of
-overlapping closed sub-intervals obeying certain restrictions to be
-described at the end of the section. First we illustrate the main
-ideas using a simple example.
-
-\begin{example}[Two-coin probability space with four intervals] \label{ex3}
-We split the unit interval $[0,1]$ in the following four closed sub-intervals:
-\begin{itemize}
-\item $[0,0]$ which we call \imposs, 
-\item $[0,\frac{1}{2}]$ which we call \unlikely, 
-\item $[\frac{1}{2},1]$ which we call \likely, and 
-\item $[1,1]$ which we call \necess.
-\end{itemize}
-Using these new values, the probability measure becomes:
+A natural generalization of the disjoint set-valued measure above is
+to allow the sets to overlap. In this case, we split the interval
+$[0,1]$ in a collection of \emph{overlapping} closed
+sub-intervals. First we illustrate the main ideas using a simple
+example.
+
+\begin{example}[Two-coin probability space with four
+  intervals] \label{ex3} We split the unit interval $[0,1]$ in the
+  following four closed sub-intervals: $[0,0]$ which we call \imposs,
+  $[0,\frac{1}{2}]$ which we call \unlikely, $[\frac{1}{2},1]$ which
+  we call \likely, and $[1,1]$ which we call \necess.  Using these new
+  values, we can modify the probability measure of Ex.~\ref{ex1} by
+  mapping each numeric value to the smallest sub-interval containing
+  it to get the following:
 \[
@@
 \]
-Not only does this probability measure reveal that the second coin is
-double-headed but it also reveals the bias in the first coin, again despite
-the absence of any numeric information.  
+This probability measure is more informative than the one in
+Ex.~\ref{ex2}: not only does it reveal that the second coin is
+double-headed but it also reveals the bias in the first coin.
 \qed\end{example}
 
-The probability measure above can be understood in reference to
-Ex.~\ref{ex1} by mapping each numeric value to the smallest interval
-containing it. The probability measure appears quite intuitive from
-that perspective. However, we also must be able to understand the
-probability measure independently of Ex.~\ref{ex1} and in particular
-justify how combinations such as
+The probability measure above appears quite intuitive but it is not
+really evident that it is well-defined. For example, how do we justify
+the following combination of assignments:
 \[ 
@@
 range $[\frac{1}{2},1]$ combine to a \necess-event whose probability
-is in the range $[1,1]$! To understand this mystery, we look at
+is in the range $[1,1]$. To understand this mystery, we look at
 another more general example and then give the formal mathematical
@@
 
-\amr{See A Simple View of the Dempster-Shafer Theory of Evidence and 
-  its Implication for the Rule of Combination Lotfi A. Zadeh, AAAI,
-  1986}
+\begin{example}[Dempster-Shafer Theory of Evidence] We have three
+  employees whose precise ages $A_1$, $A_2$, and $A_3$ are not
+  known. All is given is a range of ages for each employee:
+  $A_1 \in \{ 23,24 \}$, $A_2 \in \{ 20,21,22\}$, and
+  $A_3 \in \{ 21,22 \}$. The sample space in this case is
+  $A_1 \times A_2 \times A_3$ which represents all the possible
+  combinations of ages for the three employees:
+\[\begin{array}{rcl}
+\Omega &=& \{ 
+        (23,20,21), (23,20,22), (23,21,21), (23,21,22), (23,22,21), (23,22,22), \\
+&& ~(24,20,21), (24,20,22), (24,21,21), (24,21,22), (24,22,21), (24,22,22) \}
+\end{array}\]
+Subsets of $\Omega$ represent events as usual. Consider the event
+$\Omega$ that \emph{some} employee's age is in the range
+$\{20,21,22\}$: since that event covers the entire sample space its
+probability must be 1. We can however produce a more informative
+answer by reasoning as follows: it is \emph{impossible} for the first
+employee's age to be in the range $\{20,21,22\}$; it is \emph{certain}
+that the second employee's age is in that range; and it is
+\emph{possible} that the third's employee age is in that
+range. Aggregating the results, we see that it is \emph{necessary} for
+one out of three employees to have their age in the required range,
+and it is \emph{possible} for an additional employee to have their age
+in the required range. We summarize this information by reporting that
+the probability of this event is $[\frac{1}{3},\frac{2}{3}]$ where the
+first number reports the \emph{certainty} of the event and the second
+reports the \emph{possibility} of the event. We could also have
+reasoned about the dual event that \emph{no} employee's age is in the
+range $\{20,21,22\}$ to get the probability $[\frac{1}{3},\frac{2}{3}]$
+
+ dually
+about the evidence \emph{against} the event. The probability in this
+case
+
+Now consider the event
+that some employee's age is in the range $\{23,24\}$. Reasoning as
+above, the probability of this event is $[\frac{1}{3},\frac{1}{3}]$ as
+only the first employee qualifies. Clearly if we were to ask the
+probability that some employee's age is in the range
+$\{20,21,22,23,24\}$ the result should be $[1,1]$ as this range covers
+all the possibilities. The way to calculate this result from the two
+previous ones is as follows: the evidence for the combined event to be
+necessary is at least as strong as the evidence that each disjoint
+event that contributes to it is necessary. So the lower bound
+probability for the combined event is at least
+$\frac{1}{3}$. Similarly the upper bound probability is at least
+$1$. But now we can reason using the complements of the events about
+the necessity and possibility of refuting each event. For the event
+that some employee's age is \emph{not} in the range $\{20,21,22\}$ we
+have a probability $[\frac{1}{3},\frac{1}{3}]$ because it is necessary
+that $A_1$ is not in that range. Similary, the event that some employee's age is
+\emph{not} in the range $\{23,24\}$ is
+$[\frac{2}{3},\frac{2}{3}]$. Thus although the positive evidence for
+necessity
+
+\qed\end{example}
+
+\newpage
 

### 2016-05-04 prob.tex
prob.tex update the old [Dempster-Shafer Theory of Evidence] example...

@@
 \[\begin{array}{rcl}
-\textrm{Age}(M_{1}) & \in & [22,26]=D_{1}\\
-\textrm{Age}(M_{2}) & \in & [20,22]=D_{2}\\
-\textrm{Age}(M_{3}) & \in & [30,35]=D_{3}\\
-\textrm{Age}(M_{4}) & \in & [20,22]=D_{4}\\
-\textrm{Age}(M_{5}) & \in & [28,30]=D_{5}
+\textrm{Age}(M_{1}) & \in & \{ 23,24 \}=D_{1}\\
+\textrm{Age}(M_{2}) & \in & \{ 20,21,22\}=D_{2}\\
+\textrm{Age}(M_{3}) & \in & \{ 20,21 \}=D_{3}
 \end{array}\]
 What is the probability that an employee's age is in the range
-$[20,25]$? Looking at the data, it is \emph{possible} for $M_1$'s age
+$\{22,23,24\}$? Looking at the data, it is \emph{possible} for $M_2$'s age
 to be within the range, it is \emph{not possible} for $M_3$'s age to
 be within the range, and it is \emph{certain} or \emph{necessary} that
-$M_4$'s age is in the range. Clearly saying that an event is
+$M_1$'s age is in the range. Clearly saying that an event is
 \emph{necessary} is equivalent to saying that its complement is
-\emph{not possible}. Aggregating the results for the five employees,
-we can calculate that is necessary that 2 employees have their ages
-within the range, and it is possible that 3 employees have their ages
+\emph{not possible}. Aggregating the results for the three employees,
+we can calculate that is necessary that 1 employees have their ages
+within the range, and it is possible that 2 employees have their ages
 within the range. We express this formally as saying that the
-probability of the event is $[0.4,0.6]$. Now consider another event
-asking whether the ages are some other disjoint range
-$[26,40]$. Reasoning in a similar way we calculate that the
-probability for this event is $[0.4,0.6]$. Now let's take the two events
-together and ask about the possibility of the ages to be in the range
-$[20,40]$. Clearly that probability must be $[1,1]$ as every
-employee's age is in that range. The way to calculate this probability
-from the individual probabilities of the events is as follows: 
-\begin{itemize}
-\item \amr{can you try to fix this... perhaps it is not consistent
-    with the interval-valued formalization but it is really nice if we
-    can make it work}
-\item Because ages are all integers, and we only consider ages from 20 to
-40. Hence, the sample space~$\Omega$ can be $\left\{ 20,21,\ldots,39,40\right\} $,
-and the set of events are $2^{\Omega}$ as usual.\\
-\yutsung{I have numerically verified if we set $\Omega=\left\{ 20,22,25,26,28,30,35,40\right\} $,
-and the answer should be the same as $\left\{ 20,21,\ldots,39,40\right\} $
-because only end-points should matter in the question... I will numerically
-verify $\left\{ 20,21,\ldots,39,40\right\} $, or prove they are the
-same later...} 
-\item Given a event~$E\subseteq\Omega$, the probability of $E$ can be
-defined by 
-\[
-\pmeas(E)=\left[\frac{1}{5}\left|\left\{ i\middle|D_{i}\cap E\ne\emptyset\right\} \right|,\frac{1}{5}\left|\left\{ i\middle|D_{i}\subseteq E\right\} \right|\right]\textrm{ ,}
-\]
-where $\left|A\right|$ is the number of elements in $A$. Then, we
-can verify that $\pmeas$ in an interval-value probability measure.
+probability of the event is $\left[\frac{1}{3},\frac{2}{3}\right]$. Now consider
+another event asking whether the ages are some other disjoint range
+$\{20,21\}$. Reasoning in a similar way we calculate that the
+probability for this event is $\left[\frac{1}{3},\frac{2}{3}\right]$. Now let's
+take the two events together and ask about the possibility of the ages to be in the range
+$\{20,21,22,23,24\}$. Clearly that probability must be $[1,1]$ as every
+employee's age is in that range. This problem
+looks puzzle if we want to attack it directly, but will be more clear
+if we think in terms of conditional probability. We will compute the
+conditional probability for the usual real-valued probability first
+and for the interval-valued probability later.
+\begin{itemize}
+\item We randomly draw an employee among the three, so each employee has
+probability $\frac{1}{3}$ to be drawn, i.e.,
+\[
+\pmeas\left(\left\{ i=1\right\} \right)=\pmeas\left(\left\{ i=2\right\} \right)=\pmeas\left(\left\{ i=3\right\} \right)=\frac{1}{3}
+\]
+In order to compute the usual real-valued probability, we need a probability
+distribution within the possible range $D_{1}$, $D_{2}$, and $D_{3}$.
+Let's assume they are equally probable, i.e., 
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas\left(\left\{ \textrm{Age}(M_{1})=23\right\} \right) & = & \frac{1}{2}\\
+\pmeas\left(\left\{ \textrm{Age}(M_{1})=24\right\} \right) & = & \frac{1}{2}
+\end{array} & \begin{array}{rcl}
+\pmeas\left(\left\{ \textrm{Age}(M_{2})=20\right\} \right) & = & \frac{1}{3}\\
+\pmeas\left(\left\{ \textrm{Age}(M_{2})=21\right\} \right) & = & \frac{1}{3}\\
+\pmeas\left(\left\{ \textrm{Age}(M_{2})=22\right\} \right) & = & \frac{1}{3}
+\end{array}\end{array}\begin{array}{rcl}
+\pmeas\left(\left\{ \textrm{Age}(M_{3})=20\right\} \right) & = & \frac{1}{2}\\
+\pmeas\left(\left\{ \textrm{Age}(M_{3})=21\right\} \right) & = & \frac{1}{2}
+\end{array}
+\]
+Then, the probability that an employee's age is in the range $\{22,23,24\}$
+can be computed as follow:
+\begin{eqnarray*}
+ &  & \pmeas\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
+ & = & \pmeas\left(\left\{ i=1\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
+ &  & +\pmeas\left(\left\{ i=2\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
+ &  & +\pmeas\left(\left\{ i=3\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
+ & = & \frac{1}{3}\cdot1+\frac{1}{3}\cdot\frac{1}{3}+\frac{1}{3}\cdot0=\frac{4}{9}
+\end{eqnarray*}
+\item Assume we don't know the probability distributions within the possible
+range $D_{1}$, $D_{2}$, and $D_{3}$. All we know is whether they
+are \emph{possible} or \emph{necessary}. Then we replace the above
+computation from exact value to interval and consider
+\begin{eqnarray*}
+ &  & \pmeas\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
+ & = & \pmeas\left(\left\{ i=1\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
+ &  & +\pmeas\left(\left\{ i=2\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
+ &  & +\pmeas\left(\left\{ i=3\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
+ & = & \frac{1}{3}\cdot[1,1]+\frac{1}{3}\cdot[0,1]+\frac{1}{3}\cdot[0,0]=\left[\frac{1}{3},\frac{2}{3}\right]
+\end{eqnarray*}
+\yutsung{Check the conditional probability rule in the Dempster-Shafer
+Theory!}
 \end{itemize}

### 2016-05-04 prob.tex
simple explanation of intervals perhaps

--- 2016-05-03 prob.tex
@@
 range $[\frac{1}{2},1]$ combine to a \necess-event whose probability
-is in the range $[1,1]$! To understand this mystery, we look at
-another more general example and then give the formal mathematical
-definition of interval-valued probabilities.
-
-\amr{See A Simple View of the Dempster-Shafer Theory of Evidence and 
-  its Implication for the Rule of Combination Lotfi A. Zadeh, AAAI,
-  1986}
-
-\begin{example}[Dempster-Shafer Theory of Evidence] We have five
-  employees whose precise age is not known. All is given is a range for
-  each employee:
-\[\begin{array}{rcl}
-\textrm{Age}(M_{1}) & \in & [22,26]=D_{1}\\
-\textrm{Age}(M_{2}) & \in & [20,22]=D_{2}\\
-\textrm{Age}(M_{3}) & \in & [30,35]=D_{3}\\
-\textrm{Age}(M_{4}) & \in & [20,22]=D_{4}\\
-\textrm{Age}(M_{5}) & \in & [28,30]=D_{5}
-\end{array}\]
-What is the probability that an employee's age is in the range
-$[20,25]$? Looking at the data, it is \emph{possible} for $M_1$'s age
-to be within the range, it is \emph{not possible} for $M_3$'s age to
-be within the range, and it is \emph{certain} or \emph{necessary} that
-$M_4$'s age is in the range. Clearly saying that an event is
-\emph{necessary} is equivalent to saying that its complement is
-\emph{not possible}. Aggregating the results for the five employees,
-we can calculate that is necessary that 2 employees have their ages
-within the range, and it is possible that 3 employees have their ages
-within the range. We express this formally as saying that the
-probability of the event is $[0.4,0.6]$. Now consider another event
-asking whether the ages are some other disjoint range
-$[26,40]$. Reasoning in a similar way we calculate that the
-probability for this event is $[0.4,0.6]$. Now let's take the two events
-together and ask about the possibility of the ages to be in the range
-$[20,40]$. Clearly that probability must be $[1,1]$ as every
-employee's age is in that range. The way to calculate this probability
-from the individual probabilities of the events is as follows: 
+is in the range $[1,1]$. To understand the calculation, we provide the
+formal definition of a probability measure in this case.
+
+Fix a collection $\mathscr{I}$ of closed sub-intervals of $[0,1]$ that
+must include $[0,0]$ and $[1,1]$. An $\mathscr{I}$--interval-valued
+probability measure is a function
+$\mu : \events \rightarrow \mathscr{I}$ such that:
 \begin{itemize}
-\item \amr{can you try to fix this... perhaps it is not consistent
-    with the interval-valued formalization but it is really nice if we
-    can make it work}
-\item Because ages are all integers, and we only consider ages from 20 to
-40. Hence, the sample space~$\Omega$ can be $\left\{ 20,21,\ldots,39,40\right\} $,
-and the set of events are $2^{\Omega}$ as usual.\\
-\yutsung{I have numerically verified if we set $\Omega=\left\{ 20,22,25,26,28,30,35,40\right\} $,
-and the answer should be the same as $\left\{ 20,21,\ldots,39,40\right\} $
-because only end-points should matter in the question... I will numerically
-verify $\left\{ 20,21,\ldots,39,40\right\} $, or prove they are the
-same later...} 
-\item Given a event~$E\subseteq\Omega$, the probability of $E$ can be
-defined by 
-\[
-\pmeas(E)=\left[\frac{1}{5}\left|\left\{ i\middle|D_{i}\cap E\ne\emptyset\right\} \right|,\frac{1}{5}\left|\left\{ i\middle|D_{i}\subseteq E\right\} \right|\right]\textrm{ ,}
-\]
-where $\left|A\right|$ is the number of elements in $A$. Then, we
-can verify that $\pmeas$ in an interval-value probability measure.
+\item $\mu(\emptyset) = [0,0]$, 
+\item $\mu(\Omega) = [1,1]$, and 
+\item for any mutually disjoint events $E_1$, $E_2$, $E_3$, and $E_4$
+  where $\pmeas(E_i) = [l_i,h_i]$ and where
+  $E_1 \cup E_2 \cup E_3 \cup E_4 = \Omega$, we have:
+\[
+\pmeas(\{E_1\cup E_2\}) \subseteq
+  [\max(l_1+l_2 , 1-(h_3+h_4)), \min(h_1+h_2 , 1-(l_3+l_4))]
+\]
+We view the events $E_1$ and $E_2$ as providing evidence for the
+combined event $E_1\cup E_2$: their values set positive bounds on the
+resulting interval. But as $E_3 \cup E_4$ is the complement of
+$E_1 \cup E_2$, the events $E_3$ and $E_4$ provide negative bounds on
+the resulting interval. The calculated interval may not be in our
+fixed set $\mathscr{I}$ of chosen intervals so we embed it in the
+smallest existing interval.
 \end{itemize}
-\qed\end{example}
-
-In interval-valued probability measures, if the probability of an
-event $E$ is $[a,b]$, we think of the left-endpoint~$a$ as
-representing the strength of the evidence that supports $E$, and the
-right-endpoint~$b$ as the strength of the evidence that contradicts
-$E$.
-
-Thus if we have an event $E$ with probability $[a,b]$ where
-$a=0.1$ and $b=0.7$, we have that:
-\begin{itemize}
-\item the strength of evidence supporting $E$ is 0.1; since either $E$
-  or its complement must happen, we conclude that there is 0.9
-  evidence supporting the complement of $E$; 
-\item the strength of evidence contradicting $E$ is 0.7; again since
-  either $E$ or its complement must happen, we conclude that there is
-  0.3 evidence contradicting the complement of $E$.
-\end{itemize}
-
-\yutsung{Do we use the law of excluded middle here? You remind me Agda : ) Did
-Homotopy Type Theory people said anything about the probability?}
-
-Turning things around, the strength of evidence that contradicts
-$E$ is evidence supporting the complement of $E$. The complement of $E$ must
-therefore have probability $\left[1-b,1-a\right]$ which we abbreviate $1-\left[a,b\right]$:
-
-\begin{eqnarray*}
-\pmeas\left(\emptyset\right) & = & \imposs\\
-\pmeas\left(\Omega\right) & = & \necess\\
-\pmeas\left(\Omega\backslash E\right) & = & 1-\pmeas\left(E\right)
-\end{eqnarray*}
-Next, if we define $\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$,
-then 
-\begin{itemize}
-\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
-\end{itemize}
-Notice that the equality may not hold in general. This statement says
-that the evidences of $\bigcup_{i}E_{i}$ is at least as strong as
-putting all the evidences of $E_{i}$ together, but some evidence
-may only be acquired for $\bigcup_{i}E_{i}$ as the whole. Therefore,
-$\pmeas\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\pmeas\left(E_{i}\right)$,
-but may not equal. In our example, 
-\begin{eqnarray*}
- &  & \pmeas(\{HH,TH\})=\necess=[1,1]\\
- & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\pmeas(\{HH\})+\pmeas(\{TH\})\textrm{ .}
-\end{eqnarray*}
-However, $\pmeas(\{HH,TH\})$ is a proper subset of $\pmeas(\{HH\})+\pmeas(\{TH\})$
-because if we check the complement of $\{HH,TH\}$, we have 
-\begin{eqnarray*}
- &  & \pmeas(\{HH,TH\})=1-\pmeas(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
-\end{eqnarray*}
-and $\pmeas(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
-of $\{HH\}$ and $\{TH\}$ individually.
+
+% to think of the above combination in the context of the evidence
+% against the events established by the dual events. Writing in terms of
+% the explicit intervals we see:
+% \[\begin{array}{rcl@{\qquad}rcl}
+% \pmeas(\{HH\}) & = & [0,\frac{1}{2}] & \pmeas(\{HT\}) & = & [0,0] \\
+% \pmeas(\{TH\}) & = & [\frac{1}{2},1] &  \pmeas(\{TT\}) & = & [0,0]
+% \end{array}\]
+% The probability for $\pmeas(\{HH,TH\})$ is $[X,Y]$ where $X$ comes
+% from the positive evidence for $\{HH\}$ and $\{TH\}$ and from the
+% evidence against  is $[X,Y]$ where $X$ comes
+% \[
+% [\max(1,\frac{1}{2}),\min(1,\frac{3}{2})]
+% \]
+
+% must be at least as strong as the
+% evidence for $\{HH\}$ and $\{TH\}$ individually and hence we have the
+% tentative bounds on $\pmeas(\{HH,TH\})$ as
+% $[\frac{1}{2},\frac{3}{2}]$. The dual events, however, establish
+% evidence against $\{HH,TH\}$ with bounds $[
+
+% A=HH
+% B=TH
+% C=HT
+% D=TT
+
+% To calculate the probability of $\{HH\}\cup\{TH\}$ we gather 
+% evidence not only from the events $\{HH\}$ and $\{TH\}$, but also from 
+% the dual events $\{HT,TH,TT\}$ and $\{HH,HT,TT\}$. The minimal
+% probability for $\{HH\}\cup\{TH\}$ is\max(
+
+% To understand this mystery, we look at
+% another more general example and then give the formal mathematical
+% definition of interval-valued probabilities.
+
+% \begin{example}[Dempster-Shafer Theory of Evidence] We have three
+%   employees whose precise ages $A_1$, $A_2$, and $A_3$ are not
+%   known. All is given is a range of ages for each employee:
+%   $A_1 \in \{ 23,24 \}$, $A_2 \in \{ 20,21,22\}$, and
+%   $A_3 \in \{ 21,22 \}$. The sample space in this case is
+%   $A_1 \times A_2 \times A_3$ which represents all the possible
+%   combinations of ages for the three employees:
+% \[\begin{array}{rcl}
+% \Omega &=& \{ 
+%         (23,20,21), (23,20,22), (23,21,21), (23,21,22), (23,22,21), (23,22,22), \\
+% && ~(24,20,21), (24,20,22), (24,21,21), (24,21,22), (24,22,21), (24,22,22) \}
+% \end{array}\]
+% Subsets of $\Omega$ represent events as usual. Consider the event
+% $\Omega$ that \emph{some} employee's age is in the range
+% $\{20,21,22\}$: since that event covers the entire sample space its
+% probability must be 1. We can however produce a more informative
+% answer by reasoning as follows: it is \emph{impossible} for the first
+% employee's age to be in the range $\{20,21,22\}$; it is \emph{certain}
+% that the second employee's age is in that range; and it is
+% \emph{possible} that the third's employee age is in that
+% range. Aggregating the results, we see that it is \emph{necessary} for
+% one out of three employees to have their age in the required range,
+% and it is \emph{possible} for an additional employee to have their age
+% in the required range. We summarize this information by reporting that
+% the probability of this event is $[\frac{1}{3},\frac{2}{3}]$ where the
+% first number reports the \emph{certainty} of the event and the second
+% reports the \emph{possibility} of the event. We could also have
+% reasoned about the dual event that \emph{no} employee's age is in the
+% range $\{20,21,22\}$ to get the probability $[\frac{1}{3},\frac{2}{3}]$
+
+%  dually
+% about the evidence \emph{against} the event. The probability in this
+% case
+
+% Now consider the event
+% that some employee's age is in the range $\{23,24\}$. Reasoning as
+% above, the probability of this event is $[\frac{1}{3},\frac{1}{3}]$ as
+% only the first employee qualifies. Clearly if we were to ask the
+% probability that some employee's age is in the range
+% $\{20,21,22,23,24\}$ the result should be $[1,1]$ as this range covers
+% all the possibilities. The way to calculate this result from the two
+% previous ones is as follows: the evidence for the combined event to be
+% necessary is at least as strong as the evidence that each disjoint
+% event that contributes to it is necessary. So the lower bound
+% probability for the combined event is at least
+% $\frac{1}{3}$. Similarly the upper bound probability is at least
+% $1$. But now we can reason using the complements of the events about
+% the necessity and possibility of refuting each event. For the event
+% that some employee's age is \emph{not} in the range $\{20,21,22\}$ we
+% have a probability $[\frac{1}{3},\frac{1}{3}]$ because it is necessary
+% that $A_1$ is not in that range. Similary, the event that some employee's age is
+% \emph{not} in the range $\{23,24\}$ is
+% $[\frac{2}{3},\frac{2}{3}]$. Thus although the positive evidence for
+% necessity
+
+% \qed\end{example}
+
+% \newpage
+
+% \begin{example}[Dempster-Shafer Theory of Evidence] We have five
+%   employees whose precise age is not known. All is given is a range for
+%   each employee:
+% \[\begin{array}{rcl}
+% \textrm{Age}(M_{1}) & \in & \{ 23,24 \}=D_{1}\\
+% \textrm{Age}(M_{2}) & \in & \{ 20,21,22\}=D_{2}\\
+% \textrm{Age}(M_{3}) & \in & \{ 20,21 \}=D_{3}
+% \end{array}\]
+% What is the probability that an employee's age is in the range
+% $\{22,23,24\}$? Looking at the data, it is \emph{possible} for $M_2$'s age
+% to be within the range, it is \emph{not possible} for $M_3$'s age to
+% be within the range, and it is \emph{certain} or \emph{necessary} that
+% $M_1$'s age is in the range. Clearly saying that an event is
+% \emph{necessary} is equivalent to saying that its complement is
+% \emph{not possible}. Aggregating the results for the three employees,
+% we can calculate that is necessary that 1 employees have their ages
+% within the range, and it is possible that 2 employees have their ages
+% within the range. We express this formally as saying that the
+% probability of the event is $\left[\frac{1}{3},\frac{2}{3}\right]$. Now consider
+% another event asking whether the ages are some other disjoint range
+% $\{20,21\}$. Reasoning in a similar way we calculate that the
+% probability for this event is $\left[\frac{1}{3},\frac{2}{3}\right]$. Now let's
+% take the two events together and ask about the possibility of the ages to be in the range
+% $\{20,21,22,23,24\}$. Clearly that probability must be $[1,1]$ as every
+% employee's age is in that range. This problem
+% looks puzzle if we want to attack it directly, but will be more clear
+% if we think in terms of conditional probability. We will compute the
+% conditional probability for the usual real-valued probability first
+% and for the interval-valued probability later.
+% \begin{itemize}
+% \item We randomly draw an employee among the three, so each employee has
+% probability $\frac{1}{3}$ to be drawn, i.e.,
+% \[
+% \pmeas\left(\left\{ i=1\right\} \right)=\pmeas\left(\left\{ i=2\right\} \right)=\pmeas\left(\left\{ i=3\right\} \right)=\frac{1}{3}
+% \]
+% In order to compute the usual real-valued probability, we need a probability
+% distribution within the possible range $D_{1}$, $D_{2}$, and $D_{3}$.
+% Let's assume they are equally probable, i.e., 
+% \[
+% \begin{array}{c@{\qquad\qquad}c}
+% \begin{array}{rcl}
+% \pmeas\left(\left\{ \textrm{Age}(M_{1})=23\right\} \right) & = & \frac{1}{2}\\
+% \pmeas\left(\left\{ \textrm{Age}(M_{1})=24\right\} \right) & = & \frac{1}{2}
+% \end{array} & \begin{array}{rcl}
+% \pmeas\left(\left\{ \textrm{Age}(M_{2})=20\right\} \right) & = & \frac{1}{3}\\
+% \pmeas\left(\left\{ \textrm{Age}(M_{2})=21\right\} \right) & = & \frac{1}{3}\\
+% \pmeas\left(\left\{ \textrm{Age}(M_{2})=22\right\} \right) & = & \frac{1}{3}
+% \end{array}\end{array}\begin{array}{rcl}
+% \pmeas\left(\left\{ \textrm{Age}(M_{3})=20\right\} \right) & = & \frac{1}{2}\\
+% \pmeas\left(\left\{ \textrm{Age}(M_{3})=21\right\} \right) & = & \frac{1}{2}
+% \end{array}
+% \]
+% Then, the probability that an employee's age is in the range $\{22,23,24\}$
+% can be computed as follow:
+% \begin{eqnarray*}
+%  &  & \pmeas\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
+%  & = & \pmeas\left(\left\{ i=1\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
+%  &  & +\pmeas\left(\left\{ i=2\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
+%  &  & +\pmeas\left(\left\{ i=3\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
+%  & = & \frac{1}{3}\cdot1+\frac{1}{3}\cdot\frac{1}{3}+\frac{1}{3}\cdot0=\frac{4}{9}
+% \end{eqnarray*}
+% \item Assume we don't know the probability distributions within the possible
+% range $D_{1}$, $D_{2}$, and $D_{3}$. All we know is whether they
+% are \emph{possible} or \emph{necessary}. Then we replace the above
+% computation from exact value to interval and consider
+% \begin{eqnarray*}
+%  &  & \pmeas\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
+%  & = & \pmeas\left(\left\{ i=1\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
+%  &  & +\pmeas\left(\left\{ i=2\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
+%  &  & +\pmeas\left(\left\{ i=3\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
+%  & = & \frac{1}{3}\cdot[1,1]+\frac{1}{3}\cdot[0,1]+\frac{1}{3}\cdot[0,0]=\left[\frac{1}{3},\frac{2}{3}\right]
+% \end{eqnarray*}
+% \yutsung{Check the conditional probability rule in the Dempster-Shafer
+% Theory!}
+% \end{itemize}
+% \qed\end{example}
+
+% In interval-valued probability measures, if the probability of an
+% event $E$ is $[a,b]$, we think of the left-endpoint~$a$ as
+% representing the strength of the evidence that supports $E$, and the
+% right-endpoint~$b$ as the strength of the evidence that contradicts
+% $E$.
+
+% Thus if we have an event $E$ with probability $[a,b]$ where
+% $a=0.1$ and $b=0.7$, we have that:
+% \begin{itemize}
+% \item the strength of evidence supporting $E$ is 0.1; since either $E$
+%   or its complement must happen, we conclude that there is 0.9
+%   evidence supporting the complement of $E$; 
+% \item the strength of evidence contradicting $E$ is 0.7; again since
+%   either $E$ or its complement must happen, we conclude that there is
+%   0.3 evidence contradicting the complement of $E$.
+% \end{itemize}
+
+% \yutsung{Do we use the law of excluded middle here? You remind me Agda : ) Did
+% Homotopy Type Theory people said anything about the probability?}
+
+% Turning things around, the strength of evidence that contradicts
+% $E$ is evidence supporting the complement of $E$. The complement of $E$ must
+% therefore have probability $\left[1-b,1-a\right]$ which we abbreviate $1-\left[a,b\right]$:
+
+% \begin{eqnarray*}
+% \pmeas\left(\emptyset\right) & = & \imposs\\
+% \pmeas\left(\Omega\right) & = & \necess\\
+% \pmeas\left(\Omega\backslash E\right) & = & 1-\pmeas\left(E\right)
+% \end{eqnarray*}
+% Next, if we define $\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$,
+% then 
+% \begin{itemize}
+% \item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
+% \end{itemize}
+% Notice that the equality may not hold in general. This statement says
+% that the evidences of $\bigcup_{i}E_{i}$ is at least as strong as
+% putting all the evidences of $E_{i}$ together, but some evidence
+% may only be acquired for $\bigcup_{i}E_{i}$ as the whole. Therefore,
+% $\pmeas\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\pmeas\left(E_{i}\right)$,
+% but may not equal. In our example, 
+% \begin{eqnarray*}
+%  &  & \pmeas(\{HH,TH\})=\necess=[1,1]\\
+%  & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\pmeas(\{HH\})+\pmeas(\{TH\})\textrm{ .}
+% \end{eqnarray*}
+% However, $\pmeas(\{HH,TH\})$ is a proper subset of $\pmeas(\{HH\})+\pmeas(\{TH\})$
+% because if we check the complement of $\{HH,TH\}$, we have 
+% \begin{eqnarray*}
+%  &  & \pmeas(\{HH,TH\})=1-\pmeas(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
+% \end{eqnarray*}
+% and $\pmeas(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
+% of $\{HH\}$ and $\{TH\}$ individually.
 

### 2016-05-05 prob.tex
prob.tex "Set-valued Probability Measures" Cherry pick 48f296c to revise

@@
 \qed\end{example}
+
+If we consider set with more values, the probability measure may give
+us more information about the coins. For example, despite $\imposs$
+and $\poss$, we may also adopt three more values: $\unlikely$\ as
+the interval~$\left(0,\frac{1}{2}\right]$, $\likely$\ as the interval~$\left(\frac{1}{2},1\right]$,
+and $\overflow$\ as the empty set~$\emptyset$ which means the
+total probability may be excessed than one. In particular, $\likely\vee\likely=\overflow$
+because the probability of two disjoint events should not both bigger
+than $\frac{1}{2}$. The complete rule for operator~$\vee$ on $\mathscr{L}_{5}=\left\{ \imposs,\poss,\unlikely,\likely,\overflow\right\} $
+is defined in table~\ref{tab:The-operator-on}, or more abstractly,
+we define $(a,b]\vee(c,d]=(a+c,b+d]\cap[0,1]$. The definition of
+a probability measure can be modified as a function $\pmeas:\events\rightarrow\mathscr{L}_{5}$
+such that: 
+\begin{itemize}
+\item $\pmeas(\Omega)\in\left\{ \poss,\likely\right\} $ or equivalently
+$1\in\pmeas(\Omega)$, and 
+\item for a collection $E_{i}$, of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\bigvee_{i}\pmeas(E_{i})$. 
+\end{itemize}
+\begin{table}
+\center{%
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline 
+$\vee$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
+\hline 
+\hline 
+$\imposs$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
+\hline 
+$\poss$ & $\poss$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
+\hline 
+$\unlikely$ & $\unlikely$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
+\hline 
+$\likely$ & $\likely$ & $\likely$ & $\likely$ & $\overflow$ & $\overflow$\tabularnewline
+\hline 
+$\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$\tabularnewline
+\hline 
+\end{tabular}}
+
+\caption{\label{tab:The-operator-on}The operator~$\vee$ on $\mathscr{L}_{5}=\left\{ \imposs,\poss,\unlikely,\likely,\overflow\right\} $}
+\end{table}
+\begin{example}{[}Two-coin probability space with $\mathscr{L}_{5}$-valued
+probability measure{]} Under the new $\mathscr{L}_{5}$-valued requirement,
+the probability measure in the first example becomes: 
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) & = & \imposs\\
+\pmeas(\{HH\}) & = & \unlikely\\
+\pmeas(\{HT\}) & = & \imposs\\
+\pmeas(\{TH\}) & = & \likely\\
+\pmeas(\{TT\}) & = & \imposs\\
+\pmeas(\{HH,HT\}) & = & \unlikely\\
+\pmeas(\{HH,TH\}) & = & \likely\\
+\pmeas(\{HH,TT\}) & = & \unlikely
+\end{array} & \begin{array}{rcl}
+\pmeas(\{HT,TH\}) & = & \likely\\
+\pmeas(\{HT,TT\}) & = & \imposs\\
+\pmeas(\{TH,TT\}) & = & \likely\\
+\pmeas(\{HH,HT,TH\}) & = & \likely\\
+\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
+\pmeas(\{HH,TH,TT\}) & = & \likely\\
+\pmeas(\{HT,TH,TT\}) & = & \likely\\
+\pmeas(\{HH,HT,TH,TT\}) & = & \likely
+\end{array}\end{array}
+\]
+In this example, we can get the information that the first coin is
+weighted and the second coin is double-headed. \qed\end{example}
+
+We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
 

### 2016-05-05 prob.tex
prob.tex \section{Classical Probability Spaces} something like this?

--- 2016-05-04 prob.tex
@@
 Instead of using every point in the real interval $[0,1]$ we can
-partition the interval into disjoint sets and only consider
-probability measures up to set membership. The simplest such situation
-is to partition the interval $[0,1]$ into $\{0\}$ (which we will call
-$\imposs$) and the half-open interval $(0,1]$ (which we will call
-$\poss$). The addition that was used to aggregate probabilities is now
-abstracted to $\vee$ such that $x \vee y=\imposs$ if and only if
-$x=y=\imposs$. We will call the resulting set
-$\left\{ \imposs, \poss\right\}$ together with the with associated
-operation $\vee$, the set $\mathscr{L}_{2}$. The definition of a
-probability measure in this case is modified to a function
-$\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
-\begin{itemize}
-\item $\pmeas(\Omega) = \poss$, and
-\item for a collection $E_i$ of pairwise disjoint events, $\pmeas(\bigcup_i
-E_i) = \bigvee_i \pmeas(E_i)$.
-\end{itemize}
-
-\begin{example}[Two-coin probability space with finite set-valued
-  probability measure] \label{ex2} Under the new set-valued
-  requirement, the probability measure in the first example becomes:
-\[\begin{array}{c@{\qquad\qquad}c}
+consider subsets~$\mathscr{L}$ of $[0,1]$ and only consider probability
+measures up to set membership with intuitive addition\footnote{Notice that the set-valued measure in~\cite{Artstein1972,PuriRalescu1983},
+only require $I_{1}+I_{2}=\left\{ a_{1}+a_{2}\middle|a_{1}\in I_{1},a_{2}\in I_{2}\right\} $
+because they focused on measure theory. In probability thoery, $2\in\pmeas\left(E\right)$
+doesn't really make sense so that we consider intersect $[0,1]$ in
+our definition.} 
+\[
+I_{1}+I_{2}=\left\{ a_{1}+a_{2}\middle|a_{1}\in I_{1},a_{2}\in I_{2}\right\} \cap[0,1]\textrm{ .}
+\]
+Then, a probability measure in this case is modified to a function
+$\pmeas:\events\rightarrow\mathscr{L}$ such that: 
+\begin{itemize}
+\item $1\in\pmeas(\Omega)$, and 
+\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$. 
+\end{itemize}
+The simplest such situation is to partition the interval $[0,1]$
+into $\{0\}$ (which we will call $\imposs$) and the half-open interval
+$(0,1]$ (which we will call $\poss$). We will call the resulting
+set $\left\{ \imposs,\poss\right\} $, the set $\mathscr{L}_{2}$.
+
+\begin{example}{[}Two-coin probability space with finite set-valued
+probability measure{]} \label{ex2} Under the new set-valued requirement,
+the probability measure in the first example becomes: 
+\[
+\begin{array}{c@{\qquad\qquad}c}
 \begin{array}{rcl}
-\pmeas(\emptyset) &=& \imposs \\
-\pmeas(\{ HH \}) &=& \poss \\
-\pmeas(\{ HT \}) &=& \imposs \\
-\pmeas(\{ TH \}) &=& \poss \\
-\pmeas(\{ TT \}) &=& \imposs \\
-\pmeas(\{  HH, HT \}) &=& \poss \\
-\pmeas(\{  HH, TH \}) &=& \poss \\
-\pmeas(\{  HH , TT \}) &=& \poss \\
+\pmeas(\emptyset) & = & \imposs\\
+\pmeas(\{HH\}) & = & \poss\\
+\pmeas(\{HT\}) & = & \imposs\\
+\pmeas(\{TH\}) & = & \poss\\
+\pmeas(\{TT\}) & = & \imposs\\
+\pmeas(\{HH,HT\}) & = & \poss\\
+\pmeas(\{HH,TH\}) & = & \poss\\
+\pmeas(\{HH,TT\}) & = & \poss
 \end{array} & \begin{array}{rcl}
-\pmeas(\{  HT, TH \}) &=& \poss \\
-\pmeas(\{  HT , TT \}) &=& \imposs \\
-\pmeas(\{  TH , TT \}) &=& \poss \\
-\pmeas(\{  HH, HT, TH \}) &=& \poss \\
-\pmeas(\{  HH, HT, TT \}) &=& \poss \\
-\pmeas(\{  HH, TH, TT \}) &=& \poss \\
-\pmeas(\{  HT, TH, TT \}) &=& \poss \\
-\pmeas(\{  HH, HT, TH, TT \}) &=& \poss 
-\end{array}
-\end{array}\]
-Despite the fact that we have lost all numeric information, the
-probability measure still reveals that the second coin is
-double-headed. We have however lost the information regarding the bias
-in the first coin. This information can be recovered with a more
-refined probability measure as we show next.  
-\qed\end{example}
+\pmeas(\{HT,TH\}) & = & \poss\\
+\pmeas(\{HT,TT\}) & = & \imposs\\
+\pmeas(\{TH,TT\}) & = & \poss\\
+\pmeas(\{HH,HT,TH\}) & = & \poss\\
+\pmeas(\{HH,HT,TT\}) & = & \poss\\
+\pmeas(\{HH,TH,TT\}) & = & \poss\\
+\pmeas(\{HT,TH,TT\}) & = & \poss\\
+\pmeas(\{HH,HT,TH,TT\}) & = & \poss
+\end{array}\end{array}
+\]
+Despite the fact that we have lost all numeric information, the probability
+measure still reveals that the second coin is double-headed. We have
+however lost the information regarding the bias in the first coin.
+This information can be recovered with a more refined probability
+measure as we show next. \qed\end{example}
+
+Although $\mathscr{L}_{2}$-valued probability measure is quite intuitive,
+set-valued probability measure is not that intuitive if we extend
+to more values. For example, consider the following three \emph{overlapping}
+closed sub-intervals: $[0,0]$ is still call \imposs, $[0,\frac{1}{2}]$
+which we call \unlikely, ad $[\frac{1}{2},1]$ which we call \likely.
+The following example is a set-valued probability measure corresponding
+to the probability measure in the first example.
+
+\begin{example}\label{Two-coin-set-valued-again}{[}Two-coin probability
+space with set-valued probability measure, again{]} 
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) & = & \imposs\\
+\pmeas(\{HH\}) & = & \unlikely\\
+\pmeas(\{HT\}) & = & \imposs\\
+\pmeas(\{TH\}) & = & \likely\\
+\pmeas(\{TT\}) & = & \imposs\\
+\pmeas(\{HH,HT\}) & = & \unlikely\\
+\pmeas(\{HH,TH\}) & = & \likely\\
+\pmeas(\{HH,TT\}) & = & \unlikely
+\end{array} & \begin{array}{rcl}
+\pmeas(\{HT,TH\}) & = & \likely\\
+\pmeas(\{HT,TT\}) & = & \imposs\\
+\pmeas(\{TH,TT\}) & = & \likely\\
+\pmeas(\{HH,HT,TH\}) & = & \likely\\
+\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
+\pmeas(\{HH,TH,TT\}) & = & \likely\\
+\pmeas(\{HT,TH,TT\}) & = & \likely\\
+\pmeas(\{HH,HT,TH,TT\}) & = & \likely
+\end{array}\end{array}
+\]
+In this example, we can get the information that the first coin is
+weighted and the second coin is double-headed. However, we may notice
+that the set-valued probability of the whole space~$\{HH,HT,TH,TT\}$
+are different between these two examples. This problem can be fixed
+when we moved on to the next section. \qed\end{example}
+
+We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
 
 %%%%%
+
 \subsection{Interval-valued probability measures}
 
-A natural generalization of the disjoint set-valued measure above is
-to allow the sets to overlap. In this case, we split the interval
-$[0,1]$ in a collection of \emph{overlapping} closed
-sub-intervals. First we illustrate the main ideas using a simple
-example.
-
-\begin{example}[Two-coin probability space with four
-  intervals] \label{ex3} We split the unit interval $[0,1]$ in the
-  following four closed sub-intervals: $[0,0]$ which we call \imposs,
-  $[0,\frac{1}{2}]$ which we call \unlikely, $[\frac{1}{2},1]$ which
-  we call \likely, and $[1,1]$ which we call \necess.  Using these new
-  values, we can modify the probability measure of Ex.~\ref{ex1} by
-  mapping each numeric value to the smallest sub-interval containing
-  it to get the following:
+The singleton closed interval $[0,0]$ is a required spacial value
+for empty set, and a natural generalization is to consider another
+special closed interval $[1,1]$ which we call \necess for the whole
+space. In general, if the probability of an event $E$ is $[a,b]$,
+we think of the left-endpoint~$a$ as representing the strength of
+the evidence that supports $E$, and the right-endpoint~$b$ as the
+strength of the evidence that contradicts $E$.
+
+Thus if we have an event $E$ with probability $[a,b]$ where $a=0.1$
+and $b=0.7$, we have that: 
+\begin{itemize}
+\item the strength of evidence supporting $E$ is 0.1; since either $E$
+or its complement must happen, we conclude that there is 0.9 evidence
+supporting the complement of $E$; 
+\item the strength of evidence contradicting $E$ is 0.7; again since either
+$E$ or its complement must happen, we conclude that there is 0.3
+evidence contradicting the complement of $E$. 
+\end{itemize}
+\yutsung{Do we use the law of excluded middle here? You remind me
+Agda : ) Did Homotopy Type Theory people said anything about the probability?}\\
+Turning things around, the strength of evidence that contradicts $E$
+is evidence supporting the complement of $E$. The complement of $E$
+must therefore have probability $\left[1-b,1-a\right]$ which we abbreviate
+$1-\left[a,b\right]$, so the probability measure $\pmeas$ should
+satisfy:
+\begin{itemize}
+\item $\pmeas(\emptyset)=[0,0]$, 
+\item $\pmeas(\Omega)=[1,1]$, and 
+\item $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
+\end{itemize}
+However, if we want $\pmeas(\Omega)=[1,1]$, and the probability assignment
+for singlton sets $\pmeas(\{HH\})=\unlikely$, $\pmeas(\{HT\})=\imposs$,
+$\pmeas(\{TH\})=\likely$, and $\pmeas(\{TT\})=\imposs$ as in example~\ref{Two-coin-set-valued-again},
+we only have $\pmeas(\Omega)\subsetneq\pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})$.
+In general, we only require
+\begin{itemize}
+\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
+\end{itemize}
+This statement means that the evidences of $\bigcup_{i}E_{i}$ is
+at least as strong as putting all the evidences of $E_{i}$ together,
+but some evidence may only be acquired for $\bigcup_{i}E_{i}$ as
+the whole. Therefore, $\pmeas\left(\bigcup_{i}E_{i}\right)$ is a
+subset of $\sum_{i}\pmeas\left(E_{i}\right)$, but may not equal.
+In our example, 
+\begin{eqnarray*}
+ &  & \pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})\\
+ & = & \imposs+\unlikely+\imposs+\likely\\
+ & = & \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=\left[\frac{1}{2},\frac{3}{2}\right]
+\end{eqnarray*}
+The above equation told us $\pmeas(\Omega)\subseteq\left[\frac{1}{2},\frac{3}{2}\right]$.
+However, because of $\pmeas(\emptyset)=\imposs$, we have $\pmeas\left(\Omega\right)=1-\pmeas\left(\emptyset\right)=\necess$,
+but $\pmeas(\emptyset)=\imposs$ cannot be used to reasoning the probability
+of $\{HH\}$, $\{HT\}$, $\{TH\}$ and $\{TT\}$ individually. The
+full probability assignment is shown in the following example.
+
+\begin{example}{[}Two-coin probability space with four intervals{]}
+\label{ex3} We split the unit interval $[0,1]$ in the following
+four closed sub-intervals: $[0,0]$ which we call \imposs, $[0,\frac{1}{2}]$
+which we call \unlikely, $[\frac{1}{2},1]$ which we call \likely,
+and $[1,1]$ which we call \necess. Using these new values, we can
+modify the probability measure of Ex.~\ref{ex1} by mapping each
+numeric value to the smallest sub-interval containing it to get the
+following: 
 \[
@@
 \]
-This probability measure is more informative than the one in
-Ex.~\ref{ex2}: not only does it reveal that the second coin is
-double-headed but it also reveals the bias in the first coin.
-\qed\end{example}
-
-The probability measure above appears quite intuitive but it is not
-really evident that it is well-defined. For example, how do we justify
-the following combination of assignments:
-\[ 
-\pmeas(\{HH\}) = \unlikely, \quad\pmeas(\{TH\}) = \likely, \quad
-\pmeas(\{HH\}\cup\{TH\}) = \necess 
-\]
-which assert that an \unlikely-event whose probability is in the range
-$[0,\frac{1}{2}]$ and a \likely-event whose probability is in the
-range $[\frac{1}{2},1]$ combine to a \necess-event whose probability
-is in the range $[1,1]$. To understand the calculation, we provide the
-formal definition of a probability measure in this case.
-
-Fix a collection $\mathscr{I}$ of closed sub-intervals of $[0,1]$ that
-must include $[0,0]$ and $[1,1]$. An $\mathscr{I}$--interval-valued
-probability measure is a function
-$\mu : \events \rightarrow \mathscr{I}$ such that:
-\begin{itemize}
-\item $\mu(\emptyset) = [0,0]$, 
-\item $\mu(\Omega) = [1,1]$, and 
-\item for any mutually disjoint events $E_1$, $E_2$, $E_3$, and $E_4$
-  where $\pmeas(E_i) = [l_i,h_i]$ and where
-  $E_1 \cup E_2 \cup E_3 \cup E_4 = \Omega$, we have:
-\[
-\pmeas(\{E_1\cup E_2\}) \subseteq
-  [\max(l_1+l_2 , 1-(h_3+h_4)), \min(h_1+h_2 , 1-(l_3+l_4))]
-\]
-We view the events $E_1$ and $E_2$ as providing evidence for the
-combined event $E_1\cup E_2$: their values set positive bounds on the
-resulting interval. But as $E_3 \cup E_4$ is the complement of
-$E_1 \cup E_2$, the events $E_3$ and $E_4$ provide negative bounds on
-the resulting interval. The calculated interval may not be in our
-fixed set $\mathscr{I}$ of chosen intervals so we embed it in the
-smallest existing interval.
-\end{itemize}
+This probability measure is more informative than the one in Ex.~\ref{ex2}:
+not only does it reveal that the second coin is double-headed but
+it also reveals the bias in the first coin. \qed\end{example}
 

### 2016-05-06 prob.tex
mess

@@
 
-\makeatletter
-\newtheoremstyle{indented}
-  {3pt}% space before
-  {3pt}% space after
-  {\addtolength{\@totalleftmargin}{3.5em}
-   \addtolength{\linewidth}{-3.5em}
-   \parshape 1 3.5em \linewidth}% body font
-  {}% indent
-  {\bfseries}% header font
-  {.}% punctuation
-  {.5em}% after theorem header
-  {}% header specification (empty for default)
-\makeatother
-\theoremstyle{indented}
-%% \theoremstyle{remark}
+% \makeatletter
+% \newtheoremstyle{indented}
+%   {3pt}% space before
+%   {3pt}% space after
+%   {\addtolength{\@totalleftmargin}{3.5em}
+%    \addtolength{\linewidth}{-3.5em}
+%    \parshape 1 3.5em \linewidth}% body font
+%   {}% indent
+%   {\bfseries}% header font
+%   {.}% punctuation
+%   {.5em}% after theorem header
+%   {}% header specification (empty for default)
+% \makeatother
+% \theoremstyle{indented}
+\theoremstyle{remark}
 \newtheorem{example}{Example}
@@
 \begin{document}
-\title{Discrete Probability for Discrete Quantum Computing}
+\title{Discrete Probability for Discrete Quantum Theories}
 \author{}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Classical Probability Spaces}
 
-We review the conventional presentation of probability spaces and then
-discuss several variations that avoid using the real interval $[0,1]$.
+A \emph{probability space} specifies the necessary conditions for
+reasoning coherently about collections of uncertain events.  We review
+the conventional presentation of probability spaces and then discuss
+several variations that avoid using the real interval $[0,1]$.
 
@@
 
-A \emph{probability
-  space}~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
-specifies the necessary conditions for reasoning coherently about
-collections of uncertain events. It consists of a \emph{sample space}
-$\Omega$, a space of \emph{events}~$\events$, and a \emph{probability
-  measure}~$\pmeas$. In this paper, we will only consider
-\emph{finite} sets of events: we therefore define a sample space
-$\Omega$ as an arbitrary non-empty finite set and the space of events
-$\events$ as $2^\Omega$, the powerset of $\Omega$. Given the set of
-events $\events$, a \emph{probability measure} is a function
+The conventional definition of a probability
+space~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
+builds upon the real numbers. In more detail, a probability space
+consists of a \emph{sample space} $\Omega$, a space of
+\emph{events}~$\events$, and a \emph{probability measure}~$\pmeas$
+mapping events in $\events$ to the real interval $[0,1]$. In this
+paper, we will only consider \emph{finite} sets of events: we
+therefore restrict our attention to non-empty finite sets $\Omega$ as
+the sample space. The space of events $\events$ includes every
+possible subset of $\Omega$: it is the powerset~$2^\Omega$. Given the
+set of events $\events$, a \emph{probability measure} is a function
 $\pmeas : \events \rightarrow [0,1]$ such that:
@@
 % using base 16 directly.}
-Therefore, in a resource-aware setting, it is more appropriate to
-consider probability measures that map events to a finite set of
-elements computable with a fixed set of resources. We will consider
-two approaches: set-valued probability
-measures~\cite{Artstein1972,PuriRalescu1983} and interval-valued
-probability
+Therefore, in a resource-aware computational or experimental setting,
+it is more appropriate to consider probability measures that map
+events to a finite set of elements computable with a fixed set of
+resources. We will consider two approaches from the literature:
+set-valued probability measures~\cite{Artstein1972,PuriRalescu1983}
+and interval-valued probability
 measures~\cite{Dempster1967,Zadeh1986,Weichselberger2000,JamisonLodwick2004}.
@@
 
-Instead of using every point in the real interval $[0,1]$ we can
-consider subsets~$\mathscr{L}$ of $[0,1]$ and only consider probability
-measures up to set membership with intuitive addition\footnote{Notice that the set-valued measure in~\cite{Artstein1972,PuriRalescu1983},
-only require $I_{1}+I_{2}=\left\{ a_{1}+a_{2}\middle|a_{1}\in I_{1},a_{2}\in I_{2}\right\} $
-because they focused on measure theory. In probability thoery, $2\in\pmeas\left(E\right)$
-doesn't really make sense so that we consider intersect $[0,1]$ in
-our definition.} 
-\[
-I_{1}+I_{2}=\left\{ a_{1}+a_{2}\middle|a_{1}\in I_{1},a_{2}\in I_{2}\right\} \cap[0,1]\textrm{ .}
-\]
-Then, a probability measure in this case is modified to a function
+Instead of using every point in the real interval $[0,1]$ as a
+potential value for a probability measure, we can lump points together
+in sets and consider probability measures up to set membership. The
+simplest such situation is to partition the interval $[0,1]$ into two
+sets: the set $\{0\}$ (which we will call $\imposs$) and the set
+containing all the points in the half-open interval $(0,1]$ (which we
+will call $\poss$). We will call the resulting collection
+$\left\{ \imposs,\poss\right\} $, the collection $\mathscr{L}_{2}$. To
+completely specify a probability space, we also need to specify how to
+``add'' the probabilities in $\mathscr{L}_2$. Given two subsets of the
+real interval, $I_1$ and $I_2$, the general formula for adding them
+is:\footnote{Notice that the set-valued measure
+  in~\cite{Artstein1972,PuriRalescu1983}, only require
+  $I_{1}+I_{2}=\left\{ a_{1}+a_{2}\middle|a_{1}\in I_{1},a_{2}\in
+    I_{2}\right\} $
+  because they focused on measure theory. In probability theory,
+  $2\in\pmeas\left(E\right)$ doesn't really make sense so that we
+  consider intersect $[0,1]$ in our definition.}
+\[
+I_{1} \vee I_{2}=\left\{ x+y~\middle|~ x \in I_{1}, y \in I_{2}\right\} ~\cap~ [0,1]\textrm{ .}
+\]
+In the case of $\mathscr{L}_2$, this reduces to $x \vee y = \imposs$
+iff $x = y = \imposs$.
+
+\amr{
+From Puri and Ralescu's paper: Fix $n=1$ (only 1-dimension). Conditions on $\mu$:
+\begin{itemize}
+\item $\mu(E) \neq \emptyset$ for every $E \in \events$, 
+\item $1 \in \mu(\Omega)$, 
+\item for every disjoint family $A_i$ we have, $\mu(\bigcup_i A_i) =
+  \sum_i \mu(A_i)$
+\end{itemize}
+where the sum of subsets of $\mathbb{R}$ (not $\mathbb{R}^n$ as in the
+paper) is as follows. Let $X$ and $Y$ be subsets of $\mathbb{R}$, then
+$X + Y = \{ x + y ~|~ x \in X, y \in Y \}$
+}
+
+To summarize, an $\mathscr{L}$-valued probability is a function
 $\pmeas:\events\rightarrow\mathscr{L}$ such that:
@@
 \item $1\in\pmeas(\Omega)$, and 
-\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$. 
-\end{itemize}
-The simplest such situation is to partition the interval $[0,1]$
-into $\{0\}$ (which we will call $\imposs$) and the half-open interval
-$(0,1]$ (which we will call $\poss$). We will call the resulting
-set $\left\{ \imposs,\poss\right\} $, the set $\mathscr{L}_{2}$.
+\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\bigvee_i\pmeas(E_{i})$. 
+\end{itemize}
 
@@
 However, if we want $\pmeas(\Omega)=[1,1]$, and the probability assignment
-for singlton sets $\pmeas(\{HH\})=\unlikely$, $\pmeas(\{HT\})=\imposs$,
+for singleton sets $\pmeas(\{HH\})=\unlikely$, $\pmeas(\{HT\})=\imposs$,
 $\pmeas(\{TH\})=\likely$, and $\pmeas(\{TT\})=\imposs$ as in example~\ref{Two-coin-set-valued-again},
@@
 % have a probability $[\frac{1}{3},\frac{1}{3}]$ because it is necessary
-% that $A_1$ is not in that range. Similary, the event that some employee's age is
+% that $A_1$ is not in that range. Similarly, the event that some employee's age is
 % \emph{not} in the range $\{23,24\}$ is

### 2016-05-07 prob.tex
buffon

@@
 events to a finite set of elements computable with a fixed set of
-resources. We will consider two approaches from the literature:
-set-valued probability measures~\cite{Artstein1972,PuriRalescu1983}
-and interval-valued probability
+resources. We expand on this observation and then consider two
+approaches from the literature: set-valued probability
+measures~\cite{Artstein1972,PuriRalescu1983} and interval-valued
+probability
 measures~\cite{Dempster1967,Zadeh1986,Weichselberger2000,JamisonLodwick2004}.
+
+%%%%%
+\subsection{Buffon's Needle Problem}
+
+Suppose we drop a needle of length $\ell$ onto a floor made of equally
+spaced parallel lines a distance $\ell$ apart. It is a known fact that
+the probability of the needle crossing a line is
+$\frac{2}{\pi} = 0.6366197723675814$. We analyze this situation in the
+mathematical framework of probability spaces paying special attention
+to the resources needed to estimate the probability computationally or
+experimentally.
+
+To formalize the experiment, we consider an experimental setup
+consisting of a collection of $N$ identical needles of length
+$\ell$. We throw the $N$ needles and observe the number $X$ of needles
+that cross a line. The sample space can be expressed as the set
+$(X|-)^N$ of sequences of characters of length $N$ where each
+character is either $X$ to indicate a needle crossing a line or $-$ to
+indicate a needle not crossing a line. If $N=3$, the event that
+exactly 2 needles cross lines is $\{-XX,X-X,XX-\}$: it has
+probability~$\frac{2}{3}$. Generally, the event that exactly $M$
+needles out of the $N$ total needles cross lines is $\frac{M}{N}$.
+
+In an actual experiment with 500 needles, it was found that 321
+crossed a line which gives a probability of $0.642$. In a larger
+experiment with $3408$ needles, the probability was
+$0.6366197193098592$. Comparing the values to the idealized
+mathematical value, we see that the observed probability approaches
+$\frac{2}{\pi}$ but only if \emph{larger and larger resources} are
+expended.
+
+These resource considerations thus lead us to replace the real
+interval $[0,1]$ with intervals of confidence which contain the
+probability. The intuition is that the precision of the interval will
+depend on the amount of resources allocated for the measurement.
 

### 2016-05-07 prob.tex
buffon nice

@@
 These resource considerations thus lead us to replace the real
-interval $[0,1]$ with intervals of confidence which contain the
-probability. The intuition is that the precision of the interval will
-depend on the amount of resources allocated for the measurement.
+interval $[0,1]$ with rational numbers up to a certain precision.  The
+intuition is that the precision depends on the amount of resources
+allocated for the measurement process.
+
+There is however another more subtle source of unbounded computational
+power in the experiment. We are assuming that we can always determine
+with certainty whether a needle is crossing a line. But ``lines'' on
+the the floor have thickness, their distance apart is not exactly
+$\ell$. and the needles lengths are not all equal and are not all
+absolutely equal to $\ell$. These perturbations make the events
+``fuzzy.'' For example, instead of talking about the idealized event
+that exactly $M$ needles cross lines, we might instead talk about the
+event that $M-\delta$ needles evidently cross lines and $M+\delta'$
+needles plausibly cross lines. This fuzzy notion of events leads us to
+consider intervals of probability reflecting the certainty of the
+event and its plausibility.
 

### 2016-05-07 prob.tex
prob.tex Add some comments...

@@
 the probability of the needle crossing a line is
-$\frac{2}{\pi} = 0.6366197723675814$. We analyze this situation in the
+$\frac{2}{\pi} = 0.6366197723675814$. 
+\\
+\yutsung{Add $\ldots$ at the end? }\\
+We analyze this situation in the
 mathematical framework of probability spaces paying special attention
@@
 that cross a line. The sample space can be expressed as the set
-$(X|-)^N$ of sequences of characters of length $N$ where each
+$(X|-)^N$ \\
+\yutsung{Use more physical or mathematical notation?}\\
+of sequences of characters of length $N$ where each
 character is either $X$ to indicate a needle crossing a line or $-$ to
@@
 experiment with $3408$ needles, the probability was
-$0.6366197193098592$. Comparing the values to the idealized
+$0.6366197193098592$. 
+\\
+\yutsung{Add $\ldots$ at the end? }\\
+Comparing the values to the idealized
 mathematical value, we see that the observed probability approaches
@@
 $X + Y = \{ x + y ~|~ x \in X, y \in Y \}$
-}
+}\\
+\yutsung{Actually, using $X+Y=\{x+y~|~x\in X,y\in Y\}$ directly
+might be more confusing than I thought... Because our example will
+be follows:
+
+For $\{0\}=\imposs$ and $(0,\infty)=\poss$, it will become
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) & = & \{0\}\\
+\pmeas(\{HH\}) & = & (0,\infty)\\
+\pmeas(\{HT\}) & = & \{0\}\\
+\pmeas(\{TH\}) & = & (0,\infty)\\
+\pmeas(\{TT\}) & = & \{0\}\\
+\pmeas(\{HH,HT\}) & = & (0,\infty)\\
+\pmeas(\{HH,TH\}) & = & (0,\infty)\\
+\pmeas(\{HH,TT\}) & = & (0,\infty)
+\end{array} & \begin{array}{rcl}
+\pmeas(\{HT,TH\}) & = & (0,\infty)\\
+\pmeas(\{HT,TT\}) & = & \{0\}\\
+\pmeas(\{TH,TT\}) & = & (0,\infty)\\
+\pmeas(\{HH,HT,TH\}) & = & (0,\infty)\\
+\pmeas(\{HH,HT,TT\}) & = & (0,\infty)\\
+\pmeas(\{HH,TH,TT\}) & = & (0,\infty)\\
+\pmeas(\{HT,TH,TT\}) & = & (0,\infty)\\
+\pmeas(\{HH,HT,TH,TT\}) & = & (0,\infty)
+\end{array}\end{array}
+\]
+
+For $\{0\}=\imposs$ and $(0,1]=\poss$, it will become the following
+and gives an extra-value~$(0,2]$.
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) & = & \{0\}\\
+\pmeas(\{HH\}) & = & (0,1]\\
+\pmeas(\{HT\}) & = & \{0\}\\
+\pmeas(\{TH\}) & = & (0,1]\\
+\pmeas(\{TT\}) & = & \{0\}\\
+\pmeas(\{HH,HT\}) & = & (0,1]\\
+\pmeas(\{HH,TH\}) & = & (0,2]\\
+\pmeas(\{HH,TT\}) & = & (0,1]
+\end{array} & \begin{array}{rcl}
+\pmeas(\{HT,TH\}) & = & (0,1]\\
+\pmeas(\{HT,TT\}) & = & \{0\}\\
+\pmeas(\{TH,TT\}) & = & (0,1]\\
+\pmeas(\{HH,HT,TH\}) & = & (0,2]\\
+\pmeas(\{HH,HT,TT\}) & = & (0,1]\\
+\pmeas(\{HH,TH,TT\}) & = & (0,2]\\
+\pmeas(\{HT,TH,TT\}) & = & (0,1]\\
+\pmeas(\{HH,HT,TH,TT\}) & = & (0,2]
+\end{array}\end{array}
+\]
+
+For $\{0\}=\imposs$, $[0,\frac{1}{2}]=\unlikely$, and $[\frac{1}{2},1]=\likely$,
+it will become the following and gives an extra-value~$[\frac{1}{2},\frac{3}{2}]$.
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas(\emptyset) & = & \{0\}\\
+\pmeas(\{HH\}) & = & [0,\frac{1}{2}]\\
+\pmeas(\{HT\}) & = & \{0\}\\
+\pmeas(\{TH\}) & = & [\frac{1}{2},1]\\
+\pmeas(\{TT\}) & = & \{0\}\\
+\pmeas(\{HH,HT\}) & = & [0,\frac{1}{2}]\\
+\pmeas(\{HH,TH\}) & = & [\frac{1}{2},\frac{3}{2}]\\
+\pmeas(\{HH,TT\}) & = & [0,\frac{1}{2}]
+\end{array} & \begin{array}{rcl}
+\pmeas(\{HT,TH\}) & = & [\frac{1}{2},1]\\
+\pmeas(\{HT,TT\}) & = & \{0\}\\
+\pmeas(\{TH,TT\}) & = & [\frac{1}{2},1]\\
+\pmeas(\{HH,HT,TH\}) & = & [\frac{1}{2},\frac{3}{2}]\\
+\pmeas(\{HH,HT,TT\}) & = & [0,\frac{1}{2}]\\
+\pmeas(\{HH,TH,TT\}) & = & [\frac{1}{2},\frac{3}{2}]\\
+\pmeas(\{HT,TH,TT\}) & = & [\frac{1}{2},1]\\
+\pmeas(\{HH,HT,TH,TT\}) & = & [\frac{1}{2},\frac{3}{2}]
+\end{array}\end{array}
+\]
+
+Actually, this approach is more natural to me when I think in measure
+theory, but I guess the readers might be confused if write in this
+way?}
 

### 2016-05-07 prob.tex
sec 2 good more or less

--- 2016-05-07 prob.tex
@@
 \newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
-\newcommand{\necess}{{\mbox{\wesa{necessary}}}}
+\newcommand{\necess}{{\mbox{\wesa{certain}}}}
 \newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
@@
 \begin{document}
-\title{Discrete Probability for Discrete Quantum Theories}
+\title{Interval Probability for Fuzzy Quantum Theories}
 \author{}
@@
 
+Fuzzy quantum mechanics:
+\begin{itemize}
+\item \url{http://cds.cern.ch/record/518511/files/0107054.pdf}
+\item \url{http://link.springer.com/chapter/10.1007%2F978-3-642-35644-5_18#page-1}
+\item \url{http://link.springer.com/chapter/10.1007%2F978-3-540-93802-6_20#page-1}
+\item \url{http://www.du.edu/nsm/departments/mathematics/media/documents/preprints/m0412.pdf}
+\item \url{http://www.space-lab.ru/files/pages/PIRT_VII-XII/pages/text/PIRT_X/Bobola.pdf}
+\item \url{http://www.vub.ac.be/CLEA/aerts/publications/1993LiptovskyJan.pdf}
+\end{itemize}
+
+\noindent Pseudo-randomness:
+\begin{itemize}
+\item
+  \url{https://people.csail.mit.edu/silvio/Selected%20Scientific%20Papers/Pseudo%20Randomness/How_To_Generate_Cryptographically_Strong_Sequences_Of_Pseudo-Random_Bits.pdf}:
+  ``the randomness of an event is relative to a specific model of
+  computation with a specified amount of computing resources.''
+\item Another version \url{https://pdfs.semanticscholar.org/3e9c/5f6f48d9ef426655dc799e9b287d754e86c1.pdf}
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the conventional presentation of probability spaces and then discuss
-several variations that avoid using the real interval $[0,1]$.
+the hidden issue of computational and experimental resources.
 
@@
 
-\begin{example}[Two-coin probability space]\label{ex1}
+\begin{example}[Two-coins experiment]\label{ex1}
   Consider an experiment that tosses two coins. We have four possible
@@
 events to a finite set of elements computable with a fixed set of
-resources. We expand on this observation and then consider two
-approaches from the literature: set-valued probability
-measures~\cite{Artstein1972,PuriRalescu1983} and interval-valued
-probability
+resources. We expand on this observation and then consider 
+%% two approaches from the literature: set-valued probability
+%% measures~\cite{Artstein1972,PuriRalescu1983} and 
+interval-valued probability
 measures~\cite{Dempster1967,Zadeh1986,Weichselberger2000,JamisonLodwick2004}.
@@
 spaced parallel lines a distance $\ell$ apart. It is a known fact that
-the probability of the needle crossing a line is
-$\frac{2}{\pi} = 0.6366197723675814$. We analyze this situation in the
-mathematical framework of probability spaces paying special attention
-to the resources needed to estimate the probability computationally or
-experimentally.
+the probability of the needle crossing a line converges to
+$\frac{2}{\pi} = 0.6366197723675814$.
+%% \yutsung{Add $\ldots$ at the end? }\\
+We analyze this situation in the mathematical framework of probability
+spaces paying special attention to the resources needed to estimate
+the probability computationally or experimentally.
 
@@
 that cross a line. The sample space can be expressed as the set
-$(X|-)^N$ of sequences of characters of length $N$ where each
-character is either $X$ to indicate a needle crossing a line or $-$ to
-indicate a needle not crossing a line. If $N=3$, the event that
-exactly 2 needles cross lines is $\{-XX,X-X,XX-\}$: it has
+$(X|-)^N$
+%% \yutsung{Use more physical or mathematical notation?}\\
+of sequences of characters of length $N$ where each character is
+either $X$ to indicate a needle crossing a line or $-$ to indicate a
+needle not crossing a line. If $N=3$, the event that exactly 2 needles
+cross lines is $\{-XX,X-X,XX-\}$: it has
 probability~$\frac{2}{3}$. Generally, the event that exactly $M$
@@
 crossed a line which gives a probability of $0.642$. In a larger
-experiment with $3408$ needles, the probability was
-$0.6366197193098592$. Comparing the values to the idealized
-mathematical value, we see that the observed probability approaches
-$\frac{2}{\pi}$ but only if \emph{larger and larger resources} are
-expended.
+experiment with $3408$ needles, the probability was calculated to be
+$0.6366197193098592$.
+%% \yutsung{Add $\ldots$ at the end? }\\
+Comparing the values to the idealized mathematical value, we see that
+the observed probability approaches $\frac{2}{\pi}$ but only if
+\emph{larger and larger resources} are expended.
 
@@
 intuition is that the precision depends on the amount of resources
-allocated for the measurement process.
+allocated for the measurement process. There is clearly a connection
+between the number of needles and the achievable precision: in the
+hypothetical experiment with 3 needles, it is not sensible to retain
+100 digits in the expansion of $\frac{2}{3}$.
 
@@
 ``fuzzy.'' For example, instead of talking about the idealized event
-that exactly $M$ needles cross lines, we might instead talk about the
-event that $M-\delta$ needles evidently cross lines and $M+\delta'$
-needles plausibly cross lines. This fuzzy notion of events leads us to
-consider intervals of probability reflecting the certainty of the
-event and its plausibility.
+that exactly $M$ needles cross lines which would require the most
+expensive needles built to the most precise accuracy, laser precision
+for drawing lines on the floor, and the most powerful microscopes to
+determine if a needle does cross a line, we might instead talk about
+the event that $M-\delta$ needles evidently cross lines and
+$M+\delta'$ needles plausibly cross lines for some acceptable
+approximations $\delta$ and $\delta'$. This fuzzy notion of events
+leads us to consider intervals of probability reflecting the certainty
+of the event and its plausibility. In the hypothetical experiment with
+3 needles, assume that one needle clearly crossed a line and another
+was close enough to plausibly be considered as crossing the line: we
+would express the probability in this case as the interval
+$[\frac{1}{3},\frac{2}{3}]$ expressing that we are certain that the
+event has probability at least $\frac{1}{3}$ but it is possible that
+it would have probability $\frac{2}{3}$.
+
+% %%%%%
+% \subsection{Set-valued Probability Measures}
+
+% Instead of using every point in the real interval $[0,1]$ as a
+% potential value for a probability measure, we can lump points together
+% in sets and consider probability measures up to set membership. The
+% simplest such situation is to partition the interval $[0,1]$ into two
+% sets: the set $\{0\}$ (which we will call $\imposs$) and the set
+% containing all the points in the half-open interval $(0,1]$ (which we
+% will call $\poss$). We will call the resulting collection
+% $\left\{ \imposs,\poss\right\} $, the collection $\mathscr{L}_{2}$. To
+% completely specify a probability space, we also need to specify how to
+% ``add'' the probabilities in $\mathscr{L}_2$. Given two subsets of the
+% real interval, $I_1$ and $I_2$, the general formula for adding them
+% is:\footnote{Notice that the set-valued measure
+%   in~\cite{Artstein1972,PuriRalescu1983}, only require
+%   $I_{1}+I_{2}=\left\{ a_{1}+a_{2}\middle|a_{1}\in I_{1},a_{2}\in
+%     I_{2}\right\} $
+%   because they focused on measure theory. In probability theory,
+%   $2\in\pmeas\left(E\right)$ doesn't really make sense so that we
+%   consider intersect $[0,1]$ in our definition.}
+% \[
+% I_{1} \vee I_{2}=\left\{ x+y~\middle|~ x \in I_{1}, y \in I_{2}\right\} ~\cap~ [0,1]\textrm{ .}
+% \]
+% In the case of $\mathscr{L}_2$, this reduces to $x \vee y = \imposs$
+% iff $x = y = \imposs$.
+
+% \amr{
+% From Puri and Ralescu's paper: Fix $n=1$ (only 1-dimension). Conditions on $\mu$:
+% \begin{itemize}
+% \item $\mu(E) \neq \emptyset$ for every $E \in \events$, 
+% \item $1 \in \mu(\Omega)$, 
+% \item for every disjoint family $A_i$ we have, $\mu(\bigcup_i A_i) =
+%   \sum_i \mu(A_i)$
+% \end{itemize}
+% where the sum of subsets of $\mathbb{R}$ (not $\mathbb{R}^n$ as in the
+% paper) is as follows. Let $X$ and $Y$ be subsets of $\mathbb{R}$, then
+% $X + Y = \{ x + y ~|~ x \in X, y \in Y \}$
+% }\\
+% \yutsung{Actually, using $X+Y=\{x+y~|~x\in X,y\in Y\}$ directly
+% might be more confusing than I thought... Because our example will
+% be follows:
+
+% For $\{0\}=\imposs$ and $(0,\infty)=\poss$, it will become
+% \[
+% \begin{array}{c@{\qquad\qquad}c}
+% \begin{array}{rcl}
+% \pmeas(\emptyset) & = & \{0\}\\
+% \pmeas(\{HH\}) & = & (0,\infty)\\
+% \pmeas(\{HT\}) & = & \{0\}\\
+% \pmeas(\{TH\}) & = & (0,\infty)\\
+% \pmeas(\{TT\}) & = & \{0\}\\
+% \pmeas(\{HH,HT\}) & = & (0,\infty)\\
+% \pmeas(\{HH,TH\}) & = & (0,\infty)\\
+% \pmeas(\{HH,TT\}) & = & (0,\infty)
+% \end{array} & \begin{array}{rcl}
+% \pmeas(\{HT,TH\}) & = & (0,\infty)\\
+% \pmeas(\{HT,TT\}) & = & \{0\}\\
+% \pmeas(\{TH,TT\}) & = & (0,\infty)\\
+% \pmeas(\{HH,HT,TH\}) & = & (0,\infty)\\
+% \pmeas(\{HH,HT,TT\}) & = & (0,\infty)\\
+% \pmeas(\{HH,TH,TT\}) & = & (0,\infty)\\
+% \pmeas(\{HT,TH,TT\}) & = & (0,\infty)\\
+% \pmeas(\{HH,HT,TH,TT\}) & = & (0,\infty)
+% \end{array}\end{array}
+% \]
+
+% For $\{0\}=\imposs$ and $(0,1]=\poss$, it will become the following
+% and gives an extra-value~$(0,2]$.
+% \[
+% \begin{array}{c@{\qquad\qquad}c}
+% \begin{array}{rcl}
+% \pmeas(\emptyset) & = & \{0\}\\
+% \pmeas(\{HH\}) & = & (0,1]\\
+% \pmeas(\{HT\}) & = & \{0\}\\
+% \pmeas(\{TH\}) & = & (0,1]\\
+% \pmeas(\{TT\}) & = & \{0\}\\
+% \pmeas(\{HH,HT\}) & = & (0,1]\\
+% \pmeas(\{HH,TH\}) & = & (0,2]\\
+% \pmeas(\{HH,TT\}) & = & (0,1]
+% \end{array} & \begin{array}{rcl}
+% \pmeas(\{HT,TH\}) & = & (0,1]\\
+% \pmeas(\{HT,TT\}) & = & \{0\}\\
+% \pmeas(\{TH,TT\}) & = & (0,1]\\
+% \pmeas(\{HH,HT,TH\}) & = & (0,2]\\
+% \pmeas(\{HH,HT,TT\}) & = & (0,1]\\
+% \pmeas(\{HH,TH,TT\}) & = & (0,2]\\
+% \pmeas(\{HT,TH,TT\}) & = & (0,1]\\
+% \pmeas(\{HH,HT,TH,TT\}) & = & (0,2]
+% \end{array}\end{array}
+% \]
+
+% For $\{0\}=\imposs$, $[0,\frac{1}{2}]=\unlikely$, and $[\frac{1}{2},1]=\likely$,
+% it will become the following and gives an extra-value~$[\frac{1}{2},\frac{3}{2}]$.
+% \[
+% \begin{array}{c@{\qquad\qquad}c}
+% \begin{array}{rcl}
+% \pmeas(\emptyset) & = & \{0\}\\
+% \pmeas(\{HH\}) & = & [0,\frac{1}{2}]\\
+% \pmeas(\{HT\}) & = & \{0\}\\
+% \pmeas(\{TH\}) & = & [\frac{1}{2},1]\\
+% \pmeas(\{TT\}) & = & \{0\}\\
+% \pmeas(\{HH,HT\}) & = & [0,\frac{1}{2}]\\
+% \pmeas(\{HH,TH\}) & = & [\frac{1}{2},\frac{3}{2}]\\
+% \pmeas(\{HH,TT\}) & = & [0,\frac{1}{2}]
+% \end{array} & \begin{array}{rcl}
+% \pmeas(\{HT,TH\}) & = & [\frac{1}{2},1]\\
+% \pmeas(\{HT,TT\}) & = & \{0\}\\
+% \pmeas(\{TH,TT\}) & = & [\frac{1}{2},1]\\
+% \pmeas(\{HH,HT,TH\}) & = & [\frac{1}{2},\frac{3}{2}]\\
+% \pmeas(\{HH,HT,TT\}) & = & [0,\frac{1}{2}]\\
+% \pmeas(\{HH,TH,TT\}) & = & [\frac{1}{2},\frac{3}{2}]\\
+% \pmeas(\{HT,TH,TT\}) & = & [\frac{1}{2},1]\\
+% \pmeas(\{HH,HT,TH,TT\}) & = & [\frac{1}{2},\frac{3}{2}]
+% \end{array}\end{array}
+% \]
+
+% Actually, this approach is more natural to me when I think in measure
+% theory, but I guess the readers might be confused if write in this
+% way?}
+
+% To summarize, an $\mathscr{L}$-valued probability is a function
+% $\pmeas:\events\rightarrow\mathscr{L}$ such that:
+% \begin{itemize}
+% \item $1\in\pmeas(\Omega)$, and 
+% \item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\bigvee_i\pmeas(E_{i})$. 
+% \end{itemize}
+
+% \begin{example}{[}Two-coin probability space with finite set-valued
+% probability measure{]} \label{ex2} Under the new set-valued requirement,
+% the probability measure in the first example becomes: 
+% \[
+% \begin{array}{c@{\qquad\qquad}c}
+% \begin{array}{rcl}
+% \pmeas(\emptyset) & = & \imposs\\
+% \pmeas(\{HH\}) & = & \poss\\
+% \pmeas(\{HT\}) & = & \imposs\\
+% \pmeas(\{TH\}) & = & \poss\\
+% \pmeas(\{TT\}) & = & \imposs\\
+% \pmeas(\{HH,HT\}) & = & \poss\\
+% \pmeas(\{HH,TH\}) & = & \poss\\
+% \pmeas(\{HH,TT\}) & = & \poss
+% \end{array} & \begin{array}{rcl}
+% \pmeas(\{HT,TH\}) & = & \poss\\
+% \pmeas(\{HT,TT\}) & = & \imposs\\
+% \pmeas(\{TH,TT\}) & = & \poss\\
+% \pmeas(\{HH,HT,TH\}) & = & \poss\\
+% \pmeas(\{HH,HT,TT\}) & = & \poss\\
+% \pmeas(\{HH,TH,TT\}) & = & \poss\\
+% \pmeas(\{HT,TH,TT\}) & = & \poss\\
+% \pmeas(\{HH,HT,TH,TT\}) & = & \poss
+% \end{array}\end{array}
+% \]
+% Despite the fact that we have lost all numeric information, the probability
+% measure still reveals that the second coin is double-headed. We have
+% however lost the information regarding the bias in the first coin.
+% This information can be recovered with a more refined probability
+% measure as we show next. \qed\end{example}
+
+% Although $\mathscr{L}_{2}$-valued probability measure is quite intuitive,
+% set-valued probability measure is not that intuitive if we extend
+% to more values. For example, consider the following three \emph{overlapping}
+% closed sub-intervals: $[0,0]$ is still call \imposs, $[0,\frac{1}{2}]$
+% which we call \unlikely, ad $[\frac{1}{2},1]$ which we call \likely.
+% The following example is a set-valued probability measure corresponding
+% to the probability measure in the first example.
+
+% \begin{example}\label{Two-coin-set-valued-again}{[}Two-coin probability
+% space with set-valued probability measure, again{]} 
+% \[
+% \begin{array}{c@{\qquad\qquad}c}
+% \begin{array}{rcl}
+% \pmeas(\emptyset) & = & \imposs\\
+% \pmeas(\{HH\}) & = & \unlikely\\
+% \pmeas(\{HT\}) & = & \imposs\\
+% \pmeas(\{TH\}) & = & \likely\\
+% \pmeas(\{TT\}) & = & \imposs\\
+% \pmeas(\{HH,HT\}) & = & \unlikely\\
+% \pmeas(\{HH,TH\}) & = & \likely\\
+% \pmeas(\{HH,TT\}) & = & \unlikely
+% \end{array} & \begin{array}{rcl}
+% \pmeas(\{HT,TH\}) & = & \likely\\
+% \pmeas(\{HT,TT\}) & = & \imposs\\
+% \pmeas(\{TH,TT\}) & = & \likely\\
+% \pmeas(\{HH,HT,TH\}) & = & \likely\\
+% \pmeas(\{HH,HT,TT\}) & = & \unlikely\\
+% \pmeas(\{HH,TH,TT\}) & = & \likely\\
+% \pmeas(\{HT,TH,TT\}) & = & \likely\\
+% \pmeas(\{HH,HT,TH,TT\}) & = & \likely
+% \end{array}\end{array}
+% \]
+% In this example, we can get the information that the first coin is
+% weighted and the second coin is double-headed. However, we may notice
+% that the set-valued probability of the whole space~$\{HH,HT,TH,TT\}$
+% are different between these two examples. This problem can be fixed
+% when we moved on to the next section. \qed\end{example}
+
+% We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
 
 %%%%%
-\subsection{Set-valued Probability Measures}
-
-Instead of using every point in the real interval $[0,1]$ as a
-potential value for a probability measure, we can lump points together
-in sets and consider probability measures up to set membership. The
-simplest such situation is to partition the interval $[0,1]$ into two
-sets: the set $\{0\}$ (which we will call $\imposs$) and the set
-containing all the points in the half-open interval $(0,1]$ (which we
-will call $\poss$). We will call the resulting collection
-$\left\{ \imposs,\poss\right\} $, the collection $\mathscr{L}_{2}$. To
-completely specify a probability space, we also need to specify how to
-``add'' the probabilities in $\mathscr{L}_2$. Given two subsets of the
-real interval, $I_1$ and $I_2$, the general formula for adding them
-is:\footnote{Notice that the set-valued measure
-  in~\cite{Artstein1972,PuriRalescu1983}, only require
-  $I_{1}+I_{2}=\left\{ a_{1}+a_{2}\middle|a_{1}\in I_{1},a_{2}\in
-    I_{2}\right\} $
-  because they focused on measure theory. In probability theory,
-  $2\in\pmeas\left(E\right)$ doesn't really make sense so that we
-  consider intersect $[0,1]$ in our definition.}
-\[
-I_{1} \vee I_{2}=\left\{ x+y~\middle|~ x \in I_{1}, y \in I_{2}\right\} ~\cap~ [0,1]\textrm{ .}
-\]
-In the case of $\mathscr{L}_2$, this reduces to $x \vee y = \imposs$
-iff $x = y = \imposs$.
-
-\amr{
-From Puri and Ralescu's paper: Fix $n=1$ (only 1-dimension). Conditions on $\mu$:
-\begin{itemize}
-\item $\mu(E) \neq \emptyset$ for every $E \in \events$, 
-\item $1 \in \mu(\Omega)$, 
-\item for every disjoint family $A_i$ we have, $\mu(\bigcup_i A_i) =
-  \sum_i \mu(A_i)$
-\end{itemize}
-where the sum of subsets of $\mathbb{R}$ (not $\mathbb{R}^n$ as in the
-paper) is as follows. Let $X$ and $Y$ be subsets of $\mathbb{R}$, then
-$X + Y = \{ x + y ~|~ x \in X, y \in Y \}$
-}
-
-To summarize, an $\mathscr{L}$-valued probability is a function
-$\pmeas:\events\rightarrow\mathscr{L}$ such that:
-\begin{itemize}
-\item $1\in\pmeas(\Omega)$, and 
-\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\bigvee_i\pmeas(E_{i})$. 
-\end{itemize}
-
-\begin{example}{[}Two-coin probability space with finite set-valued
-probability measure{]} \label{ex2} Under the new set-valued requirement,
-the probability measure in the first example becomes: 
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\pmeas(\emptyset) & = & \imposs\\
-\pmeas(\{HH\}) & = & \poss\\
-\pmeas(\{HT\}) & = & \imposs\\
-\pmeas(\{TH\}) & = & \poss\\
-\pmeas(\{TT\}) & = & \imposs\\
-\pmeas(\{HH,HT\}) & = & \poss\\
-\pmeas(\{HH,TH\}) & = & \poss\\
-\pmeas(\{HH,TT\}) & = & \poss
-\end{array} & \begin{array}{rcl}
-\pmeas(\{HT,TH\}) & = & \poss\\
-\pmeas(\{HT,TT\}) & = & \imposs\\
-\pmeas(\{TH,TT\}) & = & \poss\\
-\pmeas(\{HH,HT,TH\}) & = & \poss\\
-\pmeas(\{HH,HT,TT\}) & = & \poss\\
-\pmeas(\{HH,TH,TT\}) & = & \poss\\
-\pmeas(\{HT,TH,TT\}) & = & \poss\\
-\pmeas(\{HH,HT,TH,TT\}) & = & \poss
-\end{array}\end{array}
-\]
-Despite the fact that we have lost all numeric information, the probability
-measure still reveals that the second coin is double-headed. We have
-however lost the information regarding the bias in the first coin.
-This information can be recovered with a more refined probability
-measure as we show next. \qed\end{example}
-
-Although $\mathscr{L}_{2}$-valued probability measure is quite intuitive,
-set-valued probability measure is not that intuitive if we extend
-to more values. For example, consider the following three \emph{overlapping}
-closed sub-intervals: $[0,0]$ is still call \imposs, $[0,\frac{1}{2}]$
-which we call \unlikely, ad $[\frac{1}{2},1]$ which we call \likely.
-The following example is a set-valued probability measure corresponding
-to the probability measure in the first example.
-
-\begin{example}\label{Two-coin-set-valued-again}{[}Two-coin probability
-space with set-valued probability measure, again{]} 
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\pmeas(\emptyset) & = & \imposs\\
-\pmeas(\{HH\}) & = & \unlikely\\
-\pmeas(\{HT\}) & = & \imposs\\
-\pmeas(\{TH\}) & = & \likely\\
-\pmeas(\{TT\}) & = & \imposs\\
-\pmeas(\{HH,HT\}) & = & \unlikely\\
-\pmeas(\{HH,TH\}) & = & \likely\\
-\pmeas(\{HH,TT\}) & = & \unlikely
-\end{array} & \begin{array}{rcl}
-\pmeas(\{HT,TH\}) & = & \likely\\
-\pmeas(\{HT,TT\}) & = & \imposs\\
-\pmeas(\{TH,TT\}) & = & \likely\\
-\pmeas(\{HH,HT,TH\}) & = & \likely\\
-\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
-\pmeas(\{HH,TH,TT\}) & = & \likely\\
-\pmeas(\{HT,TH,TT\}) & = & \likely\\
-\pmeas(\{HH,HT,TH,TT\}) & = & \likely
-\end{array}\end{array}
-\]
-In this example, we can get the information that the first coin is
-weighted and the second coin is double-headed. However, we may notice
-that the set-valued probability of the whole space~$\{HH,HT,TH,TT\}$
-are different between these two examples. This problem can be fixed
-when we moved on to the next section. \qed\end{example}
-
-We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.
-
-%%%%%
-
 \subsection{Interval-valued probability measures}
 
-The singleton closed interval $[0,0]$ is a required spacial value
-for empty set, and a natural generalization is to consider another
-special closed interval $[1,1]$ which we call \necess for the whole
-space. In general, if the probability of an event $E$ is $[a,b]$,
-we think of the left-endpoint~$a$ as representing the strength of
-the evidence that supports $E$, and the right-endpoint~$b$ as the
-strength of the evidence that contradicts $E$.
-
-Thus if we have an event $E$ with probability $[a,b]$ where $a=0.1$
-and $b=0.7$, we have that: 
-\begin{itemize}
-\item the strength of evidence supporting $E$ is 0.1; since either $E$
-or its complement must happen, we conclude that there is 0.9 evidence
-supporting the complement of $E$; 
-\item the strength of evidence contradicting $E$ is 0.7; again since either
-$E$ or its complement must happen, we conclude that there is 0.3
-evidence contradicting the complement of $E$. 
-\end{itemize}
-\yutsung{Do we use the law of excluded middle here? You remind me
-Agda : ) Did Homotopy Type Theory people said anything about the probability?}\\
-Turning things around, the strength of evidence that contradicts $E$
-is evidence supporting the complement of $E$. The complement of $E$
-must therefore have probability $\left[1-b,1-a\right]$ which we abbreviate
-$1-\left[a,b\right]$, so the probability measure $\pmeas$ should
-satisfy:
+We begin with an analysis explaining how to combine intervals of
+probability. Specifically if we have an event $E_1$ with an interval
+of probability $[l_1,r_1]$ and another disjoint event $E_2$ with an
+interval of probability $[l_2,r_2]$, what is the interval probability
+of the event $E_1 \cup E_2$. The answer is somewhat subtle: although
+it is possible to use the sum of the intervals $[l_1+l_2,r_1+r_2]$ as
+the combined probability, one can do find a much tighter interval if
+information \emph{against} the event (i.e., information about the dual
+event) is also taken into consideration.
+
+For a general event $E$ with probability $[l,r]$, the strength of
+evidence that contradicts $E$ is evidence supporting the complement of
+$E$. The complement of $E$ must therefore have probability
+$\left[1-r,1-l\right]$ which we abbreviate $1-\left[l,r\right]$. Given
+a collection of intervals $\mathscr{I}$, an
+$\mathscr{I}$--interval-valued probability measure is a function
+$\pmeas : \events \rightarrow \mathscr{I}$ such that:
 \begin{itemize}
 \item $\pmeas(\emptyset)=[0,0]$, 
-\item $\pmeas(\Omega)=[1,1]$, and 
-\item $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
+\item $\pmeas(\Omega)=[1,1]$, 
+\item $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$,
+  and 
+\item for a collection $E_{i}$ of pairwise disjoint events, we have
+  $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$
+  where the summation on the right is the summation of intervals that
+  sums the endpoints.
 \end{itemize}
-However, if we want $\pmeas(\Omega)=[1,1]$, and the probability assignment
-for singleton sets $\pmeas(\{HH\})=\unlikely$, $\pmeas(\{HT\})=\imposs$,
-$\pmeas(\{TH\})=\likely$, and $\pmeas(\{TT\})=\imposs$ as in example~\ref{Two-coin-set-valued-again},
-we only have $\pmeas(\Omega)\subsetneq\pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})$.
-In general, we only require
-\begin{itemize}
-\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
-\end{itemize}
-This statement means that the evidences of $\bigcup_{i}E_{i}$ is
-at least as strong as putting all the evidences of $E_{i}$ together,
-but some evidence may only be acquired for $\bigcup_{i}E_{i}$ as
-the whole. Therefore, $\pmeas\left(\bigcup_{i}E_{i}\right)$ is a
-subset of $\sum_{i}\pmeas\left(E_{i}\right)$, but may not equal.
-In our example, 
-\begin{eqnarray*}
- &  & \pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})\\
- & = & \imposs+\unlikely+\imposs+\likely\\
- & = & \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=\left[\frac{1}{2},\frac{3}{2}\right]
-\end{eqnarray*}
-The above equation told us $\pmeas(\Omega)\subseteq\left[\frac{1}{2},\frac{3}{2}\right]$.
-However, because of $\pmeas(\emptyset)=\imposs$, we have $\pmeas\left(\Omega\right)=1-\pmeas\left(\emptyset\right)=\necess$,
-but $\pmeas(\emptyset)=\imposs$ cannot be used to reasoning the probability
-of $\{HH\}$, $\{HT\}$, $\{TH\}$ and $\{TT\}$ individually. The
-full probability assignment is shown in the following example.
-
-\begin{example}{[}Two-coin probability space with four intervals{]}
-\label{ex3} We split the unit interval $[0,1]$ in the following
-four closed sub-intervals: $[0,0]$ which we call \imposs, $[0,\frac{1}{2}]$
-which we call \unlikely, $[\frac{1}{2},1]$ which we call \likely,
-and $[1,1]$ which we call \necess. Using these new values, we can
-modify the probability measure of Ex.~\ref{ex1} by mapping each
-numeric value to the smallest sub-interval containing it to get the
-following: 
+
+% The singleton closed interval $[0,0]$ is a required special value
+% for empty set, and a natural generalization is to consider another
+% special closed interval $[1,1]$ which we call \necess\ for the whole
+% space. In general, if the probability of an event $E$ is $[a,b]$,
+% we think of the left-endpoint~$a$ as representing the strength of
+% the evidence that supports $E$, and the right-endpoint~$b$ as the
+% strength of the evidence that contradicts $E$.
+
+% Thus if we have an event $E$ with probability $[a,b]$ where $a=0.1$
+% and $b=0.7$, we have that: 
+% \begin{itemize}
+% \item the strength of evidence supporting $E$ is 0.1; since either $E$
+% or its complement must happen, we conclude that there is 0.9 evidence
+% supporting the complement of $E$; 
+% \item the strength of evidence contradicting $E$ is 0.7; again since either
+% $E$ or its complement must happen, we conclude that there is 0.3
+% evidence contradicting the complement of $E$. 
+% \end{itemize}
+%% \yutsung{Do we use the law of excluded middle here? You remind me
+%% Agda : ) Did Homotopy Type Theory people said anything about the probability?}\\
+
+% Turning things around, the strength of evidence that contradicts $E$
+% is evidence supporting the complement of $E$. The complement of $E$
+% must therefore have probability $\left[1-b,1-a\right]$ which we
+% abbreviate $1-\left[a,b\right]$, so the probability measure $\pmeas$
+% should satisfy:
+% \begin{itemize}
+% \item $\pmeas(\emptyset)=[0,0]$, 
+% \item $\pmeas(\Omega)=[1,1]$, and 
+% \item $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
+% \end{itemize}
+% However, if we want $\pmeas(\Omega)=[1,1]$, and the probability assignment
+% for singleton sets $\pmeas(\{HH\})=\unlikely$, $\pmeas(\{HT\})=\imposs$,
+% $\pmeas(\{TH\})=\likely$, and $\pmeas(\{TT\})=\imposs$ as in example~\ref{Two-coin-set-valued-again},
+% we only have $\pmeas(\Omega)\subsetneq\pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})$.
+% In general, we only require
+% \begin{itemize}
+% \item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
+% \end{itemize}
+% This statement means that the evidences of $\bigcup_{i}E_{i}$ is
+% at least as strong as putting all the evidences of $E_{i}$ together,
+% but some evidence may only be acquired for $\bigcup_{i}E_{i}$ as
+% the whole. Therefore, $\pmeas\left(\bigcup_{i}E_{i}\right)$ is a
+% subset of $\sum_{i}\pmeas\left(E_{i}\right)$, but may not equal.
+% In our example, 
+% \begin{eqnarray*}
+%  &  & \pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})\\
+%  & = & \imposs+\unlikely+\imposs+\likely\\
+%  & = & \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=\left[\frac{1}{2},\frac{3}{2}\right]
+% \end{eqnarray*}
+% The above equation told us $\pmeas(\Omega)\subseteq\left[\frac{1}{2},\frac{3}{2}\right]$.
+% However, because of $\pmeas(\emptyset)=\imposs$, we have $\pmeas\left(\Omega\right)=1-\pmeas\left(\emptyset\right)=\necess$,
+% but $\pmeas(\emptyset)=\imposs$ cannot be used to reasoning the probability
+% of $\{HH\}$, $\{HT\}$, $\{TH\}$ and $\{TT\}$ individually. The
+% full probability assignment is shown in the following example.
+
+The reason the last condition is expressed using $\subseteq$ is best
+explained using a small example.
+
+\begin{example}[Two-coin experiment with interval probability]
+  \label{ex3} We split the unit interval $[0,1]$ in the following four
+  closed sub-intervals: $[0,0]$ which we call \imposs,
+  $[0,\frac{1}{2}]$ which we call \unlikely, $[\frac{1}{2},1]$ which
+  we call \likely, and $[1,1]$ which we call \necess. Using these new
+  values, we can modify the probability measure of Ex.~\ref{ex1} by
+  mapping each numeric value to the smallest sub-interval containing
+  it to get the following:
 \[
@@
 \]
-This probability measure is more informative than the one in Ex.~\ref{ex2}:
-not only does it reveal that the second coin is double-headed but
-it also reveals the bias in the first coin. \qed\end{example}
+Despite the absence of any numeric information, the probability
+measure is quite informative: it reveals that the second coin is
+double-headed and that the first coin is biased. To understand the
+$\subseteq$-condition, consider the following calculation:
+\begin{eqnarray*}
+ &  & \pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})\\
+ & = & \imposs+\unlikely+\imposs+\likely\\
+ & = & \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=\left[\frac{1}{2},\frac{3}{2}\right]
+\end{eqnarray*}
+If we were to equate $\pmeas(\Omega)$ with the sum of the individual
+probabilities we would get that
+$\pmeas(\Omega) = \left[\frac{1}{2},\frac{3}{2}\right]$. However,
+using the fact that $\pmeas(\emptyset)=\imposs$, we have
+$\pmeas\left(\Omega\right)=1-\pmeas\left(\emptyset\right)=\necess=[1,1]$. This
+interval is tighter and a better estimate for the probability of the
+event $\Omega$ and of course it is contained in
+$[\frac{1}{2},\frac{3}{2}]$. However it is only possible to exploit
+the information about the complement when all four events are
+combined. Thus the $\subseteq$-condition allows us to get an estimate
+for the combined event from each of its constituents and then gather
+more evidence knowing the aggregate event.\qed\end{example}
 

### 2016-05-07 prob.tex
prob.tex \subsection{Buffon's Needle Problem} Fix typos, add citation and comments...

@@
 the probability of the needle crossing a line converges to
-$\frac{2}{\pi} = 0.6366197723675814$.
+$\frac{2}{\pi} = 0.6366197723675814$~\cite{Buffon1777}.
 %% \yutsung{Add $\ldots$ at the end? }\\
@@
 cross lines is $\{-XX,X-X,XX-\}$: it has
-probability~$\frac{2}{3}$. Generally, the event that exactly $M$
+probability~$\frac{3}{8}$. Generally, the event that exactly $M$
 needles out of the $N$ total needles cross lines is $\frac{M}{N}$.
@@
 experiment with $3408$ needles, the probability was calculated to be
-$0.6366197193098592$.
-%% \yutsung{Add $\ldots$ at the end? }\\
+$0.6366197193098592$.\\
+\yutsung{
+May I confirm how many times needle cross the line within $3408$ needles?
+Because $\frac{2169}{3408}$ is almost $0.6364436619718310$, and
+$\frac{2170}{3408}$ is almost $0.6367370892018779$, both of them are not
+close to $0.6366197193098592$ enough\ldots }\\
 Comparing the values to the idealized mathematical value, we see that
@@
 hypothetical experiment with 3 needles, it is not sensible to retain
-100 digits in the expansion of $\frac{2}{3}$.
+100 digits in the expansion of $\frac{2}{\pi}$.
 

### 2016-05-07 prob.tex
comments

@@
 close to $0.6366197193098592$ enough\ldots }\\
+\amr{
+There are several articles and papers on the experiment. I got these
+values from wikipedia and mathworld. We need to get precise references
+and cite the papers describing the experiments. The actual values
+don't matter though.
+}
 Comparing the values to the idealized mathematical value, we see that
@@
 
+\amr{
+The idea will be the following. First describe quantum probability
+spaces conventionally. Then talk about the following:
+\begin{itemize}
+\item the dimension of the Hilbert space is a parameter that is like
+  the number of needles; it gives an upper bound on the accuracy of
+  the numbers that are relevant in expressing probabilities
+\item the intervals will come from two things: the fact that states
+  can only be prepared to a certain accuracy so when we say the state
+  is $\ket{\psi}$ we really mean a neighborhood of states close to $\ket{\psi}$
+\item similarly when we do an experiment with $\proj{\phi}$ we are
+  really testing a family of projections that are near $\proj{\phi}$;
+  this fuziness will cause the probability to only be specifiable as intervals
+\end{itemize}
+}
+
 The mathematical framework above assumes that one has complete

### 2016-05-08 prob.tex
Add citation... However, Lazzarini's seems Italian...
prob.tex \subsection{Buffon's Needle Problem} Add comments...

@@
 experiment with $3408$ needles, the probability was calculated to be
-$0.6366197193098592$.\\
+$0.6366197193098592$~\cite{Lazzarini1901,Uspenskyothers1937}.\\
 \yutsung{
@@
 $\frac{2170}{3408}$ is almost $0.6367370892018779$, both of them are not
-close to $0.6366197193098592$ enough\ldots }\\
+close to $0.6366197193098592$ enough\ldots 
+}\\
 \amr{
@@
 don't matter though.
-}
+}\\
+\yutsung{
+Although I don't know Italian, it seems that Lazzarini~\cite{Lazzarini1901}
+used the needle with length 2.5, and the length among lines is 3.
+When he tossed needles 3408 times, he got 1808 crossing, and 
+\[
+\pi\approx\frac{2\cdot2.5\cdot3408}{3\cdot1808}=\frac{355}{113}\approx3.1415929
+\]
+However, his paper was be criticized in Wikipedia, because $\frac{355}{113}$
+is the best rational approximation of $\pi$ for small intergers.
+How can his experiment just gave this number?
+
+Uspensky~\cite{Uspenskyothers1937} and Buffon~\cite{Buffon1777}
+are books. I will check out \cite{Uspenskyothers1937} on Sunday,
+and \cite{Buffon1777} on Monday...
+}\\
 Comparing the values to the idealized mathematical value, we see that

### 2016-05-08 prob.tex
small comment

@@
 
+\amr{
+We can use DQC if we have some kind of topology (distances). The idea
+will be that we want to prepare state PSI but because of errors etc we
+prepare a close state. Well the next closest state will be the next
+state in our discrete grid. I am sure that a state that's very close
+to PSI can involve some wrapping around.
+}
+
 The mathematical framework above assumes that one has complete

### 2016-05-09 prob.tex
prob.tex Add comments from Gerardo...

@@
 consisting of a collection of $N$ identical needles of length
-$\ell$. We throw the $N$ needles and observe the number $X$ of needles
-that cross a line. The sample space can be expressed as the set
-$(X|-)^N$
+$\ell$. We throw the $N$ needles one needle at a time, and observe the number
+$X$ of needles that cross a line. The sample space can be expressed as the set
+$\{X,-\}^N$
 %% \yutsung{Use more physical or mathematical notation?}\\
@@
 needle not crossing a line. If $N=3$, the event that exactly 2 needles
-cross lines is $\{-XX,X-X,XX-\}$: it has
+cross lines~$\{-XX,X-X,XX-\}$ has
 probability~$\frac{3}{8}$. Generally, the event that exactly $M$
@@
 the combined probability, one can do find a much tighter interval if
-information \emph{against} the event (i.e., information about the dual
+information \emph{against} the event (i.e., information about the complement
 event) is also taken into consideration.
@@
 The mathematical framework above assumes that one has complete
-knowledge of the events and their relationships. However, in many
-practical situations, the structure of the event space is only
+knowledge of the events and their relationships, and moreover, there exists a
+predetermined set of properties.
+However, in many practical situations, the structure of the event space is only
 partially known and the precise dependence of two events on each other
-cannot, a priori, be determined with certainty. In the quantum case,
+cannot, a priori, be determined with certainty. In the quantum framework,
 this partial knowledge is compounded by the fact that there exist
@@
   $\alpha \ket{0} + \beta \ket{1}$ such that
-  $|\alpha|^2 + |\beta|^2 = 1$. The set of events associated with this
-  Hilbert space consists of all projection operators. Each event is
+  $|\alpha|^2 + |\beta|^2 = 1$, $\alpha ,\beta \in \C$. The set of events
+  associated with this Hilbert space consists of all projection operators. Each event is
   interpreted as a possible post-measurement state of a quantum system

### 2016-05-10 prob.tex
Add more Gerardo's comments and my respondce...

@@
 \newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
+\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
+\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
 
@@
 more evidence knowing the aggregate event.\qed\end{example}
+
+\gerardo{Set-valued is a particular case?}
+
+\yutsung{Set-valued is not a particular case of interval-valued probability.
+In particular, the rule they respect are different. A real-valued
+probability measure $\pmeas:\events\rightarrow[0,1]$ should satisfy
+the following two rules:
+\begin{enumerate}
+\item $\pmeas(\Omega)=1$, and 
+\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$.
+\end{enumerate}
+When the range of $\pmeas$ is not only a real number, these conditions
+cannot be both reserved. The set-valued probability measure preserves
+Condition 2 and modifies Condition 1. The interval-valued probability
+measure preserves Condition 1 and modifies Condition 2.
+
+It seems hard to make a consistent story with the general set-valued
+probability measure framework (except possible/impossible?), so we
+just comment out set-valued probability measure here...}
 

### 2016-05-11 prob.tex
prob.tex \subsection{Buffon's Needle Problem} Update the sources...

@@
 Suppose we drop a needle of length $\ell$ onto a floor made of equally
-spaced parallel lines a distance $\ell$ apart. It is a known fact that
+spaced parallel lines a distance $h$ apart. It is a known fact that
 the probability of the needle crossing a line converges to
-$\frac{2}{\pi} = 0.6366197723675814$~\cite{Buffon1777}.
-%% \yutsung{Add $\ldots$ at the end? }\\
+$\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
 We analyze this situation in the mathematical framework of probability
@@
 $\{X,-\}^N$
-%% \yutsung{Use more physical or mathematical notation?}\\
 of sequences of characters of length $N$ where each character is
 either $X$ to indicate a needle crossing a line or $-$ to indicate a
-needle not crossing a line. If $N=3$, the event that exactly 2 needles
-cross lines~$\{-XX,X-X,XX-\}$ has
-probability~$\frac{3}{8}$. Generally, the event that exactly $M$
-needles out of the $N$ total needles cross lines is $\frac{M}{N}$.
-
-In an actual experiment with 500 needles, it was found that 321
-crossed a line which gives a probability of $0.642$. In a larger
-experiment with $3408$ needles, the probability was calculated to be
-$0.6366197193098592$~\cite{Lazzarini1901,Uspenskyothers1937}.\\
-\yutsung{
-May I confirm how many times needle cross the line within $3408$ needles?
-Because $\frac{2169}{3408}$ is almost $0.6364436619718310$, and
-$\frac{2170}{3408}$ is almost $0.6367370892018779$, both of them are not
-close to $0.6366197193098592$ enough\ldots 
-}\\
-\amr{
-There are several articles and papers on the experiment. I got these
-values from wikipedia and mathworld. We need to get precise references
-and cite the papers describing the experiments. The actual values
-don't matter though.
-}\\
-\yutsung{
-Although I don't know Italian, it seems that Lazzarini~\cite{Lazzarini1901}
-used the needle with length 2.5, and the length among lines is 3.
-When he tossed needles 3408 times, he got 1808 crossing, and 
-\[
-\pi\approx\frac{2\cdot2.5\cdot3408}{3\cdot1808}=\frac{355}{113}\approx3.1415929
-\]
-However, his paper was be criticized in Wikipedia, because $\frac{355}{113}$
-is the best rational approximation of $\pi$ for small intergers.
-How can his experiment just gave this number?
-
-Uspensky~\cite{Uspenskyothers1937} and Buffon~\cite{Buffon1777}
-are books. I will check out \cite{Uspenskyothers1937} on Sunday,
-and \cite{Buffon1777} on Monday...
-}\\
-Comparing the values to the idealized mathematical value, we see that
-the observed probability approaches $\frac{2}{\pi}$ but only if
+needle not crossing a line. If $N=3$, the probability of the event that exactly
+2 needles cross lines~$\{-XX,X-X,XX-\}$ can be 
+estimated by the relative frequency~$\frac{3}{8}$. Generally, the probability of
+the event that exactly $M$ needles out of the $N$ total needles cross lines can
+be estimated by the relative frequency~$\frac{M}{N}$.
+
+In an actual experiment with $500$ needles and the ratio
+$\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$ 
+crossed a line so the relative frequency is $0.472$ comparing 
+the values to the idealized mathematical probability $0.4775\ldots$. In a larger 
+experiment with $5000$ needles and the ratio $\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, 
+the relative frequency was calculated to be $0.5064$ comparing 
+the values to the idealized mathematical probability $0.5093\ldots$. We see that 
+the observed probability approaches $\frac{2\ell}{\pi h}$ but only if
 \emph{larger and larger resources} are expended.
@@
 hypothetical experiment with 3 needles, it is not sensible to retain
-100 digits in the expansion of $\frac{2}{\pi}$.
+100 digits in the expansion of $\frac{2\ell}{\pi h}$.
 
@@
 leads us to consider intervals of probability reflecting the certainty
-of the event and its plausibility. In the hypothetical experiment with
-3 needles, assume that one needle clearly crossed a line and another
+of the event and its plausibility. In an actual experiment with
+$3204$ needles and the ratio $\frac{\ell}{h}=0.6$~\cite{DeMorgan1872}, 
+there are $1213$ needles clearly crossed a line and $11$ ones
 was close enough to plausibly be considered as crossing the line: we
 would express the probability in this case as the interval
-$[\frac{1}{3},\frac{2}{3}]$ expressing that we are certain that the
-event has probability at least $\frac{1}{3}$ but it is possible that
-it would have probability $\frac{2}{3}$.
+$\left[\frac{1213}{3204},\frac{1234}{3204}\right]$ expressing that we are
+certain that the event has probability at least $\frac{1213}{3204}$ but it is possible that
+it would have probability $\frac{1234}{3204}$.
 

### 2016-05-11 prob.tex
prob.tex \section{Quantum Probability Spaces} updated...

@@
 leads us to consider intervals of probability reflecting the certainty
-of the event and its plausibility. In an actual experiment with
+of the event and its plausibility. In another experiment with
 $3204$ needles and the ratio $\frac{\ell}{h}=0.6$~\cite{DeMorgan1872}, 
@@
 would express the probability in this case as the interval
-$\left[\frac{1213}{3204},\frac{1234}{3204}\right]$ expressing that we are
+$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we are
 certain that the event has probability at least $\frac{1213}{3204}$ but it is possible that
-it would have probability $\frac{1234}{3204}$.
+it would have probability $\frac{1224}{3204}$.
 
@@
 
-\begin{definition}[Projection Operators; Orthogonality;
-Commutativity~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
-Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear transformation from $\Hilb$
-to itself such that $P^2 = P = P^{\dagger}$. Projection operators have the
-following properties:\footnote {``Projection'' is sometimes called
+\begin{definition}[Projection Operators; Orthogonality
+~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
+Given a Hilbert space $\Hilb$, an event, formally called elementary quantum
+test~\cite{peres1995quantum}, can be represented as a projection operator
+$P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
+events can be defined recursively as follow:
+\footnote {``Projection'' is sometimes called
 ``orthogonal projection" or ``self-adjoint projection" to
@@
 \begin{itemize}
+\item $\mathbb{0}$ is a projection.
+\item For any vector $\ket{\psi}\in \Hilb$,
+  $\frac{\proj{\psi}}{\ip{\psi}{\psi}}$ is a projection.
 \item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
-  P_2P_1 = \mathbb{0}$;
-\item Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
-  P_2P_1$;
-\item If the projections $P_1$ and $P_2$ are orthogonal then $P_1 +
-  P_2$ is also a projection;
-\item If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
-  a projection.
+  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
+  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
+  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
+  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
+  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
 \end{itemize}
@@
 
-\amr{Here it would be good to refer to the notion of ``quantum test''
-  and define events as sums of quantum tests. This will automatically
-  include everything except the products of commutative projections
-  which we will have to explain that they can be expressed as sums of
-  orthogonal projections.}
+Notice that the preceding definition exhaust all possible projection operators.
+Because every linear subspace~$S$ has an orthonormal basis~$\{\ket{\psi_j}\}$,
+the projection onto $S$ can always expressed as $\sum_j\proj{\psi_j}$.
+As operators, we can also multiply projections together.
+
+\begin{definition}[Commutativity
+~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
+Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
+  P_2P_1$;
+If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
+  a projection. Moreover, if $P_1$ and $P_2$ project onto
+  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
+  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
+\end{definition}
 

### 2016-05-11 prob.tex
prob.tex \subsection{Buffon's Needle Problem} verifying what I typed...

@@
 spaced parallel lines a distance $h$ apart. It is a known fact that
-the probability of the needle crossing a line converges to
+the probability of the needle crossing a line is
 $\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
@@
 2 needles cross lines~$\{-XX,X-X,XX-\}$ can be 
-estimated by the relative frequency~$\frac{3}{8}$. Generally, the probability of
+estimated by the relative frequency~$\frac{2}{3}$. Generally, the probability of
 the event that exactly $M$ needles out of the $N$ total needles cross lines can
-be estimated by the relative frequency~$\frac{M}{N}$.
+be estimated by $\frac{M}{N}$.
 
@@
 crossed a line so the relative frequency is $0.472$ comparing 
-the values to the idealized mathematical probability $0.4775\ldots$. In a larger 
+the values to the idealized mathematical probability $0.4774\ldots$. In a larger 
 experiment with $5000$ needles and the ratio $\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, 
 the relative frequency was calculated to be $0.5064$ comparing 
-the values to the idealized mathematical probability $0.5093\ldots$. We see that 
+the values to the idealized mathematical probability $0.5092\ldots$. We see that 
 the observed probability approaches $\frac{2\ell}{\pi h}$ but only if

### 2016-05-12 prob.tex
prob.tex "Interval-valued probability measures" update comment...

@@
 the the floor have thickness, their distance apart is not exactly
-$\ell$. and the needles lengths are not all equal and are not all
+$h$. and the needles lengths are not all equal and are not all
 absolutely equal to $\ell$. These perturbations make the events
@@
 
-\yutsung{Set-valued is not a particular case of interval-valued probability.
-In particular, the rule they respect are different. A real-valued
-probability measure $\pmeas:\events\rightarrow[0,1]$ should satisfy
-the following two rules:
+\yutsung{Set-valued is not a particular case of interval-valued probability
+because their rules are different. A set-valued probability measure
+should satisfy: 
 \begin{enumerate}
-\item $\pmeas(\Omega)=1$, and 
+\item $1\in\pmeas(\Omega)$, and 
 \item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$. 
 \end{enumerate}
-When the range of $\pmeas$ is not only a real number, these conditions
-cannot be both reserved. The set-valued probability measure preserves
-Condition 2 and modifies Condition 1. The interval-valued probability
-measure preserves Condition 1 and modifies Condition 2.
+which are completely opposite to the interval-valued probability measures.
 
 It seems hard to make a consistent story with the general set-valued
-probability measure framework (except possible/impossible?), so we
-just comment out set-valued probability measure here...}
+probability measure framework (maybe except possible/impossible?),
+so we just comment out set-valued probability measure here...}
 

### 2016-05-12 prob.tex
small revisions here and there

@@
 the conventional presentation of probability spaces and then discuss
-the hidden issue of computational and experimental resources.
+the computational resources needed to estimate probabilities.
 
@@
 it is more appropriate to consider probability measures that map
-events to a finite set of elements computable with a fixed set of
+events to a set of elements computable with a fixed set of
 resources. We expand on this observation and then consider
@@
 interval-valued probability
-measures~\cite{Dempster1967,Zadeh1986,Weichselberger2000,JamisonLodwick2004}.
+measures~\cite{Dempster1967,Zadeh1986,Weichselberger2000,JamisonLodwick2004}
+in detail.\footnote{There is another possible approach that can be
+  used to split the real interval $[0,1]$ into a collection of
+  subsets~\cite{Artstein1972,PuriRalescu1983} \amr{need to explain the
+    connection and why we are not using it.}}
 
 %%%%%
-\subsection{Buffon's Needle Problem}
+\subsection{Calculating Probabilities: Buffon's Needle Problem}
 
@@
 In an actual experiment with $500$ needles and the ratio
-$\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$ 
-crossed a line so the relative frequency is $0.472$ comparing 
-the values to the idealized mathematical probability $0.4774\ldots$. In a larger 
-experiment with $5000$ needles and the ratio $\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, 
-the relative frequency was calculated to be $0.5064$ comparing 
-the values to the idealized mathematical probability $0.5092\ldots$. We see that 
-the observed probability approaches $\frac{2\ell}{\pi h}$ but only if
-\emph{larger and larger resources} are expended.
-
-These resource considerations thus lead us to replace the real
-interval $[0,1]$ with rational numbers up to a certain precision.  The
-intuition is that the precision depends on the amount of resources
-allocated for the measurement process. There is clearly a connection
-between the number of needles and the achievable precision: in the
-hypothetical experiment with 3 needles, it is not sensible to retain
-100 digits in the expansion of $\frac{2\ell}{\pi h}$.
-
-There is however another more subtle source of unbounded computational
-power in the experiment. We are assuming that we can always determine
-with certainty whether a needle is crossing a line. But ``lines'' on
-the the floor have thickness, their distance apart is not exactly
-$h$. and the needles lengths are not all equal and are not all
-absolutely equal to $\ell$. These perturbations make the events
-``fuzzy.'' For example, instead of talking about the idealized event
-that exactly $M$ needles cross lines which would require the most
-expensive needles built to the most precise accuracy, laser precision
-for drawing lines on the floor, and the most powerful microscopes to
-determine if a needle does cross a line, we might instead talk about
-the event that $M-\delta$ needles evidently cross lines and
-$M+\delta'$ needles plausibly cross lines for some acceptable
-approximations $\delta$ and $\delta'$. This fuzzy notion of events
-leads us to consider intervals of probability reflecting the certainty
-of the event and its plausibility. In another experiment with
+$\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$ crossed
+a line which is a relative frequency of $0.472$ whereas the idealized
+mathematical probability is $0.4774\ldots$. In a larger experiment
+with $5000$ needles and the ratio
+$\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, the relative frequency was
+calculated to be $0.5064$ whereas the idealized mathematical
+probability is $0.5092\ldots$. We see that the observed probability
+approaches $\frac{2\ell}{\pi h}$ but only if \emph{larger and larger
+  resources} are expended. These resource considerations suggest that
+it is possible to replace the real interval $[0,1]$ with rational
+numbers up to a certain precision related to the particular experiment
+in question.  There is clearly a connection between the number of
+needles and the achievable precision: in the hypothetical experiment
+with 3 needles, it is not sensible to retain 100 digits in the
+expansion of $\frac{2\ell}{\pi h}$.
+
+There is however another more subtle assumption of unbounded
+computational power in the experiment. We are assuming that we can
+always determine with certainty whether a needle is crossing a
+line. But ``lines'' on the the floor have thickness, their distance
+apart is not exactly $h$. and the needles lengths are not all equal
+and are not all absolutely equal to $\ell$. These perturbations make
+the events ``fuzzy.'' Thus, in an experiment with limited resources,
+it is not possible to talk about the idealized event that exactly $M$
+needles cross lines as this would require the most expensive needles
+built to the most precise accuracy, laser precision for drawing lines
+on the floor, and the most powerful microscopes to determine if a
+needle does cross a line. Instead we might talk about the event that
+$M-\delta$ needles evidently cross lines and $M+\delta'$ needles
+plausibly cross lines where $\delta$ and $\delta'$ are
+resource-dependent approximations. This fuzzy notion of events leads
+to probabilities being only calculable within intervals of confidence
+reflecting the certainty of events and their plausibility. This is
+indeed consistent with published experiments: in an experiment with
 $3204$ needles and the ratio $\frac{\ell}{h}=0.6$~\cite{DeMorgan1872},
-there are $1213$ needles clearly crossed a line and $11$ ones
-was close enough to plausibly be considered as crossing the line: we
-would express the probability in this case as the interval
-$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we are
-certain that the event has probability at least $\frac{1213}{3204}$ but it is possible that
-it would have probability $\frac{1224}{3204}$.
+$1213$ needles clearly crossed a line and $11$ needles were close
+enough to plausibly be considered as crossing the line: we would
+express the probability in this case as the interval
+$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we
+are certain that the event has probability at least
+$\frac{1213}{3204}$ but it is possible that it would have probability
+$\frac{1224}{3204}$.
 
@@
 
-We begin with an analysis explaining how to combine intervals of
-probability. Specifically if we have an event $E_1$ with an interval
-of probability $[l_1,r_1]$ and another disjoint event $E_2$ with an
-interval of probability $[l_2,r_2]$, what is the interval probability
-of the event $E_1 \cup E_2$. The answer is somewhat subtle: although
-it is possible to use the sum of the intervals $[l_1+l_2,r_1+r_2]$ as
-the combined probability, one can do find a much tighter interval if
-information \emph{against} the event (i.e., information about the complement
-event) is also taken into consideration.
-
-For a general event $E$ with probability $[l,r]$, the strength of
-evidence that contradicts $E$ is evidence supporting the complement of
-$E$. The complement of $E$ must therefore have probability
+As motivated above, an event $E_1$ may have an interval of probability
+$[l_1,r_1]$. Assume that another disjoint event $E_2$ has interval
+probability $[l_2,r_2]$, what is the interval probability of the event
+$E_1 \cup E_2$. The answer is somewhat subtle: although it is possible
+to use the sum of the intervals $[l_1+l_2,r_1+r_2]$ as the combined
+probability, one can do find a much tighter interval if information
+\emph{against} the event (i.e., information about the complement
+event) is also taken into consideration. Formally, for a general event
+$E$ with probability $[l,r]$, the strength of evidence that
+contradicts $E$ is evidence supporting the complement of $E$. The
+complement of $E$ must therefore have probability
 $\left[1-r,1-l\right]$ which we abbreviate $1-\left[l,r\right]$. Given
@@
 
-The reason the last condition is expressed using $\subseteq$ is best
-explained using a small example.
+\noindent The reason the last condition is expressed using $\subseteq$
+is best explained using a small example.
 
@@
 
-\gerardo{Set-valued is a particular case?}
-
-\yutsung{Set-valued is not a particular case of interval-valued probability
-because their rules are different. A set-valued probability measure
-should satisfy: 
-\begin{enumerate}
-\item $1\in\pmeas(\Omega)$, and 
-\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$. 
-\end{enumerate}
-which are completely opposite to the interval-valued probability measures.
-
-It seems hard to make a consistent story with the general set-valued
-probability measure framework (maybe except possible/impossible?),
-so we just comment out set-valued probability measure here...}
+% \gerardo{Set-valued is a particular case?}
+
+% \yutsung{Set-valued is not a particular case of interval-valued probability
+% because their rules are different. A set-valued probability measure
+% should satisfy: 
+% \begin{enumerate}
+% \item $1\in\pmeas(\Omega)$, and 
+% \item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$. 
+% \end{enumerate}
+% which are completely opposite to the interval-valued probability measures.
+
+% It seems hard to make a consistent story with the general set-valued
+% probability measure framework (maybe except possible/impossible?),
+% so we just comment out set-valued probability measure here...}
 
@@
 
-\amr{
-The idea will be the following. First describe quantum probability
-spaces conventionally. Then talk about the following:
-\begin{itemize}
-\item the dimension of the Hilbert space is a parameter that is like
-  the number of needles; it gives an upper bound on the accuracy of
-  the numbers that are relevant in expressing probabilities
-\item the intervals will come from two things: the fact that states
-  can only be prepared to a certain accuracy so when we say the state
-  is $\ket{\psi}$ we really mean a neighborhood of states close to $\ket{\psi}$
-\item similarly when we do an experiment with $\proj{\phi}$ we are
-  really testing a family of projections that are near $\proj{\phi}$;
-  this fuziness will cause the probability to only be specifiable as intervals
-\end{itemize}
-}
-
-\amr{
-We can use DQC if we have some kind of topology (distances). The idea
-will be that we want to prepare state PSI but because of errors etc we
-prepare a close state. Well the next closest state will be the next
-state in our discrete grid. I am sure that a state that's very close
-to PSI can involve some wrapping around.
-}
-
-The mathematical framework above assumes that one has complete
-knowledge of the events and their relationships, and moreover, there exists a
-predetermined set of properties.
-However, in many practical situations, the structure of the event space is only
-partially known and the precise dependence of two events on each other
-cannot, a priori, be determined with certainty. In the quantum framework,
-this partial knowledge is compounded by the fact that there exist
-non-commuting events which cannot happen simultaneously. To
-accommodate these more complex situations, we abandon the sample
-space~$\Omega$ and reason directly about events. A quantum probability
-space therefore consists of just two components: a set of events
-$\qevents$ and a probability measure
+The mathematical framework above assumes that there exists a
+predetermined set of events that are independent of the particular
+experiment. However, in many practical situations, the structure of
+the event space is only partially known and the precise dependence of
+two events on each other cannot, a priori, be determined with
+certainty. In the quantum framework, this partial knowledge is
+compounded by the fact that there exist non-commuting events which
+cannot happen simultaneously. To accommodate these more complex
+situations, we abandon the sample space~$\Omega$ and reason directly
+about events. A quantum probability space therefore consists of just
+two components: a set of events $\qevents$ and a probability measure
 $\mu : \qevents \rightarrow [0,1]$. We give an example before giving
@@
 events (e.g., $\proj{0}+\proj{1}$) is the sum of the individual
-probabilities. In contrast, a collection of non-orthogonal events
-(e.g., $\proj{0}$ and $\proj{\ps}$) is not itself an event.
+probabilities. A collection of non-orthogonal events
+(e.g., $\proj{0}$ and $\proj{\ps}$) is however not even a valid event.
 In the classical example, we argued that each probability measure is
@@
 ~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
-Given a Hilbert space $\Hilb$, an event, formally called elementary quantum
-test~\cite{peres1995quantum}, can be represented as a projection operator
-$P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
-events can be defined recursively as follow:
-\footnote {``Projection'' is sometimes called
-``orthogonal projection" or ``self-adjoint projection" to
-emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
+Given a Hilbert space $\Hilb$, an event is an \emph{elementary quantum
+  test}~\cite{peres1995quantum}, which mathematically is represented
+as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear
+subspace~$S$ of $\Hilb$. The set of all events can be defined
+recursively as follow: \footnote {``Projection'' is sometimes called
+  ``orthogonal projection" or ``self-adjoint projection" to emphasize
+  $P^{\dagger} = P$~\cite{Maassen2010}.}
 \begin{itemize}
@@
 
-\newpage
+\amr{
+The idea will be the following. First describe quantum probability
+spaces conventionally. Then talk about the following:
+\begin{itemize}
+\item the dimension of the Hilbert space is a parameter that is like
+  the number of needles; it gives an upper bound on the accuracy of
+  the numbers that are relevant in expressing probabilities
+\item the intervals will come from two things: the fact that states
+  can only be prepared to a certain accuracy so when we say the state
+  is $\ket{\psi}$ we really mean a neighborhood of states close to $\ket{\psi}$
+\item similarly when we do an experiment with $\proj{\phi}$ we are
+  really testing a family of projections that are near $\proj{\phi}$;
+  this fuziness will cause the probability to only be specifiable as intervals
+\end{itemize}
+}
+
+\amr{
+We can use DQC if we have some kind of topology (distances). The idea
+will be that we want to prepare state PSI but because of errors etc we
+prepare a close state. Well the next closest state will be the next
+state in our discrete grid. I am sure that a state that's very close
+to PSI can involve some wrapping around.
+}
+
 \amr{the rest needs cleaning up and perhaps does not even belong in

### 2016-05-12 prob.tex
prob.tex \section{Quantum Probability Spaces} verifying source...

--- 2016-05-12 prob.tex
@@
 
-\begin{definition}[Projection Operators; Orthogonality
-~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
-Given a Hilbert space $\Hilb$, an event, formally called elementary quantum
-test~\cite{peres1995quantum}, can be represented as a projection operator
+\begin{definition}[Projection Operators; Orthogonality~\cite{BirkhoffVonNeumann1936,10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
+Given a Hilbert space $\Hilb$, an eventt\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
+a question~\cite{10.2307/2308516}, or an elementary quantum test~\cite{peres1995quantum}} can be represented as a projection operator
 $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
@@
 
-\begin{definition}[Commutativity
-~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
+\begin{definition}[Commutativity~\cite{Redhead1987-REDINA,peres1995quantum,Swart2013}]
 Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
@@
 
-\begin{definition}[Quantum Probability Space~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}]
+\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}]
   Given a Hilbert space $\Hilb$, a \emph{quantum probability space}

### 2016-05-12 prob.tex

--- 2016-05-12 prob.tex
@@
 
-\begin{definition}[Projection Operators; Orthogonality
-~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
-Given a Hilbert space $\Hilb$, an event is an \emph{elementary quantum
-  test}~\cite{peres1995quantum}, which mathematically is represented
-as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear
-subspace~$S$ of $\Hilb$. The set of all events can be defined
-recursively as follow: \footnote {``Projection'' is sometimes called
-  ``orthogonal projection" or ``self-adjoint projection" to emphasize
-  $P^{\dagger} = P$~\cite{Maassen2010}.}
+\begin{definition}[Projection Operators; Orthogonality~\cite{BirkhoffVonNeumann1936,10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
+Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
+a question~\cite{10.2307/2308516}, or an elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator
+$P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
+events can be defined recursively as follow:
+\footnote {``Projection'' is sometimes called
+``orthogonal projection" or ``self-adjoint projection" to
+emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
 \begin{itemize}

### 2016-05-12 prob.tex
prob.tex \section{Quantum Probability Spaces} verifying source...

@@
 
-\begin{definition}[Projection Operators; Orthogonality~\cite{BirkhoffVonNeumann1936,10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
+\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
 Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
-a question~\cite{10.2307/2308516}, or an elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator
-$P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
+a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
+elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
 events can be defined recursively as follow:
@@
 
-\begin{definition}[Commutativity~\cite{Redhead1987-REDINA,peres1995quantum,Swart2013}]
+\begin{definition}[Commutativity~\cite{peres1995quantum}]
 Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
@@
 
-\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}]
+\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
   Given a Hilbert space $\Hilb$, a \emph{quantum probability space}

### 2016-05-13 prob.tex
prob.tex \subsection{Quantum Probability Measures} Add an example...

@@
 \begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
-Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
-a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
+\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
+is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
 elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
@@
 \begin{itemize}
-\item The set of events consists of all projections. This set includes
-  the empty projection, projection operators $\proj{\psi}$ for each
-  state $\ket{\psi}$, sums of \emph{orthogonal} projections, and
-  products of \emph{commuting} projections; 
+\item The set of events consists of all projections as in
+  definition~\ref{def:Projection};
 \item $\mu(\mathbb{1})=1$, and 
@@
 
-For a given set of events $\events$, there are many possible
-probability measures $\mu : \events \rightarrow [0,1]$. The Born rule,
-a postulate of quantum mechanics, states that each quantum state
-$\ket{\phi}$ induces a probability measure $\mu_\phi$ as follows:
+For a given set of events $\events$, there are many possible probability
+measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1984,Mermin2007},
+a postulate of quantum mechanics, states that each pure quantum state
+$\ket{\phi}$ induces a probability measure $\mu_{\phi}$ as follows:
 \[
-\mu_\phi(E) = \ip{\phi}{E\phi}
+\mu_{\phi}(E)=\ip{\phi}{E\phi}
 \]
+Moreover, the Born rule can be extended to a mixed state~$\rho$.
+If the density matrix of a mixed state~$\rho$ can be expressed as
+a convex combination of pure states, i.e., $\rho=\sum_{j=1}^{N}q_{j}\proj{\psi_{j}}$,
+where $\sum_{j=1}^{N}q_{j}=1$, then the probability measure induced
+by $\rho$ can be expressed as a convex combination as well~\cite{peres1995quantum,544199}:
+\begin{eqnarray}
+\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\end{eqnarray}
+
 Conversely, Gleason's theorem states that given a probability measure
-$\mu$, there exist a quantum state $\ket{\phi}$ that induces such a
-measure using the Born rule. The theorem is only valid in Hilbert
-spaces with dimension $d \geq 3$. It is instructive to study
-counterexamples in $d=2$, i.e., the case of a one-qubit
-system. Consider five states $\ket{\psi_0}$ to $\ket{\psi_4}$ that
-form five orthogonal bases $\{ \ket{\psi_0}, \ket{\psi_1} \}$,
-$\{ \ket{\psi_1}, \ket{\psi_2} \}$,
-$\{ \ket{\psi_2}, \ket{\psi_3} \}$,
-$\{ \ket{\psi_3}, \ket{\psi_4} \}$, and
-$\{ \ket{\psi_4}, \ket{\psi_0} \}$ and consider the probability
-measure defined as follows. For all $i \in \{0,1,2,3,4\}$, we have
-$\mu_X(\proj{\psi_i}) = 1/2$. For each orthogonal basis, the
-probability is 1 as desired and yet it is impossible to find a single
-quantum state that realizes such a probability
-measure (see \url{http://tph.tuwien.ac.at/~svozil/publ/2006-gleason.pdf})
+$\mu$, there exist a mixed state~$\rho$ that induces such a measure
+using the Born rule. The theorem is only valid in Hilbert spaces with
+dimension $d\geq3$. It is instructive to study counterexamples in
+$d=2$, i.e., the case of a one-qubit system.
+
+\begin{example}[One-qubit quantum probability measure] 
+Consider a quantum probability
+measure~$\mu:\events\rightarrow[0,1]$ defined as follow:
+\[
+\mu(E)=\begin{cases}
+1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
+0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
+\mu_{\ket{0}}(E) & \textrm{, otherwise.}
+\end{cases}
+\]
+On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
+the same as $\mu_{\ket{0}}$ which is a probability measure, we only
+need to check $E=\proj{\ps}$ and $E=\proj{\ms}$. $\proj{\ps}$ and
+$\proj{\ms}$ are only orthogonal to each other, and we have 
+\[
+\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1
+\]
+which satisfies the conditions as a probability measure. On the other
+hand, $\mu$ cannot be induced by any mixed state because 
+\[
+\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
+\]
+However, $\mu_{\rho}(E)=1$ if and only if $\rho$ represents a pure
+state and $\rho=E$.
+\qed\end{example}
 

### 2016-05-13 prob.tex
prob.tex \subsection{Quantum Probability Measures} updated...

@@
 For a given set of events $\events$, there are many possible probability
-measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1984,Mermin2007},
+measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1984,Mermin2007,RiederSvozil2007},
 a postulate of quantum mechanics, states that each pure quantum state
@@
 \]
-Moreover, the Born rule can be extended to a mixed state~$\rho$.
-If the density matrix of a mixed state~$\rho$ can be expressed as
-a convex combination of pure states, i.e., $\rho=\sum_{j=1}^{N}q_{j}\proj{\psi_{j}}$,
-where $\sum_{j=1}^{N}q_{j}=1$, then the probability measure induced
-by $\rho$ can be expressed as a convex combination as well~\cite{peres1995quantum,544199}:
+
+Moreover, the Born rule can be extended to a mixed state. Suppose
+we want to prepare a quantum system. As we discussed in classical
+probability, our ability of preparing a state might not be prefect.
+If we want to prepare $\ket{\phi}$, we may turn out preparing a set
+of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$, then
+the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
+where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
+measure introduced by $\rho$ is the combination of $\mu_{\phi_{j}}$
+with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
 \begin{eqnarray}
-\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
 \end{eqnarray}
@@
 $\mu$, there exist a mixed state~$\rho$ that induces such a measure
-using the Born rule. The theorem is only valid in Hilbert spaces with
-dimension $d\geq3$. It is instructive to study counterexamples in
-$d=2$, i.e., the case of a one-qubit system.
-
-\begin{example}[One-qubit quantum probability measure] 
-Consider a quantum probability
-measure~$\mu:\events\rightarrow[0,1]$ defined as follow:
+using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+The theorem is only valid in Hilbert spaces with dimension $d\geq3$.
+It is instructive to study counterexamples in $d=2$, i.e., the case
+of a one-qubit system.
+
+\begin{example}[One-qubit quantum probability measure] Consider
+a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
+as follow: 
 \[
@@
 On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
-the same as $\mu_{\ket{0}}$ which is a probability measure, we only
-need to check $E=\proj{\ps}$ and $E=\proj{\ms}$. $\proj{\ps}$ and
-$\proj{\ms}$ are only orthogonal to each other, and we have 
+the same as a probability measure~$\mu_{\ket{0}}$, we only need
+to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$: 
 \[
-\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1
+\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
 \]
-which satisfies the conditions as a probability measure. On the other
-hand, $\mu$ cannot be induced by any mixed state because 
+On the other hand, $\mu$ cannot be induced by any mixed state because
 \[
@@
 However, $\mu_{\rho}(E)=1$ if and only if $\rho$ represents a pure
-state and $\rho=E$.
-\qed\end{example}
+state and $\rho=E$. \qed\end{example}
 

### 2016-05-14 prob.tex
prob.tex Updated summation notation and other thing according to meeting

@@
 \newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
+\usepackage{tensor}
 
@@
 \item $\pmeas(\Omega) = 1$, and 
-\item for a collection $E_i$ of pairwise disjoint events, 
-  $\pmeas(\bigcup_i E_i) = \sum_i \pmeas(E_i)$.
+\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$,
+where $a_{1}\tensor*[_{\mathbb{R}}]{+}{}a_{2}$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}a_{i}$
+explicitly specify $a_{i}\in\mathbb{R}$. We may drop the preposing
+$\mathbb{R}$ when there is no confusion. 
 \end{itemize}
@@
 %%%%%
-\subsection{Calculating Probabilities: Buffon's Needle Problem}
+\subsection{Measuring Probabilities: Buffon's Needle Problem}
 
@@
   and 
-\item for a collection $E_{i}$ of pairwise disjoint events, we have
-  $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$
-  where the summation on the right is the summation of intervals that
-  sums the endpoints.
+\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{I}]{\sum}{_{i}}\pmeas\left(E_{i}\right)$,
+where $\tensor*[_{I}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
+We may drop the preposing $I$ when summands are clear intervals. 
 \end{itemize}
@@
 \item $\mathbb{0}$ is a projection.
-\item For any vector $\ket{\psi}\in \Hilb$,
-  $\frac{\proj{\psi}}{\ip{\psi}{\psi}}$ is a projection.
+\item For any pure state~$\ket{\psi}$, $P=\proj{\psi}$ is a projection. 
 \item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
@@
 
-Notice that the preceding definition exhaust all possible projection operators.
+Notice that the preceding definition exhausts all possible projection operators.
 Because every linear subspace~$S$ has an orthonormal basis~$\{\ket{\psi_j}\}$,
@@
 \item $\mu(\mathbb{1})=1$, and 
-\item for mutually orthogonal projections $E_i$, we have
-  $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$.
+\item for mutually orthogonal projections $E_{i}$, we have $\mu\left(\tensor*[_{O}]{\sum}{_{i}}E_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(E_{i}\right)$,
+where $\tensor*[_{O}]{\sum}{_{i}}$ specifies that we add operators,
+and the preposing $O$ may be dropped when summands are clearly operators.
 \end{itemize}

### 2016-05-14 prob.tex
prob.tex \subsection{Real-Valued Probability Spaces} Modify a little bit

@@
 The conventional definition of a probability
-space~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
+space~\cite{Kolmogorov1950,rohatgi2011introduction,Swart2013}
 builds upon the real numbers. In more detail, a probability space
@@
 \item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$,
-where $a_{1}\tensor*[_{\mathbb{R}}]{+}{}a_{2}$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}a_{i}$
+where $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}a_{i}$
 explicitly specify $a_{i}\in\mathbb{R}$. We may drop the preposing

### 2016-05-14 prob.tex
prob.tex Review what has typed before typing new ones...

@@
 where $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}a_{i}$
-explicitly specify $a_{i}\in\mathbb{R}$. We may drop the preposing
+explicitly specifies $a_{i}\in\mathbb{R}$. We may drop the preposing
 $\mathbb{R}$ when there is no confusion. 
@@
 needle not crossing a line. If $N=3$, the probability of the event that exactly
-2 needles cross lines~$\{-XX,X-X,XX-\}$ can be 
+2 needles cross lines~$\{-XX,X{-}X,XX-\}$ can be 
 estimated by the relative frequency~$\frac{2}{3}$. Generally, the probability of
@@
 $\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$ crossed
-a line which is a relative frequency of $0.472$ whereas the idealized
+a line so the relative frequency is $0.472$ whereas the idealized
 mathematical probability is $0.4774\ldots$. In a larger experiment
@@
 line. But ``lines'' on the the floor have thickness, their distance
-apart is not exactly $h$. and the needles lengths are not all equal
-and are not all absolutely equal to $\ell$. These perturbations make
+apart is not exactly $h$, and the needles lengths 
+are not all absolutely equal to $\ell$. These perturbations make
 the events ``fuzzy.'' Thus, in an experiment with limited resources,
@@
 probability $[l_2,r_2]$, what is the interval probability of the event
-$E_1 \cup E_2$. The answer is somewhat subtle: although it is possible
+$E_1 \cup E_2$? The answer is somewhat subtle: although it is possible
 to use the sum of the intervals $[l_1+l_2,r_1+r_2]$ as the combined
@@
 event) is also taken into consideration. Formally, for a general event
-$E$ with probability $[l,r]$, the strength of evidence that
-contradicts $E$ is evidence supporting the complement of $E$. The
+$E$ with probability $[l,r]$, the evidence that
+contradicts $E$ is an evidence supporting the complement of $E$. The
 complement of $E$ must therefore have probability
@@
   and 
-\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{I}]{\sum}{_{i}}\pmeas\left(E_{i}\right)$,
-where $\tensor*[_{I}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
-We may drop the preposing $I$ when summands are clear intervals. 
+\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\pmeas\left(E_{i}\right)$,
+where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
+We may drop the preposing $\mathscr{I}$ when summands are clearly intervals. 
 \end{itemize}
@@
 
-\noindent The reason the last condition is expressed using $\subseteq$
-is best explained using a small example.
+\noindent We will explain why the last condition is expressed using
+$\subseteq$ by a small example.
 

### 2016-05-15 prob.tex
prob.tex Start fixing "Quantum Probability Space"...

@@
 complement of $E$ must therefore have probability
-$\left[1-r,1-l\right]$ which we abbreviate $1-\left[l,r\right]$. Given
+$\left[1-r,1-l\right]$ which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
+where the preposing $\mathscr{I}$ specifies we subtracts intervals,
+and may be dropped clearly by content. Given
 a collection of intervals $\mathscr{I}$, an
@@
 \item $\pmeas(\Omega)=[1,1]$, 
-\item $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$,
+\item $\pmeas\left(\Omega\backslash E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\pmeas\left(E\right)$,
   and 
@@
 \begin{itemize}
-\item $\mathbb{0}$ is a projection.
-\item For any pure state~$\ket{\psi}$, $P=\proj{\psi}$ is a projection. 
+\item $\mathbb{0}$ and $\mathbb{1}$ are a projection. 
+\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
+operator. 
 \item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
   P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
-  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
-  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
-  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
-  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
+  P_2$ is also a projection. 
+\item Conversely, every projection~$P$ can be expressed as $\sum_{j}\proj{\psi_{j}}$,
+where $P$ actually projects onto the linear subspace~$S$ which
+has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
 \end{itemize}
@@
 
-Notice that the preceding definition exhausts all possible projection operators.
-Because every linear subspace~$S$ has an orthonormal basis~$\{\ket{\psi_j}\}$,
-the projection onto $S$ can always expressed as $\sum_j\proj{\psi_j}$.
+Comparing to the classical events, the empty set~$\emptyset$ corresponds
+to the empty projection~$\mathbb{0}$, the event of whole sample
+space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
+
 As operators, we can also multiply projections together.

### 2016-05-15 prob.tex
prob.tex \section{Quantum Probability Spaces} updating... Besides, it seems that git cannot detact swapping text?

@@
 \item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
-  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
-  P_2$ is also a projection. 
-\item Conversely, every projection~$P$ can be expressed as $\sum_{j}\proj{\psi_{j}}$,
+  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
+is also a projection, where the preposing subscript $\mathscr{O}$
+means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
+and may be dropped when summands are clearly operators. 
+\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
+operator. Conversely, every projection~$P$ can be expressed as $\sum_{j}\proj{\psi_{j}}$,
 where $P$ actually projects onto the linear subspace~$S$ which
@@
 
-Comparing to the classical events, the empty set~$\emptyset$ corresponds
-to the empty projection~$\mathbb{0}$, the event of whole sample
-space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
-
-As operators, we can also multiply projections together.
-
-\begin{definition}[Commutativity~\cite{peres1995quantum}]
-Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
-  P_2P_1$;
-If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
-  a projection. Moreover, if $P_1$ and $P_2$ project onto
-  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
-  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
-\end{definition}
-
-% \amr{ 
-%   Projections include $\mathbb{0}, \proj{\psi}$ and $P_1 + P_2$ and
-%   $P_1 . P_2$ if $P_1$ and $P_2$ commute.
-%   When we write an event as $\sum E_i$ we are implicitly assuming they
-%   are commutative.
-%   Orthogonal implies commutative but not vice-versa
-% }
-% \yutsung{
-%   I checked \\
-%   \url{http://math.stackexchange.com/questions/1146893/on-the-sum-of-projection-operators}.\\
-%   Actually, they said $P_1 P_2 = P_2 P_1 = 0$, and the last $= 0$ is orthogonal.
-% }
+Based on the set of events, we can define the quantum probability
+space.
 
@@
 \qed\end{definition}
+
+Comparing to the classical probability space, the empty set~$\emptyset$
+corresponds to the empty projection~$\mathbb{0}$ and the event of
+whole sample space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
+In contrast, the union~$\cup$ of any two events always gives an
+event classically, the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
+of two projections may not be a projection. As the result, the equation
+$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
+is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
+however, $\mu\left(E_{1}\tensor*[_{\mathscr{O}}]{+}{}E_{2}\right)=\mu(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(E_{2})$
+is always true whenever the left-handed side is defined. Whether equation
+is defined also effects the further properties of quantum probability
+space.
+
+\begin{definition}{[}Orthogonal Complement; Commutativity~\cite{peres1995quantum}{]} 
+\begin{itemize}
+\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{O}]{-}{}P$
+is also a projection operator.
+\end{itemize}
+Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
+  P_2P_1$;
+If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
+  a projection. Moreover, if $P_1$ and $P_2$ project onto
+  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
+  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
+\end{definition}
 

### 2016-05-15 prob.tex
prob.tex \section{Quantum Probability Spaces} updates...

@@
 \begin{itemize}
-\item $\mathbb{0}$ and $\mathbb{1}$ are a projection. 
+\item $\mathbb{0}$ is a projection. 
 \item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
@@
 and may be dropped when summands are clearly operators. 
-\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
-operator. Conversely, every projection~$P$ can be expressed as $\sum_{j}\proj{\psi_{j}}$,
+\item Conversely, every projection~$P$ can be expressed as
+$\tensor*[_{\mathscr{O}}]{\sum}{_j}\proj{\psi_{j}}$,
 where $P$ actually projects onto the linear subspace~$S$ which
@@
 \end{itemize}
-\end{definition}
+\qed\end{definition}
 
@@
 \begin{itemize}
-\item The set of events consists of all projections as in
-  definition~\ref{def:Projection};
 \item $\mu(\mathbb{1})=1$, and 
-\item for mutually orthogonal projections $E_{i}$, we have $\mu\left(\tensor*[_{O}]{\sum}{_{i}}E_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(E_{i}\right)$,
-where $\tensor*[_{O}]{\sum}{_{i}}$ specifies that we add operators,
-and the preposing $O$ may be dropped when summands are clearly operators.
+\item for mutually orthogonal projections $E_{i}$, we have 
+$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}E_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(E_{i}\right)$.
 \end{itemize}
@@
 In contrast, the union~$\cup$ of any two events always gives an
-event classically, the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
-of two projections may not be a projection. As the result, the equation
-$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
+event classically, but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
+of two projections may not be a projection. As the result, the classical
+condition~$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
 is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
@@
 \begin{itemize}
-\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{O}]{-}{}P$
-is also a projection operator.
+\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
+is also a projection operator. It is orthogonal to $P$, $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$,
+and it corresponds to the complement event~$\Omega\backslash E$
+in classical probability.
 \end{itemize}
@@
   intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
-\end{definition}
+\qed\end{definition}
 

### 2016-05-16 prob.tex
prob.tex "Quantum Probability Spaces" Add thing; need to verify more...

@@
 is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
-elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
-events can be defined recursively as follow:
+elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$.
+The set of all events can be defined recursively as follow:
 \footnote {``Projection'' is sometimes called
@@
 means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
-and may be dropped when summands are clearly operators. 
+and may be dropped when there is no ambiguity. \\
+\yutsung{Need to prove: \\
+The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
+is also a projection operator if and only if they are orthogonal.}
 \item Conversely, every projection~$P$ can be expressed as
@@
 corresponds to the empty projection~$\mathbb{0}$ and the event of
-whole sample space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
+whole space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
 In contrast, the union~$\cup$ of any two events always gives an
@@
 however, $\mu\left(E_{1}\tensor*[_{\mathscr{O}}]{+}{}E_{2}\right)=\mu(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(E_{2})$
-is always true whenever the left-handed side is defined. Whether equation
+is always true whenever the left-handed side is defined. Whether an equation
 is defined also effects the further properties of quantum probability
@@
 
-\begin{definition}{[}Orthogonal Complement; Commutativity~\cite{peres1995quantum}{]} 
+\begin{definition}[Orthogonal Complement; Commutativity; Independence~\cite{peres1995quantum}]~
 \begin{itemize}
@@
 in classical probability.
+\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
+If the projections $P_{1}$ and $P_{2}$ commute, then $P_{1}P_{2}$
+is also a projection. This corresponds to the classical intersection
+between event. Given a quantum probability measure $\mu$, two projections
+$P_{1}$ and $P_{2}$ are independent if $P_{1}$ and $P_{2}$ commute
+and $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
 \end{itemize}
-Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
-  P_2P_1$;
-If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
-  a projection. Moreover, if $P_1$ and $P_2$ project onto
-  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
-  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
 \qed\end{definition}

### 2016-05-16 prob.tex
discreteGBKS.bib update citations....

@@
 
-\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
+\begin{definition}[Projection Operators;
+Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
 \label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
@@
 
-\begin{definition}[Orthogonal Complement; Commutativity; Independence~\cite{peres1995quantum}]~
+\begin{definition}[Complement; Commutativity;
+Independence~\cite{peres1995quantum,Griffiths2003}]~
 \begin{itemize}

### 2016-05-17 prob.tex
prob.tex small updates. Need to check the quantum independence...

@@
 The conventional definition of a probability
-space~\cite{Kolmogorov1950,rohatgi2011introduction,Swart2013}
+space~\cite{Kolmogorov1950,Shafer1976,Swart2013}
 builds upon the real numbers. In more detail, a probability space
@@
 interval-valued probability
-measures~\cite{Dempster1967,Zadeh1986,Weichselberger2000,JamisonLodwick2004}
+measures~\cite{Dempster1967,Shafer1976,Weichselberger2000,JamisonLodwick2004}
 in detail.\footnote{There is another possible approach that can be
@@
 \item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
-  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
-is also a projection, where the preposing subscript $\mathscr{O}$
+  P_2P_1 = \mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
+is also a projection operator if and only if they are orthogonal, 
+where the preposing subscript $\mathscr{O}$
 means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
-and may be dropped when there is no ambiguity. \\
-\yutsung{Need to prove: \\
-The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
-is also a projection operator if and only if they are orthogonal.}
+and may be dropped when there is no ambiguity. 
 \item Conversely, every projection~$P$ can be expressed as
@@
 \item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
-is also a projection operator. It is orthogonal to $P$, $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$,
-and it corresponds to the complement event~$\Omega\backslash E$
+is also a projection operator, called complement. It is orthogonal to $P$, has
+probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
+and corresponds to the complement event~$\Omega\backslash E$
 in classical probability.
 \item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
-If the projections $P_{1}$ and $P_{2}$ commute, then $P_{1}P_{2}$
-is also a projection. This corresponds to the classical intersection
+The product of two projection operators~$P_{1}P_{2}$ is also a projection
+operator if and only if they commute. This corresponds to the classical intersection
 between event. Given a quantum probability measure $\mu$, two projections

### 2016-05-18 prob.tex
prob.tex \section{Quantum Probability Spaces} Starting "independent"...

@@
 
-\begin{definition}[Complement; Commutativity;
-Independence~\cite{peres1995quantum,Griffiths2003}]~
+\begin{definition}[Complement; Commutativity~\cite{peres1995quantum,Griffiths2003}]~
 \begin{itemize}
@@
 operator if and only if they commute. This corresponds to the classical intersection
-between event. Given a quantum probability measure $\mu$, two projections
-$P_{1}$ and $P_{2}$ are independent if $P_{1}$ and $P_{2}$ commute
-and $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
+between events. 
+\item \yutsung{The definition of independence is difference from difference
+source:\\
+1. In~\cite{Swart2013}, given two algebras~$\mathscr{B}_{1}$ and
+$\mathscr{B}_{2}$ which commute with each other. They are \emph{logically
+independent} if for all state~$\rho_{1}$ on $\mathscr{B}_{1}$ and
+$\rho_{2}$ on $\mathscr{B}_{2}$, there is a unique state~$\rho$
+on $\mathscr{B}_{1}\otimes\mathscr{B}_{2}$ such that $\rho\left(B_{1}\otimes B_{2}\right)=\rho_{1}\left(B_{1}\right)\rho_{2}\left(B_{2}\right)$
+for all $B_{1}\in\mathscr{B}_{1}$ and $B_{2}\in\mathscr{B}_{2}$,
+which denoted by $\rho_{1}\otimes\rho_{2}$. Notice that we require
+$\mathscr{B}_{1}$ and $\mathscr{B}_{2}$ commute, and this definition
+doesn't depend on a particular $\rho$. Then, logically independence
+is used to defined the Bell inequality.\\
+2. In~\cite{Yuan2012}, given a $\rho$ on an algebra~$\mathscr{C}$,
+two sub-algebra $\mathscr{B}_{1}$ and $\mathscr{B}_{2}$ are independent
+if $\rho\left(B_{1}B_{2}\right)=\rho\left(B_{1}\right)\rho\left(B_{2}\right)$
+for all $B_{1}\in\mathscr{B}_{1}$ and $B_{2}\in\mathscr{B}_{2}$.
+Notice that we doesn't require $\mathscr{B}_{1}$ and $\mathscr{B}_{2}$
+commute, and this definition depend on a particular $\rho$.\\
+3. In~\cite{GuehneKleinmannCabelloEtAl2010}, let $A$, $B$ be compatible
+observables in a hidden variable model......................\\
+}
 \end{itemize}

### 2016-05-18 prob.tex
prob.tex \section{Quantum Probability Spaces} updates....

--- 2016-05-17 prob.tex
@@
 operator if and only if they commute. This corresponds to the classical intersection
-between event. Given a quantum probability measure $\mu$, two projections
-$P_{1}$ and $P_{2}$ are independent if $P_{1}$ and $P_{2}$ commute
-and $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
+between events. 
+\item ~\\ \yutsung{The definition of independence is different from different
+sources:\\
+1. In Swart's~\cite{Swart2013}, given two $*$-algebras~$\mathscr{A}_{1}$ and
+$\mathscr{A}_{2}$ which commute with each other. They are \emph{logically
+independent} if for all probability measure~$\mu_{1}$ on $\mathscr{A}_{1}$ and
+$\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu_{1}\otimes\mu_{2}$
+on $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$ such that
+$\left(\mu_{1}\otimes\mu_{2}\right)\left(A_{1}\otimes
+A_{2}\right)=\mu_{1}\left(A_{1}\right)\mu_{2}\left(A_{2}\right)$
+for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$. 
+Then, Swart proved the Bell inequality on logically independence $*$-algebras
+with product state. The problem for us is that this defines the independent of
+algebras, but not events\ldots\\
+2. In Yuan's~\cite{Yuan2012}, given a $\mu$ on an $*$-algebra~$\mathscr{A}$,
+two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are independent
+if $\mu\left(A_{1}A_{2}\right)=\mu\left(A_{1}\right)\mu\left(A_{2}\right)$
+for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.
+The problem for us is the same as the previous one: this defines the
+independent of algebras, but not events\ldots\\
+3. In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},
+we need first understand their notation. \cite{GuehneKleinmannCabelloEtAl2010}
+focus on the hidden-variable (HV) models, but their notation may be
+applied to the usual quantum model. \\
+}
 \end{itemize}

### 2016-05-19 prob.tex
prob.tex \section{Quantum Probability Spaces} Updates...

--- 2016-05-17 prob.tex
@@
 operator if and only if they commute. This corresponds to the classical intersection
-between event. Given a quantum probability measure $\mu$, two projections
-$P_{1}$ and $P_{2}$ are independent if $P_{1}$ and $P_{2}$ commute
-and $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
+between events. 
 \end{itemize}
+\yutsung{The definition of independence is different from different
+sources:
+\begin{enumerate}
+\item In Swart's~\cite{Swart2013}, two $*$-algebras~$\mathscr{A}_{1}$ and
+$\mathscr{A}_{2}$ which commute with each other are \emph{logically
+independent} if for all probability measure~$\mu_{1}$ on $\mathscr{A}_{1}$ and
+$\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu_{1}\otimes\mu_{2}$
+on $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$ such that
+$\left(\mu_{1}\otimes\mu_{2}\right)\left(A_{1}\otimes
+A_{2}\right)=\mu_{1}\left(A_{1}\right)\mu_{2}\left(A_{2}\right)$
+for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.\\
+Then, Swart proved the Bell inequality on logically independence $*$-algebras
+with product state. It is good that independence is tied up with Bell
+inequality, but the problem for us is that this defines the independent of
+algebras, but not events\ldots\\
+\item In Yuan's~\cite{Yuan2012}, given a $\mu$ on an $*$-algebra~$\mathscr{A}$,
+two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are independent
+if $\mu\left(A_{1}A_{2}\right)=\mu\left(A_{1}\right)\mu\left(A_{2}\right)$
+for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.
+The same problem as the previous one: this defines the
+independent of algebras, but not events\ldots\\
+\item In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},
+we need first understand their notation because they focused on the
+hidden-variable (HV) models. Let $\lambda$ is the HV, $A_{i}$ is
+the measurement of the observable~$A$ at the position $i$ in the
+sequence. For example, $A_{1}B_{2}C_{3}$ denotes the sequence of
+measuring $A$ first, then $B$, and finally $C$. We assume the outcome
+of an observable is deterministic by $\lambda$. For example, the
+outcome of $B_{2}$ from the preceding sequence is denoted by $v\left(B_{2}\middle|A_{1}B_{2}C_{3}\right)$.
+Then, the outcome of $A$ is independent of whether $B$ is measured
+before or after $A$ is $v\left(A_{1}\right)=v\left(A_{2}\middle|B_{1}A_{2}\right)$.\\
+If the outcomes of compatible observables are independent for any
+HV~$\lambda$, the HV model is non-contextual.\\
+Compare to the previous definitions, this definition is appealing
+in a sense that projection operators are special cases of observables,
+and the definition of independence is tied up with contextuality.
+However, before adopting their definition, we need to reformulate
+the definition to the usual quantum model....
+\end{enumerate}
+The definition of independence is interesting, and we definitely need
+to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
+theorem. However, the definition diverges, and none of them can apply
+directly. We may need to check more papers to find the majority or
+a more suitable definition...?}
 \qed\end{definition}

### 2016-05-19 prob.tex
prob.tex \section{Quantum Probability Spaces} Fix typos...

@@
 \item $\mu(\mathbb{1})=1$, and 
-\item for mutually orthogonal projections $E_{i}$, we have 
-$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}E_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(E_{i}\right)$.
+\item for mutually orthogonal projections $P_{i}$, we have 
+$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
 \end{itemize}
@@
 is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
-however, $\mu\left(E_{1}\tensor*[_{\mathscr{O}}]{+}{}E_{2}\right)=\mu(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(E_{2})$
+however, $\mu\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)=\mu(P_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(P_{2})$
 is always true whenever the left-handed side is defined. Whether an equation
@@
 inequality, but the problem for us is that this defines the independent of
-algebras, but not events\ldots\\
+algebras, but not events\ldots
 \item In Yuan's~\cite{Yuan2012}, given a $\mu$ on an $*$-algebra~$\mathscr{A}$,
@@
 The same problem as the previous one: this defines the
-independent of algebras, but not events\ldots\\
+independent of algebras, but not events\ldots
 \item In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},

### 2016-05-20 prob.tex
prob.tex \subsection{Real-Valued Probability Spaces} Add citation...
prob.tex \section{Quantum Probability Spaces} Updated....

@@
 The conventional definition of a probability
-space~\cite{Kolmogorov1950,Shafer1976,Swart2013}
+space~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}
 builds upon the real numbers. In more detail, a probability space
@@
 \end{itemize}
+\qed\end{definition}
 \yutsung{The definition of independence is different from different
@@
 the definition to the usual quantum model....
+\item For the definition we used last time, given a quantum probability
+measure~$\mu:\events\rightarrow[0,1]$, two commuting projections
+$P_{1}$ and $P_{2}$ are independent if $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
+We have two examples:
 \end{enumerate}
+}
+
+\yutsung{\begin{example}[Independence of product state] Consider
+the 2-qubit Hilbert space with a probability measure~$\mu\left(P\right)=\melement{\ps\ps}{P}$.
+Consider the following projections:
+\[
+\begin{array}{rcl}
+P_{1}=\proj{00}+\proj{01},\quad P_{2}=\proj{00}+\proj{10},\quad P_{3}=\proj{10}+\proj{11},\quad P_{4}=\proj{00}\end{array}
+\]
+and their probabilities: 
+\[
+\begin{array}{rcl}
+\mu\left(\mathbb{0}\right)=0,\quad\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/2,\quad\mu\left(P_{4}\right)=1/4\textrm{ .}\end{array}
+\]
+On one hand, $P_{1}$ and $P_{3}$ are complement to each other so
+we have
+\begin{eqnarray*}
+\mu\left(P_{1}\right)+\mu\left(P_{3}\right) & = & \frac{1}{2}+\frac{1}{2}=1\\
+\mu\left(P_{1}\right)\mu\left(P_{3}\right) & = & \frac{1}{4}\ne0=\mu\left(\mathbb{0}\right)=\mu\left(P_{1}P_{3}\right)
+\end{eqnarray*}
+Therefore, $P_{1}$ and $P_{3}$ commute, but not independent. On
+the other hand, $P_{1}$ also commutes with $P_{2}$, and
+\begin{eqnarray*}
+\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{4}\right)=\mu\left(P_{1}P_{2}\right)
+\end{eqnarray*}
+so that $P_{1}$ and $P_{2}$ are independent.\qed\end{example}
+
+\begin{example}[Independence of any states] In general, for any orthonormal
+basis~$\left\{ \ket{\psi_{j}}\right\} _{j=0}^{3}$, we can always
+pick 
+\[
+\begin{array}{rcl}
+P_{1}=\proj{\psi_{0}}+\proj{\psi_{1}},\quad P_{2}=\proj{\psi_{0}}+\proj{\psi_{2}},\quad P_{3}=\proj{\psi_{0}}\textrm{ .}\end{array}
+\]
+With the probability measure~$\mu\left(P\right)=\melement{\psi}{P}$,
+where $\ket{\psi}=\frac{1}{2}\sum_{j=0}^{3}\ket{\psi_{j}}$, their
+probabilities are
+\[
+\begin{array}{rcl}
+\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/4\textrm{ ,}\end{array}
+\]
+and we have
+\begin{eqnarray*}
+\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{3}\right)=\mu\left(P_{1}P_{2}\right)\textrm{ .}
+\end{eqnarray*}
+In particular, the following four Bell states form an orthonormal
+basis~\cite{CabelloPRL.86.2001}, 
+\begin{eqnarray*}
+\ket{\phi^{\pm}} & = & \frac{1}{\sqrt{2}}\left(\ket{00}\pm\ket{11}\right)\textrm{ ,}\\
+\ket{\psi^{\pm}} & = & \frac{1}{\sqrt{2}}\left(\ket{01}\pm\ket{10}\right)\textrm{ .}
+\end{eqnarray*}
+Their sum is also a Bell state~
+\[
+\ket{\psi}=\frac{1}{2}\left(\ket{\phi^{+}}+\ket{\phi^{-}}+\ket{\psi^{+}}+\ket{\psi^{-}}\right)=\frac{1}{\sqrt{2}}\left(\ket{00}+\ket{01}\right)\textrm{ .}
+\]
+With the probability measure~$\mu\left(P\right)=\melement{\psi}{P}$,
+$\proj{\phi^{+}}+\proj{\psi^{+}}$ and $\proj{\phi^{+}}+\proj{\psi^{-}}$
+are independent as we expect.\qed\end{example}
+
 The definition of independence is interesting, and we definitely need
 to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
-theorem. However, the definition diverges, and none of them can apply
-directly. We may need to check more papers to find the majority or
-a more suitable definition...?}
-\qed\end{definition}
+theorem. However, the definition diverges, and our definition didn't come from
+any sources directly. We may need to check more papers to find a source or
+adopt one of the majority definition (if there is one)...}
 

### 2016-05-20 prob.tex
prob.tex \section{Quantum Probability Spaces} updates...

@@
 \begin{enumerate}
-\item In Swart's~\cite{Swart2013}, two $*$-algebras~$\mathscr{A}_{1}$ and
-$\mathscr{A}_{2}$ which commute with each other are \emph{logically
+\item In Swart's~\cite{Swart2013}, given a $*$-algebra~$\mathscr{A}$,
+two commuting sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are \emph{logically
 independent} if for all probability measure~$\mu_{1}$ on $\mathscr{A}_{1}$ and
-$\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu_{1}\otimes\mu_{2}$
-on $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$ such that
-$\left(\mu_{1}\otimes\mu_{2}\right)\left(A_{1}\otimes
+$\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu$
+on the smallest sub-$*$-algebra of $\mathscr{A}$ containing both
+$\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ such that $\mu\left(A_{1}
 A_{2}\right)=\mu_{1}\left(A_{1}\right)\mu_{2}\left(A_{2}\right)$
-for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.\\
+for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$. If two
+sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are logically
+independent, the smallest sub-$*$-algebra containing both $\mathscr{A}_{1}$ and
+$\mathscr{A}_{2}$ is denoted by $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$, and
+its probability measure~$\mu$ is denoted by $\mu_{1}\otimes\mu_{2}$\\
 Then, Swart proved the Bell inequality on logically independence $*$-algebras
-with product state. It is good that independence is tied up with Bell
-inequality, but the problem for us is that this defines the independent of
-algebras, but not events\ldots
-\item In Yuan's~\cite{Yuan2012}, given a $\mu$ on an $*$-algebra~$\mathscr{A}$,
-two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are independent
+with a product state which gives a clear physical meaning. However, this
+only defines the independence of algebras instead of events.
+\item In Yuan's~\cite{Yuan2012}, given a $\mu$ on a $*$-algebra~$\mathscr{A}$,
+two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are \emph{independent}
 if $\mu\left(A_{1}A_{2}\right)=\mu\left(A_{1}\right)\mu\left(A_{2}\right)$
@@
 The same problem as the previous one: this defines the
-independent of algebras, but not events\ldots
+independent of algebras, but not events. Morever, I haven't found a clear
+physical meaning of this definition, yet\ldots
 \item In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},
-we need first understand their notation because they focused on the
+we need to first understand their notation because they focused on the
 hidden-variable (HV) models. Let $\lambda$ is the HV, $A_{i}$ is
@@
 sequence. For example, $A_{1}B_{2}C_{3}$ denotes the sequence of
-measuring $A$ first, then $B$, and finally $C$. We assume the outcome
-of an observable is deterministic by $\lambda$. For example, the
+measuring $A$ first, then $B$, and finally $C$. Given a fixed $\lambda$, we
+assume the outcome of an observable is deterministic. For example, the
 outcome of $B_{2}$ from the preceding sequence is denoted by $v\left(B_{2}\middle|A_{1}B_{2}C_{3}\right)$.
-Then, the outcome of $A$ is independent of whether $B$ is measured
+Then, the outcome of $A$ is \emph{independent} of whether $B$ is measured
 before or after $A$ is $v\left(A_{1}\right)=v\left(A_{2}\middle|B_{1}A_{2}\right)$.\\
 If the outcomes of compatible observables are independent for any
-HV~$\lambda$, the HV model is non-contextual.\\
+HV~$\lambda$, the HV model is non-contextual. (Notice that they have their own
+definition of ``compatible observables'' for their HV model\ldots)\\
 Compare to the previous definitions, this definition is appealing
 in a sense that projection operators are special cases of observables,
-and the definition of independence is tied up with contextuality.
+and this definition has a physical meaning related to contextuality.
 However, before adopting their definition, we need to reformulate
@@
 \yutsung{\begin{example}[Independence of product state] Consider
-the 2-qubit Hilbert space with a probability measure~$\mu\left(P\right)=\melement{\ps\ps}{P}$.
-Consider the following projections:
+the 2-qubit Hilbert space with a probability measure~$\mu\left(P\right)=\melement{\ps\ps}{P}$
+with the following projections:
 \[

### 2016-05-21 prob.tex
prob.tex \section{Quantum Probability Spaces} before send the email...

@@
 operator. 
-\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
+\item Projection operators $P_1$ and $P_2$ are \emph{orthogonal} if $P_1P_2 =
   P_2P_1 = \mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
@@
 \item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
-is also a projection operator, called complement. It is orthogonal to $P$, has
+is also a projection operator, called \emph{complement}. It is orthogonal to $P$, has
 probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
@@
 in classical probability.
-\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
+\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
 The product of two projection operators~$P_{1}P_{2}$ is also a projection
@@
 measure~$\mu:\events\rightarrow[0,1]$, two commuting projections
-$P_{1}$ and $P_{2}$ are independent if $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
+$P_{1}$ and $P_{2}$ are \emph{independent} if
+$\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
 We have two examples:
@@
 \end{eqnarray*}
-Therefore, $P_{1}$ and $P_{3}$ commute, but not independent. On
+Therefore, $P_{1}$ and $P_{3}$ commute, but are not independent. On
 the other hand, $P_{1}$ also commutes with $P_{2}$, and
@@
 In particular, the following four Bell states form an orthonormal
-basis~\cite{CabelloPRL.86.2001}, 
-\begin{eqnarray*}
-\ket{\phi^{\pm}} & = & \frac{1}{\sqrt{2}}\left(\ket{00}\pm\ket{11}\right)\textrm{ ,}\\
-\ket{\psi^{\pm}} & = & \frac{1}{\sqrt{2}}\left(\ket{01}\pm\ket{10}\right)\textrm{ .}
-\end{eqnarray*}
+basis~\cite{CabelloPRL.86.2001}: 
+\[
+\ket{\phi^{\pm}} = \frac{1}{\sqrt{2}}\left(\ket{00}\pm\ket{11}\right),\quad
+\ket{\psi^{\pm}} = \frac{1}{\sqrt{2}}\left(\ket{01}\pm\ket{10}\right)\textrm{ .}
+\]
 Their sum is also a Bell state~
@@
 \]
-With the probability measure~$\mu\left(P\right)=\melement{\psi}{P}$,
-$\proj{\phi^{+}}+\proj{\psi^{+}}$ and $\proj{\phi^{+}}+\proj{\psi^{-}}$
-are independent as we expect.\qed\end{example}
+We know $\proj{\phi^{+}}+\proj{\psi^{+}}$ and $\proj{\phi^{+}}+\proj{\psi^{-}}$
+are independent projections with respect to the probability
+measure~$\mu\left(P\right)=\melement{\psi}{P}$.\qed\end{example}
 
@@
 to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
-theorem. However, the definition diverges, and our definition didn't come from
-any sources directly. We may need to check more papers to find a source or
-adopt one of the majority definition (if there is one)...}
+theorem. However, the definition diverges, and I haven't found any source to
+support our definition, yet. We may need to check more papers to find a source
+to support our definition or to find the majority definition (if there is one)...}
 

### 2016-05-21 prob.tex
prob.tex Modify the discription of preposing symbols a little bit...

@@
 \item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$,
-where $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}a_{i}$
-explicitly specifies $a_{i}\in\mathbb{R}$. We may drop the preposing
-$\mathbb{R}$ when there is no confusion. 
+where $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$
+explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. Besides $\mathbb{R}$, We will
+prepose other symbols later to specify the type of operations, and they may be
+dropped when there is no ambiguity.
 \end{itemize}
@@
 $\left[1-r,1-l\right]$ which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
-where the preposing $\mathscr{I}$ specifies we subtracts intervals,
-and may be dropped clearly by content. Given
+where the preposing $\mathscr{I}$ specifies we subtracts intervals. Given
 a collection of intervals $\mathscr{I}$, an
@@
 where the preposing subscript $\mathscr{O}$
-means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
-and may be dropped when there is no ambiguity. 
+means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators. 
 \item Conversely, every projection~$P$ can be expressed as

### 2016-05-22 prob.tex
From: Tai, Yu-Tsung Sent: Saturday, May 21, 2016 23:16 To: Sabry, Amr A. <sabry@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu> Subject: RE: link
Dear all, 

I updated until the independence of quantum events... As in the PDF
file, it turns out that the definition of independence diverges, and
none of the source I have checked support our definition, yet. May I
confirm whether I should check more sources for quantum independence, or
I should move on to Section 3.1 Quantum Probability Measures first, and
we can discuss this part in our later meeting? T

@@
 ``orthogonal projection" or ``self-adjoint projection" to
-emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
+emphasize $P^{\dagger} = P$~\cite{Griffiths2003,Maassen2010}.}
 \begin{itemize}
@@
 \]
-We know $\proj{\phi^{+}}+\proj{\psi^{+}}$ and $\proj{\phi^{+}}+\proj{\psi^{-}}$
+Thus, $\proj{\phi^{+}}+\proj{\psi^{+}}$ and $\proj{\phi^{+}}+\proj{\psi^{-}}$
 are independent projections with respect to the probability
@@
 to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
-theorem. However, the definition diverges, and I haven't found any source to
+theorem. However, the definition diverges, and none of the source I have checked 
 support our definition, yet. We may need to check more papers to find a source

### 2016-05-25 prob.tex
Add reference for law of large number for Dempster-Shafer Theory

@@
 where $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$
-explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. Besides $\mathbb{R}$, We will
+explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. Besides $\mathbb{R}$, we will
 prepose other symbols later to specify the type of operations, and they may be
@@
 \subsection{Measuring Probabilities: Buffon's Needle Problem}
+
+In previous section, we assume the probability of each event is known
+a priori.
 

### 2016-05-28 prob.tex
Remove the citation which are not directly used...

@@
 interval-valued probability
-measures~\cite{Dempster1967,Shafer1976,Weichselberger2000,JamisonLodwick2004}
+measures~\cite{Dempster1967,Shafer1976,JamisonLodwick2004}
 in detail.\footnote{There is another possible approach that can be
   used to split the real interval $[0,1]$ into a collection of
-  subsets~\cite{Artstein1972,PuriRalescu1983} \amr{need to explain the
+  subsets~\cite{PuriRalescu1983} \amr{need to explain the
     connection and why we are not using it.}}

### 2016-05-28 prob.tex
prob.tex \subsection{Interval-valued probability measures} Starting verify the difference between Dempster-Shafer and Jamison-Lodwick...

@@
 $\mathscr{I}$--interval-valued probability measure is a function
-$\pmeas : \events \rightarrow \mathscr{I}$ such that:
+$\pmeas : \events \rightarrow \mathscr{I}$ such
+that~\cite{JamisonLodwick2004}:\footnote{Notice that the belief function defined by Dempster~\cite{Dempster1967}
+and Shafer~\cite{Shafer1976} is a special case of the interval-valued
+probability measures.}
 \begin{itemize}

### 2016-05-29 prob.tex
prob.tex \subsection{Measuring Probabilities: Buffon's Needle Problem} Start adding the law of large numbers...

@@
 In previous section, we assume the probability of each event is known
-a priori.
+a priori. In reality, we seldom know much about events, but we assume
+there is a probability behind each event, and the law of large numbers
+promises us a good approximation of the probability if the experiments
+run independently and identically for large enough times~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
 

### 2016-05-29 prob.tex
prob.tex \subsection{Measuring Probabilities: Buffon's Needle Problem} Updating the law of large numbers...

--- 2016-05-28 prob.tex
@@
 In previous section, we assume the probability of each event is known
-a priori.
+a priori. In reality, we seldom know much about events, but we assume
+each event~$E$ has a probability~$\pmeas(E)$. $\pmeas(E)$ could
+be approximated by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$,
+where $x_{i}$ is the outcome of $i$-th trial within total $N$ independent
+trials. This fact is called by the law of large numbers~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
 
@@
 $\frac{1224}{3204}$.
+
+Recall that the relative frequency will approximate the probability
+of an event if the event has a probability. What if the event doesn't
+have infinity precise probability because of the experimental limit?
+In this case, two sequences of independent copies of experimental
+results can have their relative frequencies converge almost surely
+to different limits~\cite{Marinacci1999,Teran2014}. In another word,
+to get a better approximation of the probability, the quality of experimental
+equipment cannot be compensated by the number of independent trials.
 

### 2016-05-30 prob.tex
prob.tex \subsection{Measuring Probabilities: Buffon's Needle Problem} update the law of large numbers...

@@
 
-In previous section, we assume the probability of each event is known
-a priori. In reality, we seldom know much about events, but we assume
-each event~$E$ has a probability~$\pmeas(E)$. $\pmeas(E)$ could
-be approximated by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$,
-where $x_{i}$ is the outcome of $i$-th trial within total $N$ independent
-trials. This fact is called by the law of large numbers~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
+In previous section, the probability of each event is known
+a priori. In reality, we seldom know much about events, but we could still assume
+each event~$E$ has a probability~$\pmeas(E)$. If we want to know the
+probability~$\pmeas(E)$, we could run $N$ independent trials. Let $x_{i}$ denote
+whether the event~$E$ occurs in the $i$-th trial or not, then $\pmeas(E)$ could
+be approximated to given accuracy by the relative
+frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability converging to one as
+$N$ goes to infinity. This fact is called the law of large numbers~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
 

### 2016-05-30 prob.tex
prob.tex After meeting...

@@
 \item Another version \url{https://pdfs.semanticscholar.org/3e9c/5f6f48d9ef426655dc799e9b287d754e86c1.pdf}
+\end{itemize}
+
+%%%%%
+\subsection{Plan}
+
+In the remainder of the paper, we consider variations of quantum
+probability spaces motivated by computation of numerical quantities in
+a world with limited resources:
+\begin{itemize}
+\item Instead of the Hilbert space $\Hilb$ (constructed over the
+  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
+  consider variants constructed over finite
+  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
+\item Instead of real-valued probability measures producing results in
+  the uncountable and uncomputable interval $[0,1]$, we will consider
+  finite set-valued probability measures~\cite{Artstein1972,PuriRalescu1983}.
+\end{itemize}
+We will then ask if it is possible to construct variants of quantum
+probability spaces under these conditions. The main question is
+related to the definition of probability measures: is it possible to
+still define a probability measure as a function that depends on a
+single state? Specifically,
+\begin{itemize}
+\item given a state $\ket{\psi}$, is there a probability measure
+  mapping events to probabilities that only depends on $\ket{\psi}$?
+  In the conventional quantum probability space, the answer is yes by
+  the Born rule~\cite{Born1984,Mermin2007} and the map is given by:
+  $E \mapsto \ip{\psi}{E\psi}$.
+\item given a probability measure $\mu$
+  mapping each event $E$
+  to a probability, is there a \emph{unique} state $\psi$
+  such that $\mu(E)
+  =
+  \ip{\psi}{E\psi}$? In the conventional case, the answer is yes by
+  Gleason's
+  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
 \end{itemize}
@@
 and Shafer~\cite{Shafer1976} is a special case of the interval-valued
-probability measures.}
+probability measures. Depending on how quantum interval probability goes, this
+section may be specialized to Dempster and Shafer only.}
 \begin{itemize}
@@
 
+\subsection{Quantum Events}
+
 \begin{definition}[Projection Operators;
@@
 \qed\end{definition}
-\yutsung{The definition of independence is different from different
-sources:
-\begin{enumerate}
-\item In Swart's~\cite{Swart2013}, given a $*$-algebra~$\mathscr{A}$,
-two commuting sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are \emph{logically
-independent} if for all probability measure~$\mu_{1}$ on $\mathscr{A}_{1}$ and
-$\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu$
-on the smallest sub-$*$-algebra of $\mathscr{A}$ containing both
-$\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ such that $\mu\left(A_{1}
-A_{2}\right)=\mu_{1}\left(A_{1}\right)\mu_{2}\left(A_{2}\right)$
-for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$. If two
-sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are logically
-independent, the smallest sub-$*$-algebra containing both $\mathscr{A}_{1}$ and
-$\mathscr{A}_{2}$ is denoted by $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$, and
-its probability measure~$\mu$ is denoted by $\mu_{1}\otimes\mu_{2}$\\
-Then, Swart proved the Bell inequality on logically independence $*$-algebras
-with a product state which gives a clear physical meaning. However, this
-only defines the independence of algebras instead of events.
-\item In Yuan's~\cite{Yuan2012}, given a $\mu$ on a $*$-algebra~$\mathscr{A}$,
-two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are \emph{independent}
-if $\mu\left(A_{1}A_{2}\right)=\mu\left(A_{1}\right)\mu\left(A_{2}\right)$
-for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.
-The same problem as the previous one: this defines the
-independent of algebras, but not events. Morever, I haven't found a clear
-physical meaning of this definition, yet\ldots
-\item In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},
-we need to first understand their notation because they focused on the
-hidden-variable (HV) models. Let $\lambda$ is the HV, $A_{i}$ is
-the measurement of the observable~$A$ at the position $i$ in the
-sequence. For example, $A_{1}B_{2}C_{3}$ denotes the sequence of
-measuring $A$ first, then $B$, and finally $C$. Given a fixed $\lambda$, we
-assume the outcome of an observable is deterministic. For example, the
-outcome of $B_{2}$ from the preceding sequence is denoted by $v\left(B_{2}\middle|A_{1}B_{2}C_{3}\right)$.
-Then, the outcome of $A$ is \emph{independent} of whether $B$ is measured
-before or after $A$ is $v\left(A_{1}\right)=v\left(A_{2}\middle|B_{1}A_{2}\right)$.\\
-If the outcomes of compatible observables are independent for any
-HV~$\lambda$, the HV model is non-contextual. (Notice that they have their own
-definition of ``compatible observables'' for their HV model\ldots)\\
-Compare to the previous definitions, this definition is appealing
-in a sense that projection operators are special cases of observables,
-and this definition has a physical meaning related to contextuality.
-However, before adopting their definition, we need to reformulate
-the definition to the usual quantum model....
-\item For the definition we used last time, given a quantum probability
-measure~$\mu:\events\rightarrow[0,1]$, two commuting projections
-$P_{1}$ and $P_{2}$ are \emph{independent} if
-$\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
-We have two examples:
-\end{enumerate}
-}
-
-\yutsung{\begin{example}[Independence of product state] Consider
-the 2-qubit Hilbert space with a probability measure~$\mu\left(P\right)=\melement{\ps\ps}{P}$
-with the following projections:
-\[
-\begin{array}{rcl}
-P_{1}=\proj{00}+\proj{01},\quad P_{2}=\proj{00}+\proj{10},\quad P_{3}=\proj{10}+\proj{11},\quad P_{4}=\proj{00}\end{array}
-\]
-and their probabilities: 
-\[
-\begin{array}{rcl}
-\mu\left(\mathbb{0}\right)=0,\quad\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/2,\quad\mu\left(P_{4}\right)=1/4\textrm{ .}\end{array}
-\]
-On one hand, $P_{1}$ and $P_{3}$ are complement to each other so
-we have
-\begin{eqnarray*}
-\mu\left(P_{1}\right)+\mu\left(P_{3}\right) & = & \frac{1}{2}+\frac{1}{2}=1\\
-\mu\left(P_{1}\right)\mu\left(P_{3}\right) & = & \frac{1}{4}\ne0=\mu\left(\mathbb{0}\right)=\mu\left(P_{1}P_{3}\right)
-\end{eqnarray*}
-Therefore, $P_{1}$ and $P_{3}$ commute, but are not independent. On
-the other hand, $P_{1}$ also commutes with $P_{2}$, and
-\begin{eqnarray*}
-\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{4}\right)=\mu\left(P_{1}P_{2}\right)
-\end{eqnarray*}
-so that $P_{1}$ and $P_{2}$ are independent.\qed\end{example}
-
-\begin{example}[Independence of any states] In general, for any orthonormal
-basis~$\left\{ \ket{\psi_{j}}\right\} _{j=0}^{3}$, we can always
-pick 
-\[
-\begin{array}{rcl}
-P_{1}=\proj{\psi_{0}}+\proj{\psi_{1}},\quad P_{2}=\proj{\psi_{0}}+\proj{\psi_{2}},\quad P_{3}=\proj{\psi_{0}}\textrm{ .}\end{array}
-\]
-With the probability measure~$\mu\left(P\right)=\melement{\psi}{P}$,
-where $\ket{\psi}=\frac{1}{2}\sum_{j=0}^{3}\ket{\psi_{j}}$, their
-probabilities are
-\[
-\begin{array}{rcl}
-\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/4\textrm{ ,}\end{array}
-\]
-and we have
-\begin{eqnarray*}
-\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{3}\right)=\mu\left(P_{1}P_{2}\right)\textrm{ .}
-\end{eqnarray*}
-In particular, the following four Bell states form an orthonormal
-basis~\cite{CabelloPRL.86.2001}: 
-\[
-\ket{\phi^{\pm}} = \frac{1}{\sqrt{2}}\left(\ket{00}\pm\ket{11}\right),\quad
-\ket{\psi^{\pm}} = \frac{1}{\sqrt{2}}\left(\ket{01}\pm\ket{10}\right)\textrm{ .}
-\]
-Their sum is also a Bell state~
-\[
-\ket{\psi}=\frac{1}{2}\left(\ket{\phi^{+}}+\ket{\phi^{-}}+\ket{\psi^{+}}+\ket{\psi^{-}}\right)=\frac{1}{\sqrt{2}}\left(\ket{00}+\ket{01}\right)\textrm{ .}
-\]
-Thus, $\proj{\phi^{+}}+\proj{\psi^{+}}$ and $\proj{\phi^{+}}+\proj{\psi^{-}}$
-are independent projections with respect to the probability
-measure~$\mu\left(P\right)=\melement{\psi}{P}$.\qed\end{example}
-
-The definition of independence is interesting, and we definitely need
-to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
-theorem. However, the definition diverges, and none of the source I have checked 
-support our definition, yet. We may need to check more papers to find a source
-to support our definition or to find the majority definition (if there is one)...}
+% \yutsung{The definition of independence is different from different
+% sources:
+% \begin{enumerate}
+% \item In Swart's~\cite{Swart2013}, given a $*$-algebra~$\mathscr{A}$,
+% two commuting sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are \emph{logically
+% independent} if for all probability measure~$\mu_{1}$ on $\mathscr{A}_{1}$ and
+% $\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu$
+% on the smallest sub-$*$-algebra of $\mathscr{A}$ containing both
+% $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ such that $\mu\left(A_{1}
+% A_{2}\right)=\mu_{1}\left(A_{1}\right)\mu_{2}\left(A_{2}\right)$
+% for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$. If two
+% sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are logically
+% independent, the smallest sub-$*$-algebra containing both $\mathscr{A}_{1}$ and
+% $\mathscr{A}_{2}$ is denoted by $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$, and
+% its probability measure~$\mu$ is denoted by $\mu_{1}\otimes\mu_{2}$\\
+% Then, Swart proved the Bell inequality on logically independence $*$-algebras
+% with a product state which gives a clear physical meaning. However, this
+% only defines the independence of algebras instead of events.
+% \item In Yuan's~\cite{Yuan2012}, given a $\mu$ on a $*$-algebra~$\mathscr{A}$,
+% two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are \emph{independent}
+% if $\mu\left(A_{1}A_{2}\right)=\mu\left(A_{1}\right)\mu\left(A_{2}\right)$
+% for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.
+% The same problem as the previous one: this defines the
+% independent of algebras, but not events. Morever, I haven't found a clear
+% physical meaning of this definition, yet\ldots
+% \item In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},
+% we need to first understand their notation because they focused on the
+% hidden-variable (HV) models. Let $\lambda$ is the HV, $A_{i}$ is
+% the measurement of the observable~$A$ at the position $i$ in the
+% sequence. For example, $A_{1}B_{2}C_{3}$ denotes the sequence of
+% measuring $A$ first, then $B$, and finally $C$. Given a fixed $\lambda$, we
+% assume the outcome of an observable is deterministic. For example, the
+% outcome of $B_{2}$ from the preceding sequence is denoted by $v\left(B_{2}\middle|A_{1}B_{2}C_{3}\right)$.
+% Then, the outcome of $A$ is \emph{independent} of whether $B$ is measured
+% before or after $A$ is $v\left(A_{1}\right)=v\left(A_{2}\middle|B_{1}A_{2}\right)$.\\
+% If the outcomes of compatible observables are independent for any
+% HV~$\lambda$, the HV model is non-contextual. (Notice that they have their own
+% definition of ``compatible observables'' for their HV model\ldots)\\
+% Compare to the previous definitions, this definition is appealing
+% in a sense that projection operators are special cases of observables,
+% and this definition has a physical meaning related to contextuality.
+% However, before adopting their definition, we need to reformulate
+% the definition to the usual quantum model....
+% \item For the definition we used last time, given a quantum probability
+% measure~$\mu:\events\rightarrow[0,1]$, two commuting projections
+% $P_{1}$ and $P_{2}$ are \emph{independent} if
+% $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
+% We have two examples:
+% \end{enumerate}
+% }
+% 
+% \yutsung{\begin{example}[Independence of product state] Consider
+% the 2-qubit Hilbert space with a probability measure~$\mu\left(P\right)=\melement{\ps\ps}{P}$
+% with the following projections:
+% \[
+% \begin{array}{rcl}
+% P_{1}=\proj{00}+\proj{01},\quad P_{2}=\proj{00}+\proj{10},\quad P_{3}=\proj{10}+\proj{11},\quad P_{4}=\proj{00}\end{array}
+% \]
+% and their probabilities: 
+% \[
+% \begin{array}{rcl}
+% \mu\left(\mathbb{0}\right)=0,\quad\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/2,\quad\mu\left(P_{4}\right)=1/4\textrm{ .}\end{array}
+% \]
+% On one hand, $P_{1}$ and $P_{3}$ are complement to each other so
+% we have
+% \begin{eqnarray*}
+% \mu\left(P_{1}\right)+\mu\left(P_{3}\right) & = & \frac{1}{2}+\frac{1}{2}=1\\
+% \mu\left(P_{1}\right)\mu\left(P_{3}\right) & = & \frac{1}{4}\ne0=\mu\left(\mathbb{0}\right)=\mu\left(P_{1}P_{3}\right)
+% \end{eqnarray*}
+% Therefore, $P_{1}$ and $P_{3}$ commute, but are not independent. On
+% the other hand, $P_{1}$ also commutes with $P_{2}$, and
+% \begin{eqnarray*}
+% \mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{4}\right)=\mu\left(P_{1}P_{2}\right)
+% \end{eqnarray*}
+% so that $P_{1}$ and $P_{2}$ are independent.\qed\end{example}
+% 
+% \begin{example}[Independence of any states] In general, for any orthonormal
+% basis~$\left\{ \ket{\psi_{j}}\right\} _{j=0}^{3}$, we can always
+% pick 
+% \[
+% \begin{array}{rcl}
+% P_{1}=\proj{\psi_{0}}+\proj{\psi_{1}},\quad P_{2}=\proj{\psi_{0}}+\proj{\psi_{2}},\quad P_{3}=\proj{\psi_{0}}\textrm{ .}\end{array}
+% \]
+% With the probability measure~$\mu\left(P\right)=\melement{\psi}{P}$,
+% where $\ket{\psi}=\frac{1}{2}\sum_{j=0}^{3}\ket{\psi_{j}}$, their
+% probabilities are
+% \[
+% \begin{array}{rcl}
+% \mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/4\textrm{ ,}\end{array}
+% \]
+% and we have
+% \begin{eqnarray*}
+% \mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{3}\right)=\mu\left(P_{1}P_{2}\right)\textrm{ .}
+% \end{eqnarray*}
+% In particular, the following four Bell states form an orthonormal
+% basis~\cite{CabelloPRL.86.2001}: 
+% \[
+% \ket{\phi^{\pm}} = \frac{1}{\sqrt{2}}\left(\ket{00}\pm\ket{11}\right),\quad
+% \ket{\psi^{\pm}} = \frac{1}{\sqrt{2}}\left(\ket{01}\pm\ket{10}\right)\textrm{ .}
+% \]
+% Their sum is also a Bell state~
+% \[
+% \ket{\psi}=\frac{1}{2}\left(\ket{\phi^{+}}+\ket{\phi^{-}}+\ket{\psi^{+}}+\ket{\psi^{-}}\right)=\frac{1}{\sqrt{2}}\left(\ket{00}+\ket{01}\right)\textrm{ .}
+% \]
+% Thus, $\proj{\phi^{+}}+\proj{\psi^{+}}$ and $\proj{\phi^{+}}+\proj{\psi^{-}}$
+% are independent projections with respect to the probability
+% measure~$\mu\left(P\right)=\melement{\psi}{P}$.\qed\end{example}}
+
+\footnote{\yutsung{The definition of independence is interesting, and we
+definitely need to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
+theorem. However, the definition diverges. So we just leave it so far, and we
+will go back if we really need it. (Maybe when discussing repeating
+experiments?)}}
 
@@
 state and $\rho=E$. \qed\end{example}
+
+\subsection{Measuring Quantum Probabilities}
+\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}
+
+\subsection{Quantum Interval-valued Probabilities Measures}
+\cite{Vourdas2014, Vourdas2015}
 
@@
 \end{proof}
-
-%%%%%
-\subsection{Plan}
-
-In the remainder of the paper, we consider variations of quantum
-probability spaces motivated by computation of numerical quantities in
-a world with limited resources:
-\begin{itemize}
-\item Instead of the Hilbert space $\Hilb$ (constructed over the
-  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
-  consider variants constructed over finite
-  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
-\item Instead of real-valued probability measures producing results in
-  the uncountable and uncomputable interval $[0,1]$, we will consider
-  finite set-valued probability measures~\cite{Artstein1972,PuriRalescu1983}.
-\end{itemize}
-We will then ask if it is possible to construct variants of quantum
-probability spaces under these conditions. The main question is
-related to the definition of probability measures: is it possible to
-still define a probability measure as a function that depends on a
-single state? Specifically,
-\begin{itemize}
-\item given a state $\ket{\psi}$, is there a probability measure
-  mapping events to probabilities that only depends on $\ket{\psi}$?
-  In the conventional quantum probability space, the answer is yes by
-  the Born rule~\cite{Born1984,Mermin2007} and the map is given by:
-  $E \mapsto \ip{\psi}{E\psi}$.
-\item given a probability measure $\mu$
-  mapping each event $E$
-  to a probability, is there a \emph{unique} state $\psi$
-  such that $\mu(E)
-  =
-  \ip{\psi}{E\psi}$? In the conventional case, the answer is yes by
-  Gleason's
-  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
-\end{itemize}
 

### 2016-05-30 prob.tex
discreteGBKS.bib update citation...

@@
 To properly explain the previous example and generalize to arbitrary
-quantum systems, we formally discuss projection operators and then
-define a quantum probability space.
+quantum systems, we formally discuss projection operators, 
+define quantum probability measures, and extend to quantum interval-valued
+probability.
 
@@
 theorem. However, the definition diverges. So we just leave it so far, and we
-will go back if we really need it. (Maybe when discussing repeating
+will go back if we really need it in this paper. (Maybe when discussing repeating
 experiments?)}}

### 2016-06-04 prob.tex
discreteGBKS.bib update citation...
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} start throwing some comments...

@@
 frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability converging to one as
-$N$ goes to infinity. This fact is called the law of large numbers~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
+$N$ goes to infinity. This fact is called the law of large
+numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
 
@@
 
+%%%%%
 \subsection{Measuring Quantum Probabilities}
@@
 
+%%%%%
 \subsection{Quantum Interval-valued Probabilities Measures}
-\cite{Vourdas2014, Vourdas2015}
+\yutsung{Vourdas' first paper~\cite{Vourdas2014} is interesting
+and highly readable until section IV. However, I don't understand
+since the second sentence in section IV:
+\begin{itemize}
+\item If $\mathfrak{d}\left(H_{1},H_{2}\middle|\rho\right)\ge0$, then $p\left(H_{1}\middle|\rho\right)$
+and $p\left(H_{2}\middle|\rho\right)$ are lower probabilities. Also,
+according to Eq. (22), in this case $\mathfrak{d}\left(H_{1}^{\perp},H_{2}^{\perp}\middle|\rho\right)\le0$,
+and therefore the $p\left(H_{1}^{\perp}\middle|\rho\right)$ and $p\left(H_{2}^{\perp}\middle|\rho\right)$
+are upper probabilities.
+\end{itemize}
+I assume Vourdas means that $p\left(H_{1}\middle|\rho\right)$ and
+$p\left(H_{1}^{\perp}\middle|\rho\right)$ are the lower and upper
+probability respectively for measuring subspace~$H_{1}$ on the system~$\rho$.
+Consider the simplest example the subspace $H_{1}$ is the zero space
+$\mathcal{O}$ which commutes with every other subspaces, so $\mathfrak{d}\left(\mathcal{O},H_{2}\middle|\rho\right)=0$.
+Then, for measuring $\mathcal{O}$ on $\rho$, the lower and upper
+probabilities are $p\left(\mathcal{O}\middle|\rho\right)=0$ and $p\left(\mathcal{O}^{\perp}\middle|\rho\right)=p\left(\mathcal{I}\middle|\rho\right)=1$,
+respectively. The lower probability is $0$ makes sense, but I don't
+understand why the upper probability is $1$. Because both the lower
+and upper probabilities of the empty set are $0$ in classical Dempster-Shafer
+theory.
+
+Start reading \cite{Vourdas2015}...}
 

### 2016-06-04 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} starting to update my last comment...

@@
 \subsection{Quantum Interval-valued Probabilities Measures}
+
 \yutsung{Vourdas' first paper~\cite{Vourdas2014} is interesting
-and highly readable until section IV. However, I don't understand
-since the second sentence in section IV:
+and highly readable until section IV. In particular, the comparison
+between the Kolmogorov's
+\[
+\delta\left(A,B\right)=q\left(A\vee B\right)-q\left(A\right)-q\left(B\right)+q\left(A\wedge B\right)
+\]
+where $A$ and $B$ are events, and $q\left(A\right)$ is the probability
+of $A$; and its quantum counterpart 
+\[
+\mathfrak{D}\left(H_{1},H_{2}\right)=\mathfrak{P}\left(H_{1}\vee H_{2}\right)-\mathfrak{P}\left(H_{1}\right)-\mathfrak{P}\left(H_{2}\right)+\mathfrak{P}\left(H_{1}\wedge H_{2}\right)
+\]
+
+However, his section VI is confusing. For example, the second sentence
+in section IV: 
 \begin{itemize}

### 2016-06-04 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} starting to update my last comment...

--- 2016-06-04 prob.tex
@@
 \subsection{Quantum Interval-valued Probabilities Measures}
-\yutsung{Vourdas' first paper~\cite{Vourdas2014} is interesting
-and highly readable until section IV. However, I don't understand
-since the second sentence in section IV:
+
+\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas made a comparison
+between additivity of Kolmogorov and quantum probabilities. The additivity
+property of Kolmogorov probabilities 
+\[
+\delta\left(A,B\right)=q\left(A\vee B\right)-q\left(A\right)-q\left(B\right)+q\left(A\wedge B\right)=0\textrm{ ,}
+\]
+where $A$ and $B$ are events, and $q\left(A\right)$ is the probability
+of $A$. Its quantum counterpart is 
+\[
+\mathfrak{D}\left(H_{1},H_{2}\right)=\Pi\left(H_{1}\vee H_{2}\right)-\Pi\left(H_{1}\right)-\Pi\left(H_{2}\right)+\Pi\left(H_{1}\wedge H_{2}\right)\textrm{ ,}
+\]
+
+However, his section VI is confusing. For example, the second sentence
+in section IV: 
 \begin{itemize}
@@
 and upper probabilities of the empty set are $0$ in classical Dempster-Shafer
-theory.
-
-Start reading \cite{Vourdas2015}...}
+theory.}
 

### 2016-06-04 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} keep updating comments...

--- 2016-06-04 prob.tex
@@
 \subsection{Quantum Interval-valued Probabilities Measures}
-\yutsung{Vourdas' first paper~\cite{Vourdas2014} is interesting
-and highly readable until section IV. However, I don't understand
-since the second sentence in section IV:
+
+\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas made a comparison
+between the additivity property of Kolmogorov probabilities 
+\[
+\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0
+\]
+and its quantum counterpart 
+\[
+\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
+\]
+where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
+maps a linear space to its projection operator. Since the non-additivity
+operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$ is non-zero when
+$S_{1}$ and $S_{2}$ does not commute.
+
+However, his section VI is confusing. For example, the second sentence
+in section IV: 
 \begin{itemize}

### 2016-06-05 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} update comments...

@@
 
-\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
+\begin{definition}[Quantum Probability
+Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
   Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
@@
 where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
-maps a linear space to its projection operator. Since the non-additivity
-operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$ is non-zero when
-$S_{1}$ and $S_{2}$ does not commute.
+maps a linear space to its projection operator. In the Dempster-Shafer
+theory, the additivity property is relaxed such that $\delta\left(E_{1},E_{2}\right)\ge0$
+for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
+for the upper probability or plausibility. The sign of $\delta\left(E_{1},E_{2}\right)$
+is then analog to $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
+given the density matrix~$\rho$ since the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
+is non-zero when $S_{1}$ and $S_{2}$ does not commute.
+
+A special feature of this theory is that it discusses the relation
+between non-commuting subspaces while the real-valued quantum probability
+measures in definition~\ref{def:QuantumProbabilitySpace} only depend
+on orthogonal (or commuting) subspaces. Thinking a physical process
+which put two non-commuting spaces together... Maybe two directions
+of the first spin in the two-spin system?
 

### 2016-06-05 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} Add an example but still don't have intuition...

@@
 
-A special feature of this theory is that it discusses the relation
-between non-commuting subspaces while the real-valued quantum probability
-measures in definition~\ref{def:QuantumProbabilitySpace} only depend
-on orthogonal (or commuting) subspaces. Thinking a physical process
-which put two non-commuting spaces together... Maybe two directions
-of the first spin in the two-spin system?
+Interestingly, this theory discussed the relation between non-commuting
+subspaces while the real-valued quantum probability measures in definition~\ref{def:QuantumProbabilitySpace}
+only depend on orthogonal (or commuting) subspaces. In order to understand
+the intuition, let's go through the simplest example.
+
+\begin{example}{[}Two-qubit quantum probability space{]} Consider
+a two-qubit Hilbert space with the following subspaces:
+\begin{eqnarray*}
+S_{00} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{0}\right\} \right)\\
+S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{+}\right\} \right)\\
+S_{00}\wedge S_{0+} & = & \mathcal{O}=\left\{ 0\right\} \\
+S_{00}\vee S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\right\} \right)\otimes\C^{2}
+\end{eqnarray*}
+ Then, their projection and non-additivity operators are 
+\begin{eqnarray*}
+\Pi\left(S_{00}\right) & = & \proj{0}\otimes\proj{0}\\
+\Pi\left(S_{0+}\right) & = & \proj{0}\otimes\proj{+}\\
+\Pi\left(S_{00}\wedge S_{0+}\right) & = & \mathbb{0}\otimes\mathbb{0}\\
+\Pi\left(S_{00}\vee S_{0+}\right) & = & \proj{0}\otimes\mathbb{1}\\
+\mathfrak{D}\left(S_{1},S_{2}\right) & = & \proj{0}\otimes\left(-\sigma_{x}-\sigma_{z}\right)
+\end{eqnarray*}
+We also consider the density matrix $\rho=a\proj{0}\otimes\proj{0}+\left(1-a\right)\proj{0}\otimes\proj{1}$
+for $a\in\left[0,1\right]$. According to the Born rule, their probabilities
+are
+\begin{eqnarray*}
+\Tr\left(\rho\Pi\left(S_{00}\right)\right) & = & a\\
+\Tr\left(\rho\Pi\left(S_{0+}\right)\right) & = & \frac{1}{2}\left[a+\left(1-a\right)\right]=\frac{1}{2}\\
+\Tr\left(\rho\Pi\left(S_{00}\wedge S_{0+}\right)\right) & = & 0\\
+\Tr\left(\rho\Pi\left(S_{00}\vee S_{0+}\right)\right) & = & a+\left(1-a\right)=1
+\end{eqnarray*}
+and the non-additivity quantity~$\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\frac{1}{2}\left[-a+\left(1-a\right)\right]=\frac{1}{2}-a$.
+However, I still don't have much intuition on why the probabilities
+should have what kind of relations?\qed\end{example}
 

### 2016-06-09 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} Updating...

@@
 \[
-\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
+\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\Tr\left(\rho\Pi\left(S_{1}\vee S_{2}\right)\right)-\Tr\left(\rho\Pi\left(S_{1}\right)\right)-\Tr\left(\rho\Pi\left(S_{2}\right)\right)+\Tr\left(\rho\Pi\left(S_{1}\wedge S_{2}\right)\right)\textrm{ ,}
 \]
 where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
-maps a linear space to its projection operator. In the Dempster-Shafer
-theory, the additivity property is relaxed such that $\delta\left(E_{1},E_{2}\right)\ge0$
+maps a linear space to its projection operator. While $\delta\left(E_{1},E_{2}\right)$
+is always zero for Kolmogorov probabilities, the additivity property
+of the Dempster-Shafer theory is relaxed to $\delta\left(E_{1},E_{2}\right)\ge0$
 for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
 for the upper probability or plausibility. The sign of $\delta\left(E_{1},E_{2}\right)$
-is then analog to $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
+is then analog to the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
 given the density matrix~$\rho$ since the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
-is non-zero when $S_{1}$ and $S_{2}$ does not commute.
+is non-zero when $S_{1}$ and $S_{2}$ does not commute so that $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
+is not always zero.
+
+The Kolmogorov's $\delta\left(E_{1},E_{2}\right)=0$ is intuitive
+because the relative frequencies of disjoint events should be additive
+if the measurement is accurate. In the Dempster-Shafer theory, the
+additivity property is modified because the imprecision of whether
+an event happens or not is taken into account, but we can still decide
+whether an instance belongs to different events concurrently. Applying
+this idea to quantum, if we runs $N$ independent Stern-Galech
 
@@
 
-\begin{example}{[}Two-qubit quantum probability space{]} Consider
+\begin{example}[Two-qubit quantum probability space] Consider
 a two-qubit Hilbert space with the following subspaces:

### 2016-06-09 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} updating...

--- 2016-06-05 prob.tex
@@
 %%%%%
-\subsection{Measuring Probabilities: Buffon's Needle Problem}
+\subsection{Measuring Probabilities: Buffon's Needle
+Problem\label{subsec:Measuring-Probabilities:-Buffon}}
 
@@
 
-\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas made a comparison
-between the additivity property of Kolmogorov probabilities 
-\[
-\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0
-\]
-and its quantum counterpart 
+\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas started from
+the additivity property of Kolmogorov probabilities 
+\begin{equation}
+\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0\label{eq:Kolmogorov}
+\end{equation}
+which is intuitive because the relative frequencies of disjoint events
+should be additive if the measurement is accurate. While $\delta\left(E_{1},E_{2}\right)$
+is always zero for Kolmogorov probabilities, the additivity property
+of the Dempster-Shafer theory is relaxed to $\delta\left(E_{1},E_{2}\right)\ge0$
+for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
+for the upper probability or plausibility. This modification is also
+intuitive because the imprecision of whether an event happens or not
+is taken into account, but we can still decide whether an instance
+belongs to different events concurrently.
+
+Vourdas observed that equation (\ref{eq:Kolmogorov}) is similar to
 \[
@@
 \]
-where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
-maps a linear space to its projection operator. In the Dempster-Shafer
-theory, the additivity property is relaxed such that $\delta\left(E_{1},E_{2}\right)\ge0$
-for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
-for the upper probability or plausibility. The sign of $\delta\left(E_{1},E_{2}\right)$
-is then analog to $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
-given the density matrix~$\rho$ since the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
-is non-zero when $S_{1}$ and $S_{2}$ does not commute.
-
-Interestingly, this theory discussed the relation between non-commuting
-subspaces while the real-valued quantum probability measures in definition~\ref{def:QuantumProbabilitySpace}
-only depend on orthogonal (or commuting) subspaces. In order to understand
-the intuition, let's go through the simplest example.
-
-\begin{example}{[}Two-qubit quantum probability space{]} Consider
+where $S_{1}$ and $S_{2}$ are arbitrary linear subspaces, and $\Pi$
+maps a linear subspace to its projection operator. After apply the
+Born rule on both sides, we get an equation about the probabilities
+\begin{equation}
+\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\Tr\left(\rho\Pi\left(S_{1}\vee S_{2}\right)\right)-\Tr\left(\rho\Pi\left(S_{1}\right)\right)-\Tr\left(\rho\Pi\left(S_{2}\right)\right)+\Tr\left(\rho\Pi\left(S_{1}\wedge S_{2}\right)\right)\textrm{ .}\label{eq:quantum-additivity}
+\end{equation}
+Given the density matrix~$\rho$, the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
+is then analog to the sign of $\delta\left(E_{1},E_{2}\right)$ since
+the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
+is non-zero when $S_{1}$ and $S_{2}$ does not commute so that $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
+is not always zero. Vourdas then considered the pair $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
+and $\Tr\left(\rho\Pi\left(S_{2}\right)\right)$ are lower or upper
+probabilities depending on the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$.
+Although Vourdas' idea is clear, the approach does not exactly fit
+the idea. First, when we measure a physical quantity, we consider
+the eigenspaces of an observable which always commute. According to
+Vourdas' definition, $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
+is then always an Kolmogorov probability within one measurement process.
+Second, if we adopt the frequency interpretation as in section \ref{subsec:Measuring-Probabilities:-Buffon},
+consider the following two-qubit example.
+
+\begin{example}[Two-qubit quantum probability space] Consider
 a two-qubit Hilbert space with the following subspaces:
@@
 \end{eqnarray*}
+We can implement the first qubit by the spin of a particle and the
+second qubit in path
+
  Then, their projection and non-additivity operators are 

### 2016-06-09 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} keep typing...

@@
 Second, if we adopt the frequency interpretation as in section \ref{subsec:Measuring-Probabilities:-Buffon},
-consider the following two-qubit example.
+and implement our one-qubit example in the Stern-Gerlach experiment.
+Let $S_{1}=\left\{ \lambda\ket{0}\middle|\lambda\in\C\right\} $ and
+$S_{2}=\left\{ \lambda\ket{\ps}\middle|\lambda\in\C\right\} $.
 

### 2016-06-10 prob.tex
Update citations...

@@
   In the conventional quantum probability space, the answer is yes by
-  the Born rule~\cite{Born1984,Mermin2007} and the map is given by:
+  the Born rule~\cite{Born1983,Mermin2007} and the map is given by:
   $E \mapsto \ip{\psi}{E\psi}$.
@@
 For a given set of events $\events$, there are many possible probability
-measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1984,Mermin2007,RiederSvozil2007},
+measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
 a postulate of quantum mechanics, states that each pure quantum state
@@
 Second, if we adopt the frequency interpretation as in section \ref{subsec:Measuring-Probabilities:-Buffon},
-and implement our one-qubit example in the Stern-Gerlach experiment.
+and implement our one-qubit example in the Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
 Let $S_{1}=\left\{ \lambda\ket{0}\middle|\lambda\in\C\right\} $ and
@@
 induces a probability measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$
-on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
+on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1983,Mermin2007}:
 \begin{equation}

### 2016-06-11 prob.tex
prob.tex Create New Branch for ignoring Vourdas' paper...

@@
 
-\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas started from
-the additivity property of Kolmogorov probabilities 
-\begin{equation}
-\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0\label{eq:Kolmogorov}
-\end{equation}
-which is intuitive because the relative frequencies of disjoint events
-should be additive if the measurement is accurate. While $\delta\left(E_{1},E_{2}\right)$
-is always zero for Kolmogorov probabilities, the additivity property
-of the Dempster-Shafer theory is relaxed to $\delta\left(E_{1},E_{2}\right)\ge0$
-for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
-for the upper probability or plausibility. This modification is also
-intuitive because the imprecision of whether an event happens or not
-is taken into account, but we can still decide whether an instance
-belongs to different events concurrently.
-
-Vourdas observed that equation (\ref{eq:Kolmogorov}) is similar to
-\[
-\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
-\]
-where $S_{1}$ and $S_{2}$ are arbitrary linear subspaces, and $\Pi$
-maps a linear subspace to its projection operator. After apply the
-Born rule on both sides, we get an equation about the probabilities
-\begin{equation}
-\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\Tr\left(\rho\Pi\left(S_{1}\vee S_{2}\right)\right)-\Tr\left(\rho\Pi\left(S_{1}\right)\right)-\Tr\left(\rho\Pi\left(S_{2}\right)\right)+\Tr\left(\rho\Pi\left(S_{1}\wedge S_{2}\right)\right)\textrm{ .}\label{eq:quantum-additivity}
-\end{equation}
-Given the density matrix~$\rho$, the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
-is then analog to the sign of $\delta\left(E_{1},E_{2}\right)$ since
-the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
-is non-zero when $S_{1}$ and $S_{2}$ does not commute so that $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
-is not always zero. Vourdas then considered the pair $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
-and $\Tr\left(\rho\Pi\left(S_{2}\right)\right)$ are lower or upper
-probabilities depending on the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$.
-Although Vourdas' idea is clear, the approach does not exactly fit
-the idea. First, when we measure a physical quantity, we consider
-the eigenspaces of an observable which always commute. According to
-Vourdas' definition, $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
-is then always an Kolmogorov probability within one measurement process.
-Second, if we adopt the frequency interpretation as in section \ref{subsec:Measuring-Probabilities:-Buffon},
-and implement our one-qubit example in the Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
-Let $S_{1}=\left\{ \lambda\ket{0}\middle|\lambda\in\C\right\} $ and
-$S_{2}=\left\{ \lambda\ket{\ps}\middle|\lambda\in\C\right\} $.
-
-\begin{example}[Two-qubit quantum probability space] Consider
-a two-qubit Hilbert space with the following subspaces:
-\begin{eqnarray*}
-S_{00} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{0}\right\} \right)\\
-S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{+}\right\} \right)\\
-S_{00}\wedge S_{0+} & = & \mathcal{O}=\left\{ 0\right\} \\
-S_{00}\vee S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\right\} \right)\otimes\C^{2}
-\end{eqnarray*}
-We can implement the first qubit by the spin of a particle and the
-second qubit in path
-
- Then, their projection and non-additivity operators are 
-\begin{eqnarray*}
-\Pi\left(S_{00}\right) & = & \proj{0}\otimes\proj{0}\\
-\Pi\left(S_{0+}\right) & = & \proj{0}\otimes\proj{+}\\
-\Pi\left(S_{00}\wedge S_{0+}\right) & = & \mathbb{0}\otimes\mathbb{0}\\
-\Pi\left(S_{00}\vee S_{0+}\right) & = & \proj{0}\otimes\mathbb{1}\\
-\mathfrak{D}\left(S_{1},S_{2}\right) & = & \proj{0}\otimes\left(-\sigma_{x}-\sigma_{z}\right)
-\end{eqnarray*}
-We also consider the density matrix $\rho=a\proj{0}\otimes\proj{0}+\left(1-a\right)\proj{0}\otimes\proj{1}$
-for $a\in\left[0,1\right]$. According to the Born rule, their probabilities
-are
-\begin{eqnarray*}
-\Tr\left(\rho\Pi\left(S_{00}\right)\right) & = & a\\
-\Tr\left(\rho\Pi\left(S_{0+}\right)\right) & = & \frac{1}{2}\left[a+\left(1-a\right)\right]=\frac{1}{2}\\
-\Tr\left(\rho\Pi\left(S_{00}\wedge S_{0+}\right)\right) & = & 0\\
-\Tr\left(\rho\Pi\left(S_{00}\vee S_{0+}\right)\right) & = & a+\left(1-a\right)=1
-\end{eqnarray*}
-and the non-additivity quantity~$\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\frac{1}{2}\left[-a+\left(1-a\right)\right]=\frac{1}{2}-a$.
-However, I still don't have much intuition on why the probabilities
-should have what kind of relations?\qed\end{example}
-
-However, his section VI is confusing. For example, the second sentence
-in section IV: 
-\begin{itemize}
-\item If $\mathfrak{d}\left(H_{1},H_{2}\middle|\rho\right)\ge0$, then $p\left(H_{1}\middle|\rho\right)$
-and $p\left(H_{2}\middle|\rho\right)$ are lower probabilities. Also,
-according to Eq. (22), in this case $\mathfrak{d}\left(H_{1}^{\perp},H_{2}^{\perp}\middle|\rho\right)\le0$,
-and therefore the $p\left(H_{1}^{\perp}\middle|\rho\right)$ and $p\left(H_{2}^{\perp}\middle|\rho\right)$
-are upper probabilities. 
-\end{itemize}
-I assume Vourdas means that $p\left(H_{1}\middle|\rho\right)$ and
-$p\left(H_{1}^{\perp}\middle|\rho\right)$ are the lower and upper
-probability respectively for measuring subspace~$H_{1}$ on the system~$\rho$.
-Consider the simplest example the subspace $H_{1}$ is the zero space
-$\mathcal{O}$ which commutes with every other subspaces, so $\mathfrak{d}\left(\mathcal{O},H_{2}\middle|\rho\right)=0$.
-Then, for measuring $\mathcal{O}$ on $\rho$, the lower and upper
-probabilities are $p\left(\mathcal{O}\middle|\rho\right)=0$ and $p\left(\mathcal{O}^{\perp}\middle|\rho\right)=p\left(\mathcal{I}\middle|\rho\right)=1$,
-respectively. The lower probability is $0$ makes sense, but I don't
-understand why the upper probability is $1$. Because both the lower
-and upper probabilities of the empty set are $0$ in classical Dempster-Shafer
-theory.}
-
 \amr{

### 2016-06-12 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities} Starting...
prob.tex \subsection{Measuring Quantum Probabilities} Updates....

@@
 \subsection{Measuring Quantum Probabilities}
+
+If we adopt the frequency interpretation as in section~\ref{subsec:Measuring-Probabilities:-Buffon},
+and measure the angular momentum for a spin-one particle in the Stern-Gerlach
+experiment~\cite{FeynmanLeightonSands1965,Stern1988,peres1995quantum,544199}.
+Ideally, if the local field strength directs to the $z$-axis, and
+all particles have the same velocity, three spots will be produced
+corresponding to $\ket{+Z}$, $\ket{0Z}$, and $\ket{-Z}$ predicted
+by the semi-classical model assuming particles have definite trajectories.
+In reality, all particles can from a hot oven cannot have the same
+velocity, as the result, spots will be broader and more washed out
+so that sometimes it may hard to decide a particle corresponding to
+which state.
+
 \amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}

### 2016-06-13 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities} updates...

--- 2016-06-11 prob.tex
@@
 \subsection{Measuring Quantum Probabilities}
+
+If we adopt the frequency interpretation as in section~\ref{subsec:Measuring-Probabilities:-Buffon},
+and measure the angular momentum for a spin-one particle in the Stern-Gerlach
+experiment~\cite{FeynmanLeightonSands1965,Stern1988,peres1995quantum,544199}.
+Ideally, if the local field strength directs to the $z$-axis, and
+all particles have the same velocity, three spots will be produced
+corresponding to $\ket{+Z}$, $\ket{0Z}$, and $\ket{-Z}$. In reality,
+the local field strength cannot prefect directs to to the $z$-axis,
+and all particles come from a hot oven cannot have the same velocity.
+As the result, spots will be broader and more washed out so that it
+may sometimes hard to decide a particle corresponding to which state\footnote{\yutsung{Citation here?}}.
+Similar to Buffon's needles, this kind of fuzziness can be taken into
+account by associating each quantum event with an interval-valued
+probability~$\left[l,r\right]$. About the imperfect direction of
+field strength, we might take it into account when we introduce the
+discrete quantum theory later.
+
 \amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}

### 2016-06-13 prob.tex
"Referenece\S. Bartlett, T. Rudolph, R. Spekkens, Reference frames, superselection rules, and quantum information.pdf" Added...

--- 2016-06-11 prob.tex
@@
 \subsection{Measuring Quantum Probabilities}
+
+Similar to the classical case, to know the quantum probability for
+each event, we can apply the law of large number, and measure the
+relative frequency. For example, Stern and Gerlach found a silver
+atoms beam deflected in a highly inhomogeneous magnetic field~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
+Ideally, if the local field strength directs to the $z$-axis, and
+all particles have the same velocity, three spots will be produced
+corresponding to $\ket{0}$ and $\ket{1}$. In reality, the local
+field strength cannot prefect directs to to the $z$-axis, and all
+atoms come from a hot oven cannot have the same velocity. The variant
+of velocity makes spots broader and more washed out so that it may
+sometimes hard to decide a particle corresponding to which state\footnote{\yutsung{Citation here?}}.
+Similar to Buffon's needles, this kind of fuzziness can be taken into
+account by associating each quantum event with an interval-valued
+probability~$\left[l,r\right]$. About the imperfect direction of
+field strength, we might take it into account when we introduce the
+discrete quantum theory later.
+
 \amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}

### 2016-06-13 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities} Updates...

@@
 all particles have the same velocity, three spots will be produced
-corresponding to $\ket{0}$ and $\ket{1}$. In reality, the local
-field strength cannot prefect directs to to the $z$-axis, and all
-atoms come from a hot oven cannot have the same velocity. The variant
-of velocity makes spots broader and more washed out so that it may
-sometimes hard to decide a particle corresponding to which state\footnote{\yutsung{Citation here?}}.
+corresponding to $\ket{0}$ and $\ket{1}$. In reality, we need a
+lot of resource to keep the local field of strength directing to the
+$z$-axis, to keep the atoms having similar velocity, and to point
+out the position each particle landed on.
+
+If the field of strength does not perfectly direct to the $z$-axis,
+we does not really test the quantum event we want to test, and we
+will go back to this problem when we introduce the discrete quantum
+theory later. Even if the field of strength is perfectly direct to
+the $z$-axis, the variant of velocity makes spots broader and more
+washed out. Together with the precision limit of the detector, it
+may sometimes hard to decide a particle corresponding to which state.
+For higher spins, this bounded resource even limits the ability of
+entangled systems to exhibit the violation of Bell's inequalities~\cite{CostaHarriganRudolphEtAl2009}.
 Similar to Buffon's needles, this kind of fuzziness can be taken into
 account by associating each quantum event with an interval-valued
-probability~$\left[l,r\right]$. About the imperfect direction of
-field strength, we might take it into account when we introduce the
-discrete quantum theory later.
+probability~$\left[l,r\right]$.
 

### 2016-06-14 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} updates...

--- 2016-06-13 prob.tex
@@
 
-If we adopt the frequency interpretation as in section~\ref{subsec:Measuring-Probabilities:-Buffon},
-and measure the angular momentum for a spin-one particle in the Stern-Gerlach
-experiment~\cite{FeynmanLeightonSands1965,Stern1988,peres1995quantum,544199}.
+Similar to the classical case, by applying the law of large number,
+quantum probabilities can be estimated by relative frequencies as
+well.. For example, Stern and Gerlach found a beam of silver atoms
+deflects in a highly inhomogeneous magnetic field~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
 Ideally, if the local field strength directs to the $z$-axis, and
-all particles have the same velocity, three spots will be produced
-corresponding to $\ket{+Z}$, $\ket{0Z}$, and $\ket{-Z}$. In reality,
-the local field strength cannot prefect directs to to the $z$-axis,
-and all particles come from a hot oven cannot have the same velocity.
-As the result, spots will be broader and more washed out so that it
-may sometimes hard to decide a particle corresponding to which state\footnote{\yutsung{Citation here?}}.
+all particles have the same velocity, two spots will be produced corresponding
+to $\ket{0}$ and $\ket{1}$. In reality, we need a lot of resource
+to keep the local field of strength directing to the $z$-axis, to
+keep the atoms having almost the same velocity, and to point out the
+exact position each particle landed on.
+
+If the field of strength does not perfectly direct to the $z$-axis,
+we does not really test the quantum event we want to test. This problem
+will be handled later when we introduce the discrete quantum theory.
+Even if the field of strength is perfectly direct to the $z$-axis,
+the variant velocity makes spots broader and more washed out. Together
+with the precision limit of the detector, it may sometimes be hard
+to decide a particle corresponding to which state. For higher spins,
+the bounded resource even limits the ability of entangled systems
+to exhibit the violation of Bell's inequalities~\cite{CostaHarriganRudolphEtAl2009}.
 Similar to Buffon's needles, this kind of fuzziness can be taken into
 account by associating each quantum event with an interval-valued
-probability~$\left[l,r\right]$. About the imperfect direction of
-field strength, we might take it into account when we introduce the
-discrete quantum theory later.
+probability~$\left[l,r\right]$.
 
@@
 %%%%%
+
 \subsection{Quantum Interval-valued Probabilities Measures}
 
-\amr{
-The idea will be the following. First describe quantum probability
+As mentioned above, each quantum event~$P$ will be associated with
+an interval-valued probability~$\left[l,r\right]$. Notice that whenever
+the magnetic field of the Stern-Gerlach is fixed, i.e., an complete
+set of orthogonal projections are picked, measuring the spin is up
+or down is exactly the same as tossing a coin. In another word, if
+somebody claimed she is tossing a coin behind a veil, and only show
+the resulting heads or tails, we cannot distinguish whether she has
+really tossed a coin, or she has run an Stern-Gerlach experiment,
+and show us the head, the tail, or the side of coin if the silver
+atoms is spin up, spin down, or just hit the middle. Therefore, applying
+interval
+
+\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
+Given a Hilbert space $\Hilb$ with the set of quantum events~$\events$,
+a \emph{quantum interval-valued probability measure} is a function
+$\mu:\events\rightarrow[0,1]$ such that:
+\begin{itemize}
+\item $\mu(\mathbb{0})=\left[0,0\right]$, 
+\item $\mu(\mathbb{1})=\left[1,1\right]$, 
+\item $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\mu\left(P\right)$,
+and 
+\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\mu\left(P_{i}\right)$. 
+\end{itemize}
+\qed\end{definition}
+
+\amr{ The idea will be the following. First describe quantum probability
 spaces conventionally. Then talk about the following: 
 \begin{itemize}
-\item the dimension of the Hilbert space is a parameter that is like
-  the number of needles; it gives an upper bound on the accuracy of
-  the numbers that are relevant in expressing probabilities
-\item the intervals will come from two things: the fact that states
-  can only be prepared to a certain accuracy so when we say the state
-  is $\ket{\psi}$ we really mean a neighborhood of states close to $\ket{\psi}$
-\item similarly when we do an experiment with $\proj{\phi}$ we are
-  really testing a family of projections that are near $\proj{\phi}$;
-  this fuziness will cause the probability to only be specifiable as intervals
+\item the dimension of the Hilbert space is a parameter that is like the
+number of needles; it gives an upper bound on the accuracy of the
+numbers that are relevant in expressing probabilities 
+\item the intervals will come from two things: the fact that states can
+only be prepared to a certain accuracy so when we say the state is
+$\ket{\psi}$ we really mean a neighborhood of states close to $\ket{\psi}$ 
+\item similarly when we do an experiment with $\proj{\phi}$ we are really
+testing a family of projections that are near $\proj{\phi}$; this
+fuziness will cause the probability to only be specifiable as intervals 
 \end{itemize}

### 2016-06-14 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} Add a comment about continuity...

@@
 
+\yutsung{About continuity, one of the confusion comes from the subtle
+correspondence between the measurement processes and observables.
+Consider the following observables and their measurement processes:
+\begin{itemize}
+\item The observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$. Except
+$x=1$, the measurement process for $\mathbf{O}_{x}$ is ${\cal O}_{x}$:
+\begin{enumerate}
+\item With probability~$\mu_{\phi}\left(\proj{1}\right)$, return the measurement
+result~$1$ with the post-measurement state~$\ket{1}$;
+\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
+result~$0$ with the post-measurement state~$\ket{0}$;
+\item With probability~$\mu_{\phi}\left(\proj{-1}\right)$, return the
+measurement result~$x$ with the post-measurement state~$\ket{-1}$.
+\end{enumerate}
+\item The observable operator~$\mathbf{J}_{z}^{2}=\proj{1}+\proj{-1}$,
+and its measurement process~${\cal J}_{z}^{2}$:
+\begin{enumerate}
+\item With probability~$\mu_{\phi}\left(\proj{1}+\proj{-1}\right)$, return
+the measurement result~$1$ with the post-measurement state~$\ket{1}\ip{1}{\phi}+\ket{-1}\ip{-1}{\phi}$;
+\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
+result~$0$ with the post-measurement state~$\ket{0}$.
+\end{enumerate}
+\end{itemize}
+As an operator, it is clear that $\lim_{x\rightarrow1}\mathbf{O}_{x}=\mathbf{J}_{z}^{2}$,
+and we should have $\lim_{x\rightarrow1}{\cal O}_{x}={\cal O}_{1}$
+for the measurement process. However, it is not obvious why ${\cal O}_{1}={\cal J}_{z}^{2}$.
+Although they have the same probability for the measurement results,
+but their post-measurement states are different. This might be a defect
+of representing a measurement process as an observable. As $\mathbf{O}_{1}=\mathbf{J}_{z}^{2}$,
+there is no observable corresponding to the measurement process~${\cal O}_{1}$.}
+
 \amr{the rest needs cleaning up and perhaps does not even belong in

### 2016-06-15 prob.tex
prob.tex \begin{definition}[Ideal Measurement; Complement; Commutativity; Complete Set~\cite{Swart2013,peres1995quantum,Griffiths2003}]~ Updates...

@@
 
-\begin{definition}[Complement; Commutativity~\cite{peres1995quantum,Griffiths2003}]~
+\begin{definition}[Ideal Measurement; Complement; Commutativity;
+Complete Set~\cite{Swart2013,peres1995quantum,Griffiths2003}]~ 
 \begin{itemize}
+\item A set of mutually orthogonal projections $P_{i}$ is called an ideal
+measurement if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$. 
 \item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
@@
 an interval-valued probability~$\left[l,r\right]$. Notice that whenever
-the magnetic field of the Stern-Gerlach is fixed, i.e., an complete
-set of orthogonal projections are picked, measuring the spin is up
-or down is exactly the same as tossing a coin. In another word, if
-somebody claimed she is tossing a coin behind a veil, and only show
-the resulting heads or tails, we cannot distinguish whether she has
-really tossed a coin, or she has run an Stern-Gerlach experiment,
-and show us the head, the tail, or the side of coin if the silver
-atoms is spin up, spin down, or just hit the middle. Therefore, applying
-interval
+the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal measurement
+is picked, measuring the spin is up or down is exactly the same as
+tossing a coin. In another word, if somebody claimed she is tossing
+a coin behind a veil, and only show the resulting heads or tails,
+we cannot distinguish whether she has really tossed a coin, or she
+has run an Stern-Gerlach experiment, and show us the head, the tail,
+or the side of coin if the silver atoms is spin up, spin down, or
+just hit the middle. Therefore, applying interval-valued
 

### 2016-06-15 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities} updates...

@@
 Similar to the classical case, by applying the law of large number,
-quantum probabilities can be estimated by relative frequencies as
-well.. For example, Stern and Gerlach found a beam of silver atoms
-deflects in a highly inhomogeneous magnetic field~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
-Ideally, if the local field strength directs to the $z$-axis, and
-all particles have the same velocity, two spots will be produced corresponding
-to $\ket{0}$ and $\ket{1}$. In reality, we need a lot of resource
-to keep the local field of strength directing to the $z$-axis, to
-keep the atoms having almost the same velocity, and to point out the
-exact position each particle landed on.
+quantum probabilities can be estimated by relative frequencies. For
+example, if we want to know the probability of the spin up in the
+Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003},
+we can put a beam of silver atoms in a highly inhomogeneous magnetic
+field, and counting the number of atoms deflects up. Ideally, if the
+local field strength directs to the $z$-axis, and all particles have
+the same velocity, the Stern-Gerlach experiment only produces two
+spots corresponding to $\ket{0}$ and $\ket{1}$. In reality, we need
+a lot of resource to keep the local field of strength directing to
+the $z$-axis, to keep the atoms having almost the same velocity,
+and to point out the exact position each particle landed on.
 
@@
 with the precision limit of the detector, it may sometimes be hard
-to decide a particle corresponding to which state. For higher spins,
-the bounded resource even limits the ability of entangled systems
-to exhibit the violation of Bell's inequalities~\cite{CostaHarriganRudolphEtAl2009}.
+to decide a particle corresponding to which state. For the Stern-Gerlach
+experiment on higher spins, the bounded resource even limits the ability
+of entangled systems to exhibit the violation of Bell's inequalities~\cite{CostaHarriganRudolphEtAl2009}.
 Similar to Buffon's needles, this kind of fuzziness can be taken into

### 2016-06-16 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities} updates...

@@
 with the precision limit of the detector, it may sometimes be hard
-to decide a particle corresponding to which state. For the Stern-Gerlach
-experiment on higher spins, the bounded resource even limits the ability
-of entangled systems to exhibit the violation of Bell's inequalities~\cite{CostaHarriganRudolphEtAl2009}.
-Similar to Buffon's needles, this kind of fuzziness can be taken into
-account by associating each quantum event with an interval-valued
+to decide a particle corresponding to which state\footnote{\yutsung{Add citations to support the idea... Haven't find suitable
+ones...}}. Similar to Buffon's needles, this kind of fuzziness can be taken
+into account by associating each quantum event with an interval-valued
 probability~$\left[l,r\right]$.

### 2016-06-16 prob.tex
prob.tex modifying texts...

@@
 with the precision limit of the detector, it may sometimes be hard
-to decide a particle corresponding to which state\footnote{\yutsung{Add citations to support the idea... Haven't find suitable
+to decide a particle corresponding to which state\footnote{\yutsung{Add citations to support the idea... Haven't found suitable
 ones...}}. Similar to Buffon's needles, this kind of fuzziness can be taken
@@
 the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal measurement
-is picked, measuring the spin is up or down is exactly the same as
-tossing a coin. In another word, if somebody claimed she is tossing
-a coin behind a veil, and only show the resulting heads or tails,
-we cannot distinguish whether she has really tossed a coin, or she
-has run an Stern-Gerlach experiment, and show us the head, the tail,
-or the side of coin if the silver atoms is spin up, spin down, or
-just hit the middle. Therefore, applying interval-valued
+is picked, measuring the spin is exactly the same as tossing a coin.
+In another word, if somebody claimed she is tossing a coin behind
+a veil, and only show the resulting heads or tails, we cannot distinguish
+whether she has really tossed a coin, or she has run an Stern-Gerlach
+experiment, and show us the head, the tail, or the side of coin if
+the silver atoms is spin up, spin down, or just hit the middle, respectively.
+Therefore, we should plug in the definition of interval-valued probability
+measure into the definition of quantum probability space for each
+ideal measurement, and get the following definition.
 
@@
 \begin{itemize}
-\item The observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$. Except
-$x=1$, the measurement process for $\mathbf{O}_{x}$ is ${\cal O}_{x}$:
+\item For any $x\in\R$, consider the observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$.
+Except $x=1$, given the system in the state~$\ket{\phi}$, we can
+denote the measurement process for $\mathbf{O}_{x}$ by ${\cal O}_{x}$:
 \begin{enumerate}

### 2016-06-17 prob.tex
"Referenece\M. Born, On the Quantum Mechanics of Collisions.pdf" Added...
Change a little bit...

@@
   the uncountable and uncomputable interval $[0,1]$, we will consider
-  finite set-valued probability measures~\cite{Artstein1972,PuriRalescu1983}.
+  finite set-valued probability measures~\cite{PuriRalescu1983}.
 \end{itemize}
@@
 \begin{itemize}
-\item A set of mutually orthogonal projections $P_{i}$ is called an ideal
-measurement if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$. 
+\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
+measurement} if it is a partition of the identity, i.e.,
+$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
 \item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
@@
 \begin{itemize}
-\item For any $x\in\R$, consider the observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$.
+\item For any $x\in\mathbb{R}$, consider the observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$.
 Except $x=1$, given the system in the state~$\ket{\phi}$, we can

### 2016-06-18 prob.tex
prob.tex \section{Quantum Probability Spaces} Add a lemma...

@@
 \newtheorem{cor}{Corollary}
+\newtheorem{lemma}{Lemma}
 \newcommand{\events}{\ensuremath{\mathcal{E}}}
@@
 \qed\end{definition}
+
+In order to motivate the definition of quantum interval-valued probability
+measures later, here is an equivalent definition of quantum probability
+measures.
+
+\begin{lemma}Given a Hilbert space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$
+is a probability measure if and only if $\mu$ satisfies the following
+conditions:
+\begin{itemize}
+\item $\mu(\mathbb{0})=0$, 
+\item $\mu(\mathbb{1})=1$, 
+\item $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$,
+and 
+\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$. 
+\end{itemize}
+\qed\end{lemma}
+
 % \yutsung{The definition of independence is different from different
@@
 If we want to prepare $\ket{\phi}$, we may turn out preparing a set
-of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$, then
+of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$. Then,
 the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
@@
 
-\subsection{Quantum Interval-valued Probabilities Measures}
+\subsection{Quantum Interval-valued Probability Measures}
 
@@
 
-\begin{example}{[}Quantum probability measure{]} Like in the classical
+\begin{example}[Quantum probability measure] Like in the classical
 case, there are $2^{8}$ events. But as Mermin explains in a simple

### 2016-06-18 prob.tex
prob.tex \section{Quantum Probability Spaces} updates...

@@
 In order to motivate the definition of quantum interval-valued probability
-measures later, here is an equivalent definition of quantum probability
+measures later, we provide an equivalent definition of quantum probability
 measures.
 
-\begin{lemma}Given a Hilbert space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$
-is a probability measure if and only if $\mu$ satisfies the following
-conditions:
+\begin{lemma}\label{lem:quantumProbabilityMeasure}Given a Hilbert
+space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$ is a probability
+measure if and only if $\mu$ satisfies the following conditions:
 \begin{itemize}
@@
 a postulate of quantum mechanics, states that each pure quantum state
-$\ket{\phi}$ induces a probability measure $\mu_{\phi}$ as follows:
+$\ket{\phi}$ induces a probability measure $\tilde{\mu}_{\phi}$
+as follows: 
 \[
-\mu_{\phi}(E)=\ip{\phi}{E\phi}
+\tilde{\mu}_{\phi}(E)=\ip{\phi}{E\phi}
 \]
@@
 where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
-measure introduced by $\rho$ is the combination of $\mu_{\phi_{j}}$
+measure introduced by $\rho$ is the combination of $\tilde{\mu}_{\phi_{j}}$
 with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
 \begin{eqnarray}
-\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
 \end{eqnarray}
 
-Conversely, Gleason's theorem states that given a probability measure
-$\mu$, there exist a mixed state~$\rho$ that induces such a measure
-using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-The theorem is only valid in Hilbert spaces with dimension $d\geq3$.
-It is instructive to study counterexamples in $d=2$, i.e., the case
-of a one-qubit system.
-
-\begin{example}[One-qubit quantum probability measure] Consider
+Conversely, in Hilbert spaces of dimension $d\geq3$, Gleason's theorem
+states that given a probability measure $\mu$, there exist a mixed
+state~$\rho$ that induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
+to the following corollary.
+
+\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$,
+for any function~$\mu:\events\rightarrow[0,1]$ satisfies the conditions
+listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist
+an unique mixed state~$\rho$ such that $\mu=\tilde{\mu}_{\rho}$.\end{cor}
+
+It is instructive to study counterexamples when $d=2$, i.e., the
+case of a one-qubit system.
+
+\begin{example}{[}One-qubit quantum probability measure{]} Consider
 a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
@@
 On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
-the same as a probability measure~$\mu_{\ket{0}}$, we only need
-to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$: 
+the same as a probability measure~$\tilde{\mu}_{\ket{0}}$, we only
+need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
 \[
@@
 \]
-However, $\mu_{\rho}(E)=1$ if and only if $\rho$ represents a pure
-state and $\rho=E$. \qed\end{example}
+However, $\tilde{\mu}_{\rho}(E)=1$ if and only if $\rho$ represents
+a pure state and $\rho=E$. \qed\end{example}
 
@@
 \qed\end{definition}
+
+Notice that if the last condition is replaced by equal sign, these
+conditions will be exactly the same as the conditions in lemma~\ref{lem:quantumProbabilityMeasure}
+which is equivalent to the Born rule as in corollary~\ref{cor:Gleason's}.
+Therefore, it is reasonable to believe these conditions should be
+equivalent to a interval-valued Born rule.
 

### 2016-06-18 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} First example...

@@
 
-\begin{example}{[}One-qubit quantum probability measure{]} Consider
+\begin{example}[One-qubit quantum probability measure] Consider
 a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
@@
 Given a Hilbert space $\Hilb$ with the set of quantum events~$\events$,
-a \emph{quantum interval-valued probability measure} is a function
-$\mu:\events\rightarrow[0,1]$ such that:
+and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
+probability measure} is a function~$\mu:\events\rightarrow\mathscr{I}$
+such that: 
 \begin{itemize}
@@
 equivalent to a interval-valued Born rule.
+
+When we pick $\mathscr{I}=\left\{ \left[x,x\right]\middle|x\in\left[0,1\right]\right\} $,
+for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
+we can define a corresponding quantum \emph{$\mathscr{I}$}-interval-valued
+probability measure~$\mu':\events\rightarrow\mathscr{I}$ by $\mu'\left(E\right)=\left[\mu\left(E\right),\mu\left(E\right)\right]$.
+In this sense, every usual quantum probability measure can be considered
+as a quantum interval-valued probability measure. There are more interesting
+examples as we now show.
 

### 2016-06-19 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} Add an exmaple...

@@
 
-Notice that if the last condition is replaced by equal sign, these
+Notice that if the last condition is replaced by the equal sign, these
 conditions will be exactly the same as the conditions in lemma~\ref{lem:quantumProbabilityMeasure}
@@
 examples as we now show.
+
+\begin{example}[Totally ignorant quantum interval-valued probability
+measure] For any Hilbert space and intervals\emph{~$\mathscr{I}=\left\{ \left[0,0\right],\left[0,1\right],\left[1,1\right]\right\} $},
+consider $\mu:\events\rightarrow\mathscr{I}$ defined as follow: 
+\[
+\mu(E)=\begin{cases}
+\left[1,1\right] & \textrm{, if }E=\mathbb{1}\textrm{ ;}\\
+\left[0,0\right] & \textrm{, if }E=\mathbb{0}\textrm{ ;}\\
+\left[0,1\right] & \textrm{, otherwise.}
+\end{cases}
+\]
+It is easy to verify $\mu$ is a quantum \emph{$\mathscr{I}$}-interval-valued
+probability measure.\qed\end{example}
 

### 2016-06-19 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} updates....

--- 2016-06-18 prob.tex
@@
 \newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
+\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
 
@@
 0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
-\mu_{\ket{0}}(E) & \textrm{, otherwise.}
+\tilde{\mu}_{\ket{0}}(E) & \textrm{, otherwise.}
 \end{cases}
@@
 examples as we now show.
+
+\begin{example}[Totally ignorant quantum interval-valued probability
+measure] We consider three intervals\emph{ }$\left[0,0\right]$,
+$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
+and $\left[1,1\right]$ are called \imposs and \necess as before,
+and \emph{$\left[0,1\right]$} is called \unknown because it provides
+no information. For any Hilbert space, consider $\mu:\events\rightarrow\mathscr{I}$
+defined as follow: 
+\[
+\mu(E)=\begin{cases}
+\necess & \textrm{, if }E=\mathbb{1}\textrm{ ;}\\
+\imposs & \textrm{, if }E=\mathbb{0}\textrm{ ;}\\
+\unknown & \textrm{, otherwise.}
+\end{cases}
+\]
+It is easy to verify $\mu$ is a quantum interval-valued probability
+measure.\qed\end{example}
 

### 2016-06-20 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} updates...

--- 2016-06-18 prob.tex
@@
 When we pick $\mathscr{I}=\left\{ \left[x,x\right]\middle|x\in\left[0,1\right]\right\} $,
-for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
+for any quantum probability measure~$\tensor*[_{\left[0,1\right]}]{\mu}{}:\events\rightarrow\left[0,1\right]$,
 we can define a corresponding quantum \emph{$\mathscr{I}$}-interval-valued
-probability measure~$\mu':\events\rightarrow\mathscr{I}$ by $\mu'\left(E\right)=\left[\mu\left(E\right),\mu\left(E\right)\right]$.
+probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
+by $\tensor*[_{\mathscr{I}}]{\mu}{}\left(E\right)=\left[\tensor*[_{\left[0,1\right]}]{\mu}{}\left(E\right),\tensor*[_{\left[0,1\right]}]{\mu}{}\left(E\right)\right]$.
 In this sense, every usual quantum probability measure can be considered
@@
 examples as we now show.
+
+\begin{example}[Quantum three-value interval-valued probability
+measure] We consider three intervals\emph{ }$\left[0,0\right]$,
+$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
+and $\left[1,1\right]$ are called \imposs~and \necess~as before,
+and \emph{$\left[0,1\right]$} is called \unknown~because it provides
+no information. For any Hilbert space and any quantum probability
+measure~$\tensor*[_{\left[0,1\right]}]{\mu}{}:\events\rightarrow\left[0,1\right]$,
+we can define a interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
+by 
+\[
+\tensor*[_{\mathscr{I}}]{\mu}{}(E)=\iota\left(\tensor*[_{\left[0,1\right]}]{\mu}{}(E)\right)\textrm{ ,}
+\]
+where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
+\[
+\iota(x)=\begin{cases}
+\necess & \textrm{, if }x=1\textrm{ ;}\\
+\imposs & \textrm{, if }x=0\textrm{ ;}\\
+\unknown & \textrm{, otherwise.}
+\end{cases}
+\]
+$\iota$ has two interested properties 
+\begin{eqnarray*}
+\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right) & = & 1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)\\
+\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right) & \subseteq & \sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)\textrm{ ,}
+\end{eqnarray*}
+where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
+By applying these two properties, it is easy to verify $\tensor*[_{\mathscr{I}}]{\mu}{}$
+is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}
 

### 2016-06-20 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} updates...

@@
 measure~$\tensor*[_{\left[0,1\right]}]{\mu}{}:\events\rightarrow\left[0,1\right]$,
-we can define a interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
+we can define a quantum interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
 by 
@@
 is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}
+
+Notice that in the above two examples, quantum interval-valued probability
+measures are all come from quantum probability measures because the
+numbers in $\left[0,1\right]$ can be mapped to the chosen intervals~$\mathscr{I}$
+naturally. This is not always the case. For example, if $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+there is no natural way to map from $\frac{1}{2}$, as both $\frac{1}{2}\in\left[0,\frac{1}{2}\right]=\unlikely$
+and $\frac{1}{2}\in\left[\frac{1}{2},1\right]=\likely$. However,
+we still can find a quantum interval-valued probability measure corresponding
+to a quantum probability measure as in the following example.
+
+Even if there is a natural map from quantum probability measures to
+quantum interval-valued probability measures, there are also some
+quantum interval-valued probability measures do not come from quantum
+probability measures.
 

### 2016-06-21 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} Add another example...

@@
 \usepackage{tensor}
+\newcommand{\rme}{\mathrm{e}}
+\newcommand{\rmi}{\mathrm{i}}
 
@@
 \]
-$\iota$ has two interested properties 
+$\iota$ has two interesting properties 
 \begin{eqnarray*}
@@
 to a quantum probability measure as in the following example.
+
+\begin{example}[One-qubit quantum interval-valued probability measure]
+Given a two dimensional Hilbert space, a vector $\ket{\psi}$ can
+be normalized and written in $\left(\begin{array}{c}
+\cos\theta\\
+\rme^{\rmi\gamma}\sin\theta
+\end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma\le2\pi$. Consider
+a quantum interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
+defined by 
+\begin{eqnarray*}
+\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
+\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{1}) & = & \necess\textrm{ ,}\\
+\tensor*[_{\mathscr{I}}]{\mu}{}(\proj{\psi}) & = & \begin{cases}
+\necess & \textrm{, if }\theta=0\textrm{ ;}\\
+\likely & \textrm{, if }0<\theta<\frac{\pi}{4}\textrm{ ;}\\
+\likely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }0\le\gamma<\pi\textrm{ ;}\\
+\unlikely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }\pi\le\gamma<2\pi\textrm{ ;}\\
+\unlikely & \textrm{, if }\frac{\pi}{4}<\theta<\frac{\pi}{2}\textrm{ ;}\\
+\imposs & \textrm{, if }\theta=\frac{\pi}{2}\textrm{ .}
+\end{cases}
+\end{eqnarray*}
+Let $\ket{\psi^{\perp}}$ be the state perpendicular to $\ket{\psi}$.
+Then, the vector representation of $\ket{\psi^{\perp}}$ can be simplified
+as 
+\[
+\left(\begin{array}{c}
+-\rme^{\rmi\gamma}\sin\theta\\
+\cos\theta
+\end{array}\right)=-\rme^{\rmi\gamma}\left(\begin{array}{c}
+\cos\left(\frac{\pi}{2}-\theta\right)\\
+\rme^{\rmi\left(\pi-\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)
+\end{array}\right)
+\]
+so we have
+\[
+\tensor*[_{\mathscr{I}}]{\mu}{}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi}\right)=\tensor*[_{\mathscr{I}}]{\mu}{}\left(\proj{\psi^{\perp}}\right)=1\tensor*[_{\mathscr{I}}]{-}{}\tensor*[_{\mathscr{I}}]{\mu}{}\left(\proj{\psi}\right)\textrm{ .}
+\]
+Hence, $\tensor*[_{\mathscr{I}}]{\mu}{}$ is a quantum $\mathscr{I}$-interval-valued
+probability measure. Notice that for all projection~$E$, $\tensor*[_{\left[0,1\right]}]{\tilde{\mu}}{_{\ket{0}}}(E)\in\tensor*[_{\mathscr{I}}]{\mu}{}(E)$
+implies that $\tensor*[_{\mathscr{I}}]{\mu}{}(E)$ is one of quantum
+$\mathscr{I}$-interval-valued probability measures corresponding
+to $\tensor*[_{\left[0,1\right]}]{\tilde{\mu}}{_{\ket{0}}}(E)$. However,
+$\tensor*[_{\left[0,1\right]}]{\tilde{\mu}}{_{\ket{0}}}(E)$ can correspond
+to infinity many quantum $\mathscr{I}$-interval-valued probability
+measures by twisting the definition involving $\gamma$.\qed\end{example}
 

### 2016-06-22 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} Start the third example...
prob.tex \subsection{Quantum Interval-valued Probability Measures} example updates...
prob.tex \subsection{Quantum Interval-valued Probability Measures} Add another example, but not what I really need...

@@
 
-Even if there is a natural map from quantum probability measures to
-quantum interval-valued probability measures, there are also some
-quantum interval-valued probability measures do not come from quantum
-probability measures.
-
-\amr{ The idea will be the following. First describe quantum probability
-spaces conventionally. Then talk about the following: 
-\begin{itemize}
-\item the dimension of the Hilbert space is a parameter that is like the
-number of needles; it gives an upper bound on the accuracy of the
-numbers that are relevant in expressing probabilities 
-\item the intervals will come from two things: the fact that states can
-only be prepared to a certain accuracy so when we say the state is
-$\ket{\psi}$ we really mean a neighborhood of states close to $\ket{\psi}$ 
-\item similarly when we do an experiment with $\proj{\phi}$ we are really
-testing a family of projections that are near $\proj{\phi}$; this
-fuziness will cause the probability to only be specifiable as intervals 
-\end{itemize}
-}
+We have enough examples for quantum interval-valued probability measure,
+it is instructive to understand the conditions by studying a measure
+which is not a quantum interval-valued probability measure.
+
+\begin{example}[Not three-dimensional quantum interval-valued probability
+measure] Given a three dimensional Hilbert space with an orthonormal
+basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
+$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
+as before. Let
+\begin{eqnarray*}
+\mu(\mathbb{0}) & = & \imposs\textrm{ ,}\\
+\mu(\mathbb{1}) & = & \necess\textrm{ ,}\\
+\mu(\proj{0}) & = & \necess\textrm{ ,}\\
+\mu(\proj{\ps}) & = & \necess\textrm{ ,}\\
+\mu(\proj{\psi}) & = & \imposs\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
+\mu(1-\proj{0}) & = & \imposs\textrm{ ,}\\
+\mu(1-\proj{\ps}) & = & \imposs\textrm{ ,}\\
+\mu(1-\proj{\psi}) & = & \necess\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
+\mu(P) & = & \unknown\textrm{, otherwise. }
+\end{eqnarray*}
+$\mu$ is not a quantum interval-valued probability measure. To verify
+this fact, we first consider an orthonormal basis
+\begin{eqnarray*}
+\ket{\psi_{0}} & = & \frac{1}{\sqrt{2}}\ket{1}+\frac{1}{\sqrt{2}}\ket{2}\\
+\ket{\psi_{1}} & = & \frac{1}{\sqrt{3}}\ket{0}-\frac{1}{\sqrt{3}}\ket{1}+\frac{1}{\sqrt{3}}\ket{2}\\
+\ket{\psi_{2}} & = & \sqrt{\frac{2}{3}}\ket{0}+\frac{1}{\sqrt{6}}\ket{1}-\frac{1}{\sqrt{6}}\ket{2}
+\end{eqnarray*}
+However,
+
+\begin{eqnarray*}
+ &  & \mu\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)=\mu\left(1-\proj{\psi_{2}}\right)=\unknown\\
+ & \nsubseteq & \imposs+\imposs=\mu\left(\proj{\psi_{1}}\right)+\mu\left(\proj{\psi_{2}}\right)\textrm{ .}
+\end{eqnarray*}
+\qed\end{example}
+
+\yutsung{For \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
+are there any quantum interval-valued probability measures do not
+come from quantum probability measures?}
 

### 2016-06-23 prob.tex
prob.tex review and small notation and variable scoping...

@@
 \item $\pmeas(\Omega)=[1,1]$, 
-\item $\pmeas\left(\Omega\backslash E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\pmeas\left(E\right)$,
-  and 
+\item for any event $E$, $\pmeas\left(\Omega\backslash
+E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\pmeas\left(E\right)$, and 
 \item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\pmeas\left(E_{i}\right)$,
@@
   consists of a set of events $\events$ and a probability measure
-  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
-    possible to define a more general space of events consisting of
+  $\tensor*[_{[0,1]}]{\mu}{} : \events \rightarrow [0,1]$ such
+  that:\footnote {It is possible to define a more general space of events consisting of
     all operators~$\mathcal{A}$ on $\Hilb$ and consider
@@
 \begin{itemize}
-\item $\mu(\mathbb{1})=1$, and 
+\item $\tensor*[_{[0,1]}]{\mu}{}(\mathbb{1})=1$, and 
 \item for mutually orthogonal projections $P_{i}$, we have 
-$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
+$\tensor*[_{[0,1]}]{\mu}{}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\tensor*[_{[0,1]}]{\mu}{}\left(P_{i}\right)$.
 \end{itemize}
+Notice that the preposing $[0,1]$ indicates the range of
+$\tensor*[_{[0,1]}]{\mu}{}$. We will only prepose the range of a
+probability measure whenever we need to compare the ranges of different
+probability measures later. 
 \qed\end{definition}
@@
 
-\begin{definition}[Ideal Measurement; Complement; Commutativity;
-Complete Set~\cite{Swart2013,peres1995quantum,Griffiths2003}]~ 
+\begin{definition}[Ideal Measurement; Complement;
+Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
 \begin{itemize}
@@
 \item $\mu(\mathbb{1})=1$, 
-\item $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$,
-and 
-\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$. 
+\item for any projection $P$,
+$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, and 
+\item for a set of mutually orthogonal projections $P_{i}$, we have
+$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
 \end{itemize}
@@
 and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
-probability measure} is a function~$\mu:\events\rightarrow\mathscr{I}$
+probability measure} is a function~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
 such that: 
 \begin{itemize}
-\item $\mu(\mathbb{0})=\left[0,0\right]$, 
-\item $\mu(\mathbb{1})=\left[1,1\right]$, 
-\item $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\mu\left(P\right)$,
-and 
-\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\mu\left(P_{i}\right)$. 
+\item $\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{0})=\left[0,0\right]$, 
+\item $\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{1})=\left[1,1\right]$, 
+\item for any projection $P$,
+$\tensor*[_{\mathscr{I}}]{\mu}{}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\tensor*[_{\mathscr{I}}]{\mu}{}\left(P\right)$, and
+\item for a set of mutually orthogonal projections $P_{i}$, we have
+$\tensor*[_{\mathscr{I}}]{\mu}{}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\tensor*[_{\mathscr{I}}]{\mu}{}\left(P_{i}\right)$.
 \end{itemize}
+As before, we will only define a quantum interval-valued probability measure
+with preposing $\mathscr{I}$ when we want to compare a quantum probability
+measure and a quantum interval-valued probability measure.
 \qed\end{definition}

### 2016-06-23 prob.tex
prob.tex Before meeting...

@@
 probability measure whenever we need to compare the ranges of different
-probability measures later. 
+probability measures. 
 \qed\end{definition}
@@
 \begin{lemma}\label{lem:quantumProbabilityMeasure}Given a Hilbert
-space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$ is a probability
+space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$ is a quantum probability
 measure if and only if $\mu$ satisfies the following conditions:
@@
 \begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$,
-for any function~$\mu:\events\rightarrow[0,1]$ satisfies the conditions
+for any function~$\mu:\events\rightarrow[0,1]$ satisfying the conditions
 listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist
@@
 \]
-On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
-the same as a probability measure~$\tilde{\mu}_{\ket{0}}$, we only
+On one hand, $\mu$ is a quantum probability measure. Because $\mu$ is almost
+the same as a quantum probability measure~$\tilde{\mu}_{\ket{0}}$, we only
 need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
@@
 a lot of resource to keep the local field of strength directing to
-the $z$-axis, to keep the atoms having almost the same velocity,
+the $z$-axis precisely, to keep the atoms having almost the same velocity,
 and to point out the exact position each particle landed on.

### 2016-06-24 prob.tex
prob.tex Global replace the notation for quantum probability measure...

@@
 $\mathscr{I}$--interval-valued probability measure is a function
-$\pmeas : \events \rightarrow \mathscr{I}$ such
+$\bar{\mu} : \events \rightarrow \mathscr{I}$ such
 that~\cite{JamisonLodwick2004}:\footnote{Notice that the belief function defined by Dempster~\cite{Dempster1967}
@@
 \begin{itemize}
-\item $\pmeas(\emptyset)=[0,0]$, 
-\item $\pmeas(\Omega)=[1,1]$, 
-\item for any event $E$, $\pmeas\left(\Omega\backslash
-E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\pmeas\left(E\right)$, and 
-\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\pmeas\left(E_{i}\right)$,
+\item $\bar{\mu}(\emptyset)=[0,0]$, 
+\item $\bar{\mu}(\Omega)=[1,1]$, 
+\item for any event $E$, $\bar{\mu}\left(\Omega\backslash
+E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$, and 
+\item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)$,
 where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
@@
 % must therefore have probability $\left[1-b,1-a\right]$ which we
-% abbreviate $1-\left[a,b\right]$, so the probability measure $\pmeas$
+% abbreviate $1-\left[a,b\right]$, so the probability measure $\bar{\mu}$
 % should satisfy:
 % \begin{itemize}
-% \item $\pmeas(\emptyset)=[0,0]$, 
-% \item $\pmeas(\Omega)=[1,1]$, and 
-% \item $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
+% \item $\bar{\mu}(\emptyset)=[0,0]$, 
+% \item $\bar{\mu}(\Omega)=[1,1]$, and 
+% \item $\bar{\mu}\left(\Omega\backslash E\right)=1-\bar{\mu}\left(E\right)$
 % \end{itemize}
-% However, if we want $\pmeas(\Omega)=[1,1]$, and the probability assignment
-% for singleton sets $\pmeas(\{HH\})=\unlikely$, $\pmeas(\{HT\})=\imposs$,
-% $\pmeas(\{TH\})=\likely$, and $\pmeas(\{TT\})=\imposs$ as in example~\ref{Two-coin-set-valued-again},
-% we only have $\pmeas(\Omega)\subsetneq\pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})$.
+% However, if we want $\bar{\mu}(\Omega)=[1,1]$, and the probability assignment
+% for singleton sets $\bar{\mu}(\{HH\})=\unlikely$, $\bar{\mu}(\{HT\})=\imposs$,
+% $\bar{\mu}(\{TH\})=\likely$, and $\bar{\mu}(\{TT\})=\imposs$ as in example~\ref{Two-coin-set-valued-again},
+% we only have $\bar{\mu}(\Omega)\subsetneq\bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})$.
 % In general, we only require
 % \begin{itemize}
-% \item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
+% \item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\bar{\mu}\left(E_{i}\right)$. 
 % \end{itemize}
@@
 % but some evidence may only be acquired for $\bigcup_{i}E_{i}$ as
-% the whole. Therefore, $\pmeas\left(\bigcup_{i}E_{i}\right)$ is a
-% subset of $\sum_{i}\pmeas\left(E_{i}\right)$, but may not equal.
+% the whole. Therefore, $\bar{\mu}\left(\bigcup_{i}E_{i}\right)$ is a
+% subset of $\sum_{i}\bar{\mu}\left(E_{i}\right)$, but may not equal.
 % In our example, 
 % \begin{eqnarray*}
-%  &  & \pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})\\
+%  &  & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
 %  & = & \imposs+\unlikely+\imposs+\likely\\
@@
 % \end{eqnarray*}
-% The above equation told us $\pmeas(\Omega)\subseteq\left[\frac{1}{2},\frac{3}{2}\right]$.
-% However, because of $\pmeas(\emptyset)=\imposs$, we have $\pmeas\left(\Omega\right)=1-\pmeas\left(\emptyset\right)=\necess$,
-% but $\pmeas(\emptyset)=\imposs$ cannot be used to reasoning the probability
+% The above equation told us $\bar{\mu}(\Omega)\subseteq\left[\frac{1}{2},\frac{3}{2}\right]$.
+% However, because of $\bar{\mu}(\emptyset)=\imposs$, we have $\bar{\mu}\left(\Omega\right)=1-\bar{\mu}\left(\emptyset\right)=\necess$,
+% but $\bar{\mu}(\emptyset)=\imposs$ cannot be used to reasoning the probability
 % of $\{HH\}$, $\{HT\}$, $\{TH\}$ and $\{TT\}$ individually. The
@@
 \begin{array}{rcl}
-\pmeas(\emptyset) & = & \imposs\\
-\pmeas(\{HH\}) & = & \unlikely\\
-\pmeas(\{HT\}) & = & \imposs\\
-\pmeas(\{TH\}) & = & \likely\\
-\pmeas(\{TT\}) & = & \imposs\\
-\pmeas(\{HH,HT\}) & = & \unlikely\\
-\pmeas(\{HH,TH\}) & = & \necess\\
-\pmeas(\{HH,TT\}) & = & \unlikely
+\bar{\mu}(\emptyset) & = & \imposs\\
+\bar{\mu}(\{HH\}) & = & \unlikely\\
+\bar{\mu}(\{HT\}) & = & \imposs\\
+\bar{\mu}(\{TH\}) & = & \likely\\
+\bar{\mu}(\{TT\}) & = & \imposs\\
+\bar{\mu}(\{HH,HT\}) & = & \unlikely\\
+\bar{\mu}(\{HH,TH\}) & = & \necess\\
+\bar{\mu}(\{HH,TT\}) & = & \unlikely
 \end{array} & \begin{array}{rcl}
-\pmeas(\{HT,TH\}) & = & \likely\\
-\pmeas(\{HT,TT\}) & = & \imposs\\
-\pmeas(\{TH,TT\}) & = & \likely\\
-\pmeas(\{HH,HT,TH\}) & = & \necess\\
-\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
-\pmeas(\{HH,TH,TT\}) & = & \necess\\
-\pmeas(\{HT,TH,TT\}) & = & \likely\\
-\pmeas(\{HH,HT,TH,TT\}) & = & \necess
+\bar{\mu}(\{HT,TH\}) & = & \likely\\
+\bar{\mu}(\{HT,TT\}) & = & \imposs\\
+\bar{\mu}(\{TH,TT\}) & = & \likely\\
+\bar{\mu}(\{HH,HT,TH\}) & = & \necess\\
+\bar{\mu}(\{HH,HT,TT\}) & = & \unlikely\\
+\bar{\mu}(\{HH,TH,TT\}) & = & \necess\\
+\bar{\mu}(\{HT,TH,TT\}) & = & \likely\\
+\bar{\mu}(\{HH,HT,TH,TT\}) & = & \necess
 \end{array}\end{array}
@@
 \begin{eqnarray*}
- &  & \pmeas(\{HH\})+\pmeas(\{HT\})+\pmeas(\{TH\})+\pmeas(\{TT\})\\
+ &  & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
  & = & \imposs+\unlikely+\imposs+\likely\\
@@
 \end{eqnarray*}
-If we were to equate $\pmeas(\Omega)$ with the sum of the individual
+If we were to equate $\bar{\mu}(\Omega)$ with the sum of the individual
 probabilities we would get that
-$\pmeas(\Omega) = \left[\frac{1}{2},\frac{3}{2}\right]$. However,
-using the fact that $\pmeas(\emptyset)=\imposs$, we have
-$\pmeas\left(\Omega\right)=1-\pmeas\left(\emptyset\right)=\necess=[1,1]$. This
+$\bar{\mu}(\Omega) = \left[\frac{1}{2},\frac{3}{2}\right]$. However,
+using the fact that $\bar{\mu}(\emptyset)=\imposs$, we have
+$\bar{\mu}\left(\Omega\right)=1-\bar{\mu}\left(\emptyset\right)=\necess=[1,1]$. This
 interval is tighter and a better estimate for the probability of the
@@
 % \begin{enumerate}
-% \item $1\in\pmeas(\Omega)$, and 
-% \item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$. 
+% \item $1\in\bar{\mu}(\Omega)$, and 
+% \item for a collection $E_{i}$ of pairwise disjoint events, $\bar{\mu}(\bigcup_{i}E_{i})=\sum_{i}\bar{\mu}(E_{i})$. 
 % \end{enumerate}
@@
 % \[\begin{array}{rcl@{\qquad}rcl}
-% \pmeas(\{HH\}) & = & [0,\frac{1}{2}] & \pmeas(\{HT\}) & = & [0,0] \\
-% \pmeas(\{TH\}) & = & [\frac{1}{2},1] &  \pmeas(\{TT\}) & = & [0,0]
+% \bar{\mu}(\{HH\}) & = & [0,\frac{1}{2}] & \bar{\mu}(\{HT\}) & = & [0,0] \\
+% \bar{\mu}(\{TH\}) & = & [\frac{1}{2},1] &  \bar{\mu}(\{TT\}) & = & [0,0]
 % \end{array}\]
-% The probability for $\pmeas(\{HH,TH\})$ is $[X,Y]$ where $X$ comes
+% The probability for $\bar{\mu}(\{HH,TH\})$ is $[X,Y]$ where $X$ comes
 % from the positive evidence for $\{HH\}$ and $\{TH\}$ and from the
@@
 % evidence for $\{HH\}$ and $\{TH\}$ individually and hence we have the
-% tentative bounds on $\pmeas(\{HH,TH\})$ as
+% tentative bounds on $\bar{\mu}(\{HH,TH\})$ as
 % $[\frac{1}{2},\frac{3}{2}]$. The dual events, however, establish
@@
 % \[
-% \pmeas\left(\left\{ i=1\right\} \right)=\pmeas\left(\left\{ i=2\right\} \right)=\pmeas\left(\left\{ i=3\right\} \right)=\frac{1}{3}
+% \bar{\mu}\left(\left\{ i=1\right\} \right)=\bar{\mu}\left(\left\{ i=2\right\} \right)=\bar{\mu}\left(\left\{ i=3\right\} \right)=\frac{1}{3}
 % \]
@@
 % \begin{array}{rcl}
-% \pmeas\left(\left\{ \textrm{Age}(M_{1})=23\right\} \right) & = & \frac{1}{2}\\
-% \pmeas\left(\left\{ \textrm{Age}(M_{1})=24\right\} \right) & = & \frac{1}{2}
+% \bar{\mu}\left(\left\{ \textrm{Age}(M_{1})=23\right\} \right) & = & \frac{1}{2}\\
+% \bar{\mu}\left(\left\{ \textrm{Age}(M_{1})=24\right\} \right) & = & \frac{1}{2}
 % \end{array} & \begin{array}{rcl}
-% \pmeas\left(\left\{ \textrm{Age}(M_{2})=20\right\} \right) & = & \frac{1}{3}\\
-% \pmeas\left(\left\{ \textrm{Age}(M_{2})=21\right\} \right) & = & \frac{1}{3}\\
-% \pmeas\left(\left\{ \textrm{Age}(M_{2})=22\right\} \right) & = & \frac{1}{3}
+% \bar{\mu}\left(\left\{ \textrm{Age}(M_{2})=20\right\} \right) & = & \frac{1}{3}\\
+% \bar{\mu}\left(\left\{ \textrm{Age}(M_{2})=21\right\} \right) & = & \frac{1}{3}\\
+% \bar{\mu}\left(\left\{ \textrm{Age}(M_{2})=22\right\} \right) & = & \frac{1}{3}
 % \end{array}\end{array}\begin{array}{rcl}
-% \pmeas\left(\left\{ \textrm{Age}(M_{3})=20\right\} \right) & = & \frac{1}{2}\\
-% \pmeas\left(\left\{ \textrm{Age}(M_{3})=21\right\} \right) & = & \frac{1}{2}
+% \bar{\mu}\left(\left\{ \textrm{Age}(M_{3})=20\right\} \right) & = & \frac{1}{2}\\
+% \bar{\mu}\left(\left\{ \textrm{Age}(M_{3})=21\right\} \right) & = & \frac{1}{2}
 % \end{array}
@@
 % \begin{eqnarray*}
-%  &  & \pmeas\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
-%  & = & \pmeas\left(\left\{ i=1\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
-%  &  & +\pmeas\left(\left\{ i=2\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
-%  &  & +\pmeas\left(\left\{ i=3\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
+%  &  & \bar{\mu}\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
+%  & = & \bar{\mu}\left(\left\{ i=1\right\} \right)\bar{\mu}\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
+%  &  & +\bar{\mu}\left(\left\{ i=2\right\} \right)\bar{\mu}\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
+%  &  & +\bar{\mu}\left(\left\{ i=3\right\} \right)\bar{\mu}\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
 %  & = & \frac{1}{3}\cdot1+\frac{1}{3}\cdot\frac{1}{3}+\frac{1}{3}\cdot0=\frac{4}{9}
@@
 % \begin{eqnarray*}
-%  &  & \pmeas\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
-%  & = & \pmeas\left(\left\{ i=1\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
-%  &  & +\pmeas\left(\left\{ i=2\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
-%  &  & +\pmeas\left(\left\{ i=3\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
+%  &  & \bar{\mu}\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
+%  & = & \bar{\mu}\left(\left\{ i=1\right\} \right)\bar{\mu}\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
+%  &  & +\bar{\mu}\left(\left\{ i=2\right\} \right)\bar{\mu}\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
+%  &  & +\bar{\mu}\left(\left\{ i=3\right\} \right)\bar{\mu}\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
 %  & = & \frac{1}{3}\cdot[1,1]+\frac{1}{3}\cdot[0,1]+\frac{1}{3}\cdot[0,0]=\left[\frac{1}{3},\frac{2}{3}\right]
@@
 % \begin{eqnarray*}
-% \pmeas\left(\emptyset\right) & = & \imposs\\
-% \pmeas\left(\Omega\right) & = & \necess\\
-% \pmeas\left(\Omega\backslash E\right) & = & 1-\pmeas\left(E\right)
+% \bar{\mu}\left(\emptyset\right) & = & \imposs\\
+% \bar{\mu}\left(\Omega\right) & = & \necess\\
+% \bar{\mu}\left(\Omega\backslash E\right) & = & 1-\bar{\mu}\left(E\right)
 % \end{eqnarray*}
@@
 % \begin{itemize}
-% \item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
+% \item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\bar{\mu}\left(E_{i}\right)$. 
 % \end{itemize}
@@
 % may only be acquired for $\bigcup_{i}E_{i}$ as the whole. Therefore,
-% $\pmeas\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\pmeas\left(E_{i}\right)$,
+% $\bar{\mu}\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\bar{\mu}\left(E_{i}\right)$,
 % but may not equal. In our example, 
 % \begin{eqnarray*}
-%  &  & \pmeas(\{HH,TH\})=\necess=[1,1]\\
-%  & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\pmeas(\{HH\})+\pmeas(\{TH\})\textrm{ .}
+%  &  & \bar{\mu}(\{HH,TH\})=\necess=[1,1]\\
+%  & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\bar{\mu}(\{HH\})+\bar{\mu}(\{TH\})\textrm{ .}
 % \end{eqnarray*}
-% However, $\pmeas(\{HH,TH\})$ is a proper subset of $\pmeas(\{HH\})+\pmeas(\{TH\})$
+% However, $\bar{\mu}(\{HH,TH\})$ is a proper subset of $\bar{\mu}(\{HH\})+\bar{\mu}(\{TH\})$
 % because if we check the complement of $\{HH,TH\}$, we have 
 % \begin{eqnarray*}
-%  &  & \pmeas(\{HH,TH\})=1-\pmeas(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
+%  &  & \bar{\mu}(\{HH,TH\})=1-\bar{\mu}(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
 % \end{eqnarray*}
-% and $\pmeas(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
+% and $\bar{\mu}(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
 % of $\{HH\}$ and $\{TH\}$ individually.
@@
   consists of a set of events $\events$ and a probability measure
-  $\tensor*[_{[0,1]}]{\mu}{} : \events \rightarrow [0,1]$ such
+  $\mu : \events \rightarrow [0,1]$ such
   that:\footnote {It is possible to define a more general space of events consisting of
@@
 \begin{itemize}
-\item $\tensor*[_{[0,1]}]{\mu}{}(\mathbb{1})=1$, and 
+\item $\mu(\mathbb{1})=1$, and 
 \item for mutually orthogonal projections $P_{i}$, we have 
-$\tensor*[_{[0,1]}]{\mu}{}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\tensor*[_{[0,1]}]{\mu}{}\left(P_{i}\right)$.
+$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
 \end{itemize}
 Notice that the preposing $[0,1]$ indicates the range of
-$\tensor*[_{[0,1]}]{\mu}{}$. We will only prepose the range of a
+$\mu$. We will only prepose the range of a
 probability measure whenever we need to compare the ranges of different
@@
 a postulate of quantum mechanics, states that each pure quantum state
-$\ket{\phi}$ induces a probability measure $\tilde{\mu}_{\phi}$
+$\ket{\phi}$ induces a probability measure $\mu^B_{\phi}$
 as follows: 
 \[
-\tilde{\mu}_{\phi}(E)=\ip{\phi}{E\phi}
+\mu^B_{\phi}(E)=\ip{\phi}{E\phi}
 \]
@@
 where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
-measure introduced by $\rho$ is the combination of $\tilde{\mu}_{\phi_{j}}$
+measure introduced by $\rho$ is the combination of $\mu^B_{\phi_{j}}$
 with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
 \begin{eqnarray}
-\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\mu^B_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
 \end{eqnarray}
@@
 listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist
-an unique mixed state~$\rho$ such that $\mu=\tilde{\mu}_{\rho}$.\end{cor}
+an unique mixed state~$\rho$ such that $\mu=\mu^B_{\rho}$.\end{cor}
 
@@
 0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
-\tilde{\mu}_{\ket{0}}(E) & \textrm{, otherwise.}
+\mu^B_{\ket{0}}(E) & \textrm{, otherwise.}
 \end{cases}
@@
 On one hand, $\mu$ is a quantum probability measure. Because $\mu$ is almost
-the same as a quantum probability measure~$\tilde{\mu}_{\ket{0}}$, we only
+the same as a quantum probability measure~$\mu^B_{\ket{0}}$, we only
 need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
@@
 \]
-However, $\tilde{\mu}_{\rho}(E)=1$ if and only if $\rho$ represents
+However, $\mu^B_{\rho}(E)=1$ if and only if $\rho$ represents
 a pure state and $\rho=E$. \qed\end{example}
@@
 and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
-probability measure} is a function~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
+probability measure} is a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that: 
 \begin{itemize}
-\item $\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{0})=\left[0,0\right]$, 
-\item $\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{1})=\left[1,1\right]$, 
+\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$, 
+\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$, 
 \item for any projection $P$,
-$\tensor*[_{\mathscr{I}}]{\mu}{}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\tensor*[_{\mathscr{I}}]{\mu}{}\left(P\right)$, and
+$\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)$, and
 \item for a set of mutually orthogonal projections $P_{i}$, we have
-$\tensor*[_{\mathscr{I}}]{\mu}{}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\tensor*[_{\mathscr{I}}]{\mu}{}\left(P_{i}\right)$.
+$\bar{\mu}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(P_{i}\right)$.
 \end{itemize}
@@
 When we pick $\mathscr{I}=\left\{ \left[x,x\right]\middle|x\in\left[0,1\right]\right\} $,
-for any quantum probability measure~$\tensor*[_{\left[0,1\right]}]{\mu}{}:\events\rightarrow\left[0,1\right]$,
+for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
 we can define a corresponding quantum \emph{$\mathscr{I}$}-interval-valued
-probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
-by $\tensor*[_{\mathscr{I}}]{\mu}{}\left(E\right)=\left[\tensor*[_{\left[0,1\right]}]{\mu}{}\left(E\right),\tensor*[_{\left[0,1\right]}]{\mu}{}\left(E\right)\right]$.
+probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+by $\bar{\mu}\left(E\right)=\left[\mu\left(E\right),\mu\left(E\right)\right]$.
 In this sense, every usual quantum probability measure can be considered
@@
 no information. For any Hilbert space and any quantum probability
-measure~$\tensor*[_{\left[0,1\right]}]{\mu}{}:\events\rightarrow\left[0,1\right]$,
-we can define a quantum interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
+measure~$\mu:\events\rightarrow\left[0,1\right]$,
+we can define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 by 
 \[
-\tensor*[_{\mathscr{I}}]{\mu}{}(E)=\iota\left(\tensor*[_{\left[0,1\right]}]{\mu}{}(E)\right)\textrm{ ,}
+\bar{\mu}(E)=\iota\left(\mu(E)\right)\textrm{ ,}
 \]
@@
 where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
-By applying these two properties, it is easy to verify $\tensor*[_{\mathscr{I}}]{\mu}{}$
+By applying these two properties, it is easy to verify $\bar{\mu}$
 is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}
@@
 \end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma\le2\pi$. Consider
-a quantum interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
+a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 defined by 
 \begin{eqnarray*}
-\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
-\tensor*[_{\mathscr{I}}]{\mu}{}(\mathbb{1}) & = & \necess\textrm{ ,}\\
-\tensor*[_{\mathscr{I}}]{\mu}{}(\proj{\psi}) & = & \begin{cases}
+\bar{\mu}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\proj{\psi}) & = & \begin{cases}
 \necess & \textrm{, if }\theta=0\textrm{ ;}\\
@@
 \[
-\tensor*[_{\mathscr{I}}]{\mu}{}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi}\right)=\tensor*[_{\mathscr{I}}]{\mu}{}\left(\proj{\psi^{\perp}}\right)=1\tensor*[_{\mathscr{I}}]{-}{}\tensor*[_{\mathscr{I}}]{\mu}{}\left(\proj{\psi}\right)\textrm{ .}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi}\right)=\bar{\mu}\left(\proj{\psi^{\perp}}\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(\proj{\psi}\right)\textrm{ .}
 \]
-Hence, $\tensor*[_{\mathscr{I}}]{\mu}{}$ is a quantum $\mathscr{I}$-interval-valued
-probability measure. Notice that for all projection~$E$, $\tensor*[_{\left[0,1\right]}]{\tilde{\mu}}{_{\ket{0}}}(E)\in\tensor*[_{\mathscr{I}}]{\mu}{}(E)$
-implies that $\tensor*[_{\mathscr{I}}]{\mu}{}(E)$ is one of quantum
+Hence, $\bar{\mu}$ is a quantum $\mathscr{I}$-interval-valued
+probability measure. Notice that for all projection~$E$, $\mu^B_{\ket{0}}(E)\in\bar{\mu}(E)$
+implies that $\bar{\mu}(E)$ is one of quantum
 $\mathscr{I}$-interval-valued probability measures corresponding
-to $\tensor*[_{\left[0,1\right]}]{\tilde{\mu}}{_{\ket{0}}}(E)$. However,
-$\tensor*[_{\left[0,1\right]}]{\tilde{\mu}}{_{\ket{0}}}(E)$ can correspond
+to $\mu^B_{\ket{0}}(E)$. However,
+$\mu^B_{\ket{0}}(E)$ can correspond
 to infinity many quantum $\mathscr{I}$-interval-valued probability
@@
 \begin{eqnarray*}
-\mu(\mathbb{0}) & = & \imposs\textrm{ ,}\\
-\mu(\mathbb{1}) & = & \necess\textrm{ ,}\\
-\mu(\proj{0}) & = & \necess\textrm{ ,}\\
-\mu(\proj{\ps}) & = & \necess\textrm{ ,}\\
-\mu(\proj{\psi}) & = & \imposs\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
-\mu(1-\proj{0}) & = & \imposs\textrm{ ,}\\
-\mu(1-\proj{\ps}) & = & \imposs\textrm{ ,}\\
-\mu(1-\proj{\psi}) & = & \necess\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
-\mu(P) & = & \unknown\textrm{, otherwise. }
+\bar{\mu}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\proj{0}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\proj{\ps}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\proj{\psi}) & = & \imposs\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
+\bar{\mu}(1-\proj{0}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(1-\proj{\ps}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(1-\proj{\psi}) & = & \necess\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
+\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
 \end{eqnarray*}
-$\mu$ is not a quantum interval-valued probability measure. To verify
+$\bar{\mu}$ is not a quantum interval-valued probability measure. To verify
 this fact, we first consider an orthonormal basis
@@
 \begin{eqnarray*}
- &  & \mu\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)=\mu\left(1-\proj{\psi_{2}}\right)=\unknown\\
- & \nsubseteq & \imposs+\imposs=\mu\left(\proj{\psi_{1}}\right)+\mu\left(\proj{\psi_{2}}\right)\textrm{ .}
+ &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)=\bar{\mu}\left(1-\proj{\psi_{2}}\right)=\unknown\\
+ & \nsubseteq & \imposs+\imposs=\bar{\mu}\left(\proj{\psi_{1}}\right)+\bar{\mu}\left(\proj{\psi_{2}}\right)\textrm{ .}
 \end{eqnarray*}
@@
 each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
-induces a probability measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$
+induces a probability measure $\mu^B_{\psi}:\qevents\rightarrow[0,1]$
 on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1983,Mermin2007}:
 \begin{equation}
-\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
+\mu^B_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
 \end{equation}
@@
 \begin{eqnarray}
-\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\mu^B_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
 \end{eqnarray}
@@
 as well.
-\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
-\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
-\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
+\item $\mu^B_{\rho}$ is a probability measure for all mixed state~$\rho$.
+\item $\ip{\psi}{\phi}=0\Leftrightarrow\mu^B_{\psi}\left(\proj{\phi}\right)=0$.
+\item $\mu^B_{\psi}\left(E\right)=\mu^B_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
 $\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
@@
 \begin{proof}
-Assume there is another function $\tilde{\mu}'$ such that $\tilde{\mu}'_{\rho}$
+Assume there is another function $\mu'^B$ such that $\mu'^B_{\rho}$
 is a quantum probability measure for all mixed state~$\rho$. We
-are going to prove $\tilde{\mu}'=\tilde{\mu}$.
-
-Fix a pure normalized state $\phi$, $\tilde{\mu}'_{\phi}$ is a quantum
+are going to prove $\mu'^B=\mu^B$.
+
+Fix a pure normalized state $\phi$, $\mu'^B_{\phi}$ is a quantum
 probability measure by condition 2. By Gleason's theorem, there is
-a mixed state ~$\rho'$, such that $\tilde{\mu}'_{\phi}\left(E\right)=\Tr\left(\rho'E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\psi_{j}}\left(E\right)$
+a mixed state ~$\rho'$, such that $\mu'^B_{\phi}\left(E\right)=\Tr\left(\rho'E\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(E\right)$
 for all event $E$.
@@
 \begin{eqnarray*}
-0 & \overset{\textrm{Condition 3}}{=} & \tilde{\mu}_{\phi}\left(E'\right)\\
- & = & \sum_{j=1}^{N}q_{j}\tilde{\mu}_{\psi_{j}}\left(E'\right)
+0 & \overset{\textrm{Condition 3}}{=} & \mu^B_{\phi}\left(E'\right)\\
+ & = & \sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(E'\right)
 \end{eqnarray*}
-Because $q_{j}>0$, we have $\tilde{\mu}_{\psi_{j}}\left(E\right)=0$,
+Because $q_{j}>0$, we have $\mu^B_{\psi_{j}}\left(E\right)=0$,
 i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $E'$.
 However, the only subspace orthogonal to $E'$ is span by $\ket{\phi}$.
-Hence, $\tilde{\mu}'_{\phi}=\tilde{\mu}_{\phi}$.
+Hence, $\mu'^B_{\phi}=\mu^B_{\phi}$.
 \end{proof}
@@
 % whether we will keep using the Born rule (\ref{eq:Born}) or there
-% is another formula $\tilde{\mu}$ such that $\tilde{\mu}_{\psi}$
+% is another formula $\mu^B$ such that $\mu^B_{\psi}$
 % is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
@@
 % i.e., the Born rule is surjective\footnote{If we extend the domain of $\mu_{\psi}$ including the mixed states.}.
-% For any other formula~$\tilde{\mu}$, we can ask whether $\tilde{\mu}$
+% For any other formula~$\mu^B$, we can ask whether $\mu^B$
 % is surjective as well.
@@
 % Obviously, we don't want arbitrarily assign a state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
-% with a probability measure $\tilde{\mu}_{\psi}$, for example, assigning
-% every state to the same probability measure. We want $\tilde{\mu}_{\psi}$
+% with a probability measure $\mu^B_{\psi}$, for example, assigning
+% every state to the same probability measure. We want $\mu^B_{\psi}$
 % satisfying the following properties with some physical meaning:
 % \begin{itemize}
-% \item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
+% \item $\ip{\psi}{\phi}=0\Leftrightarrow\mu^B_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
 % where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
 % is impossible for $\mathscr{L}_{2}=\left\{ \imposs,\poss\right\} $. 
-% \item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
+% \item $\mu^B_{\psi}\left(\proj{\phi}\right)=\mu^B_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
 % $\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
@@
 % \hline 
-% State space $\Hilb$  & Probability values  & Is there a $\tilde{\mu}$ satisfying the given conditions?  & Is the $\tilde{\mu}$ surjective?\tabularnewline
+% State space $\Hilb$  & Probability values  & Is there a $\mu^B$ satisfying the given conditions?  & Is the $\mu^B$ surjective?\tabularnewline
 % \hline 

### 2016-06-24 prob.tex
prob.tex Global replace E by P for projection~~

@@
   the Born rule~\cite{Born1983,Mermin2007} and the map is given by:
-  $E \mapsto \ip{\psi}{E\psi}$.
+  $P \mapsto \ip{\psi}{P\psi}$.
 \item given a probability measure $\mu$
-  mapping each event $E$
+  mapping each event $P$
   to a probability, is there a \emph{unique} state $\psi$
-  such that $\mu(E)
+  such that $\mu(P)
   =
-  \ip{\psi}{E\psi}$? In the conventional case, the answer is yes by
+  \ip{\psi}{P\psi}$? In the conventional case, the answer is yes by
   Gleason's
@@
 \[
-\mu^B_{\phi}(E)=\ip{\phi}{E\phi}
+\mu^B_{\phi}(P)=\ip{\phi}{P\phi}
 \]
@@
 \begin{eqnarray}
-\mu^B_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\mu^B_{\rho}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\phi_{j}}\left(P\right)\textrm{ .}\label{BornRule.mixed}
 \end{eqnarray}
@@
 \[
-\mu(E)=\begin{cases}
-1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
-0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
-\mu^B_{\ket{0}}(E) & \textrm{, otherwise.}
+\mu(P)=\begin{cases}
+1 & \textrm{, if }P=\proj{\ps}\textrm{ ;}\\
+0 & \textrm{, if }P=\proj{\ms}\textrm{ ;}\\
+\mu^B_{\ket{0}}(P) & \textrm{, otherwise.}
 \end{cases}
@@
 \]
-However, $\mu^B_{\rho}(E)=1$ if and only if $\rho$ represents
-a pure state and $\rho=E$. \qed\end{example}
+However, $\mu^B_{\rho}(P)=1$ if and only if $\rho$ represents
+a pure state and $\rho=P$. \qed\end{example}
 
@@
 probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-by $\bar{\mu}\left(E\right)=\left[\mu\left(E\right),\mu\left(E\right)\right]$.
+by $\bar{\mu}\left(P\right)=\left[\mu\left(P\right),\mu\left(P\right)\right]$.
 In this sense, every usual quantum probability measure can be considered
@@
 \[
-\bar{\mu}(E)=\iota\left(\mu(E)\right)\textrm{ ,}
+\bar{\mu}(P)=\iota\left(\mu(P)\right)\textrm{ ,}
 \]
@@
 Hence, $\bar{\mu}$ is a quantum $\mathscr{I}$-interval-valued
-probability measure. Notice that for all projection~$E$, $\mu^B_{\ket{0}}(E)\in\bar{\mu}(E)$
-implies that $\bar{\mu}(E)$ is one of quantum
+probability measure. Notice that for all projection~$P$, $\mu^B_{\ket{0}}(P)\in\bar{\mu}(P)$
+implies that $\bar{\mu}(P)$ is one of quantum
 $\mathscr{I}$-interval-valued probability measures corresponding
-to $\mu^B_{\ket{0}}(E)$. However,
-$\mu^B_{\ket{0}}(E)$ can correspond
+to $\mu^B_{\ket{0}}(P)$. However,
+$\mu^B_{\ket{0}}(P)$ can correspond
 to infinity many quantum $\mathscr{I}$-interval-valued probability
@@
 quantum probability measure~$\mu$, our $\mu$ is actually
-given by a simple formula~$\melement{0}{E}$. In general, Born discovered
+given by a simple formula~$\melement{0}{P}$. In general, Born discovered
 each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
 induces a probability measure $\mu^B_{\psi}:\qevents\rightarrow[0,1]$
-on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1983,Mermin2007}:
+on the space of events defined for any event $P\in\qevents$ as follows~\cite{Born1983,Mermin2007}:
 \begin{equation}
-\mu^B_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
+\mu^B_{\psi}(P)=\frac{\melement{\psi}{P}}{\ip{\psi}{\psi}}\label{eq:Born}
 \end{equation}
@@
 \begin{eqnarray}
-\mu^B_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
+\mu^B_{\rho}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\Psi_{j}}\left(P\right)\textrm{ .}\label{BornRule.mixed}
 \end{eqnarray}
@@
 \item $\ip{\psi}{\phi}=0\Leftrightarrow\mu^B_{\psi}\left(\proj{\phi}\right)=0$.
-\item $\mu^B_{\psi}\left(E\right)=\mu^B_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
+\item $\mu^B_{\psi}\left(P\right)=\mu^B_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}P\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
 $\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
@@
 probability measure by condition 2. By Gleason's theorem, there is
-a mixed state ~$\rho'$, such that $\mu'^B_{\phi}\left(E\right)=\Tr\left(\rho'E\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(E\right)$
-for all event $E$.
-
-Consider the event $E'=\mathbb{1}-\proj{\phi}$, we have 
+a mixed state ~$\rho'$, such that $\mu'^B_{\phi}\left(P\right)=\Tr\left(\rho'P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P\right)$
+for all event $P$.
+
+Consider the event $P'=\mathbb{1}-\proj{\phi}$, we have 
 \begin{eqnarray*}
-0 & \overset{\textrm{Condition 3}}{=} & \mu^B_{\phi}\left(E'\right)\\
- & = & \sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(E'\right)
+0 & \overset{\textrm{Condition 3}}{=} & \mu^B_{\phi}\left(P'\right)\\
+ & = & \sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P'\right)
 \end{eqnarray*}
-Because $q_{j}>0$, we have $\mu^B_{\psi_{j}}\left(E\right)=0$,
-i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $E'$.
-However, the only subspace orthogonal to $E'$ is span by $\ket{\phi}$.
+Because $q_{j}>0$, we have $\mu^B_{\psi_{j}}\left(P\right)=0$,
+i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $P'$.
+However, the only subspace orthogonal to $P'$ is span by $\ket{\phi}$.
 Hence, $\mu'^B_{\phi}=\mu^B_{\phi}$.
@@
 \[
-\hat{\mu}_{1}\left(E\right)=\begin{cases}
-\imposs & \textrm{, if }E=\proj{+};\\
-\bar{\mu}(E) & \textrm{, otherwise.}
+\hat{\mu}_{1}\left(P\right)=\begin{cases}
+\imposs & \textrm{, if }P=\proj{+};\\
+\bar{\mu}(P) & \textrm{, otherwise.}
 \end{cases}

### 2016-06-24 prob.tex
prob.tex \subsection{Quantum Events} updates...

@@
 
+Based on quantum events are projection operators, operations and properties of
+quntum events can be written in terms of those of operators.
+
+\begin{definition}[Ideal Measurement; Complement;
+Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
+\begin{itemize}
+\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
+measurement} if it is a partition of the identity, i.e.,
+$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
+\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
+is also a projection operator, called \emph{complement}. It is orthogonal to $P$,
+and corresponds to the complement event~$\Omega\backslash E$
+in classical probability.
+\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
+The product of two projection operators~$P_{1}P_{2}$ is also a projection
+operator if and only if they commute. This corresponds to the classical intersection
+between events. 
+\end{itemize}
+\qed\end{definition}
+
+%%%%%
+\subsection{Quantum Probability Measures}
+
 Based on the set of events, we can define the quantum probability
@@
 space.
-
-\begin{definition}[Ideal Measurement; Complement;
-Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
-\begin{itemize}
-\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
-measurement} if it is a partition of the identity, i.e.,
-$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
-\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
-is also a projection operator, called \emph{complement}. It is orthogonal to $P$, has
-probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
-and corresponds to the complement event~$\Omega\backslash E$
-in classical probability.
-\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
-The product of two projection operators~$P_{1}P_{2}$ is also a projection
-operator if and only if they commute. This corresponds to the classical intersection
-between events. 
-\end{itemize}
-\qed\end{definition}
 
@@
 
-%%%%%
-\subsection{Quantum Probability Measures}
-
 For a given set of events $\events$, there are many possible probability
 measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
-a postulate of quantum mechanics, states that each pure quantum state
-$\ket{\phi}$ induces a probability measure $\mu^B_{\phi}$
-as follows: 
+a postulate of quantum mechanics, states that each pure normalized
+($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$ induces a probability measure
+$\mu^B_{\phi}$ as follows: 
 \[
@@
 we want to prepare a quantum system. As we discussed in classical
-probability, our ability of preparing a state might not be prefect.
+probability, our ability of preparing a state might not be perfect.
 If we want to prepare $\ket{\phi}$, we may turn out preparing a set
@@
 
-\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$,
-for any function~$\mu:\events\rightarrow[0,1]$ satisfying the conditions
+\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$ of dimension
+$d\geq3$, for any function~$\mu:\events\rightarrow[0,1]$ satisfying the conditions
 listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist

### 2016-06-25 prob.tex
prob.tex \subsection{Quantum Probability Measures} start updating...

@@
 
-Based on the set of events, we can define the quantum probability
-space.
-
 \begin{definition}[Quantum Probability
-Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
-  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
-  consists of a set of events $\events$ and a probability measure
-  $\mu : \events \rightarrow [0,1]$ such
-  that:\footnote {It is possible to define a more general space of events consisting of
+Measure~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
+Given a Hilbert space $\Hilb$ with its set of events~$\events$, a
+\emph{quantum probability measure} is a function~$\mu : \events \rightarrow
+[0,1]$ such that:\footnote {It is possible to define a more general space of events consisting of
     all operators~$\mathcal{A}$ on $\Hilb$ and consider
@@
 \end{itemize}
-Notice that the preposing $[0,1]$ indicates the range of
-$\mu$. We will only prepose the range of a
-probability measure whenever we need to compare the ranges of different
-probability measures. 
 \qed\end{definition}
-
-Comparing to the classical probability space, the empty set~$\emptyset$
-corresponds to the empty projection~$\mathbb{0}$ and the event of
-whole space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
-In contrast, the union~$\cup$ of any two events always gives an
-event classically, but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
-of two projections may not be a projection. As the result, the classical
-condition~$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
-is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
-however, $\mu\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)=\mu(P_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(P_{2})$
-is always true whenever the left-handed side is defined. Whether an equation
-is defined also effects the further properties of quantum probability
-space.
 
@@
 \qed\end{lemma}
+
+A set of events~$\events$ together with quantum probability measure is called a
+\emph{quantum probability space}. 
+Comparing to the classical probability space, the empty set~$\emptyset$
+corresponds to the empty projection~$\mathbb{0}$ and the event of
+whole space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
+In contrast, the union~$\cup$ of any two events always gives an
+event classically, but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
+of two projections may not be a projection. As the result, the classical
+condition~$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
+is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
+however, $\mu\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)=\mu(P_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(P_{2})$
+is always true whenever the left-handed side is defined.
 
@@
 
-For a given set of events $\events$, there are many possible probability
-measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
+Another difference between classical and quantum probabiltiy space. For a
+given set of events $\events$, there are many possible probability measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
 a postulate of quantum mechanics, states that each pure normalized

### 2016-06-30 prob.tex
prob.tex \subsection{Quantum Probability Measures} Fix a typo...
prob.lyx Find a bug...>"<

@@
   \qed\end{example}
+
+Although specifying a probability for every event looks complex, a
+probability measure can be simply constructed by $\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)$,
+where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
+Furthermore, every probability measure~$\pmeas$ can be written in
+this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}
+which is called the probability distribution~\cite{GrahamKnuthPatashnik1994}.
 
@@
 
-Another difference between classical and quantum probabiltiy space. For a
+Another difference between classical and quantum probability space. For a
 given set of events $\events$, there are many possible probability measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},

### 2016-06-30 prob.tex
prob.tex Fix a bug by replacing "\mu'^B" by "\mu^{\prime B}"

@@
 \begin{proof}
-Assume there is another function $\mu'^B$ such that $\mu'^B_{\rho}$
+Assume there is another function $\mu^{\prime B}$ such that $\mu^{\prime B}_{\rho}$
 is a quantum probability measure for all mixed state~$\rho$. We
-are going to prove $\mu'^B=\mu^B$.
-
-Fix a pure normalized state $\phi$, $\mu'^B_{\phi}$ is a quantum
+are going to prove $\mu^{\prime B}=\mu^B$.
+
+Fix a pure normalized state $\phi$, $\mu^{\prime B}_{\phi}$ is a quantum
 probability measure by condition 2. By Gleason's theorem, there is
-a mixed state ~$\rho'$, such that $\mu'^B_{\phi}\left(P\right)=\Tr\left(\rho'P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P\right)$
+a mixed state ~$\rho'$, such that $\mu^{\prime B}_{\phi}\left(P\right)=\Tr\left(\rho'P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P\right)$
 for all event $P$.
@@
 However, the only subspace orthogonal to $P'$ is span by $\ket{\phi}$.
-Hence, $\mu'^B_{\phi}=\mu^B_{\phi}$.
+Hence, $\mu^{\prime B}_{\phi}=\mu^B_{\phi}$.
 \end{proof}

### 2016-06-30 prob.tex
"Referenece\O. Nikodym, Sur une généralisation des intégrales de M. J. Radon.pdf" Added...

@@
 this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}
-which is called the probability distribution~\cite{GrahamKnuthPatashnik1994}.
+which is called the probability distribution~\cite{GrahamKnuthPatashnik1994}
+or the Radon-Nikodym derivative of $\pmeas$ with respect to the counting
+measure~\cite{Nikodym1930,Torchinsky1994}.
 

### 2016-06-30 prob.tex
prob.tex Write Radon-Nikodym theorem in quantum probability space...

--- 2016-06-30 prob.tex
@@
 Furthermore, every probability measure~$\pmeas$ can be written in
-this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}
-which is called the probability distribution~\cite{GrahamKnuthPatashnik1994}.
+this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}.
+This fact is a special case of the the Radon-Nikodym theorem, and
+$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
+to the counting measure~\cite{Nikodym1930,Folland2013}. For example,
+the Radon-Nikodym derivative of $\pmeas$ in example~\ref{ex1} is:
+\[
+\begin{array}{rcl}
+\rho\left(HH\right)=1/3,\quad\rho\left(HT\right)=0,\quad\rho\left(TH\right)=2/3,\quad\rho\left(TT\right)=0\textrm{ .}\end{array}
+\]
 
@@
 more evidence knowing the aggregate event.\qed\end{example}
+\footnote{\yutsung{The Radon-Nikodym Theorem for interval-valued
+probability?\cite{GilboaSchmeidler1994}?}}
 
@@
 
-Another difference between classical and quantum probability space. For a
-given set of events $\events$, there are many possible probability measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
-a postulate of quantum mechanics, states that each pure normalized
-($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$ induces a probability measure
-$\mu^B_{\phi}$ as follows: 
+Like a classical probability measure can be easily defined by its
+Radon-Nikodym derivative, a quantum probability measure can be easily
+constructed by states according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
+For each pure normalized ($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$,
+the Born rule induces a probability measure $\mu_{\phi}^{B}$ as follows:
 \[
-\mu^B_{\phi}(P)=\ip{\phi}{P\phi}
+\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}\textrm{ .}
 \]
@@
 Moreover, the Born rule can be extended to a mixed state. Suppose
-we want to prepare a quantum system. As we discussed in classical
-probability, our ability of preparing a state might not be perfect.
-If we want to prepare $\ket{\phi}$, we may turn out preparing a set
-of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$. Then,
+we prepares a set of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$,
 the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
 where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
-measure introduced by $\rho$ is the combination of $\mu^B_{\phi_{j}}$
+measure introduced by $\rho$ is the combination of $\mu_{\phi_{j}}^{B}$
 with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
 \begin{eqnarray}
-\mu^B_{\rho}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\phi_{j}}\left(P\right)\textrm{ .}\label{BornRule.mixed}
+\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed}
 \end{eqnarray}
 
-Conversely, in Hilbert spaces of dimension $d\geq3$, Gleason's theorem
-states that given a probability measure $\mu$, there exist a mixed
-state~$\rho$ that induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+The generalized Radon-Nikodym theorem is called Gleason's theorem
+which states that, in Hilbert spaces of dimension $d\geq3$, given
+a probability measure $\mu$, there exist a mixed state~$\rho$ that
+induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}

### 2016-07-01 prob.tex
prob.tex Starting adding proof in appendix

@@
 between events. 
+\item For projection operators $P_{1}$ and $P_{2}$, we define $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$
+if $P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}$ is a projection operator;
+and $P_{1}\tensor*[_{\mathscr{O}}]{>}{}P_{2}$ if $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$
+and $P_{1}\ne P_{2}$. Also, let $S_{i}$ be the linear subspace $P_{i}$
+project onto, then $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$ if
+and only if $S_{1}\supseteq S_{2}$.\yutsung{Need to verify!}
 \end{itemize}
@@
 
+\appendix
+
+\section{Proof of Quantum Interval-valued Probability Measures}
+
+Before we prove our results, we need the following lemmas.
+
+\begin{lemma}Given a Hilbert space~$\Hilb$ with the set of quantum
+events~$\events$, a collection of intervals~$\mathscr{I}$, and
+a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
+\qed\end{lemma}
 \end{document}

### 2016-07-02 prob.tex
"Georges-Louis Leclerc, Comte de Buffon.pdf" Updated...
prob.tex \section{Proof of Quantum Interval-valued Probability Measures} updated....

@@
 
+In order to simplify the notation, consider the following definition
+for interval-valued probability measures.
+
+\begin{definition}Given a Hilbert space~$\Hilb$ with the set of
+quantum events~$\events$, a collection of intervals~$\mathscr{I}$,
+and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
+Let $l:\events\rightarrow\left[0,1\right]$ and $r:\events\rightarrow\left[0,1\right]$
+such that $\left[l\left(P\right),r\left(P\right)\right]=\bar{\mu}\left(P\right)$.\qed\end{definition}
+
 Before we prove our results, we need the following lemmas.
@@
 a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
-\qed\end{lemma}
+For projection operators $P_{1}$ and $P_{2}$, if $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$,
+then $\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{\ge}{}\bar{\mu}\left(P_{2}\right)$,
+where $\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{\ge}{}\left[l_{2},r_{2}\right]$
+if and only if $l_{1}\tensor*[_{\mathbb{R}}]{\ge}{}l_{2}$ and $r_{1}\tensor*[_{\mathbb{R}}]{\ge}{}r_{2}$.
+The preposing $\mathbb{R}$ represents its an inequality of real numbers
+as usual.\qed\end{lemma}
+
+\begin{proof}
+
+\begin{eqnarray*}
+ &  & P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}\\
+ & \Rightarrow & \bar{\mu}\left(P_{1}\right)\subseteq\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\\
+ & \Rightarrow & l\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{\ge}{}l\left(P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(P_{2}\right)\tensor*[_{\mathbb{R}}]{\ge}{}l\left(P_{2}\right)
+\end{eqnarray*}
+Similarly, 
+\begin{eqnarray*}
+ &  & \mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{1}\tensor*[_{\mathscr{O}}]{\le}{}\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\\
+ & \Rightarrow & 1\tensor*[_{\mathbb{R}}]{-}{}r\left(P_{1}\right)=l\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{1}\right)\tensor*[_{\mathbb{R}}]{\le}{}l\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)=1\tensor*[_{\mathbb{R}}]{-}{}r\left(P_{2}\right)\\
+ & \Rightarrow & r\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{\ge}{}r\left(P_{2}\right)
+\end{eqnarray*}
+
+\end{proof}
 \end{document}

### 2016-07-02 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} update the counterexample...

@@
 
+Although $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ maps every
+quantum probability measure to a quantum interval-valued probability
+measure, there is a quantum \emph{$\mathscr{I}$}-interval-valued
+probability measure which does not come from a quantum probability
+measure.
+
+\begin{example}[Three-dimensional quantum interval-valued probability
+measure] Given a three dimensional Hilbert space with an orthonormal
+basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
+$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
+as before. Let 
+\begin{eqnarray*}
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(1-\proj{0})=\bar{\mu}(1-\proj{\ps}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
+\end{eqnarray*}
+To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
+it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
+for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
+verified by enumerating all possible cases.
+
+$\bar{\mu}$ cannot correspond to any quantum probability measure.
+Suppose $\bar{\mu}(P)=\iota\left(\mu(P)\right)$ for some $\mu:\events\rightarrow\left[0,1\right]$.
+We must have 
+\begin{equation}
+\mu(\proj{0})=\mu(\proj{\ps})=0\textrm{ .}\label{eq:probability-zero-on-states}
+\end{equation}
+By Gleason's theorem, there is a mixed state~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$
+such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+where $\sum_{j}q_{j}=1$ and $q_{j}>0$. By
+equation (\ref{eq:probability-zero-on-states}),
+we have $\rho=\proj{2}$. However, 
+\[
+\iota\left(\mu(\proj{2})\right)=\necess\ne\unknown=\bar{\mu}(P)\textrm{ .}
+\]
+\qed\end{example}
+
 Notice that in the above two examples, quantum interval-valued probability
@@
 measures by twisting the definition involving $\gamma$.\qed\end{example}
-
-We have enough examples for quantum interval-valued probability measure,
-it is instructive to understand the conditions by studying a measure
-which is not a quantum interval-valued probability measure.
-
-\begin{example}[Not three-dimensional quantum interval-valued probability
-measure] Given a three dimensional Hilbert space with an orthonormal
-basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
-$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
-as before. Let
-\begin{eqnarray*}
-\bar{\mu}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1}) & = & \necess\textrm{ ,}\\
-\bar{\mu}(\proj{0}) & = & \necess\textrm{ ,}\\
-\bar{\mu}(\proj{\ps}) & = & \necess\textrm{ ,}\\
-\bar{\mu}(\proj{\psi}) & = & \imposs\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
-\bar{\mu}(1-\proj{0}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(1-\proj{\ps}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(1-\proj{\psi}) & = & \necess\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
-\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
-\end{eqnarray*}
-$\bar{\mu}$ is not a quantum interval-valued probability measure. To verify
-this fact, we first consider an orthonormal basis
-\begin{eqnarray*}
-\ket{\psi_{0}} & = & \frac{1}{\sqrt{2}}\ket{1}+\frac{1}{\sqrt{2}}\ket{2}\\
-\ket{\psi_{1}} & = & \frac{1}{\sqrt{3}}\ket{0}-\frac{1}{\sqrt{3}}\ket{1}+\frac{1}{\sqrt{3}}\ket{2}\\
-\ket{\psi_{2}} & = & \sqrt{\frac{2}{3}}\ket{0}+\frac{1}{\sqrt{6}}\ket{1}-\frac{1}{\sqrt{6}}\ket{2}
-\end{eqnarray*}
-However,
-
-\begin{eqnarray*}
- &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)=\bar{\mu}\left(1-\proj{\psi_{2}}\right)=\unknown\\
- & \nsubseteq & \imposs+\imposs=\bar{\mu}\left(\proj{\psi_{1}}\right)+\bar{\mu}\left(\proj{\psi_{2}}\right)\textrm{ .}
-\end{eqnarray*}
-\qed\end{example}
-
-\yutsung{For \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
-are there any quantum interval-valued probability measures do not
-come from quantum probability measures?}
 

### 2016-07-02 prob.tex
prob.tex update the example, and delete redundant stuff...

@@
 between events. 
-\item For projection operators $P_{1}$ and $P_{2}$, we define $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$
-if $P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}$ is a projection operator;
-and $P_{1}\tensor*[_{\mathscr{O}}]{>}{}P_{2}$ if $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$
-and $P_{1}\ne P_{2}$. Also, let $S_{i}$ be the linear subspace $P_{i}$
-project onto, then $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$ if
-and only if $S_{1}\supseteq S_{2}$.\yutsung{Need to verify!}
 \end{itemize}
@@
 basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
-$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
-as before. Let 
+$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
+and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$. Let 
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(1-\proj{0})=\bar{\mu}(1-\proj{\ps}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(1-\proj{0})=\bar{\mu}(1-\proj{\ps})=\bar{\mu}(1-\proj{\ps'}) & = & \necess\textrm{ ,}\\
 \bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
@@
 \begin{equation}
-\mu(\proj{0})=\mu(\proj{\ps})=0\textrm{ .}\label{eq:probability-zero-on-states}
+\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
 \end{equation}
@@
 such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j}q_{j}=1$ and $q_{j}>0$. By
-equation (\ref{eq:probability-zero-on-states}),
-we have $\rho=\proj{2}$. However, 
-\[
-\iota\left(\mu(\proj{2})\right)=\necess\ne\unknown=\bar{\mu}(P)\textrm{ .}
-\]
-\qed\end{example}
+where $\sum_{j}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
+satisfies
+\[
+\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0
+\]
+so that no quantum probability measure~$\mu$ such that $\bar{\mu}(P)=\iota\left(\mu(P)\right)$.\qed\end{example}
 
@@
 measures by twisting the definition involving $\gamma$.\qed\end{example}
+
+\yutsung{Is there a quantum interval-value probability measure which
+corresponds to no quantum probability measure for $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $?
+This is still important because \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
+is way to small for a general case.}
 
@@
 
-\appendix
-
-\section{Proof of Quantum Interval-valued Probability Measures}
-
-In order to simplify the notation, consider the following definition
-for interval-valued probability measures.
-
-\begin{definition}Given a Hilbert space~$\Hilb$ with the set of
-quantum events~$\events$, a collection of intervals~$\mathscr{I}$,
-and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
-Let $l:\events\rightarrow\left[0,1\right]$ and $r:\events\rightarrow\left[0,1\right]$
-such that $\left[l\left(P\right),r\left(P\right)\right]=\bar{\mu}\left(P\right)$.\qed\end{definition}
-
-Before we prove our results, we need the following lemmas.
-
-\begin{lemma}Given a Hilbert space~$\Hilb$ with the set of quantum
-events~$\events$, a collection of intervals~$\mathscr{I}$, and
-a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
-For projection operators $P_{1}$ and $P_{2}$, if $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$,
-then $\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{\ge}{}\bar{\mu}\left(P_{2}\right)$,
-where $\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{\ge}{}\left[l_{2},r_{2}\right]$
-if and only if $l_{1}\tensor*[_{\mathbb{R}}]{\ge}{}l_{2}$ and $r_{1}\tensor*[_{\mathbb{R}}]{\ge}{}r_{2}$.
-The preposing $\mathbb{R}$ represents its an inequality of real numbers
-as usual.\qed\end{lemma}
-
-\begin{proof}
-
-\begin{eqnarray*}
- &  & P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}\\
- & \Rightarrow & \bar{\mu}\left(P_{1}\right)\subseteq\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\\
- & \Rightarrow & l\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{\ge}{}l\left(P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(P_{2}\right)\tensor*[_{\mathbb{R}}]{\ge}{}l\left(P_{2}\right)
-\end{eqnarray*}
-Similarly, 
-\begin{eqnarray*}
- &  & \mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{1}\tensor*[_{\mathscr{O}}]{\le}{}\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\\
- & \Rightarrow & 1\tensor*[_{\mathbb{R}}]{-}{}r\left(P_{1}\right)=l\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{1}\right)\tensor*[_{\mathbb{R}}]{\le}{}l\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)=1\tensor*[_{\mathbb{R}}]{-}{}r\left(P_{2}\right)\\
- & \Rightarrow & r\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{\ge}{}r\left(P_{2}\right)
-\end{eqnarray*}
-
-\end{proof}
 \end{document}

### 2016-07-02 prob.tex
prob.tex \subsection{Plan} Add email and comments...

@@
 \end{itemize}
+
+\andy{Quantum meeting: the basics of classical and quantum standard
+and interval probabilities are becoming clearer (except need clearer
+exposition). The key step is the replacement of \textquotedbl{}sum\textquotedbl{}
+and \textquotedbl{}=\textquotedbl{} in the rule $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$
+by various logical operations on sets instead of actually summing
+unit norm partitions of unity in $\mathbb{R}$. What remains is to
+determine how the Meyer/Mermin debate plays out for finite precision
+or uncertain measurements of events, and its implication for the validity
+of the Kochen-Specker theorem, and hence for the validity of Gleason's
+theorem. Do we have anything ANALOGOUS to a Gleason theorem for interval
+probability quantum mechanics? If so, what are the implications for
+Kochen-Specker and Bell analogs for interval probabilities, and what
+are the implications for the Meyer/Mermin debate? And if not, what
+are the consequences? Finally, given whatever remains of Gleason/Kochen-Specker
+for uncertain event measurements, what happens when we redefine \textquotedbl{}sum\textquotedbl{}
+yet again for $\ff{p^{2}}$ valued quantum theories (and degenerate
+states, and density matrices) to create a non-wrapping extension of
+interval probability calculus to Galois fields? (The objective is
+to put possible/impossible and its extensions on a solid footing for
+DQC, and also to set up a seamless transition back to a continuous
+CQC limit that is consistent, while incorporating such issues as the
+cost of measurement precision.) }
+
+\yutsung{A mathematical reason why Gleason's theorem should not be
+valid in the interval-valued probability quantum mechanics. Every
+classical probability measure has a one-to-one correspondence to its
+Radon-Nikodym derivative. The Radon-Nikodym theorem extends to Gleason's
+theorem in quantum, while the role of Radon-Nikodym derivative is
+replaced by the density matrix. If there is no easy Radon-Nikodym
+theorem for classical interval-valued probability measure (\cite{GilboaSchmeidler1994}
+or other sources. Need verify!), it is natural that there is no easy
+Gleason's theorem for quantum interval-valued probability measure...
+
+If Gleason's theorem is not valid, a non-Born quantum probability
+measure might exist in reality... If there exists a non-Born quantum
+probability measure which cannot correspond to any state vectors,
+then what's the post-measurement quantum probability measure of it
+after measurement? If the updated post-measurement postulate is strange
+enough, then commuting observables may not interchange their measurement
+order... And commuting observables is compatible is the fundamental
+assumption for the Kochen-Specker theorem, the Bell theorem, and everything\dots{}
+If commuting observables becomes non-compatible, everything might
+need to be rewritten\dots{} }
 

### 2016-07-09 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} Fix a bug...
prob.tex \subsection{Quantum Probability Measures} Explicitly write down the connection between the Radon-Nikodym theorem and Gleason's theorem

@@
 Although specifying a probability for every event looks complex, a
-probability measure can be simply constructed by $\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)$,
+probability measure can be simply constructed by 
+\begin{equation}
+\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
+\end{equation}
 where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
@@
 
-Like a classical probability measure can be easily defined by its
-Radon-Nikodym derivative, a quantum probability measure can be easily
-constructed by states according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
+A quantum probability measure can be easily constructed by states
+according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
 For each pure normalized ($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$,
@@
 \end{eqnarray}
+
+Actually, constructing a quantum probability measures from a density
+matrix~$\rho$ is similar to defining a classical probability measure
+by its Radon-Nikodym derivative. This can be seen more easily if we
+pick an orthonormal basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
+such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\psi_{j}\in S}}\proj{\psi_{j}}$,
+where $S$ is the linear subspace $P$ projects onto. Then, a density
+matrix~$\rho$ can also be represented in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\proj{\psi_{j}}$,
+and the Born rule becomes
+\begin{eqnarray}
+\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\psi_{j}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
+\end{eqnarray}
+which is basically the same as equation (\ref{eq:Radon-Nikodym}).
 
@@
 \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(1-\proj{0})=\bar{\mu}(1-\proj{\ps})=\bar{\mu}(1-\proj{\ps'}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
 \bar{\mu}(P) & = & \unknown\textrm{, otherwise. }

### 2016-07-10 prob.tex
prob.tex \subsection{Quantum Probability Measures} Add citation...

@@
 
-The generalized Radon-Nikodym theorem is called Gleason's theorem
+The generalized Radon-Nikodym theorem is called Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA}
 which states that, in Hilbert spaces of dimension $d\geq3$, given

### 2016-07-11 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} adding example...

@@
 
-\begin{example}[Three-dimensional quantum interval-valued probability
-measure] Given a three dimensional Hilbert space with an orthonormal
-basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
-$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
-and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$. Let 
+\begin{example}[Three-dimensional quantum three-value interval-valued
+probability measure]\label{Three-dimensional-three-value} Given
+a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
+and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$. Let 
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) & = & \necess\textrm{ ,}\\
 \bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
@@
 \begin{equation}
-\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
+\mu(\proj{0})=\mu(\proj{\ps})=0\textrm{ .}\label{eq:probability-zero-on-states}
 \end{equation}
@@
 such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
+where $\sum_{j}q_{j}=1$ and $q_{j}>0$. The only pure state~$\ket{\phi}$
 satisfies
 \[
-\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0
-\]
-so that no quantum probability measure~$\mu$ such that $\bar{\mu}(P)=\iota\left(\mu(P)\right)$.\qed\end{example}
+\ip{\phi}{0}=\ip{\phi}{\ps}=0
+\]
+is $\ket{2}$, but clearly $\bar{\mu}(P)\ne\iota\left(\mu_{\ket{2}}^{B}(P)\right)$.\qed\end{example}
 
@@
 \rme^{\rmi\gamma}\sin\theta
-\end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma\le2\pi$. Consider
+\end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Consider
 a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
@@
 \]
-Hence, $\bar{\mu}$ is a quantum $\mathscr{I}$-interval-valued
-probability measure. Notice that for all projection~$P$, $\mu^B_{\ket{0}}(P)\in\bar{\mu}(P)$
-implies that $\bar{\mu}(P)$ is one of quantum
-$\mathscr{I}$-interval-valued probability measures corresponding
-to $\mu^B_{\ket{0}}(P)$. However,
-$\mu^B_{\ket{0}}(P)$ can correspond
-to infinity many quantum $\mathscr{I}$-interval-valued probability
-measures by twisting the definition involving $\gamma$.\qed\end{example}
-
-\yutsung{Is there a quantum interval-value probability measure which
-corresponds to no quantum probability measure for $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $?
-This is still important because \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
-is way to small for a general case.}
+Hence, $\bar{\mu}$ is a quantum $\mathscr{I}$-interval-valued probability
+measure. Notice that for all projection~$P$, $\mu_{\ket{0}}^{B}(P)\in\bar{\mu}(P)$
+implies that $\bar{\mu}(P)$ is one of quantum $\mathscr{I}$-interval-valued
+probability measures corresponding to $\mu_{\ket{0}}^{B}(P)$. However,
+$\mu_{\ket{0}}^{B}(P)$ can correspond to infinity many quantum $\mathscr{I}$-interval-valued
+probability measures by twisting the definition involving $\gamma$.\qed\end{example}
+
+We are going to provide an quantum 4-value interval-valued probability
+measures corresponding to no quantum probability measure, i.e., $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.
+In general, we believe this kind of quantum $\mathscr{I}$-interval-valued
+probability measure exists for any finite set of interval~$\mathscr{I}$.
+
+\begin{example}[Three-dimensional quantum 4-value interval-valued
+probability measure] Given a three dimensional Hilbert space with
+an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$,
+and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}$
+defined as follow:
+\begin{enumerate}
+\item $\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$
+and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess$.
+\item When $\ket{\psi}$ is parallel to $\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+or $-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$, where
+$0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define $\bar{\mu}(\proj{\psi})=\likely$
+and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\unlikely$.
+\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$.
+\end{enumerate}
+$\bar{\mu}$ cannot correspond to any quantum probability measure
+because of the exact same reason as in example~\ref{Three-dimensional-three-value}.
+Before we verify that $\bar{\mu}$ is a quantum interval-valued probability
+measure, we need a notation for cross product. For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
+\alpha_{1}\\
+\alpha_{2}
+\end{pmatrix}$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\begin{pmatrix}\beta_{0}\\
+\beta_{1}\\
+\beta_{2}
+\end{pmatrix}$, their cross product is defined as follow.
+\[
+\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\begin{vmatrix}\alpha_{1}^{*} & \beta_{1}^{*}\\
+\alpha_{2}^{*} & \beta_{2}^{*}
+\end{vmatrix}\ket{0}+\begin{vmatrix}\alpha_{2}^{*} & \beta_{2}^{*}\\
+\alpha_{0}^{*} & \beta_{0}^{*}
+\end{vmatrix}\ket{1}+\begin{vmatrix}\alpha_{0}^{*} & \beta_{0}^{*}\\
+\alpha_{1}^{*} & \beta_{1}^{*}
+\end{vmatrix}\ket{2}\textrm{ ,}
+\]
+where $\begin{vmatrix}\alpha & \beta\\
+\alpha' & \beta'
+\end{vmatrix}=\alpha\beta'-\alpha'\beta$. Notice that we put the complex conjugate in the cross product, so
+that the result of cross product is orthogonal to $\ket{\psi}$ and
+$\ket{\phi}$. 
+\begin{eqnarray*}
+\ip{\psi\times\phi}{\psi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}=0\textrm{ ,}\\
+\ip{\psi\times\phi}{\phi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}=0\textrm{ .}
+\end{eqnarray*}
+Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
+cross product~$\ket{\psi\times\phi}$ need not be normalized as usual.
+
+To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
+it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
+for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. We can enumerate
+all possible cases as follow. 
+\begin{enumerate}
+\item When $\ket{\psi_{1}}$ is $\ket{0}$, then $\ket{\psi_{2}}$ must
+be parallel to $\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+for $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Then, 
+\begin{eqnarray*}
+ &  & \bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\\
+ & = & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}\times\psi_{2}}\right)
+\end{eqnarray*}
+\end{enumerate}
+\qed\end{example}
 

### 2016-07-13 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} keep typing...

@@
 
-\begin{example}[Three-dimensional quantum 4-value interval-valued
-probability measure] Given a three dimensional Hilbert space with
+\begin{example}{[}Three-dimensional quantum 4-value interval-valued
+probability measure{]} Given a three dimensional Hilbert space with
 an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
@@
 and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess$.
-\item When $\ket{\psi}$ is parallel to $\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
-or $-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$, where
-$0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define $\bar{\mu}(\proj{\psi})=\likely$
-and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\unlikely$.
+\item Let $\ket{\psi\left(\theta,\gamma\right)}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+and $\ket{\phi\left(\theta,\gamma\right)}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$,
+where $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$. we define
+$\bar{\mu}(\proj{\psi\left(\theta,\gamma\right)})=\ket{\phi\left(\theta,\gamma\right)}=\likely$
+and $\bar{\mu}(\mathbb{1}-\proj{\psi\left(\theta,\gamma\right)})=\bar{\mu}(\mathbb{1}-\proj{\phi\left(\theta,\gamma\right)})=\unlikely$.
 \item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$.
@@
 To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
-it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
-for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. We can enumerate
-all possible cases as follow. 
+it is sufficient to check 
+\begin{eqnarray*}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{3}}\right) & \subseteq & \bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right) & \subseteq & \bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right) & \subseteq & \bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)
+\end{eqnarray*}
+ for every orthonormal basis $\mathcal{B}=\left\{ \ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\right\} $.
+We can enumerate all possible cases as follow. 
 \begin{enumerate}
@@
 for $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Then,
-\begin{eqnarray*}
- &  & \bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\\
- & = & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}\times\psi_{2}}\right)
-\end{eqnarray*}
+\[
+\ket{\psi_{1}}\times\ket{\psi_{2}}=\begin{pmatrix}1\\
+0\\
+0
+\end{pmatrix}\times\begin{pmatrix}0\\
+\rme^{\rmi\gamma}\sin\theta\\
+\cos\theta
+\end{pmatrix}=\begin{pmatrix}0\\
+-\cos\theta\\
+\rme^{-\rmi\gamma}\sin\theta
+\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}0\\
+\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
+\cos\left(\frac{\pi}{2}-\theta\right)
+\end{pmatrix}
+\]
+WLOG, we can pick $\ket{\psi_{2}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, and $\ket{\psi_{3}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$ 
+\[
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}\times\psi_{2}}\right)=\likely=\imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
+\]
+\[
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\necess\subseteq\likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}\times\psi_{2}}\right)
+\]
+If ($0<\theta<\frac{\pi}{2}$ and $\pi\le\gamma<2\pi$) or $\theta=\frac{\pi}{2}$
+, then 
+\[
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}\times\psi_{2}}\right)=\unlikely=\imposs\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
+\]
+Similarly, when $\ket{\psi_{1}}$ is $\ket{\ps}$, equation (\ref{eq:non-additive-vectors})
+holds.
+\item When $\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}=\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}$,
+then Similarly, when $\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}=\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}$,
+equation (\ref{eq:non-additive-vectors}) holds.
 \end{enumerate}

### 2016-07-13 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} keep updating example...

--- 2016-07-11 prob.tex
@@
 and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess$.
-\item When $\ket{\psi}$ is parallel to $\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
-or $-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$, where
-$0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define $\bar{\mu}(\proj{\psi})=\likely$
-and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\unlikely$.
+\item Consider the states orthogonal to $\ket{0}$ and $\ket{\ps}$, $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+and $\ket{\ps_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
+where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Half of
+those states need special treatment, i.e., when where $0\le\theta<\frac{\pi}{2}$
+and $0\le\gamma<\pi$, we define $\bar{\mu}(\proj{0_{\theta,\gamma}^{\perp}})=\ket{\ps_{\theta,\gamma}^{\perp}}=\likely$
+and $\bar{\mu}(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}})=\bar{\mu}(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}})=\unlikely$.
 \item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$.
@@
 To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
-it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
-for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. We can enumerate
-all possible cases as follow. 
+it is sufficient to check
+\begin{equation}
+\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{3}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
+\end{aligned}
+\label{eq:non-additive-vectors}
+\end{equation}
+ for every orthonormal basis $\mathcal{B}=\left\{ \ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\right\} $.
+We are going to enumerate all possible orthonormal bases to verify
+the equations. 
 \begin{enumerate}
-\item When $\ket{\psi_{1}}$ is $\ket{0}$, then $\ket{\psi_{2}}$ must
-be parallel to $\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
-for $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Then, 
+\item When $\ket{\psi_{1}}$ is $\ket{0}$, then $\ket{\psi_{2}}$ and $\ket{\psi_{3}}$
+must be $\ket{0_{\theta,\gamma}^{\perp}}$ for some $\theta$ and
+$\gamma$. Because of 
+\[
+\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
+0\\
+0
+\end{pmatrix}\times\begin{pmatrix}0\\
+\rme^{\rmi\gamma}\sin\theta\\
+\cos\theta
+\end{pmatrix}=\begin{pmatrix}0\\
+-\cos\theta\\
+\rme^{-\rmi\gamma}\sin\theta
+\end{pmatrix}=\rme^{-\rmi\gamma}\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
+\]
+the pair $\ket{\psi_{2}}=\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\psi_{3}}=\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}$
+for ($0<\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$) or $\theta=0$
+enumerate all possible orthonormal bases. Equation (\ref{eq:non-additive-vectors})
+can be verified as follow. 
 \begin{eqnarray*}
- &  & \bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\\
- & = & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}\times\psi_{2}}\right)
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}\right)=\necess & \subseteq & \likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & = & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\imposs=\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)=\likely & = & \imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
 \end{eqnarray*}
+Similarly, when $\ket{\psi_{1}}$ is $\ket{\ps}$, equation (\ref{eq:non-additive-vectors})
+holds.
+\item The next simplest case is $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$,
+$\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$, and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
+for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, i.e., the ``otherwise''
+case. Then, equation (\ref{eq:non-additive-vectors}) can only be
+verified once. 
+\begin{eqnarray*}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)
+\end{eqnarray*}
+\item When $\ket{0}\notin\mathcal{B}$ and $\ket{0_{\theta,\gamma}^{\perp}}\in\mathcal{B}$
+for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we want to
+prove $\ket{\ps}\notin\mathcal{B}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
+for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$. 
 \end{enumerate}

### 2016-07-14 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} keep updating the example...

@@
 prove $\ket{\ps}\notin\mathcal{B}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
-for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$. 
+for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$. Therefore,
+let $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$ and arbitrary
+$\ket{\psi_{2}}$ and $\ket{\psi_{3}}$, we have
+\begin{eqnarray*}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
+\end{eqnarray*}
+In order to verify 
 \end{enumerate}

### 2016-07-14 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} finish typing example... maybe...

@@
 \usepackage[T1]{fontenc}
+\usepackage{graphicx}
 
@@
 \begin{example}[Three-dimensional quantum three-value interval-valued
-probability measure]\label{Three-dimensional-three-value} Given
+probability measure]\label{ex:three-dimensional-three-value} Given
 a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
@@
 \left(\begin{array}{c}
--\rme^{\rmi\gamma}\sin\theta\\
+-\rme^{-\rmi\gamma}\sin\theta\\
 \cos\theta
-\end{array}\right)=-\rme^{\rmi\gamma}\left(\begin{array}{c}
+\end{array}\right)=-\rme^{-\rmi\gamma}\left(\begin{array}{c}
 \cos\left(\frac{\pi}{2}-\theta\right)\\
-\rme^{\rmi\left(\pi-\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)
+\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)
 \end{array}\right)
@@
 \begin{example}[Three-dimensional quantum 4-value interval-valued
-probability measure] Given a three dimensional Hilbert space with
-an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+probability measure]\label{ex:three-dimensional-4-value} Given
+a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
 Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
@@
 and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess$.
-\item Consider the states orthogonal to $\ket{0}$ and $\ket{\ps}$, $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
-and $\ket{\ps_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
+\item Consider the states orthogonal to $\ket{0}$ and $\ket{\ps}$ respectively,
+$\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
 where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Half of
@@
 $\bar{\mu}$ cannot correspond to any quantum probability measure
-because of the exact same reason as in example~\ref{Three-dimensional-three-value}.
+because of the exact same reason as in example~\ref{ex:three-dimensional-three-value}.
 Before we verify that $\bar{\mu}$ is a quantum interval-valued probability
@@
 We are going to enumerate all possible orthonormal bases to verify
-the equations. 
+the equations, and case 1 and 2 are illustrated in figure~\ref{fig:three-dimensional-4-value}.
+\begin{figure}
+\includegraphics{\string"Three-dimensional quantum 4-value interval-valued probability measure\string".pdf}\caption{\label{fig:three-dimensional-4-value}This figure illustrates case
+1 and 2 in $\mathbb{R}^{3}$ in example~\ref{ex:three-dimensional-4-value}.
+The red and green dotted vector are $\ket{0}$ and $\ket{\ps}$ respectively.
+All possible vectors of $\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
+are drawn in the red and green circles, respectively. Within the circles,
+a vector~$\ket{\psi}$ in dotted part means $\bar{\mu}(\proj{\psi})=\likely$;
+otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
+a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
+and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
+and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
+\end{figure}
+
 \begin{enumerate}
@@
 \rme^{-\rmi\gamma}\sin\theta
+\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}0\\
+\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
+\cos\left(\frac{\pi}{2}-\theta\right)
 \end{pmatrix}=\rme^{-\rmi\gamma}\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
@@
 holds.
-\item The next simplest case is $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$,
-$\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$, and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
-for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, i.e., the ``otherwise''
-case. Then, equation (\ref{eq:non-additive-vectors}) can only be
-verified once. 
-\begin{eqnarray*}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)
-\end{eqnarray*}
-\item When $\ket{0}\notin\mathcal{B}$ and $\ket{0_{\theta,\gamma}^{\perp}}\in\mathcal{B}$
+\item When $\ket{0}\notin\mathcal{B}$ and $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$
 for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we want to
-prove $\ket{\ps}\notin\mathcal{B}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
-for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$. Therefore,
-let $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$ and arbitrary
-$\ket{\psi_{2}}$ and $\ket{\psi_{3}}$, we have
+prove $\bar{\mu}\left(\proj{\psi_{2}}\right)=\bar{\mu}\left(\proj{\psi_{3}}\right)=\unlikely$.
+Then, we have
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-In order to verify 
+In order to verify $\bar{\mu}\left(\proj{\psi_{2}}\right)=\bar{\mu}\left(\proj{\psi_{3}}\right)=\unlikely$,
+it is sufficient to prove that $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$
+implies ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or
+$\theta'=\frac{\pi}{2}$. Recall $\ip{\ps}{\ps_{\theta',\gamma'}^{\perp}}=0$.
+Hence, if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$, we
+have $\ket{\ps_{\theta',\gamma'}^{\perp}}$ parallel to $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$.
+\[
+\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
+1\\
+0
+\end{pmatrix}\times\begin{pmatrix}0\\
+\rme^{\rmi\gamma}\sin\theta\\
+\cos\theta
+\end{pmatrix}=\begin{pmatrix}\cos\theta\\
+-\cos\theta\\
+\rme^{-\rmi\gamma}\sin\theta
+\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
+\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
+\cos\left(\frac{\pi}{2}-\theta\right)
+\end{pmatrix}=\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
+\]
+Because of $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we have
+($0<\theta'=\frac{\pi}{2}-\theta<\frac{\pi}{2}$ and $\pi\le\gamma'=\pi+\gamma<2\pi$)
+or $\theta'=\frac{\pi}{2}-\theta=\frac{\pi}{2}$. Similarly, when
+$\ket{\psi_{1}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$ and $\ket{\ps}\notin\mathcal{B}$,
+equation (\ref{eq:non-additive-vectors}) holds.
+\item Finally, when $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$,
+$\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$, and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
+for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, i.e., the ``otherwise''
+case. Then, equation (\ref{eq:non-additive-vectors}) can easily be
+verified. 
+\begin{eqnarray*}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)
+\end{eqnarray*}
 \end{enumerate}

### 2016-07-14 prob.tex
discreteGBKS.bib @Article{BiglieriLops2007} Added...

@@
 
-The generalized Radon-Nikodym theorem is called Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA}
+The generalized Radon-Nikodym theorem is called Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}
 which states that, in Hilbert spaces of dimension $d\geq3$, given

### 2016-07-14 prob.tex
From: Tai, Yu-Tsung Sent: Thursday, July 14, 2016 9:33 To: Hanson, Andrew J. <hansona@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu> Subject: RE: progress?
Updated the example for {impossible, unlikely, likely, certain}, and the
relation between Radon-Nikodym derivative and the Born rule…

To Andy, should I add labels on vectors in the figure produced by
Mathematica? I didn’t find command to add labels in Graph3D through…
Thanks.

Best regards, 
Tai, Yu-Tsung (戴淯琮)
PhD student in Mathematics & Computer Science
Indiana University, Bloomington

From: Hans

@@
 pick an orthonormal basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
-such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\psi_{j}\in S}}\proj{\psi_{j}}$,
+such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in S}}\proj{\psi_{j}}$,
 where $S$ is the linear subspace $P$ projects onto. Then, a density
-matrix~$\rho$ can also be represented in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\proj{\psi_{j}}$,
+matrix~$\rho$ can also be represented in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$,
 and the Born rule becomes
 \begin{eqnarray}
-\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\psi_{j}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
+\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\ket{\psi_{j}}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
 \end{eqnarray}

### 2016-07-15 prob.tex
prob.tex Updated relating to the Radon-Nikodym theorem...

--- 2016-07-14 prob.tex
@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{thm}{Theorem}
 \newcommand{\events}{\ensuremath{\mathcal{E}}}
@@
 \begin{equation}
-\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
+\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
 \end{equation}
 where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
-Furthermore, every probability measure~$\pmeas$ can be written in
-this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}.
-This fact is a special case of the the Radon-Nikodym theorem, and
 $\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
-to the counting measure~\cite{Nikodym1930,Folland2013}. For example,
-the Radon-Nikodym derivative of $\pmeas$ in example~\ref{ex1} is:
+to the counting measure, and the Radon-Nikodym theorem states that
+the converse is also true.
+
+\begin{thm}{[}Radon-Nikodym theorem for finite probability space~\cite{Nikodym1930,Kolmogorov1950,Folland2013,Swart2013}{]}
+For every probability measure~$\pmeas$, there exists an unique Radon-Nikodym
+derivative~$\rho$ with respect to the counting measure such that
+equation (\ref{eq:Radon-Nikodym}) holds.\qed\end{thm}
+
+For example, the Radon-Nikodym derivative of $\pmeas$ in example~\ref{ex1}
+is: 
 \[
@@
 
-Actually, constructing a quantum probability measures from a density
-matrix~$\rho$ is similar to defining a classical probability measure
-by its Radon-Nikodym derivative. This can be seen more easily if we
-pick an orthonormal basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
-such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\psi_{j}\in S}}\proj{\psi_{j}}$,
-where $S$ is the linear subspace $P$ projects onto. Then, a density
-matrix~$\rho$ can also be represented in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\proj{\psi_{j}}$,
-and the Born rule becomes
-\begin{eqnarray}
-\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\psi_{j}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
-\end{eqnarray}
-which is basically the same as equation (\ref{eq:Radon-Nikodym}).
-
-The generalized Radon-Nikodym theorem is called Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA}
-which states that, in Hilbert spaces of dimension $d\geq3$, given
-a probability measure $\mu$, there exist a mixed state~$\rho$ that
-induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+Recall that the Radon-Nikodym theorem claims every probability measure
+has an unique Radon-Nikodym derivative with respect to the counting
+measure. When we generalize the Radon-Nikodym theorem to quantum,
+the mixed state~$\rho$ can be considered as the Radon-Nikodym derivative
+with respect to the trace~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007},
+and gives Gleason's theorem: in Hilbert spaces of dimension $d\geq3$,
+given a quantum probability measure $\mu$, there exist a mixed state~$\rho$
+that induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
@@
 
-\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$ of dimension
-$d\geq3$, for any function~$\mu:\events\rightarrow[0,1]$ satisfying the conditions
-listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist
-an unique mixed state~$\rho$ such that $\mu=\mu^B_{\rho}$.\end{cor}
+\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$ of
+dimension $d\geq3$, for any function~$\mu:\events\rightarrow[0,1]$
+satisfying the conditions listed in lemma~\ref{lem:quantumProbabilityMeasure},
+there exists an unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{cor}
 

### 2016-07-17 prob.tex
prob.tex \subsection{Interval-valued probability measures} starting updating...

@@
 \end{equation}
-where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
+where $\rho:\Omega\rightarrow[0,1]$ and $\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)=1$.
 $\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
@@
 
-As motivated above, an event $E_1$ may have an interval of probability
-$[l_1,r_1]$. Assume that another disjoint event $E_2$ has interval
-probability $[l_2,r_2]$, what is the interval probability of the event
-$E_1 \cup E_2$? The answer is somewhat subtle: although it is possible
-to use the sum of the intervals $[l_1+l_2,r_1+r_2]$ as the combined
-probability, one can do find a much tighter interval if information
-\emph{against} the event (i.e., information about the complement
-event) is also taken into consideration. Formally, for a general event
-$E$ with probability $[l,r]$, the evidence that
-contradicts $E$ is an evidence supporting the complement of $E$. The
-complement of $E$ must therefore have probability
-$\left[1-r,1-l\right]$ which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
-where the preposing $\mathscr{I}$ specifies we subtracts intervals. Given
-a collection of intervals $\mathscr{I}$, an
-$\mathscr{I}$--interval-valued probability measure is a function
-$\bar{\mu} : \events \rightarrow \mathscr{I}$ such
-that~\cite{JamisonLodwick2004}:\footnote{Notice that the belief function defined by Dempster~\cite{Dempster1967}
-and Shafer~\cite{Shafer1976} is a special case of the interval-valued
-probability measures. Depending on how quantum interval probability goes, this
-section may be specialized to Dempster and Shafer only.}
+As motivated above, an event $E_{1}$ may have an interval of probability
+$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
+interval probability $[l_{2},r_{2}]$, what is the interval probability
+of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
+it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
+as the combined probability, one can do find a much tighter interval
+if information \emph{against} the event (i.e., information about the
+complement event) is also taken into consideration. Formally, for
+a general event $E$ with probability $[l,r]$, the evidence that
+contradicts $E$ is an evidence supporting the complement of $E$.
+The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
+which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
+where the preposing $\mathscr{I}$ specifies we subtracts intervals.
+Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
+probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that~\cite{JamisonLodwick2004}:\footnote{The lower and upper probability defined by Dempster~\cite{Dempster1967}
+and the belief function defined by Shafer~\cite{Shafer1976} is a
+special case of the interval-valued probability measures. } 
 \begin{itemize}

### 2016-07-17 prob.tex
prob.tex \subsection{Interval-valued probability measures} prob.tex

@@
 probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that~\cite{JamisonLodwick2004}:\footnote{The lower and upper probability defined by Dempster~\cite{Dempster1967}
-and the belief function defined by Shafer~\cite{Shafer1976} is a
-special case of the interval-valued probability measures. } 
+such that~\cite{JamisonLodwick2004}:\footnote{The lower probability (belief) and the upper probability (plausibility)
+defined by Dempster~\cite{Dempster1967} and Shafer~\cite{Shafer1976}
+is a special case of the left-end and right-end of the interval-valued
+probability measures. } 
 \begin{itemize}

### 2016-07-18 prob.tex
prob.tex \subsection{Interval-valued probability measures} finishing checking footnote...

--- 2016-07-17 prob.tex
@@
 probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that~\cite{JamisonLodwick2004}:\footnote{The lower and upper probability defined by Dempster~\cite{Dempster1967}
-and the belief function defined by Shafer~\cite{Shafer1976} is a
-special case of the interval-valued probability measures. } 
+such that~\cite{JamisonLodwick2004}:\footnote{The lower probability (belief) and the upper probability (plausibility)
+defined by Dempster~\cite{Dempster1967} and Shafer~\cite{Shafer1976}
+is a special case of the left-end and the right-end of the interval-valued
+probability measure, and the right-end of the interval-valued probability
+measure is a special case of capacity~\cite{Choquet1954,Graf1980,Goodman2013}.} 
 \begin{itemize}

### 2016-07-18 prob.tex
prob.tex \subsection{Interval-valued probability measures} expending a footnote...

@@
 more evidence knowing the aggregate event.\qed\end{example}
-\footnote{\yutsung{The Radon-Nikodym Theorem for interval-valued
-probability?\cite{GilboaSchmeidler1994}?}}
+
+Because a probability measure~$\pmeas:\events\rightarrow[0,1]$ can
+be simplified to its Radon-Nikodym derivative~$\rho:\Omega\rightarrow[0,1]$
+by the Radon-Nikodym theorem, people have tried to find a Radon-Nikodym
+Theorem for the interval-valued probability measure. One possible
+approach is to consider the inverse Möbius transform of $\bar{\mu}:\events\rightarrow\mathscr{I}$~\cite{GilboaSchmeidler1994,Goodman2013}.
+Although the inverse Möbius transform can always be defined, the domain
+of the inverse Möbius transform of of $\bar{\mu}$ is still the event
+space~$\events$ so that it does not simplify an interval-valued
+probability measure to a function from the same space~$\Omega$.
+The other approach tried to only consider the Radon-Nikodym derivative
+between two interval-valued probability measures with a special relation
+called the strong decomposition property~\cite{Choquet1954,Graf1980,Goodman2013}.
+However, only the real-valued probability measures could have a Radon-Nikodym
+derivative with respect to the counting measure\footnote{\yutsung{Need to verify a concrete example.}}.
+In summary, there is no satisfactory Radon-Nikodym Theorem to simplify
+interval-valued probability measures~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+to their Radon-Nikodym derivative~$\bar{\rho}:\Omega\rightarrow\mathscr{I}$.
 

### 2016-07-19 prob.tex
prob.tex \subsection{Real-Valued Probability Spaces} updated...

@@
 $\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
-to the counting measure, and the Radon-Nikodym theorem states that
-the converse is also true.
-
-\begin{thm}{[}Radon-Nikodym theorem for finite probability space~\cite{Nikodym1930,Kolmogorov1950,Folland2013,Swart2013}{]}
+to the counting measure, or just called the Radon-Nikodym derivative
+of $\pmeas$ because we are always with respect to the counting measure.
+The Radon-Nikodym theorem states that the converse is also true.
+
+\begin{thm}[Radon-Nikodym theorem for finite probability space~\cite{Nikodym1930,Kolmogorov1950,Folland2013,Swart2013}]
 For every probability measure~$\pmeas$, there exists an unique Radon-Nikodym
-derivative~$\rho$ with respect to the counting measure such that
-equation (\ref{eq:Radon-Nikodym}) holds.\qed\end{thm}
+derivative~$\rho$ such that equation~(\ref{eq:Radon-Nikodym})
+holds.\qed\end{thm}
 

### 2016-07-21 prob.tex
prob.tex Upgrading to BibLaTeX to handle translated sources correctly...
prob.tex Fix the bug about using BibTeX with BibLaTeX...
prob.tex Fix BibLaTeX so that it works when import to LyX...
prob.tex \subsection{Real-Valued Probability Spaces} Updated...

@@
 \documentclass{article}
+\usepackage[ backend=biber,sorting=none]{biblatex}
+\addbibresource{discreteGBKS.bib}
 \usepackage{fullpage}
@@
 $\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
-to the counting measure, or just called the Radon-Nikodym derivative
-of $\pmeas$ because we are always with respect to the counting measure.
-The Radon-Nikodym theorem states that the converse is also true.
-
-\begin{thm}[Radon-Nikodym theorem for finite probability space~\cite{Nikodym1930,Kolmogorov1950,Folland2013,Swart2013}]
+to the counting measure~\cite{Nikodym1930,Folland2013}, or just
+called the Radon-Nikodym derivative of $\pmeas$ because we are always
+with respect to the counting measure. The Radon-Nikodym theorem states
+that the converse is also true.
+
+\begin{thm}[Radon-Nikodym theorem for finite probability space~\cite{Kolmogorov1950,Swart2013}]
 For every probability measure~$\pmeas$, there exists an unique Radon-Nikodym
@@
 
-\bibliographystyle{unsrt}
-\bibliography{discreteGBKS}
+\printbibliography
 

### 2016-07-21 prob.tex
prob.tex Keep updating and fight with BibLaTeX with LyX and TeXlipse >"<

@@
 \usepackage[ backend=biber,sorting=none]{biblatex}
-\addbibresource{discreteGBKS.bib}
+\bibliography{discreteGBKS}
 \usepackage{fullpage}
@@
 replaced by the density matrix. If there is no easy Radon-Nikodym
-theorem for classical interval-valued probability measure (\cite{GilboaSchmeidler1994}
-or other sources. Need verify!), it is natural that there is no easy
-Gleason's theorem for quantum interval-valued probability measure...
+theorem for classical interval-valued probability measure, it is natural
+that there is no easy Gleason's theorem for quantum interval-valued
+probability measure...
 
@@
 
-In previous section, the probability of each event is known
-a priori. In reality, we seldom know much about events, but we could still assume
-each event~$E$ has a probability~$\pmeas(E)$. If we want to know the
-probability~$\pmeas(E)$, we could run $N$ independent trials. Let $x_{i}$ denote
-whether the event~$E$ occurs in the $i$-th trial or not, then $\pmeas(E)$ could
-be approximated to given accuracy by the relative
-frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability converging to one as
-$N$ goes to infinity. This fact is called the law of large
-numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
+In previous section, the probability~$\pmeas(E)$ of each event~$E$
+is known a priori. In reality, although the exact value of $\pmeas(E)$
+may not be known, we could still assume each event has a probability.
+If we want to know its value, we can run $N$ independent trials.
+Let $x_{i}$ denote whether the event~$E$ occurs in the $i$-th
+trial or not, then $\pmeas(E)$ could be approximated to given accuracy
+by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability
+converging to one as $N$ goes to infinity. This fact is called the
+law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
 

### 2016-07-21 prob.tex
prob.tex \subsection{Interval-valued probability measures} updating...

@@
 If we were to equate $\bar{\mu}(\Omega)$ with the sum of the individual
-probabilities we would get that
-$\bar{\mu}(\Omega) = \left[\frac{1}{2},\frac{3}{2}\right]$. However,
-using the fact that $\bar{\mu}(\emptyset)=\imposs$, we have
-$\bar{\mu}\left(\Omega\right)=1-\bar{\mu}\left(\emptyset\right)=\necess=[1,1]$. This
-interval is tighter and a better estimate for the probability of the
-event $\Omega$ and of course it is contained in
-$[\frac{1}{2},\frac{3}{2}]$. However it is only possible to exploit
-the information about the complement when all four events are
-combined. Thus the $\subseteq$-condition allows us to get an estimate
-for the combined event from each of its constituents and then gather
-more evidence knowing the aggregate event.\qed\end{example}
-
-Because a probability measure~$\pmeas:\events\rightarrow[0,1]$ can
-be simplified to its Radon-Nikodym derivative~$\rho:\Omega\rightarrow[0,1]$
-by the Radon-Nikodym theorem, people have tried to find a Radon-Nikodym
-Theorem for the interval-valued probability measure. One possible
-approach is to consider the inverse Möbius transform of $\bar{\mu}:\events\rightarrow\mathscr{I}$~\cite{GilboaSchmeidler1994,Goodman2013}.
-Although the inverse Möbius transform can always be defined, the domain
-of the inverse Möbius transform of of $\bar{\mu}$ is still the event
-space~$\events$ so that it does not simplify an interval-valued
-probability measure to a function from the same space~$\Omega$.
-The other approach tried to only consider the Radon-Nikodym derivative
-between two interval-valued probability measures with a special relation
-called the strong decomposition property~\cite{Choquet1954,Graf1980,Goodman2013}.
-However, only the real-valued probability measures could have a Radon-Nikodym
-derivative with respect to the counting measure\footnote{\yutsung{Need to verify a concrete example.}}.
-In summary, there is no satisfactory Radon-Nikodym Theorem to simplify
-interval-valued probability measures~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-to their Radon-Nikodym derivative~$\bar{\rho}:\Omega\rightarrow\mathscr{I}$.
+probabilities, we would get that $\bar{\mu}(\Omega)=\left[\frac{1}{2},\frac{3}{2}\right]$.
+However, using the fact that $\bar{\mu}(\emptyset)=\imposs$, we have
+$\bar{\mu}\left(\Omega\right)=1-\bar{\mu}\left(\emptyset\right)=\necess=[1,1]$.
+This interval is tighter and a better estimate for the probability
+of the event $\Omega$, and of course it is contained in $[\frac{1}{2},\frac{3}{2}]$.
+However it is only possible to exploit the information about the complement
+when all four events are combined. Thus the $\subseteq$-condition
+allows us to get an estimate for the combined event from each of its
+constituents and then gather more evidence knowing the aggregate event.\qed\end{example}
+
+In contrast to real-valued probability measure, there is no easy Radon-Nikodym
+theorem to simplify an interval-valued probability measure to its
+Radon-Nikodym derivative. So far the Radon-Nikodym Theorems found
+for the interval-valued probability measure are either too restricted
+to apply to all interval-valued probability measures~\cite{Choquet1954,Graf1980,Goodman2013}
+or corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+to another set function~$\bar{\rho}:\events\rightarrow\bar{\mathscr{I}}$
+which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman2013}.
 

### 2016-07-22 prob.tex
From: Tai, Yu-Tsung Sent: Friday, July 22, 2016 3:15 To: Hanson, Andrew J. <hansona@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Amr A. Sabry (sabry@indiana.edu) <sabry@indiana.edu> Subject: RE: Yu-Tsung made changes in your shared folders (fwd)
I added a citation to Choquet's paper, and I put his paper in Dropbox
because I think it is too big to put in ShareLaTeX...

Last week, we discussed Gleason's theorem is a generalization of the
Radon-Nikodym theorem in classical case, and we associate a quantum
real-valued and interval-valued probability measures with a "belong to"
relation...

@@
 which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman2013}.
+
+Although there is no easy Radon-Nikodym theorem, an interval-valued
+probability measure can still be understood by its relation with real-valued
+probability measures, like we constructed example~\ref{ex3} from
+example~\ref{ex1}. In general, a \emph{core} of an interval-valued
+probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is
+a set of real-valued probability measures~$\pmeas:\events\rightarrow[0,1]$
+such that $\pmeas\left(E\right)\in\bar{\mu}\left(E\right)$ for all
+$E\in\events$~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
+
+\yutsung{The following theorem proved that a wide variety of interval-valued
+probability measures can be associated with real-valued probability
+measures.
+
+\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
+Every convex interval-valued probability measure has a nonempty core,
+where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
+and $l\left(E_{1}\cup E_{2}\right)\le l\left(E_{1}\right)+l\left(E_{2}\right)-l\left(E_{1}\cap E_{2}\right)$
+for all $E_{1},E_{2}\in\events$.\qed\end{thm}
+
+In particular, Dempster-Shafer probability measures are all convex
+and have nonempty cores. Need to verify whether general interval-valued
+probability measures must have a core or find a counterexample.}
 

### 2016-07-24 prob.tex
prob.tex Fix a typo...
prob.tex \subsection{Quantum Probability Measures} Updates...

@@
 
-Based on quantum events are projection operators, operations and properties of
-quntum events can be written in terms of those of operators.
+Because quantum events are projection operators, operations and properties
+of quantum events can be written in terms of those of operators.
 
@@
 
-A quantum probability measure can be easily constructed by states
-according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
+Recall that classical probability measure can be constructed from
+its Radon-Nikodym derivative. Similarly, a quantum probability measure
+can be easily constructed by states according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
 For each pure normalized ($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$,
@@
 
-Recall that the Radon-Nikodym theorem claims every probability measure
-has an unique Radon-Nikodym derivative with respect to the counting
-measure. When we generalize the Radon-Nikodym theorem to quantum,
-the mixed state~$\rho$ can be considered as the Radon-Nikodym derivative
-with respect to the trace~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007},
-and gives Gleason's theorem: in Hilbert spaces of dimension $d\geq3$,
-given a quantum probability measure $\mu$, there exist a mixed state~$\rho$
-that induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+Notice that the mixed state~$\rho$ is really a generalization of
+Radon-Nikodym derivative if we pick a basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
+such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in S}}\proj{\psi_{j}}$,
+where $S$ is the linear subspace $P$ projects onto. By representing
+the density matrix~$\rho$ in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$,
+the Born rule becomes
+\begin{eqnarray}
+\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\ket{\psi_{j}}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
+\end{eqnarray}
+ which is basically the same as equation (\ref{eq:Radon-Nikodym}).
+
+Then, the Radon-Nikodym theorem is generalized quantum~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
+If the mixed state~$\rho$ is considered as the Radon-Nikodym derivative
+with respect to the trace, we have Gleason's theorem: in Hilbert spaces
+of dimension $d\geq3$, given a quantum probability measure $\mu$,
+there exist a mixed state~$\rho$ that induces such a measure using
+the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
@@
 0 & \textrm{, if }P=\proj{\ms}\textrm{ ;}\\
-\mu^B_{\ket{0}}(P) & \textrm{, otherwise.}
+\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
 \end{cases}
 \]
-On one hand, $\mu$ is a quantum probability measure. Because $\mu$ is almost
-the same as a quantum probability measure~$\mu^B_{\ket{0}}$, we only
-need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
+On one hand, $\mu$ is a quantum probability measure. Because $\mu$
+is almost the same as a quantum probability measure~$\mu_{\ket{0}}^{B}$,
+we only need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
 \[
@@
 \[
-\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
-\]
-However, $\mu^B_{\rho}(P)=1$ if and only if $\rho$ represents
-a pure state and $\rho=P$. \qed\end{example}
+\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ ,}
+\]
+and $\mu_{\rho}^{B}(P)=1$ if and only if $\rho$ represents a pure
+state and $\rho=P$. \qed\end{example}
 

### 2016-07-24 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} cleaning up...

@@
 probability measures, like we constructed example~\ref{ex3} from
-example~\ref{ex1}. In general, a \emph{core} of an interval-valued
-probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is
-a set of real-valued probability measures~$\pmeas:\events\rightarrow[0,1]$
-such that $\pmeas\left(E\right)\in\bar{\mu}\left(E\right)$ for all
-$E\in\events$~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
+example~\ref{ex1}. In general, this idea can be generalized to the
+following definition of core.
+
+\begin{definition}[Core of Interval-valued Probability Measure~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}]\label{def:CoreInterval-valuedProbability}
+A \emph{core} of an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is the set 
+\[
+\mathrm{core}\left(\bar{\mu}\right)=\left\{ \pmeas:\events\rightarrow[0,1]\textrm{ probability measure}\middle|\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\forall E\in\events\right\} \textrm{ .}
+\]
+\qed\end{definition}
 
@@
 %%%%%
-\subsection{Quantum Probability Measures}
+\subsection{Quantum Real-valued Probability Measures}
 
@@
 
-Notice that if the last condition is replaced by the equal sign, these
-conditions will be exactly the same as the conditions in lemma~\ref{lem:quantumProbabilityMeasure}
-which is equivalent to the Born rule as in corollary~\ref{cor:Gleason's}.
-Therefore, it is reasonable to believe these conditions should be
-equivalent to a interval-valued Born rule.
-
-When we pick $\mathscr{I}=\left\{ \left[x,x\right]\middle|x\in\left[0,1\right]\right\} $,
-for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
-we can define a corresponding quantum \emph{$\mathscr{I}$}-interval-valued
-probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-by $\bar{\mu}\left(P\right)=\left[\mu\left(P\right),\mu\left(P\right)\right]$.
-In this sense, every usual quantum probability measure can be considered
-as a quantum interval-valued probability measure. There are more interesting
-examples as we now show.
+Similar to the classical interval-valued probability measure, a quantum
+interval-valued probability measure can be constructed from a real-valued
+one.
 
@@
 
-Although $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ maps every
-quantum probability measure to a quantum interval-valued probability
-measure, there is a quantum \emph{$\mathscr{I}$}-interval-valued
-probability measure which does not come from a quantum probability
-measure.
+When a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+constructed from a real-valued one~$\mu:\events\rightarrow\left[0,1\right]$,
+we should say $\mu$ is in the core of $\bar{\mu}$ according to the
+following definition of core.
+
+\begin{definition}[Core of Quantum Interval-valued Probability
+Measure]\label{def:CoreQuantumInterval-valuedProbability} A \emph{core}
+of a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is the set 
+\[
+\mathrm{core}\left(\bar{\mu}\right)=\left\{ \mu:\events\rightarrow[0,1]\textrm{ quantum probability measure}\middle|\mu\left(P\right)\in\bar{\mu}\left(P\right)\forall P\in\events\right\} \textrm{ .}
+\]
+\qed\end{definition}
+
+Because the classical interval-valued probability measure has no easy
+Radon-Nikodym theorem, the quantum one should not have a easy Gleason's
+theorem. Nevertheless, the core of $\bar{\mu}$ provides an instructive
+way to understand $\bar{\mu}$, and the core may exist even without
+a natural $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ as in the
+example~\ref{ex:One-qubit-quantum-interval} in appendix. However,
+in contrast to the classical case, we have the following theorem.
+
+\begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
+There is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.\qed\end{thm}
+
+This theorem can be proved by the following example, and a more sophisticated
+example is example~\ref{ex:three-dimensional-4-value} in appendix.
 
@@
 
-Notice that in the above two examples, quantum interval-valued probability
-measures are all come from quantum probability measures because the
-numbers in $\left[0,1\right]$ can be mapped to the chosen intervals~$\mathscr{I}$
-naturally. This is not always the case. For example, if $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\printbibliography
+
+\appendix
+
+\section{Examples for Quantum Interval-valued Probability Measures}
+
+The following example verify the core of a quantum interval-valued
+probability measure is nonempty even if there is no natural correspondence.
+For example, if $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
 there is no natural way to map from $\frac{1}{2}$, as both $\frac{1}{2}\in\left[0,\frac{1}{2}\right]=\unlikely$
@@
 
-\begin{example}[One-qubit quantum interval-valued probability measure]
+\begin{example}[One-qubit quantum interval-valued probability measure]\label{ex:One-qubit-quantum-interval}
 Given a two dimensional Hilbert space, a vector $\ket{\psi}$ can
@@
 \qed\end{example}
-
-\amr{
-We can use DQC if we have some kind of topology (distances). The idea
-will be that we want to prepare state PSI but because of errors etc we
-prepare a close state. Well the next closest state will be the next
-state in our discrete grid. I am sure that a state that's very close
-to PSI can involve some wrapping around.
-}
-
-\yutsung{About continuity, one of the confusion comes from the subtle
-correspondence between the measurement processes and observables.
-Consider the following observables and their measurement processes:
-\begin{itemize}
-\item For any $x\in\mathbb{R}$, consider the observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$.
-Except $x=1$, given the system in the state~$\ket{\phi}$, we can
-denote the measurement process for $\mathbf{O}_{x}$ by ${\cal O}_{x}$:
-\begin{enumerate}
-\item With probability~$\mu_{\phi}\left(\proj{1}\right)$, return the measurement
-result~$1$ with the post-measurement state~$\ket{1}$;
-\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
-result~$0$ with the post-measurement state~$\ket{0}$;
-\item With probability~$\mu_{\phi}\left(\proj{-1}\right)$, return the
-measurement result~$x$ with the post-measurement state~$\ket{-1}$.
-\end{enumerate}
-\item The observable operator~$\mathbf{J}_{z}^{2}=\proj{1}+\proj{-1}$,
-and its measurement process~${\cal J}_{z}^{2}$:
-\begin{enumerate}
-\item With probability~$\mu_{\phi}\left(\proj{1}+\proj{-1}\right)$, return
-the measurement result~$1$ with the post-measurement state~$\ket{1}\ip{1}{\phi}+\ket{-1}\ip{-1}{\phi}$;
-\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
-result~$0$ with the post-measurement state~$\ket{0}$.
-\end{enumerate}
-\end{itemize}
-As an operator, it is clear that $\lim_{x\rightarrow1}\mathbf{O}_{x}=\mathbf{J}_{z}^{2}$,
-and we should have $\lim_{x\rightarrow1}{\cal O}_{x}={\cal O}_{1}$
-for the measurement process. However, it is not obvious why ${\cal O}_{1}={\cal J}_{z}^{2}$.
-Although they have the same probability for the measurement results,
-but their post-measurement states are different. This might be a defect
-of representing a measurement process as an observable. As $\mathbf{O}_{1}=\mathbf{J}_{z}^{2}$,
-there is no observable corresponding to the measurement process~${\cal O}_{1}$.}
-
-\amr{the rest needs cleaning up and perhaps does not even belong in
-  this section}
-
-Although it seems that we need an infinite long table to specify the
-quantum probability measure~$\mu$, our $\mu$ is actually
-given by a simple formula~$\melement{0}{P}$. In general, Born discovered
-each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
-induces a probability measure $\mu^B_{\psi}:\qevents\rightarrow[0,1]$
-on the space of events defined for any event $P\in\qevents$ as follows~\cite{Born1983,Mermin2007}:
-\begin{equation}
-\mu^B_{\psi}(P)=\frac{\melement{\psi}{P}}{\ip{\psi}{\psi}}\label{eq:Born}
-\end{equation}
-The Born rule satisfies the following properties:
-\begin{itemize}
-\item It can be extend to mixed states. Given a mixed state represented
-by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
-where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
-the Born rule can be extended to $\rho$ by 
-\begin{eqnarray}
-\mu^B_{\rho}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\Psi_{j}}\left(P\right)\textrm{ .}\label{BornRule.mixed}
-\end{eqnarray}
-Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
-is a classical probability space. Therefore, when we discretize the
-Hilbert space later, we may need to discretize this probability space
-as well.
-\item $\mu^B_{\rho}$ is a probability measure for all mixed state~$\rho$.
-\item $\ip{\psi}{\phi}=0\Leftrightarrow\mu^B_{\psi}\left(\proj{\phi}\right)=0$.
-\item $\mu^B_{\psi}\left(P\right)=\mu^B_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}P\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
-$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
-\end{itemize}
-
-Naturally, we may ask: is every probability measure induced from a
-state by the Born rule? The answer is yes by Gleason's theorem when
-the dimension~$\ge3$~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
-Furthermore, a simple corollary of Gleason's theorem can show the
-Born rule is the unique function satisfying conditions 1. to 3.
-\begin{cor}
-The Born rule is the unique function satisfying conditions 1. to 3.
-\end{cor}
-\begin{proof}
-Assume there is another function $\mu^{\prime B}$ such that $\mu^{\prime B}_{\rho}$
-is a quantum probability measure for all mixed state~$\rho$. We
-are going to prove $\mu^{\prime B}=\mu^B$.
-
-Fix a pure normalized state $\phi$, $\mu^{\prime B}_{\phi}$ is a quantum
-probability measure by condition 2. By Gleason's theorem, there is
-a mixed state ~$\rho'$, such that $\mu^{\prime B}_{\phi}\left(P\right)=\Tr\left(\rho'P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P\right)$
-for all event $P$.
-
-Consider the event $P'=\mathbb{1}-\proj{\phi}$, we have 
-\begin{eqnarray*}
-0 & \overset{\textrm{Condition 3}}{=} & \mu^B_{\phi}\left(P'\right)\\
- & = & \sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P'\right)
-\end{eqnarray*}
-Because $q_{j}>0$, we have $\mu^B_{\psi_{j}}\left(P\right)=0$,
-i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $P'$.
-However, the only subspace orthogonal to $P'$ is span by $\ket{\phi}$.
-Hence, $\mu^{\prime B}_{\phi}=\mu^B_{\phi}$.
-\end{proof}
-
-% If there may be more than one probability measure, we will discuss
-% whether we will keep using the Born rule (\ref{eq:Born}) or there
-% is another formula $\mu^B$ such that $\mu^B_{\psi}$
-% is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
-
-% Then, Gleason's theorem states given a probability measure $\mu$
-% there is a mixed state $\ket{\psi}$ such that $\mu=\mu_{\psi}$,
-% i.e., the Born rule is surjective\footnote{If we extend the domain of $\mu_{\psi}$ including the mixed states.}.
-% For any other formula~$\mu^B$, we can ask whether $\mu^B$
-% is surjective as well.
-
-% Obviously, we don't want arbitrarily assign a state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
-% with a probability measure $\mu^B_{\psi}$, for example, assigning
-% every state to the same probability measure. We want $\mu^B_{\psi}$
-% satisfying the following properties with some physical meaning:
-% \begin{itemize}
-% \item $\ip{\psi}{\phi}=0\Leftrightarrow\mu^B_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
-% where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
-% is impossible for $\mathscr{L}_{2}=\left\{ \imposs,\poss\right\} $. 
-% \item $\mu^B_{\psi}\left(\proj{\phi}\right)=\mu^B_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
-% $\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
-% map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
-% \end{itemize}
-% And the results can be summarized in the following table:\\
-% \center{ %
-% \begin{tabular}{>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}>{\raggedright}m{0.2\columnwidth}}
-% \hline 
-% State space $\Hilb$  & Probability values  & Is there a $\mu^B$ satisfying the given conditions?  & Is the $\mu^B$ surjective?\tabularnewline
-% \hline 
-% \hline 
-% $\C^{d}$ for $d\ge3$  & $\left[0,1\right]$  & Yes  & Yes\tabularnewline
-% \hline 
-% $\C^{d}$  & $\mathscr{L}_{2}$  & Yes  & No\tabularnewline
-% \hline 
-% $\ffzd{p^{2}}$for $d\ge3$ except $d=p=3$  & $\left[0,1\right]$  & No  & \tabularnewline
-% \hline 
-% $\ffzd{p^{2}}$  & $\mathscr{L}_{2}$  & Yes & No\tabularnewline
-% \hline 
-% \end{tabular}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{All Continuous or All Discrete}
-
-Before we turn to the main part of the paper, we quickly dismiss the
-possibility of having one but not the other of the discrete
-variations. Specifically, it is impossible to maintain the Hilbert
-space and have a finite set-valued probability measure and it is also
-impossible to have a vector space constructed over a finite field with
-a real-valued probability measure.
-
-%%%
-\subsection{Hilbert Space with Finite Set-Valued Probability Measure}
-
-However, there is a $\mathscr{L}_{2}$-valued probability measure
-\[
-\hat{\mu}_{1}\left(P\right)=\begin{cases}
-\imposs & \textrm{, if }P=\proj{+};\\
-\bar{\mu}(P) & \textrm{, otherwise.}
-\end{cases}
-\]
-such that $\hat{\mu}_{1}\ne\bar{\mu}_{\psi}$ for all mixed state
-$\ket{\psi}$.
-
-%%%
-\subsection{Discrete Vector Space with Real-Valued Probability Measure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\printbibliography
 

### 2016-07-25 prob.tex
prob.tex Fix citation...

@@
 and uncomputable real interval $[0,1]$. This interval includes numbers
-like $0.h_1h_2h_3\ldots$ where $h_i$ is 1 or 0 depending on whether
-Turing machine $M_i$ halts or not. Such numbers cannot be
-computed. This interval also includes numbers like $\frac{\pi}{4}$
+like $0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending
+on whether Turing machine $M_{i}$ halts or not. Such numbers cannot
+be computed. This interval also includes numbers like $\frac{\pi}{4}$
 which can only be computed with increasingly large resources as the
-precision increases.
-% \yutsung{Check the meaning of the ``computing $\frac{\pi}{4}$'', because
+precision increases. % \yutsung{Check the meaning of the ``computing $\frac{\pi}{4}$'', because
 % Bailey Borwein Plouffe formula can computing the $n$th binary digit of $\pi$ 
@@
 Therefore, in a resource-aware computational or experimental setting,
-it is more appropriate to consider probability measures that map
-events to a set of elements computable with a fixed set of
-resources. We expand on this observation and then consider
-%% two approaches from the literature: set-valued probability
+it is more appropriate to consider probability measures that map events
+to a set of elements computable with a fixed set of resources. We
+expand on this observation and then consider %% two approaches from the literature: set-valued probability
 %% measures~\cite{Artstein1972,PuriRalescu1983} and 
-interval-valued probability
-measures~\cite{Dempster1967,Shafer1976,JamisonLodwick2004}
-in detail.\footnote{There is another possible approach that can be
-  used to split the real interval $[0,1]$ into a collection of
-  subsets~\cite{PuriRalescu1983} \amr{need to explain the
-    connection and why we are not using it.}}
+interval-valued probability measures~\cite{JamisonLodwick2004} in
+detail.\footnote{There is another possible approach that can be used to split the real
+interval $[0,1]$ into a collection of subsets~\cite{PuriRalescu1983}
+\amr{need to explain the connection and why we are not using it.}}
 
@@
 is a special case of the left-end and the right-end of the interval-valued
-probability measure, and the right-end of the interval-valued probability
-measure is a special case of capacity~\cite{Choquet1954,Graf1980,Goodman2013}.} 
+probability measure. The right-end of the interval-valued probability
+measure is a special case of capacity~\cite{Choquet1954,Graf1980,Goodman2013}.
+The left-end of the interval-valued probability measure is a special
+case of game~\cite{Shapley1965}.} 
 \begin{itemize}

### 2016-07-27 prob.tex
prob.tex Fix typos and citations...

@@
 is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
-and $l\left(E_{1}\cup E_{2}\right)\le l\left(E_{1}\right)+l\left(E_{2}\right)-l\left(E_{1}\cap E_{2}\right)$
+and $l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)$
 for all $E_{1},E_{2}\in\events$.\qed\end{thm}
@@
 
-\begin{definition}[Ideal Measurement; Complement;
-Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
+\begin{definition}[Ideal Measurement; Complement; Commutativity]~ 
 \begin{itemize}
 \item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
-measurement} if it is a partition of the identity, i.e.,
-$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
+measurement} if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$~\cite{Swart2013}. 
 \item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
-is also a projection operator, called \emph{complement}. It is orthogonal to $P$,
-and corresponds to the complement event~$\Omega\backslash E$
-in classical probability.
+is also a projection operator, called \emph{complement}. It is orthogonal
+to $P$, and corresponds to the complement event~$\Omega\backslash E$
+in classical probability~\cite{Griffiths2003}. 
 \item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
 The product of two projection operators~$P_{1}P_{2}$ is also a projection
-operator if and only if they commute. This corresponds to the classical intersection
-between events. 
+operator if and only if they commute. This corresponds to the classical
+intersection between events~\cite{peres1995quantum}. 
 \end{itemize}

### 2016-07-28 prob.tex
"K. Jamison, W. Lodwick, Interval-Valued Probability in the Analysis of Problems Containing a Mixture of Fuzzy, Possibilisitic and Interval Uncertainty.pdf" "W. Lodwick, Interval and Fuzzy Analysis A Unified Approach.pdf" Added...

@@
 %% measures~\cite{Artstein1972,PuriRalescu1983} and 
-interval-valued probability measures~\cite{JamisonLodwick2004} in
-detail.\footnote{There is another possible approach that can be used to split the real
+interval-valued probability measures~\cite{Weichselberger2000,JamisonLodwick2004}
+in detail.\footnote{There is another possible approach that can be used to split the real
 interval $[0,1]$ into a collection of subsets~\cite{PuriRalescu1983}

### 2016-07-28 prob.tex
prob.tex \subsection{Quantum Events} updating definition...

@@
 \begin{itemize}
-\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
-measurement} if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$~\cite{Swart2013}. 
+\item A set of projections $P_{i}$ is called an \emph{ideal measurement}
+if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
+In this case, projections $P_{i}$ must be mutually orthogonal~\cite{Griffiths2003}.
 \item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
@@
 operator if and only if they commute. This corresponds to the classical
-intersection between events~\cite{peres1995quantum}. 
+intersection between events~\cite{peres1995quantum,Griffiths2003}. 
+\item For two commuting projection operators $P_{1}$ and $P_{2}$, their
+\emph{disjunction}~$P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}$
+is defined to be $P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\tensor*[_{\mathscr{O}}]{-}{}P_{1}P_{2}$~\cite{Griffiths2003}. 
 \end{itemize}

### 2016-07-28 prob.tex
prob.tex \subsection{Interval-valued probability measures} Add citation

@@
 \newcommand{\rmi}{\mathrm{i}}
+\usepackage{verbatim}
 
@@
 \begin{definition}[Core of Interval-valued Probability Measure~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}]\label{def:CoreInterval-valuedProbability}
-A \emph{core} of an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
+of an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 is the set
@@
 
+\begin{comment}
+\bibliographystyle{plain}
+\bibliography{discreteGBKS}
+\end{comment}
+
 \printbibliography

### 2016-07-29 prob.tex
prob.tex Filling the details to clarify the proof...

@@
 is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
-and $l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)$
+and $l\left(E_{1}\cup E_{2}\right)\ge l\left(E_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{2}\right)\tensor*[_{\mathbb{R}}]{-}{}l\left(E_{1}\cap E_{2}\right)$
 for all $E_{1},E_{2}\in\events$.\qed\end{thm}
@@
 \item for any projection $P$, 
-$\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)$, and
+\begin{equation}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Complement}
+\end{equation}
 \item for a set of mutually orthogonal projections $P_{i}$, we have 
-$\bar{\mu}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(P_{i}\right)$.
+\begin{equation}
+\bar{\mu}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\end{equation}
+\footnote{Let $\bar{\mu}\left(P\right)=\left[l\left(P\right),r\left(P\right)\right]$.
+Then, $\bar{\mu}$ is called convex if $l\left(P_{1}P_{2}\right)\ge l\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(P_{2}\right)\tensor*[_{\mathbb{R}}]{-}{}l\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)$
+for all commuting $P_{1},P_{2}\in\events$. We may further define
+a quantum Dempster-Shafer probability measure, and a quantum Dempster-Shafer
+probability measure is always convex.}
 \end{itemize}
-As before, we will only define a quantum interval-valued probability measure
-with preposing $\mathscr{I}$ when we want to compare a quantum probability
-measure and a quantum interval-valued probability measure.
+As before, we will only define a quantum interval-valued probability
+measure with preposing $\mathscr{I}$ when we want to compare a quantum
+probability measure and a quantum interval-valued probability measure.
 \qed\end{definition}
@@
 \begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
-There is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+There is a (convex) quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.\qed\end{thm}
@@
 To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
-it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
+first notice that $\bar{\mu}\left(\proj{P_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{P_{2}}\right)\subseteq\bar{\mu}\left(\proj{P_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{P_{2}}\right)$
+implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
+implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(\proj{P}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)$.
+Therefore, it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
 for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
-verified by enumerating all possible cases.
+verified by enumerating all possible cases\footnote{This is the internal note for the detail of the proof, and can be
+safely removed from the published version.}.
 

### 2016-07-29 prob.tex
prob.tex \subsection{Interval-valued probability measures} Updated...

@@
 In particular, Dempster-Shafer probability measures are all convex
-and have nonempty cores. Need to verify whether general interval-valued
-probability measures must have a core or find a counterexample.}
+and have nonempty cores.
+
+It seems general interval-valued probability measures must have a
+core. Following are proving plan:
+
+\begin{thm}[Neumaier~\cite{Neumaier2003}] For every cloud $\mathbf{x}$
+over $\mathbb{M}$ there exists a random variable $x$ with values
+in $\mathbb{M}$ contained in $\mathbf{x}$.\qed\end{thm}
+
+\begin{example}[A cloud defines an $R$-probability field~\cite{Lodwick2008}]
+...\qed\end{example}
+
+Next need to verify every interval-valued probability measures must
+define a cloud...}
 

### 2016-07-30 prob.tex
prob.tex Update the definiton of convex...

@@
 \begin{itemize}
-\item Instead of the Hilbert space $\Hilb$ (constructed over the
-  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
-  consider variants constructed over finite
-  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
+\item Instead of the Hilbert space $\Hilb$ (constructed over the uncountable
+and uncomputable complex numbers $\mathbb{C}$), we will consider
+variants constructed over finite fields~\cite{DQT2014,geometry2013}. 
 \item Instead of real-valued probability measures producing results in
@@
 where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
-and $l\left(E_{1}\cup E_{2}\right)\ge l\left(E_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{2}\right)\tensor*[_{\mathbb{R}}]{-}{}l\left(E_{1}\cap E_{2}\right)$
+is convex if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\ge\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
 for all $E_{1},E_{2}\in\events$.\qed\end{thm}
@@
 \end{equation}
-\footnote{Let $\bar{\mu}\left(P\right)=\left[l\left(P\right),r\left(P\right)\right]$.
-Then, $\bar{\mu}$ is called convex if $l\left(P_{1}P_{2}\right)\ge l\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(P_{2}\right)\tensor*[_{\mathbb{R}}]{-}{}l\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)$
+\footnote{$\bar{\mu}$ is called convex if $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\ge\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
 for all commuting $P_{1},P_{2}\in\events$. We may further define

### 2016-08-01 prob.tex
prob.tex \subsection{Interval-valued probability measures} cleaning up..

@@
 probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that~\cite{JamisonLodwick2004}:\footnote{The lower probability (belief) and the upper probability (plausibility)
-defined by Dempster~\cite{Dempster1967} and Shafer~\cite{Shafer1976}
-is a special case of the left-end and the right-end of the interval-valued
-probability measure. The right-end of the interval-valued probability
-measure is a special case of capacity~\cite{Choquet1954,Graf1980,Goodman2013}.
+such that~\cite{JamisonLodwick2004}:\footnote{The right-end of the interval-valued probability measure is a special
+case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman2013}.
 The left-end of the interval-valued probability measure is a special
@@
 E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$, and 
-\item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)$,
+\item for a collection $E_{i}$ of pairwise disjoint events, we have 
+\begin{equation}
+\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)\textrm{ ,}\label{eq:subsetInterval-valuedProbabilityMeasure}
+\end{equation}
 where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
-We may drop the preposing $\mathscr{I}$ when summands are clearly intervals. 
+We may drop the preposing $\mathscr{I}$ when summands are clearly
+intervals. 
 \end{itemize}
@@
 
-\noindent We will explain why the last condition is expressed using
-$\subseteq$ by a small example.
+An interval-valued probability measure can satisfy extra conditions.
+It is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
+for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
+For example, a special case of convex interval-valued probability
+measures consists the lower probability (belief) as the left-end and
+the upper probability (plausibility) as the right-end~\cite{GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
+They are defined by Dempster~\cite{Dempster1967} and Shafer~\cite{Shafer1976}
+and play an important role in the theory of non-additive belief.\footnote{\yutsung{If we want to use convex, we need to explain the physical
+meaning of convex interval-valued probability measures...?}}
+
+We will explain why equation (\ref{eq:subsetInterval-valuedProbabilityMeasure})
+is expressed using $\subseteq$ by a small example.
 
@@
 probability measure can still be understood by its relation with real-valued
-probability measures, like we constructed example~\ref{ex3} from
-example~\ref{ex1}. In general, this idea can be generalized to the
-following definition of core.
+probability measures, like constructing example~\ref{ex3} from example~\ref{ex1}.
+In general, this idea can be generalized to the following definition
+of core.
 
@@
 
-\yutsung{The following theorem proved that a wide variety of interval-valued
-probability measures can be associated with real-valued probability
-measures.
-
-\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
-Every convex interval-valued probability measure has a nonempty core,
-where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is convex if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\ge\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
-for all $E_{1},E_{2}\in\events$.\qed\end{thm}
-
-In particular, Dempster-Shafer probability measures are all convex
-and have nonempty cores.
-
-It seems general interval-valued probability measures must have a
-core. Following are proving plan:
+\yutsung{Because the physical meaning of convex is still not clear,
+it would be better if we can find or prove a theorem which removes
+``convex'' in the theorem. However, the literature contradicts to
+each other so at least I need to trace an example to see which one
+is correct, or neither proved the theorem we want.
+
+First, \cite{JamisonLodwick2004} shows a kind of equivalence between
+interval-valued probability measures and clouds.
+
+On one hand, a combination of the following two theorems show interval-valued
+probability measures is likely to have a core.
 
@@
 
-Next need to verify every interval-valued probability measures must
-define a cloud...}
+On the other hand, \cite{Destercke2008a} proved some clouds has no
+core.
+
+Verifying the example to see who is right...}
 

### 2016-08-03 prob.tex
prob.tex \subsection{Interval-valued probability measures} updates...

@@
 For example, a special case of convex interval-valued probability
-measures consists the lower probability (belief) as the left-end and
-the upper probability (plausibility) as the right-end~\cite{GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
-They are defined by Dempster~\cite{Dempster1967} and Shafer~\cite{Shafer1976}
-and play an important role in the theory of non-additive belief.\footnote{\yutsung{If we want to use convex, we need to explain the physical
+measures consists the Dempster-Shafer belief function as the left-end
+and the Dempster-Shafer plausibility as the right-end, which plays
+an important role in the theory of non-additive belief~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.\footnote{\yutsung{If we want to use convex, we need to explain the physical
 meaning of convex interval-valued probability measures...?}}
@@
 \qed\end{definition}
+
+Then, a wide variety of interval-valued probability measures can be
+associated with real-valued probability measures.
+
+\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
+Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}
 

### 2016-08-04 prob.tex
prob.tex Updates...

@@
 
-% \begin{example}{[}Two-coin probability space with finite set-valued
-% probability measure{]} \label{ex2} Under the new set-valued requirement,
+% \begin{example}[Two-coin probability space with finite set-valued
+% probability measure] \label{ex2} Under the new set-valued requirement,
 % the probability measure in the first example becomes: 
@@
 
-% \begin{example}\label{Two-coin-set-valued-again}{[}Two-coin probability
-% space with set-valued probability measure, again{]} 
+% \begin{example}\label{Two-coin-set-valued-again}[Two-coin probability
+% space with set-valued probability measure, again] 
 % \[
@@
 
-In contrast to real-valued probability measure, there is no easy Radon-Nikodym
-theorem to simplify an interval-valued probability measure to its
-Radon-Nikodym derivative. So far the Radon-Nikodym Theorems found
-for the interval-valued probability measure are either too restricted
-to apply to all interval-valued probability measures~\cite{Choquet1954,Graf1980,Goodman2013}
-or corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+In contrast to real-valued probability measures, there is no easy
+Radon-Nikodym theorem to simplify an interval-valued probability measure
+to its Radon-Nikodym derivative. So far, the interval-valued Radon-Nikodym
+Theorems are either too restricted to apply to all interval-valued
+probability measures~\cite{Choquet1954,Graf1980,Goodman2013} or
+corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 to another set function~$\bar{\rho}:\events\rightarrow\bar{\mathscr{I}}$
@@
 probability measure can still be understood by its relation with real-valued
-probability measures, like constructing example~\ref{ex3} from example~\ref{ex1}.
-In general, this idea can be generalized to the following definition
-of core.
+probability measures. For example, the real-valued probability measure
+in example~\ref{ex1} can be used to construct the interval-valued
+probability measure in example~\ref{ex3}. Conversely, the interval-valued
+probability measure in example~\ref{ex3} could be understood by
+the real-valued probability measure and its Radon-Nikodym derivative
+in example~\ref{ex1}. The relation between example~\ref{ex1} and
+\ref{ex3} can be abstracted into the definition of core.
 
@@
 each other so at least I need to trace an example to see which one
-is correct, or neither proved the theorem we want.
+is correct, or prove the theorem we want independently...
 
@@
 
-On one hand, a combination of the following two theorems show interval-valued
-probability measures is likely to have a core.
+On one hand, a combination of the following two theorems show every
+cloud has a core.
 
@@
 
-Verifying the example to see who is right...}
+Verifying the example to see who is right... Also need to confirm
+whether interval-valued probability measures and clouds are really
+the same.}
 
@@
 
-A set of events~$\events$ together with quantum probability measure is called a
-\emph{quantum probability space}. 
-Comparing to the classical probability space, the empty set~$\emptyset$
-corresponds to the empty projection~$\mathbb{0}$ and the event of
-whole space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
-In contrast, the union~$\cup$ of any two events always gives an
-event classically, but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
-of two projections may not be a projection. As the result, the classical
+A set of events~$\events$ together with a quantum probability measure
+is called a \emph{quantum probability space}. Comparing to classical
+probability spaces, the empty set~$\emptyset$ corresponds to the
+empty projection~$\mathbb{0}$, and the event of whole space~$\Omega$
+corresponds to the identity projection~$\mathbb{1}$. In contrast,
+the union~$\cup$ of any two events always gives an event classically,
+but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$ of two
+projections may not be a projection. As the result, the classical
 condition~$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
@@
 
-Moreover, the Born rule can be extended to a mixed state. Suppose
-we prepares a set of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$,
-the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
-where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
-measure introduced by $\rho$ is the combination of $\mu_{\phi_{j}}^{B}$
-with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
+Moreover, the Born rule can be extended to a mixed state. When we
+prepares a state, suppose the probability of preparing state~$\ket{\phi_{j}}$
+is $q_{j}$, the state of the system can be expressed as a density
+matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$, where $\sum_{j}q_{j}=1$.
+Then, the quantum probability measure introduced by $\rho$ is the
+combination of $\mu_{\phi_{j}}^{B}$ with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
 \begin{eqnarray}
@@
 
-Then, the Radon-Nikodym theorem is generalized quantum~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
-If the mixed state~$\rho$ is considered as the Radon-Nikodym derivative
-with respect to the trace, we have Gleason's theorem: in Hilbert spaces
-of dimension $d\geq3$, given a quantum probability measure $\mu$,
-there exist a mixed state~$\rho$ that induces such a measure using
-the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+In this sense, the Radon-Nikodym theorem could be generalized to Gleason's
+theorem: in quantum~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}:
+in Hilbert spaces of dimension $d\geq3$, given a quantum probability
+measure $\mu$, there exist a mixed state~$\rho$ that induces such
+a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}

### 2016-08-04 prob.tex
prob.tex Keep updating...

@@
 
-An interval-valued probability measure can satisfy extra conditions.
-It is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
-for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
-For example, a special case of convex interval-valued probability
-measures consists the Dempster-Shafer belief function as the left-end
-and the Dempster-Shafer plausibility as the right-end, which plays
-an important role in the theory of non-additive belief~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.\footnote{\yutsung{If we want to use convex, we need to explain the physical
-meaning of convex interval-valued probability measures...?}}
-
 We will explain why equation (\ref{eq:subsetInterval-valuedProbabilityMeasure})
@@
 in example~\ref{ex1}. The relation between example~\ref{ex1} and
-\ref{ex3} can be abstracted into the definition of core.
-
-\begin{definition}[Core of Interval-valued Probability Measure~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}]\label{def:CoreInterval-valuedProbability}
-A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
+\ref{ex3} can be abstracted into the definition of core. Besides
+of core, we also define another property which will be used later.
+
+\begin{definition}~
+\begin{itemize}
+\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
 of an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is the set
+is the set~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}
 \[
@@
 \]
+\item An interval-valued probability measure is called \emph{convex} or
+\emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
+for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.\footnote{\yutsung{If we want to use convex, we need to explain the physical
+meaning of convex interval-valued probability measures...? If there
+is a good explanation, we may only consider convex interval-valued
+probability measures, and replace the definition in the beginning...?}}
+\end{itemize}
 \qed\end{definition}
 
-Then, a wide variety of interval-valued probability measures can be
-associated with real-valued probability measures.
+It is common to consider convex interval-valued probability measures.
+For example, a special case of convex interval-valued probability
+measures consists the Dempster-Shafer belief function as the left-end
+and the Dempster-Shafer plausibility as the right-end, which plays
+an important role in the theory of non-additive belief~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
+Further more, convex interval-valued probability measures have good
+properties because they can always be associated with real-valued
+probability measures.
 
@@
 \begin{equation}
-\bar{\mu}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\bar{\mu}\left(\sideset{_{\mathscr{O}}}{_{i}}\sum P_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i}}\sum\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
 \end{equation}
-\footnote{$\bar{\mu}$ is called convex if $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\ge\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
-for all commuting $P_{1},P_{2}\in\events$. We may further define
-a quantum Dempster-Shafer probability measure, and a quantum Dempster-Shafer
-probability measure is always convex.}
 \end{itemize}
@@
 
-When a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-constructed from a real-valued one~$\mu:\events\rightarrow\left[0,1\right]$,
-we should say $\mu$ is in the core of $\bar{\mu}$ according to the
-following definition of core.
-
-\begin{definition}[Core of Quantum Interval-valued Probability
-Measure]\label{def:CoreQuantumInterval-valuedProbability} A \emph{core}
-of a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+Similar to classical interval-valued probability measures which have
+no easy Radon-Nikodym theorem, quantum interval-valued probability
+measures have no easy Gleason's theorem. We can further define core
+and convex for quantum interval-valued probability measures. Surprisingly,
+a convex quantum interval-valued probability measure may have a empty
+core, i.e., it cannot correspond to a quantum real-valued probability
+measure or a mixed state.
+
+\begin{definition}~
+\begin{itemize}
+\item A \emph{core} of a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 is the set 
@@
 \]
+\item $\bar{\mu}$ is called convex if $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\ge\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
+for all commuting $P_{1},P_{2}\in\events$. 
+\end{itemize}
 \qed\end{definition}
 
-Because the classical interval-valued probability measure has no easy
-Radon-Nikodym theorem, the quantum one should not have a easy Gleason's
-theorem. Nevertheless, the core of $\bar{\mu}$ provides an instructive
-way to understand $\bar{\mu}$, and the core may exist even without
-a natural $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ as in the
-example~\ref{ex:One-qubit-quantum-interval} in appendix. However,
-in contrast to the classical case, we have the following theorem.
-
 \begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
-There is a (convex) quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+There is a convex quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.\qed\end{thm}
@@
 To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
-first notice that $\bar{\mu}\left(\proj{P_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{P_{2}}\right)\subseteq\bar{\mu}\left(\proj{P_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{P_{2}}\right)$
+first notice that 
+\[
+\bar{\mu}\left(\proj{P_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{P_{2}}\right)\subseteq\bar{\mu}\left(\proj{P_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{P_{2}}\right)
+\]
 implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
 by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
-implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(\proj{P}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)$.
-Therefore, it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
+implies 
+\[
+\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(\proj{P}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)\textrm{ .}
+\]
+Therefore, it is sufficient to check 
+\[
+\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
+\]
 for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
-verified by enumerating all possible cases\footnote{This is the internal note for the detail of the proof, and can be
+verified by enumerating all possible cases\footnote{This is the internal note for the details of the proof, and can be
 safely removed from the published version.}.
@@
 \begin{example}[Three-dimensional quantum 4-value interval-valued
-probability measure]\label{ex:three-dimensional-4-value} Given
+probability measure]\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify this example is convex!}}Given
 a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.

### 2016-08-05 prob.tex
prob.tex updated...

@@
 
-\begin{definition}~
+\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
 \begin{itemize}
 \item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
-of an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is the set~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}
+of $\bar{\mu}$ is the set~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}
 \[
@@
 \]
-\item An interval-valued probability measure is called \emph{convex} or
-\emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
+\item $\bar{\mu}$ is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
 for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.\footnote{\yutsung{If we want to use convex, we need to explain the physical
@@
 
-\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
+\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]\label{thm:Shapley}
 Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}
@@
 no easy Radon-Nikodym theorem, quantum interval-valued probability
-measures have no easy Gleason's theorem. We can further define core
-and convex for quantum interval-valued probability measures. Surprisingly,
-a convex quantum interval-valued probability measure may have a empty
-core, i.e., it cannot correspond to a quantum real-valued probability
-measure or a mixed state.
-
-\begin{definition}~
+measures have no easy Gleason's theorem. Although we could define
+core and convex for quantum interval-valued probability measures,
+in contrast to theorem~\ref{thm:Shapley}, a convex quantum interval-valued
+probability measure may have a empty core, i.e., it cannot correspond
+to a quantum real-valued probability measure or a mixed state.
+
+\begin{definition}~Given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
 \begin{itemize}
-\item A \emph{core} of a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is the set 
+\item A \emph{core} of $\bar{\mu}$ is the set 
 \[
@@
 \]
-\item $\bar{\mu}$ is called convex if $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\ge\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
+\item $\bar{\mu}$ is called convex if 
+\begin{equation}
+\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
+\end{equation}
  for all commuting $P_{1},P_{2}\in\events$. 
@@
 \]
-for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
-verified by enumerating all possible cases\footnote{This is the internal note for the details of the proof, and can be
-safely removed from the published version.}.
+for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This equation
+always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$.
+
+Next, we need to verify that $\bar{\mu}$ is convex. First, for orthogonal
+projections $P_{1}$ and $P_{2}$, equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+implies equation (\ref{eq:QuantumInterval-valuedProbability-Convex}).
+Second, when $P_{1}=P_{2}+P_{3}$, equation (\ref{eq:QuantumInterval-valuedProbability-Convex})
+holds trivially. Hence, we only need to verify the case which $P_{1}=\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{3}}$
+and $P_{2}=\proj{\psi_{2}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{3}}$,
+where $\left\{ \ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\right\} $
+is an orthonormal basis. Because we have 
+\begin{eqnarray*}
+\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right) & = & \bar{\mu}\left(\mathbb{1}\right)=\necess\\
+\bar{\mu}\left(P_{1}P_{2}\right) & = & \bar{\mu}\left(\proj{\psi_{3}}\right)\subseteq\unknown
+\end{eqnarray*}
+and $\left\{ \bar{\mu}\left(P_{1}\right),\bar{\mu}\left(P_{2}\right)\right\} $
+is either $\left\{ \bar{\mu}\left(\necess\right),\bar{\mu}\left(\unknown\right)\right\} $
+or $\left\{ \bar{\mu}\left(\unknown\right),\bar{\mu}\left(\unknown\right)\right\} $.
+Therefore, we have
+\[
+\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\textrm{ .}
+\]
 

### 2016-08-05 prob.tex
prob.tex Fix small things...

@@
 E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$, and 
-\item for a collection $E_{i}$ of pairwise disjoint events, we have 
-\begin{equation}
-\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)\textrm{ ,}\label{eq:subsetInterval-valuedProbabilityMeasure}
-\end{equation}
+\item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)$,
 where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
@@
 
-We will explain why equation (\ref{eq:subsetInterval-valuedProbabilityMeasure})
-is expressed using $\subseteq$ by a small example.
+\noindent We will explain why the last condition is expressed using
+$\subseteq$ by a small example.
 
@@
 \item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
-of $\bar{\mu}$ is the set~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}
-\[
-\mathrm{core}\left(\bar{\mu}\right)=\left\{ \pmeas:\events\rightarrow[0,1]\textrm{ probability measure}\middle|\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\forall E\in\events\right\} \textrm{ .}
-\]
+of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \pmeas:\events\rightarrow[0,1]\textrm{ probability measure}\middle|\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\forall E\in\events\right\} $
+\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
 \item $\bar{\mu}$ is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
@@
 \begin{itemize}
-\item A \emph{core} of $\bar{\mu}$ is the set 
-\[
-\mathrm{core}\left(\bar{\mu}\right)=\left\{ \mu:\events\rightarrow[0,1]\textrm{ quantum probability measure}\middle|\mu\left(P\right)\in\bar{\mu}\left(P\right)\forall P\in\events\right\} \textrm{ .}
-\]
+\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \mu:\events\rightarrow[0,1]\textrm{ quantum probability measure}\middle|\mu\left(P\right)\in\bar{\mu}\left(P\right)\forall P\in\events\right\} $.
 \item $\bar{\mu}$ is called convex if 
@@
 \end{eqnarray*}
-and $\left\{ \bar{\mu}\left(P_{1}\right),\bar{\mu}\left(P_{2}\right)\right\} $
-is either $\left\{ \bar{\mu}\left(\necess\right),\bar{\mu}\left(\unknown\right)\right\} $
-or $\left\{ \bar{\mu}\left(\unknown\right),\bar{\mu}\left(\unknown\right)\right\} $.
-Therefore, we have
-\[
-\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\textrm{ .}
-\]
+and $\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
+is either $\necess\tensor*[_{\mathscr{I}}]{+}{}\unknown$ or $\unknown\tensor*[_{\mathscr{I}}]{+}{}\unknown$.
+Therefore, we have$\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$.
 
 $\bar{\mu}$ cannot correspond to any quantum probability measure.
-Suppose $\bar{\mu}(P)=\iota\left(\mu(P)\right)$ for some $\mu:\events\rightarrow\left[0,1\right]$.
+Suppose $\mu(P)\in\bar{\mu}(P)$ for some $\mu:\events\rightarrow\left[0,1\right]$.
 We must have 

### 2016-08-06 prob.tex
prob.tex Delete Appendix because examples there are not necessary...

@@
 
-This theorem can be proved by the following example, and a more sophisticated
-example is example~\ref{ex:three-dimensional-4-value} in appendix.
-
-\begin{example}[Three-dimensional quantum three-value interval-valued
-probability measure]\label{ex:three-dimensional-three-value} Given
+This theorem can be proved by the following example.
+
+\begin{example}{[}Three-dimensional quantum three-value interval-valued
+probability measure{]}\label{ex:three-dimensional-three-value} Given
 a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
 Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
-and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$. Let 
+and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$.
+Let 
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
 \bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
@@
 \]
-Therefore, it is sufficient to check 
+Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+it is sufficient to check 
 \[
@@
 $\bar{\mu}$ cannot correspond to any quantum probability measure.
-Suppose $\mu(P)\in\bar{\mu}(P)$ for some $\mu:\events\rightarrow\left[0,1\right]$.
+Suppose $\mu(P)\in\bar{\mu}(P)$ for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
 We must have 
 \begin{equation}
-\mu(\proj{0})=\mu(\proj{\ps})=0\textrm{ .}\label{eq:probability-zero-on-states}
+\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
 \end{equation}
@@
 such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j}q_{j}=1$ and $q_{j}>0$. The only pure state~$\ket{\phi}$
+where $\sum_{j}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
 satisfies
 \[
-\ip{\phi}{0}=\ip{\phi}{\ps}=0
-\]
-is $\ket{2}$, but clearly $\bar{\mu}(P)\ne\iota\left(\mu_{\ket{2}}^{B}(P)\right)$.\qed\end{example}
+\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0
+\]
+so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
+measure~$\mu$.\qed\end{example}
 
@@
 \printbibliography
-
-\appendix
-
-\section{Examples for Quantum Interval-valued Probability Measures}
-
-The following example verify the core of a quantum interval-valued
-probability measure is nonempty even if there is no natural correspondence.
-For example, if $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-there is no natural way to map from $\frac{1}{2}$, as both $\frac{1}{2}\in\left[0,\frac{1}{2}\right]=\unlikely$
-and $\frac{1}{2}\in\left[\frac{1}{2},1\right]=\likely$. However,
-we still can find a quantum interval-valued probability measure corresponding
-to a quantum probability measure as in the following example.
-
-\begin{example}[One-qubit quantum interval-valued probability measure]\label{ex:One-qubit-quantum-interval}
-Given a two dimensional Hilbert space, a vector $\ket{\psi}$ can
-be normalized and written in $\left(\begin{array}{c}
-\cos\theta\\
-\rme^{\rmi\gamma}\sin\theta
-\end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Consider
-a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-defined by 
-\begin{eqnarray*}
-\bar{\mu}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1}) & = & \necess\textrm{ ,}\\
-\bar{\mu}(\proj{\psi}) & = & \begin{cases}
-\necess & \textrm{, if }\theta=0\textrm{ ;}\\
-\likely & \textrm{, if }0<\theta<\frac{\pi}{4}\textrm{ ;}\\
-\likely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }0\le\gamma<\pi\textrm{ ;}\\
-\unlikely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }\pi\le\gamma<2\pi\textrm{ ;}\\
-\unlikely & \textrm{, if }\frac{\pi}{4}<\theta<\frac{\pi}{2}\textrm{ ;}\\
-\imposs & \textrm{, if }\theta=\frac{\pi}{2}\textrm{ .}
-\end{cases}
-\end{eqnarray*}
-Let $\ket{\psi^{\perp}}$ be the state perpendicular to $\ket{\psi}$.
-Then, the vector representation of $\ket{\psi^{\perp}}$ can be simplified
-as 
-\[
-\left(\begin{array}{c}
--\rme^{-\rmi\gamma}\sin\theta\\
-\cos\theta
-\end{array}\right)=-\rme^{-\rmi\gamma}\left(\begin{array}{c}
-\cos\left(\frac{\pi}{2}-\theta\right)\\
-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)
-\end{array}\right)
-\]
-so we have 
-\[
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi}\right)=\bar{\mu}\left(\proj{\psi^{\perp}}\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(\proj{\psi}\right)\textrm{ .}
-\]
-Hence, $\bar{\mu}$ is a quantum $\mathscr{I}$-interval-valued probability
-measure. Notice that for all projection~$P$, $\mu_{\ket{0}}^{B}(P)\in\bar{\mu}(P)$
-implies that $\bar{\mu}(P)$ is one of quantum $\mathscr{I}$-interval-valued
-probability measures corresponding to $\mu_{\ket{0}}^{B}(P)$. However,
-$\mu_{\ket{0}}^{B}(P)$ can correspond to infinity many quantum $\mathscr{I}$-interval-valued
-probability measures by twisting the definition involving $\gamma$.\qed\end{example}
-
-We are going to provide an quantum 4-value interval-valued probability
-measures corresponding to no quantum probability measure, i.e., $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.
-In general, we believe this kind of quantum $\mathscr{I}$-interval-valued
-probability measure exists for any finite set of interval~$\mathscr{I}$.
-
-\begin{example}[Three-dimensional quantum 4-value interval-valued
-probability measure]\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify this example is convex!}}Given
-a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$,
-and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}$
-defined as follow: 
-\begin{enumerate}
-\item $\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$
-and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess$.
-\item Consider the states orthogonal to $\ket{0}$ and $\ket{\ps}$ respectively,
-$\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
-and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
-where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Half of
-those states need special treatment, i.e., when where $0\le\theta<\frac{\pi}{2}$
-and $0\le\gamma<\pi$, we define $\bar{\mu}(\proj{0_{\theta,\gamma}^{\perp}})=\ket{\ps_{\theta,\gamma}^{\perp}}=\likely$
-and $\bar{\mu}(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}})=\bar{\mu}(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}})=\unlikely$.
-\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$.
-\end{enumerate}
-$\bar{\mu}$ cannot correspond to any quantum probability measure
-because of the exact same reason as in example~\ref{ex:three-dimensional-three-value}.
-Before we verify that $\bar{\mu}$ is a quantum interval-valued probability
-measure, we need a notation for cross product. For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
-\alpha_{1}\\
-\alpha_{2}
-\end{pmatrix}$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\begin{pmatrix}\beta_{0}\\
-\beta_{1}\\
-\beta_{2}
-\end{pmatrix}$, their cross product is defined as follow.
-\[
-\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\begin{vmatrix}\alpha_{1}^{*} & \beta_{1}^{*}\\
-\alpha_{2}^{*} & \beta_{2}^{*}
-\end{vmatrix}\ket{0}+\begin{vmatrix}\alpha_{2}^{*} & \beta_{2}^{*}\\
-\alpha_{0}^{*} & \beta_{0}^{*}
-\end{vmatrix}\ket{1}+\begin{vmatrix}\alpha_{0}^{*} & \beta_{0}^{*}\\
-\alpha_{1}^{*} & \beta_{1}^{*}
-\end{vmatrix}\ket{2}\textrm{ ,}
-\]
-where $\begin{vmatrix}\alpha & \beta\\
-\alpha' & \beta'
-\end{vmatrix}=\alpha\beta'-\alpha'\beta$. Notice that we put the complex conjugate in the cross product, so
-that the result of cross product is orthogonal to $\ket{\psi}$ and
-$\ket{\phi}$. 
-\begin{eqnarray*}
-\ip{\psi\times\phi}{\psi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}=0\textrm{ ,}\\
-\ip{\psi\times\phi}{\phi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}=0\textrm{ .}
-\end{eqnarray*}
-Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
-cross product~$\ket{\psi\times\phi}$ need not be normalized as usual.
-
-To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
-it is sufficient to check
-\begin{equation}
-\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{3}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
-\end{aligned}
-\label{eq:non-additive-vectors}
-\end{equation}
- for every orthonormal basis $\mathcal{B}=\left\{ \ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\right\} $.
-We are going to enumerate all possible orthonormal bases to verify
-the equations, and case 1 and 2 are illustrated in figure~\ref{fig:three-dimensional-4-value}.
-\begin{figure}
-\includegraphics{\string"Three-dimensional quantum 4-value interval-valued probability measure\string".pdf}\caption{\label{fig:three-dimensional-4-value}This figure illustrates case
-1 and 2 in $\mathbb{R}^{3}$ in example~\ref{ex:three-dimensional-4-value}.
-The red and green dotted vector are $\ket{0}$ and $\ket{\ps}$ respectively.
-All possible vectors of $\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
-are drawn in the red and green circles, respectively. Within the circles,
-a vector~$\ket{\psi}$ in dotted part means $\bar{\mu}(\proj{\psi})=\likely$;
-otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
-a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
-and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
-and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
-\end{figure}
-
-\begin{enumerate}
-\item When $\ket{\psi_{1}}$ is $\ket{0}$, then $\ket{\psi_{2}}$ and $\ket{\psi_{3}}$
-must be $\ket{0_{\theta,\gamma}^{\perp}}$ for some $\theta$ and
-$\gamma$. Because of 
-\[
-\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
-0\\
-0
-\end{pmatrix}\times\begin{pmatrix}0\\
-\rme^{\rmi\gamma}\sin\theta\\
-\cos\theta
-\end{pmatrix}=\begin{pmatrix}0\\
--\cos\theta\\
-\rme^{-\rmi\gamma}\sin\theta
-\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}0\\
-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
-\cos\left(\frac{\pi}{2}-\theta\right)
-\end{pmatrix}=\rme^{-\rmi\gamma}\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
-\]
-the pair $\ket{\psi_{2}}=\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\psi_{3}}=\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}$
-for ($0<\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$) or $\theta=0$
-enumerate all possible orthonormal bases. Equation (\ref{eq:non-additive-vectors})
-can be verified as follow. 
-\begin{eqnarray*}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}\right)=\necess & \subseteq & \likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & = & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\imposs=\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)=\likely & = & \imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
-\end{eqnarray*}
-Similarly, when $\ket{\psi_{1}}$ is $\ket{\ps}$, equation (\ref{eq:non-additive-vectors})
-holds.
-\item When $\ket{0}\notin\mathcal{B}$ and $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$
-for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we want to
-prove $\bar{\mu}\left(\proj{\psi_{2}}\right)=\bar{\mu}\left(\proj{\psi_{3}}\right)=\unlikely$.
-Then, we have
-\begin{eqnarray*}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
-\end{eqnarray*}
-In order to verify $\bar{\mu}\left(\proj{\psi_{2}}\right)=\bar{\mu}\left(\proj{\psi_{3}}\right)=\unlikely$,
-it is sufficient to prove that $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$
-implies ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or
-$\theta'=\frac{\pi}{2}$. Recall $\ip{\ps}{\ps_{\theta',\gamma'}^{\perp}}=0$.
-Hence, if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$, we
-have $\ket{\ps_{\theta',\gamma'}^{\perp}}$ parallel to $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$.
-\[
-\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
-1\\
-0
-\end{pmatrix}\times\begin{pmatrix}0\\
-\rme^{\rmi\gamma}\sin\theta\\
-\cos\theta
-\end{pmatrix}=\begin{pmatrix}\cos\theta\\
--\cos\theta\\
-\rme^{-\rmi\gamma}\sin\theta
-\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
-\cos\left(\frac{\pi}{2}-\theta\right)
-\end{pmatrix}=\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
-\]
-Because of $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we have
-($0<\theta'=\frac{\pi}{2}-\theta<\frac{\pi}{2}$ and $\pi\le\gamma'=\pi+\gamma<2\pi$)
-or $\theta'=\frac{\pi}{2}-\theta=\frac{\pi}{2}$. Similarly, when
-$\ket{\psi_{1}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$ and $\ket{\ps}\notin\mathcal{B}$,
-equation (\ref{eq:non-additive-vectors}) holds.
-\item Finally, when $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$,
-$\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$, and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
-for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, i.e., the ``otherwise''
-case. Then, equation (\ref{eq:non-additive-vectors}) can easily be
-verified. 
-\begin{eqnarray*}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)
-\end{eqnarray*}
-\end{enumerate}
-\qed\end{example}
 

### 2016-08-06 prob.tex
prob.tex Modifying sentences...

@@
 \end{equation}
-where $\rho:\Omega\rightarrow[0,1]$ and $\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)=1$.
-$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
-to the counting measure~\cite{Nikodym1930,Folland2013}, or just
-called the Radon-Nikodym derivative of $\pmeas$ because we are always
-with respect to the counting measure. The Radon-Nikodym theorem states
-that the converse is also true.
+where $\rho:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum\rho(\omega)=1$,
+and $\rho$ is called the Radon-Nikodym derivative of $\pmeas$ (with
+respect to the counting measure)~\cite{Nikodym1930,Folland2013}.
+The converse is also valid and called the Radon-Nikodym theorem.
 
@@
 interval-valued probability measures~\cite{Weichselberger2000,JamisonLodwick2004}
-in detail.\footnote{There is another possible approach that can be used to split the real
-interval $[0,1]$ into a collection of subsets~\cite{PuriRalescu1983}
-\amr{need to explain the connection and why we are not using it.}}
+in detail.
 
@@
 
-In previous section, the probability~$\pmeas(E)$ of each event~$E$
-is known a priori. In reality, although the exact value of $\pmeas(E)$
-may not be known, we could still assume each event has a probability.
+In the previous section, the probability~$\pmeas(E)$ of each event~$E$
+is known a priori. In reality, the probability of each event is assumed
+to exist although the exact value of $\pmeas(E)$ may not be known.
 If we want to know its value, we can run $N$ independent trials.

### 2016-08-07 prob.tex
prob.tex \section{Classical Probability Spaces} Fix sentences...

@@
 In the previous section, the probability~$\pmeas(E)$ of each event~$E$
-is known a priori. In reality, the probability of each event is assumed
-to exist although the exact value of $\pmeas(E)$ may not be known.
-If we want to know its value, we can run $N$ independent trials.
-Let $x_{i}$ denote whether the event~$E$ occurs in the $i$-th
-trial or not, then $\pmeas(E)$ could be approximated to given accuracy
+is known a priori. In reality, although each event is assumed to have
+a probability, the exact value of $\pmeas(E)$ may not be known. If
+we want to know its value, we can run $N$ independent trials. Let
+$x_{i}$ denote whether the event~$E$ occurs in the $i$-th trial
+or not, then $\pmeas(E)$ could be approximated to given accuracy
 by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability
@@
 which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
-where the preposing $\mathscr{I}$ specifies we subtracts intervals.
+where the preposing $\mathscr{I}$ specifies we subtract intervals.
 Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
@@
 probability measures. For example, the real-valued probability measure
-in example~\ref{ex1} can be used to construct the interval-valued
-probability measure in example~\ref{ex3}. Conversely, the interval-valued
-probability measure in example~\ref{ex3} could be understood by
-the real-valued probability measure and its Radon-Nikodym derivative
-in example~\ref{ex1}. The relation between example~\ref{ex1} and
+in example~\ref{ex1} can construct the interval-valued probability
+measure in example~\ref{ex3}. Conversely, we could understand the
+interval-valued probability measure in example~\ref{ex3} by the
+real-valued probability measure and its Radon-Nikodym derivative in
+example~\ref{ex1}. The relation between example~\ref{ex1} and
 \ref{ex3} can be abstracted into the definition of core. Besides
-of core, we also define another property which will be used later.
+of core, we also define another property, convex, which will be used
+later.
 
@@
 measures consists the Dempster-Shafer belief function as the left-end
-and the Dempster-Shafer plausibility as the right-end, which plays
-an important role in the theory of non-additive belief~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
-Further more, convex interval-valued probability measures have good
-properties because they can always be associated with real-valued
-probability measures.
+and the Dempster-Shafer plausibility as the right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
+Dempster-Shafer functions, also called \emph{completely or totally
+monotone}, plays an important role in the theory of non-additive belief.
+Furthermore, convex interval-valued probability measures have a good
+property that they can always be associated with real-valued probability
+measures.
 
@@
 
-\begin{example}{[}Three-dimensional quantum three-value interval-valued
-probability measure{]}\label{ex:three-dimensional-three-value} Given
+\begin{example}[Three-dimensional quantum three-value interval-valued
+probability measure]\label{ex:three-dimensional-three-value} Given
 a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.

### 2016-08-08 prob.tex
prob.tex \section{Quantum Probability Spaces} Fix sentences...

@@
 In this sense, the Radon-Nikodym theorem could be generalized to Gleason's
-theorem: in quantum~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}:
-in Hilbert spaces of dimension $d\geq3$, given a quantum probability
-measure $\mu$, there exist a mixed state~$\rho$ that induces such
-a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}: in Hilbert
+spaces of dimension $d\geq3$, given a quantum probability measure
+$\mu$, there exist a mixed state~$\rho$ that induces such a measure
+using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
@@
 
-It is instructive to study counterexamples when $d=2$, i.e., the
+It is instructive to study a counterexample when $d=2$, i.e., the
 case of a one-qubit system.
 
-\begin{example}[One-qubit quantum probability measure] Consider
+\begin{example}{[}One-qubit quantum probability measure{]} Consider
 a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
@@
 we only need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
-\[
-\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
-\]
-On the other hand, $\mu$ cannot be induced by any mixed state because
-\[
-\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ ,}
-\]
+$\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1$. On the other hand, $\mu$
+cannot be induced by any mixed state because $\mu(\proj{\ps})=\mu(\proj{0})=1$,
 and $\mu_{\rho}^{B}(P)=1$ if and only if $\rho$ represents a pure
@@
 field, and counting the number of atoms deflects up. Ideally, if the
-local field strength directs to the $z$-axis, and all particles have
-the same velocity, the Stern-Gerlach experiment only produces two
-spots corresponding to $\ket{0}$ and $\ket{1}$. In reality, we need
-a lot of resource to keep the local field of strength directing to
-the $z$-axis precisely, to keep the atoms having almost the same velocity,
-and to point out the exact position each particle landed on.
+local field of strength directs to the $z$-axis, and all particles
+have the same velocity, the Stern-Gerlach experiment only produces
+two spots corresponding to $\ket{0}$ and $\ket{1}$. In reality,
+we need a lot of resource to keep the local field of strength directing
+to the $z$-axis precisely, to keep the atoms having almost the same
+velocity, and to point out the exact position each particle landed
+on.
 
@@
 will be handled later when we introduce the discrete quantum theory.
-Even if the field of strength is perfectly direct to the $z$-axis,
+Even if the field of strength perfectly directs to the $z$-axis,
 the variant velocity makes spots broader and more washed out. Together
@@
 is picked, measuring the spin is exactly the same as tossing a coin.
-In another word, if somebody claimed she is tossing a coin behind
-a veil, and only show the resulting heads or tails, we cannot distinguish
+In another word, if somebody claims she is tossing a coin behind a
+veil, and only shows the resulting heads or tails, we cannot distinguish
 whether she has really tossed a coin, or she has run an Stern-Gerlach
-experiment, and show us the head, the tail, or the side of coin if
+experiment, and shows us the head, the tail, or the side of coin if
 the silver atoms is spin up, spin down, or just hit the middle, respectively.
@@
 \end{itemize}
-As before, we will only define a quantum interval-valued probability
-measure with preposing $\mathscr{I}$ when we want to compare a quantum
-probability measure and a quantum interval-valued probability measure.
 \qed\end{definition}
@@
 
-\begin{example}[Quantum three-value interval-valued probability
-measure] We consider three intervals\emph{ }$\left[0,0\right]$,
+\begin{example}{[}Quantum three-value interval-valued probability
+measure{]} We consider three intervals\emph{ }$\left[0,0\right]$,
 $\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
@@
 no information. For any Hilbert space and any quantum probability
-measure~$\mu:\events\rightarrow\left[0,1\right]$,
-we can define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-by 
-\[
-\bar{\mu}(P)=\iota\left(\mu(P)\right)\textrm{ ,}
-\]
-where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
+measure~$\mu:\events\rightarrow\left[0,1\right]$, we can define
+a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is defined by 
 \[
@@
 \]
-$\iota$ has two interesting properties 
-\begin{eqnarray*}
-\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right) & = & 1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)\\
-\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right) & \subseteq & \sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)\textrm{ ,}
-\end{eqnarray*}
+$\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
+and $\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)$,
 where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
@@
 
-\begin{example}[Three-dimensional quantum three-value interval-valued
-probability measure]\label{ex:three-dimensional-three-value} Given
+\begin{example}{[}Three-dimensional quantum three-value interval-valued
+probability measure{]}\label{ex:three-dimensional-three-value} Given
 a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
@@
 To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
-first notice that 
-\[
-\bar{\mu}\left(\proj{P_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{P_{2}}\right)\subseteq\bar{\mu}\left(\proj{P_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{P_{2}}\right)
-\]
+first notice that $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
 implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
 by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
-implies 
-\[
-\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(\proj{P}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)\textrm{ .}
-\]
+implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)$.
 Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
@@
 implies equation (\ref{eq:QuantumInterval-valuedProbability-Convex}).
-Second, when $P_{1}=P_{2}+P_{3}$, equation (\ref{eq:QuantumInterval-valuedProbability-Convex})
-holds trivially. Hence, we only need to verify the case which $P_{1}=\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{3}}$
+Second, when $P_{1}=P_{2}\tensor*[_{\mathscr{O}}]{+}{}P_{3}$, equation
+(\ref{eq:QuantumInterval-valuedProbability-Convex}) holds trivially.
+Hence, we only need to verify the case which $P_{1}=\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{3}}$
 and $P_{2}=\proj{\psi_{2}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{3}}$,
@@
 is either $\necess\tensor*[_{\mathscr{I}}]{+}{}\unknown$ or $\unknown\tensor*[_{\mathscr{I}}]{+}{}\unknown$.
-Therefore, we have$\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$.
+Therefore, we have $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$.
 
@@
 where $\sum_{j}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
-satisfies
-\[
-\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0
-\]
-so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
-measure~$\mu$.\qed\end{example}
+satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$ so that
+we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability measure~$\mu$.\qed\end{example}
 

### 2016-08-09 prob.tex
From: Tai, Yu-Tsung Sent: Tuesday, August 09, 2016 0:59 To: Hanson, Andrew J. <hansona@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Amr A. Sabry (sabry@indiana.edu) <sabry@indiana.edu> Subject: RE: Yu-Tsung made changes in your shared folders (fwd)
Dear all,

I get a little bit stuck on the classical interval-valued probability measure. Recall that a quantum interval-valued probability measure $\bar{\mu}$ cannot correspond to any mixed state if there is no quantum real-valued probability measure $\mu$ such that
	$\mu(P) \in \bar{\mu}(P)$ 		(1)
for all $P$. The set of all $\mu$ satisfy

@@
 
-\begin{example}{[}Quantum three-value interval-valued probability
-measure{]} We consider three intervals\emph{ }$\left[0,0\right]$,
+\begin{example}[Quantum three-value interval-valued probability
+measure] We consider three intervals\emph{ }$\left[0,0\right]$,
 $\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$

### 2016-08-14 prob.tex
prob.tex \subsection{Interval-valued probability measures} Update the progress...

@@
 \item $\bar{\mu}(\Omega)=[1,1]$, 
-\item for any event $E$, $\bar{\mu}\left(\Omega\backslash
-E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$, and 
+\item for every collection of pairwise disjoint events $\left\{ E_{i}\right\} ,\left\{ E_{i}'\right\} \subseteq\events$
+with $\Omega=\left(\bigcup_{i}E_{i}\right)\bigcup\left(\bigcup_{i}E_{i}'\right)$,
+we have 
+\[
+\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i}}\sum r_{i}\right\} \right]\textrm{ ,}
+\]
+where $\bar{\mu}\left(E_{i}\right)=[l_{i},r_{i}]$ and $\bar{\mu}\left(E_{i}'\right)=[l_{i}',r_{i}']$
+for all $i$.
+\end{itemize}
+In order to understand this definition, we tear the last condition
+apart and provide an equivalent definition of interval-valued probability
+measures.
+
+\begin{lemma}\label{lem:classicalProbabilityMeasure}Given a sample
+space~$\Omega$ and its event~$\events$, a function~$\mu:\events\rightarrow[0,1]$
+is a classical interval-valued probability measure if and only if
+$\mu$ satisfies the following conditions: 
+\begin{itemize}
+\item $\bar{\mu}(\emptyset)=[0,0]$, 
+\item $\bar{\mu}(\Omega)=[1,1]$, 
+\item for any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$,
+and 
 \item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)$,
@@
 \end{itemize}
+\qed\end{lemma}
 
@@
 it would be better if we can find or prove a theorem which removes
-``convex'' in the theorem. However, the literature contradicts to
-each other so at least I need to trace an example to see which one
-is correct, or prove the theorem we want independently...
-
-First, \cite{JamisonLodwick2004} shows a kind of equivalence between
-interval-valued probability measures and clouds.
-
-On one hand, a combination of the following two theorems show every
-cloud has a core.
-
-\begin{thm}[Neumaier~\cite{Neumaier2003}] For every cloud $\mathbf{x}$
-over $\mathbb{M}$ there exists a random variable $x$ with values
-in $\mathbb{M}$ contained in $\mathbf{x}$.\qed\end{thm}
-
-\begin{example}[A cloud defines an $R$-probability field~\cite{Lodwick2008}]
-...\qed\end{example}
-
-On the other hand, \cite{Destercke2008a} proved some clouds has no
-core.
-
-Verifying the example to see who is right... Also need to confirm
-whether interval-valued probability measures and clouds are really
-the same.}
+``convex'' in the theorem. However, I still have not found an example
+with an empty core or a real-valued probability measure in the core
+of each interval-valued probability measure. What we know:
+\begin{enumerate}
+\item The cloud in \cite{JamisonLodwick2004} cannot induce an interval-valued
+probability measure. Therefore, any results related to clouds cannot
+be used directly.
+\item The definition of interval-valued probability measure in \cite{JamisonLodwick2004}
+is different from any later definition of interval-valued probability
+measure written by Lodwick, including \cite{Lodwick2008}.
+\item About linear programming, the Mathematica program solving the case
+$\left|\Omega\right|=1$ or $2$ gives positive answer. The program
+ceases to respond when outputting $\left|\Omega\right|=3$. Maybe
+I should simplify the program?
+\item Check whether the Shapley value still in the core or not in our setting...?
+\end{enumerate}
+}
 

### 2016-08-16 prob.tex
prob.tex Fix some obvious typos according to meet with Prof. Ortiz...

@@
 \begin{document}
-\title{Interval Probability for Fuzzy Quantum Theories}
+\title{Interval Probability and Measurement for Fuzzy Quantum Theories}
 \author{}
@@
 exposition). The key step is the replacement of \textquotedbl{}sum\textquotedbl{}
-and \textquotedbl{}=\textquotedbl{} in the rule $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$
+and \textquotedbl{}=\textquotedbl{} in the rule $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$
 by various logical operations on sets instead of actually summing
@@
 A \emph{probability space} specifies the necessary conditions for
-reasoning coherently about collections of uncertain events.  We review
-the conventional presentation of probability spaces and then discuss
-the computational resources needed to estimate probabilities.
+reasoning coherently about collections of uncertain events~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}.
+We review the conventional presentation of probability spaces and
+then discuss the computational resources needed to estimate probabilities.
 
 %%%
-\subsection{Real-Valued Probability Spaces}
-
-The conventional definition of a probability
-space~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}
-builds upon the real numbers. In more detail, a probability space
-consists of a \emph{sample space} $\Omega$, a space of
-\emph{events}~$\events$, and a \emph{probability measure}~$\pmeas$
-mapping events in $\events$ to the real interval $[0,1]$. In this
-paper, we will only consider \emph{finite} sets of events: we
-therefore restrict our attention to non-empty finite sets $\Omega$ as
-the sample space. The space of events $\events$ includes every
-possible subset of $\Omega$: it is the powerset~$2^\Omega$. Given the
-set of events $\events$, a \emph{probability measure} is a function
-$\pmeas : \events \rightarrow [0,1]$ such that:
+
+\subsection{Classical Real-Valued Probability Spaces}
+
+The conventional definition of a probability space builds upon the
+field of real numbers. In more detail, a probability space consists
+of a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
+and a \emph{probability measure}~$\pmeas$ mapping events in $\events$
+to the real interval $[0,1]$. In this paper, we will only consider
+\emph{finite} sets of events: we therefore restrict our attention
+to non-empty finite sets $\Omega$ as the sample space. The space
+of events $\events$ includes every possible subset of $\Omega$:
+it is the powerset~$2^{\Omega}=\left\{ E\middle|E\subseteq\Omega\right\} $.
+Given the set of events $\events$, a \emph{probability measure} is
+a function $\pmeas:\events\rightarrow[0,1]$ such that: 
 \begin{itemize}
-\item $\pmeas(\Omega) = 1$, and 
-\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$,
-where $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$
-explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. Besides $\mathbb{R}$, we will
-prepose other symbols later to specify the type of operations, and they may be
-dropped when there is no ambiguity.
+\item $\pmeas(\Omega)=1$, and 
+\item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
+events, $\pmeas(\bigcup_{i=1}^{N}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$,
+where $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$ explicitly
+specifies $\pmeas(E_{i})\in\mathbb{R}$. Besides $\mathbb{R}$, we
+will prepose other symbols later to specify the type of operations,
+and they may be dropped when there is no ambiguity. 
 \end{itemize}
 
-\begin{example}[Two-coins experiment]\label{ex1}
-  Consider an experiment that tosses two coins. We have four possible
-  outcomes that constitute the sample space
-  $\Omega = \{ HH, HT, TH, TT \}$. There are 16 total events including
-  for example the event $\{ HH, HT \}$ that the first coin lands heads
-  up, the event $\{ HT, TH \}$ that the two coins land on opposite
-  sides, and the event $\{ HT, TH, TT\}$ that at least one coin lands
-  tails up. Here is a possible probability measure for these events:
-\[\begin{array}{c@{\qquad\qquad}c}
+\begin{example}[Two-coins experiment]\label{ex1} Consider an
+experiment that tosses two coins. We have four possible outcomes that
+constitute the sample space $\Omega=\{HH,HT,TH,TT\}$. There are 16
+total events including for example the event $\{HH,HT\}$ that the
+first coin lands heads up, the event $\{HT,TH\}$ that the two coins
+land on opposite sides, and the event $\{HT,TH,TT\}$ that at least
+one coin lands tails up. Here is a possible probability measure for
+these events: 
+\[
+\begin{array}{c@{\qquad\qquad}c}
 \begin{array}{rcl}
-\pmeas(\emptyset) &=& 0 \\
-\pmeas(\{ HH \}) &=& 1/3 \\
-\pmeas(\{ HT \}) &=& 0 \\
-\pmeas(\{ TH \}) &=& 2/3 \\
-\pmeas(\{ TT \}) &=& 0 \\
-\pmeas(\{  HH, HT \}) &=& 1/3 \\
-\pmeas(\{  HH, TH \}) &=& 1 \\
-\pmeas(\{  HH , TT \}) &=& 1/3 
+\pmeas(\emptyset) & = & 0\\
+\pmeas(\{HH\}) & = & 1/3\\
+\pmeas(\{HT\}) & = & 0\\
+\pmeas(\{TH\}) & = & 2/3\\
+\pmeas(\{TT\}) & = & 0\\
+\pmeas(\{HH,HT\}) & = & 1/3\\
+\pmeas(\{HH,TH\}) & = & 1\\
+\pmeas(\{HH,TT\}) & = & 1/3
 \end{array} & \begin{array}{rcl}
-\pmeas(\{  HT, TH \}) &=& 2/3 \\
-\pmeas(\{  HT , TT \}) &=& 0 \\
-\pmeas(\{  TH , TT \}) &=& 2/3 \\
-\pmeas(\{  HH, HT, TH \}) &=& 1 \\
-\pmeas(\{  HH, HT, TT \}) &=& 1/3 \\
-\pmeas(\{  HH, TH, TT \}) &=& 1 \\
-\pmeas(\{  HT, TH, TT \}) &=& 2/3 \\
-\pmeas(\{  HH, HT, TH, TT \}) &=& 1
-\end{array}
-  \end{array}\]
+\pmeas(\{HT,TH\}) & = & 2/3\\
+\pmeas(\{HT,TT\}) & = & 0\\
+\pmeas(\{TH,TT\}) & = & 2/3\\
+\pmeas(\{HH,HT,TH\}) & = & 1\\
+\pmeas(\{HH,HT,TT\}) & = & 1/3\\
+\pmeas(\{HH,TH,TT\}) & = & 1\\
+\pmeas(\{HT,TH,TT\}) & = & 2/3\\
+\pmeas(\{HH,HT,TH,TT\}) & = & 1
+\end{array}\end{array}
+\]
 The assignment satisfies the two constraints for probability measures:
 the probability of the entire sample space is 1, and the probability
-  of every collection of disjoint events (e.g.,
-  $\{ HT \} \cup \{ TH \} = \{ HT, TH \}$) is the sum of the individual
-  probabilities. The probability of collections of non-disjoint events
-  (e.g., $\{ HT, TH \} \cup \{ TH , TT \} = \{ HT, TH, TT \}$) may add
-  to something different than the probabilities of the individual
-  events. It is useful to think that this probability measure is
-  completely induced by the two coins in question and their
-  characteristics in the sense that each pair of coins induces a
-  measure, and each measure must correspond to some pair of coins.  The
-  measure above is induced by two coins such that the first coin is
-  twice as likely to land tails up than heads up and the second coin is
-  double-headed.  
-  \qed\end{example}
-
-Although specifying a probability for every event looks complex, a
-probability measure can be simply constructed by 
+of every collection of disjoint events (e.g., $\{HT\}\cup\{TH\}=\{HT,TH\}$)
+is the sum of the individual probabilities. The probability of collections
+of non-disjoint events (e.g., $\{HT,TH\}\cup\{TH,TT\}=\{HT,TH,TT\}$)
+may add to something different than the probabilities of the individual
+events. It is useful to think that this probability measure is completely
+determined by the two coins in question and their characteristics,
+in the sense that each pair of coins induces a measure, and each measure
+must correspond to some pair of coins. The measure above is induced
+by two coins such that the first coin is twice as likely to land tails
+up than heads up and the second coin is double-headed. \qed\end{example}
+
+Although specifying a probability measure for every event looks complex,
+it can be simply constructed by 
 \begin{equation}
@@
 \begin{thm}[Radon-Nikodym theorem for finite probability space~\cite{Kolmogorov1950,Swart2013}]
-For every probability measure~$\pmeas$, there exists an unique Radon-Nikodym
+For every probability measure~$\pmeas$, there exists a unique Radon-Nikodym
 derivative~$\rho$ such that equation~(\ref{eq:Radon-Nikodym})
@@
 we want to know its value, we can run $N$ independent trials. Let
-$x_{i}$ denote whether the event~$E$ occurs in the $i$-th trial
-or not, then $\pmeas(E)$ could be approximated to given accuracy
-by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability
-converging to one as $N$ goes to infinity. This fact is called the
-law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
+$x_{i}=1$ or $0$ denote whether the event~$E$ occurs in the $i$-th
+trial or not, respectively, then $\pmeas(E)$ could be approximated
+to given accuracy by the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$
+with the probability converging to one as $N$ goes to infinity, i.e.,
+. This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
 
@@
 spaced parallel lines a distance $h$ apart. It is a known fact that
-the probability of the needle crossing a line is
-$\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
+the probability of the needle crossing a line is $\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
 We analyze this situation in the mathematical framework of probability
@@
 
-To formalize the experiment, we consider an experimental setup
-consisting of a collection of $N$ identical needles of length
-$\ell$. We throw the $N$ needles one needle at a time, and observe the number
-$X$ of needles that cross a line. The sample space can be expressed as the set
-$\{X,-\}^N$
-of sequences of characters of length $N$ where each character is
-either $X$ to indicate a needle crossing a line or $-$ to indicate a
-needle not crossing a line. If $N=3$, the probability of the event that exactly
-2 needles cross lines~$\{-XX,X{-}X,XX-\}$ can be 
-estimated by the relative frequency~$\frac{2}{3}$. Generally, the probability of
-the event that exactly $M$ needles out of the $N$ total needles cross lines can
-be estimated by $\frac{M}{N}$.
+To formalize the experiment, we consider an experimental setup consisting
+of a collection of $N$ identical needles of length $\ell$. We throw
+the $N$ needles one needle at a time, and observe the number $M$
+of needles that cross a line. The sample space can be expressed as
+the set $\{X,-\}^{N}$ of sequences of characters of length $N$ where
+each character is either $X$ to indicate a needle crossing a line
+or $-$ to indicate a needle not crossing a line. If $N=3$, the probability
+of the event that exactly 2 needles cross lines~$\{-XX,X{-}X,XX-\}$
+can be estimated by the relative frequency~$\frac{2}{3}$. Generally,
+the probability of the event that exactly $M$ needles out of the
+$N$ total needles cross lines can be estimated by $\frac{M}{N}$.
 
@@
 results can have their relative frequencies converge almost surely
-to different limits~\cite{Marinacci1999,Teran2014}. In another word,
-to get a better approximation of the probability, the quality of experimental
-equipment cannot be compensated by the number of independent trials.
+to different limits~\cite{Marinacci1999,Teran2014}. In other words,
+to get a better approximation of the probability, the quality of the
+experimental equipment cannot be compensated by the number of independent
+trials.
 
@@
 %%%%%
-\subsection{Interval-valued probability measures}
+\subsection{Classical Interval-valued probability measures}
 
@@
 The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
-which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
+which we abbreviate $\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
 where the preposing $\mathscr{I}$ specifies we subtract intervals.
@@
 \item $\bar{\mu}(\Omega)=[1,1]$, 
-\item for every collection of pairwise disjoint events $\left\{ E_{i}\right\} ,\left\{ E_{i}'\right\} \subseteq\events$
-with $\Omega=\left(\bigcup_{i}E_{i}\right)\bigcup\left(\bigcup_{i}E_{i}'\right)$,
+\item for every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N}\subseteq\events$
+with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
 we have 
 \[
-\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i}}\sum r_{i}\right\} \right]\textrm{ ,}
+\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i}}\sum r_{i}\right\} \right]\textrm{ ,}
 \]
@@
 \item $\bar{\mu}(\Omega)=[1,1]$, 
-\item for any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$,
-and 
-\item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)$,
-where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
+\item for any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$,
+where $\Omega\backslash E$ is the complement event, and 
+\item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
+events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)$,
+where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
 We may drop the preposing $\mathscr{I}$ when summands are clearly
@@
 % \begin{itemize}
-% \item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\bar{\mu}\left(E_{i}\right)$. 
+% \item for a collection $E_{i}$ of pairwise disjoint events, we have $\bar{\mu}\left(\right)\subseteq\sum_{i}\bar{\mu}\left(E_{i}\right)$. 
 % \end{itemize}
-% This statement means that the evidences of $\bigcup_{i}E_{i}$ is
+% This statement means that the evidences of $$ is
 % at least as strong as putting all the evidences of $E_{i}$ together,
-% but some evidence may only be acquired for $\bigcup_{i}E_{i}$ as
-% the whole. Therefore, $\bar{\mu}\left(\bigcup_{i}E_{i}\right)$ is a
+% but some evidence may only be acquired for $$ as
+% the whole. Therefore, $\bar{\mu}\left(\right)$ is a
 % subset of $\sum_{i}\bar{\mu}\left(E_{i}\right)$, but may not equal.
@@
 \noindent We will explain why the last condition is expressed using
-$\subseteq$ by a small example.
+$\subseteq$ by the following.
 
@@
 
-The mathematical framework above assumes that there exists a
-predetermined set of events that are independent of the particular
-experiment. However, in many practical situations, the structure of
-the event space is only partially known and the precise dependence of
-two events on each other cannot, a priori, be determined with
-certainty. In the quantum framework, this partial knowledge is
-compounded by the fact that there exist non-commuting events which
-cannot happen simultaneously. To accommodate these more complex
-situations, we abandon the sample space~$\Omega$ and reason directly
-about events. A quantum probability space therefore consists of just
-two components: a set of events $\qevents$ and a probability measure
-$\mu : \qevents \rightarrow [0,1]$. We give an example before giving
-the formal definition.
-
-\begin{example}[One-qubit quantum probability space] 
-  Consider a one-qubit Hilbert space with states
-  $\alpha \ket{0} + \beta \ket{1}$ such that
-  $|\alpha|^2 + |\beta|^2 = 1$, $\alpha ,\beta \in \C$. The set of events
-  associated with this Hilbert space consists of all projection operators. Each event is
-  interpreted as a possible post-measurement state of a quantum system
-  in current state $\ket{\phi}$. For example, the event $\proj{0}$
-  indicates that the post-measurement state will be~$\ket{0}$; the
-  event $\proj{1}$ indicates that the post-measurement state will
-  be~$\ket{1}$; the event $\proj{\ps}$ where
-  $\ket{\ps} = \frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$ indicates that the
-  post-measurement state will be $\ket{\ps}$; the event
-  $\mathbb{1} = \proj{0}+\proj{1}$ indicates that the post-measurement
+The mathematical framework above assumes that there exists a predetermined
+set of events that are independent of the particular experiment. However,
+in many practical situations, the structure of the event space is
+only partially known and the precise dependence of two events on each
+other cannot, a priori, be determined with certainty. In the quantum
+framework, this partial knowledge is compounded by the fact that there
+exist non-commuting events which cannot happen simultaneously. To
+accommodate these more complex situations, we abandon the sample space~$\Omega$
+and reason directly about events. A quantum probability space therefore
+consists of just two components: a set of events $\qevents$ and a
+probability measure $\mu:\qevents\rightarrow[0,1]$. We present an
+example before giving the formal definition.
+
+\begin{example}[One-qubit quantum probability space] Consider
+a one-qubit Hilbert space with states $\ket{\phi}=\alpha\ket{0}+\beta\ket{1}$
+such that $|\alpha|^{2}+|\beta|^{2}=1$, $\alpha,\beta\in\C$. The
+set of events associated with this Hilbert space consists of all projection
+operators. Each event is interpreted as a possible post-measurement
+state of a quantum system in current state $\ket{\phi}$. For example,
+the event $\proj{0}$ indicates that the post-measurement state will
+be~$\ket{0}$; the event $\proj{1}$ indicates that the post-measurement
+state will be~$\ket{1}$; the event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
+indicates that the post-measurement state will be $\ket{\ps}$; the
+event $\mathbb{1}=\proj{0}+\proj{1}$ indicates that the post-measurement
 state will be a linear combination of $\ket{0}$ and $\ket{1}$; and
 the empty event $\mathbb{0}$ states that the post-measurement state
-  will be the empty state. As in the classical case, a probability
-  measure is a function that maps events to $[0,1]$: here is a partial
-  specification of a possible probability measure:
-\[\begin{array}{rcl}
-\mu\left(\mathbb{0}\right) = 0, \quad
-\mu\left(\mathbb{1}\right) =  1, \quad
-\mu\left(\proj{0}\right) = 1, \quad
-\mu\left(\proj{1}\right) = 0, \quad
-\mu\left(\proj{\ps}\right) = 1/2, \quad \ldots
-\end{array}\]
-Note that, similarly to the classical case, the probability of
-$\mathbb{1}$ is 1 and the probability of collections of orthogonal
-events (e.g., $\proj{0}+\proj{1}$) is the sum of the individual
-probabilities. A collection of non-orthogonal events
-(e.g., $\proj{0}$ and $\proj{\ps}$) is however not even a valid event.
-In the classical example, we argued that each probability measure is
-uniquely determined by two actual coins. A similar (but much more
-subtle) argument is valid also in the quantum case. By postulates of
-quantum mechanics and Gleason's theorem, it turns out that for large
-enough quantum systems, each probability measure is uniquely
-determined by an actual quantum state.
+will be the empty state. As in the classical case, a probability measure
+is a function that maps events to $[0,1]$: here is a partial specification
+of a possible probability measure: 
+\[
+\begin{array}{rcl}
+\mu\left(\mathbb{0}\right)=0,\quad\mu\left(\mathbb{1}\right)=1,\quad\mu\left(\proj{0}\right)=1,\quad\mu\left(\proj{1}\right)=0,\quad\mu\left(\proj{\ps}\right)=1/2,\quad\ldots\end{array}
+\]
+Note that, similarly to the classical case, the probability of $\mathbb{1}$
+is 1 and the probability of collections of orthogonal events (e.g.,
+$\proj{0}+\proj{1}$) is the sum of the individual probabilities.
+A collection of non-orthogonal events (e.g., $\proj{0}$ and $\proj{\ps}$)
+is however not even a valid event. In the classical example, we argued
+that each probability measure is uniquely determined by two actual
+coins. A similar (but much more subtle) argument is valid also in
+the quantum case. By postulates of quantum mechanics and Gleason's
+theorem, it turns out that for large enough quantum systems, each
+probability measure is uniquely determined by an actual quantum state.
 \qed\end{example}
@@
 \item A set of projections $P_{i}$ is called an \emph{ideal measurement}
-if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
+if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
 In this case, projections $P_{i}$ must be mutually orthogonal~\cite{Griffiths2003}.
@@
 
-\begin{definition}[Quantum Probability
-Measure~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
-Given a Hilbert space $\Hilb$ with its set of events~$\events$, a
-\emph{quantum probability measure} is a function~$\mu : \events \rightarrow
-[0,1]$ such that:\footnote {It is possible to define a more general space of events consisting of
-    all operators~$\mathcal{A}$ on $\Hilb$ and consider
-    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
-    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
-    the expectation value of $A$. We does not take this approach
-    because we want to focus only on probability. }
+\begin{definition}[Quantum Probability Measure~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
+Given a Hilbert space $\Hilb$ with its set of events~$\events$,
+a \emph{quantum probability measure} is a function~$\mu:\events\rightarrow[0,1]$
+such that:\footnote{It is possible to define a more general space of events consisting
+of all operators~$\mathcal{A}$ on $\Hilb$ and to extend $\mu$
+linearly to $\mathcal{A}$ and consider $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
+When an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$
+is the expectation value of $A$ which could bigger than one because
+$\mu$ is linear. We does not take this approach because we want to
+focus only on probability. } 
 \begin{itemize}
 \item $\mu(\mathbb{1})=1$, and 
-\item for mutually orthogonal projections $P_{i}$, we have 
-$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
+\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$. 
 \end{itemize}
@@
 \begin{lemma}\label{lem:quantumProbabilityMeasure}Given a Hilbert
-space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$ is a quantum probability
-measure if and only if $\mu$ satisfies the following conditions:
+space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$ is a quantum
+probability measure if and only if $\mu$ satisfies the following
+conditions: 
 \begin{itemize}
@@
 \item $\mu(\mathbb{1})=1$, 
-\item for any projection $P$,
-$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, and 
-\item for a set of mutually orthogonal projections $P_{i}$, we have
-$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
+\item for any projection $P$, $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$,
+and 
+\item for a set of mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$. 
 \end{itemize}
@@
 Moreover, the Born rule can be extended to a mixed state. When we
-prepares a state, suppose the probability of preparing state~$\ket{\phi_{j}}$
+prepare a state, suppose the probability of preparing state~$\ket{\phi_{j}}$
 is $q_{j}$, the state of the system can be expressed as a density
@@
 On one hand, $\mu$ is a quantum probability measure. Because $\mu$
-is almost the same as a quantum probability measure~$\mu_{\ket{0}}^{B}$,
+is almost the same as the quantum probability measure~$\mu_{\ket{0}}^{B}$,
 we only need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
@@
 
-Similar to the classical case, by applying the law of large number,
+Similar to the classical case, by applying the law of large numbers,
 quantum probabilities can be estimated by relative frequencies. For
@@
 If the field of strength does not perfectly direct to the $z$-axis,
-we does not really test the quantum event we want to test. This problem
+we do not really test the quantum event we want to test. This problem
 will be handled later when we introduce the discrete quantum theory.
@@
 \begin{equation}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Complement}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Complement}
 \end{equation}
@@
 \]
-$\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
+$\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
 and $\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)$,

### 2016-08-17 prob.tex
prob.tex Bound every free variables...

@@
 \item $\bar{\mu}(\Omega)=[1,1]$, 
-\item for every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N}\subseteq\events$
+\item for every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
 with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
@@
 \[
-\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i}}\sum r_{i}\right\} \right]\textrm{ ,}
+\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum r_{i}\right\} \right]\textrm{ ,}
 \]
@@
 \item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
-events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(E_{i}\right)$,
-where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
+events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\bar{\mu}\left(E_{i}\right)$,
+where $\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
 We may drop the preposing $\mathscr{I}$ when summands are clearly
@@
 means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators. 
-\item Conversely, every projection~$P$ can be expressed as
-$\tensor*[_{\mathscr{O}}]{\sum}{_j}\proj{\psi_{j}}$,
+\item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}\proj{\psi_{j}}$,
 where $P$ actually projects onto the linear subspace~$S$ which
-has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
+has an orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
 \end{itemize}
@@
 
-\begin{definition}[Ideal Measurement; Complement; Commutativity]~ 
+\begin{definition}{[}Ideal Measurement; Complement; Commutativity{]}~ 
 \begin{itemize}
-\item A set of projections $P_{i}$ is called an \emph{ideal measurement}
-if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
-In this case, projections $P_{i}$ must be mutually orthogonal~\cite{Griffiths2003}.
+\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is called
+an \emph{ideal measurement} if it is a partition of the identity,
+i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
+In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
+be mutually orthogonal~\cite{Griffiths2003}.
 \item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
@@
 \item $\mu(\mathbb{1})=1$, and 
-\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$. 
+\item for mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$. 
 \end{itemize}
@@
 and 
-\item for a set of mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$. 
+\item for a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$. 
 \end{itemize}
@@
 is $q_{j}$, the state of the system can be expressed as a density
-matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$, where $\sum_{j}q_{j}=1$.
+matrix~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\sum_{j=1}^{N}q_{j}=1$.
 Then, the quantum probability measure introduced by $\rho$ is the
@@
 \end{equation}
-\item for a set of mutually orthogonal projections $P_{i}$, we have 
+\item for a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have 
 \begin{equation}
-\bar{\mu}\left(\sideset{_{\mathscr{O}}}{_{i}}\sum P_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i}}\sum\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\bar{\mu}\left(\sideset{_{\mathscr{O}}}{_{i=1}^{N}}\sum P_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i=1}^{N}}\sum\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
 \end{equation}
@@
 $\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
-and $\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)$,
-where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
+and $\iota\left(\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum x_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i=1}^{N}}\sum\iota\left(x_{i}\right)$,
+where $x$ and $\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum x_{i}\in\left[0,1\right]$.
 By applying these two properties, it is easy to verify $\bar{\mu}$

### 2016-08-17 prob.tex
prob.tex Keep fixing small things suggested by Prof. Ortiz...

@@
 trial or not, respectively, then $\pmeas(E)$ could be approximated
-to given accuracy by the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$
+to given accuracy~$\epsilon>0$ by the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$
 with the probability converging to one as $N$ goes to infinity, i.e.,
-. This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
+\[
+\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sum_{i=1}^{N}x_{i}\right|<\epsilon\right)=1\textrm{ .}
+\]
+This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
 
 Suppose we drop a needle of length $\ell$ onto a floor made of equally
-spaced parallel lines a distance $h$ apart. It is a known fact that
-the probability of the needle crossing a line is $\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
+spaced parallel lines a distance $h$ apart, where $\ell<h$. It is
+a known fact that the probability of the needle crossing a line is
+$\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
 We analyze this situation in the mathematical framework of probability
@@
 
-\begin{definition}{[}Ideal Measurement; Complement; Commutativity{]}~ 
+\begin{definition}[Ideal Measurement; Complement; Commutativity]~ 
 \begin{itemize}
@@
 $\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
-and $\iota\left(\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum x_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i=1}^{N}}\sum\iota\left(x_{i}\right)$,
-where $x$ and $\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum x_{i}\in\left[0,1\right]$.
+and $\iota\left(\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\iota\left(x_{i}\right)$,
+where $x$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}\in\left[0,1\right]$.
 By applying these two properties, it is easy to verify $\bar{\mu}$

### 2016-08-18 prob.tex
prob.tex \section{Quantum Probability Spaces} Reorder the definition and example...

@@
 consists of just two components: a set of events $\qevents$ and a
-probability measure $\mu:\qevents\rightarrow[0,1]$. We present an
-example before giving the formal definition.
+probability measure $\mu:\qevents\rightarrow[0,1]$. To properly explain
+the quantum probability, we will first discuss projection operators
+as quantum events, provide an easy example, define quantum probability
+measures, and extend to quantum interval-valued probability.
+
+\subsection{Quantum Events}
+
+\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
+\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
+a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393},
+or an elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$
+onto a linear subspace~$S$ of $\Hilb$. The set of all events~$\events$
+can be defined recursively as follow: \footnote{``Projection'' is sometimes called ``orthogonal projection\textquotedbl{}
+or ``self-adjoint projection\textquotedbl{} to emphasize $P^{\dagger}=P$~\cite{Griffiths2003,Maassen2010}.} 
+\begin{itemize}
+\item $\mathbb{0}$ is a projection. 
+\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
+operator. 
+\item Projection operators $P_{1}$ and $P_{2}$ are \emph{orthogonal} if
+$P_{1}P_{2}=P_{2}P_{1}=\mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
+is also a projection operator if and only if they are orthogonal,
+where the preposing subscript $\mathscr{O}$ means $\tensor*[_{\mathscr{O}}]{+}{}$
+is an operation between operators. 
+\item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}\proj{\psi_{j}}$,
+where $P$ actually projects onto the linear subspace~$S$ which
+has an orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
+\end{itemize}
+\qed\end{definition}
+
+We present an example before giving the formal definition of quantum
+probability measures.
 
 \begin{example}[One-qubit quantum probability space] Consider
-a one-qubit Hilbert space with states $\ket{\phi}=\alpha\ket{0}+\beta\ket{1}$
-such that $|\alpha|^{2}+|\beta|^{2}=1$, $\alpha,\beta\in\C$. The
-set of events associated with this Hilbert space consists of all projection
-operators. Each event is interpreted as a possible post-measurement
-state of a quantum system in current state $\ket{\phi}$. For example,
-the event $\proj{0}$ indicates that the post-measurement state will
-be~$\ket{0}$; the event $\proj{1}$ indicates that the post-measurement
-state will be~$\ket{1}$; the event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
+a one-qubit Hilbert space with states $\ket{\phi}$, which can be
+expressed as a linear combination of $\ket{0}$ and $\ket{1}$, i.e.,
+$\ket{\phi}=\alpha\ket{0}+\beta\ket{1}$ such that $|\alpha|^{2}+|\beta|^{2}=1$,
+$\alpha,\beta\in\C$. The set of events associated with this Hilbert
+space consists of all projection operators. Each event is interpreted
+as a possible post-measurement state of a quantum system in current
+state $\ket{\phi}$. For example, the event $\proj{0}$ indicates
+that the post-measurement state will be $\ket{0}$; the event $\proj{1}$
+indicates that the post-measurement state will be $\ket{1}$; the
+event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
 indicates that the post-measurement state will be $\ket{\ps}$; the
-event $\mathbb{1}=\proj{0}+\proj{1}$ indicates that the post-measurement
-state will be a linear combination of $\ket{0}$ and $\ket{1}$; and
-the empty event $\mathbb{0}$ states that the post-measurement state
-will be the empty state. As in the classical case, a probability measure
-is a function that maps events to $[0,1]$: here is a partial specification
-of a possible probability measure: 
+event $\mathbb{1}=\proj{0}\tensor*[_{\mathscr{O}}]{+}{}\proj{1}$
+indicates that the post-measurement state will be a linear combination
+of $\ket{0}$ and $\ket{1}$; and the empty event $\mathbb{0}$ states
+that the post-measurement state will be the empty state. As in the
+classical case, a probability measure is a function that maps events
+to $[0,1]$: here is a partial specification of a possible probability
+measure: 
 \[
@@
 \qed\end{example}
-
-To properly explain the previous example and generalize to arbitrary
-quantum systems, we formally discuss projection operators, 
-define quantum probability measures, and extend to quantum interval-valued
-probability.
-
-\subsection{Quantum Events}
-
-\begin{definition}[Projection Operators;
-Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
-\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
-is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
-elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$.
-The set of all events can be defined recursively as follow:
-\footnote {``Projection'' is sometimes called
-``orthogonal projection" or ``self-adjoint projection" to
-emphasize $P^{\dagger} = P$~\cite{Griffiths2003,Maassen2010}.}
-\begin{itemize}
-\item $\mathbb{0}$ is a projection. 
-\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
-operator. 
-\item Projection operators $P_1$ and $P_2$ are \emph{orthogonal} if $P_1P_2 =
-  P_2P_1 = \mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
-is also a projection operator if and only if they are orthogonal, 
-where the preposing subscript $\mathscr{O}$
-means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators. 
-\item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}\proj{\psi_{j}}$,
-where $P$ actually projects onto the linear subspace~$S$ which
-has an orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
-\end{itemize}
-\qed\end{definition}
 

### 2016-08-18 prob.tex
prob.tex unifying the definitions...

@@
 it is the powerset~$2^{\Omega}=\left\{ E\middle|E\subseteq\Omega\right\} $.
+
+\begin{definition}[Probability Measure]\label{def:ClassicalProbabilitySpace}
 Given the set of events $\events$, a \emph{probability measure} is
@@
 \begin{itemize}
-\item $\pmeas(\Omega)=1$, and 
+\item $\pmeas(\emptyset)=0$. 
+\item $\pmeas(\Omega)=1$. 
+\item for any event $E$, 
+\begin{equation}
+\pmeas\left(\Omega\backslash E\right)=1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)\textrm{ ,}\label{eq:ClassicalReal-valuedProbability-Complement}
+\end{equation}
+where $\Omega\backslash E$ is the complement event, and $1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)$
+explicitly specifies $1$ and $\pmeas\left(E\right)\in\mathbb{R}$.
+Besides $\mathbb{R}$, we will prepose other symbols later to specify
+the type of operations, and they may be dropped when there is no ambiguity. 
 \item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
-events, $\pmeas(\bigcup_{i=1}^{N}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$,
-where $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$ explicitly
-specifies $\pmeas(E_{i})\in\mathbb{R}$. Besides $\mathbb{R}$, we
-will prepose other symbols later to specify the type of operations,
-and they may be dropped when there is no ambiguity. 
+events, $\pmeas(\bigcup_{i=1}^{N}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$.
+Similar to the above condition, $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$
+explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. 
 \end{itemize}
+\qed\end{definition}
+
+Notice that $\pmeas(\emptyset)=0$ and equation~(\ref{eq:ClassicalReal-valuedProbability-Complement})
+can be induced by other conditions. They are listed in here so that
+we can compare definition~\ref{def:ClassicalProbabilitySpace}, lemma~\ref{lem:classicalProbabilityMeasure},
+definition~\ref{def:QuantumProbabilitySpace}, and definition~\ref{def:QuantumInterval-valuedProbability}
+easily. We will compare these lemma and definitions when we try to
+formulate quantum interval-valued probability measures later.
 
@@
 \item for any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$,
-where $\Omega\backslash E$ is the complement event, and 
+and 
 \item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
@@
 
-We present an example before giving the formal definition of quantum
+Because quantum events are projection operators, operations and properties
+of quantum events can be written in terms of those of operators.
+
+\begin{definition}[Ideal Measurement; Complement; Commutativity]~ 
+\begin{itemize}
+\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is called
+an \emph{ideal measurement} if it is a partition of the identity,
+i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
+In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
+be mutually orthogonal~\cite{Griffiths2003}.
+\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
+is also a projection operator, called \emph{complement}. It is orthogonal
+to $P$, and corresponds to the complement event~$\Omega\backslash E$
+in classical probability~\cite{Griffiths2003}. 
+\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
+The product of two projection operators~$P_{1}P_{2}$ is also a projection
+operator if and only if they commute. This corresponds to the classical
+intersection between events~\cite{peres1995quantum,Griffiths2003}. 
+\item For two commuting projection operators $P_{1}$ and $P_{2}$, their
+\emph{disjunction}~$P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}$
+is defined to be $P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\tensor*[_{\mathscr{O}}]{-}{}P_{1}P_{2}$~\cite{Griffiths2003}. 
+\end{itemize}
+\qed\end{definition}
+
+Based on the above definition and properties of quantum events, we
+can present an example before giving the formal definition of quantum
 probability measures.
@@
 
-Because quantum events are projection operators, operations and properties
-of quantum events can be written in terms of those of operators.
-
-\begin{definition}[Ideal Measurement; Complement; Commutativity]~ 
-\begin{itemize}
-\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is called
-an \emph{ideal measurement} if it is a partition of the identity,
-i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
-In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
-be mutually orthogonal~\cite{Griffiths2003}.
-\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
-is also a projection operator, called \emph{complement}. It is orthogonal
-to $P$, and corresponds to the complement event~$\Omega\backslash E$
-in classical probability~\cite{Griffiths2003}. 
-\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
-The product of two projection operators~$P_{1}P_{2}$ is also a projection
-operator if and only if they commute. This corresponds to the classical
-intersection between events~\cite{peres1995quantum,Griffiths2003}. 
-\item For two commuting projection operators $P_{1}$ and $P_{2}$, their
-\emph{disjunction}~$P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}$
-is defined to be $P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\tensor*[_{\mathscr{O}}]{-}{}P_{1}P_{2}$~\cite{Griffiths2003}. 
-\end{itemize}
-\qed\end{definition}
-
 %%%%%
+
 \subsection{Quantum Real-valued Probability Measures}
@@
 \begin{itemize}
-\item $\mu(\mathbb{1})=1$, and 
-\item for mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$. 
-\end{itemize}
-\qed\end{definition}
-
-In order to motivate the definition of quantum interval-valued probability
-measures later, we provide an equivalent definition of quantum probability
-measures.
-
-\begin{lemma}\label{lem:quantumProbabilityMeasure}Given a Hilbert
-space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$ is a quantum
-probability measure if and only if $\mu$ satisfies the following
-conditions: 
-\begin{itemize}
 \item $\mu(\mathbb{0})=0$, 
 \item $\mu(\mathbb{1})=1$, 
-\item for any projection $P$, $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$,
+\item for any projection $P$, 
+\begin{equation}
+\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)\textrm{ ,}\label{eq:QuantumReal-valuedProbability-Complement}
+\end{equation}
 and 
@@
 \end{itemize}
-\qed\end{lemma}
-
-A set of events~$\events$ together with a quantum probability measure
-is called a \emph{quantum probability space}. Comparing to classical
-probability spaces, the empty set~$\emptyset$ corresponds to the
-empty projection~$\mathbb{0}$, and the event of whole space~$\Omega$
-corresponds to the identity projection~$\mathbb{1}$. In contrast,
-the union~$\cup$ of any two events always gives an event classically,
-but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$ of two
-projections may not be a projection. As the result, the classical
+\qed\end{definition}
+
+Similar to classical definition~\ref{def:ClassicalProbabilitySpace},
+$\mu(\mathbb{0})=0$ and equation~(\ref{eq:QuantumReal-valuedProbability-Complement})
+can be induced by other conditions. A set of events~$\events$ together
+with a quantum probability measure is called a \emph{quantum probability
+space}. Comparing to classical probability spaces, the empty set~$\emptyset$
+corresponds to the empty projection~$\mathbb{0}$, and the event
+of whole space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
+In contrast, the union~$\cup$ of any two events always gives an
+event classically, but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
+of two projections may not be a projection. As the result, the classical
 condition~$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
@@
 \end{eqnarray}
- which is basically the same as equation (\ref{eq:Radon-Nikodym}).
+which is basically the same as equation~(\ref{eq:Radon-Nikodym}).
 
@@
 using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
+By applying Gleason's theorem, we can extend definition~\ref{def:QuantumProbabilitySpace}
 to the following corollary.
@@
 dimension $d\geq3$, for any function~$\mu:\events\rightarrow[0,1]$
-satisfying the conditions listed in lemma~\ref{lem:quantumProbabilityMeasure},
+satisfying the conditions listed in definition~\ref{def:QuantumProbabilitySpace},
 there exists an unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{cor}
@@
 measure into the definition of quantum probability space for each
-ideal measurement, and get the following definition.
+ideal measurement.
+
+More specifically, for classical probability measures, definition~\ref{def:ClassicalProbabilitySpace}
+and lemma~\ref{lem:classicalProbabilityMeasure} are almost the same
+except the last condition using the equal sign~$=$ in real-valued
+definition~\ref{def:QuantumProbabilitySpace} and the subset equal
+sign~$\subseteq$ in interval-valued lemma~\ref{lem:classicalProbabilityMeasure}.
+Therefore, for quantum probability measures, replacing the the equal
+sign~$=$ in real-valued definition~\ref{def:QuantumProbabilitySpace}
+by the subset equal sign~$\subseteq$ gives the only reasonable definition
+for quantum interval-valued probability measures as follow.
 

### 2016-08-19 prob.tex
prob.tex \subsection{Radon-Nikodym and Gleason's Theorem} Add a section without type anything...
prob.tex \subsection{Measuring Quantum Probabilities: Ideal Case} Start.

@@
 
+%%%%%
+
+\subsection{Measuring Quantum Probabilities: Ideal Case}
+
+Similar to the classical case, by applying the law of large numbers,
+quantum probabilities can be estimated by relative frequencies. For
+example, if we want to know the probability of the spin up in the
+Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003},
+we can put a beam of silver atoms in a highly inhomogeneous magnetic
+field, and counting the number of atoms deflects up. Ideally, if the
+local field of strength directs to the $z$-axis, and all particles
+have the same velocity, the Stern-Gerlach experiment only produces
+two spots corresponding to $\ket{0}$ and $\ket{1}$. Notice that
+whenever the magnetic field of the Stern-Gerlach is fixed, i.e., an
+ideal measurement is picked, measuring the spin is exactly the same
+as tossing a coin. In another word, if somebody claims she is tossing
+a coin behind a veil, and only shows the resulting heads or tails,
+we cannot distinguish whether she has really tossed a coin, or she
+has run an Stern-Gerlach experiment, and shows us the head, the tail,
+or the side of coin if the silver atoms is spin up, spin down, or
+just hit the middle, respectively.
+
+Mathematically, given a Hilbert space~$\Hilb$ of dimension~$d$,
+if we pick a basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
+only consider the events~$\events'$ with the form $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in S}}\proj{\psi_{j}}$,
+where $S$ is the linear subspace $P$ projects onto, and fix a density
+matrix~$\rho$ representing in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
+The tuple~$\left(\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d},\events',\rho\right)$
+is essentially the same as an classical probability space~\cite{Maassen2010}.
+
 Notice that the mixed state~$\rho$ is really a generalization of
@@
 
-\begin{example}[One-qubit quantum probability measure] Consider
+\begin{example}{[}One-qubit quantum probability measure{]} Consider
 a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
@@
 %%%%%
-\subsection{Measuring Quantum Probabilities}
-
-Similar to the classical case, by applying the law of large numbers,
-quantum probabilities can be estimated by relative frequencies. For
-example, if we want to know the probability of the spin up in the
-Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003},
-we can put a beam of silver atoms in a highly inhomogeneous magnetic
-field, and counting the number of atoms deflects up. Ideally, if the
-local field of strength directs to the $z$-axis, and all particles
-have the same velocity, the Stern-Gerlach experiment only produces
-two spots corresponding to $\ket{0}$ and $\ket{1}$. In reality,
-we need a lot of resource to keep the local field of strength directing
-to the $z$-axis precisely, to keep the atoms having almost the same
-velocity, and to point out the exact position each particle landed
-on.
+
+\subsection{Measuring Quantum Probabilities: In Reality}
+
+In reality, we need a lot of resource to keep the local field of strength
+directing to the $z$-axis precisely, to keep the atoms having almost
+the same velocity, and to point out the exact position each particle
+landed on.
 
@@
 As mentioned above, each quantum event~$P$ will be associated with
-an interval-valued probability~$\left[l,r\right]$. Notice that whenever
-the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal measurement
-is picked, measuring the spin is exactly the same as tossing a coin.
-In another word, if somebody claims she is tossing a coin behind a
-veil, and only shows the resulting heads or tails, we cannot distinguish
-whether she has really tossed a coin, or she has run an Stern-Gerlach
-experiment, and shows us the head, the tail, or the side of coin if
-the silver atoms is spin up, spin down, or just hit the middle, respectively.
-Therefore, we should plug in the definition of interval-valued probability
-measure into the definition of quantum probability space for each
-ideal measurement.
+an interval-valued probability~$\left[l,r\right]$. Therefore, we
+should plug in the definition of interval-valued probability measure
+into the definition of quantum probability space for each ideal measurement.
 

### 2016-08-19 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities Ideally: Radon-Nikodym and Gleason's Theorem} updated...

--- 2016-08-18 prob.tex
@@
 \begin{equation}
-\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
+\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum f(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
 \end{equation}
-where $\rho:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum\rho(\omega)=1$,
-and $\rho$ is called the Radon-Nikodym derivative of $\pmeas$ (with
+where $f:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum f(\omega)=1$,
+and $f$ is called the Radon-Nikodym derivative of $\pmeas$ (with
 respect to the counting measure)~\cite{Nikodym1930,Folland2013}.
@@
 For every probability measure~$\pmeas$, there exists a unique Radon-Nikodym
-derivative~$\rho$ such that equation~(\ref{eq:Radon-Nikodym})
-holds.\qed\end{thm}
+derivative~$f$ such that equation~(\ref{eq:Radon-Nikodym}) holds.\qed\end{thm}
 
@@
 \begin{array}{rcl}
-\rho\left(HH\right)=1/3,\quad\rho\left(HT\right)=0,\quad\rho\left(TH\right)=2/3,\quad\rho\left(TT\right)=0\textrm{ .}\end{array}
+f\left(HH\right)=1/3,\quad f\left(HT\right)=0,\quad f\left(TH\right)=2/3,\quad f\left(TT\right)=0\textrm{ .}\end{array}
 \]
@@
 corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-to another set function~$\bar{\rho}:\events\rightarrow\bar{\mathscr{I}}$
+to another set function~$\bar{f}:\events\rightarrow\bar{\mathscr{I}}$
 which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman2013}.
@@
 \begin{itemize}
-\item $\mu(\mathbb{0})=0$, 
-\item $\mu(\mathbb{1})=1$, 
-\item for any projection $P$, 
+\item $\mu(\mathbb{0})=0$. 
+\item $\mu(\mathbb{1})=1$. 
+\item For any projection $P$, 
 \begin{equation}
-\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)\textrm{ ,}\label{eq:QuantumReal-valuedProbability-Complement}
+\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)\textrm{ .}\label{eq:QuantumReal-valuedProbability-Complement}
 \end{equation}
-and 
 \item for a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
@@
 is $q_{j}$, the state of the system can be expressed as a density
-matrix~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\sum_{j=1}^{N}q_{j}=1$.
-Then, the quantum probability measure introduced by $\rho$ is the
-combination of $\mu_{\phi_{j}}^{B}$ with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
+matrix~$\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}q_{j}\proj{\phi_{j}}$,
+where $\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}=1$. Then, the
+quantum probability measure introduced by $\rho$ is the combination
+of $\mu_{\phi_{j}}^{B}$ with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
 \begin{eqnarray}
-\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed}
+\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{j=1}^{N}}\sum q_{j}\mu_{\phi_{j}}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed}
 \end{eqnarray}
 
-Notice that the mixed state~$\rho$ is really a generalization of
-Radon-Nikodym derivative if we pick a basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
-such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in S}}\proj{\psi_{j}}$,
-where $S$ is the linear subspace $P$ projects onto. By representing
-the density matrix~$\rho$ in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$,
-the Born rule becomes
-\begin{eqnarray}
-\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\ket{\psi_{j}}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
-\end{eqnarray}
-which is basically the same as equation~(\ref{eq:Radon-Nikodym}).
-
-In this sense, the Radon-Nikodym theorem could be generalized to Gleason's
-theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}: in Hilbert
-spaces of dimension $d\geq3$, given a quantum probability measure
-$\mu$, there exist a mixed state~$\rho$ that induces such a measure
-using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+%%%%%
+
+\subsection{Measuring Quantum Probabilities Ideally: Radon-Nikodym and Gleason's
+Theorem}
+
+Similar to the classical case, by applying the law of large numbers,
+quantum probabilities can be estimated by relative frequencies. For
+example, if we want to know the probability of the spin up in the
+Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003},
+we can put a beam of silver atoms in a highly inhomogeneous magnetic
+field, and counting the number of atoms deflects up. Ideally, if the
+local field of strength directs to the $z$-axis, and all particles
+have the same velocity, the Stern-Gerlach experiment only produces
+two spots corresponding to $\ket{0}$ and $\ket{1}$. Notice that
+whenever the magnetic field of the Stern-Gerlach is fixed, i.e., an
+ideal measurement is picked, measuring the spin is exactly the same
+as tossing a coin. In another word, if somebody claims she is tossing
+a coin behind a veil, and only shows the resulting heads or tails,
+we cannot distinguish whether she has really tossed a coin, or she
+has run an Stern-Gerlach experiment, and shows us the head, the tail,
+or the side of coin if the silver atoms is spin up, spin down, or
+just hit the middle, respectively.
+
+Mathematically, given a Hilbert space~$\Hilb$ of dimension~$d$,
+we can pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
+and fix a density matrix~$\rho$ representing in the same basis,
+i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
+Applying the canonical inner product, we can define a Radon-Nikodym
+derivative~$f_{\rho}:\Omega\rightarrow[0,1]$ by
+\begin{equation}
+f_{\rho}\left(\ket{\psi_{j}}\right)=\ip{\psi_{j}}{\rho\psi_{j}}=r_{jj}\textrm{ .}\label{eq:quantum-Radon-Nikodym}
+\end{equation}
+Furthermore, we only consider the quantum events~$\events'$ with
+the form $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$,
+where $E\in2^{\Omega}$. The classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
+induced by the Radon-Nikodym derivative~$f_{\rho}$ is exactly the
+Born rule of the mixed state~$\rho$~\cite{Maassen2010}, 
+\begin{equation}
+\pmeas'\left(E\right)\overset{\left(\ref{eq:Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum f_{\rho}\left(\ket{\psi_{j}}\right)\overset{\left(\ref{eq:quantum-Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}=\Tr\left(\rho P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\mu_{\rho}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed-1}
+\end{equation}
+
+In this sense, the Radon-Nikodym derivative~$f_{\rho}$ is a special
+case of the mixed state~$\rho$, and the Radon-Nikodym theorem is
+a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}:
+in Hilbert spaces of dimension $d\geq3$, given a quantum probability
+measure $\mu$, there exist a mixed state~$\rho$ that induces such
+a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 By applying Gleason's theorem, we can extend definition~\ref{def:QuantumProbabilitySpace}
@@
 %%%%%
-\subsection{Measuring Quantum Probabilities}
-
-Similar to the classical case, by applying the law of large numbers,
-quantum probabilities can be estimated by relative frequencies. For
-example, if we want to know the probability of the spin up in the
-Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003},
-we can put a beam of silver atoms in a highly inhomogeneous magnetic
-field, and counting the number of atoms deflects up. Ideally, if the
-local field of strength directs to the $z$-axis, and all particles
-have the same velocity, the Stern-Gerlach experiment only produces
-two spots corresponding to $\ket{0}$ and $\ket{1}$. In reality,
-we need a lot of resource to keep the local field of strength directing
-to the $z$-axis precisely, to keep the atoms having almost the same
-velocity, and to point out the exact position each particle landed
-on.
-
-If the field of strength does not perfectly direct to the $z$-axis,
-we do not really test the quantum event we want to test. This problem
-will be handled later when we introduce the discrete quantum theory.
-Even if the field of strength perfectly directs to the $z$-axis,
-the variant velocity makes spots broader and more washed out. Together
-with the precision limit of the detector, it may sometimes be hard
-to decide a particle corresponding to which state\footnote{\yutsung{Add citations to support the idea... Haven't found suitable
-ones...}}. Similar to Buffon's needles, this kind of fuzziness can be taken
-into account by associating each quantum event with an interval-valued
-probability~$\left[l,r\right]$.
-
-\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}
-
-%%%%%
-
-\subsection{Quantum Interval-valued Probability Measures}
-
-As mentioned above, each quantum event~$P$ will be associated with
-an interval-valued probability~$\left[l,r\right]$. Notice that whenever
-the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal measurement
-is picked, measuring the spin is exactly the same as tossing a coin.
-In another word, if somebody claims she is tossing a coin behind a
-veil, and only shows the resulting heads or tails, we cannot distinguish
-whether she has really tossed a coin, or she has run an Stern-Gerlach
-experiment, and shows us the head, the tail, or the side of coin if
-the silver atoms is spin up, spin down, or just hit the middle, respectively.
-Therefore, we should plug in the definition of interval-valued probability
-measure into the definition of quantum probability space for each
-ideal measurement.
-
-More specifically, for classical probability measures, definition~\ref{def:ClassicalProbabilitySpace}
+
+\subsection{Measuring Quantum Probabilities in Reality: Quantum Interval-valued
+Probability Measures}
+
+In reality, a Stern-Gerlach experiment requires a lot of resource
+to keep the local field of strength directing to the $z$-axis precisely,
+to keep the atoms having almost the same velocity, and to point out
+the exact position each particle landed on. If the field of strength
+does not perfectly direct to the $z$-axis, we do not really test
+the quantum event we want to test. This problem will be handled later
+when we introduce the discrete quantum theory. Even if the field of
+strength perfectly directs to the $z$-axis, the variant velocity
+makes spots broader and more washed out. Together with the precision
+limit of the detector, it may sometimes be hard to decide a particle
+corresponding to which state\footnote{\yutsung{Add citations to support the idea... Haven't found suitable
+ones...}
+
+\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}} }.
+
+Similar to Buffon's needles, this kind of fuzziness can be taken into
+account by associating each quantum event with an interval-valued
+probability~$\left[l,r\right]$. Therefore, we should plug in the
+definition of interval-valued probability measure into the definition
+of quantum probability space for each ideal measurement. More specifically,
+for classical probability measures, definition~\ref{def:ClassicalProbabilitySpace}
 and lemma~\ref{lem:classicalProbabilityMeasure} are almost the same
@@
 \begin{itemize}
-\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$, 
-\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$, 
-\item for any projection $P$, 
+\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
+\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
+\item For any projection $P$, 
 \begin{equation}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Complement}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
 \end{equation}
-\item for a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
 we have 

### 2016-08-20 prob.tex
prob.tex \section{... Then?} Added...

@@
 
+\section{... Then?}
+
+\yutsung{Because theorem~\ref{def:EmptyCoreQuantumInterval-valuedProbability}
+gives a negative result, our original plan was to put the Mermin v.s.
+Meyer debate here, and move on to the discrete quantum probability
+measure. Then, discrete real-valued quantum probability measures are
+expected to fail because of John's proof, and we hope discrete interval-valued
+quantum probability measure can work in some sense?
+
+I just want to confirm whether we want to keep our original plan to
+move on to the discrete quantum probability measure. Because we don't
+really use $\mathbb{C}$ in example~\ref{ex:three-dimensional-three-value},
+I could expect example~\ref{ex:three-dimensional-three-value} is
+highly likely to serve as an counterexample for discrete interval-valued
+quantum probability measure...
+
+Some alternatives:
+\begin{enumerate}
+\item The importance of Gleason's theorem is that the Born rule could be
+deduced from other postulates. If the Gleason's theorem fails, we
+may still postulate the Born rule... But why? And this method doesn't
+really solve the problem in discrete quantum theories because there
+is no original Born rule...
+\item We may give up the idea of representing a quantum state as a density
+matrix. Actually, quantum probability people think quantum states
+are functions~\cite{Maassen2010,Swart2013,Hamhalter2013}, and Emanuel
+(Manny) Knill starts from C{*}-algebra when we talk about quantum
+measurement. Maybe reasoning quantum states as a function in every
+quantum phenomena is doable?
+\end{enumerate}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{comment}

### 2016-08-20 prob.tex
prob.tex \section{Quantum Computing on Quantum Interval-valued Probability Measures} Starting...

--- 2016-08-19 prob.tex
@@
 \usepackage{graphicx}
+\usepackage{verbatim}
 
@@
 \newcommand{\pr}[2]{\langle #1, #2 \rangle}
-\newcommand{\ket}[1]{|#1\rangle}
-\newcommand{\bra}[1]{\langle#1|}
-\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
 \newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
@@
 \newcommand{\ff}[1]{\mathbb{F}_{#1}}
-\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
 \newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
@@
 \newcommand{\rmi}{\mathrm{i}}
-\usepackage{verbatim}
+\usepackage[braket, qm]{qcircuit} 
+\newcommand{\xyR}[1]{\xymatrixrowsep={#1}}
+\newcommand{\xyC}[1]{\xymatrixcolsep={#1}}
 
@@
 
+\section{Quantum Computing on Quantum Interval-valued Probability Measures}
+
+We give up the idea of representing a quantum state as a density matrix,
+and compute the quantum state as a quantum interval-valued probability
+measure directly.
+
+%%%%%
+
+\subsection{Time Evolution and Tensor Product}
+
+In CQT, an time evolution operator~$U$ will map a state~$\ket{\phi}$
+to $U\ket{\phi}$. In this case, its quantum real-valued probability
+measure after evolution is
+\[
+\mu_{U\ket{\phi}}^{B}\left(P\right)=\ip{\phi}{U^{\dagger}PU\phi}=\mu_{\ket{\phi}}^{B}\left(U^{\dagger}PU\right)\textrm{ .}
+\]
+Hence, given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+the quantum interval-valued probability measure after time evolution
+operator~$U$ is defined as 
+\[
+\bar{\mu}_{U}\left(P\right)=\bar{\mu}\left(U^{\dagger}PU\right)\textrm{ .}
+\]
+
+%%%%%
+
+\subsection{Quantum Teleportation}
+
+\begin{figure}[t]
+\[
+\begin{array}{c}
+\hspace{1cm}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix@R=0.9em{ & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd]\\
+\lstick{\bar{\mu}} & \qw & \ctrl{1} & \qw & \gate{H} & \qw & \meter & \cw & \cw & \control\cw\\
+ & \qw & \targ & \qw & \qw & \qw & \meter & \cw & \control\cw & \cwx & \ar@{.}[dd]\\
+ & \qw & \qw & \qw & \qw & \qw & \qw & \qw & \gate{X}\cwx & \gate{Z}\cwx & \qw\\
+ & \push{\bar{\mu}_{0}} &  & \push{\bar{\mu}_{1}} &  & \push{\bar{\mu}_{2}} &  & \push{\bar{\mu}_{3}} &  &  & \push{\bar{\mu}_{4}}
+}
+\end{array}
+\]
+\caption{Circuit for Quantum Teleportation}
+
+\label{fig:QuantumTeleportation} 
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{comment}

### 2016-08-21 prob.tex
prob.tex Typed two possible plans...

@@
 
-\section{Quantum Computing on Quantum Interval-valued Probability Measures}
+\section{(One possible branch) Discrete Quantum Theory}
+
+\subsection{Discrete Quantum Real-valued Probability Measures}
+
+Killed by John... Need to be typed...
+
+\subsection{Discrete Quantum Interval-valued Probability Measures}
+
+\yutsung{Because theorem~\ref{def:EmptyCoreQuantumInterval-valuedProbability}
+gives a negative result, our original plan was to put the Mermin v.s.
+Meyer debate here, and move on to the discrete quantum probability
+measure. Then, discrete real-valued quantum probability measures are
+expected to fail because of John's proof, and we hope discrete interval-valued
+quantum probability measure can work in some sense?
+
+I just want to confirm whether we want to keep our original plan to
+move on to the discrete quantum probability measure. Because we don't
+really use $\mathbb{C}$ in example~\ref{ex:three-dimensional-three-value},
+I could expect example~\ref{ex:three-dimensional-three-value} is
+highly likely to serve as an counterexample for discrete interval-valued
+quantum probability measure...}
+
+\section{(Another possible branch) Quantum Computing on Quantum Interval-valued
+Probability Measures}
 
@@
 
-\subsection{Time Evolution and Tensor Product}
+\subsection{Time Evolution}
 
@@
 \]
+
+%%%%%
+
+\subsection{Tensor Product and Partial Measurement}
+
+\yutsung{Quantum Fubini Theorem? This might be hard?}
 

### 2016-08-21 prob.tex
prob.tex Updating...

--- 2016-08-20 prob.tex
@@
 
-\section{Quantum Computing on Quantum Interval-valued Probability Measures}
+\yutsung{I think there are two possible approaches to complete the
+story.
+
+Our original plan was to put the Mermin v.s. Meyer debate here, and
+move on to the discrete quantum probability measure. Then, discrete
+real-valued quantum probability measures are expected to fail because
+of John's proof, and we hope discrete interval-valued Gleason's theorem
+can work in some sense? This story might go to section~\ref{sec:DQT}.
+The problem of this approach is that Because we don't really use $\mathbb{C}$
+in example~\ref{ex:three-dimensional-three-value}, I could expect
+example~\ref{ex:three-dimensional-three-value} is highly likely
+to serve as an counterexample for discrete interval-valued Gleason's
+theorem...
+
+Another possible approach is to tell everybody: because Gleason's
+theorem is an accident, the original way to formulate to a quantum
+system as a state vector or density matrix is an accident. If we want
+to do thing correct, we should work on quantum (real/interval)-valued
+probability measure directly. This approach might go to section~\ref{sec:QC}.
+The problem of this approach is that we need an concrete example to
+show it is possible to work on quantum (real/interval)-valued probability
+measure directly. More precisely, we might need to verify tensor product
+and quantum teleportation works in this model...}
+
+\section{\label{sec:DQT}(One possible approach) Discrete Quantum Theory}
+
+\subsection{Discrete Quantum Real-valued Probability Measures}
+
+Killed by John... Need to be typed...
+
+\subsection{Discrete Quantum Interval-valued Probability Measures}
+
+Discrete interval-valued Gleason's theorem should be here, but we
+don't know whether it works or not... Might need to put some strange
+conditions to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.
+
+\section{\label{sec:QC}(Another possible approach) Quantum Computing on Quantum
+(Real/Interval)-valued Probability Measures}
 
 We give up the idea of representing a quantum state as a density matrix,
-and compute the quantum state as a quantum interval-valued probability
-measure directly.
+and compute the quantum state as a quantum (real/interval)-valued
+probability measure directly.
 
@@
 \]
+
+%%%%%
+
+\subsection{Tensor Product and Partial Measurement}
+
+\yutsung{Quantum Fubini Theorem?}
 

### 2016-08-21 prob.tex
prob.tex Fix some typos...

@@
 definition~\ref{def:QuantumProbabilitySpace}, and definition~\ref{def:QuantumInterval-valuedProbability}
-easily. We will compare these lemma and definitions when we try to
-formulate quantum interval-valued probability measures later.
+easily. We will compare these lemma and definitions when we formulate
+quantum interval-valued probability measures later.
 
@@
 trial or not, respectively, then $\pmeas(E)$ could be approximated
-to given accuracy~$\epsilon>0$ by the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$
+to given accuracy~$\epsilon>0$ by the relative frequency~$\frac{1}{N}\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}$
 with the probability converging to one as $N$ goes to infinity, i.e.,
 \[
-\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sum_{i=1}^{N}x_{i}\right|<\epsilon\right)=1\textrm{ .}
+\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum x_{i}\right|<\epsilon\right)=1\textrm{ .}
 \]
@@
 in example~\ref{ex:three-dimensional-three-value}, I could expect
-example~\ref{ex:three-dimensional-three-value} is highly likely
-to serve as an counterexample for discrete interval-valued Gleason's
-theorem...
+example~\ref{ex:three-dimensional-three-value} is likely to serve
+as an counterexample for discrete interval-valued Gleason's theorem...
 
@@
 system as a state vector or density matrix is an accident. If we want
-to do thing correct, we should work on quantum (real/interval)-valued
+to do things correct, we should work on quantum (real/interval)-valued
 probability measure directly. This approach might go to section~\ref{sec:QC}.
@@
 Discrete interval-valued Gleason's theorem should be here, but we
-don't know whether it works or not... Might need to put some strange
-conditions to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.
+don't know whether it works or not... Might need to put some extra-conditions
+(like \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
+is too small...) to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.
 

### 2016-08-22 prob.tex
prob.tex Updates here and there...

@@
 and the Dempster-Shafer plausibility as the right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
-Dempster-Shafer functions, also called \emph{completely or totally
+Dempster-Shafer functions, also called \emph{completely} or \emph{totally
 monotone}, plays an important role in the theory of non-additive belief.
@@
 
-\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]\label{thm:Shapley}
+\begin{thm}{[}Shapley~\cite{Shapley1965,GilboaSchmeidler1994}{]}\label{thm:Shapley}
 Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}
@@
 it would be better if we can find or prove a theorem which removes
-``convex'' in the theorem. However, I still have not found an example
-with an empty core or a real-valued probability measure in the core
-of each interval-valued probability measure. What we know:
+``convex'' in the theorem. However, I still have not found an interval-valued
+probability measure with an empty core or proved that each interval-valued
+probability measure has an nonempty core. What we know:
 \begin{enumerate}
@@
 measure written by Lodwick, including \cite{Lodwick2008}.
-\item About linear programming, the Mathematica program solving the case
-$\left|\Omega\right|=1$ or $2$ gives positive answer. The program
-ceases to respond when outputting $\left|\Omega\right|=3$. Maybe
-I should simplify the program?
+\item About linear programming, the answer of Mathematica program for $\left|\Omega\right|=3$
+is too complex to read by human. May need to simplify the result to
+a human readable one?
 \item Check whether the Shapley value still in the core or not in our setting...?
@@
 
+\[
+\left(\bar{\mu}_{1}\otimes\bar{\mu}_{2}\right)\left(P_{1}\otimes P_{2}\right)=\bar{\mu}_{1}\left(P_{1}\right)\bar{\mu}_{2}\left(P_{2}\right)?
+\]
+Is $\bar{\mu}_{1}\otimes\bar{\mu}_{2}$ still a quantum interval-valued
+probability measure?
+
+Might be hard, because let $\mu\otimes\mu$ is not a quantum real-valued
+probability measure, where $\mu$ is a non-Born real-valued probability
+measure for dimension 2.
+
 \yutsung{Quantum Fubini Theorem?}
@@
 \]
-\caption{Circuit for Quantum Teleportation}
-
-\label{fig:QuantumTeleportation} 
+\caption{\label{fig:QuantumTeleportation}Circuit for Quantum Teleportation}
 \end{figure}
+
+In figure~\ref{fig:QuantumTeleportation}, let $\ket{\phi}=\frac{1}{\sqrt{2}}\left(\ket{00}+\ket{11}\right)$.
+
+$\bar{\mu}_{0}=\bar{\mu}_{1}\otimes\mu_{\ket{\phi}}^{B}$. Notice
+that a quantum real-valued probability measure can be considered as
+an special case of quantum interval-valued probability measure.
 

### 2016-08-22 prob.tex
prob.tex Fix some typos, but still cannot make a story...

@@
 \end{equation}
-By Gleason's theorem, there is a mixed state~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$
-such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
-satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$ so that
-we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability measure~$\mu$.\qed\end{example}
+By Gleason's theorem, there is a mixed state~$\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}q_{j}\proj{\phi_{j}}$
+such that $\mu\left(P\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+where $\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}=1$ and $q_{j}>0$.
+However, no pure state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
+so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
+measure~$\mu$.\qed\end{example}
 
@@
 don't know whether it works or not... Might need to put some extra-conditions
-(like \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
-is too small...) to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.
+to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.
+
+Following are possible extra-conditions:
+\begin{enumerate}
+\item \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $} is
+too small...
+\item $\mu\otimes\mu$ is not a quantum real-valued probability measure,
+where $\mu$ is a non-Born real-valued probability measure for dimension
+2. Maybe embedding the small space into the bigger one could add extra-conditions
+to kill strange interval-valued probability measures?
+\end{enumerate}
 
@@
 
-Might be hard, because let $\mu\otimes\mu$ is not a quantum real-valued
+Might be hard, because $\mu\otimes\mu$ is not a quantum real-valued
 probability measure, where $\mu$ is a non-Born real-valued probability

### 2016-08-22 prob.tex
From: Tai, Yu-Tsung Sent: Monday, August 22, 2016 3:58 To: Ortiz, Gerardo <ortizg@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu>; Liu, Weihua <liuweih@indiana.edu> Subject: RE: can't come Mon am
Dear all, 

Fix almost everything pointed out last time, and scratch two possible
approaches to complete the story at the very end… Don’t know which one
is better or neither? 

Besides, Weihua Liu is interested in our research… so I invited him to
join our meeting next time…
He is a new post-doctor in Math, and has some backgrounds in quantum
probability, qu

@@
 \item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
-of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \pmeas:\events\rightarrow[0,1]\textrm{ probability measure}\middle|\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\forall E\in\events\right\} $
+of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
 \cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
@@
 \item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}\proj{\psi_{j}}$,
-where $P$ actually projects onto the linear subspace~$S$ which
-has an orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
+where $P$ actually projects onto the linear subspace~$S$ with an
+orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
 \end{itemize}
@@
 
-\begin{example}[One-qubit quantum probability space] Consider
+\begin{example}{[}One-qubit quantum probability space{]} Consider
 a one-qubit Hilbert space with states $\ket{\phi}$, which can be
@@
 classical case, a probability measure is a function that maps events
-to $[0,1]$: here is a partial specification of a possible probability
+to $[0,1]$. Here is a partial specification of a possible probability
 measure: 
@@
 
-\subsection{Measuring Quantum Probabilities Ideally: Radon-Nikodym and Gleason's
+\subsection{Measuring Quantum Probabilities Ideally: From Radon-Nikodym to Gleason's
 Theorem}
@@
 and fix a density matrix~$\rho$ representing in the same basis,
-i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
+i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
 Applying the canonical inner product, we can define a Radon-Nikodym
@@
 case of the mixed state~$\rho$, and the Radon-Nikodym theorem is
-a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}:
-in Hilbert spaces of dimension $d\geq3$, given a quantum probability
-measure $\mu$, there exist a mixed state~$\rho$ that induces such
-a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-By applying Gleason's theorem, we can extend definition~\ref{def:QuantumProbabilitySpace}
-to the following corollary.
-
-\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$ of
-dimension $d\geq3$, for any function~$\mu:\events\rightarrow[0,1]$
-satisfying the conditions listed in definition~\ref{def:QuantumProbabilitySpace},
-there exists an unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{cor}
+a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
+
+\begin{thm}{[}Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}{]}\label{cor:Gleason's}In
+a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
+measure~$\mu:\events\rightarrow[0,1]$, there exists an unique mixed
+state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{thm}
 
@@
 except the last condition using the equal sign~$=$ in real-valued
-definition~\ref{def:QuantumProbabilitySpace} and the subset equal
+definition~\ref{def:ClassicalProbabilitySpace} and the subset equal
 sign~$\subseteq$ in interval-valued lemma~\ref{lem:classicalProbabilityMeasure}.
@@
 by the subset equal sign~$\subseteq$ gives the only reasonable definition
-for quantum interval-valued probability measures as follow.
+for quantum interval-valued probability measures.
 
@@
 \begin{itemize}
-\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \mu:\events\rightarrow[0,1]\textrm{ quantum probability measure}\middle|\mu\left(P\right)\in\bar{\mu}\left(P\right)\forall P\in\events\right\} $.
+\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{quantum probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $.
 \item $\bar{\mu}$ is called convex if 
@@
 of John's proof, and we hope discrete interval-valued Gleason's theorem
-can work in some sense? This story might go to section~\ref{sec:DQT}.
-The problem of this approach is that Because we don't really use $\mathbb{C}$
-in example~\ref{ex:three-dimensional-three-value}, I could expect
-example~\ref{ex:three-dimensional-three-value} is likely to serve
-as an counterexample for discrete interval-valued Gleason's theorem...
+can work in some sense? This story is scratched in section~\ref{sec:DQT}.
+The problem is the discrete version of example~\ref{ex:three-dimensional-three-value}.
+Because we don't really use $\mathbb{C}$ in example~\ref{ex:three-dimensional-three-value},
+the discrete version of example~\ref{ex:three-dimensional-three-value}
+is likely to serve as an counterexample for discrete interval-valued
+Gleason's theorem... Hence, we may need to put some extra-conditions
+to by-pass the discrete version of example~\ref{ex:three-dimensional-three-value}.
 
@@
 to do things correct, we should work on quantum (real/interval)-valued
-probability measure directly. This approach might go to section~\ref{sec:QC}.
+probability measure directly. This approach is scratched in section~\ref{sec:QC}.
 The problem of this approach is that we need an concrete example to
 show it is possible to work on quantum (real/interval)-valued probability
-measure directly. More precisely, we might need to verify tensor product
+measure directly. For example, we might need to verify tensor product
 and quantum teleportation works in this model...}
@@
 
-Discrete interval-valued Gleason's theorem should be here, but we
-don't know whether it works or not... Might need to put some extra-conditions
-to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.
+Discrete interval-valued Gleason's theorem should be here, but it
+is unlikely to work if the discrete version of example~\ref{ex:three-dimensional-three-value}
+works... Might need to put some extra-conditions to by-pass it...
 
@@
 too small...
-\item $\mu\otimes\mu$ is not a quantum real-valued probability measure,
+\item $\mu\otimes\mu$ might not be a quantum real-valued probability measure,
 where $\mu$ is a non-Born real-valued probability measure for dimension
@@
 \]
-Hence, given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+Hence, given any quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
 the quantum interval-valued probability measure after time evolution
-operator~$U$ is defined as 
+operator~$U$ should be defined as 
 \[
@@
 
-Might be hard, because $\mu\otimes\mu$ is not a quantum real-valued
+Might be hard, because $\mu\otimes\mu$ might not be a quantum real-valued
 probability measure, where $\mu$ is a non-Born real-valued probability
@@
 
-\yutsung{Quantum Fubini Theorem?}
+Quantum Fubini Theorem?
 
@@
 that a quantum real-valued probability measure can be considered as
-an special case of quantum interval-valued probability measure.
+an special case of quantum interval-valued probability measure...
 

### 2016-09-02 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} Update footnotes...

@@
 such that~\cite{JamisonLodwick2004}:\footnote{The right-end of the interval-valued probability measure is a special
-case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman2013}.
-The left-end of the interval-valued probability measure is a special
-case of game~\cite{Shapley1965}.} 
+case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman2013}
+or outer measure~\cite{Folland2013}. The left-end of the interval-valued
+probability measure is a special case of game~\cite{Shapley1965}.} 
 \begin{itemize}
@@
 
-\begin{thm}{[}Shapley~\cite{Shapley1965,GilboaSchmeidler1994}{]}\label{thm:Shapley}
+\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]\label{thm:Shapley}
 Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}
@@
 
-\begin{example}{[}One-qubit quantum probability space{]} Consider
+\begin{example}[One-qubit quantum probability space] Consider
 a one-qubit Hilbert space with states $\ket{\phi}$, which can be
@@
 
-\begin{thm}{[}Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}{]}\label{cor:Gleason's}In
+\begin{thm}[Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
 a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability

### 2016-09-14 prob.tex
prob.tex \section{Classical Probability Spaces} Review and see how to add new things...

@@
 
-There is however another more subtle assumption of unbounded
-computational power in the experiment. We are assuming that we can
-always determine with certainty whether a needle is crossing a
-line. But ``lines'' on the the floor have thickness, their distance
-apart is not exactly $h$, and the needles lengths 
-are not all absolutely equal to $\ell$. These perturbations make
-the events ``fuzzy.'' Thus, in an experiment with limited resources,
-it is not possible to talk about the idealized event that exactly $M$
-needles cross lines as this would require the most expensive needles
-built to the most precise accuracy, laser precision for drawing lines
-on the floor, and the most powerful microscopes to determine if a
-needle does cross a line. Instead we might talk about the event that
-$M-\delta$ needles evidently cross lines and $M+\delta'$ needles
-plausibly cross lines where $\delta$ and $\delta'$ are
-resource-dependent approximations. This fuzzy notion of events leads
-to probabilities being only calculable within intervals of confidence
+There is however another more subtle assumption of unbounded computational
+power in the experiment. We are assuming that we can always determine
+with certainty whether a needle is crossing a line. But ``lines''
+on the the floor have thickness, their distance apart is not exactly
+$h$, and the needles' lengths are not all absolutely equal to $\ell$.
+These perturbations make the events ``fuzzy.'' Thus, in an experiment
+with limited resources, it is not possible to talk about the idealized
+event that exactly $M$ needles cross lines as this would require
+the most expensive needles built to the most precise accuracy, laser
+precision for drawing lines on the floor, and the most powerful microscopes
+to determine if a needle does cross a line. Instead we might talk
+about the event that $M-\delta$ needles evidently cross lines and
+$M+\delta'$ needles plausibly cross lines where $\delta$ and $\delta'$
+are resource-dependent approximations. This fuzzy notion of events
+leads to probabilities being only calculable within intervals of confidence
 reflecting the certainty of events and their plausibility. This is
@@
 $1213$ needles clearly crossed a line and $11$ needles were close
-enough to plausibly be considered as crossing the line: we would
-express the probability in this case as the interval
-$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we
-are certain that the event has probability at least
+enough to plausibly be considered as crossing the line: we would express
+the probability in this case as the interval $\left[\frac{1213}{3204},\frac{1224}{3204}\right]$
+expressing that we are certain that the event has probability at least
 $\frac{1213}{3204}$ but it is possible that it would have probability
@@
 \begin{lemma}\label{lem:classicalProbabilityMeasure}Given a sample
-space~$\Omega$ and its event~$\events$, a function~$\mu:\events\rightarrow[0,1]$
+space~$\Omega$ and its event~$\events$, a function~$\bar{\mu}:\events\rightarrow[0,1]$
 is a classical interval-valued probability measure if and only if
-$\mu$ satisfies the following conditions: 
+$\bar{\mu}$ satisfies the following conditions: 
 \begin{itemize}
@@
 \item $\bar{\mu}$ is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
-for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.\footnote{\yutsung{If we want to use convex, we need to explain the physical
-meaning of convex interval-valued probability measures...? If there
-is a good explanation, we may only consider convex interval-valued
-probability measures, and replace the definition in the beginning...?}}
+for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
 \end{itemize}

### 2016-09-16 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} Updating...

@@
 
-\yutsung{Because the physical meaning of convex is still not clear,
-it would be better if we can find or prove a theorem which removes
-``convex'' in the theorem. However, I still have not found an interval-valued
-probability measure with an empty core or proved that each interval-valued
-probability measure has an nonempty core. What we know:
+For the general interval-valued probability measures, the following
+theorem gives an algorithmic way to decide whether it has a non-empty
+core.
+
+\begin{thm}{[}Bondareva-Shapley~\cite{Shapley1967,Bondareva1968,Grabisch2016}{]}\label{thm:Bondareva-Shapley}
+Let $l$ be the left-end of an interval-valued probability measure~$\bar{\mu}$,
+$\bar{\mu}$ has an non-empty core if and only if for any minimal
+balanced set~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
+where:
 \begin{enumerate}
-\item The cloud in \cite{JamisonLodwick2004} cannot induce an interval-valued
-probability measure. Therefore, any results related to clouds cannot
-be used directly.
-\item The definition of interval-valued probability measure in \cite{JamisonLodwick2004}
-is different from any later definition of interval-valued probability
-measure written by Lodwick, including \cite{Lodwick2008}.
-\item About linear programming, the answer of Mathematica program for $\left|\Omega\right|=3$
-is too complex to read by human. May need to simplify the result to
-a human readable one?
-\item Check whether the Shapley value still in the core or not in our setting...?
+\item $\left\{ E_{i}\right\} _{i=1}^{N}$ is called balanced set if they
+are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$, and there exist
+positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$ such
+that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
+for all $\omega\in\Omega$.
+\item A minimal balanced set is one that includes on other balanced set.
 \end{enumerate}
-}
+\qed\end{thm}
+
+The Bondareva-Shapley theorem can be used to algorithmically decide
+non-empty core because the minimal balanced set can be generated by
+an algorithm~\cite{Peleg1965}.
 

### 2016-09-16 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} Updating...

@@
 \cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
-\item $\bar{\mu}$ is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
-for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
+\item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
+supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
+for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.
 \end{itemize}
@@
 
-\begin{thm}{[}Bondareva-Shapley~\cite{Shapley1967,Bondareva1968,Grabisch2016}{]}\label{thm:Bondareva-Shapley}
+\begin{thm}[Bondareva-Shapley~\cite{Shapley1967,Bondareva1968,Grabisch2016}]\label{thm:Bondareva-Shapley}
 Let $l$ be the left-end of an interval-valued probability measure~$\bar{\mu}$,
-$\bar{\mu}$ has an non-empty core if and only if for any minimal
-balanced set~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
-where:
-\begin{enumerate}
-\item $\left\{ E_{i}\right\} _{i=1}^{N}$ is called balanced set if they
-are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$, and there exist
-positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$ such
-that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
+$\bar{\mu}$ has a non-empty core if and only if for any minimal balanced
+set~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
+where $\left\{ E_{i}\right\} _{i=1}^{N}$ is called minimal balanced
+set if they are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$, and
+there exist a unique positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$
+such that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
 for all $\omega\in\Omega$.
-\item A minimal balanced set is one that includes on other balanced set.
-\end{enumerate}
+
 \qed\end{thm}
@@
 non-empty core because the minimal balanced set can be generated by
-an algorithm~\cite{Peleg1965}.
+an algorithm~\cite{Peleg1965}. However, the number of minimal balanced
+sets grows very rapidly with the size of $\Omega$, $\left|\Omega\right|$,
+so that we have only verified every interval-valued probability measure
+has a non-empty core when $\left|\Omega\right|\le5$ so far.
 

### 2016-09-17 prob.tex
prob.tex Updates here and there...

@@
 \item $\pmeas(\Omega)=1$. 
-\item for any event $E$, 
+\item For any event $E$, 
 \begin{equation}
@@
 the type of operations, and they may be dropped when there is no ambiguity. 
-\item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
 events, $\pmeas(\bigcup_{i=1}^{N}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$.
@@
 \begin{itemize}
-\item $\bar{\mu}(\emptyset)=[0,0]$, 
-\item $\bar{\mu}(\Omega)=[1,1]$, 
-\item for every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
+\item $\bar{\mu}(\emptyset)=[0,0]$. 
+\item $\bar{\mu}(\Omega)=[1,1]$. 
+\item For every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
 with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
@@
 \begin{itemize}
-\item $\bar{\mu}(\emptyset)=[0,0]$, 
-\item $\bar{\mu}(\Omega)=[1,1]$, 
-\item for any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$,
-and 
-\item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
+\item $\bar{\mu}(\emptyset)=[0,0]$.
+\item $\bar{\mu}(\Omega)=[1,1]$. 
+\item For any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$.
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
 events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\bar{\mu}\left(E_{i}\right)$,
@@
 
-For the general interval-valued probability measures, the following
-theorem gives an algorithmic way to decide whether it has a non-empty
-core.
+For general interval-valued probability measures, the following theorem
+gives an algorithmic way to decide whether it has a non-empty core.
 
@@
 $\bar{\mu}$ has a non-empty core if and only if for any minimal balanced
-set~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
+sets~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
 where $\left\{ E_{i}\right\} _{i=1}^{N}$ is called minimal balanced
-set if they are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$, and
-there exist a unique positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$
+sets if they are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$,
+and there exist a unique positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$
 such that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
-for all $\omega\in\Omega$.
-
-\qed\end{thm}
+for all $\omega\in\Omega$.\qed\end{thm}
 
 The Bondareva-Shapley theorem can be used to algorithmically decide
-non-empty core because the minimal balanced set can be generated by
-an algorithm~\cite{Peleg1965}. However, the number of minimal balanced
-sets grows very rapidly with the size of $\Omega$, $\left|\Omega\right|$,
+non-empty core because the minimal balanced sets can be generated
+by an algorithm~\cite{Peleg1965}. However, the number of minimal
+balanced sets grows very rapidly with $\left|\Omega\right|$, the
+size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially?}},
 so that we have only verified every interval-valued probability measure
@@
 
-\begin{definition}[Ideal Measurement; Complement; Commutativity]~ 
+\begin{definition}[Ideal Measurement; Complement; Commutativity;
+disjunction]~ 
 \begin{itemize}
@@
 \end{equation}
-\item for a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$. 
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$
+. 
 \end{itemize}
@@
 
-Mathematically, given a Hilbert space~$\Hilb$ of dimension~$d$,
-we can pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
-and fix a density matrix~$\rho$ representing in the same basis,
-i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
-Applying the canonical inner product, we can define a Radon-Nikodym
-derivative~$f_{\rho}:\Omega\rightarrow[0,1]$ by
+Mathematically, to fix the magnetic field of the Stern-Gerlach experiment
+is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
+for a given Hilbert space~$\Hilb$ of dimension~$d$. If the state
+of the silver atom is represented by a density matrix~$\rho$ written
+in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
+As we discussed in the last paragraph, the Born rule of the mixed
+state~$\rho$induces a classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
+on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
+be the quantum event corresponding to subspace span by $E$, we can
+have
 \begin{equation}
-f_{\rho}\left(\ket{\psi_{j}}\right)=\ip{\psi_{j}}{\rho\psi_{j}}=r_{jj}\textrm{ .}\label{eq:quantum-Radon-Nikodym}
+\pmeas'\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
 \end{equation}
-Furthermore, we only consider the quantum events~$\events'$ with
-the form $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$,
-where $E\in2^{\Omega}$. The classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
-induced by the Radon-Nikodym derivative~$f_{\rho}$ is exactly the
-Born rule of the mixed state~$\rho$~\cite{Maassen2010}, 
+By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
+of $\pmeas'$ $f:\Omega\rightarrow[0,1]$ is just the diagonal elements
+of $\rho$:
+
 \begin{equation}
-\pmeas'\left(E\right)\overset{\left(\ref{eq:Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum f_{\rho}\left(\ket{\psi_{j}}\right)\overset{\left(\ref{eq:quantum-Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}=\Tr\left(\rho P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\mu_{\rho}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed-1}
+f\left(\ket{\psi_{j}}\right)=r_{jj}\textrm{ .}\label{eq:quantum-Radon-Nikodym}
 \end{equation}
 
-In this sense, the Radon-Nikodym derivative~$f_{\rho}$ is a special
-case of the mixed state~$\rho$, and the Radon-Nikodym theorem is
-a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
+In this sense, the Radon-Nikodym derivative~$f$ is a special case
+of the density matrix~$\rho$, and the Radon-Nikodym theorem is a
+special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
 

### 2016-09-18 prob.tex
prob.tex Updating here and there...

@@
 balanced sets grows very rapidly with $\left|\Omega\right|$, the
-size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially?}},
-so that we have only verified every interval-valued probability measure
-has a non-empty core when $\left|\Omega\right|\le5$ so far.
+size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially
+or more?}}, so that we have only verified every interval-valued probability
+measure has a non-empty core when $\left|\Omega\right|\le5$ so far.\footnote{\yutsung{The program for $\left|\Omega\right|=6$ is running now.
+It seems that it will not blow up the memory, but I still have no
+idea when it will finish, and whether the result will be in our side
+or not...?}}
 
@@
 is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
-for a given Hilbert space~$\Hilb$ of dimension~$d$. If the state
-of the silver atom is represented by a density matrix~$\rho$ written
-in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
+for a given Hilbert space~$\Hilb$ of dimension~$d$, and the state
+of the silver atom can be represented by a density matrix~$\rho$
+written in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
 As we discussed in the last paragraph, the Born rule of the mixed
-state~$\rho$induces a classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
+state~$\rho$ induces a classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
 on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
@@
 By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
-of $\pmeas'$ $f:\Omega\rightarrow[0,1]$ is just the diagonal elements
-of $\rho$:
-
-\begin{equation}
-f\left(\ket{\psi_{j}}\right)=r_{jj}\textrm{ .}\label{eq:quantum-Radon-Nikodym}
-\end{equation}
-
-In this sense, the Radon-Nikodym derivative~$f$ is a special case
-of the density matrix~$\rho$, and the Radon-Nikodym theorem is a
-special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
+of $\pmeas'$ is $f\left(\ket{\psi_{j}}\right)=r_{jj}$, which is
+just the diagonal elements of $\rho$. In this sense, the Radon-Nikodym
+derivative~$f$ is a special case of the density matrix~$\rho$,
+and the Radon-Nikodym theorem is a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
 

### 2016-09-19 prob.tex
prob.tex \subsection{Recover an Interval-valued Born Rule(?)} Added...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum Probability Spaces}
+\section{\label{sec:Quantum-Probability-Spaces}Quantum Probability Spaces}
 
@@
 
-$\bar{\mu}$ cannot correspond to any quantum probability measure.
-Suppose $\mu(P)\in\bar{\mu}(P)$ for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
+Finally, we will prove that $\bar{\mu}$ cannot correspond to any
+quantum probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
+for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
 We must have 
@@
 
-\yutsung{I think there are two possible approaches to complete the
-story.
+\yutsung{I think there are three possible approaches to complete
+the story.
 
@@
 measure directly. For example, we might need to verify tensor product
-and quantum teleportation works in this model...}
-
+and quantum teleportation works in this model...
+
+The other approach might be keep going section~\ref{sec:Quantum-Probability-Spaces}...}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{sec:DQT}(One possible approach) Discrete Quantum Theory}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{sec:QC}(Another possible approach) Quantum Computing on Quantum
@@
 an special case of quantum interval-valued probability measure...
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }
+
+%%%%%
+
+\subsection{Recover an Interval-valued Born Rule(?)}
+
+Although not all interval-valued probability measure could correspond
+to any real-valued probability measure as in theorem~\ref{def:EmptyCoreQuantumInterval-valuedProbability},
+it does not mean we could not deduce an interval-valued Born rule.
+Notice that Gleason's theorem only says every real-valued probability
+measure can correspond to a mixed state by the Born rule, but does
+not specify the Born rule should be the only rule which corresponds
+a mixed state to a real-valued probability measure. For example, Gleason's
+theorem does not rule out the correspondence $\mu_{\phi}^{\prime B}(P)=\melem{0}{P}{0}$
+which send every state~$\ket{\phi}$ to the same real-valued probability
+measure. If we want to recover the Born rule itself, we need to more
+conditions to specify which state corresponds to which real-valued
+probability measure.
+
+\begin{thm}Consider\emph{ }$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $.
+There is a unique interval-valued Born rule~$\bar{\mu}^{B}:\left\{ \ket{\phi}\in\Hilb\middle|\ip{\phi}{\phi}=1\right\} \rightarrow\left(\events\rightarrow\mathscr{I}\right)$
+such that:
+\begin{itemize}
+\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}$ is an interval-valued
+probability measure.
+\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(\proj{\phi}\right)=\necess$.
+\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(P\right)=\bar{\mu}_{\mathbf{U}\ket{\phi}}^{B}\left(\mathbf{U}P\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
+$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
+\end{itemize}
+\qed\end{thm}
 

### 2016-09-19 prob.tex
From: Tai, Yu-Tsung Sent: Monday, September 19, 2016 1:32 To: Ortiz, Gerardo <ortizg@indiana.edu>; 'Amr Sabry (sabry@cs.indiana.edu)' <sabry@cs.indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu> Cc: Liu, Weihua <liuweih@indiana.edu> Subject: RE: ortizg@indiana.edu
Dear all,

I have just verified this week that every classical interval-valued probability measure (IVPM) has a non-empty core when the size of the sample space less or equal to 5… The program for the size of the sample space = 6 is running, but it requires to solve a linear programming (?) with 64 variables and about 815211 condi

@@
 
-The other approach might be keep going section~\ref{sec:Quantum-Probability-Spaces}...}
+The other approach might be keep going section~\ref{sec:Quantum-Probability-Spaces},
+but try to prove there is a unique interval-valued Born rule with
+extra-conditions. I sketched a possible set of conditions, but haven't
+verified whether it really works or not...}
 
@@
 \qed\end{thm}
-
+\begin{proof}
+? 
+\end{proof}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-09-23 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities in Reality: Quantum Interval-valued Probability Measures} Fix a typo...

@@
 \]
-$\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
+$\iota$ has two interesting properties $\iota\left(1\tensor*[_{\mathbb{R}}]{-}{}x\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
 and $\iota\left(\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\iota\left(x_{i}\right)$,

### 2016-09-23 prob.tex
prob.tex \section{\label{sec:Quantum-Probability-Spaces}Quantum Probability Spaces} Put operator types...?

@@
 we only need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
-$\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1$. On the other hand, $\mu$
-cannot be induced by any mixed state because $\mu(\proj{\ps})=\mu(\proj{0})=1$,
-and $\mu_{\rho}^{B}(P)=1$ if and only if $\rho$ represents a pure
-state and $\rho=P$. \qed\end{example}
+$\mu(\proj{\ps})\tensor*[_{\mathbb{R}}]{+}{}\mu(\proj{\ms})=1\tensor*[_{\mathbb{R}}]{+}{}0=1$.
+On the other hand, $\mu$ cannot be induced by any mixed state because
+$\mu(\proj{\ps})=\mu(\proj{0})=1$, and $\mu_{\rho}^{B}(P)=1$ if
+and only if $\rho$ represents a pure state and $\rho=P$. \qed\end{example}
 
@@
 \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps'}) & = & \necess\textrm{ ,}\\
 \bar{\mu}(P) & = & \unknown\textrm{, otherwise. }

### 2016-09-23 prob.tex
prob.tex Start typing some interpretation... (?)

@@
 \newtheorem{thm}{Theorem}
+\newtheorem{case}{Case}
 \newcommand{\events}{\ensuremath{\mathcal{E}}}
@@
 or more?}}, so that we have only verified every interval-valued probability
-measure has a non-empty core when $\left|\Omega\right|\le5$ so far.\footnote{\yutsung{The program for $\left|\Omega\right|=6$ is running now.
-It seems that it will not blow up the memory, but I still have no
-idea when it will finish, and whether the result will be in our side
-or not...?}}
+measure has a non-empty core when $\left|\Omega\right|\le5$ so far.\footnote{\yutsung{The program for $\left|\Omega\right|=6$ blows up the memory
+again, and the symmetric answer doesn't really work. Hence, currently
+only back-track randomized program still searches IVPM with a extremely
+slow speed...}}
 
@@
 As we discussed in the last paragraph, the Born rule of the mixed
-state~$\rho$ induces a classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
+state~$\rho$ induces a classical probability measure~$\pmeas^{\Omega}:2^{\Omega}\rightarrow[0,1]$
 on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
@@
 \begin{equation}
-\pmeas'\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
+\pmeas^{\Omega}\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
 \end{equation}
@@
 measure~$\mu$.\qed\end{example}
+
+Although theorem~\ref{thm:Shapley} and \ref{def:EmptyCoreQuantumInterval-valuedProbability}
+gives opposite results, their results are consistent. If we pick a
+orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
+let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
+be the quantum event corresponding to subspace span by $E$, we can
+define a classical interval-valued probability measure$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(P\right)$.
+There are two cases.
+
+\begin{case}If $\ket{\psi_{1}}$ is either $\ket{0}$, $\ket{\ps}$,
+or $\ket{\ps'}$, then we have
+
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \imposs\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
+\end{array} & \begin{array}{rcl}
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
+\end{array}\end{array}
+\]
+It is easy to verify that $\bar{\mu}^{\Omega}$ has an non-empty core,
+and $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$ is in
+its core. 
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas^{\Omega}(\emptyset) & = & 0\\
+\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 0\\
+\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/2\\
+\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/2
+\end{array} & \begin{array}{rcl}
+\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/2\\
+\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/2\\
+\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1\\
+\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
+\end{array}\end{array}
+\]
+\qed\end{case}
+
+\begin{case}If neither $\ket{0}$, $\ket{\ps}$, nor $\ket{\ps'}$
+is in $\Omega$, then we have
+
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
+\end{array} & \begin{array}{rcl}
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
+\end{array}\end{array}
+\]
+In this case, $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$
+defined by the following is in the core of $\bar{\mu}^{\Omega}$.
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas^{\Omega}(\emptyset) & = & 0\\
+\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/3
+\end{array} & \begin{array}{rcl}
+\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
+\end{array}\end{array}
+\]
+\qed\end{case}
 

### 2016-09-24 prob.tex
prob.tex Adding one more approach...

@@
 
-Although theorem~\ref{thm:Shapley} and \ref{def:EmptyCoreQuantumInterval-valuedProbability}
-gives opposite results, their results are consistent. If we pick a
-orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
-let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
-be the quantum event corresponding to subspace span by $E$, we can
-define a classical interval-valued probability measure$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(P\right)$.
-There are two cases.
-
-\begin{case}If $\ket{\psi_{1}}$ is either $\ket{0}$, $\ket{\ps}$,
-or $\ket{\ps'}$, then we have
-
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \imposs\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
-\end{array} & \begin{array}{rcl}
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
-\end{array}\end{array}
-\]
-It is easy to verify that $\bar{\mu}^{\Omega}$ has an non-empty core,
-and $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$ is in
-its core. 
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\pmeas^{\Omega}(\emptyset) & = & 0\\
-\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 0\\
-\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/2\\
-\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/2
-\end{array} & \begin{array}{rcl}
-\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/2\\
-\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/2\\
-\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1\\
-\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
-\end{array}\end{array}
-\]
-\qed\end{case}
-
-\begin{case}If neither $\ket{0}$, $\ket{\ps}$, nor $\ket{\ps'}$
-is in $\Omega$, then we have
-
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
-\end{array} & \begin{array}{rcl}
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
-\end{array}\end{array}
-\]
-In this case, $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$
-defined by the following is in the core of $\bar{\mu}^{\Omega}$.
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\pmeas^{\Omega}(\emptyset) & = & 0\\
-\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/3
-\end{array} & \begin{array}{rcl}
-\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
-\end{array}\end{array}
-\]
-\qed\end{case}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{proof}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }
+
+%%%%%
+
+\subsection{Question the original assumption(?)}
+
+Although theorem~\ref{thm:Shapley} and \ref{def:EmptyCoreQuantumInterval-valuedProbability}
+gives opposite results, their results are consistent. If we pick a
+orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
+let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
+be the quantum event corresponding to subspace span by $E$, we can
+define a classical interval-valued probability measure$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(P\right)$.
+There are two cases.
+
+\begin{case}If $\ket{\psi_{1}}$ is either $\ket{0}$, $\ket{\ps}$,
+or $\ket{\ps'}$, then we have
+
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \imposs\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
+\end{array} & \begin{array}{rcl}
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
+\end{array}\end{array}
+\]
+It is easy to verify that $\bar{\mu}^{\Omega}$ has an non-empty core,
+and $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$ is in
+its core. 
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas^{\Omega}(\emptyset) & = & 0\\
+\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 0\\
+\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/2\\
+\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/2
+\end{array} & \begin{array}{rcl}
+\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/2\\
+\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/2\\
+\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1\\
+\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
+\end{array}\end{array}
+\]
+\qed\end{case}
+
+\begin{case}If neither $\ket{0}$, $\ket{\ps}$, nor $\ket{\ps'}$
+is in $\Omega$, then we have
+
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
+\end{array} & \begin{array}{rcl}
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \unknown\\
+\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
+\end{array}\end{array}
+\]
+In this case, $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$
+defined by the following is in the core of $\bar{\mu}^{\Omega}$.
+\[
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\pmeas^{\Omega}(\emptyset) & = & 0\\
+\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/3
+\end{array} & \begin{array}{rcl}
+\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1/3\\
+\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
+\end{array}\end{array}
+\]
+\qed\end{case}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }
+
+If we compare the counterexample in example~\ref{ex:three-dimensional-three-value}
+and \ref{ex:three-dimensional-4-value}, we found example~\ref{ex:three-dimensional-4-value}
+is not as bad as example~\ref{ex:three-dimensional-three-value}.
+At least, the states map to $\imposs$ are all in the same plane in
+example~\ref{ex:three-dimensional-4-value}. Maybe interval-valued
+probability measures will be closer and closer to real-valued probability
+measures if the intervals are more and more precise?
+
+%%%%%
+
+\subsection{Examples for Quantum Interval-valued Probability Measures}
+
+The following example verify the core of a quantum interval-valued
+probability measure is nonempty even if there is no natural correspondence.
+For example, if $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+there is no natural way to map from $\frac{1}{2}$, as both $\frac{1}{2}\in\left[0,\frac{1}{2}\right]=\unlikely$
+and $\frac{1}{2}\in\left[\frac{1}{2},1\right]=\likely$. However,
+we still can find a quantum interval-valued probability measure corresponding
+to a quantum probability measure as in the following example.
+
+\begin{example}[One-qubit quantum interval-valued probability measure]\label{ex:One-qubit-quantum-interval}
+Given a two dimensional Hilbert space, a vector $\ket{\psi}$ can
+be normalized and written in $\left(\begin{array}{c}
+\cos\theta\\
+\rme^{\rmi\gamma}\sin\theta
+\end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Consider
+a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+defined by 
+\begin{eqnarray*}
+\bar{\mu}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(\proj{\psi}) & = & \begin{cases}
+\necess & \textrm{, if }\theta=0\textrm{ ;}\\
+\likely & \textrm{, if }0<\theta<\frac{\pi}{4}\textrm{ ;}\\
+\likely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }0\le\gamma<\pi\textrm{ ;}\\
+\unlikely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }\pi\le\gamma<2\pi\textrm{ ;}\\
+\unlikely & \textrm{, if }\frac{\pi}{4}<\theta<\frac{\pi}{2}\textrm{ ;}\\
+\imposs & \textrm{, if }\theta=\frac{\pi}{2}\textrm{ .}
+\end{cases}
+\end{eqnarray*}
+Let $\ket{\psi^{\perp}}$ be the state perpendicular to $\ket{\psi}$.
+Then, the vector representation of $\ket{\psi^{\perp}}$ can be simplified
+as 
+\[
+\left(\begin{array}{c}
+-\rme^{-\rmi\gamma}\sin\theta\\
+\cos\theta
+\end{array}\right)=-\rme^{-\rmi\gamma}\left(\begin{array}{c}
+\cos\left(\frac{\pi}{2}-\theta\right)\\
+\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)
+\end{array}\right)
+\]
+so we have 
+\[
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi}\right)=\bar{\mu}\left(\proj{\psi^{\perp}}\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(\proj{\psi}\right)\textrm{ .}
+\]
+Hence, $\bar{\mu}$ is a quantum $\mathscr{I}$-interval-valued probability
+measure. Notice that for all projection~$P$, $\mu_{\ket{0}}^{B}(P)\in\bar{\mu}(P)$
+implies that $\bar{\mu}(P)$ is one of quantum $\mathscr{I}$-interval-valued
+probability measures corresponding to $\mu_{\ket{0}}^{B}(P)$. However,
+$\mu_{\ket{0}}^{B}(P)$ can correspond to infinity many quantum $\mathscr{I}$-interval-valued
+probability measures by twisting the definition involving $\gamma$.\qed\end{example}
+
+We are going to provide an quantum 4-value interval-valued probability
+measures corresponding to no quantum probability measure, i.e., $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.
+In general, we believe this kind of quantum $\mathscr{I}$-interval-valued
+probability measure exists for any finite set of interval~$\mathscr{I}$.
+
+\begin{example}[Three-dimensional quantum 4-value interval-valued
+probability measure]\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify this example is convex!}}Given
+a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$,
+and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}$
+defined as follow: 
+\begin{enumerate}
+\item $\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$
+and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess$. 
+\item Consider the states orthogonal to $\ket{0}$ and $\ket{\ps}$ respectively,
+$\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
+where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Half of
+those states need special treatment, i.e., when where $0\le\theta<\frac{\pi}{2}$
+and $0\le\gamma<\pi$, we define $\bar{\mu}(\proj{0_{\theta,\gamma}^{\perp}})=\ket{\ps_{\theta,\gamma}^{\perp}}=\likely$
+and $\bar{\mu}(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}})=\bar{\mu}(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}})=\unlikely$. 
+\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
+\end{enumerate}
+$\bar{\mu}$ cannot correspond to any quantum probability measure
+because of the exact same reason as in example~\ref{ex:three-dimensional-three-value}.
+Before we verify that $\bar{\mu}$ is a quantum interval-valued probability
+measure, we need a notation for cross product. For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
+\alpha_{1}\\
+\alpha_{2}
+\end{pmatrix}$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\begin{pmatrix}\beta_{0}\\
+\beta_{1}\\
+\beta_{2}
+\end{pmatrix}$, their cross product is defined as follow. 
+\[
+\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\begin{vmatrix}\alpha_{1}^{*} & \beta_{1}^{*}\\
+\alpha_{2}^{*} & \beta_{2}^{*}
+\end{vmatrix}\ket{0}+\begin{vmatrix}\alpha_{2}^{*} & \beta_{2}^{*}\\
+\alpha_{0}^{*} & \beta_{0}^{*}
+\end{vmatrix}\ket{1}+\begin{vmatrix}\alpha_{0}^{*} & \beta_{0}^{*}\\
+\alpha_{1}^{*} & \beta_{1}^{*}
+\end{vmatrix}\ket{2}\textrm{ ,}
+\]
+where $\begin{vmatrix}\alpha & \beta\\
+\alpha' & \beta'
+\end{vmatrix}=\alpha\beta'-\alpha'\beta$. Notice that we put the complex conjugate in the cross product, so
+that the result of cross product is orthogonal to $\ket{\psi}$ and
+$\ket{\phi}$. 
+\begin{eqnarray*}
+\ip{\psi\times\phi}{\psi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}=0\textrm{ ,}\\
+\ip{\psi\times\phi}{\phi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}=0\textrm{ .}
+\end{eqnarray*}
+Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
+cross product~$\ket{\psi\times\phi}$ need not be normalized as usual.
+
+To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
+it is sufficient to check 
+\begin{equation}
+\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{3}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
+\end{aligned}
+\label{eq:non-additive-vectors}
+\end{equation}
+for every orthonormal basis $\mathcal{B}=\left\{ \ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\right\} $.
+We are going to enumerate all possible orthonormal bases to verify
+the equations, and case 1 and 2 are illustrated in figure~\ref{fig:three-dimensional-4-value}.
+\begin{figure}
+\includegraphics{\string"Three-dimensional quantum 4-value interval-valued probability measure\string".pdf}\caption{\label{fig:three-dimensional-4-value}This figure illustrates case
+1 and 2 in $\mathbb{R}^{3}$ in example~\ref{ex:three-dimensional-4-value}.
+The red and green dotted vector are $\ket{0}$ and $\ket{\ps}$ respectively.
+All possible vectors of $\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
+are drawn in the red and green circles, respectively. Within the circles,
+a vector~$\ket{\psi}$ in dotted part means $\bar{\mu}(\proj{\psi})=\likely$;
+otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
+a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
+and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
+and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
+\end{figure}
+
+\begin{enumerate}
+\item When $\ket{\psi_{1}}$ is $\ket{0}$, then $\ket{\psi_{2}}$ and $\ket{\psi_{3}}$
+must be $\ket{0_{\theta,\gamma}^{\perp}}$ for some $\theta$ and
+$\gamma$. Because of 
+\[
+\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
+0\\
+0
+\end{pmatrix}\times\begin{pmatrix}0\\
+\rme^{\rmi\gamma}\sin\theta\\
+\cos\theta
+\end{pmatrix}=\begin{pmatrix}0\\
+-\cos\theta\\
+\rme^{-\rmi\gamma}\sin\theta
+\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}0\\
+\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
+\cos\left(\frac{\pi}{2}-\theta\right)
+\end{pmatrix}=\rme^{-\rmi\gamma}\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
+\]
+the pair $\ket{\psi_{2}}=\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\psi_{3}}=\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}$
+for ($0<\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$) or $\theta=0$
+enumerate all possible orthonormal bases. Equation (\ref{eq:non-additive-vectors})
+can be verified as follow. 
+\begin{eqnarray*}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}\right)=\necess & \subseteq & \likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & = & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\imposs=\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)=\likely & = & \imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
+\end{eqnarray*}
+Similarly, when $\ket{\psi_{1}}$ is $\ket{\ps}$, equation (\ref{eq:non-additive-vectors})
+holds. 
+\item When $\ket{0}\notin\mathcal{B}$ and $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$
+for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we want to
+prove $\bar{\mu}\left(\proj{\psi_{2}}\right)=\bar{\mu}\left(\proj{\psi_{3}}\right)=\unlikely$.
+Then, we have 
+\begin{eqnarray*}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
+\end{eqnarray*}
+In order to verify $\bar{\mu}\left(\proj{\psi_{2}}\right)=\bar{\mu}\left(\proj{\psi_{3}}\right)=\unlikely$,
+it is sufficient to prove that $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$
+implies ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or
+$\theta'=\frac{\pi}{2}$. Recall $\ip{\ps}{\ps_{\theta',\gamma'}^{\perp}}=0$.
+Hence, if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$, we
+have $\ket{\ps_{\theta',\gamma'}^{\perp}}$ parallel to $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$.
+\[
+\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
+1\\
+0
+\end{pmatrix}\times\begin{pmatrix}0\\
+\rme^{\rmi\gamma}\sin\theta\\
+\cos\theta
+\end{pmatrix}=\begin{pmatrix}\cos\theta\\
+-\cos\theta\\
+\rme^{-\rmi\gamma}\sin\theta
+\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
+\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
+\cos\left(\frac{\pi}{2}-\theta\right)
+\end{pmatrix}=\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
+\]
+Because of $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we have
+($0<\theta'=\frac{\pi}{2}-\theta<\frac{\pi}{2}$ and $\pi\le\gamma'=\pi+\gamma<2\pi$)
+or $\theta'=\frac{\pi}{2}-\theta=\frac{\pi}{2}$. Similarly, when
+$\ket{\psi_{1}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$ and $\ket{\ps}\notin\mathcal{B}$,
+equation (\ref{eq:non-additive-vectors}) holds. 
+\item Finally, when $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$,
+$\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$, and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
+for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, i.e., the ``otherwise''
+case. Then, equation (\ref{eq:non-additive-vectors}) can easily be
+verified. 
+\begin{eqnarray*}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)
+\end{eqnarray*}
+\end{enumerate}
+\qed\end{example}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-09-24 prob.tex
prob.tex Clean up the macros...

@@
 \newcommand{\Hilb}{\mathcal{H}}
-\newcommand{\pr}[2]{\langle #1, #2 \rangle}
-\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
 \newcommand{\ps}{\texttt{+}}
@@
 \newcommand{\rmi}{\mathrm{i}}
-\usepackage[braket, qm]{qcircuit} 
+\usepackage[braket]{qcircuit} 
 \newcommand{\xyR}[1]{\xymatrixrowsep={#1}}
 \newcommand{\xyC}[1]{\xymatrixcolsep={#1}}
+\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}
+\newcommand{\melem}[3]{\ensuremath{\left\langle{#1}\middle\vert{#2}\middle\vert{#3}\right\rangle}}
+\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
+\newcommand{\pr}[2]{\ip{#1}{#2}}
+\newcommand{\proj}[1]{\op{#1}{#1}}
 
@@
 If we compare the counterexample in example~\ref{ex:three-dimensional-three-value}
-and \ref{ex:three-dimensional-4-value}, we found example~\ref{ex:three-dimensional-4-value}
-is not as bad as example~\ref{ex:three-dimensional-three-value}.
-At least, the states map to $\imposs$ are all in the same plane in
-example~\ref{ex:three-dimensional-4-value}. Maybe interval-valued
+and \ref{ex:three-dimensional-4-value}, we find that example~\ref{ex:three-dimensional-three-value}
+really use the property of $\unknown$ so that it cannot hold when
+the intervals are more precise. Also, example~\ref{ex:three-dimensional-4-value}
+is not as bad as example~\ref{ex:three-dimensional-three-value}
+in a sense that the states map to $\imposs$ are all in the same plane
+in example~\ref{ex:three-dimensional-4-value}. Maybe interval-valued
 probability measures will be closer and closer to real-valued probability
@@
 \subsection{Examples for Quantum Interval-valued Probability Measures}
-
-The following example verify the core of a quantum interval-valued
-probability measure is nonempty even if there is no natural correspondence.
-For example, if $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-there is no natural way to map from $\frac{1}{2}$, as both $\frac{1}{2}\in\left[0,\frac{1}{2}\right]=\unlikely$
-and $\frac{1}{2}\in\left[\frac{1}{2},1\right]=\likely$. However,
-we still can find a quantum interval-valued probability measure corresponding
-to a quantum probability measure as in the following example.
-
-\begin{example}[One-qubit quantum interval-valued probability measure]\label{ex:One-qubit-quantum-interval}
-Given a two dimensional Hilbert space, a vector $\ket{\psi}$ can
-be normalized and written in $\left(\begin{array}{c}
-\cos\theta\\
-\rme^{\rmi\gamma}\sin\theta
-\end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Consider
-a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-defined by 
-\begin{eqnarray*}
-\bar{\mu}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1}) & = & \necess\textrm{ ,}\\
-\bar{\mu}(\proj{\psi}) & = & \begin{cases}
-\necess & \textrm{, if }\theta=0\textrm{ ;}\\
-\likely & \textrm{, if }0<\theta<\frac{\pi}{4}\textrm{ ;}\\
-\likely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }0\le\gamma<\pi\textrm{ ;}\\
-\unlikely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }\pi\le\gamma<2\pi\textrm{ ;}\\
-\unlikely & \textrm{, if }\frac{\pi}{4}<\theta<\frac{\pi}{2}\textrm{ ;}\\
-\imposs & \textrm{, if }\theta=\frac{\pi}{2}\textrm{ .}
-\end{cases}
-\end{eqnarray*}
-Let $\ket{\psi^{\perp}}$ be the state perpendicular to $\ket{\psi}$.
-Then, the vector representation of $\ket{\psi^{\perp}}$ can be simplified
-as 
-\[
-\left(\begin{array}{c}
--\rme^{-\rmi\gamma}\sin\theta\\
-\cos\theta
-\end{array}\right)=-\rme^{-\rmi\gamma}\left(\begin{array}{c}
-\cos\left(\frac{\pi}{2}-\theta\right)\\
-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)
-\end{array}\right)
-\]
-so we have 
-\[
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi}\right)=\bar{\mu}\left(\proj{\psi^{\perp}}\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(\proj{\psi}\right)\textrm{ .}
-\]
-Hence, $\bar{\mu}$ is a quantum $\mathscr{I}$-interval-valued probability
-measure. Notice that for all projection~$P$, $\mu_{\ket{0}}^{B}(P)\in\bar{\mu}(P)$
-implies that $\bar{\mu}(P)$ is one of quantum $\mathscr{I}$-interval-valued
-probability measures corresponding to $\mu_{\ket{0}}^{B}(P)$. However,
-$\mu_{\ket{0}}^{B}(P)$ can correspond to infinity many quantum $\mathscr{I}$-interval-valued
-probability measures by twisting the definition involving $\gamma$.\qed\end{example}
 
@@
 \end{enumerate}
-$\bar{\mu}$ cannot correspond to any quantum probability measure
-because of the exact same reason as in example~\ref{ex:three-dimensional-three-value}.
 Before we verify that $\bar{\mu}$ is a quantum interval-valued probability

### 2016-09-25 prob.tex
"Three-dimensional quantum 4-value interval-valued probability measure.pdf" Updated...

@@
 
-If we compare the counterexample in example~\ref{ex:three-dimensional-three-value}
-and \ref{ex:three-dimensional-4-value}, we find that example~\ref{ex:three-dimensional-three-value}
+If we examine our examples more carefully, we find that example~\ref{ex:three-dimensional-three-value}
 really use the property of $\unknown$ so that it cannot hold when
-the intervals are more precise. Also, example~\ref{ex:three-dimensional-4-value}
-is not as bad as example~\ref{ex:three-dimensional-three-value}
-in a sense that the states map to $\imposs$ are all in the same plane
-in example~\ref{ex:three-dimensional-4-value}. Maybe interval-valued
-probability measures will be closer and closer to real-valued probability
-measures if the intervals are more and more precise?
+the intervals are more precise; example~\ref{ex:three-dimensional-4-value}
+also cannot work with any interval-values more precise than $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
+Also, example~\ref{ex:three-dimensional-4-value} is not as bad as
+example~\ref{ex:three-dimensional-three-value} in a sense that the
+$\imposs$ states are all in the same plane in example~\ref{ex:three-dimensional-4-value}
+while the $\imposs$ states are not in the same plane in example~\ref{ex:three-dimensional-4-value}.
+Maybe interval-valued probability measures will be closer and closer
+to real-valued probability measures if the intervals are more and
+more precise?
 
@@
 $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$,
-and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}$
-defined as follow: 
+and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+defined as follow. When the event is a 1-dimensional projector~$\proj{\psi}$,
+it is also illustrated in figure~\ref{fig:three-dimensional-4-value}.
 \begin{enumerate}
 \item $\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$
-and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess$. 
+and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess$,
+where $\proj{0}$ and $\proj{\ps}$ is illustrated as the red and
+green dotted vector, respectively.
 \item Consider the states orthogonal to $\ket{0}$ and $\ket{\ps}$ respectively,

### 2016-09-25 prob.tex
prob.tex "\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }" Keep updating...

@@
 the intervals are more precise; example~\ref{ex:three-dimensional-4-value}
-also cannot work with any interval-values more precise than $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
+also cannot work with any interval values more precise than $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
 Also, example~\ref{ex:three-dimensional-4-value} is not as bad as
@@
 measures corresponding to no quantum probability measure, i.e., $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.
-In general, we believe this kind of quantum $\mathscr{I}$-interval-valued
-probability measure exists for any finite set of interval~$\mathscr{I}$.
 
@@
 \item $\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$
-and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess$,
-where $\proj{0}$ and $\proj{\ps}$ is illustrated as the red and
-green dotted vector, respectively.
+and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps})=\necess$,
+where $\ket{0}$ and $\ket{\ps}$ is illustrated as the red and green
+dotted vector, respectively.
 \item Consider the states orthogonal to $\ket{0}$ and $\ket{\ps}$ respectively,
@@
 and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
-where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. Half of
-those states need special treatment, i.e., when where $0\le\theta<\frac{\pi}{2}$
-and $0\le\gamma<\pi$, we define $\bar{\mu}(\proj{0_{\theta,\gamma}^{\perp}})=\ket{\ps_{\theta,\gamma}^{\perp}}=\likely$
-and $\bar{\mu}(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}})=\bar{\mu}(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}})=\unlikely$. 
-\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
+where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. $\ket{0_{\theta,\gamma}^{\perp}}$
+and $\ket{\ps_{\theta,\gamma}^{\perp}}$ are points in the red and
+green circles, and perpendicular to $\ket{0}$ and $\ket{\ps}$, respectively.
+The dotted half of those states need special treatment, i.e., when
+where $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define
+\begin{eqnarray*}
+\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely\textrm{ .}
+\end{eqnarray*}
+\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely$. 
 \end{enumerate}
 Before we verify that $\bar{\mu}$ is a quantum interval-valued probability
-measure, we need a notation for cross product. For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
+measure, we need a notation of cross product. For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
 \alpha_{1}\\

### 2016-09-25 prob.tex
prob.tex \subsection{Examples for Quantum Interval-valued Probability Measures} Updating...

@@
 and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-defined as follow. When the event is a 1-dimensional projector~$\proj{\psi}$,
-it is also illustrated in figure~\ref{fig:three-dimensional-4-value}.
+defined as follow, where the state vectors corresponding to 1-dimensional
+projector are also illustrated in figure~\ref{fig:three-dimensional-4-value}.
 \begin{enumerate}
-\item $\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$
-and $\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps})=\necess$,
+\item We have 
+\begin{eqnarray*}
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \necess\textrm{ ,}
+\end{eqnarray*}
  where $\ket{0}$ and $\ket{\ps}$ is illustrated as the red and green
@@
 and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
-where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. $\ket{0_{\theta,\gamma}^{\perp}}$
-and $\ket{\ps_{\theta,\gamma}^{\perp}}$ are points in the red and
-green circles, and perpendicular to $\ket{0}$ and $\ket{\ps}$, respectively.
+where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$, as the
+red and green circles in figure~\ref{fig:three-dimensional-4-value}.
 The dotted half of those states need special treatment, i.e., when
@@
 \end{enumerate}
+Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$.
+Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
+and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
+we must have is $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
+so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
+\[
+\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
+\]
+A contradiction! Hence, we have $\mu(P)\notin\bar{\mu}(P)$ for all
+quantum probability measure~$\mu$.
+
 Before we verify that $\bar{\mu}$ is a quantum interval-valued probability
@@
 \beta_{2}
-\end{pmatrix}$, their cross product is defined as follow. 
+\end{pmatrix}$, their cross product is defined as follow:
 \[
@@
 
-To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
-it is sufficient to check 
+Similar to example~\ref{ex:three-dimensional-three-value}, to verify
+$\bar{\mu}$ is a quantum interval-valued probability measure, we
+only need to verify equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+and it is sufficient to check 
 \begin{equation}

### 2016-09-26 prob.tex
prob.tex "\subsection{Examples for Quantum Interval-valued Probability Measures}" Updating...

@@
 We are going to provide an quantum 4-value interval-valued probability
-measures corresponding to no quantum probability measure, i.e., $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.
+measures corresponding to no quantum probability measure, i.e., for
+all mixed state~$\rho$ there is a $P\in\events$ such that $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.
 
 \begin{example}[Three-dimensional quantum 4-value interval-valued
-probability measure]\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify this example is convex!}}Given
+probability measure]\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify whether this example is convex or not.}}Given
 a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
@@
 \begin{enumerate}
-\item We have 
+\item Let 
 \begin{eqnarray*}
@@
 dotted vector, respectively.
-\item Consider the states orthogonal to $\ket{0}$ and $\ket{\ps}$ respectively,
-$\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+\item Consider the red and green circles in figure~\ref{fig:three-dimensional-4-value}.
+They are the states orthogonal to $\ket{0}$ and $\ket{\ps}$, respectively,
+and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
 and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
-where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$, as the
-red and green circles in figure~\ref{fig:three-dimensional-4-value}.
-The dotted half of those states need special treatment, i.e., when
-where $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define
+where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
+half of those states need special treatment, i.e., when where $0\le\theta<\frac{\pi}{2}$
+and $0\le\gamma<\pi$, we define 
 \begin{eqnarray*}
@@
 \end{enumerate}
-Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$.
-Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
+That $\bar{\mu}$ has an empty core can be proved by contradiction.
+Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
+for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
 and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
-we must have is $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
+we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
 so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
@@
 \]
-A contradiction! Hence, we have $\mu(P)\notin\bar{\mu}(P)$ for all
-quantum probability measure~$\mu$.
 
@@
 Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
-cross product~$\ket{\psi\times\phi}$ need not be normalized as usual.
+cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
+as usual.
 
@@
 We are going to enumerate all possible orthonormal bases to verify
-the equations, and case 1 and 2 are illustrated in figure~\ref{fig:three-dimensional-4-value}.
+equation~(\ref{eq:non-additive-vectors}), and case 1 and 2 are illustrated
+in figure~\ref{fig:three-dimensional-4-value}. 
 \begin{figure}
@@
 \begin{enumerate}
-\item When $\ket{\psi_{1}}$ is $\ket{0}$, then $\ket{\psi_{2}}$ and $\ket{\psi_{3}}$
-must be $\ket{0_{\theta,\gamma}^{\perp}}$ for some $\theta$ and
-$\gamma$. Because of 
+\item When $\ket{\psi_{1}}$ is $\ket{0}$, then either $\ket{\psi_{2}}$
+or $\ket{\psi_{3}}$ must be $\ket{0_{\theta,\gamma}^{\perp}}$ for
+some $\theta$ and $\gamma$. Because of 
 \[
@@
 enumerate all possible orthonormal bases. Equation (\ref{eq:non-additive-vectors})
-can be verified as follow. 
+can then be verified as follow. 
 \begin{eqnarray*}

### 2016-09-27 prob.tex
prob.tex After meeting, delete the wrong(?) stories...

@@
 \newtheorem{case}{Case}
+\newtheorem{conjecture}{Conjecture}
 \newcommand{\events}{\ensuremath{\mathcal{E}}}
@@
 only back-track randomized program still searches IVPM with a extremely
-slow speed...}}
+slow speed...}} Based on the previous fact, we have the following conjecture.
+
+\begin{conjecture}Every interval-valued probability measure has a
+nonempty core.\qed\end{conjecture}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\yutsung{I think there are three possible approaches to complete
-the story.
-
-Our original plan was to put the Mermin v.s. Meyer debate here, and
-move on to the discrete quantum probability measure. Then, discrete
-real-valued quantum probability measures are expected to fail because
-of John's proof, and we hope discrete interval-valued Gleason's theorem
-can work in some sense? This story is scratched in section~\ref{sec:DQT}.
-The problem is the discrete version of example~\ref{ex:three-dimensional-three-value}.
-Because we don't really use $\mathbb{C}$ in example~\ref{ex:three-dimensional-three-value},
-the discrete version of example~\ref{ex:three-dimensional-three-value}
-is likely to serve as an counterexample for discrete interval-valued
-Gleason's theorem... Hence, we may need to put some extra-conditions
-to by-pass the discrete version of example~\ref{ex:three-dimensional-three-value}.
-
-Another possible approach is to tell everybody: because Gleason's
-theorem is an accident, the original way to formulate to a quantum
-system as a state vector or density matrix is an accident. If we want
-to do things correct, we should work on quantum (real/interval)-valued
-probability measure directly. This approach is scratched in section~\ref{sec:QC}.
-The problem of this approach is that we need an concrete example to
-show it is possible to work on quantum (real/interval)-valued probability
-measure directly. For example, we might need to verify tensor product
-and quantum teleportation works in this model...
-
-The other approach might be keep going section~\ref{sec:Quantum-Probability-Spaces},
-but try to prove there is a unique interval-valued Born rule with
-extra-conditions. I sketched a possible set of conditions, but haven't
-verified whether it really works or not...}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{sec:DQT}(One possible approach) Discrete Quantum Theory}
-
-\subsection{Discrete Quantum Real-valued Probability Measures}
-
-Killed by John... Need to be typed...
-
-\subsection{Discrete Quantum Interval-valued Probability Measures}
-
-Discrete interval-valued Gleason's theorem should be here, but it
-is unlikely to work if the discrete version of example~\ref{ex:three-dimensional-three-value}
-works... Might need to put some extra-conditions to by-pass it...
-
-Following are possible extra-conditions:
-\begin{enumerate}
-\item \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $} is
-too small...
-\item $\mu\otimes\mu$ might not be a quantum real-valued probability measure,
-where $\mu$ is a non-Born real-valued probability measure for dimension
-2. Maybe embedding the small space into the bigger one could add extra-conditions
-to kill strange interval-valued probability measures?
-\end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{sec:QC}(Another possible approach) Quantum Computing on Quantum
-(Real/Interval)-valued Probability Measures}
-
-We give up the idea of representing a quantum state as a density matrix,
-and compute the quantum state as a quantum (real/interval)-valued
-probability measure directly.
-
-%%%%%
-
-\subsection{Time Evolution}
-
-In CQT, an time evolution operator~$U$ will map a state~$\ket{\phi}$
-to $U\ket{\phi}$. In this case, its quantum real-valued probability
-measure after evolution is
-\[
-\mu_{U\ket{\phi}}^{B}\left(P\right)=\ip{\phi}{U^{\dagger}PU\phi}=\mu_{\ket{\phi}}^{B}\left(U^{\dagger}PU\right)\textrm{ .}
-\]
-Hence, given any quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-the quantum interval-valued probability measure after time evolution
-operator~$U$ should be defined as 
-\[
-\bar{\mu}_{U}\left(P\right)=\bar{\mu}\left(U^{\dagger}PU\right)\textrm{ .}
-\]
-
-%%%%%
-
-\subsection{Tensor Product and Partial Measurement}
-
-\[
-\left(\bar{\mu}_{1}\otimes\bar{\mu}_{2}\right)\left(P_{1}\otimes P_{2}\right)=\bar{\mu}_{1}\left(P_{1}\right)\bar{\mu}_{2}\left(P_{2}\right)?
-\]
-Is $\bar{\mu}_{1}\otimes\bar{\mu}_{2}$ still a quantum interval-valued
-probability measure?
-
-Might be hard, because $\mu\otimes\mu$ might not be a quantum real-valued
-probability measure, where $\mu$ is a non-Born real-valued probability
-measure for dimension 2.
-
-Quantum Fubini Theorem?
-
-%%%%%
-
-\subsection{Quantum Teleportation}
-
-\begin{figure}[t]
-\[
-\begin{array}{c}
-\hspace{1cm}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix@R=0.9em{ & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd]\\
-\lstick{\bar{\mu}} & \qw & \ctrl{1} & \qw & \gate{H} & \qw & \meter & \cw & \cw & \control\cw\\
- & \qw & \targ & \qw & \qw & \qw & \meter & \cw & \control\cw & \cwx & \ar@{.}[dd]\\
- & \qw & \qw & \qw & \qw & \qw & \qw & \qw & \gate{X}\cwx & \gate{Z}\cwx & \qw\\
- & \push{\bar{\mu}_{0}} &  & \push{\bar{\mu}_{1}} &  & \push{\bar{\mu}_{2}} &  & \push{\bar{\mu}_{3}} &  &  & \push{\bar{\mu}_{4}}
-}
-\end{array}
-\]
-\caption{\label{fig:QuantumTeleportation}Circuit for Quantum Teleportation}
-\end{figure}
-
-In figure~\ref{fig:QuantumTeleportation}, let $\ket{\phi}=\frac{1}{\sqrt{2}}\left(\ket{00}+\ket{11}\right)$.
-
-$\bar{\mu}_{0}=\bar{\mu}_{1}\otimes\mu_{\ket{\phi}}^{B}$. Notice
-that a quantum real-valued probability measure can be considered as
-an special case of quantum interval-valued probability measure...
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }
-
-%%%%%
-
-\subsection{Recover an Interval-valued Born Rule(?)}
-
-Although not all interval-valued probability measure could correspond
-to any real-valued probability measure as in theorem~\ref{def:EmptyCoreQuantumInterval-valuedProbability},
-it does not mean we could not deduce an interval-valued Born rule.
-Notice that Gleason's theorem only says every real-valued probability
-measure can correspond to a mixed state by the Born rule, but does
-not specify the Born rule should be the only rule which corresponds
-a mixed state to a real-valued probability measure. For example, Gleason's
-theorem does not rule out the correspondence $\mu_{\phi}^{\prime B}(P)=\melem{0}{P}{0}$
-which send every state~$\ket{\phi}$ to the same real-valued probability
-measure. If we want to recover the Born rule itself, we need to more
-conditions to specify which state corresponds to which real-valued
-probability measure.
-
-\begin{thm}Consider\emph{ }$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $.
-There is a unique interval-valued Born rule~$\bar{\mu}^{B}:\left\{ \ket{\phi}\in\Hilb\middle|\ip{\phi}{\phi}=1\right\} \rightarrow\left(\events\rightarrow\mathscr{I}\right)$
-such that:
-\begin{itemize}
-\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}$ is an interval-valued
-probability measure.
-\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(\proj{\phi}\right)=\necess$.
-\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(P\right)=\bar{\mu}_{\mathbf{U}\ket{\phi}}^{B}\left(\mathbf{U}P\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
-$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
-\end{itemize}
-\qed\end{thm}
-\begin{proof}
-? 
-\end{proof}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }
-
-%%%%%
-
-\subsection{Question the original assumption(?)}
-
-Although theorem~\ref{thm:Shapley} and \ref{def:EmptyCoreQuantumInterval-valuedProbability}
-gives opposite results, their results are consistent. If we pick a
-orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
-let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
-be the quantum event corresponding to subspace span by $E$, we can
-define a classical interval-valued probability measure$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(P\right)$.
-There are two cases.
-
-\begin{case}If $\ket{\psi_{1}}$ is either $\ket{0}$, $\ket{\ps}$,
-or $\ket{\ps'}$, then we have
-
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \imposs\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
-\end{array} & \begin{array}{rcl}
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
-\end{array}\end{array}
-\]
-It is easy to verify that $\bar{\mu}^{\Omega}$ has an non-empty core,
-and $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$ is in
-its core. 
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\pmeas^{\Omega}(\emptyset) & = & 0\\
-\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 0\\
-\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/2\\
-\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/2
-\end{array} & \begin{array}{rcl}
-\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/2\\
-\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/2\\
-\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1\\
-\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
-\end{array}\end{array}
-\]
-\qed\end{case}
-
-\begin{case}If neither $\ket{0}$, $\ket{\ps}$, nor $\ket{\ps'}$
-is in $\Omega$, then we have
-
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
-\end{array} & \begin{array}{rcl}
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \unknown\\
-\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
-\end{array}\end{array}
-\]
-In this case, $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$
-defined by the following is in the core of $\bar{\mu}^{\Omega}$.
-\[
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\pmeas^{\Omega}(\emptyset) & = & 0\\
-\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/3
-\end{array} & \begin{array}{rcl}
-\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1/3\\
-\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
-\end{array}\end{array}
-\]
-\qed\end{case}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }
+Recall that when approximating the probability classically, the quality
+of the experimental equipment cannot be compensated by the number
+of independent trials. If the precision of the intervals~$\mathscr{I}$
+represents the quality of the quantum experimental equipment, example~\ref{ex:three-dimensional-three-value}
+tells us that we cannot identify a particular state if the experimental
+equipment reveals too little information.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{comment}
+\bibliographystyle{plain}
+\bibliography{discreteGBKS}
+\end{comment}
+
+\printbibliography
+
+\appendix
 %%%%%
 
-\subsection{Examples for Quantum Interval-valued Probability Measures}
+\section{Examples for Quantum Interval-valued Probability Measures}
 
@@
 
-\begin{example}[Three-dimensional quantum 4-value interval-valued
-probability measure]\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify whether this example is convex or not.}}Given
+\begin{example}{[}Three-dimensional quantum 4-value interval-valued
+probability measure{]}\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify whether this example is convex or not.}}Given
 a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
@@
 \qed\end{example}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{comment}
-\bibliographystyle{plain}
-\bibliography{discreteGBKS}
-\end{comment}
-
-\printbibliography
 

### 2016-09-27 prob.tex
From: Sabry, Amr A. Sent: Tuesday, September 27, 2016 9:25 To: Tai, Yu-Tsung <yuttai@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu>; Liu, Weihua <liuweih@indiana.edu> Subject: Shapley 1965
Hi,

A central piece of information is the theorem of Shapley 1965 cited in
our draft. A few thoughts on that:

* Administrative: Yu-Tsung, you cite [28,29] for the theorem but only
[28] is by Shapley. Also that paper is an internal memorandum but there
is a published version
http://link.springer.com/article/10.1007/BF01753431
that should be cited instead.

* Yu-Ts

@@
 
-\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]\label{thm:Shapley}
+\begin{thm}[Shapley~\cite{Shapley1971}]\label{thm:Shapley}
 Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}
@@
 
-\begin{thm}[Bondareva-Shapley~\cite{Shapley1967,Bondareva1968,Grabisch2016}]\label{thm:Bondareva-Shapley}
+\begin{thm}[Bondareva-Shapley~\cite{Shapley1967,Bondareva1968}]\label{thm:Bondareva-Shapley}
 Let $l$ be the left-end of an interval-valued probability measure~$\bar{\mu}$,
@@
 non-empty core because the minimal balanced sets can be generated
-by an algorithm~\cite{Peleg1965}. However, the number of minimal
-balanced sets grows very rapidly with $\left|\Omega\right|$, the
-size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially
+by an algorithm~\cite{Peleg1965,Grabisch2016}. However, the number
+of minimal balanced sets grows very rapidly with $\left|\Omega\right|$,
+the size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially
 or more?}}, so that we have only verified every interval-valued probability
@@
 
-\begin{example}{[}Three-dimensional quantum 4-value interval-valued
-probability measure{]}\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify whether this example is convex or not.}}Given
+\begin{example}[Three-dimensional quantum 4-value interval-valued
+probability measure]\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify whether this example is convex or not.}}Given
 a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.

### 2016-09-29 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} Start typing the meaning of convex...

@@
 \item $\bar{\mu}(\Omega)=[1,1]$. 
-\item For any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$.
+\item For any event $E$, 
+\begin{equation}
+\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)\textrm{ .}\label{eq:ClassicalInterval-valuedProbability-Complement}
+\end{equation}
 \item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
@@
 supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
-for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.
+for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
+of an interval-valued probability measure~$\bar{\mu}$. Because of
+equation~(\ref{eq:ClassicalInterval-valuedProbability-Complement}),
+$\bar{\mu}$ is convex if and only if 
+\begin{equation}
+l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)\textrm{ ,}\label{eq:convex-game}
+\end{equation}
+which is a special case of the Dempster-Shafer condition
+\begin{equation}
+l\left(\bigcup_{i=1}^{N}E_{i}\right)\ge\sum_{I\subseteq\left\{ 1,\ldots,N\right\} }\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
+\end{equation}
+Therefore, in order to understand the meaning of equation~(\ref{eq:convex-game}),
+we could try to understand meaning of the Dempster-Shafer belief function.
+Unfortunately, when people introduce the Dempster-Shafer theory, they
+usually don't start from equation~(\ref{eq:Dempster-Shafer-game}).
+Instead, they introduce a basic belief assignment~$m\left(E\right)=\sum_{E'\subseteq E}\left(-1\right)^{\left|E\setminus E'\right|}l\left(E'\right)$
+first, and $m\left(E\right)$ expresses the proportion of all relevant
+and available evidence that supports the claim that the actual state
+belongs to $A$ but to no particular subset of $A$. Then, equation~(\ref{eq:Dempster-Shafer-game})
+is equivalent to $m\left(E\right)\ge0$ for all $E$~\cite{Grabisch2016},
+and the later statement is intuitive.}}
 \end{itemize}

### 2016-09-30 prob.tex
prob.tex Updating interpretation and example...

@@
 \documentclass{article}
-\usepackage[ backend=biber,sorting=none]{biblatex}
+\usepackage[ backend=biber,sorting=none,maxbibnames=5]{biblatex}
 \bibliography{discreteGBKS}
@@
 Instead, they introduce a basic belief assignment~$m\left(E\right)=\sum_{E'\subseteq E}\left(-1\right)^{\left|E\setminus E'\right|}l\left(E'\right)$
-first, and $m\left(E\right)$ expresses the proportion of all relevant
-and available evidence that supports the claim that the actual state
-belongs to $A$ but to no particular subset of $A$. Then, equation~(\ref{eq:Dempster-Shafer-game})
+first, and $m\left(E\right)$ represents the belief committed to the
+event~$E$ and only to it, in the sense that it could not be committed
+to any proper subset of $A$~\cite{Grabisch2016}. Then, equation~(\ref{eq:Dempster-Shafer-game})
 is equivalent to $m\left(E\right)\ge0$ for all $E$~\cite{Grabisch2016},
-and the later statement is intuitive.}}
+and the non-negative of $m\left(E\right)$ is intuitive.
+
+Comparing to the Dempster-Shafer condition~\ref{eq:Dempster-Shafer-game},
+the equivalent condition for convexity is more complex. At least,
+when $l$ is convex, we have 
+\begin{equation}
+m\left(\left\{ \omega_{0},\omega_{1}\right\} \right)\ge0\label{eq:convex-positive}
+\end{equation}
+ for all $\left\{ \omega_{0},\omega_{1}\right\} \subseteq\Omega$,
+although equation~(\ref{eq:convex-positive}) is not strong enough
+to imply $l$ is convex.}}
 \end{itemize}
@@
 tells us that we cannot identify a particular state if the experimental
-equipment reveals too little information.
-
-If we examine our examples more carefully, we find that example~\ref{ex:three-dimensional-three-value}
-really use the property of $\unknown$ so that it cannot hold when
-the intervals are more precise; example~\ref{ex:three-dimensional-4-value}
-also cannot work with any interval values more precise than $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
-Also, example~\ref{ex:three-dimensional-4-value} is not as bad as
-example~\ref{ex:three-dimensional-three-value} in a sense that the
-$\imposs$ states are all in the same plane in example~\ref{ex:three-dimensional-4-value}
-while the $\imposs$ states are not in the same plane in example~\ref{ex:three-dimensional-4-value}.
-Maybe interval-valued probability measures will be closer and closer
-to real-valued probability measures if the intervals are more and
-more precise?
+equipment reveals too little information. For example, $\bar{\mu}$
+might correspond to $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
+$\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
+or the density matrix~$\frac{\mathbb{1}}{3}$ because $\bar{\mu}(\proj{\phi})\ne\necess$
+for all $\ket{\phi}$. Also, example~\ref{ex:three-dimensional-three-value}
+is no longer valid if our measurement equipment is a little more precise,
+say $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+because example~\ref{ex:three-dimensional-three-value} really use
+the property of $\unknown$.
+
+If we consider $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+example~\ref{ex:three-dimensional-4-value} in appendix~\ref{sec:Examples-for-QuantumIVPM}
+provides another example with an empty core. Comparing to example~\ref{ex:three-dimensional-three-value},
+example~\ref{ex:three-dimensional-4-value} is closer to the Born
+rule in a sense that it might only correspond to $\ket{2}$ or $\frac{\mathbb{1}}{3}$,
+but not $\ket{1}$, and it is no longer valid for more precise measurement
+equipment as well. In general, we believe if the measurement equipment
+is more and more precise, its interval-valued probability measure
+will be closer and closer to the the Born rule. In the limit case,
+$\mathscr{I}=\left\{ \left\{ a\right\} \middle|a\in\left[0,1\right]\right\} $
+recovers conventional Gleason's theorem and the Born rule.
 
@@
 
-\section{Examples for Quantum Interval-valued Probability Measures}
+\section{\label{sec:Examples-for-QuantumIVPM}Examples for Quantum Interval-valued
+Probability Measures}
 
@@
 all mixed state~$\rho$ there is a $P\in\events$ such that $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.
+After the example, we will also justify why this example cannot fit
+with more precise intervals.
 
@@
 can then be verified as follow. 
-\begin{eqnarray*}
+\begin{equation}
+\begin{array}{rcl}
 \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}\right)=\necess & \subseteq & \likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\\
@@
 \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)=\likely & = & \imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
-\end{eqnarray*}
+\end{array}\label{eq:case1}
+\end{equation}
 Similarly, when $\ket{\psi_{1}}$ is $\ket{\ps}$, equation (\ref{eq:non-additive-vectors})
@@
 Then, we have 
-\begin{eqnarray*}
+\begin{equation}
+\begin{array}{rcl}
 \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
 \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
-\end{eqnarray*}
+\end{array}\label{eq:case2}
+\end{equation}
 In order to verify $\bar{\mu}\left(\proj{\psi_{2}}\right)=\bar{\mu}\left(\proj{\psi_{3}}\right)=\unlikely$,
@@
 verified. 
-\begin{eqnarray*}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)
-\end{eqnarray*}
+\begin{equation}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely\subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\label{eq:case3}
+\end{equation}
 \end{enumerate}

### 2016-10-01 prob.tex
prob.tex Fixing citations...

@@
 and $f$ is called the Radon-Nikodym derivative of $\pmeas$ (with
-respect to the counting measure)~\cite{Nikodym1930,Folland2013}.
+respect to the counting measure)~\cite{Nikodym1930,Folland1999}.
 The converse is also valid and called the Radon-Nikodym theorem.
@@
 such that~\cite{JamisonLodwick2004}:\footnote{The right-end of the interval-valued probability measure is a special
-case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman2013}
-or outer measure~\cite{Folland2013}. The left-end of the interval-valued
-probability measure is a special case of game~\cite{Shapley1965}.} 
+case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman1997}
+or outer measure~\cite{Folland1999}. The left-end of the interval-valued
+probability measure is a special case of (super-additive cooperative)
+game~\cite{Shapley1971,Grabisch2016}.} 
 \begin{itemize}
@@
 Theorems are either too restricted to apply to all interval-valued
-probability measures~\cite{Choquet1954,Graf1980,Goodman2013} or
+probability measures~\cite{Choquet1954,Graf1980,Goodman1997} or
 corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 to another set function~$\bar{f}:\events\rightarrow\bar{\mathscr{I}}$
-which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman2013}.
+which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman1997}.
 
@@
 of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
-\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
+\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
 \item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
 supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
-for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
+for all $E_{1},E_{2}\in\events$~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
 of an interval-valued probability measure~$\bar{\mu}$. Because of
@@
 \end{equation}
-which is a special case of the Dempster-Shafer condition
+which is a special case of the Dempster-Shafer condition~\cite{Shafer1976,Grabisch2016}
 \begin{equation}
@@
 event~$E$ and only to it, in the sense that it could not be committed
-to any proper subset of $A$~\cite{Grabisch2016}. Then, equation~(\ref{eq:Dempster-Shafer-game})
-is equivalent to $m\left(E\right)\ge0$ for all $E$~\cite{Grabisch2016},
-and the non-negative of $m\left(E\right)$ is intuitive.
+to any proper subset of $A$. Then, equation~(\ref{eq:Dempster-Shafer-game})
+is equivalent to $m\left(E\right)\ge0$ for all $E$, and the non-negative
+of $m\left(E\right)$ is intuitive.
 
@@
 measures consists the Dempster-Shafer belief function as the left-end
-and the Dempster-Shafer plausibility as the right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
+and the Dempster-Shafer plausibility as the right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Goodman1997,Marinacci1999,Teran2014}.
 Dempster-Shafer functions, also called \emph{completely} or \emph{totally

### 2016-10-01 prob.tex
prob.tex Add comments on convex and a new example, and fix biblatex...

@@
 only back-track randomized program still searches IVPM with a extremely
-slow speed...}} Based on the previous fact, we have the following conjecture.
+slow speed...
+
+Although the computer simulation supports the idea that every IVPM
+has a nonempty core, if we look the equations. $\bar{\mu}$ is an
+interval-valued probability measure if and only if its left-end~$l$
+satisfies equation~(\ref{eq:convex-game}) when $E_{1}\cap E_{2}=\emptyset$
+or $E_{1}\cup E_{2}=\Omega$. This condition is much weaker than convex,
+and I would be surprise that this condition is strong enough to imply
+a nonempty core.}} Based on the previous fact, we have the following conjecture.
 
@@
 \begin{equation}
-\begin{array}{rcl}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}\right)=\necess & \subseteq & \likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & = & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\imposs=\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)=\likely & = & \imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
-\end{array}\label{eq:case1}
+\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}\right)=\necess & \subseteq\likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & =\unlikely\tensor*[_{\mathscr{I}}]{+}{}\imposs=\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)=\likely & =\imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
+\end{aligned}
+\label{eq:case1}
 \end{equation}
@@
 \begin{equation}
-\begin{array}{rcl}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
-\end{array}\label{eq:case2}
+\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right)=\likely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
+\end{aligned}
+\label{eq:case2}
 \end{equation}
@@
 \end{enumerate}
-\qed\end{example}
+\footnote{\yutsung{This example is a little bit too long to human-verify, and
+we need more examples. Maybe we need to write a program for further
+verification.}}\qed\end{example}
+
+\begin{example}[Three-dimensional quantum 4-value interval-valued
+probability measure (Continue)]\label{ex:three-dimensional-4-value-1}
+In order to verify example~\ref{fig:three-dimensional-4-value} cannot
+hold with more precise intervals. Consider $\mathscr{I}=\left\{ \imposs,\left[l_{1},r_{1}\right],\left[1-r_{1},1-l_{1}\right],\necess\right\} $,
+where $\left[l_{1},r_{1}\right]$ and $\left[1-r_{1},1-l_{1}\right]$
+will be used to replace every $\unlikely$ and $\likely$ in example~\ref{fig:three-dimensional-4-value},
+respectively. In order to make the equations corresponding to equation~(\ref{eq:case1}),
+(\ref{eq:case2}), and (\ref{eq:case3}) hold, we could estimate the
+bound of $l_{1}$ and $r_{1}$.
+
+When we replace $\unlikely$ and $\likely$ by $\left[l_{1},r_{1}\right]$
+and $\left[1-r_{1},1-l_{1}\right]$, equation~(\ref{eq:case1}) will
+become
+
+\begin{equation}
+\begin{aligned}\necess & \subseteq\left[1-r_{1},1-l_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
+\left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\imposs\\
+\left[1-r_{1},1-l_{1}\right] & \subseteq\imposs\tensor*[_{\mathscr{I}}]{+}{}\left[1-r_{1},1-l_{1}\right]
+\end{aligned}
+\label{eq:case1-1}
+\end{equation}
+which are all tautologies. Equation~(\ref{eq:case2}) will become
+\begin{equation}
+\begin{aligned}\left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
+\left[1-r_{1},1-l_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[1-r_{1},1-l_{1}\right]
+\end{aligned}
+\label{eq:case2-1}
+\end{equation}
+which implies $l_{1}=0$. Finally, equation~(\ref{eq:case3}) will
+become
+\begin{equation}
+\left[1-r_{1},1-l_{1}\right]\subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\label{eq:case3-1}
+\end{equation}
+which implies $\frac{1}{2}\le r_{1}\le1$. Therefore, $l_{1}=0$ and
+$r_{1}=\frac{1}{2}$ provides the most precise intervals which make
+example~\ref{fig:three-dimensional-4-value} work, and in this case,
+the intervals are $\left\{ \imposs,\unlikely,\likely,\necess\right\} $.\qed\end{example}
 

### 2016-10-02 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} update comments...

@@
 \begin{equation}
-l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)\textrm{ ,}\label{eq:convex-game}
+l\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{2}\right)\textrm{ ,}\label{eq:convex-game}
 \end{equation}
@@
 \begin{equation}
-l\left(\bigcup_{i=1}^{N}E_{i}\right)\ge\sum_{I\subseteq\left\{ 1,\ldots,N\right\} }\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
+l\left(\bigcup_{i=1}^{N}E_{i}\right)\ge\sideset{_{\mathbb{R}}}{_{I\subseteq\left\{ 1,\ldots,N\right\} }}\sum\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
 \end{equation}
@@
 usually don't start from equation~(\ref{eq:Dempster-Shafer-game}).
-Instead, they introduce a basic belief assignment~$m\left(E\right)=\sum_{E'\subseteq E}\left(-1\right)^{\left|E\setminus E'\right|}l\left(E'\right)$
-first, and $m\left(E\right)$ represents the belief committed to the
-event~$E$ and only to it, in the sense that it could not be committed
-to any proper subset of $A$. Then, equation~(\ref{eq:Dempster-Shafer-game})
-is equivalent to $m\left(E\right)\ge0$ for all $E$, and the non-negative
-of $m\left(E\right)$ is intuitive.
-
-Comparing to the Dempster-Shafer condition~\ref{eq:Dempster-Shafer-game},
+Instead, they introduce a basic belief assignment~$m\left(E\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{E'\subseteq E}}\left(-1\right)^{\left|E\setminus E'\right|}l\left(E'\right)$
+first. $m\left(E\right)$ represents the belief committed to the event~$E$
+and only to it, in the sense that it could not be committed to any
+proper subset of $E$. Then, equation~(\ref{eq:Dempster-Shafer-game})
+is equivalent to $m\left(E\right)\ge0$ for all $E$ which is intuitive.
+
+Comparing to the Dempster-Shafer condition~(\ref{eq:Dempster-Shafer-game}),
 the equivalent condition for convexity is more complex. At least,
@@
 measure has a non-empty core when $\left|\Omega\right|\le5$ so far.\footnote{\yutsung{The program for $\left|\Omega\right|=6$ blows up the memory
-again, and the symmetric answer doesn't really work. Hence, currently
-only back-track randomized program still searches IVPM with a extremely
-slow speed...
+again. Hence, currently I only run a extremely slow backtrack program
+searching for a IVPM with an empty core...
 
 Although the computer simulation supports the idea that every IVPM
-has a nonempty core, if we look the equations. $\bar{\mu}$ is an
+has a nonempty core, if we look the equations, $\bar{\mu}$ is an
 interval-valued probability measure if and only if its left-end~$l$
@@
 or $E_{1}\cup E_{2}=\Omega$. This condition is much weaker than convex,
-and I would be surprise that this condition is strong enough to imply
+and I will be surprise if this condition is strong enough to imply
 a nonempty core.}} Based on the previous fact, we have the following conjecture.

### 2016-10-02 prob.tex
prob.tex \section{\label{sec:Examples-for-QuantumIVPM}Examples for Quantum Interval-valued Probability Measures} Updates...

@@
 where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
-half of those states need special treatment, i.e., when where $0\le\theta<\frac{\pi}{2}$
+half of those states need special treatment, i.e., whenever $0\le\theta<\frac{\pi}{2}$
 and $0\le\gamma<\pi$, we define 
@@
 
+The following example verifies example~\ref{ex:three-dimensional-4-value}
+cannot hold with more precise intervals.
+
 \begin{example}[Three-dimensional quantum 4-value interval-valued
 probability measure (Continue)]\label{ex:three-dimensional-4-value-1}
-In order to verify example~\ref{fig:three-dimensional-4-value} cannot
-hold with more precise intervals. Consider $\mathscr{I}=\left\{ \imposs,\left[l_{1},r_{1}\right],\left[1-r_{1},1-l_{1}\right],\necess\right\} $,
-where $\left[l_{1},r_{1}\right]$ and $\left[1-r_{1},1-l_{1}\right]$
-will be used to replace every $\unlikely$ and $\likely$ in example~\ref{fig:three-dimensional-4-value},
-respectively. In order to make the equations corresponding to equation~(\ref{eq:case1}),
-(\ref{eq:case2}), and (\ref{eq:case3}) hold, we could estimate the
-bound of $l_{1}$ and $r_{1}$.
+Consider $\mathscr{I}=\left\{ \imposs,\left[l_{1},r_{1}\right],\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right],\necess\right\} $,
+where $\left[l_{1},r_{1}\right]$ and $\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]$
+will be used to replace every $\unlikely$ and $\likely$ in example~\ref{ex:three-dimensional-4-value},
+respectively. The bound of $l_{1}$ and $r_{1}$ can then be estimated
+by the equations corresponding to equation~(\ref{eq:case1}), (\ref{eq:case2}),
+and (\ref{eq:case3}).
 
 When we replace $\unlikely$ and $\likely$ by $\left[l_{1},r_{1}\right]$
-and $\left[1-r_{1},1-l_{1}\right]$, equation~(\ref{eq:case1}) will
-become
+and $\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]$,
+equation~(\ref{eq:case1}) will become
 
 \begin{equation}
-\begin{aligned}\necess & \subseteq\left[1-r_{1},1-l_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
+\begin{aligned}\necess & \subseteq\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
 \left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\imposs\\
-\left[1-r_{1},1-l_{1}\right] & \subseteq\imposs\tensor*[_{\mathscr{I}}]{+}{}\left[1-r_{1},1-l_{1}\right]
+\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right] & \subseteq\imposs\tensor*[_{\mathscr{I}}]{+}{}\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]
 \end{aligned}
@@
 \begin{aligned}\left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
-\left[1-r_{1},1-l_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[1-r_{1},1-l_{1}\right]
+\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]
 \end{aligned}
@@
 \begin{equation}
-\left[1-r_{1},1-l_{1}\right]\subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\label{eq:case3-1}
+\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]\subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\label{eq:case3-1}
 \end{equation}
@@
 $r_{1}=\frac{1}{2}$ provides the most precise intervals which make
-example~\ref{fig:three-dimensional-4-value} work, and in this case,
+example~\ref{ex:three-dimensional-4-value} work, and in this case,
 the intervals are $\left\{ \imposs,\unlikely,\likely,\necess\right\} $.\qed\end{example}
+
+Although example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value}
+rely on $\imposs$ to deduce that an interval-valued probability measure
+has an empty core, it is not necessary. The following example is modified
+from example~\ref{ex:three-dimensional-4-value}, but has the property
+that $\bar{\mu}\left(P\right)=\imposs$ if and only if $P=\mathbb{0}$.
+
+\begin{example}[Another three-dimensional quantum 4-value interval-valued
+probability measure]\label{ex:three-dimensional-4-value-2} Consider\emph{
+}$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+and $\ket{0}$, $\ket{1}$, $\ket{2}$, $\ket{\ps}$, $\ket{\ms}$,
+and $\bar{\mu}$ are defined as in example~\ref{ex:three-dimensional-4-value}
+except 
+\begin{eqnarray*}
+\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \unlikely\\
+\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \likely\textrm{ .}
+\end{eqnarray*}
+By following the same as process as in example~\ref{ex:three-dimensional-4-value},
+it is easy to verify that $\bar{\mu}$ is an interval-valued probability
+measure.
+
+We now prove $\bar{\mu}$ has an empty core by contradiction. Assume
+there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
+for all $P\in\events$. \qed\end{example}
 

### 2016-10-02 prob.tex
prob.tex Global replace all array to 0-based...

@@
+%% LyX 2.2.1 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
 \documentclass{article}
+\usepackage[T1]{fontenc}
+\usepackage[latin9]{inputenc}
+\usepackage{verbatim}
+\usepackage{mathrsfs}
+\usepackage{url}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amssymb}
+\usepackage{graphicx}
+
+\makeatletter
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
 \usepackage[ backend=biber,sorting=none,maxbibnames=5]{biblatex}
-\bibliography{discreteGBKS}
+\addbibresource{discreteGBKS.bib}
 \usepackage{fullpage}
@@
 \usepackage{bbold}
-\usepackage{amssymb}
 \usepackage{amsthm}
@@
 \usepackage[all]{xy}
-\usepackage{amsmath}
 \usepackage{wesa}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
-\usepackage{verbatim}
 
@@
 
+\makeatother
+
 \begin{document}
+
 \title{Interval Probability and Measurement for Fuzzy Quantum Theories}
-\author{}
+
 \date{\today}
+
 \maketitle
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
@@
 \end{itemize}
-
 \noindent Pseudo-randomness: 
 \begin{itemize}
-\item
-  \url{https://people.csail.mit.edu/silvio/Selected%20Scientific%20Papers/Pseudo%20Randomness/How_To_Generate_Cryptographically_Strong_Sequences_Of_Pseudo-Random_Bits.pdf}:
-  ``the randomness of an event is relative to a specific model of
-  computation with a specified amount of computing resources.''
+\item \url{https://people.csail.mit.edu/silvio/Selected%20Scientific%20Papers/Pseudo%20Randomness/How_To_Generate_Cryptographically_Strong_Sequences_Of_Pseudo-Random_Bits.pdf}:
+``the randomness of an event is relative to a specific model of computation
+with a specified amount of computing resources.'' 
 \item Another version \url{https://pdfs.semanticscholar.org/3e9c/5f6f48d9ef426655dc799e9b287d754e86c1.pdf} 
 \end{itemize}
-
 %%%%%
+
 \subsection{Plan}
 
-In the remainder of the paper, we consider variations of quantum
-probability spaces motivated by computation of numerical quantities in
-a world with limited resources:
+In the remainder of the paper, we consider variations of quantum probability
+spaces motivated by computation of numerical quantities in a world
+with limited resources: 
 \begin{itemize}
@@
 variants constructed over finite fields~\cite{DQT2014,geometry2013}. 
-\item Instead of real-valued probability measures producing results in
-  the uncountable and uncomputable interval $[0,1]$, we will consider
-  finite set-valued probability measures~\cite{PuriRalescu1983}.
+\item Instead of real-valued probability measures producing results in the
+uncountable and uncomputable interval $[0,1]$, we will consider finite
+set-valued probability measures~\cite{PuriRalescu1983}. 
 \end{itemize}
 We will then ask if it is possible to construct variants of quantum
-probability spaces under these conditions. The main question is
-related to the definition of probability measures: is it possible to
-still define a probability measure as a function that depends on a
-single state? Specifically,
+probability spaces under these conditions. The main question is related
+to the definition of probability measures: is it possible to still
+define a probability measure as a function that depends on a single
+state? Specifically, 
 \begin{itemize}
-\item given a state $\ket{\psi}$, is there a probability measure
-  mapping events to probabilities that only depends on $\ket{\psi}$?
-  In the conventional quantum probability space, the answer is yes by
-  the Born rule~\cite{Born1983,Mermin2007} and the map is given by:
-  $P \mapsto \ip{\psi}{P\psi}$.
-\item given a probability measure $\mu$
-  mapping each event $P$
-  to a probability, is there a \emph{unique} state $\psi$
-  such that $\mu(P)
-  =
-  \ip{\psi}{P\psi}$? In the conventional case, the answer is yes by
-  Gleason's
-  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
+\item given a state $\ket{\psi}$, is there a probability measure mapping
+events to probabilities that only depends on $\ket{\psi}$? In the
+conventional quantum probability space, the answer is yes by the Born
+rule~\cite{Born1983,Mermin2007} and the map is given by: $P\mapsto\ip{\psi}{P\psi}$. 
+\item given a probability measure $\mu$ mapping each event $P$ to a probability,
+is there a \emph{unique} state $\psi$ such that $\mu(P)=\ip{\psi}{P\psi}$?
+In the conventional case, the answer is yes by Gleason's theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}. 
 \end{itemize}
-
 \andy{Quantum meeting: the basics of classical and quantum standard
@@
 exposition). The key step is the replacement of \textquotedbl{}sum\textquotedbl{}
-and \textquotedbl{}=\textquotedbl{} in the rule $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$
+and \textquotedbl{}=\textquotedbl{} in the rule $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{N-1}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\mu\left(P_{i}\right)$
 by various logical operations on sets instead of actually summing
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Classical Probability Spaces}
@@
 the type of operations, and they may be dropped when there is no ambiguity. 
-\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
-events, $\pmeas(\bigcup_{i=1}^{N}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$.
-Similar to the above condition, $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$
+\item For a collection $\left\{ E_{i}\right\} _{i=0}^{N-1}$ of pairwise
+disjoint events, $\pmeas(\bigcup_{i=0}^{N-1}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\pmeas(E_{i})$.
+Similar to the above condition, $\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\pmeas(E_{i})$
 explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. 
@@
 %%%%%
-\subsection{Measuring Probabilities: Buffon's Needle
-Problem\label{subsec:Measuring-Probabilities:-Buffon}}
+
+\subsection{Measuring Probabilities: Buffon's Needle Problem\label{subsec:Measuring-Probabilities:-Buffon}}
 
@@
 trial or not, respectively, then $\pmeas(E)$ could be approximated
-to given accuracy~$\epsilon>0$ by the relative frequency~$\frac{1}{N}\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}$
+to given accuracy~$\epsilon>0$ by the relative frequency~$\frac{1}{N}\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}x_{i}$
 with the probability converging to one as $N$ goes to infinity, i.e.,
 \[
-\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum x_{i}\right|<\epsilon\right)=1\textrm{ .}
+\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sideset{_{\mathbb{R}}}{_{i=0}^{N-1}}\sum x_{i}\right|<\epsilon\right)=1\textrm{ .}
 \]
@@
 
-In an actual experiment with $500$ needles and the ratio
-$\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$ crossed
-a line so the relative frequency is $0.472$ whereas the idealized
-mathematical probability is $0.4774\ldots$. In a larger experiment
-with $5000$ needles and the ratio
-$\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, the relative frequency was
-calculated to be $0.5064$ whereas the idealized mathematical
-probability is $0.5092\ldots$. We see that the observed probability
-approaches $\frac{2\ell}{\pi h}$ but only if \emph{larger and larger
-  resources} are expended. These resource considerations suggest that
-it is possible to replace the real interval $[0,1]$ with rational
-numbers up to a certain precision related to the particular experiment
-in question.  There is clearly a connection between the number of
-needles and the achievable precision: in the hypothetical experiment
-with 3 needles, it is not sensible to retain 100 digits in the
-expansion of $\frac{2\ell}{\pi h}$.
+In an actual experiment with $500$ needles and the ratio $\frac{\ell}{h}=0.75$~\cite{Hall1873},
+it was found that $236$ crossed a line so the relative frequency
+is $0.472$ whereas the idealized mathematical probability is $0.4774\ldots$.
+In a larger experiment with $5000$ needles and the ratio $\frac{\ell}{h}=0.8$~\cite{Uspensky1937},
+the relative frequency was calculated to be $0.5064$ whereas the
+idealized mathematical probability is $0.5092\ldots$. We see that
+the observed probability approaches $\frac{2\ell}{\pi h}$ but only
+if \emph{larger and larger resources} are expended. These resource
+considerations suggest that it is possible to replace the real interval
+$[0,1]$ with rational numbers up to a certain precision related to
+the particular experiment in question. There is clearly a connection
+between the number of needles and the achievable precision: in the
+hypothetical experiment with 3 needles, it is not sensible to retain
+100 digits in the expansion of $\frac{2\ell}{\pi h}$.
 
@@
 % \subsection{Set-valued Probability Measures}
-
 % Instead of using every point in the real interval $[0,1]$ as a
@@
 %%%%%
+
 \subsection{Classical Interval-valued probability measures}
@@
 \item $\bar{\mu}(\Omega)=[1,1]$. 
-\item For every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
-with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
+\item For every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=0}^{N-1},\left\{ E_{i}'\right\} _{i=0}^{N'-1}\subseteq\events$
+with $\Omega=\left(\bigcup_{i=0}^{N-1}E_{i}\right)\bigcup\left(\bigcup_{i=0}^{N'-1}E_{i}'\right)$,
 we have 
 \[
-\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum r_{i}\right\} \right]\textrm{ ,}
+\bar{\mu}\left(\bigcup_{i=0}^{N-1}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=0}^{N'-1}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i=0}^{N-1}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=0}^{N'-1}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i=0}^{N-1}}\sum r_{i}\right\} \right]\textrm{ ,}
 \]
@@
 \end{equation}
-\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
-events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\bar{\mu}\left(E_{i}\right)$,
-where $\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
+\item For a collection $\left\{ E_{i}\right\} _{i=0}^{N-1}$ of pairwise
+disjoint events, we have $\bar{\mu}\left(\bigcup_{i=0}^{N-1}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=0}^{N-1}}\bar{\mu}\left(E_{i}\right)$,
+where $\tensor*[_{\mathscr{I}}]{\sum}{_{i=0}^{N-1}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}r_{i}\right]$.
 We may drop the preposing $\mathscr{I}$ when summands are clearly
@@
 \begin{example}[Two-coin experiment with interval probability]
-  \label{ex3} We split the unit interval $[0,1]$ in the following four
-  closed sub-intervals: $[0,0]$ which we call \imposs,
-  $[0,\frac{1}{2}]$ which we call \unlikely, $[\frac{1}{2},1]$ which
-  we call \likely, and $[1,1]$ which we call \necess. Using these new
-  values, we can modify the probability measure of Ex.~\ref{ex1} by
-  mapping each numeric value to the smallest sub-interval containing
-  it to get the following:
+\label{ex3} We split the unit interval $[0,1]$ in the following
+four closed sub-intervals: $[0,0]$ which we call \imposs, $[0,\frac{1}{2}]$
+which we call \unlikely, $[\frac{1}{2},1]$ which we call \likely,
+and $[1,1]$ which we call \necess. Using these new values, we can
+modify the probability measure of Ex.~\ref{ex1} by mapping each
+numeric value to the smallest sub-interval containing it to get the
+following: 
 \[
@@
 \]
-Despite the absence of any numeric information, the probability
-measure is quite informative: it reveals that the second coin is
-double-headed and that the first coin is biased. To understand the
-$\subseteq$-condition, consider the following calculation:
+Despite the absence of any numeric information, the probability measure
+is quite informative: it reveals that the second coin is double-headed
+and that the first coin is biased. To understand the $\subseteq$-condition,
+consider the following calculation: 
 \begin{eqnarray*}
@@
 \item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
-supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
-for all $E_{1},E_{2}\in\events$~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
+supermodular} if $\bar{\mu}\left(E_{0}\cup E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}\left(E_{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\right)$
+for all $E_{0},E_{1}\in\events$~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
 of an interval-valued probability measure~$\bar{\mu}$. Because of
@@
 \begin{equation}
-l\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{2}\right)\textrm{ ,}\label{eq:convex-game}
+l\left(E_{0}\cup E_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{0}\cap E_{1}\right)\ge l\left(E_{0}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{1}\right)\textrm{ ,}\label{eq:convex-game}
 \end{equation}
@@
 \begin{equation}
-l\left(\bigcup_{i=1}^{N}E_{i}\right)\ge\sideset{_{\mathbb{R}}}{_{I\subseteq\left\{ 1,\ldots,N\right\} }}\sum\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
+l\left(\bigcup_{i=0}^{N-1}E_{i}\right)\ge\sideset{_{\mathbb{R}}}{_{I\subseteq\left\{ 0,\ldots,N-1\right\} }}\sum\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
 \end{equation}
@@
 $\bar{\mu}$ has a non-empty core if and only if for any minimal balanced
-sets~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
-where $\left\{ E_{i}\right\} _{i=1}^{N}$ is called minimal balanced
+sets~$\left\{ E_{i}\right\} _{i=0}^{N-1}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\gamma_{i}l\left(E_{i}\right)\le1$,
+where $\left\{ E_{i}\right\} _{i=0}^{N-1}$ is called minimal balanced
 sets if they are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$,
-and there exist a unique positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$
-such that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
+and there exist a unique positive coefficient~$\left\{ \gamma_{i}\right\} _{i=0}^{N-1}$
+such that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=0\textrm{ and }\omega\in E_{i}}^{N-1}}\gamma_{i}=1$
 for all $\omega\in\Omega$.\qed\end{thm}
@@
 interval-valued probability measure if and only if its left-end~$l$
-satisfies equation~(\ref{eq:convex-game}) when $E_{1}\cap E_{2}=\emptyset$
-or $E_{1}\cup E_{2}=\Omega$. This condition is much weaker than convex,
+satisfies equation~(\ref{eq:convex-game}) when $E_{0}\cap E_{1}=\emptyset$
+or $E_{0}\cup E_{1}=\Omega$. This condition is much weaker than convex,
 and I will be surprise if this condition is strong enough to imply
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{\label{sec:Quantum-Probability-Spaces}Quantum Probability Spaces}
@@
 operator. 
-\item Projection operators $P_{1}$ and $P_{2}$ are \emph{orthogonal} if
-$P_{1}P_{2}=P_{2}P_{1}=\mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
+\item Projection operators $P_{0}$ and $P_{1}$ are \emph{orthogonal} if
+$P_{0}P_{1}=P_{1}P_{0}=\mathbb{0}$. The sum of two projection operators~$P_{0}\tensor*[_{\mathscr{O}}]{+}{}P_{1}$
 is also a projection operator if and only if they are orthogonal,
@@
 is an operation between operators. 
-\item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}\proj{\psi_{j}}$,
+\item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=0}^{N-1}}\proj{\psi_{j}}$,
 where $P$ actually projects onto the linear subspace~$S$ with an
-orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
+orthonormal basis~$\left\{ \ket{\psi_{j}}\right\} _{j=0}^{N-1}$. 
 \end{itemize}
@@
 \begin{itemize}
-\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is called
+\item A set of projections $\left\{ P_{i}\right\} _{i=0}^{N-1}$ is called
 an \emph{ideal measurement} if it is a partition of the identity,
-i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
-In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
+i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{N-1}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
+In this case, projections $\left\{ P_{i}\right\} _{i=0}^{N-1}$ must
 be mutually orthogonal~\cite{Griffiths2003}.
@@
 in classical probability~\cite{Griffiths2003}. 
-\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
-The product of two projection operators~$P_{1}P_{2}$ is also a projection
+\item Projection operators $P_{0}$ and $P_{1}$ \emph{commute} if $P_{0}P_{1}=P_{1}P_{0}$.
+The product of two projection operators~$P_{0}P_{1}$ is also a projection
 operator if and only if they commute. This corresponds to the classical
 intersection between events~\cite{peres1995quantum,Griffiths2003}. 
-\item For two commuting projection operators $P_{1}$ and $P_{2}$, their
-\emph{disjunction}~$P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}$
-is defined to be $P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\tensor*[_{\mathscr{O}}]{-}{}P_{1}P_{2}$~\cite{Griffiths2003}. 
+\item For two commuting projection operators $P_{0}$ and $P_{1}$, their
+\emph{disjunction}~$P_{0}\tensor*[_{\mathscr{O}}]{\vee}{}P_{1}$
+is defined to be $P_{0}\tensor*[_{\mathscr{O}}]{+}{}P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{0}P_{1}$~\cite{Griffiths2003}. 
 \end{itemize}
@@
 \end{equation}
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=0}^{N-1}$,
+we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{N-1}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\mu\left(P_{i}\right)$
 . 
@@
 of two projections may not be a projection. As the result, the classical
-condition~$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
-is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
-however, $\mu\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)=\mu(P_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(P_{2})$
+condition~$\pmeas(E_{0}\cup E_{1})=\pmeas(E_{0})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{1})$
+is always defined, and it is true when $E_{0}$ and $E_{1}$ are disjoint;
+however, $\mu\left(P_{0}\tensor*[_{\mathscr{O}}]{+}{}P_{1}\right)=\mu(P_{0})\tensor*[_{\mathbb{R}}]{+}{}\mu(P_{1})$
 is always true whenever the left-handed side is defined.
@@
 
-\footnote{\yutsung{The definition of independence is interesting, and we
-definitely need to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
-theorem. However, the definition diverges. So we just leave it so far, and we
-will go back if we really need it in this paper. (Maybe when discussing repeating
-experiments?)}}
+\footnote{\yutsung{The definition of independence is interesting, and we definitely
+need to discuss it when we want to discuss Bell's theorem and the
+Kochen-Specker theorem. However, the definition diverges. So we just
+leave it so far, and we will go back if we really need it in this
+paper. (Maybe when discussing repeating experiments?)}}
 
@@
 is $q_{j}$, the state of the system can be expressed as a density
-matrix~$\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}q_{j}\proj{\phi_{j}}$,
-where $\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}=1$. Then, the
-quantum probability measure introduced by $\rho$ is the combination
+matrix~$\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{j=0}^{N-1}}q_{j}\proj{\phi_{j}}$,
+where $\tensor*[_{\mathbb{R}}]{\sum}{_{j=0}^{N-1}}q_{j}=1$. Then,
+the quantum probability measure introduced by $\rho$ is the combination
 of $\mu_{\phi_{j}}^{B}$ with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
 \begin{eqnarray}
-\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{j=1}^{N}}\sum q_{j}\mu_{\phi_{j}}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed}
+\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{j=0}^{N-1}}\sum q_{j}\mu_{\phi_{j}}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed}
 \end{eqnarray}
@@
 Mathematically, to fix the magnetic field of the Stern-Gerlach experiment
-is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
+is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=0}^{d-1}$
 for a given Hilbert space~$\Hilb$ of dimension~$d$, and the state
 of the silver atom can be represented by a density matrix~$\rho$
-written in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
+written in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{d-1}}\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{d-1}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
 As we discussed in the last paragraph, the Born rule of the mixed
@@
 a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
-measure~$\mu:\events\rightarrow[0,1]$, there exists an unique mixed
+measure~$\mu:\events\rightarrow[0,1]$, there exists a unique mixed
 state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{thm}
@@
 \end{equation}
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=0}^{N-1}$,
 we have 
 \begin{equation}
-\bar{\mu}\left(\sideset{_{\mathscr{O}}}{_{i=1}^{N}}\sum P_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i=1}^{N}}\sum\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\bar{\mu}\left(\sideset{_{\mathscr{O}}}{_{i=0}^{N-1}}\sum P_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i=0}^{N-1}}\sum\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
 \end{equation}
@@
 $\iota$ has two interesting properties $\iota\left(1\tensor*[_{\mathbb{R}}]{-}{}x\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
-and $\iota\left(\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\iota\left(x_{i}\right)$,
-where $x$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}\in\left[0,1\right]$.
+and $\iota\left(\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}x_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=0}^{N-1}}\iota\left(x_{i}\right)$,
+where $x$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}x_{i}\in\left[0,1\right]$.
 By applying these two properties, it is easy to verify $\bar{\mu}$
@@
 \begin{equation}
-\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
+\bar{\mu}\left(P_{0}\tensor*[_{\mathscr{O}}]{\vee}{}P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
 \end{equation}
- for all commuting $P_{1},P_{2}\in\events$. 
+ for all commuting $P_{0},P_{1}\in\events$. 
 \end{itemize}
@@
 To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
-first notice that $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
+first notice that $\bar{\mu}\left(P_{0}\tensor*[_{\mathscr{O}}]{+}{}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}\right)$
 implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
@@
 \[
-\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
+\bar{\mu}\left(\proj{\psi_{0}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)
 \]
-for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This equation
-always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$.
+for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
+always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)$.
 
 Next, we need to verify that $\bar{\mu}$ is convex. First, for orthogonal
-projections $P_{1}$ and $P_{2}$, equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+projections $P_{0}$ and $P_{1}$, equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
 implies equation (\ref{eq:QuantumInterval-valuedProbability-Convex}).
-Second, when $P_{1}=P_{2}\tensor*[_{\mathscr{O}}]{+}{}P_{3}$, equation
+Second, when $P_{0}=P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$, equation
 (\ref{eq:QuantumInterval-valuedProbability-Convex}) holds trivially.
-Hence, we only need to verify the case which $P_{1}=\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{3}}$
-and $P_{2}=\proj{\psi_{2}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{3}}$,
-where $\left\{ \ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\right\} $
+Hence, we only need to verify the case which $P_{0}=\proj{\psi_{0}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}$
+and $P_{1}=\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}$,
+where $\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
 is an orthonormal basis. Because we have 
 \begin{eqnarray*}
-\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right) & = & \bar{\mu}\left(\mathbb{1}\right)=\necess\\
-\bar{\mu}\left(P_{1}P_{2}\right) & = & \bar{\mu}\left(\proj{\psi_{3}}\right)\subseteq\unknown
+\bar{\mu}\left(P_{0}\tensor*[_{\mathscr{O}}]{\vee}{}P_{1}\right) & = & \bar{\mu}\left(\mathbb{1}\right)=\necess\\
+\bar{\mu}\left(P_{0}P_{1}\right) & = & \bar{\mu}\left(\proj{\psi_{2}}\right)\subseteq\unknown
 \end{eqnarray*}
-and $\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
+and $\bar{\mu}\left(P_{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}\right)$
 is either $\necess\tensor*[_{\mathscr{I}}]{+}{}\unknown$ or $\unknown\tensor*[_{\mathscr{I}}]{+}{}\unknown$.
-Therefore, we have $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$.
+Therefore, we have $\bar{\mu}\left(P_{0}\tensor*[_{\mathscr{O}}]{\vee}{}P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}\right)$.
 
@@
 \end{equation}
-By Gleason's theorem, there is a mixed state~$\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}q_{j}\proj{\phi_{j}}$
-such that $\mu\left(P\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}=1$ and $q_{j}>0$.
+By Gleason's theorem, there is a mixed state~$\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{j=0}^{N-1}}q_{j}\proj{\phi_{j}}$
+such that $\mu\left(P\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{j=0}^{N-1}}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+where $\tensor*[_{\mathbb{R}}]{\sum}{_{j=0}^{N-1}}q_{j}=1$ and $q_{j}>0$.
 However, no pure state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
@@
 \begin{equation}
-\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{3}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
+\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{0}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)
 \end{aligned}
@@
 \end{equation}
-for every orthonormal basis $\mathcal{B}=\left\{ \ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\right\} $.
+for every orthonormal basis $\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $.
 We are going to enumerate all possible orthonormal bases to verify
@@
 \begin{enumerate}
-\item When $\ket{\psi_{1}}$ is $\ket{0}$, then either $\ket{\psi_{2}}$
-or $\ket{\psi_{3}}$ must be $\ket{0_{\theta,\gamma}^{\perp}}$ for
+\item When $\ket{\psi_{0}}$ is $\ket{0}$, then either $\ket{\psi_{1}}$
+or $\ket{\psi_{2}}$ must be $\ket{0_{\theta,\gamma}^{\perp}}$ for
 some $\theta$ and $\gamma$. Because of 
@@
 \]
-the pair $\ket{\psi_{2}}=\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\psi_{3}}=\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}$
+the pair $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\psi_{2}}=\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}$
 for ($0<\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$) or $\theta=0$
@@
 \end{equation}
-Similarly, when $\ket{\psi_{1}}$ is $\ket{\ps}$, equation (\ref{eq:non-additive-vectors})
+Similarly, when $\ket{\psi_{0}}$ is $\ket{\ps}$, equation (\ref{eq:non-additive-vectors})
 holds. 
-\item When $\ket{0}\notin\mathcal{B}$ and $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$
+\item When $\ket{0}\notin\mathcal{B}$ and $\ket{\psi_{0}}=\ket{0_{\theta,\gamma}^{\perp}}$
 for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we want to
-prove $\bar{\mu}\left(\proj{\psi_{2}}\right)=\bar{\mu}\left(\proj{\psi_{3}}\right)=\unlikely$.
+prove $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$.
 Then, we have 
 \begin{equation}
-\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right)=\likely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{3}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
+\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
 \end{aligned}
@@
 \end{equation}
-In order to verify $\bar{\mu}\left(\proj{\psi_{2}}\right)=\bar{\mu}\left(\proj{\psi_{3}}\right)=\unlikely$,
+In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$,
 it is sufficient to prove that $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$
@@
 or $\theta'=\frac{\pi}{2}-\theta=\frac{\pi}{2}$. Similarly, when
-$\ket{\psi_{1}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$ and $\ket{\ps}\notin\mathcal{B}$,
+$\ket{\psi_{0}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$ and $\ket{\ps}\notin\mathcal{B}$,
 equation (\ref{eq:non-additive-vectors}) holds. 
@@
 \begin{equation}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely\subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\label{eq:case3}
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right)=\likely\subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\label{eq:case3}
 \end{equation}
@@
 there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
-for all $P\in\events$. \qed\end{example}
-
+for all $P\in\events$. We first claim that for all $0\le\theta<\frac{\pi}{2}$
+and $0\le\gamma<\pi$, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\frac{1}{2}$.
+On one hand, $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\in\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\likely$
+implies $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\ge\frac{1}{2}$.
+On the other hand, by figure~\ref{fig:three-dimensional-4-value},
+it is easy to see for any neighborhood of $\ket{0_{\theta,\gamma}^{\perp}}$,
+these is always a state~$\ket{\psi}$ such that $\mu_{\rho}^{B}\left(\proj{\psi}\right)\in\bar{\mu}\left(\proj{\psi}\right)=\unlikely$,
+i.e., $\mu_{\rho}^{B}\left(\proj{\psi}\right)\le\frac{1}{2}$. Because
+$\mu_{\rho}^{B}$ is continuous, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\frac{1}{2}$.
+Similarly, $\mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\frac{1}{2}$.
+
+Consider a general density matrix~ $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{2}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=0}^{2}}r_{ij}\ket{i}\bra{j}$.
+Then, we have
+\begin{eqnarray*}
+\frac{1}{2} & = & \mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\\
+ & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{0_{\theta,\gamma}^{\perp}}\right)\\
+ & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
+ & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(r_{i1}\rme^{\rmi\gamma}\sin\theta\ket{i}+r_{i2}\cos\theta\ket{i}\right)\left(\rme^{-\rmi\gamma}\sin\theta\bra{1}+\cos\theta\bra{2}\right)\right)\\
+ & = & r_{11}\sin^{2}\theta+r_{12}\cos\theta\rme^{-\rmi\gamma}\sin\theta+r_{21}\rme^{\rmi\gamma}\sin\theta\cos\theta+r_{22}\cos^{2}\theta
+\end{eqnarray*}
+Because the above equation holds for all $0\le\theta<\frac{\pi}{2}$
+and $0\le\gamma<\pi$, we must have $r_{12}=r_{21}=0$ and $r_{11}=r_{22}=\frac{1}{2}$.\qed\end{example}
 \end{document}

### 2016-10-03 prob.tex
From: Tai, Yu-Tsung Sent: Monday, October 03, 2016 1:59 To: Hanson, Andrew J. <hansona@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Liu, Weihua <liuweih@indiana.edu> Subject: RE: Shapley 1965
Dear all, 

I typed some comments about convex, and found an IVPM which doesn't rely
on the impossible to prove it has an empty core... Keep finding more
examples... Since the computation is more and more complex, maybe I
should write a program to verify some of the computation... 

Besides, when I had a dinner with Prof. Gil Kalai, he asked about
whether we hav

@@
 rule in a sense that it might only correspond to $\ket{2}$ or $\frac{\mathbb{1}}{3}$,
-but not $\ket{1}$, and it is no longer valid for more precise measurement
-equipment as well. In general, we believe if the measurement equipment
-is more and more precise, its interval-valued probability measure
-will be closer and closer to the the Born rule. In the limit case,
-$\mathscr{I}=\left\{ \left\{ a\right\} \middle|a\in\left[0,1\right]\right\} $
+but not $\ket{1}$. Example~\ref{ex:three-dimensional-4-value} is
+also no longer valid for more precise measurement equipment as well.
+In general, we believe if the measurement equipment is more and more
+precise, its interval-valued probability measure will be closer and
+closer to the the Born rule. In the limit case, $\mathscr{I}=\left\{ \left\{ a\right\} \middle|a\in\left[0,1\right]\right\} $
 recovers conventional Gleason's theorem and the Born rule.
@@
 \cos\left(\frac{\pi}{2}-\theta\right)
-\end{pmatrix}=\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
+\end{pmatrix}=\sqrt{2}\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
 \]
@@
  & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
- & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(r_{i1}\rme^{\rmi\gamma}\sin\theta\ket{i}+r_{i2}\cos\theta\ket{i}\right)\left(\rme^{-\rmi\gamma}\sin\theta\bra{1}+\cos\theta\bra{2}\right)\right)\\
+ & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(r_{i1}\rme^{\rmi\gamma}\sin\theta+r_{i2}\cos\theta\right)\ket{i}\left(\rme^{-\rmi\gamma}\sin\theta\bra{1}+\cos\theta\bra{2}\right)\right)\\
  & = & r_{11}\sin^{2}\theta+r_{12}\cos\theta\rme^{-\rmi\gamma}\sin\theta+r_{21}\rme^{\rmi\gamma}\sin\theta\cos\theta+r_{22}\cos^{2}\theta
@@
 Because the above equation holds for all $0\le\theta<\frac{\pi}{2}$
-and $0\le\gamma<\pi$, we must have $r_{12}=r_{21}=0$ and $r_{11}=r_{22}=\frac{1}{2}$.\qed\end{example}
+and $0\le\gamma<\pi$, we must have $r_{12}=r_{21}=0$ and $r_{11}=r_{22}=\frac{1}{2}$.
+We also have
+\begin{eqnarray*}
+\frac{1}{2} & = & \mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)\\
+ & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{\ps_{\theta,\gamma}^{\perp}}\right)\\
+ & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}\right)\left(-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
+ & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(-\frac{r_{i0}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{i1}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{i2}\cos\theta\right)\ket{i}\left(-\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\bra{0}+\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\bra{1}+\cos\theta\bra{2}\right)\right)\\
+ & = & -\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\left(-\frac{r_{00}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{01}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{02}\cos\theta\right)+\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\left(-\frac{r_{10}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{\rme^{\rmi\gamma}\sin\theta}{2\sqrt{2}}\right)\\
+ &  & +\cos\theta\left(-\frac{r_{20}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{\cos\theta}{2}\right)\\
+ & = & \left(\frac{r_{00}\sin^{2}\theta}{2}-\frac{r_{01}\sin^{2}\theta}{2}-\frac{r_{02}\rme^{-\rmi\gamma}\sin\theta\cos\theta}{\sqrt{2}}\right)+\left(-\frac{r_{10}\sin^{2}\theta}{2}+\frac{\sin^{2}\theta}{4}\right)+\left(-\frac{r_{20}\rme^{\rmi\gamma}\cos\theta\sin\theta}{\sqrt{2}}+\frac{\cos^{2}\theta}{2}\right)\\
+ & = & \left(\frac{r_{00}}{2}-\frac{r_{01}}{2}-\frac{r_{10}}{2}+\frac{1}{4}\right)\sin^{2}\theta+\frac{\cos^{2}\theta}{2}-\left(r_{02}\rme^{-\rmi\gamma}+r_{20}\rme^{\rmi\gamma}\right)\frac{\cos\theta\sin\theta}{\sqrt{2}}
+\end{eqnarray*}
+Because of the same reason, we have $r_{02}=r_{20}=0$ and $r_{00}=\frac{1}{2}+r_{01}+r_{10}$.
+Moreover, because $\rho$ is a density matrix, we should have $\Tr\left(\rho\right)=1$
+and $\rho^{\dagger}=\rho$ so that $r_{00}=0$, $r_{01}=-\frac{1}{4}+\rmi b$,
+and $r_{01}=-\frac{1}{4}-\rmi b$, where $b\in\mathbb{R}$. However,
+it is easy to verify that $\rho$ will have a negative eigenvalue.
+This contradicts to the fact that $\rho$ as a a density matrix must
+be a positive operator.\qed\end{example} 
 \end{document}

### 2016-10-08 prob.tex
Updates from ShareLaTeX
prob.tex \section{\label{sec:Examples-for-QuantumIVPM}Examples for Quantum Interval-valued Probability Measures} Updated...

--- 2016-10-02 prob.tex
@@
 
-Although example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value}
-rely on $\imposs$ to deduce that an interval-valued probability measure
-has an empty core, it is not necessary. The following example is modified
-from example~\ref{ex:three-dimensional-4-value}, but has the property
-that $\bar{\mu}\left(P\right)=\imposs$ if and only if $P=\mathbb{0}$.
+Although it is easier to deduce an interval-valued probability measure
+has an empty core by considering the state mapped to $\imposs$ as
+in example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
+it is not the only way to prove an interval-valued probability measure
+has an empty core. The following family of interval-valued probability
+measures satisfy that $\bar{\mu}\left(P\right)=\imposs$ if and only
+if $P=\mathbb{0}$, but we can still prove them have empty cores.
 
 \begin{example}[Another three-dimensional quantum 4-value interval-valued
-probability measure]\label{ex:three-dimensional-4-value-2} Consider\emph{
-}$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-and $\ket{0}$, $\ket{1}$, $\ket{2}$, $\ket{\ps}$, $\ket{\ms}$,
-and $\bar{\mu}$ are defined as in example~\ref{ex:three-dimensional-4-value}
-except 
+probability measure]\label{ex:three-dimensional-4-value-2} Given
+$r_{0}\in\left[\frac{1}{3},\frac{1}{2}\right]$, we are going to construct
+an interval-valued probability measures for each $r_{0}$, and it
+has an empty core whenever $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.
+
+Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\necess,\left[1-2r_{0},r_{0}\right],\left[1-r_{0},2r_{0}\right],\left[2-4r_{0},1-r_{0}\right],\left[r_{0},4r_{0}-1\right]\right\} $.
+This is well-defined since the left-end is less or equal to the right-end
+whenever $r_{0}\ge\frac{1}{3}$. If $\ket{0}$, $\ket{1}$, $\ket{2}$,
+$\ket{\ps}$, $\ket{\ms}$, $\ket{0_{\theta,\gamma}^{\perp}}$, and
+$\ket{\ps_{\theta,\gamma}^{\perp}}$ are defined as in example~\ref{ex:three-dimensional-4-value},
+a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+can be defined as follow: 
+\begin{enumerate}
+\item $\bar{\mu}(\mathbb{0})=\imposs$ and $\bar{\mu}(\mathbb{1})=\necess.$
+\item For the dotted half of the red and green circles in figure~\ref{fig:three-dimensional-4-value},
+i.e., whenever $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$,
+we define 
 \begin{eqnarray*}
-\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \unlikely\\
-\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \likely\textrm{ .}
+\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \left[r_{0},4r_{0}-1\right]\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \left[2-4r_{0},1-r_{0}\right]\textrm{ .}
 \end{eqnarray*}
-By following the same as process as in example~\ref{ex:three-dimensional-4-value},
-it is easy to verify that $\bar{\mu}$ is an interval-valued probability
-measure.
-
+\item Otherwise, $\bar{\mu}(\proj{\psi})=\left[1-2r_{0},r_{0}\right]$ and
+$\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\left[1-r_{0},2r_{0}\right]$. 
+\end{enumerate}
 We now prove $\bar{\mu}$ has an empty core by contradiction. Assume
@@
 for all $P\in\events$. We first claim that for all $0\le\theta<\frac{\pi}{2}$
-and $0\le\gamma<\pi$, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\frac{1}{2}$.
-On one hand, $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\in\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\likely$
-implies $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\ge\frac{1}{2}$.
+and $0\le\gamma<\pi$, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
+On one hand, $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\in\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\left[r_{0},4r_{0}-1\right]$
+implies $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\ge r_{0}$.
 On the other hand, by figure~\ref{fig:three-dimensional-4-value},
 it is easy to see for any neighborhood of $\ket{0_{\theta,\gamma}^{\perp}}$,
-these is always a state~$\ket{\psi}$ such that $\mu_{\rho}^{B}\left(\proj{\psi}\right)\in\bar{\mu}\left(\proj{\psi}\right)=\unlikely$,
-i.e., $\mu_{\rho}^{B}\left(\proj{\psi}\right)\le\frac{1}{2}$. Because
-$\mu_{\rho}^{B}$ is continuous, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\frac{1}{2}$.
-Similarly, $\mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\frac{1}{2}$.
+these is always a state~$\ket{\psi}$ such that $\mu_{\rho}^{B}\left(\proj{\psi}\right)\in\bar{\mu}\left(\proj{\psi}\right)=\left[1-2r_{0},r_{0}\right]$,
+i.e., $\mu_{\rho}^{B}\left(\proj{\psi}\right)\le r_{0}$. Because
+$\mu_{\rho}^{B}$ is continuous, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
+Similarly, $\mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
 
@@
 \begin{eqnarray*}
-\frac{1}{2} & = & \mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\\
+r_{0} & = & \mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\\
  & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{0_{\theta,\gamma}^{\perp}}\right)\\
  & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
- & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(r_{i1}\rme^{\rmi\gamma}\sin\theta\ket{i}+r_{i2}\cos\theta\ket{i}\right)\left(\rme^{-\rmi\gamma}\sin\theta\bra{1}+\cos\theta\bra{2}\right)\right)\\
+ & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(r_{i1}\rme^{\rmi\gamma}\sin\theta+r_{i2}\cos\theta\right)\ket{i}\left(\rme^{-\rmi\gamma}\sin\theta\bra{1}+\cos\theta\bra{2}\right)\right)\\
  & = & r_{11}\sin^{2}\theta+r_{12}\cos\theta\rme^{-\rmi\gamma}\sin\theta+r_{21}\rme^{\rmi\gamma}\sin\theta\cos\theta+r_{22}\cos^{2}\theta
@@
 Because the above equation holds for all $0\le\theta<\frac{\pi}{2}$
-and $0\le\gamma<\pi$, we must have $r_{12}=r_{21}=0$ and $r_{11}=r_{22}=\frac{1}{2}$.\qed\end{example}
+and $0\le\gamma<\pi$, we must have $r_{12}=r_{21}=0$ and $r_{11}=r_{22}=r_{0}$.
+We also have
+\begin{eqnarray*}
+r_{0} & = & \mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)\\
+ & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{\ps_{\theta,\gamma}^{\perp}}\right)\\
+ & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}\right)\left(-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
+ & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(-\frac{r_{i0}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{i1}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{i2}\cos\theta\right)\ket{i}\left(-\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\bra{0}+\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\bra{1}+\cos\theta\bra{2}\right)\right)\\
+ & = & -\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\left(-\frac{r_{00}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{01}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{02}\cos\theta\right)\\
+ &  & +\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\left(-\frac{r_{10}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{0}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}\right)+\cos\theta\left(-\frac{r_{20}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{0}\cos\theta\right)\\
+ & = & \left(\frac{r_{00}\sin^{2}\theta}{2}-\frac{r_{01}\sin^{2}\theta}{2}-\frac{r_{02}\rme^{-\rmi\gamma}\sin\theta\cos\theta}{\sqrt{2}}\right)+\left(-\frac{r_{10}\sin^{2}\theta}{2}+\frac{r_{0}\sin^{2}\theta}{2}\right)+\left(-\frac{r_{20}\rme^{\rmi\gamma}\cos\theta\sin\theta}{\sqrt{2}}+r_{0}\cos^{2}\theta\right)\\
+ & = & \left(\frac{r_{00}}{2}-\frac{r_{01}}{2}-\frac{r_{10}}{2}+\frac{r_{0}}{2}\right)\sin^{2}\theta+r_{0}\cos^{2}\theta-\left(r_{02}\rme^{-\rmi\gamma}+r_{20}\rme^{\rmi\gamma}\right)\frac{\cos\theta\sin\theta}{\sqrt{2}}
+\end{eqnarray*}
+Because of the same reason, we have $r_{02}=r_{20}=0$ and $r_{00}=r_{0}+r_{01}+r_{10}$.
+Moreover, because $\rho$ is a density matrix, we should have $\rho^{\dagger}=\rho$,
+$\Tr\left(\rho\right)=1$, and $\rho$ is a positive operator~\cite{544199}.
+These implies that we can express $r_{01}=a+\rmi b$ and $r_{10}=a-\rmi b$
+for some $a$, $b\in\mathbb{R}$. After plugging into $\Tr\left(\rho\right)=1$,
+we have $r_{00}=1-2r_{0}$, $r_{01}=\frac{1}{2}-\frac{3}{2}r_{0}+\rmi b$,
+and $r_{01}=\frac{1}{2}-\frac{3}{2}r_{0}-\rmi b$. Next, since $\rho$
+is a positive operator, $\rho$ should have all non-negative eigenvalues,
+which are the solutions of the characteristic polynomial
+\begin{eqnarray*}
+0 & = & \det\left(\rho-\lambda\mathbb{1}\right)\\
+ & = & \begin{vmatrix}1-2r_{0}-\lambda & \frac{1}{2}-\frac{3}{2}r_{0}+\rmi b & 0\\
+\frac{1}{2}-\frac{3}{2}r_{0}-\rmi b & r_{0}-\lambda & 0\\
+0 & 0 & r_{0}-\lambda
+\end{vmatrix}\\
+ & = & \left(r_{0}-\lambda\right)\left[\left(1-2r_{0}-\lambda\right)\left(r_{0}-\lambda\right)-\left(\frac{1}{2}-\frac{3}{2}r_{0}+\rmi b\right)\left(\frac{1}{2}-\frac{3}{2}r_{0}-\rmi b\right)\right]\\
+ & = & \left(r_{0}-\lambda\right)\left[\lambda^{2}-\left(1-r_{0}\right)\lambda+r_{0}-2r_{0}^{2}-\frac{1}{4}+\frac{3}{2}r_{0}-\frac{9}{4}r_{0}^{2}-b^{2}\right]\\
+ & = & \left(r_{0}-\lambda\right)\left[\lambda^{2}-\left(1-r_{0}\right)\lambda-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}-b^{2}\right]
+\end{eqnarray*}
+Hence, the solutions of $\lambda$ are $r_{0}$ and $1-r_{0}\pm\sqrt{\left(1-r_{0}\right)^{2}-4\cdot1\cdot\left(-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}-b^{2}\right)}$.
+If they are all non-negative, we want 
+\begin{eqnarray*}
+0 & \ge & -4\cdot1\cdot\left(-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}-b^{2}\right)\\
+ & = & 1-10r_{0}+17r_{0}^{2}+4b^{2}\\
+ & = & 17\left(r_{0}-\frac{5+\sqrt{25-17\cdot\left(4b^{2}+1\right)}}{17}\right)\left(r_{0}-\frac{5-\sqrt{25-17\cdot\left(4b^{2}+1\right)}}{17}\right)
+\end{eqnarray*}
+Therefore, when $r_{0}>\frac{5+2\sqrt{2}}{17}$ or $r_{0}<\frac{5-2\sqrt{2}}{17}$,
+no matter which $b\in\mathbb{R}$, $\rho$ always has a negative eigenvalue.
+This contradiction implies $\bar{\mu}$ has an empty core when $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.\qed\end{example}
+
 \end{document}

### 2016-10-10 prob.tex
prob.tex Update every idea currently have...

@@
 
+\footnote{\yutsung{Notice that Gleason used his conditions to prove quantum
+probability measures are continuous first, and then prove they can
+be got from the Born rule. Since the current examples are all discontinuous,
+maybe ``add continuous'' could give us a interval-valued Gleason's
+theorem (?)
+
+Continuity definitely has physical and computer science meaning. For
+example, we could said something like, ``no matter the underlining
+physical reality, human doesn't have the ability to distinguish discontinuous
+function,`` and cite \cite{Ziegler2007,weihrauch2012computable}.
+However, we might need to rewrite all the interpretation if this approach
+works...}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{eqnarray*}
+\footnote{\yutsung{This case might be simplify if we consider 5 values. Then,
+every state orthogonal to $\ket{0}$ and $\ket{\ps}$ can map to $\left[\frac{1}{4},\frac{3}{4}\right]$.
+Not sure whether we need to simplify the example or not, because this
+example is used in example~\ref{ex:three-dimensional-6-value}. Or
+we may just keep example~\ref{ex:three-dimensional-6-value} in the
+later version if that example is more important...}}
 \item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely$. 
@@
 \end{equation}
-for every orthonormal basis $\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $.
+for every orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $.
 We are going to enumerate all possible orthonormal bases to verify
@@
 for ($0<\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$) or $\theta=0$
-enumerate all possible orthonormal bases. Equation (\ref{eq:non-additive-vectors})
+enumerate all possible orthonormal bases. Equation~(\ref{eq:non-additive-vectors})
 can then be verified as follow. 
@@
 \end{equation}
-Similarly, when $\ket{\psi_{0}}$ is $\ket{\ps}$, equation (\ref{eq:non-additive-vectors})
+Similarly, when $\ket{\psi_{0}}$ is $\ket{\ps}$, equation~(\ref{eq:non-additive-vectors})
 holds. 
@@
 In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$,
-it is sufficient to prove that $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$
-implies ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or
-$\theta'=\frac{\pi}{2}$. Recall $\ip{\ps}{\ps_{\theta',\gamma'}^{\perp}}=0$.
-Hence, if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$, we
-have $\ket{\ps_{\theta',\gamma'}^{\perp}}$ parallel to $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$.
-\[
+it is sufficient to prove that if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
+then ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or $\theta'=\frac{\pi}{2}$.
+Recall $\ip{\ps}{\ps_{\theta',\gamma'}^{\perp}}=0$. Hence, if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
+we have $\ket{\ps_{\theta',\gamma'}^{\perp}}$ parallel to $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$.
+\begin{equation}
 \ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
@@
 \cos\left(\frac{\pi}{2}-\theta\right)
-\end{pmatrix}=\sqrt{2}\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
-\]
+\end{pmatrix}=\sqrt{2}\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\label{eq:case2-cross}
+\end{equation}
 Because of $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we have
@@
 $\ket{\psi_{0}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$ and $\ket{\ps}\notin\mathcal{B}$,
-equation (\ref{eq:non-additive-vectors}) holds. 
+equation~(\ref{eq:non-additive-vectors}) holds. 
 \item Finally, when $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$,
@@
 for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, i.e., the ``otherwise''
-case. Then, equation (\ref{eq:non-additive-vectors}) can easily be
-verified. 
+case. Then, equation~(\ref{eq:non-additive-vectors}) can easily
+be verified. 
 \begin{equation}
@@
 
-\begin{example}[Another three-dimensional quantum 4-value interval-valued
-probability measure]\label{ex:three-dimensional-4-value-2} Given
+\begin{example}{[}Another three-dimensional quantum 6-value interval-valued
+probability measure{]}\label{ex:three-dimensional-6-value} Given
 $r_{0}\in\left[\frac{1}{3},\frac{1}{2}\right]$, we are going to construct
@@
 
-Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\necess,\left[1-2r_{0},r_{0}\right],\left[1-r_{0},2r_{0}\right],\left[2-4r_{0},1-r_{0}\right],\left[r_{0},4r_{0}-1\right]\right\} $.
+Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\necess,\unlikely_{0},\likely_{0},\unlikely_{1},\likely_{1}\right\} $,
+where $\unlikely_{0}=\left[1-2r_{0},r_{0}\right]$, $\likely_{0}=\left[1-r_{0},2r_{0}\right]$,
+$\unlikely_{1}=\left[2-4r_{0},1-r_{0}\right]$, and $\likely_{1}=\left[r_{0},4r_{0}-1\right]$.
 This is well-defined since the left-end is less or equal to the right-end
@@
 \begin{eqnarray*}
-\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \left[r_{0},4r_{0}-1\right]\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \left[2-4r_{0},1-r_{0}\right]\textrm{ .}
+\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely_{1}\\
+\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely_{1}\textrm{ .}
 \end{eqnarray*}
-\item Otherwise, $\bar{\mu}(\proj{\psi})=\left[1-2r_{0},r_{0}\right]$ and
-$\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\left[1-r_{0},2r_{0}\right]$. 
+\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely_{0}$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely_{0}$. 
 \end{enumerate}
@@
 it is easy to see for any neighborhood of $\ket{0_{\theta,\gamma}^{\perp}}$,
-these is always a state~$\ket{\psi}$ such that $\mu_{\rho}^{B}\left(\proj{\psi}\right)\in\bar{\mu}\left(\proj{\psi}\right)=\left[1-2r_{0},r_{0}\right]$,
+these is always a state~$\ket{\psi}$ such that $\mu_{\rho}^{B}\left(\proj{\psi}\right)\in\bar{\mu}\left(\proj{\psi}\right)=\unlikely_{0}$,
 i.e., $\mu_{\rho}^{B}\left(\proj{\psi}\right)\le r_{0}$. Because
@@
 Therefore, when $r_{0}>\frac{5+2\sqrt{2}}{17}$ or $r_{0}<\frac{5-2\sqrt{2}}{17}$,
-no matter which $b\in\mathbb{R}$, $\rho$ always has a negative eigenvalue.
-This contradiction implies $\bar{\mu}$ has an empty core when $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.\qed\end{example}
+$\rho$ always has a negative eigenvalue for all~$b\in\mathbb{R}$.
+This contradiction implies $\bar{\mu}$ has an empty core when $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.
+
+Similar to example~\ref{ex:three-dimensional-4-value}, to verify
+$\bar{\mu}$ is a quantum interval-valued probability measure for
+$r_{0}\in\left[\frac{1}{3},\frac{1}{2}\right]$, we are going to enumerate
+all possible orthonormal bases~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
+to verify equation~(\ref{eq:non-additive-vectors}).
+\begin{enumerate}
+\item When $\ket{\psi_{0}}=\ket{0_{\theta,\gamma}^{\perp}}$ for $0\le\theta<\frac{\pi}{2}$
+and $0\le\gamma<\pi$, we want to prove $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely_{0}$.
+Then, we have 
+\begin{equation}
+\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely_{1}=\left[2-4r_{0},1-r_{0}\right]\\
+\subseteq & \left[2-4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
+ & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely_{0}=\left[1-r_{0},2r_{0}\right]\\
+\subseteq & \left[1-r_{0},5r_{0}-1\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\likely_{1}=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
+\end{aligned}
+\label{eq:case2-2}
+\end{equation}
+In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$,
+it is sufficient to prove that if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
+then ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or $\theta'=\frac{\pi}{2}$.
+This is easy because of equation~(\ref{eq:case2-cross}). Similarly,
+when $\ket{\psi_{0}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$, equation~(\ref{eq:non-additive-vectors})
+holds. 
+\item Otherwise, when $\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$,
+and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$ for $0\le\theta<\frac{\pi}{2}$
+and $0\le\gamma<\pi$, equation~(\ref{eq:non-additive-vectors})
+can easily be verified. 
+\begin{equation}
+\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right)=\likely_{0}=\left[1-r_{0},2r_{0}\right]\\
+\subseteq & \left[2-4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
+\end{aligned}
+\label{eq:case3-2}
+\end{equation}
+\end{enumerate}
+\qed\end{example}
+
+\yutsung{Since we have a family of interval-valued probability measures
+with empty cores, we need to find a more systematically way to how
+close these interval-valued probability measures to the Born rule.
+Need to check whether people defined the distance between games or
+not... Possible candidates are sup-norm or total variation distance(?)}
 

### 2016-10-10 prob.tex
prob.tex \section{\label{sec:Examples-for-QuantumIVPM}Examples for Quantum Interval-valued Probability Measures} Fixing operator types...

@@
 
-\begin{example}{[}Another three-dimensional quantum 6-value interval-valued
-probability measure{]}\label{ex:three-dimensional-6-value} Given
+Although it is easier to deduce an interval-valued probability measure
+has an empty core by considering the state mapped to $\imposs$ as
+in example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
+it is not the only way to prove an interval-valued probability measure
+has an empty core. The following family of interval-valued probability
+measures satisfy that $\bar{\mu}\left(P\right)=\imposs$ if and only
+if $P=\mathbb{0}$, but we can still prove them have empty cores.
+
+\begin{example}[Another three-dimensional quantum 6-value interval-valued
+probability measure]\label{ex:three-dimensional-6-value} Given
 $r_{0}\in\left[\frac{1}{3},\frac{1}{2}\right]$, we are going to construct
 an interval-valued probability measures for each $r_{0}$, and it
-has an empty core whenever $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.
+has an empty core whenever $r_{0}\in\left(\frac{5\tensor*[_{\mathbb{R}}]{+}{}2\sqrt{2}}{17},\frac{1}{2}\right]$.
 
 Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\necess,\unlikely_{0},\likely_{0},\unlikely_{1},\likely_{1}\right\} $,
-where $\unlikely_{0}=\left[1-2r_{0},r_{0}\right]$, $\likely_{0}=\left[1-r_{0},2r_{0}\right]$,
-$\unlikely_{1}=\left[2-4r_{0},1-r_{0}\right]$, and $\likely_{1}=\left[r_{0},4r_{0}-1\right]$.
+where $\unlikely_{0}=\left[1\tensor*[_{\mathbb{R}}]{-}{}2r_{0},r_{0}\right]$,
+$\likely_{0}=\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{0},2r_{0}\right]$,
+$\unlikely_{1}=\left[2\tensor*[_{\mathbb{R}}]{-}{}4r_{0},1\tensor*[_{\mathbb{R}}]{-}{}r_{0}\right]$,
+and $\likely_{1}=\left[r_{0},4r_{0}\tensor*[_{\mathbb{R}}]{-}{}1\right]$.
 This is well-defined since the left-end is less or equal to the right-end
@@
 and $0\le\gamma<\pi$, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
-On one hand, $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\in\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\left[r_{0},4r_{0}-1\right]$
+On one hand, $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\in\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\left[r_{0},4r_{0}\tensor*[_{\mathbb{R}}]{-}{}1\right]$
 implies $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\ge r_{0}$.
@@
 \begin{eqnarray*}
-0 & = & \det\left(\rho-\lambda\mathbb{1}\right)\\
+0 & = & \det\left(\rho\tensor*[_{\mathscr{O}}]{-}{}\lambda\mathbb{1}\right)\\
  & = & \begin{vmatrix}1-2r_{0}-\lambda & \frac{1}{2}-\frac{3}{2}r_{0}+\rmi b & 0\\
@@
 \end{eqnarray*}
-Hence, the solutions of $\lambda$ are $r_{0}$ and $1-r_{0}\pm\sqrt{\left(1-r_{0}\right)^{2}-4\cdot1\cdot\left(-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}-b^{2}\right)}$.
+Hence, the solutions of $\lambda$ are $r_{0}$ and $1-r_{0}\pm\sqrt{\left(1-r_{0}\right)^{2}-4\cdot1\cdot\left(-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}\mathbb{R}-b^{2}\right)}$.
 If they are all non-negative, we want 
@@
 $\rho$ always has a negative eigenvalue for all~$b\in\mathbb{R}$.
-This contradiction implies $\bar{\mu}$ has an empty core when $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.
+This contradiction implies $\bar{\mu}$ has an empty core when $r_{0}\in\left(\frac{5\tensor*[_{\mathbb{R}}]{+}{}2\sqrt{2}}{17},\frac{1}{2}\right]$.
 
@@
 \begin{equation}
-\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely_{1}=\left[2-4r_{0},1-r_{0}\right]\\
-\subseteq & \left[2-4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
- & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely_{0}=\left[1-r_{0},2r_{0}\right]\\
-\subseteq & \left[1-r_{0},5r_{0}-1\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\likely_{1}=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
+\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely_{1}=\left[2\tensor*[_{\mathbb{R}}]{-}{}4r_{0},1\tensor*[_{\mathbb{R}}]{-}{}r_{0}\right]\\
+\subseteq & \left[2\tensor*[_{\mathbb{R}}]{-}{}4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
+ & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely_{0}=\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{0},2r_{0}\right]\\
+\subseteq & \left[1\tensor*[_{\mathbb{R}}]{-}{}r_{0},5r_{0}\tensor*[_{\mathbb{R}}]{-}{}1\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\likely_{1}=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
 \end{aligned}
@@
 \end{equation}
-In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$,
+In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely_{0}$,
 it is sufficient to prove that if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
@@
 \begin{equation}
-\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right)=\likely_{0}=\left[1-r_{0},2r_{0}\right]\\
-\subseteq & \left[2-4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
+\begin{aligned} & \bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right)=\likely_{0}=\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{0},2r_{0}\right]\\
+\subseteq & \left[2\tensor*[_{\mathbb{R}}]{-}{}4r_{0},2r_{0}\right]=\unlikely_{0}\tensor*[_{\mathscr{I}}]{+}{}\unlikely_{0}=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
 \end{aligned}

### 2016-10-10 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} Update the type of the operators...

@@
 of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
-it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
+it is possible to use the sum of the intervals $[l_{1}\tensor*[_{\mathbb{R}}]{+}{}l_{2},r_{1}\tensor*[_{\mathbb{R}}]{+}{}r_{2}]$
 as the combined probability, one can do find a much tighter interval
@@
 contradicts $E$ is an evidence supporting the complement of $E$.
-The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
+The complement of $E$ must therefore have probability $\left[1\tensor*[_{\mathbb{R}}]{-}{}r,1\tensor*[_{\mathbb{R}}]{-}{}l\right]$
 which we abbreviate $\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
@@
 \begin{eqnarray*}
- &  & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
- & = & \imposs+\unlikely+\imposs+\likely\\
- & = & \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=\left[\frac{1}{2},\frac{3}{2}\right]
+ &  & \bar{\mu}(\{HH\})\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}(\{HT\})\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}(\{TH\})\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}(\{TT\})\\
+ & = & \imposs\tensor*[_{\mathscr{I}}]{+}{}\unlikely\tensor*[_{\mathscr{I}}]{+}{}\imposs\tensor*[_{\mathscr{I}}]{+}{}\likely\\
+ & = & \left[0,0\right]\tensor*[_{\mathscr{I}}]{+}{}\left[0,\frac{1}{2}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[0,0\right]\tensor*[_{\mathscr{I}}]{+}{}\left[\frac{1}{2},1\right]=\left[\frac{1}{2},\frac{3}{2}\right]
 \end{eqnarray*}
@@
 However, using the fact that $\bar{\mu}(\emptyset)=\imposs$, we have
-$\bar{\mu}\left(\Omega\right)=1-\bar{\mu}\left(\emptyset\right)=\necess=[1,1]$.
+$\bar{\mu}\left(\Omega\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(\emptyset\right)=\necess=[1,1]$.
 This interval is tighter and a better estimate for the probability

### 2016-10-19 prob.tex
prob.tex "\subsection{Classical Real-Valued Probability Spaces}" Matching parathesis...

@@
 \item For a collection $\left\{ E_{i}\right\} _{i=0}^{N-1}$ of pairwise
-disjoint events, $\pmeas(\bigcup_{i=0}^{N-1}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\pmeas(E_{i})$.
+disjoint events, $\pmeas\left(\bigcup_{i=0}^{N-1}E_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\pmeas(E_{i})$.
 Similar to the above condition, $\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\pmeas(E_{i})$

### 2016-10-20 prob.tex
prob.tex "\subsection{Quantum Real-valued Probability Measures}" Update citation...

@@
 its Radon-Nikodym derivative. Similarly, a quantum probability measure
-can be easily constructed by states according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
+can be easily constructed by states according to the Born rule~\cite{Born1983,Mermin2007,Jaeger2007}.
 For each pure normalized ($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$,
@@
 the quantum probability measure introduced by $\rho$ is the combination
-of $\mu_{\phi_{j}}^{B}$ with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
+of $\mu_{\phi_{j}}^{B}$ with respect to probability $q_{j}$~\cite{peres1995quantum,544199,Jaeger2007}:
 \begin{eqnarray}

### 2016-10-26 prob.tex
prob.tex "\section{Proof}" Added...
prob.tex "\section{Proof}" Updated...

@@
 
+%%%%%
+
+\section{Proof}
+
+Because the importance of Gleason's theorem, its proof have been rewritten
+to be more accessible~\cite{CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+
+Here we want to follow \cite{RichmanBridges1999} to prove under suitable
+conditions when intervals are more precise, its quantum interval-valued
+probability measures are closer to the Born rule. We will focus on
+three dimensional Hilbert space, since
+
 \end{document}

### 2016-10-26 prob.tex
prob.tex \section{Proof} Keep typing...

@@
 \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=0}^{N-1}$,
-we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{N-1}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\mu\left(P_{i}\right)$
-. 
+we have 
+\begin{equation}
+\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{N-1}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\mu\left(P_{i}\right)\textrm{ .}\label{eq:QuantumReal-valuedProbability-Add}
+\end{equation}
 \end{itemize}
@@
 to be more accessible~\cite{CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+Since the additivity of the quantum probability measure~(\ref{eq:QuantumReal-valuedProbability-Add}),
+a quantum probability measure~$\mu$ is completely determined by
+its value on the one-dimensional projections~$\mu\left(\proj{\psi}\right)$.
 

### 2016-10-27 prob.tex
prob.tex Change the symbol for Radon-Nikodym derivative from f to m...

@@
 \begin{equation}
-\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum f(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
+\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum m(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
 \end{equation}
-where $f:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum f(\omega)=1$,
-and $f$ is called the Radon-Nikodym derivative of $\pmeas$ (with
+where $m:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum m(\omega)=1$,
+and $m$ is called the Radon-Nikodym derivative of $\pmeas$ (with
 respect to the counting measure)~\cite{Nikodym1930,Folland1999}.
@@
 For every probability measure~$\pmeas$, there exists a unique Radon-Nikodym
-derivative~$f$ such that equation~(\ref{eq:Radon-Nikodym}) holds.\qed\end{thm}
+derivative~$m$ such that equation~(\ref{eq:Radon-Nikodym}) holds.\qed\end{thm}
 
@@
 \begin{array}{rcl}
-f\left(HH\right)=1/3,\quad f\left(HT\right)=0,\quad f\left(TH\right)=2/3,\quad f\left(TT\right)=0\textrm{ .}\end{array}
+m\left(HH\right)=1/3,\quad m\left(HT\right)=0,\quad m\left(TH\right)=2/3,\quad m\left(TT\right)=0\textrm{ .}\end{array}
 \]
@@
 corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-to another set function~$\bar{f}:\events\rightarrow\bar{\mathscr{I}}$
+to another set function~$\bar{m}:\events\rightarrow\bar{\mathscr{I}}$
 which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman1997}.
@@
 By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
-of $\pmeas'$ is $f\left(\ket{\psi_{j}}\right)=r_{jj}$, which is
+of $\pmeas'$ is $m\left(\ket{\psi_{j}}\right)=r_{jj}$, which is
 just the diagonal elements of $\rho$. In this sense, the Radon-Nikodym
-derivative~$f$ is a special case of the density matrix~$\rho$,
+derivative~$m$ is a special case of the density matrix~$\rho$,
 and the Radon-Nikodym theorem is a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.

### 2016-10-27 prob.tex
prob.tex \section{Proof} updating definitions...

@@
 
+\begin{definition}\cite{Hatcher2001}~The unit sphere in $\mathbb{R}^{d}$
+is denoted by $S^{d-1}$.\qed\end{definition}
+
+\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
+called an \emph{approximation frame function} of weight~$\left(\underline{W},\overline{W}\right)$
+if 
+\[
+\underline{W}\le\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{d-1}}f\left(\ket{\psi_{i}}\right)\le\overline{W}
+\]
+ for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
+of $\mathbb{R}^{d}$.\qed\end{definition}
+
+\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
+is a frame function of weight~$\left(\underline{W},\overline{W}\right)$,
+and $\ket{\psi}\in S^{2}$, then the \emph{symmetrization} of $f$
+with respect to $\ket{\psi}$ is the function~$g:S^{2}\rightarrow\mathbb{R}$
+defined by
+\[
+g\left(\ket{\phi}\right)=f\left(\ket{\phi}\right)+f\left(\sigma\ket{\phi}\right)
+\]
+where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{\psi}$.\qed\end{definition}
+
 \end{document}

### 2016-10-27 prob.tex
prob.tex \section{Proof} Updating...

--- 2016-10-27 prob.tex
@@
 
-Here we want to follow \cite{RichmanBridges1999} to prove under suitable
-conditions when intervals are more precise, its quantum interval-valued
-probability measures are closer to the Born rule. We will focus on
-three dimensional Hilbert space, since
+\begin{definition}\cite{Hatcher2001}~The unit sphere in $\mathbb{R}^{d}$
+is denoted by $S^{d-1}$.\qed\end{definition}
+
+\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
+called an \emph{approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
+if 
+\[
+W_{l}\le\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{d-1}}f\left(\ket{\psi_{i}}\right)\le W_{r}
+\]
+ for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
+of $\mathbb{R}^{d}$.\qed\end{definition}
+
+\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
+the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}
+
+\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
+the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}
+
+\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
+is a frame function of weight~$\left(W_{l},W_{r}\right)$, and $\ket{\psi}\in S^{2}$,
+then the \emph{symmetrization} of $f$ with respect to $\ket{\psi}$
+is the function~$g:S^{2}\rightarrow\mathbb{R}$ defined by
+\[
+g\left(\ket{\phi}\right)=f\left(\ket{\phi}\right)+f\left(\sigma\ket{\phi}\right)
+\]
+where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{\psi}$.\qed\end{definition}
+
+The following theorem is an analog to Corollary 22 in \cite{RichmanBridges1999}.
+
+\begin{thm}Let $f$ be an bounded continuous frame function of weight~$\left(W_{l},W_{r}\right)$,
+$m=\inf f$ or $m=\sup f$, and $W=\left(W_{l}+W_{r}\right)/2$. Let
+$Q$ be the quadratic form given by
+\[
+Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
+\]
+For each $\delta>0$, there is $\eta>0$ such that if
+\begin{itemize}
+\item $\ket{\psi}\in S^{2}$such that $\left|f\left(\ket{\psi}\right)-m\right|<\eta$,
+and 
+\item $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$.
+\end{itemize}
+then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\omega_{f}^{-1}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
+where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
+is the smallest integer not less than $x$.\qed\end{thm}
+
+We can see that for a
 

### 2016-10-29 prob.tex
prob.tex \section{Proof} Delete duplicated definition...
prob.tex \section{Proof} Add citation...

@@
 
-\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
-the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}
-
-\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
-the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}
+\begin{definition}\cite{WheedenZygmund1977}~For any continuous
+function~$f:S^{d-1}\rightarrow\mathbb{R}$, the modulus of continuity
+of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}
 

### 2016-10-30 prob.tex
prob.tex \section{Proof} Updating...

--- 2016-10-27 prob.tex
@@
 
-\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
-the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}
-
-\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
-the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}
+\begin{definition}\cite{CourantJohn1965,Voevodskyothers2013}~For
+any function~$f$, a function~$\varDelta_{f}:\left(0,\infty\right]\rightarrow\left(0,\infty\right]$
+is a modulus of continuity of $f$ if for every $\epsilon>0$, $\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\varDelta_{f}\left(\epsilon\right)$
+implies $\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|<\epsilon$.\qed\end{definition}
+
+Notice that a function $f$ may have more than one modulus of continuity.
+For example, $\varDelta_{f}\left(\epsilon\right)=\frac{\epsilon}{2}$
+and $\epsilon$ are both modulus of continuity of $f\left(\ket{\psi}\right)=\left|\ip{\psi}{0}\right|^{2}$
+on $S^{2}$. Conversely, a function may be a modulus of continuity
+of two different functions. For example, $\varDelta\left(\epsilon\right)=\frac{\epsilon}{2}$
+is a modulus of continuity of both $f\left(\ket{\psi}\right)=\left|\ip{\psi}{0}\right|^{2}$
+and $f\left(\ket{\psi}\right)=\frac{1}{3}$ on $S^{2}$.
 
 \begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
-is a frame function of weight~$\left(W_{l},W_{r}\right)$, and $\ket{\psi}\in S^{2}$,
-then the \emph{symmetrization} of $f$ with respect to $\ket{\psi}$
-is the function~$g:S^{2}\rightarrow\mathbb{R}$ defined by
+is a approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+and $\ket{\psi}\in S^{2}$, then the \emph{symmetrization} of $f$
+with respect to $\ket{\psi}$ is the function~$g:S^{2}\rightarrow\mathbb{R}$
+defined by
 \[
@@
 
-The following theorem is an analog to Corollary 22 in \cite{RichmanBridges1999}.
-
-\begin{thm}Let $f$ be an bounded continuous frame function of weight~$\left(W_{l},W_{r}\right)$,
+The following theorem is an analog to Corollary~22 in \cite{RichmanBridges1999}.
+The only significant difference is that we assume the approximation
+frame function is continuous. The approximation frame function might
+not be continuous as in all of our previous example, while the frame
+function in original Gleason's theorem is always continuous. Thus,
+we need to assume the continuity to follow the proof in \cite{RichmanBridges1999}.
+
+\begin{thm}\label{thm:analogCorollary22RichmanBridges1999}Let $f$
+be an bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
 $m=\inf f$ or $m=\sup f$, and $W=\left(W_{l}+W_{r}\right)/2$. Let
@@
 \end{itemize}
-then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\omega_{f}^{-1}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
+then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\varDelta_{f}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
 where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
@@
 
-We can see that for a
+Since $\delta$ can be arbitrary small in theorem~\ref{thm:analogCorollary22RichmanBridges1999},
+we can get the following corollary.
+
+\begin{cor}Let $f$ be a bounded continuous approximation frame function
+of weight~$\left(W_{l},W_{r}\right)$, $m=\min f=f\left(\ket{\psi}\right)$
+or $m=\max f=f\left(\ket{\psi}\right)$, and $W=\left(W_{l}+W_{r}\right)/2$.
+Let $Q$ be the quadratic form given by
+\[
+Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
+\]
+If $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$,
+then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
+
+Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
+which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
+Theorem~23 reads as the following.
+
+\begin{thm}Let $f$ be a bounded frame function on the unit sphere
+in $\mathbb{R}^{3}$, and $\delta>0$. Then there is a quadratic form
+$Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le3\delta$
+for all $\ket{\phi}$ on the sphere.\qed\end{thm}
+
+Currently, we can only prove the following.
 

### 2016-10-30 prob.tex
prob.tex Saperate two sections: Theorems and Proofs...

@@
 
-\section{Proof}
+\section{Theorems}
 
@@
 Currently, we can only prove the following.
+
+%%%%%
+
+\section{Proofs}
+
+\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
+is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+and there is a point~$\ket{\psi}\in S^{2}$, then the oscillation
+on any latitude of the symmetrization of $f$ with respect to $\ket{\psi}$
+is?\qed\end{lemma}
+\begin{proof}
+Consider $\ket{\psi}$ to be the north pole of $S^{2}$. Let $g$
+be the symmetrization of $f$ with respect to $\ket{\psi}$, and $\eta=f\left(\ket{\psi}\right)$.
+Let 
+\begin{eqnarray*}
+\omega_{f}\left(\delta\right) & = & \sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|\\
+\omega_{g}\left(\delta\right) & = & \sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|g\left(\ket{\psi}\right)-g\left(\ket{\phi}\right)\right|=2\omega_{f}\left(\delta\right)
+\end{eqnarray*}
+Then, for any latitude $\theta_{0}$, the oscillation of $g$ on the
+polar cap of latitude $2\theta_{0}-\frac{\pi}{2}$ is less than $\omega_{g}\left(2\sin2\theta_{0}\right)=2\omega_{f}\left(2\sin2\theta_{0}\right)$.
+
+Let $\ket{\phi}$ and $\ket{\phi'}$ be points in the northern hemisphere
+with the same latitude~$\theta$. If $\theta>2\theta_{0}-\frac{\pi}{2}$,
+both $\ket{\phi}$ and $\ket{\phi'}$ are in the polar cap, so $\left|g\left(\ket{\phi}\right)-g\left(\ket{\phi'}\right)\right|<\omega_{g}\left(2\sin2\theta_{0}\right)=2\omega_{f}\left(2\sin2\theta_{0}\right)$.
+Otherwise, consider $\theta\le2\theta_{0}-\frac{\pi}{2}$. Let $a$
+be the difference in longitudes of $\ket{\phi}$ and $\ket{\phi'}$.
+Take $n$ steps along east-west great circles to go from $\ket{\phi'}$
+to a point $\ket{\phi_{s}}$ due south of $\ket{\phi}$. The difference
+in latitude between $\ket{\phi}$ and $\ket{\phi_{s}}$ is at most
+$\frac{a^{2}}{n}$, while, from (Lemma 16 to be typed),
+\[
+g\left(\ket{\phi_{s}}\right)\ge g\left(\ket{\phi'}\right)-n\left[2f\left(\ket{\psi}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)
+\]
+When the difference in latitude between $\ket{\phi}$ and $\ket{\phi_{s}}$
+is at most $\frac{a^{2}}{n}$, the length between $\ket{\phi}$ and
+$\ket{\phi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
+and hence 
+\[
+g\left(\ket{\phi}\right)\ge g\left(\ket{\phi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
+\]
+for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.
+\end{proof}
 

### 2016-10-31 prob.tex
prob.tex \appendix Updating...

--- 2016-10-30 prob.tex
@@
 of $\mathbb{R}^{d}$.\qed\end{definition}
+
+\begin{definition}\cite{WheedenZygmund1977}~For any function~$f$,
+the modulus of continuity of $f$ is $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}
 
@@
 be an bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
-$m=\inf f$ or $m=\sup f$, and $W=\left(W_{l}+W_{r}\right)/2$. Let
-$Q$ be the quadratic form given by
+$m=\inf f$ or $m=\sup f$, and $W=\frac{W_{l}+W_{r}}{2}$. Let $Q$
+be the quadratic form given by
 \[
@@
 of weight~$\left(W_{l},W_{r}\right)$, $m=\min f=f\left(\ket{\psi}\right)$
-or $m=\max f=f\left(\ket{\psi}\right)$, and $W=\left(W_{l}+W_{r}\right)/2$.
+or $m=\max f=f\left(\ket{\psi}\right)$, and $W=\frac{W_{l}+W_{r}}{2}$.
 Let $Q$ be the quadratic form given by
@@
 Currently, we can only prove the following.
+
+%%%%%
+
+\section{Proofs}
+
+The following theorem is an analog to Lemma~20 in \cite{RichmanBridges1999}.
+
+\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
+is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
+of the symmetrization of $f$ with respect to $\ket{0}$ is at most
+$2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$
+for some integer $n\ge2\pi$. The exact $n$ could be computed to
+minimize the oscillation when the function $f$ is given.\qed\end{lemma}
+\begin{proof}
+Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
+the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$.
+Let $\ket{\phi}$ and $\ket{\phi'}$ be points in the northern hemisphere
+with the same latitude~$\theta$. Let $a$ be the difference in longitudes
+of $\ket{\phi}$ and $\ket{\phi'}$. Take $n$ steps along east-west
+great circles to go from $\ket{\phi'}$ to a point $\ket{\phi_{s}}$
+due south of $\ket{\phi}$. The difference in latitude between $\ket{\phi}$
+and $\ket{\phi_{s}}$ is at most $\frac{a^{2}}{n}$, while, from (Lemma
+16 to be typed),
+\[
+g\left(\ket{\phi_{s}}\right)\ge g\left(\ket{\phi'}\right)-n\left[2f\left(\ket{\psi}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
+\]
+When the difference in latitude between $\ket{\phi}$ and $\ket{\phi_{s}}$
+is at most $\frac{a^{2}}{n}$, the length between $\ket{\phi}$ and
+$\ket{\phi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
+and hence 
+\[
+g\left(\ket{\phi}\right)\ge g\left(\ket{\phi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
+\]
+for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
+Since $f$ is continuous in this case, we could solve $n\ge2\pi$
+such that $2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\le\frac{\delta}{2}$
+for any $\delta>0$, and then solve $\eta\ge0$ such that $2n\eta\le\frac{\delta}{2}$.}}
+\end{proof}
+The following theorem is an analog to Theorem~21 in \cite{RichmanBridges1999}.
+
+\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}
+\begin{itemize}
+\item Let $f$ be a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
+\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$, and 
+\item $Q\left(\ket{\phi}\right)=W\left(1-\ip{0}{\phi}^{2}\right)$. 
+\end{itemize}
+Then, $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le$.\qed\end{thm}
+\begin{proof}
+Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g$
+is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
+and that 
+\end{proof}
 

### 2016-11-01 prob.tex
prob.tex \appendix proving thm:analogTheorem21RichmanBridges1999

@@
 is a approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
-and $\ket{\psi}\in S^{2}$, then the \emph{symmetrization} of $f$
-with respect to $\ket{\psi}$ is the function~$g:S^{2}\rightarrow\mathbb{R}$
-defined by
-\[
-g\left(\ket{\phi}\right)=f\left(\ket{\phi}\right)+f\left(\sigma\ket{\phi}\right)
-\]
-where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{\psi}$.\qed\end{definition}
+then the \emph{symmetrization} of $f$ with respect to $\ket{0}$
+is the function~$g:S^{2}\rightarrow\mathbb{R}$ defined by
+\[
+g\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\sigma\ket{\psi}\right)
+\]
+where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{0}$.\qed\end{definition}
 
@@
 \[
-Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
+Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)
 \]
@@
 \begin{itemize}
-\item $\ket{\psi}\in S^{2}$such that $\left|f\left(\ket{\psi}\right)-m\right|<\eta$,
-and 
-\item $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$.
+\item $\left|f\left(\ket{0}\right)-m\right|<\eta$, and 
+\item $g$ is the symmetrization of $f$ with respect to $\ket{0}$.
 \end{itemize}
-then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\varDelta_{f}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
+then $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\varDelta_{f}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
 where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
@@
 \begin{cor}Let $f$ be a bounded continuous approximation frame function
-of weight~$\left(W_{l},W_{r}\right)$, $m=\min f=f\left(\ket{\psi}\right)$
-or $m=\max f=f\left(\ket{\psi}\right)$, and $W=\frac{W_{l}+W_{r}}{2}$.
+of weight~$\left(W_{l},W_{r}\right)$, $m=\min f=f\left(\ket{0}\right)$
+or $m=\max f=f\left(\ket{0}\right)$, and $W=\frac{W_{l}+W_{r}}{2}$.
 Let $Q$ be the quadratic form given by
 \[
-Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
-\]
-If $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$,
-then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
+Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)
+\]
+If $g$ is the symmetrization of $f$ with respect to $\ket{0}$,
+then $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
 
@@
 $Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le3\delta$
-for all $\ket{\phi}$ on the sphere.\qed\end{thm}
+for all $\ket{\psi}$ on the sphere.\qed\end{thm}
 
@@
 of the symmetrization of $f$ with respect to $\ket{0}$ is at most
-$2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$
-for some integer $n\ge2\pi$. The exact $n$ could be computed to
-minimize the oscillation when the function $f$ is given.\qed\end{lemma}
+$\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+The exact $n$ could be computed to minimize the oscillation when
+the function $f$ is given.\qed\end{lemma}
 \begin{proof}
@@
 the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$.
-Let $\ket{\phi}$ and $\ket{\phi'}$ be points in the northern hemisphere
+Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
 with the same latitude~$\theta$. Let $a$ be the difference in longitudes
-of $\ket{\phi}$ and $\ket{\phi'}$. Take $n$ steps along east-west
-great circles to go from $\ket{\phi'}$ to a point $\ket{\phi_{s}}$
-due south of $\ket{\phi}$. The difference in latitude between $\ket{\phi}$
-and $\ket{\phi_{s}}$ is at most $\frac{a^{2}}{n}$, while, from (Lemma
-16 to be typed),
-\[
-g\left(\ket{\phi_{s}}\right)\ge g\left(\ket{\phi'}\right)-n\left[2f\left(\ket{\psi}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
-\]
-When the difference in latitude between $\ket{\phi}$ and $\ket{\phi_{s}}$
-is at most $\frac{a^{2}}{n}$, the length between $\ket{\phi}$ and
-$\ket{\phi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
+of $\ket{\psi}$ and $\ket{\psi'}$. Take $n$ steps along east-west
+great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
+due south of $\ket{\psi}$\footnote{Double check how many step at least from $\ket{\psi'}$ to a point
+$\ket{\psi_{s}}$.}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
+is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be typed...},
+\[
+g\left(\ket{\psi_{s}}\right)\ge g\left(\ket{\psi'}\right)-n\left[2f\left(\ket{0}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
+\]
+When the difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
+is at most $\frac{a^{2}}{n}$, the length between $\ket{\psi}$ and
+$\ket{\psi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
 and hence 
 \[
-g\left(\ket{\phi}\right)\ge g\left(\ket{\phi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
+g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
 \]
@@
 $W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
-\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$, and 
-\item $Q\left(\ket{\phi}\right)=W\left(1-\ip{0}{\phi}^{2}\right)$. 
+\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
+\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
+and 
+\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 \end{itemize}
-Then, $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le$.\qed\end{thm}
+Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
 \begin{proof}
@@
 is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
-and that 
+and that $W_{l}\le\eta+g\left(\ket{\psi}\right)\le W_{r}$ for all
+$\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
+the oscillation of $g$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.
+
+If $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}$ are
+orthogonal vectors on the closed northern hemisphere, then $\ell\left(\ket{\psi_{0}}\right)+\ell\left(\ket{\psi_{1}}\right)+\ell\left(\ket{\psi_{2}}\right)=1$.
+Conversely, if $a_{0}+a_{1}+a_{2}=1$, for $a_{i}\in\left[0,1\right]$,
+then there exist orthogonal vectors~$\ket{\psi_{0}}$, $\ket{\psi_{1}}$,
+and $\ket{\psi_{2}}$ on the closed northern hemisphere such that
+$a_{i}=\ell\left(\ket{\psi_{i}}\right)$.
+
+For any point $\ket{\psi}$ in the closed northern hemisphere, consider
+
+For each $\varphi$ define $F_{\varphi}$ on $\left[0,1\right]$ by
+setting $F_{\varphi}\left(\ell\left(\ket{\psi}\right)\right)=W-g\left(\ket{\psi}\right)$
+where $\ket{\psi}$ is a point in the closed northern hemisphere with
+longitude~$\varphi$.
+Then, $\left|F_{\varphi}\left(a_{i}\right)-\left(W-g\left(\ket{\psi_{i}}\right)\right)\right|\le2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$
 \end{proof}

### 2016-11-01 prob.tex
prob.tex \section{Proofs} thm:analogTheorem21RichmanBridges1999 Briefly proved...

@@
 great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
-due south of $\ket{\psi}$\footnote{Double check how many step at least from $\ket{\psi'}$ to a point
-$\ket{\psi_{s}}$.}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
-is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be typed...},
+due south of $\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
+to a point $\ket{\psi_{s}}$.}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
+is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{\yutsung{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be
+typed...}},
 \[
@@
 
-\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}
+\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}~ 
 \begin{itemize}
-\item Let $f$ be a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+\item Let $f$ be a continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
+and need to rewrite Lemma~19 if we want to take away this ``continuous''...}} nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
 $W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
@@
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
+Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
 \begin{proof}
@@
 is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
-and that $W_{l}\le\eta+g\left(\ket{\psi}\right)\le W_{r}$ for all
-$\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
+and that $W_{l}-\eta\le g\left(\ket{\psi}\right)\le W_{r}-\eta$ for
+all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
 the oscillation of $g$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.
@@
 For any point $\ket{\psi}$ in the closed northern hemisphere, consider
-
-For each $\varphi$ define $F_{\varphi}$ on $\left[0,1\right]$ by
-setting $F_{\varphi}\left(\ell\left(\ket{\psi}\right)\right)=W-g\left(\ket{\psi}\right)$
-where $\ket{\psi}$ is a point in the closed northern hemisphere with
-longitude~$\varphi$.
-Then, $\left|F_{\varphi}\left(a_{i}\right)-\left(W-g\left(\ket{\psi_{i}}\right)\right)\right|\le2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$
+its longitude~$\varphi$, and a function~$F\left(a\right)=W-g\left(\ket{\psi'}\right)$,
+where $\ket{\psi'}$ is a point in the closed northern hemisphere
+with longitude~$\varphi$, and $a=\ell\left(\ket{\psi'}\right)$.
+More specifically, let $\ket{\psi_{i}'}$ be a point in the closed
+northern hemisphere with longitude~$\varphi$ such that $a_{i}=\ell\left(\ket{\psi_{i}'}\right)$.
+Hence, $\ket{\psi_{i}'}$ and $\ket{\psi_{i}}$ are in the same latitude
+so that 
+\[
+\left|F\left(a_{i}\right)-\left(W-g\left(\ket{\psi_{i}}\right)\right)\right|=\left|g\left(\ket{\psi_{i}}\right)-g\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)\textrm{ .}
+\]
+for all $i$. Whence, 
+\begin{eqnarray*}
+ &  & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-W\right|\\
+ & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right|+\left|2W-\left(g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right)\right|\\
+ & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
+ & \le & 3\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+W_{r}-W_{l}\textrm{ .}
+\end{eqnarray*}
+Therefore, by Lemma~19 in \cite{RichmanBridges1999}, 
+\[
+\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|=\left|W-g\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
+\]
 \end{proof}

### 2016-11-01 prob.tex
prob.tex \section{Proofs} Change the section name back to proofs...

@@
 
-\section{Theorems}
+\section{Proofs}
 
@@
 
-\begin{definition}\cite{CourantJohn1965,Voevodskyothers2013}~For
-any function~$f$, a function~$\varDelta_{f}:\left(0,\infty\right]\rightarrow\left(0,\infty\right]$
-is a modulus of continuity of $f$ if for every $\epsilon>0$, $\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\varDelta_{f}\left(\epsilon\right)$
-implies $\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|<\epsilon$.\qed\end{definition}
-
-Notice that a function $f$ may have more than one modulus of continuity.
-For example, $\varDelta_{f}\left(\epsilon\right)=\frac{\epsilon}{2}$
-and $\epsilon$ are both modulus of continuity of $f\left(\ket{\psi}\right)=\left|\ip{\psi}{0}\right|^{2}$
-on $S^{2}$. Conversely, a function may be a modulus of continuity
-of two different functions. For example, $\varDelta\left(\epsilon\right)=\frac{\epsilon}{2}$
-is a modulus of continuity of both $f\left(\ket{\psi}\right)=\left|\ip{\psi}{0}\right|^{2}$
-and $f\left(\ket{\psi}\right)=\frac{1}{3}$ on $S^{2}$.
-
 \begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
@@
 where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{0}$.\qed\end{definition}
-
-The following theorem is an analog to Corollary~22 in \cite{RichmanBridges1999}.
-The only significant difference is that we assume the approximation
-frame function is continuous. The approximation frame function might
-not be continuous as in all of our previous example, while the frame
-function in original Gleason's theorem is always continuous. Thus,
-we need to assume the continuity to follow the proof in \cite{RichmanBridges1999}.
-
-\begin{thm}\label{thm:analogCorollary22RichmanBridges1999}Let $f$
-be an bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
-$m=\inf f$ or $m=\sup f$, and $W=\frac{W_{l}+W_{r}}{2}$. Let $Q$
-be the quadratic form given by
-\[
-Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)
-\]
-For each $\delta>0$, there is $\eta>0$ such that if
-\begin{itemize}
-\item $\left|f\left(\ket{0}\right)-m\right|<\eta$, and 
-\item $g$ is the symmetrization of $f$ with respect to $\ket{0}$.
-\end{itemize}
-then $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\varDelta_{f}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
-where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
-is the smallest integer not less than $x$.\qed\end{thm}
-
-Since $\delta$ can be arbitrary small in theorem~\ref{thm:analogCorollary22RichmanBridges1999},
-we can get the following corollary.
-
-\begin{cor}Let $f$ be a bounded continuous approximation frame function
-of weight~$\left(W_{l},W_{r}\right)$, $m=\min f=f\left(\ket{0}\right)$
-or $m=\max f=f\left(\ket{0}\right)$, and $W=\frac{W_{l}+W_{r}}{2}$.
-Let $Q$ be the quadratic form given by
-\[
-Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)
-\]
-If $g$ is the symmetrization of $f$ with respect to $\ket{0}$,
-then $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
-
-Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
-which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
-Theorem~23 reads as the following.
-
-\begin{thm}Let $f$ be a bounded frame function on the unit sphere
-in $\mathbb{R}^{3}$, and $\delta>0$. Then there is a quadratic form
-$Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le3\delta$
-for all $\ket{\psi}$ on the sphere.\qed\end{thm}
-
-Currently, we can only prove the following.
-
-%%%%%
-
-\section{Proofs}
 
@@
 \begin{itemize}
-\item Let $f$ be a continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
-and need to rewrite Lemma~19 if we want to take away this ``continuous''...}} nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+\item Let $f$ be a nonnegative continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
+and need to rewrite Lemma~19 if we want to take away this ``continuous''...}}approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
 $W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
@@
 \]
+\end{proof}
+The following theorem is an analog to Corollary~22 in \cite{RichmanBridges1999}.
+
+\begin{cor}\label{thm:analogCorollary22RichmanBridges1999}~
+\begin{itemize}
+\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+$W=\frac{W_{l}+W_{r}}{2}$, $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$,
+$\eta=f\left(\ket{0}\right)-m$, 
+\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
+\item $Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)$,
+and 
+\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\end{itemize}
+Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
+\begin{proof}
+Clearly, $f'=f-m$ is a nonnegative frame function of weight~$\left(W_{l}',W_{r}'\right)=\left(W_{l}-3m,W_{r}-3m\right)$
+and $W'=\frac{W_{l}'+W_{r}'}{2}=W-3m$. Then, $\eta=f'\left(\ket{0}\right)$
+and $g'=g-2m$ be the symmetrization of $f'$ with respect to $\ket{0}$
+. Let $Q'\left(\ket{\psi}\right)=Q\left(\ket{\psi}\right)-2m=W'\left(1-\ip{0}{\psi}^{2}\right)$,
+and we have $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g'\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
+from theorem~\ref{thm:analogTheorem21RichmanBridges1999}.
+\end{proof}
+Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
+which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
+Theorem~23 reads as the following.
+
+\begin{thm}Let $f$ be a bounded continuous approximation frame function
+of weight~$\left(W_{l},W_{r}\right)$ on $S^{2}$. Then there is
+a quadratic form $Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le?$
+for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
+\begin{proof}
+Let $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$
+and $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0'}\right)$.
+Let $\ket{2}$ and $\ket{2'}$ be the images of $\ket{\psi_{M}}$
+and $\ket{\psi_{m}}$ under $90\textdegree$ rotation of the great
+circle joining them. Then 
+\[
+\left|\left(f\left(\ket{\psi_{M}}\right)+f\left(\ket{\psi_{M}'}\right)\right)-\left(f\left(\ket{\psi_{m}}\right)+f\left(\ket{\psi_{m}'}\right)\right)\right|\le W_{r}-W_{l}
+\]
+so
+\[
+f\left(\ket{\psi_{m}'}\right)-f\left(\ket{\psi_{M}'}\right)\ge f\left(\ket{\psi_{M}}\right)-f\left(\ket{\psi_{m}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
+\]
+whence $f\left(\ket{\psi_{M}'}\right)\le m+W_{r}-W_{l}$ and $f\left(\ket{\psi_{m}'}\right)\ge M-\left(W_{r}-W_{l}\right)$.
 \end{proof}

### 2016-11-02 prob.tex
prob.tex \appendix Single out many definitions...

@@
 all mixed state~$\rho$ there is a $P\in\events$ such that $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.
-After the example, we will also justify why this example cannot fit
-with more precise intervals.
+Before the example, we need a notation of cross product.
+
+\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
+\alpha_{1}\\
+\alpha_{2}
+\end{pmatrix}$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\begin{pmatrix}\beta_{0}\\
+\beta_{1}\\
+\beta_{2}
+\end{pmatrix}$, their cross product is defined as follow: 
+\[
+\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\begin{vmatrix}\alpha_{1}^{*} & \beta_{1}^{*}\\
+\alpha_{2}^{*} & \beta_{2}^{*}
+\end{vmatrix}\ket{0}+\begin{vmatrix}\alpha_{2}^{*} & \beta_{2}^{*}\\
+\alpha_{0}^{*} & \beta_{0}^{*}
+\end{vmatrix}\ket{1}+\begin{vmatrix}\alpha_{0}^{*} & \beta_{0}^{*}\\
+\alpha_{1}^{*} & \beta_{1}^{*}
+\end{vmatrix}\ket{2}\textrm{ ,}
+\]
+where $\begin{vmatrix}\alpha & \beta\\
+\alpha' & \beta'
+\end{vmatrix}=\alpha\beta'-\alpha'\beta$. \qed\end{definition}
+
+Notice that we put the complex conjugate in the cross product, so
+that the result of cross product is orthogonal to $\ket{\psi}$ and
+$\ket{\phi}$. 
+\begin{eqnarray*}
+\ip{\psi\times\phi}{\psi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}=0\textrm{ ,}\\
+\ip{\psi\times\phi}{\phi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}=0\textrm{ .}
+\end{eqnarray*}
+Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
+cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
+as usual.
 
@@
 \]
-
-Before we verify that $\bar{\mu}$ is a quantum interval-valued probability
-measure, we need a notation of cross product. For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
-\alpha_{1}\\
-\alpha_{2}
-\end{pmatrix}$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\begin{pmatrix}\beta_{0}\\
-\beta_{1}\\
-\beta_{2}
-\end{pmatrix}$, their cross product is defined as follow:
-\[
-\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\begin{vmatrix}\alpha_{1}^{*} & \beta_{1}^{*}\\
-\alpha_{2}^{*} & \beta_{2}^{*}
-\end{vmatrix}\ket{0}+\begin{vmatrix}\alpha_{2}^{*} & \beta_{2}^{*}\\
-\alpha_{0}^{*} & \beta_{0}^{*}
-\end{vmatrix}\ket{1}+\begin{vmatrix}\alpha_{0}^{*} & \beta_{0}^{*}\\
-\alpha_{1}^{*} & \beta_{1}^{*}
-\end{vmatrix}\ket{2}\textrm{ ,}
-\]
-where $\begin{vmatrix}\alpha & \beta\\
-\alpha' & \beta'
-\end{vmatrix}=\alpha\beta'-\alpha'\beta$. Notice that we put the complex conjugate in the cross product, so
-that the result of cross product is orthogonal to $\ket{\psi}$ and
-$\ket{\phi}$. 
-\begin{eqnarray*}
-\ip{\psi\times\phi}{\psi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}=0\textrm{ ,}\\
-\ip{\psi\times\phi}{\phi} & = & \left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}=0\textrm{ .}
-\end{eqnarray*}
-Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
-cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
-as usual.
 
@@
 
+\begin{definition}Given a vector~$\ket{\psi}\in\mathbb{R}^{3}$,
+$\sigma_{\ket{\psi},\theta}$ is rotation by $\theta$ about $\ket{\psi}$.\qed\end{definition}
+
 \begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
@@
 then the \emph{symmetrization} of $f$ with respect to $\ket{0}$
-is the function~$g:S^{2}\rightarrow\mathbb{R}$ defined by
-\[
-g\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\sigma\ket{\psi}\right)
-\]
-where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{0}$.\qed\end{definition}
+is the function~$g_{f,\ket{0}}:S^{2}\rightarrow\mathbb{R}$ defined
+by
+\[
+g_{f,\ket{0}}\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\textrm{ .}
+\]
+\qed\end{definition}
 
@@
 $W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
-\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
 \item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
@@
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
+Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
 \begin{proof}
-Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g$
+Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g_{f,\ket{0}}$
 is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
-and that $W_{l}-\eta\le g\left(\ket{\psi}\right)\le W_{r}-\eta$ for
-all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
-the oscillation of $g$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.
+and that $W_{l}-\eta\le g_{f,\ket{0}}\left(\ket{\psi}\right)\le W_{r}-\eta$
+for all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
+the oscillation of $g_{f,\ket{0}}$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.
 
@@
 For any point $\ket{\psi}$ in the closed northern hemisphere, consider
-its longitude~$\varphi$, and a function~$F\left(a\right)=W-g\left(\ket{\psi'}\right)$,
+its longitude~$\varphi$, and a function~$F\left(a\right)=W-g_{f,\ket{0}}\left(\ket{\psi'}\right)$,
 where $\ket{\psi'}$ is a point in the closed northern hemisphere
@@
 \[
-\left|F\left(a_{i}\right)-\left(W-g\left(\ket{\psi_{i}}\right)\right)\right|=\left|g\left(\ket{\psi_{i}}\right)-g\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)\textrm{ .}
+\left|F\left(a_{i}\right)-\left(W-g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right)\right|=\left|g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)-g_{f,\ket{0}}\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)\textrm{ .}
 \]
@@
  &  & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-W\right|\\
- & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right|+\left|2W-\left(g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right)\right|\\
- & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
+ & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right|+\left|2W-\left(g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right)\right|\\
+ & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
  & \le & 3\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+W_{r}-W_{l}\textrm{ .}
@@
 \[
-\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|=\left|W-g\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
+\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|W-g_{f,\ket{0}}\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
 \]
@@
 $\eta=f\left(\ket{0}\right)-m$, 
-\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
 \item $Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)$,
@@
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
+Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
 \begin{proof}
@@
 and $W'=\frac{W_{l}'+W_{r}'}{2}=W-3m$. Then, $\eta=f'\left(\ket{0}\right)$
-and $g'=g-2m$ be the symmetrization of $f'$ with respect to $\ket{0}$
-. Let $Q'\left(\ket{\psi}\right)=Q\left(\ket{\psi}\right)-2m=W'\left(1-\ip{0}{\psi}^{2}\right)$,
-and we have $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g'\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
+and $g_{f',\ket{0}}=g_{f,\ket{0}}-2m$. Let $Q'\left(\ket{\psi}\right)=Q\left(\ket{\psi}\right)-2m=W'\left(1-\ip{0}{\psi}^{2}\right)$,
+and we have $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g_{f',\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
 from theorem~\ref{thm:analogTheorem21RichmanBridges1999}.
@@
 
-\begin{thm}Let $f$ be a bounded continuous approximation frame function
-of weight~$\left(W_{l},W_{r}\right)$ on $S^{2}$. Then there is
-a quadratic form $Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le?$
-for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
+\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
+\begin{itemize}
+\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+$W=\frac{W_{l}+W_{r}}{2}$, 
+\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
+$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0'}\right)$, 
+\item $\ket{2}=\sigma_{\ket{0}\times\ket{0'},\frac{\pi}{2}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
+\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
+and 
+\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\end{itemize}
+Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
 \begin{proof}
-Let $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$
-and $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0'}\right)$.
-Let $\ket{2}$ and $\ket{2'}$ be the images of $\ket{\psi_{M}}$
-and $\ket{\psi_{m}}$ under $90\textdegree$ rotation of the great
-circle joining them. Then 
-\[
-\left|\left(f\left(\ket{\psi_{M}}\right)+f\left(\ket{\psi_{M}'}\right)\right)-\left(f\left(\ket{\psi_{m}}\right)+f\left(\ket{\psi_{m}'}\right)\right)\right|\le W_{r}-W_{l}
+Let $\ket{2'}=\sigma_{\ket{0}\times\ket{0'},\frac{\pi}{2}}\ket{0'}$.
+Then 
+\[
+\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{0'}\right)+f\left(\ket{2'}\right)\right)\right|\le W_{r}-W_{l}
 \]
@@
 \[
-f\left(\ket{\psi_{m}'}\right)-f\left(\ket{\psi_{M}'}\right)\ge f\left(\ket{\psi_{M}}\right)-f\left(\ket{\psi_{m}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
-\]
-whence $f\left(\ket{\psi_{M}'}\right)\le m+W_{r}-W_{l}$ and $f\left(\ket{\psi_{m}'}\right)\ge M-\left(W_{r}-W_{l}\right)$.
+f\left(\ket{2'}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{0'}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
+\]
+whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
+denote the coordinates of a point~$\ket{\psi}$ with respect to the
+frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.
+
+Let $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
+So 
+\begin{eqnarray*}
+ &  & \left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right|\\
+ & = & \left|\left(f\left(\ket{\psi}\right)+f\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|\\
+ & = & \left|g_{f,\ket{0}}-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|
+\end{eqnarray*}
 \end{proof}

### 2016-11-02 prob.tex
prob.tex \section{Proofs} Adding footnote...

@@
 \begin{definition}Given a vector~$\ket{\psi}\in\mathbb{R}^{3}$,
-$\sigma_{\ket{\psi},\theta}$ is rotation by $\theta$ about $\ket{\psi}$.\qed\end{definition}
+$\sigma_{\ket{\psi},\theta}$ is rotation by $\theta$ about $\ket{\psi}$.\footnote{\yutsung{Write its matrix representation?}}\qed\end{definition}
 
@@
 Let $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
-So 
+So\footnote{\yutsung{Verify the details...}} 
 \begin{eqnarray*}

### 2016-11-03 prob.tex
prob.tex \section{Proofs} Skip the annoy part and move on to the next...

@@
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
+Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
 \begin{proof}
@@
 Let $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
-So\footnote{\yutsung{Verify the details...}} 
+Then, \footnote{\yutsung{Verify the details. Especially the left-handed or right-handed
+or the coordinate system, and the rotation matrix... >''<}} 
 \begin{eqnarray*}
- &  & \left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right|\\
- & = & \left|\left(f\left(\ket{\psi}\right)+f\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|\\
- & = & \left|g_{f,\ket{0}}-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|
+\sigma_{\ket{0},\frac{\pi}{2}}\left(x,y,z\right) & = & \left(x,-z,y\right)\\
+\sigma_{\ket{2},\frac{\pi}{2}}\left(x,y,z\right) & = & \left(-y,x,z\right)
 \end{eqnarray*}
+Note that 
+\begin{eqnarray*}
+Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right) & = & 2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\\
+Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{2},\frac{\pi}{2}}\ket{\psi}\right) & = & 2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)
+\end{eqnarray*}
+which is the same as the quadratic form defined in corollary~\ref{thm:analogCorollary22RichmanBridges1999}.
+Therefore, by corollary~\ref{thm:analogCorollary22RichmanBridges1999},
+we should have 
+\begin{eqnarray*}
+\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
+\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{2},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
+\end{eqnarray*}
+Follow the same procedure in the proof in \cite{RichmanBridges1999}.
+We have 
+\[
+\left|f\left(\ket{\psi}\right)-M\left(x^{2}-z^{2}\right)-Wz^{2}\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
+\]
+ on the great circle $y=z$.
 \end{proof}

### 2016-11-04 prob.tex
prob.tex \section{Proofs} Updating...

@@
 of the symmetrization of $f$ with respect to $\ket{0}$ is at most
-$\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+$\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 The exact $n$ could be computed to minimize the oscillation when
@@
 and 
-\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\item $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
+Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
 \begin{proof}
@@
 for all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
-the oscillation of $g_{f,\ket{0}}$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.
+the oscillation of $g_{f,\ket{0}}$ on latitudes is at most $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)$.
 
@@
 \[
-\left|F\left(a_{i}\right)-\left(W-g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right)\right|=\left|g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)-g_{f,\ket{0}}\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)\textrm{ .}
+\left|F\left(a_{i}\right)-\left(W-g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right)\right|=\left|g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)-g_{f,\ket{0}}\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)\textrm{ .}
 \]
@@
  & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
- & \le & 3\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+W_{r}-W_{l}\textrm{ .}
+ & \le & 3\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+W_{r}-W_{l}\textrm{ .}
 \end{eqnarray*}
@@
 \[
-\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|W-g_{f,\ket{0}}\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
+\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|W-g_{f,\ket{0}}\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
 \]
@@
 and 
-\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\item $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
+Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
 \begin{proof}
@@
 and $g_{f',\ket{0}}=g_{f,\ket{0}}-2m$. Let $Q'\left(\ket{\psi}\right)=Q\left(\ket{\psi}\right)-2m=W'\left(1-\ip{0}{\psi}^{2}\right)$,
-and we have $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g_{f',\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
+and we have $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g_{f',\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
 from theorem~\ref{thm:analogTheorem21RichmanBridges1999}.
@@
 \item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
-$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0'}\right)$, 
-\item $\ket{2}=\sigma_{\ket{0}\times\ket{0'},\frac{\pi}{2}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
+$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
+\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
+$\ket{1}=\ket{2}\times\ket{0}$, 
 \item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
 and 
-\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\item $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 \end{itemize}
@@
 \begin{proof}
-Let $\ket{2'}=\sigma_{\ket{0}\times\ket{0'},\frac{\pi}{2}}\ket{0'}$.
+Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{\bar{0}}$.
 Then 
 \[
-\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{0'}\right)+f\left(\ket{2'}\right)\right)\right|\le W_{r}-W_{l}
+\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
 \]
@@
 \[
-f\left(\ket{2'}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{0'}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
+f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
 \]
@@
 \begin{eqnarray*}
-\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
-\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{2},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
+\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
+\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{2},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
 \end{eqnarray*}
@@
 \[
-\left|f\left(\ket{\psi}\right)-M\left(x^{2}-z^{2}\right)-Wz^{2}\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
-\]
- on the great circle $y=z$.
+\left|f'\left(\ket{\psi}\right)\right|=\left|f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
+\]
+on the six great circles~$x=\pm y$, $y=\pm z$, and $z=\pm x$ on
+$S^{2}$. In particular, 
+\[
+\left|f\left(\ket{\psi}\right)-M\left(x^{2}-z^{2}\right)-Wz^{2}\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
+\]
+ on the great circle~$y=z$.
+
+Let $M'=\max_{\ket{\psi}\in S^{2}}f'\left(\ket{\psi}\right)$, $m'=\min_{\ket{\psi}\in S^{2}}f'\left(\ket{\psi}\right)$.
+Note that the weight of $f'$ is $\left(W_{l}',W_{r}'\right)=\left(W_{l}-W,W_{r}-W\right)$
+and $W'=\frac{W_{l}'+W_{r}'}{2}=0$. Choose an orthonormal basis~$\left\{ \ket{i'}\right\} _{i=0}^{2}$
+such that $f'\left(\ket{0'}\right)=M'$ and $f\left(\ket{2'}\right)\le m'+W_{r}'-W_{l}'=m'+W_{r}-W_{l}$.
+In this case, the approximating form is$Q'\left(\ket{\psi}\right)=Mx'^{2}-\left(M+m\right)y'^{2}+mz'^{2}$.
+By the previous paragraph, for $t$ on the great circle~$y'=z'$,
+we have
+\[
+\left|f'\left(\ket{\psi}\right)-M'\left(x'^{2}-z'^{2}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
+\]
+
+Notice that the great circles~$x=\pm y$, $y=\pm z$, and $z=\pm x$
+on $S^{2}$ divide the sphere into 24 triangles. The 14 vertices are
+\[
+\begin{array}{rcl}
+\left(\pm\frac{1}{\sqrt{3}},\pm\frac{1}{\sqrt{3}},\pm\frac{1}{\sqrt{3}}\right),\quad\left(\pm1,0,0\right),\quad\left(0,\pm1,0\right),\quad\left(0,0,\pm1\right).\end{array}
+\]
+All 24 triangles congruent to 
 \end{proof}

### 2016-11-04 prob.tex
prob.tex \section{Proofs} Updating...

@@
 \[
-W_{l}\le\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{d-1}}f\left(\ket{\psi_{i}}\right)\le W_{r}
+W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}
 \]
@@
 of the symmetrization of $f$ with respect to $\ket{0}$ is at most
-$\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+$\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 The exact $n$ could be computed to minimize the oscillation when
@@
 and 
-\item $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 \end{itemize}
@@
 and 
-\item $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
+Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$.\qed\end{thm}
 \begin{proof}
@@
 \[
-\left|f'\left(\ket{\psi}\right)-M'\left(x'^{2}-z'^{2}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
+\left|f'\left(\ket{\psi}\right)-M'\left(x'^{2}-z'^{2}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)
 \]
@@
 \]
-All 24 triangles congruent to 
+All 24 triangles are congruent to
+\[
+\begin{array}{rcl}
+\left(1,0,0\right),\quad\left(\frac{1}{\sqrt{3}},\frac{1}{\sqrt{3}},\frac{1}{\sqrt{3}}\right),\quad\left(\frac{1}{\sqrt{3}},-\frac{1}{\sqrt{3}},\frac{1}{\sqrt{3}}\right).\end{array}
+\]
+The maximum distance between two vertices is $\frac{2}{\sqrt{3}}$.
+So any great circle through a point in the interior of that triangle
+must intersect the boundary at a distance at most $\frac{1}{\sqrt{3}}$
+from the point.
+
+In particular, because $\ket{0'}$ is on the great circle~$y'=z'$,
+the great circle~$y'=z'$ must intersect the boundary of one of the
+previous triangles. Let $\ket{\psi}$ be the intersection, the distance
+between $\ket{0'}$ and $\ket{\psi}$ is at most $\frac{1}{\sqrt{3}}$.
+That is
+\[
+\left(1-x'\right)^{2}+2z'^{2}=\left(1-x'\right)^{2}+y'^{2}+z'^{2}\le\frac{1}{3}\textrm{ .}
+\]
+Also $x'^{2}+2z'^{2}=1$. So $2\left(1-x'\right)\le\frac{1}{3}$ or
+$x'\ge\frac{5}{6}$ so $2z'^{2}\le\frac{11}{36}$ whence $x'^{2}-z'^{2}\ge\frac{13}{24}>\frac{1}{2}$.
+Now $\left|M'\left(x'^{2}-z'^{2}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)+\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)$
+so 
+\begin{eqnarray*}
+\left|M'\right| & \le & 3\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)+3\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)\\
+ & = & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
+\end{eqnarray*}
+Same for $m'$, so
+\begin{eqnarray*}
+\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right| & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
+\end{eqnarray*}
 \end{proof}

### 2016-11-05 prob.tex
prob.tex \section{Proofs} A loophole which cannot be fixed easily...

@@
 \begin{definition}Given a vector~$\ket{\psi}\in\mathbb{R}^{3}$,
-$\sigma_{\ket{\psi},\theta}$ is rotation by $\theta$ about $\ket{\psi}$.\footnote{\yutsung{Write its matrix representation?}}\qed\end{definition}
+$\sigma_{\ket{\psi},\theta}$ is the clockwise rotation by $\theta$
+about $\ket{\psi}$.\footnote{\yutsung{Write its matrix representation?}}\qed\end{definition}
 
@@
 
+\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
+north pole, then $\theta\left(\ket{\psi}\right)$ denotes the the
+latitude of $\ket{\psi}$.\qed\end{definition}
+
 The following theorem is an analog to Lemma~20 in \cite{RichmanBridges1999}.
@@
 is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
-and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
+and $\eta=f\left(\ket{0}\right)$, then the oscillation on the latitude~$\theta$
 of the symmetrization of $f$ with respect to $\ket{0}$ is at most
-$\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+$\min_{n\ge\max\left\{ 2\pi,\frac{\pi^{2}}{\theta}\right\} }2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 The exact $n$ could be computed to minimize the oscillation when
@@
 Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
-the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$.
-Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
-with the same latitude~$\theta$. Let $a$ be the difference in longitudes
-of $\ket{\psi}$ and $\ket{\psi'}$. Take $n$ steps along east-west
-great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
+the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$\footnote{\yutsung{Notice that \cite{RichmanBridges1999} derives the modulus
+of continuity~$\omega_{f}\left(\delta\right)$ in their Corollary~18(?).
+Maybe need to upgrade and derive the modulus of continuity in our
+case later.}}. Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
+with $\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
+Let $a$ be the difference in longitudes of $\ket{\psi}$ and $\ket{\psi'}$.
+Take $n\ge\frac{a^{2}}{\theta\left(\ket{\psi}\right)}$ steps along
+east-west great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
 due south of $\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
-to a point $\ket{\psi_{s}}$.}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
+to a point $\ket{\psi_{s}}$, and the details in the original proof...}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
 is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{\yutsung{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be

### 2016-11-07 prob.tex
prob.tex \section{Proofs} Specify the current problem...

@@
 \newtheorem{conjecture}{Conjecture}
+\newtheorem{problem}{Problem}
 \newcommand{\events}{\ensuremath{\mathcal{E}}}
@@
 
-\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
-north pole, then $\theta\left(\ket{\psi}\right)$ denotes the the
-latitude of $\ket{\psi}$.\qed\end{definition}
+\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,RichmanBridges1999,Hamhalter2013}~Given
+a vector~$\ket{\psi}\in S^{2}$ with a specified north pole~$\ket{0}\in S^{2}$,
+then 
+\begin{itemize}
+\item $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$ denotes the the
+latitude of $\ket{\psi}$.
+\item $N_{\ket{0}}$ denotes the northern hemisphere.
+\item The great circle on $S^{2}$ is the intersection of $S^{2}$ with
+a plane containing the center of $S^{2}$.
+\item If $0<\theta\left(\ket{\psi}\right)<\frac{\pi}{2}$, there is a unique
+great circle tangent to the circle of latitude through $\ket{\psi}$;
+we shall call it East-West great circle through $\ket{\psi}$, and
+denoted by $C\left(\ket{\psi}\right)$.
+\end{itemize}
+\qed\end{definition}
+
+\begin{conjecture}\cite{Hamhalter2013}~Let $\ket{\psi}$ and $\ket{\psi'}$
+be points in $N_{\ket{0}}$ with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
+Then there exist a finite number~$n$ steps along east-west great
+circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due
+south of $\ket{\psi}$.
+
+The problem is whether number~$n$ could be picked uniformly? Or
+there is a number~$n$ satisfying the given conditions for all latitude?
+
+Notice that the proof in \cite{RichmanBridges1999} doesn't require
+the number~$n$ to be picked uniformly because we could always pick
+$f\left(p\right)=0$ in Lemma~20 in \cite{RichmanBridges1999}. However,
+in the corresponding lemma~\ref{lemma:analogLemma20RichmanBridges1999},
+we need to deal with the case where $\eta$ doesn't approach $0$
+because the maximum and minimum value may not be orthogonal in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.\qed\end{conjecture}
 
@@
 Maybe need to upgrade and derive the modulus of continuity in our
-case later.}}. Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
+case later.}}. Let $\ket{\psi}$ and $\ket{\psi'}$ be points in $N_{\ket{0}}$
 with $\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
@@
 Take $n\ge\frac{a^{2}}{\theta\left(\ket{\psi}\right)}$ steps along
-east-west great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
+East-West great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
 due south of $\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$

### 2016-11-07 prob.tex
From: Tai, Yu-Tsung Sent: Monday, November 07, 2016 13:33 To: Sabry, Amr A. <sabry@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu> Subject: RE: Born rule, Bayesianism, law of total probability
Dear all,

The attachment is the current version… If we could prove geometric
conjecture 2, then we could have something like theorem 7, although
there are still some details need to fill-in and theorem 7 is still not
about IVPM, yet…

Haven’t know whether conjecture 2 is true or false so far… If it is
false, the theorems would be much uglier than the current on

--- 2016-11-05 prob.tex
@@
 
-\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
-north pole, then $\theta\left(\ket{\psi}\right)$ denotes the the
-latitude of $\ket{\psi}$.\qed\end{definition}
+\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,RichmanBridges1999,Hamhalter2013}~Given
+a vector~$\ket{\psi}\in S^{2}$ with a specified north pole~$\ket{0}\in S^{2}$,
+then 
+\begin{itemize}
+\item $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$ denotes the the
+latitude of $\ket{\psi}$.
+\item The great circle on $S^{2}$ is the intersection of $S^{2}$ with
+a plane containing the center of $S^{2}$.
+\item If $0<\theta\left(\ket{\psi}\right)<\frac{\pi}{2}$, there is a unique
+great circle tangent to the circle of latitude through $\ket{\psi}$;
+we shall call it East-West great circle through $\ket{\psi}$, and
+denoted by $C\left(\ket{\psi}\right)$.
+\end{itemize}
+\qed\end{definition}
+
+\yutsung{\begin{lemma}\label{lemma:geometricInterludeRichmanBridges1999}\cite{RichmanBridges1999}~Let
+$\ket{\psi}$ and $\ket{\psi'}$ be points in $N_{\ket{0}}$ with
+the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
+Then there exist a finite number~$n\ge\frac{a^{2}}{\theta\left(\ket{\psi}\right)}$
+steps along east-west great circles to go from $\ket{\psi'}$ to a
+point $\ket{\psi_{s}}$ due south of $\ket{\psi}$.\footnote{Verify the details more precisely...}\qed\end{lemma}
+
+Lemma~\ref{lemma:geometricInterludeRichmanBridges1999} is used to
+prove lemma~20 in \cite{RichmanBridges1999}. However, its too week
+to prove lemma~\ref{lemma:analogLemma20RichmanBridges1999} which
+is the analog to lemma~20 in \cite{RichmanBridges1999}. This difference
+is because we could always pick $f\left(p\right)=0$ in lemma~20
+in \cite{RichmanBridges1999}, while we need to deal with the case
+where $\eta$ doesn't approach $0$ in lemma~\ref{lemma:analogLemma20RichmanBridges1999}
+since the maximum and minimum value of a frame function may not occur
+on orthogonal vectors in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.
+In order to prove lemma~\ref{lemma:analogLemma20RichmanBridges1999},
+we need the following geometric conjecture.
+
+\begin{conjecture}\label{conj:analogGeometricInterludeRichmanBridges1999}There
+exist a nonempty set~$\mathcal{N}\subseteq\mathbb{N}\cap\left[2\pi,\infty\right)$
+such that for all $n\in\mathcal{N}$, if $\ket{\psi}$ and $\ket{\psi'}$
+are points in the northern hemisphere with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$,
+then we could takes $n$ steps along east-west great circles to go
+from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due south of $\ket{\psi}$.\footnote{Verify the details more precisely...}\qed\end{conjecture}
+
+I don't know whether conjecture~\ref{conj:analogGeometricInterludeRichmanBridges1999}
+is valid or not. However, if it is not valid, we need to require that
+the maximum and minimum value of a frame function occur on orthogonal
+vectors in theorem~\ref{thm:analogTheorem23RichmanBridges1999} twice.
+}
 
@@
 is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
-and $\eta=f\left(\ket{0}\right)$, then the oscillation on the latitude~$\theta$
+and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
 of the symmetrization of $f$ with respect to $\ket{0}$ is at most
-$\min_{n\ge\max\left\{ 2\pi,\frac{\pi^{2}}{\theta}\right\} }2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+$\min_{n\in\mathcal{N}}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 The exact $n$ could be computed to minimize the oscillation when
@@
 Let $a$ be the difference in longitudes of $\ket{\psi}$ and $\ket{\psi'}$.
-Take $n\ge\frac{a^{2}}{\theta\left(\ket{\psi}\right)}$ steps along
-east-west great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
-due south of $\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
+By conjecture~\ref{conj:analogGeometricInterludeRichmanBridges1999},
+we can take $n\in\mathcal{N}$ steps along East-West great circles
+to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due south of
+$\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
 to a point $\ket{\psi_{s}}$, and the details in the original proof...}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
@@
 and 
-\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\min_{n\in\mathcal{N}}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
 \end{itemize}
@@
 Then, \footnote{\yutsung{Verify the details. Especially the left-handed or right-handed
-or the coordinate system, and the rotation matrix... >''<}} 
+of the coordinate system, and the rotation matrix... >''<}} 
 \begin{eqnarray*}

### 2016-11-09 prob.tex
prob.tex \section{Proofs} Conjecture is false. So... How to fix it?

@@
 great circle tangent to the circle of latitude through $\ket{\psi}$;
-we shall call it East-West great circle through $\ket{\psi}$, and
+we shall call it a East-West great circle through $\ket{\psi}$, and
 denoted by $C\left(\ket{\psi}\right)$.
+\item A point~$\ket{\psi'}$ in a East-West great circle~$C\left(\ket{\psi}\right)$
+is \emph{close to} $\ket{\psi}$ if 
+\[
+\cos\theta\left(\ket{\psi'}\right)=\ip{0}{\psi'}\le2\ip{0}{\psi}=2\cos\theta\left(\ket{\psi}\right)\textrm{ .}
+\]
 \end{itemize}
@@
 \yutsung{\begin{lemma}\label{lemma:geometricInterludeRichmanBridges1999}\cite{RichmanBridges1999}~Let
-$\ket{\psi}$ and $\ket{\psi'}$ be points in $N_{\ket{0}}$ with
-the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
-Then there exist a finite number~$n\ge\frac{a^{2}}{\theta\left(\ket{\psi}\right)}$
-steps along east-west great circles to go from $\ket{\psi'}$ to a
-point $\ket{\psi_{s}}$ due south of $\ket{\psi}$.\footnote{Verify the details more precisely...}\qed\end{lemma}
+$\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
+with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
+Then, we can take a finite number~$n$ close steps along East-West
+great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
+due south of $\ket{\psi}$.\qed\end{lemma}
 
@@
 are points in the northern hemisphere with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$,
-then we could takes $n$ steps along east-west great circles to go
-from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due south of $\ket{\psi}$.\footnote{Verify the details more precisely...}\qed\end{conjecture}
+then we could takes $n$ close steps along east-west great circles
+to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due south of
+$\ket{\psi}$.\qed\end{conjecture}
 

### 2016-11-09 prob.tex
prob.tex \section{Proofs} Fix the lemma(?)

@@
 
-\yutsung{\begin{lemma}\label{lemma:geometricInterludeRichmanBridges1999}\cite{RichmanBridges1999}~Let
-$\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
-with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
-Then, we can take a finite number~$n$ close steps along East-West
-great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
-due south of $\ket{\psi}$.\qed\end{lemma}
-
-Lemma~\ref{lemma:geometricInterludeRichmanBridges1999} is used to
-prove lemma~20 in \cite{RichmanBridges1999}. However, its too week
-to prove lemma~\ref{lemma:analogLemma20RichmanBridges1999} which
-is the analog to lemma~20 in \cite{RichmanBridges1999}. This difference
-is because we could always pick $f\left(p\right)=0$ in lemma~20
-in \cite{RichmanBridges1999}, while we need to deal with the case
-where $\eta$ doesn't approach $0$ in lemma~\ref{lemma:analogLemma20RichmanBridges1999}
-since the maximum and minimum value of a frame function may not occur
-on orthogonal vectors in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.
-In order to prove lemma~\ref{lemma:analogLemma20RichmanBridges1999},
-we need the following geometric conjecture.
-
-\begin{conjecture}\label{conj:analogGeometricInterludeRichmanBridges1999}There
-exist a nonempty set~$\mathcal{N}\subseteq\mathbb{N}\cap\left[2\pi,\infty\right)$
-such that for all $n\in\mathcal{N}$, if $\ket{\psi}$ and $\ket{\psi'}$
-are points in the northern hemisphere with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$,
-then we could takes $n$ close steps along east-west great circles
-to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due south of
-$\ket{\psi}$.\qed\end{conjecture}
-
-I don't know whether conjecture~\ref{conj:analogGeometricInterludeRichmanBridges1999}
-is valid or not. However, if it is not valid, we need to require that
-the maximum and minimum value of a frame function occur on orthogonal
-vectors in theorem~\ref{thm:analogTheorem23RichmanBridges1999} twice.
-}
-
+\begin{lemma}\label{lemma:analogGeometricInterludeRichmanBridges1999}Let
+\[
+n\left(\theta\right)=\begin{cases}
+7 & \textrm{, if }\cos\theta\le\frac{1}{32}\textrm{ ;}\\
+k+2 & \textrm{, if }\frac{1}{2^{k-1}}<\cos\theta\le\frac{1}{2^{k}}\textrm{ for }k\ge6\textrm{ .}
+\end{cases}
+\]
+If $\ket{\psi}$ and $\ket{\psi'}$ are points in the northern hemisphere
+with the same latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$,
+and the difference of their longitude is $a$, then we could takes
+at least $n\left(\theta\left(\ket{\psi}\right)\right)$ close steps
+along East-West great circles to go from $\ket{\psi'}$ to a point
+$\ket{\psi_{s}}$ due south of $\ket{\psi}$. When taking $n\ge n\left(\theta\left(\ket{\psi}\right)\right)$
+steps, the latitude will go down by at most $\frac{a^{2}}{n}$.\qed\end{lemma}
+\begin{proof}
+...........................
+\end{proof}
 The following theorem is an analog to Lemma~20 in \cite{RichmanBridges1999}.
@@
 of the symmetrization of $f$ with respect to $\ket{0}$ is at most
-$\min_{n\in\mathcal{N}}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\[
+\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} \textrm{ .}
+\]
 The exact $n$ could be computed to minimize the oscillation when
@@
 with $\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
+Because the maximum distance between points in latitude~$\theta\left(\ket{\psi}\right)$
+is $2\cos\theta\left(\ket{\psi}\right)$, then 
+\[
+\left|g\left(\ket{\psi}\right)-g\left(\ket{\psi'}\right)\right|\le\omega_{g}\left(2\cos\theta\left(\ket{\psi}\right)\right)=2\omega_{f}\left(2\cos\theta\left(\ket{\psi}\right)\right)\textrm{ .}
+\]
 Let $a$ be the difference in longitudes of $\ket{\psi}$ and $\ket{\psi'}$.
-By conjecture~\ref{conj:analogGeometricInterludeRichmanBridges1999},
-we can take $n\in\mathcal{N}$ steps along East-West great circles
-to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due south of
-$\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
-to a point $\ket{\psi_{s}}$, and the details in the original proof...}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
-is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{\yutsung{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be
+By lemma~\ref{lemma:analogGeometricInterludeRichmanBridges1999},
+we can take $n\ge n\left(\theta\left(\ket{\psi}\right)\right)$ close
+steps along East-West great circles to go from $\ket{\psi'}$ to a
+point $\ket{\psi_{s}}$ due south of $\ket{\psi}$. The difference
+in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$ is at most
+$\frac{a^{2}}{n}$, while, from Lemma \footnote{\yutsung{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be
 typed...}},
@@
 \[
-g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
-\]
-for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
+g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\textrm{ .}
+\]
+\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
 Since $f$ is continuous in this case, we could solve $n\ge2\pi$
@@
 and 
-\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\min_{n\in\mathcal{N}}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
 \end{itemize}

### 2016-11-12 prob.tex
prob.tex \section{Proofs} update a little bit...
prob.tex \section{Proofs} Update the definitions...

@@
 \begin{definition}\cite{Hatcher2001}~The unit sphere in $\mathbb{R}^{d}$
-is denoted by $S^{d-1}$.\qed\end{definition}
+is denoted by $S^{d-1}=\left\{ \ket{\psi}\in\mathbb{R}^{d}\middle|\ip{\psi}{\psi}=1\right\} $.\qed\end{definition}
 
 \begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
-called an \emph{approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
+called a \emph{real approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
 if
-\[
-W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}
-\]
+\begin{itemize}
+\item $W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}$
 for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
-of $\mathbb{R}^{d}$.\qed\end{definition}
+of $\mathbb{R}^{d}$.
+\item For any $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $ and $\ket{\psi}\in S^{d-1}$,
+$f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$.
+\end{itemize}
+\qed\end{definition}
 
@@
 denoted by $C\left(\ket{\psi}\right)$.
-\item A point~$\ket{\psi'}$ in a East-West great circle~$C\left(\ket{\psi}\right)$
-is \emph{close to} $\ket{\psi}$ if 
+\item We say taking a small step along an East-West great circle to go from
+$\ket{\psi}$ to a point $\ket{\psi'}$ if $\ket{\psi'}\in C\left(\ket{\psi}\right)$
+and 
 \[

### 2016-11-13 prob.tex
prob.tex \section{Proofs} Fix a defintion...

@@
 
-\begin{definition}\cite{Hatcher2001}~The unit sphere in $\mathbb{R}^{d}$
-is denoted by $S^{d-1}=\left\{ \ket{\psi}\in\mathbb{R}^{d}\middle|\ip{\psi}{\psi}=1\right\} $.\qed\end{definition}
+\begin{definition}\cite{Hatcher2001,dryden2005}~The unit sphere
+in $\mathbb{R}^{d}$ is denoted by $S^{d-1}=\left\{ \ket{\psi}\in\mathbb{R}^{d}\middle|\ip{\psi}{\psi}=1\right\} $,
+while the unit sphere in $\mathbb{C}^{d}$ is denoted by $\mathbb{C}S^{d-1}=\left\{ \ket{\psi}\in\mathbb{C}^{d}\middle|\ip{\psi}{\psi}=1\right\} $.
+Since $\mathbb{C}$ is one-to-one correspondence to $\mathbb{R}^{2}$~\cite{GAMELIN2003},
+$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. Here,
+we use different symbol because they are embedded in different spaces.\qed\end{definition}
 

### 2016-11-13 prob.tex
prob.tex \section{Proofs} Updated...

@@
 Since $\mathbb{C}$ is one-to-one correspondence to $\mathbb{R}^{2}$~\cite{GAMELIN2003},
-$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. Here,
-we use different symbol because they are embedded in different spaces.\qed\end{definition}
-
-\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
-called a \emph{real approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
+$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. However,
+different symbols emphasis that they are embedded in different spaces.\qed\end{definition}
+
+\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ or
+$f:\mathbb{C}S^{d-1}\rightarrow\mathbb{R}$ is called a \emph{real}
+or \emph{complex approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
 if
@@
 for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
-of $\mathbb{R}^{d}$.
-\item For any $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $ and $\ket{\psi}\in S^{d-1}$,
-$f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$.
+of $\mathbb{R}^{d}$ or $\mathbb{C}^{d}$.
+\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
+$\ket{\psi}\in S^{d-1}$ and $\lambda\in\mathbb{R}\setminus\left\{ 0\right\} $
+or $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $.
 \end{itemize}
@@
 \item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
 and 
-\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
+\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
 \end{itemize}
@@
 
-Let $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
 Then, \footnote{\yutsung{Verify the details. Especially the left-handed or right-handed

### 2016-11-13 prob.tex
prob.tex \section{Proofs} Update definition...

@@
 \end{itemize}
-\qed\end{definition}
+Also, we will use the same letter $f$ to denote the function defined
+on nonzero vector~$\ket{\psi}$ by $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
+and its unique extension to the whole space~\cite{RichmanBridges1999}.\qed\end{definition}
 
@@
 
-\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
-is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f:S^{2}\rightarrow\left[0,\infty\right)$
+is an approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
 and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
@@
 \begin{itemize}
-\item Let $f$ be a nonnegative continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
+\item Let $f:S^{2}\rightarrow\left[0,\infty\right)$ be a continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
 and need to rewrite Lemma~19 if we want to take away this ``continuous''...}}approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
@@
 \begin{itemize}
-\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
-$W=\frac{W_{l}+W_{r}}{2}$, $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$,
-$\eta=f\left(\ket{0}\right)-m$, 
+\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
+frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$,
+$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$, $\eta=f\left(\ket{0}\right)-m$, 
 \item $Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)$,
@@
 \begin{itemize}
-\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
-$W=\frac{W_{l}+W_{r}}{2}$, 
+\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
+frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$, 
 \item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
@@
 \end{proof}
+\begin{lemma}\label{lemma:analogLemma3.3Gleason1957}~
+\begin{itemize}
+\item Let $f:\mathbb{C}S^{1}\rightarrow\mathbb{R}$ be a bounded continuous
+approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+$W=\frac{W_{l}+W_{r}}{2}$, 
+\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
+$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
+\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
+$\ket{1}=\ket{2}\times\ket{0}$, 
+\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
+and 
+\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
+\end{itemize}
+Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$.\qed\end{lemma}
 

### 2016-11-13 prob.tex
prob.tex \section{Proofs} lemma:analogLemma3.3Gleason1957 Proved...

@@
 Also, we will use the same letter $f$ to denote the function defined
-on nonzero vector~$\ket{\psi}$ by $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
-and its unique extension to the whole space~\cite{RichmanBridges1999}.\qed\end{definition}
+on nonzero vector~$\ket{\psi}$ by $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$and
+$f\left(0\right)=0$~\cite{RichmanBridges1999}.\qed\end{definition}
 
@@
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
+Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
+for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
 \begin{proof}
@@
  &  & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-W\right|\\
- & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right|+\left|2W-\left(g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right)\right|\\
+ & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right|\\
+ &  & +\left|2W-\left(g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right)\right|\\
  & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
@@
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
+Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
+for all $\ket{\psi}\in S^{2}$.\qed\end{cor}
 \begin{proof}
@@
 \end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$.\qed\end{thm}
+Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
+for all $\ket{\psi}\in S^{2}$..\qed\end{thm}
 \begin{proof}
@@
 approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
-$W=\frac{W_{l}+W_{r}}{2}$, 
-\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
-$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
-\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
-$\ket{1}=\ket{2}\times\ket{0}$, 
-\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
-\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
+$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
+to the whole space by $f\left(0\right)=0$ and $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
+for nonzero vector~$\ket{\psi}$.
+\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
+\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
+\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
+\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
+\item For any $\ket{1'}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$,
+we have $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
+for all $\ket{\psi}\in\mathbb{C}S^{1}$ such that $\ip{0}{\psi},\ip{1'}{\psi}\in\mathbb{R}$.
+\end{itemize}
+Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
+for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{lemma}
+\begin{proof}
+For all $\ket{\psi}\in\mathbb{C}S^{1}$, 
+\begin{eqnarray*}
+ &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
+ & = & \left|Q\left(\ket{\psi}\right)-f\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right|\\
+ & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right)\right|\\
+ & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\left|\ip{1}{\psi}\right|\right)\right|\\
+ & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
+\end{eqnarray*}
+where the last inequality holds because $\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\in\mathbb{C}S^{1}$
+is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
 and 
-\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
-\end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$.\qed\end{lemma}
+\[
+\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
+\]
+\end{proof}
 

### 2016-11-14 prob.tex
prob.tex \section{Proofs} Fix the definition...

@@
 \item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
-$\ket{\psi}\in S^{d-1}$ and $\lambda\in\mathbb{R}\setminus\left\{ 0\right\} $
-or $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $.
+$\ket{\psi}\in S^{d-1}$ or $\ket{\psi}\in\mathbb{C}S^{d-1}$ and
+$\lambda\in S^{0}$ or $\lambda\in\mathbb{C}S^{0}$.
 \end{itemize}
@@
 on nonzero vector~$\ket{\psi}$ by $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$and
-$f\left(0\right)=0$~\cite{RichmanBridges1999}.\qed\end{definition}
+$f\left(0\right)=0$~\cite{RichmanBridges1999}. In this case, 
+\begin{itemize}
+\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
+$\ket{\psi}\in\mathbb{R}^{d}$ or $\ket{\psi}\in\mathbb{C}^{d}$ and
+$\lambda\in\mathbb{R}\setminus\left\{ 0\right\} $ or $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $.
+\end{itemize}
+\qed\end{definition}
 

### 2016-11-15 prob.tex
prob.tex \section{Proofs} Add a definition~~

@@
 \newcommand{\proj}[1]{\op{#1}{#1}}
+\usepackage{mnsymbol}
+\newcommand{\HermitianForm}[2]{\ensuremath{\left\llangle{#1}\middle\vert{#2}\right\rrangle}}
 
@@
 \end{proof}
+\begin{definition}\cite{gleason1957,RichmanBridges1999,Jaeger2007}~On
+any complex vector space~$\mathbb{C}^{d}$, a (positive-definite)
+Hermitian form~$\HermitianForm{.}{.}:\mathbb{C}^{d}\times\mathbb{C}^{d}\rightarrow\mathbb{C}$
+is a function satisfying:
+\begin{itemize}
+\item $\HermitianForm{\phi}{\alpha_{0}\psi_{0}+\alpha_{1}\psi_{1}}=\alpha_{0}\HermitianForm{\phi}{\psi_{0}}+\alpha_{1}\HermitianForm{\phi}{\psi_{1}}$,
+where $\alpha_{0}$ and $\alpha_{1}\in\mathbb{C}$; $\ket{\phi}$,
+$\ket{\psi_{0}}$, and $\ket{\psi_{1}}\in\mathbb{C}^{d}$\footnote{Notice that in the mathematical literature~\cite{RichmanBridges1999},
+a Hermitian form is usually defined to be linear in the first complement,
+and conjugate linear in the second complement.}.
+\item $\HermitianForm{\phi}{\psi}=\HermitianForm{\psi}{\phi}^{*}$ for all
+$\ket{\phi}$ and $\ket{\psi}\in\mathbb{C}^{d}$.
+\item $\HermitianForm{\phi}{\phi}>0$ for all $\ket{\phi}\in\mathbb{C}^{d}\backslash\left\{ 0\right\} $.
+\end{itemize}
+\qed\end{definition}
 

### 2016-11-15 prob.tex
prob.tex \section{Proofs} Keep typing...

@@
 \newtheorem{problem}{Problem}
+\newtheorem{claim}{Claim}
 \newcommand{\events}{\ensuremath{\mathcal{E}}}
@@
 
+\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
+\begin{itemize}
+\item Let $f:\mathbb{C}S^{2}\rightarrow\mathbb{R}$ be a bounded continuous
+approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
+$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
+to the whole space~$\mathbb{C}^{3}$ by $f\left(0\right)=0$ and
+$f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
+for nonzero vector~$\ket{\psi}$.
+\end{itemize}
+Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
+for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}
+\begin{proof}
+This proof will be separated into two parts. The first part will estimate
+the error between the approximation frame function and the quadratic
+form on every complex two-space. The second part will then verify
+the quadratic forms in the first part could be connected and get a
+quadratic form on the whole space.
+
+\begin{claim}For any pair of vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
+\begin{itemize}
+\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
+$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
+\[
+\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
+\]
+\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
+\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
+\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
+\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
+\end{itemize}
+Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
+for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
+\begin{proof}
+For all $\ket{\psi}\in\mathbb{C}S^{1}$, 
+\begin{eqnarray*}
+ &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
+ & = & \left|Q\left(\ket{\psi}\right)-f\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right|\\
+ & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right)\right|\\
+ & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\left|\ip{1}{\psi}\right|\right)\right|\\
+ & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
+\end{eqnarray*}
+where the last inequality holds because $\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\in\mathbb{C}S^{1}$
+is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
+and 
+\[
+\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
+\]
+\end{proof}
+\end{proof}
+
 \end{document}

### 2016-11-16 prob.tex
prob.tex \section{Proofs} Typing random conjecture, and think how to glue them together...

@@
 Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
-for all $\ket{\psi}\in S^{2}$..\qed\end{thm}
+for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
 \begin{proof}
@@
 
+\yutsung{
+
 \begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
@@
 \begin{proof}
+~
+
+\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}}$,
+$\ket{\psi_{1}}$, and $\ket{\psi_{2}}\in\mathbb{C}S^{2}$. Consider
+the real vector space spanned by them, and $S^{1}$ be its unit sphere,
+i.e., 
+\[
+\left\{ \sum_{i=0}^{2}a_{i}\ket{\psi_{i}}\middle|a_{i}\in\mathbb{R}\textrm{ and }\sideset{_{\mathbb{R}}}{_{i=0}^{2}}\sum\left|\alpha_{i}\right|^{2}=1\right\} \textrm{ .}
+\]
+
+\begin{itemize}
+\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
+$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
+\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
+$\ket{1}=\ket{2}\times\ket{0}$, 
+\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
+and 
+\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
+\end{itemize}
+Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
+for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
+\begin{proof}
+Direct from theorem~\ref{thm:analogTheorem23RichmanBridges1999}.
+\end{proof}
+\begin{claim}~
+\begin{itemize}
+\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
+$m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
+\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
+$\ket{1}=\ket{2}\times\ket{0}$, 
+\item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,
+\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
+and 
+\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
+\end{itemize}
+Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
+for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
+\begin{proof}
+...................?
+
 This proof will be separated into two parts. The first part will estimate
@@
 quadratic form on the whole space.
-
-\begin{claim}For any pair of vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
+\end{proof}
+\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
 \begin{itemize}
@@
 \]
+\item $\ket{\psi_{2}}=\ket{\psi_{0}}\times\ket{\psi_{1}}\in\mathbb{C}S^{2}$.
 \item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
@@
 \begin{proof}
-For all $\ket{\psi}\in\mathbb{C}S^{1}$, 
+For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
 \begin{eqnarray*}
@@
 \end{proof}
+}
 

### 2016-11-17 prob.tex
prob.tex \section{Proofs} Add a comment... Harder than I think...
prob.tex \section{Proofs} Keep updating...

@@
 \item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
-\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
+\item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M\right)\proj{1}\right]\ket{\psi}$.
 \item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
@@
 we have $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
-for all $\ket{\psi}\in\mathbb{C}S^{1}$ such that $\ip{0}{\psi},\ip{1'}{\psi}\in\mathbb{R}$.
+for all $\ket{\psi}\in\mathbb{C}S^{1}$ such that $\ip{0}{\psi},\ip{1'}{\psi}\in\mathbb{R}$.\footnote{\yutsung{This lemma cannot fit with theorem~\ref{thm:analogTheorem23RichmanBridges1999}
+because the quadratic form required there may not be the quadratic
+form we used here... Or we should estimate the difference between
+two quadratic forms?}}
 \end{itemize}
@@
 \begin{proof}
-...................?
+For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
+\begin{eqnarray*}
+ &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
+ & = & \left|Q\left(\ket{\psi}\right)-f\left(\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
+ & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
+ & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\sum_{i=1}^{2}\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\left|\ip{i}{\psi}\right|\right)\right|
+\end{eqnarray*}
+In order to estimate the last equation, we need to verify the conditions
+listed in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.
+
+First, $\ket{0}$, $\ket{1'}=\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}$,
+and $\ket{2'}=\ket{2}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{2}{\psi}}{\left|\ip{2}{\psi}\right|}$
+form an orthonormal basis, and the restriction of $f$ on the real
+vector space spanned by $\ket{0}$, $\ket{1'}$, and $\ket{2'}$ is
+still a approximation frame function of weight~$\left(W_{l},W_{r}\right)$.
+Because $f\left(\ket{0}\right)=M$, we must also have $f\left(\ket{0}\right)=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$.
+
+where the last inequality holds because $\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\in\mathbb{C}S^{1}$
+is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
+and 
+\[
+\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
+\]
 
@@
 for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
-\begin{proof}
-For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
-\begin{eqnarray*}
- &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
- & = & \left|Q\left(\ket{\psi}\right)-f\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right|\\
- & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right)\right|\\
- & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\left|\ip{1}{\psi}\right|\right)\right|\\
- & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
-\end{eqnarray*}
-where the last inequality holds because $\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\in\mathbb{C}S^{1}$
-is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
-and 
-\[
-\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
-\]
-\end{proof}
 \end{proof}

### 2016-11-17 prob.tex
prob.tex \section{Proofs} Global replace rotation by cross product...

@@
 
-\begin{definition}Given a vector~$\ket{\psi}\in\mathbb{R}^{3}$,
-$\sigma_{\ket{\psi},\theta}$ is the clockwise rotation by $\theta$
-about $\ket{\psi}$.\footnote{\yutsung{Write its matrix representation?}}\qed\end{definition}
-
 \begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
@@
 \[
-g_{f,\ket{0}}\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\textrm{ .}
-\]
-\qed\end{definition}
+g_{f,\ket{0}}\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\ket{0}\times\ket{\psi}\right)\textrm{ .}
+\]
+Notice that $\ket{0}\times\ket{\psi}$ is the vector~$\ket{\psi}$
+clockwise-rotated by $\frac{\pi}{2}$ about $\ket{0}$.\qed\end{definition}
 
@@
 $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
-\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
-$\ket{1}=\ket{2}\times\ket{0}$, 
+\item $\ket{2}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
 \item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
@@
 \begin{proof}
-Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{\bar{0}}$.
+Let $\ket{\bar{2}}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{\bar{0}}$.
 Then 
@@
 \begin{eqnarray*}
-\sigma_{\ket{0},\frac{\pi}{2}}\left(x,y,z\right) & = & \left(x,-z,y\right)\\
-\sigma_{\ket{2},\frac{\pi}{2}}\left(x,y,z\right) & = & \left(-y,x,z\right)
+\ket{0}\times\left(x,y,z\right) & = & \left(x,-z,y\right)\\
+\ket{2}\times\left(x,y,z\right) & = & \left(-y,x,z\right)
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right) & = & 2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\\
-Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{2},\frac{\pi}{2}}\ket{\psi}\right) & = & 2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)
+Q\left(\ket{\psi}\right)+Q\left(\ket{0}\times\ket{\psi}\right) & = & 2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\\
+Q\left(\ket{\psi}\right)+Q\left(\ket{2}\times\ket{\psi}\right) & = & 2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
-\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{2},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
+\left|f'\left(\ket{\psi}\right)+f'\left(\ket{0}\times\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
+\left|f'\left(\ket{\psi}\right)+f'\left(\ket{2}\times\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
 \end{eqnarray*}
@@
 $m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
-\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
-$\ket{1}=\ket{2}\times\ket{0}$, 
+\item $\ket{2}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
 \item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,

### 2016-11-17 prob.tex
prob.tex \section{Proofs} Reorganize the scratch to print a hard copy for more scratch...

@@
 
-\yutsung{
-
-\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
+\yutsung{\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
 \begin{itemize}
@@
 Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
-for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}
+for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}}
+
+\yutsung{
 \begin{proof}
@@
 
-\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}}$,
-$\ket{\psi_{1}}$, and $\ket{\psi_{2}}\in\mathbb{C}S^{2}$. Consider
-the real vector space spanned by them, and $S^{1}$ be its unit sphere,
-i.e., 
-\[
-\left\{ \sum_{i=0}^{2}a_{i}\ket{\psi_{i}}\middle|a_{i}\in\mathbb{R}\textrm{ and }\sideset{_{\mathbb{R}}}{_{i=0}^{2}}\sum\left|\alpha_{i}\right|^{2}=1\right\} \textrm{ .}
-\]
-
-\begin{itemize}
-\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
-$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
-\item $\ket{2}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
-\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
-\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
-and 
-\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
-\end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
-for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
-\begin{proof}
-Direct from theorem~\ref{thm:analogTheorem23RichmanBridges1999}.
-\end{proof}
 \begin{claim}~
@@
 Because $f\left(\ket{0}\right)=M$, we must also have $f\left(\ket{0}\right)=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$. 
-
-where the last inequality holds because $\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\in\mathbb{C}S^{1}$
-is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
-and 
-\[
-\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
-\]
+\end{proof}
+\end{proof}
+}
+
+\yutsung{
+\begin{proof}
+~
 
@@
 quadratic form on the whole space.
-\end{proof}
+
 \begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 

### 2016-11-17 prob.tex
Revert commit 78c558c, because I forget cross product might not be normalized...

--- 2016-11-17 prob.tex
@@
 
-\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}}$,
-$\ket{\psi_{1}}$, and $\ket{\psi_{2}}\in\mathbb{C}S^{2}$. Consider
-the real vector space spanned by them, and $S^{1}$ be its unit sphere,
-i.e., 
-\[
-\left\{ \sum_{i=0}^{2}a_{i}\ket{\psi_{i}}\middle|a_{i}\in\mathbb{R}\textrm{ and }\sideset{_{\mathbb{R}}}{_{i=0}^{2}}\sum\left|\alpha_{i}\right|^{2}=1\right\} \textrm{ .}
-\]
-
-\begin{itemize}
-\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
-$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
-\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
-$\ket{1}=\ket{2}\times\ket{0}$, 
-\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
-\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
-and 
-\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
-\end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
-for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
-\begin{proof}
-Direct from theorem~\ref{thm:analogTheorem23RichmanBridges1999}.
-\end{proof}
 \begin{claim}~
@@
 Because $f\left(\ket{0}\right)=M$, we must also have $f\left(\ket{0}\right)=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$. 
-
-where the last inequality holds because $\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\in\mathbb{C}S^{1}$
-is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
-and 
-\[
-\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
-\]
-
+\end{proof}
+\end{proof}
+}
+
+\yutsung{
+\begin{proof}
+~
+\begin{proof}
 This proof will be separated into two parts. The first part will estimate

### 2016-11-17 prob.tex
prob.tex \section{Proofs} Global replace rotation by only allow π/2...

--- 2016-11-17 prob.tex
@@
 
+\begin{definition}Given a vector~$\ket{\psi}\in\mathbb{C}^{3}$,
+$\sigma_{\ket{\psi}}$ is the clockwise rotation by $\frac{\pi}{2}$
+about $\ket{\psi}$. More explicitly, for any vector~$\ket{\phi}\in\mathbb{C}S^{2}$,
+$\sigma_{\ket{\psi}}\ket{\phi}=\frac{\ket{\psi}\times\ket{\phi}}{\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert }$.\qed\end{definition}
+
 \begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
@@
 \[
-g_{f,\ket{0}}\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\ket{0}\times\ket{\psi}\right)\textrm{ .}
-\]
-Notice that $\ket{0}\times\ket{\psi}$ is the vector~$\ket{\psi}$
-clockwise-rotated by $\frac{\pi}{2}$ about $\ket{0}$.\qed\end{definition}
+g_{f,\ket{0}}\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\sigma_{\ket{0}}\ket{\psi}\right)\textrm{ .}
+\]
+\qed\end{definition}
 
@@
 $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
-\item $\ket{2}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
+\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
 \item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
@@
 \begin{proof}
-Let $\ket{\bar{2}}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{\bar{0}}$.
+Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{\bar{0}}$.
 Then 
@@
 \begin{eqnarray*}
-\ket{0}\times\left(x,y,z\right) & = & \left(x,-z,y\right)\\
-\ket{2}\times\left(x,y,z\right) & = & \left(-y,x,z\right)
+\sigma_{\ket{0}}\left(x,y,z\right) & = & \left(x,-z,y\right)\\
+\sigma_{\ket{2}}\left(x,y,z\right) & = & \left(-y,x,z\right)
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-Q\left(\ket{\psi}\right)+Q\left(\ket{0}\times\ket{\psi}\right) & = & 2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\\
-Q\left(\ket{\psi}\right)+Q\left(\ket{2}\times\ket{\psi}\right) & = & 2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)
+Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0}}\ket{\psi}\right) & = & 2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\\
+Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{2}}\ket{\psi}\right) & = & 2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-\left|f'\left(\ket{\psi}\right)+f'\left(\ket{0}\times\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
-\left|f'\left(\ket{\psi}\right)+f'\left(\ket{2}\times\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
+\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
+\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
 \end{eqnarray*}
@@
 $m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
-\item $\ket{2}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
+\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
 \item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,
@@
 ~
-
+\begin{proof}
 This proof will be separated into two parts. The first part will estimate
@@
 quadratic form on the whole space.
-
+\end{proof}
 \begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 

### 2016-11-19 prob.tex
prob.tex \section{Proofs} Found an idea of proof doesn't really work...
prob.tex \section{Proofs} Keep fixing the proof...>"<
prob.tex \section{Proofs} Still stuck... Consider to construct some examples...

@@
 \begin{proof}
-...........................
+\yutsung{{To be typed...}}
 \end{proof}
@@
 $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
-\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
-\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
+\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$.
+\item Choose $\ket{1}\in S^{2}$ such that $\ip{1}{0}=\ip{1}{2}=0$. For
+example, we may choose $\ket{1}=\ket{2}\times\ket{0}$.
+\item $Q\left(\ket{\psi}\right)=M\ip{\psi}{0}\ip{0}{\psi}+\left(W-M-m\right)\ip{\psi}{1}\ip{1}{\psi}+m\ip{\psi}{2}\ip{2}{\psi}$,
 \item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
@@
 for nonzero vector~$\ket{\psi}$.
-\end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
-for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}}
-
-\yutsung{
-\begin{proof}
-~
-
-\begin{claim}~
-\begin{itemize}
 \item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
@@
 \item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
-\item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,
+\item $Q\left(\ket{\psi}\right)=M\ip{\psi}{0}\ip{0}{\psi}+\left(W-M-m\right)\ip{\psi}{1}\ip{1}{\psi}+m\ip{\psi}{2}\ip{2}{\psi}$,
 \item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
@@
 Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
-for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
+for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}}
+
+\yutsung{
 \begin{proof}
-For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
+For every vector~$\ket{\psi}\in\mathbb{C}S^{1}$, consider the real
+vector space spanned by $\ket{0'}=\lambda_{0}\ket{0}$, $\ket{\bar{0}'}=\lambda_{\bar{0}}\ket{\bar{0}}$,
+$\ket{\psi'}=\lambda_{\psi}\ket{\psi}$, where $\lambda_{0}$, $\lambda_{\bar{0}}$,
+and $\lambda_{\psi}\in\mathbb{C}$, and denote its unit sphere as
+$S^{2}$. Then, 
+\begin{eqnarray*}
+f\left(\ket{0'}\right)=f\left(\ket{0}\right)=\max_{\ket{\phi}\in\mathbb{C}S^{2}}f\left(\ket{\phi}\right)\ge\max_{\ket{\phi}\in S^{2}}f\left(\ket{\phi}\right)\ge f\left(\ket{0'}\right) & \Rightarrow & \max_{\ket{\phi}\in S^{2}}f\left(\ket{\phi}\right)=f\left(\ket{0'}\right)\\
+f\left(\ket{\bar{0}'}\right)=f\left(\ket{\bar{0}}\right)=\min_{\ket{\phi}\in\mathbb{C}S^{2}}f\left(\ket{\phi}\right)\le\min_{\ket{\phi}\in S^{2}}f\left(\ket{\phi}\right)\le f\left(\ket{\bar{0}'}\right) & \Rightarrow & \min_{\ket{\phi}\in S^{2}}f\left(\ket{\phi}\right)=f\left(\ket{\bar{0}'}\right)\textrm{ .}
+\end{eqnarray*}
+And let 
+\begin{eqnarray*}
+\ket{2'} & = & \sigma_{\ket{0'}\times\ket{\bar{0}'}}\ket{0'}=\frac{\left[\left(\lambda_{0}\ket{0}\right)\times\left(\lambda_{\bar{0}}\ket{\bar{0}}\right)\right]\times\left(\lambda_{0}\ket{0}\right)}{\left\Vert \left[\left(\lambda_{0}\ket{0}\right)\times\left(\lambda_{\bar{0}}\ket{\bar{0}}\right)\right]\times\left(\lambda_{0}\ket{0}\right)\right\Vert }=\frac{\lambda_{0}\lambda_{\bar{0}}\lambda_{0}^{*}\left[\left(\ket{0}\times\ket{\bar{0}}\right)\times\left(\ket{0}\right)\right]}{\left\Vert \lambda_{0}\lambda_{\bar{0}}\lambda_{0}^{*}\left[\left(\ket{0}\times\ket{\bar{0}}\right)\times\left(\ket{0}\right)\right]\right\Vert }=\sigma_{\ket{0}\times\ket{\bar{0}'}}\ket{0}\frac{\lambda_{\bar{0}}}{\left|\lambda_{\bar{0}}\right|}=\ket{2}\frac{\lambda_{\bar{0}}}{\left|\lambda_{\bar{0}}\right|}
+\end{eqnarray*}
+Is $\ket{0}\times\ket{\bar{0}'}\in S^{2}$? Can't we find a rotate
+$\ket{0'}$ in $S^{2}$? And then $\ket{2'}$ will be obviously in
+$S^{2}$? Then, the problem will be whether $\ket{2'}$ parallel to
+$\ket{2}$? Use Mathematica to compute some example?
 \begin{eqnarray*}
@@
 Because $f\left(\ket{0}\right)=M$, we must also have $f\left(\ket{0}\right)=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$. 
-\end{proof}
-\end{proof}
-}
-
-\yutsung{
-\begin{proof}
-~
-\begin{proof}
-This proof will be separated into two parts. The first part will estimate
-the error between the approximation frame function and the quadratic
-form on every complex two-space. The second part will then verify
-the quadratic forms in the first part could be connected and get a
-quadratic form on the whole space.
-\end{proof}
-\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
-\begin{itemize}
-\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
-$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
-\[
-\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
-\]
-\item $\ket{\psi_{2}}=\ket{\psi_{0}}\times\ket{\psi_{1}}\in\mathbb{C}S^{2}$.
-\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
-\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
-\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
-\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
-\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
-\end{itemize}
-Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
-for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
 \end{proof}

### 2016-11-20 prob.tex
prob.tex \section{Proofs} Delete the wrong approach; revert to 5b41eb...
The previous approach is likely wrong because the complex 3-space is
really a real 6-space. Therefore, the rotation might not be able to
expressed as the cross product, and the target quadratic form might not
be as easy as the one used for real 3-space...

--- 2016-11-17 prob.tex
@@
 
-\begin{definition}Given a vector~$\ket{\psi}\in\mathbb{C}^{3}$,
+\begin{definition}Given a vector~$\ket{\psi}\in\mathbb{R}^{3}$,
 $\sigma_{\ket{\psi}}$ is the clockwise rotation by $\frac{\pi}{2}$
-about $\ket{\psi}$. More explicitly, for any vector~$\ket{\phi}\in\mathbb{C}S^{2}$,
+about $\ket{\psi}$. More explicitly, for any vector~$\ket{\phi}\in\mathbb{R}S^{2}$,
 $\sigma_{\ket{\psi}}\ket{\phi}=\frac{\ket{\psi}\times\ket{\phi}}{\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert }$.\qed\end{definition}
@@
 ~
-
+\begin{proof}
+This proof will be separated into two parts. The first part will estimate
+the error between the approximation frame function and the quadratic
+form on every complex two-space. The second part will then verify
+the quadratic forms in the first part could be connected and get a
+quadratic form on the whole space.
+\end{proof}
 \begin{claim}~
@@
 \item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$, 
-$m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
+\item $m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
 \item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
@@
 for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
-\begin{proof}
-For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
-\begin{eqnarray*}
- &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
- & = & \left|Q\left(\ket{\psi}\right)-f\left(\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
- & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
- & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\sum_{i=1}^{2}\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\left|\ip{i}{\psi}\right|\right)\right|
-\end{eqnarray*}
-In order to estimate the last equation, we need to verify the conditions
-listed in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.
-
-First, $\ket{0}$, $\ket{1'}=\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}$,
-and $\ket{2'}=\ket{2}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{2}{\psi}}{\left|\ip{2}{\psi}\right|}$
-form an orthonormal basis, and the restriction of $f$ on the real
-vector space spanned by $\ket{0}$, $\ket{1'}$, and $\ket{2'}$ is
-still a approximation frame function of weight~$\left(W_{l},W_{r}\right)$.
-Because $f\left(\ket{0}\right)=M$, we must also have $f\left(\ket{0}\right)=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$. 
-\end{proof}
-\end{proof}
-}
-
-\yutsung{
-\begin{proof}
-~
-\begin{proof}
-This proof will be separated into two parts. The first part will estimate
-the error between the approximation frame function and the quadratic
-form on every complex two-space. The second part will then verify
-the quadratic forms in the first part could be connected and get a
-quadratic form on the whole space.
-\end{proof}
+
 \begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 

### 2016-11-23 prob.tex
discreteGBKS.bib Add citations, and cited articles...
"D. Aerts, T. Durt, B. Van Bogaert, A physical example of quantum fuzzy sets, and the classical limit.pdf" Added...
discreteGBKS.bib Add citation, and change encoding to utf8

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass{article}
+\documentclass[english]{article}
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage{verbatim}
@@
 
+\usepackage{babel}
+
 \begin{document}
@@
 \begin{itemize}
-\item \url{http://cds.cern.ch/record/518511/files/0107054.pdf} 
+\item \url{http://cds.cern.ch/record/518511/files/0107054.pdf} \cite{GranikCaulfield2001}\\
+\yutsung{The journal didn't put the given volume online... Add arXiv
+version as well, and request an inter-librarian loan...}
 \item \url{http://link.springer.com/chapter/10.1007%2F978-3-642-35644-5_18#page-1}
+\cite{Pykacz2013}
 \item \url{http://link.springer.com/chapter/10.1007%2F978-3-540-93802-6_20#page-1}
+\cite{SNL2009}
 \item \url{http://www.du.edu/nsm/departments/mathematics/media/documents/preprints/m0412.pdf}
+\cite{Gudder2005}\\
+\yutsung{Cannot get the published version online. Request an inter-librarian
+loan.}
 \item \url{http://www.space-lab.ru/files/pages/PIRT_VII-XII/pages/text/PIRT_X/Bobola.pdf}
+\\
+\yutsung{Doesn't find this paper anywhere else except in this URL...
+It seems that it doesn't appear in author's homepage, and I am not
+sure if I found their institution's web page... Very strange...}
 \item \url{http://www.vub.ac.be/CLEA/aerts/publications/1993LiptovskyJan.pdf}
+\cite{aerts1993physical}
+\item \cite{RiecanNeubrunn1997}\\
+\yutsung{Might related. Get this book when I google ``Fuzzy Gleason's
+Theorem''...}
 \end{itemize}
@@
 ``the randomness of an event is relative to a specific model of computation
-with a specified amount of computing resources.'' 
+with a specified amount of computing resources.'' \cite{BlumMicali1984}
 \item Another version \url{https://pdfs.semanticscholar.org/3e9c/5f6f48d9ef426655dc799e9b287d754e86c1.pdf} 

### 2016-11-24 proposal/amr-bio.tex
proposal

\documentclass[11pt]{article}
\usepackage{fullpage,times,url}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\Large {\bf Biographical Sketch for Amr Sabry}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Preparation}

\begin{itemize}
\item Cairo University, Egypt, Electronics \& Computer Engineering, B.Sc.
  (1986)
\item Cairo University, Egypt, Computer Engineering, M.Sc. (1989)
\item Rice University, Computer Science, M.Sc. (1993) 
\item Rice University, Computer Science, Ph.D. (1994) 
\item Chalmers University, Sweden, Programming Languages, Postdoctoral
  researcher (1994-1995)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appointments}

\begin{itemize}
\item{2007-Present} Professor, School of Informatics and Computing,
Indiana University.
\item{2000-2007} Associate Professor, Computer Science Department,
Indiana University.
\item{Spring 2004} Visiting Professor, Genova University, Italy.
\item{Fall 2003} Visiting Researcher, Microsoft Research, Cambridge, UK.
\item{1995-2000} Assistant Professor, Department of Computer and
Information Science, University of Oregon.
\item{1994-1995} Postdoctoral Researcher, Department of Computer Science,
  Chalmers University, G\"oteborg, Sweden.
\item{1993-1994} Research Assistant, Rice University, visiting Carnegie 
Mellon University.
\item{1989-1993} Research and Teaching Assistant, Rice University.
\item{1987} Teaching Assistant, Polytechnic Military School, Egypt. 
\item{1986-1989} Research and Teaching Assistant, Cairo University, Egypt.
\item{1986-1989} Programmer and Consultant, Pacer, Egypt.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Closely Related Publications}

\begin{enumerate}

\item Andrew J. Hanson, Gerardo Ortiz, Amr Sabry, and Yu-Tsung
  Tai. ``Discrete Quantum Theories.'' In \emph{J. Phys. A: Math. Theor.},
  \textbf{47}, 2014.

\item Andrew J. Hanson, Gerardo Ortiz, Amr Sabry, and Yu-Tsung Tai,
  ``Geometry of Discrete Quantum Computing.'' In \emph{J. Phys. A:
  Math. Theor.}, \textbf{46}, 2013.

\item Juliana K. Vizzotto, Andr\'e Rauber Du Bois, and Amr Sabry, ``The Arrow
  Calculus as a Quantum Programming Language,'' In the \emph{Workshop on Logic,
  Language, Information and Computation}, 2009.

\item Thorsten Altenkirch, Jonathan Grattage, Juliana K. Vizzotto, and Amr
  Sabry, ``An Algebra of Pure Quantum Programming.'' In the \emph{Workshop on
  Quantum Programming Languages}, 2005. Final version in the \emph{Electronic
  Notes in Theoretical Computer Science}, vol. 170, pp. 23-47, 2007.

\item Juliana K. Vizzotto, Thorsten Altenkirch, and Amr Sabry, ``Structuring
  Quantum Effects: Superoperators as Arrows.''  \emph{Mathematical Structures
    in Computer Science} (MSCS), Volume 16, Issue 03, pages 453-468, June
  2006.

\end{enumerate}

\section*{Other Significant Publications}

\begin{enumerate}

\item Jacques Carette and Amr Sabry, ``Computing with Semirings and Weak Rig
  Groupoids.'' In the \emph{European Symposium on Programming}, ESOP 2016.

\item Roshan P. James and Amr Sabry, ``Information Effects.'' In the
  \emph{Conference Record of the ACM Symposium on Principles of Programming
  Languages}, 2012.

\item Amr Sabry, ``Side Effects.'' In \emph{Wiley Encyclopedia of Computer
  Science and Engineering, 5-Volume Set}, Volume 4, pages 2534-2543, Benjamin
  W. Wah (Editor), Hoboken: John Wiley \& Sons, Inc, January 2009.

\item Eugenio Moggi and Amr Sabry: Monadic encapsulation of effects: 
a revised approach (extended version). \emph{J. Funct. Program.} 11(6):
591-627 (2001)

\item Cormac Flanagan, Amr Sabry, Bruce F. Duba, and Matthias Felleisen:
The Essence of Compiling with Continuations. In the Proceedings of the ACM
SIGPLAN Conference on Programming Language Design and Implementation, pages
237-247, 1993. \emph{Selected as one of the best 50 PLDI papers from
1979-1999.}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Synergetic Activities}

Paul Purdom and Amr Sabry, CNF Generator for Factoring Problems.  Software
system to generate satisfiability problems used in the SAT competition
organized in conjunction with the Sixth International Conference on the
Theory and Applications of Satisfiability Testing, March 2003, and
continually used by designers of SAT solvers worldwide. Available online at
\url{http://www.cs.indiana.edu/cgi-pub/sabry/cnf.html}.

\end{document}

### 2016-11-24 proposal/dmp.tex
proposal

\documentclass[11pt]{article}
\usepackage{fullpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Data Management Plan}
\author{}
\date{}
\maketitle

The research conducted as part of this project will produce the following
deliverables:
\begin{itemize}
\item research papers and technical reports,
\item software libraries and models, and
\item curriculum materials for undergraduate students, graduate students, and
summer school participants.
\end{itemize}

\paragraph*{Research papers and technical reports.}
All papers and publications that appear in pertinent journals and
conferences will be made available through the websites of the principal
investigators and the arXiv. The websites are regularly backed up as part of
the Indiana University computational infrastructure.

\paragraph*{Software libraries and models.}
Polished libraries will be developed using robust software engineering
approaches with high coding and documentation standards. We will use an
external code repository and make the software, documentation, and examples
available under an open source license. All experimental artifacts will be
archived by the principal investigators and made freely available upon
request to interested researchers.

\paragraph*{Curriculum materials.}
We anticipate developing lecture notes and other teaching materials and we
will make every effort to make these publicly available to students and other
teachers as appropriate.

\end{document}

### 2016-11-24 proposal/obs.tex
proposal

In set theory, a function is usually defined as a mapping that relates
each element in its domain to an element in its range. For example,
the function $a^b$ where $a$ is a positive natural number and $b$ is a
natural number denotes the following infinite set whose elements are
of the form $((a,b),a^b)$ for appropriate values of $a$ and $b$:
\[
\{ ((1,0),1), ~((1,1),1),~((2,0),1) ~\ldots~,~((2,3),8),~\ldots~ \}
\]
There is no notion of this mapping being ``calculated'' in any sense:
it just is. One ``knows'' from the mapping that $2^3$ is $8$: no time,
energy, or any other resource needs to be spent to acquire this
knowledge.

The mathematical idealization of computation founded on Turing
machines~\cite{citeulike:321509} or the
$\lambda$-calculus~\cite{Barendregt:Lambda} maintains this
understanding of computations as mathematical functions. One can use
this mathematical framework to reason about computations and as the
basis for realizing computations on actual physical machines. But
ultimately, programming practice deviates (sometimes significantly)
from the set-theoretic view of functions or the mathematical
idealization of the $\lambda$-calculus. For one thing, an infinite set
cannot be directly stored in a computer; a function is therefore
represented using rules which, given enough time, energy, memory, and
other resources, can be interpreted by a computer to generate any
particular output on demand. It is these rules that we must now
discuss in some detail. For concreteness in this section, we express
them using the notation of the Haskell programming
language~\cite{peytonjones:h98}.

As a reasonable starting point, the set-theoretic function \textit{pow}
can be realized in Haskell using the following declaration:
\begin{quote}
\begin{verbatim} 
pow :: Int -> Int -> Int
pow a 0 = 1
pow a b = a * pow a (b-1)
\end{verbatim}
\end{quote}
The code fragment declares a function called \verb|pow| that takes two values from the domain of Haskell integers \verb.Int. and returns another Haskell integer whose value is the first input raised to the power of the second input. The definition relies on several pre-defined abstractions provided by Haskell. In an appropriate environment, i.e., a computer with an installed Haskell compiler and runtime system, the function declaration can be used to calculate the value of \verb|pow 2 3|. This calculation will proceed in elementary steps that require time, energy, memory, and other computational resources on the computing platform to produce the result \verb|8|.

It is of course possible to write other definitions that realize the same function, e.g:
\begin{quote}
\begin{verbatim} 
pow' :: Int -> Int -> Int
pow' a 0 = 1
pow' a 1 = a
pow' a b | even b = pow' (a * a) (b `div` 2)
pow' a b | odd b = a * pow' a (b-1)
\end{verbatim}
\end{quote}
This definition is often much more efficient. Consider for the example the calculation of $2^{9}$ using the two approaches. The first definition induces the following sequence of elementary calculations:
\begin{quote}
\begin{verbatim} 
pow 2 9 = 2 * pow 2 8
        = 2 * (2 * pow 2 7)  
        = 2 * (2 * (2 * pow 2 6))  
        = 2 * (2 * (2 * (2 * pow 2 5)))  
        = 2 * (2 * (2 * (2 * (2 * pow 2 4)))) 
        = 2 * (2 * (2 * (2 * (2 * (2 * pow 2 3))))) 
        = 2 * (2 * (2 * (2 * (2 * (2 * (2 * pow 2 2)))))) 
        = 2 * (2 * (2 * (2 * (2 * (2 * (2 * (2 * pow 2 1))))))) 
        = 2 * (2 * (2 * (2 * (2 * (2 * (2 * (2 * (2 * pow 2 0)))))))) 
        = 2 * (2 * (2 * (2 * (2 * (2 * (2 * (2 * (2 * 1)))))))) 
        = 2 * (2 * (2 * (2 * (2 * (2 * (2 * (2 * 2)))))))
        = 2 * (2 * (2 * (2 * (2 * (2 * (2 * 4))))))
        = 2 * (2 * (2 * (2 * (2 * (2 * 8)))))
        = 2 * (2 * (2 * (2 * (2 * 16))))
        = 2 * (2 * (2 * (2 * 32))) 
        = 2 * (2 * (2 * 64))
        = 2 * (2 * 128)
        = 2 * 256
        = 512
\end{verbatim}
\end{quote}
The second instead induces the following sequence of elementary calculations:
\begin{quote}
\begin{verbatim} 
pow' 2 9 = 2 * pow' 2 8
         = 2 * pow' (2 * 2) (8 `div` 2) 
         = 2 * pow' 4 4
         = 2 * pow' (4 * 4) (4 `div` 2) 
         = 2 * pow' 16 2 
         = 2 * pow' (16 * 16) (2 `div` 2) 
         = 2 * pow' 256 1
         = 2 * 256
         = 512
\end{verbatim}
\end{quote}

Despite the mismatches between the idealized set-theoretic function
and its two Haskell realizations, it is common to consider all three
definitions to be equivalent at a certain level of
abstraction. Specifically, if we constrain the \emph{observers} to
only ask questions regarding the input-output behavior of a function
(known as the function's \emph{extensional} behavior) then all three
definitions are indeed equivalent. If we however tolerate observers
asking questions regarding timing, memory usage, battery consumption,
or even electromagnetic radiation then the situation is different. For
the set-theoretic function, these observations are non-sensical. For
the Haskell functions, we have for example that one execution of
\verb|pow 2 10000| took 27.31109 ms on a modern laptop while an
execution of \verb|pow' 2 10000| under similar circumstances only took
11.72614 ms, less than half the time. The two functions \verb|pow| and
\verb|pow'| can now be distinguished by observations.

\paragraph*{Observational Equivalence.} There is a well-established
theory that formalizes equivalence of programs up to
observations~\cite{Barendregt:Lambda,Milner:1999:CMS:329902}. In the
conventional application of this theory, the only allowed observations
are the \emph{extensional} ones, i.e., the input-output relations and
other ``semantic'' communication among agents. According to this
conventional situation, the functions \verb|pow| and \verb|pow'| would
be equivalent. As we have seen, by allowing observations of timing
behavior, the two functions \verb|pow| and \verb|pow'| can be
distinguished but formalizing this appears difficult: the precise
timing depends on the particular compiler, runtime system, processor
model, available memory, the resolution of the hardware clock, the
operating system services that manage the hardware clock, and even the
ambient temperature of the room in which the experiment is set up. In
more detail, we know that in order to measure the time elapsed during
the execution of a program, the operating system must execute
additional code that itself takes time to execute and hence distorts
the results to some extent. Moreover the precision of the timing
results is not arbitrary: it is limited by the precision of the
hardware clock, the speed of the code that must execute to record the
timing, the exact memory locations in which the timing results are
stored, and the speed of common operations like addition and
subtraction that must be performed to calculate the elapsed time. In a
\emph{classical worldview}, all these factors are acknowledged to
exist but are not formalized mathematically. Instead, the experimenter
takes great care to minimize their impact by striving to communicate
reproducible results consisting of mean execution times under
carefully managed conditions. Thus, the precise timings are treated as
an objective (ontic) property of the functions and measurements are
viewed as operations that simply reveal such properties with minimal
disturbance.

### 2016-11-24 proposal/prop.tex
proposal

\documentclass{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{tensor}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{case}{Case}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newtheorem{claim}{Claim}

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
\newcommand{\bra}[1]{{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
\newcommand{\proj}[1]{\op{#1}{#1}}
\def\C{{\mathbb{C}}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\rme}{\mathrm{e}}
\newcommand{\rmi}{\mathrm{i}}

%% \title{Computational Quantum Probabilities}
%% \title{Measurement and Probability in Fuzzy Quantum Theories}
\title{Measurement and Probability in Fuzzy Quantum Theories}
\date{}
\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview, Objectives, and Expected Significance}

This is a \emph{theoretical} investigation of \emph{experimental}
physics using \emph{computational} methods. All experiments and
computations are processes bounded in space, time, energy, and other
resources. Yet, for centuries, the mathematical formalization of such
processes has been founded on the infinitely precise real or complex
numbers. Indeed, almost every description of quantum mechanics,
quantum computation, or quantum experiments refers to entities such as
$e$, $\pi$, $\sqrt{2}$, etc. From a computational perspective, such
numbers do not exist in their entirety ``for free.''  For example, the
state of the art algorithms for computing the $n$th digit of~$\pi$
require on the order of $n^2$
operations~\cite{journals/moc/BaileyBP97}. In other words, simply
referring to the $n$th digit of $\pi$ requires more and more resources
as $n$ gets larger. Taking such resource bounds in consideration is
what founded computer science as a discipline and is crucial for
understanding the very nature of computation and, following
Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, for understanding the very nature of physical processes.

We propose to revisit quantum mechanics, quantum information, and
quantum computation from this resource-aware perspective. Our initial
result in that domain showed how subtle the issues can be~\cite{usat}:
a straightforward replacement of the complex numbers by a finite field
yields a variant of quantum mechanics in which computationally hard
problems like UNIQUE-SAT (which decides whether a given Boolean
formula is unsatisfiable or has exactly one satisfying assignment) can
be deterministically solved in constant time. To eliminate such
unrealistic theories requires delicate analysis of the structure of
the Hilbert space, the process of observation, and the notion of
probability teasing apart their reliance on the infinitely precise
real numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is
to shift focus from the infinitely-specified but not directly
observable quantum states, to observable measurable properties of
quantum systems and their probabilities. Furthermore, we insist that
our theories of measurement and probability only refer to finitely
communicable evidence within feasible computational bounds. It follows
that states, observations, and probabilities all become ``fuzzy'',
i.e., specified by intervals of confidence that can only increase in
precision if the available resources increase proportionally. Our
notion of ``fuzzy quantum mechanics'' is related to existing
work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
but, as will be explained in more detail, is distinguished by its
computational character.

We will begin by reviewing existing work that recasts classical
probability spaces in a resource-aware setting and move to our
proposal which, briefly speaking, aims at recasting quantum
probability and hence quantum measurement to a corresponding
resource-aware setting. In particular, we plan on addressing the
Meyer-Mermin debate~\cite{} on the impact of finite precision
measurements on the relevance of the Kochen-Specker theorem. We argue
that no matter what the results are their impact will be
strong. Positive results that formulate a computable, with clear
resource bounds, theory of quantum measurement and quantum probability
would be essential for understanding and realizing quantum
computation. Any negative results would redirect research that aims at
realizing quantum computation to other approaches. At an intellectual
level, the results will solve or clarify several paradoxes in quantum
mechanics, quantum information, computability, and complexity theory.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background I: Classical Probability}

A \emph{probability space} specifies the necessary conditions for
reasoning coherently about collections of uncertain
events~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}.  We
review the conventional presentation of probability spaces and then
discuss the computational resources needed to estimate probabilities.

%%%
\subsection{Classical Probability Spaces}

The conventional definition of a probability space builds upon the
field of real numbers. In more detail, a probability space consists of
a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
and a \emph{probability measure}~$\pmeas$ mapping events in $\events$
to the real interval $[0,1]$. We will only consider \emph{finite} sets
of events and restrict our attention to non-empty finite sets $\Omega$
as the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the
powerset~$2^{\Omega}=\left\{ E ~\middle|~ E\subseteq\Omega\right\}
$.
For future reference, we emphasize that events are the primary notion
of interest and that the sample space is a convenient artifact that
allows us to treat events as sets obeying the laws of Boolean algebra.

\begin{definition}[Probability Measure]\label{def:ClassicalProbabilitySpace}
  Given the set of events $\events$, a \emph{probability measure} is a
  function $\pmeas:\events\rightarrow[0,1]$ such that:
\begin{itemize}
\item $\pmeas(\emptyset)=0$,
\item $\pmeas(\Omega)=1$, 
\item for every event $E$,
  $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$ where
  $\Omega\backslash E$ is the complement event of $E$, and
\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of
  pairwise disjoint events,
  $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$.
\end{itemize}
\end{definition}
\noindent There is some redundancy in the definition that will be useful when
moving to quantum probability spaces.

\begin{example}[Two-coins experiment]\label{ex1} Consider an
  experiment that tosses two coins. We have four possible outcomes
  that constitute the sample space $\Omega=\{HH,HT,TH,TT\}$. There are
  16 total events including the event $\{HH,HT\}$ that the first coin
  lands heads up, the event $\{HT,TH\}$ that the two coins land on
  opposite sides, and the event $\{HT,TH,TT\}$ that at least one coin
  lands tails up. Here is a possible probability measure for these
  events:
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) & = & 0\\
\pmeas(\{HH\}) & = & 1/3\\
\pmeas(\{HT\}) & = & 0\\
\pmeas(\{TH\}) & = & 2/3\\
\pmeas(\{TT\}) & = & 0\\
\pmeas(\{HH,HT\}) & = & 1/3\\
\pmeas(\{HH,TH\}) & = & 1\\
\pmeas(\{HH,TT\}) & = & 1/3
\end{array} & \begin{array}{rcl}
\pmeas(\{HT,TH\}) & = & 2/3\\
\pmeas(\{HT,TT\}) & = & 0\\
\pmeas(\{TH,TT\}) & = & 2/3\\
\pmeas(\{HH,HT,TH\}) & = & 1\\
\pmeas(\{HH,HT,TT\}) & = & 1/3\\
\pmeas(\{HH,TH,TT\}) & = & 1\\
\pmeas(\{HT,TH,TT\}) & = & 2/3\\
\pmeas(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\]
\end{example}

\noindent It is useful to think that this probability measure is
completely determined by the ``reality'' of the two coins in question
and their characteristics, in the sense that each pair of coins
induces a measure, and each measure must correspond to some pair of
coins. The measure above would be induced by two particular coins such
that the first coin is twice as likely to land tails up than heads up
and the second coin is double-headed. In a strict computational
or experimental setting, one should question the reliance of the
definition of probability space on the uncountable and uncomputable
real interval $[0,1]$. This interval includes numbers like
$0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether
Turing machine $M_{i}$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\frac{\pi}{4}$
which can only be computed with increasingly large resources as the
precision increases. Therefore, in a resource-aware computational or
experimental setting, it is more appropriate to consider probability
measures that map events to a set of elements computable with a fixed
set of resources. We expand on this observation in the next section
and then recall its formalization using interval-valued probability
measures~\cite{Weichselberger2000,JamisonLodwick2004}.

%%%%%
\subsection{Measuring Probabilities: Buffon's Needle Problem\label{subsec:Measuring-Probabilities:-Buffon}}

In the previous example, we assumed the probability~$\pmeas(E)$ of
each event~$E$ is known a priori. In reality, although each event is
assumed to have a probability, the exact value of $\pmeas(E)$ may not
be known. According to the \emph{frequency interpretation of
  probability} (which we will revisit when moving to the quantum
case), to determine the probability of an event, we run $N$
independent trials which gives us an approximation of the (assumed)
``true'' or ``real'' probability. Let $x_{i}$ be 1 or 0 depending on
whether the event~$E$ occurs in the $i$-th trial or not, then
$\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$ with the
probability converging to one as $N$ goes to infinity, i.e.,
\[
\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sideset{}{_{i=1}^{N}}\sum x_{i}\right|<\epsilon\right)=1\textrm{ .}
\]
This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

Let's look at a concrete example. Suppose we drop a needle of length
$\ell$ onto a floor made of equally spaced parallel lines a distance
$h$ apart, where $\ell<h$. It is a known fact that the probability of
the needle crossing a line is
$\frac{2\ell}{\pi
  h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
Consider an experimental setup consisting of a collection of $N$
identical needles of length $\ell$. We throw the $N$ needles one
needle at a time, and observe the number $M$ of needles that cross a
line, thus estimating the probability of a needle crossing a line to
be $\frac{M}{N}$. In an actual experiment with $500$ needles and the
ratio $\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$
crossed a line so the relative frequency is $0.472$ whereas the
idealized mathematical probability is $0.4774\ldots$.  In a larger
experiment with $5000$ needles and the ratio
$\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, the relative frequency was
calculated to be $0.5064$ whereas the idealized mathematical
probability is $0.5092\ldots$. We see that the observed probability
approaches $\frac{2\ell}{\pi h}$ but only if \emph{larger and larger
  resources} are expended. These resource considerations suggest that
it is possible to replace the real interval $[0,1]$ with rational
numbers up to a certain precision related to the particular experiment
in question. There is clearly a connection between the number of
needles and the achievable precision: in the hypothetical experiment
with 3 needles, it is not sensible to retain 100 digits in the
expansion of $\frac{2\ell}{\pi h}$.

There is another more subtle assumption of unbounded computational
power in the experiment. We are assuming that we can always determine
with certainty whether a needle is crossing a line. But ``lines'' on
the the floor have thickness, their distance apart is not exactly $h$,
and the needles' lengths are not all absolutely equal to $\ell$.
These perturbations make the events ``fuzzy.'' Thus, in an experiment
with limited resources, it is not possible to talk about the idealized
event that exactly $M$ needles cross lines as this would require the
most expensive needles built to the most precise accuracy, laser
precision for drawing lines on the floor, and the most powerful
microscopes to determine if a needle does cross a line. Instead we
might talk about the event that $M-\delta$ needles evidently cross
lines and $M+\delta'$ needles plausibly cross lines where $\delta$ and
$\delta'$ are resource-dependent approximations. This fuzzy notion of
events leads to probabilities being only calculable within intervals
of confidence reflecting the certainty of events and their
plausibility. This is indeed consistent with published experiments: in
an experiment with $3204$ needles and the ratio
$\frac{\ell}{h}=0.6$~\cite{DeMorgan1872}, $1213$ needles clearly
crossed a line and $11$ needles were close enough to plausibly be
considered as crossing the line: we would express the probability in
this case as the interval
$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we
are certain that the event has probability at least
$\frac{1213}{3204}$ but it is possible that it would have probability
$\frac{1224}{3204}$.

%%%%%
\subsection{Classical Interval-Valued Probability Measures}

As motivated above, an event $E_{1}$ may have an interval of
probability $[l_{1},r_{1}]$. Assume that another disjoint event
$E_{2}$ has an interval of probability $[l_{2},r_{2}]$, what is the
interval of probability for the event $E_{1}\cup E_{2}$? The answer is
somewhat subtle: although it is possible to use the sum of the
intervals $[l_{1}+l_{2},r_{1}+r_{2}]$ as the combined probability, one
can find a much tighter interval if information \emph{against} the
event (i.e., information about the complement event) is also taken
into consideration. Formally, for a general event $E$ with probability
$[l,r]$, the evidence that contradicts $E$ is evidence supporting the
complement of $E$.  The complement of $E$ must therefore have
probability $\left[1-r,1-l\right]$ which we abbreviate
$\left[1,1\right]-\left[l,r\right]$.  Given a sample space~$\Omega$
and its set of events~$\events$, a
function~$\bar{\mu}:\events\rightarrow[0,1]$ is a classical
interval-valued probability measure if and only if $\bar{\mu}$
satisfies the following conditions~\cite{JamisonLodwick2004} where the
last line uses $\subseteq$ to allow for tighter intervals that exploit
the complement event:
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$.
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For any event $E$,
  $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$
\item For a collection $\left\{ E_{i}\right\} _{i=0}^{N}$ of pairwise
  disjoint events, we have
  $\bar{\mu}\left(\bigcup_{i=0}^{N}E_{i}\right)\subseteq\sum_{i=0}^{N}\bar{\mu}\left(E_{i}\right)$.
\end{itemize}

\begin{example}[Two-coin experiment with interval probability]
\label{ex3} We split the unit interval $[0,1]$ in the following
four closed sub-intervals: $[0,0]$ which we call \imposs, $[0,\frac{1}{2}]$
which we call \unlikely, $[\frac{1}{2},1]$ which we call \likely,
and $[1,1]$ which we call \necess. Using these new values, we can
modify the probability measure of Ex.~\ref{ex1} by mapping each
numeric value to the smallest sub-interval containing it to get the
following: 
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & \imposs\\
\bar{\mu}(\{HH\}) & = & \unlikely\\
\bar{\mu}(\{HT\}) & = & \imposs\\
\bar{\mu}(\{TH\}) & = & \likely\\
\bar{\mu}(\{TT\}) & = & \imposs\\
\bar{\mu}(\{HH,HT\}) & = & \unlikely\\
\bar{\mu}(\{HH,TH\}) & = & \necess\\
\bar{\mu}(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & \likely\\
\bar{\mu}(\{HT,TT\}) & = & \imposs\\
\bar{\mu}(\{TH,TT\}) & = & \likely\\
\bar{\mu}(\{HH,HT,TH\}) & = & \necess\\
\bar{\mu}(\{HH,HT,TT\}) & = & \unlikely\\
\bar{\mu}(\{HH,TH,TT\}) & = & \necess\\
\bar{\mu}(\{HT,TH,TT\}) & = & \likely\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & \necess
\end{array}\end{array}
\]
Despite the absence of infinitely precise numeric information, the
probability measure is quite informative: it reveals that the second
coin is double-headed and that the first coin is biased. To understand
the $\subseteq$-condition, consider the following calculation:
\begin{eqnarray*}
\bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})
&=& \imposs+\unlikely+\imposs+\likely\\
&=& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]\\
&=& \left[\frac{1}{2},\frac{3}{2}\right]
\end{eqnarray*}
If we were to equate $\bar{\mu}(\Omega)$ with the sum of the individual
probabilities, we would get that $\bar{\mu}(\Omega)=\left[\frac{1}{2},\frac{3}{2}\right]$.
However, using the fact that $\bar{\mu}(\emptyset)=\imposs$, we have
$\bar{\mu}\left(\Omega\right)=1-\bar{\mu}\left(\emptyset\right)=\necess=[1,1]$.
This interval is tighter and a better estimate for the probability
of the event $\Omega$, and of course it is contained in $[\frac{1}{2},\frac{3}{2}]$.
However it is only possible to exploit the information about the complement
when all four events are combined. Thus the $\subseteq$-condition
allows us to get an estimate for the combined event from each of its
constituents and then gather more evidence knowing the aggregate
event.
\end{example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background II: Quantum Probability}

The mathematical framework of classical probability above assumes that
there exists a predetermined set of events that are independent of the
particular experiment --- classical physics is
non-contextual. However, even in classical situations, the structure
of the event space is often only partially known and the precise
dependence of two events on each other cannot, a priori, be determined
with certainty. In the quantum framework, this partial knowledge is
compounded by the fact that there exist non-commuting events which
cannot happen simultaneously. To accommodate these more complex
situations, conventional approaches to quantum probability abandon the
sample space~$\Omega$ and reason directly about events which are
generalized from plain sets to projection operators. A quantum
probability space therefore consists of just two components: a set of
events $\qevents$ often formalized as projection operators and a
probability measure $\mu:\qevents\rightarrow[0,1]$ formalized using
the Born rule.

%%%%%
\subsection{Quantum Events}

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
  \label{def:Projection} Given a Hilbert space $\Hilb$, an event (an
  experimental proposition~\cite{BirkhoffVonNeumann1936}, a
  question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or
  an elementary quantum test~\cite{peres1995quantum}) is represented
  as a (self-adjoint or orthogonal~\cite {Griffiths2003,Maassen2010})
  projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace
  of $\Hilb$. The following define projections and list some of their properties:
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_{0}$ and $P_{1}$ are \emph{orthogonal}
  if $P_{0}P_{1}=P_{1}P_{0}=\mathbb{0}$. The sum of two projection
  operators~$P_{0}+P_{1}$ is also a projection operator if and only if
  they are orthogonal.
\item Conversely, every projection~$P$ can be expressed as
  $\sum_{j=1}^{N}\proj{\psi_{j}}$, where $P$ actually projects onto
  the linear subspace with orthonormal
  basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{N}$.
\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is
  called an \emph{ideal measurement} if it is a partition of the
  identity, i.e., $\sum_{i=1}^{N}P_{i}=\mathbb{1}$~\cite{Swart2013}.
  In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
  be mutually orthogonal~\cite{Griffiths2003} and $N$ must correspond
  to the dimension of the Hilbert space.
\item If $P$ is a projection operator, then $\mathbb{1}-P$ is also a
  projection operator, called its \emph{complement}. It is orthogonal to
  $P$, and corresponds to the complement event~$\Omega\backslash E$ in
  classical probability~\cite{Griffiths2003}.
\item Projection operators $P_{0}$ and $P_{1}$ \emph{commute} if $P_{0}P_{1}=P_{1}P_{0}$.
The product of two projection operators~$P_{0}P_{1}$ is also a projection
operator if and only if they commute. This corresponds to the classical
intersection between events~\cite{peres1995quantum,Griffiths2003}. 
\item For two commuting projection operators $P_{0}$ and $P_{1}$,
  their \emph{disjunction}~$P_{0}\vee P_{1}$ is defined to be
  $P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
\end{itemize}
\end{definition}

\begin{example}[One-qubit quantum probability space] Consider a
  one-qubit Hilbert space with each event interpreted as a possible
  post-measurement state. For example, the event $\proj{0}$ indicates
  that the post-measurement state will be $\ket{0}$; the probability
  of such an event depends on the current state; the event $\proj{1}$
  indicates that the post-measurement state will be $\ket{1}$; the
  event $\proj{\ps}$ where
  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$ indicates that the
  post-measurement state will be $\ket{\ps}$; the event
  $\mathbb{1}=\proj{0}+\proj{1}$ indicates that the post-measurement
  state will be a linear combination of $\ket{0}$ and $\ket{1}$ and is
  clearly certain; finally the empty event $\mathbb{0}$ states that
  the post-measurement state will be the empty state and is
  impossible. As in the classical case, a probability measure is a
  function that maps events to $[0,1]$. Here is a partial
  specification of a possible probability measure that would be
  induced by a system whose current state is $\ket{0}$:
\[
\mu\left(\mathbb{0}\right)=0,\quad
\mu\left(\mathbb{1}\right)=1,\quad
\mu\left(\proj{0}\right)=1,\quad
\mu\left(\proj{1}\right)=0,\quad
\mu\left(\proj{\ps}\right)=1/2,\quad
\ldots
\]
Note that, similarly to the classical case, the probability of
$\mathbb{1}$ is 1 and the probability of collections of orthogonal
events (e.g., $\proj{0}+\proj{1}$) is the sum of the individual
probabilities.  A collection of non-orthogonal events (e.g.,
$\proj{0}$ and $\proj{\ps}$) is however not even a valid event. In the
classical example, we argued that each probability measure is uniquely
determined by two actual coins. A similar (but much more subtle)
argument is valid also in the quantum case. By postulates of quantum
mechanics and Gleason's theorem, it turns out that for large enough
quantum systems, each probability measure is uniquely determined by an
actual quantum state as discussed next.
\end{example}

%%%%%
\subsection{Quantum Probability Measures}

Given our setup, the definition of a quantum probability measure is a
small variation on the classical definition.

\begin{definition}[Quantum Probability Measure~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
Given a Hilbert space $\Hilb$ with its set of events~$\events$,
a \emph{quantum probability measure} is a function~$\mu:\events\rightarrow[0,1]$
such that: 
\begin{itemize}
\item $\mu(\mathbb{0})=0$. 
\item $\mu(\mathbb{1})=1$. 
\item For any projection $P$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$.
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)$.
\end{itemize}
\end{definition}

\noindent A quantum probability measure can be easily constructed if
one knows the current state of the quantum system by using the Born
rule~\cite{Born1983,Mermin2007,Jaeger2007}.  Specifically, for each
pure normalized quantum state $\ket{\phi}$, the Born rule induces a
probability measure $\mu_{\phi}^{B}$ defined as
$\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}$. Conversely every probability
measure must be of this shape (accounting for the generalization to
mixed states).

\begin{thm}[Gleason's
  theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
measure~$\mu:\events\rightarrow[0,1]$, there exists a unique mixed
state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.
\end{thm}

%%%%%
\subsection{Measuring Quantum Probabilities}

By using the law of large numbers, quantum probabilities can be also
estimated by relative frequencies. For example, if we want to know the
probability of ``spin up'' in a Stern-Gerlach
experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}, we
can put a beam of silver atoms in a highly inhomogeneous magnetic
field, and count the number of atoms deflects up. Ideally, if the
local field of strength directs to the $z$-axis, and all particles
have the same velocity, the Stern-Gerlach experiment only produces two
spots corresponding to $\ket{0}$ and $\ket{1}$. Notice that whenever
the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal
measurement is picked, measuring the spin is exactly the same as
tossing a coin. In other words, if someone claims to be tossing a coin
behind a veil, and only shows the resulting heads or tails, we cannot
distinguish whether the results are really deriving from tossing a
coin, or by running a Stern-Gerlach experiment, and showing the head,
the tail, or the side of coin if the silver atoms is spin up, spin
down, or just hit the middle, respectively. Following our theme, a
Stern-Gerlach experiment requires significant resources to keep the
local field of strength directing to the $z$-axis precisely, to keep
the atoms having almost the same velocity, and to point out the exact
position each particle landed on. If the field of strength does not
perfectly direct to the $z$-axis, we do not really test the quantum
event we want to test. Even if the field of strength perfectly directs
to the $z$-axis, the variant velocity makes spots broader and more
washed out. Together with the precision limit of the detector, it may
sometimes be hard to decide a particle corresponding to which state.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background III: From Functions to Interactive Processes}

The early formalization of the process of computing using Turing
machines~\cite{citeulike:321509} or the
$\lambda$-calculus~\cite{Barendregt:Lambda} viewed a computation as
realizing a mathematical function. From our perspective, the most
important consequence of this view is that the properties of the
computed function existed independently of any observation,
calculation, or interaction. An agent can only interact with the
computation by asking questions regarding its input-output behavior
and although such interaction would reveal fragments of the computed
function it could not change it or affect it in any way.

In a series of breakthrough papers that led to his Turing
Award~\cite{Milner:1993:EIT:151233.151240}, Milner argued that this
``closed system'' view of computation is too limiting as it cannot
adequately describe \emph{interactive computations}. Milner explained
that ``concurrency requires a new conceptual framework'' and ``not
merely an extension of the repertoire of entities and constructions
which explain sequential computing.'' He gives the following simple
but compelling example. Consider the following two programs:
\begin{verbatim}
Program P1: x := 1 ; x := x + 1 
Program P2: x := 2
\end{verbatim}
As closed systems, these two programs define the same relation, namely
the one that maps an input memory to an updated memory in which the
location named \verb|x| is assigned the value \verb|2|. But place the
programs in an environment which may involve interactions and the
equivalence is lost. Concretely, place each of the two programs
concurrently with the program:
\begin{verbatim}
Program Q: x := 3
\end{verbatim}
and we can observe the following. In the combined system of \verb|P1|
and \verb|Q| running concurrently, the location \verb|x| may end up
containing \verb|2|, \verb|3|, or \verb|4|. But in the combined system
of \verb|P2| and \verb|Q| running concurrently, the location~\verb|x|
can only end up containing \verb|2| or \verb|3|. The lesson, phrased
in physics terms, is that it not sensible to think of the properties
of a system (like \verb|P1| or \verb|P2|) independently of the
observer (\verb|Q| in this case).

This phenomenon is hardly a surprise to computer scientists or
physicists but embracing it fully does have far reaching
consequences. In computer science, the big shift was to abandon the
idea that a computation has inherent internal meaning, e.g.,
representing a pure mathematical function. Instead \emph{the meaning
  of a computational process is its observable behavior.} It is not
too difficult to imagine that, in the presence of multiple interacting
observers, the behavior observed by just one agent would appear to
involve hidden variables or action at a distance. The well-established
theory of observation of concurrent processes and their
equivalences~\cite{Hennessy1989} relies on neither.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposal: General Plan}

A major aim of this proposal is to recast quantum probability and
measurement in a computational resource-aware setting. Our vision is
to unify the strands above in a novel way as explained in this
section. We start with some immediate observations that justify the
rest of the development.

\begin{itemize}

\item If we insist that probabilities cannot be infinitely precise and
  are bound to be approximations represented by intervals of
  confidence, then by Gleason's theorem, quantum states themselves
  cannot be infinitely precise. This raises an important philosophical
  question with immense practical relevance in the context of quantum
  computing. The question, which we could largely bypass in the
  classical case, is whether there is, in the background of all the
  measurements and probabilities, a ``real'' infinitely-precise
  quantum state that is being approximated and that, in principle, can
  be more and more accurately described given more and more
  resources. The answer will have to be \emph{no} if we are to respect
  major theorems of quantum mechanics and quantum information. Thus
  our first radical departure from the classical case will be that the
  quantum state itself must be fuzzy in some sense to be formalized.

\item Going further we actually have to concede not just the infinite
  accuracy of the quantum state, but its very existence as a ``real''
  entity that exists independently of measurements and
  probabilities. The reasons for this radical position are as
  follows. First arguments embedded in the proof of the Kochen-Specker
  theorem essentially rule out the existence of a sample space as the
  probabilities of events cannot be consistently expressed using core
  assignments to elements of the sample space. Second, the frequency
  interpretation of probability which is already problematic in the
  classical case, becomes untenable in the quantum case. In both
  cases, but much more in the quantum case, it is much more sensible
  to interpret probability in the Bayesian sense as ``lack of
  knowledge''. This, and similar arguments elegantly expressed by
  recent work on Quantum Bayesianism~\cite{}, suggest that the quantum
  state is more like an interactive system in computer science
  parlance. In other words, the state is only determined by its
  interactions with the environment or observers. A rough but useful
  analogy in the context of computer science would be a web server:
  the state of such a system cannot be said to exist independently of
  the interactions with clients; each interaction with a client
  determines a future state of the system and may affect future
  interactions. Crucially, each client may have a \emph{different}
  view of the web server that is consistent with their own history of
  interactions. This computational perspective agrees with the
  philosophical position of QBism that asserts that the quantum state
  is subjective: each observer has a different view of the quantum
  system that is consistent with their previous observations and that
  allows that observer, independently of other observers, to assign
  beliefs (i.e., probabilities) to future interactions.

\end{itemize}

%%%%%
\subsection{Proposed Activity I: Quantum Interval-valued Probability Measures}

Just as it is the case for Buffon's needles, estimating quantum
probabilities (e.g., in the case of a Stern-Gerlach experiment) with
increasing accuracy requires increasingly large resources.  Therefore,
given some finite resources, it is only possible to estimate the
quantum probabilities within an interval of confidence. It is
therefore natural to introduce the notion of an ``interval-valued
quantum probability measure'' that combines the definitions of
conventional quantum probability measures with classical
interval-probabilities.

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
  Given a Hilbert space $\Hilb$ with quantum events
  (projections)~$\events$, and a collection of
  intervals~$\mathscr{I}$, a \emph{quantum
    $\mathscr{I}$-interval-valued probability measure} is a
  function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ such that:
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any projection $P$, 
\begin{equation}
\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
\end{equation}
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have:
\begin{equation}
\bar{\mu}\left(\sideset{}{_{i=1}^{N}}\sum P_{i}\right)\subseteq\sideset{}{_{i=1}^{N}}\sum\bar{\mu}\left(P_{i}\right)
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
\end{definition}

It is easy to establish that quantum interval-valued probability
measures generalize conventional quantum probability measures. In
particular, any quantum probability measure can be recast as an
interval-valued measure using the three intervals $\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where
$\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called
\unknown~because it provides no information as follows. Given a
probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
define a quantum interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where
$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{if }x=1\textrm{ ;}\\
\imposs & \textrm{if }x=0\textrm{ ;}\\
\unknown & \textrm{otherwise.}
\end{cases}
\]

The interesting question is the converse one corresponding to
Gleason's theorem. Given an interval-valued probability measure, i.e.,
given observations done with finite resources, do these observations
uniquely determine a quantum state? Our initial investigations
indicate that the answer is \emph{no}.

\begin{definition}
  Given a quantum interval-valued probability
  measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{quantum probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $.
\item $\bar{\mu}$ is called convex if 
\begin{equation}
  \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
\end{equation}
 for all commuting $P_{0},P_{1}\in\events$. 
\end{itemize}
\end{definition}

\begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
There is a convex quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.
\end{thm}

This theorem can be proved by the following example.

\begin{example}[Three-dimensional quantum three-value interval-valued
probability measure]\label{ex:three-dimensional-three-value} Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$.
Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability
measure, first notice that
$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation
(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) by
induction. Second, equation
(\ref{eq:QuantumInterval-valuedProbability-Complement}) implies
$\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation
(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), it is
sufficient to check
\[
\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
\]
for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)$.

Next, we need to verify that $\bar{\mu}$ is convex. First, for orthogonal
projections $P_{0}$ and $P_{1}$, equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
implies equation (\ref{eq:QuantumInterval-valuedProbability-Convex}).
Second, when $P_{0}=P_{1}+P_{2}$, equation
(\ref{eq:QuantumInterval-valuedProbability-Convex}) holds trivially.
Hence, we only need to verify the case which $P_{0}=\proj{\psi_{0}}+\proj{\psi_{2}}$
and $P_{1}=\proj{\psi_{1}}+\proj{\psi_{2}}$,
where $\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
is an orthonormal basis. Because we have 
\begin{eqnarray*}
\bar{\mu}\left(P_{0}\vee P_{1}\right) & = & \bar{\mu}\left(\mathbb{1}\right)=\necess\\
\bar{\mu}\left(P_{0}P_{1}\right) & = & \bar{\mu}\left(\proj{\psi_{2}}\right)\subseteq\unknown
\end{eqnarray*}
and $\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
is either $\necess+\unknown$ or $\unknown+\unknown$.
Therefore, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.

Finally, we will prove that $\bar{\mu}$ cannot correspond to any
quantum probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed
state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$ such that
$\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$.  However, no pure
state~$\ket{\phi}$ satisfies
$\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$ so that we have
$\mu(P)\notin\bar{\mu}(P)$ for all quantum probability measure~$\mu$.
\end{example}

Recall that when approximating the probability classically, the quality
of the experimental equipment cannot be compensated by the number
of independent trials. If the precision of the intervals~$\mathscr{I}$
represents the quality of the quantum experimental equipment, example~\ref{ex:three-dimensional-three-value}
tells us that we cannot identify a particular state if the experimental
equipment reveals too little information. For example, $\bar{\mu}$
might correspond to $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
$\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
or the density matrix~$\frac{\mathbb{1}}{3}$ because $\bar{\mu}(\proj{\phi})\ne\necess$
for all $\ket{\phi}$. Also, example~\ref{ex:three-dimensional-three-value}
is no longer valid if our measurement equipment is a little more precise,
say $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
because example~\ref{ex:three-dimensional-three-value} really use
the property of $\unknown$.

If we consider
$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
example~\ref{ex:three-dimensional-4-value} provides another example
with an empty core. Comparing to
example~\ref{ex:three-dimensional-three-value},
example~\ref{ex:three-dimensional-4-value} is closer to the Born rule
in a sense that it might only correspond to $\ket{2}$ or
$\frac{\mathbb{1}}{3}$, but not
$\ket{1}$. Example~\ref{ex:three-dimensional-4-value} is also no
longer valid for more precise measurement equipment as well.  In
general, we believe if the measurement equipment is more and more
precise, its interval-valued probability measure will be closer and
closer to the the Born rule. In the limit case,
$\mathscr{I}=\left\{ \left\{ a\right\}
  \middle|a\in\left[0,1\right]\right\} $
recovers conventional Gleason's theorem and the Born rule.

\begin{example}[Three-dimensional quantum 4-value interval-valued
probability measure]\label{ex:three-dimensional-4-value} \footnote{Need to verify whether this example is convex or not.}Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$,
and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
defined as follow, where the state vectors corresponding to 1-dimensional
projector are also illustrated in figure~\ref{fig:three-dimensional-4-value}.
\begin{enumerate}
\item Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \necess\textrm{ ,}
\end{eqnarray*}
 where $\ket{0}$ and $\ket{\ps}$ is illustrated as the red and green
dotted vector, respectively.
\item Consider the red and green circles in figure~\ref{fig:three-dimensional-4-value}.
They are the states orthogonal to $\ket{0}$ and $\ket{\ps}$, respectively,
and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
half of those states need special treatment, i.e., whenever $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we define 
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely\textrm{ .}
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely$. 
\end{enumerate}
That $\bar{\mu}$ has an empty core can be proved by contradiction.
Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\[
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\]

Similar to example~\ref{ex:three-dimensional-three-value}, to verify
$\bar{\mu}$ is a quantum interval-valued probability measure, we
only need to verify equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
and it is sufficient to check 
\begin{equation}
\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{0}}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)
\end{aligned}
\label{eq:non-additive-vectors}
\end{equation}
for every orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $.
We are going to enumerate all possible orthonormal bases to verify
equation~(\ref{eq:non-additive-vectors}), and case 1 and 2 are illustrated
in figure~\ref{fig:three-dimensional-4-value}. 
\begin{center}
\begin{figure}
\includegraphics[scale=0.4]{measure4.pdf}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates case
1 and 2 in $\mathbb{R}^{3}$ in example~\ref{ex:three-dimensional-4-value}.
The red and green dotted vector are $\ket{0}$ and $\ket{\ps}$ respectively.
All possible vectors of $\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
are drawn in the red and green circles, respectively. Within the circles,
a vector~$\ket{\psi}$ in dotted part means $\bar{\mu}(\proj{\psi})=\likely$;
otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
\end{figure}
\end{center}

\begin{enumerate}
\item When $\ket{\psi_{0}}$ is $\ket{0}$, then either $\ket{\psi_{1}}$
or $\ket{\psi_{2}}$ must be $\ket{0_{\theta,\gamma}^{\perp}}$ for
some $\theta$ and $\gamma$. Because of 
\[
\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
0\\
0
\end{pmatrix}\times\begin{pmatrix}0\\
\rme^{\rmi\gamma}\sin\theta\\
\cos\theta
\end{pmatrix}=\begin{pmatrix}0\\
-\cos\theta\\
\rme^{-\rmi\gamma}\sin\theta
\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}0\\
\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
\cos\left(\frac{\pi}{2}-\theta\right)
\end{pmatrix}=\rme^{-\rmi\gamma}\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
\]
the pair $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\psi_{2}}=\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}$
for ($0<\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$) or $\theta=0$
enumerate all possible orthonormal bases. Equation~(\ref{eq:non-additive-vectors})
can then be verified as follow. 
\begin{equation}
\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}\right)=\necess & \subseteq\likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & =\unlikely\tensor*[_{\mathscr{I}}]{+}{}\imposs=\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)=\likely & =\imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
\end{aligned}
\label{eq:case1}
\end{equation}
Similarly, when $\ket{\psi_{0}}$ is $\ket{\ps}$, equation~(\ref{eq:non-additive-vectors})
holds. 
\item When $\ket{0}\notin\mathcal{B}$ and $\ket{\psi_{0}}=\ket{0_{\theta,\gamma}^{\perp}}$
for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we want to
prove $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$.
Then, we have 
\begin{equation}
\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
\end{aligned}
\label{eq:case2}
\end{equation}
In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$,
it is sufficient to prove that if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
then ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or $\theta'=\frac{\pi}{2}$.
Recall $\ip{\ps}{\ps_{\theta',\gamma'}^{\perp}}=0$. Hence, if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
we have $\ket{\ps_{\theta',\gamma'}^{\perp}}$ parallel to $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$.
\begin{equation}
\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
1\\
0
\end{pmatrix}\times\begin{pmatrix}0\\
\rme^{\rmi\gamma}\sin\theta\\
\cos\theta
\end{pmatrix}=\begin{pmatrix}\cos\theta\\
-\cos\theta\\
\rme^{-\rmi\gamma}\sin\theta
\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
\cos\left(\frac{\pi}{2}-\theta\right)
\end{pmatrix}=\sqrt{2}\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\label{eq:case2-cross}
\end{equation}
Because of $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we have
($0<\theta'=\frac{\pi}{2}-\theta<\frac{\pi}{2}$ and $\pi\le\gamma'=\pi+\gamma<2\pi$)
or $\theta'=\frac{\pi}{2}-\theta=\frac{\pi}{2}$. Similarly, when
$\ket{\psi_{0}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$ and $\ket{\ps}\notin\mathcal{B}$,
equation~(\ref{eq:non-additive-vectors}) holds. 
\item Finally, when $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$,
$\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$, and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, i.e., the ``otherwise''
case. Then, equation~(\ref{eq:non-additive-vectors}) can easily
be verified. 
\begin{equation}
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right)=\likely\subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\label{eq:case3}
\end{equation}
\end{enumerate}
\footnote{This example is a little bit too long to human-verify, and
we need more examples. Maybe we need to write a program for further
verification.}
\end{example}

The following example verifies example~\ref{ex:three-dimensional-4-value}
cannot hold with more precise intervals.

\begin{example}[Three-dimensional quantum 4-value interval-valued
probability measure (Continue)]\label{ex:three-dimensional-4-value-1}
Consider $\mathscr{I}=\left\{ \imposs,\left[l_{1},r_{1}\right],\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right],\necess\right\} $,
where $\left[l_{1},r_{1}\right]$ and $\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]$
will be used to replace every $\unlikely$ and $\likely$ in example~\ref{ex:three-dimensional-4-value},
respectively. The bound of $l_{1}$ and $r_{1}$ can then be estimated
by the equations corresponding to equation~(\ref{eq:case1}), (\ref{eq:case2}),
and (\ref{eq:case3}).

When we replace $\unlikely$ and $\likely$ by $\left[l_{1},r_{1}\right]$
and $\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]$,
equation~(\ref{eq:case1}) will become

\begin{equation}
\begin{aligned}\necess & \subseteq\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
\left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\imposs\\
\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right] & \subseteq\imposs\tensor*[_{\mathscr{I}}]{+}{}\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]
\end{aligned}
\label{eq:case1-1}
\end{equation}
which are all tautologies. Equation~(\ref{eq:case2}) will become
\begin{equation}
\begin{aligned}\left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]
\end{aligned}
\label{eq:case2-1}
\end{equation}
which implies $l_{1}=0$. Finally, equation~(\ref{eq:case3}) will
become
\begin{equation}
\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]\subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\label{eq:case3-1}
\end{equation}
which implies $\frac{1}{2}\le r_{1}\le1$. Therefore, $l_{1}=0$ and
$r_{1}=\frac{1}{2}$ provides the most precise intervals which make
example~\ref{ex:three-dimensional-4-value} work, and in this case,
the intervals are $\left\{ \imposs,\unlikely,\likely,\necess\right\}
$.
\end{example}

Although it is easier to deduce an interval-valued probability measure
has an empty core by considering the state mapped to $\imposs$ as
in example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
it is not the only way to prove an interval-valued probability measure
has an empty core. The following family of interval-valued probability
measures satisfy that $\bar{\mu}\left(P\right)=\imposs$ if and only
if $P=\mathbb{0}$, but we can still prove them have empty cores.

Although it is easier to deduce an interval-valued probability measure
has an empty core by considering the state mapped to $\imposs$ as
in example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
it is not the only way to prove an interval-valued probability measure
has an empty core. The following family of interval-valued probability
measures satisfy that $\bar{\mu}\left(P\right)=\imposs$ if and only
if $P=\mathbb{0}$, but we can still prove them have empty cores.

%%%%%
\subsection{Proposed Activity II: Quantum Information Theorems}

Born
KS: Mermin-Meyer

%%%%%
\subsection{Proposed Activity III: Quantum States as Interactive Processes}

background III is classical; do quantum version; application to CS and
quantum information

may find surprises like we found with UNIQUE-SAT; not sure where that belongs

clear goals: KS with interval probability or with quantum states as
processes

talk about finite fields; previous work; unique-sat surprise; etc

... and quantum measurement expressed using game semantics

This is really about unifying classical and quantum theories of
measurement. One of the most well-developed and formalized theories of
classical measurement is the one for programming language
observational contextual equivalence.

This worldview can be maintained as long as the impact of the
measurements is really negligible on the execution time of the
functions of interest.

measurement affects runtime and hence affects other measurements;
could even conceive of programs whose input-output behavior is
affected by measurement

This intended level of abstraction is reflected in the first
line of the function declaration in Haskell. This \emph{interface} (or \emph{type}
or \emph{signature} or \emph{contract}) line:
\begin{quote}
\begin{verbatim}
square :: Int -> Int
\end{verbatim}
\end{quote}
summarizes the publicly stated, computationally relevant, aspects of the
function. In this case, it is announced that the function is a computer
realization of a pure mathematical map from one \verb|Int| to another. The
fact that executing the computer realization of the map on a particular input
might consume 10\% of the battery power on your laptop is something
that---although potentially critical knowledge in some circumstances---is not
even expressible in the notation above.

%%-------------------------------------
\subsection*{Partial Functions (Time)}

Computations take time. At some level of abstraction, we can ignore the time
taken by a computation. For example, we can pretend that a calculation that
takes one or two microseconds is similar to the ``instantaneous'' lookup in a
mathematical mapping. But we can hardly keep pretending this as the time used
by the calculation tends towards infinity.

Consider the following Java method:
\begin{quote}
\begin{verbatim}
int collatz (int n) {
  if (n == 1) return 0; 
  else if (n % 2 == 0) return 1 + collatz (n / 2);
  else return 1 + collatz (3 * n + 1);
}
\end{verbatim}
\end{quote}
As evident from the use of \verb|collatz| in the body of the method, this
method is \emph{recursive}. It takes an input number \verb|n| and:
\begin{itemize}
\item if the input number is equal to one, the method immediately stops with
the value zero, which represents in this case the total number of recursive
calls performed before stopping;
\item if the input number is even, the method divides it by two and
recursively invokes itself, adding one to the total number of recursive
calls;
\item if the input number is odd, the method multiplies it by three, adds
one, and then recursively invokes itself, after again adding one to the total
number of recursive calls.
\end{itemize}
It is a famous mathematical conjecture, \emph{the Collatz conjecture}, that
this calculation always terminates for all positive integers. One can quickly
check a few cases:
\begin{itemize}
\item invoking \verb|collatz(3)| iterates through 10, 5, 16, 8, 4, 2, 1, and
  then stops returning the result 7.
\item invoking \verb|collatz(17)| iterates through 52, 26, 13, 40, 20, 10, 5,
16, 8, 4, 2, 1, and then stops returning the result 12.
\end{itemize}

There is however no known proof that this method always stops. Thus, even
though the method has the same interface as the method \verb|square| above,
one may not be able to interpret the two interfaces in the same way. To
account for the possibility that the calculation never stops, the interface:
\begin{quote}
\begin{verbatim}
int collatz (int n)
\end{verbatim}
\end{quote}
should in general be read as saying:
\begin{quote}
Given a particular \verb|int| the method \emph{may or may not} return another
\verb|int| in a finite amount of time.
\end{quote}

Another way to look at the situation is that we have introduced ``time'' as
an implicit parameter of computations. Some computations as the method
\verb|square| update---as a side effect---this time parameter by consuming a
few ticks. By general agreement, this consumption is deemed negligible and
not ``observable'' and does not generally constitute a computational
effect. But when the consumption of time is unbounded, it arguably becomes an
observable computational effect.

%%-------------------------------------
\subsection*{Assignments (Memory)}

Computations require memory. Again, at some level of abstraction we can
pretend that memory does not exist. But what happens if a computation
starts changing external memory locations?

Consider the following variant of the method \verb.square.:
\begin{quote}
\begin{verbatim}
int square (int n) {
  count++;
  return n * n;
}
\end{verbatim}
\end{quote}
As before, the method takes an integer \verb.n. from the domain of Java
integers \verb.int. and returns another integer whose value is the square of
the input. But, as a side effect the method reads and updates an external
reference \verb.count., which can be used to find out how many times the
method was called. Thus if during the execution of a particular program the
method \verb.square. is called ten times, then the value of \verb.count. will
be ten.

Thus the interface:
\begin{quote}
\begin{verbatim}
int square (int n)
\end{verbatim}
\end{quote}
should now be read as saying:
\begin{quote}
Given a particular \verb|int| the method \emph{may possibly} read and update
external memory references and then it \emph{may or may not} return another
\verb|int| in a finite amount of time.
\end{quote}

Another way to look at the situation is that we have introduced ``memory'' as
an implicit parameter of computations. Some computations as the original
method \verb|square| might---as a side effect---allocate, update, and read
several memory locations (registers, cache entries, stack frames, etc.). By
general agreement, these actions on memory are not considered observable and
do not generally constitute a computational effect. But when a computation
updates an external memory location that other program fragments can inspect,
the update of the memory location becomes an observable computational effect.

%%-------------------------------------
\subsection*{Runtime Exceptions (Context)}

Computations occur in a context. When a computation occurs in the context of
a larger computation, it is typically expected to return its result to that
outer computation. But what if a computation cannot return a sensible value
to its context and decides instead to abort it?

Consider again the method \verb|square| whose interface is:
\begin{quote}
\begin{verbatim} 
int square (int n)
\end{verbatim}
\end{quote}
We initially argued that it is possible to interpret this interface to say
that given a particular \verb|int| the method's execution promises to return
another \verb|int|. This is clearly an idealized view: in real life, any of
an unlimited number of failures may occur in the hardware or underlying
software components including the operating system or the Java virtual
machine. The Java language collectively refers to these conditions as
\verb|Error|s or \verb|RuntimeException|s.

So to be more accurate, and putting together our observations so far, one
should interpret the interface:
\begin{quote}
\begin{verbatim} 
int square (int n)
\end{verbatim}
\end{quote}
as saying:
\begin{quote}
Given a particular \verb|int| the method \emph{may possibly} read and
update external references, and then it \emph{may or may not} return another
\verb|int| in a finite time or it \emph{may fail to return to its context}
due to any of a number of errors and runtime exceptions.
\end{quote}

Another way to look at the situation is that we have introduced the
``context'' as an implicit parameter of computations. It is expected that
every inner computation would resume its context with its result. But when an
inner computation encounters a fatal error condition, it can ignore the
context parameter, which causes the error condition to immediately terminate
the entire computation. This escape clearly constitutes an observable
computational effect.

%%-------------------------------------
\subsection*{Other Computational Effects}

The unifying theme in all the above effects is that computations do not
happen in isolation in some abstract mathematical world: rather computations
are realized in some physical computing platform. The physical interactions
of a computation with the computing platform and with other computations may
be ignored in some idealized situation corresponding to simple computations,
but they become crucial if one is interested in modeling the actual behavior
of a sophisticated realistic computation. If these interactions happen
``behind the scene'' they are considered side effects of the computation.

Without further constraints on computations and their contexts, it is
impossible to enumerate all the possible side effects that a computation may
have. The reader may find it instructive to consider the following list of
effects that could be performed by a method with the interface:
\begin{quote}
\begin{verbatim} 
int square (int n)
\end{verbatim}
\end{quote}
Given a particular \verb|int|, the method's behavior may include various
combinations of the following actions:
\begin{itemize}
\item Reading and updating external memory locations, environment parameters,
local or remote file systems or databases, etc.
\item Communicating with a user or another local or remote process.
\item Suspending itself for a certain period of time or until a certain
outside condition happens.
\item Resuming other suspended computations.
\item Loading, compiling, and executing some other computation.
\item Using reflection to examine and perhaps modify its own machine
representation.
\item Producing multiple answers by arranging for one \verb|int| to be
returned now and subsequent answers to be returned when the method is called
again (with the same parameters). 
\item Checkpointing its entire state to a log, which can be examined and
resumed later.
\item Failing due to any of a number of errors and runtime exceptions.
\item Consuming half of the battery life of a laptop and generating enough
heat to keep you warm on a cold winter night.
\end{itemize}
And yes by the way, the method may actually return another \verb|int| in a
finite amount of time.

It is clear that the method's interface is nowhere close to giving us a
reasonable approximation of the possible behaviors of the method: it sweeps
too many things under the rug. Pragmatically, if a programmer invokes a
method with the interface:
\begin{quote}
\begin{verbatim} 
int square (int n)
\end{verbatim}
\end{quote}
the implicit computational effects of the method might come as a
surprise.

The situation is not unique to Java. Almost every other programming
language allows similar computational effects to occur
implicitly. Even hardware circuits and assembly language instructions
often perform implicit effects. For example, an assembly instruction
might change the contents of the flag register as a side effect. In
fact natural languages also include various ``non-compositional
phenomena,'' which are essentially computational effects. For this
reason, programmers are universally taught to avoid side effects if
possible and to be careful when analyzing code that might contain side
effects. But when side effects are unavoidable, the solution is to
\emph{expose them} as the rest of the article explains.

Common wisdom is that classical physics has no randomness. Only
ignorance of the fine details or lack of control over them causes
\emph{statistical randomness}. In principle, but not in practice,
randomness is absent from classical physics.

In sharp contrast, quantum randomness is unavoidable even in principle.

But but but ... Nature is one. The distinction between ``classical''
and ``quantum'' can only be in our minds, or more precisely in our
mathematical models of the universe. We have two mathematical models,
one which is, in principle deterministic, and one which is
probabilistic. Nature must really be one or the other.

Consider this unsettling quote from QBism:

\begin{quote} 
Instead, the wavefunction obeys two fundamentally different laws:
\begin{enumerate}
\item As long as the electron is left to its own devices unobserved
  its wavefunction unfolds smoothly, continuously, and predictably. It
  obeys fixed mathematical laws, just like a bullet in flight and a
  wave on a lake.
\item When the electron reveals its whereabouts by leaving a dot on a
  screen, the wavefunction ``collapses'' suddenly into a new much more
  compact form concentrated on the point of impact.
\end{enumerate}

\end{quote}

Can we develop a mathematical model that unifies both the classical
deterministic perspective and the quantum probabilistic perspective?
Quantum information and quantum computation opens the door to using
computational insights. The main one is that, in a computation,
everything produced during a computation and everything observed about
a computation is finite. The computational perspective imposes a
principle we might call the principle of ``finitely communicable
evidence.''

So imprecision in classical physics becomes, not some second-class
principle that is considered to stem from practical limitations but
rather a foundational principle. If everything is ``fuzzy'' so to
speak and if our mathematical models embrace this fuzziness then a
different worldview emerges. That worldview agrees with classical
physics but embraces imprecision within the mathematical model not as
an external non-mathematical nuisance. This shift in perspective
enables a smooth transition to the world of quantum physics since our
mathematical model has already embraced probabilistic effects.

Three insights:

\begin{itemize}
\item Interactive systems: response of quantum system determined
  \emph{after} the observer initiates the experiment used to observe
  the system
\item Bayesian probability, personal
\item Finite precision
\end{itemize}

Goal: build computational model of QM that encompasses classical
(reversible), computation and observation with finite resources, and
hopefully revolutionize ``quantum thinking''

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Broader Impact and Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PI Team and Prior NSF Support}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliographystyle{acm}
\bibliography{prop}
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-11-24 proposal/summary.tex
proposal

\documentclass[11pt]{article}
\usepackage{fullpage}
\begin{document}
\pagestyle{empty}

\centerline{\Large\textbf{Project Summary}}
\medskip

\paragraph*{Overview.} This is a \emph{theoretical} investigation of
\emph{experimental} physics using \emph{computational methods}. All
experiments and computations are processes bounded in space, time, and
other resources. Yet, for centuries, the mathematical formalization of
such processes has been founded on the infinitely precise real or
complex numbers. Indeed, almost every description of quantum
mechanics, quantum computation, or quantum experiments refers to
entities such as $e$, $\pi$, $\sqrt{2}$, etc. From a computational
perspective, such numbers do not exist in their entirety ``for free.''
One must expand increasingly large resources to represent such numbers
more and more accurately.

We propose to revisit quantum mechanics, quantum information, and
quantum computation from this resource-aware perspective that is at
the core computer science. Instead of starting with
infinitely-specified but not directly observable quantum states, we
focus on observable measurable properties of quantum systems and their
probabilities. Furthermore, we insist that our theories of measurement
and probability only refer to finitely communicable evidence within
feasible computational bounds. It follows that states, observations,
and probabilities all become ``fuzzy'', i.e., specified by intervals
of confidence that can only increase in precision if the available
resources increase proportionally.

\paragraph*{Proposed Activities.} We propose to develop a complete
computational model of quantum mechanics from a computational
perspective with the salient property that every entity of interest
must be finite and efficiently computable with feasible
resources. This point of view entails somewhat radical, but
well-justified, choices: quantum states disappear as a separate
reality and are replaced by interactive systems (not unlike a web
server for a crude but useful analogy). The observable properties of
such an interactive system are local to each independent observer
(client) and totally depend on the amount of resources available to
the observer and past interactions with that particular observer. We
anticipate any positive results to strongly influence the design of
potential quantum computers and negative results to guide this search
towards fruitful approaches.

\paragraph*{Intellectual Merit.} Despite over one hundred years of
history, the \emph{how} of quantum mechanics remains a mystery. We
argue that the revolution in quantum computing will only happen when
we \emph{understand} the inner working of quantum mechanics. How
exactly is quantum information processed by Nature? Our proposal
directly attacks this questions and aims at providing positive or
negative answers to various algorithmic approaches for quantum
information processing, and resolving many intellectual paradoxes
along the way. The key foundation we aim to completely solve is to
revise the entire framework to be based on finite communicable pieces
of information.

\paragraph*{Broader Impact.} This project will have broader impacts
with respect to technology transfer, education, and outreach. Quantum
properties are keys to the future of computing and communication with
several governments and major industrial companies heavily invested in
harnessing them. It is also a source of constant intrigue attracting
the interest of students and professionals at large.

\paragraph*{Key Words:} \textbf{probability; Bayes; measurement;
  algebra; finite fields; algorithmic complexity; models of
  computation; interpretations of quantum mechanics.}

\end{document}

### 2016-11-24 proposal/H.hs

@@ -1,0 +1,27 @@
+module H where
+
+import System.Microtimer
+
+-- square :: Integer -> Integer
+-- square n = n * n
+
+pow :: Integer -> Integer -> Integer
+pow a 0 = 1
+pow a b = a * pow a (b-1)
+
+pow' :: Integer -> Integer -> Integer
+pow' a 0 = 1
+pow' a 1 = a
+pow' a b | even b = pow' (a * a) (b `div` 2)
+pow' a b | odd b = a * pow' a (b-1)
+
+timing f a b =
+  do s <- time_ $ print (f a b)
+     putStrLn (formatSeconds s)
+
+-- timing pow 2 10000
+-- 27.31109 ms
+
+-- timing pow' 2 10000
+-- 11.72614 ms
+

### 2016-11-24 proposal/prop.tex
prop.aux

@@
 probability measure $\mu_{\phi}^{B}$ defined as
-$\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}$. Conversely every probability
-measure must be of this shape (accounting for the generalization to
-mixed states).
+$\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}$. The situation generalizes to
+mixed states $\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
+$\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born rule
+induces a probability measure $\mu_{\rho}^{B}$ defined
+as follows~\cite{peres1995quantum,544199,Jaeger2007}:
+\[
+\mu_{\rho}^{B}\left(P\right) = 
+\Tr\left(\rho P\right) = 
+\sideset{}{_{j=1}^{N}}\sum q_{j}\mu_{\phi_{j}}^{B}\left(P\right)
+\]
+Conversely every probability measure must be of this form.
 

### 2016-11-24 proposal/collab.tex

\documentclass[11pt]{article}
\usepackage{fullpage,times,url}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\Large {\bf Collaborators}}
\end{center}

\begin{itemize}
\item Recent collaborators:
  Thorsten Altenkirch (University of Nottingham),
  Zena M. Ariola (University of Oregon),
  Aaron Bohannon (University of Pennsylvania),
  Jacques Carette (McMaster University),
  Ant\^onio Carlos da Rocha Costa (Univ. Cat\'olica de Pelotas, Brazil),
  Andr\'e Rauber Du Bois (Heriot-Watt University),
  Ronald Garcia (University of British Columbia),
  Jonathan Grattage (Universit\'e de Grenoble),
  Hugo Herbelin (INRIA, Futurs),
  Oleg Kiselyov,
  Giovani Rubert Librelotto (Universidade Federal de Santa Maria),
  Andrew Lumsdaine (Indiana University),
  Chung-chieh Shan (Rutgers),    
  Juliana Kaizer Vizzotto (Universidade Federal de Santa Maria).

\item Graduate and Postdoctoral Advisors: Matthias Felleisen (Northeastern
  University), Corky Cartwright (Rice University), and John Hughes (Chalmers
  University, Sweden)

\item Thesis Advisor and Postgraduate-Scholar Sponsor: 
    Roshan James (Jane Street) 
    John Fiskio-Lasseter (Lewis and Clark College), 
    Yevgeniy Makarov,
    Bart Massey (Portland State University),
    Juliana Kaizer Vizzotto (Universidade Federal de Santa Maria),
    Bennett Yates.

\end{itemize}

\end{document}

### 2016-11-24 proposal/fac.tex

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{amsfonts, verbatim}
\usepackage{proof}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{comment}
\usepackage{natbib}
\usepackage{url}
\usepackage{cmll}
\usepackage{bussproofs}
\usepackage{bbold}
\bibpunct();A{},
\bibliographystyle{plainnat}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Environments

\newenvironment{code}{\verbatim}{\endverbatim}
\newenvironment{smallcode}{\verbatim}{\endverbatim}
\newenvironment{verysmallcode}{\scriptsize\verbatim}{\endverbatim\normalsize}
\newtheorem{thm}{Theorem}[section]
\newtheorem{definition}[thm]{Definition}
\newtheorem{proposition}[thm]{Proposition}
\newtheorem{example}[thm]{Example}

%% Commands

\newcommand{\hide}[1]{}
\newcommand{\zeroH}{\mathbb{0}}
\newcommand{\oneH}{\mathbb{1}}
\newcommand{\alt}{~|~} 
\newcommand{\liftt}[1]{\llbracket #1 \rrbracket}
\newcommand{\ie}{\textit{i.e.}\xspace}
\newcommand{\eg}{\textit{e.g.}\xspace}
\newcommand{\QM}{QM}
\newcommand{\blob}{\rule[.2ex]{1ex}{1ex}}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 \alt #2 \rangle}
\newcommand{\op}[2]{|#1\rangle\langle #2|}
\newcommand{\expect}[2]{\langle #1 \alt #2 \alt #1 \rangle}
\newcommand{\Nat}{\mathbb{N}}
\newcommand{\inleft}[1]{\textsf{inL}~#1}
\newcommand{\inright}[1]{\textsf{inR}~#1}
\newcommand{\fst}[1]{\textsf{fst}~#1}
\newcommand{\snd}[1]{\textsf{snd}~#1}
\newcommand{\scalarZ}{\texttt{impossible}}
\newcommand{\scalarO}{\texttt{possible}}
\newcommand{\norm}[1]{||#1||}
\newcommand{\scalarPlus}{\ensuremath{\oplus}}
\newcommand{\scalarTimes}{\ensuremath{\wedge}}
\newcommand{\vect}[1]{\overline{#1}}
\newcommand{\dvect}[1]{\overline{\overline{#1}}}
\newcommand{\ltree}{\swarrow}
\newcommand{\rrtree}{\begin{array}{c@{\hspace{-0pt}}c}\searrow\\&\searrow\end{array}}
\newcommand{\rltree}{\begin{array}{c@{\hspace{-7pt}}c}\searrow\\&\swarrow\end{array}}

\newcommand{\todo}[1]{\textbf{TODO}: #1}
\newcommand{\note}[1]{\textsc{\textbf{NOTE: #1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Facilities, Equipment, and Other Resources at Indiana University}
\author{}
\date{}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent There are substantial central computing resources offered by
the University: our cyberinfrastructure is rated in the top 10 in the
U.S, and includes the Big Red cluster (30 TeraFlops), the Quarry
cluster (9 TeraFlops, general-purpose Unix computing), and supports
TeraGrid, I-Light, and the Open Science Grid. Dr. Ortiz (Department of
Physics) and Dr. Sabry (School of Informatics and Computing) have
access to departmental license software, as well as access to most
electronic and hard copy journals through Indiana University
Libraries, and access to conference facilities for meetings.

\bigskip
\centerline{\Large{\underline{Department of Physics}}}
\bigskip

\noindent A computer server facility specifically serving the Departments of
Physics and Astronomy is installed in the basement of Swain Hall. This $\sim
110~m^2$ room has sufficient power and cooling capacity to house 24 racks of
hardware in a single area for ease of security and maintenance resulting in a
high-quality, small-scale facility meeting local needs. In addition to the
ATLAS/DØ Tier-3 Analysis Cluster (22 eight-core 2.66/2.88 GHz Xeon nodes, >60
TB of raid disk storage), it also houses experimental computing for lattice
gauge and related calculations, the special partial-wave computing facility
for the GlueX experiment (including both regular nodes and an experimental
GPU cluster), computing access for the neutrino group, and servers for the
Physics and Astronomy Departments. Finally, it also provides an appropriate
home for interfaces to hardware such as IU\u2019s Data Capacitor, a
large-scale data storage/access system developed by Indiana University IT
Services and used heavily by Astronomy.  Indiana University and the
University of Chicago jointly manage the Midwest Tier2 (MWT2) computing
center, with hardware split approximately equally between them. The Indiana
University portion of the MWT2 is located primarily in Indianapolis on the
campus of Indiana University Purdue University Indianapolis
(IUPUI). Currently the IUPUI portion of the MWT2 has 1.8M kSi2k of computing
power and ~200 TB of storage. The CPUs are various AMD and Intel processors
purchased from several vendors \u2013 a total of 768 cores at IUPUI with
approximately 2 GB of memory per core. A 1 Gb/s link connects each compute
node to the Indiana University backbone while storage nodes are connected to
the backbone with 10 Gb/s connections. The MWT2 is connected to the outside
world with a 10 Gb/s link.  In addition to the usual desktop units, a
dedicated room is available containing projection units and a high-definition
Polycom videoconferencing unit recently acquired using DoE stimulus
funds. The Department has also requested renovation of a different space to
house this system as well as other equipment for use in distance learning.

\bigskip
\centerline{\Large{\underline{School of Informatics and Computing}}}
\bigskip

\noindent The School of Informatics and Computing maintains a highly
distributed, heterogeneous, networked computing environment consisting of
UNIX/Linux, Windows, and Macintosh workstations and servers across 3 primary
facilities (2 auxiliary). This includes over 250 Linux workstations/servers,
over 450 Windows workstations/servers and over 150 Apple
workstations/servers. There are 3 Linux clusters (128-node dual Opteron,
16-node dual Opteron, and 8-node dual Xeon) to support School
research. Additionally, there are 2 dedicated virtual machine servers
available to host VMs for both research and instruction.

The network infrastructure at the School provides 1000Mbps gigabit ethernet
connections to all servers and most workstations and as well as 802.11a/b/g
wireless connectivity. The facilities have 1 gigabit or greater connectivity
(one facility has 10 gigabit) with campus and research backbones which
provides high-speed access to university and worldwide computing resources.

Special-purpose teaching and instructional labs are provided, including 2
electronic classrooms (24-seat, 48-seat), hardware laboratories, and 4
multi-purpose Linux and Windows laboratories to support the course work for
both undergraduate and graduate students.  There are 4 rooms (2 classrooms)
within the School enabled with video conferencing technology that can be used
for both distance education and research collaboration.

The School maintains 10 full time staff members dedicated to IT
infrastructure and facilities with the mission of enabling world class
research and instruction

\end{document}

### 2016-11-24 proposal/prop.tex

@@
 can only end up containing \verb|2| or \verb|3|. The lesson, phrased
-in physics terms, is that it not sensible to think of the properties
+in physics terms, is that it is not sensible to think of the properties
 of a system (like \verb|P1| or \verb|P2|) independently of the
-observer (\verb|Q| in this case).
+observer (\verb|Q| in this case). Indeed the observation \verb|x=4|
+cannot said to have an independent existence independently from the
+interaction between \verb|P1| and \verb|Q|: it really emerges or is
+created as part of the observation process and is not a pre-existing
+``element of reality''.
 
@@
   our first radical departure from the classical case will be that the
-  quantum state itself must be fuzzy in some sense to be formalized.
+  quantum state itself must be fuzzy in some sense to be
+  formalized. In other words, does a Gleason, Bell, or Kochen-Specker
+  theorem still hold in a world with finite resources?
 

### 2016-11-25 proposal/amr-bio.tex
proposal\amr-bio.tex Upgraded to bibLaTeX to automatically put erratum in...

@@
 \usepackage{fullpage,times,url}
+\usepackage[utf8]{inputenc}
+\usepackage[ backend=biber]{biblatex}
+\addbibresource{prop.bib}
+\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Closely Related Publications}
-
-\begin{enumerate}
-
-\item Andrew J. Hanson, Gerardo Ortiz, Amr Sabry, and Yu-Tsung
-  Tai. ``Discrete Quantum Theories.'' In \emph{J. Phys. A: Math. Theor.},
-  \textbf{47}, 2014.
-
-\item Andrew J. Hanson, Gerardo Ortiz, Amr Sabry, and Yu-Tsung Tai,
-  ``Geometry of Discrete Quantum Computing.'' In \emph{J. Phys. A:
-  Math. Theor.}, \textbf{46}, 2013.
-
-\item Juliana K. Vizzotto, Andr\'e Rauber Du Bois, and Amr Sabry, ``The Arrow
-  Calculus as a Quantum Programming Language,'' In the \emph{Workshop on Logic,
-  Language, Information and Computation}, 2009.
-
-\item Thorsten Altenkirch, Jonathan Grattage, Juliana K. Vizzotto, and Amr
-  Sabry, ``An Algebra of Pure Quantum Programming.'' In the \emph{Workshop on
-  Quantum Programming Languages}, 2005. Final version in the \emph{Electronic
-  Notes in Theoretical Computer Science}, vol. 170, pp. 23-47, 2007.
-
-\item Juliana K. Vizzotto, Thorsten Altenkirch, and Amr Sabry, ``Structuring
-  Quantum Effects: Superoperators as Arrows.''  \emph{Mathematical Structures
-    in Computer Science} (MSCS), Volume 16, Issue 03, pages 453-468, June
-  2006.
-
-\end{enumerate}
+\nocite{DQT2014, geometry2013, VDS2009, AGVS2005, VAS2006}
+\printbibliography[title={Closely Related Publications}]
 

### 2016-11-25 proposal/prop.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background III: From Functions to Interactive Processes}
+\section{Proposal: General Plan}
+
+A major aim of this proposal is to recast quantum probability and
+measurement in a computational resource-aware setting. Our vision is
+to unify the strands above in a novel way as explained in this
+section. We start with some immediate observations that justify the
+rest of the development.
+
+\begin{itemize}
+
+\item If we insist that probabilities cannot be infinitely precise and
+  are bound to be approximations represented by intervals of
+  confidence, then by Gleason's theorem, quantum states themselves
+  cannot be infinitely precise. This raises an important philosophical
+  question with immense practical relevance in the context of quantum
+  computing. The question, which we could largely bypass in the
+  classical case, is whether there is, in the background of all the
+  measurements and probabilities, a ``real'' infinitely-precise
+  quantum state that is being approximated and that, in principle, can
+  be more and more accurately described given more and more
+  resources. The answer will have to be \emph{no} if we are to respect
+  major theorems of quantum mechanics and quantum information. Thus
+  our first radical departure from the classical case will be that the
+  quantum state itself must be fuzzy in some sense to be
+  formalized. In other words, does a Gleason, Bell, or Kochen-Specker
+  theorem still hold in a world with finite resources?
+
+\item Going further we actually have to concede not just the infinite
+  accuracy of the quantum state, but its very existence as a ``real''
+  entity that exists independently of measurements and
+  probabilities. The reasons for this radical position are as
+  follows. First arguments embedded in the proof of the Kochen-Specker
+  theorem essentially rule out the existence of a sample space as the
+  probabilities of events cannot be consistently expressed using core
+  assignments to elements of the sample space. Second, the frequency
+  interpretation of probability which is already problematic in the
+  classical case, becomes untenable in the quantum case. In both
+  cases, but much more in the quantum case, it is much more sensible
+  to interpret probability in the Bayesian sense as ``lack of
+  knowledge''. This, and similar arguments elegantly expressed by
+  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016},
+  suggest that the quantum state is more like an interactive system in
+  computer science parlance. In other words, the state is only
+  determined by its interactions with the environment or observers. A
+  rough but useful analogy in the context of computer science would be
+  a web server: the state of such a system cannot be said to exist
+  independently of the interactions with clients; each interaction
+  with a client determines a future state of the system and may affect
+  future interactions. Crucially, each client may have a
+  \emph{different} view of the web server that is consistent with
+  their own history of interactions. This computational perspective
+  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
+  that asserts that the quantum state is subjective: each observer has
+  a different view of the quantum system that is consistent with their
+  previous observations and that allows that observer, independently
+  of other observers, to assign beliefs (i.e., probabilities) to
+  future interactions.
+
+\end{itemize}
+
+%%%%
+\subsection{Proposed Activity I: Quantum States as Interactive Processes}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proposal: General Plan}
-
-A major aim of this proposal is to recast quantum probability and
-measurement in a computational resource-aware setting. Our vision is
-to unify the strands above in a novel way as explained in this
-section. We start with some immediate observations that justify the
-rest of the development.
-
-\begin{itemize}
-
-\item If we insist that probabilities cannot be infinitely precise and
-  are bound to be approximations represented by intervals of
-  confidence, then by Gleason's theorem, quantum states themselves
-  cannot be infinitely precise. This raises an important philosophical
-  question with immense practical relevance in the context of quantum
-  computing. The question, which we could largely bypass in the
-  classical case, is whether there is, in the background of all the
-  measurements and probabilities, a ``real'' infinitely-precise
-  quantum state that is being approximated and that, in principle, can
-  be more and more accurately described given more and more
-  resources. The answer will have to be \emph{no} if we are to respect
-  major theorems of quantum mechanics and quantum information. Thus
-  our first radical departure from the classical case will be that the
-  quantum state itself must be fuzzy in some sense to be
-  formalized. In other words, does a Gleason, Bell, or Kochen-Specker
-  theorem still hold in a world with finite resources?
-
-\item Going further we actually have to concede not just the infinite
-  accuracy of the quantum state, but its very existence as a ``real''
-  entity that exists independently of measurements and
-  probabilities. The reasons for this radical position are as
-  follows. First arguments embedded in the proof of the Kochen-Specker
-  theorem essentially rule out the existence of a sample space as the
-  probabilities of events cannot be consistently expressed using core
-  assignments to elements of the sample space. Second, the frequency
-  interpretation of probability which is already problematic in the
-  classical case, becomes untenable in the quantum case. In both
-  cases, but much more in the quantum case, it is much more sensible
-  to interpret probability in the Bayesian sense as ``lack of
-  knowledge''. This, and similar arguments elegantly expressed by
-  recent work on Quantum Bayesianism~\cite{}, suggest that the quantum
-  state is more like an interactive system in computer science
-  parlance. In other words, the state is only determined by its
-  interactions with the environment or observers. A rough but useful
-  analogy in the context of computer science would be a web server:
-  the state of such a system cannot be said to exist independently of
-  the interactions with clients; each interaction with a client
-  determines a future state of the system and may affect future
-  interactions. Crucially, each client may have a \emph{different}
-  view of the web server that is consistent with their own history of
-  interactions. This computational perspective agrees with the
-  philosophical position of QBism that asserts that the quantum state
-  is subjective: each observer has a different view of the quantum
-  system that is consistent with their previous observations and that
-  allows that observer, independently of other observers, to assign
-  beliefs (i.e., probabilities) to future interactions.
-
-\end{itemize}
+do quantum version; application to CS and quantum information
 
 %%%%%
-\subsection{Proposed Activity I: Quantum Interval-valued Probability Measures}
+\subsection{Proposed Activity II: Quantum Interval-valued Probability Measures}
 
@@
 %%%%%
-\subsection{Proposed Activity II: Quantum Information Theorems}
+\subsection{Proposed Activity III: Quantum Information Theorems}
 
@@
 %%%%%
-\subsection{Proposed Activity III: Quantum States as Interactive Processes}
-
-background III is classical; do quantum version; application to CS and
-quantum information
+\subsection{Proposed Activity IV: Computational Aspects}
 

### 2016-11-25 proposal/amr-bio.tex
amr-bio.tex Finish putting everything into bibLaTeX...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{refsection}
 \nocite{DQT2014, geometry2013, VDS2009, AGVS2005, VAS2006}
 \printbibliography[title={Closely Related Publications}]
+\end{refsection}
 
-\section*{Other Significant Publications}
-
-\begin{enumerate}
-
-\item Jacques Carette and Amr Sabry, ``Computing with Semirings and Weak Rig
-  Groupoids.'' In the \emph{European Symposium on Programming}, ESOP 2016.
-
-\item Roshan P. James and Amr Sabry, ``Information Effects.'' In the
-  \emph{Conference Record of the ACM Symposium on Principles of Programming
-  Languages}, 2012.
-
-\item Amr Sabry, ``Side Effects.'' In \emph{Wiley Encyclopedia of Computer
-  Science and Engineering, 5-Volume Set}, Volume 4, pages 2534-2543, Benjamin
-  W. Wah (Editor), Hoboken: John Wiley \& Sons, Inc, January 2009.
-
-\item Eugenio Moggi and Amr Sabry: Monadic encapsulation of effects: 
-a revised approach (extended version). \emph{J. Funct. Program.} 11(6):
-591-627 (2001)
-
-\item Cormac Flanagan, Amr Sabry, Bruce F. Duba, and Matthias Felleisen:
-The Essence of Compiling with Continuations. In the Proceedings of the ACM
-SIGPLAN Conference on Programming Language Design and Implementation, pages
-237-247, 1993. \emph{Selected as one of the best 50 PLDI papers from
-1979-1999.}
-\end{enumerate}
+\begin{refsection}
+\nocite{CaretteSabry2016, JamesSabry2012, Sabry2009, MoggiSabry2001, FSDF1993}
+\printbibliography[title={Other Significant Publications}]
+\end{refsection}
 

### 2016-11-25 proposal/prop.tex
prop.tex \section{Overview, Objectives, and Expected Significance} Cite Meyer-Mermin...

@@
 resource-aware setting. In particular, we plan on addressing the
-Meyer-Mermin debate~\cite{} on the impact of finite precision
+Meyer-Mermin debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004}
+on the impact of finite precision
 measurements on the relevance of the Kochen-Specker theorem. We argue

### 2016-11-25 proposal/prop.tex
prop

@@
 resource-aware setting. In particular, we plan on addressing the
-Meyer-Mermin debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004}
-on the impact of finite precision
-measurements on the relevance of the Kochen-Specker theorem. We argue
-that no matter what the results are their impact will be
-strong. Positive results that formulate a computable, with clear
-resource bounds, theory of quantum measurement and quantum probability
-would be essential for understanding and realizing quantum
-computation. Any negative results would redirect research that aims at
-realizing quantum computation to other approaches. At an intellectual
-level, the results will solve or clarify several paradoxes in quantum
-mechanics, quantum information, computability, and complexity theory.
+Meyer-Mermin debate~\cite{PhysRevLett.83.3751, Mermin1999,
+  BarrettKent2004} on the impact of finite precision measurements on
+the relevance of the Kochen-Specker theorem. We argue that no matter
+what the results are their impact will be strong. Positive results
+that formulate a computable, with clear resource bounds, theory of
+quantum measurement and quantum probability would be essential for
+understanding and realizing quantum computation. Any negative results
+would redirect research that aims at realizing quantum computation to
+other approaches. At an intellectual level, the results will solve or
+clarify several paradoxes in quantum mechanics, quantum information,
+computability, and complexity theory.
 
@@
   be more and more accurately described given more and more
-  resources. The answer will have to be \emph{no} if we are to respect
-  major theorems of quantum mechanics and quantum information. Thus
-  our first radical departure from the classical case will be that the
-  quantum state itself must be fuzzy in some sense to be
-  formalized. In other words, does a Gleason, Bell, or Kochen-Specker
-  theorem still hold in a world with finite resources?
+  resources. In other words, does a Gleason, Bell, or Kochen-Specker
+  theorem still hold in a world with finite resources?  The answer
+  will have to be \emph{no} if we are to respect these major theorems
+  of quantum mechanics and quantum information. Thus our first radical
+  departure from the conventional case will be that the quantum state
+  itself must be fuzzy in some sense to be formalized.
 
@@
   entity that exists independently of measurements and
-  probabilities. The reasons for this radical position are as
+  probabilities. The reasons for this second radical position are as
   follows. First arguments embedded in the proof of the Kochen-Specker
@@
   of other observers, to assign beliefs (i.e., probabilities) to
-  future interactions.
+  possible future interactions.
 
@@
 computed function existed independently of any observation,
-calculation, or interaction. An agent can only interact with the
-computation by asking questions regarding its input-output behavior
-and although such interaction would reveal fragments of the computed
-function it could not change it or affect it in any way.
+calculation, or interaction. For example, a function is
+\emph{injective} or not independently of any observation. An agent can
+only interact with the computation by asking questions regarding its
+input-output behavior and although such interaction would reveal
+fragments of the computed function and its innate properties it could
+not change it or affect it in any way.
 
@@
 merely an extension of the repertoire of entities and constructions
-which explain sequential computing.'' He gives the following simple
-but compelling example. Consider the following two programs:
+which explain sequential computing.'' In his Turing Award lecture, he
+gives the following simple but compelling example. Consider the
+following two programs:
 \begin{verbatim}
@@
 the one that maps an input memory to an updated memory in which the
-location named \verb|x| is assigned the value \verb|2|. But place the
+location named \verb|x| is assigned the value \verb|2|. An observer
+with the ability of inquire about the value of \verb|x| at the end of
+the computation cannot distinguish the two programs. But place the
 programs in an environment which may involve interactions and the
-equivalence is lost. Concretely, place each of the two programs
-concurrently with the program:
+equivalence is lost. Phrased in physical terms, give the observer the
+additional ability to access the location \verb|x| \emph{during} the
+computation, not just to observe its final value. In computing terms,
+we place each of the two programs \verb|P1| and \verb|P2| concurrently
+with the program:
 \begin{verbatim}
@@
 \end{verbatim}
-and we can observe the following. In the combined system of \verb|P1|
-and \verb|Q| running concurrently, the location \verb|x| may end up
-containing \verb|2|, \verb|3|, or \verb|4|. But in the combined system
-of \verb|P2| and \verb|Q| running concurrently, the location~\verb|x|
-can only end up containing \verb|2| or \verb|3|. The lesson, phrased
-in physics terms, is that it is not sensible to think of the properties
-of a system (like \verb|P1| or \verb|P2|) independently of the
-observer (\verb|Q| in this case). Indeed the observation \verb|x=4|
-cannot said to have an independent existence independently from the
-interaction between \verb|P1| and \verb|Q|: it really emerges or is
-created as part of the observation process and is not a pre-existing
-``element of reality''.
+In the combined system of \verb|P1| and \verb|Q| running concurrently,
+the location \verb|x| may end up containing \verb|2|, \verb|3|, or
+\verb|4|. But in the combined system of \verb|P2| and \verb|Q| running
+concurrently, the location~\verb|x| can only end up containing
+\verb|2| or \verb|3|. The lesson, phrased in physics terms, is that it
+is not sensible to think of the properties of a system (like \verb|P1|
+or \verb|P2|) independently of the observer (\verb|Q| in this
+case). Indeed the observation \verb|x=4| cannot said to have an
+existence independently from the interaction between \verb|P1| and
+\verb|Q|: it really emerges or is created as part of the observation
+process and is not a pre-existing ``element of reality''.
 
@@
 
-do quantum version; application to CS and quantum information
+\paragraph*{Research Question.} Is it possible to adapt the theory of
+observation of concurrent processes to the study of quantum states and
+confirm that the observations exhibit the same Bell-like correlations?
+
+\paragraph*{Research Question.} The theory of observation of
+concurrent processes and the theory of measurement in quantum
+mechanics are superficially different. Is it possible to reformulate
+them in a common language to benefit each theory from insights in the
+other?
 

### 2016-11-25 proposal/prop.tex
prop

@@
 mechanics are superficially different. Is it possible to reformulate
-them in a common language to benefit each theory from insights in the
-other?
+them in a common language to benefit each theory from insights derived
+from the other theory?
+
+\paragraph*{Research Question.} Does the computational and hence
+\emph{testable} hypothesis that the quantum state is nothing but an
+interactive system agree with the QBism perspective providing a
+resolution to the same paradoxes (e.g., EPR and Wigner's friend)?
 

### 2016-11-25 proposal/prop.tex
prop

@@
 ``closed system'' view of computation is too limiting as it cannot
-adequately describe \emph{interactive computations}. Milner explained
-that ``concurrency requires a new conceptual framework'' and ``not
-merely an extension of the repertoire of entities and constructions
-which explain sequential computing.'' In his Turing Award lecture, he
-gives the following simple but compelling example. Consider the
-following two programs:
+adequately describe the increasingly pervasive \emph{interactive
+  computations}. Milner explained that ``concurrency requires a new
+conceptual framework'' and ``not merely an extension of the repertoire
+of entities and constructions which explain sequential computing.'' In
+his Turing Award lecture, he gives the following simple but compelling
+example. Consider the following two programs:
 \begin{verbatim}
-Program P1: x := 1 ; x := x + 1 
+Program P1: x := 1; x := x + 1 
 Program P2: x := 2
@@
 programs in an environment which may involve interactions and the
-equivalence is lost. Phrased in physical terms, give the observer the
+equivalence is lost. Phrased in physical terms, we give the observer the
 additional ability to access the location \verb|x| \emph{during} the
@@
 This phenomenon is hardly a surprise to computer scientists or
-physicists but embracing it fully does have far reaching
+physicists but embracing it fully does have far-reaching
 consequences. In computer science, the big shift was to abandon the

### 2016-11-25 proposal/prop.tex
prop

@@
 
+This is the most developed part of our current investigation and is
+more detailed.
+
 Just as it is the case for Buffon's needles, estimating quantum
@@
 \begin{example}[Three-dimensional quantum 4-value interval-valued
-probability measure]\label{ex:three-dimensional-4-value} \footnote{Need to verify whether this example is convex or not.}Given
-a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$,
-and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-defined as follow, where the state vectors corresponding to 1-dimensional
-projector are also illustrated in figure~\ref{fig:three-dimensional-4-value}.
+probability measure]\label{ex:three-dimensional-4-value} 
+Question: Is this convex? Given a three dimensional Hilbert space with
+an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Consider\emph{
+}$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
+$\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$, and a quantum
+$\mathscr{I}$-interval-valued probability
+measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined as follow,
+where the state vectors corresponding to 1-dimensional projector are
+also illustrated in figure~\ref{fig:three-dimensional-4-value}.
 \begin{enumerate}
@@
 \end{enumerate}
-\footnote{This example is a little bit too long to human-verify, and
-we need more examples. Maybe we need to write a program for further
-verification.}
 \end{example}
@@
 
-Born
-KS: Mermin-Meyer
+Given quantum state as interactive system
+and interval-valued probability
+and perhaps additionally discrete states in finite fields (try with or without)
+investigate gleason (born), bell, KS, and revisit Mermin-Meyer and
+other debates and paradoxes
 
@@
 \subsection{Proposed Activity IV: Computational Aspects}
+
+If power of observer is limited with respect to power of quantum state
+then quantum state can always ``fool'' you and get away with things;
+you don't have the resources to catch it in an inconsistent state; if
+state is interactive and always ``uncommitted'' until you make your
+move you can never catch it in a lie
+
+explain secret key exchange; if attacker has limited power cannot
+crack it; complexity crucial.
 

### 2016-11-25 proposal/prop.tex
prob.tex Change to BibLaTeX...
prop.tex \section{Overview, Objectives, and Expected Significance} make sentence more precise...

@@
 \documentclass{article}
+\usepackage[ backend=biber]{biblatex}
+\addbibresource{prop.bib}
+\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
 \usepackage{fullpage}
@@
 numbers do not exist in their entirety ``for free.''  For example, the
-state of the art algorithms for computing the $n$th digit of~$\pi$
-require on the order of $n^2$
+state of the art algorithms for computing the $n$th binary digit of~$\pi$
+require on the order of $O(n\log^{O(1)}(n))$
 operations~\cite{journals/moc/BaileyBP97}. In other words, simply
@@
 \newpage
-\bibliographystyle{acm}
-\bibliography{prop}
+\printbibliography
 \end{document}

### 2016-11-25 proposal/prop.tex
prop

@@
 
+Over the past several years, the PI, together with other IU faculty
+members and students, has formed a group whose main interest is the
+study of paradigms of computing that either arise in nature or are
+inspired by natural phenomena. The PI is especially interested in how
+the laws of physics can inspire and guide our abstract computational
+models, as well as exposing new insights into the computational
+framework behind the natural world and the computability of physical
+theory. Our group has been active in several areas related to the
+theory behind quantum computation. Particular areas include:
+mathematical foundations of quantum computation and
+complexity~\cite{DBLP:journals/entcs/AltenkirchGVS07,1166040},
+adiabatic quantum computing, quantum logic, classical and quantum
+reversible programming languages~\cite{Sabry:2003:MQC:871895.871900},
+analog computation and its limits, and optical computing. During the
+last year, our discussions have revolved around formulating variants
+of quantum mechanics that are computable and that are as close to
+possible to classical computing. Several preliminary results have
+emerged from our collaboration~\cite{usat,finiteQC,geometry2013,DQT2014}, and the group
+is very excited about the potential implications of those
+results. This proposal brings forth a particular aspect of this
+programme related to its applications to problem areas that have
+traditionally been outside the conceptual framework of programming
+language research.
+
+In the past five years, Prof. Sabry received one NSF grant (award
+number 1217454) titled \emph{Information Effects} for the amount of
+\$275,319.00 with start and end dates of 1 September 2012 -- 31 August
+2016.
+
+% (c) a summary of the results of the completed work, including
+% accomplishments, supported by the award. The results must be
+% separately described under two distinct headings, Intellectual Merit
+% and Broader Impacts;
+
+% (d) a listing of the publications resulting from the NSF award (a
+% complete bibliographic citation for each publication must be provided
+% either in this section or in the References Cited section of the
+% proposal); if none, state "No publications were produced under this
+% award."
+
+% (e) evidence of research products and their availability, including,
+% but not limited to: data, publications, samples, physical collections,
+% software, and models, as described in any Data Management Plan; and
+
+\paragraph*{Intellectual Merit.}
+
+\paragraph*{Broader Impacts.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-11-25 proposal/prop.tex
proposal\prop.bib Remove duplicated keys...

@@
 mathematical foundations of quantum computation and
-complexity~\cite{DBLP:journals/entcs/AltenkirchGVS07,1166040},
+complexity~\cite{AGVS2007,VAS2006},
 adiabatic quantum computing, quantum logic, classical and quantum

### 2016-11-26 proposal/prop.tex
inputenc
proposal\prop.tex Add citations...

@@
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage{tensor}
@@
   BarrettKent2004} on the impact of finite precision measurements on
-the relevance of the Kochen-Specker theorem. We argue that no matter
+the relevance of the Kochen-Specker
+theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
+We argue that no matter
 what the results are their impact will be strong. Positive results
@@
 of interest and that the sample space is a convenient artifact that
-allows us to treat events as sets obeying the laws of Boolean algebra.
+allows us to treat events as sets obeying the laws of Boolean
+algebra~\cite{Boole1948,Redhead1987-REDINA,Griffiths2003}.
 
@@
 or experimental setting, one should question the reliance of the
-definition of probability space on the uncountable and uncomputable
+definition of probability space on the uncountable and
+uncomputable~\cite{Turing01011937,Ziegler2007,weihrauch2012computable}
 real interval $[0,1]$. This interval includes numbers like
@@
 The early formalization of the process of computing using Turing
-machines~\cite{citeulike:321509} or the
+machines~\cite{Turing01011937} or the
 $\lambda$-calculus~\cite{Barendregt:Lambda} viewed a computation as

### 2016-11-26 proposal/prop.tex
prop

--- 2016-11-25 proposal/prop.tex
@@
 \addbibresource{prop.bib}
-\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
+\ExecuteBibliographyOptions{sorting=nyt,maxbibnames=5,doi=false,isbn=false,url=false}
 \usepackage{fullpage}
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+%% \usepackage[T1]{fontenc}
+%% \usepackage[latin9]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage{tensor}
@@
 
-By using the law of large numbers, quantum probabilities can be also
-estimated by relative frequencies. For example, if we want to know the
-probability of ``spin up'' in a Stern-Gerlach
-experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}, we
-can put a beam of silver atoms in a highly inhomogeneous magnetic
-field, and count the number of atoms deflects up. Ideally, if the
-local field of strength directs to the $z$-axis, and all particles
-have the same velocity, the Stern-Gerlach experiment only produces two
-spots corresponding to $\ket{0}$ and $\ket{1}$. Notice that whenever
-the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal
-measurement is picked, measuring the spin is exactly the same as
-tossing a coin. In other words, if someone claims to be tossing a coin
-behind a veil, and only shows the resulting heads or tails, we cannot
-distinguish whether the results are really deriving from tossing a
-coin, or by running a Stern-Gerlach experiment, and showing the head,
-the tail, or the side of coin if the silver atoms is spin up, spin
-down, or just hit the middle, respectively. Following our theme, a
-Stern-Gerlach experiment requires significant resources to keep the
-local field of strength directing to the $z$-axis precisely, to keep
-the atoms having almost the same velocity, and to point out the exact
-position each particle landed on. If the field of strength does not
-perfectly direct to the $z$-axis, we do not really test the quantum
-event we want to test. Even if the field of strength perfectly directs
-to the $z$-axis, the variant velocity makes spots broader and more
-washed out. Together with the precision limit of the detector, it may
-sometimes be hard to decide a particle corresponding to which state.
+Similarly to the classical case, it is possible to estimate quantum
+probabilities by utilizing the frequentist approach of the previous
+section, assuming identical measurements conditions in each repeated
+experiment. For instance, if one wants to determine the probability
+that the spin of a given silver atom is +$\hbar/2$, a Stern-Gerlach
+apparatus is built where ideally an inhomogeneous magnetic field is
+generated along, let's say, the quantization axis $z$. One then
+produces a collimated beam of identically prepared (neutral) silver
+atoms that is directed between the poles of the magnet where a
+predetermined field-gradient along the $z$ direction has been
+established. Under appropriate experimental conditions we will observe
+that the beam, after traversing the magnetic-field region, will be
+deflected towards two regions identified by distinguished spots on a
+detector situated behind the
+apparatus~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
+Each of the two discrete values is associated to either +$\hbar/2$ or
+-$\hbar/2$, commonly called ``spin up'' and ``spin down'',
+respectively. By ``counting'' the number of atoms that are deflected
+in the ``spin up'' region one can, in principle, estimate the
+probability that the prepared state of the silver atom state has spin
++$\hbar/2$. Notice that a real experiment does not necessarily
+represent an ``ideal measurement''. For example, not all silver atoms
+will be identically prepared, or the field-gradient could not be large
+enough to distinguish between the spin up and down situations simply
+producing a large single blot. In other words, the closer we get to an
+ideal measurement the better we determine those probabilities at the
+cost of significantly increasing the number of resources. It is not
+very well appreciated in the literature that Bohr attempted to argue
+against the measurability of the spin of a free electron. Essentially,
+Bohr argued (and Mott later on justified his assertion by an elegant
+use of uncertainty relations~\cite{10.2307/j.ctt7ztxn5.15}) that a
+Stern-Gerlach experiment could not succeed in establishing the spin of
+an unbound electron because the Lorentz force would blur the detected
+pattern. This example illustrates the case of a fundamental physical
+limitation that not even infinite resources could mitigate.
 

### 2016-11-26 proposal/prop.tex

@@
 \usepackage{fullpage}
-%% \usepackage[T1]{fontenc}
-%% \usepackage[latin9]{inputenc}
 \usepackage[utf8]{inputenc}

### 2016-11-26 proposal/prop.tex
prob.bib Fixing bibLaTeX data file...

@@
 definition of probability space on the uncountable and
-uncomputable~\cite{Turing01011937,Ziegler2007,weihrauch2012computable}
+uncomputable~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}
 real interval $[0,1]$. This interval includes numbers like
@@
   experimental proposition~\cite{BirkhoffVonNeumann1936}, a
-  question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or
-  an elementary quantum test~\cite{peres1995quantum}) is represented
+  question~\cite{10.2307/2308516,Abramsky2012},
+  or an elementary quantum test~\cite{peres1995quantum}) is represented
   as a (self-adjoint or orthogonal~\cite {Griffiths2003,Maassen2010})
@@
 The early formalization of the process of computing using Turing
-machines~\cite{Turing01011937} or the
+machines~\cite{Turing_1937} or the
 $\lambda$-calculus~\cite{Barendregt:Lambda} viewed a computation as

### 2016-11-26 proposal/prop.tex
42

@@
 This is the most developed part of our current investigation and is
-more detailed.
-
-Just as it is the case for Buffon's needles, estimating quantum
-probabilities (e.g., in the case of a Stern-Gerlach experiment) with
-increasing accuracy requires increasingly large resources.  Therefore,
-given some finite resources, it is only possible to estimate the
-quantum probabilities within an interval of confidence. It is
-therefore natural to introduce the notion of an ``interval-valued
-quantum probability measure'' that combines the definitions of
-conventional quantum probability measures with classical
-interval-probabilities.
+presented in great detail. As argued in the previous sections, given
+fixed finite resources, it is only possible to estimate the quantum
+probabilities within an interval of confidence. It is therefore
+natural to propose the notion of an ``interval-valued quantum
+probability measure'' that combines the definitions of conventional
+quantum probability measures with classical interval-probabilities.
 
@@
 
-It is easy to establish that quantum interval-valued probability
-measures generalize conventional quantum probability measures. In
-particular, any quantum probability measure can be recast as an
-interval-valued measure using the three intervals $\left[0,0\right]$,
-$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where
-$\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
+\noindent It is easy to establish that quantum interval-valued
+probability measures generalize conventional quantum probability
+measures. In particular, any quantum probability measure can be recast
+as an interval-valued measure using the three intervals
+$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
+where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
 \necess~as before, and \emph{$\left[0,1\right]$} is called
-\unknown~because it provides no information as follows. Given a
+\unknown~because it provides no information. Given a quantum
 probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
@@
 \]
-
-The interesting question is the converse one corresponding to
-Gleason's theorem. Given an interval-valued probability measure, i.e.,
-given observations done with finite resources, do these observations
-uniquely determine a quantum state? Our initial investigations
-indicate that the answer is \emph{no}.
+This measure represents the beliefs of an experimenter with no prior
+knowledge about the particular quantum system in question. Formally,
+we can ask: what can we deduce about the state of a quantum system
+given an interval-valued quantum probability measure, i.e., given
+observations done with finite resources. In the case the intervals are
+infinitely precise the question reduces to Gleason's theorem which
+states that the state of the quantum system is uniquely determined by
+the probability measure. But surely the less resources are availble,
+the less precise the intervals, and the less we expect to know about
+the state of the system. To formally state and answer this question we
+begin with defining the \emph{core} and \emph{convexity} of a
+probability measure as follows.
 
@@
 \end{definition}
+
+core: easy
+
+convex: if certain intervals exist then combinations of these
+intervals must also exist so that we can add probabilities etc. in the
+classical case ... theorem but in the quantum case we found a counterexample
+
+It is common to consider convex interval-valued probability measures.
+For example, a special case of convex interval-valued probability
+measures consists the Dempster-Shafer belief function as the left-end
+and the Dempster-Shafer plausibility as the
+right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Goodman1997,Marinacci1999,Teran2014}.
+Dempster-Shafer functions, also called \emph{completely} or
+\emph{totally monotone}, play an important role in the theory of
+non-additive belief.  Furthermore, convex interval-valued probability
+measures have a good property that they can always be associated with
+real-valued probability measures.
+
+\begin{thm}[Shapley~\cite{Shapley1971}]\label{thm:Shapley}
+Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}
 

### 2016-11-26 proposal/prop.tex
prop

@@
 This is the most developed part of our current investigation and is
-presented in great detail. As argued in the previous sections, given
-fixed finite resources, it is only possible to estimate the quantum
-probabilities within an interval of confidence. It is therefore
-natural to propose the notion of an ``interval-valued quantum
-probability measure'' that combines the definitions of conventional
-quantum probability measures with classical interval-probabilities.
+presented in greater detail than the other proposed activities. As
+argued in the previous sections, given fixed finite resources, it is
+only possible to estimate the quantum probabilities within an interval
+of confidence. It is therefore natural to propose the notion of an
+``interval-valued quantum probability measure'' that combines the
+definitions of conventional quantum probability measures with
+classical interval-probabilities.
 
@@
 \begin{itemize}
-\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{quantum probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $.
+\item A \emph{core} of $\bar{\mu}$ is the set
+  $\mathrm{core}\left(\bar{\mu}\right)=\left\{
+    \pmeas:\events\rightarrow[0,1] ~\middle|~ \forall
+    E\in\events.~\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\}$.
 \item $\bar{\mu}$ is called convex if 
@@
 
-core: easy
-
-convex: if certain intervals exist then combinations of these
-intervals must also exist so that we can add probabilities etc. in the
-classical case ... theorem but in the quantum case we found a counterexample
-
-It is common to consider convex interval-valued probability measures.
-For example, a special case of convex interval-valued probability
-measures consists the Dempster-Shafer belief function as the left-end
-and the Dempster-Shafer plausibility as the
-right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Goodman1997,Marinacci1999,Teran2014}.
-Dempster-Shafer functions, also called \emph{completely} or
-\emph{totally monotone}, play an important role in the theory of
-non-additive belief.  Furthermore, convex interval-valued probability
-measures have a good property that they can always be associated with
-real-valued probability measures.
+\noindent The core of an interval-valued probability measure is the
+set of real-valued infinitely-precise probability measures it
+approximates. An interval-valued probability measure is convex if
+whenever certain intervals exist then combinations of these intervals
+must also exist, guaranteeing we can add and manipulate probabilities
+coherently. In the classical world, every convex measure has a
+non-empty core, which means that the interval-valued probability
+measure must approximate at least one infinitely-precise measure.
 
 \begin{thm}[Shapley~\cite{Shapley1971}]\label{thm:Shapley}
-Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}
-
-\begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
-There is a convex quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.
+  Every (classical) convex interval-valued probability measure has a
+  non-empty core.
 \end{thm}
 
-This theorem can be proved by the following example.
+In informal terms, this result states that although measurements done
+with limited resources and poor precision may not uniquely identify
+the true state of the system, there is always at least one system that
+is consistent with the measurements. Surprisingly, we discovered a
+counterexample to this statement in the quantum case, i.e., we
+constructed the following convex interval-valued quantum probability
+measure with an empty core.
 
@@
   probability measure]\label{ex:three-dimensional-three-value} Given
-a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
-and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$.
-Let 
+  a three dimensional Hilbert space with an orthonormal basis
+  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
+    $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
+  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
+  $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$, and
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
-\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})
+  &=& \imposs\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})
+  &=& \necess \\
+\bar{\mu}(P) 
+  &=& \unknown\quad\textrm{otherwise}
 \end{eqnarray*}
-To verify $\bar{\mu}$ is a quantum interval-valued probability
-measure, first notice that
-$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
-implies equation
-(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) by
-induction. Second, equation
-(\ref{eq:QuantumInterval-valuedProbability-Complement}) implies
-$\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
-Therefore, to prove equation
-(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), it is
-sufficient to check
-\[
-\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
-\]
-for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
-always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)$.
-
-Next, we need to verify that $\bar{\mu}$ is convex. First, for orthogonal
-projections $P_{0}$ and $P_{1}$, equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-implies equation (\ref{eq:QuantumInterval-valuedProbability-Convex}).
-Second, when $P_{0}=P_{1}+P_{2}$, equation
-(\ref{eq:QuantumInterval-valuedProbability-Convex}) holds trivially.
-Hence, we only need to verify the case which $P_{0}=\proj{\psi_{0}}+\proj{\psi_{2}}$
-and $P_{1}=\proj{\psi_{1}}+\proj{\psi_{2}}$,
-where $\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
-is an orthonormal basis. Because we have 
-\begin{eqnarray*}
-\bar{\mu}\left(P_{0}\vee P_{1}\right) & = & \bar{\mu}\left(\mathbb{1}\right)=\necess\\
-\bar{\mu}\left(P_{0}P_{1}\right) & = & \bar{\mu}\left(\proj{\psi_{2}}\right)\subseteq\unknown
-\end{eqnarray*}
-and $\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
-is either $\necess+\unknown$ or $\unknown+\unknown$.
-Therefore, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
-
-Finally, we will prove that $\bar{\mu}$ cannot correspond to any
-quantum probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
-for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
-We must have 
-\begin{equation}
-\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
-\end{equation}
-By Gleason's theorem, there is a mixed
+It is straightforward to verify that $\bar{\mu}$ is a convex quantum
+interval-valued probability measure. Now assume there exists a
+real-valued quantum probability measure $\mu$ such that
+$\mu(P)\in\bar{\mu}(P)$ for every event (projection)~$P$. We derive a
+contradiction as follows. Suppose $\mu(P)\in\bar{\mu}(P)$ then we must
+have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$. By Gleason's
+theorem, there is a mixed
 state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$ such that
-$\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$.  However, no pure
-state~$\ket{\phi}$ satisfies
-$\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$ so that we have
-$\mu(P)\notin\bar{\mu}(P)$ for all quantum probability measure~$\mu$.
+$\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$, where
+$\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$.  However, no pure
+state~$\ket{\phi}$ can satisfy
+$\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
 \end{example}
+
+\paragraph*{XXX.}
 
@@
 
+\paragraph*{Research Question.} confirm that we get closer and closer
+to Born rule as precision improves; find conditions on interval-valued
+quantum prob. measures that would make sense; precision improves
+implies states get sharper
+
 %%%%%
@@
 
+\paragraph*{Research Question.} the above is mostly about gleason's 
+theorem; foundational; related theorem richer are bell; and KS;
+
+\paragraph*{Research Question.} add discrete theory to the story; do
+not assume anything is infinitely precise not even the hypothetical state
+
+\paragraph*{Research Question.} revisit Mermin-Meyer etc with 
+mathematical framework we have with and without discrete theory
+
 %%%%%
 \subsection{Proposed Activity IV: Computational Aspects}
+
+mention aaronson three statements paradox. something is wrong;
+investigate; investigate complexity; p=np; mention usat and mention
+deutsch-josza improvement depends on precision not as dramatic
+
+\paragraph*{Research Question.}
 

### 2016-11-26 proposal/prop.tex
prop

@@
 states that the state of the quantum system is uniquely determined by
-the probability measure. But surely the less resources are availble,
+the probability measure. But surely the less resources are available,
 the less precise the intervals, and the less we expect to know about
@@
 
-\begin{example}[Three-dimensional quantum three-value interval-valued
+\begin{example}[Three-dimensional three-interval-valued quantum
   probability measure]\label{ex:three-dimensional-three-value} Given
@@
 
-\paragraph*{XXX.}
-
-Recall that when approximating the probability classically, the quality
-of the experimental equipment cannot be compensated by the number
-of independent trials. If the precision of the intervals~$\mathscr{I}$
-represents the quality of the quantum experimental equipment, example~\ref{ex:three-dimensional-three-value}
-tells us that we cannot identify a particular state if the experimental
-equipment reveals too little information. For example, $\bar{\mu}$
-might correspond to $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
-$\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
-or the density matrix~$\frac{\mathbb{1}}{3}$ because $\bar{\mu}(\proj{\phi})\ne\necess$
-for all $\ket{\phi}$. Also, example~\ref{ex:three-dimensional-three-value}
-is no longer valid if our measurement equipment is a little more precise,
-say $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-because example~\ref{ex:three-dimensional-three-value} really use
-the property of $\unknown$.
-
-If we consider
-$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-example~\ref{ex:three-dimensional-4-value} provides another example
-with an empty core. Comparing to
-example~\ref{ex:three-dimensional-three-value},
-example~\ref{ex:three-dimensional-4-value} is closer to the Born rule
-in a sense that it might only correspond to $\ket{2}$ or
-$\frac{\mathbb{1}}{3}$, but not
-$\ket{1}$. Example~\ref{ex:three-dimensional-4-value} is also no
-longer valid for more precise measurement equipment as well.  In
-general, we believe if the measurement equipment is more and more
-precise, its interval-valued probability measure will be closer and
-closer to the the Born rule. In the limit case,
-$\mathscr{I}=\left\{ \left\{ a\right\}
-  \middle|a\in\left[0,1\right]\right\} $
-recovers conventional Gleason's theorem and the Born rule.
-
-\begin{example}[Three-dimensional quantum 4-value interval-valued
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{measure4.pdf}
+\end{center}
+\caption{\label{fig:three-dimensional-4-value}This figure illustrates
+  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
+  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
+  and $\ket{\ps}$ respectively.  All possible vectors of the subspaces
+  $\ket{0_{\theta,\gamma}^{\perp}}$ and
+  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
+  circles, respectively. Within the circles, a dotted
+  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
+  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
+  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
+  green solid vectors are normalized
+  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
+  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
+\end{figure}
+
+Looking closely at the example above, we might think that the
+probability measure $\bar{\mu}$ is induced by the state $\ket{2}$
+because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, or we
+might think it is induced by the state $\ket{1}$ because
+$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, or yet we might
+think it is induced by the mixed state $\frac{\mathbb{1}}{3}$ because
+$\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$. Each of these
+possibilities is compatible with some but not all of the
+observations. All is not lost however: if the observations are made
+more precise, we conjecture that some of the inconsistencies
+disappear. A partial proof of this conjecture is the following example
+which refines the previous probability measure by adding more precise
+intervals. It remains to prove that this refined measure is convex,
+however.
+
+\begin{example}[Three-dimensional four-interval-valued quantum
   probability measure]\label{ex:three-dimensional-4-value}
-Question: Is this convex? Given a three dimensional Hilbert space with
-an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Consider\emph{
+  Given a three dimensional Hilbert space with an orthonormal basis
+  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
   }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
-$\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$, and a quantum
-$\mathscr{I}$-interval-valued probability
-measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined as follow,
-where the state vectors corresponding to 1-dimensional projector are
-also illustrated in figure~\ref{fig:three-dimensional-4-value}.
+  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and
+  $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$. The definition of
+  $\bar{\mu}$ below refers to Fig.~\ref{fig:three-dimensional-4-value}
+  which plots the 1-dimensional projectors:
 \begin{enumerate}
-\item Let 
+\item Let:
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \necess\textrm{ ,}
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) 
+  &=& \imposs \\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) 
+  &=& \necess
 \end{eqnarray*}
- where $\ket{0}$ and $\ket{\ps}$ is illustrated as the red and green
-dotted vector, respectively.
-\item Consider the red and green circles in figure~\ref{fig:three-dimensional-4-value}.
-They are the states orthogonal to $\ket{0}$ and $\ket{\ps}$, respectively,
-and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
-and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
+where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green dotted
+vectors, respectively.
+\item The red and green circles are are the states orthogonal to
+  $\ket{0}$ and $\ket{\ps}$, respectively, and can be parametrized as
+  $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+  and
+  $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
   where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
-half of those states need special treatment, i.e., whenever $0\le\theta<\frac{\pi}{2}$
-and $0\le\gamma<\pi$, we define 
+  half of those states need special treatment, i.e., whenever
+  $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define
 \begin{eqnarray*}
-\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely\textrm{ .}
+\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)
+  &=& \likely \\
+\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right)=
+  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right) 
+  &=& \unlikely
 \end{eqnarray*}
-\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely$. 
+\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
 \end{enumerate}
-That $\bar{\mu}$ has an empty core can be proved by contradiction.
-Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
-for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
-and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
-we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
-so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
+It is straightforward but tedious to check that $\bar{\mu}$ is an
+interval-valued quantum probability measure. Although we have not
+verified that $\bar{\mu}$ is convex, the following argument
+establishes that is has an empty core. Assume there is a real-valued
+probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for
+all $P\in\events$. Because
+$\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$ and
+$\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$, we must
+have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$ so that
+$\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However,
 \[
@@
 \]
-
-Similar to example~\ref{ex:three-dimensional-three-value}, to verify
-$\bar{\mu}$ is a quantum interval-valued probability measure, we
-only need to verify equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-and it is sufficient to check 
-\begin{equation}
-\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{0}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)
-\end{aligned}
-\label{eq:non-additive-vectors}
-\end{equation}
-for every orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $.
-We are going to enumerate all possible orthonormal bases to verify
-equation~(\ref{eq:non-additive-vectors}), and case 1 and 2 are illustrated
-in figure~\ref{fig:three-dimensional-4-value}. 
-\begin{center}
-\begin{figure}
-\includegraphics[scale=0.4]{measure4.pdf}
-\caption{\label{fig:three-dimensional-4-value}This figure illustrates case
-1 and 2 in $\mathbb{R}^{3}$ in example~\ref{ex:three-dimensional-4-value}.
-The red and green dotted vector are $\ket{0}$ and $\ket{\ps}$ respectively.
-All possible vectors of $\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
-are drawn in the red and green circles, respectively. Within the circles,
-a vector~$\ket{\psi}$ in dotted part means $\bar{\mu}(\proj{\psi})=\likely$;
-otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
-a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
-and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
-and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
-\end{figure}
-\end{center}
-
-\begin{enumerate}
-\item When $\ket{\psi_{0}}$ is $\ket{0}$, then either $\ket{\psi_{1}}$
-or $\ket{\psi_{2}}$ must be $\ket{0_{\theta,\gamma}^{\perp}}$ for
-some $\theta$ and $\gamma$. Because of 
-\[
-\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
-0\\
-0
-\end{pmatrix}\times\begin{pmatrix}0\\
-\rme^{\rmi\gamma}\sin\theta\\
-\cos\theta
-\end{pmatrix}=\begin{pmatrix}0\\
--\cos\theta\\
-\rme^{-\rmi\gamma}\sin\theta
-\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}0\\
-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
-\cos\left(\frac{\pi}{2}-\theta\right)
-\end{pmatrix}=\rme^{-\rmi\gamma}\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
-\]
-the pair $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\psi_{2}}=\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}$
-for ($0<\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$) or $\theta=0$
-enumerate all possible orthonormal bases. Equation~(\ref{eq:non-additive-vectors})
-can then be verified as follow. 
-\begin{equation}
-\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}\right)=\necess & \subseteq\likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & =\unlikely\tensor*[_{\mathscr{I}}]{+}{}\imposs=\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)=\likely & =\imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
-\end{aligned}
-\label{eq:case1}
-\end{equation}
-Similarly, when $\ket{\psi_{0}}$ is $\ket{\ps}$, equation~(\ref{eq:non-additive-vectors})
-holds. 
-\item When $\ket{0}\notin\mathcal{B}$ and $\ket{\psi_{0}}=\ket{0_{\theta,\gamma}^{\perp}}$
-for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we want to
-prove $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$.
-Then, we have 
-\begin{equation}
-\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
-\end{aligned}
-\label{eq:case2}
-\end{equation}
-In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$,
-it is sufficient to prove that if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
-then ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or $\theta'=\frac{\pi}{2}$.
-Recall $\ip{\ps}{\ps_{\theta',\gamma'}^{\perp}}=0$. Hence, if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
-we have $\ket{\ps_{\theta',\gamma'}^{\perp}}$ parallel to $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$.
-\begin{equation}
-\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
-1\\
-0
-\end{pmatrix}\times\begin{pmatrix}0\\
-\rme^{\rmi\gamma}\sin\theta\\
-\cos\theta
-\end{pmatrix}=\begin{pmatrix}\cos\theta\\
--\cos\theta\\
-\rme^{-\rmi\gamma}\sin\theta
-\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
-\cos\left(\frac{\pi}{2}-\theta\right)
-\end{pmatrix}=\sqrt{2}\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\label{eq:case2-cross}
-\end{equation}
-Because of $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we have
-($0<\theta'=\frac{\pi}{2}-\theta<\frac{\pi}{2}$ and $\pi\le\gamma'=\pi+\gamma<2\pi$)
-or $\theta'=\frac{\pi}{2}-\theta=\frac{\pi}{2}$. Similarly, when
-$\ket{\psi_{0}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$ and $\ket{\ps}\notin\mathcal{B}$,
-equation~(\ref{eq:non-additive-vectors}) holds. 
-\item Finally, when $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$,
-$\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$, and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
-for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, i.e., the ``otherwise''
-case. Then, equation~(\ref{eq:non-additive-vectors}) can easily
-be verified. 
-\begin{equation}
-\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right)=\likely\subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\label{eq:case3}
-\end{equation}
-\end{enumerate}
+This measure however is ``better'' than the previous one in the sense
+that it might only be induced by $\ket{2}$ or the density matrix
+$\frac{\mathbb{1}}{3}$, but not by
+$\ket{1}$. 
 \end{example}
 
-The following example verifies example~\ref{ex:three-dimensional-4-value}
-cannot hold with more precise intervals.
-
-\begin{example}[Three-dimensional quantum 4-value interval-valued
-probability measure (Continue)]\label{ex:three-dimensional-4-value-1}
-Consider $\mathscr{I}=\left\{ \imposs,\left[l_{1},r_{1}\right],\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right],\necess\right\} $,
-where $\left[l_{1},r_{1}\right]$ and $\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]$
-will be used to replace every $\unlikely$ and $\likely$ in example~\ref{ex:three-dimensional-4-value},
-respectively. The bound of $l_{1}$ and $r_{1}$ can then be estimated
-by the equations corresponding to equation~(\ref{eq:case1}), (\ref{eq:case2}),
-and (\ref{eq:case3}).
-
-When we replace $\unlikely$ and $\likely$ by $\left[l_{1},r_{1}\right]$
-and $\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]$,
-equation~(\ref{eq:case1}) will become
-
-\begin{equation}
-\begin{aligned}\necess & \subseteq\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
-\left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\imposs\\
-\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right] & \subseteq\imposs\tensor*[_{\mathscr{I}}]{+}{}\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]
-\end{aligned}
-\label{eq:case1-1}
-\end{equation}
-which are all tautologies. Equation~(\ref{eq:case2}) will become
-\begin{equation}
-\begin{aligned}\left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
-\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]
-\end{aligned}
-\label{eq:case2-1}
-\end{equation}
-which implies $l_{1}=0$. Finally, equation~(\ref{eq:case3}) will
-become
-\begin{equation}
-\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]\subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\label{eq:case3-1}
-\end{equation}
-which implies $\frac{1}{2}\le r_{1}\le1$. Therefore, $l_{1}=0$ and
-$r_{1}=\frac{1}{2}$ provides the most precise intervals which make
-example~\ref{ex:three-dimensional-4-value} work, and in this case,
-the intervals are $\left\{ \imposs,\unlikely,\likely,\necess\right\}
-$.
-\end{example}
-
-Although it is easier to deduce an interval-valued probability measure
-has an empty core by considering the state mapped to $\imposs$ as
-in example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
-it is not the only way to prove an interval-valued probability measure
-has an empty core. The following family of interval-valued probability
-measures satisfy that $\bar{\mu}\left(P\right)=\imposs$ if and only
-if $P=\mathbb{0}$, but we can still prove them have empty cores.
-
-Although it is easier to deduce an interval-valued probability measure
-has an empty core by considering the state mapped to $\imposs$ as
-in example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
-it is not the only way to prove an interval-valued probability measure
-has an empty core. The following family of interval-valued probability
-measures satisfy that $\bar{\mu}\left(P\right)=\imposs$ if and only
-if $P=\mathbb{0}$, but we can still prove them have empty cores.
-
-\paragraph*{Research Question.} confirm that we get closer and closer
-to Born rule as precision improves; find conditions on interval-valued
-quantum prob. measures that would make sense; precision improves
-implies states get sharper
+In general, we conjecture that if the measurement equipment is made
+more and more precise, the corresponding interval-valued probability
+measure will be closer and closer to the Born rule. In the limit case,
+$\mathscr{I}=\left\{ \left\{ a\right\}
+  \middle|a\in\left[0,1\right]\right\}$
+we do indeed recover the conventional Gleason's theorem and the Born
+rule.
+
+\paragraph*{Research Question.} Confirm that as the number and
+precision of the intervals increase the interval-valued quantum
+probability measure converges to the measure induced by the Born
+rule.
 

### 2016-11-26 proposal/prop.tex
prop

@@
 only possible to estimate the quantum probabilities within an interval
-of confidence. It is therefore natural to propose the notion of an
-``interval-valued quantum probability measure'' that combines the
+of confidence. It is therefore natural to propose the notion of a
+``quantum interval-valued probability measure'' that combines the
 definitions of conventional quantum probability measures with
@@
 we can ask: what can we deduce about the state of a quantum system
-given an interval-valued quantum probability measure, i.e., given
+given a quantum interval-valued probability measure, i.e., given
 observations done with finite resources. In the case the intervals are
@@
 counterexample to this statement in the quantum case, i.e., we
-constructed the following convex interval-valued quantum probability
+constructed the following convex quantum interval-valued probability
 measure with an empty core.
 
-\begin{example}[Three-dimensional three-interval-valued quantum
+\begin{example}[Three-dimensional quantum three-interval-valued 
   probability measure]\label{ex:three-dimensional-three-value} Given
@@
 
-\begin{example}[Three-dimensional four-interval-valued quantum
+\begin{example}[Three-dimensional quantum four-interval-valued 
   probability measure]\label{ex:three-dimensional-4-value}
@@
 \end{enumerate}
-It is straightforward but tedious to check that $\bar{\mu}$ is an
-interval-valued quantum probability measure. Although we have not
+It is straightforward but tedious to check that $\bar{\mu}$ is a
+quantum interval-valued probability measure. Although we have not
 verified that $\bar{\mu}$ is convex, the following argument
@@
 $\mathscr{I}=\left\{ \left\{ a\right\}
-  \middle|a\in\left[0,1\right]\right\}$
+  ~\middle|~a\in\left[0,1\right]\right\}$
 we do indeed recover the conventional Gleason's theorem and the Born
@@
 \paragraph*{Research Question.} Confirm that as the number and
-precision of the intervals increase the interval-valued quantum
+precision of the intervals increase the quantum interval-valued 
 probability measure converges to the measure induced by the Born
@@
 \subsection{Proposed Activity III: Quantum Information Theorems}
+
+The previous research question is essentially concerned with the
+status of Gleason's theorem in a world with finite-precision
+measurements. The following research questions are therefore natural
+follow-up questions.
+
+\paragraph*{Research Question.} Investigate the status of the theorems
+of Gleason, Bell, and Kochen-Specker for quantum interval-valued
+probability measures. Revisit the Meyer-Mermin debate in this
+mathematical framework.
+
+%%%%%
+\subsection{Proposed Activity IV: Computational Aspects}
+
+\paragraph*{Research Question.} add discrete theory to the story; do
+not assume anything is infinitely precise not even the hypothetical state
 
@@
 other debates and paradoxes
-
-\paragraph*{Research Question.} the above is mostly about gleason's 
-theorem; foundational; related theorem richer are bell; and KS;
-
-\paragraph*{Research Question.} add discrete theory to the story; do
-not assume anything is infinitely precise not even the hypothetical state
-
-\paragraph*{Research Question.} revisit Mermin-Meyer etc with 
-mathematical framework we have with and without discrete theory
-
-%%%%%
-\subsection{Proposed Activity IV: Computational Aspects}
 

### 2016-11-26 proposal/prop.tex
closer

@@
 
+The marriage of quantum mechanics and computer science first
+envisioned and popularized by Feynman has created an awkward, but
+opportune, moment. The embarrassing dilemma was concisely described by
+Aaronson as follows. Consider the following three statements:
+\begin{enumerate}
+\item[(A)] Textbook quantum mechanics is correct
+\item[(B)] There does not exist an efficient classical factoring
+  algorithm
+\item[(C)] The extended Church-Turing thesis that probabilistic Turing
+  machines can efficiently simulate any physically realizable model of
+  computation is correct.
+\end{enumerate}
+There is overwhelming evidence to support each of these
+statements. The theoretical framework of quantum mechanics (A) has
+withstood decades of experimental confirmation. Entire industries are
+founded on the assumption (B) that algorithms like RSA are secure and
+they also have withstood years of attempted attacks. Finally the
+entire field of complexity theory in computer science which has also
+withstood years of field testing rests, in essence, on assumption
+(C). And yet one of these three statements \emph{must be false}! Indeed
+if textbook quantum mechanics is false we concede (A). If it is
+correct Shor's efficient factoring algorithm is realizable. If there
+is a corresponding efficient classical factoring algorithm then we
+concede (B). If not then we concede~(C).
+
+It is unlikely that there will be a simple a resolution to this
+awkward situation. It is more likely that the resolution will emerge
+from deep and careful analyses of the foundations of each field. In
+previous work, we examined the Hilbert space mathematical framework of
+quantum mechanics and teased apart its various aspects that directly
+rely on the infinite-precision real or complex numbers. We note two
+remarkable earlier results:
+\begin{itemize}
+\item UNIQUE-SAT: Schumacher and
+  Westmoreland~\cite{Schumacher2012-SCHMQT} argue that much of the
+  structure of traditional quantum mechanics is maintained in the
+  presence of finite fields. In particular, they establish that the
+  quantum theory based on the finite field of booleans retains the
+  following characteristics of quantum mechanics: the notions of
+  superposition, interference, entanglement, and mixed states of
+  quantum systems; the time evolution of quantum systems using
+  invertible linear operators; the complementarity of incompatible
+  observables; the exclusion of local hidden variable theories and the
+  impossibility of cloning quantum states; and the presence of natural
+  counterparts of quantum information protocols such as superdense
+  coding and teleportation. However we have argued that this theory is
+  not physically realizable as it allows the solution of
+  computationally difficult problems like
+  UNIQUE-SAT~\cite{Valiant198685} in constant time~\cite{usat}.
+
+\item Deutsch-Jozsa: In a follow-up paper~\cite{DQT2014}, we proposed
+  a variant of quantum mechanics in which the underlying field of
+  complex numbers is replaced by special finite fields with enough
+  structure to model Hermitian products that \emph{locally} behave
+  like inner products. The trick is to recognize that, as the
+  characteristic of the finite field increases, larger and larger
+  regions of the finite field become totally ordered, thereby
+  restoring, with some restrictions, all the usual properties of the
+  inner product needed for conventional quantum mechanics. Using this
+  theory to analyze the Deutsch -Jozsa algorithm reveals that the
+  characteristic of the finite field plays an essential role: as the
+  size of the finite field grows, so does the numerical range of the
+  intermediate and final results of the algorithms being implemented.
+  The theory naturally recovers a deterministic measure of the
+  intrinsic resources required for a given level of complexity; this
+  measure is normally completely hidden in computations with real
+  numbers, and explicitly exposing it is one of the significant
+  achievements of our discrete field analysis of quantum computation.
+  This solves the conundrum that the conventional Deutsch-Jozsa
+  algorithm mysteriously continues to work for larger and larger input
+  functions without any apparent increase in resources.  Our analysis
+  of this problem reveals that as the size of the input increases, it
+  is necessary to increase the size of the finite field and hence the
+  size of the underlying available numeric coefficients.  This
+  observation does not fully explain the power of quantum computing
+  over classical computing, but at least it explains that some of the
+  power of quantum computing depends on increasingly larger precision
+  in the underlying field of numbers.
+
+\end{itemize}
+
 \paragraph*{Research Question.} add discrete theory to the story; do

### 2016-11-26 proposal/prop.tex
don-ish

@@
 
-\paragraph*{Research Question.} add discrete theory to the story; do
-not assume anything is infinitely precise not even the hypothetical state
-
-Given quantum state as interactive system
-and interval-valued probability
-and perhaps additionally discrete states in finite fields (try with or without)
-investigate gleason (born), bell, KS, and revisit Mermin-Meyer and
-other debates and paradoxes
-
-mention aaronson three statements paradox. something is wrong;
-investigate; investigate complexity; p=np; mention usat and mention
-deutsch-josza improvement depends on precision not as dramatic
-
-\paragraph*{Research Question.}
-
-If power of observer is limited with respect to power of quantum state
-then quantum state can always ``fool'' you and get away with things;
-you don't have the resources to catch it in an inconsistent state; if
-state is interactive and always ``uncommitted'' until you make your
-move you can never catch it in a lie
-
-explain secret key exchange; if attacker has limited power cannot
-crack it; complexity crucial.
-
-may find surprises like we found with UNIQUE-SAT; not sure where that belongs
-
-clear goals: KS with interval probability or with quantum states as
-processes
-
-talk about finite fields; previous work; unique-sat surprise; etc
-
-... and quantum measurement expressed using game semantics
-
-This is really about unifying classical and quantum theories of
-measurement. One of the most well-developed and formalized theories of
-classical measurement is the one for programming language
-observational contextual equivalence.
-
-This worldview can be maintained as long as the impact of the
-measurements is really negligible on the execution time of the
-functions of interest.
-
-measurement affects runtime and hence affects other measurements;
-could even conceive of programs whose input-output behavior is
-affected by measurement
-
-This intended level of abstraction is reflected in the first
-line of the function declaration in Haskell. This \emph{interface} (or \emph{type}
-or \emph{signature} or \emph{contract}) line:
-\begin{quote}
-\begin{verbatim}
-square :: Int -> Int
-\end{verbatim}
-\end{quote}
-summarizes the publicly stated, computationally relevant, aspects of the
-function. In this case, it is announced that the function is a computer
-realization of a pure mathematical map from one \verb|Int| to another. The
-fact that executing the computer realization of the map on a particular input
-might consume 10\% of the battery power on your laptop is something
-that---although potentially critical knowledge in some circumstances---is not
-even expressible in the notation above.
-
-%%-------------------------------------
-\subsection*{Partial Functions (Time)}
-
-Computations take time. At some level of abstraction, we can ignore the time
-taken by a computation. For example, we can pretend that a calculation that
-takes one or two microseconds is similar to the ``instantaneous'' lookup in a
-mathematical mapping. But we can hardly keep pretending this as the time used
-by the calculation tends towards infinity.
-
-Consider the following Java method:
-\begin{quote}
-\begin{verbatim}
-int collatz (int n) {
-  if (n == 1) return 0; 
-  else if (n % 2 == 0) return 1 + collatz (n / 2);
-  else return 1 + collatz (3 * n + 1);
-}
-\end{verbatim}
-\end{quote}
-As evident from the use of \verb|collatz| in the body of the method, this
-method is \emph{recursive}. It takes an input number \verb|n| and:
-\begin{itemize}
-\item if the input number is equal to one, the method immediately stops with
-the value zero, which represents in this case the total number of recursive
-calls performed before stopping;
-\item if the input number is even, the method divides it by two and
-recursively invokes itself, adding one to the total number of recursive
-calls;
-\item if the input number is odd, the method multiplies it by three, adds
-one, and then recursively invokes itself, after again adding one to the total
-number of recursive calls.
-\end{itemize}
-It is a famous mathematical conjecture, \emph{the Collatz conjecture}, that
-this calculation always terminates for all positive integers. One can quickly
-check a few cases:
-\begin{itemize}
-\item invoking \verb|collatz(3)| iterates through 10, 5, 16, 8, 4, 2, 1, and
-  then stops returning the result 7.
-\item invoking \verb|collatz(17)| iterates through 52, 26, 13, 40, 20, 10, 5,
-16, 8, 4, 2, 1, and then stops returning the result 12.
-\end{itemize}
-
-There is however no known proof that this method always stops. Thus, even
-though the method has the same interface as the method \verb|square| above,
-one may not be able to interpret the two interfaces in the same way. To
-account for the possibility that the calculation never stops, the interface:
-\begin{quote}
-\begin{verbatim}
-int collatz (int n)
-\end{verbatim}
-\end{quote}
-should in general be read as saying:
-\begin{quote}
-Given a particular \verb|int| the method \emph{may or may not} return another
-\verb|int| in a finite amount of time.
-\end{quote}
-
-Another way to look at the situation is that we have introduced ``time'' as
-an implicit parameter of computations. Some computations as the method
-\verb|square| update---as a side effect---this time parameter by consuming a
-few ticks. By general agreement, this consumption is deemed negligible and
-not ``observable'' and does not generally constitute a computational
-effect. But when the consumption of time is unbounded, it arguably becomes an
-observable computational effect.
-
-%%-------------------------------------
-\subsection*{Assignments (Memory)}
-
-Computations require memory. Again, at some level of abstraction we can
-pretend that memory does not exist. But what happens if a computation
-starts changing external memory locations?
-
-Consider the following variant of the method \verb.square.:
-\begin{quote}
-\begin{verbatim}
-int square (int n) {
-  count++;
-  return n * n;
-}
-\end{verbatim}
-\end{quote}
-As before, the method takes an integer \verb.n. from the domain of Java
-integers \verb.int. and returns another integer whose value is the square of
-the input. But, as a side effect the method reads and updates an external
-reference \verb.count., which can be used to find out how many times the
-method was called. Thus if during the execution of a particular program the
-method \verb.square. is called ten times, then the value of \verb.count. will
-be ten.
-
-Thus the interface:
-\begin{quote}
-\begin{verbatim}
-int square (int n)
-\end{verbatim}
-\end{quote}
-should now be read as saying:
-\begin{quote}
-Given a particular \verb|int| the method \emph{may possibly} read and update
-external memory references and then it \emph{may or may not} return another
-\verb|int| in a finite amount of time.
-\end{quote}
-
-Another way to look at the situation is that we have introduced ``memory'' as
-an implicit parameter of computations. Some computations as the original
-method \verb|square| might---as a side effect---allocate, update, and read
-several memory locations (registers, cache entries, stack frames, etc.). By
-general agreement, these actions on memory are not considered observable and
-do not generally constitute a computational effect. But when a computation
-updates an external memory location that other program fragments can inspect,
-the update of the memory location becomes an observable computational effect.
-
-%%-------------------------------------
-\subsection*{Runtime Exceptions (Context)}
-
-Computations occur in a context. When a computation occurs in the context of
-a larger computation, it is typically expected to return its result to that
-outer computation. But what if a computation cannot return a sensible value
-to its context and decides instead to abort it?
-
-Consider again the method \verb|square| whose interface is:
-\begin{quote}
-\begin{verbatim} 
-int square (int n)
-\end{verbatim}
-\end{quote}
-We initially argued that it is possible to interpret this interface to say
-that given a particular \verb|int| the method's execution promises to return
-another \verb|int|. This is clearly an idealized view: in real life, any of
-an unlimited number of failures may occur in the hardware or underlying
-software components including the operating system or the Java virtual
-machine. The Java language collectively refers to these conditions as
-\verb|Error|s or \verb|RuntimeException|s.
-
-So to be more accurate, and putting together our observations so far, one
-should interpret the interface:
-\begin{quote}
-\begin{verbatim} 
-int square (int n)
-\end{verbatim}
-\end{quote}
-as saying:
-\begin{quote}
-Given a particular \verb|int| the method \emph{may possibly} read and
-update external references, and then it \emph{may or may not} return another
-\verb|int| in a finite time or it \emph{may fail to return to its context}
-due to any of a number of errors and runtime exceptions.
-\end{quote}
-
-Another way to look at the situation is that we have introduced the
-``context'' as an implicit parameter of computations. It is expected that
-every inner computation would resume its context with its result. But when an
-inner computation encounters a fatal error condition, it can ignore the
-context parameter, which causes the error condition to immediately terminate
-the entire computation. This escape clearly constitutes an observable
-computational effect.
-
-%%-------------------------------------
-\subsection*{Other Computational Effects}
-
-The unifying theme in all the above effects is that computations do not
-happen in isolation in some abstract mathematical world: rather computations
-are realized in some physical computing platform. The physical interactions
-of a computation with the computing platform and with other computations may
-be ignored in some idealized situation corresponding to simple computations,
-but they become crucial if one is interested in modeling the actual behavior
-of a sophisticated realistic computation. If these interactions happen
-``behind the scene'' they are considered side effects of the computation.
-
-Without further constraints on computations and their contexts, it is
-impossible to enumerate all the possible side effects that a computation may
-have. The reader may find it instructive to consider the following list of
-effects that could be performed by a method with the interface:
-\begin{quote}
-\begin{verbatim} 
-int square (int n)
-\end{verbatim}
-\end{quote}
-Given a particular \verb|int|, the method's behavior may include various
-combinations of the following actions:
-\begin{itemize}
-\item Reading and updating external memory locations, environment parameters,
-local or remote file systems or databases, etc.
-\item Communicating with a user or another local or remote process.
-\item Suspending itself for a certain period of time or until a certain
-outside condition happens.
-\item Resuming other suspended computations.
-\item Loading, compiling, and executing some other computation.
-\item Using reflection to examine and perhaps modify its own machine
-representation.
-\item Producing multiple answers by arranging for one \verb|int| to be
-returned now and subsequent answers to be returned when the method is called
-again (with the same parameters). 
-\item Checkpointing its entire state to a log, which can be examined and
-resumed later.
-\item Failing due to any of a number of errors and runtime exceptions.
-\item Consuming half of the battery life of a laptop and generating enough
-heat to keep you warm on a cold winter night.
-\end{itemize}
-And yes by the way, the method may actually return another \verb|int| in a
-finite amount of time.
-
-It is clear that the method's interface is nowhere close to giving us a
-reasonable approximation of the possible behaviors of the method: it sweeps
-too many things under the rug. Pragmatically, if a programmer invokes a
-method with the interface:
-\begin{quote}
-\begin{verbatim} 
-int square (int n)
-\end{verbatim}
-\end{quote}
-the implicit computational effects of the method might come as a
-surprise.
-
-The situation is not unique to Java. Almost every other programming
-language allows similar computational effects to occur
-implicitly. Even hardware circuits and assembly language instructions
-often perform implicit effects. For example, an assembly instruction
-might change the contents of the flag register as a side effect. In
-fact natural languages also include various ``non-compositional
-phenomena,'' which are essentially computational effects. For this
-reason, programmers are universally taught to avoid side effects if
-possible and to be careful when analyzing code that might contain side
-effects. But when side effects are unavoidable, the solution is to
-\emph{expose them} as the rest of the article explains.
-
-Common wisdom is that classical physics has no randomness. Only
-ignorance of the fine details or lack of control over them causes
-\emph{statistical randomness}. In principle, but not in practice,
-randomness is absent from classical physics.
-
-In sharp contrast, quantum randomness is unavoidable even in principle.
-
-But but but ... Nature is one. The distinction between ``classical''
-and ``quantum'' can only be in our minds, or more precisely in our
-mathematical models of the universe. We have two mathematical models,
-one which is, in principle deterministic, and one which is
-probabilistic. Nature must really be one or the other.
-
-Consider this unsettling quote from QBism:
-
-\begin{quote} 
-Instead, the wavefunction obeys two fundamentally different laws:
-\begin{enumerate}
-\item As long as the electron is left to its own devices unobserved
-  its wavefunction unfolds smoothly, continuously, and predictably. It
-  obeys fixed mathematical laws, just like a bullet in flight and a
-  wave on a lake.
-\item When the electron reveals its whereabouts by leaving a dot on a
-  screen, the wavefunction ``collapses'' suddenly into a new much more
-  compact form concentrated on the point of impact.
-\end{enumerate}
-
-\end{quote}
-
-Can we develop a mathematical model that unifies both the classical
-deterministic perspective and the quantum probabilistic perspective?
-Quantum information and quantum computation opens the door to using
-computational insights. The main one is that, in a computation,
-everything produced during a computation and everything observed about
-a computation is finite. The computational perspective imposes a
-principle we might call the principle of ``finitely communicable
-evidence.''
-
-So imprecision in classical physics becomes, not some second-class
-principle that is considered to stem from practical limitations but
-rather a foundational principle. If everything is ``fuzzy'' so to
-speak and if our mathematical models embrace this fuzziness then a
-different worldview emerges. That worldview agrees with classical
-physics but embraces imprecision within the mathematical model not as
-an external non-mathematical nuisance. This shift in perspective
-enables a smooth transition to the world of quantum physics since our
-mathematical model has already embraced probabilistic effects.
-
-Three insights:
-
-\begin{itemize}
-\item Interactive systems: response of quantum system determined
-  \emph{after} the observer initiates the experiment used to observe
-  the system
-\item Bayesian probability, personal
-\item Finite precision
-\end{itemize}
-
-Goal: build computational model of QM that encompasses classical
-(reversible), computation and observation with finite resources, and
-hopefully revolutionize ``quantum thinking''
+\paragraph*{Research Question.} A long term, ultimate, goal of this
+research proposal would be to combine the various pieces into a
+coherent computational model of quantum mechanics that keeps explicit
+track of resources needed to represent the interactive system
+representing the quantum state, its evolution, the observables, and
+the probabilities. Such a computational model of quantum mechanics
+would encompass classical (reversible) computation and potentially
+revolutionize quantum thinking with finite resources. The explicit
+manipulation of resources enables one of key idea that emerged in our
+previous work: the resources used to represent the quantum system are
+in principle unrelated to the resources available to the various
+observers. We conjecture that this asymmetry may prove key to
+resolving some of the quantum paradoxes.
 

### 2016-11-26 proposal/prop.tex
p

@@
 quantum computation from this resource-aware perspective. Our initial
-result in that domain showed how subtle the issues can be~\cite{usat}:
+results in that domain showed how subtle the issues can be~\cite{usat}:
 a straightforward replacement of the complex numbers by a finite field
@@
 or \verb|P2|) independently of the observer (\verb|Q| in this
-case). Indeed the observation \verb|x=4| cannot said to have an
+case). Indeed the observation \verb|x=4| cannot be said to have an
 existence independently from the interaction between \verb|P1| and
@@
 representing a pure mathematical function. Instead \emph{the meaning
-  of a computational process is its observable behavior.} It is not
-too difficult to imagine that, in the presence of multiple interacting
-observers, the behavior observed by just one agent would appear to
-involve hidden variables or action at a distance. The well-established
-theory of observation of concurrent processes and their
-equivalences~\cite{Hennessy1989} relies on neither.
+  of a computational process is its observable behavior.} In this
+computational analogue to the theory of controlled open quantum
+systems, it is not too difficult to imagine that, in the presence of
+multiple interacting observers, the behavior observed by just one
+agent would appear to involve hidden variables or action at a
+distance. The well-established theory of observation of concurrent
+processes and their equivalences~\cite{Hennessy1989} relies on
+neither.
 
@@
 This is the most developed part of our current investigation and is
-presented in greater detail than the other proposed activities. As
-argued in the previous sections, given fixed finite resources, it is
-only possible to estimate the quantum probabilities within an interval
-of confidence. It is therefore natural to propose the notion of a
+presented in greater detail than the other proposed activities. It
+relies on current unpublished results. As argued in the previous
+sections, given fixed finite resources, it is only possible to
+estimate the quantum probabilities within an interval of
+confidence. It is therefore natural to propose the notion of a
 ``quantum interval-valued probability measure'' that combines the
@@
 of Gleason, Bell, and Kochen-Specker for quantum interval-valued
-probability measures. Revisit the Meyer-Mermin debate in this
-mathematical framework.
+probability measures. Revisit the Meyer-Mermin debate and its
+generalizations in this mathematical framework.
 
@@
 
+The nature of quantum mechanics realized in terms of discrete fields is
+amenable to direct computational exploration for reasonable field sizes. We
+have established a set of utility libraries in Mathematica that supports a
+wide variety of such numerical experiments, with Fig.~\ref{fig_qm} being an
+example of the typical output.
+
+Concurrently to this effort, we are also building on our previous
+work~\cite{qhaskell,DBLP:journals/entcs/AltenkirchGVS07,DBLP:journals/entcs/Vi\
+zzottoCS08,DBLP:conf/wollic/VizzottoBS09,DBLP:conf/sbmf/VizzottoLS09,1166040}
+to build semantically well-founded implementations of the computational
+models investigated in this proposal.  The aim of these implementations is
+two-fold: (i) to provide an experimental testbed that complements the
+Mathematica libraries in which discrete quantum algorithms can be simulated;
+and (ii) to establish connections between discrete quantum programming
+concepts and classical programming concepts.
+ We would also like to simulate physical phenomena by using DQCq
+ \cite{OrtizEtAl2001,SommEtAl2002}.
+
+\paragraph*{Proposed Activities.}
+\begin{itemize}
+\item We plan to make our software available for educational and
+  research purposes.
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\noindent (A) {\em Integration of research and education:} Courses on
+advanced computational models and quantum information will be further
+developed at Indiana University to communicate the basic concepts and tools
+discussed in this proposal. Dr. Ortiz taught courses on ``Quantum information   
+and Computation'' and Dr. Sabry has taught courses on ``Quantum Computing''
+for graduate students.  These courses were highly appreciated by the students
+as noted by their evaluations in making the material extremely accessible and
+interesting.  Dr.\ Hanson has taught courses on scientific visualization and
+mathematical modeling with emphasis on high-dimensional mathematics.  His
+numerous Siggraph course presentations are embodied in his 2006 book {\it       
+Visualizing Quaternions\/}, which remains the definitive treatment of the
+subject for computer science and data analysis applications and has sold
+thousands of copies. As a part of Dr.\ Hanson's commitment to exposing and
+explaining the elements of higher mathematics to the public, he has recently
+led the design of a free iPhone App, {\it 4Dice\/}, that for the first time
+makes available an interactive treatment of a correctly imaged simulation of
+the appearance of a hypercube, realizing interactively his YouTube animation
+of the same name.  This framework is now being generalized for a broad family
+of iPhone Apps to permit the hands-on study of high-dimensional mathematics.
+The PIs plan to engage high school students or undergraduates in the
+implementation of some of the ideas and the exploration of finite geometry.
+The PIs have a long standing commitment to K-12 science and math education
+(see also (C) below). The collaborative group efforts will provide students,
+as well as the PIs with a unique learning experience. The broadened
+perspectives gained through those efforts will contribute to the PIs
+effectiveness as teachers and mentors. They also will enable to better
+prepare students and postdocs for productive careers in an increasingly
+competitive global economy. Students and postdocs are encouraged to pursue
+collaborative research leading to a broader scientific program. This is
+highlighted by the PIs students' close contact with LANL, the Perimeter
+Institute, and the Institute for Quantum Computing at Waterloo.
+
+\medskip
+\noindent (B) {\em Broadening the participation of underrepresented groups:}
+Indiana University is engaged in attracting women and minorities in all
+ranks. Several programs are aimed at specifically attracting outstanding
+students into physics and computer science, and to expanding the pool of
+candidates for fellowships. Targeted recruitment of minority graduate
+students is facilitated by the Falicov Fellowship established in 2006. In
+recent years, the School of Informatics and Computing has been fortunate to
+hire several women and minorities for faculty positions, and we have been
+working toward increasing the number of women and minorities among our
+student population. To assist with this process, the PIs will encourage women
+and minorities to apply for graduate positions as well as undergraduate
+positions that may be made available by the grant and REU
+supplements. Dr. Ortiz has minority students and Dr. Sabry has graduated a
+female Ph.D. in 2005 and is currently assisting on the Ph.D. committees of
+several others. Efforts will be made to broaden diversity.
+
+\medskip
+\noindent (C) {\em Enhancing infrastructure and outreach:} Dr. Ortiz has
+pursued broad outreach by giving talks on astronomy/astrophysics in the local
+schools at Bloomington, Indiana, and by an interview in the public radio on
+quantum information. Dr. Ortiz is also guiding a high school student in work
+on interferometry in two and three slit experiments. Dr. Ortiz also guides
+undergraduate research. Dr.\ Hanson plans to add interactive exploration of
+the geometry of quantum computing (see Fig.~\ref{fig_qm}) to the suite of
+educational iPhone Apps currently being developed. All source code produced
+by this project will be made freely available via the web, and the results
+will be disseminated via technical reports, conference papers, and journal
+articles.  The software and concepts we have developed in the past have been
+employed by a wide variety of commercial and noncommercial users.  Thus, we
+expect that the successful completion of the proposed research will
+contribute to the understanding of quantum and semi quantum computation. The
+educational benefits that will flow from this proposal will extend beyond the
+students of the participating research groups. The knowledge gained through
+participation in the proposed research will further strengthen the
+effectiveness of these outreach activities.
+
+Applying within the university.. NSF funding would help us to get
+critical mass; new engineering program; credibility importance
+university will fund; new lab entanglement
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{PI Team and Prior NSF Support}
+
+There was no recent NSF support for Dr. Ortiz and Dr. Hanson. In the
+summer of 2011, Dr. Sabry received in collaboration with two of his
+colleagues two NSF grants: \emph{Effectful Software Contracts} with
+Dr. Amal Ahmed and \emph{Reversible Concurrency} with Dr. Geoffrey
+Brown. Both proposals are in their initial stages and no significant
+results have appeared yet.
 

### 2016-11-27 proposal/prop.tex
prop.tex \subsection{Classical Probability Spaces} Reorder reference...

@@
 definition of probability space on the uncountable and
-uncomputable~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}
-real interval $[0,1]$. This interval includes numbers like
+uncomputable real
+interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
+This interval includes numbers like
 $0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether

### 2016-11-27 proposal/prop.tex
prop

@@
 
-The nature of quantum mechanics realized in terms of discrete fields is
-amenable to direct computational exploration for reasonable field sizes. We
-have established a set of utility libraries in Mathematica that supports a
-wide variety of such numerical experiments, with Fig.~\ref{fig_qm} being an
-example of the typical output.
-
-Concurrently to this effort, we are also building on our previous
-work~\cite{qhaskell,DBLP:journals/entcs/AltenkirchGVS07,DBLP:journals/entcs/Vi\
-zzottoCS08,DBLP:conf/wollic/VizzottoBS09,DBLP:conf/sbmf/VizzottoLS09,1166040}
-to build semantically well-founded implementations of the computational
-models investigated in this proposal.  The aim of these implementations is
-two-fold: (i) to provide an experimental testbed that complements the
-Mathematica libraries in which discrete quantum algorithms can be simulated;
-and (ii) to establish connections between discrete quantum programming
-concepts and classical programming concepts.
- We would also like to simulate physical phenomena by using DQCq
- \cite{OrtizEtAl2001,SommEtAl2002}.
-
-\paragraph*{Proposed Activities.}
-\begin{itemize}
-\item We plan to make our software available for educational and
-  research purposes.
-\end{itemize}
+The nature of quantum mechanics realized in terms of discrete fields
+and finitely-communicable probability estimates is amenable to direct
+computational exploration for reasonable field sizes and observational
+accuracy. We have established a set of utility libraries in
+Mathematica that supports a wide variety of such numerical
+experiments. Concurrently to this effort, we are also building on our
+previous
+work~\cite{VDS2009,AGVS2007,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
+to build semantically well-founded implementations of the
+computational models investigated in this proposal.  The aim of these
+implementations is two-fold: (i) to provide an experimental testbed to
+simulate physical phenomena (e.g.~\cite{OrtizEtAl2001,SommEtAl2002})
+that complements the Mathematica libraries in which quantum algorithms
+can be simulated; and (ii) to establish connections between quantum
+programming concepts and classical programming concepts.  We plan to
+make our software available for educational and research purposes.
 
@@
 advanced computational models and quantum information will be further
-developed at Indiana University to communicate the basic concepts and tools
-discussed in this proposal. Dr. Ortiz taught courses on ``Quantum information   
-and Computation'' and Dr. Sabry has taught courses on ``Quantum Computing''
-for graduate students.  These courses were highly appreciated by the students
-as noted by their evaluations in making the material extremely accessible and
-interesting.  Dr.\ Hanson has taught courses on scientific visualization and
-mathematical modeling with emphasis on high-dimensional mathematics.  His
-numerous Siggraph course presentations are embodied in his 2006 book {\it       
-Visualizing Quaternions\/}, which remains the definitive treatment of the
-subject for computer science and data analysis applications and has sold
-thousands of copies. As a part of Dr.\ Hanson's commitment to exposing and
-explaining the elements of higher mathematics to the public, he has recently
-led the design of a free iPhone App, {\it 4Dice\/}, that for the first time
-makes available an interactive treatment of a correctly imaged simulation of
-the appearance of a hypercube, realizing interactively his YouTube animation
-of the same name.  This framework is now being generalized for a broad family
-of iPhone Apps to permit the hands-on study of high-dimensional mathematics.
-The PIs plan to engage high school students or undergraduates in the
-implementation of some of the ideas and the exploration of finite geometry.
-The PIs have a long standing commitment to K-12 science and math education
-(see also (C) below). The collaborative group efforts will provide students,
-as well as the PIs with a unique learning experience. The broadened
-perspectives gained through those efforts will contribute to the PIs
-effectiveness as teachers and mentors. They also will enable to better
-prepare students and postdocs for productive careers in an increasingly
-competitive global economy. Students and postdocs are encouraged to pursue
-collaborative research leading to a broader scientific program. This is
-highlighted by the PIs students' close contact with LANL, the Perimeter
-Institute, and the Institute for Quantum Computing at Waterloo.
+developed at Indiana University to communicate the basic concepts and
+tools discussed in this proposal. Dr. Ortiz taught courses on
+``Quantum information and Computation'' and Dr. Sabry has taught
+courses on ``Quantum Computing'' for graduate students.  These courses
+were highly appreciated by the students as noted by their evaluations
+in making the material extremely accessible and interesting.  The PIs
+plan to engage high school students or undergraduates in the
+implementation of some of the ideas and the exploration of finite
+geometry.  The PIs have a long standing commitment to K-12 science and
+math education (see also (C) below). The collaborative group efforts
+will provide students, as well as the PIs with a unique learning
+experience. The broadened perspectives gained through those efforts
+will contribute to the PIs effectiveness as teachers and mentors. They
+also will enable to better prepare students and postdocs for
+productive careers in an increasingly competitive global
+economy. Students and postdocs are encouraged to pursue collaborative
+research leading to a broader scientific program. This is highlighted
+by the PIs students' close contact with LANL, the Perimeter Institute,
+and the Institute for Quantum Computing at Waterloo.
 
@@
 \medskip
-\noindent (C) {\em Enhancing infrastructure and outreach:} Dr. Ortiz has
-pursued broad outreach by giving talks on astronomy/astrophysics in the local
-schools at Bloomington, Indiana, and by an interview in the public radio on
-quantum information. Dr. Ortiz is also guiding a high school student in work
-on interferometry in two and three slit experiments. Dr. Ortiz also guides
-undergraduate research. Dr.\ Hanson plans to add interactive exploration of
-the geometry of quantum computing (see Fig.~\ref{fig_qm}) to the suite of
-educational iPhone Apps currently being developed. All source code produced
-by this project will be made freely available via the web, and the results
-will be disseminated via technical reports, conference papers, and journal
-articles.  The software and concepts we have developed in the past have been
-employed by a wide variety of commercial and noncommercial users.  Thus, we
-expect that the successful completion of the proposed research will
-contribute to the understanding of quantum and semi quantum computation. The
-educational benefits that will flow from this proposal will extend beyond the
-students of the participating research groups. The knowledge gained through
-participation in the proposed research will further strengthen the
-effectiveness of these outreach activities.
-
-Applying within the university.. NSF funding would help us to get
-critical mass; new engineering program; credibility importance
-university will fund; new lab entanglement
+\noindent (C) {\em Enhancing infrastructure and outreach:} Dr. Ortiz
+has pursued broad outreach by giving talks on astronomy/astrophysics
+in the local schools at Bloomington, Indiana, and by an interview in
+the public radio on quantum information. Dr. Ortiz is also guiding a
+high school student in work on interferometry in two and three slit
+experiments. Dr. Ortiz also guides undergraduate research. All source
+code produced by this project will be made freely available via the
+web, and the results will be disseminated via technical reports,
+conference papers, and journal articles.  The software and concepts we
+have developed in the past have been employed by a wide variety of
+commercial and noncommercial users.  Thus, we expect that the
+successful completion of the proposed research will contribute to the
+understanding of quantum and semi quantum computation. The educational
+benefits that will flow from this proposal will extend beyond the
+students of the participating research groups. The knowledge gained
+through participation in the proposed research will further strengthen
+the effectiveness of these outreach activities.
 
@@
 
-There was no recent NSF support for Dr. Ortiz and Dr. Hanson. In the
-summer of 2011, Dr. Sabry received in collaboration with two of his
-colleagues two NSF grants: \emph{Effectful Software Contracts} with
-Dr. Amal Ahmed and \emph{Reversible Concurrency} with Dr. Geoffrey
-Brown. Both proposals are in their initial stages and no significant
-results have appeared yet.
-
-Over the past several years, the PI, together with other IU faculty
+Over the past several years, the PIs, together with other IU faculty
 members and students, has formed a group whose main interest is the
@@
 mathematical foundations of quantum computation and
-complexity~\cite{AGVS2007,VAS2006},
-adiabatic quantum computing, quantum logic, classical and quantum
-reversible programming languages~\cite{Sabry:2003:MQC:871895.871900},
-analog computation and its limits, and optical computing. During the
-last year, our discussions have revolved around formulating variants
-of quantum mechanics that are computable and that are as close to
-possible to classical computing. Several preliminary results have
-emerged from our collaboration~\cite{usat,finiteQC,geometry2013,DQT2014}, and the group
+complexity~\cite{AGVS2007,VAS2006}, adiabatic quantum computing,
+quantum logic, classical and quantum reversible programming
+languages~\cite{Sabry:2003:MQC:871895.871900}, analog computation and
+its limits, and optical computing. During the last year, our
+discussions have revolved around formulating variants of quantum
+mechanics that are computable and that are as close to possible to
+classical computing. Several preliminary results have emerged from our
+collaboration~\cite{usat,finiteQC,geometry2013,DQT2014}, and the group
 is very excited about the potential implications of those
@@
 
-In the past five years, Prof. Sabry received one NSF grant (award
-number 1217454) titled \emph{Information Effects} for the amount of
-\$275,319.00 with start and end dates of 1 September 2012 -- 31 August
-2016.
+Applying within the university.. NSF funding would help us to get
+critical mass; new engineering program; credibility importance
+university will fund; new lab entanglement
+
+There was no recent NSF support for Dr. Ortiz. In the past five years,
+Prof. Sabry received one NSF grant (award number 1217454) titled
+\emph{Information Effects} for the amount of \$275,319.00 with start
+and end dates of 1 September 2012 -- 31 August 2016.
 

### 2016-11-27 proposal/prop.tex
p

@@
   inner product needed for conventional quantum mechanics. Using this
-  theory to analyze the Deutsch -Jozsa algorithm reveals that the
+  theory to analyze the Deutsch-Jozsa algorithm reveals that the
   characteristic of the finite field plays an essential role: as the
@@
 plan to engage high school students or undergraduates in the
-implementation of some of the ideas and the exploration of finite
-geometry.  The PIs have a long standing commitment to K-12 science and
-math education (see also (C) below). The collaborative group efforts
-will provide students, as well as the PIs with a unique learning
-experience. The broadened perspectives gained through those efforts
-will contribute to the PIs effectiveness as teachers and mentors. They
-also will enable to better prepare students and postdocs for
-productive careers in an increasingly competitive global
-economy. Students and postdocs are encouraged to pursue collaborative
-research leading to a broader scientific program. This is highlighted
-by the PIs students' close contact with LANL, the Perimeter Institute,
-and the Institute for Quantum Computing at Waterloo.
+implementation of some of the ideas.  The PIs have a long standing
+commitment to K-12 science and math education (see also (C)
+below). The collaborative group efforts will provide students, as well
+as the PIs with a unique learning experience. The broadened
+perspectives gained through those efforts will contribute to the PIs
+effectiveness as teachers and mentors. They also will enable to better
+prepare students and postdocs for productive careers in an
+increasingly competitive global economy. Students and postdocs are
+encouraged to pursue collaborative research leading to a broader
+scientific program. This is highlighted by the PIs students' close
+contact with LANL, the Perimeter Institute, and the Institute for
+Quantum Computing at Waterloo.
 
@@
 
-Over the past several years, the PIs, together with other IU faculty
-members and students, has formed a group whose main interest is the
-study of paradigms of computing that either arise in nature or are
-inspired by natural phenomena. The PI is especially interested in how
-the laws of physics can inspire and guide our abstract computational
-models, as well as exposing new insights into the computational
-framework behind the natural world and the computability of physical
-theory. Our group has been active in several areas related to the
-theory behind quantum computation. Particular areas include:
-mathematical foundations of quantum computation and
+\paragraph*{PI Team.} Over the past several years, the PIs, together
+with other IU faculty members and students, have formed a group whose
+main interest is the study of paradigms of computing that either arise
+in nature or are inspired by natural phenomena. The PIs are especially
+interested in how the laws of physics can inspire and guide our
+abstract computational models, as well as exposing new insights into
+the computational framework behind the natural world and the
+computability of physical theory. Our group has been active in several
+areas related to the theory behind quantum computation. Particular
+areas include: mathematical foundations of quantum computation and
 complexity~\cite{AGVS2007,VAS2006}, adiabatic quantum computing,
@@
 languages~\cite{Sabry:2003:MQC:871895.871900}, analog computation and
-its limits, and optical computing. During the last year, our
+its limits, and optical computing. During the past several years, our
 discussions have revolved around formulating variants of quantum
@@
 programme related to its applications to problem areas that have
-traditionally been outside the conceptual framework of programming
-language research.
-
-Applying within the university.. NSF funding would help us to get
-critical mass; new engineering program; credibility importance
-university will fund; new lab entanglement
-
-There was no recent NSF support for Dr. Ortiz. In the past five years,
-Prof. Sabry received one NSF grant (award number 1217454) titled
-\emph{Information Effects} for the amount of \$275,319.00 with start
-and end dates of 1 September 2012 -- 31 August 2016.
-
-% (c) a summary of the results of the completed work, including
-% accomplishments, supported by the award. The results must be
-% separately described under two distinct headings, Intellectual Merit
-% and Broader Impacts;
+traditionally been outside the conceptual framework of quantum
+mechanics and programming language research. This proposal, if funded,
+will give our group more recognition within the university which, at
+this point, is committed to generously funding several ``emerging
+areas of research''. With the establishment of a new Intelligent
+Systems Engineering at Indiana University with a focus nanoscale
+sensors and quantum engineering and the recent hires in Physics in
+experimental atomic physics, ion-trap quantum simulation, computation,
+and measurement, the PI group is in an excellent position to receive
+additional funding from the University to reach a critical mass of
+quantum information researchers.
+
+\paragraph*{Prior Support.} There was no recent NSF support for
+Dr. Ortiz. In the past five years, Prof. Sabry received one NSF grant
+(award number 1217454) titled \emph{Information Effects} for the
+amount of \$275,319.00 with start and end dates of 1 September 2012 --
+31 August 2016.
+
+\paragraph*{Intellectual Merit.} Computing is about processing
+information. Physically speaking, information, like energy, is a
+resource that obeys a conservation principle: information can never be
+created nor destroyed; it is just transformed. Traditional models of
+computation, however, have not embraced this conservation of
+information as an explicit principle. Instead this principle appears,
+after the fact, in applications such as information-flow security
+which treats the amount of information released to the environment as
+a possible security leak and such as differential privacy which
+intentionally releases some random information to the user to confuse
+potential attackers. This project has instead embraced the principle
+of conservation of information as a key foundation for the design of
+computational models. In one perspective, computation in these models
+is constructed from reversible transformations that act on topological
+spaces, deforming them, stretching them, and shrinking them but never
+cutting nor glueing. The first main result of this project was the
+design and implementation of a programming language which captures
+these ideas and realizes them in the context of the new foundational
+framework of Homotopy Type Theory. This framework combines ideas from
+mathematics, logic, physics, and computation in a way that accounts
+for a newly-recognized higher-dimensional structure of types. This
+idea enabled us to not only represent programs as reversible
+deformations but also to represent the reversible deformations
+themselves as higher-level programs implementing reversible
+optimizations of the underlying lower-level programs. In a second
+breakthrough, viewing the higher-level programs as distinct proofs of
+reversibility enabled the definition of types whose natural
+cardinality is fractional. Having computations that manipulate
+fractional types opens the door for a rich and novel class of
+applications in which resource creation and resource use are
+separated. This idea brings speedups and convenience in a way that is
+similar to the speedup and convenience brought by the use of credit
+cards to complete transactions without necessarily having the money at
+hand: the monetary resource can be consumed by the merchant and only
+later be reconciled by the buyer.
+
+\paragraph*{Broader Impacts.} The idea of reversible computation and
+its connection to quantum mechanics is at the heart of one of the
+deepest mysteries in the universe. Any progress or theory that
+explains physical principles computationally is likely to change our
+worldview impacting everything from philosophy and religion to all
+conventional sciences. On the development of researchers, the project
+resulted in the graduation of one Ph.D. student with another one
+expected to graduate in Spring 2017, the current supervision of two
+additional Ph.D. students, the graduation of an MS student, and the
+hosting of a visiting scholar.
+
+\paragraph*{Publications.} Several papers were published to report on
+the results. On the foundational side, we have the following papers:
+\begin{itemize}
+\item Computing with Semirings and Weak Rig Groupoids, European
+  Symposium on Programming, 2016.
+\item Superstructural Reversible Logic, International Workshop on
+  Linearity, 2014.
+\item Theseus: A High Level Language for Reversible
+  Computing. Work-in-Progress report in the Conference on Reversible
+  Computation, 2014.
+\item Discrete Quantum Theories, J. Phys. A: Math. Theor. 2014.
+\item Geometry of Discrete Quantum Computing, J. Phys. A:
+  Math. Theor. 2013.
+\item Isomorphic Interpreters from Logically Reversible Abstract
+  Machines. Workshop on Reversible Computation 2012.
+\end{itemize}
+On the applications side, we have the following papers: 
+\begin{itemize}
+\item Copredication in Homotopy Type Theory: A homotopical approach
+  for formal semantics of natural languages. Workshop on Natural
+  Language and Computer Science, 2016.
+\item Contract Monitoring Semantics as Patterns of
+  Communication. International Conference on Functional Programming,
+  2015.
+\item Extensible Effects: An Alternative to Monad
+  Transformers. Haskell Symposium, 2013.
+\item Encoding Secure Information Flow with Restricted Delegation and
+  Revocation in Haskell. Workshop on Functional Programming Concepts
+  in Domain-Specific Languages, 2013.
+\end{itemize}                                                                          
+In addition to the publications, Dr. Sabry and collaborators maintain
+a public repository with software related to the project. Dr. Sabry
+was also invited to give talks at several venues, most notably:
+\begin{itemize}
+\item Colloquiumfest, University of Saskatchewan, Canada, 2014 
+\item Workshop on Quantum Information and Foundations of Quantum
+  Mechanics, University of British Columbia, Vancouver, Canada, 2013
+\end{itemize}
 
@@
 
-\paragraph*{Intellectual Merit.}
-
-\paragraph*{Broader Impacts.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-11-27 proposal/prop.tex
prop.tex \subsection{Measuring Probabilities: Buffon's Needle Problem} Add citation...

@@
   probability} (which we will revisit when moving to the quantum
-case), to determine the probability of an event, we run $N$
+case)~\cite{Venn1876,Hajek2012}, 
+to determine the probability of an event, we run $N$
 independent trials which gives us an approximation of the (assumed)

### 2016-11-27 proposal/prop.tex
with andy

@@
   specification of a possible probability measure that would be
-  induced by a system whose current state is $\ket{0}$:
-\[
-\mu\left(\mathbb{0}\right)=0,\quad
-\mu\left(\mathbb{1}\right)=1,\quad
-\mu\left(\proj{0}\right)=1,\quad
-\mu\left(\proj{1}\right)=0,\quad
-\mu\left(\proj{\ps}\right)=1/2,\quad
-\ldots
-\]
-Note that, similarly to the classical case, the probability of
-$\mathbb{1}$ is 1 and the probability of collections of orthogonal
-events (e.g., $\proj{0}+\proj{1}$) is the sum of the individual
-probabilities.  A collection of non-orthogonal events (e.g.,
-$\proj{0}$ and $\proj{\ps}$) is however not even a valid event. In the
-classical example, we argued that each probability measure is uniquely
+  induced by a system whose current state is $\ket{0}$,
+  $\mu\left(\mathbb{0}\right)=0$, $\mu\left(\mathbb{1}\right)=1$,
+  $\mu\left(\proj{0}\right)=1$, $\mu\left(\proj{1}\right)=0$,
+  $\mu\left(\proj{\ps}\right)=1/2$, \ldots. Note that, similarly to
+  the classical case, the probability of $\mathbb{1}$ is 1 and the
+  probability of collections of orthogonal events (e.g.,
+  $\proj{0}+\proj{1}$) is the sum of the individual probabilities.  A
+  collection of non-orthogonal events (e.g., $\proj{0}$ and
+  $\proj{\ps}$) is however not even a valid event. In the classical
+  example, we argued that each probability measure is uniquely
   determined by two actual coins. A similar (but much more subtle)
@@
   mechanics and Gleason's theorem, it turns out that for large enough
-quantum systems, each probability measure is uniquely determined by an
-actual quantum state as discussed next.
+  quantum systems, each probability measure is uniquely determined by
+  an actual quantum state as discussed next.
 \end{example}
@@
 induces a probability measure $\mu_{\rho}^{B}$ defined
-as follows~\cite{peres1995quantum,544199,Jaeger2007}:
-\[
-\mu_{\rho}^{B}\left(P\right) = 
-\Tr\left(\rho P\right) = 
-\sideset{}{_{j=1}^{N}}\sum q_{j}\mu_{\phi_{j}}^{B}\left(P\right)
-\]
+as~\cite{peres1995quantum,544199,Jaeger2007}
+$\mu_{\rho}^{B}\left(P\right) = \Tr\left(\rho P\right) =
+\sideset{}{_{j=1}^{N}}\sum q_{j}\mu_{\phi_{j}}^{B}\left(P\right)$.
 Conversely every probability measure must be of this form.
@@
 \item For any projection $P$,
-\begin{equation}
-\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
-\end{equation}
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have:
-\begin{equation}
-\bar{\mu}\left(\sideset{}{_{i=1}^{N}}\sum P_{i}\right)\subseteq\sideset{}{_{i=1}^{N}}\sum\bar{\mu}\left(P_{i}\right)
-\label{eq:QuantumInterval-valuedProbability-Inclusion}
-\end{equation}
+  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
+\item For a set of mutually orthogonal projections
+  $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
+  $\bar{\mu}\left(\sideset{}{_{i=1}^{N}}\sum
+    P_{i}\right)\subseteq\sideset{}{_{i=1}^{N}}\sum\bar{\mu}\left(P_{i}\right)$.
 \end{itemize}
@@
 \item $\bar{\mu}$ is called convex if
-\begin{equation}
-  \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
-\end{equation}
+  $\bar{\mu}\left(P_{0}\vee
+    P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
   for all commuting $P_{0},P_{1}\in\events$.
@@
 \begin{center}
-\includegraphics[scale=0.5]{measure4.pdf}
+\includegraphics[scale=0.48]{measure4.pdf}
 \end{center}
@@
 
+\begin{figure}
+\begin{center}
+  \includegraphics[scale=0.48]{HoughLineData.pdf}
+\end{center}
+  \caption{Curves of possible line parameters determined by noisy
+    data samples on a straight line in 2D space.}
+\label{houghline.fig}
+\end{figure}
+
+%%%%%
+\subsection{Proposed Activity V: Applications}
+
+A classic evidence-accumulation method known as the Hough
+transform~\cite{BallardGenHough1981}, which is very closely related to
+Bayesian evidence accumulation
+methods~\cite{CrandallEtal2005,CrandallEtal2006}, provides another
+example of how our proposal to define physical theories without exact
+real numbers could be combined with the measurement process. Simply
+described, the Hough transform as an abstraction of Bayesian schemes
+starts with a model of the theory being measured, typically a model
+that would ordinarily be treated {\it after\/} gathering the data by
+applying least squares to choose the optimal parameters.  But in this
+method, instead of thinking of, say, the model of a straight line
+$\hat{\mathbf{n}}\cdot \mathbf{x} = d$ as an equation for the points
+on a line $ \mathbf{x}_{i} = (x_{i},y_{i})$, we think of it as a
+time-accumulating {\it set\/} of equations for the distance $d$ of the
+nearest point on the line and the direction
+$ \hat{\mathbf{n}} = (\cos \theta, \sin \theta)$ from the origin to
+that point (the direction perpendicular to the line).  Thus each point
+of {\it evidence\/}, $(x_{i},y_{i})$, produces an {\it equation in the
+  parameter space\/} that is effectively a plot of all the possible
+values of $d(\theta)$ as a function of the possible angular directions
+$\theta$ pointing to the family of all possible lines.  A typical
+result from a set of errorful (it is impossible to measure real
+numbers, we recall) data measurements of points on a hypothetical
+straight line is shown in Fig.~\ref{houghline.fig}.
+
+The interesting step for us is now to realize that the {\it parameter
+  curves\/} shown in the figure do not need, or indeed, must not, be
+themselves infinitely precise real numbers, but they must themselves
+incorporate in some way a theory consistent with forbidding absolute
+precision.  In practice, then, the sinusoidal lines in Figure
+\ref{houghline.fig} all become fuzzy, and the accumulation of these
+fuzzy distributions produces peaks of likelihood around the values
+$(d_0, \theta_0)$ that are the optimal choices for the line describing
+the set of data.  Note that even {\it one\/} data point provides
+evidence on a set of hypotheses. The simple analysis we have outlined
+here is easily extended to much more complex situations in higher
+dimensions (see, e.g.,~\cite{BallardGenHough1981}).  Our point here is
+that essentially any physical theory that would ordinarily be
+described by a mathematical model using infinite precision numbers is
+potentially nonsensical from a computational point of view: computer
+scientists know perfectly well, and have been dealing with since the
+time of Turing and Shannon, that every single bit of precision in any
+number has a cost, and that there is not enough energy in the universe
+to computer even one general real number.  Thus the combination of
+physical models that, in some intrinsic fashion, contain only
+computable numbers, with theories of measurement and evidence in the
+fashion of the Hough transform example we have just presented, could
+contain the outline of entirely new ways of understanding what
+mathematical models of the physical world and its measurement actually
+could be.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the results. On the foundational side, we have the following papers:
-\begin{itemize}
-\item Computing with Semirings and Weak Rig Groupoids, European
-  Symposium on Programming, 2016.
-\item Superstructural Reversible Logic, International Workshop on
-  Linearity, 2014.
-\item Theseus: A High Level Language for Reversible
-  Computing. Work-in-Progress report in the Conference on Reversible
-  Computation, 2014.
-\item Discrete Quantum Theories, J. Phys. A: Math. Theor. 2014.
-\item Geometry of Discrete Quantum Computing, J. Phys. A:
-  Math. Theor. 2013.
-\item Isomorphic Interpreters from Logically Reversible Abstract
-  Machines. Workshop on Reversible Computation 2012.
-\end{itemize}
-On the applications side, we have the following papers: 
-\begin{itemize}
-\item Copredication in Homotopy Type Theory: A homotopical approach
-  for formal semantics of natural languages. Workshop on Natural
-  Language and Computer Science, 2016.
-\item Contract Monitoring Semantics as Patterns of
+(1) Computing with Semirings and Weak Rig Groupoids, European
+Symposium on Programming, 2016, (2) Superstructural Reversible Logic,
+International Workshop on Linearity, 2014, (3) Theseus: A High Level
+Language for Reversible Computing. Work-in-Progress report in the
+Conference on Reversible Computation, 2014, (4) Discrete Quantum
+Theories, J. Phys. A: Math. Theor. 2014., (5) Geometry of Discrete
+Quantum Computing, J. Phys. A: Math. Theor. 2013., (6) Isomorphic
+Interpreters from Logically Reversible Abstract Machines. Workshop on
+Reversible Computation 2012. On the applications side, we have the
+following papers: (1) Copredication in Homotopy Type Theory: A
+homotopical approach for formal semantics of natural
+languages. Workshop on Natural Language and Computer Science, 2016.,
+(2) Contract Monitoring Semantics as Patterns of
 Communication. International Conference on Functional Programming,
-  2015.
-\item Extensible Effects: An Alternative to Monad
-  Transformers. Haskell Symposium, 2013.
-\item Encoding Secure Information Flow with Restricted Delegation and
-  Revocation in Haskell. Workshop on Functional Programming Concepts
-  in Domain-Specific Languages, 2013.
-\end{itemize}                                                                          
-In addition to the publications, Dr. Sabry and collaborators maintain
-a public repository with software related to the project. Dr. Sabry
-was also invited to give talks at several venues, most notably:
-\begin{itemize}
-\item Colloquiumfest, University of Saskatchewan, Canada, 2014 
-\item Workshop on Quantum Information and Foundations of Quantum
-  Mechanics, University of British Columbia, Vancouver, Canada, 2013
-\end{itemize}
+2015., (3) Extensible Effects: An Alternative to Monad
+Transformers. Haskell Symposium, 2013., (4) Encoding Secure
+Information Flow with Restricted Delegation and Revocation in
+Haskell. Workshop on Functional Programming Concepts in
+Domain-Specific Languages, 2013. In addition to the publications,
+Dr. Sabry and collaborators maintain a public repository with software
+related to the project. Dr. Sabry was also invited to give talks at
+several venues, most notably the Colloquiumfest, University of
+Saskatchewan, Canada, 2014, and the Workshop on Quantum Information
+and Foundations of Quantum Mechanics, University of British Columbia,
+Vancouver, Canada, 2013
 

### 2016-11-27 proposal/prop.tex
typos

@@
 referring to the $n$th digit of $\pi$ requires more and more resources
-as $n$ gets larger. Taking such resource bounds in consideration is
+as $n$ gets larger. Taking such resource bounds into consideration is
 what founded computer science as a discipline and is crucial for
@@
 theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
-We argue that no matter
-what the results are their impact will be strong. Positive results
-that formulate a computable, with clear resource bounds, theory of
-quantum measurement and quantum probability would be essential for
-understanding and realizing quantum computation. Any negative results
-would redirect research that aims at realizing quantum computation to
-other approaches. At an intellectual level, the results will solve or
-clarify several paradoxes in quantum mechanics, quantum information,
-computability, and complexity theory.
+We argue that no matter what the results are their impact will be
+strong. Positive results that formulate a computable, with clear
+resource bounds, theory of quantum measurement and quantum probability
+would be essential for understanding and realizing quantum
+computation. Any negative results would redirect research that aims at
+realizing quantum computation to other approaches. At an intellectual
+level, the results have the potential to solve or clarify several
+paradoxes in quantum mechanics, quantum information, computability,
+and complexity theory.
 

### 2016-11-27 proposal/prop.tex
typo

@@
 number has a cost, and that there is not enough energy in the universe
-to computer even one general real number.  Thus the combination of
+to compute even one general real number.  Thus the combination of
 physical models that, in some intrinsic fashion, contain only

### 2016-11-27 proposal/prop.tex
From: Sabry, Amr A. Sent: Sunday, November 27, 2016 16:08 To: Tai, Yu-Tsung <yuttai@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu> Subject: Re: a section on Hough and Bayes and computable numbers
I didn’t like the sigma_0^{N-1}. It made many of the formulae difficult to read. I changed all of them to sigma_1^N but perhaps I missed some. Fix them if you have time. Thanks! —Amr

> On Nov 27, 2016, at 4:03 PM, Tai, Yu-Tsung <yuttai@indiana.edu> wrote:
>
> This is a rather small thing... I noticed that some array are

@@
   $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$
-\item For a collection $\left\{ E_{i}\right\} _{i=0}^{N}$ of pairwise
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
   disjoint events, we have
-  $\bar{\mu}\left(\bigcup_{i=0}^{N}E_{i}\right)\subseteq\sum_{i=0}^{N}\bar{\mu}\left(E_{i}\right)$.
+  $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)$.
 \end{itemize}

### 2016-11-27 proposal/prop.tex
prop.tex \section{Background II: Quantum Probability} Updating citations

@@
 \[
-\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sideset{}{_{i=1}^{N}}\sum x_{i}\right|<\epsilon\right)=1\textrm{ .}
+\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sum_{i=1}^{N} x_{i}\right|<\epsilon\right)=1\textrm{ .}
 \]
@@
 particular experiment --- classical physics is
-non-contextual. However, even in classical situations, the structure
+non-contextual~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}. 
+However, even in classical situations, the structure
 of the event space is often only partially known and the precise
@@
 probability measure $\mu:\qevents\rightarrow[0,1]$ formalized using
-the Born rule.
+the Born rule~\cite{Born1983,Mermin2007,Jaeger2007}.
 
@@
   In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
-  be mutually orthogonal~\cite{Griffiths2003} and $N$ must correspond
-  to the dimension of the Hilbert space.
+  be mutually orthogonal~\cite{Griffiths2003,Halmos1957}.
 \item If $P$ is a projection operator, then $\mathbb{1}-P$ is also a
@@
   one-qubit Hilbert space with each event interpreted as a possible
-  post-measurement state. For example, the event $\proj{0}$ indicates
+  post-measurement state~\cite{peres1995quantum,Mermin2007,Jaeger2007}. 
+  For example, the event $\proj{0}$ indicates
   that the post-measurement state will be $\ket{0}$; the probability
@@
 one knows the current state of the quantum system by using the Born
-rule~\cite{Born1983,Mermin2007,Jaeger2007}.  Specifically, for each
+rule.  Specifically, for each
 pure normalized quantum state $\ket{\phi}$, the Born rule induces a
@@
 induces a probability measure $\mu_{\rho}^{B}$ defined
-as~\cite{peres1995quantum,544199,Jaeger2007}
+as
 $\mu_{\rho}^{B}\left(P\right) = \Tr\left(\rho P\right) =
-\sideset{}{_{j=1}^{N}}\sum q_{j}\mu_{\phi_{j}}^{B}\left(P\right)$.
+\sum_{j=1}^{N}
+q_{j}\mu_{\phi_{j}}^{B}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
 Conversely every probability measure must be of this form.
@@
   $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
-  $\bar{\mu}\left(\sideset{}{_{i=1}^{N}}\sum
-    P_{i}\right)\subseteq\sideset{}{_{i=1}^{N}}\sum\bar{\mu}\left(P_{i}\right)$.
+  $\bar{\mu}\left(\sum_{i=1}^{N}
+    P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
 \end{itemize}

### 2016-11-28 proposal/prop.tex
prop.tex Updating citation, and debugs...

@@
   In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
-  be mutually orthogonal~\cite{Griffiths2003,Halmos1957}.
+  be mutually orthogonal~\cite{Griffiths2003,Halmos1957}, and $N$ must be less
+  or equal to the dimension of the Hilbert space.
 \item If $P$ is a projection operator, then $\mathbb{1}-P$ is also a
@@
 section, assuming identical measurements conditions in each repeated
-experiment. For instance, if one wants to determine the probability
-that the spin of a given silver atom is +$\hbar/2$, a Stern-Gerlach
+experiment~\cite{peres1995quantum}. 
+For instance, if one wants to determine the probability
+that the spin of a given silver atom is $+\hbar/2$, a Stern-Gerlach
 apparatus is built where ideally an inhomogeneous magnetic field is
@@
 apparatus~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
-Each of the two discrete values is associated to either +$\hbar/2$ or
--$\hbar/2$, commonly called ``spin up'' and ``spin down'',
+Each of the two discrete values is associated to either $+\hbar/2$ or
+$-\hbar/2$, commonly called ``spin up'' and ``spin down'',
 respectively. By ``counting'' the number of atoms that are deflected
@@
 probability that the prepared state of the silver atom state has spin
-+$\hbar/2$. Notice that a real experiment does not necessarily
+$+\hbar/2$. Notice that a real experiment does not necessarily
 represent an ``ideal measurement''. For example, not all silver atoms

### 2016-11-28 proposal/prop.tex
prop.tex \section{Proposal: General Plan} modifying a littel bit...

@@
   are bound to be approximations represented by intervals of
-  confidence, then by Gleason's theorem, quantum states themselves
-  cannot be infinitely precise. This raises an important philosophical
+  confidence, then quantum states themselves cannot be infinitely precise
+  because Gleason's theorem is no longer applied. 
+  This raises an important philosophical
   question with immense practical relevance in the context of quantum
@@
   be more and more accurately described given more and more
-  resources. In other words, does a Gleason, Bell, or Kochen-Specker
+  resources. In other words, does a Gleason,
+  Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}, 
+  or Kochen-Specker
   theorem still hold in a world with finite resources?  The answer
@@
   knowledge''. This, and similar arguments elegantly expressed by
-  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016},
+  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
   suggest that the quantum state is more like an interactive system in

### 2016-11-28 proposal/prop.tex
prop.tex \subsection{Proposed Activity I: Quantum States as Interactive Processes} Add citations...

@@
 The early formalization of the process of computing using Turing
-machines~\cite{Turing_1937} or the
-$\lambda$-calculus~\cite{Barendregt:Lambda} viewed a computation as
+machines~\cite{Turing_1937,blum2012complexity} or the
+$\lambda$-calculus~\cite{Church1932,Barendregt:Lambda} viewed a computation as
 realizing a mathematical function. From our perspective, the most

### 2016-11-28 proposal/prop.tex
hanson

@@
 \begin{center}
-\includegraphics[scale=0.48]{measure4.pdf}
+\includegraphics[scale=0.38]{measure4.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[scale=0.48]{HoughLineData.pdf}
+  \includegraphics[scale=0.38]{HoughLineData.pdf}
 \end{center}
@@
 ``Quantum information and Computation'' and Dr. Sabry has taught
-courses on ``Quantum Computing'' for graduate students.  These courses
-were highly appreciated by the students as noted by their evaluations
-in making the material extremely accessible and interesting.  The PIs
-plan to engage high school students or undergraduates in the
-implementation of some of the ideas.  The PIs have a long standing
-commitment to K-12 science and math education (see also (C)
-below). The collaborative group efforts will provide students, as well
-as the PIs with a unique learning experience. The broadened
-perspectives gained through those efforts will contribute to the PIs
-effectiveness as teachers and mentors. They also will enable to better
-prepare students and postdocs for productive careers in an
+courses on ``Quantum Computing'' for graduate students.  Dr.\ Hanson
+has taught courses on scientific visualization and mathematical
+modeling with emphasis on high-dimensional mathematics.  His numerous
+Siggraph course presentations are embodied in his 2006 book {\it
+  Visualizing Quaternions\/}, which remains the definitive treatment
+of the subject for computer science and data analysis applications and
+has sold thousands of copies. As a part of Dr.\ Hanson's commitment to
+exposing and explaining the elements of higher mathematics to the
+public, he has recently led the design of a free iPhone App, {\it
+  4Dice\/}, that for the first time makes available an interactive
+treatment of a correctly imaged simulation of the appearance of a
+hypercube, realizing interactively his YouTube animation of the same
+name.  This framework is now being generalized for a broad family of
+iPhone Apps to permit the hands-on study of high-dimensional
+mathematics.  These courses were highly appreciated by the students as
+noted by their evaluations in making the material extremely accessible
+and interesting.  The PIs plan to engage high school students or
+undergraduates in the implementation of some of the ideas.  The PIs
+have a long standing commitment to K-12 science and math education
+(see also (C) below). The collaborative group efforts will provide
+students, as well as the PIs with a unique learning experience. The
+broadened perspectives gained through those efforts will contribute to
+the PIs effectiveness as teachers and mentors. They also will enable
+to better prepare students and postdocs for productive careers in an
 increasingly competitive global economy. Students and postdocs are
@@
 female Ph.D. in 2005 and is currently assisting on the Ph.D. committees of
-several others. Efforts will be made to broaden diversity.
+several others.
 
@@
 \paragraph*{Prior Support.} There was no recent NSF support for
-Dr. Ortiz. In the past five years, Prof. Sabry received one NSF grant
-(award number 1217454) titled \emph{Information Effects} for the
-amount of \$275,319.00 with start and end dates of 1 September 2012 --
-31 August 2016.
+Dr. Ortiz or Dr. Hanson. In the past five years, Prof. Sabry received
+one NSF grant (award number 1217454) titled \emph{Information Effects}
+for the amount of \$275,319.00 with start and end dates of 1 September
+2012 -- 31 August 2016.
 
@@
 the results. On the foundational side, we have the following papers:
-(1) Computing with Semirings and Weak Rig Groupoids, European
-Symposium on Programming, 2016, (2) Superstructural Reversible Logic,
-International Workshop on Linearity, 2014, (3) Theseus: A High Level
-Language for Reversible Computing. Work-in-Progress report in the
-Conference on Reversible Computation, 2014, (4) Discrete Quantum
+(1) Computing with Semirings and Weak Rig Groupoids, ESOP, 2016, (2)
+Superstructural Reversible Logic, Workshop on Linearity, 2014, (3)
+Theseus: A High Level Language for Reversible
+Computing. Work-in-Progress report, RC 2014, (4) Discrete Quantum
 Theories, J. Phys. A: Math. Theor. 2014., (5) Geometry of Discrete
 Quantum Computing, J. Phys. A: Math. Theor. 2013., (6) Isomorphic
-Interpreters from Logically Reversible Abstract Machines. Workshop on
-Reversible Computation 2012. On the applications side, we have the
-following papers: (1) Copredication in Homotopy Type Theory: A
-homotopical approach for formal semantics of natural
-languages. Workshop on Natural Language and Computer Science, 2016.,
-(2) Contract Monitoring Semantics as Patterns of
-Communication. International Conference on Functional Programming,
-2015., (3) Extensible Effects: An Alternative to Monad
-Transformers. Haskell Symposium, 2013., (4) Encoding Secure
+Interpreters from Logically Reversible Abstract Machines. RC 2012. On
+the applications side, we have the following papers: (1) Copredication
+in Homotopy Type Theory: A homotopical approach for formal semantics
+of natural languages. Workshop on Natural Language and Computer
+Science, 2016., (2) Contract Monitoring Semantics as Patterns of
+Communication. ICFP, 2015., (3) Extensible Effects: An Alternative to
+Monad Transformers. Haskell Symposium, 2013., (4) Encoding Secure
 Information Flow with Restricted Delegation and Revocation in

### 2016-11-29 proposal/prop.tex
prop.tex \subsection{Proposed Activity I: Quantum States as Interactive Processes} Add citations...

@@
 interactive system agree with the QBism perspective providing a
-resolution to the same paradoxes (e.g., EPR and Wigner's friend)?
+resolution to the same paradoxes (e.g., EPR~\cite{EPR1935} and Wigner's
+friend~\cite{Wigner1961,Fuchs2010,Fuchs2012})?
 

### 2016-11-29 proposal/prop.tex
prop.tex Fix some typos...

@@
   in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
-  and $\ket{\ps}$ respectively.  All possible vectors of the subspaces
+  and $\ket{\ps}$ respectively.  All possible real vectors of the subspaces
   $\ket{0_{\theta,\gamma}^{\perp}}$ and
@@
   $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
-  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
+  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
+  $\times$ is the usual cross product in $\mathbb{R}^{3}$}
 \end{figure}
@@
 \begin{enumerate}
-\item[(A)] Textbook quantum mechanics is correct
+\item[(A)] Textbook quantum mechanics is correct.
 \item[(B)] There does not exist an efficient classical factoring
-  algorithm
+  algorithm.
 \item[(C)] The extended Church-Turing thesis that probabilistic Turing

### 2016-11-29 proposal/prop.tex
almost done

@@
 probability and hence quantum measurement to a corresponding
-resource-aware setting. In particular, we plan on addressing the
-Meyer-Mermin debate~\cite{PhysRevLett.83.3751, Mermin1999,
-  BarrettKent2004} on the impact of finite precision measurements on
-the relevance of the Kochen-Specker
+resource-aware setting.
+
+In particular, the objectives to be achieved include:
+\begin{itemize}
+\item A computational framework for quantum measurement where quantum
+  systems are described in terms of interactive processes. The
+  framework takes care of the resources required (including the ones
+  related to the observer) to determine a given property of the
+  measured system.
+\item Develop a measurement framework based on quantum interval-valued
+  probabilities measures.
+\item Assess the validity of fundamental theorems of quantum
+  mechanics, such as Gleason, Bell, and Kochen-Specker, in a quantum
+  formulation stripped away of infinite resources. We will aim to
+  provide a definite answer to the Meyer-Mermin
+  debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004} on
+  the impact of finite precision measurements on the relevance of the
+  Kochen-Specker
   theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
+\item Study the computational complexity of quantum theories and
+  simulations based on discrete (computable) fields.
+\end{itemize}
 We argue that no matter what the results are their impact will be
@@
 %%%%%
-\subsection{Proposed Activity IV: Computational Aspects}
+\subsection{Proposed Activity IV: Computational and Simulation Aspects}
 
@@
 
-\begin{figure}
-\begin{center}
-  \includegraphics[scale=0.38]{HoughLineData.pdf}
-\end{center}
-  \caption{Curves of possible line parameters determined by noisy
-    data samples on a straight line in 2D space.}
-\label{houghline.fig}
-\end{figure}
-
-%%%%%
-\subsection{Proposed Activity V: Applications}
-
-A classic evidence-accumulation method known as the Hough
-transform~\cite{BallardGenHough1981}, which is very closely related to
-Bayesian evidence accumulation
-methods~\cite{CrandallEtal2005,CrandallEtal2006}, provides another
-example of how our proposal to define physical theories without exact
-real numbers could be combined with the measurement process. Simply
-described, the Hough transform as an abstraction of Bayesian schemes
-starts with a model of the theory being measured, typically a model
-that would ordinarily be treated {\it after\/} gathering the data by
-applying least squares to choose the optimal parameters.  But in this
-method, instead of thinking of, say, the model of a straight line
-$\hat{\mathbf{n}}\cdot \mathbf{x} = d$ as an equation for the points
-on a line $ \mathbf{x}_{i} = (x_{i},y_{i})$, we think of it as a
-time-accumulating {\it set\/} of equations for the distance $d$ of the
-nearest point on the line and the direction
-$ \hat{\mathbf{n}} = (\cos \theta, \sin \theta)$ from the origin to
-that point (the direction perpendicular to the line).  Thus each point
-of {\it evidence\/}, $(x_{i},y_{i})$, produces an {\it equation in the
-  parameter space\/} that is effectively a plot of all the possible
-values of $d(\theta)$ as a function of the possible angular directions
-$\theta$ pointing to the family of all possible lines.  A typical
-result from a set of errorful (it is impossible to measure real
-numbers, we recall) data measurements of points on a hypothetical
-straight line is shown in Fig.~\ref{houghline.fig}.
-
-The interesting step for us is now to realize that the {\it parameter
-  curves\/} shown in the figure do not need, or indeed, must not, be
-themselves infinitely precise real numbers, but they must themselves
-incorporate in some way a theory consistent with forbidding absolute
-precision.  In practice, then, the sinusoidal lines in Figure
-\ref{houghline.fig} all become fuzzy, and the accumulation of these
-fuzzy distributions produces peaks of likelihood around the values
-$(d_0, \theta_0)$ that are the optimal choices for the line describing
-the set of data.  Note that even {\it one\/} data point provides
-evidence on a set of hypotheses. The simple analysis we have outlined
-here is easily extended to much more complex situations in higher
-dimensions (see, e.g.,~\cite{BallardGenHough1981}).  Our point here is
-that essentially any physical theory that would ordinarily be
-described by a mathematical model using infinite precision numbers is
-potentially nonsensical from a computational point of view: computer
-scientists know perfectly well, and have been dealing with since the
-time of Turing and Shannon, that every single bit of precision in any
-number has a cost, and that there is not enough energy in the universe
-to compute even one general real number.  Thus the combination of
-physical models that, in some intrinsic fashion, contain only
-computable numbers, with theories of measurement and evidence in the
-fashion of the Hough transform example we have just presented, could
-contain the outline of entirely new ways of understanding what
-mathematical models of the physical world and its measurement actually
-could be.
+% \begin{figure}
+% \begin{center}
+%   \includegraphics[scale=0.38]{HoughLineData.pdf}
+% \end{center}
+%   \caption{Curves of possible line parameters determined by noisy
+%     data samples on a straight line in 2D space.}
+% \label{houghline.fig}
+% \end{figure}
+
+% %%%%%
+% \subsection{Proposed Activity V: Applications}
+
+% A classic evidence-accumulation method known as the Hough
+% transform~\cite{BallardGenHough1981}, which is very closely related to
+% Bayesian evidence accumulation
+% methods~\cite{CrandallEtal2005,CrandallEtal2006}, provides another
+% example of how our proposal to define physical theories without exact
+% real numbers could be combined with the measurement process. Simply
+% described, the Hough transform as an abstraction of Bayesian schemes
+% starts with a model of the theory being measured, typically a model
+% that would ordinarily be treated {\it after\/} gathering the data by
+% applying least squares to choose the optimal parameters.  But in this
+% method, instead of thinking of, say, the model of a straight line
+% $\hat{\mathbf{n}}\cdot \mathbf{x} = d$ as an equation for the points
+% on a line $ \mathbf{x}_{i} = (x_{i},y_{i})$, we think of it as a
+% time-accumulating {\it set\/} of equations for the distance $d$ of the
+% nearest point on the line and the direction
+% $ \hat{\mathbf{n}} = (\cos \theta, \sin \theta)$ from the origin to
+% that point (the direction perpendicular to the line).  Thus each point
+% of {\it evidence\/}, $(x_{i},y_{i})$, produces an {\it equation in the
+%   parameter space\/} that is effectively a plot of all the possible
+% values of $d(\theta)$ as a function of the possible angular directions
+% $\theta$ pointing to the family of all possible lines.  A typical
+% result from a set of errorful (it is impossible to measure real
+% numbers, we recall) data measurements of points on a hypothetical
+% straight line is shown in Fig.~\ref{houghline.fig}.
+
+% The interesting step for us is now to realize that the {\it parameter
+%   curves\/} shown in the figure do not need, or indeed, must not, be
+% themselves infinitely precise real numbers, but they must themselves
+% incorporate in some way a theory consistent with forbidding absolute
+% precision.  In practice, then, the sinusoidal lines in Figure
+% \ref{houghline.fig} all become fuzzy, and the accumulation of these
+% fuzzy distributions produces peaks of likelihood around the values
+% $(d_0, \theta_0)$ that are the optimal choices for the line describing
+% the set of data.  Note that even {\it one\/} data point provides
+% evidence on a set of hypotheses. The simple analysis we have outlined
+% here is easily extended to much more complex situations in higher
+% dimensions (see, e.g.,~\cite{BallardGenHough1981}).  Our point here is
+% that essentially any physical theory that would ordinarily be
+% described by a mathematical model using infinite precision numbers is
+% potentially nonsensical from a computational point of view: computer
+% scientists know perfectly well, and have been dealing with since the
+% time of Turing and Shannon, that every single bit of precision in any
+% number has a cost, and that there is not enough energy in the universe
+% to compute even one general real number.  Thus the combination of
+% physical models that, in some intrinsic fashion, contain only
+% computable numbers, with theories of measurement and evidence in the
+% fashion of the Hough transform example we have just presented, could
+% contain the outline of entirely new ways of understanding what
+% mathematical models of the physical world and its measurement actually
+% could be.
 
@@
 \paragraph*{Prior Support.} There was no recent NSF support for
-Dr. Ortiz or Dr. Hanson. In the past five years, Prof. Sabry received
-one NSF grant (award number 1217454) titled \emph{Information Effects}
-for the amount of \$275,319.00 with start and end dates of 1 September
-2012 -- 31 August 2016.
+Dr. Ortiz. In the past five years, Dr. Sabry received one NSF grant
+(award number 1217454) titled \emph{Information Effects} for the
+amount of \$275,319.00 with start and end dates of 1 September 2012 --
+31 August 2016.
 
@@
 the results. On the foundational side, we have the following papers:
-(1) Computing with Semirings and Weak Rig Groupoids, ESOP, 2016, (2)
-Superstructural Reversible Logic, Workshop on Linearity, 2014, (3)
-Theseus: A High Level Language for Reversible
-Computing. Work-in-Progress report, RC 2014, (4) Discrete Quantum
-Theories, J. Phys. A: Math. Theor. 2014., (5) Geometry of Discrete
-Quantum Computing, J. Phys. A: Math. Theor. 2013., (6) Isomorphic
-Interpreters from Logically Reversible Abstract Machines. RC 2012. On
-the applications side, we have the following papers: (1) Copredication
-in Homotopy Type Theory: A homotopical approach for formal semantics
-of natural languages. Workshop on Natural Language and Computer
-Science, 2016., (2) Contract Monitoring Semantics as Patterns of
-Communication. ICFP, 2015., (3) Extensible Effects: An Alternative to
-Monad Transformers. Haskell Symposium, 2013., (4) Encoding Secure
-Information Flow with Restricted Delegation and Revocation in
-Haskell. Workshop on Functional Programming Concepts in
-Domain-Specific Languages, 2013. In addition to the publications,
-Dr. Sabry and collaborators maintain a public repository with software
-related to the project. Dr. Sabry was also invited to give talks at
-several venues, most notably the Colloquiumfest, University of
-Saskatchewan, Canada, 2014, and the Workshop on Quantum Information
-and Foundations of Quantum Mechanics, University of British Columbia,
-Vancouver, Canada, 2013
+\begin{enumerate}
+\item Computing with Semirings and Weak Rig Groupoids, ESOP, 2016
+\item Superstructural Reversible Logic, Workshop on Linearity, 2014
+\item Theseus: A High Level Language for Reversible
+  Computing. Work-in-Progress report, RC 2014
+\item Discrete Quantum Theories, J. Phys. A: Math. Theor. 2014.
+\item Geometry of Discrete Quantum Computing, J. Phys. A:
+  Math. Theor. 2013.
+\item Isomorphic Interpreters from Logically Reversible Abstract
+  Machines. RC 2012. 
+\end{enumerate}
+On the applications side, we have the following papers: 
+\begin{enumerate}
+\item Copredication in Homotopy Type Theory: A homotopical approach
+  for formal semantics of natural languages. Workshop on Natural
+  Language and Computer Science, 2016.
+\item Contract Monitoring Semantics as Patterns of
+  Communication. ICFP, 2015.
+\item Extensible Effects: An Alternative to Monad
+  Transformers. Haskell Symposium, 2013.
+\item Encoding Secure Information Flow with Restricted Delegation and
+  Revocation in Haskell. Workshop on Functional Programming Concepts
+  in Domain-Specific Languages, 2013
+\end{enumerate}
+In addition to the publications, Dr. Sabry and collaborators maintain
+a public repository with software related to the project. Dr. Sabry
+was also invited to give talks at several venues, most notably:
+\begin{itemize}
+\item Colloquiumfest, University of Saskatchewan, Canada, 2014
+\item Workshop on Quantum Information and Foundations of Quantum
+  Mechanics, University of British Columbia, Vancouver, Canada, 2013
+\end{itemize}
 

### 2016-11-29 proposal/prop.tex
final...

@@
 
-\paragraph*{Research Question.} A long term, ultimate, goal of this
-research proposal would be to combine the various pieces into a
-coherent computational model of quantum mechanics that keeps explicit
-track of resources needed to represent the interactive system
-representing the quantum state, its evolution, the observables, and
-the probabilities. Such a computational model of quantum mechanics
-would encompass classical (reversible) computation and potentially
-revolutionize quantum thinking with finite resources. The explicit
-manipulation of resources enables one of key idea that emerged in our
-previous work: the resources used to represent the quantum system are
-in principle unrelated to the resources available to the various
-observers. We conjecture that this asymmetry may prove key to
-resolving some of the quantum paradoxes.
-
-The nature of quantum mechanics realized in terms of discrete fields
-and finitely-communicable probability estimates is amenable to direct
-computational exploration for reasonable field sizes and observational
-accuracy. We have established a set of utility libraries in
-Mathematica that supports a wide variety of such numerical
-experiments. Concurrently to this effort, we are also building on our
-previous
-work~\cite{VDS2009,AGVS2007,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
+A long term, ultimate, goal of this research proposal would be to
+combine the various pieces into a coherent computational model of
+quantum mechanics that keeps explicit track of resources needed to
+represent the interactive system representing the quantum state, its
+evolution, the observables, and the probabilities. Such a
+computational model of quantum mechanics would encompass classical
+(reversible) computation and potentially revolutionize quantum
+thinking with finite resources. The explicit manipulation of resources
+enables one of key idea that emerged in our previous work: the
+resources used to represent the quantum system are in principle
+unrelated to the resources available to the various observers. We
+conjecture that this asymmetry may prove key to resolving some of the
+quantum paradoxes.  The nature of quantum mechanics realized in terms
+of discrete fields and finitely-communicable probability estimates is
+amenable to direct computational exploration for reasonable field
+sizes and observational accuracy. We have established a set of utility
+libraries in Mathematica that supports a wide variety of such
+numerical experiments. Concurrently to this effort, we are also
+building on our previous work~\cite
+{VDS2009,AGVS2007,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
 to build semantically well-founded implementations of the
-computational models investigated in this proposal.  The aim of these
-implementations is two-fold: (i) to provide an experimental testbed to
-simulate physical phenomena (e.g.~\cite{OrtizEtAl2001,SommEtAl2002})
-that complements the Mathematica libraries in which quantum algorithms
-can be simulated; and (ii) to establish connections between quantum
-programming concepts and classical programming concepts.  We plan to
-make our software available for educational and research purposes.
+computational models investigated in this proposal.
+
+\paragraph*{Research Questions.} The aim of these implementations
+include:
+\begin{itemize}
+\item Provide an experimental testbed to simulate physical phenomena
+  (e.g.~\cite {OrtizEtAl2001,SommEtAl2002}) that complements the
+  Mathematica libraries in which quantum algorithms can be simulated;
+\item Establish connections between quantum programming concepts and
+  classical programming concepts. We plan to make our software
+  available for educational and research purposes; and 
+\item Analyze the computational complexity of quantum theories and
+  simulations based on discrete fields. What other (apart from
+  UNIQUE-SAT) supernatural algorithms can be implemented in
+  computational models based on discrete fields?
+\end{itemize}
 

### 2016-11-29 proposal/prop.tex
refs
prob.tex \subsection{Proposed Activity IV: Computational and Simulation Aspects} Add citations...

@@
 \addbibresource{prop.bib}
-\ExecuteBibliographyOptions{sorting=nyt,maxbibnames=5,doi=false,isbn=false,url=false}
+%% \ExecuteBibliographyOptions{sorting=nyt,maxbibnames=5,doi=false,isbn=false,url=false}
+\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
 \usepackage{fullpage}
@@
   This solves the conundrum that the conventional Deutsch-Jozsa
-  algorithm mysteriously continues to work for larger and larger input
+  algorithm~\cite{DeutschJozsa1992,Jaeger2007}
+  mysteriously continues to work for larger and larger input
   functions without any apparent increase in resources.  Our analysis

### 2016-11-29 proposal/prop.tex
prop.tex \subsection{Proposed Activity IV: Computational and Simulation Aspects} Add citations...

@@
 opportune, moment. The embarrassing dilemma was concisely described by
-Aaronson as follows. Consider the following three statements:
+Aaronson as follows~\cite{AaronsonArkhipov2011,BFRDARW2013}. 
+Consider the following three statements:
 \begin{enumerate}
@@
   machines can efficiently simulate any physically realizable model of
-  computation is correct.
+  computation is correct~\cite{BernsteinVazirani1997,Kaye2007}.
 \end{enumerate}

### 2016-11-30 proposal/prop.tex
prop.tex \subsection{Proposed Activity IV: Computational and Simulation Aspects} Add citations...

@@
   $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
-  $\times$ is the usual cross product in $\mathbb{R}^{3}$}
+  $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
 \end{figure}
@@
 founded on the assumption (B) that algorithms like RSA are secure and
-they also have withstood years of attempted attacks. Finally the
+they also have withstood years of attempted
+attacks~\cite{boneh1999twenty,wiki:RSAFactoring}. Finally the
 entire field of complexity theory in computer science which has also
 withstood years of field testing rests, in essence, on assumption
-(C). And yet one of these three statements \emph{must be false}! Indeed
+(C)~\cite{Aaronson2005,Piccinini2015}. 
+And yet one of these three statements \emph{must be false}! Indeed
 if textbook quantum mechanics is false we concede (A). If it is

### 2016-11-30 proposal/prop.tex
prop.tex \section{Broader Impact and Education} Add citation...

@@
 Siggraph course presentations are embodied in his 2006 book {\it
-  Visualizing Quaternions\/}, which remains the definitive treatment
+  Visualizing Quaternions\/}~\cite{Hanson2006}, 
+which remains the definitive treatment
 of the subject for computer science and data analysis applications and

### 2016-11-30 proposal/fac.tex
done

@@
 TeraGrid, I-Light, and the Open Science Grid. Dr. Ortiz (Department of
-Physics) and Dr. Sabry (School of Informatics and Computing) have
-access to departmental license software, as well as access to most
-electronic and hard copy journals through Indiana University
-Libraries, and access to conference facilities for meetings.
+Physics) and Dr. Sabry and Dr. Hanson (School of Informatics and
+Computing) have access to departmental license software, as well as
+access to most electronic and hard copy journals through Indiana
+University Libraries, and access to conference facilities for
+meetings.
 
@@
 
-\noindent A computer server facility specifically serving the Departments of
-Physics and Astronomy is installed in the basement of Swain Hall. This $\sim
-110~m^2$ room has sufficient power and cooling capacity to house 24 racks of
-hardware in a single area for ease of security and maintenance resulting in a
-high-quality, small-scale facility meeting local needs. In addition to the
-ATLAS/DØ Tier-3 Analysis Cluster (22 eight-core 2.66/2.88 GHz Xeon nodes, >60
-TB of raid disk storage), it also houses experimental computing for lattice
-gauge and related calculations, the special partial-wave computing facility
-for the GlueX experiment (including both regular nodes and an experimental
-GPU cluster), computing access for the neutrino group, and servers for the
-Physics and Astronomy Departments. Finally, it also provides an appropriate
-home for interfaces to hardware such as IU\u2019s Data Capacitor, a
-large-scale data storage/access system developed by Indiana University IT
-Services and used heavily by Astronomy.  Indiana University and the
-University of Chicago jointly manage the Midwest Tier2 (MWT2) computing
-center, with hardware split approximately equally between them. The Indiana
-University portion of the MWT2 is located primarily in Indianapolis on the
-campus of Indiana University Purdue University Indianapolis
-(IUPUI). Currently the IUPUI portion of the MWT2 has 1.8M kSi2k of computing
-power and ~200 TB of storage. The CPUs are various AMD and Intel processors
-purchased from several vendors \u2013 a total of 768 cores at IUPUI with
-approximately 2 GB of memory per core. A 1 Gb/s link connects each compute
-node to the Indiana University backbone while storage nodes are connected to
-the backbone with 10 Gb/s connections. The MWT2 is connected to the outside
-world with a 10 Gb/s link.  In addition to the usual desktop units, a
-dedicated room is available containing projection units and a high-definition
-Polycom videoconferencing unit recently acquired using DoE stimulus
-funds. The Department has also requested renovation of a different space to
-house this system as well as other equipment for use in distance learning.
+\noindent A computer server facility specifically serving the
+Departments of Physics and Astronomy is installed in the basement of
+Swain Hall. This $\sim 110~m^2$ room has sufficient power and cooling
+capacity to house 24 racks of hardware in a single area for ease of
+security and maintenance resulting in a high-quality, small-scale
+facility meeting local needs. In addition to the ATLAS/D0 Tier-3
+Analysis Cluster (22 eight-core 2.66/2.88 GHz Xeon nodes, $>$ 60 TB of
+raid disk storage), it also houses experimental computing for lattice
+gauge and related calculations, the special partial-wave computing
+facility for the GlueX experiment (including both regular nodes and an
+experimental GPU cluster), computing access for the neutrino group,
+and servers for the Physics and Astronomy Departments. Finally, it
+also provides an appropriate home for interfaces to hardware such as
+IU's Data Capacitor, a large-scale data storage/access system
+developed by Indiana University IT Services and used heavily by
+Astronomy.  Indiana University and the University of Chicago jointly
+manage the Midwest Tier2 (MWT2) computing center, with hardware split
+approximately equally between them. The Indiana University portion of
+the MWT2 is located primarily in Indianapolis on the campus of Indiana
+University Purdue University Indianapolis (IUPUI). Currently the IUPUI
+portion of the MWT2 has 1.8M kSi2k of computing power and $\sim$ 200
+TB of storage. The CPUs are various AMD and Intel processors purchased
+from several vendors, a total of 768 cores at IUPUI with approximately
+2 GB of memory per core. A 1 Gb/s link connects each compute node to
+the Indiana University backbone while storage nodes are connected to
+the backbone with 10 Gb/s connections. The MWT2 is connected to the
+outside world with a 10 Gb/s link.  In addition to the usual desktop
+units, a dedicated room is available containing projection units and a
+high-definition Polycom videoconferencing unit recently acquired using
+DoE stimulus funds. The Department has also requested renovation of a
+different space to house this system as well as other equipment for
+use in distance learning.
 
@@
 infrastructure and facilities with the mission of enabling world class
-research and instruction
+research and instruction.
 

### 2016-12-02 prop.tex
prop.tex Copy from proposal\prop.tex

--- 2016-11-30 proposal/prop.tex
@@
 quantum computation from this resource-aware perspective. Our initial
-results in that domain showed how subtle the issues can be~\cite{usat}:
-a straightforward replacement of the complex numbers by a finite field
-yields a variant of quantum mechanics in which computationally hard
-problems like UNIQUE-SAT (which decides whether a given Boolean
-formula is unsatisfiable or has exactly one satisfying assignment) can
-be deterministically solved in constant time. To eliminate such
-unrealistic theories requires delicate analysis of the structure of
-the Hilbert space, the process of observation, and the notion of
-probability teasing apart their reliance on the infinitely precise
-real numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is
-to shift focus from the infinitely-specified but not directly
-observable quantum states, to observable measurable properties of
-quantum systems and their probabilities. Furthermore, we insist that
-our theories of measurement and probability only refer to finitely
-communicable evidence within feasible computational bounds. It follows
-that states, observations, and probabilities all become ``fuzzy'',
-i.e., specified by intervals of confidence that can only increase in
-precision if the available resources increase proportionally. Our
-notion of ``fuzzy quantum mechanics'' is related to existing
+results in that domain showed how subtle the issues can
+be~\cite{usat,geometry2013,DQT2014}: a straightforward replacement of
+the complex numbers by a finite field yields a variant of quantum
+mechanics in which computationally hard problems like UNIQUE-SAT
+(which decides whether a given Boolean formula is unsatisfiable or has
+exactly one satisfying assignment) can be deterministically solved in
+constant time. To eliminate such unrealistic theories requires
+delicate analysis of the structure of the Hilbert space, the process
+of observation, and the notion of probability teasing apart their
+reliance on the infinitely precise real
+numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is to
+shift focus from the infinitely-specified but not directly observable
+quantum states, to observable measurable properties of quantum systems
+and their probabilities. Furthermore, we insist that our theories of
+measurement and probability only refer to finitely communicable
+evidence within feasible computational bounds. It follows that states,
+observations, and probabilities all become ``fuzzy'', i.e., specified
+by intervals of confidence that can only increase in precision if the
+available resources increase proportionally. Our notion of ``fuzzy
+quantum mechanics'' is related to existing
 work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
 but, as will be explained in more detail, is distinguished by its
-computational character.
+unique computational character.
 
@@
   simulations based on discrete (computable) fields.
+\item Study the problem of finding a complete set of mutually unbiased
+  bases
+  (SIC-POVM)~\cite{1751-8121-45-8-085306,1751-8121-47-33-335302,Caves2002}
+  over finite Galois fields.
 \end{itemize}
@@
 paradoxes in quantum mechanics, quantum information, computability,
-and complexity theory.
+complexity theory, and perhaps quantum gravity.
 
@@
 $0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether
-Turing machine $M_{i}$ halts or not. Such numbers cannot be
+Turing machine $\mathit{TM}_{i}$ halts or not. Such numbers cannot be
 computed. This interval also includes numbers like $\frac{\pi}{4}$
@@
 case)~\cite{Venn1876,Hajek2012}, 
-to determine the probability of an event, we run $N$
+to determine the probability of an event, we run $M$
 independent trials which gives us an approximation of the (assumed)
@@
 $\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
-the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$ with the
-probability converging to one as $N$ goes to infinity, i.e.,
+the relative frequency~$\frac{1}{M}\sum_{i=1}^{M}x_{i}$ with the
+probability converging to one as $M$ goes to infinity, i.e.,
 \[
-\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sum_{i=1}^{N} x_{i}\right|<\epsilon\right)=1\textrm{ .}
+\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M} x_{i}\right|<\epsilon\right)=1\textrm{ .}
 \]
@@
   h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
-Consider an experimental setup consisting of a collection of $N$
-identical needles of length $\ell$. We throw the $N$ needles one
-needle at a time, and observe the number $M$ of needles that cross a
+Consider an experimental setup consisting of a collection of $M$
+identical needles of length $\ell$. We throw the $M$ needles one
+needle at a time, and observe the number $M_c$ of needles that cross a
 line, thus estimating the probability of a needle crossing a line to
-be $\frac{M}{N}$. In an actual experiment with $500$ needles and the
+be $\frac{M_c}{M}$. In an actual experiment with $500$ needles and the
 ratio $\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$
@@
 with limited resources, it is not possible to talk about the idealized
-event that exactly $M$ needles cross lines as this would require the
+event that exactly $M_c$ needles cross lines as this would require the
 most expensive needles built to the most precise accuracy, laser
@@
 microscopes to determine if a needle does cross a line. Instead we
-might talk about the event that $M-\delta$ needles evidently cross
-lines and $M+\delta'$ needles plausibly cross lines where $\delta$ and
+might talk about the event that $M_c-\delta$ needles evidently cross
+lines and $M_c+\delta'$ needles plausibly cross lines where $\delta$ and
 $\delta'$ are resource-dependent approximations. This fuzzy notion of
@@
   $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$
-\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{M}$ of pairwise
   disjoint events, we have
-  $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)$.
+  $\bar{\mu}\left(\bigcup_{i=1}^{M}E_{i}\right)\subseteq\sum_{i=1}^{M}\bar{\mu}\left(E_{i}\right)$.
 \end{itemize}
@@
 
-\item If we insist that probabilities cannot be infinitely precise and
-  are bound to be approximations represented by intervals of
-  confidence, then quantum states themselves cannot be infinitely precise
-  because Gleason's theorem is no longer applied. 
-  This raises an important philosophical
-  question with immense practical relevance in the context of quantum
-  computing. The question, which we could largely bypass in the
-  classical case, is whether there is, in the background of all the
-  measurements and probabilities, a ``real'' infinitely-precise
-  quantum state that is being approximated and that, in principle, can
-  be more and more accurately described given more and more
-  resources. In other words, does a Gleason,
+\item If we insist that probabilities cannot be computed to infinite
+  precision and are bound to be approximations represented by
+  intervals of confidence, then quantum states themselves can only be
+  discussed within intervals of confidence. This raises an important
+  philosophical question with immense practical relevance in the
+  context of quantum computing. The question, which we could largely
+  bypass in the classical case, is whether there is, in the background
+  of all the measurements and probabilities, a ``real''
+  infinitely-precise quantum state that is being approximated and
+  that, in principle, can be more and more accurately described given
+  more and more resources. In other words, does a Gleason,
   Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
-  or Kochen-Specker
-  theorem still hold in a world with finite resources?  The answer
-  will have to be \emph{no} if we are to respect these major theorems
-  of quantum mechanics and quantum information. Thus our first radical
-  departure from the conventional case will be that the quantum state
-  itself must be fuzzy in some sense to be formalized.
+  or Kochen-Specker theorem still hold in a world with finite
+  resources?  The answer will have to be \emph{no} if we are to
+  respect these major theorems of quantum mechanics and quantum
+  information. Thus our first radical departure from the conventional
+  case will be that the quantum state itself must be fuzzy in some
+  sense to be formalized.
 
@@
 machines~\cite{Turing_1937,blum2012complexity} or the
-$\lambda$-calculus~\cite{Church1932,Barendregt:Lambda} viewed a computation as
-realizing a mathematical function. From our perspective, the most
-important consequence of this view is that the properties of the
-computed function existed independently of any observation,
-calculation, or interaction. For example, a function is
-\emph{injective} or not independently of any observation. An agent can
+$\lambda$-calculus~\cite{Church1932,Barendregt:Lambda} viewed a
+computation as realizing a mathematical function. From our
+perspective, the most important consequence of this view is that the
+properties of the computed function existed independently of any
+observation, calculation, or interaction. For example, a function is
+\emph{injective} or not independent of any observation. An agent can
 only interact with the computation by asking questions regarding its
 input-output behavior and although such interaction would reveal
-fragments of the computed function and its innate properties it could
+fragments of the computed function and its innate properties, it could
 not change it or affect it in any way.
@@
 rely on the infinite-precision real or complex numbers. We note two
-remarkable earlier results:
+remarkable earlier results and an open question:
 \begin{itemize}
@@
 
+\item An important special case of a generalized measurement is the
+  symmetric, informationally complete, positive operator valued
+  measure (SIC-POVM), which has applications in quantum
+  cryptography. This problem has been formulated in the context of
+  standard quantum theory where fields are complex numbers.  Although
+  a rigorous proof for the existence of SIC-POVMs for arbitrary
+  Hilbert space dimensions is still missing, it would be illuminating
+  to look for a formulation of the same problem in a discrete quantum
+  theory defined in terms of finite Galois fields.
 \end{itemize}
@@
 building on our previous work~\cite
-{VDS2009,AGVS2007,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
+{VDS2009,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
 to build semantically well-founded implementations of the
@@
   computational models based on discrete fields?
+\item Determine, through numerical computations, solutions for
+  SIC-POVM for small vector space dimensions.
 \end{itemize}
@@
 areas include: mathematical foundations of quantum computation and
-complexity~\cite{AGVS2007,VAS2006}, adiabatic quantum computing,
+complexity~\cite{AGVS2005,VAS2006}, adiabatic quantum computing,
 quantum logic, classical and quantum reversible programming
@@
 worldview impacting everything from philosophy and religion to all
-conventional sciences. On the development of researchers, the project
-resulted in the graduation of one Ph.D. student with another one
-expected to graduate in Spring 2017, the current supervision of two
-additional Ph.D. students, the graduation of an MS student, and the
-hosting of a visiting scholar.
+conventional sciences. The project resulted in the graduation of one
+Ph.D. student with another one expected to graduate in Spring 2017,
+the current supervision of two additional Ph.D. students, the
+graduation of an MS student, and the hosting of a visiting scholar.
 

### 2016-12-02 prop.tex
prop.tex Make sure it could be biult in Eclipse.
prop.tex Clean up the parts not related to the paper...

@@
 \usepackage[ backend=biber]{biblatex}
-\addbibresource{prop.bib}
+\addbibresource{proposal/prop.bib}
 %% \ExecuteBibliographyOptions{sorting=nyt,maxbibnames=5,doi=false,isbn=false,url=false}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proposal: General Plan}
-
-A major aim of this proposal is to recast quantum probability and
-measurement in a computational resource-aware setting. Our vision is
-to unify the strands above in a novel way as explained in this
-section. We start with some immediate observations that justify the
-rest of the development.
-
-\begin{itemize}
-
-\item If we insist that probabilities cannot be computed to infinite
-  precision and are bound to be approximations represented by
-  intervals of confidence, then quantum states themselves can only be
-  discussed within intervals of confidence. This raises an important
-  philosophical question with immense practical relevance in the
-  context of quantum computing. The question, which we could largely
-  bypass in the classical case, is whether there is, in the background
-  of all the measurements and probabilities, a ``real''
-  infinitely-precise quantum state that is being approximated and
-  that, in principle, can be more and more accurately described given
-  more and more resources. In other words, does a Gleason,
-  Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
-  or Kochen-Specker theorem still hold in a world with finite
-  resources?  The answer will have to be \emph{no} if we are to
-  respect these major theorems of quantum mechanics and quantum
-  information. Thus our first radical departure from the conventional
-  case will be that the quantum state itself must be fuzzy in some
-  sense to be formalized.
-
-\item Going further we actually have to concede not just the infinite
-  accuracy of the quantum state, but its very existence as a ``real''
-  entity that exists independently of measurements and
-  probabilities. The reasons for this second radical position are as
-  follows. First arguments embedded in the proof of the Kochen-Specker
-  theorem essentially rule out the existence of a sample space as the
-  probabilities of events cannot be consistently expressed using core
-  assignments to elements of the sample space. Second, the frequency
-  interpretation of probability which is already problematic in the
-  classical case, becomes untenable in the quantum case. In both
-  cases, but much more in the quantum case, it is much more sensible
-  to interpret probability in the Bayesian sense as ``lack of
-  knowledge''. This, and similar arguments elegantly expressed by
-  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
-  suggest that the quantum state is more like an interactive system in
-  computer science parlance. In other words, the state is only
-  determined by its interactions with the environment or observers. A
-  rough but useful analogy in the context of computer science would be
-  a web server: the state of such a system cannot be said to exist
-  independently of the interactions with clients; each interaction
-  with a client determines a future state of the system and may affect
-  future interactions. Crucially, each client may have a
-  \emph{different} view of the web server that is consistent with
-  their own history of interactions. This computational perspective
-  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
-  that asserts that the quantum state is subjective: each observer has
-  a different view of the quantum system that is consistent with their
-  previous observations and that allows that observer, independently
-  of other observers, to assign beliefs (i.e., probabilities) to
-  possible future interactions.
-
-\end{itemize}
-
-%%%%
-\subsection{Proposed Activity I: Quantum States as Interactive Processes}
-
-The early formalization of the process of computing using Turing
-machines~\cite{Turing_1937,blum2012complexity} or the
-$\lambda$-calculus~\cite{Church1932,Barendregt:Lambda} viewed a
-computation as realizing a mathematical function. From our
-perspective, the most important consequence of this view is that the
-properties of the computed function existed independently of any
-observation, calculation, or interaction. For example, a function is
-\emph{injective} or not independent of any observation. An agent can
-only interact with the computation by asking questions regarding its
-input-output behavior and although such interaction would reveal
-fragments of the computed function and its innate properties, it could
-not change it or affect it in any way.
-
-In a series of breakthrough papers that led to his Turing
-Award~\cite{Milner:1993:EIT:151233.151240}, Milner argued that this
-``closed system'' view of computation is too limiting as it cannot
-adequately describe the increasingly pervasive \emph{interactive
-  computations}. Milner explained that ``concurrency requires a new
-conceptual framework'' and ``not merely an extension of the repertoire
-of entities and constructions which explain sequential computing.'' In
-his Turing Award lecture, he gives the following simple but compelling
-example. Consider the following two programs:
-\begin{verbatim}
-Program P1: x := 1; x := x + 1 
-Program P2: x := 2
-\end{verbatim}
-As closed systems, these two programs define the same relation, namely
-the one that maps an input memory to an updated memory in which the
-location named \verb|x| is assigned the value \verb|2|. An observer
-with the ability of inquire about the value of \verb|x| at the end of
-the computation cannot distinguish the two programs. But place the
-programs in an environment which may involve interactions and the
-equivalence is lost. Phrased in physical terms, we give the observer the
-additional ability to access the location \verb|x| \emph{during} the
-computation, not just to observe its final value. In computing terms,
-we place each of the two programs \verb|P1| and \verb|P2| concurrently
-with the program:
-\begin{verbatim}
-Program Q: x := 3
-\end{verbatim}
-In the combined system of \verb|P1| and \verb|Q| running concurrently,
-the location \verb|x| may end up containing \verb|2|, \verb|3|, or
-\verb|4|. But in the combined system of \verb|P2| and \verb|Q| running
-concurrently, the location~\verb|x| can only end up containing
-\verb|2| or \verb|3|. The lesson, phrased in physics terms, is that it
-is not sensible to think of the properties of a system (like \verb|P1|
-or \verb|P2|) independently of the observer (\verb|Q| in this
-case). Indeed the observation \verb|x=4| cannot be said to have an
-existence independently from the interaction between \verb|P1| and
-\verb|Q|: it really emerges or is created as part of the observation
-process and is not a pre-existing ``element of reality''.
-
-This phenomenon is hardly a surprise to computer scientists or
-physicists but embracing it fully does have far-reaching
-consequences. In computer science, the big shift was to abandon the
-idea that a computation has inherent internal meaning, e.g.,
-representing a pure mathematical function. Instead \emph{the meaning
-  of a computational process is its observable behavior.} In this
-computational analogue to the theory of controlled open quantum
-systems, it is not too difficult to imagine that, in the presence of
-multiple interacting observers, the behavior observed by just one
-agent would appear to involve hidden variables or action at a
-distance. The well-established theory of observation of concurrent
-processes and their equivalences~\cite{Hennessy1989} relies on
-neither.
-
-\paragraph*{Research Question.} Is it possible to adapt the theory of
-observation of concurrent processes to the study of quantum states and
-confirm that the observations exhibit the same Bell-like correlations?
-
-\paragraph*{Research Question.} The theory of observation of
-concurrent processes and the theory of measurement in quantum
-mechanics are superficially different. Is it possible to reformulate
-them in a common language to benefit each theory from insights derived
-from the other theory?
-
-\paragraph*{Research Question.} Does the computational and hence
-\emph{testable} hypothesis that the quantum state is nothing but an
-interactive system agree with the QBism perspective providing a
-resolution to the same paradoxes (e.g., EPR~\cite{EPR1935} and Wigner's
-friend~\cite{Wigner1961,Fuchs2010,Fuchs2012})?
-
-%%%%%
-\subsection{Proposed Activity II: Quantum Interval-valued Probability Measures}
+\section{Proposed Activity II: Quantum Interval-valued Probability Measures}
 
@@
 \begin{center}
-\includegraphics[scale=0.38]{measure4.pdf}
+\includegraphics[scale=0.38]{proposal/measure4.pdf}
 \end{center}
@@
 
-%%%%%
-\subsection{Proposed Activity III: Quantum Information Theorems}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Proposal: General Plan}
+
+A major aim of this proposal is to recast quantum probability and
+measurement in a computational resource-aware setting. Our vision is
+to unify the strands above in a novel way as explained in this
+section. We start with some immediate observations that justify the
+rest of the development.
+
+\begin{itemize}
+
+\item If we insist that probabilities cannot be computed to infinite
+  precision and are bound to be approximations represented by
+  intervals of confidence, then quantum states themselves can only be
+  discussed within intervals of confidence. This raises an important
+  philosophical question with immense practical relevance in the
+  context of quantum computing. The question, which we could largely
+  bypass in the classical case, is whether there is, in the background
+  of all the measurements and probabilities, a ``real''
+  infinitely-precise quantum state that is being approximated and
+  that, in principle, can be more and more accurately described given
+  more and more resources. In other words, does a Gleason,
+  Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
+  or Kochen-Specker theorem still hold in a world with finite
+  resources?  The answer will have to be \emph{no} if we are to
+  respect these major theorems of quantum mechanics and quantum
+  information. Thus our first radical departure from the conventional
+  case will be that the quantum state itself must be fuzzy in some
+  sense to be formalized.
+
+\item Going further we actually have to concede not just the infinite
+  accuracy of the quantum state, but its very existence as a ``real''
+  entity that exists independently of measurements and
+  probabilities. The reasons for this second radical position are as
+  follows. First arguments embedded in the proof of the Kochen-Specker
+  theorem essentially rule out the existence of a sample space as the
+  probabilities of events cannot be consistently expressed using core
+  assignments to elements of the sample space. Second, the frequency
+  interpretation of probability which is already problematic in the
+  classical case, becomes untenable in the quantum case. In both
+  cases, but much more in the quantum case, it is much more sensible
+  to interpret probability in the Bayesian sense as ``lack of
+  knowledge''. This, and similar arguments elegantly expressed by
+  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+  suggest that the quantum state is more like an interactive system in
+  computer science parlance. In other words, the state is only
+  determined by its interactions with the environment or observers. A
+  rough but useful analogy in the context of computer science would be
+  a web server: the state of such a system cannot be said to exist
+  independently of the interactions with clients; each interaction
+  with a client determines a future state of the system and may affect
+  future interactions. Crucially, each client may have a
+  \emph{different} view of the web server that is consistent with
+  their own history of interactions. This computational perspective
+  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
+  that asserts that the quantum state is subjective: each observer has
+  a different view of the quantum system that is consistent with their
+  previous observations and that allows that observer, independently
+  of other observers, to assign beliefs (i.e., probabilities) to
+  possible future interactions.
+
+\end{itemize}
 
@@
 
-%%%%%
-\subsection{Proposed Activity IV: Computational and Simulation Aspects}
-
-The marriage of quantum mechanics and computer science first
-envisioned and popularized by Feynman has created an awkward, but
-opportune, moment. The embarrassing dilemma was concisely described by
-Aaronson as follows~\cite{AaronsonArkhipov2011,BFRDARW2013}. 
-Consider the following three statements:
-\begin{enumerate}
-\item[(A)] Textbook quantum mechanics is correct.
-\item[(B)] There does not exist an efficient classical factoring
-  algorithm.
-\item[(C)] The extended Church-Turing thesis that probabilistic Turing
-  machines can efficiently simulate any physically realizable model of
-  computation is correct~\cite{BernsteinVazirani1997,Kaye2007}.
-\end{enumerate}
-There is overwhelming evidence to support each of these
-statements. The theoretical framework of quantum mechanics (A) has
-withstood decades of experimental confirmation. Entire industries are
-founded on the assumption (B) that algorithms like RSA are secure and
-they also have withstood years of attempted
-attacks~\cite{boneh1999twenty,wiki:RSAFactoring}. Finally the
-entire field of complexity theory in computer science which has also
-withstood years of field testing rests, in essence, on assumption
-(C)~\cite{Aaronson2005,Piccinini2015}. 
-And yet one of these three statements \emph{must be false}! Indeed
-if textbook quantum mechanics is false we concede (A). If it is
-correct Shor's efficient factoring algorithm is realizable. If there
-is a corresponding efficient classical factoring algorithm then we
-concede (B). If not then we concede~(C).
-
-It is unlikely that there will be a simple a resolution to this
-awkward situation. It is more likely that the resolution will emerge
-from deep and careful analyses of the foundations of each field. In
-previous work, we examined the Hilbert space mathematical framework of
-quantum mechanics and teased apart its various aspects that directly
-rely on the infinite-precision real or complex numbers. We note two
-remarkable earlier results and an open question:
-\begin{itemize}
-\item UNIQUE-SAT: Schumacher and
-  Westmoreland~\cite{Schumacher2012-SCHMQT} argue that much of the
-  structure of traditional quantum mechanics is maintained in the
-  presence of finite fields. In particular, they establish that the
-  quantum theory based on the finite field of booleans retains the
-  following characteristics of quantum mechanics: the notions of
-  superposition, interference, entanglement, and mixed states of
-  quantum systems; the time evolution of quantum systems using
-  invertible linear operators; the complementarity of incompatible
-  observables; the exclusion of local hidden variable theories and the
-  impossibility of cloning quantum states; and the presence of natural
-  counterparts of quantum information protocols such as superdense
-  coding and teleportation. However we have argued that this theory is
-  not physically realizable as it allows the solution of
-  computationally difficult problems like
-  UNIQUE-SAT~\cite{Valiant198685} in constant time~\cite{usat}.
-
-\item Deutsch-Jozsa: In a follow-up paper~\cite{DQT2014}, we proposed
-  a variant of quantum mechanics in which the underlying field of
-  complex numbers is replaced by special finite fields with enough
-  structure to model Hermitian products that \emph{locally} behave
-  like inner products. The trick is to recognize that, as the
-  characteristic of the finite field increases, larger and larger
-  regions of the finite field become totally ordered, thereby
-  restoring, with some restrictions, all the usual properties of the
-  inner product needed for conventional quantum mechanics. Using this
-  theory to analyze the Deutsch-Jozsa algorithm reveals that the
-  characteristic of the finite field plays an essential role: as the
-  size of the finite field grows, so does the numerical range of the
-  intermediate and final results of the algorithms being implemented.
-  The theory naturally recovers a deterministic measure of the
-  intrinsic resources required for a given level of complexity; this
-  measure is normally completely hidden in computations with real
-  numbers, and explicitly exposing it is one of the significant
-  achievements of our discrete field analysis of quantum computation.
-  This solves the conundrum that the conventional Deutsch-Jozsa
-  algorithm~\cite{DeutschJozsa1992,Jaeger2007}
-  mysteriously continues to work for larger and larger input
-  functions without any apparent increase in resources.  Our analysis
-  of this problem reveals that as the size of the input increases, it
-  is necessary to increase the size of the finite field and hence the
-  size of the underlying available numeric coefficients.  This
-  observation does not fully explain the power of quantum computing
-  over classical computing, but at least it explains that some of the
-  power of quantum computing depends on increasingly larger precision
-  in the underlying field of numbers.
-
-\item An important special case of a generalized measurement is the
-  symmetric, informationally complete, positive operator valued
-  measure (SIC-POVM), which has applications in quantum
-  cryptography. This problem has been formulated in the context of
-  standard quantum theory where fields are complex numbers.  Although
-  a rigorous proof for the existence of SIC-POVMs for arbitrary
-  Hilbert space dimensions is still missing, it would be illuminating
-  to look for a formulation of the same problem in a discrete quantum
-  theory defined in terms of finite Galois fields.
-\end{itemize}
-
-A long term, ultimate, goal of this research proposal would be to
-combine the various pieces into a coherent computational model of
-quantum mechanics that keeps explicit track of resources needed to
-represent the interactive system representing the quantum state, its
-evolution, the observables, and the probabilities. Such a
-computational model of quantum mechanics would encompass classical
-(reversible) computation and potentially revolutionize quantum
-thinking with finite resources. The explicit manipulation of resources
-enables one of key idea that emerged in our previous work: the
-resources used to represent the quantum system are in principle
-unrelated to the resources available to the various observers. We
-conjecture that this asymmetry may prove key to resolving some of the
-quantum paradoxes.  The nature of quantum mechanics realized in terms
-of discrete fields and finitely-communicable probability estimates is
-amenable to direct computational exploration for reasonable field
-sizes and observational accuracy. We have established a set of utility
-libraries in Mathematica that supports a wide variety of such
-numerical experiments. Concurrently to this effort, we are also
-building on our previous work~\cite
-{VDS2009,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
-to build semantically well-founded implementations of the
-computational models investigated in this proposal.
-
-\paragraph*{Research Questions.} The aim of these implementations
-include:
-\begin{itemize}
-\item Provide an experimental testbed to simulate physical phenomena
-  (e.g.~\cite {OrtizEtAl2001,SommEtAl2002}) that complements the
-  Mathematica libraries in which quantum algorithms can be simulated;
-\item Establish connections between quantum programming concepts and
-  classical programming concepts. We plan to make our software
-  available for educational and research purposes; and 
-\item Analyze the computational complexity of quantum theories and
-  simulations based on discrete fields. What other (apart from
-  UNIQUE-SAT) supernatural algorithms can be implemented in
-  computational models based on discrete fields?
-\item Determine, through numerical computations, solutions for
-  SIC-POVM for small vector space dimensions.
-\end{itemize}
-
-% \begin{figure}
-% \begin{center}
-%   \includegraphics[scale=0.38]{HoughLineData.pdf}
-% \end{center}
-%   \caption{Curves of possible line parameters determined by noisy
-%     data samples on a straight line in 2D space.}
-% \label{houghline.fig}
-% \end{figure}
-
-% %%%%%
-% \subsection{Proposed Activity V: Applications}
-
-% A classic evidence-accumulation method known as the Hough
-% transform~\cite{BallardGenHough1981}, which is very closely related to
-% Bayesian evidence accumulation
-% methods~\cite{CrandallEtal2005,CrandallEtal2006}, provides another
-% example of how our proposal to define physical theories without exact
-% real numbers could be combined with the measurement process. Simply
-% described, the Hough transform as an abstraction of Bayesian schemes
-% starts with a model of the theory being measured, typically a model
-% that would ordinarily be treated {\it after\/} gathering the data by
-% applying least squares to choose the optimal parameters.  But in this
-% method, instead of thinking of, say, the model of a straight line
-% $\hat{\mathbf{n}}\cdot \mathbf{x} = d$ as an equation for the points
-% on a line $ \mathbf{x}_{i} = (x_{i},y_{i})$, we think of it as a
-% time-accumulating {\it set\/} of equations for the distance $d$ of the
-% nearest point on the line and the direction
-% $ \hat{\mathbf{n}} = (\cos \theta, \sin \theta)$ from the origin to
-% that point (the direction perpendicular to the line).  Thus each point
-% of {\it evidence\/}, $(x_{i},y_{i})$, produces an {\it equation in the
-%   parameter space\/} that is effectively a plot of all the possible
-% values of $d(\theta)$ as a function of the possible angular directions
-% $\theta$ pointing to the family of all possible lines.  A typical
-% result from a set of errorful (it is impossible to measure real
-% numbers, we recall) data measurements of points on a hypothetical
-% straight line is shown in Fig.~\ref{houghline.fig}.
-
-% The interesting step for us is now to realize that the {\it parameter
-%   curves\/} shown in the figure do not need, or indeed, must not, be
-% themselves infinitely precise real numbers, but they must themselves
-% incorporate in some way a theory consistent with forbidding absolute
-% precision.  In practice, then, the sinusoidal lines in Figure
-% \ref{houghline.fig} all become fuzzy, and the accumulation of these
-% fuzzy distributions produces peaks of likelihood around the values
-% $(d_0, \theta_0)$ that are the optimal choices for the line describing
-% the set of data.  Note that even {\it one\/} data point provides
-% evidence on a set of hypotheses. The simple analysis we have outlined
-% here is easily extended to much more complex situations in higher
-% dimensions (see, e.g.,~\cite{BallardGenHough1981}).  Our point here is
-% that essentially any physical theory that would ordinarily be
-% described by a mathematical model using infinite precision numbers is
-% potentially nonsensical from a computational point of view: computer
-% scientists know perfectly well, and have been dealing with since the
-% time of Turing and Shannon, that every single bit of precision in any
-% number has a cost, and that there is not enough energy in the universe
-% to compute even one general real number.  Thus the combination of
-% physical models that, in some intrinsic fashion, contain only
-% computable numbers, with theories of measurement and evidence in the
-% fashion of the Hough transform example we have just presented, could
-% contain the outline of entirely new ways of understanding what
-% mathematical models of the physical world and its measurement actually
-% could be.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Broader Impact and Education}
-
-\noindent (A) {\em Integration of research and education:} Courses on
-advanced computational models and quantum information will be further
-developed at Indiana University to communicate the basic concepts and
-tools discussed in this proposal. Dr. Ortiz taught courses on
-``Quantum information and Computation'' and Dr. Sabry has taught
-courses on ``Quantum Computing'' for graduate students.  Dr.\ Hanson
-has taught courses on scientific visualization and mathematical
-modeling with emphasis on high-dimensional mathematics.  His numerous
-Siggraph course presentations are embodied in his 2006 book {\it
-  Visualizing Quaternions\/}~\cite{Hanson2006}, 
-which remains the definitive treatment
-of the subject for computer science and data analysis applications and
-has sold thousands of copies. As a part of Dr.\ Hanson's commitment to
-exposing and explaining the elements of higher mathematics to the
-public, he has recently led the design of a free iPhone App, {\it
-  4Dice\/}, that for the first time makes available an interactive
-treatment of a correctly imaged simulation of the appearance of a
-hypercube, realizing interactively his YouTube animation of the same
-name.  This framework is now being generalized for a broad family of
-iPhone Apps to permit the hands-on study of high-dimensional
-mathematics.  These courses were highly appreciated by the students as
-noted by their evaluations in making the material extremely accessible
-and interesting.  The PIs plan to engage high school students or
-undergraduates in the implementation of some of the ideas.  The PIs
-have a long standing commitment to K-12 science and math education
-(see also (C) below). The collaborative group efforts will provide
-students, as well as the PIs with a unique learning experience. The
-broadened perspectives gained through those efforts will contribute to
-the PIs effectiveness as teachers and mentors. They also will enable
-to better prepare students and postdocs for productive careers in an
-increasingly competitive global economy. Students and postdocs are
-encouraged to pursue collaborative research leading to a broader
-scientific program. This is highlighted by the PIs students' close
-contact with LANL, the Perimeter Institute, and the Institute for
-Quantum Computing at Waterloo.
-
-\medskip
-\noindent (B) {\em Broadening the participation of underrepresented groups:}
-Indiana University is engaged in attracting women and minorities in all
-ranks. Several programs are aimed at specifically attracting outstanding
-students into physics and computer science, and to expanding the pool of
-candidates for fellowships. Targeted recruitment of minority graduate
-students is facilitated by the Falicov Fellowship established in 2006. In
-recent years, the School of Informatics and Computing has been fortunate to
-hire several women and minorities for faculty positions, and we have been
-working toward increasing the number of women and minorities among our
-student population. To assist with this process, the PIs will encourage women
-and minorities to apply for graduate positions as well as undergraduate
-positions that may be made available by the grant and REU
-supplements. Dr. Ortiz has minority students and Dr. Sabry has graduated a
-female Ph.D. in 2005 and is currently assisting on the Ph.D. committees of
-several others.
-
-\medskip
-\noindent (C) {\em Enhancing infrastructure and outreach:} Dr. Ortiz
-has pursued broad outreach by giving talks on astronomy/astrophysics
-in the local schools at Bloomington, Indiana, and by an interview in
-the public radio on quantum information. Dr. Ortiz is also guiding a
-high school student in work on interferometry in two and three slit
-experiments. Dr. Ortiz also guides undergraduate research. All source
-code produced by this project will be made freely available via the
-web, and the results will be disseminated via technical reports,
-conference papers, and journal articles.  The software and concepts we
-have developed in the past have been employed by a wide variety of
-commercial and noncommercial users.  Thus, we expect that the
-successful completion of the proposed research will contribute to the
-understanding of quantum and semi quantum computation. The educational
-benefits that will flow from this proposal will extend beyond the
-students of the participating research groups. The knowledge gained
-through participation in the proposed research will further strengthen
-the effectiveness of these outreach activities.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{PI Team and Prior NSF Support}
-
-\paragraph*{PI Team.} Over the past several years, the PIs, together
-with other IU faculty members and students, have formed a group whose
-main interest is the study of paradigms of computing that either arise
-in nature or are inspired by natural phenomena. The PIs are especially
-interested in how the laws of physics can inspire and guide our
-abstract computational models, as well as exposing new insights into
-the computational framework behind the natural world and the
-computability of physical theory. Our group has been active in several
-areas related to the theory behind quantum computation. Particular
-areas include: mathematical foundations of quantum computation and
-complexity~\cite{AGVS2005,VAS2006}, adiabatic quantum computing,
-quantum logic, classical and quantum reversible programming
-languages~\cite{Sabry:2003:MQC:871895.871900}, analog computation and
-its limits, and optical computing. During the past several years, our
-discussions have revolved around formulating variants of quantum
-mechanics that are computable and that are as close to possible to
-classical computing. Several preliminary results have emerged from our
-collaboration~\cite{usat,finiteQC,geometry2013,DQT2014}, and the group
-is very excited about the potential implications of those
-results. This proposal brings forth a particular aspect of this
-programme related to its applications to problem areas that have
-traditionally been outside the conceptual framework of quantum
-mechanics and programming language research. This proposal, if funded,
-will give our group more recognition within the university which, at
-this point, is committed to generously funding several ``emerging
-areas of research''. With the establishment of a new Intelligent
-Systems Engineering at Indiana University with a focus nanoscale
-sensors and quantum engineering and the recent hires in Physics in
-experimental atomic physics, ion-trap quantum simulation, computation,
-and measurement, the PI group is in an excellent position to receive
-additional funding from the University to reach a critical mass of
-quantum information researchers.
-
-\paragraph*{Prior Support.} There was no recent NSF support for
-Dr. Ortiz. In the past five years, Dr. Sabry received one NSF grant
-(award number 1217454) titled \emph{Information Effects} for the
-amount of \$275,319.00 with start and end dates of 1 September 2012 --
-31 August 2016.
-
-\paragraph*{Intellectual Merit.} Computing is about processing
-information. Physically speaking, information, like energy, is a
-resource that obeys a conservation principle: information can never be
-created nor destroyed; it is just transformed. Traditional models of
-computation, however, have not embraced this conservation of
-information as an explicit principle. Instead this principle appears,
-after the fact, in applications such as information-flow security
-which treats the amount of information released to the environment as
-a possible security leak and such as differential privacy which
-intentionally releases some random information to the user to confuse
-potential attackers. This project has instead embraced the principle
-of conservation of information as a key foundation for the design of
-computational models. In one perspective, computation in these models
-is constructed from reversible transformations that act on topological
-spaces, deforming them, stretching them, and shrinking them but never
-cutting nor glueing. The first main result of this project was the
-design and implementation of a programming language which captures
-these ideas and realizes them in the context of the new foundational
-framework of Homotopy Type Theory. This framework combines ideas from
-mathematics, logic, physics, and computation in a way that accounts
-for a newly-recognized higher-dimensional structure of types. This
-idea enabled us to not only represent programs as reversible
-deformations but also to represent the reversible deformations
-themselves as higher-level programs implementing reversible
-optimizations of the underlying lower-level programs. In a second
-breakthrough, viewing the higher-level programs as distinct proofs of
-reversibility enabled the definition of types whose natural
-cardinality is fractional. Having computations that manipulate
-fractional types opens the door for a rich and novel class of
-applications in which resource creation and resource use are
-separated. This idea brings speedups and convenience in a way that is
-similar to the speedup and convenience brought by the use of credit
-cards to complete transactions without necessarily having the money at
-hand: the monetary resource can be consumed by the merchant and only
-later be reconciled by the buyer.
-
-\paragraph*{Broader Impacts.} The idea of reversible computation and
-its connection to quantum mechanics is at the heart of one of the
-deepest mysteries in the universe. Any progress or theory that
-explains physical principles computationally is likely to change our
-worldview impacting everything from philosophy and religion to all
-conventional sciences. The project resulted in the graduation of one
-Ph.D. student with another one expected to graduate in Spring 2017,
-the current supervision of two additional Ph.D. students, the
-graduation of an MS student, and the hosting of a visiting scholar.
-
-\paragraph*{Publications.} Several papers were published to report on
-the results. On the foundational side, we have the following papers:
-\begin{enumerate}
-\item Computing with Semirings and Weak Rig Groupoids, ESOP, 2016
-\item Superstructural Reversible Logic, Workshop on Linearity, 2014
-\item Theseus: A High Level Language for Reversible
-  Computing. Work-in-Progress report, RC 2014
-\item Discrete Quantum Theories, J. Phys. A: Math. Theor. 2014.
-\item Geometry of Discrete Quantum Computing, J. Phys. A:
-  Math. Theor. 2013.
-\item Isomorphic Interpreters from Logically Reversible Abstract
-  Machines. RC 2012. 
-\end{enumerate}
-On the applications side, we have the following papers: 
-\begin{enumerate}
-\item Copredication in Homotopy Type Theory: A homotopical approach
-  for formal semantics of natural languages. Workshop on Natural
-  Language and Computer Science, 2016.
-\item Contract Monitoring Semantics as Patterns of
-  Communication. ICFP, 2015.
-\item Extensible Effects: An Alternative to Monad
-  Transformers. Haskell Symposium, 2013.
-\item Encoding Secure Information Flow with Restricted Delegation and
-  Revocation in Haskell. Workshop on Functional Programming Concepts
-  in Domain-Specific Languages, 2013
-\end{enumerate}
-In addition to the publications, Dr. Sabry and collaborators maintain
-a public repository with software related to the project. Dr. Sabry
-was also invited to give talks at several venues, most notably:
-\begin{itemize}
-\item Colloquiumfest, University of Saskatchewan, Canada, 2014
-\item Workshop on Quantum Information and Foundations of Quantum
-  Mechanics, University of British Columbia, Vancouver, Canada, 2013
-\end{itemize}
-
-% (d) a listing of the publications resulting from the NSF award (a
-% complete bibliographic citation for each publication must be provided
-% either in this section or in the References Cited section of the
-% proposal); if none, state "No publications were produced under this
-% award."
-
-% (e) evidence of research products and their availability, including,
-% but not limited to: data, publications, samples, physical collections,
-% software, and models, as described in any Data Management Plan; and
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-12-02 prop.tex
prop.tex Updating the titles, and elimating LaTeX warning... prop.pdf Added back because sometimes we want to compare the compiled results...

@@
 \addbibresource{proposal/prop.bib}
-%% \ExecuteBibliographyOptions{sorting=nyt,maxbibnames=5,doi=false,isbn=false,url=false}
 \ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
@@
 
-%% \title{Computational Quantum Probabilities}
-%% \title{Measurement and Probability in Fuzzy Quantum Theories}
 \title{Measurement and Probability in Fuzzy Quantum Theories}
-\date{}
+\date{\today}
 \begin{document}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overview, Objectives, and Expected Significance}
+\section{Intorduction}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background I: Classical Probability}
+\section{Classical Probability}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background II: Quantum Probability}
+\section{Quantum Probability}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proposed Activity II: Quantum Interval-valued Probability Measures}
+\section{Quantum Interval-valued Probability Measures}
 
@@
 
-\paragraph*{Research Question.} Confirm that as the number and
+\begin{description}
+\item[Research Question.] Confirm that as the number and
 precision of the intervals increase the quantum interval-valued 
@@
 rule. 
+\end{description}
 
@@
 
-\paragraph*{Research Question.} Investigate the status of the theorems
+\begin{description}
+\item[Research Question.] Investigate the status of the theorems
 of Gleason, Bell, and Kochen-Specker for quantum interval-valued
@@
 generalizations in this mathematical framework.
+\end{description}
 

### 2016-12-02 prop.tex
prop.tex Clean-up unused preambles...
prop.tex \section{Conclusion and Discussion} Add research questions...

@@
 \usepackage[utf8]{inputenc}
-\usepackage{tensor}
-\usepackage{url}
 \usepackage{amsmath}
@@
 \usepackage{mathrsfs}
-\usepackage{bbm}
 \usepackage{bbold}
@@
 \newtheorem{definition}{Definition}
-\newtheorem{cor}{Corollary}
-\newtheorem{lemma}{Lemma}
 \newtheorem{thm}{Theorem}
-\newtheorem{case}{Case}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{problem}{Problem}
-\newtheorem{claim}{Claim}
 
@@
 \newcommand{\necess}{{\mbox{\wesa{certain}}}}
-\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
 \newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
-\newcommand{\bra}[1]{{\left\langle{#1}\right\vert}}
 \newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
@@
 \newcommand{\proj}[1]{\op{#1}{#1}}
-\def\C{{\mathbb{C}}}
 \newcommand{\ps}{\texttt{+}}
@@
 
-\begin{description}
-\item[Research Question.] Confirm that as the number and
-precision of the intervals increase the quantum interval-valued 
-probability measure converges to the measure induced by the Born
-rule. 
-\end{description}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proposal: General Plan}
+\section{Conclusion and Discussion}
 
@@
 \begin{description}
+\item[Research Question.] Confirm that there is always an interval-valued
+probability measure with an empty-core if the length of the interval is bigger
+than zero.
+\item[Research Question.] In example~\ref{ex:three-dimensional-three-value} and
+\ref{ex:three-dimensional-4-value}, we pick a possible candidate corresponding
+to an interval-valued probability measure by only considering the state whose
+interval-valued probability is $\necess$. Define a general method which could be
+used to determine whether an interval-valued probability measure is closer to
+the Born rule or not.
+\item[Research Question.] Confirm that as the number and
+precision of the intervals increase the quantum interval-valued 
+probability measure converges to the measure induced by the Born
+rule. 
 \item[Research Question.] Investigate the status of the theorems

### 2016-12-03 prop.tex
prop.lyx imported into LyX before drawing a table or graph...
prop.tex \section{Conclusion and Discussion} Organize the section, need to review how to write conclusion next time...

--- 2016-12-02 prop.tex
@@
 
+\begin{document}
 \title{Measurement and Probability in Fuzzy Quantum Theories}
 \date{\today}
-\begin{document}
 \maketitle
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Intorduction}
+\section{Introduction}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion and Discussion}
+
+If we insist that probabilities cannot be computed to infinite precision
+and are bound to be approximations represented by intervals of confidence,
+then quantum states themselves can only be discussed within intervals
+of confidence. This raises an important philosophical question with
+immense practical relevance in the context of quantum computing. The
+question, which we could largely bypass in the classical case, is
+whether there is, in the background of all the measurements and probabilities,
+a ``real'' infinitely-precise quantum state that is being approximated
+and that, in principle, can be more and more accurately described
+given more and more resources. In particular, we could summarize our
+examples and Gleason's theorem in table~\ref{table_long}. 
+\begin{table}[ht]
+\center{%
+\begin{tabular}{c|cccc}
+Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
+\hline 
+Number of intervals & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
+\hline 
+Maximum difference between ends of intervals & $1$ & $1/2$ & \ldots{} & $0$\tabularnewline
+\hline 
+Number of states in the core & 0 & 0 &  & 1\tabularnewline
+\hline 
+Number of states might corresponding to them & $3$ & $2$ & \ldots{} & $1$\tabularnewline
+\hline 
+How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
+\end{tabular}}\caption{Summarize example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value}
+and Gleason's theorem}
+\label{table_long}
+\end{table}
+Although the tend is clear, we still need more examples to fill the
+blank and to prove our idea. Some research questions might be
 \begin{description}
-\item[Research Question.] Confirm that as the number and
-precision of the intervals increase the quantum interval-valued 
-probability measure converges to the measure induced by the Born
-rule. 
+\item [{Research Question.}] Confirm that there is always an interval-valued
+probability measure with an empty-core if the length of the interval
+is bigger than zero. 
+\item [{Research Question.}] In example~\ref{ex:three-dimensional-three-value}
+and \ref{ex:three-dimensional-4-value}, we pick a possible candidate
+corresponding to an interval-valued probability measure by only considering
+the state whose interval-valued probability is $\necess$. Define
+a general method which could be used to determine whether an interval-valued
+probability measure is closer to the Born rule or not. 
+\item [{Research Question.}] Confirm that as the number and precision
+of the intervals increase the quantum interval-valued probability
+measure converges to the measure induced by the Born rule. 
 \end{description}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proposal: General Plan}
-
-A major aim of this proposal is to recast quantum probability and
-measurement in a computational resource-aware setting. Our vision is
-to unify the strands above in a novel way as explained in this
-section. We start with some immediate observations that justify the
-rest of the development.
-
-\begin{itemize}
-
-\item If we insist that probabilities cannot be computed to infinite
-  precision and are bound to be approximations represented by
-  intervals of confidence, then quantum states themselves can only be
-  discussed within intervals of confidence. This raises an important
-  philosophical question with immense practical relevance in the
-  context of quantum computing. The question, which we could largely
-  bypass in the classical case, is whether there is, in the background
-  of all the measurements and probabilities, a ``real''
-  infinitely-precise quantum state that is being approximated and
-  that, in principle, can be more and more accurately described given
-  more and more resources. In other words, does a Gleason,
-  Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
-  or Kochen-Specker theorem still hold in a world with finite
-  resources?  The answer will have to be \emph{no} if we are to
-  respect these major theorems of quantum mechanics and quantum
-  information. Thus our first radical departure from the conventional
-  case will be that the quantum state itself must be fuzzy in some
-  sense to be formalized.
-
-\item Going further we actually have to concede not just the infinite
+Since the validity of Gleason's theorem in a world with finite-precision
+measurements is a question, the natural follow-up questions is to
+investigate the status of the theorems of Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+and Kochen-Specker for quantum interval-valued probability measures
+as well. Going further we actually have to concede not just the infinite
 accuracy of the quantum state, but its very existence as a ``real''
-  entity that exists independently of measurements and
-  probabilities. The reasons for this second radical position are as
-  follows. First arguments embedded in the proof of the Kochen-Specker
-  theorem essentially rule out the existence of a sample space as the
-  probabilities of events cannot be consistently expressed using core
-  assignments to elements of the sample space. Second, the frequency
-  interpretation of probability which is already problematic in the
-  classical case, becomes untenable in the quantum case. In both
-  cases, but much more in the quantum case, it is much more sensible
-  to interpret probability in the Bayesian sense as ``lack of
-  knowledge''. This, and similar arguments elegantly expressed by
-  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
-  suggest that the quantum state is more like an interactive system in
-  computer science parlance. In other words, the state is only
-  determined by its interactions with the environment or observers. A
-  rough but useful analogy in the context of computer science would be
-  a web server: the state of such a system cannot be said to exist
-  independently of the interactions with clients; each interaction
-  with a client determines a future state of the system and may affect
-  future interactions. Crucially, each client may have a
-  \emph{different} view of the web server that is consistent with
-  their own history of interactions. This computational perspective
-  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
+entity that exists independently of measurements and probabilities.
+The reasons for this second radical position are as follows. First
+arguments embedded in the proof of the Kochen-Specker theorem essentially
+rule out the existence of a sample space as the probabilities of events
+cannot be consistently expressed using core assignments to elements
+of the sample space. Second, the frequency interpretation of probability
+which is already problematic in the classical case, becomes untenable
+in the quantum case. In both cases, but much more in the quantum case,
+it is much more sensible to interpret probability in the Bayesian
+sense as ``lack of knowledge''. This, and similar arguments elegantly
+expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+suggest that the quantum state is more like an interactive system
+in computer science parlance. In other words, the state is only determined
+by its interactions with the environment or observers. A rough but
+useful analogy in the context of computer science would be a web server:
+the state of such a system cannot be said to exist independently of
+the interactions with clients; each interaction with a client determines
+a future state of the system and may affect future interactions. Crucially,
+each client may have a \emph{different} view of the web server that
+is consistent with their own history of interactions. This computational
+perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
 that asserts that the quantum state is subjective: each observer has
@@
 previous observations and that allows that observer, independently
-  of other observers, to assign beliefs (i.e., probabilities) to
-  possible future interactions.
-
-\end{itemize}
-
-The previous research question is essentially concerned with the
-status of Gleason's theorem in a world with finite-precision
-measurements. The following research questions are therefore natural
-follow-up questions.
-
-\begin{description}
-\item[Research Question.] Investigate the status of the theorems
-of Gleason, Bell, and Kochen-Specker for quantum interval-valued
-probability measures. Revisit the Meyer-Mermin debate and its
-generalizations in this mathematical framework.
-\end{description}
+of other observers, to assign beliefs (i.e., probabilities) to possible
+future interactions.
 

### 2016-12-03 prop.tex
prop.tex \section{Conclusion and Discussion} Simplify table...

@@
 \hline 
-Number of intervals & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
+Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
 \hline 
-Maximum difference between ends of intervals & $1$ & $1/2$ & \ldots{} & $0$\tabularnewline
+$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $1/2$ & \ldots{} & $0$\tabularnewline
 \hline 
-Number of states in the core & 0 & 0 &  & 1\tabularnewline
+Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
 \hline 
-Number of states might corresponding to them & $3$ & $2$ & \ldots{} & $1$\tabularnewline
+Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
 \hline 

### 2016-12-04 prop.tex
prop.tex \section{Conclusion and Discussion} Update table title...

@@
 and that, in principle, can be more and more accurately described
-given more and more resources. In particular, we could summarize our
-examples and Gleason's theorem in table~\ref{table_long}. 
+given more and more resources. In particular, we could summarize example~\ref{ex:three-dimensional-three-value}
+and \ref{ex:three-dimensional-4-value} and Gleason's theorem in table~\ref{table_long}.
 \begin{table}[ht]
@@
 How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
-\end{tabular}}\caption{Summarize example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value}
-and Gleason's theorem}
+\end{tabular}}\caption{How measurement resources effect identifying states from interval-valued
+probability measures.}
 \label{table_long}

### 2016-12-04 prop.tex
prop.tex \section{Conclusion and Discussion} Updating table...

@@
 Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
-\hline 
-$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $1/2$ & \ldots{} & $0$\tabularnewline
-\hline 
+$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
 Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
-\hline 
 Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
@@
 How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
-\end{tabular}}\caption{How measurement resources effect identifying states from interval-valued
-probability measures.}
+\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
+measures}
 \label{table_long}
 \end{table}
-Although the tend is clear, we still need more examples to fill the
-blank and to prove our idea. Some research questions might be
+According to table~\ref{table_long}, when we increase the measurement
+resources, interval-valued probability measures could more and more
+likely be identified to a particular state. Although the tend is clear,
+there are still a lot of questions need to be answered, including: 
 \begin{description}

### 2016-12-05 prop.tex
prop.tex \section{Conclusion and Discussion} Keep editing according to "The Craft of Research"...
prop.tex \section{Conclusion and Discussion} Updating...

--- 2016-12-03 prop.tex
@@
 
-\begin{thm}[Shapley~\cite{Shapley1971}]\label{thm:Shapley}
+\begin{thm}[Shapley~\cite{Shapley1971,,Grabisch2016}]\label{thm:Shapley}
   Every (classical) convex interval-valued probability measure has a
@@
 and that, in principle, can be more and more accurately described
-given more and more resources. In particular, we could summarize our
-examples and Gleason's theorem in table~\ref{table_long}. 
+given more and more resources. Although a coarse quantum interval-valued
+probability measure may not be induced by one infinitely-precise quantum
+state, it might be induced by many quantum states when we examine
+different part of its probability assignment. Our examples and Gleason's
+theorem suggests that when we increase the measurement resources,
+interval-valued probability measures could more and more likely be
+identified to a particular state as shown in table~\ref{table_long}.
 \begin{table}[ht]
@@
 How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
-\end{tabular}}\caption{Summarize example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value}
-and Gleason's theorem}
+\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
+measures}
 \label{table_long}
 \end{table}
-Although the tend is clear, we still need more examples to fill the
-blank and to prove our idea. Some research questions might be
+Additional work is in progress on the following research questions:
 \begin{description}
@@
 corresponding to an interval-valued probability measure by only considering
-the state whose interval-valued probability is $\necess$. Define
-a general method which could be used to determine whether an interval-valued
+the state whose interval-valued probability is $\necess$. Find a
+general method which could be used to determine whether an interval-valued
 probability measure is closer to the Born rule or not. 
@@
 measure converges to the measure induced by the Born rule. 
+\item [{Research Question.}] Investigate the status of the theorems of
+Gleason, Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+and Kochen-Specker for quantum interval-valued probability measures.
 \end{description}
-Since the validity of Gleason's theorem in a world with finite-precision
-measurements is a question, the natural follow-up questions is to
-investigate the status of the theorems of Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-and Kochen-Specker for quantum interval-valued probability measures
-as well. Going further we actually have to concede not just the infinite
-accuracy of the quantum state, but its very existence as a ``real''
-entity that exists independently of measurements and probabilities.
-The reasons for this second radical position are as follows. First
-arguments embedded in the proof of the Kochen-Specker theorem essentially
-rule out the existence of a sample space as the probabilities of events
-cannot be consistently expressed using core assignments to elements
-of the sample space. Second, the frequency interpretation of probability
-which is already problematic in the classical case, becomes untenable
-in the quantum case. In both cases, but much more in the quantum case,
-it is much more sensible to interpret probability in the Bayesian
-sense as ``lack of knowledge''. This, and similar arguments elegantly
-expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
-suggest that the quantum state is more like an interactive system
-in computer science parlance. In other words, the state is only determined
-by its interactions with the environment or observers. A rough but
-useful analogy in the context of computer science would be a web server:
-the state of such a system cannot be said to exist independently of
-the interactions with clients; each interaction with a client determines
-a future state of the system and may affect future interactions. Crucially,
-each client may have a \emph{different} view of the web server that
-is consistent with their own history of interactions. This computational
-perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
-that asserts that the quantum state is subjective: each observer has
-a different view of the quantum system that is consistent with their
-previous observations and that allows that observer, independently
-of other observers, to assign beliefs (i.e., probabilities) to possible
-future interactions.
+Although we tried to induce a quantum interval-valued probability
+measure from a real quantum state, our investigation leaves an open
+question of whether there exists a ``real'' entity that exists independently
+of measurements and probabilities. This idea is consistent with the
+elegantly recent work on Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+which suggests that the quantum state is more like an interactive
+system in computer science parlance. Moreover, the quantum state is
+subjective: each observer has a different view of the quantum system
+that is consistent with their previous observations and that allows
+that observer, independently of other observers, to assign beliefs
+(i.e., probabilities) to possible future interactions.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+\newpage{}%
+\begin{comment}
+ \bibliographystyle{plain}
+\bibliography{proposal/prop}
+
+\end{comment}
 \printbibliography 

### 2016-12-06 prop.tex
prop.tex \section{Conclusion and Discussion} Updating...

@@
 then quantum states themselves can only be discussed within intervals
-of confidence. This raises an important philosophical question with
-immense practical relevance in the context of quantum computing. The
-question, which we could largely bypass in the classical case, is
-whether there is, in the background of all the measurements and probabilities,
-a ``real'' infinitely-precise quantum state that is being approximated
-and that, in principle, can be more and more accurately described
-given more and more resources. Although a coarse quantum interval-valued
-probability measure may not be induced by one infinitely-precise quantum
-state, it might be induced by many quantum states when we examine
-different part of its probability assignment. Our examples and Gleason's
-theorem suggests that when we increase the measurement resources,
-interval-valued probability measures could more and more likely be
-identified to a particular state as shown in table~\ref{table_long}.
+of confidence. In contrast with the classical case, we found that
+there may be no ``real'' infinitely-precise quantum state that is
+being approximated when the approximating interval-value probability
+measure is not sufficiently accurate. However, a coarse quantum interval-valued
+probability measure might still be induced by many different quantum
+states when we examine different part of its probability assignment.
+Moreover, our examples and Gleason's theorem suggests that as the
+measurement resources increase, interval-valued probability measures
+could more and more likely be identified to a particular state as
+shown in table~\ref{table_long}. 
 \begin{table}[ht]

### 2016-12-06 prop.tex

@@
 then quantum states themselves can only be discussed within intervals
-of confidence. In contrast with the classical case, we found that
-there may be no ``real'' infinitely-precise quantum state that is
-being approximated when the approximating interval-value probability
-measure is not sufficiently accurate. However, a coarse quantum interval-valued
-probability measure might still be induced by many different quantum
-states when we examine different part of its probability assignment.
-Moreover, our examples and Gleason's theorem suggests that as the
-measurement resources increase, interval-valued probability measures
-could more and more likely be identified to a particular state as
-shown in table~\ref{table_long}. 
+of confidence. Despite the fact that a classical interval-value probability
+measure could always correspond to some classical ``real'' infinitely-precise
+probability measure, we found that there may be no ``real'' infinitely-precise
+quantum state that is being approximated by a quantum interval-value
+probability measure as a whole. However, if we break a quantum interval-valued
+probability measure into pieces, each piece might still be induced
+by some quantum states. Moreover, our examples and Gleason's theorem
+suggests that as the measurement resources increase, an entire interval-valued
+probability measure could more and more likely be identified to a
+particular state as shown in table~\ref{table_long}. 
 \begin{table}[ht]

### 2016-12-06 prop.tex
prop.tex \section{Conclusion and Discussion} Updating...

--- 2016-12-06 prop.tex
@@
 then quantum states themselves can only be discussed within intervals
-of confidence. In contrast with the classical case, we found that
-there may be no ``real'' infinitely-precise quantum state that is
-being approximated when the approximating interval-value probability
-measure is not sufficiently accurate. However, a coarse quantum interval-valued
-probability measure might still be induced by many different quantum
-states when we examine different part of its probability assignment.
-Moreover, our examples and Gleason's theorem suggests that as the
-measurement resources increase, interval-valued probability measures
-could more and more likely be identified to a particular state as
-shown in table~\ref{table_long}. 
+of confidence. Despite the fact that a classical interval-value probability
+measure could always correspond to some classical ``real'' infinitely-precise
+probability measure, we found that there may be no ``real'' infinitely-precise
+quantum state approximated by a quantum interval-value probability
+measure as a whole. However, if a quantum interval-valued probability
+measure is decomposed into pieces, each piece might still be induced
+by a quantum state. Moreover, our examples and Gleason's theorem summarized
+in table~\ref{table_long} suggests that as the measurement resources
+increase, an entire interval-valued probability measure could more
+and more likely be identified to a particular state. 
 \begin{table}[ht]
@@
 is bigger than zero. 
-\item [{Research Question.}] In example~\ref{ex:three-dimensional-three-value}
-and \ref{ex:three-dimensional-4-value}, we pick a possible candidate
-corresponding to an interval-valued probability measure by only considering
-the state whose interval-valued probability is $\necess$. Find a
-general method which could be used to determine whether an interval-valued
-probability measure is closer to the Born rule or not. 
+\item [{Research Question.}] Find a general method to determine how an
+interval-valued probability measure is close to the Born rule. 
 \item [{Research Question.}] Confirm that as the number and precision

### 2016-12-08 prop.tex
prop.tex \section{Conclusion and Discussion} Updating...

@@
 then quantum states themselves can only be discussed within intervals
-of confidence. Despite the fact that a classical interval-value probability
-measure could always correspond to some classical ``real'' infinitely-precise
-probability measure, we found that there may be no ``real'' infinitely-precise
-quantum state approximated by a quantum interval-value probability
+of confidence. Despite the fact that classically a interval-valued
+probability measure could always correspond to a real-valued probability
+measure, we found that there may be no ``real'' infinitely-precise
+quantum state approximated by a quantum interval-valued probability
 measure as a whole. However, if a quantum interval-valued probability
@@
 in table~\ref{table_long} suggests that as the measurement resources
-increase, an entire interval-valued probability measure could more
-and more likely be identified to a particular state. 
+increase, an entire quantum interval-valued probability measure could
+more and more likely be identified to a particular state. 
 \begin{table}[ht]
@@
 \begin{description}
-\item [{Research Question.}] Confirm that there is always an interval-valued
-probability measure with an empty-core if the length of the interval
+\item [{Research Question.}] Confirm that there is always a quantum interval-valued
+probability measure with an empty-core if the length of the intervals
 is bigger than zero. 
-\item [{Research Question.}] Find a general method to determine how an
-interval-valued probability measure is close to the Born rule. 
+\item [{Research Question.}] Find a general method to determine how a
+quantum interval-valued probability measure is close to the Born rule. 
 \item [{Research Question.}] Confirm that as the number and precision
@@
 \end{description}
-Although we tried to induce a quantum interval-valued probability
-measure from a real quantum state, our investigation leaves an open
-question of whether there exists a ``real'' entity that exists independently
-of measurements and probabilities. This idea is consistent with the
-elegantly recent work on Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
-which suggests that the quantum state is more like an interactive
-system in computer science parlance. Moreover, the quantum state is
-subjective: each observer has a different view of the quantum system
-that is consistent with their previous observations and that allows
-that observer, independently of other observers, to assign beliefs
-(i.e., probabilities) to possible future interactions.
+Although we discussed how a quantum interval-valued probability measure
+could be induced from a real quantum state, our investigation leaves
+an open question of whether there exists a ``real'' entity that
+exists independently of measurements and probabilities. This idea
+is consistent with the elegantly recent work on Quantum Bayesianism
+or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which suggests
+that the quantum state is more like an interactive system in computer
+science parlance. Moreover, the quantum state is subjective: each
+observer has a different view of the quantum system that is consistent
+with their previous observations and that allows that observer, independently
+of other observers, to assign beliefs (i.e., probabilities) to possible
+future interactions.
 

### 2016-12-08 prop.tex
prob.tex \section{Conclusion and Discussion} Updating...

@@
 an open question of whether there exists a ``real'' entity that
-exists independently of measurements and probabilities. This idea
-is consistent with the elegantly recent work on Quantum Bayesianism
-or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which suggests
-that the quantum state is more like an interactive system in computer
-science parlance. Moreover, the quantum state is subjective: each
-observer has a different view of the quantum system that is consistent
-with their previous observations and that allows that observer, independently
-of other observers, to assign beliefs (i.e., probabilities) to possible
-future interactions.
+exists independently of measurements and probabilities. The possibility
+of no ``real'' underlying state is consistent with the elegantly
+recent work on Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+which suggests that the quantum state is more like an interactive
+system in computer science parlance. In another word, the quantum
+state is subjective: each observer has a different view of the quantum
+system that is consistent with their previous observations and that
+allows that observer, independently of other observers, to assign
+beliefs (i.e., probabilities) to possible future interactions.
 

### 2016-12-09 prop.tex
prop.tex \section{Introduction} Add citation...

@@
 This is a \emph{theoretical} investigation of \emph{experimental}
-physics using \emph{computational} methods. All experiments and
-computations are processes bounded in space, time, energy, and other
-resources. Yet, for centuries, the mathematical formalization of such
-processes has been founded on the infinitely precise real or complex
-numbers. Indeed, almost every description of quantum mechanics,
-quantum computation, or quantum experiments refers to entities such as
-$e$, $\pi$, $\sqrt{2}$, etc. From a computational perspective, such
-numbers do not exist in their entirety ``for free.''  For example, the
-state of the art algorithms for computing the $n$th binary digit of~$\pi$
-require on the order of $O(n\log^{O(1)}(n))$
-operations~\cite{journals/moc/BaileyBP97}. In other words, simply
-referring to the $n$th digit of $\pi$ requires more and more resources
-as $n$ gets larger. Taking such resource bounds into consideration is
-what founded computer science as a discipline and is crucial for
-understanding the very nature of computation and, following
-Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
+physics using \emph{computational} methods. All experiments and computations
+are processes bounded in space, time, energy, and other resources.
+Yet, for centuries, the mathematical formalization of such processes
+has been founded on the infinitely precise real or complex numbers~\cite{Kent1999,CliftonKent2000}.
+Indeed, almost every description of quantum mechanics, quantum computation,
+or quantum experiments refers to entities such as $e$, $\pi$, $\sqrt{2}$,
+etc. From a computational perspective, such numbers do not exist in
+their entirety ``for free.'' For example, the state of the art algorithms
+for computing the $n$th binary digit of~$\pi$ require on the order
+of $O(n\log^{O(1)}(n))$ operations~\cite{journals/moc/BaileyBP97}.
+In other words, simply referring to the $n$th digit of $\pi$ requires
+more and more resources as $n$ gets larger. Taking such resource
+bounds into consideration is what founded computer science as a discipline
+and is crucial for understanding the very nature of computation and,
+following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
 and others, for understanding the very nature of physical processes.

### 2016-12-09 prop.tex
prop.tex \section{Introduction} Add citations, but it's delicate whether these citations fit here or not...

@@
 physics using \emph{computational} methods. All experiments and computations
-are processes bounded in space, time, energy, and other resources.
+are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007,Li2009}.
 Yet, for centuries, the mathematical formalization of such processes
@@
 Indeed, almost every description of quantum mechanics, quantum computation,
-or quantum experiments refers to entities such as $e$, $\pi$, $\sqrt{2}$,
-etc. From a computational perspective, such numbers do not exist in
-their entirety ``for free.'' For example, the state of the art algorithms
-for computing the $n$th binary digit of~$\pi$ require on the order
-of $O(n\log^{O(1)}(n))$ operations~\cite{journals/moc/BaileyBP97}.
+or quantum experiments refers to entities such as $\rme$, $\pi$,
+$\sqrt{2}$, etc. From a computational perspective, such numbers do
+not exist in their entirety ``for free.'' For example, the state
+of the art algorithms for computing the $n$th binary digit of~$\pi$
+require on the order of $O(n\log^{O(1)}(n))$ operations~\cite{journals/moc/BaileyBP97}.
 In other words, simply referring to the $n$th digit of $\pi$ requires

### 2016-12-10 prop.tex
prop.tex \section{Introduction} Reorginize to make more like a paper...

@@
 Yet, for centuries, the mathematical formalization of such processes
-has been founded on the infinitely precise real or complex numbers~\cite{Kent1999,CliftonKent2000}.
+has been founded on the infinitely precise real or complex numbers.
+Our purpose here is exploit the consequences of replacing infinitely-specified
+quantum probabilities by finite number of intervals used in interval-valued
+probability measures; in particular, we show that a quantum interval-valued
+probability measure may not be induced by a infinitely-precise state,
+but it might be more and more likely to be identified to a particular
+state when the measurement resources increase.
+
 Indeed, almost every description of quantum mechanics, quantum computation,
@@
 $\sqrt{2}$, etc. From a computational perspective, such numbers do
-not exist in their entirety ``for free.'' For example, the state
-of the art algorithms for computing the $n$th binary digit of~$\pi$
-require on the order of $O(n\log^{O(1)}(n))$ operations~\cite{journals/moc/BaileyBP97}.
-In other words, simply referring to the $n$th digit of $\pi$ requires
-more and more resources as $n$ gets larger. Taking such resource
-bounds into consideration is what founded computer science as a discipline
-and is crucial for understanding the very nature of computation and,
-following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
-and others, for understanding the very nature of physical processes.
+not exist in their entirety ``for free~\cite{Kent1999,CliftonKent2000}.''
+For example, the state of the art algorithms for computing the $n$th
+binary digit of~$\pi$ require on the order of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
+operations~\cite{journals/moc/BaileyBP97}. In other words, simply
+referring to the $n$th digit of $\pi$ requires more and more resources
+as $n$ gets larger. Taking such resource bounds into consideration
+is what founded computer science as a discipline and is crucial for
+understanding the very nature of computation and, following Feynman~\cite{Feynman1982Simulating},
+Landauer~\cite{Landauer1996188}, and others, for understanding the
+very nature of physical processes.
 
@@
 reliance on the infinitely precise real
-numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is to
+numbers~\cite{geometry2013,DQT2014}.
+
+In this proposal, our aim is to
 shift focus from the infinitely-specified but not directly observable
@@
 \begin{itemize}
-\item A computational framework for quantum measurement where quantum
-  systems are described in terms of interactive processes. The
-  framework takes care of the resources required (including the ones
-  related to the observer) to determine a given property of the
-  measured system.
 \item Develop a measurement framework based on quantum interval-valued
@@
   theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
-\item Study the computational complexity of quantum theories and
-  simulations based on discrete (computable) fields.
-\item Study the problem of finding a complete set of mutually unbiased
-  bases
-  (SIC-POVM)~\cite{1751-8121-45-8-085306,1751-8121-47-33-335302,Caves2002}
-  over finite Galois fields.
 \end{itemize}
-We argue that no matter what the results are their impact will be
-strong. Positive results that formulate a computable, with clear
-resource bounds, theory of quantum measurement and quantum probability
-would be essential for understanding and realizing quantum
-computation. Any negative results would redirect research that aims at
-realizing quantum computation to other approaches. At an intellectual
-level, the results have the potential to solve or clarify several
-paradoxes in quantum mechanics, quantum information, computability,
-complexity theory, and perhaps quantum gravity.
 

### 2016-12-10 prop.tex
prop.tex \section{Introduction} Add citations...

@@
 physics using \emph{computational} methods. All experiments and computations
-are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007,Li2009}.
+are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007}.
 Yet, for centuries, the mathematical formalization of such processes
 has been founded on the infinitely precise real or complex numbers.
-Our purpose here is exploit the consequences of replacing infinitely-specified
+Our purpose here is to exploit the consequences of replacing infinitely-specified
 quantum probabilities by finite number of intervals used in interval-valued
@@
 or quantum experiments refers to entities such as $\rme$, $\pi$,
-$\sqrt{2}$, etc. From a computational perspective, such numbers do
-not exist in their entirety ``for free~\cite{Kent1999,CliftonKent2000}.''
-For example, the state of the art algorithms for computing the $n$th
-binary digit of~$\pi$ require on the order of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
+$\sqrt{2}$, etc (see, e.g., \cite{Redhead1987-REDINA,544199,Mermin2007}).
+From a computational perspective, such numbers do not exist in their
+entirety ``for free~\cite{Kent1999,CliftonKent2000}.'' For example,
+the state of the art algorithms for computing the $n$th binary digit
+of~$\pi$ require on the order of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
 operations~\cite{journals/moc/BaileyBP97}. In other words, simply
@@
 
-We propose to revisit quantum mechanics, quantum information, and
+We have been revisiting quantum mechanics, quantum information, and
 quantum computation from this resource-aware perspective. Our initial
-results in that domain showed how subtle the issues can
-be~\cite{usat,geometry2013,DQT2014}: a straightforward replacement of
-the complex numbers by a finite field yields a variant of quantum
-mechanics in which computationally hard problems like UNIQUE-SAT
-(which decides whether a given Boolean formula is unsatisfiable or has
-exactly one satisfying assignment) can be deterministically solved in
-constant time. To eliminate such unrealistic theories requires
-delicate analysis of the structure of the Hilbert space, the process
-of observation, and the notion of probability teasing apart their
-reliance on the infinitely precise real
-numbers~\cite{geometry2013,DQT2014}.
+results in that domain showed how subtle the issues can be~\cite{usat,geometry2013,DQT2014}:
+a straightforward replacement of the complex numbers by a finite field
+yields a variant of quantum mechanics in which computationally hard
+problems like UNIQUE-SAT (which decides whether a given Boolean formula
+is unsatisfiable or has exactly one satisfying assignment~\cite{Valiant198685,Papadimitriou1993,AroraBarak2009})
+can be deterministically solved in constant time. To eliminate such
+unrealistic theories requires delicate analysis of the structure of
+the Hilbert space, the process of observation, and the notion of probability
+teasing apart their reliance on the infinitely precise real numbers~\cite{geometry2013,DQT2014}.
 
-In this proposal, our aim is to
-shift focus from the infinitely-specified but not directly observable
-quantum states, to observable measurable properties of quantum systems
-and their probabilities. Furthermore, we insist that our theories of
-measurement and probability only refer to finitely communicable
-evidence within feasible computational bounds. It follows that states,
-observations, and probabilities all become ``fuzzy'', i.e., specified
-by intervals of confidence that can only increase in precision if the
-available resources increase proportionally. Our notion of ``fuzzy
-quantum mechanics'' is related to existing
-work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
+In this paper, we shift focus from the infinitely-specified but not
+directly observable quantum states, to observable measurable properties
+of quantum systems and their probabilities. Furthermore, we insist
+that our theories of measurement and probability only refer to finitely
+communicable evidence within feasible computational bounds. It follows
+that states, observations, and probabilities all become ``fuzzy'',
+i.e., specified by intervals of confidence that can only increase
+in precision if the available resources increase proportionally. Our
+notion of ``fuzzy quantum mechanics'' is related to existing work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
 but, as will be explained in more detail, is distinguished by its
@@
 
-We will begin by reviewing existing work that recasts classical
-probability spaces in a resource-aware setting and move to our
-proposal which, briefly speaking, aims at recasting quantum
-probability and hence quantum measurement to a corresponding
-resource-aware setting.
-
-In particular, the objectives to be achieved include:
+We will begin by reviewing existing work that recasts classical probability
+spaces in a resource-aware setting and move to aim at recasting quantum
+probability and hence quantum measurement to a corresponding resource-aware
+setting. In particular, we develop a measurement framework based on
+quantum interval-valued probabilities measures. 
 \begin{itemize}
-\item Develop a measurement framework based on quantum interval-valued
-  probabilities measures.
-\item Assess the validity of fundamental theorems of quantum
-  mechanics, such as Gleason, Bell, and Kochen-Specker, in a quantum
-  formulation stripped away of infinite resources. We will aim to
-  provide a definite answer to the Meyer-Mermin
-  debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004} on
-  the impact of finite precision measurements on the relevance of the
-  Kochen-Specker
-  theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
+\item Assess the validity of fundamental theorems of quantum mechanics,
+such as Gleason~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum},
+Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
+and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
+in a quantum formulation stripped away of infinite resources. We will
+aim to provide a definite answer to the Meyer-Mermin debate~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}
+on the impact of finite precision measurements on the relevance of
+the Kochen-Specker theorem. 
 \end{itemize}
@@
 \item [{Research Question.}] Investigate the status of the theorems of
-Gleason, Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-and Kochen-Specker for quantum interval-valued probability measures.
+Gleason, Bell, and Kochen-Specker for quantum interval-valued probability
+measures.
 \end{description}

### 2016-12-11 prop.tex
prop.tex \section{Introduction} Add Citations...

@@
 physics using \emph{computational} methods. All experiments and computations
-are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007}.
+are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007,Piccinini2015}.
 Yet, for centuries, the mathematical formalization of such processes
-has been founded on the infinitely precise real or complex numbers.
+has been founded on the infinitely precise real or complex numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
 Our purpose here is to exploit the consequences of replacing infinitely-specified

### 2016-12-11 prop.tex
prop.tex \section{Introduction} Add the main result and prospective...

@@
 quantum probabilities by finite number of intervals used in interval-valued
-probability measures; in particular, we show that a quantum interval-valued
-probability measure may not be induced by a infinitely-precise state,
-but it might be more and more likely to be identified to a particular
-state when the measurement resources increase.
+probability measures~(IVPM); in particular, we show that a quantum
+interval-valued probability measure may not be induced by a infinitely-precise
+state, but it might be more and more likely to be identified to a
+particular state when the measurement resources increase.
 
@@
 setting. In particular, we develop a measurement framework based on
-quantum interval-valued probabilities measures. 
-\begin{itemize}
-\item Assess the validity of fundamental theorems of quantum mechanics,
-such as Gleason~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum},
-Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
+quantum interval-valued probability measures. Surprisingly, we found
+a quantum IVPM which can not be induced by a state while Shapley proved
+a classical convex IVPM can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
+and Gleason proved a infinitely-specified quantum probabilities measure
+can always be induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+Nevertheless, a quantum IVPM could still correspond to many states
+while we break it into pieces. Our examples also suggest that a quantum
+IVPM could be more and more likely induced by a state while the intervals
+become sharper, i.e., the measurement resources increase.
+
+Since Gleason's theorem supports the idea of von Neumann to formulate
+quantum states as points in a projective Hilbert space, a point in
+a projective Hilbert space might not be the adequate imprecise quantum
+``state.'' Instead, a quantum state might be more like an interactive
+system suggested by Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+which would be different for different interactor. Furthermore, the
+fundamental theorems of quantum mechanics followed up by Gleason's
+theorem , such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
 and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
-in a quantum formulation stripped away of infinite resources. We will
-aim to provide a definite answer to the Meyer-Mermin debate~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}
-on the impact of finite precision measurements on the relevance of
-the Kochen-Specker theorem. 
-\end{itemize}
+might need to be reassessed the validity with imprecise measurement.
+Our research then might provide a new insight to the old debate whether
+finite precision measurement would nullify the Kochen-Specker theorem
+or not, by Meyer, Mermin, and others~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.
 

### 2016-12-12 prop.tex
prop.tex \section{Introduction} Updating...

@@
 setting. In particular, we develop a measurement framework based on
-quantum interval-valued probability measures. Surprisingly, we found
-a quantum IVPM which can not be induced by a state while Shapley proved
-a classical convex IVPM can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
+quantum IVPM. Surprisingly, we found a quantum IVPM which can not
+be induced by a state, while Shapley proved a classical convex IVPM
+can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
 and Gleason proved a infinitely-specified quantum probabilities measure
 can always be induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-Nevertheless, a quantum IVPM could still correspond to many states
-while we break it into pieces. Our examples also suggest that a quantum
-IVPM could be more and more likely induced by a state while the intervals
-become sharper, i.e., the measurement resources increase.
+Nevertheless, a quantum IVPM could still correspond to many possible
+states if we break it into pieces. Our examples also suggest that
+a quantum IVPM could be more and more likely induced by a state while
+the intervals become sharper, i.e., the measurement resources increase.
 
@@
 which would be different for different interactor. Furthermore, the
-fundamental theorems of quantum mechanics followed up by Gleason's
-theorem , such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+validity the fundamental theorems of quantum mechanics followed up
+by Gleason's theorem, such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
 and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
-might need to be reassessed the validity with imprecise measurement.
-Our research then might provide a new insight to the old debate whether
-finite precision measurement would nullify the Kochen-Specker theorem
-or not, by Meyer, Mermin, and others~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.
+might need to be reassessed based on our imprecise measurement. Our
+research then might provide a new insight to the old debate among
+Meyer, Mermin, and others about whether finite precision measurement
+would nullify the Kochen-Specker theorem or not~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.
 

### 2016-12-13 prop.tex
prop.tex \section{Introduction} \section{Conclusion and Discussion} Review before release to professors...

@@
 spaces in a resource-aware setting and move to aim at recasting quantum
-probability and hence quantum measurement to a corresponding resource-aware
-setting. In particular, we develop a measurement framework based on
-quantum IVPM. Surprisingly, we found a quantum IVPM which can not
-be induced by a state, while Shapley proved a classical convex IVPM
-can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
+probability and quantum measurement. In particular, we develop a measurement
+framework based on quantum IVPM. Surprisingly, we found a quantum
+IVPM which can not be induced by a state, while Shapley proved a classical
+convex IVPM can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
 and Gleason proved a infinitely-specified quantum probabilities measure
@@
 Nevertheless, a quantum IVPM could still correspond to many possible
-states if we break it into pieces. Our examples also suggest that
+states if it is broken into pieces. Our examples also suggest that
 a quantum IVPM could be more and more likely induced by a state while
@@
 
-Since Gleason's theorem supports the idea of von Neumann to formulate
-quantum states as points in a projective Hilbert space, a point in
-a projective Hilbert space might not be the adequate imprecise quantum
-``state.'' Instead, a quantum state might be more like an interactive
-system suggested by Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
-which would be different for different interactor. Furthermore, the
-validity the fundamental theorems of quantum mechanics followed up
-by Gleason's theorem, such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+Since Gleason's theorem supports the idea of von Neumann to define
+a state as a density matrix~\cite{Varadarajan2008}, a density matrix
+might not be a adequate imprecise quantum state. Instead, a imprecise
+quantum state might be more like an interactive system suggested by
+Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+which would interact differently with different clients. Furthermore,
+the validity the fundamental theorems of quantum mechanics followed
+up by Gleason's theorem, such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
 and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
@@
 then quantum states themselves can only be discussed within intervals
-of confidence. Despite the fact that classically a interval-valued
-probability measure could always correspond to a real-valued probability
-measure, we found that there may be no ``real'' infinitely-precise
-quantum state approximated by a quantum interval-valued probability
-measure as a whole. However, if a quantum interval-valued probability
-measure is decomposed into pieces, each piece might still be induced
-by a quantum state. Moreover, our examples and Gleason's theorem summarized
-in table~\ref{table_long} suggests that as the measurement resources
-increase, an entire quantum interval-valued probability measure could
-more and more likely be identified to a particular state. 
+of confidence. Despite the fact that classically a IVPM could always
+correspond to a real-valued probability measure, we found that there
+may be no ``real'' infinitely-precise quantum state approximated
+by a quantum IVPM as a whole. However, if a quantum IVPM is decomposed
+into pieces, each piece might still be induced by a quantum state.
+Moreover, our examples and Gleason's theorem summarized in table~\ref{table_long}
+suggests that as the measurement resources increase, an entire quantum
+IVPM could more and more likely be identified to a particular state.
 \begin{table}[ht]
@@
 Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
-Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
+Count of states correspond to pieces of $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
 \hline 
@@
 \begin{description}
-\item [{Research Question.}] Confirm that there is always a quantum interval-valued
-probability measure with an empty-core if the length of the intervals
-is bigger than zero. 
+\item [{Research Question.}] Confirm that there is always a quantum IVPM
+with an empty-core if the length of the intervals is bigger than zero. 
 \item [{Research Question.}] Find a general method to determine how a
-quantum interval-valued probability measure is close to the Born rule. 
+quantum IVPM is close to the Born rule. 
 \item [{Research Question.}] Confirm that as the number and precision
-of the intervals increase the quantum interval-valued probability
-measure converges to the measure induced by the Born rule. 
+of the intervals increase the quantum IVPM converges to the measure
+induced by the Born rule. 
 \item [{Research Question.}] Investigate the status of the theorems of
-Gleason, Bell, and Kochen-Specker for quantum interval-valued probability
-measures.
+Bell and Kochen-Specker for quantum IVPM.
 \end{description}
-Although we discussed how a quantum interval-valued probability measure
-could be induced from a real quantum state, our investigation leaves
-an open question of whether there exists a ``real'' entity that
-exists independently of measurements and probabilities. The possibility
-of no ``real'' underlying state is consistent with the elegantly
-recent work on Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
-which suggests that the quantum state is more like an interactive
-system in computer science parlance. In another word, the quantum
-state is subjective: each observer has a different view of the quantum
-system that is consistent with their previous observations and that
-allows that observer, independently of other observers, to assign
-beliefs (i.e., probabilities) to possible future interactions.
+Although we discussed how a quantum IVPM could be induced from a real
+quantum state, our investigation leaves an open question of whether
+there exists a ``real'' entity that exists independently of measurements
+and probabilities. The possibility of no ``real'' underlying state
+is consistent with the elegantly recent work on Quantum Bayesianism
+or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which suggests
+that the quantum state is more like an interactive system in computer
+science parlance. In another word, the quantum state is subjective:
+each observer has a different view of the quantum system that is consistent
+with their previous observations and that allows that observer, independently
+of other observers, to assign beliefs (i.e., probabilities) to possible
+future interactions.
 

### 2016-12-13 prop.tex
prop.tex \section{Introduction} Updating...

@@
 probability measures~(IVPM); in particular, we show that a quantum
-interval-valued probability measure may not be induced by a infinitely-precise
-state, but it might be more and more likely to be identified to a
-particular state when the measurement resources increase.
+IVPM may not be induced by a infinitely-precise state, but it might
+be more and more likely to be identified to a particular state when
+the measurement resources increase.
 

### 2016-12-21 prop.tex

@@
 Bohr argued (and Mott later on justified his assertion by an elegant
-use of uncertainty relations~\cite{10.2307/j.ctt7ztxn5.15}) that a
+use of uncertainty relations~\cite{Mott_1929}) that a
 Stern-Gerlach experiment could not succeed in establishing the spin of

### 2016-12-22 prop.tex
prop.tex \subsection{Measuring Quantum Probabilities} Add citation...

--- 2016-12-13 prop.tex
@@
 section, assuming identical measurements conditions in each repeated
-experiment~\cite{peres1995quantum}. 
-For instance, if one wants to determine the probability
-that the spin of a given silver atom is $+\hbar/2$, a Stern-Gerlach
-apparatus is built where ideally an inhomogeneous magnetic field is
-generated along, let's say, the quantization axis $z$. One then
-produces a collimated beam of identically prepared (neutral) silver
-atoms that is directed between the poles of the magnet where a
-predetermined field-gradient along the $z$ direction has been
-established. Under appropriate experimental conditions we will observe
-that the beam, after traversing the magnetic-field region, will be
-deflected towards two regions identified by distinguished spots on a
-detector situated behind the
-apparatus~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
-Each of the two discrete values is associated to either $+\hbar/2$ or
-$-\hbar/2$, commonly called ``spin up'' and ``spin down'',
+experiment~\cite{peres1995quantum}. For instance, if one wants to
+determine the probability that the spin of a given silver atom is
+$+\hbar/2$, a Stern-Gerlach apparatus is built where ideally an inhomogeneous
+magnetic field is generated along, let's say, the quantization axis
+$z$. One then produces a collimated beam of identically prepared
+(neutral) silver atoms that is directed between the poles of the magnet
+where a predetermined field-gradient along the $z$ direction has
+been established. Under appropriate experimental conditions we will
+observe that the beam, after traversing the magnetic-field region,
+will be deflected towards two regions identified by distinguished
+spots on a detector situated behind the apparatus~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
+Each of the two discrete values is associated to either $+\hbar/2$
+or $-\hbar/2$, commonly called ``spin up'' and ``spin down'',
 respectively. By ``counting'' the number of atoms that are deflected
-in the ``spin up'' region one can, in principle, estimate the
-probability that the prepared state of the silver atom state has spin
-$+\hbar/2$. Notice that a real experiment does not necessarily
-represent an ``ideal measurement''. For example, not all silver atoms
-will be identically prepared, or the field-gradient could not be large
-enough to distinguish between the spin up and down situations simply
-producing a large single blot. In other words, the closer we get to an
-ideal measurement the better we determine those probabilities at the
-cost of significantly increasing the number of resources. It is not
-very well appreciated in the literature that Bohr attempted to argue
-against the measurability of the spin of a free electron. Essentially,
-Bohr argued (and Mott later on justified his assertion by an elegant
-use of uncertainty relations~\cite{10.2307/j.ctt7ztxn5.15}) that a
-Stern-Gerlach experiment could not succeed in establishing the spin of
-an unbound electron because the Lorentz force would blur the detected
-pattern. This example illustrates the case of a fundamental physical
-limitation that not even infinite resources could mitigate.
+in the ``spin up'' region one can, in principle, estimate the probability
+that the prepared state of the silver atom state has spin $+\hbar/2$.
+Notice that a real experiment does not necessarily represent an ``ideal
+measurement''. For example, not all silver atoms will be identically
+prepared, or the field-gradient could not be large enough to distinguish
+between the spin up and down situations simply producing a large single
+blot. In other words, the closer we get to an ideal measurement the
+better we determine those probabilities at the cost of significantly
+increasing the number of resources. It is not very well appreciated
+in the literature that Bohr attempted to argue against the measurability
+of the spin of a free electron~\cite{MartensDeMuynck1994,McEvoy2001}.
+Essentially, Bohr argued (and Mott later on justified his assertion
+by an elegant use of uncertainty relations~\cite{10.2307/j.ctt7ztxn5.15})
+that a Stern-Gerlach experiment could not succeed in establishing
+the spin of an unbound electron because the Lorentz force would blur
+the detected pattern. This example illustrates the case of a fundamental
+physical limitation that not even infinite resources could mitigate.
 

### 2016-12-23 prop.tex
prop.tex \subsection{Measuring Quantum Probabilities} Cite Bohr's original work...?

--- 2016-12-13 prop.tex
@@
 section, assuming identical measurements conditions in each repeated
-experiment~\cite{peres1995quantum}. 
-For instance, if one wants to determine the probability
-that the spin of a given silver atom is $+\hbar/2$, a Stern-Gerlach
-apparatus is built where ideally an inhomogeneous magnetic field is
-generated along, let's say, the quantization axis $z$. One then
-produces a collimated beam of identically prepared (neutral) silver
-atoms that is directed between the poles of the magnet where a
-predetermined field-gradient along the $z$ direction has been
-established. Under appropriate experimental conditions we will observe
-that the beam, after traversing the magnetic-field region, will be
-deflected towards two regions identified by distinguished spots on a
-detector situated behind the
-apparatus~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
-Each of the two discrete values is associated to either $+\hbar/2$ or
-$-\hbar/2$, commonly called ``spin up'' and ``spin down'',
+experiment~\cite{peres1995quantum}. For instance, if one wants to
+determine the probability that the spin of a given silver atom is
+$+\hbar/2$, a Stern-Gerlach apparatus is built where ideally an inhomogeneous
+magnetic field is generated along, let's say, the quantization axis
+$z$. One then produces a collimated beam of identically prepared
+(neutral) silver atoms that is directed between the poles of the magnet
+where a predetermined field-gradient along the $z$ direction has
+been established. Under appropriate experimental conditions we will
+observe that the beam, after traversing the magnetic-field region,
+will be deflected towards two regions identified by distinguished
+spots on a detector situated behind the apparatus~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
+Each of the two discrete values is associated to either $+\hbar/2$
+or $-\hbar/2$, commonly called ``spin up'' and ``spin down'',
 respectively. By ``counting'' the number of atoms that are deflected
-in the ``spin up'' region one can, in principle, estimate the
-probability that the prepared state of the silver atom state has spin
-$+\hbar/2$. Notice that a real experiment does not necessarily
-represent an ``ideal measurement''. For example, not all silver atoms
-will be identically prepared, or the field-gradient could not be large
-enough to distinguish between the spin up and down situations simply
-producing a large single blot. In other words, the closer we get to an
-ideal measurement the better we determine those probabilities at the
-cost of significantly increasing the number of resources. It is not
-very well appreciated in the literature that Bohr attempted to argue
-against the measurability of the spin of a free electron. Essentially,
-Bohr argued (and Mott later on justified his assertion by an elegant
-use of uncertainty relations~\cite{10.2307/j.ctt7ztxn5.15}) that a
-Stern-Gerlach experiment could not succeed in establishing the spin of
-an unbound electron because the Lorentz force would blur the detected
-pattern. This example illustrates the case of a fundamental physical
-limitation that not even infinite resources could mitigate.
+in the ``spin up'' region one can, in principle, estimate the probability
+that the prepared state of the silver atom state has spin $+\hbar/2$.
+Notice that a real experiment does not necessarily represent an ``ideal
+measurement''. For example, not all silver atoms will be identically
+prepared, or the field-gradient could not be large enough to distinguish
+between the spin up and down situations simply producing a large single
+blot. In other words, the closer we get to an ideal measurement the
+better we determine those probabilities at the cost of significantly
+increasing the number of resources. It is not very well appreciated
+in the literature that Bohr attempted to argue against the measurability
+of the spin of a free electron~\cite{Bohr1985,MartensDeMuynck1994,McEvoy2001}.
+Essentially, Bohr argued (and Mott later on justified his assertion
+by an elegant use of uncertainty relations~\cite{10.2307/j.ctt7ztxn5.15})
+that a Stern-Gerlach experiment could not succeed in establishing
+the spin of an unbound electron because the Lorentz force would blur
+the detected pattern. This example illustrates the case of a fundamental
+physical limitation that not even infinite resources could mitigate.
 

### 2016-12-26 prop.tex
prop.tex \section{Quantum Interval-valued Probability Measures} Delete two sentences...
comment

@@
 \newcommand{\rmi}{\mathrm{i}}
+
+\usepackage{color}
+\usepackage[usenames,dvipsnames]{xcolor}
+\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
 
@@
 $\frac{1224}{3204}$.
+
+\amr{Another: the calculus of probabilities requires all probabilities to
+be \emph{coherent}. But given limited resources, a user can only
+approximate the probabilities and the approximation may not be
+completely coherent in the ideal sense.}
 
@@
 
-This is the most developed part of our current investigation and is
-presented in greater detail than the other proposed activities. It
-relies on current unpublished results. As argued in the previous
-sections, given fixed finite resources, it is only possible to
-estimate the quantum probabilities within an interval of
-confidence. It is therefore natural to propose the notion of a
-``quantum interval-valued probability measure'' that combines the
-definitions of conventional quantum probability measures with
+As argued in the previous sections, given fixed finite resources,
+it is only possible to estimate the quantum probabilities within an
+interval of confidence. It is therefore natural to propose the notion
+of a ``quantum interval-valued probability measure'' that combines
+the definitions of conventional quantum probability measures with
 classical interval-probabilities.

### 2017-01-11 Rethinking Foundations of Physics 2017/application.tex
Export to "Rethinking Foundations of Physics 2017\application.tex"

--- 2016-12-23 prop.tex
@@
+%% LyX 2.2.2 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
 \documentclass{article}
+\usepackage[utf8]{inputenc}
+\usepackage{verbatim}
+\usepackage{mathrsfs}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}
+
+\makeatletter
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
+\newcommand{\lyxaddress}[1]{
+\par {\raggedright #1
+\vspace{1.4em}
+\noindent\par}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
 \usepackage[ backend=biber]{biblatex}
-\addbibresource{proposal/prop.bib}
+%\addbibresource{../proposal/prop.bib}
+\addbibresource{C:/Users/Yu-Tsung/workspace/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/proposal/prop.bib}
 \ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
 \usepackage{fullpage}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{amsthm}
@@
 \usepackage{wesa}
-\usepackage{graphicx}
-\usepackage{verbatim}
 
 \theoremstyle{remark}
-\newtheorem{example}{Example}
-\newtheorem{definition}{Definition}
-\newtheorem{thm}{Theorem}
+\newtheorem{example}{Example}\newtheorem{definition}{Definition}\newtheorem{thm}{Theorem}
 
@@
 
+\makeatother
+
 \begin{document}
-\title{Measurement and Probability in Fuzzy Quantum Theories}
-\date{\today}
+
+\title{Application for Rethinking Foundations of Physics 2017}
+
+\author{Yu-Tsung Tai}
 \maketitle
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\lyxaddress{Department of Mathematics and School of Informatics and Computing\\
+Indiana University, Bloomington}
 
-This is a \emph{theoretical} investigation of \emph{experimental}
-physics using \emph{computational} methods. All experiments and computations
-are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007,Piccinini2015}.
-Yet, for centuries, the mathematical formalization of such processes
-has been founded on the infinitely precise real or complex numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
-Our purpose here is to exploit the consequences of replacing infinitely-specified
-quantum probabilities by finite number of intervals used in interval-valued
-probability measures~(IVPM); in particular, we show that a quantum
-IVPM may not be induced by a infinitely-precise state, but it might
-be more and more likely to be identified to a particular state when
-the measurement resources increase.
+\section{Statement of Motivation}
 
-Indeed, almost every description of quantum mechanics, quantum computation,
+It is widely believed that the Turing machine is equivalent to any
+reasonable computational models. Yet, for centuries, the mathematical
+formalization of physical processes has been founded on the infinitely
+precise real or complex numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}
+which might provide such processes more computational power. For example,
+almost every description of quantum mechanics, quantum computation,
 or quantum experiments refers to entities such as $\rme$, $\pi$,
 $\sqrt{2}$, etc (see, e.g., \cite{Redhead1987-REDINA,544199,Mermin2007}).
-From a computational perspective, such numbers do not exist in their
-entirety ``for free~\cite{Kent1999,CliftonKent2000}.'' For example,
-the state of the art algorithms for computing the $n$th binary digit
-of~$\pi$ require on the order of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
-operations~\cite{journals/moc/BaileyBP97}. In other words, simply
-referring to the $n$th digit of $\pi$ requires more and more resources
-as $n$ gets larger. Taking such resource bounds into consideration
-is what founded computer science as a discipline and is crucial for
-understanding the very nature of computation and, following Feynman~\cite{Feynman1982Simulating},
-Landauer~\cite{Landauer1996188}, and others, for understanding the
-very nature of physical processes.
+Whether these models based on real numbers faithfully describe the
+nature or just an approximation is still an open question. If they
+are faithful, how the nature store and compute these real numbers
+to produce our experimental results would be the next natural question.
+There are at least three possibilities:
+\begin{itemize}
+\item For any computable number~\cite{Turing_1937}, the nature only store
+the code of the Turing machine which computes the given number, and
+manipulate these codes directly during the computation~\cite{Ziegler2007,weihrauch2012computable}.
+\item The nature stores real numbers on infinitely long Turing machine tapes,
+and handle these numbers by a Turing machine~\cite{Ziegler2007,weihrauch2012computable}.
+In another word, the nature stores real numbers as a whole, but compute
+them piecewisely.
+\item The nature stores and computes real numbers as a whole~\cite{Ziegler2007,blum2012complexity}.
+\end{itemize}
+All these possibilities are not very desirable because they suggest
+the nature might have more computational power than a Turing machine.
+On one hand, if the nature only stores computable numbers by their
+Turing machine codes, the nature might be able to decide whether two
+Turing machines output exactly the same numbers, since this is used
+to decide whether an observable is degenerated or not. However, testing
+whether two Turing machines are output-equivalent is undecidable by
+Rice's theorem~\cite{Rice_1953,Ziegler2007,weihrauch2012computable},
+i.e., the nature has more computational power than a Turing machine.
+On the other hand, if the nature stores real numbers as a whole, any
+particular real number could serve as an oracle and give the nature
+more computational power than a Turing machine. For example, maybe
+the mass of the electron in some representation is the halting oracle
+for some representation of Turing machines. Then, we could solve the
+halting problem by just measuring the mass of the electron. This kind
+of possibility has been online discussed by Peter Shor and others~\cite{PhysicsStackExchange16889}.
 
-We have been revisiting quantum mechanics, quantum information, and
-quantum computation from this resource-aware perspective. Our initial
-results in that domain showed how subtle the issues can be~\cite{usat,geometry2013,DQT2014}:
-a straightforward replacement of the complex numbers by a finite field
-yields a variant of quantum mechanics in which computationally hard
-problems like UNIQUE-SAT (which decides whether a given Boolean formula
-is unsatisfiable or has exactly one satisfying assignment~\cite{Valiant198685,Papadimitriou1993,AroraBarak2009})
-can be deterministically solved in constant time. To eliminate such
-unrealistic theories requires delicate analysis of the structure of
-the Hilbert space, the process of observation, and the notion of probability
-teasing apart their reliance on the infinitely precise real numbers~\cite{geometry2013,DQT2014}.
+Since all possibilities that quantum theory is faithful are not very
+desirable, maybe every description of quantum theory is just an approximation.
+In this case, there is the other possibility:
+\begin{itemize}
+\item The real and complex numbers only exist in our model. The nature is
+essentially discrete, and could be simulated by a Turing machine.
+\end{itemize}
+We have followed this approach to study quantum theory over discrete
+finite fields~\cite{usat,geometry2013,DQT2014}. This yields a variant
+of quantum mechanics in which computationally hard problems like UNIQUE-SAT
+(which decides whether a given Boolean formula is unsatisfiable or
+has exactly one satisfying assignment~\cite{Valiant198685,Papadimitriou1993,AroraBarak2009})
+can be deterministically solved in constant time. We then delicate
+analysis of the structure of the Hilbert space, the process of observation,
+and the notion of probability by teasing apart their reliance on the
+infinitely precise real numbers~\cite{geometry2013,DQT2014}.
 
-In this paper, we shift focus from the infinitely-specified but not
-directly observable quantum states, to observable measurable properties
-of quantum systems and their probabilities. Furthermore, we insist
-that our theories of measurement and probability only refer to finitely
-communicable evidence within feasible computational bounds. It follows
-that states, observations, and probabilities all become ``fuzzy'',
-i.e., specified by intervals of confidence that can only increase
-in precision if the available resources increase proportionally. Our
-notion of ``fuzzy quantum mechanics'' is related to existing work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
-but, as will be explained in more detail, is distinguished by its
-unique computational character.
+\section{Proposed Question}
 
-We will begin by reviewing existing work that recasts classical probability
-spaces in a resource-aware setting and move to aim at recasting quantum
-probability and quantum measurement. In particular, we develop a measurement
-framework based on quantum IVPM. Surprisingly, we found a quantum
-IVPM which can not be induced by a state, while Shapley proved a classical
-convex IVPM can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
-and Gleason proved a infinitely-specified quantum probabilities measure
-can always be induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+In contrast to our previous works that assume the current quantum
+theory is just an approximation to the discrete reality, we now assume
+the nature really use real numbers. However, these real numbers could
+not be directly accessed by human who is bounded by finite resources.
+Therefore, even if the nature might have more computational power
+than a Turing machine, human might not be able to acquire and use
+the computational power more than a Turing machine.
+
+In order to model the bounded-resource human observers, we would like
+the theories of measurement and probability replaced by a subjective
+probability model, called the interval-valued probability. The question
+is how quantum mechanics would like with the interval-valued probability.
+
+In particular, based on conventional probability, Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
+suggests that idea to define a state as a density matrix~\cite{Varadarajan2008}.
+Since Gleason's theorem could not directly apply on interval-valued
+probability measures, we would like to ask: How a quantum state looks
+like with the interval-valued probability? When the number and precision
+of the intervals increase, would the quantum interval-valued probability
+measures converge to the quantum probability measure induced by the
+Born rule~\cite{Born1983,Mermin2007,Jaeger2007}?
+
+\section{Kick-off Talk}
+
+In the kick-off talk, we will begin by reviewing existing work that
+recasts classical probability spaces in a resource-aware setting and
+move to aim at recasting quantum probability and quantum measurement.
+In particular, we develop a measurement framework based on quantum
+interval-valued probability measures~(IVPM). Surprisingly, we found
+a quantum IVPM which can not be induced by a state, while Shapley
+proved a classical convex IVPM can always be induced by a classical
+``state''~\cite{Shapley1971,Grabisch2016}, and Gleason proved
+a infinitely-specified quantum probabilities measure can always be
+induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 Nevertheless, a quantum IVPM could still correspond to many possible
@@
 
-Since Gleason's theorem supports the idea of von Neumann to define
-a state as a density matrix~\cite{Varadarajan2008}, a density matrix
-might not be a adequate imprecise quantum state. Instead, a imprecise
-quantum state might be more like an interactive system suggested by
-Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
-which would interact differently with different clients. Furthermore,
-the validity the fundamental theorems of quantum mechanics followed
-up by Gleason's theorem, such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
-might need to be reassessed based on our imprecise measurement. Our
-research then might provide a new insight to the old debate among
-Meyer, Mermin, and others about  whether finite precision measurement
-would nullify the Kochen-Specker theorem or not~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Classical Probability}
+\subsection{Classical Probability}
 
 A \emph{probability space} specifies the necessary conditions for
-reasoning coherently about collections of uncertain
-events~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}.  We
-review the conventional presentation of probability spaces and then
-discuss the computational resources needed to estimate probabilities.
+reasoning coherently about collections of uncertain events~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}.
+We review the conventional presentation of probability spaces and
+then discuss the computational resources needed to estimate probabilities.
 
 %%%
-\subsection{Classical Probability Spaces}
+
+\subsubsection{Classical Probability Spaces}
 
 The conventional definition of a probability space builds upon the
-field of real numbers. In more detail, a probability space consists of
-a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
+field of real numbers. In more detail, a probability space consists
+of a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
 and a \emph{probability measure}~$\pmeas$ mapping events in $\events$
-to the real interval $[0,1]$. We will only consider \emph{finite} sets
-of events and restrict our attention to non-empty finite sets $\Omega$
-as the sample space. The space of events $\events$ includes every
-possible subset of $\Omega$: it is the
-powerset~$2^{\Omega}=\left\{ E ~\middle|~ E\subseteq\Omega\right\}
-$.
+to the real interval $[0,1]$. We will only consider \emph{finite}
+sets of events and restrict our attention to non-empty finite sets
+$\Omega$ as the sample space. The space of events $\events$ includes
+every possible subset of $\Omega$: it is the powerset~$2^{\Omega}=\left\{ E~\middle|~E\subseteq\Omega\right\} $.
 For future reference, we emphasize that events are the primary notion
 of interest and that the sample space is a convenient artifact that
-allows us to treat events as sets obeying the laws of Boolean
-algebra~\cite{Boole1948,Redhead1987-REDINA,Griffiths2003}.
+allows us to treat events as sets obeying the laws of Boolean algebra~\cite{Boole1948,Redhead1987-REDINA,Griffiths2003}.
 
 \begin{definition}[Probability Measure]\label{def:ClassicalProbabilitySpace}
-  Given the set of events $\events$, a \emph{probability measure} is a
-  function $\pmeas:\events\rightarrow[0,1]$ such that:
+Given the set of events $\events$, a \emph{probability measure} is
+a function $\pmeas:\events\rightarrow[0,1]$ such that: 
 \begin{itemize}
@@
 \item $\pmeas(\Omega)=1$, 
-\item for every event $E$,
-  $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$ where
-  $\Omega\backslash E$ is the complement event of $E$, and
-\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of
-  pairwise disjoint events,
-  $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$.
+\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
+where $\Omega\backslash E$ is the complement event of $E$, and 
+\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
+disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
 \end{itemize}
-\end{definition}
-\noindent There is some redundancy in the definition that will be useful when
-moving to quantum probability spaces.
+\end{definition} There is some redundancy in the definition that
+will be useful when moving to quantum probability spaces.
 
-\begin{example}[Two-coins experiment]\label{ex1} Consider an
-  experiment that tosses two coins. We have four possible outcomes
-  that constitute the sample space $\Omega=\{HH,HT,TH,TT\}$. There are
-  16 total events including the event $\{HH,HT\}$ that the first coin
-  lands heads up, the event $\{HT,TH\}$ that the two coins land on
-  opposite sides, and the event $\{HT,TH,TT\}$ that at least one coin
-  lands tails up. Here is a possible probability measure for these
+\noindent \begin{example}[Two-coins experiment]\label{ex1} Consider
+an experiment that tosses two coins. We have four possible outcomes
+that constitute the sample space $\Omega=\{HH,HT,TH,TT\}$. There
+are 16 total events including the event $\{HH,HT\}$ that the first
+coin lands heads up, the event $\{HT,TH\}$ that the two coins land
+on opposite sides, and the event $\{HT,TH,TT\}$ that at least one
+coin lands tails up. Here is a possible probability measure for these
 events: 
@@
 
-\noindent It is useful to think that this probability measure is
-completely determined by the ``reality'' of the two coins in question
-and their characteristics, in the sense that each pair of coins
-induces a measure, and each measure must correspond to some pair of
-coins. The measure above would be induced by two particular coins such
-that the first coin is twice as likely to land tails up than heads up
-and the second coin is double-headed. In a strict computational
-or experimental setting, one should question the reliance of the
-definition of probability space on the uncountable and
-uncomputable real
-interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
-This interval includes numbers like
-$0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether
-Turing machine $\mathit{TM}_{i}$ halts or not. Such numbers cannot be
-computed. This interval also includes numbers like $\frac{\pi}{4}$
-which can only be computed with increasingly large resources as the
-precision increases. Therefore, in a resource-aware computational or
-experimental setting, it is more appropriate to consider probability
-measures that map events to a set of elements computable with a fixed
-set of resources. We expand on this observation in the next section
-and then recall its formalization using interval-valued probability
-measures~\cite{Weichselberger2000,JamisonLodwick2004}.
+\noindent It is useful to think that this probability measure is completely
+determined by the ``reality'' of the two coins in question and their
+characteristics, in the sense that each pair of coins induces a measure,
+and each measure must correspond to some pair of coins. The measure
+above would be induced by two particular coins such that the first
+coin is twice as likely to land tails up than heads up and the second
+coin is double-headed. In a strict computational or experimental setting,
+one should question the reliance of the definition of probability
+space on the uncountable and uncomputable real interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
+This interval includes numbers like $0.h_{1}h_{2}h_{3}\ldots$ where
+$h_{i}$ is 1 or 0 depending on whether Turing machine $\mathit{TM}_{i}$
+halts or not. Such numbers cannot be computed. This interval also
+includes numbers like $\frac{\pi}{4}$ which can only be computed
+with increasingly large resources as the precision increases. Therefore,
+in a resource-aware computational or experimental setting, it is more
+appropriate to consider probability measures that map events to a
+set of elements computable with a fixed set of resources. We expand
+on this observation in the next section and then recall its formalization
+using interval-valued probability measures~\cite{Weichselberger2000,JamisonLodwick2004}.
 
 %%%%%
-\subsection{Measuring Probabilities: Buffon's Needle Problem\label{subsec:Measuring-Probabilities:-Buffon}}
 
-In the previous example, we assumed the probability~$\pmeas(E)$ of
-each event~$E$ is known a priori. In reality, although each event is
-assumed to have a probability, the exact value of $\pmeas(E)$ may not
-be known. According to the \emph{frequency interpretation of
-  probability} (which we will revisit when moving to the quantum
-case)~\cite{Venn1876,Hajek2012}, 
-to determine the probability of an event, we run $M$
-independent trials which gives us an approximation of the (assumed)
-``true'' or ``real'' probability. Let $x_{i}$ be 1 or 0 depending on
-whether the event~$E$ occurs in the $i$-th trial or not, then
-$\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
-the relative frequency~$\frac{1}{M}\sum_{i=1}^{M}x_{i}$ with the
-probability converging to one as $M$ goes to infinity, i.e.,
+\subsubsection{Measuring Probabilities: Buffon's Needle Problem\label{subsec:Measuring-Probabilities:-Buffon}}
+
+In the previous example, we assumed the probability~$\pmeas(E)$
+of each event~$E$ is known a priori. In reality, although each event
+is assumed to have a probability, the exact value of $\pmeas(E)$
+may not be known. According to the \emph{frequency interpretation
+of probability} (which we will revisit when moving to the quantum
+case)~\cite{Venn1876,Hajek2012}, to determine the probability of
+an event, we run $M$ independent trials which gives us an approximation
+of the (assumed) ``true'' or ``real'' probability. Let $x_{i}$
+be 1 or 0 depending on whether the event~$E$ occurs in the $i$-th
+trial or not, then $\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$
+by the relative frequency~$\frac{1}{M}\sum_{i=1}^{M}x_{i}$ with
+the probability converging to one as $M$ goes to infinity, i.e.,
 \[
-\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M} x_{i}\right|<\epsilon\right)=1\textrm{ .}
+\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M}x_{i}\right|<\epsilon\right)=1\textrm{ .}
 \]
@@
 $\ell$ onto a floor made of equally spaced parallel lines a distance
-$h$ apart, where $\ell<h$. It is a known fact that the probability of
-the needle crossing a line is
-$\frac{2\ell}{\pi
-  h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
+$h$ apart, where $\ell<h$. It is a known fact that the probability
+of the needle crossing a line is $\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
 Consider an experimental setup consisting of a collection of $M$
 identical needles of length $\ell$. We throw the $M$ needles one
-needle at a time, and observe the number $M_c$ of needles that cross a
-line, thus estimating the probability of a needle crossing a line to
-be $\frac{M_c}{M}$. In an actual experiment with $500$ needles and the
-ratio $\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$
-crossed a line so the relative frequency is $0.472$ whereas the
-idealized mathematical probability is $0.4774\ldots$.  In a larger
-experiment with $5000$ needles and the ratio
-$\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, the relative frequency was
-calculated to be $0.5064$ whereas the idealized mathematical
-probability is $0.5092\ldots$. We see that the observed probability
-approaches $\frac{2\ell}{\pi h}$ but only if \emph{larger and larger
-  resources} are expended. These resource considerations suggest that
-it is possible to replace the real interval $[0,1]$ with rational
-numbers up to a certain precision related to the particular experiment
-in question. There is clearly a connection between the number of
-needles and the achievable precision: in the hypothetical experiment
-with 3 needles, it is not sensible to retain 100 digits in the
-expansion of $\frac{2\ell}{\pi h}$.
+needle at a time, and observe the number $M_{c}$ of needles that
+cross a line, thus estimating the probability of a needle crossing
+a line to be $\frac{M_{c}}{M}$. In an actual experiment with $500$
+needles and the ratio $\frac{\ell}{h}=0.75$~\cite{Hall1873}, it
+was found that $236$ crossed a line so the relative frequency is
+$0.472$ whereas the idealized mathematical probability is $0.4774\ldots$.
+In a larger experiment with $5000$ needles and the ratio $\frac{\ell}{h}=0.8$~\cite{Uspensky1937},
+the relative frequency was calculated to be $0.5064$ whereas the
+idealized mathematical probability is $0.5092\ldots$. We see that
+the observed probability approaches $\frac{2\ell}{\pi h}$ but only
+if \emph{larger and larger resources} are expended. These resource
+considerations suggest that it is possible to replace the real interval
+$[0,1]$ with rational numbers up to a certain precision related to
+the particular experiment in question. There is clearly a connection
+between the number of needles and the achievable precision: in the
+hypothetical experiment with 3 needles, it is not sensible to retain
+100 digits in the expansion of $\frac{2\ell}{\pi h}$.
 
@@
 power in the experiment. We are assuming that we can always determine
-with certainty whether a needle is crossing a line. But ``lines'' on
-the the floor have thickness, their distance apart is not exactly $h$,
-and the needles' lengths are not all absolutely equal to $\ell$.
+with certainty whether a needle is crossing a line. But ``lines''
+on the the floor have thickness, their distance apart is not exactly
+$h$, and the needles' lengths are not all absolutely equal to $\ell$.
 These perturbations make the events ``fuzzy.'' Thus, in an experiment
 with limited resources, it is not possible to talk about the idealized
-event that exactly $M_c$ needles cross lines as this would require the
-most expensive needles built to the most precise accuracy, laser
-precision for drawing lines on the floor, and the most powerful
-microscopes to determine if a needle does cross a line. Instead we
-might talk about the event that $M_c-\delta$ needles evidently cross
-lines and $M_c+\delta'$ needles plausibly cross lines where $\delta$ and
-$\delta'$ are resource-dependent approximations. This fuzzy notion of
-events leads to probabilities being only calculable within intervals
-of confidence reflecting the certainty of events and their
-plausibility. This is indeed consistent with published experiments: in
-an experiment with $3204$ needles and the ratio
-$\frac{\ell}{h}=0.6$~\cite{DeMorgan1872}, $1213$ needles clearly
-crossed a line and $11$ needles were close enough to plausibly be
-considered as crossing the line: we would express the probability in
-this case as the interval
-$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we
-are certain that the event has probability at least
+event that exactly $M_{c}$ needles cross lines as this would require
+the most expensive needles built to the most precise accuracy, laser
+precision for drawing lines on the floor, and the most powerful microscopes
+to determine if a needle does cross a line. Instead we might talk
+about the event that $M_{c}-\delta$ needles evidently cross lines
+and $M_{c}+\delta'$ needles plausibly cross lines where $\delta$
+and $\delta'$ are resource-dependent approximations. This fuzzy notion
+of events leads to probabilities being only calculable within intervals
+of confidence reflecting the certainty of events and their plausibility.
+This is indeed consistent with published experiments: in an experiment
+with $3204$ needles and the ratio $\frac{\ell}{h}=0.6$~\cite{DeMorgan1872},
+$1213$ needles clearly crossed a line and $11$ needles were close
+enough to plausibly be considered as crossing the line: we would express
+the probability in this case as the interval $\left[\frac{1213}{3204},\frac{1224}{3204}\right]$
+expressing that we are certain that the event has probability at least
 $\frac{1213}{3204}$ but it is possible that it would have probability
@@
 %%%%%
-\subsection{Classical Interval-Valued Probability Measures}
 
-As motivated above, an event $E_{1}$ may have an interval of
-probability $[l_{1},r_{1}]$. Assume that another disjoint event
-$E_{2}$ has an interval of probability $[l_{2},r_{2}]$, what is the
-interval of probability for the event $E_{1}\cup E_{2}$? The answer is
-somewhat subtle: although it is possible to use the sum of the
-intervals $[l_{1}+l_{2},r_{1}+r_{2}]$ as the combined probability, one
-can find a much tighter interval if information \emph{against} the
-event (i.e., information about the complement event) is also taken
-into consideration. Formally, for a general event $E$ with probability
-$[l,r]$, the evidence that contradicts $E$ is evidence supporting the
-complement of $E$.  The complement of $E$ must therefore have
-probability $\left[1-r,1-l\right]$ which we abbreviate
-$\left[1,1\right]-\left[l,r\right]$.  Given a sample space~$\Omega$
-and its set of events~$\events$, a
-function~$\bar{\mu}:\events\rightarrow[0,1]$ is a classical
-interval-valued probability measure if and only if $\bar{\mu}$
-satisfies the following conditions~\cite{JamisonLodwick2004} where the
-last line uses $\subseteq$ to allow for tighter intervals that exploit
-the complement event:
+\subsubsection{Classical Interval-Valued Probability Measures}
+
+As motivated above, an event $E_{1}$ may have an interval of probability
+$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
+an interval of probability $[l_{2},r_{2}]$, what is the interval
+of probability for the event $E_{1}\cup E_{2}$? The answer is somewhat
+subtle: although it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
+as the combined probability, one can find a much tighter interval
+if information \emph{against} the event (i.e., information about the
+complement event) is also taken into consideration. Formally, for
+a general event $E$ with probability $[l,r]$, the evidence that
+contradicts $E$ is evidence supporting the complement of $E$. The
+complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
+which we abbreviate $\left[1,1\right]-\left[l,r\right]$. Given a
+sample space~$\Omega$ and its set of events~$\events$, a function~$\bar{\mu}:\events\rightarrow[0,1]$
+is a classical interval-valued probability measure if and only if
+$\bar{\mu}$ satisfies the following conditions~\cite{JamisonLodwick2004}
+where the last line uses $\subseteq$ to allow for tighter intervals
+that exploit the complement event: 
 \begin{itemize}
@@
 \item $\bar{\mu}(\Omega)=[1,1]$. 
-\item For any event $E$,
-  $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$
-\item For a collection $\left\{ E_{i}\right\} _{i=1}^{M}$ of pairwise
-  disjoint events, we have
-  $\bar{\mu}\left(\bigcup_{i=1}^{M}E_{i}\right)\subseteq\sum_{i=1}^{M}\bar{\mu}\left(E_{i}\right)$.
+\item For any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$ 
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{M}$ of pairwise disjoint
+events, we have $\bar{\mu}\left(\bigcup_{i=1}^{M}E_{i}\right)\subseteq\sum_{i=1}^{M}\bar{\mu}\left(E_{i}\right)$. 
 \end{itemize}
-
-\begin{example}[Two-coin experiment with interval probability]
-\label{ex3} We split the unit interval $[0,1]$ in the following
-four closed sub-intervals: $[0,0]$ which we call \imposs, $[0,\frac{1}{2}]$
-which we call \unlikely, $[\frac{1}{2},1]$ which we call \likely,
-and $[1,1]$ which we call \necess. Using these new values, we can
-modify the probability measure of Ex.~\ref{ex1} by mapping each
-numeric value to the smallest sub-interval containing it to get the
-following: 
+\begin{example}[Two-coin experiment with interval probability]\label{ex3}
+We split the unit interval $[0,1]$ in the following four closed sub-intervals:
+$[0,0]$ which we call \imposs, $[0,\frac{1}{2}]$ which we call
+\unlikely, $[\frac{1}{2},1]$ which we call \likely, and $[1,1]$
+which we call \necess. Using these new values, we can modify the
+probability measure of Ex.~\ref{ex1} by mapping each numeric value
+to the smallest sub-interval containing it to get the following: 
 \[
@@
 \begin{eqnarray*}
-\bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})
-&=& \imposs+\unlikely+\imposs+\likely\\
-&=& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]\\
-&=& \left[\frac{1}{2},\frac{3}{2}\right]
+\bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\}) & = & \imposs+\unlikely+\imposs+\likely\\
+ & = & \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]\\
+ & = & \left[\frac{1}{2},\frac{3}{2}\right]
 \end{eqnarray*}
@@
 allows us to get an estimate for the combined event from each of its
-constituents and then gather more evidence knowing the aggregate
-event.
+constituents and then gather more evidence knowing the aggregate event.
 \end{example}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum Probability}
 
-The mathematical framework of classical probability above assumes that
-there exists a predetermined set of events that are independent of the
-particular experiment --- classical physics is
-non-contextual~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}. 
-However, even in classical situations, the structure
-of the event space is often only partially known and the precise
-dependence of two events on each other cannot, a priori, be determined
-with certainty. In the quantum framework, this partial knowledge is
-compounded by the fact that there exist non-commuting events which
-cannot happen simultaneously. To accommodate these more complex
-situations, conventional approaches to quantum probability abandon the
-sample space~$\Omega$ and reason directly about events which are
-generalized from plain sets to projection operators. A quantum
-probability space therefore consists of just two components: a set of
-events $\qevents$ often formalized as projection operators and a
-probability measure $\mu:\qevents\rightarrow[0,1]$ formalized using
-the Born rule~\cite{Born1983,Mermin2007,Jaeger2007}.
+\subsection{Quantum Probability}
+
+The mathematical framework of classical probability above assumes
+that there exists a predetermined set of events that are independent
+of the particular experiment — classical physics is non-contextual~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
+However, even in classical situations, the structure of the event
+space is often only partially known and the precise dependence of
+two events on each other cannot, a priori, be determined with certainty.
+In the quantum framework, this partial knowledge is compounded by
+the fact that there exist non-commuting events which cannot happen
+simultaneously. To accommodate these more complex situations, conventional
+approaches to quantum probability abandon the sample space~$\Omega$
+and reason directly about events which are generalized from plain
+sets to projection operators. A quantum probability space therefore
+consists of just two components: a set of events $\qevents$ often
+formalized as projection operators and a probability measure $\mu:\qevents\rightarrow[0,1]$
+formalized using the Born rule~\cite{Born1983,Mermin2007,Jaeger2007}.
 
 %%%%%
-\subsection{Quantum Events}
 
-\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
-  \label{def:Projection} Given a Hilbert space $\Hilb$, an event (an
-  experimental proposition~\cite{BirkhoffVonNeumann1936}, a
-  question~\cite{10.2307/2308516,Abramsky2012},
-  or an elementary quantum test~\cite{peres1995quantum}) is represented
-  as a (self-adjoint or orthogonal~\cite {Griffiths2003,Maassen2010})
-  projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace
-  of $\Hilb$. The following define projections and list some of their properties:
+\subsubsection{Quantum Events}
+
+\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]\label{def:Projection}
+Given a Hilbert space $\Hilb$, an event (an experimental proposition~\cite{BirkhoffVonNeumann1936},
+a question~\cite{10.2307/2308516,Abramsky2012}, or an elementary
+quantum test~\cite{peres1995quantum}) is represented as a (self-adjoint
+or orthogonal~\cite{Griffiths2003,Maassen2010}) projection operator
+$P:\Hilb\rightarrow\Hilb$ onto a linear subspace of $\Hilb$. The
+following define projections and list some of their properties: 
 \begin{itemize}
@@
 operator. 
-\item Projection operators $P_{0}$ and $P_{1}$ are \emph{orthogonal}
-  if $P_{0}P_{1}=P_{1}P_{0}=\mathbb{0}$. The sum of two projection
-  operators~$P_{0}+P_{1}$ is also a projection operator if and only if
-  they are orthogonal.
-\item Conversely, every projection~$P$ can be expressed as
-  $\sum_{j=1}^{N}\proj{\psi_{j}}$, where $P$ actually projects onto
-  the linear subspace with orthonormal
+\item Projection operators $P_{0}$ and $P_{1}$ are \emph{orthogonal} if
+$P_{0}P_{1}=P_{1}P_{0}=\mathbb{0}$. The sum of two projection operators~$P_{0}+P_{1}$
+is also a projection operator if and only if they are orthogonal. 
+\item Conversely, every projection~$P$ can be expressed as $\sum_{j=1}^{N}\proj{\psi_{j}}$,
+where $P$ actually projects onto the linear subspace with orthonormal
 basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{N}$. 
-\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is
-  called an \emph{ideal measurement} if it is a partition of the
-  identity, i.e., $\sum_{i=1}^{N}P_{i}=\mathbb{1}$~\cite{Swart2013}.
-  In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
-  be mutually orthogonal~\cite{Griffiths2003,Halmos1957}, and $N$ must be less
+\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is called
+an \emph{ideal measurement} if it is a partition of the identity,
+i.e., $\sum_{i=1}^{N}P_{i}=\mathbb{1}$~\cite{Swart2013}. In this
+case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must be mutually
+orthogonal~\cite{Griffiths2003,Halmos1957}, and $N$ must be less
 or equal to the dimension of the Hilbert space. 
-\item If $P$ is a projection operator, then $\mathbb{1}-P$ is also a
-  projection operator, called its \emph{complement}. It is orthogonal to
-  $P$, and corresponds to the complement event~$\Omega\backslash E$ in
+\item If $P$ is a projection operator, then $\mathbb{1}-P$ is also a projection
+operator, called its \emph{complement}. It is orthogonal to $P$,
+and corresponds to the complement event~$\Omega\backslash E$ in
 classical probability~\cite{Griffiths2003}. 
@@
 intersection between events~\cite{peres1995quantum,Griffiths2003}. 
-\item For two commuting projection operators $P_{0}$ and $P_{1}$,
-  their \emph{disjunction}~$P_{0}\vee P_{1}$ is defined to be
-  $P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
+\item For two commuting projection operators $P_{0}$ and $P_{1}$, their
+\emph{disjunction}~$P_{0}\vee P_{1}$ is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}. 
 \end{itemize}
@@
 
-\begin{example}[One-qubit quantum probability space] Consider a
-  one-qubit Hilbert space with each event interpreted as a possible
-  post-measurement state~\cite{peres1995quantum,Mermin2007,Jaeger2007}. 
-  For example, the event $\proj{0}$ indicates
-  that the post-measurement state will be $\ket{0}$; the probability
-  of such an event depends on the current state; the event $\proj{1}$
-  indicates that the post-measurement state will be $\ket{1}$; the
-  event $\proj{\ps}$ where
-  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$ indicates that the
-  post-measurement state will be $\ket{\ps}$; the event
-  $\mathbb{1}=\proj{0}+\proj{1}$ indicates that the post-measurement
-  state will be a linear combination of $\ket{0}$ and $\ket{1}$ and is
-  clearly certain; finally the empty event $\mathbb{0}$ states that
-  the post-measurement state will be the empty state and is
-  impossible. As in the classical case, a probability measure is a
-  function that maps events to $[0,1]$. Here is a partial
-  specification of a possible probability measure that would be
-  induced by a system whose current state is $\ket{0}$,
-  $\mu\left(\mathbb{0}\right)=0$, $\mu\left(\mathbb{1}\right)=1$,
-  $\mu\left(\proj{0}\right)=1$, $\mu\left(\proj{1}\right)=0$,
-  $\mu\left(\proj{\ps}\right)=1/2$, \ldots. Note that, similarly to
-  the classical case, the probability of $\mathbb{1}$ is 1 and the
-  probability of collections of orthogonal events (e.g.,
-  $\proj{0}+\proj{1}$) is the sum of the individual probabilities.  A
-  collection of non-orthogonal events (e.g., $\proj{0}$ and
-  $\proj{\ps}$) is however not even a valid event. In the classical
-  example, we argued that each probability measure is uniquely
-  determined by two actual coins. A similar (but much more subtle)
-  argument is valid also in the quantum case. By postulates of quantum
-  mechanics and Gleason's theorem, it turns out that for large enough
-  quantum systems, each probability measure is uniquely determined by
-  an actual quantum state as discussed next.
-\end{example}
+\begin{example}[One-qubit quantum probability space]Consider a one-qubit
+Hilbert space with each event interpreted as a possible post-measurement
+state~\cite{peres1995quantum,Mermin2007,Jaeger2007}. For example,
+the event $\proj{0}$ indicates that the post-measurement state will
+be $\ket{0}$; the probability of such an event depends on the current
+state; the event $\proj{1}$ indicates that the post-measurement state
+will be $\ket{1}$; the event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
+indicates that the post-measurement state will be $\ket{\ps}$; the
+event $\mathbb{1}=\proj{0}+\proj{1}$ indicates that the post-measurement
+state will be a linear combination of $\ket{0}$ and $\ket{1}$ and
+is clearly certain; finally the empty event $\mathbb{0}$ states that
+the post-measurement state will be the empty state and is impossible.
+As in the classical case, a probability measure is a function that
+maps events to $[0,1]$. Here is a partial specification of a possible
+probability measure that would be induced by a system whose current
+state is $\ket{0}$, $\mu\left(\mathbb{0}\right)=0$, $\mu\left(\mathbb{1}\right)=1$,
+$\mu\left(\proj{0}\right)=1$, $\mu\left(\proj{1}\right)=0$, $\mu\left(\proj{\ps}\right)=1/2$,
+\ldots{}. Note that, similarly to the classical case, the probability
+of $\mathbb{1}$ is 1 and the probability of collections of orthogonal
+events (e.g., $\proj{0}+\proj{1}$) is the sum of the individual probabilities.
+A collection of non-orthogonal events (e.g., $\proj{0}$ and $\proj{\ps}$)
+is however not even a valid event. In the classical example, we argued
+that each probability measure is uniquely determined by two actual
+coins. A similar (but much more subtle) argument is valid also in
+the quantum case. By postulates of quantum mechanics and Gleason's
+theorem, it turns out that for large enough quantum systems, each
+probability measure is uniquely determined by an actual quantum state
+as discussed next. \end{example}
 
 %%%%%
-\subsection{Quantum Probability Measures}
 
-Given our setup, the definition of a quantum probability measure is a
-small variation on the classical definition.
+\subsubsection{Quantum Probability Measures}
+
+Given our setup, the definition of a quantum probability measure is
+a small variation on the classical definition.
 
@@
 
-\noindent A quantum probability measure can be easily constructed if
-one knows the current state of the quantum system by using the Born
-rule.  Specifically, for each
-pure normalized quantum state $\ket{\phi}$, the Born rule induces a
-probability measure $\mu_{\phi}^{B}$ defined as
-$\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}$. The situation generalizes to
-mixed states $\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
-$\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born rule
-induces a probability measure $\mu_{\rho}^{B}$ defined
-as
-$\mu_{\rho}^{B}\left(P\right) = \Tr\left(\rho P\right) =
-\sum_{j=1}^{N}
-q_{j}\mu_{\phi_{j}}^{B}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
+\noindent A quantum probability measure can be easily constructed
+if one knows the current state of the quantum system by using the
+Born rule. Specifically, for each pure normalized quantum state $\ket{\phi}$,
+the Born rule induces a probability measure $\mu_{\phi}^{B}$ defined
+as $\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}$. The situation generalizes
+to mixed states $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
+$\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born rule induces
+a probability measure $\mu_{\rho}^{B}$ defined as $\mu_{\rho}^{B}\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}^{B}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
 Conversely every probability measure must be of this form.
 
-\begin{thm}[Gleason's
-  theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
+\begin{thm}[Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
 a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
 measure~$\mu:\events\rightarrow[0,1]$, there exists a unique mixed
-state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.
-\end{thm}
+state~$\rho$ such that $\mu=\mu_{\rho}^{B}$. \end{thm}
 
 %%%%%
-\subsection{Measuring Quantum Probabilities}
+
+\subsubsection{Measuring Quantum Probabilities}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum Interval-valued Probability Measures}
 
-This is the most developed part of our current investigation and is
-presented in greater detail than the other proposed activities. It
-relies on current unpublished results. As argued in the previous
-sections, given fixed finite resources, it is only possible to
-estimate the quantum probabilities within an interval of
-confidence. It is therefore natural to propose the notion of a
-``quantum interval-valued probability measure'' that combines the
-definitions of conventional quantum probability measures with
+\subsection{Quantum Interval-valued Probability Measures}
+
+As argued in the previous sections, given fixed finite resources,
+it is only possible to estimate the quantum probabilities within an
+interval of confidence. It is therefore natural to propose the notion
+of a ``quantum interval-valued probability measure'' that combines
+the definitions of conventional quantum probability measures with
 classical interval-probabilities.
@@
 \begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
-  Given a Hilbert space $\Hilb$ with quantum events
-  (projections)~$\events$, and a collection of
-  intervals~$\mathscr{I}$, a \emph{quantum
-    $\mathscr{I}$-interval-valued probability measure} is a
-  function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ such that:
+Given a Hilbert space $\Hilb$ with quantum events (projections)~$\events$,
+and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
+probability measure} is a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that: 
 \begin{itemize}
@@
 \item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
-\item For any projection $P$,
-  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
-\item For a set of mutually orthogonal projections
-  $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
-  $\bar{\mu}\left(\sum_{i=1}^{N}
-    P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
+\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$. 
 \end{itemize}
@@
 
-\noindent It is easy to establish that quantum interval-valued
-probability measures generalize conventional quantum probability
-measures. In particular, any quantum probability measure can be recast
-as an interval-valued measure using the three intervals
-$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
-where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
-\necess~as before, and \emph{$\left[0,1\right]$} is called
-\unknown~because it provides no information. Given a quantum
+\noindent It is easy to establish that quantum interval-valued probability
+measures generalize conventional quantum probability measures. In
+particular, any quantum probability measure can be recast as an interval-valued
+measure using the three intervals $\left[0,0\right]$, $\left[1,1\right]$
+and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$ and $\left[1,1\right]$
+are called \imposs~and \necess~as before, and \emph{$\left[0,1\right]$}
+is called \unknown~because it provides no information. Given a quantum
 probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
-define a quantum interval-valued probability
-measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ by
-$\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where
-$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
+define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is defined by 
 \[
@@
 we can ask: what can we deduce about the state of a quantum system
-given a quantum interval-valued probability measure, i.e., given
-observations done with finite resources. In the case the intervals are
-infinitely precise the question reduces to Gleason's theorem which
-states that the state of the quantum system is uniquely determined by
-the probability measure. But surely the less resources are available,
-the less precise the intervals, and the less we expect to know about
-the state of the system. To formally state and answer this question we
-begin with defining the \emph{core} and \emph{convexity} of a
-probability measure as follows.
+given a quantum interval-valued probability measure, i.e., given observations
+done with finite resources. In the case the intervals are infinitely
+precise the question reduces to Gleason's theorem which states that
+the state of the quantum system is uniquely determined by the probability
+measure. But surely the less resources are available, the less precise
+the intervals, and the less we expect to know about the state of the
+system. To formally state and answer this question we begin with defining
+the \emph{core} and \emph{convexity} of a probability measure as follows.
 
-\begin{definition}
-  Given a quantum interval-valued probability
-  measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
+\begin{definition} Given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$: 
 \begin{itemize}
-\item A \emph{core} of $\bar{\mu}$ is the set
-  $\mathrm{core}\left(\bar{\mu}\right)=\left\{
-    \pmeas:\events\rightarrow[0,1] ~\middle|~ \forall
-    E\in\events.~\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\}$.
-\item $\bar{\mu}$ is called convex if
-  $\bar{\mu}\left(P_{0}\vee
-    P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \pmeas:\events\rightarrow[0,1]~\middle|~\forall E\in\events.~\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $.
+\item $\bar{\mu}$ is called convex if $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
 for all commuting $P_{0},P_{1}\in\events$. 
@@
 \noindent The core of an interval-valued probability measure is the
-set of real-valued infinitely-precise probability measures it
-approximates. An interval-valued probability measure is convex if
-whenever certain intervals exist then combinations of these intervals
-must also exist, guaranteeing we can add and manipulate probabilities
-coherently. In the classical world, every convex measure has a
-non-empty core, which means that the interval-valued probability
-measure must approximate at least one infinitely-precise measure.
+set of real-valued infinitely-precise probability measures it approximates.
+An interval-valued probability measure is convex if whenever certain
+intervals exist then combinations of these intervals must also exist,
+guaranteeing we can add and manipulate probabilities coherently. In
+the classical world, every convex measure has a non-empty core, which
+means that the interval-valued probability measure must approximate
+at least one infinitely-precise measure.
 
-\begin{thm}[Shapley~\cite{Shapley1971,,Grabisch2016}]\label{thm:Shapley}
+\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}
 Every (classical) convex interval-valued probability measure has a
-  non-empty core.
-\end{thm}
+non-empty core. \end{thm}
 
@@
 with limited resources and poor precision may not uniquely identify
-the true state of the system, there is always at least one system that
-is consistent with the measurements. Surprisingly, we discovered a
-counterexample to this statement in the quantum case, i.e., we
-constructed the following convex quantum interval-valued probability
-measure with an empty core.
+the true state of the system, there is always at least one system
+that is consistent with the measurements. Surprisingly, we discovered
+a counterexample to this statement in the quantum case, i.e., we constructed
+the following convex quantum interval-valued probability measure with
+an empty core.
 
-\begin{example}[Three-dimensional quantum three-interval-valued 
-  probability measure]\label{ex:three-dimensional-three-value} Given
-  a three dimensional Hilbert space with an orthonormal basis
-  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
-    $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
-  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
-  $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$, and
+\begin{example}[Three-dimensional quantum three-interval-valued probability measure]\label{ex:three-dimensional-three-value}
+Given a three dimensional Hilbert space with an orthonormal basis
+$\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
+$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$,
+and 
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})
-  &=& \imposs\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})
-  &=& \necess \\
-\bar{\mu}(P) 
-  &=& \unknown\quad\textrm{otherwise}
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\\
+\bar{\mu}(P) & = & \unknown\quad\textrm{otherwise}
 \end{eqnarray*}
 It is straightforward to verify that $\bar{\mu}$ is a convex quantum
-interval-valued probability measure. Now assume there exists a
-real-valued quantum probability measure $\mu$ such that
-$\mu(P)\in\bar{\mu}(P)$ for every event (projection)~$P$. We derive a
-contradiction as follows. Suppose $\mu(P)\in\bar{\mu}(P)$ then we must
-have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$. By Gleason's
-theorem, there is a mixed
-state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$ such that
-$\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$, where
-$\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$.  However, no pure
-state~$\ket{\phi}$ can satisfy
-$\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
+interval-valued probability measure. Now assume there exists a real-valued
+quantum probability measure $\mu$ such that $\mu(P)\in\bar{\mu}(P)$
+for every event (projection)~$P$. We derive a contradiction as follows.
+Suppose $\mu(P)\in\bar{\mu}(P)$ then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
+By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
+such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
+can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
 \end{example}
@@
 \begin{figure}
-\begin{center}
-\includegraphics[scale=0.38]{proposal/measure4.pdf}
-\end{center}
-\caption{\label{fig:three-dimensional-4-value}This figure illustrates
-  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
-  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
+\begin{centering}
+\includegraphics[scale=0.38]{../proposal/measure4} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-4-value}This figure illustrates cases
+1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted in
+$\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
 and $\ket{\ps}$ respectively. All possible real vectors of the subspaces
-  $\ket{0_{\theta,\gamma}^{\perp}}$ and
-  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
-  circles, respectively. Within the circles, a dotted
-  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
-  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
-  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
-  green solid vectors are normalized
-  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
-  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
-  $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
+$\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
+are drawn in the red and green circles, respectively. Within the circles,
+a dotted vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
+otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
+a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
+and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
+and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively,
+where $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
 \end{figure}
 
-Looking closely at the example above, we might think that the
-probability measure $\bar{\mu}$ is induced by the state $\ket{2}$
-because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, or we
-might think it is induced by the state $\ket{1}$ because
-$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, or yet we might
-think it is induced by the mixed state $\frac{\mathbb{1}}{3}$ because
-$\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$. Each of these
-possibilities is compatible with some but not all of the
-observations. All is not lost however: if the observations are made
-more precise, we conjecture that some of the inconsistencies
+Looking closely at the example above, we might think that the probability
+measure $\bar{\mu}$ is induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
+or we might think it is induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
+or yet we might think it is induced by the mixed state $\frac{\mathbb{1}}{3}$
+because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.
+Each of these possibilities is compatible with some but not all of
+the observations. All is not lost however: if the observations are
+made more precise, we conjecture that some of the inconsistencies
 disappear. A partial proof of this conjecture is the following example
@@
 
-\begin{example}[Three-dimensional quantum four-interval-valued 
-  probability measure]\label{ex:three-dimensional-4-value}
+\begin{example}[Three-dimensional quantum four-interval-valued probability measure]\label{ex:three-dimensional-4-value}
 Given a three dimensional Hilbert space with an orthonormal basis
-  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
-  }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and
-  $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$. The definition of
-  $\bar{\mu}$ below refers to Fig.~\ref{fig:three-dimensional-4-value}
+$\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let \emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$.
+The definition of $\bar{\mu}$ below refers to Fig.~\ref{fig:three-dimensional-4-value}
 which plots the 1-dimensional projectors: 
@@
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) 
-  &=& \imposs \\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) 
-  &=& \necess
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) & = & \necess
 \end{eqnarray*}
-where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green dotted
-vectors, respectively.
-\item The red and green circles are are the states orthogonal to
-  $\ket{0}$ and $\ket{\ps}$, respectively, and can be parametrized as
-  $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
-  and
-  $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
+where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green
+dotted vectors, respectively. 
+\item The red and green circles are are the states orthogonal to $\ket{0}$
+and $\ket{\ps}$, respectively, and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
+and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
 where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
-  half of those states need special treatment, i.e., whenever
-  $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define
+half of those states need special treatment, i.e., whenever $0\le\theta<\frac{\pi}{2}$
+and $0\le\gamma<\pi$, we define 
 \begin{eqnarray*}
-\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)
-  &=& \likely \\
-\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right)=
-  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right) 
-  &=& \unlikely
+\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely\\
+\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely
 \end{eqnarray*}
@@
 quantum interval-valued probability measure. Although we have not
-verified that $\bar{\mu}$ is convex, the following argument
-establishes that is has an empty core. Assume there is a real-valued
-probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for
-all $P\in\events$. Because
-$\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$ and
-$\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$, we must
-have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$ so that
-$\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However,
+verified that $\bar{\mu}$ is convex, the following argument establishes
+that is has an empty core. Assume there is a real-valued probability
+measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$.
+Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
+and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
+we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
+so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
 \[
@@
 \]
-This measure however is ``better'' than the previous one in the sense
-that it might only be induced by $\ket{2}$ or the density matrix
-$\frac{\mathbb{1}}{3}$, but not by
-$\ket{1}$. 
-\end{example}
+This measure however is ``better'' than the previous one in the
+sense that it might only be induced by $\ket{2}$ or the density matrix
+$\frac{\mathbb{1}}{3}$, but not by $\ket{1}$. \end{example}
 
@@
 measure will be closer and closer to the Born rule. In the limit case,
-$\mathscr{I}=\left\{ \left\{ a\right\}
-  ~\middle|~a\in\left[0,1\right]\right\}$
+$\mathscr{I}=\left\{ \left\{ a\right\} ~\middle|~a\in\left[0,1\right]\right\} $
 we do indeed recover the conventional Gleason's theorem and the Born
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion and Discussion}
+\section{About Myself}
 
-If we insist that probabilities cannot be computed to infinite precision
-and are bound to be approximations represented by intervals of confidence,
-then quantum states themselves can only be discussed within intervals
-of confidence. Despite the fact that classically a IVPM could always
-correspond to a real-valued probability measure, we found that there
-may be no ``real'' infinitely-precise quantum state approximated
-by a quantum IVPM as a whole. However, if a quantum IVPM is decomposed
-into pieces, each piece might still be induced by a quantum state.
-Moreover, our examples and Gleason's theorem summarized in table~\ref{table_long}
-suggests that as the measurement resources increase, an entire quantum
-IVPM could more and more likely be identified to a particular state.
-\begin{table}[ht]
-\center{%
-\begin{tabular}{c|cccc}
-Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
-\hline 
-Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
-$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
-Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
-Count of states correspond to pieces of $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
-\hline 
-How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
-\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
-measures}
-\label{table_long}
-\end{table}
-Additional work is in progress on the following research questions:
-\begin{description}
-\item [{Research Question.}] Confirm that there is always a quantum IVPM
-with an empty-core if the length of the intervals is bigger than zero. 
-\item [{Research Question.}] Find a general method to determine how a
-quantum IVPM is close to the Born rule. 
-\item [{Research Question.}] Confirm that as the number and precision
-of the intervals increase the quantum IVPM converges to the measure
-induced by the Born rule. 
-\item [{Research Question.}] Investigate the status of the theorems of
-Bell and Kochen-Specker for quantum IVPM.
-\end{description}
-Although we discussed how a quantum IVPM could be induced from a real
-quantum state, our investigation leaves an open question of whether
-there exists a ``real'' entity that exists independently of measurements
-and probabilities. The possibility of no ``real'' underlying state
-is consistent with the elegantly recent work on Quantum Bayesianism
-or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which suggests
-that the quantum state is more like an interactive system in computer
-science parlance. In another word, the quantum state is subjective:
-each observer has a different view of the quantum system that is consistent
-with their previous observations and that allows that observer, independently
-of other observers, to assign beliefs (i.e., probabilities) to possible
-future interactions.
+\subsection{Occupation }
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage{}%
+PhD Student
+
+\subsection{Main area of work}
+
+Quantum Mechanics and Computing over Finite Fields, Quantum Interval-valued
+Probability
+
+\subsection{Dietary requirements or allergies}
+
+I don’t eat shrimp.
+
+\subsection{Whether you would like to apply for funding?}
+
+I would like to apply for funding, but I haven’t been to Europe before…
+So I don't know the specific amount I need…
+
 \begin{comment}
  \bibliographystyle{plain}
-\bibliography{proposal/prop}
+\bibliography{../proposal/prop}
 
@@
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-01-11 Rethinking Foundations of Physics 2017/application.tex
have fun Yu-Tsung

@@
 %\addbibresource{../proposal/prop.bib}
-\addbibresource{C:/Users/Yu-Tsung/workspace/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/proposal/prop.bib}
+%%\addbibresource{C:/Users/Yu-Tsung/workspace/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/proposal/prop.bib}
+%% \addbibresource{"../proposal/prop.bib"}
+\addbibresource{prop.bib}
 \ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
@@
 
-It is widely believed that the Turing machine is equivalent to any
-reasonable computational models. Yet, for centuries, the mathematical
-formalization of physical processes has been founded on the infinitely
-precise real or complex numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}
-which might provide such processes more computational power. For example,
-almost every description of quantum mechanics, quantum computation,
-or quantum experiments refers to entities such as $\rme$, $\pi$,
-$\sqrt{2}$, etc (see, e.g., \cite{Redhead1987-REDINA,544199,Mermin2007}).
-Whether these models based on real numbers faithfully describe the
-nature or just an approximation is still an open question. If they
-are faithful, how the nature store and compute these real numbers
-to produce our experimental results would be the next natural question.
-There are at least three possibilities:
+Physical processes are ultimately bounded in space, time, energy, and
+other resources. Yet, for centuries, the mathematical formalization of
+such processes has been founded on the infinitely precise real or
+complex numbers. Indeed, physics textbooks casually refer to entities
+such as $e$, $\pi$, $\sqrt{2}$, etc. From a computational perspective,
+such numbers do not exist in their entirety ``for free.''  For
+example, the state of the art algorithms for computing the $n$th
+binary digit of~$\pi$ require on the order of $O(n\log^{O(1)}(n))$
+operations~\cite{journals/moc/BaileyBP97}. In other words, simply
+referring to the $n$th digit of $\pi$ requires more and more resources
+as $n$ gets larger. Taking such resource bounds into consideration is
+what founded computer science as a discipline and is crucial for
+understanding the very nature of computation and, following
+Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
+and others, for understanding the very nature of physical processes.
+
+\begin{quote}
+  We therefore believe that the foundations of physics must be
+  revisited from a computational perspective that only allows
+  finitely-communicable evidence \emph{and} accounts for the resources
+  needed to calculate, store, and communicate such evidence.
+\end{quote}
+
+\noindent This marriage of quantum mechanics and computer science first
+envisioned and popularized by Feynman has created an awkward, but
+opportune, moment. The embarrassing dilemma was concisely described by
+Aaronson as follows~\cite{AaronsonArkhipov2011,BFRDARW2013}.  Consider
+the following three statements:
+\begin{enumerate}
+\item[(A)] Textbook quantum mechanics is correct.
+\item[(B)] There does not exist an efficient classical factoring
+  algorithm.
+\item[(C)] The extended Church-Turing thesis --- that probabilistic
+  Turing machines can efficiently simulate any physically realizable
+  model of computation --- is
+  correct~\cite{BernsteinVazirani1997,Kaye2007}.
+\end{enumerate}
+There is overwhelming evidence to support each of these
+statements. The theoretical framework of quantum mechanics (A) has
+withstood decades of experimental confirmation. Entire industries are
+founded on the assumption (B) that algorithms like RSA are secure and
+they also have withstood years of attempted
+attacks~\cite{boneh1999twenty,wiki:RSAFactoring}. Finally the entire
+field of complexity theory in computer science which has also
+withstood years of field testing rests, in essence, on assumption
+(C)~\cite{Aaronson2005,Piccinini2015}.  And yet at least one of these
+three statements \emph{must be false}! Indeed if textbook quantum
+mechanics is false we concede (A). If it is correct Shor's efficient
+factoring algorithm is realizable. If there is a corresponding
+efficient classical factoring algorithm then we concede (B). If not
+then we concede~(C).
+
+It is unlikely that there will be a simple a resolution to this
+awkward situation. It is more likely that the resolution will emerge
+from deep and careful analyses of the foundations of each field. As
+the world-renowned logician Girard states, the foundations of physics
+and the foundations of logic and computation appear strongly
+correlated:
+\begin{quote}
+  In other terms, what is so good in logic that quantum physics should
+  obey? Can't we imagine that our conceptions about logic are wrong,
+  so wrong that they are unable to cope with the quantum miracle?
+  [\ldots] Instead of teaching logic to nature, it is more reasonable
+  to learn from her. Instead of interpreting quantum into logic, we
+  shall interpret logic into quantum~\cite{MSC:1444836}.
+\end{quote}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Proposed Question}
+
+The meaning of quantum probability
+
+The reality of the quantum state
+
+--- next section
+
+The meaning of quantum probability: probability is approximate;
+intervals; Born; no state when approximation is bad.
+
+quantum state: Bayesian perspective; probability is subjective; hence
+state is subjective; given previous results that show that state does
+not exist when you have poor approximations; ?
+
+In contrast to our previous works that assume the current quantum
+theory is just an approximation to the discrete reality, we now assume
+the nature really use real numbers. However, these real numbers could
+not be directly accessed by human who is bounded by finite resources.
+Therefore, even if the nature might have more computational power
+than a Turing machine, human might not be able to acquire and use
+the computational power more than a Turing machine.
+
+In order to model the bounded-resource human observers, we would like
+the theories of measurement and probability replaced by a subjective
+probability model, called the interval-valued probability. The question
+is how quantum mechanics would like with the interval-valued probability.
+
+In particular, based on conventional probability, Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
+suggests that idea to define a state as a density matrix~\cite{Varadarajan2008}.
+Since Gleason's theorem could not directly apply on interval-valued
+probability measures, we would like to ask: How a quantum state looks
+like with the interval-valued probability? When the number and precision
+of the intervals increase, would the quantum interval-valued probability
+measures converge to the quantum probability measure induced by the
+Born rule~\cite{Born1983,Mermin2007,Jaeger2007}?
+
+\section{Kick-off Talk}
+
+In
+previous work, we examined the Hilbert space mathematical framework of
+quantum mechanics and teased apart its various aspects that directly
+rely on the infinite-precision real or complex numbers. We note two
+remarkable earlier results and an open question:
+\begin{itemize}
+\item UNIQUE-SAT: Schumacher and
+  Westmoreland~\cite{Schumacher2012-SCHMQT} argue that much of the
+  structure of traditional quantum mechanics is maintained in the
+  presence of finite fields. In particular, they establish that the
+  quantum theory based on the finite field of booleans retains the
+  following characteristics of quantum mechanics: the notions of
+  superposition, interference, entanglement, and mixed states of
+  quantum systems; the time evolution of quantum systems using
+  invertible linear operators; the complementarity of incompatible
+  observables; the exclusion of local hidden variable theories and the
+  impossibility of cloning quantum states; and the presence of natural
+  counterparts of quantum information protocols such as superdense
+  coding and teleportation. However we have argued that this theory is
+  not physically realizable as it allows the solution of
+  computationally difficult problems like
+  UNIQUE-SAT~\cite{Valiant198685} in constant time~\cite{usat}.
+
+\item Deutsch-Jozsa: In a follow-up paper~\cite{DQT2014}, we proposed
+  a variant of quantum mechanics in which the underlying field of
+  complex numbers is replaced by special finite fields with enough
+  structure to model Hermitian products that \emph{locally} behave
+  like inner products. The trick is to recognize that, as the
+  characteristic of the finite field increases, larger and larger
+  regions of the finite field become totally ordered, thereby
+  restoring, with some restrictions, all the usual properties of the
+  inner product needed for conventional quantum mechanics. Using this
+  theory to analyze the Deutsch-Jozsa algorithm reveals that the
+  characteristic of the finite field plays an essential role: as the
+  size of the finite field grows, so does the numerical range of the
+  intermediate and final results of the algorithms being implemented.
+  The theory naturally recovers a deterministic measure of the
+  intrinsic resources required for a given level of complexity; this
+  measure is normally completely hidden in computations with real
+  numbers, and explicitly exposing it is one of the significant
+  achievements of our discrete field analysis of quantum computation.
+  This solves the conundrum that the conventional Deutsch-Jozsa
+  algorithm~\cite{DeutschJozsa1992,Jaeger2007}
+  mysteriously continues to work for larger and larger input
+  functions without any apparent increase in resources.  Our analysis
+  of this problem reveals that as the size of the input increases, it
+  is necessary to increase the size of the finite field and hence the
+  size of the underlying available numeric coefficients.  This
+  observation does not fully explain the power of quantum computing
+  over classical computing, but at least it explains that some of the
+  power of quantum computing depends on increasingly larger precision
+  in the underlying field of numbers.
+
+\item An important special case of a generalized measurement is the
+  symmetric, informationally complete, positive operator valued
+  measure (SIC-POVM), which has applications in quantum
+  cryptography. This problem has been formulated in the context of
+  standard quantum theory where fields are complex numbers.  Although
+  a rigorous proof for the existence of SIC-POVMs for arbitrary
+  Hilbert space dimensions is still missing, it would be illuminating
+  to look for a formulation of the same problem in a discrete quantum
+  theory defined in terms of finite Galois fields.
+\end{itemize}
+
+A long term, ultimate, goal of this research proposal would be to
+combine the various pieces into a coherent computational model of
+quantum mechanics that keeps explicit track of resources needed to
+represent the interactive system representing the quantum state, its
+evolution, the observables, and the probabilities. Such a
+computational model of quantum mechanics would encompass classical
+(reversible) computation and potentially revolutionize quantum
+thinking with finite resources. The explicit manipulation of resources
+enables one of key idea that emerged in our previous work: the
+resources used to represent the quantum system are in principle
+unrelated to the resources available to the various observers. We
+conjecture that this asymmetry may prove key to resolving some of the
+quantum paradoxes.  The nature of quantum mechanics realized in terms
+of discrete fields and finitely-communicable probability estimates is
+amenable to direct computational exploration for reasonable field
+sizes and observational accuracy. We have established a set of utility
+libraries in Mathematica that supports a wide variety of such
+numerical experiments. Concurrently to this effort, we are also
+building on our previous work~\cite
+{VDS2009,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
+to build semantically well-founded implementations of the
+computational models investigated in this proposal.
+
+\paragraph*{Research Questions.} The aim of these implementations
+include:
+\begin{itemize}
+\item Provide an experimental testbed to simulate physical phenomena
+  (e.g.~\cite {OrtizEtAl2001,SommEtAl2002}) that complements the
+  Mathematica libraries in which quantum algorithms can be simulated;
+\item Establish connections between quantum programming concepts and
+  classical programming concepts. We plan to make our software
+  available for educational and research purposes; and 
+\item Analyze the computational complexity of quantum theories and
+  simulations based on discrete fields. What other (apart from
+  UNIQUE-SAT) supernatural algorithms can be implemented in
+  computational models based on discrete fields?
+\item Determine, through numerical computations, solutions for
+  SIC-POVM for small vector space dimensions.
+\end{itemize}
+
+propose to revisit quantum mechanics, quantum information, quantum
+computation, and the foundations of physics from this resource-aware
+perspective.
+
+Soon after the discovery of quantum effects in the early 1900s, it
+became evident that the quantum world requires a fresh worldview, not
+merely an extension of the repertoire of entities and constructions
+which explain classical physics. In the past thirty years, however,
+the first quantum revolution mostly relied on just that: extensions of
+classical logics, classical models of computation, and classical
+analysis of algorithms. Fundamentally, the foundations of logic and
+computing still embrace, to a large extent, the notion that the truth
+of a statement is ``absolute'' and independent of any reasoning,
+understanding, or action, i.e., logical statements are viewed as
+abstract entities for which it makes no sense to talk about
+entanglement with an observer: their truth or falsity is absolute and
+does not depend on the notion of observation. This absolute view of
+truth and the use of classical logic for reasoning about this absolute
+truth have both been critiqued for centuries by philosophers and other
+scientists but it is the advent of quantum science that really
+devastates this worldview of classical determinism. Indeed, quantum
+science suggests that the properties of physical systems can only be
+learned by observers interacting with the system, and that this
+interaction may entangle the observer with the system and disturb the
+properties of interest. This suggests that the possibility structure
+of our universe is not a fixed, Boolean structure, as we supposed
+classically, but is in fact a non-Boolean structure that changes
+dynamically~\cite{bub2006}.
+
+We believe that the foundations of physics should be revisited from a
+logical and computational approach
+
+More directly, world-renowned logician Girard states:
+Our vision for this revised computational and logic theory builds upon
+programming abstractions which assume evolving, incomplete, and
+inconsistent data, and principles for reasoning about programs which
+are based on finitely communicable evidence between subsystems or
+systems and observers, rather than absolute truth. The most natural
+way to achieve this shift in our ``computational thinking'' and to
+consolidate many of the new promising trends in computational,
+informational, and logical theory is to design new programming
+models. For it is indeed a widely accepted thesis that programming
+languages shape thought processes and design
+solutions~\cite{iverson80,johansen-berg01}. Our approach therefore is
+to develop new programming models based on both logical foundations
+and pragmatic considerations, to connect them to current
+computational, informational, and logical theory, and to make
+compelling arguments for the models by using them to write several
+novel and challenging applications.
+
+There is significant IU expertise in logic foundations, including
+unconventional logics such paraconsistent logics, relevance logic,
+multivalued logic with Bayesian inference, situation theory, and the
+Dempster-Shafer theory of belief functions and plausible reasoning,
+which can handle incomplete, evolving, and inconsistent information in
+a controlled and discriminating way. There is also significant IU
+expertise in the design and implementation of programming models, type
+theories, and semantics that encompass both the classical and quantum
+worlds. What IU lacks in expertise is an expert that bridges the
+programming models with actual quantum algorithms: this is a new breed
+of theoreticians with a strong background in both physics, complexity
+theory, and cryptography.
+
+Our initial results in that domain showed how subtle the
+issues can be~\cite{usat,geometry2013,DQT2014}: a straightforward
+replacement of the complex numbers by a finite field yields a variant
+of quantum mechanics in which computationally hard problems like
+UNIQUE-SAT (which decides whether a given Boolean formula is
+unsatisfiable or has exactly one satisfying assignment) can be
+deterministically solved in constant time. To eliminate such
+unrealistic theories requires delicate analysis of the structure of
+the Hilbert space, the process of observation, and the notion of
+probability teasing apart their reliance on the infinitely precise
+real numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is
+to shift focus from the infinitely-specified but not directly
+observable quantum states, to observable measurable properties of
+quantum systems and their probabilities. Furthermore, we insist that
+our theories of measurement and probability only refer to finitely
+communicable evidence within feasible computational bounds. It follows
+that states, observations, and probabilities all become ``fuzzy'',
+i.e., specified by intervals of confidence that can only increase in
+precision if the available resources increase proportionally. Our
+notion of ``fuzzy quantum mechanics'' is related to existing
+work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
+but, as will be explained in more detail, is distinguished by its
+unique computational character.
+
+We will begin by reviewing existing work that recasts classical
+probability spaces in a resource-aware setting and move to our
+proposal which, briefly speaking, aims at recasting quantum
+probability and hence quantum measurement to a corresponding
+resource-aware setting.
+
+In particular, the objectives to be achieved include:
+\begin{itemize}
+\item A computational framework for quantum measurement where quantum
+  systems are described in terms of interactive processes. The
+  framework takes care of the resources required (including the ones
+  related to the observer) to determine a given property of the
+  measured system.
+\item Develop a measurement framework based on quantum interval-valued
+  probabilities measures.
+\item Assess the validity of fundamental theorems of quantum
+  mechanics, such as Gleason, Bell, and Kochen-Specker, in a quantum
+  formulation stripped away of infinite resources. We will aim to
+  provide a definite answer to the Meyer-Mermin
+  debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004} on
+  the impact of finite precision measurements on the relevance of the
+  Kochen-Specker
+  theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
+\item Study the computational complexity of quantum theories and
+  simulations based on discrete (computable) fields.
+\item Study the problem of finding a complete set of mutually unbiased
+  bases
+  (SIC-POVM)~\cite{1751-8121-45-8-085306,1751-8121-47-33-335302,Caves2002}
+  over finite Galois fields.
+\end{itemize}
+We argue that no matter what the results are their impact will be
+strong. Positive results that formulate a computable, with clear
+resource bounds, theory of quantum measurement and quantum probability
+would be essential for understanding and realizing quantum
+computation. Any negative results would redirect research that aims at
+realizing quantum computation to other approaches. At an intellectual
+level, the results have the potential to solve or clarify several
+paradoxes in quantum mechanics, quantum information, computability,
+complexity theory, and perhaps quantum gravity.
+
+For centuries, the mathematical formalization of physical processes
+has been founded on the infinitely precise real or complex
+numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
+For example, almost every description of quantum mechanics, quantum
+computation, or quantum experiments refers to entities such as $\rme$,
+$\pi$, $\sqrt{2}$, etc (see, e.g.,
+\cite{Redhead1987-REDINA,544199,Mermin2007}).  Whether these models
+based on real numbers faithfully describe the nature or just an
+approximation is still an open question. If they are faithful, how the
+nature store and compute these real numbers to produce our
+experimental results would be the next natural question.  There are at
+least three possibilities:
 \begin{itemize}
@@
 infinitely precise real numbers~\cite{geometry2013,DQT2014}.
-
-\section{Proposed Question}
-
-In contrast to our previous works that assume the current quantum
-theory is just an approximation to the discrete reality, we now assume
-the nature really use real numbers. However, these real numbers could
-not be directly accessed by human who is bounded by finite resources.
-Therefore, even if the nature might have more computational power
-than a Turing machine, human might not be able to acquire and use
-the computational power more than a Turing machine.
-
-In order to model the bounded-resource human observers, we would like
-the theories of measurement and probability replaced by a subjective
-probability model, called the interval-valued probability. The question
-is how quantum mechanics would like with the interval-valued probability.
-
-In particular, based on conventional probability, Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
-suggests that idea to define a state as a density matrix~\cite{Varadarajan2008}.
-Since Gleason's theorem could not directly apply on interval-valued
-probability measures, we would like to ask: How a quantum state looks
-like with the interval-valued probability? When the number and precision
-of the intervals increase, would the quantum interval-valued probability
-measures converge to the quantum probability measure induced by the
-Born rule~\cite{Born1983,Mermin2007,Jaeger2007}?
-
-\section{Kick-off Talk}
 
@@
 \bibliographystyle{plain}
-\bibliography{../proposal/prop}
-
+\bibliography{prop}
 \end{comment}

### 2017-01-13 Rethinking Foundations of Physics 2017/application.tex
"Rethinking Foundations of Physics 2017\application.tex" Fix biblatex path error?
Updates from ShareLaTeX
"Rethinking Foundations of Physics 2017\application.lyx" It seems its LyX bug... Will send LyX ticket later...
application.tex \section{Statement of Motivation} Modified accordingly...

@@
 \usepackage[ backend=biber]{biblatex}
-%\addbibresource{../proposal/prop.bib}
+\addbibresource{../proposal/prop.bib}
+\addbibresource{cites1.bib}
 %%\addbibresource{C:/Users/Yu-Tsung/workspace/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/proposal/prop.bib}
-%% \addbibresource{"../proposal/prop.bib"}
-\addbibresource{prop.bib}
+%%\addbibresource{"../proposal/prop.bib"}
+%%\addbibresource{prop.bib}
 \ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
@@
 
-Physical processes are ultimately bounded in space, time, energy, and
-other resources. Yet, for centuries, the mathematical formalization of
-such processes has been founded on the infinitely precise real or
-complex numbers. Indeed, physics textbooks casually refer to entities
-such as $e$, $\pi$, $\sqrt{2}$, etc. From a computational perspective,
-such numbers do not exist in their entirety ``for free.''  For
-example, the state of the art algorithms for computing the $n$th
-binary digit of~$\pi$ require on the order of $O(n\log^{O(1)}(n))$
-operations~\cite{journals/moc/BaileyBP97}. In other words, simply
-referring to the $n$th digit of $\pi$ requires more and more resources
-as $n$ gets larger. Taking such resource bounds into consideration is
-what founded computer science as a discipline and is crucial for
-understanding the very nature of computation and, following
-Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
+Physical processes are ultimately bounded in space, time, energy,
+and other resources. Yet, for centuries, the mathematical formalization
+of such processes has been founded on the infinitely precise real
+or complex numbers. Indeed, physics textbooks casually refer to entities
+such as $\rme$, $\pi$, $\sqrt{2}$, etc~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
+From a computational perspective, such numbers do not exist in their
+entirety ``for free.'' For example, the state of the art algorithms
+for computing the $n$th binary digit of~$\pi$ require on the order
+of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$ operations~\cite{journals/moc/BaileyBP97}.
+In other words, simply referring to the $n$th digit of $\pi$ requires
+more and more resources as $n$ gets larger. Taking such resource
+bounds into consideration is what founded computer science as a discipline
+and is crucial for understanding the very nature of computation and,
+following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
 and others, for understanding the very nature of physical processes.
@@
 \bibliographystyle{plain}
-\bibliography{prop}
+\bibliography{../proposal/prop.bib}
+\bibliography{cites1.bib}
 \end{comment}

### 2017-01-13 Rethinking Foundations of Physics 2017/application.tex
application.tex \section{Proposed Question} Copied from general plan...

@@
 \section{Proposed Question}
+
+A major aim of this proposal is to recast quantum probability and
+measurement in a computational resource-aware setting. Our vision is
+to unify the strands above in a novel way as explained in this
+section. We start with some immediate observations that justify the
+rest of the development.
+
+\begin{itemize}
+
+\item If we insist that probabilities cannot be computed to infinite
+  precision and are bound to be approximations represented by
+  intervals of confidence, then quantum states themselves can only be
+  discussed within intervals of confidence. This raises an important
+  philosophical question with immense practical relevance in the
+  context of quantum computing. The question, which we could largely
+  bypass in the classical case, is whether there is, in the background
+  of all the measurements and probabilities, a ``real''
+  infinitely-precise quantum state that is being approximated and
+  that, in principle, can be more and more accurately described given
+  more and more resources. In other words, does a Gleason,
+  Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
+  or Kochen-Specker theorem still hold in a world with finite
+  resources?  The answer will have to be \emph{no} if we are to
+  respect these major theorems of quantum mechanics and quantum
+  information. Thus our first radical departure from the conventional
+  case will be that the quantum state itself must be fuzzy in some
+  sense to be formalized.
+
+\item Going further we actually have to concede not just the infinite
+  accuracy of the quantum state, but its very existence as a ``real''
+  entity that exists independently of measurements and
+  probabilities. The reasons for this second radical position are as
+  follows. First arguments embedded in the proof of the Kochen-Specker
+  theorem essentially rule out the existence of a sample space as the
+  probabilities of events cannot be consistently expressed using core
+  assignments to elements of the sample space. Second, the frequency
+  interpretation of probability which is already problematic in the
+  classical case, becomes untenable in the quantum case. In both
+  cases, but much more in the quantum case, it is much more sensible
+  to interpret probability in the Bayesian sense as ``lack of
+  knowledge''. This, and similar arguments elegantly expressed by
+  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+  suggest that the quantum state is more like an interactive system in
+  computer science parlance. In other words, the state is only
+  determined by its interactions with the environment or observers. A
+  rough but useful analogy in the context of computer science would be
+  a web server: the state of such a system cannot be said to exist
+  independently of the interactions with clients; each interaction
+  with a client determines a future state of the system and may affect
+  future interactions. Crucially, each client may have a
+  \emph{different} view of the web server that is consistent with
+  their own history of interactions. This computational perspective
+  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
+  that asserts that the quantum state is subjective: each observer has
+  a different view of the quantum system that is consistent with their
+  previous observations and that allows that observer, independently
+  of other observers, to assign beliefs (i.e., probabilities) to
+  possible future interactions.
+
+\end{itemize}
+
+\section{Kick-off Talk}
 

### 2017-01-13 Rethinking Foundations of Physics 2017/application.tex
application.tex \section{Kick-off Talk: The Meaning of Quantum Probability} Just copy the paper to this section...

@@
 
-\item Going further we actually have to concede not just the infinite
-  accuracy of the quantum state, but its very existence as a ``real''
-  entity that exists independently of measurements and
-  probabilities. The reasons for this second radical position are as
-  follows. First arguments embedded in the proof of the Kochen-Specker
-  theorem essentially rule out the existence of a sample space as the
-  probabilities of events cannot be consistently expressed using core
-  assignments to elements of the sample space. Second, the frequency
-  interpretation of probability which is already problematic in the
-  classical case, becomes untenable in the quantum case. In both
-  cases, but much more in the quantum case, it is much more sensible
-  to interpret probability in the Bayesian sense as ``lack of
-  knowledge''. This, and similar arguments elegantly expressed by
-  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
-  suggest that the quantum state is more like an interactive system in
-  computer science parlance. In other words, the state is only
-  determined by its interactions with the environment or observers. A
-  rough but useful analogy in the context of computer science would be
-  a web server: the state of such a system cannot be said to exist
-  independently of the interactions with clients; each interaction
-  with a client determines a future state of the system and may affect
-  future interactions. Crucially, each client may have a
-  \emph{different} view of the web server that is consistent with
-  their own history of interactions. This computational perspective
-  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
+\item Going further we actually have to concede not just the infinite accuracy
+of the quantum state, but its very existence as a ``real'' entity
+that exists independently of measurements and probabilities. The reasons
+for this second radical position are as follows. First arguments embedded
+in the proof of the Kochen-Specker theorem essentially rule out the
+existence of a sample space as the probabilities of events cannot
+be consistently expressed using core assignments to elements of the
+sample space. Second, the frequency interpretation of probability
+which is already problematic in the classical case, becomes untenable
+in the quantum case. In both cases, but much more in the quantum case,
+it is much more sensible to interpret probability in the Bayesian
+sense as ``lack of knowledge''. This, and similar arguments elegantly
+expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+suggest that the quantum state is more like an interactive system
+in computer science parlance. In other words, the state is only determined
+by its interactions with the environment or observers. A rough but
+useful analogy in the context of computer science would be a web server:
+the state of such a system cannot be said to exist independently of
+the interactions with clients; each interaction with a client determines
+a future state of the system and may affect future interactions. Crucially,
+each client may have a \emph{different} view of the web server that
+is consistent with their own history of interactions. This computational
+perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
 that asserts that the quantum state is subjective: each observer has
@@
 previous observations and that allows that observer, independently
-  of other observers, to assign beliefs (i.e., probabilities) to
-  possible future interactions.
-
+of other observers, to assign beliefs (i.e., probabilities) to possible
+future interactions.
 \end{itemize}
 
-\section{Kick-off Talk}
-
-The meaning of quantum probability
-
-The reality of the quantum state
-
---- next section
-
-The meaning of quantum probability: probability is approximate;
-intervals; Born; no state when approximation is bad.
-
-quantum state: Bayesian perspective; probability is subjective; hence
-state is subjective; given previous results that show that state does
-not exist when you have poor approximations; ?
-
-In contrast to our previous works that assume the current quantum
-theory is just an approximation to the discrete reality, we now assume
-the nature really use real numbers. However, these real numbers could
-not be directly accessed by human who is bounded by finite resources.
-Therefore, even if the nature might have more computational power
-than a Turing machine, human might not be able to acquire and use
-the computational power more than a Turing machine.
-
-In order to model the bounded-resource human observers, we would like
-the theories of measurement and probability replaced by a subjective
-probability model, called the interval-valued probability. The question
-is how quantum mechanics would like with the interval-valued probability.
-
-In particular, based on conventional probability, Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
-suggests that idea to define a state as a density matrix~\cite{Varadarajan2008}.
-Since Gleason's theorem could not directly apply on interval-valued
-probability measures, we would like to ask: How a quantum state looks
-like with the interval-valued probability? When the number and precision
-of the intervals increase, would the quantum interval-valued probability
-measures converge to the quantum probability measure induced by the
-Born rule~\cite{Born1983,Mermin2007,Jaeger2007}?
-
-\section{Kick-off Talk}
-
-In
-previous work, we examined the Hilbert space mathematical framework of
-quantum mechanics and teased apart its various aspects that directly
-rely on the infinite-precision real or complex numbers. We note two
-remarkable earlier results and an open question:
-\begin{itemize}
-\item UNIQUE-SAT: Schumacher and
-  Westmoreland~\cite{Schumacher2012-SCHMQT} argue that much of the
-  structure of traditional quantum mechanics is maintained in the
-  presence of finite fields. In particular, they establish that the
-  quantum theory based on the finite field of booleans retains the
-  following characteristics of quantum mechanics: the notions of
-  superposition, interference, entanglement, and mixed states of
-  quantum systems; the time evolution of quantum systems using
-  invertible linear operators; the complementarity of incompatible
-  observables; the exclusion of local hidden variable theories and the
-  impossibility of cloning quantum states; and the presence of natural
-  counterparts of quantum information protocols such as superdense
-  coding and teleportation. However we have argued that this theory is
-  not physically realizable as it allows the solution of
-  computationally difficult problems like
-  UNIQUE-SAT~\cite{Valiant198685} in constant time~\cite{usat}.
-
-\item Deutsch-Jozsa: In a follow-up paper~\cite{DQT2014}, we proposed
-  a variant of quantum mechanics in which the underlying field of
-  complex numbers is replaced by special finite fields with enough
-  structure to model Hermitian products that \emph{locally} behave
-  like inner products. The trick is to recognize that, as the
-  characteristic of the finite field increases, larger and larger
-  regions of the finite field become totally ordered, thereby
-  restoring, with some restrictions, all the usual properties of the
-  inner product needed for conventional quantum mechanics. Using this
-  theory to analyze the Deutsch-Jozsa algorithm reveals that the
-  characteristic of the finite field plays an essential role: as the
-  size of the finite field grows, so does the numerical range of the
-  intermediate and final results of the algorithms being implemented.
-  The theory naturally recovers a deterministic measure of the
-  intrinsic resources required for a given level of complexity; this
-  measure is normally completely hidden in computations with real
-  numbers, and explicitly exposing it is one of the significant
-  achievements of our discrete field analysis of quantum computation.
-  This solves the conundrum that the conventional Deutsch-Jozsa
-  algorithm~\cite{DeutschJozsa1992,Jaeger2007}
-  mysteriously continues to work for larger and larger input
-  functions without any apparent increase in resources.  Our analysis
-  of this problem reveals that as the size of the input increases, it
-  is necessary to increase the size of the finite field and hence the
-  size of the underlying available numeric coefficients.  This
-  observation does not fully explain the power of quantum computing
-  over classical computing, but at least it explains that some of the
-  power of quantum computing depends on increasingly larger precision
-  in the underlying field of numbers.
-
-\item An important special case of a generalized measurement is the
-  symmetric, informationally complete, positive operator valued
-  measure (SIC-POVM), which has applications in quantum
-  cryptography. This problem has been formulated in the context of
-  standard quantum theory where fields are complex numbers.  Although
-  a rigorous proof for the existence of SIC-POVMs for arbitrary
-  Hilbert space dimensions is still missing, it would be illuminating
-  to look for a formulation of the same problem in a discrete quantum
-  theory defined in terms of finite Galois fields.
-\end{itemize}
-
-A long term, ultimate, goal of this research proposal would be to
-combine the various pieces into a coherent computational model of
-quantum mechanics that keeps explicit track of resources needed to
-represent the interactive system representing the quantum state, its
-evolution, the observables, and the probabilities. Such a
-computational model of quantum mechanics would encompass classical
-(reversible) computation and potentially revolutionize quantum
-thinking with finite resources. The explicit manipulation of resources
-enables one of key idea that emerged in our previous work: the
-resources used to represent the quantum system are in principle
-unrelated to the resources available to the various observers. We
-conjecture that this asymmetry may prove key to resolving some of the
-quantum paradoxes.  The nature of quantum mechanics realized in terms
-of discrete fields and finitely-communicable probability estimates is
-amenable to direct computational exploration for reasonable field
-sizes and observational accuracy. We have established a set of utility
-libraries in Mathematica that supports a wide variety of such
-numerical experiments. Concurrently to this effort, we are also
-building on our previous work~\cite
-{VDS2009,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
-to build semantically well-founded implementations of the
-computational models investigated in this proposal.
-
-\paragraph*{Research Questions.} The aim of these implementations
-include:
-\begin{itemize}
-\item Provide an experimental testbed to simulate physical phenomena
-  (e.g.~\cite {OrtizEtAl2001,SommEtAl2002}) that complements the
-  Mathematica libraries in which quantum algorithms can be simulated;
-\item Establish connections between quantum programming concepts and
-  classical programming concepts. We plan to make our software
-  available for educational and research purposes; and 
-\item Analyze the computational complexity of quantum theories and
-  simulations based on discrete fields. What other (apart from
-  UNIQUE-SAT) supernatural algorithms can be implemented in
-  computational models based on discrete fields?
-\item Determine, through numerical computations, solutions for
-  SIC-POVM for small vector space dimensions.
-\end{itemize}
-
-propose to revisit quantum mechanics, quantum information, quantum
-computation, and the foundations of physics from this resource-aware
-perspective.
-
-Soon after the discovery of quantum effects in the early 1900s, it
-became evident that the quantum world requires a fresh worldview, not
-merely an extension of the repertoire of entities and constructions
-which explain classical physics. In the past thirty years, however,
-the first quantum revolution mostly relied on just that: extensions of
-classical logics, classical models of computation, and classical
-analysis of algorithms. Fundamentally, the foundations of logic and
-computing still embrace, to a large extent, the notion that the truth
-of a statement is ``absolute'' and independent of any reasoning,
-understanding, or action, i.e., logical statements are viewed as
-abstract entities for which it makes no sense to talk about
-entanglement with an observer: their truth or falsity is absolute and
-does not depend on the notion of observation. This absolute view of
-truth and the use of classical logic for reasoning about this absolute
-truth have both been critiqued for centuries by philosophers and other
-scientists but it is the advent of quantum science that really
-devastates this worldview of classical determinism. Indeed, quantum
-science suggests that the properties of physical systems can only be
-learned by observers interacting with the system, and that this
-interaction may entangle the observer with the system and disturb the
-properties of interest. This suggests that the possibility structure
-of our universe is not a fixed, Boolean structure, as we supposed
-classically, but is in fact a non-Boolean structure that changes
-dynamically~\cite{bub2006}.
-
-We believe that the foundations of physics should be revisited from a
-logical and computational approach
-
-More directly, world-renowned logician Girard states:
-Our vision for this revised computational and logic theory builds upon
-programming abstractions which assume evolving, incomplete, and
-inconsistent data, and principles for reasoning about programs which
-are based on finitely communicable evidence between subsystems or
-systems and observers, rather than absolute truth. The most natural
-way to achieve this shift in our ``computational thinking'' and to
-consolidate many of the new promising trends in computational,
-informational, and logical theory is to design new programming
-models. For it is indeed a widely accepted thesis that programming
-languages shape thought processes and design
-solutions~\cite{iverson80,johansen-berg01}. Our approach therefore is
-to develop new programming models based on both logical foundations
-and pragmatic considerations, to connect them to current
-computational, informational, and logical theory, and to make
-compelling arguments for the models by using them to write several
-novel and challenging applications.
-
-There is significant IU expertise in logic foundations, including
-unconventional logics such paraconsistent logics, relevance logic,
-multivalued logic with Bayesian inference, situation theory, and the
-Dempster-Shafer theory of belief functions and plausible reasoning,
-which can handle incomplete, evolving, and inconsistent information in
-a controlled and discriminating way. There is also significant IU
-expertise in the design and implementation of programming models, type
-theories, and semantics that encompass both the classical and quantum
-worlds. What IU lacks in expertise is an expert that bridges the
-programming models with actual quantum algorithms: this is a new breed
-of theoreticians with a strong background in both physics, complexity
-theory, and cryptography.
-
-Our initial results in that domain showed how subtle the
-issues can be~\cite{usat,geometry2013,DQT2014}: a straightforward
-replacement of the complex numbers by a finite field yields a variant
-of quantum mechanics in which computationally hard problems like
-UNIQUE-SAT (which decides whether a given Boolean formula is
-unsatisfiable or has exactly one satisfying assignment) can be
-deterministically solved in constant time. To eliminate such
-unrealistic theories requires delicate analysis of the structure of
-the Hilbert space, the process of observation, and the notion of
-probability teasing apart their reliance on the infinitely precise
-real numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is
-to shift focus from the infinitely-specified but not directly
-observable quantum states, to observable measurable properties of
-quantum systems and their probabilities. Furthermore, we insist that
-our theories of measurement and probability only refer to finitely
-communicable evidence within feasible computational bounds. It follows
-that states, observations, and probabilities all become ``fuzzy'',
-i.e., specified by intervals of confidence that can only increase in
-precision if the available resources increase proportionally. Our
-notion of ``fuzzy quantum mechanics'' is related to existing
-work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
-but, as will be explained in more detail, is distinguished by its
-unique computational character.
-
-We will begin by reviewing existing work that recasts classical
-probability spaces in a resource-aware setting and move to our
-proposal which, briefly speaking, aims at recasting quantum
-probability and hence quantum measurement to a corresponding
-resource-aware setting.
-
-In particular, the objectives to be achieved include:
-\begin{itemize}
-\item A computational framework for quantum measurement where quantum
-  systems are described in terms of interactive processes. The
-  framework takes care of the resources required (including the ones
-  related to the observer) to determine a given property of the
-  measured system.
-\item Develop a measurement framework based on quantum interval-valued
-  probabilities measures.
-\item Assess the validity of fundamental theorems of quantum
-  mechanics, such as Gleason, Bell, and Kochen-Specker, in a quantum
-  formulation stripped away of infinite resources. We will aim to
-  provide a definite answer to the Meyer-Mermin
-  debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004} on
-  the impact of finite precision measurements on the relevance of the
-  Kochen-Specker
-  theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
-\item Study the computational complexity of quantum theories and
-  simulations based on discrete (computable) fields.
-\item Study the problem of finding a complete set of mutually unbiased
-  bases
-  (SIC-POVM)~\cite{1751-8121-45-8-085306,1751-8121-47-33-335302,Caves2002}
-  over finite Galois fields.
-\end{itemize}
-We argue that no matter what the results are their impact will be
-strong. Positive results that formulate a computable, with clear
-resource bounds, theory of quantum measurement and quantum probability
-would be essential for understanding and realizing quantum
-computation. Any negative results would redirect research that aims at
-realizing quantum computation to other approaches. At an intellectual
-level, the results have the potential to solve or clarify several
-paradoxes in quantum mechanics, quantum information, computability,
-complexity theory, and perhaps quantum gravity.
-
-For centuries, the mathematical formalization of physical processes
-has been founded on the infinitely precise real or complex
-numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
-For example, almost every description of quantum mechanics, quantum
-computation, or quantum experiments refers to entities such as $\rme$,
-$\pi$, $\sqrt{2}$, etc (see, e.g.,
-\cite{Redhead1987-REDINA,544199,Mermin2007}).  Whether these models
-based on real numbers faithfully describe the nature or just an
-approximation is still an open question. If they are faithful, how the
-nature store and compute these real numbers to produce our
-experimental results would be the next natural question.  There are at
-least three possibilities:
-\begin{itemize}
-\item For any computable number~\cite{Turing_1937}, the nature only store
-the code of the Turing machine which computes the given number, and
-manipulate these codes directly during the computation~\cite{Ziegler2007,weihrauch2012computable}.
-\item The nature stores real numbers on infinitely long Turing machine tapes,
-and handle these numbers by a Turing machine~\cite{Ziegler2007,weihrauch2012computable}.
-In another word, the nature stores real numbers as a whole, but compute
-them piecewisely.
-\item The nature stores and computes real numbers as a whole~\cite{Ziegler2007,blum2012complexity}.
-\end{itemize}
-All these possibilities are not very desirable because they suggest
-the nature might have more computational power than a Turing machine.
-On one hand, if the nature only stores computable numbers by their
-Turing machine codes, the nature might be able to decide whether two
-Turing machines output exactly the same numbers, since this is used
-to decide whether an observable is degenerated or not. However, testing
-whether two Turing machines are output-equivalent is undecidable by
-Rice's theorem~\cite{Rice_1953,Ziegler2007,weihrauch2012computable},
-i.e., the nature has more computational power than a Turing machine.
-On the other hand, if the nature stores real numbers as a whole, any
-particular real number could serve as an oracle and give the nature
-more computational power than a Turing machine. For example, maybe
-the mass of the electron in some representation is the halting oracle
-for some representation of Turing machines. Then, we could solve the
-halting problem by just measuring the mass of the electron. This kind
-of possibility has been online discussed by Peter Shor and others~\cite{PhysicsStackExchange16889}.
-
-Since all possibilities that quantum theory is faithful are not very
-desirable, maybe every description of quantum theory is just an approximation.
-In this case, there is the other possibility:
-\begin{itemize}
-\item The real and complex numbers only exist in our model. The nature is
-essentially discrete, and could be simulated by a Turing machine.
-\end{itemize}
-We have followed this approach to study quantum theory over discrete
-finite fields~\cite{usat,geometry2013,DQT2014}. This yields a variant
-of quantum mechanics in which computationally hard problems like UNIQUE-SAT
-(which decides whether a given Boolean formula is unsatisfiable or
-has exactly one satisfying assignment~\cite{Valiant198685,Papadimitriou1993,AroraBarak2009})
-can be deterministically solved in constant time. We then delicate
-analysis of the structure of the Hilbert space, the process of observation,
-and the notion of probability by teasing apart their reliance on the
-infinitely precise real numbers~\cite{geometry2013,DQT2014}.
+\section{Kick-off Talk: The Meaning of Quantum Probability}
 
@@
 
+\section{Kick-off Talk: The Reality of the Quantum State}
+
+The meaning of quantum probability
+
+The reality of the quantum state
+
+— next section
+
+The meaning of quantum probability: probability is approximate; intervals;
+Born; no state when approximation is bad.
+
+quantum state: Bayesian perspective; probability is subjective; hence
+state is subjective; given previous results that show that state does
+not exist when you have poor approximations; ?
+
+In contrast to our previous works that assume the current quantum
+theory is just an approximation to the discrete reality, we now assume
+the nature really use real numbers. However, these real numbers could
+not be directly accessed by human who is bounded by finite resources.
+Therefore, even if the nature might have more computational power
+than a Turing machine, human might not be able to acquire and use
+the computational power more than a Turing machine.
+
+In order to model the bounded-resource human observers, we would like
+the theories of measurement and probability replaced by a subjective
+probability model, called the interval-valued probability. The question
+is how quantum mechanics would like with the interval-valued probability.
+
+In particular, based on conventional probability, Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
+suggests that idea to define a state as a density matrix~\cite{Varadarajan2008}.
+Since Gleason's theorem could not directly apply on interval-valued
+probability measures, we would like to ask: How a quantum state looks
+like with the interval-valued probability? When the number and precision
+of the intervals increase, would the quantum interval-valued probability
+measures converge to the quantum probability measure induced by the
+Born rule~\cite{Born1983,Mermin2007,Jaeger2007}?
+
+\section{Kick-off Talk}
+
+In previous work, we examined the Hilbert space mathematical framework
+of quantum mechanics and teased apart its various aspects that directly
+rely on the infinite-precision real or complex numbers. We note two
+remarkable earlier results and an open question: 
+\begin{itemize}
+\item UNIQUE-SAT: Schumacher and
+  Westmoreland~\cite{Schumacher2012-SCHMQT} argue that much of the
+  structure of traditional quantum mechanics is maintained in the
+  presence of finite fields. In particular, they establish that the
+  quantum theory based on the finite field of booleans retains the
+  following characteristics of quantum mechanics: the notions of
+  superposition, interference, entanglement, and mixed states of
+  quantum systems; the time evolution of quantum systems using
+  invertible linear operators; the complementarity of incompatible
+  observables; the exclusion of local hidden variable theories and the
+  impossibility of cloning quantum states; and the presence of natural
+  counterparts of quantum information protocols such as superdense
+  coding and teleportation. However we have argued that this theory is
+  not physically realizable as it allows the solution of
+  computationally difficult problems like
+  UNIQUE-SAT~\cite{Valiant198685} in constant time~\cite{usat}.
+
+\item Deutsch-Jozsa: In a follow-up paper~\cite{DQT2014}, we proposed
+  a variant of quantum mechanics in which the underlying field of
+  complex numbers is replaced by special finite fields with enough
+  structure to model Hermitian products that \emph{locally} behave
+  like inner products. The trick is to recognize that, as the
+  characteristic of the finite field increases, larger and larger
+  regions of the finite field become totally ordered, thereby
+  restoring, with some restrictions, all the usual properties of the
+  inner product needed for conventional quantum mechanics. Using this
+  theory to analyze the Deutsch-Jozsa algorithm reveals that the
+  characteristic of the finite field plays an essential role: as the
+  size of the finite field grows, so does the numerical range of the
+  intermediate and final results of the algorithms being implemented.
+  The theory naturally recovers a deterministic measure of the
+  intrinsic resources required for a given level of complexity; this
+  measure is normally completely hidden in computations with real
+  numbers, and explicitly exposing it is one of the significant
+  achievements of our discrete field analysis of quantum computation.
+  This solves the conundrum that the conventional Deutsch-Jozsa
+  algorithm~\cite{DeutschJozsa1992,Jaeger2007}
+  mysteriously continues to work for larger and larger input
+  functions without any apparent increase in resources.  Our analysis
+  of this problem reveals that as the size of the input increases, it
+  is necessary to increase the size of the finite field and hence the
+  size of the underlying available numeric coefficients.  This
+  observation does not fully explain the power of quantum computing
+  over classical computing, but at least it explains that some of the
+  power of quantum computing depends on increasingly larger precision
+  in the underlying field of numbers.
+
+\item An important special case of a generalized measurement is the
+  symmetric, informationally complete, positive operator valued
+  measure (SIC-POVM), which has applications in quantum
+  cryptography. This problem has been formulated in the context of
+  standard quantum theory where fields are complex numbers.  Although
+  a rigorous proof for the existence of SIC-POVMs for arbitrary
+  Hilbert space dimensions is still missing, it would be illuminating
+  to look for a formulation of the same problem in a discrete quantum
+  theory defined in terms of finite Galois fields.
+\end{itemize}
+
+A long term, ultimate, goal of this research proposal would be to
+combine the various pieces into a coherent computational model of
+quantum mechanics that keeps explicit track of resources needed to
+represent the interactive system representing the quantum state, its
+evolution, the observables, and the probabilities. Such a
+computational model of quantum mechanics would encompass classical
+(reversible) computation and potentially revolutionize quantum
+thinking with finite resources. The explicit manipulation of resources
+enables one of key idea that emerged in our previous work: the
+resources used to represent the quantum system are in principle
+unrelated to the resources available to the various observers. We
+conjecture that this asymmetry may prove key to resolving some of the
+quantum paradoxes.  The nature of quantum mechanics realized in terms
+of discrete fields and finitely-communicable probability estimates is
+amenable to direct computational exploration for reasonable field
+sizes and observational accuracy. We have established a set of utility
+libraries in Mathematica that supports a wide variety of such
+numerical experiments. Concurrently to this effort, we are also
+building on our previous work~\cite
+{VDS2009,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
+to build semantically well-founded implementations of the
+computational models investigated in this proposal.
+
+\paragraph*{Research Questions.} The aim of these implementations
+include:
+\begin{itemize}
+\item Provide an experimental testbed to simulate physical phenomena
+  (e.g.~\cite {OrtizEtAl2001,SommEtAl2002}) that complements the
+  Mathematica libraries in which quantum algorithms can be simulated;
+\item Establish connections between quantum programming concepts and
+  classical programming concepts. We plan to make our software
+  available for educational and research purposes; and 
+\item Analyze the computational complexity of quantum theories and
+  simulations based on discrete fields. What other (apart from
+  UNIQUE-SAT) supernatural algorithms can be implemented in
+  computational models based on discrete fields?
+\item Determine, through numerical computations, solutions for
+  SIC-POVM for small vector space dimensions.
+\end{itemize}
+
+propose to revisit quantum mechanics, quantum information, quantum
+computation, and the foundations of physics from this resource-aware
+perspective.
+
+Soon after the discovery of quantum effects in the early 1900s, it
+became evident that the quantum world requires a fresh worldview, not
+merely an extension of the repertoire of entities and constructions
+which explain classical physics. In the past thirty years, however,
+the first quantum revolution mostly relied on just that: extensions of
+classical logics, classical models of computation, and classical
+analysis of algorithms. Fundamentally, the foundations of logic and
+computing still embrace, to a large extent, the notion that the truth
+of a statement is ``absolute'' and independent of any reasoning,
+understanding, or action, i.e., logical statements are viewed as
+abstract entities for which it makes no sense to talk about
+entanglement with an observer: their truth or falsity is absolute and
+does not depend on the notion of observation. This absolute view of
+truth and the use of classical logic for reasoning about this absolute
+truth have both been critiqued for centuries by philosophers and other
+scientists but it is the advent of quantum science that really
+devastates this worldview of classical determinism. Indeed, quantum
+science suggests that the properties of physical systems can only be
+learned by observers interacting with the system, and that this
+interaction may entangle the observer with the system and disturb the
+properties of interest. This suggests that the possibility structure
+of our universe is not a fixed, Boolean structure, as we supposed
+classically, but is in fact a non-Boolean structure that changes
+dynamically~\cite{bub2006}.
+
+We believe that the foundations of physics should be revisited from a
+logical and computational approach
+
+More directly, world-renowned logician Girard states:
+Our vision for this revised computational and logic theory builds upon
+programming abstractions which assume evolving, incomplete, and
+inconsistent data, and principles for reasoning about programs which
+are based on finitely communicable evidence between subsystems or
+systems and observers, rather than absolute truth. The most natural
+way to achieve this shift in our ``computational thinking'' and to
+consolidate many of the new promising trends in computational,
+informational, and logical theory is to design new programming
+models. For it is indeed a widely accepted thesis that programming
+languages shape thought processes and design
+solutions~\cite{iverson80,johansen-berg01}. Our approach therefore is
+to develop new programming models based on both logical foundations
+and pragmatic considerations, to connect them to current
+computational, informational, and logical theory, and to make
+compelling arguments for the models by using them to write several
+novel and challenging applications.
+
+There is significant IU expertise in logic foundations, including
+unconventional logics such paraconsistent logics, relevance logic,
+multivalued logic with Bayesian inference, situation theory, and the
+Dempster-Shafer theory of belief functions and plausible reasoning,
+which can handle incomplete, evolving, and inconsistent information in
+a controlled and discriminating way. There is also significant IU
+expertise in the design and implementation of programming models, type
+theories, and semantics that encompass both the classical and quantum
+worlds. What IU lacks in expertise is an expert that bridges the
+programming models with actual quantum algorithms: this is a new breed
+of theoreticians with a strong background in both physics, complexity
+theory, and cryptography.
+
+Our initial results in that domain showed how subtle the
+issues can be~\cite{usat,geometry2013,DQT2014}: a straightforward
+replacement of the complex numbers by a finite field yields a variant
+of quantum mechanics in which computationally hard problems like
+UNIQUE-SAT (which decides whether a given Boolean formula is
+unsatisfiable or has exactly one satisfying assignment) can be
+deterministically solved in constant time. To eliminate such
+unrealistic theories requires delicate analysis of the structure of
+the Hilbert space, the process of observation, and the notion of
+probability teasing apart their reliance on the infinitely precise
+real numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is
+to shift focus from the infinitely-specified but not directly
+observable quantum states, to observable measurable properties of
+quantum systems and their probabilities. Furthermore, we insist that
+our theories of measurement and probability only refer to finitely
+communicable evidence within feasible computational bounds. It follows
+that states, observations, and probabilities all become ``fuzzy'',
+i.e., specified by intervals of confidence that can only increase in
+precision if the available resources increase proportionally. Our
+notion of ``fuzzy quantum mechanics'' is related to existing
+work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
+but, as will be explained in more detail, is distinguished by its
+unique computational character.
+
+We will begin by reviewing existing work that recasts classical
+probability spaces in a resource-aware setting and move to our
+proposal which, briefly speaking, aims at recasting quantum
+probability and hence quantum measurement to a corresponding
+resource-aware setting.
+
+In particular, the objectives to be achieved include:
+\begin{itemize}
+\item A computational framework for quantum measurement where quantum
+  systems are described in terms of interactive processes. The
+  framework takes care of the resources required (including the ones
+  related to the observer) to determine a given property of the
+  measured system.
+\item Develop a measurement framework based on quantum interval-valued
+  probabilities measures.
+\item Assess the validity of fundamental theorems of quantum
+  mechanics, such as Gleason, Bell, and Kochen-Specker, in a quantum
+  formulation stripped away of infinite resources. We will aim to
+  provide a definite answer to the Meyer-Mermin
+  debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004} on
+  the impact of finite precision measurements on the relevance of the
+  Kochen-Specker
+  theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
+\item Study the computational complexity of quantum theories and
+  simulations based on discrete (computable) fields.
+\item Study the problem of finding a complete set of mutually unbiased
+  bases
+  (SIC-POVM)~\cite{1751-8121-45-8-085306,1751-8121-47-33-335302,Caves2002}
+  over finite Galois fields.
+\end{itemize}
+We argue that no matter what the results are their impact will be
+strong. Positive results that formulate a computable, with clear
+resource bounds, theory of quantum measurement and quantum probability
+would be essential for understanding and realizing quantum
+computation. Any negative results would redirect research that aims at
+realizing quantum computation to other approaches. At an intellectual
+level, the results have the potential to solve or clarify several
+paradoxes in quantum mechanics, quantum information, computability,
+complexity theory, and perhaps quantum gravity.
+
+For centuries, the mathematical formalization of physical processes
+has been founded on the infinitely precise real or complex
+numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
+For example, almost every description of quantum mechanics, quantum
+computation, or quantum experiments refers to entities such as $\rme$,
+$\pi$, $\sqrt{2}$, etc (see, e.g.,
+\cite{Redhead1987-REDINA,544199,Mermin2007}).  Whether these models
+based on real numbers faithfully describe the nature or just an
+approximation is still an open question. If they are faithful, how the
+nature store and compute these real numbers to produce our
+experimental results would be the next natural question.  There are at
+least three possibilities:
+\begin{itemize}
+\item For any computable number~\cite{Turing_1937}, the nature only store
+the code of the Turing machine which computes the given number, and
+manipulate these codes directly during the computation~\cite{Ziegler2007,weihrauch2012computable}.
+\item The nature stores real numbers on infinitely long Turing machine tapes,
+and handle these numbers by a Turing machine~\cite{Ziegler2007,weihrauch2012computable}.
+In another word, the nature stores real numbers as a whole, but compute
+them piecewisely.
+\item The nature stores and computes real numbers as a whole~\cite{Ziegler2007,blum2012complexity}.
+\end{itemize}
+All these possibilities are not very desirable because they suggest
+the nature might have more computational power than a Turing machine.
+On one hand, if the nature only stores computable numbers by their
+Turing machine codes, the nature might be able to decide whether two
+Turing machines output exactly the same numbers, since this is used
+to decide whether an observable is degenerated or not. However, testing
+whether two Turing machines are output-equivalent is undecidable by
+Rice's theorem~\cite{Rice_1953,Ziegler2007,weihrauch2012computable},
+i.e., the nature has more computational power than a Turing machine.
+On the other hand, if the nature stores real numbers as a whole, any
+particular real number could serve as an oracle and give the nature
+more computational power than a Turing machine. For example, maybe
+the mass of the electron in some representation is the halting oracle
+for some representation of Turing machines. Then, we could solve the
+halting problem by just measuring the mass of the electron. This kind
+of possibility has been online discussed by Peter Shor and others~\cite{PhysicsStackExchange16889}.
+
+Since all possibilities that quantum theory is faithful are not very
+desirable, maybe every description of quantum theory is just an approximation.
+In this case, there is the other possibility:
+\begin{itemize}
+\item The real and complex numbers only exist in our model. The nature is
+essentially discrete, and could be simulated by a Turing machine.
+\end{itemize}
+We have followed this approach to study quantum theory over discrete
+finite fields~\cite{usat,geometry2013,DQT2014}. This yields a variant
+of quantum mechanics in which computationally hard problems like UNIQUE-SAT
+(which decides whether a given Boolean formula is unsatisfiable or
+has exactly one satisfying assignment~\cite{Valiant198685,Papadimitriou1993,AroraBarak2009})
+can be deterministically solved in constant time. We then delicate
+analysis of the structure of the Hilbert space, the process of observation,
+and the notion of probability by teasing apart their reliance on the
+infinitely precise real numbers~\cite{geometry2013,DQT2014}.
+
 \section{About Myself}

### 2017-01-14 Rethinking Foundations of Physics 2017/application.tex
application.tex \section{Proposed Question} Only focus on one question..

--- 2017-01-13 Rethinking Foundations of Physics 2017/application.tex
@@
 
-The meaning of quantum probability
-
-The reality of the quantum state
-
---- next section
-
-The meaning of quantum probability: probability is approximate;
-intervals; Born; no state when approximation is bad.
-
-quantum state: Bayesian perspective; probability is subjective; hence
-state is subjective; given previous results that show that state does
-not exist when you have poor approximations; ?
-
-In contrast to our previous works that assume the current quantum
-theory is just an approximation to the discrete reality, we now assume
-the nature really use real numbers. However, these real numbers could
-not be directly accessed by human who is bounded by finite resources.
-Therefore, even if the nature might have more computational power
-than a Turing machine, human might not be able to acquire and use
-the computational power more than a Turing machine.
-
-In order to model the bounded-resource human observers, we would like
-the theories of measurement and probability replaced by a subjective
-probability model, called the interval-valued probability. The question
-is how quantum mechanics would like with the interval-valued probability.
-
-In particular, based on conventional probability, Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
-suggests that idea to define a state as a density matrix~\cite{Varadarajan2008}.
-Since Gleason's theorem could not directly apply on interval-valued
-probability measures, we would like to ask: How a quantum state looks
-like with the interval-valued probability? When the number and precision
-of the intervals increase, would the quantum interval-valued probability
-measures converge to the quantum probability measure induced by the
-Born rule~\cite{Born1983,Mermin2007,Jaeger2007}?
+If we insist that probabilities cannot be computed to infinite precision
+and are bound to be approximations represented by intervals of confidence,
+then quantum states themselves can only be discussed within intervals
+of confidence. This raises an important philosophical question with
+immense practical relevance in the context of quantum computing. The
+question, which we could largely bypass in the classical case, is
+whether there is, in the background of all the measurements and probabilities,
+a ``real'' infinitely-precise quantum state that is being approximated
+and that, in principle, can be more and more accurately described
+given more and more resources.
 
 \section{Kick-off Talk}
-
-In
-previous work, we examined the Hilbert space mathematical framework of
-quantum mechanics and teased apart its various aspects that directly
-rely on the infinite-precision real or complex numbers. We note two
-remarkable earlier results and an open question:
-\begin{itemize}
-\item UNIQUE-SAT: Schumacher and
-  Westmoreland~\cite{Schumacher2012-SCHMQT} argue that much of the
-  structure of traditional quantum mechanics is maintained in the
-  presence of finite fields. In particular, they establish that the
-  quantum theory based on the finite field of booleans retains the
-  following characteristics of quantum mechanics: the notions of
-  superposition, interference, entanglement, and mixed states of
-  quantum systems; the time evolution of quantum systems using
-  invertible linear operators; the complementarity of incompatible
-  observables; the exclusion of local hidden variable theories and the
-  impossibility of cloning quantum states; and the presence of natural
-  counterparts of quantum information protocols such as superdense
-  coding and teleportation. However we have argued that this theory is
-  not physically realizable as it allows the solution of
-  computationally difficult problems like
-  UNIQUE-SAT~\cite{Valiant198685} in constant time~\cite{usat}.
-
-\item Deutsch-Jozsa: In a follow-up paper~\cite{DQT2014}, we proposed
-  a variant of quantum mechanics in which the underlying field of
-  complex numbers is replaced by special finite fields with enough
-  structure to model Hermitian products that \emph{locally} behave
-  like inner products. The trick is to recognize that, as the
-  characteristic of the finite field increases, larger and larger
-  regions of the finite field become totally ordered, thereby
-  restoring, with some restrictions, all the usual properties of the
-  inner product needed for conventional quantum mechanics. Using this
-  theory to analyze the Deutsch-Jozsa algorithm reveals that the
-  characteristic of the finite field plays an essential role: as the
-  size of the finite field grows, so does the numerical range of the
-  intermediate and final results of the algorithms being implemented.
-  The theory naturally recovers a deterministic measure of the
-  intrinsic resources required for a given level of complexity; this
-  measure is normally completely hidden in computations with real
-  numbers, and explicitly exposing it is one of the significant
-  achievements of our discrete field analysis of quantum computation.
-  This solves the conundrum that the conventional Deutsch-Jozsa
-  algorithm~\cite{DeutschJozsa1992,Jaeger2007}
-  mysteriously continues to work for larger and larger input
-  functions without any apparent increase in resources.  Our analysis
-  of this problem reveals that as the size of the input increases, it
-  is necessary to increase the size of the finite field and hence the
-  size of the underlying available numeric coefficients.  This
-  observation does not fully explain the power of quantum computing
-  over classical computing, but at least it explains that some of the
-  power of quantum computing depends on increasingly larger precision
-  in the underlying field of numbers.
-
-\item An important special case of a generalized measurement is the
-  symmetric, informationally complete, positive operator valued
-  measure (SIC-POVM), which has applications in quantum
-  cryptography. This problem has been formulated in the context of
-  standard quantum theory where fields are complex numbers.  Although
-  a rigorous proof for the existence of SIC-POVMs for arbitrary
-  Hilbert space dimensions is still missing, it would be illuminating
-  to look for a formulation of the same problem in a discrete quantum
-  theory defined in terms of finite Galois fields.
-\end{itemize}
-
-A long term, ultimate, goal of this research proposal would be to
-combine the various pieces into a coherent computational model of
-quantum mechanics that keeps explicit track of resources needed to
-represent the interactive system representing the quantum state, its
-evolution, the observables, and the probabilities. Such a
-computational model of quantum mechanics would encompass classical
-(reversible) computation and potentially revolutionize quantum
-thinking with finite resources. The explicit manipulation of resources
-enables one of key idea that emerged in our previous work: the
-resources used to represent the quantum system are in principle
-unrelated to the resources available to the various observers. We
-conjecture that this asymmetry may prove key to resolving some of the
-quantum paradoxes.  The nature of quantum mechanics realized in terms
-of discrete fields and finitely-communicable probability estimates is
-amenable to direct computational exploration for reasonable field
-sizes and observational accuracy. We have established a set of utility
-libraries in Mathematica that supports a wide variety of such
-numerical experiments. Concurrently to this effort, we are also
-building on our previous work~\cite
-{VDS2009,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
-to build semantically well-founded implementations of the
-computational models investigated in this proposal.
-
-\paragraph*{Research Questions.} The aim of these implementations
-include:
-\begin{itemize}
-\item Provide an experimental testbed to simulate physical phenomena
-  (e.g.~\cite {OrtizEtAl2001,SommEtAl2002}) that complements the
-  Mathematica libraries in which quantum algorithms can be simulated;
-\item Establish connections between quantum programming concepts and
-  classical programming concepts. We plan to make our software
-  available for educational and research purposes; and 
-\item Analyze the computational complexity of quantum theories and
-  simulations based on discrete fields. What other (apart from
-  UNIQUE-SAT) supernatural algorithms can be implemented in
-  computational models based on discrete fields?
-\item Determine, through numerical computations, solutions for
-  SIC-POVM for small vector space dimensions.
-\end{itemize}
-
-propose to revisit quantum mechanics, quantum information, quantum
-computation, and the foundations of physics from this resource-aware
-perspective.
-
-Soon after the discovery of quantum effects in the early 1900s, it
-became evident that the quantum world requires a fresh worldview, not
-merely an extension of the repertoire of entities and constructions
-which explain classical physics. In the past thirty years, however,
-the first quantum revolution mostly relied on just that: extensions of
-classical logics, classical models of computation, and classical
-analysis of algorithms. Fundamentally, the foundations of logic and
-computing still embrace, to a large extent, the notion that the truth
-of a statement is ``absolute'' and independent of any reasoning,
-understanding, or action, i.e., logical statements are viewed as
-abstract entities for which it makes no sense to talk about
-entanglement with an observer: their truth or falsity is absolute and
-does not depend on the notion of observation. This absolute view of
-truth and the use of classical logic for reasoning about this absolute
-truth have both been critiqued for centuries by philosophers and other
-scientists but it is the advent of quantum science that really
-devastates this worldview of classical determinism. Indeed, quantum
-science suggests that the properties of physical systems can only be
-learned by observers interacting with the system, and that this
-interaction may entangle the observer with the system and disturb the
-properties of interest. This suggests that the possibility structure
-of our universe is not a fixed, Boolean structure, as we supposed
-classically, but is in fact a non-Boolean structure that changes
-dynamically~\cite{bub2006}.
-
-We believe that the foundations of physics should be revisited from a
-logical and computational approach
-
-More directly, world-renowned logician Girard states:
-Our vision for this revised computational and logic theory builds upon
-programming abstractions which assume evolving, incomplete, and
-inconsistent data, and principles for reasoning about programs which
-are based on finitely communicable evidence between subsystems or
-systems and observers, rather than absolute truth. The most natural
-way to achieve this shift in our ``computational thinking'' and to
-consolidate many of the new promising trends in computational,
-informational, and logical theory is to design new programming
-models. For it is indeed a widely accepted thesis that programming
-languages shape thought processes and design
-solutions~\cite{iverson80,johansen-berg01}. Our approach therefore is
-to develop new programming models based on both logical foundations
-and pragmatic considerations, to connect them to current
-computational, informational, and logical theory, and to make
-compelling arguments for the models by using them to write several
-novel and challenging applications.
-
-There is significant IU expertise in logic foundations, including
-unconventional logics such paraconsistent logics, relevance logic,
-multivalued logic with Bayesian inference, situation theory, and the
-Dempster-Shafer theory of belief functions and plausible reasoning,
-which can handle incomplete, evolving, and inconsistent information in
-a controlled and discriminating way. There is also significant IU
-expertise in the design and implementation of programming models, type
-theories, and semantics that encompass both the classical and quantum
-worlds. What IU lacks in expertise is an expert that bridges the
-programming models with actual quantum algorithms: this is a new breed
-of theoreticians with a strong background in both physics, complexity
-theory, and cryptography.
-
-Our initial results in that domain showed how subtle the
-issues can be~\cite{usat,geometry2013,DQT2014}: a straightforward
-replacement of the complex numbers by a finite field yields a variant
-of quantum mechanics in which computationally hard problems like
-UNIQUE-SAT (which decides whether a given Boolean formula is
-unsatisfiable or has exactly one satisfying assignment) can be
-deterministically solved in constant time. To eliminate such
-unrealistic theories requires delicate analysis of the structure of
-the Hilbert space, the process of observation, and the notion of
-probability teasing apart their reliance on the infinitely precise
-real numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is
-to shift focus from the infinitely-specified but not directly
-observable quantum states, to observable measurable properties of
-quantum systems and their probabilities. Furthermore, we insist that
-our theories of measurement and probability only refer to finitely
-communicable evidence within feasible computational bounds. It follows
-that states, observations, and probabilities all become ``fuzzy'',
-i.e., specified by intervals of confidence that can only increase in
-precision if the available resources increase proportionally. Our
-notion of ``fuzzy quantum mechanics'' is related to existing
-work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
-but, as will be explained in more detail, is distinguished by its
-unique computational character.
-
-We will begin by reviewing existing work that recasts classical
-probability spaces in a resource-aware setting and move to our
-proposal which, briefly speaking, aims at recasting quantum
-probability and hence quantum measurement to a corresponding
-resource-aware setting.
-
-In particular, the objectives to be achieved include:
-\begin{itemize}
-\item A computational framework for quantum measurement where quantum
-  systems are described in terms of interactive processes. The
-  framework takes care of the resources required (including the ones
-  related to the observer) to determine a given property of the
-  measured system.
-\item Develop a measurement framework based on quantum interval-valued
-  probabilities measures.
-\item Assess the validity of fundamental theorems of quantum
-  mechanics, such as Gleason, Bell, and Kochen-Specker, in a quantum
-  formulation stripped away of infinite resources. We will aim to
-  provide a definite answer to the Meyer-Mermin
-  debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004} on
-  the impact of finite precision measurements on the relevance of the
-  Kochen-Specker
-  theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
-\item Study the computational complexity of quantum theories and
-  simulations based on discrete (computable) fields.
-\item Study the problem of finding a complete set of mutually unbiased
-  bases
-  (SIC-POVM)~\cite{1751-8121-45-8-085306,1751-8121-47-33-335302,Caves2002}
-  over finite Galois fields.
-\end{itemize}
-We argue that no matter what the results are their impact will be
-strong. Positive results that formulate a computable, with clear
-resource bounds, theory of quantum measurement and quantum probability
-would be essential for understanding and realizing quantum
-computation. Any negative results would redirect research that aims at
-realizing quantum computation to other approaches. At an intellectual
-level, the results have the potential to solve or clarify several
-paradoxes in quantum mechanics, quantum information, computability,
-complexity theory, and perhaps quantum gravity.
-
-For centuries, the mathematical formalization of physical processes
-has been founded on the infinitely precise real or complex
-numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
-For example, almost every description of quantum mechanics, quantum
-computation, or quantum experiments refers to entities such as $\rme$,
-$\pi$, $\sqrt{2}$, etc (see, e.g.,
-\cite{Redhead1987-REDINA,544199,Mermin2007}).  Whether these models
-based on real numbers faithfully describe the nature or just an
-approximation is still an open question. If they are faithful, how the
-nature store and compute these real numbers to produce our
-experimental results would be the next natural question.  There are at
-least three possibilities:
-\begin{itemize}
-\item For any computable number~\cite{Turing_1937}, the nature only store
-the code of the Turing machine which computes the given number, and
-manipulate these codes directly during the computation~\cite{Ziegler2007,weihrauch2012computable}.
-\item The nature stores real numbers on infinitely long Turing machine tapes,
-and handle these numbers by a Turing machine~\cite{Ziegler2007,weihrauch2012computable}.
-In another word, the nature stores real numbers as a whole, but compute
-them piecewisely.
-\item The nature stores and computes real numbers as a whole~\cite{Ziegler2007,blum2012complexity}.
-\end{itemize}
-All these possibilities are not very desirable because they suggest
-the nature might have more computational power than a Turing machine.
-On one hand, if the nature only stores computable numbers by their
-Turing machine codes, the nature might be able to decide whether two
-Turing machines output exactly the same numbers, since this is used
-to decide whether an observable is degenerated or not. However, testing
-whether two Turing machines are output-equivalent is undecidable by
-Rice's theorem~\cite{Rice_1953,Ziegler2007,weihrauch2012computable},
-i.e., the nature has more computational power than a Turing machine.
-On the other hand, if the nature stores real numbers as a whole, any
-particular real number could serve as an oracle and give the nature
-more computational power than a Turing machine. For example, maybe
-the mass of the electron in some representation is the halting oracle
-for some representation of Turing machines. Then, we could solve the
-halting problem by just measuring the mass of the electron. This kind
-of possibility has been online discussed by Peter Shor and others~\cite{PhysicsStackExchange16889}.
-
-Since all possibilities that quantum theory is faithful are not very
-desirable, maybe every description of quantum theory is just an approximation.
-In this case, there is the other possibility:
-\begin{itemize}
-\item The real and complex numbers only exist in our model. The nature is
-essentially discrete, and could be simulated by a Turing machine.
-\end{itemize}
-We have followed this approach to study quantum theory over discrete
-finite fields~\cite{usat,geometry2013,DQT2014}. This yields a variant
-of quantum mechanics in which computationally hard problems like UNIQUE-SAT
-(which decides whether a given Boolean formula is unsatisfiable or
-has exactly one satisfying assignment~\cite{Valiant198685,Papadimitriou1993,AroraBarak2009})
-can be deterministically solved in constant time. We then delicate
-analysis of the structure of the Hilbert space, the process of observation,
-and the notion of probability by teasing apart their reliance on the
-infinitely precise real numbers~\cite{geometry2013,DQT2014}.
 
@@
 
+\subsection{Quantum Bayesianism}
+
+Although we discussed how a quantum IVPM could be induced from a real
+quantum state, our investigation leaves an open question of whether
+there exists a ``real'' entity that exists independently of measurements
+and probabilities. Since the frequency interpretation of probability
+is problematic, it is much more sensible to interpret probability
+in the Bayesian sense as ``lack of knowledge''. This, and similar
+arguments elegantly expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+suggest that the quantum state is more like an interactive system
+in computer science parlance. In other words, the state is only determined
+by its interactions with the environment or observers. A rough but
+useful analogy in the context of computer science would be a web server:
+the state of such a system cannot be said to exist independently of
+the interactions with clients; each interaction with a client determines
+a future state of the system and may affect future interactions. Crucially,
+each client may have a \emph{different} view of the web server that
+is consistent with their own history of interactions. This computational
+perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
+that asserts that the quantum state is subjective: each observer has
+a different view of the quantum system that is consistent with their
+previous observations and that allows that observer, independently
+of other observers, to assign beliefs (i.e., probabilities) to possible
+future interactions.
+
+\section{Kick-off Talk: The Reality of the Quantum State}
+
+The meaning of quantum probability
+
+The reality of the quantum state
+
+— next section
+
+The meaning of quantum probability: probability is approximate; intervals;
+Born; no state when approximation is bad.
+
+quantum state: Bayesian perspective; probability is subjective; hence
+state is subjective; given previous results that show that state does
+not exist when you have poor approximations; ?
+
+In contrast to our previous works that assume the current quantum
+theory is just an approximation to the discrete reality, we now assume
+the nature really use real numbers. However, these real numbers could
+not be directly accessed by human who is bounded by finite resources.
+Therefore, even if the nature might have more computational power
+than a Turing machine, human might not be able to acquire and use
+the computational power more than a Turing machine.
+
+In order to model the bounded-resource human observers, we would like
+the theories of measurement and probability replaced by a subjective
+probability model, called the interval-valued probability. The question
+is how quantum mechanics would like with the interval-valued probability.
+
+In particular, based on conventional probability, Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
+suggests that idea to define a state as a density matrix~\cite{Varadarajan2008}.
+Since Gleason's theorem could not directly apply on interval-valued
+probability measures, we would like to ask: How a quantum state looks
+like with the interval-valued probability? When the number and precision
+of the intervals increase, would the quantum interval-valued probability
+measures converge to the quantum probability measure induced by the
+Born rule~\cite{Born1983,Mermin2007,Jaeger2007}?
+
+\section{Kick-off Talk}
+
+In previous work, we examined the Hilbert space mathematical framework
+of quantum mechanics and teased apart its various aspects that directly
+rely on the infinite-precision real or complex numbers. We note two
+remarkable earlier results and an open question: 
+\begin{itemize}
+\item UNIQUE-SAT: Schumacher and
+  Westmoreland~\cite{Schumacher2012-SCHMQT} argue that much of the
+  structure of traditional quantum mechanics is maintained in the
+  presence of finite fields. In particular, they establish that the
+  quantum theory based on the finite field of booleans retains the
+  following characteristics of quantum mechanics: the notions of
+  superposition, interference, entanglement, and mixed states of
+  quantum systems; the time evolution of quantum systems using
+  invertible linear operators; the complementarity of incompatible
+  observables; the exclusion of local hidden variable theories and the
+  impossibility of cloning quantum states; and the presence of natural
+  counterparts of quantum information protocols such as superdense
+  coding and teleportation. However we have argued that this theory is
+  not physically realizable as it allows the solution of
+  computationally difficult problems like
+  UNIQUE-SAT~\cite{Valiant198685} in constant time~\cite{usat}.
+
+\item Deutsch-Jozsa: In a follow-up paper~\cite{DQT2014}, we proposed
+  a variant of quantum mechanics in which the underlying field of
+  complex numbers is replaced by special finite fields with enough
+  structure to model Hermitian products that \emph{locally} behave
+  like inner products. The trick is to recognize that, as the
+  characteristic of the finite field increases, larger and larger
+  regions of the finite field become totally ordered, thereby
+  restoring, with some restrictions, all the usual properties of the
+  inner product needed for conventional quantum mechanics. Using this
+  theory to analyze the Deutsch-Jozsa algorithm reveals that the
+  characteristic of the finite field plays an essential role: as the
+  size of the finite field grows, so does the numerical range of the
+  intermediate and final results of the algorithms being implemented.
+  The theory naturally recovers a deterministic measure of the
+  intrinsic resources required for a given level of complexity; this
+  measure is normally completely hidden in computations with real
+  numbers, and explicitly exposing it is one of the significant
+  achievements of our discrete field analysis of quantum computation.
+  This solves the conundrum that the conventional Deutsch-Jozsa
+  algorithm~\cite{DeutschJozsa1992,Jaeger2007}
+  mysteriously continues to work for larger and larger input
+  functions without any apparent increase in resources.  Our analysis
+  of this problem reveals that as the size of the input increases, it
+  is necessary to increase the size of the finite field and hence the
+  size of the underlying available numeric coefficients.  This
+  observation does not fully explain the power of quantum computing
+  over classical computing, but at least it explains that some of the
+  power of quantum computing depends on increasingly larger precision
+  in the underlying field of numbers.
+
+\item An important special case of a generalized measurement is the
+  symmetric, informationally complete, positive operator valued
+  measure (SIC-POVM), which has applications in quantum
+  cryptography. This problem has been formulated in the context of
+  standard quantum theory where fields are complex numbers.  Although
+  a rigorous proof for the existence of SIC-POVMs for arbitrary
+  Hilbert space dimensions is still missing, it would be illuminating
+  to look for a formulation of the same problem in a discrete quantum
+  theory defined in terms of finite Galois fields.
+\end{itemize}
+
+A long term, ultimate, goal of this research proposal would be to
+combine the various pieces into a coherent computational model of
+quantum mechanics that keeps explicit track of resources needed to
+represent the interactive system representing the quantum state, its
+evolution, the observables, and the probabilities. Such a
+computational model of quantum mechanics would encompass classical
+(reversible) computation and potentially revolutionize quantum
+thinking with finite resources. The explicit manipulation of resources
+enables one of key idea that emerged in our previous work: the
+resources used to represent the quantum system are in principle
+unrelated to the resources available to the various observers. We
+conjecture that this asymmetry may prove key to resolving some of the
+quantum paradoxes.  The nature of quantum mechanics realized in terms
+of discrete fields and finitely-communicable probability estimates is
+amenable to direct computational exploration for reasonable field
+sizes and observational accuracy. We have established a set of utility
+libraries in Mathematica that supports a wide variety of such
+numerical experiments. Concurrently to this effort, we are also
+building on our previous work~\cite
+{VDS2009,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
+to build semantically well-founded implementations of the
+computational models investigated in this proposal.
+
+\paragraph*{Research Questions.} The aim of these implementations
+include:
+\begin{itemize}
+\item Provide an experimental testbed to simulate physical phenomena
+  (e.g.~\cite {OrtizEtAl2001,SommEtAl2002}) that complements the
+  Mathematica libraries in which quantum algorithms can be simulated;
+\item Establish connections between quantum programming concepts and
+  classical programming concepts. We plan to make our software
+  available for educational and research purposes; and 
+\item Analyze the computational complexity of quantum theories and
+  simulations based on discrete fields. What other (apart from
+  UNIQUE-SAT) supernatural algorithms can be implemented in
+  computational models based on discrete fields?
+\item Determine, through numerical computations, solutions for
+  SIC-POVM for small vector space dimensions.
+\end{itemize}
+
+propose to revisit quantum mechanics, quantum information, quantum
+computation, and the foundations of physics from this resource-aware
+perspective.
+
+Soon after the discovery of quantum effects in the early 1900s, it
+became evident that the quantum world requires a fresh worldview, not
+merely an extension of the repertoire of entities and constructions
+which explain classical physics. In the past thirty years, however,
+the first quantum revolution mostly relied on just that: extensions of
+classical logics, classical models of computation, and classical
+analysis of algorithms. Fundamentally, the foundations of logic and
+computing still embrace, to a large extent, the notion that the truth
+of a statement is ``absolute'' and independent of any reasoning,
+understanding, or action, i.e., logical statements are viewed as
+abstract entities for which it makes no sense to talk about
+entanglement with an observer: their truth or falsity is absolute and
+does not depend on the notion of observation. This absolute view of
+truth and the use of classical logic for reasoning about this absolute
+truth have both been critiqued for centuries by philosophers and other
+scientists but it is the advent of quantum science that really
+devastates this worldview of classical determinism. Indeed, quantum
+science suggests that the properties of physical systems can only be
+learned by observers interacting with the system, and that this
+interaction may entangle the observer with the system and disturb the
+properties of interest. This suggests that the possibility structure
+of our universe is not a fixed, Boolean structure, as we supposed
+classically, but is in fact a non-Boolean structure that changes
+dynamically~\cite{bub2006}.
+
+We believe that the foundations of physics should be revisited from a
+logical and computational approach
+
+More directly, world-renowned logician Girard states:
+Our vision for this revised computational and logic theory builds upon
+programming abstractions which assume evolving, incomplete, and
+inconsistent data, and principles for reasoning about programs which
+are based on finitely communicable evidence between subsystems or
+systems and observers, rather than absolute truth. The most natural
+way to achieve this shift in our ``computational thinking'' and to
+consolidate many of the new promising trends in computational,
+informational, and logical theory is to design new programming
+models. For it is indeed a widely accepted thesis that programming
+languages shape thought processes and design
+solutions~\cite{iverson80,johansen-berg01}. Our approach therefore is
+to develop new programming models based on both logical foundations
+and pragmatic considerations, to connect them to current
+computational, informational, and logical theory, and to make
+compelling arguments for the models by using them to write several
+novel and challenging applications.
+
+There is significant IU expertise in logic foundations, including
+unconventional logics such paraconsistent logics, relevance logic,
+multivalued logic with Bayesian inference, situation theory, and the
+Dempster-Shafer theory of belief functions and plausible reasoning,
+which can handle incomplete, evolving, and inconsistent information in
+a controlled and discriminating way. There is also significant IU
+expertise in the design and implementation of programming models, type
+theories, and semantics that encompass both the classical and quantum
+worlds. What IU lacks in expertise is an expert that bridges the
+programming models with actual quantum algorithms: this is a new breed
+of theoreticians with a strong background in both physics, complexity
+theory, and cryptography.
+
+Our initial results in that domain showed how subtle the
+issues can be~\cite{usat,geometry2013,DQT2014}: a straightforward
+replacement of the complex numbers by a finite field yields a variant
+of quantum mechanics in which computationally hard problems like
+UNIQUE-SAT (which decides whether a given Boolean formula is
+unsatisfiable or has exactly one satisfying assignment) can be
+deterministically solved in constant time. To eliminate such
+unrealistic theories requires delicate analysis of the structure of
+the Hilbert space, the process of observation, and the notion of
+probability teasing apart their reliance on the infinitely precise
+real numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is
+to shift focus from the infinitely-specified but not directly
+observable quantum states, to observable measurable properties of
+quantum systems and their probabilities. Furthermore, we insist that
+our theories of measurement and probability only refer to finitely
+communicable evidence within feasible computational bounds. It follows
+that states, observations, and probabilities all become ``fuzzy'',
+i.e., specified by intervals of confidence that can only increase in
+precision if the available resources increase proportionally. Our
+notion of ``fuzzy quantum mechanics'' is related to existing
+work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
+but, as will be explained in more detail, is distinguished by its
+unique computational character.
+
+We will begin by reviewing existing work that recasts classical
+probability spaces in a resource-aware setting and move to our
+proposal which, briefly speaking, aims at recasting quantum
+probability and hence quantum measurement to a corresponding
+resource-aware setting.
+
+In particular, the objectives to be achieved include:
+\begin{itemize}
+\item A computational framework for quantum measurement where quantum
+  systems are described in terms of interactive processes. The
+  framework takes care of the resources required (including the ones
+  related to the observer) to determine a given property of the
+  measured system.
+\item Develop a measurement framework based on quantum interval-valued
+  probabilities measures.
+\item Assess the validity of fundamental theorems of quantum
+  mechanics, such as Gleason, Bell, and Kochen-Specker, in a quantum
+  formulation stripped away of infinite resources. We will aim to
+  provide a definite answer to the Meyer-Mermin
+  debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004} on
+  the impact of finite precision measurements on the relevance of the
+  Kochen-Specker
+  theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
+\item Study the computational complexity of quantum theories and
+  simulations based on discrete (computable) fields.
+\item Study the problem of finding a complete set of mutually unbiased
+  bases
+  (SIC-POVM)~\cite{1751-8121-45-8-085306,1751-8121-47-33-335302,Caves2002}
+  over finite Galois fields.
+\end{itemize}
+We argue that no matter what the results are their impact will be
+strong. Positive results that formulate a computable, with clear
+resource bounds, theory of quantum measurement and quantum probability
+would be essential for understanding and realizing quantum
+computation. Any negative results would redirect research that aims at
+realizing quantum computation to other approaches. At an intellectual
+level, the results have the potential to solve or clarify several
+paradoxes in quantum mechanics, quantum information, computability,
+complexity theory, and perhaps quantum gravity.
+
+For centuries, the mathematical formalization of physical processes
+has been founded on the infinitely precise real or complex
+numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
+For example, almost every description of quantum mechanics, quantum
+computation, or quantum experiments refers to entities such as $\rme$,
+$\pi$, $\sqrt{2}$, etc (see, e.g.,
+\cite{Redhead1987-REDINA,544199,Mermin2007}).  Whether these models
+based on real numbers faithfully describe the nature or just an
+approximation is still an open question. If they are faithful, how the
+nature store and compute these real numbers to produce our
+experimental results would be the next natural question.  There are at
+least three possibilities:
+\begin{itemize}
+\item For any computable number~\cite{Turing_1937}, the nature only store
+the code of the Turing machine which computes the given number, and
+manipulate these codes directly during the computation~\cite{Ziegler2007,weihrauch2012computable}.
+\item The nature stores real numbers on infinitely long Turing machine tapes,
+and handle these numbers by a Turing machine~\cite{Ziegler2007,weihrauch2012computable}.
+In another word, the nature stores real numbers as a whole, but compute
+them piecewisely.
+\item The nature stores and computes real numbers as a whole~\cite{Ziegler2007,blum2012complexity}.
+\end{itemize}
+All these possibilities are not very desirable because they suggest
+the nature might have more computational power than a Turing machine.
+On one hand, if the nature only stores computable numbers by their
+Turing machine codes, the nature might be able to decide whether two
+Turing machines output exactly the same numbers, since this is used
+to decide whether an observable is degenerated or not. However, testing
+whether two Turing machines are output-equivalent is undecidable by
+Rice's theorem~\cite{Rice_1953,Ziegler2007,weihrauch2012computable},
+i.e., the nature has more computational power than a Turing machine.
+On the other hand, if the nature stores real numbers as a whole, any
+particular real number could serve as an oracle and give the nature
+more computational power than a Turing machine. For example, maybe
+the mass of the electron in some representation is the halting oracle
+for some representation of Turing machines. Then, we could solve the
+halting problem by just measuring the mass of the electron. This kind
+of possibility has been online discussed by Peter Shor and others~\cite{PhysicsStackExchange16889}.
+
+Since all possibilities that quantum theory is faithful are not very
+desirable, maybe every description of quantum theory is just an approximation.
+In this case, there is the other possibility:
+\begin{itemize}
+\item The real and complex numbers only exist in our model. The nature is
+essentially discrete, and could be simulated by a Turing machine.
+\end{itemize}
+We have followed this approach to study quantum theory over discrete
+finite fields~\cite{usat,geometry2013,DQT2014}. This yields a variant
+of quantum mechanics in which computationally hard problems like UNIQUE-SAT
+(which decides whether a given Boolean formula is unsatisfiable or
+has exactly one satisfying assignment~\cite{Valiant198685,Papadimitriou1993,AroraBarak2009})
+can be deterministically solved in constant time. We then delicate
+analysis of the structure of the Hilbert space, the process of observation,
+and the notion of probability by teasing apart their reliance on the
+infinitely precise real numbers~\cite{geometry2013,DQT2014}.
+
 \section{About Myself}

### 2017-01-14 Rethinking Foundations of Physics 2017/application.tex
application.tex \subsection{Discussion} Added, and cleaned up...

@@
 immense practical relevance in the context of quantum computing. The
-question, which we could largely bypass in the classical case, is
-whether there is, in the background of all the measurements and probabilities,
-a ``real'' infinitely-precise quantum state that is being approximated
-and that, in principle, can be more and more accurately described
-given more and more resources.
+question is whether there is a ``real'' infinitely-precise quantum
+state that is being approximated and that can be more and more accurately
+described given more and more resources.
 
@@
 
-\subsection{Quantum Bayesianism}
+\subsection{Discussion}
 
-Although we discussed how a quantum IVPM could be induced from a real
-quantum state, our investigation leaves an open question of whether
-there exists a ``real'' entity that exists independently of measurements
-and probabilities. Since the frequency interpretation of probability
-is problematic, it is much more sensible to interpret probability
-in the Bayesian sense as ``lack of knowledge''. This, and similar
-arguments elegantly expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
-suggest that the quantum state is more like an interactive system
+Although a family of more and more precise quantum IVPMs might be
+induced from a real quantum state, given a particular quantum IVPM,
+i.e., using a particular measurement apparatus, our investigation
+leaves an open question of whether behind it there exists a ``real''
+state. There are several possibilities.
+
+One possibility is to trace back the original definition of a quantum
+state. A quantum state could be formulated as a density matrix in
+von Neumann's formalism~\cite{vonNeumann1955,Varadarajan2008}. Later,
+Mackey defined a quantum state as additive probability measure as
+we did in definition~\ref{def:QuantumProbabilitySpace}~\cite{inun.606849520040101,Varadarajan2008}.
+Although Gleason proved Mackey states are von Neumann states in dimension
+$\ge3$, it might not have to be when we generalized Mackey states
+to quantum IVPMs, and maybe we should use quantum IVPMs as the most
+primitive definition of states.
+
+The other possibility focus on the meaning of the probability. Since
+a quantum IVPM cannot be defined without consider a particular measurement
+apparatus, and the information extracted from this apparatus, the
+interval-valued probability itself could be considered subjective,
+and could be interpreted in the Bayesian sense as ``lack of knowledge''.
+This, and similar arguments elegantly expressed by recent work on
+Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which
+suggests that the quantum state is more like an interactive system
 in computer science parlance. In other words, the state is only determined
@@
 future interactions.
-
-\section{Kick-off Talk: The Reality of the Quantum State}
-
-The meaning of quantum probability
-
-The reality of the quantum state
-
-— next section
-
-The meaning of quantum probability: probability is approximate; intervals;
-Born; no state when approximation is bad.
-
-quantum state: Bayesian perspective; probability is subjective; hence
-state is subjective; given previous results that show that state does
-not exist when you have poor approximations; ?
-
-In contrast to our previous works that assume the current quantum
-theory is just an approximation to the discrete reality, we now assume
-the nature really use real numbers. However, these real numbers could
-not be directly accessed by human who is bounded by finite resources.
-Therefore, even if the nature might have more computational power
-than a Turing machine, human might not be able to acquire and use
-the computational power more than a Turing machine.
-
-In order to model the bounded-resource human observers, we would like
-the theories of measurement and probability replaced by a subjective
-probability model, called the interval-valued probability. The question
-is how quantum mechanics would like with the interval-valued probability.
-
-In particular, based on conventional probability, Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
-suggests that idea to define a state as a density matrix~\cite{Varadarajan2008}.
-Since Gleason's theorem could not directly apply on interval-valued
-probability measures, we would like to ask: How a quantum state looks
-like with the interval-valued probability? When the number and precision
-of the intervals increase, would the quantum interval-valued probability
-measures converge to the quantum probability measure induced by the
-Born rule~\cite{Born1983,Mermin2007,Jaeger2007}?
-
-\section{Kick-off Talk}
-
-In previous work, we examined the Hilbert space mathematical framework
-of quantum mechanics and teased apart its various aspects that directly
-rely on the infinite-precision real or complex numbers. We note two
-remarkable earlier results and an open question: 
-\begin{itemize}
-\item UNIQUE-SAT: Schumacher and
-  Westmoreland~\cite{Schumacher2012-SCHMQT} argue that much of the
-  structure of traditional quantum mechanics is maintained in the
-  presence of finite fields. In particular, they establish that the
-  quantum theory based on the finite field of booleans retains the
-  following characteristics of quantum mechanics: the notions of
-  superposition, interference, entanglement, and mixed states of
-  quantum systems; the time evolution of quantum systems using
-  invertible linear operators; the complementarity of incompatible
-  observables; the exclusion of local hidden variable theories and the
-  impossibility of cloning quantum states; and the presence of natural
-  counterparts of quantum information protocols such as superdense
-  coding and teleportation. However we have argued that this theory is
-  not physically realizable as it allows the solution of
-  computationally difficult problems like
-  UNIQUE-SAT~\cite{Valiant198685} in constant time~\cite{usat}.
-
-\item Deutsch-Jozsa: In a follow-up paper~\cite{DQT2014}, we proposed
-  a variant of quantum mechanics in which the underlying field of
-  complex numbers is replaced by special finite fields with enough
-  structure to model Hermitian products that \emph{locally} behave
-  like inner products. The trick is to recognize that, as the
-  characteristic of the finite field increases, larger and larger
-  regions of the finite field become totally ordered, thereby
-  restoring, with some restrictions, all the usual properties of the
-  inner product needed for conventional quantum mechanics. Using this
-  theory to analyze the Deutsch-Jozsa algorithm reveals that the
-  characteristic of the finite field plays an essential role: as the
-  size of the finite field grows, so does the numerical range of the
-  intermediate and final results of the algorithms being implemented.
-  The theory naturally recovers a deterministic measure of the
-  intrinsic resources required for a given level of complexity; this
-  measure is normally completely hidden in computations with real
-  numbers, and explicitly exposing it is one of the significant
-  achievements of our discrete field analysis of quantum computation.
-  This solves the conundrum that the conventional Deutsch-Jozsa
-  algorithm~\cite{DeutschJozsa1992,Jaeger2007}
-  mysteriously continues to work for larger and larger input
-  functions without any apparent increase in resources.  Our analysis
-  of this problem reveals that as the size of the input increases, it
-  is necessary to increase the size of the finite field and hence the
-  size of the underlying available numeric coefficients.  This
-  observation does not fully explain the power of quantum computing
-  over classical computing, but at least it explains that some of the
-  power of quantum computing depends on increasingly larger precision
-  in the underlying field of numbers.
-
-\item An important special case of a generalized measurement is the
-  symmetric, informationally complete, positive operator valued
-  measure (SIC-POVM), which has applications in quantum
-  cryptography. This problem has been formulated in the context of
-  standard quantum theory where fields are complex numbers.  Although
-  a rigorous proof for the existence of SIC-POVMs for arbitrary
-  Hilbert space dimensions is still missing, it would be illuminating
-  to look for a formulation of the same problem in a discrete quantum
-  theory defined in terms of finite Galois fields.
-\end{itemize}
-
-A long term, ultimate, goal of this research proposal would be to
-combine the various pieces into a coherent computational model of
-quantum mechanics that keeps explicit track of resources needed to
-represent the interactive system representing the quantum state, its
-evolution, the observables, and the probabilities. Such a
-computational model of quantum mechanics would encompass classical
-(reversible) computation and potentially revolutionize quantum
-thinking with finite resources. The explicit manipulation of resources
-enables one of key idea that emerged in our previous work: the
-resources used to represent the quantum system are in principle
-unrelated to the resources available to the various observers. We
-conjecture that this asymmetry may prove key to resolving some of the
-quantum paradoxes.  The nature of quantum mechanics realized in terms
-of discrete fields and finitely-communicable probability estimates is
-amenable to direct computational exploration for reasonable field
-sizes and observational accuracy. We have established a set of utility
-libraries in Mathematica that supports a wide variety of such
-numerical experiments. Concurrently to this effort, we are also
-building on our previous work~\cite
-{VDS2009,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
-to build semantically well-founded implementations of the
-computational models investigated in this proposal.
-
-\paragraph*{Research Questions.} The aim of these implementations
-include:
-\begin{itemize}
-\item Provide an experimental testbed to simulate physical phenomena
-  (e.g.~\cite {OrtizEtAl2001,SommEtAl2002}) that complements the
-  Mathematica libraries in which quantum algorithms can be simulated;
-\item Establish connections between quantum programming concepts and
-  classical programming concepts. We plan to make our software
-  available for educational and research purposes; and 
-\item Analyze the computational complexity of quantum theories and
-  simulations based on discrete fields. What other (apart from
-  UNIQUE-SAT) supernatural algorithms can be implemented in
-  computational models based on discrete fields?
-\item Determine, through numerical computations, solutions for
-  SIC-POVM for small vector space dimensions.
-\end{itemize}
-
-propose to revisit quantum mechanics, quantum information, quantum
-computation, and the foundations of physics from this resource-aware
-perspective.
-
-Soon after the discovery of quantum effects in the early 1900s, it
-became evident that the quantum world requires a fresh worldview, not
-merely an extension of the repertoire of entities and constructions
-which explain classical physics. In the past thirty years, however,
-the first quantum revolution mostly relied on just that: extensions of
-classical logics, classical models of computation, and classical
-analysis of algorithms. Fundamentally, the foundations of logic and
-computing still embrace, to a large extent, the notion that the truth
-of a statement is ``absolute'' and independent of any reasoning,
-understanding, or action, i.e., logical statements are viewed as
-abstract entities for which it makes no sense to talk about
-entanglement with an observer: their truth or falsity is absolute and
-does not depend on the notion of observation. This absolute view of
-truth and the use of classical logic for reasoning about this absolute
-truth have both been critiqued for centuries by philosophers and other
-scientists but it is the advent of quantum science that really
-devastates this worldview of classical determinism. Indeed, quantum
-science suggests that the properties of physical systems can only be
-learned by observers interacting with the system, and that this
-interaction may entangle the observer with the system and disturb the
-properties of interest. This suggests that the possibility structure
-of our universe is not a fixed, Boolean structure, as we supposed
-classically, but is in fact a non-Boolean structure that changes
-dynamically~\cite{bub2006}.
-
-We believe that the foundations of physics should be revisited from a
-logical and computational approach
-
-More directly, world-renowned logician Girard states:
-Our vision for this revised computational and logic theory builds upon
-programming abstractions which assume evolving, incomplete, and
-inconsistent data, and principles for reasoning about programs which
-are based on finitely communicable evidence between subsystems or
-systems and observers, rather than absolute truth. The most natural
-way to achieve this shift in our ``computational thinking'' and to
-consolidate many of the new promising trends in computational,
-informational, and logical theory is to design new programming
-models. For it is indeed a widely accepted thesis that programming
-languages shape thought processes and design
-solutions~\cite{iverson80,johansen-berg01}. Our approach therefore is
-to develop new programming models based on both logical foundations
-and pragmatic considerations, to connect them to current
-computational, informational, and logical theory, and to make
-compelling arguments for the models by using them to write several
-novel and challenging applications.
-
-There is significant IU expertise in logic foundations, including
-unconventional logics such paraconsistent logics, relevance logic,
-multivalued logic with Bayesian inference, situation theory, and the
-Dempster-Shafer theory of belief functions and plausible reasoning,
-which can handle incomplete, evolving, and inconsistent information in
-a controlled and discriminating way. There is also significant IU
-expertise in the design and implementation of programming models, type
-theories, and semantics that encompass both the classical and quantum
-worlds. What IU lacks in expertise is an expert that bridges the
-programming models with actual quantum algorithms: this is a new breed
-of theoreticians with a strong background in both physics, complexity
-theory, and cryptography.
-
-Our initial results in that domain showed how subtle the
-issues can be~\cite{usat,geometry2013,DQT2014}: a straightforward
-replacement of the complex numbers by a finite field yields a variant
-of quantum mechanics in which computationally hard problems like
-UNIQUE-SAT (which decides whether a given Boolean formula is
-unsatisfiable or has exactly one satisfying assignment) can be
-deterministically solved in constant time. To eliminate such
-unrealistic theories requires delicate analysis of the structure of
-the Hilbert space, the process of observation, and the notion of
-probability teasing apart their reliance on the infinitely precise
-real numbers~\cite{geometry2013,DQT2014}. In this proposal, our aim is
-to shift focus from the infinitely-specified but not directly
-observable quantum states, to observable measurable properties of
-quantum systems and their probabilities. Furthermore, we insist that
-our theories of measurement and probability only refer to finitely
-communicable evidence within feasible computational bounds. It follows
-that states, observations, and probabilities all become ``fuzzy'',
-i.e., specified by intervals of confidence that can only increase in
-precision if the available resources increase proportionally. Our
-notion of ``fuzzy quantum mechanics'' is related to existing
-work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
-but, as will be explained in more detail, is distinguished by its
-unique computational character.
-
-We will begin by reviewing existing work that recasts classical
-probability spaces in a resource-aware setting and move to our
-proposal which, briefly speaking, aims at recasting quantum
-probability and hence quantum measurement to a corresponding
-resource-aware setting.
-
-In particular, the objectives to be achieved include:
-\begin{itemize}
-\item A computational framework for quantum measurement where quantum
-  systems are described in terms of interactive processes. The
-  framework takes care of the resources required (including the ones
-  related to the observer) to determine a given property of the
-  measured system.
-\item Develop a measurement framework based on quantum interval-valued
-  probabilities measures.
-\item Assess the validity of fundamental theorems of quantum
-  mechanics, such as Gleason, Bell, and Kochen-Specker, in a quantum
-  formulation stripped away of infinite resources. We will aim to
-  provide a definite answer to the Meyer-Mermin
-  debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004} on
-  the impact of finite precision measurements on the relevance of the
-  Kochen-Specker
-  theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
-\item Study the computational complexity of quantum theories and
-  simulations based on discrete (computable) fields.
-\item Study the problem of finding a complete set of mutually unbiased
-  bases
-  (SIC-POVM)~\cite{1751-8121-45-8-085306,1751-8121-47-33-335302,Caves2002}
-  over finite Galois fields.
-\end{itemize}
-We argue that no matter what the results are their impact will be
-strong. Positive results that formulate a computable, with clear
-resource bounds, theory of quantum measurement and quantum probability
-would be essential for understanding and realizing quantum
-computation. Any negative results would redirect research that aims at
-realizing quantum computation to other approaches. At an intellectual
-level, the results have the potential to solve or clarify several
-paradoxes in quantum mechanics, quantum information, computability,
-complexity theory, and perhaps quantum gravity.
-
-For centuries, the mathematical formalization of physical processes
-has been founded on the infinitely precise real or complex
-numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
-For example, almost every description of quantum mechanics, quantum
-computation, or quantum experiments refers to entities such as $\rme$,
-$\pi$, $\sqrt{2}$, etc (see, e.g.,
-\cite{Redhead1987-REDINA,544199,Mermin2007}).  Whether these models
-based on real numbers faithfully describe the nature or just an
-approximation is still an open question. If they are faithful, how the
-nature store and compute these real numbers to produce our
-experimental results would be the next natural question.  There are at
-least three possibilities:
-\begin{itemize}
-\item For any computable number~\cite{Turing_1937}, the nature only store
-the code of the Turing machine which computes the given number, and
-manipulate these codes directly during the computation~\cite{Ziegler2007,weihrauch2012computable}.
-\item The nature stores real numbers on infinitely long Turing machine tapes,
-and handle these numbers by a Turing machine~\cite{Ziegler2007,weihrauch2012computable}.
-In another word, the nature stores real numbers as a whole, but compute
-them piecewisely.
-\item The nature stores and computes real numbers as a whole~\cite{Ziegler2007,blum2012complexity}.
-\end{itemize}
-All these possibilities are not very desirable because they suggest
-the nature might have more computational power than a Turing machine.
-On one hand, if the nature only stores computable numbers by their
-Turing machine codes, the nature might be able to decide whether two
-Turing machines output exactly the same numbers, since this is used
-to decide whether an observable is degenerated or not. However, testing
-whether two Turing machines are output-equivalent is undecidable by
-Rice's theorem~\cite{Rice_1953,Ziegler2007,weihrauch2012computable},
-i.e., the nature has more computational power than a Turing machine.
-On the other hand, if the nature stores real numbers as a whole, any
-particular real number could serve as an oracle and give the nature
-more computational power than a Turing machine. For example, maybe
-the mass of the electron in some representation is the halting oracle
-for some representation of Turing machines. Then, we could solve the
-halting problem by just measuring the mass of the electron. This kind
-of possibility has been online discussed by Peter Shor and others~\cite{PhysicsStackExchange16889}.
-
-Since all possibilities that quantum theory is faithful are not very
-desirable, maybe every description of quantum theory is just an approximation.
-In this case, there is the other possibility:
-\begin{itemize}
-\item The real and complex numbers only exist in our model. The nature is
-essentially discrete, and could be simulated by a Turing machine.
-\end{itemize}
-We have followed this approach to study quantum theory over discrete
-finite fields~\cite{usat,geometry2013,DQT2014}. This yields a variant
-of quantum mechanics in which computationally hard problems like UNIQUE-SAT
-(which decides whether a given Boolean formula is unsatisfiable or
-has exactly one satisfying assignment~\cite{Valiant198685,Papadimitriou1993,AroraBarak2009})
-can be deterministically solved in constant time. We then delicate
-analysis of the structure of the Hilbert space, the process of observation,
-and the notion of probability by teasing apart their reliance on the
-infinitely precise real numbers~\cite{geometry2013,DQT2014}.
 

### 2017-01-15 Rethinking Foundations of Physics 2017/application.tex
application.tex \section{Proposed Question} Start updating...

@@
 
-If we insist that probabilities cannot be computed to infinite precision
-and are bound to be approximations represented by intervals of confidence,
-then quantum states themselves can only be discussed within intervals
-of confidence. This raises an important philosophical question with
-immense practical relevance in the context of quantum computing. The
-question is whether there is a ``real'' infinitely-precise quantum
-state that is being approximated and that can be more and more accurately
+Quantum machines is a theory of probability, which is computed by
+the Born rule~\cite{Born1983,Mermin2007,Jaeger2007} and is used
+to be considered infinite precise and objective. If we changed the
+quantum probability to a subjective probability model, which is bound
+to be approximations represented by intervals of confidence, then
+
+quantum states themselves can only be discussed within intervals of
+confidence. This raises an important philosophical question with immense
+practical relevance in the context of quantum computing. The question
+is whether there is a ``real'' infinitely-precise quantum state
+that is being approximated and that can be more and more accurately
 described given more and more resources.

### 2017-01-15 Rethinking Foundations of Physics 2017/application.tex
application.tex Updating...

--- 2017-01-14 Rethinking Foundations of Physics 2017/application.tex
@@
 
-If we insist that probabilities cannot be computed to infinite precision
-and are bound to be approximations represented by intervals of confidence,
-then quantum states themselves can only be discussed within intervals
-of confidence. This raises an important philosophical question with
-immense practical relevance in the context of quantum computing. The
-question is whether there is a ``real'' infinitely-precise quantum
+Quantum machines is a theory of probability, which is computed by
+the Born rule~\cite{Born1983,Mermin2007,Jaeger2007} and is used
+to be considered as infinite precise and objective. If we insist that
+probabilities cannot be computed to infinite precision, we should
+change the quantum probability to a subjective probability model,
+which is bound to be approximations represented by intervals of confidence.
+Following this idea, quantum states themselves can only be discussed
+within intervals of confidence. This raises an important philosophical
+question, whether there is a ``real'' infinitely-precise quantum
 state that is being approximated and that can be more and more accurately
 described given more and more resources.
+
+Mathematically, this idea might require us to reformulate the very
+definition of a quantum state. A quantum state could be defined as
+a density matrix in von Neumann's formalism~\cite{vonNeumann1955,Varadarajan2008}.
+Later, Mackey defined a quantum state as additive probability measure
+as we did in definition~\ref{def:QuantumProbabilitySpace}~\cite{inun.606849520040101,Varadarajan2008}.
+Although Gleason proved Mackey states are von Neumann states in dimension
+$\ge3$, when we generalized Mackey states to quantum interval-valued
+probability measures (IVPM), a quantum IVPM may not correspond to
+any density matrix as in example~\ref{ex:three-dimensional-three-value}
+and \ref{ex:three-dimensional-4-value}. In this situation, we could
+consider quantum IVPMs as the most primitive definition of quantum
+states to reconstruct the whole quantum machines. Or we might follow
+the idea of Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}
+to formulate a quantum state as an interactive system in computer
+science parlance.
 
@@
 leaves an open question of whether behind it there exists a ``real''
-state. There are several possibilities.
-
-One possibility is to trace back the original definition of a quantum
-state. A quantum state could be formulated as a density matrix in
-von Neumann's formalism~\cite{vonNeumann1955,Varadarajan2008}. Later,
-Mackey defined a quantum state as additive probability measure as
-we did in definition~\ref{def:QuantumProbabilitySpace}~\cite{inun.606849520040101,Varadarajan2008}.
-Although Gleason proved Mackey states are von Neumann states in dimension
-$\ge3$, it might not have to be when we generalized Mackey states
-to quantum IVPMs, and maybe we should use quantum IVPMs as the most
-primitive definition of states.
-
-The other possibility focus on the meaning of the probability. Since
-a quantum IVPM cannot be defined without consider a particular measurement
-apparatus, and the information extracted from this apparatus, the
-interval-valued probability itself could be considered subjective,
+state. Despite the possibility to use quantum IVPMs as the most primitive
+definition of states, we might focus on the meaning of the probability.
+Since a quantum IVPM cannot be defined without consider a particular
+measurement apparatus, and the information extracted from this apparatus,
+the interval-valued probability itself could be considered subjective,
 and could be interpreted in the Bayesian sense as ``lack of knowledge''.

### 2017-01-16 Rethinking Foundations of Physics 2017/application.tex
application.tex Updated...

@@
 
-It is unlikely that there will be a simple a resolution to this
+It is unlikely that there will be a simple resolution to this
 awkward situation. It is more likely that the resolution will emerge
@@
 In particular, we develop a measurement framework based on quantum
-interval-valued probability measures~(IVPM). Surprisingly, we found
-a quantum IVPM which can not be induced by a state, while Shapley
-proved a classical convex IVPM can always be induced by a classical
-``state''~\cite{Shapley1971,Grabisch2016}, and Gleason proved
-a infinitely-specified quantum probabilities measure can always be
-induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+interval-valued probability measures. Surprisingly, we found a quantum
+IVPM which can not be induced by a state, while Shapley proved a classical
+convex IVPM can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
+and Gleason proved a infinitely-specified quantum probability measure
+can always be induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 Nevertheless, a quantum IVPM could still correspond to many possible
 states if it is broken into pieces. Our examples also suggest that
-a quantum IVPM could be more and more likely induced by a state while
-the intervals become sharper, i.e., the measurement resources increase.
+a quantum IVPM could be more and more likely induced by one state
+while the intervals become sharper, i.e., the measurement resources
+increase.
 
@@
 \item $\bar{\mu}(\Omega)=[1,1]$. 
-\item For any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$ 
-\item For a collection $\left\{ E_{i}\right\} _{i=1}^{M}$ of pairwise disjoint
-events, we have $\bar{\mu}\left(\bigcup_{i=1}^{M}E_{i}\right)\subseteq\sum_{i=1}^{M}\bar{\mu}\left(E_{i}\right)$. 
+\item For any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$.
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
+events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)$. 
 \end{itemize}
-\begin{example}[Two-coin experiment with interval probability]\label{ex3}
+\begin{example}{[}Two-coin experiment with interval probability{]}\label{ex3}
 We split the unit interval $[0,1]$ in the following four closed sub-intervals:
@@
 dotted vectors, respectively. 
-\item The red and green circles are are the states orthogonal to $\ket{0}$
+\item The red and green circles are the states orthogonal to $\ket{0}$
 and $\ket{\ps}$, respectively, and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
@@
 leaves an open question of whether behind it there exists a ``real''
-state. Despite the possibility to use quantum IVPMs as the most primitive
-definition of states, we might focus on the meaning of the probability.
-Since a quantum IVPM cannot be defined without consider a particular
-measurement apparatus, and the information extracted from this apparatus,
-the interval-valued probability itself could be considered subjective,
-and could be interpreted in the Bayesian sense as ``lack of knowledge''.
-This, and similar arguments elegantly expressed by recent work on
-Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which
-suggests that the quantum state is more like an interactive system
-in computer science parlance. In other words, the state is only determined
-by its interactions with the environment or observers. A rough but
-useful analogy in the context of computer science would be a web server:
-the state of such a system cannot be said to exist independently of
-the interactions with clients; each interaction with a client determines
-a future state of the system and may affect future interactions. Crucially,
-each client may have a \emph{different} view of the web server that
-is consistent with their own history of interactions. This computational
-perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
-that asserts that the quantum state is subjective: each observer has
-a different view of the quantum system that is consistent with their
-previous observations and that allows that observer, independently
-of other observers, to assign beliefs (i.e., probabilities) to possible
-future interactions.
+state. Despite the possibility of using quantum IVPMs as the most
+primitive definition of states, another possibility is to focus on
+the meaning of the probability.
+
+Since a quantum IVPM cannot be defined without considering a particular
+measurement apparatus, the interval-valued probability itself could
+be considered subjective, and could be interpreted in the Bayesian
+sense as ``lack of knowledge''. This, and similar arguments elegantly
+expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+which suggests that the quantum state is more like an interactive
+system in computer science parlance. In other words, the state is
+only determined by its interactions with the environment or observers.
+A rough but useful analogy in the context of computer science would
+be a web server: the state of such a system cannot be said to exist
+independently of the interactions with clients; each interaction with
+a client determines a future state of the system and may affect future
+interactions. Crucially, each client may have a \emph{different} view
+of the web server that is consistent with their own history of interactions.
+This computational perspective agrees with the philosophical position
+of QBism~\cite{VonBaeyer2016} that asserts that the quantum state
+is subjective: each observer has a different view of the quantum system
+that is consistent with their previous observations and that allows
+that observer, independently of other observers, to assign beliefs
+(i.e., probabilities) to possible future interactions.
 
@@
 
-I would like to apply for funding, but I haven’t been to Europe before…
-So I don't know the specific amount I need…
+Yes.
 

### 2017-01-16 prop.tex
prop.tex \appendix Starting...

@@
 \newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
+\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
 
@@
 \printbibliography
+
+\appendix
+
+\section{Increasing the Measurement Resource}
+
+In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
+although quantum IVPMs have empty cores, we might think that the probability
+measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
+the probability measure $\bar{\mu}$ might be induced by the state
+$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
+or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
+In example~\ref{ex:three-dimensional-4-value}, the probability measure
+$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
+Notice that the set of 1-dimensional projectors mapping to impossible,
+$\bar{\mu}^{-1}\left(\imposs\right)=\left\{ \ket{\phi}\in\mathbb{C}^{3}\middle|\bar{\mu}(\proj{\phi})=\imposs\right\} $
+provides a appealing way to suggest a possible state inducing $\bar{\mu}$.
+Since for any two states~$\ket{\phi_{0}},\ket{\phi_{1}}\in\bar{\mu}^{-1}\left(\imposs\right)$,
+we have $\bar{\mu}(\proj{\phi_{0}})=\bar{\mu}(\proj{\phi_{1}})=\imposs$
+so that $\bar{\mu}$ might be induced by the state $\ket{\phi_{0}}\times\ket{\phi_{1}}$\footnote{\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
+of $\mathbb{C}^{3}$. Although this might be just tedious details
+in this approach, still need to verify carefully.}}.
+
+\section{Subset of Computing Events}
+
+\footnote{\yutsung{The Kochen-Specker theorem is about assigning definitely
+value to observables such that the values of commuting observables
+are consistent; the Bell theorem is about entangled states in different
+locations. If our results are more related to commuting observables,
+it is more related to the Kochen-Specker theorem than the Bell theorem...}}
+
 \end{document}

### 2017-01-17 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 Notice that the set of 1-dimensional projectors mapping to impossible,
-$\bar{\mu}^{-1}\left(\imposs\right)=\left\{ \ket{\phi}\in\mathbb{C}^{3}\middle|\bar{\mu}(\proj{\phi})=\imposs\right\} $
+$\bar{\mu}^{-1}\left(\imposs\right)=\left\{ \ket{\psi}\in\mathbb{C}^{3}~\middle|~\bar{\mu}(\proj{\psi})=\imposs\right\} $
 provides a appealing way to suggest a possible state inducing $\bar{\mu}$.
-Since for any two states~$\ket{\phi_{0}},\ket{\phi_{1}}\in\bar{\mu}^{-1}\left(\imposs\right)$,
-we have $\bar{\mu}(\proj{\phi_{0}})=\bar{\mu}(\proj{\phi_{1}})=\imposs$
-so that $\bar{\mu}$ might be induced by the state $\ket{\phi_{0}}\times\ket{\phi_{1}}$\footnote{\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
+Since for any two states~$\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\bar{\mu}^{-1}\left(\imposs\right)$,
+we have $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$
+so that $\bar{\mu}$ might be induced by the state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
 of $\mathbb{C}^{3}$. Although this might be just tedious details
-in this approach, still need to verify carefully.}}.
+in this approach, still need to verify carefully.}}. Notice that even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are
+normalized, when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
+is not normalized. We will use $\ket{\psi_{0}}\times\ket{\psi_{1}}$
+and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
+when there is no confusion. There are 4 different cases.
+\begin{enumerate}
+\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$
+gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
+then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
+might induce $\bar{\mu}$, but neither $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
+nor $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core
+of $\bar{\mu}$. Actually, $\bar{\mu}$ has an empty core. 
+\item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
+always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$,
+then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
+which might induce $\bar{\mu}$. In another word, if $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
+for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
+represent the same state. 
+\item $\bar{\mu}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
+In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
+If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$ for some
+pure state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
+to $\ket{\psi_{0}}$.
+\item $\bar{\mu}^{-1}\left(\imposs\right)=\emptyset$. If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
+for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
+\end{enumerate}
+In summary, if we have an idea of $\bar{\mu}^{-1}\left(\imposs\right)$,
+we could have some idea of the pure states which are in core.
+
+As we did in Fig.~\ref{fig:three-dimensional-4-value},
 

### 2017-01-18 prop.tex
prop.tex \newcommand{\set}[2] Added...

@@
 \newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
+\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
 
@@
 The conventional definition of a probability space builds upon the
-field of real numbers. In more detail, a probability space consists of
-a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
+field of real numbers. In more detail, a probability space consists
+of a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
 and a \emph{probability measure}~$\pmeas$ mapping events in $\events$
-to the real interval $[0,1]$. We will only consider \emph{finite} sets
-of events and restrict our attention to non-empty finite sets $\Omega$
-as the sample space. The space of events $\events$ includes every
-possible subset of $\Omega$: it is the
-powerset~$2^{\Omega}=\left\{ E ~\middle|~ E\subseteq\Omega\right\}
-$.
+to the real interval $[0,1]$. We will only consider \emph{finite}
+sets of events and restrict our attention to non-empty finite sets
+$\Omega$ as the sample space. The space of events $\events$ includes
+every possible subset of $\Omega$: it is the powerset~$2^{\Omega}=\set{E}{E\subseteq\Omega}$.
 For future reference, we emphasize that events are the primary notion
 of interest and that the sample space is a convenient artifact that
-allows us to treat events as sets obeying the laws of Boolean
-algebra~\cite{Boole1948,Redhead1987-REDINA,Griffiths2003}.
+allows us to treat events as sets obeying the laws of Boolean algebra~\cite{Boole1948,Redhead1987-REDINA,Griffiths2003}.
 
@@
 measure will be closer and closer to the Born rule. In the limit case,
-$\mathscr{I}=\left\{ \left\{ a\right\}
-  ~\middle|~a\in\left[0,1\right]\right\}$
-we do indeed recover the conventional Gleason's theorem and the Born
-rule.
+$\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$ we do
+indeed recover the conventional Gleason's theorem and the Born rule.
 
@@
 Notice that the set of 1-dimensional projectors mapping to impossible,
-$\bar{\mu}^{-1}\left(\imposs\right)=\left\{ \ket{\psi}\in\mathbb{C}^{3}~\middle|~\bar{\mu}(\proj{\psi})=\imposs\right\} $
+$\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$
 provides a appealing way to suggest a possible state inducing $\bar{\mu}$.
@@
 
-\section{Subset of Computing Events}
+\section{Subset of Commuting Events}
 
@@
 
+Given an orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{1}},\ldots,\ket{\psi_{d}}\right\} $
+of a Hilbert space, the set of projections generated by the basis
+is $\events'=\set{\sum_{\ket{\psi}\in S}\ket{\psi}}{S\subseteq\mathcal{B}}$.
+Because $\left(2^{\mathcal{B}},\emptyset,\mathcal{B},\cup,\cap\right)$
+is isomorphic to $\left(\events',\mathbb{0},\mathbb{1},\vee,\cdot\right)$
+as a Boolean algebra, a quantum IVPM~$\bar{\mu}':\events'\rightarrow\mathscr{I}$
+is essentially a classical IVPM~$\bar{\mu}:2^{\mathcal{B}}\rightarrow\mathscr{I}$.
+By the Shapley theorem, if $\bar{\mu}'$ is convex, it should have
+a non-empty core.
+
+The problem is: if $\events'$ is only a commuting subset of $\events$,
+does a convex quantum IVPM~$\bar{\mu}':\events'\rightarrow\mathscr{I}$
+always has a non-empty core?
+
 \end{document}

### 2017-01-18 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 $\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
-Notice that the set of 1-dimensional projectors mapping to impossible,
-$\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$
-provides a appealing way to suggest a possible state inducing $\bar{\mu}$.
-Since for any two states~$\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\bar{\mu}^{-1}\left(\imposs\right)$,
-we have $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$
-so that $\bar{\mu}$ might be induced by the state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
-of $\mathbb{C}^{3}$. Although this might be just tedious details
-in this approach, still need to verify carefully.}}. Notice that even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are
-normalized, when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
+In general, each two 1-dimensional projectors~$\ket{\psi_{0}}$ and
+$\ket{\psi_{1}}$ mapping to impossible suggests $\bar{\mu}$ might
+be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{Notice that even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are normalized,
+when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
 is not normalized. We will use $\ket{\psi_{0}}\times\ket{\psi_{1}}$
 and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
-when there is no confusion. There are 4 different cases.
+when there is no confusion.
+
+\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
+of $\mathbb{C}^{3}$. Although this might be just tedious details
+in this approach, still need to verify carefully.}}. Therefore, the set of 1-dimensional projectors mapping to impossible,
+denoted by $\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$,
+plays an important role to understand $\bar{\mu}$. There are 4 different
+cases when analyzing $\bar{\mu}^{-1}\left(\imposs\right)$:
 \begin{enumerate}
@@
 nor $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core
-of $\bar{\mu}$. Actually, $\bar{\mu}$ has an empty core. 
+of $\bar{\mu}$ because $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
+is inconsistent with $\bar{\mu}(\proj{\psi_{0}'})=\bar{\mu}(\proj{\psi_{1}'})=\imposs$
+and $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ is inconsistent
+with $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$.
+Actually, $\bar{\mu}$ has an empty core. 
 \item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
@@
 In summary, if we have an idea of $\bar{\mu}^{-1}\left(\imposs\right)$,
-we could have some idea of the pure states which are in core.
+we could have some idea of the pure states in core.
 
-As we did in Fig.~\ref{fig:three-dimensional-4-value},
+As we did in Fig.~\ref{fig:three-dimensional-4-value}, we could
+plot the 1-dimensional projectors in a unit sphere~$S^{2}$~\cite{Hatcher2001,dryden2005}.
+Since the state mapping to impossible always contained in a plane,
+$\bar{\mu}^{-1}\left(\imposs\right)$ in the above case 2 - 4 does
+not contain any area in $S^{2}$. In contrast, if $\bar{\mu}^{-1}\left(\imposs\right)$
+contains some area in $S^{2}$, it must be the situation of case 1.
+Furthermore, the larger the area, the more 1-dimensional projectors
+which is inconsistent with any particular Born rule probability measure.
+Therefore, the area of $\bar{\mu}^{-1}\left(\imposs\right)$ could
+indicate how much $\bar{\mu}$ deviate from the Born rule probability
+measures.
 

### 2017-01-19 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 $\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
-In general, each two 1-dimensional projectors~$\ket{\psi_{0}}$ and
-$\ket{\psi_{1}}$ mapping to impossible suggests $\bar{\mu}$ might
-be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{Notice that even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are normalized,
-when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
+In general, each two real 1-dimensional projectors~$\proj{\psi_{0}}$
+and $\proj{\psi_{1}}$ mapping to impossible suggests $\bar{\mu}$
+might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
+in the Hilbert space of dimension 3. In general, we could discuss
+all 1-dimensional projectors in any dimension. However, restricting
+to $\mathbb{R}^{3}$ enable us to use cross product which will simplify
+our discussion a lot, and $\mathbb{R}^{3}$ is easy to visualize and
+imagine. Also, if a quantum IVPM~$\bar{\mu}$ has an empty core when
+restricting to $\mathbb{R}^{3}$, $\bar{\mu}$ has an empty core on
+the original space as well. So restricting on real 1-dimensional projectors
+still provides valid results.
+
+About the cross product, even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$
+are normalized, when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
 is not normalized. We will use $\ket{\psi_{0}}\times\ket{\psi_{1}}$
 and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
-when there is no confusion.
-
-\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
-of $\mathbb{C}^{3}$. Although this might be just tedious details
-in this approach, still need to verify carefully.}}. Therefore, the set of 1-dimensional projectors mapping to impossible,
+when there is no confusion.}. Therefore, the set of 1-dimensional projectors mapping to impossible,
 denoted by $\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$,
@@
 
+In order to simplify the discussion, let's set the center of $\bar{\mu}^{-1}\left(\imposs\right)$
+as the north pole, and assume $\bar{\mu}$ maps every state whose
+latitude is larger than $\theta_{0}$ to impossible. In order to simplify
+the notation, let's give the following definition.
+
+\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
+north pole~$\ket{0}\in S^{2}$, then $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
+denotes the the latitude of $\ket{\psi}$.\end{definition}
+
 \section{Subset of Commuting Events}

### 2017-01-19 prop.tex
prop.tex \section{Increasing the Measurement Resource} Try to clean up from the beginning...

@@
 and $\proj{\psi_{1}}$ mapping to impossible suggests $\bar{\mu}$
-might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
+might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
+in the Hilbert space of dimension 3\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
 in the Hilbert space of dimension 3. In general, we could discuss
@@
 and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
-when there is no confusion.}. Therefore, the set of 1-dimensional projectors mapping to impossible,
+when there is no confusion.}.
+
+Therefore, the set of 1-dimensional projectors mapping to impossible,
 denoted by $\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$,

### 2017-01-20 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 
+Since a quantum IVPM is completely determined by its value on 1-dimensional
+projectors in the Hilbert space of dimension 3, we could define the
+interval-valued frame function to simplify the later discussion.
+
+\begin{definition}\cite{Hatcher2001,dryden2005}~The unit sphere
+in $\mathbb{R}^{d}$ is denoted by $S^{d-1}=\set{\ket{\psi}\in\mathbb{R}^{d}}{\ip{\psi}{\psi}=1}$,
+while the unit sphere in $\mathbb{C}^{d}$ is denoted by $\mathbb{C}S^{d-1}=\set{\ket{\psi}\in\mathbb{C}^{d}}{\ip{\psi}{\psi}=1}$.
+Since $\mathbb{C}$ is one-to-one correspondence to $\mathbb{R}^{2}$~\cite{GAMELIN2003},
+$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. However,
+different symbols emphasis that they are embedded in different spaces.\end{definition}
+
+\begin{definition}A function~$\bar{f}:S^{d-1}\rightarrow\mathscr{I}$
+or $\bar{f}:\mathbb{C}S^{d-1}\rightarrow\mathscr{I}$ is called a
+\emph{real} or \emph{complex interval-valued approximation frame function}\end{definition}
+
 Therefore, the set of 1-dimensional projectors mapping to impossible,

### 2017-01-21 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 \newtheorem{thm}{Theorem}
+\newtheorem{lemma}{Lemma}
 
@@
 measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
-the probability measure $\bar{\mu}$ might be induced by the state
+the probability measure~$\bar{\mu}$ might be induced by the state
 $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
 or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
-In example~\ref{ex:three-dimensional-4-value}, the probability measure
-$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
+In example~\ref{ex:three-dimensional-4-value}, the probability measure~$\bar{\mu}$
+might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
 In general, each two real 1-dimensional projectors~$\proj{\psi_{0}}$
@@
 
-\begin{definition}A function~$\bar{f}:S^{d-1}\rightarrow\mathscr{I}$
-or $\bar{f}:\mathbb{C}S^{d-1}\rightarrow\mathscr{I}$ is called a
-\emph{real} or \emph{complex interval-valued approximation frame function}\end{definition}
+\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}For
+any quantum probability measure~$\mu$ on the Hilbert space of dimension
+3, we can define a \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
+quantum probability measure~$\mu_{\phi}^{B}$ induced by the Born
+rule, the frame function of $\mu_{\phi}^{B}$ is denoted by $f_{\phi}^{B}$.\end{definition}
+
+\begin{lemma}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}A
+frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
+the following properties:
+\begin{itemize}
+\item $\sum_{i=1}^{3}f\left(\ket{\psi_{i}}\right)=1$ for any orthonormal
+basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$ of $\mathbb{C}^{3}$.
+\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
+$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
+\end{itemize}
+Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+satisfies the above properties, $f$ must be a frame function.\end{lemma}
+
+\begin{definition}For any quantum IVPM~$\bar{\mu}$ on the Hilbert
+space of dimension 3, we can define an \emph{interval-valued frame
+function} $\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
+The left-end and the right-end of an interval-valued frame function
+are $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+satisfying $\bar{f}\left(\ket{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
+respectively.\end{definition}
 

### 2017-01-21 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

--- 2017-01-19 prop.tex
@@
 
-In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
-although quantum IVPMs have empty cores, we might think that the probability
-measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
-the probability measure $\bar{\mu}$ might be induced by the state
+Although quantum IVPMs in example~\ref{ex:three-dimensional-three-value}
+and \ref{ex:three-dimensional-4-value} have empty cores, we might
+still think that the probability measure~$\bar{\mu}$ is induced
+by some states. In example~\ref{ex:three-dimensional-three-value},
+the probability measure~$\bar{\mu}$ might be induced by the state
 $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
 or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
-In example~\ref{ex:three-dimensional-4-value}, the probability measure
-$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
+In example~\ref{ex:three-dimensional-4-value}, the probability measure~$\bar{\mu}$
+might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
 In general, each two real 1-dimensional projectors~$\proj{\psi_{0}}$
@@
 might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
-in the Hilbert space of dimension 3\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
+in the Hilbert space of dimension 3.\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
 in the Hilbert space of dimension 3. In general, we could discuss
@@
 and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
-when there is no confusion.}.
+when there is no confusion.}
+
+Since a quantum IVPM is completely determined by its value on 1-dimensional
+projectors in the Hilbert space of dimension 3, we could define the
+interval-valued frame function to simplify the later discussion.
+
+\begin{definition}\cite{Hatcher2001,dryden2005} The unit sphere
+in $\mathbb{R}^{d}$ is denoted by $S^{d-1}=\set{\ket{\psi}\in\mathbb{R}^{d}}{\ip{\psi}{\psi}=1}$,
+while the unit sphere in $\mathbb{C}^{d}$ is denoted by $\mathbb{C}S^{d-1}=\set{\ket{\psi}\in\mathbb{C}^{d}}{\ip{\psi}{\psi}=1}$.
+Since $\mathbb{C}$ is one-to-one correspondence to $\mathbb{R}^{2}$~\cite{GAMELIN2003},
+$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. However,
+different symbols emphasis that they are embedded in different spaces.\end{definition}
+
+\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}
+For any quantum probability measure~$\mu$ on the Hilbert space of
+dimension 3, we can define a \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
+quantum probability measure~$\mu_{\phi}^{B}$ induced by the Born
+rule, its frame function is denoted by $f_{\phi}^{B}$.\end{definition}
+
+\begin{lemma}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}
+A frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+satisfies the following properties:
+\begin{itemize}
+\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
+$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
+\item $1=\sum_{i=1}^{3}f\left(\ket{\psi_{i}}\right)$ for any orthonormal
+basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$ of $\mathbb{C}^{3}$.
+\end{itemize}
+Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+satisfies the above properties, $f$ must be a frame function.\end{lemma}
+
+\begin{definition}For any quantum IVPM~$\bar{\mu}$ on the Hilbert
+space of dimension 3, we can define an \emph{interval-valued frame
+function}~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
+The left-end and the right-end of an interval-valued frame function
+are $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+satisfying $\bar{f}\left(\ket{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
+respectively. Also, if $f$ is the frame function of $\mu$, $\bar{f}$
+is the interval-valued frame function of $\bar{\mu}$, and $\mu$
+is in the core of $\bar{\mu}$, then we say $f$ is in the core of
+$\bar{f}$.\end{definition}
+
+\begin{lemma}A interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
+satisfies the following properties:
+\begin{itemize}
+\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
+for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
+\item $1\in\sum_{i=1}^{3}\bar{f}\left(\ket{\psi_{i}}\right)$ for any orthonormal
+basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$ of $\mathbb{C}^{3}$.
+\end{itemize}
+\end{lemma}
 

### 2017-01-22 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 
-\begin{definition}\cite{Hatcher2001,dryden2005} The unit sphere
+\begin{definition}\cite{Hatcher2001,dryden2005}~The unit sphere
 in $\mathbb{R}^{d}$ is denoted by $S^{d-1}=\set{\ket{\psi}\in\mathbb{R}^{d}}{\ip{\psi}{\psi}=1}$,
@@
 
-\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}
-For any quantum probability measure~$\mu$ on the Hilbert space of
-dimension 3, we can define a \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}~For
+any quantum probability measure~$\mu$ on the Hilbert space of dimension
+3, we can define its \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
 by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
@@
 
-\begin{lemma}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}
-A frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
-satisfies the following properties:
+\begin{lemma}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}~A
+frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
+the following properties:
 \begin{itemize}
@@
 $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
-\item $1=\sum_{i=1}^{3}f\left(\ket{\psi_{i}}\right)$ for any orthonormal
-basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$ of $\mathbb{C}^{3}$.
+\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$,
+we have $1=\sum_{i=1}^{3}f\left(\ket{\psi_{i}}\right)$.
 \end{itemize}
@@
 is in the core of $\bar{\mu}$, then we say $f$ is in the core of
-$\bar{f}$.\end{definition}
+$\bar{f}$, and denoted by $f\in\mathrm{core}\left(\bar{f}\right)$.\end{definition}
 
@@
 for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
-\item $1\in\sum_{i=1}^{3}\bar{f}\left(\ket{\psi_{i}}\right)$ for any orthonormal
-basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$ of $\mathbb{C}^{3}$.
+\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$,
+we have $1\in\sum_{i=1}^{3}\bar{f}\left(\ket{\psi_{i}}\right)$ and
+$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
+where $i$, $j$, and $k$ are any permutations among $1$, $2$,
+and $3$.
 \end{itemize}
-\end{lemma}
-
-Therefore, the set of 1-dimensional projectors mapping to impossible,
-denoted by $\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$,
-plays an important role to understand $\bar{\mu}$. There are 4 different
-cases when analyzing $\bar{\mu}^{-1}\left(\imposs\right)$:
+Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
+satisfies the above properties, $\bar{f}$ must be an interval-valued
+frame function.\end{lemma}\footnote{\yutsung{{Verify the proof...}}}
+
+Since interval-valued probability measures~$\bar{\mu}$ and interval-valued
+frame functions~$\bar{f}$ are one-to-one correspondence, studying
+1-dimensional projectors mapping to impossible by $\bar{\mu}$ is
+the same as studying the points on $\mathbb{C}S^{2}$ mapping to impossible
+by $\bar{f}$. These points, denoted by $\bar{f}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{f}(\ket{\psi})=\imposs}$,
+play an important role to understand $\bar{f}$. There are 4 different
+cases when analyzing $\bar{f}^{-1}\left(\imposs\right)$:
 \begin{enumerate}
-\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$
-gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
+\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{f}^{-1}\left(\imposs\right)$\footnote{\yutsung{{Check when }$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}$ are
+complex?}} gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
 then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
-might induce $\bar{\mu}$, but neither $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
-nor $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core
-of $\bar{\mu}$ because $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
-is inconsistent with $\bar{\mu}(\proj{\psi_{0}'})=\bar{\mu}(\proj{\psi_{1}'})=\imposs$
-and $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ is inconsistent
-with $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$.
-Actually, $\bar{\mu}$ has an empty core. 
+might induce $\bar{f}$, but neither $f_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
+nor $f_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core of
+$\bar{f}$ because $f_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$ is
+inconsistent with $\bar{f}(\proj{\psi_{0}'})=\bar{f}(\proj{\psi_{1}'})=\imposs$
+and $f_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ is inconsistent
+with $\bar{f}(\proj{\psi_{0}})=\bar{f}(\proj{\psi_{1}})=\imposs$.
+Actually, $\bar{f}$ has an empty core. 
 \item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
-always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$,
+always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{f}^{-1}\left(\imposs\right)$,
 then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
-which might induce $\bar{\mu}$. In another word, if $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
+which might induce $\bar{f}$. In another word, if $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
 for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
 represent the same state. 
-\item $\bar{\mu}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
+\item $\bar{f}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
 In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
-If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$ for some
-pure state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
+If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$ for some pure
+state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
 to $\ket{\psi_{0}}$.
-\item $\bar{\mu}^{-1}\left(\imposs\right)=\emptyset$. If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
+\item $\bar{f}^{-1}\left(\imposs\right)=\emptyset$. If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
 for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
 \end{enumerate}
-In summary, if we have an idea of $\bar{\mu}^{-1}\left(\imposs\right)$,
+In summary, if we have an idea of $\bar{f}^{-1}\left(\imposs\right)$,
 we could have some idea of the pure states in core.
@@
 Since the state mapping to impossible always contained in a plane,
-$\bar{\mu}^{-1}\left(\imposs\right)$ in the above case 2 - 4 does
-not contain any area in $S^{2}$. In contrast, if $\bar{\mu}^{-1}\left(\imposs\right)$
+$\bar{f}^{-1}\left(\imposs\right)$ in the above case 2 - 4 does not
+contain any area in $S^{2}$. In contrast, if $\bar{f}^{-1}\left(\imposs\right)$
 contains some area in $S^{2}$, it must be the situation of case 1.
@@
 which is inconsistent with any particular Born rule probability measure.
-Therefore, the area of $\bar{\mu}^{-1}\left(\imposs\right)$ could
-indicate how much $\bar{\mu}$ deviate from the Born rule probability
-measures.
-
-In order to simplify the discussion, let's set the center of $\bar{\mu}^{-1}\left(\imposs\right)$
-as the north pole, and assume $\bar{\mu}$ maps every state whose
-latitude is larger than $\theta_{0}$ to impossible. In order to simplify
-the notation, let's give the following definition.
+Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)$ could indicate
+how much $\bar{f}$ deviate from the Born rule probability measures.
+
+In order to simplify the discussion, let's set the center of $\bar{f}^{-1}\left(\imposs\right)$
+as the north pole, and assume $\bar{f}$ maps every state whose latitude
+is larger than $\theta_{0}$ to impossible. In order to simplify the
+notation, let's give the following definition.
 

### 2017-01-22 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
-in the Hilbert space of dimension 3.\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
-in the Hilbert space of dimension 3. In general, we could discuss
-all 1-dimensional projectors in any dimension. However, restricting
-to $\mathbb{R}^{3}$ enable us to use cross product which will simplify
-our discussion a lot, and $\mathbb{R}^{3}$ is easy to visualize and
-imagine. Also, if a quantum IVPM~$\bar{\mu}$ has an empty core when
-restricting to $\mathbb{R}^{3}$, $\bar{\mu}$ has an empty core on
-the original space as well. So restricting on real 1-dimensional projectors
-still provides valid results.
-
-About the cross product, even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$
-are normalized, when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
-is not normalized. We will use $\ket{\psi_{0}}\times\ket{\psi_{1}}$
-and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
-when there is no confusion.}
+in the Hilbert space of dimension 3.
 
@@
 satisfies the above properties, $\bar{f}$ must be an interval-valued
-frame function.\end{lemma}\footnote{\yutsung{{Verify the proof...}}}
-
+frame function.\end{lemma}\footnote{\yutsung{Verify the proof...}}
+
+\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
+\alpha_{1}\\
+\alpha_{2}
+\end{pmatrix}$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\begin{pmatrix}\beta_{0}\\
+\beta_{1}\\
+\beta_{2}
+\end{pmatrix}$, their cross product is defined as follow: 
+\[
+\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\begin{vmatrix}\alpha_{1}^{*} & \beta_{1}^{*}\\
+\alpha_{2}^{*} & \beta_{2}^{*}
+\end{vmatrix}\ket{0}+\begin{vmatrix}\alpha_{2}^{*} & \beta_{2}^{*}\\
+\alpha_{0}^{*} & \beta_{0}^{*}
+\end{vmatrix}\ket{1}+\begin{vmatrix}\alpha_{0}^{*} & \beta_{0}^{*}\\
+\alpha_{1}^{*} & \beta_{1}^{*}
+\end{vmatrix}\ket{2}\textrm{ ,}
+\]
+where $\begin{vmatrix}\alpha & \beta\\
+\alpha' & \beta'
+\end{vmatrix}=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
+cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
+as usual. We will use $\ket{\psi}\times\ket{\phi}$ and $\frac{\ket{\psi}\times\ket{\phi}}{\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert }$
+interchanged when there is no confusion.\qed\end{definition}
+
+\begin{lemma}Given $\ket{\psi}$, $\ket{\phi}$ and $\ket{\varphi}\in\mathbb{C}^{3}$
+such that $\ket{\psi}$ is not parallel to $\ket{\phi}$. Then, $\ket{\varphi}$
+is parallel to $\ket{\psi}\times\ket{\phi}$ if and only if $\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$.\end{lemma}
+\begin{proof}
+To prove that $\ket{\varphi}$ is parallel to $\ket{\psi}\times\ket{\phi}\Rightarrow\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$,
+we can just verify 
+\begin{eqnarray*}
+\ip{\psi}{\psi\times\phi} & = & \ip{\psi\times\phi}{\psi}^{*}=\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}\right]^{*}=0\textrm{ ,}\\
+\ip{\phi}{\psi\times\phi} & = & \ip{\psi\times\phi}{\phi}^{*}=\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}\right]^{*}=0\textrm{ .}
+\end{eqnarray*}
+
+To prove the other direction, consider the linear transformation~$T:\mathbb{C}^{3}\rightarrow\mathbb{C}^{2}$
+defined by $T\left(\ket{\varphi}\right)=\begin{pmatrix}\ip{\psi}{\varphi}\\
+\ip{\phi}{\varphi}
+\end{pmatrix}$. Its rank equation~\cite{FraleighBeauregard1995} implies
+\begin{eqnarray*}
+\dim\left(\ker T\right) & = & \mathrm{nullity}\left(T\right)\\
+ & = & \dim\left(\mathrm{domain}T\right)-\mathrm{rank}\left(T\right)\\
+ & = & 3-2=1
+\end{eqnarray*}
+By the other direction of the proof, we have already known $\ket{\psi}\times\ket{\phi}\in\ker T$.
+Therefore, $\ket{\varphi}$ is parallel to $\ket{\psi}\times\ket{\phi}$.
+\end{proof}
 Since interval-valued probability measures~$\bar{\mu}$ and interval-valued
@@
 \begin{enumerate}
-\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{f}^{-1}\left(\imposs\right)$\footnote{\yutsung{{Check when }$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}$ are
-complex?}} gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
+\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{f}^{-1}\left(\imposs\right)$
+gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
 then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
@@
 Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)$ could indicate
-how much $\bar{f}$ deviate from the Born rule probability measures.
+how much $\bar{f}$ deviate from the Born rule probability measures.\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
+in the Hilbert space of dimension 3. In general, we could discuss
+all 1-dimensional projectors in any dimension. However, restricting
+to $\mathbb{R}^{3}$ enable us to use cross product which will simplify
+our discussion a lot, and $\mathbb{R}^{3}$ is easy to visualize and
+imagine. Also, if a quantum IVPM~$\bar{\mu}$ has an empty core when
+restricting to $\mathbb{R}^{3}$, $\bar{\mu}$ has an empty core on
+the original space as well. So restricting on real 1-dimensional projectors
+still provides valid results.}
 

### 2017-01-23 prop.tex
prop.tex \section{Increasing the Measurement Resource} Add a proof...

@@
 
-\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}~For
+\begin{definition}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~For
 any quantum probability measure~$\mu$ on the Hilbert space of dimension
@@
 
-\begin{lemma}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}~A
+\begin{lemma}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~A
 frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
@@
 space of dimension 3, we can define an \emph{interval-valued frame
-function}~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
-The left-end and the right-end of an interval-valued frame function
-are $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
-satisfying $\bar{f}\left(\ket{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
-respectively. Also, if $f$ is the frame function of $\mu$, $\bar{f}$
-is the interval-valued frame function of $\bar{\mu}$, and $\mu$
-is in the core of $\bar{\mu}$, then we say $f$ is in the core of
-$\bar{f}$, and denoted by $f\in\mathrm{core}\left(\bar{f}\right)$.\end{definition}
+function}~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
+where $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+are the left-end and the right-end of $\bar{f}$, respectively. Also,
+if $f$ is the frame function of $\mu$, $\bar{f}$ is the interval-valued
+frame function of $\bar{\mu}$, and $\mu$ is in the core of $\bar{\mu}$,
+then we say $f$ is in the core of $\bar{f}$, and denoted by $f\in\mathrm{core}\left(\bar{f}\right)$.\end{definition}
 
@@
 satisfies the above properties, $\bar{f}$ must be an interval-valued
-frame function.\end{lemma}\footnote{\yutsung{Verify the proof...}}
-
+frame function.\end{lemma}
+\begin{proof}
+We first prove that a interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
+induced by a quantum IVPM~$\bar{\mu}$ satisfies the above properties:
+\begin{itemize}
+\item For any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$,
+\[
+\bar{f}\left(\lambda\ket{\psi}\right)=\bar{\mu}\left(\left(\lambda\ket{\psi}\right)\left(\lambda\ket{\psi}\right)^{\dagger}\right)=\bar{\mu}\left(\lambda\lambda^{*}\proj{\psi}\right)\overset{\lambda\in\mathbb{C}S^{0}}{=}\bar{\mu}\left(\proj{\psi}\right)=\bar{f}\left(\ket{\psi}\right)\textrm{ .}
+\]
+\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$,
+we have 
+\begin{eqnarray*}
+ &  & \left[1,1\right]=\bar{\mu}(\mathbb{1})=\bar{\mu}\left(\sum_{i=1}^{3}\proj{\psi_{i}}\right)\subseteq\sum_{i=1}^{3}\bar{\mu}\left(\proj{\psi_{i}}\right)=\sum_{i=1}^{3}\bar{f}\left(\ket{\psi_{i}}\right)\\
+ & \Rightarrow & 1\in\sum_{i=1}^{3}\bar{f}\left(\ket{\psi_{i}}\right)
+\end{eqnarray*}
+Also, 
+\begin{eqnarray*}
+ &  & \left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)=\left[1,1\right]-\bar{\mu}\left(\proj{\psi_{i}}\right)=\bar{\mu}\left(\mathbb{1}-\proj{\psi_{i}}\right)\\
+ & = & \bar{\mu}\left(\proj{\psi_{j}}+\proj{\psi_{k}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{j}}\right)+\bar{\mu}\left(\proj{\psi_{k}}\right)=\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)\textrm{ ,}
+\end{eqnarray*}
+where $i$, $j$, and $k$ are any permutations among $1$, $2$,
+and $3$.
+\end{itemize}
+Given a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
+satisfies the above properties, consider $\bar{\mu}:\events\rightarrow\mathscr{I}$
+defined by
+\begin{itemize}
+\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$ and $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
+\item For any $\ket{\psi}\in\mathbb{C}S^{2}$, we have $\bar{\mu}\left(\proj{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
+and $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{\psi}\right)$.
+\end{itemize}
+We only need to verify 
+\begin{equation}
+\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:quantumIVPMconditions}
+\end{equation}
+ for any set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$.
+First, if $\mathbb{0}$ or $\mathbb{1}$ is in $\left\{ P_{i}\right\} _{i=1}^{N}$,
+the statement could be reduced to the case without $\mathbb{0}$,
+or its trivial. Hence, we only need to discuss $\left\{ P_{i}\right\} _{i=1}^{N}$
+containing 1- or 2-dimensional projectors. When $\left\{ P_{i}\right\} _{i=1}^{N}$
+containing 2-dimensional projectors, the definition of $\bar{\mu}$
+implies equation~(\ref{eq:quantumIVPMconditions}). When $\left\{ P_{i}\right\} _{i=1}^{N}$
+only containing 1-dimensional projectors, the properties of $\bar{f}$
+implies equation~(\ref{eq:quantumIVPMconditions}).
+\end{proof}
 \begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\

### 2017-01-24 prop.tex
prop.tex \section{Increasing the Measurement Resource} Simplify proof..

--- 2017-01-22 prop.tex
@@
 $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
-\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$,
-we have $1=\sum_{i=1}^{3}f\left(\ket{\psi_{i}}\right)$.
+\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
+we have $1=\sum_{i=0}^{2}f\left(\ket{\psi_{i}}\right)$.
 \end{itemize}
@@
 for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
-\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$,
-we have $1\in\sum_{i=1}^{3}\bar{f}\left(\ket{\psi_{i}}\right)$ and
+\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
+we have $1\in\sum_{i=0}^{2}\bar{f}\left(\ket{\psi_{i}}\right)$ and
 $\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
-where $i$, $j$, and $k$ are any permutations among $1$, $2$,
-and $3$.
+where $i$, $j$, and $k$ are any permutations among $0$, $1$,
+and $2$.
 \end{itemize}
@@
 satisfies the above properties, $\bar{f}$ must be an interval-valued
-frame function.\end{lemma}\footnote{\yutsung{Verify the proof...}}
-
+frame function.\end{lemma}
+\begin{proof}
+Given a quantum IVPM~$\bar{\mu}$, it is straightforward to verify
+that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
+satisfies the above properties.
+
+Conversely, given a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
+satisfying the above properties, consider $\bar{\mu}:\events\rightarrow\mathscr{I}$
+defined by
+\begin{itemize}
+\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$ and $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
+\item For any $\ket{\psi}\in\mathbb{C}S^{2}$, we have $\bar{\mu}\left(\proj{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
+and $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{\psi}\right)$.
+\end{itemize}
+Since other conditions are trivial, we only need to verify 
+\begin{equation}
+\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:quantumIVPMconditions}
+\end{equation}
+ for any set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$.
+First, if $\mathbb{0}$ or $\mathbb{1}$ is in $\left\{ P_{i}\right\} _{i=1}^{N}$,
+the statement could be reduced to the case without $\mathbb{0}$,
+or its trivial. Hence, we only need to discuss $\left\{ P_{i}\right\} _{i=1}^{N}$
+containing 1- or 2-dimensional projectors. When $\left\{ P_{i}\right\} _{i=1}^{N}$
+containing 2-dimensional projectors, the definition of $\bar{\mu}$
+implies equation~(\ref{eq:quantumIVPMconditions}). When $\left\{ P_{i}\right\} _{i=1}^{N}$
+only containing 1-dimensional projectors, the properties of $\bar{f}$
+implies equation~(\ref{eq:quantumIVPMconditions}).
+\end{proof}
 \begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\

### 2017-01-24 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 containing 1- or 2-dimensional projectors. When $\left\{ P_{i}\right\} _{i=1}^{N}$
-containing 2-dimensional projectors, the definition of $\bar{\mu}$
+containing a 2-dimensional projector, the definition of $\bar{\mu}$
 implies equation~(\ref{eq:quantumIVPMconditions}). When $\left\{ P_{i}\right\} _{i=1}^{N}$
@@
 as usual. We will use $\ket{\psi}\times\ket{\phi}$ and $\frac{\ket{\psi}\times\ket{\phi}}{\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert }$
-interchanged when there is no confusion.\qed\end{definition}
+interchanged when there is no confusion.\end{definition}
+
+\begin{definition}For $\ket{\psi}$ and $\ket{\phi}\in\mathbb{C}^{3}$,
+if $\ket{\psi}=\lambda\ket{\phi}$ for some~$\lambda\ne0$, we call
+$\ket{\psi}$ is parallel to $\ket{\phi}$ denoted by $\ket{\psi}\parallel\ket{\phi}$.
+In this case, $\ket{\psi}$ and $\ket{\phi}$ represent the same physical
+state. ``$\ket{\psi}$ is not parallel to $\ket{\phi}$'' is denoted
+by $\ket{\psi}\nparallel\ket{\phi}$.\end{definition}
 
 \begin{lemma}Given $\ket{\psi}$, $\ket{\phi}$ and $\ket{\varphi}\in\mathbb{C}^{3}$
-such that $\ket{\psi}$ is not parallel to $\ket{\phi}$. Then, $\ket{\varphi}$
-is parallel to $\ket{\psi}\times\ket{\phi}$ if and only if $\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$.\end{lemma}
+such that $\ket{\psi}\nparallel\ket{\phi}$. Then, $\ket{\varphi}\parallel\left(\ket{\psi}\times\ket{\phi}\right)$
+if and only if $\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$.\end{lemma}
 \begin{proof}
-To prove that $\ket{\varphi}$ is parallel to $\ket{\psi}\times\ket{\phi}\Rightarrow\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$,
+To prove that $\ket{\varphi}\parallel\left(\ket{\psi}\times\ket{\phi}\right)\Rightarrow\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$,
 we can just verify 
@@
 \ip{\phi}{\varphi}
-\end{pmatrix}$. Its rank equation~\cite{FraleighBeauregard1995} implies
-\begin{eqnarray*}
-\dim\left(\ker T\right) & = & \mathrm{nullity}\left(T\right)\\
- & = & \dim\left(\mathrm{domain}T\right)-\mathrm{rank}\left(T\right)\\
- & = & 3-2=1
-\end{eqnarray*}
+\end{pmatrix}$. Since $\ket{\psi}\nparallel\ket{\phi}$, we have $\mathrm{rank}\left(T\right)=2$.
+Together with the rank equation~\cite{FraleighBeauregard1995}, we
+have
+\[
+\dim\left(\ker T\right)=\mathrm{nullity}\left(T\right)=3-\mathrm{rank}\left(T\right)=3-2=1\textrm{ .}
+\]
 By the other direction of the proof, we have already known $\ket{\psi}\times\ket{\phi}\in\ker T$.
-Therefore, $\ket{\varphi}$ is parallel to $\ket{\psi}\times\ket{\phi}$.
+Therefore, $\ket{\varphi}\parallel\left(\ket{\psi}\times\ket{\phi}\right)$.
 \end{proof}
@@
 \begin{enumerate}
+\item $\bar{f}^{-1}\left(\imposs\right)=\emptyset$. If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
+for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
+\item $\bar{f}^{-1}\left(\imposs\right)=\left\{ \ket{\psi_{0}}\right\} $.
+If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$ for some pure
+state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
+to $\ket{\psi_{0}}$.
+\item Consider $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} \subseteq\bar{f}^{-1}\left(\imposs\right)$.
+If $\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)\parallel\left(\ket{\psi_{0}'}\times\ket{\psi_{1}'}\right)$
+for any $\left\{ \ket{\psi_{0}'},\ket{\psi_{1}'}\right\} \subseteq\bar{f}^{-1}\left(\imposs\right)$,
+then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
+which might induce $\bar{f}$. In another word, if $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
+for some pure state~$\ket{\phi}$, then $\ket{\phi}\parallel\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)$. 
 \item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{f}^{-1}\left(\imposs\right)$
@@
 Actually, $\bar{f}$ has an empty core. 
-\item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
-always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{f}^{-1}\left(\imposs\right)$,
-then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
-which might induce $\bar{f}$. In another word, if $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
-for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
-represent the same state. 
-\item $\bar{f}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
-In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
-If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$ for some pure
-state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
-to $\ket{\psi_{0}}$.
-\item $\bar{f}^{-1}\left(\imposs\right)=\emptyset$. If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
-for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
 \end{enumerate}

### 2017-01-24 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 
-\noindent It is easy to establish that quantum interval-valued
-probability measures generalize conventional quantum probability
-measures. In particular, any quantum probability measure can be recast
-as an interval-valued measure using the three intervals
-$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
-where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
-\necess~as before, and \emph{$\left[0,1\right]$} is called
-\unknown~because it provides no information. Given a quantum
+\noindent It is easy to establish that quantum interval-valued probability
+measures generalize conventional quantum probability measures. In
+particular, any quantum probability measure can be recast as an interval-valued
+measure using the three intervals $\left[0,0\right]$, $\left[1,1\right]$
+and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$ and $\left[1,1\right]$
+are called \imposs~and \necess~as before, and \emph{$\left[0,1\right]$}
+is called \unknown~because it provides no information. Given a quantum
 probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
-define a quantum interval-valued probability
-measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ by
-$\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where
-$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
-\[
+define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is defined by 
+\begin{equation}
 \iota(x)=\begin{cases}
@@
 \unknown & \textrm{otherwise.}
-\end{cases}
-\]
+\end{cases}\label{eq:homomorphism}
+\end{equation}
 This measure represents the beliefs of an experimenter with no prior
@@
 we can ask: what can we deduce about the state of a quantum system
-given a quantum interval-valued probability measure, i.e., given
-observations done with finite resources. In the case the intervals are
-infinitely precise the question reduces to Gleason's theorem which
-states that the state of the quantum system is uniquely determined by
-the probability measure. But surely the less resources are available,
-the less precise the intervals, and the less we expect to know about
-the state of the system. To formally state and answer this question we
-begin with defining the \emph{core} and \emph{convexity} of a
-probability measure as follows.
+given a quantum interval-valued probability measure, i.e., given observations
+done with finite resources. In the case the intervals are infinitely
+precise the question reduces to Gleason's theorem which states that
+the state of the quantum system is uniquely determined by the probability
+measure. But surely the less resources are available, the less precise
+the intervals, and the less we expect to know about the state of the
+system. To formally state and answer this question we begin with defining
+the \emph{core} and \emph{convexity} of a probability measure as follows.
 
@@
 for some pure state~$\ket{\phi}$, then $\ket{\phi}\parallel\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)$.
-\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{f}^{-1}\left(\imposs\right)$
-gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
+For example, example~\ref{ex:three-dimensional-4-value} is in this
+case when the core is empty; an interval-valued frame function defined
+by $\bar{f}\left(\ket{\psi}\right)=\iota\left(f_{\phi}^{B}\left(\ket{\psi}\right)\right)$
+is also in this case when the core is the singleton set~$\left\{ f_{\phi}^{B}\right\} $,
+where $\iota$ is defined in equation~(\ref{eq:homomorphism}).
+\item If there exist two pair of states and $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} $
+and $\left\{ \ket{\psi_{0}'},\ket{\psi_{1}'}\right\} \subseteq\bar{f}^{-1}\left(\imposs\right)$
+such that $\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)\nparallel\left(\ket{\psi_{0}'}\times\ket{\psi_{1}'}\right)$,
 then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
-might induce $\bar{f}$, but neither $f_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
-nor $f_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core of
-$\bar{f}$ because $f_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$ is
-inconsistent with $\bar{f}(\proj{\psi_{0}'})=\bar{f}(\proj{\psi_{1}'})=\imposs$
-and $f_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ is inconsistent
-with $\bar{f}(\proj{\psi_{0}})=\bar{f}(\proj{\psi_{1}})=\imposs$.
-Actually, $\bar{f}$ has an empty core. 
+might induce $\bar{f}$. However, neither $f_{\psi_{0}\times\psi_{1}}^{B}$
+nor $f_{\psi_{0}'\times\psi_{1}'}^{B}$ is in the core of $\bar{f}$
+because $f_{\psi_{0}\times\psi_{1}}^{B}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}'}\right)=\bar{f}\left(\ket{\psi_{1}'}\right)=\imposs$
+and $f_{\psi_{0}'\times\psi_{1}'}^{B}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)=\imposs$.
+Actually, $\bar{f}$ has an empty core, and this is the case for example~\ref{ex:three-dimensional-three-value}.
 \end{enumerate}
@@
 
-As we did in Fig.~\ref{fig:three-dimensional-4-value}, we could
-plot the 1-dimensional projectors in a unit sphere~$S^{2}$~\cite{Hatcher2001,dryden2005}.
-Since the state mapping to impossible always contained in a plane,
-$\bar{f}^{-1}\left(\imposs\right)$ in the above case 2 - 4 does not
-contain any area in $S^{2}$. In contrast, if $\bar{f}^{-1}\left(\imposs\right)$
-contains some area in $S^{2}$, it must be the situation of case 1.
-Furthermore, the larger the area, the more 1-dimensional projectors
-which is inconsistent with any particular Born rule probability measure.
-Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)$ could indicate
-how much $\bar{f}$ deviate from the Born rule probability measures.\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
-in the Hilbert space of dimension 3. In general, we could discuss
-all 1-dimensional projectors in any dimension. However, restricting
-to $\mathbb{R}^{3}$ enable us to use cross product which will simplify
-our discussion a lot, and $\mathbb{R}^{3}$ is easy to visualize and
-imagine. Also, if a quantum IVPM~$\bar{\mu}$ has an empty core when
-restricting to $\mathbb{R}^{3}$, $\bar{\mu}$ has an empty core on
-the original space as well. So restricting on real 1-dimensional projectors
-still provides valid results.}
-
-In order to simplify the discussion, let's set the center of $\bar{f}^{-1}\left(\imposs\right)$
+If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the above
+case 1 - 3 so that $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
+no area in $S^{2}$.\footnote{Notice that we only discuss the part of $\bar{f}^{-1}\left(\imposs\right)$
+which is in $S^{2}$. In general, we could discuss the whole $\bar{f}^{-1}\left(\imposs\right)\subseteq\mathbb{C}S^{2}$.
+However, restricting to $S^{2}$ enable us to visualize and imagine
+easily. Also, if a interval-valued frame function~$\bar{f}$ has
+an empty core when restricting to $S^{2}$, $\bar{\mu}$ has an empty
+core on the original space as well. So restricting to $S^{2}$ still
+provides valid results.} In contrast, if $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
+some area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
+has an empty core. Furthermore, the larger the area, the more state
+vectors which are inconsistent with any particular Born rule frame
+function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
+could indicate how much $\bar{f}$ deviate from the Born rule frame
+functions.
+
+In order to simplify the discussion, consider the center of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
 as the north pole, and assume $\bar{f}$ maps every state whose latitude
-is larger than $\theta_{0}$ to impossible. In order to simplify the
-notation, let's give the following definition.
+is larger than $\theta_{0}$ to impossible.
 

### 2017-01-24 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

@@
 could indicate how much $\bar{f}$ deviate from the Born rule frame
-functions.
+functions. In the following paragraphs, we will establish that if
+the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ is big,
+then the interval~$\mathscr{I}$ must be coarse. Therefore, if the
+interval~$\mathscr{I}$ is finer, then the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
+would be smaller so that $\bar{f}$ is closer to the frame function
+derived from the Born rule.
 

### 2017-01-25 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

--- 2017-01-24 prop.tex
@@
 no area in $S^{2}$.\footnote{Notice that we only discuss the part of $\bar{f}^{-1}\left(\imposs\right)$
-which is in $S^{2}$. In general, we could discuss the whole $\bar{f}^{-1}\left(\imposs\right)\subseteq\mathbb{C}S^{2}$.
+in $S^{2}$. In general, we could discuss the whole $\bar{f}^{-1}\left(\imposs\right)\subseteq\mathbb{C}S^{2}$.
 However, restricting to $S^{2}$ enable us to visualize and imagine
 easily. Also, if a interval-valued frame function~$\bar{f}$ has
-an empty core when restricting to $S^{2}$, $\bar{\mu}$ has an empty
+an empty core when restricting to $S^{2}$, $\bar{f}$ has an empty
 core on the original space as well. So restricting to $S^{2}$ still
-provides valid results.} In contrast, if $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
+provides some valid results.} In contrast, if $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
 some area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
@@
 could indicate how much $\bar{f}$ deviate from the Born rule frame
-functions.
+functions. In the following paragraphs, we will establish that if
+the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ is big,
+then the interval~$\mathscr{I}$ must be coarse. Therefore, if the
+interval~$\mathscr{I}$ is finer, then the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
+would be smaller so that $\bar{f}$ is closer to a Born rule frame
+function.
 
@@
 north pole~$\ket{0}\in S^{2}$, then $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
-denotes the the latitude of $\ket{\psi}$.\end{definition}
+denotes the latitude of $\ket{\psi}$. Conversely, $\theta^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\theta\left(\ket{\psi}\right)\in I}$.
+For example, $\theta^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\theta\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
+contains all states whose latitude is larger than $\theta_{0}$.\end{definition}
+
+\begin{lemma}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,
+if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\theta^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
+then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\theta^{-1}\left(\left[0,\theta_{0}\right]\right)$,
+$\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.\end{lemma}
 

### 2017-01-29 prop.tex
prop.tex \subsection{Classical Interval-Valued Probability Measures} Fix typos...

@@
 
-As motivated above, an event $E_{1}$ may have an interval of
-probability $[l_{1},r_{1}]$. Assume that another disjoint event
-$E_{2}$ has an interval of probability $[l_{2},r_{2}]$, what is the
-interval of probability for the event $E_{1}\cup E_{2}$? The answer is
-somewhat subtle: although it is possible to use the sum of the
-intervals $[l_{1}+l_{2},r_{1}+r_{2}]$ as the combined probability, one
-can find a much tighter interval if information \emph{against} the
-event (i.e., information about the complement event) is also taken
-into consideration. Formally, for a general event $E$ with probability
-$[l,r]$, the evidence that contradicts $E$ is evidence supporting the
-complement of $E$.  The complement of $E$ must therefore have
-probability $\left[1-r,1-l\right]$ which we abbreviate
-$\left[1,1\right]-\left[l,r\right]$.  Given a sample space~$\Omega$
-and its set of events~$\events$, a
-function~$\bar{\mu}:\events\rightarrow[0,1]$ is a classical
-interval-valued probability measure if and only if $\bar{\mu}$
-satisfies the following conditions~\cite{JamisonLodwick2004} where the
-last line uses $\subseteq$ to allow for tighter intervals that exploit
-the complement event:
+As motivated above, an event $E_{1}$ may have an interval of probability
+$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
+an interval of probability $[l_{2},r_{2}]$, what is the interval
+of probability for the event $E_{1}\cup E_{2}$? The answer is somewhat
+subtle: although it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
+as the combined probability, one can find a much tighter interval
+if information \emph{against} the event (i.e., information about the
+complement event) is also taken into consideration. Formally, for
+a general event $E$ with probability $[l,r]$, the evidence that
+contradicts $E$ is evidence supporting the complement of $E$. The
+complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
+which we abbreviate $\left[1,1\right]-\left[l,r\right]$. Given a
+sample space~$\Omega$, its set of events~$\events$, and a collection
+of intervals $\mathscr{I}$, a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is a classical interval-valued probability measure if and only if
+$\bar{\mu}$ satisfies the following conditions~\cite{JamisonLodwick2004}
+where the last line uses $\subseteq$ to allow for tighter intervals
+that exploit the complement event: 
 \begin{itemize}
@@
 \item $\bar{\mu}(\Omega)=[1,1]$. 
-\item For any event $E$,
-  $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$
-\item For a collection $\left\{ E_{i}\right\} _{i=1}^{M}$ of pairwise
-  disjoint events, we have
-  $\bar{\mu}\left(\bigcup_{i=1}^{M}E_{i}\right)\subseteq\sum_{i=1}^{M}\bar{\mu}\left(E_{i}\right)$.
+\item For any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$ 
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
+events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)$. 
 \end{itemize}

### 2017-01-30 prop.tex
prop.tex \section{Quantum Interval-valued Probability Measures} Fix typos...
prop.tex \section{Increasing the Measurement Resource} Fix typos...

@@
 \begin{itemize}
-\item A \emph{core} of $\bar{\mu}$ is the set
-  $\mathrm{core}\left(\bar{\mu}\right)=\left\{
-    \pmeas:\events\rightarrow[0,1] ~\middle|~ \forall
-    E\in\events.~\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\}$.
+\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$. 
 \item $\bar{\mu}$ is called convex if
@@
 probability measure]\label{ex:three-dimensional-three-value} Given
-  a three dimensional Hilbert space with an orthonormal basis
-  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
-    $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
-  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
+a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
 $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$, and 
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})
-  &=& \imposs\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})
-  &=& \necess \\
-\bar{\mu}(P) 
-  &=& \unknown\quad\textrm{otherwise}
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\\
+\bar{\mu}(P) & = & \unknown\quad\textrm{otherwise}
 \end{eqnarray*}
 It is straightforward to verify that $\bar{\mu}$ is a convex quantum
-interval-valued probability measure. Now assume there exists a
-real-valued quantum probability measure $\mu$ such that
-$\mu(P)\in\bar{\mu}(P)$ for every event (projection)~$P$. We derive a
-contradiction as follows. Suppose $\mu(P)\in\bar{\mu}(P)$ then we must
-have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$. By Gleason's
-theorem, there is a mixed
-state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$ such that
-$\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$, where
-$\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$.  However, no pure
-state~$\ket{\phi}$ can satisfy
-$\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
+interval-valued probability measure. Now assume there exists a real-valued
+quantum probability measure $\mu$ such that $\mu(P)\in\bar{\mu}(P)$
+for every event (projection)~$P$. We derive a contradiction as follows.
+Suppose $\mu(P)\in\bar{\mu}(P)$ then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
+By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
+such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
+can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
 \end{example}
@@
 
-\begin{lemma}A interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
+\begin{lemma}An interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
 satisfies the following properties:

### 2017-01-30 prop.tex
prop.tex \section{Increasing the Measurement Resource} Fix a typo...

@@
 the same as studying the points on $\mathbb{C}S^{2}$ mapping to impossible
-by $\bar{f}$. These points, denoted by $\bar{f}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{f}(\ket{\psi})=\imposs}$,
+by $\bar{f}$. These points, denoted by $\bar{f}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}S^{2}}{\bar{f}(\ket{\psi})=\imposs}$,
 play an important role to understand $\bar{f}$. There are 4 different

### 2017-02-01 prop.tex
prop.tex \section{Properties of Quantum IVPMs Decided by Their Range} Added...

@@
 
+\section{Properties of Quantum IVPMs Decided by Their Range}
+
+\begin{lemma}Consider a collection of intervals~$\mathscr{I}$ with
+a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ such that
+$\iota\left(0\right)=\left[0,0\right]$, $\iota\left(1\right)=\left[1,1\right]$,
+$\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and
+$\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.
+Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
+we define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$.\end{lemma}
+\begin{proof}
+~
+\begin{itemize}
+\item $\bar{\mu}(\mathbb{0})=\iota\left(\mu(\mathbb{0})\right)=\iota\left(0\right)=\left[0,0\right]$.
+\item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$. 
+\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
+\end{itemize}
+\end{proof}
+\begin{lemma}Consider a collection of intervals~$\mathscr{I}$ with
+a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ such that
+$\iota\left(0\right)=\left[0,0\right]$, $\iota\left(1\right)=\left[1,1\right]$,
+$\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and
+$\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.
+Then, there is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.\end{lemma}
+\begin{proof}
+Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$. Then,
+$\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{B}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
+i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\bar{\mu}\right)$,
+we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{B}$.
+\end{proof}
+\footnote{\yutsung{Examples of $\mathscr{I}$ with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+such that $\iota\left(0\right)=\left[0,0\right]$, $\iota\left(1\right)=\left[1,1\right]$,
+$\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and
+$\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.}}
+
 \end{document}

### 2017-02-01 prop.tex
prop.tex \section{Quantum and Classical} Finish convex question...

@@
 \item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
-events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)$. 
+events, we have 
+\begin{equation}
+\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\textrm{ .}\label{eq:classical-include}
+\end{equation}
 \end{itemize}
@@
 
-Looking closely at the example above, we might think that the
-probability measure $\bar{\mu}$ is induced by the state $\ket{2}$
-because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, or we
-might think it is induced by the state $\ket{1}$ because
-$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, or yet we might
-think it is induced by the mixed state $\frac{\mathbb{1}}{3}$ because
-$\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$. Each of these
-possibilities is compatible with some but not all of the
-observations. All is not lost however: if the observations are made
-more precise, we conjecture that some of the inconsistencies
+Looking closely at the example above, we might think that the probability
+measure $\bar{\mu}$ is induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
+or we might think it is induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
+or yet we might think it is induced by the mixed state $\frac{\mathbb{1}}{3}$
+because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.
+Each of these possibilities is compatible with some but not all of
+the observations. All is not lost however: if the observations are
+made more precise, we conjecture that some of the inconsistencies
 disappear. A partial proof of this conjecture is the following example
-which refines the previous probability measure by adding more precise
-intervals. It remains to prove that this refined measure is convex,
-however.
+which refines the previous convex probability measure by adding more
+precise intervals.
 
@@
 
-\section{Subset of Commuting Events}
-
+\section{Quantum and Classical}
+
+\begin{lemma}Given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$
+for a given Hilbert space~$\Hilb$ of dimension~$d$, and a quantum
+IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Then, the function
+$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ defined by
+$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)$
+is a classical IVPM, where $\sum_{\ket{j}\in\emptyset}\proj{j}$ is
+defined to be $\mathbb{0}$.\end{lemma}
+\begin{proof}
+~
+\begin{itemize}
+\item $\bar{\mu}^{\Omega}(\emptyset)=\bar{\mu}\left(\sum_{\ket{j}\in\emptyset}\proj{j}\right)=\bar{\mu}\left(\mathbb{0}\right)=[0,0]$. 
+\item $\bar{\mu}^{\Omega}(\Omega)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)=[1,1]$. 
+\item For any event $E$, $\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega\backslash E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)$.
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
+events, we have $\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{\ket{j}\in\bigcup_{i=1}^{N}E_{i}}\proj{j}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)$.
+\end{itemize}
+\end{proof}
 \footnote{\yutsung{The Kochen-Specker theorem is about assigning definitely
@@
 locations. If our results are more related to commuting observables,
-it is more related to the Kochen-Specker theorem than the Bell theorem...}}
-
-Given an orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{1}},\ldots,\ket{\psi_{d}}\right\} $
-of a Hilbert space, the set of projections generated by the basis
-is $\events'=\set{\sum_{\ket{\psi}\in S}\ket{\psi}}{S\subseteq\mathcal{B}}$.
-Because $\left(2^{\mathcal{B}},\emptyset,\mathcal{B},\cup,\cap\right)$
-is isomorphic to $\left(\events',\mathbb{0},\mathbb{1},\vee,\cdot\right)$
-as a Boolean algebra, a quantum IVPM~$\bar{\mu}':\events'\rightarrow\mathscr{I}$
-is essentially a classical IVPM~$\bar{\mu}:2^{\mathcal{B}}\rightarrow\mathscr{I}$.
-By the Shapley theorem, if $\bar{\mu}'$ is convex, it should have
-a non-empty core.
-
-The problem is: if $\events'$ is only a commuting subset of $\events$,
-does a convex quantum IVPM~$\bar{\mu}':\events'\rightarrow\mathscr{I}$
-always has a non-empty core?
+it is more related to the Kochen-Specker theorem than the Bell theorem...}}\begin{lemma}Given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ is a classical
+convex IVPM for any orthonormal basis~$\Omega$, then $\bar{\mu}$
+is a quantum convex IVPM.\end{lemma}
+\begin{proof}
+Pick two commuting events~$P_{0},P_{1}\in\events$. Since they are
+commuting, they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
+Since they are projectors, the eigenvalues of them are $0$ or $1$
+so that we can express them as $P_{0}=\sum_{\ket{j}\in E_{0}}\proj{j}$
+and $P_{1}=\sum_{\ket{j}\in E_{1}}\proj{j}$. Then, 
+\begin{eqnarray*}
+ &  & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
+ & = & \bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\vee\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)+\bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)\\
+ & = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cup E_{1}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cap E_{1}}\proj{j}\right)\\
+ & = & \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\\
+ & \subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\\
+ & = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\\
+ & = & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
+\end{eqnarray*}
+\end{proof}
+\begin{lemma}When the number of elements in $\Omega$ is less than
+or equal to 3, every classical convex IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$.\end{lemma}
+\begin{proof}
+Given two events~$E_{0},E_{1}\subseteq\Omega$, we want to verify
+\begin{equation}
+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}\label{eq:classical-convex}
+\end{equation}
+When $E_{0}\cap E_{1}=\emptyset$, equation~(\ref{eq:classical-convex})
+is a special case of equation~(\ref{eq:classical-include}). When
+$E_{0}\cup E_{1}=\Omega$, we have $E_{0}^{c}\cap E_{1}^{c}=\emptyset$,
+where $E_{0}^{c}=\Omega\backslash E_{0}$ and $E_{1}^{c}=\Omega\backslash E_{1}$.
+Thus, 
+\begin{eqnarray*}
+ &  & \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
+ & \Rightarrow & \left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
+ & \Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\
+ & \Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}
+\end{eqnarray*}
+When the number of elements in $\Omega$ is less than or equal to
+3, either $E_{0}\cap E_{1}=\emptyset$ or $E_{0}\cup E_{1}=\Omega$
+must happen so that $\bar{\mu}^{\Omega}$is convex.
+\end{proof}
+\begin{thm}Given a Hilbert space~$\Hilb$ of dimension~$3$, every
+quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is convex.\end{thm}
+\begin{proof}
+The direct consequence of the previous lemmas.
+\end{proof}
 

### 2017-02-02 prop.tex
prop.tex \section{Quantum and Classical} Updating...

--- 2017-02-01 prop.tex
@@
 
-\section{Subset of Commuting Events}
-
-\footnote{\yutsung{The Kochen-Specker theorem is about assigning definitely
-value to observables such that the values of commuting observables
-are consistent; the Bell theorem is about entangled states in different
-locations. If our results are more related to commuting observables,
-it is more related to the Kochen-Specker theorem than the Bell theorem...}}
-
-Given an orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{1}},\ldots,\ket{\psi_{d}}\right\} $
-of a Hilbert space, the set of projections generated by the basis
-is $\events'=\set{\sum_{\ket{\psi}\in S}\ket{\psi}}{S\subseteq\mathcal{B}}$.
-Because $\left(2^{\mathcal{B}},\emptyset,\mathcal{B},\cup,\cap\right)$
-is isomorphic to $\left(\events',\mathbb{0},\mathbb{1},\vee,\cdot\right)$
-as a Boolean algebra, a quantum IVPM~$\bar{\mu}':\events'\rightarrow\mathscr{I}$
-is essentially a classical IVPM~$\bar{\mu}:2^{\mathcal{B}}\rightarrow\mathscr{I}$.
-By the Shapley theorem, if $\bar{\mu}'$ is convex, it should have
-a non-empty core.
-
-The problem is: if $\events'$ is only a commuting subset of $\events$,
-does a convex quantum IVPM~$\bar{\mu}':\events'\rightarrow\mathscr{I}$
-always has a non-empty core?
+\section{Quantum and Classical}
+
+\begin{lemma}Given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$
+for a given Hilbert space~$\Hilb$ of dimension~$d$, and a quantum
+IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Then, the function
+$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ defined by
+$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)$
+is a classical IVPM, where $\sum_{\ket{j}\in\emptyset}\proj{j}$ is
+defined to be $\mathbb{0}$.\end{lemma}
+\begin{proof}
+~
+\begin{itemize}
+\item $\bar{\mu}^{\Omega}(\emptyset)=\bar{\mu}\left(\sum_{\ket{j}\in\emptyset}\proj{j}\right)=\bar{\mu}\left(\mathbb{0}\right)=[0,0]$. 
+\item $\bar{\mu}^{\Omega}(\Omega)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)=[1,1]$. 
+\item For any event $E$, $\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega\backslash E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)$.
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
+events, we have $\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{\ket{j}\in\bigcup_{i=1}^{N}E_{i}}\proj{j}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)$.
+\end{itemize}
+\end{proof}
+The previous lemma suggests that given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
+if we only consider the events generated by $\Omega$, $\events^{\Omega}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
+then any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+behaves classically when restricting the domain on $\events'$, i.e.,
+consider $\bar{\mu}|_{\events^{\Omega}}$. In particular, if $\bar{\mu}$
+is convex, each $\bar{\mu}|_{\events^{\Omega}}$ has a non-empty core.
+However, when they are put together, there is no quantum probability
+measure~$\mu:\events\rightarrow\left[0,1\right]$ whose restriction
+$\mu|_{\events^{\Omega}}$ inside all the core of $\bar{\mu}|_{\events^{\Omega}}$.
+Notice that every events in $\events^{\Omega}$ are commuting, which
+consistent with the idea of the Kochen-Specker theorem, that each
+triple of commuting observables could be colored well, but we cannot
+color all observables which are not all commuting.\footnote{\yutsung{Since Bell's theorem only applies to entangled states, the
+exists of entangled states is another reason why quantum theory is
+different from a classical theory. However, defining product quantum
+IVPM is much harder, and beyond the discussion here.}}
+
+\begin{lemma}Given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ is a classical
+convex IVPM for any orthonormal basis~$\Omega$, then $\bar{\mu}$
+is a quantum convex IVPM.\end{lemma}
+\begin{proof}
+Pick two commuting events~$P_{0},P_{1}\in\events$. Since they are
+commuting, they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
+Since they are projectors, the eigenvalues of them are $0$ or $1$
+so that we can express them as $P_{0}=\sum_{\ket{j}\in E_{0}}\proj{j}$
+and $P_{1}=\sum_{\ket{j}\in E_{1}}\proj{j}$. Then, 
+\begin{eqnarray*}
+ &  & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
+ & = & \bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\vee\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)+\bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)\\
+ & = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cup E_{1}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cap E_{1}}\proj{j}\right)\\
+ & = & \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\\
+ & \subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\\
+ & = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\\
+ & = & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
+\end{eqnarray*}
+\end{proof}
+\begin{lemma}When the number of elements in $\Omega$ is less than
+or equal to 3, every classical convex IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$.\end{lemma}
+\begin{proof}
+Given two events~$E_{0},E_{1}\subseteq\Omega$, we want to verify
+\begin{equation}
+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}\label{eq:classical-convex}
+\end{equation}
+When $E_{0}\cap E_{1}=\emptyset$, equation~(\ref{eq:classical-convex})
+is a special case of equation~(\ref{eq:classical-include}). When
+$E_{0}\cup E_{1}=\Omega$, we have $E_{0}^{c}\cap E_{1}^{c}=\emptyset$,
+where $E_{0}^{c}=\Omega\backslash E_{0}$ and $E_{1}^{c}=\Omega\backslash E_{1}$.
+Thus, 
+\begin{eqnarray*}
+ &  & \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
+ & \Rightarrow & \left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
+ & \Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\
+ & \Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}
+\end{eqnarray*}
+When the number of elements in $\Omega$ is less than or equal to
+3, either $E_{0}\cap E_{1}=\emptyset$ or $E_{0}\cup E_{1}=\Omega$
+must happen so that $\bar{\mu}^{\Omega}$is convex.
+\end{proof}
+\begin{thm}Given a Hilbert space~$\Hilb$ of dimension~$3$, every
+quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is convex.\end{thm}
+\begin{proof}
+The direct consequence of the previous lemmas.
+\end{proof}
 

### 2017-02-02 prop.tex
prop.tex \section{Quantum and Classical} Modifying words...

@@
 then any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-behaves classically when restricting the domain on $\events'$, i.e.,
-consider $\bar{\mu}|_{\events^{\Omega}}$. In particular, if $\bar{\mu}$
-is convex, each $\bar{\mu}|_{\events^{\Omega}}$ has a non-empty core.
-However, when they are put together, there is no quantum probability
-measure~$\mu:\events\rightarrow\left[0,1\right]$ whose restriction
-$\mu|_{\events^{\Omega}}$ inside all the core of $\bar{\mu}|_{\events^{\Omega}}$.
-Notice that every events in $\events^{\Omega}$ are commuting, which
-consistent with the idea of the Kochen-Specker theorem, that each
-triple of commuting observables could be colored well, but we cannot
-color all observables which are not all commuting.\footnote{\yutsung{Since Bell's theorem only applies to entangled states, the
+behaves classically when restricting the domain on $\events^{\Omega}$,
+i.e., consider $\bar{\mu}|_{\events^{\Omega}}$. In particular, if
+$\bar{\mu}$ is convex, each $\bar{\mu}|_{\events^{\Omega}}$ has
+a non-empty core. However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$cannot
+be glued together, and gives a core element of $\bar{\mu}$. The inability
+of gluing core elements among commuting $\events^{\Omega}$ to non-commuting
+$\events$ is consistent with the idea of the Kochen-Specker theorem,
+that each triple of commuting observables could be colored well, but
+we cannot color all observables which are not all commuting.\footnote{\yutsung{Since Bell's theorem only applies to entangled states, the
 exists of entangled states is another reason why quantum theory is
@@
 
-\begin{lemma}Given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ is a classical
-convex IVPM for any orthonormal basis~$\Omega$, then $\bar{\mu}$
-is a quantum convex IVPM.\end{lemma}
+\begin{lemma}Given a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ are all
+convex for any orthonormal basis~$\Omega$, then $\bar{\mu}$ is
+convex.\end{lemma}
 \begin{proof}
@@
 so that we can express them as $P_{0}=\sum_{\ket{j}\in E_{0}}\proj{j}$
-and $P_{1}=\sum_{\ket{j}\in E_{1}}\proj{j}$. Then, 
+and $P_{1}=\sum_{\ket{j}\in E_{1}}\proj{j}$, where $E_{0},E_{1}\subseteq\Omega$.
+Then, 
 \begin{eqnarray*}
@@
 \begin{lemma}When the number of elements in $\Omega$ is less than
-or equal to 3, every classical convex IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$.\end{lemma}
+or equal to 3, every classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
+is convex.\end{lemma}
 \begin{proof}
@@
 \begin{thm}Given a Hilbert space~$\Hilb$ of dimension~$3$, every
-quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is convex.\end{thm}
+quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is convex.\end{thm}
 \begin{proof}

### 2017-02-02 prop.tex
prop.tex \section{Properties of Quantum IVPMs Decided by Their Range} Updating...

@@
 
-\begin{lemma}Consider a collection of intervals~$\mathscr{I}$ with
-a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ such that
-$\iota\left(0\right)=\left[0,0\right]$, $\iota\left(1\right)=\left[1,1\right]$,
-$\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and
-$\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.
+\begin{definition}We say a collection of intervals~$\mathscr{I}$
+with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is
+regular\footnote{\yutsung{''regular'' is just a random name pop into my mind...}}
+if 
+\begin{itemize}
+\item $\iota\left(0\right)=\left[0,0\right]$,
+\item $\iota\left(1\right)=\left[1,1\right]$, 
+\item $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and 
+\item $\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.
+\end{itemize}
+\end{definition}
+
+\begin{lemma}Consider a regular collection of intervals~$\mathscr{I}$
+with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
 Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
-we define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$.\end{lemma}
+a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
+$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM.\end{lemma}
 \begin{proof}
@@
 \end{proof}
-\begin{lemma}Consider a collection of intervals~$\mathscr{I}$ with
-a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ such that
-$\iota\left(0\right)=\left[0,0\right]$, $\iota\left(1\right)=\left[1,1\right]$,
-$\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and
-$\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.
-Then, there is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+\begin{lemma}Consider regular a collection of intervals~$\mathscr{I}$
+with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
+Then, there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.\end{lemma}
@@
 \end{proof}
-\footnote{\yutsung{Examples of $\mathscr{I}$ with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-such that $\iota\left(0\right)=\left[0,0\right]$, $\iota\left(1\right)=\left[1,1\right]$,
-$\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and
-$\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.}}
+\begin{example}For any positive odd integer~$n$, consider the collection
+of intervals~$\mathscr{I}_{n}=\left\{ \left[0,0\right],\left[1,1\right]\right\} \cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}$,
+and the map~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
+defined by 
+\[
+\iota_{n}\left(x\right)=\begin{cases}
+\left[0,0\right] & \textrm{, if }x=0\textrm{ ;}\\
+\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{k}{n}<x\le\frac{k+1}{n}<\frac{1}{2}\textrm{ ;}\\
+\left[\frac{1}{2}-\frac{1}{2n},\frac{1}{2}+\frac{1}{2n}\right] & \textrm{, if }\frac{1}{2}-\frac{1}{2n}<x<\frac{1}{2}+\frac{1}{2n}\textrm{ ;}\\
+\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{1}{2}<\frac{k}{n}\le x<\frac{k+1}{n}\textrm{ ;}\\
+\left[1,1\right] & \textrm{, if }x=1\textrm{ .}
+\end{cases}
+\]
+\end{example}
+\begin{proof}
+~
+\begin{itemize}
+\item $\iota\left(0\right)=\left[0,0\right]$.
+\item $\iota\left(1\right)=\left[1,1\right]$. 
+\item When $x=0$, $\iota\left(1-x\right)=\iota\left(1\right)=\left[1,1\right]=\left[1,1\right]-\iota\left(x\right)$.\\
+When $\frac{k}{n}<x\le\frac{k+1}{n}<\frac{1}{2}$, we have $1-\frac{k}{n}>1-x\ge1-\frac{k+1}{n}>\frac{1}{2}$
+so that $\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.\\
+When $\frac{1}{2}-\frac{1}{2n}<x<\frac{1}{2}+\frac{1}{2n}$, we have
+$\frac{1}{2}+\frac{1}{2n}>1-x>\frac{1}{2}-\frac{1}{2n}$ so that $\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.\\
+The rest of the cases are true because of symmetry.
+\item ...................
+\end{itemize}
+\end{proof}
 

### 2017-02-03 prop.tex
prop.tex \section{Properties of Quantum IVPMs Decided by Their Range} Fix typos...

@@
 regular\footnote{\yutsung{''regular'' is just a random name pop into my mind...}}
-if 
+if they satisfies the following properties.
 \begin{itemize}
-\item $\iota\left(0\right)=\left[0,0\right]$,
-\item $\iota\left(1\right)=\left[1,1\right]$, 
-\item $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and 
-\item $\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.
+\item $\iota\left(0\right)=\left[0,0\right]$.
+\item $\iota\left(1\right)=\left[1,1\right]$. 
+\item For any $x\in\left[0,1\right]$, $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$.
+\item For a set $\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
+if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota\left(x_{i}\right)$.
 \end{itemize}
@@
 \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
+we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)=\mu\left(\sum_{i=1}^{N}P_{i}\right)\in\left[0,1\right]$
+so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
 \end{itemize}
@@
 The rest of the cases are true because of symmetry.
-\item ...................
+\item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
+if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{1}+x_{2}\right)\subseteq\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
 \end{itemize}

### 2017-02-03 prop.tex
prop.tex \section{Quantum IVPMs Whose Core has an Unique Element} Updating...

@@
 
-\section{Properties of Quantum IVPMs Decided by Their Range}
+\section{Quantum IVPMs Whose Core has an Unique Element}
 
@@
 \end{proof}
-\begin{example}For any positive odd integer~$n$, consider the collection
-of intervals~$\mathscr{I}_{n}=\left\{ \left[0,0\right],\left[1,1\right]\right\} \cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}$,
+\begin{example}For any positive odd integer~$n$, the collection
+of intervals~$\mathscr{I}_{n}=\set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}$,
 and the map~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
@@
 \iota_{n}\left(x\right)=\begin{cases}
-\left[0,0\right] & \textrm{, if }x=0\textrm{ ;}\\
-\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{k}{n}<x\le\frac{k+1}{n}<\frac{1}{2}\textrm{ ;}\\
-\left[\frac{1}{2}-\frac{1}{2n},\frac{1}{2}+\frac{1}{2n}\right] & \textrm{, if }\frac{1}{2}-\frac{1}{2n}<x<\frac{1}{2}+\frac{1}{2n}\textrm{ ;}\\
-\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{1}{2}<\frac{k}{n}\le x<\frac{k+1}{n}\textrm{ ;}\\
-\left[1,1\right] & \textrm{, if }x=1\textrm{ .}
+\left[\frac{k}{n},\frac{k}{n}\right] & \textrm{, if }x=\frac{k}{n}\textrm{ ;}\\
+\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{k}{n}<x<\frac{k+1}{n}\textrm{ .}
 \end{cases}
 \]
-\end{example}
+is regular.\end{example}
 \begin{proof}
@@
 \item $\iota\left(1\right)=\left[1,1\right]$. 
-\item When $x=0$, $\iota\left(1-x\right)=\iota\left(1\right)=\left[1,1\right]=\left[1,1\right]-\iota\left(x\right)$.\\
-When $\frac{k}{n}<x\le\frac{k+1}{n}<\frac{1}{2}$, we have $1-\frac{k}{n}>1-x\ge1-\frac{k+1}{n}>\frac{1}{2}$
-so that $\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.\\
-When $\frac{1}{2}-\frac{1}{2n}<x<\frac{1}{2}+\frac{1}{2n}$, we have
-$\frac{1}{2}+\frac{1}{2n}>1-x>\frac{1}{2}-\frac{1}{2n}$ so that $\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.\\
-The rest of the cases are true because of symmetry.
+\item When $x=\frac{k}{n}$, we have $\iota\left(1-x\right)=\left[1-\frac{k}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.\\
+When $\frac{k}{n}<x<\frac{k+1}{n}$, we have $1-\frac{k}{n}>1-x>1-\frac{k+1}{n}$
+so that $\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.
 \item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
-if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{1}+x_{2}\right)\subseteq\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
+if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{1}+x_{2}\right)\subseteq\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$,
+and the rest can be done by the induction. 
+\begin{itemize}
+\item When $x_{1}=\frac{k_{1}}{n}$, we have $\iota\left(x_{1}+x_{2}\right)=\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota\left(x_{2}\right)=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
+\item When $\frac{k_{1}}{n}<x_{1}<\frac{k_{1}+1}{n}$ and $\frac{k_{2}}{n}<x_{2}<\frac{k_{2}+1}{n}$,
+we have $\frac{k_{1}+k_{2}}{n}<x_{1}+x_{2}<\frac{k_{1}+k_{2}+2}{n}$
+$\iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]=\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
+\end{itemize}
 \end{itemize}

### 2017-02-03 prop.tex
From: Tai, Yu-Tsung Sent: Thursday, February 02, 2017 21:37 To: Sabry, Amr A. <sabry@indiana.edu> Subject: RE: today
Kind of finish the appendix B and C...
Appendix B is what Gerardo wants about recover classical from quantum,
and prove every quantum IVPM is convex on a Hilbert space H of dimension
3.
Appendix C is what you want about there is always a quantum IVPM with an
unique core for a wide variety of intervals.
Although I am not sure where to put them in the main text so far...

Going to work on Appendix A, and how to update the main text...

Best regards,
Tai, Yu-Tsung (戴淯琮)
PhD student

@@
 we have $\frac{k_{1}+k_{2}}{n}<x_{1}+x_{2}<\frac{k_{1}+k_{2}+2}{n}$
-$\iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]=\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
+so that $\iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]=\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
 \end{itemize}

### 2017-02-03 prop.tex
prop.tex \section{Quantum Interval-valued Probability Measures} Updating

@@
 \end{equation}
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.38]{measure3} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
+1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
+plotted in $\mathbb{R}^{3}$. The red vector is $\ket{0}$, and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$.
+$\ket{0}$ is the normal vector of the plane so that for any vector~$\ket{\psi}$
+in the plane, we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$.
+For any other vector~$\ket{\psi}$, we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
+\end{figure}
+For example, Fig.~\ref{fig:three-dimensional-3-value} plots the
+1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$.
 This measure represents the beliefs of an experimenter with no prior
@@
 \]
-This measure however is ``better'' than the previous one in the sense
-that it might only be induced by $\ket{2}$ or the density matrix
-$\frac{\mathbb{1}}{3}$, but not by
-$\ket{1}$. 
-\end{example}
+This measure however is ``better'' than the previous one in the
+sense that it might only be induced by $\ket{2}$ or the density matrix
+$\frac{\mathbb{1}}{3}$, but not by $\ket{1}$. \end{example}
+
+In general, each two 1-dimensional projectors~$\proj{\psi_{0}}$
+and $\proj{\psi_{1}}$ mapping to $\imposs$ suggests $\bar{\mu}$
+might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
+in the Hilbert space of dimension 3. As we illustrated in figure~\ref{fig:three-dimensional-3-value},
+if $\bar{\mu}$ has a non-empty core, the states mapping to $\imposs$
+is contained a plane, which contains no area in the sphere.
 

### 2017-02-03 prop.tex
prop.tex Fixing typos...

@@
 if $\bar{\mu}$ has a non-empty core, the states mapping to $\imposs$
-is contained a plane, which contains no area in the sphere.
+is contained in a plane, which contains no area in the sphere. On
+the other hand, if the states mapping to $\imposs$ contain some area
+in the sphere, each plane intersecting the area suggests different
+pure state inducing $\bar{\mu}$. However, as the following example,
+these suggestions contradict with each others, which implies $\bar{\mu}$
+has an empty core. Furthermore, the larger the area, the more state
+vectors which are inconsistent with any particular Born rule probability
+measure. Therefore, the area of the 1-dimensional projectors mapping
+to $\imposs$ could indicate how much $\bar{\mu}$ deviate from the
+Born rule probability measures.
 
@@
 3, either $E_{0}\cap E_{1}=\emptyset$ or $E_{0}\cup E_{1}=\Omega$
-must happen so that $\bar{\mu}^{\Omega}$is convex.
+must happen so that $\bar{\mu}^{\Omega}$ is convex.
 \end{proof}
@@
 \end{proof}
-\begin{example}For any positive odd integer~$n$, the collection
-of intervals~$\mathscr{I}_{n}=\set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}$,
-and the map~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
+\begin{example}For any positive integer~$n$, the collection of
+intervals~$\mathscr{I}_{n}$ and the map~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
 defined by
-\[
-\iota_{n}\left(x\right)=\begin{cases}
+\begin{eqnarray*}
+\mathscr{I}_{n} & = & \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\
+\iota_{n}\left(x\right) & = & \begin{cases}
 \left[\frac{k}{n},\frac{k}{n}\right] & \textrm{, if }x=\frac{k}{n}\textrm{ ;}\\
-\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{k}{n}<x<\frac{k+1}{n}\textrm{ .}
+\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{k}{n}<x<\frac{k+1}{n}
 \end{cases}
-\]
+\end{eqnarray*}
 is regular.\end{example}

### 2017-02-04 prop.tex
prop.tex Here and theres...

@@
 particular, any quantum probability measure can be recast as an interval-valued
-measure using the three intervals $\left[0,0\right]$, $\left[1,1\right]$
-and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$ and $\left[1,1\right]$
-are called \imposs~and \necess~as before, and \emph{$\left[0,1\right]$}
-is called \unknown~because it provides no information. Given a quantum
-probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
-define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+measure using arbitrary small intervals as discussed in appendix~\ref{sec:Real-and-Interval}.
+However, to simplify our discussion, we will focus on only three intervals
+$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
+where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
+\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
+it provides no information. Given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
+we define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
@@
 \end{equation}
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.38]{measure3} 
-\par\end{centering}
-\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
-1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
-plotted in $\mathbb{R}^{3}$. The red vector is $\ket{0}$, and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$.
-$\ket{0}$ is the normal vector of the plane so that for any vector~$\ket{\psi}$
-in the plane, we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$.
-For any other vector~$\ket{\psi}$, we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
-\end{figure}
 For example, Fig.~\ref{fig:three-dimensional-3-value} plots the
@@
 the \emph{core} and \emph{convexity} of a probability measure as follows.
-
-\begin{definition}
-  Given a quantum interval-valued probability
-  measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.38]{measure3} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
+1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
+plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
+and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$. $\ket{0}$
+is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$
+for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
+we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
+\end{figure}
+
+\begin{definition} Given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$: 
 \begin{itemize}
 \item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$. 
-\item $\bar{\mu}$ is called convex if
-  $\bar{\mu}\left(P_{0}\vee
-    P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+\item $\bar{\mu}$ is called convex if $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
 for all commuting $P_{0},P_{1}\in\events$. 
@@
 the other hand, if the states mapping to $\imposs$ contain some area
-in the sphere, each plane intersecting the area suggests different
-pure state inducing $\bar{\mu}$. However, as the following example,
-these suggestions contradict with each others, which implies $\bar{\mu}$
-has an empty core. Furthermore, the larger the area, the more state
-vectors which are inconsistent with any particular Born rule probability
-measure. Therefore, the area of the 1-dimensional projectors mapping
-to $\imposs$ could indicate how much $\bar{\mu}$ deviate from the
-Born rule probability measures.
+in the sphere as in figure~\ref{fig:three-dimensional-3-value-1},
+each plane intersecting the area suggests different pure state inducing
+$\bar{\mu}$. However, these suggestions contradict with each others,
+which implies $\bar{\mu}$ has an empty core. Furthermore, the larger
+the area, the more state vectors which are inconsistent with any particular
+Born rule probability measure. Therefore, the area of the 1-dimensional
+projectors mapping to $\imposs$ could indicate how much $\bar{\mu}$
+deviate from the Born rule probability measures.
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.38]{measure3-1} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-3-value-1}Plotted in $\mathbb{R}^{3}$,
+assume the 1-dimensional projectors whose latitude is higher than
+the green circle maps to $\imposs$ by $\bar{\mu}$, for example $\bar{\mu}\left(\proj{0'}\right)=\bar{\mu}\left(\proj{2'}\right)=\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$.
+Since $\ket{0'}$ and $\ket{2'}$ are in a plane, $\bar{\mu}$ might
+be induced by its normal vector~$\ket{1'}$. Also, since $\ket{0'}$
+and $\ket{\bar{2}}$ are in a plane, $\bar{\mu}$ might be induced
+by its normal vector~$\ket{\bar{1}}$. However, $\mu_{\ket{1'}}^{B}$
+is inconsistent with $\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$,
+and $\mu_{\ket{\bar{1}}}^{B}$ is inconsistent with $\bar{\mu}\left(\proj{2'}\right)=\imposs$.
+Therefore, $\bar{\mu}$ has an empty-core.}
+\end{figure}
 
@@
 
-\section{Quantum and Classical}
+\section{Quantum and Classical Interval-valued Probability Measures}
 
@@
 
-\section{Quantum IVPMs Whose Core has an Unique Element}
+\section{\label{sec:Real-and-Interval}Quantum Real-valued and Interval-valued
+Probability Measures}
 

### 2017-02-04 prop.tex
prop.tex \appendix Updating...

@@
 
-\section{Increasing the Measurement Resource}
+\section{Interval-valued Frame Functions\label{sec:Interval-valued-Frame-Functions}}
 
@@
 
-\begin{lemma}An interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
-satisfies the following properties:
+\begin{lemma}\label{lemma:interval-valued-frame-function}An interval-valued
+frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ satisfies
+the following properties:
 \begin{itemize}
@@
 
-If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the above
-case 1 - 3 so that $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
-no area in $S^{2}$.\footnote{Notice that we only discuss the part of $\bar{f}^{-1}\left(\imposs\right)$
-in $S^{2}$. In general, we could discuss the whole $\bar{f}^{-1}\left(\imposs\right)\subseteq\mathbb{C}S^{2}$.
-However, restricting to $S^{2}$ enable us to visualize and imagine
-easily. Also, if a interval-valued frame function~$\bar{f}$ has
-an empty core when restricting to $S^{2}$, $\bar{f}$ has an empty
-core on the original space as well. So restricting to $S^{2}$ still
-provides some valid results.} In contrast, if $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
-some area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
+\section{Real Interval-valued Frame Functions}
+
+In order to simplify the discussion, we call a function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$
+satisfying conditions in lemma~\ref{lemma:interval-valued-frame-function}
+a real interval-valued frame function. Obviously, any results in section~\ref{sec:Interval-valued-Frame-Functions}
+still hold if we replace every ``complex'' by ``real,'' in particular,
+replace every $\mathbb{C}S^{2}$ by $S^{2}$. Furthermore, since restricting
+the domain of a complex interval-valued frame function to $S^{2}$
+gives a real interval-valued frame function, if we prove there is
+no real interval-valued frame function satisfying a condition, then
+there must be no complex interval-valued frame function satisfying
+a corresponding condition. From now on, when we write an interval-valued
+frame function~$\bar{f}$, we would always means a real interval-valued
+frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$ without other
+specification.
+
+If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the case
+1 - 3 in the end of section~\ref{sec:Interval-valued-Frame-Functions}
+so that $\bar{f}^{-1}\left(\imposs\right)$ contains no area in $S^{2}$.
+In contrast, if $\bar{f}^{-1}\left(\imposs\right)$ contains some
+area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
 has an empty core. Furthermore, the larger the area, the more state
 vectors which are inconsistent with any particular Born rule frame
-function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
+function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)$
 could indicate how much $\bar{f}$ deviate from the Born rule frame
 functions. In the following paragraphs, we will establish that if
-the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ is big,
-then the interval~$\mathscr{I}$ must be coarse. Therefore, if the
-interval~$\mathscr{I}$ is finer, then the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
-would be smaller so that $\bar{f}$ is closer to a Born rule frame
-function.
-
-In order to simplify the discussion, consider the center of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
+the area of $\bar{f}^{-1}\left(\imposs\right)$ is big, then the interval~$\mathscr{I}$
+must be coarse. Therefore, if the interval~$\mathscr{I}$ is finer,
+then the area of $\bar{f}^{-1}\left(\imposs\right)$ would be smaller
+so that $\bar{f}$ is closer to a Born rule frame function.
+
+In order to simplify the discussion, consider the center of $\bar{f}^{-1}\left(\imposs\right)$
 as the north pole, and assume $\bar{f}$ maps every state whose latitude
@@
 \begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
-north pole~$\ket{0}\in S^{2}$, then $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
-denotes the latitude of $\ket{\psi}$. Conversely, $\theta^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\theta\left(\ket{\psi}\right)\in I}$.
-For example, $\theta^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\theta\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
+north pole~$\ket{0}\in S^{2}$, then $\angle\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
+denotes the latitude of $\ket{\psi}$. Conversely, $\angle^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\angle\left(\ket{\psi}\right)\in I}$.
+For example, $\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
 contains all states whose latitude is larger than $\theta_{0}$.\end{definition}
@@
 \begin{lemma}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,
-if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\theta^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
-then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\theta^{-1}\left(\left[0,\theta_{0}\right]\right)$,
+if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
+then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
 $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.\end{lemma}
@@
 
-\section{\label{sec:Real-and-Interval}Quantum Real-valued and Interval-valued
-Probability Measures}
+\section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}}
 

### 2017-02-04 prop.tex
prop.tex \section{Real Interval-valued Frame Functions} Updating...

@@
 satisfying conditions in lemma~\ref{lemma:interval-valued-frame-function}
-a real interval-valued frame function. Obviously, any results in section~\ref{sec:Interval-valued-Frame-Functions}
+a real interval-valued frame function. Obviously, any results in appendix~\ref{sec:Interval-valued-Frame-Functions}
 still hold if we replace every ``complex'' by ``real,'' in particular,
@@
 there must be no complex interval-valued frame function satisfying
-a corresponding condition. From now on, when we write an interval-valued
-frame function~$\bar{f}$, we would always means a real interval-valued
-frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$ without other
-specification.
+the corresponding condition. From now on, when we write an interval-valued
+frame function~$\bar{f}$ without other specification, we would always
+means a real interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$.
 
 If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the case
-1 - 3 in the end of section~\ref{sec:Interval-valued-Frame-Functions}
+1 - 3 in the end of appendix~\ref{sec:Interval-valued-Frame-Functions}
 so that $\bar{f}^{-1}\left(\imposs\right)$ contains no area in $S^{2}$.
@@
 the area of $\bar{f}^{-1}\left(\imposs\right)$ is big, then the interval~$\mathscr{I}$
-must be coarse. Therefore, if the interval~$\mathscr{I}$ is finer,
-then the area of $\bar{f}^{-1}\left(\imposs\right)$ would be smaller
-so that $\bar{f}$ is closer to a Born rule frame function.
+must be coarse. In another word, if the interval~$\mathscr{I}$ is
+finer, then the area of $\bar{f}^{-1}\left(\imposs\right)$ would
+be smaller so that $\bar{f}$ is closer to a Born rule frame function.
 

### 2017-02-05 prop.tex
prop.tex \section{Real Interval-valued Frame Functions} Updating...

@@
 
-\begin{lemma}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,
+\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,
 if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
@@
 $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.\end{lemma}
+\begin{proof}
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.38]{real-frame-1} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
+the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
+\end{figure}
+We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
+Let the yellow circle is the states whose latitude is $\theta_{0}$.
+Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
+In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
+Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
+basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
+\begin{eqnarray*}
+\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq & \bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
+\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq & \bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
+\end{eqnarray*}
+so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
+By the same reason, for any state~$\ket{\psi}$ in the dotted black
+circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
+Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
+the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
+and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
+if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
+then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.
+
+Moreover, the same argument can apply on the great circle which is
+not longitude. Since $\ket{\bar{1}}$ is the normal vector of the
+gray circle which includes $\ket{2}$ and $\ket{\bar{2}}$, we have
+$\bar{f}\left(\ket{2}\right)=\left[1,1\right]-\bar{f}\left(\ket{\bar{1}}\right)=\bar{f}\left(\ket{\bar{2}}\right)$.
+In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
+even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are not in the same
+longitude, then $\bar{f}\left(\ket{\psi_{0}}\right)$ and $\bar{f}\left(\ket{\psi_{1}}\right)$
+are still the same. Thus the lemma is proved.
+\end{proof}
 

### 2017-02-05 prop.tex
prop.tex \section{Real Interval-valued Frame Functions} Updating...

@@
 
+\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,
+if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
+then $\theta_{0}>\frac{\pi}{4}$.\end{thm}
+\begin{proof}
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.38]{real-frame-2} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-real-frame-2}This figure is used in
+the proof of theorem~\ref{thm:pi-div-4}.}
+\end{figure}
+We are going to prove by contradiction. Suppose $\theta_{0}\le\frac{\pi}{4}$,
+as illustrated in figure~\ref{fig:three-dimensional-real-frame-2}. 
+\end{proof}
 \begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,

### 2017-02-05 prop.tex
prop.tex \section{Real Interval-valued Frame Functions} Updating...

@@
 \end{figure}
-We are going to prove by contradiction. Suppose $\theta_{0}\le\frac{\pi}{4}$,
-as illustrated in figure~\ref{fig:three-dimensional-real-frame-2}. 
+We are going to prove by contradiction. Suppose $\theta_{0}\le\frac{\pi}{4}$.
+As illustrated in figure~\ref{fig:three-dimensional-real-frame-2},
+the green circle represent the states whose latitude is $\theta_{0}$
+so that .every state above it maps to $\imposs$, for example, 
 \end{proof}

### 2017-02-05 prop.tex
prop.tex \section{Real Interval-valued Frame Functions} Write another proof...

--- 2017-02-05 prop.tex
@@
 
-\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,
+\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
+and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
 if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
-then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
+then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$,
 $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.\end{lemma}
@@
 are still the same. Thus the lemma is proved.
+\end{proof}
+\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
+and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
+if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
+then $\theta_{0}>\frac{\pi}{4}$.\end{thm}
+\begin{proof}
+We are going to prove by contradiction. Suppose $\theta_{0}\le\frac{\pi}{4}$,
+we have $\left[\theta_{0},\frac{\pi}{2}\right]\cap\left[0,\frac{\pi}{2}-\theta_{0}\right]=\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\ne\emptyset$.
+Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\right)$,
+we have $\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$. Then, by lemma~\ref{lemma:imposs-imply-same-value},
+for any $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$,
+$\bar{f}\left(\ket{\psi_{1}}\right)=\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$.
+In another word, $\bar{f}$ maps every state to $\imposs$, and cannot
+be an interval-valued frame function.
 \end{proof}

### 2017-02-05 prop.tex
prop.tex \section{Real Interval-valued Frame Functions} Updating...

@@
 if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
-then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$,
-$\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.\end{lemma}
+then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
+for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$.\end{lemma}
 \begin{proof}
@@
 basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
-\begin{eqnarray*}
-\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq & \bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
-\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq & \bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
-\end{eqnarray*}
+\begin{equation}
+\begin{aligned}\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
+\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
+\end{aligned}
+\label{eq:includes}
+\end{equation}
 so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
@@
 longitude, then $\bar{f}\left(\ket{\psi_{0}}\right)$ and $\bar{f}\left(\ket{\psi_{1}}\right)$
-are still the same. Thus the lemma is proved.
+are still the same.
+
+Thus, we could plug $\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)=\left[l_{0},r_{0}\right]$
+into equation~(\ref{eq:includes}), and get 
+\begin{eqnarray*}
+ &  & \left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\\
+ & \Rightarrow & l_{0}+r_{0}=1
+\end{eqnarray*}
+Also, we have 
+\begin{eqnarray*}
+ &  & 1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\\
+ & \Rightarrow & l_{0}\le\frac{1}{2}\le r_{0}
+\end{eqnarray*}
+Thus the lemma is proved.
 \end{proof}
@@
 be an interval-valued frame function.
+\end{proof}
+\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left(\frac{\pi}{4},\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)\right]$
+and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
+if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
+then $\unknown\in\mathscr{I}$.\end{thm}
+\begin{proof}
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.38]{real-frame-2} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-real-frame-2}This figure is used in
+the proof of theorem~\ref{thm:arcsin-one-over-sqrt-three}. The latitude
+of the yellow circle is $\theta_{0}=\frac{\pi}{2}-\frac{\pi}{5}\in\left(\frac{\pi}{4},\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)\right]$,
+and the latitude of the green circle is $\frac{\pi}{5}=\frac{\pi}{2}-\theta_{0}$.}
+\end{figure}
+We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-2},
+where the latitude of of the yellow circle is $\theta_{0}$ and the
+latitude of of the green circle is $\frac{\pi}{2}-\theta_{0}$. Therefore,
+$\bar{f}$ should map any state above the yellow circle to $\imposs$
+and any states between the green circle and the equator to the same
+interval, say, $\left[l_{0},1-l_{0}\right]$, where $0\le l_{0}\le\frac{1}{2}$. 
 \end{proof}

### 2017-02-06 prop.tex
prop.tex \section{Real Interval-valued Frame Functions} Typed a proof...

@@
 denotes the latitude of $\ket{\psi}$. Conversely, $\angle^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\angle\left(\ket{\psi}\right)\in I}$.
-For example, $\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
+For example, the north pole has the latitude $0$, the equator has
+the the latitude $\frac{\pi}{2}$, and $\angle^{-1}\left(\left[0,\theta_{0}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
 contains all states whose latitude is larger than $\theta_{0}$.\end{definition}
@@
 and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
-if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
+if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
 then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
-for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$.\end{lemma}
+for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]\right)$.\end{lemma}
 \begin{proof}
@@
 $\bar{f}\left(\ket{2}\right)=\left[1,1\right]-\bar{f}\left(\ket{\bar{1}}\right)=\bar{f}\left(\ket{\bar{2}}\right)$.
-In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
+In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]\right)$,
 even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are not in the same
@@
 and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
-if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
-then $\theta_{0}>\frac{\pi}{4}$.\end{thm}
+if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
+then $\theta_{0}<\frac{\pi}{4}$.\end{thm}
 \begin{proof}
-We are going to prove by contradiction. Suppose $\theta_{0}\le\frac{\pi}{4}$,
-we have $\left[\theta_{0},\frac{\pi}{2}\right]\cap\left[0,\frac{\pi}{2}-\theta_{0}\right]=\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\ne\emptyset$.
-Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\right)$,
-we have $\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$. Then, by lemma~\ref{lemma:imposs-imply-same-value},
-for any $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$,
-$\bar{f}\left(\ket{\psi_{1}}\right)=\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$.
-In another word, $\bar{f}$ maps every state to $\imposs$, and cannot
-be an interval-valued frame function.
+We are going to prove by contradiction. Suppose $\theta_{0}\ge\frac{\pi}{4}$,
+we have $\left[0,\theta_{0}\right]\cap\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]=\left[\frac{\pi}{2}-\theta_{0},\theta_{0}\right]\ne\emptyset$.
+Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\theta_{0}\right]\right)$,
+by lemma~\ref{lemma:imposs-imply-same-value}, we have $\imposs=\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]$,
+where $l_{0}\in\left[0,\frac{\pi}{2}\right]$. A contradiction!
 \end{proof}
-\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left(\frac{\pi}{4},\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)\right]$
+\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left[\arcsin\left(\frac{1}{\sqrt{3}}\right),\frac{\pi}{4}\right)$
 and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
-if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
+if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
 then $\unknown\in\mathscr{I}$.\end{thm}
@@
 the proof of theorem~\ref{thm:arcsin-one-over-sqrt-three}. The latitude
-of the yellow circle is $\theta_{0}=\frac{\pi}{2}-\frac{\pi}{5}\in\left(\frac{\pi}{4},\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)\right]$,
-and the latitude of the green circle is $\frac{\pi}{5}=\frac{\pi}{2}-\theta_{0}$.}
+of the yellow circle is $\theta_{0}\in\left[\arcsin\left(\frac{1}{\sqrt{3}}\right),\frac{\pi}{4}\right)$,
+and the latitude of the green circle is $\frac{\pi}{2}-\theta_{0}$.}
 \end{figure}
@@
 and any states between the green circle and the equator to the same
-interval, say, $\left[l_{0},1-l_{0}\right]$, where $0\le l_{0}\le\frac{1}{2}$. 
+interval, say, $\left[l_{0},1-l_{0}\right]$, where $0\le l_{0}\le\frac{1}{2}$
+by lemma~\ref{lemma:imposs-imply-same-value}.
+
+When $\theta_{0}\ge\arcsin\left(\frac{1}{\sqrt{3}}\right)$, the latitude
+of the green circle is $\theta_{0}\le\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)$.
+Now consider three states~$\ket{A}$, $\ket{B}$, and $\ket{C}$
+whose latitude is $\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)$
+so that they are below the green circle, and these three states form
+an equilateral triangle whose center is $H$. Since the latitude of
+this triangle is $\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)$,
+we know $\overline{OH}=\frac{1}{\sqrt{3}}$, where $O$ is the center
+of the sphere. By the Pythagorean theorem, $\overline{HA}=\overline{HB}=\sqrt{\frac{2}{3}}$.
+Notice that $\triangle HAB$ is an isosceles triangle with $\angle AHB=\frac{2\pi}{3}$,
+we have $\overline{AB}=\sqrt{2}$. Since $\overline{OA}=\overline{OB}=1$
+and $\overline{AB}=\sqrt{2}$, $\triangle OAB$ is an isosceles right
+triangle with $\angle AHB=\frac{\pi}{2}$, i.e., $\ket{A}$ and $\ket{B}$
+are orthogonal. Applying the same reason on all $\ket{A}$, $\ket{B}$,
+and $\ket{C}$, $\left\{ \ket{A},\ket{B},\ket{C}\right\} $ is an
+orthonormal basis.
+
+Since $\left\{ \ket{A},\ket{B},\ket{C}\right\} $ is an orthonormal
+basis and $\bar{f}\left(\ket{A}\right)=\bar{f}\left(\ket{B}\right)=\bar{f}\left(\ket{C}\right)=\left[l_{0},1-l_{0}\right]$,
+we have the following inequalities by lemma~\ref{lemma:interval-valued-frame-function}.
+\begin{eqnarray*}
+1\in\left[3l_{0},3-3l_{0}\right] & \Rightarrow & l_{0}\le\frac{1}{3}\\
+\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right] & \Rightarrow & l_{0}\le0
+\end{eqnarray*}
+Recall that $0\le l_{0}\le\frac{1}{2}$. Therefore, $l_{0}=0$, that
+is, $\unknown=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$.
 \end{proof}

### 2017-02-06 prop.tex
prop.tex \section{Quantum Interval-valued Probability Measures} Updating

@@
 
+In this sense, we found that the area of the 1-dimensional projectors
+mapping to $\imposs$ depends on the maximal length of the intervals,
+which represents the ability of measurement equipment. In particular,
+we have the following results whose details are described in appendix~\ref{sec:Real-Interval-valued-Frame}.
+\begin{itemize}
+\item The radius of any disk inside the area of the 1-dimensional projectors
+mapping to $\imposs$ must smaller than $\frac{\pi}{4}$ (theorem~\ref{thm:pi-div-4}).
+\item When the radius of any disk inside the area of the 1-dimensional projectors
+mapping to $\imposs$ between $\arcsin\left(\frac{1}{\sqrt{3}}\right)$
+and $\frac{\pi}{4}$, we have $\unknown\in\mathscr{I}$, i.e., $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=1$
+(theorem~\ref{thm:arcsin-one-over-sqrt-three}).
+\item When the radius of any disk inside the area of the 1-dimensional projectors
+mapping to $\imposs$ between $\frac{\pi}{6}$ and $\arcsin\left(\frac{1}{\sqrt{3}}\right)$,
+we have $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=\frac{1}{3}$
+(to be typed...).
+\end{itemize}
 In general, we conjecture that if the measurement equipment is made

### 2017-02-06 prop.iop.tex
prop.iop.tex \documentclass[english,12pt]{iopart} Compiled without error

--- 2017-02-06 prop.tex
@@
-\documentclass{article}
+\documentclass[english,12pt]{iopart}
 \usepackage[ backend=biber]{biblatex}
@@
 \usepackage[utf8]{inputenc}
-\usepackage{amsmath}
 \usepackage{amssymb}
@@
 \usepackage{verbatim}
+\usepackage{iopams}
+\usepackage{setstack}
 
@@
 \newcommand{\ps}{\texttt{+}}
-\newcommand{\ms}{\texttt{-}}
+\newcommand{\minus}{\texttt{-}}
 \newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}
-\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
-\newcommand{\rme}{\mathrm{e}}
-\newcommand{\rmi}{\mathrm{i}}
 
@@
 \begin{equation}
-\iota(x)=\begin{cases}
-\necess & \textrm{if }x=1\textrm{ ;}\\
-\imposs & \textrm{if }x=0\textrm{ ;}\\
-\unknown & \textrm{otherwise.}
-\end{cases}\label{eq:homomorphism}
+\iota(x)=\cases{
+\necess & if $x=1$ ;\\
+\imposs & if $x=0$ ;\\
+\unknown & otherwise.
+}\label{eq:homomorphism}
 \end{equation}
@@
   $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and
-  $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$. The definition of
+  $\ket{\minus}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$. The definition of
   $\bar{\mu}$ below refers to Fig.~\ref{fig:three-dimensional-4-value}
@@
   and
-  $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
+  $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\minus}+\cos\theta\ket{2}$,
   where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
@@
 \end{proof}
-\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
+\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}\alpha_{0}\\
 \alpha_{1}\\
 \alpha_{2}
-\end{pmatrix}$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\begin{pmatrix}\beta_{0}\\
+\end{array}\right)$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\left(\begin{array}{c}\beta_{0}\\
 \beta_{1}\\
 \beta_{2}
-\end{pmatrix}$, their cross product is defined as follow: 
+\end{array}\right)$, their cross product is defined as follow: 
 \[
-\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\begin{vmatrix}\alpha_{1}^{*} & \beta_{1}^{*}\\
+\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\left|\begin{array}{cc}\alpha_{1}^{*} & \beta_{1}^{*}\\
 \alpha_{2}^{*} & \beta_{2}^{*}
-\end{vmatrix}\ket{0}+\begin{vmatrix}\alpha_{2}^{*} & \beta_{2}^{*}\\
+\end{array}\right|\ket{0}+\left|\begin{array}{cc}\alpha_{2}^{*} & \beta_{2}^{*}\\
 \alpha_{0}^{*} & \beta_{0}^{*}
-\end{vmatrix}\ket{1}+\begin{vmatrix}\alpha_{0}^{*} & \beta_{0}^{*}\\
+\end{array}\right|\ket{1}+\left|\begin{array}{cc}\alpha_{0}^{*} & \beta_{0}^{*}\\
 \alpha_{1}^{*} & \beta_{1}^{*}
-\end{vmatrix}\ket{2}\textrm{ ,}
+\end{array}\right|\ket{2}\textrm{ ,}
 \]
-where $\begin{vmatrix}\alpha & \beta\\
+where $\left|\begin{array}{cc}\alpha & \beta\\
 \alpha' & \beta'
-\end{vmatrix}=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
+\end{array}\right|=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
 cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
@@
 To prove the other direction, consider the linear transformation~$T:\mathbb{C}^{3}\rightarrow\mathbb{C}^{2}$
-defined by $T\left(\ket{\varphi}\right)=\begin{pmatrix}\ip{\psi}{\varphi}\\
+defined by $T\left(\ket{\varphi}\right)=\left(\begin{array}{c}\ip{\psi}{\varphi}\\
 \ip{\phi}{\varphi}
-\end{pmatrix}$. Since $\ket{\psi}\nparallel\ket{\phi}$, we have $\mathrm{rank}\left(T\right)=2$.
+\end{array}\right)$. Since $\ket{\psi}\nparallel\ket{\phi}$, we have $\mathrm{rank}\left(T\right)=2$.
 Together with the rank equation~\cite{FraleighBeauregard1995}, we
@@
 \begin{equation}
-\begin{aligned}\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
+\eqalign{\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
 \left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
-\end{aligned}
+}
 \label{eq:includes}
@@
 \mathscr{I}_{n} & = & \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\
-\iota_{n}\left(x\right) & = & \begin{cases}
-\left[\frac{k}{n},\frac{k}{n}\right] & \textrm{, if }x=\frac{k}{n}\textrm{ ;}\\
-\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{k}{n}<x<\frac{k+1}{n}
-\end{cases}
+\iota_{n}\left(x\right) & = & \cases{
+\left[\frac{k}{n},\frac{k}{n}\right] & , if $x=\frac{k}{n}$ ;\\
+\left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ .
+}
 \end{eqnarray*}

### 2017-02-08 prop_iop.tex
prop_iop.tex Rename to follow the guideline...
Rename the figures according to the guild line...
prop_iop.tex Updated until the Guildline section 4...

--- 2017-02-06 prop.iop.tex
@@
-\documentclass[english,12pt]{iopart}
+\documentclass[12pt]{iopart}
 \usepackage[ backend=biber]{biblatex}
-\addbibresource{proposal/prop.bib}
+\addbibresource{prop.bib}
 \ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
@@
 \begin{document}
-\title{Measurement and Probability in Fuzzy Quantum Theories}
-\date{\today}
-\maketitle
+\title{Measurement and Probability in Fuzzy Quantum
+Theories}
+
+\author{Andrew J Hanson$^{1}$, Gerardo Ortiz$^{2}$,
+Amr Sabry$^{1}$ and Yu-Tsung Tai$^{3,1}$}
+\address{$^{1}$ School of Informatics and Computing, Indiana
+University, Bloomington, IN 47405, USA}
+\address{$^{2}$ Department of Physics, Indiana University, Bloomington, IN
+47405, USA}
+\address{$^{3}$ Department of Mathematics, Indiana University, Bloomington,
+IN 47405, USA}
+\ead{ortizg@indiana.edu}
+\begin{abstract}
+\today
+\end{abstract}
+\pacs{03.65.-w, 03.65.Ta, 02.40.Dr, 02.50.Cw, 02.50.Le}
+\noindent{\it Keywords\/}: {Finite precision measurement, the Born rule, Gleason's theorem, interval-valued
+probability, discrete quantum theory}
+
+\submitto{\jpa}
 
@@
 Turing machine $\mathit{TM}_{i}$ halts or not. Such numbers cannot be
-computed. This interval also includes numbers like $\frac{\pi}{4}$
+computed. This interval also includes numbers like $\pi / 4$
 which can only be computed with increasingly large resources as the
@@
 $\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
-the relative frequency~$\frac{1}{M}\sum_{i=1}^{M}x_{i}$ with the
+the relative frequency~$\sum_{i=1}^{M}x_{i} / M$ with the
 probability converging to one as $M$ goes to infinity, i.e.,
@@
 \end{equation}
-For example, Fig.~\ref{fig:three-dimensional-3-value} plots the
+For example, figure~\ref{fig:three-dimensional-3-value} plots the
 1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$.
@@
 \begin{centering}
-\includegraphics[scale=0.38]{measure3} 
+\includegraphics[scale=0.38]{figure1.eps} 
 \par\end{centering}
@@
 \begin{center}
-\includegraphics[scale=0.38]{proposal/measure4.pdf}
+\includegraphics[scale=0.38]{figure2.eps}
 \end{center}
@@
   $\ket{\minus}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$. The definition of
-  $\bar{\mu}$ below refers to Fig.~\ref{fig:three-dimensional-4-value}
+  $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-4-value}
   which plots the 1-dimensional projectors:
@@
 \begin{centering}
-\includegraphics[scale=0.38]{measure3-1} 
+\includegraphics[scale=0.38]{figure3.eps} 
 \par\end{centering}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage{}%
-\begin{comment}
- \bibliographystyle{plain}
-\bibliography{proposal/prop}
-
-\end{comment}
-\printbibliography
-
+\ack
+
+Anyone who has discussed this with us?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Interval-valued Frame Functions\label{sec:Interval-valued-Frame-Functions}}
@@
 
-\section{Real Interval-valued Frame Functions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Real Interval-valued Frame Functions\label{sec:Real-Interval-valued-Frame}}
 
@@
 \begin{centering}
-\includegraphics[scale=0.38]{real-frame-1} 
+\includegraphics[scale=0.38]{figureb1.eps} 
 \par\end{centering}
@@
 \begin{centering}
-\includegraphics[scale=0.38]{real-frame-2} 
+\includegraphics[scale=0.38]{figureb2.eps} 
 \par\end{centering}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Quantum and Classical Interval-valued Probability Measures}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage{}%
+\begin{comment}
+ \bibliographystyle{plain}
+\bibliography{prop}
+
+\end{comment}
+\printbibliography
+
 \end{document}

### 2017-02-09 prop_iop.tex
prop_iop.tex Fix all fractions according "5.1. Two-line constructions"

@@
 \pmeas(\emptyset) & = & 0\\
-\pmeas(\{HH\}) & = & 1/3\\
+\pmeas(\{HH\}) & = & \frac{1}{3}\\
 \pmeas(\{HT\}) & = & 0\\
-\pmeas(\{TH\}) & = & 2/3\\
+\pmeas(\{TH\}) & = & \frac{2}{3}\\
 \pmeas(\{TT\}) & = & 0\\
-\pmeas(\{HH,HT\}) & = & 1/3\\
+\pmeas(\{HH,HT\}) & = & \frac{1}{3}\\
 \pmeas(\{HH,TH\}) & = & 1\\
-\pmeas(\{HH,TT\}) & = & 1/3
+\pmeas(\{HH,TT\}) & = & \frac{1}{3}
 \end{array} & \begin{array}{rcl}
-\pmeas(\{HT,TH\}) & = & 2/3\\
+\pmeas(\{HT,TH\}) & = & \frac{2}{3}\\
 \pmeas(\{HT,TT\}) & = & 0\\
-\pmeas(\{TH,TT\}) & = & 2/3\\
+\pmeas(\{TH,TT\}) & = & \frac{2}{3}\\
 \pmeas(\{HH,HT,TH\}) & = & 1\\
-\pmeas(\{HH,HT,TT\}) & = & 1/3\\
+\pmeas(\{HH,HT,TT\}) & = & \frac{1}{3}\\
 \pmeas(\{HH,TH,TT\}) & = & 1\\
-\pmeas(\{HT,TH,TT\}) & = & 2/3\\
+\pmeas(\{HT,TH,TT\}) & = & \frac{2}{3}\\
 \pmeas(\{HH,HT,TH,TT\}) & = & 1
@@
 the needle crossing a line is
-$\frac{2\ell}{\pi
-  h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
+$2\ell/\left(\pi h\right)$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
 Consider an experimental setup consisting of a collection of $M$
@@
 line, thus estimating the probability of a needle crossing a line to
-be $\frac{M_c}{M}$. In an actual experiment with $500$ needles and the
-ratio $\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$
+be $M_c/M$. In an actual experiment with $500$ needles and the
+ratio $\ell/h=0.75$~\cite{Hall1873}, it was found that $236$
 crossed a line so the relative frequency is $0.472$ whereas the
@@
 experiment with $5000$ needles and the ratio
-$\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, the relative frequency was
+$\ell/h=0.8$~\cite{Uspensky1937}, the relative frequency was
 calculated to be $0.5064$ whereas the idealized mathematical
 probability is $0.5092\ldots$. We see that the observed probability
-approaches $\frac{2\ell}{\pi h}$ but only if \emph{larger and larger
+approaches $2\ell/\left(\pi h\right)$ but only if \emph{larger and larger
   resources} are expended. These resource considerations suggest that
@@
 with 3 needles, it is not sensible to retain 100 digits in the
-expansion of $\frac{2\ell}{\pi h}$.
+expansion of $2\ell/\left(\pi h\right)$.
 
@@
 an experiment with $3204$ needles and the ratio
-$\frac{\ell}{h}=0.6$~\cite{DeMorgan1872}, $1213$ needles clearly
+$\ell/h=0.6$~\cite{DeMorgan1872}, $1213$ needles clearly
 crossed a line and $11$ needles were close enough to plausibly be
@@
 and $[1,1]$ which we call \necess. Using these new values, we can
-modify the probability measure of Ex.~\ref{ex1} by mapping each
+modify the probability measure of example~\ref{ex1} by mapping each
 numeric value to the smallest sub-interval containing it to get the
@@
 \begin{eqnarray*}
-\bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})
+& & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
 &=& \imposs+\unlikely+\imposs+\likely\\
@@
   event $\proj{\ps}$ where
-  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$ indicates that the
+  $\ket{\ps}=\left(\ket{0}+\ket{1}\right) / \sqrt{2}$ indicates that the
   post-measurement state will be $\ket{\ps}$; the event
@@
   $\mu\left(\proj{0}\right)=1$, $\mu\left(\proj{1}\right)=0$,
-  $\mu\left(\proj{\ps}\right)=1/2$, \ldots. Note that, similarly to
+  $\mu\left(\proj{\ps}\right)=\frac{1}{2}$, \ldots. Note that, similarly to
   the classical case, the probability of $\mathbb{1}$ is 1 and the
@@
 a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
-$\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$, and 
+Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right) / \sqrt{2}$,
+$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and 
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\\
+\bar{\mu}(\mathbb{0}) & = & \bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\\
+\bar{\mu}(\mathbb{1}) & = & \bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\\
 \bar{\mu}(P) & = & \unknown\quad\textrm{otherwise}
@@
 or we might think it is induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
-or yet we might think it is induced by the mixed state $\frac{\mathbb{1}}{3}$
+or yet we might think it is induced by the mixed state $\mathbb{1} / 3$
 because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.
@@
   }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and
-  $\ket{\minus}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$. The definition of
+  $\ket{\ps}=\left(\ket{0}+\ket{1}\right) / \sqrt{2}$, and
+  $\ket{\minus}=\left(\ket{0}-\ket{1}\right) / \sqrt{2}$. The definition of
   $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-4-value}
@@
 \begin{eqnarray*}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) 
-  &=& \imposs \\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) 
-  &=& \necess
+\bar{\mu}(\mathbb{0}) &=& \bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs \\
+\bar{\mu}(\mathbb{1}) &=& \bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess
 \end{eqnarray*}
@@
   $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\minus}+\cos\theta\ket{2}$,
-  where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
+  where $0\le\theta\le\pi / 2$ and $0\le\gamma<2\pi$. The dotted
   half of those states need special treatment, i.e., whenever
-  $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define
+  $0\le\theta<\pi / 2$ and $0\le\gamma<\pi$, we define
 \begin{eqnarray*}
-\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)
-  &=& \likely \\
-\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right)=
-  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right) 
-  &=& \unlikely
+\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right) &=& \bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\likely \\
+\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right) &=& 
+  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\unlikely
 \end{eqnarray*}
@@
 sense that it might only be induced by $\ket{2}$ or the density matrix
-$\frac{\mathbb{1}}{3}$, but not by $\ket{1}$. \end{example}
+$\mathbb{1} / 3$, but not by $\ket{1}$. \end{example}
 
@@
 \item The radius of any disk inside the area of the 1-dimensional projectors
-mapping to $\imposs$ must smaller than $\frac{\pi}{4}$ (theorem~\ref{thm:pi-div-4}).
+mapping to $\imposs$ must smaller than $\pi / 4$ (theorem~\ref{thm:pi-div-4}).
 \item When the radius of any disk inside the area of the 1-dimensional projectors
-mapping to $\imposs$ between $\arcsin\left(\frac{1}{\sqrt{3}}\right)$
-and $\frac{\pi}{4}$, we have $\unknown\in\mathscr{I}$, i.e., $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=1$
+mapping to $\imposs$ between $\arcsin\left(1 / \sqrt{3}\right)$
+and $\pi / 4$, we have $\unknown\in\mathscr{I}$, i.e., $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=1$
 (theorem~\ref{thm:arcsin-one-over-sqrt-three}).
 \item When the radius of any disk inside the area of the 1-dimensional projectors
-mapping to $\imposs$ between $\frac{\pi}{6}$ and $\arcsin\left(\frac{1}{\sqrt{3}}\right)$,
+mapping to $\imposs$ between $\pi/6$ and $\arcsin\left(1 / \sqrt{3}\right)$,
 we have $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=\frac{1}{3}$
@@
 cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
-as usual. We will use $\ket{\psi}\times\ket{\phi}$ and $\frac{\ket{\psi}\times\ket{\phi}}{\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert }$
-interchanged when there is no confusion.\end{definition}
+as usual. We will use $\ket{\psi}\times\ket{\phi}$ and
+$\ket{\psi}\times\ket{\phi}/\left\Vert
+\ket{\psi}\times\ket{\phi}\right\Vert$ interchanged when there is no
+confusion.\end{definition}
 
@@
 For example, the north pole has the latitude $0$, the equator has
-the the latitude $\frac{\pi}{2}$, and $\angle^{-1}\left(\left[0,\theta_{0}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
+the the latitude $\pi / 2$, and $\angle^{-1}\left(\left[0,\theta_{0}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\pi / 2}$
 contains all states whose latitude is larger than $\theta_{0}$.\end{definition}
 
-\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
+\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\pi / 2\right]$
 and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
@@
 then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
-for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]\right)$.\end{lemma}
+for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\pi / 2\right]\right)$.\end{lemma}
 \begin{proof}
@@
 $\bar{f}\left(\ket{2}\right)=\left[1,1\right]-\bar{f}\left(\ket{\bar{1}}\right)=\bar{f}\left(\ket{\bar{2}}\right)$.
-In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]\right)$,
+In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\pi / 2\right]\right)$,
 even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are not in the same
@@
 \end{proof}
-\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
+\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\pi / 2\right]$
 and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
 if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
-then $\theta_{0}<\frac{\pi}{4}$.\end{thm}
+then $\theta_{0}<\pi / 4$.\end{thm}
 \begin{proof}
-We are going to prove by contradiction. Suppose $\theta_{0}\ge\frac{\pi}{4}$,
-we have $\left[0,\theta_{0}\right]\cap\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]=\left[\frac{\pi}{2}-\theta_{0},\theta_{0}\right]\ne\emptyset$.
-Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\theta_{0}\right]\right)$,
+We are going to prove by contradiction. Suppose $\theta_{0}\ge\pi / 4$,
+we have $\left[0,\theta_{0}\right]\cap\left[\pi / 2-\theta_{0},\pi / 2\right]=\left[\pi / 2-\theta_{0},\theta_{0}\right]\ne\emptyset$.
+Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\theta_{0}\right]\right)$,
 by lemma~\ref{lemma:imposs-imply-same-value}, we have $\imposs=\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]$,
-where $l_{0}\in\left[0,\frac{\pi}{2}\right]$. A contradiction!
+where $l_{0}\in\left[0,\pi / 2\right]$. A contradiction!
 \end{proof}
-\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left[\arcsin\left(\frac{1}{\sqrt{3}}\right),\frac{\pi}{4}\right)$
+\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left[\arcsin\left(1 / \sqrt{3}\right),\pi / 4\right)$
 and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
@@
 then $\unknown\in\mathscr{I}$.\end{thm}
-\begin{proof}
 \begin{figure}
@@
 the proof of theorem~\ref{thm:arcsin-one-over-sqrt-three}. The latitude
-of the yellow circle is $\theta_{0}\in\left[\arcsin\left(\frac{1}{\sqrt{3}}\right),\frac{\pi}{4}\right)$,
-and the latitude of the green circle is $\frac{\pi}{2}-\theta_{0}$.}
+of the yellow circle is $\theta_{0}\in\left[\arcsin\left(1 / \sqrt{3}\right),\pi / 4\right)$,
+and the latitude of the green circle is $\pi / 2-\theta_{0}$.}
 \end{figure}
+\begin{proof}
 We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-2},
 where the latitude of of the yellow circle is $\theta_{0}$ and the
-latitude of of the green circle is $\frac{\pi}{2}-\theta_{0}$. Therefore,
+latitude of of the green circle is $\pi / 2-\theta_{0}$. Therefore,
 $\bar{f}$ should map any state above the yellow circle to $\imposs$
@@
 
-When $\theta_{0}\ge\arcsin\left(\frac{1}{\sqrt{3}}\right)$, the latitude
-of the green circle is $\theta_{0}\le\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)$.
+When $\theta_{0}\ge\arcsin\left(1 / \sqrt{3}\right)$, the latitude
+of the green circle is $\theta_{0}\le\pi / 2-\arcsin\left(1 / \sqrt{3}\right)$.
 Now consider three states~$\ket{A}$, $\ket{B}$, and $\ket{C}$
-whose latitude is $\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)$
+whose latitude is $\pi / 2-\arcsin\left(1 / \sqrt{3}\right)$
 so that they are below the green circle, and these three states form
 an equilateral triangle whose center is $H$. Since the latitude of
-this triangle is $\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)$,
-we know $\overline{OH}=\frac{1}{\sqrt{3}}$, where $O$ is the center
+this triangle is $\pi / 2-\arcsin\left(1 / \sqrt{3}\right)$,
+we know $\overline{OH}=1 / \sqrt{3}$, where $O$ is the center
 of the sphere. By the Pythagorean theorem, $\overline{HA}=\overline{HB}=\sqrt{\frac{2}{3}}$.
-Notice that $\triangle HAB$ is an isosceles triangle with $\angle AHB=\frac{2\pi}{3}$,
+Notice that $\triangle HAB$ is an isosceles triangle with $\angle AHB=2\pi / 3$,
 we have $\overline{AB}=\sqrt{2}$. Since $\overline{OA}=\overline{OB}=1$
 and $\overline{AB}=\sqrt{2}$, $\triangle OAB$ is an isosceles right
-triangle with $\angle AHB=\frac{\pi}{2}$, i.e., $\ket{A}$ and $\ket{B}$
+triangle with $\angle AHB=\pi / 2$, i.e., $\ket{A}$ and $\ket{B}$
 are orthogonal. Applying the same reason on all $\ket{A}$, $\ket{B}$,
@@
 \item $\iota\left(1\right)=\left[1,1\right]$. 
-\item When $x=\frac{k}{n}$, we have $\iota\left(1-x\right)=\left[1-\frac{k}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.\\
-When $\frac{k}{n}<x<\frac{k+1}{n}$, we have $1-\frac{k}{n}>1-x>1-\frac{k+1}{n}$
-so that $\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.
+\item When $x=k / n$, we have $\iota\left(1-x\right)=\left[1-k / n,1-k / n\right]=\left[1,1\right]-\iota\left(x\right)$.\\
+When $k / n<x<\left(k+1\right)/n$, we have $1-k / n>1-x>1-\left(k+1\right)/n$
+so that 
+\[
+\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)\textrm{ .}
+\]
 \item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
@@
 \begin{itemize}
-\item When $x_{1}=\frac{k_{1}}{n}$, we have $\iota\left(x_{1}+x_{2}\right)=\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota\left(x_{2}\right)=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
-\item When $\frac{k_{1}}{n}<x_{1}<\frac{k_{1}+1}{n}$ and $\frac{k_{2}}{n}<x_{2}<\frac{k_{2}+1}{n}$,
-we have $\frac{k_{1}+k_{2}}{n}<x_{1}+x_{2}<\frac{k_{1}+k_{2}+2}{n}$
-so that $\iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]=\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
+\item When $x_{1}=k_{1} / n$, we have
+\[
+\iota\left(x_{1}+x_{2}\right)=\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota\left(x_{2}\right)=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .}
+\]
+\item When $k_{1} / n<x_{1}<\left(k_{1}+1\right)/n$ and $k_{2}/n<x_{2}<\left(k_{2}+1\right)/n$,
+we have
+\[
+\frac{k_{1}+k_{2}}{n}<x_{1}+x_{2}<\frac{k_{1}+k_{2}+2}{n}
+\]
+so that
+\begin{eqnarray*}
+ & & \iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\
+ & = &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .}
+\end{eqnarray*}
 \end{itemize}

### 2017-02-09 prop_iop.tex
prop_iop.tex According "5.5. Alignment of displayed equations"...

@@
   events:
-\[
+\begin{equation}
 \begin{array}{c@{\qquad\qquad}c}
@@
 \end{array}\end{array}
-\]
+\end{equation}
 \end{example}
@@
 probability converging to one as $M$ goes to infinity, i.e.,
-\[
+\begin{equation}
 \forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M} x_{i}\right|<\epsilon\right)=1\textrm{ .}
-\]
+\end{equation}
 This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
@@
 \item $\bar{\mu}(\Omega)=[1,1]$. 
-\item For any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$ 
+\item For any event $E$, $\bar{\mu}\left(\Omega\backslash
+E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$.
 \item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
@@
 following: 
-\[
+\begin{equation}
 \begin{array}{c@{\qquad\qquad}c}
@@
 \end{array}\end{array}
-\]
+\end{equation}
 Despite the absence of infinitely precise numeric information, the
@@
 the $\subseteq$-condition, consider the following calculation:
-\begin{eqnarray*}
+\begin{eqnarray}
 & & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
 &=& \imposs+\unlikely+\imposs+\likely\\
-&=& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]\\
-&=& \left[\frac{1}{2},\frac{3}{2}\right]
-\end{eqnarray*}
+&=& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=
+\left[\frac{1}{2},\frac{3}{2}\right]\textrm{ .}
+\end{eqnarray}
 If we were to equate $\bar{\mu}(\Omega)$ with the sum of the individual
@@
 $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and 
-\begin{eqnarray*}
-\bar{\mu}(\mathbb{0}) & = & \bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\\
-\bar{\mu}(\mathbb{1}) & = & \bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\\
-\bar{\mu}(P) & = & \unknown\quad\textrm{otherwise}
-\end{eqnarray*}
+\begin{eqnarray}
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\
+\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.}
+\end{eqnarray}
 It is straightforward to verify that $\bar{\mu}$ is a convex quantum
@@
 \item Let:
-\begin{eqnarray*}
-\bar{\mu}(\mathbb{0}) &=& \bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs \\
-\bar{\mu}(\mathbb{1}) &=& \bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess
-\end{eqnarray*}
+\begin{eqnarray}
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,}
+\end{eqnarray}
 where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green dotted
@@
   $0\le\theta<\pi / 2$ and $0\le\gamma<\pi$, we define
-\begin{eqnarray*}
-\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right) &=& \bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\likely \\
-\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right) &=& 
-  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\unlikely
-\end{eqnarray*}
+\begin{eqnarray}
+\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\likely\textrm{ ,}\\
+\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right)=
+  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\unlikely\textrm{ .}
+\end{eqnarray}
 \item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
@@
 so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
-\[
+\begin{equation}
 \mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
-\]
+\end{equation}
 This measure however is ``better'' than the previous one in the
@@
 \end{array}\right)$, their cross product is defined as follow: 
-\[
+\begin{equation}
 \ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\left|\begin{array}{cc}\alpha_{1}^{*} & \beta_{1}^{*}\\
@@
 \end{array}\right|\ket{2}\textrm{ ,}
-\]
+\end{equation}
 where $\left|\begin{array}{cc}\alpha & \beta\\
@@
 we can just verify 
-\begin{eqnarray*}
-\ip{\psi}{\psi\times\phi} & = & \ip{\psi\times\phi}{\psi}^{*}=\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}\right]^{*}=0\textrm{ ,}\\
-\ip{\phi}{\psi\times\phi} & = & \ip{\psi\times\phi}{\phi}^{*}=\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}\right]^{*}=0\textrm{ .}
-\end{eqnarray*}
+\begin{eqnarray}
+&&\ip{\psi}{\psi\times\phi}=\ip{\psi\times\phi}{\psi}^{*}\\
+&=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}\right]^{*}=0\textrm{ ,}\\
+&&\ip{\phi}{\psi\times\phi}=\ip{\psi\times\phi}{\phi}^{*}\\
+&=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}\right]^{*}=0\textrm{ .}
+\end{eqnarray}
 
@@
 have
-\[
+\begin{equation}
 \dim\left(\ker T\right)=\mathrm{nullity}\left(T\right)=3-\mathrm{rank}\left(T\right)=3-2=1\textrm{ .}
-\]
+\end{equation}
 By the other direction of the proof, we have already known $\ket{\psi}\times\ket{\phi}\in\ker T$.
@@
 for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\pi / 2\right]\right)$.\end{lemma}
-\begin{proof}
 \begin{figure}
@@
 \end{figure}
+\begin{proof}
 We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
@@
 into equation~(\ref{eq:includes}), and get 
-\begin{eqnarray*}
- &  & \left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\\
- & \Rightarrow & l_{0}+r_{0}=1
-\end{eqnarray*}
+\begin{equation}
+\left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\Rightarrow
+l_{0}+r_{0}=1\textrm{ .}
+\end{equation}
 Also, we have 
-\begin{eqnarray*}
- &  & 1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\\
- & \Rightarrow & l_{0}\le\frac{1}{2}\le r_{0}
-\end{eqnarray*}
+\begin{equation}
+1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\Rightarrow
+l_{0}\le\frac{1}{2}\le r_{0}\textrm{ .}
+\end{equation}
 Thus the lemma is proved.
@@
 basis and $\bar{f}\left(\ket{A}\right)=\bar{f}\left(\ket{B}\right)=\bar{f}\left(\ket{C}\right)=\left[l_{0},1-l_{0}\right]$,
-we have the following inequalities by lemma~\ref{lemma:interval-valued-frame-function}.
-\begin{eqnarray*}
-1\in\left[3l_{0},3-3l_{0}\right] & \Rightarrow & l_{0}\le\frac{1}{3}\\
-\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right] & \Rightarrow & l_{0}\le0
-\end{eqnarray*}
+we have the following inequalities by
+lemma~\ref{lemma:interval-valued-frame-function},
+\begin{eqnarray}
+1\in\left[3l_{0},3-3l_{0}\right] \Rightarrow l_{0}\le\frac{1}{3}\textrm{ ,}\\
+\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right]
+\Rightarrow l_{0}\le0\textrm{ .}
+\end{eqnarray}
 Recall that $0\le l_{0}\le\frac{1}{2}$. Therefore, $l_{0}=0$, that
@@
 Then, 
-\begin{eqnarray*}
+\begin{eqnarray}
  &  & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
@@
  & = & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
-\end{eqnarray*}
+\end{eqnarray}
 \end{proof}
@@
 Thus, 
-\begin{eqnarray*}
+\begin{eqnarray}
  &  & \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
@@
  & \Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}
-\end{eqnarray*}
+\end{eqnarray}
 When the number of elements in $\Omega$ is less than or equal to
@@
 defined by
-\begin{eqnarray*}
-\mathscr{I}_{n} & = & \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\
-\iota_{n}\left(x\right) & = & \cases{
+\begin{eqnarray}
+\mathscr{I}_{n} = \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\
+\iota_{n}\left(x\right) = \cases{
 \left[\frac{k}{n},\frac{k}{n}\right] & , if $x=\frac{k}{n}$ ;\\
@@
 }
-\end{eqnarray*}
+\end{eqnarray}
 is regular.\end{example}
@@
 so that 
-\[
+\begin{equation}
 \iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)\textrm{ .}
-\]
+\end{equation}
 \item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
@@
 \item When $x_{1}=k_{1} / n$, we have
-\[
+\begin{equation}
 \iota\left(x_{1}+x_{2}\right)=\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota\left(x_{2}\right)=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .}
-\]
+\end{equation}
 \item When $k_{1} / n<x_{1}<\left(k_{1}+1\right)/n$ and $k_{2}/n<x_{2}<\left(k_{2}+1\right)/n$,
 we have
-\[
+\begin{equation}
 \frac{k_{1}+k_{2}}{n}<x_{1}+x_{2}<\frac{k_{1}+k_{2}+2}{n}
-\]
+\end{equation}
 so that
-\begin{eqnarray*}
+\begin{eqnarray}
  & & \iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\
  & = &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .}
-\end{eqnarray*}
+\end{eqnarray}
 \end{itemize}

### 2017-02-09 prop_iop.tex
prop_iop.tex According to "5.6. Miscellaneous points"...

@@
 the $\subseteq$-condition, consider the following calculation:
-\begin{eqnarray}
-& & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
-&=& \imposs+\unlikely+\imposs+\likely\\
-&=& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=
+\begin{equation}\eqalign{
+ & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
+=& \imposs+\unlikely+\imposs+\likely\\
+=& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=
 \left[\frac{1}{2},\frac{3}{2}\right]\textrm{ .}
-\end{eqnarray}
+}\end{equation}
 If we were to equate $\bar{\mu}(\Omega)$ with the sum of the individual
@@
 $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and 
-\begin{eqnarray}
+\begin{equation}\eqalign{
 \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\
@@
 \bar{\mu}(P) = \unknown\qquad\textrm{otherwise.}
-\end{eqnarray}
+}\end{equation}
 It is straightforward to verify that $\bar{\mu}$ is a convex quantum
@@
 \item Let:
-\begin{eqnarray}
+\begin{equation}\eqalign{
 \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\
 \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,}
-\end{eqnarray}
+}\end{equation}
 where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green dotted
@@
   $0\le\theta<\pi / 2$ and $0\le\gamma<\pi$, we define
-\begin{eqnarray}
+\begin{equation}\eqalign{
 \bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\likely\textrm{ ,}\\
@@
   \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\unlikely\textrm{ .}
-\end{eqnarray}
+}\end{equation}
 \item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
@@
 we can just verify 
-\begin{eqnarray}
-&&\ip{\psi}{\psi\times\phi}=\ip{\psi\times\phi}{\psi}^{*}\\
-&=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}\right]^{*}=0\textrm{ ,}\\
-&&\ip{\phi}{\psi\times\phi}=\ip{\psi\times\phi}{\phi}^{*}\\
-&=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}\right]^{*}=0\textrm{ .}
-\end{eqnarray}
+\begin{equation}\eqalign{
+&\ip{\psi}{\psi\times\phi}=\ip{\psi\times\phi}{\psi}^{*}\\
+=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}\right]^{*}=0\textrm{ ,}\\
+&\ip{\phi}{\psi\times\phi}=\ip{\psi\times\phi}{\phi}^{*}\\
+=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}\right]^{*}=0\textrm{ .}
+}\end{equation}
 
@@
 \begin{equation}
-\eqalign{\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
-\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
+\eqalign{\left[1,1\right]-\bar{f}\left(\ket{1}\right)\subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
+\left[1,1\right]-\bar{f}\left(\ket{2'}\right)\subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
 }
@@
 lemma~\ref{lemma:interval-valued-frame-function},
-\begin{eqnarray}
+\begin{equation}\eqalign{
 1\in\left[3l_{0},3-3l_{0}\right] \Rightarrow l_{0}\le\frac{1}{3}\textrm{ ,}\\
@@
 \Rightarrow l_{0}\le0\textrm{ .}
-\end{eqnarray}
+}\end{equation}
 Recall that $0\le l_{0}\le\frac{1}{2}$. Therefore, $l_{0}=0$, that
@@
 Then, 
-\begin{eqnarray}
- &  & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
- & = & \bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\vee\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)+\bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)\\
- & = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cup E_{1}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cap E_{1}}\proj{j}\right)\\
- & = & \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\\
- & \subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\\
- & = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\\
- & = & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
-\end{eqnarray}
+\begin{equation}\eqalign{
+ & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
+ = & \bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\vee\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)+\bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)\\
+ = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cup E_{1}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cap E_{1}}\proj{j}\right)\\
+ = & \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\\
+ \subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\\
+ = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\\
+ = & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
+}\end{equation}
 \end{proof}
@@
 Thus, 
-\begin{eqnarray}
- &  & \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
- & \Rightarrow & \left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
- & \Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\
- & \Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}
-\end{eqnarray}
+\begin{equation}\eqalign{
+ & \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
+ \Rightarrow & \left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
+ \Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\
+ \Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}
+}\end{equation}
 When the number of elements in $\Omega$ is less than or equal to
@@
 defined by
-\begin{eqnarray}
+\begin{equation}\eqalign{
 \mathscr{I}_{n} = \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\
@@
 }
-\end{eqnarray}
+}\end{equation}
 is regular.\end{example}
@@
 so that
-\begin{eqnarray}
- & & \iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\
- & = &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .}
-\end{eqnarray}
+\begin{equation}\eqalign{
+ & \iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\
+ = &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .}
+}\end{equation}
 \end{itemize}

### 2017-02-10 prop_iop.tex
prop_iop.tex Went through the Guildline...

@@
 IVPM could more and more likely be identified to a particular state.
-\begin{table}[ht]
-\center{%
-\begin{tabular}{c|cccc}
+\begin{table}
+\caption{\label{table_long}Relation between measurement resources and
+interval-valued probability measures.}
+\begin{indented}
+\item[]\begin{tabular}{c|cccc}
+\br
 Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
-\hline 
+\mr
 Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
@@
 Count of states correspond to pieces of $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
-\hline 
+\mr
 How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
-\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
-measures}
-\label{table_long}
+\br
+\end{tabular}
+\end{indented}
 \end{table}

### 2017-02-11 prop_iop.tex
prop.bib @Article{Bell1964} Added...

@@
 the validity the fundamental theorems of quantum mechanics followed
-up by Gleason's theorem, such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+up by Gleason's theorem, such as Bell~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
 and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},

### 2017-02-11 prop_iop.tex
prop_iop.tex \section{Quantum and Classical Interval-valued Probability Measures} Updating...

@@
 is a classical IVPM, where $\sum_{\ket{j}\in\emptyset}\proj{j}$ is
-defined to be $\mathbb{0}$.\end{lemma}
-\begin{proof}
-~
+defined to be $\mathbb{0}$. In particular, when $\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$,
+$\bar{\mu}$ is essentially a quantum real-valued probability measure
+and $\bar{\mu}^{\Omega}$ is essentially a classical real-valued probability
+measure. In another word, this lemma also holds for real-valued probability
+measures.\end{lemma}
+
+\begin{proof} ~ 
 \begin{itemize}
@@
 \item $\bar{\mu}^{\Omega}(\Omega)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)=[1,1]$. 
-\item For any event $E$, $\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega\backslash E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)$.
+\item For any event $E$,
+\begin{equation}\eqalign{ 
+\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)&=\bar{\mu}\left(\sum_{\ket{j}\in\Omega\backslash E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)\\
+&=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .} 
+}\end{equation}commuting
 \item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
-events, we have $\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{\ket{j}\in\bigcup_{i=1}^{N}E_{i}}\proj{j}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)$.
+events, we have
+\begin{equation}\eqalign{ 
+\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)&=\bar{\mu}\left(\sum_{\ket{j}\in\bigcup_{i=1}^{N}E_{i}}\proj{j}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\\
+&\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\textrm{ .} 
+}\end{equation}
 \end{itemize}
 \end{proof}
+
 The previous lemma suggests that given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
@@
 $\bar{\mu}$ is convex, each $\bar{\mu}|_{\events^{\Omega}}$ has
-a non-empty core. However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$cannot
-be glued together, and gives a core element of $\bar{\mu}$. The inability
-of gluing core elements among commuting $\events^{\Omega}$ to non-commuting
-$\events$ is consistent with the idea of the Kochen-Specker theorem,
-that each triple of commuting observables could be colored well, but
-we cannot color all observables which are not all commuting.\footnote{\yutsung{Since Bell's theorem only applies to entangled states, the
-exists of entangled states is another reason why quantum theory is
-different from a classical theory. However, defining product quantum
-IVPM is much harder, and beyond the discussion here.}}
+a non-empty core. However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$
+may not be glued together, and gives a core element of $\bar{\mu}$.
+The inability of gluing core elements among commuting $\events^{\Omega}$
+to non-commuting $\events$ is consistent with the idea of the Kochen-Specker
+theorem, that each triple of commuting observables could be colored
+well, but we cannot color all observables which are not all commuting.
+This is also consistent with the assertion that mutually commuting
+observables could be measured simultaneously~\cite{Mermin_1993}.
+In another word, if Alice and Bob in Bell's theorem can only pick
+from a set of mutually commuting observables, they could never observe
+any ``quantum,`` and we cannot eliminate the local hidden variable
+theory in this setting.
 

### 2017-02-12 prop_iop.tex
prop_iop.tex \section{Quantum and Classical Interval-valued Probability Measures} Updating...

@@
 
-\begin{lemma}Given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$
-for a given Hilbert space~$\Hilb$ of dimension~$d$, and a quantum
-IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Then, the function
-$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ defined by
-$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)$
-is a classical IVPM, where $\sum_{\ket{j}\in\emptyset}\proj{j}$ is
-defined to be $\mathbb{0}$. In particular, when $\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$,
-$\bar{\mu}$ is essentially a quantum real-valued probability measure
-and $\bar{\mu}^{\Omega}$ is essentially a classical real-valued probability
-measure. In another word, this lemma also holds for real-valued probability
-measures.\end{lemma}
-
-\begin{proof} ~ 
+In this section, we are going to discuss the relation between quantum
+and classical. We first prove that any quantum phenomenon would not
+be observed if we could only access commuting projectors since we
+can pick a common basis to measure mutually commuting observables
+simultaneously~\cite{Mermin_1993}. Based on this fact, we show a
+quantum IVPM~$\bar{\mu}$ is convex if its restriction on any orthonormal
+basis~$\Omega$, $\bar{\mu}^{\Omega}$ is a convex classical IVPM.
+Together with the fact that every classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
+is convex when the number of elements in $\Omega$ is less than or
+equal to 3, every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+must be convex on a three-dimensional Hilbert space.
+
+Before we dive into the lemmas and proofs, we start from two definitions.
+
+\begin{definition}Given a Hilbert space $\Hilb$, and a set of projections
+$\mathcal{S}\subseteq\events$, we define $\sum_{P\in\mathcal{S}}P=\mathbb{0}$
+when $\mathcal{S}=\emptyset$ since $\mathbb{0}$ is the additive
+identity in operators.\end{definition}
+
+\begin{definition}Given a Hilbert space $\Hilb$ with an orthonormal
+basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
+\begin{itemize}
+\item For any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
+we define $\mu^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$ by
+$\mu^{\Omega}\left(E\right)=\mu\left(\sum_{\ket{j}\in E}\proj{j}\right)$.
+\item For any quantum IVPM~$\bar{\mu}:\events\rightarrow\left[0,1\right]$,
+we define $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ by
+$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)$.
+\end{itemize}
+\end{definition}
+
+\begin{lemma}$\mu^{\Omega}$ and $\bar{\mu}^{\Omega}$ in the previous
+definition are classical interval-valued and real-valued probability
+measures, respectively.\end{lemma}
+
+\begin{proof}When $\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$,
+$\bar{\mu}$ and $\bar{\mu}^{\Omega}$ are essentially quantum and
+classical real-valued probability measures, respectively. Hence, it
+is sufficient to prove the interval-valued case.
 \begin{itemize}

### 2017-02-13 prop_iop.tex
prop_iop.tex \section{Quantum and Classical Interval-valued Probability Measures} Updating...

@@
 
-In this section, we are going to discuss the relation between quantum
-and classical. We first prove that any quantum phenomenon would not
-be observed if we could only access commuting projectors since we
-can pick a common basis to measure mutually commuting observables
-simultaneously~\cite{Mermin_1993}. Based on this fact, we show a
-quantum IVPM~$\bar{\mu}$ is convex if its restriction on any orthonormal
-basis~$\Omega$, $\bar{\mu}^{\Omega}$ is a convex classical IVPM.
-Together with the fact that every classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
-is convex when the number of elements in $\Omega$ is less than or
-equal to 3, every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-must be convex on a three-dimensional Hilbert space.
-
-Before we dive into the lemmas and proofs, we start from two definitions.
+This section discusses the relation between quantum and classical.
+We first prove that any quantum phenomenon would not be observed if
+we could only access commuting projectors since we can pick a common
+basis to measure mutually commuting observables simultaneously~\cite{Mermin_1993}.
+Based on this fact, we show a quantum IVPM~$\bar{\mu}$ is convex
+if its restriction on any orthonormal basis~$\Omega$, $\bar{\mu}^{\Omega}$,
+is a convex classical IVPM. Together with the fact that every classical
+IVPM~$\bar{\mu}^{\Omega}$ is convex when the number of elements
+in $\Omega\le3$, every quantum IVPM must be convex on a three-dimensional
+Hilbert space.
+
+Before diving into the lemmas and proofs, we start from two definitions.
 
@@
 \item $\bar{\mu}^{\Omega}(\Omega)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)=[1,1]$. 
-\item For any event $E$,
+\item For any event $E\in2^{\Omega}$,
 \begin{equation}\eqalign{ 
@@
 &=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .} 
-}\end{equation}commuting
-\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
-events, we have
+}\end{equation}
+\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$
+of pairwise disjoint events, we have
 \begin{equation}\eqalign{ 
@@
 
-The previous lemma suggests that given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
+By the previous lemma, given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
 if we only consider the events generated by $\Omega$, $\events^{\Omega}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
@@
 i.e., consider $\bar{\mu}|_{\events^{\Omega}}$. In particular, if
-$\bar{\mu}$ is convex, each $\bar{\mu}|_{\events^{\Omega}}$ has
-a non-empty core. However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$
+$\bar{\mu}$ is convex, each $\bar{\mu}|_{\events^{\Omega}}$ is convex
+and has a non-empty core. However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$
 may not be glued together, and gives a core element of $\bar{\mu}$.

### 2017-02-13 prop_iop.tex
prop_iop.tex \section{Between Quantum and Classical} Updating...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum and Classical Interval-valued Probability Measures}
+\section{Between Quantum and Classical}
 
@@
 We first prove that any quantum phenomenon would not be observed if
-we could only access commuting projectors since we can pick a common
-basis to measure mutually commuting observables simultaneously~\cite{Mermin_1993}.
-Based on this fact, we show a quantum IVPM~$\bar{\mu}$ is convex
-if its restriction on any orthonormal basis~$\Omega$, $\bar{\mu}^{\Omega}$,
-is a convex classical IVPM. Together with the fact that every classical
-IVPM~$\bar{\mu}^{\Omega}$ is convex when the number of elements
-in $\Omega\le3$, every quantum IVPM must be convex on a three-dimensional
-Hilbert space.
+we could only access commuting projectors since commuting projectors
+could be measured simultaneously~\cite{Mermin_1993}. Based on this
+fact, we show a quantum IVPM~$\bar{\mu}$ is convex if its restriction
+on any orthonormal basis~$\Omega$, $\bar{\mu}^{\Omega}$, is a convex
+classical IVPM. Together with the fact that every classical IVPM~$\bar{\mu}^{\Omega}$
+is convex when the number of elements in $\Omega\le3$, every quantum
+IVPM must be convex on a three-dimensional Hilbert space.
 
@@
 
-\begin{definition}Given a Hilbert space $\Hilb$ with an orthonormal
-basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
+\begin{definition}\label{definition:quantum-classical}Given a Hilbert
+space $\Hilb$ with an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
 \begin{itemize}
@@
 $\mu^{\Omega}\left(E\right)=\mu\left(\sum_{\ket{j}\in E}\proj{j}\right)$.
-\item For any quantum IVPM~$\bar{\mu}:\events\rightarrow\left[0,1\right]$,
+\item For any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
 we define $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ by
@@
 
-\begin{lemma}$\mu^{\Omega}$ and $\bar{\mu}^{\Omega}$ in the previous
-definition are classical interval-valued and real-valued probability
-measures, respectively.\end{lemma}
+\begin{lemma}\label{lemma:classical-probability-measures}$\mu^{\Omega}$
+and $\bar{\mu}^{\Omega}$ in the previous definition are classical
+real-valued and interval-valued probability measures, respectively.\end{lemma}
 
@@
 \end{proof}
+
+\begin{definition}Given a Hilbert space $\Hilb$, $\events'\subseteq\events$
+is called a sub-event if it satisfies the follow conditions.
+\begin{itemize}
+\item $\mathbb{0}\in\events'$.
+\item $\mathbb{1}\in\events'$.
+\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$.
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
+we have $\sum_{i=1}^{N}P_{i}\in\events'$.
+\end{itemize}
+By replacing every occurrence of $\events$ by $\events'$ in definition~\ref{def:QuantumProbabilitySpace}
+and \ref{def:QuantumInterval-valuedProbability}, it is straightforward
+to define a quantum real-valued and interval-valued probability measure
+on $\events'$.\end{definition}
+
+\begin{thm}Given a Hilbert space~$\Hilb$ and a mutually commuting
+sub-event~$\events'\subseteq\events$, there is set~$\Omega$ and
+a function~$\tau:\events'\rightarrow2^{\Omega}$ such that:
+\begin{itemize}
+\item If $\mu:\events'\rightarrow\left[0,1\right]$ is a quantum real-valued
+probability measure, then there is a classical real-valued probability
+measure~$\mu':\Omega\rightarrow\left[0,1\right]$ such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+for all $P\in\events'$.
+\item If $\mu:\events'\rightarrow\mathscr{I}$ is a quantum interval-valued
+probability measure, then there is a classical interval-valued probability
+measure~$\mu':\Omega\rightarrow\mathscr{I}$ such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+for all $P\in\events'$
+\end{itemize}
+\end{thm}
+
+\begin{proof}Again, it is sufficient to prove the interval-valued
+case. Since $\events'$ is a set of mutually orthogonal projections,
+they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
+Pick arbitrary projector~$P\in\events'$, its eigenvalues are $0$
+or $1$. Let $\tau\left(P\right)\subseteq\Omega$ be the set of eigenvectors
+whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$.
+By definition~\ref{definition:quantum-classical}, $\mu\left(P\right)=\mu^{\Omega}\left(\tau\left(P\right)\right)$,
+and $\mu^{\Omega}$ is a quantum interval-valued probability measure
+by lemma~\ref{lemma:classical-probability-measures}.\end{proof}
 

### 2017-02-13 prop_iop.tex
From: Tai, Yu-Tsung Sent: Monday, February 13, 2017 2:23 To: Hanson, Andrew J. <hansona@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu> Subject: RE: Belief: RE: Need a definition.
Updated appendix C, and hope it would be more readable than the previous
one...

About the Dutch book, I haven't found a detailed computation in Prof.
Busemeyer papers, but I found some in quantum Bayesian's paper
(http://link.aps.org/doi/10.1103/RevModPhys.85.1693)... Reading the
details until section 2... For the part I read so far, it seems that
they consider the Born rule a

@@
 \item For any event $E\in2^{\Omega}$,
-\begin{equation}\eqalign{ 
-\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)&=\bar{\mu}\left(\sum_{\ket{j}\in\Omega\backslash E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)\\
-&=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .} 
-}\end{equation}
+\begin{equation}
+\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .}
+\end{equation}
 \item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$
 of pairwise disjoint events, we have
-\begin{equation}\eqalign{ 
-\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)&=\bar{\mu}\left(\sum_{\ket{j}\in\bigcup_{i=1}^{N}E_{i}}\proj{j}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\\
-&\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\textrm{ .} 
-}\end{equation}
+\begin{equation}
+\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}^{\Omega}\left(E_{i}\right)\textrm{ .}
+\end{equation}
 \end{itemize}
@@
 \begin{definition}Given a Hilbert space $\Hilb$, $\events'\subseteq\events$
-is called a sub-event if it satisfies the follow conditions.
+is called a sub-event space if it satisfies the follow conditions.
 \begin{itemize}
@@
 \begin{thm}Given a Hilbert space~$\Hilb$ and a mutually commuting
-sub-event~$\events'\subseteq\events$, there is set~$\Omega$ and
-a function~$\tau:\events'\rightarrow2^{\Omega}$ such that:
+sub-event space~$\events'\subseteq\events$, there is set~$\Omega$
+and a function~$\tau:\events'\rightarrow2^{\Omega}$ such that:
 \begin{itemize}
@@
 for all $P\in\events'$.
-\item If $\mu:\events'\rightarrow\mathscr{I}$ is a quantum interval-valued
+\item If $\bar{\mu}:\events'\rightarrow\mathscr{I}$ is a quantum interval-valued
 probability measure, then there is a classical interval-valued probability
-measure~$\mu':\Omega\rightarrow\mathscr{I}$ such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+measure~$\bar{\mu}':\Omega\rightarrow\mathscr{I}$ such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
 for all $P\in\events'$
@@
 whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$.
-By definition~\ref{definition:quantum-classical}, $\mu\left(P\right)=\mu^{\Omega}\left(\tau\left(P\right)\right)$,
-and $\mu^{\Omega}$ is a quantum interval-valued probability measure
-by lemma~\ref{lemma:classical-probability-measures}.\end{proof}
-
-By the previous lemma, given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
-if we only consider the events generated by $\Omega$, $\events^{\Omega}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
+By definition~\ref{definition:quantum-classical}, $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
+and $\bar{\mu}^{\Omega}$ is a quantum interval-valued probability
+measure by lemma~\ref{lemma:classical-probability-measures}.\end{proof}
+
+Given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
+if we consider sub-event space generated by $\Omega$, $\events^{\Omega}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
 then any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-behaves classically when restricting the domain on $\events^{\Omega}$,
-i.e., consider $\bar{\mu}|_{\events^{\Omega}}$. In particular, if
-$\bar{\mu}$ is convex, each $\bar{\mu}|_{\events^{\Omega}}$ is convex
-and has a non-empty core. However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$
+restricting on $\events^{\Omega}$, denoted by $\bar{\mu}|_{\events^{\Omega}}$,
+behaves classically. In particular, if $\bar{\mu}$ is convex, each
+$\bar{\mu}|_{\events^{\Omega}}$ is convex and has a non-empty core.
+However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$
 may not be glued together, and gives a core element of $\bar{\mu}$.
@@
 
+The rest of the section focus on convexity.
+
 \begin{lemma}Given a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
@@
 convex.\end{lemma}
-\begin{proof}
-Pick two commuting events~$P_{0},P_{1}\in\events$. Since they are
-commuting, they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
-Since they are projectors, the eigenvalues of them are $0$ or $1$
-so that we can express them as $P_{0}=\sum_{\ket{j}\in E_{0}}\proj{j}$
-and $P_{1}=\sum_{\ket{j}\in E_{1}}\proj{j}$, where $E_{0},E_{1}\subseteq\Omega$.
-Then, 
+
+\begin{proof} Pick two commuting events~$P_{0},P_{1}\in\events$.
+Since they are commuting, they can be diagonalized by a common orthonormal
+basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$. Since they
+are projectors, the eigenvalues of them are $0$ or $1$ so that we
+can express them as $P_{0}=\sum_{\ket{j}\in E_{0}}\proj{j}$ and $P_{1}=\sum_{\ket{j}\in E_{1}}\proj{j}$,
+where $E_{0},E_{1}\subseteq\Omega$. Then, 
 \begin{equation}\eqalign{  
- & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
- = & \bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\vee\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)+\bar{\mu}\left(\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\right)\\
- = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cup E_{1}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{0}\cap E_{1}}\proj{j}\right)\\
- = & \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\\
- \subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\\
- = & \bar{\mu}\left(\sum_{\ket{j}\in E_{0}}\proj{j}\right)+\bar{\mu}\left(\sum_{\ket{j}\in E_{1}}\proj{j}\right)\\
- = & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
+& \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)= \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\\ 
+\subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)= \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ .} 
 }\end{equation}
 \end{proof}
+
 \begin{lemma}When the number of elements in $\Omega$ is less than
@@
 is convex.\end{lemma}
-\begin{proof}
-Given two events~$E_{0},E_{1}\subseteq\Omega$, we want to verify
+
+\begin{proof}Given two events~$E_{0},E_{1}\subseteq\Omega$, we
+want to verify 
 \begin{equation}
@@
 }\end{equation}
-When the number of elements in $\Omega$ is less than or equal to
-3, either $E_{0}\cap E_{1}=\emptyset$ or $E_{0}\cup E_{1}=\Omega$
-must happen so that $\bar{\mu}^{\Omega}$ is convex.
-\end{proof}
+When the number of elements in $\Omega\le3$, either $E_{0}\cap E_{1}=\emptyset$
+or $E_{0}\cup E_{1}=\Omega$ must happen so that $\bar{\mu}^{\Omega}$
+is convex. \end{proof}
+
 \begin{thm}Given a Hilbert space~$\Hilb$ of dimension~$3$, every
 quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is convex.\end{thm}
-\begin{proof}
-The direct consequence of the previous lemmas.
-\end{proof}
+
+\begin{proof}The direct consequence of the previous lemmas. \end{proof}
 

### 2017-02-15 prop_iop.tex
prop_iop.tex \section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}} Added...

@@
 \addbibresource{prop.bib}
-\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
+\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
 \usepackage{fullpage}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage{}%
+\section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}}
+
+\begin{example}[Three-dimensional quantum three-value interval-valued
+probability measure]\label{ex:three-dimensional-three-value-1} Given
+a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
+and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$.
+Let 
+\begin{eqnarray*}
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
+\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
+\end{eqnarray*}
+To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
+first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
+implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
+Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+it is sufficient to check 
+\[
+\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
+\]
+for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
+always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)$.
+
+Next, we need to verify that $\bar{\mu}$ is convex. First, for orthogonal
+projections $P_{0}$ and $P_{1}$, equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+implies equation (\ref{eq:QuantumInterval-valuedProbability-Convex}).
+Second, when $P_{0}=P_{1}+P_{2}$, equation (\ref{eq:QuantumInterval-valuedProbability-Convex})
+holds trivially. Hence, we only need to verify the case which $P_{0}=\proj{\psi_{0}}+\proj{\psi_{2}}$
+and $P_{1}=\proj{\psi_{1}}+\proj{\psi_{2}}$, where $\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
+is an orthonormal basis. Because we have 
+\begin{eqnarray*}
+\bar{\mu}\left(P_{0}\vee P_{1}\right) & = & \bar{\mu}\left(\mathbb{1}\right)=\necess\\
+\bar{\mu}\left(P_{0}P_{1}\right) & = & \bar{\mu}\left(\proj{\psi_{2}}\right)\subseteq\unknown
+\end{eqnarray*}
+and $\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$ is
+either $\necess+\unknown$ or $\unknown+\unknown$. Therefore, we
+have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
+
+Finally, we will prove that $\bar{\mu}$ cannot correspond to any
+quantum probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
+for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
+We must have 
+\begin{equation}
+\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
+\end{equation}
+By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
+such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. However, no pure
+state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
+so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
+measure~$\mu$.\qed\end{example}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\newpage{}%
 \begin{comment}

### 2017-02-15 prop_iop.tex
prop_iop.tex \section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}} Updating...

--- 2017-02-13 prop_iop.tex
@@
 \item For any projection $P$, 
-  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
-\item For a set of mutually orthogonal projections
-  $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
-  $\bar{\mu}\left(\sum_{i=1}^{N}
-    P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
+\begin{equation}
+\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
+\end{equation}
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have 
+\begin{equation}
+\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\end{equation}
 \end{itemize}
@@
 
-\begin{thm}Given a Hilbert space~$\Hilb$ of dimension~$3$, every
-quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is convex.\end{thm}
+\begin{thm}\label{thm:convex-3}Given a Hilbert space~$\Hilb$ of
+dimension~$3$, every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is convex.\end{thm}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage{}%
+\section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}}
+
+\begin{example}[Three-dimensional quantum three-value interval-valued
+probability measure]\label{ex:three-dimensional-three-value-1} Given
+a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
+and $\ket{\ps}=\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$.
+Let 
+\begin{equation}\eqalign{ 
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\ 
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,}\\ 
+\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
+}\end{equation}
+To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
+first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
+implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
+Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+it is sufficient to check 
+\[
+\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
+\]
+for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
+always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)$.
+
+Next, since the dimension of the Hilbert space is three, $\bar{\mu}$
+is convex by theorem~\ref{thm:convex-3}.
+
+Finally, we will prove that $\bar{\mu}$ cannot correspond to any
+quantum probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
+for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
+We must have $\mu(\proj{0})=\mu(\proj{\ps})=0$. By Gleason's theorem,
+there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
+such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. If $\ip{\phi}{0}=\ip{\phi}{\ps}=0$,
+we must have $\ket{\phi}=\ket{2}$, i.e., $\rho=\proj{2}$. However,
+$\mu(\proj{2})=\ip{2}{2}\ip{2}{2}=1\notin\unknown=\bar{\mu}\left(\proj{2}\right)$.
+Therefore, $\bar{\mu}$ has an empty core.\qed\end{example}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\newpage{}%
 \begin{comment}

### 2017-02-16 prop_iop.tex
prop.bib @Article{Bell1964} Updated, and update the font encoding...
prop_iop.tex \section{Why Empty Core?} Starting...

@@
 \usepackage{fullpage}
+\usepackage[T1,T2A]{fontenc}
 \usepackage[utf8]{inputenc}
@@
 with limited resources and poor precision may not uniquely identify
-the true state of the system, there is always at least one system that
-is consistent with the measurements. Surprisingly, we discovered a
-counterexample to this statement in the quantum case, i.e., we
-constructed the following convex quantum interval-valued probability
-measure with an empty core.
+the true state of the system, there is always at least one system
+that is consistent with the measurements. Surprisingly, we discovered
+a counterexample to this statement in the quantum case, and have the
+following theorem.
+
+\begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
+There is a convex quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.\end{thm}
+
+This theorem could be proved by constructing the following convex
+quantum interval-valued probability measure with an empty core.
 
@@
 \begin{figure}
-\begin{center}
-\includegraphics[scale=0.38]{figure2.eps}
-\end{center}
-\caption{\label{fig:three-dimensional-4-value}This figure illustrates
-  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
-  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
+\begin{centering}
+\includegraphics[scale=0.38]{figure2} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-4-value}This figure illustrates cases
+1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted in
+$\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
 and $\ket{\ps}$ respectively. All possible real vectors of the subspaces
-  $\ket{0_{\theta,\gamma}^{\perp}}$ and
-  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
-  circles, respectively. Within the circles, a dotted
-  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
-  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
-  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
-  green solid vectors are normalized
-  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
-  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
-  $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
+$\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
+are drawn in the red and green circles, respectively. Within the circles,
+a dotted vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
+otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
+a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
+and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
+and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively,
+where $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
 \end{figure}
+
+\section{Why Empty Core?}
+
+Notice that in the previous section,
+
+\subsection{Convexity}
+
+\subsection{From Quantum to Classical}
+
+\subsection{Increase the Measurement Resource}
 
@@
 or we might think it is induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
-or yet we might think it is induced by the mixed state $\mathbb{1} / 3$
+or yet we might think it is induced by the mixed state $\mathbb{1}/3$
 because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.

### 2017-02-16 prop_iop.tex
prop_iop.tex \section{Why Empty Core?} Updating...

@@
 \item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$. 
-\item $\bar{\mu}$ is called convex if $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+\item $\bar{\mu}$ is called convex if 
+\begin{equation}
+\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
+\end{equation}
 for all commuting $P_{0},P_{1}\in\events$. 
@@
 
-\begin{example}[Three-dimensional quantum three-interval-valued
-probability measure]\label{ex:three-dimensional-three-value} Given
-a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right) / \sqrt{2}$,
+\begin{example}[Three-dimensional quantum three-interval-valued probability
+measure]\label{ex:three-dimensional-three-value} Given a three dimensional
+Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
 $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and 
@@
 
+\section{Why Empty Core?}
+
+The possibility that a quantum interval-valued probability measure
+has an empty core departs from the classical cases. In order to understand
+its meaning, we will first study how to recover the non-empty core
+by adding conditions. Then, we will consider having an empty core
+as an legitimate result, and understand its consequence.
+
+\subsection{Convexity}
+
+One possibility is that the definition of quantum convexity is too
+weak to guarantee an convex quantum interval-valued probability measure
+has an non-empty core. However, the product of non-commuting projectors
+is not a projector so that equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+cannot be meaningful when $P_{0}$ and $P_{1}$ are non-commuting.
+
+Classically, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+is a special case of 
+\begin{equation}
+\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
+\end{equation}
+If a classical interval-valued probability measure~$\bar{\mu}$ satisfies
+equation~(\ref{eq:Dempster-Shafer-game}) for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
+then the left-end point of $\bar{\mu}$ is called a Dempster-Shafer
+belief function. Equation~(\ref{eq:Dempster-Shafer-game}) could
+be extended to the quantum case, and consider a quantum interval-valued
+probability measure satisfying 
+\begin{equation}
+\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
+\end{equation}
+for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
+However, example~\ref{ex:three-dimensional-three-value} satisfies
+equation~(\ref{eq:Dempster-Shafer-game-quantum}) as well. In another
+word, this kind of conditions cannot eliminate the situation of empty
+core.
+
+\subsection{Restricting the Event Space}
+
+\subsection{Increase the Measurement Resource}
+
+Looking closely at the example above, we might think that the probability
+measure $\bar{\mu}$ is induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
+or we might think it is induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
+or yet we might think it is induced by the mixed state $\mathbb{1}/3$
+because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.
+Each of these possibilities is compatible with some but not all of
+the observations. All is not lost however: if the observations are
+made more precise, we conjecture that some of the inconsistencies
+disappear. A partial proof of this conjecture is the following example
+which refines the previous convex probability measure by adding more
+precise intervals.
 \begin{figure}
@@
 
-\section{Why Empty Core?}
-
-Notice that in the previous section,
-
-\subsection{Convexity}
-
-\subsection{From Quantum to Classical}
-
-\subsection{Increase the Measurement Resource}
-
-Looking closely at the example above, we might think that the probability
-measure $\bar{\mu}$ is induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
-or we might think it is induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
-or yet we might think it is induced by the mixed state $\mathbb{1}/3$
-because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.
-Each of these possibilities is compatible with some but not all of
-the observations. All is not lost however: if the observations are
-made more precise, we conjecture that some of the inconsistencies
-disappear. A partial proof of this conjecture is the following example
-which refines the previous convex probability measure by adding more
-precise intervals.
-
-\begin{example}[Three-dimensional quantum four-interval-valued 
-  probability measure]\label{ex:three-dimensional-4-value}
-  Given a three dimensional Hilbert space with an orthonormal basis
-  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
-  }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-  $\ket{\ps}=\left(\ket{0}+\ket{1}\right) / \sqrt{2}$, and
-  $\ket{\minus}=\left(\ket{0}-\ket{1}\right) / \sqrt{2}$. The definition of
-  $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-4-value}
+\begin{example}[Three-dimensional quantum four-interval-valued probability
+measure]\label{ex:three-dimensional-4-value} Given a three dimensional
+Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Let\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
+$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, and $\ket{\minus}=\left(\ket{0}-\ket{1}\right)/\sqrt{2}$.
+The definition of $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-4-value}
 which plots the 1-dimensional projectors: 

### 2017-02-16 prop_iop.tex
prop_iop.tex \section{Quantum Interval-valued Probability Measures} Updating...

@@
 particular, any quantum probability measure can be recast as an interval-valued
-measure using arbitrary small intervals as discussed in appendix~\ref{sec:Real-and-Interval}.
+measure using arbitrary small intervals as discussed in \ref{sec:Real-and-Interval}.
 However, to simplify our discussion, we will focus on only three intervals
@@
 \unknown & otherwise. 
-}\label{eq:homomorphism}
-\end{equation}
+}\label{eq:homomorphism} \end{equation}
 For example, figure~\ref{fig:three-dimensional-3-value} plots the
@@
 This measure represents the beliefs of an experimenter with no prior
-knowledge about the particular quantum system in question. Formally,
-we can ask: what can we deduce about the state of a quantum system
-given a quantum interval-valued probability measure, i.e., given observations
-done with finite resources. In the case the intervals are infinitely
-precise the question reduces to Gleason's theorem which states that
-the state of the quantum system is uniquely determined by the probability
-measure. But surely the less resources are available, the less precise
-the intervals, and the less we expect to know about the state of the
-system. To formally state and answer this question we begin with defining
-the \emph{core} and \emph{convexity} of a probability measure as follows.
+knowledge about the particular quantum system in question.\footnote{\yutsung{Actually, $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$ is quite
+informative. Since $\iota\left(\mu_{\ket{0}}^{B}(P)\right)=\necess$
+if and only if $P=\proj{0}$, we know the core of $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
+is exactly $\left\{ \mu_{\ket{0}}^{B}\right\} $. The quantum interval-valued
+probability measure for an experimenter with no prior knowledge should
+be $\bar{\mu}(P)=\unknown$ for every projection~$P$.}} Formally, we can ask: what can we deduce about the state of a quantum
+system given a quantum interval-valued probability measure, i.e.,
+given observations done with finite resources. In the case the intervals
+are infinitely precise the question reduces to Gleason's theorem which
+states that the state of the quantum system is uniquely determined
+by the probability measure. But surely the less resources are available,
+the less precise the intervals, and the less we expect to know about
+the state of the system. To formally state and answer this question
+we begin with defining the \emph{core} and \emph{convexity} of a probability
+measure as follows. 
 \begin{figure}
 \begin{centering}
-\includegraphics[scale=0.38]{figure1.eps} 
+\includegraphics[scale=0.38]{figure1} 
 \par\end{centering}

### 2017-02-16 prop_iop.tex
prop_iop.tex Updating here and there...

@@
 that is consistent with the measurements. Surprisingly, we discovered
-a counterexample to this statement in the quantum case, and have the
-following theorem.
+a counterexample to this statement in the quantum case, and have:
 
@@
 The possibility that a quantum interval-valued probability measure
-has an empty core departs from the classical cases. In order to understand
-its meaning, we will first study how to recover the non-empty core
-by adding conditions. Then, we will consider having an empty core
+has an empty core departs from the classical case. To understand the
+meaning of it, we will first study how to recover the non-empty core
+with extra conditions. Then, we will consider having an empty core
 as an legitimate result, and understand its consequence.
@@
 One possibility is that the definition of quantum convexity is too
-weak to guarantee an convex quantum interval-valued probability measure
-has an non-empty core. However, the product of non-commuting projectors
-is not a projector so that equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-cannot be meaningful when $P_{0}$ and $P_{1}$ are non-commuting.
-
-Classically, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+weak to guarantee a convex quantum interval-valued probability measure
+having a non-empty core. On one hand, the product of non-commuting
+projectors is not a projector so equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+is unlikely to extended to non-commuting projectors~$P_{0}$ and
+$P_{1}$. On the other hand, we haven't found a way to guarantee a
+non-empty core if we only strength the condition on commuting projectors
+as well. For example, classically, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
 is a special case of 
@@
 belief function. Equation~(\ref{eq:Dempster-Shafer-game}) could
-be extended to the quantum case, and consider a quantum interval-valued
-probability measure satisfying 
+be extended to the quantum case. However, example~\ref{ex:three-dimensional-three-value}
+also satisfies the corresponding condition for quantum interval-valued
+probability measure: 
 \begin{equation}
@@
 for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
-However, example~\ref{ex:three-dimensional-three-value} satisfies
-equation~(\ref{eq:Dempster-Shafer-game-quantum}) as well. In another
-word, this kind of conditions cannot eliminate the situation of empty
-core.
+In another word, this kind of conditions cannot eliminate the situation
+of empty core.
 

### 2017-02-17 prop_iop.tex
prop_iop.tex \subsection{Convexity} Updating...

@@
 weak to guarantee a convex quantum interval-valued probability measure
-having a non-empty core. On one hand, the product of non-commuting
-projectors is not a projector so equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-is unlikely to extended to non-commuting projectors~$P_{0}$ and
-$P_{1}$. On the other hand, we haven't found a way to guarantee a
-non-empty core if we only strength the condition on commuting projectors
-as well. For example, classically, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-is a special case of 
-\begin{equation}
-\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
-\end{equation}
-If a classical interval-valued probability measure~$\bar{\mu}$ satisfies
-equation~(\ref{eq:Dempster-Shafer-game}) for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
-then the left-end point of $\bar{\mu}$ is called a Dempster-Shafer
-belief function. Equation~(\ref{eq:Dempster-Shafer-game}) could
-be extended to the quantum case. However, example~\ref{ex:three-dimensional-three-value}
-also satisfies the corresponding condition for quantum interval-valued
-probability measure: 
+having a non-empty core. On one hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+to non-commuting projectors~$P_{0}$ and $P_{1}$ is unlikely to
+success because the product of non-commuting projectors is not a projector.
+On the other hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+among commuting projectors cannot guarantee a non-empty core as well
+if we follow what people strengthen convexity classically. Equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+classically is a special case of 
+\begin{equation}
+\bar{\mu}'\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\label{eq:Dempster-Shafer-game}
+\end{equation}
+when $N=2$, where $\bar{\mu}'$ is a classical interval-valued probability
+measure. If $\bar{\mu}'$ satisfies equation~(\ref{eq:Dempster-Shafer-game})
+for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
+then the left-end point of $\bar{\mu}'$ is called a Dempster-Shafer
+belief function. It is reasonable to call a quantum interval-valued
+probability~$\bar{\mu}$ Dempster-Shafer if $\bar{\mu}$ satisfies
 \begin{equation}
@@
 for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
-In another word, this kind of conditions cannot eliminate the situation
-of empty core.
+However, the quantum interval-valued probability measure in example~\ref{ex:three-dimensional-three-value}
+is Dempster-Shafer and has an empty core. In summary, it is unlikely
+to guarantee a non-empty core by strengthening convexity.
 

### 2017-02-18 prop_iop.tex
prop_iop.tex \subsection{Restricting the Event Space} Starting...
prop_iop.tex Updating citations...

@@
 quantum state might be more like an interactive system suggested by
-Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
+Quantum Bayesianism or QBism~\cite{FuchsSchack2013,FuchsMerminSchack2014,VonBaeyer2016},
 which would interact differently with different clients. Furthermore,
@@
 \subsection{Restricting the Event Space}
+
+Since the discover of Heisenberg's uncertainty principle~\cite{Heisenberg1983,544199,Jaeger2007},
+non-commuting is one of the source of
 

### 2017-02-18 prop_iop.tex
prop_iop.tex \subsection{Restricting the Event Space} Updating...

@@
 
-Since the discover of Heisenberg's uncertainty principle~\cite{Heisenberg1983,544199,Jaeger2007},
-non-commuting is one of the source of
+Since the discover of Heisenberg's uncertainty principle~\cite{Heisenberg1983,peres1995quantum,544199,Griffiths2003,Jaeger2007},
+non-commuting observables is considered as one of the reason why quantum
+theory is different from the classical one. In another word, the uncertainty
+principle would not be observed if we could only access commuting
+observables. This is also true for a quantum interval-valued probability
+measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$. If we restrict
+our event space~$\events$ to a mutually commuting subspace~$\events'$,
+as proved in theorem~\ref{thm:sub-event-space}, the restricted $\bar{\mu}|_{\events'}$
+is essentially a classical interval-valued probability measure. Furthermore,
+if $\bar{\mu}$ is convex, then $\bar{\mu}|_{\events'}$ will be convex,
+and have a non-empty core classically.
+
+When $\bar{\mu}$ is restricted to different $\events'$, the core
+elements of each $\bar{\mu}|_{\events'}$ may not be glued together,
+and gives a core element of $\bar{\mu}$. The inability of gluing
+core elements among commuting $\events'$ to non-commuting $\events$
+is consistent with the proof of the Kochen-Specker theorem, where
+each triple of commuting observables could be colored well, but we
+cannot color all observables which are not all commuting. This is
+also consistent with the assertion that mutually commuting observables
+could be measured simultaneously~\cite{Mermin_1993}. In another
+word, if Alice and Bob in Bell's theorem can only pick from a set
+of mutually commuting observables, they could never observe any ``quantum,``
+and prove the quantum theory cannot be simulated by a local hidden
+variable theory in this setting.
 
@@
 is consistent with the elegantly recent work on Quantum Bayesianism
-or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which suggests
-that the quantum state is more like an interactive system in computer
-science parlance. In another word, the quantum state is subjective:
-each observer has a different view of the quantum system that is consistent
-with their previous observations and that allows that observer, independently
-of other observers, to assign beliefs (i.e., probabilities) to possible
-future interactions.
+or QBism~\cite{FuchsSchack2013,FuchsMerminSchack2014,VonBaeyer2016},
+which suggests that the quantum state is more like an interactive
+system in computer science parlance. In another word, the quantum
+state is subjective: each observer has a different view of the quantum
+system that is consistent with their previous observations and that
+allows that observer, independently of other observers, to assign
+beliefs (i.e., probabilities) to possible future interactions.
 
@@
 
-\begin{thm}Given a Hilbert space~$\Hilb$ and a mutually commuting
-sub-event space~$\events'\subseteq\events$, there is set~$\Omega$
-and a function~$\tau:\events'\rightarrow2^{\Omega}$ such that:
+\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
+and a mutually commuting sub-event space~$\events'\subseteq\events$,
+there is set~$\Omega$ and a function~$\tau:\events'\rightarrow2^{\Omega}$
+such that:
 \begin{itemize}

### 2017-02-18 prop_iop.tex
prop_iop.tex \section{Examples for Quantum Interval-valued Probability Measures} Updating...

@@
 \newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
+\newcommand{\midd}{{\mbox{\wesa{middle}}}}
 \newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
@@
 It is straightforward but tedious to check that $\bar{\mu}$ is a
-quantum interval-valued probability measure. Although we have not
-verified that $\bar{\mu}$ is convex, the following argument establishes
+quantum interval-valued probability measure, and $\bar{\mu}$ is convex
+by theorem~\ref{thm:convex-3}. The following argument establishes
 that is has an empty core. Assume there is a real-valued probability
@@
 sense that it might only be induced by $\ket{2}$ or the density matrix
-$\mathbb{1} / 3$, but not by $\ket{1}$. \end{example}
+$\mathbb{1}/3$, but not by $\ket{1}$. \end{example}
 
@@
 
-\begin{example}[Three-dimensional quantum three-value interval-valued
-probability measure]\label{ex:three-dimensional-three-value-1} Given
-a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
-and $\ket{\ps}=\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$.
-Let 
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.38]{figureE1} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-5-value}This figure illustrates cases
+1 and 2 of example~\ref{ex:three-dimensional-5-value} plotted in
+$\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
+and $\ket{\ps}$ respectively. All possible real vectors of the subspaces
+orthogonal to $\ket{0}$ or $\ket{\ps}$ are drawn in the red and
+green circles, respectively.}
+\end{figure}
+
+\begin{example}[Three-dimensional quantum 5-interval-valued probability
+measure]\label{ex:three-dimensional-5-value} Given a three dimensional
+Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Let\emph{ }$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\minus}=\left(\ket{0}-\ket{1}\right)/\sqrt{2}$,
+and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess,\midd\right\} $,
+where $\midd$ represents $\left[\frac{1}{4},\frac{3}{4}\right]$.
+The definition of $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-5-value}
+which plots the 1-dimensional projectors: 
+\begin{enumerate}
+\item Let: 
 \begin{equation}\eqalign{ 
 \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,}\\ 
-\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,} 
 }\end{equation}
-To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
-first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
-implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
-implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
-Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-it is sufficient to check 
-\[
-\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
-\]
-for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
-always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)$.
-
-Next, since the dimension of the Hilbert space is three, $\bar{\mu}$
-is convex by theorem~\ref{thm:convex-3}.
-
-Finally, we will prove that $\bar{\mu}$ cannot correspond to any
-quantum probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
-for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
-We must have $\mu(\proj{0})=\mu(\proj{\ps})=0$. By Gleason's theorem,
-there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
-such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. If $\ip{\phi}{0}=\ip{\phi}{\ps}=0$,
-we must have $\ket{\phi}=\ket{2}$, i.e., $\rho=\proj{2}$. However,
-$\mu(\proj{2})=\ip{2}{2}\ip{2}{2}=1\notin\unknown=\bar{\mu}\left(\proj{2}\right)$.
-Therefore, $\bar{\mu}$ has an empty core.\qed\end{example}
+where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green
+dotted vectors, respectively. 
+\item The red and green circles are are the states orthogonal to $\ket{0}$
+and $\ket{\ps}$, respectively. We define 
+\begin{equation}\eqalign{ 
+\bar{\mu}\left(\proj{\psi}\right)=\likely\textrm{ ,}\\ 
+\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\unlikely\textrm{ ,} 
+}\end{equation}
+where $\ip{\psi}{0}=0$ or $\ip{\psi}{\ps}=0$.
+\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
+\end{enumerate}
+It is straightforward but tedious to check that $\bar{\mu}$ is a
+quantum interval-valued probability measure, and $\bar{\mu}$ is convex
+by theorem~\ref{thm:convex-3}. The following argument establishes
+that is has an empty core. Assume there is a real-valued probability
+measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$.
+Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
+and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
+we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
+so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
+\begin{equation}
+\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
+\end{equation}
+This measure however is ``better'' than the previous one in the
+sense that it might only be induced by $\ket{2}$ or the density matrix
+$\mathbb{1}/3$, but not by $\ket{1}$. \end{example}
 

### 2017-02-19 prop_iop.tex
prop_iop.tex \section{Why Empty Core?} Updating...

@@
 \begin{equation}
-\bar{\mu}'\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\label{eq:Dempster-Shafer-game}
+\bar{\mu}'\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is odd}}}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is even}}}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\label{eq:Dempster-Shafer-game}
 \end{equation}
@@
 \begin{equation}
-\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
+\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is odd}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is even}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
 \end{equation}
@@
 
-\subsection{Restricting the Event Space}
+\subsection{Commuting Sub-Event Space}
 
 Since the discover of Heisenberg's uncertainty principle~\cite{Heisenberg1983,peres1995quantum,544199,Griffiths2003,Jaeger2007},
-non-commuting observables is considered as one of the reason why quantum
-theory is different from the classical one. In another word, the uncertainty
-principle would not be observed if we could only access commuting
-observables. This is also true for a quantum interval-valued probability
-measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$. If we restrict
-our event space~$\events$ to a mutually commuting subspace~$\events'$,
-as proved in theorem~\ref{thm:sub-event-space}, the restricted $\bar{\mu}|_{\events'}$
-is essentially a classical interval-valued probability measure. Furthermore,
-if $\bar{\mu}$ is convex, then $\bar{\mu}|_{\events'}$ will be convex,
-and have a non-empty core classically.
+the existence of non-commuting observables is one of the reason why
+quantum theory is different from the classical theory. In another
+word, the uncertainty principle would not be observed if we could
+only access commuting observables. This is also true for a quantum
+interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
+If we restrict our event space~$\events$ to a mutually commuting
+subspace~$\events'$, as proved in theorem~\ref{thm:sub-event-space},
+the restricted $\bar{\mu}|_{\events'}$ is essentially a classical
+interval-valued probability measure. Furthermore, if $\bar{\mu}$
+is convex, then $\bar{\mu}|_{\events'}$ will be convex, and have
+a non-empty core classically.
 

### 2017-02-19 prop_iop.tex
prop_iop.tex Updating here and there, and found the previous footnote is wrong... orz

@@
 }\end{equation}
-It is straightforward to verify that $\bar{\mu}$ is a convex quantum
-interval-valued probability measure. Now assume there exists a real-valued
-quantum probability measure $\mu$ such that $\mu(P)\in\bar{\mu}(P)$
+It is straightforward to verify that $\bar{\mu}$ is a quantum interval-valued
+probability measure by theorem~\ref{thm:interval-valued-frame-function}
+and convex by theorem~\ref{thm:convex-3}. Now assume there exists
+a real-valued quantum probability measure $\mu$ such that $\mu(P)\in\bar{\mu}(P)$
 for every event (projection)~$P$. We derive a contradiction as follows.
@@
 
-\begin{lemma}\label{lemma:interval-valued-frame-function}An interval-valued
+\begin{thm}\label{thm:interval-valued-frame-function}An interval-valued
 frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ satisfies
@@
 \item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
-we have $1\in\sum_{i=0}^{2}\bar{f}\left(\ket{\psi_{i}}\right)$ and
-$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
+we have $\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
 where $i$, $j$, and $k$ are any permutations among $0$, $1$,
@@
 satisfies the above properties, $\bar{f}$ must be an interval-valued
-frame function.\end{lemma}
-\begin{proof}
-Given a quantum IVPM~$\bar{\mu}$, it is straightforward to verify
-that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
+frame function.\end{thm}
+
+\begin{proof} Given a quantum IVPM~$\bar{\mu}$, it is straightforward
+to verify that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
 satisfies the above properties.
@@
 \end{itemize}
-Since other conditions are trivial, we only need to verify 
-\begin{equation}
-\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:quantumIVPMconditions}
-\end{equation}
- for any set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$.
-First, if $\mathbb{0}$ or $\mathbb{1}$ is in $\left\{ P_{i}\right\} _{i=1}^{N}$,
-the statement could be reduced to the case without $\mathbb{0}$,
-or its trivial. Hence, we only need to discuss $\left\{ P_{i}\right\} _{i=1}^{N}$
-containing 1- or 2-dimensional projectors. When $\left\{ P_{i}\right\} _{i=1}^{N}$
-containing a 2-dimensional projector, the definition of $\bar{\mu}$
-implies equation~(\ref{eq:quantumIVPMconditions}). When $\left\{ P_{i}\right\} _{i=1}^{N}$
-only containing 1-dimensional projectors, the properties of $\bar{f}$
-implies equation~(\ref{eq:quantumIVPMconditions}).
-\end{proof}
+Since other conditions are trivial, we only need to verify equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+First notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+implies equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+by induction. Second, equation~(\ref{eq:QuantumInterval-valuedProbability-Complement})
+implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
+Therefore, to prove equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+it is sufficient to check 
+\begin{equation}
+\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
+\end{equation}
+for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
+always holds because the properties of $\bar{f}$.\end{proof}
 \begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}\alpha_{0}\\
@@
 In order to simplify the discussion, we call a function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$
-satisfying conditions in lemma~\ref{lemma:interval-valued-frame-function}
+satisfying conditions in theorem~\ref{thm:interval-valued-frame-function}
 a real interval-valued frame function. Obviously, any results in appendix~\ref{sec:Interval-valued-Frame-Functions}
@@
 \end{figure}
-\begin{proof}
-We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
+\begin{proof} We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
 Let the yellow circle is the states whose latitude is $\theta_{0}$.
@@
 Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
-basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
+basis, by theorem~\ref{thm:interval-valued-frame-function}, we have
+
 \begin{equation} 
@@
 basis and $\bar{f}\left(\ket{A}\right)=\bar{f}\left(\ket{B}\right)=\bar{f}\left(\ket{C}\right)=\left[l_{0},1-l_{0}\right]$,
-we have the following inequalities by
-lemma~\ref{lemma:interval-valued-frame-function},
-\begin{equation}\eqalign{
-1\in\left[3l_{0},3-3l_{0}\right] \Rightarrow l_{0}\le\frac{1}{3}\textrm{ ,}\\
-\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right]
-\Rightarrow l_{0}\le0\textrm{ .}
-}\end{equation}
+we have the following inequalities by theorem~\ref{thm:interval-valued-frame-function},
+\begin{equation}
+\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right]\Rightarrow l_{0}\le0\textrm{ .}
+\end{equation}
 Recall that $0\le l_{0}\le\frac{1}{2}$. Therefore, $l_{0}=0$, that
-is, $\unknown=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$.
-\end{proof}
+is, $\unknown=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$. \end{proof}
 
@@
 \item The red and green circles are are the states orthogonal to $\ket{0}$
-and $\ket{\ps}$, respectively. We define 
-\begin{equation}\eqalign{ 
-\bar{\mu}\left(\proj{\psi}\right)=\likely\textrm{ ,}\\ 
-\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\unlikely\textrm{ ,} 
-}\end{equation}
+and $\ket{\ps}$, respectively. We define $\bar{\mu}\left(\proj{\psi}\right)=\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\midd$,
 where $\ip{\psi}{0}=0$ or $\ip{\psi}{\ps}=0$.
@@
 \end{enumerate}
-It is straightforward but tedious to check that $\bar{\mu}$ is a
-quantum interval-valued probability measure, and $\bar{\mu}$ is convex
-by theorem~\ref{thm:convex-3}. The following argument establishes
-that is has an empty core. Assume there is a real-valued probability
-measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$.
-Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
+By theorem~\ref{thm:interval-valued-frame-function}, to check $\bar{\mu}$
+a quantum interval-valued probability measure is equivalent to check
+$\bar{f}$ satisfying 
+\begin{equation}\eqalign{ 
+\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)\subseteq\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)\subseteq\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ ,}\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)\subseteq\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)\textrm{ ,}
+}\label{eq:non-additive-vectors}\end{equation}
+for every orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
+where $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
+We are going to enumerate all possible orthonormal bases to verify
+equation~(\ref{eq:non-additive-vectors}), and case 1 and 2 are illustrated
+in figure~\ref{fig:three-dimensional-5-value}.
+\begin{enumerate}
+\item When $\ket{\psi_{0}}$ is $\ket{0}$, then $\ip{\psi_{1}}{0}=\ip{\psi_{2}}{0}=0$.
+Equation~(\ref{eq:non-additive-vectors}) can then be verified as
+follow. 
+\begin{equation}\eqalign{ 
+\left[1,1\right]-\bar{f}\left(\ket{0}\right)=\necess\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\midd\subseteq\midd+\imposs=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{0}\right)\textrm{ ,}
+}\end{equation}
+Similarly, when $\ket{\psi_{0}}$ is $\ket{\ps}$, equation~(\ref{eq:non-additive-vectors})
+holds. 
+\item When $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$, $\ip{\psi_{0}}{0}=0$,
+and $\ip{\psi_{1}}{\ps}=0$, we have $\ip{\psi_{2}}{0}\ne0$ and $\ip{\psi_{2}}{\ps}\ne0$.
+Then, we have 
+\begin{equation}\eqalign{ 
+\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\midd+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)=\likely\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)\textrm{ .}
+}\end{equation}
+\item When $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$, $\ip{\psi_{0}}{0}=0$,
+$\ip{\psi_{1}}{0}\ne0$, $\ip{\psi_{1}}{\ps}\ne0$, $\ip{\psi_{2}}{0}\ne0$
+and $\ip{\psi_{2}}{\ps}\ne0$. Then, we have 
+\begin{equation}\eqalign{ 
+\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\likely\nsubseteq\unlikely+\midd=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ .}
+}\end{equation}
+\footnote{\yutsung{{My previous footnote was wrong. }Need to recompute. Sigh...}}
+\item The ``otherwise'' case. Then, equation~(\ref{eq:non-additive-vectors})
+can easily be verified. 
+\begin{equation}
+\left[1,1\right]-\bar{f}\left(\ket{\psi_{0}}\right)=\likely\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_{1}}\right)+\bar{f}\left(\ket{\psi_{2}}\right)\textrm{ .}
+\end{equation}
+\end{enumerate}
+$\bar{\mu}$ is convex by theorem~\ref{thm:convex-3}. The following
+argument establishes that is has an empty core. Assume there is a
+real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
+for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
 and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,

### 2017-02-19 prop_iop.tex
prop_iop.tex \section{Examples for Quantum Interval-valued Probability Measures} Updating...

@@
 \end{equation}
-for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
-always holds because the properties of $\bar{f}$.\end{proof}
+for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$,which always
+holds because the properties of $\bar{f}$.\end{proof}
 \begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}\alpha_{0}\\
@@
 Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let\emph{ }$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\minus}=\left(\ket{0}-\ket{1}\right)/\sqrt{2}$,
-and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess,\midd\right\} $,
+Let\emph{ }$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, and
+$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess,\midd\right\} $,
 where $\midd$ represents $\left[\frac{1}{4},\frac{3}{4}\right]$.
@@
 dotted vectors, respectively. 
-\item The red and green circles are are the states orthogonal to $\ket{0}$
+\item The red and green circles are the states orthogonal to $\ket{0}$
 and $\ket{\ps}$, respectively. We define $\bar{\mu}\left(\proj{\psi}\right)=\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\midd$,
@@
 \left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)\subseteq\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)\subseteq\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)\textrm{ ,}
+\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)\subseteq\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)
 }\label{eq:non-additive-vectors}\end{equation}
-for every orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
+for every orthonormal basis~$\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $,
 where $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
 We are going to enumerate all possible orthonormal bases to verify
-equation~(\ref{eq:non-additive-vectors}), and case 1 and 2 are illustrated
-in figure~\ref{fig:three-dimensional-5-value}.
+equation~(\ref{eq:non-additive-vectors}). Also, to simplify the
+notation, we denote $\set{\ket{\psi}}{\ip{\psi}{0}\ne0\textrm{ and }\ip{\psi}{\ps}\ne0}$
+by $\mathcal{T}$.
 \begin{enumerate}
@@
 \left[1,1\right]-\bar{f}\left(\ket{0}\right)=\necess\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\midd\subseteq\midd+\imposs=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{0}\right)\textrm{ ,}
+\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\midd=\midd+\imposs=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{0}\right)\textrm{ ,}
 }\end{equation}
@@
 holds. 
-\item When $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$, $\ip{\psi_{0}}{0}=0$,
-and $\ip{\psi_{1}}{\ps}=0$, we have $\ip{\psi_{2}}{0}\ne0$ and $\ip{\psi_{2}}{\ps}\ne0$.
-Then, we have 
+\item When $\ip{\psi_{0}}{0}=\ip{\psi_{1}}{\ps}=0$ and $\ket{\psi_{2}}\in\mathcal{T}$,
+we have 
 \begin{equation}\eqalign{ 
@@
 }\end{equation}
-\item When $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$, $\ip{\psi_{0}}{0}=0$,
-$\ip{\psi_{1}}{0}\ne0$, $\ip{\psi_{1}}{\ps}\ne0$, $\ip{\psi_{2}}{0}\ne0$
-and $\ip{\psi_{2}}{\ps}\ne0$. Then, we have 
+\item When $\ip{\psi_{0}}{0}=0$, and $\ket{\psi_{1}}$, $\ket{\psi_{2}}\in\mathcal{T}$,
+we have 
 \begin{equation}\eqalign{ 
 \left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\likely\nsubseteq\unlikely+\midd=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ .}
+\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\likely\subseteq\unlikely+\midd=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ .}
 }\end{equation}
-\footnote{\yutsung{{My previous footnote was wrong. }Need to recompute. Sigh...}}
-\item The ``otherwise'' case. Then, equation~(\ref{eq:non-additive-vectors})
+Similarly, when $\ip{\psi_{0}}{\ps}=0$, $\ket{\psi_{1}}\in\mathcal{T}$,
+and $\ket{\psi_{2}}\in\mathcal{T}$, equation~(\ref{eq:non-additive-vectors})
+holds. 
+\item When $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}\in\mathcal{T}$,
+i.e., the ``otherwise'' case. Then, equation~(\ref{eq:non-additive-vectors})
 can easily be verified. 
@@
 \end{enumerate}
-$\bar{\mu}$ is convex by theorem~\ref{thm:convex-3}. The following
-argument establishes that is has an empty core. Assume there is a
-real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
-for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
-and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
+Since we proved that $\bar{\mu}$ is a quantum interval-valued probability
+measure, $\bar{\mu}$ is convex by theorem~\ref{thm:convex-3}.
+
+The following argument establishes that $\bar{\mu}$ has an empty
+core. Assume there is a real-valued probability measure satisfying
+$\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$. Because
+$\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$ and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
 we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
@@
 \end{equation}
-This measure however is ``better'' than the previous one in the
-sense that it might only be induced by $\ket{2}$ or the density matrix
-$\mathbb{1}/3$, but not by $\ket{1}$. \end{example}
+\end{example}
 

### 2017-02-19 prop_iop.tex
prop_iop.tex \section{Why Empty Core?} Updating...

@@
 
-The possibility that a quantum interval-valued probability measure
-has an empty core departs from the classical case. To understand the
-meaning of it, we will first study how to recover the non-empty core
-with extra conditions. Then, we will consider having an empty core
-as an legitimate result, and understand its consequence.
+The possibility that a convex quantum interval-valued probability
+measure has an empty core departs from the classical case. To understand
+the meaning of it, we will first study how to recover the non-empty
+core with extra conditions. Then, we will consider having an empty
+core as an legitimate result, and understand its consequence.
 
@@
 
-One possibility is that the definition of quantum convexity is too
-weak to guarantee a convex quantum interval-valued probability measure
-having a non-empty core. On one hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+One possibility for having an empty core is that the definition of
+quantum convexity is too weak. On one hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
 to non-commuting projectors~$P_{0}$ and $P_{1}$ is unlikely to
@@
 
-Since the discover of Heisenberg's uncertainty principle~\cite{Heisenberg1983,peres1995quantum,544199,Griffiths2003,Jaeger2007},
-the existence of non-commuting observables is one of the reason why
-quantum theory is different from the classical theory. In another
-word, the uncertainty principle would not be observed if we could
-only access commuting observables. This is also true for a quantum
-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
-If we restrict our event space~$\events$ to a mutually commuting
-subspace~$\events'$, as proved in theorem~\ref{thm:sub-event-space},
+Another reason for having an empty core is the existence of non-commuting
+observables. Non-commutativity is one of the difference between quantum
+and classical since Heisenberg's uncertainty principle states there
+is an intrinsic uncertainty measuring non-commuting observables in
+quantum mechanics~\cite{Heisenberg1983,peres1995quantum,544199,Griffiths2003,Jaeger2007}.
+Similarly, we argue that the quantum phenomenon disappears when we
+restrict the domain of a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+on a mutually commuting subspace~$\events'$. As proved in theorem~\ref{thm:sub-event-space},
 the restricted $\bar{\mu}|_{\events'}$ is essentially a classical
@@
 
-When $\bar{\mu}$ is restricted to different $\events'$, the core
-elements of each $\bar{\mu}|_{\events'}$ may not be glued together,
-and gives a core element of $\bar{\mu}$. The inability of gluing
-core elements among commuting $\events'$ to non-commuting $\events$
-is consistent with the proof of the Kochen-Specker theorem, where
-each triple of commuting observables could be colored well, but we
-cannot color all observables which are not all commuting. This is
-also consistent with the assertion that mutually commuting observables
+When $\bar{\mu}$ is restricted to different commuting $\events'$,
+the core elements of each $\bar{\mu}|_{\events'}$ may not be glued
+together, and gives a core element of $\bar{\mu}$. The inability
+of gluing core elements among commuting $\events'$ to non-commuting
+$\events$ is consistent with the proof of the Kochen-Specker theorem,
+where each triple of commuting observables could be colored well,
+but we cannot color all observables which are not all commuting. This
+is also consistent with the assertion that mutually commuting observables
 could be measured simultaneously~\cite{Mermin_1993}. In another
@@
 and prove the quantum theory cannot be simulated by a local hidden
-variable theory in this setting.
+variable theory.
 
 \subsection{Increase the Measurement Resource}
+
+We can apply the idea of restricting the event space in example~\ref{ex:three-dimensional-three-value},
+but instead of commuting sub-event space, we will try to find the
+biggest subset~$\events'\subseteq\events$ such that $\bar{\mu}|_{\events'}$
+has an non-empty core.
 

### 2017-02-20 prop_iop.tex
prop_iop.tex After visiting the Writing Tutorial Services...

@@
 system given a quantum interval-valued probability measure, i.e.,
-given observations done with finite resources. In the case the intervals
-are infinitely precise the question reduces to Gleason's theorem which
-states that the state of the quantum system is uniquely determined
-by the probability measure. But surely the less resources are available,
-the less precise the intervals, and the less we expect to know about
-the state of the system. To formally state and answer this question
-we begin with defining the \emph{core} and \emph{convexity} of a probability
-measure as follows. 
+given observations done with finite resources. In the case that the
+intervals are infinitely precise, the question reduces to Gleason's
+theorem which states that the state of the quantum system is uniquely
+determined by the probability measure. But surely the less resources
+are available, the less precise the intervals, and the less we expect
+to know about the state of the system. To formally state and answer
+this question we begin with defining the \emph{core} and \emph{convexity}
+of a probability measure as follows. 
 \begin{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Why Empty Core?}
@@
 the meaning of it, we will first study how to recover the non-empty
-core with extra conditions. Then, we will consider having an empty
+core with extra conditions. We will then consider having an empty
 core as an legitimate result, and understand its consequence.
@@
 to non-commuting projectors~$P_{0}$ and $P_{1}$ is unlikely to
-success because the product of non-commuting projectors is not a projector.
+succeed because the product of non-commuting projectors is not a projector.
 On the other hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
@@
 We can apply the idea of restricting the event space in example~\ref{ex:three-dimensional-three-value},
-but instead of commuting sub-event space, we will try to find the
-biggest subset~$\events'\subseteq\events$ such that $\bar{\mu}|_{\events'}$
-has an non-empty core.
-
-Looking closely at the example above, we might think that the probability
-measure $\bar{\mu}$ is induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
-or we might think it is induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
-or yet we might think it is induced by the mixed state $\mathbb{1}/3$
+but instead of commuting sub-event space, we will try to find some
+subset~$\events'\subseteq\events$ such that $\bar{\mu}|_{\events'}$
+has an non-empty core. The following are three of all possibilities:
+\begin{itemize}
+\item When $\events'=\events\backslash\left\{ \proj{\ps'}\right\} $, because
+$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{2}}^{B}\right\} $.
+\item When $\events'=\events\backslash\left\{ \proj{\ps}\right\} $, because
+$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we have $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{1}}^{B}\right\} $.
+\item When $\events'=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
+because $\mu_{\frac{\mathbb{1}}{3}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events'}\right)$
 because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.
+\end{itemize}
 Each of these possibilities is compatible with some but not all of
-the observations. All is not lost however: if the observations are
-made more precise, we conjecture that some of the inconsistencies
-disappear. A partial proof of this conjecture is the following example
-which refines the previous convex probability measure by adding more
-precise intervals.
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.38]{figure2} 
-\par\end{centering}
-\caption{\label{fig:three-dimensional-4-value}This figure illustrates cases
-1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted in
-$\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
-and $\ket{\ps}$ respectively. All possible real vectors of the subspaces
-$\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
-are drawn in the red and green circles, respectively. Within the circles,
-a dotted vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
-otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
-a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
-and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
-and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively,
-where $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
-\end{figure}
-
-\begin{example}[Three-dimensional quantum four-interval-valued probability
-measure]\label{ex:three-dimensional-4-value} Given a three dimensional
-Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
-$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, and $\ket{\minus}=\left(\ket{0}-\ket{1}\right)/\sqrt{2}$.
-The definition of $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-4-value}
-which plots the 1-dimensional projectors: 
-\begin{enumerate}
-\item Let:
-\begin{equation}\eqalign{
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,}
-}\end{equation}
-where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green dotted
-vectors, respectively.
-\item The red and green circles are are the states orthogonal to
-  $\ket{0}$ and $\ket{\ps}$, respectively, and can be parametrized as
-  $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
-  and
-  $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\minus}+\cos\theta\ket{2}$,
-  where $0\le\theta\le\pi / 2$ and $0\le\gamma<2\pi$. The dotted
-  half of those states need special treatment, i.e., whenever
-  $0\le\theta<\pi / 2$ and $0\le\gamma<\pi$, we define
-\begin{equation}\eqalign{
-\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\likely\textrm{ ,}\\
-\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right)=
-  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\unlikely\textrm{ .}
-}\end{equation}
-\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
-\end{enumerate}
-It is straightforward but tedious to check that $\bar{\mu}$ is a
-quantum interval-valued probability measure, and $\bar{\mu}$ is convex
-by theorem~\ref{thm:convex-3}. The following argument establishes
-that is has an empty core. Assume there is a real-valued probability
-measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$.
-Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
-and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
-we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
-so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
-\begin{equation}
-\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
-\end{equation}
-This measure however is ``better'' than the previous one in the
-sense that it might only be induced by $\ket{2}$ or the density matrix
-$\mathbb{1}/3$, but not by $\ket{1}$. \end{example}
-
-In general, each two 1-dimensional projectors~$\proj{\psi_{0}}$
-and $\proj{\psi_{1}}$ mapping to $\imposs$ suggests $\bar{\mu}$
-might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
-in the Hilbert space of dimension 3. As we illustrated in figure~\ref{fig:three-dimensional-3-value},
+the observations. The first two possibilities are particular interesting
+since each two 1-dimensional projectors~$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
+mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
+such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}\right\} $
+in the Hilbert space of dimension 3, where the cross product of complex
+vectors is defined in definition~\ref{def:cross-product}.
+
+As we illustrated in figure~\ref{fig:three-dimensional-3-value},
 if $\bar{\mu}$ has a non-empty core, the states mapping to $\imposs$
@@
 \begin{centering}
-\includegraphics[scale=0.38]{figure3.eps} 
+\includegraphics[scale=0.38]{figure3} 
 \par\end{centering}

### 2017-02-20 prop_iop.tex
prop_iop.tex Updating here and there...

@@
 }\label{eq:homomorphism} \end{equation}
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.38]{figure1} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
+1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
+plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
+and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$. $\ket{0}$
+is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$
+for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
+we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
+\end{figure}
 For example, figure~\ref{fig:three-dimensional-3-value} plots the
@@
 of a probability measure as follows.
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.38]{figure1} 
-\par\end{centering}
-\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
-1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
-plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
-and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$. $\ket{0}$
-is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$
-for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
-we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
-\end{figure}
 
@@
 \noindent The core of an interval-valued probability measure is the
-set of real-valued infinitely-precise probability measures it
-approximates. An interval-valued probability measure is convex if
-whenever certain intervals exist then combinations of these intervals
-must also exist, guaranteeing we can add and manipulate probabilities
-coherently. In the classical world, every convex measure has a
-non-empty core, which means that the interval-valued probability
-measure must approximate at least one infinitely-precise measure.
+set of real-valued infinitely-precise probability measures it approximates.
+An interval-valued probability measure is convex if whenever certain
+intervals exist then combinations of these intervals must also exist,
+guaranteeing we can add and manipulate probabilities coherently. In
+the classical world, every convex measure has a non-empty core, which
+means that the interval-valued probability measure must approximate
+at least one infinitely-precise measure.
 
@@
 Every (classical) convex interval-valued probability measure has a
-  non-empty core.
-\end{thm}
+non-empty core. \end{thm}
 
@@
 quantum interval-valued probability measure with an empty core.
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.38]{figure2_1} 
+\par\end{centering}
+\caption{\label{fig:three-dimensional-3-value-2}This figure illustrates example~\ref{ex:three-dimensional-three-value}
+plotted in $\mathbb{R}^{3}$. The red, green, and blue vectors are
+$\ket{0}$, $\ket{\ps}$, and $\ket{\ps'}$ respectively. }
+\end{figure}
 
@@
 \item When $\events'=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
-because $\mu_{\frac{\mathbb{1}}{3}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events'}\right)$
-because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.
+because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$,
+we have $\mu_{\frac{\mathbb{1}}{3}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events'}\right)$
+as well as $\mu_{\ket{2}}^{B}$ and $\mu_{\ket{1}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events'}\right)$.
 \end{itemize}
@@
 Although quantum IVPMs in example~\ref{ex:three-dimensional-three-value}
-and \ref{ex:three-dimensional-4-value} have empty cores, we might
+and \ref{ex:three-dimensional-5-value} have empty cores, we might
 still think that the probability measure~$\bar{\mu}$ is induced
@@
 or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
-In example~\ref{ex:three-dimensional-4-value}, the probability measure~$\bar{\mu}$
+In example~\ref{ex:three-dimensional-5-value}, the probability measure~$\bar{\mu}$
 might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
@@
 holds because the properties of $\bar{f}$.\end{proof}
-\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}\alpha_{0}\\
+\begin{definition}\label{def:cross-product}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}
+\alpha_{0}\\
 \alpha_{1}\\
 \alpha_{2}
-\end{array}\right)$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\left(\begin{array}{c}\beta_{0}\\
+\end{array}\right)$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\left(\begin{array}{c}
+\beta_{0}\\
 \beta_{1}\\
@@
 \begin{equation}
-\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\left|\begin{array}{cc}\alpha_{1}^{*} & \beta_{1}^{*}\\
+\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\left|\begin{array}{cc}
+\alpha_{1}^{*} & \beta_{1}^{*}\\
 \alpha_{2}^{*} & \beta_{2}^{*}
-\end{array}\right|\ket{0}+\left|\begin{array}{cc}\alpha_{2}^{*} & \beta_{2}^{*}\\
+\end{array}\right|\ket{0}+\left|\begin{array}{cc}
+\alpha_{2}^{*} & \beta_{2}^{*}\\
 \alpha_{0}^{*} & \beta_{0}^{*}
-\end{array}\right|\ket{1}+\left|\begin{array}{cc}\alpha_{0}^{*} & \beta_{0}^{*}\\
+\end{array}\right|\ket{1}+\left|\begin{array}{cc}
+\alpha_{0}^{*} & \beta_{0}^{*}\\
 \alpha_{1}^{*} & \beta_{1}^{*}
@@
 \end{equation}
-where $\left|\begin{array}{cc}\alpha & \beta\\
+where $\left|\begin{array}{cc}
+\alpha & \beta\\
 \alpha' & \beta'
@@
 cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
-as usual. We will use $\ket{\psi}\times\ket{\phi}$ and
-$\ket{\psi}\times\ket{\phi}/\left\Vert
-\ket{\psi}\times\ket{\phi}\right\Vert$ interchanged when there is no
-confusion.\end{definition}
+as usual. We will use $\ket{\psi}\times\ket{\phi}$ and $\ket{\psi}\times\ket{\phi}/\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert $
+interchanged when there is no confusion.\end{definition}
 

### 2017-02-20 prop_iop.tex
prop_iop.tex \section{Interval-valued Frame Functions\label{sec:Interval-valued-Frame-Functions}} Updating...

@@
 for some pure state~$\ket{\phi}$, then $\ket{\phi}\parallel\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)$.
-For example, example~\ref{ex:three-dimensional-4-value} is in this
+For example, example~\ref{ex:three-dimensional-5-value} is in this
 case when the core is empty; an interval-valued frame function defined

### 2017-02-20 prop_iop.tex
prop_iop.tex \subsection{Increase the Measurement Resource} Updating...

@@
 
-We can apply the idea of restricting the event space in example~\ref{ex:three-dimensional-three-value},
-but instead of commuting sub-event space, we will try to find some
-subset~$\events'\subseteq\events$ such that $\bar{\mu}|_{\events'}$
-has an non-empty core. The following are three of all possibilities:
-\begin{itemize}
-\item When $\events'=\events\backslash\left\{ \proj{\ps'}\right\} $, because
-$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{2}}^{B}\right\} $.
-\item When $\events'=\events\backslash\left\{ \proj{\ps}\right\} $, because
-$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we have $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{1}}^{B}\right\} $.
-\item When $\events'=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
+This section extend the idea of restricting the event space, but instead
+of commuting sub-event space, we will try to find some subset~$\events'\subseteq\events$
+such that $\bar{\mu}|_{\events'}$ has an non-empty core. This could
+help us understand the core because of the following identity
+\begin{equation}
+\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\label{eq:core-intersection}
+\end{equation}
+if we know more about the right-hand side of the equation, we can
+have more idea about the left-hand side. This idea can be applied
+to example~\ref{ex:three-dimensional-three-value}, and the following
+are three of all possibilities:
+\begin{itemize}
+\item When $\events_{1}=\events\backslash\left\{ \proj{\ps'}\right\} $,
+because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
+$\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)=\left\{ \mu_{\ket{2}}^{B}\right\} $.
+\item When $\events_{2}=\events\backslash\left\{ \proj{\ps}\right\} $,
+because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we
+have $\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{1}}^{B}\right\} $.
+\item When $\events_{3}=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
 because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$,
-we have $\mu_{\frac{\mathbb{1}}{3}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events'}\right)$
-as well as $\mu_{\ket{2}}^{B}$ and $\mu_{\ket{1}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events'}\right)$.
+we have $\mu_{\frac{\mathbb{1}}{3}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$
+as well as $\mu_{\ket{2}}^{B}$ and $\mu_{\ket{1}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$.
 \end{itemize}
 Each of these possibilities is compatible with some but not all of
-the observations. The first two possibilities are particular interesting
-since each two 1-dimensional projectors~$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
+the observations. In another word, 
+\begin{equation}
+\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{B}\right\} \cap\left\{ \mu_{\ket{1}}^{B}\right\} =\emptyset\textrm{ .}
+\end{equation}
+The first two possibilities are particular interesting since each
+two 1-dimensional projectors~$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
 mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
@@
 the other hand, if the states mapping to $\imposs$ contain some area
-in the sphere as in figure~\ref{fig:three-dimensional-3-value-1},
-each plane intersecting the area suggests different pure state inducing
-$\bar{\mu}$. However, these suggestions contradict with each others,
-which implies $\bar{\mu}$ has an empty core. Furthermore, the larger
-the area, the more state vectors which are inconsistent with any particular
-Born rule probability measure. Therefore, the area of the 1-dimensional
-projectors mapping to $\imposs$ could indicate how much $\bar{\mu}$
-deviate from the Born rule probability measures. 
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.38]{figure3} 
-\par\end{centering}
-\caption{\label{fig:three-dimensional-3-value-1}Plotted in $\mathbb{R}^{3}$,
-assume the 1-dimensional projectors whose latitude is higher than
-the green circle maps to $\imposs$ by $\bar{\mu}$, for example $\bar{\mu}\left(\proj{0'}\right)=\bar{\mu}\left(\proj{2'}\right)=\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$.
-Since $\ket{0'}$ and $\ket{2'}$ are in a plane, $\bar{\mu}$ might
-be induced by its normal vector~$\ket{1'}$. Also, since $\ket{0'}$
-and $\ket{\bar{2}}$ are in a plane, $\bar{\mu}$ might be induced
-by its normal vector~$\ket{\bar{1}}$. However, $\mu_{\ket{1'}}^{B}$
-is inconsistent with $\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$,
-and $\mu_{\ket{\bar{1}}}^{B}$ is inconsistent with $\bar{\mu}\left(\proj{2'}\right)=\imposs$.
-Therefore, $\bar{\mu}$ has an empty-core.}
-\end{figure}
+in the sphere as in figure~\ref{fig:three-dimensional-real-frame-1},
+and this area intersects a plane~$\events'$, then $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi}}^{B}\right\} $,
+where $\ket{\psi}$ is the normal vector of $\events'$. Since different
+planes have different normal vectors, $\bar{\mu}$ has an empty core.
+Furthermore, the larger the area, the more state vectors which are
+inconsistent with any particular Born rule probability measure. In
+another word, there are more different singleton sets in the right-hand
+side of equation~(\ref{eq:core-intersection}). Therefore, the area
+of the 1-dimensional projectors mapping to $\imposs$ could indicate
+how much $\bar{\mu}$ deviate from the Born rule probability measures.
 
@@
 which represents the ability of measurement equipment. In particular,
-we have the following results whose details are described in appendix~\ref{sec:Real-Interval-valued-Frame}.
+we have the following results whose details are described in \ref{sec:Real-Interval-valued-Frame}. 
 \begin{itemize}
@@
 
-\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\pi / 2\right]$
-and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
+\begin{lemma}\label{lemma:imposs-imply-same-value}Given
+$\theta_{0}\in\left[0,\pi/2\right]$ and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
 if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
 then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
-for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\pi / 2\right]\right)$.\end{lemma}
+for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi/2-\theta_{0},\pi/2\right]\right)$.\end{lemma}
 \begin{figure}
 \begin{centering}
-\includegraphics[scale=0.38]{figureb1.eps} 
+\includegraphics[scale=0.38]{figureb1} 
 \par\end{centering}
 \caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
-the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
+the proof of lemma~\ref{lemma:imposs-imply-same-value}, where every
+vector above the light green circle maps to $\imposs$, and we want
+to prove that every vector between dark green and light blue maps
+to the same interval.}
 \end{figure}

### 2017-02-20 prop_iop.tex
beginning of intro

@@
 \section{Introduction}
+
+Textbook quantum mechanics asserts that, given a quantum system
+described by the wavefunction
+$\ket{\psi}=\frac{\sqrt{\pi}}{2}\ket{0}+\frac{\sqrt{4-\pi}}{2}\ket{1}$
+and the observable $I$, the probability of observing $\ket{0}$ is
+$\frac{\pi}{4}$ and the probability of observing $\ket{1}$ is
+$1-\frac{\pi}{4}$. According to the frequency interpretation of
+probability, the above assertion implies that when performing a very
+large number of experiments on quantum systems described by
+wavefunction $\ket{\psi}$, a fraction $\frac{\pi}{4}$ of the
+experiments will result in the observation $\ket{0}$ and the remaining
+fraction $1-\frac{\pi}{4}$ will result in the observation
+$\ket{1}$.
+
+In reality, i.e., in an actual experiment, simulation, or computation,
+bounded by space, time, and energy resources, the situation is much
+fuzzier: (i) we cannot \emph{exactly} prepare the state $\psi$; (ii)
+we cannot \emph{exactly} build a measurement apparatus corresponding
+to observable $I$; and (iii) we cannot prepare \emph{exact} replicas
+of any state. In other words, we can only perform a limited number of
+experiments on quantum systems closely related to wavefunction
+$\ket{\psi}$ and using an apparatus that closely approximates
+observable $I$. Given any fixed resources, these experiments will
+\emph{not} result in the \emph{exact} fraction $\frac{\pi}{4}$ of
+observations $\ket{0}$ and $1-\frac{\pi}{4}$ of observations
+$\ket{1}$. Indeed, the state of the art algorithms for computing the
+$n$th binary digit of~$\pi$ require on the order of
+$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
+operations~\cite{journals/moc/BaileyBP97} which means that simply
+referring to the $n$th digit of $\pi$ requires more and more resources
+as $n$ gets larger.
+
+All of this is well-known. The question is how seriously does it
+affect the foundations of quantum mechanics? We believe that the
+answer is not evident at all and should be investigated in
+detail. Indeed taking such resource bounds into consideration is what
+founded computer science as a discipline and has become crucial for
+understanding the very nature of computation. Following
+Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
+and others, one might argue that this resource-bounded perspective is
+also crucial for understanding the very nature of physical processes.
+
+\newpage
 

### 2017-02-20 prop_iop.tex
fixed intro

--- 2017-02-20 prop_iop.tex
@@
 \newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
+\newcommand{\fket}[1]{{|#1\rangle}}
+\newcommand{\fproj}[1]{|#1\rangle\langle #1|}
 \newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
@@
 \section{Introduction}
+
+Textbook quantum mechanics asserts that, given a quantum spin system
+described by the wavefunction
+$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
+and the observable $S_z = \frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
+the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$ (with
+post-measurement state $\fket{\ps\frac{1}{2}}$) is $\frac{\pi}{4}$ and
+the probability of observing $\minus\frac{\hbar}{2}$ (with post-measurement
+state $\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
+frequency interpretation of probability, the above assertion implies
+that when performing a very large number of experiments on quantum
+systems described by wavefunction $\ket{\psi}$, a fraction
+$\frac{\pi}{4}$ of the experiments will result in the observation
+$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
+result in the observation $\fket{\minus\frac{1}{2}}$.
+
+In reality, i.e., in an actual experiment, simulation, or computation,
+bounded by space, time, and energy resources, the situation is much
+fuzzier: (i) we cannot \emph{exactly} prepare the state $\psi$; (ii)
+we cannot \emph{exactly} build a measurement apparatus corresponding
+to observable $S_z$; and (iii) we cannot prepare \emph{exact} replicas
+of any state. In other words, we can only perform a limited number of
+experiments on quantum systems closely related to wavefunction
+$\ket{\psi}$ and using an apparatus that closely approximates
+observable $S_z$. Given any fixed resources, these experiments will
+\emph{not} result in the \emph{exact} fraction $\frac{\pi}{4}$ of
+observations $\ps\frac{\hbar}{2}$ and $1-\frac{\pi}{4}$ of observations
+$\minus\frac{\hbar}{2}$. Indeed, the state of the art algorithms for
+computing the $n$th binary digit of~$\pi$ require on the order of
+$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
+operations~\cite{journals/moc/BaileyBP97} which means that simply
+referring to the $n$th digit of $\pi$ requires more and more resources
+as~$n$ gets larger.
+
+All of this is well-known and holds in both the classical and quantum
+world. In the classical world, these observations are believed to be
+well-understood approximations to an idealized reality. The question
+in the quantum world is more subtle and it is not evident at all that
+it does not alter the very foundations of quantum mechanics. Indeed
+taking such resource bounds into consideration is what founded
+computer science as a discipline and has become crucial for
+understanding the very nature of computation. Following
+Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
+and others, one might argue that this resource-bounded perspective is
+also crucial for understanding the very nature of physical processes.
+
+In previous work, \ldots
+
+\newpage
 

### 2017-02-20 prop_iop.tex
intro

@@
 $\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
-result in the observation $\fket{\minus\frac{1}{2}}$.
+result in the observation $\minus\frac{\hbar}{2}$.
 
@@
 fuzzier: (i) we cannot \emph{exactly} prepare the state $\psi$; (ii)
-we cannot \emph{exactly} build a measurement apparatus corresponding
+we cannot build a measurement apparatus corresponding \emph{exactly}
 to observable $S_z$; and (iii) we cannot prepare \emph{exact} replicas
@@
 \emph{not} result in the \emph{exact} fraction $\frac{\pi}{4}$ of
-observations $\ps\frac{\hbar}{2}$ and $1-\frac{\pi}{4}$ of observations
-$\minus\frac{\hbar}{2}$. Indeed, the state of the art algorithms for
-computing the $n$th binary digit of~$\pi$ require on the order of
-$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
+observations $\ps\frac{\hbar}{2}$ and $1-\frac{\pi}{4}$ of
+observations $\minus\frac{\hbar}{2}$. Indeed, the state of the art
+algorithms for computing the $n$th binary digit of~$\pi$ require on
+the order of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
 operations~\cite{journals/moc/BaileyBP97} which means that simply

### 2017-02-20 prop_iop.tex
more on intro

@@
 $\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
-and the observable $S_z = \frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
-the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$ (with
-post-measurement state $\fket{\ps\frac{1}{2}}$) is $\frac{\pi}{4}$ and
-the probability of observing $\minus\frac{\hbar}{2}$ (with post-measurement
-state $\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
+and given the observable
+$S_z =
+\frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
+then the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$
+(with post-measurement state $\fket{\ps\frac{1}{2}}$) is
+$\frac{\pi}{4}$ and the probability of observing the eigenvalue
+$\minus\frac{\hbar}{2}$ (with post-measurement state
+$\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
 frequency interpretation of probability, the above assertion implies
@@
 bounded by space, time, and energy resources, the situation is much
-fuzzier: (i) we cannot \emph{exactly} prepare the state $\psi$; (ii)
-we cannot build a measurement apparatus corresponding \emph{exactly}
-to observable $S_z$; and (iii) we cannot prepare \emph{exact} replicas
-of any state. In other words, we can only perform a limited number of
-experiments on quantum systems closely related to wavefunction
-$\ket{\psi}$ and using an apparatus that closely approximates
-observable $S_z$. Given any fixed resources, these experiments will
-\emph{not} result in the \emph{exact} fraction $\frac{\pi}{4}$ of
-observations $\ps\frac{\hbar}{2}$ and $1-\frac{\pi}{4}$ of
-observations $\minus\frac{\hbar}{2}$. Indeed, the state of the art
-algorithms for computing the $n$th binary digit of~$\pi$ require on
-the order of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
-operations~\cite{journals/moc/BaileyBP97} which means that simply
-referring to the $n$th digit of $\pi$ requires more and more resources
-as~$n$ gets larger.
+fuzzier: (i) we cannot \emph{exactly} prepare the state $\ket{\psi}$;
+(ii) we cannot build a measurement apparatus corresponding
+\emph{exactly} to observable $S_z$; and (iii) we cannot prepare
+\emph{exact} replicas of any state. In other words, we can only
+perform a limited number of experiments on quantum systems closely
+related to wavefunction $\ket{\psi}$ and using an apparatus that
+closely approximates observable $S_z$. Given any fixed resources,
+these experiments will \emph{not} result in the \emph{exact} fraction
+$\frac{\pi}{4}$ of observations $\ps\frac{\hbar}{2}$ and
+$1-\frac{\pi}{4}$ of observations $\minus\frac{\hbar}{2}$. In fact,
+these experiments can be viewed as a method (algorithm) to calculate
+the value $\pi$ and it is known that the state of the art algorithms
+for computing the $n$th binary digit of~$\pi$ require on the order of
+$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
+operations~\cite{journals/moc/BaileyBP97}. In other words, calculating
+the $n$th digit of $\pi$ appears to require more and more physical
+resources as~$n$ gets larger.
 
 All of this is well-known and holds in both the classical and quantum
-world. In the classical world, these observations are believed to be
-well-understood approximations to an idealized reality. The question
-in the quantum world is more subtle and it is not evident at all that
-it does not alter the very foundations of quantum mechanics. Indeed
-taking such resource bounds into consideration is what founded
-computer science as a discipline and has become crucial for
-understanding the very nature of computation. Following
-Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
-and others, one might argue that this resource-bounded perspective is
-also crucial for understanding the very nature of physical processes.
-
-In previous work, \ldots
+worlds. In the classical world, these observations are believed to be
+well-understood approximations to an idealized independent reality
+that can continuously approached with more and more resources. The
+question in the quantum world is more subtle; it is not evident at all
+that this resource-aware perspective does not alter the very
+foundations of quantum mechanics. Indeed taking such resource bounds
+into consideration is what founded computer science as a discipline
+and has become crucial for understanding the very nature of
+computation. Following Feynman~\cite{Feynman1982Simulating},
+Landauer~\cite{Landauer1996188}, and others, one might argue that this
+resource-bounded perspective is also crucial for understanding the
+very nature of physical processes.
+
+In previous work, we analyzed the wavefunction description of quantum
+systems from a resource-bounded perspective. Technically, instead of
+postulating that quantum states are rays in a Hilbert space, i.e., we
+instead used special finite fields whose size reflected the available
+resources. \ldots
 

### 2017-02-20 prop_iop.tex
few changes here and there

@@
 that the first coin is twice as likely to land tails up than heads up
-and the second coin is double-headed. In a strict computational
-or experimental setting, one should question the reliance of the
-definition of probability space on the uncountable and
-uncomputable real
+and the second coin is double-headed.
+
+%%%%%
+\subsection{Measuring Probabilities: Buffon's Needle Problem\label{subsec:Measuring-Probabilities:-Buffon}}
+
+In a strict computational or experimental setting, one should question
+the reliance of the definition of probability space on the uncountable
+and uncomputable real
 interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
-This interval includes numbers like
-$0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether
-Turing machine $\mathit{TM}_{i}$ halts or not. Such numbers cannot be
-computed. This interval also includes numbers like $\pi / 4$
-which can only be computed with increasingly large resources as the
-precision increases. Therefore, in a resource-aware computational or
+This interval includes numbers like $0.h_{1}h_{2}h_{3}\ldots$ where
+$h_{i}$ is 1 or 0 depending on whether Turing machine
+$\mathit{TM}_{i}$ halts or not. Such numbers cannot be computed. This
+interval also includes numbers like $\pi / 4$ which can only be
+computed with increasingly large resources as the precision
+increases. Therefore, in a resource-aware computational or
 experimental setting, it is more appropriate to consider probability
@@
 measures~\cite{Weichselberger2000,JamisonLodwick2004}.
-
-%%%%%
-\subsection{Measuring Probabilities: Buffon's Needle Problem\label{subsec:Measuring-Probabilities:-Buffon}}
 
@@
 
-\amr{Another: the calculus of probabilities requires all probabilities to
-be \emph{coherent}. But given limited resources, a user can only
-approximate the probabilities and the approximation may not be
-completely coherent in the ideal sense.}
+Another way to re-express the above observations is that the calculus
+of probabilities requires all probabilities to be \emph{coherent}
+(e.g., the probability of the union of two disjoint events is the sum
+of their probabilities). But given limited resources, the calculation
+of a probability measure can only be approximate and hence the
+probabilities cannot be absolutely guaranteed to be coherent in the
+ideal sense.
 

### 2017-02-23 prop_iop.tex
prop_iop.tex \section{Cryptodeterministic Measures} Starting...

@@
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
+\def\C{{\mathbb{C}}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Cryptodeterministic Measures}
+
+A real or interval-valued probability is a way to model our belief
+whether an event will happen or not. Classically, when we toss a coin
+or throw a needle, if we know all the initial condition, we can determine
+whether an event happens or not for sure~\cite{DiaconisHolmesMontgomery2007}.
+
+\newpage{}
+
+One obvious way to discretize probability is to only consider a finite
+set of probability values. For example, instead of $\left[0,1\right]$,
+we only consider the probability $\check{\mathscr{L}}$ to be two
+values $\left\{ 0,1\right\} $, three values $\left\{ 0,\frac{1}{2},1\right\} $,
+or any finite set $\check{\mathscr{L}}\subset\left[0,1\right]$. Then,
+a finite value classical probability distribution is a function $\check{\mathcal{Q}}:\Omega\rightarrow\check{\mathscr{L}}$
+with 
+\begin{equation}
+\sum_{i=0}^{d-1}\check{\mathcal{Q}}\left(\omega_{i}\right)=1\textrm{ .}
+\end{equation}
+For example, a classical probability distribution for a fair coin
+is $\check{\mathcal{Q}}\left(H\right)=\check{\mathcal{Q}}\left(T\right)=\frac{1}{2}$.
+Because $\check{\mathcal{Q}}$ only takes value $\frac{1}{2}$, we
+can pick $\check{\mathscr{L}}=\left\{ \frac{1}{2}\right\} $.
+
+A finite value quantum probability distribution $\check{\mathcal{P}}:\C^{d*}\rightarrow\check{\mathscr{L}}$
+can be defined similarly with 
+\begin{equation}\eqalign{ 
+{\displaystyle \sum_{i=0}^{d-1}\check{\mathcal{P}}\left(\ket{i}\right)=1}\textrm{ for any orthonormal basis }\left\{ \ket{i}\right\} _{i=0}^{d-1}\textrm{ ;}\label{eq:total-probability-CQT-1}\\
+\check{\mathcal{P}}\left(\ket{\Phi}\right)=\check{\mathcal{P}}\left(\lambda\ket{\Phi}\right)\textrm{ for }\lambda\in\C^{*}=\C\backslash\left\{ 0\right\} \textrm{ .}\label{eq:parallel-CQT-1} 
+}\end{equation} 
+Although it seems that the definition is almost the same as the one
+in $\left[0,1\right]$-valued, actually this lead to the well-known
+Kochen-Specker theorem.
+
+\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}For
+$d\ge3$, there is no $\left\{ 0,1\right\} $-valued quantum probability
+distribution.\end{thm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Quantum Interval-valued Probability Measures}

### 2017-02-23 prop_iop.tex
prop_iop.tex \section{Cryptodeterministic Measures} Updating...

@@
 
-A real or interval-valued probability is a way to model our belief
-whether an event will happen or not. Classically, when we toss a coin
-or throw a needle, if we know all the initial condition, we can determine
+Although a real or interval-valued probability measure could be used
+to model whether we believe an event will happen or not, the classical
+world could be model in an simpler way. If the complete initial condition
+for tossing a coin or throwing a needle is known, we can determine
 whether an event happens or not for sure~\cite{DiaconisHolmesMontgomery2007}.
+In another word, Newtonian physics could be modeled by a cryptodeterministic
+measure defined as follow.
+
+\begin{definition}[Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
+the set of events~$\events$, a \emph{cryptodeterministic measure}
+is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $ such
+that: 
+\begin{itemize}
+\item $\pmeas(\emptyset)=0$, 
+\item $\pmeas(\Omega)=1$, 
+\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
+where $\Omega\backslash E$ is the complement event of $E$, and 
+\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
+disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
+\end{itemize}
+\end{definition}
 

### 2017-02-24 prop_iop.tex
prop_iop.tex Updating here and there...

--- 2017-02-20 prop_iop.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum Interval-valued Probability Measures}
+
+\section{Cryptodeterminism}
+
+Although a real or interval-valued probability measure could be used
+to model whether we believe an event will happen or not, the classical
+world could be model in an simpler way. If the complete initial condition
+for tossing a coin or throwing a needle is known, we can determine
+whether an event happens or not for sure~\cite{DiaconisHolmesMontgomery2007}.
+In another word, Newtonian physics could be modeled by a cryptodeterministic
+measure defined as follow.
+
+\begin{definition}[Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
+the set of events~$\events$, a \emph{cryptodeterministic measure}
+is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $ such
+that: 
+\begin{itemize}
+\item $\pmeas(\emptyset)=0$, 
+\item $\pmeas(\Omega)=1$, 
+\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
+where $\Omega\backslash E$ is the complement event of $E$, and 
+\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
+disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
+\end{itemize}
+\end{definition}
+
+\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
+of the prefect prediction, a cryptodeterministic measure can model
+the belief of an event which has already happened. For example, if
+we toss the coin in example~\ref{ex1}, and see $HH$, our belief
+of which event has happened can be model by the following example.
+\begin{equation}
+\begin{array}{c@{\qquad\qquad}c}
+\begin{array}{rcl}
+\bar{\mu}(\emptyset) & = & 0\\
+\bar{\mu}(\{HH\}) & = & 1\\
+\bar{\mu}(\{HT\}) & = & 0\\
+\bar{\mu}(\{TH\}) & = & 0\\
+\bar{\mu}(\{TT\}) & = & 0\\
+\bar{\mu}(\{HH,HT\}) & = & 1\\
+\bar{\mu}(\{HH,TH\}) & = & 1\\
+\bar{\mu}(\{HH,TT\}) & = & 1
+\end{array} & \begin{array}{rcl}
+\bar{\mu}(\{HT,TH\}) & = & 0\\
+\bar{\mu}(\{HT,TT\}) & = & 0\\
+\bar{\mu}(\{TH,TT\}) & = & 0\\
+\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
+\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
+\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
+\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
+\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
+\end{array}\end{array}
+\end{equation}
+\end{example}
+
+Raised by Einstein, Podolsky, and Rosen~\cite{EPR1935,peres1995quantum},
+it was a famous question whether quantum mechanics have any change
+to be improved and predict perfectly. One of the ``no'' answer was
+due to the Kochen-Specker theorem.
+
+\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}Given
+a Hilbert space of dimension~$d\ge3$, there is no cryptodeterministic
+measure~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $.\end{thm}
+
+Although sharing a lot of similarity, the Kochen-Specker theorem highlight
+the difference between quantum and classical measures. When we think
+a cryptodeterministic measure as a model of pasted events, the Kochen-Specker
+theorem also consistent with the usual interpretation of the quantum
+theory: we should not ask whether an event happened or not if an event
+is incompatible with the event really happened; events compatible
+with the event really happened are the only events which are askable.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Quantum Interval-valued Probability}
+
+%%%%%
+
+\subsection{Quantum Interval-valued Probability Measures}
 
@@
 probability measure for an experimenter with no prior knowledge should
-be $\bar{\mu}(P)=\unknown$ for every projection~$P$.}} Formally, we can ask: what can we deduce about the state of a quantum
-system given a quantum interval-valued probability measure, i.e.,
-given observations done with finite resources. In the case that the
-intervals are infinitely precise, the question reduces to Gleason's
+be $\bar{\mu}(P)=\unknown$ for every projection~$P$.}}
+
+Similarly, we can recast the result of cryptodeterminism to quantum
+interval-valued probability measures as well. In another word, for
+any classically event space~$\events$,there is always a classical
+interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
+However, given a Hilbert space of dimension~$d\ge3$, there is no
+quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
+by the Kochen-Specker theorem. The Kochen-Specker theorem provides
+an example that quantum interval-valued probability measures behave
+differently from the classical one, and the convexity and core in
+the next section provides another example that quantum interval-valued
+probability measures behave unexpectedly.
+
+%%%%%
+
+\subsection{Convexity and Core}
+
+\noindent Formally, we can ask: what can we deduce about the state
+of a quantum system given a quantum interval-valued probability measure,
+i.e., given observations done with finite resources. In the case that
+the intervals are infinitely precise, the question reduces to Gleason's
 theorem which states that the state of the quantum system is uniquely

### 2017-02-24 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

@@
 for tossing a coin or throwing a needle is known, we can determine
-whether an event happens or not for sure~\cite{DiaconisHolmesMontgomery2007}.
+whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
 In another word, Newtonian physics could be modeled by a cryptodeterministic
@@
 of the prefect prediction, a cryptodeterministic measure can model
-the belief of an event which has already happened. For example, if
-we toss the coin in example~\ref{ex1}, and see $HH$, our belief
-of which event has happened can be model by the following example.
+the belief of events which has already happened. For example, if we
+toss the coin in example~\ref{ex1}, and see $HH$, our belief of
+which event has happened can be model by the following example.
 \begin{equation}
@@
 it was a famous question whether quantum mechanics have any change
-to be improved and predict perfectly. One of the ``no'' answer was
-due to the Kochen-Specker theorem.
+to be improved and predict unambiguously, rather than probabilistic.
+One of the ``no'' answer was due to the Kochen-Specker theorem.
 

### 2017-02-25 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

@@
 
-Although a real or interval-valued probability measure could be used
+\footnote{\yutsung{The word ''cryptodeterminism'' is used by A. Peres~\cite{peres1995quantum}.
+However, he hasn't defined it explicitly so it is hard to tell how
+to use it correctly...}}Although a real or interval-valued probability measure could be used
 to model whether we believe an event will happen or not, the classical

### 2017-02-25 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

--- 2017-02-24 prop_iop.tex
@@
 
-Although a real or interval-valued probability measure could be used
+\footnote{\yutsung{The word ''cryptodeterminism'' is used by Peres~\cite{peres1995quantum}
+without a clear definition. I tried to check its meaning from other
+sources. In~\cite{Atmanspacher2014}, Atmanspacher defined `one
+might paraphrase the deterministic yet non-determinable behavior of
+such systems as ``cryptodeterminism,''' where ``deterministic''
+and ``determinable'' is defined in the same section as `The recent
+creation of the term ``deterministic chaos'' expresses the tension
+between ontic (hidden) lawfulness and epistemic (apparent) irregularity
+in chaotic system. Our description of the underlying laws of nature,
+e.g. by differential equations governing the dynamics of such systems,
+is no doubt deterministic, but their observable behavior is everything
+but determinable (in the sense of measurable, computable, or predictable)
+with arbitrary precision.' Is Atmanspacher's usage consistent with
+Peres' and ours here?}}Although a real or interval-valued probability measure could be used
 to model whether we believe an event will happen or not, the classical

### 2017-02-26 prop_iop.tex
prop_iop.tex Updating here and there...

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{cor}{Corollary}
 
@@
 
-\begin{definition}[Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
-the set of events~$\events$, a \emph{cryptodeterministic measure}
-is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $ such
-that: 
+\begin{definition}[Classical Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
+the set of events~$\events$, a \emph{classical cryptodeterministic
+measure} is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $
+such that: 
 \begin{itemize}
@@
 to be improved and predict unambiguously, rather than probabilistic.
-One of the ``no'' answer was due to the Kochen-Specker theorem.
+One way to formulate this question is to ask whether we can model
+the whole quantum theory by quantum cryptodeterministic measures.
+
+\begin{definition}[Quantum Cryptodeterministic Measure]\label{def:QuantumCryptodeterministicMeasures}Given
+a Hilbert space $\Hilb$ with its set of events~$\events$, a \emph{quantum
+cryptodeterministic measure} is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $
+such that: 
+\begin{itemize}
+\item $\pmeas(\mathbb{0})=0$, 
+\item $\pmeas(\mathbb{1})=1$, 
+\item for every event $P$, $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$
+where $\Omega\backslash P$ is the complement event of $P$, and 
+\item for every collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
+disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$. 
+\end{itemize}
+\end{definition}
+
+The answer is ``no'' due to the Kochen-Specker theorem.
 
@@
 quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
-by the Kochen-Specker theorem. The Kochen-Specker theorem provides
-an example that quantum interval-valued probability measures behave
-differently from the classical one, and the convexity and core in
-the next section provides another example that quantum interval-valued
-probability measures behave unexpectedly.
+by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
+theorem. The Kochen-Specker theorem provides an example that quantum
+interval-valued probability measures behave differently from the classical
+one, and the convexity and core in the next section provides another
+example that quantum interval-valued probability measures behave unexpectedly.
 
@@
 
+\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
+of dimension~$d\ge3$, there is no quantum interval-valued probability
+measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.\end{cor}
+
+\begin{proof}We are going to prove by contradiction! Suppose there
+is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
+Consider $\mu:\events\rightarrow\left[0,1\right]$ defined by
+\begin{equation} 
+\mu(P)=\cases{ 
+0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
+1 & if $\bar{\mu}(P)=\necess$ .
+}\label{cor:Kochen-Specker-IVPM} \end{equation}
+ We are going to verify that $\mu$ is a cryptodeterministic measure
+so that contradicts to the Kochen-Specker theorem.
+\begin{itemize}
+\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
+\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
+\item For every event $P$, we have 
+\begin{equation}\eqalign{ 
+& \pmeas\left(P\right)=0\\ 
+\Rightarrow & \bar{\mu}(P)=\imposs\\
+\Rightarrow & \bar{\mu}(\Omega\backslash P)=\left[1,1\right]-\imposs=\necess\\
+\Rightarrow & \pmeas\left(\Omega\backslash P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
+}\end{equation}
+Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$.
+\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
+disjoint events. 
+\begin{itemize}
+\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1$, then we have $\necess=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
+so that $\necess=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=1=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
+\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0$, then we have $\imposs=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
+so that $\imposs=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=0=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
+\end{itemize}
+\end{itemize}
+\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}}

### 2017-02-26 prop_iop.tex
prop_iop.tex \section{Quantum Real-valued and Interval-valued Probability Measures} Updating...
prop_iop.tex \section{Introduction} Replace "wavefunction" by "wave function".

@@
 Textbook quantum mechanics asserts that, given a quantum spin system
-described by the wavefunction
+described by the wave function
 $\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
@@
 that when performing a very large number of experiments on quantum
-systems described by wavefunction $\ket{\psi}$, a fraction
+systems described by wave function $\ket{\psi}$, a fraction
 $\frac{\pi}{4}$ of the experiments will result in the observation
@@
 perform a limited number of experiments on quantum systems closely
-related to wavefunction $\ket{\psi}$ and using an apparatus that
+related to wave function $\ket{\psi}$ and using an apparatus that
 closely approximates observable $S_z$. Given any fixed resources,
@@
 
-In previous work, we analyzed the wavefunction description of quantum
+In previous work, we analyzed the wave function description of quantum
 systems from a resource-bounded perspective. Technically, instead of
@@
 1 & if $\bar{\mu}(P)=\necess$ .
-}\label{cor:Kochen-Specker-IVPM} \end{equation}
+}\end{equation}
 We are going to verify that $\mu$ is a cryptodeterministic measure

### 2017-02-26 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

@@
 without a clear definition. I tried to check its meaning from other
-sources. In~\cite{Atmanspacher2014}, Atmanspacher defined `one
-might paraphrase the deterministic yet non-determinable behavior of
-such systems as ``cryptodeterminism,''' where ``deterministic''
-and ``determinable'' is defined in the same section as `The recent
-creation of the term ``deterministic chaos'' expresses the tension
-between ontic (hidden) lawfulness and epistemic (apparent) irregularity
-in chaotic system. Our description of the underlying laws of nature,
-e.g. by differential equations governing the dynamics of such systems,
-is no doubt deterministic, but their observable behavior is everything
-but determinable (in the sense of measurable, computable, or predictable)
-with arbitrary precision.' Is Atmanspacher's usage consistent with
-Peres' and ours here?}}Although a real or interval-valued probability measure could be used
+sources. In~\cite{Atmanspacher2014}, Atmanspacher defined 
+\begin{quote}
+...one might paraphrase the deterministic yet non-determinable behavior
+of such systems as ``cryptodeterminism''...
+\end{quote}
+where ``deterministic'' and ``determinable'' is defined in the
+same section as 
+\begin{quote}
+The recent creation of the term ``deterministic chaos'' expresses
+the tension between ontic (hidden) lawfulness and epistemic (apparent)
+irregularity in chaotic system. Our description of the underlying
+laws of nature, e.g. by differential equations governing the dynamics
+of such systems, is no doubt deterministic, but their observable behavior
+is everything but determinable (in the sense of measurable, computable,
+or predictable) with arbitrary precision....
+\end{quote}
+Is Atmanspacher's usage consistent with Peres' and ours here?}}Although a real or interval-valued probability measure could be used
 to model whether we believe an event will happen or not, the classical
@@
 \begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
-of the prefect prediction, a cryptodeterministic measure can model
-the belief of events which has already happened. For example, if we
-toss the coin in example~\ref{ex1}, and see $HH$, our belief of
-which event has happened can be model by the following example.
+the prefect prediction, a cryptodeterministic measure can model the
+belief of events which has already happened. For example, if we tossed
+the coin in example~\ref{ex1}, and saw $HH$, our belief of which
+event has happened can be model by the following example.
 \begin{equation}
@@
 
-Raised by Einstein, Podolsky, and Rosen~\cite{EPR1935,peres1995quantum},
-it was a famous question whether quantum mechanics have any change
-to be improved and predict unambiguously, rather than probabilistic.
-One way to formulate this question is to ask whether we can model
-the whole quantum theory by quantum cryptodeterministic measures.
+\noindent The ability to predict classical events unambiguously rather
+than probabilistic inspired Einstein, Podolsky, and Rosen to ask whether
+quantum mechanics have any chance to be improved and predict in the
+same way~\cite{EPR1935,peres1995quantum}. This question can be formulated
+by whether the quantum mechanics could be modeled by quantum cryptodeterministic
+measures.
 
@@
 
-The answer is ``no'' due to the Kochen-Specker theorem.
+\noindent The answer is ``no'' due to the Kochen-Specker theorem.
 
@@
 
-Although sharing a lot of similarity, the Kochen-Specker theorem highlight
-the difference between quantum and classical measures. When we think
-a cryptodeterministic measure as a model of pasted events, the Kochen-Specker
-theorem also consistent with the usual interpretation of the quantum
-theory: we should not ask whether an event happened or not if an event
-is incompatible with the event really happened; events compatible
-with the event really happened are the only events which are askable.
+\noindent Although sharing a lot of similarity, the Kochen-Specker
+theorem highlight the difference between quantum and classical measures.
+When we think a cryptodeterministic measure as a model of pasted events,
+the Kochen-Specker theorem also consistent with the usual interpretation
+of the quantum theory: we should not ask whether an event happened
+or not if an event is incompatible with the event really happened;
+events compatible with the event really happened are the only askable
+events.
 

### 2017-02-27 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

@@
 without a clear definition. I tried to check its meaning from other
-sources. In~\cite{Atmanspacher2014}, Atmanspacher defined 
+sources.
+
+In~\cite{PeresRon1988}, Peres and Ron defined
+\begin{quote}
+We now introduce the cryptodeterministic hypothesis: It is possible
+to specify all the details of a preparation, so that the result of
+any measurement becomes completely deterministic.
+\end{quote}
+Unfortunately, Google Book cannot preview all pages, and the InterLibrary
+Loan hasn't finished my request, yet...
+
+In~\cite{Atmanspacher2014}, Atmanspacher defined 
 \begin{quote}

### 2017-02-27 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

@@
 
-\footnote{\yutsung{The word ''cryptodeterminism'' is used by Peres~\cite{peres1995quantum}
-without a clear definition. I tried to check its meaning from other
-sources.
-
-In~\cite{PeresRon1988}, Peres and Ron defined
+Although a real or interval-valued probability measure could model
+whether we believe an event will happen or not, the classical world
+could be modeled in a simpler way. If the complete initial condition
+for tossing a coin or throwing a needle is known, we can determine
+whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
+In another word, Newtonian physics could be modeled by a cryptodeterministic\footnote{The word ''cryptodeterminism'' is used by Peres which means
 \begin{quote}
@@
 \end{quote}
-Unfortunately, Google Book cannot preview all pages, and the InterLibrary
-Loan hasn't finished my request, yet...
-
-In~\cite{Atmanspacher2014}, Atmanspacher defined 
+in~\cite{PeresRon1988}, and
 \begin{quote}
-...one might paraphrase the deterministic yet non-determinable behavior
-of such systems as ``cryptodeterminism''...
+... any purported cryptodeterministic theory which would attribute
+a definite result to each quantum measurement, and still reproduce
+the statistical properties of quantum theory ...
 \end{quote}
-where ``deterministic'' and ``determinable'' is defined in the
-same section as 
-\begin{quote}
-The recent creation of the term ``deterministic chaos'' expresses
-the tension between ontic (hidden) lawfulness and epistemic (apparent)
-irregularity in chaotic system. Our description of the underlying
-laws of nature, e.g. by differential equations governing the dynamics
-of such systems, is no doubt deterministic, but their observable behavior
-is everything but determinable (in the sense of measurable, computable,
-or predictable) with arbitrary precision....
-\end{quote}
-Is Atmanspacher's usage consistent with Peres' and ours here?}}Although a real or interval-valued probability measure could be used
-to model whether we believe an event will happen or not, the classical
-world could be model in an simpler way. If the complete initial condition
-for tossing a coin or throwing a needle is known, we can determine
-whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
-In another word, Newtonian physics could be modeled by a cryptodeterministic
-measure defined as follow.
+in~\cite{Peres1991,peres1995quantum}.} measure defined as follow.
 
@@
 the coin in example~\ref{ex1}, and saw $HH$, our belief of which
-event has happened can be model by the following example.
+event has happened is represented by the following example.
 \begin{equation}
@@
 quantum mechanics have any chance to be improved and predict in the
-same way~\cite{EPR1935,peres1995quantum}. This question can be formulated
-by whether the quantum mechanics could be modeled by quantum cryptodeterministic
-measures.
+same way~\cite{EPR1935,peres1995quantum,544199,Mermin2007}. This
+question can be formulated by whether the quantum mechanics could
+be modeled by quantum cryptodeterministic measures.
 

### 2017-02-27 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Fixing typos after meeting...

@@
 whether we believe an event will happen or not, the classical world
-could be modeled in a simpler way. If the complete initial condition
+could be modeled in a simpler way. If the complete initial conditions
 for tossing a coin or throwing a needle is known, we can determine
 whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
-In another word, Newtonian physics could be modeled by a cryptodeterministic\footnote{The word ''cryptodeterminism'' is used by Peres which means
+In another words, Newtonian physics could be modeled by a cryptodeterministic\footnote{The word ''cryptodeterminism'' is used by Peres which means
 \begin{quote}
@@
 \end{quote}
-in~\cite{Peres1991,peres1995quantum}.} measure defined as follow.
+in~\cite{Peres1991,peres1995quantum}.} measure defined as follows.
 
@@
 \noindent The ability to predict classical events unambiguously rather
-than probabilistic inspired Einstein, Podolsky, and Rosen to ask whether
-quantum mechanics have any chance to be improved and predict in the
-same way~\cite{EPR1935,peres1995quantum,544199,Mermin2007}. This
-question can be formulated by whether the quantum mechanics could
+than probabilistically inspired Einstein, Podolsky, and Rosen to ask
+whether quantum mechanics has any chance to be improved and predict
+in the same way~\cite{EPR1935,peres1995quantum,544199,Mermin2007}.
+This question can be formulated by whether quantum mechanics could
 be modeled by quantum cryptodeterministic measures.

### 2017-03-02 prop_iop.tex
prop_iop.tex Fix the theorem-style so that it is easier to find...
prop_iop.tex \subsection{Wigner's Friends} Added...
prop_iop.tex \subsection{Wigner's Friends} Updating...

@@
 
-\theoremstyle{remark}
-\newtheorem{example}{Example}
-\newtheorem{definition}{Definition}
+\theoremstyle{plain}
 \newtheorem{thm}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{cor}{Corollary}
+\newtheorem{lemma}[thm]{Lemma}
+\newtheorem{cor}[thm]{Corollary}
+\theoremstyle{definition}
+\newtheorem{definition}[thm]{Definition}
+\newtheorem{example}[thm]{Example}
 
@@
 indeed recover the conventional Gleason's theorem and the Born rule.
+
+%%%%%
+
+\subsection{Wigner's Friends}
+
+The situation of empty core might not be that strange if we think
+in terms of Wigner's ``friends.'' In the original story of Wigner
+and his friend~\cite{Wigner1961,FuchsMerminSchack2014}, the friend
+makes a measurement in a closed laboratory and experiences an outcome.
+Wigner, outside the laboratory, doesn't experience an outcome. If
+he believes what his friend has told him about her plans in her laboratory
+he will assign an entangled state to her, her apparatus, and the system
+on which she is making her intervention. If Wigner goes on to ask
+his friend about her experience, then the entangled state to her,
+her apparatus, and the system will change into one in which they even
+have separate wave functions, and Wigner and his friend will use the
+same wave function to describe the system.
+
+The question is what happens if Wigner has more than one friend in
+the laboratory. Suppose Wigner has three friends: E, P, and R in the
+laboratory. E, P, and R measure the spin-1 system described in example~\ref{ex:three-dimensional-three-value}.
+After the experiment, E tells Wigner $\proj{0}$ never happened, P
+tells Wigner $\proj{\ps}$ never happened, and R tells Wigner $\proj{\ps'}$
+never happened. Wigner may then need to use the quantum Dempster-Shafer
+rule(?) or other rules(?) to combine the belief told by his friends,
+and the combined belief might be the quantum interval-valued probability
+measure in example~\ref{ex:three-dimensional-three-value} which
+has an empty core.
 

### 2017-03-03 prop_iop.tex
prop_iop.tex \section{Mermin Square} Adding...
prop_iop.tex \section{Cryptodeterminism} Updating...

@@
 
-\noindent The answer is ``no'' due to the Kochen-Specker theorem.
+The answer is ``no'' due to the Kochen-Specker theorem whose proof
+can also be formulated in the language of cryptodeterministic measure
+as in \ref{sec:MerminSquare}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\newpage{}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Mermin Square\label{sec:MerminSquare}}
+
+The Kochen-Specker theorem can be proved easily by considering a pair
+of spin $\frac{1}{2}$ system with the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+\[
+\begin{array}{ccc}
+\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
+\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
+\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
+\end{array}
+\]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{comment}

### 2017-03-03 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

@@
 of spin $\frac{1}{2}$ system with the following observables~\cite{Mermin1990Simple,peres1995quantum}:
-\[
+\begin{equation}
 \begin{array}{ccc}
@@
 \sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
-\end{array}
-\]
+\end{array}\label{eq:MerminSquare}
+\end{equation}
+In the original proof, we assign value to each observable, where operators
+in each row and column commutes, and each operator is the product
+of the two others, except in the third column. Because of 
+\begin{equation}
+\left(\sigma_{x}\otimes\sigma_{z}\right)\left(\sigma_{z}\otimes\sigma_{x}\right)=\sigma_{y}\otimes\sigma_{y}=-\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)\textrm{ ,}
+\end{equation}
+it is clear impossible to attribute to each operator in equation~\ref{eq:MerminSquare}
+numerical values, $1$ or $-1$, which obey the same multiplication
+rule as the operators themselves.
+
+\begin{table}
+\caption{\label{table:commonBasis}Observables and their common eigenbasis}
+
+\begin{indented}
+\item[]\begin{tabular}{ccc} 
+\br 
+\multicolumn{3}{c}{Operators} \\
+\mr 
+$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ \\
+$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ \\
+$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ \\
+$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ \\
+$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ \\
+$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ \\
+\br 
+\end{tabular} 
+\end{indented}
+
+\end{table}
+When we reformulate the above argument in the language of quantum
+probability measures, we first need to find the common eigenbasis
+of each row and column as in table
 

### 2017-03-04 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

--- 2017-03-03 prop_iop.tex
@@
 \sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
-\end{array}
-\]
+\end{array}\label{eq:MerminSquare}
+\end{equation}
+In the original proof, we assign value to each observable, where operators
+in each row and column commutes, and each operator is the product
+of the two others, except in the third column. Because of 
+\begin{equation}
+\left(\sigma_{x}\otimes\sigma_{z}\right)\left(\sigma_{z}\otimes\sigma_{x}\right)=\sigma_{y}\otimes\sigma_{y}=-\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)\textrm{ ,}
+\end{equation}
+it is clear impossible to attribute to each operator in equation~(\ref{eq:MerminSquare})
+numerical values, $1$ or $-1$, which obey the same multiplication
+rule as the operators themselves.
+
+\begin{table}
+\caption{\label{table:commonBasis}Observables and their common eigenbasis.
+In order to unified and simplify notation, we do , and not normalize
+eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
+as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}
+
+\begin{tabular}{ccc|cccc} 
+\br 
+\multicolumn{3}{c}{Operators} & \multicolumn{4}{c}{Common eigenbasis} \\
+\mr 
+$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
+$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
+$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
+$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
+$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
+$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
+\br 
+\end{tabular} 
+\end{table}
+When we reformulate the above argument in the language of quantum
+probability measures, we first need to find the common eigenbasis
+of each row and column as in table~\ref{table:commonBasis}.
 

### 2017-03-05 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

@@
 
-The Kochen-Specker theorem can be proved easily by considering a pair
-of spin $\frac{1}{2}$ system with the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+The Kochen-Specker theorem asserts that there is no function~$v$
+assigning a definitely value to all observables such that
+\begin{equation}\eqalign{ 
+v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
+v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
+}\label{eq:Kochen-Specker-Rules}\end{equation}
+if $O_{1}$ and $O_{2}$ are commuting observables. Based on these
+two properties, they first proved that $v$ must send an observable
+to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
 \begin{equation}
@@
 \end{equation}
-In the original proof, we assign value to each observable, where operators
-in each row and column commutes, and each operator is the product
-of the two others, except in the third column. Because of 
-\begin{equation}
-\left(\sigma_{x}\otimes\sigma_{z}\right)\left(\sigma_{z}\otimes\sigma_{x}\right)=\sigma_{y}\otimes\sigma_{y}=-\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)\textrm{ ,}
-\end{equation}
-it is clear impossible to attribute to each operator in equation~(\ref{eq:MerminSquare})
-numerical values, $1$ or $-1$, which obey the same multiplication
-rule as the operators themselves.
+must be sent to $1$ or $-1$. In each row and column, operators commutes,
+and each operator is the product of the two others, except in the
+third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+Therefore, it is clear impossible to find a function~$v$ such that
+\begin{equation}
+\begin{array}{ccc}
+v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
+v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
+v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
+\end{array}\label{eq:MerminSquare-values}
+\end{equation}
+satisfying equation~(\ref{eq:Kochen-Specker-Rules}).
 
@@
 \caption{\label{table:commonBasis}Observables and their common eigenbasis.
-In order to unified and simplify notation, we do , and not normalize
-eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
+In order to unified and simplify notation, we do not normalize eigenstates,
+and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
 as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}
@@
 \end{table}
-When we reformulate the above argument in the language of quantum
+Since observables in equation~(\ref{eq:MerminSquare}) are not projectors,
+if we want to reformulate the above argument in the language of quantum
 probability measures, we first need to find the common eigenbasis
-of each row and column as in table~\ref{table:commonBasis}.
+of each row and column, and consider the projectors to each eigenvectors.
+Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
+Then, proving the Kochen-Specker theorem is proving there is no function~$\set{\proj{\psi}}{\ket{\psi}\in\mathcal{T}_{24}}$
+to $\left\{ 0,1\right\} $.
 

### 2017-03-05 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

@@
 }\label{eq:Kochen-Specker-Rules}\end{equation}
-if $O_{1}$ and $O_{2}$ are commuting observables. Based on these
-two properties, they first proved that $v$ must send an observable
-to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
+is a function~$v$ satisfying these two properties, it must send
+an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
 \begin{equation}

### 2017-03-05 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

@@
 
-\begin{lemma}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~A
+\begin{thm}\label{thm:frame-function}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~A
 frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
@@
 Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
-satisfies the above properties, $f$ must be a frame function.\end{lemma}
+satisfies the above properties, $f$ must be a frame function.\end{thm}
 
@@
 \end{table}
-Since observables in equation~(\ref{eq:MerminSquare}) are not projectors,
+Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
 if we want to reformulate the above argument in the language of quantum
 probability measures, we first need to find the common eigenbasis
-of each row and column, and consider the projectors to each eigenvectors.
+of each row and column, and consider the projections to each eigenvectors.
 Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
-Then, proving the Kochen-Specker theorem is proving there is no function~$\set{\proj{\psi}}{\ket{\psi}\in\mathcal{T}_{24}}$
-to $\left\{ 0,1\right\} $.
+The Kochen-Specker theorem could then be proved by showing there is
+no function~$v:\events'\rightarrow\left\{ 0,1\right\} $satisfying
+equation~(\ref{eq:Kochen-Specker-Rules}), where 
+\[
+\events'=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}\textrm{ is a family of mutually orthogonal projections}}\textrm{ .}
+\]
+This kind of $v$ is actually a quantum cryptodeterministic measure.
+By theorem~\ref{lemma:classical-probability-measures}, the quantum
+cryptodeterministic measure~$v$ exists if and only if there exists
+a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $.
 

### 2017-03-05 prop_iop.tex
prop_iop.tex \appendix Updating...

@@
 \begin{definition}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~For
-any quantum probability measure~$\mu$ on the Hilbert space of dimension
-3, we can define its \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+any quantum probability measure~$\mu$ on the Hilbert space of dimension~$d$,
+we can define its \emph{frame function}~$f:\mathbb{C}S^{d-1}\rightarrow\left[0,1\right]$
 by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
@@
 \begin{thm}\label{thm:frame-function}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~A
-frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
-the following properties: 
+frame function~$f:\mathbb{C}S^{d-1}\rightarrow\left[0,1\right]$
+satisfies the following properties: 
 \begin{itemize}
 \item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
-$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$. 
+$\ket{\psi}\in\mathbb{C}S^{d-1}$ and $\lambda\in\mathbb{C}S^{0}$. 
 \item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
@@
 \end{itemize}
-Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
+Conversely, if a function~$f:\mathbb{C}S^{d-1}\rightarrow\left[0,1\right]$
 satisfies the above properties, $f$ must be a frame function.\end{thm}
@@
 \begin{table}
-\caption{\label{table:commonBasis}Observables and their common eigenbasis.
-In order to unified and simplify notation, we do not normalize eigenstates,
-and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
+\caption{\label{table:commonBasis}In each row, three observables are listed
+in the left column commutes, and their common eigenbasis is listed
+in the right column. In order to unified and simplify notation, we
+do not normalize eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
 as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}
@@
 \br 
-\multicolumn{3}{c}{Operators} & \multicolumn{4}{c}{Common eigenbasis} \\
+\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
 \mr 
@@
 The Kochen-Specker theorem could then be proved by showing there is
-no function~$v:\events'\rightarrow\left\{ 0,1\right\} $satisfying
+no function~$v:\events'\rightarrow\left\{ 0,1\right\} $ satisfying
 equation~(\ref{eq:Kochen-Specker-Rules}), where 
 \[
-\events'=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}\textrm{ is a family of mutually orthogonal projections}}\textrm{ .}
+\events'=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}\textrm{ .}
 \]
@@
 cryptodeterministic measure~$v$ exists if and only if there exists
-a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $.
+a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
+which should at least satisfy
+\begin{equation}\eqalign{ 
+1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
+1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
+}\label{eq:Kernaghan-1}\end{equation}
+because of table~\ref{table:commonBasis}.
 

### 2017-03-05 prop_iop.tex
prop_iop.tex \appendix Updating...

@@
 
-\begin{definition}Given a Hilbert space $\Hilb$, $\events'\subseteq\events$
-is called a sub-event space if it satisfies the follow conditions.
+\begin{definition}\label{def:sub-event-space}Given a Hilbert space
+$\Hilb$, $\events'\subseteq\events$ is called a sub-event space
+if it satisfies the follow conditions.
 \begin{itemize}
@@
 \end{itemize}
-By replacing every occurrence of $\events$ by $\events'$ in definition~\ref{def:QuantumProbabilitySpace}
-and \ref{def:QuantumInterval-valuedProbability}, it is straightforward
-to define a quantum real-valued and interval-valued probability measure
-on $\events'$.\end{definition}
+By replacing every occurrence of $\events$ by $\events'$ in definition~\ref{def:QuantumCryptodeterministicMeasures},
+\ref{def:QuantumProbabilitySpace}, and \ref{def:QuantumInterval-valuedProbability},
+it is straightforward to define a quantum cryptodeterministic, real-valued
+probability, and interval-valued probability measure on $\events'$.\end{definition}
 
@@
 equation~(\ref{eq:Kochen-Specker-Rules}), where 
-\[
-\events'=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}\textrm{ .}
-\]
+\begin{equation}
+\events'=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
+\end{equation}
+which is a sub-event space defined in definition~\ref{def:sub-event-space}.
 This kind of $v$ is actually a quantum cryptodeterministic measure.
-By theorem~\ref{lemma:classical-probability-measures}, the quantum
-cryptodeterministic measure~$v$ exists if and only if there exists
-a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
+Since a cryptodeterministic measure are a special case of real-valued
+probability measure, by theorem~\ref{lemma:classical-probability-measures},
+the quantum cryptodeterministic measure~$v$ exists if and only if
+there exists a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
 which should at least satisfy
@@
 }\label{eq:Kernaghan-1}\end{equation}
-because of table~\ref{table:commonBasis}.
+because of table~\ref{table:commonBasis}. $f$ should also satisfy
+the following equations since the vectors in each equation form an
+orthogonal basis~\cite{Kernaghan1994,peres1995quantum}.
+\begin{equation}\eqalign{ 
+1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
+1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
+1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
+1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
+1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
+1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
+1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
+1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
+1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)
+}\label{eq:Kernaghan-2}\end{equation}
+In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
+are odd number of equations, but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
+occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
+satisfying equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}.
 

### 2017-03-05 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Fix notation...

@@
 the set of events~$\events$, a \emph{classical cryptodeterministic
-measure} is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $
+measure} is a function~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $
 such that: 
 \begin{itemize}
-\item $\pmeas(\emptyset)=0$, 
-\item $\pmeas(\Omega)=1$, 
-\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
+\item $\mu^{\mathrm{D}}(\emptyset)=0$, 
+\item $\mu^{\mathrm{D}}(\Omega)=1$, 
+\item for every event $E$, $\mu^{\mathrm{D}}\left(\Omega\backslash E\right)=1-\mu^{\mathrm{D}}\left(E\right)$
 where $\Omega\backslash E$ is the complement event of $E$, and 
 \item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
-disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
+disjoint events, $\mu^{\mathrm{D}}\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\mu^{\mathrm{D}}(E_{i})$. 
 \end{itemize}
@@
 \begin{array}{rcl}
-\bar{\mu}(\emptyset) & = & 0\\
-\bar{\mu}(\{HH\}) & = & 1\\
-\bar{\mu}(\{HT\}) & = & 0\\
-\bar{\mu}(\{TH\}) & = & 0\\
-\bar{\mu}(\{TT\}) & = & 0\\
-\bar{\mu}(\{HH,HT\}) & = & 1\\
-\bar{\mu}(\{HH,TH\}) & = & 1\\
-\bar{\mu}(\{HH,TT\}) & = & 1
+\mu^{\mathrm{D}}(\emptyset) & = & 0\\
+\mu^{\mathrm{D}}(\{HH\}) & = & 1\\
+\mu^{\mathrm{D}}(\{HT\}) & = & 0\\
+\mu^{\mathrm{D}}(\{TH\}) & = & 0\\
+\mu^{\mathrm{D}}(\{TT\}) & = & 0\\
+\mu^{\mathrm{D}}(\{HH,HT\}) & = & 1\\
+\mu^{\mathrm{D}}(\{HH,TH\}) & = & 1\\
+\mu^{\mathrm{D}}(\{HH,TT\}) & = & 1
 \end{array} & \begin{array}{rcl}
-\bar{\mu}(\{HT,TH\}) & = & 0\\
-\bar{\mu}(\{HT,TT\}) & = & 0\\
-\bar{\mu}(\{TH,TT\}) & = & 0\\
-\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
-\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
-\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
-\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
-\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
+\mu^{\mathrm{D}}(\{HT,TH\}) & = & 0\\
+\mu^{\mathrm{D}}(\{HT,TT\}) & = & 0\\
+\mu^{\mathrm{D}}(\{TH,TT\}) & = & 0\\
+\mu^{\mathrm{D}}(\{HH,HT,TH\}) & = & 1\\
+\mu^{\mathrm{D}}(\{HH,HT,TT\}) & = & 1\\
+\mu^{\mathrm{D}}(\{HH,TH,TT\}) & = & 1\\
+\mu^{\mathrm{D}}(\{HT,TH,TT\}) & = & 0\\
+\mu^{\mathrm{D}}(\{HH,HT,TH,TT\}) & = & 1
 \end{array}\end{array}
@@
 
-\noindent The ability to predict classical events unambiguously rather
-than probabilistically inspired Einstein, Podolsky, and Rosen to ask
-whether quantum mechanics has any chance to be improved and predict
-in the same way~\cite{EPR1935,peres1995quantum,544199,Mermin2007}.
-This question can be formulated by whether quantum mechanics could
-be modeled by quantum cryptodeterministic measures.
+The ability to predict classical events unambiguously rather than
+probabilistically inspired Einstein, Podolsky, and Rosen to ask whether
+quantum mechanics has any chance to be improved and predict in the
+same way~\cite{EPR1935,peres1995quantum,544199,Mermin2007}. This
+question can be formulated by whether quantum mechanics could be modeled
+by quantum cryptodeterministic measures.
 
@@
 a Hilbert space $\Hilb$ with its set of events~$\events$, a \emph{quantum
-cryptodeterministic measure} is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $
+cryptodeterministic measure} is a function~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $
 such that: 
 \begin{itemize}
-\item $\pmeas(\mathbb{0})=0$, 
-\item $\pmeas(\mathbb{1})=1$, 
-\item for every event $P$, $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$
+\item $\mu^{\mathrm{D}}(\mathbb{0})=0$, 
+\item $\mu^{\mathrm{D}}(\mathbb{1})=1$, 
+\item for every event $P$, $\mu^{\mathrm{D}}\left(\Omega\backslash P\right)=1-\mu^{\mathrm{D}}\left(P\right)$
 where $\Omega\backslash P$ is the complement event of $P$, and 
 \item for every collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
-disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$. 
+disjoint events, $\mu^{\mathrm{D}}\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu^{\mathrm{D}}(P_{i})$. 
 \end{itemize}
@@
 a Hilbert space of dimension~$d\ge3$, there is no cryptodeterministic
-measure~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $.\end{thm}
-
-\noindent Although sharing a lot of similarity, the Kochen-Specker
-theorem highlight the difference between quantum and classical measures.
-When we think a cryptodeterministic measure as a model of pasted events,
-the Kochen-Specker theorem also consistent with the usual interpretation
-of the quantum theory: we should not ask whether an event happened
-or not if an event is incompatible with the event really happened;
-events compatible with the event really happened are the only askable
-events.
+measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $.\end{thm}
+
+Although sharing a lot of similarity, the Kochen-Specker theorem highlight
+the difference between quantum and classical measures. When we think
+a cryptodeterministic measure as a model of pasted events, the Kochen-Specker
+theorem also consistent with the usual interpretation of the quantum
+theory: we should not ask whether an event happened or not if an event
+is incompatible with the event really happened; events compatible
+with the event really happened are the only askable events.
 
@@
 the following equations since the vectors in each equation form an
-orthogonal basis~\cite{Kernaghan1994,peres1995quantum}.
+orthogonal basis~\cite{Kernaghan1994,peres1995quantum}:
 \begin{equation}\eqalign{ 
@@
 1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
-1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)
+1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
 }\label{eq:Kernaghan-2}\end{equation}

### 2017-03-06 prop_iop.tex
prop_iop.tex Global replace "^{B}" by "^{\mathrm{B}}"...

@@
 pure normalized quantum state $\ket{\phi}$, the Born rule induces a
-probability measure $\mu_{\phi}^{B}$ defined as
-$\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}$. The situation generalizes to
+probability measure $\mu_{\phi}^{\mathrm{B}}$ defined as
+$\mu_{\phi}^{\mathrm{B}}(P)=\ip{\phi}{P\phi}$. The situation generalizes to
 mixed states $\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
 $\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born rule
-induces a probability measure $\mu_{\rho}^{B}$ defined
+induces a probability measure $\mu_{\rho}^{\mathrm{B}}$ defined
 as
-$\mu_{\rho}^{B}\left(P\right) = \Tr\left(\rho P\right) =
+$\mu_{\rho}^{\mathrm{B}}\left(P\right) = \Tr\left(\rho P\right) =
 \sum_{j=1}^{N}
-q_{j}\mu_{\phi_{j}}^{B}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
+q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
 Conversely every probability measure must be of this form.
@@
 measure~$\mu:\events\rightarrow[0,1]$, there exists a unique mixed
-state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.
+state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$.
 \end{thm}
@@
 \caption{\label{fig:three-dimensional-3-value}This figure illustrates the
-1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
+1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{\mathrm{B}}(P)=\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$
 plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
-and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$. $\ket{0}$
-is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$
+and $\bar{\mu}_{\ket{0}}^{\mathrm{B}}\left(\proj{0}\right)=\necess$. $\ket{0}$
+is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\imposs$
 for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
-we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
+we have $\bar{\mu}_{\ket{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\unknown$.}
 \end{figure}
 For example, figure~\ref{fig:three-dimensional-3-value} plots the
-1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$.
+1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$.
 This measure represents the beliefs of an experimenter with no prior
-knowledge about the particular quantum system in question.\footnote{\yutsung{Actually, $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$ is quite
-informative. Since $\iota\left(\mu_{\ket{0}}^{B}(P)\right)=\necess$
-if and only if $P=\proj{0}$, we know the core of $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
-is exactly $\left\{ \mu_{\ket{0}}^{B}\right\} $. The quantum interval-valued
+knowledge about the particular quantum system in question.\footnote{\yutsung{Actually, $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$ is quite
+informative. Since $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)=\necess$
+if and only if $P=\proj{0}$, we know the core of $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$
+is exactly $\left\{ \mu_{\ket{0}}^{\mathrm{B}}\right\} $. The quantum interval-valued
 probability measure for an experimenter with no prior knowledge should
@@
 because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
-$\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)=\left\{ \mu_{\ket{2}}^{B}\right\} $.
+$\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} $.
 \item When $\events_{2}=\events\backslash\left\{ \proj{\ps}\right\} $,
 because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we
-have $\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{1}}^{B}\right\} $.
+have $\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} $.
 \item When $\events_{3}=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
 because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$,
-we have $\mu_{\frac{\mathbb{1}}{3}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$
-as well as $\mu_{\ket{2}}^{B}$ and $\mu_{\ket{1}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$.
+we have $\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$
+as well as $\mu_{\ket{2}}^{\mathrm{B}}$ and $\mu_{\ket{1}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$.
 \end{itemize}
@@
 \begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{B}\right\} \cap\left\{ \mu_{\ket{1}}^{B}\right\} =\emptyset\textrm{ .}
+\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} \cap\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} =\emptyset\textrm{ .}
 \end{equation}
@@
 mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
-such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}\right\} $
+such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{\mathrm{B}}\right\} $
 in the Hilbert space of dimension 3, where the cross product of complex
@@
 in the sphere as in figure~\ref{fig:three-dimensional-real-frame-1},
-and this area intersects a plane~$\events'$, then $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi}}^{B}\right\} $,
+and this area intersects a plane~$\events'$, then $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi}}^{\mathrm{B}}\right\} $,
 where $\ket{\psi}$ is the normal vector of $\events'$. Since different
@@
 by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
-quantum probability measure~$\mu_{\phi}^{B}$ induced by the Born
-rule, its frame function is denoted by $f_{\phi}^{B}$.\end{definition}
+quantum probability measure~$\mu_{\phi}^{\mathrm{B}}$ induced by the Born
+rule, its frame function is denoted by $f_{\phi}^{\mathrm{B}}$.\end{definition}
 
@@
 \begin{enumerate}
-\item $\bar{f}^{-1}\left(\imposs\right)=\emptyset$. If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
+\item $\bar{f}^{-1}\left(\imposs\right)=\emptyset$. If $f_{\phi}^{\mathrm{B}}\in\mathrm{core}\left(\bar{f}\right)$
 for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
 \item $\bar{f}^{-1}\left(\imposs\right)=\left\{ \ket{\psi_{0}}\right\} $.
-If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$ for some pure
+If $f_{\phi}^{\mathrm{B}}\in\mathrm{core}\left(\bar{f}\right)$ for some pure
 state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
@@
 then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
-which might induce $\bar{f}$. In another word, if $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
+which might induce $\bar{f}$. In another word, if $f_{\phi}^{\mathrm{B}}\in\mathrm{core}\left(\bar{f}\right)$
 for some pure state~$\ket{\phi}$, then $\ket{\phi}\parallel\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)$.
@@
 case when the core is empty; an interval-valued frame function defined
-by $\bar{f}\left(\ket{\psi}\right)=\iota\left(f_{\phi}^{B}\left(\ket{\psi}\right)\right)$
-is also in this case when the core is the singleton set~$\left\{ f_{\phi}^{B}\right\} $,
+by $\bar{f}\left(\ket{\psi}\right)=\iota\left(f_{\phi}^{\mathrm{B}}\left(\ket{\psi}\right)\right)$
+is also in this case when the core is the singleton set~$\left\{ f_{\phi}^{\mathrm{B}}\right\} $,
 where $\iota$ is defined in equation~(\ref{eq:homomorphism}). 
@@
 then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
-might induce $\bar{f}$. However, neither $f_{\psi_{0}\times\psi_{1}}^{B}$
-nor $f_{\psi_{0}'\times\psi_{1}'}^{B}$ is in the core of $\bar{f}$
-because $f_{\psi_{0}\times\psi_{1}}^{B}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}'}\right)=\bar{f}\left(\ket{\psi_{1}'}\right)=\imposs$
-and $f_{\psi_{0}'\times\psi_{1}'}^{B}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)=\imposs$.
+might induce $\bar{f}$. However, neither $f_{\psi_{0}\times\psi_{1}}^{\mathrm{B}}$
+nor $f_{\psi_{0}'\times\psi_{1}'}^{\mathrm{B}}$ is in the core of $\bar{f}$
+because $f_{\psi_{0}\times\psi_{1}}^{\mathrm{B}}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}'}\right)=\bar{f}\left(\ket{\psi_{1}'}\right)=\imposs$
+and $f_{\psi_{0}'\times\psi_{1}'}^{\mathrm{B}}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)=\imposs$.
 Actually, $\bar{f}$ has an empty core, and this is the case for example~\ref{ex:three-dimensional-three-value}.
@@
 \begin{proof}
-Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$. Then,
-$\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{B}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
+Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$. Then,
+$\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{B}}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
 i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\bar{\mu}\right)$,
-we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{B}$.
+we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{\mathrm{B}}$.
 \end{proof}
@@
 core. Assume there is a real-valued probability measure satisfying
-$\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$. Because
-$\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$ and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
-we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
-so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
-\begin{equation}
-\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
+$\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$ for all $P\in\events$. Because
+$\mu_{\rho}^{\mathrm{B}}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$ and $\mu_{\rho}^{\mathrm{B}}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
+we must have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
+so that $\mu_{\rho}^{\mathrm{B}}=\mu_{\ket{2}}^{\mathrm{B}}$. However, 
+\begin{equation}
+\mu_{\ket{2}}^{\mathrm{B}}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
 \end{equation}

### 2017-03-06 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

@@
 The Kochen-Specker theorem could then be proved by showing there is
-no function~$v:\events'\rightarrow\left\{ 0,1\right\} $ satisfying
+no function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $ satisfying
 equation~(\ref{eq:Kochen-Specker-Rules}), where 
 \begin{equation}
-\events'=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
+\events_{24}=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
 \end{equation}
@@
 
+Although there is no quantum cryptodeterministic measure defined on
+$\mathcal{T}_{24}$, it is easy to construct a real-valued probability
+measure by the Born rule, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}|_{\events_{24}}$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-03-06 prop_iop.tex
prop_iop.tex \section{Quantum Real-valued and Interval-valued Probability Measures} Updating...

@@
 
-\begin{definition}We say a collection of intervals~$\mathscr{I}$
-with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is
-regular\footnote{\yutsung{''regular'' is just a random name pop into my mind...}}
-if they satisfies the following properties.
+\begin{definition}We say a pair~$\left(\mathscr{I},\iota\right)$
+is regular\footnote{\yutsung{''regular'' is just a random name pop into my mind...
+
+This whole definition might be rewritten using category theory...
+I would investigate it if it is necessary...}} if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is a function satisfying the following properties. 
 \begin{itemize}
@@
 
-\begin{lemma}Consider a regular collection of intervals~$\mathscr{I}$
-with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
+\begin{lemma}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
 Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
@@
 $\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM.\end{lemma}
+
 \begin{proof}
-~
 \begin{itemize}
@@
 \end{proof}
-\begin{lemma}Consider regular a collection of intervals~$\mathscr{I}$
-with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
+
+\begin{lemma}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
 Then, there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.\end{lemma}
-\begin{proof}
-Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$. Then,
-$\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{B}}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
+
+\begin{proof}Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}(P)\right)$.
+Then, $\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
 i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\bar{\mu}\right)$,
-we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{\mathrm{B}}$.
-\end{proof}
-\begin{example}For any positive integer~$n$, the collection of
-intervals~$\mathscr{I}_{n}$ and the map~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
-defined by
+we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.\end{proof}
+
+\begin{example}For any positive integer~$n$, there is a regular
+pair~$\left(\mathscr{I}_{n},\iota_{n}\right)$ defined by 
 \begin{equation}\eqalign{ 
@@
 }\end{equation}
-is regular.\end{example}
+Notice that the usual $\left\{ \necess,\imposs,\unknown\right\} $
+is $\mathscr{I}_{1}$. Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
+and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
+$\left(\mathscr{I}_{\infty},\iota_{\infty}\right)$ is a regular pair.\end{example}
+
 \begin{proof} 
-~
 \begin{itemize}
@@
 \item $\iota\left(1\right)=\left[1,1\right]$. 
-\item When $x=k / n$, we have $\iota\left(1-x\right)=\left[1-k / n,1-k / n\right]=\left[1,1\right]-\iota\left(x\right)$.\\
-When $k / n<x<\left(k+1\right)/n$, we have $1-k / n>1-x>1-\left(k+1\right)/n$
+\item When $x=k/n$, we have $\iota\left(1-x\right)=\left[1-k/n,1-k/n\right]=\left[1,1\right]-\iota\left(x\right)$.\\
+When $k/n<x<\left(k+1\right)/n$, we have $1-k/n>1-x>1-\left(k+1\right)/n$
 so that 
@@
 \begin{itemize}
-\item When $x_{1}=k_{1} / n$, we have
+\item When $x_{1}=k_{1}/n$, we have 
 \begin{equation}
@@
 \end{equation}
-\item When $k_{1} / n<x_{1}<\left(k_{1}+1\right)/n$ and $k_{2}/n<x_{2}<\left(k_{2}+1\right)/n$,
+\item When $k_{1}/n<x_{1}<\left(k_{1}+1\right)/n$ and $k_{2}/n<x_{2}<\left(k_{2}+1\right)/n$,
 we have 

### 2017-03-06 prop_iop.tex
prop_iop.tex \section{Quantum Real-valued and Interval-valued Probability Measures} Updating...
prop_iop.tex \section{Mermin Square}After the meeting...

@@
 
-\begin{proof}
+\begin{proof}~
 \begin{itemize}
@@
 
-\begin{example}For any positive integer~$n$, there is a regular
-pair~$\left(\mathscr{I}_{n},\iota_{n}\right)$ defined by 
+\begin{example}\label{ex:regular-pair}For any positive integer~$n$,
+there is a regular pair~$\left(\mathscr{I}_{n},\iota_{n}\right)$
+defined by 
 \begin{equation}\eqalign{ 
@@
 
-\begin{proof} 
+\begin{proof}~
 \begin{itemize}
@@
 This kind of $v$ is actually a quantum cryptodeterministic measure.
-Since a cryptodeterministic measure are a special case of real-valued
+Since a cryptodeterministic measure is a special case of real-valued
 probability measure, by theorem~\ref{lemma:classical-probability-measures},

### 2017-03-06 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

@@
 
+On one hand, the Kochen-Specker theorem is equivalent to non-existence
+of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
+where $\events$ is the set of all projections on a Hilbert space.
+On the other hand, if the range is the interval~$\left[0,1\right]$,
+Gleason's theorem asserts that every quantum real-valued probability
+measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
+by a density matrix according to the Born rule. These two extreme
+cases can be understood in a broader framework of quantum interval-valued
+probability~$\bar{\mu}:\events\rightarrow\mathscr{I}$, where $\mathscr{I}$
+is a collection of intervals containing in $\left[0,1\right]$. When
+we pick $\mathscr{I}$ as $\left\{ \imposs,\necess\right\} $, where
+$\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$, there
+is no quantum interval-valued probability~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
+theorem.
+
 Although there is no quantum cryptodeterministic measure defined on
 $\mathcal{T}_{24}$, it is easy to construct a real-valued probability
-measure by the Born rule, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}|_{\events_{24}}$.
+measure by the Born rule, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}|_{\events_{24}}$.\footnote{\yutsung{{Find all orthogonal basis of }$\mathcal{T}_{24}$ and solve
+the linear equations for Gleason's...}}
 

### 2017-03-07 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

--- 2017-03-06 prop_iop.tex
@@
 
-\section{Mermin Square\label{sec:MerminSquare}}
-
-The Kochen-Specker theorem asserts that there is no function~$v$
-assigning a definitely value to all observables such that
+\section{Contextuality and the Born Rule in Fuzzy Quantum Theories\label{sec:MerminSquare}}
+
+\footnote{This section will be singled out as a separated letter.}The
+Kochen-Specker theorem asserts that there is no function~$v$ assigning
+a definitely value to all observables such that
 \begin{equation}\eqalign{ 
@@
 
-Although there is no quantum cryptodeterministic measure defined on
-$\mathcal{T}_{24}$, it is easy to construct a real-valued probability
-measure by the Born rule, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}|_{\events_{24}}$.
+On one hand, the Kochen-Specker theorem is equivalent to non-existence
+of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
+where $\events$ is the set of all projections on a Hilbert space.
+On the other hand, if we replace the range by the interval~$\left[0,1\right]$,
+Gleason's theorem asserts that every quantum real-valued probability
+measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
+by a density matrix according to the Born rule. These two extreme
+cases can be understood in a broader framework of quantum interval-valued
+probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$, where
+$\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
+When we pick $\mathscr{I}$ as $\left\{ \imposs,\necess\right\} $,
+where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
+there is no quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
+theorem. When the collection of intervals is $\set{\left\{ x\right\} }{x\in\left[0,1\right]}$,
+a quantum interval-valued probability measure is well-behaved as a
+usual quantum real-valued probability measure does.
+
+Given any sub-event space~$\events'\subseteq\events$, in order to
+qualify how well-behaved a quantum interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
+could be, we introduce a notation of core.
+
+\begin{definition}A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events'\rightarrow[0,1]}{\forall P\in\events'.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}
+
+In the rest of the letter, we will provide examples of quantum interval-valued
+probability measures on $\events_{24}$, and show how a quantum interval-valued
+probability measure~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
+could be depending on different intervals~$\mathscr{I}$.
+
+First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
+it is easy to construct a quantum interval-valued probability measure
+$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$ whose unique core
+element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$. Let $\circ$ denote
+function composition.
+
+\footnote{\yutsung{Find all orthogonal basis of $\mathcal{T}_{24}$ and solve
+the linear equations for Gleason's...}}
 

### 2017-03-07 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

@@
 qualify how well-behaved a quantum interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
-could be, we introduce a notation of core.
+could be, we introduce the notion of core.
 
@@
 
-In the rest of the letter, we will provide examples of quantum interval-valued
-probability measures on $\events_{24}$, and show how a quantum interval-valued
-probability measure~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
+\noindent In the rest of the letter, we will provide examples of quantum
+interval-valued probability measures on $\events_{24}$, and show
+how a quantum interval-valued probability measure~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
 could be depending on different intervals~$\mathscr{I}$.

### 2017-03-07 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

--- 2017-03-07 prop_iop.tex
@@
 by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
-theorem. When the collection of intervals is $\set{\left\{ x\right\} }{x\in\left[0,1\right]}$,
+theorem. When the collection of intervals is $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
 a quantum interval-valued probability measure is well-behaved as a
@@
 
+\noindent Then, Gleason's theorem guarantees that when $\bar{\mu}$
+has an unique core element for any $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$.
 In the rest of the letter, we will provide examples of quantum interval-valued
@@
 $\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$ whose unique core
-element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$. Let $\circ$ denote
-function composition.
+element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$. For example, when
+$\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
+we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
+and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
+where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
+denote function composition. This provides an example that even if
+the
 

### 2017-03-07 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

@@
 cases can be understood in a broader framework of quantum interval-valued
-probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$, where
-$\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
-When we pick $\mathscr{I}$ as $\left\{ \imposs,\necess\right\} $,
+probability measure (IVPM)~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+where $\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
+When we pick $\mathscr{I}$ as $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
 where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
-there is no quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
 theorem. When the collection of intervals is $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-a quantum interval-valued probability measure is well-behaved as a
-usual quantum real-valued probability measure does.
+a quantum IVPM is well-behaved as a usual quantum real-valued probability
+measure does.
 
 Given any sub-event space~$\events'\subseteq\events$, in order to
-qualify how well-behaved a quantum interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
+qualify how well-behaved a quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
 could be, we introduce the notion of core.
@@
 
-\noindent Then, Gleason's theorem guarantees that when $\bar{\mu}$
-has an unique core element for any $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$.
-In the rest of the letter, we will provide examples of quantum interval-valued
-probability measures on $\events_{24}$, and show how a quantum interval-valued
-probability measure~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
+\noindent Then, Gleason's theorem guarantees that $\bar{\mu}$ has
+a unique core element for any $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$.
+In the rest of the letter, we will provide examples of quantum IVPMs
+on $\events_{24}$, and show how a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
 could be depending on different intervals~$\mathscr{I}$.
@@
 First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
-it is easy to construct a quantum interval-valued probability measure
-$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$ whose unique core
-element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$. For example, when
-$\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
+it is easy to construct a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
+whose unique core element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.
+For example, when $\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
 we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
@@
 where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
-denote function composition. This provides an example that even if
-the
+denote function composition. This provides an example that a well-behaved
+quantum IVPM exists even if $\mathscr{I}$ is discrete. Well-behaved
+quantum IVPMs happen when mapping to other kind of intervals. For
+example, we can add an one extra interval~$\unknown=\left[0,1\right]$
+to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
+Let 
+\begin{equation} 
+\iota_1(x)=\cases{ 
+\necess & if $x=1$ ;\\ 
+\imposs & if $x=0$ ;\\ 
+\unknown & otherwise. 
+}\label{eq:homomorphism-1} \end{equation}
+, and we still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.
 

### 2017-03-07 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

@@
 }\label{eq:homomorphism-1} \end{equation}
-, and we still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.
+We still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.
+
+Although the quantum IVPM listed above are all well-behaved, there
+are some quantum IVPMs far from the Born rule. Consider $\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
+defined by $\bar{\mu}(P)=\unknown$ for every projection~$P$. Since
+every quantum probability measure is in the core of $\bar{\mu}$,
+this measure represents the beliefs of an experimenter with no prior
+knowledge about the particular quantum system in question.
 

### 2017-03-11 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

@@
 
-\footnote{\yutsung{Find all orthogonal basis of $\mathcal{T}_{24}$ and solve
-the linear equations for Gleason's...}}
+\begin{example}[Four-dimensional quantum three-interval-valued probability
+measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
+basis~$\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $ as defined
+in table~\ref{table:commonBasis}. Let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
+$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$. Then, we can
+define a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
+as follow. 
+\begin{equation}\eqalign{ 
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
+\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
+}\end{equation}
+To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
+implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
+Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+it is sufficient to check
+\begin{equation}\eqalign{ 
+\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
+\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
+}\end{equation}
+for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}$.
+This equation always holds because $\unknown$ is a subset of the
+left-hand side of both of the equations.
+
+Second, we will prove that $\bar{\mu}$ cannot correspond to any quantum
+probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
+for some quantum probability measure~$\mu:\events_{24}\rightarrow\left[0,1\right]$.
+We must have 
+\begin{equation}
+\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
+\end{equation}
+By Gleason's theorem\footnote{\yutsung{Find all orthogonal basis of $\mathcal{T}_{24}$ and solve
+the linear equations for Gleason's...}}, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
+such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. However, no pure
+state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
+so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
+measure~$\mu$.\qed\end{example}
 
@@
 \bibliography{prop}
-
 \end{comment}

### 2017-03-13 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

@@
 
+\begin{example}[Four-dimensional quantum real-valued probability
+measure]\label{ex:four-dimensional-real-value}Consider the frame
+function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
+Except equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
+$f$ should also satisfy the following equations: 
+\begin{equation}\eqalign{ 
+1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
+1 = f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
+1 = f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
+1 = f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
+1 = f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1)+f(1,1,-1,-1)\textrm{ ,}\\ 
+1 = f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
+1 = f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
+1 = f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,0,0)\textrm{ ,}\\ 
+1 = f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1)+f(1,1,0,0)\textrm{ ,}\\ 
+1 = f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0)+f(1,1,1,-1)\textrm{ ,}\\ 
+1 = f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1)+f(1,1,1,-1)\textrm{ ,}\\ 
+1 = f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0)+f(1,1,1,1)\textrm{ ,}\\ 
+1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
+}\label{eq:non-Kernaghan}\end{equation}
+\qed\end{example}
+
 \begin{example}[Four-dimensional quantum three-interval-valued probability

### 2017-03-13 prop_letter.tex
Put the letter to a seperated file...

--- 2017-03-13 prop_iop.tex
@@
 
-On one hand, the Kochen-Specker theorem is equivalent to non-existence
+On the one hand, the Kochen-Specker theorem is equivalent to the non-existence
 of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
@@
 function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
-Except equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
+Apart from equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
 $f$ should also satisfy the following equations: 

### 2017-03-13 prop_iop.tex
Clean up files...

--- 2017-03-07 prop_iop.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Contextuality and the Born Rule in Fuzzy Quantum Theories\label{sec:MerminSquare}}
-
-\footnote{This section will be singled out as a separated letter.}The
-Kochen-Specker theorem asserts that there is no function~$v$ assigning
-a definitely value to all observables such that
-\begin{equation}\eqalign{ 
-v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
-v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
-}\label{eq:Kochen-Specker-Rules}\end{equation}
-if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
-is a function~$v$ satisfying these two properties, it must send
-an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
-\begin{equation}
-\begin{array}{ccc}
-\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
-\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
-\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
-\end{array}\label{eq:MerminSquare}
-\end{equation}
-must be sent to $1$ or $-1$. In each row and column, operators commutes,
-and each operator is the product of the two others, except in the
-third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-Therefore, it is clear impossible to find a function~$v$ such that
-\begin{equation}
-\begin{array}{ccc}
-v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
-v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
-v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
-\end{array}\label{eq:MerminSquare-values}
-\end{equation}
-satisfying equation~(\ref{eq:Kochen-Specker-Rules}).
-
-\begin{table}
-\caption{\label{table:commonBasis}In each row, three observables are listed
-in the left column commutes, and their common eigenbasis is listed
-in the right column. In order to unified and simplify notation, we
-do not normalize eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
-as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}
-
-\begin{tabular}{ccc|cccc} 
-\br 
-\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
-\mr 
-$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
-$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
-$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
-$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
-$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
-$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
-\br 
-\end{tabular} 
-\end{table}
-Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
-if we want to reformulate the above argument in the language of quantum
-probability measures, we first need to find the common eigenbasis
-of each row and column, and consider the projections to each eigenvectors.
-Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
-The Kochen-Specker theorem could then be proved by showing there is
-no function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $ satisfying
-equation~(\ref{eq:Kochen-Specker-Rules}), where 
-\begin{equation}
-\events_{24}=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
-\end{equation}
-which is a sub-event space defined in definition~\ref{def:sub-event-space}.
-This kind of $v$ is actually a quantum cryptodeterministic measure.
-Since a cryptodeterministic measure is a special case of real-valued
-probability measure, by theorem~\ref{lemma:classical-probability-measures},
-the quantum cryptodeterministic measure~$v$ exists if and only if
-there exists a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
-which should at least satisfy
-\begin{equation}\eqalign{ 
-1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
-1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
-}\label{eq:Kernaghan-1}\end{equation}
-because of table~\ref{table:commonBasis}. $f$ should also satisfy
-the following equations since the vectors in each equation form an
-orthogonal basis~\cite{Kernaghan1994,peres1995quantum}:
-\begin{equation}\eqalign{ 
-1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
-1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
-1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
-1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
-1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
-1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
-1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
-1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
-1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
-}\label{eq:Kernaghan-2}\end{equation}
-In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
-are odd number of equations, but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
-occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
-satisfying equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}.
-
-On one hand, the Kochen-Specker theorem is equivalent to non-existence
-of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
-where $\events$ is the set of all projections on a Hilbert space.
-On the other hand, if we replace the range by the interval~$\left[0,1\right]$,
-Gleason's theorem asserts that every quantum real-valued probability
-measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
-by a density matrix according to the Born rule. These two extreme
-cases can be understood in a broader framework of quantum interval-valued
-probability measure (IVPM)~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-where $\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
-When we pick $\mathscr{I}$ as $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
-there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
-theorem. When the collection of intervals is $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-a quantum IVPM is well-behaved as a usual quantum real-valued probability
-measure does.
-
-Given any sub-event space~$\events'\subseteq\events$, in order to
-qualify how well-behaved a quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
-could be, we introduce the notion of core.
-
-\begin{definition}A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events'\rightarrow[0,1]}{\forall P\in\events'.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}
-
-\noindent Then, Gleason's theorem guarantees that $\bar{\mu}$ has
-a unique core element for any $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$.
-In the rest of the letter, we will provide examples of quantum IVPMs
-on $\events_{24}$, and show how a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
-could be depending on different intervals~$\mathscr{I}$.
-
-First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
-it is easy to construct a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
-whose unique core element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.
-For example, when $\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
-we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
-and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
-where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
-denote function composition. This provides an example that a well-behaved
-quantum IVPM exists even if $\mathscr{I}$ is discrete. Well-behaved
-quantum IVPMs happen when mapping to other kind of intervals. For
-example, we can add an one extra interval~$\unknown=\left[0,1\right]$
-to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
-Let 
-\begin{equation} 
-\iota_1(x)=\cases{ 
-\necess & if $x=1$ ;\\ 
-\imposs & if $x=0$ ;\\ 
-\unknown & otherwise. 
-}\label{eq:homomorphism-1} \end{equation}
-We still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.
-
-Although the quantum IVPM listed above are all well-behaved, there
-are some quantum IVPMs far from the Born rule. Consider $\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
-defined by $\bar{\mu}(P)=\unknown$ for every projection~$P$. Since
-every quantum probability measure is in the core of $\bar{\mu}$,
-this measure represents the beliefs of an experimenter with no prior
-knowledge about the particular quantum system in question.
-
-\footnote{\yutsung{Find all orthogonal basis of $\mathcal{T}_{24}$ and solve
-the linear equations for Gleason's...}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{comment}

### 2017-03-13 prop_letter.tex
Clean up files...

@@
 \begin{document}
-\title{Measurement and Probability in Fuzzy Quantum
-Theories}
+\letter{Contextuality and the Born Rule in Fuzzy Quantum Theories}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
-Textbook quantum mechanics asserts that, given a quantum spin system
-described by the wave function
-$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
-and given the observable
-$S_z =
-\frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
-then the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$
-(with post-measurement state $\fket{\ps\frac{1}{2}}$) is
-$\frac{\pi}{4}$ and the probability of observing the eigenvalue
-$\minus\frac{\hbar}{2}$ (with post-measurement state
-$\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
-frequency interpretation of probability, the above assertion implies
-that when performing a very large number of experiments on quantum
-systems described by wave function $\ket{\psi}$, a fraction
-$\frac{\pi}{4}$ of the experiments will result in the observation
-$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
-result in the observation $\minus\frac{\hbar}{2}$.
-
-In reality, i.e., in an actual experiment, simulation, or computation,
-bounded by space, time, and energy resources, the situation is much
-fuzzier: (i) we cannot \emph{exactly} prepare the state $\ket{\psi}$;
-(ii) we cannot build a measurement apparatus corresponding
-\emph{exactly} to observable $S_z$; and (iii) we cannot prepare
-\emph{exact} replicas of any state. In other words, we can only
-perform a limited number of experiments on quantum systems closely
-related to wave function $\ket{\psi}$ and using an apparatus that
-closely approximates observable $S_z$. Given any fixed resources,
-these experiments will \emph{not} result in the \emph{exact} fraction
-$\frac{\pi}{4}$ of observations $\ps\frac{\hbar}{2}$ and
-$1-\frac{\pi}{4}$ of observations $\minus\frac{\hbar}{2}$. In fact,
-these experiments can be viewed as a method (algorithm) to calculate
-the value $\pi$ and it is known that the state of the art algorithms
-for computing the $n$th binary digit of~$\pi$ require on the order of
-$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
-operations~\cite{journals/moc/BaileyBP97}. In other words, calculating
-the $n$th digit of $\pi$ appears to require more and more physical
-resources as~$n$ gets larger.
-
-All of this is well-known and holds in both the classical and quantum
-worlds. In the classical world, these observations are believed to be
-well-understood approximations to an idealized independent reality
-that can continuously approached with more and more resources. The
-question in the quantum world is more subtle; it is not evident at all
-that this resource-aware perspective does not alter the very
-foundations of quantum mechanics. Indeed taking such resource bounds
-into consideration is what founded computer science as a discipline
-and has become crucial for understanding the very nature of
-computation. Following Feynman~\cite{Feynman1982Simulating},
-Landauer~\cite{Landauer1996188}, and others, one might argue that this
-resource-bounded perspective is also crucial for understanding the
-very nature of physical processes.
-
-In previous work, we analyzed the wave function description of quantum
-systems from a resource-bounded perspective. Technically, instead of
-postulating that quantum states are rays in a Hilbert space, i.e., we
-instead used special finite fields whose size reflected the available
-resources. \ldots
-
-\newpage
-
-This is a \emph{theoretical} investigation of \emph{experimental}
-physics using \emph{computational} methods. All experiments and computations
-are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007,Piccinini2015}.
-Yet, for centuries, the mathematical formalization of such processes
-has been founded on the infinitely precise real or complex numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
-Our purpose here is to exploit the consequences of replacing infinitely-specified
-quantum probabilities by finite number of intervals used in interval-valued
-probability measures~(IVPM); in particular, we show that a quantum
-IVPM may not be induced by a infinitely-precise state, but it might
-be more and more likely to be identified to a particular state when
-the measurement resources increase.
-
-Indeed, almost every description of quantum mechanics, quantum computation,
-or quantum experiments refers to entities such as $\rme$, $\pi$,
-$\sqrt{2}$, etc (see, e.g., \cite{Redhead1987-REDINA,544199,Mermin2007}).
-From a computational perspective, such numbers do not exist in their
-entirety ``for free~\cite{Kent1999,CliftonKent2000}.'' For example,
-the state of the art algorithms for computing the $n$th binary digit
-of~$\pi$ require on the order of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
-operations~\cite{journals/moc/BaileyBP97}. In other words, simply
-referring to the $n$th digit of $\pi$ requires more and more resources
-as $n$ gets larger. Taking such resource bounds into consideration
-is what founded computer science as a discipline and is crucial for
-understanding the very nature of computation and, following Feynman~\cite{Feynman1982Simulating},
-Landauer~\cite{Landauer1996188}, and others, for understanding the
-very nature of physical processes.
-
-We have been revisiting quantum mechanics, quantum information, and
-quantum computation from this resource-aware perspective. Our initial
-results in that domain showed how subtle the issues can be~\cite{usat,geometry2013,DQT2014}:
-a straightforward replacement of the complex numbers by a finite field
-yields a variant of quantum mechanics in which computationally hard
-problems like UNIQUE-SAT (which decides whether a given Boolean formula
-is unsatisfiable or has exactly one satisfying assignment~\cite{Valiant198685,Papadimitriou1993,AroraBarak2009})
-can be deterministically solved in constant time. To eliminate such
-unrealistic theories requires delicate analysis of the structure of
-the Hilbert space, the process of observation, and the notion of probability
-teasing apart their reliance on the infinitely precise real numbers~\cite{geometry2013,DQT2014}.
-
-In this paper, we shift focus from the infinitely-specified but not
-directly observable quantum states, to observable measurable properties
-of quantum systems and their probabilities. Furthermore, we insist
-that our theories of measurement and probability only refer to finitely
-communicable evidence within feasible computational bounds. It follows
-that states, observations, and probabilities all become ``fuzzy'',
-i.e., specified by intervals of confidence that can only increase
-in precision if the available resources increase proportionally. Our
-notion of ``fuzzy quantum mechanics'' is related to existing work~\cite{GranikCaulfield1996,Pykacz2013,SNL2009,Gudder2005,aerts1993physical}
-but, as will be explained in more detail, is distinguished by its
-unique computational character.
-
-We will begin by reviewing existing work that recasts classical probability
-spaces in a resource-aware setting and move to aim at recasting quantum
-probability and quantum measurement. In particular, we develop a measurement
-framework based on quantum IVPM. Surprisingly, we found a quantum
-IVPM which can not be induced by a state, while Shapley proved a classical
-convex IVPM can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
-and Gleason proved a infinitely-specified quantum probabilities measure
-can always be induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-Nevertheless, a quantum IVPM could still correspond to many possible
-states if it is broken into pieces. Our examples also suggest that
-a quantum IVPM could be more and more likely induced by a state while
-the intervals become sharper, i.e., the measurement resources increase.
-
-Since Gleason's theorem supports the idea of von Neumann to define
-a state as a density matrix~\cite{Varadarajan2008}, a density matrix
-might not be a adequate imprecise quantum state. Instead, a imprecise
-quantum state might be more like an interactive system suggested by
-Quantum Bayesianism or QBism~\cite{FuchsSchack2013,FuchsMerminSchack2014,VonBaeyer2016},
-which would interact differently with different clients. Furthermore,
-the validity the fundamental theorems of quantum mechanics followed
-up by Gleason's theorem, such as Bell~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
-might need to be reassessed based on our imprecise measurement. Our
-research then might provide a new insight to the old debate among
-Meyer, Mermin, and others about whether finite precision measurement
-would nullify the Kochen-Specker theorem or not~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Classical Probability}
-
-A \emph{probability space} specifies the necessary conditions for
-reasoning coherently about collections of uncertain
-events~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}.  We
-review the conventional presentation of probability spaces and then
-discuss the computational resources needed to estimate probabilities.
-
-%%%
-\subsection{Classical Probability Spaces}
-
-The conventional definition of a probability space builds upon the
-field of real numbers. In more detail, a probability space consists
-of a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
-and a \emph{probability measure}~$\pmeas$ mapping events in $\events$
-to the real interval $[0,1]$. We will only consider \emph{finite}
-sets of events and restrict our attention to non-empty finite sets
-$\Omega$ as the sample space. The space of events $\events$ includes
-every possible subset of $\Omega$: it is the powerset~$2^{\Omega}=\set{E}{E\subseteq\Omega}$.
-For future reference, we emphasize that events are the primary notion
-of interest and that the sample space is a convenient artifact that
-allows us to treat events as sets obeying the laws of Boolean algebra~\cite{Boole1948,Redhead1987-REDINA,Griffiths2003}.
-
-\begin{definition}[Probability Measure]\label{def:ClassicalProbabilitySpace}
-  Given the set of events $\events$, a \emph{probability measure} is a
-  function $\pmeas:\events\rightarrow[0,1]$ such that:
-\begin{itemize}
-\item $\pmeas(\emptyset)=0$,
-\item $\pmeas(\Omega)=1$, 
-\item for every event $E$,
-  $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$ where
-  $\Omega\backslash E$ is the complement event of $E$, and
-\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of
-  pairwise disjoint events,
-  $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$.
-\end{itemize}
-\end{definition}
-\noindent There is some redundancy in the definition that will be useful when
-moving to quantum probability spaces.
-
-\begin{example}[Two-coins experiment]\label{ex1} Consider an
-  experiment that tosses two coins. We have four possible outcomes
-  that constitute the sample space $\Omega=\{HH,HT,TH,TT\}$. There are
-  16 total events including the event $\{HH,HT\}$ that the first coin
-  lands heads up, the event $\{HT,TH\}$ that the two coins land on
-  opposite sides, and the event $\{HT,TH,TT\}$ that at least one coin
-  lands tails up. Here is a possible probability measure for these
-  events:
-\begin{equation}
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\pmeas(\emptyset) & = & 0\\
-\pmeas(\{HH\}) & = & \frac{1}{3}\\
-\pmeas(\{HT\}) & = & 0\\
-\pmeas(\{TH\}) & = & \frac{2}{3}\\
-\pmeas(\{TT\}) & = & 0\\
-\pmeas(\{HH,HT\}) & = & \frac{1}{3}\\
-\pmeas(\{HH,TH\}) & = & 1\\
-\pmeas(\{HH,TT\}) & = & \frac{1}{3}
-\end{array} & \begin{array}{rcl}
-\pmeas(\{HT,TH\}) & = & \frac{2}{3}\\
-\pmeas(\{HT,TT\}) & = & 0\\
-\pmeas(\{TH,TT\}) & = & \frac{2}{3}\\
-\pmeas(\{HH,HT,TH\}) & = & 1\\
-\pmeas(\{HH,HT,TT\}) & = & \frac{1}{3}\\
-\pmeas(\{HH,TH,TT\}) & = & 1\\
-\pmeas(\{HT,TH,TT\}) & = & \frac{2}{3}\\
-\pmeas(\{HH,HT,TH,TT\}) & = & 1
-\end{array}\end{array}
-\end{equation}
-\end{example}
-
-\noindent It is useful to think that this probability measure is
-completely determined by the ``reality'' of the two coins in question
-and their characteristics, in the sense that each pair of coins
-induces a measure, and each measure must correspond to some pair of
-coins. The measure above would be induced by two particular coins such
-that the first coin is twice as likely to land tails up than heads up
-and the second coin is double-headed.
-
-%%%%%
-\subsection{Measuring Probabilities: Buffon's Needle Problem\label{subsec:Measuring-Probabilities:-Buffon}}
-
-In a strict computational or experimental setting, one should question
-the reliance of the definition of probability space on the uncountable
-and uncomputable real
-interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
-This interval includes numbers like $0.h_{1}h_{2}h_{3}\ldots$ where
-$h_{i}$ is 1 or 0 depending on whether Turing machine
-$\mathit{TM}_{i}$ halts or not. Such numbers cannot be computed. This
-interval also includes numbers like $\pi / 4$ which can only be
-computed with increasingly large resources as the precision
-increases. Therefore, in a resource-aware computational or
-experimental setting, it is more appropriate to consider probability
-measures that map events to a set of elements computable with a fixed
-set of resources. We expand on this observation in the next section
-and then recall its formalization using interval-valued probability
-measures~\cite{Weichselberger2000,JamisonLodwick2004}.
-
-In the previous example, we assumed the probability~$\pmeas(E)$ of
-each event~$E$ is known a priori. In reality, although each event is
-assumed to have a probability, the exact value of $\pmeas(E)$ may not
-be known. According to the \emph{frequency interpretation of
-  probability} (which we will revisit when moving to the quantum
-case)~\cite{Venn1876,Hajek2012}, 
-to determine the probability of an event, we run $M$
-independent trials which gives us an approximation of the (assumed)
-``true'' or ``real'' probability. Let $x_{i}$ be 1 or 0 depending on
-whether the event~$E$ occurs in the $i$-th trial or not, then
-$\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
-the relative frequency~$\sum_{i=1}^{M}x_{i} / M$ with the
-probability converging to one as $M$ goes to infinity, i.e.,
-\begin{equation}
-\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M} x_{i}\right|<\epsilon\right)=1\textrm{ .}
-\end{equation}
-This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
-
-Let's look at a concrete example. Suppose we drop a needle of length
-$\ell$ onto a floor made of equally spaced parallel lines a distance
-$h$ apart, where $\ell<h$. It is a known fact that the probability of
-the needle crossing a line is
-$2\ell/\left(\pi h\right)$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
-Consider an experimental setup consisting of a collection of $M$
-identical needles of length $\ell$. We throw the $M$ needles one
-needle at a time, and observe the number $M_c$ of needles that cross a
-line, thus estimating the probability of a needle crossing a line to
-be $M_c/M$. In an actual experiment with $500$ needles and the
-ratio $\ell/h=0.75$~\cite{Hall1873}, it was found that $236$
-crossed a line so the relative frequency is $0.472$ whereas the
-idealized mathematical probability is $0.4774\ldots$.  In a larger
-experiment with $5000$ needles and the ratio
-$\ell/h=0.8$~\cite{Uspensky1937}, the relative frequency was
-calculated to be $0.5064$ whereas the idealized mathematical
-probability is $0.5092\ldots$. We see that the observed probability
-approaches $2\ell/\left(\pi h\right)$ but only if \emph{larger and larger
-  resources} are expended. These resource considerations suggest that
-it is possible to replace the real interval $[0,1]$ with rational
-numbers up to a certain precision related to the particular experiment
-in question. There is clearly a connection between the number of
-needles and the achievable precision: in the hypothetical experiment
-with 3 needles, it is not sensible to retain 100 digits in the
-expansion of $2\ell/\left(\pi h\right)$.
-
-There is another more subtle assumption of unbounded computational
-power in the experiment. We are assuming that we can always determine
-with certainty whether a needle is crossing a line. But ``lines'' on
-the the floor have thickness, their distance apart is not exactly $h$,
-and the needles' lengths are not all absolutely equal to $\ell$.
-These perturbations make the events ``fuzzy.'' Thus, in an experiment
-with limited resources, it is not possible to talk about the idealized
-event that exactly $M_c$ needles cross lines as this would require the
-most expensive needles built to the most precise accuracy, laser
-precision for drawing lines on the floor, and the most powerful
-microscopes to determine if a needle does cross a line. Instead we
-might talk about the event that $M_c-\delta$ needles evidently cross
-lines and $M_c+\delta'$ needles plausibly cross lines where $\delta$ and
-$\delta'$ are resource-dependent approximations. This fuzzy notion of
-events leads to probabilities being only calculable within intervals
-of confidence reflecting the certainty of events and their
-plausibility. This is indeed consistent with published experiments: in
-an experiment with $3204$ needles and the ratio
-$\ell/h=0.6$~\cite{DeMorgan1872}, $1213$ needles clearly
-crossed a line and $11$ needles were close enough to plausibly be
-considered as crossing the line: we would express the probability in
-this case as the interval
-$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we
-are certain that the event has probability at least
-$\frac{1213}{3204}$ but it is possible that it would have probability
-$\frac{1224}{3204}$.
-
-Another way to re-express the above observations is that the calculus
-of probabilities requires all probabilities to be \emph{coherent}
-(e.g., the probability of the union of two disjoint events is the sum
-of their probabilities). But given limited resources, the calculation
-of a probability measure can only be approximate and hence the
-probabilities cannot be absolutely guaranteed to be coherent in the
-ideal sense.
-
-%%%%%
-\subsection{Classical Interval-Valued Probability Measures}
-
-As motivated above, an event $E_{1}$ may have an interval of probability
-$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
-an interval of probability $[l_{2},r_{2}]$, what is the interval
-of probability for the event $E_{1}\cup E_{2}$? The answer is somewhat
-subtle: although it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
-as the combined probability, one can find a much tighter interval
-if information \emph{against} the event (i.e., information about the
-complement event) is also taken into consideration. Formally, for
-a general event $E$ with probability $[l,r]$, the evidence that
-contradicts $E$ is evidence supporting the complement of $E$. The
-complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
-which we abbreviate $\left[1,1\right]-\left[l,r\right]$. Given a
-sample space~$\Omega$, its set of events~$\events$, and a collection
-of intervals $\mathscr{I}$, a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is a classical interval-valued probability measure if and only if
-$\bar{\mu}$ satisfies the following conditions~\cite{JamisonLodwick2004}
-where the last line uses $\subseteq$ to allow for tighter intervals
-that exploit the complement event: 
-\begin{itemize}
-\item $\bar{\mu}(\emptyset)=[0,0]$. 
-\item $\bar{\mu}(\Omega)=[1,1]$. 
-\item For any event $E$, $\bar{\mu}\left(\Omega\backslash
-E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$.
-\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
-events, we have 
-\begin{equation}
-\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\textrm{ .}\label{eq:classical-include}
-\end{equation}
-\end{itemize}
-
-\begin{example}[Two-coin experiment with interval probability]
-\label{ex3} We split the unit interval $[0,1]$ in the following
-four closed sub-intervals: $[0,0]$ which we call \imposs, $[0,\frac{1}{2}]$
-which we call \unlikely, $[\frac{1}{2},1]$ which we call \likely,
-and $[1,1]$ which we call \necess. Using these new values, we can
-modify the probability measure of example~\ref{ex1} by mapping each
-numeric value to the smallest sub-interval containing it to get the
-following: 
-\begin{equation}
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\bar{\mu}(\emptyset) & = & \imposs\\
-\bar{\mu}(\{HH\}) & = & \unlikely\\
-\bar{\mu}(\{HT\}) & = & \imposs\\
-\bar{\mu}(\{TH\}) & = & \likely\\
-\bar{\mu}(\{TT\}) & = & \imposs\\
-\bar{\mu}(\{HH,HT\}) & = & \unlikely\\
-\bar{\mu}(\{HH,TH\}) & = & \necess\\
-\bar{\mu}(\{HH,TT\}) & = & \unlikely
-\end{array} & \begin{array}{rcl}
-\bar{\mu}(\{HT,TH\}) & = & \likely\\
-\bar{\mu}(\{HT,TT\}) & = & \imposs\\
-\bar{\mu}(\{TH,TT\}) & = & \likely\\
-\bar{\mu}(\{HH,HT,TH\}) & = & \necess\\
-\bar{\mu}(\{HH,HT,TT\}) & = & \unlikely\\
-\bar{\mu}(\{HH,TH,TT\}) & = & \necess\\
-\bar{\mu}(\{HT,TH,TT\}) & = & \likely\\
-\bar{\mu}(\{HH,HT,TH,TT\}) & = & \necess
-\end{array}\end{array}
-\end{equation}
-Despite the absence of infinitely precise numeric information, the
-probability measure is quite informative: it reveals that the second
-coin is double-headed and that the first coin is biased. To understand
-the $\subseteq$-condition, consider the following calculation:
-\begin{equation}\eqalign{
- & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
-=& \imposs+\unlikely+\imposs+\likely\\
-=& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=
-\left[\frac{1}{2},\frac{3}{2}\right]\textrm{ .}
-}\end{equation}
-If we were to equate $\bar{\mu}(\Omega)$ with the sum of the individual
-probabilities, we would get that $\bar{\mu}(\Omega)=\left[\frac{1}{2},\frac{3}{2}\right]$.
-However, using the fact that $\bar{\mu}(\emptyset)=\imposs$, we have
-$\bar{\mu}\left(\Omega\right)=1-\bar{\mu}\left(\emptyset\right)=\necess=[1,1]$.
-This interval is tighter and a better estimate for the probability
-of the event $\Omega$, and of course it is contained in $[\frac{1}{2},\frac{3}{2}]$.
-However it is only possible to exploit the information about the complement
-when all four events are combined. Thus the $\subseteq$-condition
-allows us to get an estimate for the combined event from each of its
-constituents and then gather more evidence knowing the aggregate
-event.
-\end{example}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum Probability}
-
-The mathematical framework of classical probability above assumes that
-there exists a predetermined set of events that are independent of the
-particular experiment --- classical physics is
-non-contextual~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}. 
-However, even in classical situations, the structure
-of the event space is often only partially known and the precise
-dependence of two events on each other cannot, a priori, be determined
-with certainty. In the quantum framework, this partial knowledge is
-compounded by the fact that there exist non-commuting events which
-cannot happen simultaneously. To accommodate these more complex
-situations, conventional approaches to quantum probability abandon the
-sample space~$\Omega$ and reason directly about events which are
-generalized from plain sets to projection operators. A quantum
-probability space therefore consists of just two components: a set of
-events $\qevents$ often formalized as projection operators and a
-probability measure $\mu:\qevents\rightarrow[0,1]$ formalized using
-the Born rule~\cite{Born1983,Mermin2007,Jaeger2007}.
-
-%%%%%
-\subsection{Quantum Events}
-
-\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
-  \label{def:Projection} Given a Hilbert space $\Hilb$, an event (an
-  experimental proposition~\cite{BirkhoffVonNeumann1936}, a
-  question~\cite{10.2307/2308516,Abramsky2012},
-  or an elementary quantum test~\cite{peres1995quantum}) is represented
-  as a (self-adjoint or orthogonal~\cite {Griffiths2003,Maassen2010})
-  projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace
-  of $\Hilb$. The following define projections and list some of their properties:
-\begin{itemize}
-\item $\mathbb{0}$ is a projection. 
-\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
-operator. 
-\item Projection operators $P_{0}$ and $P_{1}$ are \emph{orthogonal}
-  if $P_{0}P_{1}=P_{1}P_{0}=\mathbb{0}$. The sum of two projection
-  operators~$P_{0}+P_{1}$ is also a projection operator if and only if
-  they are orthogonal.
-\item Conversely, every projection~$P$ can be expressed as
-  $\sum_{j=1}^{N}\proj{\psi_{j}}$, where $P$ actually projects onto
-  the linear subspace with orthonormal
-  basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{N}$.
-\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is
-  called an \emph{ideal measurement} if it is a partition of the
-  identity, i.e., $\sum_{i=1}^{N}P_{i}=\mathbb{1}$~\cite{Swart2013}.
-  In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
-  be mutually orthogonal~\cite{Griffiths2003,Halmos1957}, and $N$ must be less
-  or equal to the dimension of the Hilbert space.
-\item If $P$ is a projection operator, then $\mathbb{1}-P$ is also a
-  projection operator, called its \emph{complement}. It is orthogonal to
-  $P$, and corresponds to the complement event~$\Omega\backslash E$ in
-  classical probability~\cite{Griffiths2003}.
-\item Projection operators $P_{0}$ and $P_{1}$ \emph{commute} if $P_{0}P_{1}=P_{1}P_{0}$.
-The product of two projection operators~$P_{0}P_{1}$ is also a projection
-operator if and only if they commute. This corresponds to the classical
-intersection between events~\cite{peres1995quantum,Griffiths2003}. 
-\item For two commuting projection operators $P_{0}$ and $P_{1}$,
-  their \emph{disjunction}~$P_{0}\vee P_{1}$ is defined to be
-  $P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
-\end{itemize}
-\end{definition}
-
-\begin{example}[One-qubit quantum probability space] Consider a
-  one-qubit Hilbert space with each event interpreted as a possible
-  post-measurement state~\cite{peres1995quantum,Mermin2007,Jaeger2007}. 
-  For example, the event $\proj{0}$ indicates
-  that the post-measurement state will be $\ket{0}$; the probability
-  of such an event depends on the current state; the event $\proj{1}$
-  indicates that the post-measurement state will be $\ket{1}$; the
-  event $\proj{\ps}$ where
-  $\ket{\ps}=\left(\ket{0}+\ket{1}\right) / \sqrt{2}$ indicates that the
-  post-measurement state will be $\ket{\ps}$; the event
-  $\mathbb{1}=\proj{0}+\proj{1}$ indicates that the post-measurement
-  state will be a linear combination of $\ket{0}$ and $\ket{1}$ and is
-  clearly certain; finally the empty event $\mathbb{0}$ states that
-  the post-measurement state will be the empty state and is
-  impossible. As in the classical case, a probability measure is a
-  function that maps events to $[0,1]$. Here is a partial
-  specification of a possible probability measure that would be
-  induced by a system whose current state is $\ket{0}$,
-  $\mu\left(\mathbb{0}\right)=0$, $\mu\left(\mathbb{1}\right)=1$,
-  $\mu\left(\proj{0}\right)=1$, $\mu\left(\proj{1}\right)=0$,
-  $\mu\left(\proj{\ps}\right)=\frac{1}{2}$, \ldots. Note that, similarly to
-  the classical case, the probability of $\mathbb{1}$ is 1 and the
-  probability of collections of orthogonal events (e.g.,
-  $\proj{0}+\proj{1}$) is the sum of the individual probabilities.  A
-  collection of non-orthogonal events (e.g., $\proj{0}$ and
-  $\proj{\ps}$) is however not even a valid event. In the classical
-  example, we argued that each probability measure is uniquely
-  determined by two actual coins. A similar (but much more subtle)
-  argument is valid also in the quantum case. By postulates of quantum
-  mechanics and Gleason's theorem, it turns out that for large enough
-  quantum systems, each probability measure is uniquely determined by
-  an actual quantum state as discussed next.
-\end{example}
-
-%%%%%
-\subsection{Quantum Probability Measures}
-
-Given our setup, the definition of a quantum probability measure is a
-small variation on the classical definition.
-
-\begin{definition}[Quantum Probability Measure~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
-Given a Hilbert space $\Hilb$ with its set of events~$\events$,
-a \emph{quantum probability measure} is a function~$\mu:\events\rightarrow[0,1]$
-such that: 
-\begin{itemize}
-\item $\mu(\mathbb{0})=0$. 
-\item $\mu(\mathbb{1})=1$. 
-\item For any projection $P$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$.
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have $\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)$.
-\end{itemize}
-\end{definition}
-
-\noindent A quantum probability measure can be easily constructed if
-one knows the current state of the quantum system by using the Born
-rule.  Specifically, for each
-pure normalized quantum state $\ket{\phi}$, the Born rule induces a
-probability measure $\mu_{\phi}^{\mathrm{B}}$ defined as
-$\mu_{\phi}^{\mathrm{B}}(P)=\ip{\phi}{P\phi}$. The situation generalizes to
-mixed states $\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
-$\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born rule
-induces a probability measure $\mu_{\rho}^{\mathrm{B}}$ defined
-as
-$\mu_{\rho}^{\mathrm{B}}\left(P\right) = \Tr\left(\rho P\right) =
-\sum_{j=1}^{N}
-q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
-Conversely every probability measure must be of this form.
-
-\begin{thm}[Gleason's
-  theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
-a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
-measure~$\mu:\events\rightarrow[0,1]$, there exists a unique mixed
-state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$.
-\end{thm}
-
-%%%%%
-\subsection{Measuring Quantum Probabilities}
-
-Similarly to the classical case, it is possible to estimate quantum
-probabilities by utilizing the frequentist approach of the previous
-section, assuming identical measurements conditions in each repeated
-experiment~\cite{peres1995quantum}. For instance, if one wants to
-determine the probability that the spin of a given silver atom is
-$+\hbar/2$, a Stern-Gerlach apparatus is built where ideally an inhomogeneous
-magnetic field is generated along, let's say, the quantization axis
-$z$. One then produces a collimated beam of identically prepared
-(neutral) silver atoms that is directed between the poles of the magnet
-where a predetermined field-gradient along the $z$ direction has
-been established. Under appropriate experimental conditions we will
-observe that the beam, after traversing the magnetic-field region,
-will be deflected towards two regions identified by distinguished
-spots on a detector situated behind the apparatus~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
-Each of the two discrete values is associated to either $+\hbar/2$
-or $-\hbar/2$, commonly called ``spin up'' and ``spin down'',
-respectively. By ``counting'' the number of atoms that are deflected
-in the ``spin up'' region one can, in principle, estimate the probability
-that the prepared state of the silver atom state has spin $+\hbar/2$.
-Notice that a real experiment does not necessarily represent an ``ideal
-measurement''. For example, not all silver atoms will be identically
-prepared, or the field-gradient could not be large enough to distinguish
-between the spin up and down situations simply producing a large single
-blot. In other words, the closer we get to an ideal measurement the
-better we determine those probabilities at the cost of significantly
-increasing the number of resources. It is not very well appreciated
-in the literature that Bohr attempted to argue against the measurability
-of the spin of a free electron~\cite{Bohr1985,MartensDeMuynck1994,McEvoy2001}.
-Essentially, Bohr argued (and Mott later on justified his assertion
-by an elegant use of uncertainty relations~\cite{10.2307/j.ctt7ztxn5.15})
-that a Stern-Gerlach experiment could not succeed in establishing
-the spin of an unbound electron because the Lorentz force would blur
-the detected pattern. This example illustrates the case of a fundamental
-physical limitation that not even infinite resources could mitigate.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Cryptodeterminism}
-
-Although a real or interval-valued probability measure could model
-whether we believe an event will happen or not, the classical world
-could be modeled in a simpler way. If the complete initial conditions
-for tossing a coin or throwing a needle is known, we can determine
-whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
-In another words, Newtonian physics could be modeled by a cryptodeterministic\footnote{The word ''cryptodeterminism'' is used by Peres which means
-\begin{quote}
-We now introduce the cryptodeterministic hypothesis: It is possible
-to specify all the details of a preparation, so that the result of
-any measurement becomes completely deterministic.
-\end{quote}
-in~\cite{PeresRon1988}, and
-\begin{quote}
-... any purported cryptodeterministic theory which would attribute
-a definite result to each quantum measurement, and still reproduce
-the statistical properties of quantum theory ...
-\end{quote}
-in~\cite{Peres1991,peres1995quantum}.} measure defined as follows.
-
-\begin{definition}[Classical Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
-the set of events~$\events$, a \emph{classical cryptodeterministic
-measure} is a function~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $
-such that: 
-\begin{itemize}
-\item $\mu^{\mathrm{D}}(\emptyset)=0$, 
-\item $\mu^{\mathrm{D}}(\Omega)=1$, 
-\item for every event $E$, $\mu^{\mathrm{D}}\left(\Omega\backslash E\right)=1-\mu^{\mathrm{D}}\left(E\right)$
-where $\Omega\backslash E$ is the complement event of $E$, and 
-\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
-disjoint events, $\mu^{\mathrm{D}}\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\mu^{\mathrm{D}}(E_{i})$. 
-\end{itemize}
-\end{definition}
-
-\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
-the prefect prediction, a cryptodeterministic measure can model the
-belief of events which has already happened. For example, if we tossed
-the coin in example~\ref{ex1}, and saw $HH$, our belief of which
-event has happened is represented by the following example.
-\begin{equation}
-\begin{array}{c@{\qquad\qquad}c}
-\begin{array}{rcl}
-\mu^{\mathrm{D}}(\emptyset) & = & 0\\
-\mu^{\mathrm{D}}(\{HH\}) & = & 1\\
-\mu^{\mathrm{D}}(\{HT\}) & = & 0\\
-\mu^{\mathrm{D}}(\{TH\}) & = & 0\\
-\mu^{\mathrm{D}}(\{TT\}) & = & 0\\
-\mu^{\mathrm{D}}(\{HH,HT\}) & = & 1\\
-\mu^{\mathrm{D}}(\{HH,TH\}) & = & 1\\
-\mu^{\mathrm{D}}(\{HH,TT\}) & = & 1
-\end{array} & \begin{array}{rcl}
-\mu^{\mathrm{D}}(\{HT,TH\}) & = & 0\\
-\mu^{\mathrm{D}}(\{HT,TT\}) & = & 0\\
-\mu^{\mathrm{D}}(\{TH,TT\}) & = & 0\\
-\mu^{\mathrm{D}}(\{HH,HT,TH\}) & = & 1\\
-\mu^{\mathrm{D}}(\{HH,HT,TT\}) & = & 1\\
-\mu^{\mathrm{D}}(\{HH,TH,TT\}) & = & 1\\
-\mu^{\mathrm{D}}(\{HT,TH,TT\}) & = & 0\\
-\mu^{\mathrm{D}}(\{HH,HT,TH,TT\}) & = & 1
-\end{array}\end{array}
-\end{equation}
-\end{example}
-
-The ability to predict classical events unambiguously rather than
-probabilistically inspired Einstein, Podolsky, and Rosen to ask whether
-quantum mechanics has any chance to be improved and predict in the
-same way~\cite{EPR1935,peres1995quantum,544199,Mermin2007}. This
-question can be formulated by whether quantum mechanics could be modeled
-by quantum cryptodeterministic measures.
-
-\begin{definition}[Quantum Cryptodeterministic Measure]\label{def:QuantumCryptodeterministicMeasures}Given
-a Hilbert space $\Hilb$ with its set of events~$\events$, a \emph{quantum
-cryptodeterministic measure} is a function~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $
-such that: 
-\begin{itemize}
-\item $\mu^{\mathrm{D}}(\mathbb{0})=0$, 
-\item $\mu^{\mathrm{D}}(\mathbb{1})=1$, 
-\item for every event $P$, $\mu^{\mathrm{D}}\left(\Omega\backslash P\right)=1-\mu^{\mathrm{D}}\left(P\right)$
-where $\Omega\backslash P$ is the complement event of $P$, and 
-\item for every collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
-disjoint events, $\mu^{\mathrm{D}}\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu^{\mathrm{D}}(P_{i})$. 
-\end{itemize}
-\end{definition}
-
-The answer is ``no'' due to the Kochen-Specker theorem whose proof
-can also be formulated in the language of cryptodeterministic measure
-as in \ref{sec:MerminSquare}.
-
-\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}Given
-a Hilbert space of dimension~$d\ge3$, there is no cryptodeterministic
-measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $.\end{thm}
-
-Although sharing a lot of similarity, the Kochen-Specker theorem highlight
-the difference between quantum and classical measures. When we think
-a cryptodeterministic measure as a model of pasted events, the Kochen-Specker
-theorem also consistent with the usual interpretation of the quantum
-theory: we should not ask whether an event happened or not if an event
-is incompatible with the event really happened; events compatible
-with the event really happened are the only askable events.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Quantum Interval-valued Probability}
-
-%%%%%
-
-\subsection{Quantum Interval-valued Probability Measures}
-
-As argued in the previous sections, given fixed finite resources,
-it is only possible to estimate the quantum probabilities within an
-interval of confidence. It is therefore natural to propose the notion
-of a ``quantum interval-valued probability measure'' that combines
-the definitions of conventional quantum probability measures with
-classical interval-probabilities.
-
-\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
-Given a Hilbert space $\Hilb$ with quantum events (projections)~$\events$,
-and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
-probability measure} is a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that: 
-\begin{itemize}
-\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
-\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
-\item For any projection $P$, 
-\begin{equation}
-\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
-\end{equation}
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have 
-\begin{equation}
-\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
-\end{equation}
-\end{itemize}
-\end{definition}
-
-\noindent It is easy to establish that quantum interval-valued probability
-measures generalize conventional quantum probability measures. In
-particular, any quantum probability measure can be recast as an interval-valued
-measure using arbitrary small intervals as discussed in \ref{sec:Real-and-Interval}.
-However, to simplify our discussion, we will focus on only three intervals
-$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
-where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
-\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
-it provides no information. Given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
-we define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-is defined by 
-\begin{equation} 
-\iota(x)=\cases{ 
-\necess & if $x=1$ ;\\ 
-\imposs & if $x=0$ ;\\ 
-\unknown & otherwise. 
-}\label{eq:homomorphism} \end{equation}
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.38]{figure1} 
-\par\end{centering}
-\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
-1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{\mathrm{B}}(P)=\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$
-plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
-and $\bar{\mu}_{\ket{0}}^{\mathrm{B}}\left(\proj{0}\right)=\necess$. $\ket{0}$
-is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\imposs$
-for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
-we have $\bar{\mu}_{\ket{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\unknown$.}
-\end{figure}
-For example, figure~\ref{fig:three-dimensional-3-value} plots the
-1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$.
-This measure represents the beliefs of an experimenter with no prior
-knowledge about the particular quantum system in question.\footnote{\yutsung{Actually, $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$ is quite
-informative. Since $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)=\necess$
-if and only if $P=\proj{0}$, we know the core of $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$
-is exactly $\left\{ \mu_{\ket{0}}^{\mathrm{B}}\right\} $. The quantum interval-valued
-probability measure for an experimenter with no prior knowledge should
-be $\bar{\mu}(P)=\unknown$ for every projection~$P$.}}
-
-Similarly, we can recast the result of cryptodeterminism to quantum
-interval-valued probability measures as well. In another word, for
-any classically event space~$\events$,there is always a classical
-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
-However, given a Hilbert space of dimension~$d\ge3$, there is no
-quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
-by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
-theorem. The Kochen-Specker theorem provides an example that quantum
-interval-valued probability measures behave differently from the classical
-one, and the convexity and core in the next section provides another
-example that quantum interval-valued probability measures behave unexpectedly.
-
-%%%%%
-
-\subsection{Convexity and Core}
-
-\noindent Formally, we can ask: what can we deduce about the state
-of a quantum system given a quantum interval-valued probability measure,
-i.e., given observations done with finite resources. In the case that
-the intervals are infinitely precise, the question reduces to Gleason's
-theorem which states that the state of the quantum system is uniquely
-determined by the probability measure. But surely the less resources
-are available, the less precise the intervals, and the less we expect
-to know about the state of the system. To formally state and answer
-this question we begin with defining the \emph{core} and \emph{convexity}
-of a probability measure as follows.
-
-\begin{definition} Given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$: 
-\begin{itemize}
-\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$. 
-\item $\bar{\mu}$ is called convex if 
-\begin{equation}
-\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
-\end{equation}
-for all commuting $P_{0},P_{1}\in\events$. 
-\end{itemize}
-\end{definition}
-
-\noindent The core of an interval-valued probability measure is the
-set of real-valued infinitely-precise probability measures it approximates.
-An interval-valued probability measure is convex if whenever certain
-intervals exist then combinations of these intervals must also exist,
-guaranteeing we can add and manipulate probabilities coherently. In
-the classical world, every convex measure has a non-empty core, which
-means that the interval-valued probability measure must approximate
-at least one infinitely-precise measure.
-
-\begin{thm}[Shapley~\cite{Shapley1971,,Grabisch2016}]\label{thm:Shapley}
-Every (classical) convex interval-valued probability measure has a
-non-empty core. \end{thm}
-
-In informal terms, this result states that although measurements done
-with limited resources and poor precision may not uniquely identify
-the true state of the system, there is always at least one system
-that is consistent with the measurements. Surprisingly, we discovered
-a counterexample to this statement in the quantum case, and have:
-
-\begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
-There is a convex quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.\end{thm}
-
-This theorem could be proved by constructing the following convex
-quantum interval-valued probability measure with an empty core.
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.38]{figure2_1} 
-\par\end{centering}
-\caption{\label{fig:three-dimensional-3-value-2}This figure illustrates example~\ref{ex:three-dimensional-three-value}
-plotted in $\mathbb{R}^{3}$. The red, green, and blue vectors are
-$\ket{0}$, $\ket{\ps}$, and $\ket{\ps'}$ respectively. }
-\end{figure}
-
-\begin{example}[Three-dimensional quantum three-interval-valued probability
-measure]\label{ex:three-dimensional-three-value} Given a three dimensional
-Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
-$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and 
-\begin{equation}\eqalign{ 
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
-\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
-}\end{equation}
-It is straightforward to verify that $\bar{\mu}$ is a quantum interval-valued
-probability measure by theorem~\ref{thm:interval-valued-frame-function}
-and convex by theorem~\ref{thm:convex-3}. Now assume there exists
-a real-valued quantum probability measure $\mu$ such that $\mu(P)\in\bar{\mu}(P)$
-for every event (projection)~$P$. We derive a contradiction as follows.
-Suppose $\mu(P)\in\bar{\mu}(P)$ then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
-By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
-such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
-can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
-\end{example}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Why Empty Core?}
-
-The possibility that a convex quantum interval-valued probability
-measure has an empty core departs from the classical case. To understand
-the meaning of it, we will first study how to recover the non-empty
-core with extra conditions. We will then consider having an empty
-core as an legitimate result, and understand its consequence.
-
-\subsection{Convexity}
-
-One possibility for having an empty core is that the definition of
-quantum convexity is too weak. On one hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-to non-commuting projectors~$P_{0}$ and $P_{1}$ is unlikely to
-succeed because the product of non-commuting projectors is not a projector.
-On the other hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-among commuting projectors cannot guarantee a non-empty core as well
-if we follow what people strengthen convexity classically. Equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-classically is a special case of 
-\begin{equation}
-\bar{\mu}'\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is odd}}}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is even}}}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\label{eq:Dempster-Shafer-game}
-\end{equation}
-when $N=2$, where $\bar{\mu}'$ is a classical interval-valued probability
-measure. If $\bar{\mu}'$ satisfies equation~(\ref{eq:Dempster-Shafer-game})
-for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
-then the left-end point of $\bar{\mu}'$ is called a Dempster-Shafer
-belief function. It is reasonable to call a quantum interval-valued
-probability~$\bar{\mu}$ Dempster-Shafer if $\bar{\mu}$ satisfies
-\begin{equation}
-\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is odd}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is even}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
-\end{equation}
-for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
-However, the quantum interval-valued probability measure in example~\ref{ex:three-dimensional-three-value}
-is Dempster-Shafer and has an empty core. In summary, it is unlikely
-to guarantee a non-empty core by strengthening convexity.
-
-\subsection{Commuting Sub-Event Space}
-
-Another reason for having an empty core is the existence of non-commuting
-observables. Non-commutativity is one of the difference between quantum
-and classical since Heisenberg's uncertainty principle states there
-is an intrinsic uncertainty measuring non-commuting observables in
-quantum mechanics~\cite{Heisenberg1983,peres1995quantum,544199,Griffiths2003,Jaeger2007}.
-Similarly, we argue that the quantum phenomenon disappears when we
-restrict the domain of a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-on a mutually commuting subspace~$\events'$. As proved in theorem~\ref{thm:sub-event-space},
-the restricted $\bar{\mu}|_{\events'}$ is essentially a classical
-interval-valued probability measure. Furthermore, if $\bar{\mu}$
-is convex, then $\bar{\mu}|_{\events'}$ will be convex, and have
-a non-empty core classically.
-
-When $\bar{\mu}$ is restricted to different commuting $\events'$,
-the core elements of each $\bar{\mu}|_{\events'}$ may not be glued
-together, and gives a core element of $\bar{\mu}$. The inability
-of gluing core elements among commuting $\events'$ to non-commuting
-$\events$ is consistent with the proof of the Kochen-Specker theorem,
-where each triple of commuting observables could be colored well,
-but we cannot color all observables which are not all commuting. This
-is also consistent with the assertion that mutually commuting observables
-could be measured simultaneously~\cite{Mermin_1993}. In another
-word, if Alice and Bob in Bell's theorem can only pick from a set
-of mutually commuting observables, they could never observe any ``quantum,``
-and prove the quantum theory cannot be simulated by a local hidden
-variable theory.
-
-\subsection{Increase the Measurement Resource}
-
-This section extend the idea of restricting the event space, but instead
-of commuting sub-event space, we will try to find some subset~$\events'\subseteq\events$
-such that $\bar{\mu}|_{\events'}$ has an non-empty core. This could
-help us understand the core because of the following identity
-\begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\label{eq:core-intersection}
-\end{equation}
-if we know more about the right-hand side of the equation, we can
-have more idea about the left-hand side. This idea can be applied
-to example~\ref{ex:three-dimensional-three-value}, and the following
-are three of all possibilities:
-\begin{itemize}
-\item When $\events_{1}=\events\backslash\left\{ \proj{\ps'}\right\} $,
-because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
-$\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} $.
-\item When $\events_{2}=\events\backslash\left\{ \proj{\ps}\right\} $,
-because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we
-have $\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} $.
-\item When $\events_{3}=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
-because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$,
-we have $\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$
-as well as $\mu_{\ket{2}}^{\mathrm{B}}$ and $\mu_{\ket{1}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$.
-\end{itemize}
-Each of these possibilities is compatible with some but not all of
-the observations. In another word, 
-\begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} \cap\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} =\emptyset\textrm{ .}
-\end{equation}
-The first two possibilities are particular interesting since each
-two 1-dimensional projectors~$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
-mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
-such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{\mathrm{B}}\right\} $
-in the Hilbert space of dimension 3, where the cross product of complex
-vectors is defined in definition~\ref{def:cross-product}.
-
-As we illustrated in figure~\ref{fig:three-dimensional-3-value},
-if $\bar{\mu}$ has a non-empty core, the states mapping to $\imposs$
-is contained in a plane, which contains no area in the sphere. On
-the other hand, if the states mapping to $\imposs$ contain some area
-in the sphere as in figure~\ref{fig:three-dimensional-real-frame-1},
-and this area intersects a plane~$\events'$, then $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi}}^{\mathrm{B}}\right\} $,
-where $\ket{\psi}$ is the normal vector of $\events'$. Since different
-planes have different normal vectors, $\bar{\mu}$ has an empty core.
-Furthermore, the larger the area, the more state vectors which are
-inconsistent with any particular Born rule probability measure. In
-another word, there are more different singleton sets in the right-hand
-side of equation~(\ref{eq:core-intersection}). Therefore, the area
-of the 1-dimensional projectors mapping to $\imposs$ could indicate
-how much $\bar{\mu}$ deviate from the Born rule probability measures.
-
-In this sense, we found that the area of the 1-dimensional projectors
-mapping to $\imposs$ depends on the maximal length of the intervals,
-which represents the ability of measurement equipment. In particular,
-we have the following results whose details are described in \ref{sec:Real-Interval-valued-Frame}. 
-\begin{itemize}
-\item The radius of any disk inside the area of the 1-dimensional projectors
-mapping to $\imposs$ must smaller than $\pi / 4$ (theorem~\ref{thm:pi-div-4}).
-\item When the radius of any disk inside the area of the 1-dimensional projectors
-mapping to $\imposs$ between $\arcsin\left(1 / \sqrt{3}\right)$
-and $\pi / 4$, we have $\unknown\in\mathscr{I}$, i.e., $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=1$
-(theorem~\ref{thm:arcsin-one-over-sqrt-three}).
-\item When the radius of any disk inside the area of the 1-dimensional projectors
-mapping to $\imposs$ between $\pi/6$ and $\arcsin\left(1 / \sqrt{3}\right)$,
-we have $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=\frac{1}{3}$
-(to be typed...).
-\end{itemize}
-In general, we conjecture that if the measurement equipment is made
-more and more precise, the corresponding interval-valued probability
-measure will be closer and closer to the Born rule. In the limit case,
-$\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$ we do
-indeed recover the conventional Gleason's theorem and the Born rule.
-
-%%%%%
-
-\subsection{Wigner's Friends}
-
-The situation of empty core might not be that strange if we think
-in terms of Wigner's ``friends.'' In the original story of Wigner
-and his friend~\cite{Wigner1961,FuchsMerminSchack2014}, the friend
-makes a measurement in a closed laboratory and experiences an outcome.
-Wigner, outside the laboratory, doesn't experience an outcome. If
-he believes what his friend has told him about her plans in her laboratory
-he will assign an entangled state to her, her apparatus, and the system
-on which she is making her intervention. If Wigner goes on to ask
-his friend about her experience, then the entangled state to her,
-her apparatus, and the system will change into one in which they even
-have separate wave functions, and Wigner and his friend will use the
-same wave function to describe the system.
-
-The question is what happens if Wigner has more than one friend in
-the laboratory. Suppose Wigner has three friends: E, P, and R in the
-laboratory. E, P, and R measure the spin-1 system described in example~\ref{ex:three-dimensional-three-value}.
-After the experiment, E tells Wigner $\proj{0}$ never happened, P
-tells Wigner $\proj{\ps}$ never happened, and R tells Wigner $\proj{\ps'}$
-never happened. Wigner may then need to use the quantum Dempster-Shafer
-rule(?) or other rules(?) to combine the belief told by his friends,
-and the combined belief might be the quantum interval-valued probability
-measure in example~\ref{ex:three-dimensional-three-value} which
-has an empty core.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion and Discussion}
-
-If we insist that probabilities cannot be computed to infinite precision
-and are bound to be approximations represented by intervals of confidence,
-then quantum states themselves can only be discussed within intervals
-of confidence. Despite the fact that classically a IVPM could always
-correspond to a real-valued probability measure, we found that there
-may be no ``real'' infinitely-precise quantum state approximated
-by a quantum IVPM as a whole. However, if a quantum IVPM is decomposed
-into pieces, each piece might still be induced by a quantum state.
-Moreover, our examples and Gleason's theorem summarized in table~\ref{table_long}
-suggests that as the measurement resources increase, an entire quantum
-IVPM could more and more likely be identified to a particular state.
-\begin{table}
-\caption{\label{table_long}Relation between measurement resources and
-interval-valued probability measures.}
-\begin{indented}
-\item[]\begin{tabular}{c|cccc}
-\br
-Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
-\mr
-Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
-$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
-Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
-Count of states correspond to pieces of $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
-\mr
-How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
-\br
-\end{tabular}
-\end{indented}
-\end{table}
-Additional work is in progress on the following research questions:
-\begin{description}
-\item [{Research Question.}] Confirm that there is always a quantum IVPM
-with an empty-core if the length of the intervals is bigger than zero. 
-\item [{Research Question.}] Find a general method to determine how a
-quantum IVPM is close to the Born rule. 
-\item [{Research Question.}] Confirm that as the number and precision
-of the intervals increase the quantum IVPM converges to the measure
-induced by the Born rule. 
-\item [{Research Question.}] Investigate the status of the theorems of
-Bell and Kochen-Specker for quantum IVPM.
-\end{description}
-Although we discussed how a quantum IVPM could be induced from a real
-quantum state, our investigation leaves an open question of whether
-there exists a ``real'' entity that exists independently of measurements
-and probabilities. The possibility of no ``real'' underlying state
-is consistent with the elegantly recent work on Quantum Bayesianism
-or QBism~\cite{FuchsSchack2013,FuchsMerminSchack2014,VonBaeyer2016},
-which suggests that the quantum state is more like an interactive
-system in computer science parlance. In another word, the quantum
-state is subjective: each observer has a different view of the quantum
-system that is consistent with their previous observations and that
-allows that observer, independently of other observers, to assign
-beliefs (i.e., probabilities) to possible future interactions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\ack
-
-Anyone who has discussed this with us?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Interval-valued Frame Functions\label{sec:Interval-valued-Frame-Functions}}
-
-Although quantum IVPMs in example~\ref{ex:three-dimensional-three-value}
-and \ref{ex:three-dimensional-5-value} have empty cores, we might
-still think that the probability measure~$\bar{\mu}$ is induced
-by some states. In example~\ref{ex:three-dimensional-three-value},
-the probability measure~$\bar{\mu}$ might be induced by the state
-$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
-or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
-In example~\ref{ex:three-dimensional-5-value}, the probability measure~$\bar{\mu}$
-might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
-In general, each two real 1-dimensional projectors~$\proj{\psi_{0}}$
-and $\proj{\psi_{1}}$ mapping to impossible suggests $\bar{\mu}$
-might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
-in the Hilbert space of dimension 3.
-
-Since a quantum IVPM is completely determined by its value on 1-dimensional
-projectors in the Hilbert space of dimension 3, we could define the
-interval-valued frame function to simplify the later discussion.
-
-\begin{definition}\cite{Hatcher2001,dryden2005}~The unit sphere
-in $\mathbb{R}^{d}$ is denoted by $S^{d-1}=\set{\ket{\psi}\in\mathbb{R}^{d}}{\ip{\psi}{\psi}=1}$,
-while the unit sphere in $\mathbb{C}^{d}$ is denoted by $\mathbb{C}S^{d-1}=\set{\ket{\psi}\in\mathbb{C}^{d}}{\ip{\psi}{\psi}=1}$.
-Since $\mathbb{C}$ is one-to-one correspondence to $\mathbb{R}^{2}$~\cite{GAMELIN2003},
-$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. However,
-different symbols emphasis that they are embedded in different spaces.\end{definition}
-
-\begin{definition}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~For
-any quantum probability measure~$\mu$ on the Hilbert space of dimension~$d$,
-we can define its \emph{frame function}~$f:\mathbb{C}S^{d-1}\rightarrow\left[0,1\right]$
-by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
-quantum probability measure~$\mu_{\phi}^{\mathrm{B}}$ induced by the Born
-rule, its frame function is denoted by $f_{\phi}^{\mathrm{B}}$.\end{definition}
-
-\begin{thm}\label{thm:frame-function}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~A
-frame function~$f:\mathbb{C}S^{d-1}\rightarrow\left[0,1\right]$
-satisfies the following properties: 
-\begin{itemize}
-\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
-$\ket{\psi}\in\mathbb{C}S^{d-1}$ and $\lambda\in\mathbb{C}S^{0}$. 
-\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
-we have $1=\sum_{i=0}^{2}f\left(\ket{\psi_{i}}\right)$. 
-\end{itemize}
-Conversely, if a function~$f:\mathbb{C}S^{d-1}\rightarrow\left[0,1\right]$
-satisfies the above properties, $f$ must be a frame function.\end{thm}
-
-\begin{definition}For any quantum IVPM~$\bar{\mu}$ on the Hilbert
-space of dimension 3, we can define an \emph{interval-valued frame
-function}~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
-where $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
-are the left-end and the right-end of $\bar{f}$, respectively. Also,
-if $f$ is the frame function of $\mu$, $\bar{f}$ is the interval-valued
-frame function of $\bar{\mu}$, and $\mu$ is in the core of $\bar{\mu}$,
-then we say $f$ is in the core of $\bar{f}$, and denoted by $f\in\mathrm{core}\left(\bar{f}\right)$.\end{definition}
-
-\begin{thm}\label{thm:interval-valued-frame-function}An interval-valued
-frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ satisfies
-the following properties:
-\begin{itemize}
-\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
-for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$. 
-\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
-we have $\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
-where $i$, $j$, and $k$ are any permutations among $0$, $1$,
-and $2$. 
-\end{itemize}
-Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
-satisfies the above properties, $\bar{f}$ must be an interval-valued
-frame function.\end{thm}
-
-\begin{proof} Given a quantum IVPM~$\bar{\mu}$, it is straightforward
-to verify that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
-satisfies the above properties.
-
-Conversely, given a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
-satisfying the above properties, consider $\bar{\mu}:\events\rightarrow\mathscr{I}$
-defined by 
-\begin{itemize}
-\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$ and $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
-\item For any $\ket{\psi}\in\mathbb{C}S^{2}$, we have $\bar{\mu}\left(\proj{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
-and $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{\psi}\right)$. 
-\end{itemize}
-Since other conditions are trivial, we only need to verify equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
-First notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
-implies equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-by induction. Second, equation~(\ref{eq:QuantumInterval-valuedProbability-Complement})
-implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
-Therefore, to prove equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-it is sufficient to check 
-\begin{equation}
-\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
-\end{equation}
-for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$,which always
-holds because the properties of $\bar{f}$.\end{proof}
-\begin{definition}\label{def:cross-product}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}
-\alpha_{0}\\
-\alpha_{1}\\
-\alpha_{2}
-\end{array}\right)$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\left(\begin{array}{c}
-\beta_{0}\\
-\beta_{1}\\
-\beta_{2}
-\end{array}\right)$, their cross product is defined as follow: 
-\begin{equation}
-\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\left|\begin{array}{cc}
-\alpha_{1}^{*} & \beta_{1}^{*}\\
-\alpha_{2}^{*} & \beta_{2}^{*}
-\end{array}\right|\ket{0}+\left|\begin{array}{cc}
-\alpha_{2}^{*} & \beta_{2}^{*}\\
-\alpha_{0}^{*} & \beta_{0}^{*}
-\end{array}\right|\ket{1}+\left|\begin{array}{cc}
-\alpha_{0}^{*} & \beta_{0}^{*}\\
-\alpha_{1}^{*} & \beta_{1}^{*}
-\end{array}\right|\ket{2}\textrm{ ,}
-\end{equation}
-where $\left|\begin{array}{cc}
-\alpha & \beta\\
-\alpha' & \beta'
-\end{array}\right|=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
-cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
-as usual. We will use $\ket{\psi}\times\ket{\phi}$ and $\ket{\psi}\times\ket{\phi}/\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert $
-interchanged when there is no confusion.\end{definition}
-
-\begin{definition}For $\ket{\psi}$ and $\ket{\phi}\in\mathbb{C}^{3}$,
-if $\ket{\psi}=\lambda\ket{\phi}$ for some~$\lambda\ne0$, we call
-$\ket{\psi}$ is parallel to $\ket{\phi}$ denoted by $\ket{\psi}\parallel\ket{\phi}$.
-In this case, $\ket{\psi}$ and $\ket{\phi}$ represent the same physical
-state. ``$\ket{\psi}$ is not parallel to $\ket{\phi}$'' is denoted
-by $\ket{\psi}\nparallel\ket{\phi}$.\end{definition}
-
-\begin{lemma}Given $\ket{\psi}$, $\ket{\phi}$ and $\ket{\varphi}\in\mathbb{C}^{3}$
-such that $\ket{\psi}\nparallel\ket{\phi}$. Then, $\ket{\varphi}\parallel\left(\ket{\psi}\times\ket{\phi}\right)$
-if and only if $\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$.\end{lemma}
-\begin{proof}
-To prove that $\ket{\varphi}\parallel\left(\ket{\psi}\times\ket{\phi}\right)\Rightarrow\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$,
-we can just verify 
-\begin{equation}\eqalign{
-&\ip{\psi}{\psi\times\phi}=\ip{\psi\times\phi}{\psi}^{*}\\
-=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}\right]^{*}=0\textrm{ ,}\\
-&\ip{\phi}{\psi\times\phi}=\ip{\psi\times\phi}{\phi}^{*}\\
-=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}\right]^{*}=0\textrm{ .}
-}\end{equation}
-
-To prove the other direction, consider the linear transformation~$T:\mathbb{C}^{3}\rightarrow\mathbb{C}^{2}$
-defined by $T\left(\ket{\varphi}\right)=\left(\begin{array}{c}\ip{\psi}{\varphi}\\
-\ip{\phi}{\varphi}
-\end{array}\right)$. Since $\ket{\psi}\nparallel\ket{\phi}$, we have $\mathrm{rank}\left(T\right)=2$.
-Together with the rank equation~\cite{FraleighBeauregard1995}, we
-have
-\begin{equation}
-\dim\left(\ker T\right)=\mathrm{nullity}\left(T\right)=3-\mathrm{rank}\left(T\right)=3-2=1\textrm{ .}
-\end{equation}
-By the other direction of the proof, we have already known $\ket{\psi}\times\ket{\phi}\in\ker T$.
-Therefore, $\ket{\varphi}\parallel\left(\ket{\psi}\times\ket{\phi}\right)$.
-\end{proof}
-Since interval-valued probability measures~$\bar{\mu}$ and interval-valued
-frame functions~$\bar{f}$ are one-to-one correspondence, studying
-1-dimensional projectors mapping to impossible by $\bar{\mu}$ is
-the same as studying the points on $\mathbb{C}S^{2}$ mapping to impossible
-by $\bar{f}$. These points, denoted by $\bar{f}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}S^{2}}{\bar{f}(\ket{\psi})=\imposs}$,
-play an important role to understand $\bar{f}$. There are 4 different
-cases when analyzing $\bar{f}^{-1}\left(\imposs\right)$:
-\begin{enumerate}
-\item $\bar{f}^{-1}\left(\imposs\right)=\emptyset$. If $f_{\phi}^{\mathrm{B}}\in\mathrm{core}\left(\bar{f}\right)$
-for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
-\item $\bar{f}^{-1}\left(\imposs\right)=\left\{ \ket{\psi_{0}}\right\} $.
-If $f_{\phi}^{\mathrm{B}}\in\mathrm{core}\left(\bar{f}\right)$ for some pure
-state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
-to $\ket{\psi_{0}}$.
-\item Consider $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} \subseteq\bar{f}^{-1}\left(\imposs\right)$.
-If $\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)\parallel\left(\ket{\psi_{0}'}\times\ket{\psi_{1}'}\right)$
-for any $\left\{ \ket{\psi_{0}'},\ket{\psi_{1}'}\right\} \subseteq\bar{f}^{-1}\left(\imposs\right)$,
-then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
-which might induce $\bar{f}$. In another word, if $f_{\phi}^{\mathrm{B}}\in\mathrm{core}\left(\bar{f}\right)$
-for some pure state~$\ket{\phi}$, then $\ket{\phi}\parallel\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)$.
-For example, example~\ref{ex:three-dimensional-5-value} is in this
-case when the core is empty; an interval-valued frame function defined
-by $\bar{f}\left(\ket{\psi}\right)=\iota\left(f_{\phi}^{\mathrm{B}}\left(\ket{\psi}\right)\right)$
-is also in this case when the core is the singleton set~$\left\{ f_{\phi}^{\mathrm{B}}\right\} $,
-where $\iota$ is defined in equation~(\ref{eq:homomorphism}). 
-\item If there exist two pair of states and $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} $
-and $\left\{ \ket{\psi_{0}'},\ket{\psi_{1}'}\right\} \subseteq\bar{f}^{-1}\left(\imposs\right)$
-such that $\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)\nparallel\left(\ket{\psi_{0}'}\times\ket{\psi_{1}'}\right)$,
-then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
-might induce $\bar{f}$. However, neither $f_{\psi_{0}\times\psi_{1}}^{\mathrm{B}}$
-nor $f_{\psi_{0}'\times\psi_{1}'}^{\mathrm{B}}$ is in the core of $\bar{f}$
-because $f_{\psi_{0}\times\psi_{1}}^{\mathrm{B}}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}'}\right)=\bar{f}\left(\ket{\psi_{1}'}\right)=\imposs$
-and $f_{\psi_{0}'\times\psi_{1}'}^{\mathrm{B}}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)=\imposs$.
-Actually, $\bar{f}$ has an empty core, and this is the case for example~\ref{ex:three-dimensional-three-value}.
-\end{enumerate}
-In summary, if we have an idea of $\bar{f}^{-1}\left(\imposs\right)$,
-we could have some idea of the pure states in core.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Real Interval-valued Frame Functions\label{sec:Real-Interval-valued-Frame}}
-
-In order to simplify the discussion, we call a function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$
-satisfying conditions in theorem~\ref{thm:interval-valued-frame-function}
-a real interval-valued frame function. Obviously, any results in appendix~\ref{sec:Interval-valued-Frame-Functions}
-still hold if we replace every ``complex'' by ``real,'' in particular,
-replace every $\mathbb{C}S^{2}$ by $S^{2}$. Furthermore, since restricting
-the domain of a complex interval-valued frame function to $S^{2}$
-gives a real interval-valued frame function, if we prove there is
-no real interval-valued frame function satisfying a condition, then
-there must be no complex interval-valued frame function satisfying
-the corresponding condition. From now on, when we write an interval-valued
-frame function~$\bar{f}$ without other specification, we would always
-means a real interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$.
-
-If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the case
-1 - 3 in the end of appendix~\ref{sec:Interval-valued-Frame-Functions}
-so that $\bar{f}^{-1}\left(\imposs\right)$ contains no area in $S^{2}$.
-In contrast, if $\bar{f}^{-1}\left(\imposs\right)$ contains some
-area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
-has an empty core. Furthermore, the larger the area, the more state
-vectors which are inconsistent with any particular Born rule frame
-function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)$
-could indicate how much $\bar{f}$ deviate from the Born rule frame
-functions. In the following paragraphs, we will establish that if
-the area of $\bar{f}^{-1}\left(\imposs\right)$ is big, then the interval~$\mathscr{I}$
-must be coarse. In another word, if the interval~$\mathscr{I}$ is
-finer, then the area of $\bar{f}^{-1}\left(\imposs\right)$ would
-be smaller so that $\bar{f}$ is closer to a Born rule frame function.
-
-In order to simplify the discussion, consider the center of $\bar{f}^{-1}\left(\imposs\right)$
-as the north pole, and assume $\bar{f}$ maps every state whose latitude
-is larger than $\theta_{0}$ to impossible.
-
-\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
-north pole~$\ket{0}\in S^{2}$, then $\angle\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
-denotes the latitude of $\ket{\psi}$. Conversely, $\angle^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\angle\left(\ket{\psi}\right)\in I}$.
-For example, the north pole has the latitude $0$, the equator has
-the the latitude $\pi / 2$, and $\angle^{-1}\left(\left[0,\theta_{0}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\pi / 2}$
-contains all states whose latitude is larger than $\theta_{0}$.\end{definition}
-
-\begin{lemma}\label{lemma:imposs-imply-same-value}Given
-$\theta_{0}\in\left[0,\pi/2\right]$ and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
-if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
-then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
-for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi/2-\theta_{0},\pi/2\right]\right)$.\end{lemma}
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.38]{figureb1} 
-\par\end{centering}
-\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
-the proof of lemma~\ref{lemma:imposs-imply-same-value}, where every
-vector above the light green circle maps to $\imposs$, and we want
-to prove that every vector between dark green and light blue maps
-to the same interval.}
-\end{figure}
-\begin{proof} We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
-Let the yellow circle is the states whose latitude is $\theta_{0}$.
-Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
-In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
-Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
-basis, by theorem~\ref{thm:interval-valued-frame-function}, we have
-
-\begin{equation} 
-\eqalign{\left[1,1\right]-\bar{f}\left(\ket{1}\right)\subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\ 
-\left[1,1\right]-\bar{f}\left(\ket{2'}\right)\subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right) 
-} 
-\label{eq:includes} 
-\end{equation}
-so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
-By the same reason, for any state~$\ket{\psi}$ in the dotted black
-circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
-Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
-the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
-and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
-if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
-then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.
-
-Moreover, the same argument can apply on the great circle which is
-not longitude. Since $\ket{\bar{1}}$ is the normal vector of the
-gray circle which includes $\ket{2}$ and $\ket{\bar{2}}$, we have
-$\bar{f}\left(\ket{2}\right)=\left[1,1\right]-\bar{f}\left(\ket{\bar{1}}\right)=\bar{f}\left(\ket{\bar{2}}\right)$.
-In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\pi / 2\right]\right)$,
-even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are not in the same
-longitude, then $\bar{f}\left(\ket{\psi_{0}}\right)$ and $\bar{f}\left(\ket{\psi_{1}}\right)$
-are still the same.
-
-Thus, we could plug $\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)=\left[l_{0},r_{0}\right]$
-into equation~(\ref{eq:includes}), and get 
-\begin{equation}
-\left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\Rightarrow
-l_{0}+r_{0}=1\textrm{ .}
-\end{equation}
-Also, we have 
-\begin{equation}
-1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\Rightarrow
-l_{0}\le\frac{1}{2}\le r_{0}\textrm{ .}
-\end{equation}
-Thus the lemma is proved.
-\end{proof}
-\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\pi / 2\right]$
-and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
-if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
-then $\theta_{0}<\pi / 4$.\end{thm}
-\begin{proof}
-We are going to prove by contradiction. Suppose $\theta_{0}\ge\pi / 4$,
-we have $\left[0,\theta_{0}\right]\cap\left[\pi / 2-\theta_{0},\pi / 2\right]=\left[\pi / 2-\theta_{0},\theta_{0}\right]\ne\emptyset$.
-Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\theta_{0}\right]\right)$,
-by lemma~\ref{lemma:imposs-imply-same-value}, we have $\imposs=\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]$,
-where $l_{0}\in\left[0,\pi / 2\right]$. A contradiction!
-\end{proof}
-\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left[\arcsin\left(1 / \sqrt{3}\right),\pi / 4\right)$
-and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
-if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
-then $\unknown\in\mathscr{I}$.\end{thm}
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.38]{figureb2.eps} 
-\par\end{centering}
-\caption{\label{fig:three-dimensional-real-frame-2}This figure is used in
-the proof of theorem~\ref{thm:arcsin-one-over-sqrt-three}. The latitude
-of the yellow circle is $\theta_{0}\in\left[\arcsin\left(1 / \sqrt{3}\right),\pi / 4\right)$,
-and the latitude of the green circle is $\pi / 2-\theta_{0}$.}
-\end{figure}
-\begin{proof}
-We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-2},
-where the latitude of of the yellow circle is $\theta_{0}$ and the
-latitude of of the green circle is $\pi / 2-\theta_{0}$. Therefore,
-$\bar{f}$ should map any state above the yellow circle to $\imposs$
-and any states between the green circle and the equator to the same
-interval, say, $\left[l_{0},1-l_{0}\right]$, where $0\le l_{0}\le\frac{1}{2}$
-by lemma~\ref{lemma:imposs-imply-same-value}.
-
-When $\theta_{0}\ge\arcsin\left(1 / \sqrt{3}\right)$, the latitude
-of the green circle is $\theta_{0}\le\pi / 2-\arcsin\left(1 / \sqrt{3}\right)$.
-Now consider three states~$\ket{A}$, $\ket{B}$, and $\ket{C}$
-whose latitude is $\pi / 2-\arcsin\left(1 / \sqrt{3}\right)$
-so that they are below the green circle, and these three states form
-an equilateral triangle whose center is $H$. Since the latitude of
-this triangle is $\pi / 2-\arcsin\left(1 / \sqrt{3}\right)$,
-we know $\overline{OH}=1 / \sqrt{3}$, where $O$ is the center
-of the sphere. By the Pythagorean theorem, $\overline{HA}=\overline{HB}=\sqrt{\frac{2}{3}}$.
-Notice that $\triangle HAB$ is an isosceles triangle with $\angle AHB=2\pi / 3$,
-we have $\overline{AB}=\sqrt{2}$. Since $\overline{OA}=\overline{OB}=1$
-and $\overline{AB}=\sqrt{2}$, $\triangle OAB$ is an isosceles right
-triangle with $\angle AHB=\pi / 2$, i.e., $\ket{A}$ and $\ket{B}$
-are orthogonal. Applying the same reason on all $\ket{A}$, $\ket{B}$,
-and $\ket{C}$, $\left\{ \ket{A},\ket{B},\ket{C}\right\} $ is an
-orthonormal basis.
-
-Since $\left\{ \ket{A},\ket{B},\ket{C}\right\} $ is an orthonormal
-basis and $\bar{f}\left(\ket{A}\right)=\bar{f}\left(\ket{B}\right)=\bar{f}\left(\ket{C}\right)=\left[l_{0},1-l_{0}\right]$,
-we have the following inequalities by theorem~\ref{thm:interval-valued-frame-function},
-\begin{equation}
-\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right]\Rightarrow l_{0}\le0\textrm{ .}
-\end{equation}
-Recall that $0\le l_{0}\le\frac{1}{2}$. Therefore, $l_{0}=0$, that
-is, $\unknown=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$. \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Between Quantum and Classical}
-
-This section discusses the relation between quantum and classical.
-We first prove that any quantum phenomenon would not be observed if
-we could only access commuting projectors since commuting projectors
-could be measured simultaneously~\cite{Mermin_1993}. Based on this
-fact, we show a quantum IVPM~$\bar{\mu}$ is convex if its restriction
-on any orthonormal basis~$\Omega$, $\bar{\mu}^{\Omega}$, is a convex
-classical IVPM. Together with the fact that every classical IVPM~$\bar{\mu}^{\Omega}$
-is convex when the number of elements in $\Omega\le3$, every quantum
-IVPM must be convex on a three-dimensional Hilbert space.
-
-Before diving into the lemmas and proofs, we start from two definitions.
-
-\begin{definition}Given a Hilbert space $\Hilb$, and a set of projections
-$\mathcal{S}\subseteq\events$, we define $\sum_{P\in\mathcal{S}}P=\mathbb{0}$
-when $\mathcal{S}=\emptyset$ since $\mathbb{0}$ is the additive
-identity in operators.\end{definition}
-
-\begin{definition}\label{definition:quantum-classical}Given a Hilbert
-space $\Hilb$ with an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
-\begin{itemize}
-\item For any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
-we define $\mu^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$ by
-$\mu^{\Omega}\left(E\right)=\mu\left(\sum_{\ket{j}\in E}\proj{j}\right)$.
-\item For any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-we define $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ by
-$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)$.
-\end{itemize}
-\end{definition}
-
-\begin{lemma}\label{lemma:classical-probability-measures}$\mu^{\Omega}$
-and $\bar{\mu}^{\Omega}$ in the previous definition are classical
-real-valued and interval-valued probability measures, respectively.\end{lemma}
-
-\begin{proof}When $\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$,
-$\bar{\mu}$ and $\bar{\mu}^{\Omega}$ are essentially quantum and
-classical real-valued probability measures, respectively. Hence, it
-is sufficient to prove the interval-valued case.
-\begin{itemize}
-\item $\bar{\mu}^{\Omega}(\emptyset)=\bar{\mu}\left(\sum_{\ket{j}\in\emptyset}\proj{j}\right)=\bar{\mu}\left(\mathbb{0}\right)=[0,0]$. 
-\item $\bar{\mu}^{\Omega}(\Omega)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)=[1,1]$. 
-\item For any event $E\in2^{\Omega}$,
-\begin{equation}
-\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .}
-\end{equation}
-\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$
-of pairwise disjoint events, we have
-\begin{equation}
-\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}^{\Omega}\left(E_{i}\right)\textrm{ .}
-\end{equation}
-\end{itemize}
-\end{proof}
-
-\begin{definition}\label{def:sub-event-space}Given a Hilbert space
-$\Hilb$, $\events'\subseteq\events$ is called a sub-event space
-if it satisfies the follow conditions.
-\begin{itemize}
-\item $\mathbb{0}\in\events'$.
-\item $\mathbb{1}\in\events'$.
-\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$.
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
-we have $\sum_{i=1}^{N}P_{i}\in\events'$.
-\end{itemize}
-By replacing every occurrence of $\events$ by $\events'$ in definition~\ref{def:QuantumCryptodeterministicMeasures},
-\ref{def:QuantumProbabilitySpace}, and \ref{def:QuantumInterval-valuedProbability},
-it is straightforward to define a quantum cryptodeterministic, real-valued
-probability, and interval-valued probability measure on $\events'$.\end{definition}
-
-\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
-and a mutually commuting sub-event space~$\events'\subseteq\events$,
-there is set~$\Omega$ and a function~$\tau:\events'\rightarrow2^{\Omega}$
-such that:
-\begin{itemize}
-\item If $\mu:\events'\rightarrow\left[0,1\right]$ is a quantum real-valued
-probability measure, then there is a classical real-valued probability
-measure~$\mu':\Omega\rightarrow\left[0,1\right]$ such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
-for all $P\in\events'$.
-\item If $\bar{\mu}:\events'\rightarrow\mathscr{I}$ is a quantum interval-valued
-probability measure, then there is a classical interval-valued probability
-measure~$\bar{\mu}':\Omega\rightarrow\mathscr{I}$ such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
-for all $P\in\events'$
-\end{itemize}
-\end{thm}
-
-\begin{proof}Again, it is sufficient to prove the interval-valued
-case. Since $\events'$ is a set of mutually orthogonal projections,
-they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
-Pick arbitrary projector~$P\in\events'$, its eigenvalues are $0$
-or $1$. Let $\tau\left(P\right)\subseteq\Omega$ be the set of eigenvectors
-whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$.
-By definition~\ref{definition:quantum-classical}, $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
-and $\bar{\mu}^{\Omega}$ is a quantum interval-valued probability
-measure by lemma~\ref{lemma:classical-probability-measures}.\end{proof}
-
-Given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
-if we consider sub-event space generated by $\Omega$, $\events^{\Omega}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
-then any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-restricting on $\events^{\Omega}$, denoted by $\bar{\mu}|_{\events^{\Omega}}$,
-behaves classically. In particular, if $\bar{\mu}$ is convex, each
-$\bar{\mu}|_{\events^{\Omega}}$ is convex and has a non-empty core.
-However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$
-may not be glued together, and gives a core element of $\bar{\mu}$.
-The inability of gluing core elements among commuting $\events^{\Omega}$
-to non-commuting $\events$ is consistent with the idea of the Kochen-Specker
-theorem, that each triple of commuting observables could be colored
-well, but we cannot color all observables which are not all commuting.
-This is also consistent with the assertion that mutually commuting
-observables could be measured simultaneously~\cite{Mermin_1993}.
-In another word, if Alice and Bob in Bell's theorem can only pick
-from a set of mutually commuting observables, they could never observe
-any ``quantum,`` and we cannot eliminate the local hidden variable
-theory in this setting.
-
-The rest of the section focus on convexity.
-
-\begin{lemma}Given a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ are all
-convex for any orthonormal basis~$\Omega$, then $\bar{\mu}$ is
-convex.\end{lemma}
-
-\begin{proof} Pick two commuting events~$P_{0},P_{1}\in\events$.
-Since they are commuting, they can be diagonalized by a common orthonormal
-basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$. Since they
-are projectors, the eigenvalues of them are $0$ or $1$ so that we
-can express them as $P_{0}=\sum_{\ket{j}\in E_{0}}\proj{j}$ and $P_{1}=\sum_{\ket{j}\in E_{1}}\proj{j}$,
-where $E_{0},E_{1}\subseteq\Omega$. Then, 
-\begin{equation}\eqalign{  
-& \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)= \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\\ 
-\subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)= \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ .} 
-}\end{equation}
-\end{proof}
-
-\begin{lemma}When the number of elements in $\Omega$ is less than
-or equal to 3, every classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
-is convex.\end{lemma}
-
-\begin{proof}Given two events~$E_{0},E_{1}\subseteq\Omega$, we
-want to verify 
-\begin{equation}
-\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}\label{eq:classical-convex}
-\end{equation}
-When $E_{0}\cap E_{1}=\emptyset$, equation~(\ref{eq:classical-convex})
-is a special case of equation~(\ref{eq:classical-include}). When
-$E_{0}\cup E_{1}=\Omega$, we have $E_{0}^{c}\cap E_{1}^{c}=\emptyset$,
-where $E_{0}^{c}=\Omega\backslash E_{0}$ and $E_{1}^{c}=\Omega\backslash E_{1}$.
-Thus, 
-\begin{equation}\eqalign{ 
-& \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
-\Rightarrow & \left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
-\Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\
-\Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}
-}\end{equation}
-When the number of elements in $\Omega\le3$, either $E_{0}\cap E_{1}=\emptyset$
-or $E_{0}\cup E_{1}=\Omega$ must happen so that $\bar{\mu}^{\Omega}$
-is convex. \end{proof}
-
-\begin{thm}\label{thm:convex-3}Given a Hilbert space~$\Hilb$ of
-dimension~$3$, every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is convex.\end{thm}
-
-\begin{proof}The direct consequence of the previous lemmas. \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}}
-
-\begin{definition}We say a pair~$\left(\mathscr{I},\iota\right)$
-is regular\footnote{\yutsung{''regular'' is just a random name pop into my mind...
-
-This whole definition might be rewritten using category theory...
-I would investigate it if it is necessary...}} if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-is a function satisfying the following properties. 
-\begin{itemize}
-\item $\iota\left(0\right)=\left[0,0\right]$. 
-\item $\iota\left(1\right)=\left[1,1\right]$. 
-\item For any $x\in\left[0,1\right]$, $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$. 
-\item For a set $\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
-if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota\left(x_{i}\right)$. 
-\end{itemize}
-\end{definition}
-
-\begin{lemma}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
-Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
-a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
-$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM.\end{lemma}
-
-\begin{proof}~
-\begin{itemize}
-\item $\bar{\mu}(\mathbb{0})=\iota\left(\mu(\mathbb{0})\right)=\iota\left(0\right)=\left[0,0\right]$.
-\item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$.
-\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)=\mu\left(\sum_{i=1}^{N}P_{i}\right)\in\left[0,1\right]$
-so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
-\end{itemize}
-\end{proof}
-
-\begin{lemma}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
-Then, there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.\end{lemma}
-
-\begin{proof}Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}(P)\right)$.
-Then, $\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
-i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\bar{\mu}\right)$,
-we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.\end{proof}
-
-\begin{example}\label{ex:regular-pair}For any positive integer~$n$,
-there is a regular pair~$\left(\mathscr{I}_{n},\iota_{n}\right)$
-defined by 
-\begin{equation}\eqalign{ 
-\mathscr{I}_{n} = \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\ 
-\iota_{n}\left(x\right) = \cases{ 
-\left[\frac{k}{n},\frac{k}{n}\right] & , if $x=\frac{k}{n}$ ;\\ 
-\left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
-} 
-}\end{equation}
-Notice that the usual $\left\{ \necess,\imposs,\unknown\right\} $
-is $\mathscr{I}_{1}$. Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
-and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
-$\left(\mathscr{I}_{\infty},\iota_{\infty}\right)$ is a regular pair.\end{example}
-
-\begin{proof}~
-\begin{itemize}
-\item $\iota\left(0\right)=\left[0,0\right]$. 
-\item $\iota\left(1\right)=\left[1,1\right]$. 
-\item When $x=k/n$, we have $\iota\left(1-x\right)=\left[1-k/n,1-k/n\right]=\left[1,1\right]-\iota\left(x\right)$.\\
-When $k/n<x<\left(k+1\right)/n$, we have $1-k/n>1-x>1-\left(k+1\right)/n$
-so that 
-\begin{equation}
-\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)\textrm{ .}
-\end{equation}
-\item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
-if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{1}+x_{2}\right)\subseteq\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$,
-and the rest can be done by the induction. 
-\begin{itemize}
-\item When $x_{1}=k_{1}/n$, we have 
-\begin{equation}
-\iota\left(x_{1}+x_{2}\right)=\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota\left(x_{2}\right)=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .}
-\end{equation}
-\item When $k_{1}/n<x_{1}<\left(k_{1}+1\right)/n$ and $k_{2}/n<x_{2}<\left(k_{2}+1\right)/n$,
-we have 
-\begin{equation}
-\frac{k_{1}+k_{2}}{n}<x_{1}+x_{2}<\frac{k_{1}+k_{2}+2}{n}
-\end{equation}
-so that 
-\begin{equation}\eqalign{ 
-& \iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\ 
-= &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .} 
-}\end{equation}
-\end{itemize}
-\end{itemize}
-\end{proof}
-
-\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
-of dimension~$d\ge3$, there is no quantum interval-valued probability
-measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.\end{cor}
-
-\begin{proof}We are going to prove by contradiction! Suppose there
-is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
-Consider $\mu:\events\rightarrow\left[0,1\right]$ defined by
-\begin{equation} 
-\mu(P)=\cases{ 
-0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
-1 & if $\bar{\mu}(P)=\necess$ .
-}\end{equation}
-We are going to verify that $\mu$ is a cryptodeterministic measure
-so that contradicts to the Kochen-Specker theorem.
-\begin{itemize}
-\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
-\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
-\item For every event $P$, we have 
-\begin{equation}\eqalign{ 
-& \pmeas\left(P\right)=0\\ 
-\Rightarrow & \bar{\mu}(P)=\imposs\\
-\Rightarrow & \bar{\mu}(\Omega\backslash P)=\left[1,1\right]-\imposs=\necess\\
-\Rightarrow & \pmeas\left(\Omega\backslash P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
-}\end{equation}
-Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$.
-\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
-disjoint events. 
-\begin{itemize}
-\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1$, then we have $\necess=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
-so that $\necess=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=1=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
-\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0$, then we have $\imposs=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
-so that $\imposs=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=0=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
-\end{itemize}
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.38]{figureE1} 
-\par\end{centering}
-\caption{\label{fig:three-dimensional-5-value}This figure illustrates cases
-1 and 2 of example~\ref{ex:three-dimensional-5-value} plotted in
-$\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
-and $\ket{\ps}$ respectively. All possible real vectors of the subspaces
-orthogonal to $\ket{0}$ or $\ket{\ps}$ are drawn in the red and
-green circles, respectively.}
-\end{figure}
-
-\begin{example}[Three-dimensional quantum 5-interval-valued probability
-measure]\label{ex:three-dimensional-5-value} Given a three dimensional
-Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let\emph{ }$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, and
-$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess,\midd\right\} $,
-where $\midd$ represents $\left[\frac{1}{4},\frac{3}{4}\right]$.
-The definition of $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-5-value}
-which plots the 1-dimensional projectors: 
-\begin{enumerate}
-\item Let: 
-\begin{equation}\eqalign{ 
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,} 
-}\end{equation}
-where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green
-dotted vectors, respectively. 
-\item The red and green circles are the states orthogonal to $\ket{0}$
-and $\ket{\ps}$, respectively. We define $\bar{\mu}\left(\proj{\psi}\right)=\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\midd$,
-where $\ip{\psi}{0}=0$ or $\ip{\psi}{\ps}=0$.
-\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
-\end{enumerate}
-By theorem~\ref{thm:interval-valued-frame-function}, to check $\bar{\mu}$
-a quantum interval-valued probability measure is equivalent to check
-$\bar{f}$ satisfying 
-\begin{equation}\eqalign{ 
-\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)\subseteq\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)\subseteq\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)\subseteq\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)
-}\label{eq:non-additive-vectors}\end{equation}
-for every orthonormal basis~$\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $,
-where $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
-We are going to enumerate all possible orthonormal bases to verify
-equation~(\ref{eq:non-additive-vectors}). Also, to simplify the
-notation, we denote $\set{\ket{\psi}}{\ip{\psi}{0}\ne0\textrm{ and }\ip{\psi}{\ps}\ne0}$
-by $\mathcal{T}$.
-\begin{enumerate}
-\item When $\ket{\psi_{0}}$ is $\ket{0}$, then $\ip{\psi_{1}}{0}=\ip{\psi_{2}}{0}=0$.
-Equation~(\ref{eq:non-additive-vectors}) can then be verified as
-follow. 
-\begin{equation}\eqalign{ 
-\left[1,1\right]-\bar{f}\left(\ket{0}\right)=\necess\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\midd=\midd+\imposs=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{0}\right)\textrm{ ,}
-}\end{equation}
-Similarly, when $\ket{\psi_{0}}$ is $\ket{\ps}$, equation~(\ref{eq:non-additive-vectors})
-holds. 
-\item When $\ip{\psi_{0}}{0}=\ip{\psi_{1}}{\ps}=0$ and $\ket{\psi_{2}}\in\mathcal{T}$,
-we have 
-\begin{equation}\eqalign{ 
-\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\midd+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)=\likely\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)\textrm{ .}
-}\end{equation}
-\item When $\ip{\psi_{0}}{0}=0$, and $\ket{\psi_{1}}$, $\ket{\psi_{2}}\in\mathcal{T}$,
-we have 
-\begin{equation}\eqalign{ 
-\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\likely\subseteq\unlikely+\midd=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ .}
-}\end{equation}
-Similarly, when $\ip{\psi_{0}}{\ps}=0$, $\ket{\psi_{1}}\in\mathcal{T}$,
-and $\ket{\psi_{2}}\in\mathcal{T}$, equation~(\ref{eq:non-additive-vectors})
-holds. 
-\item When $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}\in\mathcal{T}$,
-i.e., the ``otherwise'' case. Then, equation~(\ref{eq:non-additive-vectors})
-can easily be verified. 
-\begin{equation}
-\left[1,1\right]-\bar{f}\left(\ket{\psi_{0}}\right)=\likely\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_{1}}\right)+\bar{f}\left(\ket{\psi_{2}}\right)\textrm{ .}
-\end{equation}
-\end{enumerate}
-Since we proved that $\bar{\mu}$ is a quantum interval-valued probability
-measure, $\bar{\mu}$ is convex by theorem~\ref{thm:convex-3}.
-
-The following argument establishes that $\bar{\mu}$ has an empty
-core. Assume there is a real-valued probability measure satisfying
-$\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$ for all $P\in\events$. Because
-$\mu_{\rho}^{\mathrm{B}}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$ and $\mu_{\rho}^{\mathrm{B}}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
-we must have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-so that $\mu_{\rho}^{\mathrm{B}}=\mu_{\ket{2}}^{\mathrm{B}}$. However, 
-\begin{equation}
-\mu_{\ket{2}}^{\mathrm{B}}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
-\end{equation}
-\end{example}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Contextuality and the Born Rule in Fuzzy Quantum Theories\label{sec:MerminSquare}}
-
-\footnote{This section will be singled out as a separated letter.}The
+The
 Kochen-Specker theorem asserts that there is no function~$v$ assigning

### 2017-03-13 prop_letter.tex
prop_letter.tex Put the Introduction back...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+
+Textbook quantum mechanics asserts that, given a quantum spin system
+described by the wave function
+$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
+and given the observable
+$S_z =
+\frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
+then the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$
+(with post-measurement state $\fket{\ps\frac{1}{2}}$) is
+$\frac{\pi}{4}$ and the probability of observing the eigenvalue
+$\minus\frac{\hbar}{2}$ (with post-measurement state
+$\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
+frequency interpretation of probability, the above assertion implies
+that when performing a very large number of experiments on quantum
+systems described by wave function $\ket{\psi}$, a fraction
+$\frac{\pi}{4}$ of the experiments will result in the observation
+$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
+result in the observation $\minus\frac{\hbar}{2}$.
+
+In reality, i.e., in an actual experiment, simulation, or computation,
+bounded by space, time, and energy resources, the situation is much
+fuzzier: (i) we cannot \emph{exactly} prepare the state $\ket{\psi}$;
+(ii) we cannot build a measurement apparatus corresponding
+\emph{exactly} to observable $S_z$; and (iii) we cannot prepare
+\emph{exact} replicas of any state. In other words, we can only
+perform a limited number of experiments on quantum systems closely
+related to wave function $\ket{\psi}$ and using an apparatus that
+closely approximates observable $S_z$. Given any fixed resources,
+these experiments will \emph{not} result in the \emph{exact} fraction
+$\frac{\pi}{4}$ of observations $\ps\frac{\hbar}{2}$ and
+$1-\frac{\pi}{4}$ of observations $\minus\frac{\hbar}{2}$. In fact,
+these experiments can be viewed as a method (algorithm) to calculate
+the value $\pi$ and it is known that the state of the art algorithms
+for computing the $n$th binary digit of~$\pi$ require on the order of
+$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
+operations~\cite{journals/moc/BaileyBP97}. In other words, calculating
+the $n$th digit of $\pi$ appears to require more and more physical
+resources as~$n$ gets larger.
+
+All of this is well-known and holds in both the classical and quantum
+worlds. In the classical world, these observations are believed to be
+well-understood approximations to an idealized independent reality
+that can continuously approached with more and more resources. The
+question in the quantum world is more subtle; it is not evident at all
+that this resource-aware perspective does not alter the very
+foundations of quantum mechanics. Indeed taking such resource bounds
+into consideration is what founded computer science as a discipline
+and has become crucial for understanding the very nature of
+computation. Following Feynman~\cite{Feynman1982Simulating},
+Landauer~\cite{Landauer1996188}, and others, one might argue that this
+resource-bounded perspective is also crucial for understanding the
+very nature of physical processes.
+
+In previous work, we analyzed the wave function description of quantum
+systems from a resource-bounded perspective. Technically, instead of
+postulating that quantum states are rays in a Hilbert space, i.e., we
+instead used special finite fields whose size reflected the available
+resources. \ldots
+
+\newpage
+
 The

### 2017-03-14 prop_letter.tex
prop_letter.tex Follow "REVTEX 4.1 Author's Guide" to revise the file

@@
-\documentclass[12pt]{iopart}
-\usepackage[ backend=biber]{biblatex}
+\documentclass[reprint, aps, prl,superscriptaddress, showpacs,
+showkeys]{revtex4-1} 
+\let\bibhang\relax
+\let\citename\relax
+\let\bibfont\relax
+\let\Citeauthor\relax
+\let\textcite\relax
+\makeatletter
+\DeclareRobustCommand{\MakeUppercase}[1]{{%
+      \def\i{I}\def\j{J}%
+      \def\reserved@a##1##2{\let##1##2\reserved@a}%
+      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
+      \protected@edef\reserved@a{\uppercase{#1}}%
+      \reserved@a
+   }}
+\DeclareRobustCommand{\MakeLowercase}[1]{{%
+      \def\reserved@a##1##2{\let##2##1\reserved@a}%
+      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
+      \protected@edef\reserved@a{\lowercase{#1}}%
+      \reserved@a
+   }}
+\makeatother
+\expandafter\let\csname ver@natbib.sty\endcsname\relax
+\renewcommand{\bibliography}[1]{}
+\usepackage[ backend=biber,style=phys]{biblatex}
 \addbibresource{prop.bib}
@@
 \usepackage[utf8]{inputenc}
+\usepackage{amsmath}
 \usepackage{amssymb}
@@
 \usepackage{verbatim}
-\usepackage{iopams}
-\usepackage{setstack}
+\usepackage{hyperref}
 
@@
 \begin{document}
-\letter{Contextuality and the Born Rule in Fuzzy Quantum Theories}
 
-\author{Andrew J Hanson$^{1}$, Gerardo Ortiz$^{2}$,
-Amr Sabry$^{1}$ and Yu-Tsung Tai$^{3,1}$}
-\address{$^{1}$ School of Informatics and Computing, Indiana
-University, Bloomington, IN 47405, USA}
-\address{$^{2}$ Department of Physics, Indiana University, Bloomington, IN
-47405, USA}
-\address{$^{3}$ Department of Mathematics, Indiana University, Bloomington,
+\title{Contextuality and the Born Rule in Fuzzy Quantum Theories}
+
+\author{Andrew J Hanson}
+\affiliation{School of Informatics and Computing, Indiana University, Bloomington,
 IN 47405, USA}
-\ead{ortizg@indiana.edu}
-\begin{abstract}
-\today
-\end{abstract}
+
+\author{Gerardo Ortiz}
+\affiliation{Department of Physics, Indiana University, Bloomington, IN 47405,
+USA}
+
+\author{Amr Sabry}
+\affiliation{School of Informatics and Computing, Indiana University, Bloomington,
+IN 47405, USA}
+
+\author{Yu-Tsung Tai}
+\affiliation{Department of Mathematics, Indiana University, Bloomington, IN 47405,
+USA}
+\affiliation{School of Informatics and Computing, Indiana University, Bloomington,
+IN 47405, USA}
+
+\date{\today }
+
 \pacs{03.65.-w, 03.65.Ta, 02.40.Dr, 02.50.Cw, 02.50.Le}
-\noindent{\it Keywords\/}: {Finite precision measurement, the Born rule, Gleason's theorem, interval-valued
-probability, discrete quantum theory}
 
-\submitto{\jpa}
+\keywords{Finite precision measurement, the Born rule, Gleason's
+theorem, interval-valued probability, discrete quantum theory}
+
+\maketitle
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
 Textbook quantum mechanics asserts that, given a quantum spin system
@@
 a definitely value to all observables such that
-\begin{equation}\eqalign{ 
+\begin{eqnarray}
 v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
 v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
-}\label{eq:Kochen-Specker-Rules}\end{equation}
+\label{eq:Kochen-Specker-Rules}\end{eqnarray}
 if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
@@
 as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}
-
+\begin{ruledtabular}
 \begin{tabular}{ccc|cccc} 
-\br 
 \multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
-\mr 
 $\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
@@
 $\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
-\br 
 \end{tabular} 
+\end{ruledtabular}
 \end{table}
@@
 which should at least satisfy
-\begin{equation}\eqalign{ 
+\begin{eqnarray}
 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
 1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
-}\label{eq:Kernaghan-1}\end{equation}
+\label{eq:Kernaghan-1}\end{eqnarray}
 because of table~\ref{table:commonBasis}. $f$ should also satisfy
@@
 orthogonal basis~\cite{Kernaghan1994,peres1995quantum}:
-\begin{equation}\eqalign{ 
+\begin{eqnarray}
 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
@@
 1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
-}\label{eq:Kernaghan-2}\end{equation}
+\label{eq:Kernaghan-2}\end{eqnarray}
 In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
@@
 \begin{equation} 
-\iota_1(x)=\cases{ 
-\necess & if $x=1$ ;\\ 
-\imposs & if $x=0$ ;\\ 
-\unknown & otherwise. 
-}\label{eq:homomorphism-1} \end{equation}
+\iota_1(x)=\begin{cases} 
+\necess & \text{ if}x=1\text{ ;}\\ 
+\imposs & \text{ if}x=0\text{ ;}\\ 
+\unknown & \text{ otherwise.}
+\end{cases}\label{eq:homomorphism-1} \end{equation}
 We still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.
@@
 $f$ should also satisfy the following equations: 
-\begin{equation}\eqalign{ 
+\begin{eqnarray}
 1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
@@
 1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
-}\label{eq:non-Kernaghan}\end{equation}
+\label{eq:non-Kernaghan}\end{eqnarray}
 \qed\end{example}
@@
 as follow. 
-\begin{equation}\eqalign{ 
+\begin{eqnarray}
 \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
@@
 \bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
-}\end{equation}
+\end{eqnarray}
 To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
@@
 it is sufficient to check
-\begin{equation}\eqalign{ 
+\begin{eqnarray}
 \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
 \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
-}\end{equation}
+\end{eqnarray}
 for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}$.

### 2017-03-14 prop_letter.tex
prop_letter.tex Fix a bug according to https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib/37077#37077
prop_letter.tex Went through "REVTeX 4.1 Author's Guide"

@@
 showkeys]{revtex4-1} 
+% Follow 
+% https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib/37077#37077
+% to put RevTeX with BibLaTeX
 \let\bibhang\relax
@@
 \expandafter\let\csname ver@natbib.sty\endcsname\relax
-\renewcommand{\bibliography}[1]{}
 \usepackage[ backend=biber,style=phys]{biblatex}
@@
 \begin{document}
+\renewcommand{\bibliography}[1]{}
 
@@
 theorem, interval-valued probability, discrete quantum theory}
+
+\begin{abstract}
+\begin{description}
+\item[Background] This paper wants to understand the quantum measurement in the
+bounded resource.
+\item[Purpose] ?
+\item[Method] We replace quantum real-valued probability measures by
+interval-valued ones whose range can be restricted to finite number of
+intervals representing finite precision measurement.
+\item[Results] Quantum interval-valued probability measures provide a unified
+framework to interpret the Kochen-Specker theorem and Gleason's theorem. We also
+found some legitimate quantum interval-valued probability measures which cannot
+be explained by the Born rule.
+\item[Conclusions] Our research provide a new insight of the role of finite
+precision measurement when formulate quantum theory.
+\end{description}
+\end{abstract}
 
@@
 \begin{eqnarray}
-v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
-v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
+& & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
+& & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
 \label{eq:Kochen-Specker-Rules}\end{eqnarray}
@@
 
-\begin{table}
+\begin{table*}
 \caption{\label{table:commonBasis}In each row, three observables are listed
@@
 \multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
+\hline
 $\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
@@
 \end{ruledtabular}
-\end{table}
+\end{table*}
 Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
@@
 \begin{eqnarray}
-1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
-1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
+& & 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
+& & 1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
 \label{eq:Kernaghan-1}\end{eqnarray}
@@
 \begin{eqnarray}
-1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
-1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
-1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
-1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
-1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
-1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
-1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
-1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
-1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
+& & 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
+& & 1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
+& & 1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
+& & 1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
+& & 1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
+& & 1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
+& & 1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
+& & 1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
+& & 1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
 \label{eq:Kernaghan-2}\end{eqnarray}
@@
 \begin{eqnarray}
-1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
-1 = f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
-1 = f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
-1 = f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
-1 = f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1)+f(1,1,-1,-1)\textrm{ ,}\\ 
-1 = f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
-1 = f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
-1 = f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,0,0)\textrm{ ,}\\ 
-1 = f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1)+f(1,1,0,0)\textrm{ ,}\\ 
-1 = f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0)+f(1,1,1,-1)\textrm{ ,}\\ 
-1 = f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1)+f(1,1,1,-1)\textrm{ ,}\\ 
-1 = f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0)+f(1,1,1,1)\textrm{ ,}\\ 
-1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
+& & 1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
+& & 1 = f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
+& & 1 = f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
+& & 1 = f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
+& & 1 = f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1)+f(1,1,-1,-1)\textrm{ ,}\\ 
+& & 1 = f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
+& & 1 = f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
+& & 1 = f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,0,0)\textrm{ ,}\\ 
+& & 1 = f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1)+f(1,1,0,0)\textrm{ ,}\\ 
+& & 1 = f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0)+f(1,1,1,-1)\textrm{ ,}\\ 
+& & 1 = f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1)+f(1,1,1,-1)\textrm{ ,}\\ 
+& & 1 = f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0)+f(1,1,1,1)\textrm{ ,}\\ 
+& & 1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
 \label{eq:non-Kernaghan}\end{eqnarray}
@@
 \begin{eqnarray}
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
-\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
+& & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
+& & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
+& & \bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
 \end{eqnarray}
@@
 \begin{eqnarray}
-\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
-\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
+& & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
+& & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
 \end{eqnarray}

### 2017-03-15 prop_letter.tex
prop_letter.tex \begin{abstract} Updating...

@@
 \begin{description}
-\item[Background] This paper wants to understand the quantum measurement in the
-bounded resource.
-\item[Purpose] ?
+\item[Background] In a world of bounded resource, the quantum theory should
+base on only finite precision measurement.
+\item[Purpose] This paper wants to understand the finite precision quantum
+measurement.
 \item[Method] We replace quantum real-valued probability measures by
 interval-valued ones whose range can be restricted to finite number of
-intervals representing finite precision measurement.
+intervals.
 \item[Results] Quantum interval-valued probability measures provide a unified
@@
 be explained by the Born rule.
-\item[Conclusions] Our research provide a new insight of the role of finite
-precision measurement when formulate quantum theory.
+\item[Conclusions] Our research provides a new insight of the role of
+measurement when formulating quantum theory.
 \end{description}

### 2017-03-15 prop_letter.tex
prop_letter.tex Updating BibLaTeX according to "biblatex-phys – A biblatex implementation of the aip and aps bibliography style"
prop_letter.tex Modifying according to "Physical Review Style and Notation Guide"...

--- 2017-03-14 prop_letter.tex
@@
 \expandafter\let\csname ver@natbib.sty\endcsname\relax
-\usepackage[ backend=biber,style=phys]{biblatex}
+\usepackage[ backend=biber,style=phys,%
+articletitle=false,biblabel=brackets,%
+chaptertitle=false,pageranges=false%
+]{biblatex}
 \addbibresource{prop.bib}
-\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
+\ExecuteBibliographyOptions{sorting=none,doi=false,isbn=false,url=false}
 \usepackage{fullpage}
@@
 
-\title{Contextuality and the Born Rule in Fuzzy Quantum Theories}
+\title{Contextuality and the Born rule in fuzzy quantum theories}
 
@@
 
-\date{\today }
-
-\pacs{03.65.-w, 03.65.Ta, 02.40.Dr, 02.50.Cw, 02.50.Le}
-
-\keywords{Finite precision measurement, the Born rule, Gleason's
-theorem, interval-valued probability, discrete quantum theory}
+\date{\today}
 
@@
 \begin{description}
-\item[Background] This paper wants to understand the quantum measurement in the
-bounded resource.
-\item[Purpose] ?
-\item[Method] We replace quantum real-valued probability measures by
-interval-valued ones whose range can be restricted to finite number of
-intervals representing finite precision measurement.
+\item[Background] In a world of bounded resource, any quantum measurement can
+be only performed in finite precision.
+\item[Method] We model idea of the finite precision measurement as finite number
+of intervals, and the replace quantum real-valued probability measures by
+interval-valued ones.
 \item[Results] Quantum interval-valued probability measures provide a unified
-framework to interpret the Kochen-Specker theorem and Gleason's theorem. We also
-found some legitimate quantum interval-valued probability measures which cannot
-be explained by the Born rule.
-\item[Conclusions] Our research provide a new insight of the role of finite
-precision measurement when formulate quantum theory.
+framework to interpret the Kochen-Specker theorem and Gleason's theorem as
+two limit cases. For the cases between them, we found some legitimate quantum
+interval-valued probability measures which cannot be explained by the Born rule.
+While restricting to only commuting projectors, the interval-valued probability
+measures become classical, and these non-Born interval-valued probability
+measures disappear.
+\item[Conclusions] Our research provides a new insight of finite precision
+measurement and non-commutativity when formulating quantum theory.
 \end{description}
 \end{abstract}
+
+\pacs{03.65.Ta, 03.67.-a, 02.50.Cw, 02.50.Le}
+
+\keywords{Finite precision measurement, the Born rule, Gleason's
+theorem, the Kochen-Specker theorem, interval-valued probability measure,
+discrete quantum theory}
 

### 2017-03-17 prop_letter.tex
prop_letter.tex Give up bibLaTeX, roll back to bibTeX...
prop_letter.tex Updating...

@@
 showkeys]{revtex4-1} 
-% Follow 
-% https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib/37077#37077
-% to put RevTeX with BibLaTeX
-\let\bibhang\relax
-\let\citename\relax
-\let\bibfont\relax
-\let\Citeauthor\relax
-\let\textcite\relax
-\makeatletter
-\DeclareRobustCommand{\MakeUppercase}[1]{{%
-      \def\i{I}\def\j{J}%
-      \def\reserved@a##1##2{\let##1##2\reserved@a}%
-      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
-      \protected@edef\reserved@a{\uppercase{#1}}%
-      \reserved@a
-   }}
-\DeclareRobustCommand{\MakeLowercase}[1]{{%
-      \def\reserved@a##1##2{\let##2##1\reserved@a}%
-      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
-      \protected@edef\reserved@a{\lowercase{#1}}%
-      \reserved@a
-   }}
-\makeatother
-\expandafter\let\csname ver@natbib.sty\endcsname\relax
-\usepackage[ backend=biber,style=phys,%
-articletitle=false,biblabel=brackets,%
-chaptertitle=false,pageranges=false%
-]{biblatex}
-\addbibresource{prop.bib}
-\ExecuteBibliographyOptions{sorting=none,doi=false,isbn=false,url=false}
 \usepackage{fullpage}
@@
 \begin{document}
-\renewcommand{\bibliography}[1]{}
 
@@
 \begin{abstract}
+~
 \begin{description}
-\item[Background] In a world of bounded resource, any quantum measurement can
-be only performed in finite precision.
-\item[Method] We model idea of the finite precision measurement as finite number
-of intervals, and the replace quantum real-valued probability measures by
-interval-valued ones.
-\item[Results] Quantum interval-valued probability measures provide a unified
-framework to interpret the Kochen-Specker theorem and Gleason's theorem as
-two limit cases. For the cases between them, we found some legitimate quantum
-interval-valued probability measures which cannot be explained by the Born rule.
-While restricting to only commuting projectors, the interval-valued probability
-measures become classical, and these non-Born interval-valued probability
-measures disappear.
-\item[Conclusions] Our research provides a new insight of finite precision
-measurement and non-commutativity when formulating quantum theory.
+\item [{Background}] In a world of bounded resource, any quantum measurement
+can be only performed in finite precision. {\small \par}
+\item [{Method}] We model idea of the finite precision measurement as finite
+number of intervals, and replace quantum real-valued probability measures
+by interval-valued ones. {\small \par}
+\item [{Results}] Quantum interval-valued probability measures provide
+a unified framework to interpret the Kochen-Specker theorem and Gleason's
+theorem as two limit cases. For the cases between them, we found some
+legitimate quantum interval-valued probability measures which cannot
+be explained by the Born rule. While restricting on only commuting
+projectors, the interval-valued probability measures become classical,
+and these non-Born interval-valued probability measures disappear. {\small \par}
+\item [{Conclusions}] Our research provides a new insight of finite precision
+measurement and non-commutativity when formulating quantum theory. {\small \par}
 \end{description}
@@
 
-The
-Kochen-Specker theorem asserts that there is no function~$v$ assigning
-a definitely value to all observables such that
+Textbook quantum mechanics asserts that the probability of a measurement
+can be computed from wave function of the system and the measuring
+observable \emph{exactly}.
+
+The Kochen-Specker theorem asserts that there is no function~$v$
+assigning a definitely value to all observables such that 
 \begin{eqnarray}
  &  & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
-& & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
-\label{eq:Kochen-Specker-Rules}\end{eqnarray}
+ &  & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)\label{eq:Kochen-Specker-Rules}
+\end{eqnarray}
 if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
 is a function~$v$ satisfying these two properties, it must send
-an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+an observable to its eigenvalues so that the following observables~\citep{Mermin1990Simple,peres1995quantum}:
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment}
- \bibliographystyle{plain}
 \bibliography{prop}
-\end{comment}
-\printbibliography
 

### 2017-03-17 prop_letter.tex
prop_letter.tex Updating Intorduction...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Textbook quantum mechanics asserts that, given a quantum spin system
-described by the wave function
-$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
-and given the observable
-$S_z =
-\frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
-then the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$
-(with post-measurement state $\fket{\ps\frac{1}{2}}$) is
-$\frac{\pi}{4}$ and the probability of observing the eigenvalue
-$\minus\frac{\hbar}{2}$ (with post-measurement state
-$\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
-frequency interpretation of probability, the above assertion implies
-that when performing a very large number of experiments on quantum
-systems described by wave function $\ket{\psi}$, a fraction
-$\frac{\pi}{4}$ of the experiments will result in the observation
-$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
-result in the observation $\minus\frac{\hbar}{2}$.
-
-In reality, i.e., in an actual experiment, simulation, or computation,
-bounded by space, time, and energy resources, the situation is much
-fuzzier: (i) we cannot \emph{exactly} prepare the state $\ket{\psi}$;
-(ii) we cannot build a measurement apparatus corresponding
-\emph{exactly} to observable $S_z$; and (iii) we cannot prepare
-\emph{exact} replicas of any state. In other words, we can only
-perform a limited number of experiments on quantum systems closely
-related to wave function $\ket{\psi}$ and using an apparatus that
-closely approximates observable $S_z$. Given any fixed resources,
-these experiments will \emph{not} result in the \emph{exact} fraction
-$\frac{\pi}{4}$ of observations $\ps\frac{\hbar}{2}$ and
-$1-\frac{\pi}{4}$ of observations $\minus\frac{\hbar}{2}$. In fact,
-these experiments can be viewed as a method (algorithm) to calculate
-the value $\pi$ and it is known that the state of the art algorithms
-for computing the $n$th binary digit of~$\pi$ require on the order of
-$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
-operations~\cite{journals/moc/BaileyBP97}. In other words, calculating
-the $n$th digit of $\pi$ appears to require more and more physical
-resources as~$n$ gets larger.
-
-All of this is well-known and holds in both the classical and quantum
-worlds. In the classical world, these observations are believed to be
-well-understood approximations to an idealized independent reality
-that can continuously approached with more and more resources. The
-question in the quantum world is more subtle; it is not evident at all
-that this resource-aware perspective does not alter the very
-foundations of quantum mechanics. Indeed taking such resource bounds
-into consideration is what founded computer science as a discipline
-and has become crucial for understanding the very nature of
-computation. Following Feynman~\cite{Feynman1982Simulating},
-Landauer~\cite{Landauer1996188}, and others, one might argue that this
-resource-bounded perspective is also crucial for understanding the
-very nature of physical processes.
+Textbook quantum mechanics asserts that the probability of a measurement
+can be computed from wave function of the system and the measuring
+observable \emph{exactly}. In reality, an actual experiment is bounded
+by space, time, energy, and other resources so that an perfect measurement
+cannot be performed, and real measurements must be finite precision.
+However, it is not evident at all that this resource-aware perspective
+does not alter the very foundations of quantum mechanics. Indeed taking
+such resource bounds into consideration is what founded computer science
+as a discipline and has become crucial for understanding the very
+nature of computation. Following Feynman~\citep{Feynman1982Simulating},
+Landauer~\citep{Landauer1996188}, and others, one might argue that
+this resource-bounded perspective is also crucial for understanding
+the very nature of physical processes.
 
 In previous work, we analyzed the wave function description of quantum
-systems from a resource-bounded perspective. Technically, instead of
-postulating that quantum states are rays in a Hilbert space, i.e., we
-instead used special finite fields whose size reflected the available
-resources. \ldots
-
-\newpage
-
-Textbook quantum mechanics asserts that the probability of a measurement
-can be computed from wave function of the system and the measuring
-observable \emph{exactly}.
+systems from a resource-bounded perspective. Technically, instead
+of postulating that quantum states are rays in a Hilbert space, i.e.,
+we instead used special finite fields whose size reflected the available
+resources. \ldots{}
 

### 2017-03-19 prop_letter.tex
prop_letter.tex Updating...

@@
 cannot be performed, and real measurements must be finite precision.
+Following Feynman~\citep{Feynman1982Simulating}, Landauer~\citep{Landauer1996188},
+and others, one might argue that this resource-bounded perspective
+is also crucial for understanding the very nature of physical processes.
 However, it is not evident at all that this resource-aware perspective
-does not alter the very foundations of quantum mechanics. Indeed taking
-such resource bounds into consideration is what founded computer science
-as a discipline and has become crucial for understanding the very
-nature of computation. Following Feynman~\citep{Feynman1982Simulating},
-Landauer~\citep{Landauer1996188}, and others, one might argue that
-this resource-bounded perspective is also crucial for understanding
-the very nature of physical processes.
+does not alter the very foundations of quantum mechanics.
 
-In previous work, we analyzed the wave function description of quantum
-systems from a resource-bounded perspective. Technically, instead
-of postulating that quantum states are rays in a Hilbert space, i.e.,
-we instead used special finite fields whose size reflected the available
-resources. \ldots{}
+In conventional quantum theory, when we measure a system described
+by a state~$\ket{\phi}$ with respect to an observable~$\mathbf{O}$,
+the probability of getting a eigenvalue~$\lambda$ is completely
+determined by $\ket{\phi}$ and the eigenspace of $\lambda$, $S_{\lambda}$.
+If we denote the projector to $S_{\lambda}$ as $P_{\lambda}$, the
+probability of getting $\lambda$ can be computed by the Born rule~$\mu_{\phi}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\ip{\phi}{P_{\lambda}\phi}$.
+In another word, any state~$\ket{\phi}$ defines a quantum probability
+measure~$\mu_{\phi}^{\mathrm{\mathrm{B}}}:\events\rightarrow[0,1]$,
+where $\events$ is the set of all projectors in a Hilbert space.
+Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
+which should satisfy:
+\begin{itemize}
+\item $\mu(\mathbb{0})=0$. 
+\item $\mu(\mathbb{1})=1$. 
+\item For any projection $P$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$. 
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have $\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)$. 
+\end{itemize}
+The Gleason's theorem asserts that there exists a unique mixed state~$\rho$
+such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$ in a Hilbert space
+$\Hilb$ of dimension $d\geq3$.
+
+\paragraph{Gleason's Theorem}
+
+\paragraph{The Kochen-Specker Theorem}
 

### 2017-03-19 prop_letter.tex
prop_letter.tex \paragraph{Gleason's Theorem} Updating...

@@
 
+\paragraph{Gleason's Theorem}
+
 In conventional quantum theory, when we measure a system described
-by a state~$\ket{\phi}$ with respect to an observable~$\mathbf{O}$,
-the probability of getting a eigenvalue~$\lambda$ is completely
-determined by $\ket{\phi}$ and the eigenspace of $\lambda$, $S_{\lambda}$.
-If we denote the projector to $S_{\lambda}$ as $P_{\lambda}$, the
-probability of getting $\lambda$ can be computed by the Born rule~$\mu_{\phi}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\ip{\phi}{P_{\lambda}\phi}$.
-In another word, any state~$\ket{\phi}$ defines a quantum probability
-measure~$\mu_{\phi}^{\mathrm{\mathrm{B}}}:\events\rightarrow[0,1]$,
+by a density matrix~$\rho$ with respect to an observable~$\mathbf{O}$,
+$\rho$ and the eigenspace of a eigenvalue~$\lambda$ completely
+determines the probability of getting $\lambda$, which is computed
+by the Born rule~$\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
+where $P_{\lambda}$ denotes the projector to the eigenspace of $\lambda$.
+In another word, any density matrix~$\rho$ defines a quantum probability
+measure~$\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow[0,1]$,
 where $\events$ is the set of all projectors in a Hilbert space.
@@
 \end{itemize}
-The Gleason's theorem asserts that there exists a unique mixed state~$\rho$
+Gleason's theorem asserts that there exists a unique mixed state~$\rho$
 such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$ in a Hilbert space
-$\Hilb$ of dimension $d\geq3$.
+of dimension $d\geq3$.
 
-\paragraph{Gleason's Theorem}
+\paragraph{Quantum Interval-valued Probability Measure (IVPM)}
 

### 2017-03-19 prop_letter.tex
prop_letter.tex Fix a typo...
prop_letter.tex \paragraph{Quantum Interval-valued Probability Measure (IVPM)} Updating...

@@
 \def\C{{\mathbb{C}}}
+\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
 
@@
 \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have $\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)$. 
+we have 
+\begin{equation}
+\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
+\end{equation}
 \end{itemize}
@@
 \paragraph{Quantum Interval-valued Probability Measure (IVPM)}
+
+In order to model the idea of finite precision measurement, we replace
+the range of $\mu$ from the infinity precision~$[0,1]$ to a collection
+of finite number of intervals~$\mathscr{I}$, and consider a quantum
+IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. It is intuitive
+to consider $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$
+and to define $\left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]$
+and $[l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]$ so that
+$\bar{\mu}$ satisfy
+\begin{itemize}
+\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
+\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
+\item For any projection $P$, 
+\begin{equation}
+\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
+\end{equation}
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have 
+\begin{equation}
+\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\end{equation}
+\end{itemize}
+Notice that Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
+to inclusion. This becomes intuitive if we compare each terms in two
+sides of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement}).
+Although we have $\mathbb{1}=\left(\mathbb{1}-P\right)+P$, but when
+$r>l$, the left-hand side~$\bar{\mu}(\mathbb{1})=\left[1,1\right]$
+is a proper subset of the right-hand side~$\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$.
+Then, Gleason's theorem can be expressed as the limit case when the
+collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
+In the next paragraph, we will show the Kochen-Specker theorem is
+another limit case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
 

### 2017-03-20 prop_letter.tex
prop_letter.tex Updating after meet with Prof. Ortiz...

@@
 \begin{abstract}
-~
 \begin{description}
@@
 \item [{Results}] Quantum interval-valued probability measures provide
-a unified framework to interpret the Kochen-Specker theorem and Gleason's
-theorem as two limit cases. For the cases between them, we found some
-legitimate quantum interval-valued probability measures which cannot
-be explained by the Born rule. While restricting on only commuting
+a unified framework to interpret Gleason's theorem and the Kochen-Specker
+theorem on an equal footing. For the cases between them, we found
+some legitimate quantum interval-valued probability measures which
+cannot be explained by the Born rule. While restricting on only commuting
 projectors, the interval-valued probability measures become classical,
@@
 \item [{Conclusions}] Our research provides a new insight of finite precision
-measurement and non-commutativity when formulating quantum theory. {\small \par}
+measurement and non-commutativity when formulating quantum theory,
+and the Born rule may not be as nature as we used to believe in the
+world of finite resource.{\small \par}
 \end{description}
@@
 However, it is not evident at all that this resource-aware perspective
-does not alter the very foundations of quantum mechanics.
+does not alter the very foundations of quantum mechanics. In order
+to analyze the quantum world with finite resource, we extend the classical
+interval-valued probability measure (IVPM)~\citep{JamisonLodwick2004},
+and introduce a new framework: quantum IVPM...\newpage{}
 
@@
 another limit case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
+where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}
 

### 2017-03-20 prop_letter.tex
prop_letter.tex \begin{abstract} Small modification...

@@
 a unified framework to interpret Gleason's theorem and the Kochen-Specker
-theorem on an equal footing. For the cases between them, we found
+theorem as the limiting cases. For the cases between them, we found
 some legitimate quantum interval-valued probability measures which
@@
 \item [{Conclusions}] Our research provides a new insight of finite precision
-measurement and non-commutativity when formulating quantum theory,
-and the Born rule may not be as nature as we used to believe in the
-world of finite resource.{\small \par}
+measurement and non-commutativity when formulating quantum theory.
+Also, the Born rule may not be as nature as we used to believe in
+the world of finite resource.{\small \par}
 \end{description}

### 2017-03-21 prop_letter.tex
prop_letter.tex \paragraph{Quantum Interval-valued Probability Measure (IVPM)} Updating...

@@
 and to define $\left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]$
-and $[l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]$ so that
-$\bar{\mu}$ satisfy
+and 
+\begin{equation}
+[l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]
+\end{equation}
+ so that $\bar{\mu}$ satisfy
  \begin{itemize}

### 2017-03-21 prop_letter.tex
prop_letter.tex \newcommand{\yutsung}[1] Fix the width for two-column paper...

@@
 \usepackage[usenames,dvipsnames]{xcolor}
-\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
-\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
+\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}}}
+\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
@@
 is a proper subset of the right-hand side~$\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$.
+\yutsung{We use a section to motivate and introduce classical IVPMs.
+How to use classical IVPMs to justify quantum IVPMs without interrupting
+the flow?}\\
 Then, Gleason's theorem can be expressed as the limit case when the

### 2017-03-21 prop_letter.tex
prop_letter.tex \paragraph{Quantum Interval-valued Probability Measure (IVPM)} Updating...

@@
 relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
-to inclusion. This becomes intuitive if we compare each terms in two
-sides of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement}).
-Although we have $\mathbb{1}=\left(\mathbb{1}-P\right)+P$, but when
-$r>l$, the left-hand side~$\bar{\mu}(\mathbb{1})=\left[1,1\right]$
-is a proper subset of the right-hand side~$\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$.
+to inclusion. This becomes intuitive if we plug in Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement})
+into Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+The left-hand side becomes $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
+the right-hand side~$\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$,
+and the first interval is only a proper subset of the second one when
+$r>l$.
+
 \yutsung{We use a section to motivate and introduce classical IVPMs.

### 2017-03-21 prop_letter.tex
prop_letter.tex \paragraph{Quantum Interval-valued Probability Measure (IVPM)} Updating...

@@
 \end{equation}
- so that $\bar{\mu}$ satisfy
+ so that $\bar{\mu}$ satisfy the follow conditions:
 \begin{itemize}
@@
 The left-hand side becomes $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
-the right-hand side~$\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$,
-and the first interval is only a proper subset of the second one when
-$r>l$.
+and the right-hand side becomes $\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$
+which is a proper superset of $\left[1,1\right]$ when $r>l$.
 
-\yutsung{We use a section to motivate and introduce classical IVPMs.
-How to use classical IVPMs to justify quantum IVPMs without interrupting
-the flow?}\\
-Then, Gleason's theorem can be expressed as the limit case when the
-collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
-In the next paragraph, we will show the Kochen-Specker theorem is
-another limit case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+Although considering IVPM is new for quantum, people have already
+defined classical IVPMs~\citep{JamisonLodwick2004}. We find if we
+restrict on a mutually commuting sub-event space~$\events'\subseteq\events$,
+quantum IVPMs are one-to-one corresponding to the classical ones.
+Despite restricting on the domain of quantum IVPMs, if we pick the
+range as a limiting case, the collection of all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+then quantum IVPMs becomes real-valued probability measures which
+case Gleason's theorem applies. In the next paragraph, we will show
+the Kochen-Specker theorem is another limit case when the collection
+of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
 where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}

### 2017-03-21 prop_letter.tex
prop_letter.tex Put all \begin{eqnarray} into \begin{subequations}

@@
 assigning a definitely value to all observables such that 
+\begin{subequations}
+\label{eq:Kochen-Specker-Rules}
 \begin{eqnarray}
  &  & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
- &  & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)\label{eq:Kochen-Specker-Rules}
+ &  & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
 \end{eqnarray}
-if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
-is a function~$v$ satisfying these two properties, it must send
+\end{subequations}
+if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that
+there is a function~$v$ satisfying these two properties, it must send
 an observable to its eigenvalues so that the following observables~\citep{Mermin1990Simple,peres1995quantum}:
@@
 which should at least satisfy
+\begin{subequations}
+\label{eq:Kernaghan-1}
 \begin{eqnarray}
@@
 & & 1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
-\label{eq:Kernaghan-1}\end{eqnarray}
+\end{eqnarray}
+\end{subequations}
 because of table~\ref{table:commonBasis}. $f$ should also satisfy
@@
 orthogonal basis~\cite{Kernaghan1994,peres1995quantum}:
+\begin{subequations}
+\label{eq:Kernaghan-2}
 \begin{eqnarray}
@@
 & & 1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
-\label{eq:Kernaghan-2}\end{eqnarray}
+\end{eqnarray}
+\end{subequations}
 In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
@@
 $f$ should also satisfy the following equations: 
+\begin{subequations}
+\label{eq:non-Kernaghan}
 \begin{eqnarray}
@@
 & & 1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
-\label{eq:non-Kernaghan}\end{eqnarray}
+\end{eqnarray}
+\end{subequations}
 \qed\end{example}
@@
 as follow. 
+\begin{subequations}
 \begin{eqnarray}
@@
 \end{eqnarray}
+\end{subequations}
 To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
@@
 it is sufficient to check
+\begin{subequations}
 \begin{eqnarray}
@@
 \end{eqnarray}
+\end{subequations}
 for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}$.

### 2017-03-21 prop_letter.tex
prop_letter.tex Follow "REVTEX 4.1 Author's Guide" to break down equations...
prop_letter.tex and prop_letter.lyx Sync...

@@
 cannot be performed, and real measurements must be finite precision.
-Following Feynman~\citep{Feynman1982Simulating}, Landauer~\citep{Landauer1996188},
+Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
 and others, one might argue that this resource-bounded perspective
@@
 to analyze the quantum world with finite resource, we extend the classical
-interval-valued probability measure (IVPM)~\citep{JamisonLodwick2004},
+interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
 and introduce a new framework: quantum IVPM...\newpage{}
@@
 Although considering IVPM is new for quantum, people have already
-defined classical IVPMs~\citep{JamisonLodwick2004}. We find if we
+defined classical IVPMs~\cite{JamisonLodwick2004}. We find if we
 restrict on a mutually commuting sub-event space~$\events'\subseteq\events$,
@@
 there is a function~$v$ satisfying these two properties, it must send
-an observable to its eigenvalues so that the following observables~\citep{Mermin1990Simple,peres1995quantum}:
+an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
 \begin{equation}
@@
 \begin{eqnarray}
-& & 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
-& & 1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
+1 & = & f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) \nonumber \\*
+  &   & + f(0, 0, 0, 1) \textrm{ and} \\
+1 & = & f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) \nonumber \\*
+  &   & + f(1, 1, 1, -1)
 \end{eqnarray}
@@
 \begin{eqnarray}
-& & 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
-& & 1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
-& & 1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
-& & 1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
-& & 1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
-& & 1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
-& & 1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
-& & 1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
-& & 1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
+1 & = & f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) \nonumber \\*
+  &   & + f(0, 0, 1, -1)\textrm{ ,}\\
+1 & = & f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) \nonumber \\*
+  &   & + f(0, 1, 0, -1)\textrm{ ,}\\
+1 & = & f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) \nonumber \\*
+  &   & + f(0, 1, -1, 0)\textrm{ ,}\\
+1 & = & f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) \nonumber \\*
+  &   & + f(0, 1, 0, -1)\textrm{ ,}\\
+1 & = & f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) \nonumber \\*
+  &   & + f(1, 0, 0, -1)\textrm{ ,}\\
+1 & = & f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) \nonumber \\*
+  &   & + f(1, -1, 0, 0)\textrm{ ,}\\
+1 & = & f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) \nonumber \\*
+  &   & + f(1, -1, -1, 1)\textrm{ ,}\\
+1 & = & f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) \nonumber \\*
+  &   & + f(1, 1, -1, -1)\textrm{ ,}\\
+1 & = & f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) \nonumber \\*
+  &   & + f(1, -1, -1, 1)\textrm{ .}
 \end{eqnarray}
@@
 \begin{eqnarray}
-& & 1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
-& & 1 = f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
-& & 1 = f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
-& & 1 = f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
-& & 1 = f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1)+f(1,1,-1,-1)\textrm{ ,}\\ 
-& & 1 = f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
-& & 1 = f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
-& & 1 = f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,0,0)\textrm{ ,}\\ 
-& & 1 = f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1)+f(1,1,0,0)\textrm{ ,}\\ 
-& & 1 = f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0)+f(1,1,1,-1)\textrm{ ,}\\ 
-& & 1 = f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1)+f(1,1,1,-1)\textrm{ ,}\\ 
-& & 1 = f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0)+f(1,1,1,1)\textrm{ ,}\\ 
-& & 1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
+1 & = & f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1) \nonumber \\*
+  &   & +f(1,0,0,1)\textrm{ ,}\\ 
+1 & = & f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1) \nonumber \\*
+  &   & +f(1,0,0,1)\textrm{ ,}\\ 
+1 & = & f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0) \nonumber \\*
+  &   & +f(1,0,1,0)\textrm{ ,}\\ 
+1 & = & f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0) \nonumber \\*
+  &   & +f(1,0,1,0)\textrm{ ,}\\ 
+1 & = & f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1) \nonumber \\*
+  &   & +f(1,1,-1,-1)\textrm{ ,}\\ 
+1 & = & f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0) \nonumber \\*
+  &   & +f(1,1,0,0)\textrm{ ,}\\ 
+1 & = & f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0) \nonumber \\*
+  &   & +f(1,1,0,0)\textrm{ ,}\\ 
+1 & = & f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1) \nonumber \\*
+  &   & +f(1,1,0,0)\textrm{ ,}\\ 
+1 & = & f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1) \nonumber \\*
+  &   & +f(1,1,0,0)\textrm{ ,}\\ 
+1 & = & f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0) \nonumber \\*
+  &   & +f(1,1,1,-1)\textrm{ ,}\\ 
+1 & = & f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1) \nonumber \\*
+  &   & +f(1,1,1,-1)\textrm{ ,}\\ 
+1 & = & f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0) \nonumber \\*
+  &   & +f(1,1,1,1)\textrm{ ,}\\ 
+1 & = & f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1) \nonumber \\*
+  &   & +f(1,1,1,1)\textrm{ .} 
 \end{eqnarray}

### 2017-03-22 prop_letter.tex
Updates from ShareLaTeX

--- 2017-03-21 prop_letter.tex
@@
 
-In conventional quantum theory, when we measure a system described
-by a density matrix~$\rho$ with respect to an observable~$\mathbf{O}$,
+In conventional quantum theory, when we measure a property $\mathbf{O}$ of a 
+physical system whose state is represented by a density matrix~$\rho$, the 
+probability to obtain the value $\lambda$ is determined by the Born rule 
+$\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
+where $P_{\lambda}$ denotes the projector onto the eigenspace of $\lambda$.
+
+with respect to an observable~$\mathbf{O}$,
 $\rho$ and the eigenspace of a eigenvalue~$\lambda$ completely
@@
 \end{equation}
- so that $\bar{\mu}$ satisfy the follow conditions:
+ so that $\bar{\mu}$ satisfy
  \begin{itemize}
@@
 The left-hand side becomes $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
-and the right-hand side becomes $\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$
-which is a proper superset of $\left[1,1\right]$ when $r>l$.
+the right-hand side~$\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$,
+and the first interval is only a proper subset of the second one when
+$r>l$.
 
-Although considering IVPM is new for quantum, people have already
-defined classical IVPMs~\citep{JamisonLodwick2004}. We find if we
-restrict on a mutually commuting sub-event space~$\events'\subseteq\events$,
-quantum IVPMs are one-to-one corresponding to the classical ones.
-Despite restricting on the domain of quantum IVPMs, if we pick the
-range as a limiting case, the collection of all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-then quantum IVPMs becomes real-valued probability measures which
-case Gleason's theorem applies. In the next paragraph, we will show
-the Kochen-Specker theorem is another limit case when the collection
-of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+\yutsung{We use a section to motivate and introduce classical IVPMs.
+How to use classical IVPMs to justify quantum IVPMs without interrupting
+the flow?}\\
+Then, Gleason's theorem can be expressed as the limit case when the
+collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
+In the next paragraph, we will show the Kochen-Specker theorem is
+another limit case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
 where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}

### 2017-03-22 prop_letter.tex
Some updates with Prof. Ortiz...

--- 2017-03-21 prop_letter.tex
@@
-\documentclass[reprint, aps, prl,superscriptaddress, showpacs,
+\documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
 showkeys]{revtex4-1} 
@@
 \usepackage[utf8]{inputenc}
+\usepackage{babel}
 \usepackage{amsmath}
@@
 
-In conventional quantum theory, when we measure a system described
-by a density matrix~$\rho$ with respect to an observable~$\mathbf{O}$,
-$\rho$ and the eigenspace of a eigenvalue~$\lambda$ completely
-determines the probability of getting $\lambda$, which is computed
-by the Born rule~$\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
-where $P_{\lambda}$ denotes the projector to the eigenspace of $\lambda$.
-In another word, any density matrix~$\rho$ defines a quantum probability
+In conventional quantum theory, when we measure a property $\mathbf{O}$ of a 
+physical system whose state is represented by a density matrix~$\rho$, the 
+probability to obtain the value $\lambda$ is determined by the Born rule 
+$\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
+where $P_{\lambda}$ denotes the projector onto the eigenspace corresponding 
+to the eigenvalue $\lambda$ of the Hermitian operator $\mathbf{O}$~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
+
+In other words, any density matrix~$\rho$ defines a quantum probability
 measure~$\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow[0,1]$,
-where $\events$ is the set of all projectors in a Hilbert space.
+where $\events$ is the set of all projectors in a Hilbert space~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}.
 Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
@@
 such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$ in a Hilbert space
-of dimension $d\geq3$.
+of dimension $d\geq3$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 
@@
 case Gleason's theorem applies. In the next paragraph, we will show
-the Kochen-Specker theorem is another limit case when the collection
+the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA} is another limit case when the collection
 of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
@@
 \begin{eqnarray}
-& & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
-& & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
+&   & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) \nonumber \\*
+& = & \bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
+&   & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) \nonumber \\*
+& = & \bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
 & & \bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
@@
 \begin{eqnarray}
-& & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
-& & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
+&           & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right) \nonumber \\*
+& \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
+&           & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right) \nonumber \\*
+& \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
 \end{eqnarray}

### 2017-03-22 prop_letter.tex
prop_letter.tex Updating...

@@
 
-In conventional quantum theory, when we measure a property $\mathbf{O}$ of a 
-physical system whose state is represented by a density matrix~$\rho$, the 
-probability to obtain the value $\lambda$ is determined by the Born rule 
-$\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
+In conventional quantum theory, when we measure a property $\mathbf{O}$
+of a physical system whose state is represented by a density matrix~$\rho$,
+the probability to obtain the value $\lambda$ is determined by the
+Born rule $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
 where $P_{\lambda}$ denotes the projector onto the eigenspace corresponding
@@
 
-In other words, any density matrix~$\rho$ defines a quantum probability
-measure~$\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow[0,1]$,
-where $\events$ is the set of all projectors in a Hilbert space~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}.
-Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
-which should satisfy:
+In other words, any density matrix~$\rho$ can define a function
+$\mu_{\rho}^{\mathrm{\mathrm{B}}}$ from the set of all projectors
+in a Hilbert space~$\events$ to $[0,1]$. This function~$\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+is called a quantum probability measure because it satisfies the following
+probability axioms~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
 \begin{itemize}
-\item $\mu(\mathbb{0})=0$. 
-\item $\mu(\mathbb{1})=1$. 
-\item For any projection $P$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$. 
+\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{0})=0$. 
+\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{1})=1$. 
+\item For any projection $P$, $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\mathbb{1}-P\right)=1-\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)$. 
 \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
@@
 \begin{equation}
-\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
+\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
 \end{equation}
 \end{itemize}
-Gleason's theorem asserts that there exists a unique mixed state~$\rho$
-such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$ in a Hilbert space
-of dimension $d\geq3$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
+satisfying the above conditions, Gleason's theorem asserts that there
+exists a unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+in a Hilbert space of dimension $d\geq3$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 
@@
 In order to model the idea of finite precision measurement, we replace
-the range of $\mu$ from the infinity precision~$[0,1]$ to a collection
-of finite number of intervals~$\mathscr{I}$, and consider a quantum
-IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. It is intuitive
-to consider $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$
+the infinity precision~$[0,1]$ by a collection of finite number
+of intervals~$\mathscr{I}$, and consider quantum IVPMs~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
+It is intuitive to require $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$
 and to define $\left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]$
@@
 \end{equation}
- so that $\bar{\mu}$ satisfy the follow conditions:
+so that $\bar{\mu}$ satisfy the follow interval-valued probability
+axioms: 
 \begin{itemize}
@@
 relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
-to inclusion. This becomes intuitive if we plug in Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement})
-into Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
-The left-hand side becomes $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
+to inclusion because the equality is usually too strong to hold. For
+example, if we plug in Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement})
+into Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+the left-hand side becomes $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
 and the right-hand side becomes $\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$
@@
 Although considering IVPM is new for quantum, people have already
-defined classical IVPMs~\cite{JamisonLodwick2004}. We find if we
-restrict on a mutually commuting sub-event space~$\events'\subseteq\events$,
-quantum IVPMs are one-to-one corresponding to the classical ones.
-Despite restricting on the domain of quantum IVPMs, if we pick the
-range as a limiting case, the collection of all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-then quantum IVPMs becomes real-valued probability measures which
-case Gleason's theorem applies. In the next paragraph, we will show
-the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA} is another limit case when the collection
-of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+defined classical IVPMs~\citep{JamisonLodwick2004}. If we restrict
+quantum IVPMs~$\bar{\mu}:\events\rightarrow\mathscr{I}$ on a mutually
+commuting sub-event space~$\events'\subseteq\events$, every restricted
+quantum IVPM~$\bar{\mu}\mid_{\events'}$ is one-to-one corresponding
+to a classical one.
+
+On the other hand, Gleason's theorem can be expressed as the limit
+case when the collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
+In the next paragraph, we will show the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
+is another limit case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
 where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}

### 2017-03-23 prop_letter.tex
prop_letter.tex Updating...

@@
 
-In other words, any density matrix~$\rho$ can define a function
-$\mu_{\rho}^{\mathrm{\mathrm{B}}}$ from the set of all projectors
-in a Hilbert space~$\events$ to $[0,1]$. This function~$\mu_{\rho}^{\mathrm{\mathrm{B}}}$
-is called a quantum probability measure because it satisfies the following
-probability axioms~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
+In other words, any density matrix~$\rho$ defines a function $\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+from the set of all projectors in a Hilbert space~$\events$ to $[0,1]$.
+This function~$\mu_{\rho}^{\mathrm{\mathrm{B}}}$ is called a quantum
+probability measure because it satisfies the following probability
+axioms~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
 \begin{itemize}
@@
 Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
-satisfying the above conditions, Gleason's theorem asserts that there
+satisfying the above axioms, Gleason's theorem asserts that there
 exists a unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$
@@
 of intervals~$\mathscr{I}$, and consider quantum IVPMs~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
-It is intuitive to require $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$
-and to define $\left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]$
-and 
-\begin{equation}
-[l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]
-\end{equation}
-so that $\bar{\mu}$ satisfy the follow interval-valued probability
+Based on the intuitive requirement, $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$,
+and definition,\begin{subequations}
+\begin{eqnarray}
+ &  & \left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]\textrm{ and}\\
+ &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]
+\end{eqnarray}
+\end{subequations}a quantum IVPM~$\bar{\mu}$ should satisfy corresponding
 axioms:
@@
 
-Although considering IVPM is new for quantum, people have already
-defined classical IVPMs~\citep{JamisonLodwick2004}. If we restrict
-quantum IVPMs~$\bar{\mu}:\events\rightarrow\mathscr{I}$ on a mutually
-commuting sub-event space~$\events'\subseteq\events$, every restricted
-quantum IVPM~$\bar{\mu}\mid_{\events'}$ is one-to-one corresponding
-to a classical one.
+Although considering IVPM is new for a quantum theory, people have
+already defined classical IVPMs~\citep{JamisonLodwick2004}, which
+are essentially the same as quantum IVPMs on a restricted mutually
+commuting sub-event space~$\events'\subseteq\events$.
 

### 2017-03-23 prop_letter.tex
prop_letter.tex Updating...

@@
 In other words, any density matrix~$\rho$ defines a function $\mu_{\rho}^{\mathrm{\mathrm{B}}}$
-from the set of all projectors in a Hilbert space~$\events$ to $[0,1]$.
-This function~$\mu_{\rho}^{\mathrm{\mathrm{B}}}$ is called a quantum
-probability measure because it satisfies the following probability
-axioms~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
+from the set of all projectors~$\events$ to $[0,1]$. This function~$\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+is called a quantum probability measure because it satisfies the following
+probability axioms~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
 \begin{itemize}
@@
 In order to model the idea of finite precision measurement, we replace
-the infinity precision~$[0,1]$ by a collection of finite number
-of intervals~$\mathscr{I}$, and consider quantum IVPMs~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
+the infinity precise~$[0,1]$ by a collection of finite number of
+intervals~$\mathscr{I}$, and consider quantum IVPMs~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
 Based on the intuitive requirement, $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$,
-and definition,\begin{subequations}
+and operations on intervals,\begin{subequations}
 \begin{eqnarray}
@@
 to inclusion because the equality is usually too strong to hold. For
-example, if we plug in Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement})
-into Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-the left-hand side becomes $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
-and the right-hand side becomes $\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$
-which is a proper superset of $\left[1,1\right]$ when $r>l$.
+example, if we consider $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $,
+we have 
+\[
+\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1+l-r,1+r-l\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)
+\]
+by Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement}) when
+$r>l$.
 
@@
 
-On the other hand, Gleason's theorem can be expressed as the limit
+On the other hand, Gleason's theorem can be expressed as the limiting
 case when the collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
 In the next paragraph, we will show the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
-is another limit case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
 where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}

### 2017-03-23 prop_letter.tex
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Updating...

@@
 is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}
+where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
 
@@
 The Kochen-Specker theorem asserts that there is no function~$v$
-assigning a definitely value to all observables such that 
-\begin{subequations}
+assigning a definitely value to all observables such that \begin{subequations}
 \label{eq:Kochen-Specker-Rules} 
@@
 \end{eqnarray}
-\end{subequations}
-if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that
-there is a function~$v$ satisfying these two properties, it must send
-an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+\end{subequations} if $O_{1}$ and $O_{2}$ are commuting observables.
+Suppose that there is a function~$v$ satisfying these two properties,
+it must send an observable to its eigenvalues so that the following
+observables~\citep{Mermin1990Simple,peres1995quantum}: 
 \begin{equation}
@@
 as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}
+
 \begin{ruledtabular}
 \begin{tabular}{ccc|cccc}
-\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
+\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis}\tabularnewline
 \hline 
-$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
-$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
-$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
-$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
-$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
-$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
+$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$  & $(1,0,0,0)$  & $(0,1,0,0)$  & $(0,0,1,0)$  & $(0,0,0,1)$ \tabularnewline
+$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$  & $(1,1,1,1)$  & $(1,-1,1,-1)$  & $(1,1,-1,-1)$  & $(1,-1,-1,1)$ \tabularnewline
+$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(1,1,1,-1)$  & $(1,1,-1,1)$  & $(1,-1,1,1)$  & $(-1,1,1,1)$ \tabularnewline
+$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\mathbb{1}$  & $\sigma_{x}\otimes\sigma_{z}$  & $(1,0,1,0)$  & $(0,1,0,1)$  & $(1,0,-1,0)$  & $(0,1,0,-1)$ \tabularnewline
+$\sigma_{z}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{z}\otimes\sigma_{x}$  & $(1,1,0,0)$  & $(1,-1,0,0)$  & $(0,0,1,1)$  & $(0,0,1,-1)$ \tabularnewline
+$\sigma_{z}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(0,1,1,0)$  & $(0,1,-1,0)$  & $(1,0,0,1)$  & $(1,0,0,-1)$ \tabularnewline
 \end{tabular}
 \end{ruledtabular}
+
 \end{table*}
+
 Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
 if we want to reformulate the above argument in the language of quantum
-probability measures, we first need to find the common eigenbasis
-of each row and column, and consider the projections to each eigenvectors.
+IVPMs, we first need to find the common eigenbasis of each row and
+column, and consider the projections to each eigenvectors~\citep{Kernaghan1994,peres1995quantum}.
 Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
@@
 \begin{equation}
-\events_{24}=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
+\events_{24}=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\begin{gathered}\textrm{mutually orthogonal }\\
+\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}
+\end{gathered}
+}
 \end{equation}
-which is a sub-event space defined in definition~\ref{def:sub-event-space}.
-This kind of $v$ is actually a quantum cryptodeterministic measure.
-Since a cryptodeterministic measure is a special case of real-valued
-probability measure, by theorem~\ref{lemma:classical-probability-measures},
-the quantum cryptodeterministic measure~$v$ exists if and only if
-there exists a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
-which should at least satisfy
-\begin{subequations}
-\label{eq:Kernaghan-1}
+is a sub-event space.
+
+Assume there is a function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
+satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
+be a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
+defined by $\bar{\mu}\left(P\right)=\iota_{0}\left(v\left(P\right)\right)$,
+where 
+\begin{equation}
+\iota_{0}\left(x\right)=\begin{cases}
+\necess & \text{ if}x=1\text{ ;}\\
+\imposs & \text{ if}x=0\text{ .}
+\end{cases}\label{eq:homomorphism-0}
+\end{equation}
+Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
+defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
+Because of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+we have\begin{subequations} \label{eq:Kernaghan} 
 \begin{eqnarray}
-1 & = & f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) \nonumber \\*
-  &   & + f(0, 0, 0, 1) \textrm{ and} \\
-1 & = & f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) \nonumber \\*
-  &   & + f(1, 1, 1, -1)
+\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
+ &  & +\bar{f}(0,0,0,1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\
+ &  & +\bar{f}(1,1,1,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)+\bar{f}(0,0,1,1)\nonumber \\
+ &  & +\bar{f}(0,0,1,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
+ &  & +\bar{f}(0,1,0,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)+\bar{f}(0,1,1,0)\nonumber \\*
+ &  & +\bar{f}(0,1,-1,0)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)+\bar{f}(1,0,1,0)\nonumber \\*
+ &  & +\bar{f}(0,1,0,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)+\bar{f}(0,1,1,0)\nonumber \\*
+ &  & +\bar{f}(1,0,0,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)+\bar{f}(0,0,1,1)\nonumber \\*
+ &  & +\bar{f}(1,-1,0,0)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)+\bar{f}(1,1,1,1)\nonumber \\*
+ &  & +\bar{f}(1,-1,-1,1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)+\bar{f}(1,1,1,1)\nonumber \\*
+ &  & +\bar{f}(1,1,-1,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)+\bar{f}(1,1,-1,-1)\nonumber \\*
+ &  & +\bar{f}(1,-1,-1,1)\textrm{ .}
 \end{eqnarray}
-\end{subequations}
-because of table~\ref{table:commonBasis}. $f$ should also satisfy
-the following equations since the vectors in each equation form an
-orthogonal basis~\cite{Kernaghan1994,peres1995quantum}:
-\begin{subequations}
-\label{eq:Kernaghan-2}
-\begin{eqnarray}
-1 & = & f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) \nonumber \\*
-  &   & + f(0, 0, 1, -1)\textrm{ ,}\\
-1 & = & f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) \nonumber \\*
-  &   & + f(0, 1, 0, -1)\textrm{ ,}\\
-1 & = & f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) \nonumber \\*
-  &   & + f(0, 1, -1, 0)\textrm{ ,}\\
-1 & = & f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) \nonumber \\*
-  &   & + f(0, 1, 0, -1)\textrm{ ,}\\
-1 & = & f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) \nonumber \\*
-  &   & + f(1, 0, 0, -1)\textrm{ ,}\\
-1 & = & f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) \nonumber \\*
-  &   & + f(1, -1, 0, 0)\textrm{ ,}\\
-1 & = & f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) \nonumber \\*
-  &   & + f(1, -1, -1, 1)\textrm{ ,}\\
-1 & = & f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) \nonumber \\*
-  &   & + f(1, 1, -1, -1)\textrm{ ,}\\
-1 & = & f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) \nonumber \\*
-  &   & + f(1, -1, -1, 1)\textrm{ .}
-\end{eqnarray}
-\end{subequations}
-In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
-are odd number of equations, but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
+\end{subequations}\newpage{}
+
+In equation~\ref{eq:Kernaghan}, there are odd number of equations,
+but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
 occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
-satisfying equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}.
+satisfying equation~\ref{eq:Kernaghan} and \ref{eq:Kernaghan-2}.
 

### 2017-03-23 prop_letter.tex
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Updating...

@@
 Because of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-we have\begin{subequations} \label{eq:Kernaghan} 
+we have\begin{subequations}\label{eq:Kernaghan}
 \begin{eqnarray}
@@
  &  & +\bar{f}(0,0,0,1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\
- &  & +\bar{f}(1,1,1,-1)\textrm{ ,}\\
 \necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)+\bar{f}(0,0,1,1)\nonumber \\
@@
  &  & +\bar{f}(0,1,-1,0)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\
+ &  & +\bar{f}(1,1,1,-1)\textrm{ ,}\\
 \necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)+\bar{f}(1,0,1,0)\nonumber \\*
@@
 \end{eqnarray}
-\end{subequations}\newpage{}
+\end{subequations}If we sum up equation~\ref{eq:Kernaghan}, we
+will have
+\begin{eqnarray}
+\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(-1,1,1,1)\nonumber \\
+ &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
+\end{eqnarray}
+where 
+\begin{eqnarray}
+\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(-1,1,1,1),(1,-1,1,-1),\nonumber \\
+ &  & (1,0,-1,0),(1,0,0,1),(1,1,0,0)\}\textrm{ .}
+\end{eqnarray}
+However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
+can never be satisfied, because each term can either be $\imposs=\left[0,0\right]$
+or $\necess=\left[1,1\right]$.\newpage{}
 
-In equation~\ref{eq:Kernaghan}, there are odd number of equations,
-but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
-occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
-satisfying equation~\ref{eq:Kernaghan} and \ref{eq:Kernaghan-2}.
+On the one hand, the Kochen-Specker theorem is equivalent to the non-existence
+of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
+where $\events$ is the set of all projections on a Hilbert space.
+On the other hand, if we replace the range by the interval~$\left[0,1\right]$,
+Gleason's theorem asserts that every quantum real-valued probability
+measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
+by a density matrix according to the Born rule. These two extreme
+cases can be understood in a broader framework of quantum interval-valued
+probability measure (IVPM)~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+where $\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
+When we pick $\mathscr{I}$ as $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
+there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
+theorem. When the collection of intervals is $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+a quantum IVPM is well-behaved as a usual quantum real-valued probability
+measure does.
 

### 2017-03-24 prop_iop.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Added...

@@
 
-\begin{thm}[Shapley~\cite{Shapley1971,,Grabisch2016}]\label{thm:Shapley}
+\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}
 Every (classical) convex interval-valued probability measure has a

### 2017-03-24 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Added...

@@
 can be only performed in finite precision. {\small \par}
-\item [{Method}] We model idea of the finite precision measurement as finite
-number of intervals, and replace quantum real-valued probability measures
-by interval-valued ones. {\small \par}
+\item [{Method}] We model the idea of the finite precision measurement
+as finite number of intervals, and replace quantum real-valued probability
+measures by interval-valued ones.{\small \par}
 \item [{Results}] Quantum interval-valued probability measures provide
@@
 satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
-be a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
-defined by $\bar{\mu}\left(P\right)=\iota_{0}\left(v\left(P\right)\right)$,
+be a quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
+defined by $\bar{\mu}_{24}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
 where 
 \begin{equation}
-\iota_{0}\left(x\right)=\begin{cases}
+\iota_{\mathrm{D}}\left(x\right)=\begin{cases}
 \necess & \text{ if}x=1\text{ ;}\\
@@
 Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
-defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
-Because of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-we have\begin{subequations}\label{eq:Kernaghan}
+defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}_{24}\left(\proj{\psi}\right)$
+satisfying the following conditions because of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}\label{eq:Kernaghan}
 \begin{eqnarray}
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
- &  & +\bar{f}(0,0,0,1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)+\bar{f}(0,0,1,1)\nonumber \\
- &  & +\bar{f}(0,0,1,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
- &  & +\bar{f}(0,1,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)+\bar{f}(0,1,1,0)\nonumber \\*
- &  & +\bar{f}(0,1,-1,0)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\
- &  & +\bar{f}(1,1,1,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)+\bar{f}(1,0,1,0)\nonumber \\*
- &  & +\bar{f}(0,1,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)+\bar{f}(0,1,1,0)\nonumber \\*
- &  & +\bar{f}(1,0,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)+\bar{f}(0,0,1,1)\nonumber \\*
- &  & +\bar{f}(1,-1,0,0)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)+\bar{f}(1,1,1,1)\nonumber \\*
- &  & +\bar{f}(1,-1,-1,1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)+\bar{f}(1,1,1,1)\nonumber \\*
- &  & +\bar{f}(1,1,-1,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)+\bar{f}(1,1,-1,-1)\nonumber \\*
- &  & +\bar{f}(1,-1,-1,1)\textrm{ .}
+\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
+ &  & +\bar{f}(0,0,1,0)+\bar{f}(0,0,0,1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\
+ &  & +\bar{f}(0,0,1,1)+\bar{f}(0,0,1,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
+ &  & +\bar{f}(0,1,0,1)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)\nonumber \\*
+ &  & +\bar{f}(0,1,1,0)+\bar{f}(0,1,-1,0)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)\nonumber \\
+ &  & +\bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
+ &  & +\bar{f}(1,0,1,0)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
+ &  & +\bar{f}(0,1,1,0)+\bar{f}(1,0,0,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\nonumber \\*
+ &  & +\bar{f}(0,0,1,1)+\bar{f}(1,-1,0,0)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)\nonumber \\*
+ &  & +\bar{f}(1,1,1,1)+\bar{f}(1,-1,-1,1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)\nonumber \\*
+ &  & +\bar{f}(1,1,1,1)+\bar{f}(1,1,-1,-1)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
+ &  & +\bar{f}(1,1,-1,-1)+\bar{f}(1,-1,-1,1)\textrm{ .}
 \end{eqnarray}
@@
 However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
-can never be satisfied, because each term can either be $\imposs=\left[0,0\right]$
-or $\necess=\left[1,1\right]$.\newpage{}
+can never be satisfied. Because each term in left-hand side is either
+$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the left-hand
+side is a singleton set of an even integer while the right-hand side
+is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
+Moreover, there is no quantum IVPM defined on the set of all projectors
+as well; otherwise, if we have a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+then we can restrict $\bar{\mu}$ and define $\bar{\mu}_{24}=\left.\bar{\mu}\right|_{\events_{24}}$.
 
-On the one hand, the Kochen-Specker theorem is equivalent to the non-existence
-of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
-where $\events$ is the set of all projections on a Hilbert space.
-On the other hand, if we replace the range by the interval~$\left[0,1\right]$,
-Gleason's theorem asserts that every quantum real-valued probability
-measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
-by a density matrix according to the Born rule. These two extreme
-cases can be understood in a broader framework of quantum interval-valued
-probability measure (IVPM)~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-where $\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
-When we pick $\mathscr{I}$ as $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
-there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
-theorem. When the collection of intervals is $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-a quantum IVPM is well-behaved as a usual quantum real-valued probability
-measure does.
+\paragraph{Quantum IVPM and Real-valued Probability Measure}
 
-On the one hand, the Kochen-Specker theorem is equivalent to the non-existence
-of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
-where $\events$ is the set of all projections on a Hilbert space.
-On the other hand, if we replace the range by the interval~$\left[0,1\right]$,
-Gleason's theorem asserts that every quantum real-valued probability
-measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
-by a density matrix according to the Born rule. These two extreme
-cases can be understood in a broader framework of quantum interval-valued
-probability measure (IVPM)~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-where $\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
-When we pick $\mathscr{I}$ as $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
-there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
-theorem. When the collection of intervals is $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-a quantum IVPM is well-behaved as a usual quantum real-valued probability
-measure does.
-
-Given any sub-event space~$\events'\subseteq\events$, in order to
-qualify how well-behaved a quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
-could be, we introduce the notion of core.
-
-\begin{definition}A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events'\rightarrow[0,1]}{\forall P\in\events'.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}
-
-\noindent Then, Gleason's theorem guarantees that $\bar{\mu}$ has
-a unique core element for any $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$.
-In the rest of the letter, we will provide examples of quantum IVPMs
-on $\events_{24}$, and show how a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
-could be depending on different intervals~$\mathscr{I}$.
-
-First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
-it is easy to construct a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
-whose unique core element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.
-For example, when $\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
-we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
-and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
-where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
-denote function composition. This provides an example that a well-behaved
-quantum IVPM exists even if $\mathscr{I}$ is discrete. Well-behaved
-quantum IVPMs happen when mapping to other kind of intervals. For
+Recall we model the idea of the finite precision measurement as IVPM.
+Given a quantum IVPM, the natural question would be whether we are
+able to refine precisely enough to determine the underlying unknown
+quantum real-valued probability measure, i.e., a quantum state. This
+leads to the definition of core:\begin{definition}A \emph{core} of
+$\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}For
 example, we can add an one extra interval~$\unknown=\left[0,1\right]$
@@
 \begin{equation}
-\iota_1(x)=\begin{cases} 
+\iota_{1}(x)=\begin{cases}
 \necess & \text{ if}x=1\text{ ;}\\
@@
 \unknown & \text{ otherwise.}
-\end{cases}\label{eq:homomorphism-1} \end{equation}
-We still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.
+\end{cases}\label{eq:homomorphism-1}
+\end{equation}
+Then, $\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}_{1}$
+is a quantum IVPM, and we have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
+where $\circ$ denote function composition.
 
-Although the quantum IVPM listed above are all well-behaved, there
-are some quantum IVPMs far from the Born rule. Consider $\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
-defined by $\bar{\mu}(P)=\unknown$ for every projection~$P$. Since
-every quantum probability measure is in the core of $\bar{\mu}$,
-this measure represents the beliefs of an experimenter with no prior
-knowledge about the particular quantum system in question.
+While Shapley proved a good enough classical IVPM always has a non-empty
+core, and we haven't found any classical IVPM having an empty core,
+there are some simple quantum IVPM which has an empty core.
 
-\begin{example}[Four-dimensional quantum real-valued probability
-measure]\label{ex:four-dimensional-real-value}Consider the frame
-function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
-Apart from equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
-$f$ should also satisfy the following equations: 
-\begin{subequations}
-\label{eq:non-Kernaghan}
-\begin{eqnarray}
-1 & = & f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1) \nonumber \\*
-  &   & +f(1,0,0,1)\textrm{ ,}\\ 
-1 & = & f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1) \nonumber \\*
-  &   & +f(1,0,0,1)\textrm{ ,}\\ 
-1 & = & f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0) \nonumber \\*
-  &   & +f(1,0,1,0)\textrm{ ,}\\ 
-1 & = & f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0) \nonumber \\*
-  &   & +f(1,0,1,0)\textrm{ ,}\\ 
-1 & = & f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1) \nonumber \\*
-  &   & +f(1,1,-1,-1)\textrm{ ,}\\ 
-1 & = & f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0) \nonumber \\*
-  &   & +f(1,1,0,0)\textrm{ ,}\\ 
-1 & = & f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0) \nonumber \\*
-  &   & +f(1,1,0,0)\textrm{ ,}\\ 
-1 & = & f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1) \nonumber \\*
-  &   & +f(1,1,0,0)\textrm{ ,}\\ 
-1 & = & f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1) \nonumber \\*
-  &   & +f(1,1,0,0)\textrm{ ,}\\ 
-1 & = & f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0) \nonumber \\*
-  &   & +f(1,1,1,-1)\textrm{ ,}\\ 
-1 & = & f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1) \nonumber \\*
-  &   & +f(1,1,1,-1)\textrm{ ,}\\ 
-1 & = & f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0) \nonumber \\*
-  &   & +f(1,1,1,1)\textrm{ ,}\\ 
-1 & = & f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1) \nonumber \\*
-  &   & +f(1,1,1,1)\textrm{ .} 
-\end{eqnarray}
-\end{subequations}
-\qed\end{example}
+\begin{thm}[Shapley~\citep{Shapley1971,Grabisch2016}]\label{thm:Shapley}
+Every classical convex interval-valued probability measure has a non-empty
+core, where $\bar{\mu}$ is called convex if 
+\begin{equation}
+\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
+\end{equation}
+for all commuting $P_{0},P_{1}\in\events$, and the \emph{disjunction}~$P_{0}\vee P_{1}$
+is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\citep{Griffiths2003}.\end{thm}
 
@@
 $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$. Then, we can
-define a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
-as follow. 
-\begin{subequations}
+define a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{1}$
+as follow. \begin{subequations} 
 \begin{eqnarray}
-&   & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) \nonumber \\*
+ &  & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})\nonumber \\*
  & = & \bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\
-&   & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) \nonumber \\*
+ &  & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})\nonumber \\*
  & = & \bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\
-& & \bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
+ &  & \bar{\mu}(P)=\unknown\qquad\textrm{otherwise.}
 \end{eqnarray}
-\end{subequations}
-To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+\end{subequations} To verify $\bar{\mu}$ is a quantum IVPM, first
+notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
 implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
@@
 Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-it is sufficient to check
-\begin{subequations}
+it is sufficient to check \begin{subequations} 
 \begin{eqnarray}
-&           & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right) \nonumber \\*
+ &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\nonumber \\*
  & \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
-&           & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right) \nonumber \\*
+ &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\nonumber \\*
  & \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
 \end{eqnarray}
-\end{subequations}
-for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}$.
-This equation always holds because $\unknown$ is a subset of the
-left-hand side of both of the equations.
+\end{subequations} for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$,
+and $\ket{\psi_{2}}$. This equation always holds because $\unknown$
+is a subset of the left-hand side of both of the equations.
 
@@
 \end{equation}
-By Gleason's theorem\footnote{\yutsung{Find all orthogonal basis of $\mathcal{T}_{24}$ and solve
-the linear equations for Gleason's...}}, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
+By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
 such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,

### 2017-03-24 prop_letter.tex
prop_letter.tex Fix small things here and there...

@@
 are essentially the same as quantum IVPMs on a restricted mutually
-commuting sub-event space~$\events'\subseteq\events$.
+commuting sub-event space~$\events'\subseteq\events$, where the
+sub-event space is defined as follow.
+
+\begin{definition}\label{def:sub-event-space}Given a Hilbert space
+$\Hilb$, $\events'\subseteq\events$ is called a sub-event space
+if it satisfies the follow conditions.
+\begin{itemize}
+\item $\mathbb{0}\in\events'$.
+\item $\mathbb{1}\in\events'$.
+\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$.
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
+we have $\sum_{i=1}^{N}P_{i}\in\events'$.
+\end{itemize}
+\end{definition}
 
@@
 \begin{eqnarray}
- &  & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
- &  & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
+ &  & v\left(\mathbf{O}_{1}\right)+v\left(\mathbf{O}_{2}\right)=v\left(\mathbf{O}_{1}+\mathbf{O}_{2}\right)\textrm{ and}\\
+ &  & v\left(\mathbf{O}_{1}\right)v\left(\mathbf{O}_{2}\right)=v\left(\mathbf{O}_{1}\mathbf{O}_{2}\right)
 \end{eqnarray}
-\end{subequations} if $O_{1}$ and $O_{2}$ are commuting observables.
-Suppose that there is a function~$v$ satisfying these two properties,
-it must send an observable to its eigenvalues so that the following
-observables~\citep{Mermin1990Simple,peres1995quantum}: 
+\end{subequations} if $\mathbf{O}_{1}$ and $\mathbf{O}_{2}$ are
+commuting observables. Suppose that there is a function~$v$ satisfying
+these two properties, it must send an observable to its eigenvalues
+so that the following observables~\citep{Mermin1990Simple,peres1995quantum}:
 \begin{equation}
@@
 in the left column commutes, and their common eigenbasis is listed
-in the right column. In order to unified and simplify notation, we
-do not normalize eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
+in the right column. In order to unify and simplify the notation,
+we do not normalize eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
 as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}

### 2017-03-25 prop_letter.tex
prop_letter.tex Updating here and there...

@@
 Based on the intuitive requirement, $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$,
-and operations on intervals,\begin{subequations}
+and operations on intervals,\begin{subequations}\label{eq:interval-operations}
 \begin{eqnarray}
@@
 to inclusion because the equality is usually too strong to hold. For
-example, if we consider $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $,
-we have 
+example, if we consider $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $
+and $\bar{\mu}\left(P\right)=\left[l,r\right]$, by Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement})
+and (\ref{eq:interval-operations}), we have 
 \[
@@
 \]
-by Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement}) when
-$r>l$.
+when $r>l$.
 
@@
 are essentially the same as quantum IVPMs on a restricted mutually
-commuting sub-event space~$\events'\subseteq\events$, where the
-sub-event space is defined as follow.
-
-\begin{definition}\label{def:sub-event-space}Given a Hilbert space
-$\Hilb$, $\events'\subseteq\events$ is called a sub-event space
-if it satisfies the follow conditions.
+commuting sub-event space~$\events'\subseteq\events$, where any
+subset of $\events$ is called a sub-event space if it satisfies the
+follow conditions.
 \begin{itemize}
@@
 \end{itemize}
-\end{definition}
-
-On the other hand, Gleason's theorem can be expressed as the limiting
-case when the collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
-In the next paragraph, we will show the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
+Quantum IVPM not only stems from classical IVPM but also generalizes
+quantum real-valued probability measures which can be expressed a
+limiting case when the collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+where Gleason's theorem is applied. However, it certainly contains
+richer phenomena. For example, we will show the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
 is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
+where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
+in the next paragraph.
 
@@
 column, and consider the projections to each eigenvectors~\citep{Kernaghan1994,peres1995quantum}.
-Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
+Let $\mathcal{T}_{24}$ denote all eigenstates listed in Table~\ref{table:commonBasis}.
 The Kochen-Specker theorem could then be proved by showing there is
@@
 \iota_{\mathrm{D}}\left(x\right)=\begin{cases}
-\necess & \text{ if}x=1\text{ ;}\\
-\imposs & \text{ if}x=0\text{ .}
+\necess & \text{, if }x=1\text{ ;}\\
+\imposs & \text{, if }x=0\text{ .}
 \end{cases}\label{eq:homomorphism-0}
@@
 defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}_{24}\left(\proj{\psi}\right)$
-satisfying the following conditions because of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}\label{eq:Kernaghan}
+satisfying the following conditions because the right-hand side of
+each equation forms an orthogonal basis and we can apply Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}\label{eq:Kernaghan}
 \begin{eqnarray}

### 2017-03-25 prop_letter.tex
prop_letter.tex \allowdisplaybreaks Added...
prop_letter.tex Updating here and there...

@@
 \newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
+\allowdisplaybreaks
 
@@
  &  & +\bar{f}(0,0,1,0)+\bar{f}(0,0,0,1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\
+\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
  &  & +\bar{f}(0,0,1,1)+\bar{f}(0,0,1,-1)\textrm{ ,}\\
@@
  &  & +\bar{f}(0,1,1,0)+\bar{f}(0,1,-1,0)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)\nonumber \\
+\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)\nonumber \\*
  &  & +\bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\textrm{ ,}\\
@@
  &  & +\bar{f}(1,0,1,0)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
+\necess & \subseteq & \bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
  &  & +\bar{f}(0,1,1,0)+\bar{f}(1,0,0,-1)\textrm{ ,}\\
@@
 \end{eqnarray}
-\end{subequations}If we sum up equation~\ref{eq:Kernaghan}, we
-will have
+\end{subequations}If we sum up Eq.~(\ref{eq:Kernaghan}), we will
+have
 \begin{eqnarray}
-\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(-1,1,1,1)\nonumber \\
+\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(1,1,-1,1)\nonumber \\
  &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
@@
 \begin{eqnarray}
-\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(-1,1,1,1),(1,-1,1,-1),\nonumber \\
+\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(1,1,-1,1),(1,-1,1,-1),\nonumber \\
  &  & (1,0,-1,0),(1,0,0,1),(1,1,0,0)\}\textrm{ .}
@@
 However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
-can never be satisfied. Because each term in left-hand side is either
-$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the left-hand
-side is a singleton set of an even integer while the right-hand side
+can never be satisfied. Because each term in right-hand side is either
+$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the right-hand
+side is a singleton set of an even integer while the left-hand side
 is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
@@
 Recall we model the idea of the finite precision measurement as IVPM.
-Given a quantum IVPM, the natural question would be whether we are
-able to refine precisely enough to determine the underlying unknown
-quantum real-valued probability measure, i.e., a quantum state. This
-leads to the definition of core:\begin{definition}A \emph{core} of
-$\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}For
+When we made finite number of observations, we can use some quantum
+IVPMs to represent what we observed. The natural question would be
+whether we are able to refine precisely enough to determine the underlying
+unknown quantum real-valued probability measure, i.e., a quantum state.
+This leads to the definition of core:\begin{definition}A \emph{core}
+of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}For
 example, we can add an one extra interval~$\unknown=\left[0,1\right]$
@@
 \iota_{1}(x)=\begin{cases}
-\necess & \text{ if}x=1\text{ ;}\\
-\imposs & \text{ if}x=0\text{ ;}\\
-\unknown & \text{ otherwise.}
+\necess & \text{, if }x=1\text{ ;}\\
+\imposs & \text{, if }x=0\text{ ;}\\
+\unknown & \text{, otherwise.}
 \end{cases}\label{eq:homomorphism-1}
@@
 Then, $\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}_{1}$
-is a quantum IVPM, and we have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
+is a quantum IVPM whose core has a unique element~$\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
 where $\circ$ denote function composition.
 
-While Shapley proved a good enough classical IVPM always has a non-empty
-core, and we haven't found any classical IVPM having an empty core,
-there are some simple quantum IVPM which has an empty core.
-
-\begin{thm}[Shapley~\citep{Shapley1971,Grabisch2016}]\label{thm:Shapley}
-Every classical convex interval-valued probability measure has a non-empty
-core, where $\bar{\mu}$ is called convex if 
-\begin{equation}
-\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
-\end{equation}
-for all commuting $P_{0},P_{1}\in\events$, and the \emph{disjunction}~$P_{0}\vee P_{1}$
-is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\citep{Griffiths2003}.\end{thm}
+However, not every quantum IVPM well represent our observations. The
+following example provides a quantum IVPM with an empty core, i.e.,
+it cannot be further refined to get the underlying unknown quantum
+states.
 
@@
 
+While the above example alerts that there might be a bad choice to
+represent our observations as a quantum IVPM, this phenomena is quantum,
+because Shapley proved that a good enough classical IVPM always has
+a non-empty core. \begin{thm}[Shapley~\citep{Shapley1971,Grabisch2016}]\label{thm:Shapley}Every
+classical convex interval-valued probability measure has a non-empty
+core, where $\bar{\mu}$ is called convex if 
+\begin{equation}
+\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
+\end{equation}
+for all commuting $P_{0},P_{1}\in\events$, and the \emph{disjunction}~$P_{0}\vee P_{1}$
+is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\citep{Griffiths2003}.\end{thm}
+In general, we haven't found any classical IVPM having an empty core.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-03-26 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

@@
 When we made finite number of observations, we can use some quantum
-IVPMs to represent what we observed. The natural question would be
-whether we are able to refine precisely enough to determine the underlying
-unknown quantum real-valued probability measure, i.e., a quantum state.
-This leads to the definition of core:\begin{definition}A \emph{core}
-of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}For
-example, we can add an one extra interval~$\unknown=\left[0,1\right]$
+IVPMs to represent what we observed. The natural question would be:
+given a quantum IVPM~$\bar{\mu}$ whether we can refine precisely
+enough to determine the underlying unknown quantum real-valued probability
+measure, i.e., a quantum state. If we can, we say $\bar{\mu}$ has
+a non-empty core. More precisely, A \emph{core} of $\bar{\mu}$, $\mathrm{core}\left(\bar{\mu}\right)$,
+is the set 
+\begin{equation}
+\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
+\end{equation}
+For example, we can add an one extra interval~$\unknown=\left[0,1\right]$
 to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.

### 2017-03-26 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

@@
 When we made finite number of observations, we can use some quantum
-IVPMs to represent what we observed. The natural question would be:
-given a quantum IVPM~$\bar{\mu}$ whether we can refine precisely
-enough to determine the underlying unknown quantum real-valued probability
-measure, i.e., a quantum state. If we can, we say $\bar{\mu}$ has
-a non-empty core. More precisely, A \emph{core} of $\bar{\mu}$, $\mathrm{core}\left(\bar{\mu}\right)$,
+IVPMs to represent what we observed. Given a quantum IVPM~$\bar{\mu}$,
+the question is whether we can refine precisely enough to determine
+the underlying unknown quantum real-valued probability measure, i.e.,
+a quantum state. If we can, we say $\bar{\mu}$ has a non-empty core.
+More precisely, A \emph{core} of $\bar{\mu}$, $\mathrm{core}\left(\bar{\mu}\right)$,
 is the set 
@@
 
-However, not every quantum IVPM well represent our observations. The
-following example provides a quantum IVPM with an empty core, i.e.,
-it cannot be further refined to get the underlying unknown quantum
+However, not every quantum IVPM well represents our observations.
+The following example provides a quantum IVPM with an empty core,
+i.e., it cannot be further refined to get the underlying unknown quantum
 states.
@@
 basis~$\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $ as defined
-in table~\ref{table:commonBasis}. Let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
+in Table~\ref{table:commonBasis}. Let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
 $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$. Then, we can
 define a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{1}$
-as follow. \begin{subequations} 
+as follow:\begin{subequations} 
 \begin{eqnarray}
- &  & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})\nonumber \\*
- & = & \bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\
- &  & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})\nonumber \\*
- & = & \bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\
- &  & \bar{\mu}(P)=\unknown\qquad\textrm{otherwise.}
+\imposs & = & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})\nonumber \\*
+ & = & \bar{\mu}(\proj{\ps'})\textrm{ ,}\\
+\necess & = & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})\nonumber \\*
+ & = & \bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}\\
+\unknown & = & \bar{\mu}(P)\qquad\textrm{otherwise.}
 \end{eqnarray}
@@
 probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
-for some quantum probability measure~$\mu:\events_{24}\rightarrow\left[0,1\right]$.
+for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
 We must have 

### 2017-03-26 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

@@
 \end{eqnarray}
-\end{subequations} To verify $\bar{\mu}$ is a quantum IVPM, first
-notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+\end{subequations}
+
+To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
 implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
@@
 \end{subequations} for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$,
-and $\ket{\psi_{2}}$. This equation always holds because $\unknown$
+and $\ket{\psi_{2}}$. These equation always hold because $\unknown$
 is a subset of the left-hand side of both of the equations.
@@
 By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
-such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+such that $\mu\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
 where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. However, no pure
@@
 While the above example alerts that there might be a bad choice to
-represent our observations as a quantum IVPM, this phenomena is quantum,
-because Shapley proved that a good enough classical IVPM always has
-a non-empty core. \begin{thm}[Shapley~\citep{Shapley1971,Grabisch2016}]\label{thm:Shapley}Every
+represent our observations as a quantum IVPM, this phenomena is purely
+quantum, because Shapley proved that a good enough classical IVPM
+always has a non-empty core.
+
+\begin{thm}[Shapley~\citep{Shapley1971,Grabisch2016}]\label{thm:Shapley}Every
 classical convex interval-valued probability measure has a non-empty
@@
 is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\citep{Griffiths2003}.\end{thm}
-In general, we haven't found any classical IVPM having an empty core.
+
+Since any classical IVPM we found has a non-empty core, we conjecture
+that every classical IVPM has a non-empty core.
 

### 2017-03-26 prop_letter.tex
Updates from ShareLaTeX

--- 2017-03-26 prop_letter.tex
@@
 of a physical system whose state is represented by a density matrix~$\rho$,
-the probability to obtain the value $\lambda$ is determined by the
+the probability to obtain the value $\lambda$ of that property is determined by the
 Born rule $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
 where $P_{\lambda}$ denotes the projector onto the eigenspace corresponding
-to the eigenvalue $\lambda$ of the Hermitian operator $\mathbf{O}$~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
-
-In other words, any density matrix~$\rho$ defines a function $\mu_{\rho}^{\mathrm{\mathrm{B}}}$
-from the set of all projectors~$\events$ to $[0,1]$. This function~$\mu_{\rho}^{\mathrm{\mathrm{B}}}$
-is called a quantum probability measure because it satisfies the following
-probability axioms~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
+to the eigenvalue $\lambda$ of the Hermitian operator
+$\mathbf{O}$~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. 
+Alternatively, one may say that the state $\rho$ determines the 
+probability measure $\mu_{\rho}^{\mathrm{\mathrm{B}}}$ defined as a
+function from the set $\events$ of all possible projectors to the interval 
+$[0,1]$, and satisfies the following probability axioms~
+\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
 \begin{itemize}

### 2017-03-26 prop_letter.tex
prop_letter.tex Updated by Prof. Gerardo Ortiz...

@@
 probability measure $\mu_{\rho}^{\mathrm{\mathrm{B}}}$ defined as a
-function from the set $\events$ of all possible projectors to the interval 
+function from the set $\events$ of all possible projectors $P$ onto the interval 
 $[0,1]$, and satisfies the following probability axioms~
@@
 \item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{1})=1$. 
-\item For any projection $P$, $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\mathbb{1}-P\right)=1-\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)$. 
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\mathbb{1}-P\right)=
+1-\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)$. 
+\item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
+$P_iP_j=\delta_{ij}P_i$,
 we have 
 \begin{equation}
-\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
+\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\sum_{i=1}^{N}P_{i}\right)=
+\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{i}\right)
+\textrm{ .}\label{eq:QuantumProbability-Addition}
 \end{equation}
@@
 satisfying the above axioms, Gleason's theorem asserts that there
-exists a unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$
 in a Hilbert space of dimension $d\geq3$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 
-\paragraph{Quantum Interval-valued Probability Measure (IVPM)}
+\paragraph{Quantum Interval-valued Probability Measures ({\rm IVPMs})}
 
-In order to model the idea of finite precision measurement, we replace
-the infinity precise~$[0,1]$ by a collection of finite number of
-intervals~$\mathscr{I}$, and consider quantum IVPMs~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
-Based on the intuitive requirement, $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$,
-and operations on intervals,\begin{subequations}\label{eq:interval-operations}
+To formalize the idea of finite precision measurement, we next introduce 
+the notion of quantum IVPM~$\bar{\mu}$. The latter replaces 
+the infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$ of
+intervals. Since the intervals $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$ 
+should be included in $\mathscr{I}$, and arithmetic operations on intervals satisfy
+\begin{subequations}\label{eq:interval-operations}
 \begin{eqnarray}
- &  & \left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]\textrm{ and}\\
- &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]
+ &  & \left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right], \textrm{ and}\\
+ &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}] ,
 \end{eqnarray}
-\end{subequations}a quantum IVPM~$\bar{\mu}$ should satisfy corresponding
-axioms:
+\end{subequations}
+$\bar{\mu}:\events\rightarrow\mathscr{I}$ is defined by the axioms:
 \begin{itemize}
@@
 \item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
-\item For any projection $P$, 
-\begin{equation}
+\item 
+$
 \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
-\end{equation}
+$
 \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+$P_iP_j=\delta_{ij}P_i$, 
 we have 
@@
 The Kochen-Specker theorem asserts that there is no function~$v$
-assigning a definitely value to all observables such that \begin{subequations}
+assigning a definite value to all observables such that \begin{subequations}
 \label{eq:Kochen-Specker-Rules} 

### 2017-03-26 prop_letter.tex
prop_letter.tex \paragraph{Quantum Interval-valued Probability Measures ({\rm IVPMs})} Update a little bit...

@@
 \item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
-\item 
-$
-\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
-$
+\item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
 \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-$P_iP_j=\delta_{ij}P_i$, 
-we have 
+$P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
 \begin{equation}
@@
 example, if we consider $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $
-and $\bar{\mu}\left(P\right)=\left[l,r\right]$, by Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement})
-and (\ref{eq:interval-operations}), we have 
+and $\bar{\mu}\left(P\right)=\left[l,r\right]$, by Eq.~(\ref{eq:interval-operations}),
+we have 
 \[

### 2017-03-26 prop_letter.tex
prop_letter.tex Updaitng according to "APS Author Guide for REVTEX 4.1" until "V.7. Boxes"... I don't know how to handle \mbox so far...

@@
 \documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
-showkeys]{revtex4-1} 
+showkeys, longbibliography]{revtex4-1} 
 \usepackage{fullpage}
@@
 \affiliation{School of Informatics and Computing, Indiana University, Bloomington,
-IN 47405, USA}
+Indiana 47405, USA}
 
 \author{Gerardo Ortiz}
-\affiliation{Department of Physics, Indiana University, Bloomington, IN 47405,
+\affiliation{Department of Physics, Indiana University, Bloomington, Indiana 47405,
 USA}
@@
 \affiliation{School of Informatics and Computing, Indiana University, Bloomington,
-IN 47405, USA}
+Indiana 47405, USA}
 
 \author{Yu-Tsung Tai}
-\affiliation{Department of Mathematics, Indiana University, Bloomington, IN 47405,
+\affiliation{Department of Mathematics, Indiana University, Bloomington, Indiana 47405,
 USA}
 \affiliation{School of Informatics and Computing, Indiana University, Bloomington,
-IN 47405, USA}
+Indiana 47405, USA}
 
@@
 \item [{Background}] In a world of bounded resource, any quantum measurement
-can be only performed in finite precision. {\small \par}
+can be only performed in finite precision.
 \item [{Method}] We model the idea of the finite precision measurement
 as finite number of intervals, and replace quantum real-valued probability
-measures by interval-valued ones.{\small \par}
+measures by interval-valued ones.
 \item [{Results}] Quantum interval-valued probability measures provide
@@
 projectors, the interval-valued probability measures become classical,
-and these non-Born interval-valued probability measures disappear. {\small \par}
+and these non-Born interval-valued probability measures disappear.
 \item [{Conclusions}] Our research provides a new insight of finite precision
@@
 Also, the Born rule may not be as nature as we used to believe in
-the world of finite resource.{\small \par}
+the world of finite resource.
 \end{description}
@@
 the probability to obtain the value $\lambda$ of that property is determined by the
-Born rule $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
+Born rule $\mu_{\rho}^{\mathrm{B}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
 where $P_{\lambda}$ denotes the projector onto the eigenspace corresponding
 to the eigenvalue $\lambda$ of the Hermitian operator
-$\mathbf{O}$~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. 
+$\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}. 
 Alternatively, one may say that the state $\rho$ determines the 
-probability measure $\mu_{\rho}^{\mathrm{\mathrm{B}}}$ defined as a
+probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a
 function from the set $\events$ of all possible projectors $P$ onto the interval 
 $[0,1]$, and satisfies the following probability axioms~
-\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
+\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
 \begin{itemize}
-\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{0})=0$. 
-\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{1})=1$. 
-\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\mathbb{1}-P\right)=
-1-\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)$. 
+\item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
+\item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
+\item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
+1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
 \item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
@@
 \begin{equation}
-\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\sum_{i=1}^{N}P_{i}\right)=
-\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{i}\right)
+\mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
+\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
 \textrm{ .}\label{eq:QuantumProbability-Addition}
@@
 satisfying the above axioms, Gleason's theorem asserts that there
-exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$
-in a Hilbert space of dimension $d\geq3$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
+in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 
-\paragraph{Quantum Interval-valued Probability Measures ({\rm IVPMs})}
+\paragraph{Quantum Interval-valued Probability Measures (\emph{IVPMs})}
 
@@
 Although considering IVPM is new for a quantum theory, people have
-already defined classical IVPMs~\citep{JamisonLodwick2004}, which
+already defined classical IVPMs~\cite{JamisonLodwick2004}, which
 are essentially the same as quantum IVPMs on a restricted mutually
@@
 where Gleason's theorem is applied. However, it certainly contains
-richer phenomena. For example, we will show the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
+richer phenomena. For example, we will show the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
 is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
@@
 these two properties, it must send an observable to its eigenvalues
-so that the following observables~\citep{Mermin1990Simple,peres1995quantum}:
+so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
 \begin{equation}
@@
 IVPMs, we first need to find the common eigenbasis of each row and
-column, and consider the projections to each eigenvectors~\citep{Kernaghan1994,peres1995quantum}.
+column, and consider the projections to each eigenvectors~\cite{Kernaghan1994,peres1995quantum}.
 Let $\mathcal{T}_{24}$ denote all eigenstates listed in Table~\ref{table:commonBasis}.
@@
 \end{equation}
-Then, $\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}_{1}$
-is a quantum IVPM whose core has a unique element~$\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
+Then, $\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{B}}:\events\rightarrow\mathscr{I}_{1}$
+is a quantum IVPM whose core has a unique element~$\mu_{\ket{0}}^{\mathrm{B}}$,
 where $\circ$ denote function composition.
@@
 
-\begin{thm}[Shapley~\citep{Shapley1971,Grabisch2016}]\label{thm:Shapley}Every
+\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}Every
 classical convex interval-valued probability measure has a non-empty
@@
 for all commuting $P_{0},P_{1}\in\events$, and the \emph{disjunction}~$P_{0}\vee P_{1}$
-is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\citep{Griffiths2003}.\end{thm}
+is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.\end{thm}
 

### 2017-03-27 prop_letter.tex
prop_letter.tex Updated by Prof. Gerardo Ortiz...

@@
 \begin{equation}
-\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Inclusion}
 \end{equation}
 \end{itemize}
-Notice that Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
-to inclusion because the equality is usually too strong to hold. For
+condition that provides only a bound and not an equivalence as in Eq. 
+\eqref{eq:QuantumProbability-Addition}. For
 example, if we consider $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $
-and $\bar{\mu}\left(P\right)=\left[l,r\right]$, by Eq.~(\ref{eq:interval-operations}),
-we have 
+and $\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
 \[
-\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1+l-r,1+r-l\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)
+\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=
+\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right) .
 \]
-when $r>l$.
+
+Quantum IVPMs provide a unifying framework to account for 
+finite precision measurements in quantum physics. It has the desired 
+properties of turning into the classical IVPMs setup~\cite{JamisonLodwick2004}
+when the space of events includes only mutually commuting sub-events, and 
+of leading to the standard von Neumann projective measurement theory when 
+the collection of intervals are all singletons. To be more precise....
 
@@
 quantum real-valued probability measures which can be expressed a
-limiting case when the collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+limiting case when the collection of intervals are 
+all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
 where Gleason's theorem is applied. However, it certainly contains
-richer phenomena. For example, we will show the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
-is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+richer phenomena. For example, we will show the 
+Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
+is another limiting case when the collection of intervals are 
+$\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
 where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
@@
 
-The Kochen-Specker theorem asserts that there is no function~$v$
-assigning a definite value to all observables such that \begin{subequations}
+It asserts that there exists no function~$v$
+assigning definite values to all commuting observables, $\mathbf{O}_{j}$, such that 
+\begin{subequations}
 \label{eq:Kochen-Specker-Rules} 
 \begin{eqnarray}
- &  & v\left(\mathbf{O}_{1}\right)+v\left(\mathbf{O}_{2}\right)=v\left(\mathbf{O}_{1}+\mathbf{O}_{2}\right)\textrm{ and}\\
- &  & v\left(\mathbf{O}_{1}\right)v\left(\mathbf{O}_{2}\right)=v\left(\mathbf{O}_{1}\mathbf{O}_{2}\right)
+ &  & \sum_{j} v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j} \mathbf{O}_{j}\right)\textrm{ and}\\
+ &  & \prod_{j} v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right) .
 \end{eqnarray}
-\end{subequations} if $\mathbf{O}_{1}$ and $\mathbf{O}_{2}$ are
-commuting observables. Suppose that there is a function~$v$ satisfying
+\end{subequations} 
+Suppose that there is a function~$v$ satisfying
 these two properties, it must send an observable to its eigenvalues

### 2017-03-27 prop_letter.tex
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Updating...

@@
 
-It asserts that there exists no function~$v$
-assigning definite values to all commuting observables, $\mathbf{O}_{j}$, such that 
-\begin{subequations}
-\label{eq:Kochen-Specker-Rules} 
+It asserts that there exists no function~$v$ assigning definite
+values to all observables such that for any sequence of commuting
+observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
 \begin{eqnarray}
- &  & \sum_{j} v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j} \mathbf{O}_{j}\right)\textrm{ and}\\
- &  & \prod_{j} v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right) .
+ &  & \sum_{j}v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j}\mathbf{O}_{j}\right)\textrm{ and}\\
+ &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).
 \end{eqnarray}
-\end{subequations} 
-Suppose that there is a function~$v$ satisfying
+\end{subequations}Suppose that there is a function~$v$ satisfying
 these two properties, it must send an observable to its eigenvalues

### 2017-03-27 prop_letter.tex
prop_letter.tex Use "\usepackage{framed}" to replace "\fbox{...}"...

@@
 \usepackage[usenames,dvipsnames]{xcolor}
-\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}}}
-\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
+\usepackage{framed}
+\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
+\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}

### 2017-03-28 prop_letter.tex
prop_letter.tex Put packages "amsmath, amssymb" into class option.
prop_letter.tex \def\C{{\mathbb{C}}} Deleted to follow "APS Author Guide for REVTEX 4.1"
prop_letter.tex Use \text to replace \mbox
prop_letter.tex \begin{table*} Updating...

@@
 \documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
-showkeys, longbibliography]{revtex4-1} 
+showkeys, longbibliography, amsmath, amssymb]{revtex4-1} 
 \usepackage{fullpage}
@@
 \usepackage{babel}
-\usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{amsthm}
@@
 \newcommand{\pmeas}{\ensuremath{\mu}}
-\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
-\newcommand{\likely}{{\mbox{\wesa{likely}}}}
-\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
-\newcommand{\necess}{{\mbox{\wesa{certain}}}}
-\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
-\newcommand{\midd}{{\mbox{\wesa{middle}}}}
-\newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
+\newcommand{\imposs}{{\text{\wesa{impossible}}}}
+\newcommand{\likely}{{\text{\wesa{likely}}}}
+\newcommand{\unlikely}{{\text{\wesa{unlikely}}}}
+\newcommand{\necess}{{\text{\wesa{certain}}}}
+\newcommand{\unknown}{{\text{\wesa{unknown}}}}
+\newcommand{\midd}{{\text{\wesa{middle}}}}
+\usepackage[braket,qm]{qcircuit}
 \newcommand{\fket}[1]{{|#1\rangle}}
 \newcommand{\fproj}[1]{|#1\rangle\langle #1|}
-\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
 \newcommand{\proj}[1]{\op{#1}{#1}}
 \newcommand{\ps}{\texttt{+}}
-\newcommand{\minus}{\texttt{-}}
-\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}
+\newcommand{\ms}{\texttt{-}}
 
@@
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
-\def\C{{\mathbb{C}}}
 \newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
@@
 in the right column. In order to unify and simplify the notation,
-we do not normalize eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
-as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}
+we do not normalize eigenstates, and represent the state~$\alpha_{00}\ket{00}+\alpha_{01}\ket{01}+\alpha_{10}\ket{10}+\alpha_{11}\ket{11}$
+as $\left(\alpha_{00},\alpha_{01},\alpha_{10},\alpha_{11}\right)$.
+Also, to simplify the notation later, the projector onto each eigenstate
+is on the right of each eigenstate. A projector is named by its eigenstate
+if it is a product state, where $\ket{\ps}=\frac{1}{\sqrt{2}}\left(\ket{0}+\ket{1}\right)$
+and $\ket{\ms}=\frac{1}{\sqrt{2}}\left(\ket{0}-\ket{1}\right)$. For
+example, $P_{00}=\op{0}{0}$ and $P_{\ps\ms}=\op{\ps}{\ms}$. For
+the entangled states, $P_{\textrm{B}i}$ means it is one of the Bell
+basis, and $P_{\textrm{N}i}$ means it is not part of the Bell basis.}
 
@@
 \hline 
-$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$  & $(1,0,0,0)$  & $(0,1,0,0)$  & $(0,0,1,0)$  & $(0,0,0,1)$ \tabularnewline
-$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$  & $(1,1,1,1)$  & $(1,-1,1,-1)$  & $(1,1,-1,-1)$  & $(1,-1,-1,1)$ \tabularnewline
-$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(1,1,1,-1)$  & $(1,1,-1,1)$  & $(1,-1,1,1)$  & $(-1,1,1,1)$ \tabularnewline
-$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\mathbb{1}$  & $\sigma_{x}\otimes\sigma_{z}$  & $(1,0,1,0)$  & $(0,1,0,1)$  & $(1,0,-1,0)$  & $(0,1,0,-1)$ \tabularnewline
-$\sigma_{z}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{z}\otimes\sigma_{x}$  & $(1,1,0,0)$  & $(1,-1,0,0)$  & $(0,0,1,1)$  & $(0,0,1,-1)$ \tabularnewline
-$\sigma_{z}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(0,1,1,0)$  & $(0,1,-1,0)$  & $(1,0,0,1)$  & $(1,0,0,-1)$ \tabularnewline
+$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$  & $(1,0,0,0)\rightarrow P_{00}$  & $(0,1,0,0)\rightarrow P_{01}$  & $(0,0,1,0)\rightarrow P_{10}$  & $(0,0,0,1)\rightarrow P_{11}$ \tabularnewline
+$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$  & $(1,1,1,1)\rightarrow P_{\ps\ps}$  & $(1,-1,1,-1)\rightarrow P_{\ps\ms}$  & $(1,1,-1,-1)\rightarrow P_{\ms\ps}$  & $(1,-1,-1,1)\rightarrow P_{\ms\ms}$ \tabularnewline
+$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(1,1,1,-1)\rightarrow P_{\textrm{N}0}$  & $(1,1,-1,1)\rightarrow P_{\textrm{N}1}$  & $(1,-1,1,1)\rightarrow P_{\textrm{N}2}$  & $(-1,1,1,1)\rightarrow P_{\textrm{N}3}$ \tabularnewline
+$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\mathbb{1}$  & $\sigma_{x}\otimes\sigma_{z}$  & $(1,0,1,0)\rightarrow P_{\ps0}$  & $(0,1,0,1)\rightarrow P_{\ps1}$  & $(1,0,-1,0)\rightarrow P_{\ms0}$  & $(0,1,0,-1)\rightarrow P_{\ms1}$ \tabularnewline
+$\sigma_{z}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{z}\otimes\sigma_{x}$  & $(1,1,0,0)\rightarrow P_{0\ps}$  & $(1,-1,0,0)\rightarrow P_{0\ms}$  & $(0,0,1,1)\rightarrow P_{1\ps}$  & $(0,0,1,-1)\rightarrow P_{1\ms}$ \tabularnewline
+$\sigma_{z}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(0,1,1,0)\rightarrow P_{\textrm{B}0}$  & $(0,1,-1,0)\rightarrow P_{\textrm{B}1}$  & $(1,0,0,1)\rightarrow P_{\textrm{B}2}$  & $(1,0,0,-1)\rightarrow P_{\textrm{B}3}$ \tabularnewline
 \end{tabular}

### 2017-03-28 prop_letter.tex
prop_letter.tex Introduction Updating...
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Replace vector by projectors...

@@
 cannot be performed, and real measurements must be finite precision.
+In this paper, we model the quantum finite precision by quantum interval-valued
+probability measures (IVPMs). Under this framework,
+
 Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
@@
 \begin{eqnarray}
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
- &  & +\bar{f}(0,0,1,0)+\bar{f}(0,0,0,1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
- &  & +\bar{f}(0,0,1,1)+\bar{f}(0,0,1,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
- &  & +\bar{f}(0,1,0,1)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)\nonumber \\*
- &  & +\bar{f}(0,1,1,0)+\bar{f}(0,1,-1,0)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)\nonumber \\*
- &  & +\bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
- &  & +\bar{f}(1,0,1,0)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
- &  & +\bar{f}(0,1,1,0)+\bar{f}(1,0,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\nonumber \\*
- &  & +\bar{f}(0,0,1,1)+\bar{f}(1,-1,0,0)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)\nonumber \\*
- &  & +\bar{f}(1,1,1,1)+\bar{f}(1,-1,-1,1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)\nonumber \\*
- &  & +\bar{f}(1,1,1,1)+\bar{f}(1,1,-1,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
- &  & +\bar{f}(1,1,-1,-1)+\bar{f}(1,-1,-1,1)\textrm{ .}
+\necess & \subseteq & \bar{f}\left(P_{00}\right)+\bar{f}\left(P_{01}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{10}\right)+\bar{f}\left(P_{11}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{00}\right)+\bar{f}\left(P_{01}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{1\ps}\right)+\bar{f}\left(P_{1\ms}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{00}\right)+\bar{f}\left(P_{10}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{\ps1}\right)+\bar{f}\left(P_{\ms1}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{00}\right)+\bar{f}\left(P_{11}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{\textrm{B}0}\right)+\bar{f}\left(P_{\textrm{B}1}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{\textrm{N}3}\right)+\bar{f}\left(P_{\textrm{N}2}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{\textrm{N}1}\right)+\bar{f}\left(P_{\textrm{N}0}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{\textrm{N}3}\right)+\bar{f}\left(P_{\textrm{N}1}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{\ps0}\right)+\bar{f}\left(P_{\ms1}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{\textrm{N}2}\right)+\bar{f}\left(P_{\textrm{N}1}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{\textrm{B}0}\right)+\bar{f}\left(P_{\textrm{B}3}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{\textrm{N}1}\right)+\bar{f}\left(P_{\textrm{N}0}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{1\ps}\right)+\bar{f}\left(P_{0\ms}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{\textrm{B}1}\right)+\bar{f}\left(P_{\textrm{B}3}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{\ps\ps}\right)+\bar{f}\left(P_{\ms\ms}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{1\ms}\right)+\bar{f}\left(P_{0\ms}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{\ps\ps}\right)+\bar{f}\left(P_{\ms\ps}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{f}\left(P_{\ps0}\right)+\bar{f}\left(P_{\ps1}\right)\nonumber \\*
+ &  & +\bar{f}\left(P_{\ms\ps}\right)+\bar{f}\left(P_{\ms\ms}\right)\textrm{ .}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(1,1,-1,1)\nonumber \\
+\left[11,11\right] & \subseteq & 4\bar{f}\left(P_{00}\right)+4\bar{f}\left(P_{\textrm{N}1}\right)\nonumber \\
  &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
@@
 \begin{eqnarray}
-\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(1,1,-1,1),(1,-1,1,-1),\nonumber \\
- &  & (1,0,-1,0),(1,0,0,1),(1,1,0,0)\}\textrm{ .}
+\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{\left(P_{00}\right),\left(P_{\textrm{N}1}\right),\left(P_{\ps\ms}\right),\nonumber \\
+ &  & \left(P_{\ms0}\right),\left(P_{\textrm{B}2}\right),\left(P_{0\ps}\right)\}\textrm{ .}
 \end{eqnarray}

### 2017-03-28 prop_letter.tex
prop_letter.tex Replace every ket by projectors...

--- 2017-03-28 prop_letter.tex
@@
 column, and consider the projections to each eigenvectors~\cite{Kernaghan1994,peres1995quantum}.
-Let $\mathcal{T}_{24}$ denote all eigenstates listed in Table~\ref{table:commonBasis}.
-The Kochen-Specker theorem could then be proved by showing there is
-no function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $ satisfying
-equation~(\ref{eq:Kochen-Specker-Rules}), where 
+Let $\mathcal{T}_{24}$ denote the projectors onto each eigenstate
+listed in Table~\ref{table:commonBasis}. The Kochen-Specker theorem
+could then be proved by showing there is no function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
+satisfying equation~(\ref{eq:Kochen-Specker-Rules}), where 
 \begin{equation}
-\events_{24}=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\begin{gathered}\textrm{mutually orthogonal }\\
-\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}
-\end{gathered}
-}
+\events_{24}=\set{\sum_{i=1}^{N}P_{i}}{\textrm{orthogonal }\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
 \end{equation}
@@
 satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
-be a quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
-defined by $\bar{\mu}_{24}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
+be a quantum IVPM~$\bar{\mu}':\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
+defined by $\bar{\mu}'\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
 where 
@@
 \end{equation}
-Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
-defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}_{24}\left(\proj{\psi}\right)$
-satisfying the following conditions because the right-hand side of
-each equation forms an orthogonal basis and we can apply Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}\label{eq:Kernaghan}
-\begin{eqnarray}
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
- &  & +\bar{f}(0,0,1,0)+\bar{f}(0,0,0,1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
- &  & +\bar{f}(0,0,1,1)+\bar{f}(0,0,1,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
- &  & +\bar{f}(0,1,0,1)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)\nonumber \\*
- &  & +\bar{f}(0,1,1,0)+\bar{f}(0,1,-1,0)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)\nonumber \\*
- &  & +\bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
- &  & +\bar{f}(1,0,1,0)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
- &  & +\bar{f}(0,1,1,0)+\bar{f}(1,0,0,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\nonumber \\*
- &  & +\bar{f}(0,0,1,1)+\bar{f}(1,-1,0,0)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)\nonumber \\*
- &  & +\bar{f}(1,1,1,1)+\bar{f}(1,-1,-1,1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)\nonumber \\*
- &  & +\bar{f}(1,1,1,1)+\bar{f}(1,1,-1,-1)\textrm{ ,}\\
-\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
- &  & +\bar{f}(1,1,-1,-1)+\bar{f}(1,-1,-1,1)\textrm{ .}
-\end{eqnarray}
-\end{subequations}If we sum up Eq.~(\ref{eq:Kernaghan}), we will
-have
-\begin{eqnarray}
-\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(1,1,-1,1)\nonumber \\
- &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
-\end{eqnarray}
+Because the right-hand side of each equation forms an orthogonal basis,
+we can apply Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+and have the following conditions
+\begin{eqnarray*}
+\necess & \subseteq & \bar{\mu}'\left(P_{00}\right)+\bar{\mu}'\left(P_{01}\right)+\bar{\mu}'\left(P_{10}\right)+\bar{\mu}'\left(P_{11}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{00}\right)+\bar{\mu}'\left(P_{01}\right)+\bar{\mu}'\left(P_{1\ps}\right)+\bar{\mu}'\left(P_{1\ms}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{00}\right)+\bar{\mu}'\left(P_{10}\right)+\bar{\mu}'\left(P_{\ps1}\right)+\bar{\mu}'\left(P_{\ms1}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{00}\right)+\bar{\mu}'\left(P_{11}\right)+\bar{\mu}'\left(P_{\textrm{B}0}\right)+\bar{\mu}'\left(P_{\textrm{B}1}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{N}3}\right)+\bar{\mu}'\left(P_{\textrm{N}2}\right)+\bar{\mu}'\left(P_{\textrm{N}1}\right)+\bar{\mu}'\left(P_{\textrm{N}0}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{N}3}\right)+\bar{\mu}'\left(P_{\textrm{N}1}\right)+\bar{\mu}'\left(P_{\ps0}\right)+\bar{\mu}'\left(P_{\ms1}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{N}2}\right)+\bar{\mu}'\left(P_{\textrm{N}1}\right)+\bar{\mu}'\left(P_{\textrm{B}0}\right)+\bar{\mu}'\left(P_{\textrm{B}3}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{N}1}\right)+\bar{\mu}'\left(P_{\textrm{N}0}\right)+\bar{\mu}'\left(P_{1\ps}\right)+\bar{\mu}'\left(P_{0\ms}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{B}1}\right)+\bar{\mu}'\left(P_{\textrm{B}3}\right)+\bar{\mu}'\left(P_{\ps\ps}\right)+\bar{\mu}'\left(P_{\ms\ms}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{1\ms}\right)+\bar{\mu}'\left(P_{0\ms}\right)+\bar{\mu}'\left(P_{\ps\ps}\right)+\bar{\mu}'\left(P_{\ms\ps}\right)\textrm{ ,}\\
+\necess & \subseteq & \bar{\mu}'\left(P_{\ps0}\right)+\bar{\mu}'\left(P_{\ps1}\right)+\bar{\mu}'\left(P_{\ms\ps}\right)+\bar{\mu}'\left(P_{\ms\ms}\right)\textrm{ .}
+\end{eqnarray*}
+If we sum up the preceding equations, we will have
+\begin{equation}
+\left[11,11\right]\subseteq4\bar{\mu}'\left(P_{00}\right)+4\bar{\mu}'\left(P_{\textrm{N}1}\right)+2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{\mu}'\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
+\end{equation}
 where 
-\begin{eqnarray}
-\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(1,1,-1,1),(1,-1,1,-1),\nonumber \\
- &  & (1,0,-1,0),(1,0,0,1),(1,1,0,0)\}\textrm{ .}
-\end{eqnarray}
+\begin{equation}
+\mathcal{T}_{18}=\mathcal{T}_{24}\backslash\{P_{00},P_{\textrm{N}1},P_{\ps\ms},P_{\ms0},P_{\textrm{B}2},P_{0\ps}\}\textrm{ .}
+\end{equation}
 However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
@@
 side is a singleton set of an even integer while the left-hand side
-is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
+is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}':\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
 Moreover, there is no quantum IVPM defined on the set of all projectors
 as well; otherwise, if we have a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
-then we can restrict $\bar{\mu}$ and define $\bar{\mu}_{24}=\left.\bar{\mu}\right|_{\events_{24}}$.
+then we can restrict $\bar{\mu}$ and define $\bar{\mu}'=\left.\bar{\mu}\right|_{\events_{24}}$.
 
@@
 measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
-basis~$\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $ as defined
-in Table~\ref{table:commonBasis}. Let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
-$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$. Then, we can
-define a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{1}$
-as follow:\begin{subequations} 
-\begin{eqnarray}
-\imposs & = & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})\nonumber \\*
- & = & \bar{\mu}(\proj{\ps'})\textrm{ ,}\\
-\necess & = & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})\nonumber \\*
- & = & \bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}\\
-\unknown & = & \bar{\mu}(P)\qquad\textrm{otherwise.}
-\end{eqnarray}
-\end{subequations}
+basis~$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $ as
+defined in Table~\ref{table:commonBasis}. Then, we can define a
+quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{1}$ as follow:
+\begin{eqnarray*}
+ &  & \imposs=\bar{\mu}(\mathbb{0})=\bar{\mu}(P_{00})=\bar{\mu}(P_{0\ps})=\bar{\mu}(P_{\ps0})\textrm{ ,}\\
+ &  & \necess=\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-P_{00})=\bar{\mu}(\mathbb{1}-P_{0\ps})=\bar{\mu}(\mathbb{1}-P_{\ps0})\textrm{ ,}\\
+ &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
+\end{eqnarray*}
 
@@
 \begin{equation}
-\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
+\mu(P_{00})=\mu(P_{0\ps})=\mu(P_{\ps0})=0\textrm{ .}\label{eq:probability-zero-on-states}
 \end{equation}
@@
 where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. However, no pure
-state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
+state~$\ket{\phi}$ satisfies $\ip{\phi}{00}=\ip{\phi}{0\ps}=\ip{\phi}{\ps0}=0$
 so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability

### 2017-03-29 prop_letter.tex
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Add a footnote...

@@
 
-It asserts that there exists no function~$v$ assigning definite
-values to all observables such that for any sequence of commuting
-observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
+It asserts that there exists no function~$v$~\footnote{\yutsung{In Kochen-Specker's original paper~\cite{kochenspecker1967},
+they use $\mathcal{E}$. In The Stanford Encyclopedia of Philosophy~\cite{Held2016},
+they use $v$. I think it is less confusion to use $v$ here.}} assigning definite values to all observables such that for any sequence
+of commuting observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
 \begin{eqnarray}

### 2017-03-29 prop_letter.tex
prop_letter.tex Introduction Updating...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Even if quantum mechanics is invented for more than 60 years, quantum
+measurement is still a mystery and a source of different interpretations
+and non-classical phenomena, including non-locality and contextuality.
+In contrast to the idealized measurement process, an actual experiment
+is bounded by resources and must be finite precision. Whether finite
+precision measurement in reality affect the idealized quantum concept,
+e.g., contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
+and the very foundation of quantum mechanics is still a problem. In
+this letter, we model the finite precision quantum measurement by
+quantum interval-valued probability measures (IVPMs). Quantum IVPM
+provides not only a uniform framework to understand Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
+and the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
+but also some examples which cannot be explained by the Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+
 Textbook quantum mechanics asserts that the probability of a measurement
@@
 cannot be performed, and real measurements must be finite precision.
-In this paper, we model the quantum finite precision by quantum interval-valued
-probability measures (IVPMs). Under this framework,
+In this paper,
 

### 2017-03-29 prop_letter.tex
prop_letter.tex Introduction Updating...

--- 2017-03-29 prop_letter.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Even if quantum mechanics is invented for more than 60 years, mysterious
+quantum measurement is still a source of different interpretations
+and non-classical phenomena, including non-locality and contextuality~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
+In contrast to the idealized measurement process, an actual experiment
+is bounded by resources and must be finite precision. Whether finite
+precision measurement in reality affect the idealized quantum concept,
+e.g., contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
+and the very foundation of quantum mechanics is still a problem. In
+this letter, we model the finite precision quantum measurement by
+quantum interval-valued probability measures (IVPMs) which provides
+not only a uniform framework to understand Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
+and the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
+but also some examples which cannot be explained by the Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+
 Textbook quantum mechanics asserts that the probability of a measurement
@@
 cannot be performed, and real measurements must be finite precision.
-In this paper, we model the quantum finite precision by quantum interval-valued
-probability measures (IVPMs). Under this framework,
-
 Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
@@
 is also crucial for understanding the very nature of physical processes.
-However, it is not evident at all that this resource-aware perspective
-does not alter the very foundations of quantum mechanics. In order
-to analyze the quantum world with finite resource, we extend the classical
-interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
+The tension between finite precision measurement and the foundation
+of quantum mechanics sharpened when Meyer~\cite{PhysRevLett.83.3751}
+and Kent~\cite{Kent1999} proved the original definition of contextuality
+based on infinitely precised complex numbers cannot be experimental
+verified. There were a long debate about whether contextuality could
+be experimental verified or not~\cite{Mermin1999,Peres2003,BarrettKent2004}.
+
+In order to analyze the quantum world with finite resource, we extend
+the classical interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
 and introduce a new framework: quantum IVPM...\newpage{}

### 2017-03-29 prop_letter.tex
prop_letter.tex Intorduction Updating...

@@
 observable \emph{exactly}. In reality, an actual experiment is bounded
-by space, time, energy, and other resources so that an perfect measurement
-cannot be performed, and real measurements must be finite precision.
-Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
-and others, one might argue that this resource-bounded perspective
-is also crucial for understanding the very nature of physical processes.
-The tension between finite precision measurement and the foundation
-of quantum mechanics sharpened when Meyer~\cite{PhysRevLett.83.3751}
+by space, time, energy, and other resources so that real measurements
+must be finite precision. The tension between finite precision measurement
+and the foundation of quantum mechanics sharpened when Meyer~\cite{PhysRevLett.83.3751}
 and Kent~\cite{Kent1999} proved the original definition of contextuality
@@
 be experimental verified or not~\cite{Mermin1999,Peres2003,BarrettKent2004}.
+After the debates, people are still trying to update the definition
+of contextuality when they want to perform further experiment~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 

### 2017-03-30 prop_letter.tex
prop_letter.tex Updating...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Even if quantum mechanics is invented for more than 60 years, mysterious
-quantum measurement is still a source of different interpretations
-and non-classical phenomena, including non-locality and contextuality~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
-In contrast to the idealized measurement process, an actual experiment
-is bounded by resources and must be finite precision. Whether finite
-precision measurement in reality affect the idealized quantum concept,
-e.g., contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
+Textbook quantum mechanics asserts that the probability of a measurement
+can be computed from wave function of the system and the measuring
+observable \emph{exactly} while real measurements must be finite precision.
+Whether finite precision measurement in reality affect the idealized
+quantum concept, e.g., contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
 and the very foundation of quantum mechanics is still a problem. In
@@
 
-Textbook quantum mechanics asserts that the probability of a measurement
-can be computed from wave function of the system and the measuring
-observable \emph{exactly}. In reality, an actual experiment is bounded
-by space, time, energy, and other resources so that real measurements
-must be finite precision. The tension between finite precision measurement
-and the foundation of quantum mechanics sharpened when Meyer~\cite{PhysRevLett.83.3751}
-and Kent~\cite{Kent1999} proved the original definition of contextuality
-based on infinitely precised complex numbers cannot be experimental
-verified. There were a long debate about whether contextuality could
-be experimental verified or not~\cite{Mermin1999,Peres2003,BarrettKent2004}.
-After the debates, people are still trying to update the definition
-of contextuality when they want to perform further experiment~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+The tension between finite precision measurement and the foundation
+of quantum mechanics sharpened when the original definition of contextuality
+based on infinitely precised numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
+After a long debate~\cite{Mermin1999,Peres2003,BarrettKent2004},
+people are still trying to update the definition of contextuality
+when they want to perform further experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
-In order to analyze the quantum world with finite resource, we extend
-the classical interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
-and introduce a new framework: quantum IVPM...\newpage{}
+We found that finite precision measurement affects not only contextuality
+but also the fundamental rule computing probability from a state.
+In the early formulation of quantum mechanics, von Neumann essentially
+formulated a quantum state as a density matrix while Mackey formulated
+a quantum state as a probability measure which are proved to be the
+same as a density matrix by Gleason's theorem~\cite{Varadarajan2008}.
+If we follow Mackey's idea of probability measures together with the
+classical IVPM~\cite{JamisonLodwick2004} which could be used to
+formulate finite precision measurement in classical situation, we
+can define quantum IVPMs. Surprisingly, there is a quantum IVPM which
+can not be induced by a density matrix according to the Born rule.
+Similar to the tension between finite precision and contextuality
+are still inspiring experimental testable definition of contextuality,
+the very basic definition of a quantum state or how to compute the
+probability from a state might need to be refined when we consider
+the finite precision measurement. \newpage{}
 

### 2017-03-30 prop_letter.tex
prop_letter.tex Introduction Updating...

@@
 The tension between finite precision measurement and the foundation
-of quantum mechanics sharpened when the original definition of contextuality
+of quantum mechanics sharpened, when the original definition of contextuality
 based on infinitely precised numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
@@
 formulated a quantum state as a density matrix while Mackey formulated
-a quantum state as a probability measure which are proved to be the
-same as a density matrix by Gleason's theorem~\cite{Varadarajan2008}.
-If we follow Mackey's idea of probability measures together with the
-classical IVPM~\cite{JamisonLodwick2004} which could be used to
-formulate finite precision measurement in classical situation, we
-can define quantum IVPMs. Surprisingly, there is a quantum IVPM which
-can not be induced by a density matrix according to the Born rule.
-Similar to the tension between finite precision and contextuality
-are still inspiring experimental testable definition of contextuality,
-the very basic definition of a quantum state or how to compute the
-probability from a state might need to be refined when we consider
-the finite precision measurement. \newpage{}
+a quantum state as a quantum probability measure which are proved
+by Gleason to be the essentially same as a density matrix~\cite{Varadarajan2008}.
+Combining quantum probability measures and the classical IVPM~\cite{JamisonLodwick2004}
+which could be used to formulate classical finite precision measurement,
+we can define quantum IVPMs. Surprisingly, there is a quantum IVPM
+which cannot be compatible with any density matrix according to the
+Born rule. Similar to revising the definition of contextuality because
+of finite precision measurement, the very basic definition of a quantum
+state or how to compute the probability from a state might need to
+be refined when we consider the finite precision measurement. This
+can also provides a new quantum phenomena different from the classical
+world, because IVPMs become classical so that the non-Born IVPMs disappears
+when we restricting the domain of quantum IVPMs on a commuting sub-event
+space. \newpage{}
 

### 2017-03-30 prop_letter.tex
From: Tai, Yu-Tsung Sent: Thursday, March 30, 2017 1:41 To: Hanson, Andrew J. <hansona@indiana.edu> Subject: RE: a talk might be of interest to your department
How about something like this?
===
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly} while real measurements must be finite
precision.
Whether finite precision measurement in reality affect the idealized
quantum concept, e.g.,
contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
and the very foundation of q

@@
 of quantum mechanics sharpened, when the original definition of contextuality
-based on infinitely precised numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
+based on infinitely precise numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
 After a long debate~\cite{Mermin1999,Peres2003,BarrettKent2004},
@@
 be refined when we consider the finite precision measurement. This
-can also provides a new quantum phenomena different from the classical
+can also provide a new quantum phenomena different from the classical
 world, because IVPMs become classical so that the non-Born IVPMs disappears

### 2017-03-31 prop_letter.tex
prop_letter.tex \paragraph{Gleason's Theorem} Updating...

@@
 of a physical system whose state is represented by a density matrix~$\rho$,
-the probability to obtain the value $\lambda$ of that property is determined by the
-Born rule $\mu_{\rho}^{\mathrm{B}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
-where $P_{\lambda}$ denotes the projector onto the eigenspace corresponding
-to the eigenvalue $\lambda$ of the Hermitian operator
-$\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}. 
-Alternatively, one may say that the state $\rho$ determines the 
-probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a
-function from the set $\events$ of all possible projectors $P$ onto the interval 
-$[0,1]$, and satisfies the following probability axioms~
-\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
+the probability to obtain the value $\lambda$ of that property is
+determined by the Born rule $\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho P_{i}\right)$,
+where $P_{i}$ denotes the projector onto the eigenspace corresponding
+to the eigenvalue $\lambda_{i}$ of the Hermitian operator $\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+Alternatively, one may say that the state $\rho$ determines the probability
+measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function from the
+set $\events$ of all possible projectors $P$ onto the interval $[0,1]$,
+and satisfies the following probability axioms~ \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
 \begin{itemize}

### 2017-04-05 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

@@
 Recall we model the idea of the finite precision measurement as IVPM.
+Since the Born rule is the rule to compute the probability providing
+infinity measurement resource, it would be nature to ask whether quantum
+IVPM would approach the Born rule if we increase the measurement resource.
+In order to understand this question, it is instructive to consider
+the non-Born real-valued probability measure when $d=2$.
+
+\begin{example}[One-qubit quantum probability measure]Consider a
+quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
+as follow: 
+\[
+\mu(P)=\begin{cases}
+\mu_{\ket{\ps}}^{B}(P) & \textrm{, if }P=\proj{\ps}\textrm{ or }\proj{\ms}\textrm{ ;}\\
+\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
+\end{cases}
+\]
+Notice that $\mu$ is consistent with the Born rule, but computed
+according to different states when applying on different projectors.\qed\end{example}
+
+\newpage{}
+
+Recall we model the idea of the finite precision measurement as IVPM.
 When we made finite number of observations, we can use some quantum

### 2017-04-06 prop_letter.tex
prop_letter.tex Here and there...

--- 2017-03-31 prop_letter.tex
@@
 
-Quantum IVPMs provide a unifying framework to account for 
-finite precision measurements in quantum physics. It has the desired 
-properties of turning into the classical IVPMs setup~\cite{JamisonLodwick2004}
-when the space of events includes only mutually commuting sub-events, and 
-of leading to the standard von Neumann projective measurement theory when 
-the collection of intervals are all singletons. To be more precise....
+Quantum IVPMs provide a unifying framework to account for finite precision
+measurements in quantum physics. It has the desired properties of
+turning into the classical IVPMs setup~\cite{JamisonLodwick2004}
+when the space of events includes only mutually commuting sub-events,
+and of leading to the standard von Neumann projective measurement
+theory when the collection of intervals are all singletons. To be
+more precise....\newpage{}
 
@@
 Quantum IVPM not only stems from classical IVPM but also generalizes
-quantum real-valued probability measures which can be expressed a
-limiting case when the collection of intervals are 
-all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-where Gleason's theorem is applied. However, it certainly contains
-richer phenomena. For example, we will show the 
-Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
-is another limiting case when the collection of intervals are 
-$\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+quantum real-valued probability measures. Consider the collection
+of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
+defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. Then,
+given a quantum real value probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
+$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM, and vice
+versa. In another word, when quantum IVPMs with $\mathscr{I}_{\infty}$
+are just the same as quantum real-valued probability measures which
+can fit Gleason's theorem.
+
+However, quantum IVPMs certainly contains richer phenomena. For example,
+we will show the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
+is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
 where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
@@
 
+Recall when providing infinity measurement resource, the quantum probability
+measures are simply induced by the Born rule for $d\ge3$. If we increase
+the measurement resource, i.e., pick finer intervals when constructing
+IVPMs, it would be natural to ask whether quantum IVPMs would approach
+the Born rule. In order to understand this question, it is instructive
+to consider the 2-dimensional non-Born quantum probability measure~$\mu:\events\rightarrow[0,1]$
+defined as follow:
+\begin{equation}
+\mu(P)=\begin{cases}
+\mu_{\ket{\ps}}^{B}(P) & \textrm{, if }P=\proj{\ps}\textrm{ or }\proj{\ms}\textrm{ ;}\\
+\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
+\end{cases}
+\end{equation}
+Notice that $\mu$ is consistent with the Born rule partially, because
+it is computed according to different states when applying on different
+projectors. \newpage{}
+
 Recall we model the idea of the finite precision measurement as IVPM.

### 2017-04-06 prop_letter.tex
prop_letter.tex Here and there...

@@
 defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. Then,
-given a quantum real value probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
+given a quantum real-valued probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
 $\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM, and vice
-versa. In another word, when quantum IVPMs with $\mathscr{I}_{\infty}$
-are just the same as quantum real-valued probability measures which
-can fit Gleason's theorem.
+versa. In another word, quantum IVPMs with $\mathscr{I}_{\infty}$
+are just the same as quantum real-valued probability measures where
+Gleason's theorem can apply.
 
-However, quantum IVPMs certainly contains richer phenomena. For example,
-we will show the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
-is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
-in the next paragraph.
+$\mathscr{I}_{\infty}$ is one extreme case of quantum IVPM; another
+extreme case happens when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
+This is the case where the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
+can be applied and will be explained in the next paragraph.
 
@@
 measures are simply induced by the Born rule for $d\ge3$. If we increase
-the measurement resource, i.e., pick finer intervals when constructing
-IVPMs, it would be natural to ask whether quantum IVPMs would approach
-the Born rule. In order to understand this question, it is instructive
-to consider the 2-dimensional non-Born quantum probability measure~$\mu:\events\rightarrow[0,1]$
-defined as follow:
+the measurement resource, i.e., pick finer intervals, it is natural
+to ask whether quantum IVPMs approach the Born rule. In order to understand
+this question, it is instructive to consider the 2-dimensional non-Born
+quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
+as follow:
 \begin{equation}
-\mu(P)=\begin{cases}
-\mu_{\ket{\ps}}^{B}(P) & \textrm{, if }P=\proj{\ps}\textrm{ or }\proj{\ms}\textrm{ ;}\\
-\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
+\mu_{0}(P)=\begin{cases}
+\mu_{\ket{\ps}}^{B}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
+\mu_{\ket{0}}^{B}(P) & \textrm{, otherwis,}
 \end{cases}
 \end{equation}
-Notice that $\mu$ is consistent with the Born rule partially, because
-it is computed according to different states when applying on different
-projectors. \newpage{}
+where $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
+is a sub-event space. In another word, $\mu_{0}$ is consistent with
+the Born rule on every proper sub-event space, but not on the set
+of all projectors.
+
+Given a quantum IVPM~$\bar{\mu}$, the preceding idea motivates the
+definition of \emph{core} relative to a sub-event space~$\events'$
+as follow.
+\begin{equation}
+\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{B}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
+\end{equation}
+Although the elements of a core are density matrices, we may just
+use the state vectors for pure states if it is clear in the context.
+For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \ket{\ps}\right\} $,
+where $\circ$ denote function composition.\newpage{}
 

### 2017-04-06 prop_letter.tex
prop_letter.tex Here and there...

@@
 \item $\mathbb{1}\in\events'$. 
-\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
+\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
+\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
 we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
@@
 given a quantum real-valued probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
-$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM, and vice
-versa. In another word, quantum IVPMs with $\mathscr{I}_{\infty}$
+$\bar{\mu}(P)=\iota_{\infty}\left(\mu(P)\right)$ is a quantum IVPM,
+and vice versa. In another word, quantum IVPMs with $\mathscr{I}_{\infty}$
 are just the same as quantum real-valued probability measures where
@@
 this question, it is instructive to consider the 2-dimensional non-Born
-quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
+quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$ defined
 as follow:
@@
 Given a quantum IVPM~$\bar{\mu}$, the preceding idea motivates the
-definition of \emph{core} relative to a sub-event space~$\events'$
+definition of \emph{core} relative to a sub-event space~$\events'\subseteq\events$
 as follow.
@@
 use the state vectors for pure states if it is clear in the context.
-For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \ket{\ps}\right\} $,
-where $\circ$ denote function composition.\newpage{}
+For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \ket{\ps}\right\} $
+and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right)=\emptyset$,
+where $\circ$ denote function composition.
+
+Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
+to $\events_{0}$ where every projectors are mutually commutative.
+Recall commutative sub-event space reduces quantum IVPMs to classical
+IVPMs. In general, we haven't found any classical IVPM has a non-empty
+core, and Shapley has proved that a good enough classical IVPM always
+has a non-empty core.
+
+\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
+every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
+if the following conditions are true.
+\begin{itemize}
+\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
+\item For all commuting $P_{0},P_{1}\in\events$, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
+where $P_{0}\vee P_{1}$ is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
+\end{itemize}
+Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
+
+\newpage{}
 
@@
 
-While the above example alerts that there might be a bad choice to
-represent our observations as a quantum IVPM, this phenomena is purely
-quantum, because Shapley proved that a good enough classical IVPM
-always has a non-empty core.
-
-\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}Every
-classical convex interval-valued probability measure has a non-empty
-core, where $\bar{\mu}$ is called convex if 
-\begin{equation}
-\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
-\end{equation}
-for all commuting $P_{0},P_{1}\in\events$, and the \emph{disjunction}~$P_{0}\vee P_{1}$
-is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.\end{thm}
-
-Since any classical IVPM we found has a non-empty core, we conjecture
-that every classical IVPM has a non-empty core.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-04-06 prop_letter.tex
prop_letter.tex Here and there...

@@
 quantum real-valued probability measures. Consider the collection
-of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+of all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
 and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
@@
 $\bar{\mu}(P)=\iota_{\infty}\left(\mu(P)\right)$ is a quantum IVPM,
-and vice versa. In another word, quantum IVPMs with $\mathscr{I}_{\infty}$
+and vice versa. In another word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$
 are just the same as quantum real-valued probability measures where
@@
 
-$\mathscr{I}_{\infty}$ is one extreme case of quantum IVPM; another
-extreme case happens when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
+While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
+IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
+is another one, where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
 This is the case where the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
@@
 Although the elements of a core are density matrices, we may just
-use the state vectors for pure states if it is clear in the context.
-For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \ket{\ps}\right\} $
+use the state vectors for pure states if it is clear according to
+the context. For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \ket{\ps}\right\} $
 and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right)=\emptyset$,
@@
 Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
-to $\events_{0}$ where every projectors are mutually commutative.
-Recall commutative sub-event space reduces quantum IVPMs to classical
-IVPMs. In general, we haven't found any classical IVPM has a non-empty
-core, and Shapley has proved that a good enough classical IVPM always
-has a non-empty core.
+to $\events_{0}$ which is commutative. Recall a commutative sub-event
+space reduces quantum IVPMs to classical IVPMs. In general, we haven't
+found any classical IVPM has an empty core, and Shapley proved that
+a good enough classical IVPM always has a non-empty core.
 
@@
 Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
+
+In the language of core, Gleason's theorem states that $\mathrm{core}\left(\bar{\mu},\events\right)$
+has a unique element for any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$
+when $d\ge3$.
 

### 2017-04-07 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

@@
 has a unique element for any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$
-when $d\ge3$.
-
-\newpage{}
-
-Recall we model the idea of the finite precision measurement as IVPM.
-When we made finite number of observations, we can use some quantum
-IVPMs to represent what we observed. Given a quantum IVPM~$\bar{\mu}$,
-the question is whether we can refine precisely enough to determine
-the underlying unknown quantum real-valued probability measure, i.e.,
-a quantum state. If we can, we say $\bar{\mu}$ has a non-empty core.
-More precisely, A \emph{core} of $\bar{\mu}$, $\mathrm{core}\left(\bar{\mu}\right)$,
-is the set 
+when $d\ge3$. However, when we only have finite resources, a quantum
+IVPM may be identified to more than one states on different sub-event
+spaces. The simplest example add an one extra interval~$\unknown=\left[0,1\right]$
+to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
+Then, 
 \begin{equation}
-\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
-\end{equation}
-For example, we can add an one extra interval~$\unknown=\left[0,1\right]$
-to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
-Let 
-\begin{equation}
-\iota_{1}(x)=\begin{cases}
-\necess & \text{, if }x=1\text{ ;}\\
-\imposs & \text{, if }x=0\text{ ;}\\
+\bar{\mu}_{1}\left(P\right)=\begin{cases}
+\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
+\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
 \unknown & \text{, otherwise.}
@@
 \end{equation}
-Then, $\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{B}}:\events\rightarrow\mathscr{I}_{1}$
-is a quantum IVPM whose core has a unique element~$\mu_{\ket{0}}^{\mathrm{B}}$,
-where $\circ$ denote function composition.
-
-However, not every quantum IVPM well represents our observations.
-The following example provides a quantum IVPM with an empty core,
-i.e., it cannot be further refined to get the underlying unknown quantum
-states.
+provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
+contains every quantum real-valued probability measure on $\events'$.
+The following is a more sophisticating example.
 
@@
 basis~$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $ as
-defined in Table~\ref{table:commonBasis}. Then, we can define a
-quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{1}$ as follow:
+defined in Table~\ref{table:commonBasis}. Let
 \begin{eqnarray*}
@@
 \end{eqnarray*}
+It is straightforward to verify that $\bar{\mu}$ is a quantum IVPM.
 
-To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
-implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
-implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
-Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-it is sufficient to check \begin{subequations} 
-\begin{eqnarray}
- &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\nonumber \\*
- & \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
- &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\nonumber \\*
- & \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
-\end{eqnarray}
-\end{subequations} for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$,
-and $\ket{\psi_{2}}$. These equation always hold because $\unknown$
-is a subset of the left-hand side of both of the equations.
+\newpage{}
 

### 2017-04-07 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

@@
 
-Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
-to $\events_{0}$ which is commutative. Recall a commutative sub-event
-space reduces quantum IVPMs to classical IVPMs. In general, we haven't
-found any classical IVPM has an empty core, and Shapley proved that
-a good enough classical IVPM always has a non-empty core.
-
-\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
-every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
-if the following conditions are true.
-\begin{itemize}
-\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
-\item For all commuting $P_{0},P_{1}\in\events$, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
-where $P_{0}\vee P_{1}$ is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
-\end{itemize}
-Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
-
-In the language of core, Gleason's theorem states that $\mathrm{core}\left(\bar{\mu},\events\right)$
-has a unique element for any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$
-when $d\ge3$. However, when we only have finite resources, a quantum
-IVPM may be identified to more than one states on different sub-event
-spaces. The simplest example add an one extra interval~$\unknown=\left[0,1\right]$
+Notice that $\iota_{\infty}\circ\mu_{0}$ has different core element
+relative to different sub-event spaces so that it has an empty core
+relative to all projectors~$\events$. When $d\ge3$, if we have
+infinite measurement resource and consider $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
+by Gleason's theorem, $\mathrm{core}\left(\bar{\mu},\events\right)$
+has a unique element, i.e., we can always identify a unique state.
+However, when we only have finite resources, we usually can only identify
+a quantum IVPM to more than one states on different sub-event spaces.
+The simplest example add an one extra interval~$\unknown=\left[0,1\right]$
 to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
-Then, 
+Then, the quantum IVPM
 \begin{equation}
@@
 provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
-contains every quantum real-valued probability measure on $\events'$.
-The following is a more sophisticating example.
+contains every density matrix. A more sophisticating example is the
+following.
 
@@
 
+\newpage{}
+
+Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty
+core relative to $\events_{0}$ which is commutative. In general,
+a commutative sub-event space reduces quantum IVPMs to classical IVPMs.
+We haven't found any classical IVPM has an empty core, and Shapley
+proved that a good enough classical IVPM always has a non-empty core.
+
+\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
+every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
+if the following conditions are true.
+\begin{itemize}
+\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
+\item For all commuting $P_{0},P_{1}\in\events$, 
+\[
+\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}
+\]
+where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
+\end{itemize}
+Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-04-07 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Before roll-back to d=3...

@@
 
-Notice that $\iota_{\infty}\circ\mu_{0}$ has different core element
+Notice that $\iota_{\infty}\circ\mu_{0}$ has different core elements
 relative to different sub-event spaces so that it has an empty core
@@
 a quantum IVPM to more than one states on different sub-event spaces.
-The simplest example add an one extra interval~$\unknown=\left[0,1\right]$
+The simplest example add one extra interval~$\unknown=\left[0,1\right]$
 to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.

### 2017-04-07 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Starting roll-back to d=3...

@@
 contains every density matrix. A more sophisticating example is the
-following.
+following.\footnote{\yutsung{It seems that our example in 4 dimensions together with
+relativity core would be unnecessary complex. Therefore, I roll our
+example back to 3 dimensions.}}
 
-\begin{example}[Four-dimensional quantum three-interval-valued probability
-measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
-basis~$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $ as
-defined in Table~\ref{table:commonBasis}. Let
-\begin{eqnarray*}
- &  & \imposs=\bar{\mu}(\mathbb{0})=\bar{\mu}(P_{00})=\bar{\mu}(P_{0\ps})=\bar{\mu}(P_{\ps0})\textrm{ ,}\\
- &  & \necess=\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-P_{00})=\bar{\mu}(\mathbb{1}-P_{0\ps})=\bar{\mu}(\mathbb{1}-P_{\ps0})\textrm{ ,}\\
+\begin{example}[Three-dimensional quantum three-interval-valued probability
+measure]\label{ex:three-dimensional-three-value} Given a three dimensional
+Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
+$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
+\begin{eqnarray}
+ &  & \begin{split}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
+ & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\textrm{ ,}
+\end{split}
+\\
+ &  & \begin{split}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
+ & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
+\end{split}
+\\
  &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
-\end{eqnarray*}
-It is straightforward to verify that $\bar{\mu}$ is a quantum IVPM.
+\end{eqnarray}
+It is straightforward to verify that $\bar{\mu}$ is a quantum interval-valued
+probability measure.
 
@@
 
-Second, we will prove that $\bar{\mu}$ cannot correspond to any quantum
-probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
-for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
-We must have 
-\begin{equation}
-\mu(P_{00})=\mu(P_{0\ps})=\mu(P_{\ps0})=0\textrm{ .}\label{eq:probability-zero-on-states}
-\end{equation}
-By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
-such that $\mu\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. However, no pure
-state~$\ket{\phi}$ satisfies $\ip{\phi}{00}=\ip{\phi}{0\ps}=\ip{\phi}{\ps0}=0$
-so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
-measure~$\mu$.\qed\end{example}
+Now assume there exists a real-valued quantum probability measure
+$\mu$ such that $\mu(P)\in\bar{\mu}(P)$ for every event (projection)~$P$.
+We derive a contradiction as follows. Suppose $\mu(P)\in\bar{\mu}(P)$
+then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
+By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
+such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
+can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
+\end{example}
 

### 2017-04-08 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

@@
 \mu_{0}(P)=\begin{cases}
-\mu_{\ket{\ps}}^{B}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
-\mu_{\ket{0}}^{B}(P) & \textrm{, otherwis,}
+\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
+\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis,}
 \end{cases}
@@
 definition of \emph{core} relative to a sub-event space~$\events'\subseteq\events$
-as follow.
+as follow.\footnote{\yutsung{{I changed the definition of core} to density matrix. While
+this change might make it easier to explain the core of quantum IVPMs,
+it could increase the difficulty to explain classical IVPMs because
+we might need to explain the meaning of density matrix and the Born
+rule for classical probability measures...}}
 \begin{equation}
-\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{B}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
+\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
 \end{equation}
@@
 \begin{eqnarray}
- &  & \begin{split}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
+ &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
  & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\textrm{ ,}
-\end{split}
+\end{aligned}
 \\
- &  & \begin{split}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
+ &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
  & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
-\end{split}
+\end{aligned}
 \\
@@
 
-\newpage{}
+Let $\events_{1}$ be the minimal event space containing both $\proj{0}$
+and $\proj{\ps}$. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
+for any mixed state~$\rho\in\mathrm{core}\left(\bar{\mu},\events_{1}\right)$,
+we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$.
+Hence, $\rho$ is actually the pure state orthogonal to both $\ket{0}$
+and $\ket{\ps}$. The only choice of $\rho$ is $\ket{2}$, and it
+is easy to verify $\ket{2}$ is actually in $\mathrm{core}\left(\bar{\mu},\events_{1}\right)$.
 
-Now assume there exists a real-valued quantum probability measure
-$\mu$ such that $\mu(P)\in\bar{\mu}(P)$ for every event (projection)~$P$.
-We derive a contradiction as follows. Suppose $\mu(P)\in\bar{\mu}(P)$
-then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
-By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
-such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
-can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
-\end{example}
+Similarly, let $\events_{2}$ be the minimal event space containing
+both $\proj{0}$ and $\proj{\ps'}$. We have $\mathrm{core}\left(\bar{\mu},\events_{2}\right)=\left\{ \ket{1}\right\} $.
+Therefore, 
+\begin{equation}
+\mathrm{core}\left(\bar{\mu},\events\right)\subseteq\mathrm{core}\left(\bar{\mu},\events_{1}\right)\cap\mathrm{core}\left(\bar{\mu},\events_{2}\right)=\emptyset\textrm{ ,}
+\end{equation}
+and must be empty.\end{example}
+
+We found this kind of incompatibility can be reduced if we increase
+the measurement resource, that is, using finer intervals. We conjecture
+by consuming more and more measurement resource, it would be more
+and more likely that there is an empty core relative to all projectors~$\events$.
 

### 2017-04-08 prop_letter.tex
prop_letter.tex Updating here and there...

@@
 and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
-defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. Then,
-given a quantum real-valued probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
+defined by 
+\begin{equation}
+\iota_{\infty}\left(x\right)=\left[x,x\right]\textrm{ .}\label{eq:iota_infty}
+\end{equation}
+Then, given a quantum real-valued probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
 $\bar{\mu}(P)=\iota_{\infty}\left(\mu(P)\right)$ is a quantum IVPM,
@@
 
-Recall when providing infinity measurement resource, the quantum probability
-measures are simply induced by the Born rule for $d\ge3$. If we increase
-the measurement resource, i.e., pick finer intervals, it is natural
-to ask whether quantum IVPMs approach the Born rule. In order to understand
-this question, it is instructive to consider the 2-dimensional non-Born
-quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$ defined
-as follow:
+Formally, we can ask: what can we deduce about the state of a quantum
+system given a quantum interval-valued probability measure, i.e.,
+given observations done with finite resources. In the case that the
+intervals are infinitely precise, the question reduces to Gleason's
+theorem which states that the state of the quantum system is uniquely
+determined by the probability measure. But surely the less resources
+are available, the less precise the intervals, and the less we expect
+to know about the state of the system.
+
+In order to understand this question, it is instructive to consider
+the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
+defined as follow:
 \begin{equation}
@@
 where $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
-is a sub-event space. In another word, $\mu_{0}$ is consistent with
-the Born rule on every proper sub-event space, but not on the set
-of all projectors.
-
-Given a quantum IVPM~$\bar{\mu}$, the preceding idea motivates the
-definition of \emph{core} relative to a sub-event space~$\events'\subseteq\events$
-as follow.\footnote{\yutsung{{I changed the definition of core} to density matrix. While
-this change might make it easier to explain the core of quantum IVPMs,
-it could increase the difficulty to explain classical IVPMs because
-we might need to explain the meaning of density matrix and the Born
-rule for classical probability measures...}}
+is a sub-event space. $\mu_{0}$ is not induced by the Born rule as
+a whole, but is consistent with the Born rule on $\events_{0}$ and
+some other proper sub-event spaces. Formally, given a quantum IVPM~$\bar{\mu}$,
+the \emph{core} relative to a sub-event space~$\events'\subseteq\events$
+as follow.\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
+While this change might make it easier to explain the core of quantum
+IVPMs, it could increase the difficulty to explain classical IVPMs
+because we might need to explain the meaning of the Born rule for
+classical probability measures...}}
 \begin{equation}
@@
 \end{equation}
-Although the elements of a core are density matrices, we may just
-use the state vectors for pure states if it is clear according to
-the context. For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \ket{\ps}\right\} $
+For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \proj{\ps}\right\} $
 and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right)=\emptyset$,
-where $\circ$ denote function composition.
+where $\circ$ denote function composition, and $\iota_{\infty}$
+is defined in Eq.~(\ref{eq:iota_infty}).
 
@@
 and $\ket{\ps}$. The only choice of $\rho$ is $\ket{2}$, and it
-is easy to verify $\ket{2}$ is actually in $\mathrm{core}\left(\bar{\mu},\events_{1}\right)$.
+is easy to verify $\proj{2}$ is actually in $\mathrm{core}\left(\bar{\mu},\events_{1}\right)$.
 
 Similarly, let $\events_{2}$ be the minimal event space containing
-both $\proj{0}$ and $\proj{\ps'}$. We have $\mathrm{core}\left(\bar{\mu},\events_{2}\right)=\left\{ \ket{1}\right\} $.
+both $\proj{0}$ and $\proj{\ps'}$. We have $\mathrm{core}\left(\bar{\mu},\events_{2}\right)=\left\{ \proj{1}\right\} $.
 Therefore, 

### 2017-04-08 prop_letter.tex
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Updating...

@@
 Also, to simplify the notation later, the projector onto each eigenstate
-is on the right of each eigenstate. A projector is named by its eigenstate
-if it is a product state, where $\ket{\ps}=\frac{1}{\sqrt{2}}\left(\ket{0}+\ket{1}\right)$
-and $\ket{\ms}=\frac{1}{\sqrt{2}}\left(\ket{0}-\ket{1}\right)$. For
-example, $P_{00}=\op{0}{0}$ and $P_{\ps\ms}=\op{\ps}{\ms}$. For
-the entangled states, $P_{\textrm{B}i}$ means it is one of the Bell
-basis, and $P_{\textrm{N}i}$ means it is not part of the Bell basis.}
+is on the right of each eigenstate. Only the projectors used in Eq.~(\ref{eq:CEGA})
+will be named, and they are named so that if two projectors share
+the same index, they are commuting.}
 
@@
 \hline 
-$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$  & $(1,0,0,0)\rightarrow P_{00}$  & $(0,1,0,0)\rightarrow P_{01}$  & $(0,0,1,0)\rightarrow P_{10}$  & $(0,0,0,1)\rightarrow P_{11}$ \tabularnewline
-$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$  & $(1,1,1,1)\rightarrow P_{\ps\ps}$  & $(1,-1,1,-1)\rightarrow P_{\ps\ms}$  & $(1,1,-1,-1)\rightarrow P_{\ms\ps}$  & $(1,-1,-1,1)\rightarrow P_{\ms\ms}$ \tabularnewline
-$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(1,1,1,-1)\rightarrow P_{\textrm{N}0}$  & $(1,1,-1,1)\rightarrow P_{\textrm{N}1}$  & $(1,-1,1,1)\rightarrow P_{\textrm{N}2}$  & $(-1,1,1,1)\rightarrow P_{\textrm{N}3}$ \tabularnewline
-$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\mathbb{1}$  & $\sigma_{x}\otimes\sigma_{z}$  & $(1,0,1,0)\rightarrow P_{\ps0}$  & $(0,1,0,1)\rightarrow P_{\ps1}$  & $(1,0,-1,0)\rightarrow P_{\ms0}$  & $(0,1,0,-1)\rightarrow P_{\ms1}$ \tabularnewline
-$\sigma_{z}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{z}\otimes\sigma_{x}$  & $(1,1,0,0)\rightarrow P_{0\ps}$  & $(1,-1,0,0)\rightarrow P_{0\ms}$  & $(0,0,1,1)\rightarrow P_{1\ps}$  & $(0,0,1,-1)\rightarrow P_{1\ms}$ \tabularnewline
-$\sigma_{z}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(0,1,1,0)\rightarrow P_{\textrm{B}0}$  & $(0,1,-1,0)\rightarrow P_{\textrm{B}1}$  & $(1,0,0,1)\rightarrow P_{\textrm{B}2}$  & $(1,0,0,-1)\rightarrow P_{\textrm{B}3}$ \tabularnewline
+$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$  & $(1,0,0,0)\rightarrow P_{12}$  & $(0,1,0,0)\rightarrow P_{18}$  & $(0,0,1,0)$  & $(0,0,0,1)\rightarrow P_{28}$ \tabularnewline
+$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$  & $(1,1,1,1)\rightarrow P_{56}$  & $(1,-1,1,-1)\rightarrow P_{59}$  & $(1,1,-1,-1)\rightarrow P_{69}$  & $(1,-1,-1,1)$ \tabularnewline
+$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(1,1,1,-1)\rightarrow P_{37}$  & $(1,1,-1,1)\rightarrow P_{47}$  & $(1,-1,1,1)$  & $(-1,1,1,1)\rightarrow P_{34}$ \tabularnewline
+$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\mathbb{1}$  & $\sigma_{x}\otimes\sigma_{z}$  & $(1,0,1,0)\rightarrow P_{48}$  & $(0,1,0,1)$  & $(1,0,-1,0)\rightarrow P_{58}$  & $(0,1,0,-1)\rightarrow P_{45}$ \tabularnewline
+$\sigma_{z}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{z}\otimes\sigma_{x}$  & $(1,1,0,0)$  & $(1,-1,0,0)\rightarrow P_{67}$  & $(0,0,1,1)\rightarrow P_{17}$  & $(0,0,1,-1)\rightarrow P_{16}$ \tabularnewline
+$\sigma_{z}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(0,1,1,0)\rightarrow P_{29}$  & $(0,1,-1,0)\rightarrow P_{23}$  & $(1,0,0,1)\rightarrow P_{39}$  & $(1,0,0,-1)$ \tabularnewline
 \end{tabular}
@@
 IVPMs, we first need to find the common eigenbasis of each row and
-column, and consider the projections to each eigenvectors~\cite{Kernaghan1994,peres1995quantum}.
-Let $\mathcal{T}_{24}$ denote the projectors onto each eigenstate
-listed in Table~\ref{table:commonBasis}. The Kochen-Specker theorem
-could then be proved by showing there is no function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
+column, and consider the projections to each eigenvectors~\cite{peres1995quantum,CabelloEstebaranzGarcia-Alcaine1996,Cabello_2008}.
+Let $\mathcal{T}_{18}$ denote the named projectors onto eigenstates
+listed in Table~\ref{table:commonBasis}, and the eigenstates they
+project to are denoted by $\events_{18}$. The Kochen-Specker theorem
+could then be proved by showing there is no function~$v:\events_{18}\rightarrow\left\{ 0,1\right\} $
 satisfying equation~(\ref{eq:Kochen-Specker-Rules}), where
 \begin{equation}
-\events_{24}=\set{\sum_{i=1}^{N}P_{i}}{\textrm{orthogonal }\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
+\events_{18}=\set{\sum_{i=1}^{N}P_{i}}{\textrm{orthogonal }\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
 \end{equation}
@@
 
-Assume there is a function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
+Assume there is a function~$v:\events_{18}\rightarrow\left\{ 0,1\right\} $
 satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
-be a quantum IVPM~$\bar{\mu}':\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
-defined by $\bar{\mu}'\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
+be a quantum IVPM~$\bar{\mu}:\events_{18}\rightarrow\mathscr{I}_{\mathrm{D}}$
+defined by $\bar{\mu}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
 where 
@@
 and have the following conditions 
-\begin{eqnarray*}
-\necess & \subseteq & \bar{\mu}'\left(P_{00}\right)+\bar{\mu}'\left(P_{01}\right)+\bar{\mu}'\left(P_{10}\right)+\bar{\mu}'\left(P_{11}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{00}\right)+\bar{\mu}'\left(P_{01}\right)+\bar{\mu}'\left(P_{1\ps}\right)+\bar{\mu}'\left(P_{1\ms}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{00}\right)+\bar{\mu}'\left(P_{10}\right)+\bar{\mu}'\left(P_{\ps1}\right)+\bar{\mu}'\left(P_{\ms1}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{00}\right)+\bar{\mu}'\left(P_{11}\right)+\bar{\mu}'\left(P_{\textrm{B}0}\right)+\bar{\mu}'\left(P_{\textrm{B}1}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{N}3}\right)+\bar{\mu}'\left(P_{\textrm{N}2}\right)+\bar{\mu}'\left(P_{\textrm{N}1}\right)+\bar{\mu}'\left(P_{\textrm{N}0}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{N}3}\right)+\bar{\mu}'\left(P_{\textrm{N}1}\right)+\bar{\mu}'\left(P_{\ps0}\right)+\bar{\mu}'\left(P_{\ms1}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{N}2}\right)+\bar{\mu}'\left(P_{\textrm{N}1}\right)+\bar{\mu}'\left(P_{\textrm{B}0}\right)+\bar{\mu}'\left(P_{\textrm{B}3}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{N}1}\right)+\bar{\mu}'\left(P_{\textrm{N}0}\right)+\bar{\mu}'\left(P_{1\ps}\right)+\bar{\mu}'\left(P_{0\ms}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{\textrm{B}1}\right)+\bar{\mu}'\left(P_{\textrm{B}3}\right)+\bar{\mu}'\left(P_{\ps\ps}\right)+\bar{\mu}'\left(P_{\ms\ms}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{1\ms}\right)+\bar{\mu}'\left(P_{0\ms}\right)+\bar{\mu}'\left(P_{\ps\ps}\right)+\bar{\mu}'\left(P_{\ms\ps}\right)\textrm{ ,}\\
-\necess & \subseteq & \bar{\mu}'\left(P_{\ps0}\right)+\bar{\mu}'\left(P_{\ps1}\right)+\bar{\mu}'\left(P_{\ms\ps}\right)+\bar{\mu}'\left(P_{\ms\ms}\right)\textrm{ .}
-\end{eqnarray*}
+\begin{equation}
+\begin{aligned}\necess & \subseteq\bar{\mu}\left(P_{12}\right)+\bar{\mu}\left(P_{18}\right)+\bar{\mu}\left(P_{17}\right)+\bar{\mu}\left(P_{16}\right)\textrm{ ,}\\
+\necess & \subseteq\bar{\mu}\left(P_{16}\right)+\bar{\mu}\left(P_{67}\right)+\bar{\mu}\left(P_{69}\right)+\bar{\mu}\left(P_{56}\right)\textrm{ ,}\\
+\necess & \subseteq\bar{\mu}\left(P_{56}\right)+\bar{\mu}\left(P_{59}\right)+\bar{\mu}\left(P_{58}\right)+\bar{\mu}\left(P_{45}\right)\textrm{ ,}\\
+\necess & \subseteq\bar{\mu}\left(P_{45}\right)+\bar{\mu}\left(P_{48}\right)+\bar{\mu}\left(P_{47}\right)+\bar{\mu}\left(P_{34}\right)\textrm{ ,}\\
+\necess & \subseteq\bar{\mu}\left(P_{34}\right)+\bar{\mu}\left(P_{37}\right)+\bar{\mu}\left(P_{39}\right)+\bar{\mu}\left(P_{23}\right)\textrm{ ,}\\
+\necess & \subseteq\bar{\mu}\left(P_{23}\right)+\bar{\mu}\left(P_{29}\right)+\bar{\mu}\left(P_{28}\right)+\bar{\mu}\left(P_{12}\right)\textrm{ ,}\\
+\necess & \subseteq\bar{\mu}\left(P_{28}\right)+\bar{\mu}\left(P_{18}\right)+\bar{\mu}\left(P_{58}\right)+\bar{\mu}\left(P_{48}\right)\textrm{ ,}\\
+\necess & \subseteq\bar{\mu}\left(P_{47}\right)+\bar{\mu}\left(P_{37}\right)+\bar{\mu}\left(P_{17}\right)+\bar{\mu}\left(P_{67}\right)\textrm{ ,}\\
+\necess & \subseteq\bar{\mu}\left(P_{69}\right)+\bar{\mu}\left(P_{59}\right)+\bar{\mu}\left(P_{39}\right)+\bar{\mu}\left(P_{29}\right)\textrm{ ,}
+\end{aligned}
+\label{eq:CEGA}
+\end{equation}
 If we sum up the preceding equations, we will have
 \begin{equation}
-\left[11,11\right]\subseteq4\bar{\mu}'\left(P_{00}\right)+4\bar{\mu}'\left(P_{\textrm{N}1}\right)+2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{\mu}'\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
-\end{equation}
-where 
-\begin{equation}
-\mathcal{T}_{18}=\mathcal{T}_{24}\backslash\{P_{00},P_{\textrm{N}1},P_{\ps\ms},P_{\ms0},P_{\textrm{B}2},P_{0\ps}\}\textrm{ .}
+\left[9,9\right]\subseteq2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{\mu}\left(\ket{\psi}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Total}
 \end{equation}
@@
 side is a singleton set of an even integer while the left-hand side
-is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}':\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
+is $\left[9,9\right]$. Therefore, there is no quantum IVPM~$\bar{\mu}:\events_{18}\rightarrow\mathscr{I}_{\mathrm{D}}$.
 Moreover, there is no quantum IVPM defined on the set of all projectors
-as well; otherwise, if we have a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
-then we can restrict $\bar{\mu}$ and define $\bar{\mu}'=\left.\bar{\mu}\right|_{\events_{24}}$.
+as well; otherwise, if we have a quantum IVPM~$\bar{\mu}':\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+then we can restrict $\bar{\mu}'$ and define $\bar{\mu}=\left.\bar{\mu}'\right|_{\events_{18}}$.
 

### 2017-04-08 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

@@
 a whole, but is consistent with the Born rule on $\events_{0}$ and
-some other proper sub-event spaces. Formally, given a quantum IVPM~$\bar{\mu}$,
-the \emph{core} relative to a sub-event space~$\events'\subseteq\events$
-as follow.\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
+some other proper sub-event spaces. The similar phenomena happens
+for IVPMs as well. Formally, given a quantum IVPM~$\bar{\mu}$, the
+\emph{core} relative to a sub-event space~$\events'\subseteq\events$
+is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
 While this change might make it easier to explain the core of quantum
-IVPMs, it could increase the difficulty to explain classical IVPMs
-because we might need to explain the meaning of the Born rule for
-classical probability measures...}}
+IVPMs, should we explain the meaning of the Born rule for classical
+probability measures?}}
 \begin{equation}
@@
 \end{equation}
-For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \proj{\ps}\right\} $
+The core of an interval-valued probability measure is the set of states
+it approximates. For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \proj{\ps}\right\} $,
+$\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{1}\right)=\left\{ \proj{0}\right\} $
 and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right)=\emptyset$,
-where $\circ$ denote function composition, and $\iota_{\infty}$
-is defined in Eq.~(\ref{eq:iota_infty}).
+where $\circ$ denotes function composition, $\iota_{\infty}$ is
+defined in Eq.~(\ref{eq:iota_infty}), and $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
+That is, $\iota_{\infty}\circ\mu_{0}$ approximates $\proj{\ps}$
+if we are only allowed to use $\events_{0}$ during the measurement,
+approximates $\proj{0}$ if $\events_{1}$ is allowed, and approximates
+nothing if every projector is allowed.
+
+Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
+to $\events_{0}$ and $\events_{1}$ which are all commutative. In
+general, a commutative sub-event space reduces quantum IVPMs to classical
+IVPMs. If a classical IVPM satisfies a coherence condition, convexity,
+it must approximate at least one infinitely-precise measure.
+
+\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
+every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
+if the following conditions are true.
+\begin{itemize}
+\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
+\item $\bar{\mu}$ is convex, i.e., for all commuting $P_{0},P_{1}\in\events$,
+\[
+\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}
+\]
+where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
+\end{itemize}
+Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
+
+\newpage{}
 
@@
 
-\newpage{}
-
-Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty
-core relative to $\events_{0}$ which is commutative. In general,
-a commutative sub-event space reduces quantum IVPMs to classical IVPMs.
-We haven't found any classical IVPM has an empty core, and Shapley
-proved that a good enough classical IVPM always has a non-empty core.
-
-\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
-every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
-if the following conditions are true.
-\begin{itemize}
-\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
-\item For all commuting $P_{0},P_{1}\in\events$, 
-\[
-\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}
-\]
-where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
-\end{itemize}
-Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-04-09 prop_letter.tex
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Updating...

@@
 
-It asserts that there exists no function~$v$~\footnote{\yutsung{In Kochen-Specker's original paper~\cite{kochenspecker1967},
-they use $\mathcal{E}$. In The Stanford Encyclopedia of Philosophy~\cite{Held2016},
-they use $v$. I think it is less confusion to use $v$ here.}} assigning definite values to all observables such that for any sequence
+It asserts that there exists no function~$v$~\footnote{\yutsung{Kochen-Specker's original paper~\cite{kochenspecker1967}
+used $\mathcal{E}$, but the Stanford Encyclopedia of Philosophy~\cite{Held2016}
+used $v$. I think it is less confusion to use $v$ here.}} assigning definite values to all observables such that for any sequence
 of commuting observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}

### 2017-04-09 prop_letter.tex
prop_letter.tex \paragraph{Contextuality Inequality} Added...
prop_letter.tex Updating here and there...

@@
 While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
-IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-is another one, where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
-This is the case where the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
-can be applied and will be explained in the next paragraph.
+IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
+is another one corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
 
@@
 \begin{equation}
-\begin{array}{ccc}
-\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
-\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
-\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
-\end{array}\label{eq:MerminSquare}
+\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
+\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
+\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
+\end{aligned}
+\label{eq:MerminSquare}
 \end{equation}
@@
 \begin{equation}
-\begin{array}{ccc}
-v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
-v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
-v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
-\end{array}\label{eq:MerminSquare-values}
+\begin{aligned}v(\mathbb{1} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\mathbb{1}) & v(\sigma_{z} & \otimes\sigma_{z})\\
+v(\sigma_{x} & \otimes\mathbb{1}) & v(\mathbb{1} & \otimes\sigma_{x}) & v(\sigma_{x} & \otimes\sigma_{x})\\
+v(\sigma_{x} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\sigma_{x}) & v(\sigma_{y} & \otimes\sigma_{y})
+\end{aligned}
+\label{eq:MerminSquare-values}
 \end{equation}
@@
 
+\newpage{}
+
+\paragraph{Contextuality Inequality}
+
+Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
+and we want to adopt these inequalities into our setting.
+
+First, notice that his inequality (4)
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-04-10 prop_letter.tex
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Updating...

@@
 \usepackage{babel}
+\usepackage{mmap}
 \usepackage{amsthm}
@@
 \end{equation}
-satisfying equation~(\ref{eq:Kochen-Specker-Rules}).
+satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
 
@@
 as $\left(\alpha_{00},\alpha_{01},\alpha_{10},\alpha_{11}\right)$.
-Also, to simplify the notation later, the projector onto each eigenstate
-is on the right of each eigenstate. Only the projectors used in Eq.~(\ref{eq:CEGA})
-will be named, and they are named so that if two projectors share
-the same index, they are commuting.}
+Also, to simplify the notation further, the projector onto each eigenstate
+used in Eq.~(\ref{eq:CEGA}) is named such that if two projectors
+share the same index, they are commuting.}
 
 \begin{ruledtabular}
-\begin{tabular}{ccc|cccc}
-\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis}\tabularnewline
+\begin{tabular}{c|c}
+Commuting observables & Common eigenbasis\tabularnewline
 \hline 
-$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$  & $(1,0,0,0)\rightarrow P_{12}$  & $(0,1,0,0)\rightarrow P_{18}$  & $(0,0,1,0)$  & $(0,0,0,1)\rightarrow P_{28}$ \tabularnewline
-$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$  & $(1,1,1,1)\rightarrow P_{56}$  & $(1,-1,1,-1)\rightarrow P_{59}$  & $(1,1,-1,-1)\rightarrow P_{69}$  & $(1,-1,-1,1)$ \tabularnewline
-$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(1,1,1,-1)\rightarrow P_{37}$  & $(1,1,-1,1)\rightarrow P_{47}$  & $(1,-1,1,1)$  & $(-1,1,1,1)\rightarrow P_{34}$ \tabularnewline
-$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\mathbb{1}$  & $\sigma_{x}\otimes\sigma_{z}$  & $(1,0,1,0)\rightarrow P_{48}$  & $(0,1,0,1)$  & $(1,0,-1,0)\rightarrow P_{58}$  & $(0,1,0,-1)\rightarrow P_{45}$ \tabularnewline
-$\sigma_{z}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{z}\otimes\sigma_{x}$  & $(1,1,0,0)$  & $(1,-1,0,0)\rightarrow P_{67}$  & $(0,0,1,1)\rightarrow P_{17}$  & $(0,0,1,-1)\rightarrow P_{16}$ \tabularnewline
-$\sigma_{z}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(0,1,1,0)\rightarrow P_{29}$  & $(0,1,-1,0)\rightarrow P_{23}$  & $(1,0,0,1)\rightarrow P_{39}$  & $(1,0,0,-1)$ \tabularnewline
+$\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
+\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
+\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}\\
+\mathbb{1} & \otimes\sigma_{z} & \sigma_{x} & \otimes\mathbb{1} & \sigma_{x} & \otimes\sigma_{z}\\
+\sigma_{z} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{z} & \otimes\sigma_{x}\\
+\sigma_{z} & \otimes\sigma_{z} & \sigma_{x} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
+\end{aligned}
+$ & $\begin{aligned}(1,0,0,0) & \rightarrow P_{12} & (0,1,0,0) & \rightarrow P_{18} & (0,0,1,0) &  & (0,0,0,1) & \rightarrow P_{28}\\
+(1,1,1,1) & \rightarrow P_{56} & (1,-1,1,-1) & \rightarrow P_{59} & (1,1,-1,-1) & \rightarrow P_{69} & (1,-1,-1,1)\\
+(1,1,1,-1) & \rightarrow P_{37} & (1,1,-1,1) & \rightarrow P_{47} & (1,-1,1,1) &  & (-1,1,1,1) & \rightarrow P_{34}\\
+(1,0,1,0) & \rightarrow P_{48} & (0,1,0,1) &  & (1,0,-1,0) & \rightarrow P_{58} & (0,1,0,-1) & \rightarrow P_{45}\\
+(1,1,0,0) &  & (1,-1,0,0) & \rightarrow P_{67} & (0,0,1,1) & \rightarrow P_{17} & (0,0,1,-1) & \rightarrow P_{16}\\
+(0,1,1,0) & \rightarrow P_{29} & (0,1,-1,0) & \rightarrow P_{23} & (1,0,0,1) & \rightarrow P_{39} & (1,0,0,-1)
+\end{aligned}
+$\tabularnewline
 \end{tabular}
@@
 
-Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
-if we want to reformulate the above argument in the language of quantum
-IVPMs, we first need to find the common eigenbasis of each row and
-column, and consider the projections to each eigenvectors~\cite{peres1995quantum,CabelloEstebaranzGarcia-Alcaine1996,Cabello_2008}.
+Since observables in Eq.~(\ref{eq:MerminSquare}) are not projections,
+if we want to reformulate the above argument in the language of IVPMs,
+we first need to find the common eigenbasis of each row and column,
+and consider the projections to each eigenvectors~\cite{peres1995quantum,CabelloEstebaranzGarcia-Alcaine1996,Cabello_2008}.
 Let $\mathcal{T}_{18}$ denote the named projectors onto eigenstates
@@
 could then be proved by showing there is no function~$v:\events_{18}\rightarrow\left\{ 0,1\right\} $
-satisfying equation~(\ref{eq:Kochen-Specker-Rules}), where
+satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}), where
 \begin{equation}
-\events_{18}=\set{\sum_{i=1}^{N}P_{i}}{\textrm{orthogonal }\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
+\events_{18}=\set{\sum_{i=1}^{N}P_{i}}{\textrm{orthogonal }\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{18}}
 \end{equation}
@@
 Assume there is a function~$v:\events_{18}\rightarrow\left\{ 0,1\right\} $
-satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
-be a quantum IVPM~$\bar{\mu}:\events_{18}\rightarrow\mathscr{I}_{\mathrm{D}}$
+satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}). There must be a
+quantum IVPM~$\bar{\mu}:\events_{18}\rightarrow\mathscr{I}_{\mathrm{D}}$
 defined by $\bar{\mu}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
@@
 \end{equation}
-Because the right-hand side of each equation forms an orthogonal basis,
-we can apply Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-and have the following conditions 
+Since each orthogonal basis can form an instance of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+the orthogonal bases in $\events_{18}$ gives the following equations:
 \begin{equation}
@@
 \necess & \subseteq\bar{\mu}\left(P_{47}\right)+\bar{\mu}\left(P_{37}\right)+\bar{\mu}\left(P_{17}\right)+\bar{\mu}\left(P_{67}\right)\textrm{ ,}\\
-\necess & \subseteq\bar{\mu}\left(P_{69}\right)+\bar{\mu}\left(P_{59}\right)+\bar{\mu}\left(P_{39}\right)+\bar{\mu}\left(P_{29}\right)\textrm{ ,}
+\necess & \subseteq\bar{\mu}\left(P_{69}\right)+\bar{\mu}\left(P_{59}\right)+\bar{\mu}\left(P_{39}\right)+\bar{\mu}\left(P_{29}\right)\textrm{ .}
 \end{aligned}

### 2017-04-10 prop_letter.tex
prop_letter.tex Updating here and there...

@@
 \end{itemize}
-condition that provides only a bound and not an equivalence as in Eq. 
-\eqref{eq:QuantumProbability-Addition}. For
-example, if we consider $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $
-and $\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
+condition that provides only a bound and not an equivalence as in
+Eq. \eqref{eq:QuantumProbability-Addition}. For example, if we consider
+$\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
+$\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
 \[
-\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=
-\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right) .
+\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
 \]
 
-Quantum IVPMs provide a unifying framework to account for finite precision
-measurements in quantum physics. It has the desired properties of
-turning into the classical IVPMs setup~\cite{JamisonLodwick2004}
+It is easy to establish that quantum IVPMs generalize conventional
+quantum probability measures and classical IVPMs. In particular, any
+quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+can be recast as an interval-valued measure~$\iota_{\infty}\circ\mu:\events\rightarrow\mathscr{I}_{\infty}$,
+where $\circ$ denotes function composition, $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
+defined by 
+\begin{equation}
+\iota_{\infty}\left(x\right)=\left[x,x\right]\textrm{ .}\label{eq:iota_infty}
+\end{equation}
+In another word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$
+are just the same as quantum real-valued probability measures where
+Gleason's theorem can apply.
+
+More interesting examples comes when we focus on only three intervals
+$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
+where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
+\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
+it provides no information. Then,
+\begin{equation}
+\bar{\mu}_{1}\left(P\right)=\begin{cases}
+\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
+\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
+\unknown & \text{, otherwise.}
+\end{cases}\label{eq:homomorphism-1}
+\end{equation}
+is a quantum IVPM. This measure represents the beliefs of an experimenter
+with no prior knowledge about the particular quantum system in question.
+
+Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
 when the space of events includes only mutually commuting sub-events,
-and of leading to the standard von Neumann projective measurement
-theory when the collection of intervals are all singletons. To be
-more precise....\newpage{}
-
-Although considering IVPM is new for a quantum theory, people have
-already defined classical IVPMs~\cite{JamisonLodwick2004}, which
-are essentially the same as quantum IVPMs on a restricted mutually
-commuting sub-event space~$\events'\subseteq\events$, where any
-subset of $\events$ is called a sub-event space if it satisfies the
-follow conditions. 
+where any subset of $\events$ is called a sub-event space if it satisfies
+the follow conditions. 
 \begin{itemize}
@@
 \end{itemize}
-Quantum IVPM not only stems from classical IVPM but also generalizes
-quantum real-valued probability measures. Consider the collection
-of all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
-defined by 
+For example, $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
+is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
+$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
 \begin{equation}
-\iota_{\infty}\left(x\right)=\left[x,x\right]\textrm{ .}\label{eq:iota_infty}
+\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
+\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
+\end{aligned}
 \end{equation}
-Then, given a quantum real-valued probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
-$\bar{\mu}(P)=\iota_{\infty}\left(\mu(P)\right)$ is a quantum IVPM,
-and vice versa. In another word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$
-are just the same as quantum real-valued probability measures where
-Gleason's theorem can apply.
+If we identify $\proj{0}$ and $\proj{1}$ as the head and the tail
+of a coin, respectively, then $\bar{\mu}_{2}$ represents experimenter
+know nothing about a coin before she toss it.
 
 While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
-IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
+IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
 is another one corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
@@
 \end{equation}
-Since each orthogonal basis can form an instance of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-the orthogonal bases in $\events_{18}$ gives the following equations:
+For each the orthogonal basis in $\events_{18}$, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+gives the following equations: 
 \begin{equation}
@@
 
-\paragraph{Quantum IVPM and Real-valued Probability Measure}
+\paragraph{Quantum IVPM and States}
 
@@
 given observations done with finite resources. In the case that the
-intervals are infinitely precise, the question reduces to Gleason's
-theorem which states that the state of the quantum system is uniquely
-determined by the probability measure. But surely the less resources
-are available, the less precise the intervals, and the less we expect
-to know about the state of the system.
+intervals are infinitely precise for $d\ge3$, the question reduces
+to Gleason's theorem which states that the state of the quantum system
+is uniquely determined by the probability measure. But surely the
+less resources are available, the less precise the intervals, and
+the less we expect to know about the state of the system.
 
-In order to understand this question, it is instructive to consider
-the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
+To understand the relation between IVPMs and states, it is instructive
+to consider the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
 defined as follow:
@@
 \mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
-\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis,}
+\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis.}
 \end{cases}
 \end{equation}
-where $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
-is a sub-event space. $\mu_{0}$ is not induced by the Born rule as
-a whole, but is consistent with the Born rule on $\events_{0}$ and
-some other proper sub-event spaces. The similar phenomena happens
-for IVPMs as well. Formally, given a quantum IVPM~$\bar{\mu}$, the
-\emph{core} relative to a sub-event space~$\events'\subseteq\events$
-is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
+$\mu_{0}$ is not induced by the Born rule as a whole, but is consistent
+with the Born rule on $\events_{0}$ and some other proper sub-event
+spaces. The similar phenomena happens for IVPMs as well. Formally,
+given a quantum IVPM~$\bar{\mu}$, the \emph{core} relative to a
+sub-event space~$\events'\subseteq\events$ is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
 While this change might make it easier to explain the core of quantum
@@
 The core of an interval-valued probability measure is the set of states
-it approximates. For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \proj{\ps}\right\} $,
-$\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{1}\right)=\left\{ \proj{0}\right\} $
-and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right)=\emptyset$,
-where $\circ$ denotes function composition, $\iota_{\infty}$ is
-defined in Eq.~(\ref{eq:iota_infty}), and $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
+it approximates. For example, $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
+contains every density matrix. The 2-dimensional measure~$\mu_{0}$
+can be understood by core as well:\begin{subequations}
+\begin{eqnarray}
+\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
+\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
+\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right) & = & \emptyset\textrm{ ,}
+\end{eqnarray}
+\end{subequations}where $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
 That is, $\iota_{\infty}\circ\mu_{0}$ approximates $\proj{\ps}$
 if we are only allowed to use $\events_{0}$ during the measurement,
-approximates $\proj{0}$ if $\events_{1}$ is allowed, and approximates
-nothing if every projector is allowed.
+and approximates $\proj{0}$ if $\events_{1}$ are the only allowed
+ones. Since $\iota_{\infty}\circ\mu_{0}$ approximates different states
+on different sub-event space, it intuitively approximates nothing
+if every projector is allowed.
 
@@
 \item $\bar{\mu}$ is convex, i.e., for all commuting $P_{0},P_{1}\in\events$,
-\[
-\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}
-\]
+$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
 where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
@@
 
-\newpage{}
-
-Notice that $\iota_{\infty}\circ\mu_{0}$ has different core elements
-relative to different sub-event spaces so that it has an empty core
-relative to all projectors~$\events$. When $d\ge3$, if we have
-infinite measurement resource and consider $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
-by Gleason's theorem, $\mathrm{core}\left(\bar{\mu},\events\right)$
-has a unique element, i.e., we can always identify a unique state.
-However, when we only have finite resources, we usually can only identify
-a quantum IVPM to more than one states on different sub-event spaces.
-The simplest example add one extra interval~$\unknown=\left[0,1\right]$
-to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
-Then, the quantum IVPM
-\begin{equation}
-\bar{\mu}_{1}\left(P\right)=\begin{cases}
-\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
-\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
-\unknown & \text{, otherwise.}
-\end{cases}\label{eq:homomorphism-1}
-\end{equation}
-provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
-contains every density matrix. A more sophisticating example is the
-following.\footnote{\yutsung{It seems that our example in 4 dimensions together with
+In informal terms, this result states that although measurements done
+with limited resources and poor precision may not uniquely identify
+the true state of the system, there is always at least one system
+that is consistent with the measurements. However, similar to 2-dimensional
+$\iota_{\infty}\circ\mu_{0}$, even if a quantum IVPM approximates
+some states for each classical sub-event space, it may not approximate
+any particular state while considering for all projectors~$\events$.\footnote{\yutsung{It seems that our example in 4 dimensions together with
 relativity core would be unnecessary complex. Therefore, I roll our
@@
 Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
-$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
+Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
+$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
+and\begin{subequations}
 \begin{eqnarray}
@@
 \end{eqnarray}
-It is straightforward to verify that $\bar{\mu}$ is a quantum interval-valued
-probability measure.
+\end{subequations}It is straightforward to verify that $\bar{\mu}$
+is a quantum interval-valued probability measure.
 

### 2017-04-10 prop_letter.tex
prop_letter.tex \usepackage{cmap} Fixing bugs...
prop_letter.tex Updating here and there...

@@
 \usepackage{fullpage}
+\usepackage{cmap}
 \usepackage[T1,T2A]{fontenc}
@@
 \usepackage{babel}
-\usepackage{mmap}
 \usepackage{amsthm}
@@
 and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
-defined by 
-\begin{equation}
-\iota_{\infty}\left(x\right)=\left[x,x\right]\textrm{ .}\label{eq:iota_infty}
-\end{equation}
-In another word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$
-are just the same as quantum real-valued probability measures where
-Gleason's theorem can apply.
+defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. In another
+word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$ are just the
+same as quantum real-valued probability measures where Gleason's theorem
+can apply.
 
@@
 contains every density matrix. The 2-dimensional measure~$\mu_{0}$
-can be understood by core as well:\begin{subequations}
+can be understood by core as well. Consider the IVPM~$\bar{\mu}_{0}=\iota_{\infty}\circ\mu_{0}$
+whose cores are\begin{subequations}
 \begin{eqnarray}
-\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
-\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
-\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right) & = & \emptyset\textrm{ ,}
+\mathrm{core}\left(\bar{\mu}_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
+\mathrm{core}\left(\bar{\mu}_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
+\mathrm{core}\left(\bar{\mu}_{0},\events\right) & = & \emptyset\textrm{ ,}
 \end{eqnarray}
 \end{subequations}where $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
-That is, $\iota_{\infty}\circ\mu_{0}$ approximates $\proj{\ps}$
-if we are only allowed to use $\events_{0}$ during the measurement,
-and approximates $\proj{0}$ if $\events_{1}$ are the only allowed
-ones. Since $\iota_{\infty}\circ\mu_{0}$ approximates different states
-on different sub-event space, it intuitively approximates nothing
-if every projector is allowed.
+That is, $\bar{\mu}_{0}$ approximates $\proj{\ps}$ if we are only
+allowed to use $\events_{0}$ during the measurement, and approximates
+$\proj{0}$ if $\events_{1}$ are the only allowed ones. Since $\bar{\mu}_{0}$
+approximates different states on different sub-event space, it intuitively
+approximates nothing if every projector is allowed.
 
-Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
-to $\events_{0}$ and $\events_{1}$ which are all commutative. In
-general, a commutative sub-event space reduces quantum IVPMs to classical
-IVPMs. If a classical IVPM satisfies a coherence condition, convexity,
-it must approximate at least one infinitely-precise measure.
+Notice that $\bar{\mu}_{0}$ has a non-empty core relative to $\events_{0}$
+and $\events_{1}$ which are all commutative. In general, a commutative
+sub-event space reduces quantum IVPMs to classical IVPMs. If a classical
+IVPM satisfies a coherence condition, convexity, it must approximate
+at least one infinitely-precise measure.
 

### 2017-04-10 prop_letter.tex
prop_letter.tex \paragraph{Contextuality Inequality} Updating...

@@
 
-First, notice that his inequality (4)
+First, although his inequality (4) bases on Mermin square and looks
+simple, we cannot use it directly because they are not projectors.
+Instead $A_{ij}$ in his equation (1) are almost projectors, because
+$A_{ij}=2\proj{v_{ij}}-\mathbb{1}$, and $\ket{v_{ij}}$ are eigenstates
+of Mermin square. It is easier to write an inequality start from equation
+(1).
 

### 2017-04-10 prop_letter.tex
prop_letter.tex Updating footnotes according to the meeting...

@@
 
-It asserts that there exists no function~$v$~\footnote{\yutsung{Kochen-Specker's original paper~\cite{kochenspecker1967}
-used $\mathcal{E}$, but the Stanford Encyclopedia of Philosophy~\cite{Held2016}
-used $v$. I think it is less confusion to use $v$ here.}} assigning definite values to all observables such that for any sequence
-of commuting observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
+It asserts that there exists no function~$v$ assigning definite
+values to all observables such that for any sequence of commuting
+observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
 \begin{eqnarray}
@@
 IVPMs, should we explain the meaning of the Born rule for classical
-probability measures?}}
+probability measures? Check this definition in the classical setting,
+like commuting observables or product states... etc.}}
 \begin{equation}

### 2017-04-10 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Added...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Expectation Values for IVPMs\label{sec:ExpectationValue}}
+
+We may need to understand how to define expectation values of an observable
+for quantum IVPMs. Recall an observable is the quantum version of
+a random variable. Hence, in order to define expectation values of
+an observable, we need to understand the definition of expectation
+values of a random variable for an classical IVPM.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{comment}

### 2017-04-11 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 
-\section{Expectation Values for IVPMs\label{sec:ExpectationValue}}
+\section{Expectation Values for IVPMs}
 
@@
 an observable, we need to understand the definition of expectation
-values of a random variable for an classical IVPM.
+values of a random variable for an classical IVPM. Since the expectation
+value of random variable~$X$ is the integral $\int X\rmd\pmeas$~\cite{Kolmogorov1950},
+we need to understand the meaning of integration on IVPMs. In the
+rest of the section, we will consider the real-valued and interval-valued
+probability measure defined in example~\ref{ex1} and \ref{ex3},
+and see how to compute the expectation value of different random variables.
 

### 2017-04-11 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 \item $\bar{\mu}(\Omega)=[1,1]$. 
-\item For any event $E$, $\bar{\mu}\left(\Omega\backslash
-E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$.
+\item For any event $E$, 
+\begin{equation}
+\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)\textrm{ .}\label{eq:classical-complement}
+\end{equation}
 \item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
@@
 
+Consider the random variable~$X$ representing the number of tails.
+For the probability measure~$\pmeas$ in example~\ref{ex1}, the
+expectation value of $X$ is
+\begin{eqnarray*}
+\int X\rmd\pmeas & = & 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
+ & = & 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .}
+\end{eqnarray*}
+Now consider the IVPM~$\bar{\mu}$ in example~\ref{ex3}. First,
+since the left-end and the right-end satisfies equation~(\ref{eq:classical-complement})
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-04-11 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

--- 2017-04-11 prop_iop.tex
@@
 
+Consider the random variable~$X_{0}$ representing the number of
+tails. For the probability measure~$\pmeas$ in example~\ref{ex1},
+the expectation value of $X_{0}$ is
+\begin{eqnarray*}
+\int X_{0}\rmd\pmeas & = & 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
+ & = & 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .}
+\end{eqnarray*}
+
+Now consider the IVPM~$\bar{\mu}$ in example~\ref{ex3}. First,
+the only source use the exact same definition as ours is written by
+Jamison and Lodwick~\cite{JamisonLodwick2004}. They introduced a
+definition of integration as follow\footnote{\yutsung{Although they said they would explore their integration
+in more details, they change their definition of IVPM later. Hence,
+I don't know if they have any further development of their integration.}}. If we denote the indicator function by 
+\begin{equation} 
+\mathbf{1}_{A}(x)=\cases{ 
+1 & if $x\in A$ ;\\ 
+0 & if $x\notin A$, 
+}
+\end{equation}
+then given a random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{A_{i}}$,
+where $x_{i}$ are all different, the integral of $X$ is defined
+by 
+\begin{eqnarray*}
+\int_{A}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)},\right.\\
+ &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)}\right]\textrm{ .}
+\end{eqnarray*}
+For example, $X_{0}=0\cdot\mathbf{1}_{\{HH\}}+1\cdot\mathbf{1}_{\{HT,TH\}}+2\cdot\mathbf{1}_{\{TT\}}$,
+and $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$. Therefore, 
+\begin{eqnarray*}
+\int_{\Omega}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1},\right.\\
+ &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1}\right]\\
+ & = & \left[\inf\set{a_{1}+2a_{2}}{a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{1}+a_{2}=1},\right.\\
+ &  & \left.\sup\set{a_{1}+2a_{2}}{a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{1}+a_{2}=1}\right]\\
+ & = & \left[\inf\set{a_{1}+2a_{2}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{1}+a_{2}=1},\right.\\
+ &  & \left.\sup\set{a_{1}+2a_{2}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{1}+a_{2}=1}\right]\\
+ & = & \left[\inf\set{a_{1}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{1}=1},\right.\\
+ &  & \left.\sup\set{a_{1}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{1}=1}\right]\\
+ & = & \left[1,1\right]
+\end{eqnarray*}
+What does this means...?
+
+In other references, since the left-end and the right-end of an IVPM
+satisfies equation~(\ref{eq:classical-complement}),
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-04-11 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Hot fix...

@@
  &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1}\right]\\
- & = & \left[\inf\set{a_{1}+2a_{2}}{a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{1}+a_{2}=1},\right.\\
- &  & \left.\sup\set{a_{1}+2a_{2}}{a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{1}+a_{2}=1}\right]\\
- & = & \left[\inf\set{a_{1}+2a_{2}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{1}+a_{2}=1},\right.\\
- &  & \left.\sup\set{a_{1}+2a_{2}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{1}+a_{2}=1}\right]\\
- & = & \left[\inf\set{a_{1}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{1}=1},\right.\\
- &  & \left.\sup\set{a_{1}}{\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{1}=1}\right]\\
- & = & \left[1,1\right]
+ & = & \left[\inf\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
+ &  & \left.\sup\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
+ & = & \left[\inf\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
+ &  & \left.\sup\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
+ & = & \left[\inf\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1},\right.\\
+ &  & \left.\sup\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1}\right]\\
+ & = & \left[\frac{1}{2},1\right]
 \end{eqnarray*}

### 2017-04-11 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 and see how to compute the expectation value of different random variables.
-
-Consider the random variable~$X_{0}$ representing the number of
-tails. For the probability measure~$\pmeas$ in example~\ref{ex1},
-the expectation value of $X_{0}$ is
+To simplify the discussion later, we will only consider a random variable~$X:\Omega\rightarrow\left[0,1\right]$
+which is a step function, i.e., $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{A_{i}}$,
+where $A_{i}\in\events$ and $\mathbf{1}_{A}$ is the indicator function
+defined by 
+\begin{equation} 
+\mathbf{1}_{A}(x)=\cases{ 
+1 & if $x\in A$ ;\\ 
+0 & if $x\notin A$. 
+}
+\end{equation}
+
+Given a random variable~$X$ and a probability measure~$\pmeas$,
+the expectation value of $X$ is 
+\begin{eqnarray*}
+\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(A_{i}\right)\textrm{ .}
+\end{eqnarray*}
+Intuitively, the expectation value is weighted average of the possible
+outcomes of $X$ with the weight equal to the probability of each
+outcome could happen. For example, consider the random variable~$X_{0}$
+representing the number of tails. For the probability measure~$\pmeas$
+in example~\ref{ex1}, the expectation value of $X_{0}$ is
 \begin{eqnarray*}
@@
 
-Now consider the IVPM~$\bar{\mu}$ in example~\ref{ex3}. First,
-the only source use the exact same definition as ours is written by
-Jamison and Lodwick~\cite{JamisonLodwick2004}. They introduced a
-definition of integration as follow\footnote{\yutsung{Although they said they would explore their integration
-in more details, they change their definition of IVPM later. Hence,
-I don't know if they have any further development of their integration.}}. If we denote the indicator function by 
-\begin{equation} 
-\mathbf{1}_{A}(x)=\cases{ 
-1 & if $x\in A$ ;\\ 
-0 & if $x\notin A$, 
-}
-\end{equation}
-then given a random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{A_{i}}$,
-where $x_{i}$ are all different, the integral of $X$ is defined
-by 
+After we discussed the conventional expectation value, we can start
+to discuss the expectation value of IVPM. First, the only source use
+the exact same definition as ours is written by Jamison and Lodwick~\cite{JamisonLodwick2004}
+so it's reasonable to start from their definition of integration\footnote{Although they said they would explore their integration in more details,
+they change their definition of IVPM later. Hence, I don't know if
+they have any further development of their integration.}. Their integral of $X$ is defined by 
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-For example, $X_{0}=0\cdot\mathbf{1}_{\{HH\}}+1\cdot\mathbf{1}_{\{HT,TH\}}+2\cdot\mathbf{1}_{\{TT\}}$,
-and $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$. Therefore, 
+In this definition, we still work on the weighted average. Since we
+don't know the exact probability, we want to average on all possible
+allowed probability, which represents the requirement on $a_{i}\in\bar{\mu}\left(A_{i}\right)$.
+However, I don't have a clear intuition on why they want $\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)$
+and $\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)$, and we will
+have a more intuitive definition following this line when we move
+on to Choquet integral.
+
+After we have the definition, we can consider the IVPM~$\bar{\mu}$
+in example~\ref{ex3} as an example. Because $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$,
+we have 
 \begin{eqnarray*}

### 2017-04-12 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 the expectation value of $X$ is 
-\begin{eqnarray*}
+\begin{eqnarray}
 \int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(A_{i}\right)\textrm{ .}
-\end{eqnarray*}
+\end{eqnarray}
 Intuitively, the expectation value is weighted average of the possible
@@
 don't know the exact probability, we want to average on all possible
-allowed probability, which represents the requirement on $a_{i}\in\bar{\mu}\left(A_{i}\right)$.
+allowed probability, which is represented by the requirement on $a_{i}\in\bar{\mu}\left(A_{i}\right)$.
 However, I don't have a clear intuition on why they want $\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)$
@@
 have a more intuitive definition following this line when we move
-on to Choquet integral.
+on to Choquet integral~\cite{Choquet1954,Grabisch2016}.
 

### 2017-04-12 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 To simplify the discussion later, we will only consider a random variable~$X:\Omega\rightarrow\left[0,1\right]$
-which is a step function, i.e., $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{A_{i}}$,
-where $A_{i}\in\events$ and $\mathbf{1}_{A}$ is the indicator function
+which is a step function, i.e., $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
+where $E_{i}\in\events$ and $\mathbf{1}_{E}$ is the indicator function
 defined by 
@@
 \begin{eqnarray}
-\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(A_{i}\right)\textrm{ .}
+\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(E_{i}\right)\textrm{ .}
 \end{eqnarray}
@@
 \begin{eqnarray*}
-\int_{A}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)},\right.\\
- &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)}\right]\textrm{ .}
+\int_{E}^{\textrm{JL}}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}e_{i}}{e_{i}\in\bar{\mu}\left(E_{i}\right)\textrm{ and }\sum_{i=1}^{N}e_{i}=\min\bar{\mu}\left(E\right)},\right.\\
+ &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}e_{i}}{e_{i}\in\bar{\mu}\left(E_{i}\right)\textrm{ and }\sum_{i=1}^{N}e_{i}=\max\bar{\mu}\left(E\right)}\right]\textrm{ .}
 \end{eqnarray*}
@@
 don't know the exact probability, we want to average on all possible
-allowed probability, which is represented by the requirement on $a_{i}\in\bar{\mu}\left(A_{i}\right)$.
-However, I don't have a clear intuition on why they want $\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)$
-and $\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)$, and we will
+allowed probability, which is represented by the requirement on $e_{i}\in\bar{\mu}\left(E_{i}\right)$.
+However, I don't have a clear intuition on why they want $\sum_{i=1}^{N}e_{i}=\min\bar{\mu}\left(E\right)$
+and $\sum_{i=1}^{N}e_{i}=\max\bar{\mu}\left(E\right)$, and we will
 have a more intuitive definition following this line when we move
-on to Choquet integral~\cite{Choquet1954,Grabisch2016}.
-
-After we have the definition, we can consider the IVPM~$\bar{\mu}$
-in example~\ref{ex3} as an example. Because $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$,
-we have 
+on to Choquet integral~\cite{Choquet1954,Grabisch2016}. After we
+have the definition, we can consider the IVPM~$\bar{\mu}$ in example~\ref{ex3}.
+Because $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$, we have
 \begin{eqnarray*}
-\int_{\Omega}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1},\right.\\
- &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1}\right]\\
- & = & \left[\inf\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
- &  & \left.\sup\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
- & = & \left[\inf\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
- &  & \left.\sup\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
- & = & \left[\inf\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1},\right.\\
- &  & \left.\sup\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1}\right]\\
- & = & \left[\frac{1}{2},1\right]
+\int_{\Omega}^{\textrm{JL}}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}e_{i}}{e_{i}\in\bar{\mu}\left(E_{i}\right)\textrm{ and }\sum_{i=1}^{N}e_{i}=1},\right.\\
+ &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}e_{i}}{e_{i}\in\bar{\mu}\left(E_{i}\right)\textrm{ and }\sum_{i=1}^{N}e_{i}=1}\right]\\
+ & = & \left[\inf\set{e_{1}+2e_{2}}{e_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ , }e_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ , }e_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ , and }e_{0}+e_{1}+e_{2}=1},\right.\\
+ &  & \left.\sup\set{e_{1}+2e_{2}}{e_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ , }e_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ , }e_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ , and }e_{0}+e_{1}+e_{2}=1}\right]\\
+ & = & \left[\inf\set{e_{1}+2e_{2}}{0\le e_{0}\le\frac{1}{2}\textrm{ , }\frac{1}{2}\le e_{1}\le1\textrm{ , }e_{2}=0\textrm{ , and }e_{0}+e_{1}+e_{2}=1},\right.\\
+ &  & \left.\sup\set{e_{1}+2e_{2}}{0\le e_{0}\le\frac{1}{2}\textrm{ , }\frac{1}{2}\le e_{1}\le1\textrm{ , }e_{2}=0\textrm{ , and }e_{0}+e_{1}+e_{2}=1}\right]\\
+ & = & \left[\inf\set{e_{1}}{0\le e_{0}\le\frac{1}{2}\textrm{ , }\frac{1}{2}\le e_{1}\le1\textrm{ , and }e_{0}+e_{1}=1},\right.\\
+ &  & \left.\sup\set{e_{1}}{0\le e_{0}\le\frac{1}{2}\textrm{ , }\frac{1}{2}\le e_{1}\le1\textrm{ , and }e_{0}+e_{1}=1}\right]\\
+ & = & \left[\frac{1}{2},1\right]\textrm{ .}
 \end{eqnarray*}
-What does this means...?
-
-In other references, since the left-end and the right-end of an IVPM
-satisfies equation~(\ref{eq:classical-complement}),
+
+\yutsung{{Put the definition of }Choquet integral, other meta-discourse
+here...}
+
+\begin{thm}\cite{Grabisch2016}For every classical interval-valued
+probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
+any random variable~$X:\Omega\rightarrow\mathbb{R}$, let $l:\events\rightarrow\left[0,1\right]$
+and $r:\events\rightarrow\left[0,1\right]$ be the left-end and the
+right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
+The following statements are equivalent.
+\begin{itemize}
+\item $\bar{\mu}$ is convex.
+\item The Choquet integral on $l$ satisfies $\int X\rmd l=\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu$.
+\item The Choquet integral on $r$ satisfies $\int X\rmd r=\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu$.
+\end{itemize}
+\end{thm}
+
+\yutsung{{Put an example}, and other integral here...}
 

### 2017-04-15 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 and see how to compute the expectation value of different random variables.
-To simplify the discussion later, we will only consider a random variable~$X:\Omega\rightarrow\left[0,1\right]$
+To simplify the discussion later, we will only consider a random variable~$X:\Omega\rightarrow\mathbb{R}$
 which is a step function, i.e., $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
@@
 \begin{eqnarray}
-\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(E_{i}\right)\textrm{ .}
+\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(E_{i}\right)\textrm{ .}\label{eq:expectation}
 \end{eqnarray}
@@
 
-After we discussed the conventional expectation value, we can start
-to discuss the expectation value of IVPM. First, the only source use
-the exact same definition as ours is written by Jamison and Lodwick~\cite{JamisonLodwick2004}
-so it's reasonable to start from their definition of integration\footnote{Although they said they would explore their integration in more details,
-they change their definition of IVPM later. Hence, I don't know if
-they have any further development of their integration.}. Their integral of $X$ is defined by 
-\begin{eqnarray*}
-\int_{E}^{\textrm{JL}}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}e_{i}}{e_{i}\in\bar{\mu}\left(E_{i}\right)\textrm{ and }\sum_{i=1}^{N}e_{i}=\min\bar{\mu}\left(E\right)},\right.\\
- &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}e_{i}}{e_{i}\in\bar{\mu}\left(E_{i}\right)\textrm{ and }\sum_{i=1}^{N}e_{i}=\max\bar{\mu}\left(E\right)}\right]\textrm{ .}
-\end{eqnarray*}
-In this definition, we still work on the weighted average. Since we
-don't know the exact probability, we want to average on all possible
-allowed probability, which is represented by the requirement on $e_{i}\in\bar{\mu}\left(E_{i}\right)$.
-However, I don't have a clear intuition on why they want $\sum_{i=1}^{N}e_{i}=\min\bar{\mu}\left(E\right)$
-and $\sum_{i=1}^{N}e_{i}=\max\bar{\mu}\left(E\right)$, and we will
-have a more intuitive definition following this line when we move
-on to Choquet integral~\cite{Choquet1954,Grabisch2016}. After we
-have the definition, we can consider the IVPM~$\bar{\mu}$ in example~\ref{ex3}.
-Because $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$, we have
-\begin{eqnarray*}
-\int_{\Omega}^{\textrm{JL}}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}e_{i}}{e_{i}\in\bar{\mu}\left(E_{i}\right)\textrm{ and }\sum_{i=1}^{N}e_{i}=1},\right.\\
- &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}e_{i}}{e_{i}\in\bar{\mu}\left(E_{i}\right)\textrm{ and }\sum_{i=1}^{N}e_{i}=1}\right]\\
- & = & \left[\inf\set{e_{1}+2e_{2}}{e_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ , }e_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ , }e_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ , and }e_{0}+e_{1}+e_{2}=1},\right.\\
- &  & \left.\sup\set{e_{1}+2e_{2}}{e_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ , }e_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ , }e_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ , and }e_{0}+e_{1}+e_{2}=1}\right]\\
- & = & \left[\inf\set{e_{1}+2e_{2}}{0\le e_{0}\le\frac{1}{2}\textrm{ , }\frac{1}{2}\le e_{1}\le1\textrm{ , }e_{2}=0\textrm{ , and }e_{0}+e_{1}+e_{2}=1},\right.\\
- &  & \left.\sup\set{e_{1}+2e_{2}}{0\le e_{0}\le\frac{1}{2}\textrm{ , }\frac{1}{2}\le e_{1}\le1\textrm{ , }e_{2}=0\textrm{ , and }e_{0}+e_{1}+e_{2}=1}\right]\\
- & = & \left[\inf\set{e_{1}}{0\le e_{0}\le\frac{1}{2}\textrm{ , }\frac{1}{2}\le e_{1}\le1\textrm{ , and }e_{0}+e_{1}=1},\right.\\
- &  & \left.\sup\set{e_{1}}{0\le e_{0}\le\frac{1}{2}\textrm{ , }\frac{1}{2}\le e_{1}\le1\textrm{ , and }e_{0}+e_{1}=1}\right]\\
- & = & \left[\frac{1}{2},1\right]\textrm{ .}
-\end{eqnarray*}
-
-\yutsung{{Put the definition of }Choquet integral, other meta-discourse
-here...}
+There are various different integral defined for IVPMs, and the most
+famous one is called the Choquet integral~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
+Let $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$ be a positive random
+variable with $0\le x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$
+and $\bar{\mu}:\events\rightarrow\mathscr{I}$ a classical IVPM such
+that $l:\events\rightarrow\left[0,1\right]$ and $r:\events\rightarrow\left[0,1\right]$
+be the left-end and the right-end of $\bar{\mu}$, respectively, i.e.,
+$\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$,
+the Choquet integral of $X$ with respect to $\bar{\mu}$ is 
+\begin{eqnarray}
+\int X\rmd\bar{\mu} & = & \sum_{i=1}^{N}\left(x_{i}-x_{i-1}\right)\bar{\mu}\left(\bigcup_{j\ge i}E_{j}\right)\textrm{ ,}\\
+ & = & \sum_{i=1}^{N}x_{i}\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\label{eq:interval-expectation}
+\end{eqnarray}
+where $x_{0}=0$, and $x[l,r]=[xl,xr]$ for $x\ge0$. Similar to equation~(\ref{eq:expectation}),
+equation~(\ref{eq:interval-expectation}) can be considered as weighted
+average of the possible outcomes of $X$ as well, where the ``weight''
+\[
+\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\subseteq\left[l\left(E_{i}\right),r\left(E_{i}\right)\right]=\bar{\mu}\left(E_{i}\right)\textrm{ .}
+\]
+is tighter than the natural weight. This is reasonable because only
+one event can happen at once so we don't be so pessimistic to accumulate
+all possible fuzziness together, and use $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}\right)$.
 

### 2017-04-16 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 famous one is called the Choquet integral~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
-Let $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$ be a positive random
-variable with $0\le x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$
-and $\bar{\mu}:\events\rightarrow\mathscr{I}$ a classical IVPM such
-that $l:\events\rightarrow\left[0,1\right]$ and $r:\events\rightarrow\left[0,1\right]$
-be the left-end and the right-end of $\bar{\mu}$, respectively, i.e.,
-$\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$,
-the Choquet integral of $X$ with respect to $\bar{\mu}$ is 
-\begin{eqnarray}
-\int X\rmd\bar{\mu} & = & \sum_{i=1}^{N}\left(x_{i}-x_{i-1}\right)\bar{\mu}\left(\bigcup_{j\ge i}E_{j}\right)\textrm{ ,}\\
- & = & \sum_{i=1}^{N}x_{i}\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\label{eq:interval-expectation}
-\end{eqnarray}
-where $x_{0}=0$, and $x[l,r]=[xl,xr]$ for $x\ge0$. Similar to equation~(\ref{eq:expectation}),
-equation~(\ref{eq:interval-expectation}) can be considered as weighted
-average of the possible outcomes of $X$ as well, where the ``weight''
+Let $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$ be a random variable
+with $x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$ and $\bar{\mu}:\events\rightarrow\mathscr{I}$
+a classical IVPM such that $l:\events\rightarrow\left[0,1\right]$
+and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
+right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
+Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
+\begin{equation}
+\int X\rmd\bar{\mu}=\sum_{i=1}^{N}x_{i}\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\textrm{ ,}\label{eq:interval-expectation}
+\end{equation}
+where 
+\begin{equation} 
+x[l,r]=\cases{ 
+[xl,xr] & for $x\ge0$ ;\\
+[xr,xl] & for $x\le0$ .
+}
+\end{equation}
+Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
+can be considered as weighted average of the possible outcomes of
+$X$ as well, despite the ``weight''
 \[
-\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\subseteq\left[l\left(E_{i}\right),r\left(E_{i}\right)\right]=\bar{\mu}\left(E_{i}\right)\textrm{ .}
+\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\subseteq\left[l\left(E_{i}\right),r\left(E_{i}\right)\right]=\bar{\mu}\left(E_{i}\right)
 \]
-is tighter than the natural weight. This is reasonable because only
-one event can happen at once so we don't be so pessimistic to accumulate
-all possible fuzziness together, and use $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}\right)$.
-
-\begin{thm}\cite{Grabisch2016}For every classical interval-valued
-probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
-any random variable~$X:\Omega\rightarrow\mathbb{R}$, let $l:\events\rightarrow\left[0,1\right]$
-and $r:\events\rightarrow\left[0,1\right]$ be the left-end and the
-right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
-The following statements are equivalent.
-\begin{itemize}
-\item $\bar{\mu}$ is convex.
-\item The Choquet integral on $l$ satisfies $\int X\rmd l=\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu$.
-\item The Choquet integral on $r$ satisfies $\int X\rmd r=\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu$.
-\end{itemize}
+is tighter than the interval-valued probability of the corresponding
+event. Since only one event can happen at once, we don't have to be
+so pessimistic to accumulate all possible fuzziness together, and
+expect $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}\right)$ to happen.
+
+The Choquet integral has many desirable properties. For example, it
+can be represented as a weighted average over all minimum and maximum
+of the random variable. Most importantly, the Choquet integral has
+the same range as all expectation value in the core.
+
+\begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
+interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+and any random variable~$X:\Omega\rightarrow\mathbb{R}$. $\bar{\mu}$
+is convex if and only if
+
+\begin{equation}
+\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\textrm{ .}
+\end{equation}
 \end{thm}
 
-\yutsung{{Put an example}, and other integral here...}
+\yutsung{Put an example here if we need...}
+
+Before discussing the measurement process and their manifestations
+with quantum IVPMs, we first review various notations brought forward
+from conventional quantum theory. Assume that a physical system is
+represented by a density matrix~$\rho$, and that we wish to measure
+a physical quantity~${\cal O}$ of this system, with corresponding
+observable~$\mathbf{O}$, whose spectrum decomposition is given by
+\begin{equation}
+\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}\ .
+\end{equation}
+where $P_{i}$ is the projector onto the eigenspace of the eigenvalue~$\lambda_{i}$.
+Then the Born rule of CQT tells us that the expectation value of the
+observable~$\mathbf{O}$ is given by
+\begin{equation}
+\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\Tr\left(\rho P_{i}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .
+\end{equation}
 

### 2017-04-16 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 \end{equation}
-where 
+where multiplying a negative number switching the left and right end
+of an interval 
 \begin{equation} 
@@
 The Choquet integral has many desirable properties. For example, it
-can be represented as a weighted average over all minimum and maximum
-of the random variable. Most importantly, the Choquet integral has
-the same range as all expectation value in the core.
+has the same range as all expectation value in the core.
 
@@
 
-Before discussing the measurement process and their manifestations
-with quantum IVPMs, we first review various notations brought forward
-from conventional quantum theory. Assume that a physical system is
-represented by a density matrix~$\rho$, and that we wish to measure
-a physical quantity~${\cal O}$ of this system, with corresponding
+Before discussing quantum IVPMs, we first review various notations
+brought forward from conventional quantum theory. Assume that a physical
+system is represented by a density matrix~$\rho$, and that we wish
+to measure a physical quantity~${\cal O}$ of this system, with corresponding
 observable~$\mathbf{O}$, whose spectrum decomposition is given by
-\begin{equation}
-\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}\ .
-\end{equation}
-where $P_{i}$ is the projector onto the eigenspace of the eigenvalue~$\lambda_{i}$.
-Then the Born rule of CQT tells us that the expectation value of the
-observable~$\mathbf{O}$ is given by
+$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, where $P_{i}$ is the
+projector onto the eigenspace of the eigenvalue~$\lambda_{i}$. Then,
+the Born rule of CQT tells us that the expectation value of the observable~$\mathbf{O}$
+is given by
 \begin{equation}

### 2017-04-16 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 \newcommand{\midd}{{\mbox{\wesa{middle}}}}
-\newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
+\usepackage[braket,qm]{qcircuit}
 \newcommand{\fket}[1]{{|#1\rangle}}
 \newcommand{\fproj}[1]{|#1\rangle\langle #1|}
-\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
 \newcommand{\proj}[1]{\op{#1}{#1}}
@@
 \newcommand{\minus}{\texttt{-}}
-\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}
 
@@
 interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-and any random variable~$X:\Omega\rightarrow\mathbb{R}$. $\bar{\mu}$
+and any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
 is convex if and only if
@@
 the Born rule of CQT tells us that the expectation value of the observable~$\mathbf{O}$
-is given by
-\begin{equation}
-\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\Tr\left(\rho P_{i}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .
+is given by~\cite{544199,Jaeger2007}
+\begin{equation}
+\expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
+\end{equation}
+
+Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
+and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
+right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
+Given the same observable with an extra condition~$x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$,
+we can combine equation~(\ref{eq:interval-expectation}) and (\ref{eq:quantum-expectation})
+to define the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
+as
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N}\lambda_{i}\left[l\left(\sum_{j\ge i}P_{j}\right)-l\left(\sum_{j\ge i+1}P_{j}\right),r\left(\sum_{j\ge i}P_{j}\right)-r\left(\sum_{j\ge i+1}P_{j}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
 \end{equation}

### 2017-04-16 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 \begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-and any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
-is convex if and only if
-
+IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and any random variable~$X:\Omega\rightarrow\mathbb{R}$,
+$\bar{\mu}$ is convex if and only if 
 \begin{equation}
@@
 \end{equation}
+Let $\events'$ denote the minimal commuting sub-event space containing
+$\left\{ P_{i}\right\} _{i=1}^{N}$. Then, we have the corresponding
+theorem.
+
+\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+and any observable~$\mathbf{O}$, if $\bar{\mu}$ is convex, then
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\mathrm{core}\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\mathrm{core}\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
+\end{equation}
+Conversely, if equation~(\ref{eq:quantum-interval-expectation-core})
+holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
 

### 2017-04-16 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 in example~\ref{ex1}, the expectation value of $X_{0}$ is
-\begin{eqnarray*}
-\int X_{0}\rmd\pmeas & = & 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
- & = & 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .}
-\end{eqnarray*}
+\begin{equation}\eqalign{ 
+\int X_{0}\rmd\pmeas & = 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
+ & = 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .} 
+}\end{equation}
 
@@
 \end{equation}
-Let $\events'$ denote the minimal commuting sub-event space containing
-$\left\{ P_{i}\right\} _{i=1}^{N}$. Then, we have the corresponding
-theorem.
+Let $\events\left(\mathbf{O}\right)$ denote the minimal sub-event
+space containing $\left\{ P_{i}\right\} _{i=1}^{N}$. Then, we have
+the corresponding theorem.
 
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\mathrm{core}\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\mathrm{core}\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\mathrm{core}\left(\bar{\mu},\events\left(\mathbf{O}\right)\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\mathrm{core}\left(\bar{\mu},\events\left(\mathbf{O}\right)\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
 \end{equation}

### 2017-04-17 prop_iop.tex
prop_iop.tex Splitting \section{Expectation Values for IVPMs} into two versions...

@@
 
-\section{Expectation Values for IVPMs}
+\section{Expectation Values for IVPMs (Version 1)}
 
@@
 
-There are various different integral defined for IVPMs, and the most
+There are various kind of integrals defined for IVPMs, and the most
 famous one is called the Choquet integral~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
-Let $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$ be a random variable
-with $x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$ and $\bar{\mu}:\events\rightarrow\mathscr{I}$
-a classical IVPM such that $l:\events\rightarrow\left[0,1\right]$
-and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
-right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
-Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
-\begin{equation}
-\int X\rmd\bar{\mu}=\sum_{i=1}^{N}x_{i}\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\textrm{ ,}\label{eq:interval-expectation}
-\end{equation}
-where multiplying a negative number switching the left and right end
-of an interval 
+
+\begin{definition}Consider the following.
+\begin{itemize}
+\item $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$ be a random variable with
+$x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$ and $E_{i}\cap E_{j}=\emptyset$.
+\item $\bar{\mu}:\events\rightarrow\mathscr{I}$ a classical IVPM such that
+$l:\events\rightarrow\left[0,1\right]$ and $r:\events\rightarrow\left[0,1\right]$
+are the left-end and the right-end of $\bar{\mu}$, respectively,
+i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
+\item Multiplying a negative number switching the left and right end of
+an interval 
 \begin{equation} 
@@
 \end{equation}
+\end{itemize}
+Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
+\begin{equation}
+\int X\rmd\bar{\mu}=\sum_{i=1}^{N}x_{i}\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\textrm{ .}\label{eq:interval-expectation}
+\end{equation}
+\end{definition}
+
 Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
@@
 to measure a physical quantity~${\cal O}$ of this system, with corresponding
-observable~$\mathbf{O}$, whose spectrum decomposition is given by
+observable~$\mathbf{O}$, whose spectral decomposition is given by
 $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, where $P_{i}$ is the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Expectation Values for IVPMs (Version 2)}
+
+We may need to understand how to define expectation values of an observable
+for quantum IVPMs. Recall an observable is the quantum version of
+a random variable. Hence, in order to define expectation values of
+an observable, we need to understand the definition of expectation
+values of a random variable for an classical IVPM. Since the expectation
+value of random variable~$X$ is the integral $\int X\rmd\pmeas$~\cite{Kolmogorov1950},
+we need to understand the meaning of integration on IVPMs. In the
+rest of the section, we will consider the real-valued and interval-valued
+probability measure defined in example~\ref{ex1} and \ref{ex3},
+and see how to compute the expectation value of different random variables.
+To simplify the discussion later, we will only consider a random variable~$X:\Omega\rightarrow\mathbb{R}$
+which is a step function, i.e., $X=\sum_{i=N^{-}}^{N^{+}}x_{i}\mathbf{1}_{E_{i}}$,
+where 
+\begin{itemize}
+\item $x_{i}\ge0$ for $i\ge0$ and $x_{i}\le0$ for $i\le0$.
+\item $E_{N^{+}}\subseteq E_{N^{+}-1}\subseteq\ldots\subseteq E_{2}\subseteq E_{1}\subseteq\Omega\backslash E_{-1}$,
+$E_{N^{-}}\subseteq E_{N^{-}+1}\subseteq\ldots\subseteq E_{-2}\subseteq E_{-1}\subseteq\Omega\backslash E_{1}$,
+and $\Omega=E_{0}$.
+\item $\mathbf{1}_{E}$ is the indicator function defined by 
+\begin{equation} 
+\mathbf{1}_{A}(x)=\cases{ 
+1 & if $x\in A$ ;\\ 
+0 & if $x\notin A$. 
+}
+\end{equation}
+\end{itemize}
+Given a random variable~$X$ and a probability measure~$\pmeas$,
+the expectation value of $X$ is 
+\begin{eqnarray}
+\int X\rmd\pmeas & = & \sum_{i=N^{-}}^{N^{+}}x_{i}\pmeas\left(E_{i}\right)\textrm{ .}\label{eq:expectation-1}
+\end{eqnarray}
+
+There are various kind of integrals defined for IVPMs, and the most
+famous one is called the Choquet integral~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
+
+\begin{definition}Given the random variable~$X$ as previous paragraph,
+and a classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
+Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
+\begin{equation}
+\int X\rmd\bar{\mu}=\sum_{i=N^{-}}^{N^{+}}x_{i}\bar{\mu}\left(E_{i}\right)\textrm{ ,}\label{eq:interval-expectation-1}
+\end{equation}
+where multiplying a negative number switching the left and right end
+of an interval 
+\begin{equation} 
+x[l,r]=\cases{ 
+[xl,xr] & for $x\ge0$ ;\\
+[xr,xl] & for $x\le0$ .
+}
+\end{equation}
+\end{definition}
+
+The Choquet integral has many desirable properties. For example, it
+has the same range as all expectation value in the core.
+
+\begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
+IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and any random variable~$X:\Omega\rightarrow\mathbb{R}$,
+$\bar{\mu}$ is convex if and only if 
+\begin{equation}
+\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\textrm{ .}
+\end{equation}
+\end{thm}
+
+\yutsung{Put an example here if we need...}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{comment}

### 2017-04-18 prop_iop.tex
prop.tex \section{Expectation Values for IVPMs} Updating...

@@
 
-\section{Expectation Values for IVPMs (Version 1)}
+\section{Expectation Values for IVPMs}
 
@@
 There are various kind of integrals defined for IVPMs, and the most
-famous one is called the Choquet integral~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
+famous one is called the Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
 
@@
 \begin{itemize}
-\item $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$ be a random variable with
-$x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$ and $E_{i}\cap E_{j}=\emptyset$.
+\item Let $X=\sum_{i=N^{-}}^{N^{+}}x_{i}\mathbf{1}_{E_{i}}$ be a positive
+random variable with 
+\[
+x_{N^{-}}\le x_{N^{-}+1}\le\ldots\le x_{-2}\le x_{-1}\le x_{0}=0\le x_{1}\le x_{2}\le\ldots\le x_{N^{+}-1}\le x_{N^{+}}
+\]
+ and $E_{i}\cap E_{j}=\emptyset$.
+\item Let $E_{i}'=\bigcup_{j\ge i}E_{j}=\set{\omega\in\Omega}{X\left(\omega\right)\ge x_{i}}\in\events$
+for $i>0$, and $E_{i}'=\bigcup_{j\le i}E_{j}=\set{\omega\in\Omega}{X\left(\omega\right)\le x_{i}}\in\events$
+for $i<0$.
 \item $\bar{\mu}:\events\rightarrow\mathscr{I}$ a classical IVPM such that
@@
 \end{equation}
+\item We also need to define the sign function as 
+\begin{equation} 
+\mathrm{sign}=\cases{ 
+1 & for $x\ge0$ ;\\
+0 & for $x=0$ ;\\
+-1 & for $x\le0$ .
+}
+\end{equation}
 \end{itemize}
@@
 \begin{equation}
-\int X\rmd\bar{\mu}=\sum_{i=1}^{N}x_{i}\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\textrm{ .}\label{eq:interval-expectation}
+\int X\rmd\bar{\mu}=\sum_{i=N^{-}}^{N^{+}}x_{i}\left[l\left(E_{i}'\right)-l\left(E_{i+\mathrm{sign}\left(i\right)}'\right),r\left(E_{i}'\right)-r\left(E_{i+\mathrm{sign}\left(i\right)}'\right)\right]\textrm{ .}\label{eq:interval-expectation}
 \end{equation}
@@
 \[
-\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\subseteq\left[l\left(E_{i}\right),r\left(E_{i}\right)\right]=\bar{\mu}\left(E_{i}\right)
+\left[l\left(E_{i}'\right)-l\left(E_{i+1}'\right),r\left(E_{i}'\right)-r\left(E_{i+1}'\right)\right]\subseteq\left[l\left(E_{i}\right),r\left(E_{i}\right)\right]=\bar{\mu}\left(E_{i}\right)
 \]
@@
 right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
-Given the same observable with an extra condition~$x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$,
-we can combine equation~(\ref{eq:interval-expectation}) and (\ref{eq:quantum-expectation})
-to define the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
-as
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N}\lambda_{i}\left[l\left(\sum_{j\ge i}P_{j}\right)-l\left(\sum_{j\ge i+1}P_{j}\right),r\left(\sum_{j\ge i}P_{j}\right)-r\left(\sum_{j\ge i+1}P_{j}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
+Given the same observable with an extra condition~
+\[
+x_{N^{-}}\le x_{N^{-}+1}\le\ldots\le x_{-2}\le x_{-1}\le x_{0}=0\le x_{1}\le x_{2}\le\ldots\le x_{N^{+}-1}\le x_{N^{+}}
+\]
+and let $P_{i}'=\sum_{j\ge i}P_{j}\in\events$ for $i>0$, and $P_{i}'=\sum_{j\le i}P_{j}\in\events$
+for $i<0$, we can combine equation~(\ref{eq:interval-expectation})
+and (\ref{eq:quantum-expectation}) to define the expectation value
+of $\mathbf{O}$ with respect to $\bar{\mu}$ as
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N}\lambda_{i}\left[l\left(P_{i}'\right)-l\left(P_{i+\mathrm{sign}\left(i\right)}'\right),r\left(P_{i}'\right)-r\left(P_{i+\mathrm{sign}\left(i\right)}'\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
 \end{equation}
@@
 the corresponding theorem.
-
-\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-and any observable~$\mathbf{O}$, if $\bar{\mu}$ is convex, then
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\mathrm{core}\left(\bar{\mu},\events\left(\mathbf{O}\right)\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\mathrm{core}\left(\bar{\mu},\events\left(\mathbf{O}\right)\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
-\end{equation}
-Conversely, if equation~(\ref{eq:quantum-interval-expectation-core})
-holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Expectation Values for IVPMs (Version 2)}
-
-We may need to understand how to define expectation values of an observable
-for quantum IVPMs. Recall an observable is the quantum version of
-a random variable. Hence, in order to define expectation values of
-an observable, we need to understand the definition of expectation
-values of a random variable for an classical IVPM. Since the expectation
-value of random variable~$X$ is the integral $\int X\rmd\pmeas$~\cite{Kolmogorov1950},
-we need to understand the meaning of integration on IVPMs. In the
-rest of the section, we will consider the real-valued and interval-valued
-probability measure defined in example~\ref{ex1} and \ref{ex3},
-and see how to compute the expectation value of different random variables.
-To simplify the discussion later, we will only consider a random variable~$X:\Omega\rightarrow\mathbb{R}$
-which is a step function, i.e., $X=\sum_{i=N^{-}}^{N^{+}}x_{i}\mathbf{1}_{E_{i}}$,
-where 
-\begin{itemize}
-\item $x_{i}\ge0$ for $i\ge0$ and $x_{i}\le0$ for $i\le0$.
-\item $E_{N^{+}}\subseteq E_{N^{+}-1}\subseteq\ldots\subseteq E_{2}\subseteq E_{1}\subseteq\Omega\backslash E_{-1}$,
-$E_{N^{-}}\subseteq E_{N^{-}+1}\subseteq\ldots\subseteq E_{-2}\subseteq E_{-1}\subseteq\Omega\backslash E_{1}$,
-and $\Omega=E_{0}$.
-\item $\mathbf{1}_{E}$ is the indicator function defined by 
-\begin{equation} 
-\mathbf{1}_{A}(x)=\cases{ 
-1 & if $x\in A$ ;\\ 
-0 & if $x\notin A$. 
-}
-\end{equation}
-\end{itemize}
-Given a random variable~$X$ and a probability measure~$\pmeas$,
-the expectation value of $X$ is 
-\begin{eqnarray}
-\int X\rmd\pmeas & = & \sum_{i=N^{-}}^{N^{+}}x_{i}\pmeas\left(E_{i}\right)\textrm{ .}\label{eq:expectation-1}
-\end{eqnarray}
-
-There are various kind of integrals defined for IVPMs, and the most
-famous one is called the Choquet integral~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
-
-\begin{definition}Given the random variable~$X$ as previous paragraph,
-and a classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
-Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
-\begin{equation}
-\int X\rmd\bar{\mu}=\sum_{i=N^{-}}^{N^{+}}x_{i}\bar{\mu}\left(E_{i}\right)\textrm{ ,}\label{eq:interval-expectation-1}
-\end{equation}
-where multiplying a negative number switching the left and right end
-of an interval 
-\begin{equation} 
-x[l,r]=\cases{ 
-[xl,xr] & for $x\ge0$ ;\\
-[xr,xl] & for $x\le0$ .
-}
-\end{equation}
-\end{definition}
-
-The Choquet integral has many desirable properties. For example, it
-has the same range as all expectation value in the core.
-
-\begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
-IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and any random variable~$X:\Omega\rightarrow\mathbb{R}$,
-$\bar{\mu}$ is convex if and only if 
-\begin{equation}
-\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\textrm{ .}
-\end{equation}
-\end{thm}
-
-\yutsung{Put an example here if we need...}
 

### 2017-04-19 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Fix typos...

@@
 
-\begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
-IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and any random variable~$X:\Omega\rightarrow\mathbb{R}$,
-$\bar{\mu}$ is convex if and only if 
+\begin{thm}\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}For
+every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
+any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
+is convex if and only if 
 \begin{equation}
@@
 \[
-x_{N^{-}}\le x_{N^{-}+1}\le\ldots\le x_{-2}\le x_{-1}\le x_{0}=0\le x_{1}\le x_{2}\le\ldots\le x_{N^{+}-1}\le x_{N^{+}}
+\lambda_{N^{-}}\le\lambda_{N^{-}+1}\le\ldots\le\lambda_{-2}\le\lambda_{-1}\le\lambda_{0}=0\le\lambda_{1}\le\lambda_{2}\le\ldots\le\lambda_{N^{+}-1}\le\lambda_{N^{+}}
 \]

### 2017-04-19 prop_letter.tex
prop_letter.tex \paragraph{Quantum Interval-valued Probability Measures (\emph{IVPMs})} Updating...

@@
 condition that provides only a bound and not an equivalence as in
-Eq. \eqref{eq:QuantumProbability-Addition}. For example, if we consider
+Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
 $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
@@
 
-It is easy to establish that quantum IVPMs generalize conventional
-quantum probability measures and classical IVPMs. In particular, any
-quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-can be recast as an interval-valued measure~$\iota_{\infty}\circ\mu:\events\rightarrow\mathscr{I}_{\infty}$,
-where $\circ$ denotes function composition, $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
-defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. In another
-word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$ are just the
-same as quantum real-valued probability measures where Gleason's theorem
-can apply.
+Formally, we can ask: what can we deduce about the state of a quantum
+system given a quantum interval-valued probability measure, i.e.,
+given observations done with finite resources. Since the probabilities
+are intervals, it is intuitive to say a state~$\rho$ is consistent
+with $\bar{\mu}$ on a projector~$P$ if 
+\begin{equation}
+\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)\textrm{ .}
+\end{equation}
 
-More interesting examples comes when we focus on only three intervals
-$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
+Since our measurement is fuzzy, generally there are more than one
+state consistent with a particular quantum IVPM. For example, consider
+three intervals $\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
 where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
@@
 is a quantum IVPM. This measure represents the beliefs of an experimenter
-with no prior knowledge about the particular quantum system in question.
+with no prior knowledge about the particular quantum system in question,
+and any state is consistent with $\bar{\mu}_{1}$ on any projectors.
+
+In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+any quantum probability measure can be recast as an interval-valued
+one. For $d\ge3$, the question reduces to Gleason's theorem which
+states that for any quantum IVPM~$\bar{\mu}$, there is an unique
+state can be consistent with $\bar{\mu}$ on every projector.
+
+While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
+IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
+is another one corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
+However, before dive into the Kochen-Specker theorem, it is better
+to understand how to define expectation value of an observable with
+quantum IVPMs.
+
+\newpage{}
 
@@
 know nothing about a coin before she toss it.
-
-While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
-IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-is another one corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
 

### 2017-04-20 prop_letter.tex
prop_letter.tex \newcommand{\coreBorn}{\mathrm{C}} Added...

@@
 \allowdisplaybreaks
+\newcommand{\coreBorn}{\mathrm{C}}
 
@@
 
+Furthermore, if we express the observable~$\mathbf{O}$ as its spectrum
+decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
+value of $\mathbf{O}$ is given by~\cite{544199,Jaeger2007}
+\begin{equation}
+\expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
+\end{equation}
+
 \paragraph{Quantum Interval-valued Probability Measures (\emph{IVPMs})}
@@
 To formalize the idea of finite precision measurement, we next introduce
-the notion of quantum IVPM~$\bar{\mu}$. The latter replaces 
-the infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$ of
-intervals. Since the intervals $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$ 
-should be included in $\mathscr{I}$, and arithmetic operations on intervals satisfy
-\begin{subequations}\label{eq:interval-operations}
+the notion of quantum IVPM~$\bar{\mu}$. The latter replaces the
+infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$
+of intervals. Since the intervals $\imposs=\left[0,0\right]$ and
+$\necess=\left[1,1\right]$ should be included in $\mathscr{I}$,
+and arithmetic operations on intervals satisfy \begin{subequations}\label{eq:interval-operations}
 \begin{eqnarray}
- &  & \left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right], \textrm{ and}\\
- &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}] ,
+ &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
+ &  & x[l,r]=\begin{cases}
+[xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
+[xr,xl] & \textrm{for }x\le0\textrm{ .}
+\end{cases}
 \end{eqnarray}
-\end{subequations}
-$\bar{\mu}:\events\rightarrow\mathscr{I}$ is defined by the axioms:
+\end{subequations} $\bar{\mu}:\events\rightarrow\mathscr{I}$ is
+defined by the axioms: 
 \begin{itemize}
@@
 given observations done with finite resources. Since the probabilities
-are intervals, it is intuitive to say a state~$\rho$ is consistent
+are now intervals, it is intuitive to say a state~$\rho$ is consistent
 with $\bar{\mu}$ on a projector~$P$ if 
 \begin{equation}
-\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)\textrm{ .}
+\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)\textrm{ ,}
 \end{equation}
+and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
 
@@
 states that for any quantum IVPM~$\bar{\mu}$, there is an unique
-state can be consistent with $\bar{\mu}$ on every projector.
+state consistent with $\bar{\mu}$ on every projector.
 
@@
 IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-is another one corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
+is another one, and corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
 However, before dive into the Kochen-Specker theorem, it is better
@@
 quantum IVPMs.
+
+\paragraph{Expectation Values for Quantum IVPMs}
+
+Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
+and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
+right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
+This time, when we express the observable~$\mathbf{O}$ as its spectrum
+decomposition~$\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}$,
+we separate the positive and negative eigenvalues and order them from
+the smallest to the largest 
+\begin{equation}
+\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
+\end{equation}
+Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta f\left(P_{i}^{s\prime}\right)=f\left(P_{i}^{s\prime}\right)-f\left(P_{i+1}^{s\prime}\right)$,
+where $s\in\left\{ +,-\right\} $ and $f\in\left\{ l,r\right\} $.
+We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+with (\ref{eq:quantum-expectation}) to define the expectation value
+of $\mathbf{O}$ with respect to $\bar{\mu}$ as
+\begin{eqnarray}
+\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta l\left(P_{i}^{+\prime}\right),\Delta r\left(P_{i}^{+\prime}\right)\right]\\
+ &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta l\left(P_{i}^{-\prime}\right),\Delta r\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
+\end{eqnarray}
+Let $\events'$ denote the set containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$
+and satisfies the following conditions.
+\begin{itemize}
+\item $\mathbb{0}\in\events'$. 
+\item $\mathbb{1}\in\events'$. 
+\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
+\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
+we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
+\end{itemize}
+Then, we have the following theorem.
+
+\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+and any observable~$\mathbf{O}$, if $\bar{\mu}$ is convex, then
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
+\end{equation}
+Conversely, if equation~(\ref{eq:quantum-interval-expectation-core})
+holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
 
@@
 the follow conditions.
-\begin{itemize}
-\item $\mathbb{0}\in\events'$. 
-\item $\mathbb{1}\in\events'$. 
-\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
-\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
-we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
-\end{itemize}
+
 For example, $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
@@
 \begin{equation}
-\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
+\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
 \end{equation}
 The core of an interval-valued probability measure is the set of states
-it approximates. For example, $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
+it approximates. For example, $\coreBorn\left(\bar{\mu}_{1},\events'\right)$
 contains every density matrix. The 2-dimensional measure~$\mu_{0}$
@@
 \begin{eqnarray}
-\mathrm{core}\left(\bar{\mu}_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
-\mathrm{core}\left(\bar{\mu}_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
-\mathrm{core}\left(\bar{\mu}_{0},\events\right) & = & \emptyset\textrm{ ,}
+\coreBorn\left(\bar{\mu}_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
+\coreBorn\left(\bar{\mu}_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
+\coreBorn\left(\bar{\mu}_{0},\events\right) & = & \emptyset\textrm{ ,}
 \end{eqnarray}
@@
 \end{itemize}
-Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
+Then, $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
 
@@
 and $\proj{\ps}$. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
-for any mixed state~$\rho\in\mathrm{core}\left(\bar{\mu},\events_{1}\right)$,
+for any mixed state~$\rho\in\coreBorn\left(\bar{\mu},\events_{1}\right)$,
 we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$.
@@
 and $\ket{\ps}$. The only choice of $\rho$ is $\ket{2}$, and it
-is easy to verify $\proj{2}$ is actually in $\mathrm{core}\left(\bar{\mu},\events_{1}\right)$.
+is easy to verify $\proj{2}$ is actually in $\coreBorn\left(\bar{\mu},\events_{1}\right)$.
 
 Similarly, let $\events_{2}$ be the minimal event space containing
-both $\proj{0}$ and $\proj{\ps'}$. We have $\mathrm{core}\left(\bar{\mu},\events_{2}\right)=\left\{ \proj{1}\right\} $.
+both $\proj{0}$ and $\proj{\ps'}$. We have $\coreBorn\left(\bar{\mu},\events_{2}\right)=\left\{ \proj{1}\right\} $.
 Therefore, 
 \begin{equation}
-\mathrm{core}\left(\bar{\mu},\events\right)\subseteq\mathrm{core}\left(\bar{\mu},\events_{1}\right)\cap\mathrm{core}\left(\bar{\mu},\events_{2}\right)=\emptyset\textrm{ ,}
+\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},\events_{1}\right)\cap\coreBorn\left(\bar{\mu},\events_{2}\right)=\emptyset\textrm{ ,}
 \end{equation}

### 2017-04-20 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

@@
 \imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
-\unknown & \text{, otherwise.}
+\unknown & \text{, otherwise,}
 \end{cases}\label{eq:homomorphism-1}
@@
 is another one, and corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
-However, before dive into the Kochen-Specker theorem, it is better
+However, before diving into the Kochen-Specker theorem, it is better
 to understand how to define expectation value of an observable with
@@
 
-Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
-and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
-right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
+Consider a quantum IVPM~$\bar{\mu}$ such that $\boldsymbol{l}:\events\rightarrow\left[0,1\right]$
+and $\boldsymbol{r}:\events\rightarrow\left[0,1\right]$ are the left-end
+and the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\boldsymbol{l}\left(E\right),\boldsymbol{r}\left(E\right)\right]$.
 This time, when we express the observable~$\mathbf{O}$ as its spectrum
@@
 Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta f\left(P_{i}^{s\prime}\right)=f\left(P_{i}^{s\prime}\right)-f\left(P_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $f\in\left\{ l,r\right\} $.
+where $s\in\left\{ +,-\right\} $ and $f\in\left\{ \boldsymbol{l},\boldsymbol{r}\right\} $.
 We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-with (\ref{eq:quantum-expectation}) to define the expectation value
-of $\mathbf{O}$ with respect to $\bar{\mu}$ as
+with Eq.~(\ref{eq:quantum-expectation}) to define the expectation
+value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
 \begin{eqnarray}
-\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta l\left(P_{i}^{+\prime}\right),\Delta r\left(P_{i}^{+\prime}\right)\right]\\
- &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta l\left(P_{i}^{-\prime}\right),\Delta r\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
+\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\boldsymbol{l}\left(P_{i}^{+\prime}\right),\Delta\boldsymbol{r}\left(P_{i}^{+\prime}\right)\right]\nonumber \\
+ &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\boldsymbol{l}\left(P_{i}^{-\prime}\right),\Delta\boldsymbol{r}\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
 \end{eqnarray}
@@
 \end{itemize}
+And $\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
+$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
+where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
 Then, we have the following theorem.
@@
 \end{equation}
-Conversely, if equation~(\ref{eq:quantum-interval-expectation-core})
+Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
 holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
+
+For example, to compute the expectation value of $\sigma_{\mathrm{z}}=\proj{0}-\proj{1}$
+with respect to $\bar{\mu}_{1}$, we have $N^{+}=N^{-}=1$, $\lambda_{1}^{+}=1$,
+$\lambda_{1}^{-}=-1$, $P_{1}^{+\prime}=\proj{0}$, $P_{1}^{-\prime}=\proj{1}$,
+$P_{2}^{+\prime}=P_{2}^{-\prime}=\mathbb{0}$. Let $\left[\boldsymbol{l}_{1}\left(E\right),\boldsymbol{r}_{1}\left(E\right)\right]=\bar{\mu}_{1}\left(E\right)$,
+then $\Delta\boldsymbol{l}_{1}\left(P_{1}^{+\prime}\right)=\boldsymbol{l}_{1}\left(\proj{0}\right)-\boldsymbol{l}_{1}\left(\mathbb{0}\right)=0$,
+$\Delta\boldsymbol{l}_{1}\left(P_{1}^{-\prime}\right)=\boldsymbol{l}_{1}\left(\proj{1}\right)-\boldsymbol{l}_{1}\left(\mathbb{0}\right)=0$,
+$\Delta\boldsymbol{r}_{1}\left(P_{1}^{+\prime}\right)=\boldsymbol{r}_{1}\left(\proj{0}\right)-\boldsymbol{r}_{1}\left(\mathbb{0}\right)=1$,
+$\Delta\boldsymbol{r}_{1}\left(P_{1}^{-\prime}\right)=\boldsymbol{r}_{1}\left(\proj{1}\right)-\boldsymbol{r}_{1}\left(\mathbb{0}\right)=1$.
+Therefore, $\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}=\left[0,1\right]+\left(-1\right)\left[0,1\right]=\left[-1,1\right]$.
+
+On the other hand, it is easy to verify that $\bar{\mu}_{1}$ is convex.
+Every state is consistent with $\bar{\mu}_{1}$, in particular $\proj{0}$
+and $\proj{1}$. It is easy to see 
+\begin{eqnarray*}
+\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{1}}=-1\textrm{ ,}\\
+\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{0}}=1\textrm{ ,}
+\end{eqnarray*}
+which is consistent with the theorem.
 

### 2017-04-21 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

@@
 where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
-Then, we have the following theorem.
+Then, the expectation value of an observable with respect to a convex
+IVPM is just the minimum and maximum expectation value of the same
+observable with respect to the consistent states. Formally speaking,
+we have the following theorem.
 
@@
 which is consistent with the theorem.
+
+In contrast to the usual identity~$\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\rho}=\expval{\mathbf{O}_{1}}_{\rho}+\expval{\mathbf{O}_{2}}_{\rho}$,
+we have
+\[
+\expval{\mathbb{0}}_{\bar{\mu}_{1}}=\left[0,0\right]\ne\left[-2,2\right]=\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}+\expval{-\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}
+\]
+because the precision is easily be lost when applying arithmetic operations.
 

### 2017-04-22 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

@@
 IVPM is just the minimum and maximum expectation value of the same
-observable with respect to the consistent states. Formally speaking,
+observable with respect to its consistent states. Formally speaking,
 we have the following theorem.

### 2017-04-22 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

@@
 Every state is consistent with $\bar{\mu}_{1}$, in particular $\proj{0}$
-and $\proj{1}$. It is easy to see 
-\begin{eqnarray*}
+and $\proj{1}$. It is easy to see\begin{subequations}
+\begin{eqnarray}
 \min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{1}}=-1\textrm{ ,}\\
 \max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{0}}=1\textrm{ ,}
-\end{eqnarray*}
-which is consistent with the theorem.
+\end{eqnarray}
+\end{subequations}which is consistent with the theorem.
 
@@
 we have
-\[
-\expval{\mathbb{0}}_{\bar{\mu}_{1}}=\left[0,0\right]\ne\left[-2,2\right]=\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}+\expval{-\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}
-\]
+\begin{equation}
+\expval{\mathbb{0}}_{\bar{\mu}_{1}}=\left[0,0\right]\subsetneq\left[-2,2\right]=\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}+\expval{-\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}
+\end{equation}
 because the precision is easily be lost when applying arithmetic operations.
+In general, when $\bar{\mu}$ is convex, we have 
+\begin{equation}
+\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\bar{\mu}}\subseteq\expval{\mathbf{O}_{1}}_{\bar{\mu}}+\expval{\mathbf{O}_{2}}_{\bar{\mu}}\textrm{.}
+\end{equation}
 

### 2017-04-22 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

@@
 \begin{equation}
-\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\bar{\mu}}\subseteq\expval{\mathbf{O}_{1}}_{\bar{\mu}}+\expval{\mathbf{O}_{2}}_{\bar{\mu}}\textrm{.}
+\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\bar{\mu}}\subseteq\expval{\mathbf{O}_{1}}_{\bar{\mu}}+\expval{\mathbf{O}_{2}}_{\bar{\mu}}\textrm{ ,}
 \end{equation}
+for commuting $\mathbf{O}_{1}$ and $\mathbf{O}_{2}$.
+
+\yutsung{{Even if we have expectation value of }an observable, I
+don't know how to reason Mermin square~(\ref{eq:MerminSquare}) directly
+with quantum IVPM so far. The problem is the valuation function~$v$
+is not an expectation value. Since the corresponding of Eq.~(\ref{eq:deterministic-product}),
+$E\left[XY\right]=E\left[X\right]E\left[Y\right]$, doesn't hold for
+expectation value except $X$ and $Y$ are uncorrelated or even independent~\cite{rohatgi2011introduction}.}
 
@@
  &  & \sum_{j}v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j}\mathbf{O}_{j}\right)\textrm{ and}\\
- &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).
+ &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).\label{eq:deterministic-product}
 \end{eqnarray}

### 2017-04-23 prop_letter.tex
prop_letter.tex Small things here and there...

@@
 not only a uniform framework to understand Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
-and the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
+and the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
 but also some examples which cannot be explained by the Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
@@
 decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
-value of $\mathbf{O}$ is given by~\cite{544199,Jaeger2007}
+value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
 \begin{equation}
@@
 \begin{equation}
-\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion}
 \end{equation}
@@
 IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-is another one, and corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
+is another one, and corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
 However, before diving into the Kochen-Specker theorem, it is better
@@
 
-\yutsung{{Even if we have expectation value of }an observable, I
-don't know how to reason Mermin square~(\ref{eq:MerminSquare}) directly
+\yutsung{Even if we have expectation value of an observable, I don't
+know how to reason Mermin square~(\ref{eq:MerminSquare}) directly
 with quantum IVPM so far. The problem is the valuation function~$v$
-is not an expectation value. Since the corresponding of Eq.~(\ref{eq:deterministic-product}),
-$E\left[XY\right]=E\left[X\right]E\left[Y\right]$, doesn't hold for
-expectation value except $X$ and $Y$ are uncorrelated or even independent~\cite{rohatgi2011introduction}.}
+is not an expectation value. Since $E\left[XY\right]=E\left[X\right]E\left[Y\right]$,
+corresponding to Eq.~(\ref{eq:deterministic-product}), doesn't hold
+for expectation value except $X$ and $Y$ are uncorrelated or even
+independent~\cite{rohatgi2011introduction}.}
 

### 2017-04-23 prop_letter.tex
prop_letter.tex Add the following new commends...
\newcommand{\mul}{\ensuremath{\mu^{\mathrm{l}}}}
\newcommand{\mur}{\ensuremath{\mu^{\mathrm{r}}}}

@@
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
-\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
+\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
 \allowdisplaybreaks
-\newcommand{\coreBorn}{\mathrm{C}}
+\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
+\newcommand{\mul}{\ensuremath{\mu^{\mathrm{l}}}}
+\newcommand{\mur}{\ensuremath{\mu^{\mathrm{r}}}}
 
@@
 
-Consider a quantum IVPM~$\bar{\mu}$ such that $\boldsymbol{l}:\events\rightarrow\left[0,1\right]$
-and $\boldsymbol{r}:\events\rightarrow\left[0,1\right]$ are the left-end
-and the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\boldsymbol{l}\left(E\right),\boldsymbol{r}\left(E\right)\right]$.
+Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
 This time, when we express the observable~$\mathbf{O}$ as its spectrum
@@
 Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta f\left(P_{i}^{s\prime}\right)=f\left(P_{i}^{s\prime}\right)-f\left(P_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $f\in\left\{ \boldsymbol{l},\boldsymbol{r}\right\} $.
+where $s\in\left\{ +,-\right\} $ and $f\in\left\{ \mul,\mur\right\} $.
 We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
@@
 \begin{eqnarray}
-\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\boldsymbol{l}\left(P_{i}^{+\prime}\right),\Delta\boldsymbol{r}\left(P_{i}^{+\prime}\right)\right]\nonumber \\
- &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\boldsymbol{l}\left(P_{i}^{-\prime}\right),\Delta\boldsymbol{r}\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
+\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]\nonumber \\
+ &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
 \end{eqnarray}
@@
 $\lambda_{1}^{-}=-1$, $P_{1}^{+\prime}=\proj{0}$, $P_{1}^{-\prime}=\proj{1}$,
-$P_{2}^{+\prime}=P_{2}^{-\prime}=\mathbb{0}$. Let $\left[\boldsymbol{l}_{1}\left(E\right),\boldsymbol{r}_{1}\left(E\right)\right]=\bar{\mu}_{1}\left(E\right)$,
-then $\Delta\boldsymbol{l}_{1}\left(P_{1}^{+\prime}\right)=\boldsymbol{l}_{1}\left(\proj{0}\right)-\boldsymbol{l}_{1}\left(\mathbb{0}\right)=0$,
-$\Delta\boldsymbol{l}_{1}\left(P_{1}^{-\prime}\right)=\boldsymbol{l}_{1}\left(\proj{1}\right)-\boldsymbol{l}_{1}\left(\mathbb{0}\right)=0$,
-$\Delta\boldsymbol{r}_{1}\left(P_{1}^{+\prime}\right)=\boldsymbol{r}_{1}\left(\proj{0}\right)-\boldsymbol{r}_{1}\left(\mathbb{0}\right)=1$,
-$\Delta\boldsymbol{r}_{1}\left(P_{1}^{-\prime}\right)=\boldsymbol{r}_{1}\left(\proj{1}\right)-\boldsymbol{r}_{1}\left(\mathbb{0}\right)=1$.
+$P_{2}^{+\prime}=P_{2}^{-\prime}=\mathbb{0}$. Let $\left[\mul_{1}\left(E\right),\mur_{1}\left(E\right)\right]=\bar{\mu}_{1}\left(E\right)$,
+then $\Delta\mul_{1}\left(P_{1}^{+\prime}\right)=\mul_{1}\left(\proj{0}\right)-\mul_{1}\left(\mathbb{0}\right)=0$,
+$\Delta\mul_{1}\left(P_{1}^{-\prime}\right)=\mul_{1}\left(\proj{1}\right)-\mul_{1}\left(\mathbb{0}\right)=0$,
+$\Delta\mur_{1}\left(P_{1}^{+\prime}\right)=\mur_{1}\left(\proj{0}\right)-\mur_{1}\left(\mathbb{0}\right)=1$,
+$\Delta\mur_{1}\left(P_{1}^{-\prime}\right)=\mur_{1}\left(\proj{1}\right)-\mur_{1}\left(\mathbb{0}\right)=1$.
 Therefore, $\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}=\left[0,1\right]+\left(-1\right)\left[0,1\right]=\left[-1,1\right]$.

### 2017-04-23 prop_iop.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Verify the definitions...

@@
 complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
-which we abbreviate $\left[1,1\right]-\left[l,r\right]$. Given a
-sample space~$\Omega$, its set of events~$\events$, and a collection
-of intervals $\mathscr{I}$, a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+which we abbreviate $\left[1,1\right]-\left[l,r\right]$. In general,
+the scalar multiplication of an interval is defined by 
+\begin{equation} 
+x[l,r]=\cases{ 
+[xl,xr] & for $x\ge0$ ;\\
+[xr,xl] & for $x\le0$ .
+}
+\end{equation}
+Given a sample space~$\Omega$, its set of events~$\events$, and
+a collection of intervals $\mathscr{I}$, a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 is a classical interval-valued probability measure if and only if
@@
 
-\begin{definition}Consider the following.
-\begin{itemize}
-\item Let $X=\sum_{i=N^{-}}^{N^{+}}x_{i}\mathbf{1}_{E_{i}}$ be a positive
-random variable with 
-\[
-x_{N^{-}}\le x_{N^{-}+1}\le\ldots\le x_{-2}\le x_{-1}\le x_{0}=0\le x_{1}\le x_{2}\le\ldots\le x_{N^{+}-1}\le x_{N^{+}}
-\]
- and $E_{i}\cap E_{j}=\emptyset$.
-\item Let $E_{i}'=\bigcup_{j\ge i}E_{j}=\set{\omega\in\Omega}{X\left(\omega\right)\ge x_{i}}\in\events$
-for $i>0$, and $E_{i}'=\bigcup_{j\le i}E_{j}=\set{\omega\in\Omega}{X\left(\omega\right)\le x_{i}}\in\events$
-for $i<0$.
-\item $\bar{\mu}:\events\rightarrow\mathscr{I}$ a classical IVPM such that
-$l:\events\rightarrow\left[0,1\right]$ and $r:\events\rightarrow\left[0,1\right]$
-are the left-end and the right-end of $\bar{\mu}$, respectively,
-i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
-\item Multiplying a negative number switching the left and right end of
-an interval
-\begin{equation} 
-x[l,r]=\cases{ 
-[xl,xr] & for $x\ge0$ ;\\
-[xr,xl] & for $x\le0$ .
-}
-\end{equation}
-\item We also need to define the sign function as 
-\begin{equation} 
-\mathrm{sign}=\cases{ 
-1 & for $x\ge0$ ;\\
-0 & for $x=0$ ;\\
--1 & for $x\le0$ .
-}
-\end{equation}
+\begin{definition}~
+\begin{itemize}
+\item Consider a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
+\item We still decompose a random variable~$X$ into step functions, but
+we separate the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
+i.e., 
+\begin{equation}
+x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
+\end{equation}
+ and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
+are all disjoint.
+\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-f\left(E_{i+1}^{s\prime}\right)$,
+where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
 \end{itemize}
@@
 \begin{equation}
-\int X\rmd\bar{\mu}=\sum_{i=N^{-}}^{N^{+}}x_{i}\left[l\left(E_{i}'\right)-l\left(E_{i+\mathrm{sign}\left(i\right)}'\right),r\left(E_{i}'\right)-r\left(E_{i+\mathrm{sign}\left(i\right)}'\right)\right]\textrm{ .}\label{eq:interval-expectation}
+\int X\rmd\bar{\mu}=\sum_{i=1}^{N^{+}}x_{i}^{+}\left[\Delta\mul\left(E_{i}^{+\prime}\right),\Delta\mur\left(E_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}x_{i}^{-}\left[\Delta\mul\left(E_{i}^{-\prime}\right),\Delta\mur\left(E_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:interval-expectation}
 \end{equation}
 \end{definition}
+
+The following lemma shows our definition is exactly the same as in
+the literature.
+
+\begin{lemma}Follow the same notation in the definition, we also
+define $X^{+}=\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$
+and $X^{-}=\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}$. Then,
+\begin{equation}
+\int X\rmd\bar{\mu}=\int X^{+}\rmd\bar{\mu}-\int\left(-X^{-}\right)\rmd\bar{\mu}\textrm{ .}
+\end{equation}
+
+\end{lemma}
+
+\begin{proof}
+\begin{eqnarray*}
+\int X\rmd\bar{\mu} & = & \sum_{i=1}^{N^{+}}x_{i}^{+}\left[\Delta\mul\left(E_{i}^{+\prime}\right),\Delta\mur\left(E_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}x_{i}^{-}\left[\Delta\mul\left(E_{i}^{-\prime}\right),\Delta\mur\left(E_{i}^{-\prime}\right)\right]\\
+ & = & \int X^{+}\rmd\bar{\mu}+\left[\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mul\left(E_{i}^{-\prime}\right),\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mur\left(E_{i}^{-\prime}\right)\right]\\
+ & = & \int X^{+}\rmd\bar{\mu}-\left[-\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mur\left(E_{i}^{-\prime}\right),-\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mul\left(E_{i}^{-\prime}\right)\right]\\
+ & = & \int X^{+}\rmd\bar{\mu}-\left[\sum_{i=1}^{N^{-}}\left(-x_{i}^{-}\right)\Delta\mur\left(E_{i}^{-\prime}\right),\sum_{i=1}^{N^{-}}\left(-x_{i}^{-}\right)\Delta\mul\left(E_{i}^{-\prime}\right)\right]\\
+ & = & \int X^{+}\rmd\bar{\mu}-\sum_{i=1}^{N^{-}}\left(-x_{i}^{-}\right)\left[\Delta\mur\left(E_{i}^{-\prime}\right),\Delta\mul\left(E_{i}^{-\prime}\right)\right]\\
+ & = & \int X^{+}\rmd\bar{\mu}-\int\left(-X^{-}\right)\rmd\bar{\mu}\textrm{ .}
+\end{eqnarray*}
+\end{proof}
 
@@
 $X$ as well, despite the ``weight''
-\[
-\left[l\left(E_{i}'\right)-l\left(E_{i+1}'\right),r\left(E_{i}'\right)-r\left(E_{i+1}'\right)\right]\subseteq\left[l\left(E_{i}\right),r\left(E_{i}\right)\right]=\bar{\mu}\left(E_{i}\right)
-\]
+\begin{equation}
+\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\subseteq\left[\mul\left(E_{i}^{s}\right),\mur\left(E_{i}^{s}\right)\right]=\bar{\mu}\left(E_{i}^{s}\right)\textrm{ for }s\in\left\{ +,-\right\}
+\end{equation}
 is tighter than the interval-valued probability of the corresponding
@@
 so pessimistic to accumulate all possible fuzziness together, and
-expect $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}\right)$ to happen.
+expect $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}^{s}\right)$ to happen.
 
@@
 
-Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
-and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
-right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
-Given the same observable with an extra condition~
-\[
-\lambda_{N^{-}}\le\lambda_{N^{-}+1}\le\ldots\le\lambda_{-2}\le\lambda_{-1}\le\lambda_{0}=0\le\lambda_{1}\le\lambda_{2}\le\ldots\le\lambda_{N^{+}-1}\le\lambda_{N^{+}}
-\]
-and let $P_{i}'=\sum_{j\ge i}P_{j}\in\events$ for $i>0$, and $P_{i}'=\sum_{j\le i}P_{j}\in\events$
-for $i<0$, we can combine equation~(\ref{eq:interval-expectation})
-and (\ref{eq:quantum-expectation}) to define the expectation value
-of $\mathbf{O}$ with respect to $\bar{\mu}$ as
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N}\lambda_{i}\left[l\left(P_{i}'\right)-l\left(P_{i+\mathrm{sign}\left(i\right)}'\right),r\left(P_{i}'\right)-r\left(P_{i+\mathrm{sign}\left(i\right)}'\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
+Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
+This time, when we express the observable~$\mathbf{O}$ as its spectrum
+decomposition~$\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}$,
+we separate the positive and negative eigenvalues and order them from
+the smallest to the largest 
+\begin{equation}
+\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
+\end{equation}
+Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
+where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
+We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+with Eq.~(\ref{eq:quantum-expectation}) to define the expectation
+value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
 \end{equation}
@@
 the corresponding theorem.
+
+\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+and any observable~$\mathbf{O}$, if $\bar{\mu}$ is convex, then
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events\left(\mathbf{O}\right)\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events\left(\mathbf{O}\right)\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
+\end{equation}
+Conversely, if equation~(\ref{eq:quantum-interval-expectation-core})
+holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
 

### 2017-04-24 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Verify the definitions...
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

@@
 \newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
-\newcommand{\mul}{\ensuremath{\mu^{\mathrm{l}}}}
-\newcommand{\mur}{\ensuremath{\mu^{\mathrm{r}}}}
+\newcommand{\mul}{\ensuremath{\mu^{\mathrm{L}}}}
+\newcommand{\mur}{\ensuremath{\mu^{\mathrm{R}}}}
 
@@
 and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
-This time, when we express the observable~$\mathbf{O}$ as its spectrum
-decomposition~$\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}$,
-we separate the positive and negative eigenvalues and order them from
-the smallest to the largest 
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$
+for all $E\in\events$. This time, when we express the observable
+as its spectrum decomposition
+\begin{equation}
+\mathbf{O}=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}\textrm{ ,}\label{eq:spectrum-decomposition}
+\end{equation}
+we separate the positive and negative eigenvalues and order its eigenvalues
+from the smallest to the largest 
 \begin{equation}
@@
 \end{equation}
-Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta f\left(P_{i}^{s\prime}\right)=f\left(P_{i}^{s\prime}\right)-f\left(P_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $f\in\left\{ \mul,\mur\right\} $.
+Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
+where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
 We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-with Eq.~(\ref{eq:quantum-expectation}) to define the expectation
+with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
 value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
@@
 \end{eqnarray}
-Let $\events'$ denote the set containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$
-and satisfies the following conditions.
+
+Intuitively, the expectation value of an observable with respect to
+an IVPM should be the minimum and maximum expectation value of the
+same observable with respect to its consistent states. We found this
+is true when we require our IVPM to be convex, and on a commuting
+sub-event space, whose definition is given as follow.
+
+\begin{definition}$\bar{\mu}$ is called convex if for all commuting
+$P_{0},P_{1}\in\events$, $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
+where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.\end{definition}
+
+\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
+decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
+is called a sub-event space induced by $\mathbf{O}$ if it satisfies
+the following conditions.
 \begin{itemize}
+\item $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
 \item $\mathbb{0}\in\events'$. 
@@
 \end{itemize}
-And $\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
-$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
-where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
-Then, the expectation value of an observable with respect to a convex
-IVPM is just the minimum and maximum expectation value of the same
-observable with respect to its consistent states. Formally speaking,
-we have the following theorem.
+\end{definition}
+
+\noindent Having the above two definitions, we can write down our
+idea formally as follow.
 
 \begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-and any observable~$\mathbf{O}$, if $\bar{\mu}$ is convex, then
+and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
+if $\bar{\mu}$ is convex, then
 \begin{equation}

### 2017-04-24 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Keep proving the details...

@@
 probability measure, then there is a classical real-valued probability
-measure~$\mu':\Omega\rightarrow\left[0,1\right]$ such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$ such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
 for all $P\in\events'$.
@@
 probability measure, then there is a classical interval-valued probability
-measure~$\bar{\mu}':\Omega\rightarrow\mathscr{I}$ such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
+measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ such that
+$\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
 for all $P\in\events'$
@@
 and $X^{-}=\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}$. Then,
-\begin{equation}
-\int X\rmd\bar{\mu}=\int X^{+}\rmd\bar{\mu}-\int\left(-X^{-}\right)\rmd\bar{\mu}\textrm{ .}
-\end{equation}
-
-\end{lemma}
+$\int X\rmd\bar{\mu}=\int X^{+}\rmd\bar{\mu}-\int\left(-X^{-}\right)\rmd\bar{\mu}$.\end{lemma}
 
@@
 any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
-is convex if and only if 
-\begin{equation}
-\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\textrm{ .}
-\end{equation}
-\end{thm}
+is convex if and only if $\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]$.\end{thm}
 
@@
 and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
-This time, when we express the observable~$\mathbf{O}$ as its spectrum
-decomposition~$\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}$,
-we separate the positive and negative eigenvalues and order them from
-the smallest to the largest 
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
+for all $P\in\events$. This time, when we express the observable
+as its spectrum decomposition
+\begin{equation}
+\mathbf{O}=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}\textrm{ ,}\label{eq:spectrum-decomposition}
+\end{equation}
+we separate the positive and negative eigenvalues and order its eigenvalues
+from the smallest to the largest 
 \begin{equation}
@@
 We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-with Eq.~(\ref{eq:quantum-expectation}) to define the expectation
+with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
 value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
@@
 \end{equation}
-Let $\events\left(\mathbf{O}\right)$ denote the minimal sub-event
-space containing $\left\{ P_{i}\right\} _{i=1}^{N}$. Then, we have
-the corresponding theorem.
+
+Intuitively, the expectation value of an observable with respect to
+an IVPM should be the minimum and maximum expectation value of the
+same observable with respect to its consistent states. We found this
+is true when we require our IVPM to be convex, and on a commuting
+sub-event space, whose definition is given as follow.
+
+\begin{definition}A state~$\rho$ is consistent with $\bar{\mu}$
+on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.\end{definition}
+
+\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
+decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
+is called a sub-event space induced by $\mathbf{O}$ if $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
+
+\end{definition}
+
+\noindent Having these two definition, we can write down our idea
+formally as follow.
 
 \begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-and any observable~$\mathbf{O}$, if $\bar{\mu}$ is convex, then
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events\left(\mathbf{O}\right)\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events\left(\mathbf{O}\right)\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
-\end{equation}
-Conversely, if equation~(\ref{eq:quantum-interval-expectation-core})
+and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
+if $\bar{\mu}$ is convex, then
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
+\end{equation}
+Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
 holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
+
+\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
+commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
+a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
+interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
+such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
+and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
+and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
+for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
+defined by $X=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mathbf{1}_{\tau\left(P_{i}^{-}\right)}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mathbf{1}_{\tau\left(P_{i}^{+}\right)}$.
+Then, 
+\begin{eqnarray*}
+\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
+ & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right)\right]\\
+ & = & \int X\rmd\bar{\mu}'\\
+ & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu\right]
+\end{eqnarray*}
+\end{proof}
 

### 2017-04-24 prop_letter.tex
prop_iop.tex \section{Expectation Values for IVPMs} Keep proving the details...

@@
 are now intervals, it is intuitive to say a state~$\rho$ is consistent
-with $\bar{\mu}$ on a projector~$P$ if 
-\begin{equation}
-\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)\textrm{ ,}
-\end{equation}
+with $\bar{\mu}$ on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
 and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
@@
 and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$
-for all $E\in\events$. This time, when we express the observable
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
+for all $P\in\events$. This time, when we express the observable
 as its spectrum decomposition
@@
 
-\noindent Having the above two definitions, we can write down our
-idea formally as follow.
+\noindent Having these two definitions, we can write down our idea
+formally as follow.
 

### 2017-04-24 prop_iop.tex
prop_letter.tex Fix typo...

@@
 for all $P\in\events$. This time, when we express the observable
-as its spectrum decomposition
+as its spectral decomposition
 \begin{equation}
@@
 
-\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
+\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
 decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
@@
 \begin{eqnarray*}
-\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
+ &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
+ & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
  & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right)\right]\\
  & = & \int X\rmd\bar{\mu}'\\
- & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu\right]
+ & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
+ & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right)\right]\\
+ & = & \textrm{(Need to verify the detail, but seems correct...)}\\
+ & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right)\right]\\
+ & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{+}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{+}\right)\right]\\
+ & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]
 \end{eqnarray*}

### 2017-04-25 prop_letter.tex
prop_letter.tex Fix typo...

@@
 for expectation value except $X$ and $Y$ are uncorrelated or even
-independent~\cite{rohatgi2011introduction}.}
+independent~\cite{rohatgi2011introduction}.
+
+I think the real question is: Can we use the expectation value and
+Mermin square to simplify the proof that there is no $\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $?}
 

### 2017-04-26 prop_letter.tex
Revert "Updates from ShareLaTeX"
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Start type something...

--- 2017-04-24 prop_letter.tex
@@
 
+\paragraph{The Kochen-Specker Theorem}
+
+After we defined the expectation value, we will use the essential
+idea of the Kochen-Specker theorem to prove there is no quantum IVPM
+mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
+Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+it is easy to prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton
+set~$\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
+of $\mathbf{O}$. If we define the multiplication of two singleton
+sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $
+to be $\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have 
+\begin{equation}
+\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
+\end{equation}
+for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $.
+
+Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
+these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+\begin{equation}
+\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
+\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
+\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
+\end{aligned}
+\label{eq:MerminSquare}
+\end{equation}
+must be sent to $1$ or $-1$. In each row and column, operators commutes,
+and each operator is the product of the two others, except in the
+third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
+that 
+\begin{equation}
+\begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
+\langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
+\langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
+\end{aligned}
+\label{eq:MerminSquare-values}
+\end{equation}
+satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
+
+\newpage{}
+
 For example, to compute the expectation value of $\sigma_{\mathrm{z}}=\proj{0}-\proj{1}$
@@
 
-\yutsung{Even if we have expectation value of an observable, I don't
-know how to reason Mermin square~(\ref{eq:MerminSquare}) directly
-with quantum IVPM so far. The problem is the valuation function~$v$
-is not an expectation value. Since $E\left[XY\right]=E\left[X\right]E\left[Y\right]$,
-corresponding to Eq.~(\ref{eq:deterministic-product}), doesn't hold
-for expectation value except $X$ and $Y$ are uncorrelated or even
-independent~\cite{rohatgi2011introduction}.}
-
-\newpage{}
-
 Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
@@
 \paragraph{The Kochen-Specker Theorem}
-
-It asserts that there exists no function~$v$ assigning definite
-values to all observables such that for any sequence of commuting
-observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
-\begin{eqnarray}
- &  & \sum_{j}v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j}\mathbf{O}_{j}\right)\textrm{ and}\\
- &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).\label{eq:deterministic-product}
-\end{eqnarray}
-\end{subequations}Suppose that there is a function~$v$ satisfying
-these two properties, it must send an observable to its eigenvalues
-so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
-\begin{equation}
-\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
-\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
-\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
-\end{aligned}
-\label{eq:MerminSquare}
-\end{equation}
-must be sent to $1$ or $-1$. In each row and column, operators commutes,
-and each operator is the product of the two others, except in the
-third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-Therefore, it is clear impossible to find a function~$v$ such that
-\begin{equation}
-\begin{aligned}v(\mathbb{1} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\mathbb{1}) & v(\sigma_{z} & \otimes\sigma_{z})\\
-v(\sigma_{x} & \otimes\mathbb{1}) & v(\mathbb{1} & \otimes\sigma_{x}) & v(\sigma_{x} & \otimes\sigma_{x})\\
-v(\sigma_{x} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\sigma_{x}) & v(\sigma_{y} & \otimes\sigma_{y})
-\end{aligned}
-\label{eq:MerminSquare-values}
-\end{equation}
-satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
 

### 2017-04-26 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

--- 2017-04-24 prop_iop.tex
@@
 \def\C{{\mathbb{C}}}
+\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
+\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
+\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
 
@@
 \begin{eqnarray*}
-\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
+ &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
+ & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
  & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right)\right]\\
  & = & \int X\rmd\bar{\mu}'\\
- & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu\right]
+ & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
+ & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right)\right]\\
+ & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right)\right]\\
+ & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{+}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{+}\right)\right]\\
+ & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
 \end{eqnarray*}
-\end{proof}
+where 
+\begin{equation}
+\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right)\le\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right)
+\end{equation}
+because $\tau$ in theorem~\ref{thm:sub-event-space} applies to
+both real-valued and interval-valued probability measure, for any
+$\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)$, there exists
+a $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that $\mu=\mu'\circ\tau$.
+On the other hand, 
+\begin{equation}
+\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right)\ge\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right)
+\end{equation}
+because for any $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we
+have 
+\begin{eqnarray*}
+ &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
+ & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
+\end{eqnarray*}
+Let $\rho=\sum_{i=1}^{N^{-}}\frac{\mu'\left(\tau\left(P_{i}^{-}\right)\right)}{\Tr\left(P_{i}^{-}\right)}P_{i}^{-}+\sum_{i=1}^{N^{+}}\frac{\mu'\left(\tau\left(P_{i}^{+}\right)\right)}{\Tr\left(P_{i}^{+}\right)}P_{i}^{+}$.
+Then, we have 
+\begin{eqnarray*}
+\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{-}\right) & = & \sum_{i=1}^{N^{-}}\frac{\mu'\left(\tau\left(P_{i}^{-}\right)\right)}{\Tr\left(P_{i}^{-}\right)}\Tr\left(P_{i}^{-}P_{j}^{-}\right)+\sum_{i=1}^{N^{+}}\frac{\mu'\left(\tau\left(P_{i}^{+}\right)\right)}{\Tr\left(P_{i}^{+}\right)}\Tr\left(P_{i}^{+}P_{j}^{-}\right)=\mu'\left(\tau\left(P_{j}^{-}\right)\right)\\
+\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{+}\right) & = & \sum_{i=1}^{N^{-}}\frac{\mu'\left(\tau\left(P_{i}^{-}\right)\right)}{\Tr\left(P_{i}^{-}\right)}\Tr\left(P_{i}^{-}P_{j}^{+}\right)+\sum_{i=1}^{N^{+}}\frac{\mu'\left(\tau\left(P_{i}^{+}\right)\right)}{\Tr\left(P_{i}^{+}\right)}\Tr\left(P_{i}^{+}P_{j}^{+}\right)=\mu'\left(\tau\left(P_{j}^{+}\right)\right)
+\end{eqnarray*}
+Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$.\end{proof}
 

### 2017-04-27 prop_iop.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Use \sum to simplify the formula...

--- 2017-04-24 prop_iop.tex
@@
 
-\begin{definition}~
+\begin{definition}\label{def:Choquet}~
 \begin{itemize}
@@
 \begin{equation}
-\int X\rmd\bar{\mu}=\sum_{i=1}^{N^{+}}x_{i}^{+}\left[\Delta\mul\left(E_{i}^{+\prime}\right),\Delta\mur\left(E_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}x_{i}^{-}\left[\Delta\mul\left(E_{i}^{-\prime}\right),\Delta\mur\left(E_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:interval-expectation}
+\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:interval-expectation}
 \end{equation}
@@
 
-The following lemma shows our definition is exactly the same as in
-the literature.
+\noindent The following lemma shows our definition is exactly the
+same as in the literature.
 
@@
 
-Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
+\noindent Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
 can be considered as weighted average of the possible outcomes of
@@
 
-\begin{thm}\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}For
+\begin{thm}\label{thm:Rosenmuller}\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}For
 every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
@@
 for all $P\in\events$. This time, when we express the observable
-as its spectrum decomposition
-\begin{equation}
-\mathbf{O}=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}\textrm{ ,}\label{eq:spectrum-decomposition}
+as its spectral decomposition
+\begin{equation}
+\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\textrm{ ,}\label{eq:spectrum-decomposition}
 \end{equation}
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
 \end{equation}
@@
 for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
-defined by $X=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mathbf{1}_{\tau\left(P_{i}^{-}\right)}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mathbf{1}_{\tau\left(P_{i}^{+}\right)}$.
+defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$.
 Then, 
 \begin{eqnarray*}
-\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
- & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right)\right]\\
- & = & \int X\rmd\bar{\mu}'\\
- & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu\right]
+ &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
+ & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
+ & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
+ & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\\
+ & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
+ & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\right]\\
+ & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\right]\\
+ & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\right]\\
+ & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
 \end{eqnarray*}
-\end{proof}
+where 
+\begin{equation}
+\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\le\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)
+\end{equation}
+because $\tau$ in theorem~\ref{thm:sub-event-space} applies to
+both real-valued and interval-valued probability measure, for any
+$\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)$, there exists
+a $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that $\mu=\mu'\circ\tau$.
+On the other hand, 
+\begin{equation}
+\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\ge\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)
+\end{equation}
+because for any $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we
+have 
+\begin{eqnarray*}
+ &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
+ & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
+\end{eqnarray*}
+Let $\rho=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}P_{i}^{s}$.
+Then, we have 
+\begin{eqnarray*}
+\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{-}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{-}\right)=\mu'\left(\tau\left(P_{j}^{-}\right)\right)\\
+\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{+}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{+}\right)=\mu'\left(\tau\left(P_{j}^{+}\right)\right)
+\end{eqnarray*}
+Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$.\end{proof}
 

### 2017-04-27 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 
-\begin{definition}A state~$\rho$ is consistent with $\bar{\mu}$
-on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
-and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.\end{definition}
+\begin{definition}\label{def:consistent-state}A state~$\rho$ is
+consistent with $\bar{\mu}$ on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
+is consistent with $\bar{\mu}$ on every projector in $S$. Notice
+that $\rho\in\coreBorn\left(\bar{\mu},S\right)$ if and only if $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},S\right)$.\end{definition}
 
@@
 interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
-such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
-and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
-and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
+such that 
+\begin{equation}
+\bar{\mu}=\bar{\mu}'\circ\tau\textrm{ .}\label{eq:sub-event-space}
+\end{equation}
+Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$ and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$
+are the left-end and the right-end of $\bar{\mu}'$, respectively,
+i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
 for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
@@
  &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
- & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
- & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
+ & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
+ & \stackrel{\textrm{Equation }(\ref{eq:sub-event-space})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
  & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\\
  & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
- & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\right]\\
- & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\right]\\
- & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\right]\\
- & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
+ & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\right]\\
+ & \stackrel{\textrm{Claim }\ref{claim:min-max-core}}{=} & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\right]\\
+ & \stackrel{\textrm{Definition }\ref{def:consistent-state}}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\right]\\
+ & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
 \end{eqnarray*}
-where 
+where claim~\ref{claim:min-max-core} is going to be proved in the
+next paragraph.
+
+\begin{claim}\label{claim:min-max-core}
+\begin{eqnarray}
+\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right) & = & \min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\label{eq:min-core}\\
+\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right) & = & \max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\label{eq:max-core}
+\end{eqnarray}
+
+\end{claim}
+
+\begin{proof}Since equation~(\ref{eq:min-core}) and (\ref{eq:max-core})
+are essentially the same, we are only going to prove equation~(\ref{eq:min-core}).
+
+We have
 \begin{equation}
@@
 \end{equation}
-because $\tau$ in theorem~\ref{thm:sub-event-space} applies to
-both real-valued and interval-valued probability measure, for any
-$\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)$, there exists
-a $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that $\mu=\mu'\circ\tau$.
+because the same $\tau$ in theorem~\ref{thm:sub-event-space} applies
+to both real-valued and interval-valued probability measure, i.e.,
+for any $\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)$, there
+exists a $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that
+$\mu=\mu'\circ\tau$.
+
 On the other hand, 
@@
 have 
-\begin{eqnarray*}
+\begin{eqnarray}
  &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
  & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
-\end{eqnarray*}
+\end{eqnarray}
 Let $\rho=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}P_{i}^{s}$.
 Then, we have 
-\begin{eqnarray*}
+\begin{eqnarray}
 \mu_{\rho}^{\mathrm{B}}\left(P_{j}^{-}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{-}\right)=\mu'\left(\tau\left(P_{j}^{-}\right)\right)\\
 \mu_{\rho}^{\mathrm{B}}\left(P_{j}^{+}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{+}\right)=\mu'\left(\tau\left(P_{j}^{+}\right)\right)
-\end{eqnarray*}
-Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$.\end{proof}
+\end{eqnarray}
+Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$.\end{proof}\end{proof}
 

### 2017-04-28 prop_iop.tex
prop_iop.tex Update preamble...
prop_iop.tex \section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}} Updating...

@@
 \newtheorem{example}[thm]{Example}
+\theoremstyle{remark}
+\newtheorem{claim}[thm]{Claim}
 
@@
 any classically event space~$\events$,there is always a classical
-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
+interval-valued probability measure mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
 However, given a Hilbert space of dimension~$d\ge3$, there is no
-quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
+quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
 by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
@@
 
-\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
-of dimension~$d\ge3$, there is no quantum interval-valued probability
-measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.\end{cor}
-
-\begin{proof}We are going to prove by contradiction! Suppose there
-is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
-Consider $\mu:\events\rightarrow\left[0,1\right]$ defined by
+Previously we discussed how to construct a quantum IVPM from a quantum
+real-valued probability measure; we then switch our focus to how to
+construct a quantum real-valued probability measure from a special
+kind of quantum IVPM.
+
+\begin{lemma}\label{lemma:QIVPM2QCM}Let $\mathscr{I}_{\mathrm{D}}$
+be $\left\{ \imposs,\necess\right\} $. Given a quantum interval-valued
+probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+$\mu:\events\rightarrow\left[0,1\right]$ defined by 
 \begin{equation} 
@@
 0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
-1 & if $\bar{\mu}(P)=\necess$ .
+1 & if $\bar{\mu}(P)=\necess$ ,
 }\end{equation}
-We are going to verify that $\mu$ is a cryptodeterministic measure
-so that contradicts to the Kochen-Specker theorem.
+ is a cryptodeterministic measure.\end{lemma}
+
+\begin{proof}~
 \begin{itemize}
@@
 \end{proof}
+
+Together with the Kochen-Specker theorem, we will have the following
+corollary.
+
+\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
+of dimension~$d\ge3$, there is no quantum interval-valued probability
+measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.\end{cor}
 
@@
 
+Our next lemma discusses the Choquet integral on the real-valued probability
+measure reduced to the conventional expectation value.
+
+After we defined the expectation value, we can provide another proof
+of corollary~\ref{cor:Kochen-Specker-IVPM} which doesn't refer the
+Kochen-Specker theorem directly.
+
+\begin{thm}\label{cor:Kochen-Specker-expectation}Given a Hilbert
+space of dimension~$d\ge3$, there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+where $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
+as before.\end{thm}
+
+\begin{proof}Assume there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+we will prove $\bar{\mu}$ has such bizarre properties that it cannot
+exist.\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-04-28 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 \begin{lemma}\label{lemma:QIVPM2QCM}Let $\mathscr{I}_{\mathrm{D}}$
-be $\left\{ \imposs,\necess\right\} $. Given a quantum interval-valued
-probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
-$\mu:\events\rightarrow\left[0,1\right]$ defined by 
+be $\left\{ \imposs,\necess\right\} $. Given a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+then $\mu:\events\rightarrow\left[0,1\right]$ defined by 
 \begin{equation} 
@@
 0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
-1 & if $\bar{\mu}(P)=\necess$ ,
+1 & if $\bar{\mu}(P)=\necess$
 }\end{equation}
@@
 
+\begin{lemma}\label{lemma:Choquet-Lebesgue}\cite{Grabisch2016}When
+$\mul:\events\rightarrow\left[0,1\right]$ and $\mur:\events\rightarrow\left[0,1\right]$
+are real-valued probability measures, we have $\mul=\mur$ and $\int X\rmd\bar{\mu}=\left\{ \int X\rmd\mul\right\} =\left\{ \int X\rmd\mur\right\} $.\end{lemma}
+
 \yutsung{Put an example here if we need...}
@@
 
-Our next lemma discusses the Choquet integral on the real-valued probability
-measure reduced to the conventional expectation value.
+Our next lemma discusses the quantum version of lemma~\ref{lemma:Choquet-Lebesgue}.
+
+\begin{lemma}Given a Hilbert space of $d\ge3$, when $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$ are real-valued probability
+measures, we have $\mul=\mur=\mu_{\rho}^{\mathrm{B}}$ for some density
+matrix~$\rho$. Then, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.\end{lemma}
+
+\begin{proof}The first part of the lemma is the consequence of Gleason's
+theorem directly. For the second part of the lemma \end{proof}
 

### 2017-04-29 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Dividing into subsections...

@@
 
+\subsection{Expectation Values for Classical IVPMs}
+
 We may need to understand how to define expectation values of an observable
@@
 
+\subsection{Expectation Values for Quantum IVPMs}
+
 Before discussing quantum IVPMs, we first review various notations
@@
 
+\subsection{Between Expectation Values for Classical and Quantum IVPMs}
+
+Since the similarity between classical and quantum expectation values,
+we would prove some lemmas\footnote{\yutsung{functor?}} which can
+help us move the classical results to quantum.
+
+\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
+decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
+is called a sub-event space induced by $\mathbf{O}$ if it is the
+minimal sub-event space satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.\end{definition}
+
+Notice that a sub-event space induced by any observable commutes so
+that we can find a set~$\Omega$, a function~$\tau:\events'\rightarrow2^{\Omega}$
+to pull quantum real-valued or interval-valued probability measures
+to classical ones by theorem~\ref{thm:sub-event-space}. Although
+it is a powerful tool, it would be more powerful if we can pull an
+observable to a random variable as well.
+
+\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
+decomposition~(\ref{eq:spectrum-decomposition}) and its inducing
+sub-event space $\events'$, set~$\Omega$, and function~$\tau:\events'\rightarrow2^{\Omega}$.
+Then, the random variable~$X:\Omega\rightarrow\mathbb{R}$ defined
+by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$
+is called the random variable induced by $\mathbf{O}$.\end{definition}
+
+\begin{lemma}Adopting the definitions in this subsection. Given a
+density matrix~$\rho$, there is a classical real-valued probability
+measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$ such that $\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$.
+Then, we have $\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}
+
+\begin{proof}
+\begin{eqnarray*}
+\expval{\mathbf{O}}_{\rho} & \stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\\
+ & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\\
+ & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\left(\mu'\right)
+\end{eqnarray*}
+\end{proof}
+
+\begin{lemma}Adopting the definitions in this subsection. Given a
+quantum IVPM~$\bar{\mu}$, there is a classical real-valued probability
+measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ such that
+$\bar{\mu}=\bar{\mu}'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'$.\end{lemma}
+
+\begin{proof}
+\begin{eqnarray*}
+\expval{\mathbf{O}}_{\bar{\mu}} & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
+ & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
+ & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'
+\end{eqnarray*}
+\end{proof}
+
+\subsection{Between Expectation Values for Quantum Real-valued and Interval-valued
+Probability Measures}
+
 Intuitively, the expectation value of an observable with respect to
@@
 is true when we require our IVPM to be convex, and on a commuting
-sub-event space, whose definition is given as follow.
+sub-event space, whose definition is given in the next subsection.
 
@@
 
-\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
-decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
-is called a sub-event space induced by $\mathbf{O}$ if $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
-
-\end{definition}
-
 \noindent Having these two definition, we can write down our idea
@@
 i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
-for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
+for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathbb{R}$
 defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$.

### 2017-04-29 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Cleaning up proofs..

@@
 
-\subsection{Between Expectation Values for Classical and Quantum IVPMs}
+\subsection{Between Expectation Values for Classical and Quantum IVPMs\label{subsec:Between-Expectation-Values-Classical-Quantum}}
 
@@
 
-Notice that a sub-event space induced by any observable commutes so
-that we can find a set~$\Omega$, a function~$\tau:\events'\rightarrow2^{\Omega}$
-to pull quantum real-valued or interval-valued probability measures
-to classical ones by theorem~\ref{thm:sub-event-space}. Although
-it is a powerful tool, it would be more powerful if we can pull an
-observable to a random variable as well.
+Notice that a sub-event space induced by any observable commutes.
+By theorem~\ref{thm:sub-event-space}, we can find a set~$\Omega$,
+a function~$\tau:\events'\rightarrow2^{\Omega}$ to pull quantum
+real-valued or interval-valued probability measures to classical ones.
+Although it is a powerful tool, it would be more powerful if we can
+pull an observable to a random variable as well.
 
@@
 
-\begin{lemma}Adopting the definitions in this subsection. Given a
-density matrix~$\rho$, there is a classical real-valued probability
-measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$ such that $\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$.
-Then, we have $\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}
+\begin{lemma}\label{lemma:real-expectation-value-between-classical-quantum}Adopting
+the definitions in this subsection. Given a density matrix~$\rho$,
+there is a classical real-valued probability measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$
+such that $\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. Then, we have
+$\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}
 
@@
  & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\\
- & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\left(\mu'\right)
+ & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\mu'\textrm{ .}
 \end{eqnarray*}
@@
 
-\begin{lemma}Adopting the definitions in this subsection. Given a
-quantum IVPM~$\bar{\mu}$, there is a classical real-valued probability
-measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ such that
-$\bar{\mu}=\bar{\mu}'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'$.\end{lemma}
-
-\begin{proof}
+\begin{lemma}\label{lemma:interval-expectation-value-between-classical-quantum}Adopting
+the definitions in this subsection. Given a quantum IVPM~$\bar{\mu}$,
+there is a classical real-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
+such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'$.\end{lemma}
+
+\begin{proof}Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
+and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
+and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
+for all $E\in2^{\Omega}$. Then, 
 \begin{eqnarray*}
@@
  & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
- & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'
+ & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\textrm{ .}
 \end{eqnarray*}
@@
 
-\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
-commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
-a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
-interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
-such that 
-\begin{equation}
-\bar{\mu}=\bar{\mu}'\circ\tau\textrm{ .}\label{eq:sub-event-space}
-\end{equation}
-Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$ and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$
-are the left-end and the right-end of $\bar{\mu}'$, respectively,
-i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
-for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathbb{R}$
-defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$.
-Then, 
+\begin{proof}Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
+it is easy to prove
 \begin{eqnarray*}
- &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
- & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
- & \stackrel{\textrm{Equation }(\ref{eq:sub-event-space})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
- & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\\
+\expval{\mathbf{O}}_{\bar{\mu}} & \stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=} & \int X\rmd\bar{\mu}'\\
  & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
- & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\right]\\
- & \stackrel{\textrm{Claim }\ref{claim:min-max-core}}{=} & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\right]\\
- & \stackrel{\textrm{Definition }\ref{def:consistent-state}}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\right]\\
- & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
+ & \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}
 \end{eqnarray*}
-where claim~\ref{claim:min-max-core} is going to be proved in the
-next paragraph.
-
-\begin{claim}\label{claim:min-max-core}
-\begin{eqnarray}
-\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right) & = & \min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\label{eq:min-core}\\
-\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right) & = & \max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\label{eq:max-core}
-\end{eqnarray}
-
-\end{claim}
-
-\begin{proof}Since equation~(\ref{eq:min-core}) and (\ref{eq:max-core})
-are essentially the same, we are only going to prove equation~(\ref{eq:min-core}).
-
-We have
-\begin{equation}
-\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\le\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)
-\end{equation}
-because the same $\tau$ in theorem~\ref{thm:sub-event-space} applies
-to both real-valued and interval-valued probability measure, i.e.,
-for any $\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)$, there
-exists a $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that
-$\mu=\mu'\circ\tau$.
-
-On the other hand, 
-\begin{equation}
-\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\ge\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)
-\end{equation}
-because for any $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we
-have 
+Therefore, equation~(\ref{eq:quantum-interval-expectation-core})
+is equivalent to convexity if $\mathrm{core}\left(\bar{\mu}'\right)$
+and $\coreBorn\left(\bar{\mu},\events'\right)$ are one-to-one correspondence
+so that
+\begin{equation}
+\left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}
+\end{equation}
+
+Notice that lemma~\ref{lemma:real-expectation-value-between-classical-quantum}
+guarantees that for any $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
+there exists $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that
+$\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. On the other hand, for any
+$\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we have
 \begin{eqnarray}
@@
 \end{eqnarray}
-Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$.\end{proof}\end{proof}
+Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
+i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}
 

### 2017-04-29 prop_iop.tex
prop_iop.tex \subsection{Between Expectation Values for Quantum Real-valued and Interval-valued Probability Measures} Updating...
prop_iop.tex \subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability Measures} Added...

@@
 The Choquet integral has many desirable properties. For example, it
-has the same range as all expectation value in the core.
+has the same range as all expectation value in the core, and it generalizes
+the Lebesgue integral.
 
@@
 the definitions in this subsection. Given a quantum IVPM~$\bar{\mu}$,
-there is a classical real-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
+there is a classical IVPM~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
 such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'$.\end{lemma}
@@
 Let $\rho=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}P_{i}^{s}$.
-Then, we have 
+$\rho$ is a density matrix because~\cite{544199}
 \begin{eqnarray}
-\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{-}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{-}\right)=\mu'\left(\tau\left(P_{j}^{-}\right)\right)\\
-\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{+}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{+}\right)=\mu'\left(\tau\left(P_{j}^{+}\right)\right)
+\Tr\left(\rho\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}\right)=1\textrm{ .}
 \end{eqnarray}
-Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
+Also, 
+\begin{eqnarray}
+\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{s'}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{s'}\right)=\mu'\left(\tau\left(P_{j}^{s'}\right)\right)
+\end{eqnarray}
+for $s'\in\left\{ +,-\right\} $ and $1\le j\le N^{s'}$. Therefore,
+$\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
 i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}
@@
 
-\begin{lemma}Given a Hilbert space of $d\ge3$, when $\mul:\events\rightarrow\left[0,1\right]$
+\begin{lemma}\label{lemma:expectation-singleton}Given a Hilbert
+space of $d\ge3$, when $\mul:\events\rightarrow\left[0,1\right]$
 and $\mur:\events\rightarrow\left[0,1\right]$ are real-valued probability
@@
 
-\begin{proof}The first part of the lemma is the consequence of Gleason's
-theorem directly. For the second part of the lemma \end{proof}
+\begin{proof}Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
+we have
+\[
+\expval{\mathbf{O}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=}\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu'\right\} \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=}\left\{ \expval{\mathbf{O}}_{\rho}\right\} \textrm{ ,}
+\]
+where $\mu'=\mul[\prime]=\mur[\prime]$.\end{proof}
+
+\subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability
+Measures}
 
@@
 of corollary~\ref{cor:Kochen-Specker-IVPM} which doesn't refer the
-Kochen-Specker theorem directly.
+Kochen-Specker theorem directly. Assume there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+we will prove $\bar{\mu}$ has such bizarre properties that it cannot
+exist. These properties will be summarized in the following two lemmas.
+
+\begin{lemma}For any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+$\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
+where $\lambda$ is an eigenvalue of $\mathbf{O}$.\end{lemma}
+
+\begin{proof}Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum}.
+By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
+real-valued probability measures called $\mu:\events\rightarrow\left\{ 1,0\right\} $.
+By lemma~\ref{lemma:expectation-singleton}, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.
+Since $\mu$ is a probability measure, there is only one pair of $\left(s_{0},i_{0}\right)$
+such that $\mu\left(P_{i_{0}}^{s_{0}}\right)=1$. Therefore, 
+\[
+\expval{\mathbf{O}}_{\rho}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\textrm{ .}
+\]
+\end{proof}
 
@@
 
-\begin{proof}Assume there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
-we will prove $\bar{\mu}$ has such bizarre properties that it cannot
-exist.\end{proof}
+\begin{proof}\end{proof}
 

### 2017-04-29 prop_iop.tex
prop_iop.tex \subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability Measures} Updating...

@@
 By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
-real-valued probability measures called $\mu:\events\rightarrow\left\{ 1,0\right\} $.
+real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
 By lemma~\ref{lemma:expectation-singleton}, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.
-Since $\mu$ is a probability measure, there is only one pair of $\left(s_{0},i_{0}\right)$
-such that $\mu\left(P_{i_{0}}^{s_{0}}\right)=1$. Therefore, 
-\[
-\expval{\mathbf{O}}_{\rho}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\textrm{ .}
-\]
+Since $\mu$ is a cryptodeterministic measure, there is only one pair
+of $\left(s_{0},i_{0}\right)$ such that $\mu\left(P_{i_{0}}^{s_{0}}\right)=1$.
+Therefore, 
+\begin{equation}
+\expval{\mathbf{O}}_{\rho}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\textrm{ .}\label{eq:expectation-value-eigenvalue}
+\end{equation}
 \end{proof}
 
-\begin{thm}\label{cor:Kochen-Specker-expectation}Given a Hilbert
+Given two singleton sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $,
+it is intuitive to define their multiplication of to be $\left\{ \lambda_{1}\lambda_{2}\right\} $
+which gives the following lemma.
+
+\begin{lemma}For any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $,
+\begin{equation}
+\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\textrm{ .}\label{eq:Kochen-Specker-Rules}
+\end{equation}
+\end{lemma}
+
+\begin{proof}Since $\left\{ \mathbf{O}_{j}\right\} $ is a sequence
+of commuting observables, they can be diagonalized by a common orthonormal
+basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$. By lemma~\ref{lemma:QIVPM2QCM},
+$\mul$ and $\mur$ are the same cryptodeterministic measure, and
+is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
+Since $\mu$ is a cryptodeterministic measure, there is only one $j_{0}$
+such that $\mu\left(\proj{j_{0}}\right)=1$. Therefore, by the same
+reason as equation~(\ref{eq:expectation-value-eigenvalue}), the
+both sides of equation~(\ref{eq:Kochen-Specker-Rules}) are the product
+of eigenvalues corresponding to eigenstate~$\ket{j_{0}}$, and should
+be equal.\end{proof}
+
+Based on the previous lemmas, we could follow Mermin's idea to prove
+the Kochen-Specker theorem again~\cite{Mermin1990Simple,peres1995quantum}.
+
+\begin{thm}\label{thm:Kochen-Specker-expectation}Given a Hilbert
 space of dimension~$d\ge3$, there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
@@
 
-\begin{proof}\end{proof}
+\begin{proof}Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$
+satisfying the previous lemmas, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+\begin{equation}
+\begin{array}{ccc}
+\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
+\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
+\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
+\end{array}\label{eq:MerminSquare}
+\end{equation}
+must be sent to $1$ or $-1$. In each row and column, operators commutes,
+and each operator is the product of the two others, except in the
+third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
+that 
+\begin{equation}
+\begin{array}{ccc}
+\expval{\mathbb{1}\otimes\sigma_{z}}_{\bar{\mu}} & \expval{\sigma_{z}\otimes\mathbb{1}}_{\bar{\mu}} & \expval{\sigma_{z}\otimes\sigma_{z}}_{\bar{\mu}}\\
+\expval{\sigma_{x}\otimes\mathbb{1}}_{\bar{\mu}} & \expval{\mathbb{1}\otimes\sigma_{x}}_{\bar{\mu}} & \expval{\sigma_{x}\otimes\sigma_{x}}_{\bar{\mu}}\\
+\expval{\sigma_{x}\otimes\sigma_{z}}_{\bar{\mu}} & \expval{\sigma_{z}\otimes\sigma_{x}}_{\bar{\mu}} & \expval{\sigma_{y}\otimes\sigma_{y}}_{\bar{\mu}}
+\end{array}\label{eq:MerminSquare-values}
+\end{equation}
+satisfying equation~(\ref{eq:Kochen-Specker-Rules}).\end{proof}
 

### 2017-04-30 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Use \sum to simplify the formula...
prop_iop.tex \section{Expectation Values for IVPMs} Updating...
prop_letter.tex Delete old Kochen-Specker theorem section...

@@
 and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
+is consistent with $\bar{\mu}$ on every projector in $S$.
 
@@
 \begin{equation}
-\mathbf{O}=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}\textrm{ ,}\label{eq:spectrum-decomposition}
+\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\textrm{ ,}\label{eq:spectrum-decomposition}
 \end{equation}
@@
 \begin{eqnarray}
-\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]\nonumber \\
- &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
+\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
 \end{eqnarray}
@@
 know nothing about a coin before she toss it.
-
-\paragraph{The Kochen-Specker Theorem}
-
-\begin{table*}
-\caption{\label{table:commonBasis}In each row, three observables are listed
-in the left column commutes, and their common eigenbasis is listed
-in the right column. In order to unify and simplify the notation,
-we do not normalize eigenstates, and represent the state~$\alpha_{00}\ket{00}+\alpha_{01}\ket{01}+\alpha_{10}\ket{10}+\alpha_{11}\ket{11}$
-as $\left(\alpha_{00},\alpha_{01},\alpha_{10},\alpha_{11}\right)$.
-Also, to simplify the notation further, the projector onto each eigenstate
-used in Eq.~(\ref{eq:CEGA}) is named such that if two projectors
-share the same index, they are commuting.}
-
-\begin{ruledtabular}
-\begin{tabular}{c|c}
-Commuting observables & Common eigenbasis\tabularnewline
-\hline 
-$\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
-\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
-\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}\\
-\mathbb{1} & \otimes\sigma_{z} & \sigma_{x} & \otimes\mathbb{1} & \sigma_{x} & \otimes\sigma_{z}\\
-\sigma_{z} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{z} & \otimes\sigma_{x}\\
-\sigma_{z} & \otimes\sigma_{z} & \sigma_{x} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
-\end{aligned}
-$ & $\begin{aligned}(1,0,0,0) & \rightarrow P_{12} & (0,1,0,0) & \rightarrow P_{18} & (0,0,1,0) &  & (0,0,0,1) & \rightarrow P_{28}\\
-(1,1,1,1) & \rightarrow P_{56} & (1,-1,1,-1) & \rightarrow P_{59} & (1,1,-1,-1) & \rightarrow P_{69} & (1,-1,-1,1)\\
-(1,1,1,-1) & \rightarrow P_{37} & (1,1,-1,1) & \rightarrow P_{47} & (1,-1,1,1) &  & (-1,1,1,1) & \rightarrow P_{34}\\
-(1,0,1,0) & \rightarrow P_{48} & (0,1,0,1) &  & (1,0,-1,0) & \rightarrow P_{58} & (0,1,0,-1) & \rightarrow P_{45}\\
-(1,1,0,0) &  & (1,-1,0,0) & \rightarrow P_{67} & (0,0,1,1) & \rightarrow P_{17} & (0,0,1,-1) & \rightarrow P_{16}\\
-(0,1,1,0) & \rightarrow P_{29} & (0,1,-1,0) & \rightarrow P_{23} & (1,0,0,1) & \rightarrow P_{39} & (1,0,0,-1)
-\end{aligned}
-$\tabularnewline
-\end{tabular}
-\end{ruledtabular}
-
-\end{table*}
-
-Since observables in Eq.~(\ref{eq:MerminSquare}) are not projections,
-if we want to reformulate the above argument in the language of IVPMs,
-we first need to find the common eigenbasis of each row and column,
-and consider the projections to each eigenvectors~\cite{peres1995quantum,CabelloEstebaranzGarcia-Alcaine1996,Cabello_2008}.
-Let $\mathcal{T}_{18}$ denote the named projectors onto eigenstates
-listed in Table~\ref{table:commonBasis}, and the eigenstates they
-project to are denoted by $\events_{18}$. The Kochen-Specker theorem
-could then be proved by showing there is no function~$v:\events_{18}\rightarrow\left\{ 0,1\right\} $
-satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}), where
-\begin{equation}
-\events_{18}=\set{\sum_{i=1}^{N}P_{i}}{\textrm{orthogonal }\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{18}}
-\end{equation}
-is a sub-event space.
-
-Assume there is a function~$v:\events_{18}\rightarrow\left\{ 0,1\right\} $
-satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}). There must be a
-quantum IVPM~$\bar{\mu}:\events_{18}\rightarrow\mathscr{I}_{\mathrm{D}}$
-defined by $\bar{\mu}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
-where 
-\begin{equation}
-\iota_{\mathrm{D}}\left(x\right)=\begin{cases}
-\necess & \text{, if }x=1\text{ ;}\\
-\imposs & \text{, if }x=0\text{ .}
-\end{cases}\label{eq:homomorphism-0}
-\end{equation}
-For each the orthogonal basis in $\events_{18}$, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-gives the following equations: 
-\begin{equation}
-\begin{aligned}\necess & \subseteq\bar{\mu}\left(P_{12}\right)+\bar{\mu}\left(P_{18}\right)+\bar{\mu}\left(P_{17}\right)+\bar{\mu}\left(P_{16}\right)\textrm{ ,}\\
-\necess & \subseteq\bar{\mu}\left(P_{16}\right)+\bar{\mu}\left(P_{67}\right)+\bar{\mu}\left(P_{69}\right)+\bar{\mu}\left(P_{56}\right)\textrm{ ,}\\
-\necess & \subseteq\bar{\mu}\left(P_{56}\right)+\bar{\mu}\left(P_{59}\right)+\bar{\mu}\left(P_{58}\right)+\bar{\mu}\left(P_{45}\right)\textrm{ ,}\\
-\necess & \subseteq\bar{\mu}\left(P_{45}\right)+\bar{\mu}\left(P_{48}\right)+\bar{\mu}\left(P_{47}\right)+\bar{\mu}\left(P_{34}\right)\textrm{ ,}\\
-\necess & \subseteq\bar{\mu}\left(P_{34}\right)+\bar{\mu}\left(P_{37}\right)+\bar{\mu}\left(P_{39}\right)+\bar{\mu}\left(P_{23}\right)\textrm{ ,}\\
-\necess & \subseteq\bar{\mu}\left(P_{23}\right)+\bar{\mu}\left(P_{29}\right)+\bar{\mu}\left(P_{28}\right)+\bar{\mu}\left(P_{12}\right)\textrm{ ,}\\
-\necess & \subseteq\bar{\mu}\left(P_{28}\right)+\bar{\mu}\left(P_{18}\right)+\bar{\mu}\left(P_{58}\right)+\bar{\mu}\left(P_{48}\right)\textrm{ ,}\\
-\necess & \subseteq\bar{\mu}\left(P_{47}\right)+\bar{\mu}\left(P_{37}\right)+\bar{\mu}\left(P_{17}\right)+\bar{\mu}\left(P_{67}\right)\textrm{ ,}\\
-\necess & \subseteq\bar{\mu}\left(P_{69}\right)+\bar{\mu}\left(P_{59}\right)+\bar{\mu}\left(P_{39}\right)+\bar{\mu}\left(P_{29}\right)\textrm{ .}
-\end{aligned}
-\label{eq:CEGA}
-\end{equation}
-If we sum up the preceding equations, we will have
-\begin{equation}
-\left[9,9\right]\subseteq2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{\mu}\left(\ket{\psi}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Total}
-\end{equation}
-However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
-can never be satisfied. Because each term in right-hand side is either
-$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the right-hand
-side is a singleton set of an even integer while the left-hand side
-is $\left[9,9\right]$. Therefore, there is no quantum IVPM~$\bar{\mu}:\events_{18}\rightarrow\mathscr{I}_{\mathrm{D}}$.
-Moreover, there is no quantum IVPM defined on the set of all projectors
-as well; otherwise, if we have a quantum IVPM~$\bar{\mu}':\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
-then we can restrict $\bar{\mu}'$ and define $\bar{\mu}=\left.\bar{\mu}'\right|_{\events_{18}}$.
 

### 2017-04-30 prop_letter.tex
prop_letter.tex \paragraph{Contextuality Inequality} Type something...

@@
 
-Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
-and we want to adopt these inequalities into our setting.
-
-First, although his inequality (4) bases on Mermin square and looks
-simple, we cannot use it directly because they are not projectors.
-Instead $A_{ij}$ in his equation (1) are almost projectors, because
-$A_{ij}=2\proj{v_{ij}}-\mathbb{1}$, and $\ket{v_{ij}}$ are eigenstates
-of Mermin square. It is easier to write an inequality start from equation
-(1).
+Although Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
+it seems not directly relating to empty/non-empty core. On one hand,
+the part using hidden variables cannot really apply on quantum IVPM
+expect $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
+case discussed in the Kochen-Specker theorem paragraph. On the other
+hand, for the part predicted by quantum mechanics, the product of
+observables in inequalities are always either $\mathbb{1}$ or $-\mathbb{1}$
+whose the interval-valued probabilities and expectation values are
+always $\necess$. In these kind of situation, the inequalities applies
+on all IVPMs, no matter whether it has an empty or non-empty core.
 

### 2017-04-30 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Adding new example, and delete the old one...

@@
 
-Intuitively, the expectation value of an observable with respect to
-an IVPM should be the minimum and maximum expectation value of the
-same observable with respect to its consistent states. We found this
-is true when we require our IVPM to be convex, and on a commuting
+\begin{table*}
+\caption{\label{table:quantum-interval-expectation}This table highlight the
+process to compute $\expval{\mathbf{O}}_{\bar{\mu}_{1}}$. Notice
+that $\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$
+and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$. }
+
+\begin{ruledtabular}
+\begin{tabular}{c|ccccccccc}
+$i$ & $\lambda_{i}^{+}$ & $P_{i}^{+}$ & $\bar{\mu}_{1}\left(P_{i}^{+}\right)$ & $P_{i}^{+\prime}$ & $\bar{\mu}_{1}\left(P_{i}^{+\prime}\right)$ & $\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\mur_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mur_{1}\left(P_{i}^{+\prime}\right)$\tabularnewline
+\hline 
+$1$ & $1$ & $\proj{0}+\proj{2}$ & $\unknown$ & $\mathbb{1}$ & $\necess$ & $1$ & $1$ & $1$ & $0$\tabularnewline
+$2$ & $2$ & $\proj{1}$ & $\unknown$ & $\proj{1}$ & $\unknown$ & $0$ & $1$ & $0$ & $1$\tabularnewline
+\end{tabular}
+\end{ruledtabular}
+
+\end{table*}
+Since Eq.~(\ref{eq:quantum-interval-expectation}) is more complex
+than Eq.~(\ref{eq:quantum-expectation}), it is instructive to check
+an example. Given a three dimensional Hilbert space with an orthonormal
+basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
+and $\mathbf{O}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
+By following Table~\ref{table:quantum-interval-expectation}, we
+have 
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
+\end{equation}
+$\left[1,2\right]$ is an intuitively result. Since two possible outcomes
+are $1$ and $2$, the expectation value is between one of them even
+if we no prior knowledge about the likelihood of outcomes. In contrast,
+if we naively multiply eigenvalues with intervals, their sum is $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$
+which is a worse estimation. Because even if we no prior knowledge,
+we know one of them will happen, and estimating the lower-bound by$1\cdot0+2\cdot0=0$
+is too pessimistic.
+
+Formally, the expectation value of an observable with respect to an
+IVPM should intuitively be the minimum and maximum expectation value
+of the same observable with respect to its consistent states. We found
+this is true when we require our IVPM to be convex, and on a commuting
 sub-event space, whose definition is given as follow.
@@
 \newpage{}
-
-For example, to compute the expectation value of $\sigma_{\mathrm{z}}=\proj{0}-\proj{1}$
-with respect to $\bar{\mu}_{1}$, we have $N^{+}=N^{-}=1$, $\lambda_{1}^{+}=1$,
-$\lambda_{1}^{-}=-1$, $P_{1}^{+\prime}=\proj{0}$, $P_{1}^{-\prime}=\proj{1}$,
-$P_{2}^{+\prime}=P_{2}^{-\prime}=\mathbb{0}$. Let $\left[\mul_{1}\left(E\right),\mur_{1}\left(E\right)\right]=\bar{\mu}_{1}\left(E\right)$,
-then $\Delta\mul_{1}\left(P_{1}^{+\prime}\right)=\mul_{1}\left(\proj{0}\right)-\mul_{1}\left(\mathbb{0}\right)=0$,
-$\Delta\mul_{1}\left(P_{1}^{-\prime}\right)=\mul_{1}\left(\proj{1}\right)-\mul_{1}\left(\mathbb{0}\right)=0$,
-$\Delta\mur_{1}\left(P_{1}^{+\prime}\right)=\mur_{1}\left(\proj{0}\right)-\mur_{1}\left(\mathbb{0}\right)=1$,
-$\Delta\mur_{1}\left(P_{1}^{-\prime}\right)=\mur_{1}\left(\proj{1}\right)-\mur_{1}\left(\mathbb{0}\right)=1$.
-Therefore, $\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}=\left[0,1\right]+\left(-1\right)\left[0,1\right]=\left[-1,1\right]$.
-
-On the other hand, it is easy to verify that $\bar{\mu}_{1}$ is convex.
-Every state is consistent with $\bar{\mu}_{1}$, in particular $\proj{0}$
-and $\proj{1}$. It is easy to see\begin{subequations}
-\begin{eqnarray}
-\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{1}}=-1\textrm{ ,}\\
-\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{0}}=1\textrm{ ,}
-\end{eqnarray}
-\end{subequations}which is consistent with the theorem.
-
-In contrast to the usual identity~$\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\rho}=\expval{\mathbf{O}_{1}}_{\rho}+\expval{\mathbf{O}_{2}}_{\rho}$,
-we have
-\begin{equation}
-\expval{\mathbb{0}}_{\bar{\mu}_{1}}=\left[0,0\right]\subsetneq\left[-2,2\right]=\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}+\expval{-\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}
-\end{equation}
-because the precision is easily be lost when applying arithmetic operations.
-In general, when $\bar{\mu}$ is convex, we have 
-\begin{equation}
-\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\bar{\mu}}\subseteq\expval{\mathbf{O}_{1}}_{\bar{\mu}}+\expval{\mathbf{O}_{2}}_{\bar{\mu}}\textrm{ ,}
-\end{equation}
-for commuting $\mathbf{O}_{1}$ and $\mathbf{O}_{2}$.
 

### 2017-04-30 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

@@
 \unknown & \text{, otherwise,}
-\end{cases}\label{eq:homomorphism-1}
+\end{cases}\label{eq:no-information-IVPM}
 \end{equation}
@@
 the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
-for all $P\in\events$. This time, when we express the observable
-as its spectral decomposition
+for all $P\in\events$. This time, when we express an observable as
+its spectral decomposition
 \begin{equation}
@@
 \begin{table*}
-\caption{\label{table:quantum-interval-expectation}This table highlight the
-process to compute $\expval{\mathbf{O}}_{\bar{\mu}_{1}}$. Notice
-that $\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$
+\caption{\label{table:quantum-interval-expectation}This table highlights the
+process to compute $\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}$. Notice
+that $\bar{\mu}_{1}$ is defined by Eq.~(\ref{eq:no-information-IVPM}),
+$\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$,
 and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$. }
@@
 \end{table*}
-Since Eq.~(\ref{eq:quantum-interval-expectation}) is more complex
-than Eq.~(\ref{eq:quantum-expectation}), it is instructive to check
-an example. Given a three dimensional Hilbert space with an orthonormal
+For example, given a three dimensional Hilbert space with an orthonormal
 basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
-and $\mathbf{O}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
+and $\mathbf{O}_{1}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
 By following Table~\ref{table:quantum-interval-expectation}, we
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
+\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
 \end{equation}

### 2017-05-01 prop_letter.tex
prop_letter.tex Small things here and there...

@@
 \begin{equation}
-\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
+\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]
 \end{equation}
-$\left[1,2\right]$ is an intuitively result. Since two possible outcomes
-are $1$ and $2$, the expectation value is between one of them even
-if we no prior knowledge about the likelihood of outcomes. In contrast,
-if we naively multiply eigenvalues with intervals, their sum is $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$
-which is a worse estimation. Because even if we no prior knowledge,
-we know one of them will happen, and estimating the lower-bound by$1\cdot0+2\cdot0=0$
-is too pessimistic.
+intuitively. Since two possible outcomes are $1$ and $2$, the expectation
+value should be between them even if we no prior knowledge about the
+likelihood of outcomes. In contrast, if we naively multiply eigenvalues
+with intervals, their sum, $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$,
+is a worse estimation. In fact, estimating the lower-bound by $1\cdot0+2\cdot0=0$
+is too pessimistic because we know one of outcomes must be happen
+even without any prior knowledge.
 
 Formally, the expectation value of an observable with respect to an
-IVPM should intuitively be the minimum and maximum expectation value
-of the same observable with respect to its consistent states. We found
-this is true when we require our IVPM to be convex, and on a commuting
+IVPM should be the minimum and maximum expectation value of the same
+observable with respect to states consistent with it. We found this
+is true when we require our IVPM to be convex, and on a commuting
 sub-event space, whose definition is given as follow.
@@
 decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
-is called a sub-event space induced by $\mathbf{O}$ if it satisfies
-the following conditions.
+is called a sub-event space induced by $\mathbf{O}$ if it is the
+minimal set satisfying the following conditions.
 \begin{itemize}
-\item $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
-\item $\mathbb{0}\in\events'$. 
-\item $\mathbb{1}\in\events'$. 
+\item $\left\{ \mathbb{0},\mathbb{1}\right\} \cup\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
 \item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
@@
 mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
-Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
-it is easy to prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton
-set~$\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
-of $\mathbf{O}$. If we define the multiplication of two singleton
-sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $
-to be $\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have 
+Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
+We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
+where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
+multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
+and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
+then we have 
 \begin{equation}
@@
 \end{equation}
-must be sent to $1$ or $-1$. In each row and column, operators commutes,
-and each operator is the product of the two others, except in the
-third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+must have the the expectation value~$1$ or $-1$. In each row and
+column, operators commutes, and each operator is the product of the
+two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
 Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such

### 2017-05-01 prop_letter.tex
prop_letter.tex \paragraph{Quantum and Classical IVPMs} Added...

@@
 
-\newpage{}
+\paragraph{Quantum and Classical IVPMs}
 
 Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
-when the space of events includes only mutually commuting sub-events,
-where any subset of $\events$ is called a sub-event space if it satisfies
-the follow conditions.
-
-For example, $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
+when the space of events includes only mutually commuting sub-events.
+For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
 is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
@@
 \end{equation}
-If we identify $\proj{0}$ and $\proj{1}$ as the head and the tail
-of a coin, respectively, then $\bar{\mu}_{2}$ represents experimenter
-know nothing about a coin before she toss it.
+If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
+the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
+represents experimenter know nothing about a coin before she tosses
+it, and two classical states~$\proj{0}$ and $\proj{1}$ are both
+consistent with $\bar{\mu}_{2}$ on $\events_{0}$.
 
-\paragraph{Quantum IVPM and States}
+In general, although measurements done with limited resources and
+poor precision may not uniquely identify the true state of a classical
+system, there is always at least one system that is consistent with
+the measurements.
 
-Formally, we can ask: what can we deduce about the state of a quantum
-system given a quantum interval-valued probability measure, i.e.,
-given observations done with finite resources. In the case that the
-intervals are infinitely precise for $d\ge3$, the question reduces
-to Gleason's theorem which states that the state of the quantum system
-is uniquely determined by the probability measure. But surely the
-less resources are available, the less precise the intervals, and
-the less we expect to know about the state of the system.
+\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}\label{thm:Shapley}]
+For every convex IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
+if $\events'$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
+\end{thm}
 
-To understand the relation between IVPMs and states, it is instructive
-to consider the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
-defined as follow:
-\begin{equation}
-\mu_{0}(P)=\begin{cases}
-\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
-\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis.}
-\end{cases}
-\end{equation}
-$\mu_{0}$ is not induced by the Born rule as a whole, but is consistent
-with the Born rule on $\events_{0}$ and some other proper sub-event
-spaces. The similar phenomena happens for IVPMs as well. Formally,
-given a quantum IVPM~$\bar{\mu}$, the \emph{core} relative to a
-sub-event space~$\events'\subseteq\events$ is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
-While this change might make it easier to explain the core of quantum
-IVPMs, should we explain the meaning of the Born rule for classical
-probability measures? Check this definition in the classical setting,
-like commuting observables or product states... etc.}}
-\begin{equation}
-\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
-\end{equation}
-The core of an interval-valued probability measure is the set of states
-it approximates. For example, $\coreBorn\left(\bar{\mu}_{1},\events'\right)$
-contains every density matrix. The 2-dimensional measure~$\mu_{0}$
-can be understood by core as well. Consider the IVPM~$\bar{\mu}_{0}=\iota_{\infty}\circ\mu_{0}$
-whose cores are\begin{subequations}
-\begin{eqnarray}
-\coreBorn\left(\bar{\mu}_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
-\coreBorn\left(\bar{\mu}_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
-\coreBorn\left(\bar{\mu}_{0},\events\right) & = & \emptyset\textrm{ ,}
-\end{eqnarray}
-\end{subequations}where $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
-That is, $\bar{\mu}_{0}$ approximates $\proj{\ps}$ if we are only
-allowed to use $\events_{0}$ during the measurement, and approximates
-$\proj{0}$ if $\events_{1}$ are the only allowed ones. Since $\bar{\mu}_{0}$
-approximates different states on different sub-event space, it intuitively
-approximates nothing if every projector is allowed.
-
-Notice that $\bar{\mu}_{0}$ has a non-empty core relative to $\events_{0}$
-and $\events_{1}$ which are all commutative. In general, a commutative
-sub-event space reduces quantum IVPMs to classical IVPMs. If a classical
-IVPM satisfies a coherence condition, convexity, it must approximate
-at least one infinitely-precise measure.
-
-\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
-every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
-if the following conditions are true.
-\begin{itemize}
-\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
-\item $\bar{\mu}$ is convex, i.e., for all commuting $P_{0},P_{1}\in\events$,
-$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
-where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
-\end{itemize}
-Then, $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
-
-In informal terms, this result states that although measurements done
-with limited resources and poor precision may not uniquely identify
-the true state of the system, there is always at least one system
-that is consistent with the measurements. However, similar to 2-dimensional
-$\iota_{\infty}\circ\mu_{0}$, even if a quantum IVPM approximates
-some states for each classical sub-event space, it may not approximate
-any particular state while considering for all projectors~$\events$.\footnote{\yutsung{It seems that our example in 4 dimensions together with
-relativity core would be unnecessary complex. Therefore, I roll our
-example back to 3 dimensions.}}
+However, even if a quantum IVPM approximates some states for each
+classical sub-event space, it may not approximate any particular state
+while considering all projectors~$\events$.
 
 \begin{example}[Three-dimensional quantum three-interval-valued probability
-measure]\label{ex:three-dimensional-three-value} Given a three dimensional
-Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
+measure\label{ex:three-dimensional-three-value}]
+Given a three dimensional Hilbert space with an orthonormal basis
+$\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
 $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
-and\begin{subequations}
+and
+\begin{subequations}
 \begin{eqnarray}
@@
 \end{eqnarray}
-\end{subequations}It is straightforward to verify that $\bar{\mu}$
-is a quantum interval-valued probability measure.
+\end{subequations}
+It is straightforward to verify that $\bar{\mu}$ is a quantum IVPM.
 
@@
 \end{equation}
-and must be empty.\end{example}
+and must be empty.
+\end{example}
 
@@
 by consuming more and more measurement resource, it would be more
-and more likely that there is an empty core relative to all projectors~$\events$.
+and more likely that a quantum IVPM has a state consistent with it
+on all projectors~$\events$.
 
-\newpage{}
-
-\paragraph{Contextuality Inequality}
-
-Although Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
+\yutsung{Although Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
 it seems not directly relating to empty/non-empty core. On one hand,
@@
 expect $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-case discussed in the Kochen-Specker theorem paragraph. On the other
-hand, for the part predicted by quantum mechanics, the product of
-observables in inequalities are always either $\mathbb{1}$ or $-\mathbb{1}$
-whose the interval-valued probabilities and expectation values are
-always $\necess$. In these kind of situation, the inequalities applies
-on all IVPMs, no matter whether it has an empty or non-empty core.
+case. On the other hand, for the part predicted by quantum mechanics,
+the product of observables in inequalities are always either $\mathbb{1}$
+or $-\mathbb{1}$ whose the interval-valued probabilities and expectation
+values are always $\necess$. In this kind of situation, the inequalities
+applies on all IVPMs, no matter whether it has an empty or non-empty
+core.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibliography{prop}

### 2017-05-01 prop_letter.tex
prop_letter.tex Small things here and there...

@@
 
-Furthermore, if we express the observable~$\mathbf{O}$ as its spectrum
+Furthermore, if we express an observable~$\mathbf{O}$ as its spectrum
 decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
@@
 Formally, we can ask: what can we deduce about the state of a quantum
-system given a quantum interval-valued probability measure, i.e.,
-given observations done with finite resources. Since the probabilities
-are now intervals, it is intuitive to say a state~$\rho$ is consistent
-with $\bar{\mu}$ on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+system given a quantum IVPM, i.e., given observations done with finite
+resources. Since the probabilities are now intervals, it is intuitive
+to say a state~$\rho$ is consistent with $\bar{\mu}$ on a projector~$P$
+if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
 and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
@@
 any quantum probability measure can be recast as an interval-valued
-one. For $d\ge3$, the question reduces to Gleason's theorem which
+one. When $d\ge3$, the question reduces to Gleason's theorem which
 states that for any quantum IVPM~$\bar{\mu}$, there is an unique
@@
 While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
-IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-is another one, and corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
+IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
+is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
 However, before diving into the Kochen-Specker theorem, it is better
-to understand how to define expectation value of an observable with
-quantum IVPMs.
+to understand how to define the expectation value of an observable
+with quantum IVPMs.
 

### 2017-05-01 prop_letter.tex
prop_letter.tex \section{Theory} Added...

@@
 
+\section{Theory}
+
 \paragraph{Gleason's Theorem}
@@
 
-In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-any quantum probability measure can be recast as an interval-valued
-one. When $d\ge3$, the question reduces to Gleason's theorem which
-states that for any quantum IVPM~$\bar{\mu}$, there is an unique
-state consistent with $\bar{\mu}$ on every projector.
+\paragraph{Quantum and Classical IVPMs}
 
-While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
-IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
-However, before diving into the Kochen-Specker theorem, it is better
-to understand how to define the expectation value of an observable
-with quantum IVPMs.
+Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
+when the space of events includes only mutually commuting sub-events,
+where $\events'\subseteq\events$ is called a sub-event space if it
+satisfies the following conditions.
+\begin{itemize}
+\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
+\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
+\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
+we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
+\end{itemize}
+For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
+is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
+$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
+\begin{equation}
+\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
+\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
+\end{aligned}
+\end{equation}
+If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
+the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
+represents experimenter know nothing about a coin before she tosses
+it, and two classical states~$\proj{0}$ and $\proj{1}$ are both
+consistent with $\bar{\mu}_{2}$ on $\events_{0}$.
+
+In general, although measurements done with limited resources and
+poor precision may not uniquely identify the true state of a classical
+system, when the system satisfies an extra-condition called convex,
+there is always at least one system that is consistent with the measurements.
+
+\begin{definition}
+$\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
+$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
+where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
+\end{definition}
+
+\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}\label{thm:Shapley}]
+For every convex IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
+if $\events'$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
+\end{thm}
 
@@
 is true when we require our IVPM to be convex, and on a commuting
-sub-event space, whose definition is given as follow.
+sub-event space induced by an observable.
 
-\begin{definition}$\bar{\mu}$ is called convex if for all commuting
-$P_{0},P_{1}\in\events$, $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
-where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.\end{definition}
-
-\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
-decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
-is called a sub-event space induced by $\mathbf{O}$ if it is the
-minimal set satisfying the following conditions.
-\begin{itemize}
-\item $\left\{ \mathbb{0},\mathbb{1}\right\} \cup\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
-\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
-\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
-we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
-\end{itemize}
+\begin{definition}
+Given an observable~$\mathbf{O}$ with its spectrum decomposition~(\ref{eq:spectrum-decomposition}).
+A set of projectors~$\events'\subseteq\events$ is called a sub-event
+space induced by $\mathbf{O}$ if it is the minimal sub-event space
+satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
 \end{definition}
 
-\noindent Having these two definitions, we can write down our idea
-formally as follow.
+\noindent Having this definitions, we can write down our idea formally
+as follow.
 
-\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+\begin{thm}
+Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
@@
 Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
-holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
+holds for every observable, then $\bar{\mu}$ is convex.
+\end{thm}
+
+\newpage{}
+
+In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+any quantum probability measure can be recast as an interval-valued
+one. When $d\ge3$, the question reduces to Gleason's theorem which
+states that for any quantum IVPM~$\bar{\mu}$, there is an unique
+state consistent with $\bar{\mu}$ on every projector.
+
+While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
+IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
+is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
+However, before diving into the Kochen-Specker theorem, it is better
+to understand how to define the expectation value of an observable
+with quantum IVPMs.
 
@@
 satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
-
-\paragraph{Quantum and Classical IVPMs}
-
-Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
-when the space of events includes only mutually commuting sub-events.
-For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
-is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
-$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
-\begin{equation}
-\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
-\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
-\end{aligned}
-\end{equation}
-If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
-the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
-represents experimenter know nothing about a coin before she tosses
-it, and two classical states~$\proj{0}$ and $\proj{1}$ are both
-consistent with $\bar{\mu}_{2}$ on $\events_{0}$.
-
-In general, although measurements done with limited resources and
-poor precision may not uniquely identify the true state of a classical
-system, there is always at least one system that is consistent with
-the measurements.
-
-\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}\label{thm:Shapley}]
-For every convex IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
-if $\events'$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
-\end{thm}
 

### 2017-05-03 prop_letter.tex
prop_letter.tex \setcounter{secnumdepth}{3} Added...
prop_letter.tex \paragraph{Quantum and Classical IVPMs} Updating...

@@
 \newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
-\newcommand{\mul}{\ensuremath{\mu^{\mathrm{L}}}}
-\newcommand{\mur}{\ensuremath{\mu^{\mathrm{R}}}}
+\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
+\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
+\setcounter{secnumdepth}{3}
 
@@
 
-Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
-when the space of events includes only mutually commuting sub-events,
-where $\events'\subseteq\events$ is called a sub-event space if it
-satisfies the following conditions.
+Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} when
+the space of events includes only mutually commuting sub-events, where
+$\events'\subseteq\events$ is called a sub-event space if it satisfies
+the following conditions.
 \begin{itemize}

### 2017-05-03 prop_iop.tex
prop_letter.tex Small things here and there...
prop_iop.tex \subsection{Describe Classical World by Quantum Probability Measures with a Commuting Sub-event Space} Adding...

@@
 
+\subsection{Classical and Quantum Probability Measures}
+
 Before diving into the lemmas and proofs, we start from two definitions.
@@
 and a mutually commuting sub-event space~$\events'\subseteq\events$,
-there is set~$\Omega$ and a function~$\tau:\events'\rightarrow2^{\Omega}$
+there is a set~$\Omega$ and a function~$\tau:\events'\rightarrow2^{\Omega}$
 such that:
@@
 theory in this setting.
+
+\subsection{Describe Classical World by Quantum Probability Measures with a Commuting
+Sub-event Space}
+
+Since there is a correspondence between classical probability measures
+and quantum ones on a commuting sub-event space, we can use the quantum
+language to describe the classical world given a commuting sub-event
+space.
+
+\subsection{Application on Convexity}
 

### 2017-05-03 prop_iop.tex
prop_iop.tex \subsection{Describe Classical World by Quantum Probability Measures with a Commuting Sub-event Space} Updating...

@@
 \begin{proof}Again, it is sufficient to prove the interval-valued
-case. Since $\events'$ is a set of mutually orthogonal projections,
+case. Since $\events'$ is a set of mutually commuting projections,
 they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
@@
 and quantum ones on a commuting sub-event space, we can use the quantum
-language to describe the classical world given a commuting sub-event
-space.
+language to describe the classical world given an orthonormal basis.
+
+\begin{definition}Given a Hilbert space~$\Hilb$, an orthonormal
+basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$, a classical
+real-valued probability measures~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$
+on the sample space~$\Omega$. The density matrix~$\sum_{j=0}^{d-1}\pmeas\left(\left\{ j\right\} \right)\proj{j}$
+is call classical with respect to $\Omega$.\end{definition}
+
+\begin{definition}\label{def:consistent-state}A state~$\rho$ is
+consistent with $\bar{\mu}$ on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
+is consistent with $\bar{\mu}$ on every projector in $S$. Notice
+that $\rho\in\coreBorn\left(\bar{\mu},S\right)$ if and only if $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},S\right)$.\end{definition}
+
+Then, we can rephrase theorem~\ref{thm:Shapley}, in the language
+of quantum IVPM with an orthonormal basis.
+
+\begin{cor}For every convex quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
+if $\events'$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{cor}
+
+\begin{proof}Since $\events'$ is a set of mutually commuting projections,
+they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
+and we can find a function~$\tau:\events'\rightarrow2^{\Omega}$
+such that the condition of theorem~\ref{thm:sub-event-space} holds.
+This means that we can find a convex classical IVPM~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
+such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
+for all $P\in\events'$. By theorem~\ref{thm:Shapley}, there is
+a. classical probability measure~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$
+such that $\pmeas\in\mathrm{core}\left(\bar{\mu}'\right)$. Then,
+it is easy to verify that the density matrix~$\sum_{j=0}^{d-1}\pmeas\left(\left\{ j\right\} \right)\proj{j}\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}
 
@@
 is true when we require our IVPM to be convex, and on a commuting
-sub-event space, whose definition is given in the next subsection.
-
-\begin{definition}\label{def:consistent-state}A state~$\rho$ is
-consistent with $\bar{\mu}$ on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
-and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
-Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
-is consistent with $\bar{\mu}$ on every projector in $S$. Notice
-that $\rho\in\coreBorn\left(\bar{\mu},S\right)$ if and only if $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},S\right)$.\end{definition}
-
-\noindent Having these two definition, we can write down our idea
-formally as follow.
+sub-event space.
 

### 2017-05-04 prop_iop.tex
prop_iop.tex \subsection{Classical and Quantum Probability Measures} Updating...

--- 2017-05-03 prop_iop.tex
@@
 and a mutually commuting sub-event space~$\events'\subseteq\events$,
-there is a set~$\Omega$ and a function~$\tau:\events'\rightarrow2^{\Omega}$
-such that:
+there is a set~$\Omega$, another commuting sub-event space~$\widehat{\events}$
+with $\events'\subseteq\widehat{\events}\subseteq\events$, and a
+bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ such that:
 \begin{itemize}
@@
 $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
-for all $P\in\events'$
+for all $P\in\events'$.
 \end{itemize}
@@
 or $1$. Let $\tau\left(P\right)\subseteq\Omega$ be the set of eigenvectors
-whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$.
+whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$,
+$\widehat{\events}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
+and $\tau$ is a bijection between $\widehat{\events}$ and $2^{\Omega}$.
 By definition~\ref{definition:quantum-classical}, $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
-and $\bar{\mu}^{\Omega}$ is a quantum interval-valued probability
+and $\bar{\mu}^{\Omega}$ is a classical interval-valued probability
 measure by lemma~\ref{lemma:classical-probability-measures}.\end{proof}
@@
 and quantum ones on a commuting sub-event space, we can use the quantum
-language to describe the classical world given a commuting sub-event
-space.
+language to describe the classical world given an orthonormal basis.
+
+\begin{definition}Given a Hilbert space~$\Hilb$, an orthonormal
+basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$, and a classical
+real-valued probability measures~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$
+on the sample space~$\Omega$, the density matrix~$\sum_{j=0}^{d-1}\pmeas\left(\left\{ j\right\} \right)\proj{j}$
+is called classical with respect to $\Omega$.\end{definition}
+
+\begin{definition}\label{def:consistent-state}A state~$\rho$ is
+consistent with $\bar{\mu}$ on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
+is consistent with $\bar{\mu}$ on every projector in $S$. Notice
+that $\rho\in\coreBorn\left(\bar{\mu},S\right)$ if and only if $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},S\right)$.\end{definition}
+
+Then, we can rephrase theorem~\ref{thm:Shapley}, in the language
+of quantum IVPM with an orthonormal basis.
+
+\begin{cor}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+if $\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{cor}
+
+\begin{proof}Since $\events'$ is a set of mutually commuting projections,
+they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
+By theorem~\ref{thm:sub-event-space}, we can find a bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$
+and a classical IVPM~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
+such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
+for all $P\in\events'$. Since $\tau$ is a bijection, $\bar{\mu}'$
+is convex. By theorem~\ref{thm:Shapley}, there is a. classical probability
+measure~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$ such that
+\begin{eqnarray*}
+ &  & \pmeas\in\mathrm{core}\left(\bar{\mu}'\right)\\
+ & \Rightarrow & \pmeas\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
+ & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)\textrm{ for all }P\in\widehat{\events}\\
+ & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}\left(P\right)\textrm{ for all }P\in\widehat{\events}
+\end{eqnarray*}
+Then, it is easy to verify that the density matrix~$\sum_{j=0}^{d-1}\pmeas\left(\left\{ j\right\} \right)\proj{j}\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}
 

### 2017-05-05 prop_iop.tex
prop_iop.tex \subsection{Describe Classical World by Quantum Probability Measures with a Commuting Sub-event Space} Updating...

@@
 \begin{cor}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-if $\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{cor}
+if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{cor}
 
@@
 for all $P\in\events'$. Since $\tau$ is a bijection, $\bar{\mu}'$
-is convex. By theorem~\ref{thm:Shapley}, there is a. classical probability
+is convex. By theorem~\ref{thm:Shapley}, there is a classical probability
 measure~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$ such that

### 2017-05-05 prop_iop.tex
prop_iop.tex \begin{thm}\label{thm:sub-event-space}...\end{thm} Add a new case...

@@
 bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ such that:
-\begin{itemize}
-\item If $\mu:\events'\rightarrow\left[0,1\right]$ is a quantum real-valued
-probability measure, then there is a classical real-valued probability
-measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$ such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+\begin{enumerate}
+\item \label{enu:sub-event-space-real-quantum2classical}If $\mu:\events'\rightarrow\left[0,1\right]$
+is a quantum real-valued probability measure, then there is a classical
+real-valued probability measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$
+such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
 for all $P\in\events'$.
-\item If $\bar{\mu}:\events'\rightarrow\mathscr{I}$ is a quantum interval-valued
-probability measure, then there is a classical interval-valued probability
-measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ such that
-$\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
+\item \label{enu:sub-event-space-interval-quantum2classical}If $\bar{\mu}:\events'\rightarrow\mathscr{I}$
+is a quantum interval-valued probability measure, then there is a
+classical interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
+such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
 for all $P\in\events'$.
-\end{itemize}
+\item \label{enu:sub-event-space-real-classical2quantum}If $\mu':2^{\Omega}\rightarrow\left[0,1\right]$
+is a classical real-valued probability measure, then there is a density
+matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+for all $P\in\widehat{\events}$.
+\end{enumerate}
 \end{thm}
 
-\begin{proof}Again, it is sufficient to prove the interval-valued
-case. Since $\events'$ is a set of mutually commuting projections,
-they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
+\begin{proof}Since case \ref{enu:sub-event-space-real-quantum2classical}
+is a special case of case \ref{enu:sub-event-space-interval-quantum2classical},
+it is sufficient to prove case \ref{enu:sub-event-space-interval-quantum2classical}.
+Since $\events'$ is a set of mutually commuting projections, they
+can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
 Pick arbitrary projector~$P\in\events'$, its eigenvalues are $0$
@@
 and $\bar{\mu}^{\Omega}$ is a classical interval-valued probability
-measure by lemma~\ref{lemma:classical-probability-measures}.\end{proof}
+measure by lemma~\ref{lemma:classical-probability-measures}.
+
+For case \ref{enu:sub-event-space-real-classical2quantum}, if we
+pick $\rho=\sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\proj{j}$,
+then $\rho$ is a density matrix because~\cite{544199}
+\begin{eqnarray}
+\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\Tr\left(\proj{j}\right)=1\textrm{ .}
+\end{eqnarray}
+Also, 
+\begin{eqnarray*}
+ &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)=\sum_{j=1}^{N}\mu'\left(\left\{ j\right\} \right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)=\mu'\left(\left\{ j\right\} \right)=\mu'\left(\tau\left(\proj{i}\right)\right)\textrm{ for all }i\textrm{ ,}\\
+ &  & \mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)\overset{\textrm{IH}}{=}\mu'\left(\tau\left(P_{1}\right)\right)+\mu'\left(\tau\left(P_{2}\right)\right)=\mu'\left(\tau\left(P_{1}\right)\cup\tau\left(P_{2}\right)\right)=\mu'\left(\tau\left(P_{1}+P_{2}\right)\right)\textrm{ for commuting }P_{0},P_{1}\in\events\textrm{ with }P_{0}P_{1}=\mathbb{0}\textrm{ .}
+\end{eqnarray*}
+Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+for all $P\in\widehat{\events}$ by induction.\end{proof}
 
@@
  & \Rightarrow & \pmeas\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
- & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)\textrm{ for all }P\in\widehat{\events}\\
+ & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\widehat{\events}\\
  & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}\left(P\right)\textrm{ for all }P\in\widehat{\events}
 \end{eqnarray*}
-Then, it is easy to verify that the density matrix~$\sum_{j=0}^{d-1}\pmeas\left(\left\{ j\right\} \right)\proj{j}\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}
+By case \ref{enu:sub-event-space-real-classical2quantum} in theorem~\ref{thm:sub-event-space},
+there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+for all $P\in\events'$. Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
+i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}
 
@@
 \end{eqnarray}
-Let $\rho=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}P_{i}^{s}$.
-$\rho$ is a density matrix because~\cite{544199}
-\begin{eqnarray}
-\Tr\left(\rho\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}\right)=1\textrm{ .}
-\end{eqnarray}
-Also, 
-\begin{eqnarray}
-\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{s'}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{s'}\right)=\mu'\left(\tau\left(P_{j}^{s'}\right)\right)
-\end{eqnarray}
-for $s'\in\left\{ +,-\right\} $ and $1\le j\le N^{s'}$. Therefore,
-$\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
+By case \ref{enu:sub-event-space-real-classical2quantum} in theorem~\ref{thm:sub-event-space},
+there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+for all $P\in\events'$. Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
 i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}

### 2017-05-05 prop_letter.tex
prop_letter.tex \paragraph{Quantum and Classical IVPMs} Updating according to the proof in prop_iop.tex...

@@
 represents experimenter know nothing about a coin before she tosses
-it, and two classical states~$\proj{0}$ and $\proj{1}$ are both
-consistent with $\bar{\mu}_{2}$ on $\events_{0}$.
+it, and the mixed state~$p\proj{0}+\left(1-p\right)\proj{1}$ is
+consistent with $\bar{\mu}_{2}$ on $\events_{0}$ for all $p\in\left[0,1\right]$,
+because each corresponds to a classical coin with probability~$p$
+to get head.
 
@@
 \begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}\label{thm:Shapley}]
-For every convex IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
-if $\events'$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
+For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
 \end{thm}

### 2017-05-05 prop_letter.tex
prop_letter.tex \paragraph{Quantum and Classical IVPMs} Updating...

@@
 \end{equation}
+For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
+is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
+$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
+\begin{equation}
+\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
+\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
+\end{aligned}
+\end{equation}
 If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
@@
 represents experimenter know nothing about a coin before she tosses
-it, and the mixed state~$p\proj{0}+\left(1-p\right)\proj{1}$ is
-consistent with $\bar{\mu}_{2}$ on $\events_{0}$ for all $p\in\left[0,1\right]$,
-because each corresponds to a classical coin with probability~$p$
-to get head.
+it. Moreover, for each $p\in\left[0,1\right]$, the mixed state~$p\proj{0}+\left(1-p\right)\proj{1}$
+represents a classical coin with probability~$p$ to get head, and
+$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with $\bar{\mu}_{2}$
+on $\events_{0}$ because any classical coin should be consistent
+with the situation where an experimenter has no prior knowledge.
 
-In general, although measurements done with limited resources and
-poor precision may not uniquely identify the true state of a classical
-system, when the system satisfies an extra-condition called convex,
-there is always at least one system that is consistent with the measurements.
+In general, measurements done with limited resources and poor precision
+may not uniquely identify the true state of a classical system. When
+the system satisfies an extra-condition called convex, there is always
+at least one system that is consistent with the measurements.
 

### 2017-05-06 prop_letter.tex
prop_letter.tex \paragraph{Quantum and Classical IVPMs} Updating...

@@
 \end{equation}
-For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
-is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
-$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
-\begin{equation}
-\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
-\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
-\end{aligned}
-\end{equation}
 If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
 the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
-represents experimenter know nothing about a coin before she tosses
-it. Moreover, for each $p\in\left[0,1\right]$, the mixed state~$p\proj{0}+\left(1-p\right)\proj{1}$
-represents a classical coin with probability~$p$ to get head, and
-$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with $\bar{\mu}_{2}$
-on $\events_{0}$ because any classical coin should be consistent
-with the situation where an experimenter has no prior knowledge.
+represents that an experimenter knows nothing about a coin before
+she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
+state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
+coin with probability~$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
+is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
+classical coin should be consistent with the situation where an experimenter
+has no prior knowledge.
 
 In general, measurements done with limited resources and poor precision
-may not uniquely identify the true state of a classical system. When
-the system satisfies an extra-condition called convex, there is always
-at least one system that is consistent with the measurements.
+may not uniquely identify the true state of a classical system. However,
+at least one system is consistent with the measurements when the system
+satisfies an extra-condition called convex.
 

### 2017-05-06 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

@@
 $\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$,
-and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$. }
+and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$ so that $\mul_{1}\left(P_{3}^{+\prime}\right)=\mur_{1}\left(P_{3}^{+\prime}\right)=0$.}
 
@@
 \begin{equation}
-\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]
+\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
 \end{equation}
-intuitively. Since two possible outcomes are $1$ and $2$, the expectation
-value should be between them even if we no prior knowledge about the
-likelihood of outcomes. In contrast, if we naively multiply eigenvalues
-with intervals, their sum, $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$,
-is a worse estimation. In fact, estimating the lower-bound by $1\cdot0+2\cdot0=0$
-is too pessimistic because we know one of outcomes must be happen
-even without any prior knowledge.
+The expectation value is intuitively between two possible outcomes,
+$1$ and $2$, even if we have no prior knowledge about the likelihood
+of outcomes. In contrast, if we naively multiply eigenvalues with
+intervals, their sum, $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$,
+is a worse and counter-intuitive estimation. In fact, estimating the
+lower-bound by $1\cdot0+2\cdot0=0$ is too pessimistic because we
+know one of outcomes must happen without any prior knowledge.
 
@@
 IVPM should be the minimum and maximum expectation value of the same
-observable with respect to states consistent with it. We found this
-is true when we require our IVPM to be convex, and on a commuting
-sub-event space induced by an observable.
+observable with respect to states consistent with it. This is true
+when we require our IVPM to be convex, and on a commuting sub-event
+space induced by an observable.
 
-\begin{definition}
-Given an observable~$\mathbf{O}$ with its spectrum decomposition~(\ref{eq:spectrum-decomposition}).
-A set of projectors~$\events'\subseteq\events$ is called a sub-event
-space induced by $\mathbf{O}$ if it is the minimal sub-event space
-satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
-\end{definition}
+\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
+decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
+is called a sub-event space induced by $\mathbf{O}$ if it is the
+minimal sub-event space containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$.\end{definition}
 
-\noindent Having this definitions, we can write down our idea formally
-as follow.
-
-\begin{thm}
-Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
@@
 Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
-holds for every observable, then $\bar{\mu}$ is convex.
-\end{thm}
+holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
 

### 2017-05-06 prop_letter.tex
prop_letter.tex \section{Results} Added...

@@
 
-\paragraph{Gleason's Theorem}
+\paragraph{Conventional Quantum Theory (\emph{CQT})}
 
@@
 
-\newpage{}
+\section{Results}
 
-In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-any quantum probability measure can be recast as an interval-valued
-one. When $d\ge3$, the question reduces to Gleason's theorem which
-states that for any quantum IVPM~$\bar{\mu}$, there is an unique
-state consistent with $\bar{\mu}$ on every projector.
+\paragraph{Gleason's Theorem}
+
+In CQT, Gleason's theorem asserts any quantum real-valued probability
+measure is consistent with a unique mixed state, and Shapley proved
+a convex quantum IVPM must approximate some states for each classical
+sub-event space. However, a quantum IVPM may not approximate any particular
+state while considering all projectors~$\events$.
+
+\begin{example}[Three-dimensional quantum three-interval-valued probability
+measure\label{ex:three-dimensional-three-value}]
+Given a three dimensional Hilbert space with an orthonormal basis
+$\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
+$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
+and
+\begin{subequations}
+\begin{eqnarray}
+ &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
+ & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\textrm{ ,}
+\end{aligned}
+\\
+ &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
+ & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
+\end{aligned}
+\\
+ &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
+\end{eqnarray}
+\end{subequations}
+It is straightforward to verify that $\bar{\mu}$ is a convex quantum
+IVPM.
+
+Let $\events_{1}$ be the minimal event space containing both $\proj{0}$
+and $\proj{\ps}$. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
+for any mixed state~$\rho\in\coreBorn\left(\bar{\mu},\events_{1}\right)$,
+we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$.
+Hence, $\rho$ is actually the pure state orthogonal to both $\ket{0}$
+and $\ket{\ps}$. The only choice of $\rho$ is $\ket{2}$, and it
+is easy to verify $\proj{2}$ is actually in $\coreBorn\left(\bar{\mu},\events_{1}\right)$.
+
+Similarly, let $\events_{2}$ be the minimal event space containing
+both $\proj{0}$ and $\proj{\ps'}$. We have $\coreBorn\left(\bar{\mu},\events_{2}\right)=\left\{ \proj{1}\right\} $.
+Therefore, 
+\begin{equation}
+\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},\events_{1}\right)\cap\coreBorn\left(\bar{\mu},\events_{2}\right)=\emptyset\textrm{ ,}
+\end{equation}
+and must be empty.
+\end{example}
+
+Although Gleason's theorem doesn't hold for every quantum IVPM, when
+the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+any quantum IVPM can be recast as an real-valued one. When $d\ge3$,
+the question reduces to Gleason's theorem which states that for any
+quantum IVPM~$\bar{\mu}$, there is an unique state consistent with
+$\bar{\mu}$ on every projector. In general, this kind of inconsistency
+can be reduced if we increase the measurement resource, that is, using
+finer intervals. We conjecture by consuming more and more measurement
+resource, it would be more and more likely that there is a state consistent
+with a quantum IVPM on all projectors~$\events$.
+
+\paragraph{The Kochen-Specker Theorem}
 
@@
 is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
-However, before diving into the Kochen-Specker theorem, it is better
-to understand how to define the expectation value of an observable
-with quantum IVPMs.
-
-\paragraph{The Kochen-Specker Theorem}
-
-After we defined the expectation value, we will use the essential
-idea of the Kochen-Specker theorem to prove there is no quantum IVPM
-mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
+We will use the essential idea of the Kochen-Specker theorem to prove
+there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
 Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
@@
 
-However, even if a quantum IVPM approximates some states for each
-classical sub-event space, it may not approximate any particular state
-while considering all projectors~$\events$.
-
-\begin{example}[Three-dimensional quantum three-interval-valued probability
-measure\label{ex:three-dimensional-three-value}]
-Given a three dimensional Hilbert space with an orthonormal basis
-$\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
-$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
-and
-\begin{subequations}
-\begin{eqnarray}
- &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
- & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\textrm{ ,}
-\end{aligned}
-\\
- &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
- & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
-\end{aligned}
-\\
- &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
-\end{eqnarray}
-\end{subequations}
-It is straightforward to verify that $\bar{\mu}$ is a quantum IVPM.
-
-Let $\events_{1}$ be the minimal event space containing both $\proj{0}$
-and $\proj{\ps}$. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
-for any mixed state~$\rho\in\coreBorn\left(\bar{\mu},\events_{1}\right)$,
-we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$.
-Hence, $\rho$ is actually the pure state orthogonal to both $\ket{0}$
-and $\ket{\ps}$. The only choice of $\rho$ is $\ket{2}$, and it
-is easy to verify $\proj{2}$ is actually in $\coreBorn\left(\bar{\mu},\events_{1}\right)$.
-
-Similarly, let $\events_{2}$ be the minimal event space containing
-both $\proj{0}$ and $\proj{\ps'}$. We have $\coreBorn\left(\bar{\mu},\events_{2}\right)=\left\{ \proj{1}\right\} $.
-Therefore, 
-\begin{equation}
-\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},\events_{1}\right)\cap\coreBorn\left(\bar{\mu},\events_{2}\right)=\emptyset\textrm{ ,}
-\end{equation}
-and must be empty.
-\end{example}
-
-We found this kind of incompatibility can be reduced if we increase
-the measurement resource, that is, using finer intervals. We conjecture
-by consuming more and more measurement resource, it would be more
-and more likely that a quantum IVPM has a state consistent with it
-on all projectors~$\events$.
-
-\yutsung{Although Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
-it seems not directly relating to empty/non-empty core. On one hand,
-the part using hidden variables cannot really apply on quantum IVPM
-expect $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-case. On the other hand, for the part predicted by quantum mechanics,
-the product of observables in inequalities are always either $\mathbb{1}$
-or $-\mathbb{1}$ whose the interval-valued probabilities and expectation
-values are always $\necess$. In this kind of situation, the inequalities
-applies on all IVPMs, no matter whether it has an empty or non-empty
-core.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-05-06 prop_letter.tex
prop_letter.tex Update here and there...

@@
 
-\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}\label{thm:Shapley}]
-For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
-\end{thm}
+Based on Shapley's classical result~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
+we have the following theorem.
+
+\begin{thm}\label{thm:Shapley}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
 
@@
 
-In CQT, Gleason's theorem asserts any quantum real-valued probability
-measure is consistent with a unique mixed state, and Shapley proved
-a convex quantum IVPM must approximate some states for each classical
-sub-event space. However, a quantum IVPM may not approximate any particular
-state while considering all projectors~$\events$.
+Gleason's theorem asserts any quantum real-valued probability measure
+is consistent with a unique mixed state, and Shapley proved a convex
+quantum IVPM must approximate some states for each classical sub-event
+space. However, it may not approximate the same state in every sub-event
+space. As the result, there may be no state consistent with a convex
+quantum IVPM on all projectors~$\events$.
 
-\begin{example}[Three-dimensional quantum three-interval-valued probability
-measure\label{ex:three-dimensional-three-value}]
-Given a three dimensional Hilbert space with an orthonormal basis
-$\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
+\begin{example}\label{ex:three-dimensional-three-value}Given a three
+dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
 $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
@@
 
-Let $\events_{1}$ be the minimal event space containing both $\proj{0}$
-and $\proj{\ps}$. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
-for any mixed state~$\rho\in\coreBorn\left(\bar{\mu},\events_{1}\right)$,
-we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$.
-Hence, $\rho$ is actually the pure state orthogonal to both $\ket{0}$
-and $\ket{\ps}$. The only choice of $\rho$ is $\ket{2}$, and it
-is easy to verify $\proj{2}$ is actually in $\coreBorn\left(\bar{\mu},\events_{1}\right)$.
+Let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
+we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
+for any mixed state~$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
+Hence, $\rho$ is actually $\ket{2}$, the only pure state orthogonal
+to both $\ket{0}$ and $\ket{\ps}$. It is easy to verify $\proj{2}$
+is actually in $\coreBorn\left(\bar{\mu},S_{1}\right)$.
 
-Similarly, let $\events_{2}$ be the minimal event space containing
-both $\proj{0}$ and $\proj{\ps'}$. We have $\coreBorn\left(\bar{\mu},\events_{2}\right)=\left\{ \proj{1}\right\} $.
+Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We
+have $\coreBorn\left(\bar{\mu},S_{2}\right)=\left\{ \proj{1}\right\} $.
 Therefore, 
 \begin{equation}
-\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},\events_{1}\right)\cap\coreBorn\left(\bar{\mu},\events_{2}\right)=\emptyset\textrm{ ,}
+\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},S_{1}\right)\cap\coreBorn\left(\bar{\mu},S_{2}\right)=\emptyset
 \end{equation}
@@
 
-Although Gleason's theorem doesn't hold for every quantum IVPM, when
-the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-any quantum IVPM can be recast as an real-valued one. When $d\ge3$,
-the question reduces to Gleason's theorem which states that for any
-quantum IVPM~$\bar{\mu}$, there is an unique state consistent with
-$\bar{\mu}$ on every projector. In general, this kind of inconsistency
-can be reduced if we increase the measurement resource, that is, using
-finer intervals. We conjecture by consuming more and more measurement
-resource, it would be more and more likely that there is a state consistent
-with a quantum IVPM on all projectors~$\events$.
+Although Gleason's theorem doesn't hold for every quantum IVPM, it
+can be applied in a limit case when the intervals are infinitely precise.
+That is, when $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+any quantum IVPM can be recast as an real-valued one and has an unique
+state consistent with it on every projector when $d\ge3$.
+
+In general, this kind of inconsistency can be reduced if we increase
+the measurement resource, that is, using finer intervals. We conjecture
+by using finer and finer intervals, it would be more and more likely
+that there is a state consistent with a quantum IVPM on all projectors~$\events$.
 
@@
 \begin{equation}
-\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
+\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
 \end{equation}
-for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $.
+for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
 
@@
 \end{equation}
-must have the the expectation value~$1$ or $-1$. In each row and
-column, operators commutes, and each operator is the product of the
-two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
+In each row and column, operators commutes, and each operator is the
+product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
 Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such

### 2017-05-10 prop_letter.tex
prop_letter.tex \paragraph{Gleason's Theorem} Add subscript in example.

@@
 \begin{eqnarray}
- &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
- & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\textrm{ ,}
+ &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
+ & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\textrm{ ,}
 \end{aligned}
 \\
- &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
- & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
+ &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
+ & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
 \end{aligned}
 \\
- &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
+ &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
 \end{eqnarray}
 \end{subequations}
-It is straightforward to verify that $\bar{\mu}$ is a convex quantum
-IVPM.
+It is straightforward to verify that $\bar{\mu}_{3}$ is a convex
+quantum IVPM.
 
-Let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
+Let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because $\bar{\mu}_{3}(\proj{0})=\bar{\mu}_{3}(\proj{\ps})=\imposs$,
 we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-for any mixed state~$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
+for any mixed state~$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
 Hence, $\rho$ is actually $\ket{2}$, the only pure state orthogonal
 to both $\ket{0}$ and $\ket{\ps}$. It is easy to verify $\proj{2}$
-is actually in $\coreBorn\left(\bar{\mu},S_{1}\right)$.
+is actually in $\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
 
 Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We
-have $\coreBorn\left(\bar{\mu},S_{2}\right)=\left\{ \proj{1}\right\} $.
+have $\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\left\{ \proj{1}\right\} $.
 Therefore, 
 \begin{equation}
-\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},S_{1}\right)\cap\coreBorn\left(\bar{\mu},S_{2}\right)=\emptyset
+\coreBorn\left(\bar{\mu}_{3},\events\right)\subseteq\coreBorn\left(\bar{\mu}_{3},S_{1}\right)\cap\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\emptyset
 \end{equation}
-and must be empty.
-\end{example}
+and must be empty.\end{example}
 

### 2017-05-10 prop_letter.tex
From: Hanson, Andrew J. Sent: Wednesday, May 10, 2017 11:27 To: Tai, Yu-Tsung <yuttai@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu> Subject: Here is the first draft intro text
Here is our starting draft of the intro page text:
   -- the last paragraphs in particular depend a lot on opinions of what
we should emphasize, and so are heavily open to discussion, revision,
and improvement.
    -Andy and Yu-Tsung
----------------------------------------------------

In this letter, we extend our previous work on the foundations of
computability in quantum mec

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Textbook quantum mechanics asserts that the probability of a measurement
-can be computed from wave function of the system and the measuring
-observable \emph{exactly} while real measurements must be finite precision.
-Whether finite precision measurement in reality affect the idealized
-quantum concept, e.g., contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
-and the very foundation of quantum mechanics is still a problem. In
-this letter, we model the finite precision quantum measurement by
-quantum interval-valued probability measures (IVPMs) which provides
-not only a uniform framework to understand Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
-and the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
-but also some examples which cannot be explained by the Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+In this letter, we extend our previous work on the foundations of computability in quantum mechanics by exploring the application of interval-valued probability measures (IVPM) to achieving a coherent formulation of finite-resource quantum mechanics.
 
-The tension between finite precision measurement and the foundation
-of quantum mechanics sharpened, when the original definition of contextuality
-based on infinitely precise numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
-After a long debate~\cite{Mermin1999,Peres2003,BarrettKent2004},
-people are still trying to update the definition of contextuality
-when they want to perform further experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+There are long-standing debates in the foundations of quantum mechanics regarding the tension between finite precision measurement and contextuality~\cite{Peres2003,BarrettKent2004}.
+For example, Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree on whether finite-precision measurement invalidate the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion continues on whether contextuality is experimentally verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+The
+fundamental question is how to make mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.
 
-We found that finite precision measurement affects not only contextuality
-but also the fundamental rule computing probability from a state.
-In the early formulation of quantum mechanics, von Neumann essentially
-formulated a quantum state as a density matrix while Mackey formulated
-a quantum state as a quantum probability measure which are proved
-by Gleason to be the essentially same as a density matrix~\cite{Varadarajan2008}.
-Combining quantum probability measures and the classical IVPM~\cite{JamisonLodwick2004}
-which could be used to formulate classical finite precision measurement,
-we can define quantum IVPMs. Surprisingly, there is a quantum IVPM
-which cannot be compatible with any density matrix according to the
-Born rule. Similar to revising the definition of contextuality because
-of finite precision measurement, the very basic definition of a quantum
-state or how to compute the probability from a state might need to
-be refined when we consider the finite precision measurement. This
-can also provide a new quantum phenomena different from the classical
-world, because IVPMs become classical so that the non-Born IVPMs disappears
-when we restricting the domain of quantum IVPMs on a commuting sub-event
-space. \newpage{}
+Our first observation is that essential objectives of our program to achieve a computable theory of quantum mechanics and finite-resource measurement, attempted previously with computable number systems~\cite{usat,geometry2013,DQT2014}, may be achievable by extending classical interval-valued probability measures~\cite{JamisonLodwick2004} to the quantum domain.
+We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework exploiting the fact that a density matrix approach can be considered as equivalent to a description of quantum states using probability measures~\cite{10.2307/2308516,Varadarajan2008}.
+%Mackey=10.2307 One result is that the expectation value of an observable with respect to a QIVPM can be defined to be consistent with the constraints on the expectation value of the same observable expected from continuous quantum mechanics.
+We then examine Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the Kochen-Specker theorem in the context of QIVPM's, and conclude that they correspond to the limit of an infinite number of precise intervals, and the set of crypto-deterministic intervals (the set $\{\imposs,\necess\}$), respectively.
+
+We note, however, that in this approach there exist QIVPM's that do not correspond to a density matrix computable by the Born rule, so that Gleason's theorem cannot hold in general.
+It thus remains possible that a refinement of the basic definition of a quantum state or the computation of probability from a state may be required when we rigorously consider the implications of finite precision measurement.
 

### 2017-05-10 prop_letter.tex
prop.bib Updated to fix our erratum with BibTeX with PRL...

@@
 
-Our first observation is that essential objectives of our program to achieve a computable theory of quantum mechanics and finite-resource measurement, attempted previously with computable number systems~\cite{usat,geometry2013,DQT2014}, may be achievable by extending classical interval-valued probability measures~\cite{JamisonLodwick2004} to the quantum domain.
+Our first observation is that essential objectives of our program to achieve a
+computable theory of quantum mechanics and finite-resource measurement,
+attempted previously with computable number systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by extending classical interval-valued probability measures~\cite{JamisonLodwick2004} to the quantum domain.
 We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework exploiting the fact that a density matrix approach can be considered as equivalent to a description of quantum states using probability measures~\cite{10.2307/2308516,Varadarajan2008}.

### 2017-05-10 prop_letter.tex
begin restructure

--- 2017-05-10 prop_letter.tex
@@
 
-\title{Contextuality and the Born rule in fuzzy quantum theories}
+\title{Interval-Valued Quantum Probabilities: Contextuality and the Born Rule}
+
+\author{Yu-Tsung Tai}
+\affiliation{Department of Mathematics, Indiana University, Bloomington, Indiana 47405,
+USA}
+\affiliation{Department of Computer Science, Indiana University, Bloomington,
+Indiana 47405, USA}
 
 \author{Andrew J Hanson}
-\affiliation{School of Informatics and Computing, Indiana University, Bloomington,
+\affiliation{Department of Informatics, Indiana University, Bloomington,
 Indiana 47405, USA}
@@
 \author{Amr Sabry}
-\affiliation{School of Informatics and Computing, Indiana University, Bloomington,
-Indiana 47405, USA}
-
-\author{Yu-Tsung Tai}
-\affiliation{Department of Mathematics, Indiana University, Bloomington, Indiana 47405,
-USA}
-\affiliation{School of Informatics and Computing, Indiana University, Bloomington,
+\affiliation{Department of Computer Science, Indiana University, Bloomington,
 Indiana 47405, USA}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this letter, we extend our previous work on the foundations of computability in quantum mechanics by exploring the application of interval-valued probability measures (IVPM) to achieving a coherent formulation of finite-resource quantum mechanics.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
 
-There are long-standing debates in the foundations of quantum mechanics regarding the tension between finite precision measurement and contextuality~\cite{Peres2003,BarrettKent2004}.
-For example, Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree on whether finite-precision measurement invalidate the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion continues on whether contextuality is experimentally verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
-The
-fundamental question is how to make mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.
+In this letter, we extend our previous work on the foundations of
+computability in quantum mechanics by exploring the application of
+interval-valued probability measures (IVPM) to achieving a coherent
+formulation of finite-resource quantum mechanics.
 
-Our first observation is that essential objectives of our program to achieve a computable theory of quantum mechanics and finite-resource measurement, attempted previously with computable number systems~\cite{usat,geometry2013,DQT2014}, may be achievable by extending classical interval-valued probability measures~\cite{JamisonLodwick2004} to the quantum domain.
-We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework exploiting the fact that a density matrix approach can be considered as equivalent to a description of quantum states using probability measures~\cite{10.2307/2308516,Varadarajan2008}.
-%Mackey=10.2307 One result is that the expectation value of an observable with respect to a QIVPM can be defined to be consistent with the constraints on the expectation value of the same observable expected from continuous quantum mechanics.
-We then examine Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the Kochen-Specker theorem in the context of QIVPM's, and conclude that they correspond to the limit of an infinite number of precise intervals, and the set of crypto-deterministic intervals (the set $\{\imposs,\necess\}$), respectively.
+There are long-standing debates in the foundations of quantum
+mechanics regarding the tension between finite precision measurement
+and contextuality~\cite{Peres2003,BarrettKent2004}.  For example,
+Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree
+on whether finite-precision measurement invalidate the Kochen-Specker
+theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion
+continues on whether contextuality is experimentally
+verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
+fundamental question is how to make mathematical theories of quantum
+mechanics that are intrinsically, rather than only implicitly,
+consistent with the resources available for the realistic accuracy of
+an actual measurement.
 
-We note, however, that in this approach there exist QIVPM's that do not correspond to a density matrix computable by the Born rule, so that Gleason's theorem cannot hold in general.
-It thus remains possible that a refinement of the basic definition of a quantum state or the computation of probability from a state may be required when we rigorously consider the implications of finite precision measurement.
+Our first observation is that essential objectives of our program to
+achieve a computable theory of quantum mechanics and finite-resource
+measurement, attempted previously with computable number
+systems~\cite{usat,geometry2013,DQT2014}, may be achievable by
+extending classical interval-valued probability
+measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by
+axiomatizing a quantum interval-valued probability measure (QIVPM)
+framework exploiting the fact that a density matrix approach can be
+considered as equivalent to a description of quantum states using
+probability
+measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
+One result is that the expectation value of an observable with respect
+to a QIVPM can be defined to be consistent with the constraints on the
+expectation value of the same observable expected from continuous
+quantum mechanics.  We then examine Gleason's
+theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
+Kochen-Specker theorem in the context of QIVPM's, and conclude
+that they correspond to the limit of an infinite number of precise
+intervals, and the set of crypto-deterministic intervals (the set
+$\{\imposs,\necess\}$), respectively.
 
-\section{Theory}
+We note, however, that in this approach there exist QIVPM's that do
+not correspond to a density matrix computable by the Born rule, so
+that Gleason's theorem cannot hold in general.  It thus remains
+possible that a refinement of the basic definition of a quantum state
+or the computation of probability from a state may be required when we
+rigorously consider the implications of finite precision measurement.
 
-\paragraph{Conventional Quantum Theory (\emph{CQT})}
+% Textbook quantum mechanics asserts that the probability of a
+% measurement can be computed from wave function of the system and the
+% measuring observable \emph{exactly} while real measurements must be
+% finite precision.  Whether finite precision measurement in reality
+% affect the idealized quantum concept, e.g.,
+% contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
+% and the very foundation of quantum mechanics is still a problem. In
+% this letter, we model the finite precision quantum measurement by
+% quantum interval-valued probability measures (IVPMs) which provides
+% not only a uniform framework to understand Gleason's
+% theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
+% Kochen-Specker
+% theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
+% but also some examples which cannot be explained by the Born
+% rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
 
-In conventional quantum theory, when we measure a property $\mathbf{O}$
-of a physical system whose state is represented by a density matrix~$\rho$,
-the probability to obtain the value $\lambda$ of that property is
-determined by the Born rule $\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho P_{i}\right)$,
-where $P_{i}$ denotes the projector onto the eigenspace corresponding
-to the eigenvalue $\lambda_{i}$ of the Hermitian operator $\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
-Alternatively, one may say that the state $\rho$ determines the probability
-measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function from the
-set $\events$ of all possible projectors $P$ onto the interval $[0,1]$,
-and satisfies the following probability axioms~ \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
+% The tension between finite precision measurement and the foundation of
+% quantum mechanics sharpened, when the original definition of
+% contextuality based on infinitely precise numbers is proved not
+% experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.  After a
+% long debate~\cite{Mermin1999,Peres2003,BarrettKent2004}, people are
+% still trying to update the definition of contextuality when they want
+% to perform further
+% experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+
+% We found that finite precision measurement affects not only
+% contextuality but also the fundamental rule computing probability from
+% a state.  In the early formulation of quantum mechanics, von Neumann
+% essentially formulated a quantum state as a density matrix while
+% Mackey formulated a quantum state as a quantum probability measure
+% which are proved by Gleason to be the essentially same as a density
+% matrix~\cite{Varadarajan2008}.  Combining quantum probability measures
+% and the classical IVPM~\cite{JamisonLodwick2004} which could be used
+% to formulate classical finite precision measurement, we can define
+% quantum IVPMs. Surprisingly, there is a quantum IVPM which cannot be
+% compatible with any density matrix according to the Born rule. Similar
+% to revising the definition of contextuality because of finite
+% precision measurement, the very basic definition of a quantum state or
+% how to compute the probability from a state might need to be refined
+% when we consider the finite precision measurement. This can also
+% provide a new quantum phenomena different from the classical world,
+% because IVPMs become classical so that the non-Born IVPMs disappears
+% when we restricting the domain of quantum IVPMs on a commuting
+% sub-event space.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Quantum Measurements}
+
+A \emph{probability space} is a mathematical abstraction specifying
+the necessary conditions for reasoning coherently about collections of
+uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the set
+of events is the set of \emph{projection operators} $P$. This set
+includes the empty projection~$\mathbb{0}$, the identity
+projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
+$\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
+projections, and products of \emph{commuting} projections. In a
+quantum probability
+space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
+each event $P_i$ is associated with a probability $\mu(P_i)$ subject
+to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
+$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set of
+mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$, we
+have:
+\begin{equation}
+\mu\left(\sum_{i=1}^{N}P_{i}\right)=
+\sum_{i=1}^{N}\mu\left(P_{i}\right)
+\textrm{ .}\label{eq:QuantumProbability-Addition}
+\end{equation}
+
+\newpage
+
+Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
+satisfying the above axioms, Gleason's theorem asserts that there
+exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
+in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+
+In conventional quantum theory (CQT), when we measure a property
+$\mathbf{O}$ of a physical system whose state is represented by a
+density matrix~$\rho$, the probability to obtain the value $\lambda$
+of that property is determined by the Born rule
+$\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
+  P_{i}\right)$, where $P_{i}$ denotes the projector onto the
+eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
+Hermitian operator
+$\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+Alternatively, one may say that the state $\rho$ determines the
+probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
+from the set $\events$ of all possible projectors $P$ onto the
+interval $[0,1]$, and satisfies the following probability axioms~
+\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:
 \begin{itemize}
@@
 
-\paragraph{Quantum Interval-valued Probability Measures (\emph{IVPMs})}
-
-To formalize the idea of finite precision measurement, we next introduce
-the notion of quantum IVPM~$\bar{\mu}$. The latter replaces the
-infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$
-of intervals. Since the intervals $\imposs=\left[0,0\right]$ and
-$\necess=\left[1,1\right]$ should be included in $\mathscr{I}$,
-and arithmetic operations on intervals satisfy \begin{subequations}\label{eq:interval-operations}
+To formalize the idea of finite precision measurement, we next
+introduce the notion of quantum interval-valued probability measures
+(\emph{IVPMs})~$\bar{\mu}$. The latter replaces the infinitely precise
+interval $[0,1]$ by a finite collection $\mathscr{I}$ of
+intervals. Since the intervals $\imposs=\left[0,0\right]$ and
+$\necess=\left[1,1\right]$ should be included in $\mathscr{I}$, and
+arithmetic operations on intervals
+satisfy \begin{subequations}\label{eq:interval-operations}
 \begin{eqnarray}
@@
 
-\paragraph{Quantum and Classical IVPMs}
-
 Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} when
@@
 if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
-
-\paragraph{Expectation Values for Quantum IVPMs}
 
@@
 
-\section{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Quantum States}
 
-\paragraph{Gleason's Theorem}
+%%%%%
+\subsection{Gleason}
 
@@
 
-\paragraph{The Kochen-Specker Theorem}
+%%%
+\subsection{Kochen-Specker}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliography{prop}
-
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-05-10 prop_letter.tex
a bit on section 2

@@
 the necessary conditions for reasoning coherently about collections of
-uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the set
-of events is the set of \emph{projection operators} $P$. This set
+uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the
+events of interests are the \emph{projection operators} $P$. This set
 includes the empty projection~$\mathbb{0}$, the identity
@@
 projections, and products of \emph{commuting} projections. In a
-quantum probability
+well-defined quantum probability
 space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
@@
 \end{equation}
+
+As an example, consider a three-dimensional Hilbert space with
+orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable $Q$
+with spectral decomposition $\proj{1} + 2\,\proj{2} +
+3\,\proj{3}$. Here are two fragments of valid probability measures
+$\mu_1$ and $\mu_2$ that can associated with this space:
+$\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
+$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0$,
+$\mu_2(\proj{1}) = 0.5$, $\mu_2(\proj{2}) = 0.5$. By the Born rule,
+the first probability measure corresponds to the quantum system being
+in the state $1/\sqrt{2}(\ket{0}+\ket{1})$ and the second corresponds
+to the quantum system being in the state
+$1/\sqrt{2}(\ket{1}+\ket{2})$. The expectation value of the observable
+is the first case is 1.5 and in the second it is 2.
 
@@
 \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:
+
 \begin{itemize}

### 2017-05-11 prop_letter.tex
prop_letter.tex \section{Quantum Measurements} Fix typos...

@@
 orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable $Q$
-with spectral decomposition $\proj{1} + 2\,\proj{2} +
-3\,\proj{3}$. Here are two fragments of valid probability measures
+with spectral decomposition $\proj{0} + 2\,\proj{1} +
+3\,\proj{2}$. Here are two fragments of valid probability measures
 $\mu_1$ and $\mu_2$ that can associated with this space:
 $\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
-$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0$,
-$\mu_2(\proj{1}) = 0.5$, $\mu_2(\proj{2}) = 0.5$. By the Born rule,
+$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0.5$,
+$\mu_2(\proj{1}) = 0$, $\mu_2(\proj{2}) = 0.5$. By the Born rule,
 the first probability measure corresponds to the quantum system being
-in the state $1/\sqrt{2}(\ket{0}+\ket{1})$ and the second corresponds
+in the state $(\ket{0}+\ket{1})/\sqrt{2}$ and the second corresponds
 to the quantum system being in the state
-$1/\sqrt{2}(\ket{1}+\ket{2})$. The expectation value of the observable
+$(\ket{0}+\ket{2})/\sqrt{2}$. The expectation value of the observable
 is the first case is 1.5 and in the second it is 2.

### 2017-05-11 prop_letter.tex
more on sec 2

@@
 $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set of
-mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$, we
+mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$, we
 have:
@@
 the first probability measure corresponds to the quantum system being
-in the state $(\ket{0}+\ket{1})/\sqrt{2}$ and the second corresponds
+in the state $(\ket{0}\pm\ket{1})/\sqrt{2}$ and the second corresponds
 to the quantum system being in the state
-$(\ket{0}+\ket{2})/\sqrt{2}$. The expectation value of the observable
+$(\ket{0}\pm\ket{2})/\sqrt{2}$. The expectation value of the observable
 is the first case is 1.5 and in the second it is 2.
+
+The above axioms describe a mathematical idealization involving
+infinitely precise measurements. In an actual experimental setup with
+an ensemble of quantum states that are not exactly identical, and with
+small imperfections and inaccuracies in measuring devices, an
+experimenter might only be able to determine that the probability of
+the event $\proj{0}$ is in the range $[0.49,0.51]$. The spread in this
+range depends on the amount of resources (time, energy, money, etc)
+that are devoted to the experiment. In the classical setting, this
+``fuzziness'' is formalized by moving to \emph{interval-valued
+  probability measures} (IVPMs).
+
+To adapt the axioms of such IVPMs to the quantum case, we proceed as
+follows. First we fix a collection of intervals $\mathscr{I}$ that
+represent an abstraction of the available experimental resources. At
+one extreme, infinitely precise resources would correspond to the
+collection of intervals $\{[x,x] \mid x \in [0,1]\}$. This case should
+coincide with the idealized situation above. At another extreme, an
+experiment with \emph{no} resources would correspond to the following
+three intervals $\imposs=\left[0,0\right]$,
+$\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
+two intervals are associated with the empty projection and the
+identity projection but every other projection would be associated
+with $\unknown$; its probability can be anything in the range
+$[0,1]$. A third special situation would be to consider IVPMs with
+only the two intervals $\imposs=\left[0,0\right]$ and
+$\necess=\left[1,1\right]$. This is what Peres calls the
+\emph{crypto-deterministic} case in which there is no ambiguity about
+the status of any event; we know for certain if it will occur or not.
 

### 2017-05-11 prop_letter.tex
done with sec 2 first pass

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum Measurements}
+\section{Fuzzy Measurements}
 
@@
 ``fuzziness'' is formalized by moving to \emph{interval-valued
-  probability measures} (IVPMs).
+  probability measures}.
 
@@
 
-\newpage
-
-Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
-satisfying the above axioms, Gleason's theorem asserts that there
-exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
-in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-
-In conventional quantum theory (CQT), when we measure a property
-$\mathbf{O}$ of a physical system whose state is represented by a
-density matrix~$\rho$, the probability to obtain the value $\lambda$
-of that property is determined by the Born rule
-$\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
-  P_{i}\right)$, where $P_{i}$ denotes the projector onto the
-eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
-Hermitian operator
-$\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
-Alternatively, one may say that the state $\rho$ determines the
-probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
-from the set $\events$ of all possible projectors $P$ onto the
-interval $[0,1]$, and satisfies the following probability axioms~
-\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:
-
-\begin{itemize}
-\item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
-\item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
-\item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
-1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
-\item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
-$P_iP_j=\delta_{ij}P_i$,
-we have 
-\begin{equation}
-\mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
-\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
-\textrm{ .}\label{eq:QuantumProbability-Addition}
-\end{equation}
-\end{itemize}
-Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
-satisfying the above axioms, Gleason's theorem asserts that there
-exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
-in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-
-Furthermore, if we express an observable~$\mathbf{O}$ as its spectrum
-decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
-value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
-\begin{equation}
-\expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
-\end{equation}
-
-To formalize the idea of finite precision measurement, we next
-introduce the notion of quantum interval-valued probability measures
-(\emph{IVPMs})~$\bar{\mu}$. The latter replaces the infinitely precise
-interval $[0,1]$ by a finite collection $\mathscr{I}$ of
-intervals. Since the intervals $\imposs=\left[0,0\right]$ and
-$\necess=\left[1,1\right]$ should be included in $\mathscr{I}$, and
-arithmetic operations on intervals
-satisfy \begin{subequations}\label{eq:interval-operations}
+Given a collection of intervals $\mathscr{I}$ with addition and scalar
+multiplication defined as follows: 
+\begin{subequations}\label{eq:interval-operations}
 \begin{eqnarray}
@@
 [xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
-[xr,xl] & \textrm{for }x\le0\textrm{ .}
+[xr,xl] & \textrm{for }x\le0\textrm{ ,}
 \end{cases}
 \end{eqnarray}
-\end{subequations} $\bar{\mu}:\events\rightarrow\mathscr{I}$ is
-defined by the axioms: 
-\begin{itemize}
-\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
-\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
-\item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-$P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
+\end{subequations}
+a QIVPM $\bar{\mu}$ is an assignment of intervals to each event
+obeying the following axioms:
+$\bar{\mu}(\mathbb{0})=\imposs=\left[0,0\right]$,
+$\bar{\mu}(\mathbb{1})=\necess=\left[1,1\right]$,
+$\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
+and for a set of mutually orthogonal projections
+$\left\{ P_{i}\right\} _{i=1}^{N}$, we have:
 \begin{equation}
@@
 \end{equation}
-\end{itemize}
-condition that provides only a bound and not an equivalence as in
-Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
-$\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
-$\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
-\[
-\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
-\]
+The first three axioms are the direct counterpart of the corresponding
+axioms for conventional probability measures. The last condition
+allows for the interval associated with a composite event to be
+sharper than the interval calculated from each individual
+event. Intuitively, consider an event $P$ and its complement
+$\mathbb{1}-P$. Looking at each separately we may discover
+$\bar{\mu}(P) = [0.2,0.3]$ and $\bar{\mu}(\mathbb{1}-P)=[0.7,0.8]$. By
+adding the individual intervals, we predict the probability of the
+composite event $P+(\mathbb{1}-P)$ to be in the range
+$[0.9,1.1]$. Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}
+allows us to refine this to $[1,1]$ by recognizing that the composite
+event is the identity projection.
+
+% In conventional quantum theory (CQT), when we measure a property
+% $\mathbf{O}$ of a physical system whose state is represented by a
+% density matrix~$\rho$, the probability to obtain the value $\lambda$
+% of that property is determined by the Born rule
+% $\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
+%   P_{i}\right)$, where $P_{i}$ denotes the projector onto the
+% eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
+% Hermitian operator
+% $\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+% Alternatively, one may say that the state $\rho$ determines the
+% probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
+% from the set $\events$ of all possible projectors $P$ onto the
+% interval $[0,1]$, and satisfies the following probability axioms~
+% \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:
+
+% \begin{itemize}
+% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
+% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
+% \item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
+% 1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
+% \item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
+% $P_iP_j=\delta_{ij}P_i$,
+% we have 
+% \begin{equation}
+% \mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
+% \sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
+% \textrm{ .}\label{eq:QuantumProbability-Addition}
+% \end{equation}
+% \end{itemize}
+% Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
+% satisfying the above axioms, Gleason's theorem asserts that there
+% exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
+% in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+
+% Furthermore, if we express an observable~$\mathbf{O}$ as its spectrum
+% decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
+% value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
+% \begin{equation}
+% \expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
+% \end{equation}
+
+% To formalize the idea of finite precision measurement, we next
+% introduce the notion of quantum interval-valued probability measures
+% (\emph{IVPMs})~$\bar{\mu}$. The latter replaces the infinitely precise
+% interval $[0,1]$ by a finite collection $\mathscr{I}$ of
+% intervals. Since the intervals $\imposs=\left[0,0\right]$ and
+% $\necess=\left[1,1\right]$ should be included in $\mathscr{I}$, and
+% arithmetic operations on intervals
+% satisfy \begin{subequations}\label{eq:interval-operations}
+% \begin{eqnarray}
+%  &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
+%  &  & x[l,r]=\begin{cases}
+% [xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
+% [xr,xl] & \textrm{for }x\le0\textrm{ .}
+% \end{cases}
+% \end{eqnarray}
+% \end{subequations} $\bar{\mu}:\events\rightarrow\mathscr{I}$ is
+% defined by the axioms: 
+% \begin{itemize}
+% \item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
+% \item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
+% \item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
+% \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+% $P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
+% \begin{equation}
+% \bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion}
+% \end{equation}
+% \end{itemize}
+% condition that provides only a bound and not an equivalence as in
+% Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
+% $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
+% $\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
+% \[
+% \bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
+% \]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Fuzzy States}
 

### 2017-05-11 prop_letter.tex
prop_letter.tex Some formating updates. For example, remove extra unbreakable space, especially before \cite.

@@
 
-\pacs{03.65.Ta, 03.67.-a, 02.50.Cw, 02.50.Le}
+\pacs{ % https://publishing.aip.org/publishing/pacs/pacs-2010-regular-edition
+03.65.Ta, % Foundations of quantum mechanics; measurement theory 
+03.67.-a, % Quantum information
+02.50.Cw, % Probability theory
+02.50.Le} % Decision theory and game theory
 
@@
 mechanics regarding the tension between finite precision measurement
-and contextuality~\cite{Peres2003,BarrettKent2004}.  For example,
-Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree
+and contextuality \cite{Peres2003,BarrettKent2004}.  For example,
+Meyer \cite{PhysRevLett.83.3751} and Mermin \cite{Mermin1999} disagree
 on whether finite-precision measurement invalidate the Kochen-Specker
-theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion
+theorem \cite{kochenspecker1967,peres1995quantum}, and discussion
 continues on whether contextuality is experimentally
-verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
+verifiable \cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
 fundamental question is how to make mathematical theories of quantum
@@
 measurement, attempted previously with computable number
-systems~\cite{usat,geometry2013,DQT2014}, may be achievable by
+systems \cite{usat,geometry2013,DQT2014}, may be achievable by
 extending classical interval-valued probability
-measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by
+measures \cite{JamisonLodwick2004} to the quantum domain.  We begin by
 axiomatizing a quantum interval-valued probability measure (QIVPM)
@@
 probability
-measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
+measures \cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
 One result is that the expectation value of an observable with respect
@@
 quantum mechanics.  We then examine Gleason's
-theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
+theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
 Kochen-Specker theorem in the context of QIVPM's, and conclude
@@
 % affect the idealized quantum concept, e.g.,
-% contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
+% contextuality \cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
 % and the very foundation of quantum mechanics is still a problem. In
@@
 % not only a uniform framework to understand Gleason's
-% theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
+% theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
 % Kochen-Specker
-% theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
+% theorem \cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
 % but also some examples which cannot be explained by the Born
-% rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+% rule \cite{Born1983,peres1995quantum,544199,Jaeger2007}.
 
@@
 % contextuality based on infinitely precise numbers is proved not
-% experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.  After a
-% long debate~\cite{Mermin1999,Peres2003,BarrettKent2004}, people are
+% experimental verifiable \cite{PhysRevLett.83.3751,Kent1999}.  After a
+% long debate \cite{Mermin1999,Peres2003,BarrettKent2004}, people are
 % still trying to update the definition of contextuality when they want
 % to perform further
-% experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+% experiments \cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
@@
 % which are proved by Gleason to be the essentially same as a density
-% matrix~\cite{Varadarajan2008}.  Combining quantum probability measures
-% and the classical IVPM~\cite{JamisonLodwick2004} which could be used
+% matrix \cite{Varadarajan2008}.  Combining quantum probability measures
+% and the classical IVPM \cite{JamisonLodwick2004} which could be used
 % to formulate classical finite precision measurement, we can define
@@
 the necessary conditions for reasoning coherently about collections of
-uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the
+uncertain events \cite{Kolmogorov1950}.  In the quantum case, the
 events of interests are the \emph{projection operators} $P$. This set
-includes the empty projection~$\mathbb{0}$, the identity
-projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
+includes the empty projection $\mathbb{0}$, the identity
+projection $\mathbb{1}$, projections of the form $\proj{\psi}$ where
 $\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
@@
 well-defined quantum probability
-space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
+space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
 each event $P_i$ is associated with a probability $\mu(P_i)$ subject
@@
 % $\mathbf{O}$ of a physical system whose state is represented by a
-% density matrix~$\rho$, the probability to obtain the value $\lambda$
+% density matrix $\rho$, the probability to obtain the value $\lambda$
 % of that property is determined by the Born rule
@@
 % Hermitian operator
-% $\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+% $\mathbf{O}$ \cite{Born1983,peres1995quantum,544199,Jaeger2007}.
 % Alternatively, one may say that the state $\rho$ determines the
@@
 % from the set $\events$ of all possible projectors $P$ onto the
-% interval $[0,1]$, and satisfies the following probability axioms~
+% interval $[0,1]$, and satisfies the following probability axioms 
 % \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:
@@
 % \end{itemize}
-% Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
+% Conversely, given any quantum probability measure $\mu:\events\rightarrow[0,1]$
 % satisfying the above axioms, Gleason's theorem asserts that there
-% exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
-% in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+% exists a unique state $\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
+% in a Hilbert space of dimension $d\geq3$ \cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 
-% Furthermore, if we express an observable~$\mathbf{O}$ as its spectrum
-% decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
-% value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
+% Furthermore, if we express an observable $\mathbf{O}$ as its spectrum
+% decomposition $\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
+% value of $\mathbf{O}$ is given by \cite{peres1995quantum,544199,Jaeger2007}
 % \begin{equation}
@@
 % introduce the notion of quantum interval-valued probability measures
-% (\emph{IVPMs})~$\bar{\mu}$. The latter replaces the infinitely precise
+% (\emph{IVPMs}) $\bar{\mu}$. The latter replaces the infinitely precise
 % interval $[0,1]$ by a finite collection $\mathscr{I}$ of
@@
 resources. Since the probabilities are now intervals, it is intuitive
-to say a state~$\rho$ is consistent with $\bar{\mu}$ on a projector~$P$
+to say a state $\rho$ is consistent with $\bar{\mu}$ on a projector $P$
 if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
@@
 three intervals $\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
-where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
-\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
+where $\left[0,0\right]$ and $\left[1,1\right]$ are called $\imposs$ and
+$\necess$ as before, and \emph{$\left[0,1\right]$} is called $\unknown$ because
 it provides no information. Then,
@@
 
-Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} when
+Quantum IVPMs become classical IVPMs \cite{JamisonLodwick2004} when
 the space of events includes only mutually commuting sub-events, where
@@
 \item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
-\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
-\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
+\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
 we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
@@
 is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
-$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
+$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM $\bar{\mu}_{2}$:
 \begin{equation}
@@
 \end{equation}
-If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
+If we identify the density matrices $\proj{0}$ and $\proj{1}$ as
 the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
@@
 she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
-state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
-coin with probability~$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
+state $p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
+coin with probability $p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
 is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
@@
 $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
-where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
+where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$ \cite{Griffiths2003}.
 \end{definition}
 
-Based on Shapley's classical result~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
+Based on Shapley's classical result \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
 we have the following theorem.
 
-\begin{thm}\label{thm:Shapley}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
+\begin{thm}\label{thm:Shapley}For every convex quantum IVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$,
+if a sub-event space $\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
 
-Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+Consider a quantum IVPM $\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
 and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
@@
 where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+We can combine the classical Choquet integral \cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
 with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
@@
 
-\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
-decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
+\begin{definition}Given an observable $\mathbf{O}$ with its spectrum
+decomposition (\ref{eq:spectrum-decomposition}). A set of projectors $\events'\subseteq\events$
 is called a sub-event space induced by $\mathbf{O}$ if it is the
@@
 
-\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
+\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
+and any observable $\mathbf{O}$ inducing a sub-event space $\events'$,
 if $\bar{\mu}$ is convex, then
@@
 space. As the result, there may be no state consistent with a convex
-quantum IVPM on all projectors~$\events$.
+quantum IVPM on all projectors $\events$.
 
@@
 we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-for any mixed state~$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
+for any mixed state $\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
 Hence, $\rho$ is actually $\ket{2}$, the only pure state orthogonal
@@
 by using finer and finer intervals, it would be more and more likely
-that there is a state consistent with a quantum IVPM on all projectors~$\events$.
+that there is a state consistent with a quantum IVPM on all projectors $\events$.
 
@@
 IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
+is another one, corresponding to the Kochen-Specker theorem \cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
 We will use the essential idea of the Kochen-Specker theorem to prove
 there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
-Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
-We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
+Suppose there is a quantum IVPM $\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
+We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set $\left\{ \lambda\right\} $,
 where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
-multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
+multiplication of two singleton sets $\left\{ \lambda_{1}\right\} $
 and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
@@
 \end{equation}
-for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
+for any sequence of commuting observables $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
 
-Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
-these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+Since the expectation value $\expval{\cdot}_{\bar{\mu}}$ satisfying
+these two properties, the following observables \cite{Mermin1990Simple,peres1995quantum}:
 \begin{equation}
@@
 \end{equation}
-must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
+must have the the expectation value $\left\{ 1\right\} $ or $\left\{ -1\right\} $.
 In each row and column, operators commutes, and each operator is the
 product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
+Therefore, it is clear impossible to find a IVPM $\bar{\mu}$ such
 that 

### 2017-05-12 prop_letter.tex
prop_letter.tex Fix typos proposed in Andy's email...

@@
 \usepackage{verbatim}
-\usepackage{hyperref}
+\usepackage[backref=false]{hyperref}
 
@@
 
-\begin{abstract}
+\begin{abstract}~
 \begin{description}
@@
 \pacs{ % https://publishing.aip.org/publishing/pacs/pacs-2010-regular-edition
-03.65.Ta, % Foundations of quantum mechanics; measurement theory 
-03.67.-a, % Quantum information
-02.50.Cw, % Probability theory
-02.50.Le} % Decision theory and game theory
+03.65.Ta, 03.67.-a, 02.50.Cw, 02.50.Le}
 
@@
 Meyer \cite{PhysRevLett.83.3751} and Mermin \cite{Mermin1999} disagree
-on whether finite-precision measurement invalidate the Kochen-Specker
+on whether finite-precision measurements invalidate the Kochen-Specker
 theorem \cite{kochenspecker1967,peres1995quantum}, and discussion
@@
 measurement, attempted previously with computable number
-systems \cite{usat,geometry2013,DQT2014}, may be achievable by
+systems \cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
 extending classical interval-valued probability
@@
 uncertain events \cite{Kolmogorov1950}.  In the quantum case, the
-events of interests are the \emph{projection operators} $P$. This set
+events of interest are the \emph{projection operators} $P$. This set
 includes the empty projection $\mathbb{0}$, the identity
@@
 $(\ket{0}\pm\ket{2})/\sqrt{2}$. The expectation value of the observable
-is the first case is 1.5 and in the second it is 2.
+in the first case is 1.5 and in the second it is 2.
 
@@
 follows. First we fix a collection of intervals $\mathscr{I}$ that
-represent an abstraction of the available experimental resources. At
+represents an abstraction of the available experimental resources. At
 one extreme, infinitely precise resources would correspond to the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{apsrev4-1}
 \bibliography{prop}

### 2017-05-12 prop_letter.tex
conclusion

@@
 
+Foundational concepts in quantum mechanics, such as Gleason and
+Kochen-Specker theorems, rely in a very subtle way on the use of
+unbounded resources. By assuming infinitely precise measurements,
+these two insightful theorems underline two fundamental aspects of
+quantum mechanics. On the one hand, Gleason's result establishes a
+relationship between quantum states and probabilities uniquely defined
+by Born's rule, on the other, Kochen-Specker unveils a distinctive
+aspect of physical reality, the fact that it is contextual.  Our goal
+in this paper has been to analyze the physical consequences of a
+mathematical framework that allows for finite precision measurements
+by introducing the concept of quantum interval-valued probability. The
+latter incorporates uncertainty in the measurement results by defining
+fuzzy probability measures, and includes standard quantum measurement
+as the particular instance of sharp, infinitely precise, intervals.
+In addition, we showed how these two theorems emerge as limiting cases
+of this very same framework, thus connecting two seemingly unrelated
+aspects of quantum physics. Most importantly, we concluded that
+arbitrary finite precision measurement conditions nullify the main
+tenets of both theorems.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-05-13 prop_letter.tex
restructure a bit
question

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Fuzzy States}
+\section{Convexity}
+
+In the classical setting, IVPMs typically are equipped with additional
+conditions to ensure they are ``well-behaved.''
+
+Yu-Tsung: please construct an example with commuting events P0 and P1 such that:
+
+mu(P0 + P1 - P0P1) + mu(P0P1) = [x,y]
+mu(P0) + mu(P1) = [z,w]
+
+and [x,y] is NOT included in [z,w]
 
@@
 and any state is consistent with $\bar{\mu}_{1}$ on any projectors.
+
+Not specific to quantum; fuziness also in classical setting
 
@@
 \begin{definition}
-$\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
-$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
-where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$ \cite{Griffiths2003}.
+$\bar{\mu}$ is called convex~\cite{Griffiths2003}. if for all
+commuting $P_{0},P_{1}\in\events$, we have
+$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
 \end{definition}
@@
 if a sub-event space $\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Fuzzy Observables}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum States}
+\section{Fuzzy States}
 

### 2017-05-13 prop_letter.tex
prop_letter.tex \section{Fuzzy Measurements} Fix corresponding states...

--- 2017-05-12 prop_letter.tex
@@
 the first probability measure corresponds to the quantum system being
-in the state $(\ket{0}\pm\ket{1})/\sqrt{2}$ and the second corresponds
+in the state $(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second corresponds
 to the quantum system being in the state
-$(\ket{0}\pm\ket{2})/\sqrt{2}$. The expectation value of the observable
-in the first case is 1.5 and in the second it is 2.
+$(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where $|\alpha|=1$. The expectation value
+of the observable in the first case is 1.5 and in the second it is 2.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Fuzzy States}
+\section{Classical IVPMs}
 

### 2017-05-13 prop_letter.tex
Revert "prop_letter.tex Some formating updates. For example, remove extra"
This reverts commit e743a017237cf096dcd652930c2be3ce40598d7c.

# Conflicts:
#	prop_letter.tex

@@
 mechanics regarding the tension between finite precision measurement
-and contextuality \cite{Peres2003,BarrettKent2004}.  For example,
-Meyer \cite{PhysRevLett.83.3751} and Mermin \cite{Mermin1999} disagree
+and contextuality~\cite{Peres2003,BarrettKent2004}.  For example,
+Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree
 on whether finite-precision measurements invalidate the Kochen-Specker
-theorem \cite{kochenspecker1967,peres1995quantum}, and discussion
+theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion
 continues on whether contextuality is experimentally
-verifiable \cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
+verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
 fundamental question is how to make mathematical theories of quantum
@@
 measurement, attempted previously with computable number
-systems \cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
-extending classical interval-valued probability
-measures \cite{JamisonLodwick2004} to the quantum domain.  We begin by
+systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable byextending classical interval-valued probability
+measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by
 axiomatizing a quantum interval-valued probability measure (QIVPM)
@@
 probability
-measures \cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
+measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
 One result is that the expectation value of an observable with respect
@@
 quantum mechanics.  We then examine Gleason's
-theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
+theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
 Kochen-Specker theorem in the context of QIVPM's, and conclude
@@
 % affect the idealized quantum concept, e.g.,
-% contextuality \cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
+% contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
 % and the very foundation of quantum mechanics is still a problem. In
@@
 % not only a uniform framework to understand Gleason's
-% theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
+% theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
 % Kochen-Specker
-% theorem \cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
+% theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
 % but also some examples which cannot be explained by the Born
-% rule \cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+% rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
 
@@
 % contextuality based on infinitely precise numbers is proved not
-% experimental verifiable \cite{PhysRevLett.83.3751,Kent1999}.  After a
-% long debate \cite{Mermin1999,Peres2003,BarrettKent2004}, people are
+% experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.  After a
+% long debate~\cite{Mermin1999,Peres2003,BarrettKent2004}, people are
 % still trying to update the definition of contextuality when they want
 % to perform further
-% experiments \cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+% experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
@@
 % which are proved by Gleason to be the essentially same as a density
-% matrix \cite{Varadarajan2008}.  Combining quantum probability measures
-% and the classical IVPM \cite{JamisonLodwick2004} which could be used
+% matrix~\cite{Varadarajan2008}.  Combining quantum probability measures
+% and the classical IVPM~\cite{JamisonLodwick2004} which could be used
 % to formulate classical finite precision measurement, we can define
@@
 the necessary conditions for reasoning coherently about collections of
-uncertain events \cite{Kolmogorov1950}.  In the quantum case, the
+uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the
 events of interest are the \emph{projection operators} $P$. This set
-includes the empty projection $\mathbb{0}$, the identity
-projection $\mathbb{1}$, projections of the form $\proj{\psi}$ where
+includes the empty projection~$\mathbb{0}$, the identity
+projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
 $\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
@@
 well-defined quantum probability
-space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
+space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
 each event $P_i$ is associated with a probability $\mu(P_i)$ subject
@@
 % $\mathbf{O}$ of a physical system whose state is represented by a
-% density matrix $\rho$, the probability to obtain the value $\lambda$
+% density matrix~$\rho$, the probability to obtain the value $\lambda$
 % of that property is determined by the Born rule
@@
 % Hermitian operator
-% $\mathbf{O}$ \cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+% $\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
 % Alternatively, one may say that the state $\rho$ determines the
@@
 % from the set $\events$ of all possible projectors $P$ onto the
-% interval $[0,1]$, and satisfies the following probability axioms 
+% interval $[0,1]$, and satisfies the following probability axioms~
 % \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:
@@
 % \end{itemize}
-% Conversely, given any quantum probability measure $\mu:\events\rightarrow[0,1]$
+% Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
 % satisfying the above axioms, Gleason's theorem asserts that there
-% exists a unique state $\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
-% in a Hilbert space of dimension $d\geq3$ \cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+% exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
+% in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 
-% Furthermore, if we express an observable $\mathbf{O}$ as its spectrum
-% decomposition $\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
-% value of $\mathbf{O}$ is given by \cite{peres1995quantum,544199,Jaeger2007}
+% Furthermore, if we express an observable~$\mathbf{O}$ as its spectrum
+% decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
+% value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
 % \begin{equation}
@@
 % introduce the notion of quantum interval-valued probability measures
-% (\emph{IVPMs}) $\bar{\mu}$. The latter replaces the infinitely precise
+% (\emph{IVPMs})~$\bar{\mu}$. The latter replaces the infinitely precise
 % interval $[0,1]$ by a finite collection $\mathscr{I}$ of
@@
 resources. Since the probabilities are now intervals, it is intuitive
-to say a state $\rho$ is consistent with $\bar{\mu}$ on a projector $P$
+to say a state~$\rho$ is consistent with $\bar{\mu}$ on a projector~$P$
 if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
@@
 three intervals $\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
-where $\left[0,0\right]$ and $\left[1,1\right]$ are called $\imposs$ and
-$\necess$ as before, and \emph{$\left[0,1\right]$} is called $\unknown$ because
+where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
+\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
 it provides no information. Then,
@@
 
-Quantum IVPMs become classical IVPMs \cite{JamisonLodwick2004} when
-the space of events includes only mutually commuting sub-events, where
+Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} whenthe space of events includes only mutually commuting sub-events, where
 $\events'\subseteq\events$ is called a sub-event space if it satisfies
@@
 \item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
-\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
+\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
+\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
 we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
@@
 is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
-$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM $\bar{\mu}_{2}$:
+$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
 \begin{equation}
@@
 \end{equation}
-If we identify the density matrices $\proj{0}$ and $\proj{1}$ as
+If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
 the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
@@
 she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
-state $p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
-coin with probability $p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
+state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
+coin with probability~$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
 is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
@@
 $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
-where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$ \cite{Griffiths2003}.
+where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
 \end{definition}
 
-Based on Shapley's classical result \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
+Based on Shapley's classical result~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
 we have the following theorem.
 
-\begin{thm}\label{thm:Shapley}For every convex quantum IVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$,
-if a sub-event space $\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
+\begin{thm}\label{thm:Shapley}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
 
@@
 where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-We can combine the classical Choquet integral \cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
 with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
@@
 
-\begin{definition}Given an observable $\mathbf{O}$ with its spectrum
-decomposition (\ref{eq:spectrum-decomposition}). A set of projectors $\events'\subseteq\events$
+\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
+decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
 is called a sub-event space induced by $\mathbf{O}$ if it is the
@@
 
-\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
-and any observable $\mathbf{O}$ inducing a sub-event space $\events'$,
+\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
 if $\bar{\mu}$ is convex, then
@@
 space. As the result, there may be no state consistent with a convex
-quantum IVPM on all projectors $\events$.
+quantum IVPM on all projectors~$\events$.
 
@@
 we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-for any mixed state $\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
+for any mixed state~$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
 Hence, $\rho$ is actually $\ket{2}$, the only pure state orthogonal
@@
 by using finer and finer intervals, it would be more and more likely
-that there is a state consistent with a quantum IVPM on all projectors $\events$.
+that there is a state consistent with a quantum IVPM on all projectors~$\events$.
 
@@
 IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-is another one, corresponding to the Kochen-Specker theorem \cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
+is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
 We will use the essential idea of the Kochen-Specker theorem to prove
 there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
-Suppose there is a quantum IVPM $\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
-We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set $\left\{ \lambda\right\} $,
+Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
+We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
 where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
-multiplication of two singleton sets $\left\{ \lambda_{1}\right\} $
+multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
 and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
@@
 \end{equation}
-for any sequence of commuting observables $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
+for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
 
-Since the expectation value $\expval{\cdot}_{\bar{\mu}}$ satisfying
-these two properties, the following observables \cite{Mermin1990Simple,peres1995quantum}:
+Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
+these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
 \begin{equation}
@@
 \end{equation}
-must have the the expectation value $\left\{ 1\right\} $ or $\left\{ -1\right\} $.
+must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
 In each row and column, operators commutes, and each operator is the
 product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-Therefore, it is clear impossible to find a IVPM $\bar{\mu}$ such
+Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
 that 

### 2017-05-13 prop_letter.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Classical IVPMs}
+\section{Convexity}
+
+In the classical setting, IVPMs typically are equipped with additional
+conditions to ensure they are ``well-behaved.''
+
+Yu-Tsung: please construct an example with commuting events P0 and P1 such that:
+
+mu(P0 + P1 - P0P1) + mu(P0P1) = [x,y]
+mu(P0) + mu(P1) = [z,w]
+
+and [x,y] is NOT included in [z,w]
 
@@
 \begin{definition}
-$\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
-$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
-where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
+$\bar{\mu}$ is called convex~\cite{Griffiths2003}. if for all
+commuting $P_{0},P_{1}\in\events$, we have
+$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
 \end{definition}

### 2017-05-14 prop_letter.tex
questions

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Kochen-Specker}
+
+Our first result is that a QIVPM cannot be crypto-deterministic. We
+will use the proof of the Kochen-Specker
+theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
+to show that it is, in general, impossible to just have the two
+intervals \imposs\ and \necess: every QIVPM must be parameterized by a
+collection of intervals that includes at least one ``fuzzy'' interval
+and some events must be associated with these uncertain intervals.
+
+We will proceed by assuming a crypto-deterministic QIVMP $\bar{\mu}$
+and derive a contradiction using the following nine ``Mermin square''
+observables~\cite{Mermin1990Simple,peres1995quantum}:
+\begin{equation}
+\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
+\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
+\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
+\end{aligned}
+\label{eq:MerminSquare}
+\end{equation}
+
+\newpage
+
+Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
+We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
+where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
+multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
+and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
+then we have 
+\begin{equation}
+\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
+\end{equation}
+for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
+
+Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
+these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+\begin{equation}
+\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
+\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
+\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
+\end{aligned}
+\label{eq:MerminSquare}
+\end{equation}
+must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
+In each row and column, operators commutes, and each operator is the
+product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
+that 
+\begin{equation}
+\begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
+\langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
+\langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
+\end{aligned}
+\label{eq:MerminSquare-values}
+\end{equation}
+satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Convexity}
@@
 
-%%%
-\subsection{Kochen-Specker}
+% %%%
+% \subsection{Kochen-Specker}
 
-While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
-IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
-We will use the essential idea of the Kochen-Specker theorem to prove
-there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
-Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
-We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
-where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
-multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
-and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
-then we have 
-\begin{equation}
-\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
-\end{equation}
-for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
+% While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
+% IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
+% is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
+% We will use the essential idea of the Kochen-Specker theorem to prove
+% there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
+% Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
+% We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
+% where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
+% multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
+% and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
+% then we have 
+% \begin{equation}
+% \prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
+% \end{equation}
+% for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
 
-Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
-these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
-\begin{equation}
-\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
-\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
-\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
-\end{aligned}
-\label{eq:MerminSquare}
-\end{equation}
-must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
-In each row and column, operators commutes, and each operator is the
-product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
-that 
-\begin{equation}
-\begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
-\langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
-\langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
-\end{aligned}
-\label{eq:MerminSquare-values}
-\end{equation}
-satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
+% Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
+% these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+% \begin{equation}
+% \begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
+% \sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
+% \sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
+% \end{aligned}
+% \label{eq:MerminSquare}
+% \end{equation}
+% must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
+% In each row and column, operators commutes, and each operator is the
+% product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+% Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
+% that 
+% \begin{equation}
+% \begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
+% \langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
+% \langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
+% \end{aligned}
+% \label{eq:MerminSquare-values}
+% \end{equation}
+% satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
 

### 2017-05-15 prop_letter.tex
prop_letter.tex \section{Convexity} Added a comment...

--- 2017-05-13 prop_letter.tex
@@
 
-and [x,y] is NOT included in [z,w]
+and $[x,y]$ is NOT included in $[z,w]$
+
+\yutsung{{Consider a four dimensional Hilbert space with an orthonormal
+basis}~$\Omega=\{\ket{0},\ket{1},\ket{2},\ket{3}\}$, and the commuting
+sub-event space~$\events'=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$.
+Then, $\bar{\mu}_{0}:\events'\rightarrow\mathscr{I}$ defined by\begin{subequations}
+\begin{eqnarray}
+ &  & \imposs=\bar{\mu}_{0}(\mathbb{0})\textrm{ ,}\\
+ &  & \necess=\bar{\mu}_{0}(\mathbb{1})\textrm{ ,}\\
+ &  & \begin{aligned}\unlikely & =\bar{\mu}_{0}(\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{1})\\
+ & =\bar{\mu}_{0}(\proj{0}+\proj{2})\\
+ & =\bar{\mu}_{0}(\proj{1}+\proj{2})\textrm{ ,}
+\end{aligned}
+\\
+ &  & \begin{aligned}\likely & =\bar{\mu}_{0}(\mathbb{1}-\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{2})\\
+ & =\bar{\mu}_{0}(\proj{1}+\proj{3})\\
+ & =\bar{\mu}_{0}(\proj{2}+\proj{3})
+\end{aligned}
+\end{eqnarray}
+\end{subequations}is an IVPM, where $\ket{j}\in\Omega$ and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
+However, $\bar{\mu}_{0}$ is not convex because
+\begin{equation}
+\begin{aligned} & \bar{\mu}_{0}(\proj{0})+\bar{\mu}_{0}(\mathbb{1}-\proj{3})\\
+= & \left[\frac{1}{2},\frac{3}{2}\right]\nsubseteq\left[1,2\right]\\
+= & \bar{\mu}_{0}(\proj{0}+\proj{1})+\bar{\mu}_{0}(\proj{0}+\proj{2})\textrm{ .}
+\end{aligned}
+\end{equation}
+}
 

### 2017-05-15 prop_letter.tex
small fixes

@@
 uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the
-events of interest are the \emph{projection operators} $P$. This set
-includes the empty projection~$\mathbb{0}$, the identity
-projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
-$\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
-projections, and products of \emph{commuting} projections. In a
-well-defined quantum probability
+events of interest are specified by \emph{projection operators}
+$P$. This set $P$ includes the empty projection~$\mathbb{0}$, the
+identity projection~$\mathbb{1}$, projections of the form
+$\proj{\psi}$ where $\ket{\psi}$ is a pure quantum state, sums of
+\emph{orthogonal} projections, and products of \emph{commuting}
+projections. In a well-defined quantum probability
 space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
@@
 with spectral decomposition $\proj{0} + 2\,\proj{1} +
-3\,\proj{2}$. Here are two fragments of valid probability measures
-$\mu_1$ and $\mu_2$ that can associated with this space:
-$\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
-$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0.5$,
-$\mu_2(\proj{1}) = 0$, $\mu_2(\proj{2}) = 0.5$. By the Born rule,
-the first probability measure corresponds to the quantum system being
-in the state $(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second corresponds
-to the quantum system being in the state
-$(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where $|\alpha|=1$. The expectation value
-of the observable in the first case is 1.5 and in the second it is 2.
+3\,\proj{2}$. Two fragments of valid probability measures $\mu_1$ and
+$\mu_2$ that can associated with this space: $\mu_1(\proj{0}) = 0.5$,
+$\mu_1(\proj{1}) = 0.5$, $\mu_1(\proj{2}) = 0$, and
+$\mu_2(\proj{0}) = 0.5$, $\mu_2(\proj{1}) = 0$,
+$\mu_2(\proj{2}) = 0.5$. By the Born rule, the first probability
+measure corresponds to the quantum system being in the state
+$(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second corresponds to the
+quantum system being in the state $(\ket{0}+\alpha\ket{2})/\sqrt{2}$,
+where $|\alpha|=1$. The expectation value of the observable in the
+first case is 1.5 and in the second it is 2.
 
@@
 coincide with the idealized situation above. At another extreme, an
-experiment with \emph{no} resources would correspond to the following
-three intervals $\imposs=\left[0,0\right]$,
+experiment with ``minimal'' resources would correspond to the
+following three intervals $\imposs=\left[0,0\right]$,
 $\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
@@
 event. Intuitively, consider an event $P$ and its complement
-$\mathbb{1}-P$. Looking at each separately we may discover
-$\bar{\mu}(P) = [0.2,0.3]$ and $\bar{\mu}(\mathbb{1}-P)=[0.7,0.8]$. By
-adding the individual intervals, we predict the probability of the
-composite event $P+(\mathbb{1}-P)$ to be in the range
+$\mathbb{1}-P$. Looking at each separately we may discover as a result
+of an experiment that $\bar{\mu}(P) = [0.2,0.3]$ and
+$\bar{\mu}(\mathbb{1}-P)=[0.7,0.8]$. By adding the individual
+intervals, we predict the probability of the composite event
+$P+(\mathbb{1}-P)$ to be in the range
 $[0.9,1.1]$. Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}
@@
 
+\amr{does the following rely on convexity?}
+
 \newpage
@@
 
+\amr{
 Yu-Tsung: please construct an example with commuting events P0 and P1 such that:
@@
 and $[x,y]$ is NOT included in $[z,w]$
+}
 

### 2017-05-16 prop_letter.tex
prop_letter.tex Add some comments...

@@
 
-Our first observation is that essential objectives of our program to
-achieve a computable theory of quantum mechanics and finite-resource
-measurement, attempted previously with computable number
-systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable byextending classical interval-valued probability
-measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by
-axiomatizing a quantum interval-valued probability measure (QIVPM)
+Our first observation is that essential objectives of our program
+to achieve a computable theory of quantum mechanics and finite-resource
+measurement, attempted previously with computable number systems~\cite{usat,geometry2013apsrev4,DQT2014},
+may be achievable by extending classical interval-valued probability
+measures~\cite{JamisonLodwick2004} to the quantum domain. We begin
+by axiomatizing a quantum interval-valued probability measure (QIVPM)
 framework exploiting the fact that a density matrix approach can be
 considered as equivalent to a description of quantum states using
-probability
-measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
+probability measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
 One result is that the expectation value of an observable with respect
-to a QIVPM can be defined to be consistent with the constraints on the
-expectation value of the same observable expected from continuous
-quantum mechanics.  We then examine Gleason's
-theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
-Kochen-Specker theorem in the context of QIVPM's, and conclude
+to a QIVPM can be defined to be consistent with the constraints on
+the expectation value of the same observable expected from continuous
+quantum mechanics. We then examine Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
+and the Kochen-Specker theorem in the context of QIVPM's, and conclude
 that they correspond to the limit of an infinite number of precise
-intervals, and the set of crypto-deterministic intervals (the set
-$\{\imposs,\necess\}$), respectively.
+intervals, and the set of crypto-deterministic intervals (the set~$\{\imposs,\necess\}$),
+respectively.
 
@@
 A \emph{probability space} is a mathematical abstraction specifying
-the necessary conditions for reasoning coherently about collections of
-uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the
-events of interest are specified by \emph{projection operators}
-$P$. This set $P$ includes the empty projection~$\mathbb{0}$, the
-identity projection~$\mathbb{1}$, projections of the form
-$\proj{\psi}$ where $\ket{\psi}$ is a pure quantum state, sums of
-\emph{orthogonal} projections, and products of \emph{commuting}
-projections. In a well-defined quantum probability
-space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
-each event $P_i$ is associated with a probability $\mu(P_i)$ subject
-to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
-$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set of
-mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$, we
-have:
+the necessary conditions for reasoning coherently about collections
+of uncertain events~\cite{Kolmogorov1950}. In the quantum case,
+the events of interest are specified by \emph{projection operators}
+$P$. This set $P$ includes the empty projection~$\mathbb{0}$,
+the identity projection~$\mathbb{1}$, projections of the form $\proj{\psi}$
+where $\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
+projections, and products of \emph{commuting} projections. In a well-defined
+quantum probability space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
+each event $P_{i}$ is associated with a probability $\mu(P_{i})$
+subject to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
+$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set
+of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have: 
 \begin{equation}
-\mu\left(\sum_{i=1}^{N}P_{i}\right)=
-\sum_{i=1}^{N}\mu\left(P_{i}\right)
-\textrm{ .}\label{eq:QuantumProbability-Addition}
+\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
 \end{equation}
+\yutsung{Should we define orthogonality between projectors? Also,
+in order to compare the Eq.~\ref{eq:QuantumProbability-Addition}
+and convexity in definition~\ref{def:convex}, maybe it's better
+to write just two terms 
+\begin{equation}
+\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\textrm{ .}\label{eq:QuantumProbability-Addition-1}
+\end{equation}
+}
 
@@
 
-To adapt the axioms of such IVPMs to the quantum case, we proceed as
-follows. First we fix a collection of intervals $\mathscr{I}$ that
-represents an abstraction of the available experimental resources. At
-one extreme, infinitely precise resources would correspond to the
-collection of intervals $\{[x,x] \mid x \in [0,1]\}$. This case should
+To adapt the axioms of such IVPMs to the quantum case, we proceed
+as follows. First we fix a collection of intervals $\mathscr{I}$
+that represents an abstraction of the available experimental resources.
+At one extreme, infinitely precise resources would correspond to the
+collection of intervals $\{[x,x]\mid x\in[0,1]\}$. This case should
 coincide with the idealized situation above. At another extreme, an
-experiment with ``minimal'' resources would correspond to the
-following three intervals $\imposs=\left[0,0\right]$,
-$\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
-two intervals are associated with the empty projection and the
-identity projection but every other projection would be associated
-with $\unknown$; its probability can be anything in the range
-$[0,1]$. A third special situation would be to consider IVPMs with
-only the two intervals $\imposs=\left[0,0\right]$ and
-$\necess=\left[1,1\right]$. This is what Peres calls the
-\emph{crypto-deterministic} case in which there is no ambiguity about
-the status of any event; we know for certain if it will occur or not.
+experiment with ``minimal'' resources would correspond to the following
+three intervals $\imposs=\left[0,0\right]$, $\necess=\left[1,1\right]$,
+and $\unknown=[0,1]$. As before, the first two intervals are associated
+with the empty projection and the identity projection, but every other
+projection would be associated with $\unknown$; its probability can
+be anything in the range $[0,1]$. A third special situation would
+be to consider IVPMs with only the two intervals $\imposs=\left[0,0\right]$
+and $\necess=\left[1,1\right]$. This is what Peres calls the \emph{crypto-deterministic}
+case~\cite{PeresRon1988,peres1995quantum} in which there is no ambiguity
+about the status of any event; we know for certain if it will occur
+or not.
 
@@
 
-\begin{definition}
-$\bar{\mu}$ is called convex~\cite{Griffiths2003}. if for all
-commuting $P_{0},P_{1}\in\events$, we have
-$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
+\begin{definition}\label{def:convex}$\bar{\mu}$ is called convex~\cite{Griffiths2003}
+if for all commuting $P_{0},P_{1}\in\events$, we have $\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
 \end{definition}

### 2017-05-16 prop_letter.tex
major reorganization

--- 2017-05-15 prop_letter.tex
@@
 measurement, attempted previously with computable number
-systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable byextending classical interval-valued probability
+systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
+extending classical interval-valued probability
 measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by
@@
 theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
-Kochen-Specker theorem in the context of QIVPM's, and conclude
-that they correspond to the limit of an infinite number of precise
+Kochen-Specker theorem in the context of QIVPM's, and conclude that
+they correspond to the limit of an infinite number of precise
 intervals, and the set of crypto-deterministic intervals (the set
@@
 3\,\proj{2}$. Two fragments of valid probability measures $\mu_1$ and
-$\mu_2$ that can associated with this space: $\mu_1(\proj{0}) = 0.5$,
-$\mu_1(\proj{1}) = 0.5$, $\mu_1(\proj{2}) = 0$, and
-$\mu_2(\proj{0}) = 0.5$, $\mu_2(\proj{1}) = 0$,
-$\mu_2(\proj{2}) = 0.5$. By the Born rule, the first probability
-measure corresponds to the quantum system being in the state
-$(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second corresponds to the
-quantum system being in the state $(\ket{0}+\alpha\ket{2})/\sqrt{2}$,
-where $|\alpha|=1$. The expectation value of the observable in the
-first case is 1.5 and in the second it is 2.
+$\mu_2$ that can associated with this space are:
+$\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
+$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0.5$,
+$\mu_2(\proj{1}) = 0$, $\mu_2(\proj{2}) = 0.5$. By the Born rule, the
+first probability measure corresponds to the quantum system being in a
+state $(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second corresponds to
+the quantum system being in the state
+$(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where in both cases
+$|\alpha|=1$. The expectation value of the observable in the first
+case is 1.5 and in the second it is 2.
 
@@
 experimenter might only be able to determine that the probability of
-the event $\proj{0}$ is in the range $[0.49,0.51]$. The spread in this
-range depends on the amount of resources (time, energy, money, etc)
-that are devoted to the experiment. In the classical setting, this
-``fuzziness'' is formalized by moving to \emph{interval-valued
-  probability measures}.
-
-To adapt the axioms of such IVPMs to the quantum case, we proceed as
-follows. First we fix a collection of intervals $\mathscr{I}$ that
-represents an abstraction of the available experimental resources. At
-one extreme, infinitely precise resources would correspond to the
-collection of intervals $\{[x,x] \mid x \in [0,1]\}$. This case should
-coincide with the idealized situation above. At another extreme, an
-experiment with ``minimal'' resources would correspond to the
-following three intervals $\imposs=\left[0,0\right]$,
-$\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
-two intervals are associated with the empty projection and the
-identity projection but every other projection would be associated
-with $\unknown$; its probability can be anything in the range
-$[0,1]$. A third special situation would be to consider IVPMs with
-only the two intervals $\imposs=\left[0,0\right]$ and
-$\necess=\left[1,1\right]$. This is what Peres calls the
-\emph{crypto-deterministic} case in which there is no ambiguity about
-the status of any event; we know for certain if it will occur or not.
-
-Given a collection of intervals $\mathscr{I}$ with addition and scalar
-multiplication defined as follows: 
-\begin{subequations}\label{eq:interval-operations}
-\begin{eqnarray}
- &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
- &  & x[l,r]=\begin{cases}
-[xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
-[xr,xl] & \textrm{for }x\le0\textrm{ ,}
-\end{cases}
-\end{eqnarray}
-\end{subequations}
-a QIVPM $\bar{\mu}$ is an assignment of intervals to each event
-obeying the following axioms:
-$\bar{\mu}(\mathbb{0})=\imposs=\left[0,0\right]$,
-$\bar{\mu}(\mathbb{1})=\necess=\left[1,1\right]$,
-$\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
-and for a set of mutually orthogonal projections
-$\left\{ P_{i}\right\} _{i=1}^{N}$, we have:
-\begin{equation}
-\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion}
-\end{equation}
-The first three axioms are the direct counterpart of the corresponding
-axioms for conventional probability measures. The last condition
-allows for the interval associated with a composite event to be
-sharper than the interval calculated from each individual
-event. Intuitively, consider an event $P$ and its complement
-$\mathbb{1}-P$. Looking at each separately we may discover as a result
-of an experiment that $\bar{\mu}(P) = [0.2,0.3]$ and
-$\bar{\mu}(\mathbb{1}-P)=[0.7,0.8]$. By adding the individual
-intervals, we predict the probability of the composite event
-$P+(\mathbb{1}-P)$ to be in the range
-$[0.9,1.1]$. Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}
-allows us to refine this to $[1,1]$ by recognizing that the composite
-event is the identity projection.
+the event $\proj{0}$ is in the range $[0.49,0.51]$ instead of
+precisely 0.5. The spread in this range depends on the amount of
+resources (time, energy, money, etc) that are devoted to the
+experiment. In the classical setting, this ``fuzziness'' is formalized
+by moving to \emph{interval-valued probability measures}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Intervals of Uncertainty}
+
+We will start by reviewing IVPMs in the classical
+setting~\cite{JamisonLodwick2004} and then propose our quantum
+framework. In the classical setting, there are several proposals for
+``imprecise probabilities.'' Although these proposals differ in some
+details, they all share the fact that the probability $\mu(E)$ of an
+event $E$ is generalized from a single real number to an interval of
+certainty $[\ell,r]$ where~$\ell$ intuitively corresponds to the
+strength of evidence for the event and $r$ corresponds to the strength
+of evidence against the event. The collection of intervals used in the
+definition of a probability measure must satisfy certain properties
+which we explain next.
+
+First for each interval $[\ell,r]$ we have the natural constraint
+$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
+interval can be interpreted as a conventional probability. We also
+include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
+refer to the probability of impossible events (e.g., the null event)
+and certain events (e.g., the event covering the entire space). For
+each interval $[\ell,r]$, we also need the interval $[1-r,1-\ell]$ so
+that if one interval refers to the probability of an event, the other
+refers to the probability of the complement event. For example, if we
+discover as a result of an experiment that $\mu(E) = [0.2,0.3]$ for
+some event $E$, we may conclude that $\mu(\overline{E}) = [0.7,0.8]$
+for the complement event $\overline{E}$. In addition to these simple
+conditions, there are some subtle conditions on how intervals are
+combined, which we discuss next.
+
+Let $E_1$ and $E_2$ be to disjoint events with probabilities
+$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
+at calculating the probability of the combined event that $E_1$ or
+$E_2$ occurs might be $\mu(E_1+E_2) = [\ell_1+\ell_2,r_1+r_2]$. In
+some cases, this is indeed a sensible definition. For example, if
+$\mu(E_1)=[0.1,0.2]$ and $\mu(E_2)=[0.3,0.4]$ we get
+$\mu(E_1+E_2) = [0.4,0.6]$. But consider an event $E$ such that
+$\mu(E)=[0.2,0.3]$ and hence $\mu(\overline{E})=[0.7,0.8]$. The two
+events are disjoint; the previous na\"\i ve way of combining the
+intervals would give $\mu(E+\overline(E))=[0.9,1.1]$ which is not a
+valid probability interval. Moreover the event $E+\overline{E}$ is the
+identity event covering the entire space; its probability interval
+should be $[1,1]$ which is sharper than $[0.9,1.1]$. The problem is
+that the two intervals are correlated: there is more information in
+the combined event than in each event separately. In our example, even
+though the true probability of $\mu(E)$ can be in anywhere in the
+range $[0.2,0.3]$ and the true probability of $\mu(\overline{E})$ can
+be in anywhere in the range $[0.7,0.8]$, the values are not
+independent. Any value of $\mu(E) \leq 0.25$ will force
+$\mu(\overline{E})\geq 0.75$. To account for such subtleties, the
+axioms of interval-valued probability do not use a strict equality for
+the combination of disjoint events. The correct constraint regarding
+the probability of $E_1+E_2$ when $E_1$ and $E_2$ are disjoint is
+$\mu(E_1+E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in combination
+with the requirement for the identity event would force
+$\mu(E+\overline{E})$ to always be $[1,1]$ irrespective of the
+particular assignments of $\mu(E)$ or $\mu(\overline{E})$. When
+combining non-disjoint events, there is a further subtlety whose
+resolution will give the most general and final condition as
+follows. For general, non-necessarily disjoint events $E_1$ and $E_2$,
+we have:
+\begin{equation}
+\mu(E_1+E_2) + \mu(E_1E_2) \subseteq \mu(E_1) + \mu(E_2)
+\label{eq:classicalconvex}
+\end{equation}
+which is a generalization of the classical inclusion-exclusion
+principle that uses $\subseteq$ instead of $=$ for the same reason as
+before. The new condition reduces to the previously motivated
+condition when the events are disjoint, i.e., when $\mu(E_1E_2) = 0$.
+
+We now have the necessary ingredients to define QIVPMs as a
+generalization of the above observations. More precisely the quantum
+definition will reduce to the classical one when the space of quantum
+events is restricted to mutually commuting sub-events.
+
+\begin{definition}[QIVPM]
+  Given a collection of intervals $\mathscr{I}$ including
+  $\imposs=[0,0]$ and $\necess=[1,1]$ and with addition and scalar
+  multiplication defined as follows:
+  \begin{subequations}\label{eq:interval-operations}
+  \begin{eqnarray}
+   &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
+   &  & x[l,r]=\begin{cases}
+  [xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
+  [xr,xl] & \textrm{for }x\le0\textrm{ ,}
+  \end{cases}
+  \end{eqnarray}
+  \end{subequations}
+  a QIVPM $\bar{\mu}$ is an assignment of intervals to each event
+  (projection operator) obeying the following axioms:
+  $\bar{\mu}(\mathbb{0})=\imposs=\left[0,0\right]$,
+  $\bar{\mu}(\mathbb{1})=\necess=\left[1,1\right]$,
+  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
+  and for each pair of \emph{commuting} projections $P_0$ and $P_1$,
+  we have:
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
+\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\end{equation}
+\end{definition}
+The first three axioms are the direct counterpart of the corresponding
+axioms for conventional probability measures. With the understanding
+that the union of classical sets $E_1+E_2$ is replaced by
+$P_0+P_1-P_0P_1$ in the case of projection operators, the last
+condition, Eq~\ref{eq:QuantumInterval-valuedProbability-Inclusion},
+is a direct counterpart of Eq.~\ref{eq:classicalconvex}.
+
+Quantum IVPMs become classical IVPMs when the space of events includes
+only mutually commuting sub-events, where $\events'\subseteq\events$
+is called a sub-event space if it satisfies the following conditions.
+\begin{itemize}
+\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
+\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
+\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
+we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
+\end{itemize}
+
+For example, assuming the three intervals $\imposs$, $\necess$, and
+$\unknown=\left[0,1\right]$, then:
+\begin{equation}
+\bar{\mu}_{1}\left(P\right)=\begin{cases}
+\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
+\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
+\unknown & \text{, otherwise,}
+\end{cases}\label{eq:no-information-IVPM}
+\end{equation}
+is a quantum IVPM. This measure represents the beliefs of an
+experimenter with no prior knowledge about the particular quantum
+system in question, and any state is consistent with $\bar{\mu}_{1}$
+on any projectors. We have that
+$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
+is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on
+$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
+IVPM~$\bar{\mu}_{2}$:
+\begin{equation}
+\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
+\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
+\end{aligned}
+\end{equation}
+If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
+the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
+represents that an experimenter knows nothing about a coin before
+she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
+state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
+coin with probability~$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
+is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
+classical coin should be consistent with the situation where an experimenter
+has no prior knowledge.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Kochen-Specker}
 
-Our first result is that a QIVPM cannot be crypto-deterministic. We
-will use the proof of the Kochen-Specker
+Our first result regarding QIVPM is that a QIVPM cannot be
+crypto-deterministic in the sense of Peres. We will use the proof of
+the Kochen-Specker
 theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
@@
 intervals \imposs\ and \necess: every QIVPM must be parameterized by a
-collection of intervals that includes at least one ``fuzzy'' interval
-and some events must be associated with these uncertain intervals.
+collection of intervals that includes at least one additional
+``fuzzy'' interval and some events must be associated with such
+uncertain intervals. The significance of this observation is that the
+uncertainty in the intervals is, in contrast to the classical case,
+\emph{a fundamental part of quantum theory}. There is in fact two
+sources of imprecision: one due to the finite measurement resources
+and one due to complementarity which requires every QIVPM to be truly
+probabilistic.
 
@@
 
-\amr{does the following rely on convexity?}
+The argument refers to the expectation value of these
+observables. In the case of QIVPM this is defined as follows.
 
-\newpage
+\begin{definition} Given an observable~$\mathbf{O}$ with spectral
+  decomposition
+  $\mathbf{O}=\sum_{s\in\left\{ +,-\right\}
+  }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}$, a set of
+  projectors~$\events'\subseteq\events$ is called a sub-event space
+  induced by $\mathbf{O}$ if it is the minimal sub-event space
+  containing
+  $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{
+    P_{i}^{+}\right\} _{i=1}^{N^{+}}$.
+\end{definition}
 
-Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
-We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
-where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
+\begin{thm} Given a Hilbert space of $d\ge3$, for every
+  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and any
+  observable~$\mathbf{O}$ inducing a sub-event space~$\events'$, 
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
+\end{equation}
+\end{thm}
+
+The expectation value is intuitively between two possible outcomes
+which lie between the minimum and maximum bounds of the given
+probability intervals. If the QIVPM is crypto-deterministic, this
+interval collapses to a singleton $\left\{ \lambda\right\} $, where
+$\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
 multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
-and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
-then we have 
+and $\left\{ \lambda_{2}\right\} $ to be
+$\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Convexity}
+\newpage  
+\section{Rest of Paper}
+
+ To adapt the axioms of such IVPMs to the quantum case, we proceed as
+follows. First we fix a collection of intervals $\mathscr{I}$ that
+represents an abstraction of the available experimental resources. At
+one extreme, infinitely precise resources would correspond to the
+collection of intervals $\{[x,x] \mid x \in [0,1]\}$. This case should
+coincide with the idealized situation above. At another extreme, an
+experiment with ``minimal'' resources would correspond to the
+following three intervals $\imposs=\left[0,0\right]$,
+$\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
+two intervals are associated with the empty projection and the
+identity projection but every other projection would be associated
+with $\unknown$; its probability can be anything in the range
+$[0,1]$. A third special situation would be to consider IVPMs with
+only the two intervals $\imposs=\left[0,0\right]$ and
+$\necess=\left[1,1\right]$. This is what Peres calls the
+\emph{crypto-deterministic} case in which there is no ambiguity about
+the status of any event; we know for certain if it will occur or not.
+
+ In general, measurements done with limited resources and poor precision
+may not uniquely identify the true state of a classical system. However,
+at least one system is consistent with the measurements when the system
+satisfies an extra-condition called convex.
+
+\begin{definition}
+$\bar{\mu}$ is called convex~\cite{Griffiths2003}. if for all
+commuting $P_{0},P_{1}\in\events$, we have
+$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
+\end{definition}
+
+Based on Shapley's classical result~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
+we have the following theorem.
+
+\begin{thm}\label{thm:Shapley}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
+
+Consider again
+Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}. We will
+generalize it as follows for all commuting $P_{0},P_{1}\in\events$, we
+have
+$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$. Note
+that if $P_0$ and $P_1$ are \emph{orthogonal}, i.e., if $P_0P_1=0$ the
+new equation reduces to
+Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}.
+
+\begin{verbatim}
+Inclusion exclusion principle 
+ pr(e1 union e2) + pr (e1 intersect e2) = 
+  pr(e1) + pr(e2)
+
+in classical Real number prob. LHS = X; RHS = X
+
+---
+
+in classical IVPM; we only get LHS <= X; RHS <= X
+but we have no connection between LHS and RHS
+
+convexity imposes that LHS >= RHS
+
+---
+
+our condition in the quantum case is the same; 
+our left(LHS) is >= left(RHS); the right is dual, 
+which makes LHS interval subset RHS interval.
+
+--
+
+replace set union by projection sum = p0 + p1 - p0p1
+replace = by subseteq
+
+and we get convexity definition
+
+--
+
+Now we need a simple classical example that shows 
+why we need convexity or at least what it means
+
+must be dimension 4 because everything of dim 3 
+is convex in classical case
+
+Consider omega = { 0, 1, 2, 3 }
+intervals = imposssible, certain, 
+            unlikely = [0,0.5], likely [0.5,1]
+
+mu(empty) = imposs
+mu(omega) = certain
+mu({j}) = unlikely
+mu(Omega \ {j}) = likely
+mu({0,1}) = mu({0,2}) = mu({1,2}) = unlikely
+mu({0,3}) = mu({1,3}) = mu({2,3}) = likely
+
+EQ A:
+mu({0}) + mu({0,1,2}) = [0.5,1.5]
+mu({0,1}) + mu({0,2}) = [0,1]
+
+AND [0.5,1.5] is not subseteq of [0,1]
+
+Note that there is a core p(0) = p(1) = p(2) = 0.2, 
+p(3) = 0.4, and under that core both sides of EQ A 
+have prob. 0.8. So one way to make it convex is 
+to use very precise intervals [0.2,0.2] etc.
+
+Another way to make this convex is by choosing 
+just one additional interval unknown [0,1] 
+instead of unlikely and likely.
+
+Intuition: the more you group the more 
+precise you get
+
+\end{verbatim}
 
@@
 is consistent with $\bar{\mu}$ on every projector in $S$.
-
-Since our measurement is fuzzy, generally there are more than one
-state consistent with a particular quantum IVPM. For example, consider
-three intervals $\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
-where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
-\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
-it provides no information. Then,
-\begin{equation}
-\bar{\mu}_{1}\left(P\right)=\begin{cases}
-\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
-\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
-\unknown & \text{, otherwise,}
-\end{cases}\label{eq:no-information-IVPM}
-\end{equation}
-is a quantum IVPM. This measure represents the beliefs of an experimenter
-with no prior knowledge about the particular quantum system in question,
-and any state is consistent with $\bar{\mu}_{1}$ on any projectors.
-
-Not specific to quantum; fuziness also in classical setting
-
-Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} whenthe space of events includes only mutually commuting sub-events, where
-$\events'\subseteq\events$ is called a sub-event space if it satisfies
-the following conditions.
-\begin{itemize}
-\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
-\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
-\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
-we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
-\end{itemize}
-For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
-is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
-$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
-\begin{equation}
-\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
-\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
-\end{aligned}
-\end{equation}
-If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
-the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
-represents that an experimenter knows nothing about a coin before
-she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
-state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
-coin with probability~$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
-is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
-classical coin should be consistent with the situation where an experimenter
-has no prior knowledge.
-
-In general, measurements done with limited resources and poor precision
-may not uniquely identify the true state of a classical system. However,
-at least one system is consistent with the measurements when the system
-satisfies an extra-condition called convex.
-
-\begin{definition}
-$\bar{\mu}$ is called convex~\cite{Griffiths2003}. if for all
-commuting $P_{0},P_{1}\in\events$, we have
-$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
-\end{definition}
-
-Based on Shapley's classical result~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
-we have the following theorem.
-
-\begin{thm}\label{thm:Shapley}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Fuzzy Observables}
 
@@
 
-Formally, the expectation value of an observable with respect to an
-IVPM should be the minimum and maximum expectation value of the same
-observable with respect to states consistent with it. This is true
-when we require our IVPM to be convex, and on a commuting sub-event
-space induced by an observable.
-
-\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
-decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
-is called a sub-event space induced by $\mathbf{O}$ if it is the
-minimal sub-event space containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$.\end{definition}
-
-\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
-if $\bar{\mu}$ is convex, then
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
-\end{equation}
-Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
-holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Fuzzy States}
+Intuitively, the expectation value of an observable with respect to a
+QIVPM is bounded by the minimum and maximum expectation value of the
+same observable with respect to states consistent with it. This is
+true when we require our IVPM to be convex, and on a commuting
+sub-event space induced by an observable.
 

### 2017-05-16 prop_letter.tex

@@
 considered as equivalent to a description of quantum states using
-probability
-measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
+probability measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
 One result is that the expectation value of an observable with respect
@@
 they correspond to the limit of an infinite number of precise
-intervals, and the set of crypto-deterministic intervals (the set
-$\{\imposs,\necess\}$), respectively.
+intervals, and the set of crypto-deterministic intervals (the set~$\{\imposs,\necess\}$),
+respectively.
 
@@
 A \emph{probability space} is a mathematical abstraction specifying
-the necessary conditions for reasoning coherently about collections of
-uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the
-events of interest are specified by \emph{projection operators}
-$P$. This set $P$ includes the empty projection~$\mathbb{0}$, the
-identity projection~$\mathbb{1}$, projections of the form
-$\proj{\psi}$ where $\ket{\psi}$ is a pure quantum state, sums of
-\emph{orthogonal} projections, and products of \emph{commuting}
-projections. In a well-defined quantum probability
-space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
-each event $P_i$ is associated with a probability $\mu(P_i)$ subject
-to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
-$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set of
-mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$, we
-have:
+the necessary conditions for reasoning coherently about collections
+of uncertain events~\cite{Kolmogorov1950}. In the quantum case,
+the events of interest are specified by \emph{projection operators}
+$P$. This set $P$ includes the empty projection~$\mathbb{0}$,
+the identity projection~$\mathbb{1}$, projections of the form $\proj{\psi}$
+where $\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
+projections, and products of \emph{commuting} projections. In a well-defined
+quantum probability space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
+each event $P_{i}$ is associated with a probability $\mu(P_{i})$
+subject to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
+$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set
+of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have: 
 \begin{equation}
-\mu\left(\sum_{i=1}^{N}P_{i}\right)=
-\sum_{i=1}^{N}\mu\left(P_{i}\right)
-\textrm{ .}\label{eq:QuantumProbability-Addition}
+\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
 \end{equation}
+\yutsung{Should we define orthogonality between projectors? Also,
+in order to compare the Eq.~\ref{eq:QuantumProbability-Addition}
+and Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, maybe
+it's better to write just two terms 
+\begin{equation}
+\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\textrm{ .}\label{eq:QuantumProbability-Addition-1}
+\end{equation}
+}
 

### 2017-05-16 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Add citations...

@@
 
-We will start by reviewing IVPMs in the classical
-setting~\cite{JamisonLodwick2004} and then propose our quantum
-framework. In the classical setting, there are several proposals for
-``imprecise probabilities.'' Although these proposals differ in some
-details, they all share the fact that the probability $\mu(E)$ of an
-event $E$ is generalized from a single real number to an interval of
-certainty $[\ell,r]$ where~$\ell$ intuitively corresponds to the
-strength of evidence for the event and $r$ corresponds to the strength
-of evidence against the event. The collection of intervals used in the
-definition of a probability measure must satisfy certain properties
-which we explain next.
+We will start by reviewing IVPMs in the classical setting~\cite{JamisonLodwick2004}
+and then propose our quantum framework. In the classical setting,
+there are several proposals for ``imprecise probabilities~\cite{Dempster1967,Artstein1972,Shafer1976,PuriRalescu1983,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Teran2014,Grabisch2016}.''
+Although these proposals differ in some details, they all share the
+fact that the probability $\mu(E)$ of an event $E$ is generalized
+from a single real number to an interval of certainty $[\ell,r]$
+where~$\ell$ intuitively corresponds to the strength of evidence
+for the event and $r$ corresponds to the strength of evidence against
+the event. The collection of intervals used in the definition of a
+probability measure must satisfy certain properties which we explain
+next.
 

### 2017-05-16 prop_letter.tex
Updates from ShareLaTeX

--- 2017-05-16 prop_letter.tex
@@
 We will proceed by assuming a crypto-deterministic QIVMP $\bar{\mu}$
-and derive a contradiction using the following nine ``Mermin square''
+and derive a contradiction using the following nine ``Mermin-Peres square''
 observables~\cite{Mermin1990Simple,peres1995quantum}:
-\begin{equation}
-\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
-\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
-\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
-\end{aligned}
+\begin{center}
+\begin{tabular}{| c | c | c |}
+\hline
+$\mathbb{1} \otimes\sigma_{z}$ & $\sigma_{z}  \otimes\mathbb{1}$ & $\sigma_{z} \otimes\sigma_{z}$  \\ \hline
+$\sigma_{x} \otimes\mathbb{1}$ & $\mathbb{1} \otimes\sigma_{x}$ & $\sigma_{x} \otimes\sigma_{x}$ \\ \hline
+$\sigma_{x} \otimes\sigma_{z}$ & $\sigma_{z} \otimes\sigma_{x}$ & $\sigma_{y} \otimes\sigma_{y}$ \\ \hline
+\end{tabular}
 \label{eq:MerminSquare}
-\end{equation}
+\end{center}
 

### 2017-05-16 prop_letter.tex
prop_letter.tex Small things here and there...

@@
 the events of interest are specified by \emph{projection operators}
-$P$. This set $P$ includes the empty projection~$\mathbb{0}$,
-the identity projection~$\mathbb{1}$, projections of the form $\proj{\psi}$
+$P$. This set includes the empty projection~$\mathbb{0}$, the identity
+projection~$\mathbb{1}$, projections of the form $\proj{\psi}$
 where $\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
@@
 subject to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
-$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set
-of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have: 
+$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each
+pair of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, we have:
 \begin{equation}
-\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}\label{eq:QuantumProbability-Addition}
 \end{equation}
-\yutsung{Should we define orthogonality between projectors? Also,
-in order to compare the Eq.~\ref{eq:QuantumProbability-Addition}
-and Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, maybe
-it's better to write just two terms 
-\begin{equation}
-\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\textrm{ .}\label{eq:QuantumProbability-Addition-1}
-\end{equation}
-}
+where $P_{0}$ and $P_{1}$ are called orthogonal if $P_{0}P_{1}=\mathbb{0}$.
 
@@
 \begin{center}
-\begin{tabular}{| c | c | c |}
+\begin{tabular}{|c|c|c|}
 \hline 
-$\mathbb{1} \otimes\sigma_{z}$ & $\sigma_{z}  \otimes\mathbb{1}$ & $\sigma_{z} \otimes\sigma_{z}$  \\ \hline
-$\sigma_{x} \otimes\mathbb{1}$ & $\mathbb{1} \otimes\sigma_{x}$ & $\sigma_{x} \otimes\sigma_{x}$ \\ \hline
-$\sigma_{x} \otimes\sigma_{z}$ & $\sigma_{z} \otimes\sigma_{x}$ & $\sigma_{y} \otimes\sigma_{y}$ \\ \hline
+$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
+\hline 
+$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
+\hline 
+$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
+\hline 
 \end{tabular}
-\label{eq:MerminSquare}
-\end{center}
+\par\end{center}
 

### 2017-05-16 prop_letter.tex
Updates from ShareLaTeX

--- 2017-05-16 prop_letter.tex
@@
 events are disjoint; the previous na\"\i ve way of combining the
-intervals would give $\mu(E+\overline(E))=[0.9,1.1]$ which is not a
+intervals would give $\mu(E+\overline{E})=[0.9,1.1]$ which is not a
 valid probability interval. Moreover the event $E+\overline{E}$ is the

### 2017-05-16 prop_letter.tex
prop_letter.tex \bibliographystyle{apsrev4-1} Deleted to make sure longbibliography works...
fixed comments by gerardo

@@
 A \emph{probability space} is a mathematical abstraction specifying
-the necessary conditions for reasoning coherently about collections
-of uncertain events~\cite{Kolmogorov1950}. In the quantum case,
-the events of interest are specified by \emph{projection operators}
-$P$. This set includes the empty projection~$\mathbb{0}$, the identity
-projection~$\mathbb{1}$, projections of the form $\proj{\psi}$
-where $\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
-projections, and products of \emph{commuting} projections. In a well-defined
-quantum probability space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
-each event $P_{i}$ is associated with a probability $\mu(P_{i})$
-subject to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
-$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each
-pair of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, we have:
+the necessary conditions for reasoning coherently about collections of
+uncertain events~\cite{Kolmogorov1950}. In the quantum case, the
+events of interest are specified by \emph{projection operators}
+$P$. These include the empty projection~$\mathbb{0}$, the identity
+projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
+$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
+sums of \emph{orthogonal} projections $P_0$ and $P_1$ such
+$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
+$P_0$ and $P_1$ such $P_0P_1=P_1P_0$. In a well-defined quantum
+probability
+space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
+each event $P_{i}$ is mapped using a probability measure
+$\mu : P \rightarrow [0,1]$ to a probability $\mu(P_{i})$ subject to
+the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
+$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
+of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, we have:
 \begin{equation}
-\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}\label{eq:QuantumProbability-Addition}
+{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\textrm{.}\label{eq:QuantumProbability-Addition}
 \end{equation}
-where $P_{0}$ and $P_{1}$ are called orthogonal if $P_{0}P_{1}=\mathbb{0}$.
 
 As an example, consider a three-dimensional Hilbert space with
-orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable $Q$
-with spectral decomposition $\proj{0} + 2\,\proj{1} +
-3\,\proj{2}$. Two fragments of valid probability measures $\mu_1$ and
-$\mu_2$ that can associated with this space are:
-$\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
+orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable
+$\mathbf{O}$ with spectral decomposition
+$\proj{0} + 2\,\proj{1} + 3\,\proj{2}$. Two fragments of valid
+probability measures $\mu_1$ and $\mu_2$ that can associated with this
+space are: $\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
 $\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0.5$,
@@
 
-We will start by reviewing IVPMs in the classical setting~\cite{JamisonLodwick2004}
-and then propose our quantum framework. In the classical setting,
-there are several proposals for ``imprecise probabilities~\cite{Dempster1967,Artstein1972,Shafer1976,PuriRalescu1983,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Teran2014,Grabisch2016}.''
+We will start by reviewing IVPMs in the classical
+setting~\cite{JamisonLodwick2004} and then propose our quantum
+generalization. In the classical setting, there are several proposals
+for ``imprecise
+probabilities~\cite{Dempster1967,Artstein1972,Shafer1976,PuriRalescu1983,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Teran2014,Grabisch2016}.''
 Although these proposals differ in some details, they all share the
-fact that the probability $\mu(E)$ of an event $E$ is generalized
-from a single real number to an interval of certainty $[\ell,r]$
-where~$\ell$ intuitively corresponds to the strength of evidence
-for the event and $r$ corresponds to the strength of evidence against
-the event. The collection of intervals used in the definition of a
+fact that the probability $\mu(E)$ of an event $E$ is generalized from
+a single real number to an interval of certainty $[\ell,r]$
+where~$\ell$ intuitively corresponds to the strength of evidence for
+the event and $r$ corresponds to the strength of evidence against the
+event. The collection of intervals used in the definition of a
 probability measure must satisfy certain properties which we explain
@@
 refer to the probability of impossible events (e.g., the null event)
-and certain events (e.g., the event covering the entire space). For
-each interval $[\ell,r]$, we also need the interval $[1-r,1-\ell]$ so
-that if one interval refers to the probability of an event, the other
-refers to the probability of the complement event. For example, if we
-discover as a result of an experiment that $\mu(E) = [0.2,0.3]$ for
-some event $E$, we may conclude that $\mu(\overline{E}) = [0.7,0.8]$
-for the complement event $\overline{E}$. In addition to these simple
-conditions, there are some subtle conditions on how intervals are
-combined, which we discuss next.
+and certain events (e.g., the event covering the entire space of
+events). For each interval $[\ell,r]$, we also need the interval
+$[1-r,1-\ell]$ so that if one interval refers to the probability of an
+event, the other refers to the probability of the complement
+event. For example, if we discover as a result of an experiment that
+$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude thatv
+$\mu(\overline{E}) = [0.7,0.8]$ for the complement event
+$\overline{E}$. In addition to these simple conditions, there are some
+subtle conditions on how intervals are combined, which we discuss
+next.
 
@@
 $\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
-at calculating the probability of the combined event that $E_1$ or
-$E_2$ occurs might be $\mu(E_1+E_2) = [\ell_1+\ell_2,r_1+r_2]$. In
+at calculating the probability of the combined event that either $E_1$
+or $E_2$ occurs might be $\mu(E_1+E_2) = [\ell_1+\ell_2,r_1+r_2]$. In
 some cases, this is indeed a sensible definition. For example, if
@@
 $\mu(E)=[0.2,0.3]$ and hence $\mu(\overline{E})=[0.7,0.8]$. The two
-events are disjoint; the previous na\"\i ve way of combining the
-intervals would give $\mu(E+\overline{E})=[0.9,1.1]$ which is not a
-valid probability interval. Moreover the event $E+\overline{E}$ is the
-identity event covering the entire space; its probability interval
-should be $[1,1]$ which is sharper than $[0.9,1.1]$. The problem is
-that the two intervals are correlated: there is more information in
-the combined event than in each event separately. In our example, even
-though the true probability of $\mu(E)$ can be in anywhere in the
-range $[0.2,0.3]$ and the true probability of $\mu(\overline{E})$ can
-be in anywhere in the range $[0.7,0.8]$, the values are not
-independent. Any value of $\mu(E) \leq 0.25$ will force
-$\mu(\overline{E})\geq 0.75$. To account for such subtleties, the
-axioms of interval-valued probability do not use a strict equality for
-the combination of disjoint events. The correct constraint regarding
-the probability of $E_1+E_2$ when $E_1$ and $E_2$ are disjoint is
+events $E$ and $\overline{E}$ are disjoint; the previous na\"\i ve way
+of combining the intervals would give $\mu(E+\overline{E})=[0.9,1.1]$
+which is not a valid probability interval. Moreover the event
+$E+\overline{E}$ is the identity event covering the entire space; its
+probability interval should be $[1,1]$ which is sharper than
+$[0.9,1.1]$. The problem is that the two intervals are correlated:
+there is more information in the combined event than in each event
+separately. In our example, even though the true probability of
+$\mu(E)$ can be in anywhere in the range $[0.2,0.3]$ and the true
+probability of $\mu(\overline{E})$ can be in anywhere in the range
+$[0.7,0.8]$, the values are not independent. Any value of
+$\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq 0.75$. To account
+for such subtleties, the axioms of interval-valued probability do not
+use a strict equality for the combination of disjoint events. The
+correct constraint regarding the probability of $E_1+E_2$ when $E_1$
+and $E_2$ are disjoint is
 $\mu(E_1+E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in combination
@@
 $\mu(E+\overline{E})$ to always be $[1,1]$ irrespective of the
-particular assignments of $\mu(E)$ or $\mu(\overline{E})$. When
-combining non-disjoint events, there is a further subtlety whose
+particular assignments of $\mu(E)$ or $\mu(\overline{E})$.
+
+When combining non-disjoint events, there is a further subtlety whose
 resolution will give the most general and final condition as
@@
 principle that uses $\subseteq$ instead of $=$ for the same reason as
-before. The new condition reduces to the previously motivated
-condition when the events are disjoint, i.e., when $\mu(E_1E_2) = 0$.
+before. The new condition, known as \emph{convexity}, reduces to the
+previously motivated condition when the events are disjoint, i.e.,
+when $\mu(E_1E_2) = 0$.
 
 We now have the necessary ingredients to define QIVPMs as a
-generalization of the above observations. More precisely the quantum
-definition will reduce to the classical one when the space of quantum
-events is restricted to mutually commuting sub-events.
+generalization of both classical IVPMs and conventional quantum
+probability measures. More precisely the quantum IVPM will reduce to
+the classical IVPM when the space of quantum events is restricted to
+mutually commuting sub-events.
 
@@
   a QIVPM $\bar{\mu}$ is an assignment of intervals to each event
-  (projection operator) obeying the following axioms:
-  $\bar{\mu}(\mathbb{0})=\imposs=\left[0,0\right]$,
-  $\bar{\mu}(\mathbb{1})=\necess=\left[1,1\right]$,
+  (projection operator) subject to the following constraints:
+  $\bar{\mu}(\mathbb{0})=\left[0,0\right]$,
+  $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
   $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
@@
 \end{definition}
-The first three axioms are the direct counterpart of the corresponding
-axioms for conventional probability measures. With the understanding
-that the union of classical sets $E_1+E_2$ is replaced by
-$P_0+P_1-P_0P_1$ in the case of projection operators, the last
-condition, Eq~\ref{eq:QuantumInterval-valuedProbability-Inclusion},
-is a direct counterpart of Eq.~\ref{eq:classicalconvex}.
+The first three constraints are the direct counterpart of the
+corresponding ones for conventional probability measures. With the
+understanding that the union of classical sets $E_1+E_2$ is replaced
+by $P_0+P_1-P_0P_1$ in the case of projection operators, the last
+condition, Eq~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
+a direct counterpart of Eq.~\ref{eq:classicalconvex}.
+
+Contrary to the case with conventional quantum probability spaces,
+there is generally no unique state consistent with a QIVPM. Given
+observations done with finite resources, the probabilities become
+intervals, and we say a state~$\rho$ is consistent with $\bar{\mu}$ on
+a projector~$P$ if
+$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
+denoted by
+$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$ is
+consistent with $\bar{\mu}$ on every projector in $S$.
 
@@
 \item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
-\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
-we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
+\item For each pair of orthogonal projections~$P_0 \in \events'$ and
+  $P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. 
 \end{itemize}
@@
 experimenter with no prior knowledge about the particular quantum
-system in question, and any state is consistent with $\bar{\mu}_{1}$
-on any projectors. We have that
+system in question; any quantum state would be consistent with
+$\bar{\mu}_{1}$ on any projectors. We have that
 $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
@@
 Our first result regarding QIVPM is that a QIVPM cannot be
-crypto-deterministic in the sense of Peres. We will use the proof of
-the Kochen-Specker
-theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
-to show that it is, in general, impossible to just have the two
-intervals \imposs\ and \necess: every QIVPM must be parameterized by a
-collection of intervals that includes at least one additional
-``fuzzy'' interval and some events must be associated with such
-uncertain intervals. The significance of this observation is that the
-uncertainty in the intervals is, in contrast to the classical case,
-\emph{a fundamental part of quantum theory}. There is in fact two
-sources of imprecision: one due to the finite measurement resources
-and one due to complementarity which requires every QIVPM to be truly
+crypto-deterministic in the sense of Peres~\cite{peres1995quantum}. We
+will adapt the proof of the Kochen-Specker
+theorem~\cite{kochenspecker1967,
+  peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
+is, in general, impossible to just have the two intervals \imposs\ and
+\necess: every QIVPM must be parameterized by a collection of
+intervals that includes at least one additional ``fuzzy'' interval and
+some events must be associated with such uncertain intervals. The
+significance of this observation is that the uncertainty in the
+intervals is, in contrast to the classical case, \emph{a fundamental
+  part of quantum theory}. There are in fact two sources of
+uncertainty: one due to the finite measurement resources and one due
+to complementarity which requires every quantum framework to be truly
 probabilistic.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{apsrev4-1}
 \bibliography{prop}

### 2017-05-17 prop_letter.tex
pass over entire paper

@@
 principle that uses $\subseteq$ instead of $=$ for the same reason as
-before. The new condition, known as \emph{convexity}, reduces to the
-previously motivated condition when the events are disjoint, i.e.,
-when $\mu(E_1E_2) = 0$.
+before. The new condition, known as
+\emph{convexity}~\cite{Griffiths2003}, reduces to the previously
+motivated condition when the events are disjoint, i.e., when
+$\mu(E_1E_2) = 0$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage  
-\section{Rest of Paper}
+\section{Gleason}
+
+In the classical setting, measurements done with limited resources and
+poor precision may not uniquely identify the true state of a system
+system. However, there is always at least one state that is consistent
+with the imprecise
+measurements~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
+
+\begin{thm}\label{thm:Shapley}
+  For every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
+  sub-event space~$\events'\subseteq\events$ commutes, then
+  $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
+\end{thm}
+
+Gleason's theorem asserts any quantum real-valued probability measure
+is consistent with a unique mixed state, and Shapley proved a quantum
+IVPM must approximate some states for each classical sub-event
+space. However, it may not approximate the same state in every
+sub-event space. As the result, there may be no state consistent with
+a quantum IVPM on all projectors~$\events$.
+
+\begin{example}\label{ex:three-dimensional-three-value}
+  Given a three dimensional Hilbert space with an orthonormal basis
+  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let
+  $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
+  $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
+  $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
+\begin{subequations}
+\begin{eqnarray}
+ &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
+ & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\textrm{ ,}
+\end{aligned}
+\\
+ &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
+ & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
+\end{aligned}
+\\
+ &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
+\end{eqnarray}
+\end{subequations}
+It is straightforward to verify that $\bar{\mu}_{3}$ is a convex
+quantum IVPM.
+
+Let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because
+$\bar{\mu}_{3}(\proj{0})=\bar{\mu}_{3}(\proj{\ps})=\imposs$, we have
+$\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
+for any mixed
+state~$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.  Hence,
+$\rho$ is actually $\ket{2}$, the only pure state orthogonal to both
+$\ket{0}$ and $\ket{\ps}$. It is easy to verify $\proj{2}$ is actually
+in $\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
+
+Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We have
+$\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\left\{ \proj{1}\right\} $.
+Therefore,
+\begin{equation}
+\coreBorn\left(\bar{\mu}_{3},\events\right)\subseteq\coreBorn\left(\bar{\mu}_{3},S_{1}\right)\cap\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\emptyset
+\end{equation}
+and must be empty.
+\end{example}
+
+Although Gleason's theorem doesn't hold for every quantum IVPM, it
+can be applied in a limit case when the intervals are infinitely precise.
+That is, when $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+any quantum IVPM can be recast as an real-valued one and has a unique
+state consistent with it on every projector when $d\ge3$.
+
+In general, this kind of inconsistency can be reduced if we increase
+the measurement resource, that is, using finer intervals. We conjecture
+by using finer and finer intervals, it would be more and more likely
+that there is a state consistent with a quantum IVPM on all projectors~$\events$.
+
+% %%%
+% \subsection{Kochen-Specker}
+
+% While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
+% IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
+% is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
+% We will use the essential idea of the Kochen-Specker theorem to prove
+% there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
+% Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
+% We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
+% where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
+% multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
+% and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
+% then we have 
+% \begin{equation}
+% \prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
+% \end{equation}
+% for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
+
+% Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
+% these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+% \begin{equation}
+% \begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
+% \sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
+% \sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
+% \end{aligned}
+% \label{eq:MerminSquare}
+% \end{equation}
+% must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
+% In each row and column, operators commutes, and each operator is the
+% product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+% Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
+% that 
+% \begin{equation}
+% \begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
+% \langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
+% \langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
+% \end{aligned}
+% \label{eq:MerminSquare-values}
+% \end{equation}
+% satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+
+Foundational concepts in quantum mechanics, such as Gleason and
+Kochen-Specker theorems, rely in a very subtle way on the use of
+unbounded resources. By assuming infinitely precise measurements,
+these two insightful theorems underline two fundamental aspects of
+quantum mechanics. On the one hand, Gleason's result establishes a
+relationship between quantum states and probabilities uniquely defined
+by Born's rule, on the other, Kochen-Specker unveils a distinctive
+aspect of physical reality, the fact that it is contextual.  Our goal
+in this paper has been to analyze the physical consequences of a
+mathematical framework that allows for finite precision measurements
+by introducing the concept of quantum interval-valued probability. The
+latter incorporates uncertainty in the measurement results by defining
+fuzzy probability measures, and includes standard quantum measurement
+as the particular instance of sharp, infinitely precise, intervals.
+In addition, we showed how these two theorems emerge as limiting cases
+of this very same framework, thus connecting two seemingly unrelated
+aspects of quantum physics. Most importantly, we concluded that
+arbitrary finite precision measurement conditions nullify the main
+tenets of both theorems.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{prop}
+\end{document}
 
@@
 
- In general, measurements done with limited resources and poor precision
-may not uniquely identify the true state of a classical system. However,
-at least one system is consistent with the measurements when the system
-satisfies an extra-condition called convex.
-
 \begin{definition}
-$\bar{\mu}$ is called convex~\cite{Griffiths2003}. if for all
+$\bar{\mu}$ is called convex. if for all
 commuting $P_{0},P_{1}\in\events$, we have
@@
 \end{definition}
-
-Based on Shapley's classical result~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
-we have the following theorem.
-
-\begin{thm}\label{thm:Shapley}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
 
@@
 \subsection{Gleason}
-
-Gleason's theorem asserts any quantum real-valued probability measure
-is consistent with a unique mixed state, and Shapley proved a convex
-quantum IVPM must approximate some states for each classical sub-event
-space. However, it may not approximate the same state in every sub-event
-space. As the result, there may be no state consistent with a convex
-quantum IVPM on all projectors~$\events$.
-
-\begin{example}\label{ex:three-dimensional-three-value}Given a three
-dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
-$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
-and
-\begin{subequations}
-\begin{eqnarray}
- &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
- & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\textrm{ ,}
-\end{aligned}
-\\
- &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
- & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
-\end{aligned}
-\\
- &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
-\end{eqnarray}
-\end{subequations}
-It is straightforward to verify that $\bar{\mu}_{3}$ is a convex
-quantum IVPM.
-
-Let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because $\bar{\mu}_{3}(\proj{0})=\bar{\mu}_{3}(\proj{\ps})=\imposs$,
-we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-for any mixed state~$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
-Hence, $\rho$ is actually $\ket{2}$, the only pure state orthogonal
-to both $\ket{0}$ and $\ket{\ps}$. It is easy to verify $\proj{2}$
-is actually in $\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
-
-Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We
-have $\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\left\{ \proj{1}\right\} $.
-Therefore, 
-\begin{equation}
-\coreBorn\left(\bar{\mu}_{3},\events\right)\subseteq\coreBorn\left(\bar{\mu}_{3},S_{1}\right)\cap\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\emptyset
-\end{equation}
-and must be empty.\end{example}
-
-Although Gleason's theorem doesn't hold for every quantum IVPM, it
-can be applied in a limit case when the intervals are infinitely precise.
-That is, when $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-any quantum IVPM can be recast as an real-valued one and has an unique
-state consistent with it on every projector when $d\ge3$.
-
-In general, this kind of inconsistency can be reduced if we increase
-the measurement resource, that is, using finer intervals. We conjecture
-by using finer and finer intervals, it would be more and more likely
-that there is a state consistent with a quantum IVPM on all projectors~$\events$.
-
-% %%%
-% \subsection{Kochen-Specker}
-
-% While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
-% IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-% is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
-% We will use the essential idea of the Kochen-Specker theorem to prove
-% there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
-% Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
-% We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
-% where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
-% multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
-% and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
-% then we have 
-% \begin{equation}
-% \prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
-% \end{equation}
-% for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
-
-% Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
-% these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
-% \begin{equation}
-% \begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
-% \sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
-% \sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
-% \end{aligned}
-% \label{eq:MerminSquare}
-% \end{equation}
-% must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
-% In each row and column, operators commutes, and each operator is the
-% product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-% Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
-% that 
-% \begin{equation}
-% \begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
-% \langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
-% \langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
-% \end{aligned}
-% \label{eq:MerminSquare-values}
-% \end{equation}
-% satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-
-Foundational concepts in quantum mechanics, such as Gleason and
-Kochen-Specker theorems, rely in a very subtle way on the use of
-unbounded resources. By assuming infinitely precise measurements,
-these two insightful theorems underline two fundamental aspects of
-quantum mechanics. On the one hand, Gleason's result establishes a
-relationship between quantum states and probabilities uniquely defined
-by Born's rule, on the other, Kochen-Specker unveils a distinctive
-aspect of physical reality, the fact that it is contextual.  Our goal
-in this paper has been to analyze the physical consequences of a
-mathematical framework that allows for finite precision measurements
-by introducing the concept of quantum interval-valued probability. The
-latter incorporates uncertainty in the measurement results by defining
-fuzzy probability measures, and includes standard quantum measurement
-as the particular instance of sharp, infinitely precise, intervals.
-In addition, we showed how these two theorems emerge as limiting cases
-of this very same framework, thus connecting two seemingly unrelated
-aspects of quantum physics. Most importantly, we concluded that
-arbitrary finite precision measurement conditions nullify the main
-tenets of both theorems.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{prop}
-\end{document}

### 2017-05-17 prop_letter.tex
prop.bib Update citations...

@@
 
-We will start by reviewing IVPMs in the classical
-setting~\cite{JamisonLodwick2004} and then propose our quantum
-generalization. In the classical setting, there are several proposals
-for ``imprecise
-probabilities~\cite{Dempster1967,Artstein1972,Shafer1976,PuriRalescu1983,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Teran2014,Grabisch2016}.''
+We will start by reviewing IVPMs in the classical setting~\cite{JamisonLodwick2004}
+and then propose our quantum generalization. In the classical setting,
+there are several proposals for ``imprecise probabilities~\cite{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Grabisch2016}.''
 Although these proposals differ in some details, they all share the
-fact that the probability $\mu(E)$ of an event $E$ is generalized from
-a single real number to an interval of certainty $[\ell,r]$
-where~$\ell$ intuitively corresponds to the strength of evidence for
-the event and $r$ corresponds to the strength of evidence against the
-event. The collection of intervals used in the definition of a
+fact that the probability $\mu(E)$ of an event $E$ is generalized
+from a single real number to an interval of certainty $[\ell,r]$
+where~$\ell$ intuitively corresponds to the strength of evidence
+for the event and $r$ corresponds to the strength of evidence against
+the event. The collection of intervals used in the definition of a
 probability measure must satisfy certain properties which we explain

### 2017-05-17 prop_letter.tex
prop_letter.tex Small things here and there...

@@
 refer to the probability of impossible events (e.g., the null event)
-and certain events (e.g., the event covering the entire space of
-events). For each interval $[\ell,r]$, we also need the interval
+and certain events (e.g., the event covering the entire sample space
+). For each interval $[\ell,r]$, we also need the interval
 $[1-r,1-\ell]$ so that if one interval refers to the probability of an
@@
 $\mu(E)=[0.2,0.3]$ and hence $\mu(\overline{E})=[0.7,0.8]$. The two
-events $E$ and $\overline{E}$ are disjoint; the previous na\"\i ve way
+events $E$ and $\overline{E}$ are disjoint; the previous naïve way
 of combining the intervals would give $\mu(E+\overline{E})=[0.9,1.1]$
@@
 before. The new condition, known as
-\emph{convexity}~\cite{Griffiths2003}, reduces to the previously
+\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
+reduces to the previously
 motivated condition when the events are disjoint, i.e., when
@@
   \begin{eqnarray}
-   &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
-   &  & x[l,r]=\begin{cases}
-  [xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
-  [xr,xl] & \textrm{for }x\le0\textrm{ ,}
+   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
+   &  & x[\ell,r]=\begin{cases}
+  [x\ell,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
+  [xr,x\ell] & \textrm{for }x\le0\textrm{ ,}
   \end{cases}
@@
 understanding that the union of classical sets $E_1+E_2$ is replaced
-by $P_0+P_1-P_0P_1$ in the case of projection operators, the last
-condition, Eq~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
+by $P_0+P_1-P_0P_1$ in the case of projection operators~\cite{Griffiths2003}, the last
+condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
 a direct counterpart of Eq.~\ref{eq:classicalconvex}.
@@
 denoted by
-$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
+where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
+is the probability that the event~$P$ happens determined by the
+Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
 Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$ is
@@
 \end{aligned}
+\textrm{ .}
 \end{equation}
@@
 Our first result regarding QIVPM is that a QIVPM cannot be
-crypto-deterministic in the sense of Peres~\cite{peres1995quantum}. We
+crypto-deterministic in the sense of Peres~\cite{PeresRon1988,peres1995quantum}. We
 will adapt the proof of the Kochen-Specker
@@
 
-\begin{definition} Given an observable~$\mathbf{O}$ with spectral
-  decomposition
-  $\mathbf{O}=\sum_{s\in\left\{ +,-\right\}
-  }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}$, a set of
-  projectors~$\events'\subseteq\events$ is called a sub-event space
-  induced by $\mathbf{O}$ if it is the minimal sub-event space
-  containing
-  $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{
-    P_{i}^{+}\right\} _{i=1}^{N^{+}}$.
-\end{definition}
-
-\begin{thm} Given a Hilbert space of $d\ge3$, for every
-  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and any
-  observable~$\mathbf{O}$ inducing a sub-event space~$\events'$, 
+\begin{definition}Given a Hilbert space of $d\ge3$, for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+any observable~$\mathbf{O}$ with spectral decomposition $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$,
+and $\events'$ is minimal sub-event space containing $\left\{ P_{i}\right\} _{i=1}^{N}$,
+we have
 \begin{equation}
@@
 \end{equation}
-\end{thm}
+\end{definition}
 
@@
 Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
-these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
-\begin{equation}
-\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
-\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
-\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
-\end{aligned}
-\label{eq:MerminSquare}
-\end{equation}
-must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
+these two properties, the observables in the Mermin-Peres square must
+have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
 In each row and column, operators commutes, and each operator is the
@@
 \end{subequations}
-It is straightforward to verify that $\bar{\mu}_{3}$ is a convex
+It is straightforward to verify that $\bar{\mu}_{3}$ is a
 quantum IVPM.
@@
 state~$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.  Hence,
-$\rho$ is actually $\ket{2}$, the only pure state orthogonal to both
-$\ket{0}$ and $\ket{\ps}$. It is easy to verify $\proj{2}$ is actually
+$\rho$ cannot be any state other than $\ket{2}$, the only pure state orthogonal to both
+$\ket{0}$ and $\ket{\ps}$, and it is easy to verify $\proj{2}$ is actually
 in $\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.

### 2017-05-18 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Add Choquet integral citation

@@
 which lie between the minimum and maximum bounds of the given
-probability intervals. If the QIVPM is crypto-deterministic, this
+probability intervals, and this definition also consistent with the classical
+Choquet integral on commuting sub-event space by adopting the classical
+theorem~\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
+If the QIVPM is crypto-deterministic, this
 interval collapses to a singleton $\left\{ \lambda\right\} $, where

### 2017-05-18 prop_letter.tex
prop.bib @Article{Appleby_2005} Added...

@@
 mechanics regarding the tension between finite precision measurement
-and contextuality~\cite{Peres2003,BarrettKent2004}.  For example,
+and contextuality~\cite{BarrettKent2004,Appleby_2005}.  For example,
 Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree

### 2017-05-18 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Classical events are sets so better to use cup and cap.

@@
 at calculating the probability of the combined event that either $E_1$
-or $E_2$ occurs might be $\mu(E_1+E_2) = [\ell_1+\ell_2,r_1+r_2]$. In
+or $E_2$ occurs might be $\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In
 some cases, this is indeed a sensible definition. For example, if
 $\mu(E_1)=[0.1,0.2]$ and $\mu(E_2)=[0.3,0.4]$ we get
-$\mu(E_1+E_2) = [0.4,0.6]$. But consider an event $E$ such that
+$\mu(E_1\cup E_2) = [0.4,0.6]$. But consider an event $E$ such that
 $\mu(E)=[0.2,0.3]$ and hence $\mu(\overline{E})=[0.7,0.8]$. The two
 events $E$ and $\overline{E}$ are disjoint; the previous naïve way
-of combining the intervals would give $\mu(E+\overline{E})=[0.9,1.1]$
+of combining the intervals would give $\mu(E\cup\overline{E})=[0.9,1.1]$
 which is not a valid probability interval. Moreover the event
-$E+\overline{E}$ is the identity event covering the entire space; its
+$E\cup\overline{E}$ is the identity event covering the entire space; its
 probability interval should be $[1,1]$ which is sharper than
@@
 use a strict equality for the combination of disjoint events. The
-correct constraint regarding the probability of $E_1+E_2$ when $E_1$
+correct constraint regarding the probability of $E_1\cup E_2$ when $E_1$
 and $E_2$ are disjoint is
-$\mu(E_1+E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in combination
+$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in combination
 with the requirement for the identity event would force
-$\mu(E+\overline{E})$ to always be $[1,1]$ irrespective of the
+$\mu(E\cup\overline{E})$ to always be $[1,1]$ irrespective of the
 particular assignments of $\mu(E)$ or $\mu(\overline{E})$.
@@
 \begin{equation}
-\mu(E_1+E_2) + \mu(E_1E_2) \subseteq \mu(E_1) + \mu(E_2)
+\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
 \label{eq:classicalconvex}
@@
 motivated condition when the events are disjoint, i.e., when
-$\mu(E_1E_2) = 0$.
+$\mu(E_1\cap E_2) = 0$.
 
@@
 corresponding ones for conventional probability measures. With the
-understanding that the union of classical sets $E_1+E_2$ is replaced
+understanding that the union of classical sets $E_1\cup E_2$ is replaced
 by $P_0+P_1-P_0P_1$ in the case of projection operators~\cite{Griffiths2003}, the last

### 2017-05-18 prop_letter.tex
prop_letter.tex Fix some typos...

@@
 refer to the probability of impossible events (e.g., the null event)
-and certain events (e.g., the event covering the entire sample space
-). For each interval $[\ell,r]$, we also need the interval
+and certain events (e.g., the event covering the entire sample space).
+For each interval $[\ell,r]$, we also need the interval
 $[1-r,1-\ell]$ so that if one interval refers to the probability of an
@@
 event. For example, if we discover as a result of an experiment that
-$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude thatv
+$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
 $\mu(\overline{E}) = [0.7,0.8]$ for the complement event
@@
 Choquet integral on commuting sub-event space by adopting the classical
-theorem~\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
+results~\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
 If the QIVPM is crypto-deterministic, this

### 2017-05-19 prop_letter.tex
prop_letter.tex Change non-breaking space setting...
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }

@@
 \setcounter{secnumdepth}{3}
+% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
+% Change non-breaking space to \nolinebreak[1] 
+% Hence, it will not hyphenate too much surrounding words.
+\newcommand{\nb}{\nolinebreak[1] }
 
@@
 mechanics regarding the tension between finite precision measurement
-and contextuality~\cite{BarrettKent2004,Appleby_2005}.  For example,
-Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999} disagree
+and contextuality\nb\cite{BarrettKent2004,Appleby_2005}.  For example,
+Meyer\nb\cite{PhysRevLett.83.3751} and Mermin\nb\cite{Mermin1999} disagree
 on whether finite-precision measurements invalidate the Kochen-Specker
-theorem~\cite{kochenspecker1967,peres1995quantum}, and discussion
+theorem\nb\cite{kochenspecker1967,peres1995quantum}, and discussion
 continues on whether contextuality is experimentally
-verifiable~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
+verifiable\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
 fundamental question is how to make mathematical theories of quantum
@@
 measurement, attempted previously with computable number
-systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
+systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
 extending classical interval-valued probability
-measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by
+measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We begin by
 axiomatizing a quantum interval-valued probability measure (QIVPM)
@@
 considered as equivalent to a description of quantum states using
-probability measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
+probability measures\nb\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
 One result is that the expectation value of an observable with respect
@@
 quantum mechanics.  We then examine Gleason's
-theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
+theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
 Kochen-Specker theorem in the context of QIVPM's, and conclude that
 they correspond to the limit of an infinite number of precise
-intervals, and the set of crypto-deterministic intervals (the set~$\{\imposs,\necess\}$),
+intervals, and the set of crypto-deterministic intervals (the set\nb$\{\imposs,\necess\}$),
 respectively.
@@
 % affect the idealized quantum concept, e.g.,
-% contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
+% contextuality\nb\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
 % and the very foundation of quantum mechanics is still a problem. In
@@
 % not only a uniform framework to understand Gleason's
-% theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
+% theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
 % Kochen-Specker
-% theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
+% theorem\nb\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
 % but also some examples which cannot be explained by the Born
-% rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+% rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
 
@@
 % contextuality based on infinitely precise numbers is proved not
-% experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.  After a
-% long debate~\cite{Mermin1999,Peres2003,BarrettKent2004}, people are
+% experimental verifiable\nb\cite{PhysRevLett.83.3751,Kent1999}.  After a
+% long debate\nb\cite{Mermin1999,Peres2003,BarrettKent2004}, people are
 % still trying to update the definition of contextuality when they want
 % to perform further
-% experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+% experiments\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
@@
 % which are proved by Gleason to be the essentially same as a density
-% matrix~\cite{Varadarajan2008}.  Combining quantum probability measures
-% and the classical IVPM~\cite{JamisonLodwick2004} which could be used
+% matrix\nb\cite{Varadarajan2008}.  Combining quantum probability measures
+% and the classical IVPM\nb\cite{JamisonLodwick2004} which could be used
 % to formulate classical finite precision measurement, we can define
@@
 the necessary conditions for reasoning coherently about collections of
-uncertain events~\cite{Kolmogorov1950}. In the quantum case, the
+uncertain events\nb\cite{Kolmogorov1950}. In the quantum case, the
 events of interest are specified by \emph{projection operators}
-$P$. These include the empty projection~$\mathbb{0}$, the identity
-projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
+$P$. These include the empty projection\nb$\mathbb{0}$, the identity
+projection\nb$\mathbb{1}$, projections of the form $\proj{\psi}$ where
 $\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
@@
 probability
-space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
+space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
 each event $P_{i}$ is mapped using a probability measure
@@
 % $\mathbf{O}$ of a physical system whose state is represented by a
-% density matrix~$\rho$, the probability to obtain the value $\lambda$
+% density matrix\nb$\rho$, the probability to obtain the value $\lambda$
 % of that property is determined by the Born rule
@@
 % Hermitian operator
-% $\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+% $\mathbf{O}$\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
 % Alternatively, one may say that the state $\rho$ determines the
@@
 % from the set $\events$ of all possible projectors $P$ onto the
-% interval $[0,1]$, and satisfies the following probability axioms~
+% interval $[0,1]$, and satisfies the following probability axioms\nb
 % \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:
@@
 % \end{itemize}
-% Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
+% Conversely, given any quantum probability measure\nb$\mu:\events\rightarrow[0,1]$
 % satisfying the above axioms, Gleason's theorem asserts that there
-% exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
-% in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+% exists a unique state\nb$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
+% in a Hilbert space of dimension $d\geq3$\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 
-% Furthermore, if we express an observable~$\mathbf{O}$ as its spectrum
-% decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
-% value of $\mathbf{O}$ is given by~\cite{peres1995quantum,544199,Jaeger2007}
+% Furthermore, if we express an observable\nb$\mathbf{O}$ as its spectrum
+% decomposition\nb$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
+% value of $\mathbf{O}$ is given by\nb\cite{peres1995quantum,544199,Jaeger2007}
 % \begin{equation}
@@
 % introduce the notion of quantum interval-valued probability measures
-% (\emph{IVPMs})~$\bar{\mu}$. The latter replaces the infinitely precise
+% (\emph{IVPMs})\nb$\bar{\mu}$. The latter replaces the infinitely precise
 % interval $[0,1]$ by a finite collection $\mathscr{I}$ of
@@
 
-We will start by reviewing IVPMs in the classical setting~\cite{JamisonLodwick2004}
+We will start by reviewing IVPMs in the classical setting\nb\cite{JamisonLodwick2004}
 and then propose our quantum generalization. In the classical setting,
-there are several proposals for ``imprecise probabilities~\cite{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Grabisch2016}.''
+there are several proposals for ``imprecise probabilities\nb\cite{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Grabisch2016}.''
 Although these proposals differ in some details, they all share the
@@
 from a single real number to an interval of certainty $[\ell,r]$
-where~$\ell$ intuitively corresponds to the strength of evidence
+where\nb$\ell$ intuitively corresponds to the strength of evidence
 for the event and $r$ corresponds to the strength of evidence against
@@
 event. For example, if we discover as a result of an experiment that
-$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
+$\mu(E) = [0.2,0.3]$ for some event\nb$E$, we may conclude that
 $\mu(\overline{E}) = [0.7,0.8]$ for the complement event
@@
 before. The new condition, known as
-\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
+\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
 reduces to the previously
@@
 understanding that the union of classical sets $E_1\cup E_2$ is replaced
-by $P_0+P_1-P_0P_1$ in the case of projection operators~\cite{Griffiths2003}, the last
+by $P_0+P_1-P_0P_1$ in the case of projection operators\nb\cite{Griffiths2003}, the last
 condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
@@
 observations done with finite resources, the probabilities become
-intervals, and we say a state~$\rho$ is consistent with $\bar{\mu}$ on
-a projector~$P$ if
+intervals, and we say a state\nb$\rho$ is consistent with $\bar{\mu}$ on
+a projector\nb$P$ if
 $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
@@
 where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
-is the probability that the event~$P$ happens determined by the
-Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+is the probability that the event\nb$P$ happens determined by the
+Born rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
 Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$ is
@@
 \item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
-\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
-\item For each pair of orthogonal projections~$P_0 \in \events'$ and
+\item For any projection\nb$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
+\item For each pair of orthogonal projections\nb$P_0 \in \events'$ and
   $P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. 
@@
 $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
-IVPM~$\bar{\mu}_{2}$:
+IVPM\nb$\bar{\mu}_{2}$:
 \begin{equation}
@@
 \end{equation}
-If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
+If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
 the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
@@
 she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
-state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
-coin with probability~$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
+state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
+coin with probability\nb$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
 is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
@@
 Our first result regarding QIVPM is that a QIVPM cannot be
-crypto-deterministic in the sense of Peres~\cite{PeresRon1988,peres1995quantum}. We
+crypto-deterministic in the sense of Peres\nb\cite{PeresRon1988,peres1995quantum}. We
 will adapt the proof of the Kochen-Specker
-theorem~\cite{kochenspecker1967,
+theorem\nb\cite{kochenspecker1967,
   peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
@@
 and derive a contradiction using the following nine ``Mermin-Peres square''
-observables~\cite{Mermin1990Simple,peres1995quantum}:
+observables\nb\cite{Mermin1990Simple,peres1995quantum}:
 \begin{center}
@@
 
-\begin{definition}Given a Hilbert space of $d\ge3$, for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-any observable~$\mathbf{O}$ with spectral decomposition $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$,
+\begin{definition}Given a Hilbert space of $d\ge3$, for every QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+any observable\nb$\mathbf{O}$ with spectral decomposition $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$,
 and $\events'$ is minimal sub-event space containing $\left\{ P_{i}\right\} _{i=1}^{N}$,
@@
 Choquet integral on commuting sub-event space by adopting the classical
-results~\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
+results\nb\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
 If the QIVPM is crypto-deterministic, this
@@
 $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
-multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
+multiplication of two singleton sets\nb$\left\{ \lambda_{1}\right\} $
 and $\left\{ \lambda_{2}\right\} $ to be
@@
 \end{equation}
-for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
+for any sequence of commuting observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
 
-Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
+Since the expectation value\nb$\expval{\cdot}_{\bar{\mu}}$ satisfying
 these two properties, the observables in the Mermin-Peres square must
-have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
+have the the expectation value\nb$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
 In each row and column, operators commutes, and each operator is the
 product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
+Therefore, it is clear impossible to find a IVPM\nb$\bar{\mu}$ such
 that 
@@
 with the imprecise
-measurements~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
+measurements\nb\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
 
 \begin{thm}\label{thm:Shapley}
-  For every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
-  sub-event space~$\events'\subseteq\events$ commutes, then
+  For every QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
+  sub-event space\nb$\events'\subseteq\events$ commutes, then
   $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
@@
 sub-event space. As the result, there may be no state consistent with
-a quantum IVPM on all projectors~$\events$.
+a quantum IVPM on all projectors\nb$\events$.
 
@@
 for any mixed
-state~$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.  Hence,
+state\nb$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.  Hence,
 $\rho$ cannot be any state other than $\ket{2}$, the only pure state orthogonal to both
@@
 by using finer and finer intervals, it would be more and more likely
-that there is a state consistent with a quantum IVPM on all projectors~$\events$.
+that there is a state consistent with a quantum IVPM on all projectors\nb$\events$.
 
@@
 % IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-% is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
+% is another one, corresponding to the Kochen-Specker theorem\nb\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
 % We will use the essential idea of the Kochen-Specker theorem to prove
 % there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
-% Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
-% We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
+% Suppose there is a quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
+% We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set\nb$\left\{ \lambda\right\} $,
 % where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
-% multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
+% multiplication of two singleton sets\nb$\left\{ \lambda_{1}\right\} $
 % and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
@@
 % \end{equation}
-% for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
+% for any sequence of commuting observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
 
-% Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
-% these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
+% Since the expectation value\nb$\expval{\cdot}_{\bar{\mu}}$ satisfying
+% these two properties, the following observables\nb\cite{Mermin1990Simple,peres1995quantum}:
 % \begin{equation}
@@
 % \end{equation}
-% must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
+% must have the the expectation value\nb$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
 % In each row and column, operators commutes, and each operator is the
 % product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-% Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
+% Therefore, it is clear impossible to find a IVPM\nb$\bar{\mu}$ such
 % that 
@@
 \yutsung{{Consider a four dimensional Hilbert space with an orthonormal
-basis}~$\Omega=\{\ket{0},\ket{1},\ket{2},\ket{3}\}$, and the commuting
-sub-event space~$\events'=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$.
+basis}\nb$\Omega=\{\ket{0},\ket{1},\ket{2},\ket{3}\}$, and the commuting
+sub-event space\nb$\events'=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$.
 Then, $\bar{\mu}_{0}:\events'\rightarrow\mathscr{I}$ defined by\begin{subequations}
@@
 resources. Since the probabilities are now intervals, it is intuitive
-to say a state~$\rho$ is consistent with $\bar{\mu}$ on a projector~$P$
+to say a state\nb$\rho$ is consistent with $\bar{\mu}$ on a projector\nb$P$
 if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
@@
 where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+We can combine the classical Choquet integral\nb\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
 with Eq.~(\ref{eq:quantum-expectation}) and define the expectation

### 2017-05-20 prop_letter.tex
questions by GO
prop_letter.tex \hyphenation{cryp-to-de-ter-min-is-tic cryp-to-de-ter-min-ism} Added...

@@
 \newcommand{\nb}{\nolinebreak[1] }
+\hyphenation{cryp-to-de-ter-min-is-tic cryp-to-de-ter-min-ism}
 
@@
 they correspond to the limit of an infinite number of precise
-intervals, and the set of crypto-deterministic intervals (the set\nb$\{\imposs,\necess\}$),
+intervals, and the set of cryptodeterministic intervals (the set\nb$\{\imposs,\necess\}$),
 respectively.
@@
 rigorously consider the implications of finite precision measurement.
+
+A question we want to entertain in this paper is \ldots
+Can one incorporate in a rigorous mathematical framework the idea of
+finite precision measurement? Yes QIVPM. Now what is the fate of the 
+foundational theorems of QM when this framework is applied?
 
@@
 Quantum IVPMs become classical IVPMs when the space of events includes
-only mutually commuting sub-events, where $\events'\subseteq\events$
+only mutually commuting events, where $\events'\subseteq\events$
 is called a sub-event space if it satisfies the following conditions.
@@
 Our first result regarding QIVPM is that a QIVPM cannot be
-crypto-deterministic in the sense of Peres\nb\cite{PeresRon1988,peres1995quantum}. We
+cryptodeterministic in the sense of Peres\nb\cite{PeresRon1988,peres1995quantum}. We
 will adapt the proof of the Kochen-Specker
@@
 
-We will proceed by assuming a crypto-deterministic QIVMP $\bar{\mu}$
+We will proceed by assuming a cryptodeterministic QIVMP $\bar{\mu}$
 and derive a contradiction using the following nine ``Mermin-Peres square''
@@
 results\nb\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
-If the QIVPM is crypto-deterministic, this
+If the QIVPM is cryptodeterministic, this
 interval collapses to a singleton $\left\{ \lambda\right\} $, where
@@
 $\necess=\left[1,1\right]$. This is what Peres calls the
-\emph{crypto-deterministic} case in which there is no ambiguity about
+\emph{cryptodeterministic} case in which there is no ambiguity about
 the status of any event; we know for certain if it will occur or not.

### 2017-05-21 prop_iop.tex
prop_iop.tex \subsection{Quantum $\delta$-deterministic Probability Measures} Added...

@@
 \newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
+% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
+% Change non-breaking space to \nolinebreak[1] 
+% Hence, it will not hyphenate too much surrounding words.
+\newcommand{\nb}{\nolinebreak[1] }
 
@@
 can also be formulated in the language of cryptodeterministic measure
-as in \ref{sec:MerminSquare}.
+as in section~\ref{subsec:Quantum-I_D-valued-Probability}.
 
@@
 \subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability
-Measures}
+Measures\label{subsec:Quantum-I_D-valued-Probability}}
 
@@
 
+\subsection{Quantum $\delta$-deterministic Probability Measures}
+
+Since there is no quantum $\mathscr{I}_{\mathrm{D}}$-valued probability
+measures, we want to know whether there is something which is almost
+quantum $\mathscr{I}_{\mathrm{D}}$-valued probability measures. This
+gives the following definition.
+
+\begin{definition}An interval-valued probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is called $\delta$-deterministic if either $\left[l,r\right]\subseteq\left[0,\delta\right]$
+or $\left[l,r\right]\subseteq\left[1-\delta,1\right]$ for every $\left[l,r\right]\in\mathscr{I}$.\end{definition}
+
+Given the preceding definition, theorem~\ref{thm:Kochen-Specker-expectation}
+says there is no quantum $0$-deterministic probability measures.
+In contrast, given a three-dimensional Hilbert space, there is $\frac{1}{3}$-deterministic
+probability measures\nb$\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $.
+The real problem is if we decrease $\delta$ from $\frac{1}{3}$,
+when quantum $\delta$-deterministic probability measures starts to
+disappear?
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-05-22 prop_iop.tex
prop_iop.tex \subsection{From Interval-valued to Real-valued} Added...

@@
 
+\subsection{From Real-valued to Interval-valued}
+
 \begin{definition}We say a pair~$\left(\mathscr{I},\iota\right)$
@@
 
+\subsection{From Interval-valued to Real-valued}
+
 Previously we discussed how to construct a quantum IVPM from a quantum
@@
 
-\begin{lemma}\label{lemma:QIVPM2QCM}Let $\mathscr{I}_{\mathrm{D}}$
-be $\left\{ \imposs,\necess\right\} $. Given a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
-then $\mu:\events\rightarrow\left[0,1\right]$ defined by 
+\begin{definition}An interval-valued probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is called $\delta$-deterministic if either $\left[l,r\right]\subseteq\left[0,\delta\right]$
+or $\left[l,r\right]\subseteq\left[1-\delta,1\right]$ for every $\left[l,r\right]\in\mathscr{I}$.\end{definition}
+
+For example, recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
+then a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $0$-deterministic.
+For another example, given a three-dimensional Hilbert space, $\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $
+is a $\frac{1}{3}$-deterministic. However, we will prove there is
+no $\delta$-deterministic probability measures for smaller $\delta$
+due to the Kochen-Specker theorem.
+
+\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
+and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+with $\delta<\left(1+d\right)^{-1}$, then $\mu:\events\rightarrow\left[0,1\right]$
+defined by 
 \begin{equation} 
 \mu(P)=\cases{ 
-0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
-1 & if $\bar{\mu}(P)=\necess$
+0 & if $\bar{\mu}(P)\subseteq\left[0,\delta\right]$ ;\\ 
+1 & if $\bar{\mu}(P)\subseteq\left[1-\delta,1\right]$
 }\end{equation}
@@
 & \pmeas\left(P\right)=0\\ 
-\Rightarrow & \bar{\mu}(P)=\imposs\\
-\Rightarrow & \bar{\mu}(\Omega\backslash P)=\left[1,1\right]-\imposs=\necess\\
-\Rightarrow & \pmeas\left(\Omega\backslash P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
+\Rightarrow & \bar{\mu}(P)\subseteq\left[0,\delta\right]\\
+\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
+\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
 }\end{equation}
-Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$.
+Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
 \item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
-disjoint events. 
+orthogonal events, we must have $N\le d$. Also, $\delta<\left(1+d\right)^{-1}\Rightarrow\delta\le d\delta<1-\delta$.
 \begin{itemize}
-\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1$, then we have $\necess=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
-so that $\necess=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=1=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
-\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0$, then we have $\imposs=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
-so that $\imposs=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=0=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
+\item If $\pmeas(P_{i})=0$ for all $i$, then
+\begin{equation}\eqalign{ 
+& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\subseteq\left[0,d\delta\right]\\
+\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
+\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
+}\end{equation}
+\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then
+\begin{equation}\eqalign{ 
+& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1+(N-1)\delta\right]\\
+\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[0,\delta\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[1-\delta,1\right]\\
+\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
+}\end{equation}
+\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
+for $i_{0}\ne i_{1}$, then
+\begin{equation}\eqalign{ 
+& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]\\
+\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[0,\delta\right]=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]\textrm{Ø}\textrm{ .}
+}\end{equation}
+A contradiction! Therefore, this case is impossible, and need no further
+discussion.
 \end{itemize}
@@
 \begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
-of dimension~$d\ge3$, there is no quantum interval-valued probability
-measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.\end{cor}
+of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
+probability measure for $\delta<\left(1+d\right)^{-1}$. When $\delta\ge\left(1+d\right)^{-1}$,
+there exists a quantum $\delta$-deterministic probability measure
+$\bar{\mu}:\events\rightarrow\mathscr{I}$ for some $\mathscr{I}$.\end{cor}
+
+\begin{proof}...\end{proof}
 
@@
 
-\subsection{Quantum $\delta$-deterministic Probability Measures}
-
-Since there is no quantum $\mathscr{I}_{\mathrm{D}}$-valued probability
-measures, we want to know whether there is something which is almost
-quantum $\mathscr{I}_{\mathrm{D}}$-valued probability measures. This
-gives the following definition.
-
-\begin{definition}An interval-valued probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is called $\delta$-deterministic if either $\left[l,r\right]\subseteq\left[0,\delta\right]$
-or $\left[l,r\right]\subseteq\left[1-\delta,1\right]$ for every $\left[l,r\right]\in\mathscr{I}$.\end{definition}
-
-Given the preceding definition, theorem~\ref{thm:Kochen-Specker-expectation}
-says there is no quantum $0$-deterministic probability measures.
-In contrast, given a three-dimensional Hilbert space, there is $\frac{1}{3}$-deterministic
-probability measures\nb$\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $.
-The real problem is if we decrease $\delta$ from $\frac{1}{3}$,
-when quantum $\delta$-deterministic probability measures starts to
-disappear?
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-05-22 prop_iop.tex
prop_letter.tex \subsection{From Interval-valued to Real-valued} Updating...

@@
 construct a quantum real-valued probability measure from a special
-kind of quantum IVPM.
-
-\begin{definition}An interval-valued probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+kind of quantum IVPMs.
+
+\begin{definition}\label{def:delta-deterministic}An interval-valued
+probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
 is called $\delta$-deterministic if either $\left[l,r\right]\subseteq\left[0,\delta\right]$
@@
 
-For example, recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
-then a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $0$-deterministic.
+Recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
+so that a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $0$-deterministic.
 For another example, given a three-dimensional Hilbert space, $\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $
 is a $\frac{1}{3}$-deterministic. However, we will prove there is
-no $\delta$-deterministic probability measures for smaller $\delta$
+no $\delta$-deterministic probability measures for small $\delta$
 due to the Kochen-Specker theorem.
@@
 \begin{equation}\eqalign{ 
-& \pmeas\left(P\right)=0\\ 
-\Rightarrow & \bar{\mu}(P)\subseteq\left[0,\delta\right]\\
+& \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
 \Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
@@
 \item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
-orthogonal events, we must have $N\le d$. Also, $\delta<\left(1+d\right)^{-1}\Rightarrow\delta\le d\delta<1-\delta$.
+orthogonal events, we must have $N\le d$. 
 \begin{itemize}
@@
 & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\subseteq\left[0,d\delta\right]\\
-\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
+\overset{d\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
 \Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
@@
 & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1+(N-1)\delta\right]\\
-\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[0,\delta\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[1-\delta,1\right]\\
-\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
+\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[1-\delta,1\right]\Rightarrow\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
 }\end{equation}
@@
 for $i_{0}\ne i_{1}$, then
-\begin{equation}\eqalign{ 
-& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]\\
-\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[0,\delta\right]=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]\textrm{Ø}\textrm{ .}
-}\end{equation}
-A contradiction! Therefore, this case is impossible, and need no further
-discussion.
+\begin{equation}
+\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]
+\end{equation}
+which contradicts to definition~\ref{def:delta-deterministic} so
+that this case is impossible.
 \end{itemize}
@@
 of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
-probability measure for $\delta<\left(1+d\right)^{-1}$. When $\delta\ge\left(1+d\right)^{-1}$,
-there exists a quantum $\delta$-deterministic probability measure
-$\bar{\mu}:\events\rightarrow\mathscr{I}$ for some $\mathscr{I}$.\end{cor}
-
-\begin{proof}...\end{proof}
+probability measure for $\delta<\left(1+d\right)^{-1}$. \end{cor}
 

### 2017-05-23 prop_letter.tex
prop_letter.tex ...
prop_iop.tex \subsection{Quantum $\delta$-deterministic Probability Measures} Added...
prop_letter.tex \section{Kochen-Specker} Merge results from prop_iop.tex

@@
 \newcommand{\nb}{\nolinebreak[1] }
-\hyphenation{cryp-to-de-ter-min-is-tic cryp-to-de-ter-min-ism}
 
@@
 
-For example, assuming the three intervals $\imposs$, $\necess$, and
+For example, assuming the three intervals \imposs, \necess, and
 $\unknown=\left[0,1\right]$, then:
@@
 satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
+
+According to Mermin's comment\nb\cite{Mermin1999},
+\begin{quote}
+...although the outcomes deduced from such imperfect measurements
+will occasionally differ dramatically from those allowed in the ideal
+case, if the misalignment is very slight, the statistical distribution
+of outcomes will differ only slightly from the ideal case...
+\end{quote}
+if the imperfection of the measurement is small enough, the finitely
+precise measurement should not nullify the Kochen-Specker theorem.
+This idea can be modeled precisely by QIVPMs.
+
+\begin{definition}\label{def:delta-deterministic}An interval-valued
+probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is called $\delta$-deterministic if either $\left[\ell,r\right]\subseteq\left[0,\delta\right]$
+or $\left[\ell,r\right]\subseteq\left[1-\delta,1\right]$ for every
+$\left[\ell,r\right]\in\mathscr{I}$.\end{definition}
+
+For example, any cryptodeterministic QIVPM is $0$-deterministic.
+For another example, given a three-dimensional Hilbert space, 
+\begin{equation}
+\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
+\end{equation}
+is a $\frac{1}{3}$-deterministic, where $\iota_{\infty}\left(x\right)=\left[x,x\right]$.
+However, we will prove there is no $\delta$-deterministic probability
+measures for small $\delta$ due to the Kochen-Specker theorem.
+
+\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
+and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+with $\delta<\left(1+d\right)^{-1}$, then $\mu:\events\rightarrow\left[0,1\right]$
+defined by
+\begin{equation}
+\mu(P)=\begin{cases}
+0 & \textrm{if }\bar{\mu}(P)\subseteq\left[0,\delta\right]\textrm{ ;}\\
+1 & \textrm{if }\bar{\mu}(P)\subseteq\left[1-\delta,1\right]
+\end{cases}
+\end{equation}
+ is a cryptodeterministic quantum probability measure.\end{lemma}
+
+\begin{proof}~
+\begin{itemize}
+\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
+\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
+\item For every event $P$, we have\begin{subequations}
+\begin{eqnarray}
+ &  & \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
+ & \Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
+ & \Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
+\end{eqnarray}
+\end{subequations}Similarly, when $\pmeas\left(P\right)=1$, we also
+have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
+\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
+orthogonal events, we must have $N\le d$. 
+\begin{itemize}
+\item If $\pmeas(P_{i})=0$ for all $i$, then\begin{subequations}
+\begin{eqnarray}
+ &  & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\\
+ & \overset{d\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\\
+ & \Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
+ & \Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
+\end{eqnarray}
+\end{subequations}
+\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then\begin{subequations}
+\begin{eqnarray}
+ &  & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1\right]\\
+ & \Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
+\end{eqnarray}
+\end{subequations}
+\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
+for $i_{0}\ne i_{1}$, then
+\begin{equation}
+\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]
+\end{equation}
+which contradicts to definition~\ref{def:delta-deterministic} so
+that this case is impossible.
+\end{itemize}
+\end{itemize}
+\end{proof}
+
+Together with the Kochen-Specker theorem, we will have the following
+corollary.
+
+\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
+of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
+probability measure for $\delta<\left(1+d\right)^{-1}$. \end{cor}
 

### 2017-05-24 prop_iop.tex
prop_letter.tex \section{Kochen-Specker} Improving the bound...

@@
 and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-with $\delta<\left(1+d\right)^{-1}$, then $\mu:\events\rightarrow\left[0,1\right]$
+with $\delta<\frac{1}{3}$, then $\mu:\events\rightarrow\left[0,1\right]$
 defined by 
@@
 Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
-\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
-orthogonal events, we must have $N\le d$. 
+\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
+have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})$.
+Without loss of generality, there are two cases:
 \begin{itemize}
-\item If $\pmeas(P_{i})=0$ for all $i$, then
+\item If $\pmeas\left(P_{0}\right)=\pmeas\left(P_{1}\right)=0$, then
 \begin{equation}\eqalign{ 
-& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\subseteq\left[0,d\delta\right]\\
-\overset{d\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
-\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
+& \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[0,2\delta\right]\\
+\overset{2\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset\Rightarrow\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]\\
+\Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=0=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
 }\end{equation}
-\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then
+\item If $\pmeas\left(P_{0}\right)=0$ and $\pmeas\left(P_{1}\right)=1$,
+then
 \begin{equation}\eqalign{ 
-& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1+(N-1)\delta\right]\\
-\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[1-\delta,1\right]\Rightarrow\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
+& \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[1-\delta,1\right]\\
+\Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=1=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
 }\end{equation}
-\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
-for $i_{0}\ne i_{1}$, then
-\begin{equation}
-\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]
-\end{equation}
-which contradicts to definition~\ref{def:delta-deterministic} so
-that this case is impossible.
 \end{itemize}
+Therefore, we always have $\pmeas\left(P_{0}+P_{1}\right)=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)$.
+By induction, we have $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$
+for any mutually orthogonal events\nb$\left\{ P_{i}\right\} _{i=1}^{N}$. 
 \end{itemize}
@@
 of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
-probability measure for $\delta<\left(1+d\right)^{-1}$. \end{cor}
+probability measure for $\delta<\frac{1}{3}$.\end{cor}
 

### 2017-05-24 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Improving the bound...

@@
 and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-with $\delta<\left(1+d\right)^{-1}$, then $\mu:\events\rightarrow\left[0,1\right]$
+with $\delta<\frac{1}{3}$, then $\mu:\events\rightarrow\left[0,1\right]$
 defined by
@@
 have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
-\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
-orthogonal events, we must have $N\le d$. 
+\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
+have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})$.
+Without loss of generality, there are two cases:
 \begin{itemize}
-\item If $\pmeas(P_{i})=0$ for all $i$, then\begin{subequations}
+\item If $\pmeas\left(P_{0}\right)=\pmeas\left(P_{1}\right)=0$, then\begin{subequations}
 \begin{eqnarray}
- &  & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\\
- & \overset{d\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\\
- & \Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
- & \Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
+ &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[0,2\delta\right]\\
+ & \overset{2\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset\\
+ & \Rightarrow & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]\\
+ & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=0=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
 \end{eqnarray}
 \end{subequations}
-\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then\begin{subequations}
+\item If $\pmeas\left(P_{0}\right)=0$ and $\pmeas\left(P_{1}\right)=1$,
+then\begin{subequations}
 \begin{eqnarray}
- &  & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1\right]\\
- & \Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
+ &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[1-\delta,1\right]\\
+ & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=1=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
 \end{eqnarray}
 \end{subequations}
-\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
-for $i_{0}\ne i_{1}$, then
-\begin{equation}
-\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]
-\end{equation}
-which contradicts to definition~\ref{def:delta-deterministic} so
-that this case is impossible.
 \end{itemize}
+Therefore, we always have $\pmeas\left(P_{0}+P_{1}\right)=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)$.
+By induction, we have $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$
+for any mutually orthogonal events\nb$\left\{ P_{i}\right\} _{i=1}^{N}$. 
 \end{itemize}
@@
 of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
-probability measure for $\delta<\left(1+d\right)^{-1}$. \end{cor}
+probability measure for $\delta<\frac{1}{3}$. \end{cor}
 

### 2017-05-25 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Simplify the proof a little bit
Updated by Prof. Hanson

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+%\section{Introduction}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Fuzzy Measurements}
+%\section{Fuzzy Measurements}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Intervals of Uncertainty}
+%\section{Intervals of Uncertainty}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Kochen-Specker}
+%\section{Kochen-Specker}
 
@@
 and derive a contradiction using the following nine ``Mermin-Peres square''
-observables\nb\cite{Mermin1990Simple,peres1995quantum}:
+observables $\mathbf{O}_{ij}$\nb\cite{Mermin1990Simple,peres1995quantum}:
 \begin{center}
@@
 Therefore, it is clear impossible to find a IVPM\nb$\bar{\mu}$ such
-that 
-\begin{equation}
-\begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
-\langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
-\langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
-\end{aligned}
-\label{eq:MerminSquare-values}
-\end{equation}
+that $\langle \mathbf{O}_{ij}\rangle_{\bar \mu}$
+%\begin{equation}
+%\begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} %& \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
+%\langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & %\otimes\sigma_{x}\rangle_{\bar{\mu}}\\
+%\langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & %\otimes\sigma_{y}\rangle_{\bar{\mu}}
+%\end{aligned}
+%\label{eq:MerminSquare-values}
+%\end{equation}
 satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
@@
 \end{itemize}
-Therefore, we always have $\pmeas\left(P_{0}+P_{1}\right)=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)$.
-By induction, we have $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$
-for any mutually orthogonal events\nb$\left\{ P_{i}\right\} _{i=1}^{N}$. 
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Gleason}
+%\section{Gleason}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
+%\section{Conclusion}
 

### 2017-06-05 prop_iop.tex
prop_iop.tex \subsection{From Interval-valued to Real-valued} Updating..

@@
 
-\begin{lemma}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
+\begin{lemma}\label{lemma:real2interval}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
 Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
@@
 probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is called $\delta$-deterministic if either $\left[l,r\right]\subseteq\left[0,\delta\right]$
-or $\left[l,r\right]\subseteq\left[1-\delta,1\right]$ for every $\left[l,r\right]\in\mathscr{I}$.\end{definition}
+is called $\left(1/n,\delta\right)$-deterministic if for every $\left[l,r\right]\in\mathscr{I}$,
+there is a $k\in\mathbb{Z}$ such that $\left[l,r\right]\subseteq\left[k/n-\delta,k/n+\delta\right]$.\end{definition}
 
 Recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-so that a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $0$-deterministic.
-For another example, given a three-dimensional Hilbert space, $\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $
-is a $\frac{1}{3}$-deterministic. However, we will prove there is
-no $\delta$-deterministic probability measures for small $\delta$
-due to the Kochen-Specker theorem.
+so that a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $\left(1,0\right)$-deterministic.
+For another example, given a three-dimensional Hilbert space, 
+\begin{equation}
+\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
+\end{equation}
+is a $\left(1,\frac{1}{3}\right)$-deterministic and $\left(\frac{1}{3},0\right)$-deterministic.
+However, we will prove there is generally no $\left(1/n,\delta\right)$-deterministic
+probability measures when $\delta$ is much smaller than $1/n$.
 
 \begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
-and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-with $\delta<\frac{1}{3}$, then $\mu:\events\rightarrow\left[0,1\right]$
-defined by 
-\begin{equation} 
-\mu(P)=\cases{ 
-0 & if $\bar{\mu}(P)\subseteq\left[0,\delta\right]$ ;\\ 
-1 & if $\bar{\mu}(P)\subseteq\left[1-\delta,1\right]$
-}\end{equation}
-is a cryptodeterministic measure.\end{lemma}
+and a quantum $\left(1/n,\delta\right)$-deterministic probability
+measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<1/\left(3n\right)$,
+if $\bar{\mu}(P)\subseteq\left[k/n-\delta,k/n+\delta\right]$, let
+$\mu(P)=k/n$, then $\mu:\events\rightarrow\left[0,1\right]$ is a
+quantum IVPM. In another word, $\iota_{\infty}\circ\mu$ is $\left(1/n,0\right)$-deterministic
+by lemma~\ref{lemma:real2interval}.\end{lemma}
 
@@
 \begin{equation}\eqalign{ 
-& \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
-\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
-\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
+& \pmeas\left(P\right)=\frac{k}{n}\Rightarrow\bar{\mu}(P)\subseteq\left[\frac{k}{n}-\delta,\frac{k}{n}+\delta\right]\\
+\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\frac{k}{n}-\delta,1-\frac{k}{n}+\delta\right]\\
+\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1-\frac{k}{n}=1-\pmeas\left(P\right)\textrm{ .}
 }\end{equation}
-Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
-\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
-have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})$.
-Without loss of generality, there are two cases:
-\begin{itemize}
-\item If $\pmeas\left(P_{0}\right)=\pmeas\left(P_{1}\right)=0$, then
-\begin{equation}\eqalign{ 
-& \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[0,2\delta\right]\\
-\overset{2\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset\Rightarrow\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]\\
-\Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=0=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
-}\end{equation}
-\item If $\pmeas\left(P_{0}\right)=0$ and $\pmeas\left(P_{1}\right)=1$,
-then
-\begin{equation}\eqalign{ 
-& \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[1-\delta,1\right]\\
-\Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=1=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
-}\end{equation}
-\end{itemize}
-Therefore, we always have $\pmeas\left(P_{0}+P_{1}\right)=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)$.
+\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, let
+$\pmeas\left(P_{0}\right)=k_{0}/n$ and $\pmeas\left(P_{1}\right)=k_{1}/n$.
+Then, 
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[\frac{k_{0}+k_{1}}{n}-2\delta,\frac{k_{0}+k_{1}}{n}+2\delta\right]\textrm{ .}
+\end{equation}
+Since $\delta<1/\left(3n\right)$, we have
+\begin{equation}
+\frac{k_{0}+k_{1}-1}{n}+\delta<\frac{k_{0}+k_{1}}{n}-2\delta\le\frac{k_{0}+k_{1}}{n}+2\delta<\frac{k_{0}+k_{1}+1}{n}-\delta\textrm{ .}
+\end{equation}
+The previous inequality implies that if$\bar{\mu}\left(P_{0}+P_{1}\right)$
+overlap with any interval of the form $\left[k/n-\delta,k/n+\delta\right]$
+for some $k$, $k$ must be $k_{0}+k_{1}$, i.e., 
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-\delta,\frac{k_{0}+k_{1}}{n}+\delta\right]\textrm{ .}
+\end{equation}
+Therefore, 
+\begin{equation}
+\pmeas\left(P_{0}+P_{1}\right)=\frac{k_{0}+k_{1}}{n}=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
+\end{equation}
 By induction, we have $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$
@@
 \begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
-of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
+of dimension\nb$d\ge3$, there is no quantum $\left(1,\delta\right)$-deterministic
 probability measure for $\delta<\frac{1}{3}$.\end{cor}
+
+In general~\cite{Redhead1987-REDINA}, Gleason's theorem asserts
+that a quantum probability measure must be continuous. Therefore,
+a $\left(1/n,0\right)$-deterministic QIVPM exists if and only if
+$d\mid n$, and so does a $\left(1/n,\delta\right)$-deterministic
+QIVPM for $\delta<1/\left(3n\right)$.
 

### 2017-06-05 prop_iop.tex
prop_letter.tex Merge change from prop_iop.tex...

@@
 \end{equation}
-is a $\left(1,\frac{1}{3}\right)$-deterministic and $\left(\frac{1}{3},0\right)$-deterministic.
+is $\left(1,\frac{1}{3}\right)$-deterministic and $\left(\frac{1}{3},0\right)$-deterministic.
 However, we will prove there is generally no $\left(1/n,\delta\right)$-deterministic
@@
 $\mu(P)=k/n$, then $\mu:\events\rightarrow\left[0,1\right]$ is a
-quantum IVPM. In another word, $\iota_{\infty}\circ\mu$ is $\left(1/n,0\right)$-deterministic
-by lemma~\ref{lemma:real2interval}.\end{lemma}
+quantum probability measure. In another word, $\iota_{\infty}\circ\mu$
+is $\left(1/n,0\right)$-deterministic by lemma~\ref{lemma:real2interval}.\end{lemma}
 
@@
 \end{equation}
-The previous inequality implies that if$\bar{\mu}\left(P_{0}+P_{1}\right)$
+The previous inequality implies that if $\bar{\mu}\left(P_{0}+P_{1}\right)$
 overlap with any interval of the form $\left[k/n-\delta,k/n+\delta\right]$

### 2017-06-05 prop_letter.tex
prop_letter.tex Merge change from prop_iop.tex...

@@
 probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is called $\delta$-deterministic if either $\left[\ell,r\right]\subseteq\left[0,\delta\right]$
-or $\left[\ell,r\right]\subseteq\left[1-\delta,1\right]$ for every
-$\left[\ell,r\right]\in\mathscr{I}$.\end{definition}
-
-For example, any cryptodeterministic QIVPM is $0$-deterministic.
+is called $\left(1/n,\delta\right)$-deterministic if for every $\left[\ell,r\right]\in\mathscr{I}$,
+there is a $k\in\mathbb{Z}$ such that $\left[\ell,r\right]\subseteq\left[k/n-\delta,k/n+\delta\right]$.\end{definition}
+
+For example, any cryptodeterministic QIVPM is $\left(1,0\right)$-deterministic.
 For another example, given a three-dimensional Hilbert space, 
@@
 \end{equation}
-is a $\frac{1}{3}$-deterministic, where $\iota_{\infty}\left(x\right)=\left[x,x\right]$.
-However, we will prove there is no $\delta$-deterministic probability
-measures for small $\delta$ due to the Kochen-Specker theorem.
+is $\left(1,\frac{1}{3}\right)$-deterministic and $\left(\frac{1}{3},0\right)$-deterministic,
+where $\iota_{\infty}\left(x\right)=\left[x,x\right]$. However, we
+will prove there is generally no $\left(1/n,\delta\right)$-deterministic
+probability measures when $\delta$ is much smaller than $1/n$.
 
 \begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
-and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-with $\delta<\frac{1}{3}$, then $\mu:\events\rightarrow\left[0,1\right]$
-defined by 
-\begin{equation}
-\mu(P)=\begin{cases}
-0 & \textrm{if }\bar{\mu}(P)\subseteq\left[0,\delta\right]\textrm{ ;}\\
-1 & \textrm{if }\bar{\mu}(P)\subseteq\left[1-\delta,1\right]
-\end{cases}
-\end{equation}
-is a cryptodeterministic quantum probability measure.\end{lemma}
-
-\begin{proof}~ 
-\begin{itemize}
-\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$. 
-\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$. 
-\item For every event $P$, we have\begin{subequations} 
+and a quantum $\left(1/n,\delta\right)$-deterministic probability
+measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<1/\left(3n\right)$,
+if $\bar{\mu}(P)\subseteq\left[k/n-\delta,k/n+\delta\right]$, let
+$\mu(P)=k/n$, then $\mu:\events\rightarrow\left[0,1\right]$ is a
+quantum probability measure. In another word, $\iota_{\infty}\circ\mu$
+is $\left(1/n,0\right)$-deterministic.\end{lemma}
+
+\begin{proof} The essential part to verify $\mu$ is a quantum probability
+measure is to verify Eq.~(\ref{eq:QuantumProbability-Addition}). Given a pair of orthogonal
+operators\nb$P_{0}$ and $P_{1}$, let $\pmeas\left(P_{0}\right)=k_{0}/n$ and $\pmeas\left(P_{1}\right)=k_{1}/n$.
+Then, 
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-2\delta,\frac{k_{0}+k_{1}}{n}+2\delta\right]\textrm{ .}
+\end{equation}
+Since $\delta<1/\left(3n\right)$, we have
+\begin{subequations}
 \begin{eqnarray}
- &  & \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
- & \Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
- & \Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
-\end{eqnarray}
-\end{subequations}Similarly, when $\pmeas\left(P\right)=1$, we also
-have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$. 
-\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
-have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})$.
-Without loss of generality, there are two cases: 
-\begin{itemize}
-\item If $\pmeas\left(P_{0}\right)=\pmeas\left(P_{1}\right)=0$, then\begin{subequations}
-\begin{eqnarray}
- &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[0,2\delta\right]\\
- & \overset{2\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset\\
- & \Rightarrow & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]\\
- & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=0=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
+\frac{k_{0}+k_{1}-1}{n}+\delta&<&\frac{k_{0}+k_{1}}{n}-2\delta\\
+\frac{k_{0}+k_{1}}{n}+2\delta&<&\frac{k_{0}+k_{1}+1}{n}-\delta\textrm{ .}
 \end{eqnarray}
 \end{subequations}
-\item If $\pmeas\left(P_{0}\right)=0$ and $\pmeas\left(P_{1}\right)=1$,
-then\begin{subequations} 
-\begin{eqnarray}
- &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[1-\delta,1\right]\\
- & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=1=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
-\end{eqnarray}
-\end{subequations} 
-\end{itemize}
-\end{itemize}
+The previous inequalities imply that if $\bar{\mu}\left(P_{0}+P_{1}\right)$
+overlap with any interval of the form $\left[k/n-\delta,k/n+\delta\right]$
+for some $k$, $k$ must be $k_{0}+k_{1}$, i.e., 
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-\delta,\frac{k_{0}+k_{1}}{n}+\delta\right]\textrm{ .}
+\end{equation}
+Therefore, 
+\begin{equation}
+\pmeas\left(P_{0}+P_{1}\right)=\frac{k_{0}+k_{1}}{n}=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
+\end{equation}
 \end{proof}
@@
 \begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
-of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
-probability measure for $\delta<\frac{1}{3}$. \end{cor}
+of dimension\nb$d\ge3$, there is no quantum $\left(1,\delta\right)$-deterministic
+probability measure for $\delta<\frac{1}{3}$.\end{cor}
+
+In general~\cite{Redhead1987-REDINA}, Gleason's theorem asserts
+that a quantum probability measure must be continuous. Therefore,
+a $\left(1/n,0\right)$-deterministic QIVPM exists if and only if
+$d\mid n$, and so does a $\left(1/n,\delta\right)$-deterministic
+QIVPM for $\delta<1/\left(3n\right)$.
 

### 2017-06-06 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

@@
 
-\begin{definition}We say a pair~$\left(\mathscr{I},\iota\right)$
-is regular\footnote{\yutsung{''regular'' is just a random name pop into my mind...
-
-This whole definition might be rewritten using category theory...
-I would investigate it if it is necessary...}} if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+\begin{definition}We say a pair\nb$\left(\mathscr{I},\iota\right)$
+is additive\footnote{\yutsung{This whole definition might be rewritten using category
+theory... I would investigate it if it is necessary...}} if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 is a function satisfying the following properties. 
@@
 \item For any $x\in\left[0,1\right]$, $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$. 
-\item For a set $\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
+\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
 if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota\left(x_{i}\right)$. 
 \end{itemize}
-\end{definition}
-
-\begin{lemma}\label{lemma:real2interval}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
-Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
-a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
-$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM.\end{lemma}
+Moreover, $\left(\mathscr{I},\iota\right)$ is called convex if for
+any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
+if $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}
+
+\begin{lemma}\label{lemma:real2interval}Consider an additive pair\nb$\left(\mathscr{I},\iota\right)$.
+Then, given a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$,
+a function\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
+$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM. Moreover,
+if $\left(\mathscr{I},\iota\right)$ is convex, then $\bar{\mu}(P)$
+is a convex.\end{lemma}
 
@@
 \item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
-\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
+\item For a set of mutually orthogonal projections\nb$\left\{ P_{i}\right\} _{i=1}^{N}$,
 we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)=\mu\left(\sum_{i=1}^{N}P_{i}\right)\in\left[0,1\right]$
 so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
+\item For convexity part, given a pair of commuting operators\nb$P_{0}$
+and $P_{1}$, they and $P_{0}\vee P_{1}$ can be expressed by the
+summation among $P_{0}\left(\mathbb{1}-P_{1}\right)$, $\left(\mathbb{1}-P_{0}\right)P_{1}$,
+and $P_{0}P_{1}$. Hence, 
+\begin{equation}\eqalign{ 
+ & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\iota\left(\mu\left(P_{0}\vee P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
+= & \iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
+\subseteq&\iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)\\
+= & \iota\left(\mu\left(P_{0}\right)\right)+\iota\left(\mu\left(P_{1}\right)\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right) 
+}\end{equation}
 \end{itemize}
@@
 
-\begin{lemma}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
-Then, there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.\end{lemma}
+\begin{lemma}Consider an additive pair\nb$\left(\mathscr{I},\iota\right)$.
+Then, there is a quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.
+Obviously, if $\left(\mathscr{I},\iota\right)$ is convex, so does
+$\bar{\mu}$.\end{lemma}
 
@@
 \begin{example}\label{ex:regular-pair}For any positive integer~$n$,
-there is a regular pair~$\left(\mathscr{I}_{n},\iota_{n}\right)$
+there is an additive pair\nb$\left(\mathscr{I}_{n},\iota_{n}\right)$
 defined by 

### 2017-06-11 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

@@
 \newcommand{\nb}{\nolinebreak[1] }
+\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
+\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}
 
@@
 
+Recall that given a set of intervals\nb$\mathscr{I}$, we want to
+know whether there is an QIVPM mapping to $\mathscr{I}$. If there
+is a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we want
+to verify whether $\bar{\mu}$ has a non-empty core. Usually, the
+easiest way to prove the existence is to construct an example. As
+in example~\ref{ex:three-dimensional-5-value}, constructing a QIVPM
+directly is long and tedious. In contrast, a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$
+can be easily constructed by the Born rule. Therefore, it would be
+desirable if we can construct a QIVPM\nb$\bar{\mu}$ from $\mu$,
+and expect $\mu$ is in the core of $\bar{\mu}$.
+
+Notice that the range of $\mu$ and $\bar{\mu}$ are different. If
+there is a good function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
+then a QIVPM can be easily defined by function composition\nb$\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
+This gives the following definition.
+
 \begin{definition}We say a pair\nb$\left(\mathscr{I},\iota\right)$
@@
 if $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}
+
+Although a convex pair\nb$\left(\mathscr{I},\iota\right)$ may look
+exotic, the left end of $\iota$, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
+is the well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
+After we define\nb$\left(\mathscr{I},\iota\right)$, we are ready
+to construct a QIVPM from a quantum probability measure.
 
@@
 \end{proof}
+
+Although a QIVPM can be constructed by an additive pair easily, a
+convex pair may not give a convex QIVPM with non-trivial finite number
+of intervals. Notice a Wright-convex function is midpoint-convex or
+Jensen-convex, i.e., 
+\begin{equation}
+\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\textrm{ ,}
+\end{equation}
+and a midpoint-convex function is continuous on an open interval if
+we cannot use the Axiom of Choices\nb\cite{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
+Therefore, for any convex QIVPM constructed by a convex pair\nb$\left(\mathscr{I},\iota\right)$,
+$\mathscr{I}$ must either be $\left\{ \necess,\imposs,\unknown\right\} $
+or contain infinitely many intervals.
 

### 2017-06-11 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

@@
 Notice that the range of $\mu$ and $\bar{\mu}$ are different. If
-there is a good function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
-then a QIVPM can be easily defined by function composition\nb$\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
-This gives the following definition.
+there is a ``homomorphism''\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+preserving the desiring properties of the ranges, then we could easily
+inducing a map from quantum real-valued probability measures to QIVPMs
+by function composition\nb$\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
+This idea gives the following definition.
 
 \begin{definition}We say a pair\nb$\left(\mathscr{I},\iota\right)$
-is additive\footnote{\yutsung{This whole definition might be rewritten using category
-theory... I would investigate it if it is necessary...}} if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is additive if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 is a function satisfying the following properties. 
@@
 any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
-if $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}
+$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}
 
@@
 exotic, the left end of $\iota$, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
-is the well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
+is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
 After we define\nb$\left(\mathscr{I},\iota\right)$, we are ready
@@
 \item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$.
-\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
+\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
 \item For a set of mutually orthogonal projections\nb$\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)=\mu\left(\sum_{i=1}^{N}P_{i}\right)\in\left[0,1\right]$
-so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
+we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)\in\left[0,1\right]$
+so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
 \item For convexity part, given a pair of commuting operators\nb$P_{0}$
@@
 \begin{equation}\eqalign{ 
- & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\iota\left(\mu\left(P_{0}\vee P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
+ & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
 = & \iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
 \subseteq&\iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)\\
-= & \iota\left(\mu\left(P_{0}\right)\right)+\iota\left(\mu\left(P_{1}\right)\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right) 
+= & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right) 
 }\end{equation}

### 2017-06-12 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

@@
 is a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we want
-to verify whether $\bar{\mu}$ has a non-empty core. Usually, the
-easiest way to prove the existence is to construct an example. As
-in example~\ref{ex:three-dimensional-5-value}, constructing a QIVPM
-directly is long and tedious. In contrast, a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$
-can be easily constructed by the Born rule. Therefore, it would be
-desirable if we can construct a QIVPM\nb$\bar{\mu}$ from $\mu$,
-and expect $\mu$ is in the core of $\bar{\mu}$.
+to further verify whether $\bar{\mu}$ has a non-empty core. Usually,
+the easiest way to prove the existence is to construct an example.
+As in example~\ref{ex:three-dimensional-5-value}, constructing a
+QIVPM directly is long and tedious. In contrast, a quantum probability
+measure\nb$\mu:\events\rightarrow\left[0,1\right]$ can be easily
+constructed by the Born rule. Therefore, it would be desirable if
+we can construct a QIVPM\nb$\bar{\mu}$ from $\mu$, and expect $\mu$
+is in the core of $\bar{\mu}$.
 
@@
 we cannot use the Axiom of Choices\nb\cite{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
-Therefore, for any convex QIVPM constructed by a convex pair\nb$\left(\mathscr{I},\iota\right)$,
+Therefore, for any convex pair\nb$\left(\mathscr{I},\iota\right)$,
 $\mathscr{I}$ must either be $\left\{ \necess,\imposs,\unknown\right\} $
 or contain infinitely many intervals.
+
+Although a pair\nb$\left(\mathscr{I},\iota\right)$ is not convex,
+it can still induce a convex QIVPM. In particular, every QIVPM on
+a three-dimensional Hilbert space is convex by theorem~\ref{thm:convex-3}.
+The next natural question is whether a non-convex pair always induces
+some non-convex QIVPM, and the answer is ``yes'' by the following
+lemma.
+
+\begin{lemma}Given an additive but non-convex pair\nb$\left(\mathscr{I},\iota\right)$,
+there is a non-convex quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$.\end{lemma}
+
+\begin{proof}Since $\left(\mathscr{I},\iota\right)$ is additive
+but non-convex, there are three numbers\nb$x_{0}$, $x_{1}$, and
+$x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
+but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
+Consider a 4-dimensional Hilbert space and a density matrix
+\begin{equation}
+\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\textrm{ .}
+\end{equation}
+Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}(P)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(P)\right)$.
+Then,
+\begin{equation}\eqalign{ 
+ & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)
+=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{0}+\proj{1}+\proj{2})\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{2})\right)\\ 
+= & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)
+\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\\ 
+= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{0}+\proj{2})\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{1}+\proj{2})\right)
+=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ .} 
+}\end{equation}
+\end{proof}
 

### 2017-06-12 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

@@
 a function\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
-$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM. Moreover,
-if $\left(\mathscr{I},\iota\right)$ is convex, then $\bar{\mu}(P)$
-is a convex.\end{lemma}
+$\bar{\mu}\left(P\right)=\iota\left(\mu\left(P\right)\right)$ is
+a quantum IVPM. Moreover, if $\left(\mathscr{I},\iota\right)$ is
+convex, then $\bar{\mu}$ is convex.\end{lemma}
 
@@
 \item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$.
-\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
+\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(1-\mu\left(P\right)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
 \item For a set of mutually orthogonal projections\nb$\left\{ P_{i}\right\} _{i=1}^{N}$,
@@
 
-\begin{proof}Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}(P)\right)$.
+\begin{proof}Consider $\bar{\mu}\left(P\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
 Then, $\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
@@
 and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
-$\left(\mathscr{I}_{\infty},\iota_{\infty}\right)$ is a regular pair.\end{example}
+$\left(\mathscr{I}_{\infty},\iota_{\infty}\right)$ is an additive
+pair.\end{example}
 
@@
 
-Although a QIVPM can be constructed by an additive pair easily, a
-convex pair may not give a convex QIVPM with non-trivial finite number
-of intervals. Notice a Wright-convex function is midpoint-convex or
-Jensen-convex, i.e., 
+Although a convex QIVPM can be constructed by a convex pair easily,
+any convex pair either is $\left\{ \necess,\imposs,\unknown\right\} $
+or contains infinitely many intervals. The reason is that a Wright-convex
+function is midpoint-convex or Jensen-convex, i.e., 
 \begin{equation}
@@
 we cannot use the Axiom of Choices\nb\cite{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
-Therefore, for any convex pair\nb$\left(\mathscr{I},\iota\right)$,
-$\mathscr{I}$ must either be $\left\{ \necess,\imposs,\unknown\right\} $
-or contain infinitely many intervals.
-
-Although a pair\nb$\left(\mathscr{I},\iota\right)$ is not convex,
-it can still induce a convex QIVPM. In particular, every QIVPM on
-a three-dimensional Hilbert space is convex by theorem~\ref{thm:convex-3}.
+
+Even if an additive pair\nb$\left(\mathscr{I},\iota\right)$ is not
+convex, it may still induce a convex QIVPM. In particular, every QIVPM
+on a three-dimensional Hilbert space is convex by theorem~\ref{thm:convex-3}.
 The next natural question is whether a non-convex pair always induces
@@
 \end{equation}
-Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}(P)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(P)\right)$.
+Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}\left(P\right)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
 Then,
@@
  & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)
-=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{0}+\proj{1}+\proj{2})\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{2})\right)\\ 
+=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\ 
 = & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)
 \nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\\ 
-= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{0}+\proj{2})\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{1}+\proj{2})\right)
+= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)
 =\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ .} 
@@
 \end{proof}
+
+In conclusion, we may still use an additive but non-convex pair to
+construct QIVPMs, but we need to verify the convexity of the constructed
+QIVPM one-by-one which might be long and tedious.
 

### 2017-06-13 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Change "pair" to "interval-valued function"...

@@
 
-\begin{definition}We say a pair\nb$\left(\mathscr{I},\iota\right)$
-is additive if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-is a function satisfying the following properties. 
+\begin{definition}Given $\mathscr{I}$ is a collection of intervals,
+we say a interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is additive if $\iota$ satisfies the following properties. 
 \begin{itemize}
@@
 \end{itemize}
-Moreover, $\left(\mathscr{I},\iota\right)$ is called convex if for
-any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
-$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}
-
-Although a convex pair\nb$\left(\mathscr{I},\iota\right)$ may look
-exotic, the left end of $\iota$, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
+Moreover, $\iota$ is called convex if for any three numbers\nb$x_{0}$,
+$x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
+implies $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}
+
+Although a convex interval-valued function\nb$\iota$ may look exotic,
+its left end, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
 is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
-After we define\nb$\left(\mathscr{I},\iota\right)$, we are ready
-to construct a QIVPM from a quantum probability measure.
-
-\begin{lemma}\label{lemma:real2interval}Consider an additive pair\nb$\left(\mathscr{I},\iota\right)$.
-Then, given a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$,
+After we define interval-valued function, we are ready to construct
+a QIVPM from a quantum probability measure.
+
+\begin{lemma}\label{lemma:real2interval}Consider an additive interval-valued
+function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$. Then,
+given a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$,
 a function\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
 $\bar{\mu}\left(P\right)=\iota\left(\mu\left(P\right)\right)$ is
-a quantum IVPM. Moreover, if $\left(\mathscr{I},\iota\right)$ is
-convex, then $\bar{\mu}$ is convex.\end{lemma}
+a quantum IVPM. Moreover, if $\iota$ is convex, then $\bar{\mu}$
+is convex.\end{lemma}
 
@@
 
-\begin{lemma}Consider an additive pair\nb$\left(\mathscr{I},\iota\right)$.
+\begin{lemma}Consider an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
 Then, there is a quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.
-Obviously, if $\left(\mathscr{I},\iota\right)$ is convex, so does
-$\bar{\mu}$.\end{lemma}
+Obviously, if $\iota$ is convex, so does $\bar{\mu}$.\end{lemma}
 
@@
 \begin{example}\label{ex:regular-pair}For any positive integer~$n$,
-there is an additive pair\nb$\left(\mathscr{I}_{n},\iota_{n}\right)$
+there is an additive interval-valued function\nb$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
 defined by
@@
 and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
-$\left(\mathscr{I}_{\infty},\iota_{\infty}\right)$ is an additive
-pair.\end{example}
+$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
+is an additive interval-valued function.\end{example}
 
@@
 
-Although a convex QIVPM can be constructed by a convex pair easily,
-any convex pair either is $\left\{ \necess,\imposs,\unknown\right\} $
+Although a convex QIVPM can be constructed by a convex interval-valued
+function easily, its range either is $\left\{ \necess,\imposs,\unknown\right\} $
 or contains infinitely many intervals. The reason is that a Wright-convex
@@
 
-Even if an additive pair\nb$\left(\mathscr{I},\iota\right)$ is not
-convex, it may still induce a convex QIVPM. In particular, every QIVPM
-on a three-dimensional Hilbert space is convex by theorem~\ref{thm:convex-3}.
-The next natural question is whether a non-convex pair always induces
-some non-convex QIVPM, and the answer is ``yes'' by the following
-lemma.
-
-\begin{lemma}Given an additive but non-convex pair\nb$\left(\mathscr{I},\iota\right)$,
+Even if an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is not convex, it may still induce a convex QIVPM. In particular,
+every QIVPM on a three-dimensional Hilbert space is convex by theorem~\ref{thm:convex-3}.
+The next natural question is whether a non-convex interval-valued
+function always induces some non-convex QIVPM, and the answer is ``yes''
+by the following lemma.
+
+\begin{lemma}Given an additive but non-convex interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
 there is a non-convex quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$.\end{lemma}
@@
 
-In conclusion, we may still use an additive but non-convex pair to
-construct QIVPMs, but we need to verify the convexity of the constructed
-QIVPM one-by-one which might be long and tedious.
+In conclusion, we may still use an additive but non-convex interval-valued
+function to construct QIVPMs, but we need to verify the convexity
+of the constructed QIVPM one-by-one which might be long and tedious.
 

### 2017-06-13 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued II} Added..

@@
 
-\subsection{From Real-valued to Interval-valued}
+\subsection{From Real-valued to Interval-valued I}
 
@@
 of the constructed QIVPM one-by-one which might be long and tedious.
+
+\subsection{From Real-valued to Interval-valued II}
+
+Since we cannot restrict our convex interval-valued function mapping
+only finite number of intervals, let's consider another natural interval-valued
+function. Before we consider them, we review the counterpart of Weight-convex,
+Weight-concave\nb\cite{PecaricTong1992,Brzdek_2014}.
+
+\begin{definition}A function\nb$c:\left[0,1\right]\rightarrow\left[0,1\right]$
+is called Wright-concave if for any three numbers\nb$x_{0}$, $x_{1}$,
+and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
+implies $c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)$.\end{definition}
+
+\begin{example}Given a concave function\nb$c:$ For any $\delta\ge0$,
+there is an additive interval-valued function\nb$\iota_{\delta}':\left[0,1\right]\rightarrow\mathscr{I}_{\delta}'$
+defined by\end{example}
 

### 2017-06-13 prop_iop.tex
prop_iop.tex \DeclareUnicodeCharacter{0229}{\c{e}} Added to eliminate biblatex error...
prop_iop.tex Elimating pdfLaTeX warnings...

@@
 \usepackage[utf8]{inputenc}
+\DeclareUnicodeCharacter{0229}{\c{e}}
 \usepackage{amssymb}
@@
 % Hence, it will not hyphenate too much surrounding words.
-\newcommand{\nb}{\nolinebreak[1] }
+\newcommand{\nb}{\nolinebreak[3] }
 \newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
@@
 The first two possibilities are particular interesting since each
-two 1-dimensional projectors~$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
+two 1-dimensional projectors\nb$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
 mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
@@
 
-In order to simplify the discussion, we call a function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$
+In order to simplify the discussion, we call a function\nb$\bar{f}:S^{2}\rightarrow\mathscr{I}$
 satisfying conditions in theorem~\ref{thm:interval-valued-frame-function}
@@
 \begin{equation}
-\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .}
+\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .}
 \end{equation}
@@
 \begin{equation}
-\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}^{\Omega}\left(E_{i}\right)\textrm{ .}
+\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}^{\Omega}\left(E_{i}\right)\textrm{ .}
 \end{equation}
@@
 \begin{eqnarray*}
- &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)=\sum_{j=1}^{N}\mu'\left(\left\{ j\right\} \right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)=\mu'\left(\left\{ j\right\} \right)=\mu'\left(\tau\left(\proj{i}\right)\right)\textrm{ for all }i\textrm{ ,}\\
- &  & \mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)\overset{\textrm{IH}}{=}\mu'\left(\tau\left(P_{1}\right)\right)+\mu'\left(\tau\left(P_{2}\right)\right)=\mu'\left(\tau\left(P_{1}\right)\cup\tau\left(P_{2}\right)\right)=\mu'\left(\tau\left(P_{1}+P_{2}\right)\right)\textrm{ for commuting }P_{0},P_{1}\in\events\textrm{ with }P_{0}P_{1}=\mathbb{0}\textrm{ .}
+ &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)
+ =\sum_{j=1}^{N}\mu'\left(\left\{ j\right\} \right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)
+ =\mu'\left(\left\{ j\right\} \right)
+ =\mu'\left(\tau\left(\proj{i}\right)\right)\textrm{ for all }i\textrm{ ,}\\
+ &  & \mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)
+ \overset{\textrm{IH}}{=}\mu'\left(\tau\left(P_{1}\right)\right)+\mu'\left(\tau\left(P_{2}\right)\right)
+ =\mu'\left(\tau\left(P_{1}+P_{2}\right)\right)
 \end{eqnarray*}
+for commuting\nb$P_{0},P_{1}\in\events$ with $P_{0}P_{1}=\mathbb{0}$.
 Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
@@
 & \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
-\Rightarrow & \left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
 \Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\
@@
 \begin{equation}\eqalign{ 
- & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)
-=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\ 
+ & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
+= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\ 
 = & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)

### 2017-06-14 prop_iop.tex
prop_iop.tex \section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}} Fixing citations...

@@
 its left end, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
-is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
+is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,PecaricTong1992}.
 After we define interval-valued function, we are ready to construct
@@
 only finite number of intervals, let's consider another natural interval-valued
-function. Before we consider them, we review the counterpart of Weight-convex,
-Weight-concave\nb\cite{PecaricTong1992,Brzdek_2014}.
+function. Before we consider them, we review the counterpart of Wright-convex,
+Wright-concave\nb\cite{Brzdek_2014}.
 

### 2017-06-14 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued II} Updating...

@@
 Since we cannot restrict our convex interval-valued function mapping
-only finite number of intervals, let's consider another natural interval-valued
-function. Before we consider them, we review the counterpart of Wright-convex,
-Wright-concave\nb\cite{Brzdek_2014}.
-
-\begin{definition}A function\nb$c:\left[0,1\right]\rightarrow\left[0,1\right]$
-is called Wright-concave if for any three numbers\nb$x_{0}$, $x_{1}$,
-and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
-implies $c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)$.\end{definition}
-
-\begin{example}Given a concave function\nb$c:$ For any $\delta\ge0$,
-there is an additive interval-valued function\nb$\iota_{\delta}':\left[0,1\right]\rightarrow\mathscr{I}_{\delta}'$
-defined by\end{example}
+to only finite number of intervals, let's consider another family
+of natural interval-valued functions.
+
+\begin{lemma}Given a function\nb$c:\left[0,1\right]\rightarrow\left[0,1\right]$
+satisfying the following conditions:
+\begin{itemize}
+\item For all $x\in\left[0,1\right]$, $c\left(x\right)\le x$.
+\item For all $x\in\left[0,1\right]$, $c\left(1-x\right)=c\left(x\right)$.
+\item $c$ is Wright-concave\nb\cite{Brzdek_2014}, i.e., for any three
+numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
+implies $c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)$.
+\end{itemize}
+Then, there is a convex interval-valued function\nb$\iota_{c}':\left[0,1\right]\rightarrow\mathscr{I}_{c}'$
+defined by $\iota_{c}'\left(x\right)=\left[x-c\left(x\right),x+c\left(x\right)\right]$,
+where $\mathscr{I}_{c}'=\set{\iota_{c}'\left(x\right)}{x\in\left[0,1\right]}$.\end{lemma}
+
+\begin{proof}~
+\begin{itemize}
+\item Since $c\left(x\right)\le x$, $0\le x-c\left(x\right)$. Also, $c\left(x\right)=c\left(1-x\right)\le1-x$
+implies $x+c\left(x\right)\le1$. Therefore, $\iota_{c}'\left(x\right)=\left[x-c\left(x\right),x+c\left(x\right)\right]\subseteq\left[0,1\right]$.
+\item For any $x\in\left[0,1\right]$, $\iota_{c}'\left(1-x\right)=\left[1,1\right]-\left[x-c\left(1-x\right),x+c\left(1-x\right)\right]=\left[1,1\right]-\iota_{c}'\left(x\right)$.
+\item Since $c\left(0\right)\in\left[0,1\right]$ and $c\left(0\right)\le0$,
+we have $c\left(0\right)=0$. Therefore, $\iota_{c}'\left(0\right)=\left[0,0\right]$,
+and $\iota_{c}'\left(1\right)=\left[1,1\right]-\iota_{c}'\left(0\right)=\left[1,1\right]$. 
+\item Given any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
+if $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have
+\begin{equation}\eqalign{ 
+ & c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)\\
+\Rightarrow & \left[x_{0}+x_{1}+x_{2}+c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}+c\left(x_{2}\right)\right]\\
+ & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\textrm{ .} }\end{equation}
+Also, 
+\begin{equation}\eqalign{ 
+ & c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)\\
+\Rightarrow & -c\left(x_{0}+x_{2}\right)-c\left(x_{1}+x_{2}\right)\le-c\left(x_{0}+x_{1}+x_{2}\right)-c\left(x_{2}\right)\\
+\Rightarrow & \left[x_{0}+x_{2}-c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}-c\left(x_{1}+x_{2}\right)\right]\\
+ & \le\left[x_{0}+x_{1}+x_{2}-c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}-c\left(x_{2}\right)\right]\textrm{ .} 
+}\end{equation}
+The above two equations implies $\iota_{c}'\left(x_{0}+x_{1}+x_{2}\right)+\iota_{c}'\left(x_{2}\right)\subseteq\iota_{c}'\left(x_{0}+x_{2}\right)+\iota_{c}'\left(x_{1}+x_{2}\right)$.
+\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
+if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota_{c}'\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota_{c}'\left(x_{i}\right)$
+by inducting on the convex condition listed previously with $x_{2}=0$.
+\end{itemize}
+\end{proof}
 

### 2017-06-15 prop_letter.tex
prop_letter.tex Galvan2008 should be cited.

@@
 
-We will start by reviewing IVPMs in the classical setting\nb\cite{JamisonLodwick2004}
+We will start by reviewing IVPMs in the classical setting\nb\citep{JamisonLodwick2004,Galvan2008}
 and then propose our quantum generalization. In the classical setting,
-there are several proposals for ``imprecise probabilities\nb\cite{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Grabisch2016}.''
+there are several proposals for ``imprecise probabilities\nb\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,Grabisch2016}.''
 Although these proposals differ in some details, they all share the

### 2017-06-16 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued I} Updating

@@
 
-Although a convex interval-valued function\nb$\iota$ may look exotic,
-its left end, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
-is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,PecaricTong1992}.
-After we define interval-valued function, we are ready to construct
-a QIVPM from a quantum probability measure.
+Although a interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+may look exotic, its left-end and right-end\nb$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$
+are just usual functions from a unit interval to another unit interval.
+For an additive interval-valued function, $\iotal$ is superadditive,
+i.e., $\iotal\left(x_{0}+x_{1}\right)\ge\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)$,
+and $\iotar$ is subadditive, i.e., $\iotar\left(x_{0}+x_{1}\right)\le\iotar\left(x_{0}\right)+\iotar\left(x_{1}\right)$\nb\cite{PecaricTong1992}.
+For a convex interval-valued function, $\iotal$ is Wright-convex,
+i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
+and $\iotar$ is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
+Also, if $\mathscr{I}$ contains only finite number of intervals,
+$\iotal$ and $\iotar$ must be step functions. After we define interval-valued
+function, we are ready to construct a QIVPM from a quantum probability
+measure.
 

### 2017-06-18 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued I} Updating

@@
 
-\begin{example}\label{ex:regular-pair}For any positive integer~$n$,
-there is an additive interval-valued function\nb$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
+\begin{example}\label{ex:regular-pair}For any positive integer~$n$
+and $\delta\in\left[0,1\right]$, there is an additive interval-valued
+function\nb$\iota_{n,\delta}:\left[0,1\right]\rightarrow\mathscr{I}_{n,\delta}$
 defined by
 \begin{equation}\eqalign{ 
-\mathscr{I}_{n} = \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\ 
-\iota_{n}\left(x\right) = \cases{ 
-\left[\frac{k}{n},\frac{k}{n}\right] & , if $x=\frac{k}{n}$ ;\\ 
+\eqalign{\mathscr{I}_{n,\delta} =& \set{\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right]}{k=1,\ldots,n-1}\\
+&\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\cup\left\{\left[0,0\right],\left[1,1\right]\right\}}\\ 
+\iota_{n,\delta}\left(x\right) = \cases{ 
+\left[x,x\right] & , if $x=0$ or  $x=1$ ;\\ 
+\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right] & , if $x=\frac{k}{n}\in\left(0,1\right)$ ;\\ 
 \left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
@@
 }\end{equation}
-Notice that the usual $\left\{ \necess,\imposs,\unknown\right\} $
-is $\mathscr{I}_{1}$. Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
+When we use the same notation in other place in this paper, we may
+write $\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$ to represent
+$\iota_{n,0}:\left[0,1\right]\rightarrow\mathscr{I}_{n,0}$. Notice
+that the usual $\left\{ \necess,\imposs,\unknown\right\} $ is $\mathscr{I}_{1}$.
+Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
 and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
@@
 \begin{itemize}
-\item $\iota\left(0\right)=\left[0,0\right]$. 
-\item $\iota\left(1\right)=\left[1,1\right]$. 
-\item When $x=k/n$, we have $\iota\left(1-x\right)=\left[1-k/n,1-k/n\right]=\left[1,1\right]-\iota\left(x\right)$.\\
+\item Since $\delta\in\left[0,1\right]$ and $\iota_{n,\delta}\left(x\right)=\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right]$
+only when $0<x=\frac{k}{n}<1$, we have $\iota_{n,\delta}\left(x\right)\subseteq\left[0,1\right]$.
+\item $\iota_{n,\delta}\left(0\right)=\left[0,0\right]$. 
+\item $\iota_{n,\delta}\left(1\right)=\left[1,1\right]$. 
+\item When $x=0$ or $x=1$, we have $\iota_{n,\delta}\left(1-x\right)=\left[1-x,1-x\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)$.\\
+When $x=k/n\in\left(0,1\right)$, we have 
+\begin{equation}
+\iota_{n,\delta}\left(1-x\right)=\left[\frac{n-k-\delta}{n},\frac{n-k+\delta}{n}\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)\textrm{ .}
+\end{equation}
 When $k/n<x<\left(k+1\right)/n$, we have $1-k/n>1-x>1-\left(k+1\right)/n$
@@
 \begin{equation}
-\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)\textrm{ .}
+\iota_{n,\delta}\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)\textrm{ .}
 \end{equation}
 \item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
-if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{1}+x_{2}\right)\subseteq\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$,
+if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota_{n,\delta}\left(x_{1}+x_{2}\right)\subseteq\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)$,
 and the rest can be done by the induction. 
 \begin{itemize}
-\item When $x_{1}=k_{1}/n$, we have 
-\begin{equation}
-\iota\left(x_{1}+x_{2}\right)=\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota\left(x_{2}\right)=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .}
-\end{equation}
+\item When $x_{1}=0$, we have $\iota_{n,\delta}\left(x_{1}+x_{2}\right)=\iota_{n,\delta}\left(x_{2}\right)=\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)$.
+\item When $x_{1}=k_{1}/n\in\left(0,1\right)$, we have 
+\begin{equation}
+\iota_{n,\delta}\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota_{n,\delta}\left(x_{2}\right)\subseteq\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)\textrm{ ,}
+\end{equation}
+where $\iota_{n,\delta}\left(x_{1}+x_{2}\right)$ is a proper subset
+of $\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota_{n,\delta}\left(x_{2}\right)$
+only when $x_{1}+x_{2}=1$.
 \item When $k_{1}/n<x_{1}<\left(k_{1}+1\right)/n$ and $k_{2}/n<x_{2}<\left(k_{2}+1\right)/n$,
@@
 \begin{equation}\eqalign{ 
-& \iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\ 
-= &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .} 
+& \iota_{n,\delta}\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\ 
+= &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)\textrm{ .} 
 }\end{equation}

### 2017-06-18 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued I} Updating

@@
 = &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)\textrm{ .} 
+}\end{equation}
+\end{itemize}
+\end{itemize}
+\end{proof}
+
+\begin{example}For any positive integer~$n$, there is an additive
+interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
+defined by the following:
+\begin{itemize}
+\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
+\item when $0<x<1$, we have $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
+where $k$ is defined by either one of the following:
+\begin{itemize}
+\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
+\item $2\nmid k$ and $k-0.5<2nx<k+0.5$,
+\end{itemize}
+\end{itemize}
+where $\widehat{\mathscr{I}}_{n}=\set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\cup\left\{ \left[0,0\right],\left[1,1\right]\right\} $.\end{example}
+
+\begin{proof}~
+\begin{itemize}
+\item $\widehat{\iota}_{n}\left(0\right)=\left[0,0\right]$. 
+\item $\widehat{\iota}_{n}\left(1\right)=\left[1,1\right]$. 
+\item When $x=0$ or $x=1$, we have $\widehat{\iota}_{n}\left(1-x\right)=\left[1-x,1-x\right]=\left[1,1\right]-\widehat{\iota}_{n}\left(x\right)$.
+Otherwise, since $2\mid k\Leftrightarrow2\mid\left(2n-k\right)$,
+we always have
+\begin{equation}
+\widehat{\iota}_{n}\left(1-x\right)=\left[1-\frac{k+1}{2n},1-\frac{k-1}{2n}\right]\cap\left[0,1\right]=\left[1,1\right]-\widehat{\iota}_{n}\left(x\right)\textrm{ .}
+\end{equation}
+\item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
+if $x_{1}+x_{2}\in\left[0,1\right]$, then $\widehat{\iota}_{n}\left(x_{1}+x_{2}\right)\subseteq\widehat{\iota}_{n}\left(x_{1}\right)+\widehat{\iota}_{n}\left(x_{2}\right)$,
+and the rest can be done by the induction. 
+\begin{itemize}
+\item When $x_{1}=0$, we have $\widehat{\iota}_{n}\left(x_{1}+x_{2}\right)=\widehat{\iota}_{n}\left(x_{2}\right)=\widehat{\iota}_{n}\left(x_{1}\right)+\widehat{\iota}_{n}\left(x_{2}\right)$.
+\item When $x_{1}=1$, we must have $x_{2}=0$ which reduces to the previous
+case.
+\item When $\widehat{\iota}_{n}\left(x_{1}\right)=\left[\frac{k_{1}-1}{2n},\frac{k_{1}+1}{2n}\right]\cap\left[0,1\right]$
+and $\widehat{\iota}_{n}\left(x_{2}\right)=\left[\frac{k_{2}-1}{2n},\frac{k_{2}+1}{2n}\right]\cap\left[0,1\right]$,
+we have $k_{1}-0.5\le2nx_{1}\le k_{1}+0.5$ and $k_{2}-0.5\le2nx_{2}\le k_{2}+0.5$
+so that $k_{1}+k_{2}-1\le2n\left(x_{1}+x_{2}\right)\le k_{1}+k_{2}+1$.
+Hence, no matter whether $x_{1}+x_{2}=1$ or not, we always have 
+\begin{equation}\eqalign{ 
+& \widehat{\iota}_{n}\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}-2}{2n},\frac{k_{1}+k_{2}+2}{2n}\right]\cap\left[0,1\right]\\ 
+= &\left[\frac{k_{1}-1}{2n},\frac{k_{1}+1}{2n}\right]\cap\left[0,1\right]+\left[\frac{k_{2}-1}{2n},\frac{k_{2}+1}{2n}\right]\cap\left[0,1\right]\\
+= &\widehat{\iota}_{n}\left(x_{1}\right)+\widehat{\iota}_{n}\left(x_{2}\right)\textrm{ .} 
 }\end{equation}

### 2017-06-18 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

@@
 
-\subsection{From Real-valued to Interval-valued I}
+\subsection{From Real-valued to Interval-valued}
 
@@
 
-\begin{lemma}Consider an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
-Then, there is a quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.
-Obviously, if $\iota$ is convex, so does $\bar{\mu}$.\end{lemma}
-
-\begin{proof}Consider $\bar{\mu}\left(P\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
-Then, $\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
-i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\bar{\mu}\right)$,
-we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.\end{proof}
+\begin{lemma}Consider a set of intervals\nb$\mathscr{I}$ with an
+additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
+For any normalized pure state\nb$\ket{\phi}$, $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$
+is a quantum IVPM such that $\mathrm{core}\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$
+has an unique element. Obviously, if $\iota$ is convex, so does $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{lemma}
+
+\begin{proof}$\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)\left(\proj{\phi}\right)=\iota\left(\mu_{\phi}^{\mathrm{\mathrm{B}}}\left(\proj{\phi}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
+i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$,
+we have $\mu\left(\proj{\phi}\right)=1$. Therefore, $\mu=\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{proof}
 
@@
 
-\subsection{From Real-valued to Interval-valued II}
+\subsubsection{Convex and Finite Number of Intervals in Low Dimension}
+
+\subsubsection{Convex but Infinite Number of Intervals}
 

### 2017-06-20 prop_letter.tex
prop_letter.tex Fix a typo suggested by Prof. Hanson.

@@
   \end{subequations}
-  a QIVPM $\bar{\mu}$ is an assignment of intervals to each event
+  a QIVPM $\bar{\mu}$ is an assignment of an interval to each event
   (projection operator) subject to the following constraints:

### 2017-06-21 prop_iop.tex
Fixing the spaces...

@@
 \begin{equation}
-\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M} x_{i}\right|<\epsilon\right)=1\textrm{ .}
+\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M} x_{i}\right|<\epsilon\right)=1\,.
 \end{equation}
@@
 \begin{equation}
-\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)\textrm{ .}\label{eq:classical-complement}
+\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)\,.\label{eq:classical-complement}
 \end{equation}
@@
 \begin{equation}
-\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\textrm{ .}\label{eq:classical-include}
+\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\,.\label{eq:classical-include}
 \end{equation}
@@
 =& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=
-\left[\frac{1}{2},\frac{3}{2}\right]\textrm{ .}
+\left[\frac{1}{2},\frac{3}{2}\right]\,.
 }\end{equation}
@@
 \begin{equation}
-\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
+\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,.\label{eq:QuantumInterval-valuedProbability-Complement}
 \end{equation}
@@
 \begin{equation}
-\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\,.\label{eq:QuantumInterval-valuedProbability-Inclusion}
 \end{equation}
@@
 \begin{equation}\eqalign{ 
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\,,\\ 
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\,,\\ 
 \bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
@@
 \begin{equation}
-\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is odd}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is even}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
+\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is odd}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is even}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\,.\label{eq:Dempster-Shafer-game-quantum}
 \end{equation}
@@
 \begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} \cap\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} =\emptyset\textrm{ .}
+\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} \cap\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} =\emptyset\,.
 \end{equation}
@@
 \alpha_{1}^{*} & \beta_{1}^{*}
-\end{array}\right|\ket{2}\textrm{ ,}
+\end{array}\right|\ket{2}\,,
 \end{equation}
@@
 &\ip{\psi}{\psi\times\phi}=\ip{\psi\times\phi}{\psi}^{*}\\
-=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}\right]^{*}=0\textrm{ ,}\\
+=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\alpha_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\alpha_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\alpha_{2}\right]^{*}=0\,,\\
 &\ip{\phi}{\psi\times\phi}=\ip{\psi\times\phi}{\phi}^{*}\\
-=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}\right]^{*}=0\textrm{ .}
+=&\left[\left(\alpha_{1}\beta_{2}-\alpha_{2}\beta_{1}\right)\beta_{0}+\left(\alpha_{2}\beta_{0}-\alpha_{0}\beta_{2}\right)\beta_{1}+\left(\alpha_{0}\beta_{1}-\alpha_{1}\beta_{0}\right)\beta_{2}\right]^{*}=0\,.
 }\end{equation}
@@
 \begin{equation}
-\dim\left(\ker T\right)=\mathrm{nullity}\left(T\right)=3-\mathrm{rank}\left(T\right)=3-2=1\textrm{ .}
+\dim\left(\ker T\right)=\mathrm{nullity}\left(T\right)=3-\mathrm{rank}\left(T\right)=3-2=1\,.
 \end{equation}
@@
 \left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\Rightarrow
-l_{0}+r_{0}=1\textrm{ .}
+l_{0}+r_{0}=1\,.
 \end{equation}
@@
 1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\Rightarrow
-l_{0}\le\frac{1}{2}\le r_{0}\textrm{ .}
+l_{0}\le\frac{1}{2}\le r_{0}\,.
 \end{equation}
@@
 \begin{equation}
-\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right]\Rightarrow l_{0}\le0\textrm{ .}
+\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right]\Rightarrow l_{0}\le0\,.
 \end{equation}
@@
 \begin{equation}
-\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .}
+\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\,.
 \end{equation}
@@
 \begin{equation}
-\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}^{\Omega}\left(E_{i}\right)\textrm{ .}
+\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}^{\Omega}\left(E_{i}\right)\,.
 \end{equation}
@@
 \begin{eqnarray}
-\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\Tr\left(\proj{j}\right)=1\textrm{ .}
+\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\Tr\left(\proj{j}\right)=1\,.
 \end{eqnarray}
@@
  =\mu'\left(\left\{ j\right\} \right)
- =\mu'\left(\tau\left(\proj{i}\right)\right)\textrm{ for all }i\textrm{ ,}\\
+ =\mu'\left(\tau\left(\proj{i}\right)\right)\textrm{ for all }i\,,\\
  &  & \mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)
@@
 & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)= \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\\ 
-\subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)= \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ .} 
+\subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)= \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,. 
 }\end{equation}
@@
 \begin{equation}
-\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}\label{eq:classical-convex}
+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\,.\label{eq:classical-convex}
 \end{equation}
@@
 \Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\
-\Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}
+\Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\,. 
 }\end{equation}
@@
 \iota_{n,\delta}\left(x\right) = \cases{ 
-\left[x,x\right] & , if $x=0$ or  $x=1$ ;\\ 
-\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right] & , if $x=\frac{k}{n}\in\left(0,1\right)$ ;\\ 
-\left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
+\left[x,x\right]\,, &if $x=0$ or  $x=1$ ;\\ 
+\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right]\,, &if
+$x=\frac{k}{n}\in\left(0,1\right)$ ;\\
+\left[\frac{k}{n},\frac{k+1}{n}\right]\,, &if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
 }
@@
 \begin{equation}
-\iota_{n,\delta}\left(1-x\right)=\left[\frac{n-k-\delta}{n},\frac{n-k+\delta}{n}\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)\textrm{ .}
+\iota_{n,\delta}\left(1-x\right)=\left[\frac{n-k-\delta}{n},\frac{n-k+\delta}{n}\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)\,.
 \end{equation}
@@
 \begin{equation}
-\iota_{n,\delta}\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)\textrm{ .}
+\iota_{n,\delta}\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)\,.
 \end{equation}
@@
 \begin{equation}
-\iota_{n,\delta}\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota_{n,\delta}\left(x_{2}\right)\subseteq\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)\textrm{ ,}
+\iota_{n,\delta}\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota_{n,\delta}\left(x_{2}\right)\subseteq\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)\,,
 \end{equation}
@@
 & \iota_{n,\delta}\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\ 
-= &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)\textrm{ .} 
+= &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)\,. 
 }\end{equation}
@@
 \begin{equation}
-\widehat{\iota}_{n}\left(1-x\right)=\left[1-\frac{k+1}{2n},1-\frac{k-1}{2n}\right]\cap\left[0,1\right]=\left[1,1\right]-\widehat{\iota}_{n}\left(x\right)\textrm{ .}
+\widehat{\iota}_{n}\left(1-x\right)=\left[1-\frac{k+1}{2n},1-\frac{k-1}{2n}\right]\cap\left[0,1\right]=\left[1,1\right]-\widehat{\iota}_{n}\left(x\right)\,.
 \end{equation}
@@
 = &\left[\frac{k_{1}-1}{2n},\frac{k_{1}+1}{2n}\right]\cap\left[0,1\right]+\left[\frac{k_{2}-1}{2n},\frac{k_{2}+1}{2n}\right]\cap\left[0,1\right]\\
-= &\widehat{\iota}_{n}\left(x_{1}\right)+\widehat{\iota}_{n}\left(x_{2}\right)\textrm{ .} 
+= &\widehat{\iota}_{n}\left(x_{1}\right)+\widehat{\iota}_{n}\left(x_{2}\right)\,. 
 }\end{equation}
@@
 \begin{equation}
-\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\textrm{ ,}
+\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,,
 \end{equation}
@@
 \begin{equation}
-\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\textrm{ .}
+\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
 \end{equation}
@@
 = & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)
-=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ .} 
+=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,. 
 }\end{equation}
@@
 \Rightarrow & \left[x_{0}+x_{1}+x_{2}+c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}+c\left(x_{2}\right)\right]\\
- & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\textrm{ .} }\end{equation}
+ & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\,. }\end{equation}
 Also, 
@@
 \Rightarrow & \left[x_{0}+x_{2}-c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}-c\left(x_{1}+x_{2}\right)\right]\\
- & \le\left[x_{0}+x_{1}+x_{2}-c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}-c\left(x_{2}\right)\right]\textrm{ .} 
+ & \le\left[x_{0}+x_{1}+x_{2}-c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}-c\left(x_{2}\right)\right]\,. 
 }\end{equation}
@@
 \Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\frac{k}{n}-\delta,1-\frac{k}{n}+\delta\right]\\
-\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1-\frac{k}{n}=1-\pmeas\left(P\right)\textrm{ .}
+\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1-\frac{k}{n}=1-\pmeas\left(P\right)\,.
 }\end{equation}
@@
 \begin{equation}
-\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[\frac{k_{0}+k_{1}}{n}-2\delta,\frac{k_{0}+k_{1}}{n}+2\delta\right]\textrm{ .}
+\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[\frac{k_{0}+k_{1}}{n}-2\delta,\frac{k_{0}+k_{1}}{n}+2\delta\right]\,.
 \end{equation}
@@
 \begin{equation}
-\frac{k_{0}+k_{1}-1}{n}+\delta<\frac{k_{0}+k_{1}}{n}-2\delta\le\frac{k_{0}+k_{1}}{n}+2\delta<\frac{k_{0}+k_{1}+1}{n}-\delta\textrm{ .}
+\frac{k_{0}+k_{1}-1}{n}+\delta<\frac{k_{0}+k_{1}}{n}-2\delta\le\frac{k_{0}+k_{1}}{n}+2\delta<\frac{k_{0}+k_{1}+1}{n}-\delta\,.
 \end{equation}
@@
 \begin{equation}
-\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-\delta,\frac{k_{0}+k_{1}}{n}+\delta\right]\textrm{ .}
+\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-\delta,\frac{k_{0}+k_{1}}{n}+\delta\right]\,.
 \end{equation}
@@
 \begin{equation}
-\pmeas\left(P_{0}+P_{1}\right)=\frac{k_{0}+k_{1}}{n}=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
+\pmeas\left(P_{0}+P_{1}\right)=\frac{k_{0}+k_{1}}{n}=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\,.
 \end{equation}
@@
 \begin{equation}\eqalign{ 
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,} 
+\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\,,\\
+\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\,, 
 }\end{equation}
@@
 \begin{equation}\eqalign{ 
-\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)\subseteq\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)\subseteq\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ ,}\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)\subseteq\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\,,\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)\subseteq\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\,,\\
 \left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)\subseteq\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)
@@
 \begin{equation}\eqalign{ 
-\left[1,1\right]-\bar{f}\left(\ket{0}\right)=\necess\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\midd=\midd+\imposs=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{0}\right)\textrm{ ,}
+\left[1,1\right]-\bar{f}\left(\ket{0}\right)=\necess\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\,,\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\midd=\midd+\imposs=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{0}\right)\,,
 }\end{equation}
@@
 \begin{equation}\eqalign{ 
-\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\midd+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)=\likely\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)\textrm{ .}
+\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\midd+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\,,\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)=\likely\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)\,.
 }\end{equation}
@@
 \begin{equation}\eqalign{ 
-\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
-\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\likely\subseteq\unlikely+\midd=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ .}
+\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\,,\\
+\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\likely\subseteq\unlikely+\midd=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\,.
 }\end{equation}
@@
 \begin{equation}
-\left[1,1\right]-\bar{f}\left(\ket{\psi_{0}}\right)=\likely\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_{1}}\right)+\bar{f}\left(\ket{\psi_{2}}\right)\textrm{ .}
+\left[1,1\right]-\bar{f}\left(\ket{\psi_{0}}\right)=\likely\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_{1}}\right)+\bar{f}\left(\ket{\psi_{2}}\right)\,.
 \end{equation}
@@
 \begin{equation}
-\mu_{\ket{2}}^{\mathrm{B}}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
+\mu_{\ket{2}}^{\mathrm{B}}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\,.
 \end{equation}
@@
 \begin{eqnarray}
-\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(E_{i}\right)\textrm{ .}\label{eq:expectation}
+\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(E_{i}\right)\,.\label{eq:expectation}
 \end{eqnarray}
@@
 \int X_{0}\rmd\pmeas & = 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
- & = 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .} 
+ & = 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\,. 
 }\end{equation}
@@
 \begin{equation}
-\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:interval-expectation}
+\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,.\label{eq:interval-expectation}
 \end{equation}
@@
  & = & \int X^{+}\rmd\bar{\mu}-\sum_{i=1}^{N^{-}}\left(-x_{i}^{-}\right)\left[\Delta\mur\left(E_{i}^{-\prime}\right),\Delta\mul\left(E_{i}^{-\prime}\right)\right]\\
- & = & \int X^{+}\rmd\bar{\mu}-\int\left(-X^{-}\right)\rmd\bar{\mu}\textrm{ .}
+ & = & \int X^{+}\rmd\bar{\mu}-\int\left(-X^{-}\right)\rmd\bar{\mu}\,.
 \end{eqnarray*}
@@
 \begin{equation}
-\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\textrm{ ,}\label{eq:spectrum-decomposition}
+\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
 \end{equation}
@@
 \begin{equation}
-\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
+\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
 \end{equation}
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
 \end{equation}
@@
  & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\\
- & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\mu'\textrm{ .}
+ & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\mu'\,.
 \end{eqnarray*}
@@
  & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
- & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\textrm{ .}
+ & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\,.
 \end{eqnarray*}
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
 \end{equation}
@@
  & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
- & \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}
+ & \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.
 \end{eqnarray*}
@@
 \begin{equation}
-\left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}
+\left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.
 \end{equation}
@@
 \[
-\expval{\mathbf{O}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=}\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu'\right\} \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=}\left\{ \expval{\mathbf{O}}_{\rho}\right\} \textrm{ ,}
+\expval{\mathbf{O}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=}\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu'\right\} \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=}\left\{ \expval{\mathbf{O}}_{\rho}\right\} \,,
 \]
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\rho}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\textrm{ .}\label{eq:expectation-value-eigenvalue}
+\expval{\mathbf{O}}_{\rho}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\,.\label{eq:expectation-value-eigenvalue}
 \end{equation}
@@
 \begin{equation}
-\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\textrm{ .}\label{eq:Kochen-Specker-Rules}
+\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
 \end{equation}

### 2017-06-21 prop_letter.tex
Fixing the spaces...

@@
 \begin{equation}
-{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\textrm{.}\label{eq:QuantumProbability-Addition}
+{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
 \end{equation}
@@
 % \sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
-% \textrm{ .}\label{eq:QuantumProbability-Addition}
+% \,.\label{eq:QuantumProbability-Addition}
 % \end{equation}
@@
 %  &  & x[l,r]=\begin{cases}
-% [xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
-% [xr,xl] & \textrm{for }x\le0\textrm{ .}
+% [xl,xr] & \textrm{for }x\ge0\,;\\{}
+% [xr,xl] & \textrm{for }x\le0\,.
 % \end{cases}
@@
    &  & x[\ell,r]=\begin{cases}
-  [x\ell,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
-  [xr,x\ell] & \textrm{for }x\le0\textrm{ ,}
+  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
+  [xr,x\ell] & \textrm{for }x\le0\,,
   \end{cases}
@@
 \bar{\mu}_{1}\left(P\right)=\begin{cases}
-\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
-\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
-\unknown & \text{, otherwise,}
+\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
+\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
+\unknown\,, & \text{otherwise,}
 \end{cases}\label{eq:no-information-IVPM}
@@
 \end{aligned}
-\textrm{ .}
+\,.
 \end{equation}
@@
 \begin{equation}
-\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-2\delta,\frac{k_{0}+k_{1}}{n}+2\delta\right]\textrm{ .}
+\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-2\delta,\frac{k_{0}+k_{1}}{n}+2\delta\right]\,.
 \end{equation}
@@
 \frac{k_{0}+k_{1}-1}{n}+\delta&<&\frac{k_{0}+k_{1}}{n}-2\delta\\
-\frac{k_{0}+k_{1}}{n}+2\delta&<&\frac{k_{0}+k_{1}+1}{n}-\delta\textrm{ .}
+\frac{k_{0}+k_{1}}{n}+2\delta&<&\frac{k_{0}+k_{1}+1}{n}-\delta\,.
 \end{eqnarray}
@@
  &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
- & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\textrm{ ,}
+ & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\,,
 \end{aligned}
@@
  &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
- & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
+ & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\,,
 \end{aligned}
@@
 \begin{eqnarray}
- &  & \imposs=\bar{\mu}_{0}(\mathbb{0})\textrm{ ,}\\
- &  & \necess=\bar{\mu}_{0}(\mathbb{1})\textrm{ ,}\\
+ &  & \imposs=\bar{\mu}_{0}(\mathbb{0})\,,\\
+ &  & \necess=\bar{\mu}_{0}(\mathbb{1})\,,\\
  &  & \begin{aligned}\unlikely & =\bar{\mu}_{0}(\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{1})\\
  & =\bar{\mu}_{0}(\proj{0}+\proj{2})\\
- & =\bar{\mu}_{0}(\proj{1}+\proj{2})\textrm{ ,}
+ & =\bar{\mu}_{0}(\proj{1}+\proj{2})\,,
 \end{aligned}
@@
 = & \left[\frac{1}{2},\frac{3}{2}\right]\nsubseteq\left[1,2\right]\\
-= & \bar{\mu}_{0}(\proj{0}+\proj{1})+\bar{\mu}_{0}(\proj{0}+\proj{2})\textrm{ .}
+= & \bar{\mu}_{0}(\proj{0}+\proj{1})+\bar{\mu}_{0}(\proj{0}+\proj{2})\,.
 \end{aligned}
@@
 \begin{eqnarray}
-\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
+\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
 \end{eqnarray}
@@
 \begin{equation}
-\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
+\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\,.
 \end{equation}

### 2017-06-21 prop_letter.tex
prop_letter.tex Updated...

@@
 
-According to Mermin's comment\nb\cite{Mermin1999},
+According to Mermin's comment\nb\citep{Mermin1999}, 
 \begin{quote}
@@
 precise measurement should not nullify the Kochen-Specker theorem.
-This idea can be modeled precisely by QIVPMs.
-
-\begin{definition}\label{def:delta-deterministic}An interval-valued
-probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is called $\left(1/n,\delta\right)$-deterministic if for every $\left[\ell,r\right]\in\mathscr{I}$,
-there is a $k\in\mathbb{Z}$ such that $\left[\ell,r\right]\subseteq\left[k/n-\delta,k/n+\delta\right]$.\end{definition}
-
-For example, any cryptodeterministic QIVPM is $\left(1,0\right)$-deterministic.
-For another example, given a three-dimensional Hilbert space, 
-\begin{equation}
-\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
-\end{equation}
-is $\left(1,\frac{1}{3}\right)$-deterministic and $\left(\frac{1}{3},0\right)$-deterministic,
-where $\iota_{\infty}\left(x\right)=\left[x,x\right]$. However, we
-will prove there is generally no $\left(1/n,\delta\right)$-deterministic
-probability measures when $\delta$ is much smaller than $1/n$.
-
-\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
-and a quantum $\left(1/n,\delta\right)$-deterministic probability
-measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<1/\left(3n\right)$,
-if $\bar{\mu}(P)\subseteq\left[k/n-\delta,k/n+\delta\right]$, let
-$\mu(P)=k/n$, then $\mu:\events\rightarrow\left[0,1\right]$ is a
-quantum probability measure. In another word, $\iota_{\infty}\circ\mu$
-is $\left(1/n,0\right)$-deterministic.\end{lemma}
-
-\begin{proof} The essential part to verify $\mu$ is a quantum probability
-measure is to verify Eq.~(\ref{eq:QuantumProbability-Addition}). Given a pair of orthogonal
-operators\nb$P_{0}$ and $P_{1}$, let $\pmeas\left(P_{0}\right)=k_{0}/n$ and $\pmeas\left(P_{1}\right)=k_{1}/n$.
-Then, 
-\begin{equation}
-\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-2\delta,\frac{k_{0}+k_{1}}{n}+2\delta\right]\,.
-\end{equation}
-Since $\delta<1/\left(3n\right)$, we have
-\begin{subequations}
+This idea can be modeled precisely by considering the following kind
+of QIVPMs.
+
+\begin{definition}\label{def:delta-deterministic}An QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is called $\delta$-deterministic if either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
+or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$ for
+any $P\in\events$.\end{definition}
+
+For example, any cryptodeterministic QIVPM is $0$-deterministic.
+For another example, given a three-dimensional Hilbert space, a $\frac{1}{3}$-deterministic
+QIVPM can be given by $\bar{\mu}\left(P\right)=\left[x,x\right]$,
+where $P$ projects onto a $x$-dimensional subspace. By utilizing
+$\delta$-deterministic QIVPMs, we can have a Kochen-Specker theorem
+with finite precision measurement.
+
+\begin{thm}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
+of dimension\nb$d\ge3$, there is no $\delta$-deterministic QIVPM
+for $\delta<\frac{1}{3}$.\end{thm}
+
+\begin{proof}Suppose there is a $\delta$-deterministic QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+then we can define a cryptodeterministic QIVPM\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $
+by 
+\begin{equation}
+\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
+\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
+\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
+\end{cases}
+\end{equation}
+
+The essential part to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
+QIVPM is to verify\begin{subequations}
 \begin{eqnarray}
-\frac{k_{0}+k_{1}-1}{n}+\delta&<&\frac{k_{0}+k_{1}}{n}-2\delta\\
-\frac{k_{0}+k_{1}}{n}+2\delta&<&\frac{k_{0}+k_{1}+1}{n}-\delta\,.
+ &  & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs\\
+ & \Rightarrow & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs
 \end{eqnarray}
-\end{subequations}
-The previous inequalities imply that if $\bar{\mu}\left(P_{0}+P_{1}\right)$
-overlap with any interval of the form $\left[k/n-\delta,k/n+\delta\right]$
-for some $k$, $k$ must be $k_{0}+k_{1}$, i.e., 
-\begin{equation}
-\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-\delta,\frac{k_{0}+k_{1}}{n}+\delta\right]\,.
-\end{equation}
-Therefore, 
-\begin{equation}
-\pmeas\left(P_{0}+P_{1}\right)=\frac{k_{0}+k_{1}}{n}=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\,.
-\end{equation}
-\end{proof}
-
-Together with the Kochen-Specker theorem, we will have the following
-corollary.
-
-\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
-of dimension\nb$d\ge3$, there is no quantum $\left(1,\delta\right)$-deterministic
-probability measure for $\delta<\frac{1}{3}$.\end{cor}
-
-In general~\cite{Redhead1987-REDINA}, Gleason's theorem asserts
-that a quantum probability measure must be continuous. Therefore,
-a $\left(1/n,0\right)$-deterministic QIVPM exists if and only if
-$d\mid n$, and so does a $\left(1/n,\delta\right)$-deterministic
-QIVPM for $\delta<1/\left(3n\right)$.
+\end{subequations}for orthogonal operators\nb$P_{0}$ and $P_{1}$
+which is a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+
+When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
+and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
+implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
+Since $\delta<\frac{1}{3}\Rightarrow2\delta<1-\delta$, $\bar{\mu}\left(P_{0}+P_{1}\right)$
+cannot be a subset of $\left[1-\delta,1\right]$, but $\bar{\mu}\left(P_{0}+P_{1}\right)$
+is a subset of either $\left[0,\delta\right]$ or $\left[1-\delta,1\right]$.
+Hence, $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[0,\delta\right]$,
+which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+The remain part of the proof are routine verification.\end{proof}
 

### 2017-06-22 prop_letter.tex
prop_letter.tex and "Kochen-Specker Theorem in QIVPM.pptx" Updating...

@@
 if the imperfection of the measurement is small enough, the finitely
-precise measurement should not nullify the Kochen-Specker theorem.
-This idea can be modeled precisely by considering the following kind
-of QIVPMs.
+precise measurement should be close to idealized measurement, and
+cannot nullify the Kochen-Specker theorem. This idea can be modeled
+precisely by considering the following kind of QIVPMs.
 
@@
 The essential part to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
-QIVPM is to verify\begin{subequations}
+QIVPM is to verify a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}
 \begin{eqnarray}
@@
 \end{eqnarray}
-\end{subequations}for orthogonal operators\nb$P_{0}$ and $P_{1}$
-which is a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+\end{subequations}for orthogonal operators\nb$P_{0}$ and $P_{1}$.
 
 When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
-and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
-implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
+we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$
+which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
 Since $\delta<\frac{1}{3}\Rightarrow2\delta<1-\delta$, $\bar{\mu}\left(P_{0}+P_{1}\right)$
@@
 which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+
 The remain part of the proof are routine verification.\end{proof}

### 2017-06-23 prop_letter.tex
prop_letter.tex and "Kochen-Specker Theorem in QIVPM.pptx" Updating...

@@
 
-\begin{definition}\label{def:delta-deterministic}An QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+\begin{definition}\label{def:delta-deterministic}A QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
 is called $\delta$-deterministic if either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
@@
 For example, any cryptodeterministic QIVPM is $0$-deterministic.
-For another example, given a three-dimensional Hilbert space, a $\frac{1}{3}$-deterministic
-QIVPM can be given by $\bar{\mu}\left(P\right)=\left[x,x\right]$,
-where $P$ projects onto a $x$-dimensional subspace. By utilizing
-$\delta$-deterministic QIVPMs, we can have a Kochen-Specker theorem
-with finite precision measurement.
+As another example, a $\frac{1}{3}$-deterministic QIVPM can be given
+by $\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
+onto a $x$-dimensional subspace in a three-dimensional Hilbert space.
+By utilizing $\delta$-deterministic QIVPMs, we can have a Kochen-Specker
+theorem with finite precision measurement.
 
@@
 \begin{proof}Suppose there is a $\delta$-deterministic QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-then we can define a cryptodeterministic QIVPM\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $
+we can define a cryptodeterministic QIVPM\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $
 by 
@@
 \end{equation}
+However, there is no cryptodeterministic QIVPM as we discussed according
+to the Mermin-Peres square, so that there is no $\delta$-deterministic
+QIVPM.
 
 The essential part to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
-QIVPM is to verify a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}
+QIVPM is to verify a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),\begin{subequations}
 \begin{eqnarray}
@@
 
-The remain part of the proof are routine verification.\end{proof}
+By discussing the remaining cases, we can easily verify that $\bar{\mu}^{\textrm{D}}$
+is a cryptodeterministic QIVPM.\end{proof}
 

### 2017-06-23 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Added...

@@
 
-\subsubsection{Convex and Finite Number of Intervals in Low Dimension}
-
 \subsubsection{Convex but Infinite Number of Intervals}
@@
 \Rightarrow & \left[x_{0}+x_{1}+x_{2}+c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}+c\left(x_{2}\right)\right]\\
- & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\,. }\end{equation}
+ & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\textrm{ .} }\end{equation}
 Also, 
@@
 \Rightarrow & \left[x_{0}+x_{2}-c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}-c\left(x_{1}+x_{2}\right)\right]\\
- & \le\left[x_{0}+x_{1}+x_{2}-c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}-c\left(x_{2}\right)\right]\,. 
+ & \le\left[x_{0}+x_{1}+x_{2}-c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}-c\left(x_{2}\right)\right]\textrm{ .} 
 }\end{equation}
@@
 \end{proof}
+
+\subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule}
+
+Since we want to consider QIVPMs induced by the Born rule, it is easier
+to work with the states instead of the probability measures, which
+gives us the following definition.
+
+\begin{definition}A state\nb$\rho$ is consistent with $\bar{\mu}$
+on a projector\nb$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+i.e., $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\left\{ P\right\} }\right)$,
+and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
+is consistent with $\bar{\mu}$ on every projector in $S$, i.e.,
+$\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{S}\right)$.\end{definition}
 

### 2017-06-25 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...
prop_iop.tex Fix spacing again...

--- 2017-06-21 prop_iop.tex
@@
 \end{itemize}
+\end{proof}
+
+\subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule}
+
+Since we want to consider QIVPMs induced by the Born rule, it is easier
+to work with the states instead of the probability measures, which
+gives us the following definition.
+
+\begin{definition}A state\nb$\rho$ is consistent with $\bar{\mu}$
+on a projector\nb$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+i.e., $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\left\{ P\right\} }\right)$,
+and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
+is consistent with $\bar{\mu}$ on every projector in $S$, i.e.,
+$\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{S}\right)$.\end{definition}
+
+When we work with mixed states or density matrices, we also need a
+norm to compute the distance among them.
+
+\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
+and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+with the maximum length of intervals in $\mathscr{I}$ is $1/n$.
+For two mixed state\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+then $\left\Vert \rho-\rho'\right\Vert \le1/n$.\end{lemma}
+
+\begin{proof}By definition, we have
+\begin{equation}\eqalign{ 
+ & \rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)\\ 
+\Leftrightarrow & \forall P\in\events\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)\\ 
+\Rightarrow & \forall\textrm{ normalized pure state }\ket{\psi}\ \mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right) 
+}\end{equation}
 \end{proof}

### 2017-06-25 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

@@
 
+Since we want to consider QIVPMs induced by the Born rule, it is easier
+to work with the states instead of the probability measures, which
+gives us the following definition.
+
+\begin{definition}A state\nb$\rho$ is consistent with $\bar{\mu}$
+on a projector\nb$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+i.e., $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\left\{ P\right\} }\right)$,
+and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
+is consistent with $\bar{\mu}$ on every projector in $S$, i.e.,
+$\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{S}\right)$.\end{definition}
+
 \begin{lemma}Consider a set of intervals\nb$\mathscr{I}$ with an
@@
 For any normalized pure state\nb$\ket{\phi}$, $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$
-is a quantum IVPM such that $\mathrm{core}\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$
+is a quantum IVPM such that $\coreBorn\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$
 has an unique element. Obviously, if $\iota$ is convex, so does $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{lemma}
@@
 \begin{proof}$\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)\left(\proj{\phi}\right)=\iota\left(\mu_{\phi}^{\mathrm{\mathrm{B}}}\left(\proj{\phi}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
-i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$,
+i.e., for any quantum probability measure~$\mu\in\coreBorn\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$,
 we have $\mu\left(\proj{\phi}\right)=1$. Therefore, $\mu=\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{proof}
@@
 
-Since we want to consider QIVPMs induced by the Born rule, it is easier
-to work with the states instead of the probability measures, which
-gives us the following definition.
-
-\begin{definition}A state\nb$\rho$ is consistent with $\bar{\mu}$
-on a projector\nb$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
-i.e., $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\left\{ P\right\} }\right)$,
-and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
-Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
-is consistent with $\bar{\mu}$ on every projector in $S$, i.e.,
-$\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{S}\right)$.\end{definition}
-
 When we work with mixed states or density matrices, we also need a
 norm to compute the distance among them.
+
+\begin{definition}\cite{RobertsVarberg1973,peres1995quantum,544199}Given
+a operator or matrix\nb$\rho$, the norm of $\rho$ is defined by
+\begin{equation}
+\left\Vert \rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho}{\psi}\right|\,.
+\end{equation}
+\end{definition}
 
@@
 
-\begin{proof}By definition, we have
-\begin{equation}\eqalign{ 
- & \rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)\\ 
-\Leftrightarrow & \forall P\in\events\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)\\ 
-\Rightarrow & \forall\textrm{ normalized pure state }\ket{\psi}\ \mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right) 
-}\end{equation}
+\begin{proof}By definition, we have $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
+for all $P\in\events$. By substitute $P=\proj{\psi}$, we have 
+\begin{equation}
+\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)\,.\label{eq:consistent2another_state}
+\end{equation}
+Since the maximum length of intervals in $\mathscr{I}$ is $1/n$,
+we can move $\rho$ and $\rho'$ to the same side and rewrite equation~(\ref{eq:consistent2another_state})
+as
+\begin{equation}
+\frac{1}{n}\ge\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,.
+\end{equation}
+Applying maximum on both side, we have
+\begin{equation}
+\frac{1}{n}\ge\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left\Vert \rho'-\rho\right\Vert \,.
+\end{equation}
 \end{proof}
+
+Previously, we proved that if $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
+then $\rho'$ is close to $\rho$. Conversely, if $\rho'$ is close
+to $\rho$, $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
+by the following lemma.
+
+\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
+and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+with the minimum length of intervals in $\mathscr{I}\backslash\left\{ \imposs,\necess\right\} $
+is $1/n$. For two mixed state\nb$\rho$ and $\rho'$, if the following
+conditions holds.
+\begin{itemize}
+\item $\left\Vert \rho-\rho'\right\Vert \le1/n$.
+\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\imposs$ if and only if $P=\mathbb{0}$.
+\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\necess$ if and only if $P=\mathbb{1}$.
+\end{itemize}
+Then, $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.\end{lemma}
+
+\begin{proof}Since
+\begin{equation}
+\frac{1}{n}\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
+\end{equation}
+we have
+\begin{equation}
+\frac{1}{n}\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|
+\end{equation}
+for all normalized pure state\nb$\ket{\psi}$. \end{proof}
 

### 2017-06-25 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

@@
 and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-with the maximum length of intervals in $\mathscr{I}$ is $1/n$.
+with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
 For two mixed state\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-then $\left\Vert \rho-\rho'\right\Vert \le1/n$.\end{lemma}
+then $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{lemma}
 
@@
 \end{equation}
-Since the maximum length of intervals in $\mathscr{I}$ is $1/n$,
+Since the maximum length of intervals in $\mathscr{I}$ is $\delta$,
 we can move $\rho$ and $\rho'$ to the same side and rewrite equation~(\ref{eq:consistent2another_state})
@@
 \begin{equation}
-\frac{1}{n}\ge\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,.
+\delta\ge\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,.
 \end{equation}
@@
 \begin{equation}
-\frac{1}{n}\ge\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left\Vert \rho'-\rho\right\Vert \,.
+\delta\ge\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left\Vert \rho'-\rho\right\Vert \,.
 \end{equation}
@@
 
-\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
-and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-with the minimum length of intervals in $\mathscr{I}\backslash\left\{ \imposs,\necess\right\} $
-is $1/n$. For two mixed state\nb$\rho$ and $\rho'$, if the following
-conditions holds.
-\begin{itemize}
-\item $\left\Vert \rho-\rho'\right\Vert \le1/n$.
-\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\imposs$ if and only if $P=\mathbb{0}$.
-\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\necess$ if and only if $P=\mathbb{1}$.
+\begin{lemma}Given a $d$-dimensional Hilbert space with the set
+of all projectors\nb$\events$, and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
+For two mixed state\nb$\rho$ and $\rho'$, if the following conditions
+holds.
+\begin{itemize}
+\item Let $\delta=\min_{x\in\left(0,1\right)}\left\{ \max\iota\left(x\right)-x,x-\min\iota\left(x\right)\right\} $.
+In another word, if $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
+\item $\left\Vert \rho-\rho'\right\Vert \le d\delta$.
+\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=0$ if and only if $P=\mathbb{0}$.
+\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=1$ if and only if $P=\mathbb{1}$.
 \end{itemize}
@@
 \begin{equation}
-\frac{1}{n}\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
+d\delta\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
 \end{equation}
@@
 \begin{equation}
-\frac{1}{n}\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|
-\end{equation}
-for all normalized pure state\nb$\ket{\psi}$. \end{proof}
+d\delta\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
+\end{equation}
+for all normalized pure state\nb$\ket{\psi}$.
+
+When $P\in\left\{ \mathbb{0},\mathbb{1}\right\} $, it is obvious
+$\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.
+
+When $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
+there exists an orthonormal set $\left\{ \ket{i}\right\} _{i=0}^{d'-1}$
+such that $P=\sum_{i=0}^{d'-1}\proj{i}$. By applying equation~(\ref{eq:Born_rule_difference}),
+\begin{equation}
+\left|\mu_{\rho'}^{\mathrm{B}}\left(P\right)-\mu_{\rho}^{\mathrm{B}}\left(P\right)\right|\le\sum_{i=0}^{d'-1}\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{i}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)\right|\le\delta\,.
+\end{equation}
+
+Since $P$ is neither $\mathbb{0}$ nor $\mathbb{1}$, $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\left(0,1\right)$.
+Hence, we have $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.\end{proof}
 

### 2017-06-25 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

@@
 
-\begin{example}For any positive integer~$n$, there is an additive
-interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
+\begin{example}\label{ex:equilateral}For any positive integer~$n$,
+there is an additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
 defined by the following:
@@
 Hence, we have $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.\end{proof}
+
+The previous two lemmas can be applied on example~\ref{ex:equilateral},
+we can estimate the states consistent with a QIVPM more tightly.
+
+\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
+the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
+$1/n$, and $\min_{x\in\left(0,1\right)}\left\{ \max\widehat{\iota}_{n}\left(x\right)-x,x-\min\widehat{\iota}_{n}\left(x\right)\right\} =1/\left(4n\right)$.
+Therefore, for any mixed state\nb$\rho$ such that .\end{example}
 

### 2017-06-26 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

@@
 then $\rho'$ is close to $\rho$. Conversely, if $\rho'$ is close
-to $\rho$, $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
-by the following lemma.
+to $\rho$, $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$.
+Before we introduce the lemma, we start the following definition.
+
+\begin{definition}A mixed state\nb$\rho$ is called totally mixed
+if it satisfies the following conditions.
+\begin{itemize}
+\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=0$ if and only if $P=\mathbb{0}$.
+\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=1$ if and only if $P=\mathbb{1}$.
+\end{itemize}
+\end{definition}
+
+For example, any pure state is not totally mixed, and $\mathbb{1}/3$
+is a totally mixed over a three-dimensional Hilbert space.
 
@@
 In another word, if $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
-\item $\left\Vert \rho-\rho'\right\Vert \le d\delta$.
-\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=0$ if and only if $P=\mathbb{0}$.
-\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=1$ if and only if $P=\mathbb{1}$.
+\item $\left\Vert \rho-\rho'\right\Vert \le\delta/d$.
+\item $\rho$ is a totally mixed.
 \end{itemize}
@@
 \begin{equation}
-d\delta\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
+\frac{\delta}{d}\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
 \end{equation}
@@
 \begin{equation}
-d\delta\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
+\frac{\delta}{d}\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
 \end{equation}
@@
 $1/n$, and $\min_{x\in\left(0,1\right)}\left\{ \max\widehat{\iota}_{n}\left(x\right)-x,x-\min\widehat{\iota}_{n}\left(x\right)\right\} =1/\left(4n\right)$.
-Therefore, for any mixed state\nb$\rho$ such that .\end{example}
+Therefore, for any totally mixed state\nb$\rho$ on a $d$-dimensional
+Hilbert space, we have
+\begin{itemize}
+\item If $\left\Vert \rho-\rho'\right\Vert \le\left(4dn\right)^{-1}$, then
+$\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
+\item If $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
+\end{itemize}
+\end{example}
 

### 2017-06-27 prop_iop.tex
Updating according to the meeting...
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

@@
 
-\begin{definition}\cite{RobertsVarberg1973,peres1995quantum,544199}Given
-a operator or matrix\nb$\rho$, the norm of $\rho$ is defined by
+\begin{definition}\cite{544199} Given a operator or matrix\nb$\rho$,
+the norm of $\rho$ is defined by 
 \begin{equation}
@@
 \end{equation}
-\end{definition}
+\footnote{Notice that it doesn't have square root, and this definition only
+appears in \cite{544199}... Need to this definition in other sources.}\end{definition}
 
@@
 
-For example, any pure state is not totally mixed, and $\mathbb{1}/3$
+For example, any pure state is not totally mixed, and $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
 is a totally mixed over a three-dimensional Hilbert space.
@@
 \begin{itemize}
-\item If $\left\Vert \rho-\rho'\right\Vert \le\left(4dn\right)^{-1}$, then
-$\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
-\item If $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, then
+$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
+\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
 then $\left\Vert \rho-\rho'\right\Vert \le1/n$.

### 2017-06-29 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

@@
 
-\begin{definition}\cite{544199} Given a operator or matrix\nb$\rho$,
-the norm of $\rho$ is defined by 
-\begin{equation}
-\left\Vert \rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho}{\psi}\right|\,.
-\end{equation}
-\footnote{Notice that it doesn't have square root, and this definition only
-appears in \cite{544199}... Need to this definition in other sources.}\end{definition}
+\begin{definition}\cite{544199} Given a operator or matrix\nb$A$,
+the norm of $A$ is defined by 
+\begin{equation}
+\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|\,.
+\end{equation}
+\end{definition}
+
+The previously defined matrix norm is not one of the common matrix
+norms as in the following example.
+
+\begin{example}Consider $A=\left(\begin{array}{cc}
+1 & 0\\
+1 & 1
+\end{array}\right)$. Then, 
+\begin{equation}
+\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|=\frac{3}{2}\,.
+\end{equation}
+\end{example}
 

### 2017-06-30 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

@@
 1 & 1
-\end{array}\right)$. Then, 
-\begin{equation}
-\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|=\frac{3}{2}\,.
-\end{equation}
-\end{example}
+\end{array}\right)$. Then, it is easy to verify that $\left\Vert A\right\Vert =3/2$.
+On the other hand, its Frobenius norm or Hilbert-Schmidt norm\nb$\left\Vert A\right\Vert _{\mathrm{F}}$
+is $\sqrt{3}$\nb\cite{Jaeger2007}; its operator $p$-norms\nb$\left\Vert A\right\Vert _{p}$
+are $\left\Vert A\right\Vert _{1}=\left\Vert A\right\Vert _{\infty}=2$
+and $\left\Vert A\right\Vert _{2}=\left[\left(3+\sqrt{5}\right)/2\right]^{\frac{1}{2}}$\nb\cite{RobertsVarberg1973,peres1995quantum}.\end{example}
 

### 2017-06-30 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

--- 2017-06-29 prop_iop.tex
@@
 
-\begin{definition}\cite{544199} Given a operator or matrix\nb$A$,
-the norm of $A$ is defined by 
+\begin{definition}\label{def:norm}\cite{544199} Given a operator
+or matrix\nb$A$, the norm of $A$ is defined by 
 \begin{equation}
@@
 The previously defined matrix norm is not one of the common matrix
-norms as in the following example.
+norms as shown in the following example.
 
@@
 1 & 1
-\end{array}\right)$. Then, 
-\begin{equation}
-\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|=\frac{3}{2}\,.
-\end{equation}
-\end{example}
+\end{array}\right)$. It is easy to verify $\left\Vert A\right\Vert =3/2$. On the other
+hand, its Frobenius norm or Hilbert-Schmidt norm
+\begin{equation}
+\left\Vert A\right\Vert _{\mathrm{F}}=\Tr\left(A^{\dagger}A\right)=\left(\sum_{i,j}\left|a_{ij}\right|^{2}\right)^{1/2}
+\end{equation}
+is $\sqrt{3}$\nb\cite{GolubVanLoan1996,Jaeger2007}, where $a_{ij}$
+are the $\left(i,j\right)$-th entry of $A$; its operator $p$-norms
+\begin{equation}
+\left\Vert A\right\Vert _{p}=\sup_{\left\Vert \ket{\psi}\right\Vert _{p}=1}\left\Vert A\ket{\psi}\right\Vert _{p}=\sup_{\ket{\psi}\ne0}\left\Vert A\ket{\psi}\right\Vert _{p}/\left\Vert \ket{\psi}\right\Vert _{p}
+\end{equation}
+are $\left\Vert A\right\Vert _{1}=\left\Vert A\right\Vert _{\infty}=2$
+and $\left\Vert A\right\Vert _{2}=\left[\left(3+\sqrt{5}\right)/2\right]^{1/2}$\nb\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996},
+where $\ket{\psi}=\sum_{i=1}^{d}\alpha_{i}\ket{i}$, $\left\Vert \ket{\psi}\right\Vert _{\infty}=\max_{i}\left|\alpha_{i}\right|$,
+and $\left\Vert \ket{\psi}\right\Vert _{p}=\left(\sum_{i=1}^{d}\left|\alpha_{i}\right|^{p}\right)^{1/p}$
+for $1\le p<\infty$. The common matrix norms of $A$ are all different
+from $3/2$ so that our norm defined in definition~\ref{def:norm}
+is different from them.\end{example}
 
@@
 \begin{equation}
-\frac{\delta}{d}\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
+\delta/d\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
 \end{equation}
@@
 \begin{equation}
-\frac{\delta}{d}\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
+\delta/d\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
 \end{equation}

### 2017-06-30 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

@@
 
-\begin{definition}\label{def:norm}\cite{544199} Given a operator
-or matrix\nb$A$, the norm of $A$ is defined by 
+\begin{definition}\label{def:norm}Given a operator or matrix\nb$A$,
+the norm of $A$ is defined by\nb\cite{544199}
 \begin{equation}
@@
 \end{array}\right)$. It is easy to verify $\left\Vert A\right\Vert =3/2$. On the other
-hand, its Frobenius norm or Hilbert-Schmidt norm
+hand, its Frobenius norm or Hilbert-Schmidt norm\nb\cite{GolubVanLoan1996,Jaeger2007}
 \begin{equation}
@@
 \end{equation}
-is $\sqrt{3}$\nb\cite{GolubVanLoan1996,Jaeger2007}, where $a_{ij}$
-are the $\left(i,j\right)$-th entry of $A$; its operator $p$-norms
+is $\sqrt{3}$, where $a_{ij}$ are the $\left(i,j\right)$-th entry
+of $A$; its operator $p$-norms\nb\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996}
 \begin{equation}
@@
 are $\left\Vert A\right\Vert _{1}=\left\Vert A\right\Vert _{\infty}=2$
-and $\left\Vert A\right\Vert _{2}=\left[\left(3+\sqrt{5}\right)/2\right]^{1/2}$\nb\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996},
+and $\left\Vert A\right\Vert _{2}=\left[\left(3+\sqrt{5}\right)/2\right]^{1/2}$,
 where $\ket{\psi}=\sum_{i=1}^{d}\alpha_{i}\ket{i}$, $\left\Vert \ket{\psi}\right\Vert _{\infty}=\max_{i}\left|\alpha_{i}\right|$,
@@
 from $3/2$ so that our norm defined in definition~\ref{def:norm}
-is different from them.\end{example}
+is different from all of them.\end{example}
 

### 2017-07-02 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

@@
 
-The previously defined matrix norm is not one of the common matrix
-norms as shown in the following example.
+Notice that the norm in definition~\ref{def:norm} is not one of
+the common matrix norms.
 
@@
 \end{array}\right)$. It is easy to verify $\left\Vert A\right\Vert =3/2$. On the other
-hand, its Frobenius norm or Hilbert-Schmidt norm\nb\cite{GolubVanLoan1996,Jaeger2007}
-\begin{equation}
-\left\Vert A\right\Vert _{\mathrm{F}}=\Tr\left(A^{\dagger}A\right)=\left(\sum_{i,j}\left|a_{ij}\right|^{2}\right)^{1/2}
-\end{equation}
-is $\sqrt{3}$, where $a_{ij}$ are the $\left(i,j\right)$-th entry
-of $A$; its operator $p$-norms\nb\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996}
-\begin{equation}
-\left\Vert A\right\Vert _{p}=\sup_{\left\Vert \ket{\psi}\right\Vert _{p}=1}\left\Vert A\ket{\psi}\right\Vert _{p}=\sup_{\ket{\psi}\ne0}\left\Vert A\ket{\psi}\right\Vert _{p}/\left\Vert \ket{\psi}\right\Vert _{p}
-\end{equation}
-are $\left\Vert A\right\Vert _{1}=\left\Vert A\right\Vert _{\infty}=2$
+hand, its Frobenius norm or Hilbert-Schmidt norm is\nb\cite{GolubVanLoan1996,Jaeger2007}
+\begin{equation}
+\left\Vert A\right\Vert _{\mathrm{F}}=\Tr\left(A^{\dagger}A\right)=\left(\sum_{i,j}\left|a_{ij}\right|^{2}\right)^{1/2}=\sqrt{3}\,,
+\end{equation}
+where $a_{ij}$ are the $\left(i,j\right)$-th entry of $A$. If we
+consider the operator $p$-norms\nb\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996}
+\begin{equation}
+\left\Vert A\right\Vert _{p}=\sup_{\left\Vert \ket{\psi}\right\Vert _{p}=1}\left\Vert A\ket{\psi}\right\Vert _{p}=\sup_{\ket{\psi}\ne0}\frac{\left\Vert A\ket{\psi}\right\Vert _{p}}{\left\Vert \ket{\psi}\right\Vert _{p}}\,,
+\end{equation}
+we have $\left\Vert A\right\Vert _{1}=\left\Vert A\right\Vert _{\infty}=2$
 and $\left\Vert A\right\Vert _{2}=\left[\left(3+\sqrt{5}\right)/2\right]^{1/2}$,

### 2017-07-04 prop_iop.tex
prop_letter.tex Updating...

@@
 \begin{definition}A mixed state\nb$\rho$ is called totally mixed
-if it satisfies the following conditions.
-\begin{itemize}
-\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=0$ if and only if $P=\mathbb{0}$.
-\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=1$ if and only if $P=\mathbb{1}$.
-\end{itemize}
-\end{definition}
+if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.\end{definition}
 

### 2017-07-04 prop_letter.tex
prop_letter.tex Updating...

@@
 
-Although Gleason's theorem doesn't hold for every quantum IVPM, it
-can be applied in a limit case when the intervals are infinitely precise.
-That is, when $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+Although Gleason's theorem doesn't hold for every quantum IVPM, if
+a quantum IVPM\nb$\bar{\mu}$ is induced by a totally mixed state\nb$\rho$
+nicely, then whether another density matrix\nb$\rho'\in\coreBorn\left(\bar{\mu},\events'\right)$
+can be estimated by $\left\Vert \rho-\rho'\right\Vert $, where a
+state\nb$\rho$ is called totally mixed if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
+for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
+and the the norm of a matrix\nb$A$ is defined by $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
+For example, consider the intervals\nb$\widehat{\mathscr{I}}_{n}=\set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\cup\left\{ \left[0,0\right],\left[1,1\right]\right\} $
+which are overlapping intervals with length\nb$1/n$ except the intervals
+near the ends. We can define an interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
+by the following:
+\begin{itemize}
+\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
+\item when $0<x<1$, we have $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
+where $k$ is defined by either one of the following:
+\begin{itemize}
+\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
+\item $2\nmid k$ and $k-0.5<2nx<k+0.5$.
+\end{itemize}
+\end{itemize}
+Then, for any totally mixed state\nb$\rho$ on a $d$-dimensional
+Hilbert space, $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+is a QIVPM, and we have
+\begin{itemize}
+\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, then
+$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
+\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
+\end{itemize}
+In summary, the states consistent with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+will be closer and closer to $\rho$ as $n$ goes to infinity. In
+a limit case when the intervals are infinitely precise, i.e., $\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
 any quantum IVPM can be recast as an real-valued one and has a unique

### 2017-07-04 prop_letter.tex
prop.tex @Book{HuberRonchetti2009} Added...

@@
 
-We will start by reviewing IVPMs in the classical setting\nb\citep{JamisonLodwick2004,Galvan2008}
+We will start by reviewing IVPMs in the classical setting
 and then propose our quantum generalization. In the classical setting,
-there are several proposals for ``imprecise probabilities\nb\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,Grabisch2016}.''
+there are several proposals for ``imprecise
+probabilities\nb\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,HuberRonchetti2009,Grabisch2016}.''
 Although these proposals differ in some details, they all share the

### 2017-07-05 prop_letter.tex
prop_letter.tex Updating...

@@
 and the the norm of a matrix\nb$A$ is defined by $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
-For example, consider the intervals\nb$\widehat{\mathscr{I}}_{n}=\set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\cup\left\{ \left[0,0\right],\left[1,1\right]\right\} $
+For example, consider the intervals
+\begin{eqnarray}
+\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
+ &  & \cup\left\{ \left[0,0\right],\left[1,1\right]\right\} 
+\end{eqnarray}
 which are overlapping intervals with length\nb$1/n$ except the intervals
@@
 \item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
-\item when $0<x<1$, we have $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
-where $k$ is defined by either one of the following:
+\item when $0<x<1$, $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
+where $k$ is defined by one of the following:
 \begin{itemize}
@@
 \begin{itemize}
-\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, then
-$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
+\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
 \item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,

### 2017-07-06 prop_letter.tex
minor changes up in first three sections

@@
 \begin{abstract}~
+\amr{rewrite from scratch}
 \begin{description}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Introduction}
+\section{Introduction}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Fuzzy Measurements}
+\section{Fuzzy Measurements}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Intervals of Uncertainty}
-
-We will start by reviewing IVPMs in the classical setting
-and then propose our quantum generalization. In the classical setting,
-there are several proposals for ``imprecise
-probabilities\nb\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,HuberRonchetti2009,Grabisch2016}.''
+\section{Intervals of Uncertainty}
+
+We will start by reviewing IVPMs in the classical setting and then
+propose our quantum generalization. In the classical setting, there
+are several proposals for ``imprecise
+probabilities''~\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,HuberRonchetti2009,Grabisch2016}.
 Although these proposals differ in some details, they all share the
-fact that the probability $\mu(E)$ of an event $E$ is generalized
-from a single real number to an interval of certainty $[\ell,r]$
-where\nb$\ell$ intuitively corresponds to the strength of evidence
-for the event and $r$ corresponds to the strength of evidence against
-the event. The collection of intervals used in the definition of a
+fact that the probability $\mu(E)$ of an event~$E$ is generalized from
+a single real number to an interval of certainty $[\ell,r]$
+where\nb$\ell$ intuitively corresponds to the strength of evidence for
+the event and~$r$ corresponds to the strength of evidence against the
+event. The collection of intervals used in the definition of a
 probability measure must satisfy certain properties which we explain
@@
 event. For example, if we discover as a result of an experiment that
-$\mu(E) = [0.2,0.3]$ for some event\nb$E$, we may conclude that
+$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
 $\mu(\overline{E}) = [0.7,0.8]$ for the complement event
@@
 When combining non-disjoint events, there is a further subtlety whose
-resolution will give the most general and final condition as
-follows. For general, non-necessarily disjoint events $E_1$ and $E_2$,
-we have:
+resolution will give the most general and final condition. For
+general, non-necessarily disjoint events $E_1$ and $E_2$, we have:
 \begin{equation}
@@
 understanding that the union of classical sets $E_1\cup E_2$ is replaced
-by $P_0+P_1-P_0P_1$ in the case of projection operators\nb\cite{Griffiths2003}, the last
+by $P_0+P_1-P_0P_1$ in the case of projection operators~\cite{Griffiths2003}, the last
 condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
@@
 Born rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
-Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$ is
+Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
 consistent with $\bar{\mu}$ on every projector in $S$.
@@
 \end{equation}
-is a quantum IVPM. This measure represents the beliefs of an
-experimenter with no prior knowledge about the particular quantum
-system in question; any quantum state would be consistent with
-$\bar{\mu}_{1}$ on any projectors. We have that
+is a QIVPM. This measure represents the beliefs of an experimenter
+with no prior knowledge about the particular quantum system in
+question; any quantum state would be consistent with $\bar{\mu}_{1}$
+on any projectors. We have that
 $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
@@
 $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
-IVPM\nb$\bar{\mu}_{2}$:
+IVPM~$\bar{\mu}_{2}$:
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Kochen-Specker}
-
-Our first result regarding QIVPM is that a QIVPM cannot be
-cryptodeterministic in the sense of Peres\nb\cite{PeresRon1988,peres1995quantum}. We
-will adapt the proof of the Kochen-Specker
-theorem\nb\cite{kochenspecker1967,
+\section{Kochen-Specker}
+
+Our first result is that a QIVPM cannot be cryptodeterministic in the
+sense of Peres\nb\cite{PeresRon1988,peres1995quantum}. We will adapt
+the proof of the Kochen-Specker theorem~\cite{kochenspecker1967,
   peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
@@
 
-\begin{definition}Given a Hilbert space of $d\ge3$, for every QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-any observable\nb$\mathbf{O}$ with spectral decomposition $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$,
-and $\events'$ is minimal sub-event space containing $\left\{ P_{i}\right\} _{i=1}^{N}$,
-we have
+\begin{definition}Given a Hilbert space of $d\ge3$, for every
+  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, any
+  observable\nb$\mathbf{O}$ with spectral decomposition
+  $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, and $\events'$ is
+  minimal sub-event space containing
+  $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
 \begin{equation}
@@
 \begin{definition}\label{def:delta-deterministic}A QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is called $\delta$-deterministic if either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
-or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$ for
-any $P\in\events$.\end{definition}
+  is called $\delta$-deterministic if either
+  $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$ or
+  $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$ for any
+  $P\in\events$.\end{definition}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Gleason}
+\section{Gleason}
 
@@
 sub-event space. As the result, there may be no state consistent with
-a quantum IVPM on all projectors\nb$\events$.
+a QIVPM on all projectors\nb$\events$.
 
@@
 \end{subequations}
-It is straightforward to verify that $\bar{\mu}_{3}$ is a
-quantum IVPM.
+It is straightforward to verify that $\bar{\mu}_{3}$ is a QIVPM.
 
@@
 
-Although Gleason's theorem doesn't hold for every quantum IVPM, if
-a quantum IVPM\nb$\bar{\mu}$ is induced by a totally mixed state\nb$\rho$
-nicely, then whether another density matrix\nb$\rho'\in\coreBorn\left(\bar{\mu},\events'\right)$
-can be estimated by $\left\Vert \rho-\rho'\right\Vert $, where a
-state\nb$\rho$ is called totally mixed if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
-for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
-and the the norm of a matrix\nb$A$ is defined by $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
+Although Gleason's theorem doesn't hold for every QIVPM, if a quantum
+IVPM\nb$\bar{\mu}$ is induced by a totally mixed state\nb$\rho$
+nicely, then whether another density
+matrix\nb$\rho'\in\coreBorn\left(\bar{\mu},\events'\right)$ can be
+estimated by $\left\Vert \rho-\rho'\right\Vert $, where a
+state\nb$\rho$ is called totally mixed if
+$0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
+$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $, and the
+the norm of a matrix\nb$A$ is defined by
+$\left\Vert A\right\Vert
+=\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
 For example, consider the intervals
@@
 \end{itemize}
-In summary, the states consistent with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-will be closer and closer to $\rho$ as $n$ goes to infinity. In
-a limit case when the intervals are infinitely precise, i.e., $\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-any quantum IVPM can be recast as an real-valued one and has a unique
-state consistent with it on every projector when $d\ge3$.
+In summary, the states consistent with
+$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will be closer and
+closer to $\rho$ as $n$ goes to infinity. In a limit case when the
+intervals are infinitely precise, i.e.,
+$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
+recast as an real-valued one and has a unique state consistent with it
+on every projector when $d\ge3$.
 
@@
 by using finer and finer intervals, it would be more and more likely
-that there is a state consistent with a quantum IVPM on all projectors\nb$\events$.
+that there is a state consistent with a QIVPM on all projectors\nb$\events$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusion}
+\section{Conclusion}
 
@@
 
-To adapt the axioms of such IVPMs to the quantum case, we proceed as
-follows. First we fix a collection of intervals $\mathscr{I}$ that
-represents an abstraction of the available experimental resources. At
-one extreme, infinitely precise resources would correspond to the
-collection of intervals $\{[x,x] \mid x \in [0,1]\}$. This case should
-coincide with the idealized situation above. At another extreme, an
-experiment with ``minimal'' resources would correspond to the
-following three intervals $\imposs=\left[0,0\right]$,
-$\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
-two intervals are associated with the empty projection and the
-identity projection but every other projection would be associated
-with $\unknown$; its probability can be anything in the range
-$[0,1]$. A third special situation would be to consider IVPMs with
-only the two intervals $\imposs=\left[0,0\right]$ and
-$\necess=\left[1,1\right]$. This is what Peres calls the
-\emph{cryptodeterministic} case in which there is no ambiguity about
-the status of any event; we know for certain if it will occur or not.
-
-\begin{definition}
-$\bar{\mu}$ is called convex. if for all
-commuting $P_{0},P_{1}\in\events$, we have
-$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
-\end{definition}
-
-Consider again
-Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}. We will
-generalize it as follows for all commuting $P_{0},P_{1}\in\events$, we
-have
-$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$. Note
-that if $P_0$ and $P_1$ are \emph{orthogonal}, i.e., if $P_0P_1=0$ the
-new equation reduces to
-Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}.
-
-\begin{verbatim}
-Inclusion exclusion principle 
- pr(e1 union e2) + pr (e1 intersect e2) = 
-  pr(e1) + pr(e2)
-
-in classical Real number prob. LHS = X; RHS = X
-
----
-
-in classical IVPM; we only get LHS <= X; RHS <= X
-but we have no connection between LHS and RHS
-
-convexity imposes that LHS >= RHS
-
----
-
-our condition in the quantum case is the same; 
-our left(LHS) is >= left(RHS); the right is dual, 
-which makes LHS interval subset RHS interval.
-
---
-
-replace set union by projection sum = p0 + p1 - p0p1
-replace = by subseteq
-
-and we get convexity definition
-
---
-
-Now we need a simple classical example that shows 
-why we need convexity or at least what it means
-
-must be dimension 4 because everything of dim 3 
-is convex in classical case
-
-Consider omega = { 0, 1, 2, 3 }
-intervals = imposssible, certain, 
-            unlikely = [0,0.5], likely [0.5,1]
-
-mu(empty) = imposs
-mu(omega) = certain
-mu({j}) = unlikely
-mu(Omega \ {j}) = likely
-mu({0,1}) = mu({0,2}) = mu({1,2}) = unlikely
-mu({0,3}) = mu({1,3}) = mu({2,3}) = likely
-
-EQ A:
-mu({0}) + mu({0,1,2}) = [0.5,1.5]
-mu({0,1}) + mu({0,2}) = [0,1]
-
-AND [0.5,1.5] is not subseteq of [0,1]
-
-Note that there is a core p(0) = p(1) = p(2) = 0.2, 
-p(3) = 0.4, and under that core both sides of EQ A 
-have prob. 0.8. So one way to make it convex is 
-to use very precise intervals [0.2,0.2] etc.
-
-Another way to make this convex is by choosing 
-just one additional interval unknown [0,1] 
-instead of unlikely and likely.
-
-Intuition: the more you group the more 
-precise you get
-
-\end{verbatim}
-
-In the classical setting, IVPMs typically are equipped with additional
-conditions to ensure they are ``well-behaved.''
-
-\amr{
-Yu-Tsung: please construct an example with commuting events P0 and P1 such that:
-
-mu(P0 + P1 - P0P1) + mu(P0P1) = [x,y]
-mu(P0) + mu(P1) = [z,w]
-
-and $[x,y]$ is NOT included in $[z,w]$
-}
-
-\yutsung{{Consider a four dimensional Hilbert space with an orthonormal
-basis}\nb$\Omega=\{\ket{0},\ket{1},\ket{2},\ket{3}\}$, and the commuting
-sub-event space\nb$\events'=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$.
-Then, $\bar{\mu}_{0}:\events'\rightarrow\mathscr{I}$ defined by\begin{subequations}
-\begin{eqnarray}
- &  & \imposs=\bar{\mu}_{0}(\mathbb{0})\,,\\
- &  & \necess=\bar{\mu}_{0}(\mathbb{1})\,,\\
- &  & \begin{aligned}\unlikely & =\bar{\mu}_{0}(\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{1})\\
- & =\bar{\mu}_{0}(\proj{0}+\proj{2})\\
- & =\bar{\mu}_{0}(\proj{1}+\proj{2})\,,
-\end{aligned}
-\\
- &  & \begin{aligned}\likely & =\bar{\mu}_{0}(\mathbb{1}-\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{2})\\
- & =\bar{\mu}_{0}(\proj{1}+\proj{3})\\
- & =\bar{\mu}_{0}(\proj{2}+\proj{3})
-\end{aligned}
-\end{eqnarray}
-\end{subequations}is an IVPM, where $\ket{j}\in\Omega$ and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
-However, $\bar{\mu}_{0}$ is not convex because
-\begin{equation}
-\begin{aligned} & \bar{\mu}_{0}(\proj{0})+\bar{\mu}_{0}(\mathbb{1}-\proj{3})\\
-= & \left[\frac{1}{2},\frac{3}{2}\right]\nsubseteq\left[1,2\right]\\
-= & \bar{\mu}_{0}(\proj{0}+\proj{1})+\bar{\mu}_{0}(\proj{0}+\proj{2})\,.
-\end{aligned}
-\end{equation}
-}
-
-Formally, we can ask: what can we deduce about the state of a quantum
-system given a quantum IVPM, i.e., given observations done with finite
-resources. Since the probabilities are now intervals, it is intuitive
-to say a state\nb$\rho$ is consistent with $\bar{\mu}$ on a projector\nb$P$
-if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
-and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
-Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
-is consistent with $\bar{\mu}$ on every projector in $S$.
-
-Consider a quantum IVPM $\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
-and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
-for all $P\in\events$. This time, when we express an observable as
-its spectral decomposition
-\begin{equation}
-\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
-\end{equation}
-we separate the positive and negative eigenvalues and order its eigenvalues
-from the smallest to the largest 
-\begin{equation}
-\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
-\end{equation}
-Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-We can combine the classical Choquet integral\nb\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
-value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
-\begin{eqnarray}
-\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
-\end{eqnarray}
-
-\begin{table*}
-\caption{\label{table:quantum-interval-expectation}This table highlights the
-process to compute $\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}$. Notice
-that $\bar{\mu}_{1}$ is defined by Eq.~(\ref{eq:no-information-IVPM}),
-$\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$,
-and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$ so that $\mul_{1}\left(P_{3}^{+\prime}\right)=\mur_{1}\left(P_{3}^{+\prime}\right)=0$.}
-
-\begin{ruledtabular}
-\begin{tabular}{c|ccccccccc}
-$i$ & $\lambda_{i}^{+}$ & $P_{i}^{+}$ & $\bar{\mu}_{1}\left(P_{i}^{+}\right)$ & $P_{i}^{+\prime}$ & $\bar{\mu}_{1}\left(P_{i}^{+\prime}\right)$ & $\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\mur_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mur_{1}\left(P_{i}^{+\prime}\right)$\tabularnewline
-\hline 
-$1$ & $1$ & $\proj{0}+\proj{2}$ & $\unknown$ & $\mathbb{1}$ & $\necess$ & $1$ & $1$ & $1$ & $0$\tabularnewline
-$2$ & $2$ & $\proj{1}$ & $\unknown$ & $\proj{1}$ & $\unknown$ & $0$ & $1$ & $0$ & $1$\tabularnewline
-\end{tabular}
-\end{ruledtabular}
-
-\end{table*}
-For example, given a three dimensional Hilbert space with an orthonormal
-basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
-and $\mathbf{O}_{1}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
-By following Table~\ref{table:quantum-interval-expectation}, we
-have 
-\begin{equation}
-\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\,.
-\end{equation}
-The expectation value is intuitively between two possible outcomes,
-$1$ and $2$, even if we have no prior knowledge about the likelihood
-of outcomes. In contrast, if we naively multiply eigenvalues with
-intervals, their sum, $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$,
-is a worse and counter-intuitive estimation. In fact, estimating the
-lower-bound by $1\cdot0+2\cdot0=0$ is too pessimistic because we
-know one of outcomes must happen without any prior knowledge.
-
-Intuitively, the expectation value of an observable with respect to a
-QIVPM is bounded by the minimum and maximum expectation value of the
-same observable with respect to states consistent with it. This is
-true when we require our IVPM to be convex, and on a commuting
-sub-event space induced by an observable.
-
-%%%%%
-\subsection{Gleason}
+% To adapt the axioms of such IVPMs to the quantum case, we proceed as
+% follows. First we fix a collection of intervals $\mathscr{I}$ that
+% represents an abstraction of the available experimental resources. At
+% one extreme, infinitely precise resources would correspond to the
+% collection of intervals $\{[x,x] \mid x \in [0,1]\}$. This case should
+% coincide with the idealized situation above. At another extreme, an
+% experiment with ``minimal'' resources would correspond to the
+% following three intervals $\imposs=\left[0,0\right]$,
+% $\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
+% two intervals are associated with the empty projection and the
+% identity projection but every other projection would be associated
+% with $\unknown$; its probability can be anything in the range
+% $[0,1]$. A third special situation would be to consider IVPMs with
+% only the two intervals $\imposs=\left[0,0\right]$ and
+% $\necess=\left[1,1\right]$. This is what Peres calls the
+% \emph{cryptodeterministic} case in which there is no ambiguity about
+% the status of any event; we know for certain if it will occur or not.
+
+% \begin{definition}
+% $\bar{\mu}$ is called convex. if for all
+% commuting $P_{0},P_{1}\in\events$, we have
+% $\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
+% \end{definition}
+
+% Consider again
+% Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}. We will
+% generalize it as follows for all commuting $P_{0},P_{1}\in\events$, we
+% have
+% $\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$. Note
+% that if $P_0$ and $P_1$ are \emph{orthogonal}, i.e., if $P_0P_1=0$ the
+% new equation reduces to
+% Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}.
+
+% \begin{verbatim}
+% Inclusion exclusion principle 
+%  pr(e1 union e2) + pr (e1 intersect e2) = 
+%   pr(e1) + pr(e2)
+
+% in classical Real number prob. LHS = X; RHS = X
+
+% ---
+
+% in classical IVPM; we only get LHS <= X; RHS <= X
+% but we have no connection between LHS and RHS
+
+% convexity imposes that LHS >= RHS
+
+% ---
+
+% our condition in the quantum case is the same; 
+% our left(LHS) is >= left(RHS); the right is dual, 
+% which makes LHS interval subset RHS interval.
+
+% --
+
+% replace set union by projection sum = p0 + p1 - p0p1
+% replace = by subseteq
+
+% and we get convexity definition
+
+% --
+
+% Now we need a simple classical example that shows 
+% why we need convexity or at least what it means
+
+% must be dimension 4 because everything of dim 3 
+% is convex in classical case
+
+% Consider omega = { 0, 1, 2, 3 }
+% intervals = imposssible, certain, 
+%             unlikely = [0,0.5], likely [0.5,1]
+
+% mu(empty) = imposs
+% mu(omega) = certain
+% mu({j}) = unlikely
+% mu(Omega \ {j}) = likely
+% mu({0,1}) = mu({0,2}) = mu({1,2}) = unlikely
+% mu({0,3}) = mu({1,3}) = mu({2,3}) = likely
+
+% EQ A:
+% mu({0}) + mu({0,1,2}) = [0.5,1.5]
+% mu({0,1}) + mu({0,2}) = [0,1]
+
+% AND [0.5,1.5] is not subseteq of [0,1]
+
+% Note that there is a core p(0) = p(1) = p(2) = 0.2, 
+% p(3) = 0.4, and under that core both sides of EQ A 
+% have prob. 0.8. So one way to make it convex is 
+% to use very precise intervals [0.2,0.2] etc.
+
+% Another way to make this convex is by choosing 
+% just one additional interval unknown [0,1] 
+% instead of unlikely and likely.
+
+% Intuition: the more you group the more 
+% precise you get
+
+% \end{verbatim}
+
+% In the classical setting, IVPMs typically are equipped with additional
+% conditions to ensure they are ``well-behaved.''
+
+% \amr{
+% Yu-Tsung: please construct an example with commuting events P0 and P1 such that:
+
+% mu(P0 + P1 - P0P1) + mu(P0P1) = [x,y]
+% mu(P0) + mu(P1) = [z,w]
+
+% and $[x,y]$ is NOT included in $[z,w]$
+% }
+
+% \yutsung{{Consider a four dimensional Hilbert space with an orthonormal
+% basis}\nb$\Omega=\{\ket{0},\ket{1},\ket{2},\ket{3}\}$, and the commuting
+% sub-event space\nb$\events'=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$.
+% Then, $\bar{\mu}_{0}:\events'\rightarrow\mathscr{I}$ defined by\begin{subequations}
+% \begin{eqnarray}
+%  &  & \imposs=\bar{\mu}_{0}(\mathbb{0})\,,\\
+%  &  & \necess=\bar{\mu}_{0}(\mathbb{1})\,,\\
+%  &  & \begin{aligned}\unlikely & =\bar{\mu}_{0}(\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{1})\\
+%  & =\bar{\mu}_{0}(\proj{0}+\proj{2})\\
+%  & =\bar{\mu}_{0}(\proj{1}+\proj{2})\,,
+% \end{aligned}
+% \\
+%  &  & \begin{aligned}\likely & =\bar{\mu}_{0}(\mathbb{1}-\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{2})\\
+%  & =\bar{\mu}_{0}(\proj{1}+\proj{3})\\
+%  & =\bar{\mu}_{0}(\proj{2}+\proj{3})
+% \end{aligned}
+% \end{eqnarray}
+% \end{subequations}is an IVPM, where $\ket{j}\in\Omega$ and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
+% However, $\bar{\mu}_{0}$ is not convex because
+% \begin{equation}
+% \begin{aligned} & \bar{\mu}_{0}(\proj{0})+\bar{\mu}_{0}(\mathbb{1}-\proj{3})\\
+% = & \left[\frac{1}{2},\frac{3}{2}\right]\nsubseteq\left[1,2\right]\\
+% = & \bar{\mu}_{0}(\proj{0}+\proj{1})+\bar{\mu}_{0}(\proj{0}+\proj{2})\,.
+% \end{aligned}
+% \end{equation}
+% }
+
+% Formally, we can ask: what can we deduce about the state of a quantum
+% system given a quantum IVPM, i.e., given observations done with finite
+% resources. Since the probabilities are now intervals, it is intuitive
+% to say a state\nb$\rho$ is consistent with $\bar{\mu}$ on a projector\nb$P$
+% if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+% and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
+% Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
+% is consistent with $\bar{\mu}$ on every projector in $S$.
+
+% Consider a quantum IVPM $\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+% and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
+% the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
+% for all $P\in\events$. This time, when we express an observable as
+% its spectral decomposition
+% \begin{equation}
+% \mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
+% \end{equation}
+% we separate the positive and negative eigenvalues and order its eigenvalues
+% from the smallest to the largest 
+% \begin{equation}
+% \lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
+% \end{equation}
+% Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
+% where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
+% We can combine the classical Choquet integral\nb\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+% with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
+% value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
+% \begin{eqnarray}
+% \expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
+% \end{eqnarray}
+
+% \begin{table*}
+% \caption{\label{table:quantum-interval-expectation}This table highlights the
+% process to compute $\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}$. Notice
+% that $\bar{\mu}_{1}$ is defined by Eq.~(\ref{eq:no-information-IVPM}),
+% $\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$,
+% and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$ so that $\mul_{1}\left(P_{3}^{+\prime}\right)=\mur_{1}\left(P_{3}^{+\prime}\right)=0$.}
+
+% \begin{ruledtabular}
+% \begin{tabular}{c|ccccccccc}
+% $i$ & $\lambda_{i}^{+}$ & $P_{i}^{+}$ & $\bar{\mu}_{1}\left(P_{i}^{+}\right)$ & $P_{i}^{+\prime}$ & $\bar{\mu}_{1}\left(P_{i}^{+\prime}\right)$ & $\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\mur_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mur_{1}\left(P_{i}^{+\prime}\right)$\tabularnewline
+% \hline 
+% $1$ & $1$ & $\proj{0}+\proj{2}$ & $\unknown$ & $\mathbb{1}$ & $\necess$ & $1$ & $1$ & $1$ & $0$\tabularnewline
+% $2$ & $2$ & $\proj{1}$ & $\unknown$ & $\proj{1}$ & $\unknown$ & $0$ & $1$ & $0$ & $1$\tabularnewline
+% \end{tabular}
+% \end{ruledtabular}
+
+% \end{table*}
+% For example, given a three dimensional Hilbert space with an orthonormal
+% basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
+% and $\mathbf{O}_{1}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
+% By following Table~\ref{table:quantum-interval-expectation}, we
+% have 
+% \begin{equation}
+% \expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\,.
+% \end{equation}
+% The expectation value is intuitively between two possible outcomes,
+% $1$ and $2$, even if we have no prior knowledge about the likelihood
+% of outcomes. In contrast, if we naively multiply eigenvalues with
+% intervals, their sum, $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$,
+% is a worse and counter-intuitive estimation. In fact, estimating the
+% lower-bound by $1\cdot0+2\cdot0=0$ is too pessimistic because we
+% know one of outcomes must happen without any prior knowledge.
+
+% Intuitively, the expectation value of an observable with respect to a
+% QIVPM is bounded by the minimum and maximum expectation value of the
+% same observable with respect to states consistent with it. This is
+% true when we require our IVPM to be convex, and on a commuting
+% sub-event space induced by an observable.
+
+% %%%%%
+% \subsection{Gleason}

### 2017-07-06 prop_letter.tex
sec 4

@@
 
-The argument refers to the expectation value of these
+\noindent The argument refers to the expectation value of these
 observables. In the case of QIVPM this is defined as follows.
@@
   observable\nb$\mathbf{O}$ with spectral decomposition
-  $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, and $\events'$ is
-  minimal sub-event space containing
+  $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, and any minimal
+  sub-event space $\events'$ containing
   $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
@@
 which lie between the minimum and maximum bounds of the given
-probability intervals, and this definition also consistent with the classical
-Choquet integral on commuting sub-event space by adopting the classical
-results\nb\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
-If the QIVPM is cryptodeterministic, this
-interval collapses to a singleton $\left\{ \lambda\right\} $, where
-$\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
-multiplication of two singleton sets\nb$\left\{ \lambda_{1}\right\} $
-and $\left\{ \lambda_{2}\right\} $ to be
+probability intervals. (This definition is consistent with the
+classical Choquet integral on commuting sub-event spaces by adopting
+the classical
+results\nb\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.)
+If the QIVPM is cryptodeterministic, this interval collapses to a
+singleton $\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
+of~$\mathbf{O}$. If we define the multiplication of two singleton
+sets\nb$\left\{ \lambda_{1}\right\} $ and
+$\left\{ \lambda_{2}\right\} $ to be
 $\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
@@
 
-Since the expectation value\nb$\expval{\cdot}_{\bar{\mu}}$ satisfying
+Since the expectation value\nb$\expval{\cdot}_{\bar{\mu}}$ satisfies
 these two properties, the observables in the Mermin-Peres square must
-have the the expectation value\nb$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
-In each row and column, operators commutes, and each operator is the
-product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-Therefore, it is clear impossible to find a IVPM\nb$\bar{\mu}$ such
+have the the expectation value\nb$\left\{ 1\right\} $ or
+$\left\{ -1\right\} $.  In each row and column, the operators commute,
+and each operator is the product of the two others, except in the
+third column
+$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+Therefore, it is clearly impossible to find a QIVPM\nb$\bar{\mu}$ such
 that $\langle \mathbf{O}_{ij}\rangle_{\bar \mu}$
@@
 %\end{equation}
-satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
-
-According to Mermin's comment\nb\citep{Mermin1999}, 
+satisfies Eq.~(\ref{eq:Kochen-Specker-Rules}).
+
+The question now is what happens if we relax the perfect measurement
+assumption that entails that the intervals are precisely $[0,0]$ and
+$[1,1]$. What if the measurement imperfections occasionally cause an
+ideally impossible event to be detected or an ideally certain event to
+be not be detected. Mermin argues in this case that:
 \begin{quote}
-...although the outcomes deduced from such imperfect measurements
-will occasionally differ dramatically from those allowed in the ideal
-case, if the misalignment is very slight, the statistical distribution
-of outcomes will differ only slightly from the ideal case... 
+  \ldots although the outcomes deduced from such imperfect
+  measurements will occasionally differ dramatically from those
+  allowed in the ideal case, if the misalignment is very slight, the
+  statistical distribution of outcomes will differ only slightly from
+  the ideal case~\citep{Mermin1999}.
 \end{quote}
-if the imperfection of the measurement is small enough, the finitely
-precise measurement should be close to idealized measurement, and
-cannot nullify the Kochen-Specker theorem. This idea can be modeled
-precisely by considering the following kind of QIVPMs.
+
+We can formally test this hypothesis by considering the notion of
+$\delta$-deterministic QIVPM below.
 
@@
 
-For example, any cryptodeterministic QIVPM is $0$-deterministic.
-As another example, a $\frac{1}{3}$-deterministic QIVPM can be given
-by $\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
+A cryptodeterministic QIVPM is $0$-deterministic.  As $\delta$ gets
+bigger, the QIVPM allows more and more indeterminate behavior. A
+$\frac{1}{3}$-deterministic QIVPM can be given by
+$\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
 onto a $x$-dimensional subspace in a three-dimensional Hilbert space.
-By utilizing $\delta$-deterministic QIVPMs, we can have a Kochen-Specker
-theorem with finite precision measurement.
-
-\begin{thm}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
-of dimension\nb$d\ge3$, there is no $\delta$-deterministic QIVPM
-for $\delta<\frac{1}{3}$.\end{thm}
-
-\begin{proof}Suppose there is a $\delta$-deterministic QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-we can define a cryptodeterministic QIVPM\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $
-by 
+
+We now prove that for small enough $\delta$, the Kochen-Specker is
+still valid, i.e., if the measurement imperfections are small enough,
+we cannot nullify the Kochen-Specker theorem as
+Meyer~\cite{PhysRevLett.83.3751} argued.
+
+\begin{thm}\label{cor:Kochen-Specker-IVPM} Given a Hilbert space
+  of dimension\nb$d\ge3$, there is no $\delta$-deterministic QIVPM for
+  $\delta<\frac{1}{3}$.\end{thm}
+
+\begin{proof} Suppose there is a $\delta$-deterministic
+  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
+  following QIVPM
+  \nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
+    \imposs,\necess\right\} $ is cryptodeterministic:
 \begin{equation}
@@
 \end{equation}
-However, there is no cryptodeterministic QIVPM as we discussed according
-to the Mermin-Peres square, so that there is no $\delta$-deterministic
-QIVPM.
-
-The essential part to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
-QIVPM is to verify a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),\begin{subequations}
+However, since we know that there is no cryptodeterministic QIVPM,
+$\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ cannot
+exist.
+
+It remains to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
+QIVPM. The main part of that verification is to check:
+\begin{subequations}
 \begin{eqnarray}
@@
 which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. 
-
-By discussing the remaining cases, we can easily verify that $\bar{\mu}^{\textrm{D}}$
-is a cryptodeterministic QIVPM.\end{proof}
+\end{proof}
 

### 2017-07-06 prop_letter.tex
done except abstract and intro

@@
 \begin{abstract}~
-\amr{rewrite from scratch}
 \begin{description}
@@
 In the classical setting, measurements done with limited resources and
-poor precision may not uniquely identify the true state of a system
+poor precision may not uniquely identify the true state of a
 system. However, there is always at least one state that is consistent
 with the imprecise
-measurements\nb\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
+measurements~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
 
 \begin{thm}\label{thm:Shapley}
-  For every QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
+  For a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
   sub-event space\nb$\events'\subseteq\events$ commutes, then
@@
 
-Gleason's theorem asserts any quantum real-valued probability measure
-is consistent with a unique mixed state, and Shapley proved a quantum
-IVPM must approximate some states for each classical sub-event
-space. However, it may not approximate the same state in every
-sub-event space. As the result, there may be no state consistent with
-a QIVPM on all projectors\nb$\events$.
+In the idealized situation of real-valued quantum probability
+measures, Gleason's theorem asserts that every measure is determined
+by a unique mixed state. The theorem above is weaker however: it
+asserts that, for each classical sub-event subspace, a QIVPM must be
+consistent with \emph{some} state. But the states consistent with
+different subspaces may be incomparable as the following example
+shows.
 
@@
 \end{subequations}
-It is straightforward to verify that $\bar{\mu}_{3}$ is a QIVPM.
-
-Let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because
+It is straightforward to verify that $\bar{\mu}_{3}$ is a QIVPM. Now
+let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because
 $\bar{\mu}_{3}(\proj{0})=\bar{\mu}_{3}(\proj{\ps})=\imposs$, we have
@@
 state\nb$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.  Hence,
-$\rho$ cannot be any state other than $\ket{2}$, the only pure state orthogonal to both
-$\ket{0}$ and $\ket{\ps}$, and it is easy to verify $\proj{2}$ is actually
-in $\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
-
-Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We have
+$\rho$ cannot be any state other than $\ket{2}$, the only pure state
+orthogonal to both $\ket{0}$ and $\ket{\ps}$, and it is easy to verify
+$\proj{2}$ is actually in
+$\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$. Similarly, let
+$S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We have
 $\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\left\{ \proj{1}\right\} $.
@@
 \end{equation}
-and must be empty.
+Thus, there is no state that is consistent with the QIVPM on all
+projectors\nb$\events$ invalidating Gleason's theorem.
 \end{example}
 
-Although Gleason's theorem doesn't hold for every QIVPM, if a quantum
-IVPM\nb$\bar{\mu}$ is induced by a totally mixed state\nb$\rho$
-nicely, then whether another density
-matrix\nb$\rho'\in\coreBorn\left(\bar{\mu},\events'\right)$ can be
-estimated by $\left\Vert \rho-\rho'\right\Vert $, where a
-state\nb$\rho$ is called totally mixed if
+Although Gleason's theorem does not hold for every QIVPM, we can show
+that for a certain class of QIVPMs, the collection of states
+consistent with the projectors get closer and closer to each other as
+the intervals get narrower and narrower, eventually collapsing to a
+single state when the intervals become infinitely precise real
+numbers. To state this result, we introduce a few technical notions.
+
+We call a state $\rho$ a \emph{totally mixed state} if
 $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
-$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $, and the
-the norm of a matrix\nb$A$ is defined by
+$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $. We also
+define a notion of distance based on the following norm of a
+matrix\nb$A$ as
 $\left\Vert A\right\Vert
-=\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
-For example, consider the intervals
+=\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}. Now
+consider the following collection of intervals:
 \begin{eqnarray}
@@
 which are overlapping intervals with length\nb$1/n$ except the intervals
-near the ends. We can define an interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
-by the following:
+near the ends.
+
+A totally mixed state induces a QIVPM over the intervals above as
+follows. We first define a map $\widehat{\iota}_{n}$ from the interval
+$[0,1]$ to the collection of intervals above as follows:
 \begin{itemize}
@@
 \end{itemize}
-Then, for any totally mixed state\nb$\rho$ on a $d$-dimensional
-Hilbert space, $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-is a QIVPM, and we have
+
+It is now not difficult to verify that for any totally mixed
+state\nb$\rho$ on a $d$-dimensional Hilbert space,
+$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is a
+QIVPM. Furthemore, we have:
 \begin{itemize}
@@
 \end{itemize}
-In summary, the states consistent with
+In other words, the states consistent with this QIVMP
 $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will be closer and
-closer to $\rho$ as $n$ goes to infinity. In a limit case when the
-intervals are infinitely precise, i.e.,
+closer to $\rho$ as $n$ goes to infinity. In the limiting case when
+the intervals are infinitely precise, i.e.,
 $\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
-recast as an real-valued one and has a unique state consistent with it
-on every projector when $d\ge3$.
-
-In general, this kind of inconsistency can be reduced if we increase
-the measurement resource, that is, using finer intervals. We conjecture
-by using finer and finer intervals, it would be more and more likely
-that there is a state consistent with a QIVPM on all projectors\nb$\events$.
+recast as an real-valued one and will have a unique state consistent
+with it on every projector when $d\ge3$.
+
+% In general, this kind of inconsistency can be reduced if we increase
+% the measurement resource, that is, using finer intervals. We conjecture
+% by using finer and finer intervals, it would be more and more likely
+% that there is a state consistent with a QIVPM on all projectors\nb$\events$.
+% We can define an interval-valued function\nb
+% :\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
+% by the following:
+
+% if a QIVPM\nb$\bar{\mu}$ is induced by a totally mixed
+% state\nb$\rho$ nicely, then whether another density
+% matrix\nb$\rho'\in\coreBorn\left(\bar{\mu},\events'\right)$ can be
+% estimated by $\left\Vert \rho-\rho'\right\Vert
+% $, where a
+% state\nb$\rho$ is called totally mixed if
+% $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
+% $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\}
+% $, and the the norm of a matrix\nb$A$ is defined by $\left\Vert
+%   A\right\Vert
+% =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
+% For example, consider the intervals
 

### 2017-07-06 prop_letter.tex
prop_letter.tex Trim Reference...

@@
 are several proposals for ``imprecise
-probabilities''~\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,HuberRonchetti2009,Grabisch2016}.
+probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
 Although these proposals differ in some details, they all share the
@@
 before. The new condition, known as
-\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
+\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
 reduces to the previously
@@
 is the probability that the event\nb$P$ happens determined by the
-Born rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
+Born rule\nb\cite{Born1983,peres1995quantum,544199}.
 Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
@@
 the classical
-results\nb\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.)
+results\nb\cite{GilboaSchmeidler1994,Grabisch2016}.)
 If the QIVPM is cryptodeterministic, this interval collapses to a

### 2017-07-07 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Fix a typo...

@@
 by $P_0+P_1-P_0P_1$ in the case of projection operators~\cite{Griffiths2003}, the last
-condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
-a direct counterpart of Eq.~\ref{eq:classicalconvex}.
+condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is
+a direct counterpart of Eq.~(\ref{eq:classicalconvex}).
 

### 2017-07-08 prop_iop.tex
prop_letter.pptx "Recover QRVPM and CIVPM as a special case" Updating...

@@
 QIVPM for $\delta<1/\left(3n\right)$.
+
+Lemma~\ref{lemma:QIVPM2QCM} may be extended in another trivial way.
+
+\begin{lemma}If every interval in $\mathscr{I}$ is a singleton set,
+given a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, then
+$\mu:\events\rightarrow\left[0,1\right]$defined by $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
+is a quantum probability measure.\end{lemma}
+
+\begin{proof}~
+\begin{itemize}
+\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
+\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
+\item For every event $P$, we have
+\begin{eqnarray*}
+ &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\\
+ & \Rightarrow & \left\{ \mu\left(\mathbb{1}-P\right)\right\} =\left[1,1\right]-\left\{ \mu\left(P\right)\right\} =\left\{ 1-\mu\left(P\right)\right\} \\
+ & \Rightarrow & \mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)\,.
+\end{eqnarray*}
+\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
+have
+\begin{eqnarray*}
+ &  & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\\
+ & \Rightarrow & \left\{ \mu\left(P_{0}+P_{1}\right)\right\} \subseteq\left\{ \mu\left(P_{0}\right)\right\} +\left\{ \mu\left(P_{1}\right)\right\} =\left\{ \mu\left(P_{0}\right)+\mu\left(P_{1}\right)\right\} \\
+ & \Rightarrow & \mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.
+\end{eqnarray*}
+\end{itemize}
+\end{proof}
+
+Together with example~\ref{ex:regular-pair}, we know QIVPMs with
+$\mathscr{I}_{\infty}$ is one-to-one correspondence to quantum real-valued
+probability measures.
 

### 2017-07-10 prop_letter.tex
After meeting...

@@
 
-\title{Interval-Valued Quantum Probabilities: Contextuality and the Born Rule}
+\title{Quantum Interval-Valued Probability: Contextuality and the Born Rule}
 
@@
 the world of finite resource.
+
 \end{description}
@@
 
-In this letter, we extend our previous work on the foundations of
+In this paper, we extend our previous work on the foundations of
 computability in quantum mechanics by exploring the application of
@@
 formulation of finite-resource quantum mechanics.
+In particular, we quantify the concept of imperfect quantum measurement and its impact on the interpretation of the Kochen-Specker and Gleason theorems and their implications for the foundations of quantum mechanics.
 
@@
 theorem\nb\cite{kochenspecker1967,peres1995quantum}, and discussion
-continues on whether contextuality is experimentally
-verifiable\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
-fundamental question is how to make mathematical theories of quantum
-mechanics that are intrinsically, rather than only implicitly,
-consistent with the resources available for the realistic accuracy of
-an actual measurement.
-
+has continued on whether contextuality is consistent with  experimental outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
+fundamental question is how to make mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.
+
+Here we develop a mathematical framework that includes the uncertainties of finite precision and imperfections in the quantum measurement process.
 Our first observation is that essential objectives of our program to
@@
 extending classical interval-valued probability
-measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We begin by
-axiomatizing a quantum interval-valued probability measure (QIVPM)
+measures\nb\cite{JamisonLodwick2004} to the quantum domain.
+We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework, which will provide a quantitative description of the impact of finite precision on the foundations of quantum mechanics.
+
+% exploiting the fact that a density matrix approach can be
+% considered as equivalent to a description of quantum states
+% using probability  measures\nb\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
+
+In particular, the effect of finite precision on contextuality, and the Kochen-Specker theorem, is shown to have a resolution in terms of the quantum interval valued probability measure framework that we introduce.
+To proceed, we use a formulation of the Mermin square that uses the
+expectation value of an observable with respect
+to a QIVPM can be defined to be consistent with the constraints on the
+expectation value of the same observable expected from continuous
+quantum mechanics.  We then examine Gleason's
+theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
+Kochen-Specker theorem in the context of QIVPM's, and conclude that
+they correspond to the limit of an infinite number of precise
+intervals, and the set of cryptodeterministic intervals (the set\nb$\{\imposs,\necess\}$),
+respectively.
+
+\begin{itemize}
+\item Develop a framework that includes the uncertainties of finite precision in the quantum measurement process.
+\item Provide a quantitative description of the impact of finite precision on the foundations of quantum mechanics.
+\item In particular, the effect of finite precision on contextuality is shown to have a resolution in terms of the quantum interval valued probability measure framework that we introduce.
+\item A key aspect of quantum measurement is its stochastic nature as reflected in Born's rule.
+Gleason's theorem establishes the existence of a unique state (in Hilbert spaces of dimension $\ge 3$), the probabilities of whose outcomes are computed from Born's rule assuming infinite precision.
+Then it is legitimate to question what happens when infinite precision cannot be achieved.
+\item 
+\end{itemize}
+
+Our first observation is that essential objectives of our program to
+achieve a computable theory of quantum mechanics and finite-resource
+measurement, attempted previously with computable number
+systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
+extending classical interval-valued probability
+measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We begin by axiomatizing a quantum interval-valued probability measure (QIVPM)
 framework exploiting the fact that a density matrix approach can be
@@
 foundational theorems of QM when this framework is applied?
+
+The paper is organized as follows.
+In Sec.\ \ref{sec:fuzzy} we begin by introducing the foundations of quantum probability space and fuzzy measurement.
+We then move on to introduce the concept of quantum interval valued probability in Sec.\ \ref{sec:Interval-Uncertainty}.
+This QIVPM will provide the mathematical framework to quantify the impact of finite precision measurements on quantum mechanics.
+For instance, in Sec.\ \ref{sec:Kochen-Specker},  we quantify the domain of validity of a  contextual measurement, thus addressing the conditions under which the Kochen-Specker theorem applies.
+This provides a way of resolving the Meyer-Mermin debate, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
+In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid, holds asymptotically.
+Finally, we present our conclusions in Sec.~\ref{sec:Conclusion}.
 
@@
 \section{Fuzzy Measurements}
-
+ \label{sec:fuzzy}
 A \emph{probability space} is a mathematical abstraction specifying
@@
 \section{Intervals of Uncertainty}
-
+  \label{sec:Interval-Uncertainty}
 We will start by reviewing IVPMs in the classical setting and then
@@
 \section{Kochen-Specker} 
+  \label{sec:Kochen-Specker}
 
@@
 \section{Gleason}
-
+  \label{sec:Gleason}
 In the classical setting, measurements done with limited resources and
@@
 \section{Conclusion}
-
-Foundational concepts in quantum mechanics, such as Gleason and
-Kochen-Specker theorems, rely in a very subtle way on the use of
+  \label{sec:Conclusion}
+
+Foundational concepts in quantum mechanics, such as the Kochen-Specker and
+Gleason theorems, rely in a very subtle way on the use of
 unbounded resources. By assuming infinitely precise measurements,
-these two insightful theorems underline two fundamental aspects of
-quantum mechanics. On the one hand, Gleason's result establishes a
+these two insightful theorems underlie two fundamental aspects of
+quantum mechanics. On the one hand, Kochen-Specker's result reveals a distinctive aspect of physical reality, the fact that it is contextual, and on the other hand, Gleason's theorem establishes a
 relationship between quantum states and probabilities uniquely defined
-by Born's rule, on the other, Kochen-Specker unveils a distinctive
-aspect of physical reality, the fact that it is contextual.  Our goal
+by Born's rule.  Our goal
 in this paper has been to analyze the physical consequences of a
 mathematical framework that allows for finite precision measurements
-by introducing the concept of quantum interval-valued probability. The
-latter incorporates uncertainty in the measurement results by defining
+by introducing the concept of quantum interval-valued probability. This
+framework incorporates uncertainty in the measurement results by defining
 fuzzy probability measures, and includes standard quantum measurement
@@
 In addition, we showed how these two theorems emerge as limiting cases
-of this very same framework, thus connecting two seemingly unrelated
-aspects of quantum physics. Most importantly, we concluded that
-arbitrary finite precision measurement conditions nullify the main
+of this same framework, thus connecting two seemingly unrelated
+aspects of quantum physics. We noted that
+{\it arbitrary\/} finite precision measurement conditions can nullify the main
 tenets of both theorems.
+However, by carefully specifying experimental uncertainties, we were able to establish rigorous bounds on the validity of these two theorems.
+Therefore, we have established a context in which infinite precision quantum mechanical theories can be reconciled with finite precision quantum mechanical measurements, and have provided a possible resolution of the Meyer-Mermin debate on the impact of finite precision on the Kochen-Specker theorem \cite{PhysRevLett.83.3751,Mermin1999}.
 

### 2017-07-10 prop_letter.tex
prop_letter.tex Abstract Updated...

@@
 
-\begin{abstract}~
-\begin{description}
-\item [{Background}] In a world of bounded resource, any quantum measurement
-can be only performed in finite precision.
-\item [{Method}] We model the idea of the finite precision measurement
-as finite number of intervals, and replace quantum real-valued probability
-measures by interval-valued ones.
-\item [{Results}] Quantum interval-valued probability measures provide
-a unified framework to interpret Gleason's theorem and the Kochen-Specker
-theorem as the limiting cases. For the cases between them, we found
-some legitimate quantum interval-valued probability measures which
-cannot be explained by the Born rule. While restricting on only commuting
-projectors, the interval-valued probability measures become classical,
-and these non-Born interval-valued probability measures disappear.
-\item [{Conclusions}] Our research provides a new insight of finite precision
-measurement and non-commutativity when formulating quantum theory.
-Also, the Born rule may not be as nature as we used to believe in
-the world of finite resource.
-
-\end{description}
+\begin{abstract}
+It is well-known that any quantum measurement can be only performed
+in finite precision. However, quantum theory is usually based on infinitely
+precise real and complex numbers, and physicists handle this imperfection
+by statistical methods without understanding how finite precision
+measurement affect the mathematical foundation of quantum theory.
+Our purpose here is to examine a quantum model cooperating the idea
+of finite precision at very beginning. Within our quantum interval-valued
+probability measure (QIVPM) framework, we found a QIVPM become classical
+when the projectors all commute, and the expectation value of an observable
+can still be computed as expected. Two fundamental quantum theorems,
+the Kochen-Specker and Gleason theorem, can be reformulated by QIVPM
+given a particular choice of intervals, and we can discuss their validity
+within a certain bound. Our research provides a new insight to quantify
+the idea of finite precision measurement, and provides a possible
+resolution of the Meyer-Mermin debate on the impact of finite precision
+on the Kochen-Specker theorem.
 \end{abstract}
@@
 
-In particular, the effect of finite precision on contextuality, and the Kochen-Specker theorem, is shown to have a resolution in terms of the quantum interval valued probability measure framework that we introduce.
+In particular, the effect of finite precision on contextuality, and the
+Kochen-Specker theorem, is shown to have a resolution in terms of the quantum interval-valued probability measure framework that we introduce.
 To proceed, we use a formulation of the Mermin square that uses the
@@
 are several proposals for ``imprecise
-probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
 Although these proposals differ in some details, they all share the
@@
 before. The new condition, known as
-\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
+\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
 reduces to the previously

### 2017-07-10 prop_letter.tex
After meeting...

@@
 \begin{abstract}
-It is well-known that any quantum measurement can be only performed
-in finite precision. However, quantum theory is usually based on infinitely
-precise real and complex numbers, and physicists handle this imperfection
-by statistical methods without understanding how finite precision
-measurement affect the mathematical foundation of quantum theory.
-Our purpose here is to examine a quantum model cooperating the idea
-of finite precision at very beginning. Within our quantum interval-valued
-probability measure (QIVPM) framework, we found a QIVPM become classical
-when the projectors all commute, and the expectation value of an observable
-can still be computed as expected. Two fundamental quantum theorems,
-the Kochen-Specker and Gleason theorem, can be reformulated by QIVPM
-given a particular choice of intervals, and we can discuss their validity
-within a certain bound. Our research provides a new insight to quantify
-the idea of finite precision measurement, and provides a possible
-resolution of the Meyer-Mermin debate on the impact of finite precision
+
+We present a mathematical framework based on quantum interval-valued
+probability measures to study the effect of experimental imperfections
+and finite precision measurements on defining features of quantum
+mechanics such as contextuality and the Born rule. While foundational
+results such as the Kochen-Specker and Gleason theorems fail to hold
+in general in a world with limited resources, when we allow infinite
+precision, their validity is recovered.  However, we are able to use
+the interval-valued framework to establish bounds on the validity of
+those theorems in realistic experimental environments. In this way,
+not only can we quantify the idea of finite-precision measurement
+within our theory, but we can also suggest a possible resolution of
+the Meyer-Mermin debate on the impact of finite-precision measurement
 on the Kochen-Specker theorem.
+
 \end{abstract}
@@
 measures\nb\cite{JamisonLodwick2004} to the quantum domain.
-We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework, which will provide a quantitative description of the impact of finite precision on the foundations of quantum mechanics.
+We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework, which will provide a quantitative description of the impact of finite precision quantum measurements.
 
@@
 
-In particular, the effect of finite precision on contextuality, and the
-Kochen-Specker theorem, is shown to have a resolution in terms of the quantum interval-valued probability measure framework that we introduce.
-To proceed, we use a formulation of the Mermin square that uses the
+In particular, the effect of finite precision on contextuality and the
+Kochen-Specker theorem is shown to have a resolution in terms of our quantum interval-valued probability measure framework.  To proceed, we use a formulation of the Mermin square that uses the
 expectation value of an observable with respect
@@
 
-\begin{itemize}
-\item Develop a framework that includes the uncertainties of finite precision in the quantum measurement process.
-\item Provide a quantitative description of the impact of finite precision on the foundations of quantum mechanics.
-\item In particular, the effect of finite precision on contextuality is shown to have a resolution in terms of the quantum interval valued probability measure framework that we introduce.
-\item A key aspect of quantum measurement is its stochastic nature as reflected in Born's rule.
+${\bullet}$ A key aspect of quantum measurement is its stochastic nature as reflected in Born's rule.
 Gleason's theorem establishes the existence of a unique state (in Hilbert spaces of dimension $\ge 3$), the probabilities of whose outcomes are computed from Born's rule assuming infinite precision.
 Then it is legitimate to question what happens when infinite precision cannot be achieved.
-\item 
-\end{itemize}
-
-Our first observation is that essential objectives of our program to
-achieve a computable theory of quantum mechanics and finite-resource
-measurement, attempted previously with computable number
-systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
-extending classical interval-valued probability
-measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We begin by axiomatizing a quantum interval-valued probability measure (QIVPM)
-framework exploiting the fact that a density matrix approach can be
+
+${\bullet}$ Exploiting the fact that a density matrix approach can be
 considered as equivalent to a description of quantum states using
 probability measures\nb\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
-One result is that the expectation value of an observable with respect
-to a QIVPM can be defined to be consistent with the constraints on the
-expectation value of the same observable expected from continuous
-quantum mechanics.  We then examine Gleason's
-theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
-Kochen-Specker theorem in the context of QIVPM's, and conclude that
-they correspond to the limit of an infinite number of precise
-intervals, and the set of cryptodeterministic intervals (the set\nb$\{\imposs,\necess\}$),
-respectively.
 

### 2017-07-11 prop_letter.tex
prop_letter.tex Introduction Updating...

@@
 on whether finite-precision measurements invalidate the Kochen-Specker
-theorem\nb\cite{kochenspecker1967,peres1995quantum}, and discussion
+theorem\nb\cite{kochenspecker1967,peres1995quantum}. In particular,
+the Kochen-Specker theorem is based on the two sphere\nb$S^{2}$
+cannot be colored by red and green such that any orthogonal basis
+has exactly one red vector. On the one hand, Meyer argued that the
+rational dense subset of $S^{2}$, $S^{2}\cap\mathbb{Q}^{3}$, is
+colorable, and we cannot distinguish $S^{2}$ and $S^{2}\cap\mathbb{Q}^{3}$
+since finite precision measurement\nb\citep{PhysRevLett.83.3751,Szangolies2015}.
+On the another hand, Mermin argued any physical outcome must be a
+continuous function on the experimental configuration\nb\citep{Mermin1999,Szangolies2015}.
+Discussion
 has continued on whether contextuality is consistent with  experimental outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The

### 2017-07-11 prop_letter.tex
Updates from ShareLaTeX

--- 2017-07-10 prop_letter.tex
@@
 probability measures to study the effect of experimental imperfections
-and finite precision measurements on defining features of quantum
+and finite precision measurements on defining aspects of quantum
 mechanics such as contextuality and the Born rule. While foundational

### 2017-07-11 prop_letter.tex
prop_letter.tex Updating...

@@
 On the another hand, Mermin argued any physical outcome must be a
-continuous function on the experimental configuration\nb\citep{Mermin1999,Szangolies2015}.
+continuous function on the experimental configuration so that small
+experimental imperfection should not ``nullify'' an idealized theorem\nb\citep{Mermin1999,Szangolies2015}.
 Discussion
@@
 
-% exploiting the fact that a density matrix approach can be
-% considered as equivalent to a description of quantum states
-% using probability  measures\nb\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
-
 In particular, the effect of finite precision on contextuality and the
@@
 expectation value of an observable with respect
-to a QIVPM can be defined to be consistent with the constraints on the
-expectation value of the same observable expected from continuous
-quantum mechanics.  We then examine Gleason's
-theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
-Kochen-Specker theorem in the context of QIVPM's, and conclude that
-they correspond to the limit of an infinite number of precise
-intervals, and the set of cryptodeterministic intervals (the set\nb$\{\imposs,\necess\}$),
-respectively.
-
-${\bullet}$ A key aspect of quantum measurement is its stochastic nature as reflected in Born's rule.
-Gleason's theorem establishes the existence of a unique state (in Hilbert spaces of dimension $\ge 3$), the probabilities of whose outcomes are computed from Born's rule assuming infinite precision.
-Then it is legitimate to question what happens when infinite precision cannot be achieved.
-
-${\bullet}$ Exploiting the fact that a density matrix approach can be
-considered as equivalent to a description of quantum states using
-probability measures\nb\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307
-
-We note, however, that in this approach there exist QIVPM's that do
-not correspond to a density matrix computable by the Born rule, so
-that Gleason's theorem cannot hold in general.  It thus remains
-possible that a refinement of the basic definition of a quantum state
-or the computation of probability from a state may be required when we
-rigorously consider the implications of finite precision measurement.
-
-A question we want to entertain in this paper is \ldots
-Can one incorporate in a rigorous mathematical framework the idea of
-finite precision measurement? Yes QIVPM. Now what is the fate of the 
-foundational theorems of QM when this framework is applied?
+to a QIVPM, where the interval-valued
+expectation value is consistent with the expectation value of the
+same observable on continuous quantum mechanics. Furthermore, the
+Kochen-Specker theorem is robust in our framework in a sense that
+it would remain valid when the experimental error is less than a particular
+bound.
+
+A key aspect of quantum measurement is its stochastic nature as reflected
+in Born's rule\nb\citep{Born1983,peres1995quantum,544199}. Gleason's
+theorem establishes the existence of a unique state (in Hilbert spaces
+of dimension $\ge3$), the probabilities of whose outcomes are computed
+from Born's rule assuming infinite precision\nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+Then it is legitimate to question what happens when infinite precision
+cannot be achieved. While a QIVPM\nb$\bar{\mu}$ might not be consistent
+with a unique state\nb$\rho'$ on all projectors on a Hilbert space,
+if $\bar{\mu}$ is induced by a mixed state\nb$\rho$, $\rho'$ would
+close to $\rho$ when we shirk the length of intervals under some
+good conditions, and recover original Gleason's theorem in the limiting
+case. Since Gleason's theorem cannot apply on QIVPMs in general, it
+thus remains possible that a refinement of the basic definition of
+a quantum state or the computation of probability from a state may
+be required when we rigorously consider the implications of finite
+precision measurement.
 
@@
 It is now not difficult to verify that for any totally mixed
-state\nb$\rho$ on a $d$-dimensional Hilbert space,
+state\nb$\rho$ on a three-dimensional Hilbert space,
 $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is a
@@
 \begin{itemize}
-\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
+\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(12n\right)$,
+$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
 \item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,

### 2017-07-11 prop_letter.tex
After meeting...

@@
 
+\begin{comment}
 \keywords{Finite precision measurement, the Born rule, Gleason's
@@
 discrete quantum theory}
+\end{comment}
 
@@
 In this paper, we extend our previous work on the foundations of
-computability in quantum mechanics by exploring the application of
+computability in quantum physics by exploring the application of
 interval-valued probability measures (IVPM) to achieving a coherent
@@
 mechanics regarding the tension between finite precision measurement
-and contextuality\nb\cite{BarrettKent2004,Appleby_2005}.  For example,
+and contextuality\nb\cite{BarrettKent2004,Appleby_2005}, which refers to the fact that the results of measuring compatible sets of observables depend  on whether they are measured together or separately.
+For example,
 Meyer\nb\cite{PhysRevLett.83.3751} and Mermin\nb\cite{Mermin1999} disagree
-on whether finite-precision measurements invalidate the Kochen-Specker
-theorem\nb\cite{kochenspecker1967,peres1995quantum}. In particular,
-the Kochen-Specker theorem is based on the two sphere\nb$S^{2}$
-cannot be colored by red and green such that any orthogonal basis
-has exactly one red vector. On the one hand, Meyer argued that the
-rational dense subset of $S^{2}$, $S^{2}\cap\mathbb{Q}^{3}$, is
-colorable, and we cannot distinguish $S^{2}$ and $S^{2}\cap\mathbb{Q}^{3}$
-since finite precision measurement\nb\citep{PhysRevLett.83.3751,Szangolies2015}.
-On the another hand, Mermin argued any physical outcome must be a
-continuous function on the experimental configuration so that small
-experimental imperfection should not ``nullify'' an idealized theorem\nb\citep{Mermin1999,Szangolies2015}.
+on whether finite-precision measurements invalidate the spirit of the Kochen-Specker
+theorem\nb\cite{kochenspecker1967,peres1995quantum}, which is a mathematical statement about contextuality.   The Kochen-Specker theorem asserts that, in a Hilbert space of dimension
+$d \ge 3$, it is impossible to associate definite measured values, $\mu(P_i)= 0$
+or $1$, with every projection operator\nb$P_i$, in such a way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then $\sum_i \mu(P_i) = 1$. In contrast, Meyer showed that 
+one {\it can\/}  assign definite values $0$ or $1$ to the measurement outcome $\mu(P_i)$ when the Hilbert space is defined over the field of rational numbers, therefore nullifying the theorem\nb\citep{PhysRevLett.83.3751}.
+However, Mermin then argued that measurement outcomes must depend smoothly
+on slight changes in the experimental configuration. Mermin therefore claimed that 
+the impact of Meyer's negative result  is ``unsupportable''\nb\citep{Mermin1999}. 
 Discussion
-has continued on whether contextuality is consistent with  experimental outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
-fundamental question is how to make mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.
+has continued on whether contextuality is consistent with  experimental outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+A fundamental question is how to address this controversy by developing
+ mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.
 

### 2017-07-12 prop_letter.tex
prop_letter.tex Updating according to the meeting...

@@
 if $\bar{\mu}$ is induced by a mixed state\nb$\rho$, $\rho'$ would
-close to $\rho$ when we shirk the length of intervals under some
+close to $\rho$ when we shrink the length of intervals under some
 good conditions, and recover original Gleason's theorem in the limiting
-case. Since Gleason's theorem cannot apply on QIVPMs in general, it
-thus remains possible that a refinement of the basic definition of
-a quantum state or the computation of probability from a state may
-be required when we rigorously consider the implications of finite
-precision measurement.
+case.
 
@@
 $\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
-sums of \emph{orthogonal} projections $P_0$ and $P_1$ such
+sums of \emph{orthogonal} projections $P_0$ and $P_1$ with
 $P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
-$P_0$ and $P_1$ such $P_0P_1=P_1P_0$. In a well-defined quantum
+$P_0$ and $P_1$ with $P_0P_1=P_1P_0$. In a well-defined quantum
 probability
 space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
-each event $P_{i}$ is mapped using a probability measure
-$\mu : P \rightarrow [0,1]$ to a probability $\mu(P_{i})$ subject to
+each event $P_{i}$ is mapped to a probability using a probability measure
+$\mu : P \rightarrow [0,1]$ to a probability $\mu(P_{i})$. We impose
 the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
 $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
-of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, we have:
+of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, standard probability
+measures obey
 \begin{equation}
@@
 precisely 0.5. The spread in this range depends on the amount of
-resources (time, energy, money, etc) that are devoted to the
-experiment. In the classical setting, this ``fuzziness'' is formalized
-by moving to \emph{interval-valued probability measures}.
+resources (time, energy, money, etc.) that are devoted to the
+experiment. In the classical setting, this ``fuzziness'' can be formalized
+by moving to \emph{interval-valued probability measures}, which we explore in
+the next section, along with our proposed extension to the quantum domain.
 
@@
 fact that the probability $\mu(E)$ of an event~$E$ is generalized from
-a single real number to an interval of certainty $[\ell,r]$
+a single real number to an interval\nb$[\ell,r]$
 where\nb$\ell$ intuitively corresponds to the strength of evidence for
-the event and~$r$ corresponds to the strength of evidence against the
+the event and~$1-r$ corresponds to the strength of evidence against the
 event. The collection of intervals used in the definition of a
-probability measure must satisfy certain properties which we explain
+probability measure must satisfy certain properties that we explain
 next.
 
-First for each interval $[\ell,r]$ we have the natural constraint
+First, for each interval $[\ell,r]$ we have the natural constraint
 $0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
@@
 $[1-r,1-\ell]$ so that if one interval refers to the probability of an
-event, the other refers to the probability of the complement
-event. For example, if we discover as a result of an experiment that
+event, the other refers to the probability of the event's complement.
+For example, if we discover as a result of an experiment that
 $\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
-$\mu(\overline{E}) = [0.7,0.8]$ for the complement event
+$\mu(\overline{E}) = [0.7,0.8]$ for the complementary event
 $\overline{E}$. In addition to these simple conditions, there are some
@@
 
-Let $E_1$ and $E_2$ be to disjoint events with probabilities
+Let $E_1$ and $E_2$ be two disjoint events with probabilities
 $\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
-at calculating the probability of the combined event that either $E_1$
+at calculating the probability of the combined event that \emph{either} $E_1$
 or $E_2$ occurs might be $\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In
@@
 separately. In our example, even though the true probability of
-$\mu(E)$ can be in anywhere in the range $[0.2,0.3]$ and the true
+$\mu(E)$ can be anywhere in the range $[0.2,0.3]$ and the true
 probability of $\mu(\overline{E})$ can be in anywhere in the range
@@
 When combining non-disjoint events, there is a further subtlety whose
-resolution will give the most general and final condition. For
-general, non-necessarily disjoint events $E_1$ and $E_2$, we have:
+resolution will give us one final general condition. For
+general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
 \begin{equation}
@@
 generalization of both classical IVPMs and conventional quantum
-probability measures. More precisely the quantum IVPM will reduce to
+probability measures. We will assume that the quantum IVPM will reduce to
 the classical IVPM when the space of quantum events is restricted to
@@
 \begin{definition}[QIVPM]
-  Given a collection of intervals $\mathscr{I}$ including
-  $\imposs=[0,0]$ and $\necess=[1,1]$ and with addition and scalar
+  Assume a collection of intervals $\mathscr{I}$ including
+  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
   multiplication defined as follows:
@@
   [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
-  [xr,x\ell] & \textrm{for }x\le0\,,
+  [xr,x\ell] & \textrm{for }x\le0\,.
   \end{cases}
@@
   \end{subequations}
-  a QIVPM $\bar{\mu}$ is an assignment of an interval to each event
-  (projection operator) subject to the following constraints:
-  $\bar{\mu}(\mathbb{0})=\left[0,0\right]$,
-  $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
-  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
-  and for each pair of \emph{commuting} projections $P_0$ and $P_1$,
-  we have:
+  Then we take a QIVPM\nb$\bar{\mu}$ to be an assignment of an interval to each
+  event (projection operator\nb$P$) subject to the following constraints:
+  \begin{subequations}\label{eq:QIVPM-constraints}
+  \begin{eqnarray}
+   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
+   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
+   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
+  \end{eqnarray}
+  \end{subequations}
+  and satisfying for each pair of \emph{commuting} projections $P_0$ and $P_1$,
+  ($P_0P_1=P_1P_0$)
 \begin{equation}
-\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
+\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
 \label{eq:QuantumInterval-valuedProbability-Inclusion}
@@
 \end{definition}
-The first three constraints are the direct counterpart of the
-corresponding ones for conventional probability measures. With the
-understanding that the union of classical sets $E_1\cup E_2$ is replaced
-by $P_0+P_1-P_0P_1$ in the case of projection operators~\cite{Griffiths2003}, the last
-condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is
+The first three constraints\nb(\ref{eq:QIVPM-constraints}) are the direct
+counterpart of the corresponding ones for conventional interval probability
+measures.
+With the understanding that the union of classical sets $E_1\cup E_2$ is replaced
+by $P_0+P_1-P_0P_1$ in the case of quantum projection
+operators~\cite{Griffiths2003}, the last condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is
 a direct counterpart of Eq.~(\ref{eq:classicalconvex}).
@@
 observations done with finite resources, the probabilities become
-intervals, and we say a state\nb$\rho$ is consistent with $\bar{\mu}$ on
-a projector\nb$P$ if
+intervals, and we say a state\nb$\rho$ is consistent with the
+measure\nb$\bar{\mu}$ acting on a projector\nb$P$ if
 $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
@@
 Born rule\nb\cite{Born1983,peres1995quantum,544199}.
-Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
+$\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
 consistent with $\bar{\mu}$ on every projector in $S$.
@@
 Quantum IVPMs become classical IVPMs when the space of events includes
-only mutually commuting events, where $\events'\subseteq\events$
-is called a sub-event space if it satisfies the following conditions.
+only mutually commuting events. We define $\events'\subseteq\events$
+to be a sub-event space if it satisfies the following conditions.
 \begin{itemize}
@@
 
-For example, assuming the three intervals \imposs, \necess, and
-$\unknown=\left[0,1\right]$, then:
+For example, assuming the three intervals $\imposs=\left[0,0\right]$,
+$\necess=\left[1,1\right]$, and $\unknown=\left[0,1\right]$, then:
 \begin{equation}
@@
 $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
-is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on
+is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ to
 $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
@@
 the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
-represents that an experimenter knows nothing about a coin before
-she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
+represents the situation in which that an experimenter knows nothing about a
+coin before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
 state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
-coin with probability\nb$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
-is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
-classical coin should be consistent with the situation where an experimenter
+coin with probability\nb$p$ to get heads, and
+$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
+classical coin should be consistent with the situation for which an experimenter
 has no prior knowledge.
@@
 
-Our first result is that a QIVPM cannot be cryptodeterministic in the
-sense of Peres\nb\cite{PeresRon1988,peres1995quantum}. We will adapt
+Our first result is that a QIVPM is consistent with the inability to avoid
+uncertainty found in conventional infinite precise quantum
+mechanics\nb\cite{PeresRon1988,peres1995quantum}. We will adapt
 the proof of the Kochen-Specker theorem~\cite{kochenspecker1967,
   peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
-is, in general, impossible to just have the two intervals \imposs\ and
+is, in general, impossible to have just the two intervals \imposs\ and
 \necess: every QIVPM must be parameterized by a collection of
@@
 uncertainty: one due to the finite measurement resources and one due
-to complementarity which requires every quantum framework to be truly
+to complementarity, which requires every quantum framework to be truly
 probabilistic.
 
-We will proceed by assuming a cryptodeterministic QIVMP $\bar{\mu}$
+We will proceed by assuming a QIVMP $\bar{\mu}$
 and derive a contradiction using the following nine ``Mermin-Peres square''
@@
 \hline 
-\end{tabular}
+\end{tabular}\,,
 \par\end{center}

### 2017-07-12 prop_letter.tex
prop_letter.tex Updating according to the meeting...

@@
 
-We will proceed by assuming a QIVMP $\bar{\mu}$
+We will proceed by assuming a cryptodeterministic QIVMP $\bar{\mu}$
 and derive a contradiction using the following nine ``Mermin-Peres square''
@@
 
-\noindent The argument refers to the expectation value of these
-observables. In the case of QIVPM this is defined as follows.
-
-\begin{definition}Given a Hilbert space of $d\ge3$, for every
+\noindent where $\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are
+Pauli matrices acting on a pair of spin-$\frac{1}{2}$ state. We now define the
+expectation value of the QIVPM for our Mermin-Peres square.
+
+\begin{definition}Given a Hilbert space of dimension\nb$d\ge3$, for every
   QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, any
@@
 
-The expectation value is intuitively between two possible outcomes
-which lie between the minimum and maximum bounds of the given
+The expectation value is intuitively between two possible outcomes,
+which themselves lie between the minimum and maximum bounds of the given
 probability intervals. (This definition is consistent with the
@@
 \end{equation}
-for any sequence of commuting observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
+for any set of commuting observables\nb$\left\{ \mathbf{O}_{j}\right\}
+_{j=1}^{N}$.
 
@@
 $\left\{ -1\right\} $.  In each row and column, the operators commute,
-and each operator is the product of the two others, except in the
-third column
+and each operator is the product of two others, except in the
+third column, where
 $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
@@
 The question now is what happens if we relax the perfect measurement
-assumption that entails that the intervals are precisely $[0,0]$ and
-$[1,1]$. What if the measurement imperfections occasionally cause an
+assumption that the intervals are precisely $[0,0]$ and
+$[1,1]$. We need to examine what happens if
+measurement imperfections occasionally cause an
 ideally impossible event to be detected or an ideally certain event to

### 2017-07-12 prop_letter.tex
prop_letter.tex After merge small changes to main text...

@@
 measurement imperfections occasionally cause an
-ideally impossible event to be detected or an ideally certain event to
-be not be detected. Mermin argues in this case that:
+ideally impossible event to be detected or an ideally certain event
+not to be detected. Mermin argues in this case that:
 \begin{quote}
@@
 We can formally test this hypothesis by considering the notion of
-$\delta$-deterministic QIVPM below.
-
-\begin{definition}\label{def:delta-deterministic}A QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
-  is called $\delta$-deterministic if either
+a $\delta$-deterministic QIVPM below.
+
+\begin{definition}\label{def:delta-deterministic}We define
+  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+  as $\delta$-deterministic if either
   $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$ or
@@
 $\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
-onto a $x$-dimensional subspace in a three-dimensional Hilbert space.
-
-We now prove that for small enough $\delta$, the Kochen-Specker is
+onto an $x$-dimensional subspace of a three-dimensional Hilbert space.
+
+We now prove that for small enough $\delta$, the Kochen-Specker result is
 still valid, i.e., if the measurement imperfections are small enough,
@@
 
-It remains to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
-QIVPM. The main part of that verification is to check:
+It remains to verify that $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
+QIVPM by checking the properties of
 \begin{subequations}
@@
 Hence, $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[0,\delta\right]$,
-which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. 
+which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
+theorem holds when $\delta<\frac{1}{3}$.
 \end{proof}
@@
 measures, Gleason's theorem asserts that every measure is determined
-by a unique mixed state. The theorem above is weaker however: it
+by a unique mixed state. The theorem above is weaker: it
 asserts that, for each classical sub-event subspace, a QIVPM must be
 consistent with \emph{some} state. But the states consistent with
-different subspaces may be incomparable as the following example
+different subspaces may be incomparable, as the following example
 shows.
@@
 \begin{example}\label{ex:three-dimensional-three-value}
-  Given a three dimensional Hilbert space with an orthonormal basis
-  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let
+  Given a three-dimensional Hilbert space with an orthonormal basis
+  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,  let
   $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
@@
 Thus, there is no state that is consistent with the QIVPM on all
-projectors\nb$\events$ invalidating Gleason's theorem.
+projectors\nb$\events$, so Gleason's theorem does not hold for at least this
+example.
 \end{example}
@@
 which are overlapping intervals with length\nb$1/n$ except the intervals
-near the ends.
+at each end.
 
@@
 follows. We first define a map $\widehat{\iota}_{n}$ from the interval
-$[0,1]$ to the collection of intervals above as follows:
+$[0,1]$ to the collection of intervals as:
 \begin{itemize}
@@
 where $k$ is defined by one of the following:
-\begin{itemize}
-\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
-\item $2\nmid k$ and $k-0.5<2nx<k+0.5$.
-\end{itemize}
+\begin{enumerate}
+\item $k$ even and $k-0.5\le2nx\le k+0.5$;
+\item $k$ odd and $k-0.5<2nx<k+0.5$.
+\end{enumerate}
 \end{itemize}
@@
 \end{itemize}
-In other words, the states consistent with this QIVMP
-$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will be closer and
+In other words, for the states consistent with this QIVPM,
+$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will become closer and
 closer to $\rho$ as $n$ goes to infinity. In the limiting case when
@@
 $\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
-recast as an real-valued one and will have a unique state consistent
+recast as a real-valued one and will have a unique state consistent
 with it on every projector when $d\ge3$.

### 2017-07-13 prop_letter.tex
prop_letter.tex \section{Gleason} Update the proof...

@@
 \end{subequations}
-It is straightforward to verify that $\bar{\mu}_{3}$ is a QIVPM. Now
-let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because
-$\bar{\mu}_{3}(\proj{0})=\bar{\mu}_{3}(\proj{\ps})=\imposs$, we have
-$\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-for any mixed
-state\nb$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.  Hence,
-$\rho$ cannot be any state other than $\ket{2}$, the only pure state
-orthogonal to both $\ket{0}$ and $\ket{\ps}$, and it is easy to verify
-$\proj{2}$ is actually in
-$\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$. Similarly, let
-$S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We have
-$\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\left\{ \proj{1}\right\} $.
-Therefore,
+It is straightforward to verify that $\bar{\mu}_{3}$ is a QIVPM. Then we will
+prove $\coreBorn\left(\bar{\mu}_{3},\events\right)$ is an empty set by
+contradiction. Suppose there is a mixed
+state\nb$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu}_{3},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}_{3}(P)$
+for any\nb$P$, the mixed state\nb$\rho$ must satisfy
 \begin{equation}
-\coreBorn\left(\bar{\mu}_{3},\events\right)\subseteq\coreBorn\left(\bar{\mu}_{3},S_{1}\right)\cap\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\emptyset
+\melem{0}{\rho}{0}=\melem{\ps}{\rho}{\ps}=\melem{\ps'}{\rho}{\ps'}=0
 \end{equation}
-Thus, there is no state that is consistent with the QIVPM on all
-projectors\nb$\events$, so Gleason's theorem does not hold for at least this
+which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
+for all $j$. However, the last equation never holds. 
+Thus, there is no state consistent with the QIVPM on all 
+projectors\nb$P\in\events$, so Gleason's theorem does not hold for at least this
 example.
@@
 these two insightful theorems underlie two fundamental aspects of
-quantum mechanics. On the one hand, Kochen-Specker's result reveals a distinctive aspect of physical reality, the fact that it is contextual, and on the other hand, Gleason's theorem establishes a
-relationship between quantum states and probabilities uniquely defined
+quantum mechanics. On the one hand, Kochen-Specker's result reveals a
+distinctive aspect of physical reality, the fact that it is contextual, and, on the other hand, Gleason's theorem establishes a relationship between quantum states and probabilities uniquely defined
 by Born's rule.  Our goal

### 2017-07-13 prop_letter.tex
prop_letter.tex C(\bar{μ}, S) reorganizing...

@@
 the necessary conditions for reasoning coherently about collections of
-uncertain events\nb\cite{Kolmogorov1950}. In the quantum case, the
+uncertain events\nb\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the quantum case, the
 events of interest are specified by \emph{projection operators}
@@
 space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
-each event $P_{i}$ is mapped to a probability using a probability measure
-$\mu : P \rightarrow [0,1]$ to a probability $\mu(P_{i})$. We impose
+each event $P_{i}$ is mapped to a probability\nb$\mu(P_{i})$ using
+a probability measure\nb$\mu:\events\rightarrow[0,1]$, where $\events$
+is the set of all projections on a given Hilbert space. We impose
 the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
@@
 measure\nb$\bar{\mu}$ acting on a projector\nb$P$ if
-$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
-denoted by
-$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
+$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
 where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
 is the probability that the event\nb$P$ happens determined by the
-Born rule\nb\cite{Born1983,peres1995quantum,544199}.
-$\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
-consistent with $\bar{\mu}$ on every projector in $S$.
+Born rule\nb\citep{Born1983,peres1995quantum,544199}. Given a set
+of projectors\nb$S$, 
+\begin{equation}
+\coreBorn\left(\bar{\mu},S\right)=\set{\textrm{mixed state }\rho}{\forall P\in S\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}
+\end{equation}
+is the set of all mixed states consistent with $\bar{\mu}$ on every
+projector in $S$. For example, assuming the three intervals $\imposs=\left[0,0\right]$,
+$\necess=\left[1,1\right]$, and $\unknown=\left[0,1\right]$, then:
+\begin{equation}
+\bar{\mu}_{1}\left(P\right)=\begin{cases}
+\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
+\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
+\unknown\,, & \text{otherwise,}
+\end{cases}\label{eq:no-information-IVPM}
+\end{equation}
+is a QIVPM. This measure represents the beliefs of an experimenter
+with no prior knowledge about the particular quantum system in question;
+any quantum state would be consistent with $\bar{\mu}_{1}$ on any
+projectors, and $\coreBorn\left(\bar{\mu}_{1},\events\right)$ is
+just the set of all mixed states.
 
@@
 
-For example, assuming the three intervals $\imposs=\left[0,0\right]$,
-$\necess=\left[1,1\right]$, and $\unknown=\left[0,1\right]$, then:
-\begin{equation}
-\bar{\mu}_{1}\left(P\right)=\begin{cases}
-\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
-\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
-\unknown\,, & \text{otherwise,}
-\end{cases}\label{eq:no-information-IVPM}
-\end{equation}
-is a QIVPM. This measure represents the beliefs of an experimenter
-with no prior knowledge about the particular quantum system in
-question; any quantum state would be consistent with $\bar{\mu}_{1}$
-on any projectors. We have that
-$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
-is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ to
+For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
+is a commuting sub-event space. Consider $\bar{\mu}_{1}$ defined
+in the previous paragraph. Restricting $\bar{\mu}_{1}$ to
 $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical

### 2017-07-13 prop_letter.tex
Some updates from Gerardo...
Updating by Gerardo...

@@
 \section{Introduction}
-
-In this paper, we extend our previous work on the foundations of
-computability in quantum physics by exploring the application of
-interval-valued probability measures (IVPM) to achieving a coherent
-formulation of finite-resource quantum mechanics.
-In particular, we quantify the concept of imperfect quantum measurement and its impact on the interpretation of the Kochen-Specker and Gleason theorems and their implications for the foundations of quantum mechanics.
 
@@
 
-Here we develop a mathematical framework that includes the uncertainties of finite precision and imperfections in the quantum measurement process.
+In this paper, we extend our previous work on the foundations of
+computability in quantum physics by exploring the application of
+interval-valued probability measures (IVPM) to achieving a coherent
+formulation of finite-resource quantum mechanics.
+To this end, we develop a mathematical framework that includes the uncertainties of finite precision and imperfections in the quantum measurement process.
+In particular, we quantify the concept of imperfect quantum measurement and its impact on the interpretation of the Kochen-Specker and Gleason theorems and their implications for the foundations of quantum mechanics.
 Our first observation is that essential objectives of our program to
@@
 extending classical interval-valued probability
-measures\nb\cite{JamisonLodwick2004} to the quantum domain.
-We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework, which will provide a quantitative description of the impact of finite precision quantum measurements.
-
-In particular, the effect of finite precision on contextuality and the
-Kochen-Specker theorem is shown to have a resolution in terms of our quantum interval-valued probability measure framework.  To proceed, we use a formulation of the Mermin square that uses the
-expectation value of an observable with respect
+measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We thus begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework.
+
+The effect of finite precision and imperfections on contextuality and the
+Kochen-Specker theorem is shown to have a resolution in terms of our QIVPM framework.  
+To proceed, we use a formulation of the ``Mermin-Peres square'' \nb\cite{peres1995quantum,Mermin1990Simple} that uses the
+expectation value of a physical observable with respect
 to a QIVPM, where the interval-valued
 expectation value is consistent with the expectation value of the
-same observable on continuous quantum mechanics. Furthermore, the
-Kochen-Specker theorem is robust in our framework in a sense that
-it would remain valid when the experimental error is less than a particular
-bound.
-
-A key aspect of quantum measurement is its stochastic nature as reflected
-in Born's rule\nb\citep{Born1983,peres1995quantum,544199}. Gleason's
-theorem establishes the existence of a unique state (in Hilbert spaces
-of dimension $\ge3$), the probabilities of whose outcomes are computed
-from Born's rule assuming infinite precision\nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-Then it is legitimate to question what happens when infinite precision
-cannot be achieved. While a QIVPM\nb$\bar{\mu}$ might not be consistent
-with a unique state\nb$\rho'$ on all projectors on a Hilbert space,
-if $\bar{\mu}$ is induced by a mixed state\nb$\rho$, $\rho'$ would
+same observable in conventional quantum mechanics with infinite resources. We show that, 
+as long as errors and uncertainties remain smaller that a particular value, the
+Kochen-Specker theorem remains valid. In other words, we established a rigorous bound for 
+its validity and, therefore, the limits for physical reality to remain contextual.
+
+A key aspect of a quantum measurement is its statistical nature, as reflected
+in the application of the Born rule to determine the probability of a given measurement 
+outcome \nb\citep{Born1983,peres1995quantum,544199}. The Gleason
+theorem establishes that there is no alternative to the Born rule by 
+demonstrating, using reasonable continuity arguments in Hilbert spaces
+of dimension $d\ge3$, the existence of a unique state 
+$\rho$ consistent with the statistical predictions computed from 
+that rule \nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+It is then legitimate to question what happens when infinite precision
+cannot be achieved. We will show that, 
+while a QIVPM  might not be consistent
+with a unique state\nb$\rho$ on all projectors defined on a Hilbert space of dimension $d\ge3$,
+if the QIVPM is induced by some mixed state\nb$\rho'$ ,
+
+$\rho'$ would
 close to $\rho$ when we shrink the length of intervals under some
-good conditions, and recover original Gleason's theorem in the limiting
+good conditions, and recover the original Gleason theorem in the limiting
 case.
@@
 This provides a way of resolving the Meyer-Mermin debate, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
-In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid, holds asymptotically.
+In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.
 Finally, we present our conclusions in Sec.~\ref{sec:Conclusion}.

### 2017-07-14 prop_letter.tex
Updating by Gerardo...

@@
 A key aspect of a quantum measurement is its statistical nature, as reflected
-in the application of the Born rule to determine the probability of a given measurement 
+by application of the Born rule to determine the probability of a given measurement 
 outcome \nb\citep{Born1983,peres1995quantum,544199}. The Gleason
@@
 It is then legitimate to question what happens when infinite precision
-cannot be achieved. We will show that, 
+cannot be achieved. We will show that, if the effect of finite precision is incorporated, 
 while a QIVPM  might not be consistent
 with a unique state\nb$\rho$ on all projectors defined on a Hilbert space of dimension $d\ge3$, 
-if the QIVPM is induced by some mixed state\nb$\rho'$ ,
-
-$\rho'$ would
-close to $\rho$ when we shrink the length of intervals under some
-good conditions, and recover the original Gleason theorem in the limiting
-case.
+there is a mathematically precise sense in which one recovers the original Gleason theorem asymptotically. 
+Specifically, if for bounded resources the QIVPM is induced by some mixed states \nb$\rho'$, 
+those states will converge to a unique state $\rho$ when the size of the intervals characterizing 
+the uncertainties tends to zero.
 

### 2017-07-14 prop_letter.tex
prop_letter.tex Fix typos...

@@
 same observable in conventional quantum mechanics with infinite resources. We show that, 
-as long as errors and uncertainties remain smaller that a particular value, the
+as long as errors and uncertainties remain smaller than a particular value, the
 Kochen-Specker theorem remains valid. In other words, we established a rigorous bound for 
@@
 \end{definition}
-The first three constraints\nb(\ref{eq:QIVPM-constraints}) are the direct
+The first three constraints, Eq.\nb(\ref{eq:QIVPM-constraints}), are the direct
 counterpart of the corresponding ones for conventional interval probability

### 2017-07-14 prop_letter.tex
prop_letter.tex Small things here and there...

@@
 \bar{\mu}_{1}\left(P\right)=\begin{cases}
+\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
 \necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
-\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
 \unknown\,, & \text{otherwise,}
@@
 mechanics\nb\cite{PeresRon1988,peres1995quantum}. We will adapt
-the proof of the Kochen-Specker theorem~\cite{kochenspecker1967,
+the proof of the Kochen-Specker theorem\nb\cite{kochenspecker1967,
   peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
@@
 \begin{eqnarray}
- &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
- & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\,,
+ &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
+ & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\,,
 \end{aligned}
 \\
- &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
- & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\,,
+ &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
+ & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\,,
 \end{aligned}
 \\
- &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
+ &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
 \end{eqnarray}
 \end{subequations}
-It is straightforward to verify that $\bar{\mu}_{3}$ is a QIVPM. Then we will
-prove $\coreBorn\left(\bar{\mu}_{3},\events\right)$ is an empty set by
+It is straightforward to verify that $\bar{\mu}$ is a QIVPM. Then we will
+prove $\coreBorn\left(\bar{\mu},\events\right)$ is an empty set by
 contradiction. Suppose there is a mixed
-state\nb$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu}_{3},\events\right)$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}_{3}(P)$
+state\nb$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
 for any\nb$P$, the mixed state\nb$\rho$ must satisfy

### 2017-07-15 prop_iop.tex
prop_iop.tex \subsection{Between Expectation Values for Classical and Quantum IVPMs} Updated...

@@
 there is a classical real-valued probability measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$
-such that $\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. Then, we have
-$\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}
-
-\begin{proof}
+such that $\mu_{\rho}^{\mathrm{B}}|_{\events'}=\mu'\circ\tau$. Then,
+we have $\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}
+
+\begin{proof}Since $\mu_{\rho}^{\mathrm{B}}:\events\rightarrow\left[0,1\right]$
+is a QRVPM, $\mu_{\rho}^{\mathrm{B}}|_{\events'}$ is a QRVPM on the
+commuting sub-event space\nb$\events'$. By case\nb\ref{enu:sub-event-space-real-quantum2classical}
+in theorem~\ref{thm:sub-event-space}, there is a CRVPM such that
+$\mu_{\rho}^{\mathrm{B}}|_{\events'}=\mu'\circ\tau$. 
 \begin{eqnarray*}

### 2017-07-15 prop_letter.tex
prop_letter.tex 55e2cf6 Revert...

@@
   QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
-  following QIVPM
-  \nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
-    \imposs,\necess\right\} $ is cryptodeterministic:
+  following function\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
+    \imposs,\necess\right\} $ is a cryptodeterministic QIVPM:
 \begin{equation}
@@
 \end{subequations}
-It is straightforward to verify that $\bar{\mu}$ is a QIVPM. Then we will
-prove $\coreBorn\left(\bar{\mu},\events\right)$ is an empty set by
-contradiction. Suppose there is a mixed
-state\nb$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
-for any\nb$P$, the mixed state\nb$\rho$ must satisfy
+It is straightforward to verify that $\bar{\mu}$
+is a QIVPM. Now let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $.
+Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
+$\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
+for any mixed state\nb$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
+Hence, $\rho$ cannot be any state other than $\ket{2}$, the only
+pure state orthogonal to both $\ket{0}$ and $\ket{\ps}$, and it
+is easy to verify $\proj{2}$ is actually in $\coreBorn\left(\bar{\mu},S_{1}\right)$.
+Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We
+have $\coreBorn\left(\bar{\mu},S_{2}\right)=\left\{ \proj{1}\right\} $.
+Therefore, 
 \begin{equation}
-\melem{0}{\rho}{0}=\melem{\ps}{\rho}{\ps}=\melem{\ps'}{\rho}{\ps'}=0
+\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},S_{1}\right)\cap\coreBorn\left(\bar{\mu},S_{2}\right)=\emptyset
 \end{equation}
-which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all $j$. However, the last equation never holds. 
-Thus, there is no state consistent with the QIVPM on all 
-projectors\nb$P\in\events$, so Gleason's theorem does not hold for at least this
-example.
+Thus, there is no state that is consistent with the QIVPM on all projectors\nb$\events$,
+so Gleason's theorem does not hold for at least this example.
 \end{example}
@@
 $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will become closer and
-closer to $\rho$ as $n$ goes to infinity. In the limiting case when
+closer to $\rho'$ as $n$ goes to infinity. In the limiting case when
 the intervals are infinitely precise, i.e.,

### 2017-07-16 prop_iop.tex
prop_iop.tex \subsection{Classical and Quantum Probability Measures} Updating...

@@
 \begin{enumerate}
-\item \label{enu:sub-event-space-real-quantum2classical}If $\mu:\events'\rightarrow\left[0,1\right]$
+\item \label{enu:sub-event-space-real-quantum2classical}If $\mu':\events'\rightarrow\left[0,1\right]$
 is a quantum real-valued probability measure, then there is a classical
-real-valued probability measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$
-such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+real-valued probability measure\nb$\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+such that $\mu'\left(P\right)=\mu\left(\tau\left(P\right)\right)$
 for all $P\in\events'$.
-\item \label{enu:sub-event-space-interval-quantum2classical}If $\bar{\mu}:\events'\rightarrow\mathscr{I}$
+\item \label{enu:sub-event-space-interval-quantum2classical}If $\bar{\mu}':\events'\rightarrow\mathscr{I}$
 is a quantum interval-valued probability measure, then there is a
-classical interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
-such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
+classical interval-valued probability measure\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+such that $\bar{\mu}'\left(P\right)=\bar{\mu}\left(\tau\left(P\right)\right)$
 for all $P\in\events'$.
-\item \label{enu:sub-event-space-real-classical2quantum}If $\mu':2^{\Omega}\rightarrow\left[0,1\right]$
-is a classical real-valued probability measure, then there is a density
-matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+\item \label{enu:sub-event-space-real-classical2quantum}If $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+is a classical real-valued probability measure, then $\mu\circ\tau:\widehat{\events}\rightarrow\left[0,1\right]$
+is a QRVPM.
+\item \label{enu:sub-event-space-Gleason}Given a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$,
+there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
 for all $P\in\widehat{\events}$.
+\item $\rho$ in the previous case may not be unique.
 \end{enumerate}
@@
 
-\begin{proof}Since case \ref{enu:sub-event-space-real-quantum2classical}
-is a special case of case \ref{enu:sub-event-space-interval-quantum2classical},
-it is sufficient to prove case \ref{enu:sub-event-space-interval-quantum2classical}.
-Since $\events'$ is a set of mutually commuting projections, they
-can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
-Pick arbitrary projector~$P\in\events'$, its eigenvalues are $0$
-or $1$. Let $\tau\left(P\right)\subseteq\Omega$ be the set of eigenvectors
-whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$,
+\begin{proof}
+\begin{enumerate}
+\item Since this case is a special case of the next case, it is sufficient
+to prove the next case. 
+\item Since $\events'$ is a set of mutually commuting projections, they
+can be diagonalized by a common orthonormal basis\nb$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
+Pick arbitrary projector\nb$P\in\events'$, its eigenvalues are $0$
+or $1$. Select its eigenvectors whose eigenvalues are $1$ into a
+set\nb$\tau\left(P\right)\subseteq\Omega$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$,
 $\widehat{\events}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
 and $\tau$ is a bijection between $\widehat{\events}$ and $2^{\Omega}$.
-By definition~\ref{definition:quantum-classical}, $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
+By definition\nb\ref{definition:quantum-classical}, $\bar{\mu}'\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
 and $\bar{\mu}^{\Omega}$ is a classical interval-valued probability
-measure by lemma~\ref{lemma:classical-probability-measures}.
-
-For case \ref{enu:sub-event-space-real-classical2quantum}, if we
-pick $\rho=\sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\proj{j}$,
-then $\rho$ is a density matrix because~\cite{544199}
+measure by lemma\nb\ref{lemma:classical-probability-measures}.
+\item Trivial.
+\item If we pick $\rho=\sum_{j=1}^{d}\widehat{\mu}\left(\proj{j}\right)\proj{j}$,
+then $\rho$ is a density matrix because\nb\cite{544199}
 \begin{eqnarray}
-\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\Tr\left(\proj{j}\right)=1\,.
+\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\widehat{\mu}\left(\proj{j}\right)\Tr\left(\proj{j}\right)=1\,.
 \end{eqnarray}
 Also, 
+\begin{eqnarray}
+ &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)=\sum_{j=1}^{N}\widehat{\mu}\left(\proj{j}\right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)=\widehat{\mu}\left(\proj{i}\right)\textrm{ for all }i\,,\\
+ &  & \mu_{\rho}^{\mathrm{B}}\left(P_{0}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)\overset{\textrm{IH}}{=}\widehat{\mu}\left(P_{0}\right)+\widehat{\mu}\left(P_{1}\right)=\widehat{\mu}\left(P_{0}+P_{1}\right)
+\end{eqnarray}
+for orthogonal\nb$P_{0},P_{1}\in\events$. Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
+for all $P\in\widehat{\events}$ by induction.
+\item Consider a Hilbert space\nb$\Hilb$ of dimension 2, a mutually commuting
+sub-event space~$\widehat{\events}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $,
+and a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$
+such that $\widehat{\mu}\left(\proj{0}\right)=\widehat{\mu}\left(\proj{1}\right)=\frac{1}{2}$.
+Then, $\proj{\ps}$ and $\proj{\minus}$ are both density matrices,
+and 
 \begin{eqnarray*}
- &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)
- =\sum_{j=1}^{N}\mu'\left(\left\{ j\right\} \right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)
- =\mu'\left(\left\{ j\right\} \right)
- =\mu'\left(\tau\left(\proj{i}\right)\right)\textrm{ for all }i\,,\\
- &  & \mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)
- \overset{\textrm{IH}}{=}\mu'\left(\tau\left(P_{1}\right)\right)+\mu'\left(\tau\left(P_{2}\right)\right)
- =\mu'\left(\tau\left(P_{1}+P_{2}\right)\right)
+ &  & \mu_{\ket{\ps}}^{\mathrm{B}}\left(\proj{0}\right)=\mu_{\ket{\minus}}^{\mathrm{B}}\left(\proj{0}\right)=\frac{1}{2}=\widehat{\mu}\left(\proj{0}\right)\,,\\
+ &  & \mu_{\ket{\ps}}^{\mathrm{B}}\left(\proj{1}\right)=\mu_{\ket{\minus}}^{\mathrm{B}}\left(\proj{1}\right)=\frac{1}{2}=\widehat{\mu}\left(\proj{1}\right)\,.
 \end{eqnarray*}
-for commuting\nb$P_{0},P_{1}\in\events$ with $P_{0}P_{1}=\mathbb{0}$.
-Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
-for all $P\in\widehat{\events}$ by induction.\end{proof}
+\end{enumerate}
+\end{proof}
 
@@
 \end{eqnarray*}
-By case \ref{enu:sub-event-space-real-classical2quantum} in theorem~\ref{thm:sub-event-space},
+By theorem~\ref{thm:sub-event-space},
 there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
@@
 \end{eqnarray}
-By case \ref{enu:sub-event-space-real-classical2quantum} in theorem~\ref{thm:sub-event-space},
+By theorem~\ref{thm:sub-event-space},
 there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$

### 2017-07-17 prop_letter.tex
prop_iop.tex \subsection{Classical and Quantum Probability Measures} Updating...
small

@@
 a probability measure\nb$\mu:\events\rightarrow[0,1]$, where $\events$
-is the set of all projections on a given Hilbert space. We impose
+is the set of all projections on a given Hilbert space, subject to
 the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
 $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
-of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, standard probability
-measures obey
+of \emph{orthogonal} projections $P_{0}$ and $P_{1}$:
 \begin{equation}
@@
 generalization of both classical IVPMs and conventional quantum
-probability measures. We will assume that the quantum IVPM will reduce to
+probability measures. We will show that the quantum IVPM will reduce to
 the classical IVPM when the space of quantum events is restricted to
@@
 $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is a
-QIVPM. Furthemore, we have:
+QIVPM. Furthermore, we have:
 \begin{itemize}

### 2017-07-19 prop_letter.tex
prop_letter.pptx First draft...

@@
 these two properties, the observables in the Mermin-Peres square must
-have the the expectation value\nb$\left\{ 1\right\} $ or
+have the expectation value\nb$\left\{ 1\right\} $ or
 $\left\{ -1\right\} $.  In each row and column, the operators commute,

### 2017-07-21 prop_letter.tex
copy prop_letter.pptx to prop_short.pptm ...

@@
   observable\nb$\mathbf{O}$ with spectral decomposition
-  $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, and any minimal
+  $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, and the minimal
   sub-event space $\events'$ containing

### 2017-08-04 prop_letter.tex
prop.bib @InProceedings{Cabello2017} Added...

@@
 Kochen-Specker theorem is shown to have a resolution in terms of our QIVPM framework.  
-To proceed, we use a formulation of the ``Mermin-Peres square'' \nb\cite{peres1995quantum,Mermin1990Simple} that uses the
+To proceed, we use a formulation of the ``Mermin-Peres square''\nb\cite{peres1995quantum,Mermin1990Simple} that uses the
 expectation value of a physical observable with respect
@@
 by application of the Born rule to determine the probability of a given measurement 
-outcome \nb\citep{Born1983,peres1995quantum,544199}. The Gleason
+outcome\nb\citep{Born1983,peres1995quantum,544199}. The Gleason
 theorem establishes that there is no alternative to the Born rule by 
@@
 $\rho$ consistent with the statistical predictions computed from 
-that rule \nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+that rule\nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 It is then legitimate to question what happens when infinite precision
@@
 there is a mathematically precise sense in which one recovers the original Gleason theorem asymptotically. 
-Specifically, if for bounded resources the QIVPM is induced by some mixed states \nb$\rho'$, 
+Specifically, if for bounded resources the QIVPM is induced by some mixed states\nb$\rho'$, 
 those states will converge to a unique state $\rho$ when the size of the intervals characterizing 
@@
 For instance, in Sec.\ \ref{sec:Kochen-Specker},  we quantify the domain of validity of a  contextual measurement, thus addressing the conditions under which the Kochen-Specker theorem applies.
-This provides a way of resolving the Meyer-Mermin debate, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
+This provides a way of resolving the Meyer-Mermin debate\nb\footnote{Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
 In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.

### 2017-08-05 prop_letter.tex
prop_letter.tex \section{Introduction} Update comments...

@@
 For instance, in Sec.\ \ref{sec:Kochen-Specker},  we quantify the domain of validity of a  contextual measurement, thus addressing the conditions under which the Kochen-Specker theorem applies.
-This provides a way of resolving the Meyer-Mermin debate\nb\footnote{Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
+This provides a way of resolving the Meyer-Mermin debate\nb\footnote{There is nothing found when google ``Meyer-Mermin debate.''\\
+Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.\\
+Jochen Szangolies called this ``the Finite-Precision Problem''~\citep{Szangolies2015}.}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
 In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.

### 2017-08-06 prop_letter.tex
prop_letter.tex \section{Introduction} Update the comment...

--- 2017-08-04 prop_letter.tex
@@
 For instance, in Sec.\ \ref{sec:Kochen-Specker},  we quantify the domain of validity of a  contextual measurement, thus addressing the conditions under which the Kochen-Specker theorem applies.
-This provides a way of resolving the Meyer-Mermin debate\nb\footnote{Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
+This provides a way of resolving the Meyer-Mermin debate\nb\footnote{There is nothing found when google ``Meyer-Mermin debate.'' This
+is not a very good name, since there are more people involve in this
+debate. For example, Cabello~\citep{Cabello2002} and Larsson~\citep{Larsson2002}
+attended the conference, and they commented on this issue as well.
+They might not be very happy if we are our referees and only see Meyer
+and Mermin's name??\\
+Adán Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.\\
+Jochen Szangolies called this ``the Finite-Precision Problem''~\citep{Szangolies2015}.\\
+D.M.
+Appleby doesn't refer this problem by any special name~\citep{Appleby_2005}...}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
 In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.

### 2017-08-08 prop_letter.tex
prop_letter.tex \section{Introduction} Update the comment...

@@
 Jochen Szangolies called this ``the Finite-Precision Problem''~\citep{Szangolies2015}.\\
-D.M.
-Appleby doesn't refer this problem by any special name~\citep{Appleby_2005}...}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
+\citep{BarrettKent2004,Appleby_2005} don't refer this problem by
+any special name...}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
 In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.

### 2017-08-10 prop_letter.tex
pass over paper

--- 2017-08-05 prop_letter.tex
@@
 \begin{abstract}
-
 We present a mathematical framework based on quantum interval-valued
@@
 on the Kochen-Specker theorem.
-
 \end{abstract}
@@
 
-\begin{comment}
-\keywords{Finite precision measurement, the Born rule, Gleason's
-theorem, the Kochen-Specker theorem, interval-valued probability measure,
-discrete quantum theory}
-\end{comment}
+% \keywords{Finite precision measurement, the Born rule, Gleason's
+% theorem, the Kochen-Specker theorem, interval-valued probability measure,
+% discrete quantum theory}
 
@@
 mechanics regarding the tension between finite precision measurement
-and contextuality\nb\cite{BarrettKent2004,Appleby_2005}, which refers to the fact that the results of measuring compatible sets of observables depend  on whether they are measured together or separately.
-For example,
-Meyer\nb\cite{PhysRevLett.83.3751} and Mermin\nb\cite{Mermin1999} disagree
-on whether finite-precision measurements invalidate the spirit of the Kochen-Specker
-theorem\nb\cite{kochenspecker1967,peres1995quantum}, which is a mathematical statement about contextuality.   The Kochen-Specker theorem asserts that, in a Hilbert space of dimension
-$d \ge 3$, it is impossible to associate definite measured values, $\mu(P_i)= 0$
-or $1$, with every projection operator\nb$P_i$, in such a way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then $\sum_i \mu(P_i) = 1$. In contrast, Meyer showed that 
-one {\it can\/}  assign definite values $0$ or $1$ to the measurement outcome $\mu(P_i)$ when the Hilbert space is defined over the field of rational numbers, therefore nullifying the theorem\nb\citep{PhysRevLett.83.3751}.
-However, Mermin then argued that measurement outcomes must depend smoothly
-on slight changes in the experimental configuration. Mermin therefore claimed that 
-the impact of Meyer's negative result  is ``unsupportable''\nb\citep{Mermin1999}. 
-Discussion
-has continued on whether contextuality is consistent with  experimental outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
-A fundamental question is how to address this controversy by developing
- mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.
+and contextuality\nb\cite{BarrettKent2004,Appleby_2005}, which refers
+to the fact that the results of measuring compatible sets of
+observables depend on whether they are measured together or
+separately.  For example, Meyer\nb\cite{PhysRevLett.83.3751} and
+Mermin\nb\cite{Mermin1999} disagree on whether finite-precision
+measurements invalidate the spirit of the Kochen-Specker
+theorem\nb\cite{kochenspecker1967,peres1995quantum}, which is a
+mathematical statement about contextuality.  The Kochen-Specker
+theorem asserts that, in a Hilbert space of dimension $d \ge 3$, it is
+impossible to associate definite measured values, $\mu(P_i)= 0$ or
+$1$, with every projection operator\nb$P_i$, in such a way that, if a
+set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
+$\sum_i \mu(P_i) = 1$. In contrast, Meyer showed that one {\it can\/}
+assign definite values $0$ or $1$ to the measurement outcome
+$\mu(P_i)$ when the Hilbert space is defined over the field of
+rational numbers, therefore nullifying the
+theorem\nb\citep{PhysRevLett.83.3751}.  However, Mermin then argued
+that measurement outcomes must depend smoothly on slight changes in
+the experimental configuration. Mermin therefore claimed that the
+impact of Meyer's negative result is
+``unsupportable''\nb\citep{Mermin1999}.  Discussion has continued on
+whether contextuality is consistent with experimental
+outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+A fundamental question is how to address this controversy by
+developing mathematical theories of quantum mechanics that are
+intrinsically, rather than only implicitly, consistent with the
+resources available for the realistic accuracy of an actual
+measurement.
 
@@
 interval-valued probability measures (IVPM) to achieving a coherent
-formulation of finite-resource quantum mechanics.
-To this end, we develop a mathematical framework that includes the uncertainties of finite precision and imperfections in the quantum measurement process.
-In particular, we quantify the concept of imperfect quantum measurement and its impact on the interpretation of the Kochen-Specker and Gleason theorems and their implications for the foundations of quantum mechanics.
-Our first observation is that essential objectives of our program to
-achieve a computable theory of quantum mechanics and finite-resource
-measurement, attempted previously with computable number
-systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
-extending classical interval-valued probability
-measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We thus begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework.
+formulation of finite-resource quantum mechanics.  To this end, we
+develop a mathematical framework that includes the uncertainties of
+finite precision and imperfections in the quantum measurement
+process. In particular, we quantify the concept of imperfect quantum
+measurement and its impact on the interpretation of the Kochen-Specker
+and Gleason theorems and their implications for the foundations of
+quantum mechanics.  Our first observation is that essential objectives
+of our program to achieve a computable theory of quantum mechanics and
+finite-resource measurement, attempted previously with computable
+number systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be
+achievable by extending classical interval-valued probability
+measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We thus
+begin by axiomatizing a quantum interval-valued probability measure
+(QIVPM) framework.
 
-The effect of finite precision and imperfections on contextuality and the
-Kochen-Specker theorem is shown to have a resolution in terms of our QIVPM framework.  
-To proceed, we use a formulation of the ``Mermin-Peres square''\nb\cite{peres1995quantum,Mermin1990Simple} that uses the
-expectation value of a physical observable with respect
-to a QIVPM, where the interval-valued
-expectation value is consistent with the expectation value of the
-same observable in conventional quantum mechanics with infinite resources. We show that, 
-as long as errors and uncertainties remain smaller than a particular value, the
-Kochen-Specker theorem remains valid. In other words, we established a rigorous bound for 
-its validity and, therefore, the limits for physical reality to remain contextual.
+The effect of finite precision and imperfections on contextuality and
+the Kochen-Specker theorem is shown to have a resolution in terms of
+our QIVPM framework.  To proceed, we use a formulation of the
+``Mermin-Peres square''\nb\cite{peres1995quantum,Mermin1990Simple}
+that uses the expectation value of a physical observable with respect
+to a QIVPM, where the interval-valued expectation value is consistent
+with the expectation value of the same observable in conventional
+quantum mechanics with infinite resources. We show that, as long as
+errors and uncertainties remain smaller than a particular value, the
+Kochen-Specker theorem remains valid. In other words, we established a
+rigorous bound for its validity and, therefore, the limits for
+physical reality to remain contextual.
 
-A key aspect of a quantum measurement is its statistical nature, as reflected
-by application of the Born rule to determine the probability of a given measurement 
+A key aspect of a quantum measurement is its statistical nature, as
+reflected by application of the Born rule to determine the probability
+of a given measurement
 outcome\nb\citep{Born1983,peres1995quantum,544199}. The Gleason
@@
 demonstrating, using reasonable continuity arguments in Hilbert spaces
-of dimension $d\ge3$, the existence of a unique state 
-$\rho$ consistent with the statistical predictions computed from 
-that rule\nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-It is then legitimate to question what happens when infinite precision
-cannot be achieved. We will show that, if the effect of finite precision is incorporated, 
-while a QIVPM  might not be consistent
-with a unique state\nb$\rho$ on all projectors defined on a Hilbert space of dimension $d\ge3$, 
-there is a mathematically precise sense in which one recovers the original Gleason theorem asymptotically. 
-Specifically, if for bounded resources the QIVPM is induced by some mixed states\nb$\rho'$, 
-those states will converge to a unique state $\rho$ when the size of the intervals characterizing 
-the uncertainties tends to zero.
+of dimension $d\ge3$, the existence of a unique state $\rho$
+consistent with the statistical predictions computed from that
+rule\nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  It is
+then legitimate to question what happens when infinite precision
+cannot be achieved. We will show that, if the effect of finite
+precision is incorporated, while a QIVPM might not be consistent with
+a unique state\nb$\rho$ on all projectors defined on a Hilbert space
+of dimension $d\ge3$, there is a mathematically precise sense in which
+one recovers the original Gleason theorem asymptotically.
+Specifically, if for bounded resources the QIVPM is induced by some
+states\nb$\rho'$, those states will converge to a unique state $\rho$
+when the size of the intervals characterizing the uncertainties tends
+to zero.
 
-The paper is organized as follows.
-In Sec.\ \ref{sec:fuzzy} we begin by introducing the foundations of quantum probability space and fuzzy measurement.
-We then move on to introduce the concept of quantum interval valued probability in Sec.\ \ref{sec:Interval-Uncertainty}.
-This QIVPM will provide the mathematical framework to quantify the impact of finite precision measurements on quantum mechanics.
-For instance, in Sec.\ \ref{sec:Kochen-Specker},  we quantify the domain of validity of a  contextual measurement, thus addressing the conditions under which the Kochen-Specker theorem applies.
-This provides a way of resolving the Meyer-Mermin debate\nb\footnote{There is nothing found when google ``Meyer-Mermin debate.''\\
-Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.\\
-Jochen Szangolies called this ``the Finite-Precision Problem''~\citep{Szangolies2015}.}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.
-In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.
-Finally, we present our conclusions in Sec.~\ref{sec:Conclusion}.
-
-% Textbook quantum mechanics asserts that the probability of a
-% measurement can be computed from wave function of the system and the
-% measuring observable \emph{exactly} while real measurements must be
-% finite precision.  Whether finite precision measurement in reality
-% affect the idealized quantum concept, e.g.,
-% contextuality\nb\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
-% and the very foundation of quantum mechanics is still a problem. In
-% this letter, we model the finite precision quantum measurement by
-% quantum interval-valued probability measures (IVPMs) which provides
-% not only a uniform framework to understand Gleason's
-% theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
-% Kochen-Specker
-% theorem\nb\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
-% but also some examples which cannot be explained by the Born
-% rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
-
-% The tension between finite precision measurement and the foundation of
-% quantum mechanics sharpened, when the original definition of
-% contextuality based on infinitely precise numbers is proved not
-% experimental verifiable\nb\cite{PhysRevLett.83.3751,Kent1999}.  After a
-% long debate\nb\cite{Mermin1999,Peres2003,BarrettKent2004}, people are
-% still trying to update the definition of contextuality when they want
-% to perform further
-% experiments\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
-
-% We found that finite precision measurement affects not only
-% contextuality but also the fundamental rule computing probability from
-% a state.  In the early formulation of quantum mechanics, von Neumann
-% essentially formulated a quantum state as a density matrix while
-% Mackey formulated a quantum state as a quantum probability measure
-% which are proved by Gleason to be the essentially same as a density
-% matrix\nb\cite{Varadarajan2008}.  Combining quantum probability measures
-% and the classical IVPM\nb\cite{JamisonLodwick2004} which could be used
-% to formulate classical finite precision measurement, we can define
-% quantum IVPMs. Surprisingly, there is a quantum IVPM which cannot be
-% compatible with any density matrix according to the Born rule. Similar
-% to revising the definition of contextuality because of finite
-% precision measurement, the very basic definition of a quantum state or
-% how to compute the probability from a state might need to be refined
-% when we consider the finite precision measurement. This can also
-% provide a new quantum phenomena different from the classical world,
-% because IVPMs become classical so that the non-Born IVPMs disappears
-% when we restricting the domain of quantum IVPMs on a commuting
-% sub-event space.
+The paper is organized as follows.  In Sec.\ \ref{sec:fuzzy} we begin
+by introducing the foundations of quantum probability space and fuzzy
+measurement.  We then move on to introduce the concept of quantum
+interval valued probability in Sec.\ \ref{sec:Interval-Uncertainty}.
+This QIVPM will provide the mathematical framework to quantify the
+impact of finite precision measurements on quantum mechanics.  For
+instance, in Sec.\ \ref{sec:Kochen-Specker}, we quantify the domain of
+validity of a contextual measurement, thus addressing the conditions
+under which the Kochen-Specker theorem applies.  This provides a way
+of resolving the Meyer-Mermin debate, which is the main result of our
+Thm~\ref{cor:Kochen-Specker-IVPM}.  In Sec.\ \ref{sec:Gleason}, we
+study Gleason's theorem in the context of imprecise measurements,
+concluding that QIVPM provides a framework with quantitative bounds in
+which Gleason's theorem, while formally invalid in a universe with
+bounded resources, holds asymptotically in a mathematically precise
+way.  Finally, we present our conclusions in
+Sec.~\ref{sec:Conclusion}.
 
@@
 \label{sec:fuzzy}
+
 A \emph{probability space} is a mathematical abstraction specifying
 the necessary conditions for reasoning coherently about collections of
-uncertain events\nb\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the quantum case, the
-events of interest are specified by \emph{projection operators}
-$P$. These include the empty projection\nb$\mathbb{0}$, the identity
-projection\nb$\mathbb{1}$, projections of the form $\proj{\psi}$ where
-$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
-sums of \emph{orthogonal} projections $P_0$ and $P_1$ with
+uncertain
+events\nb\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In
+the quantum case, the events of interest are specified by
+\emph{projection operators} $P$. These include the empty
+projection\nb$\mathbb{0}$, the identity projection\nb$\mathbb{1}$,
+projections of the form $\proj{\phi}$ where $\ket{\phi}$ is a pure
+quantum state (an element of a Hilbert space), sums of
+\emph{orthogonal} projections $P_0$ and $P_1$ with
 $P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
@@
 space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
-each event $P_{i}$ is mapped to a probability\nb$\mu(P_{i})$ using
-a probability measure\nb$\mu:\events\rightarrow[0,1]$, where $\events$
-is the set of all projections on a given Hilbert space, subject to
-the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
+each event $P_{i}$ is mapped to a probability\nb$\mu(P_{i})$ using a
+probability measure\nb$\mu:\events\rightarrow[0,1]$, where $\events$
+is the set of all projections on a given Hilbert space, subject to the
+following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
 $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
@@
 \end{equation}
+
+\noindent A quantum probability measure can be easily constructed if
+one knows the current state of the quantum system by using the Born
+rule.  Specifically, for each pure normalized quantum state
+$\ket{\phi}$, the Born rule induces a probability measure
+$\mu_{\phi}^{\mathrm{B}}$ defined as
+$\mu_{\phi}^{\mathrm{B}}(P)=\ip{\phi}{P\phi}$. The situation
+generalizes to mixed states
+$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
+$\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born rule
+induces a probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as
+$\mu_{\rho}^{\mathrm{B}}\left(P\right) = \Tr\left(\rho P\right) =
+\sum_{j=1}^{N}
+q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
 
@@
 $\mu_2(\proj{1}) = 0$, $\mu_2(\proj{2}) = 0.5$. By the Born rule, the
-first probability measure corresponds to the quantum system being in a
-state $(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second corresponds to
-the quantum system being in the state
+first probability measure corresponds to the quantum system being in
+the pure state $(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second
+corresponds to the quantum system being in the pure state
 $(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where in both cases
@@
 resources (time, energy, money, etc.) that are devoted to the
-experiment. In the classical setting, this ``fuzziness'' can be formalized
-by moving to \emph{interval-valued probability measures}, which we explore in
-the next section, along with our proposed extension to the quantum domain.
-
-% In conventional quantum theory (CQT), when we measure a property
-% $\mathbf{O}$ of a physical system whose state is represented by a
-% density matrix\nb$\rho$, the probability to obtain the value $\lambda$
-% of that property is determined by the Born rule
-% $\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
-%   P_{i}\right)$, where $P_{i}$ denotes the projector onto the
-% eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
-% Hermitian operator
-% $\mathbf{O}$\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
-% Alternatively, one may say that the state $\rho$ determines the
-% probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
-% from the set $\events$ of all possible projectors $P$ onto the
-% interval $[0,1]$, and satisfies the following probability axioms\nb
-% \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:
-
-% \begin{itemize}
-% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
-% \item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
-% \item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
-% 1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
-% \item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
-% $P_iP_j=\delta_{ij}P_i$,
-% we have 
-% \begin{equation}
-% \mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
-% \sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
-% \,.\label{eq:QuantumProbability-Addition}
-% \end{equation}
-% \end{itemize}
-% Conversely, given any quantum probability measure\nb$\mu:\events\rightarrow[0,1]$
-% satisfying the above axioms, Gleason's theorem asserts that there
-% exists a unique state\nb$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
-% in a Hilbert space of dimension $d\geq3$\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-
-% Furthermore, if we express an observable\nb$\mathbf{O}$ as its spectrum
-% decomposition\nb$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
-% value of $\mathbf{O}$ is given by\nb\cite{peres1995quantum,544199,Jaeger2007}
-% \begin{equation}
-% \expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
-% \end{equation}
-
-% To formalize the idea of finite precision measurement, we next
-% introduce the notion of quantum interval-valued probability measures
-% (\emph{IVPMs})\nb$\bar{\mu}$. The latter replaces the infinitely precise
-% interval $[0,1]$ by a finite collection $\mathscr{I}$ of
-% intervals. Since the intervals $\imposs=\left[0,0\right]$ and
-% $\necess=\left[1,1\right]$ should be included in $\mathscr{I}$, and
-% arithmetic operations on intervals
-% satisfy \begin{subequations}\label{eq:interval-operations}
-% \begin{eqnarray}
-%  &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
-%  &  & x[l,r]=\begin{cases}
-% [xl,xr] & \textrm{for }x\ge0\,;\\{}
-% [xr,xl] & \textrm{for }x\le0\,.
-% \end{cases}
-% \end{eqnarray}
-% \end{subequations} $\bar{\mu}:\events\rightarrow\mathscr{I}$ is
-% defined by the axioms: 
-% \begin{itemize}
-% \item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
-% \item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
-% \item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
-% \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
-% $P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
-% \begin{equation}
-% \bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion}
-% \end{equation}
-% \end{itemize}
-% condition that provides only a bound and not an equivalence as in
-% Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
-% $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
-% $\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
-% \[
-% \bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
-% \]
+experiment. In the classical setting, this ``fuzziness'' can be
+formalized by moving to \emph{interval-valued probability measures},
+which we explore in the next section, along with our proposed
+extension to the quantum domain.
 
@@
 \label{sec:Interval-Uncertainty}
+
 We will start by reviewing IVPMs in the classical setting and then
@@
 fact that the probability $\mu(E)$ of an event~$E$ is generalized from
-a single real number to an interval\nb$[\ell,r]$
+a single \emph{real number} to an \emph{interval}\nb$[\ell,r]$
 where\nb$\ell$ intuitively corresponds to the strength of evidence for
-the event and~$1-r$ corresponds to the strength of evidence against the
-event. The collection of intervals used in the definition of a
-probability measure must satisfy certain properties that we explain
-next.
+the event~$E$ and~$1-r$ corresponds to the strength of evidence
+against the same event. The collection of intervals used in the
+definition of a probability measure must satisfy certain properties
+that we explain next.
 
@@
 refer to the probability of impossible events (e.g., the null event)
-and certain events (e.g., the event covering the entire sample space).
-For each interval $[\ell,r]$, we also need the interval
-$[1-r,1-\ell]$ so that if one interval refers to the probability of an
-event, the other refers to the probability of the event's complement.
-For example, if we discover as a result of an experiment that
-$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
-$\mu(\overline{E}) = [0.7,0.8]$ for the complementary event
+and events that are certain (e.g., the event covering the entire
+sample space).  For each interval $[\ell,r]$, we also need the
+interval $[1-r,1-\ell]$ so that if one interval refers to the
+probability of an event, the other refers to the probability of the
+event's complement.  For example, if we discover as a result of an
+experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$, we may
+conclude that $\mu(\overline{E}) = [0.7,0.8]$ for the complement event
 $\overline{E}$. In addition to these simple conditions, there are some
@@
 $\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
-at calculating the probability of the combined event that \emph{either} $E_1$
-or $E_2$ occurs might be $\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In
-some cases, this is indeed a sensible definition. For example, if
-$\mu(E_1)=[0.1,0.2]$ and $\mu(E_2)=[0.3,0.4]$ we get
-$\mu(E_1\cup E_2) = [0.4,0.6]$. But consider an event $E$ such that
-$\mu(E)=[0.2,0.3]$ and hence $\mu(\overline{E})=[0.7,0.8]$. The two
-events $E$ and $\overline{E}$ are disjoint; the previous naïve way
-of combining the intervals would give $\mu(E\cup\overline{E})=[0.9,1.1]$
-which is not a valid probability interval. Moreover the event
-$E\cup\overline{E}$ is the identity event covering the entire space; its
-probability interval should be $[1,1]$ which is sharper than
-$[0.9,1.1]$. The problem is that the two intervals are correlated:
-there is more information in the combined event than in each event
-separately. In our example, even though the true probability of
-$\mu(E)$ can be anywhere in the range $[0.2,0.3]$ and the true
-probability of $\mu(\overline{E})$ can be in anywhere in the range
-$[0.7,0.8]$, the values are not independent. Any value of
-$\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq 0.75$. To account
-for such subtleties, the axioms of interval-valued probability do not
-use a strict equality for the combination of disjoint events. The
-correct constraint regarding the probability of $E_1\cup E_2$ when $E_1$
-and $E_2$ are disjoint is
-$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in combination
-with the requirement for the identity event would force
-$\mu(E\cup\overline{E})$ to always be $[1,1]$ irrespective of the
+at calculating the probability of the combined event that
+\emph{either} $E_1$ or $E_2$ occurs might be
+$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
+indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
+$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
+consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
+$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
+are disjoint; the previous naïve way of combining the intervals would
+give $\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
+probability interval. Moreover the event $E\cup\overline{E}$ is the
+identity event covering the entire space; its probability interval
+should be $[1,1]$ which is sharper than $[0.9,1.1]$. The problem is
+that the two intervals are correlated: there is more information in
+the combined event than in each event separately. In our example, even
+though the true probability of $\mu(E)$ can be anywhere in the range
+$[0.2,0.3]$ and the true probability of $\mu(\overline{E})$ can be in
+anywhere in the range $[0.7,0.8]$, the values are not independent. Any
+value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
+0.75$. To account for such subtleties, the axioms of interval-valued
+probability do not use a strict equality for the combination of
+disjoint events. The correct constraint regarding the probability of
+$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
+$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
+combination with the requirement for the identity event would force
+$\mu(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
 particular assignments of $\mu(E)$ or $\mu(\overline{E})$.
@@
 When combining non-disjoint events, there is a further subtlety whose
-resolution will give us one final general condition. For
+resolution will give us the final general condition for IVPMs. For
 general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
@@
 
-We now have the necessary ingredients to define QIVPMs as a
-generalization of both classical IVPMs and conventional quantum
-probability measures. We will show that the quantum IVPM will reduce to
-the classical IVPM when the space of quantum events is restricted to
-mutually commuting sub-events.
+We now have the necessary ingredients to define the quantum extension,
+QIVPMs, as a generalization of both classical IVPMs and conventional
+quantum probability measures. We will show that QIVPMs reduce to
+classical IVPMs when the space of quantum events is restricted to
+mutually commuting sub-events, i.e., to compatible events that can be
+measured simultaneously.
 
@@
   \end{subequations}
-  and satisfying for each pair of \emph{commuting} projections $P_0$ and $P_1$,
-  ($P_0P_1=P_1P_0$)
+  and satisfying for each pair of \emph{commuting} projections $P_0$
+  and $P_1$ with $P_0P_1=P_1P_0$,
 \begin{equation}
@@
 \end{definition}
-The first three constraints, Eq.\nb(\ref{eq:QIVPM-constraints}), are the direct
-counterpart of the corresponding ones for conventional interval probability
-measures.
-With the understanding that the union of classical sets $E_1\cup E_2$ is replaced
-by $P_0+P_1-P_0P_1$ in the case of quantum projection
-operators~\cite{Griffiths2003}, the last condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is
-a direct counterpart of Eq.~(\ref{eq:classicalconvex}).
+\noindent The first three constraints, Eqs.\nb(\ref{eq:QIVPM-constraints}), are
+the direct counterpart of the corresponding ones for IVPMs.  With the
+understanding that the union of classical sets $E_1\cup E_2$ is
+replaced by $P_0+P_1-P_0P_1$ in the case of quantum projection
+operators~\cite{Griffiths2003}, the last condition,
+Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
+direct counterpart of Eq.~(\ref{eq:classicalconvex}).
 
@@
 \begin{equation}
-\coreBorn\left(\bar{\mu},S\right)=\set{\textrm{mixed state }\rho}{\forall P\in S\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}
+\coreBorn\left(\bar{\mu},S\right)=\set{\textrm{state }\rho}{\forall P\in S\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}
 \end{equation}
-is the set of all mixed states consistent with $\bar{\mu}$ on every
-projector in $S$. For example, assuming the three intervals $\imposs=\left[0,0\right]$,
-$\necess=\left[1,1\right]$, and $\unknown=\left[0,1\right]$, then:
+is the set of all states consistent with $\bar{\mu}$ on every
+projector in $S$. For example, assuming the three intervals $\imposs$,
+$\necess$, and $\unknown=\left[0,1\right]$, then:
 \begin{equation}
@@
 is a QIVPM. This measure represents the beliefs of an experimenter
-with no prior knowledge about the particular quantum system in question;
-any quantum state would be consistent with $\bar{\mu}_{1}$ on any
-projectors, and $\coreBorn\left(\bar{\mu}_{1},\events\right)$ is
-just the set of all mixed states.
+with no prior knowledge about the particular quantum system in
+question; any quantum state would be consistent with $\bar{\mu}_{1}$
+on any projectors, and $\coreBorn\left(\bar{\mu}_{1},\events\right)$
+is just the set of all states.
 
-Quantum IVPMs become classical IVPMs when the space of events includes
-only mutually commuting events. We define $\events'\subseteq\events$
-to be a sub-event space if it satisfies the following conditions.
+As mentioned earlier, QIVPMs become classical IVPMs when the space of
+events includes only mutually commuting events. We define
+$\events'\subseteq\events$ to be a sub-event space if it satisfies the
+following conditions.
 \begin{itemize}
@@
 \end{equation}
-If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
-the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
-represents the situation in which that an experimenter knows nothing about a
-coin before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
+If we identify the states \nb$\proj{0}$ and $\proj{1}$ with the head
+and the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents
+the situation in which that an experimenter knows nothing about a coin
+before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
 state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
 coin with probability\nb$p$ to get heads, and
-$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
-classical coin should be consistent with the situation for which an experimenter
-has no prior knowledge.
+$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with
+$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin should be
+consistent with the situation for which an experimenter has no prior
+knowledge.
 
@@
 uncertainty found in conventional infinite precise quantum
-mechanics\nb\cite{PeresRon1988,peres1995quantum}. We will adapt
-the proof of the Kochen-Specker theorem\nb\cite{kochenspecker1967,
+mechanics\nb\cite{PeresRon1988,peres1995quantum}.
+
+\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}Given
+  a Hilbert space of dimension~$d\ge3$, there is no 0-deterministic
+  measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}
+  $.\end{thm}
+
+We will adapt the proof of the Kochen-Specker
+theorem~\cite{kochenspecker1967,
   peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
@@
 
-We will proceed by assuming a cryptodeterministic QIVMP $\bar{\mu}$
-and derive a contradiction using the following nine ``Mermin-Peres square''
-observables $\mathbf{O}_{ij}$\nb\cite{Mermin1990Simple,peres1995quantum}:
+We will proceed by assuming a 0-deterministic QIVMP $\bar{\mu}$ and
+derive a contradiction using the following nine ``Mermin-Peres
+square'' observables
+$\mathbf{O}_{ij}$\nb\cite{Mermin1990Simple,peres1995quantum}:
 \begin{center}
@@
 \noindent where $\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are
-Pauli matrices acting on a pair of spin-$\frac{1}{2}$ state. We now define the
+Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. We now define the
 expectation value of the QIVPM for our Mermin-Peres square.
@@
 The expectation value is intuitively between two possible outcomes,
-which themselves lie between the minimum and maximum bounds of the given
-probability intervals. (This definition is consistent with the
+which themselves lie between the minimum and maximum bounds of the
+given probability intervals. (This definition is consistent with the
 classical Choquet integral on commuting sub-event spaces by adopting
-the classical
-results\nb\cite{GilboaSchmeidler1994,Grabisch2016}.)
-If the QIVPM is cryptodeterministic, this interval collapses to a
-singleton $\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
+the classical results\nb\cite{GilboaSchmeidler1994,Grabisch2016}.)  If
+the QIVPM is 0-deterministic, this interval collapses to a singleton
+$\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
 of~$\mathbf{O}$. If we define the multiplication of two singleton
@@
 $\left\{ -1\right\} $.  In each row and column, the operators commute,
-and each operator is the product of two others, except in the
-third column, where
+and each operator is the product of two others, except in the third
+column, where
 $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
 Therefore, it is clearly impossible to find a QIVPM\nb$\bar{\mu}$ such
-that $\langle \mathbf{O}_{ij}\rangle_{\bar \mu}$
-%\begin{equation}
-%\begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} %& \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
-%\langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & %\otimes\sigma_{x}\rangle_{\bar{\mu}}\\
-%\langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & %\otimes\sigma_{y}\rangle_{\bar{\mu}}
-%\end{aligned}
-%\label{eq:MerminSquare-values}
-%\end{equation}
-satisfies Eq.~(\ref{eq:Kochen-Specker-Rules}).
+that $\langle \mathbf{O}_{ij}\rangle_{\bar \mu}$ satisfies
+Eq.~(\ref{eq:Kochen-Specker-Rules}).
 
@@
 
-A cryptodeterministic QIVPM is $0$-deterministic.  As $\delta$ gets
-bigger, the QIVPM allows more and more indeterminate behavior. A
-$\frac{1}{3}$-deterministic QIVPM can be given by
+As $\delta$ gets bigger, the QIVPM allows more and more indeterminate
+behavior. A $\frac{1}{3}$-deterministic QIVPM can be given by
 $\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
@@
 \label{sec:Gleason}
+
 In the classical setting, measurements done with limited resources and
@@
 system. However, there is always at least one state that is consistent
-with the imprecise
-measurements~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
+with the imprecise measurements.
 
-\begin{thm}\label{thm:Shapley}
+\begin{thm}[Shapley~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}]\label{thm:Shapley}
   For a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
@@
 measures, Gleason's theorem asserts that every measure is determined
-by a unique mixed state. The theorem above is weaker: it
-asserts that, for each classical sub-event subspace, a QIVPM must be
-consistent with \emph{some} state. But the states consistent with
-different subspaces may be incomparable, as the following example
-shows.
+by a unique state.
+
+\begin{thm}[Gleason~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
+a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
+measure~$\mu:\events\rightarrow[0,1]$, there exists a unique 
+state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$.
+\end{thm}
+
+Thm.~\ref{thm:Shapley} is weaker: it asserts that, for each
+classical sub-event subspace, a QIVPM must be consistent with
+\emph{some} state. But the states consistent with different subspaces
+may be incomparable, as the following example shows.
 
@@
 $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-for any mixed state\nb$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
+for any state\nb$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
 Hence, $\rho$ cannot be any state other than $\ket{2}$, the only
@@
 
-% In general, this kind of inconsistency can be reduced if we increase
-% the measurement resource, that is, using finer intervals. We conjecture
-% by using finer and finer intervals, it would be more and more likely
-% that there is a state consistent with a QIVPM on all projectors\nb$\events$.
-% We can define an interval-valued function\nb
-% :\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
-% by the following:
-
-% if a QIVPM\nb$\bar{\mu}$ is induced by a totally mixed
-% state\nb$\rho$ nicely, then whether another density
-% matrix\nb$\rho'\in\coreBorn\left(\bar{\mu},\events'\right)$ can be
-% estimated by $\left\Vert \rho-\rho'\right\Vert
-% $, where a
-% state\nb$\rho$ is called totally mixed if
-% $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
-% $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\}
-% $, and the the norm of a matrix\nb$A$ is defined by $\left\Vert
-%   A\right\Vert
-% =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
-% For example, consider the intervals
-
-% %%%
-% \subsection{Kochen-Specker}
-
-% While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
-% IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
-% is another one, corresponding to the Kochen-Specker theorem\nb\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
-% We will use the essential idea of the Kochen-Specker theorem to prove
-% there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
-% Suppose there is a quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
-% We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set\nb$\left\{ \lambda\right\} $,
-% where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
-% multiplication of two singleton sets\nb$\left\{ \lambda_{1}\right\} $
-% and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
-% then we have 
-% \begin{equation}
-% \prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
-% \end{equation}
-% for any sequence of commuting observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
-
-% Since the expectation value\nb$\expval{\cdot}_{\bar{\mu}}$ satisfying
-% these two properties, the following observables\nb\cite{Mermin1990Simple,peres1995quantum}:
-% \begin{equation}
-% \begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
-% \sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
-% \sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
-% \end{aligned}
-% \label{eq:MerminSquare}
-% \end{equation}
-% must have the the expectation value\nb$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
-% In each row and column, operators commutes, and each operator is the
-% product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-% Therefore, it is clear impossible to find a IVPM\nb$\bar{\mu}$ such
-% that 
-% \begin{equation}
-% \begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
-% \langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
-% \langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
-% \end{aligned}
-% \label{eq:MerminSquare-values}
-% \end{equation}
-% satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Foundational concepts in quantum mechanics, such as the Kochen-Specker and
-Gleason theorems, rely in a very subtle way on the use of
+Foundational concepts in quantum mechanics, such as the Kochen-Specker
+and Gleason theorems, rely in a very subtle way on the use of
 unbounded resources. By assuming infinitely precise measurements,
@@
 quantum mechanics. On the one hand, Kochen-Specker's result reveals a
-distinctive aspect of physical reality, the fact that it is contextual, and, on the other hand, Gleason's theorem establishes a relationship between quantum states and probabilities uniquely defined
-by Born's rule.  Our goal
-in this paper has been to analyze the physical consequences of a
-mathematical framework that allows for finite precision measurements
-by introducing the concept of quantum interval-valued probability. This
-framework incorporates uncertainty in the measurement results by defining
-fuzzy probability measures, and includes standard quantum measurement
-as the particular instance of sharp, infinitely precise, intervals.
-In addition, we showed how these two theorems emerge as limiting cases
-of this same framework, thus connecting two seemingly unrelated
-aspects of quantum physics. We noted that
-{\it arbitrary\/} finite precision measurement conditions can nullify the main
-tenets of both theorems.
-However, by carefully specifying experimental uncertainties, we were able to establish rigorous bounds on the validity of these two theorems.
-Therefore, we have established a context in which infinite precision quantum mechanical theories can be reconciled with finite precision quantum mechanical measurements, and have provided a possible resolution of the Meyer-Mermin debate on the impact of finite precision on the Kochen-Specker theorem \cite{PhysRevLett.83.3751,Mermin1999}.
+distinctive aspect of physical reality, the fact that it is
+contextual, and, on the other hand, Gleason's theorem establishes a
+relationship between quantum states and probabilities uniquely defined
+by Born's rule.  Our goal in this paper has been to analyze the
+physical consequences of a mathematical framework that allows for
+finite precision measurements by introducing the concept of quantum
+interval-valued probability. This framework incorporates uncertainty
+in the measurement results by defining fuzzy probability measures, and
+includes standard quantum measurement as the particular instance of
+sharp, infinitely precise, intervals.  In addition, we showed how
+these two theorems emerge as limiting cases of this same framework,
+thus connecting two seemingly unrelated aspects of quantum physics. We
+noted that {\it arbitrary\/} finite precision measurement conditions
+can nullify the main tenets of both theorems. However, by carefully
+specifying experimental uncertainties, we were able to establish
+rigorous bounds on the validity of these two theorems. Therefore, we
+have established a context in which infinite precision quantum
+mechanical theories can be reconciled with finite precision quantum
+mechanical measurements, and have provided a possible resolution of
+the Meyer-Mermin debate on the impact of finite precision on the
+Kochen-Specker theorem \cite{PhysRevLett.83.3751,Mermin1999}.
 
@@
 \end{document}
-
-% To adapt the axioms of such IVPMs to the quantum case, we proceed as
-% follows. First we fix a collection of intervals $\mathscr{I}$ that
-% represents an abstraction of the available experimental resources. At
-% one extreme, infinitely precise resources would correspond to the
-% collection of intervals $\{[x,x] \mid x \in [0,1]\}$. This case should
-% coincide with the idealized situation above. At another extreme, an
-% experiment with ``minimal'' resources would correspond to the
-% following three intervals $\imposs=\left[0,0\right]$,
-% $\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
-% two intervals are associated with the empty projection and the
-% identity projection but every other projection would be associated
-% with $\unknown$; its probability can be anything in the range
-% $[0,1]$. A third special situation would be to consider IVPMs with
-% only the two intervals $\imposs=\left[0,0\right]$ and
-% $\necess=\left[1,1\right]$. This is what Peres calls the
-% \emph{cryptodeterministic} case in which there is no ambiguity about
-% the status of any event; we know for certain if it will occur or not.
-
-% \begin{definition}
-% $\bar{\mu}$ is called convex. if for all
-% commuting $P_{0},P_{1}\in\events$, we have
-% $\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
-% \end{definition}
-
-% Consider again
-% Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}. We will
-% generalize it as follows for all commuting $P_{0},P_{1}\in\events$, we
-% have
-% $\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$. Note
-% that if $P_0$ and $P_1$ are \emph{orthogonal}, i.e., if $P_0P_1=0$ the
-% new equation reduces to
-% Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}.
-
-% \begin{verbatim}
-% Inclusion exclusion principle 
-%  pr(e1 union e2) + pr (e1 intersect e2) = 
-%   pr(e1) + pr(e2)
-
-% in classical Real number prob. LHS = X; RHS = X
-
-% ---
-
-% in classical IVPM; we only get LHS <= X; RHS <= X
-% but we have no connection between LHS and RHS
-
-% convexity imposes that LHS >= RHS
-
-% ---
-
-% our condition in the quantum case is the same; 
-% our left(LHS) is >= left(RHS); the right is dual, 
-% which makes LHS interval subset RHS interval.
-
-% --
-
-% replace set union by projection sum = p0 + p1 - p0p1
-% replace = by subseteq
-
-% and we get convexity definition
-
-% --
-
-% Now we need a simple classical example that shows 
-% why we need convexity or at least what it means
-
-% must be dimension 4 because everything of dim 3 
-% is convex in classical case
-
-% Consider omega = { 0, 1, 2, 3 }
-% intervals = imposssible, certain, 
-%             unlikely = [0,0.5], likely [0.5,1]
-
-% mu(empty) = imposs
-% mu(omega) = certain
-% mu({j}) = unlikely
-% mu(Omega \ {j}) = likely
-% mu({0,1}) = mu({0,2}) = mu({1,2}) = unlikely
-% mu({0,3}) = mu({1,3}) = mu({2,3}) = likely
-
-% EQ A:
-% mu({0}) + mu({0,1,2}) = [0.5,1.5]
-% mu({0,1}) + mu({0,2}) = [0,1]
-
-% AND [0.5,1.5] is not subseteq of [0,1]
-
-% Note that there is a core p(0) = p(1) = p(2) = 0.2, 
-% p(3) = 0.4, and under that core both sides of EQ A 
-% have prob. 0.8. So one way to make it convex is 
-% to use very precise intervals [0.2,0.2] etc.
-
-% Another way to make this convex is by choosing 
-% just one additional interval unknown [0,1] 
-% instead of unlikely and likely.
-
-% Intuition: the more you group the more 
-% precise you get
-
-% \end{verbatim}
-
-% In the classical setting, IVPMs typically are equipped with additional
-% conditions to ensure they are ``well-behaved.''
-
-% \amr{
-% Yu-Tsung: please construct an example with commuting events P0 and P1 such that:
-
-% mu(P0 + P1 - P0P1) + mu(P0P1) = [x,y]
-% mu(P0) + mu(P1) = [z,w]
-
-% and $[x,y]$ is NOT included in $[z,w]$
-% }
-
-% \yutsung{{Consider a four dimensional Hilbert space with an orthonormal
-% basis}\nb$\Omega=\{\ket{0},\ket{1},\ket{2},\ket{3}\}$, and the commuting
-% sub-event space\nb$\events'=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$.
-% Then, $\bar{\mu}_{0}:\events'\rightarrow\mathscr{I}$ defined by\begin{subequations}
-% \begin{eqnarray}
-%  &  & \imposs=\bar{\mu}_{0}(\mathbb{0})\,,\\
-%  &  & \necess=\bar{\mu}_{0}(\mathbb{1})\,,\\
-%  &  & \begin{aligned}\unlikely & =\bar{\mu}_{0}(\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{1})\\
-%  & =\bar{\mu}_{0}(\proj{0}+\proj{2})\\
-%  & =\bar{\mu}_{0}(\proj{1}+\proj{2})\,,
-% \end{aligned}
-% \\
-%  &  & \begin{aligned}\likely & =\bar{\mu}_{0}(\mathbb{1}-\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{2})\\
-%  & =\bar{\mu}_{0}(\proj{1}+\proj{3})\\
-%  & =\bar{\mu}_{0}(\proj{2}+\proj{3})
-% \end{aligned}
-% \end{eqnarray}
-% \end{subequations}is an IVPM, where $\ket{j}\in\Omega$ and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
-% However, $\bar{\mu}_{0}$ is not convex because
-% \begin{equation}
-% \begin{aligned} & \bar{\mu}_{0}(\proj{0})+\bar{\mu}_{0}(\mathbb{1}-\proj{3})\\
-% = & \left[\frac{1}{2},\frac{3}{2}\right]\nsubseteq\left[1,2\right]\\
-% = & \bar{\mu}_{0}(\proj{0}+\proj{1})+\bar{\mu}_{0}(\proj{0}+\proj{2})\,.
-% \end{aligned}
-% \end{equation}
-% }
-
-% Formally, we can ask: what can we deduce about the state of a quantum
-% system given a quantum IVPM, i.e., given observations done with finite
-% resources. Since the probabilities are now intervals, it is intuitive
-% to say a state\nb$\rho$ is consistent with $\bar{\mu}$ on a projector\nb$P$
-% if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
-% and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
-% Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
-% is consistent with $\bar{\mu}$ on every projector in $S$.
-
-% Consider a quantum IVPM $\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
-% and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-% the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
-% for all $P\in\events$. This time, when we express an observable as
-% its spectral decomposition
-% \begin{equation}
-% \mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
-% \end{equation}
-% we separate the positive and negative eigenvalues and order its eigenvalues
-% from the smallest to the largest 
-% \begin{equation}
-% \lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
-% \end{equation}
-% Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
-% where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-% We can combine the classical Choquet integral\nb\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-% with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
-% value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
-% \begin{eqnarray}
-% \expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
-% \end{eqnarray}
-
-% \begin{table*}
-% \caption{\label{table:quantum-interval-expectation}This table highlights the
-% process to compute $\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}$. Notice
-% that $\bar{\mu}_{1}$ is defined by Eq.~(\ref{eq:no-information-IVPM}),
-% $\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$,
-% and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$ so that $\mul_{1}\left(P_{3}^{+\prime}\right)=\mur_{1}\left(P_{3}^{+\prime}\right)=0$.}
-
-% \begin{ruledtabular}
-% \begin{tabular}{c|ccccccccc}
-% $i$ & $\lambda_{i}^{+}$ & $P_{i}^{+}$ & $\bar{\mu}_{1}\left(P_{i}^{+}\right)$ & $P_{i}^{+\prime}$ & $\bar{\mu}_{1}\left(P_{i}^{+\prime}\right)$ & $\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\mur_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mur_{1}\left(P_{i}^{+\prime}\right)$\tabularnewline
-% \hline 
-% $1$ & $1$ & $\proj{0}+\proj{2}$ & $\unknown$ & $\mathbb{1}$ & $\necess$ & $1$ & $1$ & $1$ & $0$\tabularnewline
-% $2$ & $2$ & $\proj{1}$ & $\unknown$ & $\proj{1}$ & $\unknown$ & $0$ & $1$ & $0$ & $1$\tabularnewline
-% \end{tabular}
-% \end{ruledtabular}
-
-% \end{table*}
-% For example, given a three dimensional Hilbert space with an orthonormal
-% basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
-% and $\mathbf{O}_{1}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
-% By following Table~\ref{table:quantum-interval-expectation}, we
-% have 
-% \begin{equation}
-% \expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\,.
-% \end{equation}
-% The expectation value is intuitively between two possible outcomes,
-% $1$ and $2$, even if we have no prior knowledge about the likelihood
-% of outcomes. In contrast, if we naively multiply eigenvalues with
-% intervals, their sum, $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$,
-% is a worse and counter-intuitive estimation. In fact, estimating the
-% lower-bound by $1\cdot0+2\cdot0=0$ is too pessimistic because we
-% know one of outcomes must happen without any prior knowledge.
-
-% Intuitively, the expectation value of an observable with respect to a
-% QIVPM is bounded by the minimum and maximum expectation value of the
-% same observable with respect to states consistent with it. This is
-% true when we require our IVPM to be convex, and on a commuting
-% sub-event space induced by an observable.
-
-% %%%%%
-% \subsection{Gleason}

### 2017-08-11 prop_letter.tex
prop_letter.tex \section{Introduction} Add citations...

@@
 whether contextuality is consistent with experimental
-outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+outcomes\nb\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}..
 A fundamental question is how to address this controversy by

### 2017-08-14 prop_letter.tex
before merge

--- 2017-08-10 prop_letter.tex
@@
 \allowdisplaybreaks
-\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
+\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
 \newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
@@
 mechanics regarding the tension between finite precision measurement
-and contextuality\nb\cite{BarrettKent2004,Appleby_2005}, which refers
+and contextuality~\cite{BarrettKent2004,Appleby_2005}, which refers
 to the fact that the results of measuring compatible sets of
 observables depend on whether they are measured together or
-separately.  For example, Meyer\nb\cite{PhysRevLett.83.3751} and
-Mermin\nb\cite{Mermin1999} disagree on whether finite-precision
+separately.  For example, Meyer~\cite{PhysRevLett.83.3751} and
+Mermin~\cite{Mermin1999} disagree on whether finite-precision
 measurements invalidate the spirit of the Kochen-Specker
-theorem\nb\cite{kochenspecker1967,peres1995quantum}, which is a
+theorem~\cite{kochenspecker1967,peres1995quantum}, which is a
 mathematical statement about contextuality.  The Kochen-Specker
@@
 impossible to associate definite measured values, $\mu(P_i)= 0$ or
-$1$, with every projection operator\nb$P_i$, in such a way that, if a
+$1$, with every projection operator~$P_i$, in such a way that, if a
 set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
@@
 rational numbers, therefore nullifying the
-theorem\nb\citep{PhysRevLett.83.3751}.  However, Mermin then argued
+theorem~\citep{PhysRevLett.83.3751}.  However, Mermin then argued
 that measurement outcomes must depend smoothly on slight changes in
@@
 impact of Meyer's negative result is
-``unsupportable''\nb\citep{Mermin1999}.  Discussion has continued on
+``unsupportable''~\citep{Mermin1999}.  Discussion has continued on
 whether contextuality is consistent with experimental
-outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+outcomes~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 A fundamental question is how to address this controversy by
@@
 finite-resource measurement, attempted previously with computable
-number systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be
+number systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be
 achievable by extending classical interval-valued probability
-measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We thus
+measures~\cite{JamisonLodwick2004} to the quantum domain.  We thus
 begin by axiomatizing a quantum interval-valued probability measure
@@
 our QIVPM framework.  To proceed, we use a formulation of the
-``Mermin-Peres square''\nb\cite{peres1995quantum,Mermin1990Simple}
+``Mermin-Peres square''~\cite{peres1995quantum,Mermin1990Simple}
 that uses the expectation value of a physical observable with respect
@@
 of a given measurement
-outcome\nb\citep{Born1983,peres1995quantum,544199}. The Gleason
+outcome~\citep{Born1983,peres1995quantum,544199}. The Gleason
 theorem establishes that there is no alternative to the Born rule by
@@
 consistent with the statistical predictions computed from that
-rule\nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  It is
+rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  It is
 then legitimate to question what happens when infinite precision
@@
 precision is incorporated, while a QIVPM might not be consistent with
-a unique state\nb$\rho$ on all projectors defined on a Hilbert space
+a unique state~$\rho$ on all projectors defined on a Hilbert space
 of dimension $d\ge3$, there is a mathematically precise sense in which
@@
 Specifically, if for bounded resources the QIVPM is induced by some
-states\nb$\rho'$, those states will converge to a unique state $\rho$
+states~$\rho'$, those states will converge to a unique state $\rho$
 when the size of the intervals characterizing the uncertainties tends
@@
 uncertain
-events\nb\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In
-the quantum case, the events of interest are specified by
-\emph{projection operators} $P$. These include the empty
-projection\nb$\mathbb{0}$, the identity projection\nb$\mathbb{1}$,
-projections of the form $\proj{\phi}$ where $\ket{\phi}$ is a pure
-quantum state (an element of a Hilbert space), sums of
-\emph{orthogonal} projections $P_0$ and $P_1$ with
-$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
-$P_0$ and $P_1$ with $P_0P_1=P_1P_0$. In a well-defined quantum
-probability
-space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
-each event $P_{i}$ is mapped to a probability\nb$\mu(P_{i})$ using a
-probability measure\nb$\mu:\events\rightarrow[0,1]$, where $\events$
-is the set of all projections on a given Hilbert space, subject to the
+events~\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the
+quantum case, the events of interest are specified by \emph{projection
+  operators} $P$. These include the empty projector~$\mathbb{0}$,
+the identity projector~$\mathbb{1}$, projectors of the form
+$\proj{\phi}$ where $\ket{\phi}$ is a pure quantum state (an element
+of a Hilbert space), sums of \emph{orthogonal} projectors $P_0$
+and~$P_1$ with $P_0P_1=\mathbb{0}$, and products of \emph{commuting}
+projectors $P_0$ and~$P_1$ with $P_0P_1=P_1P_0$. In a well-defined
+quantum probability
+space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
+each event $P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
+probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$
+is the set of all projectors on a given Hilbert space, subject to the
 following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
 $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
-of \emph{orthogonal} projections $P_{0}$ and $P_{1}$:
+of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
 \begin{equation}
@@
 fact that the probability $\mu(E)$ of an event~$E$ is generalized from
-a single \emph{real number} to an \emph{interval}\nb$[\ell,r]$
-where\nb$\ell$ intuitively corresponds to the strength of evidence for
+a single \emph{real number} to an \emph{interval}~$[\ell,r]$
+where~$\ell$ intuitively corresponds to the strength of evidence for
 the event~$E$ and~$1-r$ corresponds to the strength of evidence
@@
 $\mu(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
-particular assignments of $\mu(E)$ or $\mu(\overline{E})$.
+particular assignments of $\mu(E)$ or~$\mu(\overline{E})$.
 
@@
 before. The new condition, known as
-\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
+\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
 reduces to the previously
@@
   \end{subequations}
-  Then we take a QIVPM\nb$\bar{\mu}$ to be an assignment of an interval to each
-  event (projection operator\nb$P$) subject to the following constraints:
+  Then we take a QIVPM~$\bar{\mu}$ to be an assignment of an interval to each
+  event (projection operator~$P$) subject to the following constraints:
   \begin{subequations}\label{eq:QIVPM-constraints}
@@
   \end{subequations}
-  and satisfying for each pair of \emph{commuting} projections $P_0$
+  and satisfying for each pair of \emph{commuting} projectors $P_0$
   and $P_1$ with $P_0P_1=P_1P_0$,
@@
 \end{definition}
-\noindent The first three constraints, Eqs.\nb(\ref{eq:QIVPM-constraints}), are
-the direct counterpart of the corresponding ones for IVPMs.  With the
-understanding that the union of classical sets $E_1\cup E_2$ is
-replaced by $P_0+P_1-P_0P_1$ in the case of quantum projection
-operators~\cite{Griffiths2003}, the last condition,
-Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
-direct counterpart of Eq.~(\ref{eq:classicalconvex}).
+\noindent The first three constraints,
+Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
+corresponding ones for classical IVPMs.  With the understanding that the union
+of classical sets $E_1\cup E_2$ is replaced by $P_0+P_1-P_0P_1$ in the
+case of quantum projection operators~\cite{Griffiths2003}, the last
+condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+is a direct counterpart of Eq.~(\ref{eq:classicalconvex}). Thus the
+definition of QIVPM is an amalgamation of both classical IVPMs and
+conventional quantum probability measures.
 
-Contrary to the case with conventional quantum probability spaces,
-there is generally no unique state consistent with a QIVPM. Given
-observations done with finite resources, the probabilities become
-intervals, and we say a state\nb$\rho$ is consistent with the
-measure\nb$\bar{\mu}$ acting on a projector\nb$P$ if
-$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
+In Sec.~\ref{sec:Gleason}, we will show that QIVPMs generalize
+conventional quantum probability measures in the limit where the lower
+and upper end of each interval coincide exactly. In the remainder of
+this section, we will show that our definition of QIVPMs is consistent
+with classical IVPMs in the sense that a restriction of QIVPMs to
+commuting events recovers the definition of classical IVPMs.
+
+\paragraph*{QIVPMs and Classical IVPMs.} To formalize this connection,
+we first note that contrary to the case with conventional quantum
+probability spaces, there is generally no unique state consistent with
+a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent with a state
+$\rho$ and projector $P$ if the interval $\bar{\mu}(P)$ contains the
+exact probability calculated by the Born rule, i.e, if:
+\begin{equation}
+\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
+\end{equation}
 where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
-is the probability that the event\nb$P$ happens determined by the
-Born rule\nb\citep{Born1983,peres1995quantum,544199}. Given a set
-of projectors\nb$S$, 
+is the probability that the event~$P$ happens determined by the Born
+rule~\citep{Born1983,peres1995quantum,544199}.
+
+We generalize this consistency relation to sets of states and general
+subspaces of events as follows. A set of events $\events'$ is a
+\emph{subspace} if it contains $\mathbb{0}$ and $\mathbb{1}$ and is
+closed under complements and sums, i.e., for any
+projector~$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for
+each pair of orthogonal projectors~$P_0 \in \events'$ and
+$P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. Given a
+probability measure $\bar{\mu}$ and a subspace of events $\events'$,
+we can collect the set of all states $\coreBorn(\bar{\mu},\events')$
+that are consistent with $\bar{\mu}$ on every projector in $\events'$
+as:
 \begin{equation}
-\coreBorn\left(\bar{\mu},S\right)=\set{\textrm{state }\rho}{\forall P\in S\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}
+\coreBorn\left(\bar{\mu},\events'\right)=\set{\textrm{state }\rho}{\forall P\in \events',~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}.
 \end{equation}
-is the set of all states consistent with $\bar{\mu}$ on every
-projector in $S$. For example, assuming the three intervals $\imposs$,
-$\necess$, and $\unknown=\left[0,1\right]$, then:
+
+In the long version of this paper, we establish that QIVPMs become
+classical IVPMs when the space of events includes only mutually
+commuting events. The idea of the proof is as follows. Given a
+subspace of commuting events $\events_C$, we can construct a partial
+orthonormal basis by diagonalization and complete it to a full
+orthonornal basis $\overline{\events_C}$. We then build a bijection
+between the QIVPM on the set of projectors associated with this basis
+and the set of classical events corresponding to this basis. This
+correspondence leads to a crucial property in our setting.
+
+\begin{thm}\label{thm:Shapley}
+  For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
+  of events~$\events'\subseteq\events$ commutes, then
+  $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
+\end{thm}
+
+The theorem follows directly from our correspondence and Shapley's
+theorem that proves that a classical IVPM always contains at least one
+state that is consistent with every
+event~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}. As we will
+illustrate in the next section, the set of states
+$\coreBorn\left(\bar{\mu},\events'\right)$ consistent with some events
+$\events'$ and a particular QIVPM $\bar{\mu}$ may be
+\emph{empty}.
+
+For example, a well-defined  
+QIVPM, assuming the three intervals $\imposs$, $\necess$, and
+$\unknown=\left[0,1\right]$, is:
 \begin{equation}
@@
 \necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
-\unknown\,, & \text{otherwise,}
+\unknown\,, & \text{otherwise.}
 \end{cases}\label{eq:no-information-IVPM}
 \end{equation}
-is a QIVPM. This measure represents the beliefs of an experimenter
-with no prior knowledge about the particular quantum system in
-question; any quantum state would be consistent with $\bar{\mu}_{1}$
-on any projectors, and $\coreBorn\left(\bar{\mu}_{1},\events\right)$
-is just the set of all states.
-
-As mentioned earlier, QIVPMs become classical IVPMs when the space of
-events includes only mutually commuting events. We define
-$\events'\subseteq\events$ to be a sub-event space if it satisfies the
-following conditions.
-\begin{itemize}
-\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
-\item For any projection\nb$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
-\item For each pair of orthogonal projections\nb$P_0 \in \events'$ and
-  $P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. 
-\end{itemize}
-
-For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
-is a commuting sub-event space. Consider $\bar{\mu}_{1}$ defined
-in the previous paragraph. Restricting $\bar{\mu}_{1}$ to
-$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
+This measure represents the beliefs of an experimenter with no prior
+knowledge about the particular quantum system in question; any quantum
+state would be consistent with $\bar{\mu}_{1}$ on any projectors, and
+$\coreBorn\left(\bar{\mu}_{1},\events\right)$ is just the set of all
+states. The subspace
+$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
+is a subspace of commuting events. Indeed restricting $\bar{\mu}_{1}$
+to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
 IVPM~$\bar{\mu}_{2}$:
@@
 \end{aligned}
-\,.
 \end{equation}
-If we identify the states \nb$\proj{0}$ and $\proj{1}$ with the head
+If we identify the states ~$\proj{0}$ and $\proj{1}$ with the head
 and the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents
@@
 before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
-state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
-coin with probability\nb$p$ to get heads, and
+state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
+coin with probability~$p$ to get heads, and
 $p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with
@@
 uncertainty found in conventional infinite precise quantum
-mechanics\nb\cite{PeresRon1988,peres1995quantum}.
+mechanics~\cite{PeresRon1988,peres1995quantum}.
 
-\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}Given
-  a Hilbert space of dimension~$d\ge3$, there is no 0-deterministic
+\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}
+  Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
+  0-deterministic
   measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}
@@
 
-We will proceed by assuming a 0-deterministic QIVMP $\bar{\mu}$ and
+We will proceed by assuming a 0-deterministic QIVPM $\bar{\mu}$ and
 derive a contradiction using the following nine ``Mermin-Peres
-square'' observables
-$\mathbf{O}_{ij}$\nb\cite{Mermin1990Simple,peres1995quantum}:
+square''
+observables~$\mathbf{O}_{ij}$~\cite{Mermin1990Simple,peres1995quantum}:
 \begin{center}
@@
 
-\begin{definition}Given a Hilbert space of dimension\nb$d\ge3$, for every
-  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, any
-  observable\nb$\mathbf{O}$ with spectral decomposition
+\begin{definition}Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
+  for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, any
+  observable~$\mathbf{O}$ with spectral decomposition
   $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, and the minimal
-  sub-event space $\events'$ containing
+  subspace of events $\events'$ containing
   $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
@@
 given probability intervals. (This definition is consistent with the
-classical Choquet integral on commuting sub-event spaces by adopting
-the classical results\nb\cite{GilboaSchmeidler1994,Grabisch2016}.)  If
-the QIVPM is 0-deterministic, this interval collapses to a singleton
+classical Choquet integral on subspaces of commuting events by
+adopting the classical
+results~\cite{GilboaSchmeidler1994,Grabisch2016}.)  If the QIVPM is
+0-deterministic, this interval collapses to a singleton
 $\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
 of~$\mathbf{O}$. If we define the multiplication of two singleton
-sets\nb$\left\{ \lambda_{1}\right\} $ and
-$\left\{ \lambda_{2}\right\} $ to be
-$\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
+sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $
+to be $\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
 \begin{equation}
@@
 \end{equation}
-for any set of commuting observables\nb$\left\{ \mathbf{O}_{j}\right\}
+for any set of commuting observables~$\left\{ \mathbf{O}_{j}\right\}
 _{j=1}^{N}$.
 
-Since the expectation value\nb$\expval{\cdot}_{\bar{\mu}}$ satisfies
+Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfies
 these two properties, the observables in the Mermin-Peres square must
-have the expectation value\nb$\left\{ 1\right\} $ or
+have the expectation value~$\left\{ 1\right\} $ or
 $\left\{ -1\right\} $.  In each row and column, the operators commute,
@@
 $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-Therefore, it is clearly impossible to find a QIVPM\nb$\bar{\mu}$ such
+Therefore, it is clearly impossible to find a QIVPM~$\bar{\mu}$ such
 that $\langle \mathbf{O}_{ij}\rangle_{\bar \mu}$ satisfies
@@
 \begin{definition}\label{def:delta-deterministic}We define
-  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
   as $\delta$-deterministic if either
@@
 
-\begin{thm}\label{cor:Kochen-Specker-IVPM} Given a Hilbert space
-  of dimension\nb$d\ge3$, there is no $\delta$-deterministic QIVPM for
+\begin{thm}\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$
+  of dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
   $\delta<\frac{1}{3}$.\end{thm}
@@
 \begin{proof} Suppose there is a $\delta$-deterministic
-  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
-  following function\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
+  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
+  following function~$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
     \imposs,\necess\right\} $ is a cryptodeterministic QIVPM:
@@
 \end{eqnarray}
-\end{subequations}for orthogonal operators\nb$P_{0}$ and $P_{1}$.
+\end{subequations}for orthogonal operators~$P_{0}$ and $P_{1}$.
 
@@
 \begin{thm}[Shapley~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}]\label{thm:Shapley}
-  For a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
-  sub-event space\nb$\events'\subseteq\events$ commutes, then
+  For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
+  of events~$\events'\subseteq\events$ commutes, then
   $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
@@
 
-Thm.~\ref{thm:Shapley} is weaker: it asserts that, for each
-classical sub-event subspace, a QIVPM must be consistent with
-\emph{some} state. But the states consistent with different subspaces
-may be incomparable, as the following example shows.
+Thm.~\ref{thm:Shapley} is weaker: it asserts that, for each classical
+subspace of events, a QIVPM must be consistent with \emph{some}
+state. But the states consistent with different subspaces may be
+incomparable, as the following example shows.
 
 \begin{example}\label{ex:three-dimensional-three-value}
-  Given a three-dimensional Hilbert space with an orthonormal basis
-  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,  let
+  Given a three-dimensional Hilbert space $\Hilb$ with an orthonormal
+  basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let
   $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
@@
 $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-for any state\nb$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
+for any state~$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
 Hence, $\rho$ cannot be any state other than $\ket{2}$, the only
@@
 \end{equation}
-Thus, there is no state that is consistent with the QIVPM on all projectors\nb$\events$,
+Thus, there is no state that is consistent with the QIVPM on all projectors~$\events$,
 so Gleason's theorem does not hold for at least this example.
@@
 define a notion of distance based on the following norm of a
-matrix\nb$A$ as
+matrix~$A$ as
 $\left\Vert A\right\Vert
-=\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}. Now
+=\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}. Now
 consider the following collection of intervals:
@@
 \end{eqnarray}
-which are overlapping intervals with length\nb$1/n$ except the intervals
+which are overlapping intervals with length~$1/n$ except the intervals
 at each end.
@@
 It is now not difficult to verify that for any totally mixed
-state\nb$\rho$ on a three-dimensional Hilbert space,
+state~$\rho$ on a three-dimensional Hilbert space,
 $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is a

### 2017-08-14 prop_letter.tex
small wording

@@
 we first note that contrary to the case with conventional quantum
-probability spaces, there is generally no unique state consistent with
-a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent with a state
-$\rho$ and projector $P$ if the interval $\bar{\mu}(P)$ contains the
-exact probability calculated by the Born rule, i.e, if:
+probability spaces, there is generally no unique state $\rho$
+consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent
+with a state $\rho$ and projector $P$ if the interval $\bar{\mu}(P)$
+contains the exact probability calculated by the Born rule, i.e, if:
 \begin{equation}
@@
 probability measure $\bar{\mu}$ and a subspace of events $\events'$,
-we can collect the set of all states $\coreBorn(\bar{\mu},\events')$
+we denote the collection $\coreBorn(\bar{\mu},\events')$ of all states
 that are consistent with $\bar{\mu}$ on every projector in $\events'$
@@
 \begin{equation}
-\coreBorn\left(\bar{\mu},\events'\right)=\set{\textrm{state }\rho}{\forall P\in \events',~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}.
+\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in \events',~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}.
 \end{equation}

### 2017-08-14 prop_letter.tex
small things

@@
   For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
-  of events~$\events'\subseteq\events$ commutes, then
-  $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
+  of events~$\events_C\subseteq\events$ commutes, then
+  $\coreBorn\left(\bar{\mu},\events_C\right)\ne\emptyset$.
 \end{thm}

### 2017-08-14 prop_letter.tex
small things

@@
 Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
-corresponding ones for classical IVPMs.  With the understanding that the union
-of classical sets $E_1\cup E_2$ is replaced by $P_0+P_1-P_0P_1$ in the
-case of quantum projection operators~\cite{Griffiths2003}, the last
-condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-is a direct counterpart of Eq.~(\ref{eq:classicalconvex}). Thus the
-definition of QIVPM is an amalgamation of both classical IVPMs and
-conventional quantum probability measures.
+corresponding ones for classical IVPMs.  With the understanding that
+the union of classical sets $E_1\cup E_2$ is replaced by
+$P_0+P_1-P_0P_1$ in the case of quantum projection
+operators~\cite{Griffiths2003}, the last condition,
+Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
+direct counterpart of Eq.~(\ref{eq:classicalconvex}). Thus our
+definition of QIVPMs merges classical IVPMs with conventional quantum
+probability measures.
 
 In Sec.~\ref{sec:Gleason}, we will show that QIVPMs generalize
-conventional quantum probability measures in the limit where the lower
-and upper end of each interval coincide exactly. In the remainder of
-this section, we will show that our definition of QIVPMs is consistent
-with classical IVPMs in the sense that a restriction of QIVPMs to
-commuting events recovers the definition of classical IVPMs.
+conventional quantum probability measures in the limit where each the
+lower and upper end of each interval coincide exactly and the
+intervals cover $[0,1]$. In this section, we will show that our
+definition of QIVPMs is consistent with classical IVPMs in the sense
+that a restriction of QIVPMs to commuting events recovers the
+definition of classical IVPMs.
 
-\paragraph*{QIVPMs and Classical IVPMs.} To formalize this connection,
-we first note that contrary to the case with conventional quantum
+To formalize this connection between QIVPMs and classical IVPMs, we
+first note that contrary to the case with conventional quantum
 probability spaces, there is generally no unique state $\rho$

### 2017-08-14 prop_letter.tex
small things

@@
 To formalize this connection between QIVPMs and classical IVPMs, we
-first note that contrary to the case with conventional quantum
+first note that in contrast to the case with conventional quantum
 probability spaces, there is generally no unique state $\rho$
@@
 illustrate in the next section, the set of states
-$\coreBorn\left(\bar{\mu},\events'\right)$ consistent with some events
-$\events'$ and a particular QIVPM $\bar{\mu}$ may be
+$\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
+some events $\events'$ and a particular QIVPM $\bar{\mu}$ may be
 \emph{empty}.

### 2017-08-14 prop_letter.tex
small things

@@
 orthonormal basis by diagonalization and complete it to a full
-orthonornal basis $\overline{\events_C}$. We then build a bijection
+orthonormal basis $\overline{\events_C}$. We then build a bijection
 between the QIVPM on the set of projectors associated with this basis

### 2017-08-15 prop_letter.tex
prop_letter.tex Add citations...

@@
 
-In the long version of this paper, we establish that QIVPMs become
-classical IVPMs when the space of events includes only mutually
+In the long version of this paper~\cite{HOSTunpublished}, we establish that
+QIVPMs become classical IVPMs when the space of events includes only mutually
 commuting events. The idea of the proof is as follows. Given a
@@
 \begin{thm}\label{thm:Shapley}
-  For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
-  of events~$\events_C\subseteq\events$ commutes, then
+  \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}~For a
+  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace of events~$\events_C\subseteq\events$ commutes, then
   $\coreBorn\left(\bar{\mu},\events_C\right)\ne\emptyset$.
@@
 \end{subequations}
-It is straightforward to verify that $\bar{\mu}$
-is a QIVPM. Now let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $.
-Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
-$\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-for any state~$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
-Hence, $\rho$ cannot be any state other than $\ket{2}$, the only
-pure state orthogonal to both $\ket{0}$ and $\ket{\ps}$, and it
-is easy to verify $\proj{2}$ is actually in $\coreBorn\left(\bar{\mu},S_{1}\right)$.
-Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We
-have $\coreBorn\left(\bar{\mu},S_{2}\right)=\left\{ \proj{1}\right\} $.
-Therefore, 
+It is straightforward to verify that $\bar{\mu}$ is a QIVPM. Then we will
+prove $\coreBorn\left(\bar{\mu},\events\right)$ is an empty set by
+contradiction. Suppose there is a
+state\nb$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
+for any\nb$P$, the state\nb$\rho$ must satisfy
 \begin{equation}
-\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},S_{1}\right)\cap\coreBorn\left(\bar{\mu},S_{2}\right)=\emptyset
+\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0
 \end{equation}
-Thus, there is no state that is consistent with the QIVPM on all projectors~$\events$,
-so Gleason's theorem does not hold for at least this example.
+which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
+for all $j$. However, the last equation never holds. 
+Thus, there is no state consistent with the QIVPM on all 
+projectors\nb$P\in\events$, so Gleason's theorem does not hold for at least this
+example.
 \end{example}

### 2017-08-15 prop_letter.tex
before KS

@@
 \newtheorem{thm}{Theorem}
-\newtheorem{lemma}[thm]{Lemma}
-\newtheorem{cor}[thm]{Corollary}
+\newtheorem{lemma}{Lemma}[thm]
+\newtheorem{cor}{Corollary}[thm]
 \theoremstyle{definition}
-\newtheorem{definition}[thm]{Definition}
-\newtheorem{example}[thm]{Example}
+\newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 outcomes~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+
 A fundamental question is how to address this controversy by
@@
 resources available for the realistic accuracy of an actual
-measurement.
-
-In this paper, we extend our previous work on the foundations of
-computability in quantum physics by exploring the application of
-interval-valued probability measures (IVPM) to achieving a coherent
-formulation of finite-resource quantum mechanics.  To this end, we
-develop a mathematical framework that includes the uncertainties of
-finite precision and imperfections in the quantum measurement
-process. In particular, we quantify the concept of imperfect quantum
-measurement and its impact on the interpretation of the Kochen-Specker
-and Gleason theorems and their implications for the foundations of
-quantum mechanics.  Our first observation is that essential objectives
-of our program to achieve a computable theory of quantum mechanics and
-finite-resource measurement, attempted previously with computable
-number systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be
-achievable by extending classical interval-valued probability
-measures~\cite{JamisonLodwick2004} to the quantum domain.  We thus
-begin by axiomatizing a quantum interval-valued probability measure
-(QIVPM) framework.
+measurement. In this paper, we extend our previous work on the
+foundations of computability in quantum physics by exploring the
+application of interval-valued probability measures (IVPMs) to
+achieving a coherent formulation of finite-resource quantum mechanics.
+To this end, we develop a mathematical framework that includes the
+uncertainties of finite precision and imperfections in the quantum
+measurement process. In particular, we quantify the concept of
+imperfect quantum measurement and its impact on the interpretation of
+the Kochen-Specker and Gleason theorems and their implications for the
+foundations of quantum mechanics.  Our first observation is that
+essential objectives of our program to achieve a computable theory of
+quantum mechanics and finite-resource measurement, attempted
+previously with computable number
+systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
+extending classical IVPMs~\cite{JamisonLodwick2004} to the quantum
+domain.  We thus begin by axiomatizing a quantum interval-valued
+probability measure (QIVPM) framework.
 
@@
 of a given measurement
-outcome~\citep{Born1983,peres1995quantum,544199}. The Gleason
-theorem establishes that there is no alternative to the Born rule by
+outcome~\citep{Born1983,peres1995quantum,544199}. The Gleason theorem
+establishes that there is no alternative to the Born rule by
 demonstrating, using reasonable continuity arguments in Hilbert spaces
@@
 a unique state~$\rho$ on all projectors defined on a Hilbert space
-of dimension $d\ge3$, there is a mathematically precise sense in which
-one recovers the original Gleason theorem asymptotically.
+$\Hilb$ of dimension $d\ge3$, there is a mathematically precise sense
+in which one recovers the original Gleason theorem asymptotically.
 Specifically, if for bounded resources the QIVPM is induced by some
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Fuzzy Measurements}
@@
 space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
-each event $P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
+each event~$P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
 probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$
@@
 
-\noindent A quantum probability measure can be easily constructed if
-one knows the current state of the quantum system by using the Born
-rule.  Specifically, for each pure normalized quantum state
-$\ket{\phi}$, the Born rule induces a probability measure
+\noindent A conventional quantum probability measure can be easily
+constructed if one knows the current state of the quantum system by
+using the Born rule.  Specifically, for each pure normalized quantum
+state $\ket{\phi}$, the Born rule induces a probability measure
 $\mu_{\phi}^{\mathrm{B}}$ defined as
@@
 $\mathbf{O}$ with spectral decomposition
-$\proj{0} + 2\,\proj{1} + 3\,\proj{2}$. Two fragments of valid
-probability measures $\mu_1$ and $\mu_2$ that can associated with this
-space are: $\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
+$\mathbf{O} = \proj{0} + 2\,\proj{1} + 3\,\proj{2}$. Two fragments of
+valid probability measures $\mu_1$ and $\mu_2$ that can be associated
+with this space are: $\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
 $\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0.5$,
@@
 $(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where in both cases
-$|\alpha|=1$. The expectation value of the observable in the first
-case is 1.5 and in the second it is 2.
+$|\alpha|=1$. The expectation value of the observable $\mathbf{O}$ in
+the first case is 1.5 and in the second it is 2.
 
@@
 infinitely precise measurements. In an actual experimental setup with
-an ensemble of quantum states that are not exactly identical, and with
-small imperfections and inaccuracies in measuring devices, an
-experimenter might only be able to determine that the probability of
-the event $\proj{0}$ is in the range $[0.49,0.51]$ instead of
-precisely 0.5. The spread in this range depends on the amount of
-resources (time, energy, money, etc.) that are devoted to the
-experiment. In the classical setting, this ``fuzziness'' can be
-formalized by moving to \emph{interval-valued probability measures},
-which we explore in the next section, along with our proposed
+an ensemble of quantum states that are not exactly identically
+prepared, and with small imperfections and inaccuracies in measuring
+devices, an experimenter might only be able to determine that the
+probability of the event $\proj{0}$ is in the range $[0.49,0.51]$
+instead of precisely 0.5. The spread in this range depends on the
+amount of resources (time, energy, money, etc.) that are devoted to
+the experiment. In the classical setting, this ``fuzziness'' can be
+formalized by moving to \emph{interval-valued probability measures}
+(IVPMs), which we explore in the next section, along with our proposed
 extension to the quantum domain.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Intervals of Uncertainty}
@@
 We now have the necessary ingredients to define the quantum extension,
-QIVPMs, as a generalization of both classical IVPMs and conventional
-quantum probability measures. We will show that QIVPMs reduce to
-classical IVPMs when the space of quantum events is restricted to
-mutually commuting sub-events, i.e., to compatible events that can be
-measured simultaneously.
+QIVPMs, as a generalization of both classical IVPMs and quantum
+probability measures. We will show that QIVPMs reduce to classical
+IVPMs when the space of quantum events is restricted to mutually
+commuting events, i.e., to compatible events that can be measured
+simultaneously.
 
@@
 Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
-direct counterpart of Eq.~(\ref{eq:classicalconvex}). Thus our
-definition of QIVPMs merges classical IVPMs with conventional quantum
-probability measures.
+direct counterpart of the convexity condition of
+Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
+classical IVPMs with quantum probability measures. In
+Sec.~\ref{sec:Gleason}, we will show that QIVPMs generalize
+conventional quantum probability measures in the limit where the
+endpoints of each interval coincide and this dense set of point
+intervals covers $[0,1]$.
 
-In Sec.~\ref{sec:Gleason}, we will show that QIVPMs generalize
-conventional quantum probability measures in the limit where each the
-lower and upper end of each interval coincide exactly and the
-intervals cover $[0,1]$. In this section, we will show that our
-definition of QIVPMs is consistent with classical IVPMs in the sense
-that a restriction of QIVPMs to commuting events recovers the
-definition of classical IVPMs.
-
-To formalize this connection between QIVPMs and classical IVPMs, we
-first note that in contrast to the case with conventional quantum
-probability spaces, there is generally no unique state $\rho$
-consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent
-with a state $\rho$ and projector $P$ if the interval $\bar{\mu}(P)$
-contains the exact probability calculated by the Born rule, i.e, if:
+In the remainder of this section, we will show that our definition of
+QIVPMs is consistent with classical IVPMs in the sense that a
+restriction of QIVPMs to commuting events recovers the definition of
+classical IVPMs. To formalize this connection between QIVPMs and
+classical IVPMs, we first note that in contrast to the case with
+conventional quantum probability spaces, there is generally no unique
+state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
+is consistent with a state $\rho$ and projector $P$ if the interval
+$\bar{\mu}(P)$ contains the exact probability calculated by the Born
+rule, i.e, if:
 \begin{equation}
@@
 where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
-is the probability that the event~$P$ happens determined by the Born
+is the probability that the event~$P$ is determined by the Born
 rule~\citep{Born1983,peres1995quantum,544199}.
@@
 subspaces of events as follows. A set of events $\events'$ is a
-\emph{subspace} if it contains $\mathbb{0}$ and $\mathbb{1}$ and is
+\emph{subspace} if it contains $\mathbb{0}$ and~$\mathbb{1}$ and is
 closed under complements and sums, i.e., for any
@@
 \begin{thm}\label{thm:Shapley}
-  \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}~For a
-  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace of events~$\events_C\subseteq\events$ commutes, then
+  For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
+  of events~$\events_C\subseteq\events$ commutes, then
   $\coreBorn\left(\bar{\mu},\events_C\right)\ne\emptyset$.
@@
 
-The theorem follows directly from our correspondence and Shapley's
-theorem that proves that a classical IVPM always contains at least one
-state that is consistent with every
-event~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}. As we will
+This theorem follows directly from our
+correspondence~\cite{HOSTunpublished} and Shapley's
+theorem~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}, which
+proves that a classical IVPM always contains at least one state $\rho$
+that is consistent with every event in $\events_C$. As we will
 illustrate in the next section, the set of states
 $\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
-some events $\events'$ and a particular QIVPM $\bar{\mu}$ may be
-\emph{empty}.
+some arbitrary (not necessarily commuting) events $\events'$ and a
+particular QIVPM $\bar{\mu}$ may be \emph{empty}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Kochen-Specker} 
@@
 
-Our first result is that a QIVPM is consistent with the inability to avoid
-uncertainty found in conventional infinite precise quantum
+Our first result is that a QIVPM is consistent with the inability to
+avoid uncertainty found in conventional infinite precise quantum
 mechanics~\cite{PeresRon1988,peres1995quantum}.
+
+The technical question is what happens if we relax the perfect
+measurement assumption that the intervals are precisely $[0,0]$ and
+$[1,1]$. We need to examine what happens if measurement imperfections
+occasionally cause an ideally impossible event to be detected or an
+ideally certain event not to be detected. Mermin argues in this case
+that:
+\begin{quote}
+  \ldots although the outcomes deduced from such imperfect
+  measurements will occasionally differ dramatically from those
+  allowed in the ideal case, if the misalignment is very slight, the
+  statistical distribution of outcomes will differ only slightly from
+  the ideal case~\citep{Mermin1999}.
+\end{quote}
+
+We can formally test this hypothesis by considering the notion of
+a $\delta$-deterministic QIVPM below.
+
+\begin{definition}\label{def:delta-deterministic}We define
+  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+  as $\delta$-deterministic if either
+  $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$ or
+  $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$ for any
+  $P\in\events$.\end{definition}
+
+As $\delta$ gets bigger, the QIVPM allows more and more indeterminate
+behavior. A $\frac{1}{3}$-deterministic QIVPM can be given by
+$\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
+onto an $x$-dimensional subspace of a three-dimensional Hilbert space.
+
+We now prove that for small enough $\delta$, the Kochen-Specker result is
+still valid, i.e., if the measurement imperfections are small enough,
+we cannot nullify the Kochen-Specker theorem as
+Meyer~\cite{PhysRevLett.83.3751} argued.
 
@@
 
-The question now is what happens if we relax the perfect measurement
-assumption that the intervals are precisely $[0,0]$ and
-$[1,1]$. We need to examine what happens if
-measurement imperfections occasionally cause an
-ideally impossible event to be detected or an ideally certain event
-not to be detected. Mermin argues in this case that:
-\begin{quote}
-  \ldots although the outcomes deduced from such imperfect
-  measurements will occasionally differ dramatically from those
-  allowed in the ideal case, if the misalignment is very slight, the
-  statistical distribution of outcomes will differ only slightly from
-  the ideal case~\citep{Mermin1999}.
-\end{quote}
-
-We can formally test this hypothesis by considering the notion of
-a $\delta$-deterministic QIVPM below.
-
-\begin{definition}\label{def:delta-deterministic}We define
-  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-  as $\delta$-deterministic if either
-  $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$ or
-  $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$ for any
-  $P\in\events$.\end{definition}
-
-As $\delta$ gets bigger, the QIVPM allows more and more indeterminate
-behavior. A $\frac{1}{3}$-deterministic QIVPM can be given by
-$\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
-onto an $x$-dimensional subspace of a three-dimensional Hilbert space.
-
-We now prove that for small enough $\delta$, the Kochen-Specker result is
-still valid, i.e., if the measurement imperfections are small enough,
-we cannot nullify the Kochen-Specker theorem as
-Meyer~\cite{PhysRevLett.83.3751} argued.
-
 \begin{thm}\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Gleason}
@@
 
-\begin{example}\label{ex:three-dimensional-three-value}
 Given a three-dimensional Hilbert space $\Hilb$ with an orthonormal
@@
 example.
-\end{example}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}

### 2017-08-15 prop_letter.tex
KS

@@
 
-The technical question is what happens if we relax the perfect
-measurement assumption that the intervals are precisely $[0,0]$ and
-$[1,1]$. We need to examine what happens if measurement imperfections
-occasionally cause an ideally impossible event to be detected or an
-ideally certain event not to be detected. Mermin argues in this case
-that:
+KS is formulated under the assumption that all observables for a QM
+system have definite values at all times. (cite)
+
+Our QIVPM framework allows us to reformulate KS by relaxing this
+assumption.
+
+This quantifies Mermin's argument:
+
 \begin{quote}
@@
 \end{quote}
+
+%%%%%
+\subsection{$\delta$-Determinism}
+
+The technical question is what happens if we relax the perfect
+measurement assumption that the intervals are precisely $[0,0]$ and
+$[1,1]$. We need to examine what happens if measurement imperfections
+occasionally cause an ideally impossible event to be detected or an
+ideally certain event not to be detected.
 
@@
 As $\delta$ gets bigger, the QIVPM allows more and more indeterminate
-behavior. A $\frac{1}{3}$-deterministic QIVPM can be given by
-$\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
-onto an $x$-dimensional subspace of a three-dimensional Hilbert space.
-
-We now prove that for small enough $\delta$, the Kochen-Specker result is
+behavior. We now prove that for small enough $\delta$, the Kochen-Specker result is
 still valid, i.e., if the measurement imperfections are small enough,
@@
 
-\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}
-  Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
-  0-deterministic
-  measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}
-  $.\end{thm}
-
-We will adapt the proof of the Kochen-Specker
-theorem~\cite{kochenspecker1967,
-  peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
-is, in general, impossible to have just the two intervals \imposs\ and
-\necess: every QIVPM must be parameterized by a collection of
-intervals that includes at least one additional ``fuzzy'' interval and
-some events must be associated with such uncertain intervals. The
-significance of this observation is that the uncertainty in the
-intervals is, in contrast to the classical case, \emph{a fundamental
-  part of quantum theory}. There are in fact two sources of
-uncertainty: one due to the finite measurement resources and one due
-to complementarity, which requires every quantum framework to be truly
-probabilistic.
-
-We will proceed by assuming a 0-deterministic QIVPM $\bar{\mu}$ and
-derive a contradiction using the following nine ``Mermin-Peres
-square''
-observables~$\mathbf{O}_{ij}$~\cite{Mermin1990Simple,peres1995quantum}:
-\begin{center}
-\begin{tabular}{|c|c|c|}
-\hline 
-$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
-\hline 
-$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
-\hline 
-$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
-\hline 
-\end{tabular}\,,
-\par\end{center}
-
-\noindent where $\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are
-Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. We now define the
-expectation value of the QIVPM for our Mermin-Peres square.
+%%%%%
+\subsection{Expectation Values of Fuzzy Observables}
 
@@
 
+%%%%%
+\subsection{Finite Precision KS}
+
+Statement of reformulated KS
+\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}
+  Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
+  0-deterministic
+  measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}
+  $.\end{thm}
+
+Proof of reformulated KS. We will proceed by assuming a 0-deterministic QIVPM $\bar{\mu}$ and
+derive a contradiction using the following nine ``Mermin-Peres
+square''
+observables~$\mathbf{O}_{ij}$~\cite{Mermin1990Simple,peres1995quantum}:
+{\renewcommand{\arraystretch}{2}%
+\begin{center}
+\begin{tabular}{|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|}
+\hline 
+$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
+\hline 
+$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
+\hline 
+$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
+\hline 
+\end{tabular}\,,
+\par\end{center}
+}
+
+\noindent where $\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are
+Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. We now define the
+expectation value of the QIVPM for our Mermin-Peres square.
+
 Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfies
@@
 Eq.~(\ref{eq:Kochen-Specker-Rules}).
+
+\paragraph*{Stronger KS: Main Result.}
+
+We will adapt the proof of the Kochen-Specker
+theorem~\cite{kochenspecker1967,
+  peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
+is, in general, impossible to have just the two intervals \imposs\ and
+\necess: every QIVPM must be parameterized by a collection of
+intervals that includes at least one additional ``fuzzy'' interval and
+some events must be associated with such uncertain intervals. The
+significance of this observation is that the uncertainty in the
+intervals is, in contrast to the classical case, \emph{a fundamental
+  part of quantum theory}. There are in fact two sources of
+uncertainty: one due to the finite measurement resources and one due
+to complementarity, which requires every quantum framework to be truly
+probabilistic.
 
@@
 \end{proof}
+
+%%%%%
+\subsection{HV}
+
+A $\frac{1}{3}$-deterministic QIVPM can be given by
+$\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
+onto an $x$-dimensional subspace of a three-dimensional Hilbert space.
 

### 2017-08-16 prop_letter.tex
some work on KS

--- 2017-08-15 prop_letter.tex
@@
 
-Our first result is that a QIVPM is consistent with the inability to
-avoid uncertainty found in conventional infinite precise quantum
-mechanics~\cite{PeresRon1988,peres1995quantum}.
-
-The technical question is what happens if we relax the perfect
-measurement assumption that the intervals are precisely $[0,0]$ and
-$[1,1]$. We need to examine what happens if measurement imperfections
-occasionally cause an ideally impossible event to be detected or an
-ideally certain event not to be detected. Mermin argues in this case
-that:
+Our generalization of quantum probability measures to QIVPMs will
+allow us to strengthen one of the fundamental theorems in of quantum
+information: the Kochen-Specker
+theorem~\cite{PeresRon1988,peres1995quantum}. Our stronger version of
+the theorem will suggest a resolution to the debate initiated by Meyer
+and Mermin on the relevance of the Kochen-Specker to experimental, and
+hence finite-precision, quantum
+measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+. Specifically, the original Kochen-Specker theorem is formulated
+under the assumption that all observables of a quantum mechanical
+system have \emph{definite values at all
+  times}~\cite{StanfordXXX}. Our interval-valued framework will allow
+us to state, and prove, a stronger version of the theorem that holds
+even if the observables have values that are only definite up to some
+specific parameter that quantifies experimental uncertainty. Put
+differently, our stronger statement and theorem quantifies Mermin's
+qualitative argument:
 \begin{quote}
@@
 
-We can formally test this hypothesis by considering the notion of
-a $\delta$-deterministic QIVPM below.
+\paragraph*{$\delta$-Determinism.} The first step in our formalization
+is to introduce a family of QIVPMs parameterized by an uncertainty
+$\delta$ which we call $\delta$-deterministic QIVPMs.
 
-\begin{definition}\label{def:delta-deterministic}We define
-  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-  as $\delta$-deterministic if either
+\begin{definition}\label{def:delta-deterministic} A
+  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is
+  $\delta$-deterministic if, for every event $P\in\events$, we have
+  that either 
   $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$ or
-  $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$ for any
-  $P\in\events$.\end{definition}
+  $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. 
+\end{definition}
 
-As $\delta$ gets bigger, the QIVPM allows more and more indeterminate
-behavior. A $\frac{1}{3}$-deterministic QIVPM can be given by
-$\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
-onto an $x$-dimensional subspace of a three-dimensional Hilbert space.
+When $\delta=0$ , every event must be assigned a probability in either
+the interval $[0,0]$ or $[1,1]$, i.e., every event is completely
+determined with certainty. As $\delta$ gets bigger, the QIVPM allows
+more and more indeterminate behavior. Our technical result will be
+that for ``small enough'' $\delta$, a variant of the Kochen-Specker
+theorem is still valid. To state and prove this result we will first
+reformulate the original Kochen-Specker as a statement regarding the
+non-existence of $0$-deterministic QIVPM. We will then strengthen this
+result to show the non-existence of any $\delta$-deterministic QIVPM
+when $\delta < 1/3$ and the Hilbert space dimension is greater than
+2.
 
-We now prove that for small enough $\delta$, the Kochen-Specker result is
-still valid, i.e., if the measurement imperfections are small enough,
-we cannot nullify the Kochen-Specker theorem as
-Meyer~\cite{PhysRevLett.83.3751} argued.
+\paragraph*{Expectation Values of Fuzzy Observables.}  Our following
+development will crucially rely on analyzing the expectation values of
+families of observables. We introduce the necessary definitions before
+stating and proving our variants of the Kochen-Specker theorem.
 
-\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}
-  Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
-  0-deterministic
-  measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}
-  $.\end{thm}
-
-We will adapt the proof of the Kochen-Specker
-theorem~\cite{kochenspecker1967,
-  peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
-is, in general, impossible to have just the two intervals \imposs\ and
-\necess: every QIVPM must be parameterized by a collection of
-intervals that includes at least one additional ``fuzzy'' interval and
-some events must be associated with such uncertain intervals. The
-significance of this observation is that the uncertainty in the
-intervals is, in contrast to the classical case, \emph{a fundamental
-  part of quantum theory}. There are in fact two sources of
-uncertainty: one due to the finite measurement resources and one due
-to complementarity, which requires every quantum framework to be truly
-probabilistic.
-
-We will proceed by assuming a 0-deterministic QIVPM $\bar{\mu}$ and
-derive a contradiction using the following nine ``Mermin-Peres
-square''
-observables~$\mathbf{O}_{ij}$~\cite{Mermin1990Simple,peres1995quantum}:
-\begin{center}
-\begin{tabular}{|c|c|c|}
-\hline 
-$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
-\hline 
-$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
-\hline 
-$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
-\hline 
-\end{tabular}\,,
-\par\end{center}
-
-\noindent where $\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are
-Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. We now define the
-expectation value of the QIVPM for our Mermin-Peres square.
-
-\begin{definition}Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
+\begin{definition} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
   for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, any
@@
 
+We now state and prove a theorem that is equivalent to the original
+Kochen-Specker theorem but that is formulated in terms of
+$0$-deterministic QIVPMs.
+
+\begin{thm}[0-deterministic variant of Kochen-Specker] 
+\label{thm:Kochen-Specker}
+Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
+0-deterministic
+measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}$.
+\end{thm}
+
+To prove this result, we proceed by assuming a 0-deterministic QIVPM
+$\bar{\mu}$ and derive a contradiction using the same nine observables
+$\mathbf{O}_{ij}$ used in the ``Mermin-Peres'' proof of the
+Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum}:
+{\renewcommand{\arraystretch}{2}%
+\begin{center}
+\begin{tabular}{|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|}
+\hline 
+$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
+\hline 
+$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
+\hline 
+$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
+\hline 
+\end{tabular}\,,
+\par\end{center}
+}
+\noindent where $\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are
+Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. We now define the
+expectation value of the QIVPM for our Mermin-Peres square.
+
 Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfies
@@
 Eq.~(\ref{eq:Kochen-Specker-Rules}).
+
+We will now adapt the proof above to show that it is, in general,
+impossible to have just the two intervals \imposs\ and \necess: every
+QIVPM must be parameterized by a collection of intervals that includes
+at least one additional ``fuzzy'' interval and some events must be
+associated with such uncertain intervals. The significance of this
+observation is that the uncertainty in the intervals is, in contrast
+to the classical case, \emph{a fundamental part of quantum
+  theory}. There are in fact two sources of uncertainty: one due to
+the finite measurement resources and one due to complementarity, which
+requires every quantum framework to be truly probabilistic.
+
+???~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
 
@@
 the Meyer-Mermin debate on the impact of finite precision on the
-Kochen-Specker theorem \cite{PhysRevLett.83.3751,Mermin1999}.
+Kochen-Specker theorem~\cite{PhysRevLett.83.3751,Mermin1999}.
 

### 2017-08-16 prop_letter.tex
From: Hanson, Andrew J. Sent: Tuesday, August 15, 2017 18:48 To: Tai, Yu-Tsung <yuttai@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: My version of section I
Hi all -
    I am afraid of messing things up, so I just took out a copy of the file, and then edited in a separate subfile -- here is what I came up with for a rephrasing of Section I, which is all I have time for now.  I tried to maintain as much as possible in unaltered lines to make  'xxdiff'  more relevant.
   Are we meeting again on Thursday, or when?

   -Andy

@@
 mechanics regarding the tension between finite precision measurement
-and contextuality~\cite{BarrettKent2004,Appleby_2005}, which refers
-to the fact that the results of measuring compatible sets of
-observables depend on whether they are measured together or
-separately.  For example, Meyer~\cite{PhysRevLett.83.3751} and
-Mermin~\cite{Mermin1999} disagree on whether finite-precision
+and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome
+of a theory that is contextual depends upon
+whether  compatible sets of observables are measured together or
+separately; a non-contextual theory gives the same results in either
+case.  A classic example of the varying opinions on the impact of
+imprecision is the disagreement between
+Meyer~\cite{PhysRevLett.83.3751} and 
+Mermin~\cite{Mermin1999}  on whether finite-precision
 measurements invalidate the spirit of the Kochen-Specker
-theorem~\cite{kochenspecker1967,peres1995quantum}, which is a
-mathematical statement about contextuality.  The Kochen-Specker
-theorem asserts that, in a Hilbert space of dimension $d \ge 3$, it is
+theorem~\cite{kochenspecker1967,peres1995quantum}.  The Kochen-Specker  
+theorem is in essence a
+mathematical statement about contextuality, asserting that
+in a Hilbert space of dimension $d \ge 3$, it is
 impossible to associate definite measured values, $\mu(P_i)= 0$ or
@@
 set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
-$\sum_i \mu(P_i) = 1$. In contrast, Meyer showed that one {\it can\/}
+$\sum_i \mu(P_i) = 1$.   Meyer showed that one {\it can\/}
 assign definite values $0$ or $1$ to the measurement outcome
@@
 that measurement outcomes must depend smoothly on slight changes in
-the experimental configuration. Mermin therefore claimed that the
+the experimental configuration, leading him to assert that the
 impact of Meyer's negative result is
-``unsupportable''~\citep{Mermin1999}.  Discussion has continued on
+``unsupportable''~\citep{Mermin1999}.  The question of
 whether contextuality is consistent with experimental
-outcomes~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+outcomes continues to be an active topic of discussion~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
-A fundamental question is how to address this controversy by
-developing mathematical theories of quantum mechanics that are
+The question of how to address this controversy is therefore a
+fundamental problem.  How does one
+develop mathematical theories of quantum mechanics that are
 intrinsically, rather than only implicitly, consistent with the
 resources available for the realistic accuracy of an actual
-measurement. In this paper, we extend our previous work on the
+measurement?   In this paper, we extend our previous work on the
 foundations of computability in quantum physics by exploring the
@@
 achieving a coherent formulation of finite-resource quantum mechanics.
-To this end, we develop a mathematical framework that includes the
+From this starting point, we develop a mathematical framework that includes the
 uncertainties of finite precision and imperfections in the quantum
-measurement process. In particular, we quantify the concept of
+measurement process.  In particular, we are able to quantify the concept of
 imperfect quantum measurement and its impact on the interpretation of
 the Kochen-Specker and Gleason theorems and their implications for the
-foundations of quantum mechanics.  Our first observation is that
+foundations of quantum mechanics.  We have reason to believe that
 essential objectives of our program to achieve a computable theory of
@@
 
-The effect of finite precision and imperfections on contextuality and
-the Kochen-Specker theorem is shown to have a resolution in terms of
-our QIVPM framework.  To proceed, we use a formulation of the
-``Mermin-Peres square''~\cite{peres1995quantum,Mermin1990Simple}
-that uses the expectation value of a physical observable with respect
-to a QIVPM, where the interval-valued expectation value is consistent
-with the expectation value of the same observable in conventional
-quantum mechanics with infinite resources. We show that, as long as
-errors and uncertainties remain smaller than a particular value, the
-Kochen-Specker theorem remains valid. In other words, we established a
-rigorous bound for its validity and, therefore, the limits for
-physical reality to remain contextual.
+A principal result is that recasting the Kochen-Specker theorem in
+terms of ``$\delta$-determinism'', with $\delta$ denoting a
+\emph{range} of outcomes, reducing to the purely deterministic
+Kochen-Specker case for $\delta=0$, can resolve the question of effect
+of finite precision and imperfections on contextuality.  A remarkable
+consequence of our analysis is that not only does the
+quantum-mechanical requirement for contextuality continue to hold,
+thus maintaining the Kochen-Specker result for a \emph{non-vanishing}
+range of $\delta$, but that at a \emph{certain fixed value} of
+$\delta$, there is a sharp transition, parallel in its consequences
+to, say, a phase transition, to \emph{non-contextuality}; that is,
+quantum mechanics suddenly fails to hold, and all variables can be
+specified simultaneously, turning the theory effectively into a
+classical theory that can be specified consistently by hidden
+variables.  These results provide a new insight into the
+Meyer-Mermin debate by presenting a theory in which there is a
+\emph{parameter} interpolating between what appeared previously to be
+irreconcilable interpretations of contextuality.
 
-A key aspect of a quantum measurement is its statistical nature, as
-reflected by application of the Born rule to determine the probability
-of a given measurement
-outcome~\citep{Born1983,peres1995quantum,544199}. The Gleason theorem
-establishes that there is no alternative to the Born rule by
+%   To proceed, we use a formulation of the
+% ``Mermin-Peres square''~\cite{peres1995quantum,Mermin1990Simple}
+% that uses the expectation value of a physical observable with respect
+% to a QIVPM, where the interval-valued expectation value is consistent
+% with the expectation value of the same observable in conventional
+% quantum mechanics with infinite resources. We show that, as long as
+% errors and uncertainties remain smaller than a particular value, the
+% Kochen-Specker theorem remains valid. In other words, we established a
+% rigorous bound for its validity and, therefore, the limits for
+% physical reality to remain contextual.
+
+We also investigate, though with less insight-generating results, the
+second key aspect of imprecise quantum measurement, which is its
+statistical nature as reflected in the application of the Born rule
+determining the probability of a given measurement
+outcome~\citep{Born1983,peres1995quantum,544199}.  Here, the Gleason
+theorem establishes that there is no alternative to the Born rule by
 demonstrating, using reasonable continuity arguments in Hilbert spaces
@@
 consistent with the statistical predictions computed from that
-rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  It is
-then legitimate to question what happens when infinite precision
-cannot be achieved. We will show that, if the effect of finite
-precision is incorporated, while a QIVPM might not be consistent with
-a unique state~$\rho$ on all projectors defined on a Hilbert space
+rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  Our
+question then concerns what happens when infinite precision cannot be
+achieved.  We are able to show that, while a QIVPM incorporating the
+effects of finite precision might not be consistent with Gleason's
+unique state~$\rho$ on all projectors defined on a Hilbert space
 $\Hilb$ of dimension $d\ge3$, there is a mathematically precise sense
 in which one recovers the original Gleason theorem asymptotically.
-Specifically, if for bounded resources the QIVPM is induced by some
-states~$\rho'$, those states will converge to a unique state $\rho$
-when the size of the intervals characterizing the uncertainties tends
-to zero.
+Specifically, if a set of QIVPMs representing bounded resources
+correspond individually to at least one state's~$\rho'$, those states
+will converge to a unique state $\rho$ when the size of the intervals
+characterizing the uncertainties tends to zero, and the set of
+single-point QIVPMs densely covers the entire real interval $[0,1]$.
 
@@
 interval valued probability in Sec.\ \ref{sec:Interval-Uncertainty}.
-This QIVPM will provide the mathematical framework to quantify the
+The QIVPM will provide the mathematical framework we need to quantify the
 impact of finite precision measurements on quantum mechanics.  For
@@
 under which the Kochen-Specker theorem applies.  This provides a way
-of resolving the Meyer-Mermin debate, which is the main result of our
+not only of resolving the Meyer-Mermin debate, but also revealing a
+precise transition to non-contextuality;  these are the results of our
 Thm~\ref{cor:Kochen-Specker-IVPM}.  In Sec.\ \ref{sec:Gleason}, we
@@
 bounded resources, holds asymptotically in a mathematically precise
-way.  Finally, we present our conclusions in
-Sec.~\ref{sec:Conclusion}.
+way.  Finally, we present our conclusions in Sec.~\ref{sec:Conclusion}.
 

### 2017-08-16 prop_letter.tex
prop_letter.tex Fix a citation...

@@
 system have \emph{definite values at all
-  times}~\cite{StanfordXXX}. Our interval-valued framework will allow
+  times}~\cite{Held2016}. Our interval-valued framework will allow
 us to state, and prove, a stronger version of the theorem that holds

### 2017-08-16 prop_letter.tex
prop_letter.tex Updated from Gerardo...

@@
 impact of Meyer's negative result is
-``unsupportable''~\citep{Mermin1999}.  The question of
+``unsupportable''~\citep{Mermin1999}.  The debate on
 whether contextuality is consistent with experimental
-outcomes continues to be an active topic of discussion~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
@@
 A principal result is that recasting the Kochen-Specker theorem in
-terms of ``$\delta$-determinism'', with $\delta$ denoting a
-\emph{range} of outcomes, reducing to the purely deterministic
+terms of ``$\delta$-determinism'', with $\delta$ 
+quantifying the effect of finite-precision uncertainties on measurement 
+outcomes, reducing to the purely deterministic
 Kochen-Specker case for $\delta=0$, can resolve the question of effect

### 2017-08-16 prop_letter.tex
prop_letter.tex After meeting...

@@
 \end{equation}
+Given an observable~$\mathbf{O}$ with spectral decomposition
+$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$ one can define the 
+expectation value of that observable as
+\begin{eqnarray}
+\langle \mathbf{O} \rangle_{\mu}=
+\sum_{i=1}^{N}\lambda_{i}\mu(P_{i}) .
+\end{eqnarray}
 
-\noindent A conventional quantum probability measure can be easily
+A conventional quantum probability measure can be easily
 constructed if one knows the current state of the quantum system by
@@
 first probability measure corresponds to the quantum system being in
-the pure state $(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second
+the pure state $\ket{\phi_1}=(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second
 corresponds to the quantum system being in the pure state
-$(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where in both cases
-$|\alpha|=1$. The expectation value of the observable $\mathbf{O}$ in
+$\ket{\phi_2}=(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where in both cases
+$|\alpha|=1$. The expectation value of the observable $\mathbf{O}$, 
+$\langle \mathbf{O} \rangle_{\mu_{1,2}}$,in
 the first case is 1.5 and in the second it is 2.
@@
 measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
-. Specifically, the original Kochen-Specker theorem is formulated
+Specifically, the original Kochen-Specker theorem is formulated
 under the assumption that all observables of a quantum mechanical
@@
 
-\begin{definition} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
-  for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, any
-  observable~$\mathbf{O}$ with spectral decomposition
-  $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, and the minimal
+\begin{thm} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
+  for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, and the minimal
   subspace of events $\events'$ containing
-  $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
+  $\left\{ P_{i}\right\} _{i=1}^{N}$, then
 \begin{equation}
@@
 \end{equation}
-\end{definition}
+\end{thm}
 
@@
 
-\begin{thm}[0-deterministic variant of Kochen-Specker] 
-\label{thm:Kochen-Specker}
+\begin{thm}
+\label{thm:Kochen-Specker} {\rm [0-deterministic variant of Kochen-Specker]}
 Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no

### 2017-08-16 prop_letter.tex
prop_letter.tex Update citations...

@@
 whether contextuality is consistent with experimental
-outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 

### 2017-08-17 prop_letter.tex
prop_letter.tex Updating expectation value...

@@
 expectation value of that observable as
-\begin{eqnarray}
-\langle \mathbf{O} \rangle_{\mu}=
-\sum_{i=1}^{N}\lambda_{i}\mu(P_{i}) .
-\end{eqnarray}
+\begin{equation}
+\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{N}\lambda_{i}\mu(P_{i})\,.
+\end{equation}
 
@@
 $|\alpha|=1$. The expectation value of the observable $\mathbf{O}$, 
-$\langle \mathbf{O} \rangle_{\mu_{1,2}}$,in
+$\expval{\mathbf{O}}_{\mu_{1,2}}$, in
 the first case is 1.5 and in the second it is 2.
@@
 $\mu(E_1\cap E_2) = 0$.
+
+The similar kind of subtleties happens when we want to define the
+expectation value of a random variable. Given a random variable
+\begin{equation}
+X\left(\omega\right)=\begin{cases}
+1 & \textrm{, if }\omega\in E\textrm{ ;}\\
+2 & \textrm{, if }\omega\notin E\textrm{ .}
+\end{cases}
+\end{equation}
+If we define its expectation value with respect to the IVPM~$\mu$defined
+in the previous paragraph naïvely, it would be\begin{subequations}
+\begin{eqnarray}
+1\cdot\mu(E)+2\cdot\mu(\overline{E}) & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
+ & = & [1\cdot0.2+2\cdot0.7,1\cdot0.3+2\cdot0.8]\\
+ & = & [1.6,1.9]\,.
+\end{eqnarray}
+\end{subequations}
 

### 2017-08-17 prop_letter.tex
prop_letter.tex Updating Expectation value...

@@
 \newcommand{\nb}{\nolinebreak[1] }
+\newcommand{\rmd}{\mathrm{d}}
 
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{N}\lambda_{i}\mu(P_{i})\,.
+\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{N}\lambda_{i}\mu(P_{i})\,.\label{eq:quantum-expectation}
 \end{equation}
@@
 Although these proposals differ in some details, they all share the
-fact that the probability $\mu(E)$ of an event~$E$ is generalized from
+fact that the probability $\bar{\mu}(E)$ of an event~$E$ is generalized from
 a single \emph{real number} to an \emph{interval}~$[\ell,r]$
@@
 event's complement.  For example, if we discover as a result of an
-experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$, we may
-conclude that $\mu(\overline{E}) = [0.7,0.8]$ for the complement event
+experiment that $\bar{\mu}(E) = [0.2,0.3]$ for some event~$E$, we may
+conclude that $\bar{\mu}(\overline{E}) = [0.7,0.8]$ for the complement event
 $\overline{E}$. In addition to these simple conditions, there are some
@@
 Let $E_1$ and $E_2$ be two disjoint events with probabilities
-$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
+$\bar{\mu}(E_1)=[\ell_1,r_1]$ and $\bar{\mu}(E_2)=[\ell_2,r_2]$. A first attempt
 at calculating the probability of the combined event that
 \emph{either} $E_1$ or $E_2$ occurs might be
-$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
-indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
-$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
-consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
-$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
+$\bar{\mu}(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
+indeed a sensible definition. For example, if $\bar{\mu}(E_1)=[0.1,0.2]$ and
+$\bar{\mu}(E_2)=[0.3,0.4]$ we get $\bar{\mu}(E_1\cup E_2) = [0.4,0.6]$. But
+consider an event $E$ such that $\bar{\mu}(E)=[0.2,0.3]$ and hence
+$\bar{\mu}(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
 are disjoint; the previous naïve way of combining the intervals would
-give $\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
+give $\bar{\mu}(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
 probability interval. Moreover the event $E\cup\overline{E}$ is the
@@
 the combined event than in each event separately. In our example, even
-though the true probability of $\mu(E)$ can be anywhere in the range
-$[0.2,0.3]$ and the true probability of $\mu(\overline{E})$ can be in
+though the true probability of {$\bar{\mu}(E)$}, $\mu(E)$, can be anywhere in the range
+$[0.2,0.3]$ and the true probability of {$\bar{\mu}(\overline{E})$}, $\mu(\overline{E})$, can be in
 anywhere in the range $[0.7,0.8]$, the values are not independent. Any
@@
 $E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
-$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
+$\bar{\mu}(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
 combination with the requirement for the identity event would force
-$\mu(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
-particular assignments of $\mu(E)$ or~$\mu(\overline{E})$.
+$\bar{\mu}(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
+particular assignments of $\bar{\mu}(E)$ or~$\bar{\mu}(\overline{E})$.
 
@@
 \begin{equation}
-\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
+\bar{\mu}(E_1\cup E_2) + \bar{\mu}(E_1\cap E_2) \subseteq \bar{\mu}(E_1) + \bar{\mu}(E_2)
 \label{eq:classicalconvex}
@@
 motivated condition when the events are disjoint, i.e., when
-$\mu(E_1\cap E_2) = 0$.
+$\bar{\mu}(E_1\cap E_2) = 0$.
 
@@
 \end{equation}
-If we define its expectation value with respect to the IVPM~$\mu$defined
+If we define its expectation value with respect to the IVPM~$\bar{\mu}$defined
 in the previous paragraph naïvely, it would be\begin{subequations}
 \begin{eqnarray}
-1\cdot\mu(E)+2\cdot\mu(\overline{E}) & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
+ &  & 1\cdot\bar{\mu}(E)+2\cdot\bar{\mu}(\overline{E})\\
+ & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
  & = & [1\cdot0.2+2\cdot0.7,1\cdot0.3+2\cdot0.8]\\
@@
 \end{eqnarray}
-\end{subequations}
+\end{subequations}However, if the true probability of {$\bar{\mu}(E)$},
+$\mu(E)$, is $0.2$, the expectation value with respect to $\mu$
+is 
+\begin{equation}
+1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.2+2\cdot0.8=1.8\,;
+\end{equation}
+if the true probability of {$\bar{\mu}(E)$}, $\mu(E)$, is $0.3$,
+the expectation value with respect to $\mu$ is
+\begin{equation}
+1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.3+2\cdot0.7=1.7\,.
+\end{equation}
+No matter what the true probability of {$\bar{\mu}(E)$ is the expectation
+value of it never reach $1.6$ and $1.9$ because the }naïve expectation
+value with respect to $\bar{\mu}$ combines impossible situation all
+together. Since a random variable may have more than two values, the
+realistic expectation value called the Choquet integral is much more
+complex than the naïve one~\citep{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
+
+\begin{definition}\label{def:Choquet}Consider a classical IVPM~$\bar{\mu}$
+such that $\mul:\events\rightarrow\left[0,1\right]$ and $\mur:\events\rightarrow\left[0,1\right]$
+are the left-end and the right-end of $\bar{\mu}$, respectively,
+i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
+We decompose a random variable~$X$ into step functions, but we separate
+the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
+where 
+\begin{equation}
+x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
+\end{equation}
+ and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
+are all disjoint. Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$
+and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
+where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
+Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
+\begin{equation}
+\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,.\label{eq:interval-expectation}
+\end{equation}
+\end{definition}
+
+The Choquet integral is actually what we desire. Consider the \emph{core}
+of $\bar{\mu}$ is the set 
+\begin{equation}
+\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,
+\end{equation}
+i.e., the set of real-value probability measure consistent with $\bar{\mu}$.
+According to Shapley's theorem~\citep{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
+the core of $\bar{\mu}$ is always non-empty, and we have the following
+theorem\nb\citep{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
+
+\begin{thm}\label{thm:Rosenmuller}For every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+and any random variable~$X:\Omega\rightarrow\mathbb{R}$, 
+\begin{equation}
+\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.
+\end{equation}
+\end{thm}
 
@@
 intervals covers $[0,1]$.
+
+After we defined QIVPM, we can merge the definition of quantum expectation
+value~(\ref{eq:quantum-expectation}) and the classical Choquet integral~(\ref{eq:interval-expectation})
+to the following definition.
+
+\begin{definition}Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
+for all $P\in\events$. This time, when we express the observable
+as its spectral decomposition
+\begin{equation}
+\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
+\end{equation}
+we separate the positive and negative eigenvalues and order its eigenvalues
+from the smallest to the largest 
+\begin{equation}
+\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
+\end{equation}
+Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
+where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
+Then, the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
+is defined as
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
+\end{equation}
+\end{definition}
 
@@
 
+Since Thm.~\ref{thm:Shapley} corresponds to classical Shapley's
+theorem, Thm.~\ref{thm:Rosenmuller} has its quantum counterpart.
+
+\begin{thm} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
+for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, and an
+observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition}),
+let $\events'$ be the minimal subspace of events containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$,
+then 
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
+\end{equation}
+\end{thm}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 stating and proving our variants of the Kochen-Specker theorem.
-
-\begin{thm} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
-  for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, and the minimal
-  subspace of events $\events'$ containing
-  $\left\{ P_{i}\right\} _{i=1}^{N}$, then
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
-\end{equation}
-\end{thm}
 

### 2017-08-17 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Classical expectation value updated...

@@
 The similar kind of subtleties happens when we want to define the
-expectation value of a random variable. Given a random variable
+expectation value of a random variable. Consider an event $E$ such
+that $\bar{\mu}(E)=[0.2,0.3]$ and $\bar{\mu}(\overline{E})=[0.7,0.8]$.
+Given a random variable
 \begin{equation}
@@
 1 & \textrm{, if }\omega\in E\textrm{ ;}\\
-2 & \textrm{, if }\omega\notin E\textrm{ .}
+2 & \textrm{, if }\omega\notin E\textrm{ ,}
 \end{cases}
 \end{equation}
-If we define its expectation value with respect to the IVPM~$\bar{\mu}$defined
-in the previous paragraph naïvely, it would be\begin{subequations}
+its expectation value with respect to $\bar{\mu}$ might naïvely be
+defined as\begin{subequations}
 \begin{eqnarray}
@@
 \end{eqnarray}
-\end{subequations}However, if the true probability of {$\bar{\mu}(E)$},
-$\mu(E)$, is $0.2$, the expectation value with respect to $\mu$
-is 
+\end{subequations}As we discussed in the previous paragraph, the
+true probability of $\bar{\mu}(E)$, $\mu(E)$, can be anywhere in
+the range $[0.2,0.3]$ and the true probability of $\bar{\mu}(\overline{E})$,
+$\mu(\overline{E})$, is $1-\mu(E)$. If $\mu(E)=0.2$, the expectation
+value with respect to $\mu$ is 
 \begin{equation}
@@
 \end{equation}
-if the true probability of {$\bar{\mu}(E)$}, $\mu(E)$, is $0.3$,
-the expectation value with respect to $\mu$ is
+if $\mu(E)=0.3$, the expectation value with respect to $\mu$ is
 \begin{equation}
@@
 \end{equation}
-No matter what the true probability of {$\bar{\mu}(E)$ is the expectation
-value of it never reach $1.6$ and $1.9$ because the }naïve expectation
-value with respect to $\bar{\mu}$ combines impossible situation all
-together. Since a random variable may have more than two values, the
-realistic expectation value called the Choquet integral is much more
-complex than the naïve one~\citep{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
+In another word, no matter how we pick $\mu(E)$, its expectation
+value ranges in $\left[1.7,1.8\right]$ which is narrower than the
+naïve expectation value~$[1.6,1.9]$ because the naïve one combines
+contradicting situations in the computation. In general, the realistic
+expectation value, called the Choquet integral, is more complex than
+what we discussed as a random variable may have more than two values.
+Despite its complexity, it is still a weight average among the values
+of a random variable as in Def.~\ref{def:Choquet}. After we formulate
+the idea of the ``true'' probability measure of an IVPM~$\bar{\mu}$
+as 
+\begin{equation}
+\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,\label{eq:core}
+\end{equation}
+Thm.~\ref{thm:Rosenmuller} claims the expectation value of $\bar{\mu}$
+is the range of the expectation value of the probability measure in
+the core of $\bar{\mu}$, which was intuitively discussed in the previous
+example.
 
-\begin{definition}\label{def:Choquet}Consider a classical IVPM~$\bar{\mu}$
-such that $\mul:\events\rightarrow\left[0,1\right]$ and $\mur:\events\rightarrow\left[0,1\right]$
-are the left-end and the right-end of $\bar{\mu}$, respectively,
-i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
+\begin{definition}[Choquet integral~\citep{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}Consider
+a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
 We decompose a random variable~$X$ into step functions, but we separate
@@
 
-The Choquet integral is actually what we desire. Consider the \emph{core}
-of $\bar{\mu}$ is the set 
-\begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,
-\end{equation}
-i.e., the set of real-value probability measure consistent with $\bar{\mu}$.
-According to Shapley's theorem~\citep{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
-the core of $\bar{\mu}$ is always non-empty, and we have the following
-theorem\nb\citep{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
-
-\begin{thm}\label{thm:Rosenmuller}For every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-and any random variable~$X:\Omega\rightarrow\mathbb{R}$, 
+\begin{thm}\label{thm:Rosenmuller}\citep{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}~For
+every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
+any random variable~$X:\Omega\rightarrow\mathbb{R}$, 
 \begin{equation}
@@
 
-\begin{thm}[Shapley~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}]\label{thm:Shapley}
+\begin{thm}[Shapley~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}]
   For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace

### 2017-08-18 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Classical expectation value updating...

@@
 \end{equation}
-its expectation value with respect to $\bar{\mu}$ might naïvely be
+its expectation value with respect to $\bar{\mu}$ might be naïvely
 defined as\begin{subequations}
@@
 true probability of $\bar{\mu}(E)$, $\mu(E)$, can be anywhere in
-the range $[0.2,0.3]$ and the true probability of $\bar{\mu}(\overline{E})$,
-$\mu(\overline{E})$, is $1-\mu(E)$. If $\mu(E)=0.2$, the expectation
-value with respect to $\mu$ is 
+the range $[0.2,0.3]$ and the true probability of $\bar{\mu}(\overline{E})$
+is $\mu(\overline{E})=1-\mu(E)$. If $\mu(E)=0.2$, the expectation
+value of $X$ with respect to $\mu$ is 
 \begin{equation}
@@
 \end{equation}
-if $\mu(E)=0.3$, the expectation value with respect to $\mu$ is
+if $\mu(E)=0.3$, the expectation value of $X$ with respect to $\mu$
+is
 \begin{equation}
@@
 \end{equation}
-In another word, no matter how we pick $\mu(E)$, its expectation
-value ranges in $\left[1.7,1.8\right]$ which is narrower than the
-naïve expectation value~$[1.6,1.9]$ because the naïve one combines
-contradicting situations in the computation. In general, the realistic
-expectation value, called the Choquet integral, is more complex than
-what we discussed as a random variable may have more than two values.
-Despite its complexity, it is still a weight average among the values
-of a random variable as in Def.~\ref{def:Choquet}. After we formulate
-the idea of the ``true'' probability measure of an IVPM~$\bar{\mu}$
-as 
-\begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,\label{eq:core}
-\end{equation}
-Thm.~\ref{thm:Rosenmuller} claims the expectation value of $\bar{\mu}$
-is the range of the expectation value of the probability measure in
-the core of $\bar{\mu}$, which was intuitively discussed in the previous
-example.
+In another word, no matter how we pick $\mu(E)$, the expectation
+value of $X$ is in $\left[1.7,1.8\right]$ which is a more realistic
+expectation value of $X$ with respect to $\bar{\mu}$. The interval~$\left[1.7,1.8\right]$
+is narrower than the naïve expectation value~$[1.6,1.9]$ because
+the naïve one combines contradicting situations in the computation.
+In general, the computation of the realistic expectation value, called
+the Choquet integral, is more complex than what we discussed because
+a random variable may have more than two values. Despite its complexity,
+it is still a weight average among the values of a random variable
+as given in the following definition.
 
@@
 We decompose a random variable~$X$ into step functions, but we separate
-the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
-where 
+the positive and negative terms and write like
+\begin{equation}
+X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\mathbf{1}_{E_{i}^{s}}\,,
+\end{equation}
+where $\mathbf{1}_{E_{i}^{s}}$ is the indicator function of $E_{i}^{s}$,
+and we order the value of its range from the smallest to the largest
 \begin{equation}
@@
 \end{definition}
+
+Although Def.~\ref{def:Choquet} looks complex, it matches with our
+intuition in the previous example. Let
+\begin{equation}
+\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,\label{eq:core}
+\end{equation}
+be the set of possible ``true'' probability measure of an IVPM~$\bar{\mu}$.
+Then, the following theorem claims the expectation value of $\bar{\mu}$
+is the range of the expectation value of the probability measure in
+the core of $\bar{\mu}$.
 

### 2017-08-18 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Quantum Expectation Value updated...

@@
 
-After we defined QIVPM, we can merge the definition of quantum expectation
-value~(\ref{eq:quantum-expectation}) and the classical Choquet integral~(\ref{eq:interval-expectation})
-to the following definition.
+After we defined QIVPMs, we can easily define the expectation value
+of an observable with respect to a QIVPM by adopting the idea of the
+classical Choquet integral. Notice that the quantum expectation value~(\ref{eq:quantum-expectation})
+is the weight average among the eigenvalues with the weight~$\mu(P_{i})$.
+Similarly, given a classical random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
+the expectation value of $X$ with respect to a probability measure~$\mu$
+is the weight average among $x_{i}$ with the weight~$\mu(E_{i})$.
+Since the definition of Choquet integral is just using a more complex
+but reasonable way to compute the weight, we can apply the same algorithm
+on an observable and get the following definition.
 

### 2017-08-18 prop_letter.tex
prop_letter.tex \newcommand{\nb}{\nolinebreak[1]\ }
expectation values

@@
 % Hence, it will not hyphenate too much surrounding words.
-\newcommand{\nb}{\nolinebreak[1] }
+\newcommand{\nb}{\nolinebreak[1]\ }
 \newcommand{\rmd}{\mathrm{d}}
@@
 
-%   To proceed, we use a formulation of the
-% ``Mermin-Peres square''~\cite{peres1995quantum,Mermin1990Simple}
-% that uses the expectation value of a physical observable with respect
-% to a QIVPM, where the interval-valued expectation value is consistent
-% with the expectation value of the same observable in conventional
-% quantum mechanics with infinite resources. We show that, as long as
-% errors and uncertainties remain smaller than a particular value, the
-% Kochen-Specker theorem remains valid. In other words, we established a
-% rigorous bound for its validity and, therefore, the limits for
-% physical reality to remain contextual.
-
 We also investigate, though with less insight-generating results, the
@@
 $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$ one can define the 
-expectation value of that observable as
+expectation value of that observable as:
 \begin{equation}
@@
 using the Born rule.  Specifically, for each pure normalized quantum
-state $\ket{\phi}$, the Born rule induces a probability measure
+state~$\ket{\phi}$, the Born rule induces a probability measure
 $\mu_{\phi}^{\mathrm{B}}$ defined as
@@
 first probability measure corresponds to the quantum system being in
-the pure state $\ket{\phi_1}=(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second
-corresponds to the quantum system being in the pure state
+the pure state $\ket{\phi_1}=(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the
+second corresponds to the quantum system being in the pure state
 $\ket{\phi_2}=(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where in both cases
-$|\alpha|=1$. The expectation value of the observable $\mathbf{O}$, 
-$\expval{\mathbf{O}}_{\mu_{1,2}}$, in
-the first case is 1.5 and in the second it is 2.
+$|\alpha|=1$. The expectation values of the observable $\mathbf{O}$,
+$\expval{\mathbf{O}}_{\mu_{1,2}}$, are 1.5 in the first case is 1.5
+and 2 in the second.
 
@@
 
-The similar kind of subtleties happens when we want to define the
-expectation value of a random variable. Consider an event $E$ such
-that $\bar{\mu}(E)=[0.2,0.3]$ and $\bar{\mu}(\overline{E})=[0.7,0.8]$.
-Given a random variable
-\begin{equation}
-X\left(\omega\right)=\begin{cases}
-1 & \textrm{, if }\omega\in E\textrm{ ;}\\
-2 & \textrm{, if }\omega\notin E\textrm{ ,}
-\end{cases}
-\end{equation}
-its expectation value with respect to $\bar{\mu}$ might be naïvely
-defined as\begin{subequations}
-\begin{eqnarray}
- &  & 1\cdot\bar{\mu}(E)+2\cdot\bar{\mu}(\overline{E})\\
- & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
- & = & [1\cdot0.2+2\cdot0.7,1\cdot0.3+2\cdot0.8]\\
- & = & [1.6,1.9]\,.
-\end{eqnarray}
-\end{subequations}As we discussed in the previous paragraph, the
-true probability of $\bar{\mu}(E)$, $\mu(E)$, can be anywhere in
-the range $[0.2,0.3]$ and the true probability of $\bar{\mu}(\overline{E})$
-is $\mu(\overline{E})=1-\mu(E)$. If $\mu(E)=0.2$, the expectation
-value of $X$ with respect to $\mu$ is 
-\begin{equation}
-1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.2+2\cdot0.8=1.8\,;
-\end{equation}
-if $\mu(E)=0.3$, the expectation value of $X$ with respect to $\mu$
-is
-\begin{equation}
-1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.3+2\cdot0.7=1.7\,.
-\end{equation}
-In another word, no matter how we pick $\mu(E)$, the expectation
-value of $X$ is in $\left[1.7,1.8\right]$ which is a more realistic
-expectation value of $X$ with respect to $\bar{\mu}$. The interval~$\left[1.7,1.8\right]$
-is narrower than the naïve expectation value~$[1.6,1.9]$ because
-the naïve one combines contradicting situations in the computation.
-In general, the computation of the realistic expectation value, called
-the Choquet integral, is more complex than what we discussed because
-a random variable may have more than two values. Despite its complexity,
-it is still a weight average among the values of a random variable
-as given in the following definition.
-
-\begin{definition}[Choquet integral~\citep{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}Consider
-a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
-and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
-We decompose a random variable~$X$ into step functions, but we separate
-the positive and negative terms and write like
-\begin{equation}
-X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\mathbf{1}_{E_{i}^{s}}\,,
-\end{equation}
-where $\mathbf{1}_{E_{i}^{s}}$ is the indicator function of $E_{i}^{s}$,
-and we order the value of its range from the smallest to the largest
-\begin{equation}
-x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
-\end{equation}
- and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
-are all disjoint. Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$
-and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
-\begin{equation}
-\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,.\label{eq:interval-expectation}
-\end{equation}
-\end{definition}
-
-Although Def.~\ref{def:Choquet} looks complex, it matches with our
-intuition in the previous example. Let
-\begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,\label{eq:core}
-\end{equation}
-be the set of possible ``true'' probability measure of an IVPM~$\bar{\mu}$.
-Then, the following theorem claims the expectation value of $\bar{\mu}$
-is the range of the expectation value of the probability measure in
-the core of $\bar{\mu}$.
-
-\begin{thm}\label{thm:Rosenmuller}\citep{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}~For
-every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
-any random variable~$X:\Omega\rightarrow\mathbb{R}$, 
-\begin{equation}
-\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.
-\end{equation}
-\end{thm}
-
 We now have the necessary ingredients to define the quantum extension,
@@
 
-After we defined QIVPMs, we can easily define the expectation value
-of an observable with respect to a QIVPM by adopting the idea of the
-classical Choquet integral. Notice that the quantum expectation value~(\ref{eq:quantum-expectation})
-is the weight average among the eigenvalues with the weight~$\mu(P_{i})$.
-Similarly, given a classical random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
-the expectation value of $X$ with respect to a probability measure~$\mu$
-is the weight average among $x_{i}$ with the weight~$\mu(E_{i})$.
-Since the definition of Choquet integral is just using a more complex
-but reasonable way to compute the weight, we can apply the same algorithm
-on an observable and get the following definition.
-
-\begin{definition}Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
-and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
-for all $P\in\events$. This time, when we express the observable
-as its spectral decomposition
-\begin{equation}
-\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
-\end{equation}
-we separate the positive and negative eigenvalues and order its eigenvalues
-from the smallest to the largest 
-\begin{equation}
-\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
-\end{equation}
-Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-Then, the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
-is defined as
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
-\end{equation}
-\end{definition}
-
 In the remainder of this section, we will show that our definition of
@@
 state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
-is consistent with a state $\rho$ and projector $P$ if the interval
+is consistent with a state $\rho$ and projector~$P$ if the interval
 $\bar{\mu}(P)$ contains the exact probability calculated by the Born
@@
 \begin{thm}\label{thm:Shapley}
-  For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
+  For QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
   of events~$\events_C\subseteq\events$ commutes, then
@@
 
-Since Thm.~\ref{thm:Shapley} corresponds to classical Shapley's
-theorem, Thm.~\ref{thm:Rosenmuller} has its quantum counterpart.
-
-\begin{thm} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
-for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, and an
-observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition}),
-let $\events'$ be the minimal subspace of events containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$,
-then 
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
-\end{equation}
-\end{thm}
+In conventional quantum mechanics the expectation value of an
+observable is defined in Eq.~\ref{eq:quantum-expectation} as a precise
+real number. The generalization of quantum measures to QIVPMs implies
+that the real-valued expectation value will be generalized to an
+interval.
+
+\begin{definition}[Expectation Value of Observables over QIVPMs] Let
+  $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space of
+  dimension~$d\ge3$ with event space $\events$; and $\mathbf{O}$ an
+  observable with spectral decomposition
+  $\Sigma_{i=1}^N \lambda_iP_i$. Let $\events'$ be the minimal
+  subspace of events containing all the projectors $P_i$, then we define:
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
+\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
+\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,.\label{eq:quantum-interval-expectation-core}
+\end{equation}
+\end{definition}
+
+If $\bar{\mu}$ is a conventional (Born) probability measure defined by
+state $\rho$, then $\coreBorn\left(\bar{\mu},\events'\right)$ will
+contain the singleton state $\rho$ and both endpoints of the interval
+will agree, thus reducing the definition to that of
+Eq.~\ref{eq:quantum-expectation}. We also note that, when restricted
+to commuting projectors, the definition above is consistent with the
+classical notion of the \emph{Choquet
+  integral}~\cite{GilboaSchmeidler1994,Grabisch2016} which is used to
+calculate the expectation value of random variables as a weighted
+average.
 
@@
 \end{document}
+
+The similar kind of subtleties happens when we want to define the
+expectation value of a random variable. Consider an event $E$ such
+that $\bar{\mu}(E)=[0.2,0.3]$ and $\bar{\mu}(\overline{E})=[0.7,0.8]$.
+Given a random variable
+\begin{equation}
+X\left(\omega\right)=\begin{cases}
+1 & \textrm{, if }\omega\in E\textrm{ ;}\\
+2 & \textrm{, if }\omega\notin E\textrm{ ,}
+\end{cases}
+\end{equation}
+its expectation value with respect to $\bar{\mu}$ might be naïvely
+defined as\begin{subequations}
+\begin{eqnarray}
+ &  & 1\cdot\bar{\mu}(E)+2\cdot\bar{\mu}(\overline{E})\\
+ & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
+ & = & [1\cdot0.2+2\cdot0.7,1\cdot0.3+2\cdot0.8]\\
+ & = & [1.6,1.9]\,.
+\end{eqnarray}
+\end{subequations}As we discussed in the previous paragraph, the
+true probability of $\bar{\mu}(E)$, $\mu(E)$, can be anywhere in
+the range $[0.2,0.3]$ and the true probability of $\bar{\mu}(\overline{E})$
+is $\mu(\overline{E})=1-\mu(E)$. If $\mu(E)=0.2$, the expectation
+value of $X$ with respect to $\mu$ is 
+\begin{equation}
+1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.2+2\cdot0.8=1.8\,;
+\end{equation}
+if $\mu(E)=0.3$, the expectation value of $X$ with respect to $\mu$
+is
+\begin{equation}
+1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.3+2\cdot0.7=1.7\,.
+\end{equation}
+In another word, no matter how we pick $\mu(E)$, the expectation
+value of $X$ is in $\left[1.7,1.8\right]$ which is a more realistic
+expectation value of $X$ with respect to $\bar{\mu}$. The interval~$\left[1.7,1.8\right]$
+is narrower than the naïve expectation value~$[1.6,1.9]$ because
+the naïve one combines contradicting situations in the computation.
+In general, the computation of the realistic expectation value, called
+the Choquet integral, is more complex than what we discussed because
+a random variable may have more than two values. Despite its complexity,
+it is still a weight average among the values of a random variable
+as given in the following definition.
+
+\begin{definition}[Choquet integral~\citep{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}Consider
+a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
+We decompose a random variable~$X$ into step functions, but we separate
+the positive and negative terms and write like
+\begin{equation}
+X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\mathbf{1}_{E_{i}^{s}}\,,
+\end{equation}
+where $\mathbf{1}_{E_{i}^{s}}$ is the indicator function of $E_{i}^{s}$,
+and we order the value of its range from the smallest to the largest
+\begin{equation}
+x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
+\end{equation}
+ and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
+are all disjoint. Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$
+and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
+where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
+Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
+\begin{equation}
+\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,.\label{eq:interval-expectation}
+\end{equation}
+\end{definition}
+
+Although Def.~\ref{def:Choquet} looks complex, it matches with our
+intuition in the previous example. Let
+\begin{equation}
+\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,\label{eq:core}
+\end{equation}
+be the set of possible ``true'' probability measure of an IVPM~$\bar{\mu}$.
+Then, the following theorem claims the expectation value of $\bar{\mu}$
+is the range of the expectation value of the probability measure in
+the core of $\bar{\mu}$.
+
+\begin{thm}\label{thm:Rosenmuller}\citep{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}~For
+every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
+any random variable~$X:\Omega\rightarrow\mathbb{R}$, 
+\begin{equation}
+\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.
+\end{equation}
+\end{thm}
+
+%   To proceed, we use a formulation of the
+% ``Mermin-Peres square''~\cite{peres1995quantum,Mermin1990Simple}
+% that uses the expectation value of a physical observable with respect
+% to a QIVPM, where the interval-valued expectation value is consistent
+% with the expectation value of the same observable in conventional
+% quantum mechanics with infinite resources. We show that, as long as
+% errors and uncertainties remain smaller than a particular value, the
+% Kochen-Specker theorem remains valid. In other words, we established a
+% rigorous bound for its validity and, therefore, the limits for
+% physical reality to remain contextual.
+
+% \begin{thm} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
+% for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, and an
+% observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition}),
+% let $\events'$ be the minimal subspace of events containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$,
+% then 
+% \begin{equation}
+% \expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
+% \end{equation}
+% \end{thm}
+
+After we defined QIVPMs, we can easily define the expectation value
+of an observable with respect to a QIVPM by adopting the idea of the
+classical Choquet integral. Notice that the quantum expectation value~(\ref{eq:quantum-expectation})
+is the weight average among the eigenvalues with the weight~$\mu(P_{i})$.
+Similarly, given a classical random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
+the expectation value of $X$ with respect to a probability measure~$\mu$
+is the weight average among $x_{i}$ with the weight~$\mu(E_{i})$.
+Since the definition of Choquet integral is just using a more complex
+but reasonable way to compute the weight, we can apply the same algorithm
+on an observable and get the following definition.
+
+\begin{definition}Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
+the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
+for all $P\in\events$. This time, when we express the observable
+as its spectral decomposition
+\begin{equation}
+\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
+\end{equation}
+we separate the positive and negative eigenvalues and order its eigenvalues
+from the smallest to the largest 
+\begin{equation}
+\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
+\end{equation}
+Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
+where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
+Then, the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
+is defined as
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
+\end{equation}
+\end{definition}

### 2017-08-18 prop_letter.tex
prop_letter.tex \section{Kochen-Specker}  Change N to M...
lots of small changes

@@
 
-The paper is organized as follows.  In Sec.\ \ref{sec:fuzzy} we begin
+The paper is organized as follows.  In Sec.~\ref{sec:fuzzy} we begin
 by introducing the foundations of quantum probability space and fuzzy
 measurement.  We then move on to introduce the concept of quantum
-interval valued probability in Sec.\ \ref{sec:Interval-Uncertainty}.
+interval valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
 The QIVPM will provide the mathematical framework we need to quantify the
 impact of finite precision measurements on quantum mechanics.  For
-instance, in Sec.\ \ref{sec:Kochen-Specker}, we quantify the domain of
+instance, in Sec.~\ref{sec:Kochen-Specker}, we quantify the domain of
 validity of a contextual measurement, thus addressing the conditions
@@
 precise transition to non-contextuality;  these are the results of our
-Thm~\ref{cor:Kochen-Specker-IVPM}.  In Sec.\ \ref{sec:Gleason}, we
+Thm~\ref{cor:Kochen-Specker-IVPM}.  In Sec.~\ref{sec:Gleason}, we
 study Gleason's theorem in the context of imprecise measurements,
@@
 quantum case, the events of interest are specified by \emph{projection
-  operators} $P$. These include the empty projector~$\mathbb{0}$,
-the identity projector~$\mathbb{1}$, projectors of the form
-$\proj{\phi}$ where $\ket{\phi}$ is a pure quantum state (an element
-of a Hilbert space), sums of \emph{orthogonal} projectors $P_0$
-and~$P_1$ with $P_0P_1=\mathbb{0}$, and products of \emph{commuting}
-projectors $P_0$ and~$P_1$ with $P_0P_1=P_1P_0$. In a well-defined
-quantum probability
+  operators} $P$. These include the empty projector~$\mathbb{0}$, the
+identity projector~$\mathbb{1}$, projectors of the form $\proj{\phi}$
+where $\ket{\phi}$ is a pure quantum state (an element of a Hilbert
+space), sums of \emph{orthogonal} projectors $P_0$ and~$P_1$ with
+$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projectors $P_0$
+and~$P_1$ with $P_0P_1=P_1P_0$. In a quantum probability
 space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
 each event~$P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
-probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$
-is the set of all projectors on a given Hilbert space, subject to the
+probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$ is
+the set of all projectors on a given Hilbert space, subject to the
 following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
@@
 \end{equation}
-Given an observable~$\mathbf{O}$ with spectral decomposition
-$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$ one can define the 
-expectation value of that observable as:
+Given a probability for every projector, we can associate an
+expectation value with an observable~$\mathbf{O}$ with spectral
+decomposition $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$ as:
 \begin{equation}
@@
 $\mu_{\phi}^{\mathrm{B}}$ defined as
-$\mu_{\phi}^{\mathrm{B}}(P)=\ip{\phi}{P\phi}$. The situation
+$\mu_{\phi}^{\mathrm{B}}(P)=\ip{\phi}{P\vert\phi}$. The situation
 generalizes to mixed states
@@
 Although these proposals differ in some details, they all share the
-fact that the probability $\bar{\mu}(E)$ of an event~$E$ is generalized from
+fact that the probability $\mu(E)$ of an event~$E$ is generalized from
 a single \emph{real number} to an \emph{interval}~$[\ell,r]$
@@
 interval $[1-r,1-\ell]$ so that if one interval refers to the
-probability of an event, the other refers to the probability of the
-event's complement.  For example, if we discover as a result of an
-experiment that $\bar{\mu}(E) = [0.2,0.3]$ for some event~$E$, we may
-conclude that $\bar{\mu}(\overline{E}) = [0.7,0.8]$ for the complement event
-$\overline{E}$. In addition to these simple conditions, there are some
-subtle conditions on how intervals are combined, which we discuss
-next.
+probability of an event $E$, the other refers to the probability of
+the event's complement $\overline{E}$.  For example, if we discover as
+a result of an experiment that $\mu(E) = [0.2,0.3]$ for some
+event~$E$, we may conclude that $\mu(\overline{E}) = [0.7,0.8]$ for
+the complement event $\overline{E}$. In addition to these simple
+conditions, there are some subtle conditions on how intervals are
+combined, which we discuss next.
 
 Let $E_1$ and $E_2$ be two disjoint events with probabilities
-$\bar{\mu}(E_1)=[\ell_1,r_1]$ and $\bar{\mu}(E_2)=[\ell_2,r_2]$. A first attempt
+$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
 at calculating the probability of the combined event that
 \emph{either} $E_1$ or $E_2$ occurs might be
-$\bar{\mu}(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
-indeed a sensible definition. For example, if $\bar{\mu}(E_1)=[0.1,0.2]$ and
-$\bar{\mu}(E_2)=[0.3,0.4]$ we get $\bar{\mu}(E_1\cup E_2) = [0.4,0.6]$. But
-consider an event $E$ such that $\bar{\mu}(E)=[0.2,0.3]$ and hence
-$\bar{\mu}(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
+$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
+indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
+$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
+consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
+$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
 are disjoint; the previous naïve way of combining the intervals would
-give $\bar{\mu}(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
+give $\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
 probability interval. Moreover the event $E\cup\overline{E}$ is the
@@
 the combined event than in each event separately. In our example, even
-though the true probability of {$\bar{\mu}(E)$}, $\mu(E)$, can be anywhere in the range
-$[0.2,0.3]$ and the true probability of {$\bar{\mu}(\overline{E})$}, $\mu(\overline{E})$, can be in
+though the ``true'' probability of $E$ can be anywhere in the range
+$[0.2,0.3]$ and the ``true'' probability of $\overline{E}$ can be in
 anywhere in the range $[0.7,0.8]$, the values are not independent. Any
@@
 $E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
-$\bar{\mu}(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
+$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
 combination with the requirement for the identity event would force
-$\bar{\mu}(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
-particular assignments of $\bar{\mu}(E)$ or~$\bar{\mu}(\overline{E})$.
+$\mu(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
+particular assignments of $\mu(E)$ or~$\mu(\overline{E})$.
 
@@
 \begin{equation}
-\bar{\mu}(E_1\cup E_2) + \bar{\mu}(E_1\cap E_2) \subseteq \bar{\mu}(E_1) + \bar{\mu}(E_2)
+\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
 \label{eq:classicalconvex}
@@
 motivated condition when the events are disjoint, i.e., when
-$\bar{\mu}(E_1\cap E_2) = 0$.
+$\mu(E_1\cap E_2) = 0$.
 
@@
   $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space of
-  dimension~$d\ge3$ with event space $\events$; and $\mathbf{O}$ an
+  dimension~$d\ge3$ with event space~$\events$; and $\mathbf{O}$ an
   observable with spectral decomposition
@@
 
-Our generalization of quantum probability measures to QIVPMs will
-allow us to strengthen one of the fundamental theorems in of quantum
+Our generalization of quantum probability measures to QIVPMs allows us
+to strengthen one of the fundamental theorems in of quantum
 information: the Kochen-Specker
@@
 measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
-Specifically, the original Kochen-Specker theorem is formulated
-under the assumption that all observables of a quantum mechanical
-system have \emph{definite values at all
-  times}~\cite{Held2016}. Our interval-valued framework will allow
-us to state, and prove, a stronger version of the theorem that holds
-even if the observables have values that are only definite up to some
-specific parameter that quantifies experimental uncertainty. Put
-differently, our stronger statement and theorem quantifies Mermin's
-qualitative argument:
+Specifically, the original Kochen-Specker theorem is formulated under
+the assumption that all observables of a quantum mechanical system
+have \emph{definite values at all times}~\cite{Held2016}. Our
+interval-valued framework will allow us to state, and prove, a
+stronger version of the theorem that holds even if the observables
+have values that are only definite up to some specific parameter that
+quantifies experimental uncertainty. Put differently, our stronger
+statement and theorem quantifies Mermin's qualitative argument:
 \begin{quote}
@@
 
-\paragraph*{Expectation Values of Fuzzy Observables.}  Our following
-development will crucially rely on analyzing the expectation values of
-families of observables. We introduce the necessary definitions before
-stating and proving our variants of the Kochen-Specker theorem.
-
-The expectation value is intuitively between two possible outcomes,
-which themselves lie between the minimum and maximum bounds of the
-given probability intervals. (This definition is consistent with the
-classical Choquet integral on subspaces of commuting events by
-adopting the classical
-results~\cite{GilboaSchmeidler1994,Grabisch2016}.)  If the QIVPM is
+If a QIVPM is 0-deterministic, then for a family of commuting
+observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$, we have:
+\begin{equation}
+\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
+\end{equation}
+Intuitively the expectation value of an observable lies between two
+possible outcomes, which themselves lie between the minimum and
+maximum bounds of the given probability intervals.  If the QIVPM is
 0-deterministic, this interval collapses to a singleton
 $\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
-of~$\mathbf{O}$. If we define the multiplication of two singleton
-sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $
-to be $\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
-\begin{equation}
-\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
-\end{equation}
-for any set of commuting observables~$\left\{ \mathbf{O}_{j}\right\}
-_{j=1}^{N}$.
+of~$\mathbf{O}$.
 
@@
 \end{definition}
+
+If we define the multiplication of two singleton
+sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $
+to be $\left\{ \lambda_{1}\lambda_{2}\right\} $.

### 2017-08-19 prop_letter.tex
prop_letter.tex Updated by Gerardo...

@@
 have \emph{definite values at all times}~\cite{Held2016}. Our
-interval-valued framework will allow us to state, and prove, a
+interval-valued probability framework will allow us to state, and prove, a
 stronger version of the theorem that holds even if the observables
@@
 quantifies experimental uncertainty. Put differently, our stronger
-statement and theorem quantifies Mermin's qualitative argument:
+statement and theorem quantifies Mermin's intuition:
 \begin{quote}

### 2017-08-20 prop_letter.tex
prop_letter.tex Updated by Gerardo...

@@
 
-\begin{thm}\label{thm:Shapley}
+\begin{thm}[Non-empty Core for Compatible Measurements] \label{thm:Shapley}
   For QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
@@
 In conventional quantum mechanics the expectation value of an
-observable is defined in Eq.~\ref{eq:quantum-expectation} as a precise
+observable is defined in Eq.~\eqref{eq:quantum-expectation} as a precise
 real number. The generalization of quantum measures to QIVPMs implies
@@
 
-\paragraph*{$\delta$-Determinism.} The first step in our formalization
+%\paragraph*{$\delta$-Determinism.}
+
+The first step in our formalization
 is to introduce a family of QIVPMs parameterized by an uncertainty
@@
 
-\begin{definition}\label{def:delta-deterministic} A
+\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic} A
   QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is
@@
 \begin{thm}
-\label{thm:Kochen-Specker} {\rm [0-deterministic variant of Kochen-Specker]}
+[0-Deterministic Variant of Kochen-Specker] \label{thm:Kochen-Specker} 
 Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
@@
 Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. We now define the
-expectation value of the QIVPM for our Mermin-Peres square.
-
-Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfies
+expectation value over the QIVPM for our Mermin-Peres square.
+
+Since the expectation value~$\expval{\mathbf{O}_{ij}}_{\bar{\mu}}$ satisfies
 these two properties, the observables in the Mermin-Peres square must
@@
 
-\begin{thm}\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$
+\begin{thm}[Finite-precision Extension of Kochen-Specker] \label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$
   of dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
@@
 
-\begin{proof} Suppose there is a $\delta$-deterministic
+%\begin{proof} 
+Suppose there is a $\delta$-deterministic
   QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
@@
 theorem holds when $\delta<\frac{1}{3}$.
-\end{proof}
+%\end{proof}
 
@@
 A $\frac{1}{3}$-deterministic QIVPM can be given by
-$\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
-onto an $x$-dimensional subspace of a three-dimensional Hilbert space.
+$\bar{\mu}\left(P\right)=\left[n/3,n/3\right]$, where $P$ projects
+onto an $n$-dimensional subspace of a three-dimensional Hilbert space.
 

### 2017-08-20 prop_letter.tex
prop_letter.tex \section{Introduction} Add a comment...

@@
 classical theory that can be specified consistently by hidden
-variables.  These results provide a new insight into the
+variables.  
+\yutsung{The part after ``that is'' looks strange.
+\begin{enumerate}
+\item The Kochen-Specker theorem is not about quantum mechanics, is about whether
+quantum mechanics can be simulated by a non-contextual deterministic hidden
+variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
+doesn't make a lot sense.
+\item The question is whether there exist a QIVPM means ``a classical theory
+consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
+I need to check whether it qualities as a classical probabilitic hidden variable
+theory\ldots(?)
+\end{enumerate}
+}
+These results provide a new insight into the
 Meyer-Mermin debate by presenting a theory in which there is a

### 2017-08-21 prop_letter.tex
prop.bib @Article{FeintzeigFletcher2017} Added...

@@
 consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
-I need to check whether it qualities as a classical probabilitic hidden variable
+I need to check whether it qualities as a classical probabilistic hidden variable
 theory\ldots(?)

### 2017-08-22 prop_letter.tex
sec 1-3

@@
 A principal result is that recasting the Kochen-Specker theorem in
-terms of ``$\delta$-determinism'', with $\delta$ 
+terms of ``$\delta$-determinism'', with~$\delta$ 
 quantifying the effect of finite-precision uncertainties on measurement 
@@
 determining the probability of a given measurement
-outcome~\citep{Born1983,peres1995quantum,544199}.  Here, the Gleason
+outcome~\citep{Born1983,peres1995quantum,544199}.  Here, Gleason's
 theorem establishes that there is no alternative to the Born rule by
@@
 interval valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
-The QIVPM will provide the mathematical framework we need to quantify the
+The QIVPMs will provide the mathematical framework we need to quantify the
 impact of finite precision measurements on quantum mechanics.  For
@@
 study Gleason's theorem in the context of imprecise measurements,
-concluding that QIVPM provides a framework with quantitative bounds in
+concluding that QIVPMs provide a framework with quantitative bounds in
 which Gleason's theorem, while formally invalid in a universe with
@@
 $|\alpha|=1$. The expectation values of the observable $\mathbf{O}$,
-$\expval{\mathbf{O}}_{\mu_{1,2}}$, are 1.5 in the first case is 1.5
-and 2 in the second.
+$\expval{\mathbf{O}}_{\mu_{1,2}}$, are 1.5 in the first case and 2 in
+the second.
 
@@
 and events that are certain (e.g., the event covering the entire
-sample space).  For each interval $[\ell,r]$, we also need the
+sample space).  For each interval $[\ell,r]$, we also need the dual
 interval $[1-r,1-\ell]$ so that if one interval refers to the
-probability of an event $E$, the other refers to the probability of
-the event's complement $\overline{E}$.  For example, if we discover as
-a result of an experiment that $\mu(E) = [0.2,0.3]$ for some
-event~$E$, we may conclude that $\mu(\overline{E}) = [0.7,0.8]$ for
-the complement event $\overline{E}$. In addition to these simple
+probability of an event~$E$, the dual refers to the probability of the
+event's complement $\overline{E}$.  For example, if we discover as a
+result of an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$,
+we may conclude that $\mu(\overline{E}) = [0.7,0.8]$ for the
+complement event $\overline{E}$. In addition to these simple
 conditions, there are some subtle conditions on how intervals are
@@
 $\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
-are disjoint; the previous naïve way of combining the intervals would
-give $\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
-probability interval. Moreover the event $E\cup\overline{E}$ is the
-identity event covering the entire space; its probability interval
-should be $[1,1]$ which is sharper than $[0.9,1.1]$. The problem is
-that the two intervals are correlated: there is more information in
-the combined event than in each event separately. In our example, even
-though the ``true'' probability of $E$ can be anywhere in the range
-$[0.2,0.3]$ and the ``true'' probability of $\overline{E}$ can be in
-anywhere in the range $[0.7,0.8]$, the values are not independent. Any
-value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
-0.75$. To account for such subtleties, the axioms of interval-valued
-probability do not use a strict equality for the combination of
-disjoint events. The correct constraint regarding the probability of
-$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
+are disjoint; the naïve addition of intervals would give
+$\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid probability
+interval. Moreover the event $E\cup\overline{E}$ is the identity event
+covering the entire space; its probability interval should be $[1,1]$
+which is sharper than $[0.9,1.1]$. The problem is that the two
+intervals are correlated: there is more information in the combined
+event than in each event separately. In our example, even though the
+``true'' probability of $E$ can be anywhere in the range $[0.2,0.3]$
+and the ``true'' probability of~$\overline{E}$ can be in anywhere in
+the range $[0.7,0.8]$, the values are not independent. Any value of
+$\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq 0.75$. To account
+for such subtleties, the axioms of interval-valued probability do not
+use a strict equality for the combination of disjoint events. The
+correct constraint regarding the probability of $E_1\cup E_2$ when
+$E_1$ and $E_2$ are disjoint is
 $\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
@@
 commuting events, i.e., to compatible events that can be measured
-simultaneously.
+simultaneously. In Sec.~\ref{sec:Gleason} we will discuss the
+connection between QIVPMs and conventional quantum probability
+measures.
 
@@
 Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
-classical IVPMs with quantum probability measures. In
-Sec.~\ref{sec:Gleason}, we will show that QIVPMs generalize
-conventional quantum probability measures in the limit where the
-endpoints of each interval coincide and this dense set of point
-intervals covers $[0,1]$.
+classical IVPMs with quantum probability measures.
 
@@
 probability measure $\bar{\mu}$ and a subspace of events $\events'$,
-we denote the collection $\coreBorn(\bar{\mu},\events')$ of all states
-that are consistent with $\bar{\mu}$ on every projector in $\events'$
-as:
+we denote the collection of all states that are consistent with
+$\bar{\mu}$ on every projector in $\events'$ as
+$\coreBorn(\bar{\mu},\events')$:
 \begin{equation}
@@
 
-In the long version of this paper~\cite{HOSTunpublished}, we establish that
-QIVPMs become classical IVPMs when the space of events includes only mutually
-commuting events. The idea of the proof is as follows. Given a
-subspace of commuting events $\events_C$, we can construct a partial
-orthonormal basis by diagonalization and complete it to a full
-orthonormal basis $\overline{\events_C}$. We then build a bijection
-between the QIVPM on the set of projectors associated with this basis
-and the set of classical events corresponding to this basis. This
-correspondence leads to a crucial property in our setting.
+The proof that QIVPMs become classical IVPMs when the space of events
+includes only mutually commuting events is presented in detail in the
+long version of this paper~\cite{HOSTunpublished}. The idea of the
+proof is as follows. Given a subspace of commuting events $\events_C$,
+we can construct a partial orthonormal basis by diagonalization and
+complete it to a full orthonormal basis $\overline{\events_C}$. We
+then build a bijection between the QIVPM on the set of projectors
+associated with this basis and the set of classical events
+corresponding to this basis. This correspondence leads to a crucial
+property in our setting.
 
@@
 proves that a classical IVPM always contains at least one state $\rho$
-that is consistent with every event in $\events_C$. As we will
+that is consistent with every event in $\events_C$. In contrast, as we
 illustrate in the next section, the set of states
@@
 
-In conventional quantum mechanics the expectation value of an
-observable is defined in Eq.~\eqref{eq:quantum-expectation} as a precise
-real number. The generalization of quantum measures to QIVPMs implies
-that the real-valued expectation value will be generalized to an
-interval.
+We conclude this section with a generalization of expectation values
+of observables in the context of QIVPMs. In conventional quantum
+mechanics the expectation value of an observable as defined in
+Eq.~\eqref{eq:quantum-expectation} is a unique real number. The
+generalization to QIVPMs implies that this expectation value will
+itself become bounded by an interval.
 
@@
   $\Sigma_{i=1}^N \lambda_iP_i$. Let $\events'$ be the minimal
-  subspace of events containing all the projectors $P_i$, then we define:
+  subspace of events containing all the projectors $P_i$ in the
+  spectral decomposition of $\mathbf{O}$, then we define:
 \begin{equation}
@@
 
-If $\bar{\mu}$ is a conventional (Born) probability measure defined by
-state $\rho$, then $\coreBorn\left(\bar{\mu},\events'\right)$ will
+If $\bar{\mu}$ is a conventional (Born) probability measure induced by
+a state $\rho$, then $\coreBorn\left(\bar{\mu},\events'\right)$ will
 contain the singleton state $\rho$ and both endpoints of the interval

### 2017-08-22 prop_letter.tex
pass over sec 4

@@
 Our generalization of quantum probability measures to QIVPMs allows us
-to strengthen one of the fundamental theorems in of quantum
-information: the Kochen-Specker
-theorem~\cite{PeresRon1988,peres1995quantum}. Our stronger version of
-the theorem will suggest a resolution to the debate initiated by Meyer
-and Mermin on the relevance of the Kochen-Specker to experimental, and
-hence finite-precision, quantum
+to strengthen one of the fundamental theorems of quantum information:
+the Kochen-Specker theorem~\cite{PeresRon1988,peres1995quantum}. Our
+stronger version of the theorem will suggest a resolution to the
+debate initiated by Meyer and Mermin on the relevance of the
+Kochen-Specker to experimental, and hence finite-precision, quantum
 measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
@@
 have \emph{definite values at all times}~\cite{Held2016}. Our
-interval-valued probability framework will allow us to state, and prove, a
-stronger version of the theorem that holds even if the observables
-have values that are only definite up to some specific parameter that
-quantifies experimental uncertainty. Put differently, our stronger
-statement and theorem quantifies Mermin's intuition:
+interval-valued probability framework will allow us to state, and
+prove, a stronger version of the theorem that holds even if the
+observables have values that are only definite up to some specific
+parameter that quantifies experimental uncertainty. Put differently,
+our stronger statement and theorem quantifies Mermin's intuition:
 \begin{quote}
@@
 
-The first step in our formalization
-is to introduce a family of QIVPMs parameterized by an uncertainty
-$\delta$ which we call $\delta$-deterministic QIVPMs.
+The first step in our formalization is to introduce a family of QIVPMs
+parameterized by an uncertainty~$\delta$ which we call
+$\delta$-deterministic QIVPMs.
 
@@
 If a QIVPM is 0-deterministic, then for a family of commuting
-observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$, we have:
+observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$, we can prove
+that the product of expectation values of the individual observables
+is the expectation value of the product of the family:
 \begin{equation}
@@
 \end{equation}
-Intuitively the expectation value of an observable lies between two
-possible outcomes, which themselves lie between the minimum and
-maximum bounds of the given probability intervals.  If the QIVPM is
-0-deterministic, this interval collapses to a singleton
-$\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
-of~$\mathbf{O}$.
+\amr{Talk with Yu-Tsung about this} Intuitively the expectation value
+of each observable lies between two possible outcomes, which
+themselves lie between the minimum and maximum bounds of the given
+probability intervals.  If the QIVPM is 0-deterministic, this interval
+collapses to a singleton $\left\{ \lambda\right\} $, where $\lambda$
+is an eigenvalue of~$\mathbf{O}$.
 
@@
 
-\begin{thm}
-[0-Deterministic Variant of Kochen-Specker] \label{thm:Kochen-Specker} 
-Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
-0-deterministic
-measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}$.
+\begin{thm} [0-Deterministic Variant of
+  Kochen-Specker] \label{thm:Kochen-Specker} Given a Hilbert space
+  $\Hilb$ of dimension~$d\ge3$, there is no 0-deterministic
+  measure~$\bar{\mu}$ mapping every event to either $[0,0]$ or $[1,1]$.
 \end{thm}
 
-To prove this result, we proceed by assuming a 0-deterministic QIVPM
-$\bar{\mu}$ and derive a contradiction using the same nine observables
-$\mathbf{O}_{ij}$ used in the ``Mermin-Peres'' proof of the
-Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum}:
+To explain why this result is equivalent to the original
+Kochen-Specker theorem and to prove it at the same time, we proceed by
+assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive a
+contradiction to the original Kochen-Specker theorem using the same
+nine observables $\mathbf{O}_{ij}$ used in the ``Mermin-Peres'' proof
+of the Kochen-Specker
+theorem~\cite{Mermin1990Simple,peres1995quantum}:
 {\renewcommand{\arraystretch}{2}%
@@
 }
-\noindent where $\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are
-Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. We now define the
-expectation value over the QIVPM for our Mermin-Peres square.
-
-Since the expectation value~$\expval{\mathbf{O}_{ij}}_{\bar{\mu}}$ satisfies
-these two properties, the observables in the Mermin-Peres square must
-have the expectation value~$\left\{ 1\right\} $ or
-$\left\{ -1\right\} $.  In each row and column, the operators commute,
-and each operator is the product of two others, except in the third
-column, where
+\noindent where
+$\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are Pauli
+matrices acting on a pair of spin-$\frac{1}{2}$ states.  The
+observables in the Mermin-Peres square must have expectation
+values~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.  In each row and
+column, the operators commute, and each operator is the product of two
+others, except in the third column, where
 $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
@@
 
-We will now adapt the proof above to show that it is, in general,
-impossible to have just the two intervals \imposs\ and \necess: every
-QIVPM must be parameterized by a collection of intervals that includes
-at least one additional ``fuzzy'' interval and some events must be
-associated with such uncertain intervals. The significance of this
-observation is that the uncertainty in the intervals is, in contrast
-to the classical case, \emph{a fundamental part of quantum
-  theory}. There are in fact two sources of uncertainty: one due to
-the finite measurement resources and one due to complementarity, which
-requires every quantum framework to be truly probabilistic.
-
-???~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
+We can in fact generalize the above theorem to state than for small
+enough $\delta$, it is impossible to have just the two intervals
+\imposs\ and \necess: every QIVPM must be parameterized by a
+collection of intervals that includes at least one additional
+``fuzzy'' interval and some events must be associated with such
+uncertain intervals. The significance of this observation is that the
+uncertainty in the intervals is, in contrast to the classical case,
+\emph{a fundamental part of quantum theory}. There are in fact two
+sources of uncertainty: one due to the finite measurement resources
+and one due to complementarity, which requires every quantum framework
+to be truly probabilistic.
 
@@
 
-%\begin{proof} 
-Suppose there is a $\delta$-deterministic
+For the proof, suppose there is a $\delta$-deterministic
 QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
-  following function~$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
-    \imposs,\necess\right\} $ is a cryptodeterministic QIVPM:
+following
+map~$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
+  \imposs,\necess\right\} $ is a 0-deterministic QIVPM:
 \begin{equation}
@@
 \end{equation}
-However, since we know that there is no cryptodeterministic QIVPM,
-$\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ cannot
-exist.
-
-It remains to verify that $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
-QIVPM by checking the properties of
+However, since we know that 0-deterministic QIVPMs do not exist, the
+map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ does
+not exist.
+
+It remains to verify that $\bar{\mu}^{\textrm{D}}$ is indeed a 0-deterministic
+QIVPM by checking the following property:
 \begin{subequations}
@@
 theorem holds when $\delta<\frac{1}{3}$.
-%\end{proof}
-
-%%%%%
-\subsection{HV}
-
-A $\frac{1}{3}$-deterministic QIVPM can be given by
-$\bar{\mu}\left(P\right)=\left[n/3,n/3\right]$, where $P$ projects
-onto an $n$-dimensional subspace of a three-dimensional Hilbert space.
+
+When $\delta \ge \frac{1}{3}$, the situation abruptly
+changes. Assuming a Hilbert space $\Hilb$ of dimension $\ge 3$, then
+for any projector $P$ that projects onto an $n$-dimensional subspace
+of $\Hilb$, it is straightforward to check that
+$\bar{\mu}\left(P\right)=\left[n/3,n/3\right]$ is a valid
+$\frac{1}{3}$-deterministic QIVPM.
+
+\amr{Explain significance}
 
@@
 to be $\left\{ \lambda_{1}\lambda_{2}\right\} $.
+
+We will now adapt the proof above to show that it is, in general,
+impossible to have just the two intervals \imposs\ and \necess: every
+QIVPM must be parameterized by a collection of intervals that includes
+at least one additional ``fuzzy'' interval and some events must be
+associated with such uncertain intervals. The significance of this
+observation is that the uncertainty in the intervals is, in contrast
+to the classical case, \emph{a fundamental part of quantum
+  theory}. There are in fact two sources of uncertainty: one due to
+the finite measurement resources and one due to complementarity, which
+requires every quantum framework to be truly probabilistic.
+
+???~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}

### 2017-08-22 prop_letter.tex
working on sec4

@@
 mechanics the expectation value of an observable as defined in
-Eq.~\eqref{eq:quantum-expectation} is a unique real number. The
+Eq.~(\eqref{eq:quantum-expectation}) is a unique real number. The
 generalization to QIVPMs implies that this expectation value will
@@
 \expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
-\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,.\label{eq:quantum-interval-expectation-core}
+\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,. \label{eq:quantum-interval-expectation-core}
 \end{equation}
@@
 
-If $\bar{\mu}$ is a conventional (Born) probability measure induced by
-a state $\rho$, then $\coreBorn\left(\bar{\mu},\events'\right)$ will
-contain the singleton state $\rho$ and both endpoints of the interval
-will agree, thus reducing the definition to that of
-Eq.~\ref{eq:quantum-expectation}. We also note that, when restricted
+\noindent Intuitively the expectation value of an observable relative
+to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
+themselves lie between the minimum and maximum bounds of the
+probability intervals associated with each state~$\rho$ that is
+consistent with $\bar{\mu}$ on every projector in the spectral
+decomposition of the observable. If $\bar{\mu}$ is a conventional
+(Born) probability measure induced by a state $\rho$, then
+$\coreBorn\left(\bar{\mu},\events'\right)$ will contain the singleton
+state $\rho$ and both endpoints of the interval will agree, thus
+reducing the definition to that of
+Eq.~(\ref{eq:quantum-expectation}). We also note that, when restricted
 to commuting projectors, the definition above is consistent with the
@@
 Our generalization of quantum probability measures to QIVPMs allows us
-to strengthen one of the fundamental theorems of quantum information:
-the Kochen-Specker theorem~\cite{PeresRon1988,peres1995quantum}. Our
-stronger version of the theorem will suggest a resolution to the
-debate initiated by Meyer and Mermin on the relevance of the
-Kochen-Specker to experimental, and hence finite-precision, quantum
+to strengthen the scope of one of the fundamental theorems of quantum
+information: the Kochen-Specker
+theorem~\cite{PeresRon1988,peres1995quantum}. Our finite-precision
+extension of the theorem will suggest a resolution to the debate
+initiated by Meyer and Mermin on the relevance of the Kochen-Specker
+to experimental, and hence finite-precision, quantum
 measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
@@
 
-If a QIVPM is 0-deterministic, then for a family of commuting
+\amr{Fix below until next marker}
+If a QIVPM is 0-deterministic, then for a family of $M$ commuting
 observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$, we can prove
 that the product of expectation values of the individual observables
-is the expectation value of the product of the family:
+relative to $\bar{\mu}$ is the expectation value of the product of the
+family relative to $\bar{\mu}$:
 \begin{equation}
@@
 \end{equation}
-\amr{Talk with Yu-Tsung about this} Intuitively the expectation value
-of each observable lies between two possible outcomes, which
-themselves lie between the minimum and maximum bounds of the given
-probability intervals.  If the QIVPM is 0-deterministic, this interval
-collapses to a singleton $\left\{ \lambda\right\} $, where $\lambda$
-is an eigenvalue of~$\mathbf{O}$.
-
-We now state and prove a theorem that is equivalent to the original
-Kochen-Specker theorem but that is formulated in terms of
+If the QIVPM $\bar{\mu}$ is 0-deterministic, the expectation value of
+each observable $\mathbf{O}_j$ given by
+Eq.~(\ref{eq:quantum-interval-expectation-core}) collapses to a single
+point
+
+this interval collapses
+to a singleton $\left\{ \lambda\right\} $, where $\lambda$ is an
+eigenvalue of~$\mathbf{O}$.
+
+\amr{End marker}
+
+We now state and prove a theorem that is equivalent in scope to the
+original Kochen-Specker theorem but that is formulated in terms of
 $0$-deterministic QIVPMs.
@@
 
-We can in fact generalize the above theorem to state than for small
-enough $\delta$, it is impossible to have just the two intervals
-\imposs\ and \necess: every QIVPM must be parameterized by a
-collection of intervals that includes at least one additional
-``fuzzy'' interval and some events must be associated with such
-uncertain intervals. The significance of this observation is that the
-uncertainty in the intervals is, in contrast to the classical case,
-\emph{a fundamental part of quantum theory}. There are in fact two
-sources of uncertainty: one due to the finite measurement resources
-and one due to complementarity, which requires every quantum framework
-to be truly probabilistic.
+We can in fact generalize the above theorem to state that for small
+enough $\delta$, it is impossible to have $\delta$-deterministic
+QIVPMs. Every QIVPM must map some events to truly uncertain intervals,
+not just ``almost definite intervals.'' The significance of this
+observation is that the uncertainty in the intervals is, in contrast
+to the classical case, \emph{a fundamental part of quantum
+  theory}. There are in fact two sources of uncertainty: one due to
+the finite measurement resources and one due to complementarity, which
+requires every quantum framework to be truly probabilistic.
 
@@
 
-For the proof, suppose there is a $\delta$-deterministic
+The proof is by contradiction: suppose there is a
+$\delta$-deterministic
 QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
@@
 
-It remains to verify that $\bar{\mu}^{\textrm{D}}$ is indeed a 0-deterministic
-QIVPM by checking the following property:
-\begin{subequations}
-\begin{eqnarray}
- &  & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs\\
- & \Rightarrow & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs
-\end{eqnarray}
-\end{subequations}for orthogonal operators~$P_{0}$ and $P_{1}$.
-
-When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$
-which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
-Since $\delta<\frac{1}{3}\Rightarrow2\delta<1-\delta$, $\bar{\mu}\left(P_{0}+P_{1}\right)$
-cannot be a subset of $\left[1-\delta,1\right]$, but $\bar{\mu}\left(P_{0}+P_{1}\right)$
-is a subset of either $\left[0,\delta\right]$ or $\left[1-\delta,1\right]$.
-Hence, $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[0,\delta\right]$,
-which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
+It remains to verify that $\bar{\mu}^{\textrm{D}}$ is indeed a
+0-deterministic QIVPM by checking that for orthogonal
+operators~$P_{0}$ and $P_{1}$, we have that
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
+implies
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Indeed when
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+we have both $\bar{\mu}\left(P_{0}\right)$ and
+$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
+implies
+$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
+When $\delta<\frac{1}{3}$, i.e., $2\delta<1-\delta$, it follows that
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ cannot be a subset of
+$\left[1-\delta,1\right]$, but $\bar{\mu}\left(P_{0}+P_{1}\right)$ is
+a subset of either $\left[0,\delta\right]$ or
+$\left[1-\delta,1\right]$.  Hence, $\bar{\mu}\left(P_{0}+P_{1}\right)$
+must be a subset of $\left[0,\delta\right]$, which implies
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
 theorem holds when $\delta<\frac{1}{3}$.
@@
 When $\delta \ge \frac{1}{3}$, the situation abruptly
-changes. Assuming a Hilbert space $\Hilb$ of dimension $\ge 3$, then
+changes. Assuming a Hilbert space $\Hilb$ of dimension $d \ge 3$, then
 for any projector $P$ that projects onto an $n$-dimensional subspace

### 2017-08-23 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for Classical IVPMs} Updating...
prop_iop.tex \section{Expectation Values for IVPMs} Updating lemmas and proofs...

@@
 \begin{document}
-\title{Measurement and Probability in Fuzzy Quantum
-Theories}
+\title{Quantum Interval-Valued Probability: Measurement and Probability}
 
@@
 are all disjoint.
-\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-f\left(E_{i+1}^{s\prime}\right)$,
+\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
 where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
@@
 \begin{lemma}\label{lemma:real-expectation-value-between-classical-quantum}Adopting
-the definitions in this subsection. Given a density matrix~$\rho$,
+the definitions in this subsection. Given a QRVPM~$\mu:\events\rightarrow\left[0,1\right]$,
 there is a classical real-valued probability measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$
-such that $\mu_{\rho}^{\mathrm{B}}|_{\events'}=\mu'\circ\tau$. Then,
-we have $\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}
-
-\begin{proof}Since $\mu_{\rho}^{\mathrm{B}}:\events\rightarrow\left[0,1\right]$
-is a QRVPM, $\mu_{\rho}^{\mathrm{B}}|_{\events'}$ is a QRVPM on the
-commuting sub-event space\nb$\events'$. By case\nb\ref{enu:sub-event-space-real-quantum2classical}
-in theorem~\ref{thm:sub-event-space}, there is a CRVPM such that
-$\mu_{\rho}^{\mathrm{B}}|_{\events'}=\mu'\circ\tau$. 
+such that $\mu|_{\events'}=\mu'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\mu}=\int X\rmd\mu'$.\end{lemma}
+
+\begin{proof}Since $\mu:\events\rightarrow\left[0,1\right]$ is a
+QRVPM, $\mu|_{\events'}$ is a QRVPM on the commuting sub-event space\nb$\events'$.
+By case\nb\ref{enu:sub-event-space-real-quantum2classical} in theorem~\ref{thm:sub-event-space},
+there is a CRVPM such that $\mu|_{\events'}=\mu'\circ\tau$. 
 \begin{eqnarray*}
-\expval{\mathbf{O}}_{\rho} & \stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\\
+\expval{\mathbf{O}}_{\mu} & \stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\\
  & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\\
@@
 and $\mur:\events\rightarrow\left[0,1\right]$ are real-valued probability
-measures, we have $\mul=\mur=\mu_{\rho}^{\mathrm{B}}$ for some density
-matrix~$\rho$. Then, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.\end{lemma}
+measures, we have $\mul=\mur=\mu$. Then, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\mu}\right\} $.\end{lemma}
 
@@
 we have
-\[
-\expval{\mathbf{O}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=}\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu'\right\} \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=}\left\{ \expval{\mathbf{O}}_{\rho}\right\} \,,
-\]
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=}\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu'\right\} \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=}\left\{ \expval{\mathbf{O}}_{\mu}\right\} \,,
+\end{equation}
 where $\mu'=\mul[\prime]=\mur[\prime]$.\end{proof}
@@
 real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
-By lemma~\ref{lemma:expectation-singleton}, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.
+By lemma~\ref{lemma:expectation-singleton}, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\mu}\right\} $.
 Since $\mu$ is a cryptodeterministic measure, there is only one pair
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\rho}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\,.\label{eq:expectation-value-eigenvalue}
+\expval{\mathbf{O}}_{\mu}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\,.\label{eq:expectation-value-eigenvalue}
 \end{equation}

### 2017-08-24 prop_iop.tex
prop_iop.tex Split Appendix D into Appendix D and E...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}}
-
-\subsection{From Real-valued to Interval-valued}
+\section{From QRVPM to QIVPM\label{sec:Real-and-Interval}}
 
@@
 
-\subsubsection{Convex but Infinite Number of Intervals}
+\subsection{Convex but Infinite Number of Intervals}
 
@@
 
-\subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule}
+\subsection{Sates Consistent with a QIVPM Induced by the Born Rule}
 
@@
 
-\subsection{From Interval-valued to Real-valued}
+\section{From Interval-valued to Real-valued}
 
@@
 construct a quantum real-valued probability measure from a special
-kind of quantum IVPMs.
+kind of quantum IVPMs. Since the only properties we use in this section
+is whether its interval-valued or real-valued, the results in this
+section applies on every subspace of events\nb$\events'$. In particular,
+when $\events'$ is commuting, any quantum results will be classical
+as shown in theorem~\ref{thm:sub-event-space}.
 
 \begin{definition}\label{def:delta-deterministic}An interval-valued
-probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
+probability measure\nb$\bar{\mu}:\events'\rightarrow\mathscr{I}$
 is called $\left(1/n,\delta\right)$-deterministic if for every $\left[l,r\right]\in\mathscr{I}$,
@@
 \begin{equation}
-\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
+\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events'\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
 \end{equation}
@@
 and a quantum $\left(1/n,\delta\right)$-deterministic probability
-measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<1/\left(3n\right)$,
+measure\nb$\bar{\mu}:\events'\rightarrow\mathscr{I}$ with $\delta<1/\left(3n\right)$,
 if $\bar{\mu}(P)\subseteq\left[k/n-\delta,k/n+\delta\right]$, let
-$\mu(P)=k/n$, then $\mu:\events\rightarrow\left[0,1\right]$ is a
-quantum probability measure. In another word, $\iota_{\infty}\circ\mu$
+$\mu(P)=k/n$, then $\mu:\events'\rightarrow\left[0,1\right]$ is
+a quantum probability measure. In another word, $\iota_{\infty}\circ\mu$
 is $\left(1/n,0\right)$-deterministic by lemma~\ref{lemma:real2interval}.\end{lemma}
@@
 \begin{lemma}If every interval in $\mathscr{I}$ is a singleton set,
-given a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, then
-$\mu:\events\rightarrow\left[0,1\right]$defined by $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
+given a QIVPM\nb$\bar{\mu}:\events'\rightarrow\mathscr{I}$, then
+$\mu:\events'\rightarrow\left[0,1\right]$defined by $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
 is a quantum probability measure.\end{lemma}

### 2017-08-24 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for Classical IVPMs} Add a lemma...

@@
 
+Finally, we are going to focus on CIVPMs whose range is $\mathscr{I}_{\mathrm{D}}$.
+
+\begin{lemma}For any CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
+and a random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
+$\int X\rmd\bar{\mu}$ is a singleton set~$\left\{ x_{i}\right\} $
+for some $i$.\end{lemma}
+
+\begin{proof}By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$
+are the same CRVPM, and is simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $.
+By lemma~\ref{lemma:Choquet-Lebesgue}, $\int X\rmd\bar{\mu}=\left\{ \int X\rmd\mu\right\} $.
+Since the range of $\pmeas$ is $\left\{ 1,0\right\} $ and $\sum_{i=1}^{N}\pmeas\left(E_{i}\right)=1$,
+there is a unique $i_{0}$ such that $\mu\left(E_{i_{0}}\right)=1$.
+Therefore, 
+\begin{equation}
+\int X\rmd\mu\stackrel{\textrm{Equation }(\ref{eq:expectation})}{=}\sum_{i=1}^{N}x_{i}\pmeas\left(E_{i}\right)=x_{i_{0}}\,.\label{eq:expectation-value-eigenvalue-classical}
+\end{equation}
+\end{proof}
+
 \subsection{Expectation Values for Quantum IVPMs}

### 2017-08-24 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for Classical IVPMs} Add more lemmas...

--- 2017-08-24 prop_iop.tex
@@
 
+Finally, we are going to focus on CIVPMs whose range is $\mathscr{I}_{\mathrm{D}}$.
+
+\begin{lemma}\label{lemma:deterministic-CIVPM}Given a CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
+the following statements are true:
+\begin{enumerate}
+\item Its left-end~$\mul$ and right-end~$\mur$ are the same CRVPM, and
+will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $
+\item There is a unique $\omega_{0}\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\left\{ \pmeas\left(\left\{ \omega_{0}\right\} \right)\right\} =\necess$,
+denoted by $\pmeas^{-1}\left(1\right)$ or $\bar{\mu}^{-1}\left(\necess\right)$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}~
+\begin{enumerate}
+\item The directly consequence of lemma~\ref{lemma:QIVPM2QCM}.
+\item Since the range of $\pmeas$ is $\left\{ 1,0\right\} $ and $\sum_{\omega\in\Omega}\pmeas\left(\left\{ \omega\right\} \right)=1$,
+there is a unique $\omega_{0}$ such that $\mu\left(\left\{ \omega_{0}\right\} \right)=1$
+which implies $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\necess$.
+\end{enumerate}
+\end{proof}
+
+\begin{lemma}\label{lemma:deterministic-CIVPM-expectation}For any
+CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$ and
+a random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$, then
+$\int X\rmd\bar{\mu}=\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} $.\end{lemma}
+
+\begin{proof}By adopting the notation in lemma~\ref{lemma:deterministic-CIVPM},
+we have
+\begin{equation}
+\int X\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu\right\} \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=}\left\{ X\left(\pmeas^{-1}\left(1\right)\right)\cdot1\right\} =\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \,.\label{eq:expectation-value-eigenvalue-classical}
+\end{equation}
+\end{proof}
+
+Given two singleton sets~$\left\{ x_{1}\right\} $ and $\left\{ x_{2}\right\} $,
+it is intuitive to define their multiplication of to be $\left\{ x_{1}x_{2}\right\} $
+which gives the following lemma.
+
+\begin{lemma}For any CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
+and a sequence of random variable~$\left\{ X_{j}\right\} $,
+\begin{equation}
+\prod_{j}\int X_{j}\rmd\bar{\mu}=\int\prod_{j}X_{j}\rmd\bar{\mu}\,.\label{eq:Kochen-Specker-Rules-classical}
+\end{equation}
+\end{lemma}
+
+\begin{proof} 
+\begin{equation}
+\prod_{j}\int X_{j}\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\prod_{j}\left\{ X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} =\left\{ \prod_{j}X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\int\prod_{j}X_{j}\rmd\bar{\mu}\,.\label{eq:expectation-value-eigenvalue-classical-1}
+\end{equation}
+\end{proof}
+
 \subsection{Expectation Values for Quantum IVPMs}

### 2017-08-25 prop_iop.tex
prop_iop.tex Proof fixed (?)

@@
 \item $\rho$ in the previous case may not be unique.
+\item The bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ preserves
+the following operations.
+\begin{itemize}
+\item $\tau\left(\mathbb{0}\right)=\emptyset$.
+\item $\tau\left(\mathbb{1}\right)=\Omega$.
+\item For any projection $P\in\widehat{\events}$, we have $\tau\left(\mathbb{1}-P\right)=\Omega-\tau\left(P\right)$.
+\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\widehat{\events}$,
+we have $\tau\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\tau\left(P_{i}\right)$.
+\end{itemize}
 \end{enumerate}
@@
 \end{eqnarray*}
+\item Trivial.
 \end{enumerate}
@@
 we have
-\begin{equation}
-\int X\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu\right\} \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=}\left\{ X\left(\pmeas^{-1}\left(1\right)\right)\cdot1\right\} =\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \,.\label{eq:expectation-value-eigenvalue-classical}
-\end{equation}
+\begin{eqnarray*}
+ &  & \int X\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu\right\} \\
+ & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \left\{ X\left(\pmeas^{-1}\left(1\right)\right)\cdot1\right\} =\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \,.
+\end{eqnarray*}
 \end{proof}
@@
 
-\begin{lemma}For any CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
+\begin{lemma}\label{lemma:deterministic-CIVPM-product}For any CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
 and a sequence of random variable~$\left\{ X_{j}\right\} $,
@@
 \begin{proof}
-\begin{equation}
-\prod_{j}\int X_{j}\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\prod_{j}\left\{ X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} =\left\{ \prod_{j}X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\int\prod_{j}X_{j}\rmd\bar{\mu}\,.\label{eq:expectation-value-eigenvalue-classical-1}
-\end{equation}
+\begin{eqnarray*}
+ &  & \prod_{j}\int X_{j}\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\prod_{j}\left\{ X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \\
+ & = & \left\{ \prod_{j}X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\int\prod_{j}X_{j}\rmd\bar{\mu}\,.
+\end{eqnarray*}
 \end{proof}
@@
 
-\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
-decomposition~(\ref{eq:spectrum-decomposition}) and its inducing
-sub-event space $\events'$, set~$\Omega$, and function~$\tau:\events'\rightarrow2^{\Omega}$.
-Then, the random variable~$X:\Omega\rightarrow\mathbb{R}$ defined
-by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$
+\begin{definition}\label{def:observable2random-variable}Given an
+observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition})
+and its inducing subspace of events\nb$\events'$, set~$\Omega$,
+and function~$\tau:\events'\rightarrow2^{\Omega}$. Then, the random
+variable~$X:\Omega\rightarrow\mathbb{R}$ defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$
 is called the random variable induced by $\mathbf{O}$.\end{definition}
+
+The following lemma shows that .
+
+\begin{lemma}\label{lemma:observable2random-variable}Given an observable~$\mathbf{O}$
+with an orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$,
+$\widehat{\events}=\set{\sum_{\ket{k}\in E}\proj{k}}{E\subseteq\Omega}$,
+and the bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$
+defined in theorem~\ref{thm:sub-event-space}. By definition~\ref{def:observable2random-variable},
+$\mathbf{O}$ induces a random variable\nb$X:\Omega\rightarrow\mathbb{R}$,
+if $\mathbf{O}=\sum_{k=0}^{d-1}\lambda_{k}\proj{k}$, then $X=\sum_{k=0}^{d-1}\lambda_{k}\mathbf{1}_{\left\{ \ket{k}\right\} }$.\end{lemma}
+
+\begin{proof}Since $\mathbf{O}$ can be diagonalized by $\Omega$,
+each projector in the spectral decomposition\nb$P_{i}^{s}$ is the
+summation of some basis vectors\nb$\sum_{k\in S_{i}^{s}}\proj{k}$.
+Since
+\begin{equation}
+\mathbf{1}_{\tau\left(P_{i}^{s}\right)}=\mathbf{1}_{\tau\left(\sum_{k\in S_{i}^{s}}\proj{k}\right)}=\mathbf{1}_{\bigcup_{k\in S_{i}^{s}}\tau\left(\proj{k}\right)}=\sum_{k\in S_{i}^{s}}\mathbf{1}_{\left\{ \ket{k}\right\} }\,,
+\end{equation}
+we have $X=\sum_{k=0}^{d-1}\lambda_{k}\mathbf{1}_{\ket{k}}$.\end{proof}
 
@@
 
-\begin{proof}Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum}.
+\begin{proof}[Proof 1]Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum}.
 By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
@@
 
+\begin{proof}[Proof 2]Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
+we have
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \,,
+\end{equation}
+where $X\left(\bar{\mu}^{-1}\left(\necess\right)\right)$ is an eigenvalue
+of $\mathbf{O}$ by the definition of $X$.\end{proof}
+
 Given two singleton sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $,
@@
 
-\begin{lemma}For any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $,
+\begin{lemma}For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
+and a sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $,
 \begin{equation}
@@
 of commuting observables, they can be diagonalized by a common orthonormal
-basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$. By lemma~\ref{lemma:QIVPM2QCM},
-$\mul$ and $\mur$ are the same cryptodeterministic measure, and
-is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
-Since $\mu$ is a cryptodeterministic measure, there is only one $j_{0}$
-such that $\mu\left(\proj{j_{0}}\right)=1$. Therefore, by the same
-reason as equation~(\ref{eq:expectation-value-eigenvalue}), the
-both sides of equation~(\ref{eq:Kochen-Specker-Rules}) are the product
-of eigenvalues corresponding to eigenstate~$\ket{j_{0}}$, and should
-be equal.\end{proof}
+basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$. By theorem~\ref{thm:sub-event-space},
+there is a commuting sub-event space\nb$\widehat{\events}$ with
+$\widehat{\events}\subseteq\events$ and a bijection\nb$\tau:\widehat{\events}\rightarrow2^{\Omega}$
+such that there is a CIVPM\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}_{\mathrm{D}}$
+such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
+for all $P\in\widehat{\events}$.
+
+Let $\events'_{j}$ be the subspace of events induced by $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$.
+Clearly, $\events'_{j}\subseteq\widehat{\events}$. Therefore, restricting
+$\tau$ on each $\events'_{j}$ gives a function\nb$\tau|_{\events'_{j}}:\events'_{j}\rightarrow2^{\Omega}$.
+Then, we can follow lemma~\ref{lemma:observable2random-variable}
+to induce random variables\nb$X_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }$,
+and have $\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\int X_{j}\rmd\bar{\mu}'$
+by lemma~\ref{lemma:interval-expectation-value-between-classical-quantum}.
+Therefore, 
+\begin{eqnarray*}
+ &  & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\prod_{j}\int X_{j}\rmd\bar{\mu}'\\
+ & \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-product}}{=} & \int\prod_{j}X_{j}\rmd\bar{\mu}'=\int\prod_{j}\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'\\
+ & = & \int\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'=\expval{\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}}_{\bar{\mu}}\\
+ & = & \expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.
+\end{eqnarray*}
+\end{proof}
 

### 2017-08-25 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updates...

@@
 
-There are various kind of integrals defined for IVPMs, and the most
-famous one is called the Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
-
-\begin{definition}\label{def:Choquet}~
+There is a subtlety happens when we want to define the expectation
+value of a random variable on IVPMs, and will be demonstrated by the
+following example.
+
+\begin{example}\label{ex:expectation}Consider an CIVPM\nb$\bar{\mu}$
+and an event\nb$E$ such that $\bar{\mu}(E)=[0.2,0.3]$ and $\bar{\mu}(\overline{E})=[0.7,0.8]$.
+Given a random variable
+\begin{equation} 
+X\left(\omega\right)=\cases{ 
+1 & , if $\omega\in E$ ;\\
+2 & , if $\omega\notin E$ , 
+}
+\end{equation}
+its expectation value with respect to $\bar{\mu}$ might be naïvely
+defined as
+\begin{equation}\eqalign{ 
+ & 1\cdot\bar{\mu}(E)+2\cdot\bar{\mu}(\overline{E})\\
+= & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
+= & [1\cdot0.2+2\cdot0.7,1\cdot0.3+2\cdot0.8]\\
+= & [1.6,1.9]\,.
+}\end{equation}
+As we discussed when introducing the core, the true probability of
+$\bar{\mu}(E)$, $\mu(E)$, can be anywhere in the range $[0.2,0.3]$
+and the true probability of $\bar{\mu}(\overline{E})$ is $\mu(\overline{E})=1-\mu(E)$,
+that is, $\mu\in\mathrm{core}\left(\bar{\mu}\right)$. If $\mu(E)=0.2$,
+the expectation value of $X$ with respect to $\mu$ is 
+\begin{equation}
+1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.2+2\cdot0.8=1.8\,;
+\end{equation}
+if $\mu(E)=0.3$, the expectation value of $X$ with respect to $\mu$
+is
+\begin{equation}
+1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.3+2\cdot0.7=1.7\,.
+\end{equation}
+In another word, no matter how we pick $\mu(E)$, the expectation
+value of $X$ is in $\left[1.7,1.8\right]$ which is a more realistic
+expectation value of $X$ with respect to $\bar{\mu}$. The interval~$\left[1.7,1.8\right]$
+is narrower than the naïve expectation value~$[1.6,1.9]$ because
+the naïve one combines contradicting situations in the computation.\end{example}
+
+In general, the computation of the realistic expectation value, called
+the Choquet integral, is more complex than what we discussed because
+a random variable may have more than two values. Despite its complexity,
+it is still a weight average among the values of a random variable
+as given in the following definition.
+
+\begin{definition}[Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}~
 \begin{itemize}
@@
 any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
-is convex if and only if $\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]$.\end{thm}
+is convex if and only if
+\begin{equation}
+\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.\label{eq:Rosenmuller}
+\end{equation}
+\end{thm}
+
+Notice that $\left[1.7,1.8\right]$ in example~\ref{ex:expectation}
+is just the right-hand side of equation~(\ref{eq:Rosenmuller}).
+Let compute the left-hand side of equation~(\ref{eq:Rosenmuller})
+in table~\ref{table:Choquet} and see they are equal.
+\begin{table}
+\begin{tabular}{|c|c|c|c|}
+\hline 
+$i$ & 1 & 2 & 3\tabularnewline
+\hline 
+\hline 
+$x_{i}^{+}$ & 1 & 2 & \tabularnewline
+\hline 
+$E_{i}^{+}$ & $E$ & $\overline{E}$ & \tabularnewline
+\hline 
+$E_{i}^{+\prime}$ & $E$ & $\Omega$ & $\emptyset$\tabularnewline
+\hline 
+$\mul\left(E_{i}^{+\prime}\right)$ &  &  & \tabularnewline
+\hline 
+ &  &  & \tabularnewline
+\hline 
+ &  &  & \tabularnewline
+\hline 
+ &  &  & \tabularnewline
+\hline 
+\end{tabular}\caption{\label{table:Choquet}}
+\end{table}
 
@@
 
-\yutsung{Put an example here if we need...}
+\subsection{Expectation Values for $0$-deterministic CIVPMs}
 
@@
 \item Its left-end~$\mul$ and right-end~$\mur$ are the same CRVPM, and
-will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $
+will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $.
 \item There is a unique $\omega_{0}\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\left\{ \pmeas\left(\left\{ \omega_{0}\right\} \right)\right\} =\necess$,

### 2017-08-26 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for Classical IVPMs} Updating...

@@
 \begin{equation}
-\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,.\label{eq:interval-expectation}
+\int X\rmd\bar{\mu}=\left[\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mul\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mur\left(E_{i}^{-\prime}\right),\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mur\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mul\left(E_{i}^{-\prime}\right)\right]\,.\label{eq:interval-expectation}
 \end{equation}
@@
 
-\noindent The following lemma shows our definition is exactly the
-same as in the literature.
+\begin{table}
+\caption{\label{table:Choquet}
+\[
+\int X\rmd\bar{\mu}=\left[1\cdot0.3+2\cdot0.7,1\cdot0.2+2\cdot0.8\right]=\left[1.7,1.8\right]\,.
+\]
+}
+
+\begin{indented}
+\item\begin{tabular}{|c|c|c|c|c|c|c|c|} 
+\br 
+$i$ & $x_{i}^{+}$ & $E_{i}^{+}$ & $E_{i}^{+\prime}$ & $\mul\left(E_{i}^{+\prime}\right)$ & $\Delta\mul\left(E_{i}^{+\prime}\right)$ & $\mur\left(E_{i}^{+\prime}\right)$ & $\Delta\mur\left(E_{i}^{+\prime}\right)$\tabularnewline
+\mr 
+$1$ & $1$ & $E$ & $\Omega$ & $1$ & $0.3$ & $1$ & $0.2$\tabularnewline 
+\mr 
+$2$ & $2$ & $\overline{E}$ & $\overline{E}$ & $0.7$ & $0.7$ & $0.8$ & $0.8$\tabularnewline 
+\mr 
+$3$ &  &  & $\emptyset$ & $0$ &  & $0$ & \tabularnewline 
+\br 
+\end{tabular}
+\end{indented}
+\end{table}
+Table~\ref{table:Choquet} follows the definition to compute $\int X\rmd\bar{\mu}$.
+Notice that equation~(\ref{eq:interval-expectation}) looks complex.
+On the one hand, it would be a little bit easier to think its right-hand
+side as 
+\begin{equation}
+\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,,\label{eq:interval-expectation-1}
+\end{equation}
+$\Delta\mul\left(E_{i}^{s\prime}\right)$ can be larger than $\Delta\mur\left(E_{i}^{s\prime}\right)$
+as in the second row in table~\ref{table:Choquet}. Therefore, if
+we want to use this notation, we need to stick to this convention
+that not reverse the two ends of intervals, even if the left-end is
+larger than the right-end. On the other hand, similar to equation~(\ref{eq:expectation}),
+equation~(\ref{eq:interval-expectation-1}) can be considered as
+weighted average of the possible outcomes of $X$ as well, despite
+the ``weight''
+\begin{equation}
+\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\subseteq\left[\mul\left(E_{i}^{s}\right),\mur\left(E_{i}^{s}\right)\right]=\bar{\mu}\left(E_{i}^{s}\right)\textrm{ for }s\in\left\{ +,-\right\}
+\end{equation}
+is tighter than the interval-valued probability of the corresponding
+event. This makes it easier to remember.
+
+Also, $\left[1.7,1.8\right]$ in example~\ref{ex:expectation} is
+exactly the same as the expectation value computed in table~\ref{table:Choquet}.
+This nature property can be generated to the following theorem.
+
+\begin{thm}\label{thm:Rosenmuller}\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}For
+every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
+any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
+is convex if and only if
+\begin{equation}
+\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.\label{eq:Rosenmuller}
+\end{equation}
+\end{thm}
+
+The next lemmas shows our definition is exactly the same as in the
+literature, and is consistent with the CRVPM.
 
@@
 \end{proof}
-
-\noindent Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
-can be considered as weighted average of the possible outcomes of
-$X$ as well, despite the ``weight''
-\begin{equation}
-\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\subseteq\left[\mul\left(E_{i}^{s}\right),\mur\left(E_{i}^{s}\right)\right]=\bar{\mu}\left(E_{i}^{s}\right)\textrm{ for }s\in\left\{ +,-\right\}
-\end{equation}
-is tighter than the interval-valued probability of the corresponding
-event. Since only one event can happen at once, we don't have to be
-so pessimistic to accumulate all possible fuzziness together, and
-expect $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}^{s}\right)$ to happen.
-
-The Choquet integral has many desirable properties. For example, it
-has the same range as all expectation value in the core, and it generalizes
-the Lebesgue integral.
-
-\begin{thm}\label{thm:Rosenmuller}\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}For
-every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
-any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
-is convex if and only if
-\begin{equation}
-\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.\label{eq:Rosenmuller}
-\end{equation}
-\end{thm}
-
-Notice that $\left[1.7,1.8\right]$ in example~\ref{ex:expectation}
-is just the right-hand side of equation~(\ref{eq:Rosenmuller}).
-Let compute the left-hand side of equation~(\ref{eq:Rosenmuller})
-in table~\ref{table:Choquet} and see they are equal.
-\begin{table}
-\begin{tabular}{|c|c|c|c|}
-\hline 
-$i$ & 1 & 2 & 3\tabularnewline
-\hline 
-\hline 
-$x_{i}^{+}$ & 1 & 2 & \tabularnewline
-\hline 
-$E_{i}^{+}$ & $E$ & $\overline{E}$ & \tabularnewline
-\hline 
-$E_{i}^{+\prime}$ & $E$ & $\Omega$ & $\emptyset$\tabularnewline
-\hline 
-$\mul\left(E_{i}^{+\prime}\right)$ &  &  & \tabularnewline
-\hline 
- &  &  & \tabularnewline
-\hline 
- &  &  & \tabularnewline
-\hline 
- &  &  & \tabularnewline
-\hline 
-\end{tabular}\caption{\label{table:Choquet}}
-\end{table}
 

### 2017-08-26 prop_letter.tex
prop_letter.tex Fix some typos and citations...

@@
 mechanics the expectation value of an observable as defined in
-Eq.~(\eqref{eq:quantum-expectation}) is a unique real number. The
+Eq.~\eqref{eq:quantum-expectation} is a unique real number. The
 generalization to QIVPMs implies that this expectation value will
@@
 to experimental, and hence finite-precision, quantum
-measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 Specifically, the original Kochen-Specker theorem is formulated under
@@
 parameter that quantifies experimental uncertainty. Put differently,
-our stronger statement and theorem quantifies Mermin's intuition:
+our stronger statement and theorem quantifies Mermin's
+intuition~\citep{Mermin1999}:
 \begin{quote}
@@
   statistical distribution of outcomes will differ only slightly from
-  the ideal case~\citep{Mermin1999}.
+  the ideal case.
 \end{quote}

### 2017-08-27 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

@@
 \amr{Fix below until next marker}
-If a QIVPM is 0-deterministic, then for a family of $M$ commuting
-observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$, we can prove
-that the product of expectation values of the individual observables
-relative to $\bar{\mu}$ is the expectation value of the product of the
-family relative to $\bar{\mu}$:
+
+If a QIVPM~$\bar{\mu}$ is 0-deterministic, then for a family of
+$M$ commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$,
+they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
+By restricting to the commuting subspace of events~$\set{\sum_{\ket{k}\in E}\proj{k}}{E\subseteq\Omega}$,
+the quantum expectation values of the observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
+and the product observables~$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
+are equal to the Choquet integral of the corresponding random variables
+relative to the 0-deterministic classical IVPM~$\bar{\mu}'$ corresponding
+to $\bar{\mu}$. The Choquet integral relative to 0-deterministic
+$\bar{\mu}'$ is a singleton set. If we adopt the product rule of
+singleton sets, $\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $,
+we can can prove that the product of expectation values of the individual
+observables relative to $\bar{\mu}$ is the expectation value of the
+product of the family relative to $\bar{\mu}$~\citep{HOSTunpublished}:
 \begin{equation}
@@
 \end{equation}
-If the QIVPM $\bar{\mu}$ is 0-deterministic, the expectation value of
-each observable $\mathbf{O}_j$ given by
-Eq.~(\ref{eq:quantum-interval-expectation-core}) collapses to a single
-point
-
-this interval collapses
-to a singleton $\left\{ \lambda\right\} $, where $\lambda$ is an
-eigenvalue of~$\mathbf{O}$.
+because the Choquet integral relative to 0-deterministic $\bar{\mu}'$
+has the corresponding property.
 
@@
 When $\delta \ge \frac{1}{3}$, the situation abruptly
-changes. Assuming a Hilbert space $\Hilb$ of dimension $d \ge 3$, then
+changes. Assuming a Hilbert space $\Hilb$ of dimension $3$, then
 for any projector $P$ that projects onto an $n$-dimensional subspace

### 2017-08-27 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

@@
 $M$ commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$,
-they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
-By restricting to the commuting subspace of events~$\set{\sum_{\ket{k}\in E}\proj{k}}{E\subseteq\Omega}$,
-the quantum expectation values of the observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
+they can be diagonalized by a common orthonormal basis~$\Omega$.
+By restricting to the subspace of commuting events generated by the
+set of projectors associated with $\Omega$, the quantum expectation
+values of the observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
 and the product observables~$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
@@
 relative to the 0-deterministic classical IVPM~$\bar{\mu}'$ corresponding
-to $\bar{\mu}$. The Choquet integral relative to 0-deterministic
-$\bar{\mu}'$ is a singleton set. If we adopt the product rule of
-singleton sets, $\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $,
-we can can prove that the product of expectation values of the individual
-observables relative to $\bar{\mu}$ is the expectation value of the
-product of the family relative to $\bar{\mu}$~\citep{HOSTunpublished}:
-\begin{equation}
-\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
-\end{equation}
-because the Choquet integral relative to 0-deterministic $\bar{\mu}'$
-has the corresponding property.
+to $\bar{\mu}$~\citep{HOSTunpublished}. The Choquet integral relative
+to 0-deterministic $\bar{\mu}'$ is a singleton set which have an
+intuitive the product rule $\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
+Because the product of the Choquet integrals of individual random
+variables relative to $\bar{\mu}'$ is the Choquet integral of the
+product of the family relative to $\bar{\mu}'$, we can then prove
+that the expectation values of the observables has the corresponding
+property: 
+\begin{equation}
+\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
+\end{equation}
 

### 2017-08-28 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

@@
 
-If a QIVPM~$\bar{\mu}$ is 0-deterministic, then for a family of
-$M$ commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$,
-they can be diagonalized by a common orthonormal basis~$\Omega$.
-By restricting to the subspace of commuting events generated by the
-set of projectors associated with $\Omega$, the quantum expectation
-values of the observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
-and the product observables~$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
+If a QIVPM\nb$\bar{\mu}$ is 0-deterministic, a family of $M$ commuting
+observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ can be
+diagonalized by a common orthonormal basis~$\Omega$. By restricting
+to the subspace of commuting events generated by the set of projectors
+associated with $\Omega$, $\bar{\mu}$ become a 0-deterministic classical
+IVPM\nb$\bar{\mu}'$. Moreover, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
+and the product observables\nb$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
 are equal to the Choquet integral of the corresponding random variables
-relative to the 0-deterministic classical IVPM~$\bar{\mu}'$ corresponding
-to $\bar{\mu}$~\citep{HOSTunpublished}. The Choquet integral relative
-to 0-deterministic $\bar{\mu}'$ is a singleton set which have an
-intuitive the product rule $\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
+relative to $\bar{\mu}'$\nb\citep{HOSTunpublished}. The Choquet
+integral relative to $\bar{\mu}'$ is a singleton set which have an
+intuitive the product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
 Because the product of the Choquet integrals of individual random
 variables relative to $\bar{\mu}'$ is the Choquet integral of the
-product of the family relative to $\bar{\mu}'$, we can then prove
-that the expectation values of the observables has the corresponding
-property: 
+product of the family relative to $\bar{\mu}'$, the expectation values
+of the observables has the corresponding property: 
 \begin{equation}

### 2017-08-29 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for Classical IVPMs} Fix equation too long...
prop_iop.tex \subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability Measures\label{subsec:Quantum-I_D-valued-Probability}} Updating...

@@
 Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
-\begin{equation}
-\int X\rmd\bar{\mu}=\left[\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mul\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mur\left(E_{i}^{-\prime}\right),\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mur\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mul\left(E_{i}^{-\prime}\right)\right]\,.\label{eq:interval-expectation}
-\end{equation}
+\begin{equation}\eqalign{ 
+\int X\rmd\bar{\mu} = & \left[\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mul\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mur\left(E_{i}^{-\prime}\right),\right.\\  
+& \left.\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mur\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mul\left(E_{i}^{-\prime}\right)\right]\,.
+}\label{eq:interval-expectation}\end{equation}
 \end{definition}
@@
 
-\begin{proof}Since $\left\{ \mathbf{O}_{j}\right\} $ is a sequence
-of commuting observables, they can be diagonalized by a common orthonormal
-basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$. By theorem~\ref{thm:sub-event-space},
-there is a commuting sub-event space\nb$\widehat{\events}$ with
-$\widehat{\events}\subseteq\events$ and a bijection\nb$\tau:\widehat{\events}\rightarrow2^{\Omega}$
+\begin{proof}[Proof 1]Since $\left\{ \mathbf{O}_{j}\right\} $ is
+a sequence of commuting observables, they can be diagonalized by a
+common orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
+By theorem~\ref{thm:sub-event-space}, there is a commuting sub-event
+space\nb$\widehat{\events}$ with $\widehat{\events}\subseteq\events$
+and a bijection\nb$\tau:\widehat{\events}\rightarrow2^{\Omega}$
 such that there is a CIVPM\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}_{\mathrm{D}}$
@@
 
+\begin{proof}[Proof 2]Since $\left\{ \mathbf{O}_{j}\right\} $ is
+a sequence of commuting observables, they can be diagonalized by a
+common orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$,
+i.e., $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$ and
+$\prod_{j}\mathbf{O}_{j}=\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}$.
+By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
+real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
+Since $\mu$ is a cryptodeterministic measure, there is only one $\proj{k}$
+such that $\mu\left(\proj{k}\right)=1$.
+\begin{eqnarray*}
+ &  & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} \\
+ & = & \prod_{j}\left\{ \lambda_{j,k}\right\} =\left\{ \prod_{j}\lambda_{j,k}\right\} \\
+ & = & \expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.
+\end{eqnarray*}
+\end{proof}
+
 Based on the previous lemmas, we could follow Mermin's idea to prove

### 2017-08-29 prop_iop.tex
prop_iop.tex \subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability Measures\label{subsec:Quantum-I_D-valued-Probability}} Editing equations...

@@
 Therefore, 
-\begin{eqnarray*}
- &  & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\prod_{j}\int X_{j}\rmd\bar{\mu}'\\
- & \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-product}}{=} & \int\prod_{j}X_{j}\rmd\bar{\mu}'=\int\prod_{j}\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'\\
- & = & \int\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'=\expval{\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}}_{\bar{\mu}}\\
- & = & \expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.
-\end{eqnarray*}
+\begin{equation}\eqalign{ 
+ & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\prod_{j}\int X_{j}\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-product}}{=}\int\prod_{j}X_{j}\rmd\bar{\mu}'\\
+= & \int\prod_{j}\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'=\int\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'\\
+= & \expval{\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,. 
+}\end{equation}
 \end{proof}
@@
 such that $\mu\left(\proj{k}\right)=1$.
-\begin{eqnarray*}
- &  & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} \\
- & = & \prod_{j}\left\{ \lambda_{j,k}\right\} =\left\{ \prod_{j}\lambda_{j,k}\right\} \\
- & = & \expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.
-\end{eqnarray*}
+\begin{equation}\eqalign{ 
+ & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} =\prod_{j}\left\{ \lambda_{j,k}\right\} \\
+= & \left\{ \prod_{j}\lambda_{j,k}\right\} =\expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,. 
+}\end{equation}
 \end{proof}

### 2017-08-29 prop_iop.tex
prop_iop.tex \subsection{Between Expectation Values for Quantum Real-valued and Interval-valued Probability Measures} Updating...

@@
 \def\C{{\mathbb{C}}}
-\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
+\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
 \newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
+\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
 \end{equation}
@@
 
-\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+\begin{thm}\label{thm:quantum-Rosenmuller}Given a Hilbert space
+of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
@@
 \begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,.\label{eq:quantum-interval-expectation-core}
 \end{equation}
@@
  & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
- & \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.
+ & \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,.
 \end{eqnarray*}
@@
 \begin{equation}
-\left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.
+\left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,.
 \end{equation}
@@
 \end{eqnarray}
-By theorem~\ref{thm:sub-event-space},
-there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+By theorem~\ref{thm:sub-event-space}, there is a density matrix~$\rho$
+such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
 for all $P\in\events'$. Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
@@
 
-\begin{proof}Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
+\begin{proof}[Proof 1]Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
 we have
@@
 where $\mu'=\mul[\prime]=\mur[\prime]$.\end{proof}
+
+\begin{proof}[Proof 2]Let $\events'$ be the subspace of events
+induced by $\mathbf{O}$. For any state\nb$\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
+we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
+for all $P\in\events'$. Thus, $\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\expval{\mathbf{O}}_{\mu}$.
+By theorem~\ref{thm:quantum-Rosenmuller}, we have
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]=\left\{ \expval{\mathbf{O}}_{\mu}\right\}
+\end{equation}
+\end{proof}
 
@@
 real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
-Since $\mu$ is a cryptodeterministic measure, there is only one $\proj{k}$
-such that $\mu\left(\proj{k}\right)=1$.
+Since $\mu$ is a cryptodeterministic measure, there is only one $\proj{k_{0}}$
+such that $\mu\left(\proj{k_{0}}\right)=1$.
 \begin{equation}\eqalign{ 
- & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} =\prod_{j}\left\{ \lambda_{j,k}\right\} \\
-= & \left\{ \prod_{j}\lambda_{j,k}\right\} =\expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,. 
+ & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} =\prod_{j}\left\{ \lambda_{j,k_{0}}\right\} \\
+= & \left\{ \prod_{j}\lambda_{j,k_{0}}\right\} =\expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,. 
 }\end{equation}

### 2017-08-29 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

@@
 observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ can be
-diagonalized by a common orthonormal basis~$\Omega$. By restricting
-to the subspace of commuting events generated by the set of projectors
-associated with $\Omega$, $\bar{\mu}$ become a 0-deterministic classical
-IVPM\nb$\bar{\mu}'$. Moreover, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
+diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
+Since $\bar{\mu}$ is 0-deterministic, there is a quantum probability
+measure\nb$\mu$ such that $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
+and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$\nb\citep{HOSTunpublished}.
+Hence, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
 and the product observables\nb$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
-are equal to the Choquet integral of the corresponding random variables
-relative to $\bar{\mu}'$\nb\citep{HOSTunpublished}. The Choquet
-integral relative to $\bar{\mu}'$ is a singleton set which have an
-intuitive the product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
-Because the product of the Choquet integrals of individual random
-variables relative to $\bar{\mu}'$ is the Choquet integral of the
-product of the family relative to $\bar{\mu}'$, the expectation values
-of the observables has the corresponding property: 
+are equal to the singleton set\nb$\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} $
+and $\left\{ \expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\mu}\right\} $,
+respectively, which have an intuitive product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
+Since $\mu\left(\proj{k}\right)$ is either $0$ or $1$, there exists
+an unique $\ket{k_{0}}$ such that $\mu\left(\proj{k_{0}}\right)=1$
+and $\mu\left(\proj{k}\right)=0$ for $k\ne k_{0}$, both $\prod_{j=1}^{M}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} $
+and $\left\{ \expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\mu}\right\} $
+are equal to the product of the eigenvalues corresponding to the pure
+state\nb$\ket{k_{0}}$ for each observables. Therefore, we have the
+following property: 
 \begin{equation}

### 2017-08-30 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

@@
 and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$\nb\citep{HOSTunpublished}.
-Hence, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
-and the product observables\nb$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
-are equal to the singleton set\nb$\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} $
-and $\left\{ \expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\mu}\right\} $,
-respectively, which have an intuitive product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
-Since $\mu\left(\proj{k}\right)$ is either $0$ or $1$, there exists
-an unique $\ket{k_{0}}$ such that $\mu\left(\proj{k_{0}}\right)=1$
-and $\mu\left(\proj{k}\right)=0$ for $k\ne k_{0}$, both $\prod_{j=1}^{M}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} $
-and $\left\{ \expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\mu}\right\} $
-are equal to the product of the eigenvalues corresponding to the pure
-state\nb$\ket{k_{0}}$ for each observables. Therefore, we have the
-following property: 
+By denoting the product observables\nb$\prod_{j=1}^{M}\mathbf{O}_{j}$
+as $\overline{\mathbf{O}}$, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
+and $\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
+singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
+and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Also, since
+$\mu\left(\proj{k}\right)$ is either $0$ or $1$, there exists an
+unique $\ket{k_{0}}$ such that $\mu\left(\proj{k}\right)=1$ if and
+only if $k=k_{0}$. Both $\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$
+and $\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product
+of the eigenvalues corresponding to the pure state\nb$\ket{k_{0}}$
+for each observable\nb$\mathbf{O}_{j}$. By adopting an intuitive
+product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $,
+we have the following property: 
 \begin{equation}

### 2017-08-31 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

@@
 
-If a QIVPM\nb$\bar{\mu}$ is 0-deterministic, a family of $M$ commuting
-observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ can be
-diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
-Since $\bar{\mu}$ is 0-deterministic, there is a quantum probability
-measure\nb$\mu$ such that $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
-and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$\nb\citep{HOSTunpublished}.
-By denoting the product observables\nb$\prod_{j=1}^{M}\mathbf{O}_{j}$
+A 0-deterministic QIVPM\nb$\bar{\mu}$ has an important property
+regarding to the expectation values of a family of commuting observables
+relative to $\bar{\mu}$. A family of $M$ commuting observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
+can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
+Since $\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ exists
+such that $\bar{\mu}\left(\proj{k}\right)=\necess$ if and only if
+$k=k_{0}$\nb\citep{HOSTunpublished}. Also, a unique quantum probability
+measure\nb$\mu$ exists such that $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
+and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$.
+Especially, $\mu\left(\proj{k}\right)=1$ if and only if $k=k_{0}$.
+If we denote the product observables\nb$\prod_{j=1}^{M}\mathbf{O}_{j}$
 as $\overline{\mathbf{O}}$, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
@@
 singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
-and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Also, since
-$\mu\left(\proj{k}\right)$ is either $0$ or $1$, there exists an
-unique $\ket{k_{0}}$ such that $\mu\left(\proj{k}\right)=1$ if and
-only if $k=k_{0}$. Both $\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$
+and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Both $\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$
 and $\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product

### 2017-09-01 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating...

@@
 measurements invalidate the spirit of the Kochen-Specker
-theorem~\cite{kochenspecker1967,peres1995quantum}.  The Kochen-Specker  
+theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.  The Kochen-Specker  
 theorem is in essence a
@@
 information: the Kochen-Specker
-theorem~\cite{PeresRon1988,peres1995quantum}. Our finite-precision
+theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}. Our finite-precision
 extension of the theorem will suggest a resolution to the debate
@@
 determined with certainty. As $\delta$ gets bigger, the QIVPM allows
-more and more indeterminate behavior. Our technical result will be
+more and more indeterminate behavior. For example, when $\delta=\frac{1}{3}$,
+two possible collection of intervals\nb$\mathscr{I}$ are $\left\{ \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],\necess\right\} $
+and $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\left[\frac{5}{6},\frac{5}{6}\right],\necess\right\} $.
+Our technical result will be
 that for ``small enough'' $\delta$, a variant of the Kochen-Specker
@@
 A 0-deterministic QIVPM\nb$\bar{\mu}$ has an important property
-regarding to the expectation values of a family of commuting observables
-relative to $\bar{\mu}$. A family of $M$ commuting observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
-can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
-Since $\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ exists
-such that $\bar{\mu}\left(\proj{k}\right)=\necess$ if and only if
-$k=k_{0}$\nb\citep{HOSTunpublished}. Also, a unique quantum probability
-measure\nb$\mu$ exists such that $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
-and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$.
-Especially, $\mu\left(\proj{k}\right)=1$ if and only if $k=k_{0}$.
+regarding to the expectation values of a family of $M$ commuting
+observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ relative
+to $\bar{\mu}$. Since $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
+commutes, they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
+Since $\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ and
+a unique quantum probability measure\nb$\mu$ exists such that $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
+and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$;
+$\mu\left(\proj{k}\right)=1$ if and only if $k=k_{0}$\nb\citep{HOSTunpublished}.
 If we denote the product observables\nb$\prod_{j=1}^{M}\mathbf{O}_{j}$

### 2017-09-02 prop_letter.tex
Updates from ShareLaTeX

@@
 
-When $\delta=0$ , every event must be assigned a probability in either
-the interval $[0,0]$ or $[1,1]$, i.e., every event is completely
-determined with certainty. As $\delta$ gets bigger, the QIVPM allows
-more and more indeterminate behavior. For example, when $\delta=\frac{1}{3}$,
-two possible collection of intervals\nb$\mathscr{I}$ are $\left\{ \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],\necess\right\} $
-and $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\left[\frac{5}{6},\frac{5}{6}\right],\necess\right\} $.
-Our technical result will be
+When $\delta=0$, every event must be assigned a probability in either
+interval $[0,0]$ or $[1,1]$, i.e., every event is completely
+determined with certainty. As $\delta$ gets larger, the QIVPM allows for
+more indeterminate behavior. For example, when $\delta=\frac{1}{3}$,
+two possible collections of intervals\nb$\mathscr{I}$ could be 
+$\left\{ \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],
+\necess\right\}$ and $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],
+\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],
+\left[\frac{5}{6},\frac{5}{6}\right],\necess\right\}$. Our technical result will be
 that for ``small enough'' $\delta$, a variant of the Kochen-Specker
-theorem is still valid. To state and prove this result we will first
-reformulate the original Kochen-Specker as a statement regarding the
+result is still valid. To state and prove this generalization we will first
+reformulate the original Kochen-Specker theorem as a statement regarding the
 non-existence of $0$-deterministic QIVPM. We will then strengthen this

### 2017-09-03 prop_letter.tex
section KS is a messgit add prop_letter.tex git add prop_letter.tex

@@
 % Hence, it will not hyphenate too much surrounding words.
-\newcommand{\nb}{\nolinebreak[1]\ }
 \newcommand{\rmd}{\mathrm{d}}
@@
 $\sum_i \mu(P_i) = 1$.   Meyer showed that one {\it can\/}
-assign definite values $0$ or $1$ to the measurement outcome
+assign definite values $0$ or~$1$ to the measurement outcome
 $\mu(P_i)$ when the Hilbert space is defined over the field of
@@
 interval. Moreover the event $E\cup\overline{E}$ is the identity event
-covering the entire space; its probability interval should be $[1,1]$
-which is sharper than $[0.9,1.1]$. The problem is that the two
-intervals are correlated: there is more information in the combined
-event than in each event separately. In our example, even though the
-``true'' probability of $E$ can be anywhere in the range $[0.2,0.3]$
-and the ``true'' probability of~$\overline{E}$ can be in anywhere in
-the range $[0.7,0.8]$, the values are not independent. Any value of
-$\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq 0.75$. To account
-for such subtleties, the axioms of interval-valued probability do not
-use a strict equality for the combination of disjoint events. The
-correct constraint regarding the probability of $E_1\cup E_2$ when
-$E_1$ and $E_2$ are disjoint is
+covering the entire space; its probability interval should be
+$\necess$ which is sharper than $[0.9,1.1]$. The problem is that the
+two intervals are correlated: there is more information in the
+combined event than in each event separately. In our example, even
+though the ``true'' probability of $E$ can be anywhere in the range
+$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be in
+anywhere in the range $[0.7,0.8]$, the values are not independent. Any
+value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
+0.75$. To account for such subtleties, the axioms of interval-valued
+probability do not use a strict equality for the combination of
+disjoint events. The correct constraint regarding the probability of
+$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
 $\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
 combination with the requirement for the identity event would force
-$\mu(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
+$\mu(E \cup \overline{E})$ to always be $\necess$ irrespective of the
 particular assignments of $\mu(E)$ or~$\mu(\overline{E})$.
@@
 \begin{definition}[QIVPM]
-  Assume a collection of intervals $\mathscr{I}$ including
-  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
-  multiplication defined as follows:
+  Assume a collection of intervals $\mathscr{I}$ including $\imposs$
+  and $\necess$ with addition and scalar multiplication defined as
+  follows:
   \begin{subequations}\label{eq:interval-operations}
@@
   \begin{eqnarray}
-   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
-   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
-   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
+   &  & \bar{\mu}(\mathbb{0})=\imposs\,,\\
+   &  & \bar{\mu}(\mathbb{1})=\necess\,,\\
+   &  & \bar{\mu}\left(\mathbb{1}-P\right)= \necess -\bar{\mu}\left(P\right)\,,
   \end{eqnarray}
   \end{subequations}
-  and satisfying for each pair of \emph{commuting} projectors $P_0$
-  and $P_1$ with $P_0P_1=P_1P_0$,
+  and satisfying for each pair of \emph{commuting} projectors~$P_0$
+  and~$P_1$ with $P_0P_1=P_1P_0$,
 \begin{equation}
@@
 long version of this paper~\cite{HOSTunpublished}. The idea of the
-proof is as follows. Given a subspace of commuting events $\events_C$,
+proof is as follows. Given a subspace of commuting events~$\events_C$,
 we can construct a partial orthonormal basis by diagonalization and
@@
 information: the Kochen-Specker
-theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}. Our finite-precision
-extension of the theorem will suggest a resolution to the debate
-initiated by Meyer and Mermin on the relevance of the Kochen-Specker
-to experimental, and hence finite-precision, quantum
+theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}. Our
+finite-precision extension of the theorem will suggest a resolution to
+the debate initiated by Meyer and Mermin on the relevance of the
+Kochen-Specker to experimental, and hence finite-precision, quantum
 measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
@@
 the assumption that all observables of a quantum mechanical system
-have \emph{definite values at all times}~\cite{Held2016}. Our
-interval-valued probability framework will allow us to state, and
-prove, a stronger version of the theorem that holds even if the
-observables have values that are only definite up to some specific
-parameter that quantifies experimental uncertainty. Put differently,
-our stronger statement and theorem quantifies Mermin's
-intuition~\citep{Mermin1999}:
+have \emph{definite values at all times}~\cite{Held2016}, i.e., they
+have infinitely precise values at all times. Our interval-valued
+probability framework will allow us to state, and prove, a stronger
+version of the theorem that holds even if the observables have values
+that are only definite up to some precision specified by a parameter
+$\delta$. Put differently, our stronger statement and theorem
+quantifies Mermin's intuition~\citep{Mermin1999}:
 \begin{quote}
@@
 
-When $\delta=0$, every event must be assigned a probability in either
-interval $[0,0]$ or $[1,1]$, i.e., every event is completely
-determined with certainty. As $\delta$ gets larger, the QIVPM allows for
-more indeterminate behavior. For example, when $\delta=\frac{1}{3}$,
-two possible collections of intervals\nb$\mathscr{I}$ could be 
-$\left\{ \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],
-\necess\right\}$ and $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],
-\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],
-\left[\frac{5}{6},\frac{5}{6}\right],\necess\right\}$. Our technical result will be
-that for ``small enough'' $\delta$, a variant of the Kochen-Specker
-result is still valid. To state and prove this generalization we will first
-reformulate the original Kochen-Specker theorem as a statement regarding the
-non-existence of $0$-deterministic QIVPM. We will then strengthen this
-result to show the non-existence of any $\delta$-deterministic QIVPM
-when $\delta < 1/3$ and the Hilbert space dimension is greater than
-2.
-
-\amr{Fix below until next marker}
-
-A 0-deterministic QIVPM\nb$\bar{\mu}$ has an important property
-regarding to the expectation values of a family of $M$ commuting
-observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ relative
-to $\bar{\mu}$. Since $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
-commutes, they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
-Since $\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ and
-a unique quantum probability measure\nb$\mu$ exists such that $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
-and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$;
-$\mu\left(\proj{k}\right)=1$ if and only if $k=k_{0}$\nb\citep{HOSTunpublished}.
-If we denote the product observables\nb$\prod_{j=1}^{M}\mathbf{O}_{j}$
-as $\overline{\mathbf{O}}$, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
-and $\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
-singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
-and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Both $\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$
-and $\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product
-of the eigenvalues corresponding to the pure state\nb$\ket{k_{0}}$
-for each observable\nb$\mathbf{O}_{j}$. By adopting an intuitive
-product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $,
-we have the following property: 
-\begin{equation}
-\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
-\end{equation}
-
-\amr{End marker}
-
-We now state and prove a theorem that is equivalent in scope to the
-original Kochen-Specker theorem but that is formulated in terms of
-$0$-deterministic QIVPMs.
+\noindent The definition puts no restrictions on the choice of
+intervals, only on the assignment of intervals to events. When
+$\delta=0$, every event must be assigned a probability in either
+interval $\imposs$ or $\necess$, i.e., every event is completely
+determined with certainty. As $\delta$ gets larger, the QIVPM allows
+for more indeterminate behavior. % For example, when
+% $\delta=\frac{1}{3}$, two possible collections of
+% intervals\nb$\mathscr{I}$ could be
+% $\left\{
+%   \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],
+%   \necess\right\}$ and
+% $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],
+%   \left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],
+%   \left[\frac{5}{6},\frac{5}{6}\right],\necess\right\}$.
+Our technical result will be that for ``small enough'' $\delta$, a
+variant of the Kochen-Specker result is still valid. To state and
+prove this generalization we will first reformulate the original
+Kochen-Specker theorem as a statement regarding the non-existence of
+$0$-deterministic QIVPM. We will then strengthen this result to show
+the non-existence of any $\delta$-deterministic QIVPM when
+$\delta < 1/3$ and the Hilbert space dimension is greater than 2.
 
@@
   $\Hilb$ of dimension~$d\ge3$, there is no 0-deterministic
-  measure~$\bar{\mu}$ mapping every event to either $[0,0]$ or $[1,1]$.
+  measure~$\bar{\mu}$ mapping every event to either $\imposs$ or
+  $\necess$.
 \end{thm}
@@
 contradiction to the original Kochen-Specker theorem using the same
-nine observables $\mathbf{O}_{ij}$ used in the ``Mermin-Peres'' proof
-of the Kochen-Specker
-theorem~\cite{Mermin1990Simple,peres1995quantum}:
-{\renewcommand{\arraystretch}{2}%
+nine observables $\mathbf{O}_{ij}$ with both $i$ and $j$ in the range
+${1,2,3}$ used in the ``Mermin-Peres'' proof of the Kochen-Specker
+theorem~\cite{Mermin1990Simple,peres1995quantum}. These nine
+observables are given below: {\renewcommand{\arraystretch}{2}%
 \begin{center}
@@
 \noindent where
-$\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are Pauli
-matrices acting on a pair of spin-$\frac{1}{2}$ states.  The
-observables in the Mermin-Peres square must have expectation
-values~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.  In each row and
-column, the operators commute, and each operator is the product of two
-others, except in the third column, where
+$\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are the
+Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. These
+matrices satisfy
 $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+Furthermore we have that the observables in the square satisfy the
+following properties: each observable has expectation value~$1$
+or~$-1$; in each row and column, the observables commute; and in each
+row and column except the third column, each operator is the product
+of the other two. To find a QIVPM~$\bar{\mu}$ \ldots
+
 Therefore, it is clearly impossible to find a QIVPM~$\bar{\mu}$ such
@@
 Eq.~(\ref{eq:Kochen-Specker-Rules}).
+
+A 0-deterministic QIVPM~$\bar{\mu}$ has an important property
+regarding to the expectation values of a family of $M$ commuting
+observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ relative to
+$\bar{\mu}$. Since $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
+commutes, they can be diagonalized by a common orthonormal
+basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.  Since
+$\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ and a unique
+quantum probability measure~$\mu$ exists such that
+$\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $ and
+$\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$;
+$\mu\left(\proj{k}\right)=1$ if and only if
+$k=k_{0}$~\citep{HOSTunpublished}.  If we denote the product
+observables~$\prod_{j=1}^{M}\mathbf{O}_{j}$ as
+$\overline{\mathbf{O}}$, the expectation values of the
+observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$ and
+$\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
+singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
+and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Both
+$\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$ and
+$\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product of the
+eigenvalues corresponding to the pure state~$\ket{k_{0}}$ for each
+observable~$\mathbf{O}_{j}$. By adopting an intuitive product
+rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{
+  x_{0}x_{1}\right\} $, we have the following property:
+\begin{equation}
+\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
+\end{equation}
 
@@
 \end{subequations}
-It is straightforward to verify that $\bar{\mu}$ is a QIVPM. Then we will
-prove $\coreBorn\left(\bar{\mu},\events\right)$ is an empty set by
-contradiction. Suppose there is a
-state\nb$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
-for any\nb$P$, the state\nb$\rho$ must satisfy
+It is straightforward to verify that $\bar{\mu}$ is a QIVPM. Then we
+will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an empty set
+by contradiction. Suppose there is a state
+$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since
+$\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$ for any~$P$, the
+state~$\rho$ must satisfy:
 \begin{equation}
@@
 \end{equation}
-which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all $j$. However, the last equation never holds. 
-Thus, there is no state consistent with the QIVPM on all 
-projectors\nb$P\in\events$, so Gleason's theorem does not hold for at least this
-example.
+which implies
+$\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$ for all
+$j$. However, the last equation never holds.  Thus, there is no state
+consistent with the QIVPM on all projectors~$P\in\events$, so
+Gleason's theorem does not hold for at least this example.
 
@@
 \widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
- &  & \cup\left\{ \left[0,0\right],\left[1,1\right]\right\} 
+ &  & \cup\{ \imposs, \necess \}
 \end{eqnarray}

### 2017-09-03 prop_letter.tex
comments

@@
 
+\amr{Start comments}
+
+2 qubit system
+otimes is tensor product
+mathbb{1} is identity projector/observable/matrix
+expectation value relative to mubar
+explain why expectation value of 0-determinstic qivpm is eigen value
+of observable
+
 To explain why this result is equivalent to the original
@@
 nine observables $\mathbf{O}_{ij}$ with both $i$ and $j$ in the range
-${1,2,3}$ used in the ``Mermin-Peres'' proof of the Kochen-Specker
+$\{1,2,3\}$ used in the ``Mermin-Peres'' proof of the Kochen-Specker
 theorem~\cite{Mermin1990Simple,peres1995quantum}. These nine

### 2017-09-03 prop_iop.tex
prop_letter.tex Definition 2 Remove $d \ge 3$...

@@
 
-\begin{thm}\label{thm:quantum-Rosenmuller}Given a Hilbert space
-of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+\begin{thm}\label{thm:quantum-Rosenmuller}Given a Hilbert space,
+for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,

### 2017-09-03 prop_letter.tex
prop_letter.tex Definition 2 Remove $d \ge 3$...

@@
 \begin{definition}[Expectation Value of Observables over QIVPMs] Let
-  $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space of
-  dimension~$d\ge3$ with event space~$\events$; and $\mathbf{O}$ an
+  $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space
+  with event space~$\events$; and $\mathbf{O}$ an
   observable with spectral decomposition

### 2017-09-03 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Add the computation...

@@
 }
-\noindent where
-$\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are the
-Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. These
-matrices satisfy
-$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+\noindent where $\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\} $
+are the Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states.
+These matrices satisfy $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
 Furthermore we have that the observables in the square satisfy the
 following properties: each observable has expectation value~$1$
-or~$-1$; in each row and column, the observables commute; and in each
-row and column except the third column, each operator is the product
-of the other two. To find a QIVPM~$\bar{\mu}$ \ldots
+or~$-1$;
+
+\begin{table*}
+\caption{\label{tab:Mermin-Peres-Computation}Compute the expectation value
+of of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$, $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$,
+and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ relative to a 0-deterministic
+QIVPM~$\bar{\mu}$. During the computation, whenever $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
+$\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)$ and $\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)$
+must be the value list in the table. Therefore, $\expval{\mathbf{O}}_{\bar{\mu}}$
+is a singleton set.}
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+\hline 
+Observable~$\mathbf{O}$ & Spectral Decomposition~$1\cdot P_{1}-1\cdot P_{2}$ & $\bar{\mu}\left(P_{1}\right)$ & $\bar{\mu}\left(P_{2}\right)$ & $\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)$ & $\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)$ & $\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}$ & $\expval{\mathbf{O}}_{\bar{\mu}}$\tabularnewline
+\hline 
+\hline 
+$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{2}\right)-1\cdot\left(\proj{1}+\proj{3}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
+\hline 
+$\ensuremath{\sigma_{z}\otimes\mathbb{1}}$ & $1\cdot\left(\proj{0}+\proj{1}\right)-1\cdot\left(\proj{2}+\proj{3}\right)$ & $\necess$ & $\imposs$ & $1$ & $0$ & $1\cdot1-1\cdot0=1$ & $\left\{ 1\right\} $\tabularnewline
+\hline 
+$\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{3}\right)-1\cdot\left(\proj{1}+\proj{2}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
+\hline 
+\end{tabular}
+\end{table*}
+\yutsung{In order to understand the expectation value of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$,
+$\ensuremath{\sigma_{z}\otimes\mathbb{1}}$, and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$
+relative to a 0-deterministic QIVPM~$\bar{\mu}$, we first diagonalize
+these observables by the computational basis~$\Omega=\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $,
+where $\ket{0}=\ket{0}\otimes\ket{0}$, $\ket{1}=\ket{0}\otimes\ket{1}$,
+$\ket{2}=\ket{1}\otimes\ket{0}$, and $\ket{3}=\ket{1}\otimes\ket{1}$.
+Since $\bar{\mu}$ is 0-deterministic, there is a unique $\ket{k_{0}}\in\Omega$
+such that $\bar{\mu}\left(\proj{k_{0}}\right)=\necess$ and $\bar{\mu}\left(\proj{k}\right)=\imposs$
+for $k\ne k_{0}$~\citep{HOSTunpublished}. Without loss of generality,
+assume $k_{0}=1$, the expectation values can be computed step-by-step
+in Table~\ref{tab:Mermin-Peres-Computation}. They are singleton
+sets whose only element is the eigenvalue of the observable. By adopting
+an intuitive product rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $
+for singleton sets, these expectation values also satisfy the property~$\expval{\ensuremath{\mathbb{1}\otimes\sigma_{z}}}_{\bar{\mu}}\cdot\expval{\ensuremath{\sigma_{z}\otimes\mathbb{1}}}_{\bar{\mu}}=\expval{\ensuremath{\sigma_{z}\otimes\sigma_{z}}}_{\bar{\mu}}$
+since $\left(\ensuremath{\mathbb{1}\otimes\sigma_{z}}\right)\cdot\left(\ensuremath{\sigma_{z}\otimes\mathbb{1}}\right)=\left(\ensuremath{\sigma_{z}\otimes\sigma_{z}}\right)$.}
+
+\noindent in each row and column, the observables commute; and in
+each row and column except the third column, each operator is the
+product of the other two. To find a QIVPM~$\bar{\mu}$ \ldots{}
 

### 2017-09-04 prop_letter.tex
KS

--- 2017-09-03 prop_letter.tex
@@
 \begin{equation}
+\label{eq:hbar}
 \coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in \events',~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}.
@@
 determined with certainty. As $\delta$ gets larger, the QIVPM allows
-for more indeterminate behavior. % For example, when
-% $\delta=\frac{1}{3}$, two possible collections of
-% intervals\nb$\mathscr{I}$ could be
-% $\left\{
-%   \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],
-%   \necess\right\}$ and
-% $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],
-%   \left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],
-%   \left[\frac{5}{6},\frac{5}{6}\right],\necess\right\}$.
-Our technical result will be that for ``small enough'' $\delta$, a
-variant of the Kochen-Specker result is still valid. To state and
-prove this generalization we will first reformulate the original
-Kochen-Specker theorem as a statement regarding the non-existence of
-$0$-deterministic QIVPM. We will then strengthen this result to show
-the non-existence of any $\delta$-deterministic QIVPM when
-$\delta < 1/3$ and the Hilbert space dimension is greater than 2.
-
-\begin{thm} [0-Deterministic Variant of
+for more indeterminate behavior.
+
+The expectation value of an observable relative to a 0-deterministic
+QIVPM is fully determinate and is equal to one of the eigenvalues of
+that observable. To see this, note that given an orthonormal basis
+$\Omega=\{ \ket{\psi_0},\ket{\psi_1},\ldots\}$, a 0-deterministic
+QIVPM must map exactly one of the projectors $\proj{\psi_i}$ to
+$\necess$ and all others to $\imposs$. This is because by
+Eq.~(\ref{eq:QIVPM-constraints}b), we have
+$\bar{\mu}(\Sigma_i{\proj{\psi_i}})=\necess$ and by
+Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, we must have
+one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all others mapped to
+$\imposs$. Given any state~$\rho$ that is consistent with this QIVPM
+on all the projectors in $\Omega$, we have by Eq.~(\ref{eq:hbar}) that
+$\mu_{\rho}^{\mathrm{B}}$ must also map exactly one of the projectors
+to 1 and all others to 0. If an observable has a spectral
+decomposition along $\Omega$ then, by
+Eq.~(\ref{eq:quantum-expectation}), its expectation value relative to
+$\mu_{\rho}^{\mathrm{B}}$ is the eigenvalue $\lambda$ whose projector
+is mapped to 1. It therefore follows, by
+Eq.~(\ref{eq:quantum-interval-expectation-core}), that the expectation
+value relative to the 0-deterministic~${\bar{\mu}}$ is fully
+determinate and lies in the interval $[\lambda,\lambda]$.
+
+We can now proceed with our technical result which is that the
+original Kochen-Specker theorem is a statement regarding the
+non-existence of $0$-deterministic QIVPM.
+
+\begin{thm}[0-Deterministic Variant of
   Kochen-Specker] \label{thm:Kochen-Specker} Given a Hilbert space
@@
 
-\amr{Start comments}
-
-2 qubit system
-otimes is tensor product
-mathbb{1} is identity projector/observable/matrix
-expectation value relative to mubar
-explain why expectation value of 0-determinstic qivpm is eigen value
-of observable
-
-To explain why this result is equivalent to the original
+\noindent To explain why this result is equivalent to the original
 Kochen-Specker theorem and to prove it at the same time, we proceed by
 assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive a
-contradiction to the original Kochen-Specker theorem using the same
-nine observables $\mathbf{O}_{ij}$ with both $i$ and $j$ in the range
-$\{1,2,3\}$ used in the ``Mermin-Peres'' proof of the Kochen-Specker
-theorem~\cite{Mermin1990Simple,peres1995quantum}. These nine
-observables are given below: {\renewcommand{\arraystretch}{2}%
+contradiction to the original Kochen-Specker theorem. Our
+counterexample uses the simpler proof for a Hilbert space of dimension
+$d=4$ and is constructed as follows.
+
+We consider a 2-qubit Hilbert space $\Hilb=\Hilb_1\otimes\Hilb_2$
+representing pairs of spin-$\frac{1}{2}$ states. We use the same nine
+observables $\mathbf{O}_{ij}$ with $i$ and $j$ ranging over
+$\{0,1,2\}$ from the ``Mermin-Peres'' proof of the Kochen-Specker
+theorem~\cite{Mermin1990Simple,peres1995quantum}:
+
+{\renewcommand{\arraystretch}{2}%
 \begin{center}
-\begin{tabular}{|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|}
+\begin{tabular}{r|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|}
+$\mathbf{O}_{ij}$~ & $j=0$ & $j=1$ & $j=2$ \\
 \hline 
-$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
+$i=0~$ & $\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
 \hline 
-$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
+$i=1~$ & $\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
 \hline 
-$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
+$i=2~$ & $\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
 \hline 
@@
 }
-\noindent where
-$\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are the
-Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. These
-matrices satisfy
-$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
-Furthermore we have that the observables in the square satisfy the
-following properties: each observable has expectation value~$1$
-or~$-1$; in each row and column, the observables commute; and in each
-row and column except the third column, each operator is the product
-of the other two. To find a QIVPM~$\bar{\mu}$ \ldots
-
-Therefore, it is clearly impossible to find a QIVPM~$\bar{\mu}$ such
-that $\langle \mathbf{O}_{ij}\rangle_{\bar \mu}$ satisfies
-Eq.~(\ref{eq:Kochen-Specker-Rules}).
-
-A 0-deterministic QIVPM~$\bar{\mu}$ has an important property
-regarding to the expectation values of a family of $M$ commuting
-observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ relative to
-$\bar{\mu}$. Since $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
-commutes, they can be diagonalized by a common orthonormal
-basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.  Since
-$\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ and a unique
-quantum probability measure~$\mu$ exists such that
-$\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $ and
-$\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$;
-$\mu\left(\proj{k}\right)=1$ if and only if
-$k=k_{0}$~\citep{HOSTunpublished}.  If we denote the product
-observables~$\prod_{j=1}^{M}\mathbf{O}_{j}$ as
-$\overline{\mathbf{O}}$, the expectation values of the
-observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$ and
-$\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
-singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
-and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Both
-$\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$ and
-$\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product of the
-eigenvalues corresponding to the pure state~$\ket{k_{0}}$ for each
-observable~$\mathbf{O}_{j}$. By adopting an intuitive product
-rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{
-  x_{0}x_{1}\right\} $, we have the following property:
-\begin{equation}
-\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
-\end{equation}
-
-We can in fact generalize the above theorem to state that for small
-enough $\delta$, it is impossible to have $\delta$-deterministic
-QIVPMs. Every QIVPM must map some events to truly uncertain intervals,
-not just ``almost definite intervals.'' The significance of this
-observation is that the uncertainty in the intervals is, in contrast
-to the classical case, \emph{a fundamental part of quantum
-  theory}. There are in fact two sources of uncertainty: one due to
-the finite measurement resources and one due to complementarity, which
-requires every quantum framework to be truly probabilistic.
+
+\noindent The observables are constructed using the Pauli matrices
+$\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ whose
+eigenvalues are all either 1 or -1. They are arranged such that in
+each row and column, \emph{except the column $j=2$}, every observable
+is the product of the other two. In the $j=2$ column, we have instead
+that
+$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$. Now
+assume a QIVPM ${\bar{\mu}}$; the expectation values of the
+observables in each row relative to this QIVPM are fully determinate
+and must lie in either the interval $[1,1]$ or the interval $[-1,-1]$
+depending on which eigenvalue is the one whose associated projector is
+certain. Since the product of any two observables in a row is equal to
+the third, there must be an even number of occurrences of the interval
+$[-1,-1]$ in each row and hence in the entire table. However, looking
+at the expectation values of the observables in each column, there
+must be an even number of occurrences of the interval $[-1,-1]$ in the
+first two columns and an odd number in the $j=2$ column and hence in
+the entire table. The contradiction implies the non-existence of the
+assumed QIVPM.
+
+% \begin{table*}
+% \caption{\label{tab:Mermin-Peres-Computation}Compute the expectation value
+% of of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$, $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$,
+% and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ relative to a 0-deterministic
+% QIVPM~$\bar{\mu}$. During the computation, whenever $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
+% $\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)$ and $\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)$
+% must be the value list in the table. Therefore, $\expval{\mathbf{O}}_{\bar{\mu}}$
+% is a singleton set.}
+% \begin{tabular}{|c|c|c|c|c|c|c|c|}
+% \hline 
+% Observable~$\mathbf{O}$ & Spectral Decomposition~$1\cdot P_{1}-1\cdot P_{2}$ & $\bar{\mu}\left(P_{1}\right)$ & $\bar{\mu}\left(P_{2}\right)$ & $\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)$ & $\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)$ & $\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}$ & $\expval{\mathbf{O}}_{\bar{\mu}}$\tabularnewline
+% \hline 
+% \hline 
+% $\ensuremath{\mathbb{1}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{2}\right)-1\cdot\left(\proj{1}+\proj{3}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
+% \hline 
+% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$ & $1\cdot\left(\proj{0}+\proj{1}\right)-1\cdot\left(\proj{2}+\proj{3}\right)$ & $\necess$ & $\imposs$ & $1$ & $0$ & $1\cdot1-1\cdot0=1$ & $\left\{ 1\right\} $\tabularnewline
+% \hline 
+% $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{3}\right)-1\cdot\left(\proj{1}+\proj{2}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
+% \hline 
+% \end{tabular}
+% \end{table*}
+% \yutsung{In order to understand the expectation value of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$,
+% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$, and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$
+% relative to a 0-deterministic QIVPM~$\bar{\mu}$, we first diagonalize
+% these observables by the computational basis~$\Omega=\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $,
+% where $\ket{0}=\ket{0}\otimes\ket{0}$, $\ket{1}=\ket{0}\otimes\ket{1}$,
+% $\ket{2}=\ket{1}\otimes\ket{0}$, and $\ket{3}=\ket{1}\otimes\ket{1}$.
+% Since $\bar{\mu}$ is 0-deterministic, there is a unique $\ket{k_{0}}\in\Omega$
+% such that $\bar{\mu}\left(\proj{k_{0}}\right)=\necess$ and $\bar{\mu}\left(\proj{k}\right)=\imposs$
+% for $k\ne k_{0}$~\citep{HOSTunpublished}. Without loss of generality,
+% assume $k_{0}=1$, the expectation values can be computed step-by-step
+% in Table~\ref{tab:Mermin-Peres-Computation}. They are singleton
+% sets whose only element is the eigenvalue of the observable. By adopting
+% an intuitive product rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $
+% for singleton sets, these expectation values also satisfy the property~$\expval{\ensuremath{\mathbb{1}\otimes\sigma_{z}}}_{\bar{\mu}}\cdot\expval{\ensuremath{\sigma_{z}\otimes\mathbb{1}}}_{\bar{\mu}}=\expval{\ensuremath{\sigma_{z}\otimes\sigma_{z}}}_{\bar{\mu}}$
+% since $\left(\ensuremath{\mathbb{1}\otimes\sigma_{z}}\right)\cdot\left(\ensuremath{\sigma_{z}\otimes\mathbb{1}}\right)=\left(\ensuremath{\sigma_{z}\otimes\sigma_{z}}\right)$.}
+
+% A 0-deterministic QIVPM~$\bar{\mu}$ has an important property
+% regarding to the expectation values of a family of $M$ commuting
+% observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ relative to
+% $\bar{\mu}$. Since $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
+% commutes, they can be diagonalized by a common orthonormal
+% basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.  Since
+% $\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ and a unique
+% quantum probability measure~$\mu$ exists such that
+% $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $ and
+% $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$;
+% $\mu\left(\proj{k}\right)=1$ if and only if
+% $k=k_{0}$~\citep{HOSTunpublished}.  If we denote the product
+% observables~$\prod_{j=1}^{M}\mathbf{O}_{j}$ as
+% $\overline{\mathbf{O}}$, the expectation values of the
+% observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$ and
+% $\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
+% singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
+% and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Both
+% $\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$ and
+% $\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product of the
+% eigenvalues corresponding to the pure state~$\ket{k_{0}}$ for each
+% observable~$\mathbf{O}_{j}$. By adopting an intuitive product
+% rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{
+%   x_{0}x_{1}\right\} $, we have the following property:
+% \begin{equation}
+% \prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
+% \end{equation}
+
+Our framework allows us to generalize the above theorem to state that
+for small enough $\delta$, it is impossible to have
+$\delta$-deterministic QIVPMs. Every QIVPM must map some events to
+truly uncertain intervals, not just ``almost definite intervals.'' The
+significance of this observation is that the uncertainty in the
+intervals is, in contrast to the classical case, \emph{a fundamental
+  part of quantum theory}. There are in fact two sources of
+uncertainty: one due to the finite measurement resources and one due
+to complementarity, which requires every quantum framework to be truly
+probabilistic.
 
@@
 When $\delta \ge \frac{1}{3}$, the situation abruptly
-changes. Assuming a Hilbert space $\Hilb$ of dimension $3$, then
-for any projector $P$ that projects onto an $n$-dimensional subspace
-of $\Hilb$, it is straightforward to check that
+changes. Assuming a Hilbert space $\Hilb$ of dimension $3$, then for
+any projector $P$ that projects onto an $n$-dimensional subspace of
+$\Hilb$, it is straightforward to check that
 $\bar{\mu}\left(P\right)=\left[n/3,n/3\right]$ is a valid
-$\frac{1}{3}$-deterministic QIVPM.
-
-\amr{Explain significance}
+$\frac{1}{3}$-deterministic QIVPM. In other words, when the uncertainty
+in measurements becomes so large, the Kochen-Specker theorem no longer
+holds and it becomes possible to map every observable to some (quite
+inaccurate) probability interval.
 

### 2017-09-04 prop_letter.tex
prop_letter.tex \section{Gleason} Updated by Gerardo...
sec 4

@@
 determined with certainty. As $\delta$ gets larger, the QIVPM allows
-for more indeterminate behavior.
+for more indeterminate behavior. For example, assuming a set of
+intervals including $\imposs$, $\necess$, and
+$\{ [0,1/4], [1/4,1/2], [1/2,3/4], [3/4,1] \}$, the probability
+measure that maps every event to either $\imposs$ or $\necess$ would
+be a 0-deterministic QIVPM, and the probability measure that maps
+every event to one of $\imposs$, $\necess$, $[0,1/5]$, or $[4/5,1]$
+would be a $\delta$-deterministic QIVPM for every
+$1/5 \le \delta \le 1$.
 
@@
 $\mu_{\rho}^{\mathrm{B}}$ must also map exactly one of the projectors
-to 1 and all others to 0. If an observable has a spectral
+in $\Omega$ to 1 and all others to 0. If an observable has a spectral
 decomposition along $\Omega$ then, by
@@
 assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive a
-contradiction to the original Kochen-Specker theorem. Our
-counterexample uses the simpler proof for a Hilbert space of dimension
-$d=4$ and is constructed as follows.
+contradiction to the original Kochen-Specker theorem. Instead of
+adapting the more complicated proof for $d=3$, our counterexample uses
+the simpler proof for a Hilbert space of dimension $d=4$ and is
+constructed as follows.
 
@@
 $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$. Now
-assume a QIVPM ${\bar{\mu}}$; the expectation values of the
-observables in each row relative to this QIVPM are fully determinate
-and must lie in either the interval $[1,1]$ or the interval $[-1,-1]$
-depending on which eigenvalue is the one whose associated projector is
-certain. Since the product of any two observables in a row is equal to
-the third, there must be an even number of occurrences of the interval
-$[-1,-1]$ in each row and hence in the entire table. However, looking
-at the expectation values of the observables in each column, there
-must be an even number of occurrences of the interval $[-1,-1]$ in the
-first two columns and an odd number in the $j=2$ column and hence in
-the entire table. The contradiction implies the non-existence of the
-assumed QIVPM.
+assume a 0-deterministic QIVPM ${\bar{\mu}}$; the expectation values
+of the observables in each row relative to this 0-deterministic QIVPM
+are fully determinate and must lie in either the interval $[1,1]$ or
+the interval $[-1,-1]$ depending on which eigenvalue is the one whose
+associated projector is certain. Since the product of any two
+observables in a row is equal to the third, there must be an even
+number of occurrences of the interval $[-1,-1]$ in each row and hence
+in the entire table. However, looking at the expectation values of the
+observables in each column, there must be an even number of
+occurrences of the interval $[-1,-1]$ in the first two columns and an
+odd number in the $j=2$ column and hence in the entire table. The
+contradiction implies the non-existence of the assumed 0-deterministic
+QIVPM. We therefore prove a stronger statement of contextuality that
+includes the effects of finite-precision.
 
@@
 % \begin{equation}
-% \prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
+% \prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbF{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
 % \end{equation}
@@
 $\bar{\mu}\left(P\right)=\left[n/3,n/3\right]$ is a valid
-$\frac{1}{3}$-deterministic QIVPM. In other words, when the uncertainty
-in measurements becomes so large, the Kochen-Specker theorem no longer
-holds and it becomes possible to map every observable to some (quite
-inaccurate) probability interval.
+$\frac{1}{3}$-deterministic QIVPM. In other words, when the
+uncertainty in measurements becomes so large, the Kochen-Specker
+theorem no longer holds and it becomes possible to map every
+observable to some (quite inaccurate) probability interval, and hence
+the theory becomes non-contextual.
 

### 2017-09-04 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Add the suggestions from Gerardo...

--- 2017-09-04 prop_letter.tex
@@
 $\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ whose
-eigenvalues are all either 1 or -1. They are arranged such that in
+eigenvalues are all either 1 or $-1$. They are arranged such that in
 each row and column, \emph{except the column $j=2$}, every observable
@@
 $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$. Now
-assume a QIVPM ${\bar{\mu}}$; the expectation values of the
+assume a 0-deterministic QIVPM ${\bar{\mu}}$; the expectation values of the
 observables in each row relative to this QIVPM are fully determinate
@@
 for small enough $\delta$, it is impossible to have
-$\delta$-deterministic QIVPMs. Every QIVPM must map some events to
+$\delta$-deterministic QIVPMs. We therefore prove a stronger statement of 
+contextuality that includes the effects of finite-precision.
+Every QIVPM must map some events to
 truly uncertain intervals, not just ``almost definite intervals.'' The
@@
 holds and it becomes possible to map every observable to some (quite
-inaccurate) probability interval.
+inaccurate) probability interval and hence the theory becomes non-contextual.
 

### 2017-09-07 prop_letter.tex
intro but need to fix sentence about classical

@@
 A principal result is that recasting the Kochen-Specker theorem in
-terms of ``$\delta$-determinism'', with~$\delta$ 
-quantifying the effect of finite-precision uncertainties on measurement 
-outcomes, reducing to the purely deterministic
-Kochen-Specker case for $\delta=0$, can resolve the question of effect
-of finite precision and imperfections on contextuality.  A remarkable
-consequence of our analysis is that not only does the
-quantum-mechanical requirement for contextuality continue to hold,
-thus maintaining the Kochen-Specker result for a \emph{non-vanishing}
-range of $\delta$, but that at a \emph{certain fixed value} of
-$\delta$, there is a sharp transition, parallel in its consequences
-to, say, a phase transition, to \emph{non-contextuality}; that is,
-quantum mechanics suddenly fails to hold, and all variables can be
-specified simultaneously, turning the theory effectively into a
-classical theory that can be specified consistently by hidden
-variables.  
-\yutsung{The part after ``that is'' looks strange.
-\begin{enumerate}
-\item The Kochen-Specker theorem is not about quantum mechanics, is about whether
-quantum mechanics can be simulated by a non-contextual deterministic hidden
-variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
-doesn't make a lot sense.
-\item The question is whether there exist a QIVPM means ``a classical theory
-consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
-I need to check whether it qualities as a classical probabilistic hidden variable
-theory\ldots(?)
-\end{enumerate}
-}
-These results provide a new insight into the
-Meyer-Mermin debate by presenting a theory in which there is a
-\emph{parameter} interpolating between what appeared previously to be
-irreconcilable interpretations of contextuality.
+terms of ``$\delta$-determinism'', with~$\delta$ quantifying the
+effect of finite-precision uncertainties on measurement outcomes,
+reducing to the purely deterministic Kochen-Specker case for
+$\delta=0$, can resolve the question of the effect of finite precision
+and imperfections on contextuality.  A remarkable consequence of our
+analysis is that not only does the quantum-mechanical requirement for
+contextuality continue to hold, thus maintaining the Kochen-Specker
+result for a \emph{non-vanishing} range of $\delta$, but that at a
+\emph{certain fixed value} of $\delta$, there is a sharp transition,
+parallel in its consequences to, say, a phase transition, to
+\emph{non-contextuality}; that is, suddenly a quantum system can be
+simulated by a non-contextual hidden variable theory, turning the
+system effectively from a quantum system into a classical system. 
+% that is, quantum mechanics suddenly fails to hold, and all variables
+% can be specified simultaneously, turning the theory effectively into a
+% classical theory that can be specified consistently by hidden
+% variables.
+% \yutsung{The part after ``that is''
+%   looks strange.
+% \begin{enumerate}
+% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
+% quantum mechanics can be simulated by a non-contextual deterministic hidden
+% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
+% doesn't make a lot sense.
+% \item The question is whether there exist a QIVPM means ``a classical theory
+% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
+% I need to check whether it qualities as a classical probabilistic hidden variable
+% theory\ldots(?)
+% \end{enumerate}
+% }
+These results provide a new insight into the Meyer-Mermin debate by
+presenting a theory in which there is a \emph{parameter} interpolating
+between what appeared previously to be irreconcilable interpretations
+of contextuality.
 

### 2017-09-08 prop_letter.tex
prop_letter.tex Updating Andy's note...

@@
 correspond individually to at least one state's~$\rho'$, those states
-will converge to a unique state $\rho$ when the size of the intervals
-characterizing the uncertainties tends to zero, and the set of
-single-point QIVPMs densely covers the entire real interval $[0,1]$.
+will converge to a unique state $\rho$ in the limit as the size of the intervals
+characterizing the uncertainties goes to zero, and the set of
+single-point QIVPMs densely covers the entire real interval $[0,1]$ or the
+appropriate subset corresponding to a given quantum system.
 
@@
 \end{equation}
-Given a probability for every projector, we can associate an
-expectation value with an observable~$\mathbf{O}$ with spectral
+Given a probability for every projector, we can define the
+expectation value of an observable~$\mathbf{O}$ having spectral
 decomposition $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$ as:
@@
 
-A conventional quantum probability measure can be easily
-constructed if one knows the current state of the quantum system by
-using the Born rule.  Specifically, for each pure normalized quantum
+A conventional quantum probability measure can easily be
+constructed using the Born rule if one knows the current state of the quantum
+system.  Specifically, for each pure normalized quantum
 state~$\ket{\phi}$, the Born rule induces a probability measure
@@
 $\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
-$\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born rule
+$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
 induces a probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as
@@
 $\mathbf{O}$ with spectral decomposition
-$\mathbf{O} = \proj{0} + 2\,\proj{1} + 3\,\proj{2}$. Two fragments of
-valid probability measures $\mu_1$ and $\mu_2$ that can be associated
+$\mathbf{O} = \proj{0} + 2\,\proj{1} + 3\,\proj{2}$, i.e., $q_{j} = j$ and
+$\ket{\phi_{j}} = \ket{j - 1}$.
+Two fragments of valid probability measures $\mu_1$ and $\mu_2$ that can be associated
 with this space are: $\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
@@
 devices, an experimenter might only be able to determine that the
-probability of the event $\proj{0}$ is in the range $[0.49,0.51]$
+probability of the event $\proj{0}$ is concentrated in the range $[0.49,0.51]$
 instead of precisely 0.5. The spread in this range depends on the
@@
 the event~$E$ and~$1-r$ corresponds to the strength of evidence
-against the same event. The collection of intervals used in the
+against the same event. More generally, this inverval would be interpreted as
+the Guassian width of a probability distribution, but for notational convenience
+we will continue in the following to write this as a definite interval.
+The collection of intervals used in the
 definition of a probability measure must satisfy certain properties
@@
 we may conclude that $\mu(\overline{E}) = [0.7,0.8]$ for the
-complement event $\overline{E}$. In addition to these simple
+complementary event $\overline{E}$. In addition to these simple
 conditions, there are some subtle conditions on how intervals are
@@
 $\mu(E \cup \overline{E})$ to always be $\necess$ irrespective of the
-particular assignments of $\mu(E)$ or~$\mu(\overline{E})$.
+particular assignments of $\mu(E)$ or~$\mu(\overline{E})$. Parallel arguments
+can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
+essential new information seems to be introduced.
 
@@
 generalization to QIVPMs implies that this expectation value will
-itself become bounded by an interval.
+itself become bounded by or, more generally distributed around, an interval.
 
@@
   subspace of events containing all the projectors $P_i$ in the
-  spectral decomposition of $\mathbf{O}$, then we define:
+  spectral decomposition of $\mathbf{O}$ and define:
 \begin{equation}
@@
 $\coreBorn\left(\bar{\mu},\events'\right)$ will contain the singleton
-state $\rho$ and both endpoints of the interval will agree, thus
+state $\rho$ and the interval collapses to a point, thus
 reducing the definition to that of

### 2017-09-09 prop_letter.tex
prop_letter.tex Keep Updating Andy's note...

@@
 and the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents
-the situation in which that an experimenter knows nothing about a coin
+the situation in which an experimenter knows nothing about a coin
 before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
@@
 measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
-Specifically, the original Kochen-Specker theorem is formulated under
-the assumption that all observables of a quantum mechanical system
-have \emph{definite values at all times}~\cite{Held2016}, i.e., they
+Specifically, the original Kochen-Specker theorem is formulated
+using a model quantum mechanical system that
+has \emph{definite values at all times}~\cite{Held2016}, i.e., they
 have infinitely precise values at all times. Our interval-valued
@@
 that are only definite up to some precision specified by a parameter
-$\delta$. Put differently, our stronger statement and theorem
-quantifies Mermin's intuition~\citep{Mermin1999}:
+$\delta$. Our approach provides a quantitative realization of
+Mermin's intuition~\citep{Mermin1999}:
 \begin{quote}
@@
 The first step in our formalization is to introduce a family of QIVPMs
-parameterized by an uncertainty~$\delta$ which we call
+parameterized by an uncertainty~$\delta$, which we call
 $\delta$-deterministic QIVPMs.
@@
 intervals, only on the assignment of intervals to events. When
-$\delta=0$, every event must be assigned a probability in either
-interval $\imposs$ or $\necess$, i.e., every event is completely
+$\delta=0$, every event must be assigned a probability either in the
+interval $\imposs$ or in $\necess$, i.e., every event is completely
 determined with certainty. As $\delta$ gets larger, the QIVPM allows
@@
 Eq.~(\ref{eq:QIVPM-constraints}b), we have
-$\bar{\mu}(\Sigma_i{\proj{\psi_i}})=\necess$ and by
-Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, we must have
+$\bar{\mu}(\Sigma_i{\proj{\psi_i}})=\necess$ and by inductively applying
+Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion} , we must have
 one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all others mapped to

### 2017-09-09 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Adding an example...

@@
 average.
+
+For example, we can extend one of the fragments of valid probability
+measures~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy} to a QIVPM~$\bar{\mu}_{3}$:
+$\bar{\mu}_{3}(\proj{0})=\left[0.5,0.5\right]$, $\bar{\mu}_{3}(\proj{1})=\left[0.5,0.5\right]$,
+and $\bar{\mu}_{3}(\proj{2})=\left[0,0\right]$. For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
+the Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ of any state~$\rho$
+consistent with $\bar{\mu}_{3}$ on $\proj{0}$, $\proj{1}$, and
+$\proj{2}$ must be $\mu_{1}$. Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
+which is an interval, but not between $0$ and $1$ because it is
+not a probability of an event.
 

### 2017-09-10 prop_letter.tex
prop_letter.tex Finish Updating the easy parts of Andy's note...

@@
 
-We can now proceed with our technical result which is that the
+We can now proceed with our technical result, which is that the
 original Kochen-Specker theorem is a statement regarding the
@@
 Kochen-Specker theorem and to prove it at the same time, we proceed by
-assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive a
-contradiction to the original Kochen-Specker theorem. Instead of
+assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive the same
+contradiction as the original Kochen-Specker theorem. Instead of
 adapting the more complicated proof for $d=3$, our counterexample uses
@@
 
-The proof is by contradiction: suppose there is a
+The proof is by contradiction: Suppose there is a
 $\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. We claim that the
 following
@@
 consistent with the QIVPM on all projectors~$P\in\events$, so
-Gleason's theorem does not hold for at least this example.
+Gleason's theorem does not hold, at least for this example.
 
@@
 which are overlapping intervals with length~$1/n$ except the intervals
-at each end.
+at length~$\left(2n\right)^{-1}$ at each end.
 

### 2017-09-10 prop_letter.tex
prop_letter.tex Adding two comments...

@@
 each pair of orthogonal projectors~$P_0 \in \events'$ and
-$P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. Given a
+$P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. 
+\yutsung{{Check this definition with convex?}}Given a
 probability measure $\bar{\mu}$ and a subspace of events $\events'$,
@@
 $\bar{\mu}(\Sigma_i{\proj{\psi_i}})=\necess$ and by inductively applying
-Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion} , we must have
+Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, \yutsung{Check whether
+we can explain how to apply
+Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion} in this situation
+better.} we must have
 one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all others mapped to

### 2017-09-10 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Updating...

@@
 (Born) probability measure induced by a state $\rho$, then
-$\coreBorn\left(\bar{\mu},\events'\right)$ will contain the singleton
-state $\rho$ and the interval collapses to a point, thus
+the Born rule probability induced by every state in
+$\coreBorn\left(\bar{\mu},\events'\right)$ will be
+$\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point, thus
 reducing the definition to that of
-Eq.~(\ref{eq:quantum-expectation}). We also note that, when restricted
-to commuting projectors, the definition above is consistent with the
-classical notion of the \emph{Choquet
-  integral}~\cite{GilboaSchmeidler1994,Grabisch2016} which is used to
-calculate the expectation value of random variables as a weighted
-average.
-
+Eq.~(\ref{eq:quantum-expectation}).
 For example, we can extend one of the fragments of valid probability
@@
 which is an interval, but not between $0$ and $1$ because it is
-not a probability of an event.
+not a probability of an event. We also note that, when restricted
+to commuting projectors, the definition above is consistent with the
+classical notion of the \emph{Choquet
+  integral}~\cite{GilboaSchmeidler1994,Grabisch2016} which is used to
+calculate the expectation value of random variables as a weighted
+average.
 

### 2017-09-10 prop_iop.tex
prop_iop.tex \subsection{Classical and Quantum Probability Measures} Updating a deinition...

@@
 \begin{definition}\label{def:sub-event-space}Given a Hilbert space
-$\Hilb$, $\events'\subseteq\events$ is called a sub-event space
-if it satisfies the follow conditions.
+$\Hilb$, a set of event~$\events'\subseteq\events$ is called a
+subspace if it satisfies the follow conditions.
 \begin{itemize}
@@
 it is straightforward to define a quantum cryptodeterministic, real-valued
-probability, and interval-valued probability measure on $\events'$.\end{definition}
+probability, and interval-valued probability measure on $\events'$.{
+Also, }$\events'$ is called convex if we have $P_{1}P_{2}\in\events'$
+for a pair of mutually commuting projections $P_{1}$ and $P_{2}\in\events'$.\end{definition}
 
@@
 \item $\tau\left(\mathbb{1}\right)=\Omega$.
-\item For any projection $P\in\widehat{\events}$, we have $\tau\left(\mathbb{1}-P\right)=\Omega-\tau\left(P\right)$.
+\item For any projection $P\in\widehat{\events}$, we have $\tau\left(\mathbb{1}-P\right)=\Omega\backslash\tau\left(P\right)$.
 \item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\widehat{\events}$,
-we have $\tau\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\tau\left(P_{i}\right)$.
+we have $\tau\left(\sum_{i=1}^{N}P_{i}\right)=\bigcup_{i=1}^{N}\tau\left(P_{i}\right)$.
+\item For a pair of mutually commuting projections $P_{1}$ and $P_{2}\in\events'$,
+we have $\tau\left(P_{1}P_{2}\right)=\tau\left(P_{1}\right)\cap\tau\left(P_{2}\right)$.
 \end{itemize}
@@
 \begin{definition}Given an observable~$\mathbf{O}$ with its spectral
-decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
-is called a sub-event space induced by $\mathbf{O}$ if it is the
-minimal sub-event space satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.\end{definition}
+decomposition~(\ref{eq:spectrum-decomposition}). A subspace of events~$\events'\subseteq\events$
+is called a subspace of events induced by $\mathbf{O}$ if it is the
+minimal subspace of events satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
+Obvious, $\events'$ is convex.\end{definition}
 

### 2017-09-10 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Updating...

@@
 \emph{subspace} if it contains $\mathbb{0}$ and~$\mathbb{1}$ and is
-closed under complements and sums, i.e., for any
-projector~$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for
-each pair of orthogonal projectors~$P_0 \in \events'$ and
-$P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. 
-\yutsung{{Check this definition with convex?}}Given a
+closed under complements, sums, and product, i.e., for any projector~$P\in\events'$,
+we have $\mathbb{1}-P\in\events'$ and for each pair of commuting
+projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have $P_{0}+P_{1}-P_{0}P_{1}$
+and $P_{0}P_{1}\in\events'$. Given a
 probability measure $\bar{\mu}$ and a subspace of events $\events'$,

### 2017-09-11 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \section{Gleason}
+
 \label{sec:Gleason}
 
-In the classical setting, measurements done with limited resources and
-poor precision may not uniquely identify the true state of a
-system. However, there is always at least one state that is consistent
-with the imprecise measurements.
+While the finite-precision extension of Kochen-Specker theorem asserts
+the non-existence of certain QIVPMs, we also want to understand what
+a QIVPM can be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
+the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
+probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
+In this section, we first generalize this result, and then show general
+QIVPMs may not be induced by any classical IVPM, i.e., no state is
+consistent with these kind of QIVPMs.
+
+When we induce $\bar{\mu}_{3}$ by $\mu_{1}$ in Sec.~\ref{sec:Interval-Uncertainty},
+we replace $0$ and $0.5$ by $\left[0,0\right]$ and $\left[0.5,0.5\right]$
+which are essentially the same as the replaced real numbers. In general,
+if we carefully pick a set of overlapping intervals, we can replace
+the numbers by the interval containing it. For example, consider the
+following collection of intervals: 
+\begin{eqnarray}
+\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
+ &  & \cup\{\imposs,\necess\}
+\end{eqnarray}
+which are overlapping intervals with length~$1/n$ except the intervals
+at length~$\left(2n\right)^{-1}$ at each end. Then, any state~$\rho$
+on a three-dimensional Hilbert space can induce a QIVPM over the intervals
+above as follows. We first define a map $\widehat{\iota}_{n}$ from
+the interval $[0,1]$ to the collection of intervals as: 
+\begin{itemize}
+\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$; 
+\item when $0<x<1$, $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
+where $k$ is defined by one of the following: 
+\begin{enumerate}
+\item $k$ even and $\frac{k-0.5}{2n}\le x\le\frac{k+0.5}{2n}$; 
+\item $k$ odd and $\frac{k-0.5}{2n}<x<\frac{k+0.5}{2n}$. 
+\end{enumerate}
+\end{itemize}
+It is now not difficult to verify that $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+is a QIVPM. For example, consider $n=2$, 
+\begin{eqnarray}
+\widehat{\mathscr{I}}_{1} & = & \set{\left[\frac{k-1}{4},\frac{k+1}{4}\right]\cap\left[0,1\right]}{k=0,\ldots,4}\cup\{\imposs,\necess\}\nonumber \\
+ & = & \{\imposs,\left[0,\frac{1}{4}\right],\left[0,\frac{1}{2}\right],\left[\frac{1}{4},\frac{3}{4}\right],\left[\frac{1}{2},1\right],\left[\frac{1}{4},1\right],\necess\}\,.
+\end{eqnarray}
+\begin{table}
+\caption{\label{tab:Compute-the-QIVPM}Compute the QIVPM~$\widehat{\iota}_{2}\circ\mu_{1}$
+from $\mu_{1}$}
+\end{table}
+Then, $\widehat{\iota}_{2}\circ\mu_{1}$, the QIVPM induced by $\mu_{1}$,
+can be computed by Table~\ref{tab:Compute-the-QIVPM}.
+
+\yutsung{Clean up until here.}
+
+In the classical setting, measurements done with limited resources
+and poor precision may not uniquely identify the true state of a system.
+However, there is always at least one state that is consistent with
+the imprecise measurements.
 

### 2017-09-11 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 the non-existence of certain QIVPMs, we also want to understand what
-a QIVPM can be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
+a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
 the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
 probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
-In this section, we first generalize this result, and then show general
+In this section, this result is generalized first, and then show some
 QIVPMs may not be induced by any classical IVPM, i.e., no state is
@@
 we replace $0$ and $0.5$ by $\left[0,0\right]$ and $\left[0.5,0.5\right]$
-which are essentially the same as the replaced real numbers. In general,
-if we carefully pick a set of overlapping intervals, we can replace
-the numbers by the interval containing it. For example, consider the
-following collection of intervals: 
+which are the smallest intervals containing these two numbers. In
+general, if we carefully pick a set of overlapping intervals, we can
+replace the numbers by the interval containing it. For example, consider
+the following collection of intervals: 
 \begin{eqnarray}

### 2017-09-13 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

--- 2017-09-10 prop_letter.tex
@@
 \section{Gleason}
+
 \label{sec:Gleason}
 
-In the classical setting, measurements done with limited resources and
-poor precision may not uniquely identify the true state of a
-system. However, there is always at least one state that is consistent
-with the imprecise measurements.
+While the finite-precision extension of Kochen-Specker theorem asserts
+the non-existence of certain QIVPMs, we also want to understand what
+a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
+the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
+probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
+This result will first be generalized, and then we will show some
+QIVPMs may not be induced by any classical IVPM, i.e., no state is
+consistent with these kind of QIVPMs.
+
+The quantum probability measure~$\mu_{1}$ maps some projectors to
+$0$ or $0.5$, which are replaced by $\left[0,0\right]$ or $\left[0.5,0.5\right]$
+to get $\bar{\mu}_{3}$. This is replacing two numbers by the smallest
+intervals containing them. In general, any set of the numbers can
+be replaced by the interval containing them if we carefully pick a
+set of overlapping intervals. For example, consider the following
+collection of intervals: 
+\begin{eqnarray}
+\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
+ &  & \cup\{\imposs,\necess\}
+\end{eqnarray}
+which are overlapping intervals with length~$1/n$ except the intervals
+at length~$\left(2n\right)^{-1}$ at each end. Then, any Born rule
+probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional Hilbert
+space can induce a QIVPM over the intervals above as follows. We first
+define a map $\widehat{\iota}_{n}$ from $[0,1]$ to $\widehat{\mathscr{I}}_{n}$
+as: 
+\begin{itemize}
+\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$; 
+\item when $0<x<1$, $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
+where $k$ is defined by one of the following: 
+\begin{enumerate}
+\item $k$ even and $\frac{k-0.5}{2n}\le x\le\frac{k+0.5}{2n}$; 
+\item $k$ odd and $\frac{k-0.5}{2n}<x<\frac{k+0.5}{2n}$. 
+\end{enumerate}
+\end{itemize}
+It is now not difficult to verify that $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+is a QIVPM. For example, consider $n=2$, 
+\begin{eqnarray}
+\widehat{\mathscr{I}}_{1} & = & \set{\left[\frac{k-1}{4},\frac{k+1}{4}\right]\cap\left[0,1\right]}{k=0,\ldots,4}\nonumber \\
+ &  & \cup\{\imposs,\necess\}\nonumber \\
+ & = & \left\{ \imposs,\left[0,\frac{1}{4}\right],\left[0,\frac{1}{2}\right],\left[\frac{1}{4},\frac{3}{4}\right],\right.\nonumber \\
+ &  & \left.\left[\frac{1}{2},1\right],\left[\frac{1}{4},1\right],\necess\right\} \,.
+\end{eqnarray}
+Then, $\widehat{\iota}_{2}\circ\mu_{1}$, the QIVPM induced by $\mu_{1}$,
+can be computed by Table~\ref{tab:Compute-the-QIVPM}.
+\begin{table}
+\caption{\label{tab:Compute-the-QIVPM}Compute the QIVPM~$\widehat{\iota}_{2}\circ\mu_{1}$
+from $\mu_{1}$}
+\end{table}
+
+\yutsung{Clean up until here.}
+
+In the classical setting, measurements done with limited resources
+and poor precision may not uniquely identify the true state of a system.
+However, there is always at least one state that is consistent with
+the imprecise measurements.
 

### 2017-09-13 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \usepackage[backref=false]{hyperref}
+\usepackage{booktabs}
 
@@
 which are overlapping intervals with length~$1/n$ except the intervals
-at length~$\left(2n\right)^{-1}$ at each end. Then, any Born rule
-probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional Hilbert
-space can induce a QIVPM over the intervals above as follows. We first
-define a map $\widehat{\iota}_{n}$ from $[0,1]$ to $\widehat{\mathscr{I}}_{n}$
-as: 
-\begin{itemize}
-\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$; 
-\item when $0<x<1$, $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
-where $k$ is defined by one of the following: 
-\begin{enumerate}
-\item $k$ even and $\frac{k-0.5}{2n}\le x\le\frac{k+0.5}{2n}$; 
-\item $k$ odd and $\frac{k-0.5}{2n}<x<\frac{k+0.5}{2n}$. 
-\end{enumerate}
-\end{itemize}
-It is now not difficult to verify that $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-is a QIVPM. For example, consider $n=2$, 
+at length~$\left(2n\right)^{-1}$ at each end. Then, we can define
+a QIVPM mapping to $\widehat{\mathscr{I}}_{n}$ based on any Born
+rule probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional
+Hilbert space by replacing the probability~$\mu_{\rho}^{\mathrm{B}}\left(P\right)$
+with the interval containing it, $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.
+Since intervals in $\widehat{\mathscr{I}}_{n}$ are overlapping, if
+$\mu_{\rho}^{\mathrm{B}}\left(P\right)$ are contained in both intervals~$[\ell_{1},r_{1}]$
+and $[\ell_{2},r_{2}]$, $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
+will be $[\ell_{i},r_{i}]$ if $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
+is closer to the center of $[\ell_{i},r_{i}]$. When there is a tie,
+we set $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$
+if $k$ even. For example, consider $n=2$, 
 \begin{eqnarray}
@@
 \end{eqnarray}
-Then, $\widehat{\iota}_{2}\circ\mu_{1}$, the QIVPM induced by $\mu_{1}$,
-can be computed by Table~\ref{tab:Compute-the-QIVPM}.
+$\widehat{\iota}_{2}\circ\mu_{1}$ can be computed by Table~\ref{tab:Compute-the-QIVPM}.
 \begin{table}
 \caption{\label{tab:Compute-the-QIVPM}Compute the QIVPM~$\widehat{\iota}_{2}\circ\mu_{1}$
-from $\mu_{1}$}
+from $\mu_{1}$ on the minimal subspace of events containing $\proj{0}$,
+$\proj{1}$, and $\proj{2}$.}
+\begin{tabular}{ccc}
+\toprule 
+$P$ & $\mu_{1}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{1}\left(P\right)\right)$\tabularnewline
+\midrule
+\midrule 
+$\mathbb{0}$ & $0$ & $\left[0,0\right]$\tabularnewline
+\midrule 
+$\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+\midrule 
+$\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+\midrule 
+$\proj{2}$ & $0$ & $\left[0,0\right]$\tabularnewline
+\midrule 
+$\mathbb{1}-\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+\midrule 
+$\mathbb{1}-\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+\midrule 
+$\mathbb{1}-\proj{2}$ & $1$ & $\left[1,1\right]$\tabularnewline
+\midrule 
+$\mathbb{1}$ & $1$ & $\left[1,1\right]$\tabularnewline
+\bottomrule
+\end{tabular}
 \end{table}
+It is clear that $\widehat{\iota}_{2}\circ\mu_{1}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}).
+For Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
 

### 2017-09-13 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

--- 2017-09-13 prop_letter.tex
@@
 \end{eqnarray}
-Then, $\widehat{\iota}_{2}\circ\mu_{1}$, the QIVPM induced by $\mu_{1}$,
-can be computed by Table~\ref{tab:Compute-the-QIVPM}.
+$\widehat{\iota}_{2}\circ\mu_{1}$ can be computed by Table~\ref{tab:Compute-the-QIVPM}.
 \begin{table}
 \caption{\label{tab:Compute-the-QIVPM}Compute the QIVPM~$\widehat{\iota}_{2}\circ\mu_{1}$
-from $\mu_{1}$}
+from $\mu_{1}$ on the minimal subspace of events containing $\proj{0}$,
+$\proj{1}$, and $\proj{2}$.}
+\begin{tabular}{ccc}
+\toprule 
+$P$ & $\mu_{1}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{1}\left(P\right)\right)$\tabularnewline
+\midrule
+\midrule 
+$\mathbb{0}$ & $0$ & $\left[0,0\right]$\tabularnewline
+\midrule 
+$\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+\midrule 
+$\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+\midrule 
+$\proj{2}$ & $0$ & $\left[0,0\right]$\tabularnewline
+\midrule 
+$\mathbb{1}-\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+\midrule 
+$\mathbb{1}-\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+\midrule 
+$\mathbb{1}-\proj{2}$ & $1$ & $\left[1,1\right]$\tabularnewline
+\midrule 
+$\mathbb{1}$ & $1$ & $\left[1,1\right]$\tabularnewline
+\bottomrule
+\end{tabular}
 \end{table}
+Let $\bar{\mu}_{4}$ be $\widehat{\iota}_{2}\circ\mu_{1}$. It is
+clear that $\bar{\mu}_{4}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}).
+For Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+given a pair of commuting projectors~$P_{0}$ and $P_{1}$ on a three-dimensional
+Hilbert space, one of the following must hold:
+\begin{enumerate}
+\item When the pair of $P_{0}$ and $P_{1}$ is the same as the pair $P_{0}P_{1}$
+and $P_{0}+P_{1}-P_{0}P_{1}$, we have $\bar{\mu}_{4}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}_{4}\left(P_{0}P_{1}\right)=\bar{\mu}_{4}\left(P_{0}\right)+\bar{\mu}_{4}\left(P_{1}\right)$,
+so that Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+clearly holds.
+\item When either $P_{0}P_{1}=\mathbb{0}$ or $P_{0}+P_{1}-P_{0}P_{1}=\mathbb{1}$,
+we must have 
+\begin{eqnarray}
+ &  & \bar{\mu}_{4}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}_{4}\left(P_{0}P_{1}\right)\nonumber \\
+ & \subseteq & \left[\mu_{1}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\mu_{1}\left(P_{0}P_{1}\right)-\frac{1}{4},\right.\nonumber \\
+ &  & \left.\mu_{1}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\mu_{1}\left(P_{0}P_{1}\right)+\frac{1}{4}\right]\nonumber \\
+ & = & \left[\mu_{1}\left(P_{0}\right)+\mu_{1}\left(P_{1}\right)-\frac{1}{4},\mu_{1}\left(P_{0}\right)+\mu_{1}\left(P_{1}\right)+\frac{1}{4}\right]\nonumber \\
+ & \subseteq & \bar{\mu}_{4}\left(P_{0}\right)+\bar{\mu}_{4}\left(P_{1}\right)\,.
+\end{eqnarray}
+\end{enumerate}
+Therefore, $\bar{\mu}_{4}$ is a QIVPM.
 

### 2017-09-14 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

--- 2017-09-13 prop_letter.tex
@@
    &  & \bar{\mu}(\mathbb{0})=\imposs\,,\\
-   &  & \bar{\mu}(\mathbb{1})=\necess\,,\\
+   &  & \bar{\mu}(\mathbb{1})=\necess\,,\label{eq:necess}\\
    &  & \bar{\mu}\left(\mathbb{1}-P\right)= \necess -\bar{\mu}\left(P\right)\,,
@@
 $\necess$ and all others to $\imposs$. This is because by
-Eq.~(\ref{eq:QIVPM-constraints}b), we have
+Eq.~(\ref{eq:necess}), we have
 $\bar{\mu}(\Sigma_i{\proj{\psi_i}})=\necess$ and by inductively applying
-Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, \yutsung{Check whether
+Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), \yutsung{Check whether
 we can explain how to apply
-Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion} in this situation
+Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) in this situation
 better.} we must have
@@
 we set $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$
-if $k$ even. For example, consider $n=2$, 
+for even $k$. For example, when $n=2$, 
 \begin{eqnarray}
-\widehat{\mathscr{I}}_{1} & = & \set{\left[\frac{k-1}{4},\frac{k+1}{4}\right]\cap\left[0,1\right]}{k=0,\ldots,4}\nonumber \\
+\widehat{\mathscr{I}}_{2} & = & \set{\left[\frac{k-1}{4},\frac{k+1}{4}\right]\cap\left[0,1\right]}{k=0,\ldots,4}\nonumber \\
  &  & \cup\{\imposs,\necess\}\nonumber \\
@@
 \end{eqnarray}
-$\widehat{\iota}_{2}\circ\mu_{1}$ can be computed by Table~\ref{tab:Compute-the-QIVPM}.
+It is straightforward to verify $\widehat{\iota}_{2}\circ\mu_{1}$
+is a QIVPM. It will be denoted by $\bar{\mu}_{4}$ whose values on
+the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
+and $\proj{2}$, $\events_{C}$, is computed by Table~\ref{tab:Compute-the-QIVPM}.
 \begin{table}
-\caption{\label{tab:Compute-the-QIVPM}Compute the QIVPM~$\widehat{\iota}_{2}\circ\mu_{1}$
-from $\mu_{1}$ on the minimal subspace of events containing $\proj{0}$,
-$\proj{1}$, and $\proj{2}$.}
+\caption{\label{tab:Compute-the-QIVPM}Compute $\bar{\mu}_{4}$ based on $\mu_{1}$
+on $\events_{C}$.}
 \begin{tabular}{ccc}
 \toprule 
-$P$ & $\mu_{1}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{1}\left(P\right)\right)$\tabularnewline
+$P$ & $\mu_{1}\left(P\right)$ & $\bar{\mu}_{4}\left(P\right)$\tabularnewline
 \midrule
@@
 \end{table}
-It is clear that $\widehat{\iota}_{2}\circ\mu_{1}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}).
-For Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+
+The QIVPM~$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is well-behavior
+in a sense that the collection of states consistent it get closer
+and closer to $\rho$ as the intervals get narrower and narrower,
+eventually collapsing to $\rho$ when the intervals become infinitely
+precise real numbers. To state this result, we need some more technical
+notions. We first define a notion of distance based on the following
+norm of a matrix~$A$ as $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}.
+Then, for any state~$\rho$ satisfying $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
+for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
+any other state~$\rho'$ consistent with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+must close to $\rho$ in a sense that $\left\Vert \rho-\rho'\right\Vert \le1/\left(12n\right)$.
+Reversely, if a state~$\rho'$ is close to $\rho$ in a sense that
+$\left\Vert \rho-\rho'\right\Vert \le1/n$, then $\rho'$ is consistent
+with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$. In other
+words, for the states consistent with this QIVPM, $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+will become closer and closer to $\rho'$ as $n$ goes to infinity.
+In the limiting case when the intervals are infinitely precise, i.e.,
+$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
+recast as a real-valued one and will have a unique state consistent
+with it on every projector.
 
@@
 Gleason's theorem does not hold, at least for this example.
-
-Although Gleason's theorem does not hold for every QIVPM, we can show
-that for a certain class of QIVPMs, the collection of states
-consistent with the projectors get closer and closer to each other as
-the intervals get narrower and narrower, eventually collapsing to a
-single state when the intervals become infinitely precise real
-numbers. To state this result, we introduce a few technical notions.
-
-We call a state $\rho$ a \emph{totally mixed state} if
-$0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
-$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $. We also
-define a notion of distance based on the following norm of a
-matrix~$A$ as
-$\left\Vert A\right\Vert
-=\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}. Now
-consider the following collection of intervals:
-\begin{eqnarray}
-\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
- &  & \cup\{ \imposs, \necess \}
-\end{eqnarray}
-which are overlapping intervals with length~$1/n$ except the intervals
-at length~$\left(2n\right)^{-1}$ at each end.
-
-A totally mixed state induces a QIVPM over the intervals above as
-follows. We first define a map $\widehat{\iota}_{n}$ from the interval
-$[0,1]$ to the collection of intervals as:
-\begin{itemize}
-\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
-\item when $0<x<1$, $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
-where $k$ is defined by one of the following:
-\begin{enumerate}
-\item $k$ even and $k-0.5\le2nx\le k+0.5$;
-\item $k$ odd and $k-0.5<2nx<k+0.5$.
-\end{enumerate}
-\end{itemize}
-
-It is now not difficult to verify that for any totally mixed
-state~$\rho$ on a three-dimensional Hilbert space,
-$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is a
-QIVPM. Furthermore, we have:
-\begin{itemize}
-\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(12n\right)$,
-$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
-\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
-\end{itemize}
-In other words, for the states consistent with this QIVPM,
-$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will become closer and
-closer to $\rho'$ as $n$ goes to infinity. In the limiting case when
-the intervals are infinitely precise, i.e.,
-$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
-recast as a real-valued one and will have a unique state consistent
-with it on every projector when $d\ge3$.
 

### 2017-09-14 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 will become closer and closer to $\rho'$ as $n$ goes to infinity.
+
 In the limiting case when the intervals are infinitely precise, i.e.,
-$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
-recast as a real-valued one and will have a unique state consistent
-with it on every projector.
-
-\yutsung{Clean up until here.}
-
-In the classical setting, measurements done with limited resources
-and poor precision may not uniquely identify the true state of a system.
-However, there is always at least one state that is consistent with
-the imprecise measurements.
-
-\begin{thm}[Shapley~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}]
-  For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
-  of events~$\events'\subseteq\events$ commutes, then
-  $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
-\end{thm}
-
-In the idealized situation of real-valued quantum probability
-measures, Gleason's theorem asserts that every measure is determined
-by a unique state.
-
-\begin{thm}[Gleason~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
+$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, even if a QIVPM is
+not \emph{a priori} known to be induced by a state, it can be recast
+as a real-valued one and will have a unique state consistent with
+it on every projector. This fact is called Gleason's theorem.
+
+\begin{thm}[Gleason~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
 a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
-measure~$\mu:\events\rightarrow[0,1]$, there exists a unique 
-state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$.
-\end{thm}
-
-Thm.~\ref{thm:Shapley} is weaker: it asserts that, for each classical
-subspace of events, a QIVPM must be consistent with \emph{some}
-state. But the states consistent with different subspaces may be
-incomparable, as the following example shows.
-
-Given a three-dimensional Hilbert space $\Hilb$ with an orthonormal
-basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let
-$\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
-$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
-$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
-\begin{subequations}
+measure~$\mu:\events\rightarrow[0,1]$, there exists a unique state~$\rho$
+such that $\mu=\mu_{\rho}^{\mathrm{B}}$. \end{thm}
+
+\noindent However, if the intervals are only with finite-precision,
+there are some QIVPMs which cannot be consistent with any state. Given
+a three-dimensional Hilbert space $\Hilb$ with an orthonormal basis
+$\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
+$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
+and \begin{subequations} 
 \begin{eqnarray}
@@
 \end{eqnarray}
-\end{subequations}
-It is straightforward to verify that $\bar{\mu}$ is a QIVPM. Then we
-will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an empty set
-by contradiction. Suppose there is a state
-$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since
-$\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$ for any~$P$, the
-state~$\rho$ must satisfy:
+\end{subequations} It is straightforward to verify that $\bar{\mu}$
+is a QIVPM. Then we will prove $\coreBorn\left(\bar{\mu},\events\right)$
+is an empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
+for any~$P$, the state~$\rho$ must satisfy: 
 \begin{equation}
@@
 \end{equation}
-which implies
-$\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$ for all
-$j$. However, the last equation never holds.  Thus, there is no state
-consistent with the QIVPM on all projectors~$P\in\events$, so
-Gleason's theorem does not hold, at least for this example.
+which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
+for all $j$. However, the last equation never holds. Thus, there
+is no state consistent with the QIVPM on all projectors~$P\in\events$,
+so Gleason's theorem cannot be extended to general QIVPMs because
+of this example.
 

### 2017-09-14 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 It is straightforward to verify $\widehat{\iota}_{2}\circ\mu_{1}$
-is a QIVPM. It will be denoted by $\bar{\mu}_{4}$ whose values on
-the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
-and $\proj{2}$, $\events_{C}$, is computed by Table~\ref{tab:Compute-the-QIVPM}.
+is a QIVPM whose values on the minimal subspace of events containing
+$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, is computed
+by Table~\ref{tab:Compute-the-QIVPM}. 
 \begin{table}
-\caption{\label{tab:Compute-the-QIVPM}Compute $\bar{\mu}_{4}$ based on $\mu_{1}$
-on $\events_{C}$.}
+\caption{\label{tab:Compute-the-QIVPM}Compute $\widehat{\iota}_{2}\circ\mu_{1}$
+based on $\mu_{1}$ on $\events_{C}$.}
 \begin{tabular}{ccc}
 \toprule 
-$P$ & $\mu_{1}\left(P\right)$ & $\bar{\mu}_{4}\left(P\right)$\tabularnewline
+$P$ & $\mu_{1}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{1}\left(P\right)\right)$\tabularnewline
 \midrule
@@
 
-The QIVPM~$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is well-behavior
-in a sense that the collection of states consistent it get closer
+Given any state~$\rho$ satisfying $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
+for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
+we know not only $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+is a QIVPM, but also the collection of states consistent it get closer
 and closer to $\rho$ as the intervals get narrower and narrower,
 eventually collapsing to $\rho$ when the intervals become infinitely
-precise real numbers. To state this result, we need some more technical
-notions. We first define a notion of distance based on the following
-norm of a matrix~$A$ as $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}.
-Then, for any state~$\rho$ satisfying $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
-for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
-any other state~$\rho'$ consistent with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-must close to $\rho$ in a sense that $\left\Vert \rho-\rho'\right\Vert \le1/\left(12n\right)$.
-Reversely, if a state~$\rho'$ is close to $\rho$ in a sense that
-$\left\Vert \rho-\rho'\right\Vert \le1/n$, then $\rho'$ is consistent
+precise real numbers. To state this result, we need to define a notion
+of distance based on the following norm of a matrix~$A$ as $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}.
+If a state~$\rho'$ is consistent with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
+its distance with $\rho$, $\left\Vert \rho-\rho'\right\Vert $, must
+be bounded by $1/\left(12n\right)$. Reversely, if the distance between
+$\rho$ and $\rho'$ is bounded by $1/n$, then $\rho'$ is consistent
 with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$. In other

### 2017-09-14 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 $\ket{\phi_2}=(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where in both cases
-$|\alpha|=1$. The expectation values of the observable $\mathbf{O}$,
+$|\alpha|=1$. \yutsung{Notice that we also have \mu_{1}=\mu_{\rho}^{\mathrm{B}}
+for a mixed state \rho=0.5\proj{0}+0.5\proj{1}. Maybe we should add ``Or other mixed states.''} 
+The expectation values of the observable $\mathbf{O}$,
 $\expval{\mathbf{O}}_{\mu_{1,2}}$, are 1.5 in the first case and 2 in
@@
 will be $[\ell_{i},r_{i}]$ if $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
-is closer to the center of $[\ell_{i},r_{i}]$. When there is a tie,
-we set $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$
+is closer to the center of $[\ell_{i},r_{i}]$\yutsung{{Verify...}}.
+When there is a tie, we set $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$
 for even $k$. For example, when $n=2$, 
@@
 It is straightforward to verify $\widehat{\iota}_{2}\circ\mu_{1}$
-is a QIVPM whose values on the minimal subspace of events containing
-$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, is computed
-by Table~\ref{tab:Compute-the-QIVPM}. 
+and $\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$ are
+QIVPMs whose values on the minimal subspace of events containing $\proj{0}$,
+$\proj{1}$, and $\proj{2}$, $\events_{C}$, is computed by Table~\ref{tab:Compute-the-QIVPM}.
 \begin{table}
 \caption{\label{tab:Compute-the-QIVPM}Compute $\widehat{\iota}_{2}\circ\mu_{1}$
-based on $\mu_{1}$ on $\events_{C}$.}
-\begin{tabular}{ccc}
+and $\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$ based
+on $\mu_{1}$ and $\mu_{\mathbb{1}/3}^{\mathrm{B}}$ on $\events_{C}$.}
+\begin{tabular}{ccccc}
 \toprule 
-$P$ & $\mu_{1}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{1}\left(P\right)\right)$\tabularnewline
+$P$ & $\mu_{1}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{1}\left(P\right)\right)$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline
 \midrule
 \midrule 
-$\mathbb{0}$ & $0$ & $\left[0,0\right]$\tabularnewline
+$\mathbb{0}$ & $0$ & $\left[0,0\right]$ & $0$ & $\left[0,0\right]$\tabularnewline
 \midrule 
-$\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+$\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
 \midrule 
-$\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+$\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
 \midrule 
-$\proj{2}$ & $0$ & $\left[0,0\right]$\tabularnewline
+$\proj{2}$ & $0$ & $\left[0,0\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
 \midrule 
-$\mathbb{1}-\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+$\mathbb{1}-\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
 \midrule 
-$\mathbb{1}-\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$\tabularnewline
+$\mathbb{1}-\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
 \midrule 
-$\mathbb{1}-\proj{2}$ & $1$ & $\left[1,1\right]$\tabularnewline
+$\mathbb{1}-\proj{2}$ & $1$ & $\left[1,1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
 \midrule 
-$\mathbb{1}$ & $1$ & $\left[1,1\right]$\tabularnewline
+$\mathbb{1}$ & $1$ & $\left[1,1\right]$ & $1$ & $\left[1,1\right]$\tabularnewline
 \bottomrule
@@
 for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
-we know not only $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+called totally mixed state, we know not only $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
 is a QIVPM, but also the collection of states consistent it get closer
@@
 will become closer and closer to $\rho'$ as $n$ goes to infinity.
+
+For example, since $\mu_{1}\left(\proj{2}\right)=0$, any state corresponds
+to $\mu_{1}$is not totally mixed state. On the other hand, $\mathbb{1}/3$
+is a totally mixed state. \yutsung{{To be continue...}}
 

### 2017-09-14 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 $\ket{\phi_2}=(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where in both cases
-$|\alpha|=1$. \yutsung{Notice that we also have \mu_{1}=\mu_{\rho}^{\mathrm{B}}
-for a mixed state \rho=0.5\proj{0}+0.5\proj{1}. Maybe we should add ``Or other mixed states.''} 
+$|\alpha|=1$. \yutsung{Notice that we also have
+$\mu_{1}=\mu_{\rho}^{\mathrm{B}}$ for a mixed state~$\rho=0.5\proj{0}+0.5\proj{1}$.
+Maybe we should add ``Or other mixed states.''}
 The expectation values of the observable $\mathbf{O}$,
@@
 intervals containing them. In general, any set of the numbers can
-be replaced by the interval containing them if we carefully pick a
-set of overlapping intervals. For example, consider the following
-collection of intervals: 
+be replaced by an interval containing them if we carefully pick a
+set of intervals and the rule to select the correct interval when
+intervals are overlapping. For example, consider the following collection
+of intervals: 
 \begin{eqnarray}
-\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
+\mathscr{I}_{n} & = & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
  &  & \cup\{\imposs,\necess\}
@@
 which are overlapping intervals with length~$1/n$ except the intervals
-at length~$\left(2n\right)^{-1}$ at each end. Then, we can define
-a QIVPM mapping to $\widehat{\mathscr{I}}_{n}$ based on any Born
-rule probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional
+at length~$\left(2n\right)^{-1}$ at each end. Since these intervals
+are overlapping, we define the interior part of these intervals
+
+Then, we can define a QIVPM mapping to $\mathscr{I}_{n}$ based on
+any Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional
 Hilbert space by replacing the probability~$\mu_{\rho}^{\mathrm{B}}\left(P\right)$
-with the interval containing it, $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.
-Since intervals in $\widehat{\mathscr{I}}_{n}$ are overlapping, if
-$\mu_{\rho}^{\mathrm{B}}\left(P\right)$ are contained in both intervals~$[\ell_{1},r_{1}]$
-and $[\ell_{2},r_{2}]$, $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
-will be $[\ell_{i},r_{i}]$ if $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
-is closer to the center of $[\ell_{i},r_{i}]$\yutsung{{Verify...}}.
-When there is a tie, we set $\widehat{\iota}_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$
+with the interval containing it, $\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.
+Since intervals in $\mathscr{I}_{n}$ are overlapping, if $\mu_{\rho}^{\mathrm{B}}\left(P\right)$
+are contained in both intervals~$[\ell_{1},r_{1}]$ and $[\ell_{2},r_{2}]$,
+$\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$ will
+be $[\ell_{i},r_{i}]$ if $\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
+is closer to the center of $[\ell_{i},r_{i}]$\yutsung{Verify...}.
+When there is a tie, we set $\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$
 for even $k$. For example, when $n=2$, 
 \begin{eqnarray}
-\widehat{\mathscr{I}}_{2} & = & \set{\left[\frac{k-1}{4},\frac{k+1}{4}\right]\cap\left[0,1\right]}{k=0,\ldots,4}\nonumber \\
+\mathscr{I}_{2} & = & \set{\left[\tfrac{k-1}{4},\tfrac{k+1}{4}\right]\cap\left[0,1\right]}{k=0,\ldots,4}\nonumber \\
  &  & \cup\{\imposs,\necess\}\nonumber \\
- & = & \left\{ \imposs,\left[0,\frac{1}{4}\right],\left[0,\frac{1}{2}\right],\left[\frac{1}{4},\frac{3}{4}\right],\right.\nonumber \\
- &  & \left.\left[\frac{1}{2},1\right],\left[\frac{1}{4},1\right],\necess\right\} \,.
+ & = & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\nonumber \\
+ &  & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{1}{4},1\right],\necess\right\} \,.
 \end{eqnarray}
-It is straightforward to verify $\widehat{\iota}_{2}\circ\mu_{1}$
-and $\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$ are
-QIVPMs whose values on the minimal subspace of events containing $\proj{0}$,
-$\proj{1}$, and $\proj{2}$, $\events_{C}$, is computed by Table~\ref{tab:Compute-the-QIVPM}.
+It is straightforward to verify $\iota_{2}\circ\mu_{1}$ and $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+are QIVPMs whose values on the minimal subspace of events containing
+$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, is computed
+by Table~\ref{tab:Compute-the-QIVPM}. 
 \begin{table}
-\caption{\label{tab:Compute-the-QIVPM}Compute $\widehat{\iota}_{2}\circ\mu_{1}$
-and $\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$ based
-on $\mu_{1}$ and $\mu_{\mathbb{1}/3}^{\mathrm{B}}$ on $\events_{C}$.}
+\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{1}$ and
+$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$ based on $\mu_{1}$
+and $\mu_{\mathbb{1}/3}^{\mathrm{B}}$ on $\events_{C}$.}
 \begin{tabular}{ccccc}
 \toprule 
-$P$ & $\mu_{1}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{1}\left(P\right)\right)$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline
+$P$ & $\mu_{1}\left(P\right)$ & $\iota_{2}\left(\mu_{1}\left(P\right)\right)$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline
 \midrule
@@
 for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
-called totally mixed state, we know not only $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+called totally mixed state, we know not only $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
 is a QIVPM, but also the collection of states consistent it get closer
@@
 of distance based on the following norm of a matrix~$A$ as $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}.
-If a state~$\rho'$ is consistent with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
+If a state~$\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
 its distance with $\rho$, $\left\Vert \rho-\rho'\right\Vert $, must
@@
 $\rho$ and $\rho'$ is bounded by $1/n$, then $\rho'$ is consistent
-with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$. In other
-words, for the states consistent with this QIVPM, $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$. In other words, for
+the states consistent with this QIVPM, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
 will become closer and closer to $\rho'$ as $n$ goes to infinity.

### 2017-09-15 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 $0$ or $0.5$, which are replaced by $\left[0,0\right]$ or $\left[0.5,0.5\right]$
-to get $\bar{\mu}_{3}$. This is replacing two numbers by the smallest
-intervals containing them. In general, any set of the numbers can
-be replaced by an interval containing them if we carefully pick a
-set of intervals and the rule to select the correct interval when
+to get $\bar{\mu}_{3}$. The way we replace two numbers by the smallest
+intervals containing them can be generalized if we carefully pick
+a set of intervals and the rule to select the correct interval when
 intervals are overlapping. For example, consider the following collection
@@
 at length~$\left(2n\right)^{-1}$ at each end. Since these intervals
-are overlapping, we define the interior part of these intervals
-
-Then, we can define a QIVPM mapping to $\mathscr{I}_{n}$ based on
-any Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional
-Hilbert space by replacing the probability~$\mu_{\rho}^{\mathrm{B}}\left(P\right)$
-with the interval containing it, $\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.
-Since intervals in $\mathscr{I}_{n}$ are overlapping, if $\mu_{\rho}^{\mathrm{B}}\left(P\right)$
-are contained in both intervals~$[\ell_{1},r_{1}]$ and $[\ell_{2},r_{2}]$,
-$\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$ will
-be $[\ell_{i},r_{i}]$ if $\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
-is closer to the center of $[\ell_{i},r_{i}]$\yutsung{Verify...}.
-When there is a tie, we set $\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$
-for even $k$. For example, when $n=2$, 
+are overlapping, we define the non-overlapping interior part of a
+interval according to the following rule.\begin{subequations}
 \begin{eqnarray}
-\mathscr{I}_{2} & = & \set{\left[\tfrac{k-1}{4},\tfrac{k+1}{4}\right]\cap\left[0,1\right]}{k=0,\ldots,4}\nonumber \\
- &  & \cup\{\imposs,\necess\}\nonumber \\
- & = & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\nonumber \\
- &  & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{1}{4},1\right],\necess\right\} \,.
+\textrm{Int}\left(\imposs\right) & = & \imposs\,,\\
+\textrm{Int}\left(\left[0,\tfrac{1}{2n}\right]\right) & = & \left(0,\tfrac{0.5}{2n}\right]\,,\\
+\textrm{Int}\left(\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\right) & = & \left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]\nonumber \\
+ &  & \textrm{for even }0<k<2n\,,\\
+\textrm{Int}\left(\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\right) & = & \left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)\nonumber \\
+ &  & \textrm{for odd }k\,,\\
+\textrm{Int}\left(\left[\tfrac{2n-1}{2n},1\right]\right) & = & \left[\tfrac{2n-0.5}{2n},1\right)\,,\\
+\textrm{Int}\left(\necess\right) & = & \necess\,.
 \end{eqnarray}
-It is straightforward to verify $\iota_{2}\circ\mu_{1}$ and $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
-are QIVPMs whose values on the minimal subspace of events containing
-$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, is computed
-by Table~\ref{tab:Compute-the-QIVPM}. 
+\end{subequations}Hence, given a real-valued probability~$x$, we
+will replace it with an interval~$\iota_{n}\left(x\right)=[\ell,r]$
+if $x\in\textrm{Int}\left([\ell,r]\right)$.
+
+After we have a rule to replace a real number by an interval, any
+Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional
+Hilbert space can be extended to a QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
+where $\circ$ is the function concatenation. For example, when $n=2$,
+we can summarize the set of intervals~$\mathscr{I}_{2}$ and their
+interior in Table~\ref{tab:I2}.
+\begin{table}
+\caption{\label{tab:I2}Intervals in $\mathscr{I}_{2}$ and their interior.}
+\begin{tabular}{cc}
+\toprule 
+$[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline
+\midrule
+\midrule 
+$\imposs$ & $\imposs$\tabularnewline
+\midrule 
+$\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline
+\midrule 
+$\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline
+\midrule 
+$\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline
+\midrule 
+$\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline
+\midrule 
+$\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline
+\midrule 
+$\necess$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+Given two quantum probability measure~$\mu_{1}$ and $\mu_{\mathbb{1}/3}^{\mathrm{B}}$,
+where $\frac{\mathbb{1}}{3}=\frac{1}{3}\left(\proj{0}+\proj{1}+\proj{2}\right)$,
+it is then easy to compute $\iota_{2}\circ\mu_{1}$ and $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+on the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
+and $\proj{2}$, $\events_{C}$ as in Table~\ref{tab:Compute-the-QIVPM}.
 \begin{table}
@@
 \midrule 
-$\mathbb{0}$ & $0$ & $\left[0,0\right]$ & $0$ & $\left[0,0\right]$\tabularnewline
+$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline
 \midrule 
@@
 \midrule 
-$\proj{2}$ & $0$ & $\left[0,0\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
+$\proj{2}$ & $0$ & $\imposs$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
 \midrule 
@@
 \midrule 
-$\mathbb{1}-\proj{2}$ & $1$ & $\left[1,1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
-\midrule 
-$\mathbb{1}$ & $1$ & $\left[1,1\right]$ & $1$ & $\left[1,1\right]$\tabularnewline
+$\mathbb{1}-\proj{2}$ & $1$ & $\necess$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
+\midrule 
+$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline
 \bottomrule
@@
 \end{table}
+Verifying $\iota_{2}\circ\mu_{1}$ and $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+are QIVPMs are also straightforward.
 
@@
 its distance with $\rho$, $\left\Vert \rho-\rho'\right\Vert $, must
-be bounded by $1/\left(12n\right)$. Reversely, if the distance between
-$\rho$ and $\rho'$ is bounded by $1/n$, then $\rho'$ is consistent
-with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$. In other words, for
-the states consistent with this QIVPM, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+be bounded by $\left(12n\right)^{-1}$. Reversely, if the distance
+between $\rho$ and $\rho'$ is bounded by $1/n$, then $\rho'$ is
+consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$. In other
+words, for the states consistent with this QIVPM, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
 will become closer and closer to $\rho'$ as $n$ goes to infinity.
@@
 For example, since $\mu_{1}\left(\proj{2}\right)=0$, any state corresponds
-to $\mu_{1}$is not totally mixed state. On the other hand, $\mathbb{1}/3$
-is a totally mixed state. \yutsung{{To be continue...}}
+to $\mu_{1}$ is not totally mixed state. On the other hand, $\mathbb{1}/3$
+is a totally mixed state. \yutsung{To be continue...}
 

### 2017-09-15 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 which are overlapping intervals with length~$1/n$ except the intervals
-at length~$\left(2n\right)^{-1}$ at each end. Since these intervals
+with length~$\left(2n\right)^{-1}$ at each end. Since these intervals~$[\ell,r]$
 are overlapping, we define the non-overlapping interior part of a
-interval according to the following rule.\begin{subequations}
-\begin{eqnarray}
-\textrm{Int}\left(\imposs\right) & = & \imposs\,,\\
-\textrm{Int}\left(\left[0,\tfrac{1}{2n}\right]\right) & = & \left(0,\tfrac{0.5}{2n}\right]\,,\\
-\textrm{Int}\left(\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\right) & = & \left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]\nonumber \\
- &  & \textrm{for even }0<k<2n\,,\\
-\textrm{Int}\left(\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\right) & = & \left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)\nonumber \\
- &  & \textrm{for odd }k\,,\\
-\textrm{Int}\left(\left[\tfrac{2n-1}{2n},1\right]\right) & = & \left[\tfrac{2n-0.5}{2n},1\right)\,,\\
-\textrm{Int}\left(\necess\right) & = & \necess\,.
-\end{eqnarray}
-\end{subequations}Hence, given a real-valued probability~$x$, we
-will replace it with an interval~$\iota_{n}\left(x\right)=[\ell,r]$
-if $x\in\textrm{Int}\left([\ell,r]\right)$.
+interval~$\textrm{Int}\left([\ell,r]\right)$ as in Table~\ref{tab:I2}
+which also contains an concrete example for $\mathscr{I}_{2}$.
+\begin{table}
+\caption{\label{tab:I2}Intervals in $\mathscr{I}_{n}$ and their interior
+with an concrete example for $\mathscr{I}_{2}$. Although intervals~$[\ell,r]$
+are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
+are non-overlapping.}
+\begin{tabular}{cccc}
+\toprule 
+\multicolumn{2}{c}{$\mathscr{I}_{n}$} & \multicolumn{2}{c}{$\mathscr{I}_{2}$}\tabularnewline
+\midrule 
+$[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline
+\midrule
+\midrule 
+$\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
+\midrule 
+$\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline
+\midrule 
+$\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
+\textrm{for odd }k
+\end{gathered}
+$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline
+\midrule 
+\multirow{2}{*}{$\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
+\textrm{for even }k\\
+0<k<2n
+\end{gathered}
+$} & \multirow{2}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$} & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline
+\cmidrule{3-4} 
+ &  & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline
+\midrule 
+$\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline
+\midrule 
+$\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+Hence, given a real-valued probability~$x$, we could easily replace
+it with an interval~$\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$.
 
@@
 where $\circ$ is the function concatenation. For example, when $n=2$,
-we can summarize the set of intervals~$\mathscr{I}_{2}$ and their
-interior in Table~\ref{tab:I2}.
-\begin{table}
-\caption{\label{tab:I2}Intervals in $\mathscr{I}_{2}$ and their interior.}
-\begin{tabular}{cc}
-\toprule 
-$[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline
-\midrule
-\midrule 
-$\imposs$ & $\imposs$\tabularnewline
-\midrule 
-$\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline
-\midrule 
-$\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline
-\midrule 
-$\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline
-\midrule 
-$\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline
-\midrule 
-$\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline
-\midrule 
-$\necess$ & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{table}
-Given two quantum probability measure~$\mu_{1}$ and $\mu_{\mathbb{1}/3}^{\mathrm{B}}$,
-where $\frac{\mathbb{1}}{3}=\frac{1}{3}\left(\proj{0}+\proj{1}+\proj{2}\right)$,
-it is then easy to compute $\iota_{2}\circ\mu_{1}$ and $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
-on the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
-and $\proj{2}$, $\events_{C}$ as in Table~\ref{tab:Compute-the-QIVPM}.
+two quantum probability measure~$\mu_{1}$ and $\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+can induce two QIVPMs, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$.
+The interval-valued probability of the induced QIVPMs, $\iota_{2}\left(\mu_{1}\left(P\right)\right)$
+and $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$,
+for projector $P$ in the minimal subspace of events containing $\proj{0}$,
+$\proj{1}$, and $\proj{2}$, $\events_{C}$, are computed straightforwardly
+in Table~\ref{tab:Compute-the-QIVPM}.
 \begin{table}
@@
 
-Given any state~$\rho$ satisfying $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
-for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
-called totally mixed state, we know not only $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+A state~$\rho$ is called totally mixed state if it satisfies $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
+for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
+Given any totally mixed state~$\rho$, we know not only $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
 is a QIVPM, but also the collection of states consistent it get closer
@@
 its distance with $\rho$, $\left\Vert \rho-\rho'\right\Vert $, must
-be bounded by $\left(12n\right)^{-1}$. Reversely, if the distance
-between $\rho$ and $\rho'$ is bounded by $1/n$, then $\rho'$ is
-consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$. In other
-words, for the states consistent with this QIVPM, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-will become closer and closer to $\rho'$ as $n$ goes to infinity.
-
-For example, since $\mu_{1}\left(\proj{2}\right)=0$, any state corresponds
-to $\mu_{1}$ is not totally mixed state. On the other hand, $\mathbb{1}/3$
-is a totally mixed state. \yutsung{To be continue...}
+be bounded by $1/n$. Reversely, if the distance between $\rho$ and
+$\rho'$ is bounded by $\left(12n\right)^{-1}$, then $\rho'$ is
+consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$. For example,
+since $\mu_{1}\left(\proj{2}\right)=0$, any state corresponds to
+$\mu_{1}$ is not totally mixed state. On the other hand, $\mathbb{1}/3$
+is a totally mixed state. Consider $\rho'=\left(\frac{1}{3}+\frac{1}{24}\right)\proj{0}+\left(\frac{1}{3}-\frac{1}{24}\right)\proj{1}+\frac{1}{3}\cdot\proj{2}$.
+Since $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{12\cdot2}$, we
+should have $\rho'\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$.
+Although verifying the general case is non-trivial, it is easy to
+see $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$
+for $P\in\events_{C}$. As $n$ goes to infinity, only the states
+very close to $\rho$ is guarantied belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$,
+and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+will become closer and closer to $\rho$.
 
@@
 a three-dimensional Hilbert space $\Hilb$ with an orthonormal basis
-$\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
+$\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
 $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,

### 2017-09-16 prop_letter.tex
prop_letter.tex \usepackage{multirow} Added...
prop_letter.tex \section{Gleason} Updating...

@@
 \usepackage{booktabs}
+\usepackage{multirow}
 
@@
 probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
-This result will first be generalized, and then we will show some
-QIVPMs may not be induced by any classical IVPM, i.e., no state is
-consistent with these kind of QIVPMs.
+This result will first be generalized in this section, and then we
+will show some QIVPMs may not be induced by any classical IVPM, i.e.,
+no state is consistent with these kind of QIVPMs.
 
@@
 $0$ or $0.5$, which are replaced by $\left[0,0\right]$ or $\left[0.5,0.5\right]$
-to get $\bar{\mu}_{3}$. The way we replace two numbers by the smallest
-intervals containing them can be generalized if we carefully pick
-a set of intervals and the rule to select the correct interval when
-intervals are overlapping. For example, consider the following collection
-of intervals: 
+to get $\bar{\mu}_{3}$. The way we replace numbers by intervals containing
+them can be generalized if we carefully pick a set of intervals and
+the rule to select the correct interval when intervals are overlapping.
+For example, consider the following collection of intervals: 
 \begin{eqnarray}
@@
 are overlapping, we define the non-overlapping interior part of a
-interval~$\textrm{Int}\left([\ell,r]\right)$ as in Table~\ref{tab:I2}
-which also contains an concrete example for $\mathscr{I}_{2}$.
+interval, $\textrm{Int}\left([\ell,r]\right)$, as in Table~\ref{tab:I2}.
 \begin{table}
@@
 \midrule
+\midrule 
 $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline
-\midrule
 \midrule 
@@
 \end{gathered}
-$} & \multirow{2}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$} & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline
+$} & \multirow{2}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$} & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
 \cmidrule{3-4} 
- &  & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline
+ &  & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
 \midrule 
@@
 where $\circ$ is the function concatenation. For example, when $n=2$,
-two quantum probability measure~$\mu_{1}$ and $\mu_{\mathbb{1}/3}^{\mathrm{B}}$
-can induce two QIVPMs, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$.
-The interval-valued probability of the induced QIVPMs, $\iota_{2}\left(\mu_{1}\left(P\right)\right)$
-and $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$,
+two quantum probability measure~$\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+and $\mu_{\rho_{0}}^{\mathrm{B}}$ can induce two QIVPMs, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
+and $\rho_{0}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$.
+The interval-valued probability of the induced QIVPMs, $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$
+and $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$,
 for projector $P$ in the minimal subspace of events containing $\proj{0}$,
@@
 \begin{table}
-\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{1}$ and
-$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$ based on $\mu_{1}$
-and $\mu_{\mathbb{1}/3}^{\mathrm{B}}$ on $\events_{C}$.}
+\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$ based on $\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+and $\mu_{\rho_{0}}^{\mathrm{B}}$ on $\events_{C}$.}
 \begin{tabular}{ccccc}
 \toprule 
-$P$ & $\mu_{1}\left(P\right)$ & $\iota_{2}\left(\mu_{1}\left(P\right)\right)$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline
+$P$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline
 \midrule
@@
 \midrule 
-$\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
-\midrule 
-$\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
-\midrule 
-$\proj{2}$ & $0$ & $\imposs$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
-\midrule 
-$\mathbb{1}-\proj{0}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
-\midrule 
-$\mathbb{1}-\proj{1}$ & $0.5$ & $\left[\frac{1}{4},\frac{3}{4}\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
-\midrule 
-$\mathbb{1}-\proj{2}$ & $1$ & $\necess$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
+$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
+\midrule 
+$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
+\midrule 
+$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline
+\midrule 
+$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline
+\midrule 
+$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
+\midrule 
+$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
 \midrule 
@@
 consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$. For example,
-since $\mu_{1}\left(\proj{2}\right)=0$, any state corresponds to
-$\mu_{1}$ is not totally mixed state. On the other hand, $\mathbb{1}/3$
-is a totally mixed state. Consider $\rho'=\left(\frac{1}{3}+\frac{1}{24}\right)\proj{0}+\left(\frac{1}{3}-\frac{1}{24}\right)\proj{1}+\frac{1}{3}\cdot\proj{2}$.
-Since $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{12\cdot2}$, we
-should have $\rho'\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$.
-Although verifying the general case is non-trivial, it is easy to
-see $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$
-for $P\in\events_{C}$. As $n$ goes to infinity, only the states
-very close to $\rho$ is guarantied belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$,
+$\mathbb{1}/3$ and $\rho_{0}$ are both totally mixed states. Since
+$\left\Vert \frac{\mathbb{1}}{3}-\rho_{0}\right\Vert \le\frac{1}{24}$,
+we should have $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$
+and $\mathbb{1}/3\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
+and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
+In general, as $n$ goes to infinity, only the states very close to
+$\rho$ is guarantied belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$,
 and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$

### 2017-09-16 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 While the finite-precision extension of Kochen-Specker theorem asserts
-the non-existence of certain QIVPMs, we also want to understand what
-a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
+the non-existence of certain kind of QIVPMs, we also want to understand
+what a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
 the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
@@
 This result will first be generalized in this section, and then we
-will show some QIVPMs may not be induced by any classical IVPM, i.e.,
-no state is consistent with these kind of QIVPMs.
+will show some QIVPMs may not be induced by any quantum probability
+measure, i.e., no state is consistent with these kind of QIVPMs.
 
@@
 $0$ or $0.5$, which are replaced by $\left[0,0\right]$ or $\left[0.5,0.5\right]$
-to get $\bar{\mu}_{3}$. The way we replace numbers by intervals containing
+to get $\bar{\mu}_{3}$. Replacing numbers by intervals containing
 them can be generalized if we carefully pick a set of intervals and

### 2017-09-16 prop_letter.tex
prop_letter.tex Dealing with the table height again...
prop_letter.tex \section{Gleason} Updating...

@@
 will show some QIVPMs may not be induced by any quantum probability
-measure, i.e., no state is consistent with these kind of QIVPMs.
+measure, i.e., no state is consistent with these kind of QIVPMs, while
+a quantum probability measure is always induced by an unique state
+by Gleason's theorem.
 
@@
 them can be generalized if we carefully pick a set of intervals and
-the rule to select the correct interval when intervals are overlapping.
+a rule to select the correct interval when intervals are overlapping.
 For example, consider the following collection of intervals: 
@@
 are non-overlapping.}
+
 \begin{tabular}{cccc}
 \toprule 
-\multicolumn{2}{c}{$\mathscr{I}_{n}$} & \multicolumn{2}{c}{$\mathscr{I}_{2}$}\tabularnewline
-\midrule
-\midrule 
-$[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline
-\midrule 
-$\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
-\midrule 
-$\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline
-\midrule 
+\addlinespace
+\multicolumn{2}{c}{$\mathscr{I}_{n}$} & \multicolumn{2}{c}{$\mathscr{I}_{2}$}\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
 $\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
@@
 \end{gathered}
-$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline
-\midrule 
+$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
 \multirow{2}{*}{$\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
@@
 \cmidrule{3-4} 
+\addlinespace
  &  & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
 \midrule 
-$\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline
-\midrule 
-$\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
+\addlinespace
+$\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
 \bottomrule
@@
 
-After we have a rule to replace a real number by an interval, any
+After we have the rule to replace a real number by an interval, any
 Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional
 Hilbert space can be extended to a QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
-where $\circ$ is the function concatenation. For example, when $n=2$,
-two quantum probability measure~$\mu_{\mathbb{1}/3}^{\mathrm{B}}$
-and $\mu_{\rho_{0}}^{\mathrm{B}}$ can induce two QIVPMs, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
+where $\circ$ is the function concatenation~\citep{HOSTunpublished}.
+For example, when $n=2$, two quantum probability measures~$\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+and $\mu_{\rho_{0}}^{\mathrm{B}}$ can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
 and $\rho_{0}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$.
@@
 and $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$,
-for projector $P$ in the minimal subspace of events containing $\proj{0}$,
-$\proj{1}$, and $\proj{2}$, $\events_{C}$, are computed straightforwardly
-in Table~\ref{tab:Compute-the-QIVPM}.
+for any projector $P$ in the minimal subspace of events containing
+$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, are computed
+straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
 \begin{table}
@@
 and $\mu_{\rho_{0}}^{\mathrm{B}}$ on $\events_{C}$.}
+
 \begin{tabular}{ccccc}
 \toprule 
-$P$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline
-\midrule
-\midrule 
-$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline
-\midrule 
-$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
-\midrule 
-$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline
-\midrule 
-$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline
-\midrule 
-$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline
-\midrule 
-$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
-\midrule 
-$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline
-\midrule 
-$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline
+\addlinespace
+$P$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline\addlinespace
 \bottomrule
@@
 $\rho'$ is bounded by $\left(12n\right)^{-1}$, then $\rho'$ is
-consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$. For example,
-$\mathbb{1}/3$ and $\rho_{0}$ are both totally mixed states. Since
-$\left\Vert \frac{\mathbb{1}}{3}-\rho_{0}\right\Vert \le\frac{1}{24}$,
+consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$~\citep{HOSTunpublished}.
+For example, $\mathbb{1}/3$ and $\rho_{0}$ are both totally mixed
+states. Since $\left\Vert \frac{\mathbb{1}}{3}-\rho_{0}\right\Vert \le\frac{1}{24}$,
 we should have $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$

### 2017-09-17 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 measure, i.e., no state is consistent with these kind of QIVPMs, while
-a quantum probability measure is always induced by an unique state
-by Gleason's theorem.
+there is always an unique state consistent with a quantum probability
+measure by Gleason's theorem.
 
@@
 For example, consider the following collection of intervals: 
-\begin{eqnarray}
-\mathscr{I}_{n} & = & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
- &  & \cup\{\imposs,\necess\}
-\end{eqnarray}
+\begin{equation}
+\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
+ & \cup\{\imposs,\necess\}
+\end{aligned}
+\end{equation}
 which are overlapping intervals with length~$1/n$ except the intervals

### 2017-09-17 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating...

@@
 \end{aligned}
+\label{eq:classical-no-information-IVPM}
 \end{equation}
@@
 
-\noindent The definition puts no restrictions on the choice of
-intervals, only on the assignment of intervals to events. When
-$\delta=0$, every event must be assigned a probability either in the
-interval $\imposs$ or in $\necess$, i.e., every event is completely
-determined with certainty. As $\delta$ gets larger, the QIVPM allows
-for more indeterminate behavior. For example, assuming a set of
-intervals including $\imposs$, $\necess$, and
-$\{ [0,1/4], [1/4,1/2], [1/2,3/4], [3/4,1] \}$, the probability
-measure that maps every event to either $\imposs$ or $\necess$ would
-be a 0-deterministic QIVPM, and the probability measure that maps
-every event to one of $\imposs$, $\necess$, $[0,1/5]$, or $[4/5,1]$
-would be a $\delta$-deterministic QIVPM for every
-$1/5 \le \delta \le 1$.
+\noindent The definition puts no restrictions on the choice of intervals,
+only on the assignment of intervals to events. When $\delta=0$, every
+event must be assigned a probability either in the interval $\imposs$
+or in $\necess$, i.e., every event is completely determined with
+certainty. As $\delta$ gets larger, the QIVPM allows for more indeterminate
+behavior. To illustrate the example easier, we restrict ourselves
+to the classical subspace of commuting events~$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
+If we apply the same definition in the classical case, the classical
+IVPM~$\bar{\mu}_{4}$ defined in Table~\ref{tab:classical-IVPMs}
+is $0$-deterministic because $\imposs\subseteq\left[0,0\right]$
+and $\necess\subseteq\left[1-0,1\right]$.
+\begin{table}
+\noindent \centering{}\caption{\label{tab:classical-IVPMs}Classical IVPMs~$\bar{\mu}_{4}$, $\bar{\mu}_{5}$
+and $\bar{\mu}_{6}$ on $\events_{0}$.}
+\begin{tabular}{cccc}
+\toprule 
+\addlinespace
+$P$ & $\bar{\mu}_{4}(P)$ & $\bar{\mu}_{5}(P)$ & $\bar{\mu}_{6}(P)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{0}$ & $\necess$ & $\left[\frac{1}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{1}$ & $\imposs$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+By interpreting the states ~$\proj{0}$ and $\proj{1}$ with the
+head and the tail of a coin again, $\bar{\mu}_{4}$ represents tossing
+a double-headed coin which can be predicted with certain. When $\delta$
+is increased to $\frac{1}{3}$, the classical IVPMs~$\bar{\mu}_{5}$
+and $\bar{\mu}_{6}$ defined in Table~\ref{tab:classical-IVPMs}
+are clearly $\frac{1}{3}$-deterministic, and they have more indeterminate
+behavior than $\bar{\mu}_{4}$. However, the most indeterminate classical
+IVPM~$\bar{\mu}_{2}$ defined in Eq.~(\ref{eq:classical-no-information-IVPM})
+is still not $\frac{1}{3}$-deterministic because $\bar{\mu}_{2}(\proj{0})=\bar{\mu}_{2}(\proj{1})=\unknown$,
+but neither $\unknown\subseteq\left[0,\frac{1}{3}\right]$ nor $\unknown\subseteq\left[1-\frac{1}{3},1\right]$.
 
@@
 $\bar{\mu}(\Sigma_i{\proj{\psi_i}})=\necess$ and by inductively applying
-Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), \yutsung{Check whether
-we can explain how to apply
-Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) in this situation
-better.} we must have
+Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), we must have
 one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all others mapped to

### 2017-09-17 prop_letter.tex
prop_letter.tex Reviewing from \section{Fuzzy Measurements}...

@@
 $\mathbf{O}$ with spectral decomposition
-$\mathbf{O} = \proj{0} + 2\,\proj{1} + 3\,\proj{2}$, i.e., $q_{j} = j$ and
-$\ket{\phi_{j}} = \ket{j - 1}$.
+$\mathbf{O} = \proj{0} + 2\,\proj{1} + 3\,\proj{2}$, i.e., $\lambda_{i}=j$ and $P_{i}=\proj{j-1}$.
 Two fragments of valid probability measures $\mu_1$ and $\mu_2$ that can be associated
@@
 we will continue in the following to write this as a definite interval.
-The collection of intervals used in the
+\yutsung{Check the interpretation in the statistics literature~\citep{HuberRonchetti2009}!
+Or we may need to prove it could be interpreted as Guassian width
+by ourselves...} The collection of intervals used in the
 definition of a probability measure must satisfy certain properties
@@
 $\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid probability
-interval. Moreover the event $E\cup\overline{E}$ is the identity event
-covering the entire space; its probability interval should be
+interval. Moreover the event $E\cup\overline{E}$ is the
+entire space; its probability interval should be
 $\necess$ which is sharper than $[0.9,1.1]$. The problem is that the
@@
 $\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
-combination with the requirement for the identity event would force
+combination with the requirement for the event of the entire space would force
 $\mu(E \cup \overline{E})$ to always be $\necess$ irrespective of the

### 2017-09-17 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
+\newtheorem*{example*}{Example}
 
@@
 probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
-This result will first be generalized in this section, and then we
-will show some QIVPMs may not be induced by any quantum probability
-measure, i.e., no state is consistent with these kind of QIVPMs, while
-there is always an unique state consistent with a quantum probability
-measure by Gleason's theorem.
+This result will first be generalized in this section, and introduce
+a finite-precision extension of the Born rule~\citep{peres1995quantum,544199,Jaeger2007}.
+The Born rule is essential to compute the conventional quantum probability
+because any quantum probability measure can be induced by the Born
+rule according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+We then provide a finite precision variant of Gleason's theorem for
+QIVPMs induced by the Born rule, but there are also some general QIVPMs
+may not be induced by any quantum probability measure, i.e., no state
+is consistent with these kind of QIVPMs.
 
@@
 \end{tabular}
+
+\yutsung{Not sure what is the best way embedding the condition for
+$k$ in the table...}
 \end{table}
@@
 
-After we have the rule to replace a real number by an interval, any
-Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional
-Hilbert space can be extended to a QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
-where $\circ$ is the function concatenation~\citep{HOSTunpublished}.
-For example, when $n=2$, two quantum probability measures~$\mu_{\mathbb{1}/3}^{\mathrm{B}}$
-and $\mu_{\rho_{0}}^{\mathrm{B}}$ can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+After we have the rule to replace a real number by an interval, we
+can induce a QIVPM from a state according to the following theorem.
+
+\begin{thm}[Finite-precision Extension of the Born rule~\citep{HOSTunpublished}]For
+any state $\rho$ on a three-dimensional Hilbert space, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+is a QIVPM, where $\circ$ is the function concatenation.\end{thm}\yutsung{Do
+we need to summarize the proof?}
+
+\noindent For example, when $n=2$, two states~$\mathbb{1}/3$ and
+$\rho_{0}$ can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
 and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
@@
 \end{table}
-Verifying $\iota_{2}\circ\mu_{1}$ and $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
-are QIVPMs are also straightforward.
-
-A state~$\rho$ is called totally mixed state if it satisfies $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
-for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
-Given any totally mixed state~$\rho$, we know not only $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-is a QIVPM, but also the collection of states consistent it get closer
-and closer to $\rho$ as the intervals get narrower and narrower,
-eventually collapsing to $\rho$ when the intervals become infinitely
-precise real numbers. To state this result, we need to define a notion
-of distance based on the following norm of a matrix~$A$ as $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}.
-If a state~$\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
-its distance with $\rho$, $\left\Vert \rho-\rho'\right\Vert $, must
-be bounded by $1/n$. Reversely, if the distance between $\rho$ and
-$\rho'$ is bounded by $\left(12n\right)^{-1}$, then $\rho'$ is
-consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$~\citep{HOSTunpublished}.
+
+In the limiting case when the intervals are infinitely precise, i.e.,
+$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$
+with its corresponding $\iota_{\infty}\left(x\right)=[x,x]$, we can
+formulate Gleason's theorem in our framework.
+
+\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
+a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
+the states consistent with it on every project, $\coreBorn\left(\bar{\mu},\events\right)$
+has a unique element. \end{thm}
+
+Our framework allows us to generalize the above theorem to QIVPMs
+induced by the finite-precision extension of the Born rule~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
+The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+get closer and closer to $\rho$ as the intervals get narrower and
+narrower, eventually collapsing to $\rho$ when the intervals become
+infinitely precise real numbers. To state this result, we introduce
+a few technical notions. We call a state~$\rho$ a \emph{totally
+mixed state} if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
+$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $. We
+also define a notion of distance between two states~$\rho$ and $\rho'$
+as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
+and the set of all states whose distance with $\rho$ is bounded by
+$\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.
+
+\begin{thm}[Finite-precision Extension of Gleason~\citep{HOSTunpublished}]In
+a Hilbert space $\Hilb$ of dimension $3$, given any totally mixed
+state~$\rho$, 
+\begin{equation}
+B_{\frac{1}{12n}}\left(\rho\right)\subseteq\coreBorn\left(\iota_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)\subseteq B_{1/n}\left(\rho\right)\,.
+\end{equation}
+\end{thm}\yutsung{Do we need to summarize the proof?}
+
+\noindent In another word, if a state~$\rho'$ is consistent with
+$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, its distance with $\rho$,
+$\left\Vert \rho-\rho'\right\Vert $, must be bounded by $1/n$. Reversely,
+if the distance between $\rho$ and $\rho'$ is bounded by $\frac{1}{12n}$,
+then $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
 For example, $\mathbb{1}/3$ and $\rho_{0}$ are both totally mixed
@@
 
-In the limiting case when the intervals are infinitely precise, i.e.,
-$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, even if a QIVPM is
-not \emph{a priori} known to be induced by a state, it can be recast
-as a real-valued one and will have a unique state consistent with
-it on every projector. This fact is called Gleason's theorem.
-
-\begin{thm}[Gleason~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
-a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
-measure~$\mu:\events\rightarrow[0,1]$, there exists a unique state~$\rho$
-such that $\mu=\mu_{\rho}^{\mathrm{B}}$. \end{thm}
-
-\noindent However, if the intervals are only with finite-precision,
-there are some QIVPMs which cannot be consistent with any state. Given
-a three-dimensional Hilbert space $\Hilb$ with an orthonormal basis
-$\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
+If a QIVPM is not \emph{a priori} known to be induced by a state,
+there are some QIVPMs which cannot be consistent with any state.
+
+\begin{example*}Given a three-dimensional Hilbert space $\Hilb$
+with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
+let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
 $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
@@
 so Gleason's theorem cannot be extended to general QIVPMs because
-of this example.
+of this example.\end{example*}
 

### 2017-09-18 prop_letter.tex
prop_letter.tex floatfix Added, but still stuck...
prop_letter.tex \section{Gleason} Updating...

@@
 \documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
-showkeys, longbibliography, amsmath, amssymb]{revtex4-1} 
+showkeys, longbibliography, amsmath, amssymb, floatfix]{revtex4-1} 
 \usepackage{fullpage}
@@
 We then provide a finite precision variant of Gleason's theorem for
-QIVPMs induced by the Born rule, but there are also some general QIVPMs
-may not be induced by any quantum probability measure, i.e., no state
-is consistent with these kind of QIVPMs.
+the Born QIVPMs, but there are also some general QIVPMs may not be
+induced by any quantum probability measure, i.e., no state is consistent
+with these kind of QIVPMs.
 
@@
 
-Our framework allows us to generalize the above theorem to QIVPMs
-induced by the finite-precision extension of the Born rule~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
-The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-get closer and closer to $\rho$ as the intervals get narrower and
-narrower, eventually collapsing to $\rho$ when the intervals become
-infinitely precise real numbers. To state this result, we introduce
-a few technical notions. We call a state~$\rho$ a \emph{totally
-mixed state} if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
-$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $. We
-also define a notion of distance between two states~$\rho$ and $\rho'$
-as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
+Our framework allows us to generalize the above theorem to the Born
+QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$: The collection of
+states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ get closer
+and closer to $\rho$ as the intervals get narrower and narrower,
+eventually collapsing to $\rho$ when the intervals become infinitely
+precise real numbers. To state this result, we introduce a few technical
+notions. We call a state~$\rho$ a \emph{totally mixed state} if
+$0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
+We also define a notion of distance between two states~$\rho$ and
+$\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
 and the set of all states whose distance with $\rho$ is bounded by
@@
 
-\begin{thm}[Finite-precision Extension of Gleason~\citep{HOSTunpublished}]In
-a Hilbert space $\Hilb$ of dimension $3$, given any totally mixed
-state~$\rho$, 
+\begin{thm}[Finite-precision Extension of Gleason's theorem for the
+Born QIVPMs~\citep{HOSTunpublished}]In a Hilbert space $\Hilb$
+of dimension $3$, given any totally mixed state~$\rho$, 
 \begin{equation}
@@
 
-\begin{example*}Given a three-dimensional Hilbert space $\Hilb$
-with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
-let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
+\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]In
+a Hilbert space $\Hilb$ of dimension $3$, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
+
+Given a three-dimensional Hilbert space $\Hilb$ with an orthonormal
+basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
 $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
@@
 so Gleason's theorem cannot be extended to general QIVPMs because
-of this example.\end{example*}
+of this example.
 

### 2017-09-18 prop_letter.tex
prop_letter.tex Updating the example...

@@
 \newcommand{\rmd}{\mathrm{d}}
+\newcommand{\rmi}{\mathrm{i}}
 
@@
 
-As an example, consider a three-dimensional Hilbert space with
-orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable
-$\mathbf{O}$ with spectral decomposition
-$\mathbf{O} = \proj{0} + 2\,\proj{1} + 3\,\proj{2}$, i.e., $\lambda_{i}=j$ and $P_{i}=\proj{j-1}$.
-Two fragments of valid probability measures $\mu_1$ and $\mu_2$ that can be associated
-with this space are: $\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
-$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0.5$,
-$\mu_2(\proj{1}) = 0$, $\mu_2(\proj{2}) = 0.5$. By the Born rule, the
-first probability measure corresponds to the quantum system being in
-the pure state $\ket{\phi_1}=(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the
-second corresponds to the quantum system being in the pure state
-$\ket{\phi_2}=(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where in both cases
-$|\alpha|=1$. \yutsung{Notice that we also have
-$\mu_{1}=\mu_{\rho}^{\mathrm{B}}$ for a mixed state~$\rho=0.5\proj{0}+0.5\proj{1}$.
-Maybe we should add ``Or other mixed states.''}
-The expectation values of the observable $\mathbf{O}$,
-$\expval{\mathbf{O}}_{\mu_{1,2}}$, are 1.5 in the first case and 2 in
-the second.
+As an example, consider a three-dimensional Hilbert space with orthonormal
+basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable $\mathbf{O}$
+with spectral decomposition $\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
+i.e., $\lambda_{i}=j$ and $P_{i}=\proj{j-1}$. Two fragments of valid
+probability measures~$\mu_{1}$ and $\mu_{2}$ that can be associated
+with this space are defined in Table~\ref{tab:quantum-probability-measure}.
+\begin{table}
+\noindent \centering{}\caption{\label{tab:quantum-probability-measure}Two fragments of valid probability
+measures~$\mu_{1}$ and $\mu_{2}$.}
+\begin{tabular}{ccc}
+\toprule 
+\addlinespace
+$\ket{\psi}$ & $\mu_{1}(\proj{\psi})$ & $\mu_{2}(\proj{\psi})$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\ket{0}$ & $\frac{1}{2}$ & $\frac{1}{2}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\ket{1}$ & $\frac{1}{2}$ & $0$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\ket{2}$ & $0$ & $\frac{1}{2}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ & $1$ & $\frac{1}{4}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\ket{\rmi}=\frac{\ket{0}+\rmi\ket{1}}{\sqrt{2}}$ & $\frac{1}{2}$ & $\frac{1}{4}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\ket{\ps'}=\frac{\ket{0}+\ket{2}}{\sqrt{2}}$ & $\frac{1}{4}$ & $\frac{1}{2}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\ket{\rmi'}=\frac{\ket{0}+\rmi\ket{2}}{\sqrt{2}}$ & $\frac{1}{4}$ & $\frac{1}{2}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\ket{\ps''}=\frac{\ket{1}+\ket{2}}{\sqrt{2}}$ & $\frac{1}{4}$ & $\frac{1}{4}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\ket{\rmi''}=\frac{\ket{1}+\rmi\ket{2}}{\sqrt{2}}$ & $\frac{1}{4}$ & $\frac{1}{4}$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+By the Born rule, the first probability measure corresponds to the
+quantum system being in the pure state $\ket{\ps}=(\ket{0}+\ket{1})/\sqrt{2}$
+and the second corresponds to the quantum system being in the state
+$\rho=(\proj{0}+\proj{2})/2$. The expectation values of the observable
+$\mathbf{O}$, $\expval{\mathbf{O}}_{\mu_{1,2}}$, are 1.5 in the
+first case and 2 in the second.
 
@@
 to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
-themselves lie between the minimum and maximum bounds of the
-probability intervals associated with each state~$\rho$ that is
-consistent with $\bar{\mu}$ on every projector in the spectral
-decomposition of the observable. If $\bar{\mu}$ is a conventional
-(Born) probability measure induced by a state $\rho$, then
-the Born rule probability induced by every state in
-$\coreBorn\left(\bar{\mu},\events'\right)$ will be
-$\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point, thus
-reducing the definition to that of
-Eq.~(\ref{eq:quantum-expectation}).
+themselves lie between the minimum and maximum bounds of the probability
+intervals associated with each state~$\rho$ that is consistent with
+$\bar{\mu}$ on every projector in the spectral decomposition of the
+observable. If $\bar{\mu}$ is a conventional (Born) probability measure
+induced by a state $\rho$, then the Born rule probability induced
+by every state in $\coreBorn\left(\bar{\mu},\events'\right)$ will
+be $\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point,
+thus reducing the definition to that of Eq.~(\ref{eq:quantum-expectation}).
 For example, we can extend one of the fragments of valid probability
-measures~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy} to a QIVPM~$\bar{\mu}_{3}$:
-$\bar{\mu}_{3}(\proj{0})=\left[0.5,0.5\right]$, $\bar{\mu}_{3}(\proj{1})=\left[0.5,0.5\right]$,
-and $\bar{\mu}_{3}(\proj{2})=\left[0,0\right]$. For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
-the Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ of any state~$\rho$
-consistent with $\bar{\mu}_{3}$ on $\proj{0}$, $\proj{1}$, and
-$\proj{2}$ must be $\mu_{1}$. Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
+measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
+to a QIVPM~$\bar{\mu}_{3}$: $\bar{\mu}_{3}(\proj{0})=\left[\frac{1}{2},\frac{1}{2}\right]$,
+$\bar{\mu}_{3}(\proj{1})=\left[\frac{1}{2},\frac{1}{2}\right]$, and
+$\bar{\mu}_{3}(\proj{2})=\left[0,0\right]$, ... etc. For the same
+observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$, the only
+state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$, $\proj{1}$,
+and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
+Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
 which is an interval, but not between $0$ and $1$ because it is
@@
 to commuting projectors, the definition above is consistent with the
-classical notion of the \emph{Choquet
-  integral}~\cite{GilboaSchmeidler1994,Grabisch2016} which is used to
-calculate the expectation value of random variables as a weighted
-average.
+classical notion of the \emph{Choquet integral}~\citep{GilboaSchmeidler1994,Grabisch2016}
+which is used to calculate the expectation value of random variables
+as a weighted average.
 
@@
 what a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
-the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
-probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
-This result will first be generalized in this section, and introduce
-a finite-precision extension of the Born rule~\citep{peres1995quantum,544199,Jaeger2007}.
-The Born rule is essential to compute the conventional quantum probability
-because any quantum probability measure can be induced by the Born
-rule according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the state~$\proj{\ps}$.
+The way we extending a state to a QIVPM will first be generalized
+in this section, and introduce a finite-precision extension of the
+Born rule~\citep{peres1995quantum,544199,Jaeger2007}. The Born rule
+is essential to compute the conventional quantum probability because
+any quantum probability measure can be induced by the Born rule according
+to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 We then provide a finite precision variant of Gleason's theorem for
@@
 
-The quantum probability measure~$\mu_{1}$ maps some projectors to
-$0$ or $0.5$, which are replaced by $\left[0,0\right]$ or $\left[0.5,0.5\right]$
-to get $\bar{\mu}_{3}$. Replacing numbers by intervals containing
-them can be generalized if we carefully pick a set of intervals and
-a rule to select the correct interval when intervals are overlapping.
-For example, consider the following collection of intervals: 
+When we constructed $\bar{\mu}_{3}$, we replaced the real-valued
+probability~$0$ and $\frac{1}{2}$ by $\left[0,0\right]$ and $\left[\frac{1}{2},\frac{1}{2}\right]$,
+respectively. Replacing numbers by intervals containing them can be
+generalized if we carefully pick a set of intervals and a rule to
+select the correct interval when intervals are overlapping. For example,
+consider the following collection of intervals: 
 \begin{equation}

### 2017-09-18 prop_letter.tex
prop_letter.tex Reviewing...

@@
 % }
+\yutsung{Still not comfortable about the current statement...}
 These results provide a new insight into the Meyer-Mermin debate by
@@
 with spectral decomposition $\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
-i.e., $\lambda_{i}=j$ and $P_{i}=\proj{j-1}$. Two fragments of valid
+i.e., $\lambda_{i}=i$ and $P_{i}=\proj{i-1}$. Two fragments of valid
 probability measures~$\mu_{1}$ and $\mu_{2}$ that can be associated
@@
 but neither $\unknown\subseteq\left[0,\frac{1}{3}\right]$ nor $\unknown\subseteq\left[1-\frac{1}{3},1\right]$.
+Finally, when $\delta=1$, because every interval is a subset of $\unknown$,
+every QIVPM is $1$-deterministic. In particular, the informativeness
+QIVPM~$\bar{\mu}_{1}$ and the Born QIVPM~$\bar{\mu}_{3}$ defined
+in Sec.~\ref{sec:Interval-Uncertainty} are both $1$-deterministic.
 
@@
 in this section, and introduce a finite-precision extension of the
-Born rule~\citep{peres1995quantum,544199,Jaeger2007}. The Born rule
-is essential to compute the conventional quantum probability because
-any quantum probability measure can be induced by the Born rule according
-to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. The
+Born rule is essential to compute the conventional quantum probability
+because any quantum probability measure can be induced by the Born
+rule according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 We then provide a finite precision variant of Gleason's theorem for

### 2017-09-19 prop_letter.tex
prop_letter.tex Reviewing...

@@
 conventional quantum probability spaces, there is generally no unique
-state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
+state~$\rho$ consistent with a QIVPM~\citep{HOSTunpublished}. We say that a QIVPM $\bar{\mu}$
 is consistent with a state $\rho$ and projector~$P$ if the interval
@@
 measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
-to a QIVPM~$\bar{\mu}_{3}$: $\bar{\mu}_{3}(\proj{0})=\left[\frac{1}{2},\frac{1}{2}\right]$,
-$\bar{\mu}_{3}(\proj{1})=\left[\frac{1}{2},\frac{1}{2}\right]$, and
-$\bar{\mu}_{3}(\proj{2})=\left[0,0\right]$, ... etc. For the same
+to a QIVPM~$\bar{\mu}_{3}$:
+\begin{equation}
+\begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
+\bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
+\end{aligned}
+\label{eq:Born-QIVPM}
+\end{equation}
+For the same
 observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$, the only
@@
 every QIVPM is $1$-deterministic. In particular, the informativeness
-QIVPM~$\bar{\mu}_{1}$ and the Born QIVPM~$\bar{\mu}_{3}$ defined
-in Sec.~\ref{sec:Interval-Uncertainty} are both $1$-deterministic.
+QIVPM~$\bar{\mu}_{1}$ defined in Eq.~(\ref{eq:no-information-IVPM})
+and the Born QIVPM~$\bar{\mu}_{3}$ defined in Eq.~(\ref{eq:Born-QIVPM})
+are both $1$-deterministic.
 
@@
 
-\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]In
+\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
 a Hilbert space $\Hilb$ of dimension $3$, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
@@
 
-Given a three-dimensional Hilbert space $\Hilb$ with an orthonormal
-basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
-$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
-and \begin{subequations} 
+\noindent Given a three-dimensional Hilbert space $\Hilb$ with an
+orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let
+$\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
+$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and \begin{subequations}
 \begin{eqnarray}
@@
 of this example.
+
+Despite the non-extensible of Gleason's theorem to general QIVPMs,
+when we restrict $\bar{\mu}$ on any commuting subspace of events~$\events_{C}$,
+$\bar{\mu}$ becomes classical, and Thm.~\ref{thm:Shapley} guarantees
+$\coreBorn\left(\bar{\mu},\events_{C}\right)$ is nonempty. In this
+sense, Thm.~\ref{thm:Non-extensible-of-Gleason's} is a completely
+new phenomena when we generalize both classical IVPMs and quantum
+probability measures to QIVPMs.
 

### 2017-09-19 prop_letter.tex
prop_letter.tex Add comments...

@@
 conventional quantum probability spaces, there is generally no unique
-state~$\rho$ consistent with a QIVPM~\citep{HOSTunpublished}. We say that a QIVPM $\bar{\mu}$
+state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
 is consistent with a state $\rho$ and projector~$P$ if the interval
@@
 that is consistent with every event in $\events_C$. In contrast, as we
-illustrate in the next section, the set of states
+illustrate in Sec.~\ref{sec:Gleason}, the set of states
 $\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
@@
 be $\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point,
-thus reducing the definition to that of Eq.~(\ref{eq:quantum-expectation}).
+thus reducing the definition to that of Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
 For example, we can extend one of the fragments of valid probability
@@
 \end{equation}
-For the same
-observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$, the only
-state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$, $\proj{1}$,
-and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
+For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
+the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
+$\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
 Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
@@
 which is used to calculate the expectation value of random variables
-as a weighted average.
+as a weighted average~\citep{HOSTunpublished}.
 
@@
 certainty. As $\delta$ gets larger, the QIVPM allows for more indeterminate
-behavior. To illustrate the example easier, we restrict ourselves
+behavior. To illustrate the examples easier, we restrict ourselves
 to the classical subspace of commuting events~$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
@@
 Finally, when $\delta=1$, because every interval is a subset of $\unknown$,
-every QIVPM is $1$-deterministic. In particular, the informativeness
+every QIVPM is $1$-deterministic. In particular, the non-informative
 QIVPM~$\bar{\mu}_{1}$ defined in Eq.~(\ref{eq:no-information-IVPM})
@@
 number of occurrences of the interval $[-1,-1]$ in each row and hence
-in the entire table. However, looking at the expectation values of the
+in the entire table~\citep{HOSTunpublished}. However, looking at the expectation values of the
 observables in each column, there must be an even number of
 occurrences of the interval $[-1,-1]$ in the first two columns and an
-odd number in the $j=2$ column and hence in the entire table. The
+odd number in the $j=2$ column and hence in the entire table~\citep{HOSTunpublished}. The
 contradiction implies the non-existence of the assumed 0-deterministic
@@
 It remains to verify that $\bar{\mu}^{\textrm{D}}$ is indeed a
-0-deterministic QIVPM by checking that for orthogonal
+0-deterministic QIVPM by checking~\citep{HOSTunpublished} that for orthogonal
 operators~$P_{0}$ and $P_{1}$, we have that
@@
 the theory becomes non-contextual.
+
+\yutsung{About contextuality or non-contextuality, summarize the
+existence and non-existence of $\delta$-deterministic QIVPMs in Fig.~\ref{fig:contextuality-non-contextuality}.}
+\begin{figure*}
+\[
+\xymatrix{ & \delta=0 &  & \delta=\frac{1}{3} & \delta=1\\
+\textrm{Classical IVPMs} & \ar[rrr] &  &  & \,\\
+\textrm{Instance} & \bar{\mu}_{4} &  & \bar{\mu}_{5},\bar{\mu}_{6} & \bar{\mu}_{2},\textrm{ every classical IVPM}\\
+\textrm{Interpertation} & \textrm{D Classical Theory} &  & \textrm{P Classical Theory?} & \textrm{P Classical Theory?}\\
+\textrm{QIVPMs} & \ar@2{|-|}[rr]_{\textrm{NE by Thm. \ref{cor:Kochen-Specker-IVPM}}}\ar[rrr] &  &  & \,\\
+\textrm{Instance} & \textrm{NE by Thm. }\ref{thm:Kochen-Specker} &  & \iota_{\infty}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}} & \bar{\mu}_{1},\bar{\mu}_{3}\textrm{, every QIVPM}\\
+\textrm{Interpertation} & \textrm{NEDNCHVT}\ar@{}[rr]|-{\textrm{NEPNCHVT?}} &  & \textrm{EPNCHVT?} & \textrm{EPNCHVT?}
+}
+\]
+\caption{\label{fig:contextuality-non-contextuality}The figure summarize the
+existence and non-existence of $\delta$-deterministic classical IVPMs
+and QIVPMs. In the figure, ``D'' denotes ``deterministic,'' P
+denotes ``probabilitic,'' ``(N)E'' denotes ``(Non-)Exist,''
+``(N)C'' denotes ``(Non-)Contextuality,'' and HVT denotes ``Hidden-Variable
+Theory.''}
+\end{figure*}
 

### 2017-09-20 prop_iop.tex
prop_letter.tex \section{Gleason} Updating...
prop_letter.tex Updating comments...

@@
 }\end{equation}
-When the number of elements in $\Omega\le3$, either $E_{0}\cap E_{1}=\emptyset$
-or $E_{0}\cup E_{1}=\Omega$ must happen so that $\bar{\mu}^{\Omega}$
-is convex. \end{proof}
+When the number of elements in $\Omega\le3$, one of the following
+must happen
+\begin{enumerate}
+\item $E_{0}\cap E_{1}=\emptyset$.
+\item $E_{0}\cup E_{1}=\Omega$.
+\item $E_{0}\subseteq E_{1}$ or $E_{1}\subseteq E_{0}$.
+\end{enumerate}
+so that $\bar{\mu}^{\Omega}$ is convex. \end{proof}
 
@@
 
-\subsection{Expectation Values for $0$-deterministic CIVPMs}
-
-Finally, we are going to focus on CIVPMs whose range is $\mathscr{I}_{\mathrm{D}}$.
-
-\begin{lemma}\label{lemma:deterministic-CIVPM}Given a CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
-the following statements are true:
+\subsection{Expectation Values for $\delta$-deterministic CIVPMs}
+
+Finally, we are going to focus on $\delta$-deterministic CIVPMs.
+
+\begin{lemma}\label{lemma:deterministic-CIVPM}Consider a sample
+space~$\Omega$ with $d$ elements, and $\delta<1/d$. Given a $\delta$-deterministic
+CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, the following statements
+are true:
 \begin{enumerate}
-\item Its left-end~$\mul$ and right-end~$\mur$ are the same CRVPM, and
-will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $.
-\item There is a unique $\omega_{0}\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\left\{ \pmeas\left(\left\{ \omega_{0}\right\} \right)\right\} =\necess$,
+\item If $\bar{\mu}$ is $0$-deterministic, its left-end~$\mul$ and right-end~$\mur$
+are the same CRVPM, and will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $.
+\item There is a unique element~$\omega_{0}\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)\subseteq\left[1-\delta,1\right]$,
+denoted by $\bar{\mu}^{-1}\left(\left[1-\delta,1\right]\right)$.
+In particular, if $\bar{\mu}$ is $0$-deterministic, $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\left\{ \pmeas\left(\left\{ \omega_{0}\right\} \right)\right\} =\necess$,
 denoted by $\pmeas^{-1}\left(1\right)$ or $\bar{\mu}^{-1}\left(\necess\right)$.
@@
 \item The directly consequence of lemma~\ref{lemma:QIVPM2QCM}.
-\item Since the range of $\pmeas$ is $\left\{ 1,0\right\} $ and $\sum_{\omega\in\Omega}\pmeas\left(\left\{ \omega\right\} \right)=1$,
-there is a unique $\omega_{0}$ such that $\mu\left(\left\{ \omega_{0}\right\} \right)=1$
-which implies $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\necess$.
+\item We have either $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,\delta\right]$
+or $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[1-\delta,1\right]$.
+\begin{casenv}
+\item If $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,\delta\right]$
+for all $\omega\in\Omega$, then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,d\delta\right]\Rightarrow d\delta>1$.
+A contradiction!
+\item If there are more than one~$\omega\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[1-\delta,1\right]$,
+then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[2-2\delta,d\right]\Rightarrow2\delta>1$.
+A contradiction!
+\end{casenv}
+Therefore, there is a unique element~$\omega_{0}\in\Omega$ such
+that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)\subseteq\left[1-\delta,1\right]$.
 \end{enumerate}

### 2017-09-20 prop_letter.tex
prop_letter.tex Updating comments...

@@
 % }
-\yutsung{Still not comfortable about the current statement...}
+\yutsung{Still not comfortable about the current statement... Notice
+that the key properties of the non-contextual hidden variable theory
+used in our Mermin-Peres square proof is
+\begin{itemize}
+\item The expectation value of an observable is one of the eigenvalue of
+that observable.
+\item For $0$-deterministic QIVPMs, we have
+\begin{equation}
+\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
+\end{equation}
+\end{itemize}
+I think these two properties might be weakened when $0<\delta<\frac{1}{3}$,
+and completely break down when $\delta\ge\frac{1}{3}$. (Need a proof!)
+If this is the case, the correct statement is that ``the assumption
+of non-contextuality hidden variable theory could be considered hold
+when $\delta<\frac{1}{3}$, and is completely void when $\delta\ge\frac{1}{3}$.''
+So we should not even ask ``whether the existence of QIVPMs when
+$\delta\ge\frac{1}{3}$ implies non-contextuality hidden variable
+theory or not.'' A little bit different analog could be: we should
+not ask ``where is the momentum of a particle when we measure its
+position...''}
+
 These results provide a new insight into the Meyer-Mermin debate by
@@
 
-\yutsung{About contextuality or non-contextuality, summarize the
-existence and non-existence of $\delta$-deterministic QIVPMs in Fig.~\ref{fig:contextuality-non-contextuality}.}
-\begin{figure*}
-\[
-\xymatrix{ & \delta=0 &  & \delta=\frac{1}{3} & \delta=1\\
-\textrm{Classical IVPMs} & \ar[rrr] &  &  & \,\\
-\textrm{Instance} & \bar{\mu}_{4} &  & \bar{\mu}_{5},\bar{\mu}_{6} & \bar{\mu}_{2},\textrm{ every classical IVPM}\\
-\textrm{Interpertation} & \textrm{D Classical Theory} &  & \textrm{P Classical Theory?} & \textrm{P Classical Theory?}\\
-\textrm{QIVPMs} & \ar@2{|-|}[rr]_{\textrm{NE by Thm. \ref{cor:Kochen-Specker-IVPM}}}\ar[rrr] &  &  & \,\\
-\textrm{Instance} & \textrm{NE by Thm. }\ref{thm:Kochen-Specker} &  & \iota_{\infty}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}} & \bar{\mu}_{1},\bar{\mu}_{3}\textrm{, every QIVPM}\\
-\textrm{Interpertation} & \textrm{NEDNCHVT}\ar@{}[rr]|-{\textrm{NEPNCHVT?}} &  & \textrm{EPNCHVT?} & \textrm{EPNCHVT?}
-}
-\]
-\caption{\label{fig:contextuality-non-contextuality}The figure summarize the
-existence and non-existence of $\delta$-deterministic classical IVPMs
-and QIVPMs. In the figure, ``D'' denotes ``deterministic,'' P
-denotes ``probabilitic,'' ``(N)E'' denotes ``(Non-)Exist,''
-``(N)C'' denotes ``(Non-)Contextuality,'' and HVT denotes ``Hidden-Variable
-Theory.''}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-09-20 prop_letter.tex
prop_letter.tex Updating interpertation...

@@
 \newtheorem{cor}{Corollary}[thm]
+\newtheorem{assumption}{Assumption}
 \theoremstyle{definition}
@@
 \newtheorem*{example*}{Example}
+\newtheorem{condition}[assumption]{Condition}
 
@@
 % }
-\yutsung{Still not comfortable about the current statement... Notice
-that the key properties of the non-contextual hidden variable theory
-used in our Mermin-Peres square proof is
+\yutsung{Still not comfortable about the current statement... To
+clarify what we did, here we review the assumption in the original
+Kochen-Specker theorem, and what we used in our variant version.}
+
+The original Kochen-Specker theorem assumes the following there is
+a hidden variable assignment~$v$ for every observables~$\mathbf{O}$
+such that
+
+\begin{assumption}If $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$ are
+commuting, then $v$ is linear, i.e., $v\left(x_{0}\mathbf{O}_{0}+x_{1}\mathbf{O}_{1}\right)=x_{0}v\left(\mathbf{O}_{0}\right)+x_{1}v\left(\mathbf{O}_{1}\right)$
+for $x_{0}$ and $x_{1}\in\mathbb{C}$.\end{assumption}
+
+\begin{assumption}\label{assu:times}If $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$
+are commuting, then $v\left(\mathbf{O}_{0}\mathbf{O}_{1}\right)=v\left(\mathbf{O}_{0}\right)v\left(\mathbf{O}_{1}\right)$.\end{assumption}
+
+\noindent These two assumptions implies the following conditions:
+
+\begin{condition}\label{cond:eigenvalue}$v\left(\mathbf{O}\right)$
+must be an eigenvalue of $\mathbf{O}$.\end{condition}
+
+\noindent In particular, Condition~\ref{cond:eigenvalue} implies
+$v(P)=0$ or $1$ for any projector~$P$. Together with $v\left(\mathbb{1}\right)=1$.
+We have:
+
+\begin{condition}\label{cond:sum-one}If a set of commuting projectors~$P_{i}$
+satisfies $\sum_{i}P_{i}=1$, then $\sum_{i}v(P_{i})=1$.\end{condition}
+
+\noindent Kochen-Specker~\citep{kochenspecker1967} and Peres~\citep{peres1995quantum}
+then proved the contradiction based on Condition~\ref{cond:sum-one}.
+The proof given by Mermin~\citep{Mermin1990Simple} is particular
+short and easy to understand, because he proved proved the contradiction
+based on Assumption~\ref{assu:times} and Condition~\ref{cond:eigenvalue}.
+
+\yutsung{Let's move on to what we did for 0-Deterministic Variant
+of Kochen-Specker theorem~\ref{thm:Kochen-Specker}.}
+
+\yutsung{Finally, we can say about Finite-precision Extension of
+Kochen-Specker theorem~\ref{cor:Kochen-Specker-IVPM}.}
+
+Notice that the key properties of the non-contextual hidden variable
+theory used in our Mermin-Peres square proof is
 \begin{itemize}
@@
 not ask ``where is the momentum of a particle when we measure its
-position...''}
+position...''
+
+\yutsung{End of discussion!}
 

### 2017-09-21 prop_letter.tex
prop_letter.tex Updating interpertation...

@@
 \yutsung{Still not comfortable about the current statement... To
-clarify what we did, here we review the assumption in the original
-Kochen-Specker theorem, and what we used in our variant version.}
-
-The original Kochen-Specker theorem assumes the following there is
-a hidden variable assignment~$v$ for every observables~$\mathbf{O}$
-such that
-
-\begin{assumption}If $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$ are
-commuting, then $v$ is linear, i.e., $v\left(x_{0}\mathbf{O}_{0}+x_{1}\mathbf{O}_{1}\right)=x_{0}v\left(\mathbf{O}_{0}\right)+x_{1}v\left(\mathbf{O}_{1}\right)$
+clarify what we did as requested by Andy, here we review the assumption
+in the original Kochen-Specker theorem, and what we used in our variant
+version.}
+
+The original Kochen-Specker theorem assumes there is a hidden variable
+assignment~$v$ for every observables~$\mathbf{O}$ such that $v\left(\mathbf{O}\right)\in\mathbb{R}$
+and satisfying the following two assumptions.
+
+\begin{assumption}\label{assu:linear}If $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$
+are commuting, then $v$ is linear, i.e., $v\left(x_{0}\mathbf{O}_{0}+x_{1}\mathbf{O}_{1}\right)=x_{0}v\left(\mathbf{O}_{0}\right)+x_{1}v\left(\mathbf{O}_{1}\right)$
 for $x_{0}$ and $x_{1}\in\mathbb{C}$.\end{assumption}
@@
 
+\noindent Or equivalently.
+
+\begin{condition}\label{cond:one-one}If a set of commuting projectors~$P_{i}$
+satisfies $\sum_{i}P_{i}=1$, then there exists exactly one $P_{i_{0}}$
+such that $v\left(P_{i_{0}}\right)=1$ and $v\left(P_{i}\right)=0$
+for $i\ne i_{0}$.\end{condition}
+
 \noindent Kochen-Specker~\citep{kochenspecker1967} and Peres~\citep{peres1995quantum}
-then proved the contradiction based on Condition~\ref{cond:sum-one}.
-The proof given by Mermin~\citep{Mermin1990Simple} is particular
-short and easy to understand, because he proved proved the contradiction
-based on Assumption~\ref{assu:times} and Condition~\ref{cond:eigenvalue}.
+then got the contradiction based on Condition~\ref{cond:sum-one}
+or \ref{cond:one-one}. Instead of Condition~\ref{cond:sum-one},
+Mermin~\citep{Mermin1990Simple} got the contradiction based on Assumption~\ref{assu:times}
+and Condition~\ref{cond:eigenvalue} which makes his proof particularly
+short and easy to understand.
 
@@
 
+The natural KS assumption in 0-deterministic QIVPM is the following
+one correspondence of Condition~\ref{cond:sum-one}.
+
+\begin{assumption}\label{assu:0-deterministicQIVPM}There exists
+a 0-deterministic QIVPM.\end{assumption}
+
+\noindent This assumption itself can deduce the same contradiction
+exactly the same as Kochen-Specker~\citep{kochenspecker1967} and
+Peres~\citep{peres1995quantum} did, but the proof will be as long
+and tedious as theirs. In order to follow the clearer Mermin's proof,
+we deduce the following condition based on our assumption:
+
+\noindent \begin{condition}\label{cond:one-one-0-deterministicQIVPM}For
+a $0$-deterministic QIVPMs~$\bar{\mu}$, if a set of commuting projectors~$P_{i}$
+satisfies $\sum_{i}P_{i}=1$, then there exists exactly one $P_{i_{0}}$
+such that $\bar{\mu}\left(P_{i_{0}}\right)=\necess$ and $\bar{\mu}\left(P_{i}\right)=\imposs$
+for $i\ne i_{0}$.\end{condition}
+
+\noindent The preceding condition is the key step to deduce the following
+two conditions used in Mermin's proof.
+
+\begin{condition}\label{cond:eigenvalue-0-deterministicQIVPM}For
+a $0$-deterministic QIVPMs~$\bar{\mu}$, $\expval{\mathbf{O}}_{\bar{\mu}}$
+must be an eigenvalue of $\mathbf{O}$.\end{condition}
+
+\begin{condition}\label{assu:times-0-deterministicQIVPM}For a $0$-deterministic
+QIVPMs~$\bar{\mu}$, if $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$ are
+commuting, then $\expval{\mathbf{O}_{0}\mathbf{O}_{1}}_{\bar{\mu}}=\expval{\mathbf{O}_{0}}_{\bar{\mu}}\expval{\mathbf{O}_{1}}_{\bar{\mu}}$.\end{condition}
+
+\noindent Notice that the expectation value relative to $0$-deterministic
+$\bar{\mu}$ plays the same role as the hidden variable assignment~$v$
+in the original Kochen-Specker theorem. After we proved these two
+conditions, we can easily follow Mermin to build a contradiction.
+
 \yutsung{Finally, we can say about Finite-precision Extension of
@@
 
-Notice that the key properties of the non-contextual hidden variable
-theory used in our Mermin-Peres square proof is
-\begin{itemize}
-\item The expectation value of an observable is one of the eigenvalue of
-that observable.
-\item For $0$-deterministic QIVPMs, we have
-\begin{equation}
-\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
-\end{equation}
-\end{itemize}
+The natural KS assumption for 0-deterministic QIVPM is just ``it
+exists.'' We might image the natural KS assumption for $\delta$-deterministic
+QIVPM is the same, and start from the following assumption.
+
+\begin{assumption}\label{assu:delta-deterministicQIVPM}There exists
+a $\delta$-deterministic QIVPM.\end{assumption}
+
+\noindent This assumption draw the same contradiction when $\delta<\frac{1}{3}$,
+and there is no contradiction when $\delta\ge\frac{1}{3}$. Therefore,
+we want to understand what happens when $\delta$ passing $\frac{1}{3}$.
+Notice that Assumption~\ref{assu:delta-deterministicQIVPM} looks
+similar, but is not exactly equivalent to Condition~\ref{cond:sum-one}
+and Assumption~\ref{assu:0-deterministicQIVPM}. Therefore, in order
+to understand better the physical meaning, and in order to know whether
+we get a non-contextual hidden variable theory, a contextual hidden
+variable theory, or not a hidden variable theory at all, we might
+need to prove the corresponding states of Condition~\ref{cond:one-one},
+Condition~\ref{cond:eigenvalue}, Assumption~\ref{assu:linear},
+and Assumption~\ref{assu:times}.
+
+\noindent I personally believe they are approximately hold for small
+$\delta$, but void when $\delta$ is large enough.
+
 I think these two properties might be weakened when $0<\delta<\frac{1}{3}$,

### 2017-09-21 prop_letter.tex
prop_letter.tex Updating Kochen-Specker interpertation...

@@
 
-\begin{condition}\label{cond:one-one}If a set of commuting projectors~$P_{i}$
-satisfies $\sum_{i}P_{i}=1$, then there exists exactly one $P_{i_{0}}$
-such that $v\left(P_{i_{0}}\right)=1$ and $v\left(P_{i}\right)=0$
+\begin{condition}\label{cond:one-one}Given an orthonormal basis~$\Omega$,
+then there exists exactly one $\ket{\psi_{i_{0}}}\in\Omega$ such
+that $v\left(\proj{\psi_{i_{0}}}\right)=1$ and $v\left(\proj{\psi_{i}}\right)=0$
 for $i\ne i_{0}$.\end{condition}
@@
 
-\noindent \begin{condition}\label{cond:one-one-0-deterministicQIVPM}For
-a $0$-deterministic QIVPMs~$\bar{\mu}$, if a set of commuting projectors~$P_{i}$
-satisfies $\sum_{i}P_{i}=1$, then there exists exactly one $P_{i_{0}}$
-such that $\bar{\mu}\left(P_{i_{0}}\right)=\necess$ and $\bar{\mu}\left(P_{i}\right)=\imposs$
+\begin{condition}[0-deterministic Variant of Condition~\ref{cond:one-one}]\label{cond:one-one-0-deterministicQIVPM}For
+a $0$-deterministic QIVPMs~$\bar{\mu}$, given an orthonormal basis~$\Omega$,
+then there exists exactly one $\ket{\psi_{i_{0}}}\in\Omega$ such
+that $\bar{\mu}\left(\proj{\psi_{i_{0}}}\right)=\necess$ and $\bar{\mu}\left(\proj{\psi_{i}}\right)=\imposs$
 for $i\ne i_{0}$.\end{condition}
@@
 
-\begin{condition}\label{cond:eigenvalue-0-deterministicQIVPM}For
+\begin{condition}[0-deterministic Variant of Condition~\ref{cond:eigenvalue}]\label{cond:eigenvalue-0-deterministicQIVPM}For
 a $0$-deterministic QIVPMs~$\bar{\mu}$, $\expval{\mathbf{O}}_{\bar{\mu}}$
@@
 
-\begin{condition}\label{assu:times-0-deterministicQIVPM}For a $0$-deterministic
-QIVPMs~$\bar{\mu}$, if $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$ are
-commuting, then $\expval{\mathbf{O}_{0}\mathbf{O}_{1}}_{\bar{\mu}}=\expval{\mathbf{O}_{0}}_{\bar{\mu}}\expval{\mathbf{O}_{1}}_{\bar{\mu}}$.\end{condition}
+\begin{condition}[0-deterministic Variant of Assumption~\ref{assu:times}]\label{assu:times-0-deterministicQIVPM}For
+a $0$-deterministic QIVPMs~$\bar{\mu}$, if $\mathbf{O}_{0}$ and
+$\mathbf{O}_{1}$ are commuting, then $\expval{\mathbf{O}_{0}\mathbf{O}_{1}}_{\bar{\mu}}=\expval{\mathbf{O}_{0}}_{\bar{\mu}}\expval{\mathbf{O}_{1}}_{\bar{\mu}}$.\end{condition}
 
@@
 
-\begin{assumption}\label{assu:delta-deterministicQIVPM}There exists
-a $\delta$-deterministic QIVPM.\end{assumption}
+\begin{assumption}[Finite-precision Extension of {Condition~}\ref{cond:sum-one}]\label{assu:delta-deterministicQIVPM}There
+exists a $\delta$-deterministic QIVPM.\end{assumption}
 
@@
 and Assumption~\ref{assu:times}.
-
-\noindent I personally believe they are approximately hold for small
-$\delta$, but void when $\delta$ is large enough.
-
-I think these two properties might be weakened when $0<\delta<\frac{1}{3}$,
-and completely break down when $\delta\ge\frac{1}{3}$. (Need a proof!)
-If this is the case, the correct statement is that ``the assumption
-of non-contextuality hidden variable theory could be considered hold
-when $\delta<\frac{1}{3}$, and is completely void when $\delta\ge\frac{1}{3}$.''
-So we should not even ask ``whether the existence of QIVPMs when
-$\delta\ge\frac{1}{3}$ implies non-contextuality hidden variable
-theory or not.'' A little bit different analog could be: we should
-not ask ``where is the momentum of a particle when we measure its
-position...''
 

### 2017-09-21 prop_iop.tex
prop_iop.tex Updating preamble...

@@
 \usepackage{setstack}
+\usepackage{enumitem}
+\usepackage{amstext}
 
@@
 \newtheorem{claim}[thm]{Claim}
+
+\newlist{casenv}{enumerate}{4}
+\setlist[casenv]{leftmargin=*,align=left,widest={iiii}}
+\setlist[casenv,1]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
+\setlist[casenv,2]{label={{\itshape\ \casename} \roman*.},ref=\roman*}
+\setlist[casenv,3]{label={{\itshape\ \casename\ \alph*.}},ref=\alph*}
+\setlist[casenv,4]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
+\providecommand{\casename}{Case}
 
@@
 
-\subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability
-Measures\label{subsec:Quantum-I_D-valued-Probability}}
+\subsection{Expectation Values for $\delta$-deterministic QIVPMs\label{subsec:Quantum-I_D-valued-Probability}}
 
@@
 of corollary~\ref{cor:Kochen-Specker-IVPM} which doesn't refer the
-Kochen-Specker theorem directly. Assume there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
-we will prove $\bar{\mu}$ has such bizarre properties that it cannot
-exist. These properties will be summarized in the following two lemmas.
+Kochen-Specker theorem directly. Assume there is a $\delta$-deterministic
+QIVPM~$\bar{\mu}$, we will prove $\bar{\mu}$ has such bizarre properties
+that it cannot exist for small $\delta$.
 

### 2017-09-22 prop_iop.tex
prop_letter.tex Updating Kochen-Specker interpertation...

@@
 In particular, if $\bar{\mu}$ is $0$-deterministic, $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\left\{ \pmeas\left(\left\{ \omega_{0}\right\} \right)\right\} =\necess$,
-denoted by $\pmeas^{-1}\left(1\right)$ or $\bar{\mu}^{-1}\left(\necess\right)$.
+$\omega_{0}$ could be denoted by $\pmeas^{-1}\left(1\right)$ or
+$\bar{\mu}^{-1}\left(\necess\right)$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item The directly consequence of lemma~\ref{lemma:QIVPM2QCM}.
+\item The direct consequence of lemma~\ref{lemma:QIVPM2QCM}.
 \item We have either $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,\delta\right]$
@@
 \item If $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,\delta\right]$
-for all $\omega\in\Omega$, then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,d\delta\right]\Rightarrow d\delta>1$.
+for all $\omega\in\Omega$, then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,d\delta\right]\Rightarrow d\delta\ge1$.
 A contradiction!
 \item If there are more than one~$\omega\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[1-\delta,1\right]$,
-then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[2-2\delta,d\right]\Rightarrow2\delta>1$.
+then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[2-2\delta,d\right]\Rightarrow2\delta\ge1$.
 A contradiction!
@@
 that it cannot exist for small $\delta$.
+
+\begin{lemma}\label{lemma:deterministic-QIVPM}Given a Hilbert space
+of dimension~$d$, $\delta<1/d$, and a $\delta$-deterministic QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
+the following statements are true:
+\begin{enumerate}
+\item If $\bar{\mu}$ is $0$-deterministic, its left-end~$\mul$ and right-end~$\mur$
+are the same QRVPM, and will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $.
+\item Given an orthonormal basis~$\Omega$, there is a unique element~$\ket{\psi_{i_{0}}}\in\Omega$
+such that $\bar{\mu}\left(\proj{\psi_{i_{0}}}\right)\subseteq\left[1-\delta,1\right]$,
+denoted by $\bar{\mu}^{-1}\left(\left[1-\delta,1\right]\right)\cap\Omega$.
+In particular, if $\bar{\mu}$ is $0$-deterministic, $\bar{\mu}\left(\proj{\psi_{i_{0}}}\right)=\left\{ \pmeas\left(\proj{\psi_{i_{0}}}\right)\right\} =\necess$,
+$\proj{\psi_{i_{0}}}$ could be denoted by $\pmeas^{-1}\left(1\right)\cap\Omega$
+or $\bar{\mu}^{-1}\left(\necess\right)\cap\Omega$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}~
+\begin{enumerate}
+\item The direct consequence of lemma~\ref{lemma:QIVPM2QCM}.
+\end{enumerate}
+\end{proof}
 

### 2017-09-22 prop_letter.tex
prop_letter.tex Updating Kochen-Specker interpertation...

@@
 
-The natural KS assumption in 0-deterministic QIVPM is the following
-one correspondence of Condition~\ref{cond:sum-one}.
+The natural KS assumption in 0-deterministic QIVPM is the one corresponding
+to Condition~\ref{cond:sum-one}.
 
@@
 
-\noindent Notice that the expectation value relative to $0$-deterministic
-$\bar{\mu}$ plays the same role as the hidden variable assignment~$v$
-in the original Kochen-Specker theorem. After we proved these two
-conditions, we can easily follow Mermin to build a contradiction.
+\noindent After we proved these two conditions, we can easily follow
+Mermin's proof to build a contradiction. Notice that the expectation
+value relative to $0$-deterministic $\bar{\mu}$ plays the same role
+as the hidden variable assignment~$v$ in the original Kochen-Specker
+theorem despite their physical meanings are not exactly the same.
 

### 2017-09-22 prop_letter.tex
prop_letter.tex Achieved the discussion about $\delta \ge 1/3$ into a git tag and clean-up...

--- 2017-09-21 prop_letter.tex
@@
 % }
-\yutsung{Still not comfortable about the current statement... To
-clarify what we did as requested by Andy, here we review the assumption
-in the original Kochen-Specker theorem, and what we used in our variant
-version.}
-
-The original Kochen-Specker theorem assumes there is a hidden variable
-assignment~$v$ for every observables~$\mathbf{O}$ such that $v\left(\mathbf{O}\right)\in\mathbb{R}$
-and satisfying the following two assumptions.
-
-\begin{assumption}\label{assu:linear}If $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$
-are commuting, then $v$ is linear, i.e., $v\left(x_{0}\mathbf{O}_{0}+x_{1}\mathbf{O}_{1}\right)=x_{0}v\left(\mathbf{O}_{0}\right)+x_{1}v\left(\mathbf{O}_{1}\right)$
-for $x_{0}$ and $x_{1}\in\mathbb{C}$.\end{assumption}
-
-\begin{assumption}\label{assu:times}If $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$
-are commuting, then $v\left(\mathbf{O}_{0}\mathbf{O}_{1}\right)=v\left(\mathbf{O}_{0}\right)v\left(\mathbf{O}_{1}\right)$.\end{assumption}
-
-\noindent These two assumptions implies the following conditions:
-
-\begin{condition}\label{cond:eigenvalue}$v\left(\mathbf{O}\right)$
-must be an eigenvalue of $\mathbf{O}$.\end{condition}
-
-\noindent In particular, Condition~\ref{cond:eigenvalue} implies
-$v(P)=0$ or $1$ for any projector~$P$. Together with $v\left(\mathbb{1}\right)=1$.
-We have:
-
-\begin{condition}\label{cond:sum-one}If a set of commuting projectors~$P_{i}$
-satisfies $\sum_{i}P_{i}=1$, then $\sum_{i}v(P_{i})=1$.\end{condition}
-
-\noindent Or equivalently.
-
-\begin{condition}\label{cond:one-one}Given an orthonormal basis~$\Omega$,
-then there exists exactly one $\ket{\psi_{i_{0}}}\in\Omega$ such
-that $v\left(\proj{\psi_{i_{0}}}\right)=1$ and $v\left(\proj{\psi_{i}}\right)=0$
-for $i\ne i_{0}$.\end{condition}
-
-\noindent Kochen-Specker~\citep{kochenspecker1967} and Peres~\citep{peres1995quantum}
-then got the contradiction based on Condition~\ref{cond:sum-one}
-or \ref{cond:one-one}. Instead of Condition~\ref{cond:sum-one},
-Mermin~\citep{Mermin1990Simple} got the contradiction based on Assumption~\ref{assu:times}
-and Condition~\ref{cond:eigenvalue} which makes his proof particularly
-short and easy to understand.
-
-\yutsung{Let's move on to what we did for 0-Deterministic Variant
-of Kochen-Specker theorem~\ref{thm:Kochen-Specker}.}
-
-The natural KS assumption in 0-deterministic QIVPM is the following
-one correspondence of Condition~\ref{cond:sum-one}.
-
-\begin{assumption}\label{assu:0-deterministicQIVPM}There exists
-a 0-deterministic QIVPM.\end{assumption}
-
-\noindent This assumption itself can deduce the same contradiction
-exactly the same as Kochen-Specker~\citep{kochenspecker1967} and
-Peres~\citep{peres1995quantum} did, but the proof will be as long
-and tedious as theirs. In order to follow the clearer Mermin's proof,
-we deduce the following condition based on our assumption:
-
-\begin{condition}[0-deterministic Variant of Condition~\ref{cond:one-one}]\label{cond:one-one-0-deterministicQIVPM}For
-a $0$-deterministic QIVPMs~$\bar{\mu}$, given an orthonormal basis~$\Omega$,
-then there exists exactly one $\ket{\psi_{i_{0}}}\in\Omega$ such
-that $\bar{\mu}\left(\proj{\psi_{i_{0}}}\right)=\necess$ and $\bar{\mu}\left(\proj{\psi_{i}}\right)=\imposs$
-for $i\ne i_{0}$.\end{condition}
-
-\noindent The preceding condition is the key step to deduce the following
-two conditions used in Mermin's proof.
-
-\begin{condition}[0-deterministic Variant of Condition~\ref{cond:eigenvalue}]\label{cond:eigenvalue-0-deterministicQIVPM}For
-a $0$-deterministic QIVPMs~$\bar{\mu}$, $\expval{\mathbf{O}}_{\bar{\mu}}$
-must be an eigenvalue of $\mathbf{O}$.\end{condition}
-
-\begin{condition}[0-deterministic Variant of Assumption~\ref{assu:times}]\label{assu:times-0-deterministicQIVPM}For
-a $0$-deterministic QIVPMs~$\bar{\mu}$, if $\mathbf{O}_{0}$ and
-$\mathbf{O}_{1}$ are commuting, then $\expval{\mathbf{O}_{0}\mathbf{O}_{1}}_{\bar{\mu}}=\expval{\mathbf{O}_{0}}_{\bar{\mu}}\expval{\mathbf{O}_{1}}_{\bar{\mu}}$.\end{condition}
-
-\noindent Notice that the expectation value relative to $0$-deterministic
-$\bar{\mu}$ plays the same role as the hidden variable assignment~$v$
-in the original Kochen-Specker theorem. After we proved these two
-conditions, we can easily follow Mermin to build a contradiction.
-
-\yutsung{Finally, we can say about Finite-precision Extension of
-Kochen-Specker theorem~\ref{cor:Kochen-Specker-IVPM}.}
-
-The natural KS assumption for 0-deterministic QIVPM is just ``it
-exists.'' We might image the natural KS assumption for $\delta$-deterministic
-QIVPM is the same, and start from the following assumption.
-
-\begin{assumption}[Finite-precision Extension of {Condition~}\ref{cond:sum-one}]\label{assu:delta-deterministicQIVPM}There
-exists a $\delta$-deterministic QIVPM.\end{assumption}
-
-\noindent This assumption draw the same contradiction when $\delta<\frac{1}{3}$,
-and there is no contradiction when $\delta\ge\frac{1}{3}$. Therefore,
-we want to understand what happens when $\delta$ passing $\frac{1}{3}$.
-Notice that Assumption~\ref{assu:delta-deterministicQIVPM} looks
-similar, but is not exactly equivalent to Condition~\ref{cond:sum-one}
-and Assumption~\ref{assu:0-deterministicQIVPM}. Therefore, in order
-to understand better the physical meaning, and in order to know whether
-we get a non-contextual hidden variable theory, a contextual hidden
-variable theory, or not a hidden variable theory at all, we might
-need to prove the corresponding states of Condition~\ref{cond:one-one},
-Condition~\ref{cond:eigenvalue}, Assumption~\ref{assu:linear},
-and Assumption~\ref{assu:times}.
-
-\yutsung{End of discussion!}
-
+\yutsung{Still not comfortable about the current statement...}
 These results provide a new insight into the Meyer-Mermin debate by

### 2017-09-22 prop_letter.tex
prop_letter.tex \section{Gleason} Reviewing...

@@
 the non-existence of certain kind of QIVPMs, we also want to understand
-what a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
-the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the state~$\proj{\ps}$.
-The way we extending a state to a QIVPM will first be generalized
-in this section, and introduce a finite-precision extension of the
-Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. The
-Born rule is essential to compute the conventional quantum probability
+what a QIVPM could be when it exists. A conventional quantum probability
+measure can be easily be constructed using the Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}
+from a unique state, and this is the only way to construct a conventional
+quantum probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+
+In Sec.~\ref{sec:Interval-Uncertainty}, the only non-trivial QIVPM~
+$\bar{\mu}_{3}$ is induced by the state~$\proj{\ps}$. The way we
+extending a state to a QIVPM will first be generalized in this section,
+and introduce a finite-precision extension of the Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
+The Born rule is essential to compute the conventional quantum probability
 because any quantum probability measure can be induced by the Born

### 2017-09-22 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

--- 2017-09-22 prop_letter.tex
@@
 the non-existence of certain kind of QIVPMs, we also want to understand
-what a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
-the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the state~$\proj{\ps}$.
-The way we extending a state to a QIVPM will first be generalized
-in this section, and introduce a finite-precision extension of the
-Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. The
-Born rule is essential to compute the conventional quantum probability
-because any quantum probability measure can be induced by the Born
-rule according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-We then provide a finite precision variant of Gleason's theorem for
-the Born QIVPMs, but there are also some general QIVPMs may not be
-induced by any quantum probability measure, i.e., no state is consistent
-with these kind of QIVPMs.
-
-When we constructed $\bar{\mu}_{3}$, we replaced the real-valued
-probability~$0$ and $\frac{1}{2}$ by $\left[0,0\right]$ and $\left[\frac{1}{2},\frac{1}{2}\right]$,
-respectively. Replacing numbers by intervals containing them can be
-generalized if we carefully pick a set of intervals and a rule to
-select the correct interval when intervals are overlapping. For example,
-consider the following collection of intervals: 
+what a QIVPM could be when it exists. A conventional quantum probability
+measure~$\mu$ can be easily be constructed using the Born rule when
+one knows the current state of the system~\citep{Born1983,peres1995quantum,544199,Jaeger2007},
+and Gleason's theorem asserts that the only state consistent with
+$\mu$ on all projectors is the one used to construct $\mu$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+Although the Born rule could incorporate the idea of finite precision
+easily, there is a QIVPM such that every state can only consistent
+with it on some of projectors. However, if we only focus on the QIVPM~$\bar{\mu}$
+induced by a state~$\rho$ according to the Born rule, called the
+Born QIVPMs, we found the states consistent with $\bar{\mu}$ will
+be closer and closer to $\rho$ while shrinking the length of intervals.
+
+The first step toward a finite precision Born rule is to find a way
+replacing the computed probability by an interval. This can be done
+by carefully picking a set of intervals and a rule to select the correct
+interval when intervals are overlapping. For example, consider the
+following collection of intervals: 
 \begin{equation}
@@
 which are overlapping intervals with length~$1/n$ except the intervals
-with length~$\left(2n\right)^{-1}$ at each end. Since these intervals~$[\ell,r]$
-are overlapping, we define the non-overlapping interior part of a
-interval, $\textrm{Int}\left([\ell,r]\right)$, as in Table~\ref{tab:I2}.
+with length~$\left(2n\right)^{-1}$ at each end. To select the correct
+interval from these overlapping intervals~$[\ell,r]$, we define
+the non-overlapping interior part of a interval, $\textrm{Int}\left([\ell,r]\right)$,
+as in Table~\ref{tab:I2}.
 \begin{table}
@@
 \end{table}
-Hence, given a real-valued probability~$x$, we could easily replace
-it with an interval~$\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$.
+Then, given a real-valued probability~$x$, we will select a interval~$\iota_{n}\left(x\right)=[\ell,r]$
+if $x\in\textrm{Int}\left([\ell,r]\right)$.
 
@@
 
-\begin{thm}[Finite-precision Extension of the Born rule~\citep{HOSTunpublished}]For
-any state $\rho$ on a three-dimensional Hilbert space, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-is a QIVPM, where $\circ$ is the function concatenation.\end{thm}\yutsung{Do
-we need to summarize the proof?}
-
-\noindent For example, when $n=2$, two states~$\mathbb{1}/3$ and
-$\rho_{0}$ can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+\begin{thm}[Finite-precision Extension of the Born rule]For any
+state $\rho$ on a three-dimensional Hilbert space, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+is a QIVPM, where $\circ$ is the function concatenation.\end{thm}
+
+\noindent Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$,
+it is easy to verify $\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)$.
+This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
+are not orthogonal on a three-dimensional Hilbert space, either one
+of them projects onto the subspace which the other one project onto,
+or their complements are orthogonal which reduced the case we discussed~\citep{HOSTunpublished}.
+Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is indeed a QIVPM.
+For example, when $n=2$, two states~$\mathbb{1}/3$ and $\rho_{0}$
+can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
 and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$

### 2017-09-22 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-While the finite-precision extension of Kochen-Specker theorem asserts
-the non-existence of certain kind of QIVPMs, we also want to understand
-what a QIVPM could be when it exists. A conventional quantum probability
-measure~$\mu$ can be easily be constructed using the Born rule when
-one knows the current state of the system~\citep{Born1983,peres1995quantum,544199,Jaeger2007},
-and Gleason's theorem asserts that the only state consistent with
-$\mu$ on all projectors is the one used to construct $\mu$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+While the finite-precision extension of the Kochen-Specker theorem
+asserts the non-existence of a certain kind of QIVPMs, we also want
+to understand what a QIVPM could be when it exists. A conventional
+quantum probability measure~$\mu$ can easily be constructed using
+the Born rule when one knows the current state of the system~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
+Gleason's theorem asserts that the only state consistent with $\mu$
+on all projectors is the one used to construct $\mu$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 Although the Born rule could incorporate the idea of finite precision
 easily, there is a QIVPM such that every state can only consistent
-with it on some of projectors. However, if we only focus on the QIVPM~$\bar{\mu}$
-induced by a state~$\rho$ according to the Born rule, called the
-Born QIVPMs, we found the states consistent with $\bar{\mu}$ will
-be closer and closer to $\rho$ while shrinking the length of intervals.
+with it on some of the projectors. However, if we only focus on the
+Born QIVPMs~$\bar{\mu}$, that is, QIVPM's induced by a state~$\rho$
+according to the Born rule, we find that if we monotonically shrink
+the length of intervals, the states consistent with $\bar{\mu}$ will
+be closer and closer to $\rho$, and vise visa.
 
 The first step toward a finite precision Born rule is to find a way
-replacing the computed probability by an interval. This can be done
-by carefully picking a set of intervals and a rule to select the correct
-interval when intervals are overlapping. For example, consider the
-following collection of intervals: 
+of replacing the computed probability by an interval. This can be
+done by carefully picking a set of intervals and a rule to select
+the correct interval when intervals are overlapping. For example,
+consider the following collection of intervals: 
 \begin{equation}
@@
 \end{equation}
-which are overlapping intervals with length~$1/n$ except the intervals
-with length~$\left(2n\right)^{-1}$ at each end. To select the correct
-interval from these overlapping intervals~$[\ell,r]$, we define
-the non-overlapping interior part of a interval, $\textrm{Int}\left([\ell,r]\right)$,
+which are overlapping intervals with length~$1/n$ except for the
+intervals with length~$\left(2n\right)^{-1}$ at each end. To select
+the correct interval from these overlapping intervals~$[\ell,r]$,
+we define the non-overlapping interior part of a interval, $\textrm{Int}\left([\ell,r]\right)$,
 as in Table~\ref{tab:I2}.
@@
 \end{table}
-Then, given a real-valued probability~$x$, we will select a interval~$\iota_{n}\left(x\right)=[\ell,r]$
+Then, given a real-valued probability~$x$, we will select an interval~$\iota_{n}\left(x\right)=[\ell,r]$
 if $x\in\textrm{Int}\left([\ell,r]\right)$.
@@
 After we have the rule to replace a real number by an interval, we
-can induce a QIVPM from a state according to the following theorem.
+can induce a QIVPM from a state according to the following theorem:
 
@@
 \noindent Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$,
-it is easy to verify $\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)$.
+it is easy to verify that
+\begin{equation}
+\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.
+\end{equation}
 This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
 when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
-are not orthogonal on a three-dimensional Hilbert space, either one
-of them projects onto the subspace which the other one project onto,
-or their complements are orthogonal which reduced the case we discussed~\citep{HOSTunpublished}.
-Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is indeed a QIVPM.
-For example, when $n=2$, two states~$\mathbb{1}/3$ and $\rho_{0}$
-can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+are not orthogonal on a three-dimensional Hilbert space, then we have
+two possibilities:
+\begin{itemize}
+\item Their complements are orthogonal reducing to the case we discussed.
+\item One of them projects onto the subspace which the other one projects
+onto.
+\end{itemize}
+\noindent Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is indeed
+a QIVPM. For example, when $n=2$, two states~$\mathbb{1}/3$ and
+$\rho_{0}$ can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
 and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$

### 2017-09-23 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 on all projectors is the one used to construct $\mu$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-Although the Born rule could incorporate the idea of finite precision
-easily, there is a QIVPM such that every state can only consistent
-with it on some of the projectors. However, if we only focus on the
-Born QIVPMs~$\bar{\mu}$, that is, QIVPM's induced by a state~$\rho$
+In another word, the set of all quantum probability measures is one-to-one
+corresponding to the set of states so that studying the set of states
+is sufficient to understand all possible phenomenon regarding to quantum
+probability. Although we can extend the Born rule to its finite precision
+version easily, there are some subtleties extending Gleason's theorem.
+In particular, there is a QIVPM such that no state can be consistent
+with it on every projector. However, if we only focus on the Born
+QIVPMs~$\bar{\mu}$, that is, QIVPM's induced by a state~$\rho$
 according to the Born rule, we find that if we monotonically shrink
 the length of intervals, the states consistent with $\bar{\mu}$ will
-be closer and closer to $\rho$, and vise visa.
+be closer and closer to $\rho$, and vise visa. As the result, although
+a finite precision version of Gleason's theorem is stated, there might
+be more rich phenomenon regarding to quantum probability when considering
+finite precision measurement, and highlight the necessity to develop
+a mathematical theory of quantum mechanics that intrinsically consistent
+with the resources available for realistic measurement.
 
@@
 the correct interval when intervals are overlapping. For example,
-consider the following collection of intervals: 
+consider the following collection of overlapping intervals: 
 \begin{equation}
@@
 we define the non-overlapping interior part of a interval, $\textrm{Int}\left([\ell,r]\right)$,
-as in Table~\ref{tab:I2}.
+as in Table~\ref{tab:I_n}.
 \begin{table}
-\caption{\label{tab:I2}Intervals in $\mathscr{I}_{n}$ and their interior
-with an concrete example for $\mathscr{I}_{2}$. Although intervals~$[\ell,r]$
-are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
+\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$ and their interior.
+Although intervals~$[\ell,r]$ are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
 are non-overlapping.}
 
-\begin{tabular}{cccc}
+\begin{tabular}{ccc}
 \toprule 
 \addlinespace
-\multicolumn{2}{c}{$\mathscr{I}_{n}$} & \multicolumn{2}{c}{$\mathscr{I}_{2}$}\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-$\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
-\textrm{for odd }k
-\end{gathered}
-$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
-\textrm{for even }k\\
-0<k<2n
-\end{gathered}
-$} & \multirow{2}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$} & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
-\cmidrule{3-4} 
-\addlinespace
- &  & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
+$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Any odd number & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+Any even number\tabularnewline
+with $0<k<2n$\tabularnewline
+\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & \multirow{1}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$}\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $\necess$\tabularnewline\addlinespace
 \bottomrule
 \end{tabular}
-
-\yutsung{Not sure what is the best way embedding the condition for
-$k$ in the table...}
+\end{table}
+ To understand these intervals and their interior part more clear,
+a special case $\mathscr{I}_{2}$ is also listed in Table~\ref{tab:I_2}.
+\begin{table}
+\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$ and their interior.
+Although intervals~$[\ell,r]$ are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
+are non-overlapping.}
+
+\begin{tabular}{ccc}
+\toprule 
+\addlinespace
+$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$3$ & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$4$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $\necess$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
 \end{table}
@@
 
-\begin{thm}[Finite-precision Extension of the Born rule]For any
-state $\rho$ on a three-dimensional Hilbert space, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+\begin{thm}[Finite-precision Extension of the Born rule]\label{thm:Finite-precision-Born}For
+any state $\rho$ on a three-dimensional Hilbert space, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
 is a QIVPM, where $\circ$ is the function concatenation.\end{thm}
@@
 \begin{equation}
-\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.
+\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
 \end{equation}
@@
 \begin{itemize}
-\item Their complements are orthogonal reducing to the case we discussed.
+\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
+on their complements.
 \item One of them projects onto the subspace which the other one projects
@@
 \end{itemize}
-\noindent Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is indeed
-a QIVPM. For example, when $n=2$, two states~$\mathbb{1}/3$ and
-$\rho_{0}$ can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
-and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
-and $\rho_{0}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$.
-The interval-valued probability of the induced QIVPMs, $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$
+\noindent No matter which case, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+can be deduced easily. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+is indeed a QIVPM. As a concrete example of Thm.~\ref{thm:Finite-precision-Born},
+when $n=2$, two states~$\rho_{1}$ and $\rho_{0}$ can induce two
+QIVPMs~$\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$,
+where $\rho_{1}=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$ and $\rho_{0}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$.
+The interval-valued probability of the induced QIVPMs, $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$
 and $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$,
@@
 \begin{table}
-\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
-and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$ based on $\mu_{\mathbb{1}/3}^{\mathrm{B}}$
+\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$
+and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$ based on $\mu_{\rho_{1}}^{\mathrm{B}}$
 and $\mu_{\rho_{0}}^{\mathrm{B}}$ on $\events_{C}$.}
@@
 \addlinespace
-$P$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
+$P$ & $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
 \midrule
@@
 then $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
-For example, $\mathbb{1}/3$ and $\rho_{0}$ are both totally mixed
-states. Since $\left\Vert \frac{\mathbb{1}}{3}-\rho_{0}\right\Vert \le\frac{1}{24}$,
-we should have $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$
-and $\mathbb{1}/3\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
+For example, $\rho_{1}$ and $\rho_{0}$ are both totally mixed states.
+Since $\left\Vert \rho_{1}-\rho_{0}\right\Vert \le\frac{1}{24}$,
+we should have $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
+and $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
 and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
 In general, as $n$ goes to infinity, only the states very close to
-$\rho$ is guarantied belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$,
+$\rho$ is guarantied belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
 and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$

### 2017-09-23 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 for any projector $P$ in the minimal subspace of events containing
-$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, are computed
+$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, is computed
 straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
@@
 with its corresponding $\iota_{\infty}\left(x\right)=[x,x]$, we can
-formulate Gleason's theorem in our framework.
+formulate Gleason's theorem in our framework as follow.
 
@@
 
-Our framework allows us to generalize the above theorem to the Born
-QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$: The collection of
-states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ get closer
-and closer to $\rho$ as the intervals get narrower and narrower,
-eventually collapsing to $\rho$ when the intervals become infinitely
-precise real numbers. To state this result, we introduce a few technical
-notions. We call a state~$\rho$ a \emph{totally mixed state} if
-$0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
+Our framework allows us to generalize the above theorem to Born QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
+The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+gets closer and closer to $\rho$ as the intervals get narrower and
+narrower, eventually collapsing to $\rho$ when the intervals become
+infinitely precise real numbers covering the real line. To state this
+result, we introduce a few technical notions. We call a state~$\rho$
+a \emph{totally mixed state} if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
+for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
 We also define a notion of distance between two states~$\rho$ and
@@
 
+In another word, if a state~$\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
+its distance with $\rho$, $\left\Vert \rho-\rho'\right\Vert $, must
+be bounded by $1/n$. Reversely, if the distance between $\rho$ and
+$\rho'$ is bounded by $\frac{1}{12n}$, then $\rho'$ is consistent
+with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
+
 \begin{thm}[Finite-precision Extension of Gleason's theorem for the
@@
 
-\noindent In another word, if a state~$\rho'$ is consistent with
-$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, its distance with $\rho$,
-$\left\Vert \rho-\rho'\right\Vert $, must be bounded by $1/n$. Reversely,
-if the distance between $\rho$ and $\rho'$ is bounded by $\frac{1}{12n}$,
-then $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
-For example, $\rho_{1}$ and $\rho_{0}$ are both totally mixed states.
-Since $\left\Vert \rho_{1}-\rho_{0}\right\Vert \le\frac{1}{24}$,
+\noindent For example, $\rho_{1}$ and $\rho_{0}$ are both totally
+mixed states. Since $\left\Vert \rho_{1}-\rho_{0}\right\Vert \le\frac{1}{24}$,
 we should have $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
@@
 and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
-In general, as $n$ goes to infinity, only the states very close to
-$\rho$ is guarantied belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
+In general, as $n$ goes to infinity, only the state very close to
+$\rho$ are guaranteed to belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
 and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
@@
 If a QIVPM is not \emph{a priori} known to be induced by a state,
-there are some QIVPMs which cannot be consistent with any state.
+there are some QIVPMs that cannot be consistent with any state.
 
@@
 \end{subequations} It is straightforward to verify that $\bar{\mu}$
-is a QIVPM. Then we will prove $\coreBorn\left(\bar{\mu},\events\right)$
+is a QIVPM. Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$
 is an empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
@@
 \begin{equation}
-\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0
+\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
 \end{equation}
 which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all $j$. However, the last equation never holds. Thus, there
-is no state consistent with the QIVPM on all projectors~$P\in\events$,
-so Gleason's theorem cannot be extended to general QIVPMs because
-of this example.
-
-Despite the non-extensible of Gleason's theorem to general QIVPMs,
+for all $j$. The last equation never holds proving the theorem. Thus,
+there is no state consistent with the QIVPM on all projectors~$P\in\events$,
+so Gleason's theorem cannot be extended to general QIVPMs.
+
+Despite the non-extensibility of Gleason's theorem to general QIVPMs,
 when we restrict $\bar{\mu}$ on any commuting subspace of events~$\events_{C}$,
@@
 sense, Thm.~\ref{thm:Non-extensible-of-Gleason's} is a completely
-new phenomena when we generalize both classical IVPMs and quantum
+new phenomenon when we generalize both classical IVPMs and quantum
 probability measures to QIVPMs.

### 2017-09-23 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 $\Hilb$, it is straightforward to check that
-$\bar{\mu}\left(P\right)=\left[n/3,n/3\right]$ is a valid
+$\bar{\mu}\left(P\right)=\left[\frac{n}{3},\frac{n}{3}\right]$ is a valid
 $\frac{1}{3}$-deterministic QIVPM. In other words, when the
@@
 the length of intervals, the states consistent with $\bar{\mu}$ will
-be closer and closer to $\rho$, and vise visa. As the result, although
-a finite precision version of Gleason's theorem is stated, there might
-be more rich phenomenon regarding to quantum probability when considering
-finite precision measurement, and highlight the necessity to develop
-a mathematical theory of quantum mechanics that intrinsically consistent
-with the resources available for realistic measurement.
+be closer and closer to $\rho$, and vise visa. In another word, although
+we can prove a finite precision version of Gleason's theorem, there
+might be more rich phenomenon regarding to quantum probability when
+considering finite precision measurement. Our result also highlight
+the necessity to develop a mathematical theory of quantum mechanics
+that intrinsically consistent with the resources available for realistic
+measurement.
 
@@
 which are overlapping intervals with length~$1/n$ except for the
-intervals with length~$\left(2n\right)^{-1}$ at each end. To select
-the correct interval from these overlapping intervals~$[\ell,r]$,
-we define the non-overlapping interior part of a interval, $\textrm{Int}\left([\ell,r]\right)$,
-as in Table~\ref{tab:I_n}.
+intervals with length~$\left(2n\right)^{-1}$ at each end. As in
+Table~\ref{tab:I_n}, To select the correct interval from these overlapping
+intervals~$[\ell,r]$, we define the non-overlapping interior part
+of a interval, $\textrm{Int}\left([\ell,r]\right)$.
 \begin{table}
@@
 Although intervals~$[\ell,r]$ are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
-are non-overlapping.}
+are non-overlapping. See Table~\ref{tab:I_2} for a concrete example
+when $n=2$.}
 
@@
 \end{table}
- To understand these intervals and their interior part more clear,
-a special case $\mathscr{I}_{2}$ is also listed in Table~\ref{tab:I_2}.
+ Table~\ref{tab:I_2} lists a special case $\mathscr{I}_{2}$ to
+illustrate these intervals and their interior parts more clearly.
 \begin{table}
@@
 
-\noindent Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$,
-it is easy to verify that
+\noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
+Eqs.(\ref{eq:QIVPM-constraints}), the condition really need to be
+checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
+is easy to verify that
 \begin{equation}
@@
 when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
-are not orthogonal on a three-dimensional Hilbert space, then we have
-two possibilities:
+are not orthogonal on a three-dimensional Hilbert space, we have two
+possibilities:
 \begin{itemize}
@@
 can be deduced easily. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-is indeed a QIVPM. As a concrete example of Thm.~\ref{thm:Finite-precision-Born},
-when $n=2$, two states~$\rho_{1}$ and $\rho_{0}$ can induce two
-QIVPMs~$\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$,
-where $\rho_{1}=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$ and $\rho_{0}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$.
-The interval-valued probability of the induced QIVPMs, $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$
-and $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$,
-for any projector $P$ in the minimal subspace of events containing
-$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, is computed
-straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
+is indeed a QIVPM.
+
+As a concrete example of Thm.~\ref{thm:Finite-precision-Born}, when
+$n=2$, two states~$\rho_{0}=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
+and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$
+can induce two QIVPMs~$\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$. Given any projector
+$P$ in the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
+and $\proj{2}$, $\events_{C}$, the interval-valued probability of
+the induced QIVPMs, $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
+and $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$,
+is computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
 \begin{table}
-\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$
-and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$ based on $\mu_{\rho_{1}}^{\mathrm{B}}$
-and $\mu_{\rho_{0}}^{\mathrm{B}}$ on $\events_{C}$.}
+\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ based on $\mu_{\rho_{0}}^{\mathrm{B}}$
+and $\mu_{\rho_{1}}^{\mathrm{B}}$ on $\events_{C}$.}
 
@@
 \addlinespace
-$P$ & $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
+$P$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
 \midrule
@@
 In the limiting case when the intervals are infinitely precise, i.e.,
-$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$
-with its corresponding $\iota_{\infty}\left(x\right)=[x,x]$, we can
-formulate Gleason's theorem in our framework as follow.
+$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+we can formulate Gleason's theorem in our framework as follow.
 
@@
 a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
-the states consistent with it on every project, $\coreBorn\left(\bar{\mu},\events\right)$
+the states consistent with it on every project, $\coreBorn\left(\bar{\mu},\events\right)$,
 has a unique element. \end{thm}
@@
 
-\noindent For example, $\rho_{1}$ and $\rho_{0}$ are both totally
-mixed states. Since $\left\Vert \rho_{1}-\rho_{0}\right\Vert \le\frac{1}{24}$,
-we should have $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
-and $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
+\noindent For example, $\rho_{0}$ and $\rho_{1}$ are both totally
+mixed states. Since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$,
+we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
+and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
 and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
 In general, as $n$ goes to infinity, only the state very close to
-$\rho$ are guaranteed to belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
+$\rho$ are guaranteed to belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
 and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$

### 2017-09-24 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 version easily, there are some subtleties extending Gleason's theorem.
-In particular, there is a QIVPM such that no state can be consistent
-with it on every projector. However, if we only focus on the Born
-QIVPMs~$\bar{\mu}$, that is, QIVPM's induced by a state~$\rho$
-according to the Born rule, we find that if we monotonically shrink
-the length of intervals, the states consistent with $\bar{\mu}$ will
-be closer and closer to $\rho$, and vise visa. In another word, although
-we can prove a finite precision version of Gleason's theorem, there
-might be more rich phenomenon regarding to quantum probability when
-considering finite precision measurement. Our result also highlight
-the necessity to develop a mathematical theory of quantum mechanics
-that intrinsically consistent with the resources available for realistic
-measurement.
+If we only focus on the Born QIVPMs~$\bar{\mu}$, that is, QIVPM's
+induced by a state~$\rho$ according to the Born rule, we find that
+if we monotonically shrink the length of intervals, the states consistent
+with $\bar{\mu}$ will be closer and closer to $\rho$, and vise visa.
+However, there is a QIVPM such that no state can be consistent with
+it on every projector. In another word, although the Born rule and
+Gleason's theorem can be extended to consider finite precision measurement,
+the problem of finite precision measurement itself is not limited
+in just applying error analysis in experimental results, but it highlight
+some new phenomenon regarding to the foundation of quantum machines,
+and it is necessary to embedding the idea of the resources available
+for realistic measurement into the formulation of quantum theory.
 
@@
 intervals with length~$\left(2n\right)^{-1}$ at each end. As in
-Table~\ref{tab:I_n}, To select the correct interval from these overlapping
+Table~\ref{tab:I_n}, to select the correct interval from these overlapping
 intervals~$[\ell,r]$, we define the non-overlapping interior part
@@
 \noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
-Eqs.(\ref{eq:QIVPM-constraints}), the condition really need to be
-checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+Eqs.~(\ref{eq:QIVPM-constraints}), the condition really need to
+be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
 Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
@@
 on their complements.
-\item One of them projects onto the subspace which the other one projects
+\item One of them projects onto a subspace which the other one projects
 onto.
@@
 As a concrete example of Thm.~\ref{thm:Finite-precision-Born}, when
-$n=2$, two states~$\rho_{0}=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
+$n=2$, two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
 and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$
@@
 and $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$,
-is computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
+can be computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
 \begin{table}
@@
 a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
-the states consistent with it on every project, $\coreBorn\left(\bar{\mu},\events\right)$,
+the states consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
 has a unique element. \end{thm}
@@
 for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
-We also define a notion of distance between two states~$\rho$ and
-$\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
+For example, $\rho_{0}$ and $\rho_{1}$ are both totally mixed states,
+but any pure state is not totally mixed. We also define a notion of
+distance between two states~$\rho$ and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
 and the set of all states whose distance with $\rho$ is bounded by
 $\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.
-
-In another word, if a state~$\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
-its distance with $\rho$, $\left\Vert \rho-\rho'\right\Vert $, must
-be bounded by $1/n$. Reversely, if the distance between $\rho$ and
-$\rho'$ is bounded by $\frac{1}{12n}$, then $\rho'$ is consistent
-with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
+For example, since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$,
+we have $\rho_{0}\in B_{\epsilon}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{\epsilon}\left(\rho_{0}\right)$.
+
+After we have enough definitions, we can replace the QIVPM~$\bar{\mu}$
+in Thm.~\ref{cor:Gleason's} by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
+and estimate the states consistent with it by the following theorem.
 
@@
 
-\noindent For example, $\rho_{0}$ and $\rho_{1}$ are both totally
-mixed states. Since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$,
-we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
+\noindent In another word, if a state~$\rho'$ is consistent with
+$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, its distance with $\rho$,
+$\left\Vert \rho-\rho'\right\Vert $, must be bounded by $1/n$. Reversely,
+if the distance between $\rho$ and $\rho'$ is bounded by $\frac{1}{12n}$,
+then $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
+For example, we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
 and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,

### 2017-09-24 prop_iop.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \begin{itemize}
-\item Let $\delta=\min_{x\in\left(0,1\right)}\left\{ \max\iota\left(x\right)-x,x-\min\iota\left(x\right)\right\} $.
-In another word, if $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
+\item If $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
 \item $\left\Vert \rho-\rho'\right\Vert \le\delta/d$.
@@
 the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
-$1/n$, and $\min_{x\in\left(0,1\right)}\left\{ \max\widehat{\iota}_{n}\left(x\right)-x,x-\min\widehat{\iota}_{n}\left(x\right)\right\} =1/\left(4n\right)$.
-Therefore, for any totally mixed state\nb$\rho$ on a $d$-dimensional
-Hilbert space, we have
+$1/n$, and If $\left|x-y\right|\le\left(4n\right)^{-1}$, we must
+have $y\in\widehat{\iota}_{n}\left(x\right)$. Therefore, for any
+totally mixed state\nb$\rho$ on a $d$-dimensional Hilbert space,
+we have
 \begin{itemize}

### 2017-09-24 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \begin{table}
-\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$ and their interior.
-Although intervals~$[\ell,r]$ are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
-are non-overlapping. See Table~\ref{tab:I_2} for a concrete example
-when $n=2$.}
-
-\begin{tabular}{ccc}
+\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their interior, and
+their length, where $2\mid k$ means $k$ is even, and $2\nmid k$
+means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
+their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.
+See Table~\ref{tab:I_2} for a concrete example when $n=2$.}
+
+\begin{tabular}{cccc}
 \toprule 
 \addlinespace
-$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
- & $\imposs$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-Any odd number & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
+$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $r-\ell$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $\imposs$ & $0$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$ & $\tfrac{1}{2n}$\tabularnewline\addlinespace
 \midrule 
@@
 \begin{tabular}{c}
-Any even number\tabularnewline
-with $0<k<2n$\tabularnewline
-\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & \multirow{1}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$}\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
- & $\necess$ & $\necess$\tabularnewline\addlinespace
+$0<k<2n$\tabularnewline
+and $2\nmid k$\tabularnewline
+\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$ & $\tfrac{1}{n}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+$0<k<2n$\tabularnewline
+and $2\mid k$\tabularnewline
+\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & \multirow{1}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$} & $\tfrac{1}{n}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$ & $\tfrac{1}{2n}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $\necess$ & $0$\tabularnewline\addlinespace
 \bottomrule
@@
 \begin{table}
-\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$ and their interior.
-Although intervals~$[\ell,r]$ are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
-are non-overlapping.}
-
-\begin{tabular}{ccc}
+\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$, their interior, and
+their length. Although intervals~$[\ell,r]$ are overlapping, their
+interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
+
+\begin{tabular}{cccc}
 \toprule 
 \addlinespace
-$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
- & $\imposs$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$3$ & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$4$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
- & $\necess$ & $\necess$\tabularnewline\addlinespace
+$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $r-\ell$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $\imposs$ & $0$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$ & $\tfrac{1}{4}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$ & $\tfrac{1}{2}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$ & $\tfrac{1}{2}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$3$ & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$ & $\tfrac{1}{2}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$4$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$ & $\tfrac{1}{4}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $\necess$ & $0$\tabularnewline\addlinespace
 \bottomrule
@@
 on their complements.
-\item One of them projects onto a subspace which the other one projects
+\item One of them projects onto a subspace of what the other one projects
 onto.
@@
 \noindent No matter which case, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-can be deduced easily. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+can be deduced easily~\citep{HOSTunpublished}. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
 is indeed a QIVPM.
@@
 $\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.
-For example, since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$,
-we have $\rho_{0}\in B_{\epsilon}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{\epsilon}\left(\rho_{0}\right)$.
-
-After we have enough definitions, we can replace the QIVPM~$\bar{\mu}$
+For example, since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$~\citep{HOSTunpublished},
+we have $\rho_{0}\in B_{1/24}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{1/24}\left(\rho_{0}\right)$.
+
+Since we have enough definitions, we can replace the QIVPM~$\bar{\mu}$
 in Thm.~\ref{cor:Gleason's} by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
@@
 \begin{thm}[Finite-precision Extension of Gleason's theorem for the
-Born QIVPMs~\citep{HOSTunpublished}]In a Hilbert space $\Hilb$
-of dimension $3$, given any totally mixed state~$\rho$, 
+Born QIVPMs]In a Hilbert space $\Hilb$ of dimension $3$, given
+any totally mixed state~$\rho$, 
 \begin{equation}
@@
 \end{equation}
-\end{thm}\yutsung{Do we need to summarize the proof?}
+\end{thm}
 
@@
 $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, its distance with $\rho$,
-$\left\Vert \rho-\rho'\right\Vert $, must be bounded by $1/n$. Reversely,
-if the distance between $\rho$ and $\rho'$ is bounded by $\frac{1}{12n}$,
-then $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
+$\left\Vert \rho-\rho'\right\Vert $, must be bounded by $1/n$ which
+is the maximal length of the intervals in $\mathscr{I}_{n}$~\citep{HOSTunpublished}.
+Conversely, if the distance between $\rho$ and $\rho'$ is bounded
+by $\frac{1}{12n}$, their Born quantum probability on any projector~$P$
+is $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|\le\frac{1}{4n}$~\citep{HOSTunpublished}.
+Moreover, the interiors of the intervals in $\mathscr{I}_{n}$ shrinks
+$\frac{0.5}{2n}$ from the both ends, excepts $\imposs$, $\left[0,\tfrac{1}{2n}\right]$,
+$\left[\tfrac{2n-1}{2n},1\right]$, and $\necess$. Together with
+the fact that $0<\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)<1$ and
+$0<\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)<1$, $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$
+and $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ are both in the same
+intervals, and $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
 For example, we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$

### 2017-09-25 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \begin{table}
-\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their interior, and
-their length, where $2\mid k$ means $k$ is even, and $2\nmid k$
+\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
+their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
 means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
@@
 \addlinespace
-$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $r-\ell$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
- & $\imposs$ & $\imposs$ & $0$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$ & $\tfrac{1}{2n}$\tabularnewline\addlinespace
+$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
 \midrule 
@@
 and $2\nmid k$\tabularnewline
-\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$ & $\tfrac{1}{n}$\tabularnewline\addlinespace
+\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
 \midrule 
@@
 and $2\mid k$\tabularnewline
-\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & \multirow{1}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$} & $\tfrac{1}{n}$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$ & $\tfrac{1}{2n}$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
- & $\necess$ & $\necess$ & $0$\tabularnewline\addlinespace
+\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
 \bottomrule
@@
 \begin{table}
-\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$, their interior, and
-their length. Although intervals~$[\ell,r]$ are overlapping, their
-interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
+\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$, , their lengths,
+and their interiors. Although intervals~$[\ell,r]$ are overlapping,
+their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
 
@@
 \addlinespace
-$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $r-\ell$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
- & $\imposs$ & $\imposs$ & $0$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$ & $\tfrac{1}{4}$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$ & $\tfrac{1}{2}$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$ & $\tfrac{1}{2}$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$3$ & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$ & $\tfrac{1}{2}$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$4$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$ & $\tfrac{1}{4}$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
- & $\necess$ & $\necess$ & $0$\tabularnewline\addlinespace
+$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\tfrac{1}{4}$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\tfrac{1}{2}$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$3$ & $\left[\tfrac{1}{2},1\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$4$ & $\left[\tfrac{1}{4},1\right]$ & $\tfrac{1}{4}$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
 \bottomrule
@@
 \end{table}
- Then, given a real-valued probability~$x$, we will select an interval~$\iota_{n}\left(x\right)=[\ell,r]$
+ Then, given a real-valued probability~$x$, we will select the interval~$\iota_{n}\left(x\right)=[\ell,r]$
 if $x\in\textrm{Int}\left([\ell,r]\right)$.
@@
 \begin{thm}[Finite-precision Extension of Gleason's theorem for the
-Born QIVPMs]In a Hilbert space $\Hilb$ of dimension $3$, given
-any totally mixed state~$\rho$, 
+Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
+$\Hilb$ of dimension $3$, given any totally mixed state~$\rho$,
 \begin{equation}
@@
 \noindent In another word, if a state~$\rho'$ is consistent with
-$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, its distance with $\rho$,
-$\left\Vert \rho-\rho'\right\Vert $, must be bounded by $1/n$ which
-is the maximal length of the intervals in $\mathscr{I}_{n}$~\citep{HOSTunpublished}.
-Conversely, if the distance between $\rho$ and $\rho'$ is bounded
-by $\frac{1}{12n}$, their Born quantum probability on any projector~$P$
-is $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|\le\frac{1}{4n}$~\citep{HOSTunpublished}.
-Moreover, the interiors of the intervals in $\mathscr{I}_{n}$ shrinks
-$\frac{0.5}{2n}$ from the both ends, excepts $\imposs$, $\left[0,\tfrac{1}{2n}\right]$,
-$\left[\tfrac{2n-1}{2n},1\right]$, and $\necess$. Together with
-the fact that $0<\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)<1$ and
-$0<\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)<1$, $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$
+$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, the difference between the
+Born quantum probabilities on any projector~$P$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|$,
+must be bounded by $1/n$ which is the maximal length of the intervals
+in $\mathscr{I}_{n}$. So does the distance between $\rho$ and $\rho'$,
+$\left\Vert \rho-\rho'\right\Vert $. Conversely, if the distance
+between $\rho$ and $\rho'$ is bounded by $\frac{1}{12n}$, so does
+the difference between their Born quantum probabilities on any 1-dimensioal
+projector~$\proj{\psi}$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\le\frac{1}{12n}$.
+Since the dimension of the Hilbert space is $3$, the same difference
+on any projector~$P$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|$,
+is bounded by $\frac{1}{4n}$. Moreover, the interiors of the intervals
+in $\mathscr{I}_{n}$ shrinks $\frac{0.5}{2n}$ from the both ends,
+excepts $\imposs$, $\left[0,\tfrac{1}{2n}\right]$, $\left[\tfrac{2n-1}{2n},1\right]$,
+and $\necess$. Together with the fact that $0<\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)<1$
+and $0<\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)<1$, $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$
 and $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ are both in the same
 intervals, and $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
-For example, we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
+
+As a concrete example of Thm.~\ref{thm:Finite-precision-Gleason},
+we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
 and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
@@
 
-\noindent Given a three-dimensional Hilbert space $\Hilb$ with an
-orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let
-$\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
-$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and \begin{subequations}
-\begin{eqnarray}
- &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
- & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\,,
-\end{aligned}
-\\
- &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
- & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\,,
-\end{aligned}
-\\
- &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
-\end{eqnarray}
-\end{subequations} It is straightforward to verify that $\bar{\mu}$
-is a QIVPM. Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$
-is an empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+\noindent Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
+let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
+$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
+The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
+in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly.
+\begin{table}
+\caption{\label{tab:non-Born-QIVPM}Define a non-Born QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+on the three-dimensional Hilbert space.}
+
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, $\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+All other projectors & $\unknown$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
+empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
 where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
@@
 
-Despite the non-extensibility of Gleason's theorem to general QIVPMs,
-when we restrict $\bar{\mu}$ on any commuting subspace of events~$\events_{C}$,
-$\bar{\mu}$ becomes classical, and Thm.~\ref{thm:Shapley} guarantees
-$\coreBorn\left(\bar{\mu},\events_{C}\right)$ is nonempty. In this
-sense, Thm.~\ref{thm:Non-extensible-of-Gleason's} is a completely
-new phenomenon when we generalize both classical IVPMs and quantum
-probability measures to QIVPMs.
+Notice that if we restrict $\bar{\mu}$ on the commuting subspace
+of events~$\events_{C}$, the state~$\frac{1}{2}\cdot\proj{1}+\frac{1}{2}\cdot\proj{2}\in\coreBorn\left(\bar{\mu},\events_{C}\right)$
+so that $\coreBorn\left(\bar{\mu},\events_{C}\right)$ is non-empty.
+In general, for any commuting subspace of events~$\events_{C}'$,
+$\coreBorn\left(\bar{\mu},\events_{C}'\right)$ is non-empty according
+to the classical Thm.~\ref{thm:Shapley}. The difference between
+classical and quantum highlights the following fact: Although classically
+we could build a theory and deal the finite-precision measurement
+in error analysis, it is necessary to embed the finite-precision measurement
+into the foundation of quantum theory.
 

### 2017-09-26 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \end{itemize}
-\noindent No matter which case, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-can be deduced easily~\citep{HOSTunpublished}. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
+\noindent No matter which case Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+can be deduced easily. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
 is indeed a QIVPM.
@@
 $\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.
-For example, since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$~\citep{HOSTunpublished},
-we have $\rho_{0}\in B_{1/24}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{1/24}\left(\rho_{0}\right)$.
-
-Since we have enough definitions, we can replace the QIVPM~$\bar{\mu}$
+By expending the definitions, we have $\rho'\in B_{\epsilon}\left(\rho\right)$
+if and only if $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\le\epsilon$
+for any pure state~$\ket{\psi}$. This fact will be used to prove
+the following theorem that is obtained by replacing the QIVPM~$\bar{\mu}$
 in Thm.~\ref{cor:Gleason's} by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
-and estimate the states consistent with it by the following theorem.
+and estimate the states consistent with it.
 
@@
 
-\noindent In another word, if a state~$\rho'$ is consistent with
+\noindent On the one hand, if a state~$\rho'$ is consistent with
 $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, the difference between the
-Born quantum probabilities on any projector~$P$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|$,
+Born quantum probabilities on any 1-dimensioal projector~$\proj{\psi}$,
+$\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
 must be bounded by $1/n$ which is the maximal length of the intervals
-in $\mathscr{I}_{n}$. So does the distance between $\rho$ and $\rho'$,
-$\left\Vert \rho-\rho'\right\Vert $. Conversely, if the distance
-between $\rho$ and $\rho'$ is bounded by $\frac{1}{12n}$, so does
-the difference between their Born quantum probabilities on any 1-dimensioal
-projector~$\proj{\psi}$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\le\frac{1}{12n}$.
-Since the dimension of the Hilbert space is $3$, the same difference
-on any projector~$P$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|$,
+in $\mathscr{I}_{n}$, i.e., $\rho'\in B_{1/n}\left(\rho\right)$.
+On the other hand, if $\rho'\in B_{\frac{1}{12n}}\left(\rho\right)$,
+we have $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\le\frac{1}{12n}$
+for any pure state~$\ket{\psi}$. Since the dimension of the Hilbert
+space is $3$, the same difference on any projector~$P$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|$,
 is bounded by $\frac{1}{4n}$. Moreover, the interiors of the intervals
@@
 and $0<\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)<1$, $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$
-and $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ are both in the same
-intervals, and $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
+and $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ must both be in the
+same intervals, and $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
 
 As a concrete example of Thm.~\ref{thm:Finite-precision-Gleason},
-we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
+since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$~\citep{HOSTunpublished},
+we have $\rho_{0}\in B_{1/24}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{1/24}\left(\rho_{0}\right)$
+that should imply $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
 and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,

### 2017-09-26 prop_iop.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-Previously, we proved that if $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
-then $\rho'$ is close to $\rho$. Conversely, if $\rho'$ is close
-to $\rho$, $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$.
-Before we introduce the lemma, we start the following definition.
-
-\begin{definition}A mixed state\nb$\rho$ is called totally mixed
-if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.\end{definition}
-
-For example, any pure state is not totally mixed, and $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
-is a totally mixed over a three-dimensional Hilbert space.
-
-\begin{lemma}Given a $d$-dimensional Hilbert space with the set
-of all projectors\nb$\events$, and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
-For two mixed state\nb$\rho$ and $\rho'$, if the following conditions
-holds.
-\begin{itemize}
-\item If $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
-\item $\left\Vert \rho-\rho'\right\Vert \le\delta/d$.
-\item $\rho$ is a totally mixed.
-\end{itemize}
-Then, $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.\end{lemma}
-
-\begin{proof}Since
-\begin{equation}
-\delta/d\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
-\end{equation}
-we have
-\begin{equation}
-\delta/d\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
-\end{equation}
-for all normalized pure state\nb$\ket{\psi}$.
-
-When $P\in\left\{ \mathbb{0},\mathbb{1}\right\} $, it is obvious
-$\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.
-
-When $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
-there exists an orthonormal set $\left\{ \ket{i}\right\} _{i=0}^{d'-1}$
-such that $P=\sum_{i=0}^{d'-1}\proj{i}$. By applying equation~(\ref{eq:Born_rule_difference}),
-\begin{equation}
-\left|\mu_{\rho'}^{\mathrm{B}}\left(P\right)-\mu_{\rho}^{\mathrm{B}}\left(P\right)\right|\le\sum_{i=0}^{d'-1}\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{i}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)\right|\le\delta\,.
-\end{equation}
-
-Since $P$ is neither $\mathbb{0}$ nor $\mathbb{1}$, $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\left(0,1\right)$.
-Hence, we have $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.\end{proof}
-
-The previous two lemmas can be applied on example~\ref{ex:equilateral},
+The previous lemma can be applied on example~\ref{ex:equilateral},
 we can estimate the states consistent with a QIVPM more tightly.
@@
 the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
-$1/n$, and If $\left|x-y\right|\le\left(4n\right)^{-1}$, we must
-have $y\in\widehat{\iota}_{n}\left(x\right)$. Therefore, for any
-totally mixed state\nb$\rho$ on a $d$-dimensional Hilbert space,
-we have
-\begin{itemize}
-\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, then
-$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
-\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
-\end{itemize}
-\end{example}
+$1/n$. Therefore, for any totally mixed state\nb$\rho$ on a $d$-dimensional
+Hilbert space, if $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+then $\left\Vert \rho-\rho'\right\Vert \le1/n$.\end{example}
+
+Previously, we proved that if $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
+then $\rho'$ is close to $\rho$. However, if $\rho'$ is close to
+$\rho$, there is no way to guarantee $\rho'$ is consistent with
+$\iota\circ\mu_{\rho}^{\mathrm{B}}$ because no matter how close between
+two real numbers~$x$ and $y$, we can never guarantee $y\in\iota\left(x\right)$.
 

### 2017-09-26 prop_letter.tex
prop_letter.tex \lineskiplimit=1pt Added...
prop_letter.tex \section{Gleason} Updating...

@@
 \newcommand{\rmi}{\mathrm{i}}
+\lineskiplimit=1pt
 
@@
 infinitely precise real numbers covering the real line. To state this
-result, we introduce a few technical notions. We call a state~$\rho$
-a \emph{totally mixed state} if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
-for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
-For example, $\rho_{0}$ and $\rho_{1}$ are both totally mixed states,
-but any pure state is not totally mixed. We also define a notion of
-distance between two states~$\rho$ and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
-and the set of all states whose distance with $\rho$ is bounded by
-$\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.
-By expending the definitions, we have $\rho'\in B_{\epsilon}\left(\rho\right)$
-if and only if $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\le\epsilon$
-for any pure state~$\ket{\psi}$. This fact will be used to prove
-the following theorem that is obtained by replacing the QIVPM~$\bar{\mu}$
+result, we need to introduce a notion of distance between two states~$\rho$
+and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
+The following theorem that is obtained by replacing the QIVPM~$\bar{\mu}$
 in Thm.~\ref{cor:Gleason's} by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
@@
 Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
-$\Hilb$ of dimension $3$, given any totally mixed state~$\rho$,
-\begin{equation}
-B_{\frac{1}{12n}}\left(\rho\right)\subseteq\coreBorn\left(\iota_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)\subseteq B_{1/n}\left(\rho\right)\,.
-\end{equation}
-\end{thm}
-
-\noindent On the one hand, if a state~$\rho'$ is consistent with
-$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, the difference between the
-Born quantum probabilities on any 1-dimensioal projector~$\proj{\psi}$,
-$\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
-must be bounded by $1/n$ which is the maximal length of the intervals
-in $\mathscr{I}_{n}$, i.e., $\rho'\in B_{1/n}\left(\rho\right)$.
-On the other hand, if $\rho'\in B_{\frac{1}{12n}}\left(\rho\right)$,
-we have $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\le\frac{1}{12n}$
-for any pure state~$\ket{\psi}$. Since the dimension of the Hilbert
-space is $3$, the same difference on any projector~$P$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|$,
-is bounded by $\frac{1}{4n}$. Moreover, the interiors of the intervals
-in $\mathscr{I}_{n}$ shrinks $\frac{0.5}{2n}$ from the both ends,
-excepts $\imposs$, $\left[0,\tfrac{1}{2n}\right]$, $\left[\tfrac{2n-1}{2n},1\right]$,
-and $\necess$. Together with the fact that $0<\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)<1$
-and $0<\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)<1$, $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$
-and $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ must both be in the
-same intervals, and $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
-
-As a concrete example of Thm.~\ref{thm:Finite-precision-Gleason},
-since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$~\citep{HOSTunpublished},
-we have $\rho_{0}\in B_{1/24}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{1/24}\left(\rho_{0}\right)$
-that should imply $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
-and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
-and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
-In general, as $n$ goes to infinity, only the state very close to
-$\rho$ are guaranteed to belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
-and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-will become closer and closer to $\rho$.
+$\Hilb$ of dimension $3$, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\iota_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
+
+\noindent If a state~$\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
+the difference between the Born quantum probabilities on any 1-dimensioal
+projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
+must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
+by definition. As a concrete example of Thm.~\ref{thm:Finite-precision-Gleason},
+since $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
+and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
+which is easy to see on the commuting subspace of event~$\events_{C}$
+according to Table~\ref{tab:Compute-the-QIVPM}, we have $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$,
+and this is indeed the case because $\left\Vert \rho_{0}-\rho_{1}\right\Vert =\frac{1}{24}$~\citep{HOSTunpublished}.
 

### 2017-09-27 prop_iop.tex
prop_iop.tex \subsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

@@
 \begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
-and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+and an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
-For two mixed state\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+For two mixed states\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
 then $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{lemma}
@@
 
-The previous lemma can be applied on example~\ref{ex:equilateral},
+By applying the previous lemma on example~\ref{ex:equilateral},
 we can estimate the states consistent with a QIVPM more tightly.
@@
 $\iota\circ\mu_{\rho}^{\mathrm{B}}$ because no matter how close between
-two real numbers~$x$ and $y$, we can never guarantee $y\in\iota\left(x\right)$.
+two real numbers~$x$ and $y$, we can never guarantee $y\in\iota\left(x\right)$
+as in the following example.
+
+\begin{example}Given an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
+consider let $x_{0}=\sup\set{x\in\left[0,1\right]}{\iota\left(x\right)=\left[0,0\right]}$.
+Since $\iota\left(1\right)=\left[1,1\right]$, $x_{0}<1$. For any
+$\varepsilon>0$, $\left|\left(x+\frac{\varepsilon}{2}\right)-x\right|=\frac{\varepsilon}{2}<\varepsilon$,
+and $x+\frac{\varepsilon}{2}\ge\frac{\varepsilon}{2}>0$ implies $x+\frac{\varepsilon}{2}\notin\left[0,0\right]=\iota\left(x\right)$.
+
+Notice that even if we explicitly exclude $0$ and $1$, the previous
+argument applies on any boundary points among intervals. Therefore,
+there is no way to avoid this problem if we have more than three intervals.\end{example}
 

### 2017-09-27 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
-The following theorem that is obtained by replacing the QIVPM~$\bar{\mu}$
-in Thm.~\ref{cor:Gleason's} by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
-and estimate the states consistent with it.
+By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
+by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, we obtain
+the following theorem that estimates the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
 
@@
 \noindent If a state~$\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
-the difference between the Born quantum probabilities on any 1-dimensioal
+the difference between their Born quantum probabilities on any 1-dimensioal
 projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
 must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
-by definition. As a concrete example of Thm.~\ref{thm:Finite-precision-Gleason},
-since $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
-and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
-which is easy to see on the commuting subspace of event~$\events_{C}$
-according to Table~\ref{tab:Compute-the-QIVPM}, we have $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$,
-and this is indeed the case because $\left\Vert \rho_{0}-\rho_{1}\right\Vert =\frac{1}{24}$~\citep{HOSTunpublished}.
+by definition. For example, Table~\ref{tab:Compute-the-QIVPM} shows
+that $\rho_{0}$ is consistent with $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$
+and $\rho_{1}$ is consistent with $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+both on every projectors in $\events_{C}$. Indeed, they are consistent
+with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
+by Thm.\ref{thm:Finite-precision-Gleason}. This is true because the
+exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is $\frac{1}{24}$~\citep{544199}.
 
@@
 \caption{\label{tab:non-Born-QIVPM}Define a non-Born QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
-on the three-dimensional Hilbert space.}
+on the three-dimensional Hilbert space. The projectors mapping to
+the same interval is listed in the column labeled by $P$ and separated
+by commas.}
 
@@
 \addlinespace
-$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, $\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
+$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
+$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
 \midrule 
@@
 Notice that if we restrict $\bar{\mu}$ on the commuting subspace
-of events~$\events_{C}$, the state~$\frac{1}{2}\cdot\proj{1}+\frac{1}{2}\cdot\proj{2}\in\coreBorn\left(\bar{\mu},\events_{C}\right)$
-so that $\coreBorn\left(\bar{\mu},\events_{C}\right)$ is non-empty.
-In general, for any commuting subspace of events~$\events_{C}'$,
+of events~$\events_{C}$, the state~$\frac{1}{2}\cdot\proj{1}+\frac{1}{2}\cdot\proj{2}$
+is consistent with $\bar{\mu}$ so that $\coreBorn\left(\bar{\mu},\events_{C}\right)$
+is non-empty. In general, for any commuting subspace of events~$\events_{C}'$,
 $\coreBorn\left(\bar{\mu},\events_{C}'\right)$ is non-empty according

### 2017-09-27 prop_letter.tex
prop_letter.tex \section{Gleason} After meet with WTS...

@@
 on all projectors is the one used to construct $\mu$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-In another word, the set of all quantum probability measures is one-to-one
-corresponding to the set of states so that studying the set of states
+In other words, the set of all quantum probability measures corresponds
+one-to-one to the set of states so that studying the set of states
 is sufficient to understand all possible phenomenon regarding to quantum
@@
 if we monotonically shrink the length of intervals, the states consistent
-with $\bar{\mu}$ will be closer and closer to $\rho$, and vise visa.
+with $\bar{\mu}$ will be closer and closer to $\rho$, and vice versa.
 However, there is a QIVPM such that no state can be consistent with
@@
 the problem of finite precision measurement itself is not limited
-in just applying error analysis in experimental results, but it highlight
+in just applying error analysis in experimental results, but it highlights
 some new phenomenon regarding to the foundation of quantum machines,
@@
 \noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
-Eqs.~(\ref{eq:QIVPM-constraints}), the condition really need to
-be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+Eqs.~(\ref{eq:QIVPM-constraints}), the condition really needing
+to be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
 Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
@@
 $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-we can formulate Gleason's theorem in our framework as follow.
+we can formulate Gleason's theorem in our framework as follows.
 
@@
 with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
-by Thm.\ref{thm:Finite-precision-Gleason}. This is true because the
-exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is $\frac{1}{24}$~\citep{544199}.
+by Thm.~\ref{thm:Finite-precision-Gleason}. This is true because
+the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
+$\frac{1}{24}$~\citep{544199}.
 
@@
 
-\noindent Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
+\noindent To prove the theorem, we first need to construct a QIVPM,
+and then verify that no states consistent with it on all projectors.
+Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
 let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,

### 2017-09-28 prop_letter.tex
prop_letter.tex \section{Gleason} Merges Prof. Hanson's suggestion after meeting...

@@
 Gleason's theorem asserts that the only state consistent with $\mu$
-on all projectors is the one used to construct $\mu$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-In other words, the set of all quantum probability measures corresponds
-one-to-one to the set of states so that studying the set of states
-is sufficient to understand all possible phenomenon regarding to quantum
+on all projectors is the one used to construct $\mu$ by the Born
+rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}. In
+other words, the set of all quantum probability measures corresponds
+one-to-one to the set of states, so that studying the set of states
+is sufficient to understand all possible phenomena regarding to quantum
 probability. Although we can extend the Born rule to its finite precision
-version easily, there are some subtleties extending Gleason's theorem.
+version easily, there are some subtleties to extending Gleason's theorem.
 If we only focus on the Born QIVPMs~$\bar{\mu}$, that is, QIVPM's
@@
 However, there is a QIVPM such that no state can be consistent with
-it on every projector. In another word, although the Born rule and
+it on every projector. In another words, although the Born rule and
 Gleason's theorem can be extended to consider finite precision measurement,
 the problem of finite precision measurement itself is not limited
-in just applying error analysis in experimental results, but it highlights
-some new phenomenon regarding to the foundation of quantum machines,
-and it is necessary to embedding the idea of the resources available
-for realistic measurement into the formulation of quantum theory.
+to error analysis in experimental results, but it highlights some
+new phenomena regarding the foundation of quantum mechanics, and it
+is necessary to embed the idea of the resources available for realistic
+measurement into the formulation of quantum theory.
 
@@
 which are overlapping intervals with length~$1/n$ except for the
-intervals with length~$\left(2n\right)^{-1}$ at each end. As in
-Table~\ref{tab:I_n}, to select the correct interval from these overlapping
-intervals~$[\ell,r]$, we define the non-overlapping interior part
-of a interval, $\textrm{Int}\left([\ell,r]\right)$.
+intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
+in Table~\ref{tab:I_n}, we select the correct interval from these
+overlapping intervals~$[\ell,r]$, and define $\textrm{Int}\left([\ell,r]\right)$,
+the non-overlapping interior part of an interval.
 \begin{table}
@@
 \noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
-Eqs.~(\ref{eq:QIVPM-constraints}), the condition really needing
-to be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+Eqs.~(\ref{eq:QIVPM-constraints}), the condition that needs to be
+checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
 Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
@@
 \end{itemize}
-\noindent No matter which case Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+\noindent No matter which case holds, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
 can be deduced easily. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
@@
 a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
-the states consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
-has a unique element. \end{thm}
+the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
+is unique. \end{thm}
 

### 2017-09-29 prop_letter.tex
prop_letter.tex \section{Gleason} Start reconstruction...

@@
 
+\begin{comment}
 While the finite-precision extension of the Kochen-Specker theorem
@@
 measurement into the formulation of quantum theory.
+\end{comment}
+
+Notice that if we restrict $\bar{\mu}$ on the commuting subspace
+of events~$\events_{C}$, the state~$\frac{1}{2}\cdot\proj{1}+\frac{1}{2}\cdot\proj{2}$
+is consistent with $\bar{\mu}$ so that $\coreBorn\left(\bar{\mu},\events_{C}\right)$
+is non-empty. In general, for any commuting subspace of events~$\events_{C}'$,
+$\coreBorn\left(\bar{\mu},\events_{C}'\right)$ is non-empty according
+to the classical Thm.~\ref{thm:Shapley}. The difference between
+classical and quantum highlights the following fact: Although classically
+we could build a theory and deal the finite-precision measurement
+in error analysis, it is necessary to embed the finite-precision measurement
+into the foundation of quantum theory.
+
+If a QIVPM is not \emph{a priori} known to be induced by a state,
+there are some QIVPMs that cannot be consistent with any state.
+
+\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
+a Hilbert space $\Hilb$ of dimension $3$, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
+
+\noindent To prove the theorem, we first need to construct a QIVPM,
+and then verify that no states consistent with it on all projectors.
+Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
+let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
+$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
+The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
+in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly.
+\begin{table}
+\caption{\label{tab:non-Born-QIVPM}Define a non-Born QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+on the three-dimensional Hilbert space. The projectors mapping to
+the same interval is listed in the column labeled by $P$ and separated
+by commas.}
+
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
+$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+All other projectors & $\unknown$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
+empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
+for any~$P$, the state~$\rho$ must satisfy: 
+\begin{equation}
+\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
+\end{equation}
+which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
+for all $j$. The last equation never holds proving the theorem. Thus,
+there is no state consistent with the QIVPM on all projectors~$P\in\events$,
+so Gleason's theorem cannot be extended to general QIVPMs.
 
@@
 
-In the limiting case when the intervals are infinitely precise, i.e.,
-$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-we can formulate Gleason's theorem in our framework as follows.
-
-\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
-a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
-the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
-is unique. \end{thm}
-
 Our framework allows us to generalize the above theorem to Born QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
@@
 then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
+
+\yutsung{Compare the norm we used with other distances. For example,
+the trace distance defined in Sec.~9.2.1 in Nielsen and Chuang~\citep{544199}.}
 
@@
 
-If a QIVPM is not \emph{a priori} known to be induced by a state,
-there are some QIVPMs that cannot be consistent with any state.
-
-\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
-a Hilbert space $\Hilb$ of dimension $3$, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
-
-\noindent To prove the theorem, we first need to construct a QIVPM,
-and then verify that no states consistent with it on all projectors.
-Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
-let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
-$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
-The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
-in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly.
-\begin{table}
-\caption{\label{tab:non-Born-QIVPM}Define a non-Born QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
-on the three-dimensional Hilbert space. The projectors mapping to
-the same interval is listed in the column labeled by $P$ and separated
-by commas.}
-
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
-$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-All other projectors & $\unknown$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
-Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
-empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
-for any~$P$, the state~$\rho$ must satisfy: 
-\begin{equation}
-\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
-\end{equation}
-which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all $j$. The last equation never holds proving the theorem. Thus,
-there is no state consistent with the QIVPM on all projectors~$P\in\events$,
-so Gleason's theorem cannot be extended to general QIVPMs.
-
-Notice that if we restrict $\bar{\mu}$ on the commuting subspace
-of events~$\events_{C}$, the state~$\frac{1}{2}\cdot\proj{1}+\frac{1}{2}\cdot\proj{2}$
-is consistent with $\bar{\mu}$ so that $\coreBorn\left(\bar{\mu},\events_{C}\right)$
-is non-empty. In general, for any commuting subspace of events~$\events_{C}'$,
-$\coreBorn\left(\bar{\mu},\events_{C}'\right)$ is non-empty according
-to the classical Thm.~\ref{thm:Shapley}. The difference between
-classical and quantum highlights the following fact: Although classically
-we could build a theory and deal the finite-precision measurement
-in error analysis, it is necessary to embed the finite-precision measurement
-into the foundation of quantum theory.
+In the limiting case when the intervals are infinitely precise, i.e.,
+$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+we can formulate Gleason's theorem in our framework as follows.
+
+\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
+a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
+the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
+is unique. \end{thm}
 

### 2017-09-29 prop_letter.tex
prop_letter.tex \section{Gleason} Keep reconstruction...

@@
 
-Notice that if we restrict $\bar{\mu}$ on the commuting subspace
-of events~$\events_{C}$, the state~$\frac{1}{2}\cdot\proj{1}+\frac{1}{2}\cdot\proj{2}$
-is consistent with $\bar{\mu}$ so that $\coreBorn\left(\bar{\mu},\events_{C}\right)$
-is non-empty. In general, for any commuting subspace of events~$\events_{C}'$,
-$\coreBorn\left(\bar{\mu},\events_{C}'\right)$ is non-empty according
-to the classical Thm.~\ref{thm:Shapley}. The difference between
-classical and quantum highlights the following fact: Although classically
-we could build a theory and deal the finite-precision measurement
-in error analysis, it is necessary to embed the finite-precision measurement
-into the foundation of quantum theory.
-
-If a QIVPM is not \emph{a priori} known to be induced by a state,
-there are some QIVPMs that cannot be consistent with any state.
+In Sec.~\ref{sec:Interval-Uncertainty}, we discussed how states
+consistent with a QIVPM~$\bar{\mu}$ on the projectors in a subspace
+of event~$\events'$. In particular, if $\events'$ commutes, the
+classical Thm.~\ref{thm:Shapley} claims that there is always a state~$\rho$
+consistent with $\bar{\mu}$. In this section, we want to shift our
+attention to consider state consistent with $\bar{\mu}$ on every
+event, $\coreBorn\left(\bar{\mu},\events\right)$. While the intervals
+are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+Gleason's theorem claimed that there is always a unique consistent
+with $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+If we consider general QIVPMs mapping to an \emph{arbitrary} set of
+intervals, there are some QIVPMs that cannot be consistent with any
+state.
 
@@
 which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all $j$. The last equation never holds proving the theorem. Thus,
-there is no state consistent with the QIVPM on all projectors~$P\in\events$,
-so Gleason's theorem cannot be extended to general QIVPMs.
+for all $j$. The last equation never holds proving the theorem.
+
+In other words, if the measurement intervals are too unprecise, the
+results we get might contradict to each other, and exclude all possible
+states consistent with the results.
+
+\yutsung{{Clean up until here.}}
+
+Notice that if we restrict $\bar{\mu}$ on the commuting subspace
+of events~$\events_{C}$, the state~$\frac{1}{2}\cdot\proj{1}+\frac{1}{2}\cdot\proj{2}$
+is consistent with $\bar{\mu}$ so that $\coreBorn\left(\bar{\mu},\events_{C}\right)$
+is non-empty. In general, for any commuting subspace of events~$\events_{C}'$,
+$\coreBorn\left(\bar{\mu},\events_{C}'\right)$ is non-empty according
+to the classical Thm.~\ref{thm:Shapley}. The difference between
+classical and quantum highlights the following fact: Although classically
+we could build a theory and deal the finite-precision measurement
+in error analysis, it is necessary to embed the finite-precision measurement
+into the foundation of quantum theory.
+
+If a QIVPM is not \emph{a priori} known to be induced by a state,
+
+\noindent Thus, there is no state consistent with the QIVPM on all
+projectors~$P\in\events$, so Gleason's theorem cannot be extended
+to general QIVPMs.
 

### 2017-09-30 prop_letter.tex
prop_letter.tex \section{Gleason} Global replace 	\iota_{*}\circ\mu_{*}^{\mathrm{B}} by 	\left[\mu_{*}^{\mathrm{B}}\right]_{*} .

--- 2017-09-28 prop_letter.tex
@@
 
+In Sec.~\ref{sec:Interval-Uncertainty}, we discussed how states
+consistent with a QIVPM~$\bar{\mu}$ on the projectors in a subspace
+of event~$\events'$. In particular, if $\events'$ commutes, $\bar{\mu}$
+restricting on $\events'$ is essentially a classical IVPM, and Thm.~\ref{thm:Shapley}
+claims that there is always a state~$\rho$ consistent with $\bar{\mu}$.
+In this section, we want to shift our attention to consider states
+consistent with $\bar{\mu}$ on every event, $\coreBorn\left(\bar{\mu},\events\right)$,
+so that these states could characterize $\bar{\mu}$ comprehensively.
+When the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+QIVPMs become to quantum probability measures~\citep{HOSTunpublished},
+and Gleason's theorem claims that there is always a unique state consistent
+with $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+However, if we consider general QIVPMs mapping to an \emph{arbitrary}
+set of intervals, there is a QIVPM that no state can be consistent
+with it.
+
+\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
+a Hilbert space $\Hilb$ of dimension $3$, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
+
+\noindent To prove the theorem, we first need to construct a QIVPM,
+and then verify that no states consistent with it on all projectors.
+Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
+let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
+$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
+The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
+in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly.
+\begin{table}
+\caption{\label{tab:non-Born-QIVPM}Define a non-Born QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+on the three-dimensional Hilbert space. The projectors mapping to
+the same interval is listed in the column labeled by $P$ and separated
+by commas.}
+
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
+$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+All other projectors & $\unknown$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
+empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
+for any~$P$, the state~$\rho$ must satisfy: 
+\begin{equation}
+\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
+\end{equation}
+which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
+for all $j$. The last equation never holds proving the theorem.
+
+In other words, if the measurement intervals are too imprecise, the
+results we get might contradict to each other, and exclude all possible
+states consistent with the measurement results. There are many ways
+to avoid these kind of too imprecise intervals~\citep{HOSTunpublished}.
+Following, we consider a concrete family of intervals and QIVPMs~$\bar{\mu}$
+such that if we monotonically shrink the length of intervals, the
+states consistent with $\bar{\mu}$ will be closer and closer to $\rho$
+which inducing $\bar{\mu}$.
+\begin{equation}
+\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
+ & \cup\{\imposs,\necess\}
+\end{aligned}
+\end{equation}
+which are overlapping intervals with length~$1/n$ except for the
+intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
+in Table~\ref{tab:I_n}, we select the correct interval from these
+overlapping intervals~$[\ell,r]$, and define $\textrm{Int}\left([\ell,r]\right)$,
+the non-overlapping interior part of an interval.
+\begin{table}
+\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
+their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
+means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
+their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.
+See Table~\ref{tab:I_2} for a concrete example when $n=2$.}
+
+\begin{tabular}{cccc}
+\toprule 
+\addlinespace
+$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+$0<k<2n$\tabularnewline
+and $2\nmid k$\tabularnewline
+\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+$0<k<2n$\tabularnewline
+and $2\mid k$\tabularnewline
+\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+Then, given a real-valued probability~$x$, we will select the interval~$\iota_{n}\left(x\right)=[\ell,r]$
+if $x\in\textrm{Int}\left([\ell,r]\right)$.
+
+After we have the rule to replace a real number by an interval, we
+can induce a QIVPM from a state according to the following theorem:
+
+\begin{thm}[Finite-precision Extension of the Born rule]\label{thm:Finite-precision-Born}For
+any state $\rho$ on a three-dimensional Hilbert space, a function~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}:\events\rightarrow\mathscr{I}_{n}$
+defined by $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}\left(P\right)=\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
+is a QIVPM.\end{thm}
+
+\noindent Since $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$ clearly
+satisfies Eqs.~(\ref{eq:QIVPM-constraints}), the condition that
+needs to be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
+is easy to verify that
+\begin{equation}
+\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
+\end{equation}
+This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
+are not orthogonal on a three-dimensional Hilbert space, we have two
+possibilities:
+\begin{itemize}
+\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
+on their complements.
+\item One of them projects onto a subspace of what the other one projects
+onto.
+\end{itemize}
+\noindent No matter which case holds, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+can be deduced easily. Therefore, $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
+is indeed a QIVPM.
+
+\yutsung{Clean up until here.}
+
 While the finite-precision extension of the Kochen-Specker theorem
@@
 
-The first step toward a finite precision Born rule is to find a way
-of replacing the computed probability by an interval. This can be
-done by carefully picking a set of intervals and a rule to select
-the correct interval when intervals are overlapping. For example,
-consider the following collection of overlapping intervals: 
-\begin{equation}
-\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
- & \cup\{\imposs,\necess\}
-\end{aligned}
-\end{equation}
-which are overlapping intervals with length~$1/n$ except for the
-intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
-in Table~\ref{tab:I_n}, we select the correct interval from these
-overlapping intervals~$[\ell,r]$, and define $\textrm{Int}\left([\ell,r]\right)$,
-the non-overlapping interior part of an interval.
-\begin{table}
-\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
-their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
-means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
-their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.
-See Table~\ref{tab:I_2} for a concrete example when $n=2$.}
-
-\begin{tabular}{cccc}
-\toprule 
-\addlinespace
-$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
- & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-\begin{tabular}{c}
-$0<k<2n$\tabularnewline
-and $2\nmid k$\tabularnewline
-\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-\begin{tabular}{c}
-$0<k<2n$\tabularnewline
-and $2\mid k$\tabularnewline
-\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
- & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
- Table~\ref{tab:I_2} lists a special case $\mathscr{I}_{2}$ to
-illustrate these intervals and their interior parts more clearly.
-\begin{table}
-\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$, , their lengths,
-and their interiors. Although intervals~$[\ell,r]$ are overlapping,
-their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
-
-\begin{tabular}{cccc}
-\toprule 
-\addlinespace
-$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
- & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\tfrac{1}{4}$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\tfrac{1}{2}$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$3$ & $\left[\tfrac{1}{2},1\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$4$ & $\left[\tfrac{1}{4},1\right]$ & $\tfrac{1}{4}$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
- & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
- Then, given a real-valued probability~$x$, we will select the interval~$\iota_{n}\left(x\right)=[\ell,r]$
-if $x\in\textrm{Int}\left([\ell,r]\right)$.
-
-After we have the rule to replace a real number by an interval, we
-can induce a QIVPM from a state according to the following theorem:
-
-\begin{thm}[Finite-precision Extension of the Born rule]\label{thm:Finite-precision-Born}For
-any state $\rho$ on a three-dimensional Hilbert space, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-is a QIVPM, where $\circ$ is the function concatenation.\end{thm}
-
-\noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
-Eqs.~(\ref{eq:QIVPM-constraints}), the condition that needs to be
-checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
-Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
-is easy to verify that
-\begin{equation}
-\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
-\end{equation}
-This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
-are not orthogonal on a three-dimensional Hilbert space, we have two
-possibilities:
-\begin{itemize}
-\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
-on their complements.
-\item One of them projects onto a subspace of what the other one projects
-onto.
-\end{itemize}
-\noindent No matter which case holds, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-can be deduced easily. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-is indeed a QIVPM.
-
-As a concrete example of Thm.~\ref{thm:Finite-precision-Born}, when
-$n=2$, two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
-and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$
-can induce two QIVPMs~$\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
-and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$. Given any projector
-$P$ in the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
-and $\proj{2}$, $\events_{C}$, the interval-valued probability of
-the induced QIVPMs, $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
-and $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$,
-can be computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
-\begin{table}
-\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
-and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ based on $\mu_{\rho_{0}}^{\mathrm{B}}$
-and $\mu_{\rho_{1}}^{\mathrm{B}}$ on $\events_{C}$.}
-
-\begin{tabular}{ccccc}
-\toprule 
-\addlinespace
-$P$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
-
-In the limiting case when the intervals are infinitely precise, i.e.,
-$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-we can formulate Gleason's theorem in our framework as follows.
-
-\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
-a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
-the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
-is unique. \end{thm}
-
-Our framework allows us to generalize the above theorem to Born QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
-The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
-gets closer and closer to $\rho$ as the intervals get narrower and
-narrower, eventually collapsing to $\rho$ when the intervals become
-infinitely precise real numbers covering the real line. To state this
-result, we need to introduce a notion of distance between two states~$\rho$
-and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
-By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
-by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, we obtain
-the following theorem that estimates the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
-
-\begin{thm}[Finite-precision Extension of Gleason's theorem for the
-Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
-$\Hilb$ of dimension $3$, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\iota_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
-
-\noindent If a state~$\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
-the difference between their Born quantum probabilities on any 1-dimensioal
-projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
-must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
-by definition. For example, Table~\ref{tab:Compute-the-QIVPM} shows
-that $\rho_{0}$ is consistent with $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$
-and $\rho_{1}$ is consistent with $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
-both on every projectors in $\events_{C}$. Indeed, they are consistent
-with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
-by Thm.~\ref{thm:Finite-precision-Gleason}. This is true because
-the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
-$\frac{1}{24}$~\citep{544199}.
-
-If a QIVPM is not \emph{a priori} known to be induced by a state,
-there are some QIVPMs that cannot be consistent with any state.
-
-\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
-a Hilbert space $\Hilb$ of dimension $3$, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
-
-\noindent To prove the theorem, we first need to construct a QIVPM,
-and then verify that no states consistent with it on all projectors.
-Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
-let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
-$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
-The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
-in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly.
-\begin{table}
-\caption{\label{tab:non-Born-QIVPM}Define a non-Born QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
-on the three-dimensional Hilbert space. The projectors mapping to
-the same interval is listed in the column labeled by $P$ and separated
-by commas.}
-
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
-$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-All other projectors & $\unknown$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
-Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
-empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
-for any~$P$, the state~$\rho$ must satisfy: 
-\begin{equation}
-\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
-\end{equation}
-which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all $j$. The last equation never holds proving the theorem. Thus,
-there is no state consistent with the QIVPM on all projectors~$P\in\events$,
-so Gleason's theorem cannot be extended to general QIVPMs.
-
 Notice that if we restrict $\bar{\mu}$ on the commuting subspace
@@
 into the foundation of quantum theory.
+
+If a QIVPM is not \emph{a priori} known to be induced by a state,
+
+\noindent Thus, there is no state consistent with the QIVPM on all
+projectors~$P\in\events$, so Gleason's theorem cannot be extended
+to general QIVPMs.
+
+The first step toward a finite precision Born rule is to find a way
+of replacing the computed probability by an interval. This can be
+done by carefully picking a set of intervals and a rule to select
+the correct interval when intervals are overlapping. For example,
+consider the following collection of overlapping intervals:
+
+Table~\ref{tab:I_2} lists a special case $\mathscr{I}_{2}$ to illustrate
+these intervals and their interior parts more clearly.
+\begin{table}
+\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$, , their lengths,
+and their interiors. Although intervals~$[\ell,r]$ are overlapping,
+their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
+
+\begin{tabular}{cccc}
+\toprule 
+\addlinespace
+$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\tfrac{1}{4}$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\tfrac{1}{2}$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$3$ & $\left[\tfrac{1}{2},1\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$4$ & $\left[\tfrac{1}{4},1\right]$ & $\tfrac{1}{4}$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+
+As a concrete example of Thm.~\ref{thm:Finite-precision-Born}, when
+$n=2$, two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
+and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$
+can induce two QIVPMs~$\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
+and $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$. Given any projector
+$P$ in the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
+and $\proj{2}$, $\events_{C}$, the interval-valued probability of
+the induced QIVPMs, $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
+and $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$,
+can be computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
+\begin{table}
+\caption{\label{tab:Compute-the-QIVPM}Compute $\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
+and $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$ based on $\mu_{\rho_{0}}^{\mathrm{B}}$
+and $\mu_{\rho_{1}}^{\mathrm{B}}$ on $\events_{C}$.}
+
+\begin{tabular}{ccccc}
+\toprule 
+\addlinespace
+$P$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+
+Our framework allows us to generalize the above theorem to Born QIVPMs~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$:
+The collection of states consistent $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
+gets closer and closer to $\rho$ as the intervals get narrower and
+narrower, eventually collapsing to $\rho$ when the intervals become
+infinitely precise real numbers covering the real line. To state this
+result, we need to introduce a notion of distance between two states~$\rho$
+and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
+By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
+by a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$, we obtain
+the following theorem that estimates the states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.
+
+\begin{thm}[Finite-precision Extension of Gleason's theorem for the
+Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
+$\Hilb$ of dimension $3$, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
+then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
+
+\yutsung{Compare the norm we used with other distances. For example,
+the trace distance defined in Sec.~9.2.1 in Nielsen and Chuang~\citep{544199}.}
+
+\noindent If a state~$\rho'$ is consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
+the difference between their Born quantum probabilities on any 1-dimensioal
+projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
+must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
+by definition. For example, Table~\ref{tab:Compute-the-QIVPM} shows
+that $\rho_{0}$ is consistent with $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$
+and $\rho_{1}$ is consistent with $\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
+both on every projectors in $\events_{C}$. Indeed, they are consistent
+with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
+by Thm.~\ref{thm:Finite-precision-Gleason}. This is true because
+the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
+$\frac{1}{24}$~\citep{544199}.
+
+In the limiting case when the intervals are infinitely precise, i.e.,
+$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+we can formulate Gleason's theorem in our framework as follows.
+
+\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
+a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
+the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
+is unique. \end{thm}
 

### 2017-09-30 prop_letter.tex
prop_letter.tex \section{Gleason} Keep reconstructing...

@@
 
-\noindent Since $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$ clearly
-satisfies Eqs.~(\ref{eq:QIVPM-constraints}), the condition that
-needs to be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+\noindent To prove that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
+is a QIVPM, it is sufficient to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
 Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
@@
 \end{itemize}
-\noindent No matter which case holds, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-can be deduced easily. Therefore, $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
-is indeed a QIVPM.
+\noindent Both cases deduce Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+easily so that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$ is indeed
+a QIVPM.
+
+The collection of states consistent $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
+gets closer and closer to $\rho$ as the intervals get narrower and
+narrower, eventually collapsing to $\rho$ when the intervals become
+infinitely precise real numbers covering the real line. To state this
+result, we need to introduce a notion of distance between two states~$\rho$
+and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
+By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
+by a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$, we obtain
+the following theorem that estimates the states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.
+
+\begin{thm}[Finite-precision Extension of Gleason's theorem for the
+Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
+$\Hilb$ of dimension $3$, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
+then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
+
+\yutsung{Compare the norm we used with other distances. For example,
+the trace distance defined in Sec.~9.2.1 in Nielsen and Chuang~\citep{544199}.}
+
+\noindent If a state~$\rho'$ is consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
+the difference between their Born quantum probabilities on any 1-dimensioal
+projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
+must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
+by definition.
 
@@
 Our framework allows us to generalize the above theorem to Born QIVPMs~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$:
-The collection of states consistent $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
-gets closer and closer to $\rho$ as the intervals get narrower and
-narrower, eventually collapsing to $\rho$ when the intervals become
-infinitely precise real numbers covering the real line. To state this
-result, we need to introduce a notion of distance between two states~$\rho$
-and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
-By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
-by a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$, we obtain
-the following theorem that estimates the states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.
-
-\begin{thm}[Finite-precision Extension of Gleason's theorem for the
-Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
-$\Hilb$ of dimension $3$, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
-then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
-
-\yutsung{Compare the norm we used with other distances. For example,
-the trace distance defined in Sec.~9.2.1 in Nielsen and Chuang~\citep{544199}.}
-
-\noindent If a state~$\rho'$ is consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
-the difference between their Born quantum probabilities on any 1-dimensioal
-projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
-must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
-by definition. For example, Table~\ref{tab:Compute-the-QIVPM} shows
+
+\noindent  For example, Table~\ref{tab:Compute-the-QIVPM} shows
 that $\rho_{0}$ is consistent with $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$

### 2017-09-30 prop_letter.tex
prop_letter.tex \section{Gleason} Keep reconstructing...

@@
 When the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-QIVPMs become to quantum probability measures~\citep{HOSTunpublished},
-and Gleason's theorem claims that there is always a unique state consistent
-with $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$ becomes
+quantum probability measure~\citep{HOSTunpublished}, and Gleason's
+theorem claims that there is always a unique state consistent with
+$\bar{\mu}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 However, if we consider general QIVPMs mapping to an \emph{arbitrary}
@@
 let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
-$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
+$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
 The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
@@
 \begin{table}
-\caption{\label{tab:non-Born-QIVPM}Define a non-Born QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+\caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
 on the three-dimensional Hilbert space. The projectors mapping to
@@
 results we get might contradict to each other, and exclude all possible
-states consistent with the measurement results. There are many ways
-to avoid these kind of too imprecise intervals~\citep{HOSTunpublished}.
-Following, we consider a concrete family of intervals and QIVPMs~$\bar{\mu}$
-such that if we monotonically shrink the length of intervals, the
-states consistent with $\bar{\mu}$ will be closer and closer to $\rho$
-which inducing $\bar{\mu}$.
+states consistent with the measurement results. To avoid this problem,
+instead of proposing an abstract framework~\citep{HOSTunpublished},
+we start from a concrete family of intervals as follow:
 \begin{equation}
@@
 intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
-in Table~\ref{tab:I_n}, we select the correct interval from these
-overlapping intervals~$[\ell,r]$, and define $\textrm{Int}\left([\ell,r]\right)$,
-the non-overlapping interior part of an interval.
+in Table~\ref{tab:I_n}, for each interval~$[\ell,r]$, we define
+$\textrm{Int}\left([\ell,r]\right)$, the non-overlapping interior
+part of $[\ell,r]$.
 \begin{table}
@@
 means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
-their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.
-See Table~\ref{tab:I_2} for a concrete example when $n=2$.}
+their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
 
@@
 \end{table}
-Then, given a real-valued probability~$x$, we will select the interval~$\iota_{n}\left(x\right)=[\ell,r]$
-if $x\in\textrm{Int}\left([\ell,r]\right)$.
-
-After we have the rule to replace a real number by an interval, we
-can induce a QIVPM from a state according to the following theorem:
+Since the interior part of intervals are non-overlapping, we can define
+a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
+by selecting the interval~$\iota_{n}\left(x\right)=[\ell,r]$ if
+$x\in\textrm{Int}\left([\ell,r]\right)$.
+
+After we have the way mapping a real-valued probability to an interval-valued
+one, we can induce a QIVPM from a state according to the following
+theorem:
 
@@
 defined by $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}\left(P\right)=\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
-is a QIVPM.\end{thm}
+is a QIVPM, called the Born QIVPM.\end{thm}
 
@@
 is a QIVPM, it is sufficient to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
-Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
-is easy to verify that
-\begin{equation}
-\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
-\end{equation}
-This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$,
+\begin{equation}
+\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\label{eq:iota-add}
+\end{equation}
+implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
 when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
@@
 
-The collection of states consistent $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
+Because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
+there is always a state consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.
+Moreover by introducing a notion of distance between two states~$\rho$
+and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
+the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
 gets closer and closer to $\rho$ as the intervals get narrower and
 narrower, eventually collapsing to $\rho$ when the intervals become
-infinitely precise real numbers covering the real line. To state this
-result, we need to introduce a notion of distance between two states~$\rho$
-and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
-By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
-by a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$, we obtain
-the following theorem that estimates the states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.
+infinitely precise real numbers covering the real line.
 
@@
 
+\noindent Given state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
+the difference between their Born quantum probabilities on any 1-dimensioal
+projector~$\proj{\psi}$ is $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
+and must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
+by definition.
+
 \yutsung{Compare the norm we used with other distances. For example,
@@
 
-\noindent If a state~$\rho'$ is consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
-the difference between their Born quantum probabilities on any 1-dimensioal
-projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
-must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
-by definition.
+In the limiting case when the intervals are infinitely precise, the
+original Gleason theorem is recovered, and can be formulated in our
+framework as follows.
+
+\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
+a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
+the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
+is unique. \end{thm}
 
@@
 
-\noindent  For example, Table~\ref{tab:Compute-the-QIVPM} shows
-that $\rho_{0}$ is consistent with $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$
+\noindent For example, Table~\ref{tab:Compute-the-QIVPM} shows that
+$\rho_{0}$ is consistent with $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$
 and $\rho_{1}$ is consistent with $\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
@@
 $\frac{1}{24}$~\citep{544199}.
-
-In the limiting case when the intervals are infinitely precise, i.e.,
-$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-we can formulate Gleason's theorem in our framework as follows.
-
-\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
-a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
-the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
-is unique. \end{thm}
 

### 2017-10-01 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 on the three-dimensional Hilbert space. The projectors mapping to
-the same interval is listed in the column labeled by $P$ and separated
+the same interval are listed in the column labeled by $P$ and separated
 by commas.}
@@
 results we get might contradict to each other, and exclude all possible
-states consistent with the measurement results. To avoid this problem,
-instead of proposing an abstract framework~\citep{HOSTunpublished},
-we start from a concrete family of intervals as follow:
+states consistent with the measurement results. Although we will not
+dig into the general abstract framework to avoid this problem here~\citep{HOSTunpublished},
+we will solve this problem with a concrete family of intervals and
+QIVPMs. The following intervals 
 \begin{equation}
@@
 \end{equation}
-which are overlapping intervals with length~$1/n$ except for the
-intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
-in Table~\ref{tab:I_n}, for each interval~$[\ell,r]$, we define
-$\textrm{Int}\left([\ell,r]\right)$, the non-overlapping interior
-part of $[\ell,r]$.
+are overlapping intervals with length~$1/n$ except for the intervals
+with length~$\left(2n\right)^{-1}$ at each end. As shown in Table~\ref{tab:I_n},
+for each interval~$[\ell,r]$, we define $\textrm{Int}\left([\ell,r]\right)$,
+the non-overlapping interior part of $[\ell,r]$.
 \begin{table}
@@
 \end{table}
-Since the interior part of intervals are non-overlapping, we can define
-a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
-by selecting the interval~$\iota_{n}\left(x\right)=[\ell,r]$ if
-$x\in\textrm{Int}\left([\ell,r]\right)$.
+Since the interior parts are non-overlapping, we can define a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
+by $\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$.
 

### 2017-10-01 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-\noindent To prove the theorem, we first need to construct a QIVPM,
-and then verify that no states consistent with it on all projectors.
-Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
+To prove the theorem, we first need to construct a QIVPM, and then
+verify that no states consistent with it on all projectors. Given
+an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
 let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
@@
 The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
-in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly.
+in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished}.
 \begin{table}
@@
 In other words, if the measurement intervals are too imprecise, the
-results we get might contradict to each other, and exclude all possible
-states consistent with the measurement results. Although we will not
-dig into the general abstract framework to avoid this problem here~\citep{HOSTunpublished},
+results we get might contradict to each other, and exclude the possibility
+that any state is consistent with the measurement results. Although
+we will not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
 we will solve this problem with a concrete family of intervals and
@@
 \end{table}
-Since the interior parts are non-overlapping, we can define a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
+Since their interior parts are non-overlapping, we can define a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
 by $\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$.
-
 After we have the way mapping a real-valued probability to an interval-valued
@@
 defined by $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}\left(P\right)=\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
-is a QIVPM, called the Born QIVPM.\end{thm}
-
-\noindent To prove that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
-is a QIVPM, it is sufficient to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+is a QIVPM, called a Born QIVPM.\end{thm}
+
+To prove that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$ is a QIVPM,
+it is sufficient to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
 Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$,
@@
 \noindent Both cases deduce Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-easily so that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$ is indeed
-a QIVPM.
+easily~\citep{HOSTunpublished} so that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
+is indeed a QIVPM.
 
@@
 there is always a state consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.
-Moreover by introducing a notion of distance between two states~$\rho$
+Moreover, by introducing a notion of distance between two states~$\rho$
 and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
 the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
-gets closer and closer to $\rho$ as the intervals get narrower and
-narrower, eventually collapsing to $\rho$ when the intervals become
-infinitely precise real numbers covering the real line.
+gets closer and closer to $\rho$ with respect to $\left\Vert \cdot\right\Vert $
+as the intervals get narrower and narrower.
 
@@
 
-In the limiting case when the intervals are infinitely precise, the
-original Gleason theorem is recovered, and can be formulated in our
-framework as follows.
+In the limiting case when the intervals are infinitely precise real
+numbers covering the real line, the original Gleason theorem is recovered,
+and can be formulated in our framework as follows.
 

### 2017-10-01 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
-a Hilbert space $\Hilb$ of dimension $3$, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+a three-dimensional Hilbert space, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
@@
 In other words, if the measurement intervals are too imprecise, the
-results we get might contradict to each other, and exclude the possibility
-that any state is consistent with the measurement results. Although
-we will not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
+results we get might contradict to each other, and exclude any possible
+state being consistent with the measurement results. Although we will
+not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
 we will solve this problem with a concrete family of intervals and
-QIVPMs. The following intervals 
+QIVPMs. Consider the following intervals 
 \begin{equation}
@@
 \end{equation}
-are overlapping intervals with length~$1/n$ except for the intervals
-with length~$\left(2n\right)^{-1}$ at each end. As shown in Table~\ref{tab:I_n},
-for each interval~$[\ell,r]$, we define $\textrm{Int}\left([\ell,r]\right)$,
-the non-overlapping interior part of $[\ell,r]$.
+which are overlapping intervals with length~$1/n$ except for the
+intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
+in Table~\ref{tab:I_n}, for each interval~$[\ell,r]$, we define
+$\textrm{Int}\left([\ell,r]\right)$, the non-overlapping interior
+part of $[\ell,r]$.
 \begin{table}
@@
 
-Because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
-there is always a state consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.
+In contrast with the QIVPM defined in Thm.~\ref{thm:Non-extensible-of-Gleason's},
+there is always a state consistent with a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
+because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$.
 Moreover, by introducing a notion of distance between two states~$\rho$
@@
 the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
-gets closer and closer to $\rho$ with respect to $\left\Vert \cdot\right\Vert $
-as the intervals get narrower and narrower.
+gets closer and closer to $\rho$ as the intervals get narrower and
+narrower.
 
 \begin{thm}[Finite-precision Extension of Gleason's theorem for the
-Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
-$\Hilb$ of dimension $3$, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
+Born QIVPMs]\label{thm:Finite-precision-Gleason}In a three-dimensional
+Hilbert space, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
 then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
 
-\noindent Given state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
-the difference between their Born quantum probabilities on any 1-dimensioal
-projector~$\proj{\psi}$ is $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
-and must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
+\noindent Given a state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
+we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
+on any 1-dimensioal projector~$\proj{\psi}$ by Thm.~\ref{thm:Finite-precision-Born}.
+Since the maximum length of the intervals in $\mathscr{I}_{n}$ is
+$1/n$, the difference between the Born quantum probabilities~$\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$
+is bounded by $1/n$.  This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
 by definition.

### 2017-10-01 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
-we will solve this problem with a concrete family of intervals and
+we will address this problem with a concrete family of intervals and
 QIVPMs. Consider the following intervals 
@@
 Since their interior parts are non-overlapping, we can define a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
-by $\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$.
-After we have the way mapping a real-valued probability to an interval-valued
-one, we can induce a QIVPM from a state according to the following
-theorem:
+by $\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$
+to map a real-valued probability to an interval-valued one. This function
+can then induce a QIVPM from a state according to the following theorem:
 
@@
 
-In contrast with the QIVPM defined in Thm.~\ref{thm:Non-extensible-of-Gleason's},
-there is always a state consistent with a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
+In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
+there is always a state consistent with a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
 because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$.
-Moreover, by introducing a notion of distance between two states~$\rho$
-and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
+Moreover, with respect to a notion of distance between two states~$\rho$
+and $\rho'$, $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
 the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
@@
 we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
-on any 1-dimensioal projector~$\proj{\psi}$ by Thm.~\ref{thm:Finite-precision-Born}.
-Since the maximum length of the intervals in $\mathscr{I}_{n}$ is
-$1/n$, the difference between the Born quantum probabilities~$\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$
-is bounded by $1/n$.  This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
-by definition.
+for any 1-dimensioal projector~$\proj{\psi}$. Since the maximum
+length of the intervals in $\mathscr{I}_{n}$ is $1/n$, $1/n$ is
+the upper bound of the difference between the Born quantum probabilities
+$\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
+ This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$ by
+definition.
 

### 2017-10-01 prop_iop.tex
prop_letter.tex -> prop_iop.tex Move a concrete example...

@@
 
-\begin{example}\label{ex:equilateral}For any positive integer~$n$,
-there is an additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
-defined by the following:
-\begin{itemize}
-\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
-\item when $0<x<1$, we have $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
-where $k$ is defined by either one of the following:
-\begin{itemize}
-\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
-\item $2\nmid k$ and $k-0.5<2nx<k+0.5$,
-\end{itemize}
-\end{itemize}
-where $\widehat{\mathscr{I}}_{n}=\set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\cup\left\{ \left[0,0\right],\left[1,1\right]\right\} $.\end{example}
+\begin{example}\label{ex:equilateral}Consider the following intervals
+\begin{equation}\eqalign{ 
+\widehat{\mathscr{I}}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
+ & \cup\{\imposs,\necess\}
+}\end{equation}
+which are overlapping intervals with length~$1/n$ except for the
+intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
+in Table~\ref{tab:I_n}, for each interval~$[\ell,r]$, we define
+$\textrm{Int}\left([\ell,r]\right)$, the non-overlapping interior
+part of $[\ell,r]$.
+\begin{table}
+\caption{\label{tab:I_n}Intervals in $\widehat{\mathscr{I}}_{n}$, their lengths,
+and their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
+means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
+their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
+\centering{}%
+\begin{tabular}{cccc}
+\toprule 
+\addlinespace
+$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+$0<k<2n$\tabularnewline
+and $2\nmid k$\tabularnewline
+\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+$0<k<2n$\tabularnewline
+and $2\mid k$\tabularnewline
+\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+Since their interior parts are non-overlapping, we can define a function~$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
+by $\widehat{\iota}_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$
+to map a real-valued probability to an interval-valued one. Table~\ref{tab:I_2}
+lists a special case $\widehat{\mathscr{I}}_{2}$ to illustrate these
+intervals and their interior parts more clearly.
+\begin{table}
+\caption{\label{tab:I_2}Intervals in $\widehat{\mathscr{I}}_{2}$, , their
+lengths, and their interiors. Although intervals~$[\ell,r]$ are
+overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
+are non-overlapping.}
+\centering{}%
+\begin{tabular}{cccc}
+\toprule 
+\addlinespace
+$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\tfrac{1}{4}$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\tfrac{1}{2}$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$3$ & $\left[\tfrac{1}{2},1\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$4$ & $\left[\tfrac{1}{4},1\right]$ & $\tfrac{1}{4}$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+\end{example}
 

### 2017-10-02 prop_letter.tex
prop_letter.tex -> prop_iop.tex Move a concrete example...
prop_letter.tex \section{Gleason} Updating...

@@
 results we get might contradict to each other, and exclude any possible
-state being consistent with the measurement results. Although we will
-not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
+state from being consistent with the measurement results. Although
+we will not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
 we will address this problem with a concrete family of intervals and
@@
 Born QIVPMs]\label{thm:Finite-precision-Gleason}In a three-dimensional
-Hilbert space, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
-then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
+Hilbert space, given any state~$\rho$, if a state $\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
+then their distance $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
 
@@
 for any 1-dimensioal projector~$\proj{\psi}$. Since the maximum
-length of the intervals in $\mathscr{I}_{n}$ is $1/n$, $1/n$ is
-the upper bound of the difference between the Born quantum probabilities
+length of the intervals in $\mathscr{I}_{n}$ is $1/n$, it is the
+upper bound of the difference between the Born quantum probabilities
 $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
@@
 consider the following collection of overlapping intervals:
-
-Table~\ref{tab:I_2} lists a special case $\mathscr{I}_{2}$ to illustrate
-these intervals and their interior parts more clearly.
-\begin{table}
-\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$, , their lengths,
-and their interiors. Although intervals~$[\ell,r]$ are overlapping,
-their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
-
-\begin{tabular}{cccc}
-\toprule 
-\addlinespace
-$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
- & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\tfrac{1}{4}$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\tfrac{1}{2}$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$3$ & $\left[\tfrac{1}{2},1\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$4$ & $\left[\tfrac{1}{4},1\right]$ & $\tfrac{1}{4}$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
- & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
 

### 2017-10-02 prop_iop.tex
prop_letter.tex \section{Gleason} Updating...
prop_letter.tex -> prop_iop.tex Move a concrete example...

@@
 \usepackage{amstext}
+\usepackage{array}
+\usepackage{booktabs}
+\usepackage{multirow}
 
@@
 \newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}
+\newcommand{\tfrac}[2]{\textstyle\frac{#1}{#2}}
 
@@
 
-\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
-and an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+\begin{lemma}\label{thm:Finite-precision-Gleason}Given a Hilbert
+space with the set of all projectors\nb$\events$, and an additive
+interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
@@
 Hilbert space, if $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-then $\left\Vert \rho-\rho'\right\Vert \le1/n$.\end{example}
+then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
+
+For example, when $n=2$, two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
+and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$
+can induce two QIVPMs~$\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+and $\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$. Given
+any projector $P$ in the minimal subspace of events containing $\proj{0}$,
+$\proj{1}$, and $\proj{2}$, $\events_{C}$, the interval-valued
+probability of the induced QIVPMs, $\widehat{\iota}_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
+and $\widehat{\iota}_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$,
+can be computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
+\begin{table}
+\caption{\label{tab:Compute-the-QIVPM}Compute $\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+and $\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ based on
+$\mu_{\rho_{0}}^{\mathrm{B}}$ and $\mu_{\rho_{1}}^{\mathrm{B}}$
+on $\events_{C}$.}
+\centering{}%
+\begin{tabular}{ccccc}
+\toprule 
+\addlinespace
+$P$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+Table~\ref{tab:Compute-the-QIVPM} shows that $\rho_{0}$ is consistent
+with $\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ and $\rho_{1}$
+is consistent with $\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+both on every projectors in $\events_{C}$. Indeed, they are consistent
+with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
+by lemma~\ref{thm:Finite-precision-Gleason}. This is true because
+the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
+$\frac{1}{24}$~\cite{544199}.\end{example}
 

### 2017-10-02 prop_letter.tex
prop_letter.tex -> prop_iop.tex Move a concrete example...

@@
 
-\yutsung{Clean up until here.}
-
-While the finite-precision extension of the Kochen-Specker theorem
-asserts the non-existence of a certain kind of QIVPMs, we also want
-to understand what a QIVPM could be when it exists. A conventional
-quantum probability measure~$\mu$ can easily be constructed using
-the Born rule when one knows the current state of the system~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
-Gleason's theorem asserts that the only state consistent with $\mu$
-on all projectors is the one used to construct $\mu$ by the Born
-rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}. In
-other words, the set of all quantum probability measures corresponds
-one-to-one to the set of states, so that studying the set of states
-is sufficient to understand all possible phenomena regarding to quantum
-probability. Although we can extend the Born rule to its finite precision
-version easily, there are some subtleties to extending Gleason's theorem.
-If we only focus on the Born QIVPMs~$\bar{\mu}$, that is, QIVPM's
-induced by a state~$\rho$ according to the Born rule, we find that
-if we monotonically shrink the length of intervals, the states consistent
-with $\bar{\mu}$ will be closer and closer to $\rho$, and vice versa.
-However, there is a QIVPM such that no state can be consistent with
-it on every projector. In another words, although the Born rule and
-Gleason's theorem can be extended to consider finite precision measurement,
-the problem of finite precision measurement itself is not limited
-to error analysis in experimental results, but it highlights some
-new phenomena regarding the foundation of quantum mechanics, and it
-is necessary to embed the idea of the resources available for realistic
-measurement into the formulation of quantum theory.
-
-Notice that if we restrict $\bar{\mu}$ on the commuting subspace
-of events~$\events_{C}$, the state~$\frac{1}{2}\cdot\proj{1}+\frac{1}{2}\cdot\proj{2}$
-is consistent with $\bar{\mu}$ so that $\coreBorn\left(\bar{\mu},\events_{C}\right)$
-is non-empty. In general, for any commuting subspace of events~$\events_{C}'$,
-$\coreBorn\left(\bar{\mu},\events_{C}'\right)$ is non-empty according
-to the classical Thm.~\ref{thm:Shapley}. The difference between
-classical and quantum highlights the following fact: Although classically
-we could build a theory and deal the finite-precision measurement
-in error analysis, it is necessary to embed the finite-precision measurement
-into the foundation of quantum theory.
-
-If a QIVPM is not \emph{a priori} known to be induced by a state,
-
-\noindent Thus, there is no state consistent with the QIVPM on all
-projectors~$P\in\events$, so Gleason's theorem cannot be extended
-to general QIVPMs.
-
-The first step toward a finite precision Born rule is to find a way
-of replacing the computed probability by an interval. This can be
-done by carefully picking a set of intervals and a rule to select
-the correct interval when intervals are overlapping. For example,
-consider the following collection of overlapping intervals:
-
-As a concrete example of Thm.~\ref{thm:Finite-precision-Born}, when
-$n=2$, two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
-and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$
-can induce two QIVPMs~$\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
-and $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$. Given any projector
-$P$ in the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
-and $\proj{2}$, $\events_{C}$, the interval-valued probability of
-the induced QIVPMs, $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
-and $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$,
-can be computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
-\begin{table}
-\caption{\label{tab:Compute-the-QIVPM}Compute $\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
-and $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$ based on $\mu_{\rho_{0}}^{\mathrm{B}}$
-and $\mu_{\rho_{1}}^{\mathrm{B}}$ on $\events_{C}$.}
-
-\begin{tabular}{ccccc}
-\toprule 
-\addlinespace
-$P$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
-
-Our framework allows us to generalize the above theorem to Born QIVPMs~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$:
-
-\noindent For example, Table~\ref{tab:Compute-the-QIVPM} shows that
-$\rho_{0}$ is consistent with $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$
-and $\rho_{1}$ is consistent with $\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
-both on every projectors in $\events_{C}$. Indeed, they are consistent
-with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
-by Thm.~\ref{thm:Finite-precision-Gleason}. This is true because
-the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
-$\frac{1}{24}$~\citep{544199}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-10-02 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$ becomes
-quantum probability measure~\citep{HOSTunpublished}, and Gleason's
-theorem claims that there is always a unique state consistent with
-$\bar{\mu}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-However, if we consider general QIVPMs mapping to an \emph{arbitrary}
-set of intervals, there is a QIVPM that no state can be consistent
-with it.
+quantum probability measure~\citep{HOSTunpublished}. In this situation,
+Gleason's theorem claims that there is always a unique state consistent
+with $\bar{\mu}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum},
+and this state can easily construct $\bar{\mu}$ according to the
+Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. However,
+if we consider general QIVPMs mapping to an \emph{arbitrary} set of
+intervals, there is a QIVPM that no state can be consistent with it.
 
@@
 results we get might contradict to each other, and exclude any possible
-state from being consistent with the measurement results. Although
-we will not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
-we will address this problem with a concrete family of intervals and
-QIVPMs. Consider the following intervals 
+state from being consistent with the measurement results. We will
+address this problem with a concrete family of intervals and QIVPMs,
+and leave for another time the general framework~\citep{HOSTunpublished}.
+Consider the following intervals 
 \begin{equation}
@@
 we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
-for any 1-dimensioal projector~$\proj{\psi}$. Since the maximum
+for any 1-dimensional projector~$\proj{\psi}$. Since the maximum
 length of the intervals in $\mathscr{I}_{n}$ is $1/n$, it is the
-upper bound of the difference between the Born quantum probabilities
-$\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
+upper bound of the difference $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
  This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$ by

### 2017-10-02 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 with $\bar{\mu}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum},
-and this state can easily construct $\bar{\mu}$ according to the
-Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. However,
+and this state can easily induce $\bar{\mu}$ according to the Born
+rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. However,
 if we consider general QIVPMs mapping to an \emph{arbitrary} set of

### 2017-10-03 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 for any 1-dimensional projector~$\proj{\psi}$. Since the maximum
-length of the intervals in $\mathscr{I}_{n}$ is $1/n$, it is the
-upper bound of the difference $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
+length of the intervals in $\mathscr{I}_{n}$ is $1/n$, it is also
+the upper bound of the difference $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
  This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$ by

### 2017-10-03 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 In this section, we want to shift our attention to consider states
-consistent with $\bar{\mu}$ on every event, $\coreBorn\left(\bar{\mu},\events\right)$,
+consistent with $\bar{\mu}$ on \emph{every} event, $\coreBorn\left(\bar{\mu},\events\right)$,
 so that these states could characterize $\bar{\mu}$ comprehensively.
@@
 means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
-their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
+their interiors~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
 
@@
 \begin{itemize}
-\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
-on their complements.
+\item Their complements~$\mathbb{1}-P_{0}$ and $\mathbb{1}-P_{1}$ are
+orthogonal so that we can apply Eq.~(\ref{eq:iota-add}) on their
+complements.
 \item One of them projects onto a subspace of what the other one projects

### 2017-10-04 prop_letter.tex
prop_letter.tex \section{Gleason} Discussing norm...

@@
 \newtheorem{assumption}{Assumption}
+\newtheorem{fact}{Fact}
 \theoremstyle{definition}
@@
 In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-there is always a state consistent with a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
+there is always a state consistent with a Born QIVPM $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
 because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$.
 Moreover, with respect to a notion of distance between two states~$\rho$
-and $\rho'$, $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
+and $\rho'$~\citep{544199}, 
+\begin{equation}
+\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\,,\label{eq:norm}
+\end{equation}
 the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
@@
 
-\yutsung{Compare the norm we used with other distances. For example,
-the trace distance defined in Sec.~9.2.1 in Nielsen and Chuang~\citep{544199}.}
-
 In the limiting case when the intervals are infinitely precise real
@@
 is unique. \end{thm}
+
+\yutsung{Following are the discussion and personal notes about our
+norm and other notation of norm and distance.}
+
+Nielsen and Chuang~\citep{544199} defined their norm~(\ref{eq:norm})
+in Appendix~6
+
+Although Nielsen and Chuang~\citep{544199} in Appendix 6 follow
+Simon {[}2{]} to prove theorems, it seems Simon didn't define the
+norm in his book {[}2{]}, and the definition used in Nielsen and Chuang
+{[}1{]} is clearly not what Simon would like to use... Figuring out
+what we should use...
+
+\begin{fact}Let $\sigma\left(\rho-\rho'\right)$ denote the set of
+eigenvalues of $\rho-\rho'$. Since $\rho$ and $\rho'$ are states,
+they are Hermitian~\citep{544199}, and so does $\rho-\rho'$. In
+this situation, $\left\Vert \rho-\rho'\right\Vert =\max\set{\left|\lambda\right|}{\lambda\in\sigma\left(\rho-\rho'\right)}$~\citep{544199}.\end{fact}
+
+\yutsung{End of discussion.}
 

### 2017-10-04 prop_letter.tex
prop_letter.tex \section{Gleason} Discussing norm...

@@
 Nielsen and Chuang~\citep{544199} defined their norm~(\ref{eq:norm})
-in Appendix~6
-
-Although Nielsen and Chuang~\citep{544199} in Appendix 6 follow
-Simon {[}2{]} to prove theorems, it seems Simon didn't define the
-norm in his book {[}2{]}, and the definition used in Nielsen and Chuang
-{[}1{]} is clearly not what Simon would like to use... Figuring out
-what we should use...
+in Appendix~6. While their Appendix~6 followed Simon~\citep{Simon2005}
+and Uhlmann~\citep{Uhlmann1977} to prove Lieb's theorem~\citep{Lieb_1973,544199,Simon2005},
+Simon~\citep{Simon2005} and Uhlmann~\citep{Uhlmann1977} didn't
+explicitly define the norm as in Eq.~(\ref{eq:norm}) although Simon
+used the same norm thoroughly in his book~\citep{Simon2005}. There
+are two possibilities:
+\begin{enumerate}
+\item Simon really used Eq.~(\ref{eq:norm}) to define his norm.\\
+If this is true, there must be some books cited by Simon, and defined
+the norm in the same way.
+\item The norm Simon used is different from Eq.~(\ref{eq:norm}), and Nielsen
+and Chuang defined this norm from nowhere in order to write a proof
+of Lieb's theorem.\\
+If this is true, Nielsen and Chuang might be the \emph{only} literature
+which used this norm. We might have no other literature to check the
+properties of this norm and other distances, and need to prove the
+properties of this norm by ourselves.
+\end{enumerate}
+In order to understand this norm and compare with others, the following
+are useful facts.
 

### 2017-10-04 prop_letter.tex
prop_letter.tex \section{Gleason} Discussing norm...

@@
 In order to understand this norm and compare with others, the following
-are useful facts.
-
-\begin{fact}Let $\sigma\left(\rho-\rho'\right)$ denote the set of
-eigenvalues of $\rho-\rho'$. Since $\rho$ and $\rho'$ are states,
-they are Hermitian~\citep{544199}, and so does $\rho-\rho'$. In
-this situation, $\left\Vert \rho-\rho'\right\Vert =\max\set{\left|\lambda\right|}{\lambda\in\sigma\left(\rho-\rho'\right)}$~\citep{544199}.\end{fact}
+are useful facts. Let $\sigma\left(\rho-\rho'\right)$ denote the
+set of eigenvalues of $\rho-\rho'$. Since $\rho$ and $\rho'$ are
+states, they are Hermitian~\citep{544199}, and so does $\rho-\rho'$.
+In this situation~\citep{544199}, 
+\begin{equation}
+\left\Vert \rho-\rho'\right\Vert =\max_{\lambda\in\sigma\left(\rho-\rho'\right)}\left|\lambda\right|
+\end{equation}
+which is just its spectral radius or spectral norm~\citep{GolubVanLoan1996,Foucart2012}
+\begin{equation}
+\max_{\left\Vert \ket{\psi}\right\Vert =1}\left\Vert \left(\rho-\rho'\right)\ket{\psi}\right\Vert \,.
+\end{equation}
+For their trace distance~\citep{544199}
+\begin{equation}
+D\left(\rho,\rho'\right)=\frac{1}{2}\Tr\left[\sqrt{\left(\rho-\rho'\right)^{2}}\right]=\frac{1}{2}\sum_{\lambda\in\sigma\left(\rho-\rho'\right)}\left|\lambda\right|\,,
+\end{equation}
+since it can also be represented as the eigenvalue of $\rho-\rho'$.
+It should not be hard to estimate their trace distance based on their
+norm.
 

### 2017-10-05 prop_letter.tex
prop_letter.tex \section{Gleason} Small modification after the meeting..

@@
 
+\begin{comment}
 As an example, consider a three-dimensional Hilbert space with orthonormal
@@
 first case and 2 in the second.
+\end{comment}
 
@@
 against the same event. More generally, this inverval would be interpreted as
-the Guassian width of a probability distribution, but for notational convenience
-we will continue in the following to write this as a definite interval.
+the Gaussian width of a probability distribution, but for notational
+convenience we will continue in the following to write this as a definite interval.
 \yutsung{Check the interpretation in the statistics literature~\citep{HuberRonchetti2009}!
@@
 
-\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
-a three-dimensional Hilbert space, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+\begin{thm}[Empty core for general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
+a three-dimensional Hilbert space, there exists a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
@@
 
-\begin{thm}[Finite-precision Extension of the Born rule]\label{thm:Finite-precision-Born}For
+\begin{thm}[A finite-precision Extension of the Born rule]\label{thm:Finite-precision-Born}For
 any state $\rho$ on a three-dimensional Hilbert space, a function~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}:\events\rightarrow\mathscr{I}_{n}$
@@
 
-\begin{thm}[Finite-precision Extension of Gleason's theorem for the
-Born QIVPMs]\label{thm:Finite-precision-Gleason}In a three-dimensional
+\begin{thm}[A finite-precision extension of weak Gleason's theorem
+for Born QIVPMs]\label{thm:Finite-precision-Gleason}In a three-dimensional
 Hilbert space, given any state~$\rho$, if a state $\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,

### 2017-10-06 prop_letter.tex
prop_letter.tex \section{Born} Added...

@@
 \usepackage{multirow}
+\DeclareUnicodeCharacter{0229}{\c{e}}
 
@@
 \lineskiplimit=1pt
+\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
+\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Born}
+
+Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
+postulates of the quantum probability measures first, and then introduce
+the Born rule which induces the quantum probability measures for each
+state. When we shift our attention to QIVPMs, we also want to construct
+a QIVPMs according to a simple rule. Since the ranges of the quantum
+probability measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$,
+respectively, if there is a function~$\iota$ mapping any number~$x\in\left[0,1\right]$
+to $\iota\left(x\right)\in\mathscr{I}$, then we can concatenate it
+with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+and get a QIVPM~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
+Although the idea is simple, $\iota$ needs to satisfy some conditions;
+otherwise, the concatenated function~$\bar{\mu}$ may not be a QIVPM.
+
+\begin{thm}If $\iota\circ\mu:\events\rightarrow\mathscr{I}$ is always
+a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+in any Hilbert space $\Hilb$, then $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+must subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
+\begin{eqnarray}
+ &  & \iota(0)=\imposs\,,\\
+ &  & \iota(1)=\necess\,,\\
+ &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
+\end{eqnarray}
+\end{subequations} and satisfying for any three numbers~$x_{0}$,
+$x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
+implies
+\begin{equation}
+\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
+\end{equation}
+\end{thm}
+
+If the first three constraints, Eqs.~(\ref{eq:iota-constraints}),
+fails, it is easy to see that the concatenated function~$\iota\circ\mu$
+may not be a QIVPM. Suppose $\iota$ fails to satisfy Eq.~(\ref{eq:iota-Inclusion}),
+consider the state
+\begin{equation}
+\begin{aligned}\rho= & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
+ & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
+\end{aligned}
+\end{equation}
+Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}\left(P\right)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
+Then,
+\begin{equation}
+\begin{aligned} & \bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
+= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
+= & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
+\nsubseteq & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\\
+= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\\
+= & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
+\end{aligned}
+\end{equation}
+Therefore, $\iota$ must satisfy Eqs.~(\ref{eq:iota-constraints})
+and Eq.~(\ref{eq:iota-Inclusion}) to guarantee $\iota\circ\mu$
+is always a QIVPM.
+
+Although a interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+may look exotic, its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$
+are just usual functions from a unit interval to another unit interval.
+Eq.~(\ref{eq:iota-Inclusion}) then implies that $\iotal$ is Wright-convex,
+i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
+and $\iotar$ is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
+Notice that a Wright-convex function is midpoint-convex or Jensen-convex,
+i.e., 
+\begin{equation}
+\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,,
+\end{equation}
+and a midpoint-convex function is continuous on an open interval if
+we cannot use the Axiom of Choices~\citep{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
+Therefore, the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
+or contains infinitely many intervals.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Gleason}

### 2017-10-06 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 
+\yutsung{Notice that the use of quantum is minumalized in this section.
+In another word, the results of this section should apply to both
+quantum and classical case.}
+
 Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
@@
 probability measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$,
-respectively, if there is a function~$\iota$ mapping any number~$x\in\left[0,1\right]$
+respectively, if there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
 to $\iota\left(x\right)\in\mathscr{I}$, then we can concatenate it
@@
 and get a QIVPM~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
-Although the idea is simple, $\iota$ needs to satisfy some conditions;
-otherwise, the concatenated function~$\bar{\mu}$ may not be a QIVPM.
+Although their concatenation $\iota\circ\mu$ is always a function
+from $\events$ to $\mathscr{I}$, to guarantee $\iota\circ\mu$ is
+a QIVPM, $\iota$ needs to satisfy some extra conditions.
 
@@
 
-If the first three constraints, Eqs.~(\ref{eq:iota-constraints}),
-fails, it is easy to see that the concatenated function~$\iota\circ\mu$
+If $\iota$ fails to satisfy the first three constraints, Eqs.~(\ref{eq:iota-constraints}),
+it is easy to see that the concatenated function~$\iota\circ\mu$
 may not be a QIVPM. Suppose $\iota$ fails to satisfy Eq.~(\ref{eq:iota-Inclusion}),

### 2017-10-07 prop_letter.tex
prop.bib @Article{Sierpinski1920} Updated to fix a babel error...
prop_letter.tex Using phantom so that spacing are induced by semantic...
prop_letter.tex \section{Born} Updating...

@@
 \usepackage[utf8]{inputenc}
-\usepackage{babel}
+\usepackage[french,main=english]{babel}
 \usepackage{amsthm}
@@
 \newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
-\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
+\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{\vphantom{|}}\middle|\mathrel{\vphantom{|}}{#2}\right\} }}
 \newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
@@
 may not be a QIVPM. Suppose $\iota$ fails to satisfy Eq.~(\ref{eq:iota-Inclusion}),
-consider the state
-\begin{equation}
-\begin{aligned}\rho= & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
- & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
+i.e., there exists three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but 
+\begin{equation}
+\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion-not}
+\end{equation}
+Consider the state
+\begin{equation}
+\begin{aligned}\rho=\vphantom{x_{0}} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
+ & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\textrm{ .}
 \end{aligned}
 \end{equation}
-Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}\left(P\right)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
-Then,
-\begin{equation}
-\begin{aligned} & \bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
-= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
-= & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
-\nsubseteq & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\\
-= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\\
-= & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
+Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$. Then,
+the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}$
+fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+
+\begin{eqnarray}
+ &  & \begin{aligned} & \mathrel{\hphantom{=}}\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\end{aligned}
+\nonumber \\
+ &  & \begin{aligned} & =\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
+ & \nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)
 \end{aligned}
-\end{equation}
-Therefore, $\iota$ must satisfy Eqs.~(\ref{eq:iota-constraints})
+\\
+ &  & \begin{aligned} & =\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\textrm{ ,}\end{aligned}
+\nonumber 
+\end{eqnarray}
+and cannot be a QIVPM. Therefore, $\iota$ must satisfy Eqs.~(\ref{eq:iota-constraints})
 and Eq.~(\ref{eq:iota-Inclusion}) to guarantee $\iota\circ\mu$

### 2017-10-08 prop_letter.tex
prop_letter.tex Simplify the TeX code...
prop_letter.tex \section{Born} Updating...

@@
 \newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
-\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{\vphantom{|}}\middle|\mathrel{\vphantom{|}}{#2}\right\} }}
+\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
 \newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
@@
 In another word, the results of this section should apply to both
-quantum and classical case.}
+quantum and classical IVPMs.}
 
@@
 with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-and get a QIVPM~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
-Although their concatenation $\iota\circ\mu$ is always a function
-from $\events$ to $\mathscr{I}$, to guarantee $\iota\circ\mu$ is
-a QIVPM, $\iota$ needs to satisfy some extra conditions.
-
-\begin{thm}If $\iota\circ\mu:\events\rightarrow\mathscr{I}$ is always
-a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-in any Hilbert space $\Hilb$, then $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-must subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
-\begin{eqnarray}
- &  & \iota(0)=\imposs\,,\\
- &  & \iota(1)=\necess\,,\\
- &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
-\end{eqnarray}
-\end{subequations} and satisfying for any three numbers~$x_{0}$,
-$x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
-implies
-\begin{equation}
-\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
-\end{equation}
-\end{thm}
-
-If $\iota$ fails to satisfy the first three constraints, Eqs.~(\ref{eq:iota-constraints}),
-it is easy to see that the concatenated function~$\iota\circ\mu$
-may not be a QIVPM. Suppose $\iota$ fails to satisfy Eq.~(\ref{eq:iota-Inclusion}),
-i.e., there exists three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
-such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but 
+and get a function~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
+Although $\bar{\mu}$ has the same the domain and range, $\bar{\mu}$
+may or may not be a QIVPM. For example, the following theorem highlight
+the situation when $\bar{\mu}$ cannot be a QIVPM.
+
+\begin{thm}If there exists three numbers~$x_{0}$, $x_{1}$, and
+$x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
+but 
 \begin{equation}
@@
 \end{equation}
+Then, there is a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+such that $\iota\circ\mu$ is not a QIVPM, where $\circ$ is the function
+concatenation.\end{thm}
+
 Consider the state
 \begin{equation}
-\begin{aligned}\rho=\vphantom{x_{0}} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
+\begin{aligned}\rho={} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
  & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\textrm{ .}
@@
 \end{equation}
-Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$. Then,
-the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}$
+Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}$
 fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-
 \begin{eqnarray}
@@
 \end{eqnarray}
-and cannot be a QIVPM. Therefore, $\iota$ must satisfy Eqs.~(\ref{eq:iota-constraints})
-and Eq.~(\ref{eq:iota-Inclusion}) to guarantee $\iota\circ\mu$
-is always a QIVPM.
+and cannot be a QIVPM.
+
+In other words, even if $\iota\circ\mu$ has the same domain and range
+as a QIVPM, we may need to verify whether $\iota\circ\mu$ is a QIVPM
+individually. For example, consider the following easy example. In
+the four-dimensional Hilbert space, 
+\begin{equation}
+\iota\left(x\right)=\begin{cases}
+\imposs & \textrm{, if }x=0\textrm{ ;}\\
+\left[0,\tfrac{1}{2}\right] & \textrm{, if }x\in\left(0,\tfrac{1}{4}\right]\textrm{ ;}\\
+\unknown & \textrm{, if }x\in\left(\tfrac{1}{4},\tfrac{3}{4}\right)\textrm{ ;}\\
+\left[\tfrac{1}{2},1\right] & \textrm{, if }x\in\left[\tfrac{3}{4},1\right)\textrm{ ;}\\
+\necess & \textrm{, if }x=1\textrm{ .}
+\end{cases}
+\end{equation}
+and $\rho=\left(\proj{0}+\proj{1}+\proj{2}+\proj{3}\right)/4$ induce
+a QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ which is a
+non-trivial fact~\citep{HOSTunpublished}. In order to verify whether
+$\iota\circ\mu$ is a QIVPM easier, we want to impose some conditions
+on $\iota$. Notice that our counterexamples are in a four-dimensional
+Hilbert space, the conditions for $\iota$ for a Hilbert space of
+dimension~$d\le3$ is not as strict as the general conditions.
+
+\begin{thm}In a Hilbert space of dimension~$d\le3$, if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
+\begin{eqnarray}
+ &  & \iota(0)=\imposs\,,\\
+ &  & \iota(1)=\necess\,,\\
+ &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
+\end{eqnarray}
+\end{subequations}and satisfying for any three numbers~$x_{0}$
+and $x_{1}\in\left[0,1\right]$, $x_{0}+x_{1}\in\left[0,1\right]$
+implies
+\begin{equation}
+\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\textrm{ .}\label{eq:iota-add}
+\end{equation}
+Then, $\iota\circ\mu:\events\rightarrow\mathscr{I}$ is always a QIVPM
+for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.\end{thm}
+
+Although their concatenation $\iota\circ\mu$ is always a function
+from $\events$ to $\mathscr{I}$, to guarantee $\iota\circ\mu$ is
+a QIVPM, $\iota$ needs to satisfy some extra conditions.
+
+\begin{thm}If $\iota\circ\mu:\events\rightarrow\mathscr{I}$ is always
+a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+in any Hilbert space $\Hilb$, then $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+must subject to the following constraints:\begin{subequations}
+\begin{eqnarray}
+ &  & \iota(0)=\imposs\,,\\
+ &  & \iota(1)=\necess\,,\\
+ &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
+\end{eqnarray}
+\end{subequations} and satisfying for any three numbers~$x_{0}$,
+$x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
+implies
+\begin{equation}
+\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
+\end{equation}
+\end{thm}
 

### 2017-10-08 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-and get a function~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
-Although $\bar{\mu}$ has the same the domain and range, $\bar{\mu}$
-may or may not be a QIVPM. For example, the following theorem highlight
-the situation when $\bar{\mu}$ cannot be a QIVPM.
+and get a $\mathscr{I}$-valued function~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
+Although $\bar{\mu}$ and QIVPMs have the same the domain and range,
+$\bar{\mu}$ is not necessary a QIVPM. For example, the following
+theorem highlight a situation where $\bar{\mu}$ cannot be a QIVPM.
 

### 2017-10-08 prop_iop.tex
prop_letter.tex \section{Born} Updating...

@@
+%% LyX 2.2.3 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
 \documentclass[12pt]{iopart}
+\usepackage[T1,T2A]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{array}
+\usepackage{verbatim}
+\usepackage{booktabs}
+\usepackage{mathrsfs}
+\usepackage{enumitem}
+\usepackage{multirow}
+\usepackage{amstext}
+\usepackage{amsthm}
+\usepackage{amssymb}
+\usepackage{graphicx}
+
+\makeatletter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% Because html converters don't know tabularnewline
+\providecommand{\tabularnewline}{\\}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
+\usepackage{iopams}
+\usepackage{setstack}
+ \newlist{casenv}{enumerate}{4}
+ \setlist[casenv]{leftmargin=*,align=left,widest={iiii}}
+ \setlist[casenv,1]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
+ \setlist[casenv,2]{label={{\itshape\ \casename} \roman*.},ref=\roman*}
+ \setlist[casenv,3]{label={{\itshape\ \casename\ \alph*.}},ref=\alph*}
+ \setlist[casenv,4]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
 \usepackage[ backend=biber]{biblatex}
@@
 \ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
+\DeclareUnicodeCharacter{0229}{\c{e}}
+\usepackage{mmap}
 \usepackage{fullpage}
-\usepackage{cmap}
-\usepackage[T1,T2A]{fontenc}
-\usepackage[utf8]{inputenc}
-\DeclareUnicodeCharacter{0229}{\c{e}}
-\usepackage{amssymb}
 \usepackage{amsthm}
@@
 \usepackage{setstack}
-\usepackage{enumitem}
-\usepackage{amstext}
-\usepackage{array}
-\usepackage{booktabs}
-\usepackage{multirow}
 
@@
 \newtheorem{claim}[thm]{Claim}
-
-\newlist{casenv}{enumerate}{4}
-\setlist[casenv]{leftmargin=*,align=left,widest={iiii}}
-\setlist[casenv,1]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
-\setlist[casenv,2]{label={{\itshape\ \casename} \roman*.},ref=\roman*}
-\setlist[casenv,3]{label={{\itshape\ \casename\ \alph*.}},ref=\alph*}
-\setlist[casenv,4]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
-\providecommand{\casename}{Case}
 
@@
 \newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}
+\renewcommand{\maketitle}{}
 \newcommand{\tfrac}[2]{\textstyle\frac{#1}{#2}}
 
+\makeatother
+
+ \providecommand{\casename}{Case}
+
 \begin{document}
+
 \title{Quantum Interval-Valued Probability: Measurement and Probability}
 
-\author{Andrew J Hanson$^{1}$, Gerardo Ortiz$^{2}$,
-Amr Sabry$^{1}$ and Yu-Tsung Tai$^{3,1}$}
-\address{$^{1}$ School of Informatics and Computing, Indiana
-University, Bloomington, IN 47405, USA}
+\author{Andrew J Hanson$^{1}$, Gerardo Ortiz$^{2}$, Amr Sabry$^{1}$ and
+Yu-Tsung Tai$^{3,1}$}
+
+\address{$^{1}$ School of Informatics and Computing, Indiana University,
+Bloomington, IN 47405, USA}
+
 \address{$^{2}$ Department of Physics, Indiana University, Bloomington, IN
 47405, USA}
+
 \address{$^{3}$ Department of Mathematics, Indiana University, Bloomington,
 IN 47405, USA}
+
 \ead{ortizg@indiana.edu}
@@
 \end{abstract}
+
 \pacs{03.65.-w, 03.65.Ta, 02.40.Dr, 02.50.Cw, 02.50.Le}
-\noindent{\it Keywords\/}: {Finite precision measurement, the Born rule, Gleason's theorem, interval-valued
-probability, discrete quantum theory}
+
+\noindent{\it Keywords\/}: {\noindent Finite precision measurement, the Born rule, Gleason's
+theorem, interval-valued probability, discrete quantum theory}
 
@@
 
+\maketitle
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
@@
 Textbook quantum mechanics asserts that, given a quantum spin system
-described by the wave function
-$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
-and given the observable
-$S_z =
-\frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
+described by the wave function $\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
+and given the observable $S_{z}=\frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
 then the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$
-(with post-measurement state $\fket{\ps\frac{1}{2}}$) is
-$\frac{\pi}{4}$ and the probability of observing the eigenvalue
-$\minus\frac{\hbar}{2}$ (with post-measurement state
-$\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
-frequency interpretation of probability, the above assertion implies
-that when performing a very large number of experiments on quantum
-systems described by wave function $\ket{\psi}$, a fraction
+(with post-measurement state $\fket{\ps\frac{1}{2}}$) is $\frac{\pi}{4}$
+and the probability of observing the eigenvalue $\minus\frac{\hbar}{2}$
+(with post-measurement state $\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$.
+According to the frequency interpretation of probability, the above
+assertion implies that when performing a very large number of experiments
+on quantum systems described by wave function $\ket{\psi}$, a fraction
 $\frac{\pi}{4}$ of the experiments will result in the observation
-$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
-result in the observation $\minus\frac{\hbar}{2}$.
+$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$
+will result in the observation $\minus\frac{\hbar}{2}$.
 
@@
 fuzzier: (i) we cannot \emph{exactly} prepare the state $\ket{\psi}$;
-(ii) we cannot build a measurement apparatus corresponding
-\emph{exactly} to observable $S_z$; and (iii) we cannot prepare
-\emph{exact} replicas of any state. In other words, we can only
-perform a limited number of experiments on quantum systems closely
-related to wave function $\ket{\psi}$ and using an apparatus that
-closely approximates observable $S_z$. Given any fixed resources,
-these experiments will \emph{not} result in the \emph{exact} fraction
-$\frac{\pi}{4}$ of observations $\ps\frac{\hbar}{2}$ and
-$1-\frac{\pi}{4}$ of observations $\minus\frac{\hbar}{2}$. In fact,
-these experiments can be viewed as a method (algorithm) to calculate
-the value $\pi$ and it is known that the state of the art algorithms
-for computing the $n$th binary digit of~$\pi$ require on the order of
-$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
+(ii) we cannot build a measurement apparatus corresponding \emph{exactly}
+to observable $S_{z}$; and (iii) we cannot prepare \emph{exact} replicas
+of any state. In other words, we can only perform a limited number
+of experiments on quantum systems closely related to wave function
+$\ket{\psi}$ and using an apparatus that closely approximates observable
+$S_{z}$. Given any fixed resources, these experiments will \emph{not}
+result in the \emph{exact} fraction $\frac{\pi}{4}$ of observations
+$\ps\frac{\hbar}{2}$ and $1-\frac{\pi}{4}$ of observations $\minus\frac{\hbar}{2}$.
+In fact, these experiments can be viewed as a method (algorithm) to
+calculate the value $\pi$ and it is known that the state of the art
+algorithms for computing the $n$th binary digit of~$\pi$ require
+on the order of $O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
 operations~\cite{journals/moc/BaileyBP97}. In other words, calculating
@@
 All of this is well-known and holds in both the classical and quantum
-worlds. In the classical world, these observations are believed to be
-well-understood approximations to an idealized independent reality
+worlds. In the classical world, these observations are believed to
+be well-understood approximations to an idealized independent reality
 that can continuously approached with more and more resources. The
-question in the quantum world is more subtle; it is not evident at all
-that this resource-aware perspective does not alter the very
-foundations of quantum mechanics. Indeed taking such resource bounds
-into consideration is what founded computer science as a discipline
-and has become crucial for understanding the very nature of
-computation. Following Feynman~\cite{Feynman1982Simulating},
-Landauer~\cite{Landauer1996188}, and others, one might argue that this
-resource-bounded perspective is also crucial for understanding the
-very nature of physical processes.
+question in the quantum world is more subtle; it is not evident at
+all that this resource-aware perspective does not alter the very foundations
+of quantum mechanics. Indeed taking such resource bounds into consideration
+is what founded computer science as a discipline and has become crucial
+for understanding the very nature of computation. Following Feynman~\cite{Feynman1982Simulating},
+Landauer~\cite{Landauer1996188}, and others, one might argue that
+this resource-bounded perspective is also crucial for understanding
+the very nature of physical processes.
 
 In previous work, we analyzed the wave function description of quantum
-systems from a resource-bounded perspective. Technically, instead of
-postulating that quantum states are rays in a Hilbert space, i.e., we
-instead used special finite fields whose size reflected the available
-resources. \ldots
-
-\newpage
+systems from a resource-bounded perspective. Technically, instead
+of postulating that quantum states are rays in a Hilbert space, i.e.,
+we instead used special finite fields whose size reflected the available
+resources. \ldots{}
+
+\newpage{}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Classical Probability}
@@
 A \emph{probability space} specifies the necessary conditions for
-reasoning coherently about collections of uncertain
-events~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}.  We
-review the conventional presentation of probability spaces and then
-discuss the computational resources needed to estimate probabilities.
+reasoning coherently about collections of uncertain events~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}.
+We review the conventional presentation of probability spaces and
+then discuss the computational resources needed to estimate probabilities.
 
 %%%
+
 \subsection{Classical Probability Spaces}
@@
 \begin{definition}[Probability Measure]\label{def:ClassicalProbabilitySpace}
-  Given the set of events $\events$, a \emph{probability measure} is a
-  function $\pmeas:\events\rightarrow[0,1]$ such that:
+Given the set of events $\events$, a \emph{probability measure} is
+a function $\pmeas:\events\rightarrow[0,1]$ such that: 
 \begin{itemize}
@@
 \item $\pmeas(\Omega)=1$, 
-\item for every event $E$,
-  $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$ where
-  $\Omega\backslash E$ is the complement event of $E$, and
-\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of
-  pairwise disjoint events,
-  $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$.
+\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
+where $\Omega\backslash E$ is the complement event of $E$, and 
+\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
+disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
 \end{itemize}
-\end{definition}
-\noindent There is some redundancy in the definition that will be useful when
-moving to quantum probability spaces.
-
-\begin{example}[Two-coins experiment]\label{ex1} Consider an
-  experiment that tosses two coins. We have four possible outcomes
-  that constitute the sample space $\Omega=\{HH,HT,TH,TT\}$. There are
-  16 total events including the event $\{HH,HT\}$ that the first coin
-  lands heads up, the event $\{HT,TH\}$ that the two coins land on
-  opposite sides, and the event $\{HT,TH,TT\}$ that at least one coin
-  lands tails up. Here is a possible probability measure for these
+\end{definition} There is some redundancy in the definition that
+will be useful when moving to quantum probability spaces.
+
+\noindent \begin{example}[Two-coins experiment]\label{ex1} Consider
+an experiment that tosses two coins. We have four possible outcomes
+that constitute the sample space $\Omega=\{HH,HT,TH,TT\}$. There
+are 16 total events including the event $\{HH,HT\}$ that the first
+coin lands heads up, the event $\{HT,TH\}$ that the two coins land
+on opposite sides, and the event $\{HT,TH,TT\}$ that at least one
+coin lands tails up. Here is a possible probability measure for these
 events: 
@@
 
-\noindent It is useful to think that this probability measure is
-completely determined by the ``reality'' of the two coins in question
-and their characteristics, in the sense that each pair of coins
-induces a measure, and each measure must correspond to some pair of
-coins. The measure above would be induced by two particular coins such
-that the first coin is twice as likely to land tails up than heads up
-and the second coin is double-headed.
+\noindent It is useful to think that this probability measure is completely
+determined by the ``reality'' of the two coins in question and their
+characteristics, in the sense that each pair of coins induces a measure,
+and each measure must correspond to some pair of coins. The measure
+above would be induced by two particular coins such that the first
+coin is twice as likely to land tails up than heads up and the second
+coin is double-headed.
 
 %%%%%
+
 \subsection{Measuring Probabilities: Buffon's Needle Problem\label{subsec:Measuring-Probabilities:-Buffon}}
@@
 the reliance of the definition of probability space on the uncountable
-and uncomputable real
-interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
+and uncomputable real interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
 This interval includes numbers like $0.h_{1}h_{2}h_{3}\ldots$ where
-$h_{i}$ is 1 or 0 depending on whether Turing machine
-$\mathit{TM}_{i}$ halts or not. Such numbers cannot be computed. This
-interval also includes numbers like $\pi / 4$ which can only be
-computed with increasingly large resources as the precision
-increases. Therefore, in a resource-aware computational or
-experimental setting, it is more appropriate to consider probability
-measures that map events to a set of elements computable with a fixed
-set of resources. We expand on this observation in the next section
-and then recall its formalization using interval-valued probability
-measures~\cite{Weichselberger2000,JamisonLodwick2004}.
-
-In the previous example, we assumed the probability~$\pmeas(E)$ of
-each event~$E$ is known a priori. In reality, although each event is
-assumed to have a probability, the exact value of $\pmeas(E)$ may not
-be known. According to the \emph{frequency interpretation of
-  probability} (which we will revisit when moving to the quantum
-case)~\cite{Venn1876,Hajek2012}, 
-to determine the probability of an event, we run $M$
-independent trials which gives us an approximation of the (assumed)
-``true'' or ``real'' probability. Let $x_{i}$ be 1 or 0 depending on
-whether the event~$E$ occurs in the $i$-th trial or not, then
-$\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
-the relative frequency~$\sum_{i=1}^{M}x_{i} / M$ with the
-probability converging to one as $M$ goes to infinity, i.e.,
-\begin{equation}
-\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M} x_{i}\right|<\epsilon\right)=1\,.
+$h_{i}$ is 1 or 0 depending on whether Turing machine $\mathit{TM}_{i}$
+halts or not. Such numbers cannot be computed. This interval also
+includes numbers like $\pi/4$ which can only be computed with increasingly
+large resources as the precision increases. Therefore, in a resource-aware
+computational or experimental setting, it is more appropriate to consider
+probability measures that map events to a set of elements computable
+with a fixed set of resources. We expand on this observation in the
+next section and then recall its formalization using interval-valued
+probability measures~\cite{Weichselberger2000,JamisonLodwick2004}.
+
+In the previous example, we assumed the probability~$\pmeas(E)$
+of each event~$E$ is known a priori. In reality, although each event
+is assumed to have a probability, the exact value of $\pmeas(E)$
+may not be known. According to the \emph{frequency interpretation
+of probability} (which we will revisit when moving to the quantum
+case)~\cite{Venn1876,Hajek2012}, to determine the probability of
+an event, we run $M$ independent trials which gives us an approximation
+of the (assumed) ``true'' or ``real'' probability. Let $x_{i}$
+be 1 or 0 depending on whether the event~$E$ occurs in the $i$-th
+trial or not, then $\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$
+by the relative frequency~$\sum_{i=1}^{M}x_{i}/M$ with the probability
+converging to one as $M$ goes to infinity, i.e., 
+\begin{equation}
+\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M}x_{i}\right|<\epsilon\right)=1\,.
 \end{equation}
@@
 $\ell$ onto a floor made of equally spaced parallel lines a distance
-$h$ apart, where $\ell<h$. It is a known fact that the probability of
-the needle crossing a line is
-$2\ell/\left(\pi h\right)$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
+$h$ apart, where $\ell<h$. It is a known fact that the probability
+of the needle crossing a line is $2\ell/\left(\pi h\right)$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
 Consider an experimental setup consisting of a collection of $M$
 identical needles of length $\ell$. We throw the $M$ needles one
-needle at a time, and observe the number $M_c$ of needles that cross a
-line, thus estimating the probability of a needle crossing a line to
-be $M_c/M$. In an actual experiment with $500$ needles and the
-ratio $\ell/h=0.75$~\cite{Hall1873}, it was found that $236$
-crossed a line so the relative frequency is $0.472$ whereas the
-idealized mathematical probability is $0.4774\ldots$.  In a larger
-experiment with $5000$ needles and the ratio
-$\ell/h=0.8$~\cite{Uspensky1937}, the relative frequency was
-calculated to be $0.5064$ whereas the idealized mathematical
-probability is $0.5092\ldots$. We see that the observed probability
-approaches $2\ell/\left(\pi h\right)$ but only if \emph{larger and larger
-  resources} are expended. These resource considerations suggest that
-it is possible to replace the real interval $[0,1]$ with rational
-numbers up to a certain precision related to the particular experiment
-in question. There is clearly a connection between the number of
-needles and the achievable precision: in the hypothetical experiment
-with 3 needles, it is not sensible to retain 100 digits in the
-expansion of $2\ell/\left(\pi h\right)$.
+needle at a time, and observe the number $M_{c}$ of needles that
+cross a line, thus estimating the probability of a needle crossing
+a line to be $M_{c}/M$. In an actual experiment with $500$ needles
+and the ratio $\ell/h=0.75$~\cite{Hall1873}, it was found that
+$236$ crossed a line so the relative frequency is $0.472$ whereas
+the idealized mathematical probability is $0.4774\ldots$. In a larger
+experiment with $5000$ needles and the ratio $\ell/h=0.8$~\cite{Uspensky1937},
+the relative frequency was calculated to be $0.5064$ whereas the
+idealized mathematical probability is $0.5092\ldots$. We see that
+the observed probability approaches $2\ell/\left(\pi h\right)$ but
+only if \emph{larger and larger resources} are expended. These resource
+considerations suggest that it is possible to replace the real interval
+$[0,1]$ with rational numbers up to a certain precision related to
+the particular experiment in question. There is clearly a connection
+between the number of needles and the achievable precision: in the
+hypothetical experiment with 3 needles, it is not sensible to retain
+100 digits in the expansion of $2\ell/\left(\pi h\right)$.
 
@@
 power in the experiment. We are assuming that we can always determine
-with certainty whether a needle is crossing a line. But ``lines'' on
-the the floor have thickness, their distance apart is not exactly $h$,
-and the needles' lengths are not all absolutely equal to $\ell$.
+with certainty whether a needle is crossing a line. But ``lines''
+on the the floor have thickness, their distance apart is not exactly
+$h$, and the needles' lengths are not all absolutely equal to $\ell$.
 These perturbations make the events ``fuzzy.'' Thus, in an experiment
 with limited resources, it is not possible to talk about the idealized
-event that exactly $M_c$ needles cross lines as this would require the
-most expensive needles built to the most precise accuracy, laser
-precision for drawing lines on the floor, and the most powerful
-microscopes to determine if a needle does cross a line. Instead we
-might talk about the event that $M_c-\delta$ needles evidently cross
-lines and $M_c+\delta'$ needles plausibly cross lines where $\delta$ and
-$\delta'$ are resource-dependent approximations. This fuzzy notion of
-events leads to probabilities being only calculable within intervals
-of confidence reflecting the certainty of events and their
-plausibility. This is indeed consistent with published experiments: in
-an experiment with $3204$ needles and the ratio
-$\ell/h=0.6$~\cite{DeMorgan1872}, $1213$ needles clearly
-crossed a line and $11$ needles were close enough to plausibly be
-considered as crossing the line: we would express the probability in
-this case as the interval
-$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we
-are certain that the event has probability at least
+event that exactly $M_{c}$ needles cross lines as this would require
+the most expensive needles built to the most precise accuracy, laser
+precision for drawing lines on the floor, and the most powerful microscopes
+to determine if a needle does cross a line. Instead we might talk
+about the event that $M_{c}-\delta$ needles evidently cross lines
+and $M_{c}+\delta'$ needles plausibly cross lines where $\delta$
+and $\delta'$ are resource-dependent approximations. This fuzzy notion
+of events leads to probabilities being only calculable within intervals
+of confidence reflecting the certainty of events and their plausibility.
+This is indeed consistent with published experiments: in an experiment
+with $3204$ needles and the ratio $\ell/h=0.6$~\cite{DeMorgan1872},
+$1213$ needles clearly crossed a line and $11$ needles were close
+enough to plausibly be considered as crossing the line: we would express
+the probability in this case as the interval $\left[\frac{1213}{3204},\frac{1224}{3204}\right]$
+expressing that we are certain that the event has probability at least
 $\frac{1213}{3204}$ but it is possible that it would have probability
@@
 of probabilities requires all probabilities to be \emph{coherent}
-(e.g., the probability of the union of two disjoint events is the sum
-of their probabilities). But given limited resources, the calculation
-of a probability measure can only be approximate and hence the
-probabilities cannot be absolutely guaranteed to be coherent in the
-ideal sense.
+(e.g., the probability of the union of two disjoint events is the
+sum of their probabilities). But given limited resources, the calculation
+of a probability measure can only be approximate and hence the probabilities
+cannot be absolutely guaranteed to be coherent in the ideal sense.
 
 %%%%%
+
 \subsection{Classical Interval-Valued Probability Measures}
@@
 \end{itemize}
-
-\begin{example}[Two-coin experiment with interval probability]
-\label{ex3} We split the unit interval $[0,1]$ in the following
-four closed sub-intervals: $[0,0]$ which we call \imposs, $[0,\frac{1}{2}]$
-which we call \unlikely, $[\frac{1}{2},1]$ which we call \likely,
-and $[1,1]$ which we call \necess. Using these new values, we can
-modify the probability measure of example~\ref{ex1} by mapping each
-numeric value to the smallest sub-interval containing it to get the
-following: 
+\begin{example}[Two-coin experiment with interval probability]\label{ex3}
+We split the unit interval $[0,1]$ in the following four closed sub-intervals:
+$[0,0]$ which we call \imposs, $[0,\frac{1}{2}]$ which we call
+\unlikely, $[\frac{1}{2},1]$ which we call \likely, and $[1,1]$
+which we call \necess. Using these new values, we can modify the
+probability measure of example~\ref{ex1} by mapping each numeric
+value to the smallest sub-interval containing it to get the following:
 \begin{equation}
@@
 =& \imposs+\unlikely+\imposs+\likely\\
-=& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=
-\left[\frac{1}{2},\frac{3}{2}\right]\,.
+=& \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]= \left[\frac{1}{2},\frac{3}{2}\right]\,. 
 }\end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Quantum Probability}
 
-The mathematical framework of classical probability above assumes that
-there exists a predetermined set of events that are independent of the
-particular experiment --- classical physics is
-non-contextual~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}. 
-However, even in classical situations, the structure
-of the event space is often only partially known and the precise
-dependence of two events on each other cannot, a priori, be determined
-with certainty. In the quantum framework, this partial knowledge is
-compounded by the fact that there exist non-commuting events which
-cannot happen simultaneously. To accommodate these more complex
-situations, conventional approaches to quantum probability abandon the
-sample space~$\Omega$ and reason directly about events which are
-generalized from plain sets to projection operators. A quantum
-probability space therefore consists of just two components: a set of
-events $\qevents$ often formalized as projection operators and a
-probability measure $\mu:\qevents\rightarrow[0,1]$ formalized using
-the Born rule~\cite{Born1983,Mermin2007,Jaeger2007}.
+The mathematical framework of classical probability above assumes
+that there exists a predetermined set of events that are independent
+of the particular experiment — classical physics is non-contextual~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
+However, even in classical situations, the structure of the event
+space is often only partially known and the precise dependence of
+two events on each other cannot, a priori, be determined with certainty.
+In the quantum framework, this partial knowledge is compounded by
+the fact that there exist non-commuting events which cannot happen
+simultaneously. To accommodate these more complex situations, conventional
+approaches to quantum probability abandon the sample space~$\Omega$
+and reason directly about events which are generalized from plain
+sets to projection operators. A quantum probability space therefore
+consists of just two components: a set of events $\qevents$ often
+formalized as projection operators and a probability measure $\mu:\qevents\rightarrow[0,1]$
+formalized using the Born rule~\cite{Born1983,Mermin2007,Jaeger2007}.
 
 %%%%%
+
 \subsection{Quantum Events}
 
-\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
-  \label{def:Projection} Given a Hilbert space $\Hilb$, an event (an
-  experimental proposition~\cite{BirkhoffVonNeumann1936}, a
-  question~\cite{10.2307/2308516,Abramsky2012},
-  or an elementary quantum test~\cite{peres1995quantum}) is represented
-  as a (self-adjoint or orthogonal~\cite {Griffiths2003,Maassen2010})
-  projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace
-  of $\Hilb$. The following define projections and list some of their properties:
+\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]\label{def:Projection}
+Given a Hilbert space $\Hilb$, an event (an experimental proposition~\cite{BirkhoffVonNeumann1936},
+a question~\cite{10.2307/2308516,Abramsky2012}, or an elementary
+quantum test~\cite{peres1995quantum}) is represented as a (self-adjoint
+or orthogonal~\cite{Griffiths2003,Maassen2010}) projection operator
+$P:\Hilb\rightarrow\Hilb$ onto a linear subspace of $\Hilb$. The
+following define projections and list some of their properties: 
 \begin{itemize}
@@
 post-measurement state~\cite{peres1995quantum,Mermin2007,Jaeger2007}.
-  For example, the event $\proj{0}$ indicates
-  that the post-measurement state will be $\ket{0}$; the probability
-  of such an event depends on the current state; the event $\proj{1}$
-  indicates that the post-measurement state will be $\ket{1}$; the
-  event $\proj{\ps}$ where
-  $\ket{\ps}=\left(\ket{0}+\ket{1}\right) / \sqrt{2}$ indicates that the
-  post-measurement state will be $\ket{\ps}$; the event
-  $\mathbb{1}=\proj{0}+\proj{1}$ indicates that the post-measurement
-  state will be a linear combination of $\ket{0}$ and $\ket{1}$ and is
-  clearly certain; finally the empty event $\mathbb{0}$ states that
-  the post-measurement state will be the empty state and is
-  impossible. As in the classical case, a probability measure is a
-  function that maps events to $[0,1]$. Here is a partial
-  specification of a possible probability measure that would be
-  induced by a system whose current state is $\ket{0}$,
-  $\mu\left(\mathbb{0}\right)=0$, $\mu\left(\mathbb{1}\right)=1$,
-  $\mu\left(\proj{0}\right)=1$, $\mu\left(\proj{1}\right)=0$,
-  $\mu\left(\proj{\ps}\right)=\frac{1}{2}$, \ldots. Note that, similarly to
-  the classical case, the probability of $\mathbb{1}$ is 1 and the
-  probability of collections of orthogonal events (e.g.,
-  $\proj{0}+\proj{1}$) is the sum of the individual probabilities.  A
-  collection of non-orthogonal events (e.g., $\proj{0}$ and
-  $\proj{\ps}$) is however not even a valid event. In the classical
-  example, we argued that each probability measure is uniquely
-  determined by two actual coins. A similar (but much more subtle)
-  argument is valid also in the quantum case. By postulates of quantum
-  mechanics and Gleason's theorem, it turns out that for large enough
-  quantum systems, each probability measure is uniquely determined by
-  an actual quantum state as discussed next.
-\end{example}
+For example, the event $\proj{0}$ indicates that the post-measurement
+state will be $\ket{0}$; the probability of such an event depends
+on the current state; the event $\proj{1}$ indicates that the post-measurement
+state will be $\ket{1}$; the event $\proj{\ps}$ where $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$
+indicates that the post-measurement state will be $\ket{\ps}$; the
+event $\mathbb{1}=\proj{0}+\proj{1}$ indicates that the post-measurement
+state will be a linear combination of $\ket{0}$ and $\ket{1}$ and
+is clearly certain; finally the empty event $\mathbb{0}$ states that
+the post-measurement state will be the empty state and is impossible.
+As in the classical case, a probability measure is a function that
+maps events to $[0,1]$. Here is a partial specification of a possible
+probability measure that would be induced by a system whose current
+state is $\ket{0}$, $\mu\left(\mathbb{0}\right)=0$, $\mu\left(\mathbb{1}\right)=1$,
+$\mu\left(\proj{0}\right)=1$, $\mu\left(\proj{1}\right)=0$, $\mu\left(\proj{\ps}\right)=\frac{1}{2}$,
+\ldots{}. Note that, similarly to the classical case, the probability
+of $\mathbb{1}$ is 1 and the probability of collections of orthogonal
+events (e.g., $\proj{0}+\proj{1}$) is the sum of the individual probabilities.
+A collection of non-orthogonal events (e.g., $\proj{0}$ and $\proj{\ps}$)
+is however not even a valid event. In the classical example, we argued
+that each probability measure is uniquely determined by two actual
+coins. A similar (but much more subtle) argument is valid also in
+the quantum case. By postulates of quantum mechanics and Gleason's
+theorem, it turns out that for large enough quantum systems, each
+probability measure is uniquely determined by an actual quantum state
+as discussed next. \end{example}
 
 %%%%%
+
 \subsection{Quantum Probability Measures}
 
-Given our setup, the definition of a quantum probability measure is a
-small variation on the classical definition.
+Given our setup, the definition of a quantum probability measure is
+a small variation on the classical definition.
 
@@
 
-\noindent A quantum probability measure can be easily constructed if
-one knows the current state of the quantum system by using the Born
-rule.  Specifically, for each
-pure normalized quantum state $\ket{\phi}$, the Born rule induces a
-probability measure $\mu_{\phi}^{\mathrm{B}}$ defined as
-$\mu_{\phi}^{\mathrm{B}}(P)=\ip{\phi}{P\phi}$. The situation generalizes to
-mixed states $\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
-$\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born rule
-induces a probability measure $\mu_{\rho}^{\mathrm{B}}$ defined
-as
-$\mu_{\rho}^{\mathrm{B}}\left(P\right) = \Tr\left(\rho P\right) =
-\sum_{j=1}^{N}
-q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
+\noindent A quantum probability measure can be easily constructed
+if one knows the current state of the quantum system by using the
+Born rule. Specifically, for each pure normalized quantum state $\ket{\phi}$,
+the Born rule induces a probability measure $\mu_{\phi}^{\mathrm{B}}$
+defined as $\mu_{\phi}^{\mathrm{\mathrm{B}}}(P)=\ip{\phi}{P\phi}$.
+The situation generalizes to mixed states $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$,
+where $\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born
+rule induces a probability measure $\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+defined as $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}^{\mathrm{\mathrm{B}}}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
 Conversely every probability measure must be of this form.
 
-\begin{thm}[Gleason's
-  theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
+\begin{thm}[Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
 a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
 measure~$\mu:\events\rightarrow[0,1]$, there exists a unique mixed
-state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$.
+state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$.
 \end{thm}
@@
 %%%%%
+
 \subsection{Measuring Quantum Probabilities}
@@
 \caption{\label{fig:three-dimensional-3-value}This figure illustrates the
-1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{\mathrm{B}}(P)=\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$
+1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{\mathrm{\mathrm{B}}}(P)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}(P)\right)$
 plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
-and $\bar{\mu}_{\ket{0}}^{\mathrm{B}}\left(\proj{0}\right)=\necess$. $\ket{0}$
-is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\imposs$
+and $\bar{\mu}_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(\proj{0}\right)=\necess$.
+$\ket{0}$ is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(\proj{\psi}\right)=\imposs$
 for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
-we have $\bar{\mu}_{\ket{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\unknown$.}
+we have $\bar{\mu}_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(\proj{\psi}\right)=\unknown$.}
 \end{figure}
 For example, figure~\ref{fig:three-dimensional-3-value} plots the
-1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$.
+1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}(P)\right)$.
 This measure represents the beliefs of an experimenter with no prior
-knowledge about the particular quantum system in question.\footnote{\yutsung{Actually, $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$ is quite
-informative. Since $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)=\necess$
-if and only if $P=\proj{0}$, we know the core of $\iota\left(\mu_{\ket{0}}^{\mathrm{B}}(P)\right)$
-is exactly $\left\{ \mu_{\ket{0}}^{\mathrm{B}}\right\} $. The quantum interval-valued
-probability measure for an experimenter with no prior knowledge should
-be $\bar{\mu}(P)=\unknown$ for every projection~$P$.}}
+knowledge about the particular quantum system in question.\footnote{\yutsung{Actually, $\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}(P)\right)$
+is quite informative. Since $\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}(P)\right)=\necess$
+if and only if $P=\proj{0}$, we know the core of $\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}(P)\right)$
+is exactly $\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.
+The quantum interval-valued probability measure for an experimenter
+with no prior knowledge should be $\bar{\mu}(P)=\unknown$ for every
+projection~$P$.}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Why Empty Core?}
@@
 because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
-$\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} $.
+$\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{\mathrm{B}}}\right\} $.
 \item When $\events_{2}=\events\backslash\left\{ \proj{\ps}\right\} $,
 because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we
-have $\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} $.
+have $\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{1}}^{\mathrm{\mathrm{B}}}\right\} $.
 \item When $\events_{3}=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
 because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$,
-we have $\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$
-as well as $\mu_{\ket{2}}^{\mathrm{B}}$ and $\mu_{\ket{1}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$.
+we have $\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{\mathrm{B}}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$
+as well as $\mu_{\ket{2}}^{\mathrm{\mathrm{B}}}$ and $\mu_{\ket{1}}^{\mathrm{\mathrm{B}}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$.
 \end{itemize}
@@
 \begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} \cap\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} =\emptyset\,.
+\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{\mathrm{B}}}\right\} \cap\left\{ \mu_{\ket{1}}^{\mathrm{\mathrm{B}}}\right\} =\emptyset\,.
 \end{equation}
@@
 mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
-such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{\mathrm{B}}\right\} $
+such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{\mathrm{\mathrm{B}}}\right\} $
 in the Hilbert space of dimension 3, where the cross product of complex
@@
 in the sphere as in figure~\ref{fig:three-dimensional-real-frame-1},
-and this area intersects a plane~$\events'$, then $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi}}^{\mathrm{B}}\right\} $,
+and this area intersects a plane~$\events'$, then $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi}}^{\mathrm{\mathrm{B}}}\right\} $,
 where $\ket{\psi}$ is the normal vector of $\events'$. Since different
@@
 \item The radius of any disk inside the area of the 1-dimensional projectors
-mapping to $\imposs$ must smaller than $\pi / 4$ (theorem~\ref{thm:pi-div-4}).
+mapping to $\imposs$ must smaller than $\pi/4$ (theorem~\ref{thm:pi-div-4}). 
 \item When the radius of any disk inside the area of the 1-dimensional projectors
-mapping to $\imposs$ between $\arcsin\left(1 / \sqrt{3}\right)$
-and $\pi / 4$, we have $\unknown\in\mathscr{I}$, i.e., $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=1$
+mapping to $\imposs$ between $\arcsin\left(1/\sqrt{3}\right)$ and
+$\pi/4$, we have $\unknown\in\mathscr{I}$, i.e., $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=1$
 (theorem~\ref{thm:arcsin-one-over-sqrt-three}). 
 \item When the radius of any disk inside the area of the 1-dimensional projectors
-mapping to $\imposs$ between $\pi/6$ and $\arcsin\left(1 / \sqrt{3}\right)$,
+mapping to $\imposs$ between $\pi/6$ and $\arcsin\left(1/\sqrt{3}\right)$,
 we have $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=\frac{1}{3}$
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion and Discussion}
@@
 \begin{table}
-\caption{\label{table_long}Relation between measurement resources and
-interval-valued probability measures.}
+\caption{\label{table_long}Relation between measurement resources and interval-valued
+probability measures.}
+
 \begin{indented}
-\item[]\begin{tabular}{c|cccc}
+\item\begin{tabular}{c|cccc} 
 \br 
@@
 \end{indented}
+
 \end{table}
+
 Additional work is in progress on the following research questions: 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%dummy comment inserted by tex2lyx to ensure that this paragraph is not empty%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Interval-valued Frame Functions\label{sec:Interval-valued-Frame-Functions}}
@@
 by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
-quantum probability measure~$\mu_{\phi}^{\mathrm{B}}$ induced by the Born
-rule, its frame function is denoted by $f_{\phi}^{\mathrm{B}}$.\end{definition}
+quantum probability measure~$\mu_{\phi}^{\mathrm{\mathrm{B}}}$ induced
+by the Born rule, its frame function is denoted by $f_{\phi}^{\mathrm{\mathrm{B}}}$.\end{definition}
 
@@
 holds because the properties of $\bar{f}$.\end{proof}
+
 \begin{definition}\label{def:cross-product}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}
@@
 if and only if $\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$.\end{lemma}
-\begin{proof}
-To prove that $\ket{\varphi}\parallel\left(\ket{\psi}\times\ket{\phi}\right)\Rightarrow\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$,
+\begin{proof} To prove that $\ket{\varphi}\parallel\left(\ket{\psi}\times\ket{\phi}\right)\Rightarrow\ip{\psi}{\varphi}=\ip{\phi}{\varphi}=0$,
 we can just verify 
@@
 To prove the other direction, consider the linear transformation~$T:\mathbb{C}^{3}\rightarrow\mathbb{C}^{2}$
-defined by $T\left(\ket{\varphi}\right)=\left(\begin{array}{c}\ip{\psi}{\varphi}\\
+defined by $T\left(\ket{\varphi}\right)=\left(\begin{array}{c}
+\ip{\psi}{\varphi}\\
 \ip{\phi}{\varphi}
@@
 Therefore, $\ket{\varphi}\parallel\left(\ket{\psi}\times\ket{\phi}\right)$.
-\end{proof}
-Since interval-valued probability measures~$\bar{\mu}$ and interval-valued
-frame functions~$\bar{f}$ are one-to-one correspondence, studying
-1-dimensional projectors mapping to impossible by $\bar{\mu}$ is
-the same as studying the points on $\mathbb{C}S^{2}$ mapping to impossible
-by $\bar{f}$. These points, denoted by $\bar{f}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}S^{2}}{\bar{f}(\ket{\psi})=\imposs}$,
+\end{proof} Since interval-valued probability measures~$\bar{\mu}$
+and interval-valued frame functions~$\bar{f}$ are one-to-one correspondence,
+studying 1-dimensional projectors mapping to impossible by $\bar{\mu}$
+is the same as studying the points on $\mathbb{C}S^{2}$ mapping to
+impossible by $\bar{f}$. These points, denoted by $\bar{f}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}S^{2}}{\bar{f}(\ket{\psi})=\imposs}$,
 play an important role to understand $\bar{f}$. There are 4 different
@@
 \begin{enumerate}
-\item $\bar{f}^{-1}\left(\imposs\right)=\emptyset$. If $f_{\phi}^{\mathrm{B}}\in\mathrm{core}\left(\bar{f}\right)$
+\item $\bar{f}^{-1}\left(\imposs\right)=\emptyset$. If $f_{\phi}^{\mathrm{\mathrm{B}}}\in\mathrm{core}\left(\bar{f}\right)$
 for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$. 
 \item $\bar{f}^{-1}\left(\imposs\right)=\left\{ \ket{\psi_{0}}\right\} $.
-If $f_{\phi}^{\mathrm{B}}\in\mathrm{core}\left(\bar{f}\right)$ for some pure
-state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
-to $\ket{\psi_{0}}$.
+If $f_{\phi}^{\mathrm{\mathrm{B}}}\in\mathrm{core}\left(\bar{f}\right)$
+for some pure state~$\ket{\phi}$, $\ket{\phi}$ could be any state
+orthogonal to $\ket{\psi_{0}}$. 
 \item Consider $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} \subseteq\bar{f}^{-1}\left(\imposs\right)$.
@@
 then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
-which might induce $\bar{f}$. In another word, if $f_{\phi}^{\mathrm{B}}\in\mathrm{core}\left(\bar{f}\right)$
+which might induce $\bar{f}$. In another word, if $f_{\phi}^{\mathrm{\mathrm{B}}}\in\mathrm{core}\left(\bar{f}\right)$
 for some pure state~$\ket{\phi}$, then $\ket{\phi}\parallel\left(\ket{\psi_{0}}\times\ket{\psi_{1}}\right)$.
@@
 case when the core is empty; an interval-valued frame function defined
-by $\bar{f}\left(\ket{\psi}\right)=\iota\left(f_{\phi}^{\mathrm{B}}\left(\ket{\psi}\right)\right)$
-is also in this case when the core is the singleton set~$\left\{ f_{\phi}^{\mathrm{B}}\right\} $,
+by $\bar{f}\left(\ket{\psi}\right)=\iota\left(f_{\phi}^{\mathrm{\mathrm{B}}}\left(\ket{\psi}\right)\right)$
+is also in this case when the core is the singleton set~$\left\{ f_{\phi}^{\mathrm{\mathrm{B}}}\right\} $,
 where $\iota$ is defined in equation~(\ref{eq:homomorphism}). 
@@
 then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
-might induce $\bar{f}$. However, neither $f_{\psi_{0}\times\psi_{1}}^{\mathrm{B}}$
-nor $f_{\psi_{0}'\times\psi_{1}'}^{\mathrm{B}}$ is in the core of $\bar{f}$
-because $f_{\psi_{0}\times\psi_{1}}^{\mathrm{B}}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}'}\right)=\bar{f}\left(\ket{\psi_{1}'}\right)=\imposs$
-and $f_{\psi_{0}'\times\psi_{1}'}^{\mathrm{B}}$ is inconsistent with $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)=\imposs$.
+might induce $\bar{f}$. However, neither $f_{\psi_{0}\times\psi_{1}}^{\mathrm{\mathrm{B}}}$
+nor $f_{\psi_{0}'\times\psi_{1}'}^{\mathrm{\mathrm{B}}}$ is in the
+core of $\bar{f}$ because $f_{\psi_{0}\times\psi_{1}}^{\mathrm{\mathrm{B}}}$
+is inconsistent with $\bar{f}\left(\ket{\psi_{0}'}\right)=\bar{f}\left(\ket{\psi_{1}'}\right)=\imposs$
+and $f_{\psi_{0}'\times\psi_{1}'}^{\mathrm{\mathrm{B}}}$ is inconsistent
+with $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)=\imposs$.
 Actually, $\bar{f}$ has an empty core, and this is the case for example~\ref{ex:three-dimensional-three-value}. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Real Interval-valued Frame Functions\label{sec:Real-Interval-valued-Frame}}
@@
 For example, the north pole has the latitude $0$, the equator has
-the the latitude $\pi / 2$, and $\angle^{-1}\left(\left[0,\theta_{0}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\pi / 2}$
+the the latitude $\pi/2$, and $\angle^{-1}\left(\left[0,\theta_{0}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\pi/2}$
 contains all states whose latitude is larger than $\theta_{0}$.\end{definition}
 
-\begin{lemma}\label{lemma:imposs-imply-same-value}Given
-$\theta_{0}\in\left[0,\pi/2\right]$ and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
+\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\pi/2\right]$
+and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
 if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
@@
 \end{figure}
+
 \begin{proof} We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
@@
 $\bar{f}\left(\ket{2}\right)=\left[1,1\right]-\bar{f}\left(\ket{\bar{1}}\right)=\bar{f}\left(\ket{\bar{2}}\right)$.
-In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\pi / 2\right]\right)$,
+In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[\pi/2-\theta_{0},\pi/2\right]\right)$,
 even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are not in the same
@@
 \begin{equation}
-\left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\Rightarrow
-l_{0}+r_{0}=1\,.
+\left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\Rightarrow l_{0}+r_{0}=1\,.
 \end{equation}
@@
 \begin{equation}
-1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\Rightarrow
-l_{0}\le\frac{1}{2}\le r_{0}\,.
-\end{equation}
-Thus the lemma is proved.
-\end{proof}
-\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\pi / 2\right]$
-and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
-if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
-then $\theta_{0}<\pi / 4$.\end{thm}
-\begin{proof}
-We are going to prove by contradiction. Suppose $\theta_{0}\ge\pi / 4$,
-we have $\left[0,\theta_{0}\right]\cap\left[\pi / 2-\theta_{0},\pi / 2\right]=\left[\pi / 2-\theta_{0},\theta_{0}\right]\ne\emptyset$.
-Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\theta_{0}\right]\right)$,
+1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\Rightarrow l_{0}\le\frac{1}{2}\le r_{0}\,.
+\end{equation}
+Thus the lemma is proved. \end{proof} \begin{thm}\label{thm:pi-div-4}Given
+$\theta_{0}\in\left[0,\pi/2\right]$ and an interval-valued frame
+function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$, if $\bar{f}\left(\ket{\psi}\right)=\imposs$
+for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
+then $\theta_{0}<\pi/4$.\end{thm} \begin{proof} We are going to
+prove by contradiction. Suppose $\theta_{0}\ge\pi/4$, we have $\left[0,\theta_{0}\right]\cap\left[\pi/2-\theta_{0},\pi/2\right]=\left[\pi/2-\theta_{0},\theta_{0}\right]\ne\emptyset$.
+Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi/2-\theta_{0},\theta_{0}\right]\right)$,
 by lemma~\ref{lemma:imposs-imply-same-value}, we have $\imposs=\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]$,
-where $l_{0}\in\left[0,\pi / 2\right]$. A contradiction!
-\end{proof}
-\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left[\arcsin\left(1 / \sqrt{3}\right),\pi / 4\right)$
+where $l_{0}\in\left[0,\pi/2\right]$. A contradiction! \end{proof}
+\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left[\arcsin\left(1/\sqrt{3}\right),\pi/4\right)$
 and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
@@
 \begin{centering}
-\includegraphics[scale=0.38]{figureb2.eps} 
+\includegraphics[scale=0.38]{figureb2} 
 \par\end{centering}
@@
 the proof of theorem~\ref{thm:arcsin-one-over-sqrt-three}. The latitude
-of the yellow circle is $\theta_{0}\in\left[\arcsin\left(1 / \sqrt{3}\right),\pi / 4\right)$,
-and the latitude of the green circle is $\pi / 2-\theta_{0}$.}
+of the yellow circle is $\theta_{0}\in\left[\arcsin\left(1/\sqrt{3}\right),\pi/4\right)$,
+and the latitude of the green circle is $\pi/2-\theta_{0}$.}
 \end{figure}
-\begin{proof}
-We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-2},
+
+\begin{proof} We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-2},
 where the latitude of of the yellow circle is $\theta_{0}$ and the
-latitude of of the green circle is $\pi / 2-\theta_{0}$. Therefore,
+latitude of of the green circle is $\pi/2-\theta_{0}$. Therefore,
 $\bar{f}$ should map any state above the yellow circle to $\imposs$
@@
 
-When $\theta_{0}\ge\arcsin\left(1 / \sqrt{3}\right)$, the latitude
-of the green circle is $\theta_{0}\le\pi / 2-\arcsin\left(1 / \sqrt{3}\right)$.
+When $\theta_{0}\ge\arcsin\left(1/\sqrt{3}\right)$, the latitude
+of the green circle is $\theta_{0}\le\pi/2-\arcsin\left(1/\sqrt{3}\right)$.
 Now consider three states~$\ket{A}$, $\ket{B}$, and $\ket{C}$
-whose latitude is $\pi / 2-\arcsin\left(1 / \sqrt{3}\right)$
-so that they are below the green circle, and these three states form
-an equilateral triangle whose center is $H$. Since the latitude of
-this triangle is $\pi / 2-\arcsin\left(1 / \sqrt{3}\right)$,
-we know $\overline{OH}=1 / \sqrt{3}$, where $O$ is the center
-of the sphere. By the Pythagorean theorem, $\overline{HA}=\overline{HB}=\sqrt{\frac{2}{3}}$.
-Notice that $\triangle HAB$ is an isosceles triangle with $\angle AHB=2\pi / 3$,
-we have $\overline{AB}=\sqrt{2}$. Since $\overline{OA}=\overline{OB}=1$
-and $\overline{AB}=\sqrt{2}$, $\triangle OAB$ is an isosceles right
-triangle with $\angle AHB=\pi / 2$, i.e., $\ket{A}$ and $\ket{B}$
-are orthogonal. Applying the same reason on all $\ket{A}$, $\ket{B}$,
-and $\ket{C}$, $\left\{ \ket{A},\ket{B},\ket{C}\right\} $ is an
-orthonormal basis.
+whose latitude is $\pi/2-\arcsin\left(1/\sqrt{3}\right)$ so that
+they are below the green circle, and these three states form an equilateral
+triangle whose center is $H$. Since the latitude of this triangle
+is $\pi/2-\arcsin\left(1/\sqrt{3}\right)$, we know $\overline{OH}=1/\sqrt{3}$,
+where $O$ is the center of the sphere. By the Pythagorean theorem,
+$\overline{HA}=\overline{HB}=\sqrt{\frac{2}{3}}$. Notice that $\triangle HAB$
+is an isosceles triangle with $\angle AHB=2\pi/3$, we have $\overline{AB}=\sqrt{2}$.
+Since $\overline{OA}=\overline{OB}=1$ and $\overline{AB}=\sqrt{2}$,
+$\triangle OAB$ is an isosceles right triangle with $\angle AHB=\pi/2$,
+i.e., $\ket{A}$ and $\ket{B}$ are orthogonal. Applying the same
+reason on all $\ket{A}$, $\ket{B}$, and $\ket{C}$, $\left\{ \ket{A},\ket{B},\ket{C}\right\} $
+is an orthonormal basis.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Between Quantum and Classical}
@@
 it is straightforward to define a quantum cryptodeterministic, real-valued
-probability, and interval-valued probability measure on $\events'$.{
-Also, }$\events'$ is called convex if we have $P_{1}P_{2}\in\events'$
+probability, and interval-valued probability measure on $\events'$.
+Also, $\events'$ is called convex if we have $P_{1}P_{2}\in\events'$
 for a pair of mutually commuting projections $P_{1}$ and $P_{2}\in\events'$.\end{definition}
@@
 \end{eqnarray*}
-By theorem~\ref{thm:sub-event-space},
-there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
+By theorem~\ref{thm:sub-event-space}, there is a density matrix~$\rho$
+such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
 for all $P\in\events'$. Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{From QRVPM to QIVPM\label{sec:Real-and-Interval}}
@@
 \left[x,x\right]\,, &if $x=0$ or $x=1$ ;\\ 
-\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right]\,, &if
-$x=\frac{k}{n}\in\left(0,1\right)$ ;\\
+\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right]\,, &if $x=\frac{k}{n}\in\left(0,1\right)$ ;\\ 
 \left[\frac{k}{n},\frac{k+1}{n}\right]\,, &if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
@@
 \Rightarrow & \left[x_{0}+x_{1}+x_{2}+c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}+c\left(x_{2}\right)\right]\\
- & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\,. }\end{equation}
+ & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\,.
+}\end{equation}
 Also, 
@@
 \par\end{centering}
-\caption{\label{fig:three-dimensional-5-value}This figure illustrates cases
-1 and 2 of example~\ref{ex:three-dimensional-5-value} plotted in
-$\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
-and $\ket{\ps}$ respectively. All possible real vectors of the subspaces
-orthogonal to $\ket{0}$ or $\ket{\ps}$ are drawn in the red and
-green circles, respectively.}
+\caption{\label{fig:three-dimensional-5-value}This figure illustrates example~\ref{ex:three-dimensional-5-value}
+plotted in $\mathbb{R}^{3}$. The red and green dotted vectors are
+$\ket{0}$ and $\ket{\ps}$ respectively. All possible real vectors
+of the subspaces orthogonal to $\ket{0}$ or $\ket{\ps}$ are drawn
+in the red and green circles, respectively.}
 \end{figure}
@@
 core. Assume there is a real-valued probability measure satisfying
-$\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$ for all $P\in\events$. Because
-$\mu_{\rho}^{\mathrm{B}}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$ and $\mu_{\rho}^{\mathrm{B}}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
-we must have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
-so that $\mu_{\rho}^{\mathrm{B}}=\mu_{\ket{2}}^{\mathrm{B}}$. However, 
-\begin{equation}
-\mu_{\ket{2}}^{\mathrm{B}}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\,.
+$\mu_{\rho}^{\mathrm{\mathrm{B}}}(P)\in\bar{\mu}(P)$ for all $P\in\events$.
+Because $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
+and $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
+we must have $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{0})=\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{\ps})=0$
+so that $\mu_{\rho}^{\mathrm{\mathrm{B}}}=\mu_{\ket{2}}^{\mathrm{\mathrm{B}}}$.
+However, 
+\begin{equation}
+\mu_{\ket{2}}^{\mathrm{\mathrm{B}}}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\,.
 \end{equation}
@@
 
+\yutsung{{Example for when }$\bar{\mu}$ is not convex, Eq.~(\ref{eq:Rosenmuller})
+doesn't hold. This can justify why we need convex...}
+
 The next lemmas shows our definition is exactly the same as in the
@@
 \printbibliography
-
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-10-08 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 postulates of the quantum probability measures first, and then introduce
-the Born rule which induces the quantum probability measures for each
+the Born rule which induces a quantum probability measures from each
 state. When we shift our attention to QIVPMs, we also want to construct
-a QIVPMs according to a simple rule. Since the ranges of the quantum
+QIVPMs according to a simple rule. Since the ranges of the quantum
 probability measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$,
 respectively, if there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
-to $\iota\left(x\right)\in\mathscr{I}$, then we can concatenate it
-with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+to an interval~$\iota\left(x\right)\in\mathscr{I}$, then we can
+concatenate it with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
 and get a $\mathscr{I}$-valued function~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
@@
 
-\begin{thm}If there exists three numbers~$x_{0}$, $x_{1}$, and
-$x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
-but 
+\begin{thm}Given a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
+if there exists three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but 
 \begin{equation}
@@
 fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-\begin{eqnarray}
- &  & \begin{aligned} & \mathrel{\hphantom{=}}\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\end{aligned}
-\nonumber \\
- &  & \begin{aligned} & =\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
- & \nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)
+\begin{equation}
+\begin{aligned} & \mathrel{\hphantom{\nsubseteq}}\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
+ & \nsubseteq\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\textrm{ ,}
 \end{aligned}
-\\
- &  & \begin{aligned} & =\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\textrm{ ,}\end{aligned}
-\nonumber 
-\end{eqnarray}
+\end{equation}
 and cannot be a QIVPM.
@@
 as a QIVPM, we may need to verify whether $\iota\circ\mu$ is a QIVPM
-individually. For example, consider the following easy example. In
-the four-dimensional Hilbert space, 
+individually. For example, in the four-dimensional Hilbert space,
 \begin{equation}
@@
 \end{equation}
-and $\rho=\left(\proj{0}+\proj{1}+\proj{2}+\proj{3}\right)/4$ induce
-a QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ which is a
-non-trivial fact~\citep{HOSTunpublished}. In order to verify whether
-$\iota\circ\mu$ is a QIVPM easier, we want to impose some conditions
-on $\iota$. Notice that our counterexamples are in a four-dimensional
-Hilbert space, the conditions for $\iota$ for a Hilbert space of
-dimension~$d\le3$ is not as strict as the general conditions.
+and $\rho=\left(\proj{0}+\proj{1}+\proj{2}+\proj{3}\right)/4$ inducing
+a QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ is a non-trivial
+fact~\citep{HOSTunpublished}. In order to verify whether $\iota\circ\mu$
+is a QIVPM easier, we can impose some conditions on $\iota$. Notice
+that our counterexamples are in a four-dimensional Hilbert space,
+the conditions for $\iota$ for a Hilbert space of dimension~$d\le3$
+is not as strict as the general conditions.
 

### 2017-10-08 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 state. When we shift our attention to QIVPMs, we also want to construct
-QIVPMs according to a simple rule. Since the ranges of the quantum
-probability measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$,
-respectively, if there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
+QIVPMs according to a simple rule. Since the ranges of quantum probability
+measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$, respectively,
+if there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
 to an interval~$\iota\left(x\right)\in\mathscr{I}$, then we can
@@
 and get a $\mathscr{I}$-valued function~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
-Although $\bar{\mu}$ and QIVPMs have the same the domain and range,
-$\bar{\mu}$ is not necessary a QIVPM. For example, the following
-theorem highlight a situation where $\bar{\mu}$ cannot be a QIVPM.
+Although $\bar{\mu}$ and QIVPMs have the same domain and range, $\bar{\mu}$
+is not necessary a QIVPM. For example, the following theorem highlight
+a situation where $\bar{\mu}$ cannot be a QIVPM.
 
@@
 \begin{aligned}\rho={} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
- & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\textrm{ .}
+ & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
 \end{aligned}
@@
 \begin{aligned} & \mathrel{\hphantom{\nsubseteq}}\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
- & \nsubseteq\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\textrm{ ,}
+ & \nsubseteq\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\,,
 \end{aligned}
@@
 \iota\left(x\right)=\begin{cases}
-\imposs & \textrm{, if }x=0\textrm{ ;}\\
-\left[0,\tfrac{1}{2}\right] & \textrm{, if }x\in\left(0,\tfrac{1}{4}\right]\textrm{ ;}\\
-\unknown & \textrm{, if }x\in\left(\tfrac{1}{4},\tfrac{3}{4}\right)\textrm{ ;}\\
-\left[\tfrac{1}{2},1\right] & \textrm{, if }x\in\left[\tfrac{3}{4},1\right)\textrm{ ;}\\
-\necess & \textrm{, if }x=1\textrm{ .}
+\imposs\,, & \textrm{ if }x=0\,;\\
+\left[0,\tfrac{1}{2}\right]\,, & \textrm{ if }x\in\left(0,\tfrac{1}{4}\right]\,;\\
+\unknown\,, & \textrm{ if }x\in\left(\tfrac{1}{4},\tfrac{3}{4}\right)\,;\\
+\left[\tfrac{1}{2},1\right]\,, & \textrm{ if }x\in\left[\tfrac{3}{4},1\right)\,;\\
+\necess\,, & \textrm{ if }x=1\,.
 \end{cases}
@@
 \begin{equation}
-\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\textrm{ .}\label{eq:iota-add}
+\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
 \end{equation}

### 2017-10-08 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 Although $\bar{\mu}$ and QIVPMs have the same domain and range, $\bar{\mu}$
-is not necessary a QIVPM. For example, the following theorem highlight
-a situation where $\bar{\mu}$ cannot be a QIVPM.
-
-\begin{thm}Given a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
-if there exists three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
-such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but 
-\begin{equation}
-\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion-not}
-\end{equation}
-Then, there is a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-such that $\iota\circ\mu$ is not a QIVPM, where $\circ$ is the function
-concatenation.\end{thm}
-
-Consider the state
-\begin{equation}
-\begin{aligned}\rho={} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
- & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
-\end{aligned}
-\end{equation}
-Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}$
-fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-\begin{equation}
-\begin{aligned} & \mathrel{\hphantom{\nsubseteq}}\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
- & \nsubseteq\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\,,
-\end{aligned}
-\end{equation}
-and cannot be a QIVPM.
-
-In other words, even if $\iota\circ\mu$ has the same domain and range
-as a QIVPM, we may need to verify whether $\iota\circ\mu$ is a QIVPM
-individually. For example, in the four-dimensional Hilbert space,
-\begin{equation}
-\iota\left(x\right)=\begin{cases}
+is not necessary a QIVPM. For example, in the four-dimensional Hilbert
+space with 
+\begin{equation}
+\iota'\left(x\right)=\begin{cases}
 \imposs\,, & \textrm{ if }x=0\,;\\
@@
 \left[\tfrac{1}{2},1\right]\,, & \textrm{ if }x\in\left[\tfrac{3}{4},1\right)\,;\\
-\necess\,, & \textrm{ if }x=1\,.
-\end{cases}
-\end{equation}
-and $\rho=\left(\proj{0}+\proj{1}+\proj{2}+\proj{3}\right)/4$ inducing
-a QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ is a non-trivial
-fact~\citep{HOSTunpublished}. In order to verify whether $\iota\circ\mu$
-is a QIVPM easier, we can impose some conditions on $\iota$. Notice
-that our counterexamples are in a four-dimensional Hilbert space,
-the conditions for $\iota$ for a Hilbert space of dimension~$d\le3$
-is not as strict as the general conditions.
-
-\begin{thm}In a Hilbert space of dimension~$d\le3$, if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
+\necess\,, & \textrm{ if }x=1\,,
+\end{cases}\label{eq:iota}
+\end{equation}
+the function~$\iota'\circ\mu_{\rho_{0}}^{\mathrm{\mathrm{B}}}$ induced
+by $\rho_{0}=\frac{1}{4}\cdot\proj{0}+\frac{1}{4}\cdot\proj{1}+\frac{1}{4}\cdot\proj{2}+\frac{1}{4}\cdot\proj{3}$
+is a QIVPM, but the function~$\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
+induced by $\rho_{1}=\frac{1}{8}\cdot\proj{0}+\frac{1}{8}\cdot\proj{1}+\frac{1}{8}\cdot\proj{2}+\frac{5}{8}\cdot\proj{3}$
+is \emph{not} a QIVPM, where $\circ$ is the function concatenation.
+In particular, verifying whether an \emph{arbitrary} function is a
+QIVPM is a long and tedious process~\citep{HOSTunpublished}, so
+that it would be good if $\iota\circ\mu$ is automatically a QIVPM
+during some situations.
+
+\begin{thm}\label{thm:QRVPM2QIVPM-3}In a Hilbert space of dimension~$d\le3$,
+if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ subject to the
+following constraints:\begin{subequations}\label{eq:iota-constraints}
 \begin{eqnarray}
@@
 \begin{equation}
-\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
+\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
 \end{equation}
@@
 
-Although their concatenation $\iota\circ\mu$ is always a function
-from $\events$ to $\mathscr{I}$, to guarantee $\iota\circ\mu$ is
-a QIVPM, $\iota$ needs to satisfy some extra conditions.
+The situation for $d=2$ is trivial. When $d=3$, to prove that $\iota\circ\mu$
+is a QIVPM, it is sufficient to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+When $P_{0}$ and $P_{1}$ are orthogonal, Eq.~(\ref{eq:iota-add})
+implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
+When $P_{0}$ and $P_{1}$ are not orthogonal on a three-dimensional
+Hilbert space, we have two possibilities:
+\begin{itemize}
+\item Their complements~$\mathbb{1}-P_{0}$ and $\mathbb{1}-P_{1}$ are
+orthogonal so that we can apply Eq.~(\ref{eq:iota-add}) on their
+complements.
+\item One of them projects onto a subspace of what the other one projects
+onto.
+\end{itemize}
+\noindent Both cases deduce Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+easily~\citep{HOSTunpublished} so that $\iota\circ\mu$ is indeed
+a QIVPM.
+
+Since $\iota'$ defined in Eq.~(\ref{eq:iota}) satisfies Eq.~(\ref{eq:iota-constraints})
+and Eq.~(\ref{eq:iota-add}), every function~$\iota'\circ\mu$ on
+a three-dimensional Hilbert space is a QIVPM according to Thm.~\ref{thm:QRVPM2QIVPM-3}.
+However, we knows that $\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
+is not a QIVPM. This highlight the necessity of the conditions to
+guarantee $\iota\circ\mu$ is always a QIVPM.
 
@@
 in any Hilbert space $\Hilb$, then $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-must subject to the following constraints:\begin{subequations}
-\begin{eqnarray}
- &  & \iota(0)=\imposs\,,\\
- &  & \iota(1)=\necess\,,\\
- &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
-\end{eqnarray}
-\end{subequations} and satisfying for any three numbers~$x_{0}$,
-$x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
-implies
+must subject to Eqs.~(\ref{eq:iota-constraints}) and satisfying
+for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
+$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies
 \begin{equation}
@@
 
-Although a interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-may look exotic, its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$
-are just usual functions from a unit interval to another unit interval.
-Eq.~(\ref{eq:iota-Inclusion}) then implies that $\iotal$ is Wright-convex,
-i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
+Suppose $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
+there must exist three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but 
+\[
+\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
+\]
+Consider the state
+\begin{equation}
+\begin{aligned}\rho={} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
+ & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
+\end{aligned}
+\end{equation}
+Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}$
+fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+\[
+\begin{aligned} & \mathrel{\hphantom{\nsubseteq}}\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
+ & \nsubseteq\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\,,
+\end{aligned}
+\]
+and cannot be a QIVPM. Therefore, to make sure $\iota\circ\mu$ is
+always a QIVPM, $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ should
+satisfy Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-Inclusion}).
+
+Since $\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$ is not a
+QIVPM, we know $\iota'$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}).
+In order to find a function~$\iota$ satisfies Eq.~(\ref{eq:iota-Inclusion}),
+we break down into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
+They are both usual functions from a unit interval to another unit
+interval. Eq.~(\ref{eq:iota-Inclusion}) then implies that $\iotal$
+is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
 and $\iotar$ is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
@@
 \begin{equation}
-\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\label{eq:iota-add}
+\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\label{eq:iota-add-1}
 \end{equation}
@@
 \item Their complements~$\mathbb{1}-P_{0}$ and $\mathbb{1}-P_{1}$ are
-orthogonal so that we can apply Eq.~(\ref{eq:iota-add}) on their
+orthogonal so that we can apply Eq.~(\ref{eq:iota-add-1}) on their
 complements.

### 2017-10-09 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 
-\yutsung{Notice that the use of quantum is minumalized in this section.
+\yutsung{Notice that the use of quantum is minimized in this section.
 In another word, the results of this section should apply to both
@@
 Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
-postulates of the quantum probability measures first, and then introduce
+postulates for the quantum probability measures first, and then introduce
 the Born rule which induces a quantum probability measures from each
-state. When we shift our attention to QIVPMs, we also want to construct
-QIVPMs according to a simple rule. Since the ranges of quantum probability
-measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$, respectively,
-if there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
+state. Since the postulates for QIVPMs in Sec.~\ref{sec:Interval-Uncertainty}
+are also non-constructive, we also want to find a simple rule to construct
+a QIVPM. Notice that the biggest difference between a quantum probability
+measure~$\mu:\events\rightarrow\left[0,1\right]$ and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+is their ranges. If there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
 to an interval~$\iota\left(x\right)\in\mathscr{I}$, then we can
 concatenate it with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-and get a $\mathscr{I}$-valued function~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
-Although $\bar{\mu}$ and QIVPMs have the same domain and range, $\bar{\mu}$
-is not necessary a QIVPM. For example, in the four-dimensional Hilbert
-space with 
+and easily get a $\mathscr{I}$-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$,
+where $\circ$ is the function concatenation. This $\iota\circ\mu$
+may or may not be a QIVPM as shown in the following example. In the
+four-dimensional Hilbert space with 
 \begin{equation}
@@
 induced by $\rho_{1}=\frac{1}{8}\cdot\proj{0}+\frac{1}{8}\cdot\proj{1}+\frac{1}{8}\cdot\proj{2}+\frac{5}{8}\cdot\proj{3}$
-is \emph{not} a QIVPM, where $\circ$ is the function concatenation.
-In particular, verifying whether an \emph{arbitrary} function is a
-QIVPM is a long and tedious process~\citep{HOSTunpublished}, so
-that it would be good if $\iota\circ\mu$ is automatically a QIVPM
-during some situations.
+is \emph{not} a QIVPM. Although we could verify whether $\iota\circ\mu$
+is a QIVPM or not directly, it is a long and tedious process. Therefore,
+it is desirable to find some criteria when $\iota\circ\mu$ is a QIVPM.
 
@@
 \end{eqnarray}
-\end{subequations}and satisfying for any three numbers~$x_{0}$
-and $x_{1}\in\left[0,1\right]$, $x_{0}+x_{1}\in\left[0,1\right]$
-implies
+\end{subequations}and satisfying for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
+$x_{0}+x_{1}\in\left[0,1\right]$ implies
 \begin{equation}
@@
 
-The situation for $d=2$ is trivial. When $d=3$, to prove that $\iota\circ\mu$
-is a QIVPM, it is sufficient to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
-When $P_{0}$ and $P_{1}$ are orthogonal, Eq.~(\ref{eq:iota-add})
-implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
-When $P_{0}$ and $P_{1}$ are not orthogonal on a three-dimensional
-Hilbert space, we have two possibilities:
+The situation for $d=2$ is trivial. On a three-dimensional Hilbert
+space, to prove that $\iota\circ\mu$ is a QIVPM, it is sufficient
+to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}):
+\begin{equation}
+\begin{aligned} & \iota\left(\mu\left(P_{0}+P_{1}-P_{0}P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
+\subseteq{} & \iota\left(\mu\left(P_{0}\right)\right)+\iota\left(\mu\left(P_{1}\right)\right)\,.
+\end{aligned}
+\label{eq:QuantumInterval-valuedProbability-Inclusion-case}
+\end{equation}
+ Depending on the relation between $P_{0}$ and $P_{1}$, we have
+three possibilities:
 \begin{itemize}
+\item $P_{0}$ and $P_{1}$ are orthogonal.
 \item Their complements~$\mathbb{1}-P_{0}$ and $\mathbb{1}-P_{1}$ are
@@
 \end{itemize}
-\noindent Both cases deduce Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+\noindent All cases deduce Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion-case})
 easily~\citep{HOSTunpublished} so that $\iota\circ\mu$ is indeed
@@
 
-Since $\iota'$ defined in Eq.~(\ref{eq:iota}) satisfies Eq.~(\ref{eq:iota-constraints})
+Since $\iota'$ defined in Eq.~(\ref{eq:iota}) satisfies Eqs.~(\ref{eq:iota-constraints})
 and Eq.~(\ref{eq:iota-add}), every function~$\iota'\circ\mu$ on
-a three-dimensional Hilbert space is a QIVPM according to Thm.~\ref{thm:QRVPM2QIVPM-3}.
-However, we knows that $\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
+a three-dimensional Hilbert space is a QIVPM. However, on four-dimensional
+Hilbert space, $\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
 is not a QIVPM. This highlight the necessity of the conditions to
@@
 Suppose $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
-there must exist three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
-such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but 
+we can find three particular numbers~$x_{0}'$, $x_{1}'$, and $x_{2}'\in\left[0,1\right]$
+such that $x_{0}'+x_{1}'+x_{2}'\in\left[0,1\right]$, but 
 \[
-\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
+\iota\left(x_{0}'+x_{1}'+x_{2}'\right)+\iota\left(x_{2}'\right)\nsubseteq\iota\left(x_{0}'+x_{2}'\right)+\iota\left(x_{1}'+x_{2}'\right)\,.
 \]
@@
 \begin{equation}
-\begin{aligned}\rho={} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
- & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
+\begin{aligned}\rho={} & x_{0}'\proj{0}+x_{1}'\proj{1}+x_{2}'\proj{2}\\
+ & +\left(1-x_{0}'-x_{1}'-x_{2}'\right)\proj{3}\,.
 \end{aligned}
@@
 QIVPM, we know $\iota'$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}).
-In order to find a function~$\iota$ satisfies Eq.~(\ref{eq:iota-Inclusion}),
-we break down into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
+In order to find $\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
+we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
 They are both usual functions from a unit interval to another unit

### 2017-10-09 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 are also non-constructive, we also want to find a simple rule to construct
-a QIVPM. Notice that the biggest difference between a quantum probability
-measure~$\mu:\events\rightarrow\left[0,1\right]$ and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-is their ranges. If there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
-to an interval~$\iota\left(x\right)\in\mathscr{I}$, then we can
-concatenate it with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-and easily get a $\mathscr{I}$-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$,
-where $\circ$ is the function concatenation. This $\iota\circ\mu$
-may or may not be a QIVPM as shown in the following example. In the
-four-dimensional Hilbert space with 
+a QIVPM. When we generalize quantum probability measures to QIVPMs,
+we replace the unit interval range~$\left[0,1\right]$ by a set of
+intervals~$\mathscr{I}$. This replacement suggests a function~$\iota$
+mapping a number~$x\in\left[0,1\right]$ to an interval~$\iota\left(x\right)\in\mathscr{I}$.
+The function~$\iota$ can then be concatenated with a quantum probability
+measure~$\mu:\events\rightarrow\left[0,1\right]$ and easily get
+an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$,
+where $\circ$ is the function concatenation. However, the concatenated
+function~$\iota\circ\mu$ may or may not be a QIVPM. For example,
+in a four-dimensional Hilbert space, consider the function 
 \begin{equation}
@@
 \left[\tfrac{1}{2},1\right]\,, & \textrm{ if }x\in\left[\tfrac{3}{4},1\right)\,;\\
-\necess\,, & \textrm{ if }x=1\,,
+\necess\,, & \textrm{ if }x=1\,.
 \end{cases}\label{eq:iota}
 \end{equation}
-the function~$\iota'\circ\mu_{\rho_{0}}^{\mathrm{\mathrm{B}}}$ induced
-by $\rho_{0}=\frac{1}{4}\cdot\proj{0}+\frac{1}{4}\cdot\proj{1}+\frac{1}{4}\cdot\proj{2}+\frac{1}{4}\cdot\proj{3}$
-is a QIVPM, but the function~$\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
+While the function~$\iota'\circ\mu_{\rho_{0}}^{\mathrm{\mathrm{B}}}$
+induced by $\rho_{0}=\frac{1}{4}\cdot\proj{0}+\frac{1}{4}\cdot\proj{1}+\frac{1}{4}\cdot\proj{2}+\frac{1}{4}\cdot\proj{3}$
+is a QIVPM, the function~$\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
 induced by $\rho_{1}=\frac{1}{8}\cdot\proj{0}+\frac{1}{8}\cdot\proj{1}+\frac{1}{8}\cdot\proj{2}+\frac{5}{8}\cdot\proj{3}$
 is \emph{not} a QIVPM. Although we could verify whether $\iota\circ\mu$
-is a QIVPM or not directly, it is a long and tedious process. Therefore,
-it is desirable to find some criteria when $\iota\circ\mu$ is a QIVPM.
+is a QIVPM or not for any pair of $\iota$ and $\mu$ individually,
+the verification process is long and tedious. Therefore, it is desirable
+to have some easy criteria to get a QIVPM~$\iota\circ\mu$.
 

### 2017-10-09 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 state. Since the postulates for QIVPMs in Sec.~\ref{sec:Interval-Uncertainty}
-are also non-constructive, we also want to find a simple rule to construct
-a QIVPM. When we generalize quantum probability measures to QIVPMs,
-we replace the unit interval range~$\left[0,1\right]$ by a set of
-intervals~$\mathscr{I}$. This replacement suggests a function~$\iota$
-mapping a number~$x\in\left[0,1\right]$ to an interval~$\iota\left(x\right)\in\mathscr{I}$.
-The function~$\iota$ can then be concatenated with a quantum probability
-measure~$\mu:\events\rightarrow\left[0,1\right]$ and easily get
-an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$,
+are also non-constructive, we want to find a simple rule to construct
+a QIVPM as well. When we generalized quantum probability measures
+to QIVPMs, we changed the range from the unit interval~$\left[0,1\right]$
+to a set of intervals~$\mathscr{I}$. This replacement suggests us
+to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+which can then be concatenated with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+and easily produce an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$,
 where $\circ$ is the function concatenation. However, the concatenated
@@
 the verification process is long and tedious. Therefore, it is desirable
-to have some easy criteria to get a QIVPM~$\iota\circ\mu$.
+to have some easy criteria to decide when $\iota\circ\mu$ is a QIVPM.
 
@@
 
-Suppose $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
-we can find three particular numbers~$x_{0}'$, $x_{1}'$, and $x_{2}'\in\left[0,1\right]$
-such that $x_{0}'+x_{1}'+x_{2}'\in\left[0,1\right]$, but 
+The proof is by contradiction: Suppose $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
+we can find three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but 
 \[
-\iota\left(x_{0}'+x_{1}'+x_{2}'\right)+\iota\left(x_{2}'\right)\nsubseteq\iota\left(x_{0}'+x_{2}'\right)+\iota\left(x_{1}'+x_{2}'\right)\,.
+\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
 \]
-Consider the state
-\begin{equation}
-\begin{aligned}\rho={} & x_{0}'\proj{0}+x_{1}'\proj{1}+x_{2}'\proj{2}\\
- & +\left(1-x_{0}'-x_{1}'-x_{2}'\right)\proj{3}\,.
-\end{aligned}
-\end{equation}
+Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
 Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}$
 fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-\[
-\begin{aligned} & \mathrel{\hphantom{\nsubseteq}}\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
- & \nsubseteq\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\,,
-\end{aligned}
-\]
+\begin{eqnarray*}
+ &  & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
+ & \nsubseteq & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\,,
+\end{eqnarray*}
 and cannot be a QIVPM. Therefore, to make sure $\iota\circ\mu$ is
@@
 QIVPM, we know $\iota'$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}).
-In order to find $\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
+In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
 we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
@@
 and $\iotar$ is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
-Notice that a Wright-convex function is midpoint-convex or Jensen-convex,
-i.e., 
-\begin{equation}
-\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,,
-\end{equation}
-and a midpoint-convex function is continuous on an open interval if
-we cannot use the Axiom of Choices~\citep{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
+A Wright-convex function is midpoint-convex or Jensen-convex~\citep{RobertsVarberg1973,PecaricTong1992},
+i.e., we have
+\begin{equation}
+\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
+\end{equation}
+A midpoint-convex function is continuous on an open interval if we
+cannot use the Axiom of Choices~\citep{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
 Therefore, the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
 or contains infinitely many intervals.
+
+\yutsung{Another idea might be fixing a quantum probability measure~$\mu$,
+whether there is a length of intervals, such that if $\iota$ mapping
+to a interval tighter than the given length, then $\iota\circ\mu$
+is always a QIVPM... I don't know the answer of this question.}
 

### 2017-10-09 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-which can then be concatenated with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-and easily produce an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$,
-where $\circ$ is the function concatenation. However, the concatenated
+which can be used to replace the probability on a projector, $\mu\left(P\right)$,
+by an interval~$\iota\left(\mu\left(P\right)\right)$. In other words,
+concatenating $\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+produces an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
+which has the same domain and range as a QIVPM. However, the concatenated
 function~$\iota\circ\mu$ may or may not be a QIVPM. For example,
@@
 \begin{equation}
-\iota'\left(x\right)=\begin{cases}
+\iota_{1}\left(x\right)=\begin{cases}
 \imposs\,, & \textrm{ if }x=0\,;\\
@@
 \end{equation}
-While the function~$\iota'\circ\mu_{\rho_{0}}^{\mathrm{\mathrm{B}}}$
+While the function~$\iota_{1}\circ\mu_{\rho_{0}}^{\mathrm{\mathrm{B}}}$
 induced by $\rho_{0}=\frac{1}{4}\cdot\proj{0}+\frac{1}{4}\cdot\proj{1}+\frac{1}{4}\cdot\proj{2}+\frac{1}{4}\cdot\proj{3}$
-is a QIVPM, the function~$\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
+is a QIVPM, the function~$\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
 induced by $\rho_{1}=\frac{1}{8}\cdot\proj{0}+\frac{1}{8}\cdot\proj{1}+\frac{1}{8}\cdot\proj{2}+\frac{5}{8}\cdot\proj{3}$
-is \emph{not} a QIVPM. Although we could verify whether $\iota\circ\mu$
-is a QIVPM or not for any pair of $\iota$ and $\mu$ individually,
-the verification process is long and tedious. Therefore, it is desirable
-to have some easy criteria to decide when $\iota\circ\mu$ is a QIVPM.
+is \emph{not} a QIVPM~\citep{HOSTunpublished}. Although we could
+verify whether $\iota\circ\mu$ is a QIVPM or not for any pair of
+$\iota$ and $\mu$ individually, the verification process is long
+and tedious. Therefore, it is desirable to have some easy criteria
+to decide when $\iota\circ\mu$ is a QIVPM.
 
@@
 
-Since $\iota'$ defined in Eq.~(\ref{eq:iota}) satisfies Eqs.~(\ref{eq:iota-constraints})
-and Eq.~(\ref{eq:iota-add}), every function~$\iota'\circ\mu$ on
-a three-dimensional Hilbert space is a QIVPM. However, on four-dimensional
-Hilbert space, $\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
-is not a QIVPM. This highlight the necessity of the conditions to
+Since $\iota_{1}$ defined in Eq.~(\ref{eq:iota}) satisfies Eqs.~(\ref{eq:iota-constraints})
+and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, every function~$\iota_{1}\circ\mu$
+on a three-dimensional Hilbert space is a QIVPM. However, on four-dimensional
+Hilbert space, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
+is not a QIVPM. This highlights the necessity of the conditions to
 guarantee $\iota\circ\mu$ is always a QIVPM.
 
-\begin{thm}If $\iota\circ\mu:\events\rightarrow\mathscr{I}$ is always
-a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-in any Hilbert space $\Hilb$, then $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-must subject to Eqs.~(\ref{eq:iota-constraints}) and satisfying
-for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
+\begin{thm}The following two statements are equivalent:
+\begin{enumerate}
+\item \label{enu:iota-subject-to}$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+subject to Eqs.~(\ref{eq:iota-constraints}) and satisfying for any
+three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
 $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies
@@
 \end{equation}
+\item \label{enu:iota-mu-QIVPM}$\iota\circ\mu:\events\rightarrow\mathscr{I}$
+is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+in any Hilbert space~$\Hilb$.
+\end{enumerate}
 \end{thm}
 
-The proof is by contradiction: Suppose $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
-we can find three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+It is clear that Statement~\ref{enu:iota-subject-to} implies Statement~\ref{enu:iota-mu-QIVPM},
+and the rest of the proof is to prove the negation of Statement~\ref{enu:iota-subject-to}
+implies the negation of Statement~\ref{enu:iota-mu-QIVPM}. If $\iota$
+doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}), we can find three
+particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
 such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but 
@@
 \end{eqnarray*}
-and cannot be a QIVPM. Therefore, to make sure $\iota\circ\mu$ is
-always a QIVPM, $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ should
-satisfy Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-Inclusion}).
-
-Since $\iota'\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$ is not a
-QIVPM, we know $\iota'$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}).
+and cannot be a QIVPM. Therefore, Statement~\ref{enu:iota-subject-to}
+is true if and only if Statement~\ref{enu:iota-mu-QIVPM} is true.
+
+Since $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$ is not
+a QIVPM, we know $\iota_{1}$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}).
 In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
@@
 and $\iotar$ is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
-A Wright-convex function is midpoint-convex or Jensen-convex~\citep{RobertsVarberg1973,PecaricTong1992},
+A Wright-convex function is midpoint-convex or Jensen-convex~\citep{Jensen_1906,Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
 i.e., we have

### 2017-10-10 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-which can be used to replace the probability on a projector, $\mu\left(P\right)$,
-by an interval~$\iota\left(\mu\left(P\right)\right)$. In other words,
-concatenating $\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+which can be used to replace a real-valued probability~$\mu\left(P\right)$
+by an interval-valued one~$\iota\left(\mu\left(P\right)\right)$.
+In other words, compositing $\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
 produces an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
-which has the same domain and range as a QIVPM. However, the concatenated
+which has the same domain and range as a QIVPM. However, the composited
 function~$\iota\circ\mu$ may or may not be a QIVPM. For example,
@@
 induced by $\rho_{1}=\frac{1}{8}\cdot\proj{0}+\frac{1}{8}\cdot\proj{1}+\frac{1}{8}\cdot\proj{2}+\frac{5}{8}\cdot\proj{3}$
-is \emph{not} a QIVPM~\citep{HOSTunpublished}. Although we could
-verify whether $\iota\circ\mu$ is a QIVPM or not for any pair of
-$\iota$ and $\mu$ individually, the verification process is long
-and tedious. Therefore, it is desirable to have some easy criteria
-to decide when $\iota\circ\mu$ is a QIVPM.
+is \emph{not} a QIVPM~\citep{HOSTunpublished}. In order not to verify
+whether $\iota\circ\mu$ is a QIVPM for each individual case, it is
+desirable to have some criteria to discriminate different cases. We
+will start from the simpler criteria for the dimension~$d\le3$,
+and then the general case.
 
@@
 \item Their complements~$\mathbb{1}-P_{0}$ and $\mathbb{1}-P_{1}$ are
-orthogonal so that we can apply Eq.~(\ref{eq:iota-add}) on their
-complements.
+orthogonal.
 \item One of them projects onto a subspace of what the other one projects
@@
 \begin{enumerate}
-\item \label{enu:iota-subject-to}$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+\item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 subject to Eqs.~(\ref{eq:iota-constraints}) and satisfying for any
@@
 \begin{equation}
-\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
-\end{equation}
-\item \label{enu:iota-mu-QIVPM}$\iota\circ\mu:\events\rightarrow\mathscr{I}$
+\begin{aligned} & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
+\subseteq{} & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
+\end{aligned}
+\label{eq:iota-Inclusion}
+\end{equation}
+\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
 is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-in any Hilbert space~$\Hilb$.
+on any Hilbert space~$\Hilb$.
 \end{enumerate}
@@
 It is clear that Statement~\ref{enu:iota-subject-to} implies Statement~\ref{enu:iota-mu-QIVPM},
-and the rest of the proof is to prove the negation of Statement~\ref{enu:iota-subject-to}
-implies the negation of Statement~\ref{enu:iota-mu-QIVPM}. If $\iota$
-doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}), we can find three
-particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
-such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but 
-\[
-\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
-\]
+and the rest of the proof is to prove that if Statement~\ref{enu:iota-subject-to}
+is false, then Statement~\ref{enu:iota-mu-QIVPM} is false as well.
+If $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}), we can
+find three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
 Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
@@
 we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
-They are both usual functions from a unit interval to another unit
-interval. Eq.~(\ref{eq:iota-Inclusion}) then implies that $\iotal$
-is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
+They both map from a unit interval to another unit interval. Eq.~(\ref{eq:iota-Inclusion})
+then implies that $\iotal$ is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
 and $\iotar$ is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
-A Wright-convex function is midpoint-convex or Jensen-convex~\citep{Jensen_1906,Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
+It is well-known that a Wright-convex function is midpoint-convex
+or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
 i.e., we have
@@
 \end{equation}
-A midpoint-convex function is continuous on an open interval if we
-cannot use the Axiom of Choices~\citep{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
-Therefore, the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
-or contains infinitely many intervals.
+Furthermore, a midpoint-convex function is either continuous on $\left(0,1\right)$
+or Lebesgue non-measurable~\citep{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
+When $\iotal$ is Lebesgue non-measurable,
+
+When $\iotal$ is continuous, the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
+or contains uncountably many intervals.
 

### 2017-10-10 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 \begin{thm}\label{thm:QRVPM2QIVPM-3}In a Hilbert space of dimension~$d\le3$,
-if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ subject to the
+if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is subject to the
 following constraints:\begin{subequations}\label{eq:iota-constraints}
@@
 \end{eqnarray}
-\end{subequations}and satisfying for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
-$x_{0}+x_{1}\in\left[0,1\right]$ implies
+\end{subequations}and satisfies that for any numbers~$x_{0}$ and
+$x_{1}\in\left[0,1\right]$, $x_{0}+x_{1}\in\left[0,1\right]$ implies
 \begin{equation}
@@
 
-\begin{thm}The following two statements are equivalent:
+\begin{thm}\label{thm:iota-statements}The following two statements
+are equivalent:
 \begin{enumerate}
 \item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-subject to Eqs.~(\ref{eq:iota-constraints}) and satisfying for any
-three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
+is subject to Eqs.~(\ref{eq:iota-constraints}) and satisfies that
+for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
 $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies
@@
 we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
-They both map from a unit interval to another unit interval. Eq.~(\ref{eq:iota-Inclusion})
-then implies that $\iotal$ is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
-and $\iotar$ is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
+By Eq.~(\ref{eq:iota-Inclusion}), the left-end~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
+is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
+and the right-end~$\iotar:\left[0,1\right]\rightarrow\left[0,1\right]$
+is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
 It is well-known that a Wright-convex function is midpoint-convex
@@
 \end{equation}
-Furthermore, a midpoint-convex function is either continuous on $\left(0,1\right)$
-or Lebesgue non-measurable~\citep{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
-When $\iotal$ is Lebesgue non-measurable,
-
-When $\iotal$ is continuous, the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
-or contains uncountably many intervals.
+Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
+$\iotal$ must be continuous on the unit open interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}
+which implies the number of intervals that $\iota$ maps to must be
+uncountable.
+
+\begin{thm}If $\iota$ satisfies the Statements in Thm.~\ref{thm:iota-statements},
+then the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
+or contains uncountably many intervals.\end{thm}
 

### 2017-10-10 prop_letter.tex
prop_letter.tex \section{Gleason} Clean up the part moved to Born Sec.

@@
 
-\section{Born}
+\section{Born\label{sec:Born}}
 
@@
 the Born rule which induces a quantum probability measures from each
-state. Since the postulates for QIVPMs in Sec.~\ref{sec:Interval-Uncertainty}
+state~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. Since
+the postulates for QIVPMs in Sec.~\ref{sec:Interval-Uncertainty}
 are also non-constructive, we want to find a simple rule to construct
@@
 
+\yutsung{The other idea: We never proved or find an counterexample
+that a non-convex QIVPM has empty core, and its expectation value
+is not the same as defined from core... If it is true, the convex
+condition may not be necessary, but this might be hard to prove...}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In this section, we want to shift our attention to consider states
-consistent with $\bar{\mu}$ on \emph{every} event, $\coreBorn\left(\bar{\mu},\events\right)$,
-so that these states could characterize $\bar{\mu}$ comprehensively.
+consistent with $\bar{\mu}$ on \emph{every} event, $\coreBorn\left(\bar{\mu},\events\right)$.
 When the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
@@
 Gleason's theorem claims that there is always a unique state consistent
-with $\bar{\mu}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum},
-and this state can easily induce $\bar{\mu}$ according to the Born
-rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. However,
-if we consider general QIVPMs mapping to an \emph{arbitrary} set of
-intervals, there is a QIVPM that no state can be consistent with it.
+with $\bar{\mu}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+
+\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
+a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
+the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
+is unique. \end{thm}
+
+\noindent However, if we consider general QIVPMs mapping to an \emph{arbitrary}
+set of intervals, there is a QIVPM that no state can be consistent
+with it.
 
@@
 results we get might contradict to each other, and exclude any possible
-state from being consistent with the measurement results. We will
-address this problem with a concrete family of intervals and QIVPMs,
-and leave for another time the general framework~\citep{HOSTunpublished}.
-Consider the following intervals 
-\begin{equation}
-\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
- & \cup\{\imposs,\necess\}
-\end{aligned}
-\end{equation}
-which are overlapping intervals with length~$1/n$ except for the
-intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
-in Table~\ref{tab:I_n}, for each interval~$[\ell,r]$, we define
-$\textrm{Int}\left([\ell,r]\right)$, the non-overlapping interior
-part of $[\ell,r]$.
-\begin{table}
-\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
-their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
-means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
-their interiors~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}
-
-\begin{tabular}{cccc}
-\toprule 
-\addlinespace
-$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
- & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-\begin{tabular}{c}
-$0<k<2n$\tabularnewline
-and $2\nmid k$\tabularnewline
-\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-\begin{tabular}{c}
-$0<k<2n$\tabularnewline
-and $2\mid k$\tabularnewline
-\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
- & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
-Since their interior parts are non-overlapping, we can define a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
-by $\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$
-to map a real-valued probability to an interval-valued one. This function
-can then induce a QIVPM from a state according to the following theorem:
-
-\begin{thm}[A finite-precision Extension of the Born rule]\label{thm:Finite-precision-Born}For
-any state $\rho$ on a three-dimensional Hilbert space, a function~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}:\events\rightarrow\mathscr{I}_{n}$
-defined by $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}\left(P\right)=\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
-is a QIVPM, called a Born QIVPM.\end{thm}
-
-To prove that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$ is a QIVPM,
-it is sufficient to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
-Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$,
-\begin{equation}
-\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\label{eq:iota-add-1}
-\end{equation}
-implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
-are not orthogonal on a three-dimensional Hilbert space, we have two
-possibilities:
-\begin{itemize}
-\item Their complements~$\mathbb{1}-P_{0}$ and $\mathbb{1}-P_{1}$ are
-orthogonal so that we can apply Eq.~(\ref{eq:iota-add-1}) on their
-complements.
-\item One of them projects onto a subspace of what the other one projects
-onto.
-\end{itemize}
-\noindent Both cases deduce Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-easily~\citep{HOSTunpublished} so that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
-is indeed a QIVPM.
-
-In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-there is always a state consistent with a Born QIVPM $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
-because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$.
+state from being consistent with the measurement results. In contrast
+with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM}, if a QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$
+is induced by a conventional quantum probability measure~$\mu_{\rho}^{\mathrm{B}}$
+and a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ defined
+in Sec.~\ref{sec:Born}, there is always a state consistent with
+it because $\rho\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
 Moreover, with respect to a notion of distance between two states~$\rho$
@@
 \end{equation}
-the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
+the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
 gets closer and closer to $\rho$ as the intervals get narrower and
@@
 \begin{thm}[A finite-precision extension of weak Gleason's theorem
-for Born QIVPMs]\label{thm:Finite-precision-Gleason}In a three-dimensional
-Hilbert space, given any state~$\rho$, if a state $\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
-then their distance $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}
-
-\noindent Given a state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
-we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
+for Born QIVPMs]\label{thm:Finite-precision-Gleason}Consider a three-dimensional
+Hilbert space, and an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
+Given any state~$\rho$, if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+then their distance $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}
+
+\noindent Given a state~$\rho'$ consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
+we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
 for any 1-dimensional projector~$\proj{\psi}$. Since the maximum
-length of the intervals in $\mathscr{I}_{n}$ is $1/n$, it is also
+length of the intervals in $\mathscr{I}$ is $\delta$, it is also
 the upper bound of the difference $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
- This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$ by
-definition.
-
-In the limiting case when the intervals are infinitely precise real
-numbers covering the real line, the original Gleason theorem is recovered,
-and can be formulated in our framework as follows.
-
-\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
-a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
-the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
-is unique. \end{thm}
+This implies $\left\Vert \rho-\rho'\right\Vert \le\delta$ by definition.
 

### 2017-10-10 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 Hilbert space, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
-is not a QIVPM. This highlights the necessity of the conditions to
-guarantee $\iota\circ\mu$ is always a QIVPM.
+is not a QIVPM. This highlights the necessity to have conditions disregarding
+the dimension of the Hilbert space.
 
@@
 \item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-is subject to Eqs.~(\ref{eq:iota-constraints}) and satisfies that
-for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
-$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies
+satisfies Eqs.~(\ref{eq:iota-constraints}) and for any three numbers~$x_{0}$,
+$x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
+implies
 \begin{equation}

### 2017-10-11 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 
-Since $\iota_{1}$ defined in Eq.~(\ref{eq:iota}) satisfies Eqs.~(\ref{eq:iota-constraints})
-and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, every function~$\iota_{1}\circ\mu$
-on a three-dimensional Hilbert space is a QIVPM. However, on four-dimensional
-Hilbert space, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
-is not a QIVPM. This highlights the necessity to have conditions disregarding
-the dimension of the Hilbert space.
+On the one hand, $\iota_{1}$ defined in Eq.~(\ref{eq:iota}) satisfies
+Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}
+so that every function~$\iota_{1}\circ\mu$ on a three-dimensional
+Hilbert space is a QIVPM. On the other hand, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
+is not a QIVPM on four-dimensional Hilbert space. Therefore, we need
+to strengthen Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add})
+to guarantee $\iota\circ\mu$ is always a QIVPM.
 
@@
 
-Since $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$ is not
-a QIVPM, we know $\iota_{1}$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}).
 In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
 we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
-By Eq.~(\ref{eq:iota-Inclusion}), the left-end~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
+By Eq.~(\ref{eq:iota-Inclusion}), the left-end function~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
 is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
-and the right-end~$\iotar:\left[0,1\right]\rightarrow\left[0,1\right]$
+and the right-end function~$\iotar:\left[0,1\right]\rightarrow\left[0,1\right]$
 is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
@@
 Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
-$\iotal$ must be continuous on the unit open interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}
+the left-end function~$\iotal$ must be continuous on the unit open
+interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}
 which implies the number of intervals that $\iota$ maps to must be
@@
 
-\begin{thm}If $\iota$ satisfies the Statements in Thm.~\ref{thm:iota-statements},
-then the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
-or contains uncountably many intervals.\end{thm}
+\begin{thm}For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $
+or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
 

### 2017-10-11 prop_letter.tex
prop_letter.tex \section{Born} and \section{Gleason} Updating...

@@
 Hilbert space is a QIVPM. On the other hand, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
-is not a QIVPM on four-dimensional Hilbert space. Therefore, we need
-to strengthen Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add})
-to guarantee $\iota\circ\mu$ is always a QIVPM.
+is not a QIVPM on four-dimensional Hilbert space. Hence, to guarantee
+$\iota\circ\mu$ is always a QIVPM, we need to strengthen Eq.~(\ref{eq:iota-add})
+and consider the following conditions.
 
@@
 the left-end function~$\iotal$ must be continuous on the unit open
-interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}
-which implies the number of intervals that $\iota$ maps to must be
-uncountable.
-
-\begin{thm}For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $
-or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
+interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
+Therefore, either $\iota$ maps every number in the same interval,
+or the number of intervals that $\iota$ maps to must be uncountable.
+
+\begin{thm}\label{thm:convex-uncountable}Let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $.
+For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}$
+is $\mathscr{I}_{0}$ or $\mathscr{I}$ contains uncountably many
+intervals.\end{thm}
 
 \yutsung{Another idea might be fixing a quantum probability measure~$\mu$,
-whether there is a length of intervals, such that if $\iota$ mapping
-to a interval tighter than the given length, then $\iota\circ\mu$
-is always a QIVPM... I don't know the answer of this question.}
+whether there is a length of intervals, such that if $\iota$ maps
+to intervals tighter than the given length, then $\iota\circ\mu$
+is always a QIVPM... I don't know the answer of this question, and
+it might not be very easy...}
 
@@
 
-\noindent However, if we consider general QIVPMs mapping to an \emph{arbitrary}
+However, if we consider general QIVPMs mapping to an \emph{arbitrary}
 set of intervals, there is a QIVPM that no state can be consistent
@@
 an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
-let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
-$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
+let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$ and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
 The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
-in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished}.
+in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished},
+where $\mathscr{I}_{0}$ is defined in Thm.~\ref{thm:convex-uncountable}.
 \begin{table}
@@
 is induced by a conventional quantum probability measure~$\mu_{\rho}^{\mathrm{B}}$
-and a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ defined
+and a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ considered
 in Sec.~\ref{sec:Born}, there is always a state consistent with
 it because $\rho\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
-Moreover, with respect to a notion of distance between two states~$\rho$
-and $\rho'$~\citep{544199}, 
-\begin{equation}
-\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\,,\label{eq:norm}
-\end{equation}
-the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
+Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
 gets closer and closer to $\rho$ as the intervals get narrower and
-narrower.
+narrower. To state this result, we introduce a few technical notions.
+First, the norm of a pure state is defined as usual $||\psi||=\sqrt{\ip{\psi}{\psi}}$.
+Then, the norm of the difference of two states~$\rho$ and $\rho'$
+is just the usual operator norm
+\begin{equation}
+\left\Vert \rho-\rho'\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert \left(\rho-\rho'\right)\ket{\psi}\right\Vert \,,
+\end{equation}
+which is also commonly known as $L^{2}$ norm or spectral norm~\citep{GolubVanLoan1996,Foucart2012}.
 
@@
 Given any state~$\rho$, if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-then their distance $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}
-
-\noindent Given a state~$\rho'$ consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
+then the norm of their difference is $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}
+
+Given a state~$\rho'$ consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
 we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
@@
 the upper bound of the difference $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
+Since $\rho-\rho'$ is Hermitian, $\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$is
+the maximum absolute value of the eigenvalues of $\rho-\rho'$~\citep{544199},
+and equal to $\left\Vert \rho-\rho'\right\Vert $~\citep{GolubVanLoan1996,Foucart2012}.
 This implies $\left\Vert \rho-\rho'\right\Vert \le\delta$ by definition.
-
-\yutsung{Following are the discussion and personal notes about our
-norm and other notation of norm and distance.}
-
-Nielsen and Chuang~\citep{544199} defined their norm~(\ref{eq:norm})
-in Appendix~6. While their Appendix~6 followed Simon~\citep{Simon2005}
-and Uhlmann~\citep{Uhlmann1977} to prove Lieb's theorem~\citep{Lieb_1973,544199,Simon2005},
-Simon~\citep{Simon2005} and Uhlmann~\citep{Uhlmann1977} didn't
-explicitly define the norm as in Eq.~(\ref{eq:norm}) although Simon
-used the same norm thoroughly in his book~\citep{Simon2005}. There
-are two possibilities:
-\begin{enumerate}
-\item Simon really used Eq.~(\ref{eq:norm}) to define his norm.\\
-If this is true, there must be some books cited by Simon, and defined
-the norm in the same way.
-\item The norm Simon used is different from Eq.~(\ref{eq:norm}), and Nielsen
-and Chuang defined this norm from nowhere in order to write a proof
-of Lieb's theorem.\\
-If this is true, Nielsen and Chuang might be the \emph{only} literature
-which used this norm. We might have no other literature to check the
-properties of this norm and other distances, and need to prove the
-properties of this norm by ourselves.
-\end{enumerate}
-In order to understand this norm and compare with others, the following
-are useful facts. Let $\sigma\left(\rho-\rho'\right)$ denote the
-set of eigenvalues of $\rho-\rho'$. Since $\rho$ and $\rho'$ are
-states, they are Hermitian~\citep{544199}, and so does $\rho-\rho'$.
-In this situation~\citep{544199}, 
-\begin{equation}
-\left\Vert \rho-\rho'\right\Vert =\max_{\lambda\in\sigma\left(\rho-\rho'\right)}\left|\lambda\right|
-\end{equation}
-which is just its spectral radius or spectral norm~\citep{GolubVanLoan1996,Foucart2012}
-\begin{equation}
-\max_{\left\Vert \ket{\psi}\right\Vert =1}\left\Vert \left(\rho-\rho'\right)\ket{\psi}\right\Vert \,.
-\end{equation}
-For their trace distance~\citep{544199}
-\begin{equation}
-D\left(\rho,\rho'\right)=\frac{1}{2}\Tr\left[\sqrt{\left(\rho-\rho'\right)^{2}}\right]=\frac{1}{2}\sum_{\lambda\in\sigma\left(\rho-\rho'\right)}\left|\lambda\right|\,,
-\end{equation}
-since it can also be represented as the eigenvalue of $\rho-\rho'$.
-It should not be hard to estimate their trace distance based on their
-norm.
-
-\yutsung{End of discussion.}
 

### 2017-10-12 prop_letter.tex
prop_letter.tex \section{Born} and \section{Gleason} Updating...

@@
 interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
-Therefore, either $\iota$ maps every number in the same interval,
+Therefore, either $\iota$ maps every number to the same interval,
 or the number of intervals that $\iota$ maps to must be uncountable.
 
-\begin{thm}\label{thm:convex-uncountable}Let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $.
+\begin{thm}\label{thm:convex-uncountable}Let 
+\[
+\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.
+\]
 For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}$
-is $\mathscr{I}_{0}$ or $\mathscr{I}$ contains uncountably many
-intervals.\end{thm}
+described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\mathscr{I}_{0}$
+or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
 
@@
 
-\yutsung{The other idea: We never proved or find an counterexample
-that a non-convex QIVPM has empty core, and its expectation value
-is not the same as defined from core... If it is true, the convex
-condition may not be necessary, but this might be hard to prove...}
+\yutsung{The other idea: We never proved a non-convex QIVPM always
+have a non-empty core or find an counterexample that a non-convex
+QIVPM has empty core. Moreover, we have no idea the relation between
+its expectation value and the Choquet integral... Depending the on
+situation, the convex condition may not be necessary, but this might
+be hard to prove...}
 
@@
 \end{equation}
-which is also commonly known as $L^{2}$ norm or spectral norm~\citep{GolubVanLoan1996,Foucart2012}.
-
-\begin{thm}[A finite-precision extension of weak Gleason's theorem
-for Born QIVPMs]\label{thm:Finite-precision-Gleason}Consider a three-dimensional
-Hilbert space, and an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
-Given any state~$\rho$, if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+which is also commonly known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+
+\begin{thm}[A finite-precision extension of weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
+a three-dimensional Hilbert space, and an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+with the maximum length of intervals $\delta$. Given any state~$\rho$,
+if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
 then the norm of their difference is $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}
@@
 the upper bound of the difference $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
-Since $\rho-\rho'$ is Hermitian, $\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$is
-the maximum absolute value of the eigenvalues of $\rho-\rho'$~\citep{544199},
+Since $\rho-\rho'$ is Hermitian, $\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
+is the maximum absolute value of the eigenvalues of $\rho-\rho'$~\citep{544199},
 and equal to $\left\Vert \rho-\rho'\right\Vert $~\citep{GolubVanLoan1996,Foucart2012}.
-This implies $\left\Vert \rho-\rho'\right\Vert \le\delta$ by definition.
+Hence, $\left\Vert \rho-\rho'\right\Vert \le\delta$.
 

### 2017-10-12 prop_letter.tex
prop_letter.tex \section{Born} Updating...

@@
 \end{subequations}and satisfies that for any numbers~$x_{0}$ and
-$x_{1}\in\left[0,1\right]$, $x_{0}+x_{1}\in\left[0,1\right]$ implies
+$x_{1}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}\in\left[0,1\right]$
+implies
 \begin{equation}
@@
 space, to prove that $\iota\circ\mu$ is a QIVPM, it is sufficient
-to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}):
+to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
 \begin{equation}
@@
 satisfies Eqs.~(\ref{eq:iota-constraints}) and for any three numbers~$x_{0}$,
-$x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
+$x_{1}$, and $x_{2}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
 implies
@@
 By Eq.~(\ref{eq:iota-Inclusion}), the left-end function~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
-is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
-and the right-end function~$\iotar:\left[0,1\right]\rightarrow\left[0,1\right]$
-is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
+is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992}.
 It is well-known that a Wright-convex function is midpoint-convex
@@
 \begin{thm}\label{thm:convex-uncountable}Let 
-\[
+\begin{equation}
 \mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.
-\]
+\end{equation}
 For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$

### 2017-10-12 prop_letter.tex
prop_letter.tex \section{Born} and \section{Gleason} Updating...

@@
 \begin{equation}
-\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.
+\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
 \end{equation}
@@
 in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished},
-where $\mathscr{I}_{0}$ is defined in Thm.~\ref{thm:convex-uncountable}.
+where $\mathscr{I}_{0}$ is defined in Eq.~(\ref{eq:3-value-intervals}).
 \begin{table}
@@
 narrower. To state this result, we introduce a few technical notions.
-First, the norm of a pure state is defined as usual $||\psi||=\sqrt{\ip{\psi}{\psi}}$.
-Then, the norm of the difference of two states~$\rho$ and $\rho'$
-is just the usual operator norm
+First, the norm of a pure state~$\ket{\psi}$ is defined as usual
+$||\psi||=\sqrt{\ip{\psi}{\psi}}$. Then, the norm of the difference
+of two states~$\rho$ and $\rho'$ is just the usual operator norm
 \begin{equation}

### 2017-10-14 prop_iop.tex
Updates from ShareLaTeX
prop_letter.tex \section{Gleason} Clean up the part moved to Born Sec.
prop_iop.tex \subsection{Application on Convexity} Updating...

@@
 resources. \ldots{}
+
+\yutsung{If the core is non-empty, could the core characterize $\bar{\mu}$
+comprehensively?}
 
@@
 
-\begin{lemma}Given a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
-if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ are all
-convex for any orthonormal basis~$\Omega$, then $\bar{\mu}$ is
-convex.\end{lemma}
+\begin{lemma}\label{lemma:classical-quantum-convex}Given a quantum
+IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
+are all convex for any orthonormal basis~$\Omega$, then $\bar{\mu}$
+is convex.\end{lemma}
 
@@
 
-\begin{lemma}When the number of elements in $\Omega$ is less than
-or equal to 3, every classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
-is convex.\end{lemma}
+\begin{lemma}\label{lemma:classical-convex-condition-lemma}Given
+a classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$,
+the following statements are true:
+\begin{enumerate}
+\item If $E_{0}\subseteq E_{1}$, then $\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)$.
+\item If $\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)$,
+then $\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup\overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap\overline{E_{1}}\right)\subseteq\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)$,
+where $\overline{E_{0}}=\Omega\backslash E_{0}$ and $\overline{E_{1}}=\Omega\backslash E_{1}$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+\begin{enumerate}
+\item $\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)=\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)$.
+\item 
+\begin{equation}\eqalign{ 
+ & \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\\
+\Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\cap \overline{E_{1}}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\cup \overline{E_{1}}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{1}}\right)\right)\\
+\Rightarrow & 2-\left[\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap \overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup \overline{E_{1}}\right)\right]\subseteq2-\left[\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)\right]\\
+\Rightarrow & \bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap \overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup \overline{E_{1}}\right)\subseteq\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)\,.
+}\end{equation}
+\end{enumerate}
+\end{proof}
+
+\begin{lemma}\label{lemma:classical-3-elements}When the number of
+elements in $\Omega$ is less than or equal to 3, every classical
+IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ is convex.\end{lemma}
 
@@
 \end{equation}
-When $E_{0}\cap E_{1}=\emptyset$, equation~(\ref{eq:classical-convex})
-is a special case of equation~(\ref{eq:classical-include}). When
-$E_{0}\cup E_{1}=\Omega$, we have $E_{0}^{c}\cap E_{1}^{c}=\emptyset$,
-where $E_{0}^{c}=\Omega\backslash E_{0}$ and $E_{1}^{c}=\Omega\backslash E_{1}$.
-Thus, 
-\begin{equation}\eqalign{ 
-& \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\
-\Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\
-\Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\,. 
-}\end{equation}
 When the number of elements in $\Omega\le3$, one of the following
@@
 \begin{enumerate}
-\item $E_{0}\cap E_{1}=\emptyset$.
-\item $E_{0}\cup E_{1}=\Omega$.
-\item $E_{0}\subseteq E_{1}$ or $E_{1}\subseteq E_{0}$.
+\item When $E_{0}\cap E_{1}=\emptyset$, equation~(\ref{eq:classical-convex})
+is a special case of equation~(\ref{eq:classical-include}). 
+\item When $E_{0}\cup E_{1}=\Omega$, we have $\overline{E_{0}}\cap\overline{E_{1}}=\emptyset$,
+where $\overline{E_{0}}=\Omega\backslash E_{0}$ and $\overline{E_{1}}=\Omega\backslash E_{1}$.
+By equation~(\ref{eq:classical-include}), we have $\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup\overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap\overline{E_{1}}\right)\subseteq\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)$.
+Then, lemma~\ref{lemma:classical-convex-condition-lemma} proves
+equation~(\ref{eq:classical-convex}).
+\item When $E_{0}\subseteq E_{1}$ or $E_{1}\subseteq E_{0}$, equation~(\ref{eq:classical-convex})
+is also followed by lemma~\ref{lemma:classical-convex-condition-lemma}.
 \end{enumerate}
-so that $\bar{\mu}^{\Omega}$ is convex. \end{proof}
+so that $\bar{\mu}^{\Omega}$ is convex.\end{proof}
+
+\begin{lemma}\label{lemma:quantum-convex-condition-lemma}Given a
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, the following statements
+are true:
+\begin{enumerate}
+\item If $P_{1}=P_{0}+P_{2}$, then $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
+\item If $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
+then $\bar{\mu}\left(\overline{P_{0}}\vee\overline{P_{1}}\right)+\bar{\mu}\left(\overline{P_{0}}\overline{P_{1}}\right)\subseteq\bar{\mu}\left(\overline{P_{0}}\right)+\bar{\mu}\left(\overline{P_{1}}\right)$,
+where $\overline{P_{0}}=\Omega\backslash P_{0}$ and $\overline{P_{1}}=\Omega\backslash P_{1}$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}The direct consequence of lemma~\ref{lemma:classical-convex-condition-lemma}
+and theorem~\ref{thm:sub-event-space}.\end{proof}
 
@@
 
-\begin{proof}The direct consequence of the previous lemmas. \end{proof}
+\begin{proof}The direct consequence of lemma~\ref{lemma:classical-quantum-convex}
+and lemma~\ref{lemma:classical-3-elements}. \end{proof}
 

### 2017-10-14 prop_iop.tex
prop_iop.tex \subsection{Convexity and Core} Updating...

@@
 
-\begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
-There is a convex quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.\end{thm}
-
-This theorem could be proved by constructing the following convex
-quantum interval-valued probability measure with an empty core.
+\begin{thm}[Empty core for general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
+a Hilbert space of dimension~$d$, there exists a convex QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
+
+\begin{proof}To prove the theorem, we first need to construct a QIVPM,
+and then verify that no states consistent with it on all projectors.
+Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2},\ldots,\ket{d-1}\right\} $,
+let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$ and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
+Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+defined in Table~\ref{tab:non-Born-QIVPM}, where $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $.
+\begin{table}
+\caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+on the three-dimensional Hilbert space. The projectors mapping to
+the same interval are listed in the column labeled by $P$ and separated
+by commas.}
+\centering{}%
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
+$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+All other projectors & $\unknown$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+The situation when $d=3$ is illustrated in figure~\ref{fig:three-dimensional-3-value-2}.
 \begin{figure}
@@
 \par\end{centering}
-\caption{\label{fig:three-dimensional-3-value-2}This figure illustrates example~\ref{ex:three-dimensional-three-value}
+\caption{\label{fig:three-dimensional-3-value-2}This figure illustrates theorem~\ref{thm:Non-extensible-of-Gleason's}
 plotted in $\mathbb{R}^{3}$. The red, green, and blue vectors are
@@
 \end{figure}
-
-\begin{example}[Three-dimensional quantum three-interval-valued probability
-measure]\label{ex:three-dimensional-three-value} Given a three dimensional
-Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
-$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and 
+To verify $\bar{\mu}$ be a convex QIVPM, it is sufficient to verify
+equation~(\ref{eq:QuantumInterval-valuedProbability-Convex}). There
+are several cases:
+\begin{itemize}
+\item When $P_{0}=\mathbb{0}$, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+holds by lemma~\ref{lemma:quantum-convex-condition-lemma}. This
+lemma also implies equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+is true when when $P_{0}=\mathbb{1}$.
+\item When $P_{0}=\proj{0}$, if $P_{1}=\proj{0}+P_{2}$, then equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+holds by lemma~\ref{lemma:quantum-convex-condition-lemma}. Otherwise,
+we have $P_{0}P_{1}=\mathbb{0}$, and $\bar{\mu}\left(P_{0}P_{1}\right)=\bar{\mu}\left(P_{0}\right)=\imposs$.
+There are two cases:
+\begin{itemize}
+\item When $P_{1}=\mathbb{1}-\proj{0}$, we have
 \begin{equation}\eqalign{ 
-\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\,,\\ 
-\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\,,\\ 
-\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
+ & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\bar{\mu}\left(\mathbb{1}\right)+\bar{\mu}\left(\mathbb{0}\right)\\
+={} & \bar{\mu}\left(\mathbb{1}-\proj{0}\right)+\bar{\mu}\left(\proj{0}\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
 }\end{equation}
-It is straightforward to verify that $\bar{\mu}$ is a quantum interval-valued
-probability measure by theorem~\ref{thm:interval-valued-frame-function}
-and convex by theorem~\ref{thm:convex-3}. Now assume there exists
-a real-valued quantum probability measure $\mu$ such that $\mu(P)\in\bar{\mu}(P)$
-for every event (projection)~$P$. We derive a contradiction as follows.
-Suppose $\mu(P)\in\bar{\mu}(P)$ then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
-By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
-such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
-can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
-\end{example}
+\item When $P_{1}\ne\mathbb{1}-\proj{0}$, we have
+\begin{equation}
+\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\unknown+\imposs=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
+\end{equation}
+\end{itemize}
+Therefore, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+holds when $P_{0}=\proj{0}$. Similarly, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+holds when $P_{0}=\proj{\ps}$ or $P_{0}=\proj{\ps'}$. By lemma~\ref{lemma:quantum-convex-condition-lemma},
+equation~(\ref{eq:QuantumInterval-valuedProbability-Convex}) is
+also true when when $P_{0}=\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$,
+or $\mathbb{1}-\proj{\ps'}$.
+\item If neither the above two cases holds, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\unknown+\unknown=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
+\end{itemize}
+Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
+empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
+for any~$P$, the state~$\rho$ must satisfy: 
+\begin{equation}
+\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
+\end{equation}
+which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
+for all $j$. The last equation never holds proving the theorem.\end{proof}
 

### 2017-10-14 prop_letter.tex
prop_letter.tex \section{Gleason} Add a comment...
prop_letter.tex \section{Gleason} Updating...

@@
 \begin{equation}
-\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
+\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.
 \end{equation}
@@
 \begin{thm}[Empty core for general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
-a three-dimensional Hilbert space, there exists a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+a Hilbert space of dimension~$d$, there exists a convex QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
@@
 verify that no states consistent with it on all projectors. Given
-an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
+an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2},\ldots,\ket{d-1}\right\} $,
 let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$ and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
@@
 in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished},
-where $\mathscr{I}_{0}$ is defined in Eq.~(\ref{eq:3-value-intervals}).
+where
+\begin{equation}
+\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
+\end{equation}
 \begin{table}

### 2017-10-15 prop_iop.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \begin{thm}[Empty core for general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
-a Hilbert space of dimension~$d$, there exists a convex QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+a Hilbert space of dimension~$d\ge3$, there exists a convex QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
@@
 Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2},\ldots,\ket{d-1}\right\} $,
-let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$ and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
+let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
+and $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $.
 Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
-defined in Table~\ref{tab:non-Born-QIVPM}, where $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $.
+defined in Table~\ref{tab:non-Born-QIVPM}
 \begin{table}

### 2017-10-15 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 are also non-constructive, we want to find a simple rule to construct
-a QIVPM as well. When we generalized quantum probability measures
-to QIVPMs, we changed the range from the unit interval~$\left[0,1\right]$
-to a set of intervals~$\mathscr{I}$. This replacement suggests us
-to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-which can be used to replace a real-valued probability~$\mu\left(P\right)$
-by an interval-valued one~$\iota\left(\mu\left(P\right)\right)$.
-In other words, compositing $\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-produces an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
-which has the same domain and range as a QIVPM. However, the composited
-function~$\iota\circ\mu$ may or may not be a QIVPM. For example,
-in a four-dimensional Hilbert space, consider the function 
+a QIVPM as well.
+
+However, the composited function~$\iota\circ\mu$ may or may not
+be a QIVPM. For example, in a four-dimensional Hilbert space, consider
+the function 
 \begin{equation}
@@
 \begin{thm}[Empty core for general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
-a Hilbert space of dimension~$d$, there exists a convex QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+a Hilbert space of dimension~$d\ge3$, there exists a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
@@
 an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2},\ldots,\ket{d-1}\right\} $,
-let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$ and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
+let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
+and
+\begin{equation}
+\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
+\end{equation}
 The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
-in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished},
-where
-\begin{equation}
-\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
-\end{equation}
+in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished}.
 \begin{table}
@@
 results we get might contradict to each other, and exclude any possible
-state from being consistent with the measurement results. In contrast
-with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM}, if a QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$
-is induced by a conventional quantum probability measure~$\mu_{\rho}^{\mathrm{B}}$
-and a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ considered
-in Sec.~\ref{sec:Born}, there is always a state consistent with
-it because $\rho\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
+state from being consistent with the measurement results. To address
+this problem, we are going to consider a particular family of QIVPMs
+induced by quantum probability measures. When we generalized quantum
+probability measures to QIVPMs, we changed the range from the unit
+interval~$\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
+This replacement suggests us to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+which can be used to replace a real-valued probability~$\mu\left(P\right)$
+by an interval-valued one~$\iota\left(\mu\left(P\right)\right)$.
+In other words, compositing $\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+produces an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
+which has the same domain and range as a QIVPM. Although there are
+infinitely many different choice of $\iota$, the function~$\iota$
+satisfies the following homomorphism-like properties are of particular
+interest, because it guarantee $\iota\circ\mu$ is always a QIVPM.
+
+\begin{definition}Assume a collection of intervals $\mathscr{I}$
+including $\imposs$ and $\necess$. \end{definition}
+
+In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
+if a QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$ is induced by a conventional
+quantum probability measure~$\mu_{\rho}^{\mathrm{B}}$ and a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+considered in Sec.~\ref{sec:Born}, there is always a state consistent
+with it because $\rho\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
 Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$

### 2017-10-15 prop_iop.tex
prop_iop.tex \subsection{Category Theory} Adding...

@@
 
+\subsection{Category Theory}
+
+It looks like $\iota$ might be a morphism in a category. Let's try
+to check if it is true here.
+
+\begin{definition}Given $\mathscr{I}$ is a collection of intervals,
+we say a interval-valued function\nb$\iota:\mathscr{I}'\rightarrow\mathscr{I}''$
+is additive if $\iota$ satisfies the following properties. 
+\begin{itemize}
+\item $\iota\left(\imposs\right)=\imposs$. 
+\item $\iota\left(\necess\right)=\necess$. 
+\item For any $\left[\ell,r\right]\in\mathscr{I}'$, $\iota\left(\necess-\left[\ell,r\right]\right)=\necess-\iota\left(\left[\ell,r\right]\right)$. 
+\item For a pair\nb$\left[\ell_{0},r_{0}\right]$ and $\left[\ell_{1},r_{1}\right]\in\mathscr{I}'$,
+if $\left[\ell_{0},r_{0}\right]\subseteq\left[\ell_{1},r_{1}\right]$,
+then $\iota\left(\left[\ell_{0},r_{0}\right]\right)\subseteq\iota\left(\left[\ell_{1},r_{1}\right]\right)$. 
+\item For a pair\nb$\left[\ell_{0},r_{0}\right]$ and $\left[\ell_{1},r_{1}\right]\in\mathscr{I}'$,
+if $\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]\cap\left[0,1\right]\neq\emptyset$,
+then $\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]\in\mathscr{I}'$
+and $\iota\left(\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]\right)\subseteq\iota\left(\left[\ell_{0},r_{0}\right]\right)+\iota\left(\left[\ell_{1},r_{1}\right]\right)$. 
+\end{itemize}
+Moreover, $\iota$ is called convex if for any three intervals\nb$\left[\ell_{0},r_{0}\right]$,
+$\left[\ell_{1},r_{1}\right]$, and $\left[\ell_{2},r_{2}\right]\in\mathscr{I}'$,
+their sum $\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]+\left[\ell_{2},r_{2}\right]\in\mathscr{I}'$
+implies $\iota\left(\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]+\left[\ell_{2},r_{2}\right]\right)+\iota\left(\left[\ell_{2},r_{2}\right]\right)\subseteq\iota\left(\left[\ell_{0},r_{0}\right]+\left[\ell_{2},r_{2}\right]\right)+\iota\left(\left[\ell_{1},r_{1}\right]+\left[\ell_{2},r_{2}\right]\right)$.\end{definition}
+
+\begin{lemma}\label{lemma:interval2interval}Consider an additive
+interval-valued function\nb$\iota:\mathscr{I}'\rightarrow\mathscr{I}''$.
+Then, given a QIVPM\nb$\bar{\mu}':\events\rightarrow\mathscr{I}'$,
+a function\nb$\bar{\mu}'':\events\rightarrow\mathscr{I}''$ defined
+by $\bar{\mu}''\left(P\right)=\iota\left(\bar{\mu}'\left(P\right)\right)$
+is a QIVPM.\end{lemma}
+
+\begin{proof}~
+\begin{itemize}
+\item $\bar{\mu}''\left(\mathbb{0}\right)=\iota\left(\bar{\mu}'\left(\mathbb{0}\right)\right)=\iota\left(\imposs\right)=\imposs$.
+\item $\bar{\mu}''\left(\mathbb{1}\right)=\iota\left(\bar{\mu}'\left(\mathbb{1}\right)\right)=\iota\left(\necess\right)=\necess$.
+\item For any projection $P$, $\bar{\mu}''\left(\mathbb{1}-P\right)=\iota\left(\necess-\bar{\mu}'\left(P\right)\right)=\necess-\bar{\mu}''\left(P\right)$.
+\item For a pair of mutually orthogonal projections\nb$P_{0}$ and $P_{1}\in\events$,
+since $\emptyset\neq\bar{\mu}'\left(P_{0}+P_{1}\right)\cap\left[0,1\right]\subseteq\bar{\mu}'\left(P_{0}\right)+\bar{\mu}'\left(P_{1}\right)\cap\left[0,1\right]$,
+we have $\bar{\mu}'\left(P_{0}\right)+\bar{\mu}'\left(P_{1}\right)\in\mathscr{I}'$
+and
+\[
+\bar{\mu}''\left(P_{0}+P_{1}\right)=\iota\left(\bar{\mu}'\left(P_{0}+P_{1}\right)\right)\subseteq\iota\left(\bar{\mu}'\left(P_{0}\right)+\bar{\mu}'\left(P_{1}\right)\right)\subseteq\iota\left(\bar{\mu}'\left(P_{0}\right)\right)+\iota\left(\bar{\mu}'\left(P_{1}\right)\right)=\bar{\mu}''\left(P_{0}\right)+\bar{\mu}''\left(P_{1}\right)\,.
+\]
+\end{itemize}
+\end{proof}
+
 \section{From Interval-valued to Real-valued}

### 2017-10-16 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-\begin{thm}\label{thm:QRVPM2QIVPM-3}In a Hilbert space of dimension~$d\le3$,
-if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is subject to the
-following constraints:\begin{subequations}\label{eq:iota-constraints}
-\begin{eqnarray}
- &  & \iota(0)=\imposs\,,\\
- &  & \iota(1)=\necess\,,\\
- &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
-\end{eqnarray}
-\end{subequations}and satisfies that for any numbers~$x_{0}$ and
-$x_{1}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}\in\left[0,1\right]$
-implies
-\begin{equation}
-\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
-\end{equation}
-Then, $\iota\circ\mu:\events\rightarrow\mathscr{I}$ is always a QIVPM
-for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.\end{thm}
+\begin{thm}\label{thm:QRVPM2QIVPM-3}In  for any quantum probability
+measure~$\mu:\events\rightarrow\left[0,1\right]$.\end{thm}
 
@@
 
-\begin{thm}\label{thm:iota-statements}The following two statements
-are equivalent:
-\begin{enumerate}
-\item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-satisfies Eqs.~(\ref{eq:iota-constraints}) and for any three numbers~$x_{0}$,
-$x_{1}$, and $x_{2}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
-implies
-\begin{equation}
-\begin{aligned} & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
-\subseteq{} & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
-\end{aligned}
-\label{eq:iota-Inclusion}
-\end{equation}
-\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
-is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-on any Hilbert space~$\Hilb$.
-\end{enumerate}
-\end{thm}
-
-It is clear that Statement~\ref{enu:iota-subject-to} implies Statement~\ref{enu:iota-mu-QIVPM},
-and the rest of the proof is to prove that if Statement~\ref{enu:iota-subject-to}
-is false, then Statement~\ref{enu:iota-mu-QIVPM} is false as well.
-If $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}), we can
-find three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
-such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
-Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
-Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}$
-fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-\begin{eqnarray*}
- &  & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
- & \nsubseteq & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\,,
-\end{eqnarray*}
-and cannot be a QIVPM. Therefore, Statement~\ref{enu:iota-subject-to}
-is true if and only if Statement~\ref{enu:iota-mu-QIVPM} is true.
-
-In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
-we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
-By Eq.~(\ref{eq:iota-Inclusion}), the left-end function~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
-is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992}.
-It is well-known that a Wright-convex function is midpoint-convex
-or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
-i.e., we have
-\begin{equation}
-\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
-\end{equation}
-Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
-the left-end function~$\iotal$ must be continuous on the unit open
-interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
-Therefore, either $\iota$ maps every number to the same interval,
-or the number of intervals that $\iota$ maps to must be uncountable.
-
-\begin{thm}\label{thm:convex-uncountable}Let 
-\begin{equation}
-\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.
-\end{equation}
-For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\mathscr{I}_{0}$
-or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
-
 \yutsung{Another idea might be fixing a quantum probability measure~$\mu$,
@@
 
-However, if we consider general QIVPMs mapping to an \emph{arbitrary}
+\noindent However, if we consider general QIVPMs mapping to an \emph{arbitrary}
 set of intervals, there is a QIVPM that no state can be consistent
@@
 
-\begin{definition}Assume a collection of intervals $\mathscr{I}$
-including $\imposs$ and $\necess$. \end{definition}
+\begin{definition}Given a collection of intervals $\mathscr{I}$
+including $\imposs$ and $\necess$, a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is called a \emph{morphism}\yutsung{I may need to know the precise
+conditions when $\iota$ is a morphism in the sense of category theory,
+or we need to find a better name for this function.}if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
+\begin{eqnarray}
+ &  & \iota(0)=\imposs\,,\\
+ &  & \iota(1)=\necess\,,\\
+ &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
+\end{eqnarray}
+\end{subequations}and satisfies that for any three numbers~$x_{0}$,
+$x_{1}$, and $x_{2}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
+implies
+\begin{equation}
+\begin{aligned} & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
+\subseteq{} & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
+\end{aligned}
+\label{eq:iota-Inclusion}
+\end{equation}
+\end{definition}
+
+\noindent Then, $\iota$ is a morphism precisely characterizes that
+$\iota\circ\mu$ is always a IVPM no matter in classical or quantum
+cases.
+
+\begin{thm}\label{thm:iota-statements}The following three statements
+are equivalent:
+\begin{enumerate}
+\item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is a morphism.
+\item \label{enu:iota-mu-CIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
+is always a classical IVPM for any classical probability measure~$\mu:\events_{C}\rightarrow\left[0,1\right]$.
+\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
+is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+on any Hilbert space~$\Hilb$.
+\end{enumerate}
+\end{thm}
+
+Because the similarity between classical and quantum cases, we will
+only prove the equivalence between Statement~\ref{enu:iota-subject-to}
+and Statement~\ref{enu:iota-mu-QIVPM}. It is clear that $\iota$
+is a morphism implies $\iota\circ\mu$ is always a QIVPM, and the
+rest of the proof is to prove that if $\iota$ is not a morphism,
+then $\iota\circ\mu$ might not be a QIVPM. If $\iota$ doesn't satisfy
+Eq.~(\ref{eq:iota-Inclusion}), we can find three particular numbers~$x_{0}$,
+$x_{1}$, and $x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
+but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
+Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
+Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}$
+fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+\begin{eqnarray*}
+ &  & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
+ & \nsubseteq & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\,,
+\end{eqnarray*}
+and cannot be a QIVPM. Therefore, $\iota$ is a morphism if and only
+if $\iota\circ\mu$ is always a QIVPM.
+
+Although the composited function~$\iota\circ\mu$ may not guarantee
+to be a QIVPM when $\iota$ is not a morphism, it may still be a QIVPM
+under so suitable conditions. For example, given a Hilbert space of
+dimension~$d\le3$, we can guarantee $\iota\circ\mu$ is a QIVPM
+when $\iota$ satisfies Eqs.~(\ref{eq:iota-constraints}) and a weaker
+condition: for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
+their sum~$x_{0}+x_{1}\in\left[0,1\right]$ implies
+\begin{equation}
+\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
+\end{equation}
 
@@
 quantum probability measure~$\mu_{\rho}^{\mathrm{B}}$ and a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-considered in Sec.~\ref{sec:Born}, there is always a state consistent
-with it because $\rho\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
+, there is always a state consistent with it because $\rho\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
 Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
@@
 Hence, $\left\Vert \rho-\rho'\right\Vert \le\delta$.
+
+\begin{thm}\label{thm:convex-uncountable}Let 
+\begin{equation}
+\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.
+\end{equation}
+For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\mathscr{I}_{0}$
+or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
+
+In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
+we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
+By Eq.~(\ref{eq:iota-Inclusion}), the left-end function~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
+is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992}.
+It is well-known that a Wright-convex function is midpoint-convex
+or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
+i.e., we have
+\begin{equation}
+\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
+\end{equation}
+Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
+the left-end function~$\iotal$ must be continuous on the unit open
+interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
+Therefore, either $\iota$ maps every number to the same interval,
+or the number of intervals that $\iota$ maps to must be uncountable.
 

### 2017-10-16 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 \caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
-on the three-dimensional Hilbert space. The projectors mapping to
-the same interval are listed in the column labeled by $P$ and separated
-by commas.}
+on a Hilbert space of dimension~$d\ge3$. The projectors mapping
+to the same interval are listed in the column labeled by $P$ and
+separated by commas.}
 
@@
 
-In other words, if the measurement intervals are too imprecise, the
-results we get might contradict to each other, and exclude any possible
-state from being consistent with the measurement results. To address
-this problem, we are going to consider a particular family of QIVPMs
-induced by quantum probability measures. When we generalized quantum
-probability measures to QIVPMs, we changed the range from the unit
-interval~$\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
+In other words, if the measurement intervals are too imprecise and
+the QIVPM are defined so wildly, the results we get might contradict
+to each other, and exclude any possible state from being consistent
+with the measurement results. To address this problem, we are going
+to consider a simple rule which can induce well-behaved QIVPMs by
+quantum probability measures systematically. Recall when we generalized
+quantum probability measures to QIVPMs, we changed the range from
+the unit interval~$\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
 This replacement suggests us to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
@@
 including $\imposs$ and $\necess$, a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-is called a \emph{morphism}\yutsung{I may need to know the precise
-conditions when $\iota$ is a morphism in the sense of category theory,
-or we need to find a better name for this function.}if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+is called a \emph{morphism}\yutsung{Haven't found a better name so
+far, but haven't proved that it is a morphism in the sense of category
+theory as well...}if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 is subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
@@
 \begin{equation}
-\begin{aligned} & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
-\subseteq{} & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
-\end{aligned}
-\label{eq:iota-Inclusion}
+\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
 \end{equation}
@@
 $\iota\circ\mu$ is always a IVPM no matter in classical or quantum
-cases.
+sense.
 
@@
 
-Because the similarity between classical and quantum cases, we will
+Since the similarity between classical and quantum cases, we will
 only prove the equivalence between Statement~\ref{enu:iota-subject-to}
-and Statement~\ref{enu:iota-mu-QIVPM}. It is clear that $\iota$
-is a morphism implies $\iota\circ\mu$ is always a QIVPM, and the
-rest of the proof is to prove that if $\iota$ is not a morphism,
-then $\iota\circ\mu$ might not be a QIVPM. If $\iota$ doesn't satisfy
-Eq.~(\ref{eq:iota-Inclusion}), we can find three particular numbers~$x_{0}$,
-$x_{1}$, and $x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
-but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
+and \ref{enu:iota-mu-QIVPM}. It is clear that $\iota$ is a morphism
+implies $\iota\circ\mu$ is always a QIVPM, and the rest of the proof
+is to prove that if $\iota$ is not a morphism, then $\iota\circ\mu$
+might not be a QIVPM. If $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
+we can find three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
 Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.

### 2017-10-17 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-\section{Born\label{sec:Born}}
-
-\yutsung{Notice that the use of quantum is minimized in this section.
-In another word, the results of this section should apply to both
-quantum and classical IVPMs.}
-
-Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
-postulates for the quantum probability measures first, and then introduce
-the Born rule which induces a quantum probability measures from each
-state~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. Since
-the postulates for QIVPMs in Sec.~\ref{sec:Interval-Uncertainty}
-are also non-constructive, we want to find a simple rule to construct
-a QIVPM as well.
-
-However, the composited function~$\iota\circ\mu$ may or may not
-be a QIVPM. For example, in a four-dimensional Hilbert space, consider
-the function 
-\begin{equation}
-\iota_{1}\left(x\right)=\begin{cases}
-\imposs\,, & \textrm{ if }x=0\,;\\
-\left[0,\tfrac{1}{2}\right]\,, & \textrm{ if }x\in\left(0,\tfrac{1}{4}\right]\,;\\
-\unknown\,, & \textrm{ if }x\in\left(\tfrac{1}{4},\tfrac{3}{4}\right)\,;\\
-\left[\tfrac{1}{2},1\right]\,, & \textrm{ if }x\in\left[\tfrac{3}{4},1\right)\,;\\
-\necess\,, & \textrm{ if }x=1\,.
-\end{cases}\label{eq:iota}
-\end{equation}
-While the function~$\iota_{1}\circ\mu_{\rho_{0}}^{\mathrm{\mathrm{B}}}$
-induced by $\rho_{0}=\frac{1}{4}\cdot\proj{0}+\frac{1}{4}\cdot\proj{1}+\frac{1}{4}\cdot\proj{2}+\frac{1}{4}\cdot\proj{3}$
-is a QIVPM, the function~$\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
-induced by $\rho_{1}=\frac{1}{8}\cdot\proj{0}+\frac{1}{8}\cdot\proj{1}+\frac{1}{8}\cdot\proj{2}+\frac{5}{8}\cdot\proj{3}$
-is \emph{not} a QIVPM~\citep{HOSTunpublished}. In order not to verify
-whether $\iota\circ\mu$ is a QIVPM for each individual case, it is
-desirable to have some criteria to discriminate different cases. We
-will start from the simpler criteria for the dimension~$d\le3$,
-and then the general case.
-
-\begin{thm}\label{thm:QRVPM2QIVPM-3}In  for any quantum probability
-measure~$\mu:\events\rightarrow\left[0,1\right]$.\end{thm}
-
-The situation for $d=2$ is trivial. On a three-dimensional Hilbert
-space, to prove that $\iota\circ\mu$ is a QIVPM, it is sufficient
-to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-\begin{equation}
-\begin{aligned} & \iota\left(\mu\left(P_{0}+P_{1}-P_{0}P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
-\subseteq{} & \iota\left(\mu\left(P_{0}\right)\right)+\iota\left(\mu\left(P_{1}\right)\right)\,.
-\end{aligned}
-\label{eq:QuantumInterval-valuedProbability-Inclusion-case}
-\end{equation}
- Depending on the relation between $P_{0}$ and $P_{1}$, we have
-three possibilities:
-\begin{itemize}
-\item $P_{0}$ and $P_{1}$ are orthogonal.
-\item Their complements~$\mathbb{1}-P_{0}$ and $\mathbb{1}-P_{1}$ are
-orthogonal.
-\item One of them projects onto a subspace of what the other one projects
-onto.
-\end{itemize}
-\noindent All cases deduce Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion-case})
-easily~\citep{HOSTunpublished} so that $\iota\circ\mu$ is indeed
-a QIVPM.
-
-On the one hand, $\iota_{1}$ defined in Eq.~(\ref{eq:iota}) satisfies
-Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}
-so that every function~$\iota_{1}\circ\mu$ on a three-dimensional
-Hilbert space is a QIVPM. On the other hand, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
-is not a QIVPM on four-dimensional Hilbert space. Hence, to guarantee
-$\iota\circ\mu$ is always a QIVPM, we need to strengthen Eq.~(\ref{eq:iota-add})
-and consider the following conditions.
-
-\yutsung{Another idea might be fixing a quantum probability measure~$\mu$,
-whether there is a length of intervals, such that if $\iota$ maps
-to intervals tighter than the given length, then $\iota\circ\mu$
-is always a QIVPM... I don't know the answer of this question, and
-it might not be very easy...}
-
-\yutsung{The other idea: We never proved a non-convex QIVPM always
-have a non-empty core or find an counterexample that a non-convex
-QIVPM has empty core. Moreover, we have no idea the relation between
-its expectation value and the Choquet integral... Depending the on
-situation, the convex condition may not be necessary, but this might
-be hard to prove...}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Gleason}
@@
 produces an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
-which has the same domain and range as a QIVPM. Although there are
-infinitely many different choice of $\iota$, the function~$\iota$
-satisfies the following homomorphism-like properties are of particular
-interest, because it guarantee $\iota\circ\mu$ is always a QIVPM.
-
-\begin{definition}Given a collection of intervals $\mathscr{I}$
-including $\imposs$ and $\necess$, a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-is called a \emph{morphism}\yutsung{Haven't found a better name so
-far, but haven't proved that it is a morphism in the sense of category
-theory as well...}if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+which has the same domain and range as a QIVPM. In order to guarantee
+$\iota\circ\mu$ is always a QIVPM, we consider the following homomorphism-like
+properties for $\iota$.
+
+\begin{definition}[{morphism}]{\label{def:morphism}}Given a collection
+of intervals $\mathscr{I}$ including $\imposs$ and $\necess$, a
+function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is called
+a \emph{morphism}\yutsung{We can give it a better name. If sticking
+with this name, we may need to prove that it is a morphism in the
+sense of category theory or something...}if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 is subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
@@
 
-\noindent Then, $\iota$ is a morphism precisely characterizes that
-$\iota\circ\mu$ is always a IVPM no matter in classical or quantum
-sense.
+\noindent Because the similarity between Def.~\ref{def:morphism}
+and Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM
+no matter in classical or quantum case. Surprisingly, if $\iota\circ\mu$
+is always a IVPM, then $\iota$ must be a morphism.
 
@@
 
-Since the similarity between classical and quantum cases, we will
-only prove the equivalence between Statement~\ref{enu:iota-subject-to}
-and \ref{enu:iota-mu-QIVPM}. It is clear that $\iota$ is a morphism
-implies $\iota\circ\mu$ is always a QIVPM, and the rest of the proof
-is to prove that if $\iota$ is not a morphism, then $\iota\circ\mu$
-might not be a QIVPM. If $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
-we can find three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
-such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
+As we have discussed, Statement~\ref{enu:iota-subject-to} implies
+\ref{enu:iota-mu-QIVPM}. The rest of the proof is to prove that if
+$\iota$ is not a morphism, then $\iota\circ\mu$ might not be a QIVPM
+for any quantum probability measure~$\mu$. If $\iota$ doesn't satisfy
+Eq.~(\ref{eq:iota-Inclusion}), we can find three particular numbers~$x_{0}$,
+$x_{1}$, and $x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
+but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
 Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
@@
 and cannot be a QIVPM. Therefore, $\iota$ is a morphism if and only
-if $\iota\circ\mu$ is always a QIVPM.
-
-Although the composited function~$\iota\circ\mu$ may not guarantee
-to be a QIVPM when $\iota$ is not a morphism, it may still be a QIVPM
-under so suitable conditions. For example, given a Hilbert space of
-dimension~$d\le3$, we can guarantee $\iota\circ\mu$ is a QIVPM
-when $\iota$ satisfies Eqs.~(\ref{eq:iota-constraints}) and a weaker
-condition: for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
+if $\iota\circ\mu$ is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
+and \ref{enu:iota-mu-CIVPM} are equivalent as well~\citep{HOSTunpublished}.
+
+Even if $\iota$ is not a morphism, the composited function~$\iota\circ\mu$
+may still be a QIVPM under so suitable conditions. For example, Eq.~(\ref{eq:iota-Inclusion})
+can be weaken as follow: for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
 their sum~$x_{0}+x_{1}\in\left[0,1\right]$ implies
@@
 \end{equation}
+Then, given a Hilbert space of dimension~$d\le3$, when $\iota$
+satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),$\iota\circ\mu$
+still must be a QIVPM~\citep{HOSTunpublished}.
 
 In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-if a QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$ is induced by a conventional
-quantum probability measure~$\mu_{\rho}^{\mathrm{B}}$ and a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-, there is always a state consistent with it because $\rho\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
+there is always a state consistent with the composited QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$~\citep{HOSTunpublished}.
 Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
@@
 First, the norm of a pure state~$\ket{\psi}$ is defined as usual
-$||\psi||=\sqrt{\ip{\psi}{\psi}}$. Then, the norm of the difference
-of two states~$\rho$ and $\rho'$ is just the usual operator norm
+$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Then, the norm
+of the difference of two states~$\rho$ and $\rho'$ is just the
+usual operator norm
 \begin{equation}
@@
 
-\begin{thm}\label{thm:convex-uncountable}Let 
-\begin{equation}
-\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.
-\end{equation}
-For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+Since morphisms have many desirable properties, the intervals it mapping
+to either is trivial or contains infinity intervals.
+
+\begin{thm}\label{thm:convex-uncountable}For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\mathscr{I}_{0}$
-or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
-
-In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
-we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
+defined in Eq.(\ref{eq:3-value-intervals}) or $\mathscr{I}$ contains
+uncountably many intervals.\end{thm}
+
+Since $\iota$ maps to intervals, we can decompose it into two functions:
+its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
 By Eq.~(\ref{eq:iota-Inclusion}), the left-end function~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$

### 2017-10-18 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-\begin{definition}[QIVPM]
+\begin{definition}[QIVPM]\label{def:QIVPM}
   Assume a collection of intervals $\mathscr{I}$ including $\imposs$
@@
 
-In Sec.~\ref{sec:Interval-Uncertainty}, we discussed how states
-consistent with a QIVPM~$\bar{\mu}$ on the projectors in a subspace
-of event~$\events'$. In particular, if $\events'$ commutes, $\bar{\mu}$
-restricting on $\events'$ is essentially a classical IVPM, and Thm.~\ref{thm:Shapley}
-claims that there is always a state~$\rho$ consistent with $\bar{\mu}$.
-In this section, we want to shift our attention to consider states
-consistent with $\bar{\mu}$ on \emph{every} event, $\coreBorn\left(\bar{\mu},\events\right)$.
-When the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
-a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$ becomes
-quantum probability measure~\citep{HOSTunpublished}. In this situation,
-Gleason's theorem claims that there is always a unique state consistent
-with $\bar{\mu}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+While the finite-precision extension of the Kochen-Specker theorem
+asserts the non-existence of a certain kind of QIVPMs, we also want
+to understand what a QIVPM could be when it exists. In contrast with
+the conventional Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}
+and Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}:
 
 \begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
-a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
+a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
 the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
@@
 
-\noindent However, if we consider general QIVPMs mapping to an \emph{arbitrary}
-set of intervals, there is a QIVPM that no state can be consistent
-with it.
+\noindent We haven't discussed how to construct a QIVPM according
+to a simple rule. Even if we have a QIVPM, there might not have any
+states consistent with it.
 
@@
 
-\begin{definition}[{morphism}]{\label{def:morphism}}Given a collection
+\begin{definition}[THOS rule]\label{def:THOS}Given a collection
 of intervals $\mathscr{I}$ including $\imposs$ and $\necess$, a
 function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is called
-a \emph{morphism}\yutsung{We can give it a better name. If sticking
-with this name, we may need to prove that it is a morphism in the
-sense of category theory or something...}if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-is subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
+a THOS rule if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is
+subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
 \begin{eqnarray}
@@
 
-\noindent Because the similarity between Def.~\ref{def:morphism}
-and Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM
-no matter in classical or quantum case. Surprisingly, if $\iota\circ\mu$
-is always a IVPM, then $\iota$ must be a morphism.
-
-\begin{thm}\label{thm:iota-statements}The following three statements
-are equivalent:
+\noindent Because the similarity between Def.~\ref{def:THOS} and
+Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM no
+matter in classical or quantum case. Surprisingly, if $\iota\circ\mu$
+is always a IVPM, then $\iota$ must be a THOS rule.
+
+\begin{thm}[The equivalence among THOS rules and IVPMs]\label{thm:iota-statements}The
+following three statements are equivalent:
 \begin{enumerate}
 \item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-is a morphism.
+is a THOS rule.
 \item \label{enu:iota-mu-CIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
@@
 \ref{enu:iota-mu-QIVPM}. The rest of the proof is to prove that if
-$\iota$ is not a morphism, then $\iota\circ\mu$ might not be a QIVPM
-for any quantum probability measure~$\mu$. If $\iota$ doesn't satisfy
-Eq.~(\ref{eq:iota-Inclusion}), we can find three particular numbers~$x_{0}$,
-$x_{1}$, and $x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
-but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
+$\iota$ is not a THOS rule, then $\iota\circ\mu$ might not be a
+QIVPM for any quantum probability measure~$\mu$. If $\iota$ doesn't
+satisfy Eq.~(\ref{eq:iota-Inclusion}), we can find three particular
+numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$ such
+that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
 Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
@@
 \end{eqnarray*}
-and cannot be a QIVPM. Therefore, $\iota$ is a morphism if and only
+and cannot be a QIVPM. Therefore, $\iota$ is a THOS rule if and only
 if $\iota\circ\mu$ is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
@@
 
-Even if $\iota$ is not a morphism, the composited function~$\iota\circ\mu$
+Even if $\iota$ is not a THOS rule, the composited function~$\iota\circ\mu$
 may still be a QIVPM under so suitable conditions. For example, Eq.~(\ref{eq:iota-Inclusion})
@@
 
-Since morphisms have many desirable properties, the intervals it mapping
-to either is trivial or contains infinity intervals.
-
-\begin{thm}\label{thm:convex-uncountable}For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\mathscr{I}_{0}$
+Since THOS rules have many desirable properties, the intervals it
+mapping to either is trivial or contains infinity intervals.
+
+\begin{thm}[{The range of THOS rule}s]\label{thm:convex-uncountable}For
+any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ described
+in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\mathscr{I}_{0}$
 defined in Eq.(\ref{eq:3-value-intervals}) or $\mathscr{I}$ contains

### 2017-10-18 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-While the finite-precision extension of the Kochen-Specker theorem
-asserts the non-existence of a certain kind of QIVPMs, we also want
-to understand what a QIVPM could be when it exists. In contrast with
-the conventional Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}
-and Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}:
+A conventional quantum probability measure can be easily constructed
+from a state according to Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
+This state is also the unique state consistent with the constructed
+probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}:
 
@@
 
-\noindent We haven't discussed how to construct a QIVPM according
-to a simple rule. Even if we have a QIVPM, there might not have any
-states consistent with it.
+\noindent Since QIVPMs are just finite precision generalization of
+conventional quantum probability measures, we also want to seek a
+simple rule to construct them, and understand which states are consistent
+with the constructed QIVPM. However, there exists a QIVPM such that
+no state can be consistent with it. Since no state is consistent with
+it, there is no natural way to construct it from any state.
 
@@
 the unit interval~$\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
-This replacement suggests us to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-which can be used to replace a real-valued probability~$\mu\left(P\right)$
-by an interval-valued one~$\iota\left(\mu\left(P\right)\right)$.
-In other words, compositing $\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
+This replacement suggests to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+to replace a real-valued probability~$\mu\left(P\right)$ by an interval-valued
+one~$\iota\left(\mu\left(P\right)\right)$. In other words, compositing
+$\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
 produces an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
 which has the same domain and range as a QIVPM. In order to guarantee
-$\iota\circ\mu$ is always a QIVPM, we consider the following homomorphism-like
+$\iota\circ\mu$ always a QIVPM, we consider the following homomorphism-like
 properties for $\iota$.

### 2017-10-18 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 This state is also the unique state consistent with the constructed
-probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}:
+probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}
+which can be reformulated in QIVPM using infinitely precise intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:
 
 \begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
-a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
+a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
 the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
@@
 
-\noindent Since QIVPMs are just finite precision generalization of
-conventional quantum probability measures, we also want to seek a
-simple rule to construct them, and understand which states are consistent
-with the constructed QIVPM. However, there exists a QIVPM such that
-no state can be consistent with it. Since no state is consistent with
-it, there is no natural way to construct it from any state.
+\noindent When generalizing to finite precision QIVPMs, we also want
+to seek a simple rule to construct them, and understand which states
+are consistent with them. However, if the measurement intervals are
+too imprecise and the QIVPM are defined so wildly, the results we
+get might contradict to each other, and exclude any possible state
+from being consistent with the measurement results.
 
@@
 
-In other words, if the measurement intervals are too imprecise and
-the QIVPM are defined so wildly, the results we get might contradict
-to each other, and exclude any possible state from being consistent
-with the measurement results. To address this problem, we are going
-to consider a simple rule which can induce well-behaved QIVPMs by
-quantum probability measures systematically. Recall when we generalized
-quantum probability measures to QIVPMs, we changed the range from
-the unit interval~$\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
-This replacement suggests to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+To address this problem, we are going to consider a simple rule which
+can induce well-behaved QIVPMs by quantum probability measures systematically.
+When we generalized quantum probability measures to QIVPMs, we changed
+the range from the unit interval~$\left[0,1\right]$ to a set of
+intervals~$\mathscr{I}$. This replacement suggests to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 to replace a real-valued probability~$\mu\left(P\right)$ by an interval-valued
@@
 $\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-produces an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
+produces a function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
 which has the same domain and range as a QIVPM. In order to guarantee
@@
 Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM no
-matter in classical or quantum case. Surprisingly, if $\iota\circ\mu$
+matter in classical or quantum case. Conversely, if $\iota\circ\mu$
 is always a IVPM, then $\iota$ must be a THOS rule.
@@
 is a THOS rule.
-\item \label{enu:iota-mu-CIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
+\item \label{enu:iota-mu-CIVPM}The composited function~$\iota\circ\mu:\events_{C}\rightarrow\mathscr{I}$
 is always a classical IVPM for any classical probability measure~$\mu:\events_{C}\rightarrow\left[0,1\right]$.
@@
 $\iota$ is not a THOS rule, then $\iota\circ\mu$ might not be a
-QIVPM for any quantum probability measure~$\mu$. If $\iota$ doesn't
-satisfy Eq.~(\ref{eq:iota-Inclusion}), we can find three particular
-numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$ such
-that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
+QIVPM. If $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
+we can find three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
 Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
@@
 
-Since THOS rules have many desirable properties, the intervals it
-mapping to either is trivial or contains infinity intervals.
-
-\begin{thm}[{The range of THOS rule}s]\label{thm:convex-uncountable}For
-any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ described
-in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\mathscr{I}_{0}$
-defined in Eq.(\ref{eq:3-value-intervals}) or $\mathscr{I}$ contains
-uncountably many intervals.\end{thm}
+Although THOS rules have many desirable properties, the intervals
+it mapping to either is trivial or contains infinity intervals.
+
+\begin{thm}[The range of THOS rules]\label{thm:convex-uncountable}For
+any THOS rule~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$, either
+$\mathscr{I}=\mathscr{I}_{0}$ defined in Eq.(\ref{eq:3-value-intervals})
+or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
 

### 2017-10-18 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 A conventional quantum probability measure can be easily constructed
-from a state according to Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
+from a state according to the Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
 This state is also the unique state consistent with the constructed
 probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}
-which can be reformulated in QIVPM using infinitely precise intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:
+which can be reformulated in QIVPMs using infinitely precise intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:
 
@@
 \noindent When generalizing to finite precision QIVPMs, we also want
-to seek a simple rule to construct them, and understand which states
+to seek a simple rule to construct them, and to understand which states
 are consistent with them. However, if the measurement intervals are
 too imprecise and the QIVPM are defined so wildly, the results we
-get might contradict to each other, and exclude any possible state
-from being consistent with the measurement results.
+get might contradict to each other. This contradicting results would
+exclude any possible state from being consistent with them.
 

### 2017-10-19 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-\noindent When generalizing to finite precision QIVPMs, we also want
-to seek a simple rule to construct them, and to understand which states
-are consistent with them. However, if the measurement intervals are
-too imprecise and the QIVPM are defined so wildly, the results we
-get might contradict to each other. This contradicting results would
-exclude any possible state from being consistent with them.
+\noindent For general QIVPMs mapping to finitely precise intervals,
+we also want to seek a simple rule to construct them, and to understand
+which states are consistent with them. However, if measurement intervals
+are too imprecise and QIVPMs are defined so wildly, the results we
+get might contradict to each other. These contradicting results would
+exclude any possible state from being consistent with the given QIVPM.
 
@@
 function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is called
-a THOS rule if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is
-subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
+a THOS rule if $\iota$ is subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
 \begin{eqnarray}
@@
 \begin{enumerate}
-\item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+\item \label{enu:iota-subject-to}A function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 is a THOS rule.
@@
 Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
-Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}$
+Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
 fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
@@
 length of the intervals in $\mathscr{I}$ is $\delta$, it is also
-the upper bound of the difference $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
+the upper bound of the difference 
+\[
+\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le\delta\,.
+\]
 Since $\rho-\rho'$ is Hermitian, $\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
@@
 Since $\iota$ maps to intervals, we can decompose it into two functions:
-its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
-By Eq.~(\ref{eq:iota-Inclusion}), the left-end function~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
+its left-end and right-end $\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
+By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
 is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992}.

### 2017-10-19 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-\begin{thm}[Empty core for general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
+\begin{thm}[Empty Core for General QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
 a Hilbert space of dimension~$d\ge3$, there exists a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
@@
 
-\begin{definition}[THOS rule]\label{def:THOS}Given a collection
+\begin{definition}[THOS Rule]\label{def:THOS}Given a collection
 of intervals $\mathscr{I}$ including $\imposs$ and $\necess$, a
@@
 
-\noindent Because the similarity between Def.~\ref{def:THOS} and
-Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM no
-matter in classical or quantum case. Conversely, if $\iota\circ\mu$
+\noindent Because of the similarity between Def.~\ref{def:THOS}
+and Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM
+no matter in classical or quantum case. Conversely, if $\iota\circ\mu$
 is always a IVPM, then $\iota$ must be a THOS rule.
 
-\begin{thm}[The equivalence among THOS rules and IVPMs]\label{thm:iota-statements}The
+\begin{thm}[Equivalence among THOS Rules and IVPMs]\label{thm:iota-statements}The
 following three statements are equivalent:
@@
 
-\begin{thm}[A finite-precision extension of weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
+\begin{thm}[Finite-Precision Extension of Weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
 a three-dimensional Hilbert space, and an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
@@
 
-\begin{thm}[The range of THOS rules]\label{thm:convex-uncountable}For
+\begin{thm}[Range of THOS Rules]\label{thm:convex-uncountable}For
 any THOS rule~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$, either

### 2017-10-19 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 
-To address this problem, we are going to consider a simple rule which
+To address this problem, we are going to introduce a simple rule which
 can induce well-behaved QIVPMs by quantum probability measures systematically.
@@
 $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Then, the norm
-of the difference of two states~$\rho$ and $\rho'$ is just the
-usual operator norm
+of the difference between two states~$\rho$ and $\rho'$ is just
+the usual operator norm
 \begin{equation}
@@
 
-Although THOS rules have many desirable properties, the intervals
-it mapping to either is trivial or contains infinity intervals.
+Although a THOS rule have many desirable properties, the set of intervals
+it mapping to either is trivial or contains infinite intervals.
 
@@
 interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
-Therefore, either $\iota$ maps every number to the same interval,
-or the number of intervals that $\iota$ maps to must be uncountable.
+Therefore, either $\iota$ maps every number in $\left(0,1\right)$
+to the same interval, or the number of intervals that $\iota$ maps
+to must be uncountable.
 

### 2017-10-19 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

@@
 Even if $\iota$ is not a THOS rule, the composited function~$\iota\circ\mu$
-may still be a QIVPM under so suitable conditions. For example, Eq.~(\ref{eq:iota-Inclusion})
-can be weaken as follow: for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
-their sum~$x_{0}+x_{1}\in\left[0,1\right]$ implies
+may still be a QIVPM under some suitable conditions. For example,
+Eq.~(\ref{eq:iota-Inclusion}) can be weaken as follow: for any numbers~$x_{0}$
+and $x_{1}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}\in\left[0,1\right]$
+implies
 \begin{equation}
@@
 Then, given a Hilbert space of dimension~$d\le3$, when $\iota$
-satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),$\iota\circ\mu$
-still must be a QIVPM~\citep{HOSTunpublished}.
+satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
+$\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
 

### 2017-10-19 prop_letter.tex
prop_letter.tex Easy updates after the meeting...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Kochen-Specker} 
+\section{Kochen-Specker Theorem and Contextuality}
 \label{sec:Kochen-Specker}
@@
 
-\section{Gleason}
+\section{Gleason's Theorem and Born rule}
 
@@
 
-\noindent Because of the similarity between Def.~\ref{def:THOS}
-and Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM
-no matter in classical or quantum case. Conversely, if $\iota\circ\mu$
-is always a IVPM, then $\iota$ must be a THOS rule.
+\noindent Because Eqs.~(\ref{eq:iota-constraints}) are the direct
+counterpart of Eqs.~(\ref{eq:QIVPM-constraints}) and Eq.~(\ref{eq:iota-Inclusion})
+is the direct counterpart of the convexity condition, Eq.~(\ref{eq:classicalconvex})
+and Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+$\iota\circ\mu$ should always be a IVPM no matter in classical or
+quantum case. Conversely, if $\iota\circ\mu$ is always a IVPM, then
+$\iota$ must be a THOS rule. In other words, $\iota$ is a THOS rule
+is a necessary and sufficient condition for $\iota\circ\mu$ is always
+a IVPM as we next show.
 
@@
 
-Even if $\iota$ is not a THOS rule, the composited function~$\iota\circ\mu$
-may still be a QIVPM under some suitable conditions. For example,
-Eq.~(\ref{eq:iota-Inclusion}) can be weaken as follow: for any numbers~$x_{0}$
-and $x_{1}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}\in\left[0,1\right]$
-implies
-\begin{equation}
-\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
-\end{equation}
-Then, given a Hilbert space of dimension~$d\le3$, when $\iota$
-satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
-$\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
-
 In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
@@
 \begin{thm}[Finite-Precision Extension of Weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
-a three-dimensional Hilbert space, and an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 with the maximum length of intervals $\delta$. Given any state~$\rho$,
@@
 to must be uncountable.
+
+Even if a THOS rule~$\iota$ maps to $\mathscr{I}_{0}$ or infinite
+intervals, the composited function~$\iota\circ\mu$ mapping to a
+finite set of intervals~$\mathscr{I}$ may still be a QIVPM when
+$\iota$ is not a THOS rule. For example, we can weaken Eq.~(\ref{eq:iota-Inclusion})
+to the following condition: for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
+their sum~$x_{0}+x_{1}\in\left[0,1\right]$ implies
+\begin{equation}
+\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
+\end{equation}
+Then, given a Hilbert space of dimension~$d\le3$, when $\iota$
+satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
+$\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
+More concretely, given a three-dimensional Hilbert space, consider
+two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
+and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$,
+and a interval-valued function~$\iota_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
+\begin{equation}
+\iota_{2}\left(x\right)=\begin{cases}
+\imposs\,, & \textrm{ if }x=0\,;\\
+\left[0,\tfrac{1}{4}\right]\,, & \textrm{ if }x\in\left(0,\tfrac{1}{8}\right]\,;\\
+\left[0,{\textstyle \tfrac{1}{2}}\right]\,, & \textrm{ if }x\in\left(\tfrac{1}{8},\tfrac{3}{8}\right)\,;\\
+\left[\tfrac{1}{4},\tfrac{3}{4}\right]\,, & \textrm{ if }x\in\left[\tfrac{3}{8},\tfrac{5}{8}\right]\,;\\
+\left[\tfrac{1}{2},1\right]\,, & \textrm{ if }x\in\left(\tfrac{5}{8},\tfrac{7}{8}\right)\,;\\
+\left[\tfrac{1}{4},1\right]\,, & \textrm{ if }x\in\left[\tfrac{7}{8},1\right)\,;\\
+\necess\,, & \textrm{ if }x=1\,.
+\end{cases}\label{eq:iota}
+\end{equation}
+Since $\iota_{2}$ satisfies Eqs.~(\ref{eq:iota-constraints}) and
+Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are a QIVPMs. By
+Thm.~\ref{thm:Finite-precision-Gleason}, $\rho_{0}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
+and $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
+implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$.
+This is true because the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $
+is $\frac{1}{24}$.
 

### 2017-10-20 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 
-\section{Gleason's Theorem and Born rule}
+\section{Born rule and Gleason's Theorem}
 
@@
 
-\noindent Because Eqs.~(\ref{eq:iota-constraints}) are the direct
-counterpart of Eqs.~(\ref{eq:QIVPM-constraints}) and Eq.~(\ref{eq:iota-Inclusion})
+\noindent The first three constraints, Eqs.~(\ref{eq:iota-constraints}),
+are the direct counterpart of the corresponding QIVPM constraints,
+Eqs.~(\ref{eq:QIVPM-constraints}); the last condition, Eq.~(\ref{eq:iota-Inclusion}),
 is the direct counterpart of the convexity condition, Eq.~(\ref{eq:classicalconvex})
-and Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-$\iota\circ\mu$ should always be a IVPM no matter in classical or
-quantum case. Conversely, if $\iota\circ\mu$ is always a IVPM, then
-$\iota$ must be a THOS rule. In other words, $\iota$ is a THOS rule
-is a necessary and sufficient condition for $\iota\circ\mu$ is always
-a IVPM as we next show.
+and (\ref{eq:QuantumInterval-valuedProbability-Inclusion}). Therefore
+the composited function~$\iota\circ\mu$ satisfies the constraints
+for IVPMs naturally no matter in classical or quantum case. Conversely,
+if $\iota\circ\mu$ is always a IVPM, then $\iota$ must be a THOS
+rule. In other words, $\iota$ is a THOS rule is a necessary and sufficient
+condition for $\iota\circ\mu$ is always a IVPM as we next show.
 
@@
 As we have discussed, Statement~\ref{enu:iota-subject-to} implies
-\ref{enu:iota-mu-QIVPM}. The rest of the proof is to prove that if
+\ref{enu:iota-mu-QIVPM}. The rest of the proof is to show that if
 $\iota$ is not a THOS rule, then $\iota\circ\mu$ might not be a
-QIVPM. If $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
-we can find three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
-such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
-Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
-Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
-fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-\begin{eqnarray*}
- &  & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
- & \nsubseteq & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\,,
-\end{eqnarray*}
-and cannot be a QIVPM. Therefore, $\iota$ is a THOS rule if and only
-if $\iota\circ\mu$ is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
-and \ref{enu:iota-mu-CIVPM} are equivalent as well~\citep{HOSTunpublished}.
+QIVPM. Suppose there are three particular numbers~$x_{0}$, $x_{1}$,
+and $x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
+but they doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider
+the state 
+\begin{equation}
+\begin{aligned}\rho={} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
+ & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
+\end{aligned}
+\end{equation}
+When $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$, we
+have $P_{0}P_{1}=\proj{2}$ and $P_{0}+P_{1}-P_{0}P_{1}=\proj{0}+\proj{1}+\proj{2}$.
+By applying $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ on these
+projectors, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+becomes Eq.~(\ref{eq:iota-Inclusion}) which cannot be satisfied
+by how we pick $x_{0}$, $x_{1}$, and $x_{2}$. Therefore, $\iota$
+is a THOS rule if and only if $\iota\circ\mu$ is always a QIVPM.
+Similarly, Statement~\ref{enu:iota-subject-to} and \ref{enu:iota-mu-CIVPM}
+are equivalent as well~\citep{HOSTunpublished}.
 

### 2017-10-21 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 for IVPMs naturally no matter in classical or quantum case. Conversely,
-if $\iota\circ\mu$ is always a IVPM, then $\iota$ must be a THOS
-rule. In other words, $\iota$ is a THOS rule is a necessary and sufficient
+if $\iota\circ\mu$ is always a IVPM, then $\iota$ is a THOS rule.
+In other words, $\iota$ is a THOS rule is a necessary and sufficient
 condition for $\iota\circ\mu$ is always a IVPM as we next show.
@@
 projectors, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-becomes Eq.~(\ref{eq:iota-Inclusion}) which cannot be satisfied
-by how we pick $x_{0}$, $x_{1}$, and $x_{2}$. Therefore, $\iota$
-is a THOS rule if and only if $\iota\circ\mu$ is always a QIVPM.
-Similarly, Statement~\ref{enu:iota-subject-to} and \ref{enu:iota-mu-CIVPM}
-are equivalent as well~\citep{HOSTunpublished}.
+becomes Eq.~(\ref{eq:iota-Inclusion}) which cannot be satisfied.
+Therefore, $\iota$ is a THOS rule if and only if $\iota\circ\mu$
+is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
+and \ref{enu:iota-mu-CIVPM} are equivalent as well~\citep{HOSTunpublished}.
 

### 2017-10-21 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 
-Although a THOS rule have many desirable properties, the set of intervals
+Although a THOS rule has many desirable properties, the set of intervals
 it mapping to either is trivial or contains infinite intervals.
@@
 By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
-is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992}.
-It is well-known that a Wright-convex function is midpoint-convex
-or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
-i.e., we have
-\begin{equation}
-\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
-\end{equation}
+is Wright-convex~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992},
+i.e., 
+\begin{equation}
+\begin{aligned} & \iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\\
+\ge{} & \iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)\,.
+\end{aligned}
+\end{equation}
+Then, for any $x_{0}'$ and $x_{1}'\in\left[0,1\right]$, we can substitute
+$x_{0}$ and $x_{1}$ by $\left(x_{0}'-x_{1}'\right)/2$ , substitute
+$x_{2}$ by $x_{1}'$, and get the following inequality 
+\begin{eqnarray}
+\frac{\iotal\left(x_{0}'\right)+\iotal\left(x_{1}'\right)}{2} & \ge & \iotal\left(\frac{x_{0}'+x_{1}'}{2}\right)\,,
+\end{eqnarray}
+i.e., $\iotal$ is midpoint-convex or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992}.
 Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,

### 2017-10-21 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 \end{equation}
-When $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$, we
-have $P_{0}P_{1}=\proj{2}$ and $P_{0}+P_{1}-P_{0}P_{1}=\proj{0}+\proj{1}+\proj{2}$.
-By applying $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ on these
-projectors, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-becomes Eq.~(\ref{eq:iota-Inclusion}) which cannot be satisfied.
-Therefore, $\iota$ is a THOS rule if and only if $\iota\circ\mu$
-is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
+Then, the composited function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$, and
+cannot be a QIVPM. Therefore, $\iota$ is a THOS rule if and only
+if $\iota\circ\mu$ is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
 and \ref{enu:iota-mu-CIVPM} are equivalent as well~\citep{HOSTunpublished}.
@@
 \end{equation}
-Then, for any $x_{0}'$ and $x_{1}'\in\left[0,1\right]$, we can substitute
-$x_{0}$ and $x_{1}$ by $\left(x_{0}'-x_{1}'\right)/2$ , substitute
-$x_{2}$ by $x_{1}'$, and get the following inequality 
+Then, for any $x_{0}'$ and $x_{1}'\in\left[0,1\right]$ with $x_{0}'\ge x_{1}'$,
+we can substitute $x_{0}$ and $x_{1}$ by $\left(x_{0}'-x_{1}'\right)/2$
+, substitute $x_{2}$ by $x_{1}'$, and get the following inequality
 \begin{eqnarray}
@@
 
-Even if a THOS rule~$\iota$ maps to $\mathscr{I}_{0}$ or infinite
-intervals, the composited function~$\iota\circ\mu$ mapping to a
-finite set of intervals~$\mathscr{I}$ may still be a QIVPM when
-$\iota$ is not a THOS rule. For example, we can weaken Eq.~(\ref{eq:iota-Inclusion})
-to the following condition: for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
-their sum~$x_{0}+x_{1}\in\left[0,1\right]$ implies
+Even if $\iota$ has to be a THOS rule to guarantee $\iota\circ\mu$
+to be a QIVPM, the composited function~$\iota\circ\mu$ may still
+be a QIVPM when $\iota$ is not a THOS rule. In this case, the composited
+function~$\iota\circ\mu$ could only map to a finite set of intervals.
+For example, we can weaken the convex condition Eq.~(\ref{eq:iota-Inclusion})
+to the following additive condition: for any numbers~$x_{0}$ and
+$x_{1}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}\in\left[0,1\right]$
+implies
 \begin{equation}
@@
 and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$,
+a set of intervals
+\begin{equation}
+\begin{aligned}\mathscr{I}_{2}={} & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\\
+ & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{1}{4},1\right],\necess\right\} 
+\end{aligned}
+\end{equation}
 and a interval-valued function~$\iota_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
-\begin{equation}
-\iota_{2}\left(x\right)=\begin{cases}
-\imposs\,, & \textrm{ if }x=0\,;\\
-\left[0,\tfrac{1}{4}\right]\,, & \textrm{ if }x\in\left(0,\tfrac{1}{8}\right]\,;\\
-\left[0,{\textstyle \tfrac{1}{2}}\right]\,, & \textrm{ if }x\in\left(\tfrac{1}{8},\tfrac{3}{8}\right)\,;\\
-\left[\tfrac{1}{4},\tfrac{3}{4}\right]\,, & \textrm{ if }x\in\left[\tfrac{3}{8},\tfrac{5}{8}\right]\,;\\
-\left[\tfrac{1}{2},1\right]\,, & \textrm{ if }x\in\left(\tfrac{5}{8},\tfrac{7}{8}\right)\,;\\
-\left[\tfrac{1}{4},1\right]\,, & \textrm{ if }x\in\left[\tfrac{7}{8},1\right)\,;\\
-\necess\,, & \textrm{ if }x=1\,.
-\end{cases}\label{eq:iota}
-\end{equation}
+defined in Table~\ref{tab:I_2}.
+\begin{table}
+\caption{\label{tab:I_2}A interval-valued function~$\iota_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$.}
+\centering{}%
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$x$ & $\iota_{2}\left(x\right)$\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+$x=0$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$0<x\le\tfrac{1}{8}$ & $\left[0,\tfrac{1}{4}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\tfrac{1}{8}<x<\tfrac{3}{8}$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\tfrac{3}{8}\le x\le\tfrac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\tfrac{5}{8}<x<\tfrac{7}{8}$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\tfrac{7}{8}\le x<1$ & $\left[\tfrac{1}{4},1\right]$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$x=1$ & $\necess$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
 Since $\iota_{2}$ satisfies Eqs.~(\ref{eq:iota-constraints}) and
 Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
-and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are a QIVPMs. By
-Thm.~\ref{thm:Finite-precision-Gleason}, $\rho_{0}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
+and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are both QIVPMs.
+By Thm.~\ref{thm:Finite-precision-Gleason}, $\rho_{0}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
 and $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$

### 2017-10-22 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 gets closer and closer to $\rho$ as the intervals get narrower and
-narrower. To state this result, we introduce a few technical notions.
-First, the norm of a pure state~$\ket{\psi}$ is defined as usual
-$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Then, the norm
-of the difference between two states~$\rho$ and $\rho'$ is just
-the usual operator norm
+narrower. Eventually, the collection of consistent states collapses
+to the singleton set~$\left\{ \rho\right\} $ as the intervals becomes
+the infinite precise intervals~$\mathscr{I}_{\infty}$. This fact
+is essentially Gleason's theorem, but a little bit weaker because
+we only consider the composited QIVPMs~$\iota\circ\mu_{\rho}^{\mathrm{B}}$
+instead of general QIVPMs~$\bar{\mu}$. To state this result, we
+introduce a few technical notions. First, the norm of a pure state~$\ket{\psi}$
+is defined as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
+Then, the norm of the difference between two states~$\rho$ and $\rho'$
+is just the usual operator norm
 \begin{equation}
@@
 \end{equation}
-which is also commonly known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
 
@@
 if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-then the norm of their difference is $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}
+then the norm of their difference $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}
 
@@
 i.e., $\iotal$ is midpoint-convex or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992}.
-Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
+Together with the fact that $\iotal$ maps to a bounded interval $\left[0,1\right]$,
 the left-end function~$\iotal$ must be continuous on the unit open
-interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
+interval $\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
 Therefore, either $\iota$ maps every number in $\left(0,1\right)$
@@
 Even if $\iota$ has to be a THOS rule to guarantee $\iota\circ\mu$
-to be a QIVPM, the composited function~$\iota\circ\mu$ may still
-be a QIVPM when $\iota$ is not a THOS rule. In this case, the composited
-function~$\iota\circ\mu$ could only map to a finite set of intervals.
-For example, we can weaken the convex condition Eq.~(\ref{eq:iota-Inclusion})
-to the following additive condition: for any numbers~$x_{0}$ and
-$x_{1}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}\in\left[0,1\right]$
+a QIVPM, the composited function $\iota\circ\mu$ may still be a QIVPM
+when $\iota$ is not a THOS rule. In this case, the composited function
+$\iota\circ\mu$ could only map to a finite set of intervals. For
+example, we can weaken the convex condition Eq.~(\ref{eq:iota-Inclusion})
+to the following additive condition: for any numbers $x_{0}$ and
+$x_{1}\in\left[0,1\right]$, their sum $x_{0}+x_{1}\in\left[0,1\right]$
 implies

### 2017-10-22 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-there is always a state consistent with the composited QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$~\citep{HOSTunpublished}.
+there is always a state consistent with composited QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$~\citep{HOSTunpublished}.
 Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
@@
 is essentially Gleason's theorem, but a little bit weaker because
-we only consider the composited QIVPMs~$\iota\circ\mu_{\rho}^{\mathrm{B}}$
-instead of general QIVPMs~$\bar{\mu}$. To state this result, we
-introduce a few technical notions. First, the norm of a pure state~$\ket{\psi}$
-is defined as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
-Then, the norm of the difference between two states~$\rho$ and $\rho'$
-is just the usual operator norm
+we only consider composited QIVPMs~$\iota\circ\mu_{\rho}^{\mathrm{B}}$
+instead of general QIVPMs~$\bar{\mu}$. To state this weak version
+of Gleason's theorem, we need to introduce a few technical notions.
+First, the norm of a pure state~$\ket{\psi}$ is defined as usual
+$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Then, the norm
+of the difference between two states~$\rho$ and $\rho'$ is just
+the usual operator norm
 \begin{equation}
@@
 \end{equation}
-which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012},
+and a weak version of Gleason's theorem can be stated as follow.
 
 \begin{thm}[Finite-Precision Extension of Weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
-an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+an interval-valued function $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
 with the maximum length of intervals $\delta$. Given any state~$\rho$,
@@
 when $\iota$ is not a THOS rule. In this case, the composited function
-$\iota\circ\mu$ could only map to a finite set of intervals. For
-example, we can weaken the convex condition Eq.~(\ref{eq:iota-Inclusion})
+$\iota\circ\mu$ could only map to finite intervals. For example,
+we can weaken the convex condition, Eq.~(\ref{eq:iota-Inclusion}),
 to the following additive condition: for any numbers $x_{0}$ and
@@
 \end{equation}
-Then, given a Hilbert space of dimension~$d\le3$, when $\iota$
-satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
+Then, given a three-dimensional Hilbert space, when $\iota$ satisfies
+Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
 $\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
-More concretely, given a three-dimensional Hilbert space, consider
-two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
+More concretely, consider two states $\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
 and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$,
-a set of intervals
+and a set of intervals
 \begin{equation}
 \begin{aligned}\mathscr{I}_{2}={} & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\\
- & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{1}{4},1\right],\necess\right\} 
+ & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{1}{4},1\right],\necess\right\} \,.
 \end{aligned}
 \end{equation}
-and a interval-valued function~$\iota_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
-defined in Table~\ref{tab:I_2}.
+Since the interval-valued function~$\iota_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
+defined in Table~\ref{tab:I_2} satisfies Eqs.~(\ref{eq:iota-constraints})
+and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are both QIVPMs.
 \begin{table}
@@
 \end{table}
-Since $\iota_{2}$ satisfies Eqs.~(\ref{eq:iota-constraints}) and
-Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
-and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are both QIVPMs.
-By Thm.~\ref{thm:Finite-precision-Gleason}, $\rho_{0}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
-and $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
-implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$.
+Because of $\rho_{0}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
+and $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$~\citep{HOSTunpublished},
+Thm.~\ref{thm:Finite-precision-Gleason} asserts $\left\Vert \rho_{0}-\rho_{1}\right\Vert $
+less than or equal to the maximum length of intervals $\frac{1}{2}$.
 This is true because the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $

### 2017-10-22 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 \end{equation}
-Then, the composited function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+Then, the function induced by $\rho$, $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$,
 fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
@@
 In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-there is always a state consistent with composited QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$~\citep{HOSTunpublished}.
+there is always a state consistent with composited QIVPM $\iota\circ\mu_{\rho}^{\mathrm{B}}$.
 Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
@@
 when $\iota$ is not a THOS rule. In this case, the composited function
-$\iota\circ\mu$ could only map to finite intervals. For example,
-we can weaken the convex condition, Eq.~(\ref{eq:iota-Inclusion}),
+$\iota\circ\mu$ could map to only finite number of intervals. For
+example, we can weaken the convex condition, Eq.~(\ref{eq:iota-Inclusion}),
 to the following additive condition: for any numbers $x_{0}$ and

### 2017-10-23 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
    &  & \bar{\mu}(\mathbb{1})=\necess\,,\label{eq:necess}\\
-   &  & \bar{\mu}\left(\mathbb{1}-P\right)= \necess -\bar{\mu}\left(P\right)\,,
+   &  & \bar{\mu}\left(\mathbb{1}-P\right)= \necess-\bar{\mu}\left(P\right)\,,\label{eq:complement}
   \end{eqnarray}
@@
 \end{table}
-Because of $\rho_{0}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$
-and $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$~\citep{HOSTunpublished},
-Thm.~\ref{thm:Finite-precision-Gleason} asserts $\left\Vert \rho_{0}-\rho_{1}\right\Vert $
+Given any one dimensional projector $\proj{\psi}$, we have $\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\frac{1}{3}$
+so that $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
+On the other hand, 
+\begin{eqnarray*}
+\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right) & = & \frac{7}{24}\cdot\left|\ip{\psi}{0}\right|^{2}+\frac{1}{3}\cdot\left|\ip{\psi}{0}\right|^{2}+\frac{3}{8}\cdot\left|\ip{\psi}{0}\right|^{2}
+\end{eqnarray*}
+which is bounded between $\frac{7}{24}$ and $\frac{3}{8}$. Therefore,
+$\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$.
+According to the complement condition Eq.~(\ref{eq:complement}),
+any two dimensional projector~$P$, we also have $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\in\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$.
+Hence, $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
+and Thm.~\ref{thm:Finite-precision-Gleason} asserts $\left\Vert \rho_{0}-\rho_{1}\right\Vert $
 less than or equal to the maximum length of intervals $\frac{1}{2}$.

### 2017-10-23 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 $\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
-More concretely, consider two states $\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
-and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$,
+More concretely, consider two states $\rho_{0}=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
+and $\rho_{1}=\frac{7}{24}\proj{0}+\frac{1}{3}\proj{1}+\frac{3}{8}\proj{2}$,
 and a set of intervals
@@
 \begin{eqnarray*}
-\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right) & = & \frac{7}{24}\cdot\left|\ip{\psi}{0}\right|^{2}+\frac{1}{3}\cdot\left|\ip{\psi}{0}\right|^{2}+\frac{3}{8}\cdot\left|\ip{\psi}{0}\right|^{2}
+\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right) & = & \tfrac{7}{24}\left|\ip{\psi}{0}\right|^{2}+\tfrac{1}{3}\left|\ip{\psi}{0}\right|^{2}+\tfrac{3}{8}\left|\ip{\psi}{0}\right|^{2}
 \end{eqnarray*}

### 2017-10-23 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 long version of this paper~\cite{HOSTunpublished}. The idea of the
-proof is as follows. Given a subspace of commuting events~$\events_C$,
+proof is as follows. Given a subspace of commuting events~$\events_{\mathrm{C}}$,
 we can construct a partial orthonormal basis by diagonalization and
-complete it to a full orthonormal basis $\overline{\events_C}$. We
+complete it to a full orthonormal basis $\overline{\events_{\mathrm{C}}}$. We
 then build a bijection between the QIVPM on the set of projectors
@@
   For QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
-  of events~$\events_C\subseteq\events$ commutes, then
-  $\coreBorn\left(\bar{\mu},\events_C\right)\ne\emptyset$.
+  of events~$\events_{\mathrm{C}}\subseteq\events$ commutes, then
+  $\coreBorn\left(\bar{\mu},\events_{\mathrm{C}}\right)\ne\emptyset$.
 \end{thm}
@@
 proves that a classical IVPM always contains at least one state $\rho$
-that is consistent with every event in $\events_C$. In contrast, as we
+that is consistent with every event in $\events_{\mathrm{C}}$. In contrast, as we
 illustrate in Sec.~\ref{sec:Gleason}, the set of states
@@
 When we generalized quantum probability measures to QIVPMs, we changed
-the range from the unit interval~$\left[0,1\right]$ to a set of
-intervals~$\mathscr{I}$. This replacement suggests to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-to replace a real-valued probability~$\mu\left(P\right)$ by an interval-valued
-one~$\iota\left(\mu\left(P\right)\right)$. In other words, compositing
-$\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-produces a function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
+the range from the unit interval $\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
+This replacement suggests to find a function $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+to replace a real-valued probability $\mu\left(P\right)$ by an interval-valued
+one $\iota\left(\mu\left(P\right)\right)$. In other words, compositing
+$\iota$ with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+produces a function $\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
 which has the same domain and range as a QIVPM. In order to guarantee
 $\iota\circ\mu$ always a QIVPM, we consider the following homomorphism-like
-properties for $\iota$.
+properties for~$\iota$.
 
@@
 of intervals $\mathscr{I}$ including $\imposs$ and $\necess$, a
-function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is called
+function $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is called
 a THOS rule if $\iota$ is subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
@@
 is a THOS rule.
-\item \label{enu:iota-mu-CIVPM}The composited function~$\iota\circ\mu:\events_{C}\rightarrow\mathscr{I}$
-is always a classical IVPM for any classical probability measure~$\mu:\events_{C}\rightarrow\left[0,1\right]$.
+\item \label{enu:iota-mu-CIVPM}The composited function~$\iota\circ\mu:\events_{\mathrm{C}}\rightarrow\mathscr{I}$
+is always a classical IVPM for any classical probability measure~$\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$.
 \item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
@@
 \end{equation}
-Then, the function induced by $\rho$, $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$,
+whose inducing function $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
 fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
@@
 gets closer and closer to $\rho$ as the intervals get narrower and
-narrower. Eventually, the collection of consistent states collapses
+narrower. Eventually, the collection of consisting states collapses
 to the singleton set~$\left\{ \rho\right\} $ as the intervals becomes
 the infinite precise intervals~$\mathscr{I}_{\infty}$. This fact
-is essentially Gleason's theorem, but a little bit weaker because
-we only consider composited QIVPMs~$\iota\circ\mu_{\rho}^{\mathrm{B}}$
-instead of general QIVPMs~$\bar{\mu}$. To state this weak version
-of Gleason's theorem, we need to introduce a few technical notions.
-First, the norm of a pure state~$\ket{\psi}$ is defined as usual
-$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Then, the norm
-of the difference between two states~$\rho$ and $\rho'$ is just
-the usual operator norm
+is a weak version of Gleason's theorem because we only consider composited
+QIVPMs $\iota\circ\mu_{\rho}^{\mathrm{B}}$ instead of general QIVPMs~$\bar{\mu}$.
+To state this result, we need to introduce the norm of pure states
+and operstors. The norm of a pure state~$\ket{\psi}$ is defined
+as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$, and
+the norm of the difference between two states~$\rho$ and $\rho'$
+is just the usual operator norm
 \begin{equation}
@@
 \end{equation}
-which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012},
-and a weak version of Gleason's theorem can be stated as follow.
+which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+Then, a weak version of Gleason's theorem can be stated as follow.
 
@@
 any THOS rule~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$, either
-$\mathscr{I}=\mathscr{I}_{0}$ defined in Eq.(\ref{eq:3-value-intervals})
-or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
+$\mathscr{I}=\mathscr{I}_{0}$ or $\mathscr{I}$ contains uncountably
+many intervals.\end{thm}
 
@@
 \begin{eqnarray*}
-\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right) & = & \tfrac{7}{24}\left|\ip{\psi}{0}\right|^{2}+\tfrac{1}{3}\left|\ip{\psi}{0}\right|^{2}+\tfrac{3}{8}\left|\ip{\psi}{0}\right|^{2}
+\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right) & = & \tfrac{7}{24}\left|\ip{\psi}{0}\right|^{2}+\tfrac{1}{3}\left|\ip{\psi}{1}\right|^{2}+\tfrac{3}{8}\left|\ip{\psi}{2}\right|^{2}
 \end{eqnarray*}
@@
 According to the complement condition Eq.~(\ref{eq:complement}),
-any two dimensional projector~$P$, we also have $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\in\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$.
-Hence, $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
+we also have $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\in\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
+for any two dimensional projector~$P$. Hence, $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
 and Thm.~\ref{thm:Finite-precision-Gleason} asserts $\left\Vert \rho_{0}-\rho_{1}\right\Vert $

### 2017-10-24 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 and $x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
-but they doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider
-the state 
+but they don't satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the
+state 
 \begin{equation}
@@
 In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-there is always a state consistent with composited QIVPM $\iota\circ\mu_{\rho}^{\mathrm{B}}$.
+there is always a state consistent with any composited QIVPM $\iota\circ\mu_{\rho}^{\mathrm{B}}$.
 Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
@@
 to the singleton set~$\left\{ \rho\right\} $ as the intervals becomes
-the infinite precise intervals~$\mathscr{I}_{\infty}$. This fact
+the infinitely precise intervals~$\mathscr{I}_{\infty}$. This fact
 is a weak version of Gleason's theorem because we only consider composited
 QIVPMs $\iota\circ\mu_{\rho}^{\mathrm{B}}$ instead of general QIVPMs~$\bar{\mu}$.
-To state this result, we need to introduce the norm of pure states
-and operstors. The norm of a pure state~$\ket{\psi}$ is defined
-as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$, and
-the norm of the difference between two states~$\rho$ and $\rho'$
-is just the usual operator norm
-\begin{equation}
-\left\Vert \rho-\rho'\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert \left(\rho-\rho'\right)\ket{\psi}\right\Vert \,,
+To precisely state this result, we need to introduce the norm of pure
+states and operators. The norm of a pure state~$\ket{\psi}$ is defined
+as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Similarly,
+given any Hermitian operator~$A$, we consider the usual operator
+norm
+\begin{equation}
+\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert \,,
 \end{equation}
@@
 we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
-for any 1-dimensional projector~$\proj{\psi}$. Since the maximum
+for any one-dimensional projector $\proj{\psi}$. Since the maximum
 length of the intervals in $\mathscr{I}$ is $\delta$, it is also
@@
 \caption{\label{tab:I_2}A interval-valued function~$\iota_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$.}
-\centering{}%
+
+\hfill{}%
+\begin{minipage}[t]{2.5cm}%
+\begin{center}
 \begin{tabular}{cc}
@@
 $\tfrac{3}{8}\le x\le\tfrac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\par\end{center}%
+\end{minipage}\hfill{}%
+\begin{minipage}[t]{2.5cm}%
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$x$ & $\iota_{2}\left(x\right)$\tabularnewline\addlinespace
+\midrule
 \midrule 
@@
 \end{tabular}
+\par\end{center}%
+\end{minipage}\hfill{}
 \end{table}
-Given any one dimensional projector $\proj{\psi}$, we have $\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\frac{1}{3}$
+Given any one-dimensional projector $\proj{\psi}$, we have $\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\frac{1}{3}$
 so that $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
@@
 $\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$.
-According to the complement condition Eq.~(\ref{eq:complement}),
+According to the complement condition, Eq.~(\ref{eq:complement}),
 we also have $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\in\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
-for any two dimensional projector~$P$. Hence, $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
+for any two-dimensional projector~$P$. Hence, $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
 and Thm.~\ref{thm:Finite-precision-Gleason} asserts $\left\Vert \rho_{0}-\rho_{1}\right\Vert $

### 2017-10-24 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 Eqs.~(\ref{eq:QIVPM-constraints}); the last condition, Eq.~(\ref{eq:iota-Inclusion}),
-is the direct counterpart of the convexity condition, Eq.~(\ref{eq:classicalconvex})
+is the direct counterpart of the convexity conditions, Eq.~(\ref{eq:classicalconvex})
 and (\ref{eq:QuantumInterval-valuedProbability-Inclusion}). Therefore
@@
 fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$, and
-cannot be a QIVPM. Therefore, $\iota$ is a THOS rule if and only
-if $\iota\circ\mu$ is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
-and \ref{enu:iota-mu-CIVPM} are equivalent as well~\citep{HOSTunpublished}.
+when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. Thus,
+$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ cannot be a QIVPM. Therefore,
+$\iota$ is a THOS rule if and only if $\iota\circ\mu$ is always
+a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to} and \ref{enu:iota-mu-CIVPM}
+are equivalent as well~\citep{HOSTunpublished}.
 
@@
 given any Hermitian operator~$A$, we consider the usual operator
-norm
-\begin{equation}
-\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert \,,
-\end{equation}
+norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
 which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
@@
 \]
-Since $\rho-\rho'$ is Hermitian, $\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
+Since $\rho-\rho'$ is Hermitian, $\max_{\left\Vert \psi\right\Vert =1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
 is the maximum absolute value of the eigenvalues of $\rho-\rho'$~\citep{544199},
@@
 when $\iota$ is not a THOS rule. In this case, the composited function
-$\iota\circ\mu$ could map to only finite number of intervals. For
-example, we can weaken the convex condition, Eq.~(\ref{eq:iota-Inclusion}),
+$\iota\circ\mu$ could map to non-trivial finite number of intervals.
+For example, we can weaken the convex condition, Eq.~(\ref{eq:iota-Inclusion}),
 to the following additive condition: for any numbers $x_{0}$ and
@@
 $\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
-More concretely, consider two states $\rho_{0}=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
+More concretely, consider an orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$,
+two states $\rho_{0}=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
 and $\rho_{1}=\frac{7}{24}\proj{0}+\frac{1}{3}\proj{1}+\frac{3}{8}\proj{2}$,

### 2017-10-24 prop_letter.tex
Updating by Prof. Ortiz...

@@
 
-The question of how to address this controversy is therefore a
-fundamental problem.  How does one
+The question of how to address this controversy, and the effect of 
+finite precision on measurements in general, is therefore 
+a fundamental problem.  How does one
 develop mathematical theories of quantum mechanics that are
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Kochen-Specker Theorem and Contextuality}
+\section{The Kochen-Specker Theorem and Contextuality}
 \label{sec:Kochen-Specker}
@@
 
-\section{Born rule and Gleason's Theorem}
+\section{The Born rule and Gleason's Theorem}
 

### 2017-10-24 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 \end{equation}
-whose inducing function $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+Its inducing function $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
 fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. Thus,
-$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ cannot be a QIVPM. Therefore,
-$\iota$ is a THOS rule if and only if $\iota\circ\mu$ is always
-a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to} and \ref{enu:iota-mu-CIVPM}
-are equivalent as well~\citep{HOSTunpublished}.
+when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$ so
+that $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ cannot be a QIVPM.
+Therefore, $\iota$ is a THOS rule if and only if $\iota\circ\mu$
+is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
+and \ref{enu:iota-mu-CIVPM} are equivalent as well~\citep{HOSTunpublished}.
 
@@
 an interval-valued function $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-with the maximum length of intervals $\delta$. Given any state~$\rho$,
+with the maximum length of intervals~$m$. Given any state~$\rho$,
 if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-then the norm of their difference $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}
+then the norm of their difference $\left\Vert \rho-\rho'\right\Vert \le m$.\end{thm}
 
@@
 for any one-dimensional projector $\proj{\psi}$. Since the maximum
-length of the intervals in $\mathscr{I}$ is $\delta$, it is also
-the upper bound of the difference 
+length of the intervals in $\mathscr{I}$ is $m$, it is also the
+upper bound of the difference 
 \[
-\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le\delta\,.
+\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le m\,.
 \]
@@
 and equal to $\left\Vert \rho-\rho'\right\Vert $~\citep{GolubVanLoan1996,Foucart2012}.
-Hence, $\left\Vert \rho-\rho'\right\Vert \le\delta$.
+Hence, $\left\Vert \rho-\rho'\right\Vert \le m$.
 
@@
 \end{eqnarray*}
-which is bounded between $\frac{7}{24}$ and $\frac{3}{8}$. Therefore,
+is bounded between $\frac{7}{24}$ and $\frac{3}{8}$. Therefore,
 $\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$.

### 2017-10-25 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 narrower. Eventually, the collection of consisting states collapses
-to the singleton set~$\left\{ \rho\right\} $ as the intervals becomes
+to the singleton set~$\left\{ \rho\right\} $ as the intervals become
 the infinitely precise intervals~$\mathscr{I}_{\infty}$. This fact

### 2017-10-26 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 \lineskiplimit=1pt
-\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
-\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}
+\newcommand{\ultramodular}{\ensuremath{f}}
+\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{\mathrm{L{#1}}}}}
+\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{\mathrm{R{#1}}}}}
 
@@
 the range from the unit interval $\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
-This replacement suggests to find a function $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+This replacement suggests to find a function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
 to replace a real-valued probability $\mu\left(P\right)$ by an interval-valued
-one $\iota\left(\mu\left(P\right)\right)$. In other words, compositing
-$\iota$ with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
-produces a function $\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
-which has the same domain and range as a QIVPM. In order to guarantee
-$\iota\circ\mu$ always a QIVPM, we consider the following homomorphism-like
-properties for~$\iota$.
-
-\begin{definition}[THOS Rule]\label{def:THOS}Given a collection
-of intervals $\mathscr{I}$ including $\imposs$ and $\necess$, a
-function $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is called
-a THOS rule if $\iota$ is subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
+one $\ultramodular\left(\mu\left(P\right)\right)$. In other words,
+compositing $\ultramodular$ with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+produces a function $\ultramodular\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\ultramodular}{\rightarrow}\mathscr{I}$
+with the same domain and range as a QIVPM. In order to guarantee $\ultramodular\circ\mu$
+always a QIVPM, we consider the following homomorphism-like properties
+for~$\ultramodular$.
+
+\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
+a collection of intervals $\mathscr{I}$ including $\imposs$ and
+$\necess$, a function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
+is called a ultramodular function if $\ultramodular$ is subject to
+the following constraints:\begin{subequations}\label{eq:iota-constraints}
 \begin{eqnarray}
- &  & \iota(0)=\imposs\,,\\
- &  & \iota(1)=\necess\,,\\
- &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
+ &  & \ultramodular(0)=\imposs\,,\\
+ &  & \ultramodular(1)=\necess\,,\\
+ &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
 \end{eqnarray}
@@
 \begin{equation}
-\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
+\ultramodular\left(x_{0}+x_{1}+x_{2}\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
 \end{equation}
@@
 and (\ref{eq:QuantumInterval-valuedProbability-Inclusion}). Therefore
-the composited function~$\iota\circ\mu$ satisfies the constraints
+the composited function~$\ultramodular\circ\mu$ satisfies the constraints
 for IVPMs naturally no matter in classical or quantum case. Conversely,
-if $\iota\circ\mu$ is always a IVPM, then $\iota$ is a THOS rule.
-In other words, $\iota$ is a THOS rule is a necessary and sufficient
-condition for $\iota\circ\mu$ is always a IVPM as we next show.
-
-\begin{thm}[Equivalence among THOS Rules and IVPMs]\label{thm:iota-statements}The
+if $\ultramodular\circ\mu$ is always a IVPM, then the function~$\ultramodular$
+is ultramodular. In other words, $\ultramodular$ is ultramodular
+is a necessary and sufficient condition for $\ultramodular\circ\mu$
+is always a IVPM as we next show.
+
+\begin{thm}[Equivalence among ultramodular functions and IVPMs]\label{thm:iota-statements}The
 following three statements are equivalent:
 \begin{enumerate}
-\item \label{enu:iota-subject-to}A function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
-is a THOS rule.
-\item \label{enu:iota-mu-CIVPM}The composited function~$\iota\circ\mu:\events_{\mathrm{C}}\rightarrow\mathscr{I}$
+\item \label{enu:iota-subject-to}A function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
+is ultramodular.
+\item \label{enu:iota-mu-CIVPM}The composited function~$\ultramodular\circ\mu:\events_{\mathrm{C}}\rightarrow\mathscr{I}$
 is always a classical IVPM for any classical probability measure~$\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$.
-\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
+\item \label{enu:iota-mu-QIVPM}The composited function~$\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$
 is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
@@
 
-As we have discussed, Statement~\ref{enu:iota-subject-to} implies
-\ref{enu:iota-mu-QIVPM}. The rest of the proof is to show that if
-$\iota$ is not a THOS rule, then $\iota\circ\mu$ might not be a
+The equivalence between Statement~\ref{enu:iota-subject-to} and
+\ref{enu:iota-mu-CIVPM} is a well-known classical result~\citep{Choquet1954,NgMoYeh1997,Marinacci_2004}.
+For quantum case, Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-QIVPM}
+as we have discussed. The rest of the proof is to show that if $\ultramodular$
+is not ultramodular, then $\ultramodular\circ\mu$ might not be a
 QIVPM. Suppose there are three particular numbers~$x_{0}$, $x_{1}$,
@@
 \end{equation}
-Its inducing function $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+Its inducing function $\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
 fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
 when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$ so
-that $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ cannot be a QIVPM.
-Therefore, $\iota$ is a THOS rule if and only if $\iota\circ\mu$
-is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
-and \ref{enu:iota-mu-CIVPM} are equivalent as well~\citep{HOSTunpublished}.
+that $\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ cannot
+be a QIVPM. Therefore, $\ultramodular$ is ultramodular if and only
+if $\ultramodular\circ\mu$ is always a QIVPM.
 
 In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-there is always a state consistent with any composited QIVPM $\iota\circ\mu_{\rho}^{\mathrm{B}}$.
-Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
+there is always a state consistent with any composited QIVPM $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$.
+Moreover, the collection of states consistent with $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$
 gets closer and closer to $\rho$ as the intervals get narrower and
@@
 is a weak version of Gleason's theorem because we only consider composited
-QIVPMs $\iota\circ\mu_{\rho}^{\mathrm{B}}$ instead of general QIVPMs~$\bar{\mu}$.
-To precisely state this result, we need to introduce the norm of pure
-states and operators. The norm of a pure state~$\ket{\psi}$ is defined
-as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Similarly,
-given any Hermitian operator~$A$, we consider the usual operator
-norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
+QIVPMs $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$ instead of general
+QIVPMs~$\bar{\mu}$. To precisely state this result, we need to introduce
+the norm of pure states and operators. The norm of a pure state~$\ket{\psi}$
+is defined as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
+Similarly, given any Hermitian operator~$A$, we consider the usual
+operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
 which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
@@
 \begin{thm}[Finite-Precision Extension of Weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
-an interval-valued function $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
+an interval-valued function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
 with the maximum length of intervals~$m$. Given any state~$\rho$,
-if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+if a state $\rho'\in\coreBorn\left(\ultramodular\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
 then the norm of their difference $\left\Vert \rho-\rho'\right\Vert \le m$.\end{thm}
 
-Given a state~$\rho'$ consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
-we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
+Given a state~$\rho'$ consistent with $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$,
+we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\ultramodular\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
 for any one-dimensional projector $\proj{\psi}$. Since the maximum
@@
 
-Although a THOS rule has many desirable properties, the set of intervals
-it mapping to either is trivial or contains infinite intervals.
-
-\begin{thm}[Range of THOS Rules]\label{thm:convex-uncountable}For
-any THOS rule~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$, either
-$\mathscr{I}=\mathscr{I}_{0}$ or $\mathscr{I}$ contains uncountably
+Although a ultramodular function has many desirable properties, the
+set of intervals it mapping to either is trivial or contains infinite
+intervals.
+
+\begin{thm}[Range of ultramodular functions]\label{thm:convex-uncountable}For
+any ultramodular function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$,
+either $\mathscr{I}=\mathscr{I}_{0}$ or $\mathscr{I}$ contains uncountably
 many intervals.\end{thm}
 
-Since $\iota$ maps to intervals, we can decompose it into two functions:
-its left-end and right-end $\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
-By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
+Since $\ultramodular$ maps to intervals, we can decompose it into
+two functions: its left-end and right-end $\left[\ultramodularL\left(x\right),\ultramodularR\left(x\right)\right]=\ultramodular\left(x\right)$.
+By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\ultramodularL:\left[0,1\right]\rightarrow\left[0,1\right]$
 is Wright-convex~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992},
@@
 \begin{equation}
-\begin{aligned} & \iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\\
-\ge{} & \iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)\,.
+\begin{aligned} & \ultramodularL\left(x_{0}+x_{1}+x_{2}\right)+\ultramodularL\left(x_{2}\right)\\
+\ge{} & \ultramodularL\left(x_{0}+x_{2}\right)+\ultramodularL\left(x_{1}+x_{2}\right)\,.
 \end{aligned}
@@
 \begin{eqnarray}
-\frac{\iotal\left(x_{0}'\right)+\iotal\left(x_{1}'\right)}{2} & \ge & \iotal\left(\frac{x_{0}'+x_{1}'}{2}\right)\,,
+\frac{\ultramodularL\left(x_{0}'\right)+\ultramodularL\left(x_{1}'\right)}{2} & \ge & \ultramodularL\left(\frac{x_{0}'+x_{1}'}{2}\right)\,,
 \end{eqnarray}
-i.e., $\iotal$ is midpoint-convex or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992}.
-Together with the fact that $\iotal$ maps to a bounded interval $\left[0,1\right]$,
-the left-end function~$\iotal$ must be continuous on the unit open
-interval $\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
-Therefore, either $\iota$ maps every number in $\left(0,1\right)$
-to the same interval, or the number of intervals that $\iota$ maps
-to must be uncountable.
-
-Even if $\iota$ has to be a THOS rule to guarantee $\iota\circ\mu$
-a QIVPM, the composited function $\iota\circ\mu$ may still be a QIVPM
-when $\iota$ is not a THOS rule. In this case, the composited function
-$\iota\circ\mu$ could map to non-trivial finite number of intervals.
-For example, we can weaken the convex condition, Eq.~(\ref{eq:iota-Inclusion}),
-to the following additive condition: for any numbers $x_{0}$ and
-$x_{1}\in\left[0,1\right]$, their sum $x_{0}+x_{1}\in\left[0,1\right]$
-implies
-\begin{equation}
-\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
-\end{equation}
-Then, given a three-dimensional Hilbert space, when $\iota$ satisfies
-Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
-$\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
+i.e., $\ultramodularL$ is midpoint-convex or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992}.
+Together with the fact that $\ultramodularL$ maps to a bounded interval
+$\left[0,1\right]$, the left-end function~$\ultramodularL$ must
+be continuous on the unit open interval $\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
+Therefore, either $\ultramodular$ maps every number in $\left(0,1\right)$
+to the same interval, or the number of intervals that $\ultramodular$
+maps to must be uncountable.
+
+Even if $\ultramodular$ has to be ultramodular to guarantee $\ultramodular\circ\mu$
+a QIVPM, the composited function $\ultramodular\circ\mu$ may still
+be a QIVPM when $\ultramodular$ is not ultramodular. In this case,
+the composited function $\ultramodular\circ\mu$ could map to non-trivial
+finite number of intervals. For example, we can weaken the convex
+condition, Eq.~(\ref{eq:iota-Inclusion}), to the following additive
+condition: for any numbers $x_{0}$ and $x_{1}\in\left[0,1\right]$,
+their sum $x_{0}+x_{1}\in\left[0,1\right]$ implies
+\begin{equation}
+\ultramodular\left(x_{0}+x_{1}\right)\subseteq\ultramodular\left(x_{0}\right)+\ultramodular\left(x_{1}\right)\,.\label{eq:iota-add}
+\end{equation}
+Then, given a three-dimensional Hilbert space, when $\ultramodular$
+satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
+$\ultramodular\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
 More concretely, consider an orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$,
@@
 \begin{aligned}\mathscr{I}_{2}={} & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\\
- & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{1}{4},1\right],\necess\right\} \,.
+ & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{3}{4},1\right],\necess\right\} \,.
 \end{aligned}
 \end{equation}
-Since the interval-valued function~$\iota_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
+Since the interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
 defined in Table~\ref{tab:I_2} satisfies Eqs.~(\ref{eq:iota-constraints})
-and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
-and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are both QIVPMs.
+and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\ultramodular_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+and $\ultramodular_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are both
+QIVPMs.
 \begin{table}
-\caption{\label{tab:I_2}A interval-valued function~$\iota_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$.}
+\caption{\label{tab:I_2}A interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$.}
 
@@
 \addlinespace
-$x$ & $\iota_{2}\left(x\right)$\tabularnewline\addlinespace
+$x$ & $\ultramodular_{2}\left(x\right)$\tabularnewline\addlinespace
 \midrule
@@
 \addlinespace
-$\tfrac{7}{8}\le x<1$ & $\left[\tfrac{1}{4},1\right]$\tabularnewline\addlinespace
+$\tfrac{7}{8}\le x<1$ & $\left[\tfrac{3}{4},1\right]$\tabularnewline\addlinespace
 \midrule 
@@
 Given any one-dimensional projector $\proj{\psi}$, we have $\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\frac{1}{3}$
-so that $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
+so that $\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
 On the other hand, 
@@
 is bounded between $\frac{7}{24}$ and $\frac{3}{8}$. Therefore,
-$\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$.
+$\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\in\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$.
 According to the complement condition, Eq.~(\ref{eq:complement}),
-we also have $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\in\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
-for any two-dimensional projector~$P$. Hence, $\rho_{1}\in\coreBorn\left(\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
+we also have $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\in\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
+for any two-dimensional projector~$P$. Hence, $\rho_{1}\in\coreBorn\left(\ultramodular_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
 and Thm.~\ref{thm:Finite-precision-Gleason} asserts $\left\Vert \rho_{0}-\rho_{1}\right\Vert $

### 2017-10-26 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

@@
 
-\begin{thm}[Equivalence among ultramodular functions and IVPMs]\label{thm:iota-statements}The
+\begin{thm}[Equivalence among Ultramodular Functions and IVPMs]\label{thm:iota-statements}The
 following three statements are equivalent:
@@
 
-\begin{thm}[Range of ultramodular functions]\label{thm:convex-uncountable}For
+\begin{thm}[Range of Ultramodular Functions]\label{thm:convex-uncountable}For
 any ultramodular function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$,

### 2017-10-26 prop_letter.tex
intro

--- 2017-10-25 prop_letter.tex
@@
 mechanics regarding the tension between finite precision measurement
-and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome
-of a theory that is contextual depends upon
-whether  compatible sets of observables are measured together or
-separately; a non-contextual theory gives the same results in either
-case.  A classic example of the varying opinions on the impact of
-imprecision is the disagreement between
-Meyer~\cite{PhysRevLett.83.3751} and 
-Mermin~\cite{Mermin1999}  on whether finite-precision
-measurements invalidate the spirit of the Kochen-Specker
-theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.  The Kochen-Specker  
-theorem is in essence a
-mathematical statement about contextuality, asserting that
-in a Hilbert space of dimension $d \ge 3$, it is
-impossible to associate definite measured values, $\mu(P_i)= 0$ or
-$1$, with every projection operator~$P_i$, in such a way that, if a
-set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
-$\sum_i \mu(P_i) = 1$.   Meyer showed that one {\it can\/}
-assign definite values $0$ or~$1$ to the measurement outcome
-$\mu(P_i)$ when the Hilbert space is defined over the field of
-rational numbers, therefore nullifying the
-theorem~\citep{PhysRevLett.83.3751}.  However, Mermin then argued
-that measurement outcomes must depend smoothly on slight changes in
-the experimental configuration, leading him to assert that the
-impact of Meyer's negative result is
-``unsupportable''~\citep{Mermin1999}.  The debate on
-whether contextuality is consistent with experimental
-outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of
+a theory that is contextual depends upon whether compatible sets of
+observables are measured together or separately; a non-contextual
+theory gives the same results in either case.  A classic example of
+the varying opinions on the impact of imprecision is the disagreement
+between Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999}
+on whether finite-precision measurements invalidate the spirit of the
+Kochen-Specker
+theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.
+The Kochen-Specker theorem is in essence a mathematical statement
+about contextuality, asserting that in a Hilbert space of dimension
+$d \ge 3$, it is impossible to associate definite probabilities,
+$\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
+way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
+$\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
+definite probabilities $0$ or~$1$ to the measurement outcomes when the
+Hilbert space is defined over the field of rational numbers, therefore
+nullifying the theorem~\citep{PhysRevLett.83.3751}.  However, Mermin
+then argued that measurement outcomes must depend smoothly on slight
+changes in the experimental configuration, leading him to assert that
+the impact of Meyer's negative result is
+``unsupportable''~\citep{Mermin1999}.  The debate on whether
+contextuality is consistent with experimental outcomes continues to be
+an active topic of
+research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
@@
 \emph{non-contextuality}; that is, suddenly a quantum system can be
-simulated by a non-contextual hidden variable theory, turning the
-system effectively from a quantum system into a classical system. 
+simulated by a non-contextual hidden variable theory.
+%% , turning the
+%% system effectively from a quantum system into a classical system. 
 % that is, quantum mechanics suddenly fails to hold, and all variables
@@
 % }
-\yutsung{Still not comfortable about the current statement...}
+%% \yutsung{Still not comfortable about the current statement...}
 These results provide a new insight into the Meyer-Mermin debate by
@@
 
-We also investigate, though with less insight-generating results, the
-second key aspect of imprecise quantum measurement, which is its
-statistical nature as reflected in the application of the Born rule
-determining the probability of a given measurement
-outcome~\citep{Born1983,peres1995quantum,544199}.  Here, Gleason's
-theorem establishes that there is no alternative to the Born rule by
-demonstrating, using reasonable continuity arguments in Hilbert spaces
-of dimension $d\ge3$, the existence of a unique state $\rho$
-consistent with the statistical predictions computed from that
+We also investigate the second key aspect of imprecise quantum
+measurement, which is its statistical nature as reflected in the
+application of the Born rule determining the probability of a given
+measurement outcome~\citep{Born1983,peres1995quantum,544199}.  Here,
+Gleason's theorem establishes that there is no alternative to the Born
+rule by demonstrating, using reasonable continuity arguments in
+Hilbert spaces of dimension $d\ge3$, the existence of a unique state
+$\rho$ consistent with the statistical predictions computed from that
 rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  Our
@@
 in which one recovers the original Gleason theorem asymptotically.
-Specifically, if a set of QIVPMs representing bounded resources
-correspond individually to at least one state's~$\rho'$, those states
-will converge to a unique state $\rho$ in the limit as the size of the intervals
-characterizing the uncertainties goes to zero, and the set of
-single-point QIVPMs densely covers the entire real interval $[0,1]$ or the
-appropriate subset corresponding to a given quantum system.
+Specifically, it is possible to construct a class of QIVPMs
+representing bounded resources that is parameterized by the size of
+the probability intervals of uncertainty. We then demonstrate that all
+QIVPMs in this class are consistent with a non-empty set of quantum
+states, and as the size of the intervals characterizing the
+uncertainties goes to zero, this set of quantum states converges to
+the unique state consistent with the Born rule. We furthermore
+establish a mathematical correlation between the sizes of the
+intervals and the volume of states that are all consistent with an
+imprecise measurement.
 
@@
 the event~$E$ and~$1-r$ corresponds to the strength of evidence
-against the same event. More generally, this inverval would be interpreted as
+against the same event. More generally, this interval would be interpreted as
 the Gaussian width of a probability distribution, but for notational
@@
 \yutsung{Check the interpretation in the statistics literature~\citep{HuberRonchetti2009}!
-Or we may need to prove it could be interpreted as Guassian width
+Or we may need to prove it could be interpreted as Gaussian width
 by ourselves...} The collection of intervals used in the
@@
 \begin{aligned}\mathscr{I}_{2}={} & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\\
- & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{1}{4},1\right],\necess\right\} \,.
+ & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{3}{4},1\right],\necess\right\} \,.
 \end{aligned}

### 2017-10-26 prop_letter.tex
sec 2 and 3

@@
 the event~$E$ and~$1-r$ corresponds to the strength of evidence
-against the same event. More generally, this interval would be interpreted as
-the Gaussian width of a probability distribution, but for notational
-convenience we will continue in the following to write this as a definite interval.
-\yutsung{Check the interpretation in the statistics literature~\citep{HuberRonchetti2009}!
-Or we may need to prove it could be interpreted as Gaussian width
-by ourselves...} The collection of intervals used in the
-definition of a probability measure must satisfy certain properties
-that we explain next.
+against the same event. Under some additional assumptions, this
+interval could be interpreted as the Gaussian width of a probability
+distribution. We use general intervals with no constraints other than
+the ones needed to maintain coherence: these are described next.
 
@@
 $\mu(E \cup \overline{E})$ to always be $\necess$ irrespective of the
-particular assignments of $\mu(E)$ or~$\mu(\overline{E})$. Parallel arguments
-can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
-essential new information seems to be introduced.
+particular assignments of $\mu(E)$ or~$\mu(\overline{E})$. 
+%% Parallel arguments
+%% can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
+%% essential new information seems to be introduced.
 
@@
 We now have the necessary ingredients to define the quantum extension,
-QIVPMs, as a generalization of both classical IVPMs and quantum
-probability measures. We will show that QIVPMs reduce to classical
-IVPMs when the space of quantum events is restricted to mutually
-commuting events, i.e., to compatible events that can be measured
-simultaneously. In Sec.~\ref{sec:Gleason} we will discuss the
+QIVPMs, as a generalization of both classical IVPMs and conventional
+quantum probability measures. We will show that QIVPMs reduce to
+classical IVPMs when the space of quantum events is restricted to
+mutually commuting events, i.e., to compatible events that can be
+measured simultaneously. In Sec.~\ref{sec:Gleason} we will discuss the
 connection between QIVPMs and conventional quantum probability
-measures.
+measures in detail.
 
@@
 \end{equation}
-If we identify the states ~$\proj{0}$ and $\proj{1}$ with the head
-and the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents
-the situation in which an experimenter knows nothing about a coin
-before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
-state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
-coin with probability~$p$ to get heads, and
-$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with
-$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin should be
-consistent with the situation for which an experimenter has no prior
-knowledge.
+If we identify the states ~$\proj{0}$ and $\proj{1}$ with the head and
+the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents the
+situation in which an experimenter knows nothing about a coin before
+she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
+state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical coin
+with probability~$p$ to get heads, and
+$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent
+with~$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin
+should be consistent with the situation for which an experimenter has
+no prior knowledge.
 
@@
 to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
-themselves lie between the minimum and maximum bounds of the probability
-intervals associated with each state~$\rho$ that is consistent with
-$\bar{\mu}$ on every projector in the spectral decomposition of the
-observable. If $\bar{\mu}$ is a conventional (Born) probability measure
-induced by a state $\rho$, then the Born rule probability induced
-by every state in $\coreBorn\left(\bar{\mu},\events'\right)$ will
-be $\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point,
-thus reducing the definition to that of Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
-For example, we can extend one of the fragments of valid probability
-measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
-to a QIVPM~$\bar{\mu}_{3}$:
-\begin{equation}
-\begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
-\bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
-\end{aligned}
-\label{eq:Born-QIVPM}
-\end{equation}
-For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
-the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
-$\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
-Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
-which is an interval, but not between $0$ and $1$ because it is
-not a probability of an event. We also note that, when restricted
-to commuting projectors, the definition above is consistent with the
-classical notion of the \emph{Choquet integral}~\citep{GilboaSchmeidler1994,Grabisch2016}
+themselves lie between the minimum and maximum bounds of the
+probability intervals associated with each state~$\rho$ that is
+consistent with~$\bar{\mu}$ on every projector in the spectral
+decomposition of the observable. If $\bar{\mu}$ is a conventional
+(Born) probability measure induced by a state $\rho$, then the Born
+rule probability induced by every state in
+$\coreBorn\left(\bar{\mu},\events'\right)$ will be
+$\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point, thus
+reducing the definition to that of
+Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
+% For example, we can extend one of the fragments of valid probability
+% measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
+% to a QIVPM~$\bar{\mu}_{3}$:
+% \begin{equation}
+% \begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
+% \bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
+% \end{aligned}
+% \label{eq:Born-QIVPM}
+% \end{equation}
+% For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
+% the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
+% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
+% Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
+% which is an interval, but not between $0$ and $1$ because it is
+% not a probability of an event. 
+We also note that, when restricted to commuting projectors, the
+definition above is consistent with the classical notion of the
+\emph{Choquet integral}~\citep{GilboaSchmeidler1994,Grabisch2016}
 which is used to calculate the expectation value of random variables

### 2017-10-26 prop_letter.tex
sec 4

@@
 A principal result is that recasting the Kochen-Specker theorem in
-terms of ``$\delta$-determinism'', with~$\delta$ quantifying the
+terms of ``$\delta$-determinism,'' with~$\delta$ quantifying the
 effect of finite-precision uncertainties on measurement outcomes,
@@
 
-\noindent The definition puts no restrictions on the choice of intervals,
-only on the assignment of intervals to events. When $\delta=0$, every
-event must be assigned a probability either in the interval $\imposs$
-or in $\necess$, i.e., every event is completely determined with
-certainty. As $\delta$ gets larger, the QIVPM allows for more indeterminate
-behavior. To illustrate the examples easier, we restrict ourselves
-to the classical subspace of commuting events~$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
-If we apply the same definition in the classical case, the classical
-IVPM~$\bar{\mu}_{4}$ defined in Table~\ref{tab:classical-IVPMs}
-is $0$-deterministic because $\imposs\subseteq\left[0,0\right]$
-and $\necess\subseteq\left[1-0,1\right]$.
 \begin{table}
-\noindent \centering{}\caption{\label{tab:classical-IVPMs}Classical IVPMs~$\bar{\mu}_{4}$, $\bar{\mu}_{5}$
-and $\bar{\mu}_{6}$ on $\events_{0}$.}
+  \noindent \centering{}\caption{\label{tab:classical-IVPMs}Example 
+    IVPMs~$\bar{\mu}_{4}$, $\bar{\mu}_{5}$ and $\bar{\mu}_{6}$.}
 \begin{tabular}{cccc}
@@
 \end{table}
-By interpreting the states ~$\proj{0}$ and $\proj{1}$ with the
-head and the tail of a coin again, $\bar{\mu}_{4}$ represents tossing
-a double-headed coin which can be predicted with certain. When $\delta$
-is increased to $\frac{1}{3}$, the classical IVPMs~$\bar{\mu}_{5}$
-and $\bar{\mu}_{6}$ defined in Table~\ref{tab:classical-IVPMs}
-are clearly $\frac{1}{3}$-deterministic, and they have more indeterminate
-behavior than $\bar{\mu}_{4}$. However, the most indeterminate classical
-IVPM~$\bar{\mu}_{2}$ defined in Eq.~(\ref{eq:classical-no-information-IVPM})
-is still not $\frac{1}{3}$-deterministic because $\bar{\mu}_{2}(\proj{0})=\bar{\mu}_{2}(\proj{1})=\unknown$,
-but neither $\unknown\subseteq\left[0,\frac{1}{3}\right]$ nor $\unknown\subseteq\left[1-\frac{1}{3},1\right]$.
-Finally, when $\delta=1$, because every interval is a subset of $\unknown$,
-every QIVPM is $1$-deterministic. In particular, the non-informative
-QIVPM~$\bar{\mu}_{1}$ defined in Eq.~(\ref{eq:no-information-IVPM})
-and the Born QIVPM~$\bar{\mu}_{3}$ defined in Eq.~(\ref{eq:Born-QIVPM})
-are both $1$-deterministic.
+
+\noindent The definition puts no restrictions on the set of intervals
+itself, only on which intervals are assigned to events. When
+$\delta=0$, every event must be assigned a probability either in the
+interval $\imposs$ or in $\necess$, i.e., every event is completely
+determined with certainty. As $\delta$ gets larger, the QIVPM allows
+for more indeterminate behavior. For example, the IVPM~$\bar{\mu}_{4}$
+defined in Table~\ref{tab:classical-IVPMs} is $0$-deterministic
+because $\imposs\subseteq\left[0,0\right]$ and
+$\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
+~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
+$\bar{\mu}_{4}$ represents tossing a double-headed coin. When $\delta$
+is increased to $\frac{1}{3}$, both the IVPMs~$\bar{\mu}_{5}$ and
+$\bar{\mu}_{6}$ become $\frac{1}{3}$-deterministic. In contrast, the
+IVPM~$\bar{\mu}_{2}$ defined in
+Eq.~(\ref{eq:classical-no-information-IVPM}) is still not
+$\frac{1}{3}$-deterministic because
+$\bar{\mu}_{2}(\proj{0})=\bar{\mu}_{2}(\proj{1})=\unknown$, but
+neither $\unknown\subseteq\left[0,\frac{1}{3}\right]$ nor
+$\unknown\subseteq\left[1-\frac{1}{3},1\right]$.  Finally, when
+$\delta=1$, because every interval is a subset of $\unknown$, every
+QIVPM is $1$-deterministic. In particular, the non-informative
+QIVPM~$\bar{\mu}_{1}$ defined in Eq.~(\ref{eq:no-information-IVPM}) is
+1-deterministic. 
+%% and the Born QIVPM~$\bar{\mu}_{3}$ defined in
+%% Eq.~(\ref{eq:Born-QIVPM}) are both $1$-deterministic.
 
@@
 
-We can now proceed with our technical result, which is that the
-original Kochen-Specker theorem is a statement regarding the
-non-existence of $0$-deterministic QIVPM.
+We can now proceed with the main technical result of this section. We
+start with a remark that the original Kochen-Specker theorem is a
+statement regarding the non-existence of $0$-deterministic QIVPM and
+generalize to $\delta$-deterministic QIVPMs.
 
@@
 contradiction as the original Kochen-Specker theorem. Instead of
-adapting the more complicated proof for $d=3$, our counterexample uses
-the simpler proof for a Hilbert space of dimension $d=4$ and is
-constructed as follows.
+adapting the more complicated proof for $d=3$, the counterexample
+presented below uses the simpler proof for a Hilbert space of
+dimension $d=4$ and is constructed as follows.
 
@@
 $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$. Now
-assume a 0-deterministic QIVPM ${\bar{\mu}}$; the expectation values
+assume a 0-deterministic QIVPM~${\bar{\mu}}$; the expectation values
 of the observables in each row relative to this 0-deterministic QIVPM
@@
 contradiction implies the non-existence of the assumed 0-deterministic
-QIVPM. We therefore prove a stronger statement of contextuality that
-includes the effects of finite-precision.
+QIVPM. 
+%% We therefore prove a stronger statement of contextuality that 
+%% includes the effects of finite-precision.
 
@@
 $\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. We claim that the
-following
-map~$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
-  \imposs,\necess\right\} $ is a 0-deterministic QIVPM:
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. We will use this
+assumed QIVPM to construct the following 0-deterministic QIVPM
+$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
+  \imposs,\necess\right\}$:
 \begin{equation}
@@
 map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ does
-not exist.
-
-It remains to verify that $\bar{\mu}^{\textrm{D}}$ is indeed a
-0-deterministic QIVPM by checking~\citep{HOSTunpublished} that for orthogonal
+not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$ is
+indeed a 0-deterministic QIVPM by checking that for orthogonal
 operators~$P_{0}$ and $P_{1}$, we have that

### 2017-10-26 prop_letter.tex
sec 5

@@
 \lineskiplimit=1pt
-\newcommand{\ultramodular}{\ensuremath{f}}
+\newcommand{\ultramodular}{\mathcal{M}}
 \newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{\mathrm{L{#1}}}}}
@@
 A conventional quantum probability measure can be easily constructed
-from a state according to the Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
-This state is also the unique state consistent with the constructed
-probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}
-which can be reformulated in QIVPMs using infinitely precise intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:
+from a state according to the Born
+rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.  According
+to Gleason's
+theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}, this
+state is also the unique state consistent with any possible
+probability measure. In order to re-examine these results in our
+framework, we first reformulate Gleason's theorem in QIVPMs using
+infinitely precise
+intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:
 
@@
 
-\noindent For general QIVPMs mapping to finitely precise intervals,
-we also want to seek a simple rule to construct them, and to understand
-which states are consistent with them. However, if measurement intervals
-are too imprecise and QIVPMs are defined so wildly, the results we
-get might contradict to each other. These contradicting results would
-exclude any possible state from being consistent with the given QIVPM.
+\noindent For general QIVPMs mapping to finitely precise intervals, we
+also want to seek a simple rule to construct them, and to understand
+which states are consistent with them. However, if measurement
+intervals are too imprecise, the state consistent with the results of
+measurements on some projectors might contradict the state induced by
+some other projectors. Indeed we can formally prove that, in general,
+there may be \emph{no} state consistent with some arbitrary QIVPM.
 
@@
 To prove the theorem, we first need to construct a QIVPM, and then
-verify that no states consistent with it on all projectors. Given
-an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2},\ldots,\ket{d-1}\right\} $,
-let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
-and
+verify that there are no states that are consistent with it on all
+projectors. Given an orthonormal basis
+$\left\{ \ket{0},\ket{1},\ket{2},\ldots,\ket{d-1}\right\} $, let
+$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
+$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
 \begin{equation}
@@
 \end{equation}
-The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
-in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished}.
+The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined in
+Table~\ref{tab:non-Born-QIVPM} can be verified as a
+QIVPM~\citep{HOSTunpublished}.
 \begin{table}
@@
 which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all $j$. The last equation never holds proving the theorem.
-
-To address this problem, we are going to introduce a simple rule which
-can induce well-behaved QIVPMs by quantum probability measures systematically.
-When we generalized quantum probability measures to QIVPMs, we changed
-the range from the unit interval $\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
-This replacement suggests to find a function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
-to replace a real-valued probability $\mu\left(P\right)$ by an interval-valued
-one $\ultramodular\left(\mu\left(P\right)\right)$. In other words,
-compositing $\ultramodular$ with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
-produces a function $\ultramodular\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\ultramodular}{\rightarrow}\mathscr{I}$
-with the same domain and range as a QIVPM. In order to guarantee $\ultramodular\circ\mu$
-always a QIVPM, we consider the following homomorphism-like properties
-for~$\ultramodular$.
+for all~$j$. The last equation never holds proving the theorem.
+
+The fact that a collection of poor measurements on a quantum system
+cannot reveal the underlying state is not surprising. Under certain
+conditions, we can however guarantee that the uncertainty in
+measurements is consistent with \emph{some} non-empty collection of
+quantum states. Furthermore, we can relate the uncertainty in
+measurements to the volume of quantum states such that, in the limit
+of infinitely precise measurements, the volume of states collapses to
+a single point corresponding to a single state.
+
+To that end, we construct a family of QIVPMs parameterized by a
+functions $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ that
+formalize how the real-valued probabilities are mapped to
+intervals. These functions, are called \emph{ultramodular}, when they
+satisfy certain properties defined next.
 
@@
 $\necess$, a function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
-is called a ultramodular function if $\ultramodular$ is subject to
-the following constraints:\begin{subequations}\label{eq:iota-constraints}
+is called a ultramodular function if:
+\begin{subequations}\label{eq:iota-constraints}
 \begin{eqnarray}
@@
 \end{eqnarray}
-\end{subequations}and satisfies that for any three numbers~$x_{0}$,
-$x_{1}$, and $x_{2}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
-implies
+\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$, and
+$x_{2}\in\left[0,1\right]$ such that
+$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have:
 \begin{equation}
@@
 
-\noindent The first three constraints, Eqs.~(\ref{eq:iota-constraints}),
-are the direct counterpart of the corresponding QIVPM constraints,
-Eqs.~(\ref{eq:QIVPM-constraints}); the last condition, Eq.~(\ref{eq:iota-Inclusion}),
-is the direct counterpart of the convexity conditions, Eq.~(\ref{eq:classicalconvex})
-and (\ref{eq:QuantumInterval-valuedProbability-Inclusion}). Therefore
-the composited function~$\ultramodular\circ\mu$ satisfies the constraints
-for IVPMs naturally no matter in classical or quantum case. Conversely,
-if $\ultramodular\circ\mu$ is always a IVPM, then the function~$\ultramodular$
-is ultramodular. In other words, $\ultramodular$ is ultramodular
-is a necessary and sufficient condition for $\ultramodular\circ\mu$
-is always a IVPM as we next show.
-
-\begin{thm}[Equivalence among Ultramodular Functions and IVPMs]\label{thm:iota-statements}The
+\noindent The first three constraints,
+Eqs.~(\ref{eq:iota-constraints}), are the direct counterpart of the
+corresponding QIVPM constraints, Eqs.~(\ref{eq:QIVPM-constraints});
+the last condition, Eq.~(\ref{eq:iota-Inclusion}), is the direct
+counterpart of the convexity conditions,
+Eq.~(\ref{eq:classicalconvex}) and
+(\ref{eq:QuantumInterval-valuedProbability-Inclusion}). Therefore,
+these conditions guarantee that, for any conventional quantum
+probability measure $\mu$, the composition $\ultramodular \circ \mu$,
+defines a valid QIVPM. Conversely, it is the case that if
+$f \circ \mu$ is a QIVPM for some function $f$ then $f$ is an
+ultramodular function. Formally, we have the following result.
+
+% the composited function~$\ultramodular\circ\mu$ satisfies the constraints
+% for IVPMs naturally no matter in classical or quantum case. Conversely,
+% if $\ultramodular\circ\mu$ is always a IVPM, then the function~$\ultramodular$
+% is ultramodular. In other words, $\ultramodular$ is ultramodular
+% is a necessary and sufficient condition for $\ultramodular\circ\mu$
+% is always a IVPM as we next show.
+
+% When we generalized quantum probability measures to QIVPMs, we changed
+% the range from the unit interval $\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
+% This replacement suggests to find a function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
+% to replace a real-valued probability $\mu\left(P\right)$ by an interval-valued 
+% one $\ultramodular\left(\mu\left(P\right)\right)$. In other words,
+% compositing $\ultramodular$ with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+% produces a function $\ultramodular\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\ultramodular}{\rightarrow}\mathscr{I}$
+% with the same domain and range as a QIVPM. In order to guarantee $\ultramodular\circ\mu$
+% always a QIVPM, we consider the following homomorphism-like properties
+% for~$\ultramodular$.
+
+\begin{thm}[Equivalence of Ultramodular Functions and IVPMs]\label{thm:iota-statements}The
 following three statements are equivalent:
@@
 is ultramodular.
-\item \label{enu:iota-mu-CIVPM}The composited function~$\ultramodular\circ\mu:\events_{\mathrm{C}}\rightarrow\mathscr{I}$
-is always a classical IVPM for any classical probability measure~$\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$.
-\item \label{enu:iota-mu-QIVPM}The composited function~$\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$
-is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
-on any Hilbert space~$\Hilb$.
+\item \label{enu:iota-mu-CIVPM}The composite
+  function~$\ultramodular\circ\mu:\events_{\mathrm{C}}\rightarrow\mathscr{I}$
+  is a classical IVPM for any classical probability
+  measure~$\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$.
+\item \label{enu:iota-mu-QIVPM}The composite
+  function~$\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$ is a
+  QIVPM for any quantum probability
+  measure~$\mu:\events\rightarrow\left[0,1\right]$ on any Hilbert
+  space~$\Hilb$.
 \end{enumerate}
@@
 The equivalence between Statement~\ref{enu:iota-subject-to} and
-\ref{enu:iota-mu-CIVPM} is a well-known classical result~\citep{Choquet1954,NgMoYeh1997,Marinacci_2004}.
-For quantum case, Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-QIVPM}
-as we have discussed. The rest of the proof is to show that if $\ultramodular$
-is not ultramodular, then $\ultramodular\circ\mu$ might not be a
-QIVPM. Suppose there are three particular numbers~$x_{0}$, $x_{1}$,
-and $x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
-but they don't satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the
-state 
+\ref{enu:iota-mu-CIVPM} is a well-known classical
+result~\citep{Choquet1954,NgMoYeh1997,Marinacci_2004}.  For the
+quantum case, Statement~\ref{enu:iota-subject-to} implies
+\ref{enu:iota-mu-QIVPM} as we have outlined above. The rest of the
+proof is to show that if $\ultramodular$ is not ultramodular, then
+$\ultramodular\circ\mu$ might not be a QIVPM. Suppose there are three
+particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but they don't
+satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the state:
 \begin{equation}
@@
 \end{equation}
-Its inducing function $\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
-fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$ so
-that $\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ cannot
-be a QIVPM. Therefore, $\ultramodular$ is ultramodular if and only
-if $\ultramodular\circ\mu$ is always a QIVPM.
+The induced map using the Born rule and approximated by
+$\ultramodular$, $\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
+fails to satisfy
+Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
+$P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. In other
+words, this induced map fails to be a QIVPM.
 
 In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-there is always a state consistent with any composited QIVPM $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$.
-Moreover, the collection of states consistent with $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$
-gets closer and closer to $\rho$ as the intervals get narrower and
-narrower. Eventually, the collection of consisting states collapses
-to the singleton set~$\left\{ \rho\right\} $ as the intervals become
-the infinitely precise intervals~$\mathscr{I}_{\infty}$. This fact
-is a weak version of Gleason's theorem because we only consider composited
-QIVPMs $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$ instead of general
-QIVPMs~$\bar{\mu}$. To precisely state this result, we need to introduce
-the norm of pure states and operators. The norm of a pure state~$\ket{\psi}$
-is defined as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
-Similarly, given any Hermitian operator~$A$, we consider the usual
-operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
-which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
-Then, a weak version of Gleason's theorem can be stated as follow.
-
-\begin{thm}[Finite-Precision Extension of Weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
-an interval-valued function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
-with the maximum length of intervals~$m$. Given any state~$\rho$,
-if a state $\rho'\in\coreBorn\left(\ultramodular\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-then the norm of their difference $\left\Vert \rho-\rho'\right\Vert \le m$.\end{thm}
+there is always a state consistent with any composite QIVPM
+$\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$.  Moreover, the collection
+of states consistent with $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$
+gets closer and closer to~$\rho$ as the intervals get narrower and
+narrower. Eventually, the collection of states collapses to the
+singleton set~$\left\{ \rho\right\} $ as the intervals become the
+infinitely precise intervals~$\mathscr{I}_{\infty}$. To precisely
+state this result, we introduce the norm of pure states and
+operators. The norm of a pure state~$\ket{\psi}$ is defined as usual
+$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
+given any Hermitian operator~$A$, we consider the usual operator norm
+$\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert
+  =1}\left\Vert A\ket{\psi}\right\Vert $, which is also known as the
+$2$-norm or the spectral
+norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+Then, a version of Gleason's theorem can be stated as follow.
+
+\begin{thm}[Finite-Precision Extension of Gleason's
+  theorem]\label{thm:Finite-precision-Gleason}Consider
+  an ultramodular function
+  $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ and let $m$
+  be the maximum length of intervals in its image. Given any
+  state~$\rho$, if a state
+  $\rho'\in\coreBorn\left(\ultramodular\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+  then the norm of their difference is bounded by $m$, i.e.,
+  $\left\Vert \rho-\rho'\right\Vert \le m$.\end{thm}
 
@@
 length of the intervals in $\mathscr{I}$ is $m$, it is also the
-upper bound of the difference 
+upper bound of the difference:
 \[
@@
 Hence, $\left\Vert \rho-\rho'\right\Vert \le m$.
+
+The previous theorem generalizes Gleason's theorem in the sense that
+it accounts for a larger class of probability measures which includes
+the conventional one as a limit. The theorem is however ``weak'' in
+the sense that it only applies to the particular class of QIVPMs
+constructed by composing an ultramodular function with a conventional
+quantum probability measure.
+
+\amr{***WAVEFRONT***}
 

### 2017-10-26 prop_letter.tex
Updates from ShareLaTeX

--- 2017-10-26 prop_letter.tex
@@
 mechanics regarding the tension between finite precision measurement
-and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of
-a theory that is contextual depends upon whether compatible sets of
-observables are measured together or separately; a non-contextual
-theory gives the same results in either case.  A classic example of
-the varying opinions on the impact of imprecision is the disagreement
-between Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999}
-on whether finite-precision measurements invalidate the spirit of the
-Kochen-Specker
-theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.
-The Kochen-Specker theorem is in essence a mathematical statement
-about contextuality, asserting that in a Hilbert space of dimension
-$d \ge 3$, it is impossible to associate definite probabilities,
-$\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
-way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
-$\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
-definite probabilities $0$ or~$1$ to the measurement outcomes when the
-Hilbert space is defined over the field of rational numbers, therefore
-nullifying the theorem~\citep{PhysRevLett.83.3751}.  However, Mermin
-then argued that measurement outcomes must depend smoothly on slight
-changes in the experimental configuration, leading him to assert that
-the impact of Meyer's negative result is
-``unsupportable''~\citep{Mermin1999}.  The debate on whether
-contextuality is consistent with experimental outcomes continues to be
-an active topic of
-research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome
+of a theory that is contextual depends upon
+whether  compatible sets of observables are measured together or
+separately; a non-contextual theory gives the same results in either
+case.  A classic example of the varying opinions on the impact of
+imprecision is the disagreement between
+Meyer~\cite{PhysRevLett.83.3751} and 
+Mermin~\cite{Mermin1999}  on whether finite-precision
+measurements invalidate the spirit of the Kochen-Specker
+theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.  The Kochen-Specker  
+theorem is in essence a
+mathematical statement about contextuality, asserting that
+in a Hilbert space of dimension $d \ge 3$, it is
+impossible to associate definite measured values, $\mu(P_i)= 0$ or
+$1$, with every projection operator~$P_i$, in such a way that, if a
+set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
+$\sum_i \mu(P_i) = 1$.   Meyer showed that one {\it can\/}
+assign definite values $0$ or~$1$ to the measurement outcome
+$\mu(P_i)$ when the Hilbert space is defined over the field of
+rational numbers, therefore nullifying the
+theorem~\citep{PhysRevLett.83.3751}.  However, Mermin then argued
+that measurement outcomes must depend smoothly on slight changes in
+the experimental configuration, leading him to assert that the
+impact of Meyer's negative result is
+``unsupportable'' on physical grounds ~\citep{Mermin1999}.  The debate on
+whether contextuality is consistent with experimental
+outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
@@
 \emph{non-contextuality}; that is, suddenly a quantum system can be
-simulated by a non-contextual hidden variable theory.
-%% , turning the
-%% system effectively from a quantum system into a classical system. 
+simulated by a non-contextual hidden variable theory, turning the
+system effectively from a quantum system into a classical system. 
 % that is, quantum mechanics suddenly fails to hold, and all variables
@@
 % }
-%% \yutsung{Still not comfortable about the current statement...}
+\yutsung{Still not comfortable about the current statement...}
 These results provide a new insight into the Meyer-Mermin debate by
@@
 
-We also investigate the second key aspect of imprecise quantum
-measurement, which is its statistical nature as reflected in the
-application of the Born rule determining the probability of a given
-measurement outcome~\citep{Born1983,peres1995quantum,544199}.  Here,
-Gleason's theorem establishes that there is no alternative to the Born
-rule by demonstrating, using reasonable continuity arguments in
-Hilbert spaces of dimension $d\ge3$, the existence of a unique state
-$\rho$ consistent with the statistical predictions computed from that
+We also investigate, though with less insight-generating results, the
+second key aspect of imprecise quantum measurement, which is its
+statistical nature as reflected in the application of the Born rule
+determining the probability of a given measurement
+outcome~\citep{Born1983,peres1995quantum,544199}.  Here, Gleason's
+theorem establishes that there is no alternative to the Born rule by
+demonstrating, using reasonable continuity arguments in Hilbert spaces
+of dimension $d\ge3$, the existence of a unique state $\rho$
+consistent with the statistical predictions computed from that
 rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  Our
@@
 in which one recovers the original Gleason theorem asymptotically.
-Specifically, it is possible to construct a class of QIVPMs
-representing bounded resources that is parameterized by the size of
-the probability intervals of uncertainty. We then demonstrate that all
-QIVPMs in this class are consistent with a non-empty set of quantum
-states, and as the size of the intervals characterizing the
-uncertainties goes to zero, this set of quantum states converges to
-the unique state consistent with the Born rule. We furthermore
-establish a mathematical correlation between the sizes of the
-intervals and the volume of states that are all consistent with an
-imprecise measurement.
+Specifically, if a set of QIVPMs representing bounded resources
+correspond individually to at least one state's~$\rho'$, those states
+will converge to a unique state $\rho$ in the limit as the size of the intervals
+characterizing the uncertainties goes to zero, and the set of
+single-point QIVPMs densely covers the entire real interval $[0,1]$ or the
+appropriate subset corresponding to a given quantum system.
 
@@
 the event~$E$ and~$1-r$ corresponds to the strength of evidence
-against the same event. Under some additional assumptions, this
-interval could be interpreted as the Gaussian width of a probability
-distribution. We use general intervals with no constraints other than
-the ones needed to maintain coherence: these are described next.
+against the same event. More generally, this inverval would be interpreted as
+the Gaussian width of a probability distribution, but for notational
+convenience we will continue in the following to write this as a definite interval.
+\yutsung{Check the interpretation in the statistics literature~\citep{HuberRonchetti2009}!
+Or we may need to prove it could be interpreted as Guassian width
+by ourselves...} The collection of intervals used in the
+definition of a probability measure must satisfy certain properties
+that we explain next.
 
@@
 $\mu(E \cup \overline{E})$ to always be $\necess$ irrespective of the
-particular assignments of $\mu(E)$ or~$\mu(\overline{E})$. 
-%% Parallel arguments
-%% can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
-%% essential new information seems to be introduced.
+particular assignments of $\mu(E)$ or~$\mu(\overline{E})$. Parallel arguments
+can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
+essential new information seems to be introduced.
 
@@
 We now have the necessary ingredients to define the quantum extension,
-QIVPMs, as a generalization of both classical IVPMs and conventional
-quantum probability measures. We will show that QIVPMs reduce to
-classical IVPMs when the space of quantum events is restricted to
-mutually commuting events, i.e., to compatible events that can be
-measured simultaneously. In Sec.~\ref{sec:Gleason} we will discuss the
+QIVPMs, as a generalization of both classical IVPMs and quantum
+probability measures. We will show that QIVPMs reduce to classical
+IVPMs when the space of quantum events is restricted to mutually
+commuting events, i.e., to compatible events that can be measured
+simultaneously. In Sec.~\ref{sec:Gleason} we will discuss the
 connection between QIVPMs and conventional quantum probability
-measures in detail.
+measures.
 
@@
 \end{equation}
-If we identify the states ~$\proj{0}$ and $\proj{1}$ with the head and
-the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents the
-situation in which an experimenter knows nothing about a coin before
-she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
-state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical coin
-with probability~$p$ to get heads, and
-$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent
-with~$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin
-should be consistent with the situation for which an experimenter has
-no prior knowledge.
+If we identify the states ~$\proj{0}$ and $\proj{1}$ with the head
+and the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents
+the situation in which an experimenter knows nothing about a coin
+before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
+state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
+coin with probability~$p$ to get heads, and
+$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with
+$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin should be
+consistent with the situation for which an experimenter has no prior
+knowledge.
 
@@
 to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
-themselves lie between the minimum and maximum bounds of the
-probability intervals associated with each state~$\rho$ that is
-consistent with~$\bar{\mu}$ on every projector in the spectral
-decomposition of the observable. If $\bar{\mu}$ is a conventional
-(Born) probability measure induced by a state $\rho$, then the Born
-rule probability induced by every state in
-$\coreBorn\left(\bar{\mu},\events'\right)$ will be
-$\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point, thus
-reducing the definition to that of
-Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
-% For example, we can extend one of the fragments of valid probability
-% measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
-% to a QIVPM~$\bar{\mu}_{3}$:
-% \begin{equation}
-% \begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
-% \bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
-% \end{aligned}
-% \label{eq:Born-QIVPM}
-% \end{equation}
-% For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
-% the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
-% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
-% Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
-% which is an interval, but not between $0$ and $1$ because it is
-% not a probability of an event. 
-We also note that, when restricted to commuting projectors, the
-definition above is consistent with the classical notion of the
-\emph{Choquet integral}~\citep{GilboaSchmeidler1994,Grabisch2016}
+themselves lie between the minimum and maximum bounds of the probability
+intervals associated with each state~$\rho$ that is consistent with
+$\bar{\mu}$ on every projector in the spectral decomposition of the
+observable. If $\bar{\mu}$ is a conventional (Born) probability measure
+induced by a state $\rho$, then the Born rule probability induced
+by every state in $\coreBorn\left(\bar{\mu},\events'\right)$ will
+be $\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point,
+thus reducing the definition to that of Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
+For example, we can extend one of the fragments of valid probability
+measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
+to a QIVPM~$\bar{\mu}_{3}$:
+\begin{equation}
+\begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
+\bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
+\end{aligned}
+\label{eq:Born-QIVPM}
+\end{equation}
+For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
+the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
+$\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
+Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
+which is an interval, but not between $0$ and $1$ because it is
+not a probability of an event. We also note that, when restricted
+to commuting projectors, the definition above is consistent with the
+classical notion of the \emph{Choquet integral}~\citep{GilboaSchmeidler1994,Grabisch2016}
 which is used to calculate the expectation value of random variables

### 2017-10-26 prop_letter.tex

--- 2017-10-26 prop_letter.tex
@@
 the impact of Meyer's negative result is
-``unsupportable''~\citep{Mermin1999}.  The debate on whether
+``unsupportable'' on physical grounds~\citep{Mermin1999}.  The debate on whether
 contextuality is consistent with experimental outcomes continues to be

### 2017-10-26 prop_letter.tex
revision

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{The Born rule and Gleason's Theorem}
@@
 
-\noindent For general QIVPMs mapping to finitely precise intervals, we
-also want to seek a simple rule to construct them, and to understand
-which states are consistent with them. However, if measurement
-intervals are too imprecise, the state consistent with the results of
-measurements on some projectors might contradict the state induced by
-some other projectors. Indeed we can formally prove that, in general,
-there may be \emph{no} state consistent with some arbitrary QIVPM.
+\noindent For general QIVPMs mapping to imprecise intervals, we also
+want to seek a simple rule to construct them, and to understand which
+states are consistent with them. However, if measurement intervals are
+too imprecise, the state consistent with the results of measurements
+on some projectors might contradict the state induced by some other
+projectors. Indeed we can formally prove that, in general, there may
+be \emph{no} state consistent with some arbitrary QIVPM.
 
@@
 
-To prove the theorem, we first need to construct a QIVPM, and then
-verify that there are no states that are consistent with it on all
+To prove the theorem, we just need to construct a QIVPM, and verify
+that there are no states that are consistent with it on all
 projectors. Given an orthonormal basis
@@
 
-To that end, we construct a family of QIVPMs parameterized by a
-functions $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ that
+To that end, we construct a family of QIVPMs parameterized by
+clustering functions $f:\left[0,1\right]\rightarrow\mathscr{I}$ that
 formalize how the real-valued probabilities are mapped to
-intervals. These functions, are called \emph{ultramodular}, when they
-satisfy certain properties defined next.
-
-\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
-a collection of intervals $\mathscr{I}$ including $\imposs$ and
-$\necess$, a function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
-is called a ultramodular function if:
-\begin{subequations}\label{eq:iota-constraints}
-\begin{eqnarray}
- &  & \ultramodular(0)=\imposs\,,\\
- &  & \ultramodular(1)=\necess\,,\\
- &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
-\end{eqnarray}
-\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$, and
-$x_{2}\in\left[0,1\right]$ such that
-$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have:
-\begin{equation}
-\ultramodular\left(x_{0}+x_{1}+x_{2}\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
-\end{equation}
-\end{definition}
-
-\noindent The first three constraints,
-Eqs.~(\ref{eq:iota-constraints}), are the direct counterpart of the
-corresponding QIVPM constraints, Eqs.~(\ref{eq:QIVPM-constraints});
-the last condition, Eq.~(\ref{eq:iota-Inclusion}), is the direct
-counterpart of the convexity conditions,
-Eq.~(\ref{eq:classicalconvex}) and
-(\ref{eq:QuantumInterval-valuedProbability-Inclusion}). Therefore,
-these conditions guarantee that, for any conventional quantum
-probability measure $\mu$, the composition $\ultramodular \circ \mu$,
-defines a valid QIVPM. Conversely, it is the case that if
-$f \circ \mu$ is a QIVPM for some function $f$ then $f$ is an
-ultramodular function. Formally, we have the following result.
+intervals. We also introduce a notion of norm that quantifies the
+distance between (pure or mixed) states.  The norm of a pure
+state~$\ket{\psi}$ is defined as usual
+$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
+given any Hermitian operator~$A$, we consider the usual operator norm
+$\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert
+  =1}\left\Vert A\ket{\psi}\right\Vert $, which is also known as the
+$2$-norm or the spectral
+norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+Then, a version of Gleason's theorem can be stated as follows.
 
@@
 
+\begin{thm}[Finite-Precision Extension of Gleason's
+  theorem]\label{thm:Finite-precision-Gleason}Let $f$ be a clustering
+  function and let $f \circ \mu_{\rho}^{\mathrm{B}}$ be a QIVPM, where
+  $\mu_{\rho}^{\mathrm{B}}$ is the probability measure induced by the
+  Born rule for a given state $\rho$. Let $\alpha$ be the maximum
+  length of intervals in its image. If a state $\rho'$ is consistent
+  with $f\circ\mu_{\rho}^{\mathrm{B}}$ on all events, i.e.,
+  $\rho'\in\coreBorn\left(f\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+  then the norm of their difference is bounded by $\alpha$, i.e.,
+  $\left\Vert \rho-\rho'\right\Vert \le \alpha$.\end{thm}
+
+The proof proceeds as follows. Given a state~$\rho'$ consistent with
+$f\circ\mu_{\rho}^{\mathrm{B}}$, we have
+$\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in
+f\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$ for any
+one-dimensional projector $\proj{\psi}$. Since the maximum length of
+the intervals in $\mathscr{I}$ is $\alpha$, it is also the upper bound
+of the difference:
+\[
+\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le \alpha\,.
+\]
+Since $\rho-\rho'$ is Hermitian, $\max_{\left\Vert \psi\right\Vert =1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
+is the maximum absolute value of the eigenvalues of $\rho-\rho'$~\citep{544199},
+and equal to $\left\Vert \rho-\rho'\right\Vert $~\citep{GolubVanLoan1996,Foucart2012}.
+Hence, $\left\Vert \rho-\rho'\right\Vert \le \alpha$.
+
+The previous theorem generalizes Gleason's theorem in the sense that
+it accounts for a larger class of probability measures which includes
+the conventional one as a limit. The theorem is however ``special'' in
+the sense that it only applies to the particular class of QIVPMs
+constructed by composing a clustering function with a conventional
+quantum probability measure. QIVPMs constructed in this manner have
+some peculiar properties which we examine next.
+
+A clustering function is called \emph{ultramodular} if it satisfies
+certain properties.
+
+\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
+  a collection of intervals $\mathscr{I}$ including $\imposs$ and
+  $\necess$, a clustering function
+  $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
+  ultramodular if:
+\begin{subequations}\label{eq:iota-constraints}
+\begin{eqnarray}
+ &  & \ultramodular(0)=\imposs\,,\\
+ &  & \ultramodular(1)=\necess\,,\\
+ &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
+\end{eqnarray}
+\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$, and
+$x_{2}\in\left[0,1\right]$ such that
+$y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have:
+\begin{equation}
+\ultramodular\left(y\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
+\end{equation}
+\end{definition}
+
+\noindent The first three constraints,
+Eqs.~(\ref{eq:iota-constraints}), are the direct counterpart of the
+corresponding QIVPM constraints, Eqs.~(\ref{eq:QIVPM-constraints});
+the last condition, Eq.~(\ref{eq:iota-Inclusion}), is the direct
+counterpart of the convexity conditions,
+Eq.~(\ref{eq:classicalconvex}) and
+(\ref{eq:QuantumInterval-valuedProbability-Inclusion}). Therefore,
+these conditions guarantee that, for any conventional quantum
+probability measure $\mu$, the composition $\ultramodular \circ \mu$,
+defines a valid QIVPM. Conversely, if for every quantum probability
+measure $\mu$, it is the case that $f \circ \mu$ is a QIVPM, then $f$
+is an ultramodular function. Formally, we have the following result.
+
 \begin{thm}[Equivalence of Ultramodular Functions and IVPMs]\label{thm:iota-statements}The
@@
   function~$\ultramodular\circ\mu:\events_{\mathrm{C}}\rightarrow\mathscr{I}$
-  is a classical IVPM for any classical probability
+  is a classical IVPM for all classical probability
   measure~$\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$.
@@
   function~$\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$ is a
-  QIVPM for any quantum probability
-  measure~$\mu:\events\rightarrow\left[0,1\right]$ on any Hilbert
-  space~$\Hilb$.
+  QIVPM for all quantum probability
+  measure~$\mu:\events\rightarrow\left[0,1\right]$.
 \end{enumerate}
@@
 \ref{enu:iota-mu-QIVPM} as we have outlined above. The rest of the
-proof is to show that if $\ultramodular$ is not ultramodular, then
+proof is to show that if $\ultramodular$ is not ultramodular, then for
+some quantum probability measure $\mu$, the composite
 $\ultramodular\circ\mu$ might not be a QIVPM. Suppose there are three
@@
 \end{equation}
-The induced map using the Born rule and approximated by
-$\ultramodular$, $\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
-fails to satisfy
+The induced map using the Born rule and clustered by $\ultramodular$,
+$\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ fails to satisfy
 Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
@@
 
-In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-there is always a state consistent with any composite QIVPM
-$\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$.  Moreover, the collection
-of states consistent with $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$
-gets closer and closer to~$\rho$ as the intervals get narrower and
-narrower. Eventually, the collection of states collapses to the
-singleton set~$\left\{ \rho\right\} $ as the intervals become the
-infinitely precise intervals~$\mathscr{I}_{\infty}$. To precisely
-state this result, we introduce the norm of pure states and
-operators. The norm of a pure state~$\ket{\psi}$ is defined as usual
-$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
-given any Hermitian operator~$A$, we consider the usual operator norm
-$\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert
-  =1}\left\Vert A\ket{\psi}\right\Vert $, which is also known as the
-$2$-norm or the spectral
-norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
-Then, a version of Gleason's theorem can be stated as follow.
-
-\begin{thm}[Finite-Precision Extension of Gleason's
-  theorem]\label{thm:Finite-precision-Gleason}Consider
-  an ultramodular function
-  $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ and let $m$
-  be the maximum length of intervals in its image. Given any
-  state~$\rho$, if a state
-  $\rho'\in\coreBorn\left(\ultramodular\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
-  then the norm of their difference is bounded by $m$, i.e.,
-  $\left\Vert \rho-\rho'\right\Vert \le m$.\end{thm}
-
-Given a state~$\rho'$ consistent with $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$,
-we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\ultramodular\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
-for any one-dimensional projector $\proj{\psi}$. Since the maximum
-length of the intervals in $\mathscr{I}$ is $m$, it is also the
-upper bound of the difference:
-\[
-\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le m\,.
-\]
-Since $\rho-\rho'$ is Hermitian, $\max_{\left\Vert \psi\right\Vert =1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
-is the maximum absolute value of the eigenvalues of $\rho-\rho'$~\citep{544199},
-and equal to $\left\Vert \rho-\rho'\right\Vert $~\citep{GolubVanLoan1996,Foucart2012}.
-Hence, $\left\Vert \rho-\rho'\right\Vert \le m$.
-
-The previous theorem generalizes Gleason's theorem in the sense that
-it accounts for a larger class of probability measures which includes
-the conventional one as a limit. The theorem is however ``weak'' in
-the sense that it only applies to the particular class of QIVPMs
-constructed by composing an ultramodular function with a conventional
-quantum probability measure.
-
-\amr{***WAVEFRONT***}
-
-Although a ultramodular function has many desirable properties, the
-set of intervals it mapping to either is trivial or contains infinite
-intervals.
+% In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
+% there is always a state consistent with any composite QIVPM
+% $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$.  Moreover, the collection
+% of states consistent with $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$
+% gets closer and closer to~$\rho$ as the intervals get narrower and
+% narrower. Eventually, the collection of states collapses to the
+% singleton set~$\left\{ \rho\right\} $ as the intervals become the
+% infinitely precise intervals~$\mathscr{I}_{\infty}$. To precisely
+% state this result, we introduce the norm of pure states and
+% operators. The norm of a pure state~$\ket{\psi}$ is defined as usual
+% $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
+% given any Hermitian operator~$A$, we consider the usual operator norm
+% $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert
+%   =1}\left\Vert A\ket{\psi}\right\Vert $, which is also known as the
+% $2$-norm or the spectral
+% norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+% Then, a version of Gleason's theorem can be stated as follow.
+
+In other words, essential properties of QIVPMs constructed using
+clustering functions can be gleaned from the properties of
+ultramodular functions. The following is a most interesting property
+in our setting.
 
@@
 \end{eqnarray}
-i.e., $\ultramodularL$ is midpoint-convex or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992}.
-Together with the fact that $\ultramodularL$ maps to a bounded interval
-$\left[0,1\right]$, the left-end function~$\ultramodularL$ must
-be continuous on the unit open interval $\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
-Therefore, either $\ultramodular$ maps every number in $\left(0,1\right)$
-to the same interval, or the number of intervals that $\ultramodular$
-maps to must be uncountable.
-
-Even if $\ultramodular$ has to be ultramodular to guarantee $\ultramodular\circ\mu$
-a QIVPM, the composited function $\ultramodular\circ\mu$ may still
-be a QIVPM when $\ultramodular$ is not ultramodular. In this case,
-the composited function $\ultramodular\circ\mu$ could map to non-trivial
-finite number of intervals. For example, we can weaken the convex
-condition, Eq.~(\ref{eq:iota-Inclusion}), to the following additive
-condition: for any numbers $x_{0}$ and $x_{1}\in\left[0,1\right]$,
-their sum $x_{0}+x_{1}\in\left[0,1\right]$ implies
-\begin{equation}
-\ultramodular\left(x_{0}+x_{1}\right)\subseteq\ultramodular\left(x_{0}\right)+\ultramodular\left(x_{1}\right)\,.\label{eq:iota-add}
-\end{equation}
-Then, given a three-dimensional Hilbert space, when $\ultramodular$
-satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
-$\ultramodular\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
-More concretely, consider an orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$,
-two states $\rho_{0}=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
-and $\rho_{1}=\frac{7}{24}\proj{0}+\frac{1}{3}\proj{1}+\frac{3}{8}\proj{2}$,
-and a set of intervals
-\begin{equation}
-\begin{aligned}\mathscr{I}_{2}={} & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\\
- & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{3}{4},1\right],\necess\right\} \,.
-\end{aligned}
-\end{equation}
-Since the interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
-defined in Table~\ref{tab:I_2} satisfies Eqs.~(\ref{eq:iota-constraints})
-and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\ultramodular_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
-and $\ultramodular_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are both
-QIVPMs.
-\begin{table}
-\caption{\label{tab:I_2}A interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$.}
-
-\hfill{}%
-\begin{minipage}[t]{2.5cm}%
-\begin{center}
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$x$ & $\ultramodular_{2}\left(x\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-$x=0$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$0<x\le\tfrac{1}{8}$ & $\left[0,\tfrac{1}{4}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\tfrac{1}{8}<x<\tfrac{3}{8}$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\tfrac{3}{8}\le x\le\tfrac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\par\end{center}%
-\end{minipage}\hfill{}%
-\begin{minipage}[t]{2.5cm}%
-\begin{center}
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$x$ & $\ultramodular_{2}\left(x\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-$\tfrac{5}{8}<x<\tfrac{7}{8}$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\tfrac{7}{8}\le x<1$ & $\left[\tfrac{3}{4},1\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$x=1$ & $\necess$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\par\end{center}%
-\end{minipage}\hfill{}
-\end{table}
-Given any one-dimensional projector $\proj{\psi}$, we have $\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\frac{1}{3}$
-so that $\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
-On the other hand, 
-\begin{eqnarray*}
-\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right) & = & \tfrac{7}{24}\left|\ip{\psi}{0}\right|^{2}+\tfrac{1}{3}\left|\ip{\psi}{1}\right|^{2}+\tfrac{3}{8}\left|\ip{\psi}{2}\right|^{2}
-\end{eqnarray*}
-is bounded between $\frac{7}{24}$ and $\frac{3}{8}$. Therefore,
-$\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\in\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$.
-According to the complement condition, Eq.~(\ref{eq:complement}),
-we also have $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\in\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
-for any two-dimensional projector~$P$. Hence, $\rho_{1}\in\coreBorn\left(\ultramodular_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
-and Thm.~\ref{thm:Finite-precision-Gleason} asserts $\left\Vert \rho_{0}-\rho_{1}\right\Vert $
-less than or equal to the maximum length of intervals $\frac{1}{2}$.
-This is true because the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $
-is $\frac{1}{24}$.
+i.e., $\ultramodularL$ is midpoint-convex or
+Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992}.
+Together with the fact that $\ultramodularL$ maps to a bounded
+interval $\left[0,1\right]$, the left-end function~$\ultramodularL$
+must be continuous on the unit open interval
+$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.  Therefore,
+either $\ultramodular$ maps every number in $\left[0,1\right]$ to the
+same interval, or the number of intervals that $\ultramodular$ maps to
+must be uncountable.
+
+To summarize, a conventional quantum probability measure, has an
+uncountable range $[0,1]$. A QIVPM constructed by clustering such a
+conventional quantum probabily measure, must also have an uncountable
+range of intervals. Of course, any particular QIVPM, or any particular
+experiment, will use a fixed collection of intervals appropriate for
+the resources and precision of the particular experiment.
+
+% The essential reason for getting an uncountable number of intervals is
+% the convexity condition we imposed on QIVPMs. This condition is widely
+% used in the classical setting but it is possible that it should be
+% modified or weakened in the quantum case. If we take this approach and 
+% % Even if $\ultramodular$ has to be ultramodular to guarantee
+% % $\ultramodular\circ\mu$ a QIVPM, the composited function
+% % $\ultramodular\circ\mu$ may still be a QIVPM when $\ultramodular$ is
+% % not ultramodular. In this case, the composited function
+% % $\ultramodular\circ\mu$ could map to non-trivial finite number of
+% % intervals. For example, we can 
+% weaken the convexity condition, Eq.~(\ref{eq:iota-Inclusion}), we can
+% recover QIVPMs that only require countable and even finite collections
+% of intervals. Formally, we weaken the convexity condition to the
+% following additive condition: for any numbers $x_{0}$ and
+% $x_{1}\in\left[0,1\right]$, their sum $x_{0}+x_{1}\in\left[0,1\right]$
+% implies
+% \begin{equation}
+% \ultramodular\left(x_{0}+x_{1}\right)\subseteq\ultramodular\left(x_{0}\right)+\ultramodular\left(x_{1}\right)\,.\label{eq:iota-add}
+% \end{equation}
+% Then, given a three-dimensional Hilbert space, if $\ultramodular$
+% satisfies Eqs.~(\ref{eq:iota-constraints}) and
+% Eq.~(\ref{eq:iota-add}), then $\ultramodular\circ\mu$ is a
+% QIVPM~\citep{HOSTunpublished}.  For example, consider an orthonormal
+% basis $\{\ket{0},\ket{1},\ket{2}\}$, two states
+% $\rho_{0}=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
+% and
+% $\rho_{1}=\frac{7}{24}\proj{0}+\frac{1}{3}\proj{1}+\frac{3}{8}\proj{2}$,
+% and a set of intervals:
+% \begin{equation}
+% \begin{aligned}\mathscr{I}_{2}={} & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\\
+%  & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{3}{4},1\right],\necess\right\} \,.
+% \end{aligned}
+% \end{equation}
+% Since the interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
+% defined in Table~\ref{tab:I_2} satisfies Eqs.~(\ref{eq:iota-constraints})
+% and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\ultramodular_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
+% and $\ultramodular_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are both
+% QIVPMs.
+% \begin{table}
+% \caption{\label{tab:I_2}A interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$.}
+
+% \hfill{}%
+% \begin{minipage}[t]{2.5cm}%
+% \begin{center}
+% \begin{tabular}{cc}
+% \toprule 
+% \addlinespace
+% $x$ & $\ultramodular_{2}\left(x\right)$\tabularnewline\addlinespace
+% \midrule
+% \midrule 
+% \addlinespace
+% $x=0$ & $\imposs$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $0<x\le\tfrac{1}{8}$ & $\left[0,\tfrac{1}{4}\right]$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $\tfrac{1}{8}<x<\tfrac{3}{8}$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $\tfrac{3}{8}\le x\le\tfrac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
+% \bottomrule
+% \end{tabular}
+% \par\end{center}%
+% \end{minipage}\hfill{}%
+% \begin{minipage}[t]{2.5cm}%
+% \begin{center}
+% \begin{tabular}{cc}
+% \toprule 
+% \addlinespace
+% $x$ & $\ultramodular_{2}\left(x\right)$\tabularnewline\addlinespace
+% \midrule
+% \midrule 
+% \addlinespace
+% $\tfrac{5}{8}<x<\tfrac{7}{8}$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $\tfrac{7}{8}\le x<1$ & $\left[\tfrac{3}{4},1\right]$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $x=1$ & $\necess$\tabularnewline\addlinespace
+% \bottomrule
+% \end{tabular}
+% \par\end{center}%
+% \end{minipage}\hfill{}
+% \end{table}
+% Given any one-dimensional projector $\proj{\psi}$, we have $\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\frac{1}{3}$
+% so that $\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
+% On the other hand, 
+% \begin{eqnarray*}
+% \mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right) & = & \tfrac{7}{24}\left|\ip{\psi}{0}\right|^{2}+\tfrac{1}{3}\left|\ip{\psi}{1}\right|^{2}+\tfrac{3}{8}\left|\ip{\psi}{2}\right|^{2}
+% \end{eqnarray*}
+% is bounded between $\frac{7}{24}$ and $\frac{3}{8}$. Therefore,
+% $\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\in\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$.
+% According to the complement condition, Eq.~(\ref{eq:complement}), we
+% also have
+% $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\in\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
+% for any two-dimensional projector~$P$. Hence,
+% $\rho_{1}\in\coreBorn\left(\ultramodular_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
+% and Thm.~\ref{thm:Finite-precision-Gleason} asserts that
+% $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is less than or equal to the
+% maximum length of intervals $\frac{1}{2}$.  This is true because the
+% exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
+% $\frac{1}{24}$.
 

### 2017-10-27 prop_letter.tex
prop_letter.tex \section{Fuzzy Measurements} Updating...

@@
 $\mu_{\phi}^{\mathrm{B}}$ defined as
-$\mu_{\phi}^{\mathrm{B}}(P)=\ip{\phi}{P\vert\phi}$. The situation
+$\mu_{\phi}^{\mathrm{B}}(P)=\melem{\phi}{P}{\phi}$. The situation
 generalizes to mixed states

### 2017-10-28 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Updating...

@@
 before. The new condition, known as
-\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
+\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,Marinacci_2004,Grabisch2016},
 reduces to the previously

### 2017-10-28 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Updating...

@@
 correspondence~\cite{HOSTunpublished} and Shapley's
-theorem~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}, which
-proves that a classical IVPM always contains at least one state $\rho$
+theorem~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci_2004,Grabisch2016},
+which proves that a classical IVPM always contains at least one state $\rho$
 that is consistent with every event in $\events_{\mathrm{C}}$. In contrast, as we
@@
 definition above is consistent with the classical notion of the
-\emph{Choquet integral}~\citep{GilboaSchmeidler1994,Grabisch2016}
+\emph{Choquet integral}~\citep{Choquet1954,GilboaSchmeidler1994,Marinacci_2004,Grabisch2016}
 which is used to calculate the expectation value of random variables

### 2017-10-29 prop_iop.tex
prop_letter.tex \section{Gleason} Updating...
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...
prop_letter.tex \section{The Kochen-Specker Theorem and Contextuality} Updating...

@@
 \caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
-on the three-dimensional Hilbert space. The projectors mapping to
-the same interval are listed in the column labeled by $P$ and separated
-by commas.}
+on a Hilbert space of dimension~$d\ge3$. The projectors mapping
+to the same interval are listed in the column labeled by $P$ and
+separated by commas.}
 \centering{}%
@@
 $\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
-is an additive interval-valued function.\end{example}
+is a convex interval-valued function.\end{example}
 
@@
 \addlinespace
-$4$ & $\left[\tfrac{1}{4},1\right]$ & $\tfrac{1}{4}$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
+$4$ & $\left[\tfrac{3}{4},1\right]$ & $\tfrac{1}{4}$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
 \midrule 
@@
 given a QIVPM\nb$\bar{\mu}:\events'\rightarrow\mathscr{I}$, then
-$\mu:\events'\rightarrow\left[0,1\right]$defined by $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
+$\mu:\events'\rightarrow\left[0,1\right]$ defined by $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
 is a quantum probability measure.\end{lemma}
@@
 $\mathscr{I}_{\infty}$ is one-to-one correspondence to quantum real-valued
-probability measures.
+probability measures. Moreover, since $\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
+is convex, we have the following corollary.
+
+\begin{cor}If every interval in $\mathscr{I}$ is a singleton set,
+then every QIVPM\nb$\bar{\mu}:\events'\rightarrow\mathscr{I}$ is
+convex.\end{cor}
 

### 2017-10-29 prop_letter.tex
prop_letter.tex \section{The Kochen-Specker Theorem and Contextuality} Updating...

@@
   Kochen-Specker] \label{thm:Kochen-Specker} Given a Hilbert space
-  $\Hilb$ of dimension~$d\ge3$, there is no 0-deterministic
+  $\Hilb$ of dimension $d\ge3$, there is no 0-deterministic
   measure~$\bar{\mu}$ mapping every event to either $\imposs$ or
@@
 \hline 
-\end{tabular}\,,
+\end{tabular}
 \par\end{center}
@@
 implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Indeed when
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{HOSTunpublished}. Indeed when
 $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,

### 2017-10-30 prop_letter.tex
prop_letter.tex \section{The Born rule and Gleason's Theorem} Updating..

@@
 before. The new condition, known as
-\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,Marinacci_2004,Grabisch2016},
+\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,Grabisch2016},
 reduces to the previously
@@
 correspondence~\cite{HOSTunpublished} and Shapley's
-theorem~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci_2004,Grabisch2016},
+theorem~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
 which proves that a classical IVPM always contains at least one state $\rho$
@@
 definition above is consistent with the classical notion of the
-\emph{Choquet integral}~\citep{Choquet1954,GilboaSchmeidler1994,Marinacci_2004,Grabisch2016}
+\emph{Choquet integral}~\citep{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
 which is used to calculate the expectation value of random variables
@@
 
-The equivalence between Statement~\ref{enu:iota-subject-to} and
-\ref{enu:iota-mu-CIVPM} is a well-known classical
-result~\citep{Choquet1954,NgMoYeh1997,Marinacci_2004}.  For the
-quantum case, Statement~\ref{enu:iota-subject-to} implies
-\ref{enu:iota-mu-QIVPM} as we have outlined above. The rest of the
-proof is to show that if $\ultramodular$ is not ultramodular, then for
+Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
+and~\ref{enu:iota-mu-QIVPM} as we have outlined above. For the quantum case, we want
+to show that if $\ultramodular$ is not ultramodular, then for
 some quantum probability measure $\mu$, the composite
@@
 $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. In other
-words, this induced map fails to be a QIVPM.
+words, this induced map fails to be a QIVPM. For the classical case, if
+$\ultramodular$ is not ultramodular, consider the commuting subspace of
+event~$\events_{\mathrm{C}}$ generated by $\proj{0}$, $\proj{1}$, $\proj{2}$,
+and $\proj{3}$, and then state~$\rho$ defined previously. Then, restricting
+$\mu_{\rho}^{\mathrm{\mathrm{B}}}$ to $\events_{\mathrm{C}}$,
+$\mu_{\rho}^{\mathrm{\mathrm{B}}}|_{\events_{0}}$, gives a classical probability
+measure $\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$. By the same
+reason as the quantum case, the induced map $\ultramodular\circ\mu$ fails to be
+a classical IVPM.
 

### 2017-10-31 prop_letter.tex
prop_letter.tex \section{The Born rule and Gleason's Theorem} Updating..

@@
 principle that uses $\subseteq$ instead of $=$ for the same reason as
-before. The new condition, known as
-\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,Grabisch2016},
+before. The new condition, known as \emph{convexity}
+\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,MarinacciMontrucchio2005,Grabisch2016},
 reduces to the previously
@@
 Eq.~(\ref{eq:classicalconvex}) and
-(\ref{eq:QuantumInterval-valuedProbability-Inclusion}). Therefore,
+(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+\cite{Choquet1954,Shapley1971,NgMoYeh1997,MarinacciMontrucchio2005}. Therefore,
 these conditions guarantee that, for any conventional quantum
@@
 Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
-and~\ref{enu:iota-mu-QIVPM} as we have outlined above. For the quantum case, we want
+and~\ref{enu:iota-mu-QIVPM} as we have outlined above. Conversely, for the quantum case, we want
 to show that if $\ultramodular$ is not ultramodular, then for
@@
 particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
-such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but they don't
+such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but they don't
 satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the state:
-\begin{equation}
-\begin{aligned}\rho={} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
- & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
-\end{aligned}
-\end{equation}
+\[
+\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-y\right)\proj{3}\,.
+\]
 The induced map using the Born rule and clustered by $\ultramodular$,
-$\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ fails to satisfy
+$\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$, fails to satisfy
 Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
@@
 words, this induced map fails to be a QIVPM. For the classical case, if
-$\ultramodular$ is not ultramodular, consider the commuting subspace of
+$\ultramodular$ is not ultramodular, we also want to find a classical
+probability measure $\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$ such
+that $\ultramodular\circ\mu$ is not a classical IVPM. This can be
+done by restricting our previous quantum probability measure
+$\mu_{\rho}^{\mathrm{\mathrm{B}}}$ on a commuting subspace of
 event~$\events_{\mathrm{C}}$ generated by $\proj{0}$, $\proj{1}$, $\proj{2}$,
-and $\proj{3}$, and then state~$\rho$ defined previously. Then, restricting
-$\mu_{\rho}^{\mathrm{\mathrm{B}}}$ to $\events_{\mathrm{C}}$,
-$\mu_{\rho}^{\mathrm{\mathrm{B}}}|_{\events_{0}}$, gives a classical probability
-measure $\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$. By the same
-reason as the quantum case, the induced map $\ultramodular\circ\mu$ fails to be
-a classical IVPM.
+and $\proj{3}$. The restricted function
+$\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}|_{\events_{\mathrm{C}}}$ is a classical probability
+measure, and the induced map $\ultramodular\circ\mu$ fails to be
+a classical IVPM by the same reason as the quantum case.
 
@@
 i.e., 
-\begin{equation}
-\begin{aligned} & \ultramodularL\left(x_{0}+x_{1}+x_{2}\right)+\ultramodularL\left(x_{2}\right)\\
-\ge{} & \ultramodularL\left(x_{0}+x_{2}\right)+\ultramodularL\left(x_{1}+x_{2}\right)\,.
-\end{aligned}
-\end{equation}
-Then, for any $x_{0}'$ and $x_{1}'\in\left[0,1\right]$ with $x_{0}'\ge x_{1}'$,
-we can substitute $x_{0}$ and $x_{1}$ by $\left(x_{0}'-x_{1}'\right)/2$
-, substitute $x_{2}$ by $x_{1}'$, and get the following inequality
-\begin{eqnarray}
-\frac{\ultramodularL\left(x_{0}'\right)+\ultramodularL\left(x_{1}'\right)}{2} & \ge & \ultramodularL\left(\frac{x_{0}'+x_{1}'}{2}\right)\,,
-\end{eqnarray}
-i.e., $\ultramodularL$ is midpoint-convex or
-Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992}.
+\[
+\ultramodularL\left(y\right)+\ultramodularL\left(x_{2}\right)\ge\ultramodularL\left(x_{0}+x_{2}\right)+\ultramodularL\left(x_{1}+x_{2}\right)
+\]
+for three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$ with
+$y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$. 
 Together with the fact that $\ultramodularL$ maps to a bounded
@@
 must be continuous on the unit open interval
-$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.  Therefore,
+$\left(0,1\right)$~\citep{MarinacciMontrucchio2005}.  Therefore,
 either $\ultramodular$ maps every number in $\left[0,1\right]$ to the

### 2017-11-02 prop_letter.tex
prop_letter.tex \section{The Kochen-Specker Theorem and Contextuality} Updating...
meeting

@@
 interval valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
-The QIVPMs will provide the mathematical framework we need to quantify the
-impact of finite precision measurements on quantum mechanics.  For
+The QIVPMs will provide the mathematical framework we need to quantify
+the impact of finite precision measurements on quantum mechanics.  For
 instance, in Sec.~\ref{sec:Kochen-Specker}, we quantify the domain of
@@
 under which the Kochen-Specker theorem applies.  This provides a way
-not only of resolving the Meyer-Mermin debate, but also revealing a
+not only of resolving the Meyer-Mermin debate, but also revealing of a
 precise transition to non-contextuality; these are the results of our
@@
 bounded resources, holds asymptotically in a mathematically precise
-way.  Finally, we present our conclusions in Sec.~\ref{sec:Conclusion}.
+way.  Finally, we present our conclusions in
+Sec.~\ref{sec:Conclusion}.
 
@@
 quantum case, the events of interest are specified by \emph{projection
-  operators} $P$. These include the empty projector~$\mathbb{0}$, the
-identity projector~$\mathbb{1}$, projectors of the form $\proj{\phi}$
-where $\ket{\phi}$ is a pure quantum state (an element of a Hilbert
-space), sums of \emph{orthogonal} projectors $P_0$ and~$P_1$ with
-$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projectors $P_0$
-and~$P_1$ with $P_0P_1=P_1P_0$. In a quantum probability
+  operators} $P$ satisfying the condition $P^2=P$. These include the
+empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
+projectors of the form $\proj{\phi}$ where $\ket{\phi}$ is a pure
+quantum state (an element of a Hilbert space), sums of
+\emph{orthogonal} projectors $P_0$ and~$P_1$ with $P_0P_1=\mathbb{0}$,
+and products of \emph{commuting} projectors $P_0$ and~$P_1$ with
+$P_0P_1=P_1P_0$. In a quantum probability
 space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
@@
 \end{equation}
-Given a probability for every projector, we can define the
-expectation value of an observable~$\mathbf{O}$ having spectral
-decomposition $\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$ as:
-\begin{equation}
-\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{N}\lambda_{i}\mu(P_{i})\,.\label{eq:quantum-expectation}
-\end{equation}
-
-A conventional quantum probability measure can easily be
-constructed using the Born rule if one knows the current state of the quantum
+Given a Hilbert space of dimension $d$ and a probability assignment
+for every projector $P$, we can define the expectation value of an
+observable~$\mathbf{O}$ having spectral decomposition
+$\mathbf{O}=\sum_{i=1}^{d}\lambda_{i}P_{i}$ as:
+\begin{equation}
+\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{d}\lambda_{i}\mu(P_{i})\,.\label{eq:quantum-expectation}
+\end{equation}
+
+A conventional quantum probability measure can easily be constructed
+using the Born rule if one knows the current state of the quantum
 system.  Specifically, for each pure normalized quantum
@@
 generalizes to mixed states
-$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
+$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $q_j > 0$ and
 $\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
@@
 devices, an experimenter might only be able to determine that the
-probability of the event $\proj{0}$ is concentrated in the range $[0.49,0.51]$
-instead of precisely 0.5. The spread in this range depends on the
-amount of resources (time, energy, money, etc.) that are devoted to
-the experiment. In the classical setting, this ``fuzziness'' can be
-formalized by moving to \emph{interval-valued probability measures}
-(IVPMs), which we explore in the next section, along with our proposed
-extension to the quantum domain.
+probability of an event $P$ is concentrated in the range $[0.49,0.51]$
+instead of being precisely 0.5. The spread in this range depends on
+the quantities of resources (time, energy, money, etc.) that are
+devoted to the experiment. In the classical setting, this
+``fuzziness'' can be formalized by moving to \emph{interval-valued
+  probability measures} (IVPMs), which we explore in the next section,
+along with our proposed extension to the quantum domain.
 
@@
 disjoint events. The correct constraint regarding the probability of
-$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
-$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
-combination with the requirement for the event of the entire space would force
-$\mu(E \cup \overline{E})$ to always be $\necess$ irrespective of the
-particular assignments of $\mu(E)$ or~$\mu(\overline{E})$. 
+$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is:
+\begin{equation}
+\label{eq:disjoint}
+\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]
+\end{equation}
+which, in combination with the requirement for the event of the entire
+space would force $\mu(E \cup \overline{E})$ to always be $\necess$
+irrespective of the particular assignments of $\mu(E)$
+or~$\mu(\overline{E})$.
 %% Parallel arguments
@@
 \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,MarinacciMontrucchio2005,Grabisch2016},
-reduces to the previously
-motivated condition when the events are disjoint, i.e., when
-$\mu(E_1\cap E_2) = 0$.
+reduces to the previously motivated Eq.~(\ref{eq:disjoint}) when the
+events are disjoint, i.e., when $\mu(E_1\cap E_2) = 0$.
 
@@
 quantum probability measures. We will show that QIVPMs reduce to
-classical IVPMs when the space of quantum events is restricted to
-mutually commuting events, i.e., to compatible events that can be
-measured simultaneously. In Sec.~\ref{sec:Gleason} we will discuss the
-connection between QIVPMs and conventional quantum probability
-measures in detail.
+classical IVPMs when the space of quantum events $\events$ is
+restricted to mutually commuting events $\events_{\mathrm{C}}$, i.e.,
+to compatible events that can be measured simultaneously. In
+Sec.~\ref{sec:Gleason} we will discuss the connection between QIVPMs
+and conventional quantum probability measures in detail.
 
@@
 where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
-is the probability that the event~$P$ is determined by the Born
-rule~\citep{Born1983,peres1995quantum,544199}.
+is the probability of the event~$P$ as determined by the Born
+rule~\citep{Born1983,Mermin2007}.
 
@@
 subspaces of events as follows. A set of events $\events'$ is a
-\emph{subspace} if it contains $\mathbb{0}$ and~$\mathbb{1}$ and is
-closed under complements, sums, and product, i.e., for any projector~$P\in\events'$,
-we have $\mathbb{1}-P\in\events'$ and for each pair of commuting
-projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have $P_{0}+P_{1}-P_{0}P_{1}$
-and $P_{0}P_{1}\in\events'$. Given a
+\emph{subspace} of $\events$ if it contains $\mathbb{0}$
+and~$\mathbb{1}$ and is closed under complements, sums, and products,
+i.e., for any projector~$P\in\events'$, we have
+$\mathbb{1}-P\in\events'$ and for each pair of commuting
+projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
+$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$. Given a
 probability measure $\bar{\mu}$ and a subspace of events $\events'$,
@@
 long version of this paper~\cite{HOSTunpublished}. The idea of the
-proof is as follows. Given a subspace of commuting events~$\events_{\mathrm{C}}$,
-we can construct a partial orthonormal basis by diagonalization and
-complete it to a full orthonormal basis $\overline{\events_{\mathrm{C}}}$. We
-then build a bijection between the QIVPM on the set of projectors
-associated with this basis and the set of classical events
-corresponding to this basis. This correspondence leads to a crucial
-property in our setting.
+proof is as follows. Given a subspace of mutually commuting
+events~$\events_{\mathrm{C}}$, we can construct a partial orthonormal
+basis by diagonalization and complete it to a full orthonormal basis
+$\overline{\events_{\mathrm{C}}}$. We then build a bijection between
+the QIVPM on the set of projectors associated with this basis and the
+set of classical events corresponding to this basis. This
+correspondence leads to a crucial property in our setting.
 
@@
 knowledge about the particular quantum system in question; any quantum
-state would be consistent with $\bar{\mu}_{1}$ on any projectors, and
-$\coreBorn\left(\bar{\mu}_{1},\events\right)$ is just the set of all
+state would be consistent with $\bar{\mu}_{1}$ on any projectors. That
+is, $\coreBorn\left(\bar{\mu}_{1},\events\right)$ is the set of all
 states. The subspace
@@
 is a subspace of commuting events. Indeed restricting $\bar{\mu}_{1}$
-to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
-IVPM~$\bar{\mu}_{2}$:
+to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a measure
+$\bar{\mu}_{2}$:
 \begin{equation}
@@
 \end{equation}
-If we identify the states ~$\proj{0}$ and $\proj{1}$ with the head and
-the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents the
-situation in which an experimenter knows nothing about a coin before
-she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
+that corresponds to a classical IVPM. Indeed, if we identify the
+states~$\proj{0}$ and $\proj{1}$ with the head and the tail of a coin,
+respectively, then $\bar{\mu}_{2}$ represents the situation in which
+an experimenter knows nothing about a coin before she tosses
+it. Moreover, for each $p\in\left[0,1\right]$, the
 state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical coin
@@
 \begin{definition}[Expectation Value of Observables over QIVPMs] Let
-  $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space
-  with event space~$\events$; and $\mathbf{O}$ an
+  $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space of
+  dimension $d$ with event space~$\events$; and $\mathbf{O}$ an
   observable with spectral decomposition
-  $\Sigma_{i=1}^N \lambda_iP_i$. Let $\events'$ be the minimal
+  $\Sigma_{i=1}^d \lambda_iP_i$. Let $\events'$ be the minimal
   subspace of events containing all the projectors $P_i$ in the
@@
 % not a probability of an event. 
-We also note that, when restricted to commuting projectors, the
-definition above is consistent with the classical notion of the
-\emph{Choquet integral}~\citep{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+We also note that, when restricted to commuting projectors,
+Eq.~(\ref{eq:quantum-interval-expectation-core}) is consistent with
+the classical notion of the \emph{Choquet
+  integral}~\citep{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
 which is used to calculate the expectation value of random variables
@@
 to strengthen the scope of one of the fundamental theorems of quantum
-information: the Kochen-Specker
+physics: the Kochen-Specker
 theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}. Our
-finite-precision extension of the theorem will suggest a resolution to
-the debate initiated by Meyer and Mermin on the relevance of the
+finite-precision extension of that theorem will suggest a resolution
+to the debate initiated by Meyer and Mermin on the relevance of the
 Kochen-Specker to experimental, and hence finite-precision, quantum
 measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
-Specifically, the original Kochen-Specker theorem is formulated
-using a model quantum mechanical system that
-has \emph{definite values at all times}~\cite{Held2016}, i.e., they
-have infinitely precise values at all times. Our interval-valued
-probability framework will allow us to state, and prove, a stronger
-version of the theorem that holds even if the observables have values
-that are only definite up to some precision specified by a parameter
-$\delta$. Our approach provides a quantitative realization of
-Mermin's intuition~\citep{Mermin1999}:
+Specifically, the original Kochen-Specker theorem is formulated using
+a model quantum mechanical system that has \emph{definite values at
+  all times}~\cite{Held2016}, i.e., its observables have infinitely
+precise values at all times. Our interval-valued probability framework
+will allow us to state, and prove, a stronger version of the theorem
+that holds even if the observables have values that are only definite
+up to some precision specified by a parameter $\delta$. Our approach
+provides a quantitative realization of Mermin's
+intuition~\citep{Mermin1999}:
 \begin{quote}
@@
   \noindent \centering{}\caption{\label{tab:classical-IVPMs}Example 
-    IVPMs~$\bar{\mu}_{4}$, $\bar{\mu}_{5}$ and $\bar{\mu}_{6}$.}
+    QIVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ on
+    commuting events $P$.}
 \begin{tabular}{cccc}
@@
 \addlinespace
-$P$ & $\bar{\mu}_{4}(P)$ & $\bar{\mu}_{5}(P)$ & $\bar{\mu}_{6}(P)$\tabularnewline\addlinespace
+$P$ & $\bar{\mu}_{A}(P)$ & $\bar{\mu}_{B}(P)$ & $\bar{\mu}_{C}(P)$\tabularnewline\addlinespace
 \midrule
@@
 \addlinespace
-$\proj{0}$ & $\necess$ & $\left[\frac{1}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline\addlinespace
+$\proj{0}$ & $\necess$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline\addlinespace
 \midrule 
@@
 
-\noindent The definition puts no restrictions on the set of intervals
+\noindent This definition puts no restrictions on the set of intervals
 itself, only on which intervals are assigned to events. When
@@
 determined with certainty. As $\delta$ gets larger, the QIVPM allows
-for more indeterminate behavior. For example, the IVPM~$\bar{\mu}_{4}$
-defined in Table~\ref{tab:classical-IVPMs} is $0$-deterministic
-because $\imposs\subseteq\left[0,0\right]$ and
+for more indeterminate behavior. For example, $\bar{\mu}_{A}$ defined
+in Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
+$\imposs\subseteq\left[0,0\right]$ and
 $\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
 ~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
-$\bar{\mu}_{4}$ represents tossing a double-headed coin. When $\delta$
-is increased to $\frac{1}{3}$, both the IVPMs~$\bar{\mu}_{5}$ and
-$\bar{\mu}_{6}$ become $\frac{1}{3}$-deterministic. In contrast, the
-IVPM~$\bar{\mu}_{2}$ defined in
+$\bar{\mu}_{A}$ represents tossing a double-headed coin. When $\delta$
+is increased to $\frac{1}{3}$, both $\bar{\mu}_{B}$ and
+$\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
+$\bar{\mu}_{2}$ defined in
 Eq.~(\ref{eq:classical-no-information-IVPM}) is still not
@@
 
-The expectation value of an observable relative to a 0-deterministic
-QIVPM is fully determinate and is equal to one of the eigenvalues of
-that observable. To see this, note that given an orthonormal basis
-$\Omega=\{ \ket{\psi_0},\ket{\psi_1},\ldots\}$, a 0-deterministic
-QIVPM must map exactly one of the projectors $\proj{\psi_i}$ to
-$\necess$ and all others to $\imposs$. This is because by
-Eq.~(\ref{eq:necess}), we have
-$\bar{\mu}(\Sigma_i{\proj{\psi_i}})=\necess$ and by inductively applying
-Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), we must have
-one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all others mapped to
-$\imposs$. Given any state~$\rho$ that is consistent with this QIVPM
-on all the projectors in $\Omega$, we have by Eq.~(\ref{eq:hbar}) that
-$\mu_{\rho}^{\mathrm{B}}$ must also map exactly one of the projectors
-in $\Omega$ to 1 and all others to 0. If an observable has a spectral
-decomposition along $\Omega$ then, by
+The expectation value of an observable $\mathbf{O}$ in a Hilbert space
+of dimension $d$ relative to a 0-deterministic QIVPM is fully
+determinate and is equal to one of the eigenvalues $\lambda_i$ of that
+observable. To see this, note that given an orthonormal basis
+$\Omega=\{ \ket{\psi_0},\ket{\psi_1},\ldots,\ket{\psi_{d-1}}\}$, a
+0-deterministic QIVPM must map exactly one of the projectors
+$\proj{\psi_i}$ to $\necess$ and all others to $\imposs$. This is
+because, by Eq.~(\ref{eq:necess}), we have
+$\bar{\mu}(\Sigma_{j=0}^{d-1}{\proj{\psi_j}})=\necess$ and by inductively
+applying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+we must have one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all
+others mapped to $\imposs$. Given any state~$\rho$ that is consistent
+with this QIVPM on all the projectors in $\Omega$, we have by
+Eq.~(\ref{eq:hbar}) that $\mu_{\rho}^{\mathrm{B}}$ must also map
+exactly one of the projectors in $\Omega$ to 1 and all others to 0. If
+an observable has a spectral decomposition along $\Omega$ then, by
 Eq.~(\ref{eq:quantum-expectation}), its expectation value relative to
@@
 We can now proceed with the main technical result of this section. We
-start with a remark that the original Kochen-Specker theorem is a
-statement regarding the non-existence of $0$-deterministic QIVPM and
+first observe that the original Kochen-Specker theorem is a statement
+regarding the non-existence of a $0$-deterministic QIVPM, and
 generalize to $\delta$-deterministic QIVPMs.
 
-\begin{thm}[0-Deterministic Variant of
-  Kochen-Specker] \label{thm:Kochen-Specker} Given a Hilbert space
-  $\Hilb$ of dimension $d\ge3$, there is no 0-deterministic
-  measure~$\bar{\mu}$ mapping every event to either $\imposs$ or
-  $\necess$.
+\begin{thm}[0-Deterministic Variant of the Kochen-Specker
+  Theorem] \label{thm:Kochen-Specker} Given a Hilbert space $\Hilb$ of
+  dimension $d\ge3$, there is no 0-deterministic measure~$\bar{\mu}$
+  mapping every event to either $\imposs$ or $\necess$.
 \end{thm}
@@
 
-We consider a 2-qubit Hilbert space $\Hilb=\Hilb_1\otimes\Hilb_2$
-representing pairs of spin-$\frac{1}{2}$ states. We use the same nine
+We consider a two spin-$\frac{1}{2}$ Hilbert space
+$\Hilb=\Hilb_1\otimes\Hilb_2$ of dimension $d=4$. We use the same nine
 observables $\mathbf{O}_{ij}$ with $i$ and $j$ ranging over
-$\{0,1,2\}$ from the ``Mermin-Peres'' proof of the Kochen-Specker
-theorem~\cite{Mermin1990Simple,peres1995quantum}:
+$\{0,1,2\}$ from the Mermin-Peres ``magic square'' proof of the
+Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum}:
 
@@
 for small enough $\delta$, it is impossible to have
-$\delta$-deterministic QIVPMs. We therefore prove a stronger statement of 
-contextuality that includes the effects of finite-precision.
-Every QIVPM must map some events to
-truly uncertain intervals, not just ``almost definite intervals.'' The
-significance of this observation is that the uncertainty in the
-intervals is, in contrast to the classical case, \emph{a fundamental
-  part of quantum theory}. There are in fact two sources of
-uncertainty: one due to the finite measurement resources and one due
-to complementarity, which requires every quantum framework to be truly
-probabilistic.
-
-\begin{thm}[Finite-precision Extension of Kochen-Specker] \label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$
-  of dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
-  $\delta<\frac{1}{3}$.\end{thm}
+$\delta$-deterministic QIVPMs. We next prove a main result of this
+paper which is a stronger statement of contextuality that includes the
+effects of finite-precision.  Every QIVPM must map some events to
+truly uncertain intervals, not just ``almost definite intervals.''
+
+\begin{thm}[Finite-precision Extension of the Kochen-Specker
+  Theorem] \label{cor:Kochen-Specker-IVPM} Given a Hilbert space
+  $\Hilb$ of dimension~$d\ge3$, there is no $\delta$-deterministic
+  QIVPM for $\delta<\frac{1}{3}$.\end{thm}
 
@@
 implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{HOSTunpublished}. Indeed when
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{HOSTunpublished}. Indeed
+when
 $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
@@
 $\bar{\mu}\left(P_{0}+P_{1}\right)$ cannot be a subset of
-$\left[1-\delta,1\right]$, but $\bar{\mu}\left(P_{0}+P_{1}\right)$ is
-a subset of either $\left[0,\delta\right]$ or
-$\left[1-\delta,1\right]$.  Hence, $\bar{\mu}\left(P_{0}+P_{1}\right)$
-must be a subset of $\left[0,\delta\right]$, which implies
+$\left[1-\delta,1\right]$. Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
+is a subset of either $\left[0,\delta\right]$ or
+$\left[1-\delta,1\right]$ and the latter is excluded, then
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
+$\left[0,\delta\right]$, which implies
 $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
@@
 
-When $\delta \ge \frac{1}{3}$, the situation abruptly
-changes. Assuming a Hilbert space $\Hilb$ of dimension $3$, then for
-any projector $P$ that projects onto an $n$-dimensional subspace of
-$\Hilb$, it is straightforward to check that
-$\bar{\mu}\left(P\right)=\left[\frac{n}{3},\frac{n}{3}\right]$ is a valid
-$\frac{1}{3}$-deterministic QIVPM. In other words, when the
-uncertainty in measurements becomes so large, the Kochen-Specker
-theorem no longer holds and it becomes possible to map every
+The bound $\delta < \frac{1}{3}$ is tight as it is possible to
+construct $\frac{1}{3}$-deterministic QIVPMs. For example, take $d=3$,
+and let $P$ be a projector onto an $n$-dimensional subspace of
+$\Hilb$, where $n \leq 3$. It is straightforward to check that
+$\bar{\mu}\left(P\right)=\left[\frac{n}{3},\frac{n}{3}\right]$ is a
+valid $\frac{1}{3}$-deterministic QIVPM.
+
+When $\delta \geq \frac{1}{3}$, i.e, when the uncertainty in
+measurements becomes that large, it becomes possible to map every
 observable to some (quite inaccurate) probability interval, and hence
-the theory becomes non-contextual.
+invalidating the Kochen-Specker theorem.
+
+\amr{
+Something like this: We have quantified one aspect of imprecision in
+QM (originally noted by Heisenberg -- cite microscope paper). This
+does not account for all the probabilistic nature of QM,
+however. Merge with original sentence: The significance of this
+observation is that the uncertainty in the intervals is, in contrast
+to the classical case, \emph{a fundamental part of quantum
+  theory}. There are in fact two sources of uncertainty: one due to
+the finite measurement resources and one due to complementarity, which
+requires every quantum framework to be truly probabilistic.
+}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Born rule and Gleason's Theorem}
+\section{The Born Rule and Gleason's Theorem}
 
@@
 A conventional quantum probability measure can be easily constructed
-from a state according to the Born
+from a state $\rho$ according to the Born
 rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.  According
@@
 theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}, this
-state is also the unique state consistent with any possible
+state $\rho$ is also the unique state consistent with any possible
 probability measure. In order to re-examine these results in our
@@
 
-\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
-a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
-the state consistent with it on every projector, $\coreBorn\left(\bar{\mu},\events\right)$,
-is unique. \end{thm}
+\begin{thm}[$\mathscr{I}_{\infty}$ Variant of the Gleason
+  Theorem]\label{cor:Gleason's}In
+  a Hilbert space $\Hilb$ of dimension $d\geq3$, given a
+  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$, the state
+  $\rho$ consistent with it on every projector,
+  $\coreBorn\left(\bar{\mu},\events\right)$, is unique. \end{thm}
+
+\amr{Rewrite next sentence. Thm 4 assumes infinite
+  precision. Question: what happens with finite precision
+  intervals. Two thoughts: (1) multiple states will match the
+  probab. distribution, (2) for small collections of projectors
+  different states will agree with observations; if one looks at all
+  projectors it may be the case that no state agrees with all.}
 
@@
 
-\begin{thm}[Empty Core for General QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
-a Hilbert space of dimension~$d\ge3$, there exists a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
-such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
-
-To prove the theorem, we just need to construct a QIVPM, and verify
-that there are no states that are consistent with it on all
-projectors. Given an orthonormal basis
-$\left\{ \ket{0},\ket{1},\ket{2},\ldots,\ket{d-1}\right\} $, let
+\begin{thm}[Empty Core for General
+  QIVPMs]\label{thm:Non-extensible-of-Gleason's}There exists a Hilbert
+  space and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ such
+  that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
+
+To prove this theorem, we need to construct a QIVPM on some Hilbert
+space, and verify that there are no states that are consistent with it
+on all possible events. Assume a Hilbert space of dimention $d=3$ with
+orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let
 $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
@@
 \end{equation}
-The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined in
-Table~\ref{tab:non-Born-QIVPM} can be verified as a
+The map~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined in
+Table~\ref{tab:non-Born-QIVPM} can be verified to be a
 QIVPM~\citep{HOSTunpublished}.
 \begin{table}
-\caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
-on a Hilbert space of dimension~$d\ge3$. The projectors mapping
-to the same interval are listed in the column labeled by $P$ and
-separated by commas.}
+\caption{\label{tab:non-Born-QIVPM}QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+on a Hilbert space of dimension~$d=3$. Events are listed in the column
+labeled by $P$.}
 
@@
 \addlinespace
-$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
+$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, 
 $\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
@@
 \end{table}
-Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
-empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
-where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
-for any~$P$, the state~$\rho$ must satisfy: 
+Next we will prove by contradiction that
+$\coreBorn\left(\bar{\mu},\events\right)$ is the empty set. Suppose
+there is a state
+$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
+$\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$ for any~$P$, the
+state~$\rho$ must satisfy:
 \begin{equation}
@@
 To that end, we construct a family of QIVPMs parameterized by
-clustering functions $f:\left[0,1\right]\rightarrow\mathscr{I}$ that
+\emph{blurring} functions $f:\left[0,1\right]\rightarrow\mathscr{I}$ that
 formalize how the real-valued probabilities are mapped to
@@
 
-\begin{thm}[Finite-Precision Extension of Gleason's
-  theorem]\label{thm:Finite-precision-Gleason}Let $f$ be a clustering
+\begin{thm}[Finite-Precision Extension of the Gleason
+  Theorem]\label{thm:Finite-precision-Gleason}Let $f$ be a blurring
   function and let $f \circ \mu_{\rho}^{\mathrm{B}}$ be a QIVPM, where
@@
 the sense that it only applies to the particular class of QIVPMs
-constructed by composing a clustering function with a conventional
+constructed by composing a blurring function with a conventional
 quantum probability measure. QIVPMs constructed in this manner have
@@
 
-A clustering function is called \emph{ultramodular} if it satisfies
+A blurring function is called \emph{ultramodular} if it satisfies
 certain properties.
@@
   a collection of intervals $\mathscr{I}$ including $\imposs$ and
-  $\necess$, a clustering function
+  $\necess$, a blurring function
   $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
@@
 \]
-The induced map using the Born rule and clustered by $\ultramodular$,
+The induced map using the Born rule and blurred by $\ultramodular$,
 $\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$, fails to satisfy
@@
 In other words, essential properties of QIVPMs constructed using
-clustering functions can be gleaned from the properties of
+blurring functions can be gleaned from the properties of
 ultramodular functions. The following is a most interesting property
@@
 To summarize, a conventional quantum probability measure, has an
-uncountable range $[0,1]$. A QIVPM constructed by clustering such a
-conventional quantum probabily measure, must also have an uncountable
+uncountable range $[0,1]$. A QIVPM constructed by blurring such a
+conventional quantum probability measure, must also have an uncountable
 range of intervals. Of course, any particular QIVPM, or any particular

### 2017-11-03 prop_letter.tex
Updated by Prof. Ortiz...

@@
 \end{equation}
-Given a Hilbert space of dimension $d$ and a probability assignment
+Given a Hilbert space ${\cal H}$ of dimension $d$ and a probability assignment
 for every projector $P$, we can define the expectation value of an
 observable~$\mathbf{O}$ having spectral decomposition
-$\mathbf{O}=\sum_{i=1}^{d}\lambda_{i}P_{i}$ as:
+$\mathbf{O}=\sum_{i=1}^{d}\lambda_{i}P_{i}$, with eigenvalues $\lambda_i \in \mathbb{R}$, as:
 \begin{equation}
@@
 system.  Specifically, for each pure normalized quantum
-state~$\ket{\phi}$, the Born rule induces a probability measure
+state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
 $\mu_{\phi}^{\mathrm{B}}$ defined as
@@
 generalizes to mixed states
-$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $q_j > 0$ and
+$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, $\ket{\phi_j} \in {\cal H}$, where $q_j > 0$ and
 $\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule

### 2017-11-03 prop_letter.tex
From: Tai, Yu-Tsung Sent: Friday, November 03, 2017 0:29 To: 'Gerardo Ortiz' <ortizg@indiana.edu>; Amr Sabry <sabry@indiana.edu>; Andrew J. Hanson <hansona@indiana.edu> Subject: RE: KS
Merged suggestions into the texts… 

Best regards,
Tai, Yu-Tsung (戴淯琮)
PhD Candidate in Mathematics & Computer Science Indiana University,
Bloomington

-----Original Message-----
From: Gerardo Ortiz [mailto:ortizg@indiana.edu]
Sent: Thursday, November 02, 2017 17:53
To: Tai, Yu-Tsung <yuttai@imail.iu.edu>; Amr Sabry <sabry@indiana.edu>;
Andrew J. Hanson <hansona@indiana.edu>
Subject: KS

Hi guys,

    I was thin

@@
 \newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
+\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
+\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{blue}{Andy says: #1}\end{minipage}}}
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
@@
 in general in a world with limited resources, when we allow infinite
-precision, their validity is recovered.  However, we are able to use
-the interval-valued framework to establish bounds on the validity of
+precision, their validity is recovered. \andy{<reverse this?> are valid in the
+context of infinite precision, they fail to hold in general in a world with
+limited resourses.} Here we employ an
+interval-valued framework to establish bounds on the validity of
 those theorems in realistic experimental environments. In this way,
@@
 uncertainties of finite precision and imperfections in the quantum
-measurement process.  In particular, we are able to quantify the concept of
-imperfect quantum measurement and its impact on the interpretation of
+measurement process.  In particular, we are able to suggest a way to quantify
+the concept of imperfect quantum measurement and its impact on the interpretation of
 the Kochen-Specker and Gleason theorems and their implications for the
@@
 % }
-%% \yutsung{Still not comfortable about the current statement...}
+\yutsung{Rewrite to match the interpretation of the Kochen-Specker section.}
 These results provide a new insight into the Meyer-Mermin debate by
@@
 application of the Born rule determining the probability of a given
-measurement outcome~\citep{Born1983,peres1995quantum,544199}.  Here,
+measurement outcome~\citep{Born1983,Mermin2007,Jaeger2007}.  Here,
 Gleason's theorem establishes that there is no alternative to the Born
@@
 under which the Kochen-Specker theorem applies.  This provides a way
-not only of resolving the Meyer-Mermin debate, but also revealing of a
+of not only resolving the Meyer-Mermin debate, but also revealing of a
 precise transition to non-contextuality; these are the results of our
@@
 \sum_{j=1}^{N}
-q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\cite{peres1995quantum,544199,Jaeger2007}.
+q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\citep{Born1983,Mermin2007,Jaeger2007}.
 
@@
 probability of an event $P$ is concentrated in the range $[0.49,0.51]$
-instead of being precisely 0.5. The spread in this range depends on
+instead of being precisely $0.5$. The spread in this range depends on
 the quantities of resources (time, energy, money, etc.) that are
@@
 is the probability of the event~$P$ as determined by the Born
-rule~\citep{Born1983,Mermin2007}.
+rule~\citep{Born1983,Mermin2007,Jaeger2007}.
 
@@
   \imposs,\necess\right\}$:
-\begin{equation}
+\[
 \bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
@@
 \end{cases}
-\end{equation}
+\]
 However, since we know that 0-deterministic QIVPMs do not exist, the
@@
 from a state $\rho$ according to the Born
-rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.  According
+rule~\citep{Born1983,Mermin2007,Jaeger2007}.  According
 to Gleason's
@@
 distance between (pure or mixed) states.  The norm of a pure
-state~$\ket{\psi}$ is defined as usual
+state $\rho=\proj{\psi}$ is defined as usual
 $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
@@
 norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
-Then, a version of Gleason's theorem can be stated as follows.
+Then, a finite-precision extension of Gleason's theorem can be stated as
+follows.
 
@@
 f\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$ for any
-one-dimensional projector $\proj{\psi}$. Since the maximum length of
+one-dimensional projector $P=\proj{\psi}$. Since the maximum length of
 the intervals in $\mathscr{I}$ is $\alpha$, it is also the upper bound
@@
 
-The previous theorem generalizes Gleason's theorem in the sense that
-it accounts for a larger class of probability measures which includes
+Previous theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
+theorem in the sense that it accounts for a larger class of probability measures which includes
 the conventional one as a limit. The theorem is however ``special'' in
@@
 A blurring function is called \emph{ultramodular} if it satisfies
-certain properties.
+the following properties.
 
@@
 defines a valid QIVPM. Conversely, if for every quantum probability
-measure $\mu$, it is the case that $f \circ \mu$ is a QIVPM, then $f$
-is an ultramodular function. Formally, we have the following result.
+measure $\mu$, it is the case that $f \circ \mu$ is a QIVPM, then blurring
+function~$f$ is an ultramodular function. Formally, we have the following
+result.
 
@@
 any ultramodular function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$,
-either $\mathscr{I}=\mathscr{I}_{0}$ or $\mathscr{I}$ contains uncountably
-many intervals.\end{thm}
+either $\mathscr{I}=\mathscr{I}_{0}$ in Eq.~(\ref{eq:3-value-intervals}) or
+$\mathscr{I}$ contains uncountably many intervals.\end{thm}
 
@@
 the resources and precision of the particular experiment. 
-
+\gerardo{We need to explain physically what it means?}
 % The essential reason for getting an uncountable number of intervals is

### 2017-11-06 prop_letter.tex
prop_letter.tex Fixing typos...

@@
 \newtheorem{definition}{Definition}
-\newtheorem*{example*}{Example}
 \newtheorem{condition}[assumption]{Condition}
@@
 context of infinite precision, they fail to hold in general in a world with
-limited resourses.} Here we employ an
+limited resources.} Here we employ an
 interval-valued framework to establish bounds on the validity of
@@
 precise transition to non-contextuality; these are the results of our
-Thm~\ref{cor:Kochen-Specker-IVPM}.  In Sec.~\ref{sec:Gleason}, we
+Thm.~\ref{cor:Kochen-Specker-IVPM}.  In Sec.~\ref{sec:Gleason}, we
 study Gleason's theorem in the context of imprecise measurements,
@@
 space, and verify that there are no states that are consistent with it
-on all possible events. Assume a Hilbert space of dimention $d=3$ with
+on all possible events. Assume a Hilbert space of dimension $d=3$ with
 orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let

### 2017-11-06 prop_iop.tex
From: Tai, Yu-Tsung Sent: Friday, November 03, 2017 0:29 To: 'Gerardo Ortiz' <ortizg@indiana.edu>; Amr Sabry <sabry@indiana.edu>; Andrew J. Hanson <hansona@indiana.edu> Subject: RE: KS
Merged suggestions into the texts… 

Best regards,
Tai, Yu-Tsung (戴淯琮)
PhD Candidate in Mathematics & Computer Science Indiana University,
Bloomington

-----Original Message-----
From: Gerardo Ortiz [mailto:ortizg@indiana.edu]
Sent: Thursday, November 02, 2017 17:53
To: Tai, Yu-Tsung <yuttai@imail.iu.edu>; Amr Sabry <sabry@indiana.edu>;
Andrew J. Hanson <hansona@indiana.edu>
Subject: KS

Hi guys,

    I was thin

@@
 
-\begin{proof}To prove the theorem, we first need to construct a QIVPM,
-and then verify that no states consistent with it on all projectors.
-Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2},\ldots,\ket{d-1}\right\} $,
-let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
+\begin{proof}To prove this theorem, we need to construct a QIVPM
+on some Hilbert space, and verify that there are no states that are
+consistent with it on all possible events. Assume a Hilbert space
+of dimension~$d$ with orthonormal basis $\left\{ \ket{0},\ket{1},\ldots,\ket{d-1}\right\} $
 and $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $.
+For $i=1,\ldots,d-1$, let $\ket{i'}=\left(\ket{0}+\ket{i}\right)/\sqrt{2}$.
+The inner product of two distinguish states $\ket{i'}\ne\ket{j'}$
+is $\ip{i'}{j'}=\frac{1}{4}\ne0$. Also, the inner product $\ip{i'}{0}=1/\sqrt{2}\ne0$.
+Hence,
+
 Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
@@
 \end{itemize}
-Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
-empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+Next we will prove by contradiction that $\coreBorn\left(\bar{\mu},\events\right)$
+is the empty set. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
 where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
@@
 which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all $j$. The last equation never holds proving the theorem.\end{proof}
+for all~$j$. The last equation never holds proving the theorem.\end{proof}
 
@@
 for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
-However, the quantum interval-valued probability measure in example~\ref{ex:three-dimensional-three-value}
+However, the quantum interval-valued probability measure in theorem~\ref{thm:Non-extensible-of-Gleason's}
 is Dempster-Shafer and has an empty core. In summary, it is unlikely
@@
 have more idea about the left-hand side. This idea can be applied
-to example~\ref{ex:three-dimensional-three-value}, and the following
+to theorem~\ref{thm:Non-extensible-of-Gleason's}, and the following
 are three of all possibilities:
@@
 the laboratory. Suppose Wigner has three friends: E, P, and R in the
-laboratory. E, P, and R measure the spin-1 system described in example~\ref{ex:three-dimensional-three-value}.
+laboratory. E, P, and R measure the spin-1 system described in theorem~\ref{thm:Non-extensible-of-Gleason's}.
 After the experiment, E tells Wigner $\proj{0}$ never happened, P
@@
 and the combined belief might be the quantum interval-valued probability
-measure in example~\ref{ex:three-dimensional-three-value} which
+measure in theorem~\ref{thm:Non-extensible-of-Gleason's} which
 has an empty core.
@@
 
-Although quantum IVPMs in example~\ref{ex:three-dimensional-three-value}
+Although quantum IVPMs in theorem~\ref{thm:Non-extensible-of-Gleason's}
 and \ref{ex:three-dimensional-5-value} have empty cores, we might
 still think that the probability measure~$\bar{\mu}$ is induced
-by some states. In example~\ref{ex:three-dimensional-three-value},
+by some states. In theorem~\ref{thm:Non-extensible-of-Gleason's},
 the probability measure~$\bar{\mu}$ might be induced by the state
@@
 with $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)=\imposs$.
-Actually, $\bar{f}$ has an empty core, and this is the case for example~\ref{ex:three-dimensional-three-value}. 
+Actually, $\bar{f}$ has an empty core, and this is the case for theorem~\ref{thm:Non-extensible-of-Gleason's}. 
 \end{enumerate}

### 2017-11-07 prop_iop.tex
prop_iop.tex \subsection{Convexity and Core} Updating...

@@
 For $i=1,\ldots,d-1$, let $\ket{i'}=\left(\ket{0}+\ket{i}\right)/\sqrt{2}$.
-The inner product of two distinguish states $\ket{i'}\ne\ket{j'}$
-is $\ip{i'}{j'}=\frac{1}{4}\ne0$. Also, the inner product $\ip{i'}{0}=1/\sqrt{2}\ne0$.
-Hence,
-
 Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
@@
 \addlinespace
-$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
+$\mathbb{0}$, $\proj{0}$, $\proj{i'}$ & $\imposs$\tabularnewline\addlinespace
 \midrule 
 \addlinespace
-$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
-$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{i'}$ & $\necess$\tabularnewline\addlinespace
 \midrule 
@@
 \end{figure}
+The inner product of two distinguish states $\ket{i'}\ne\ket{j'}$
+is $\ip{i'}{j'}=\frac{1}{4}\ne0$. Also, the inner product $\ip{i'}{0}=1/\sqrt{2}\ne0$.
+Hence, a set of projections $\mathcal{S}=\left\{ \proj{0}\right\} \cup\set{}$.
 To verify $\bar{\mu}$ be a convex QIVPM, it is sufficient to verify

### 2017-11-07 prop_iop.tex
prop_iop.tex \subsection{Convexity and Core} Updating...

@@
 \begin{proof}To prove this theorem, we need to construct a QIVPM
-on some Hilbert space, and verify that there are no states that are
+on the Hilbert space, and verify that there are no states that are
 consistent with it on all possible events. Assume a Hilbert space
@@
 For $i=1,\ldots,d-1$, let $\ket{i'}=\left(\ket{0}+\ket{i}\right)/\sqrt{2}$.
-Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
-defined in Table~\ref{tab:non-Born-QIVPM}
-\begin{table}
-\caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
-on a Hilbert space of dimension~$d\ge3$. The projectors mapping
-to the same interval are listed in the column labeled by $P$ and
-separated by commas.}
-\centering{}%
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$, $\proj{0}$, $\proj{i'}$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{i'}$ & $\necess$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-All other projectors & $\unknown$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
+Given two distinguish states $\ket{i'}\ne\ket{j'}$, since the inner
+products $\ip{i'}{j'}$ and $\ip{i'}{0}$ are both non-zero, all projectors
+in $\mathcal{S}=\left\{ \proj{0}\right\} \cup\set{\proj{i'}}{i=1,\ldots,d-1}$
+are not commuting. Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+defined by 
+\begin{equation} 
+\bar{\mu}\left(P\right)=\cases{ 
+\imposs\,, & if $P=\mathbb{0}$ or $P\in\mathcal{S}$ ;\\ 
+\necess\,, & if $P=\mathbb{1}$ or $\mathbb{1}-P\in\mathcal{S}$ ;\\ 
+\unknown\,, & otherwise. 
+}\label{eq:non-Born-QIVPM} \end{equation}
 The situation when $d=3$ is illustrated in figure~\ref{fig:three-dimensional-3-value-2}.
@@
 plotted in $\mathbb{R}^{3}$. The red, green, and blue vectors are
-$\ket{0}$, $\ket{\ps}$, and $\ket{\ps'}$ respectively. }
+$\ket{0}$, $\ket{1'}$, and $\ket{2'}$ respectively. }
 \end{figure}
-The inner product of two distinguish states $\ket{i'}\ne\ket{j'}$
-is $\ip{i'}{j'}=\frac{1}{4}\ne0$. Also, the inner product $\ip{i'}{0}=1/\sqrt{2}\ne0$.
-Hence, a set of projections $\mathcal{S}=\left\{ \proj{0}\right\} \cup\set{}$.
 To verify $\bar{\mu}$ be a convex QIVPM, it is sufficient to verify
@@
 is true when when $P_{0}=\mathbb{1}$.
-\item When $P_{0}=\proj{0}$, if $P_{1}=\proj{0}+P_{2}$, then equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
+\item When $P_{0}=\proj{\psi}\in\mathcal{S}$, if $P_{1}=\proj{\psi}+P_{2}$,
+then equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
 holds by lemma~\ref{lemma:quantum-convex-condition-lemma}. Otherwise,
@@
 \begin{itemize}
-\item When $P_{1}=\mathbb{1}-\proj{0}$, we have
+\item When $P_{1}=\mathbb{1}-\proj{\psi}$, we have
 \begin{equation}\eqalign{ 
  & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\bar{\mu}\left(\mathbb{1}\right)+\bar{\mu}\left(\mathbb{0}\right)\\
-={} & \bar{\mu}\left(\mathbb{1}-\proj{0}\right)+\bar{\mu}\left(\proj{0}\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
+={} & \necess+\imposs=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
 }\end{equation}
-\item When $P_{1}\ne\mathbb{1}-\proj{0}$, we have
+\item When $P_{1}\ne\mathbb{1}-\proj{\psi}$, neither $P_{1}\in\mathcal{S}$
+nor $\mathbb{1}-P_{1}\in\mathcal{S}$ because all projectors in $\mathcal{S}$
+are not commuting. Hence,
 \begin{equation}
@@
 Therefore, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-holds when $P_{0}=\proj{0}$. Similarly, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-holds when $P_{0}=\proj{\ps}$ or $P_{0}=\proj{\ps'}$. By lemma~\ref{lemma:quantum-convex-condition-lemma},
+holds when $P_{0}=\proj{\psi}\in\mathcal{S}$. By lemma~\ref{lemma:quantum-convex-condition-lemma},
 equation~(\ref{eq:QuantumInterval-valuedProbability-Convex}) is
-also true when when $P_{0}=\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$,
-or $\mathbb{1}-\proj{\ps'}$.
+also true when when $P_{0}=\mathbb{1}-\proj{\psi}$, where $\proj{\psi}\in\mathcal{S}$.
 \item If neither the above two cases holds, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\unknown+\unknown=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
@@
 where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
-for any~$P$, the state~$\rho$ must satisfy: 
-\begin{equation}
-\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
-\end{equation}
-which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all~$j$. The last equation never holds proving the theorem.\end{proof}
+for any~$P$, the state~$\rho$ must satisfy $\mu_{\rho}^{\mathrm{B}}(P)$
+for all $P\in\mathcal{S}$. This implies 
+\begin{equation}
+\ip{\phi_{j}}{0}=\ip{\phi_{j}}{i'}=0\label{eq:probability-zero-on-states}
+\end{equation}
+for all $i=1,\ldots d-1$ and for all $j=1,\ldots N$. Eq.~(\ref{eq:probability-zero-on-states})
+never holds proving the theorem.\end{proof}
 

### 2017-11-08 prop_iop.tex
prop_iop.pdf Updating...

@@
 consistent with it on all possible events. Assume a Hilbert space
-of dimension~$d$ with orthonormal basis $\left\{ \ket{0},\ket{1},\ldots,\ket{d-1}\right\} $
+of dimension $d\ge3$ with orthonormal basis $\left\{ \ket{0},\ket{1},\ldots,\ket{d-1}\right\} $
 and $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $.
@@
 in $\mathcal{S}=\left\{ \proj{0}\right\} \cup\set{\proj{i'}}{i=1,\ldots,d-1}$
-are not commuting. Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+are not commuting with each other. Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
 defined by 
@@
 To verify $\bar{\mu}$ be a convex QIVPM, it is sufficient to verify
-equation~(\ref{eq:QuantumInterval-valuedProbability-Convex}). There
-are several cases:
+the convexity condition, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex}).
+There are several cases:
 \begin{itemize}
@@
 
-\begin{lemma}\label{lemma:classical-quantum-convex}Given a quantum
-IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
-are all convex for any orthonormal basis~$\Omega$, then $\bar{\mu}$
-is convex.\end{lemma}
-
-\begin{proof} Pick two commuting events~$P_{0},P_{1}\in\events$.
-Since they are commuting, they can be diagonalized by a common orthonormal
-basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$. Since they
-are projectors, the eigenvalues of them are $0$ or $1$ so that we
-can express them as $P_{0}=\sum_{\ket{j}\in E_{0}}\proj{j}$ and $P_{1}=\sum_{\ket{j}\in E_{1}}\proj{j}$,
-where $E_{0},E_{1}\subseteq\Omega$. Then, 
-\begin{equation}\eqalign{  
-& \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)= \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\\ 
-\subseteq & \bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)= \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,. 
-}\end{equation}
-\end{proof}
-
-\begin{lemma}\label{lemma:classical-convex-condition-lemma}Given
-a classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$,
+\begin{thm}\label{lemma:classical-convex-condition-lemma}Given a
+classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$,
 the following statements are true:
@@
 \end{enumerate}
-\end{lemma}
+\end{thm}
 
@@
 \item 
-\begin{equation}\eqalign{ 
- & \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\\
-\Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\cap \overline{E_{1}}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\cup \overline{E_{1}}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{1}}\right)\right)\\
-\Rightarrow & 2-\left[\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap \overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup \overline{E_{1}}\right)\right]\subseteq2-\left[\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)\right]\\
-\Rightarrow & \bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap \overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup \overline{E_{1}}\right)\subseteq\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)\,.
-}\end{equation}
+\begin{eqnarray*}
+ &  & \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\\
+ & \Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\cap\overline{E_{1}}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\cup\overline{E_{1}}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{1}}\right)\right)\\
+ & \Rightarrow & 2-\left[\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap\overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup\overline{E_{1}}\right)\right]\subseteq2-\left[\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)\right]\\
+ & \Rightarrow & \bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap\overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup\overline{E_{1}}\right)\subseteq\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)\,.
+\end{eqnarray*}
 \end{enumerate}
@@
 By equation~(\ref{eq:classical-include}), we have $\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup\overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap\overline{E_{1}}\right)\subseteq\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)$.
-Then, lemma~\ref{lemma:classical-convex-condition-lemma} proves
+Then, theorem~\ref{lemma:classical-convex-condition-lemma} proves
 equation~(\ref{eq:classical-convex}).
 \item When $E_{0}\subseteq E_{1}$ or $E_{1}\subseteq E_{0}$, equation~(\ref{eq:classical-convex})
-is also followed by lemma~\ref{lemma:classical-convex-condition-lemma}.
+is also followed by theorem~\ref{lemma:classical-convex-condition-lemma}.
 \end{enumerate}
@@
 \begin{lemma}\label{lemma:quantum-convex-condition-lemma}Given a
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, the following statements
+QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, the following statements
 are true:
@@
 \item If $P_{1}=P_{0}+P_{2}$, then $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
-\item If $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
+\item Given commuting $P_{0}$ and $P_{1}\in\events$, if $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
 then $\bar{\mu}\left(\overline{P_{0}}\vee\overline{P_{1}}\right)+\bar{\mu}\left(\overline{P_{0}}\overline{P_{1}}\right)\subseteq\bar{\mu}\left(\overline{P_{0}}\right)+\bar{\mu}\left(\overline{P_{1}}\right)$,
@@
 
-\begin{proof}The direct consequence of lemma~\ref{lemma:classical-convex-condition-lemma}
+\begin{proof}The direct consequence of theorem~\ref{lemma:classical-convex-condition-lemma}
 and theorem~\ref{thm:sub-event-space}.\end{proof}
@@
 \begin{thm}\label{thm:convex-3}Given a Hilbert space~$\Hilb$ of
-dimension~$3$, every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+dimension~$3$, every quantum IVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
 is convex.\end{thm}
 
-\begin{proof}The direct consequence of lemma~\ref{lemma:classical-quantum-convex}
-and lemma~\ref{lemma:classical-3-elements}. \end{proof}
+\begin{proof}The direct consequence of lemma~\ref{lemma:classical-3-elements}
+and theorem~\ref{thm:sub-event-space}. \end{proof}
 

### 2017-11-08 prop_iop.tex
prop_iop.tex \subsection{Convexity and Core} Updating...

@@
 lemma also implies equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-is true when when $P_{0}=\mathbb{1}$.
+when $P_{0}=\mathbb{1}$.
 \item When $P_{0}=\proj{\psi}\in\mathcal{S}$, if $P_{1}=\proj{\psi}+P_{2}$,
@@
 nor $\mathbb{1}-P_{1}\in\mathcal{S}$ because all projectors in $\mathcal{S}$
-are not commuting. Hence,
-\begin{equation}
-\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\unknown+\imposs=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
-\end{equation}
+are not commuting. Hence,$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\unknown+\imposs=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
 \end{itemize}
 Therefore, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
-holds when $P_{0}=\proj{\psi}\in\mathcal{S}$. By lemma~\ref{lemma:quantum-convex-condition-lemma},
-equation~(\ref{eq:QuantumInterval-valuedProbability-Convex}) is
-also true when when $P_{0}=\mathbb{1}-\proj{\psi}$, where $\proj{\psi}\in\mathcal{S}$.
-\item If neither the above two cases holds, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\unknown+\unknown=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
+holds when $P_{0}=\proj{\psi}\in\mathcal{S}$.
+\item When $P_{0}=\mathbb{1}-\proj{\psi}$ for $\proj{\psi}\in\mathcal{S}$,
+equation~(\ref{eq:QuantumInterval-valuedProbability-Convex}) follows
+from the previous case with lemma~\ref{lemma:quantum-convex-condition-lemma}.
+\item If neither the above cases holds, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\unknown+\unknown=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
 \end{itemize}
@@
 where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
-for any~$P$, the state~$\rho$ must satisfy $\mu_{\rho}^{\mathrm{B}}(P)$
+for any~$P$, the state~$\rho$ must satisfy $\mu_{\rho}^{\mathrm{B}}(P)=0$
 for all $P\in\mathcal{S}$. This implies 

### 2017-11-09 prop_letter.tex
prop_letter.tex \section{The Kochen-Specker Theorem and Contextuality} Updating...

@@
 invalidating the Kochen-Specker theorem.
+
+For two-dimensional Hilbert space, there exists a non-contextual hidden
+variable model~\cite{kochenspecker1967,BellBook1987}. This non-contextual
+model can be represented as a quantum probability measure $\mu:\events\rightarrow[0,1]$
+satisfying an extra condition, either $\mu\left(P\right)=0$ or~$1$,
+but not any intermediate values. A quantum probability measure of
+this kind, $\mu$, is equivalent to a 0-deterministic QIVPM $\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
+since the latter can be constructed according to the following way:
+\begin{equation}
+\bar{\mu}\left(P\right)=\begin{cases}
+\imposs\,, & \textrm{ if }\mu\left(P\right)=0\:;\\
+\necess\,, & \textrm{ if }\mu\left(P\right)=1\:,
+\end{cases}
+\end{equation}
+and vice versa. Moreover, the QIVPM~$\bar{\mu}$ is also $\delta$-deterministic
+for any $\delta\in\left[0,1\right]$ since $\imposs\subseteq\left[0,\delta\right]$
+and $\necess\subseteq\left[1-\delta,1\right]$. Conversely, as shown
+in the proof of Thm.~\ref{cor:Kochen-Specker-IVPM}, any $\delta$-deterministic
+QIVPM for $\delta<\frac{1}{3}$ induces a 0-deterministic QIVPM so
+as a non-contextual hidden variable model. In summary, the existence
+of $\delta$-deterministic QIVPM for $\delta<\frac{1}{3}$ is equivalent
+to the existence of a non-contextual hidden variable model. Both of
+them exist for $d=2$, while none of them exist for $d\ge3$.
 

### 2017-11-09 prop_letter.tex
prop_letter.tex \section{The Kochen-Specker Theorem and Contextuality} Updating...
nov 9

--- 2017-11-06 prop_letter.tex
@@
   We present a mathematical framework based on quantum interval-valued
-probability measures to study the effect of experimental imperfections
-and finite precision measurements on defining aspects of quantum
-mechanics such as contextuality and the Born rule. While foundational
-results such as the Kochen-Specker and Gleason theorems fail to hold
-in general in a world with limited resources, when we allow infinite
-precision, their validity is recovered. \andy{<reverse this?> are valid in the
-context of infinite precision, they fail to hold in general in a world with
-limited resources.} Here we employ an
+  probability measures to study the effect of experimental
+  imperfections and finite precision measurements on defining aspects
+  of quantum mechanics such as contextuality and the Born rule. While
+  foundational results such as the Kochen-Specker and Gleason theorems
+  are valid in the context of infinite precision, they fail to hold in
+  general in a world with limited resources. Here we employ an
   interval-valued framework to establish bounds on the validity of
@@
   within our theory, but we can also suggest a possible resolution of
-the Meyer-Mermin debate on the impact of finite-precision measurement
-on the Kochen-Specker theorem.
+  the Meyer-Mermin debate on the impact of finite-precision
+  measurement on the Kochen-Specker theorem.
 \end{abstract}
@@
 about contextuality, asserting that in a Hilbert space of dimension
-$d \ge 3$, it is impossible to associate definite probabilities,
+$d \ge 3$, it is impossible to associate determinate probabilities,
 $\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
@@
 $\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
-definite probabilities $0$ or~$1$ to the measurement outcomes when the
-Hilbert space is defined over the field of rational numbers, therefore
-nullifying the theorem~\citep{PhysRevLett.83.3751}.  However, Mermin
-then argued that measurement outcomes must depend smoothly on slight
-changes in the experimental configuration, leading him to assert that
-the impact of Meyer's negative result is
-``unsupportable'' on physical grounds~\citep{Mermin1999}.  The debate on whether
-contextuality is consistent with experimental outcomes continues to be
-an active topic of
+determinate probabilities $0$ or~$1$ to the measurement outcomes when
+the Hilbert space is defined over the field of rational numbers,
+therefore nullifying the theorem~\citep{PhysRevLett.83.3751}.
+However, Mermin then argued that measurement outcomes must depend
+smoothly on slight changes in the experimental configuration, leading
+him to assert that the impact of Meyer's negative result is
+``unsupportable'' on physical grounds~\citep{Mermin1999}.  The debate
+on whether contextuality is consistent with experimental outcomes
+continues to be an active topic of
 research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
@@
 parallel in its consequences to, say, a phase transition, to
-\emph{non-contextuality}; that is, suddenly a quantum system can be
-simulated by a non-contextual hidden variable theory.
+\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
+%% simulated by a non-contextual hidden variable theory.
 %% , turning the
@@
 % }
-\yutsung{Rewrite to match the interpretation of the Kochen-Specker section.}
 These results provide a new insight into the Meyer-Mermin debate by
@@
 
-\amr{
-Something like this: We have quantified one aspect of imprecision in
-QM (originally noted by Heisenberg -- cite microscope paper). This
-does not account for all the probabilistic nature of QM,
-however. Merge with original sentence: The significance of this
-observation is that the uncertainty in the intervals is, in contrast
-to the classical case, \emph{a fundamental part of quantum
-  theory}. There are in fact two sources of uncertainty: one due to
-the finite measurement resources and one due to complementarity, which
-requires every quantum framework to be truly probabilistic.
-}
+As is the case for conventional, infinitely-precise, quantum
+probability measures, the theorem is only applicable to dimensions
+$d \geq 3$. Indeed when the Hilbert space has dimension 2, it is
+straightforward to construct a 0-deterministic QIVPM as
+follows. Consider a non-contextual hidden variable model (e.g., as
+proposed by Bell or
+Kochen-Specker~\cite{BELL_1966,kochenspecker1967}). Such a model
+assigns definite values to all observables at all times, and hence
+assigns a \emph{determinate} probability (0 or 1) to each event. Such
+a probability measure directly induces a 0-deterministic QIVPM by
+changing 0 to $\imposs$ and 1 to $\necess$.
+
+% In conventional quantum mechanics, there exists a non-contextual 
+% hidden variable model for the special case of a two-dimensional 
+% Hilbert space~\cite{BELL_1966,kochenspecker1967}. This non-contextual
+% model can be modeled by a quantum probability measure 
+% $\mu:\events\rightarrow[0,1]$ which maps every event to either 0 or 
+% 1. Such a quantum probability measure, $\mu$, is clearly equivalent to
+% a 0-deterministic QIVPM
+% $\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $ and
+% hence a $\delta$-deterministic QIVPM for any
+% $\delta\in\left[0,1\right]$.
+% % \begin{equation}
+% % \bar{\mu}\left(P\right)=\begin{cases}
+% % \imposs\,, & \textrm{ if }\mu\left(P\right)=0\:;\\
+% % \necess\,, & \textrm{ if }\mu\left(P\right)=1\:,
+% % \end{cases}
+% % \end{equation}
+% % and vice versa. 
+% %% Moreover, the QIVPM~$\bar{\mu}$ is also $\delta$-deterministic
+% %% for any $\delta\in\left[0,1\right]$ since $\imposs\subseteq\left[0,\delta\right]$
+% %% and $\necess\subseteq\left[1-\delta,1\right]$. 
+% Conversely, as shown in the proof of
+% Thm.~\ref{cor:Kochen-Specker-IVPM}, any $\delta$-deterministic QIVPM
+% for $\delta<\frac{1}{3}$ induces a 0-deterministic QIVPM.
+
+%  so as a
+% non-contextual hidden variable model. In summary, the existence of
+% $\delta$-deterministic QIVPM for $\delta<\frac{1}{3}$ is equivalent to
+% the existence of a non-contextual hidden variable model. Both of them
+% exist for $d=2$, while none of them exist for $d\ge3$.
+
+We have quantified one aspect of uncertainty in quantum
+mechanics---due to the imprecise nature of devices---which is a novel
+addition to the theory of measurement. Indeed, as Heisenberg
+emphasized in his famous microscope
+example~\cite{Heisenberg1927,Heisenberg1983}, the conventional theory
+of measurement states that it is impossible to precisely measure any
+property of a system without disturbing it somewhat. There are
+fundamental limits to what one can measure and these limits are
+typically attributed to complementarity. Our imprecision is an
+\emph{additional} indeterminacy to the inherent probabilistic nature
+of quantum mechanics.
+
+% The significance of this observation is that the uncertainty in the
+% intervals is, in contrast to the classical case, \emph{a fundamental
+%   part of quantum theory}. There are in fact two sources of
+% uncertainty: one due to the finite measurement resources and one due
+% to complementarity, which requires every quantum framework to be truly
+% probabilistic.
+
+% We have quantified one aspect of imprecision in quantum mechanics
+% which is due to the imprecise nature of devices. There is however
+% another
+
+% QM (originally noted by Heisenberg -- cite microscope paper).
+
+% Something like this: We have quantified one aspect of imprecision in 
+% QM (originally noted by Heisenberg -- cite microscope paper). This
+% does not account for all the probabilistic nature of QM,
+% however. Merge with original sentence: The significance of this
+% observation is that the uncertainty in the intervals is, in contrast
+% to the classical case, \emph{a fundamental part of quantum
+%   theory}. There are in fact two sources of uncertainty: one due to
+% the finite measurement resources and one due to complementarity, which
+% requires every quantum framework to be truly probabilistic.
 

### 2017-11-10 prop_letter.tex
prop_letter.tex Fix translated item with bibTeX...

@@
 application of the Born rule determining the probability of a given
-measurement outcome~\citep{Born1983,Mermin2007,Jaeger2007}.  Here,
+measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.  Here,
 Gleason's theorem establishes that there is no alternative to the Born
@@
 uncertain
-events~\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the
+events~\cite{Kolmogorov1950bibTeX,544199,Griffiths2003,Grabisch2016}. In the
 quantum case, the events of interest are specified by \emph{projection
@@
 \sum_{j=1}^{N}
-q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\citep{Born1983,Mermin2007,Jaeger2007}.
+q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
 
@@
 is the probability of the event~$P$ as determined by the Born
-rule~\citep{Born1983,Mermin2007,Jaeger2007}.
+rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
 
@@
 emphasized in his famous microscope
-example~\cite{Heisenberg1927,Heisenberg1983}, the conventional theory
+example~\cite{Heisenberg1983apsrev4}, the conventional theory
 of measurement states that it is impossible to precisely measure any
@@
 from a state $\rho$ according to the Born
-rule~\citep{Born1983,Mermin2007,Jaeger2007}.  According
+rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.  According
 to Gleason's

### 2017-11-10 prop_letter.tex
prop_letter.tex \newcommand{\muB}{\ensuremath{\mu^{B}}} Defined to satisfy the different requirement for different journals...

@@
 \newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{\mathrm{R{#1}}}}}
+\newcommand{\muB}{\ensuremath{\mu^{B}}}
 
@@
 state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
-$\mu_{\phi}^{\mathrm{B}}$ defined as
-$\mu_{\phi}^{\mathrm{B}}(P)=\melem{\phi}{P}{\phi}$. The situation
+$\muB_{\phi}$ defined as
+$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
 generalizes to mixed states
@@
 $\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
-induces a probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as
-$\mu_{\rho}^{\mathrm{B}}\left(P\right) = \Tr\left(\rho P\right) =
+induces a probability measure $\muB_{\rho}$ defined as
+$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
 \sum_{j=1}^{N}
-q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
+q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
 
@@
 \begin{equation}
-\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
-\end{equation}
-where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
+\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
+\end{equation}
+where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
 is the probability of the event~$P$ as determined by the Born
@@
 \label{eq:hbar}
-\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in \events',~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}.
+\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in \events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)}.
 \end{equation}
@@
 \expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
-\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
-\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,. \label{eq:quantum-interval-expectation-core}
+\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
+\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,. \label{eq:quantum-interval-expectation-core}
 \end{equation}
@@
 $\coreBorn\left(\bar{\mu},\events'\right)$ will be
-$\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point, thus
+$\muB_{\rho}$ and the interval collapses to a point, thus
 reducing the definition to that of
@@
 % the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
-% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
+% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\muB_{\proj{\ps}}$.
 % Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
@@
 with this QIVPM on all the projectors in $\Omega$, we have by
-Eq.~(\ref{eq:hbar}) that $\mu_{\rho}^{\mathrm{B}}$ must also map
+Eq.~(\ref{eq:hbar}) that $\muB_{\rho}$ must also map
 exactly one of the projectors in $\Omega$ to 1 and all others to 0. If
@@
 Eq.~(\ref{eq:quantum-expectation}), its expectation value relative to
-$\mu_{\rho}^{\mathrm{B}}$ is the eigenvalue $\lambda$ whose projector
+$\muB_{\rho}$ is the eigenvalue $\lambda$ whose projector
 is mapped to 1. It therefore follows, by
@@
 % QIVPM~$\bar{\mu}$. During the computation, whenever $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
-% $\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)$ and $\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)$
+% $\muB_{\rho}\left(P_{1}\right)$ and $\muB_{\rho}\left(P_{2}\right)$
 % must be the value list in the table. Therefore, $\expval{\mathbf{O}}_{\bar{\mu}}$
@@
 % \hline 
-% Observable~$\mathbf{O}$ & Spectral Decomposition~$1\cdot P_{1}-1\cdot P_{2}$ & $\bar{\mu}\left(P_{1}\right)$ & $\bar{\mu}\left(P_{2}\right)$ & $\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)$ & $\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)$ & $\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}$ & $\expval{\mathbf{O}}_{\bar{\mu}}$\tabularnewline
+% Observable~$\mathbf{O}$ & Spectral Decomposition~$1\cdot P_{1}-1\cdot P_{2}$ & $\bar{\mu}\left(P_{1}\right)$ & $\bar{\mu}\left(P_{2}\right)$ & $\muB_{\rho}\left(P_{1}\right)$ & $\muB_{\rho}\left(P_{2}\right)$ & $\expval{\mathbf{O}}_{\muB_{\rho}}$ & $\expval{\mathbf{O}}_{\bar{\mu}}$\tabularnewline
 % \hline 
@@
 where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
-$\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$ for any~$P$, the
+$\muB_{\rho}(P)\in\bar{\mu}(P)$ for any~$P$, the
 state~$\rho$ must satisfy:
 \begin{equation}
-\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
+\muB_{\rho}(\proj{0})=\muB_{\rho}(\proj{\ps})=\muB_{\rho}(\proj{\ps'})=0\,,
 \end{equation}
@@
   Theorem]\label{thm:Finite-precision-Gleason}Let $f$ be a blurring
-  function and let $f \circ \mu_{\rho}^{\mathrm{B}}$ be a QIVPM, where
-  $\mu_{\rho}^{\mathrm{B}}$ is the probability measure induced by the
+  function and let $f \circ \muB_{\rho}$ be a QIVPM, where
+  $\muB_{\rho}$ is the probability measure induced by the
   Born rule for a given state $\rho$. Let $\alpha$ be the maximum
   length of intervals in its image. If a state $\rho'$ is consistent
-  with $f\circ\mu_{\rho}^{\mathrm{B}}$ on all events, i.e.,
-  $\rho'\in\coreBorn\left(f\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
+  with $f\circ\muB_{\rho}$ on all events, i.e.,
+  $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
   then the norm of their difference is bounded by $\alpha$, i.e.,
@@
 The proof proceeds as follows. Given a state~$\rho'$ consistent with
-$f\circ\mu_{\rho}^{\mathrm{B}}$, we have
-$\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in
-f\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$ for any
+$f\circ\muB_{\rho}$, we have
+$\muB_{\rho'}\left(\proj{\psi}\right)\in
+f\left(\muB_{\rho}\left(\proj{\psi}\right)\right)$ for any
 one-dimensional projector $P=\proj{\psi}$. Since the maximum length of
@@
 \[
-\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le \alpha\,.
+\left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le \alpha\,.
 \]
@@
 The induced map using the Born rule and blurred by $\ultramodular$,
-$\ultramodular\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$, fails to satisfy
+$\ultramodular\circ\muB_{\rho}$, fails to satisfy
 Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
@@
 done by restricting our previous quantum probability measure
-$\mu_{\rho}^{\mathrm{\mathrm{B}}}$ on a commuting subspace of
+$\muB_{\rho}$ on a commuting subspace of
 event~$\events_{\mathrm{C}}$ generated by $\proj{0}$, $\proj{1}$, $\proj{2}$,
 and $\proj{3}$. The restricted function
-$\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}|_{\events_{\mathrm{C}}}$ is a classical probability
+$\mu=\muB_{\rho}|_{\events_{\mathrm{C}}}$ is a classical probability
 measure, and the induced map $\ultramodular\circ\mu$ fails to be
@@
 % there is always a state consistent with any composite QIVPM
-% $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$.  Moreover, the collection
-% of states consistent with $\ultramodular\circ\mu_{\rho}^{\mathrm{B}}$
+% $\ultramodular\circ\muB_{\rho}$.  Moreover, the collection
+% of states consistent with $\ultramodular\circ\muB_{\rho}$
 % gets closer and closer to~$\rho$ as the intervals get narrower and
@@
 % defined in Table~\ref{tab:I_2} satisfies Eqs.~(\ref{eq:iota-constraints})
-% and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\ultramodular_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
-% and $\ultramodular_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ are both
+% and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\ultramodular_{2}\circ\muB_{\rho_{0}}$
+% and $\ultramodular_{2}\circ\muB_{\rho_{1}}$ are both
 % QIVPMs.
@@
 % \end{table}
-% Given any one-dimensional projector $\proj{\psi}$, we have $\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)=\frac{1}{3}$
-% so that $\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
+% Given any one-dimensional projector $\proj{\psi}$, we have $\muB_{\rho_{0}}\left(\proj{\psi}\right)=\frac{1}{3}$
+% so that $\ultramodular_{2}\left(\muB_{\rho_{0}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
 % On the other hand, 
 % \begin{eqnarray*}
-% \mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right) & = & \tfrac{7}{24}\left|\ip{\psi}{0}\right|^{2}+\tfrac{1}{3}\left|\ip{\psi}{1}\right|^{2}+\tfrac{3}{8}\left|\ip{\psi}{2}\right|^{2}
+% \muB_{\rho_{1}}\left(\proj{\psi}\right) & = & \tfrac{7}{24}\left|\ip{\psi}{0}\right|^{2}+\tfrac{1}{3}\left|\ip{\psi}{1}\right|^{2}+\tfrac{3}{8}\left|\ip{\psi}{2}\right|^{2}
 % \end{eqnarray*}
 % is bounded between $\frac{7}{24}$ and $\frac{3}{8}$. Therefore,
-% $\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\in\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$.
+% $\muB_{\rho_{1}}\left(\proj{\psi}\right)\in\ultramodular_{2}\left(\muB_{\rho_{0}}\left(\proj{\psi}\right)\right)$.
 % According to the complement condition, Eq.~(\ref{eq:complement}), we
 % also have
-% $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\in\ultramodular_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
+% $\muB_{\rho_{1}}\left(P\right)\in\ultramodular_{2}\left(\muB_{\rho_{0}}\left(P\right)\right)$
 % for any two-dimensional projector~$P$. Hence,
-% $\rho_{1}\in\coreBorn\left(\ultramodular_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
+% $\rho_{1}\in\coreBorn\left(\ultramodular_{2}\circ\muB_{\rho_{0}},\events\right)$,
 % and Thm.~\ref{thm:Finite-precision-Gleason} asserts that

### 2017-11-10 prop_letter.tex
prop_letter.tex \newcommand{\eventsC}{\ensuremath{\events_{C}}} Defined to satisfy the different requirement for different journals...

@@
 \newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
-\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
-\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
+\newcommand{\mul}[1][]{\ensuremath{\mu^{L{#1}}}}
+\newcommand{\mur}[1][]{\ensuremath{\mu^{R{#1}}}}
 \setcounter{secnumdepth}{3}
@@
 % Hence, it will not hyphenate too much surrounding words.
-\newcommand{\rmd}{\mathrm{d}}
-\newcommand{\rmi}{\mathrm{i}}
+\newcommand{\rmd}{d}
+\newcommand{\rmi}{i}
 \lineskiplimit=1pt
 \newcommand{\ultramodular}{\mathcal{M}}
-\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{\mathrm{L{#1}}}}}
-\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{\mathrm{R{#1}}}}}
+\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{L{#1}}}}
+\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{R{#1}}}}
 \newcommand{\muB}{\ensuremath{\mu^{B}}}
+\newcommand{\eventsC}{\ensuremath{\events_{C}}}
 
@@
 classical IVPMs when the space of quantum events $\events$ is
-restricted to mutually commuting events $\events_{\mathrm{C}}$, i.e.,
+restricted to mutually commuting events $\eventsC$, i.e.,
 to compatible events that can be measured simultaneously. In
@@
 proof is as follows. Given a subspace of mutually commuting
-events~$\events_{\mathrm{C}}$, we can construct a partial orthonormal
+events~$\eventsC$, we can construct a partial orthonormal
 basis by diagonalization and complete it to a full orthonormal basis
-$\overline{\events_{\mathrm{C}}}$. We then build a bijection between
+$\overline{\eventsC}$. We then build a bijection between
 the QIVPM on the set of projectors associated with this basis and the
@@
   For QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
-  of events~$\events_{\mathrm{C}}\subseteq\events$ commutes, then
-  $\coreBorn\left(\bar{\mu},\events_{\mathrm{C}}\right)\ne\emptyset$.
+  of events~$\eventsC\subseteq\events$ commutes, then
+  $\coreBorn\left(\bar{\mu},\eventsC\right)\ne\emptyset$.
 \end{thm}
@@
 which proves that a classical IVPM always contains at least one state $\rho$
-that is consistent with every event in $\events_{\mathrm{C}}$. In contrast, as we
+that is consistent with every event in $\eventsC$. In contrast, as we
 illustrate in Sec.~\ref{sec:Gleason}, the set of states
@@
 \item \label{enu:iota-mu-CIVPM}The composite
-  function~$\ultramodular\circ\mu:\events_{\mathrm{C}}\rightarrow\mathscr{I}$
+  function~$\ultramodular\circ\mu:\eventsC\rightarrow\mathscr{I}$
   is a classical IVPM for all classical probability
-  measure~$\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$.
+  measure~$\mu:\eventsC\rightarrow\left[0,1\right]$.
 \item \label{enu:iota-mu-QIVPM}The composite
@@
 $\ultramodular$ is not ultramodular, we also want to find a classical
-probability measure $\mu:\events_{\mathrm{C}}\rightarrow\left[0,1\right]$ such
+probability measure $\mu:\eventsC\rightarrow\left[0,1\right]$ such
 that $\ultramodular\circ\mu$ is not a classical IVPM. This can be
@@
 $\muB_{\rho}$ on a commuting subspace of
-event~$\events_{\mathrm{C}}$ generated by $\proj{0}$, $\proj{1}$, $\proj{2}$,
+event~$\eventsC$ generated by $\proj{0}$, $\proj{1}$, $\proj{2}$,
 and $\proj{3}$. The restricted function
-$\mu=\muB_{\rho}|_{\events_{\mathrm{C}}}$ is a classical probability
+$\mu=\muB_{\rho}|_{\eventsC}$ is a classical probability
 measure, and the induced map $\ultramodular\circ\mu$ fails to be

### 2017-11-11 prop_letter.tex
prop_letter.tex Fixing references...

@@
 $P_0P_1=P_1P_0$. In a quantum probability
-space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
+space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
 each event~$P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a

### 2017-11-13 prop_letter.tex
comment fixed

@@
 
-\amr{Rewrite next sentence. Thm 4 assumes infinite
-  precision. Question: what happens with finite precision
-  intervals. Two thoughts: (1) multiple states will match the
-  probab. distribution, (2) for small collections of projectors
-  different states will agree with observations; if one looks at all
-  projectors it may be the case that no state agrees with all.}
-
-\noindent For general QIVPMs mapping to imprecise intervals, we also
-want to seek a simple rule to construct them, and to understand which
-states are consistent with them. However, if measurement intervals are
-too imprecise, the state consistent with the results of measurements
-on some projectors might contradict the state induced by some other
-projectors. Indeed we can formally prove that, in general, there may
-be \emph{no} state consistent with some arbitrary QIVPM.
+As the intervals in the image of a QIVPM become less and less sharp,
+we expect more and more states to be consistent with it. Indeed, in
+the limit, the intervals become \imposs, \necess, and \unknown and
+every state is consistent with an assignment that states that its
+projections are unknown. There is however a subtlety: as shown in the
+theorem below, an arbitrary assignment of intervals to projectors
+might be globally inconsistent.
+
+% \noindent For general QIVPMs mapping to imprecise intervals, we also
+% want to seek a simple rule to construct them, and to understand which
+% states are consistent with them. However, if measurement intervals are
+% too imprecise, the state consistent with the results of measurements
+% on some projectors might contradict the state induced by some other
+% projectors. Indeed we can formally prove that, in general, there may
+% be \emph{no} state consistent with some arbitrary QIVPM.
 

### 2017-11-13 prop_letter.tex
prop.bib @PhdThesis{TaiThesis2018} Added...

@@
 includes only mutually commuting events is presented in detail in the
-long version of this paper~\cite{HOSTunpublished}. The idea of the
+long version of this paper~\cite{TaiThesis2018}. The idea of the
 proof is as follows. Given a subspace of mutually commuting
@@
 This theorem follows directly from our
-correspondence~\cite{HOSTunpublished} and Shapley's
+correspondence~\cite{TaiThesis2018} and Shapley's
 theorem~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
@@
 reducing the definition to that of
-Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
+Eq.~(\ref{eq:quantum-expectation})~\citep{TaiThesis2018}.
 % For example, we can extend one of the fragments of valid probability
@@
 which is used to calculate the expectation value of random variables
-as a weighted average~\citep{HOSTunpublished}.
+as a weighted average~\citep{TaiThesis2018}.
 
@@
 number of occurrences of the interval $[-1,-1]$ in each row and hence
-in the entire table~\citep{HOSTunpublished}. However, looking at the expectation values of the
+in the entire table~\citep{TaiThesis2018}. However, looking at the expectation values of the
 observables in each column, there must be an even number of
 occurrences of the interval $[-1,-1]$ in the first two columns and an
-odd number in the $j=2$ column and hence in the entire table~\citep{HOSTunpublished}. The
+odd number in the $j=2$ column and hence in the entire table~\citep{TaiThesis2018}. The
 contradiction implies the non-existence of the assumed 0-deterministic
@@
 % such that $\bar{\mu}\left(\proj{k_{0}}\right)=\necess$ and $\bar{\mu}\left(\proj{k}\right)=\imposs$
-% for $k\ne k_{0}$~\citep{HOSTunpublished}. Without loss of generality,
+% for $k\ne k_{0}$~\citep{TaiThesis2018}. Without loss of generality,
 % assume $k_{0}=1$, the expectation values can be computed step-by-step
@@
 % $\mu\left(\proj{k}\right)=1$ if and only if
-% $k=k_{0}$~\citep{HOSTunpublished}.  If we denote the product
+% $k=k_{0}$~\citep{TaiThesis2018}.  If we denote the product
 % observables~$\prod_{j=1}^{M}\mathbf{O}_{j}$ as
@@
 implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{HOSTunpublished}. Indeed
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{TaiThesis2018}. Indeed
 when
@@
 Table~\ref{tab:non-Born-QIVPM} can be verified to be a
-QIVPM~\citep{HOSTunpublished}.
+QIVPM~\citep{TaiThesis2018}.
 \begin{table}
@@
 % Eq.~(\ref{eq:iota-add}), then $\ultramodular\circ\mu$ is a
-% QIVPM~\citep{HOSTunpublished}.  For example, consider an orthonormal
+% QIVPM~\citep{TaiThesis2018}.  For example, consider an orthonormal
 % basis $\{\ket{0},\ket{1},\ket{2}\}$, two states
@@
 % defined in Table~\ref{tab:I_2} satisfies Eqs.~(\ref{eq:iota-constraints})
-% and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, $\ultramodular_{2}\circ\muB_{\rho_{0}}$
+% and Eq.~(\ref{eq:iota-add})~\citep{TaiThesis2018}, $\ultramodular_{2}\circ\muB_{\rho_{0}}$
 % and $\ultramodular_{2}\circ\muB_{\rho_{1}}$ are both

### 2017-11-14 prop_letter.tex
prop_letter.tex Re-organize the references...

@@
 Kochen-Specker
-theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.
+theorem~\cite{kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}.
 The Kochen-Specker theorem is in essence a mathematical statement
@@
 physics: the Kochen-Specker
-theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}. Our
+theorem~\cite{kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}. Our
 finite-precision extension of that theorem will suggest a resolution

### 2017-11-16 prop_letter.tex
prop_letter.tex Cite BELL_1966 when discussing K-S theorem...

--- 2017-11-13 prop_letter.tex
@@
 Kochen-Specker
-theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.
+theorem~\cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}.
 The Kochen-Specker theorem is in essence a mathematical statement
@@
 physics: the Kochen-Specker
-theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}. Our
+theorem~\cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}. Our
 finite-precision extension of that theorem will suggest a resolution

### 2017-11-16 prop_letter.tex
prop_letter.tex \section{The Kochen-Specker Theorem and Contextuality} Update citations...

@@
 $\{0,1,2\}$ from the Mermin-Peres ``magic square'' proof of the
-Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum}:
+Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
 
@@
 $\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ whose
-eigenvalues are all either 1 or $-1$. They are arranged such that in
+eigenvalues are all either $1$ or $-1$
+\cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
+They are arranged such that in
 each row and column, \emph{except the column $j=2$}, every observable

### 2017-11-16 prop_letter.tex
Updating what Prof. Ortiz typed...

@@
 finite precision on measurements in general, is therefore 
-a fundamental problem.  How does one
+a fundamental problem of physics.  How does one
 develop mathematical theories of quantum mechanics that are
@@
 measurement.  We then move on to introduce the concept of quantum
-interval valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
+interval-valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
 The QIVPMs will provide the mathematical framework we need to quantify
@@
 projectors of the form $\proj{\phi}$ where $\ket{\phi}$ is a pure
-quantum state (an element of a Hilbert space), sums of
+quantum state (an element of a Hilbert space ${\cal H}$), sums of
 \emph{orthogonal} projectors $P_0$ and~$P_1$ with $P_0P_1=\mathbb{0}$,
@@
 probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$ is
-the set of all projectors on a given Hilbert space, subject to the
+the set of all events, projectors on a given Hilbert space, subject to the
 following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
@@
 instead of being precisely $0.5$. The spread in this range depends on
-the quantities of resources (time, energy, money, etc.) that are
+the amount of resources (time, energy, money, etc.) that are
 devoted to the experiment. In the classical setting, this
@@
 QIVPMs is consistent with classical IVPMs in the sense that a
-restriction of QIVPMs to commuting events recovers the definition of
+restriction of QIVPMs to mutually commuting events recovers the definition of
 classical IVPMs. To formalize this connection between QIVPMs and
@@
 $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
-is a subspace of commuting events. Indeed restricting $\bar{\mu}_{1}$
+is a subspace of commuting events. Restricting $\bar{\mu}_{1}$
 to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a measure
@@
 The expectation value of an observable $\mathbf{O}$ in a Hilbert space
-of dimension $d$ relative to a 0-deterministic QIVPM is fully
+${\cal H}$ of dimension $d$ relative to a 0-deterministic QIVPM is fully
 determinate and is equal to one of the eigenvalues $\lambda_i$ of that
@@
 Eq.~(\ref{eq:quantum-expectation}), its expectation value relative to
-$\muB_{\rho}$ is the eigenvalue $\lambda$ whose projector
+$\muB_{\rho}$ is the eigenvalue $\lambda_i$ whose projector
 is mapped to 1. It therefore follows, by
@@
 value relative to the 0-deterministic~${\bar{\mu}}$ is fully
-determinate and lies in the interval $[\lambda,\lambda]$.
+determinate and lies in the interval $[\lambda_i,\lambda_i]$.
 
@@
 indeed a 0-deterministic QIVPM by checking that for orthogonal
-operators~$P_{0}$ and $P_{1}$, we have that
+projectors~$P_{0}$ and $P_{1}$, we have that
 $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
@@
 
-We have quantified one aspect of uncertainty in quantum
+We have quantified one important aspect of uncertainty in quantum
 mechanics---due to the imprecise nature of devices---which is a novel
@@
 of measurement states that it is impossible to precisely measure any
-property of a system without disturbing it somewhat. There are
-fundamental limits to what one can measure and these limits are
-typically attributed to complementarity. Our imprecision is an
-\emph{additional} indeterminacy to the inherent probabilistic nature
+property of a system without disturbing it somewhat. Thus, there are
+fundamental limits to what one can measure and these limits have traditionally 
+been attributed to complementarity. Our imprecision represents an 
+\emph{additional} source of indeterminacy to the inherent probabilistic nature
 of quantum mechanics.
@@
 we expect more and more states to be consistent with it. Indeed, in
-the limit, the intervals become \imposs, \necess, and \unknown and
+the limit, the intervals become \imposs, \necess, and \unknown,  and
 every state is consistent with an assignment that states that its

### 2017-11-16 prop_letter.tex
Updating what Prof. Ortiz did...

@@
 defines a valid QIVPM. Conversely, if for every quantum probability
-measure $\mu$, it is the case that $f \circ \mu$ is a QIVPM, then blurring
+measure $\mu$, it is the case that $f \circ \mu$ is a QIVPM, then the blurring
 function~$f$ is an ultramodular function. Formally, we have the following
@@
   is a classical IVPM for all classical probability
-  measure~$\mu:\eventsC\rightarrow\left[0,1\right]$.
+  measures~$\mu:\eventsC\rightarrow\left[0,1\right]$.
 \item \label{enu:iota-mu-QIVPM}The composite
@@
   QIVPM for all quantum probability
-  measure~$\mu:\events\rightarrow\left[0,1\right]$.
+  measures~$\mu:\events\rightarrow\left[0,1\right]$.
 \end{enumerate}

### 2017-11-16 prop_letter.tex
nov 16

@@
 showkeys, longbibliography, amsmath, amssymb, floatfix]{revtex4-1}
+
 \usepackage{fullpage}
@@
 \usepackage{multirow}
-\DeclareUnicodeCharacter{0229}{\c{e}}
+\usepackage[braket,qm]{qcircuit}
+\usepackage{color}
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{framed}
 
@@
 \newtheorem{condition}[assumption]{Condition}
+
+\DeclareUnicodeCharacter{0229}{\c{e}}
 
@@
 \newcommand{\midd}{{\text{\wesa{middle}}}}
-\usepackage[braket,qm]{qcircuit}
 \newcommand{\fket}[1]{{|#1\rangle}}
@@
 \newcommand{\ms}{\texttt{-}}
-
-\usepackage{color}
-\usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{framed}
-\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
-\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
-\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
-\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{blue}{Andy says: #1}\end{minipage}}}
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
@@
 
+\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
+\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
+\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
+\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{blue}{Andy says: #1}\end{minipage}}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
@@
 
-A principal result is that recasting the Kochen-Specker theorem in
-terms of ``$\delta$-determinism,'' with~$\delta$ quantifying the
-effect of finite-precision uncertainties on measurement outcomes,
-reducing to the purely deterministic Kochen-Specker case for
-$\delta=0$, can resolve the question of the effect of finite precision
-and imperfections on contextuality.  A remarkable consequence of our
-analysis is that not only does the quantum-mechanical requirement for
-contextuality continue to hold, thus maintaining the Kochen-Specker
-result for a \emph{non-vanishing} range of $\delta$, but that at a
-\emph{certain fixed value} of $\delta$, there is a sharp transition,
-parallel in its consequences to, say, a phase transition, to
+We begin with the concept of $\delta$-determinism where~$\delta$
+quantifies the effect of finite-precision uncertainties on measurement
+outcomes. We recast the Kochen-Specker theorem using
+$\delta$-determinism to quantify the effects of finite precision and
+imperfections on contextuality. When $\delta=0$, the generalized
+theorem reduces to the conventional one but as $\delta$ varies from 0
+to 1 we note a transition from contextuality to non-contextuality.
+% A principal result is that recasting the Kochen-Specker theorem in 
+% terms of ``$\delta$-determinism,'' with~$\delta$ quantifying the 
+% effect of finite-precision uncertainties on measurement outcomes, 
+% reducing to the purely deterministic Kochen-Specker case for 
+% $\delta=0$, can resolve the question of the effect of finite precision 
+% and imperfections on contextuality.  
+In more detail, the quantum-mechanical requirement for contextuality
+continues to hold, thus maintaining the Kochen-Specker result for a
+\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
+  fixed value} of $\delta$, there is a sharp transition, parallel in
+its consequences to, say, a phase transition, to
 \emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
@@
 quantum state (an element of a Hilbert space ${\cal H}$), sums of
-\emph{orthogonal} projectors $P_0$ and~$P_1$ with $P_0P_1=\mathbb{0}$,
+\emph{orthogonal} projectors~$P_0$ and~$P_1$ with $P_0P_1=\mathbb{0}$,
 and products of \emph{commuting} projectors $P_0$ and~$P_1$ with
@@
 we may conclude that $\mu(\overline{E}) = [0.7,0.8]$ for the
-complementary event $\overline{E}$. In addition to these simple
+complementary event~$\overline{E}$. In addition to these simple
 conditions, there are some subtle conditions on how intervals are
@@
 
-In the remainder of this section, we will show that our definition of
-QIVPMs is consistent with classical IVPMs in the sense that a
-restriction of QIVPMs to mutually commuting events recovers the definition of
-classical IVPMs. To formalize this connection between QIVPMs and
-classical IVPMs, we first note that in contrast to the case with
+We now show that our definition of QIVPMs is consistent with classical
+IVPMs in the sense that a restriction of QIVPMs to mutually commuting
+events recovers the definition of classical IVPMs. To formalize this
+connection, we first note that in contrast to the case with
 conventional quantum probability spaces, there is generally no unique
 state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
-is consistent with a state $\rho$ and projector~$P$ if the interval
-$\bar{\mu}(P)$ contains the exact probability calculated by the Born
-rule, i.e, if:
+is \emph{consistent} with a state $\rho$ and projector~$P$ if the
+interval $\bar{\mu}(P)$ contains the exact probability calculated by
+the Born rule, i.e, if:
 \begin{equation}
@@
 probability measure $\bar{\mu}$ and a subspace of events $\events'$,
-we denote the collection of all states that are consistent with
-$\bar{\mu}$ on every projector in $\events'$ as
-$\coreBorn(\bar{\mu},\events')$:
+we define the \emph{core} of $\bar{\mu}$ relative to $\events'$ as the
+collection of all states $\rho$ that are consistent with $\bar{\mu}$
+on every projector in $\events'$ as $\coreBorn(\bar{\mu},\events')$:
 \begin{equation}
@@
 The proof that QIVPMs become classical IVPMs when the space of events
-includes only mutually commuting events is presented in detail in the
-long version of this paper~\cite{TaiThesis2018}. The idea of the
-proof is as follows. Given a subspace of mutually commuting
-events~$\eventsC$, we can construct a partial orthonormal
-basis by diagonalization and complete it to a full orthonormal basis
-$\overline{\eventsC}$. We then build a bijection between
-the QIVPM on the set of projectors associated with this basis and the
-set of classical events corresponding to this basis. This
-correspondence leads to a crucial property in our setting.
+includes only mutually commuting events is presented in detail in a
+forthcoming thesis~\cite{TaiThesis2018}. The idea of the proof is as
+follows. Given a subspace of mutually commuting events~$\eventsC$, we
+can construct a partial orthonormal basis by diagonalization and
+complete it to a full orthonormal basis $\overline{\eventsC}$. We then
+build a bijection between the QIVPM on the set of projectors
+associated with this basis and the set of classical events
+corresponding to this basis. Using this correspondence together with a
+classical result by
+Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
+we can establish that for the special case of commuting events, a
+QIVPM will always have a non-empty core~\footnote{Shapley's result
+  proves that a classical IVPM always contains at least one state that
+  is consistent with every event.}.
 
@@
 
-This theorem follows directly from our
-correspondence~\cite{TaiThesis2018} and Shapley's
-theorem~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
-which proves that a classical IVPM always contains at least one state $\rho$
-that is consistent with every event in $\eventsC$. In contrast, as we
-illustrate in Sec.~\ref{sec:Gleason}, the set of states
+The importance of this property is that it is violated in
+finite-precision versions of Gleason's theorem
+(cf. Sec.~\ref{sec:Gleason}). As we will show, the set of states
 $\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
-some arbitrary (not necessarily commuting) events $\events'$ and a
+some arbitrary (not necessarily commuting) events~$\events'$ and a
 particular QIVPM $\bar{\mu}$ may be \emph{empty}.
 
-For example, a well-defined  
-QIVPM, assuming the three intervals $\imposs$, $\necess$, and
-$\unknown=\left[0,1\right]$, is:
-\begin{equation}
-\bar{\mu}_{1}\left(P\right)=\begin{cases}
-\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
-\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
-\unknown\,, & \text{otherwise.}
-\end{cases}\label{eq:no-information-IVPM}
-\end{equation}
-This measure represents the beliefs of an experimenter with no prior
-knowledge about the particular quantum system in question; any quantum
-state would be consistent with $\bar{\mu}_{1}$ on any projectors. That
-is, $\coreBorn\left(\bar{\mu}_{1},\events\right)$ is the set of all
-states. The subspace
-$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
-is a subspace of commuting events. Restricting $\bar{\mu}_{1}$
-to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a measure
-$\bar{\mu}_{2}$:
-\begin{equation}
-\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
-\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
-\end{aligned}
-\label{eq:classical-no-information-IVPM}
-\end{equation}
-that corresponds to a classical IVPM. Indeed, if we identify the
-states~$\proj{0}$ and $\proj{1}$ with the head and the tail of a coin,
-respectively, then $\bar{\mu}_{2}$ represents the situation in which
-an experimenter knows nothing about a coin before she tosses
-it. Moreover, for each $p\in\left[0,1\right]$, the
-state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical coin
-with probability~$p$ to get heads, and
-$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent
-with~$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin
-should be consistent with the situation for which an experimenter has
-no prior knowledge.
+% For example, a well-defined QIVPM, assuming the three intervals
+% $\imposs$, $\necess$, and $\unknown=\left[0,1\right]$, is:
+% \begin{equation}
+% \bar{\mu}_{1}\left(P\right)=\begin{cases}
+% \imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
+% \necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
+% \unknown\,, & \text{otherwise.}
+% \end{cases}\label{eq:no-information-IVPM}
+% \end{equation}
+% This measure represents the beliefs of an experimenter with no prior
+% knowledge about the particular quantum system in question; any quantum
+% state would be consistent with $\bar{\mu}_{1}$ on any projectors. That
+% is, $\coreBorn\left(\bar{\mu}_{1},\events\right)$ is the set of all
+% states. The subspace
+% $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
+% is a subspace of commuting events. Restricting $\bar{\mu}_{1}$
+% to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a measure
+% $\bar{\mu}_{2}$:
+% \begin{equation}
+% \begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
+% \bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
+% \end{aligned}
+% \label{eq:classical-no-information-IVPM}
+% \end{equation}
+% that corresponds to a classical IVPM. Indeed, if we identify the
+% states~$\proj{0}$ and $\proj{1}$ with the head and the tail of a coin,
+% respectively, then $\bar{\mu}_{2}$ represents the situation in which
+% an experimenter knows nothing about a coin before she tosses
+% it. Moreover, for each $p\in\left[0,1\right]$, the
+% state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical coin
+% with probability~$p$ to get heads, and
+% $p\proj{0}+\left(1-p\right)\proj{1}$ is consistent
+% with~$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin
+% should be consistent with the situation for which an experimenter has
+% no prior knowledge.
 
@@
 The expectation value of an observable $\mathbf{O}$ in a Hilbert space
-${\cal H}$ of dimension $d$ relative to a 0-deterministic QIVPM is fully
-determinate and is equal to one of the eigenvalues $\lambda_i$ of that
-observable. To see this, note that given an orthonormal basis
+${\cal H}$ of dimension $d$ relative to a 0-deterministic QIVPM is
+fully determinate and is equal to one of the eigenvalues $\lambda_i$
+of that observable. To see this, note that given an orthonormal basis
 $\Omega=\{ \ket{\psi_0},\ket{\psi_1},\ldots,\ket{\psi_{d-1}}\}$, a
@@
 because, by Eq.~(\ref{eq:necess}), we have
-$\bar{\mu}(\Sigma_{j=0}^{d-1}{\proj{\psi_j}})=\necess$ and by inductively
-applying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-we must have one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all
-others mapped to $\imposs$. Given any state~$\rho$ that is consistent
-with this QIVPM on all the projectors in $\Omega$, we have by
-Eq.~(\ref{eq:hbar}) that $\muB_{\rho}$ must also map
-exactly one of the projectors in $\Omega$ to 1 and all others to 0. If
-an observable has a spectral decomposition along $\Omega$ then, by
-Eq.~(\ref{eq:quantum-expectation}), its expectation value relative to
-$\muB_{\rho}$ is the eigenvalue $\lambda_i$ whose projector
-is mapped to 1. It therefore follows, by
+$\bar{\mu}(\Sigma_{j=0}^{d-1}{\proj{\psi_j}})=\necess$ and by
+inductively applying
+Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), we must
+have one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all others
+mapped to $\imposs$. Given any state~$\rho$ that is consistent with
+this QIVPM on all the projectors in $\Omega$, we have by
+Eq.~(\ref{eq:hbar}) that $\muB_{\rho}$ must also map exactly one of
+the projectors in $\Omega$ to 1 and all others to 0. If an observable
+has a spectral decomposition along~$\Omega$ then, by
+Eq.~(\ref{eq:quantum-expectation}), its expectation value relative
+to~$\muB_{\rho}$ is the eigenvalue $\lambda_i$ whose projector is
+mapped to 1. It therefore follows, by
 Eq.~(\ref{eq:quantum-interval-expectation-core}), that the expectation
@@
 $\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ whose
-eigenvalues are all either $1$ or $-1$
+eigenvalues are all either~$1$ or $-1$
 \cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
@@
 straightforward to construct a 0-deterministic QIVPM as
-follows. Consider a non-contextual hidden variable model (e.g., as
-proposed by Bell or
-Kochen-Specker~\cite{BELL_1966,kochenspecker1967}). Such a model
-assigns definite values to all observables at all times, and hence
-assigns a \emph{determinate} probability (0 or 1) to each event. Such
-a probability measure directly induces a 0-deterministic QIVPM by
-changing 0 to $\imposs$ and 1 to $\necess$.
+follows. Consider a non-contextual hidden variable model for $d=2$
+(e.g., as proposed by Bell or
+Kochen-Specker~\cite{BELL_1966,kochenspecker1967}). Such a
+two-dimensional model assigns definite values to all observables at
+all times, and hence assigns a \emph{determinate} probability (0 or 1)
+to each event. This probability measure directly induces a
+0-deterministic QIVPM by changing 0 to $\imposs$ and 1 to $\necess$,
+and therefore a $\delta$-deterministic one.
 
@@
   $\muB_{\rho}$ is the probability measure induced by the
-  Born rule for a given state $\rho$. Let $\alpha$ be the maximum
+  Born rule for a given state~$\rho$. Let $\alpha$ be the maximum
   length of intervals in its image. If a state $\rho'$ is consistent

### 2017-11-17 prop_letter.tex
prop_letter.tex After meeting with Prof. Hanson individually...

@@
 
-\author{Andrew J Hanson}
+\author{Andrew J. Hanson}
 \affiliation{Department of Informatics, Indiana University, Bloomington,
@@
 Hilbert spaces of dimension $d\ge3$, the existence of a unique state
-$\rho$ consistent with the statistical predictions computed from that
+$\rho$ consistent with the statistical predictions computed from the Born
 rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  Our
@@
 representing bounded resources that is parameterized by the size of
-the probability intervals of uncertainty. We then demonstrate that all
+the intervals. We then demonstrate that all
 QIVPMs in this class are consistent with a non-empty set of quantum
@@
 imprecise measurement.
+\yutsung{``volume of states" are not defined in the Gleason's section.}
 
@@
 under which the Kochen-Specker theorem applies.  This provides a way
-of not only resolving the Meyer-Mermin debate, but also revealing of a
+not only of resolving the Meyer-Mermin debate, but also of revealing a
 precise transition to non-contextuality; these are the results of our
@@
 include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
-refer to the probability of impossible events (e.g., the null event)
-and events that are certain (e.g., the event covering the entire
-sample space).  For each interval $[\ell,r]$, we also need the dual
+refer to the probability interval for impossible events
+and events that are certain. We can write this, respectively, as
+$\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$ is
+the null event and $\Omega$ is the event covering the entire
+sample space.  For each interval $[\ell,r]$, we also need the dual
 interval $[1-r,1-\ell]$ so that if one interval refers to the
@@
 though the ``true'' probability of $E$ can be anywhere in the range
-$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be in
+$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be
 anywhere in the range $[0.7,0.8]$, the values are not independent. Any
@@
 probability do not use a strict equality for the combination of
-disjoint events. The correct constraint regarding the probability of
+disjoint events. The correct constraint enforcing coherence of
+the probability assignment for
 $E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is:
@@
 \label{eq:disjoint}
-\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]
+\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]\,,
 \end{equation}
 which, in combination with the requirement for the event of the entire
-space would force $\mu(E \cup \overline{E})$ to always be $\necess$
+space, would force $\mu(E \cup \overline{E})$ to always be $\necess$
 irrespective of the particular assignments of $\mu(E)$
@@
 %% essential new information seems to be introduced.
+\yutsung{Need to be rewrite and make it more clear. Say with symbol and
+equation is better.}
 
@@
 resolution will give us the final general condition for IVPMs. For
-general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
-\begin{equation}
-\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
+events $E_1$ and $E_2$, necessarily disjoint, we have:
+\begin{equation}
+\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)\,,
 \label{eq:classicalconvex}
@@
 generalization to QIVPMs implies that this expectation value will
-itself become bounded by or, more generally distributed around, an interval.
+itself become bounded by or, more generally, distributed around, an interval.
 
@@
 $\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
-$\bar{\mu}_{2}$ defined in
-Eq.~(\ref{eq:classical-no-information-IVPM}) is still not
+$\bar{\mu}_{A}$ is still not
 $\frac{1}{3}$-deterministic because
-$\bar{\mu}_{2}(\proj{0})=\bar{\mu}_{2}(\proj{1})=\unknown$, but
-neither $\unknown\subseteq\left[0,\frac{1}{3}\right]$ nor
-$\unknown\subseteq\left[1-\frac{1}{3},1\right]$.  Finally, when
+$\bar{\mu}_{A}(\proj{0})=\bar{\mu}_{A}(\proj{1})=\unknown=[0,1]$, but
+both $\unknown\subseteq\left[0,\frac{1}{3}\right]$ and
+$\unknown\subseteq\left[1-\frac{1}{3},1\right]$ are false.  Finally, when
 $\delta=1$, because every interval is a subset of $\unknown$, every
 QIVPM is $1$-deterministic. In particular, the non-informative
-QIVPM~$\bar{\mu}_{1}$ defined in Eq.~(\ref{eq:no-information-IVPM}) is
+QIVPM~$\bar{\mu}_{A}$ is
 1-deterministic.
@@
 regarding the non-existence of a $0$-deterministic QIVPM, and
-generalize to $\delta$-deterministic QIVPMs.
+generalize to a corresponding statement about $\delta$-deterministic QIVPMs.
 
@@
 truly uncertain intervals, not just ``almost definite intervals.'' 
+\yutsung{contextuality is never defined.}
 
@@
 $\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. We will use this
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this
 assumed QIVPM to construct the following 0-deterministic QIVPM
@@
 valid $\frac{1}{3}$-deterministic QIVPM.
+\yutsung{Redefine $\bar{\mu}$ to be more clear!}
 
@@
 measurements becomes that large, it becomes possible to map every
-observable to some (quite inaccurate) probability interval, and hence
+observable to some (quite inaccurate) probability interval, thus
 invalidating the Kochen-Specker theorem.
@@
 
-We have quantified one important aspect of uncertainty in quantum
-mechanics---due to the imprecise nature of devices---which is a novel
+We have thus quantified one important aspect of uncertainty in quantum
+mechanics---the effect of the imprecise nature of devices---which is a novel
 addition to the theory of measurement. Indeed, as Heisenberg
@@
 been attributed to complementarity. Our imprecision represents an 
-\emph{additional} source of indeterminacy to the inherent probabilistic nature
+\emph{additional} source of indeterminacy beyond the inherent probabilistic nature
 of quantum mechanics.
-
+\yutsung{To Amr, the ``beyond'' is changed from ``to''. Andy wants to make sure
+you are OK with it.}
 % The significance of this observation is that the uncertainty in the
@@
 framework, we first reformulate Gleason's theorem in QIVPMs using
-infinitely precise
+infinitely precise uncountable
 intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:
@@
   QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$, the state
-  $\rho$ consistent with it on every projector,
-  $\coreBorn\left(\bar{\mu},\events\right)$, is unique. \end{thm}
-
+  $\rho$ consistent with $\bar{\mu}$ on every projector
+  is unique, i.e., there exists a
+  unique state~$\rho$ such that
+  $\coreBorn\left(\bar{\mu},\events\right)=\{\rho\}$.
+  \end{thm}
+
+Now let us consider relaxing $\mathscr{I}$
+to a countable set of finite-width intervals.
 As the intervals in the image of a QIVPM become less and less sharp,
@@
 projections are unknown. There is however a subtlety: as shown in the
-theorem below, an arbitrary assignment of intervals to projectors
-might be globally inconsistent.
+theorem below, it is possible for an arbitrary assignment of intervals to projectors
+to be globally inconsistent.
 
@@
 where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
-$\muB_{\rho}(P)\in\bar{\mu}(P)$ for any~$P$, the
-state~$\rho$ must satisfy:
-\begin{equation}
-\muB_{\rho}(\proj{0})=\muB_{\rho}(\proj{\ps})=\muB_{\rho}(\proj{\ps'})=0\,,
-\end{equation}
-which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all~$j$. The last equation never holds proving the theorem.
+we assumed the core is non-empty $\muB_{\rho}(P)\in\bar{\mu}(P)$, then
+$\bar{\mu}(\proj{0})=\imposs=[0,0]$ from Table~\ref{tab:non-Born-QIVPM} requires
+$\muB_{\rho}(P)=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
+Therefore, $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
+for all~$j$. The last equation never holds, proving the theorem.
 
@@
 of infinitely precise measurements, the volume of states collapses to
-a single point corresponding to a single state.
+a single state.
 
@@
 distance between (pure or mixed) states.  The norm of a pure
-state $\rho=\proj{\psi}$ is defined as usual
+state $\rho=\proj{\psi}$ is defined as usual by
 $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
@@
 
-Previous theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
-theorem in the sense that it accounts for a larger class of probability measures which includes
+Thm.~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
+theorem in the sense that it accounts for a larger class of probability measures that includes
 the conventional one as a limit. The theorem is however ``special'' in
@@
 quantum probability measure. QIVPMs constructed in this manner have
-some peculiar properties which we examine next.
+some peculiar properties that we examine next.
 
@@
 these conditions guarantee that, for any conventional quantum
-probability measure $\mu$, the composition $\ultramodular \circ \mu$,
+probability measure $\mu$, the composition $\ultramodular \circ \mu$
 defines a valid QIVPM. Conversely, if for every quantum probability
@@
 done by restricting our previous quantum probability measure
-$\muB_{\rho}$ on a commuting subspace of
+$\muB_{\rho}$ to a commuting subspace of
 event~$\eventsC$ generated by $\proj{0}$, $\proj{1}$, $\proj{2}$,
@@
 measure, and the induced map $\ultramodular\circ\mu$ fails to be
-a classical IVPM by the same reason as the quantum case.
+a classical IVPM for the same reason as the quantum case.
 
@@
 any ultramodular function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$,
-either $\mathscr{I}=\mathscr{I}_{0}$ in Eq.~(\ref{eq:3-value-intervals}) or
+either $\mathscr{I}=\mathscr{I}_{0}$ as defined in Eq.~(\ref{eq:3-value-intervals}) or
 $\mathscr{I}$ contains uncountably many intervals.\end{thm}
@@
 Since $\ultramodular$ maps to intervals, we can decompose it into
-two functions: its left-end and right-end $\left[\ultramodularL\left(x\right),\ultramodularR\left(x\right)\right]=\ultramodular\left(x\right)$.
+two functions: its left-end and right-end, where
+ $\left[\ultramodularL\left(x\right),\ultramodularR\left(x\right)\right]=\ultramodular\left(x\right)$.
 By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\ultramodularL:\left[0,1\right]\rightarrow\left[0,1\right]$
@@
 either $\ultramodular$ maps every number in $\left[0,1\right]$ to the
-same interval, or the number of intervals that $\ultramodular$ maps to
+same interval, or the number of intervals to which $\ultramodular$ maps
 must be uncountable.
 
-To summarize, a conventional quantum probability measure, has an
+To summarize, a conventional quantum probability measure has an
 uncountable range $[0,1]$. A QIVPM constructed by blurring such a
-conventional quantum probability measure, must also have an uncountable
+conventional quantum probability measure must also have an uncountable
 range of intervals. Of course, any particular QIVPM, or any particular
@@
 Foundational concepts in quantum mechanics, such as the Kochen-Specker
-and Gleason theorems, rely in a very subtle way on the use of
+and Gleason theorems, rely in subtle ways on the use of
 unbounded resources. By assuming infinitely precise measurements,
-these two insightful theorems underlie two fundamental aspects of
-quantum mechanics. On the one hand, Kochen-Specker's result reveals a
+these two insightful theorems form the foundations of two fundamental aspects of
+quantum mechanics. On the one hand, the Kochen-Specker result reveals a
 distinctive aspect of physical reality, the fact that it is
@@
 includes standard quantum measurement as the particular instance of
-sharp, infinitely precise, intervals.  In addition, we showed how
+sharp, infinitely precise, intervals.  
+\yutsung{``quantum measurement'' should be replaced by the }
+In addition, we showed how
 these two theorems emerge as limiting cases of this same framework,

### 2017-11-17 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Resolve a box...

@@
 $\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$ is
-the null event and $\Omega$ is the event covering the entire
+the empty set and $\Omega$ is the event covering the entire
 sample space.  For each interval $[\ell,r]$, we also need the dual
@@
 \end{equation}
-which, in combination with the requirement for the event of the entire
-space, would force $\mu(E \cup \overline{E})$ to always be $\necess$
-irrespective of the particular assignments of $\mu(E)$
-or~$\mu(\overline{E})$.
+which is sensible because for any event $E$ with $\mu(E)=[\ell,r]$, we always
+have $\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E\cup\overline{E})$.
 %% Parallel arguments
@@
 %% essential new information seems to be introduced.
-\yutsung{Need to be rewrite and make it more clear. Say with symbol and
-equation is better.}
 

### 2017-11-18 prop_letter.tex
prop_letter.tex \section{The Kochen-Specker Theorem and Contextuality} Eliminating a box and add a new one...

@@
 \end{definition}
+\yutsung{Clarify the domain of this.}
 
@@
 The bound $\delta < \frac{1}{3}$ is tight as it is possible to
-construct $\frac{1}{3}$-deterministic QIVPMs. For example, take $d=3$,
-and let $P$ be a projector onto an $n$-dimensional subspace of
+construct a $\frac{1}{3}$-deterministic QIVPM
+$\bar{\mu}:\events\rightarrow\mathscr{I}$. For example, consider a
+three-dimensional Hilbert space~$\Hilb$ with orthonormal basis
+$\left\{\ket{0},\ket{1},\ket{2}\right\}$ and a state
+$\rho=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$.
+Let $P$ be an operator projecting onto an $n$-dimensional subspace of
 $\Hilb$, where $n \leq 3$. It is straightforward to check that
-$\bar{\mu}\left(P\right)=\left[\frac{n}{3},\frac{n}{3}\right]$ is a
-valid $\frac{1}{3}$-deterministic QIVPM.
-\yutsung{Redefine $\bar{\mu}$ to be more clear!}
+$\muB_{\rho}\left(P\right)=\frac{n}{3}$. Therefore,
+$\bar{\mu}\left(P\right)=\left[\muB_{\rho}\left(P\right),\muB_{\rho}\left(P\right)\right]$
+is a valid $\frac{1}{3}$-deterministic QIVPM.
 

### 2017-11-19 prop_letter.tex
prop_letter.tex Updating...

@@
 imprecise measurement.
-\yutsung{``volume of states" are not defined in the Gleason's section.}
+\andy{``volume of states" are not defined in the Gleason's section.}
 
@@
 \end{definition}
-\yutsung{Clarify the domain of this.}
 
@@
 \end{tabular}
+\yutsung{$\bar{\mu}_{A}$ is neither a QIVPM nor a restriction of a QIVPM
+according to the current definition. Need to fix this example or fix the definition.}
 \end{table}
@@
 truly uncertain intervals, not just ``almost definite intervals.'' 
-\yutsung{contextuality is never defined.}
+\andy{contextuality is never defined.}
+\yutsung{Actually, the second sentence in the introduction defines
+``contextuality''. The problem is that there is no direct relation between what
+defined in the introduction and here.}
 
@@
 of quantum mechanics.
-\yutsung{To Amr, the ``beyond'' is changed from ``to''. Andy wants to make sure
-you are OK with it.}
+\andy{Make sure Amr is OK with the ``beyond'' here. This was previously ``to''.}
 % The significance of this observation is that the uncertainty in the
@@
 sharp, infinitely precise, intervals.  
-\yutsung{``quantum measurement'' should be replaced by the }
+\andy{``quantum measurement'' should be replaced by the }
 In addition, we showed how

### 2017-11-21 prop_letter.tex
done

--- 2017-11-18 prop_letter.tex
@@
 application of the Born rule determining the probability of a given
-measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.  Here,
-Gleason's theorem establishes that there is no alternative to the Born
-rule by demonstrating, using reasonable continuity arguments in
-Hilbert spaces of dimension $d\ge3$, the existence of a unique state
-$\rho$ consistent with the statistical predictions computed from the Born
-rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  Our
-question then concerns what happens when infinite precision cannot be
-achieved.  We are able to show that, while a QIVPM incorporating the
-effects of finite precision might not be consistent with Gleason's
-unique state~$\rho$ on all projectors defined on a Hilbert space
-$\Hilb$ of dimension $d\ge3$, there is a mathematically precise sense
-in which one recovers the original Gleason theorem asymptotically.
-Specifically, it is possible to construct a class of QIVPMs
-representing bounded resources that is parameterized by the size of
-the intervals. We then demonstrate that all
-QIVPMs in this class are consistent with a non-empty set of quantum
-states, and as the size of the intervals characterizing the
-uncertainties goes to zero, this set of quantum states converges to
-the unique state consistent with the Born rule. We furthermore
-establish a mathematical correlation between the sizes of the
-intervals and the volume of states that are all consistent with an
-imprecise measurement.
-\yutsung{``volume of states" are not defined in the Gleason's section.}
+measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
+Here, Gleason's theorem establishes that there is no alternative to
+the Born rule by demonstrating, using reasonable continuity arguments
+in Hilbert spaces of dimension $d\ge3$, the existence of a unique
+state $\rho$ consistent with the statistical predictions computed from
+the Born rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+Our question then concerns what happens when infinite precision cannot
+be achieved.  We are able to show that, while a QIVPM incorporating
+the effects of finite precision might not be consistent with Gleason's
+unique state~$\rho$ on all projectors defined on a Hilbert
+space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
+sense in which one recovers the original Gleason theorem
+asymptotically.  Specifically, it is possible to construct a class of
+QIVPMs representing bounded resources that is parameterized by the
+size of the intervals. We then demonstrate that all QIVPMs in this
+class are consistent with a non-empty ``ball'' of quantum states whose
+distance are all within a distance proportional to the size of the
+intervals, and as the size of the intervals characterizing the
+uncertainties goes to zero, this ball of quantum states converges to a
+point representing the unique state consistent with the Born rule. 
+%% We furthermore establish a mathematical correlation between the sizes
+%% of the intervals and the volume of states that are all consistent with
+%% an imprecise measurement.  \andy{``volume of states" are not defined
+%%   in the Gleason's section.}
 
@@
 measurement.  We then move on to introduce the concept of quantum
-interval-valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
-The QIVPMs will provide the mathematical framework we need to quantify
-the impact of finite precision measurements on quantum mechanics.  For
-instance, in Sec.~\ref{sec:Kochen-Specker}, we quantify the domain of
-validity of a contextual measurement, thus addressing the conditions
-under which the Kochen-Specker theorem applies.  This provides a way
-not only of resolving the Meyer-Mermin debate, but also of revealing a
-precise transition to non-contextuality; these are the results of our
+interval-valued probability measures in
+Sec.~\ref{sec:Interval-Uncertainty}.  These QIVPMs will provide the
+mathematical framework we need to quantify the impact of finite
+precision measurements on quantum mechanics.  For instance, in
+Sec.~\ref{sec:Kochen-Specker}, we quantify the domain of validity of a
+contextual measurement, thus addressing the conditions under which the
+Kochen-Specker theorem applies.  This provides a way not only of
+resolving the Meyer-Mermin debate, but also of revealing a precise
+transition to non-contextuality; these are the results of our
 Thm.~\ref{cor:Kochen-Specker-IVPM}.  In Sec.~\ref{sec:Gleason}, we
@@
 
-The above axioms describe a mathematical idealization involving
-infinitely precise measurements. In an actual experimental setup with
-an ensemble of quantum states that are not exactly identically
-prepared, and with small imperfections and inaccuracies in measuring
-devices, an experimenter might only be able to determine that the
-probability of an event $P$ is concentrated in the range $[0.49,0.51]$
-instead of being precisely $0.5$. The spread in this range depends on
-the amount of resources (time, energy, money, etc.) that are
-devoted to the experiment. In the classical setting, this
+The above axioms describe a mathematical idealization in which the
+state of the quantum is known and involving infinitely precise
+measurements. In an actual experimental setup with an ensemble of
+quantum states whose states are unknown, that are not exactly
+identically prepared, and with small imperfections and inaccuracies in
+measuring devices, an experimenter might only be able to determine
+that the probability of an event $P$ is concentrated in the range
+$[0.49,0.51]$ instead of being precisely $0.5$. The spread in this
+range depends on the amount of resources (time, energy, money, etc.)
+that are devoted to the experiment. In the classical setting, this
 ``fuzziness'' can be formalized by moving to \emph{interval-valued
@@
 interval could be interpreted as the Gaussian width of a probability
-distribution. We use general intervals with no constraints other than
-the ones needed to maintain coherence: these are described next.
+distribution. We, however, use general intervals with no constraints
+other than the ones needed to maintain coherence: these are described
+next.
 
@@
 the probability assignment for
-$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is:
+$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is therefore:
 \begin{equation}
@@
 \end{equation}
-which is sensible because for any event $E$ with $\mu(E)=[\ell,r]$, we always
-have $\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E\cup\overline{E})$.
+Note that for any event $E$ with $\mu(E)=[\ell,r]$, we always have
+$\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E\cup\overline{E})$.
 %% Parallel arguments
@@
 resolution will give us the final general condition for IVPMs. For
-events $E_1$ and $E_2$, necessarily disjoint, we have:
+events $E_1$ and~$E_2$, not necessarily disjoint, we have:
 \begin{equation}
@@
 Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
-classical IVPMs with quantum probability measures.
+aspects of both classical IVPMs and quantum probability measures.
 
@@
 generalization to QIVPMs implies that this expectation value will
-itself become bounded by or, more generally, distributed around, an interval.
+itself become bounded by an interval.
 
@@
 \end{definition}
-\yutsung{Clarify the domain of this.}
-
-\begin{table}
-  \noindent \centering{}\caption{\label{tab:classical-IVPMs}Example 
-    QIVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ on
-    commuting events $P$.}
-\begin{tabular}{cccc}
-\toprule 
-\addlinespace
-$P$ & $\bar{\mu}_{A}(P)$ & $\bar{\mu}_{B}(P)$ & $\bar{\mu}_{C}(P)$\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\proj{0}$ & $\necess$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\proj{1}$ & $\imposs$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-$\mathbb{1}$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
+
+% \begin{table}
+%   \noindent \centering{}\caption{\label{tab:classical-IVPMs}Example 
+%     QIVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ on
+%     commuting events $P$.}
+% \begin{tabular}{cccc}
+% \toprule 
+% \addlinespace
+% $P$ & $\bar{\mu}_{A}(P)$ & $\bar{\mu}_{B}(P)$ & $\bar{\mu}_{C}(P)$\tabularnewline\addlinespace
+% \midrule
+% \midrule 
+% \addlinespace
+% $\mathbb{0}$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $\proj{0}$ & $\necess$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $\proj{1}$ & $\imposs$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $\mathbb{1}$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
+% \bottomrule
+% \end{tabular}
+% \yutsung{$\bar{\mu}_{A}$ is neither a QIVPM nor a restriction of a QIVPM
+% according to the current definition. Need to fix this example or fix the definition.}
+% \end{table}
 
@@
 itself, only on which intervals are assigned to events. When
-$\delta=0$, every event must be assigned a probability either in the
-interval $\imposs$ or in $\necess$, i.e., every event is completely
-determined with certainty. As $\delta$ gets larger, the QIVPM allows
-for more indeterminate behavior. For example, $\bar{\mu}_{A}$ defined
-in Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
-$\imposs\subseteq\left[0,0\right]$ and
-$\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
-~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
-$\bar{\mu}_{A}$ represents tossing a double-headed coin. When $\delta$
-is increased to $\frac{1}{3}$, both $\bar{\mu}_{B}$ and
-$\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
-$\bar{\mu}_{A}$ is still not
-$\frac{1}{3}$-deterministic because
-$\bar{\mu}_{A}(\proj{0})=\bar{\mu}_{A}(\proj{1})=\unknown=[0,1]$, but
-both $\unknown\subseteq\left[0,\frac{1}{3}\right]$ and
-$\unknown\subseteq\left[1-\frac{1}{3},1\right]$ are false.  Finally, when
-$\delta=1$, because every interval is a subset of $\unknown$, every
-QIVPM is $1$-deterministic. In particular, the non-informative
-QIVPM~$\bar{\mu}_{A}$ is
-1-deterministic.
-%% and the Born QIVPM~$\bar{\mu}_{3}$ defined in
-%% Eq.~(\ref{eq:Born-QIVPM}) are both $1$-deterministic.
+$\delta=0$, every event must be assigned a probability either in
+$\imposs$ or in $\necess$, i.e., every event is completely determined
+with certainty. As $\delta$ gets larger, the QIVPM allows for more
+indeterminate behavior. % For example, $\bar{\mu}_{A}$ defined in
+% Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
+% $\imposs\subseteq\left[0,0\right]$ and
+% $\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
+% ~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
+% $\bar{\mu}_{A}$ represents tossing a double-headed coin. When $\delta$
+% is increased to $\frac{1}{3}$, both $\bar{\mu}_{B}$ and
+% $\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
+% $\bar{\mu}_{A}$ is still not $\frac{1}{3}$-deterministic because
+% $\bar{\mu}_{A}(\proj{0})=\bar{\mu}_{A}(\proj{1})=\unknown=[0,1]$, but
+% both $\unknown\subseteq\left[0,\frac{1}{3}\right]$ and
+% $\unknown\subseteq\left[1-\frac{1}{3},1\right]$ are false.  Finally,
+% when $\delta=1$, because every interval is a subset of $\unknown$,
+% every QIVPM is $1$-deterministic. In particular, the non-informative
+% QIVPM~$\bar{\mu}_{A}$ is 1-deterministic.
+% %% and the Born QIVPM~$\bar{\mu}_{3}$ defined in
+% %% Eq.~(\ref{eq:Born-QIVPM}) are both $1$-deterministic.
 
@@
 observables $\mathbf{O}_{ij}$ with $i$ and $j$ ranging over
-$\{0,1,2\}$ from the Mermin-Peres ``magic square'' proof of the
-Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
+$\{0,1,2\}$ from the Mermin-Peres ``magic square'' used to prove the
+Kochen-Specker
+theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
 
@@
 truly uncertain intervals, not just ``almost definite intervals.'' 
-\yutsung{contextuality is never defined.}
+% \andy{contextuality is never defined.}
+% \yutsung{Actually, the second sentence in the introduction defines
+% ``contextuality''. The problem is that there is no direct relation between what
+% defined in the introduction and here.}
 
@@
 $\rho=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$.
-Let $P$ be an operator projecting onto an $n$-dimensional subspace of
-$\Hilb$, where $n \leq 3$. It is straightforward to check that
+Let $P$ be an operator projecting onto an $n$-dimensional subspace
+of~$\Hilb$, where $n \leq 3$. It is straightforward to check that
 $\muB_{\rho}\left(P\right)=\frac{n}{3}$. Therefore,
@@
 When $\delta \geq \frac{1}{3}$, i.e, when the uncertainty in
-measurements becomes that large, it becomes possible to map every
+measurements becomes so large, it becomes possible to map every
 observable to some (quite inaccurate) probability interval, thus
@@
 to each event. This probability measure directly induces a
-0-deterministic QIVPM by changing 0 to $\imposs$ and 1 to $\necess$,
-and therefore a $\delta$-deterministic one.
+0-deterministic QIVPM by changing 0 to $\imposs$ and 1 to
+$\necess$. The result follows is every 0-deterministic QIVPM is a
+$\delta$-deterministic one.
 
@@
 of quantum mechanics.
-\yutsung{To Amr, the ``beyond'' is changed from ``to''. Andy wants to make sure
-you are OK with it.}
+%% \andy{Make sure Amr is OK with the ``beyond'' here. This was previously ``to''.}
 % The significance of this observation is that the uncertainty in the
@@
   QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$, the state
-  $\rho$ consistent with $\bar{\mu}$ on every projector
+  $\rho$ consistent with~$\bar{\mu}$ on every projector
   is unique, i.e., there exists a
@@
 defines a valid QIVPM. Conversely, if for every quantum probability
-measure $\mu$, it is the case that $f \circ \mu$ is a QIVPM, then the blurring
+measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the blurring
 function~$f$ is an ultramodular function. Formally, we have the following
@@
 sharp, infinitely precise, intervals.  
-\yutsung{``quantum measurement'' should be replaced by the }
-In addition, we showed how
-these two theorems emerge as limiting cases of this same framework,
-thus connecting two seemingly unrelated aspects of quantum physics. We
-noted that {\it arbitrary\/} finite precision measurement conditions
-can nullify the main tenets of both theorems. However, by carefully
-specifying experimental uncertainties, we were able to establish
-rigorous bounds on the validity of these two theorems. Therefore, we
-have established a context in which infinite precision quantum
-mechanical theories can be reconciled with finite precision quantum
-mechanical measurements, and have provided a possible resolution of
-the Meyer-Mermin debate on the impact of finite precision on the
-Kochen-Specker theorem~\cite{PhysRevLett.83.3751,Mermin1999}.
+%% \andy{``quantum measurement'' should be replaced by the }
+
+In addition, we showed how these two theorems emerge as limiting cases
+of this same framework, thus connecting two seemingly unrelated
+aspects of quantum physics. We noted that {\it arbitrary\/} finite
+precision measurement conditions can nullify the main tenets of both
+theorems. However, by carefully specifying experimental uncertainties,
+we were able to establish rigorous bounds on the validity of these two
+theorems. Therefore, we have established a context in which infinite
+precision quantum mechanical theories can be reconciled with finite
+precision quantum mechanical measurements, and have provided a
+possible resolution of the Meyer-Mermin debate on the impact of finite
+precision on the Kochen-Specker
+theorem~\cite{PhysRevLett.83.3751,Mermin1999}.
 

### 2017-11-22 prop_letter.tex
prop_letter.tex Small things...

@@
 generalizes to mixed states
-$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, $\ket{\phi_j} \in {\cal H}$, where $q_j > 0$ and
+$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
 $\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
@@
 fact that the probability $\mu(E)$ of an event~$E$ is generalized from
-a single \emph{real number} to an \emph{interval}~$[\ell,r]$
+a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
 where~$\ell$ intuitively corresponds to the strength of evidence for
@@
 \label{eq:disjoint}
-\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]\,,
+\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]\,.
 \end{equation}

### 2017-11-22 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Small things...

@@
 \begin{thm}[Non-empty Core for Compatible Measurements] \label{thm:Shapley}
-  For QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
+  For every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
   of events~$\eventsC\subseteq\events$ commutes, then
@@
 finite-precision versions of Gleason's theorem
-(cf. Sec.~\ref{sec:Gleason}). As we will show, the set of states
+(cf. Thm.~\ref{thm:Non-extensible-of-Gleason's} in Sec.~\ref{sec:Gleason}). As we will show, the set of states
 $\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with

### 2017-11-23 prop_letter.tex
prop_letter.tex Updated by Prof. Ortiz...

@@
 class are consistent with a non-empty ``ball'' of quantum states whose
-distance are all within a distance proportional to the size of the
-intervals, and as the size of the intervals characterizing the
-uncertainties goes to zero, this ball of quantum states converges to a
-point representing the unique state consistent with the Born rule. 
+radius is defined by the maximal length of the
+intervals characterizing the uncertainties. As the size of the intervals  
+goes to zero, this ball of quantum states converges to a
+point representing the unique state consistent with the Born rule and 
+Gleason's theorem. 
 %% We furthermore establish a mathematical correlation between the sizes
@@
 the resources and precision of the particular experiment. 
-\gerardo{We need to explain physically what it means?}
+%\gerardo{We need to explain physically what it means?}
 % The essential reason for getting an uncountable number of intervals is

### 2017-11-24 prop_letter.tex
prop_letter.tex I reviewed and made the following changes: 1. Add \left and \right on every parenthesis enclosing \overline 2. Fixing a typo by replacing "\mu(E\cup\overline{E})" by "\mu(E)\cup\mu\left(\overline{E}\right)" at the end of paragraph below Eq. (3). 3. Define $\unknown=\left[0,1\right]$ above Thm. 5.

@@
 result of an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$,
-we may conclude that $\mu(\overline{E}) = [0.7,0.8]$ for the
+we may conclude that $\mu\left(\overline{E}\right) = [0.7,0.8]$ for the
 complementary event~$\overline{E}$. In addition to these simple
@@
 consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
-$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
+$\mu\left(\overline{E}\right)=[0.7,0.8]$. The two events $E$ and $\overline{E}$
 are disjoint; the naïve addition of intervals would give
-$\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid probability
+$\mu\eft(E\cup\overline{E}\right)=[0.9,1.1]$ which is not a valid probability
 interval. Moreover the event $E\cup\overline{E}$ is the
@@
 anywhere in the range $[0.7,0.8]$, the values are not independent. Any
-value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
+value of $\mu(E) \leq 0.25$ will force $\mu\left(\overline{E}\right)\geq
 0.75$. To account for such subtleties, the axioms of interval-valued
@@
 Note that for any event $E$ with $\mu(E)=[\ell,r]$, we always have
-$\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E\cup\overline{E})$.
+$\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E)\cup\mu\left(\overline{E}\right)$.
 %% Parallel arguments
@@
 we expect more and more states to be consistent with it. Indeed, in
-the limit, the intervals become \imposs, \necess, and \unknown,  and
+the limit, the intervals become \imposs, \necess, and $\unknown=\left[0,1\right]$,  and
 every state is consistent with an assignment that states that its
@@
 expectation value of a random variable. Consider an event $E$ such
-that $\bar{\mu}(E)=[0.2,0.3]$ and $\bar{\mu}(\overline{E})=[0.7,0.8]$.
+that $\bar{\mu}(E)=[0.2,0.3]$ and $\bar{\mu}\left(\overline{E}\right)=[0.7,0.8]$.
 Given a random variable
@@
 \begin{eqnarray}
- &  & 1\cdot\bar{\mu}(E)+2\cdot\bar{\mu}(\overline{E})\\
+ &  & 1\cdot\bar{\mu}(E)+2\cdot\bar{\mu}\left(\overline{E}\right)\\
  & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
@@
 true probability of $\bar{\mu}(E)$, $\mu(E)$, can be anywhere in
-the range $[0.2,0.3]$ and the true probability of $\bar{\mu}(\overline{E})$
-is $\mu(\overline{E})=1-\mu(E)$. If $\mu(E)=0.2$, the expectation
+the range $[0.2,0.3]$ and the true probability of $\bar{\mu}\left(\overline{E}\right)$
+is $\mu\left(\overline{E}\right)=1-\mu(E)$. If $\mu(E)=0.2$, the expectation
 value of $X$ with respect to $\mu$ is 
 \begin{equation}
-1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.2+2\cdot0.8=1.8\,;
+1\cdot\mu(E)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.2+2\cdot0.8=1.8\,;
 \end{equation}
@@
 \begin{equation}
-1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.3+2\cdot0.7=1.7\,.
+1\cdot\mu(E)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.3+2\cdot0.7=1.7\,.
 \end{equation}

### 2017-11-24 prop_letter.tex
prop_letter.tex typo in the previous commit...

@@
 are disjoint; the naïve addition of intervals would give
-$\mu\eft(E\cup\overline{E}\right)=[0.9,1.1]$ which is not a valid probability
+$\mu\left(E\cup\overline{E}\right)=[0.9,1.1]$ which is not a valid probability
 interval. Moreover the event $E\cup\overline{E}$ is the

### 2017-11-25 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 observable~$\mathbf{O}$, whose spectral decomposition is given by
-$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, where $P_{i}$ is the
-projector onto the eigenspace of the eigenvalue~$\lambda_{i}$. Then,
-the Born rule of CQT tells us that the expectation value of the observable~$\mathbf{O}$
-is given by~\cite{544199,Jaeger2007}
+\begin{equation}
+\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}\,,\label{eq:spectrum-decomposition}
+\end{equation}
+where $P_{i}$ is the projector onto the eigenspace of each distinct
+eigenvalue~$\lambda_{i}$. Since $\lambda_{i}$ are distinct, $N$
+may be less than $d$. Although we requires the eigenvalues in a spectral
+decomposition to be distinct, we will relax this requirement in the
+next section. Then, the Born rule of CQT tells us that the expectation
+value of the observable~$\mathbf{O}$ is given by~\cite{544199,Jaeger2007}
 \begin{equation}
@@
 \begin{equation}
-\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
+\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition-distinct}
 \end{equation}
@@
 
-\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
-decomposition~(\ref{eq:spectrum-decomposition}). A subspace of events~$\events'\subseteq\events$
-is called a subspace of events induced by $\mathbf{O}$ if it is the
-minimal subspace of events satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
-Obvious, $\events'$ is convex.\end{definition}
-
-Notice that a sub-event space induced by any observable commutes.
+\begin{definition}Given an observable~$\mathbf{O}$ with any its
+spectral decomposition~(\ref{eq:spectrum-decomposition}) whose eigenvalues
+are not necessary distinct. A subspace of events~$\events'\subseteq\events$
+is called consistent with $\mathbf{O}$ if it is the minimal subspace
+of events satisfying $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$.
+Obviously, $\events'$ is commuting and convex.\end{definition}
+
 By theorem~\ref{thm:sub-event-space}, we can find a set~$\Omega$,
@@
 \begin{definition}\label{def:observable2random-variable}Given an
-observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition})
+observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition-distinct})
 and its inducing subspace of events\nb$\events'$, set~$\Omega$,

### 2017-11-25 prop_iop.tex
prop_iop.tex Updating...

@@
 \begin{equation}
-x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
+x_{N^{-}}^{-}<\ldots<x_{1}^{-}<0\le x_{1}^{+}<\ldots<x_{N^{+}}^{+}
 \end{equation}
@@
 
-\subsection{Expectation Values for Quantum IVPMs}
-
-Before discussing quantum IVPMs, we first review various notations
-brought forward from conventional quantum theory. Assume that a physical
-system is represented by a density matrix~$\rho$, and that we wish
-to measure a physical quantity~${\cal O}$ of this system, with corresponding
+\subsection{Expectation Values for QIVPMs}
+
+Before discussing QIVPMs, we first review various notations brought
+forward from conventional quantum theory. Assume that a physical system
+is represented by a density matrix~$\rho$, and that we wish to measure
+a physical quantity~${\cal O}$ of this system, with corresponding
 observable~$\mathbf{O}$, whose spectral decomposition is given by
 \begin{equation}
-\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}\,,\label{eq:spectrum-decomposition}
-\end{equation}
-where $P_{i}$ is the projector onto the eigenspace of each distinct
-eigenvalue~$\lambda_{i}$. Since $\lambda_{i}$ are distinct, $N$
-may be less than $d$. Although we requires the eigenvalues in a spectral
-decomposition to be distinct, we will relax this requirement in the
-next section. Then, the Born rule of CQT tells us that the expectation
-value of the observable~$\mathbf{O}$ is given by~\cite{544199,Jaeger2007}
+\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition-distinct}
+\end{equation}
+where the positive and negative eigenvalues are ordered from the smallest
+to the largest 
+\begin{equation}
+\lambda_{N^{-}}^{-}<\ldots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\ldots<\lambda_{N^{+}}^{+}\,,
+\end{equation}
+and $P_{i}$ is the projector onto the eigenspace of each distinct
+eigenvalue~$\lambda_{i}$. This spectral decomposition might be different
+from the one people used to~.
+
+Since $\lambda_{i}$ are distinct, $N$ may be less than $d$. Although
+we requires the eigenvalues in equation~(\ref{eq:spectrum-decomposition-distinct})
+to be distinct, we will consider the other type of spectral decomposition,
+especially $\mathbf{O}=\sum_{k=1}^{d}\lambda_{k}\proj{k}$ in lemma~\ref{lemma:observable2random-variable}
+later. Then, the Born rule of CQT tells us that the expectation value
+of the observable~$\mathbf{O}$ is given by~\cite{544199,Jaeger2007}
 \begin{equation}
@@
 
-Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
+Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
 and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
@@
 as its spectral decomposition
-\begin{equation}
-\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition-distinct}
-\end{equation}
-we separate the positive and negative eigenvalues and order its eigenvalues
-from the smallest to the largest 
-\begin{equation}
-\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
-\end{equation}
+
 Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
@@
 Since the similarity between classical and quantum expectation values,
-we would prove some lemmas\footnote{\yutsung{functor?}} which can
-help us move the classical results to quantum.
+we would prove some lemmas\footnote{\yutsung{functor? Galois connection?}}
+which can help us move the classical results to quantum.
 

### 2017-11-26 prop_iop.tex
prop_letter.tex \section{Fuzzy Measurements} Add citations...

@@
 a physical quantity~${\cal O}$ of this system, with corresponding
-observable~$\mathbf{O}$, whose spectral decomposition is given by
+observable~$\mathbf{O}$, whose spectral decomposition is given by~\cite{544199,Jaeger2007}
 \begin{equation}

### 2017-11-26 prop_letter.tex
prop_letter.tex \section{Fuzzy Measurements} Add citations...

@@
 observable~$\mathbf{O}$ having spectral decomposition
-$\mathbf{O}=\sum_{i=1}^{d}\lambda_{i}P_{i}$, with eigenvalues $\lambda_i \in \mathbb{R}$, as:
+$\mathbf{O}=\sum_{i=1}^{d}\lambda_{i}P_{i}$, with eigenvalues $\lambda_i \in
+\mathbb{R}$, as~\cite{544199,Jaeger2007}:
 \begin{equation}

### 2017-11-26 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for QIVPMs} Add more reference...

--- 2017-11-25 prop_iop.tex
@@
 a physical quantity~${\cal O}$ of this system, with corresponding
-observable~$\mathbf{O}$, whose spectral decomposition is given by
+observable~$\mathbf{O}$, whose spectral decomposition is given by~\cite{Griffiths1994,FraleighBeauregard1995,544199,FriedbergInselSpence2002,Jaeger2007}
 \begin{equation}

### 2017-11-27 prop_PRA.tex
prop_PRA.tex For REVTeX and LaTeX files, please run BibTeX before submitting your paper, and read-in (i.e., \input) or paste the resulting .bbl file within the reference section of your paper. https://journals.aps.org/authors/tips-authors-physical-review-physical-review-letters

--- 2017-11-26 prop_letter.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{prop}
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (0) dotless jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (1) range
+%Control: year (0) verbatim
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{52}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Barrett}\ and\ \citenamefont
+  {Kent}(2004)}]{BarrettKent2004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jonathan}\
+  \bibnamefont {Barrett}}\ and\ \bibinfo {author} {\bibfnamefont {Adrian}\
+  \bibnamefont {Kent}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Non-contextuality, finite precision measurement and the {K}ochen--{S}pecker
+  theorem},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Studies in History and Philosophy of Science Part B: Studies in History and
+  Philosophy of Modern Physics}\ }\textbf {\bibinfo {volume} {35}},\ \bibinfo
+  {pages} {151--176} (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Appleby}(2005)}]{Appleby_2005}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont
+  {Appleby}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
+  {B}ell–{K}ochen–{S}pecker theorem},}\ }\href {\doibase
+  10.1016/j.shpsb.2004.05.003} {\bibfield  {journal} {\bibinfo  {journal}
+  {Studies in History and Philosophy of Science Part B: Studies in History and
+  Philosophy of Modern Physics}\ }\textbf {\bibinfo {volume} {36}},\ \bibinfo
+  {pages} {1--28} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Meyer}(1999)}]{PhysRevLett.83.3751}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {David}\ \bibnamefont
+  {Meyer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Finite precision
+  measurement nullifies the {K}ochen-{S}pecker theorem},}\ }\href {\doibase
+  10.1103/PhysRevLett.83.3751} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {83}},\ \bibinfo {pages}
+  {3751--3754} (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mermin}(1999)}]{Mermin1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~David}\
+  \bibnamefont {Mermin}},\ }\href@noop {} {\enquote {\bibinfo {title} {A
+  {K}ochen-{S}pecker theorem for imprecisely specified measurement},}\ }
+  (\bibinfo {year} {1999}),\ \Eprint {http://arxiv.org/abs/quant-ph/9912081v1}
+  {quant-ph/9912081v1} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bell}(1966)}]{BELL_1966}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {John~S.}\ \bibnamefont
+  {Bell}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {On the problem of
+  hidden variables in quantum mechanics},}\ }\href {\doibase
+  10.1103/RevModPhys.38.447} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+  Mod. Phys.}\ }\textbf {\bibinfo {volume} {38}},\ \bibinfo {pages} {447--452}
+  (\bibinfo {year} {1966})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kochen}\ and\ \citenamefont
+  {Specker}(1968)}]{kochenspecker1967}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Kochen}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Specker}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The problem of
+  hidden variables in quantum mechanics},}\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Indiana Univ. Math. J.}\ }\textbf {\bibinfo
+  {volume} {17}},\ \bibinfo {pages} {59--87} (\bibinfo {year}
+  {1968})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Redhead}(1987)}]{Redhead1987-REDINA}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Michael}\ \bibnamefont
+  {Redhead}},\ }\href@noop {} {\emph {\bibinfo {title} {Incompleteness,
+  Nonlocality, and Realism: A Prolegomenon to the Philosophy of Quantum
+  Mechanics}}}\ (\bibinfo  {publisher} {Oxford University Press},\ \bibinfo
+  {year} {1987})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mermin}(1990)}]{Mermin1990Simple}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~David}\
+  \bibnamefont {Mermin}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Simple unified form for the major no-hidden-variables theorems},}\ }\href
+  {\doibase 10.1103/physrevlett.65.3373} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {65}},\ \bibinfo
+  {pages} {3373--3376} (\bibinfo {year} {1990})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Peres}(1995)}]{peres1995quantum}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Asher}\ \bibnamefont
+  {Peres}},\ }\href {http://books.google.com/books?id=rMGqMyFBcL8C} {\emph
+  {\bibinfo {title} {Quantum Theory: Concepts and Methods}}},\ Fundamental
+  Theories of Physics\ (\bibinfo  {publisher} {Springer},\ \bibinfo {year}
+  {1995})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jaeger}(2007)}]{Jaeger2007}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Gregg}\ \bibnamefont
+  {Jaeger}},\ }\href
+  {http://www.ebook.de/de/product/24986917/gregg_jaeger_quantum_information.html}
+  {\emph {\bibinfo {title} {Quantum Information}}}\ (\bibinfo  {publisher}
+  {Springer New York},\ \bibinfo {year} {2007})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Held}(2016)}]{Held2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Carsten}\ \bibnamefont
+  {Held}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
+  {K}ochen-{S}pecker theorem},}\ }in\ \href
+  {https://plato.stanford.edu/entries/kochen-specker/} {\emph {\bibinfo
+  {booktitle} {The Stanford Encyclopedia of Philosophy}}},\ \bibinfo {editor}
+  {edited by\ \bibinfo {editor} {\bibfnamefont {Edward~N.}\ \bibnamefont
+  {Zalta}}}\ (\bibinfo  {publisher} {Metaphysics Research Lab, Stanford
+  University},\ \bibinfo {year} {2016})\ \bibinfo {edition} {{F}all 2016}\
+  ed.\BibitemShut {Stop}%
+\bibitem [{\citenamefont {Kent}(1999)}]{Kent1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Adrian}\ \bibnamefont
+  {Kent}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Noncontextual
+  hidden variables and physical measurements},}\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {83}},\ \bibinfo {pages} {3755} (\bibinfo {year}
+  {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Havlicek}\ \emph {et~al.}(2001)\citenamefont
+  {Havlicek}, \citenamefont {Krenn}, \citenamefont {Summhammer},\ and\
+  \citenamefont {Svozil}}]{HavlicekKrennSummhammerSvozil2001}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Hans}\ \bibnamefont
+  {Havlicek}}, \bibinfo {author} {\bibfnamefont {Günther}\ \bibnamefont
+  {Krenn}}, \bibinfo {author} {\bibfnamefont {Johann}\ \bibnamefont
+  {Summhammer}}, \ and\ \bibinfo {author} {\bibfnamefont {Karl}\ \bibnamefont
+  {Svozil}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Colouring the
+  rational quantum sphere and the {K}ochen-{S}pecker theorem},}\ }\href
+  {\doibase 10.1088/0305-4470/34/14/312} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Phys. A: Math. Gen.}\ }\textbf {\bibinfo {volume} {34}},\
+  \bibinfo {pages} {3071} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Simon}\ \emph {et~al.}(2001)\citenamefont {Simon},
+  \citenamefont {Brukner},\ and\ \citenamefont
+  {Zeilinger}}]{SimonBruknerZeilinger2001}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Christoph}\
+  \bibnamefont {Simon}}, \bibinfo {author} {\bibfnamefont {\ifmmode
+  \check{C}\else~\v{C}\fi{}aslav}\ \bibnamefont {Brukner}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {Anton}\ \bibnamefont {Zeilinger}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Hidden-variable theorems for real
+  experiments},}\ }\href {\doibase 10.1103/PhysRevLett.86.4427} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {86}},\ \bibinfo {pages} {4427--4430} (\bibinfo {year}
+  {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cabello}(2002)}]{Cabello2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Ad\'an}\ \bibnamefont
+  {Cabello}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Finite-precision measurement does not nullify the {K}ochen-{S}pecker
+  theorem},}\ }\href {\doibase 10.1103/PhysRevA.65.052101} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+  {65}},\ \bibinfo {pages} {052101} (\bibinfo {year} {2002})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Larsson}(2002)}]{Larsson2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-Å.}\ \bibnamefont
+  {Larsson}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {A
+  {K}ochen-{S}pecker inequality},}\ }\href {\doibase 10.1209/epl/i2002-00444-0}
+  {\bibfield  {journal} {\bibinfo  {journal} {Europhys. Lett.}\ }\textbf
+  {\bibinfo {volume} {58}},\ \bibinfo {pages} {799} (\bibinfo {year}
+  {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Appleby}(2002)}]{Appleby2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont
+  {Appleby}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Existential
+  contextuality and the models of {M}eyer, {K}ent, and {C}lifton},}\ }\href
+  {\doibase 10.1103/PhysRevA.65.022105} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {65}},\ \bibinfo
+  {pages} {022105} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Spekkens}(2005)}]{Spekkens2005}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Robert~W.}\
+  \bibnamefont {Spekkens}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Contextuality for preparations, transformations, and unsharp
+  measurements},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {71}},\ \bibinfo {pages} {052108}
+  (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {G{\"u}hne}\ \emph {et~al.}(2010)\citenamefont
+  {G{\"u}hne}, \citenamefont {Kleinmann}, \citenamefont {Cabello},
+  \citenamefont {Larsson}, \citenamefont {Kirchmair}, \citenamefont
+  {Z{\"a}hringer}, \citenamefont {Gerritsma},\ and\ \citenamefont
+  {Roos}}]{GuehneKleinmannCabelloEtAl2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Otfried}\ \bibnamefont
+  {G{\"u}hne}}, \bibinfo {author} {\bibfnamefont {Matthias}\ \bibnamefont
+  {Kleinmann}}, \bibinfo {author} {\bibfnamefont {Ad{\'a}n}\ \bibnamefont
+  {Cabello}}, \bibinfo {author} {\bibfnamefont {Jan-{\AA}ke}\ \bibnamefont
+  {Larsson}}, \bibinfo {author} {\bibfnamefont {Gerhard}\ \bibnamefont
+  {Kirchmair}}, \bibinfo {author} {\bibfnamefont {Florian}\ \bibnamefont
+  {Z{\"a}hringer}}, \bibinfo {author} {\bibfnamefont {Rene}\ \bibnamefont
+  {Gerritsma}}, \ and\ \bibinfo {author} {\bibfnamefont {Christian~F}\
+  \bibnamefont {Roos}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Compatibility and noncontextuality for sequential measurements},}\ }\href
+  {\doibase 10.1103/PhysRevA.81.022121} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo
+  {pages} {022121} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mazurek}\ \emph {et~al.}(2016)\citenamefont
+  {Mazurek}, \citenamefont {Pusey}, \citenamefont {Kunjwal}, \citenamefont
+  {Resch},\ and\ \citenamefont {Spekkens}}]{MazurekPuseyKunjwalEtAl2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Michael~D.}\
+  \bibnamefont {Mazurek}}, \bibinfo {author} {\bibfnamefont {Matthew~F.}\
+  \bibnamefont {Pusey}}, \bibinfo {author} {\bibfnamefont {Ravi}\ \bibnamefont
+  {Kunjwal}}, \bibinfo {author} {\bibfnamefont {Kevin~J.}\ \bibnamefont
+  {Resch}}, \ and\ \bibinfo {author} {\bibfnamefont {Robert~W.}\ \bibnamefont
+  {Spekkens}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {An
+  experimental test of noncontextuality without unphysical idealizations},}\
+  }\href {\doibase 10.1038/ncomms11780} {\bibfield  {journal} {\bibinfo
+  {journal} {Nat. Commun.}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages}
+  {ncomms11780} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Willcock}\ and\ \citenamefont {Sabry}(2011)}]{usat}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jeremiah}\
+  \bibnamefont {Willcock}}\ and\ \bibinfo {author} {\bibfnamefont {Amr}\
+  \bibnamefont {Sabry}},\ }\href@noop {} {\enquote {\bibinfo {title} {Solving
+  {UNIQUE}-{SAT} in a modal quantum theory},}\ } (\bibinfo {year} {2011}),\
+  \Eprint {http://arxiv.org/abs/1102.3587v1} {1102.3587v1} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Hanson}\ \emph {et~al.}(2013)\citenamefont {Hanson},
+  \citenamefont {Ortiz}, \citenamefont {Sabry},\ and\ \citenamefont
+  {Tai}}]{geometry2013apsrev4}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Andrew~J.}\
+  \bibnamefont {Hanson}}, \bibinfo {author} {\bibfnamefont {Gerardo}\
+  \bibnamefont {Ortiz}}, \bibinfo {author} {\bibfnamefont {Amr}\ \bibnamefont
+  {Sabry}}, \ and\ \bibinfo {author} {\bibfnamefont {Yu-Tsung}\ \bibnamefont
+  {Tai}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Geometry of
+  discrete quantum computing},}\ }\href {\doibase
+  10.1088/1751-8113/46/18/185301} {\bibfield  {journal} {\bibinfo  {journal}
+  {J. Phys. A: Math. Theor.}\ }\textbf {\bibinfo {volume} {46}},\ \bibinfo
+  {pages} {185301} (\bibinfo {year} {2013})},\ \bibinfo {note} {{E}rratum
+  \bibfield {title} {\enquote {\bibinfo {title} {Corrigendum: Geometry of
+  discrete quantum computing},}\ }\href
+  {http://stacks.iop.org/1751-8121/49/i=3/a=039501} {\bibfield {journal}
+  {\bibinfo {journal} {J. Phys. A: Math. Theor.}\ }\textbf {\bibinfo {volume}
+  {49}},\ \bibinfo {pages} {039501} (\bibinfo {year} {2016})}}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Hanson}\ \emph {et~al.}(2014)\citenamefont {Hanson},
+  \citenamefont {Ortiz}, \citenamefont {Sabry},\ and\ \citenamefont
+  {Tai}}]{DQT2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Andrew~J.}\
+  \bibnamefont {Hanson}}, \bibinfo {author} {\bibfnamefont {Gerardo}\
+  \bibnamefont {Ortiz}}, \bibinfo {author} {\bibfnamefont {Amr}\ \bibnamefont
+  {Sabry}}, \ and\ \bibinfo {author} {\bibfnamefont {Yu-Tsung}\ \bibnamefont
+  {Tai}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Discrete quantum
+  theories},}\ }\href {http://stacks.iop.org/1751-8121/47/i=11/a=115305}
+  {\bibfield  {journal} {\bibinfo  {journal} {J. Phys. A: Math. Theor.}\
+  }\textbf {\bibinfo {volume} {47}},\ \bibinfo {pages} {115305} (\bibinfo
+  {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jamison}\ and\ \citenamefont
+  {Lodwick}(2004)}]{JamisonLodwick2004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Kenneth~David}\
+  \bibnamefont {Jamison}}\ and\ \bibinfo {author} {\bibfnamefont {Weldon~A.}\
+  \bibnamefont {Lodwick}},\ }\href {http://ccm.ucdenver.edu/reports/rep213.pdf}
+  {\emph {\bibinfo {title} {Interval-Valued Probability Measures}}},\ \bibinfo
+  {type} {Tech. Rep.}\ \bibinfo {number} {213}\ (\bibinfo  {institution}
+  {Center for Computational Mathematics, University of Colorado Denver},\
+  \bibinfo {year} {2004})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Born}(1983)}]{Born1983bibTeX}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Max}\ \bibnamefont
+  {Born}},\ }\bibfield  {title} {{\selectlanguage {English}\enquote {\bibinfo
+  {title} {On the quantum mechanics of collisions},}\ }}in\ \href@noop {}
+  {{\selectlanguage {English}\emph {\bibinfo {booktitle} {Quantum Theory and
+  Measurement}}}}\ (\bibinfo  {publisher} {Princeton University Press},\
+  \bibinfo {year} {1983})\ pp.\ \bibinfo {pages} {52--55},\ \bibinfo {note}
+  {{E}nglish Trans. by John Archibald Wheeler and Wojciech Hubert
+  Zurek}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mermin}(2007)}]{Mermin2007}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~David}\
+  \bibnamefont {Mermin}},\ }\href@noop {} {\emph {\bibinfo {title} {Quantum
+  Computer Science}}}\ (\bibinfo  {publisher} {Cambridge University Press},\
+  \bibinfo {year} {2007})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gleason}(1957)}]{gleason1957}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Andrew}\ \bibnamefont
+  {Gleason}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Measures on the
+  closed subspaces of a {Hilbert} space},}\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Indiana Univ. Math. J.}\ }\textbf {\bibinfo
+  {volume} {6}},\ \bibinfo {pages} {885--893} (\bibinfo {year}
+  {1957})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kolmogorov}(1950)}]{Kolmogorov1950bibTeX}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Andrei~Nikolaevich}\
+  \bibnamefont {Kolmogorov}},\ }\href@noop {} {{\selectlanguage {English}\emph
+  {\bibinfo {title} {Foundations of the Theory of Probability}}}}\ (\bibinfo
+  {publisher} {Chelsea Publishing Company},\ \bibinfo {year} {1950})\ \bibinfo
+  {note} {{E}nglish Trans. from the German by Nathan Morrison.}\BibitemShut
+  {Stop}%
+\bibitem [{\citenamefont {Nielsen}\ and\ \citenamefont
+  {Chuang}(2000)}]{544199}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Michael~A.}\
+  \bibnamefont {Nielsen}}\ and\ \bibinfo {author} {\bibfnamefont {Isaac~L.}\
+  \bibnamefont {Chuang}},\ }\href@noop {} {\emph {\bibinfo {title} {Quantum
+  computation and quantum information}}}\ (\bibinfo  {publisher} {Cambridge
+  University Press},\ \bibinfo {address} {New York, NY, USA},\ \bibinfo {year}
+  {2000})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Griffiths}(2003)}]{Griffiths2003}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Robert~B.}\
+  \bibnamefont {Griffiths}},\ }\href@noop {} {\emph {\bibinfo {title}
+  {Consistent quantum theory}}}\ (\bibinfo  {publisher} {Cambridge University
+  Press},\ \bibinfo {year} {2003})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Grabisch}(2016)}]{Grabisch2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Michel}\ \bibnamefont
+  {Grabisch}},\ }\href {\doibase 10.1007/978-3-319-30690-2} {\emph {\bibinfo
+  {title} {Set functions, games and capacities in decision making}}},\ \bibinfo
+  {series} {Theory and Decision Library C}\ No.~\bibinfo {number} {46}\
+  (\bibinfo  {publisher} {Springer International Publishing},\ \bibinfo {year}
+  {2016})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mackey}(1957)}]{10.2307/2308516}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {George~W.}\
+  \bibnamefont {Mackey}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Quantum mechanics and {H}ilbert space},}\ }\href
+  {http://www.jstor.org/stable/2308516} {\bibfield  {journal} {\bibinfo
+  {journal} {Amer. Math. Monthly}\ }\textbf {\bibinfo {volume} {64}},\ \bibinfo
+  {pages} {45--57} (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Maassen}(2010)}]{Maassen2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Hans}\ \bibnamefont
+  {Maassen}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Quantum
+  probability and quantum information theory},}\ }in\ \href@noop {} {\emph
+  {\bibinfo {booktitle} {Quantum information, computation and cryptography}}}\
+  (\bibinfo  {publisher} {Springer},\ \bibinfo {year} {2010})\ pp.\ \bibinfo
+  {pages} {65--108}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Abramsky}(2012)}]{Abramsky2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Samson}\ \bibnamefont
+  {Abramsky}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Big toy
+  models: Representing physical systems as {C}hu spaces},}\ }\href {\doibase
+  10.1007/s11229-011-9912-x} {\bibfield  {journal} {\bibinfo  {journal}
+  {Synthese}\ }\textbf {\bibinfo {volume} {186}},\ \bibinfo {pages} {697--718}
+  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dempster}(1967)}]{Dempster1967}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
+  {Dempster}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Upper and
+  lower probabilities induced by a multivalued mapping},}\ }\href {\doibase
+  10.1214/aoms/1177698950} {\bibfield  {journal} {\bibinfo  {journal} {Ann.
+  Math. Statist.}\ }\textbf {\bibinfo {volume} {38}},\ \bibinfo {pages}
+  {325--339} (\bibinfo {year} {1967})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Shafer}(1976)}]{Shafer1976}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Glenn}\ \bibnamefont
+  {Shafer}},\ }\href
+  {http://www.ebook.de/de/product/14595404/glenn_shafer_a_mathematical_theory_of_evidence.html}
+  {\emph {\bibinfo {title} {A Mathematical Theory of Evidence}}}\ (\bibinfo
+  {publisher} {Princeton University Press},\ \bibinfo {year}
+  {1976})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gilboa}\ and\ \citenamefont
+  {Schmeidler}(1994)}]{GilboaSchmeidler1994}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Itzhak}\ \bibnamefont
+  {Gilboa}}\ and\ \bibinfo {author} {\bibfnamefont {David}\ \bibnamefont
+  {Schmeidler}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Additive
+  representations of non-additive measures and the {C}hoquet integral.}}\
+  }\href
+  {http://proxyiub.uits.iu.edu/login?url=http://search.ebscohost.com/login.aspx?direct=true&db=bth&AN=18661313&site=ehost-live&scope=site}
+  {\bibfield  {journal} {\bibinfo  {journal} {Annals of Operations Research}\
+  }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {43--65} (\bibinfo
+  {year} {1994})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Marinacci}(1999)}]{Marinacci1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Massimo}\ \bibnamefont
+  {Marinacci}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Limit laws
+  for non-additive probabilities and their frequentist interpretation},}\
+  }\href {\doibase 10.1006/jeth.1998.2479} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Economic Theory}\ }\textbf {\bibinfo {volume} {84}},\
+  \bibinfo {pages} {145--195} (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Weichselberger}(2000)}]{Weichselberger2000}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Kurt}\ \bibnamefont
+  {Weichselberger}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
+  theory of interval-probability as a unifying concept for uncertainty},}\
+  }\href {\doibase 10.1016/s0888-613x(00)00032-3} {\bibfield  {journal}
+  {\bibinfo  {journal} {Int. J. Approximate Reasoning}\ }\textbf {\bibinfo
+  {volume} {24}},\ \bibinfo {pages} {149--170} (\bibinfo {year}
+  {2000})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Huber}\ and\ \citenamefont
+  {Ronchetti}(2009)}]{HuberRonchetti2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Peter~J.}\
+  \bibnamefont {Huber}}\ and\ \bibinfo {author} {\bibfnamefont {Elvezio~M.}\
+  \bibnamefont {Ronchetti}},\ }\href
+  {http://www.ebook.de/de/product/7871112/peter_j_huber_elvezio_m_ronchetti_robust_statistics.html}
+  {{\selectlanguage {English}\emph {\bibinfo {title} {Robust Statistics}}}},\
+  \bibinfo {edition} {2nd}\ ed.,\ Wiley Series in Probability and Statistics\
+  (\bibinfo  {publisher} {John Wiley \& Sons Inc.},\ \bibinfo {year}
+  {2009})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Shapley}(1971)}]{Shapley1971}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Lloyd~S.}\
+  \bibnamefont {Shapley}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Cores of convex games},}\ }\href {\doibase 10.1007/BF01753431} {\bibfield
+  {journal} {\bibinfo  {journal} {International Journal of Game Theory}\
+  }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {11--26} (\bibinfo {year}
+  {1971})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ng}\ \emph {et~al.}(1997)\citenamefont {Ng},
+  \citenamefont {Mo},\ and\ \citenamefont {Yeh}}]{NgMoYeh1997}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Man-Chung}\
+  \bibnamefont {Ng}}, \bibinfo {author} {\bibfnamefont {Chi-Ping}\ \bibnamefont
+  {Mo}}, \ and\ \bibinfo {author} {\bibfnamefont {Yeong-Nan}\ \bibnamefont
+  {Yeh}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {On the cores of
+  scalar measure games},}\ }\href {http://www.jstor.org/stable/43833386}
+  {\bibfield  {journal} {\bibinfo  {journal} {Taiwanese Journal of
+  Mathematics}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {171--180}
+  (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Marinacci}\ and\ \citenamefont
+  {Montrucchio}(2005)}]{MarinacciMontrucchio2005}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Massimo}\ \bibnamefont
+  {Marinacci}}\ and\ \bibinfo {author} {\bibfnamefont {Luigi}\ \bibnamefont
+  {Montrucchio}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Ultramodular functions},}\ }\href {http://www.jstor.org/stable/25151654}
+  {\bibfield  {journal} {\bibinfo  {journal} {Math. Oper. Res.}\ }\textbf
+  {\bibinfo {volume} {30}},\ \bibinfo {pages} {311--332} (\bibinfo {year}
+  {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tai}(forthcoming)}]{TaiThesis2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Yu-Tsung}\
+  \bibnamefont {Tai}},\ }\emph {\bibinfo {title} {Discrete Quantum Theories and
+  Computing}},\ \href@noop {} {Ph.D. thesis},\ \bibinfo  {school} {Indiana
+  University, Bloomington} (\bibinfo {year} {forthcoming})\BibitemShut
+  {NoStop}%
+\bibitem [{Note1()}]{Note1}%
+  \BibitemOpen
+  \bibinfo {note} {Shapley's result proves that a classical IVPM always
+  contains at least one state that is consistent with every event.}\BibitemShut
+  {Stop}%
+\bibitem [{\citenamefont {Choquet}(1954)}]{Choquet1954}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Gustave}\ \bibnamefont
+  {Choquet}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Theory of
+  capacities},}\ }\href {\doibase 10.5802/aif.53} {\bibfield  {journal}
+  {\bibinfo  {journal} {Ann. Inst. Fourier}\ }\textbf {\bibinfo {volume} {5}},\
+  \bibinfo {pages} {131--295} (\bibinfo {year} {1954})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Heisenberg}(1983)}]{Heisenberg1983apsrev4}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Heisenberg}},\ }\href {https://ntrs.nasa.gov/search.jsp?R=19840008978}
+  {{\selectlanguage {English}\emph {\bibinfo {title} {The actual content of
+  quantum theoretical kinematics and mechanics}}}},\ \bibinfo {type} {Tech.
+  Rep.}\ \bibinfo {number} {NASA-TM-77379}\ (\bibinfo  {institution} {National
+  Aeronautics and Space Administration},\ \bibinfo {year} {1983})\ \bibinfo
+  {note} {{E}nglish. Trans. from \bibfield {title} {\enquote {\bibinfo {title}
+  {{\"U}ber den anschaulichen inhalt der quantentheoretischen kinematik und
+  mechanik},}\ }\href {\doibase 10.1007/BF01397280} {\bibfield {journal}
+  {\bibinfo {journal} {Z. Phys.}\ }\textbf {\bibinfo {volume} {43}},\ \bibinfo
+  {pages} {172--198} (\bibinfo {year} {1927})}}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Roberts}\ and\ \citenamefont
+  {Varberg}(1973)}]{RobertsVarberg1973}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~Wayne}\
+  \bibnamefont {Roberts}}\ and\ \bibinfo {author} {\bibfnamefont {Dale~E.}\
+  \bibnamefont {Varberg}},\ }\href
+  {https://www.amazon.com/Convex-Functions-Pure-Applied-Mathematics/dp/0125897405?SubscriptionId=0JYN1NVW651KCA56C102&tag=techkie-20&linkCode=xm2&camp=2025&creative=165953&creativeASIN=0125897405}
+  {\emph {\bibinfo {title} {Convex Functions}}},\ Pure \& Applied Mathematics\
+  (\bibinfo  {publisher} {Academic Press Inc},\ \bibinfo {year}
+  {1973})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Golub}\ and\ \citenamefont
+  {Loan}(1996)}]{GolubVanLoan1996}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Gene~H.}\ \bibnamefont
+  {Golub}}\ and\ \bibinfo {author} {\bibfnamefont {Charles F.~Van}\
+  \bibnamefont {Loan}},\ }\href
+  {https://www.amazon.com/Computations-Hopkins-Studies-Mathematical-Sciences/dp/0801854148?SubscriptionId=0JYN1NVW651KCA56C102&tag=techkie-20&linkCode=xm2&camp=2025&creative=165953&creativeASIN=0801854148}
+  {\emph {\bibinfo {title} {Matrix Computations}}},\ \bibinfo {edition} {3rd}\
+  ed.,\ Johns Hopkins Studies in Mathematical Sciences\ (\bibinfo  {publisher}
+  {Johns Hopkins University Press},\ \bibinfo {year} {1996})\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Foucart}(2012)}]{Foucart2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Simon}\ \bibnamefont
+  {Foucart}},\ }\href
+  {http://www.math.drexel.edu/~foucart/TeachingFiles/F12/M504Lect6.pdf}
+  {\enquote {\bibinfo {title} {Lecture 6: Matrix norms and spectral radii},}\ }
+  (\bibinfo {year} {2012}),\ \bibinfo {note} {lecture notes for the course
+  NSTP187 at Drexel University, Philadelphia, PA, Fall 2012.}\BibitemShut
+  {Stop}%
+\bibitem [{\citenamefont {Wright}(1954)}]{Wright1954}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~M.}\ \bibnamefont
+  {Wright}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {An inequality
+  for convex functions},}\ }\href {\doibase 10.2307/2307675} {\bibfield
+  {journal} {\bibinfo  {journal} {Amer. Math. Monthly}\ }\textbf {\bibinfo
+  {volume} {61}},\ \bibinfo {pages} {620--622} (\bibinfo {year}
+  {1954})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pečarić}\ \emph {et~al.}(1992)\citenamefont
+  {Pečarić}, \citenamefont {Proschan},\ and\ \citenamefont
+  {Tong}}]{PecaricTong1992}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Josip~E.}\
+  \bibnamefont {Pečarić}}, \bibinfo {author} {\bibfnamefont {Frank}\
+  \bibnamefont {Proschan}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {Yung~Liang}\ \bibnamefont {Tong}},\ }\href
+  {http://www.ebook.de/de/product/3649336/josip_e_peajcariaac_y_l_tong_convex_functions_partial_orderings_and_statistical_applications.html}
+  {\emph {\bibinfo {title} {Convex Functions, Partial Orderings and Statistical
+  Applications}}},\ \bibinfo {series} {Mathematics in Science and Engineering},
+  Vol.\ \bibinfo {volume} {187}\ (\bibinfo  {publisher} {Academic Press Inc},\
+  \bibinfo {year} {1992})\BibitemShut {NoStop}%
+\end{thebibliography}%
+
 \end{document}

### 2017-11-28 prop_iop.tex
prop_iop.tex \DeclareUnicodeCharacter{00A0}{~} Add to eliminate an error...
prop_iop.tex \subsection{Expectation Values for QIVPMs} Cleaning up...

@@
 \DeclareUnicodeCharacter{0229}{\c{e}}
+\DeclareUnicodeCharacter{00A0}{~}
 \usepackage{mmap}
@@
 and $P_{i}$ is the projector onto the eigenspace of each distinct
-eigenvalue~$\lambda_{i}$. This spectral decomposition might be different
-from the one people used to~.
-
-Since $\lambda_{i}$ are distinct, $N$ may be less than $d$. Although
-we requires the eigenvalues in equation~(\ref{eq:spectrum-decomposition-distinct})
-to be distinct, we will consider the other type of spectral decomposition,
-especially $\mathbf{O}=\sum_{k=1}^{d}\lambda_{k}\proj{k}$ in lemma~\ref{lemma:observable2random-variable}
-later. Then, the Born rule of CQT tells us that the expectation value
-of the observable~$\mathbf{O}$ is given by~\cite{544199,Jaeger2007}
-\begin{equation}
-\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
+eigenvalue~$\lambda_{i}$. Compare to equation~(\ref{eq:spectrum-decomposition-distinct}),
+the spectral decomposition of $\mathbf{O}$ may be represented in
+term of outer product as $\mathbf{O}=\sum_{k=1}^{d}\lambda_{k}\proj{k}$
+which would be used in lemma~\ref{lemma:observable2random-variable}
+later. Disregard the representation of the spectral decomposition,
+it can be used to defined the expectation value of the observable~$\mathbf{O}$
+as~\cite{544199,Jaeger2007}
+\begin{equation}
+\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\Tr\left(\rho\mathbf{O}\right)=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\ .\label{eq:quantum-expectation}
 \end{equation}
@@
 and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
-for all $P\in\events$. This time, when we express the observable
-as its spectral decomposition
-
-Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
-value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
+the right-end of $\bar{\mu}$. Similar to the classical Choquet integral
+in definition~\ref{def:Choquet}, we can let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$
+and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
+where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $,
+and define the expectation value of $\mathbf{O}$ with respect to
+$\bar{\mu}$ as
 \begin{equation}

### 2017-11-30 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

@@
 \item We still decompose a random variable~$X$ into step functions, but
-we separate the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
-i.e., 
+we separate the positive and negative terms and write 
+\begin{equation}
+X=\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}\,,\label{eq:classical-decomposition}
+\end{equation}
+where 
 \begin{equation}
@@
 are all disjoint.
-\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
 \end{itemize}
@@
 Before discussing QIVPMs, we first review various notations brought
-forward from conventional quantum theory. Assume that a physical system
-is represented by a density matrix~$\rho$, and that we wish to measure
-a physical quantity~${\cal O}$ of this system, with corresponding
-observable~$\mathbf{O}$, whose spectral decomposition is given by~\cite{Griffiths1994,FraleighBeauregard1995,544199,FriedbergInselSpence2002,Jaeger2007}
+forward from the conventional quantum theory. Assume that we wish
+to measure a physical quantity~${\cal O}$ of this system, with corresponding
+observable~$\mathbf{O}$. Its spectral decomposition can either be
+represented in term of outer product or projector. Since we want to
+define the expectation value of~$\mathbf{O}$ with respect to a QIVPM
+as the classical Choquet integral in definition~\ref{def:Choquet},
+we are going to order the eigenvalues of~$\mathbf{O}$ as we ordered
+the step functions for classical random variables, and to represent
+the spectral decomposition of~$\mathbf{O}$ by~\cite{Griffiths1994,FraleighBeauregard1995,544199,FriedbergInselSpence2002,Jaeger2007}
 \begin{equation}
@@
 \end{equation}
-and $P_{i}$ is the projector onto the eigenspace of each distinct
-eigenvalue~$\lambda_{i}$. Compare to equation~(\ref{eq:spectrum-decomposition-distinct}),
-the spectral decomposition of $\mathbf{O}$ may be represented in
-term of outer product as $\mathbf{O}=\sum_{k=1}^{d}\lambda_{k}\proj{k}$
-which would be used in lemma~\ref{lemma:observable2random-variable}
-later. Disregard the representation of the spectral decomposition,
-it can be used to defined the expectation value of the observable~$\mathbf{O}$
-as~\cite{544199,Jaeger2007}
+and $P_{i}^{s}$ is the projector onto the eigenspace of each distinct
+eigenvalue~$\lambda_{i}^{s}$.
+
+For the conventional quantum theory, a physical system can be represented
+by a density matrix~$\rho$, the expectation value of the observable~$\mathbf{O}$
+is defined as~\cite{544199,Jaeger2007}
 \begin{equation}
@@
 \end{equation}
-
-Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
-and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$. Similar to the classical Choquet integral
-in definition~\ref{def:Choquet}, we can let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$
+Equation~(\ref{eq:quantum-expectation}) can be combined with definition~\ref{def:Choquet}
+to define the expectation value of $\mathbf{O}$ with respect to a
+QIVPM~$\bar{\mu}$. Similar to definition~\ref{def:Choquet}, we
+first separate the left-end and the right-end of $\bar{\mu}$ as $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$. Then, let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$
 and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $,
-and define the expectation value of $\mathbf{O}$ with respect to
-$\bar{\mu}$ as
+where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
+Finally, the expectation value of $\mathbf{O}$ with respect to a
+QIVPM~$\bar{\mu}$ is defined to be
 \begin{equation}
@@
 
-\subsection{Between Expectation Values for Classical and Quantum IVPMs\label{subsec:Between-Expectation-Values-Classical-Quantum}}
-
-Since the similarity between classical and quantum expectation values,
-we would prove some lemmas\footnote{\yutsung{functor? Galois connection?}}
-which can help us move the classical results to quantum.
+Notice that the similarity between classical Choquet integral and
+quantum expectation values as in Table~\ref{tab:compare-CIVPM-QRVPM}.
+\begin{table}
+\caption{\label{tab:compare-CIVPM-QRVPM}Compare the similarity between the
+classical and quantum}
+\centering{}%
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+Classical & Quantum\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+CIVPM~$\bar{\mu}$ & QIVPM~$\bar{\mu}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Random variable~$X$ & Observable~$\mathbf{O}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Classical step function decomposition, equation~(\ref{eq:classical-decomposition}) & Spectral decomposition, equation~(\ref{eq:spectrum-decomposition-distinct})\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Distinct value~$x_{i}^{s}$ & Distinct eigenvalue~$\lambda_{i}^{s}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Non-overlapping sets~$E_{i}^{s}$ & Orthogonal projector~$E_{i}^{s}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & \tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & \tabularnewline\addlinespace
+\midrule 
+\addlinespace
+ & \tabularnewline\addlinespace
+\bottomrule
+\end{tabular}
+\end{table}
+\footnote{\yutsung{functor? Galois connection?}},
+
+we would prove some lemmas which can help us move the classical results
+to quantum.
 

### 2017-12-03 prop_letter_ajhs.tex
prop_letter_ajhs.tex Copied from prop_letter_ajhs.tex...

--- 2017-11-26 prop_letter.tex
@@
 
+%% ajh - SUGGESTED INTRO SENTENCE: TEXT #0 would go here.
+
 There are long-standing debates in the foundations of quantum
@@
 
-We begin with the concept of $\delta$-determinism where~$\delta$
+%% ajh "begin" doubled, replace here; two missing commas
+We start our investigation with the concept of $\delta$-determinism, where~$\delta$
 quantifies the effect of finite-precision uncertainties on measurement
@@
 imperfections on contextuality. When $\delta=0$, the generalized
-theorem reduces to the conventional one but as $\delta$ varies from 0
+theorem reduces to the conventional one, but as $\delta$ varies from 0
 to 1 we note a transition from contextuality to non-contextuality.
@@
 % and imperfections on contextuality.  
-In more detail, the quantum-mechanical requirement for contextuality
+%% ajh kill "In more detail"
+%% ajh -  LONG SUGGESTED TEXT #1 would go here
+The quantum-mechanical requirement for contextuality
 continues to hold, thus maintaining the Kochen-Specker result for a
@@
 presenting a theory in which there is a \emph{parameter} interpolating
-between what appeared previously to be irreconcilable interpretations
+between what appeared previously to be irreconcilable aspects %interpretations
 of contextuality.
+% ajh- above: I think "interpretations" is not quite right -> "aspects"?
 
@@
 Gleason's theorem. 
+%% ajh: above starting at "We then demonstrate" LONG SUGGESTED TEXT #2
+%% would go here: use PLURAL, ball -> balls, and then, to me, it would
+%% be better as "..converges to a dense set of points."
+
 %% We furthermore establish a mathematical correlation between the sizes
@@
 probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$ is
-the set of all events, projectors on a given Hilbert space, subject to the
+the set of all events, (i.e., projectors on a given Hilbert space), %% ajh ()
+subject to the 
 following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
@@
 
+%% ajh: Inverted logic: LONG SUGGESTED TEXT #3 would go here
 A conventional quantum probability measure can easily be constructed
@@
 
+%% ajh: big problems here: LONG SUGGESTED TEXT #5 would go here.  To
+%% begin with, "axioms" is COMPLETELY undefined, appears NOWHERE in
+%% the text except here.  So either NAME and LIST (instead of inline
+%% text)  the several statements around Eq. (6) as axioms, or use
+%% another term.  In addition the english "state of the quantum" is
+%% wrong here.  Including fixing that, I would replace the first two
+%% sentences by TEXT # 5.  It's really strangely written.
 The above axioms describe a mathematical idealization in which the
-state of the quantum is known and involving infinitely precise
+%%state of the quantum is known and involving infinitely precise
+quantum state is known and involving infinitely precise
 measurements. In an actual experimental setup with an ensemble of
@@
 next.
+%% ajh; previous sentence: I am aware of no previous definition of the
+%% concept of "the constraints needed to maintain coherence" or what
+%% that possibly means in definable sense. I do not know how to fix
+%% it, or even if anyone else has trouble with this phrase as I did.
 
@@
 
+%% ajh: inverted logic and phrasing.  I would start at "To formalize
+%% this ..." and replace all the way to Eq (9) by LONG SUGGESTED TEXT
+%% #6,  which coherently introduces the "core" and sets if off as a
+%% DEFINITION, etc. 
 We now show that our definition of QIVPMs is consistent with classical
@@
 
+%%ajh: This story order is incomprehensible.  In my suggested
+%% replacement: LONG SUGGESTED TEXT #7, I would state FIRST that 'here
+%% is the outline of the proof', and LAST 'Thm 1..., whose full proof
+%% will appear in [44].
 The proof that QIVPMs become classical IVPMs when the space of events
@@
 
+%% ajh - inverted narrative order, suggested fix in 
+%%   LONG SUGGESTED TEXT #8 would go here
 The importance of this property is that it is violated in
@@
 0-deterministic QIVPM by changing 0 to $\imposs$ and 1 to
-$\necess$. The result follows is every 0-deterministic QIVPM is a
-$\delta$-deterministic one.
+$\necess$.  It follows that every 0-deterministic QIVPM is
+$\delta$-deterministic.
+%% ajh: Fixed garbled sentence.
 
@@
 
-\begin{thm}[Empty Core for General
+\begin{thm}[Empty Cores Exist for General
   QIVPMs]\label{thm:Non-extensible-of-Gleason's}There exists a Hilbert
-  space and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ such
+  space  ${\cal H}$ and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ such
   that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
+%% ajh: fixed garbled statement, add ${\cal H}$
 
@@
 where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
-we assumed the core is non-empty $\muB_{\rho}(P)\in\bar{\mu}(P)$, then
-$\bar{\mu}(\proj{0})=\imposs=[0,0]$ from Table~\ref{tab:non-Born-QIVPM} requires
+we assumed the core $\coreBorn\left(\bar{\mu},\events\right)$ 
+is non-empty, so  $\muB_{\rho}(P)\in\bar{\mu}(P)$, and 
+Table~\ref{tab:non-Born-QIVPM} tells us that
+$\bar{\mu}(\proj{0})=\imposs=[0,0]$, we must conclude that
 $\muB_{\rho}(P)=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
-Therefore, $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
+If this is true, then $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
 for all~$j$. The last equation never holds, proving the theorem.
+%%ajh: garbled argument starting at 'Since we assumed', tried to fix.
 
@@
 
-Thm.~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
+%% ajh: no abbreviations as first words of sentences.
+Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
 theorem in the sense that it accounts for a larger class of probability measures that includes
@@
 done by restricting our previous quantum probability measure
-$\muB_{\rho}$ to a commuting subspace of
-event~$\eventsC$ generated by $\proj{0}$, $\proj{1}$, $\proj{2}$,
-and $\proj{3}$. The restricted function
-$\mu=\muB_{\rho}|_{\eventsC}$ is a classical probability
+$\muB_{\rho}$ to the space of events  $\eventsC$  generated by the
+mutually commuting projectors $\proj{0}$, $\proj{1}$, $\proj{2}$, and
+$\proj{3}$.  The restricted function
+$\mu=\muB_{\rho}|_{\eventsC}$ is then a classical probability
 measure, and the induced map $\ultramodular\circ\mu$ fails to be
-a classical IVPM for the same reason as the quantum case.
+a classical IVPM for the same reason as in the quantum case.
+%% ajh: sentence "This can be done..." is somehow garbled, tried to
+%% fix.  $\eventsC$ is by DEFINITION a commuting subspace, so the
+%% original sentence does not seem to have any meaning.  Are there
+%% MORE mutually commuting projectors in $\eventsC$?  It would seem
+%% that there are no others, so this is all confusing, as that would
+%% make this sentence completely vacuous.
 

### 2017-12-03 prop_letter_ajhs.tex
From: Ortiz, Gerardo Sent: Saturday, December 02, 2017 18:17 To: Tai, Yu-Tsung <yuttai@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu> Subject: Re: AJH typo corrections and separate major suggested edits: re: AL11679 Tai
My suggestions are:

1) Put Andy's prop_letter_ajh.tex in Sharelatex AS A SEPARATE FILE.

2) Produce a NEW file prop_letter_ajhs.tex AS ANOTHER SEPARATE FILE, and
put it ALSO in Sharelatex.

In the end there will be THREE tex files that we need to compare on
Thursday. 

   Thanks,

      Gerardo

PS: If we start mixing files we will

@@
 
-%% ajh - SUGGESTED INTRO SENTENCE: TEXT #0 would go here.
+\andy{TEXT \#0 would go here.}
+  In this investigation, we explore the implications of extending
+  point-like quantum-mechanical probability measures to finite
+  intervals. 
+\andy{End of TEXT \#0}
 
@@
 %% ajh kill "In more detail"
-%% ajh -  LONG SUGGESTED TEXT #1 would go here
+\andy{TEXT \#1 would go here}
+quantum-mechanical contextuality continues to hold, maintaining the 
+Kochen-Specker result, but at a   \emph{certain fixed value} of
+$\delta$, there is a sharp transition to   \emph{non-contextuality},
+parallel in character to, say, a  phase transition.
+These results provide a new insight into the Meyer-Mermin debate by
+presenting a theory in which there is a \emph{parameter} interpolating
+between what appeared previously to be irreconcilable aspects
+of contextuality.
+\andy{End of \#1}
 The quantum-mechanical requirement for contextuality
@@
 Gleason's theorem. 
+\andy{TEXT \#2 would go here}
+We then demonstrate that all QIVPMs in this class are
+consistent with non-empty ``balls'' of quantum states whose radii
+correspond to the lengths of the intervals characterizing the
+uncertainties.  As the sizes of the intervals go to zero, these balls
+of quantum states converge to a dense, continuous, set of points
+representing the unique states consistent with the Born rule and
+Gleason's theorem.
+\andy{End of TEXT \#2}
 %% ajh: above starting at "We then demonstrate" LONG SUGGESTED TEXT #2
@@
 
-%% ajh: Inverted logic: LONG SUGGESTED TEXT #3 would go here
+%% ajh: Inverted logic: LONG SUGGESTED 
+\andy{TEXT \#3 would go here}
+A conventional quantum probability measure can easily be constructed
+using the Born rule if one knows the current state of the quantum
+system.  Specifically, for each pure normalized quantum
+state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
+$\muB_{\phi}$ defined as
+$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
+generalizes to mixed states
+$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
+$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
+induces a probability measure $\muB_{\rho}$ defined as
+$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
+\sum_{j=1}^{N}
+q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
+\andy{End of TEXT \#3}
 A conventional quantum probability measure can easily be constructed
@@
 
-%% ajh: big problems here: LONG SUGGESTED TEXT #5 would go here.  To
+%% ajh: big problems here: LONG SUGGESTED 
+\andy{TEXT \#5 would go here.}
+The above construction assumes a mathematical idealization
+having known quantum state and infinitely precise measuring
+instruments.  In an actual experimental setup with an ensemble of
+quantum states that would ideally be identical, but are not actually
+identically prepared, with imperfections and inaccuracies in the
+measuring devices,  an experimenter might only be able to determine
+that the probability of an event $P$ is concentrated in the range
+$[0.49,0.51]$ instead of being precisely $0.5$.   The spread in this
+range depends on the amount of resources (time, energy, money, etc.)
+that are devoted to the experiment.  In the classical setting, this
+``fuzziness'' can be formalized by moving to \emph{interval-valued
+  probability measures} (IVPMs), which we explore in the next section,
+along with our proposed extension to the quantum domain.
+\andy{End of TEXT \#5}
+%% To
 %% begin with, "axioms" is COMPLETELY undefined, appears NOWHERE in
@@
 %% ajh: inverted logic and phrasing.  I would start at "To formalize
-%% this ..." and replace all the way to Eq (9) by LONG SUGGESTED TEXT
-%% #6,  which coherently introduces the "core" and sets if off as a
+%% this ..." and replace all the way to Eq (9) by LONG SUGGESTED 
+\andy{TEXT \#6}
+We now show that our definition of QIVPMs is consistent
+with classical IVPMs in the sense that a restriction of QIVPMs to
+mutually commuting events recovers the definition of classical
+IVPMs.  However, we must refine this context for the quantum case,
+defining a QIVPM  $\bar{\mu}$ to be \emph{consistent} with a state $\rho$ and
+projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
+probability calculated by the Born
+rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007} , i.e, if:
+
+ To formalize this connection, we first note that in contrast to
+the case with conventional quantum probability spaces, there is
+generally no unique state~$\rho$ consistent with a QIVPM. We say that
+a QIVPM $\bar{\mu}$ is \emph{consistent} with a state $\rho$ and
+projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
+probability calculated by the Born rule,
+  \begin{equation}
+  \muB_{\rho}\left(P\right) = \Tr\left(\rho
+  P\right)\in\bar{\mu}\left(P\right)\ .
+  \end{equation}
+In contrast with conventional probability spaces, there is \emph{no
+guarantee} that a unique state $\rho$ consistent with a QIVPM exists.
+
+  We next refine the concept of consistency by introducing the idea of
+a ``core'' set of states relative to subspaces. First, we define
+$\events'$ as a \emph{subspace} of a set of events if $\events$ if
+$\events'$ contains  $\mathbb{0}$ and $\mathbb{1}$ and is closed under
+complements, sums, and products.  In particular, for any
+projector~$P\in\events'$, we have
+$\mathbb{1}-P\in\events'$ and for each pair of commuting
+projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
+$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$.
+
+\begin{definition}[The core of a probability measure] The \emph{core}
+$\coreBorn\left(\bar{\mu},\events'\right)$ of a probability measure 
+$\bar{\mu}$ relative to a subspace of events $\events'$ is the
+collection of all states $\rho$ that are \emph{consistent} with 
+$\bar{\mu}$ on every projector in $\events'$, that is
+\begin{equation}
+\label{eq:hbar}
+\coreBorn\left(\bar{\mu},\events'\right) = \set{\rho}{\forall P\in
+\events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)} \ .
+\end{equation}
+\end{definition}
+\andy{End of TEXT \#6}
+%% which coherently introduces the "core" and sets if off as a
 %% DEFINITION, etc. 
@@
 %%ajh: This story order is incomprehensible.  In my suggested
-%% replacement: LONG SUGGESTED TEXT #7, I would state FIRST that 'here
+%% replacement: LONG SUGGESTED 
+\andy{TEXT \#7}
+   The general idea of the proof that QIVPMs become classical
+IVPMs when the space of events includes only mutually commuting
+events depends on showing the existence of a non-empty core for such
+commuting events.  The first step in establishing this assertion is to
+to take a subspace $\eventsC$ of mutually commuting events, construct
+a partial orthonormal basis by diagonalization, and complete this to a
+full orthonormal basis  $\overline{\eventsC}$.  We then
+build a bijection between the QIVPM on the set of projectors
+associated with this basis and the set of classical events
+corresponding to this basis.  Using this correspondence together with a
+classical result by
+Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
+we can establish that for the special case of commuting events, a
+QIVPM will always have a non-empty core~\footnote{Shapley's result
+  proves that a classical IVPM always contains at least one state that
+  is consistent with every event.}.  This leads to
+\begin{thm}[Non-empty Core for Compatible Measurements] \label{thm:Shapley}
+  For every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
+  of events~$\eventsC\subseteq\events$ commutes, then
+  $\coreBorn\left(\bar{\mu},\eventsC\right)\ne\emptyset$,
+\end{thm}
+whose full proof will appear in ~\cite{TaiThesis2018}.
+\andy{End of TEXT \#7}
+%% I would state FIRST that 'here
 %% is the outline of the proof', and LAST 'Thm 1..., whose full proof
@@
 %% ajh - inverted narrative order, suggested fix in 
-%%   LONG SUGGESTED TEXT #8 would go here
+%%   LONG SUGGESTED 
+\andy{TEXT \#8 would go here}
+The importance of the existence of empty cores combined with
+  the conditions guaranteeing non-empty cores is that one cannot
+  guarantee non-empty cores for finite-precision attempts at proving
+  Gleason's theorem by extending the Born measure
+  $\muB_{\rho}\left(P\right)$ to QIVPMs $\bar{\mu}\left(P\right)$.  We
+  will show in  Sec.~\ref{sec:Gleason} that a core defined by the set
+  of states $\coreBorn\left(\bar{\mu},\events'\right)$ that is
+  consistent with some arbitrary (not necessarily commuting)
+  events~$\events'$  and a particular QIVPM  $\bar{\mu}$
+   \emph{may be empty}.
+\andy{End of TEXT \#8}
 The importance of this property is that it is violated in

### 2017-12-04 prop_letter_ajhs.tex
From: Hanson, Andrew J. Sent: Monday, December 04, 2017 1:18 To: Tai, Yu-Tsung <yuttai@indiana.edu> Cc: Hanson, Andrew J. <hansona@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: #3 corrected. RE: AJH typo corrections and separate major suggested edits: re: AL11679 Tai
Hi -  missed that - the "**" meant it was copied and I was supposed to
edit it and erase the "**": Here is the correct #3, which my be too
simple, but it seemed to me that the thought of the last paragraph at
the bottom of p2/top of p3 was written backwards, and could be made
clearer

@@
 \andy{TEXT \#3 would go here}
-A conventional quantum probability measure can easily be constructed
-using the Born rule if one knows the current state of the quantum
-system.  Specifically, for each pure normalized quantum
-state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
-$\muB_{\phi}$ defined as
-$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
-generalizes to mixed states
-$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
-$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
-induces a probability measure $\muB_{\rho}$ defined as
-$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
-\sum_{j=1}^{N}
-q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
+If all the conditions are satisfied, and one knows all the
+  $\ket{\phi_j} = \sum_{k=1}^{d}\alpha_{k}\ket{k}$ representing
+the current state $\rho$ of the quantum system, then a conventional
+probability measure can easily be
+constructed~\citep{Born1983bibTeX,Mermin2007,Jaeger2007},  taking the 
+form
+\[ \muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
+\sum_{j=1}^{N}  q_{j}\muB_{\phi_{j}}\left(P\right) \ . \]
 \andy{End of TEXT \#3}

### 2017-12-04 prop_letter.tex
Git Test
prop_letter.tex prop_letter_ajh.tex prop_letter_ajhs.tex Fix a typo...

@@
 $\bar{\mu}(\proj{0})=\imposs=[0,0]$ from Table~\ref{tab:non-Born-QIVPM} requires
-$\muB_{\rho}(P)=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
+$\muB_{\rho}(\proj{0})=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
 Therefore, $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$

### 2017-12-04 prop_letter_ajh.tex
prop_letter.tex prop_letter_ajh.tex prop_letter_ajhs.tex Fix a typo...

--- 2017-12-03 prop_letter_ajhs.tex
@@
 $\bar{\mu}(\proj{0})=\imposs=[0,0]$, we must conclude that
-$\muB_{\rho}(P)=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
+$\muB_{\rho}(\proj{0})=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
 If this is true, then $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$

### 2017-12-05 prop_letter_ajhs.tex
prop_letter_ajhs.tex \newenvironment{andySuggest}[1] defined...

@@
 \usepackage{framed}
+\usepackage{comment}
 
@@
 \newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{blue}{Andy says: #1}\end{minipage}}}
+% \excludecomment{andySuggest}
+\newenvironment{andySuggest}[1]{\andy{TEXT \# #1 would go here.}}{\andy{End of SUGGESTED TEXT.}}
 
@@
 
-\andy{TEXT \#0 would go here.}
+\begin{andySuggest}{0}
   In this investigation, we explore the implications of extending
@@
   intervals. 
-\andy{End of TEXT \#0}
+\end{andySuggest}
 
@@
 %% ajh kill "In more detail"
-\andy{TEXT \#1 would go here}
+\begin{andySuggest}{1}
 quantum-mechanical contextuality continues to hold, maintaining the 
@@
 of contextuality.
-\andy{End of \#1}
+\end{andySuggest}
 The quantum-mechanical requirement for contextuality
@@
 Gleason's theorem. 
-\andy{TEXT \#2 would go here}
+\begin{andySuggest}{2}
 We then demonstrate that all QIVPMs in this class are
@@
 Gleason's theorem.
-\andy{End of TEXT \#2}
+\end{andySuggest}
 %% ajh: above starting at "We then demonstrate" LONG SUGGESTED TEXT #2
@@
 %% ajh: Inverted logic: LONG SUGGESTED 
-\andy{TEXT \#3 would go here}
+\begin{andySuggest}{3}
 If all the conditions are satisfied, and one knows all the
@@
 \sum_{j=1}^{N}  q_{j}\muB_{\phi_{j}}\left(P\right) \ . \]
-\andy{End of TEXT \#3}
+\end{andySuggest}
 A conventional quantum probability measure can easily be constructed
@@
 %% ajh: big problems here: LONG SUGGESTED 
-\andy{TEXT \#5 would go here.}
+\begin{andySuggest}{5}
 The above construction assumes a mathematical idealization
@@
 along with our proposed extension to the quantum domain.
-\andy{End of TEXT \#5}
+\end{andySuggest}
 %% To
@@
 %% this ..." and replace all the way to Eq (9) by LONG SUGGESTED 
-\andy{TEXT \#6}
+\begin{andySuggest}{6}
 We now show that our definition of QIVPMs is consistent
@@
 \end{definition}
-\andy{End of TEXT \#6}
+\end{andySuggest}
 %% which coherently introduces the "core" and sets if off as a
@@
 %% replacement: LONG SUGGESTED 
-\andy{TEXT \#7}
+\begin{andySuggest}{7}
    The general idea of the proof that QIVPMs become classical
@@
 whose full proof will appear in ~\cite{TaiThesis2018}.
-\andy{End of TEXT \#7}
+\end{andySuggest}
 %% I would state FIRST that 'here
@@
 %%   LONG SUGGESTED 
-\andy{TEXT \#8 would go here}
+\begin{andySuggest}{8}
 The importance of the existence of empty cores combined with
@@
    \emph{may be empty}.
-\andy{End of TEXT \#8}
+\end{andySuggest}
 The importance of this property is that it is violated in

### 2017-12-05 prop_letter_ajhs.tex
From: Tai, Yu-Tsung Sent: Tuesday, December 05, 2017 15:16 To: Hanson, Andrew J. <hansona@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: RE: AJH typo corrections and separate major suggested edits: re: AL11679 Tai
Dear Prof. Hanson,

I merged your updated #3 into prop_letter_ajhs.tex... However, in your
suggested text #3, $\ket{k}$ and $\muB_{\phi_{j}}$ haven't been defined,
"the Born rule" haven't been mentioned, and the relation between pure
and mixed states are not precise enough... etc. How about deleting the
sentence for the pure state in

@@
 \usepackage{comment}
+\usepackage{xparse}
 
@@
 
-\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
-\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
-\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
-\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{blue}{Andy says: #1}\end{minipage}}}
-% \excludecomment{andySuggest}
-\newenvironment{andySuggest}[1]{\andy{TEXT \# #1 would go here.}}{\andy{End of SUGGESTED TEXT.}}
+\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
+\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
+\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
+\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
+\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
+% \excludecomment{suggest}
+\NewDocumentEnvironment{suggest}{m m}{#1{TEXT \# #2 would go here.}}{#1{TEXT \# #2 end here.}}
 
@@
 
-\begin{andySuggest}{0}
+\begin{suggest}{\andy}{0}
   In this investigation, we explore the implications of extending
@@
   intervals. 
-\end{andySuggest}
+\end{suggest}
 
@@
 %% ajh kill "In more detail"
-\begin{andySuggest}{1}
+\begin{suggest}{\andy}{1}
 quantum-mechanical contextuality continues to hold, maintaining the 
@@
 of contextuality.
-\end{andySuggest}
+\end{suggest}
 The quantum-mechanical requirement for contextuality
@@
 Gleason's theorem. 
-\begin{andySuggest}{2}
+\begin{suggest}{\andy}{2}
 We then demonstrate that all QIVPMs in this class are
@@
 Gleason's theorem.
-\end{andySuggest}
+\end{suggest}
 %% ajh: above starting at "We then demonstrate" LONG SUGGESTED TEXT #2
@@
 %% ajh: Inverted logic: LONG SUGGESTED 
-\begin{andySuggest}{3}
+\begin{suggest}{\yutsung}{3}
+A conventional quantum probability measure can easily be constructed
+using the Born rule if one knows the current state of the quantum
+system.  Specifically, for each mixed states $\rho =
+\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j >
+0$, and $\sum_{j=1}^{N}q_{j}=1$, the Born rule
+induces a probability measure~$\muB_{\rho}$ defined as
+$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
+\sum_{j=1}^{N}
+\melem{\phi_{j}}{P}{\phi_{j}}$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
+\end{suggest}
+\begin{suggest}{\andy}{3}
 If all the conditions are satisfied, and one knows all the
@@
 \sum_{j=1}^{N}  q_{j}\muB_{\phi_{j}}\left(P\right) \ . \]
-\end{andySuggest}
+\end{suggest}
 A conventional quantum probability measure can easily be constructed
@@
 %% ajh: big problems here: LONG SUGGESTED 
-\begin{andySuggest}{5}
+\begin{suggest}{\andy}{5}
 The above construction assumes a mathematical idealization
@@
 along with our proposed extension to the quantum domain.
-\end{andySuggest}
+\end{suggest}
 %% To
@@
 %% this ..." and replace all the way to Eq (9) by LONG SUGGESTED 
-\begin{andySuggest}{6}
+\begin{suggest}{\andy}{6}
 We now show that our definition of QIVPMs is consistent
@@
 \end{definition}
-\end{andySuggest}
+\end{suggest}
 %% which coherently introduces the "core" and sets if off as a
@@
 %% replacement: LONG SUGGESTED 
-\begin{andySuggest}{7}
+\begin{suggest}{\andy}{7}
    The general idea of the proof that QIVPMs become classical
@@
 whose full proof will appear in ~\cite{TaiThesis2018}.
-\end{andySuggest}
+\end{suggest}
 %% I would state FIRST that 'here
@@
 %%   LONG SUGGESTED 
-\begin{andySuggest}{8}
+\begin{suggest}{\andy}{8}
 The importance of the existence of empty cores combined with
@@
    \emph{may be empty}.
-\end{andySuggest}
+\end{suggest}
 The importance of this property is that it is violated in

### 2017-12-07 prop_letter_ajhs.tex
prop_letter_ajhs.tex Moved Andy's comments from comment to "Andy says:"

@@
 % \excludecomment{suggest}
-\NewDocumentEnvironment{suggest}{m m}{#1{TEXT \# #2 would go here.}}{#1{TEXT \# #2 end here.}}
+\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
 
@@
 Gleason's theorem. 
-\begin{suggest}{\andy}{2}
+\begin{suggest}{\andy}{2}[use PLURAL, ball -> balls, and then, to me, it would
+be better as "..converges to a dense set of points."]
 We then demonstrate that all QIVPMs in this class are
@@
 \end{suggest}
-%% ajh: above starting at "We then demonstrate" LONG SUGGESTED TEXT #2
-%% would go here: use PLURAL, ball -> balls, and then, to me, it would
-%% be better as "..converges to a dense set of points."
 
@@
 
-%% ajh: Inverted logic: LONG SUGGESTED 
 \begin{suggest}{\yutsung}{3}
@@
 
-%% ajh: big problems here: LONG SUGGESTED 
-\begin{suggest}{\andy}{5}
+\begin{suggest}{\andy}{5}[To
+begin with, "axioms" is COMPLETELY undefined, appears NOWHERE in
+the text except here.  So either NAME and LIST (instead of inline
+text)  the several statements around Eqs.~(\ref{eq:QIVPM-constraints}) as axioms, or use
+another term.  In addition the english "state of the quantum" is
+wrong here.  Including fixing that, I would replace the first two
+sentences by TEXT \# 5.  It's really strangely written.]
 The above construction assumes a mathematical idealization
@@
 \end{suggest}
-%% To
-%% begin with, "axioms" is COMPLETELY undefined, appears NOWHERE in
-%% the text except here.  So either NAME and LIST (instead of inline
-%% text)  the several statements around Eq. (6) as axioms, or use
-%% another term.  In addition the english "state of the quantum" is
-%% wrong here.  Including fixing that, I would replace the first two
-%% sentences by TEXT # 5.  It's really strangely written.
+
 The above axioms describe a mathematical idealization in which the
@@
 
-%% ajh: inverted logic and phrasing.  I would start at "To formalize
-%% this ..." and replace all the way to Eq (9) by LONG SUGGESTED 
-\begin{suggest}{\andy}{6}
+\begin{suggest}{\andy}{6}[inverted logic and phrasing.  I would start at "To formalize
+this ..." and replace all the way to Eq.~(\ref{eq:hbar})]
 We now show that our definition of QIVPMs is consistent
@@
 
-%%ajh: This story order is incomprehensible.  In my suggested
-%% replacement: LONG SUGGESTED 
-\begin{suggest}{\andy}{7}
+\begin{suggest}{\andy}{7}[This story order is incomprehensible. I would state FIRST that 'here
+is the outline of the proof', and LAST 'Thm 1..., whose full proof
+will appear in~\cite{TaiThesis2018}.]
    The general idea of the proof that QIVPMs become classical
@@
 \end{suggest}
-%% I would state FIRST that 'here
-%% is the outline of the proof', and LAST 'Thm 1..., whose full proof
-%% will appear in [44].
 The proof that QIVPMs become classical IVPMs when the space of events
@@
 
-%% ajh - inverted narrative order, suggested fix in 
-%%   LONG SUGGESTED 
-\begin{suggest}{\andy}{8}
+\begin{suggest}{\andy}{8}[inverted narrative order]
 The importance of the existence of empty cores combined with

### 2017-12-07 prop_letter_ajhs.tex
prop_letter_ajhs.tex Resolving SUGGEST TEXT #3....

@@
 
-\begin{suggest}{\yutsung}{3}
 A conventional quantum probability measure can easily be constructed
-using the Born rule if one knows the current state of the quantum
-system.  Specifically, for each mixed states $\rho =
-\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j >
-0$, and $\sum_{j=1}^{N}q_{j}=1$, the Born rule
-induces a probability measure~$\muB_{\rho}$ defined as
-$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
-\sum_{j=1}^{N}
-\melem{\phi_{j}}{P}{\phi_{j}}$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
-\end{suggest}
-\begin{suggest}{\andy}{3}
-If all the conditions are satisfied, and one knows all the
-  $\ket{\phi_j} = \sum_{k=1}^{d}\alpha_{k}\ket{k}$ representing
-the current state $\rho$ of the quantum system, then a conventional
-probability measure can easily be
-constructed~\citep{Born1983bibTeX,Mermin2007,Jaeger2007},  taking the 
-form
-\[ \muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
-\sum_{j=1}^{N}  q_{j}\muB_{\phi_{j}}\left(P\right) \ . \]
-\end{suggest}
-A conventional quantum probability measure can easily be constructed
-using the Born rule if one knows the current state of the quantum
+using the Born rule if one knows the current pure state of the quantum
 system.  Specifically, for each pure normalized quantum

### 2017-12-07 prop_letter_ajhs.tex
meeting of dec 7

@@
 
-\begin{suggest}{\andy}{0}
 In this investigation, we explore the implications of extending
-  point-like quantum-mechanical probability measures to finite
-  intervals. 
-\end{suggest}
+conventional quantum-mechanical probability measures to include the
+effect of imprecise measurements.
 
@@
 %% ajh "begin" doubled, replace here; two missing commas
-We start our investigation with the concept of $\delta$-determinism, where~$\delta$
-quantifies the effect of finite-precision uncertainties on measurement
-outcomes. We recast the Kochen-Specker theorem using
+We start our investigation with the concept of $\delta$-determinism,
+where~$\delta$ quantifies the effect of finite-precision uncertainties
+on measurement outcomes. We recast the Kochen-Specker theorem using
 $\delta$-determinism to quantify the effects of finite precision and
@@
 theorem reduces to the conventional one, but as $\delta$ varies from 0
-to 1 we note a transition from contextuality to non-contextuality.
-% A principal result is that recasting the Kochen-Specker theorem in 
-% terms of ``$\delta$-determinism,'' with~$\delta$ quantifying the 
-% effect of finite-precision uncertainties on measurement outcomes, 
-% reducing to the purely deterministic Kochen-Specker case for 
-% $\delta=0$, can resolve the question of the effect of finite precision 
-% and imperfections on contextuality.  
-%% ajh kill "In more detail"
-\begin{suggest}{\andy}{1}
-quantum-mechanical contextuality continues to hold, maintaining the 
-Kochen-Specker result, but at a   \emph{certain fixed value} of
-$\delta$, there is a sharp transition to   \emph{non-contextuality},
-parallel in character to, say, a  phase transition.
-These results provide a new insight into the Meyer-Mermin debate by
-presenting a theory in which there is a \emph{parameter} interpolating
-between what appeared previously to be irreconcilable aspects
-of contextuality.
-\end{suggest}
+to 1 we note a transition from contextuality to non-contextuality. For
+a \emph{non-vanishing} range of $\delta$, quantum-mechanical
+contextuality continues to hold, maintaining the Kochen-Specker
+result, but at a \emph{certain fixed value}, $\delta = \frac{1}{3}$,
+there is a sharp transition to \emph{non-contextuality}, parallel in
+character to a phase transition.  These results provide a new insight
+into the Meyer-Mermin debate by presenting a theory in which there is
+a \emph{parameter} interpolating between what appeared previously to
+be irreconcilable aspects of contextuality.
+
 The quantum-mechanical requirement for contextuality
@@
 class are consistent with a non-empty ``ball'' of quantum states whose
-radius is defined by the maximal length of the
-intervals characterizing the uncertainties. As the size of the intervals  
-goes to zero, this ball of quantum states converges to a
-point representing the unique state consistent with the Born rule and 
-Gleason's theorem. 
-\begin{suggest}{\andy}{2}[use PLURAL, ball -> balls, and then, to me, it would
-be better as "..converges to a dense set of points."]
-We then demonstrate that all QIVPMs in this class are
-consistent with non-empty ``balls'' of quantum states whose radii
-correspond to the lengths of the intervals characterizing the
-uncertainties.  As the sizes of the intervals go to zero, these balls
-of quantum states converge to a dense, continuous, set of points
-representing the unique states consistent with the Born rule and
-Gleason's theorem.
-\end{suggest}
-
-%% We furthermore establish a mathematical correlation between the sizes
-%% of the intervals and the volume of states that are all consistent with
-%% an imprecise measurement.  \andy{``volume of states" are not defined
-%%   in the Gleason's section.}
+radius is defined by the maximal length of the intervals
+characterizing the uncertainties. As the size of the intervals goes to
+zero, this ball of quantum states converges to a point representing
+the unique state consistent with the Born rule and Gleason's theorem.
 
@@
 A conventional quantum probability measure can easily be constructed
-using the Born rule if one knows the current pure state of the quantum
-system.  Specifically, for each pure normalized quantum
-state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
-$\muB_{\phi}$ defined as
-$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
-generalizes to mixed states
-$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
-$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
-induces a probability measure $\muB_{\rho}$ defined as
-$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
-\sum_{j=1}^{N}
+using the Born rule if one knows the current pure normalized quantum
+state $\ket{\phi} \in {\cal H}$; then the Born rule induces a
+probability measure $\muB_{\phi}$ defined as
+$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. For mixed states
+$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
+$\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and $\sum_{j=1}^{N}q_{j}=1$,
+the generalized Born rule induces a probability measure $\muB_{\rho}$
+defined as
+$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) = \sum_{j=1}^{N}
 q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
@@
 
-\begin{suggest}{\andy}{5}[To
-begin with, "axioms" is COMPLETELY undefined, appears NOWHERE in
-the text except here.  So either NAME and LIST (instead of inline
-text)  the several statements around Eqs.~(\ref{eq:QIVPM-constraints}) as axioms, or use
-another term.  In addition the english "state of the quantum" is
-wrong here.  Including fixing that, I would replace the first two
-sentences by TEXT \# 5.  It's really strangely written.]
-The above construction assumes a mathematical idealization
-having known quantum state and infinitely precise measuring
-instruments.  In an actual experimental setup with an ensemble of
-quantum states that would ideally be identical, but are not actually
-identically prepared, with imperfections and inaccuracies in the
-measuring devices,  an experimenter might only be able to determine
-that the probability of an event $P$ is concentrated in the range
-$[0.49,0.51]$ instead of being precisely $0.5$.   The spread in this
-range depends on the amount of resources (time, energy, money, etc.)
-that are devoted to the experiment.  In the classical setting, this
-``fuzziness'' can be formalized by moving to \emph{interval-valued
-  probability measures} (IVPMs), which we explore in the next section,
-along with our proposed extension to the quantum domain.
-\end{suggest}
-
-The above axioms describe a mathematical idealization in which the
-%%state of the quantum is known and involving infinitely precise
-quantum state is known and involving infinitely precise
-measurements. In an actual experimental setup with an ensemble of
-quantum states whose states are unknown, that are not exactly
-identically prepared, and with small imperfections and inaccuracies in
-measuring devices, an experimenter might only be able to determine
-that the probability of an event $P$ is concentrated in the range
-$[0.49,0.51]$ instead of being precisely $0.5$. The spread in this
-range depends on the amount of resources (time, energy, money, etc.)
-that are devoted to the experiment. In the classical setting, this
-``fuzziness'' can be formalized by moving to \emph{interval-valued
-  probability measures} (IVPMs), which we explore in the next section,
-along with our proposed extension to the quantum domain.
+The quantum probability postulates assume a mathematical idealization
+in which quantum states and measurements are both infinitely
+precise. In an actual experimental setup with an ensemble of quantum
+states that would ideally be identical, but are not actually
+identically prepared, with imperfections and inaccuracies in measuring
+devices, an experimenter might only be able to determine that the
+probability of an event $P$ is concentrated in the range $[0.49,0.51]$
+instead of being precisely $0.5$. The spread in this range depends on
+the amount of resources (time, energy, money, etc.)  that are devoted
+to the experiment. In the classical setting, this ``fuzziness'' can be
+formalized by moving to \emph{interval-valued probability measures}
+(IVPMs), which we explore in the next section, along with our proposed
+extension to the quantum domain.
 
@@
 interval could be interpreted as the Gaussian width of a probability
-distribution. We, however, use general intervals with no constraints
-other than the ones needed to maintain coherence: these are described
-next.
-%% ajh; previous sentence: I am aware of no previous definition of the
-%% concept of "the constraints needed to maintain coherence" or what
-%% that possibly means in definable sense. I do not know how to fix
-%% it, or even if anyone else has trouble with this phrase as I did.
-
-First, for each interval $[\ell,r]$ we have the natural constraint
+distribution.
+
+We next introduce probability axioms for IVPMs. First, for each
+interval $[\ell,r]$ we have the natural constraint
 $0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
@@
 include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
-refer to the probability interval for impossible events
-and events that are certain. We can write this, respectively, as
-$\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$ is
-the empty set and $\Omega$ is the event covering the entire
-sample space.  For each interval $[\ell,r]$, we also need the dual
-interval $[1-r,1-\ell]$ so that if one interval refers to the
-probability of an event~$E$, the dual refers to the probability of the
-event's complement $\overline{E}$.  For example, if we discover as a
-result of an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$,
-we may conclude that $\mu\left(\overline{E}\right) = [0.7,0.8]$ for the
+refer to the probability interval for impossible events and events
+that are certain. We can write this, respectively, as
+$\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$
+is the empty set and $\Omega$ is the event covering the entire sample
+space.  For each interval $[\ell,r]$, we also need the dual interval
+$[1-r,1-\ell]$ so that if one interval refers to the probability of an
+event~$E$, the dual refers to the probability of the event's
+complement $\overline{E}$.  For example, if we discover as a result of
+an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$, we may
+conclude that $\mu\left(\overline{E}\right) = [0.7,0.8]$ for the
 complementary event~$\overline{E}$. In addition to these simple
@@
 
+\newpage
+
 \begin{suggest}{\andy}{6}[inverted logic and phrasing.  I would start at "To formalize
@@
 defining a QIVPM  $\bar{\mu}$ to be \emph{consistent} with a state $\rho$ and
-projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
+a projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
 probability calculated by the Born
-rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007} , i.e, if:
-
- To formalize this connection, we first note that in contrast to
-the case with conventional quantum probability spaces, there is
-generally no unique state~$\rho$ consistent with a QIVPM. We say that
-a QIVPM $\bar{\mu}$ is \emph{consistent} with a state $\rho$ and
-projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
-probability calculated by the Born rule,
+rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e., 
   \begin{equation}
@@
 %% DEFINITION, etc.
+
+\newpage
+
 We now show that our definition of QIVPMs is consistent with classical
@@
 \end{equation}
+
+\newpage
 
@@
 \end{document}
-
-The similar kind of subtleties happens when we want to define the
-expectation value of a random variable. Consider an event $E$ such
-that $\bar{\mu}(E)=[0.2,0.3]$ and $\bar{\mu}\left(\overline{E}\right)=[0.7,0.8]$.
-Given a random variable
-\begin{equation}
-X\left(\omega\right)=\begin{cases}
-1 & \textrm{, if }\omega\in E\textrm{ ;}\\
-2 & \textrm{, if }\omega\notin E\textrm{ ,}
-\end{cases}
-\end{equation}
-its expectation value with respect to $\bar{\mu}$ might be naïvely
-defined as\begin{subequations}
-\begin{eqnarray}
- &  & 1\cdot\bar{\mu}(E)+2\cdot\bar{\mu}\left(\overline{E}\right)\\
- & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
- & = & [1\cdot0.2+2\cdot0.7,1\cdot0.3+2\cdot0.8]\\
- & = & [1.6,1.9]\,.
-\end{eqnarray}
-\end{subequations}As we discussed in the previous paragraph, the
-true probability of $\bar{\mu}(E)$, $\mu(E)$, can be anywhere in
-the range $[0.2,0.3]$ and the true probability of $\bar{\mu}\left(\overline{E}\right)$
-is $\mu\left(\overline{E}\right)=1-\mu(E)$. If $\mu(E)=0.2$, the expectation
-value of $X$ with respect to $\mu$ is 
-\begin{equation}
-1\cdot\mu(E)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.2+2\cdot0.8=1.8\,;
-\end{equation}
-if $\mu(E)=0.3$, the expectation value of $X$ with respect to $\mu$
-is
-\begin{equation}
-1\cdot\mu(E)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.3+2\cdot0.7=1.7\,.
-\end{equation}
-In another word, no matter how we pick $\mu(E)$, the expectation
-value of $X$ is in $\left[1.7,1.8\right]$ which is a more realistic
-expectation value of $X$ with respect to $\bar{\mu}$. The interval~$\left[1.7,1.8\right]$
-is narrower than the naïve expectation value~$[1.6,1.9]$ because
-the naïve one combines contradicting situations in the computation.
-In general, the computation of the realistic expectation value, called
-the Choquet integral, is more complex than what we discussed because
-a random variable may have more than two values. Despite its complexity,
-it is still a weight average among the values of a random variable
-as given in the following definition.
-
-\begin{definition}[Choquet integral~\citep{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}Consider
-a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
-and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
-We decompose a random variable~$X$ into step functions, but we separate
-the positive and negative terms and write like
-\begin{equation}
-X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\mathbf{1}_{E_{i}^{s}}\,,
-\end{equation}
-where $\mathbf{1}_{E_{i}^{s}}$ is the indicator function of $E_{i}^{s}$,
-and we order the value of its range from the smallest to the largest
-\begin{equation}
-x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
-\end{equation}
- and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
-are all disjoint. Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$
-and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
-\begin{equation}
-\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,.\label{eq:interval-expectation}
-\end{equation}
-\end{definition}
-
-Although Def.~\ref{def:Choquet} looks complex, it matches with our
-intuition in the previous example. Let
-\begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,\label{eq:core}
-\end{equation}
-be the set of possible ``true'' probability measure of an IVPM~$\bar{\mu}$.
-Then, the following theorem claims the expectation value of $\bar{\mu}$
-is the range of the expectation value of the probability measure in
-the core of $\bar{\mu}$.
-
-\begin{thm}\label{thm:Rosenmuller}\citep{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}~For
-every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
-any random variable~$X:\Omega\rightarrow\mathbb{R}$, 
-\begin{equation}
-\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.
-\end{equation}
-\end{thm}
-
-%   To proceed, we use a formulation of the
-% ``Mermin-Peres square''~\cite{peres1995quantum,Mermin1990Simple}
-% that uses the expectation value of a physical observable with respect
-% to a QIVPM, where the interval-valued expectation value is consistent
-% with the expectation value of the same observable in conventional
-% quantum mechanics with infinite resources. We show that, as long as
-% errors and uncertainties remain smaller than a particular value, the
-% Kochen-Specker theorem remains valid. In other words, we established a
-% rigorous bound for its validity and, therefore, the limits for
-% physical reality to remain contextual.
-
-% \begin{thm} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
-% for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, and an
-% observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition}),
-% let $\events'$ be the minimal subspace of events containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$,
-% then 
-% \begin{equation}
-% \expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
-% \end{equation}
-% \end{thm}
-
-After we defined QIVPMs, we can easily define the expectation value
-of an observable with respect to a QIVPM by adopting the idea of the
-classical Choquet integral. Notice that the quantum expectation value~(\ref{eq:quantum-expectation})
-is the weight average among the eigenvalues with the weight~$\mu(P_{i})$.
-Similarly, given a classical random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
-the expectation value of $X$ with respect to a probability measure~$\mu$
-is the weight average among $x_{i}$ with the weight~$\mu(E_{i})$.
-Since the definition of Choquet integral is just using a more complex
-but reasonable way to compute the weight, we can apply the same algorithm
-on an observable and get the following definition.
-
-\begin{definition}Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
-and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
-the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
-for all $P\in\events$. This time, when we express the observable
-as its spectral decomposition
-\begin{equation}
-\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
-\end{equation}
-we separate the positive and negative eigenvalues and order its eigenvalues
-from the smallest to the largest 
-\begin{equation}
-\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
-\end{equation}
-Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
-where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
-Then, the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
-is defined as
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
-\end{equation}
-\end{definition}
-
-If we define the multiplication of two singleton
-sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $
-to be $\left\{ \lambda_{1}\lambda_{2}\right\} $.
-
-We will now adapt the proof above to show that it is, in general,
-impossible to have just the two intervals \imposs\ and \necess: every
-QIVPM must be parameterized by a collection of intervals that includes
-at least one additional ``fuzzy'' interval and some events must be
-associated with such uncertain intervals. The significance of this
-observation is that the uncertainty in the intervals is, in contrast
-to the classical case, \emph{a fundamental part of quantum
-  theory}. There are in fact two sources of uncertainty: one due to
-the finite measurement resources and one due to complementarity, which
-requires every quantum framework to be truly probabilistic.
-
-???~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}

### 2017-12-09 prop_letter_ajhs.tex

@@
 conventional quantum-mechanical probability measures to include the
-effect of imprecise measurements.
-
+effect of imperfect measurements. 
 There are long-standing debates in the foundations of quantum
@@
 there is a sharp transition to \emph{non-contextuality}, parallel in
-character to a phase transition.  These results provide a new insight
+spirit to a phase transition.  These results provide a new insight
 into the Meyer-Mermin debate by presenting a theory in which there is
@@
 
-The quantum-mechanical requirement for contextuality
-continues to hold, thus maintaining the Kochen-Specker result for a
-\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
-  fixed value} of $\delta$, there is a sharp transition, parallel in
-its consequences to, say, a phase transition, to
-\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
+%The quantum-mechanical requirement for contextuality
+%continues to hold, thus maintaining the Kochen-Specker result for a
+%\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
+%  fixed value} of $\delta$, there is a sharp transition, parallel in
+%its consequences to, say, a phase transition, to
+%\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
 %% simulated by a non-contextual hidden variable theory.
@@
 % }
-These results provide a new insight into the Meyer-Mermin debate by
-presenting a theory in which there is a \emph{parameter} interpolating
-between what appeared previously to be irreconcilable aspects %interpretations
-of contextuality.
+%These results provide a new insight into the Meyer-Mermin debate by
+%presenting a theory in which there is a \emph{parameter} interpolating
+%between what appeared previously to be irreconcilable aspects %interpretations
+%of contextuality.
 % ajh- above: I think "interpretations" is not quite right -> "aspects"?
@@
 in which quantum states and measurements are both infinitely
-precise. In an actual experimental setup with an ensemble of quantum
+precise, i.e., {\it sharp}. 
+In an actual experimental setup with an ensemble of quantum
 states that would ideally be identical, but are not actually

### 2017-12-14 prop_letter_ajhs.tex
done?

@@
 principle that uses $\subseteq$ instead of $=$ for the same reason as
-before. The new condition, known as \emph{convexity}
-\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,MarinacciMontrucchio2005,Grabisch2016},
+before. The new condition, known as
+\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,MarinacciMontrucchio2005,Grabisch2016},
 reduces to the previously motivated Eq.~(\ref{eq:disjoint}) when the
@@
 
-\newpage
-
-\begin{suggest}{\andy}{6}[inverted logic and phrasing.  I would start at "To formalize
-this ..." and replace all the way to Eq.~(\ref{eq:hbar})]
-We now show that our definition of QIVPMs is consistent
-with classical IVPMs in the sense that a restriction of QIVPMs to
-mutually commuting events recovers the definition of classical
-IVPMs.  However, we must refine this context for the quantum case,
-defining a QIVPM  $\bar{\mu}$ to be \emph{consistent} with a state $\rho$ and
-a projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
-probability calculated by the Born
-rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e., 
+Our definition of QIVPMs is consistent with classical IVPMs in the
+sense that a restriction of QIVPMs to mutually commuting events,
+$\eventsC$, recovers the definition of classical IVPMs. The proof of
+this fact is included in the forthcoming thesis by the first author. A
+consequence of this fact is that known properties of classical IVPMs
+directly hold for QIVPMs when one restricts to mutually commuting
+events, $\eventsC$. In particular, in the classical world, it is
+\emph{impossible} for experiments to result in probabilities that are
+inconsistent with \emph{some} state of the system under consideration,
+i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
+  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
+  proves that a classical IVPM always contains at least one state that
+  is consistent with every event.}. Interestingly, as we show in
+Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
+probabilities associated with some events to be inconsistent with
+\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
+in that case, one cannot guarantee non-empty cores for finite-precision
+attempts at proving Gleason's theorem by extending the Born measure
+$\muB_{\rho}\left(P\right)$ to QIVPMs
+$\bar{\mu}\left(P\right)$. However, if the set of events is mutually
+commuting, the situation reverts to the classical case in which
+probabilities always determine at least one state.
+
+We now give the necessary technical definitions to prove this
+non-empty core property. We say a QIVPM $\bar{\mu}$ is
+\emph{consistent} with a state $\rho$ and a projector~$P$ if the
+interval $\bar{\mu}(P)$ contains the exact probability calculated by
+the Born rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
   \begin{equation}
@@
   \end{equation}
-In contrast with conventional probability spaces, there is \emph{no
-guarantee} that a unique state $\rho$ consistent with a QIVPM exists.
+In contrast with classical probability spaces, there is \emph{no
+guarantee} that there exists a unique state $\rho$ consistent with a QIVPM.
 
@@
 \end{definition}
-\end{suggest}
-%% which coherently introduces the "core" and sets if off as a
-%% DEFINITION, etc.
-
-\newpage
-
-We now show that our definition of QIVPMs is consistent with classical
-IVPMs in the sense that a restriction of QIVPMs to mutually commuting
-events recovers the definition of classical IVPMs. To formalize this
-connection, we first note that in contrast to the case with
-conventional quantum probability spaces, there is generally no unique
-state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
-is \emph{consistent} with a state $\rho$ and projector~$P$ if the
-interval $\bar{\mu}(P)$ contains the exact probability calculated by
-the Born rule, i.e, if:
-\begin{equation}
-\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
-\end{equation}
-where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
-is the probability of the event~$P$ as determined by the Born
-rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
-
-We generalize this consistency relation to sets of states and general
-subspaces of events as follows. A set of events $\events'$ is a
-\emph{subspace} of $\events$ if it contains $\mathbb{0}$
-and~$\mathbb{1}$ and is closed under complements, sums, and products,
-i.e., for any projector~$P\in\events'$, we have
-$\mathbb{1}-P\in\events'$ and for each pair of commuting
-projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
-$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$. Given a
-probability measure $\bar{\mu}$ and a subspace of events $\events'$,
-we define the \emph{core} of $\bar{\mu}$ relative to $\events'$ as the
-collection of all states $\rho$ that are consistent with $\bar{\mu}$
-on every projector in $\events'$ as $\coreBorn(\bar{\mu},\events')$:
-\begin{equation}
-\label{eq:hbar}
-\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in \events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)}.
-\end{equation}
-
-\newpage
-
-\begin{suggest}{\andy}{7}[This story order is incomprehensible. I would state FIRST that 'here
-is the outline of the proof', and LAST 'Thm 1..., whose full proof
-will appear in~\cite{TaiThesis2018}.]
-   The general idea of the proof that QIVPMs become classical
-IVPMs when the space of events includes only mutually commuting
-events depends on showing the existence of a non-empty core for such
-commuting events.  The first step in establishing this assertion is to
-to take a subspace $\eventsC$ of mutually commuting events, construct
-a partial orthonormal basis by diagonalization, and complete this to a
-full orthonormal basis  $\overline{\eventsC}$.  We then
-build a bijection between the QIVPM on the set of projectors
-associated with this basis and the set of classical events
-corresponding to this basis.  Using this correspondence together with a
-classical result by
-Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
-we can establish that for the special case of commuting events, a
-QIVPM will always have a non-empty core~\footnote{Shapley's result
-  proves that a classical IVPM always contains at least one state that
-  is consistent with every event.}.  This leads to
-\begin{thm}[Non-empty Core for Compatible Measurements] \label{thm:Shapley}
-  For every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
-  of events~$\eventsC\subseteq\events$ commutes, then
-  $\coreBorn\left(\bar{\mu},\eventsC\right)\ne\emptyset$,
-\end{thm}
-whose full proof will appear in ~\cite{TaiThesis2018}.
-\end{suggest}
-The proof that QIVPMs become classical IVPMs when the space of events
-includes only mutually commuting events is presented in detail in a
-forthcoming thesis~\cite{TaiThesis2018}. The idea of the proof is as
-follows. Given a subspace of mutually commuting events~$\eventsC$, we
-can construct a partial orthonormal basis by diagonalization and
-complete it to a full orthonormal basis $\overline{\eventsC}$. We then
-build a bijection between the QIVPM on the set of projectors
-associated with this basis and the set of classical events
-corresponding to this basis. Using this correspondence together with a
-classical result by
-Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
-we can establish that for the special case of commuting events, a
-QIVPM will always have a non-empty core~\footnote{Shapley's result
-  proves that a classical IVPM always contains at least one state that
-  is consistent with every event.}.
+
+We are now in position to state and prove that, for the special case
+of commuting events, a QIVPM will always have a non-empty core.
 
@@
 
-\begin{suggest}{\andy}{8}[inverted narrative order]
-The importance of the existence of empty cores combined with
-  the conditions guaranteeing non-empty cores is that one cannot
-  guarantee non-empty cores for finite-precision attempts at proving
-  Gleason's theorem by extending the Born measure
-  $\muB_{\rho}\left(P\right)$ to QIVPMs $\bar{\mu}\left(P\right)$.  We
-  will show in  Sec.~\ref{sec:Gleason} that a core defined by the set
-  of states $\coreBorn\left(\bar{\mu},\events'\right)$ that is
-  consistent with some arbitrary (not necessarily commuting)
-  events~$\events'$  and a particular QIVPM  $\bar{\mu}$
-   \emph{may be empty}.
-\end{suggest}
-The importance of this property is that it is violated in
-finite-precision versions of Gleason's theorem
-(cf. Thm.~\ref{thm:Non-extensible-of-Gleason's} in Sec.~\ref{sec:Gleason}). As we will show, the set of states
-$\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
-some arbitrary (not necessarily commuting) events~$\events'$ and a
-particular QIVPM $\bar{\mu}$ may be \emph{empty}.
+The proof, detailed in the forthcoming thesis, proceeds as
+follows. From a subspace $\eventsC$ of mutually commuting events, one
+can construct a partial orthonormal basis by diagonalization, and
+complete this to a full orthonormal basis $\overline{\eventsC}$.  We
+can then build a bijection between the QIVPM on the set of projectors
+associated with this basis and the set of classical events
+corresponding to this basis.  Using this correspondence together with
+the classical result by
+Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
+we can establish that for the special case of commuting events, a
+QIVPM will always have a non-empty core.
 

### 2017-12-15 prop_letter_ajhs.tex
prop_letter_ajhs.tex Add citations...

@@
 sense that a restriction of QIVPMs to mutually commuting events,
-$\eventsC$, recovers the definition of classical IVPMs. The proof of
-this fact is included in the forthcoming thesis by the first author. A
+$\eventsC$, recovers the definition of classical
+IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
+forthcoming thesis by the first author~\citep{TaiThesis2018}. A
 consequence of this fact is that known properties of classical IVPMs
@@
 
-The proof, detailed in the forthcoming thesis, proceeds as
+The proof, detailed in the forthcoming thesis~\citep{TaiThesis2018}, proceeds as
 follows. From a subspace $\eventsC$ of mutually commuting events, one

### 2018-01-10 prop_letter_ajhs.tex
From: e-prints@arxiv.org [mailto:e-prints@arxiv.org] Sent: Monday, December 25, 2017 12:54 To: Tai, Yu-Tsung <yuttai@indiana.edu> Subject: arXiv submission submit/2114094
We have received your submission to arXiv. Your temporary submission
identifier is: submit/2114094.

You may update your submission at: https://arxiv.org/submit/2114094

Your article is scheduled to be announced at Wed, 27 Dec 2017 01:00:00
GMT.
The abstract will appear in the subsequent mailing as displayed below,
except that the submission identifier will be replaced by the official
arXiv identifier. Updates before Tue, 26

@@
 showkeys, longbibliography, amsmath, amssymb, floatfix]{revtex4-1} 
+\pdfoutput=1
 
@@
 the Hilbert space is defined over the field of rational numbers,
-therefore nullifying the theorem~\citep{PhysRevLett.83.3751}.
+therefore nullifying the theorem~\cite{PhysRevLett.83.3751}.
 However, Mermin then argued that measurement outcomes must depend
@@
 him to assert that the impact of Meyer's negative result is
-``unsupportable'' on physical grounds~\citep{Mermin1999}.  The debate
+``unsupportable'' on physical grounds~\cite{Mermin1999}.  The debate
 on whether contextuality is consistent with experimental outcomes
 continues to be an active topic of
-research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+research~\cite{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
@@
 application of the Born rule determining the probability of a given
-measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
+measurement outcome~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}.
 Here, Gleason's theorem establishes that there is no alternative to
@@
 state $\rho$ consistent with the statistical predictions computed from
-the Born rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
 Our question then concerns what happens when infinite precision cannot
@@
 $\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) = \sum_{j=1}^{N}
-q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
+q_{j}\muB_{\phi_{j}}\left(P\right)$~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}.
 
@@
 are several proposals for ``imprecise
-probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+probabilities''~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
 Although these proposals differ in some details, they all share the
@@
 IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
-forthcoming thesis by the first author~\citep{TaiThesis2018}. A
+forthcoming thesis by the first author~\cite{TaiThesis2018}. A
 consequence of this fact is that known properties of classical IVPMs
@@
 interval $\bar{\mu}(P)$ contains the exact probability calculated by
-the Born rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
+the Born rule~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
   \begin{equation}
@@
 
-The proof, detailed in the forthcoming thesis~\citep{TaiThesis2018}, proceeds as
+The proof, detailed in the forthcoming thesis~\cite{TaiThesis2018}, proceeds as
 follows. From a subspace $\eventsC$ of mutually commuting events, one
@@
 reducing the definition to that of
-Eq.~(\ref{eq:quantum-expectation})~\citep{TaiThesis2018}.
+Eq.~(\ref{eq:quantum-expectation})~\cite{TaiThesis2018}.
 % For example, we can extend one of the fragments of valid probability
@@
 the classical notion of the \emph{Choquet
-  integral}~\citep{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+  integral}~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
 which is used to calculate the expectation value of random variables
-as a weighted average~\citep{TaiThesis2018}.
+as a weighted average~\cite{TaiThesis2018}.
 
@@
 Kochen-Specker to experimental, and hence finite-precision, quantum
-measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+measurements~\cite{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 Specifically, the original Kochen-Specker theorem is formulated using
@@
 provides a quantitative realization of Mermin's
-intuition~\citep{Mermin1999}:
+intuition~\cite{Mermin1999}:
 \begin{quote}
@@
 number of occurrences of the interval $[-1,-1]$ in each row and hence
-in the entire table~\citep{TaiThesis2018}. However, looking at the expectation values of the
+in the entire table~\cite{TaiThesis2018}. However, looking at the expectation values of the
 observables in each column, there must be an even number of
 occurrences of the interval $[-1,-1]$ in the first two columns and an
-odd number in the $j=2$ column and hence in the entire table~\citep{TaiThesis2018}. The
+odd number in the $j=2$ column and hence in the entire table~\cite{TaiThesis2018}. The
 contradiction implies the non-existence of the assumed 0-deterministic
@@
 % such that $\bar{\mu}\left(\proj{k_{0}}\right)=\necess$ and $\bar{\mu}\left(\proj{k}\right)=\imposs$
-% for $k\ne k_{0}$~\citep{TaiThesis2018}. Without loss of generality,
+% for $k\ne k_{0}$~\cite{TaiThesis2018}. Without loss of generality,
 % assume $k_{0}=1$, the expectation values can be computed step-by-step
@@
 % $\mu\left(\proj{k}\right)=1$ if and only if
-% $k=k_{0}$~\citep{TaiThesis2018}.  If we denote the product
+% $k=k_{0}$~\cite{TaiThesis2018}.  If we denote the product
 % observables~$\prod_{j=1}^{M}\mathbf{O}_{j}$ as
@@
 implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{TaiThesis2018}. Indeed
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\cite{TaiThesis2018}. Indeed
 when
@@
 from a state $\rho$ according to the Born
-rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.  According
+rule~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}.  According
 to Gleason's
-theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}, this
+theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}, this
 state $\rho$ is also the unique state consistent with any possible
@@
 Table~\ref{tab:non-Born-QIVPM} can be verified to be a
-QIVPM~\citep{TaiThesis2018}.
+QIVPM~\cite{TaiThesis2018}.
 \begin{table}
@@
 $2$-norm or the spectral
-norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
 Then, a finite-precision extension of Gleason's theorem can be stated as
@@
 Since $\rho-\rho'$ is Hermitian, $\max_{\left\Vert \psi\right\Vert =1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
-is the maximum absolute value of the eigenvalues of $\rho-\rho'$~\citep{544199},
-and equal to $\left\Vert \rho-\rho'\right\Vert $~\citep{GolubVanLoan1996,Foucart2012}.
+is the maximum absolute value of the eigenvalues of $\rho-\rho'$~\cite{544199},
+and equal to $\left\Vert \rho-\rho'\right\Vert $~\cite{GolubVanLoan1996,Foucart2012}.
 Hence, $\left\Vert \rho-\rho'\right\Vert \le \alpha$.
@@
 % $2$-norm or the spectral
-% norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+% norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
 % Then, a version of Gleason's theorem can be stated as follow.
@@
 By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\ultramodularL:\left[0,1\right]\rightarrow\left[0,1\right]$
-is Wright-convex~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992},
+is Wright-convex~\cite{Wright1954,RobertsVarberg1973,PecaricTong1992},
 i.e., 
@@
 must be continuous on the unit open interval
-$\left(0,1\right)$~\citep{MarinacciMontrucchio2005}.  Therefore,
+$\left(0,1\right)$~\cite{MarinacciMontrucchio2005}.  Therefore,
 either $\ultramodular$ maps every number in $\left[0,1\right]$ to the
@@
 % Eq.~(\ref{eq:iota-add}), then $\ultramodular\circ\mu$ is a
-% QIVPM~\citep{TaiThesis2018}.  For example, consider an orthonormal
+% QIVPM~\cite{TaiThesis2018}.  For example, consider an orthonormal
 % basis $\{\ket{0},\ket{1},\ket{2}\}$, two states
@@
 % defined in Table~\ref{tab:I_2} satisfies Eqs.~(\ref{eq:iota-constraints})
-% and Eq.~(\ref{eq:iota-add})~\citep{TaiThesis2018}, $\ultramodular_{2}\circ\muB_{\rho_{0}}$
+% and Eq.~(\ref{eq:iota-add})~\cite{TaiThesis2018}, $\ultramodular_{2}\circ\muB_{\rho_{0}}$
 % and $\ultramodular_{2}\circ\muB_{\rho_{1}}$ are both

### 2018-01-24 dissertation.tex
https://math.indiana.edu/graduate/index.html
IU Thesis Document Class

The iuthesis document class is a LaTeX document class that produces output acceptable (as of Summer 2013) for an Indiana University Bloomington Masters or Doctoral thesis. It is available free for anybody's use, but comes with NO WARRANTY. In particular, the author is not responsible if it produces output that is not acceptable to the graduate school. This document class is not officially sanctioned by the University Graduate School, although several theses have been written with it and accepted.

Per the University Graduat

\documentclass{iuphd}
\usepackage[utf8]{inputenc}
\usepackage{cite}

%data for Title Page
\title{Dissertation Title}
\author{Author}
\date{Completion Date}

%data for Acceptance Page
\committeechair{Committee Chair}
\readertwo{2nd Reader}
\readerthree{3rd Reader}
\readerfour{4th Reader}
\defensedate{Defense Date}

%data for Copyright Page
\cryear{Current Year}

\begin{document}
\maketitle

\acceptancepage

\copyrightpage

%\begin{dedication}
%\end{dedication}

\begin{acknowledgments}
The acknowledgments are designed to recognize people or agencies to whom you feel grateful for any academic,
technical, financial, or personal aid in the preparation of your thesis or dissertation; as a matter of
courtesy, you would ordinarily mention the members of your committee here, as well as institutions that
provided funding, your typist, or anyone else who helped.
\end{acknowledgments}

%\begin{preface}
%\end{preface}

\begin{abstract}
 The abstract is double-spaced and limited to 350 words. As many people will learn about
your work through your abstract published in Dissertation Abstracts (http://proquest.umi.com/login),
you should spend a good bit of effort in the composition of both the abstract and the title of your work.
Try to convey the flavor of your work, not just the bare bones of your findings; in an average abstract
there will be about 70 characters per line with a maximum of 35 lines. You should also work to phrase your
title so that it truly describes the contents and will be easily found in the index of Dissertation Abstracts.
The index is based on key words, so be as specific as you can be about your subject. 
\end{abstract}

\tableofcontents

\include{iuphd-doc}

\bibliographystyle{plain}
\bibliography{dissertation}

%\include{CV}
\end{document}

### 2018-01-24 dissertation.tex
dissertation.tex Merge everything into one tex file...

@@
 \documentclass{iuphd}
+\usepackage[T1,T2A]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage{cite}
+\usepackage[ backend=biber]{biblatex}
+\addbibresource{prop.bib}
+\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
+\DeclareUnicodeCharacter{0229}{\c{e}}
+\DeclareUnicodeCharacter{00A0}{~}
+\usepackage{mmap}
+\usepackage{comment}
 
@@
 
-\include{iuphd-doc}
+\chapter{Documentation}
 
+This pdf doubles as documentation for the iuphd.cls file, and as a sample for the output.
+The iuphd class is based on the standard \LaTeX \ report class, and as such you may assume that it follows
+the default formatting of the report class unless otherwise specified below.  The
+changes to the report class include the following:
+
+\begin{itemize}
+ \item changes to the default settings for margins, font size (11pt), spacing (double), and pagination,
+ \item the quote, quotation, and verse environments have been changed to switch temporarily to single spacing, and
+       remove the extra space at the top and bottom,
+ \item the enumerate and itemize environments have been changed to remove extra space between the items and at the
+       top and bottom,
+ \item a line has been added to prevent the double spacing from affecting arrays,
+ \item both numbered and unnumbered chapter headings are now centered by default,
+ \item heading names such as CHAPTER, and BIBLIOGRAPHY are now all caps by default regardless of how they are typed,
+ \emph{(This is accomplished with the help of textcase.sty.  Not all latex distributions come with this by default.)}
+ \item changes to the definitions of \textbackslash maketitle and the `abstract' environment,
+ \item the addition of commands for creating the acceptance page and copyright page,
+ \item the addition of the `acknowledgments', `preface', and `dedication' environments,
+ \item the addition of macros for specifying the department or school name, the names of
+ the committee members, the defense date, and the copyright year,
+ \item document class options for changing ``Department'' to ``School'' on the title page, and for showing
+ the abstract, preface, acknowledgments, or dedication in the table of contents.
+\end{itemize}
+
+The appropriate commands for using these features are already typed into the dissertation.tex sample file,
+with the optional items (dedication, preface, and copyright) commented out.  Simply remove the \% from the front
+of these optional commands if you wish to use them.  The headings for the acknowledgments, preface, and dedication have
+been defined as unnumbered chapter headings, which means they will not show up in the table of contents by default.
+See the instructions below for adding them to the table of contents if desired.
+
+\section{Current Standards at IU}
+The current version of iuphd.cls complies with the standards of formatting a dissertation at IU as of 2013.  Below is a discussion of
+some of the main points.
+
+The current pagination standard is for the page number to appear centered at the top or bottom of the
+page, and to use lowercase roman numerals for the material preceding the first chapter with the title page unnumbered but counting as
+page one. The only part of this that is not standard in the \LaTeX \ report class is the use of roman numerals, which was accomplished
+by changing the definitions to \textbackslash maketitle and \textbackslash tableofcontents.
+
+The current standard for chapter headings seems to be that they are centered and in all caps.  The iuphd.cls enforces these
+conventions automatically, however it is possible to override these changes with titlesec and titletoc. Because the textcase package is used,
+the capitalization is not affected in math mode, so for instance
+\medskip
+
+\textbackslash section\{\$p\$-adic numbers\}
+\medskip
+
+\noindent will give the output ``$p$-ADIC NUMBERS'' in both the section heading and in the table of contents
+(unless the value of \textbackslash tocdepth is changed to prevent sections from being listed in the table of contents).
+Since all caps takes up more space horizontally than mixed upper and lowecase text, the size of the chapter headings
+has been reduced to \textbackslash LARGE from \textbackslash huge.  However, no changes have been made to the size of any of the
+other headings in the report class.
+
+Most dissertations are one-sided, with an additional half inch added to the left hand margin on each page for the purpose of binding.
+Although this is the standard, they do allow for the possibility of two-sided printing, which would cause the side with the extra margin
+to alternate for binding.  This is automatically enforced simply by using the twoside option (a feature already built into the
+standard report class). This is done as follows:
+\medskip
+
+\textbackslash documentclass[twoside]\{iuphd\}
+\medskip
+
+There does not seem to be a standard about whether the abstract, preface, acknowledgments, and dedication are listed in the table of
+contents (TOC) or not.  As such, an option has been provided for including or excluding each one individually.  The syntax for these options
+follows the pattern `showX' if X is to be listed in the TOC, and 'hideX' if X is to be omitted from the TOC, where X can be any of the four
+items listed above.  In all cases, the default is for these \emph{not} to have entries in the table of contents.  So for example, to include
+both the abstract and the preface in the table of contents, but not the dedication or acknowledgments, you would use the code:
+\medskip
+
+\textbackslash documentclass[showabstract,showpreface]\{iuphd\}
+\medskip
+
+\noindent To include a line for the bibliography in the table of contents, the command
+\medskip
+
+\textbackslash addcontentsline\{toc\}\{chapter\}\{BIBLIOGRAPHY\}
+\medskip
+
+\noindent should be placed directly above the \textbackslash bibliography and \textbackslash bibliographystyle commands.  It may be necessary
+to use \textbackslash clearpage above this command to get the page number displayed in the contents to be correct.  However, if you are using
+\textbackslash include for each chapter, then \textbackslash clearpage has technically already been used in this case, and so it is not
+necessary to use it again. Similar commands will work for including any unnumbered heading in the table of contents, with careful attention
+to the effects of \textbackslash clearpage.
+
+Various commands have been defined for the data that will show up on the title page, acceptance page, and copyright page.  These include:
+\begin{itemize}
+ \item \textbackslash title - for the title of the dissertation
+ \item \textbackslash author - for the name of the author of the dissertation
+ \item \textbackslash date - for the \emph{completion date} of the dissertation
+ \item \textbackslash department - this is optional.  The default value is ``Mathematics,'' but if you are in a different department, this
+        command can be used to change its value to the name of whatever department (or school) you are in.  
+ \item \textbackslash committeechair, \textbackslash readertwo, \textbackslash readerthree, \textbackslash readerfour - for the names of the
+                      dissertation committee members.
+ \item \textbackslash defensedate - for the \emph{defense date} of the dissertation (which may not match the completion date).
+ \item \textbackslash cryear - for the copyright year.
+\end{itemize}
+
+Additionally the commands \textbackslash acceptancepage and \textbackslash copyrightpage have been defined to generate the acceptance page and copyright page
+respectively.  The copyright page is not required, so it has been commented out of my dissertation.tex sample file.  Two document class options have been provided
+for switching the text on the title page between ``Department'' and ``School.''  These options are given the obvious names `department' and `school'. The
+default option is `department', so it only needs to be changed if you are in a school rather than a department.
+
+A CV is also required following the bibliography, however, to maintain maximum flexibility I have not provided any special tools for
+formatting a CV.  Various packages are available that do this, although I prefer custom formatting. As such, I have provided only a
+line for including the CV after the bibliography, which is currently commented out.
+
+\section{Suggestions for additional formatting}
+
+For longer documents, it is often easier to manage if it is broken into multiple files.  This can be done by using the
+\textbackslash include\{filename\} or \textbackslash input\{filename\} commands.  You can think of
+\textbackslash input\{filename\} as an alias for all of the text contained in filename.tex: the text contained in that file,
+simply gets inserted at the exact spot where the command \textbackslash input is used.  This means that filename.tex should not have
+\textbackslash begin\{document\}, \textbackslash end\{document\}, or a preamble, as illustrated by iuphd-doc.tex in this example.
+On the other hand, \textbackslash include\{filename\} has the additional feature of adding \textbackslash clearpage both before and after
+the text being inserted.  This has important consequences for formatting.  Say that you have a file for each chapter,
+and your first chapter is the introduction.  If you do something like this:
+\medskip
+
+\textbackslash chapter\{Introduction\}
+
+\textbackslash include\{chap1\}
+\medskip
+
+\noindent then the title is formatted on its own page, and the text in chap1.tex will start on a new page; it produces
+the same result as
+\medskip
+
+\textbackslash chapter\{Introduction\}
+
+\textbackslash clearpage
+
+\textbackslash input\{chap1\}
+\medskip
+
+\noindent To avoid having the title put on a separate page there are two options: use input instead of include
+(without \textbackslash clearpage), or use the command \textbackslash chapter\{INTRODUCTION\} inside the file chap1.tex.
+I favor the second option as illustrated in this example with iuphd-doc.tex.
+
+Many \LaTeX \ packages are already available for additional customization of the formatting which is otherwise built in.
+Some of these are listed below.  To use them, simply declare them with \textbackslash usepackage in the preamble
+and refer to the documentation files for them, which are easily available online.
+
+\begin{itemize}
+ \item titlesec - for custom formatting of part, chapter, and section headings.
+ \item titletoc or tocloft - for custom formatting of the table of contents.
+ \item nomencl - for lists of notation (a tweak of makeindex).
+ \item prettyref - for custom formatting of references (e.g. referencing equations as (1), (2), etc., instead of the default
+       1, 2, etc.).  The ams packages also have a similar feature but it is much more limited.
+ \item natbib, custom-bib, or biblatex - offer additional flexibility for bibliography formatting beyond the standard used by
+       the mathematics community.
+ \item setspace - contains features for resetting the global line spacing, as well as environments that can be used to change
+       spacing locally, which are compatible with the quote, quotation, and verse environments.
+ \item quoting - provides a more flexible quotation environment, with options for adjusting the margins manually.  This package
+     should be used with setspace, to ensure single spacing of the quotations.
+ \item enumitem or paralist - provide several more flexible list environments.
+ \item titling - for custom changes to maketitle.
+ \item geometry - for customizing the page layout.
+\end{itemize}
+
+%add features for block quotes, underlined titles, and different departments.
+
+The last two should not be necessary unless the standards at IU change.  However, if that happens, it would really be better to
+rewrite the iuphd document class.  Additional packages and other useful information can be found in \cite{mittelbach2004latex}.
+
+\section{quote samples}
+The quote environment:
+\begin{quote}
+``God does not play dice with the universe.'' - Albert Einstein
+\end{quote}
+The quotation environment:
+\begin{quotation}
+ ``A GREAT discovery solves a great problem, but there is a grain of discovery in the solution of any problem.
+ Your problem may be modest, but if it challenges your curiosity and brings into play your inventive faculties,
+ and if you solve it by your own means, you may experience the tension and enjoy the triumph of discovery.''
+
+ - George P\'olya
+\end{quotation}
+The verse environment:
+\begin{verse}
+Im September ist alles aus Gold:\\ 
+die Sonne, die durch das Blau hinrollt,\\
+das Stoppelfeld,\\
+die Sonnenblume, schläfrig am Zaun,\\
+das Kreuz auf der Kirche,\\
+der Apfel im Baum.\\
+Ob er h\"alt,\\
+ob er f\"allt? \\
+Da wirft ihn geschwind\\
+der Wind\\
+in die goldene Welt.
+
+- Georg Britting
+\end{verse}
+
+\section{Troubleshooting}
+
+If you are getting an error with the TOC, you may have at least one of the following two problems:
+\begin{enumerate}
+ \item you do not have textcase.sty in your latex distribution,
+ \item you compiled a previous *.toc file with a different latex class (e.g. the amsbook class).
+\end{enumerate}
+Make sure you have textcase.sty, delete the *.toc file, and recompile.
+
+\begin{comment}
  \bibliographystyle{plain}
-\bibliography{dissertation}
+\bibliography{prop}
+\end{comment}
+\printbibliography
 

### 2018-01-24 dissertation.tex

@@
 das Stoppelfeld,\\
-die Sonnenblume, schläfrig am Zaun,\\
+die Sonnenblume, schlafrig am Zaun,\\
 das Kreuz auf der Kirche,\\

### 2018-01-24 dissertation.tex
dissertation.lyx Imported from dissertation.tex ...

@@
-\documentclass{iuphd}
+\documentclass[twoside]{iuphd}
 \usepackage[T1,T2A]{fontenc}
@@
 
+\begin{document}
 %data for Title Page
+\begin{comment}
 \title{Dissertation Title}
@@
 \date{Completion Date}
+\end{comment}
+\title{Discrete Quantum Theories and Computing}
+\author{Yu-Tsung Tai}
+\date{\today}
+\maketitle
 
@@
 \defensedate{Defense Date}
+\acceptancepage
 
 %data for Copyright Page
+\begin{comment}
 \cryear{Current Year}
-
-\begin{document}
-\maketitle
-
-\acceptancepage
-
+\end{comment}
+\cryear{2018}
 \copyrightpage
@@
 \begin{abstract}
+\begin{comment}
  The abstract is double-spaced and limited to 350 words. As many people will learn about
@@
 The index is based on key words, so be as specific as you can be about your subject.
+\end{comment}
+Our primary research interest is to build a quantum computing model
+characterizing realistic quantum computers. While most of the quantum
+computing models based on uncomputable numbers, that is, the continuum
+of real numbers, most of the classical computers in our daily life
+are digital instead of analog computers. This highlight the necessity
+to investigate discrete models for quantum theory and computing. Specifically,
+we start from replacing the continuum of complex numbers by the discrete
+finite fields. Although we have fruitful results on their geometric
+implications and computing powers, their probability models are still
+not completely satisfactory. To address this issue, we further exploited
+quantum interval-valued probability, and proved an imprecise version
+of foundational results such as the Gleason and Kochen-Specker theorems.
 \end{abstract}

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex
Clean up "prop_prop_letter_ajhs_referee_response.tex", and import into "prop_prop_letter_ajhs_referee_response.lyx"...

\documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
showkeys, longbibliography, amsmath, amssymb, floatfix]{revtex4-1} 
\pdfoutput=1

\usepackage{fullpage}
\usepackage{cmap}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[french,main=english]{babel}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[backref=false]{hyperref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[braket,qm]{qcircuit}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\usepackage{comment}
\usepackage{xparse}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}[thm]
\newtheorem{cor}{Corollary}[thm]
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{condition}[assumption]{Condition}

\DeclareUnicodeCharacter{0229}{\c{e}}

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\imposs}{{\text{\wesa{impossible}}}}
\newcommand{\likely}{{\text{\wesa{likely}}}}
\newcommand{\unlikely}{{\text{\wesa{unlikely}}}}
\newcommand{\necess}{{\text{\wesa{certain}}}}
\newcommand{\unknown}{{\text{\wesa{unknown}}}}
\newcommand{\midd}{{\text{\wesa{middle}}}}
\newcommand{\fket}[1]{{|#1\rangle}}
\newcommand{\fproj}[1]{|#1\rangle\langle #1|}
\newcommand{\proj}[1]{\op{#1}{#1}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{L{#1}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{R{#1}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\rmd}{d}
\newcommand{\rmi}{i}
\lineskiplimit=1pt
\newcommand{\ultramodular}{\mathcal{M}}
\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{L{#1}}}}
\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{R{#1}}}}
\newcommand{\muB}{\ensuremath{\mu^{B}}}
\newcommand{\eventsC}{\ensuremath{\events_{C}}}

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Response of the Referee Report of Quantum Interval-Valued Probability:
Contextuality and the Born Rule}

\author{Yu-Tsung Tai}
\affiliation{Department of Mathematics, Indiana University, Bloomington, Indiana 47405,
USA}
\affiliation{Department of Computer Science, Indiana University, Bloomington,
Indiana 47405, USA}

\author{Andrew J. Hanson}
\affiliation{Department of Informatics, Indiana University, Bloomington,
Indiana 47405, USA}

\author{Gerardo Ortiz}
\affiliation{Department of Physics, Indiana University, Bloomington, Indiana 47405,
USA}

\author{Amr Sabry}
\affiliation{Department of Computer Science, Indiana University, Bloomington,
Indiana 47405, USA}

\date{\today}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Classical $\frac{1}{4}$-deterministic Probability Measure}

The first step in our formalization is to introduce a family of QIVPMs
parameterized by an uncertainty~$\delta$, which we call
$\delta$-deterministic QIVPMs.

\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic} A
  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is
  $\delta$-deterministic if, for every event $P\in\events$, we have
  that either 
  $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$ or
  $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. 
\end{definition}

\begin{table}
  \noindent \centering{}\caption{\label{tab:classical-IVPMs}Example
    QIVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ on
    commuting events $P$.}
\begin{tabular}{cccc}
\toprule
\addlinespace
$P$ & $\bar{\mu}_{A}(P)$ & $\bar{\mu}_{B}(P)$ & $\bar{\mu}_{C}(P)$\tabularnewline\addlinespace
\midrule
\midrule
\addlinespace
$\mathbb{0}$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
\midrule
\addlinespace
$\proj{0}$ & $\necess$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline\addlinespace
\midrule
\addlinespace
$\proj{1}$ & $\imposs$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline\addlinespace
\midrule
\addlinespace
$\mathbb{1}$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\yutsung{$\bar{\mu}_{A}$ is neither a QIVPM nor a restriction of a QIVPM
according to the current definition. Need to fix this example or fix the definition.}
\end{table}

\noindent This definition puts no restrictions on the set of intervals
itself, only on which intervals are assigned to events. When
$\delta=0$, every event must be assigned a probability either in
$\imposs$ or in $\necess$, i.e., every event is completely determined
with certainty. As $\delta$ gets larger, the QIVPM allows for more
indeterminate behavior. 
For example, $\bar{\mu}_{A}$ defined in
Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
$\imposs\subseteq\left[0,0\right]$ and
$\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
$\bar{\mu}_{A}$ represents tossing a double-headed coin. When $\delta$
is increased to $\frac{1}{3}$, both $\bar{\mu}_{B}$ and
$\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
$\bar{\mu}_{A}$ is still not $\frac{1}{3}$-deterministic because
$\bar{\mu}_{A}(\proj{0})=\bar{\mu}_{A}(\proj{1})=\unknown=[0,1]$, but
both $\unknown\subseteq\left[0,\frac{1}{3}\right]$ and
$\unknown\subseteq\left[1-\frac{1}{3},1\right]$ are false.  Finally,
when $\delta=1$, because every interval is a subset of $\unknown$,
every QIVPM is $1$-deterministic. In particular, the non-informative
QIVPM~$\bar{\mu}_{A}$ is 1-deterministic.
\begin{comment}
and the Born QIVPM~$\bar{\mu}_{3}$ defined in
Eq.~(\ref{eq:Born-QIVPM}) are both $1$-deterministic.
\end{comment}

\paragraph{Why a Quantum $\frac{1}{4}$-deterministic Probability Measure is
Impossible}

Our framework allows us to generalize the above theorem to state that
for small enough $\delta$, it is impossible to have
$\delta$-deterministic QIVPMs. We next prove a main result of this
paper which is a stronger statement of contextuality that includes the
effects of finite-precision.  Every QIVPM must map some events to
truly uncertain intervals, not just ``almost definite intervals.'' 
\begin{comment}
\andy{contextuality is never defined.}
\yutsung{Actually, the second sentence in the introduction defines
``contextuality''. The problem is that there is no direct relation between what
defined in the introduction and here.}
\end{comment}

\begin{thm}[Finite-precision Extension of the Kochen-Specker
  Theorem] \label{cor:Kochen-Specker-IVPM} Given a Hilbert space
  $\Hilb$ of dimension~$d\ge3$, there is no $\delta$-deterministic
  QIVPM for $\delta<\frac{1}{3}$.\end{thm}

The proof is by contradiction: Suppose there is a
$\delta$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this
assumed QIVPM to construct the following 0-deterministic QIVPM
$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
  \imposs,\necess\right\}$:
\[
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\]
However, since we know that 0-deterministic QIVPMs do not exist, the
map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ does
not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$ is
indeed a 0-deterministic QIVPM by checking that for orthogonal
projectors~$P_{0}$ and $P_{1}$, we have that
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\cite{TaiThesis2018}. Indeed
when
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and
$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
implies
$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
When $\delta<\frac{1}{3}$, i.e., $2\delta<1-\delta$, it follows that
$\bar{\mu}\left(P_{0}+P_{1}\right)$ cannot be a subset of
$\left[1-\delta,1\right]$. Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
is a subset of either $\left[0,\delta\right]$ or
$\left[1-\delta,1\right]$ and the latter is excluded, then
$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
$\left[0,\delta\right]$, which implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
theorem holds when $\delta<\frac{1}{3}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{prop}
\end{document}

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex \paragraph{Classical $\frac{1}{4}$-deterministic Probability Measure} Updating...

@@
 
-The first step in our formalization is to introduce a family of QIVPMs
-parameterized by an uncertainty~$\delta$, which we call
-$\delta$-deterministic QIVPMs.
+Although the definition of $\delta$-determinism in our paper only
+applied on QIVPMs~\cite{THOS2017}, this definition can be easily
+extended to apply on both classical and quantum IVPMs as follow.
 
-\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic} A
-  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is
-  $\delta$-deterministic if, for every event $P\in\events$, we have
-  that either 
-  $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$ or
-  $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. 
-\end{definition}
+\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
+Given a classical or quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
+where $\events'$ is the set of all events, $\events$, when $\bar{\mu}$
+is a QIVPM and $\events'$ is the set of mutually commuting events,
+$\eventsC$, when $\bar{\mu}$ is a classical one. $\bar{\mu}$ is
+$\delta$-deterministic if, for every event $P\in\events'$, we have
+that either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
+or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}
 
 \begin{table}
-  \noindent \centering{}\caption{\label{tab:classical-IVPMs}Example
-    QIVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ on
+\noindent \centering{}\caption{\label{tab:classical-IVPMs}Example $\frac{1}{4}$-deterministic classical
+IVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ on
 commuting events $P$.}
@@
 \addlinespace
-$P$ & $\bar{\mu}_{A}(P)$ & $\bar{\mu}_{B}(P)$ & $\bar{\mu}_{C}(P)$\tabularnewline\addlinespace
+$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$  & $\bar{\mu}_{C}(P)$\tabularnewline
 \midrule
@@
 \addlinespace
-$\mathbb{0}$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
+$\mathbb{0}$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline
 \midrule 
 \addlinespace
-$\proj{0}$ & $\necess$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline\addlinespace
+$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$  & $\left[\frac{3}{4},1\right]$\tabularnewline
 \midrule 
 \addlinespace
-$\proj{1}$ & $\imposs$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline\addlinespace
+$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$  & $\left[1,\frac{1}{4}\right]$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbb{1}$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
+$\mathbb{1}$  & $\necess$  & $\necess$  & $\necess$\tabularnewline
 \bottomrule
 \end{tabular}
-\yutsung{$\bar{\mu}_{A}$ is neither a QIVPM nor a restriction of a QIVPM
-according to the current definition. Need to fix this example or fix the definition.}
 \end{table}
+
+Then, it is easy to construct $\frac{1}{4}$-deterministic classical
+IVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ defined
+in Table~\ref{tab:classical-IVPMs}.
 
@@
 QIVPM~$\bar{\mu}_{A}$ is 1-deterministic.
-\begin{comment}
-and the Born QIVPM~$\bar{\mu}_{3}$ defined in
-Eq.~(\ref{eq:Born-QIVPM}) are both $1$-deterministic.
-\end{comment}
 
@@
 truly uncertain intervals, not just ``almost definite intervals.''
-\begin{comment}
-\andy{contextuality is never defined.}
-\yutsung{Actually, the second sentence in the introduction defines
-``contextuality''. The problem is that there is no direct relation between what
-defined in the introduction and here.}
-\end{comment}
 

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex \paragraph{Classical $\frac{1}{4}$-deterministic Probability Measure} Updating...

@@
 
-\title{Response of the Referee Report of Quantum Interval-Valued Probability:
-Contextuality and the Born Rule}
+\title{Response of the Referee Report of ``Quantum Interval-Valued Probability:
+Contextuality and the Born Rule''}
 
@@
 is a QIVPM and $\events'$ is the set of mutually commuting events,
-$\eventsC$, when $\bar{\mu}$ is a classical one. $\bar{\mu}$ is
-$\delta$-deterministic if, for every event $P\in\events'$, we have
-that either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
+$\eventsC$, when $\bar{\mu}$ is a classical one. Then, $\bar{\mu}$
+is $\delta$-deterministic if, for every event $P\in\events'$, we
+have that either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
 or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}
@@
 \begin{table}
-\noindent \centering{}\caption{\label{tab:classical-IVPMs}Example $\frac{1}{4}$-deterministic classical
-IVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ on
-commuting events $P$.}
-\begin{tabular}{cccc}
+\noindent \centering{}\caption{\label{tab:classical-IVPMs}Examples of $\delta$-deterministic classical
+IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ on commuting events $P$.}
+\begin{tabular}{ccc}
 \toprule 
 \addlinespace
-$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$  & $\bar{\mu}_{C}(P)$\tabularnewline
+$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$ \tabularnewline
 \midrule
@@
 \addlinespace
-$\mathbb{0}$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline
+$\mathbb{0}$  & $\imposs$  & $\imposs$ \tabularnewline
 \midrule 
 \addlinespace
-$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$  & $\left[\frac{3}{4},1\right]$\tabularnewline
+$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$ \tabularnewline
 \midrule 
 \addlinespace
-$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$  & $\left[1,\frac{1}{4}\right]$\tabularnewline
+$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$ \tabularnewline
 \midrule 
 \addlinespace
-$\mathbb{1}$  & $\necess$  & $\necess$  & $\necess$\tabularnewline
+$\mathbb{1}$  & $\necess$  & $\necess$ \tabularnewline
 \bottomrule
@@
 
-Then, it is easy to construct $\frac{1}{4}$-deterministic classical
-IVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ defined
-in Table~\ref{tab:classical-IVPMs}.
-
-\noindent This definition puts no restrictions on the set of intervals
-itself, only on which intervals are assigned to events. When
-$\delta=0$, every event must be assigned a probability either in
-$\imposs$ or in $\necess$, i.e., every event is completely determined
-with certainty. As $\delta$ gets larger, the QIVPM allows for more
-indeterminate behavior. 
-For example, $\bar{\mu}_{A}$ defined in
-Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
-$\imposs\subseteq\left[0,0\right]$ and
-$\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
-~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
-$\bar{\mu}_{A}$ represents tossing a double-headed coin. When $\delta$
-is increased to $\frac{1}{3}$, both $\bar{\mu}_{B}$ and
-$\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
-$\bar{\mu}_{A}$ is still not $\frac{1}{3}$-deterministic because
-$\bar{\mu}_{A}(\proj{0})=\bar{\mu}_{A}(\proj{1})=\unknown=[0,1]$, but
-both $\unknown\subseteq\left[0,\frac{1}{3}\right]$ and
-$\unknown\subseteq\left[1-\frac{1}{3},1\right]$ are false.  Finally,
-when $\delta=1$, because every interval is a subset of $\unknown$,
-every QIVPM is $1$-deterministic. In particular, the non-informative
-QIVPM~$\bar{\mu}_{A}$ is 1-deterministic.
+\noindent Then, it is easy to construct $\delta$-deterministic classical
+IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
+where $\proj{0}$ and $\proj{1}$ represents heads and tails in coin-tossing,
+respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
+a double-headed coin that always lands on head. For $\bar{\mu}_{B}$,
+the interpretation is that we throw a coin $1000$ times and we observe
+$750$ heads and $200$ tails and the coin falls under the couch $50$
+times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
+$\delta=\frac{1}{4}$, and $\delta$ qualifies how a coin close to
+double-headed, which we can certainly know the outcome of an coin
+even before tossing. We see here that we can construct $0$-deterministic
+as well as $\frac{1}{4}$-deterministic and in fact for any $\delta$
+in the range $\left[0,1\right]$ we can construct a $\delta$-deterministic
+classical probability measure. BUT the situation changes in the quantum
+case, WE CANNOT construct $\delta$-deterministic probability measures
+for $\delta$ that are less than $\frac{1}{3}$.
 

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex \paragraph{Why a Quantum $\frac{1}{4}$-deterministic Probability Measure is Impossible} Updating...

@@
 
-Our framework allows us to generalize the above theorem to state that
-for small enough $\delta$, it is impossible to have
-$\delta$-deterministic QIVPMs. We next prove a main result of this
-paper which is a stronger statement of contextuality that includes the
-effects of finite-precision.  Every QIVPM must map some events to
-truly uncertain intervals, not just ``almost definite intervals.''
-
-\begin{thm}[Finite-precision Extension of the Kochen-Specker
-  Theorem] \label{cor:Kochen-Specker-IVPM} Given a Hilbert space
-  $\Hilb$ of dimension~$d\ge3$, there is no $\delta$-deterministic
-  QIVPM for $\delta<\frac{1}{3}$.\end{thm}
-
-The proof is by contradiction: Suppose there is a
-$\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this
-assumed QIVPM to construct the following 0-deterministic QIVPM
-$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
-  \imposs,\necess\right\}$:
+To illustrate our proof for non-existence of $\delta$-deterministic
+QIVPMs for $\delta<\frac{1}{3}$, we will explain why we cannot construct
+any $\frac{1}{4}$-deterministic QIVPM in full details. The proof
+is by contradiction: Suppose there is a $\frac{1}{4}$-deterministic
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
+QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
 \[
 \bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
-\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
-\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
+\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\tfrac{1}{4}\right]\:;\\
+\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[\tfrac{3}{4},1\right]\:.
 \end{cases}
 \]
-However, since we know that 0-deterministic QIVPMs do not exist, the
-map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ does
-not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$ is
-indeed a 0-deterministic QIVPM by checking that for orthogonal
-projectors~$P_{0}$ and $P_{1}$, we have that
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
-implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\cite{TaiThesis2018}. Indeed
-when
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have both $\bar{\mu}\left(P_{0}\right)$ and
-$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
-implies
-$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
-When $\delta<\frac{1}{3}$, i.e., $2\delta<1-\delta$, it follows that
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ cannot be a subset of
-$\left[1-\delta,1\right]$. Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
-is a subset of either $\left[0,\delta\right]$ or
-$\left[1-\delta,1\right]$ and the latter is excluded, then
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
-$\left[0,\delta\right]$, which implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
-theorem holds when $\delta<\frac{1}{3}$.
+However, since we know that $0$-deterministic QIVPMs do not exist,
+the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
+does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
+is indeed a $0$-deterministic QIVPM.
+
+by checking that for orthogonal projectors~$P_{0}$ and $P_{1}$,
+we have that $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
+implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\cite{TaiThesis2018}.
+Indeed when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
+which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
+or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
+in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
+must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+
+\begin{figure}
+
+\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
+must be a subset of $\left[0,\frac{1}{4}\right]$.}
+
+\end{figure}
 

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Updating...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Classical $\frac{1}{4}$-deterministic Probability Measure}
+\subsection{Classical $\frac{1}{4}$-deterministic Probability Measure}
 
@@
 case, WE CANNOT construct $\delta$-deterministic probability measures
-for $\delta$ that are less than $\frac{1}{3}$.
+for $\delta<\frac{1}{3}$.
 
-\paragraph{Why a Quantum $\frac{1}{4}$-deterministic Probability Measure is
+\subsection{Why a Quantum $\frac{1}{4}$-deterministic Probability Measure is
 Impossible}
@@
 QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
-\[
+\begin{equation}
 \bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
@@
 \end{cases}
-\]
+\end{equation}
 However, since we know that $0$-deterministic QIVPMs do not exist,
@@
 does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
-is indeed a $0$-deterministic QIVPM.
+is indeed a QIVPM. Since the range of $\bar{\mu}^{\textrm{D}}$, $\left\{ \imposs,\necess\right\} $,
+is a set of singleton sets, if $\bar{\mu}^{\textrm{D}}$ satisfies
+that for orthogonal projectors~$P_{0}$ and $P_{1}$, 
+\begin{equation}
+\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
+\end{equation}
+then we can apply the same reason of proving classical inclusion-exclusion
+principle~\cite{TaiThesis2018} to get
+\[
+\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}^{\textrm{D}}\left(P_{0}P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)
+\]
+which implies $\bar{\mu}^{\textrm{D}}$ is convex, i.e., $\bar{\mu}^{\textrm{D}}$
+is a QIVPM. Therefore, our task now is to prove Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
 
-by checking that for orthogonal projectors~$P_{0}$ and $P_{1}$,
-we have that $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
-implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\cite{TaiThesis2018}.
-Indeed when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+\begin{figure*}
+\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
+must be a subset of $\left[0,\frac{1}{4}\right]$.}
+\end{figure*}
+For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
+and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+$\bar{\mu}\left(P_{0}\right)\subseteq\left[\frac{3}{4},1\right]$,
+$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$,
+and $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},\frac{5}{4}\right]$.
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
+we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
+i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.
+
+For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
 we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
@@
 
-\begin{figure}
-
-\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
-must be a subset of $\left[0,\frac{1}{4}\right]$.}
-
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex
Eliminate LaTeX errors...
prop_prop_letter_ajhs_referee_response.tex Updated...

@@
 
-\title{Response of the Referee Report of ``Quantum Interval-Valued Probability:
+\title{Response to the Referee Report of ``Quantum Interval-Valued Probability:
 Contextuality and the Born Rule''}
@@
 \author{Yu-Tsung Tai}
-\affiliation{Department of Mathematics, Indiana University, Bloomington, Indiana 47405,
-USA}
+
+\affiliation{Department of Mathematics, Indiana University, Bloomington, Indiana
+47405, USA}
+
 \affiliation{Department of Computer Science, Indiana University, Bloomington,
@@
 \author{Andrew J. Hanson}
-\affiliation{Department of Informatics, Indiana University, Bloomington,
-Indiana 47405, USA}
+
+\affiliation{Department of Informatics, Indiana University, Bloomington, Indiana
+47405, USA}
 
 \author{Gerardo Ortiz}
+
 \affiliation{Department of Physics, Indiana University, Bloomington, Indiana 47405,
@@
 \author{Amr Sabry}
+
 \affiliation{Department of Computer Science, Indiana University, Bloomington,
@@
 \maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Classical $\frac{1}{4}$-deterministic Probability Measure}
+\section{Classical \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Probability
+Measure}
 
@@
 is $\delta$-deterministic if, for every event $P\in\events'$, we
-have that either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
+have either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
 or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}
@@
 
-\noindent Then, it is easy to construct $\delta$-deterministic classical
+\noindent It is easy to construct $\delta$-deterministic classical
 IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
@@
 
-\subsection{Why a Quantum $\frac{1}{4}$-deterministic Probability Measure is
+\section{Why a Quantum \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Probability Measure is
 Impossible}

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Proofread by Prof. Hanson~~

@@
 Although the definition of $\delta$-determinism in our paper only
-applied on QIVPMs~\cite{THOS2017}, this definition can be easily
-extended to apply on both classical and quantum IVPMs as follow.
+applied to QIVPMs~\cite{THOS2017}, this definition can be easily
+extended to apply to both classical and quantum IVPMs as follow.
 
@@
 respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
-a double-headed coin that always lands on head. For $\bar{\mu}_{B}$,
+a double-headed coin that always comes up heads. For $\bar{\mu}_{B}$,
 the interpretation is that we throw a coin $1000$ times and we observe
@@
 times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
-$\delta=\frac{1}{4}$, and $\delta$ qualifies how a coin close to
-double-headed, which we can certainly know the outcome of an coin
+$\delta=\frac{1}{4}$, and $\delta$ qualifies how close a coin is
+to double-headed, which we can certainly know the outcome of a coin
 even before tossing. We see here that we can construct $0$-deterministic

### 2018-01-26 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Updating...

@@
 \newcommand{\pmeas}{\ensuremath{\mu}}
-\newcommand{\imposs}{{\text{\wesa{impossible}}}}
-\newcommand{\likely}{{\text{\wesa{likely}}}}
-\newcommand{\unlikely}{{\text{\wesa{unlikely}}}}
-\newcommand{\necess}{{\text{\wesa{certain}}}}
-\newcommand{\unknown}{{\text{\wesa{unknown}}}}
-\newcommand{\midd}{{\text{\wesa{middle}}}}
+% \newcommand{\imposs}{{\text{\wesa{impossible}}}}
+% \newcommand{\likely}{{\text{\wesa{likely}}}}
+% \newcommand{\unlikely}{{\text{\wesa{unlikely}}}}
+% \newcommand{\necess}{{\text{\wesa{certain}}}}
+% \newcommand{\unknown}{{\text{\wesa{unknown}}}}
+% \newcommand{\midd}{{\text{\wesa{middle}}}}
+\newcommand{\imposs}{\ensuremath{\left[0,0\right]}}
+\newcommand{\likely}{\ensuremath{\left[\tfrac{1}{2},1\right]}}
+\newcommand{\unlikely}{\ensuremath{\left[0,\tfrac{1}{2}\right]}}
+\newcommand{\necess}{\ensuremath{\left[1,1\right]}}
+\newcommand{\unknown}{\ensuremath{\left[0,1\right]}}
+\newcommand{\midd}{\ensuremath{\left[\tfrac{1}{4},\tfrac{3}{4}\right]}}
 \newcommand{\fket}[1]{{|#1\rangle}}
@@
 
+\section{Why a Quantum \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic
+Probability Measure is Impossible}
+
+To illustrate our proof for non-existence of $\delta$-deterministic
+QIVPMs for $\delta<\frac{1}{3}$, we will explain why we cannot construct
+any $\frac{1}{4}$-deterministic QIVPM in full details. The proof
+is by contradiction: Suppose there is a $\frac{1}{4}$-deterministic
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
+QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
+\begin{equation}
+\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
+\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\tfrac{1}{4}\right]\:;\\
+\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[\tfrac{3}{4},1\right]\:.
+\end{cases}
+\end{equation}
+However, since we know that $0$-deterministic QIVPMs do not exist,
+the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
+does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
+is indeed a QIVPM. Since the range of $\bar{\mu}^{\textrm{D}}$, $\left\{ \imposs,\necess\right\} $,
+is a set of singleton sets, if $\bar{\mu}^{\textrm{D}}$ satisfies
+that for orthogonal projectors~$P_{0}$ and $P_{1}$, 
+\begin{equation}
+\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
+\end{equation}
+then we can apply the same reason of proving classical inclusion-exclusion
+principle~\cite{TaiThesis2018} to get 
+\[
+\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}^{\textrm{D}}\left(P_{0}P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)
+\]
+which implies $\bar{\mu}^{\textrm{D}}$ is convex, i.e., $\bar{\mu}^{\textrm{D}}$
+is a QIVPM. Therefore, our task now is to prove Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
+
+\begin{figure*}
+\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
+must be a subset of $\left[0,\frac{1}{4}\right]$.}
+\end{figure*}
+
+For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
+and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+$\bar{\mu}\left(P_{0}\right)\subseteq\left[\frac{3}{4},1\right]$,
+$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$,
+and $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},\frac{5}{4}\right]$.
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
+we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
+i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.
+
+For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
+which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
+or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
+in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
+must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+
 \section{Classical \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Probability
@@
 
-\section{Why a Quantum \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Probability Measure is
-Impossible}
+\section{Missing Record Interpretation}
 
-To illustrate our proof for non-existence of $\delta$-deterministic
-QIVPMs for $\delta<\frac{1}{3}$, we will explain why we cannot construct
-any $\frac{1}{4}$-deterministic QIVPM in full details. The proof
-is by contradiction: Suppose there is a $\frac{1}{4}$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
-QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
-\begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
-\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\tfrac{1}{4}\right]\:;\\
-\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[\tfrac{3}{4},1\right]\:.
-\end{cases}
-\end{equation}
-However, since we know that $0$-deterministic QIVPMs do not exist,
-the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
-does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
-is indeed a QIVPM. Since the range of $\bar{\mu}^{\textrm{D}}$, $\left\{ \imposs,\necess\right\} $,
-is a set of singleton sets, if $\bar{\mu}^{\textrm{D}}$ satisfies
-that for orthogonal projectors~$P_{0}$ and $P_{1}$, 
-\begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
-\end{equation}
-then we can apply the same reason of proving classical inclusion-exclusion
-principle~\cite{TaiThesis2018} to get
-\[
-\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}^{\textrm{D}}\left(P_{0}P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)
-\]
-which implies $\bar{\mu}^{\textrm{D}}$ is convex, i.e., $\bar{\mu}^{\textrm{D}}$
-is a QIVPM. Therefore, our task now is to prove Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
+\begin{figure}
 
-\begin{figure*}
-\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
-must be a subset of $\left[0,\frac{1}{4}\right]$.}
-\end{figure*}
-For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
-and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-$\bar{\mu}\left(P_{0}\right)\subseteq\left[\frac{3}{4},1\right]$,
-$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$,
-and $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},\frac{5}{4}\right]$.
-Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
-we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
-i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.
-
-For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
-which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
-Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
-or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
-in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
-must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+\includegraphics[scale=0.8]{Cabello}\caption{\label{fig:Cabello}FIG.~1 in \cite{Cabello_2008}. Each dot represents
+a vector~$v_{ij}$. Each of the $6$ sides of the regular hexagon
+and each of the $3$ rectangles contains only orthogonal vectors.}
+\end{figure}
+Consider $18$ vectors used to prove Kochen-Specker theorem defined
+in Fig.~\ref{fig:Cabello} \cite{CabelloEstebaranzGarcia-Alcaine1996,Cabello_2008}.
 

### 2018-01-27 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex \section{Missing Record Interpretation} Updating...

@@
 
+\label{sec:Classical-=0000BC-deterministic}
+
 Although the definition of $\delta$-determinism in our paper only
@@
 
-\begin{figure}
-
-\includegraphics[scale=0.8]{Cabello}\caption{\label{fig:Cabello}FIG.~1 in \cite{Cabello_2008}. Each dot represents
-a vector~$v_{ij}$. Each of the $6$ sides of the regular hexagon
-and each of the $3$ rectangles contains only orthogonal vectors.}
-\end{figure}
-Consider $18$ vectors used to prove Kochen-Specker theorem defined
-in Fig.~\ref{fig:Cabello} \cite{CabelloEstebaranzGarcia-Alcaine1996,Cabello_2008}.
+\begin{table}
+\noindent \centering{}\caption{\label{tab:classical-IVPMs-results}A sample experimental record for
+a classical experiment with three possible outcomes $\proj{0}$, $\proj{1}$,
+and $\proj{2}$. A event might be happened (H) or not happened (N),
+and the experimental results could be summarized by a $0$-deterministic
+classical IVPM~$\bar{\mu}_{C}$.}
+\begin{tabular}{ccccc}
+\toprule 
+\addlinespace
+$P$  & Trial~1 & Trial~2 & Trial~3 & $\bar{\mu}_{C}(P)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & N & N & N & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{0}$  & N & N & N & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{1}$  & N & N & N & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{2}$ & H & H & H & $\necess$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{0}$  & H & H & H & $\necess$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{1}$  & H & H & H & $\necess$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{2}$ & N & N & N & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & H & H & H & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+A sample experimental results with three possible outcomes $\proj{0}$,
+$\proj{1}$, and $\proj{2}$ are listed in Table~\ref{tab:classical-IVPMs-results}.
+These results could be interpreted as in Sec.~\ref{sec:Classical-=0000BC-deterministic},
+and summarized to a $0$-deterministic classical IVPM~$\bar{\mu}_{C}$.
+Given any Hilbert space of dimension~$d\ge3$, the Kochen-Specker
+theorem asserts that we cannot have a table of experimental results
+summarizing to a $0$-deterministic QIVPM\cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}.
+However, we could have a table of experimental results if some results
+are missing.
 

### 2018-01-27 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex \section{Missing Record Interpretation} Updating...

--- 2018-01-26 prop_prop_letter_ajhs_referee_response.tex
@@
 
+\newcommand{\happen}{\text{H}}
+\newcommand{\notHappen}{\text{N}}
+\newcommand{\missing}{\text{M}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{figure}
+\begin{table}
+\noindent \centering{}\caption{\label{tab:classical-IVPMs-results}A sample experimental record for
+a classical experiment with three possible outcomes $\proj{0}$, $\proj{1}$,
+and $\proj{2}$. A event can be happened ($\happen$) or not happened
+($\notHappen$), and the experimental results could be summarized
+by a $0$-deterministic classical IVPM~$\bar{\mu}_{\ref{tab:classical-IVPMs-results}}$.}
+\begin{tabular}{ccccc}
+\toprule 
+\addlinespace
+$P$  & Trial~1 & Trial~2 & Trial~3 & $\bar{\mu}_{\ref{tab:classical-IVPMs-results}}(P)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{1}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{2}$ & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{0}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{2}$ & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+A sample experimental results with three possible outcomes $\proj{0}$,
+$\proj{1}$, and $\proj{2}$ are listed in Table~\ref{tab:classical-IVPMs-results}.
+Because the results of every event is always the same, they could
+be summarized to a $0$-deterministic classical IVPM~$\bar{\mu}_{\ref{tab:classical-IVPMs-results}}$.
+Given any Hilbert space of dimension~$d\ge3$, the Kochen-Specker
+theorem asserts that we cannot have a table where every event always
+has the same result~\cite{THOS2017}. For example, Table~\ref{tab:quantum-IVPMs-results}
+doesn't give coherent experimental results, and cannot be summarized
+as a QIVPM because given any two one-dimensional projectors $P_{0}$
+and $P_{1}$, 
+\begin{equation}
+\begin{aligned} & \bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}P_{1}\right)=\necess\\
+\nsubseteq & \imposs=\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{1}\right)\,.
+\end{aligned}
+\end{equation}
 
-\includegraphics[scale=0.8]{Cabello}\caption{\label{fig:Cabello}FIG.~1 in \cite{Cabello_2008}. Each dot represents
-a vector~$v_{ij}$. Each of the $6$ sides of the regular hexagon
-and each of the $3$ rectangles contains only orthogonal vectors.}
-\end{figure}
-Consider $18$ vectors used to prove Kochen-Specker theorem defined
-in Fig.~\ref{fig:Cabello} \cite{CabelloEstebaranzGarcia-Alcaine1996,Cabello_2008}.
+\begin{table}
+\noindent \centering{}\caption{\label{tab:quantum-IVPMs-results}A sample inconsistent experimental
+record for a quantum experiment on a three-dimensional Hilbert space,
+where $\proj{\psi}$ is any one-dimensional projector, and $\mathbb{1}-\proj{\psi}$
+is any two-dimensional projector. A event can be happened ($\happen$)
+or not happened ($\notHappen$), but $\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}$
+which summarizes the experimental results is not a QIVPM.}
+\begin{tabular}{ccccc}
+\toprule 
+\addlinespace
+$P$  & Trial~1 & Trial~2 & Trial~3 & $\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}(P)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{\psi}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{\psi}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+However, we can have a table where every event always has the same
+result or missing as long as
 

### 2018-01-27 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex \section{Missing Record Interpretation} Updating...

@@
 \addlinespace
-$P$  & Trial~1 & Trial~2 & Trial~3 & $\bar{\mu}_{\ref{tab:classical-IVPMs-results}}(P)$\tabularnewline
+$P$  & Trial~0 & Trial~1 & Trial~2 & $\bar{\mu}_{\ref{tab:classical-IVPMs-results}}(P)$\tabularnewline
 \midrule
@@
 \end{table}
-A sample experimental results with three possible outcomes $\proj{0}$,
+Sample experimental results with three possible outcomes $\proj{0}$,
 $\proj{1}$, and $\proj{2}$ are listed in Table~\ref{tab:classical-IVPMs-results}.
-Because the results of every event is always the same, they could
+Because the results of every event are always the same, they could
 be summarized to a $0$-deterministic classical IVPM~$\bar{\mu}_{\ref{tab:classical-IVPMs-results}}$.
@@
 theorem asserts that we cannot have a table where every event always
-has the same result~\cite{THOS2017}. For example, Table~\ref{tab:quantum-IVPMs-results}
-doesn't give coherent experimental results, and cannot be summarized
-as a QIVPM because given any two one-dimensional projectors $P_{0}$
-and $P_{1}$, 
-\begin{equation}
-\begin{aligned} & \bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}P_{1}\right)=\necess\\
-\nsubseteq & \imposs=\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{1}\right)\,.
-\end{aligned}
-\end{equation}
-
+has the same result~\cite{THOS2017}. 
 \begin{table}
@@
 or not happened ($\notHappen$), but $\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}$
-which summarizes the experimental results is not a QIVPM.}
+that summarizes the experimental results is not a QIVPM.}
 \begin{tabular}{ccccc}
@@
 \addlinespace
-$P$  & Trial~1 & Trial~2 & Trial~3 & $\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}(P)$\tabularnewline
+$P$  & Trial~0 & Trial~1 & Trial~2 & $\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}(P)$\tabularnewline
 \midrule
@@
 \end{table}
-However, we can have a table where every event always has the same
-result or missing as long as
+For example, Table~\ref{tab:quantum-IVPMs-results} doesn't give
+coherent experimental results, and cannot be summarized as a QIVPM
+because given any two distinct one-dimensional projectors $P_{0}$
+and $P_{1}$, 
+\begin{equation}
+\begin{aligned} & \bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}P_{1}\right)=\necess\\
+\nsubseteq & \imposs=\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{1}\right)\,.
+\end{aligned}
+\end{equation}
+
+\begin{table}
+\noindent \centering{}\caption{\label{tab:quantum-IVPMs-missing}A sample experimental record for
+a quantum experiment on a three-dimensional Hilbert space with some
+records missing. Now a event can be happened ($\happen$), not happened
+($\notHappen$), or missing ($\missing$), and $\proj{\psi_{i}}$
+is any one-dimensional projector with Trial~$i$ missing, and $\mathbb{1}-\proj{\psi_{i}}$
+is any two-dimensional projector with Trial~$i$ missing. Although
+$\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}$ which summarizes the
+experimental results is not directly a QIVPM, the whole records might
+come from coherent experimental results with a QIVPM $\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}'$.}
+\begin{tabular}{cccccc}
+\toprule 
+\addlinespace
+$P$  & Trial~0 & Trial~1 & Trial~2 & $\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}(P)$ & $\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}'(P)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{\psi_{0}}$  & $\missing$ & $\notHappen$ & $\notHappen$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{\psi_{1}}$  & $\notHappen$ & $\missing$ & $\notHappen$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\proj{\psi_{2}}$  & $\notHappen$ & $\notHappen$ & $\missing$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{\psi_{0}}$  & $\missing$ & $\happen$ & $\happen$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{\psi_{1}}$  & $\happen$ & $\missing$ & $\happen$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}-\proj{\psi_{2}}$  & $\happen$ & $\happen$ & $\missing$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+If $\frac{1}{3}$ of records in Table~\ref{tab:quantum-IVPMs-results}
+is missing, we will have a record as in Table~\ref{tab:quantum-IVPMs-missing},
+whose results cannot be directly summarized as a QIVPM. However, because
+a missing record could come from either happened or not happened,
+if every missing record for one-dimensional projectors come from happened,
+and every missing record for two-dimensional projectors come from
+not happened, then the experimental results can be summarized as a
+QIVPM $\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}'$.
 

### 2018-01-28 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Updating...

@@
 
-\section{Why a Quantum \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic
-Probability Measure is Impossible}
+\section{Why a \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic QIVPM is
+Impossible?}
 
@@
 \end{equation}
-However, since we know that $0$-deterministic QIVPMs do not exist,
+However, since we know that $0$-deterministic QIVPMs do not exist~\cite{THOS2017},
 the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
@@
 is a set of singleton sets, if $\bar{\mu}^{\textrm{D}}$ satisfies
-that for orthogonal projectors~$P_{0}$ and $P_{1}$, 
+that for orthogonal projectors $P_{0}$ and~$P_{1}$, 
 \begin{equation}
@@
 then we can apply the same reason of proving classical inclusion-exclusion
-principle~\cite{TaiThesis2018} to get 
+principle to get for each pair of \emph{commuting} projectors $P_{0}$
+and~$P_{1}$, 
 \[
@@
 
-\section{Classical \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Probability
-Measure}
+\section{\texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Classical IVPM}
 
@@
 $\delta=\frac{1}{4}$, and $\delta$ qualifies how close a coin is
-to double-headed, which we can certainly know the outcome of a coin
-even before tossing. We see here that we can construct $0$-deterministic
-as well as $\frac{1}{4}$-deterministic and in fact for any $\delta$
-in the range $\left[0,1\right]$ we can construct a $\delta$-deterministic
-classical probability measure. BUT the situation changes in the quantum
-case, WE CANNOT construct $\delta$-deterministic probability measures
-for $\delta<\frac{1}{3}$.
+to double-headed (or double-tailed), which we can certainly know the
+outcome of a coin even before tossing. We see here that we can construct
+$0$-deterministic as well as $\frac{1}{4}$-deterministic and in
+fact for any $\delta$ in the range $\left[0,1\right]$ we can construct
+a $\delta$-deterministic classical probability measure. BUT the situation
+changes in the quantum case, WE CANNOT construct $\delta$-deterministic
+probability measures for $\delta<\frac{1}{3}$.
 
-\section{Missing Record Interpretation}
+\section{Why a \texorpdfstring{$\frac{1}{3}$}{⅓}-deterministic QIVPM exists?}
 

### 2018-01-28 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Updating...

@@
 does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
-is indeed a QIVPM. Since the range of $\bar{\mu}^{\textrm{D}}$, $\left\{ \imposs,\necess\right\} $,
-is a set of singleton sets, if $\bar{\mu}^{\textrm{D}}$ satisfies
-that for orthogonal projectors $P_{0}$ and~$P_{1}$, 
+is indeed a QIVPM by checking that for orthogonal projectors $P_{0}$
+and~$P_{1}$, 
 \begin{equation}
@@
 \end{equation}
-then we can apply the same reason of proving classical inclusion-exclusion
-principle to get for each pair of \emph{commuting} projectors $P_{0}$
-and~$P_{1}$, 
-\[
-\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}^{\textrm{D}}\left(P_{0}P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)
-\]
-which implies $\bar{\mu}^{\textrm{D}}$ is convex, i.e., $\bar{\mu}^{\textrm{D}}$
-is a QIVPM. Therefore, our task now is to prove Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
+because similar to classical inclusion-exclusion principle, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal})
+implies for each pair of commuting projectors $P_{0}$ and~$P_{1}$,
+\begin{equation}
+\begin{aligned} & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}^{\textrm{D}}\left(P_{0}P_{1}\right)\\
+={} & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,
+\end{aligned}
+\end{equation}
+i.e., $\bar{\mu}^{\textrm{D}}$ is convex.
+
+For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
+and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
+and 
+\begin{equation}
+\begin{aligned} & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\\
+\subseteq{} & \left[\tfrac{3}{4},1\right]+\left[0,\tfrac{1}{4}\right]=\left[\tfrac{3}{4},\tfrac{5}{4}\right]\,.
+\end{aligned}
+\end{equation}
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
+we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
+i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.
 
@@
 \end{figure*}
-
-For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
-and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-$\bar{\mu}\left(P_{0}\right)\subseteq\left[\frac{3}{4},1\right]$,
-$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$,
-and $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},\frac{5}{4}\right]$.
-Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
-we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
-i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.
-
 For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
@@
 \begin{aligned} & \bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}P_{1}\right)=\necess\\
-\nsubseteq & \imposs=\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{1}\right)\,.
+\nsubseteq{} & \imposs=\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{1}\right)\,.
 \end{aligned}

### 2018-01-28 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Updating...

@@
 
-\section{\texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Classical IVPM}
+After we explained why there is no $\delta$-deterministic QIVPMs
+for $\delta<\frac{1}{3}$, we are going to explain the physical meaning
+of $\delta$-deterministic, and understand the transition from $\delta<\frac{1}{3}$
+to $\delta\ge\frac{1}{3}$.
 
-\label{sec:Classical-=0000BC-deterministic}
+\section{Physical Meaning of $\delta$-Determinism}
 
-Although the definition of $\delta$-determinism in our paper only
-applied to QIVPMs~\cite{THOS2017}, this definition can be easily
-extended to apply to both classical and quantum IVPMs as follow.
+Since QIVPMs are extensional of both quantum probability measures
+and classical IVPMs, the meaning of $\delta$-determinism can be explained
+better when we consider $\delta$-deterministic classical IVPMs.
 
-\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
-Given a classical or quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
-where $\events'$ is the set of all events, $\events$, when $\bar{\mu}$
-is a QIVPM and $\events'$ is the set of mutually commuting events,
-$\eventsC$, when $\bar{\mu}$ is a classical one. Then, $\bar{\mu}$
+\begin{definition}[$\delta$-Determinism for classical IVPMs]\label{def:delta-deterministic-classical}
+Given a classical IVPM~$\bar{\mu}:\eventsC\rightarrow\mathscr{I}$,
+where $\eventsC$ is the set of mutually commuting events. Then, $\bar{\mu}$
 is $\delta$-deterministic if, for every event $P\in\events'$, we

### 2018-01-29 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex \section{Physical Meaning of \texorpdfstring{$\delta$}{δ}-Determinism} Updating...

@@
 
-\section{Physical Meaning of $\delta$-Determinism}
+\section{Physical Meaning of \texorpdfstring{$\delta$}{δ}-Determinism}
 
-Since QIVPMs are extensional of both quantum probability measures
-and classical IVPMs, the meaning of $\delta$-determinism can be explained
-better when we consider $\delta$-deterministic classical IVPMs.
+Since the definition of QIVPMs is a generalization of both classical
+IVPMs and conventional quantum probability measures, the meaning of
+$\delta$-determinism can be explained better when we consider $\delta$-deterministic
+classical IVPMs.
 

### 2018-02-04 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Updating...

--- 2018-01-28 prop_prop_letter_ajhs_referee_response.tex
@@
 
-\section{Why a \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic QIVPM is
-Impossible?}
+\section{Finite-precision Extension of the Kochen-Specker Theorem}
 
-To illustrate our proof for non-existence of $\delta$-deterministic
-QIVPMs for $\delta<\frac{1}{3}$, we will explain why we cannot construct
-any $\frac{1}{4}$-deterministic QIVPM in full details. The proof
-is by contradiction: Suppose there is a $\frac{1}{4}$-deterministic
+\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
+\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of
+dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
+$\delta<\frac{1}{3}$.\end{thm}
+
+The proof is by contradiction: Suppose there is a $\delta$-deterministic
 QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
@@
 \end{equation}
-However, since we know that $0$-deterministic QIVPMs do not exist~\cite{THOS2017},
+However, since we know that $0$-deterministic QIVPMs do not exist,
 the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
@@
 \begin{aligned} & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\\
-\subseteq{} & \left[\tfrac{3}{4},1\right]+\left[0,\tfrac{1}{4}\right]=\left[\tfrac{3}{4},\tfrac{5}{4}\right]\,.
+\subseteq{} & \left[1-\delta,1\right]+\left[0,\delta\right]=\left[1-\delta,1+\delta\right]\,.
 \end{aligned}
@@
 Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
-we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
+we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1\right]$,
 i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.
@@
 \begin{figure*}
-\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
-must be a subset of $\left[0,\frac{1}{4}\right]$.}
+\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Either $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]$
+or $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1\right]$.
+Together with the fact that $\bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset$,
+we have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]$.}
 \end{figure*}
 For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
-which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
-Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
-or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
+we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$
+which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\delta\right]$
+or $\left[1-\delta,1\right]$ and the latter is excluded as illustrated
 in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
-must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+must be a subset of $\left[0,\delta\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
 
-\section{\texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Classical IVPM}
+\section{Mermin-Peres ``Magic Square''}
 
-\label{sec:Classical-=0000BC-deterministic}
+In our response, we provide an example to show that if enough experimental
+records are missing, there exists a probability measure consistent
+with the experimental records even if the presented experimental records
+are always the same. In this section, we want to provide a similar
+example on the Mermin-Peres ''Magic Square''. We consider a two
+spin-$\frac{1}{2}$ Hilbert space $\Hilb=\Hilb_{1}\otimes\Hilb_{2}$
+of dimension $d=4$. We use the same nine observables $\mathbf{O}_{ij}$
+with $i$ and $j$ ranging over $\{0,1,2\}$ from the Mermin-Peres
+``magic square'' used to prove the Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
 
-Although the definition of $\delta$-determinism in our paper only
-applied to QIVPMs~\cite{THOS2017}, this definition can be easily
-extended to apply to both classical and quantum IVPMs as follow.
+{{\renewcommand{\arraystretch}{2}% 
+\begin{center} 
+\begin{tabular}{r|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|} 
+$\mathbf{O}_{ij}$~ & $j=0$ & $j=1$ & $j=2$ \\ 
+\hline  
+$i=0~$ & $\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline 
+\hline  
+$i=1~$ & $\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline 
+\hline  
+$i=2~$ & $\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline 
+\hline  
+\end{tabular}\,.
+\par\end{center} 
+}
 
-\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
-Given a classical or quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
-where $\events'$ is the set of all events, $\events$, when $\bar{\mu}$
-is a QIVPM and $\events'$ is the set of mutually commuting events,
-$\eventsC$, when $\bar{\mu}$ is a classical one. Then, $\bar{\mu}$
-is $\delta$-deterministic if, for every event $P\in\events'$, we
-have either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
-or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}
+\noindent The observables are constructed using the Pauli matrices
+$\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\} $ whose
+eigenvalues are all either~$1$ or $-1$ \cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
+They are arranged such that in each row and column, \emph{except the
+column $j=2$}, every observable is the product of the other two.
+In the $j=2$ column, we have instead that $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
 
-\begin{table}
-\noindent \centering{}\caption{\label{tab:classical-IVPMs}Examples of $\delta$-deterministic classical
-IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ on commuting events $P$.}
+Assume we measure these observables twice. By the Kochen-Specker theorem,
+the following measurement results is impossible because the number
+of expectation values in the $j=2$ column is odd.
+\begin{center}
 \begin{tabular}{ccc}
@@
 \addlinespace
-$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$ \tabularnewline
+$\mathbf{O}_{ij}$  & Trial~0 & Trial~1\tabularnewline
 \midrule
@@
 \addlinespace
-$\mathbb{0}$  & $\imposs$  & $\imposs$ \tabularnewline
+$\mathbf{O}_{00}$ , $\mathbf{O}_{01}$, $\mathbf{O}_{10}$ , $\mathbf{O}_{11}$  & $-1$ & $-1$\tabularnewline
 \midrule 
 \addlinespace
-$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$ \tabularnewline
-\midrule 
-\addlinespace
-$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$ \tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$  & $\necess$ \tabularnewline
+$\mathbf{O}_{02}$ , $\mathbf{O}_{12}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{21}$
+, $\mathbf{O}_{22}$  & $1$ & $1$\tabularnewline
 \bottomrule
 \end{tabular}
-\end{table}
+\par\end{center}
 
-\noindent It is easy to construct $\delta$-deterministic classical
-IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
-where $\proj{0}$ and $\proj{1}$ represents heads and tails in coin-tossing,
-respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
-a double-headed coin that always comes up heads. For $\bar{\mu}_{B}$,
-the interpretation is that we throw a coin $1000$ times and we observe
-$750$ heads and $200$ tails and the coin falls under the couch $50$
-times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
-$\delta=\frac{1}{4}$, and $\delta$ qualifies how close a coin is
-to double-headed (or double-tailed), which we can certainly know the
-outcome of a coin even before tossing. We see here that we can construct
-$0$-deterministic as well as $\frac{1}{4}$-deterministic and in
-fact for any $\delta$ in the range $\left[0,1\right]$ we can construct
-a $\delta$-deterministic classical probability measure. BUT the situation
-changes in the quantum case, WE CANNOT construct $\delta$-deterministic
-probability measures for $\delta<\frac{1}{3}$.
-
-\section{Why a \texorpdfstring{$\frac{1}{3}$}{⅓}-deterministic QIVPM exists?}
-
-\begin{table}
-\noindent \centering{}\caption{\label{tab:classical-IVPMs-results}A sample experimental record for
-a classical experiment with three possible outcomes $\proj{0}$, $\proj{1}$,
-and $\proj{2}$. A event can be happened ($\happen$) or not happened
-($\notHappen$), and the experimental results could be summarized
-by a $0$-deterministic classical IVPM~$\bar{\mu}_{\ref{tab:classical-IVPMs-results}}$.}
-\begin{tabular}{ccccc}
+However, if half of the records are missing, i.e., $\delta=\frac{1}{2}$,
+we might get the following measurement results, where $\missing$
+stands for missing data.
+\begin{center}
+\begin{tabular}{cccc}
 \toprule 
 \addlinespace
-$P$  & Trial~0 & Trial~1 & Trial~2 & $\bar{\mu}_{\ref{tab:classical-IVPMs-results}}(P)$\tabularnewline
+$\mathbf{O}_{ij}$  & Trial~0 & Trial~1 & $\begin{aligned} & \textrm{Missing Record}\\
+ & \textrm{Might Be}
+\end{aligned}
+$\tabularnewline
 \midrule
@@
 \addlinespace
-$\mathbb{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
+$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$ & $\missing$ & $1$\tabularnewline
 \midrule 
 \addlinespace
-$\proj{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
+$\mathbf{O}_{01}$ , $\mathbf{O}_{10}$  & $\missing$ & $-1$ & $1$\tabularnewline
 \midrule 
 \addlinespace
-$\proj{1}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
+$\mathbf{O}_{02}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$  & $1$ & $\missing$ & $-1$\tabularnewline
 \midrule 
 \addlinespace
-$\proj{2}$ & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{0}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{2}$ & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
+$\mathbf{O}_{12}$ , $\mathbf{O}_{21}$  & $\missing$ & $1$ & $-1$\tabularnewline
 \bottomrule
 \end{tabular}
-\end{table}
-Sample experimental results with three possible outcomes $\proj{0}$,
-$\proj{1}$, and $\proj{2}$ are listed in Table~\ref{tab:classical-IVPMs-results}.
-Because the results of every event are always the same, they could
-be summarized to a $0$-deterministic classical IVPM~$\bar{\mu}_{\ref{tab:classical-IVPMs-results}}$.
-Given any Hilbert space of dimension~$d\ge3$, the Kochen-Specker
-theorem asserts that we cannot have a table where every event always
-has the same result~\cite{THOS2017}. 
-\begin{table}
-\noindent \centering{}\caption{\label{tab:quantum-IVPMs-results}A sample inconsistent experimental
-record for a quantum experiment on a three-dimensional Hilbert space,
-where $\proj{\psi}$ is any one-dimensional projector, and $\mathbb{1}-\proj{\psi}$
-is any two-dimensional projector. A event can be happened ($\happen$)
-or not happened ($\notHappen$), but $\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}$
-that summarizes the experimental results is not a QIVPM.}
-\begin{tabular}{ccccc}
-\toprule 
-\addlinespace
-$P$  & Trial~0 & Trial~1 & Trial~2 & $\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}(P)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-$\proj{\psi}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{\psi}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{table}
-For example, Table~\ref{tab:quantum-IVPMs-results} doesn't give
-coherent experimental results, and cannot be summarized as a QIVPM
-because given any two distinct one-dimensional projectors $P_{0}$
-and $P_{1}$, 
-\begin{equation}
-\begin{aligned} & \bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}P_{1}\right)=\necess\\
-\nsubseteq{} & \imposs=\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{1}\right)\,.
-\end{aligned}
-\end{equation}
+\par\end{center}
 
-\begin{table}
-\noindent \centering{}\caption{\label{tab:quantum-IVPMs-missing}A sample experimental record for
-a quantum experiment on a three-dimensional Hilbert space with some
-records missing. Now a event can be happened ($\happen$), not happened
-($\notHappen$), or missing ($\missing$), and $\proj{\psi_{i}}$
-is any one-dimensional projector with Trial~$i$ missing, and $\mathbb{1}-\proj{\psi_{i}}$
-is any two-dimensional projector with Trial~$i$ missing. Although
-$\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}$ which summarizes the
-experimental results is not directly a QIVPM, the whole records might
-come from coherent experimental results with a QIVPM $\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}'$.}
-\begin{tabular}{cccccc}
-\toprule 
-\addlinespace
-$P$  & Trial~0 & Trial~1 & Trial~2 & $\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}(P)$ & $\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}'(P)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$ & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-$\proj{\psi_{0}}$  & $\missing$ & $\notHappen$ & $\notHappen$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\proj{\psi_{1}}$  & $\notHappen$ & $\missing$ & $\notHappen$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\proj{\psi_{2}}$  & $\notHappen$ & $\notHappen$ & $\missing$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{\psi_{0}}$  & $\missing$ & $\happen$ & $\happen$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{\psi_{1}}$  & $\happen$ & $\missing$ & $\happen$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}-\proj{\psi_{2}}$  & $\happen$ & $\happen$ & $\missing$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$ & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{table}
-If $\frac{1}{3}$ of records in Table~\ref{tab:quantum-IVPMs-results}
-is missing, we will have a record as in Table~\ref{tab:quantum-IVPMs-missing},
-whose results cannot be directly summarized as a QIVPM. However, because
-a missing record could come from either happened or not happened,
-if every missing record for one-dimensional projectors come from happened,
-and every missing record for two-dimensional projectors come from
-not happened, then the experimental results can be summarized as a
-QIVPM $\bar{\mu}_{\ref{tab:quantum-IVPMs-missing}}'$.
+Since the experimental results are missing, it might come form the
+third column. In this kind of situation, the expectation values of
+each observables are always $0$, and the product relations among
+these the expectation values must be consistent with the the product
+relations among observables.
+
+Notice that we need more experimental results when considering the
+Mermin-Peres ``magic square'' example. The reason is that in a four-dimensional
+Hilbert space, we know a $\frac{1}{2}$-deterministic QIVPMs, but
+we don't know whether there exists a $\delta$-deterministic QIVPM
+for $\frac{1}{3}<\delta\le\frac{1}{2}$.
 

### 2018-02-06 dissertation.tex
Updates from ShareLaTeX
dissertation.tex Updating informations...

@@
 \usepackage{comment}
+%\usepackage[basic]{complexity}
+\newcommand{\lang}[1]{{\ensuremath{\mathsf{#1}}}}
+\newcommand{\newlang}[2]{\newcommand{#1}{\lang{#2}}}
+\newlang{\usat}{UNIQUE-SAT}
+\usepackage[all]{xy}
+\usepackage{framed}
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage[braket,qm]{qcircuit}
+\usepackage{mathrsfs}
+\usepackage{amssymb}
+
+\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
+\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
+\newcommand{\muB}{\ensuremath{\mu^{B}}}
+\newcommand{\events}{\ensuremath{\mathcal{E}}}
+\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
 
@@
 %data for Title Page
-\begin{comment}
-\title{Dissertation Title}
-\author{Author}
-\date{Completion Date}
-\end{comment}
 \title{Discrete Quantum Theories and Computing}
@@
 \date{\today}
-\maketitle
+\maketitle[Department of Mathematics][Department of Computer Science]
 
 %data for Acceptance Page
-\committeechair{Committee Chair}
-\readertwo{2nd Reader}
-\readerthree{3rd Reader}
-\readerfour{4th Reader}
 \defensedate{Defense Date}
-\acceptancepage
+\acceptancepage{Prof. Amr A. Sabry}{Prof. Dylan Paul Thurston}{Prof. Gerardo Ortiz}{Prof. Andrew J. Hanson}[Prof. Shouhong Wang]
 
 %data for Copyright Page
-\begin{comment}
-\cryear{Current Year}
-\end{comment}
 \cryear{2018}
@@
 \begin{abstract}
-\begin{comment}
- The abstract is double-spaced and limited to 350 words. As many people will learn about
-your work through your abstract published in Dissertation Abstracts (http://proquest.umi.com/login),
-you should spend a good bit of effort in the composition of both the abstract and the title of your work.
-Try to convey the flavor of your work, not just the bare bones of your findings; in an average abstract
-there will be about 70 characters per line with a maximum of 35 lines. You should also work to phrase your
-title so that it truly describes the contents and will be easily found in the index of Dissertation Abstracts.
-The index is based on key words, so be as specific as you can be about your subject.
-\end{comment}
 Our primary research interest is to build a quantum computing model
@@
 \end{abstract}
+\tableofcontents{}
 
-\tableofcontents
+\chapter{Introduction}
 
-\chapter{Documentation}
+Before diving into quantum computing, it is instructive to review
+two kinds of classical computers: digital and analog. Although discrete
+digital computers could be modeled by various computational models,
+including Turing machines~\cite{Turing_1937}, these models are essentially
+the same by the (strong) Church-Turing thesis \cite{Church_1936,Turing_1937,Kleene_1943}.
+Moreover, any Turing-computable function could be carried out by a
+digital computer as long as it has enough resources~\cite{Piccinini2015}.
+In contrast, there are various idealized real computation models \cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
+Although these models are usually more powerful than discrete Turing
+machines, their computational powers might not be realized by realistic
+analog chips and computers, and the realized analog computational
+devices are mostly chips embedded in our digital computers to communicate
+with non-computational analog devices~\cite{Camenzind2005}. Currently
+most of the quantum computing models based on the continuum of real
+numbers. Similar to the development classical computers, the computational
+power of realistic quantum computers might not be the same as predicted
+by current quantum computing models. When developing realistic quantum
+computers or estimating the computational powers of realistic quantum
+computers, it might also be helpful to study discrete quantum computing
+models.
 
-This pdf doubles as documentation for the iuphd.cls file, and as a sample for the output.
-The iuphd class is based on the standard \LaTeX \ report class, and as such you may assume that it follows
-the default formatting of the report class unless otherwise specified below.  The
-changes to the report class include the following:
+Despite the history of computation, when replacing the continuum of
+complex and real numbers by the discrete finite fields and finite
+number of intervals, we show how a number of subtle properties of
+quantum computing can be teased apart, step by step, as we explore
+the implications of \emph{discrete quantum theories} in a systematic
+fashion. In particular, on different discrete quantum theories, we
+will present how geometrical structure of states and quantum probability
+could be, and how these mathematical structures affect the power of
+discrete quantum computing.
 
-\begin{itemize}
- \item changes to the default settings for margins, font size (11pt), spacing (double), and pagination,
- \item the quote, quotation, and verse environments have been changed to switch temporarily to single spacing, and
-       remove the extra space at the top and bottom,
- \item the enumerate and itemize environments have been changed to remove extra space between the items and at the
-       top and bottom,
- \item a line has been added to prevent the double spacing from affecting arrays,
- \item both numbered and unnumbered chapter headings are now centered by default,
- \item heading names such as CHAPTER, and BIBLIOGRAPHY are now all caps by default regardless of how they are typed,
- \emph{(This is accomplished with the help of textcase.sty.  Not all latex distributions come with this by default.)}
- \item changes to the definitions of \textbackslash maketitle and the `abstract' environment,
- \item the addition of commands for creating the acceptance page and copyright page,
- \item the addition of the `acknowledgments', `preface', and `dedication' environments,
- \item the addition of macros for specifying the department or school name, the names of
- the committee members, the defense date, and the copyright year,
- \item document class options for changing ``Department'' to ``School'' on the title page, and for showing
- the abstract, preface, acknowledgments, or dedication in the table of contents.
-\end{itemize}
+\chapter{Conventional Quantum Theory}
 
-The appropriate commands for using these features are already typed into the dissertation.tex sample file,
-with the optional items (dedication, preface, and copyright) commented out.  Simply remove the \% from the front
-of these optional commands if you wish to use them.  The headings for the acknowledgments, preface, and dedication have
-been defined as unnumbered chapter headings, which means they will not show up in the table of contents by default.
-See the instructions below for adding them to the table of contents if desired.
+\section{Geometrical Structure of States}
 
-\section{Current Standards at IU}
-The current version of iuphd.cls complies with the standards of formatting a dissertation at IU as of 2013.  Below is a discussion of
-some of the main points.
+An $n$-qubit pure state in the conventional quantum theory (CQT)
+is represented as a vector in the $2^{n}$-dimensional Hilbert space.
+If we eliminate all symmetries, an irreducible state is actually a
+point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
+also known as the complex projective space~$\mathbb{CP}^{2^{n}-1}$
+\cite{Hatcher2001,Bengtsson2007}. These irreducible quantum states
+can also be classified as product states and entangled states, and
+the latter one plays the essential role for pure-state algorithms
+\cite{Mermin2007,Jaeger2007}.
 
-The current pagination standard is for the page number to appear centered at the top or bottom of the
-page, and to use lowercase roman numerals for the material preceding the first chapter with the title page unnumbered but counting as
-page one. The only part of this that is not standard in the \LaTeX \ report class is the use of roman numerals, which was accomplished
-by changing the definitions to \textbackslash maketitle and \textbackslash tableofcontents.
+\section{Quantum Probability}
 
-The current standard for chapter headings seems to be that they are centered and in all caps.  The iuphd.cls enforces these
-conventions automatically, however it is possible to override these changes with titlesec and titletoc. Because the textcase package is used,
-the capitalization is not affected in math mode, so for instance
-\medskip
+Given a pure state~$\ket{\phi}$, when we measure an observable represented
+by an Hermitian matrix~$\mathbf{O}$, the measurement result is one
+of the eigenvalues of $\mathbf{O}$. The probability of getting a
+particular eigenvalue~$\lambda$ is $\melem{\phi}{P}{\phi}$, where
+$P$ is the projection operator onto the eigenspace of $\lambda$.
+This rule of computing the probability is called the Born rule \cite{Born1983,Mermin2007,Jaeger2007},
+which is used when we want to extract information from a quantum computer.
+For any mixed state~$\rho$, the generalized Born rule induces a
+conventional quantum probability measure $\muB_{\rho}:\events\rightarrow[0,1]$,
+where $\events$ is the set of all projection operators on a given
+Hilbert space. Conversely, any quantum probability measure $\mu:\events\rightarrow[0,1]$
+can be induced from a mixed state $\rho$ in the Hilbert space of
+dimension $d\ge3$ according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+In another word, this state $\rho$ is the unique state consistent
+with any given quantum probability measure.
 
-\textbackslash section\{\$p\$-adic numbers\}
-\medskip
+\chapter{Quantum Theories and Computing over Finite Fields}
 
-\noindent will give the output ``$p$-ADIC NUMBERS'' in both the section heading and in the table of contents
-(unless the value of \textbackslash tocdepth is changed to prevent sections from being listed in the table of contents).
-Since all caps takes up more space horizontally than mixed upper and lowecase text, the size of the chapter headings
-has been reduced to \textbackslash LARGE from \textbackslash huge.  However, no changes have been made to the size of any of the
-other headings in the report class.
+\section{Modal Quantum Theory and Computing}
 
-Most dissertations are one-sided, with an additional half inch added to the left hand margin on each page for the purpose of binding.
-Although this is the standard, they do allow for the possibility of two-sided printing, which would cause the side with the extra margin
-to alternate for binding.  This is automatically enforced simply by using the twoside option (a feature already built into the
-standard report class). This is done as follows:
-\medskip
+Our first discrete model replaces the complex numbers by a unrestricted
+finite field~$\mathbb{F}_{q}$ \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
+In this model, an $n$-qubit state is a non-zero vector in $\mathbb{F}_{q}^{2^{n}}$.
+When we measure a given state~$\ket{\phi}$, an observable is replaced
+by a basis~$\mathcal{B}$ of $\mathbb{F}_{q}^{2^{n}}$. Since $\ket{\phi}$
+can be represented by the summation across a unique subset~$\mathcal{S}$
+of the basis~$\mathcal{B}$, whether it is possible or impossible
+to measure a basis vector~$\ket{i}$ depends on whether $\ket{i}$
+is in $\mathcal{S}$ or not. Because this model only predicts whether
+a result is possible or impossible, it is called the modal quantum
+theory. Its computational model, called the modal quantum computing,
+is far from conventional quantum computing. Although modal quantum
+computing can express simple algorithms such as quantum teleportation
+\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
+it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
+This quantum theory is, however, also so powerful that it can be used
+to solve an unstructured database search of size $N$ using $O(\log(N))$
+steps, which outperforms the known asymptotic bound $O(\sqrt{N})$
+in conventional quantum computing \cite{Grover:1996:FQM:237814.237866,BennettBernsteinBrassardVazirani1997,Mermin2007,Jaeger2007}.
 
-\textbackslash documentclass[twoside]\{iuphd\}
-\medskip
+\section{Discrete Quantum Theory and Computing (I)}
 
-There does not seem to be a standard about whether the abstract, preface, acknowledgments, and dedication are listed in the table of
-contents (TOC) or not.  As such, an option has been provided for including or excluding each one individually.  The syntax for these options
-follows the pattern `showX' if X is to be listed in the TOC, and 'hideX' if X is to be omitted from the TOC, where X can be any of the four
-items listed above.  In all cases, the default is for these \emph{not} to have entries in the table of contents.  So for example, to include
-both the abstract and the preface in the table of contents, but not the dedication or acknowledgments, you would use the code:
-\medskip
+Our second model called discrete quantum theory (I) considers only
+finite fields of order $p^{2}$, with the prime $p$ of the form $4\ell+3$
+($\ell$ a non-negative integer) \cite{geometry2013,DQT2014}. In
+this model, an irreducible state is a vector in $\mathbb{F}_{p^{2}}^{2^{n}}$,
+and can be reduced to a point in the discrete complex projective space~$\mathbb{DCP}^{2^{n}-1}$.
+Among these irreducible states, the product states and entangled states
+can not only be identified as in CQT but also be counted for different
+$p$. Although the state space is a natural discrete analog to CQT,
+this model still only predicts whether a measurement result is possible
+or impossible, because it is not possible to define an inner product
+in the usual sense due to the modular arithmetic~\cite{grove2002classical}.
+Under suitable conditions, we can have deterministic quantum algorithms
+such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
+and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
+but this still leads to excessive computational power for the unstructured
+database search problem for certain database sizes.
 
-\textbackslash documentclass[showabstract,showpreface]\{iuphd\}
-\medskip
+\section{Discrete Quantum Theory and Computing (II)}
 
-\noindent To include a line for the bibliography in the table of contents, the command
-\medskip
+Our third model, discrete quantum theory (II)~\cite{DQT2014}, restricts
+states in some local region of $\mathbb{F}_{p^{2}}^{2^{n}}$. Within
+a local region, a notion of inner product and probability could be
+recovered. Its discrete quantum computing can be further applied to
+the deterministic Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007}
+and the probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
 
-\textbackslash addcontentsline\{toc\}\{chapter\}\{BIBLIOGRAPHY\}
-\medskip
+\section{Toward Discrete Quantum Probability}
 
-\noindent should be placed directly above the \textbackslash bibliography and \textbackslash bibliographystyle commands.  It may be necessary
-to use \textbackslash clearpage above this command to get the page number displayed in the contents to be correct.  However, if you are using
-\textbackslash include for each chapter, then \textbackslash clearpage has technically already been used in this case, and so it is not
-necessary to use it again. Similar commands will work for including any unnumbered heading in the table of contents, with careful attention
-to the effects of \textbackslash clearpage.
+When people tried to define quantum probability over finite fields,
+people tended to treat the original Born rule as an axiom, and tried
+to modify it to get a discrete Born rule \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644,DQT2014,Ellerman2016a}.
+However, any modified Born rule could hardly work on the whole vector
+space, since there is no inner product on the whole vector space over
+finite fields. Instead of treating the Born rule as an axiom, the
+Born rule can actually be deduced from a set of abstract definitions
+and axioms according to Gleason's theorem. Although we might hope
+to deduce a discrete Born rule directly from a similar set of definitions
+and axioms, no discrete Born rule satisfies certain properties motivated
+by Gleason's theorem with infinitely precise real-number probability~\cite{Gardiner2014}.
+Since the state spaces are now discrete and finite, this suggests
+us to consider a discrete Born rule mapping to finite number of intervals
+called interval-valued probability~\cite{JamisonLodwick2004,THOS2017}.
+To adopting the idea of interval-valued probability step-by-step,
+before attempting to study quantum interval-valued probability over
+finite fields, we will first review the classical interval-valued
+probability, and extend it with the conventional quantum theory.
 
-Various commands have been defined for the data that will show up on the title page, acceptance page, and copyright page.  These include:
-\begin{itemize}
- \item \textbackslash title - for the title of the dissertation
- \item \textbackslash author - for the name of the author of the dissertation
- \item \textbackslash date - for the \emph{completion date} of the dissertation
- \item \textbackslash department - this is optional.  The default value is ``Mathematics,'' but if you are in a different department, this
-        command can be used to change its value to the name of whatever department (or school) you are in.  
- \item \textbackslash committeechair, \textbackslash readertwo, \textbackslash readerthree, \textbackslash readerfour - for the names of the
-                      dissertation committee members.
- \item \textbackslash defensedate - for the \emph{defense date} of the dissertation (which may not match the completion date).
- \item \textbackslash cryear - for the copyright year.
-\end{itemize}
+\chapter{Quantum Interval-Valued Probability}
 
-Additionally the commands \textbackslash acceptancepage and \textbackslash copyrightpage have been defined to generate the acceptance page and copyright page
-respectively.  The copyright page is not required, so it has been commented out of my dissertation.tex sample file.  Two document class options have been provided
-for switching the text on the title page between ``Department'' and ``School.''  These options are given the obvious names `department' and `school'. The
-default option is `department', so it only needs to be changed if you are in a school rather than a department.
+\section{Classical Interval-Valued Probability}
 
-A CV is also required following the bibliography, however, to maintain maximum flexibility I have not provided any special tools for
-formatting a CV.  Various packages are available that do this, although I prefer custom formatting. As such, I have provided only a
-line for including the CV after the bibliography, which is currently commented out.
+In the classical setting, there are several proposals for ``imprecise
+probabilities'' \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+Although these proposals differ in some details, they all share the
+fact that the probability $\bar{\mu}(E)$ of an event~$E$ is generalized
+from a single \emph{real number} to an \emph{interval}~$[l,r]$,
+where~$l$ intuitively corresponds to the strength of evidence for
+the event~$E$ and~$1-r$ corresponds to the strength of evidence
+against the same event. Given a sample space~$\Omega$ and a set
+of intervals~$\mathscr{I}$, similar to a classical probability measure
+$\mu:2^{\Omega}\rightarrow\left[0,1\right]$, a classical interval-valued
+probability measure (IVPM) $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+needs to satisfy some coherent axioms. By satisfying the convexity
+axiom \cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
+Shapley proved that there is always a classical probability measure
+consistent with the classical IVPM~$\bar{\mu}$ \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
+Given any random variable, its expectation value with respect to classical
+probability measures consistent with~$\bar{\mu}$ is consistent with
+its Choquet integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+with respect to $\bar{\mu}$ \cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
 
-\section{Suggestions for additional formatting}
+\section{Quantum Interval-Valued Probability}
 
-For longer documents, it is often easier to manage if it is broken into multiple files.  This can be done by using the
-\textbackslash include\{filename\} or \textbackslash input\{filename\} commands.  You can think of
-\textbackslash input\{filename\} as an alias for all of the text contained in filename.tex: the text contained in that file,
-simply gets inserted at the exact spot where the command \textbackslash input is used.  This means that filename.tex should not have
-\textbackslash begin\{document\}, \textbackslash end\{document\}, or a preamble, as illustrated by iuphd-doc.tex in this example.
-On the other hand, \textbackslash include\{filename\} has the additional feature of adding \textbackslash clearpage both before and after
-the text being inserted.  This has important consequences for formatting.  Say that you have a file for each chapter,
-and your first chapter is the introduction.  If you do something like this:
-\medskip
+The quantum extension, quantum interval-valued probability measure
+(QIVPM) $\bar{\mu}:\events\rightarrow\mathscr{I}$, is a generalization
+of both classical IVPMs $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+and conventional quantum probability measures $\mu:\events\rightarrow[0,1]$
+\cite{THOS2017}, because QIVPMs reduce to classical IVPMs when the
+space of quantum events $\events$ is restricted to mutually commuting
+events, and reduces to conventional quantum probability measures when
+mapping to infinitely precise uncountable intervals $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
+While Shapley and Gleason both proved there must be a ``state''
+consistent with any given QIVPM in the reduced cases, in general there
+exists a QIVPM such that no state is consistent with it. However,
+we found a class of QIVPMs such that all QIVPMs in this class are
+consistent with a non-empty ``ball'' of quantum states whose radius
+is defined by the maximal length of the intervals, and recovers the
+original Gleason theorem asymptotically. Similarly, the conventional
+quantum expectation value and the classical Choquet integral are together
+generalized to the quantum interval-valued expectation value. This
+is used to prove an imprecise Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+which suggests a possible resolution of the Meyer-Mermin debate on
+the impact of finite-precision measurement on the Kochen-Specker theorem
+\cite{PhysRevLett.83.3751,Mermin1999}.
 
-\textbackslash chapter\{Introduction\}
+\chapter{Further Questions}
 
-\textbackslash include\{chap1\}
-\medskip
-
-\noindent then the title is formatted on its own page, and the text in chap1.tex will start on a new page; it produces
-the same result as
-\medskip
-
-\textbackslash chapter\{Introduction\}
-
-\textbackslash clearpage
-
-\textbackslash input\{chap1\}
-\medskip
-
-\noindent To avoid having the title put on a separate page there are two options: use input instead of include
-(without \textbackslash clearpage), or use the command \textbackslash chapter\{INTRODUCTION\} inside the file chap1.tex.
-I favor the second option as illustrated in this example with iuphd-doc.tex.
-
-Many \LaTeX \ packages are already available for additional customization of the formatting which is otherwise built in.
-Some of these are listed below.  To use them, simply declare them with \textbackslash usepackage in the preamble
-and refer to the documentation files for them, which are easily available online.
-
-\begin{itemize}
- \item titlesec - for custom formatting of part, chapter, and section headings.
- \item titletoc or tocloft - for custom formatting of the table of contents.
- \item nomencl - for lists of notation (a tweak of makeindex).
- \item prettyref - for custom formatting of references (e.g. referencing equations as (1), (2), etc., instead of the default
-       1, 2, etc.).  The ams packages also have a similar feature but it is much more limited.
- \item natbib, custom-bib, or biblatex - offer additional flexibility for bibliography formatting beyond the standard used by
-       the mathematics community.
- \item setspace - contains features for resetting the global line spacing, as well as environments that can be used to change
-       spacing locally, which are compatible with the quote, quotation, and verse environments.
- \item quoting - provides a more flexible quotation environment, with options for adjusting the margins manually.  This package
-     should be used with setspace, to ensure single spacing of the quotations.
- \item enumitem or paralist - provide several more flexible list environments.
- \item titling - for custom changes to maketitle.
- \item geometry - for customizing the page layout.
-\end{itemize}
-
-%add features for block quotes, underlined titles, and different departments.
-
-The last two should not be necessary unless the standards at IU change.  However, if that happens, it would really be better to
-rewrite the iuphd document class.  Additional packages and other useful information can be found in \cite{mittelbach2004latex}.
-
-\section{quote samples}
-The quote environment:
-\begin{quote}
-``God does not play dice with the universe.'' - Albert Einstein
-\end{quote}
-The quotation environment:
-\begin{quotation}
- ``A GREAT discovery solves a great problem, but there is a grain of discovery in the solution of any problem.
- Your problem may be modest, but if it challenges your curiosity and brings into play your inventive faculties,
- and if you solve it by your own means, you may experience the tension and enjoy the triumph of discovery.''
-
- - George P\'olya
-\end{quotation}
-The verse environment:
-\begin{verse}
-Im September ist alles aus Gold:\\ 
-die Sonne, die durch das Blau hinrollt,\\
-das Stoppelfeld,\\
-die Sonnenblume, schlafrig am Zaun,\\
-das Kreuz auf der Kirche,\\
-der Apfel im Baum.\\
-Ob er h\"alt,\\
-ob er f\"allt? \\
-Da wirft ihn geschwind\\
-der Wind\\
-in die goldene Welt.
-
-- Georg Britting
-\end{verse}
-
-\section{Troubleshooting}
-
-If you are getting an error with the TOC, you may have at least one of the following two problems:
-\begin{enumerate}
- \item you do not have textcase.sty in your latex distribution,
- \item you compiled a previous *.toc file with a different latex class (e.g. the amsbook class).
-\end{enumerate}
-Make sure you have textcase.sty, delete the *.toc file, and recompile.
+When people proved the original Gleason theorem, people usually exploited
+the geometrical structure of real 3-dimensional Hilbert space \cite{gleason1957,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+Since our finite-precision extension of the Gleason theorem only applies
+on a class of QIVPMs, we might want to ask how to modify these geometrical
+arguments to have a Gleason-type theorem for general QIVPMs. We will
+further study the tensor product structure among QIVPMs which is essential
+for defining product and entangled states, and serves the basis to
+discuss quantum nonlocality~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+and quantum computing with QIVPMs. Finally, we want to improve the
+discrete quantum theories to consider QIVPMs over finite fields in
+future research.
 
@@
 \bibliography{prop}
+
 \end{comment}

### 2018-02-06 prop_prop_letter_ajhs_referee_proof.tex
prop_prop_letter_ajhs_referee_proof.tex Copied from prop_prop_letter_ajhs_referee_response.tex...

\documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
showkeys, longbibliography, amsmath, amssymb, floatfix]{revtex4-1} 
\pdfoutput=1

\usepackage{fullpage}
\usepackage{cmap}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[french,main=english]{babel}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[backref=false]{hyperref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[braket,qm]{qcircuit}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\usepackage{comment}
\usepackage{xparse}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}[thm]
\newtheorem{cor}{Corollary}[thm]
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{condition}[assumption]{Condition}

\DeclareUnicodeCharacter{0229}{\c{e}}

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
% \newcommand{\imposs}{{\text{\wesa{impossible}}}}
% \newcommand{\likely}{{\text{\wesa{likely}}}}
% \newcommand{\unlikely}{{\text{\wesa{unlikely}}}}
% \newcommand{\necess}{{\text{\wesa{certain}}}}
% \newcommand{\unknown}{{\text{\wesa{unknown}}}}
% \newcommand{\midd}{{\text{\wesa{middle}}}}
\newcommand{\imposs}{\ensuremath{\left[0,0\right]}}
\newcommand{\likely}{\ensuremath{\left[\tfrac{1}{2},1\right]}}
\newcommand{\unlikely}{\ensuremath{\left[0,\tfrac{1}{2}\right]}}
\newcommand{\necess}{\ensuremath{\left[1,1\right]}}
\newcommand{\unknown}{\ensuremath{\left[0,1\right]}}
\newcommand{\midd}{\ensuremath{\left[\tfrac{1}{4},\tfrac{3}{4}\right]}}
\newcommand{\fket}[1]{{|#1\rangle}}
\newcommand{\fproj}[1]{|#1\rangle\langle #1|}
\newcommand{\proj}[1]{\op{#1}{#1}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{L{#1}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{R{#1}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\rmd}{d}
\newcommand{\rmi}{i}
\lineskiplimit=1pt
\newcommand{\ultramodular}{\mathcal{M}}
\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{L{#1}}}}
\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{R{#1}}}}
\newcommand{\muB}{\ensuremath{\mu^{B}}}
\newcommand{\eventsC}{\ensuremath{\events_{C}}}

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}

\newcommand{\happen}{\text{H}}
\newcommand{\notHappen}{\text{N}}
\newcommand{\missing}{\text{M}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Response to the Referee Report of ``Quantum Interval-Valued Probability:
Contextuality and the Born Rule''}

\author{Yu-Tsung Tai}

\affiliation{Department of Mathematics, Indiana University, Bloomington, Indiana
47405, USA}

\affiliation{Department of Computer Science, Indiana University, Bloomington,
Indiana 47405, USA}

\author{Andrew J. Hanson}

\affiliation{Department of Informatics, Indiana University, Bloomington, Indiana
47405, USA}

\author{Gerardo Ortiz}

\affiliation{Department of Physics, Indiana University, Bloomington, Indiana 47405,
USA}

\author{Amr Sabry}

\affiliation{Department of Computer Science, Indiana University, Bloomington,
Indiana 47405, USA}

\date{\today}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Finite-precision Extension of the Kochen-Specker Theorem}

\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of
dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
$\delta<\frac{1}{3}$.\end{thm}

The proof is by contradiction: Suppose there is a $\delta$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\end{equation}
However, since we know that $0$-deterministic QIVPMs do not exist,
the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
is indeed a QIVPM by checking that for orthogonal projectors $P_{0}$
and~$P_{1}$, 
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
\end{equation}
because Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) implies
the convexity condition.

When one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
is $\necess$, say $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$
and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[1-\delta,1\right]$
and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1+\delta\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of $\left[0,1\right]$,
$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess$.

\begin{figure*}
\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
and $\left[1-\delta,1\right]$ are disjoint, $\bar{\mu}\left(P_{0}+P_{1}\right)$
is a subset of $\left[0,\delta\right]$.}
\end{figure*}
When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$
which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\delta\right]$
or $\left[1-\delta,1\right]$ and the latter is excluded as illustrated
in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\delta\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.

\section{Mermin-Peres ``Magic Square''}

In our response, we provide an example to show that if enough experimental
records are missing, there exists a probability measure consistent
with the experimental records. In this section, we want to provide
a similar example on the same nine observables $\mathbf{O}_{ij}$
with $i$ and $j$ ranging over $\{0,1,2\}$ from the Mermin-Peres
``magic square'' used to prove the Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:

{{\renewcommand{\arraystretch}{2}% 
\begin{center} 
\begin{tabular}{r|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|} 
$\mathbf{O}_{ij}$~ & $j=0$ & $j=1$ & $j=2$ \\ 
\hline  
$i=0~$ & $\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline 
\hline  
$i=1~$ & $\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline 
\hline  
$i=2~$ & $\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline 
\hline  
\end{tabular}\,.
\par\end{center} 
}

\noindent The observables are constructed using the Pauli matrices
$\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\} $ whose
eigenvalues are all either~$1$ or $-1$ \cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
They are arranged such that in each row and column, \emph{except the
column $j=2$}, every observable is the product of the other two,
so does the expectation value of every observable is the product of
the other two. In the $j=2$ column, we have instead that $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$
and $\expval{\mathbf{O}_{12}}\expval{\mathbf{O}_{22}}=-\expval{\mathbf{O}_{22}}$.

Assume we measure each observable twice. By the Kochen-Specker theorem,
the following measurement results is impossible because $\expval{\mathbf{O}_{12}}\expval{\mathbf{O}_{22}}=1\ne-1=-\expval{\mathbf{O}_{22}}$.
\begin{center}
\begin{tabular}{ccc}
\toprule 
\addlinespace
$\mathbf{O}_{ij}$  & Trial~0 & Trial~1\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbf{O}_{00}$ , $\mathbf{O}_{01}$, $\mathbf{O}_{10}$ , $\mathbf{O}_{11}$  & $-1$ & $-1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{02}$ , $\mathbf{O}_{12}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{21}$
, $\mathbf{O}_{22}$  & $1$ & $1$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

However, if half of the records are missing, i.e., $\delta=\frac{1}{2}$,
we might get the following measurement results, where $\missing$
stands for missing data.
\begin{center}
\begin{tabular}{cccc}
\toprule 
\addlinespace
$\mathbf{O}_{ij}$  & Trial~0 & Trial~1 & $\begin{aligned} & \textrm{Missing Record}\\
 & \textrm{Might Be}
\end{aligned}
$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$ & $\missing$ & $1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{01}$ , $\mathbf{O}_{10}$  & $\missing$ & $-1$ & $1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{02}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$  & $1$ & $\missing$ & $-1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{12}$ , $\mathbf{O}_{21}$  & $\missing$ & $1$ & $-1$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

Since the experimental results are missing, it might come form the
third column. In this kind of situation, the expectation values of
each observables is always $0$, and the product relations among these
the expectation values must be consistent with the the product relations
among observables.

We missed half of the experimental results when considering the Mermin-Peres
``magic square'' example, which is more than $\frac{1}{3}$ when
considering a three-dimensional Hilbert space. The reason is that
while there exists a $\frac{1}{3}$-deterministic QIVPMs in a three-dimensional
Hilbert space, we only know a $\frac{1}{2}$-deterministic QIVPMs,
but not any $\delta$-deterministic QIVPM for $\frac{1}{3}<\delta\le\frac{1}{2}$
in a four-dimensional Hilbert space.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{prop}
\end{document}

### 2018-02-06 prop_prop_letter_ajhs_referee_proof.tex
prop_prop_letter_ajhs_referee_proof.tex Remove non-proof parts...

@@
 
-\title{Response to the Referee Report of ``Quantum Interval-Valued Probability:
-Contextuality and the Born Rule''}
+\title{Proof of ``Finite-precision Extension of the Kochen-Specker Theorem''}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Finite-precision Extension of the Kochen-Specker Theorem}
 
@@
 
-\begin{figure*}
-\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
-and $\left[1-\delta,1\right]$ are disjoint, $\bar{\mu}\left(P_{0}+P_{1}\right)$
-is a subset of $\left[0,\delta\right]$.}
-\end{figure*}
 When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
@@
 or $\left[1-\delta,1\right]$ and the latter is excluded as illustrated
-in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
+in Fig.~1\ref{fig:Show-subset}, then $\bar{\mu}\left(P_{0}+P_{1}\right)$
 must be a subset of $\left[0,\delta\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
-
-\section{Mermin-Peres ``Magic Square''}
-
-In our response, we provide an example to show that if enough experimental
-records are missing, there exists a probability measure consistent
-with the experimental records. In this section, we want to provide
-a similar example on the same nine observables $\mathbf{O}_{ij}$
-with $i$ and $j$ ranging over $\{0,1,2\}$ from the Mermin-Peres
-``magic square'' used to prove the Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
-
-{{\renewcommand{\arraystretch}{2}% 
+\begin{widetext}
 \begin{center}
-\begin{tabular}{r|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|} 
-$\mathbf{O}_{ij}$~ & $j=0$ & $j=1$ & $j=2$ \\ 
-\hline  
-$i=0~$ & $\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline 
-\hline  
-$i=1~$ & $\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline 
-\hline  
-$i=2~$ & $\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline 
-\hline  
-\end{tabular}\,.
-\par\end{center} 
-}
-
-\noindent The observables are constructed using the Pauli matrices
-$\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\} $ whose
-eigenvalues are all either~$1$ or $-1$ \cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
-They are arranged such that in each row and column, \emph{except the
-column $j=2$}, every observable is the product of the other two,
-so does the expectation value of every observable is the product of
-the other two. In the $j=2$ column, we have instead that $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$
-and $\expval{\mathbf{O}_{12}}\expval{\mathbf{O}_{22}}=-\expval{\mathbf{O}_{22}}$.
-
-Assume we measure each observable twice. By the Kochen-Specker theorem,
-the following measurement results is impossible because $\expval{\mathbf{O}_{12}}\expval{\mathbf{O}_{22}}=1\ne-1=-\expval{\mathbf{O}_{22}}$.
-\begin{center}
-\begin{tabular}{ccc}
-\toprule 
-\addlinespace
-$\mathbf{O}_{ij}$  & Trial~0 & Trial~1\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbf{O}_{00}$ , $\mathbf{O}_{01}$, $\mathbf{O}_{10}$ , $\mathbf{O}_{11}$  & $-1$ & $-1$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbf{O}_{02}$ , $\mathbf{O}_{12}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{21}$
-, $\mathbf{O}_{22}$  & $1$ & $1$\tabularnewline
-\bottomrule
-\end{tabular}
+\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\\
+Figure 1.~\label{fig:Show-subset}Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
+and $\left[1-\delta,1\right]$ are disjoint, $\bar{\mu}\left(P_{0}+P_{1}\right)$
+is a subset of $\left[0,\delta\right]$.
 \par\end{center}
 
-However, if half of the records are missing, i.e., $\delta=\frac{1}{2}$,
-we might get the following measurement results, where $\missing$
-stands for missing data.
-\begin{center}
-\begin{tabular}{cccc}
-\toprule 
-\addlinespace
-$\mathbf{O}_{ij}$  & Trial~0 & Trial~1 & $\begin{aligned} & \textrm{Missing Record}\\
- & \textrm{Might Be}
-\end{aligned}
-$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$ & $\missing$ & $1$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbf{O}_{01}$ , $\mathbf{O}_{10}$  & $\missing$ & $-1$ & $1$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbf{O}_{02}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$  & $1$ & $\missing$ & $-1$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbf{O}_{12}$ , $\mathbf{O}_{21}$  & $\missing$ & $1$ & $-1$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
-
-Since the experimental results are missing, it might come form the
-third column. In this kind of situation, the expectation values of
-each observables is always $0$, and the product relations among these
-the expectation values must be consistent with the the product relations
-among observables.
-
-We missed half of the experimental results when considering the Mermin-Peres
-``magic square'' example, which is more than $\frac{1}{3}$ when
-considering a three-dimensional Hilbert space. The reason is that
-while there exists a $\frac{1}{3}$-deterministic QIVPMs in a three-dimensional
-Hilbert space, we only know a $\frac{1}{2}$-deterministic QIVPMs,
-but not any $\delta$-deterministic QIVPM for $\frac{1}{3}<\delta\le\frac{1}{2}$
-in a four-dimensional Hilbert space.
+\end{widetext}
 

### 2018-02-06 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Merged with reply.txt...

@@
 
-\section{Finite-precision Extension of the Kochen-Specker Theorem}
+In our QIVPM framework, the Kochen-Specker (KS) theorem is equivalent
+to stating that there does not exist a ($\delta=$)$0$-deterministic
+QIVPM. We further claim that there cannot exist any $\delta$-deterministic
+QIVPM for $\delta<\frac{1}{3}$ and that there exist QIVPMs for every
+$\delta\ge\frac{1}{3}$.
 
-\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
-\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of
-dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
-$\delta<\frac{1}{3}$.\end{thm}
+The referee questions the correctness of the theorem and the physical
+interpretation of $\delta$-determinism. In answer to the question
+of correctness we attach the complete proof of our theorem which we
+verified again. In the next paragraphs, we explain the physical interpretation
+of $\delta$-determinism and provide examples that illustrate why
+$\frac{1}{3}$ is special.
 
-The proof is by contradiction: Suppose there is a $\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
-QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
+We understand that the argument against $\delta$-determinism by the
+referee assumes that the parameter $\delta$ is \emph{exclusively}
+related to the density of points (states) defined in a general Hilbert
+space. This is indeed Meyer's great insight and main assumption in
+his proof about the field of rationals nullifying the KS theorem.
+In other words, Meyer attributes finite-precision errors to the description
+of the states. We, however, make no particular assumptions about the
+description of the states, and attribute finite-precision errors to
+the measurement process itself as realized in a laboratory. In our
+framework, the parameter $\delta$ reflects insufficient knowledge
+of the experimenter which could be due to a variety of reasons related
+to imperfections of devices. A typical question that an experimenter
+may not be able to answer accurately would be \char`\"{}did an electron
+land to the left or to the right of the screen\char`\"{}? There are
+cases in which the electron would land too close to the middle of
+the screen for the experimenter to be able to determine with certainty
+if that is closer to the left or the right. That imprecision might
+be modeled by limiting the description of the quantum states to rational
+points but we do not make this assumption. We simply record this imprecision
+in the probability we assign to events and use the axioms of probability
+theory (additivity, etc) to argue that a sharp transition occurs when
+the imprecisions reach a certain value.
+
+The following argument shows a concrete but simplified situation which
+explains the physical significance of the parameter $\delta$. We
+then follow this explanation by providing experimental results for
+a three-dimensional quantum system which cannot be described by any
+$\delta$-deterministic QIVPM for $\delta<\frac{1}{3}$ but can be
+described by a $\frac{1}{3}$-deterministic QIVPM.
+
+The meaning of $\delta$: To determine the probability of any event,
+we typically repeat an experiment $n$ times and count the number
+of times we witness the event. This assumes that for each run of the
+experiment we can determine, using our apparatuses, whether the event
+occurred or not. Assume an event has an ideal mathematical probability
+of $0$, and we repeat the experiment $100$ times. In a perfect world
+we should be able to refute the event $100$ times and calculate that
+the probability is $0$. We might also observe the event $2$ times
+and refute it $98$ times and therefore calculate the probability
+to be $0.02$. This situation still assumes perfect measurement conditions
+however. The question we focus on is what happens if we are only able
+to refute it $97$ times and are uncertain $3$ times? This is quite
+common in actual experiments. Mathematically we can model this idea
+by stating that the probability of the event is in the range $\left[0,0.03\right]$
+which says that the probability of the event could be $0$, $0.01$,
+$0.02$, or $0.03$ as each the three missing records could either
+be evidence for the event or against it. We just can't nail it down
+given the current experimental results and therefore use a $\delta=0.03$-deterministic
+probability measure. The interesting observation is that the axioms
+of probability theory (like additivity and convexity) impose enough
+constraints on the structure of probability measures that make them
+robust in the face of small $\delta$s.
+
+To see this in detail, consider a three-dimensional Hilbert space
+and an experiment repeated $12$ times. By the KS theorem, it is impossible
+to build a probability measure that maps every projection to either
+$0=\frac{0}{12}$ or $1=\frac{12}{12}$. Now consider what happens
+if $\frac{1}{4}$ of the data for every one-dimensional projector~$P$
+is missing yielding the following probability measure as a possible
+formalization:
+
 \begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
-\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\tfrac{1}{4}\right]\:;\\
-\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[\tfrac{3}{4},1\right]\:.
-\end{cases}
-\end{equation}
-However, since we know that $0$-deterministic QIVPMs do not exist,
-the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
-does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
-is indeed a QIVPM by checking that for orthogonal projectors $P_{0}$
-and~$P_{1}$, 
-\begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
-\end{equation}
-because similar to classical inclusion-exclusion principle, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal})
-implies for each pair of commuting projectors $P_{0}$ and~$P_{1}$,
-\begin{equation}
-\begin{aligned} & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}^{\textrm{D}}\left(P_{0}P_{1}\right)\\
-={} & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,
+\begin{aligned}\mu\left(\mathbb{0}\right) & =\imposs & \mu\left(\mathbb{1}\right) & =\necess\\
+\mu\left(P\right) & =\left[0,\tfrac{1}{4}\right] & \mu\left(\mathbb{1}-P\right) & =\left[\tfrac{3}{4},1\right]
 \end{aligned}
 \end{equation}
-i.e., $\bar{\mu}^{\textrm{D}}$ is convex.
+Indeed for every one-dimensional projector, the missing data could
+either refute or support the associated event. This measure does not
+satisfy the axioms of probability measures and cannot be extended
+to any valid QIVPM. In particular for any two one-dimensional events
+$P_{0}$ and $P_{1}$, we have $\mu\left(P_{0}\right)+\mu\left(P_{1}\right)=\left[0,\tfrac{1}{2}\right]$
+but $\mu\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$ because
+the latter is a two-dimensional event. This violates the condition
+that $\mu\left(P_{0}+P_{1}\right)$ is a subset of $\mu\left(P_{0}\right)+\mu\left(P_{1}\right)$.
 
-For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
-and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
-and 
+The situation changes sharply if the missing data reaches $\frac{1}{3}$,
+which gives the following probability measure as a possible formalization:
+
 \begin{equation}
-\begin{aligned} & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\\
-\subseteq{} & \left[1-\delta,1\right]+\left[0,\delta\right]=\left[1-\delta,1+\delta\right]\,.
+\begin{aligned}\mu\left(\mathbb{0}\right) & =\imposs & \mu\left(\mathbb{1}\right) & =\necess\\
+\mu\left(P\right) & =\left[0,\tfrac{1}{3}\right] & \mu\left(\mathbb{1}-P\right) & =\left[\tfrac{2}{3},1\right]
 \end{aligned}
 \end{equation}
-Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
-we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1\right]$,
-i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.
+This is not a valid probability measure for the same argument as above.
+However, it might be the case that the missing data for one-dimensional
+projectors always support the associated event while those for two-dimensional
+projectors always refute the event. In this case, the same experimental
+data is consistent with the following probability measure:
 
-\begin{figure*}
-\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Either $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]$
-or $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1\right]$.
-Together with the fact that $\bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset$,
-we have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]$.}
-\end{figure*}
-For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$
-which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
-Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\delta\right]$
-or $\left[1-\delta,1\right]$ and the latter is excluded as illustrated
-in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
-must be a subset of $\left[0,\delta\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
-
-\section{Mermin-Peres ``Magic Square''}
+\begin{equation}
+\begin{aligned}\mu\left(\mathbb{0}\right) & =\imposs & \mu\left(\mathbb{1}\right) & =\necess\\
+\mu\left(P\right) & =\left[\tfrac{1}{3},\tfrac{1}{3}\right] & \mu\left(\mathbb{1}-P\right) & =\left[\tfrac{2}{3},\tfrac{2}{3}\right]
+\end{aligned}
+\end{equation}
+which can be easily verified to be a valid QIVPM.
 
@@
 records are missing, there exists a probability measure consistent
-with the experimental records even if the presented experimental records
-are always the same. In this section, we want to provide a similar
-example on the Mermin-Peres ''Magic Square''. We consider a two
-spin-$\frac{1}{2}$ Hilbert space $\Hilb=\Hilb_{1}\otimes\Hilb_{2}$
-of dimension $d=4$. We use the same nine observables $\mathbf{O}_{ij}$
+with the experimental records. In this section, we want to provide
+a similar example on the same nine observables $\mathbf{O}_{ij}$
 with $i$ and $j$ ranging over $\{0,1,2\}$ from the Mermin-Peres
@@
 They are arranged such that in each row and column, \emph{except the
-column $j=2$}, every observable is the product of the other two.
-In the $j=2$ column, we have instead that $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+column $j=2$}, every observable is the product of the other two,
+so does the expectation value of every observable is the product of
+the other two. In the $j=2$ column, we have instead that $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$
+and $\expval{\mathbf{O}_{12}}\expval{\mathbf{O}_{22}}=-\expval{\mathbf{O}_{22}}$.
 
-Assume we measure these observables twice. By the Kochen-Specker theorem,
-the following measurement results is impossible because the number
-of expectation values in the $j=2$ column is odd.
+Assume we measure each observable twice. By the Kochen-Specker theorem,
+the following measurement results is impossible because $\expval{\mathbf{O}_{12}}\expval{\mathbf{O}_{22}}=1\ne-1=-\expval{\mathbf{O}_{22}}$.
 \begin{center}
@@
 third column. In this kind of situation, the expectation values of
-each observables are always $0$, and the product relations among
-these the expectation values must be consistent with the the product
-relations among observables.
+each observables is always $0$, and the product relations among these
+the expectation values must be consistent with the the product relations
+among observables.
 
-Notice that we need more experimental results when considering the
-Mermin-Peres ``magic square'' example. The reason is that in a four-dimensional
-Hilbert space, we know a $\frac{1}{2}$-deterministic QIVPMs, but
-we don't know whether there exists a $\delta$-deterministic QIVPM
-for $\frac{1}{3}<\delta\le\frac{1}{2}$.
+We missed half of the experimental results when considering the Mermin-Peres
+``magic square'' example, which is more than $\frac{1}{3}$ when
+considering a three-dimensional Hilbert space. The reason is that
+while there exists a $\frac{1}{3}$-deterministic QIVPMs in a three-dimensional
+Hilbert space, we only know a $\frac{1}{2}$-deterministic QIVPMs,
+but not any $\delta$-deterministic QIVPM for $\frac{1}{3}<\delta\le\frac{1}{2}$
+in a four-dimensional Hilbert space.
 

### 2018-02-06 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Fix a LaTeX error...
prop_prop_letter_ajhs_referee_response.tex Updating...

@@
 interpretation of $\delta$-determinism. In answer to the question
-of correctness we attach the complete proof of our theorem which we
-verified again. In the next paragraphs, we explain the physical interpretation
-of $\delta$-determinism and provide examples that illustrate why
-$\frac{1}{3}$ is special.
+of correctness, we attach the complete proof of our theorem which
+we verified again. In the next paragraphs, we explain the physical
+interpretation of $\delta$-determinism and provide examples that
+illustrate why $\frac{1}{3}$ is special.
 
@@
 to imperfections of devices. A typical question that an experimenter
-may not be able to answer accurately would be \char`\"{}did an electron
-land to the left or to the right of the screen\char`\"{}? There are
-cases in which the electron would land too close to the middle of
-the screen for the experimenter to be able to determine with certainty
-if that is closer to the left or the right. That imprecision might
-be modeled by limiting the description of the quantum states to rational
-points but we do not make this assumption. We simply record this imprecision
+may not be able to answer accurately would be ``did an electron land
+to the left or to the right of the screen''? There are cases in which
+the electron would land too close to the middle of the screen for
+the experimenter to be able to determine with certainty if that is
+closer to the left or the right. That imprecision might be modeled
+by limiting the description of the quantum states to rational points
+but we do not make this assumption. We simply record this imprecision
 in the probability we assign to events and use the axioms of probability
@@
 be evidence for the event or against it. We just can't nail it down
-given the current experimental results and therefore use a $\delta=0.03$-deterministic
+given the current experimental results and therefore use a ($\delta=$)$0.03$-deterministic
 probability measure. The interesting observation is that the axioms
@@
 \end{aligned}
+\,.
 \end{equation}
@@
 $P_{0}$ and $P_{1}$, we have $\mu\left(P_{0}\right)+\mu\left(P_{1}\right)=\left[0,\tfrac{1}{2}\right]$
-but $\mu\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$ because
+but $\mu\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$, because
 the latter is a two-dimensional event. This violates the condition
@@
 \end{aligned}
+\,,
 \end{equation}
@@
 
-In our response, we provide an example to show that if enough experimental
-records are missing, there exists a probability measure consistent
-with the experimental records. In this section, we want to provide
-a similar example on the same nine observables $\mathbf{O}_{ij}$
+Similar argument can be applied on the same nine observables $\mathbf{O}_{ij}$
 with $i$ and $j$ ranging over $\{0,1,2\}$ from the Mermin-Peres
-``magic square'' used to prove the Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
+``magic square'' used to prove the Kochen-Specker theorem \cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
 
-{{\renewcommand{\arraystretch}{2}% 
+{\renewcommand{\arraystretch}{2}% 
 \begin{center} 
@@
 column $j=2$}, every observable is the product of the other two,
-so does the expectation value of every observable is the product of
-the other two. In the $j=2$ column, we have instead that $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$
-and $\expval{\mathbf{O}_{12}}\expval{\mathbf{O}_{22}}=-\expval{\mathbf{O}_{22}}$.
+and the expectation value of every observable is the product of the
+other two as well. In the $j=2$ column, we have instead that $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$
+and 
+\begin{equation}
+\expval{\mathbf{O}_{02}}\expval{\mathbf{O}_{12}}=-\expval{\mathbf{O}_{22}}\,.\label{eq:j_2_expectation_value}
+\end{equation}
 
 Assume we measure each observable twice. By the Kochen-Specker theorem,
-the following measurement results is impossible because $\expval{\mathbf{O}_{12}}\expval{\mathbf{O}_{22}}=1\ne-1=-\expval{\mathbf{O}_{22}}$.
+it is impossible to get the following measurement results because
+the product of the expectation values in the $j=2$ column violate
+Eq.~(\ref{eq:j_2_expectation_value}).
 \begin{center}
@@
 
-However, if half of the records are missing, i.e., $\delta=\frac{1}{2}$,
-we might get the following measurement results, where $\missing$
-stands for missing data.
+Now consider what happens if if half of the records are missing, i.e.,
+$\delta=\frac{1}{2}$, which gives the following measurement results,
+where $\missing$ stands for missing data.
 \begin{center}
@@
 
-Since the experimental results are missing, it might come form the
+Since the experimental results are missing, they might come form the
 third column. In this kind of situation, the expectation values of
 each observables is always $0$, and the product relations among these
-the expectation values must be consistent with the the product relations
-among observables.
+expectation values must be consistent with the product relations among
+observables.
 

### 2018-02-07 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Updating...

@@
 $0.02$, or $0.03$ as each the three missing records could either
-be evidence for the event or against it. We just can't nail it down
+be evidence for the event or against it. We just cannot nail it down
 given the current experimental results and therefore use a ($\delta=$)$0.03$-deterministic
@@
 with $i$ and $j$ ranging over $\{0,1,2\}$ from the Mermin-Peres
-``magic square'' used to prove the Kochen-Specker theorem \cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
+``magic square'' used to prove the KS theorem \cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
 
@@
 They are arranged such that in each row and column, \emph{except the
-column $j=2$}, every observable is the product of the other two,
-and the expectation value of every observable is the product of the
-other two as well. In the $j=2$ column, we have instead that $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$
+column $j=2$}, every observable and its expectation value is the
+product of the other two. In the $j=2$ column, we have instead that
+$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$
 and 
@@
 
-Assume we measure each observable twice. By the Kochen-Specker theorem,
-it is impossible to get the following measurement results because
-the product of the expectation values in the $j=2$ column violate
-Eq.~(\ref{eq:j_2_expectation_value}).
+Assume we measure each observable twice. By the KS theorem, it is
+impossible to get the following measurement results because the product
+of the expectation values in the $j=2$ column violate Eq.~(\ref{eq:j_2_expectation_value}).
 \begin{center}
-\begin{tabular}{ccc}
+\begin{tabular}{cccc}
 \toprule 
 \addlinespace
-$\mathbf{O}_{ij}$  & Trial~0 & Trial~1\tabularnewline
+$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\expval{\mathbf{O}_{ij}}$\tabularnewline
 \midrule
@@
 \addlinespace
-$\mathbf{O}_{00}$ , $\mathbf{O}_{01}$, $\mathbf{O}_{10}$ , $\mathbf{O}_{11}$  & $-1$ & $-1$\tabularnewline
+$\mathbf{O}_{00}$ , $\mathbf{O}_{01}$, $\mathbf{O}_{10}$ , $\mathbf{O}_{11}$  & $-1$ & $-1$ & $-1$\tabularnewline
 \midrule 
@@
 $\mathbf{O}_{02}$ , $\mathbf{O}_{12}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{21}$
-, $\mathbf{O}_{22}$  & $1$ & $1$\tabularnewline
+, $\mathbf{O}_{22}$  & $1$ & $1$ & $1$\tabularnewline
 \bottomrule
@@
 \begin{center}
-\begin{tabular}{cccc}
+\begin{tabular}{ccccc}
 \toprule 
 \addlinespace
-$\mathbf{O}_{ij}$  & Trial~0 & Trial~1 & $\begin{aligned} & \textrm{Missing Record}\\
+$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
+ & \textrm{Record}\\
  & \textrm{Might Be}
+\end{aligned}
+$ & $\begin{aligned} & \textrm{Possible}\\
+ & \expval{\mathbf{O}_{ij}}
 \end{aligned}
@@
 \addlinespace
-$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$ & $\missing$ & $1$\tabularnewline
+$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$ & $\missing$ & $1$ & $0$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{01}$ , $\mathbf{O}_{10}$  & $\missing$ & $-1$ & $1$\tabularnewline
+$\mathbf{O}_{01}$ , $\mathbf{O}_{10}$  & $\missing$ & $-1$ & $1$ & $0$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{02}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$  & $1$ & $\missing$ & $-1$\tabularnewline
+$\mathbf{O}_{02}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$  & $1$ & $\missing$ & $-1$ & $0$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{12}$ , $\mathbf{O}_{21}$  & $\missing$ & $1$ & $-1$\tabularnewline
+$\mathbf{O}_{12}$ , $\mathbf{O}_{21}$  & $\missing$ & $1$ & $-1$ & $0$\tabularnewline
 \bottomrule
@@
 
-Since the experimental results are missing, they might come form the
-third column. In this kind of situation, the expectation values of
-each observables is always $0$, and the product relations among these
-expectation values must be consistent with the product relations among
-observables.
+\noindent Since the experimental results are missing, they might come
+form the third column. In this kind of situation, the expectation
+values of each observables is always $0$, and the product relations
+among these expectation values must be consistent with the product
+relations among observables.
 

### 2018-02-07 prop_prop_letter_ajhs_referee_response.tex
From: Tai, Yu-Tsung Sent: Wednesday, February 07, 2018 1:24 To: Sabry, Amr A. <sabry@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu> Subject: RE: reply draft (start)
Updated what you asked and some other small things…

Best regards,
Tai, Yu-Tsung (戴淯琮)
PhD Candidate double-majoring in Mathematics & Computer Science
Indiana University, Bloomington
https://www.linkedin.com/in/yu-tsung-tai-9aa30551

@@
 \newtheorem{condition}[assumption]{Condition}
+\setcounter{thm}{2}
 
@@
 
-The referee questions the correctness of the theorem and the physical
-interpretation of $\delta$-determinism. In answer to the question
-of correctness, we attach the complete proof of our theorem which
-we verified again. In the next paragraphs, we explain the physical
-interpretation of $\delta$-determinism and provide examples that
-illustrate why $\frac{1}{3}$ is special.
+The referee questions the correctness of Thm.~\ref{cor:Kochen-Specker-IVPM}
+and the physical interpretation of $\delta$-determinism. In answer
+to the question of correctness, we attach the complete proof of Thm.~\ref{cor:Kochen-Specker-IVPM}
+which we verified again in Appendix~\ref{sec:Proof-of-Theorem}.
+In the next paragraphs, we explain the physical interpretation of
+$\delta$-determinism and provide examples that illustrate why $\frac{1}{3}$
+is special.
 
@@
 to be $0.02$. This situation still assumes perfect measurement conditions
-however. The question we focus on is what happens if we are only able
-to refute it $97$ times and are uncertain $3$ times? This is quite
-common in actual experiments. Mathematically we can model this idea
-by stating that the probability of the event is in the range $\left[0,0.03\right]$
+however.
+
+Let the quantum system be in state~$\ket{\psi}$ and the probability
+of some event be $0$. Assume we repeat the experiment $100$ times
+and we observe the event $1$ time. The Godsil-Zaks-Meyer approach
+interprets this by assuming that the state was actually $\ket{\psi'}$
+which is infinitesimally close to $\ket{\psi}$ and proceed to reason
+about how coloring the states with rational points relates to the
+coloring of arbitrary states. We make no such assumptions and do not
+impose any constraints on the actual state of the system. In fact
+we do not make any statements about such situations. What we are addressing
+is a situation in which our devices do not allow to make a clear determination
+of whether an event has happened or not. We model this by an uncertainty
+in the probability of the event and then reason using the axioms of
+probability theory to bound this uncertainty.
+
+The question we focus on is what happens if we are only able to refute
+it $97$ times and are uncertain $3$ times? This is quite common
+in actual experiments. Mathematically we can model this idea by stating
+that the probability of the event is in the range $\left[0,0.03\right]$
 which says that the probability of the event could be $0$, $0.01$,
@@
 
-We missed half of the experimental results when considering the Mermin-Peres
-``magic square'' example, which is more than $\frac{1}{3}$ when
-considering a three-dimensional Hilbert space. The reason is that
-while there exists a $\frac{1}{3}$-deterministic QIVPMs in a three-dimensional
-Hilbert space, we only know a $\frac{1}{2}$-deterministic QIVPMs,
-but not any $\delta$-deterministic QIVPM for $\frac{1}{3}<\delta\le\frac{1}{2}$
-in a four-dimensional Hilbert space.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliography{prop}
+
+\appendix
+
+\section{\label{sec:Proof-of-Theorem}Proof of Theorem~\ref{cor:Kochen-Specker-IVPM}}
+
+\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
+\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of
+dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
+$\delta<\frac{1}{3}$.\end{thm}
+
+The proof is by contradiction: Suppose there is a $\delta$-deterministic
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
+QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
+\begin{equation}
+\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
+\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
+\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
+\end{cases}
+\end{equation}
+However, since we know that $0$-deterministic QIVPMs do not exist,
+the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
+does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
+is indeed a QIVPM by checking that for orthogonal projectors $P_{0}$
+and~$P_{1}$, 
+\begin{equation}
+\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
+\end{equation}
+because Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) implies
+the convexity condition.
+
+When one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
+is $\necess$, say $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$
+and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[1-\delta,1\right]$
+and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
+implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1+\delta\right]$.
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of $\left[0,1\right]$,
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
+which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess$.
+
+When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$
+which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\delta\right]$
+or $\left[1-\delta,1\right]$ and the latter is excluded as illustrated
+in Fig.~1, then $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset
+of $\left[0,\delta\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+\begin{widetext}
+\begin{center}
+\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\\
+Figure 1.~\label{fig:Show-subset}Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
+and $\left[1-\delta,1\right]$ are disjoint, $\bar{\mu}\left(P_{0}+P_{1}\right)$
+is a subset of $\left[0,\delta\right]$.
+\par\end{center}
+\end{widetext}
 \end{document}

### 2018-02-07 prop_prop_letter_ajhs_referee_response.tex
Updated some sentence from Gerardo...

@@
 to the question of correctness, we attach the complete proof of Thm.~\ref{cor:Kochen-Specker-IVPM}
-which we verified again in Appendix~\ref{sec:Proof-of-Theorem}.
-In the next paragraphs, we explain the physical interpretation of
-$\delta$-determinism and provide examples that illustrate why $\frac{1}{3}$
-is special.
+which we verified again in Appendix~\ref{sec:Proof-of-Theorem} for
+the referee's convenience. In the next paragraphs, we explain the
+physical interpretation of $\delta$-determinism and provide examples
+that illustrate why $\frac{1}{3}$ is special.
 
@@
 in the probability of the event and then reason using the axioms of
-probability theory to bound this uncertainty.
+probability theory to bound this uncertainty. We should add that our
+approach is agnostic about attributing elements of reality to the
+state function (as Meyer). We simply attribute lack of certainty to
+the measured results through the use of an instrument.
+
+The question we focus on is what happens if we are only able to refute
+it $97$ times and are uncertain $3$ times? This is quite common
+in actual experiments. Mathematically we can model this idea by stating
+that the probability of the event is in the range $\left[0,0.03\right]$
+which says that the probability of the event could be $0$, $0.01$,
+$0.02$, or $0.03$ as each the three missing records could either
+be evidence for the event or against it. We just cannot nail it down
+given the current experimental results and therefore use a ($\delta=$)$0.03$-deterministic
+probability measure. The interesting observation is that the axioms
+of probability theory (like additivity and convexity) impose enough
+constraints on the structure of probability measures that make them
+robust in the face of small $\delta$s.
 

### 2018-02-08 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Updating Andy's small comments...

@@
 
-\title{Response to the Referee Report of ``Quantum Interval-Valued Probability:
+\title{Response to the Referee Report for ``Quantum Interval-Valued Probability:
 Contextuality and the Born Rule''}
@@
 and the physical interpretation of $\delta$-determinism. In answer
-to the question of correctness, we attach the complete proof of Thm.~\ref{cor:Kochen-Specker-IVPM}
-which we verified again in Appendix~\ref{sec:Proof-of-Theorem} for
-the referee's convenience. In the next paragraphs, we explain the
-physical interpretation of $\delta$-determinism and provide examples
+to the question of correctness, we attach an expended complete proof
+of Thm.~\ref{cor:Kochen-Specker-IVPM} in Appendix~\ref{sec:Proof-of-Theorem}
+for the referee's convenience. In the next paragraphs, we explain
+the physical interpretation of $\delta$-determinism and provide examples
 that illustrate why $\frac{1}{3}$ is special.
 
-We understand that the argument against $\delta$-determinism by the
-referee assumes that the parameter $\delta$ is \emph{exclusively}
+To the best of our understanding, the argument against $\delta$-determinism
+by the referee assumes that the parameter $\delta$ is \emph{exclusively}
 related to the density of points (states) defined in a general Hilbert
-space. This is indeed Meyer's great insight and main assumption in
-his proof about the field of rationals nullifying the KS theorem.
+space. This is indeed Meyer's great insight and the main assumption
+in his proof that using the field of rationals nullifies the KS theorem.
 In other words, Meyer attributes finite-precision errors to the description
@@
 framework, the parameter $\delta$ reflects insufficient knowledge
-of the experimenter which could be due to a variety of reasons related
+of the experimenter, which could be due to a variety of reasons related
 to imperfections of devices. A typical question that an experimenter
 may not be able to answer accurately would be ``did an electron land
-to the left or to the right of the screen''? There are cases in which
-the electron would land too close to the middle of the screen for
-the experimenter to be able to determine with certainty if that is
-closer to the left or the right. That imprecision might be modeled
+in the left half or the right half of the screen''? There are cases
+in which the electron would land too close to the middle of the screen
+for the experimenter to be able to determine with certainty that it
+was left or right of the center. That imprecision might be modeled
 by limiting the description of the quantum states to rational points
 but we do not make this assumption. We simply record this imprecision
-in the probability we assign to events and use the axioms of probability
+in the probability we assign to events, and use the axioms of probability
 theory (additivity, etc) to argue that a sharp transition occurs when
-the imprecisions reach a certain value.
+the imprecision reaches a certain value.
 
-The following argument shows a concrete but simplified situation which
-explains the physical significance of the parameter $\delta$. We
-then follow this explanation by providing experimental results for
-a three-dimensional quantum system which cannot be described by any
-$\delta$-deterministic QIVPM for $\delta<\frac{1}{3}$ but can be
-described by a $\frac{1}{3}$-deterministic QIVPM.
+We next give an argument showing a concrete but simplified situation
+that explains the physical significance of the parameter $\delta$,
+followed by a description of the experimental results for a three-dimensional
+quantum system that cannot be described by any $\delta$-deterministic
+QIVPM for $\delta<\frac{1}{3}$, but \emph{can} be described by a
+$\frac{1}{3}$-deterministic QIVPM.
 
@@
 of times we witness the event. This assumes that for each run of the
-experiment we can determine, using our apparatuses, whether the event
+experiment we can determine, using our apparatus, whether the event
 occurred or not. Assume an event has an ideal mathematical probability
@@
 and refute it $98$ times and therefore calculate the probability
-to be $0.02$. This situation still assumes perfect measurement conditions
-however.
+to be $0.02$. Note that this situation assumes perfect measurement
+conditions.
 
@@
 The question we focus on is what happens if we are only able to refute
-it $97$ times and are uncertain $3$ times? This is quite common
-in actual experiments. Mathematically we can model this idea by stating
-that the probability of the event is in the range $\left[0,0.03\right]$
+it $97$ times and are \emph{uncertain} $3$ times? This is quite
+common in actual experiments. Mathematically we can model this idea
+by stating that the probability of the event is in the range $\left[0,0.03\right]$
 which says that the probability of the event could be $0$, $0.01$,
@@
 of probability theory (like additivity and convexity) impose enough
-constraints on the structure of probability measures that make them
-robust in the face of small $\delta$s.
-
-The question we focus on is what happens if we are only able to refute
-it $97$ times and are uncertain $3$ times? This is quite common
-in actual experiments. Mathematically we can model this idea by stating
-that the probability of the event is in the range $\left[0,0.03\right]$
-which says that the probability of the event could be $0$, $0.01$,
-$0.02$, or $0.03$ as each the three missing records could either
-be evidence for the event or against it. We just cannot nail it down
-given the current experimental results and therefore use a ($\delta=$)$0.03$-deterministic
-probability measure. The interesting observation is that the axioms
-of probability theory (like additivity and convexity) impose enough
-constraints on the structure of probability measures that make them
-robust in the face of small $\delta$s.
+constraints on the structure of probability measures to make them
+robust in the face of small $\delta$'s.
 
@@
 if $\frac{1}{4}$ of the data for every one-dimensional projector~$P$
-is missing yielding the following probability measure as a possible
+is missing, yielding the following probability measure as a possible
 formalization:
@@
 \end{equation}
-This is not a valid probability measure for the same argument as above.
+This is not a valid probability measure by the same argument as above.
 However, it might be the case that the missing data for one-dimensional
-projectors always support the associated event while those for two-dimensional
+projectors always support the associated event, while those for two-dimensional
 projectors always refute the event. In this case, the same experimental
@@
 
-Similar argument can be applied on the same nine observables $\mathbf{O}_{ij}$
-with $i$ and $j$ ranging over $\{0,1,2\}$ from the Mermin-Peres
-``magic square'' used to prove the KS theorem \cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
+Similar argument can be applied to the same nine observables $\mathbf{O}_{ij}$
+with $i$ and $j$ ranging over $\{0,1,2\}$, corresponding to the
+Mermin-Peres ``magic square'' used to prove the KS theorem \cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
 
@@
 impossible to get the following measurement results because the product
-of the expectation values in the $j=2$ column violate Eq.~(\ref{eq:j_2_expectation_value}).
+of the expectation values in the $j=2$ column violates Eq.~(\ref{eq:j_2_expectation_value}).
 \begin{center}
@@
 
-Now consider what happens if if half of the records are missing, i.e.,
+Now consider what happens if half of the records are missing, i.e.,
 $\delta=\frac{1}{2}$, which gives the following measurement results,
@@
 \noindent Since the experimental results are missing, they might come
-form the third column. In this kind of situation, the expectation
-values of each observables is always $0$, and the product relations
-among these expectation values must be consistent with the product
-relations among observables.
+form the third column. In this situation, the expectation values of
+each observables is always $0$, and the product relations among these
+expectation values must be consistent with the product relations among
+observables.
 
@@
 which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
-Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\delta\right]$
-or $\left[1-\delta,1\right]$ and the latter is excluded as illustrated
-in Fig.~1, then $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset
-of $\left[0,\delta\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
-\begin{widetext}
+As illustrated in the following figure, because of $\delta<\frac{1}{3}$,
+$\left[0,2\delta\right]$ and $\left[1-\delta,1\right]$ are disjoint,
+which implies $\bar{\mu}\left(P_{0}+P_{1}\right)$ and $\left[1-\delta,1\right]$
+are disjoint.
 \begin{center}
-\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\\
-Figure 1.~\label{fig:Show-subset}Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
-and $\left[1-\delta,1\right]$ are disjoint, $\bar{\mu}\left(P_{0}+P_{1}\right)$
-is a subset of $\left[0,\delta\right]$.
+\includegraphics[scale=0.5]{prop_prop_letter_ajhs_referee_response_nb}
 \par\end{center}
-\end{widetext}
+
+\noindent Together with the fact that $\bar{\mu}\left(P_{0}+P_{1}\right)$
+is a subset of either $\left[0,\delta\right]$ or $\left[1-\delta,1\right]$,
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[0,\delta\right]$,
+which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
 \end{document}

### 2018-02-08 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Completely rewrite the example Andy complained...

@@
 $0=\frac{0}{12}$ or $1=\frac{12}{12}$. Now consider what happens
-if $\frac{1}{4}$ of the data for every one-dimensional projector~$P$
-is missing, yielding the following probability measure as a possible
-formalization:
+if $\frac{1}{4}$ of the data for every one-dimensional projector
+is missing. This yields the following probability measure~$\bar{\mu}$
+as a possible formalization, where the column labeled by $P$ lists
+projectors, and the column labeled by $\bar{\mu}\left(P\right)$ lists
+the probability of these projectors.
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors & $\left[0,\tfrac{1}{4}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors & $\left[\tfrac{3}{4},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
 
-\begin{equation}
-\begin{aligned}\mu\left(\mathbb{0}\right) & =\imposs & \mu\left(\mathbb{1}\right) & =\necess\\
-\mu\left(P\right) & =\left[0,\tfrac{1}{4}\right] & \mu\left(\mathbb{1}-P\right) & =\left[\tfrac{3}{4},1\right]
-\end{aligned}
-\,.
-\end{equation}
-Indeed for every one-dimensional projector, the missing data could
-either refute or support the associated event. This measure does not
-satisfy the axioms of probability measures and cannot be extended
-to any valid QIVPM. In particular for any two one-dimensional events
-$P_{0}$ and $P_{1}$, we have $\mu\left(P_{0}\right)+\mu\left(P_{1}\right)=\left[0,\tfrac{1}{2}\right]$
-but $\mu\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$, because
-the latter is a two-dimensional event. This violates the condition
-that $\mu\left(P_{0}+P_{1}\right)$ is a subset of $\mu\left(P_{0}\right)+\mu\left(P_{1}\right)$.
+\noindent Indeed for every one-dimensional projector, the missing
+data could either refute or support the associated event. This measure
+cannot be extended to any valid QIVPM because it does not satisfy
+the convexity condition: for any two orthogonal one-dimensional events
+$P_{0}$ and $P_{1}$, the convexity condition requires$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
+However, in this example, $\bar{\mu}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
+which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
 

### 2018-02-09 prop_prop_letter_ajhs_referee_response.tex
prop_prop_letter_ajhs_referee_response.tex Updating until Gerardo called me...

@@
 the convexity condition: for any two orthogonal one-dimensional events
-$P_{0}$ and $P_{1}$, the convexity condition requires$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
-However, in this example, $\bar{\mu}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
-which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
+$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
+but $\bar{\mu}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
+which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+in this example.
 
@@
 which gives the following probability measure as a possible formalization:
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors & $\left[0,\tfrac{1}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors & $\left[\tfrac{2}{3},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
 
-\begin{equation}
-\begin{aligned}\mu\left(\mathbb{0}\right) & =\imposs & \mu\left(\mathbb{1}\right) & =\necess\\
-\mu\left(P\right) & =\left[0,\tfrac{1}{3}\right] & \mu\left(\mathbb{1}-P\right) & =\left[\tfrac{2}{3},1\right]
-\end{aligned}
-\,.
-\end{equation}
-This is not a valid probability measure by the same argument as above.
-However, it might be the case that the missing data for one-dimensional
-projectors always support the associated event, while those for two-dimensional
-projectors always refute the event. In this case, the same experimental
-data is consistent with the following probability measure:
+\noindent This is not a valid probability measure by the same argument
+as above. However, it might be the case that the missing data for
+one-dimensional projectors always support the associated event, while
+those for two-dimensional projectors always refute the event. In this
+case, the same experimental data is consistent with the following
+probability measure:
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
 
-\begin{equation}
-\begin{aligned}\mu\left(\mathbb{0}\right) & =\imposs & \mu\left(\mathbb{1}\right) & =\necess\\
-\mu\left(P\right) & =\left[\tfrac{1}{3},\tfrac{1}{3}\right] & \mu\left(\mathbb{1}-P\right) & =\left[\tfrac{2}{3},\tfrac{2}{3}\right]
-\end{aligned}
-\,,
-\end{equation}
-which can be easily verified to be a valid QIVPM.
+\noindent which can verified to be a valid QIVPM.
 
-Similar argument can be applied to the same nine observables $\mathbf{O}_{ij}$
+The similar situation happens when more than $\frac{1}{3}$ of data
+is missing. In particular, half of the data missing gives the following
+probability measure as a possible formalization:
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors & $\left[\tfrac{1}{2},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
+
+\noindent In this case, the probability measure itself is a QIVPM.
+
+By progressively degrading the certainty of the measured data, we
+can show using a Mermin square like argument a transition occurs from
+contextuality to a situation that we cannot determine the contextuality
+of a system. Consider the same nine observables $\mathbf{O}_{ij}$
 with $i$ and $j$ ranging over $\{0,1,2\}$, corresponding to the
@@
 \addlinespace
-$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\expval{\mathbf{O}_{ij}}$\tabularnewline
+$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Possible}\\
+ & \expval{\mathbf{O}_{ij}}
+\end{aligned}
+$\tabularnewline
 \midrule
@@
 \addlinespace
-$\mathbf{O}_{00}$ , $\mathbf{O}_{01}$, $\mathbf{O}_{10}$ , $\mathbf{O}_{11}$  & $-1$ & $-1$ & $-1$\tabularnewline
+$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$ & $-1$ & $-1$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{02}$ , $\mathbf{O}_{12}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{21}$
-, $\mathbf{O}_{22}$  & $1$ & $1$ & $1$\tabularnewline
+$\mathbf{O}_{01}$ , $\mathbf{O}_{10}$  & $-1$ & $-1$ & $-1$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbf{O}_{02}$ , $\mathbf{O}_{12}$ & $1$ & $1$ & $1$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbf{O}_{20}$ , $\mathbf{O}_{22}$ , $\mathbf{O}_{21}$  & $1$ & $1$ & $1$\tabularnewline
 \bottomrule
@@
 \addlinespace
-$\mathbf{O}_{02}$ , $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$  & $1$ & $\missing$ & $-1$ & $0$\tabularnewline
+$\mathbf{O}_{02}$ , $\mathbf{O}_{12}$ & $1$ & $\missing$ & $-1$ & $0$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{12}$ , $\mathbf{O}_{21}$  & $\missing$ & $1$ & $-1$ & $0$\tabularnewline
+$\mathbf{O}_{20}$ , $\mathbf{O}_{22}$ , $\mathbf{O}_{21}$  & $\missing$ & $1$ & $-1$ & $0$\tabularnewline
 \bottomrule
@@
 \noindent Since the experimental results are missing, they might come
-form the third column. In this situation, the expectation values of
+from the third column. In this situation, the expectation values of
 each observables is always $0$, and the product relations among these
 expectation values must be consistent with the product relations among
-observables.
+observables. Here missing half of the data might not be the
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{plain}
 \bibliography{prop}

### 2018-02-09 prop_prop_letter_ajhs_referee_response.tex
From: Ortiz, Gerardo Sent: Friday, February 09, 2018 9:46 To: Tai, Yu-Tsung <yuttai@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: Re: cabello
I have already changed (attached) the very beginning of the response. It reads
better in my modest opinion.

    Best,

      Gerardo

@@
 to stating that there does not exist a ($\delta=$)$0$-deterministic
-QIVPM. We further claim that there cannot exist any $\delta$-deterministic
+QIVPM. We further claim (Thm.~\ref{cor:Kochen-Specker-IVPM}) that there cannot exist any $\delta$-deterministic
 QIVPM for $\delta<\frac{1}{3}$ and that there exist QIVPMs for every
 $\delta\ge\frac{1}{3}$.
-
 The referee questions the correctness of Thm.~\ref{cor:Kochen-Specker-IVPM}
@@
 for the experimenter to be able to determine with certainty that it
-was left or right of the center. That imprecision might be modeled
-by limiting the description of the quantum states to rational points
-but we do not make this assumption. We simply record this imprecision
+was left or right of the center. We simply record this imprecision
 in the probability we assign to events, and use the axioms of probability
 theory (additivity, etc) to argue that a sharp transition occurs when
-the imprecision reaches a certain value.
+the imprecision reaches a certain value. Our
+approach is agnostic about attributing elements of reality to the
+state function (as Meyer). We simply attribute lack of certainty to
+the measured results through the use of an instrument.
 
-We next give an argument showing a concrete but simplified situation
-that explains the physical significance of the parameter $\delta$,
-followed by a description of the experimental results for a three-dimensional
-quantum system that cannot be described by any $\delta$-deterministic
-QIVPM for $\delta<\frac{1}{3}$, but \emph{can} be described by a
-$\frac{1}{3}$-deterministic QIVPM.
-
-The meaning of $\delta$: To determine the probability of any event,
+To determine the probability of any event,
 we typically repeat an experiment $n$ times and count the number
@@
 conditions.
-
-Let the quantum system be in state~$\ket{\psi}$ and the probability
-of some event  be $0$. Assume we repeat the experiment $100$ times
-and we observe the event $1$ time. The Godsil-Zaks-Meyer approach
-interprets this by assuming that the state was actually $\ket{\psi'}$
-which is infinitesimally close to $\ket{\psi}$ and proceed to reason
-about how coloring the states with rational points relates to the
-coloring of arbitrary states. We make no such assumptions and do not
-impose any constraints on the actual state of the system. In fact
-we do not make any statements about such situations. What we are addressing
-is a situation in which our devices do not allow to make a clear determination
-of whether an event has happened or not. We model this by an uncertainty
-in the probability of the event and then reason using the axioms of
-probability theory to bound this uncertainty. We should add that our
-approach is agnostic about attributing elements of reality to the
-state function (as Meyer). We simply attribute lack of certainty to
-the measured results through the use of an instrument.
-
+%Let the quantum system be in state~$\ket{\psi}$ and the probability
+%of some event  be $0$. Assume we repeat the experiment $100$ times
+%and we observe the event $1$ time. The Godsil-Zaks-Meyer approach
+%interprets this by assuming that the state was actually $\ket{\psi'}$
+%which is infinitesimally close to $\ket{\psi}$ and proceed to reason
+%about how coloring the states with rational points relates to the
+%coloring of arbitrary states. We make no such assumptions and do not
+%impose any constraints on the actual state of the system. In fact
+%we do not make any statements about such situations. What we are addressing
+%is a situation in which our devices do not allow to make a clear determination
+%of whether an event has happened or not. We model this by an uncertainty
+%in the probability of the event and then reason using the axioms of
+%probability theory to bound this uncertainty. We should add that our
+%approach is agnostic about attributing elements of reality to the
+%state function (as Meyer). We simply attribute lack of certainty to
+%the measured results through the use of an instrument. 
 The question we focus on is what happens if we are only able to refute

### 2018-02-10 prop_letter_ajhs_referee_response.tex
Apparently ShareLaTeX hasn't merged renaming files...

--- 2018-02-09 prop_prop_letter_ajhs_referee_response.tex
@@
 \newcommand{\notHappen}{\text{N}}
-\newcommand{\missing}{\text{M}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\missing}{?}
+
 \begin{document}
 
-\title{Response to the Referee Report for ``Quantum Interval-Valued Probability:
-Contextuality and the Born Rule''}
-
-\author{Yu-Tsung Tai}
-
-\affiliation{Department of Mathematics, Indiana University, Bloomington, Indiana
-47405, USA}
-
-\affiliation{Department of Computer Science, Indiana University, Bloomington,
-Indiana 47405, USA}
-
-\author{Andrew J. Hanson}
-
-\affiliation{Department of Informatics, Indiana University, Bloomington, Indiana
-47405, USA}
-
-\author{Gerardo Ortiz}
-
-\affiliation{Department of Physics, Indiana University, Bloomington, Indiana 47405,
-USA}
-
-\author{Amr Sabry}
-
-\affiliation{Department of Computer Science, Indiana University, Bloomington,
-Indiana 47405, USA}
-
+\title{Response to the Referee Report for \\
+``Quantum Interval-Valued Probability: Contextuality and the Born Rule''}
 \date{\today}
@@
 \maketitle
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 to stating that there does not exist a ($\delta=$)$0$-deterministic
-QIVPM. We further claim (Thm.~\ref{cor:Kochen-Specker-IVPM}) that there cannot exist any $\delta$-deterministic
-QIVPM for $\delta<\frac{1}{3}$ and that there exist QIVPMs for every
-$\delta\ge\frac{1}{3}$.
-The referee questions the correctness of Thm.~\ref{cor:Kochen-Specker-IVPM}
-and the physical interpretation of $\delta$-determinism. In answer
-to the question of correctness, we attach an expended complete proof
-of Thm.~\ref{cor:Kochen-Specker-IVPM} in Appendix~\ref{sec:Proof-of-Theorem}
-for the referee's convenience. In the next paragraphs, we explain
-the physical interpretation of $\delta$-determinism and provide examples
-that illustrate why $\frac{1}{3}$ is special.
+QIVPM. We further claim (Thm.~\ref{cor:Kochen-Specker-IVPM}) that
+there cannot exist any $\delta$-deterministic QIVPM for
+$\delta<\frac{1}{3}$ and that there exist QIVPMs for every
+$\delta\ge\frac{1}{3}$.  The referee questions the correctness of
+Thm.~\ref{cor:Kochen-Specker-IVPM} and the physical interpretation of
+$\delta$-determinism. In answer to the question of correctness, we
+attach, for the referee's convenience, an expanded complete proof of
+Thm.~\ref{cor:Kochen-Specker-IVPM} at the end of this response. In the
+next paragraphs, we explain the physical interpretation of
+$\delta$-determinism and provide examples that illustrate why
+$\frac{1}{3}$ is special.
 
-To the best of our understanding, the argument against $\delta$-determinism
-by the referee assumes that the parameter $\delta$ is \emph{exclusively}
-related to the density of points (states) defined in a general Hilbert
-space. This is indeed Meyer's great insight and the main assumption
-in his proof that using the field of rationals nullifies the KS theorem.
-In other words, Meyer attributes finite-precision errors to the description
-of the states. We, however, make no particular assumptions about the
-description of the states, and attribute finite-precision errors to
-the measurement process itself as realized in a laboratory. In our
-framework, the parameter $\delta$ reflects insufficient knowledge
-of the experimenter, which could be due to a variety of reasons related
-to imperfections of devices. A typical question that an experimenter
-may not be able to answer accurately would be ``did an electron land
-in the left half or the right half of the screen''? There are cases
-in which the electron would land too close to the middle of the screen
-for the experimenter to be able to determine with certainty that it
-was left or right of the center. We simply record this imprecision
-in the probability we assign to events, and use the axioms of probability
-theory (additivity, etc) to argue that a sharp transition occurs when
-the imprecision reaches a certain value. Our
-approach is agnostic about attributing elements of reality to the
-state function (as Meyer). We simply attribute lack of certainty to
-the measured results through the use of an instrument.
+\bigskip
+
+\paragraph*{Experimental Data and $\delta$-determinism.} To the best of
+our understanding, the argument against $\delta$-determinism by the
+referee assumes that the parameter $\delta$ is \emph{exclusively}
+related to the density of states defined in a general Hilbert
+space. This is indeed Meyer's great insight and the main assumption in
+his proof that using the field of rationals nullifies the KS theorem.
+In other words, Meyer attributes finite-precision errors to the
+description of the states, which is an idea that has been challenged
+by several researchers, including Ax and Kochen (as cited by Cabello
+2002), who argue that the effect of finite-precision measurements on
+the KS theorem requires a different formalization. Our paper, indeed,
+makes no particular assumptions about the description of the states,
+and attributes finite-precision errors to the measurement process
+itself as realized in a laboratory. In our framework, the parameter
+$\delta$ reflects insufficient knowledge of the experimenter, which
+could be due to a variety of reasons related to imperfections of
+devices. A typical question that an experimenter may not be able to
+answer accurately would be ``did an electron land in the left half or
+the right half of the screen''? There are cases in which the electron
+would land too close to the middle of the screen for the experimenter
+to be able to determine with certainty that it was left or right of
+the center. We simply record this imprecision in the probability we
+assign to events, and use the axioms of probability theory
+(additivity, convexity, etc) to argue that a sharp transition occurs
+when the imprecision reaches a certain value. Our approach is agnostic
+about attributing elements of reality to the state function (as
+Meyer). We simply attribute lack of certainty to the measured results
+through the use of an instrument.
 
@@
 
-To see this in detail, consider a three-dimensional Hilbert space
-and an experiment repeated $12$ times. By the KS theorem, it is impossible
+To see this in detail, consider a three-dimensional Hilbert space and
+an experiment repeated $12$ times. By the KS theorem, it is impossible
 to build a probability measure that maps every projection to either
-$0=\frac{0}{12}$ or $1=\frac{12}{12}$. Now consider what happens
-if $\frac{1}{4}$ of the data for every one-dimensional projector
-is missing. This yields the following probability measure~$\bar{\mu}$
-as a possible formalization, where the column labeled by $P$ lists
-projectors, and the column labeled by $\bar{\mu}\left(P\right)$ lists
-the probability of these projectors.
+$0=\frac{0}{12}$ or $1=\frac{12}{12}$. Now consider what happens if
+$\frac{1}{4}$ of the data for every one-dimensional projector is
+missing. A potential account of this degradation is to assign to each
+event $P$ the entire range of possibilities $\bar{\mu}(P)$:
 \begin{center}
@@
 
-\noindent Indeed for every one-dimensional projector, the missing
-data could either refute or support the associated event. This measure
-cannot be extended to any valid QIVPM because it does not satisfy
-the convexity condition: for any two orthogonal one-dimensional events
-$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
+\noindent This measure is not a valid QIVPM because it does not
+satisfy the convexity condition: for any two orthogonal
+one-dimensional events $P_{0}$ and $P_{1}$, the convexity condition
+requires
+$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
 but $\bar{\mu}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
-which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
-in this example.
+which is not a subset of
+$\left[0,\tfrac{1}{2}\right]=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$. Interestingly,
+it is impossible to find any probability measure that would be
+consistent with these observations as the interval
+$\left[\tfrac{3}{4},1\right]$ is completely disjoint from the interval
+$\left[0,\tfrac{1}{2}\right]$ and no amount of shifting of assumptions
+regarding the precise outcome of the missing observations could change
+that disjointness. However, a sharp transition occurs when
+$\delta=\tfrac{1}{3}$ as shown next.
 
-The situation changes sharply if the missing data reaches $\frac{1}{3}$,
-which gives the following probability measure as a possible formalization:
+%% Indeed for every one-dimensional projector, the missing
+%% data could either refute or support the associated event. 
+%% This yields the following probability measure~$\bar{\mu}$
+%% as a possible formalization, where the column labeled by $P$ lists
+%% projectors, and the column labeled by $\bar{\mu}\left(P\right)$ lists
+%% the probability of these projectors.
+
+In case the missing data reaches $\frac{1}{3}$, the probability
+measure that assigns to each event the entire range of possibilities
+is:
 \begin{center}
@@
 
-\noindent This is not a valid probability measure by the same argument
-as above. However, it might be the case that the missing data for
+\noindent This is also not a valid probability measure by the same
+argument as above. However, in this case
+$\bar{\mu}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$ and
+$\left[0,\tfrac{2}{3}\right]=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+have a common point. And hence by assuming that the missing data for
 one-dimensional projectors always support the associated event, while
-those for two-dimensional projectors always refute the event. In this
-case, the same experimental data is consistent with the following
-probability measure:
+those for two-dimensional projectors always refute the event, we can
+find the following probability measure which can verified to be a
+valid QIVPM and which is consistent with the experimental data:
 \begin{center}
@@
 
-\noindent which can verified to be a valid QIVPM.
+A similar situation happens when more than $\frac{1}{3}$ of data is
+missing. In particular, having half of the data missing, the
+probability measure that assigns to each event the entire range of
+possibilities is already a QIVPM:
 
-The similar situation happens when more than $\frac{1}{3}$ of data
-is missing. In particular, half of the data missing gives the following
-probability measure as a possible formalization:
 \begin{center}
@@
 
-\noindent In this case, the probability measure itself is a QIVPM.
+The above arguments could be summarized and illustrated using the following figure: 
+\begin{center}
+\includegraphics[scale=0.5]{prop_prop_letter_ajhs_referee_response_nb}
+\par\end{center}
 
-By progressively degrading the certainty of the measured data, we
-can show using a Mermin square like argument a transition occurs from
-contextuality to a situation that we cannot determine the contextuality
-of a system. Consider the same nine observables $\mathbf{O}_{ij}$
-with $i$ and $j$ ranging over $\{0,1,2\}$, corresponding to the
-Mermin-Peres ``magic square'' used to prove the KS theorem \cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
+\noindent The region to the left of the vertical line at
+$\delta=\frac{1}{3}$ is where we assume small measurement degradation;
+in that region our extension of the KS theorem definitely demonstrates
+contextuality. In the region to the right, the degradation of the data
+is large and our extension of the KS theorem no longer refutes other
+explanations for the experimental data.
+
+\bigskip
+
+\paragraph*{Mermin-Peres ``Magic Square''.} We now use this same idea
+to analyze the Mermin-Peres ``magic square'' argument. We show that
+when the measurements are infinitely precise, the Mermin-Peres ``magic
+square'' argument definitely demonstrates contextuality. But as we
+progressively degrade the certainty of the data, a transition happens
+in which the Mermin-Peres ``magic square'' argument no longer
+demonstrates contextuality. Consider the nine observables
+$\mathbf{O}_{ij}$ with $i$ and $j$ ranging over $\{0,1,2\}$,
+corresponding to the Mermin-Peres ``magic square'' used to prove the
+KS theorem:
 
@@
 $\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\} $ whose
-eigenvalues are all either~$1$ or $-1$ \cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
+eigenvalues are all either~$1$ or $-1$.
 They are arranged such that in each row and column, \emph{except the
@@
 each observables is always $0$, and the product relations among these
-expectation values must be consistent with the product relations among
-observables. Here missing half of the data might not be the
+expectation values is consistent with the product relations among
+observables.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{plain}
-\bibliography{prop}
+\bigskip
 
-\appendix
-
-\section{\label{sec:Proof-of-Theorem}Proof of Theorem~\ref{cor:Kochen-Specker-IVPM}}
+\paragraph*{Expanded Proof of Thm.~3.}
 
@@
 
-When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$
-which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
-As illustrated in the following figure, because of $\delta<\frac{1}{3}$,
-$\left[0,2\delta\right]$ and $\left[1-\delta,1\right]$ are disjoint,
-which implies $\bar{\mu}\left(P_{0}+P_{1}\right)$ and $\left[1-\delta,1\right]$
-are disjoint.
-\begin{center}
-\includegraphics[scale=0.5]{prop_prop_letter_ajhs_referee_response_nb}
-\par\end{center}
-
-\noindent Together with the fact that $\bar{\mu}\left(P_{0}+P_{1}\right)$
-is a subset of either $\left[0,\delta\right]$ or $\left[1-\delta,1\right]$,
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[0,\delta\right]$,
-which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+When
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+we have both $\bar{\mu}\left(P_{0}\right)$ and
+$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
+implies
+$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
+Since $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
+$\left[1-\delta,1\right]$ are disjoint, which implies
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ and $\left[1-\delta,1\right]$ are
+disjoint. Together with the fact that
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either
+$\left[0,\delta\right]$ or $\left[1-\delta,1\right]$,
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
+$\left[0,\delta\right]$, which implies
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
 \end{document}

### 2018-02-10 prop_letter_ajhs_referee_response.tex
Fix a rename problem...
Updated from Gerardo...

@@
 In our QIVPM framework, the Kochen-Specker (KS) theorem is equivalent
-to stating that there does not exist a ($\delta=$)$0$-deterministic
+to stating that there does not exist a ($\delta$=)$0$-deterministic
 QIVPM. We further claim (Thm.~\ref{cor:Kochen-Specker-IVPM}) that
@@
 
-\bigskip
+%\bigskip
 
@@
 \begin{center}
-\includegraphics[scale=0.5]{prop_prop_letter_ajhs_referee_response_nb}
+\includegraphics[scale=0.5]{prop_letter_ajhs_referee_response_nb}
 \par\end{center}
@@
 $\mathbf{O}_{ij}$ with $i$ and $j$ ranging over $\{0,1,2\}$,
-corresponding to the Mermin-Peres ``magic square'' used to prove the
+corresponding to the Mermin-Peres ``magic square'' used to illustrate the
 KS theorem:

### 2018-02-11 prop_letter_ajhs_referee_response.tex
prop_letter_ajhs_referee_response.tex \paragraph*{Experimental Data and $\delta$-determinism.} Updating...
prop_letter_ajhs_referee_response.tex \paragraph*{Mermin-Peres ``Magic Square''.} Updating...

@@
 be evidence for the event or against it. We just cannot nail it down
-given the current experimental results and therefore use a ($\delta=$)$0.03$-deterministic
+given the current experimental results and therefore represent them as a ($\delta=$)$0.03$-deterministic
 probability measure. The interesting observation is that the axioms
@@
 
-To see this in detail, consider a three-dimensional Hilbert space and
-an experiment repeated $12$ times. By the KS theorem, it is impossible
+To see this in detail, consider a three-dimensional Hilbert space
+and an experiment repeated $12$ times. By the KS theorem, it is impossible
 to build a probability measure that maps every projection to either
-$0=\frac{0}{12}$ or $1=\frac{12}{12}$. Now consider what happens if
-$\frac{1}{4}$ of the data for every one-dimensional projector is
-missing. A potential account of this degradation is to assign to each
-event $P$ the entire range of possibilities $\bar{\mu}(P)$:
+$0=\frac{0}{12}$ or $1=\frac{12}{12}$. Now consider what happens
+if $\frac{1}{4}$ of the data for every one-dimensional projector
+is missing. A potential account of this degradation is to assign to
+each event $P$ the entire range of possibilities $\bar{\mu}_{0}(P)$: 
 \begin{center}
@@
 \addlinespace
-$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+$P$  & $\bar{\mu}_{0}\left(P\right)$\tabularnewline
 \midrule
@@
 
-\noindent This measure is not a valid QIVPM because it does not
-satisfy the convexity condition: for any two orthogonal
-one-dimensional events $P_{0}$ and $P_{1}$, the convexity condition
-requires
-$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
-but $\bar{\mu}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
-which is not a subset of
-$\left[0,\tfrac{1}{2}\right]=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$. Interestingly,
-it is impossible to find any probability measure that would be
-consistent with these observations as the interval
-$\left[\tfrac{3}{4},1\right]$ is completely disjoint from the interval
-$\left[0,\tfrac{1}{2}\right]$ and no amount of shifting of assumptions
-regarding the precise outcome of the missing observations could change
-that disjointness. However, a sharp transition occurs when
-$\delta=\tfrac{1}{3}$ as shown next.
+\noindent This measure is not a valid QIVPM because it does not satisfy
+the convexity condition: for any two orthogonal one-dimensional events
+$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}_{0}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}_{0}\left(P_{0}\right)+\bar{\mu}_{0}\left(P_{1}\right)$,
+but $\bar{\mu}_{0}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
+which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}_{0}\left(P_{0}\right)+\bar{\mu}_{0}\left(P_{1}\right)$.
+Interestingly, it is impossible to find any probability measure that
+would be consistent with these observations as the interval $\left[\tfrac{3}{4},1\right]$
+is completely disjoint from the interval $\left[0,\tfrac{1}{2}\right]$
+and no amount of shifting of assumptions regarding the precise outcome
+of the missing observations could change that disjointness. However,
+a sharp transition occurs when $\delta=\tfrac{1}{3}$ as shown next.
 
@@
 
-In case the missing data reaches $\frac{1}{3}$, the probability
-measure that assigns to each event the entire range of possibilities
-is:
+In case the missing data reaches $\frac{1}{3}$, the probability measure
+that assigns to each event the entire range of possibilities is: 
 \begin{center}
@@
 \addlinespace
-$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+$P$  & $\bar{\mu}_{1}\left(P\right)$\tabularnewline
 \midrule
@@
 \noindent This is also not a valid probability measure by the same
-argument as above. However, in this case
-$\bar{\mu}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$ and
-$\left[0,\tfrac{2}{3}\right]=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
+argument as above. However, in this case $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
+and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$
 have a common point. And hence by assuming that the missing data for
@@
 \addlinespace
-$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+$P$  & $\bar{\mu}_{1}'\left(P\right)$\tabularnewline
 \midrule
@@
 
-A similar situation happens when more than $\frac{1}{3}$ of data is
-missing. In particular, having half of the data missing, the
-probability measure that assigns to each event the entire range of
-possibilities is already a QIVPM:
-
+A similar situation happens when more than $\frac{1}{3}$ of data
+is missing. In particular, having half of the data missing, the probability
+measure that assigns to each event the entire range of possibilities
+is already a QIVPM:
 \begin{center}
@@
 \addlinespace
-$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+$P$  & $\bar{\mu}_{2}\left(P\right)$\tabularnewline
 \midrule
@@
 
-The above arguments could be summarized and illustrated using the following figure: 
+The above arguments could be summarized and illustrated using the
+following figure: 
 \begin{center}
@@
 
-\noindent The region to the left of the vertical line at
-$\delta=\frac{1}{3}$ is where we assume small measurement degradation;
-in that region our extension of the KS theorem definitely demonstrates
-contextuality. In the region to the right, the degradation of the data
-is large and our extension of the KS theorem no longer refutes other
-explanations for the experimental data.
+\noindent The region to the left of the vertical line at $\delta=\frac{1}{3}$
+is where we assume small measurement degradation; in that region our
+extension of the KS theorem definitely demonstrates contextuality.
+In the region to the right, the degradation of the data is large and
+our extension of the KS theorem no longer refutes other explanations
+for the experimental data.
 
-\bigskip
+\bigskip{}
 
-\paragraph*{Mermin-Peres ``Magic Square''.} We now use this same idea
-to analyze the Mermin-Peres ``magic square'' argument. We show that
-when the measurements are infinitely precise, the Mermin-Peres ``magic
-square'' argument definitely demonstrates contextuality. But as we
-progressively degrade the certainty of the data, a transition happens
-in which the Mermin-Peres ``magic square'' argument no longer
-demonstrates contextuality. Consider the nine observables
-$\mathbf{O}_{ij}$ with $i$ and $j$ ranging over $\{0,1,2\}$,
-corresponding to the Mermin-Peres ``magic square'' used to illustrate the
-KS theorem:
+\paragraph*{Mermin-Peres ``Magic Square''.}
+
+We now use this same idea to analyze the Mermin-Peres ``magic square''
+argument. We show that when the measurements are infinitely precise,
+the Mermin-Peres ``magic square'' argument definitely demonstrates
+contextuality. But as we progressively degrade the certainty of the
+data, a transition happens in which the Mermin-Peres ``magic square''
+argument no longer demonstrates contextuality. Consider the nine observables
+$\mathbf{O}_{ij}$ with $i$ and $j$ ranging over $\{0,1,2\}$, corresponding
+to the Mermin-Peres ``magic square'' used to illustrate the KS theorem:
 
@@
 \hline  
-\end{tabular}\,.
+\end{tabular}\,,
 \par\end{center} 
@@
 $\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\} $ whose
-eigenvalues are all either~$1$ or $-1$.
-They are arranged such that in each row and column, \emph{except the
-column $j=2$}, every observable and its expectation value is the
-product of the other two. In the $j=2$ column, we have instead that
-$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$
+eigenvalues are all either~$1$ or $-1$. They are arranged such
+that in each row and column, \emph{except the column $j=2$}, every
+observable is the product of the other two, and its expectation value
+satisfies 
+\begin{eqnarray}
+\expval{\mathbf{O}_{i0}}\expval{\mathbf{O}_{i1}} & = & \expval{\mathbf{O}_{i2}}\,,\label{eq:i_expectation_value}\\
+\expval{\mathbf{O}_{j2}}\expval{\mathbf{O}_{j2}} & = & \expval{\mathbf{O}_{j2}}\,,\label{eq:j_0_1_expectation_value}
+\end{eqnarray}
+where $i\in\{0,1,2\}$ and $j\in\{0,1\}$. In the $j=2$ column, we
+have instead that $\mathbf{O}_{02}\mathbf{O}_{12}=-\mathbf{O}_{22}$
 and 
@@
 
-Assume we measure each observable twice. By the KS theorem, it is
-impossible to get the following measurement results because the product
-of the expectation values in the $j=2$ column violates Eq.~(\ref{eq:j_2_expectation_value}).
+Assume we measure each observable twice. By the KS theorem, the following
+measurement results are inconsistent with the prediction of quantum
+machines because the product of the expectation values in the $j=2$
+column violates Eq.~(\ref{eq:j_2_expectation_value}). 
 \begin{center}
@@
 \addlinespace
-$\mathbf{O}_{01}$ , $\mathbf{O}_{10}$  & $-1$ & $-1$ & $-1$\tabularnewline
+$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  & $-1$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{02}$ , $\mathbf{O}_{12}$ & $1$ & $1$ & $1$\tabularnewline
+$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  & $1$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{20}$ , $\mathbf{O}_{22}$ , $\mathbf{O}_{21}$  & $1$ & $1$ & $1$\tabularnewline
+$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$ & $1$  & $1$  & $1$\tabularnewline
 \bottomrule
@@
 
-Now consider what happens if half of the records are missing, i.e.,
-$\delta=\frac{1}{2}$, which gives the following measurement results,
-where $\missing$ stands for missing data.
+Now consider a small potion of experimantal results are missing. For
+example, we disgrad the results of $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$
+, and $\mathbf{O}_{21}$ in the first trial, and get the following
+measurement results:
 \begin{center}
@@
 $\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
- & \textrm{Record}\\
  & \textrm{Might Be}
@@
 \addlinespace
-$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$ & $\missing$ & $1$ & $0$\tabularnewline
+$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$ &  & $-1$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{01}$ , $\mathbf{O}_{10}$  & $\missing$ & $-1$ & $1$ & $0$\tabularnewline
+$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{02}$ , $\mathbf{O}_{12}$ & $1$ & $\missing$ & $-1$ & $0$\tabularnewline
+$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{20}$ , $\mathbf{O}_{22}$ , $\mathbf{O}_{21}$  & $\missing$ & $1$ & $-1$ & $0$\tabularnewline
+\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
+\cmidrule{4-5} 
+\addlinespace
+ &  &  & $-1$ & $0$\tabularnewline
 \bottomrule
@@
 
-\noindent Since the experimental results are missing, they might come
-from the third column. In this situation, the expectation values of
-each observables is always $0$, and the product relations among these
-expectation values is consistent with the product relations among
-observables.
+\noindent If all of the missing results are $1$, these experimental
+results reduced to the previous case; if any of $\expval{\mathbf{O}_{i2}}$
+is $0$, Eq.~(\ref{eq:i_expectation_value}) is violated in the $i$-th
+row. Hence, these results are still inconsistent with the prediction
+of quantum machines. Similar to the situation that even if $\frac{1}{4}$
+of the data is missing, $\bar{\mu}_{0}$cannot be extened to a valid
+QIVPM.
+
+Similar situation happens even if we miss a little more data. For
+example, the following measurement results is still not consistent
+with the prediction of quantum machines.
+\begin{center}
+\begin{tabular}{ccccc}
+\toprule 
+\addlinespace
+$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
+ & \textrm{Might Be}
+\end{aligned}
+$  & $\begin{aligned} & \textrm{Possible}\\
+ & \expval{\mathbf{O}_{ij}}
+\end{aligned}
+$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+\multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
+\cmidrule{4-5} 
+\addlinespace
+ &  &  & $-1$ & $-1$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
+\midrule 
+\addlinespace
+\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
+\cmidrule{4-5} 
+\addlinespace
+ &  &  & $-1$ & $0$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
+
+\noindent However, when we disgrad enough experimental results, the
+experimental results would start to be consistent with the prediction
+of quantum machines.
+\begin{center}
+\begin{tabular}{ccccc}
+\toprule 
+\addlinespace
+$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
+ & \textrm{Might Be}
+\end{aligned}
+$  & $\begin{aligned} & \textrm{Possible}\\
+ & \expval{\mathbf{O}_{ij}}
+\end{aligned}
+$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+\multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
+\cmidrule{4-5} 
+\addlinespace
+ &  &  & $-1$ & $-1$\tabularnewline
+\midrule 
+\addlinespace
+\multirow{2}{*}{$\mathbf{O}_{01}$, $\mathbf{O}_{10}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$-1$ } & $1$ & $0$\tabularnewline
+\cmidrule{4-5} 
+\addlinespace
+ &  &  & $-1$ & $-1$\tabularnewline
+\midrule 
+\addlinespace
+\multirow{2}{*}{$\mathbf{O}_{20}$, $\mathbf{O}_{21}$} & \multirow{2}{*}{$1$ } & \multirow{2}{*}{$\missing$} & $1$ & $1$\tabularnewline
+\cmidrule{4-5} 
+\addlinespace
+ &  &  & $-1$ & $0$\tabularnewline
+\midrule 
+\addlinespace
+\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
+\cmidrule{4-5} 
+\addlinespace
+ &  &  & $-1$ & $0$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
+
+\noindent By suitably assuming the missing data such that the expectation
+values of each observables are always $0$, the product relations
+among these expectation values is consistent with with the prediction
+of quantum machines. This kind of transition from inconsistence to
+consistence with the prediction of quantum machines is similar to
+the transition from inconsistence to consistence with a QIVPM when
+increasing $\delta$ from $<\tfrac{1}{3}$ to $\ge\tfrac{1}{3}$.
 

### 2018-02-11 prop_letter_ajhs_referee_response.tex
Updates from ShareLaTeX

--- 2018-02-10 prop_letter_ajhs_referee_response.tex
@@
 in that region our extension of the KS theorem definitely demonstrates
-contextuality. In the region to the right, the degradation of the data
+contextuality ({\bf{\sf C}}). In the region to the right, the degradation of the data
 is large and our extension of the KS theorem no longer refutes other

### 2018-02-11 prop_letter_ajhs_referee_response.tex

--- 2018-02-11 prop_letter_ajhs_referee_response.tex
@@
 
-\noindent The region to the left of the vertical line at $\delta=\frac{1}{3}$
-is where we assume small measurement degradation; in that region our
-extension of the KS theorem definitely demonstrates contextuality.
-In the region to the right, the degradation of the data is large and
-our extension of the KS theorem no longer refutes other explanations
-for the experimental data.
+\noindent The region to the left of the vertical line at
+$\delta=\frac{1}{3}$ is where we assume small measurement degradation;
+in that region our extension of the KS theorem definitely demonstrates
+contextuality ({\bf{\sf C}}). In the region to the right, the degradation of the data
+is large and our extension of the KS theorem no longer refutes other
+explanations for the experimental data.
 

### 2018-02-11 prop_letter_ajhs_referee_response.tex
one pass over response

@@
 \newcommand{\pmeas}{\ensuremath{\mu}}
-% \newcommand{\imposs}{{\text{\wesa{impossible}}}}
-% \newcommand{\likely}{{\text{\wesa{likely}}}}
-% \newcommand{\unlikely}{{\text{\wesa{unlikely}}}}
-% \newcommand{\necess}{{\text{\wesa{certain}}}}
-% \newcommand{\unknown}{{\text{\wesa{unknown}}}}
-% \newcommand{\midd}{{\text{\wesa{middle}}}}
 \newcommand{\imposs}{\ensuremath{\left[0,0\right]}}
@@
 \setcounter{secnumdepth}{3}
-% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
-% Change non-breaking space to \nolinebreak[1] 
-% Hence, it will not hyphenate too much surrounding words.
 \newcommand{\rmd}{d}
@@
 
-In our QIVPM framework, the Kochen-Specker (KS) theorem is equivalent
-to stating that there does not exist a ($\delta$=)$0$-deterministic
-QIVPM. We further claim (Thm.~\ref{cor:Kochen-Specker-IVPM}) that
-there cannot exist any $\delta$-deterministic QIVPM for
-$\delta<\frac{1}{3}$ and that there exist QIVPMs for every
-$\delta\ge\frac{1}{3}$.  The referee questions the correctness of
-Thm.~\ref{cor:Kochen-Specker-IVPM} and the physical interpretation of
-$\delta$-determinism. In answer to the question of correctness, we
-attach, for the referee's convenience, an expanded complete proof of
-Thm.~\ref{cor:Kochen-Specker-IVPM} at the end of this response. In the
-next paragraphs, we explain the physical interpretation of
-$\delta$-determinism and provide examples that illustrate why
-$\frac{1}{3}$ is special.
+\noindent In our QIVPM framework, the Kochen-Specker (KS) theorem is
+equivalent to stating that there does not exist a
+($\delta$=)$0$-deterministic QIVPM. We further claim
+(Thm.~\ref{cor:Kochen-Specker-IVPM}) that there cannot exist any
+$\delta$-deterministic QIVPM for $\delta<\frac{1}{3}$ and that there
+exist QIVPMs for every $\delta\ge\frac{1}{3}$.  The referee questions
+the correctness of Thm.~\ref{cor:Kochen-Specker-IVPM} and the physical
+interpretation of $\delta$-determinism. In answer to the question of
+correctness, we include below, for the referee's convenience, an
+expanded proof. In the remainder of the response, we explain the
+physical interpretation of $\delta$-determinism and provide examples
+that illustrate why $\frac{1}{3}$ is special.
 
-%\bigskip
+\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
+\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of
+dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
+$\delta<\frac{1}{3}$.\end{thm}
 
-\paragraph*{Experimental Data and $\delta$-determinism.} To the best of
-our understanding, the argument against $\delta$-determinism by the
-referee assumes that the parameter $\delta$ is \emph{exclusively}
-related to the density of states defined in a general Hilbert
-space. This is indeed Meyer's great insight and the main assumption in
-his proof that using the field of rationals nullifies the KS theorem.
-In other words, Meyer attributes finite-precision errors to the
-description of the states, which is an idea that has been challenged
-by several researchers, including Ax and Kochen (as cited by Cabello
-2002), who argue that the effect of finite-precision measurements on
-the KS theorem requires a different formalization. Our paper, indeed,
-makes no particular assumptions about the description of the states,
-and attributes finite-precision errors to the measurement process
-itself as realized in a laboratory. In our framework, the parameter
-$\delta$ reflects insufficient knowledge of the experimenter, which
-could be due to a variety of reasons related to imperfections of
-devices. A typical question that an experimenter may not be able to
-answer accurately would be ``did an electron land in the left half or
-the right half of the screen''? There are cases in which the electron
+The proof is by contradiction: Suppose there is a $\delta$-deterministic
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
+QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
+\begin{equation}
+\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
+\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
+\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
+\end{cases}
+\end{equation}
+However, since we know that $0$-deterministic QIVPMs do not exist,
+the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
+does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
+is indeed a QIVPM by checking that for orthogonal projectors $P_{0}$
+and~$P_{1}$, 
+\begin{equation}
+\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
+\end{equation}
+because Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) implies
+the convexity condition.
+
+When one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
+is $\necess$, say $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$
+and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[1-\delta,1\right]$
+and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
+implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1+\delta\right]$.
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of $\left[0,1\right]$,
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
+which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess$.
+
+When
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
+we have both $\bar{\mu}\left(P_{0}\right)$ and
+$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
+implies
+$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
+Since $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
+$\left[1-\delta,1\right]$ are disjoint, which implies
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ and $\left[1-\delta,1\right]$ are
+disjoint. Together with the fact that
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either
+$\left[0,\delta\right]$ or $\left[1-\delta,1\right]$,
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
+$\left[0,\delta\right]$, which implies
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+
+\subsection*{Experimental Data and $\delta$-determinism}
+
+To the best of our understanding, the argument against
+$\delta$-determinism by the referee assumes that the parameter
+$\delta$ is \emph{exclusively} related to the density of states
+defined in a general Hilbert space. This is indeed Meyer's great
+insight and the main assumption in his proof that using the field of
+rationals nullifies the KS theorem.  In other words, Meyer attributes
+finite-precision errors to the description of the states.
+
+In addition to responses like Mermin's that argue against Meyer's
+interpretation but accept his framework, there has been responses that
+argue that the effect of finite-precision measurements on the KS
+theorem requires a different approach altogether (see for example Ax
+and Kochen as cited by Cabello 2002). Our paper, indeed, takes a
+different approach. Our approach is agnostic about attributing
+elements of reality to the state function (as Meyer). We simply
+attribute lack of certainty to the measured results through the use of
+an instrument. Thus, the parameter $\delta$ in our framework reflects
+insufficient knowledge of the experimenter, which could be due to a
+variety of reasons related to imperfections of devices. For example, a
+typical question that an experimenter may not be able to answer
+accurately would be ``did an electron land in the left half or the
+right half of the screen''? There are cases in which the electron
 would land too close to the middle of the screen for the experimenter
@@
 the center. We simply record this imprecision in the probability we
-assign to events, and use the axioms of probability theory
-(additivity, convexity, etc) to argue that a sharp transition occurs
-when the imprecision reaches a certain value. Our approach is agnostic
-about attributing elements of reality to the state function (as
-Meyer). We simply attribute lack of certainty to the measured results
-through the use of an instrument.
+assign to events, and use the axioms of probability theory to argue
+that a sharp transition occurs when the imprecision reaches a certain
+value.
 
-To determine the probability of any event,
-we typically repeat an experiment $n$ times and count the number
-of times we witness the event. This assumes that for each run of the
-experiment we can determine, using our apparatus, whether the event
-occurred or not. Assume an event has an ideal mathematical probability
-of $0$, and we repeat the experiment $100$ times. In a perfect world
-we should be able to refute the event $100$ times and calculate that
-the probability is $0$. We might also observe the event $2$ times
-and refute it $98$ times and therefore calculate the probability
-to be $0.02$. Note that this situation assumes perfect measurement
-conditions.
-%Let the quantum system be in state~$\ket{\psi}$ and the probability
-%of some event  be $0$. Assume we repeat the experiment $100$ times
-%and we observe the event $1$ time. The Godsil-Zaks-Meyer approach
-%interprets this by assuming that the state was actually $\ket{\psi'}$
-%which is infinitesimally close to $\ket{\psi}$ and proceed to reason
-%about how coloring the states with rational points relates to the
-%coloring of arbitrary states. We make no such assumptions and do not
-%impose any constraints on the actual state of the system. In fact
-%we do not make any statements about such situations. What we are addressing
-%is a situation in which our devices do not allow to make a clear determination
-%of whether an event has happened or not. We model this by an uncertainty
-%in the probability of the event and then reason using the axioms of
-%probability theory to bound this uncertainty. We should add that our
-%approach is agnostic about attributing elements of reality to the
-%state function (as Meyer). We simply attribute lack of certainty to
-%the measured results through the use of an instrument. 
-The question we focus on is what happens if we are only able to refute
-it $97$ times and are \emph{uncertain} $3$ times? This is quite
-common in actual experiments. Mathematically we can model this idea
-by stating that the probability of the event is in the range $\left[0,0.03\right]$
-which says that the probability of the event could be $0$, $0.01$,
-$0.02$, or $0.03$ as each the three missing records could either
-be evidence for the event or against it. We just cannot nail it down
-given the current experimental results and therefore represent them as a ($\delta=$)$0.03$-deterministic
-probability measure. The interesting observation is that the axioms
-of probability theory (like additivity and convexity) impose enough
-constraints on the structure of probability measures to make them
-robust in the face of small $\delta$'s.
+In an experimental setup, $\delta$ is calculated as follows. To
+determine the probability of any event, we typically repeat an
+experiment $n$ times and count the number of times we witness the
+event. This assumes that for each run of the experiment we can
+determine, using our apparatus, whether the event occurred or
+not. Assume an event has an ideal mathematical probability of $0$, and
+we repeat the experiment $100$ times. In a perfect world we should be
+able to refute the event $100$ times and calculate that the
+probability is $0$. We might also observe the event $2$ times and
+refute it $98$ times and therefore calculate the probability to be
+$0.02$. Note that this situation assumes perfect measurement
+conditions and remains within the context of conventional
+(real-valued) probability theory. The question we focus on is what
+happens if we are only able to refute it $97$ times and are
+\emph{uncertain} $3$ times? This is quite common in actual
+experiments. Mathematically we can model this idea by stating that the
+probability of the event is in the range $\left[0,0.03\right]$ which
+says that the probability of the event could be $0$, $0.01$, $0.02$,
+or $0.03$ as each the three missing records could either be evidence
+for the event or against it. We just cannot nail it down given the
+current experimental results and therefore represent them as a
+($\delta=$)$0.03$-deterministic probability measure. The interesting
+observation is that the axioms of probability theory (like additivity
+and convexity) impose enough constraints on the structure of
+interval-valued quantum probability measures to make them robust in
+the face of small $\delta$'s.
 
-To see this in detail, consider a three-dimensional Hilbert space
-and an experiment repeated $12$ times. By the KS theorem, it is impossible
-to build a probability measure that maps every projection to either
-$0=\frac{0}{12}$ or $1=\frac{12}{12}$. Now consider what happens
-if $\frac{1}{4}$ of the data for every one-dimensional projector
-is missing. A potential account of this degradation is to assign to
-each event $P$ the entire range of possibilities $\bar{\mu}_{0}(P)$: 
+To see this idea in the context of a quantum experiment, consider a
+three-dimensional Hilbert space and an experiment repeated $12$
+times. By the KS theorem, it is impossible to build a probability
+measure that maps every projection to either $0=\frac{0}{12}$ or
+$1=\frac{12}{12}$. Now consider what happens if $\frac{1}{4}$ of the
+data for every one-dimensional projector is missing. A potential
+account of this degradation is to assign to each event $P$ the entire
+range of possibilities $\bar{\mu}_{0}(P)$:
 \begin{center}
@@
 a sharp transition occurs when $\delta=\tfrac{1}{3}$ as shown next.
-
-%% Indeed for every one-dimensional projector, the missing
-%% data could either refute or support the associated event. 
-%% This yields the following probability measure~$\bar{\mu}$
-%% as a possible formalization, where the column labeled by $P$ lists
-%% projectors, and the column labeled by $\bar{\mu}\left(P\right)$ lists
-%% the probability of these projectors.
 
@@
 
-\bigskip{}
-
-\paragraph*{Mermin-Peres ``Magic Square''.}
+\subsection*{Mermin-Peres ``Magic Square''}
 
@@
 
-Now consider a small potion of experimantal results are missing. For
-example, we disgrad the results of $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$
+Now consider a small potion of experimental results are missing. For
+example, we disregard the results of $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$
 , and $\mathbf{O}_{21}$ in the first trial, and get the following
@@
 of quantum machines. Similar to the situation that even if $\frac{1}{4}$
-of the data is missing, $\bar{\mu}_{0}$cannot be extened to a valid
+of the data is missing, $\bar{\mu}_{0}$cannot be extended to a valid
 QIVPM.
@@
 
-\noindent However, when we disgrad enough experimental results, the
+\noindent However, when we disregard enough experimental results, the
 experimental results would start to be consistent with the prediction
@@
 
-\bigskip
-
-\paragraph*{Expanded Proof of Thm.~3.}
-
-\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
-\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of
-dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
-$\delta<\frac{1}{3}$.\end{thm}
-
-The proof is by contradiction: Suppose there is a $\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
-QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
-\begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
-\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
-\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
-\end{cases}
-\end{equation}
-However, since we know that $0$-deterministic QIVPMs do not exist,
-the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
-does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
-is indeed a QIVPM by checking that for orthogonal projectors $P_{0}$
-and~$P_{1}$, 
-\begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
-\end{equation}
-because Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) implies
-the convexity condition.
-
-When one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
-is $\necess$, say $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$
-and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[1-\delta,1\right]$
-and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
-implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1+\delta\right]$.
-Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of $\left[0,1\right]$,
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
-which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess$.
-
-When
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have both $\bar{\mu}\left(P_{0}\right)$ and
-$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
-implies
-$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
-Since $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
-$\left[1-\delta,1\right]$ are disjoint, which implies
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ and $\left[1-\delta,1\right]$ are
-disjoint. Together with the fact that
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either
-$\left[0,\delta\right]$ or $\left[1-\delta,1\right]$,
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
-$\left[0,\delta\right]$, which implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
 \end{document}

### 2018-02-11 prop_letter_ajhs_referee_response.tex
nice revision

@@
 
-Assume we measure each observable twice. By the KS theorem, the following
-measurement results are inconsistent with the prediction of quantum
-machines because the product of the expectation values in the $j=2$
-column violates Eq.~(\ref{eq:j_2_expectation_value}). 
+Assume we measure each observable twice and get the following results
+where the ? indicates that we are uncertain about the actual outcome
+of observables $\mathbf{O}_{00}$ and $\mathbf{O}_{11}$ in the first run:
 \begin{center}
-\begin{tabular}{cccc}
+\begin{tabular}{l@{\qquad}r@{\qquad}r}
 \toprule 
 \addlinespace
-$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Possible}\\
- & \expval{\mathbf{O}_{ij}}
-\end{aligned}
-$\tabularnewline
+$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} \\
 \midrule
@@
 \addlinespace
-$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$  & $-1$\tabularnewline
+$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $?$  & $-1$  \\
 \midrule 
 \addlinespace
-$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  & $-1$\tabularnewline
+$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  \\
 \midrule 
 \addlinespace
-$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  & $1$\tabularnewline
+$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  \\
 \midrule 
 \addlinespace
-$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$ & $1$  & $1$  & $1$\tabularnewline
+$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$ & $1$  & $1$  \\
 \bottomrule
@@
 
-Now consider a small potion of experimental results are missing. For
-example, we disregard the results of $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$
-, and $\mathbf{O}_{21}$ in the first trial, and get the following
-measurement results:
+Irrespective of the undetermined result $?$ this table is inconsistent
+with Eq.~(\ref{eq:j_2_expectation_value}) as all the results in the
+last line are positive. In other words, these experimental results
+would be inconsistent with the predictions of quantum mechanics.
+
+Now consider an experiment in which the results of $\mathbf{O}_{20}$,
+$\mathbf{O}_{22}$, and $\mathbf{O}_{21}$ in the first trial are all
+undetermined:
+
 \begin{center}
-\begin{tabular}{ccccc}
+\begin{tabular}{l@{\qquad}r@{\qquad}r}
 \toprule 
 \addlinespace
-$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
- & \textrm{Might Be}
-\end{aligned}
-$  & $\begin{aligned} & \textrm{Possible}\\
- & \expval{\mathbf{O}_{ij}}
-\end{aligned}
-$\tabularnewline
+$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} \\
 \midrule
@@
 \addlinespace
-$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$ &  & $-1$\tabularnewline
+$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$  \\
 \midrule 
 \addlinespace
-$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
+$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  \\
 \midrule 
 \addlinespace
-$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
+$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  \\
 \midrule 
 \addlinespace
-\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $0$\tabularnewline
+$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$ & $?$  & $1$  \\
 \bottomrule
@@
 
-\noindent If all of the missing results are $1$, these experimental
-results reduced to the previous case; if any of $\expval{\mathbf{O}_{i2}}$
-is $0$, Eq.~(\ref{eq:i_expectation_value}) is violated in the $i$-th
-row. Hence, these results are still inconsistent with the prediction
-of quantum machines. Similar to the situation that even if $\frac{1}{4}$
-of the data is missing, $\bar{\mu}_{0}$cannot be extended to a valid
-QIVPM.
+% \begin{center}
+% \begin{tabular}{cccc}
+% \toprule 
+% \addlinespace
+% $\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Possible}\\
+%  & \expval{\mathbf{O}_{ij}}
+% \end{aligned}
+% $\tabularnewline
+% \midrule
+% \midrule 
+% \addlinespace
+% $\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$  & $-1$\tabularnewline
+% \midrule 
+% \addlinespace
+% $\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  & $-1$\tabularnewline
+% \midrule 
+% \addlinespace
+% $\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  & $1$\tabularnewline
+% \midrule 
+% \addlinespace
+% $\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$ & $1$  & $1$  & $1$\tabularnewline
+% \bottomrule
+% \end{tabular}
+% \par\end{center}
+%% Now consider a small potion of experimental results are missing. For
+%% example, we disregard the results of $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$
+%% , and $\mathbf{O}_{21}$ in the first trial, and get the following
+%% measurement results:
 
-Similar situation happens even if we miss a little more data. For
-example, the following measurement results is still not consistent
-with the prediction of quantum machines.
+% \begin{center}
+% \begin{tabular}{ccccc}
+% \toprule 
+% \addlinespace
+% $\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
+%  & \textrm{Might Be}
+% \end{aligned}
+% $  & $\begin{aligned} & \textrm{Possible}\\
+%  & \expval{\mathbf{O}_{ij}}
+% \end{aligned}
+% $\tabularnewline
+% \midrule
+% \midrule 
+% \addlinespace
+% $\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$ &  & $-1$\tabularnewline
+% \midrule 
+% \addlinespace
+% $\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
+% \midrule 
+% \addlinespace
+% $\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
+% \midrule 
+% \addlinespace
+% \multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
+% \cmidrule{4-5} 
+% \addlinespace
+%  &  &  & $-1$ & $0$\tabularnewline
+% \bottomrule
+% \end{tabular}
+% \par\end{center}
+
+\noindent If all of the missing results are $1$, the results violate
+Eq.~(\ref{eq:j_2_expectation_value}) as before. If any of the results
+is $-1$ meaning that the corresponding expectation value is 0,
+the corresponding Eq.~(\ref{eq:i_expectation_value}) is violated. Thus
+this table, although incomplete, is still inconsistent with the
+predictions of quantum mechanics.
+
+% Similar situation happens even if we miss a little more data. For
+% example, the following measurement results is still not consistent
+% with the prediction of quantum machines.
+% \begin{center}
+% \begin{tabular}{ccccc}
+% \toprule 
+% \addlinespace
+% $\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
+%  & \textrm{Might Be}
+% \end{aligned}
+% $  & $\begin{aligned} & \textrm{Possible}\\
+%  & \expval{\mathbf{O}_{ij}}
+% \end{aligned}
+% $\tabularnewline
+% \midrule
+% \midrule 
+% \addlinespace
+% \multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
+% \cmidrule{4-5} 
+% \addlinespace
+%  &  &  & $-1$ & $-1$\tabularnewline
+% \midrule 
+% \addlinespace
+% $\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
+% \midrule 
+% \addlinespace
+% $\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
+% \midrule 
+% \addlinespace
+% \multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
+% \cmidrule{4-5} 
+% \addlinespace
+%  &  &  & $-1$ & $0$\tabularnewline
+% \bottomrule
+% \end{tabular}
+% \par\end{center}
+
+\noindent At some point, however, when we disregard enough
+experimental results, the table becomes consistent with the prediction
+of quantum mechanics. For example:
+
 \begin{center}
-\begin{tabular}{ccccc}
+\begin{tabular}{l@{\qquad}r@{\qquad}r}
 \toprule 
 \addlinespace
-$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
- & \textrm{Might Be}
-\end{aligned}
-$  & $\begin{aligned} & \textrm{Possible}\\
- & \expval{\mathbf{O}_{ij}}
-\end{aligned}
-$\tabularnewline
+$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} \\
 \midrule
@@
 \addlinespace
-\multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $-1$\tabularnewline
+$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $?$  \\
 \midrule 
 \addlinespace
-$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
+$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $?$  & $-1$  \\
 \midrule 
 \addlinespace
-$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
+$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $?$  \\
 \midrule 
 \addlinespace
-\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $0$\tabularnewline
+$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$ & $?$  & $1$  \\
 \bottomrule
@@
 
-\noindent However, when we disregard enough experimental results, the
-experimental results would start to be consistent with the prediction
-of quantum machines.
-\begin{center}
-\begin{tabular}{ccccc}
-\toprule 
-\addlinespace
-$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
- & \textrm{Might Be}
-\end{aligned}
-$  & $\begin{aligned} & \textrm{Possible}\\
- & \expval{\mathbf{O}_{ij}}
-\end{aligned}
-$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $-1$\tabularnewline
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{01}$, $\mathbf{O}_{10}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$-1$ } & $1$ & $0$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $-1$\tabularnewline
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{20}$, $\mathbf{O}_{21}$} & \multirow{2}{*}{$1$ } & \multirow{2}{*}{$\missing$} & $1$ & $1$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $0$\tabularnewline
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $0$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
+% \begin{center}
+% \begin{tabular}{ccccc}
+% \toprule 
+% \addlinespace
+% $\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
+%  & \textrm{Might Be}
+% \end{aligned}
+% $  & $\begin{aligned} & \textrm{Possible}\\
+%  & \expval{\mathbf{O}_{ij}}
+% \end{aligned}
+% $\tabularnewline
+% \midrule
+% \midrule 
+% \addlinespace
+% \multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
+% \cmidrule{4-5} 
+% \addlinespace
+%  &  &  & $-1$ & $-1$\tabularnewline
+% \midrule 
+% \addlinespace
+% \multirow{2}{*}{$\mathbf{O}_{01}$, $\mathbf{O}_{10}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$-1$ } & $1$ & $0$\tabularnewline
+% \cmidrule{4-5} 
+% \addlinespace
+%  &  &  & $-1$ & $-1$\tabularnewline
+% \midrule 
+% \addlinespace
+% \multirow{2}{*}{$\mathbf{O}_{20}$, $\mathbf{O}_{21}$} & \multirow{2}{*}{$1$ } & \multirow{2}{*}{$\missing$} & $1$ & $1$\tabularnewline
+% \cmidrule{4-5} 
+% \addlinespace
+%  &  &  & $-1$ & $0$\tabularnewline
+% \midrule 
+% \addlinespace
+% \multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
+% \cmidrule{4-5} 
+% \addlinespace
+%  &  &  & $-1$ & $0$\tabularnewline
+% \bottomrule
+% \end{tabular}
+% \par\end{center}
 
-\noindent By suitably assuming the missing data such that the expectation
-values of each observables are always $0$, the product relations
-among these expectation values is consistent with with the prediction
-of quantum machines. This kind of transition from inconsistence to
-consistence with the prediction of quantum machines is similar to
-the transition from inconsistence to consistence with a QIVPM when
-increasing $\delta$ from $<\tfrac{1}{3}$ to $\ge\tfrac{1}{3}$.
+\noindent Indeed it is possible to assign for each $?$ the opposite of
+the other result, to ensure that all expectation values become 0, thus
+trivially validating the required equations.
+
+% By suitably assuming the missing data such that the expectation
+% values of each observables are always $0$, the product relations
+% among these expectation values is consistent with with the prediction
+% of quantum machines. This kind of transition from inconsistence to
+% consistence with the prediction of quantum machines is similar to
+% the transition from inconsistence to consistence with a QIVPM when
+% increasing $\delta$ from $<\tfrac{1}{3}$ to $\ge\tfrac{1}{3}$.
 

### 2018-02-13 prop_letter_ajhs_referee_response.tex
prop_letter_ajhs_referee_response.tex Fix the LaTeX warnings...
Programs/prop_letter_ajhs_referee_response.nb Relocated...
prop_letter_ajhs_referee_response.tex Eliminate ShareLaTeX warning...

--- 2018-02-11 prop_letter_ajhs_referee_response.tex
@@
 
-\title{Response to the Referee Report for \\
+\title{Response to the Referee Report for \texorpdfstring{\\}{}
 ``Quantum Interval-Valued Probability: Contextuality and the Born Rule''}
@@
 
-\subsection*{Experimental Data and $\delta$-determinism}
+\subsection*{Experimental Data and \texorpdfstring{$\delta$}{delta}-determinism}
 
@@
 
-To see this idea in the context of a quantum experiment, consider a
-three-dimensional Hilbert space and an experiment repeated $12$
+To see this idea in the context of a quantum experiment, consider
+a three-dimensional Hilbert space and an experiment repeated $12$
 times. By the KS theorem, it is impossible to build a probability
 measure that maps every projection to either $0=\frac{0}{12}$ or
-$1=\frac{12}{12}$. Now consider what happens if $\frac{1}{4}$ of the
-data for every one-dimensional projector is missing. A potential
-account of this degradation is to assign to each event $P$ the entire
-range of possibilities $\bar{\mu}_{0}(P)$:
+$1=\frac{12}{12}$. That is, the following assignment~$\bar{\mu}_{0}$
+is not a QIVPM
 \begin{center}
@@
 $P$  & $\bar{\mu}_{0}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors  & $\left[0,0\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors  & $\left[1,1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
+
+Now consider what happens if $\frac{1}{4}$ of the data for every
+one-dimensional projector is missing. A potential account of this
+degradation is to assign to each event $P$ the entire range of possibilities
+$\bar{\mu}_{1}(P)$: 
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{1}\left(P\right)$\tabularnewline
 \midrule
@@
 the convexity condition: for any two orthogonal one-dimensional events
-$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}_{0}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}_{0}\left(P_{0}\right)+\bar{\mu}_{0}\left(P_{1}\right)$,
-but $\bar{\mu}_{0}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
-which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}_{0}\left(P_{0}\right)+\bar{\mu}_{0}\left(P_{1}\right)$.
+$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$,
+but $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
+which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$.
 Interestingly, it is impossible to find any probability measure that
@@
 \addlinespace
-$P$  & $\bar{\mu}_{1}\left(P\right)$\tabularnewline
+$P$  & $\bar{\mu}_{2}\left(P\right)$\tabularnewline
 \midrule
@@
 \noindent This is also not a valid probability measure by the same
-argument as above. However, in this case $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
-and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$
+argument as above. However, in this case $\bar{\mu}_{2}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
+and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{2}\left(P_{0}\right)+\bar{\mu}_{2}\left(P_{1}\right)$
 have a common point. And hence by assuming that the missing data for
@@
 \addlinespace
-$P$  & $\bar{\mu}_{1}'\left(P\right)$\tabularnewline
+$P$  & $\bar{\mu}_{2}'\left(P\right)$\tabularnewline
 \midrule
@@
 \addlinespace
-$P$  & $\bar{\mu}_{2}\left(P\right)$\tabularnewline
+$P$  & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
 \midrule
@@
 
-We now use this same idea to analyze the Mermin-Peres ``magic square''
-argument. We show that when the measurements are infinitely precise,
-the Mermin-Peres ``magic square'' argument definitely demonstrates
-contextuality. But as we progressively degrade the certainty of the
-data, a transition happens in which the Mermin-Peres ``magic square''
-argument no longer demonstrates contextuality. Consider the nine observables
-$\mathbf{O}_{ij}$ with $i$ and $j$ ranging over $\{0,1,2\}$, corresponding
-to the Mermin-Peres ``magic square'' used to illustrate the KS theorem:
+We are going to phrase our results in a different way. When we see
+a set of experimental data with $\frac{1}{3}$ missing represented
+by $\bar{\mu}_{2}$, we could not determine whether the original record
+is come from the quantum mechanical $\bar{\mu}_{2}'$ or the hidden
+variable theory~$\bar{\mu}_{0}$ despite the fact that the hidden
+variable theory~$\bar{\mu}_{0}$ is not consistent with the prediction
+of quantum mechanics at all, i.e., $\bar{\mu}_{0}$ is not a QIVPM.
+The situation changes when we miss a little less records, say $\frac{1}{4}$.
+Since we proved missing $\frac{1}{4}$ of the measurement results
+of a hidden variable theory or $0$-deterministic QIVPM cannot be
+consistent with any valid QIVPM, symmetrically missing $\frac{1}{4}$
+of the measurement results of a valid QIVPM cannot be consistent with
+any hidden variable theory.
+
+This same idea can be used to analyze the Mermin-Peres ``magic square''
+argument experimentally, while this time we start from a possible
+quantum mechanical results, and show that it could be consistent with
+a hidden variable theory if missing enough records. Although the results
+could be consistent with a hidden variable theory missing much less
+data, because the Mermin-Peres ``magic square'' does use the full
+set of observables in a Hilbert space, it is less constraint than
+QIVPMs. Consider the nine observables $\mathbf{O}_{ij}$ with $i$
+and $j$ ranging over $\{0,1,2\}$, corresponding to the Mermin-Peres
+``magic square'' used to illustrate the KS theorem:
 
@@
 that in each row and column, \emph{except the column $j=2$}, every
-observable is the product of the other two, and its expectation value
-satisfies 
-\begin{eqnarray}
-\expval{\mathbf{O}_{i0}}\expval{\mathbf{O}_{i1}} & = & \expval{\mathbf{O}_{i2}}\,,\label{eq:i_expectation_value}\\
-\expval{\mathbf{O}_{j2}}\expval{\mathbf{O}_{j2}} & = & \expval{\mathbf{O}_{j2}}\,,\label{eq:j_0_1_expectation_value}
-\end{eqnarray}
-where $i\in\{0,1,2\}$ and $j\in\{0,1\}$. In the $j=2$ column, we
-have instead that $\mathbf{O}_{02}\mathbf{O}_{12}=-\mathbf{O}_{22}$
-and 
+observable is the product of the other two. In the $j=2$ column,
+we have instead that 
 \begin{equation}
-\expval{\mathbf{O}_{02}}\expval{\mathbf{O}_{12}}=-\expval{\mathbf{O}_{22}}\,.\label{eq:j_2_expectation_value}
+\mathbf{O}_{02}\mathbf{O}_{12}=-\mathbf{O}_{22}\,.\label{eq:j_2_expectation_value}
 \end{equation}
 
-Assume we measure each observable twice. By the KS theorem, the following
-measurement results are inconsistent with the prediction of quantum
-machines because the product of the expectation values in the $j=2$
-column violates Eq.~(\ref{eq:j_2_expectation_value}). 
+Since the observables in each row and column commute, they can be
+measured simultaneously. Assume we measure the observables row-by-row
+and then column-by-column, and get the following results, where the
+? indicates that we are uncertain about the actual outcome of observables~$\mathbf{O}_{22}$
+in the last run:
 \begin{center}
-\begin{tabular}{cccc}
+\begin{tabular}{l@{\qquad}r@{\qquad}r@{\qquad}r}
 \toprule 
 \addlinespace
-$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Possible}\\
- & \expval{\mathbf{O}_{ij}}
-\end{aligned}
-$\tabularnewline
+Trials & \multicolumn{3}{c}{Results}\tabularnewline
 \midrule
@@
 \addlinespace
-$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$  & $-1$\tabularnewline
+$0$ & $\mathbf{O}_{00}=-1$ & $\mathbf{O}_{01}=-1$ & $\mathbf{O}_{02}=1$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  & $-1$\tabularnewline
+$1$ & $\mathbf{O}_{10}=-1$ & $\mathbf{O}_{11}=-1$ & $\mathbf{O}_{12}=1$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  & $1$\tabularnewline
+$2$ & $\mathbf{O}_{20}=1$ & $\mathbf{O}_{21}=1$ & $\mathbf{O}_{22}=1$\tabularnewline
 \midrule 
 \addlinespace
-$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$ & $1$  & $1$  & $1$\tabularnewline
+$3$ & $\mathbf{O}_{00}=-1$ & $\mathbf{O}_{10}=-1$ & $\mathbf{O}_{20}=1$\tabularnewline
+\midrule 
+\addlinespace
+$4$ & $\mathbf{O}_{01}=-1$ & $\mathbf{O}_{11}=-1$ & $\mathbf{O}_{21}=1$\tabularnewline
+\midrule 
+\addlinespace
+$5$ & $\mathbf{O}_{02}=1$ & $\mathbf{O}_{12}=1$ & $\mathbf{O}_{22}=?$\tabularnewline
 \bottomrule
@@
 
-Now consider a small potion of experimental results are missing. For
-example, we disregard the results of $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$
-, and $\mathbf{O}_{21}$ in the first trial, and get the following
-measurement results:
-\begin{center}
-\begin{tabular}{ccccc}
-\toprule 
-\addlinespace
-$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
- & \textrm{Might Be}
-\end{aligned}
-$  & $\begin{aligned} & \textrm{Possible}\\
- & \expval{\mathbf{O}_{ij}}
-\end{aligned}
-$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$ &  & $-1$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $0$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
-
-\noindent If all of the missing results are $1$, these experimental
-results reduced to the previous case; if any of $\expval{\mathbf{O}_{i2}}$
-is $0$, Eq.~(\ref{eq:i_expectation_value}) is violated in the $i$-th
-row. Hence, these results are still inconsistent with the prediction
-of quantum machines. Similar to the situation that even if $\frac{1}{4}$
-of the data is missing, $\bar{\mu}_{0}$cannot be extended to a valid
-QIVPM.
-
-Similar situation happens even if we miss a little more data. For
-example, the following measurement results is still not consistent
-with the prediction of quantum machines.
-\begin{center}
-\begin{tabular}{ccccc}
-\toprule 
-\addlinespace
-$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
- & \textrm{Might Be}
-\end{aligned}
-$  & $\begin{aligned} & \textrm{Possible}\\
- & \expval{\mathbf{O}_{ij}}
-\end{aligned}
-$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $-1$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $0$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
-
-\noindent However, when we disregard enough experimental results, the
-experimental results would start to be consistent with the prediction
-of quantum machines.
-\begin{center}
-\begin{tabular}{ccccc}
-\toprule 
-\addlinespace
-$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
- & \textrm{Might Be}
-\end{aligned}
-$  & $\begin{aligned} & \textrm{Possible}\\
- & \expval{\mathbf{O}_{ij}}
-\end{aligned}
-$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $-1$\tabularnewline
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{01}$, $\mathbf{O}_{10}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$-1$ } & $1$ & $0$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $-1$\tabularnewline
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{20}$, $\mathbf{O}_{21}$} & \multirow{2}{*}{$1$ } & \multirow{2}{*}{$\missing$} & $1$ & $1$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $0$\tabularnewline
-\midrule 
-\addlinespace
-\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
-\cmidrule{4-5} 
-\addlinespace
- &  &  & $-1$ & $0$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
-
-\noindent By suitably assuming the missing data such that the expectation
-values of each observables are always $0$, the product relations
-among these expectation values is consistent with with the prediction
-of quantum machines. This kind of transition from inconsistence to
-consistence with the prediction of quantum machines is similar to
-the transition from inconsistence to consistence with a QIVPM when
-increasing $\delta$ from $<\tfrac{1}{3}$ to $\ge\tfrac{1}{3}$.
+If the undetermined result $?$ is $-1$, this table is consistent
+with Eq.~(\ref{eq:j_2_expectation_value}) and could be predicted
+by quantum mechanics. If the undetermined result $?$ is $1$, every
+observable has a definite measurement result, and form a hidden variable
+theory which is not completely consistent with the prediction of quantum
+mechanics.
 

### 2018-02-13 prop_letter_ajhs_referee_response.tex
prop_letter_ajhs_referee_response.tex Updating...

@@
 When one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
-is $\necess$, say $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$
-and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[1-\delta,1\right]$
-and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
+is $\necess$, say $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\imposs$
+and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\necess$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
+and $\bar{\mu}\left(P_{1}\right)\subseteq\left[1-\delta,1\right]$ which
 implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1+\delta\right]$.
@@
 
-We are going to phrase our results in a different way. When we see
-a set of experimental data with $\frac{1}{3}$ missing represented
+We are going to phrase our results in a different way. Since $\bar{\mu}_{0}$
+maps every projectors to $\imposs$ or $\necess$, $\bar{\mu}_{0}$
+can predict experimental results deterministically, i.e., it is a
+deterministic hidden variable theory despite the fact that $\bar{\mu}_{0}$
+is not consistent with the prediction of quantum mechanics. When we
+see a set of experimental data with $\frac{1}{3}$ missing represented
 by $\bar{\mu}_{2}$, we could not determine whether the original record
-is come from the quantum mechanical $\bar{\mu}_{2}'$ or the hidden
-variable theory~$\bar{\mu}_{0}$ despite the fact that the hidden
-variable theory~$\bar{\mu}_{0}$ is not consistent with the prediction
-of quantum mechanics at all, i.e., $\bar{\mu}_{0}$ is not a QIVPM.
-The situation changes when we miss a little less records, say $\frac{1}{4}$.
-Since we proved missing $\frac{1}{4}$ of the measurement results
-of a hidden variable theory or $0$-deterministic QIVPM cannot be
-consistent with any valid QIVPM, symmetrically missing $\frac{1}{4}$
-of the measurement results of a valid QIVPM cannot be consistent with
-any hidden variable theory.
+is come from the quantum mechanical $\bar{\mu}_{2}'$ or the deterministic
+hidden variable theory~$\bar{\mu}_{0}$. The situation changes when
+we miss a little less records, say $\frac{1}{4}$. Since we proved
+missing $\frac{1}{4}$ of the measurement results of a hidden variable
+theory cannot be consistent with any valid QIVPM, symmetrically missing
+$\frac{1}{4}$ of the measurement results of a valid QIVPM cannot
+be consistent with any hidden variable theory.
 
@@
 quantum mechanical results, and show that it could be consistent with
-a hidden variable theory if missing enough records. Although the results
-could be consistent with a hidden variable theory missing much less
-data, because the Mermin-Peres ``magic square'' does use the full
-set of observables in a Hilbert space, it is less constraint than
-QIVPMs. Consider the nine observables $\mathbf{O}_{ij}$ with $i$
-and $j$ ranging over $\{0,1,2\}$, corresponding to the Mermin-Peres
-``magic square'' used to illustrate the KS theorem:
+a deterministic hidden variable theory if missing enough records.
+The missing records for the Mermin-Peres ``magic square'' could
+be much less than the previous examples, because the Mermin-Peres
+``magic square'' does use the full set of observables in a Hilbert
+space which imposing less constraints. Consider the nine observables
+$\mathbf{O}_{ij}$ with $i$ and $j$ ranging over $\{0,1,2\}$, corresponding
+to the Mermin-Peres ``magic square'' used to illustrate the KS theorem:
 
@@
 \hline  
-\end{tabular}\,,
+\end{tabular}\,.
 \par\end{center} 
@@
 If the undetermined result $?$ is $-1$, this table is consistent
-with Eq.~(\ref{eq:j_2_expectation_value}) and could be predicted
-by quantum mechanics. If the undetermined result $?$ is $1$, every
-observable has a definite measurement result, and form a hidden variable
-theory which is not completely consistent with the prediction of quantum
-mechanics.
+with Eq.~(\ref{eq:j_2_expectation_value}) and the prediction of
+quantum mechanics. If the undetermined result $?$ is $1$, every
+observable has a definite measurement result, and form a deterministic
+hidden variable theory although they are not completely consistent
+with the prediction of quantum mechanics.
 

### 2018-02-14 prop_letter_ajhs_referee_response.tex
revised response

@@
 
-\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
-\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of
-dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for
-$\delta<\frac{1}{3}$.\end{thm}
+\subsection*{Expanded Proof of Thm.~3}
 
-The proof is by contradiction: Suppose there is a $\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
-QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
+We begin with a lemma related $\delta$-deterministic QIVPMs and
+0-deterministic QIVPMs.
+
+\begin{lemma} 
+  From any $\delta$-deterministic
+  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ with
+  $\delta < \frac{1}{3}$, we can construct the $0$-deterministic QIVPM
+  $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
+    \imposs,\necess\right\}$ defined as follows:
 \begin{equation}
@@
 \end{equation}
-However, since we know that $0$-deterministic QIVPMs do not exist,
-the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
-does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
-is indeed a QIVPM by checking that for orthogonal projectors $P_{0}$
+\end{lemma}
+The most important part of the proof is to verify the convexity
+condition for $\bar{\mu}^{\textrm{D}}$. Because
+$\bar{\mu}^{\textrm{D}}$ is 0-deterministic, it is sufficient to
+verify the following equation for orthogonal projectors $P_{0}$
 and~$P_{1}$,
 \begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
+\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,. \label{eq:QuantumInterval-valuedProbability-Equal}
 \end{equation}
-because Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) implies
-the convexity condition.
 
@@
 $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
-which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess$.
+which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)$ is also
+$\necess$ satisfying Eq.~\ref{eq:QuantumInterval-valuedProbability-Equal}.
 
-When
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have both $\bar{\mu}\left(P_{0}\right)$ and
+When both
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
+are $\imposs$, we have both $\bar{\mu}\left(P_{0}\right)$ and
 $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
@@
 $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
-Since $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
+Since we assume $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
 $\left[1-\delta,1\right]$ are disjoint, which implies
@@
 $\left[0,\delta\right]$, which implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$ and hence
+also satisfying Eq.~\ref{eq:QuantumInterval-valuedProbability-Equal}.
+
+\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
+\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of 
+dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for 
+$\delta<\frac{1}{3}$.\end{thm}
+The proof is by contradiction: Suppose there is a $\delta$-deterministic 
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. By the previous
+lemma, we can construct a 0-deterministic QIVPM but by Thm.~2 in the
+paper, such 0-deterministic QIVPMs do not exist.
 
@@
 In addition to responses like Mermin's that argue against Meyer's
-interpretation but accept his framework, there has been responses that
-argue that the effect of finite-precision measurements on the KS
+interpretation but accept his framework, there have been responses
+that argue that the effect of finite-precision measurements on the KS
 theorem requires a different approach altogether (see for example Ax
-and Kochen as cited by Cabello 2002). Our paper, indeed, takes a
-different approach. Our approach is agnostic about attributing
-elements of reality to the state function (as Meyer). We simply
-attribute lack of certainty to the measured results through the use of
-an instrument. Thus, the parameter $\delta$ in our framework reflects
-insufficient knowledge of the experimenter, which could be due to a
-variety of reasons related to imperfections of devices. For example, a
-typical question that an experimenter may not be able to answer
-accurately would be ``did an electron land in the left half or the
-right half of the screen''? There are cases in which the electron
-would land too close to the middle of the screen for the experimenter
-to be able to determine with certainty that it was left or right of
-the center. We simply record this imprecision in the probability we
-assign to events, and use the axioms of probability theory to argue
-that a sharp transition occurs when the imprecision reaches a certain
-value.
+and Kochen as cited by Cabello 2002). Our approach is agnostic about
+attributing elements of reality to the state function (as Meyer
+did). We simply attribute lack of certainty to the measured results
+through the use of an instrument. Thus, the parameter $\delta$ in our
+framework reflects insufficient knowledge of the experimenter, which
+could be due to a variety of reasons related to imperfections of
+devices. For example, a typical question that an experimenter may not
+be able to answer accurately would be ``did an electron land in the
+left half or the right half of the screen''? There are cases in which
+the electron would land too close to the middle of the screen for the
+experimenter to be able to determine with certainty that it was left
+or right of the center. We simply record this imprecision in the
+probability we assign to events, and use the axioms of probability
+theory to argue that a sharp transition occurs when the imprecision
+reaches a certain value.
 
@@
 
+\end{document}
+
 \subsection*{Mermin-Peres ``Magic Square''}
@@
 If the undetermined result $?$ is $-1$, this table is consistent
-with Eq.~(\ref{eq:j_2_expectation_value}) and the prediction of
+with Eq.~(\ref{eq:j_2_expectation_value}) and the predictions of
 quantum mechanics. If the undetermined result $?$ is $1$, every
@@
 with the prediction of quantum mechanics.
-
-\end{document}

### 2018-02-14 prop_letter_ajhs_referee_response.tex
revised response

@@
 
-We begin with a lemma related $\delta$-deterministic QIVPMs and
-0-deterministic QIVPMs.
+We begin by presenting two lemmas to make the presentation more
+modular.
+
+The first lemma shows a simpler way to prove the convexity
+condition. Recall that convexity condition for a QIVPM
+$\mu : \events \rightarrow \mathscr{I}$ states that for each pair of
+\emph{commuting} projectors~$P$ and~$P'$ with $PP'=P'P$, the following
+equation holds:
+\begin{equation}
+\bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(P'\right)\,.
+\end{equation}
+
+\begin{lemma}
+  To verify the convexity condition of a QIVPM
+  $\mu : \events \rightarrow \mathscr{I}$, it is sufficient to verify
+  that for all orthogonal projectors $P_{0}$ and~$P_{1}$, we have
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.\label{amr}
+\end{equation}
+\end{lemma}
+\noindent The proof follows the outline of the proof of the classical
+inclusion-exclusion principle. From the commuting projectors $P$ and
+$P'$, we construct the following three orthogonal projectors $PP'$,
+$P(\mathbb{1}-P')$, and $(\mathbb{1}-P)P'$. Then we proceed as
+follows: {\footnotesize
+\[\begin{array}{rcl}
+&& \bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right) \\
+&& \hfill(\mbox{because } P = PP' + P - PP') \\
+&=& \bar{\mu}\left(PP'+P(\mathbb{1}-P')+P'-PP'\right)+\bar{\mu}\left(PP'\right) \\
+&=& \bar{\mu}\left(P(\mathbb{1}-P')+P'\right)+\bar{\mu}\left(PP'\right) \\
+&& \hfill(\mbox{because } P' = PP' + P' - PP') \\
+&=& \bar{\mu}\left(P(\mathbb{1}-P')+PP'+(\mathbb{1}-P)P'\right)+\bar{\mu}\left(PP'\right) \\
+&& \hfill(\mbox{using Eq.~(2) twice}) \\
+&=&
+    \bar{\mu}(P(\mathbb{1}-P'))+\bar{\mu}(PP')+\bar{\mu}((\mathbb{1}-P)P')+
+    \bar{\mu}\left(PP'\right) \\
+&& \hfill(\mbox{using Eq.~(2) twice}) \\
+&=&
+    \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') \\
+&=&
+    \bar{\mu}(P) + \bar{\mu}(P')
+\end{array}\]}
+
+The next lemma relates $\delta$-deterministic QIVPMs with $\delta <
+\frac{1}{3}$ to 0-deterministic QIVPMs.
 
@@
 \end{lemma}
-The most important part of the proof is to verify the convexity
-condition for $\bar{\mu}^{\textrm{D}}$. Because
-$\bar{\mu}^{\textrm{D}}$ is 0-deterministic, it is sufficient to
-verify the following equation for orthogonal projectors $P_{0}$
+\noindent The most important part of the proof is to verify the convexity
+condition for $\bar{\mu}^{\textrm{D}}$. By Lemma~2.1, it is sufficient
+to verify the following equation for orthogonal projectors $P_{0}$
 and~$P_{1}$,
@@
 which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)$ is also
-$\necess$ satisfying Eq.~\ref{eq:QuantumInterval-valuedProbability-Equal}.
+$\necess$ satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
 
@@
 $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$ and hence
-also satisfying Eq.~\ref{eq:QuantumInterval-valuedProbability-Equal}.
+also satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
 
@@
 $\delta<\frac{1}{3}$.\end{thm}
-The proof is by contradiction: Suppose there is a $\delta$-deterministic 
+\noindent The proof is by contradiction: Suppose there is a $\delta$-deterministic 
 QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. By the previous
@@
 
-Now consider what happens if $\frac{1}{4}$ of the data for every
+Now consider what happens if $\frac{1}{4}$ of the data for \emph{every}
 one-dimensional projector is missing. A potential account of this
@@
 and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{2}\left(P_{0}\right)+\bar{\mu}_{2}\left(P_{1}\right)$
-have a common point. And hence by assuming that the missing data for
+have a \emph{common point}. And hence by assuming that the missing data for
 one-dimensional projectors always support the associated event, while

### 2018-02-14 prop_letter_ajhs_referee_response.tex
prop_letter_ajhs_referee_response.tex Change any "missing" to "uncertain".

@@
 says that the probability of the event could be $0$, $0.01$, $0.02$,
-or $0.03$ as each the three missing records could either be evidence
+or $0.03$ as each the three uncertain records could either be evidence
 for the event or against it. We just cannot nail it down given the
@@
 $1=\frac{12}{12}$. That is, the following assignment~$\bar{\mu}_{0}$
-is not a QIVPM
+is not a QIVPM:
 \begin{center}
@@
 Now consider what happens if $\frac{1}{4}$ of the data for \emph{every}
-one-dimensional projector is missing. A potential account of this
+one-dimensional projector is uncertain. A potential account of this
 degradation is to assign to each event $P$ the entire range of possibilities
@@
 and no amount of shifting of assumptions regarding the precise outcome
-of the missing observations could change that disjointness. However,
+of the uncertain observations could change that disjointness. However,
 a sharp transition occurs when $\delta=\tfrac{1}{3}$ as shown next.
 
-In case the missing data reaches $\frac{1}{3}$, the probability measure
+In case the uncertain data reaches $\frac{1}{3}$, the probability measure
 that assigns to each event the entire range of possibilities is: 
@@
 and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{2}\left(P_{0}\right)+\bar{\mu}_{2}\left(P_{1}\right)$
-have a \emph{common point}. And hence by assuming that the missing data for
+have a \emph{common point}. And hence by assuming that the uncertain data for
 one-dimensional projectors always support the associated event, while
@@
 A similar situation happens when more than $\frac{1}{3}$ of data
-is missing. In particular, having half of the data missing, the probability
+is uncertain. In particular, if half of the data is uncertain, the probability
 measure that assigns to each event the entire range of possibilities
@@
 is not consistent with the prediction of quantum mechanics. When we
-see a set of experimental data with $\frac{1}{3}$ missing represented
+see a set of experimental data with $\frac{1}{3}$ uncertain represented
 by $\bar{\mu}_{2}$, we could not determine whether the original record
@@
 we miss a little less records, say $\frac{1}{4}$. Since we proved
-missing $\frac{1}{4}$ of the measurement results of a hidden variable
-theory cannot be consistent with any valid QIVPM, symmetrically missing
+uncertain $\frac{1}{4}$ of the measurement results of a hidden variable
+theory cannot be consistent with any valid QIVPM, symmetrically uncertain
 $\frac{1}{4}$ of the measurement results of a valid QIVPM cannot
@@
 quantum mechanical results, and show that it could be consistent with
-a deterministic hidden variable theory if missing enough records.
-The missing records for the Mermin-Peres ``magic square'' could
+a deterministic hidden variable theory if enough records is uncertain.
+The uncertain records for the Mermin-Peres ``magic square'' could
 be much less than the previous examples, because the Mermin-Peres

### 2018-02-15 prop_letter_ajhs_referee_response.tex
From: Tai, Yu-Tsung Sent: Wednesday, February 14, 2018 19:57 To: Sabry, Amr A. <sabry@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu> Subject: RE: revised referee response
I changed every "missing" to "uncertain" as suggested by Gerardo, and some other small things... The current version is attached, and I will submit the response to the editor if I didn't receive any further issue until tomorrow morning...

To Amr, about automatically putting parenthesis when cross-referencing equations, I think it might be more useful to generate the text prepend

@@
   QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ with
-  $\delta < \frac{1}{3}$, we can construct the $0$-deterministic QIVPM
+  $\delta < \frac{1}{3}$, we can construct a $0$-deterministic QIVPM
   $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
@@
 When both
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
 are $\imposs$, we have both $\bar{\mu}\left(P_{0}\right)$ and

### 2018-02-15 dissertation.tex
dissertation.tex "Acceptance Page" Updating...
dissertation.tex Update the requirements for CV...

@@
 \usepackage{amssymb}
+\usepackage{pdfpages}
 
@@
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
+\newcommand{\gmult}{*}
+\newcommand{\Fpx}[1]{\mathbb{F}_{#1}}
+\newcommand{\Fq}{\mathbb{F}_{q}}
+\newcommand{\ff}[1]{\mathbb{F}_{#1}}
 
@@
 \defensedate{Defense Date}
-\acceptancepage{Prof. Amr A. Sabry}{Prof. Dylan Paul Thurston}{Prof. Gerardo Ortiz}{Prof. Andrew J. Hanson}[Prof. Shouhong Wang]
+\acceptancepage{Amr A. Sabry, PhD}{Dylan Paul Thurston, PhD}{Gerardo Ortiz, PhD}{Andrew J. Hanson, PhD}[Shouhong Wang, PhD]
 
@@
 \chapter{Quantum Theories and Computing over Finite Fields}
+
+\section{Fundamentals of Finite Fields\label{sec:background}}
+
+A field~$\mathbb{F}$ is an algebraic structure consisting of a set
+of elements equipped with the operations of addition, subtraction,
+multiplication, and division \cite{fieldtheory.ref,numtheory.ref}.
+Fields may contain an infinite or a finite number of elements. The
+rational~$\mathbb{Q}$, real~$\mathbb{R}$, and complex numbers~$\mathbb{C}$
+are examples of infinite fields, while the set $\mathbb{F}_{3}=\{0,1,2\}$,
+under multiplication and addition modulo $3$, is an example of a
+finite field.
+
+There are two distinguished elements in a field, the addition identity
+$0$, and the multiplication identity $1$. Given the field~$\mathbb{F}$,
+the closed operations of addition, ``$+$,'' and multiplication,
+``$\gmult$,'' satisfy the following set of axioms: 
+\begin{enumerate}
+\item $\mathbb{F}$ is an Abelian group under the addition operation~$+$
+(additive group); 
+\item The multiplication operation~$\gmult$ is associative and commutative.
+The field has a multiplicative identity and the property that every
+nonzero element has a multiplicative inverse; 
+\item Distributive laws: For all $a,b,c\in\mathbb{F}$ 
+\begin{eqnarray}
+a\gmult(b+c) & = & a\gmult b+a\gmult c\\
+(b+c)\gmult a & = & b\gmult a+c\gmult a\ .
+\end{eqnarray}
+\end{enumerate}
+\noindent From now on, unless specified, we will omit the symbol~$\gmult$
+whenever we multiply two elements of a field.
+
+Finite fields of $q$ elements, $\Fq=\{0,\ldots,q-1\}$, will play
+a special role in this work. A simple explicit example is $\mathbb{F}_{3}$
+with the following addition and multiplication tables: 
+\[
+\begin{array}{c|ccc}
++ & 0 & 1 & 2\\[0.1in]
+\hline 0 & 0 & 1 & 2\\
+1 & 1 & 2 & 0\\
+2 & 2 & 0 & 1
+\end{array}\hspace*{2cm}\begin{array}{c|ccc}
+\gmult & 0 & 1 & 2\\[0.1in]
+\hline 0 & 0 & 0 & 0\\
+1 & 0 & 1 & 2\\
+2 & 0 & 2 & 1
+\end{array}
+\]
+
+The characteristic of a field is the least positive integer~$m$
+such that $m=1+1+1+\cdots+1=0$, and if no such $m$ exists we say
+that the field has characteristic zero (which is the case for $\mathbb{R}$
+for example). It turns out that if the characteristic is non-zero
+it must be a prime~$p$. For every prime~$p$ and positive integer~$r$
+there is a finite field~$\Fpx{p^{r}}$ of size $q=p^{r}$ and characteristic~$p$,
+which is unique up to field isomorphism \cite{Artin1991,DummitFoote2004}.
+The exponent $r$ is known as the \emph{degree} of the field over
+its prime subfield\footnote{ Fields $\ff{q}$ where $q$ is a power of a prime $p$, i.e., $q=p^{r}$,
+are known as Galois fields.}~\cite{GT.ref}. If the characteristic $p$ is an arbitrary prime
+number, we call the field \emph{unrestricted}.
+
+For every $a\in\Fq$, $a\neq0$, then $a^{q-1}=1$, implying the Frobenius
+endomorphism (also a consequence of Fermat's little theorem) $a^{q}=a$,
+which in turn permits us to write the multiplicative inverse of any
+non-zero element in the field as $a^{-1}=a^{q-2}$, since $a^{q-2}a=a^{q-1}=1$.
+Every subfield of the field~$\Fq$, of size $q=p^{r}$, has $p^{r'}$
+elements with some $r'$ dividing $r$, and for a given $r'$ it is
+unique.
+
+\section{Modal Quantum Theory\label{modalquantum}}
 
@@
 
-%\include{CV}
+% http://latex.org/forum/viewtopic.php?t=7312
+% http://latex.org/forum/viewtopic.php?t=17956
+\addtocontents{toc}{\noindent\contentsline{chapter}{Curriculum Vitae}{}}
+\includepdf[pages=-]{CV_thesis}
 \end{document}

### 2018-02-16 prop_letter_ajhs_referee_response.tex
prop_letter_ajhs_referee_response.tex Updated according to Andy's suggestion...

@@
 The first lemma shows a simpler way to prove the convexity
-condition. Recall that convexity condition for a QIVPM
-$\mu : \events \rightarrow \mathscr{I}$ states that for each pair of
+condition. Recall that the convexity condition for a QIVPM
+$\bar{\mu} : \events \rightarrow \mathscr{I}$ states that for each pair of
 \emph{commuting} projectors~$P$ and~$P'$ with $PP'=P'P$, the following
@@
 inclusion-exclusion principle. From the commuting projectors $P$ and
-$P'$, we construct the following three orthogonal projectors $PP'$,
+$P'$, we construct the following three orthogonal projectors: $PP'$,
 $P(\mathbb{1}-P')$, and $(\mathbb{1}-P)P'$. Then we proceed as
-follows: {\footnotesize
-\[\begin{array}{rcl}
-&& \bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right) \\
-&& \hfill(\mbox{because } P = PP' + P - PP') \\
-&=& \bar{\mu}\left(PP'+P(\mathbb{1}-P')+P'-PP'\right)+\bar{\mu}\left(PP'\right) \\
-&=& \bar{\mu}\left(P(\mathbb{1}-P')+P'\right)+\bar{\mu}\left(PP'\right) \\
-&& \hfill(\mbox{because } P' = PP' + P' - PP') \\
-&=& \bar{\mu}\left(P(\mathbb{1}-P')+PP'+(\mathbb{1}-P)P'\right)+\bar{\mu}\left(PP'\right) \\
-&& \hfill(\mbox{using Eq.~(2) twice}) \\
-&=&
-    \bar{\mu}(P(\mathbb{1}-P'))+\bar{\mu}(PP')+\bar{\mu}((\mathbb{1}-P)P')+
-    \bar{\mu}\left(PP'\right) \\
-&& \hfill(\mbox{using Eq.~(2) twice}) \\
-&=&
-    \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') \\
-&=&
-    \bar{\mu}(P) + \bar{\mu}(P')
-\end{array}\]}
+follows:
+\begin{widetext}
+\begin{equation}
+\begin{aligned}
+& \bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right) & (\mbox{because } P = PP' + P - PP') \\
+=& \bar{\mu}\left(PP'+P(\mathbb{1}-P')+P'-PP'\right)+\bar{\mu}\left(PP'\right) \\
+=& \bar{\mu}\left(P(\mathbb{1}-P')+P'\right)+\bar{\mu}\left(PP'\right) & (\mbox{because } P' = PP' + P' - PP') \\
+=& \bar{\mu}\left(P(\mathbb{1}-P')+PP'+(\mathbb{1}-P)P'\right)+\bar{\mu}\left(PP'\right) & (\mbox{using Eq.~(2) twice}) \\
+=& \bar{\mu}(P(\mathbb{1}-P'))+\bar{\mu}(PP')+\bar{\mu}((\mathbb{1}-P)P')+
+    \bar{\mu}\left(PP'\right) & (\mbox{using Eq.~(2) twice}) \\
+=& \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') \\
+=& \bar{\mu}(P) + \bar{\mu}(P')
+\end{aligned}
+\end{equation}
+\end{widetext}
 
@@
 \begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,. \label{eq:QuantumInterval-valuedProbability-Equal}
+\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,, \label{eq:QuantumInterval-valuedProbability-Equal}
 \end{equation}
+for two conditions, which we now examine in detail.
 
@@
 which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)$ is also
-$\necess$ satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
+$\necess$, thus satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
 
@@
 $\left[0,\delta\right]$, which implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$ and hence
-also satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$, and hence
+also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) is again satisfied.
 
@@
 QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. By the previous
-lemma, we can construct a 0-deterministic QIVPM but by Thm.~2 in the
+lemma, we can construct a 0-deterministic QIVPM; however, by Thm.~2 in the
 paper, such 0-deterministic QIVPMs do not exist.
@@
 attributing elements of reality to the state function (as Meyer
-did). We simply attribute lack of certainty to the measured results
-through the use of an instrument. Thus, the parameter $\delta$ in our
+did). We simply attribute lack of certainty to the uncertain
+results obtained through the use of a measuring instrument. Thus, the parameter~$\delta$ in our
 framework reflects insufficient knowledge of the experimenter, which
@@
 be able to answer accurately would be ``did an electron land in the
-left half or the right half of the screen''? There are cases in which
+left half or the right half of the screen?'' There are cases in which
 the electron would land too close to the middle of the screen for the
@@
 for the event or against it. We just cannot nail it down given the
-current experimental results and therefore represent them as a
+current experimental results and therefore represent the evidence as a
 ($\delta=$)$0.03$-deterministic probability measure. The interesting
@@
 interval-valued quantum probability measures to make them robust in
-the face of small $\delta$'s.
+the face of small nonvanishing $\delta$'s.
 
 To see this idea in the context of a quantum experiment, consider
-a three-dimensional Hilbert space and an experiment repeated $12$
+a three-dimensional Hilbert space with
+one-dimensional projectors~$P_\rho$, two-dimensional projectors
+$P_\rho + P_\sigma$, and an experiment that is experiment repeated $12$
 times. By the KS theorem, it is impossible to build a probability
@@
 Interestingly, it is impossible to find any probability measure that
-would be consistent with these observations as the interval $\left[\tfrac{3}{4},1\right]$
+would be consistent with these observations, as the interval $\left[\tfrac{3}{4},1\right]$
 is completely disjoint from the interval $\left[0,\tfrac{1}{2}\right]$
@@
 of the uncertain observations could change that disjointness. However,
-a sharp transition occurs when $\delta=\tfrac{1}{3}$ as shown next.
+as shown next, a sharp transition occurs when $\delta=\tfrac{1}{3}$.
 
-In case the uncertain data reaches $\frac{1}{3}$, the probability measure
+When the proportion of uncertain data reaches $\frac{1}{3}$, the probability measure
 that assigns to each event the entire range of possibilities is: 
@@
 and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{2}\left(P_{0}\right)+\bar{\mu}_{2}\left(P_{1}\right)$
-have a \emph{common point}. And hence by assuming that the uncertain data for
+have a \emph{common point}. Hence, by assuming that the uncertain data for
 one-dimensional projectors always support the associated event, while
 those for two-dimensional projectors always refute the event, we can
-find the following probability measure which can verified to be a
-valid QIVPM and which is consistent with the experimental data: 
+find the following probability measure that can verified to be a
+valid QIVPM and is consistent with the experimental data: 
 \begin{center}

### 2018-02-17 revised_prop_letter_ajhs.PRA.tex
revised_prop_letter_ajhs.tex \input{revised_prop_letter_ajhs.bbl} Added to make sure PRA can compile...

--- 2018-01-10 prop_letter_ajhs.tex
@@
 \newtheorem{thm}{Theorem}
-\newtheorem{lemma}{Lemma}[thm]
-\newtheorem{cor}{Corollary}[thm]
+\newtheorem{lemma}{Lemma}
+\newtheorem{cor}{Corollary}
 \newtheorem{assumption}{Assumption}
@@
 for small enough $\delta$, it is impossible to have
-$\delta$-deterministic QIVPMs. We next prove a main result of this
-paper which is a stronger statement of contextuality that includes the
-effects of finite-precision.  Every QIVPM must map some events to
-truly uncertain intervals, not just ``almost definite intervals.'' 
-% \andy{contextuality is never defined.}
-% \yutsung{Actually, the second sentence in the introduction defines
-% ``contextuality''. The problem is that there is no direct relation between what
-% defined in the introduction and here.}
-
-\begin{thm}[Finite-precision Extension of the Kochen-Specker
-  Theorem] \label{cor:Kochen-Specker-IVPM} Given a Hilbert space
-  $\Hilb$ of dimension~$d\ge3$, there is no $\delta$-deterministic
-  QIVPM for $\delta<\frac{1}{3}$.\end{thm}
-
-The proof is by contradiction: Suppose there is a
-$\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this
-assumed QIVPM to construct the following 0-deterministic QIVPM
+$\delta$-deterministic QIVPMs.
+
+We next prove a main result of this paper which is a stronger
+statement of contextuality that includes the effects of
+finite-precision.  Every QIVPM must map some events to truly uncertain
+intervals, not just ``almost definite intervals.'' The proof requires
+two simple lemmas which we present first.
+
+The first lemma shows a simpler way to prove the convexity
+condition. Recall that the convexity condition for a QIVPM
+$\bar{\mu} : \events \rightarrow \mathscr{I}$ states that for each pair of
+\emph{commuting} projectors~$P$ and~$P'$ with $PP'=P'P$, the following
+equation holds:
+\begin{equation}
+\bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(P'\right)\,.
+\end{equation}
+
+\begin{lemma}
+  To verify the convexity condition of a QIVPM
+  $\mu : \events \rightarrow \mathscr{I}$, it is sufficient to check
+  that:
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{amr}
+\end{equation}
+ for all orthogonal projectors $P_{0}$ and~$P_{1}$.
+\end{lemma}
+\noindent The proof follows the outline of the proof of the classical
+inclusion-exclusion principle. From the commuting projectors $P$ and
+$P'$, we construct the following three orthogonal projectors: $PP'$,
+$P(\mathbb{1}-P')$, and $(\mathbb{1}-P)P'$. Then we proceed as
+follows:
+\begin{widetext}
+\begin{equation*}
+\begin{aligned}
+\noalign{$\bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right)$}
+\qquad\qquad=~~&\bar{\mu}\left(PP'+P(\mathbb{1}-P')+P'-PP'\right)+\bar{\mu}\left(PP'\right) 
+  & (\mbox{because } P = PP' + P - PP') \\
+=~~& \bar{\mu}\left(P(\mathbb{1}-P')+P'\right)+\bar{\mu}\left(PP'\right) \\
+=~~& \bar{\mu}\left(P(\mathbb{1}-P')+PP'+(\mathbb{1}-P)P'\right)+\bar{\mu}\left(PP'\right) 
+      & (\mbox{because } P' = PP' + P' - PP') \\
+=~~& \bar{\mu}(P(\mathbb{1}-P'))+\bar{\mu}(PP')+\bar{\mu}((\mathbb{1}-P)P')+
+    \bar{\mu}\left(PP'\right) & (\mbox{using Eq.~(2) twice}) \\
+=~~& \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') & (\mbox{using Eq.~(2) twice}) \\
+=~~& \bar{\mu}(P) + \bar{\mu}(P')
+\end{aligned}
+\end{equation*}
+\end{widetext}
+
+The next lemma relates $\delta$-deterministic QIVPMs with $\delta <
+\frac{1}{3}$ to 0-deterministic QIVPMs.
+
+\begin{lemma} 
+  From any $\delta$-deterministic
+  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ with
+  $\delta < \frac{1}{3}$, we can construct a $0$-deterministic QIVPM
   $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
-  \imposs,\necess\right\}$:
-\[
+    \imposs,\necess\right\}$ defined as follows:
+\begin{equation}
 \bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
@@
 \end{cases}
-\]
-However, since we know that 0-deterministic QIVPMs do not exist, the
-map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ does
-not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$ is
-indeed a 0-deterministic QIVPM by checking that for orthogonal
-projectors~$P_{0}$ and $P_{1}$, we have that
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
-implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\cite{TaiThesis2018}. Indeed
-when
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
-we have both $\bar{\mu}\left(P_{0}\right)$ and
+\end{equation}
+\end{lemma}
+\noindent The most important part of the proof is to verify the convexity
+condition for $\bar{\mu}^{\textrm{D}}$. By Lemma~2.1, it is sufficient
+to verify the following equation for orthogonal projectors $P_{0}$
+and~$P_{1}$,
+\begin{equation}
+\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,, \label{eq:QuantumInterval-valuedProbability-Equal}
+\end{equation}
+for two conditions, which we now examine in detail.
+
+When one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
+is $\necess$, say $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\imposs$
+and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\necess$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
+and $\bar{\mu}\left(P_{1}\right)\subseteq\left[1-\delta,1\right]$ which
+implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1+\delta\right]$.
+Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of $\left[0,1\right]$,
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
+which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)$ is also
+$\necess$, thus satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
+
+When both
+$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
+are $\imposs$, we have both $\bar{\mu}\left(P_{0}\right)$ and
 $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
@@
 $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
-When $\delta<\frac{1}{3}$, i.e., $2\delta<1-\delta$, it follows that
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ cannot be a subset of
-$\left[1-\delta,1\right]$. Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
-is a subset of either $\left[0,\delta\right]$ or
-$\left[1-\delta,1\right]$ and the latter is excluded, then
+Since we assume $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
+$\left[1-\delta,1\right]$ are disjoint, which implies
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ and $\left[1-\delta,1\right]$ are
+disjoint. Together with the fact that
+$\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either
+$\left[0,\delta\right]$ or $\left[1-\delta,1\right]$,
 $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
 $\left[0,\delta\right]$, which implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
-theorem holds when $\delta<\frac{1}{3}$.
+$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$, and hence
+also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) is again satisfied.
+
+\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
+\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of 
+dimension~$d\ge3$, there is no $\delta$-deterministic QIVPM for 
+$\delta<\frac{1}{3}$.\end{thm}
+\noindent The proof is by contradiction: Suppose there is a
+$\delta$-deterministic
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. By the previous
+lemma, we can construct a 0-deterministic QIVPM; however, by
+Thm.~\ref{thm:Kochen-Specker}, such 0-deterministic QIVPMs do not
+exist.
 
@@
 invalidating the Kochen-Specker theorem.
+
+The above arguments could be summarized and illustrated using
+Fig.~\ref{fignoname}. An additional perspective on the physical
+interpretation of the theorem is in the appendix.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{prop_letter_ajhs_referee_response_nb} 
+\par\end{center}
+\caption{The region to the left of the vertical line at
+$\delta=\frac{1}{3}$ is where we assume small measurement degradation;
+in that region our extension of the KS theorem definitely demonstrates
+contextuality ({\bf{\sf C}}). In the region to the right, the degradation of the data
+is large and our extension of the KS theorem no longer refutes other
+explanations for the experimental data.}
+\label{fignoname}
+\end{figure}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix*
+\section{Experimental Data and \texorpdfstring{$\delta$}{delta}-determinism}
+
+Meyer's insight and the main assumption in his proof that using the
+field of rationals nullifies the Kochen-Specker theorem.  In other
+words, Meyer exclusively attributes finite-precision errors to the
+description of the states defined in a general Hilbert space. The
+response of Mermin, argues against Meyer's interpretation but accepts
+his framework. More generally, there have been responses that argue
+that the effect of finite-precision measurements on the Kochen-Specker
+theorem requires a different approach altogether (see for example Ax
+and Kochen's communication cited by Cabello~\cite{Cabello2002}). Our
+approach is agnostic about attributing elements of reality to the
+state function (as Meyer did). We simply attribute lack of certainty
+to the uncertain results obtained through the use of a measuring
+instrument. Thus, the parameter~$\delta$ in our framework reflects
+insufficient knowledge of the experimenter, which could be due to a
+variety of reasons related to imperfections of devices. For example, a
+typical question that an experimenter may not be able to answer
+accurately would be ``did an electron land in the left half or the
+right half of the screen?''  There are cases in which the electron
+would land too close to the middle of the screen for the experimenter
+to be able to determine with certainty that it was left or right of
+the center. We simply record this imprecision in the probability we
+assign to events, and use the axioms of probability theory to argue
+that a sharp transition occurs when the imprecision reaches a certain
+value.
+
+In an experimental setup, $\delta$ is calculated as follows. To
+determine the probability of any event, we typically repeat an
+experiment $n$ times and count the number of times we witness the
+event. This assumes that for each run of the experiment we can
+determine, using our apparatus, whether the event occurred or
+not. Assume an event has an ideal mathematical probability of $0$, and
+we repeat the experiment $100$ times. In a perfect world we should be
+able to refute the event $100$ times and calculate that the
+probability is $0$. We might also observe the event $2$ times and
+refute it $98$ times and therefore calculate the probability to be
+$0.02$. Note that this situation assumes perfect measurement
+conditions and remains within the context of conventional
+(real-valued) probability theory. The question we focus on is what
+happens if we are only able to refute it $97$ times and are
+\emph{uncertain} $3$ times? This is quite common in actual
+experiments. Mathematically we can model this idea by stating that the
+probability of the event is in the range $\left[0,0.03\right]$ which
+says that the probability of the event could be $0$, $0.01$, $0.02$,
+or $0.03$ as each the three uncertain records could either be evidence
+for the event or against it. We just cannot nail it down given the
+current experimental results and therefore represent the evidence as a
+($\delta=$)$0.03$-deterministic probability measure. The interesting
+observation is that the axioms of probability theory (like additivity
+and convexity) impose enough constraints on the structure of
+interval-valued quantum probability measures to make them robust in
+the face of small non-vanishing $\delta$'s.
+
+To see this idea in the context of a quantum experiment, consider
+a three-dimensional Hilbert space with
+one-dimensional projectors~$P_\rho$, two-dimensional projectors
+$P_\rho + P_\sigma$, and an experiment that is experiment repeated $12$
+times. By the Kochen-Specker theorem, it is impossible to build a probability
+measure that maps every projection to either $0=\frac{0}{12}$ or
+$1=\frac{12}{12}$. That is, the following assignment~$\bar{\mu}_{0}$
+is not a QIVPM:
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{0}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors  & $\left[0,0\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors  & $\left[1,1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
+
+Now consider what happens if $\frac{1}{4}$ of the data for \emph{every}
+one-dimensional projector is uncertain. A potential account of this
+degradation is to assign to each event $P$ the entire range of possibilities
+$\bar{\mu}_{1}(P)$: 
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{1}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors  & $\left[0,\tfrac{1}{4}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors  & $\left[\tfrac{3}{4},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
+
+\noindent This measure is not a valid QIVPM because it does not satisfy
+the convexity condition: for any two orthogonal one-dimensional events
+$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$,
+but $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
+which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$.
+Interestingly, it is impossible to find any probability measure that
+would be consistent with these observations, as the interval $\left[\tfrac{3}{4},1\right]$
+is completely disjoint from the interval $\left[0,\tfrac{1}{2}\right]$
+and no amount of shifting of assumptions regarding the precise outcome
+of the uncertain observations could change that disjointness. However,
+as shown next, a sharp transition occurs when $\delta=\tfrac{1}{3}$.
+
+When the proportion of uncertain data reaches $\frac{1}{3}$, the probability measure
+that assigns to each event the entire range of possibilities is: 
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{2}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors  & $\left[0,\tfrac{1}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors  & $\left[\tfrac{2}{3},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
+
+\noindent This is also not a valid probability measure by the same
+argument as above. However, in this case $\bar{\mu}_{2}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
+and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{2}\left(P_{0}\right)+\bar{\mu}_{2}\left(P_{1}\right)$
+have a \emph{common point}. Hence, by assuming that the uncertain data for
+one-dimensional projectors always support the associated event, while
+those for two-dimensional projectors always refute the event, we can
+find the following probability measure that can verified to be a
+valid QIVPM and is consistent with the experimental data: 
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{2}'\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
+
+A similar situation happens when more than $\frac{1}{3}$ of data
+is uncertain. In particular, if half of the data is uncertain, the probability
+measure that assigns to each event the entire range of possibilities
+is already a QIVPM:
+\begin{center}
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors  & $\left[\tfrac{1}{2},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{center}
+
 \bibliography{prop}

### 2018-02-18 dissertation.tex
dissertation.tex Updating according to the current format of document class...

@@
 \usepackage{framed}
-\usepackage[usenames,dvipsnames]{xcolor}
 \usepackage[braket,qm]{qcircuit}
@@
 \usepackage{pdfpages}
+\usepackage{setspace}
 
 \newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
-\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
 \newcommand{\muB}{\ensuremath{\mu^{B}}}
@@
 \title{Discrete Quantum Theories and Computing}
-\author{Yu-Tsung Tai}
+\author{\large{Yu-Tsung Tai}}
 \date{\today}
-\maketitle[Department of Mathematics][Department of Computer Science]
+\department{Department of Mathematics}
+\department{Department of Computer Science}
+\maketitle
 
 %data for Acceptance Page
+\committeeMember{Amr A. Sabry, PhD}
+\committeeMember{Dylan Paul Thurston, PhD}
+\committeeMember{Gerardo Ortiz, PhD}
+\committeeMember{Andrew J. Hanson, PhD}
+\committeeMember{Shouhong Wang, PhD}
 \defensedate{Defense Date}
-\acceptancepage{Amr A. Sabry, PhD}{Dylan Paul Thurston, PhD}{Gerardo Ortiz, PhD}{Andrew J. Hanson, PhD}[Shouhong Wang, PhD]
+\acceptancepage
 
 %data for Copyright Page
-\cryear{2018}
-\copyrightpage
+% \cryear{2018}
+% \copyrightpage
 
-%\begin{dedication}
-%\end{dedication}
+% \dedication{}
+% \dedicationpage
 
-\begin{acknowledgments}
-The acknowledgments are designed to recognize people or agencies to whom you feel grateful for any academic,
+\acknowledgements{The acknowledgments are designed to recognize people or agencies to whom you feel grateful for any academic,
 technical, financial, or personal aid in the preparation of your thesis or dissertation; as a matter of
 courtesy, you would ordinarily mention the members of your committee here, as well as institutions that
-provided funding, your typist, or anyone else who helped.
-\end{acknowledgments}
+provided funding, your typist, or anyone else who helped.}
+\acknowledgementspage
 
-%\begin{preface}
-%\end{preface}
+%\preface{}
+% \prefacepage
 
-\begin{abstract}
-Our primary research interest is to build a quantum computing model
+\abstract{Our primary research interest is to build a quantum computing model
 characterizing realistic quantum computers. While most of the quantum
@@
 quantum interval-valued probability, and proved an imprecise version
-of foundational results such as the Gleason and Kochen-Specker theorems. 
-\end{abstract}
+of foundational results such as the Gleason and Kochen-Specker theorems.}
+\abstractpage
+
 \tableofcontents{}
@@
 
+\addcontentsline{toc}{chapter}{Bibliography}
 \begin{comment}

### 2018-02-19 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Remove T2A encoding to make sure APS website can successfully preview the PDF file...
revised_prop_letter_ajhs.tex Fix a typo...

--- 2018-02-17 revised_prop_letter_ajhs.PRA.tex
@@
 \usepackage{cmap}
-\usepackage[T1,T2A]{fontenc}
+% \usepackage[T1,T2A]{fontenc}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
@@
 $\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
-way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
+way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = \mathbb{1}$, then
 $\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
@@
 
-\bibliography{prop}
+\input{revised_prop_letter_ajhs.bbl}
+% \bibliography{prop}
 \end{document}

### 2018-02-19 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fix typos suggested by Andy...

@@
 
-The above arguments could be summarized and illustrated using
+We can summarize and illustrate the above arguments using
 Fig.~\ref{fignoname}. An additional perspective on the physical
@@
 
-Meyer's insight and the main assumption in his proof that using the
+This is Meyer's great insight and the main assumption in his proof that using the
 field of rationals nullifies the Kochen-Specker theorem.  In other

### 2018-02-19 revised_prop_letter_ajhs.tex
From: Tai, Yu-Tsung Sent: Monday, February 19, 2018 5:29 To: Hanson, Andrew J. <hansona@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu> Subject: RE: letter to the editor
Dear all,

I changed the text according to my previous email, and the source files are in the ShareLaTeX and GitHub as usual. Please check whether it looks fine and see if you have any suggestions… Thanks : )

Best regards,
Tai, Yu-Tsung (戴淯琮)
PhD Candidate double-majoring in Mathematics & Computer Science
Indiana University, Bloomington
https://www.linkedin.com/in/yu-tsung-tai-9aa30551

@@
 two intervals are correlated: there is more information in the
-combined event than in each event separately. In our example, even
+combined event than in each event separately so the combined event should be mapped to
+a sharper interval. In our example, even
 though the ``true'' probability of $E$ can be anywhere in the range
@@
 
+\begin{table*}
+\caption{\label{tab:probability-measures}Possible probability measures on
+a Hilbert space of dimension~$d=3$, where $\bar{\mu}_{2}'$ and
+$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
+and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
+by $P$.}
+\centering{}%
+\begin{tabular}{cccccc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{0}\left(P\right)$ & $\bar{\mu}_{1}\left(P\right)$ & $\bar{\mu}_{2}\left(P\right)$ & $\bar{\mu}_{2}'\left(P\right)$ & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors  & $\left[0,0\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left[0,\tfrac{1}{3}\right]$ & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$ & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors  & $\left[1,1\right]$ & $\left[\tfrac{3}{4},1\right]$ & $\left[\tfrac{2}{3},1\right]$ & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$ & $\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
 This is Meyer's great insight and the main assumption in his proof that using the
@@
 a three-dimensional Hilbert space with
-one-dimensional projectors~$P_\rho$, two-dimensional projectors
-$P_\rho + P_\sigma$, and an experiment that is experiment repeated $12$
+one-dimensional projectors~$P_{\rho}$, two-dimensional projectors
+$P_{\rho}+P_{\sigma}$, and an experiment that is experiment repeated $12$
 times. By the Kochen-Specker theorem, it is impossible to build a probability
 measure that maps every projection to either $0=\frac{0}{12}$ or
-$1=\frac{12}{12}$. That is, the following assignment~$\bar{\mu}_{0}$
-is not a QIVPM:
-\begin{center}
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$P$  & $\bar{\mu}_{0}\left(P\right)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-All one-dimensional projectors  & $\left[0,0\right]$\tabularnewline
-\midrule 
-\addlinespace
-All two-dimensional projectors  & $\left[1,1\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
+$1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
+defined in Table~\ref{tab:probability-measures} is not a QIVPM.
 
@@
 degradation is to assign to each event $P$ the entire range of possibilities
-$\bar{\mu}_{1}(P)$: 
-\begin{center}
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$P$  & $\bar{\mu}_{1}\left(P\right)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-All one-dimensional projectors  & $\left[0,\tfrac{1}{4}\right]$\tabularnewline
-\midrule 
-\addlinespace
-All two-dimensional projectors  & $\left[\tfrac{3}{4},1\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
-
-\noindent This measure is not a valid QIVPM because it does not satisfy
+$\bar{\mu}_{1}(P)$ as defined in Table~\ref{tab:probability-measures}.
+This measure is not a valid QIVPM because it does not satisfy
 the convexity condition: for any two orthogonal one-dimensional events
@@
 When the proportion of uncertain data reaches $\frac{1}{3}$, the probability measure
-that assigns to each event the entire range of possibilities is: 
-\begin{center}
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$P$  & $\bar{\mu}_{2}\left(P\right)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-All one-dimensional projectors  & $\left[0,\tfrac{1}{3}\right]$\tabularnewline
-\midrule 
-\addlinespace
-All two-dimensional projectors  & $\left[\tfrac{2}{3},1\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
-
-\noindent This is also not a valid probability measure by the same
+that assigns to each event the entire range of possibilities is
+$\bar{\mu}_{2}$ defined in Table~\ref{tab:probability-measures}.
+This is also not a valid probability measure by the same
 argument as above. However, in this case $\bar{\mu}_{2}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
@@
 those for two-dimensional projectors always refute the event, we can
-find the following probability measure that can verified to be a
-valid QIVPM and is consistent with the experimental data: 
-\begin{center}
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$P$  & $\bar{\mu}_{2}'\left(P\right)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-All one-dimensional projectors  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$\tabularnewline
-\midrule 
-\addlinespace
-All two-dimensional projectors  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
+find the probability measure~$\bar{\mu}_{2}'$ that can verified to be a
+valid QIVPM and is consistent with the experimental data.
 
@@
 is uncertain. In particular, if half of the data is uncertain, the probability
-measure that assigns to each event the entire range of possibilities
-is already a QIVPM:
-\begin{center}
-\begin{tabular}{cc}
-\toprule 
-\addlinespace
-$P$  & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-All one-dimensional projectors  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
-\midrule 
-\addlinespace
-All two-dimensional projectors  & $\left[\tfrac{1}{2},1\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\par\end{center}
+measure~$\bar{\mu}_{3}$ that assigns to each event the entire range of possibilities
+is already a QIVPM.
 

### 2018-02-19 revised_prop_letter_ajhs.tex
Updated according to Gerardo's suggestion...

@@
 \end{table*}
-This is Meyer's great insight and the main assumption in his proof that using the
-field of rationals nullifies the Kochen-Specker theorem.  In other
+It is Meyer's great insight to realize that the Kochen-Specker theorem can be nullified 
+by replacing the field of the reals by rational numbers.  In other
 words, Meyer exclusively attributes finite-precision errors to the

### 2018-02-19 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fixed some cross-references in Lemmas and Thm. 3…

@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:verify-convexity}
   To verify the convexity condition of a QIVPM
@@
 =~~& \bar{\mu}(P(\mathbb{1}-P'))+\bar{\mu}(PP')+\bar{\mu}((\mathbb{1}-P)P')+
-    \bar{\mu}\left(PP'\right) & (\mbox{using Eq.~(2) twice}) \\
-=~~& \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') & (\mbox{using Eq.~(2) twice}) \\
+    \bar{\mu}\left(PP'\right) & (\mbox{using Eq.~(\ref{amr}) twice}) \\
+=~~& \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') & (\mbox{using Eq.~(\ref{amr}) twice}) \\
 =~~& \bar{\mu}(P) + \bar{\mu}(P')
@@
 
-\begin{lemma} 
+\begin{lemma}\label{lemma:delta2zero} 
   From any $\delta$-deterministic
@@
 \noindent The most important part of the proof is to verify the convexity
-condition for $\bar{\mu}^{\textrm{D}}$. By Lemma~2.1, it is sufficient
+condition for $\bar{\mu}^{\textrm{D}}$. By Lemma~\ref{lemma:verify-convexity}, it is sufficient
 to verify the following equation for orthogonal projectors $P_{0}$
@@
 $\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. By the previous
-lemma, we can construct a 0-deterministic QIVPM; however, by
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. By
+Lemma~\ref{lemma:delta2zero}, we can construct a 0-deterministic QIVPM; however, by
 Thm.~\ref{thm:Kochen-Specker}, such 0-deterministic QIVPMs do not

### 2018-02-24 dissertation.tex
dissertation.lyx "3.2 Modal Quantum Theory" Updating...

@@
+%% LyX 2.2.3 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
 \documentclass[twoside]{iuphd}
@@
 \usepackage[utf8]{inputenc}
+\setcounter{secnumdepth}{3}
+\setcounter{tocdepth}{3}
+\usepackage{verbatim}
+\usepackage{mathrsfs}
+\usepackage{pdfpages}
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\makeatletter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% A simple dot to overcome graphicx limitations
+\newcommand{\lyxdot}{.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
 \usepackage[ backend=biber]{biblatex}
@@
 \usepackage{comment}
+
 %\usepackage[basic]{complexity}
@@
 \newlang{\usat}{UNIQUE-SAT}
+
 \usepackage[all]{xy}
@@
 \usepackage{mathrsfs}
-\usepackage{amssymb}
-\usepackage{pdfpages}
 \usepackage{setspace}
@@
 \newcommand{\gmult}{*}
-\newcommand{\Fpx}[1]{\mathbb{F}_{#1}}
-\newcommand{\Fq}{\mathbb{F}_{q}}
-\newcommand{\ff}[1]{\mathbb{F}_{#1}}
+\newcommand{\Fpx}[1]{\mathbb{F}_{{#1}}}
+\newcommand{\Fq}{\Fpx{q}}
+\newcommand{\ff}[1]{\Fpx{#1}}
+\newcommand{\ffzx}[2]{\Fpx{#1}^{{#2}\;*}}
+\newcommand{\ffx}[2]{\Fpx{#1}^{{#2}}}
+\newcommand{\ffzd}[1]{\ffzx{#1}{d}}
+\newcommand{\ffd}[1]{\ffx{#1}{d}}
+\newcommand{\VVec}[1]{\vec{\bf #1}}
+\newcommand{\mathComplex}{\mathbb{C}}
+\newcommand{\braket}[2]{\ip{#1}{#2}}
+
+\department{Department of Mathematics}
+\department{Department of Computer Science}
+
+\makeatother
 
@@
 %data for Title Page
+
 \title{Discrete Quantum Theories and Computing}
-\author{\large{Yu-Tsung Tai}}
+
+\author{{Yu-Tsung Tai}}
+
 \date{\today}
-\department{Department of Mathematics}
-\department{Department of Computer Science}
+
 \maketitle
-
 %data for Acceptance Page
-\committeeMember{Amr A. Sabry, PhD}
-\committeeMember{Dylan Paul Thurston, PhD}
-\committeeMember{Gerardo Ortiz, PhD}
-\committeeMember{Andrew J. Hanson, PhD}
-\committeeMember{Shouhong Wang, PhD}
-\defensedate{Defense Date}
-\acceptancepage
+\committeeMember{Amr A. Sabry, PhD} \committeeMember{Dylan Paul
+Thurston, PhD} \committeeMember{Gerardo Ortiz, PhD} \committeeMember{Andrew
+J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{Defense
+Date} \acceptancepage
 
@@
 
-\acknowledgements{The acknowledgments are designed to recognize people or agencies to whom you feel grateful for any academic,
-technical, financial, or personal aid in the preparation of your thesis or dissertation; as a matter of
-courtesy, you would ordinarily mention the members of your committee here, as well as institutions that
-provided funding, your typist, or anyone else who helped.}
-\acknowledgementspage
+\acknowledgements{The acknowledgments are designed to recognize
+people or agencies to whom you feel grateful for any academic, technical,
+financial, or personal aid in the preparation of your thesis or dissertation;
+as a matter of courtesy, you would ordinarily mention the members
+of your committee here, as well as institutions that provided funding,
+your typist, or anyone else who helped.} \acknowledgementspage
 
@@
 
-\abstract{Our primary research interest is to build a quantum computing model
-characterizing realistic quantum computers. While most of the quantum
-computing models based on uncomputable numbers, that is, the continuum
-of real numbers, most of the classical computers in our daily life
-are digital instead of analog computers. This highlight the necessity
-to investigate discrete models for quantum theory and computing. Specifically,
-we start from replacing the continuum of complex numbers by the discrete
-finite fields. Although we have fruitful results on their geometric
-implications and computing powers, their probability models are still
-not completely satisfactory. To address this issue, we further exploited
-quantum interval-valued probability, and proved an imprecise version
-of foundational results such as the Gleason and Kochen-Specker theorems.}
-\abstractpage
+\abstract{Our primary research interest is to build a quantum computing
+model characterizing realistic quantum computers. While most of the
+quantum computing models based on uncomputable numbers, that is, the
+continuum of real numbers, most of the classical computers in our
+daily life are digital instead of analog computers. This highlight
+the necessity to investigate discrete models for quantum theory and
+computing. Specifically, we start from replacing the continuum of
+complex numbers by the discrete finite fields. Although we have fruitful
+results on their geometric implications and computing powers, their
+probability models are still not completely satisfactory. To address
+this issue, we further exploited quantum interval-valued probability,
+and proved an imprecise version of foundational results such as the
+Gleason and Kochen-Specker theorems.} \abstractpage
 
@@
 
-\section{Geometrical Structure of States}
+\section{Geometrical Structure of States\label{CQC1qubitBloch.sec}}
+
+Conventional quantum theory (CQT) is described by the following: 
+\begin{enumerate}
+\item[(i)] $D=2^{n}$ orthonormal basis vectors of an $n$-qubit state, 
+\item[(ii)] the normalized $D$ complex probability amplitude coefficients describing
+the contribution of each basis vector, 
+\item[(iii)] a set of probability-conserving unitary matrix operators that suffice
+to describe all required state transformations of a quantum circuit, 
+\item[(iv)] and a measurement framework. 
+\end{enumerate}
+We remark that there are many things that are assumed in CQT, such
+as the absence of zero norm states for non-zero vectors, and the decomposition
+of complex amplitudes into a pair of ordinary real numbers. One also
+typically assumes the existence of a Hilbert space with an orthonormal
+basis, allowing us to write $n$-qubit \textit{pure} states in general
+as Hilbert space vectors with an Hermitian inner product: 
+\begin{eqnarray}
+\ket{\Psi} & = & \sum_{i=0}^{D-1}\alpha_{i}\ket{i}\,.
+\end{eqnarray}
+Here $\alpha_{i}\in\mathComplex$ are complex probability amplitudes,
+$\VVec{\alpha}\in\mathComplex^{D}$, and the $\{\ket{i}\}$ is an
+orthonormal basis of states obeying 
+\begin{equation}
+\braket{i}{k}=\delta_{ik}\,,
+\end{equation}
+where $\bra{i}$ is called the dual vector of $\ket{i}$.
+
+The meaning of this is that any state $\ket{\Phi}=\sum_{i=0}^{D-1}\beta_{i}\ket{i}$
+can be projected onto another state $\ket{\Psi}$ by writing 
+\begin{eqnarray}
+\braket{\Phi}{\Psi} & = & \sum_{i=0}^{D-1}\beta_{i}^{*}\alpha_{i}\,,
+\end{eqnarray}
+thus quantifying the proximity of the two states. (Here $^{*}$ denotes
+complex conjugation.) This is one of many properties we take for granted
+in continuum quantum mechanics that challenge us in defining a discrete
+quantum geometry.
+
+In this paper, we focus on the discrete geometric issues raised by
+the properties (i) and (ii) given above for CQT, and leave for another
+time the important issues of (iii), (iv), and such conundrums as probabilities,
+zero norms, and dynamics in the theory of DQT. To facilitate the transition
+to DQT carried out in later sections, we concern ourselves first with
+the properties of the simplest possible abstract state object in CQT,
+the single qubit state.
+
+\begin{comment}
+
+\subsection{The single qubit problem}
+
+A single qubit already provides access to a wealth of geometric information
+and context. We write the single qubit state as 
+\begin{equation}
+\begin{array}{lr}
+\ket{\psi_{1}}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}\  & \ \alpha_{0},\alpha_{1}\in\C\end{array}\ .%%
+%%\alpha_{1}{array}
+\label{A1.eq}
+\end{equation}
+
+A convenience for probability calculations and a necessity for computing
+relative state properties is the normalization condition 
+\begin{equation}
+\|\psi_{1}\|^{2}=|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=\alpha_{0}^{*}\alpha_{0}+\alpha_{1}^{*}\alpha_{1}=1\ ,\label{A2.eq}
+\end{equation}
+which identifies $\alpha_{0}$ and $\alpha_{1}$ as (complex) probability
+amplitudes and implies the conservation of probability in the closed
+world spanned by $\{\ket{0},\ket{1}\}$. Note that we distinguish
+for future use the \textit{norm\/} $\|\cdot\|$ of a vector from
+the \textit{modulus\/} $|\cdot|$ of a complex number. Continuing,
+we see that if we want only the irreducible state descriptions, we
+must supplement the process of computing \Eq{A2.eq} by finding a
+way to remove the distinction between states that differ only by an
+overall phase transformation $e^{i\phi}$, that is, 
+\begin{equation}
+(\alpha_{0},\alpha_{1})\sim(e^{i\phi}\alpha_{0},e^{i\phi}\alpha_{1})\ .\label{A3.eq}
+\end{equation}
+This can be accomplished by the Hopf fibration, which we can write
+down as follows: let 
+\begin{equation}
+\begin{array}{cc}
+\alpha_{0}=x_{0}+iy_{0}, & \alpha_{1}=x_{1}+iy_{1}\end{array}\ .\label{A4.eq}
+\end{equation}
+Then \Eq{A2.eq} becomes the condition that the four real variables
+describing a qubit denote a point on the three-sphere $\Sphere{3}$
+(a 3-manifold) embedded in $\R^{4}$: 
+\begin{equation}
+x_{0}^{\ 2}+y_{0}^{\ 2}+x_{1}^{\ 2}+y_{1}^{\ 2}=1\ .\label{A5.eq}
+\end{equation}
+
+There is a family of 6 equivalence classes of quadratic maps that
+take the remaining 3 degrees of freedom in \Eq{A5.eq} and reduce
+them to 2 degrees of freedom by effectively removing $e^{i\phi}$
+(``fibering out by the circle $\Sphere{1}$''). The standard form
+of this class of maps (``the Hopf fibration'') is 
+\begin{eqnarray}
+X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\nonumber \\
+Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\\
+Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}=x_{0}^{\ 2}+y_{0}^{\ 2}-x_{1}^{\ 2}-y_{1}^{\ 2}\ .\nonumber 
+\end{eqnarray}
+These transformed coordinates obey 
+\begin{equation}
+\|\Vec{X}\|^{2}=X^{2}+Y^{2}+Z^{2}=\left(|\alpha_{0}|^{2}+|\alpha_{1}|^{2}\right)^{2}=1\label{A7.eq}
+\end{equation}
+and therefore have only two remaining degrees of freedom describing
+all possible distinct one-qubit quantum states. In Figure \ref{hopfFibers.fig}
+we illustrate schematically the family of circles \textit{each one
+of which is collapsed to a point\/} $(\theta,\phi)$ on the surface
+$X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
+
+%% (We try to list the sources of all computed figures)%% Sources for hopfFibers.fig:  dqc-geom-2012/00mathFigs/Hopf-Fiber.nb
+\begin{figure}[htb]
+\centerline{ \includegraphics[width=0.48\columnwidth,bb = 0 0 200 100, draft, type=eps]{../../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/hopfS2.pdf}\hspace{0.03in}
+\includegraphics[width=0.48\columnwidth,bb = 0 0 200 100, draft, type=eps]{../../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/hopfFibers.pdf}}
+\centerline{\hspace{1in} (a) \hfill{}(b) \hspace{1in}} \caption{(a) The sphere represented by \Eq{A7.eq}, which is the irreducible
+space of one-qubit states, along with a representative set of points
+on the sphere. (b) Representation of the Hopf fibration as a family
+of circles (the paths of $e^{i\phi}$), each corresponding to a single
+point on the sphere in (a). Points in (a) are color coded corresponding
+to circles in (b), e.g., one pole contains the red elliptical circle
+that would become an infinite-radius circle in a slightly different
+projection, and the opposite pole corresponds to the large perfectly
+round red circle at the equator.}
+\label{hopfFibers.fig} 
+\end{figure}
+
+The resulting manifold is the two-sphere $\Sphere{2}$ (a 2-manifold)
+embedded in $\R^{3}$. If we choose one of many possible coordinate
+systems describing $\Sphere{3}$ via \Eq{A5.eq} such as 
+\begin{eqnarray}
+\hspace*{-0.5cm}\left(x_{0},y_{0},x_{1},y_{1}\right) & = & \left(\cos\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\,\sin\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\ \right.\nonumber \\
+ &  & \left.\cos\frac{\theta-\phi}{2}\sin\frac{\psi}{2},\ \sin\frac{\theta-\phi}{2}\sin\frac{\psi}{2}\right),\label{A8a.eq}
+\end{eqnarray}
+where %% $0\leq \theta \leq 2 \pi$,  $-\pi \leq \phi \leq  \pi$, 
+$0\leq\psi\leq\pi$, with $0\leq\frac{\theta+\phi}{2}<2\pi$ and $0\leq\frac{\theta-\phi}{2}<2\pi$,
+we see that 
+\begin{eqnarray}
+\left(X,Y,Z\right)=\left(\cos\phi\sin\psi,\,\sin\phi\sin\psi,\,\cos\psi\right)\ .\label{A8b.eq}
+\end{eqnarray}
+Thus the one-qubit state is independent of $\theta$, and we can choose
+$\theta=\phi$ without loss of generality, reducing the form of the
+unique one-qubit states to 
+\begin{equation}
+\ket{\psi_{1}}=e^{i\phi}\cos\frac{\psi}{2}\ket{0}+\sin\frac{\psi}{2}\ket{1}\ ,\label{A9.eq}
+\end{equation}
+and an irreducible state can be represented as a point on a sphere,
+as shown in Figure \ref{blochSphere.fig}(a).
+
+\begin{figure}[thb]
+\begin{centering}
+\includegraphics[width=0.47\columnwidth,bb = 0 0 200 100, draft, type=eps]{../../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/blochSphere.pdf}
+\hspace{0.01in} \includegraphics[width=0.47\columnwidth,bb = 0 0 200 100, draft, type=eps]{../../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/blochSphereArc.pdf} 
+\par\end{centering}
+\centerline{\hspace{1in} (a) \hfill{}(b) \hspace{1in}} \caption{(a) The conventional Bloch sphere with a unique state represented
+by the point at the red sphere. (b) The geodesic shortest-distance
+arc connecting two one-qubit quantum states.}
+\label{blochSphere.fig} 
+\end{figure}
+
+Thus the geometry of a single qubit reduces to transformations among
+points on $\Sphere{2}$, which can be parametrized in an infinite
+one-parameter family of transformations, one of which is the geodesic
+or minimal-length transformation. Explicitly, given two one-qubit
+states denoted by points $\Vec{a}$ and $\Vec{b}$ on $\Sphere{2}$,
+the shortest rotation carrying the unit normal $\Hat{a}$ to the unit
+normal $\Hat{b}$ is the SLERP (spherical linear interpolation) 
+\begin{equation}
+S(\Hat{a},\Hat{b},t)=\Hat{a}\,\frac{\sin((1-t)\theta)}{\sin\theta}\,+\,\Hat{b}\,\frac{\sin(t\theta)}{\sin\theta}\ ,\label{slerp.eq}
+\end{equation}
+where $\Hat{a}\cdot\Hat{b}=\cos\theta$. Figure \ref{blochSphere.fig}(b)
+illustrates the path traced by a SLERP between two irreducible one-qubit
+states on the Bloch sphere. Because states in CQC are defined by infinite
+precision real numbers, it is not possible, even in principle, to
+make an exact state transition as implied by Figure \ref{blochSphere.fig}(b).
+In practice, one has to be content with approximate, typically exponentially
+expensive, transitions from state to state.
+
+%% AMR: replaced ', probabilistic, exponentially complex transitions from%% state to state' with the above
+
+\subsection{The $n$-qubit problem}
+
+For $n$ qubits, the irreducible states are encoded in a similar family
+of geometric structures known technically as the complex projective
+space $\CP{D-1}$. We obtain these structures starting with the $D=2^{n}$
+initially unnormalized complex coefficients of the $n$-qubit state
+basis 
+\begin{eqnarray}
+\ket{\Psi} & = & \sum_{i=0}^{D-1}\alpha_{i}\ket{i}\ .\label{N1.eq}
+\end{eqnarray}
+We then follow the analog of the one-qubit procedure: Conservation
+of probability requires that the norm of the vector $\VVec{\alpha}$
+be normalized to unity: 
+\begin{eqnarray}
+\braket{\Psi}{\Psi}=\|\VVec{\alpha}\|^{2} & = & \sum_{i=0}^{D-1}|\alpha_{i}|^{2}\,=\,1\ .\label{probEq1.eq}
+\end{eqnarray}
+Thus the initial equation for the geometry of a quantum state describes
+a \textit{topological sphere\/} $\Sphere{2D-1}$ embedded in $\mathReal^{2D}$.
+To see this, remember that we can write the real and imaginary parts
+of $\alpha_{i}$ as $\alpha_{i}=x_{i}+iy_{i}$, so 
+\begin{eqnarray}
+\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=\sum_{i=0}^{D-1}\left(x_{i}^{\ 2}+y_{i}^{\ 2}\right)=1
+\end{eqnarray}
+describes the locus of a $2D$-dimensional real unit vector in $\mathReal^{2D}$,
+which is by definition $\Sphere{2D-1}$, the $(2D-1)$-sphere, with
+$D=2^{n}$ for an $n$-qubit state.
+
+This $\Sphere{2D-1}$ in turn is ambiguous up to the usual overall
+phase, inducing an $\Sphere{1}$ symmetry action, and identifying
+$\Sphere{2D-1}$ as an $\Sphere{1}$ bundle, whose base space is the
+$(D-1)$-complex-dimensional projective space $\CP{D-1}$. There are
+thus $2D-2$ irreducible real degrees of freedom ($D-1$ complex degrees
+of freedom) for a quantum state with a $D$-dimensional basis, $\{\ket{i}\,|\,i=0,\ldots,D-1\}$.
+
+In summary, the full space of a $D=2^{n}$-dimensional $n$-qubit
+quantum state, including its overall phase defining its relationship
+to other quantum states, is the topological space $\Sphere{2D-1}$.
+For an isolated system, the overall phase is not measurable, and eliminating
+the phase dependence in turn corresponds to identifying $\Sphere{2D-1}$
+as a circle bundle over the base space $\CP{D-1}$, and therefore
+$\CP{D-1}=\CP{2^{n}-1}$ defines the $2D-2$ intrinsic, irreducible,
+degrees of freedom of the isolated $n$-qubit state's dynamics. In
+mathematical notation, this would be written
+
+%% From Wiki: Hopf-fibration: S^1\hookrightarrow S^3 \rightarrow S^2
+\[
+\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}\ ,
+\]
+with $D=2^{n}$ as usual. For $n=1$, the single qubit, we have $2^{n}-1=2-1=1$,
+and the base space of the circle bundle is $\CP{1}=\Sphere{2}$, the
+usual Bloch sphere. Note that only for $n=1$ is this actually a sphere-like
+geometry due to an accident of low-dimensional topology.
+
+\subsection{Explicit $n$-qubit generalization of the Hopf fibration construction}
+
+For one qubit, we could easily solve the problem of reducing the full
+unit-norm space to its irreducible components $\Vec{X}=(X,Y,Z)$ characterizing
+the Bloch sphere. We have just argued that essentially the same process
+is possible for $n$-qubits: in the abstract argument, we simply identify
+the family of coefficients $\{\alpha_{i}\}$ as being the same if
+they differ only by an overall phase $e^{i\phi}$. However, in practice
+this is not a construction that is easy to realize in a practical
+computation. We now outline an explicit algorithm for accomplishing
+the reduction to the irreducible $n$-qubit state space $\CP{D-1}$;
+this construction will turn out to be useful for the validation of
+our discrete results to follow below.
+
+We begin by noting that a natural quantity characterizing an $n$-qubit
+system is its \textit{density matrix\/}, $\rho=\left[\alpha_{i}\alpha_{j}^{*}\right]$,
+or 
+\begin{equation}
+\rho=\left[\begin{array}{cccc}
+|\alpha_{0}|^{2} & \alpha_{0}\alpha_{1}^{*} & \cdots & \alpha_{0}\alpha_{D-1}^{*}\\
+\alpha_{1}\alpha_{0}^{*} & |\alpha_{1}|^{2} & \cdots & \alpha_{1}\alpha_{D-1}^{*}\\
+\vdots & \vdots & \ddots & \vdots\\
+\alpha_{D-1}\alpha_{0}^{*} & \cdots & \alpha_{D-1}\alpha_{D-2}^{*} & |\alpha_{D-1}|^{2}
+\end{array}\right]\ .\label{nqDensity.eq}
+\end{equation}
+
+We can now use the complex generalization of the classical Veronese
+coordinate system for projective geometry to remove the overall phase
+ambiguity $e^{i\phi}$ from the $n$-qubit states. If we take a particular
+weighting of the elements of the density matrix $\rho$, we can construct
+a \textit{unit vector\/} of real dimension $D^{2}$ with the form:
+\begin{equation}
+\Vec{X}=(|\alpha_{i}|^{2},\ldots,\sqrt{2}\,\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\,\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots)\ ,\label{nqCoords.eq}
+\end{equation}
+where 
+\begin{eqnarray}
+\Vec{X}\cdot\Vec{X}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
+\end{eqnarray}
+This construction gives an explicit embedding of the $(D-1)$-dimensional
+complex, or $(2D-2)=(2^{n+1}-2)$-dimensional real, object in a real
+space of dimension $D^{2}=2^{2n}$. However, this is somewhat subtle
+because the vector is of unit length, so technically the embedding
+space is a sphere of dimension $D^{2}-1=2^{2n}-1$ embedded in $\R^{D^{2}}$;
+the one-qubit irreducible states could be represented in a 4D embedding,
+but the magnitude of every coordinate would be one; furthermore, the
+object embedded in the resulting $\Sphere{3}$ is indeed $\Sphere{2}$
+because we can fix one complex coordinate to be unity, and let one
+vary, giving a total of two irreducible dimensions. In fact one must
+choose \textit{two\/} coordinate patches, one covering one pole of
+$\Sphere{2}$ with coordinates 
+\begin{eqnarray}
+\begin{array}{ccc}
+\alpha_{0} & = & 1+0i\\
+\alpha_{1} & = & x_{1}+iy_{1}
+\end{array}
+\end{eqnarray}
+and the other patch covering the other pole of $\Sphere{2}$ with
+coordinates 
+\begin{eqnarray}
+\begin{array}{ccc}
+\alpha_{0} & = & x_{0}+iy_{0}\\
+\alpha_{1} & = & 1+0i\ .
+\end{array}
+\end{eqnarray}
+
+We finally see that the irreducible $n$-qubit state space $\CP{D-1}$
+is described by $D$ projectively equivalent coordinates, one of which
+can always be scaled out to leave $(D-1)$ actual (complex) degrees
+of freedom. We must choose, in turn, $D$ different local sets of
+complex variables defined by taking the value $\alpha_{k}=1$, with
+$k=0,\ldots,D-1$, and allowing the remaining $D-1$ complex (or $2D-2$
+real) variables to run free. No single set of coordinates will work,
+since the submanifold including $\alpha_{k}=0$ is undefined and another
+coordinate system must be chosen to cover that coordinate patch. This
+is a standard feature of the topology of non-trivial manifolds such
+as $\CP{D-1}$ (see any textbook on geometry \cite{Berger}).
+
+\subsection{The geometry of entanglement}
+
+Entanglement may be regarded as one of the main characteristics distinguishing
+quantum from classical mechanics. Entanglement involves quantum correlations
+such that the measurement outcomes in one subsystem are related to
+the measurement outcomes in another one. Within the standard framework,
+given a quantum system composed of $n$ qubit subsystems, a pure state
+of the total system $\ket{\Psi}$ is said to be entangled if it cannot
+be written as a product of states of each subsystem. That is, a state
+$\ket{\Psi}$ is entangled if 
+\begin{eqnarray}
+\ket{\Psi}\ne\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}},
+\end{eqnarray}
+where $\ket{\psi_{j}}$ refers to an arbitrary state of the $j$-th
+qubit, and $\otimes$ represents the tensor product. This is equivalent
+to saying that if one calculates the reduced density operator $\rho_{j}$
+of the $j$th subsystem by tracing out all the other subsystems, $\rho_{j}={\sf tr}_{\{1,\cdots,j-1,j+1,\cdots,n\}}(\rho)$,
+with $j=1,\cdots,n$ and $\rho=\ket{\Psi}\bra{\Psi}$, the normalized
+state $\ket{\Psi}$, $\langle\Psi|\Psi\rangle=1$, is entangled if
+and only if at least one subsystem state is \textit{mixed\/}; i.e.,
+${\sf tr}_{j}(\rho_{j}^{2})<1$. For example, consider 
+\begin{eqnarray}
+\rho_{j}=\frac{1}{2}(\mathds{1}+\sum\limits _{\mu=x,y,z}\langle\sigma_{\mu}^{j}\rangle\ \sigma_{\mu}^{j}),
+\end{eqnarray}
+where $\sigma_{\mu}^{j}$, $\mu=x,y,z$, are the Pauli operators acting
+on the $j$-th spin, 
+\begin{equation}
+\sigma_{\mu}^{j}=\overbrace{\mathds{1}\otimes\mathds{1}\otimes\cdots\otimes\underbrace{\sigma_{\mu}}_{j^{th}\ \mbox{factor}}\otimes\cdots\otimes\mathds{1}}^{n\ \mbox{factors}}\;,\label{pauli3}
+\end{equation}
+with 
+\begin{eqnarray}
+\hspace*{-0.5cm}\sigma_{x}=\left(\begin{array}{cc}
+0 & 1\\
+1 & 0
+\end{array}\right),\sigma_{y}=\left(\begin{array}{cc}
+0 & -i\\
+i & 0
+\end{array}\right),\sigma_{z}=\left(\begin{array}{cc}
+1 & 0\\
+0 & -1
+\end{array}\right),
+\end{eqnarray}
+and $\langle\sigma_{\mu}^{j}\rangle=\langle\Psi|\sigma_{\mu}^{j}|\Psi\rangle$
+denotes the corresponding expectation value. The vectors ${\bf X}_{j}=(\langle\sigma_{x}^{j}\rangle,\langle\sigma_{y}^{j}\rangle,\langle\sigma_{y}^{j}\rangle)$,
+${\bf X}_{j}\in{\mathbb{R}}^{3}$, allow a geometric representation
+of each reduced state in ${\mathbb{R}}^{3}$, satisfying $0\le\|{\bf X}_{j}\|\le1$.
+Since ${\sf tr}_{j}(\rho_{j}^{2})=\frac{1}{2}(1+\|{\bf X}_{j}\|^{2})$,
+the state $\ket{\Psi}$ is entangled if $\|{\bf X}_{j}\|<1$ for at
+least one $j$, represented by a point {\em inside} the corresponding
+local Bloch sphere. One may therefore consider $\ket{\Psi}$ to be
+maximally entangled if $\|{\bf X}_{j}\|=0$ for all $j$. On the other
+hand, the state $\ket{\Psi}$ is unentangled (i.e., a product state)
+if $\|{\bf X}_{j}\|=1$ for all $j$, corresponding to points lying
+on the surface of the Bloch sphere.
+
+A natural geometric measure of multipartite entanglement is obtained
+by defining the {\em purity of a state relative to a set of observables}
+\cite{Barnum2003,Barnum2004}. If the set is chosen to be the set
+of {\em all local observables}, i.e., corresponding to each of
+the subsystems that compose the actual system, one recovers the standard
+notion of entanglement for multipartite systems. For example, if the
+system consists of $n$ qubits, we obtain a measure of conventional
+entanglement by calculating the purity relative to the set $\fh=\{\sigma_{x}^{1},\sigma_{y}^{1},\sigma_{z}^{1},\ldots,\sigma_{x}^{n},\sigma_{y}^{n},\sigma_{z}^{n}\}$,
+\begin{equation}
+P_{\fh}=\frac{1}{n}\sum\limits _{j=1}^{n}\sum\limits _{\mu=x,y,z}\langle\sigma_{\mu}^{j}\rangle^{2}\:,\ \ 0\leq P_{\fh}\leq1\ .\label{purityMeasure.eq}
+\end{equation}
+Since $\fh$ is a semi-simple Lie algebra, its generalized unentangled
+states are the generalized coherent states obtained by applying any
+group operation to a reference state such as $\ket{\sf0}=\ket{0}\otimes\cdots\otimes\ket{0}$.
+For the algebra $\fh$ of local observables, such group operations
+are simply local rotations on each qubit. In other words, the group
+orbit describing the generalized coherent states of $\fh$ comprises
+all the product states of the form $\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{n}}$,
+which have maximum purity (i.e., $P_{\fh}=1$). Other states such
+as the Greenberger-Horne-Zeilinger state $\ket{\Psi}=\ket{{\sf GHZ}_{n}}=\frac{1}{\sqrt{2}}(\ket{0}\otimes\cdots\otimes\ket{0}+\ket{1}\otimes\cdots\otimes\ket{1})$
+are (maximally) entangled relative to the set of local observables
+(i.e., $P_{\fh}=0$).
+
+Different entanglement measures are obtained when a set $\fh$ different
+from the local observables is chosen. An obvious example, in particular,
+is given by the set of all observables. In this case, the purity takes
+its maximum value independently of the pure quantum state \cite{Barnum2003,Barnum2004},
+expressing the fact that any state is a generalized coherent state
+of the Lie algebra of all observables.
+\end{comment}
 
@@
 with any given quantum probability measure.
+
+\section{Quantum Contextuality}
 
@@
 that the field has characteristic zero (which is the case for $\mathbb{R}$
-for example). It turns out that if the characteristic is non-zero
+for example). It turns out that if the characteristic is non-zero,
 it must be a prime~$p$. For every prime~$p$ and positive integer~$r$
@@
 \section{Modal Quantum Theory\label{modalquantum}}
+
+Recently, Schumacher and Westmoreland~\cite{Schumacher2012-SCHMQT,SchumacherWestmoreland2010}
+and Chang et al.~\cite{doi:10.1142/S0217984913500644,1751-8121-47-40-405304}
+defined versions of quantum theory over \textit{unrestricted} finite
+fields, which they call modal quantum theories (MQT) or Galois field
+quantum theories. Such theories retain several key quantum characteristics
+including notions of superposition, interference, entanglement, and
+mixed states, along with time evolution using invertible linear operators,
+complementarity of incompatible observables, exclusion of local hidden
+variable theories, impossibility of cloning quantum states, and the
+presence of natural counterparts of quantum information protocols
+such as superdense coding and teleportation. These modal theories
+are obtained by collapsing the Hilbert space structure over the field
+of complex numbers to that of a vector space over an \emph{unrestricted}
+finite field. In the resulting structure, all non-zero vectors represent
+valid quantum states, and the evolution of a closed quantum system
+is described by \emph{arbitrary} invertible linear maps.
+
+Specifically, consider a one-qubit system with basis vectors $\ket{0}$
+and~$\ket{1}$. In conventional quantum theory, there exists an infinite
+number of states for a qubit of the form $\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$,
+with $\alpha_{0}$ and $\alpha_{1}$ elements of the underlying field
+of complex numbers subject to the normalization condition $|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=1$.
+Moving to a finite field immediately limits the set of possible states
+as the coefficients~$\alpha_{0}$ and~$\alpha_{1}$ are now drawn
+from a finite set. In particular, in the field $\ff{2}=\{0,1\}$ of
+booleans, there are exactly four possible vectors: the zero vector,
+the vector~$\ket{0}$, the vector $\ket{1}$, and the vector $\ket{0}+\ket{1}=\ket{+}$,
+where $\left\{ \ket{0},\ket{1},\ket{+}\right\} $ is denoted as $\ffzx{2}{2}$.
+Since the zero vector is considered non-physical, a one-qubit system
+can be in one of only three states. The dynamics of these one-qubit
+states is realized by any invertible linear map, i.e., by any linear
+map that is guaranteed never to produce the zero vector from a valid
+state. There are exactly $6$ such maps: 
+\begin{equation}
+\begin{aligned}X_{0} & =\begin{pmatrix}1 & 0\\
+0 & 1
+\end{pmatrix}\,, & S & =\begin{pmatrix}1 & 0\\
+1 & 1
+\end{pmatrix}\,, & D_{1} & =\begin{pmatrix}0 & 1\\
+1 & 1
+\end{pmatrix}\,,\\
+X_{1} & =\begin{pmatrix}0 & 1\\
+1 & 0
+\end{pmatrix}\,, & S^{\dagger} & =\begin{pmatrix}1 & 1\\
+0 & 1
+\end{pmatrix}\,, & D_{2} & =\begin{pmatrix}1 & 1\\
+1 & 0
+\end{pmatrix}\,.
+\end{aligned}
+\end{equation}
+This set of maps is clearly quite impoverished compared to the full
+set of one-qubit unitary maps in conventional quantum theory. In particular,
+it does not include the Hadamard transformation. However, this set
+also includes non-unitary maps such as $S$ and $S^{\dagger}$ that
+are not allowed in conventional quantum computation.
+
+Measurement in the standard basis is fairly straightforward: measuring
+$\ket{0}$ or $\ket{1}$ deterministically produces the same state
+while measuring $\ket{+}$ nondeterministically produces $\ket{0}$
+or $\ket{1}$ with no assigned probability distribution. When measuring
+an arbitrary state~$\ket{\phi}$ in other bases $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} $,
+we first represents $\ket{\phi}$ as the linear combination of the
+basis vectors $\beta_{0}\ket{\psi_{0}}+\beta_{1}\ket{\psi_{1}}$,
+and measuring $\ket{\phi}$ is impossible to produce $\ket{\psi_{i}}$
+if $\beta_{i}$ is zero, and is possible to produce $\ket{\psi_{i}}$
+if $\beta_{i}$ is non-zero. Since only possibility and impossibility
+is predicted by the theory, the modal quantum theories is named after
+these “modal” concepts.
+
+Notice that the measurement process is complicated by the fact that
+the possibility to produce a basis vector~$\ket{\psi_{i}}$ depending
+on the measurement basis. This is one step further than the usual
+CQT, where the probability to produce a basis vector~$\ket{\psi_{i}}$
+measuring a state~$\ket{\phi}$ is completely determined by the inner
+products between $\ket{\psi_{i}}$ and $\ket{\phi}$; only when simulating
+the measurement results by a deterministic hidden variable theory,
+other measurement basis vectors effects the measurement results. Despite
+this kind of ``supercontextuality,'' its computational model, modal
+quantum computing (MQC), having ``supernatural'' computational power
+is also far from conventional quantum computing as we will describe
+next.
+
+\begin{comment}
+
+\section{Modal Quantum Computing}
+
+\label{modalquantumcomputing}
+
+To understand the computational implications of the modal quantum
+theory defined over the field $\ff{2}$ of booleans, we developed
+a quantum computing model and established its correspondence to a
+classical model of logical programming with a feature that has quantum-like
+behavior~\cite{qc-rel}. In a conventional logic program, answers
+produced by different execution paths are collected in a sequence
+with \emph{no} interference. However, in this modal quantum computing
+model over $\ff{2}$, these answers may interfere destructively with
+one another.
+
+Our computations with this ``toy'' modal quantum theory showed that
+it possesses ``supernatural'' computational power. For example,
+one can solve a black box version of the \usat\ problem~\cite{wsusat}
+in a way that outperforms conventional quantum computing. The classical
+\usat\ problem (also known as \texttt{USAT} or \texttt{UNAMBIGUOUS-SAT})
+is the problem of deciding whether a given boolean formula has a satisfying
+assignment, assuming that it has at most one such assignment~\cite{complexity}.
+This problem is, in a precise sense~\cite{Valiant198685}, just as
+hard as the general satisfiability problem and hence all problems
+in the~NP complexity class. Our black-box version of the \usat\ problem
+replaces the boolean formula with an arbitrary black box. Solutions
+to this generalized problem can be used to solve an unstructured database
+search of size $N$ using $O(\log{N})$ black box evaluations by binary
+search on the database. This algorithm then outperforms the known
+asymptotic bound $O(\sqrt{N})$ for unstructured database search in
+conventional quantum computing.
+
+\begin{figure}[t]
+\[
+\begin{array}{@{\!\!}c}
+\hspace*{1.35cm}\Qcircuit@C=1.3em@R=.9em{\lstick{y=\ket{0}}}\end{array}
+\]
+\caption[]{\label{fig:alg}Circuit for black box \usat\ in modal quantum theory
+over the field $\ff{2}$. $\uf$ is a Deutsch quantum black box~\cite{NCbook}
+with $\uf\ket{y}\ket{\overline{x}}~=~\ket{y\scalarPlus f(\overline{x})}\ket{\overline{x}}$,
+where $\overline{x}$ denotes a sequence $x_{1},x_{2},\ldots,x_{n}$
+of $n$ bits. For further notation see text.}
+\end{figure}
+
+We can prove the unreasonable power of the arbitrary-function \usat\ starting
+with a classical function $f:\boolt^{n}\rightarrow\boolt$ that takes
+$n$ bits and returns at most one \btrue\ result. Then we can give
+an algorithm (see Fig.~\ref{fig:alg}) taking as input such a classical
+function that decides, deterministically and in a constant number
+of black box evaluations, whether $f$ is satisfiable or not:
+
+\paragraph*{Case I: $f$ is unsatisfiable; the measurement deterministically
+produces $\ket{0}\ket{\overline{0}}$.}
+
+The state is initialized to $\ket{0}\ket{\overline{0}}$, with $\ket{\overline{0}}=\ket{0}\ket{0}\cdots\ket{0}$,
+i.e., the tensor product of $n$ $\ket{0}$ states. Applying the map
+$S$ (defined in the previous section) to each qubit in the second
+component of the state produces $\ket{0}\ket{\overline{+}}$ where
+$\ket{\overline{+}}$ denotes the sequence $\ket{+}\ldots\ket{+}$
+of length $n$. Applying $\uf$ to the entire state has no effect
+since $U_{f}$ is the identity when $f$ is unsatisfiable. Applying
+$S$ to each qubit in the second component of the state produces $\ket{0}\ket{\overline{0}}$.
+Applying $S^{\dagger}$ to the first component leaves the state unchanged.
+As the first component of the state is 0, applying the map $X_{0}$
+(which is the identity) leaves the state unchanged. Applying $S^{\dagger}$
+to the first component leaves the state unchanged. Measuring the state
+will deterministically produce $\ket{0}\ket{\overline{0}}$.
+
+\paragraph*{Case II: $f$ is satisfiable; the measurement produces some state
+other than $\ket{0}\ket{\overline{0}}$.}
+
+Assume the function $f$ is satisfiable at some input $a_{1},a_{2},\ldots,a_{n}$
+denoted $\overline{a}$, and where $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$.
+In the second step, the state becomes $\ket{0}\ket{\overline{+}}$
+as above. We can write this state as $\ket{0}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
+Applying $U_{f}$ produces $\ket{1}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
+We can rewrite this state as $\ket{+}\ket{\overline{a}}+\Sigma_{\overline{x}}\ket{0}\ket{\overline{x}}=\ket{+}\ket{\overline{a}}+\ket{0}\ket{\overline{+}}$,
+where the summation is now over all vectors (notice that $\ket{0}\ket{\overline{a}}+\ket{0}\ket{\overline{a}}$
+is the zero vector). Applying $S$ to each qubit in the second component
+produces $\ket{+}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
+Applying $S^{\dagger}$ to the first component produces: $\ket{1}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
+Applying $X_{b}$, where $b$ is the first component of the state,
+to each qubit in the second component produces $\ket{1}\ket{\overline{{\sf not}(S(a))}}+\ket{0}\ket{\overline{0}}$.
+Applying $S^{\dagger}$ to the first component produces $\ket{+}\ket{\overline{{\sf not}(S(a))}}+\ket{0}\ket{\overline{0}}$.
+For the measurement of $\ket{+}\ket{\overline{{\sf not}(S(a))}}+\ket{0}\ket{\overline{0}}$
+to be guaranteed to never be $\ket{0}\ket{\overline{0}}$, we need
+to verify that $\ket{+}\ket{\overline{{\sf not}(S(a))}}$ has one
+occurrence $\ket{0}\ket{\overline{0}}$. This can be easily proved
+as follows. Since each $a_{i}$ is either 0 or 1, then each $S(a_{i})$
+is either $+$ or $1$, and hence each ${\sf not}(S(a_{i}))$ is either~$+$
+or~$0$. The result follows since any state with a combination of
+$+$ and $0$, when expressed in the standard basis, would consist
+of a superposition containing the state $\ket{0\ldots}$.
+
+%% WE have a problem with notation - what do we use for "dot product"
+%%  and/or "field norm" in the three or four instances below.
+%%  Here is Yu-Tsung's comment:
+
+% Actually, Grove didn't told about any quadratic residues, and didn't
+% defined the field norm. Grove 
+%  used "the quadratic form Q corresponding to a Hermitian form" instead
+% of "field norm." When I wrote 
+% this proof, I really read the following books:
+% [12] Stewart I 2004 Galois theory (Boca Raton: Chapman and Hall/CRC).
+% Field norm defined in almost all field theory books. In particular, in
+% page 197 in Section 18.4  [12].
+% [11] Hardy G H and Wright E M 1938 An Introduction to the Theory of
+% Numbers (Oxford: Oxford University Press).
+% Quadratic residues explained in almost all number theory books. In
+% particular, in page 69 in Chapter VI [11].
+%%  HERMITIAN (outside if needed) \define{dotprod}{dot product}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discrete Quantum Theory (I) }
+
+\label{discretequantumtheoryI}
+
+Our next objective is to develop more realistic discrete quantum theory
+variants that exclude ``supernatural'' algorithms such as the one
+presented above. Our first such plausible framework~\cite{powerdqc}
+is based on complexifiable finite fields. To incorporate complex numbers
+for quantum amplitudes, we exploit the fact that the polynomial $x^{2}+1=0$
+is \emph{irreducible} (has no solution) over a prime field $\ff{p}$
+with $p$ odd if and only if $p$ is of the form~$4\ell+3$, with
+$\ell$ a non-negative integer. In other words, $x^{2}+1=0$ is irreducible
+over $\ff{3},\ff{7},\ff{11},\ff{19},\ldots$. We achieve our goal
+by observing that any field in this family is extensible to a field~$\ff{p^{2}}$
+whose elements can be viewed as discrete complex numbers with the
+real and imaginary parts in~$\ff{p}$. In the field~$\ff{p^{2}}$,
+the Frobenius automorphism of an element $\alpha$ (defined as $\alpha^{p}$)
+represents the usual definition of complex conjugation~\cite{fieldexample}.
+
+The next task is to examine the consequences when we attempt to construct
+$d$-dimensional vector spaces over the complexified fields $\ff{p^{2}}$
+\cite{geom1}. (For readability, instead of writing column vectors,
+we will often use the vector notation $\ket{\Psi}=(\alpha_{0}~\alpha_{1}~\ldots~\alpha_{d-1})^{T}$
+and $\ket{\Phi}=(\beta_{0}~\beta_{1}~\ldots~\beta_{d-1})^{T}$, where
+$(.)^{T}$ is the transpose of the \textit{row} vector $(.)$.) It
+can be shown~\cite{HermitianProd} that, given two vectors 
+\begin{equation}
+\ket{\Psi}=\sum_{i=0}^{d-1}~\alpha_{i}\ket{i}\ ,\ \ket{\Phi}=\sum_{i=0}^{d-1}~\beta_{i}\ket{i},
+\end{equation}
+with scalars $\alpha_{i}$ and $\beta_{i}$ drawn from the field elements,
+and orthonormal basis $\{\ket{i}\}$, the Hermitian \dotprod\ is
+always reducible to the form \vspace{-0.1in}
+
+\begin{equation}
+\ip{\Phi}{\Psi}=\sum_{i=0}^{d-1}~\beta_{i}^{p}~\alpha_{i}^{\;}\ .\vspace{-0.1in}\label{innerprod}
+\end{equation}
+
+This product satisfies conditions A and B below, but not~C, because
+in a finite field, addition can ``wrap around,'' making the concepts
+of positive and negative meaningless and allowing the sum of non-zero
+elements to be zero: 
+\begin{itemize}
+\item A. $\ip{\Phi}{\Psi}$ is the complex conjugate of $\ip{\Psi}{\Phi}$;
+\vspace*{-0.25cm}
+
+\item B. $\ip{\Phi}{\Psi}$ is conjugate linear in its first argument and
+linear in its second argument; \vspace*{-0.25cm}
+
+\item C. $\ip{\Psi}{\Psi}$ is always non-negative and is equal to~0 only
+if $\ket{\Psi}$ is the zero vector. 
+\end{itemize}
+With just conditions A and B, it is possible to recover unitary operators,
+and thus recover much of the relevant structure of Hilbert spaces
+over the field of complex numbers. The failure of condition C, however,
+plays havoc with the traditional notions of ordered probabilities
+as well as the geometric notions of ordered distances and angles,
+whose lengths and cosines, respectively, are normally expressed using
+the inner product~\cite{geom}. In a separate development, we explore
+the geometry of these finite fields and define a discrete version
+of the Hopf fibration extending the Bloch sphere to $n$-qubits, as
+well as determining discrete measures for the relative sizes of the
+entangled, maximally entangled, and unentangled discrete states~\cite{geom1}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\emph{Discrete Quantum Computing with Complexifiable Finite Fields. }
+%% NOTE (ajh): we decided Fp was complexifiable and Fpp was complexified.
+
+\section{Discrete Quantum Computing (I)}
+
+\label{discretequantumcomputingI}
+
+Given a complexified finite field $\ff{p^{2}}$ and its Hermitian
+\dotprod\
+(Eq.~\eqref{innerprod}) much of the structure of conventional quantum
+computing can be recovered. For example, the smallest field~$\ff{3^{2}}$
+is already rich enough to express the standard Deutsch-Jozsa~\cite{NCbook}
+algorithm, which requires only normalized versions of vectors or matrices
+with the scalars $0$, $1$, and $-1$. Similarly, other deterministic
+quantum algorithms (algorithms for which we may determine the outcome
+with certainty), such as Simon's and Bernstein-Vazirani, perform as
+desired~\cite{simon}. Algorithms such as Grover's search will not
+work in the usual way because we lack (the notion of) ordered angles
+and probability in general.
+
+\begin{figure}[t]
+\[
+\begin{array}{c}
+\hspace*{1.5cm}\Qcircuit@C=1.7em@R=.9em{\lstick{y=\ket{0}}}\end{array}
+\]
+\caption[]{Circuit for black box \usat\ in discrete quantum computing.}
+
+\label{fig:dbsearch} 
+\end{figure}
+
+It is possible, in some situations, to exploit the cyclic behavior
+of the field to creatively cancel probability amplitudes and solve
+problems with what again appears to be ``supernatural'' efficiency.
+We illustrate this behavior with the algorithm in Fig.~\ref{fig:dbsearch},
+which is a variant of the one in Fig.~\ref{fig:alg}. Unlike the
+modal quantum theory algorithm, the new algorithm does not always
+succeed deterministically using a constant number of black box evaluations.
+We can, however, show that supernatural behavior occurs if the characteristic
+$p$ of the field divides $2^{N}-1$. For a database of fixed size
+$N$, matching the conditions becomes less likely as the size of the
+field increases. Nevertheless, for a \textit{given\/} field, it is
+always possible to expand any database with dummy records to satisfy
+the divisibility property. Physically, we are taking advantage of
+additional interference processes that happen because of the possibility
+of ``wrapping around'' due to modular arithmetic. We do not know,
+in general, whether this version of discrete quantum computing actually
+enables the rapid solution of NP-complete problems.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%  Since forging a connection between  
+% a framework for discrete quantum computing based on complexifiable
+% finite fields and conventional quantum mechanics is blocked in the
+% general case by the violation of condition (C) on inner products, the
+% only logical alternative is to seek a way around the impasse.
+\end{comment}
 
@@
 
-\addcontentsline{toc}{chapter}{Bibliography}
+\addcontentsline{toc}{chapter}{Bibliography} %
 \begin{comment}
@@
 % http://latex.org/forum/viewtopic.php?t=17956
-\addtocontents{toc}{\noindent\contentsline{chapter}{Curriculum Vitae}{}}
+\addtocontents{toc}{\contentsline{chapter}{Curriculum Vitae}{}}
 \includepdf[pages=-]{CV_thesis} 

### 2018-02-25 dissertation.tex
dissertation.lyx 3.2 Modal Quantum Theory Updating...

@@
 booleans, there are exactly four possible vectors: the zero vector,
-the vector~$\ket{0}$, the vector $\ket{1}$, and the vector $\ket{0}+\ket{1}=\ket{+}$,
-where $\left\{ \ket{0},\ket{1},\ket{+}\right\} $ is denoted as $\ffzx{2}{2}$.
+the vector~$\ket{0}$, the vector $\ket{1}$, and the vector $\ket{0}+\ket{1}=\ket{+}$.
 Since the zero vector is considered non-physical, a one-qubit system
@@
 while measuring $\ket{+}$ nondeterministically produces $\ket{0}$
-or $\ket{1}$ with no assigned probability distribution. When measuring
-an arbitrary state~$\ket{\phi}$ in other bases $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} $,
+or $\ket{1}$ with no assigned probability distribution, . When measuring
+an arbitrary state~$\ket{\phi}\in\left\{ \ket{0},\ket{1},\ket{+}\right\} $
+in other bases $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} $,
 we first represents $\ket{\phi}$ as the linear combination of the
 basis vectors $\beta_{0}\ket{\psi_{0}}+\beta_{1}\ket{\psi_{1}}$,
-and measuring $\ket{\phi}$ is impossible to produce $\ket{\psi_{i}}$
-if $\beta_{i}$ is zero, and is possible to produce $\ket{\psi_{i}}$
-if $\beta_{i}$ is non-zero. Since only possibility and impossibility
+where $\beta_{0}$ and $\beta_{1}$ are elements in the field~$\ff{2}$.
+If $\beta_{i}$ is zero, measuring $\ket{\phi}$ is impossible to
+produce $\ket{\psi_{i}}$; otherwise, measuring $\ket{\phi}$ is possible
+to produce $\ket{\psi_{i}}$. Since only possibility and impossibility
 is predicted by the theory, the modal quantum theories is named after
@@
 the possibility to produce a basis vector~$\ket{\psi_{i}}$ depending
-on the measurement basis. This is one step further than the usual
-CQT, where the probability to produce a basis vector~$\ket{\psi_{i}}$
-measuring a state~$\ket{\phi}$ is completely determined by the inner
-products between $\ket{\psi_{i}}$ and $\ket{\phi}$; only when simulating
-the measurement results by a deterministic hidden variable theory,
-other measurement basis vectors effects the measurement results. Despite
-this kind of ``supercontextuality,'' its computational model, modal
-quantum computing (MQC), having ``supernatural'' computational power
-is also far from conventional quantum computing as we will describe
-next.
+on the measurement basis. For example, measuring $\ket{+}$ is possible
+to produce $\ket{0}$ in the standard basis $\left\{ \ket{0},\ket{1}\right\} $
+but is impossible to produce $\ket{0}$ in another basis $\left\{ \ket{+},\ket{0}\right\} $.
+In contrast, when measuring a state~$\ket{\phi}$ in CQT, the probability
+to produce a basis vector~$\ket{\psi_{i}}$ is completely determined
+by $\ket{\psi_{i}}$ and $\ket{\phi}$ no matter $\ket{\psi_{i}}$
+is in which measurement basis. In CQT, the measurement basis matters
+only when discussing quantum contextuality. Despite this kind of ``supercontextuality''
+of MQT, its computational model, modal quantum computing (MQC), having
+``supernatural'' computational power is also far from conventional
+quantum computing as we will describe next.
 

### 2018-02-25 dissertation.tex
dissertation.lyx Updating...

@@
 
-\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
 \newcommand{\muB}{\ensuremath{\mu^{B}}}
@@
 \newcommand{\braket}[2]{\ip{#1}{#2}}
+\newcommand{\todo}[1]{\textbf{TODO.~#1}}
 
@@
 \tableofcontents{}
+
+\todo{{Table of symbols?}}
 
@@
 
-\section{Geometrical Structure of States\label{CQC1qubitBloch.sec}}
-
 Conventional quantum theory (CQT) is described by the following: 
@@
 
-In this paper, we focus on the discrete geometric issues raised by
-the properties (i) and (ii) given above for CQT, and leave for another
-time the important issues of (iii), (iv), and such conundrums as probabilities,
-zero norms, and dynamics in the theory of DQT. To facilitate the transition
-to DQT carried out in later sections, we concern ourselves first with
-the properties of the simplest possible abstract state object in CQT,
-the single qubit state.
+In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the discrete geometric
+issues raised by the properties (i) and (ii) given above for CQT.
+
+(iii)
+
+In Sec.~\ref{sec:fuzzy}, we introduces the important issues of (iv)
+and the foundations of quantum probability space and fuzzy measurement.
+
+To facilitate the transition to DQT carried out in later sections,
+we concern ourselves first with the properties of the simplest possible
+abstract state object in CQT, the single qubit state.
+
+\section{Geometrical Structure of States\label{CQC1qubitBloch.sec}}
 
@@
 
-\section{Quantum Probability}
+\section{Quantum Probability\label{sec:fuzzy}}
 
@@
 while measuring $\ket{+}$ nondeterministically produces $\ket{0}$
-or $\ket{1}$ with no assigned probability distribution, . When measuring
+or $\ket{1}$ with no assigned probability distribution. When measuring
 an arbitrary state~$\ket{\phi}\in\left\{ \ket{0},\ket{1},\ket{+}\right\} $
@@
 to produce $\ket{\psi_{i}}$. Since only possibility and impossibility
-is predicted by the theory, the modal quantum theories is named after
+is predicted by the theory, modal quantum theories are named after
 these “modal” concepts.
@@
 by $\ket{\psi_{i}}$ and $\ket{\phi}$ no matter $\ket{\psi_{i}}$
-is in which measurement basis. In CQT, the measurement basis matters
-only when discussing quantum contextuality. Despite this kind of ``supercontextuality''
-of MQT, its computational model, modal quantum computing (MQC), having
-``supernatural'' computational power is also far from conventional
-quantum computing as we will describe next.
+is in which measurement basis. This phenomena of the measurement basis
+dependence in CQT only exists when discussing quantum contextuality.
+Despite this kind of ``supercontextuality'' of MQT, its computational
+model, modal quantum computing (MQC), having ``supernatural'' computational
+power is also far from conventional quantum computing as we will describe
+next.
 

### 2018-02-27 dissertation.tex
Updates from ShareLaTeX
dissertation.lyx "Chapter 2 Conventional Quantum Theory" Updating...

@@
 \usepackage{mathrsfs}
+\usepackage{enumitem}
 \usepackage{pdfpages}
@@
 \usepackage{amssymb}
+\usepackage{graphicx}
 
@@
 \newcommand{\lyxdot}{.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
+\newlength{\lyxlabelwidth}      % auxiliary length
 
@@
 \usepackage{comment}
-
-%\usepackage[basic]{complexity}
-\newcommand{\lang}[1]{{\ensuremath{\mathsf{#1}}}}
-\newcommand{\newlang}[2]{\newcommand{#1}{\lang{#2}}}
-\newlang{\usat}{UNIQUE-SAT}
-
 \usepackage[all]{xy}
@@
 \usepackage{setspace}
+
+%\usepackage[basic]{complexity}
+\newcommand{\lang}[1]{{\ensuremath{\mathsf{#1}}}}
+\newcommand{\newlang}[2]{\newcommand{#1}{\lang{#2}}}
+\newlang{\usat}{UNIQUE-SAT}
 
@@
 \newcommand{\todo}[1]{\textbf{TODO.~#1}}
+\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
+\newcommand{\Sphere}[1]{\mathbf{S}^{#1}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\rmi}{i}
+\newcommand{\rme}{e}
 
@@
 
-\todo{{Table of symbols?}}
+\todo{Table of symbols?}
 
@@
 Conventional quantum theory (CQT) is described by the following:
-\begin{enumerate}
-\item[(i)] $D=2^{n}$ orthonormal basis vectors of an $n$-qubit state, 
-\item[(ii)] the normalized $D$ complex probability amplitude coefficients describing
-the contribution of each basis vector, 
-\item[(iii)] a set of probability-conserving unitary matrix operators that suffice
-to describe all required state transformations of a quantum circuit, 
-\item[(iv)] and a measurement framework. 
+\begin{enumerate}[label=(\roman{enumi})]
+\item \label{enu:-orthonormal-basis}$D$ orthonormal basis vectors for
+a Hilbert space of dimension~$D$, 
+\item \label{enu:probability-amplitude}the normalized $D$ complex probability
+amplitude coefficients describing the contribution of each basis vector, 
+\item \label{enu:unitary-matrix}a set of probability-conserving unitary
+matrix operators that suffice to describe all required state transformations, 
+\item \label{enu:measurement-framework}and a measurement framework. 
 \end{enumerate}
@@
 of complex amplitudes into a pair of ordinary real numbers. One also
-typically assumes the existence of a Hilbert space with an orthonormal
-basis, allowing us to write $n$-qubit \textit{pure} states in general
-as Hilbert space vectors with an Hermitian inner product: 
+typically assumes the existence of a $D$-dimensional Hilbert space
+with an orthonormal basis, allowing us to write \textit{pure} states
+in general as Hilbert space vectors with an Hermitian inner product:
 \begin{eqnarray}
@@
 \begin{equation}
-\braket{i}{k}=\delta_{ik}\,,
-\end{equation}
-where $\bra{i}$ is called the dual vector of $\ket{i}$.
+\braket{i}{k}=\delta_{ik}\,.
+\end{equation}
 
@@
 In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the discrete geometric
-issues raised by the properties (i) and (ii) given above for CQT.
-
-(iii)
-
-In Sec.~\ref{sec:fuzzy}, we introduces the important issues of (iv)
-and the foundations of quantum probability space and fuzzy measurement.
-
-To facilitate the transition to DQT carried out in later sections,
-we concern ourselves first with the properties of the simplest possible
-abstract state object in CQT, the single qubit state.
+issues raised by the properties \ref{enu:-orthonormal-basis} and
+\ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:Quantum-Circuit-Model},
+we describe product and entangled $n$-qubit states used in circuit
+model, and the unitary matrices used to transform states as addressed
+by by the property \ref{enu:unitary-matrix}. In Sec.~\ref{sec:fuzzy},
+we introduces the important issues of \ref{enu:measurement-framework}
+and the foundations of quantum probability space. To facilitate the
+transition to DQT carried out in later sections, we concern ourselves
+first with the properties of the simplest possible abstract state
+object in CQT, the single qubit state.
 
@@
 
-\begin{comment}
-
-\subsection{The single qubit problem}
-
-A single qubit already provides access to a wealth of geometric information
-and context. We write the single qubit state as 
-\begin{equation}
-\begin{array}{lr}
-\ket{\psi_{1}}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}\  & \ \alpha_{0},\alpha_{1}\in\C\end{array}\ .%%
-%%\alpha_{1}{array}
-\label{A1.eq}
-\end{equation}
+\subsection{The System Described by a Two-dimensional Hilbert Space}
+
+A state in a two-dimensional Hilbert space, also called a qubit, already
+provides access to a wealth of geometric information and context.
+We write the single qubit state as 
+\begin{align}
+\ket{\psi_{1}} & =\alpha_{0}\ket{0}+\alpha_{1}\ket{1} & \alpha_{0},\alpha_{1}\in\mathbb{C}\,.\label{A1.eq}
+\end{align}
 
@@
 way to remove the distinction between states that differ only by an
-overall phase transformation $e^{i\phi}$, that is, 
-\begin{equation}
-(\alpha_{0},\alpha_{1})\sim(e^{i\phi}\alpha_{0},e^{i\phi}\alpha_{1})\ .\label{A3.eq}
+overall phase transformation $\rme^{\rmi\phi}$, that is, 
+\begin{equation}
+\left(\alpha_{0},\alpha_{1}\right)\sim\left(\rme^{\rmi\phi}\alpha_{0},\rme^{\rmi\phi}\alpha_{1}\right)\,.\label{A3.eq}
 \end{equation}
@@
 down as follows: let 
-\begin{equation}
-\begin{array}{cc}
-\alpha_{0}=x_{0}+iy_{0}, & \alpha_{1}=x_{1}+iy_{1}\end{array}\ .\label{A4.eq}
-\end{equation}
+\begin{align}
+\alpha_{0} & =x_{0}+\rmi y_{0}\,, & \alpha_{1} & =x_{1}+\rmi y_{1}\,.\label{A4.eq}
+\end{align}
 Then \Eq{A2.eq} becomes the condition that the four real variables
@@
 take the remaining 3 degrees of freedom in \Eq{A5.eq} and reduce
-them to 2 degrees of freedom by effectively removing $e^{i\phi}$
+them to 2 degrees of freedom by effectively removing $\rme^{\rmi\phi}$
 (``fibering out by the circle $\Sphere{1}$''). The standard form
@@
 \begin{figure}[htb]
-\centerline{ \includegraphics[width=0.48\columnwidth,bb = 0 0 200 100, draft, type=eps]{../../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/hopfS2.pdf}\hspace{0.03in}
-\includegraphics[width=0.48\columnwidth,bb = 0 0 200 100, draft, type=eps]{../../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/hopfFibers.pdf}}
-\centerline{\hspace{1in} (a) \hfill{}(b) \hspace{1in}} \caption{(a) The sphere represented by \Eq{A7.eq}, which is the irreducible
+\centerline{ \includegraphics[width=0.48\columnwidth]{hopfS2}\hspace{0.03in}
+\includegraphics[width=0.48\columnwidth]{hopfFibers}} \centerline{\hspace{1in}
+(a) \hfill{}(b) \hspace{1in}} \caption{(a) The sphere represented by \Eq{A7.eq}, which is the irreducible
 space of one-qubit states, along with a representative set of points
 on the sphere. (b) Representation of the Hopf fibration as a family
-of circles (the paths of $e^{i\phi}$), each corresponding to a single
-point on the sphere in (a). Points in (a) are color coded corresponding
-to circles in (b), e.g., one pole contains the red elliptical circle
-that would become an infinite-radius circle in a slightly different
+of circles (the paths of $\rme^{\rmi\phi}$), each corresponding to
+a single point on the sphere in (a). Points in (a) are color coded
+corresponding to circles in (b), e.g., one pole contains the red elliptical
+circle that would become an infinite-radius circle in a slightly different
 projection, and the opposite pole corresponds to the large perfectly
@@
 \begin{equation}
-\ket{\psi_{1}}=e^{i\phi}\cos\frac{\psi}{2}\ket{0}+\sin\frac{\psi}{2}\ket{1}\ ,\label{A9.eq}
+\ket{\psi_{1}}=\rme^{\rmi\phi}\cos\frac{\psi}{2}\ket{0}+\sin\frac{\psi}{2}\ket{1}\ ,\label{A9.eq}
 \end{equation}
@@
 \begin{centering}
-\includegraphics[width=0.47\columnwidth,bb = 0 0 200 100, draft, type=eps]{../../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/blochSphere.pdf}
-\hspace{0.01in} \includegraphics[width=0.47\columnwidth,bb = 0 0 200 100, draft, type=eps]{../../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/blochSphereArc.pdf} 
+\includegraphics[width=0.47\columnwidth]{blochSphere} \hspace{0.01in}
+\includegraphics[width=0.47\columnwidth]{blochSphereArc} 
 \par\end{centering}
@@
 
-%% AMR: replaced ', probabilistic, exponentially complex transitions from%% state to state' with the above
+\begin{comment}
 
@@
 the family of coefficients $\{\alpha_{i}\}$ as being the same if
-they differ only by an overall phase $e^{i\phi}$. However, in practice
-this is not a construction that is easy to realize in a practical
-computation. We now outline an explicit algorithm for accomplishing
-the reduction to the irreducible $n$-qubit state space $\CP{D-1}$;
-this construction will turn out to be useful for the validation of
-our discrete results to follow below.
+they differ only by an overall phase $\rme^{\rmi\phi}$. However,
+in practice this is not a construction that is easy to realize in
+a practical computation. We now outline an explicit algorithm for
+accomplishing the reduction to the irreducible $n$-qubit state space
+$\CP{D-1}$; this construction will turn out to be useful for the
+validation of our discrete results to follow below.
 
@@
 coordinate system for projective geometry to remove the overall phase
-ambiguity $e^{i\phi}$ from the $n$-qubit states. If we take a particular
-weighting of the elements of the density matrix $\rho$, we can construct
-a \textit{unit vector\/} of real dimension $D^{2}$ with the form:
+ambiguity $\rme^{\rmi\phi}$ from the $n$-qubit states. If we take
+a particular weighting of the elements of the density matrix $\rho$,
+we can construct a \textit{unit vector\/} of real dimension $D^{2}$
+with the form: 
 \begin{equation}
@@
 as $\CP{D-1}$ (see any textbook on geometry \cite{Berger}).
+\end{comment}
+
+An $n$-qubit pure state in the conventional quantum theory (CQT)
+is represented as a vector in the $2^{n}$-dimensional Hilbert space.
+If we eliminate all symmetries, an irreducible state is actually a
+point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
+also known as the complex projective space~$\mathbb{CP}^{2^{n}-1}$
+\cite{Hatcher2001,Bengtsson2007}. These irreducible quantum states
+can also be classified as product states and entangled states, and
+the latter one plays the essential role for pure-state algorithms
+\cite{Mermin2007,Jaeger2007}.
+
+\section{Quantum Circuit Model\label{sec:Quantum-Circuit-Model}}
+
+\begin{comment}
 
@@
 \end{comment}
-
-An $n$-qubit pure state in the conventional quantum theory (CQT)
-is represented as a vector in the $2^{n}$-dimensional Hilbert space.
-If we eliminate all symmetries, an irreducible state is actually a
-point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
-also known as the complex projective space~$\mathbb{CP}^{2^{n}-1}$
-\cite{Hatcher2001,Bengtsson2007}. These irreducible quantum states
-can also be classified as product states and entangled states, and
-the latter one plays the essential role for pure-state algorithms
-\cite{Mermin2007,Jaeger2007}.
 
@@
 \section{Quantum Contextuality}
+
+\todo{Explain enough background knowledge to support the discussion
+about contextuality in the end of Sec.~\ref{modalquantum}.}
 

### 2018-02-27 dissertation.tex
Updates from ShareLaTeX
dissertation.lyx "Chapter 2 Conventional Quantum Theory" Updating...

@@
 \newcommand{\R}{\mathbb{R}}
-\newcommand{\rmi}{i}
-\newcommand{\rme}{e}
+\newcommand{\rme}{\mathrm{e}}
+\newcommand{\rmi}{\mathrm{i}}
 
@@
 
-Conventional quantum theory (CQT) is described by the following:
+The part of conventional quantum theory (CQT) used by quantum circuit
+model is described by the following:
 \begin{enumerate}[label=(\roman{enumi})]
@@
 \end{enumerate}
-We remark that there are many things that are assumed in CQT, such
-as the absence of zero norm states for non-zero vectors, and the decomposition
-of complex amplitudes into a pair of ordinary real numbers. One also
+In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the discrete geometric
+issues raised by the properties \ref{enu:-orthonormal-basis} and
+\ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:Quantum-Circuit-Model},
+we describe product and entangled $n$-qubit states used in quantum
+circuit model, and the unitary matrices used to build circuit as addressed
+by by the property \ref{enu:unitary-matrix}. In Sec.~\ref{sec:fuzzy},
+we introduce the important issues of \ref{enu:measurement-framework}
+and the foundations of quantum probability space.
+
+\section{Geometrical Structure of States\label{CQC1qubitBloch.sec}}
+
+There are many things that are assumed in CQT, such as the absence
+of zero norm states for non-zero vectors, and the decomposition of
+complex amplitudes into a pair of ordinary real numbers. One also
 typically assumes the existence of a $D$-dimensional Hilbert space
@@
 in continuum quantum mechanics that challenge us in defining a discrete
-quantum geometry.
-
-In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the discrete geometric
-issues raised by the properties \ref{enu:-orthonormal-basis} and
-\ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:Quantum-Circuit-Model},
-we describe product and entangled $n$-qubit states used in circuit
-model, and the unitary matrices used to transform states as addressed
-by by the property \ref{enu:unitary-matrix}. In Sec.~\ref{sec:fuzzy},
-we introduces the important issues of \ref{enu:measurement-framework}
-and the foundations of quantum probability space. To facilitate the
-transition to DQT carried out in later sections, we concern ourselves
-first with the properties of the simplest possible abstract state
-object in CQT, the single qubit state.
-
-\section{Geometrical Structure of States\label{CQC1qubitBloch.sec}}
+quantum geometry. To facilitate the transition to DQT carried out
+in later sections, we concern ourselves first with the properties
+of the simplest possible abstract state object in CQT, the single
+qubit state.
 
@@
 \begin{align}
-\ket{\psi_{1}} & =\alpha_{0}\ket{0}+\alpha_{1}\ket{1} & \alpha_{0},\alpha_{1}\in\mathbb{C}\,.\label{A1.eq}
+\ket{\psi_{1}} & =\alpha_{0}\ket{0}+\alpha_{1}\ket{1} & \alpha_{0},\alpha_{1} & \in\mathbb{C}\,.\label{A1.eq}
 \end{align}
@@
 \end{equation}
-This can be accomplished by the Hopf fibration, which we can write
-down as follows: let 
+This can be accomplished by the Hopf fibration \cite{Hatcher2001,MosseriDandoloff2001,Bengtsson2007},
+which we can write down as follows: let 
 \begin{align}
@@
 
+\section{Quantum Circuit Model\label{sec:Quantum-Circuit-Model}}
+
 An $n$-qubit pure state in the conventional quantum theory (CQT)
@@
 \cite{Mermin2007,Jaeger2007}.
-
-\section{Quantum Circuit Model\label{sec:Quantum-Circuit-Model}}
 

### 2018-02-28 dissertation.tex
Updates from ShareLaTeX
dissertation.tex Uploading local copy to ShareLaTeX to fix to sync problems...
dissertation.lyx "Chapter 2 Conventional Quantum Theory" Updating...

@@
 \item \label{enu:unitary-matrix}a set of probability-conserving unitary
-matrix operators that suffice to describe all required state transformations, 
+matrix operators that suffice to describe all required state transformations
+of a quantum circuit, 
 \item \label{enu:measurement-framework}and a measurement framework. 
@@
 \ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:Quantum-Circuit-Model},
-we describe product and entangled $n$-qubit states used in quantum
-circuit model, and the unitary matrices used to build circuit as addressed
-by by the property \ref{enu:unitary-matrix}. In Sec.~\ref{sec:fuzzy},
-we introduce the important issues of \ref{enu:measurement-framework}
-and the foundations of quantum probability space.
+we address the property~\ref{enu:unitary-matrix} by describing product
+and entangled $n$-qubit states and unitary matrices in quantum circuit
+model. In Sec.~\ref{sec:fuzzy}, we introduce the important issues
+of \ref{enu:measurement-framework} and the foundations of quantum
+probability space.
 
@@
 
-\subsection{The System Described by a Two-dimensional Hilbert Space}
+\subsection{The single qubit problem}
 
@@
 
-There is a family of 6 equivalence classes of quadratic maps that
-take the remaining 3 degrees of freedom in \Eq{A5.eq} and reduce
-them to 2 degrees of freedom by effectively removing $\rme^{\rmi\phi}$
-(``fibering out by the circle $\Sphere{1}$''). The standard form
-of this class of maps (``the Hopf fibration'') is 
-\begin{eqnarray}
-X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\nonumber \\
-Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\\
-Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}=x_{0}^{\ 2}+y_{0}^{\ 2}-x_{1}^{\ 2}-y_{1}^{\ 2}\ .\nonumber 
-\end{eqnarray}
-These transformed coordinates obey 
+We can reduce 3 real degrees of freedom in \Eq{A5.eq} to 2 real
+degrees of freedom by effectively removing $\rme^{\rmi\phi}$ (``fibering
+out by the circle $\Sphere{1}$''). The standard form of this maps
+(``the Hopf fibration'') is 
+\begin{eqnarray}
+X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
+Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\\
+Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}=x_{0}^{\ 2}+y_{0}^{\ 2}-x_{1}^{\ 2}-y_{1}^{\ 2}\,.\nonumber 
+\end{eqnarray}
+By denoting the the three-dimensional vector~$\left(X,Y,Z\right)$
+as $\Vec{X}$, \Eq{A5.eq} implies these transformed coordinates
+obeying 
 \begin{equation}
@@
 and therefore have only two remaining degrees of freedom describing
-all possible distinct one-qubit quantum states. In Figure \ref{hopfFibers.fig}
+all possible distinct one-qubit quantum states. In Fig.~\ref{hopfFibers.fig},
 we illustrate schematically the family of circles \textit{each one

### 2018-03-01 dissertation.tex
dissertation.lyx "2.1.1 The single qubit problem" Updating...

@@
 
-A convenience for probability calculations and a necessity for computing
-relative state properties is the normalization condition 
+A convenience for computing probability and relative state properties
+is the normalization condition 
 \begin{equation}
@@
 and therefore have only two remaining degrees of freedom describing
-all possible distinct one-qubit quantum states. In Fig.~\ref{hopfFibers.fig},
-we illustrate schematically the family of circles \textit{each one
-of which is collapsed to a point\/} $(\theta,\phi)$ on the surface
-$X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
-
-%% (We try to list the sources of all computed figures)%% Sources for hopfFibers.fig:  dqc-geom-2012/00mathFigs/Hopf-Fiber.nb
-\begin{figure}[htb]
+all possible distinct one-qubit quantum states. 
+\begin{figure}[tbh]
 \centerline{ \includegraphics[width=0.48\columnwidth]{hopfS2}\hspace{0.03in}
@@
 \end{figure}
+In Fig.~\ref{hopfFibers.fig}, we illustrate schematically the family
+of circles \textit{each one of which is collapsed to a point\/} $(\theta,\phi)$
+on the surface $X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
 
@@
 systems describing $\Sphere{3}$ via \Eq{A5.eq} such as 
-\begin{eqnarray}
-\hspace*{-0.5cm}\left(x_{0},y_{0},x_{1},y_{1}\right) & = & \left(\cos\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\,\sin\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\ \right.\nonumber \\
- &  & \left.\cos\frac{\theta-\phi}{2}\sin\frac{\psi}{2},\ \sin\frac{\theta-\phi}{2}\sin\frac{\psi}{2}\right),\label{A8a.eq}
-\end{eqnarray}
+\begin{equation}
+\left(x_{0},y_{0},x_{1},y_{1}\right)=\left(\cos\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\,\sin\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\ \cos\frac{\theta-\phi}{2}\sin\frac{\psi}{2},\ \sin\frac{\theta-\phi}{2}\sin\frac{\psi}{2}\right)\,,\label{A8a.eq}
+\end{equation}
 where %% $0\leq \theta \leq 2 \pi$,  $-\pi \leq \phi \leq  \pi$, 
@@
 we see that 
-\begin{eqnarray}
-\left(X,Y,Z\right)=\left(\cos\phi\sin\psi,\,\sin\phi\sin\psi,\,\cos\psi\right)\ .\label{A8b.eq}
-\end{eqnarray}
+\begin{equation}
+\left(X,Y,Z\right)=\left(\cos\phi\sin\psi,\,\sin\phi\sin\psi,\,\cos\psi\right)\,.\label{A8b.eq}
+\end{equation}
 Thus the one-qubit state is independent of $\theta$, and we can choose
@@
 \begin{equation}
-\ket{\psi_{1}}=\rme^{\rmi\phi}\cos\frac{\psi}{2}\ket{0}+\sin\frac{\psi}{2}\ket{1}\ ,\label{A9.eq}
+\ket{\psi_{1}}=\rme^{\rmi\phi}\cos\frac{\psi}{2}\ket{0}+\sin\frac{\psi}{2}\ket{1}\,,\label{A9.eq}
 \end{equation}

### 2018-03-02 dissertation.tex
Updates from ShareLaTeX
dissertation.lyx "2.1.1 The single qubit problem" Updating...

@@
 
+\@ifundefined{showcaptionsetup}{}{%
+ \PassOptionsToPackage{caption=false}{subfig}}
+\usepackage{subfig}
 \makeatother
@@
 way to remove the distinction between states that differ only by an
-overall phase transformation $\rme^{\rmi\phi}$, that is, 
-\begin{equation}
-\left(\alpha_{0},\alpha_{1}\right)\sim\left(\rme^{\rmi\phi}\alpha_{0},\rme^{\rmi\phi}\alpha_{1}\right)\,.\label{A3.eq}
+overall phase transformation $\rme^{\rmi\frac{\theta}{2}}$, that
+is, 
+\begin{equation}
+\left(\alpha_{0},\alpha_{1}\right)\sim\left(\rme^{\rmi\frac{\theta}{2}}\alpha_{0},\rme^{\rmi\frac{\theta}{2}}\alpha_{1}\right)\,.\label{A3.eq}
 \end{equation}
@@
 We can reduce 3 real degrees of freedom in \Eq{A5.eq} to 2 real
-degrees of freedom by effectively removing $\rme^{\rmi\phi}$ (``fibering
-out by the circle $\Sphere{1}$''). The standard form of this maps
-(``the Hopf fibration'') is 
+degrees of freedom by effectively removing $\rme^{\rmi\frac{\theta}{2}}$
+(``fibering out by the circle $\Sphere{1}$''). The standard form
+of this maps (``the Hopf fibration'') is 
 \begin{eqnarray}
@@
 and therefore have only two remaining degrees of freedom describing
-all possible distinct one-qubit quantum states. 
+all possible distinct one-qubit quantum states. In Fig.~\ref{hopfFibers.fig},
+we illustrate schematically the family of circles \textit{each one
+of which is collapsed to a point\/} $\left(\phi,\psi\right)$ on
+the surface $X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
+
 \begin{figure}[tbh]
-\centerline{ \includegraphics[width=0.48\columnwidth]{hopfS2}\hspace{0.03in}
-\includegraphics[width=0.48\columnwidth]{hopfFibers}} \centerline{\hspace{1in}
-(a) \hfill{}(b) \hspace{1in}} \caption{(a) The sphere represented by \Eq{A7.eq}, which is the irreducible
+\hfill{}\subfloat[]{\centering{}\includegraphics[width=0.48\columnwidth]{hopfS2}}\hfill{}\subfloat[]{\begin{centering}
+\includegraphics[width=0.48\columnwidth]{hopfFibers}
+\par\end{centering}
+}\hfill{} \caption{(a) The sphere represented by \Eq{A7.eq}, which is the irreducible
 space of one-qubit states, along with a representative set of points
 on the sphere. (b) Representation of the Hopf fibration as a family
-of circles (the paths of $\rme^{\rmi\phi}$), each corresponding to
-a single point on the sphere in (a). Points in (a) are color coded
-corresponding to circles in (b), e.g., one pole contains the red elliptical
-circle that would become an infinite-radius circle in a slightly different
-projection, and the opposite pole corresponds to the large perfectly
-round red circle at the equator.}
+of circles (the paths of $\rme^{\rmi\frac{\theta}{2}}$), each corresponding
+to a single point on the sphere in (a).\protect \\
+\todo{{Since }the Hopf fibration{ is fibering out by} the circle
+$\Sphere{1}${ }on the three-sphere $\Sphere{3}$ embedded in $\R^{4}$.
+Need to confirm whether (b) is a figure in $\R^{4}$ and how to understand
+the next sentence.}\protect \\
+Points in (a) are color coded corresponding to circles in (b), e.g.,
+one pole contains the red elliptical circle that would become an infinite-radius
+circle in a slightly different projection, and the opposite pole corresponds
+to the large perfectly round red circle at the equator.}
 \label{hopfFibers.fig} 
 \end{figure}
-In Fig.~\ref{hopfFibers.fig}, we illustrate schematically the family
-of circles \textit{each one of which is collapsed to a point\/} $(\theta,\phi)$
-on the surface $X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
 
@@
 \begin{equation}
-\left(x_{0},y_{0},x_{1},y_{1}\right)=\left(\cos\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\,\sin\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\ \cos\frac{\theta-\phi}{2}\sin\frac{\psi}{2},\ \sin\frac{\theta-\phi}{2}\sin\frac{\psi}{2}\right)\,,\label{A8a.eq}
+\left(x_{0},y_{0},x_{1},y_{1}\right)=\left(\cos\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\,\sin\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\,\cos\frac{\theta-\phi}{2}\sin\frac{\psi}{2},\,\sin\frac{\theta-\phi}{2}\sin\frac{\psi}{2}\right)\,,\label{A8a.eq}
 \end{equation}
@@
 \end{equation}
-and an irreducible state can be represented as a point on a sphere,
-as shown in Figure \ref{blochSphere.fig}(a).
+and an irreducible state can be represented as a point on a sphere
+called the Bloch sphere, as shown in Fig.~\ref{blochSphere.fig}(a).
 
@@
 \begin{centering}
-\includegraphics[width=0.47\columnwidth]{blochSphere} \hspace{0.01in}
+\hfill{}\subfloat[]{\centering{}\includegraphics[width=0.47\columnwidth]{blochSphere}}\hfill{}\subfloat[]{\begin{centering}
 \includegraphics[width=0.47\columnwidth]{blochSphereArc}
 \par\end{centering}
-\centerline{\hspace{1in} (a) \hfill{}(b) \hspace{1in}} \caption{(a) The conventional Bloch sphere with a unique state represented
+}\hfill{}
+\par\end{centering}
+\caption{(a) The conventional Bloch sphere with a unique state represented
 by the point at the red sphere. (b) The geodesic shortest-distance
@@
 precision real numbers, it is not possible, even in principle, to
-make an exact state transition as implied by Figure \ref{blochSphere.fig}(b).
+make an exact state transition as implied by Fig.~\ref{blochSphere.fig}(b).
 In practice, one has to be content with approximate, typically exponentially
@@
 the family of coefficients $\{\alpha_{i}\}$ as being the same if
-they differ only by an overall phase $\rme^{\rmi\phi}$. However,
-in practice this is not a construction that is easy to realize in
-a practical computation. We now outline an explicit algorithm for
+they differ only by an overall phase $\rme^{\rmi\frac{\theta}{2}}$.
+However, in practice this is not a construction that is easy to realize
+in a practical computation. We now outline an explicit algorithm for
 accomplishing the reduction to the irreducible $n$-qubit state space
@@
 coordinate system for projective geometry to remove the overall phase
-ambiguity $\rme^{\rmi\phi}$ from the $n$-qubit states. If we take
-a particular weighting of the elements of the density matrix $\rho$,
-we can construct a \textit{unit vector\/} of real dimension $D^{2}$
-with the form: 
+ambiguity $\rme^{\rmi\frac{\theta}{2}}$ from the $n$-qubit states.
+If we take a particular weighting of the elements of the density matrix
+$\rho$, we can construct a \textit{unit vector\/} of real dimension
+$D^{2}$ with the form: 
 \begin{equation}

### 2018-03-03 dissertation.tex
dissertation.lyx "2.1.1 The single qubit problem" Updating...

@@
 \end{equation}
-This can be accomplished by the Hopf fibration \cite{Hatcher2001,MosseriDandoloff2001,Bengtsson2007},
+This can be accomplished by the Hopf fibration \cite{Hatcher2001,MosseriDandoloff2001,Bengtsson2007,wiki:HopfFibration},
 which we can write down as follows: let 
@@
 X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
-Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\\
+Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{eq:HopfFibration}\\
 Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}=x_{0}^{\ 2}+y_{0}^{\ 2}-x_{1}^{\ 2}-y_{1}^{\ 2}\,.\nonumber 
@@
 By denoting the the three-dimensional vector~$\left(X,Y,Z\right)$
-as $\Vec{X}$, \Eq{A5.eq} implies these transformed coordinates
+as $\Hat{a}$, \Eq{A5.eq} implies these transformed coordinates
 obeying 
 \begin{equation}
-\|\Vec{X}\|^{2}=X^{2}+Y^{2}+Z^{2}=\left(|\alpha_{0}|^{2}+|\alpha_{1}|^{2}\right)^{2}=1\label{A7.eq}
+\|\Hat{a}\|^{2}=X^{2}+Y^{2}+Z^{2}=\left(|\alpha_{0}|^{2}+|\alpha_{1}|^{2}\right)^{2}=1\label{A7.eq}
 \end{equation}
@@
 space of one-qubit states, along with a representative set of points
-on the sphere. (b) Representation of the Hopf fibration as a family
-of circles (the paths of $\rme^{\rmi\frac{\theta}{2}}$), each corresponding
-to a single point on the sphere in (a).\protect \\
-\todo{{Since }the Hopf fibration{ is fibering out by} the circle
-$\Sphere{1}${ }on the three-sphere $\Sphere{3}$ embedded in $\R^{4}$.
-Need to confirm whether (b) is a figure in $\R^{4}$ and how to understand
-the next sentence.}\protect \\
-Points in (a) are color coded corresponding to circles in (b), e.g.,
-one pole contains the red elliptical circle that would become an infinite-radius
-circle in a slightly different projection, and the opposite pole corresponds
-to the large perfectly round red circle at the equator.}
+on the sphere. (b) Representation of the Hopf fibration, \ref{eq:HopfFibration},
+as a family of circles (the paths of $\rme^{\rmi\frac{\theta}{2}}$)
+on the three-sphere $\Sphere{3}$. Although $\Sphere{3}$ cannot be
+directly embedded in $\R^{3}$, $\Sphere{3}$ can be regarded as attaching
+two three-dimensional ball on two sides of two-sphere $\Sphere{2}$.
+In this way, each circle in $\Sphere{3}$ corresponding to a single
+point on the sphere in (a) can be represented as a circle in the three-dimensional
+ball. Moreover, points in (a) are color coded corresponding to circles
+in (b), e.g., one pole contains the red elliptical circle that would
+become an infinite-radius circle by a slightly different way to represent
+$\Sphere{3}$ in $\R^{3}$, and the opposite pole corresponds to the
+large perfectly round red circle at the equator.}
 \label{hopfFibers.fig} 
@@
 \begin{equation}
-S(\Hat{a},\Hat{b},t)=\Hat{a}\,\frac{\sin((1-t)\theta)}{\sin\theta}\,+\,\Hat{b}\,\frac{\sin(t\theta)}{\sin\theta}\ ,\label{slerp.eq}
-\end{equation}
-where $\Hat{a}\cdot\Hat{b}=\cos\theta$. Figure \ref{blochSphere.fig}(b)
+S(\Hat{a},\Hat{b},t)=\Hat{a}\,\frac{\sin((1-t)\omega)}{\sin\omega}\,+\,\Hat{b}\,\frac{\sin(t\omega)}{\sin\omega}\ ,\label{slerp.eq}
+\end{equation}
+where $\Hat{a}\cdot\Hat{b}=\cos\omega$. Figure \ref{blochSphere.fig}(b)
 illustrates the path traced by a SLERP between two irreducible one-qubit

### 2018-03-04 dissertation.tex
dissertation.lyx "2.1.1 The single qubit problem" Updating...

@@
 \begin{equation}
-x_{0}^{\ 2}+y_{0}^{\ 2}+x_{1}^{\ 2}+y_{1}^{\ 2}=1\ .\label{A5.eq}
+{x_{0}}^{2}+{y_{0}}^{2}+{x_{1}}^{2}+{y_{1}}^{2}=1\ .\label{A5.eq}
 \end{equation}
@@
 Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{eq:HopfFibration}\\
-Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}=x_{0}^{\ 2}+y_{0}^{\ 2}-x_{1}^{\ 2}-y_{1}^{\ 2}\,.\nonumber 
+Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
 \end{eqnarray}
@@
 or minimal-length transformation. Explicitly, given two one-qubit
-states denoted by points $\Vec{a}$ and $\Vec{b}$ on $\Sphere{2}$,
-the shortest rotation carrying the unit normal $\Hat{a}$ to the unit
-normal $\Hat{b}$ is the SLERP (spherical linear interpolation) 
+states denoted by points $\Hat{a}$ and $\Hat{b}$ on $\Sphere{2}$,
+the shortest rotation carrying $\Hat{a}$ to $\Hat{b}$ is the SLERP
+(spherical linear interpolation) \cite{Shoemake:1985:ARQ:325334.325242,wiki:Slerp}
 \begin{equation}

### 2018-03-04 dissertation.tex
dissertation.lyx "2.1 Geometrical Structure of States" Updating...

@@
 $\VVec{\alpha}\in\mathComplex^{D}$, and the $\{\ket{i}\}$ is an
-orthonormal basis of states obeying 
-\begin{equation}
-\braket{i}{k}=\delta_{ik}\,.
-\end{equation}
+orthonormal basis of states obeying $\braket{i}{k}=\delta_{ik}$.
 
@@
 
-A state in a two-dimensional Hilbert space, also called a qubit, already
+A state in a two-dimensional Hilbert space, known as a qubit, already
 provides access to a wealth of geometric information and context.
-We write the single qubit state as 
-\begin{align}
-\ket{\psi_{1}} & =\alpha_{0}\ket{0}+\alpha_{1}\ket{1} & \alpha_{0},\alpha_{1} & \in\mathbb{C}\,.\label{A1.eq}
-\end{align}
-
-A convenience for computing probability and relative state properties
+When we write the single qubit state as $\ket{\psi_{1}}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$,
+a convenience for computing probability and relative state properties
 is the normalization condition 
 \begin{equation}
-\|\psi_{1}\|^{2}=|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=\alpha_{0}^{*}\alpha_{0}+\alpha_{1}^{*}\alpha_{1}=1\ ,\label{A2.eq}
-\end{equation}
-which identifies $\alpha_{0}$ and $\alpha_{1}$ as (complex) probability
+\left\Vert \psi_{1}\right\Vert ^{2}=\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=\alpha_{0}^{*}\alpha_{0}+\alpha_{1}^{*}\alpha_{1}=1\,,\label{A2.eq}
+\end{equation}
+which identifies $\alpha_{0}$ and $\alpha_{1}\in\mathbb{C}$ as probability
 amplitudes and implies the conservation of probability in the closed
-world spanned by $\{\ket{0},\ket{1}\}$. Note that we distinguish
-for future use the \textit{norm\/} $\|\cdot\|$ of a vector from
-the \textit{modulus\/} $|\cdot|$ of a complex number. Continuing,
-we see that if we want only the irreducible state descriptions, we
-must supplement the process of computing \Eq{A2.eq} by finding a
-way to remove the distinction between states that differ only by an
-overall phase transformation $\rme^{\rmi\frac{\theta}{2}}$, that
-is, 
-\begin{equation}
-\left(\alpha_{0},\alpha_{1}\right)\sim\left(\rme^{\rmi\frac{\theta}{2}}\alpha_{0},\rme^{\rmi\frac{\theta}{2}}\alpha_{1}\right)\,.\label{A3.eq}
-\end{equation}
+world spanned by $\left\{ \ket{0},\ket{1}\right\} $. Note that we
+distinguish for future use the \textit{norm}~$\left\Vert \cdot\right\Vert $
+of a vector from the \textit{modulus}~$\left|\cdot\right|$ of a
+complex number. Continuing, we see that if we want only the irreducible
+state descriptions, we must supplement the process of computing \Eq{A2.eq}
+by finding a way to remove the distinction between states that differ
+only by an overall phase transformation $\rme^{\rmi\theta}$, that
+is, $\left(\alpha_{0},\alpha_{1}\right)\sim\left(\rme^{\rmi\theta}\alpha_{0},\rme^{\rmi\theta}\alpha_{1}\right)$.
 This can be accomplished by the Hopf fibration \cite{Hatcher2001,MosseriDandoloff2001,Bengtsson2007,wiki:HopfFibration},
-which we can write down as follows: let 
-\begin{align}
-\alpha_{0} & =x_{0}+\rmi y_{0}\,, & \alpha_{1} & =x_{1}+\rmi y_{1}\,.\label{A4.eq}
-\end{align}
-Then \Eq{A2.eq} becomes the condition that the four real variables
-describing a qubit denote a point on the three-sphere $\Sphere{3}$
-(a 3-manifold) embedded in $\R^{4}$: 
-\begin{equation}
-{x_{0}}^{2}+{y_{0}}^{2}+{x_{1}}^{2}+{y_{1}}^{2}=1\ .\label{A5.eq}
+which can be written down as follows: let $\alpha_{0}=x_{0}+\rmi y_{0}$
+and $\alpha_{1}=x_{1}+\rmi y_{1}$. Then \Eq{A2.eq} becomes the
+condition that the four real variables describing a qubit denote a
+point on the three-sphere $\Sphere{3}$ (a 3-manifold) embedded in
+$\R^{4}$: 
+\begin{equation}
+{x_{0}}^{2}+{y_{0}}^{2}+{x_{1}}^{2}+{y_{1}}^{2}=1\,.\label{A5.eq}
 \end{equation}
@@
 We can reduce 3 real degrees of freedom in \Eq{A5.eq} to 2 real
-degrees of freedom by effectively removing $\rme^{\rmi\frac{\theta}{2}}$
-(``fibering out by the circle $\Sphere{1}$''). The standard form
-of this maps (``the Hopf fibration'') is 
+degrees of freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
+out by the circle $\Sphere{1}$''). The standard form of this maps
+(``the Hopf fibration'') is 
 \begin{eqnarray}
@@
 Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{eq:HopfFibration}\\
-Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
+Z & = & \left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
 \end{eqnarray}
@@
 \begin{equation}
-\|\Hat{a}\|^{2}=X^{2}+Y^{2}+Z^{2}=\left(|\alpha_{0}|^{2}+|\alpha_{1}|^{2}\right)^{2}=1\label{A7.eq}
+\left\Vert \Hat{a}\right\Vert ^{2}=X^{2}+Y^{2}+Z^{2}=\left(\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}\right)^{2}=1\label{A7.eq}
 \end{equation}
@@
 we illustrate schematically the family of circles \textit{each one
-of which is collapsed to a point\/} $\left(\phi,\psi\right)$ on
-the surface $X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
-
-\begin{figure}[tbh]
+of which is collapsed to a point}~$\left(\phi,\psi\right)$ on the
+surface $X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
+
+\begin{figure}[tb]
 \hfill{}\subfloat[]{\centering{}\includegraphics[width=0.48\columnwidth]{hopfS2}}\hfill{}\subfloat[]{\begin{centering}
@@
 space of one-qubit states, along with a representative set of points
-on the sphere. (b) Representation of the Hopf fibration, \ref{eq:HopfFibration},
-as a family of circles (the paths of $\rme^{\rmi\frac{\theta}{2}}$)
-on the three-sphere $\Sphere{3}$. Although $\Sphere{3}$ cannot be
-directly embedded in $\R^{3}$, $\Sphere{3}$ can be regarded as attaching
+on the sphere. (b) Representation of the Hopf fibration, Eq.~(\ref{eq:HopfFibration}),
+as a family of circles (the paths of $\rme^{\rmi\theta}$) on the
+three-sphere $\Sphere{3}$. Although $\Sphere{3}$ cannot be directly
+embedded in $\R^{3}$, $\Sphere{3}$ can be regarded as attaching
 two three-dimensional ball on two sides of two-sphere $\Sphere{2}$.
@@
 \begin{equation}
-\left(x_{0},y_{0},x_{1},y_{1}\right)=\left(\cos\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\,\sin\frac{\theta+\phi}{2}\cos\frac{\psi}{2},\,\cos\frac{\theta-\phi}{2}\sin\frac{\psi}{2},\,\sin\frac{\theta-\phi}{2}\sin\frac{\psi}{2}\right)\,,\label{A8a.eq}
+\left(x_{0},y_{0},x_{1},y_{1}\right)=\left(\cos\left(\theta+\phi\right)\cos\psi,\,\sin\left(\theta+\phi\right)\cos\psi,\,\cos\left(\theta-\phi\right)\sin\psi,\,\sin\left(\theta-\phi\right)\sin\psi\right)\,,\label{A8a.eq}
 \end{equation}
 where %% $0\leq \theta \leq 2 \pi$,  $-\pi \leq \phi \leq  \pi$, 
-$0\leq\psi\leq\pi$, with $0\leq\frac{\theta+\phi}{2}<2\pi$ and $0\leq\frac{\theta-\phi}{2}<2\pi$,
+$0\leq\psi\leq\frac{\pi}{2}$, with $0\leq\theta+\phi<2\pi$ and $0\leq\theta-\phi<2\pi$,
 we see that 
 \begin{equation}
-\left(X,Y,Z\right)=\left(\cos\phi\sin\psi,\,\sin\phi\sin\psi,\,\cos\psi\right)\,.\label{A8b.eq}
+\left(X,Y,Z\right)=\left(\cos\left(2\phi\right)\sin\left(2\psi\right),\,\sin\left(2\phi\right)\sin\left(2\psi\right),\,\cos\left(2\psi\right)\right)\,.\label{A8b.eq}
 \end{equation}
@@
 $\theta=\phi$ without loss of generality, reducing the form of the
-unique one-qubit states to 
-\begin{equation}
-\ket{\psi_{1}}=\rme^{\rmi\phi}\cos\frac{\psi}{2}\ket{0}+\sin\frac{\psi}{2}\ket{1}\,,\label{A9.eq}
-\end{equation}
+unique one-qubit states to $\ket{\psi_{1}}=\rme^{2\rmi\phi}\cos\psi\ket{0}+\sin\psi\ket{1}$,
 and an irreducible state can be represented as a point on a sphere
@@
 
-\begin{figure}[thb]
+\begin{figure}[tb]
 \begin{centering}
@@
 the family of coefficients $\{\alpha_{i}\}$ as being the same if
-they differ only by an overall phase $\rme^{\rmi\frac{\theta}{2}}$.
-However, in practice this is not a construction that is easy to realize
-in a practical computation. We now outline an explicit algorithm for
+they differ only by an overall phase $\rme^{\rmi\theta}$. However,
+in practice this is not a construction that is easy to realize in
+a practical computation. We now outline an explicit algorithm for
 accomplishing the reduction to the irreducible $n$-qubit state space
@@
 coordinate system for projective geometry to remove the overall phase
-ambiguity $\rme^{\rmi\frac{\theta}{2}}$ from the $n$-qubit states.
-If we take a particular weighting of the elements of the density matrix
-$\rho$, we can construct a \textit{unit vector\/} of real dimension
-$D^{2}$ with the form: 
+ambiguity $\rme^{\rmi\theta}$ from the $n$-qubit states. If we take
+a particular weighting of the elements of the density matrix $\rho$,
+we can construct a \textit{unit vector\/} of real dimension $D^{2}$
+with the form: 
 \begin{equation}

### 2018-03-05 dissertation.tex
dissertation.lyx "2.1.1 The single qubit problem" Updating...

@@
 
+\todo{The page of Bibliography is not correct?}
+
 \todo{Table of symbols?}
@@
 only by an overall phase transformation $\rme^{\rmi\theta}$, that
-is, $\left(\alpha_{0},\alpha_{1}\right)\sim\left(\rme^{\rmi\theta}\alpha_{0},\rme^{\rmi\theta}\alpha_{1}\right)$.
-This can be accomplished by the Hopf fibration \cite{Hatcher2001,MosseriDandoloff2001,Bengtsson2007,wiki:HopfFibration},
+is, $\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$ and $\rme^{\rmi\theta}\alpha_{0}\ket{0}+\rme^{\rmi\theta}\alpha_{1}\ket{1}$
+are considered as the same state. This can be accomplished by the
+Hopf fibration \cite{Hatcher2001,MosseriDandoloff2001,Bengtsson2007,wiki:HopfFibration},
 which can be written down as follows: let $\alpha_{0}=x_{0}+\rmi y_{0}$
@@
 \end{eqnarray}
-By denoting the the three-dimensional vector~$\left(X,Y,Z\right)$
-as $\Hat{a}$, \Eq{A5.eq} implies these transformed coordinates
-obeying 
+By denoting the three-dimensional vector~$\left(X,Y,Z\right)$ as
+$\Hat{a}$, \Eq{A5.eq} implies these transformed coordinates obeying
 \begin{equation}
@@
 \par\end{centering}
-}\hfill{} \caption{(a) The sphere represented by \Eq{A7.eq}, which is the irreducible
-space of one-qubit states, along with a representative set of points
-on the sphere. (b) Representation of the Hopf fibration, Eq.~(\ref{eq:HopfFibration}),
-as a family of circles (the paths of $\rme^{\rmi\theta}$) on the
-three-sphere $\Sphere{3}$. Although $\Sphere{3}$ cannot be directly
-embedded in $\R^{3}$, $\Sphere{3}$ can be regarded as attaching
-two three-dimensional ball on two sides of two-sphere $\Sphere{2}$.
-In this way, each circle in $\Sphere{3}$ corresponding to a single
-point on the sphere in (a) can be represented as a circle in the three-dimensional
-ball. Moreover, points in (a) are color coded corresponding to circles
+}\hfill{} \caption{(a) The two-sphere~$\Sphere{2}$ represented by \Eq{A7.eq}, which
+is the irreducible space of one-qubit states, along with a representative
+set of points on the sphere. Each single point on the sphere in (a)
+corresponding to a circle in (b), and a whole family of circles (the
+paths of $\rme^{\rmi\theta}$) on the three-sphere~$\Sphere{3}$
+represents the Hopf fibration, Eq.~(\ref{eq:HopfFibration}). Although
+$\Sphere{3}$ cannot be directly embedded in $\R^{3}$, three-sphere~$\Sphere{3}$
+can be regarded as attaching two three-dimensional ball on two sides
+of two-sphere~$\Sphere{2}$. In this way, each circle in $\Sphere{3}$
+can be represented as a circle in the three-dimensional ball as shown
+in (b). Moreover, points in (a) are color coded corresponding to circles
 in (b), e.g., one pole contains the red elliptical circle that would

### 2018-03-06 dissertation.tex
dissertation.lyx "2.1.1 The single qubit problem" Updating...

@@
 is, $\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$ and $\rme^{\rmi\theta}\alpha_{0}\ket{0}+\rme^{\rmi\theta}\alpha_{1}\ket{1}$
-are considered as the same state. This can be accomplished by the
-Hopf fibration \cite{Hatcher2001,MosseriDandoloff2001,Bengtsson2007,wiki:HopfFibration},
+are representing the same physical state. This can be accomplished
+by the Hopf fibration \cite{Hatcher2001,MosseriDandoloff2001,Hanson2006,Bengtsson2007,wiki:HopfFibration},
 which can be written down as follows: let $\alpha_{0}=x_{0}+\rmi y_{0}$

### 2018-03-07 dissertation.tex
dissertation.lyx "2.1.1 The single qubit problem" Updating...

@@
 are representing the same physical state. This can be accomplished
-by the Hopf fibration \cite{Hatcher2001,MosseriDandoloff2001,Hanson2006,Bengtsson2007,wiki:HopfFibration},
+by the Hopf fibration \cite{Artin1991,Hatcher2001,MosseriDandoloff2001,Hanson2006,Bengtsson2007,wiki:HopfFibration},
 which can be written down as follows: let $\alpha_{0}=x_{0}+\rmi y_{0}$

### 2018-03-08 dissertation.tex
dissertation.lyx "Chapter 2 Conventional Quantum Theory" Uncommented...

@@
 \usepackage{setspace}
+\usepackage{dsfont}
 
@@
 \newcommand{\VVec}[1]{\vec{\bf #1}}
+\newcommand{\mathReal}{\mathbb{R}}
 \newcommand{\mathComplex}{\mathbb{C}}
@@
 \newcommand{\Sphere}[1]{\mathbf{S}^{#1}}
-\newcommand{\R}{\mathbb{R}}
+\newcommand{\R}{\mathReal}
 \newcommand{\rme}{\mathrm{e}}
 \newcommand{\rmi}{\mathrm{i}}
+\newcommand{\CP}[1]{\mathbf{CP}^{#1}}  % Complex projective space
+\newcommand{\DCP}[1]{\mathbf{DCP}^{#1}} % Discrete complex projective
+\def\fh{\mathfrak{h}}
 
@@
 
-We can reduce 3 real degrees of freedom in \Eq{A5.eq} to 2 real
-degrees of freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
+We can reduce 3 degrees of freedom in \Eq{A5.eq} to 2 degrees of
+freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
 out by the circle $\Sphere{1}$''). The standard form of this maps
@@
 
-\begin{comment}
-
 \subsection{The $n$-qubit problem}
@@
 as $\CP{D-1}$ (see any textbook on geometry \cite{Berger}).
-\end{comment}
 
@@
 \cite{Mermin2007,Jaeger2007}.
-
-\begin{comment}
 
@@
 of the Lie algebra of all observables.
-\end{comment}
 

### 2018-03-09 dissertation.tex
dissertation.lyx "Chapter 3 Quantum Theories and Computing over Finite Fields" Start to uncomment...
dissertation.lyx "Chapter 3 Quantum Theories and Computing over Finite Fields" Updating...
dissertation.lyx "2.1.2 D-dimensional Hilbert Space" Updating...

@@
 \usepackage{graphicx}
+\usepackage[all]{xy}
 
@@
 \newcommand{\rmi}{\mathrm{i}}
-\newcommand{\CP}[1]{\mathbf{CP}^{#1}}  % Complex projective space
-\newcommand{\DCP}[1]{\mathbf{DCP}^{#1}} % Discrete complex projective
+\newcommand{\CP}[1]{\mathComplex\mathbf{P}^{#1}}  % Complex projective space
+\newcommand{\DCP}[1]{\mathbf{D}\mathComplex\mathbf{P}^{#1}} % Discrete complex projective
 \def\fh{\mathfrak{h}}
+\newcommand{\uf}{U_{\!f}}
+\newcommand{\scalarPlus}{+}
+\newcommand{\boolt}{\textsf{Bool}} 
+\newcommand{\bfalse}{\texttt{\textbf{false}}}
+\newcommand{\btrue}{\texttt{\textbf{true}}}
+\newcommand{\dotprod}{dot product}
 
@@
 
-\subsection{The single qubit problem}
+\subsection{Two-dimensional Hilbert Space}
 
@@
 
-\subsection{The $n$-qubit problem}
-
-For $n$ qubits, the irreducible states are encoded in a similar family
-of geometric structures known technically as the complex projective
-space $\CP{D-1}$. We obtain these structures starting with the $D=2^{n}$
-initially unnormalized complex coefficients of the $n$-qubit state
-basis 
-\begin{eqnarray}
-\ket{\Psi} & = & \sum_{i=0}^{D-1}\alpha_{i}\ket{i}\ .\label{N1.eq}
-\end{eqnarray}
-We then follow the analog of the one-qubit procedure: Conservation
-of probability requires that the norm of the vector $\VVec{\alpha}$
-be normalized to unity: 
-\begin{eqnarray}
-\braket{\Psi}{\Psi}=\|\VVec{\alpha}\|^{2} & = & \sum_{i=0}^{D-1}|\alpha_{i}|^{2}\,=\,1\ .\label{probEq1.eq}
-\end{eqnarray}
+\subsection{$D$-dimensional Hilbert Space}
+
+The irreducible states in a $D$-dimensional Hilbert space are encoded
+in a similar family of geometric structures known technically as the
+complex projective space $\CP{D-1}$. We obtain these structures starting
+with the $D$ initially unnormalized complex coefficients of the $D$-dimensional
+basis $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$. We then follow
+the analog of the two-dimensional procedure: Conservation of probability
+requires that the norm of the vector $\VVec{\alpha}$ be normalized
+to unity: 
+\begin{equation}
+\braket{\Psi}{\Psi}=\|\VVec{\alpha}\|^{2}=\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=1\,.\label{probEq1.eq}
+\end{equation}
 Thus the initial equation for the geometry of a quantum state describes
-a \textit{topological sphere\/} $\Sphere{2D-1}$ embedded in $\mathReal^{2D}$.
+a \textit{topological sphere~}$\Sphere{2D-1}$ embedded in $\mathReal^{2D}$.
 To see this, remember that we can write the real and imaginary parts
-of $\alpha_{i}$ as $\alpha_{i}=x_{i}+iy_{i}$, so 
-\begin{eqnarray}
-\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=\sum_{i=0}^{D-1}\left(x_{i}^{\ 2}+y_{i}^{\ 2}\right)=1
-\end{eqnarray}
+of $\alpha_{i}$ as $\alpha_{i}=x_{i}+\rmi y_{i}$, so 
+\begin{equation}
+\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=\sum_{i=0}^{D-1}{x_{i}}^{2}+{y_{i}}^{2}=1
+\end{equation}
 describes the locus of a $2D$-dimensional real unit vector in $\mathReal^{2D}$,
-which is by definition $\Sphere{2D-1}$, the $(2D-1)$-sphere, with
-$D=2^{n}$ for an $n$-qubit state.
+which is by definition $\Sphere{2D-1}$, the $(2D-1)$-sphere.
 
@@
 thus $2D-2$ irreducible real degrees of freedom ($D-1$ complex degrees
-of freedom) for a quantum state with a $D$-dimensional basis, $\{\ket{i}\,|\,i=0,\ldots,D-1\}$.
-
-In summary, the full space of a $D=2^{n}$-dimensional $n$-qubit
-quantum state, including its overall phase defining its relationship
-to other quantum states, is the topological space $\Sphere{2D-1}$.
-For an isolated system, the overall phase is not measurable, and eliminating
-the phase dependence in turn corresponds to identifying $\Sphere{2D-1}$
-as a circle bundle over the base space $\CP{D-1}$, and therefore
-$\CP{D-1}=\CP{2^{n}-1}$ defines the $2D-2$ intrinsic, irreducible,
-degrees of freedom of the isolated $n$-qubit state's dynamics. In
-mathematical notation, this would be written
-
-%% From Wiki: Hopf-fibration: S^1\hookrightarrow S^3 \rightarrow S^2
-\[
-\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}\ ,
-\]
-with $D=2^{n}$ as usual. For $n=1$, the single qubit, we have $2^{n}-1=2-1=1$,
-and the base space of the circle bundle is $\CP{1}=\Sphere{2}$, the
-usual Bloch sphere. Note that only for $n=1$ is this actually a sphere-like
-geometry due to an accident of low-dimensional topology.
+of freedom) for a quantum state with a $D$-dimensional basis, $\set{\ket{i}}{i=0,\ldots,D-1}$.
+
+In summary, the full space of a $D$-dimensional quantum state, including
+its overall phase defining its relationship to other quantum states,
+is the topological space $\Sphere{2D-1}$. For an isolated system,
+the overall phase is not measurable, and eliminating the phase dependence
+in turn corresponds to identifying $\Sphere{2D-1}$ as a circle bundle
+over the base space $\CP{D-1}$, and therefore $\CP{D-1}$ defines
+the $2D-2$ intrinsic, irreducible, degrees of freedom of the isolated
+$D$-dimensional state's dynamics. In mathematical notation, this
+would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$.
+For $D=2$, the single qubit, we have $2-1=1$, and the base space
+of the circle bundle is $\CP{1}=\Sphere{2}$, the usual Bloch sphere.
+Note that only for $D=2$ is this actually a sphere-like geometry
+due to an accident of low-dimensional topology.
 
@@
 
-\begin{comment}
-
-\section{Modal Quantum Computing}
-
-\label{modalquantumcomputing}
+\section{Modal Quantum Computing\label{modalquantumcomputing}}
 
@@
 \begin{array}{@{\!\!}c}
-\hspace*{1.35cm}\Qcircuit@C=1.3em@R=.9em{\lstick{y=\ket{0}}}\end{array}
+\hspace*{1.35cm}\xymatrix@C=0pt{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \gate{~S^{\dagger}~} & \ctrl{3} & \gate{~S^{\dagger}~} & \multimeasureD{3}{\text{measure}}\\
+\lstick{x_{1}=\ket{0}} & \multigate{2}{\otimes S} & \ghost{\uf} & \multigate{2}{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
+\lstick{\ldots} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
+\lstick{x_{n}=\ket{0}} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}
+}
+\end{array}
 \]
@@
 
-%% WE have a problem with notation - what do we use for "dot product"
-%%  and/or "field norm" in the three or four instances below.
-%%  Here is Yu-Tsung's comment:
-
-% Actually, Grove didn't told about any quadratic residues, and didn't
-% defined the field norm. Grove 
-%  used "the quadratic form Q corresponding to a Hermitian form" instead
-% of "field norm." When I wrote 
-% this proof, I really read the following books:
-% [12] Stewart I 2004 Galois theory (Boca Raton: Chapman and Hall/CRC).
-% Field norm defined in almost all field theory books. In particular, in
-% page 197 in Section 18.4  [12].
-% [11] Hardy G H and Wright E M 1938 An Introduction to the Theory of
-% Numbers (Oxford: Oxford University Press).
-% Quadratic residues explained in almost all number theory books. In
-% particular, in page 69 in Chapter VI [11].
-%%  HERMITIAN (outside if needed) \define{dotprod}{dot product}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discrete Quantum Theory (I) }
-
-\label{discretequantumtheoryI}
-
-Our next objective is to develop more realistic discrete quantum theory
-variants that exclude ``supernatural'' algorithms such as the one
-presented above. Our first such plausible framework~\cite{powerdqc}
-is based on complexifiable finite fields. To incorporate complex numbers
-for quantum amplitudes, we exploit the fact that the polynomial $x^{2}+1=0$
-is \emph{irreducible} (has no solution) over a prime field $\ff{p}$
-with $p$ odd if and only if $p$ is of the form~$4\ell+3$, with
-$\ell$ a non-negative integer. In other words, $x^{2}+1=0$ is irreducible
-over $\ff{3},\ff{7},\ff{11},\ff{19},\ldots$. We achieve our goal
-by observing that any field in this family is extensible to a field~$\ff{p^{2}}$
-whose elements can be viewed as discrete complex numbers with the
-real and imaginary parts in~$\ff{p}$. In the field~$\ff{p^{2}}$,
-the Frobenius automorphism of an element $\alpha$ (defined as $\alpha^{p}$)
-represents the usual definition of complex conjugation~\cite{fieldexample}.
-
-The next task is to examine the consequences when we attempt to construct
-$d$-dimensional vector spaces over the complexified fields $\ff{p^{2}}$
-\cite{geom1}. (For readability, instead of writing column vectors,
-we will often use the vector notation $\ket{\Psi}=(\alpha_{0}~\alpha_{1}~\ldots~\alpha_{d-1})^{T}$
-and $\ket{\Phi}=(\beta_{0}~\beta_{1}~\ldots~\beta_{d-1})^{T}$, where
-$(.)^{T}$ is the transpose of the \textit{row} vector $(.)$.) It
-can be shown~\cite{HermitianProd} that, given two vectors 
-\begin{equation}
-\ket{\Psi}=\sum_{i=0}^{d-1}~\alpha_{i}\ket{i}\ ,\ \ket{\Phi}=\sum_{i=0}^{d-1}~\beta_{i}\ket{i},
-\end{equation}
-with scalars $\alpha_{i}$ and $\beta_{i}$ drawn from the field elements,
-and orthonormal basis $\{\ket{i}\}$, the Hermitian \dotprod\ is
-always reducible to the form \vspace{-0.1in}
-
-\begin{equation}
-\ip{\Phi}{\Psi}=\sum_{i=0}^{d-1}~\beta_{i}^{p}~\alpha_{i}^{\;}\ .\vspace{-0.1in}\label{innerprod}
-\end{equation}
-
-This product satisfies conditions A and B below, but not~C, because
-in a finite field, addition can ``wrap around,'' making the concepts
-of positive and negative meaningless and allowing the sum of non-zero
-elements to be zero: 
-\begin{itemize}
-\item A. $\ip{\Phi}{\Psi}$ is the complex conjugate of $\ip{\Psi}{\Phi}$;
-\vspace*{-0.25cm}
-
-\item B. $\ip{\Phi}{\Psi}$ is conjugate linear in its first argument and
-linear in its second argument; \vspace*{-0.25cm}
-
-\item C. $\ip{\Psi}{\Psi}$ is always non-negative and is equal to~0 only
-if $\ket{\Psi}$ is the zero vector. 
-\end{itemize}
-With just conditions A and B, it is possible to recover unitary operators,
-and thus recover much of the relevant structure of Hilbert spaces
-over the field of complex numbers. The failure of condition C, however,
-plays havoc with the traditional notions of ordered probabilities
-as well as the geometric notions of ordered distances and angles,
-whose lengths and cosines, respectively, are normally expressed using
-the inner product~\cite{geom}. In a separate development, we explore
-the geometry of these finite fields and define a discrete version
-of the Hopf fibration extending the Bloch sphere to $n$-qubits, as
-well as determining discrete measures for the relative sizes of the
-entangled, maximally entangled, and unentangled discrete states~\cite{geom1}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\emph{Discrete Quantum Computing with Complexifiable Finite Fields. }
-%% NOTE (ajh): we decided Fp was complexifiable and Fpp was complexified.
-
-\section{Discrete Quantum Computing (I)}
-
-\label{discretequantumcomputingI}
-
-Given a complexified finite field $\ff{p^{2}}$ and its Hermitian
-\dotprod\
-(Eq.~\eqref{innerprod}) much of the structure of conventional quantum
-computing can be recovered. For example, the smallest field~$\ff{3^{2}}$
-is already rich enough to express the standard Deutsch-Jozsa~\cite{NCbook}
-algorithm, which requires only normalized versions of vectors or matrices
-with the scalars $0$, $1$, and $-1$. Similarly, other deterministic
-quantum algorithms (algorithms for which we may determine the outcome
-with certainty), such as Simon's and Bernstein-Vazirani, perform as
-desired~\cite{simon}. Algorithms such as Grover's search will not
-work in the usual way because we lack (the notion of) ordered angles
-and probability in general.
-
-\begin{figure}[t]
-\[
-\begin{array}{c}
-\hspace*{1.5cm}\Qcircuit@C=1.7em@R=.9em{\lstick{y=\ket{0}}}\end{array}
-\]
-\caption[]{Circuit for black box \usat\ in discrete quantum computing.}
-
-\label{fig:dbsearch} 
-\end{figure}
-
-It is possible, in some situations, to exploit the cyclic behavior
-of the field to creatively cancel probability amplitudes and solve
-problems with what again appears to be ``supernatural'' efficiency.
-We illustrate this behavior with the algorithm in Fig.~\ref{fig:dbsearch},
-which is a variant of the one in Fig.~\ref{fig:alg}. Unlike the
-modal quantum theory algorithm, the new algorithm does not always
-succeed deterministically using a constant number of black box evaluations.
-We can, however, show that supernatural behavior occurs if the characteristic
-$p$ of the field divides $2^{N}-1$. For a database of fixed size
-$N$, matching the conditions becomes less likely as the size of the
-field increases. Nevertheless, for a \textit{given\/} field, it is
-always possible to expand any database with dummy records to satisfy
-the divisibility property. Physically, we are taking advantage of
-additional interference processes that happen because of the possibility
-of ``wrapping around'' due to modular arithmetic. We do not know,
-in general, whether this version of discrete quantum computing actually
-enables the rapid solution of NP-complete problems.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  Since forging a connection between  
-% a framework for discrete quantum computing based on complexifiable
-% finite fields and conventional quantum mechanics is blocked in the
-% general case by the violation of condition (C) on inner products, the
-% only logical alternative is to seek a way around the impasse.
-\end{comment}
+\begin{comment}
 
@@
 in conventional quantum computing \cite{Grover:1996:FQM:237814.237866,BennettBernsteinBrassardVazirani1997,Mermin2007,Jaeger2007}.
+\end{comment}
+
+\section{Discrete Quantum Theory (I)\label{discretequantumtheoryI}}
+
+Our next objective is to develop more realistic discrete quantum theory
+variants that exclude ``supernatural'' algorithms such as the one
+presented above. Our first such plausible framework~\cite{powerdqc}
+is based on complexifiable finite fields. To incorporate complex numbers
+for quantum amplitudes, we exploit the fact that the polynomial $x^{2}+1=0$
+is \emph{irreducible} (has no solution) over a prime field $\ff{p}$
+with $p$ odd if and only if $p$ is of the form~$4\ell+3$, with
+$\ell$ a non-negative integer. In other words, $x^{2}+1=0$ is irreducible
+over $\ff{3},\ff{7},\ff{11},\ff{19},\ldots$. We achieve our goal
+by observing that any field in this family is extensible to a field~$\ff{p^{2}}$
+whose elements can be viewed as discrete complex numbers with the
+real and imaginary parts in~$\ff{p}$. In the field~$\ff{p^{2}}$,
+the Frobenius automorphism of an element $\alpha$ (defined as $\alpha^{p}$)
+represents the usual definition of complex conjugation~\cite{fieldexample}.
+
+The next task is to examine the consequences when we attempt to construct
+$d$-dimensional vector spaces over the complexified fields $\ff{p^{2}}$
+\cite{geom1}. (For readability, instead of writing column vectors,
+we will often use the vector notation $\ket{\Psi}=(\alpha_{0}~\alpha_{1}~\ldots~\alpha_{d-1})^{T}$
+and $\ket{\Phi}=(\beta_{0}~\beta_{1}~\ldots~\beta_{d-1})^{T}$, where
+$(.)^{T}$ is the transpose of the \textit{row} vector $(.)$.) It
+can be shown~\cite{HermitianProd} that, given two vectors 
+\begin{equation}
+\ket{\Psi}=\sum_{i=0}^{d-1}~\alpha_{i}\ket{i}\ ,\ \ket{\Phi}=\sum_{i=0}^{d-1}~\beta_{i}\ket{i},
+\end{equation}
+with scalars $\alpha_{i}$ and $\beta_{i}$ drawn from the field elements,
+and orthonormal basis $\{\ket{i}\}$, the Hermitian \dotprod\ is
+always reducible to the form \vspace{-0.1in}
+
+\begin{equation}
+\ip{\Phi}{\Psi}=\sum_{i=0}^{d-1}~\beta_{i}^{p}~\alpha_{i}^{\;}\ .\vspace{-0.1in}\label{innerprod}
+\end{equation}
+
+This product satisfies conditions A and B below, but not~C, because
+in a finite field, addition can ``wrap around,'' making the concepts
+of positive and negative meaningless and allowing the sum of non-zero
+elements to be zero: 
+\begin{itemize}
+\item A. $\ip{\Phi}{\Psi}$ is the complex conjugate of $\ip{\Psi}{\Phi}$;
+\vspace*{-0.25cm}
+
+\item B. $\ip{\Phi}{\Psi}$ is conjugate linear in its first argument and
+linear in its second argument; \vspace*{-0.25cm}
+
+\item C. $\ip{\Psi}{\Psi}$ is always non-negative and is equal to~0 only
+if $\ket{\Psi}$ is the zero vector. 
+\end{itemize}
+With just conditions A and B, it is possible to recover unitary operators,
+and thus recover much of the relevant structure of Hilbert spaces
+over the field of complex numbers. The failure of condition C, however,
+plays havoc with the traditional notions of ordered probabilities
+as well as the geometric notions of ordered distances and angles,
+whose lengths and cosines, respectively, are normally expressed using
+the inner product~\cite{geom}. In a separate development, we explore
+the geometry of these finite fields and define a discrete version
+of the Hopf fibration extending the Bloch sphere to $n$-qubits, as
+well as determining discrete measures for the relative sizes of the
+entangled, maximally entangled, and unentangled discrete states~\cite{geom1}.
+
+\begin{comment}
+
+\section{Vector Spaces over Complexified Finite Fields}
+
+In order to address the intrinsic problems induced by the notion of
+the continuum calculations of the previous section, one is led to
+replace the infinite fields of CQC by discrete computable fields.
+Accomplishing this while maintaining the essential elements of addition
+and multiplication requires a brief excursion into the theory of fields,
+and particularly the theory of finite fields.
+
+\subsection{Background}
+
+Abstract algebra deals with various kinds of algebraic structures,
+such as groups, rings, and fields, each defined by a different system
+of axioms. A field~$\mathbf{F}$ is an algebraic structure consisting
+of a set of elements equipped with the operations of addition, subtraction,
+multiplication, and division \cite{numtheory.ref}. Fields may contain
+an infinite or a finite number of elements. The rational $\mathbb{Q}$,
+real $\mathbb{R}$, and complex numbers $\mathbb{C}$ are examples
+of infinite fields, while the set $\mathbf{F}_{3}=\{0,1,2\}$ under
+the usual multiplication and modular addition is an example of a finite
+field. Finite fields are also known as Galois fields \cite{GT.ref}.
+
+There are two distinguished elements in a field, the addition identity
+$0$, and the multiplication identity $1$. Given the field $\mathbf{F}$,
+the closed operations of addition, ``$+$'', and multiplication,
+``$\gmult$'', satisfy the following set of axioms:
+\begin{enumerate}
+\item $\mathbf{F}$ is an Abelian group under the addition operation $+$
+(additive group)
+\item The multiplication operation $\gmult$ is associative and commutative.
+The field has a multiplicative identity and the property that every
+nonzero element has a multiplicative inverse
+\item Distributive laws: For all $a,b,c\in\mathbf{F}$ 
+\begin{eqnarray}
+a\gmult(b+c)=a\gmult b+a\gmult c\\
+(b+c)\gmult a=b\gmult a+c\gmult a\ .
+\end{eqnarray}
+\end{enumerate}
+{}From now on, unless specified, we will omit the symbol $\gmult$
+whenever we multiply two elements of a field.
+
+Finite fields of $q$ elements, $\Fq=\{0,\ldots,q-1\}$, will play
+a special role in this work. A simple explicit example is the following
+addition and multiplication tables for $\mathbf{F}_{3}$: 
+\[
+\begin{array}{c|ccc}
++ & 0 & 1 & 2\\[0.1in]
+\hline 0 & 0 & 1 & 2\\
+1 & 1 & 2 & 0\\
+2 & 2 & 0 & 1
+\end{array}\hspace*{2cm}\begin{array}{c|ccc}
+\gmult & 0 & 1 & 2\\[0.1in]
+\hline 0 & 0 & 0 & 0\\
+1 & 0 & 1 & 2\\
+2 & 0 & 2 & 1
+\end{array}
+\]
+
+\subsection{Cyclic Properties of Finite Fields}
+
+Finite fields are classified by size. The characteristic of a field
+is the least positive integer $m$ such that $m=1+1+1+\cdots+1\equiv0$,
+and if no such $m$ exists we say that the field has characteristic
+zero (which is the case for infinite fields such as $\mathbb{R}$).
+It turns out that if the characteristic is non-zero it must be a prime
+$p$. For every prime $p$ and positive integer $r$ there is a finite
+field $\Fpx{p^{r}}$ of cardinality $q=p^{r}$ and characteristic
+$p$ (Lagrange's theorem), which is unique up to field isomorphisms.
+For every $a\in\Fq$, $a\neq0$, then $a^{q-1}=1$, implying the Frobenius
+endomorphism (also a consequence of Fermat's little theorem) $a^{q}=a$,
+which in turn permits us to write the multiplicative inverse of any
+non-zero element in the field as $a^{-1}=a^{q-2}$, since $a^{q-2}a=a^{q-1}=1$.
+Every subfield of the field $\Fq$, of cardinality $q=p^{r}$, has
+$p^{r'}$ elements with some $r'$ dividing $r$, and for a given
+$r'$ it is unique. Notice that a fundamental difference between finite
+and infinite fields is one of topology: finite fields induce a compact
+structure because of their modular arithmetic, permitting \textit{wrapping
+around}, while that is not the case for fields of characteristic zero.
+This feature may lead to fundamental physical consequences.
+
+\subsection{Complexified Finite Fields}
+
+Consider the polynomial $x^{2}+1=0$ over a finite field $\Fp$. It
+is known that this polynomial does not have solutions in the field
+precisely when the prime $p$ is congruent to $3\imod{4}$ (see, e.g.,
+\cite{numtheory.ref}).
+
+For such primes, it is therefore possible to construct an extended
+field $\Fpp$ whose elements are of the form $\alpha=a+ib$ with $a\in\Fp$,
+$b\in\Fp$, and $i$ the root of the polynomial $x^{2}+1=0$. Since
+the field elements $a+ib$ behave like discrete versions of the complex
+numbers, we will refer to fields $\Fp$ with prime $p$ congruent
+to $3\imod{4}$ as \emph{complexifiable finite fields}, and $i$-extended
+fields $\Fpp$ with $p$ congruent to $3\imod{4}$ as \emph{complexified
+finite fields}.
+
+In a complexified finite field $\Fpp$, the Frobenius automorphism
+that maps $\alpha\in\Fpp$ to $\alpha^{p}\in\Fpp$ acts like complex
+conjugation. For example, in $\Fppx{3}$, we have $(2+i)^{3}=8+12i-6-i=2+11i$
+which, in the field, is equal to $2-i$ since $11\equiv-1\imod{3}$.
+
+We define the \emph{field norm} $\fnorm{\cdot}$ as the map from $(a+ib)\in\Fpp$
+to $a^{2}+b^{2}\in\Fp$, 
+\begin{equation}
+\fnorm{\alpha=a+ib}=a^{2}+b^{2}\ .\label{fieldnorm.eq}
+\end{equation}
+We avoid the square root in the discrete field framework because,
+unlike the continuous case, the square root does not always exist.
+
+\subsection{Vector Spaces}
+
+In this section we want to build a theory of discrete vector spaces
+that approximates as closely as possible the features of conventional
+quantum theory. Such a structure would ideally consist of the following:
+(i) a vector space over the field of complex numbers, and (ii) an
+inner product $\ip{\Phi}{\Psi}$ associating to each pair of vectors
+a complex number, and satisfying the following properties: 
+\begin{itemize}
+\item[A.] $\ip{\Phi}{\Psi}$ is the complex conjugate of $\ip{\Psi}{\Phi}$; 
+\item[B.] $\ip{\Phi}{\Psi}$ is conjugate linear in its first argument and
+linear in its second argument; 
+\item[C.] $\ip{\Psi}{\Psi}$ is always non-negative and is equal to~0 only
+if $\ket{\Psi}$ is the zero vector. 
+\end{itemize}
+It turns out that a vector space defined over a finite field cannot
+have an inner product satisfying the properties above. However, we
+will introduce an Hermitian ``dot product'' satisfying some of those
+properties.
+
+We are interested in the $n$-qubit vector space ${\cal H}$ of dimension
+$D=2^{n}$ defined over the complexified field $\Fpp$. Let $\ket{\Psi}=(\alpha_{0}~\alpha_{1}~\ldots~\alpha_{D-1})^{T}$
+and $\ket{\Phi}=(\beta_{0}~\beta_{1}~\ldots~\beta_{D-1})^{T}$ represent
+vectors in ${\cal H}$, with numbers $\alpha_{i}$ and $\beta_{i}$
+drawn from $\Fpp$, and where $(\cdot)^{T}$ is the transpose.
+
+\begin{definition}{[}Hermitian dot product{]} Given vectors $\ket{\Phi}$
+and $\ket{\Psi}\in{\cal H}$, the Hermitian dot product of these vectors
+is: 
+\begin{equation}
+\ip{\Phi}{\Psi}=\sum_{i=0}^{D-1}~\beta_{i}^{p}~\alpha_{i}^{\;}\ .
+\end{equation}
+\end{definition} Two vectors $\ket{\Phi}$ and $\ket{\Psi}\in{\cal H}$
+are said to be orthogonal if $\ip{\Phi}{\Psi}=0$. This product satisfies
+conditions A and B for inner products but violates condition C since
+in every finite field there always exists a non-zero vector $\ket{\Psi}$
+such that $\ip{\Psi}{\Psi}=0$. The reason is that addition in finite
+fields eventually ``wraps around'' (because of their cyclic or modular
+structure), allowing the sum of non-zero elements to be zero. The
+fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$ decreases
+with the order $p$.
+
+For any vector $\ket{\Psi}=(\alpha_{0}~\alpha_{1}~\ldots~\alpha_{D-1})^{T}$,
+the Hermitian dot product $\ip{\Psi}{\Psi}$ is equal to $\sum_{i=0}^{D-1}~\fnorm{\alpha_{i}}$,
+which is the sum of the field norms for the complex coefficients.
+For convenience, we now extend the field norm to include vector arguments
+by defining 
+\begin{equation}
+\fnorm{\ket{\Psi}}=\ip{\Psi}{\Psi}=\sum_{i=0}^{D-1}~\fnorm{\alpha_{i}}\ .\label{fnormD.eq}
+\end{equation}
+The field norm of a vector can vanish for non-vanishing vectors.
+
+For vectors $\ket{\Psi}$ such that $\ip{\Psi}{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}^{p}\,\alpha_{i}^{\;}=\sum_{i=0}^{D-1}\alpha_{i}^{p+1}=\sum_{i=0}^{D-1}|\alpha_{i}|^{2}$
+has a square root in the field, one can define the following ``norm'':
+\begin{equation}
+||\Psi||=\sqrt{\ip{\Psi}{\Psi}}\ ,\label{norm-eq}
+\end{equation}
+which is valid only on a subspace of the field norm for finite fields.
+
+%There is an alternative way of defining a proper inner product over a subset of the %field $\Fpp$.
+Consider prime numbers $p= 8 \prod_{l=1}^k q_l -1$, where  %$q_l$ are odd primes.
+This subset of the primes congruent to $3 \imod 4$ has the %special properti
+
+\section{Irreducible Discrete $n$-qubit States: Generalized Discrete Bloch
+Sphere}
+
+\label{DQCnqubitBloch.sec}
+
+In the one-qubit state with coefficients in $\Fpp$, the discrete
+analog of the Bloch sphere is constructed by exact analogy to the
+continuous case: we first require that the coefficients of the single
+qubit basis obey 
+\begin{equation}
+\|\psi_{1}\|^{2}=|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=1\label{DQA2.eq}
+\end{equation}
+in the discrete field. In \ref{appU.sec}, we show that there are
+$p(p^{2}-1)$ such values. Given this requirement, which is similar
+in form to the conservation of probability, but not as useful due
+to the lack of orderable probability values, we can immediately conclude
+that the discrete analog of the Hopf fibration is again 
+\begin{eqnarray}
+X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\nonumber \\
+Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\label{DQA6.eq}\\
+Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}=x_{0}^{\ 2}+y_{0}^{\ 2}-x_{1}^{\ 2}-y_{1}^{\ 2}\ ,\nonumber 
+\end{eqnarray}
+but now with all computations in $(\mbox{mod}~p)$. At this point
+one simply writes down all possible discrete values for the complex
+numbers $\{\alpha_{0},\alpha_{1}\}$ satisfying Eq.~(\ref{DQA2.eq})
+and enumerates those that project to the same value of $\{X,Y,Z\}$.
+This equivalence class is the discrete analog of the circle in the
+complex plane that was eliminated in the continuous case. In \ref{appH.sec},
+we show that $p+1$ discrete values of $\{\alpha_{0},\alpha_{1}\}$
+with unit norm map to the same point under the Hopf map \Eq{DQA6.eq};
+we may think of these as discrete circles or projective lines of equivalent,
+physically indistinguishable, complex phase. The surviving $p(p-1)$
+values of $\{\alpha_{0},\alpha_{1}\}$ correspond to irreducible physical
+states of the discrete single qubit system. %% Several examples are shown in Figure \ref{bloch.fig}. %%Thus,
+for example, choosing the underlying field to be $\Fppx{3}$, there
+are exactly 6 single-qubit state vectors to populate the Bloch sphere;
+the four equivalent phase-multiples mapping to each of the six points
+on the $\Fppx{3}$ Bloch sphere are collapsed and regarded as physically
+indistinguishable. In Figure \ref{bloch.fig}, we plot the irreducible
+states on the Bloch sphere for $p=3$, $7$, and $11$. Note that
+the Cartesian lengths of the real vectors corresponding to the points
+on the Bloch sphere vary considerably due to the nature of discrete
+fields; we have artificially normalized them to a ``continuous world''
+unit radius sphere for conceptual clarity.
+
+\begin{figure}[htb]
+%\vspace{-0.2in}  %% \includegraphics[width=0.9\columnwidth]{./Bloch_sphere.pdf}%%\includegraphics[width=2.0\columnwidth]{./picA.png}%%\includegraphics[width=2.0\columnwidth]{./picB.png}
+
+\begin{centering}
+\hspace*{-0.5cm}\includegraphics[width=1.1\columnwidth]{../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/picC.png}
+%%\includegraphics[width=0.5\textwidth]{./picAB.eps}\vspace{-0.2in}
+ %% adjust blank space?
+\par\end{centering}
+\caption{Schematically normalized plots of the elements of the discrete Bloch
+sphere, the irreducible single-qubit (two-dimensional) state vectors
+with unit norm over the field $\Fpp$. We show the results for $p=3$,
+$7$, and $11$. For example, in $\Fppx{3}$, there are 24 vectors
+of unit norm, but only the 6 inequivalent classes appear in the plot.
+The $p+1=4$ equivalent vectors in each class differ only by a complex
+discrete phase.}
+\label{bloch.fig} 
+\end{figure}
+
+\subsection{Counting states on the $n$-qubit Bloch sphere}
+
+We have the unique opportunity in the finite-field approach to quantum
+computing to precisely identify and enumerate the physical states.
+In the conventional theory, as we have seen, we employ a generalized
+Hopf fibration on the normalized states to project out a circle of
+phase-equivalent states, yielding the generalized Bloch sphere.
+
+In the introduction to this section, we sketched the counting of the
+irreducible single-qubit discrete states. To count the number of inequivalent
+discrete states for the general $n$-qubit case with coefficients
+in $\Fpp$, we first must find the set of unit-norm states, and then
+determine the equivalence classes of unit-norm states under discrete
+phase transformations; we can then enumerate the list of states on
+the discrete generalized Bloch sphere. By executing computer searches
+of these spaces, we discovered an hypothesis for a closed-form solution
+for the counting of the states, and were then able to find a rigorous
+inductive proof of the enumeration, which is presented in the Appendix.
+
+This process of describing the discrete $n$-qubit irreducible states
+can again be understood geometrically by following the discrete analog
+of the Hopf fibration. First, we construct the discrete version of
+the quadratic unit-length form that automatically annihilates the
+distinction among states differing only by a discrete phase, 
+\begin{eqnarray}
+\hspace*{-0.5cm}\Vec{X}=(|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots)\ ,
+\end{eqnarray}
+where 
+\begin{eqnarray}
+\Vec{X}\cdot\Vec{X}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
+\end{eqnarray}
+{}From \ref{appH.sec}, we know that $p+1$ elements of this discrete
+$\Sphere{2\times2^{n}-1}$ structure map to the \textit{same point\/}
+in $\Vec{X}$. Each set of $(p+1)$ redundant points is, geometrically
+speaking, the \textit{discrete Hopf fibration circle\/} living above
+each \textit{irreducible\/} point of the $n$-qubit state description.
+These $p+1$ points are interpretable as the $p$ finite points plus
+the single point at infinity of the projective discrete line (see,
+e.g., \cite{Arnold}).
+
+The next part of this argument is the determination of the unit-norm
+states, effectively the space of allowed discrete partitions of unity;
+we cannot exactly call these ``probability-conserving'' sectors
+of the state coefficients since we do not have a well defined notion
+of probability, but we do have a well-defined notion of partition
+of unity. The tally of unit-norm states is $p^{2^{n}-1}(p^{2^{n}}-1)$
+(see \ref{appU.sec}) compared to the total number $p^{2\times2^{n}}$
+of possible complex integer state vectors that could be chosen. This
+unit-norm state structure is the discrete analog of $\Sphere{2\times2^{n}-1}$.
+
+Finally, we repeat the last step of the $n$-qubit continuous Hopf
+fibration process for discrete $n$-qubit states, eliminating the
+discrete set of $p+1$ equivalent points that map to the same point
+$\Vec{X}$ on the generalized $n$-qubit Bloch sphere. Dividing the
+tally $p^{2^{n}-1}(p^{2^{n}}-1)$ of unit norm states by the $p+1$
+elements of each phase-equivalent discrete circle, we find 
+\[
+\frac{p^{2^{n}-1}(p^{2^{n}}-1)}{p+1}=p^{2^{n}-1}(p-1)\,\prod_{k=1}^{n-1}(p^{2^{k}}+1)
+\]
+as the total count of unique irreducible states in a discrete $n$-qubit
+configuration (see \ref{appI.sec}). The resulting object is precisely
+the discrete version of $\CP{D-1}$, which we might call a \textit{discrete
+complex projective space\/} or $\DCP{D-1}$, where $D=2^{n}$ as
+usual.
+
+\Comment{
+
+\subsection{Counting states on the $n$-qubit Bloch sphere}
+
+Although we do not have a rigorous proof for the counting of discrete
+unit-norm states and the number of irreducible unit-norm states in
+the discrete generalized Bloch sphere for $n$-qubit states with coefficients
+in $\Fpp$, we have run extensive computer searches of the state features
+for a range of compatible primes $p$ and number of qubits $n$. From
+these experimental investigations, we have induced a closed-form solution
+for the counting that agrees for every possible combination of parameters
+that can be computed in reasonable time (the computational complexity
+becomes intractable very quickly).
+
+For $n$-qubit discrete states with coefficients in $\Fpp$, our calculation
+begins with an enumeration of all possible $2^{n}$-tuples of state
+coefficients in $\Fpp$; then the moduli-squared of these tuples are
+summed and compared to unity in $(\mbox{mod}~p)$. Those that survive
+are accumulated in a list of allowed discrete partitions of unity;
+we cannot exactly call these ``probability-conserving'' sectors
+of the state coefficients since we do not have a well defined notion
+of probability, but we do have a well-defined notion of partition
+of unity. The heuristic number that results for the tally of unit-norm
+states is $p^{2^{n}-1}(p^{2^{n}}-1)$, compared to the total number
+$p^{2\times2^{n}}$ of possible complex integer state vectors that
+could be chosen. This unit-norm state structure is now the discrete
+analog of $\Sphere{2\times2^{n}-1}$.
+
+Finally, we construct the discrete version of the quadratic unit-length
+form that automatically annihilates the distinction among states differing
+only by a discrete phase, 
+\begin{eqnarray}
+\hspace*{-0.5cm}\Vec{X}=\{|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\}\ ,
+\end{eqnarray}
+where 
+\begin{eqnarray}
+\Vec{X}\cdot\Vec{X}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
+\end{eqnarray}
+Computing all the elements of the discrete $\Sphere{2\times2^{n}-1}$
+structure that map to the \textit{same point\/} in $\Vec{X}$, we
+find a $(p+1)$-fold redundancy, exactly as for the one-qubit case;
+each set of $(p+1)$ redundant points is, geometrically speaking,
+the \textit{discrete Hopf fibration circle\/} (see, e.g., Arnold
+\cite{Arnold}) living above each \textit{irreducible\/} point of
+the $n$-qubit state description.
+
+In summary, when the $n$-qubit continuous Hopf fibration process
+is repeated for the discrete analog of $n$-qubit states, we find
+that that analog of a phase ``circle'' is a discrete set $p+1$
+equivalent points that map to the same point $\Vec{X}$ on the generalized
+$n$-qubit Bloch sphere, and therefore there are a total of $p^{2^{n}-1}(p^{2^{n}}-1)/(p+1)$
+unique irreducible states in a discrete $n$-qubit configuration.
+The resulting object is precisely the discrete version of $\CP{D-1}$,
+which we might call a \textit{discrete complex projective space\/}
+or $\DCP{D-1}$. }
+
+\section{Geometry of Entangled States}
+
+Without regard to uniqueness, an $n$-qubit state with discrete complex
+coefficients in $\Fpp$ will have the total possible space of coefficients
+with dimension $p^{2\times2^{n}}$ (including the null state). Imposing
+the condition of a length-one norm %% AMR: replaced 'inner-product' by 'norm'in
+$\Fp$, this number is reduced to $p^{2^{n}-1}(p^{2^{n}}-1)$. The
+ratio of all the states to the unit-norm states is asymptotically
+$p$: 
+\begin{eqnarray}
+\frac{p^{2^{n}+1}}{p^{2^{n}}-1}\rightarrow p\ ,
+\end{eqnarray}
+so there are roughly $p$ sets of coefficients, for any number of
+qubits $n$, that are discarded for each retained unit-length state
+vector. A factor of $p+1$ more states are discarded in forming the
+discrete Bloch sphere of irreducible states. Selected plots of the
+full space compared to both the unit-norm space and the irreducible
+space for a selection of complexified finite fields are shown in Figure
+\ref{statePlot3Unit.fig} for 1, 2, 3, and 4 qubits. %Figure \ref{statePlot3Unit.fig} adds the size of the irreducible state%space at the bottom.
+
+%% Source of this is%%  ~hansona/home2/papers/dqc-geom-2012/00mathFigs/A-Test-Galois-Nqubit.nb
+
+%\begin{figure}[htb]%\begin{center}%\includegraphics[width=1.0\columnwidth]{./statePlot1.pdf}%%\vspace{-0.2in}  %% adjust blank space?%\end{center}% \caption{Logarithmic plot of the number of discrete unnormalized%states (top, in red), vs the number of normalized discrete states%(bottom, in blue) for the first 6 $\Fpp$-compatible primes,  (3, 7,%11, 19, 23, 31), for the number of qubits 1, 2, 3 and 4.
+}% \label{statePlotUnit.fig}%\end{figure}
+
+\begin{figure}[htb]
+\begin{centering}
+\includegraphics[width=1\columnwidth]{../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/statePlot3.pdf}
+%\vspace{-0.2in}  %% adjust blank space?
+\par\end{centering}
+\caption{Logarithmic plot of the number of discrete unnormalized states (top,
+in red), vs the number of normalized discrete states (middle, in blue),
+vs the irreducible states (bottom, in green) for the first 6 $\Fpp$-compatible
+primes, (3, 7, 11, 19, 23, 31), for the number of qubits 1, 2, 3 and
+4. }
+\label{statePlot3Unit.fig} 
+\end{figure}
+
+\subsection{Unentangled vs Entangled Discrete States}
+
+For a given $p$ and the corresponding complexified field $\Fpp$,
+the $n$-qubit discrete quantum states with coefficients in $\Fpp$
+can be classified by their degree of entanglement to a level of precision
+that is unavailable in the continuous theory. We look first at the
+unentangled $n$-qubit states, which are direct product states of
+the form 
+\begin{equation}
+\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}\ .\label{dqcNqUntg.eq}
+\end{equation}
+Without regard to normalization, there are $(p^{4})^{n}$ possible
+unentangled states out of the total of $p^{2\times2^{n}}$ states
+noted above. When we normalize the individual product states to unit
+norm, the norm of the entire $n$-qubit state becomes the product
+of those unit norms, and is automatically normalized to one. We have
+already seen that each single-qubit normalized state in the tensor
+product \Eq{dqcNqUntg.eq} has precisely $p(p-1)$ irreducible components.
+
+\subsection{Completely Unentangled States and the Discrete Bloch Sphere}
+
+In effect, the irreducible states for unentangled $n$-qubit configurations
+reduce to a single Bloch sphere for each one-qubit component $\ket{\psi_{j}}$,
+and thus the whole set of states is defined by an $n$-tuple of discrete
+Bloch sphere coordinates. Since each Bloch sphere in $\Fpp$ has $p(p-1)$
+distinct irreducible components, we have 
+\[
+\mbox{{\bf Count of Unentangled States}}=p^{n}(p-1)^{n}\ .
+\]
+
+We know that the total number of irreducible states (points in the
+generalized $\DCP{2^{n}-1}$ Bloch sphere) for an $n$-qubit state
+is $p^{2^{n}-1}(p^{2^{n}}-1)/(p+1)$, and so the number of states
+containing some measure of entanglement is 
+\begin{eqnarray*}
+\mbox{{\bf Count of Entangled States}}=\frac{p^{2^{n}-1}(p^{2^{n}}-1)}{p+1}-p^{n}(p-1)^{n}\ .
+\end{eqnarray*}
+Therefore a very small fraction of the unit norm states are unentangled.
+
+\subsection{Partial entanglement}
+
+A partially entangled state can be constructed by taking individual
+component states to enter as direct products, starting by picking
+$n$ distinct single qubits to be unentangled ($n=2$ exhausts its
+freedom with one pick). Then we can choose $n(n-1)/2$ pairs of distinct
+qubits as product states ($n=3$ exhausts its freedom with one pick),
+and so on. Then, starting with $n=3$, we can pick fully entangled
+2-qubit subspaces as product spaces, combining them with single-qubit
+product components ($n=3$ has no single-qubit freedom left after
+picking any of its three 2-qubit subspaces), and so on. Precise measures
+of entanglement such as that given in \Eq{purityMeasure.eq} can
+then be applied just as in the continuous case.
+
+\subsection{Maximal entanglement}
+
+Numerical and analytic calculations of the entanglement measure \Eq{purityMeasure.eq},
+taken $(\mbox{mod}~p)$, extend to the best of our knowledge to the
+discrete case, so that the unentangled states constructed above have
+$P_{\fh}=1$. This leads us to study one final aspect of the discrete
+$n$-qubit states, namely the \textit{maximally\/} entangled states
+with $P_{\fh}=0$.
+
+Computing some examples for various $n$ and small values of $p$,
+one can verify explicitly that unit-norm unentangled states for $n=2$,
+$p=\{3,7,11,19,\ldots\}$ occur with frequency 
+\[
+(p+1)p^{2}(p-1)^{2}=\{144,14112,145200,2339280,\ldots\}\ ,
+\]
+and for general $n$, $(p+1)p^{n}(p-1)^{n}$.
+
+The irreducible state counts are reduced by $(p+1)$, giving 
+\[
+p^{2}(p-1)^{2}=\{36,1764,12100,116964,\ldots\}\ ,
+\]
+and in general for $n$-qubits, $p^{n}(p-1)^{n}$ instances of pure
+states with $P_{\fh}=1$.
+
+Repeating the computation to discover the frequency of maximally entangled
+(purity $P_{\fh}=0$ states), we find $p^{n+1}(p-1)(p+1)^{n}$ maximally
+entangled states, with example frequencies for two qubits of 
+\[
+p^{3}(p-1)(p+1)^{2}=\{864,131712,1916640,49384800,\ldots\}\ .
+\]
+
+The irreducible state counts for maximal entanglement are reduced
+by $(p+1)$, giving for $n=2$ 
+\[
+p^{3}(p^{2}-1)=\{216,16464,159720,2469240,\ldots\}\ ,
+\]
+and in general for $n$-qubits, $p^{n+1}(p-1)(p+1)^{n-1}$ instances
+of pure states with $P_{\fh}=0$.
+
+Therefore, the ratio of maximally entangled to unentangled states
+is 
+\[
+\mbox{{\bf Max Entangled/Unentangled}}=p\left(\frac{p+1}{p-1}\right)^{n-1}\ .
+\]
+
+\section{Summary}
+
+Given a discrete basis for the complex coefficients of an $n$-qubit
+quantum state, DQC permits us in principle to explicitly determine
+the relative frequencies of phases and to determine exactly the generalized
+Bloch sphere coordinates of the irreducible states. The size of the
+set of states that must be taken as equivalent to get irreducibility
+is the size of the ``circle'' or phase group, and this is $p+1$
+for any $p$ and for any $n$ (related to the size of the finite projective
+line, see \cite{Arnold}). Exploring the discrete manifestation of
+the purity measure \Eq{purityMeasure.eq}, our DQC approach can determine
+not only the size of the irreducible space of states, but also the
+relative sizes of the unentangled and entangled states for $n$ discrete
+qubits.
+
+\vspace{0.5in}
+
+\noindent \textbf{References} \vspace*{0.5cm}
+
+\bibitem{GeomQStates2008} I. Bengtsson and K. Zyczkowski, \textit{Geometry
+of Quantum States: An Introduction to Quantum Entanglement} (Cambridge
+University Press, Cambridge, 2008).
+
+\bibitem{mosseri2001} R. Mosseri and R. Dandoloff, \textit{J. Phys.
+A: Math. Gen.} \textbf{34}, 10243 (2001).
+
+\bibitem{Arnold} V. I. Arnold, \textit{Dynamics, Statistics and Projective
+Geometry of Galois Fields\/} (Cambridge University Press, Cambridge,
+2011).
+
+\bibitem{Turing37} A. M. Turing, \textit{Proceedings of the London
+Mathematical Society} Series 2, \textbf{42}, 230 (1937). Errata appeared
+in Series 2, \textbf{43} 544 (1937).
+
+\bibitem{Minsky67} M. Minsky, \textit{Computation: Finite and Infinite
+Machines} (Prentice-Hall, Englewood Cliffs, 1967). See chapter 9,
+``The Computable Real Numbers.''
+
+\bibitem{Chaitin} G. J. Chaitin, \textit{Thinking about Gödel and
+Turing} (World Scientific, Singapore, 2007).
+
+\bibitem{Feynman} R. P. Feynman, \textit{Int. J. Theor. Phys.} \textbf{21},
+467 (1982).
+
+\bibitem{Landauer} R. Landauer, \textit{Physics Letters A\/} \textbf{217},
+188 (1996).
+
+\bibitem{SchuWest2010} B. Schumacher and M. D. Westmoreland, \textit{Found.
+Phys. \/} \textbf{42}, 918 (2012).
+
+\bibitem{James2011} R. P. James, G. Ortiz, and A. Sabry, \texttt{http://arxiv.org/abs/1101.3764}.
+
+\bibitem{HOSW2011} A. J. Hanson, G. Ortiz, A. Sabry, and J. Willcock,
+\texttt{http://arxiv.org/abs/1104.1630}.
+
+\bibitem{Berger} M. Berger and B. Gostiaux, \textit{Differential
+Geometry: Manifolds, Curves, and Surfaces\/} (Springer-Verlag, New
+York, 1988).
+
+\bibitem{numtheory.ref-1} G. H. Hardy and E. M. Wright, \textit{An
+Introduction to the Theory of Numbers\/} (Oxford University Press,
+Oxford, 2006).
+
+\bibitem{GT.ref-1} I. Stewart, \textit{Galois theory\/} (Chapman
+and Hall/CRC, Boca Raton, 2004). \Comment{
+
+\bibitem{WB.ref} Wildberger N J 2005 \textit{Divine Proportions:
+Rational Trigonometry to Universal Geometry} (Sydney: Wild Egg Books)
+
+\bibitem{OT} Ovsienko V and Tabachnikov S 2005 \textit{Projective
+Differential Geometry Old and New} (Cambridge: Cambridge University
+Press)
+
+\bibitem{VY} Veblen O and J. W. Young J W 1946 \textit{Projective
+Geometry Vol. 2} (Blaisdell Publishing Company), pp 55–57
+
+\bibitem{Ztransform} Campello de Souza R M, de Oliveira H M and Silva
+D 2002 The Z Transform over Finite Fields \textit{International Telecommunications
+Symposium, ITS 2002, Brazil} }
+
+\bibitem{Barnum2003} H. Barnum, E. Knill, G. Ortiz, and L. Viola,
+\textit{Phys. Rev. A} \textbf{68}, 032308 (2003).
+
+\bibitem{Barnum2004} H. Barnum, E. Knill, G. Ortiz, R. Somma, and
+L. Viola, \textit{Phys. Rev. Lett.} \textbf{92}, 107902 (2004). 
+\end{comment}
+
+\section{Discrete Quantum Computing (I)\label{discretequantumcomputingI}}
+
+Given a complexified finite field $\ff{p^{2}}$ and its Hermitian
+\dotprod\
+(Eq.~\eqref{innerprod}) much of the structure of conventional quantum
+computing can be recovered. For example, the smallest field~$\ff{3^{2}}$
+is already rich enough to express the standard Deutsch-Jozsa~\cite{NCbook}
+algorithm, which requires only normalized versions of vectors or matrices
+with the scalars $0$, $1$, and $-1$. Similarly, other deterministic
+quantum algorithms (algorithms for which we may determine the outcome
+with certainty), such as Simon's and Bernstein-Vazirani, perform as
+desired~\cite{simon}. Algorithms such as Grover's search will not
+work in the usual way because we lack (the notion of) ordered angles
+and probability in general.
+
+\begin{figure}[t]
+\[
+\begin{array}{c}
+\hspace*{1.5cm}\xymatrix@C=0pt{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \qw & \multimeasureD{3}{\text{measure}}\\
+\lstick{x_{1}=\ket{0}} & \multigate{2}{H} & \ghost{\uf} & \multigate{2}{H} & \ghost{\text{measure}}\\
+\lstick{\ldots} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}\\
+\lstick{x_{n}=\ket{0}} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}
+}
+\end{array}
+\]
+\caption[]{Circuit for black box \usat\ in discrete quantum computing.}
+\label{fig:dbsearch} 
+\end{figure}
+
+It is possible, in some situations, to exploit the cyclic behavior
+of the field to creatively cancel probability amplitudes and solve
+problems with what again appears to be ``supernatural'' efficiency.
+We illustrate this behavior with the algorithm in Fig.~\ref{fig:dbsearch},
+which is a variant of the one in Fig.~\ref{fig:alg}. Unlike the
+modal quantum theory algorithm, the new algorithm does not always
+succeed deterministically using a constant number of black box evaluations.
+We can, however, show that supernatural behavior occurs if the characteristic
+$p$ of the field divides $2^{N}-1$. For a database of fixed size
+$N$, matching the conditions becomes less likely as the size of the
+field increases. Nevertheless, for a \textit{given\/} field, it is
+always possible to expand any database with dummy records to satisfy
+the divisibility property. Physically, we are taking advantage of
+additional interference processes that happen because of the possibility
+of ``wrapping around'' due to modular arithmetic. We do not know,
+in general, whether this version of discrete quantum computing actually
+enables the rapid solution of NP-complete problems
+
+.%
+\begin{comment}
 
@@
 database search problem for certain database sizes.
+\end{comment}
 

### 2018-03-09 dissertation.tex
dissertation.lyx "2.1.3 Explicit generalization of the Hopf fibration construction" Cleaned up...

@@
 \begin{equation}
-S(\Hat{a},\Hat{b},t)=\Hat{a}\,\frac{\sin((1-t)\omega)}{\sin\omega}\,+\,\Hat{b}\,\frac{\sin(t\omega)}{\sin\omega}\ ,\label{slerp.eq}
+S\left(\Hat{a},\Hat{b},t\right)=\Hat{a}\,\frac{\sin((1-t)\omega)}{\sin\omega}\,+\,\Hat{b}\,\frac{\sin(t\omega)}{\sin\omega}\,,\label{slerp.eq}
 \end{equation}
@@
 
-\subsection{Explicit $n$-qubit generalization of the Hopf fibration construction}
-
-For one qubit, we could easily solve the problem of reducing the full
-unit-norm space to its irreducible components $\Vec{X}=(X,Y,Z)$ characterizing
-the Bloch sphere. We have just argued that essentially the same process
-is possible for $n$-qubits: in the abstract argument, we simply identify
-the family of coefficients $\{\alpha_{i}\}$ as being the same if
-they differ only by an overall phase $\rme^{\rmi\theta}$. However,
-in practice this is not a construction that is easy to realize in
-a practical computation. We now outline an explicit algorithm for
-accomplishing the reduction to the irreducible $n$-qubit state space
-$\CP{D-1}$; this construction will turn out to be useful for the
-validation of our discrete results to follow below.
-
-We begin by noting that a natural quantity characterizing an $n$-qubit
-system is its \textit{density matrix\/}, $\rho=\left[\alpha_{i}\alpha_{j}^{*}\right]$,
-or 
-\begin{equation}
-\rho=\left[\begin{array}{cccc}
-|\alpha_{0}|^{2} & \alpha_{0}\alpha_{1}^{*} & \cdots & \alpha_{0}\alpha_{D-1}^{*}\\
+\subsection{Explicit generalization of the Hopf fibration construction}
+
+For a two-dimensional system, we could easily solve the problem of
+reducing the full unit-norm space to its irreducible components $\Hat{a}=\left(X,Y,Z\right)$
+characterizing the Bloch sphere. We have just argued that essentially
+the same process is possible for $D$-dimensional system: in the abstract
+argument, we simply identify the family of coefficients $\left\{ \alpha_{i}\right\} $
+as being the same if they differ only by an overall phase $\rme^{\rmi\theta}$.
+However, in practice this is not a construction that is easy to realize
+in a practical computation. We now outline an explicit algorithm for
+accomplishing the reduction to the irreducible $D$-dimensional state
+space $\CP{D-1}$; this construction will turn out to be useful for
+the validation of our discrete results to follow below.
+
+Given a normalized pure state $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$,
+a natural quantity characterizing an $D$-dimensional system is its
+\textit{density matrix}, $\rho=\op{\Psi}{\Psi}$, or 
+\begin{equation}
+\rho=\begin{bmatrix}|\alpha_{0}|^{2} & \alpha_{0}\alpha_{1}^{*} & \cdots & \alpha_{0}\alpha_{D-1}^{*}\\
 \alpha_{1}\alpha_{0}^{*} & |\alpha_{1}|^{2} & \cdots & \alpha_{1}\alpha_{D-1}^{*}\\
@@
 \alpha_{D-1}\alpha_{0}^{*} & \cdots & \alpha_{D-1}\alpha_{D-2}^{*} & |\alpha_{D-1}|^{2}
-\end{array}\right]\ .\label{nqDensity.eq}
-\end{equation}
-
+\end{bmatrix}\,.\label{nqDensity.eq}
+\end{equation}
 We can now use the complex generalization of the classical Veronese
 coordinate system for projective geometry to remove the overall phase
-ambiguity $\rme^{\rmi\theta}$ from the $n$-qubit states. If we take
-a particular weighting of the elements of the density matrix $\rho$,
-we can construct a \textit{unit vector\/} of real dimension $D^{2}$
+ambiguity $\rme^{\rmi\theta}$ from the $D$-dimensional states. If
+we take a particular weighting of the elements of the density matrix~$\rho$,
+we can construct a \textit{unit vector} of real dimension $D^{2}$
 with the form: 
 \begin{equation}
-\Vec{X}=(|\alpha_{i}|^{2},\ldots,\sqrt{2}\,\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\,\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots)\ ,\label{nqCoords.eq}
+\Hat{a}=\left(|\alpha_{i}|^{2},\ldots,\sqrt{2}\,\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\,\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\right)\,,\label{nqCoords.eq}
 \end{equation}
 where 
-\begin{eqnarray}
-\Vec{X}\cdot\Vec{X}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
-\end{eqnarray}
-This construction gives an explicit embedding of the $(D-1)$-dimensional
-complex, or $(2D-2)=(2^{n+1}-2)$-dimensional real, object in a real
-space of dimension $D^{2}=2^{2n}$. However, this is somewhat subtle
-because the vector is of unit length, so technically the embedding
-space is a sphere of dimension $D^{2}-1=2^{2n}-1$ embedded in $\R^{D^{2}}$;
-the one-qubit irreducible states could be represented in a 4D embedding,
-but the magnitude of every coordinate would be one; furthermore, the
-object embedded in the resulting $\Sphere{3}$ is indeed $\Sphere{2}$
+\begin{equation}
+\Hat{a}\cdot\Hat{a}=\sum_{i=0}^{D-1}\left(\left|\alpha_{i}\right|^{2}\right)^{2}+\sum_{i=0}^{D-1}\sum_{\substack{j=0\\
+j\ne i
+}
+}^{D-1}\left(\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}+\left(\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)\left(\sum_{j=0}^{D-1}\left|\alpha_{j}\right|^{2}\right)=1\,.
+\end{equation}
+This construction gives an explicit embedding of the $\left(D-1\right)$-dimensional
+complex, or $\left(2D-2\right)$-dimensional real, object in a real
+space of dimension $D^{2}$. However, this is somewhat subtle because
+the vector is of unit length, so technically the embedding space is
+a sphere of dimension $D^{2}-1$ embedded in $\R^{D^{2}}$. For example,
+the two-dimensional irreducible states could be represented in a four-dimensional
+embedding, but the magnitude of every coordinate would be one; furthermore,
+the object embedded in the resulting $\Sphere{3}$ is indeed $\Sphere{2}$
 because we can fix one complex coordinate to be unity, and let one
 vary, giving a total of two irreducible dimensions. In fact one must
-choose \textit{two\/} coordinate patches, one covering one pole of
-$\Sphere{2}$ with coordinates 
-\begin{eqnarray}
-\begin{array}{ccc}
-\alpha_{0} & = & 1+0i\\
-\alpha_{1} & = & x_{1}+iy_{1}
-\end{array}
-\end{eqnarray}
+choose \textit{two} coordinate patches, one covering one pole of $\Sphere{2}$
+with coordinates $\alpha_{0}=1+\rmi0$ and $\alpha_{1}=x_{1}+\rmi y_{1}$,
 and the other patch covering the other pole of $\Sphere{2}$ with
-coordinates 
-\begin{eqnarray}
-\begin{array}{ccc}
-\alpha_{0} & = & x_{0}+iy_{0}\\
-\alpha_{1} & = & 1+0i\ .
-\end{array}
-\end{eqnarray}
-
-We finally see that the irreducible $n$-qubit state space $\CP{D-1}$
+coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=1+\rmi0$.
+
+We finally see that the irreducible $D$-dimensional state space $\CP{D-1}$
 is described by $D$ projectively equivalent coordinates, one of which
@@
 is a standard feature of the topology of non-trivial manifolds such
-as $\CP{D-1}$ (see any textbook on geometry \cite{Berger}).
+as $\CP{D-1}$ (see any textbook on geometry~\cite{Berger_1988}).
 
@@
 \begin{eqnarray}
-\hspace*{-0.5cm}\Vec{X}=(|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots)\ ,
+\hspace*{-0.5cm}\Hat{a}=(|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots)\ ,
 \end{eqnarray}
@@
 \begin{eqnarray}
-\Vec{X}\cdot\Vec{X}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
+\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
 \end{eqnarray}
@@
 $\Sphere{2\times2^{n}-1}$ structure map to the \textit{same point\/}
-in $\Vec{X}$. Each set of $(p+1)$ redundant points is, geometrically
+in $\Hat{a}$. Each set of $(p+1)$ redundant points is, geometrically
 speaking, the \textit{discrete Hopf fibration circle\/} living above
@@
 discrete set of $p+1$ equivalent points that map to the same point
-$\Vec{X}$ on the generalized $n$-qubit Bloch sphere. Dividing the
+$\Hat{a}$ on the generalized $n$-qubit Bloch sphere. Dividing the
 tally $p^{2^{n}-1}(p^{2^{n}}-1)$ of unit norm states by the $p+1$
@@
 \begin{eqnarray}
-\hspace*{-0.5cm}\Vec{X}=\{|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\}\ ,
+\hspace*{-0.5cm}\Hat{a}=\{|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\}\ ,
 \end{eqnarray}
@@
 \begin{eqnarray}
-\Vec{X}\cdot\Vec{X}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
+\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
 \end{eqnarray}
 Computing all the elements of the discrete $\Sphere{2\times2^{n}-1}$
-structure that map to the \textit{same point\/} in $\Vec{X}$, we
+structure that map to the \textit{same point\/} in $\Hat{a}$, we
 find a $(p+1)$-fold redundancy, exactly as for the one-qubit case;
@@
 that that analog of a phase ``circle'' is a discrete set $p+1$
-equivalent points that map to the same point $\Vec{X}$ on the generalized
+equivalent points that map to the same point $\Hat{a}$ on the generalized
 $n$-qubit Bloch sphere, and therefore there are a total of $p^{2^{n}-1}(p^{2^{n}}-1)/(p+1)$

### 2018-03-10 dissertation.tex
dissertation.lyx "2.2 Quantum Circuit Model" Updating...

@@
 
-\todo{Table of symbols?}
-
 \chapter{Introduction}
@@
 
+\begin{comment}
 An $n$-qubit pure state in the conventional quantum theory (CQT)
@@
 point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
-also known as the complex projective space~$\mathbb{CP}^{2^{n}-1}$
-\cite{Hatcher2001,Bengtsson2007}. These irreducible quantum states
-can also be classified as product states and entangled states, and
-the latter one plays the essential role for pure-state algorithms
-\cite{Mermin2007,Jaeger2007}.
+also known as the complex projective space~$\CP{2^{n}-1}$ \cite{Hatcher2001,Bengtsson2007}.
+These irreducible quantum states can also be classified as product
+states and entangled states, and the latter one plays the essential
+role for pure-state algorithms \cite{Mermin2007,Jaeger2007}.
+\end{comment}
+It has been 36 years since Feynman~\cite{Feynman1982Simulating}
+proposed the idea about quantum computation. Although there are many
+models for quantum computing, the circuit model is still one of the
+most widespread models~\cite{544199} no matter whether in theoretical
+study or in building a real quantum computation. Information in a
+quantum circuit is stored in qubits. Each qubit is a two-dimensional
+quantum system. For a two-qubit system, if the first and second qubit
+are described as the state~$\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$
+and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}$, the state of
+the whole system is their tensor product 
+\begin{equation}
+\begin{aligned} & \ket{\psi}\ket{\phi}=\ket{\psi}\otimes\ket{\phi}=\left(\alpha_{0}\ket{0}+\alpha_{1}\ket{1}\right)\otimes\left(\beta_{0}\ket{0}+\beta_{1}\ket{1}\right)\\
+= & \alpha_{0}\beta_{0}\ket{0}\otimes\ket{0}+\alpha_{0}\beta_{1}\ket{0}\otimes\ket{1}+\alpha_{1}\beta_{0}\ket{1}\otimes\ket{0}+\alpha_{1}\beta_{1}\ket{1}\otimes\ket{1}\\
+= & \alpha_{0}\beta_{0}\ket{0}\ket{0}+\alpha_{0}\beta_{1}\ket{0}\ket{1}+\alpha_{1}\beta_{0}\ket{1}\ket{0}+\alpha_{1}\beta_{1}\ket{1}\ket{1}
+\end{aligned}
+\end{equation}
+.
 
@@
 be written as a product of states of each subsystem. That is, a state
-$\ket{\Psi}$ is entangled if 
-\begin{eqnarray}
-\ket{\Psi}\ne\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}},
-\end{eqnarray}
+$\ket{\Psi}$ is entangled if $\ket{\Psi}\ne\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$,
 where $\ket{\psi_{j}}$ refers to an arbitrary state of the $j$-th
@@
 of the Lie algebra of all observables.
+
+\subsection{Deutsch Algorithm}
 

### 2018-03-10 dissertation.tex
dissertation.lyx "2.2 Quantum Circuit Model" Updating...

@@
 choose \textit{two} coordinate patches, one covering one pole of $\Sphere{2}$
-with coordinates $\alpha_{0}=1+\rmi0$ and $\alpha_{1}=x_{1}+\rmi y_{1}$,
+with coordinates $\alpha_{0}=0$ and $\alpha_{1}=x_{1}+\rmi y_{1}$,
 and the other patch covering the other pole of $\Sphere{2}$ with
-coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=1+\rmi0$.
+coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=0$.
 
@@
 \begin{aligned} & \ket{\psi}\ket{\phi}=\ket{\psi}\otimes\ket{\phi}=\left(\alpha_{0}\ket{0}+\alpha_{1}\ket{1}\right)\otimes\left(\beta_{0}\ket{0}+\beta_{1}\ket{1}\right)\\
-= & \alpha_{0}\beta_{0}\ket{0}\otimes\ket{0}+\alpha_{0}\beta_{1}\ket{0}\otimes\ket{1}+\alpha_{1}\beta_{0}\ket{1}\otimes\ket{0}+\alpha_{1}\beta_{1}\ket{1}\otimes\ket{1}\\
-= & \alpha_{0}\beta_{0}\ket{0}\ket{0}+\alpha_{0}\beta_{1}\ket{0}\ket{1}+\alpha_{1}\beta_{0}\ket{1}\ket{0}+\alpha_{1}\beta_{1}\ket{1}\ket{1}
+={} & \alpha_{0}\beta_{0}\ket{0}\otimes\ket{0}+\alpha_{0}\beta_{1}\ket{0}\otimes\ket{1}+\alpha_{1}\beta_{0}\ket{1}\otimes\ket{0}+\alpha_{1}\beta_{1}\ket{1}\otimes\ket{1}\\
+={} & \alpha_{0}\beta_{0}\ket{0}\ket{0}+\alpha_{0}\beta_{1}\ket{0}\ket{1}+\alpha_{1}\beta_{0}\ket{1}\ket{0}+\alpha_{1}\beta_{1}\ket{1}\ket{1}
 \end{aligned}
 \end{equation}
-.
+in the four-dimensional Hilbert space. For a $n$-qubit system, if
+we describe the $j$-th qubit as the state~$\ket{\psi_{j}}$, the
+state of the whole system is tensor product of all subsystems $\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$
+in the Hilbert space of dimension $2^{n}$.
 

### 2018-03-11 dissertation.tex
dissertation.lyx "2.2.1 The geometry of entanglement" Updated...

@@
 \newcommand{\dotprod}{dot product}
+\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
 
@@
 state of the whole system is tensor product of all subsystems $\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$
-in the Hilbert space of dimension $2^{n}$.
+in the Hilbert space of dimension $2^{n}$. However, not all quantum
+system can be expressed as the tensor product of its subsystems. This
+kind of system is called entangled, and will be described in the next
+section.
 
 \subsection{The geometry of entanglement}
+
+\todo{{Need to define }(partial) trace and mixed state before this
+subsection...}
 
@@
 to saying that if one calculates the reduced density operator $\rho_{j}$
-of the $j$th subsystem by tracing out all the other subsystems, $\rho_{j}={\sf tr}_{\{1,\cdots,j-1,j+1,\cdots,n\}}(\rho)$,
-with $j=1,\cdots,n$ and $\rho=\ket{\Psi}\bra{\Psi}$, the normalized
-state $\ket{\Psi}$, $\langle\Psi|\Psi\rangle=1$, is entangled if
-and only if at least one subsystem state is \textit{mixed\/}; i.e.,
-${\sf tr}_{j}(\rho_{j}^{2})<1$. For example, consider 
-\begin{eqnarray}
-\rho_{j}=\frac{1}{2}(\mathds{1}+\sum\limits _{\mu=x,y,z}\langle\sigma_{\mu}^{j}\rangle\ \sigma_{\mu}^{j}),
-\end{eqnarray}
+of the $j$-th subsystem by tracing out all the other subsystems,
+$\rho_{j}=\Tr_{\{1,\cdots,j-1,j+1,\cdots,n\}}\left(\rho\right)$,
+with $j=1,\cdots,n$ and $\rho=\op{\Psi}{\Psi}$, the normalized state~$\ket{\Psi}$
+is entangled if and only if at least one subsystem state is \textit{mixed};
+i.e., $\Tr_{j}\left(\rho_{j}^{2}\right)<1$. For example, consider
+\begin{equation}
+\rho_{j}=\frac{1}{2}\left(\sigma_{0}+\sum\limits _{\mu=x,y,z}\expval{\sigma_{\mu}^{j}}\sigma_{\mu}^{j}\right)\,,
+\end{equation}
 where $\sigma_{\mu}^{j}$, $\mu=x,y,z$, are the Pauli operators acting
-on the $j$-th spin, 
-\begin{equation}
-\sigma_{\mu}^{j}=\overbrace{\mathds{1}\otimes\mathds{1}\otimes\cdots\otimes\underbrace{\sigma_{\mu}}_{j^{th}\ \mbox{factor}}\otimes\cdots\otimes\mathds{1}}^{n\ \mbox{factors}}\;,\label{pauli3}
+on the $j$-th spin~\cite{544199}, 
+\begin{equation}
+\sigma_{\mu}^{j}=\overbrace{\sigma_{0}\otimes\cdots\otimes\sigma_{0}\otimes\underbrace{\sigma_{\mu}}_{j^{th}\ \mbox{factor}}\otimes\sigma_{0}\otimes\cdots\otimes\sigma_{0}}^{n\ \mbox{factors}}\,,\label{pauli3}
 \end{equation}
 with 
-\begin{eqnarray}
-\hspace*{-0.5cm}\sigma_{x}=\left(\begin{array}{cc}
+\begin{equation}
+\begin{aligned}\sigma_{0} & =\left(\begin{array}{cc}
+1 & 0\\
+0 & 1
+\end{array}\right)\,, & \sigma_{x} & =\left(\begin{array}{cc}
 0 & 1\\
 1 & 0
-\end{array}\right),\sigma_{y}=\left(\begin{array}{cc}
+\end{array}\right)\,, & \sigma_{y} & =\left(\begin{array}{cc}
 0 & -i\\
 i & 0
-\end{array}\right),\sigma_{z}=\left(\begin{array}{cc}
+\end{array}\right)\,, & \sigma_{z} & =\left(\begin{array}{cc}
 1 & 0\\
 0 & -1
-\end{array}\right),
-\end{eqnarray}
-and $\langle\sigma_{\mu}^{j}\rangle=\langle\Psi|\sigma_{\mu}^{j}|\Psi\rangle$
-denotes the corresponding expectation value. The vectors ${\bf X}_{j}=(\langle\sigma_{x}^{j}\rangle,\langle\sigma_{y}^{j}\rangle,\langle\sigma_{y}^{j}\rangle)$,
-${\bf X}_{j}\in{\mathbb{R}}^{3}$, allow a geometric representation
-of each reduced state in ${\mathbb{R}}^{3}$, satisfying $0\le\|{\bf X}_{j}\|\le1$.
-Since ${\sf tr}_{j}(\rho_{j}^{2})=\frac{1}{2}(1+\|{\bf X}_{j}\|^{2})$,
-the state $\ket{\Psi}$ is entangled if $\|{\bf X}_{j}\|<1$ for at
-least one $j$, represented by a point {\em inside} the corresponding
+\end{array}\right)\,,\end{aligned}
+\end{equation}
+and $\expval{\sigma_{\mu}^{j}}=\melem{\Psi}{\sigma_{\mu}^{j}}{\Psi}$
+denotes the corresponding expectation value. The vectors 
+\begin{equation}
+{\bf X}_{j}=\left(\expval{\sigma_{x}^{j}},\expval{\sigma_{y}^{j}},\expval{\sigma_{y}^{j}}\right)\in\mathbb{R}^{3}
+\end{equation}
+allow a geometric representation of each reduced state in $\mathbb{R}^{3}$,
+satisfying $0\le\left\Vert {\bf X}_{j}\right\Vert \le1$. Since $\Tr_{j}\left(\rho_{j}^{2}\right)=\frac{1}{2}\left(1+\left\Vert {\bf X}_{j}\right\Vert ^{2}\right)$,
+the state $\ket{\Psi}$ is entangled if $\left\Vert {\bf X}_{j}\right\Vert <1$
+for at least one $j$, represented by a point \emph{inside} the corresponding
 local Bloch sphere. One may therefore consider $\ket{\Psi}$ to be
-maximally entangled if $\|{\bf X}_{j}\|=0$ for all $j$. On the other
-hand, the state $\ket{\Psi}$ is unentangled (i.e., a product state)
-if $\|{\bf X}_{j}\|=1$ for all $j$, corresponding to points lying
-on the surface of the Bloch sphere.
+maximally entangled if $\left\Vert {\bf X}_{j}\right\Vert =0$ for
+all $j$. On the other hand, the state $\ket{\Psi}$ is unentangled
+(i.e., a product state) if $\left\Vert {\bf X}_{j}\right\Vert =1$
+for all $j$, corresponding to points lying on the surface of the
+Bloch sphere.
 
 A natural geometric measure of multipartite entanglement is obtained
-by defining the {\em purity of a state relative to a set of observables}
-\cite{Barnum2003,Barnum2004}. If the set is chosen to be the set
-of {\em all local observables}, i.e., corresponding to each of
-the subsystems that compose the actual system, one recovers the standard
-notion of entanglement for multipartite systems. For example, if the
-system consists of $n$ qubits, we obtain a measure of conventional
-entanglement by calculating the purity relative to the set $\fh=\{\sigma_{x}^{1},\sigma_{y}^{1},\sigma_{z}^{1},\ldots,\sigma_{x}^{n},\sigma_{y}^{n},\sigma_{z}^{n}\}$,
-\begin{equation}
-P_{\fh}=\frac{1}{n}\sum\limits _{j=1}^{n}\sum\limits _{\mu=x,y,z}\langle\sigma_{\mu}^{j}\rangle^{2}\:,\ \ 0\leq P_{\fh}\leq1\ .\label{purityMeasure.eq}
+by defining the \emph{purity of a state relative to a set of observables}
+\cite{BKOV2003,BKOSV2004}. If the set is chosen to be the set of
+\emph{all local observables}, i.e., corresponding to each of the subsystems
+that compose the actual system, one recovers the standard notion of
+entanglement for multipartite systems. For example, if the system
+consists of $n$ qubits, we obtain a measure of conventional entanglement
+by calculating the purity relative to the set $\fh=\left\{ \sigma_{x}^{1},\sigma_{y}^{1},\sigma_{z}^{1},\ldots,\sigma_{x}^{n},\sigma_{y}^{n},\sigma_{z}^{n}\right\} $,
+\begin{equation}
+\begin{aligned}P_{\fh} & =\frac{1}{n}\sum\limits _{j=1}^{n}\sum\limits _{\mu=x,y,z}\expval{\sigma_{\mu}^{j}}^{2}\,, & 0\leq P_{\fh}\leq1\,.\end{aligned}
+\label{purityMeasure.eq}
 \end{equation}
@@
 states are the generalized coherent states obtained by applying any
-group operation to a reference state such as $\ket{\sf0}=\ket{0}\otimes\cdots\otimes\ket{0}$.
+group operation to a reference state such as $\ket{\overline{0}}=\ket{0}\otimes\cdots\otimes\ket{0}$.
 For the algebra $\fh$ of local observables, such group operations
@@
 which have maximum purity (i.e., $P_{\fh}=1$). Other states such
-as the Greenberger-Horne-Zeilinger state $\ket{\Psi}=\ket{{\sf GHZ}_{n}}=\frac{1}{\sqrt{2}}(\ket{0}\otimes\cdots\otimes\ket{0}+\ket{1}\otimes\cdots\otimes\ket{1})$
+as the Greenberger-Horne-Zeilinger state $\ket{\Psi}=\ket{\mathsf{GHZ}_{n}}=\frac{1}{\sqrt{2}}\left(\ket{0}\otimes\cdots\otimes\ket{0}+\ket{1}\otimes\cdots\otimes\ket{1}\right)$
 are (maximally) entangled relative to the set of local observables
@@
 is given by the set of all observables. In this case, the purity takes
-its maximum value independently of the pure quantum state \cite{Barnum2003,Barnum2004},
+its maximum value independently of the pure quantum state \cite{BKOV2003,BKOSV2004},
 expressing the fact that any state is a generalized coherent state

### 2018-03-12 dissertation.tex
dissertation.lyx "2.1 Geometrical Structure of States" Updating...

@@
 $D$-dimensional state's dynamics. In mathematical notation, this
-would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$.
+would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$\todo{Citation?}.
 For $D=2$, the single qubit, we have $2-1=1$, and the base space
@@
 \begin{equation}
-\rho=\begin{bmatrix}|\alpha_{0}|^{2} & \alpha_{0}\alpha_{1}^{*} & \cdots & \alpha_{0}\alpha_{D-1}^{*}\\
+\rho=\begin{pmatrix}|\alpha_{0}|^{2} & \alpha_{0}\alpha_{1}^{*} & \cdots & \alpha_{0}\alpha_{D-1}^{*}\\
 \alpha_{1}\alpha_{0}^{*} & |\alpha_{1}|^{2} & \cdots & \alpha_{1}\alpha_{D-1}^{*}\\
@@
 \alpha_{D-1}\alpha_{0}^{*} & \cdots & \alpha_{D-1}\alpha_{D-2}^{*} & |\alpha_{D-1}|^{2}
-\end{bmatrix}\,.\label{nqDensity.eq}
+\end{pmatrix}\,.\label{nqDensity.eq}
 \end{equation}
@@
 choose \textit{two} coordinate patches, one covering one pole of $\Sphere{2}$
-with coordinates $\alpha_{0}=0$ and $\alpha_{1}=x_{1}+\rmi y_{1}$,
+with coordinates $\alpha_{0}=1+\rmi0$ and $\alpha_{1}=x_{1}+\rmi y_{1}$,
 and the other patch covering the other pole of $\Sphere{2}$ with
-coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=0$.
+coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=1+\rmi0$.
+\todo{Explain the last part more clear or add a picture.}
 
@@
 
-\todo{{Need to define }(partial) trace and mixed state before this
+\todo{Need to define (partial) trace and mixed state before this
 subsection...}

### 2018-03-12 dissertation.tex
dissertation.lyx "2.2 Quantum Circuit Model" Updating...

@@
 most widespread models~\cite{544199} no matter whether in theoretical
-study or in building a real quantum computation. Information in a
-quantum circuit is stored in qubits. Each qubit is a two-dimensional
-quantum system. For a two-qubit system, if the first and second qubit
-are described as the state~$\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$
+study or in building a real quantum computer. Information in a quantum
+circuit is stored in qubits. Each qubit is a two-dimensional quantum
+system. For a two-qubit system, if the first and second qubit are
+described as the state~$\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$
 and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}$, the state of
@@
 state of the whole system is tensor product of all subsystems $\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$
-in the Hilbert space of dimension $2^{n}$. However, not all quantum
+in the Hilbert space of dimension $D=2^{n}$. However, not all quantum
 system can be expressed as the tensor product of its subsystems. This
 kind of system is called entangled, and will be described in the next
-section.
+section.\todo{This paragraph need to be polished.}
 
@@
 \subsection{Deutsch Algorithm}
+
+\todo{Further explain $\sigma_{\mu}^{j}$ used as a quantum circuit,
+control not, the Deutsch quantum black box~\cite{NCbook}, and maybe
+Deutsch Algorithm...}
 

### 2018-03-13 dissertation.tex
dissertation.lyx "Chapter 2 Conventional Quantum Theory" Updating...

@@
 \end{array}\right)\,, & \sigma_{y} & =\left(\begin{array}{cc}
-0 & -i\\
-i & 0
+0 & -\rmi\\
+\rmi & 0
 \end{array}\right)\,, & \sigma_{z} & =\left(\begin{array}{cc}
@@
 \todo{Explain enough background knowledge to support the discussion
-about contextuality in the end of Sec.~\ref{modalquantum}.}
+about contextuality in the end of Sec.~\ref{modalquantum}. I have
+typed some literature review in writing course, but I need to decide
+whether it could be used or not before finish Sec.~\ref{sec:fuzzy}.}
 

### 2018-03-13 dissertation.tex
dissertation.lyx "Chapter 3 Quantum Theories and Computing over Finite Fields" Updating...

@@
 \begin{equation}
-\begin{aligned}X_{0} & =\begin{pmatrix}1 & 0\\
+\begin{aligned}\sigma_{0} & =\begin{pmatrix}1 & 0\\
 0 & 1
@@
 1 & 1
-\end{pmatrix}\,, & D_{1} & =\begin{pmatrix}0 & 1\\
+\end{pmatrix}\,, &  & \begin{pmatrix}0 & 1\\
 1 & 1
 \end{pmatrix}\,,\\
-X_{1} & =\begin{pmatrix}0 & 1\\
+\sigma_{x} & =\begin{pmatrix}0 & 1\\
 1 & 0
@@
 0 & 1
-\end{pmatrix}\,, & D_{2} & =\begin{pmatrix}1 & 1\\
+\end{pmatrix}\,, &  & \begin{pmatrix}1 & 1\\
 1 & 0
@@
 classical model of logical programming with a feature that has quantum-like
-behavior~\cite{qc-rel}. In a conventional logic program, answers
+behavior~\cite{finiteQC}. In a conventional logic program, answers
 produced by different execution paths are collected in a sequence
@@
 it possesses ``supernatural'' computational power. For example,
-one can solve a black box version of the \usat\ problem~\cite{wsusat}
+one can solve a black box version of the \usat\ problem~\cite{usat}
 in a way that outperforms conventional quantum computing. The classical

### 2018-03-13 dissertation.tex
dissertation.lyx "3.3 Modal Quantum Computing" Updating...

@@
 \usepackage{comment}
-\usepackage[all]{xy}
 \usepackage{framed}
@@
 \usepackage{dsfont}
+
+\usepackage[all]{xy}
+\newcommand{\xyR}[1]{\xymatrixrowsep={#1}}
+\newcommand{\xyC}[1]{\xymatrixcolsep={#1}}
 
@@
 in a way that outperforms conventional quantum computing. The classical
-\usat\ problem (also known as \texttt{USAT} or \texttt{UNAMBIGUOUS-SAT})
-is the problem of deciding whether a given boolean formula has a satisfying
-assignment, assuming that it has at most one such assignment~\cite{complexity}.
+\usat\ problem (also known as $\lang{USAT}$ or $\lang{UNAMBIGUOUS-SAT}$\todo{Add
+citation about where these two names come from.}) is the problem
+of deciding whether a given boolean formula has a satisfying assignment,
+assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
 This problem is, in a precise sense~\cite{Valiant198685}, just as
@@
 to this generalized problem can be used to solve an unstructured database
-search of size $N$ using $O(\log{N})$ black box evaluations by binary
-search on the database. This algorithm then outperforms the known
-asymptotic bound $O(\sqrt{N})$ for unstructured database search in
-conventional quantum computing.
+search of size $N$ using $O\left(\log N\right)$ black box evaluations
+by binary search on the database. This algorithm then outperforms
+the known asymptotic bound $O\left(\sqrt{N}\right)$ for unstructured
+database search in conventional quantum computing.
 
@@
 \[
-\begin{array}{@{\!\!}c}
-\hspace*{1.35cm}\xymatrix@C=0pt{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \gate{~S^{\dagger}~} & \ctrl{3} & \gate{~S^{\dagger}~} & \multimeasureD{3}{\text{measure}}\\
+\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \gate{~S^{\dagger}~} & \ctrl{3} & \gate{~S^{\dagger}~} & \multimeasureD{3}{\text{measure}}\\
 \lstick{x_{1}=\ket{0}} & \multigate{2}{\otimes S} & \ghost{\uf} & \multigate{2}{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
@@
 }
-\end{array}
 \]
-\caption[]{\label{fig:alg}Circuit for black box \usat\ in modal quantum theory
-over the field $\ff{2}$. $\uf$ is a Deutsch quantum black box~\cite{NCbook}
+\caption{\label{fig:alg}Circuit for black box \usat\ in modal quantum theory
+over the field $\ff{2}$. $\uf$ is a Deutsch quantum black box~\cite{544199}
 with $\uf\ket{y}\ket{\overline{x}}~=~\ket{y\scalarPlus f(\overline{x})}\ket{\overline{x}}$,
@@
 \bibitem{VY} Veblen O and J. W. Young J W 1946 \textit{Projective
-Geometry Vol. 2} (Blaisdell Publishing Company), pp 55–57
+Geometry Vol. 2} (Blaisdell Publishing Company), pp 55??7
 
@@
 \[
-\begin{array}{c}
-\hspace*{1.5cm}\xymatrix@C=0pt{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \qw & \multimeasureD{3}{\text{measure}}\\
+\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \qw & \multimeasureD{3}{\text{measure}}\\
 \lstick{x_{1}=\ket{0}} & \multigate{2}{H} & \ghost{\uf} & \multigate{2}{H} & \ghost{\text{measure}}\\
@@
 }
-\end{array}
 \]

### 2018-03-14 dissertation.tex
dissertation.lyx Updating...

@@
 we describe the $j$-th qubit as the state~$\ket{\psi_{j}}$, the
-state of the whole system is tensor product of all subsystems $\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$
+state of the whole system is tensor product of all subsystems 
+\begin{equation}
+\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}=\ket{\psi_{1}}\cdots\ket{\psi_{j}}\cdots\ket{\psi_{n}}
+\end{equation}
 in the Hilbert space of dimension $D=2^{n}$. However, not all quantum
@@
 
-\subsection{Deutsch Algorithm}
+\subsection{Quantum Circuits\label{subsec:Quantum-Circuits}}
 
@@
 map that is guaranteed never to produce the zero vector from a valid
-state. There are exactly $6$ such maps: 
+state. There are exactly $6$ such maps, and their matrix representation
+with respect to the standard basis are: 
 \begin{equation}
@@
 \end{aligned}
+\label{eq:MQT-dynamics}
+\end{equation}
+For example, 
+\begin{equation}
+\begin{aligned}S\ket{0} & =\begin{pmatrix}1 & 0\\
+1 & 1
+\end{pmatrix}\begin{pmatrix}1\\
+0
+\end{pmatrix}=\begin{pmatrix}1\\
+1
+\end{pmatrix}=\ket{+}\,, & S\ket{+} & =\begin{pmatrix}1 & 0\\
+1 & 1
+\end{pmatrix}\begin{pmatrix}1\\
+1
+\end{pmatrix}=\begin{pmatrix}1\\
+0
+\end{pmatrix}=\ket{0}\,.\end{aligned}
+\label{eq:MQT-dynamics-apply}
 \end{equation}
@@
 
-The state is initialized to $\ket{0}\ket{\overline{0}}$, with $\ket{\overline{0}}=\ket{0}\ket{0}\cdots\ket{0}$,
-i.e., the tensor product of $n$ $\ket{0}$ states. Applying the map
-$S$ (defined in the previous section) to each qubit in the second
-component of the state produces $\ket{0}\ket{\overline{+}}$ where
-$\ket{\overline{+}}$ denotes the sequence $\ket{+}\ldots\ket{+}$
-of length $n$. Applying $\uf$ to the entire state has no effect
-since $U_{f}$ is the identity when $f$ is unsatisfiable. Applying
-$S$ to each qubit in the second component of the state produces $\ket{0}\ket{\overline{0}}$.
+\todo{This part use $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$
+while previous parts use $\ket{\Psi}=\ket{\psi_{1}}\cdots\ket{\psi_{j}}\cdots\ket{\psi_{n}}$.
+Moreover, bar is heavily used in QIVPM discussion later, so maybe
+not using bar here????}The state is initialized to $\ket{0}\ket{\overline{0}}$,
+with $\ket{\overline{0}}=\ket{0}\ket{0}\cdots\ket{0}$, i.e., the
+tensor product of $n$ $\ket{0}$ states. As Eq.~(\ref{eq:MQT-dynamics-apply}),
+applying the map $S$ to each qubit in the second component of the
+state produces $\ket{0}\ket{\overline{+}}$ where $\ket{\overline{+}}$
+denotes the sequence $\ket{+}\ldots\ket{+}$ of length $n$. Applying
+$\uf$ to the entire state has no effect since $U_{f}$ is the identity
+when $f$ is unsatisfiable. Applying $S$ to each qubit in the second
+component of the state produces $\ket{0}\ket{\overline{0}}$. Applying
+$S^{\dagger}$ to the first component leaves the state unchanged.
+As the first component of the state is $0$, applying the map $\sigma_{0}$
+(which is the identity) leaves the state unchanged.\todo{Control-not
+need to be defined and explained in Sec.~\ref{subsec:Quantum-Circuits}}
 Applying $S^{\dagger}$ to the first component leaves the state unchanged.
-As the first component of the state is 0, applying the map $X_{0}$
-(which is the identity) leaves the state unchanged. Applying $S^{\dagger}$
-to the first component leaves the state unchanged. Measuring the state
-will deterministically produce $\ket{0}\ket{\overline{0}}$.
+Measuring the state will deterministically produce $\ket{0}\ket{\overline{0}}$.
 

### 2018-03-15 dissertation.tex
dissertation.lyx "3.3 Modal Quantum Computing" Updating...

@@
 \caption{\label{fig:alg}Circuit for black box \usat\ in modal quantum theory
-over the field $\ff{2}$. $\uf$ is a Deutsch quantum black box~\cite{544199}
-with $\uf\ket{y}\ket{\overline{x}}~=~\ket{y\scalarPlus f(\overline{x})}\ket{\overline{x}}$,
-where $\overline{x}$ denotes a sequence $x_{1},x_{2},\ldots,x_{n}$
-of $n$ bits. For further notation see text.}
+over the field $\ff{2}$. For further notation see text.}
 \end{figure}
@@
 with a classical function $f:\boolt^{n}\rightarrow\boolt$ that takes
-$n$ bits and returns at most one \btrue\ result. Then we can give
-an algorithm (see Fig.~\ref{fig:alg}) taking as input such a classical
-function that decides, deterministically and in a constant number
-of black box evaluations, whether $f$ is satisfiable or not:
+$n$ bits and returns at most one \btrue\ result. To build a quantum
+algorithm, $f$ is first represented as the Deutsch quantum black
+box~$\uf$ with \cite{Deutsch1985,544199} 
+\begin{equation}
+\uf\ket{y}\ket{\overline{x}}=\begin{cases}
+\ket{y}\ket{\overline{x}}\,, & \textrm{if }f\left(\overline{x}\right)=\bfalse\,;\\
+\ket{\mathsf{not}\left(y\right)}\ket{\overline{x}}\,, & \textrm{if }f\left(\overline{x}\right)=\btrue\,,
+\end{cases}
+\end{equation}
+where $\overline{x}$ denotes a sequence $x_{1},x_{2},\ldots,x_{n}$
+of $n$ bits and $0$ and $1$ are identified as $\bfalse$ and $\btrue$,
+respectively. Then, we can give an algorithm (see Fig.~\ref{fig:alg})
+taking as input such a classical function that decides, deterministically
+and in a constant number of black box evaluations, whether $f$ is
+satisfiable or not:
 
@@
 Applying $S^{\dagger}$ to the first component produces: $\ket{1}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
-Applying $X_{b}$, where $b$ is the first component of the state,
-to each qubit in the second component produces $\ket{1}\ket{\overline{{\sf not}(S(a))}}+\ket{0}\ket{\overline{0}}$.
-Applying $S^{\dagger}$ to the first component produces $\ket{+}\ket{\overline{{\sf not}(S(a))}}+\ket{0}\ket{\overline{0}}$.
-For the measurement of $\ket{+}\ket{\overline{{\sf not}(S(a))}}+\ket{0}\ket{\overline{0}}$
+Applying control-not gate, which applying $\sigma_{0}$ or $\sigma_{x}$
+on the second component depending on the first component of the state,
+and produces 
+\begin{equation}
+\ket{1}\left(\sigma_{x}\ket{\overline{S(a)}}\right)+\ket{0}\left(\sigma_{0}\ket{\overline{0}}\right)=\ket{1}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}\,.
+\end{equation}
+Applying $S^{\dagger}$ to the first component produces $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$.
+For the measurement of $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$
 to be guaranteed to never be $\ket{0}\ket{\overline{0}}$, we need
-to verify that $\ket{+}\ket{\overline{{\sf not}(S(a))}}$ has one
-occurrence $\ket{0}\ket{\overline{0}}$. This can be easily proved
-as follows. Since each $a_{i}$ is either 0 or 1, then each $S(a_{i})$
-is either $+$ or $1$, and hence each ${\sf not}(S(a_{i}))$ is either~$+$
-or~$0$. The result follows since any state with a combination of
-$+$ and $0$, when expressed in the standard basis, would consist
-of a superposition containing the state $\ket{0\ldots}$.
+to verify that $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}$
+has one occurrence $\ket{0}\ket{\overline{0}}$. This can be easily
+proved as follows. Since each $a_{i}$ is either 0 or 1, then each
+$S(a_{i})$ is either $+$ or $1$, and hence each $\mathsf{not}\left(S(a_{i})\right)$
+is either~$+$ or~$0$. The result follows since any state with
+a combination of $+$ and $0$, when expressed in the standard basis,
+would consist of a superposition containing the state $\ket{0\ldots}$.
 

### 2018-03-16 dissertation.tex
dissertation.lyx Updating spacing in multi-line equations...

@@
 \begin{equation}
-\sigma_{\mu}^{j}=\overbrace{\sigma_{0}\otimes\cdots\otimes\sigma_{0}\otimes\underbrace{\sigma_{\mu}}_{j^{th}\ \mbox{factor}}\otimes\sigma_{0}\otimes\cdots\otimes\sigma_{0}}^{n\ \mbox{factors}}\,,\label{pauli3}
+\sigma_{\mu}^{j}=\overbrace{\sigma_{0}\otimes\cdots\otimes\sigma_{0}\otimes\underbrace{\sigma_{\mu}}_{j^{\textrm{th}}\textrm{ factors}}\otimes\sigma_{0}\otimes\cdots\otimes\sigma_{0}}^{n\textrm{ factors}}\,,\label{pauli3}
 \end{equation}
 with 
-\begin{equation}
-\begin{aligned}\sigma_{0} & =\left(\begin{array}{cc}
+\begin{align}
+\sigma_{0} & =\left(\begin{array}{cc}
 1 & 0\\
@@
 0 & -1
-\end{array}\right)\,,\end{aligned}
-\end{equation}
+\end{array}\right)\,,
+\end{align}
 and $\expval{\sigma_{\mu}^{j}}=\melem{\Psi}{\sigma_{\mu}^{j}}{\Psi}$
@@
 by calculating the purity relative to the set $\fh=\left\{ \sigma_{x}^{1},\sigma_{y}^{1},\sigma_{z}^{1},\ldots,\sigma_{x}^{n},\sigma_{y}^{n},\sigma_{z}^{n}\right\} $,
-\begin{equation}
-\begin{aligned}P_{\fh} & =\frac{1}{n}\sum\limits _{j=1}^{n}\sum\limits _{\mu=x,y,z}\expval{\sigma_{\mu}^{j}}^{2}\,, & 0\leq P_{\fh}\leq1\,.\end{aligned}
-\label{purityMeasure.eq}
-\end{equation}
+\begin{align}
+P_{\fh} & =\frac{1}{n}\sum\limits _{j=1}^{n}\sum\limits _{\mu=x,y,z}\expval{\sigma_{\mu}^{j}}^{2}\,, & 0\leq P_{\fh}\leq1\,.\label{purityMeasure.eq}
+\end{align}
 Since $\fh$ is a semi-simple Lie algebra, its generalized unentangled
@@
 \begin{eqnarray}
-a\gmult(b+c) & = & a\gmult b+a\gmult c\\
-(b+c)\gmult a & = & b\gmult a+c\gmult a\ .
+a\gmult(b+c) & = & a\gmult b+a\gmult c\,,\\
+(b+c)\gmult a & = & b\gmult a+c\gmult a\,.
 \end{eqnarray}
@@
 with the following addition and multiplication tables: 
-\[
+\begin{align*}
 \begin{array}{c|ccc}
@@
 2 & 2 & 0 & 1
-\end{array}\hspace*{2cm}\begin{array}{c|ccc}
+\end{array} &  & \begin{array}{c|ccc}
 \gmult & 0 & 1 & 2\\[0.1in]
@@
 \end{array}
-\]
+\end{align*}
 
@@
 with respect to the standard basis are:
-\begin{equation}
-\begin{aligned}\sigma_{0} & =\begin{pmatrix}1 & 0\\
+\begin{subequations}\label{eq:MQT-dynamics}
+\begin{align}
+\sigma_{0} & =\begin{pmatrix}1 & 0\\
 0 & 1
@@
 \end{pmatrix}\,.
-\end{aligned}
-\label{eq:MQT-dynamics}
-\end{equation}
+\end{align}
+\end{subequations}
+
 For example, 
-\begin{equation}
-\begin{aligned}S\ket{0} & =\begin{pmatrix}1 & 0\\
+\begin{align}
+S\ket{0} & =\begin{pmatrix}1 & 0\\
 1 & 1
@@
 0
-\end{pmatrix}=\ket{0}\,.\end{aligned}
-\label{eq:MQT-dynamics-apply}
-\end{equation}
+\end{pmatrix}=\ket{0}\,.\label{eq:MQT-dynamics-apply}
+\end{align}
 This set of maps is clearly quite impoverished compared to the full

### 2018-03-17 dissertation.tex
dissertation.lyx "Chapter 3 Quantum Theories and Computing over Finite Fields" Updating...

@@
 
+\usepackage{amsthm}
+\theoremstyle{definition}
+\newtheorem{definition}{}[section]
+
 \newcommand{\muB}{\ensuremath{\mu^{B}}}
@@
 \newcommand{\Fpx}[1]{\mathbb{F}_{{#1}}}
+\newcommand{\Fp}{\Fpx{p}}
+\newcommand{\Fppx}[1]{\Fpx{{#1}^2}}
+\newcommand{\Fpp}{\Fppx{p}}
 \newcommand{\Fq}{\Fpx{q}}
@@
 \newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
+\newcommand{\fnorm}[1]{\mathsf{N}(#1)}
 
@@
 
+\subsection{Background}
+
 A field~$\mathbb{F}$ is an algebraic structure consisting of a set
@@
 \end{align*}
+
+\subsection{Cyclic Properties of Finite Fields}
 
@@
 to verify that $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}$
-has one occurrence $\ket{0}\ket{\overline{0}}$. This can be easily
-proved as follows. Since each $a_{i}$ is either 0 or 1, then each
-$S(a_{i})$ is either $+$ or $1$, and hence each $\mathsf{not}\left(S(a_{i})\right)$
-is either~$+$ or~$0$. The result follows since any state with
-a combination of $+$ and $0$, when expressed in the standard basis,
-would consist of a superposition containing the state $\ket{0\ldots}$.
+has one occurrence $\ket{0}\ket{\overline{0}}$. \todo{The following
+need to be rewritten.}This can be easily proved as follows. Since
+each $a_{i}$ is either 0 or 1, then each $S(a_{i})$ is either $+$
+or $1$, and hence each $\mathsf{not}\left(S(a_{i})\right)$ is either~$+$
+or~$0$. The result follows since any state with a combination of
+$+$ and $0$, when expressed in the standard basis, would consist
+of a superposition containing the state $\ket{0\ldots}$.
 
@@
 
+\subsection{Complexified Finite Fields}
+
 Our next objective is to develop more realistic discrete quantum theory
@@
 
-The next task is to examine the consequences when we attempt to construct
-$d$-dimensional vector spaces over the complexified fields $\ff{p^{2}}$
-\cite{geom1}. (For readability, instead of writing column vectors,
-we will often use the vector notation $\ket{\Psi}=(\alpha_{0}~\alpha_{1}~\ldots~\alpha_{d-1})^{T}$
-and $\ket{\Phi}=(\beta_{0}~\beta_{1}~\ldots~\beta_{d-1})^{T}$, where
-$(.)^{T}$ is the transpose of the \textit{row} vector $(.)$.) It
-can be shown~\cite{HermitianProd} that, given two vectors 
-\begin{equation}
-\ket{\Psi}=\sum_{i=0}^{d-1}~\alpha_{i}\ket{i}\ ,\ \ket{\Phi}=\sum_{i=0}^{d-1}~\beta_{i}\ket{i},
-\end{equation}
-with scalars $\alpha_{i}$ and $\beta_{i}$ drawn from the field elements,
-and orthonormal basis $\{\ket{i}\}$, the Hermitian \dotprod\ is
-always reducible to the form \vspace{-0.1in}
-
-\begin{equation}
-\ip{\Phi}{\Psi}=\sum_{i=0}^{d-1}~\beta_{i}^{p}~\alpha_{i}^{\;}\ .\vspace{-0.1in}\label{innerprod}
-\end{equation}
-
-This product satisfies conditions A and B below, but not~C, because
-in a finite field, addition can ``wrap around,'' making the concepts
-of positive and negative meaningless and allowing the sum of non-zero
-elements to be zero: 
-\begin{itemize}
-\item A. $\ip{\Phi}{\Psi}$ is the complex conjugate of $\ip{\Psi}{\Phi}$;
-\vspace*{-0.25cm}
-
-\item B. $\ip{\Phi}{\Psi}$ is conjugate linear in its first argument and
-linear in its second argument; \vspace*{-0.25cm}
-
-\item C. $\ip{\Psi}{\Psi}$ is always non-negative and is equal to~0 only
-if $\ket{\Psi}$ is the zero vector. 
-\end{itemize}
-With just conditions A and B, it is possible to recover unitary operators,
-and thus recover much of the relevant structure of Hilbert spaces
-over the field of complex numbers. The failure of condition C, however,
-plays havoc with the traditional notions of ordered probabilities
-as well as the geometric notions of ordered distances and angles,
-whose lengths and cosines, respectively, are normally expressed using
-the inner product~\cite{geom}. In a separate development, we explore
-the geometry of these finite fields and define a discrete version
-of the Hopf fibration extending the Bloch sphere to $n$-qubits, as
-well as determining discrete measures for the relative sizes of the
-entangled, maximally entangled, and unentangled discrete states~\cite{geom1}.
-
-\begin{comment}
-
-\section{Vector Spaces over Complexified Finite Fields}
-
-In order to address the intrinsic problems induced by the notion of
-the continuum calculations of the previous section, one is led to
-replace the infinite fields of CQC by discrete computable fields.
-Accomplishing this while maintaining the essential elements of addition
-and multiplication requires a brief excursion into the theory of fields,
-and particularly the theory of finite fields.
-
-\subsection{Background}
-
-Abstract algebra deals with various kinds of algebraic structures,
-such as groups, rings, and fields, each defined by a different system
-of axioms. A field~$\mathbf{F}$ is an algebraic structure consisting
-of a set of elements equipped with the operations of addition, subtraction,
-multiplication, and division \cite{numtheory.ref}. Fields may contain
-an infinite or a finite number of elements. The rational $\mathbb{Q}$,
-real $\mathbb{R}$, and complex numbers $\mathbb{C}$ are examples
-of infinite fields, while the set $\mathbf{F}_{3}=\{0,1,2\}$ under
-the usual multiplication and modular addition is an example of a finite
-field. Finite fields are also known as Galois fields \cite{GT.ref}.
-
-There are two distinguished elements in a field, the addition identity
-$0$, and the multiplication identity $1$. Given the field $\mathbf{F}$,
-the closed operations of addition, ``$+$'', and multiplication,
-``$\gmult$'', satisfy the following set of axioms:
-\begin{enumerate}
-\item $\mathbf{F}$ is an Abelian group under the addition operation $+$
-(additive group)
-\item The multiplication operation $\gmult$ is associative and commutative.
-The field has a multiplicative identity and the property that every
-nonzero element has a multiplicative inverse
-\item Distributive laws: For all $a,b,c\in\mathbf{F}$ 
-\begin{eqnarray}
-a\gmult(b+c)=a\gmult b+a\gmult c\\
-(b+c)\gmult a=b\gmult a+c\gmult a\ .
-\end{eqnarray}
-\end{enumerate}
-{}From now on, unless specified, we will omit the symbol $\gmult$
-whenever we multiply two elements of a field.
-
-Finite fields of $q$ elements, $\Fq=\{0,\ldots,q-1\}$, will play
-a special role in this work. A simple explicit example is the following
-addition and multiplication tables for $\mathbf{F}_{3}$: 
-\[
-\begin{array}{c|ccc}
-+ & 0 & 1 & 2\\[0.1in]
-\hline 0 & 0 & 1 & 2\\
-1 & 1 & 2 & 0\\
-2 & 2 & 0 & 1
-\end{array}\hspace*{2cm}\begin{array}{c|ccc}
-\gmult & 0 & 1 & 2\\[0.1in]
-\hline 0 & 0 & 0 & 0\\
-1 & 0 & 1 & 2\\
-2 & 0 & 2 & 1
-\end{array}
-\]
-
-\subsection{Cyclic Properties of Finite Fields}
-
-Finite fields are classified by size. The characteristic of a field
-is the least positive integer $m$ such that $m=1+1+1+\cdots+1\equiv0$,
-and if no such $m$ exists we say that the field has characteristic
-zero (which is the case for infinite fields such as $\mathbb{R}$).
-It turns out that if the characteristic is non-zero it must be a prime
-$p$. For every prime $p$ and positive integer $r$ there is a finite
-field $\Fpx{p^{r}}$ of cardinality $q=p^{r}$ and characteristic
-$p$ (Lagrange's theorem), which is unique up to field isomorphisms.
-For every $a\in\Fq$, $a\neq0$, then $a^{q-1}=1$, implying the Frobenius
-endomorphism (also a consequence of Fermat's little theorem) $a^{q}=a$,
-which in turn permits us to write the multiplicative inverse of any
-non-zero element in the field as $a^{-1}=a^{q-2}$, since $a^{q-2}a=a^{q-1}=1$.
-Every subfield of the field $\Fq$, of cardinality $q=p^{r}$, has
-$p^{r'}$ elements with some $r'$ dividing $r$, and for a given
-$r'$ it is unique. Notice that a fundamental difference between finite
-and infinite fields is one of topology: finite fields induce a compact
-structure because of their modular arithmetic, permitting \textit{wrapping
-around}, while that is not the case for fields of characteristic zero.
-This feature may lead to fundamental physical consequences.
-
-\subsection{Complexified Finite Fields}
-
-Consider the polynomial $x^{2}+1=0$ over a finite field $\Fp$. It
-is known that this polynomial does not have solutions in the field
-precisely when the prime $p$ is congruent to $3\imod{4}$ (see, e.g.,
-\cite{numtheory.ref}).
-
-For such primes, it is therefore possible to construct an extended
-field $\Fpp$ whose elements are of the form $\alpha=a+ib$ with $a\in\Fp$,
-$b\in\Fp$, and $i$ the root of the polynomial $x^{2}+1=0$. Since
-the field elements $a+ib$ behave like discrete versions of the complex
-numbers, we will refer to fields $\Fp$ with prime $p$ congruent
-to $3\imod{4}$ as \emph{complexifiable finite fields}, and $i$-extended
-fields $\Fpp$ with $p$ congruent to $3\imod{4}$ as \emph{complexified
-finite fields}.
-
 In a complexified finite field $\Fpp$, the Frobenius automorphism
@@
 conjugation. For example, in $\Fppx{3}$, we have $(2+i)^{3}=8+12i-6-i=2+11i$
-which, in the field, is equal to $2-i$ since $11\equiv-1\imod{3}$.
+which, in the field, is equal to $2-i$ since $11\equiv-1\pmod{3}$.
 
@@
 
-\begin{definition}{[}Hermitian dot product{]} Given vectors $\ket{\Phi}$
+\begin{definition}[Hermitian dot product] Given vectors $\ket{\Phi}$
 and $\ket{\Psi}\in{\cal H}$, the Hermitian dot product of these vectors
@@
 The field norm of a vector can vanish for non-vanishing vectors.
-
-For vectors $\ket{\Psi}$ such that $\ip{\Psi}{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}^{p}\,\alpha_{i}^{\;}=\sum_{i=0}^{D-1}\alpha_{i}^{p+1}=\sum_{i=0}^{D-1}|\alpha_{i}|^{2}$
-has a square root in the field, one can define the following ``norm'':
-\begin{equation}
-||\Psi||=\sqrt{\ip{\Psi}{\Psi}}\ ,\label{norm-eq}
-\end{equation}
-which is valid only on a subspace of the field norm for finite fields.
-
-%There is an alternative way of defining a proper inner product over a subset of the %field $\Fpp$.
-Consider prime numbers $p= 8 \prod_{l=1}^k q_l -1$, where  %$q_l$ are odd primes.
-This subset of the primes congruent to $3 \imod 4$ has the %special properti
-
-\section{Irreducible Discrete $n$-qubit States: Generalized Discrete Bloch
-Sphere}
-
-\label{DQCnqubitBloch.sec}
-
-In the one-qubit state with coefficients in $\Fpp$, the discrete
-analog of the Bloch sphere is constructed by exact analogy to the
-continuous case: we first require that the coefficients of the single
-qubit basis obey 
-\begin{equation}
-\|\psi_{1}\|^{2}=|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=1\label{DQA2.eq}
-\end{equation}
-in the discrete field. In \ref{appU.sec}, we show that there are
-$p(p^{2}-1)$ such values. Given this requirement, which is similar
-in form to the conservation of probability, but not as useful due
-to the lack of orderable probability values, we can immediately conclude
-that the discrete analog of the Hopf fibration is again 
-\begin{eqnarray}
-X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\nonumber \\
-Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\label{DQA6.eq}\\
-Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}=x_{0}^{\ 2}+y_{0}^{\ 2}-x_{1}^{\ 2}-y_{1}^{\ 2}\ ,\nonumber 
-\end{eqnarray}
-but now with all computations in $(\mbox{mod}~p)$. At this point
-one simply writes down all possible discrete values for the complex
-numbers $\{\alpha_{0},\alpha_{1}\}$ satisfying Eq.~(\ref{DQA2.eq})
-and enumerates those that project to the same value of $\{X,Y,Z\}$.
-This equivalence class is the discrete analog of the circle in the
-complex plane that was eliminated in the continuous case. In \ref{appH.sec},
-we show that $p+1$ discrete values of $\{\alpha_{0},\alpha_{1}\}$
-with unit norm map to the same point under the Hopf map \Eq{DQA6.eq};
-we may think of these as discrete circles or projective lines of equivalent,
-physically indistinguishable, complex phase. The surviving $p(p-1)$
-values of $\{\alpha_{0},\alpha_{1}\}$ correspond to irreducible physical
-states of the discrete single qubit system. %% Several examples are shown in Figure \ref{bloch.fig}. %%Thus,
-for example, choosing the underlying field to be $\Fppx{3}$, there
-are exactly 6 single-qubit state vectors to populate the Bloch sphere;
-the four equivalent phase-multiples mapping to each of the six points
-on the $\Fppx{3}$ Bloch sphere are collapsed and regarded as physically
-indistinguishable. In Figure \ref{bloch.fig}, we plot the irreducible
-states on the Bloch sphere for $p=3$, $7$, and $11$. Note that
-the Cartesian lengths of the real vectors corresponding to the points
-on the Bloch sphere vary considerably due to the nature of discrete
-fields; we have artificially normalized them to a ``continuous world''
-unit radius sphere for conceptual clarity.
-
-\begin{figure}[htb]
-%\vspace{-0.2in}  %% \includegraphics[width=0.9\columnwidth]{./Bloch_sphere.pdf}%%\includegraphics[width=2.0\columnwidth]{./picA.png}%%\includegraphics[width=2.0\columnwidth]{./picB.png}
-
-\begin{centering}
-\hspace*{-0.5cm}\includegraphics[width=1.1\columnwidth]{../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/picC.png}
-%%\includegraphics[width=0.5\textwidth]{./picAB.eps}\vspace{-0.2in}
- %% adjust blank space?
-\par\end{centering}
-\caption{Schematically normalized plots of the elements of the discrete Bloch
-sphere, the irreducible single-qubit (two-dimensional) state vectors
-with unit norm over the field $\Fpp$. We show the results for $p=3$,
-$7$, and $11$. For example, in $\Fppx{3}$, there are 24 vectors
-of unit norm, but only the 6 inequivalent classes appear in the plot.
-The $p+1=4$ equivalent vectors in each class differ only by a complex
-discrete phase.}
-\label{bloch.fig} 
-\end{figure}
-
-\subsection{Counting states on the $n$-qubit Bloch sphere}
-
-We have the unique opportunity in the finite-field approach to quantum
-computing to precisely identify and enumerate the physical states.
-In the conventional theory, as we have seen, we employ a generalized
-Hopf fibration on the normalized states to project out a circle of
-phase-equivalent states, yielding the generalized Bloch sphere.
-
-In the introduction to this section, we sketched the counting of the
-irreducible single-qubit discrete states. To count the number of inequivalent
-discrete states for the general $n$-qubit case with coefficients
-in $\Fpp$, we first must find the set of unit-norm states, and then
-determine the equivalence classes of unit-norm states under discrete
-phase transformations; we can then enumerate the list of states on
-the discrete generalized Bloch sphere. By executing computer searches
-of these spaces, we discovered an hypothesis for a closed-form solution
-for the counting of the states, and were then able to find a rigorous
-inductive proof of the enumeration, which is presented in the Appendix.
-
-This process of describing the discrete $n$-qubit irreducible states
-can again be understood geometrically by following the discrete analog
-of the Hopf fibration. First, we construct the discrete version of
-the quadratic unit-length form that automatically annihilates the
-distinction among states differing only by a discrete phase, 
-\begin{eqnarray}
-\hspace*{-0.5cm}\Hat{a}=(|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots)\ ,
-\end{eqnarray}
-where 
-\begin{eqnarray}
-\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
-\end{eqnarray}
-{}From \ref{appH.sec}, we know that $p+1$ elements of this discrete
-$\Sphere{2\times2^{n}-1}$ structure map to the \textit{same point\/}
-in $\Hat{a}$. Each set of $(p+1)$ redundant points is, geometrically
-speaking, the \textit{discrete Hopf fibration circle\/} living above
-each \textit{irreducible\/} point of the $n$-qubit state description.
-These $p+1$ points are interpretable as the $p$ finite points plus
-the single point at infinity of the projective discrete line (see,
-e.g., \cite{Arnold}).
-
-The next part of this argument is the determination of the unit-norm
-states, effectively the space of allowed discrete partitions of unity;
-we cannot exactly call these ``probability-conserving'' sectors
-of the state coefficients since we do not have a well defined notion
-of probability, but we do have a well-defined notion of partition
-of unity. The tally of unit-norm states is $p^{2^{n}-1}(p^{2^{n}}-1)$
-(see \ref{appU.sec}) compared to the total number $p^{2\times2^{n}}$
-of possible complex integer state vectors that could be chosen. This
-unit-norm state structure is the discrete analog of $\Sphere{2\times2^{n}-1}$.
-
-Finally, we repeat the last step of the $n$-qubit continuous Hopf
-fibration process for discrete $n$-qubit states, eliminating the
-discrete set of $p+1$ equivalent points that map to the same point
-$\Hat{a}$ on the generalized $n$-qubit Bloch sphere. Dividing the
-tally $p^{2^{n}-1}(p^{2^{n}}-1)$ of unit norm states by the $p+1$
-elements of each phase-equivalent discrete circle, we find 
-\[
-\frac{p^{2^{n}-1}(p^{2^{n}}-1)}{p+1}=p^{2^{n}-1}(p-1)\,\prod_{k=1}^{n-1}(p^{2^{k}}+1)
-\]
-as the total count of unique irreducible states in a discrete $n$-qubit
-configuration (see \ref{appI.sec}). The resulting object is precisely
-the discrete version of $\CP{D-1}$, which we might call a \textit{discrete
-complex projective space\/} or $\DCP{D-1}$, where $D=2^{n}$ as
-usual.
-
-\Comment{
-
-\subsection{Counting states on the $n$-qubit Bloch sphere}
-
-Although we do not have a rigorous proof for the counting of discrete
-unit-norm states and the number of irreducible unit-norm states in
-the discrete generalized Bloch sphere for $n$-qubit states with coefficients
-in $\Fpp$, we have run extensive computer searches of the state features
-for a range of compatible primes $p$ and number of qubits $n$. From
-these experimental investigations, we have induced a closed-form solution
-for the counting that agrees for every possible combination of parameters
-that can be computed in reasonable time (the computational complexity
-becomes intractable very quickly).
-
-For $n$-qubit discrete states with coefficients in $\Fpp$, our calculation
-begins with an enumeration of all possible $2^{n}$-tuples of state
-coefficients in $\Fpp$; then the moduli-squared of these tuples are
-summed and compared to unity in $(\mbox{mod}~p)$. Those that survive
-are accumulated in a list of allowed discrete partitions of unity;
-we cannot exactly call these ``probability-conserving'' sectors
-of the state coefficients since we do not have a well defined notion
-of probability, but we do have a well-defined notion of partition
-of unity. The heuristic number that results for the tally of unit-norm
-states is $p^{2^{n}-1}(p^{2^{n}}-1)$, compared to the total number
-$p^{2\times2^{n}}$ of possible complex integer state vectors that
-could be chosen. This unit-norm state structure is now the discrete
-analog of $\Sphere{2\times2^{n}-1}$.
-
-Finally, we construct the discrete version of the quadratic unit-length
-form that automatically annihilates the distinction among states differing
-only by a discrete phase, 
-\begin{eqnarray}
-\hspace*{-0.5cm}\Hat{a}=\{|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\}\ ,
-\end{eqnarray}
-where 
-\begin{eqnarray}
-\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
-\end{eqnarray}
-Computing all the elements of the discrete $\Sphere{2\times2^{n}-1}$
-structure that map to the \textit{same point\/} in $\Hat{a}$, we
-find a $(p+1)$-fold redundancy, exactly as for the one-qubit case;
-each set of $(p+1)$ redundant points is, geometrically speaking,
-the \textit{discrete Hopf fibration circle\/} (see, e.g., Arnold
-\cite{Arnold}) living above each \textit{irreducible\/} point of
-the $n$-qubit state description.
-
-In summary, when the $n$-qubit continuous Hopf fibration process
-is repeated for the discrete analog of $n$-qubit states, we find
-that that analog of a phase ``circle'' is a discrete set $p+1$
-equivalent points that map to the same point $\Hat{a}$ on the generalized
-$n$-qubit Bloch sphere, and therefore there are a total of $p^{2^{n}-1}(p^{2^{n}}-1)/(p+1)$
-unique irreducible states in a discrete $n$-qubit configuration.
-The resulting object is precisely the discrete version of $\CP{D-1}$,
-which we might call a \textit{discrete complex projective space\/}
-or $\DCP{D-1}$. }
-
-\section{Geometry of Entangled States}
-
-Without regard to uniqueness, an $n$-qubit state with discrete complex
-coefficients in $\Fpp$ will have the total possible space of coefficients
-with dimension $p^{2\times2^{n}}$ (including the null state). Imposing
-the condition of a length-one norm %% AMR: replaced 'inner-product' by 'norm'in
-$\Fp$, this number is reduced to $p^{2^{n}-1}(p^{2^{n}}-1)$. The
-ratio of all the states to the unit-norm states is asymptotically
-$p$: 
-\begin{eqnarray}
-\frac{p^{2^{n}+1}}{p^{2^{n}}-1}\rightarrow p\ ,
-\end{eqnarray}
-so there are roughly $p$ sets of coefficients, for any number of
-qubits $n$, that are discarded for each retained unit-length state
-vector. A factor of $p+1$ more states are discarded in forming the
-discrete Bloch sphere of irreducible states. Selected plots of the
-full space compared to both the unit-norm space and the irreducible
-space for a selection of complexified finite fields are shown in Figure
-\ref{statePlot3Unit.fig} for 1, 2, 3, and 4 qubits. %Figure \ref{statePlot3Unit.fig} adds the size of the irreducible state%space at the bottom.
-
-%% Source of this is%%  ~hansona/home2/papers/dqc-geom-2012/00mathFigs/A-Test-Galois-Nqubit.nb
-
-%\begin{figure}[htb]%\begin{center}%\includegraphics[width=1.0\columnwidth]{./statePlot1.pdf}%%\vspace{-0.2in}  %% adjust blank space?%\end{center}% \caption{Logarithmic plot of the number of discrete unnormalized%states (top, in red), vs the number of normalized discrete states%(bottom, in blue) for the first 6 $\Fpp$-compatible primes,  (3, 7,%11, 19, 23, 31), for the number of qubits 1, 2, 3 and 4.
-}% \label{statePlotUnit.fig}%\end{figure}
-
-\begin{figure}[htb]
-\begin{centering}
-\includegraphics[width=1\columnwidth]{../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/statePlot3.pdf}
-%\vspace{-0.2in}  %% adjust blank space?
-\par\end{centering}
-\caption{Logarithmic plot of the number of discrete unnormalized states (top,
-in red), vs the number of normalized discrete states (middle, in blue),
-vs the irreducible states (bottom, in green) for the first 6 $\Fpp$-compatible
-primes, (3, 7, 11, 19, 23, 31), for the number of qubits 1, 2, 3 and
-4. }
-\label{statePlot3Unit.fig} 
-\end{figure}
-
-\subsection{Unentangled vs Entangled Discrete States}
-
-For a given $p$ and the corresponding complexified field $\Fpp$,
-the $n$-qubit discrete quantum states with coefficients in $\Fpp$
-can be classified by their degree of entanglement to a level of precision
-that is unavailable in the continuous theory. We look first at the
-unentangled $n$-qubit states, which are direct product states of
-the form 
-\begin{equation}
-\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}\ .\label{dqcNqUntg.eq}
-\end{equation}
-Without regard to normalization, there are $(p^{4})^{n}$ possible
-unentangled states out of the total of $p^{2\times2^{n}}$ states
-noted above. When we normalize the individual product states to unit
-norm, the norm of the entire $n$-qubit state becomes the product
-of those unit norms, and is automatically normalized to one. We have
-already seen that each single-qubit normalized state in the tensor
-product \Eq{dqcNqUntg.eq} has precisely $p(p-1)$ irreducible components.
-
-\subsection{Completely Unentangled States and the Discrete Bloch Sphere}
-
-In effect, the irreducible states for unentangled $n$-qubit configurations
-reduce to a single Bloch sphere for each one-qubit component $\ket{\psi_{j}}$,
-and thus the whole set of states is defined by an $n$-tuple of discrete
-Bloch sphere coordinates. Since each Bloch sphere in $\Fpp$ has $p(p-1)$
-distinct irreducible components, we have 
-\[
-\mbox{{\bf Count of Unentangled States}}=p^{n}(p-1)^{n}\ .
-\]
-
-We know that the total number of irreducible states (points in the
-generalized $\DCP{2^{n}-1}$ Bloch sphere) for an $n$-qubit state
-is $p^{2^{n}-1}(p^{2^{n}}-1)/(p+1)$, and so the number of states
-containing some measure of entanglement is 
-\begin{eqnarray*}
-\mbox{{\bf Count of Entangled States}}=\frac{p^{2^{n}-1}(p^{2^{n}}-1)}{p+1}-p^{n}(p-1)^{n}\ .
-\end{eqnarray*}
-Therefore a very small fraction of the unit norm states are unentangled.
-
-\subsection{Partial entanglement}
-
-A partially entangled state can be constructed by taking individual
-component states to enter as direct products, starting by picking
-$n$ distinct single qubits to be unentangled ($n=2$ exhausts its
-freedom with one pick). Then we can choose $n(n-1)/2$ pairs of distinct
-qubits as product states ($n=3$ exhausts its freedom with one pick),
-and so on. Then, starting with $n=3$, we can pick fully entangled
-2-qubit subspaces as product spaces, combining them with single-qubit
-product components ($n=3$ has no single-qubit freedom left after
-picking any of its three 2-qubit subspaces), and so on. Precise measures
-of entanglement such as that given in \Eq{purityMeasure.eq} can
-then be applied just as in the continuous case.
-
-\subsection{Maximal entanglement}
-
-Numerical and analytic calculations of the entanglement measure \Eq{purityMeasure.eq},
-taken $(\mbox{mod}~p)$, extend to the best of our knowledge to the
-discrete case, so that the unentangled states constructed above have
-$P_{\fh}=1$. This leads us to study one final aspect of the discrete
-$n$-qubit states, namely the \textit{maximally\/} entangled states
-with $P_{\fh}=0$.
-
-Computing some examples for various $n$ and small values of $p$,
-one can verify explicitly that unit-norm unentangled states for $n=2$,
-$p=\{3,7,11,19,\ldots\}$ occur with frequency 
-\[
-(p+1)p^{2}(p-1)^{2}=\{144,14112,145200,2339280,\ldots\}\ ,
-\]
-and for general $n$, $(p+1)p^{n}(p-1)^{n}$.
-
-The irreducible state counts are reduced by $(p+1)$, giving 
-\[
-p^{2}(p-1)^{2}=\{36,1764,12100,116964,\ldots\}\ ,
-\]
-and in general for $n$-qubits, $p^{n}(p-1)^{n}$ instances of pure
-states with $P_{\fh}=1$.
-
-Repeating the computation to discover the frequency of maximally entangled
-(purity $P_{\fh}=0$ states), we find $p^{n+1}(p-1)(p+1)^{n}$ maximally
-entangled states, with example frequencies for two qubits of 
-\[
-p^{3}(p-1)(p+1)^{2}=\{864,131712,1916640,49384800,\ldots\}\ .
-\]
-
-The irreducible state counts for maximal entanglement are reduced
-by $(p+1)$, giving for $n=2$ 
-\[
-p^{3}(p^{2}-1)=\{216,16464,159720,2469240,\ldots\}\ ,
-\]
-and in general for $n$-qubits, $p^{n+1}(p-1)(p+1)^{n-1}$ instances
-of pure states with $P_{\fh}=0$.
-
-Therefore, the ratio of maximally entangled to unentangled states
-is 
-\[
-\mbox{{\bf Max Entangled/Unentangled}}=p\left(\frac{p+1}{p-1}\right)^{n-1}\ .
-\]
-
-\section{Summary}
-
-Given a discrete basis for the complex coefficients of an $n$-qubit
-quantum state, DQC permits us in principle to explicitly determine
-the relative frequencies of phases and to determine exactly the generalized
-Bloch sphere coordinates of the irreducible states. The size of the
-set of states that must be taken as equivalent to get irreducibility
-is the size of the ``circle'' or phase group, and this is $p+1$
-for any $p$ and for any $n$ (related to the size of the finite projective
-line, see \cite{Arnold}). Exploring the discrete manifestation of
-the purity measure \Eq{purityMeasure.eq}, our DQC approach can determine
-not only the size of the irreducible space of states, but also the
-relative sizes of the unentangled and entangled states for $n$ discrete
-qubits.
-
-\vspace{0.5in}
-
-\noindent \textbf{References} \vspace*{0.5cm}
-
-\bibitem{GeomQStates2008} I. Bengtsson and K. Zyczkowski, \textit{Geometry
-of Quantum States: An Introduction to Quantum Entanglement} (Cambridge
-University Press, Cambridge, 2008).
-
-\bibitem{mosseri2001} R. Mosseri and R. Dandoloff, \textit{J. Phys.
-A: Math. Gen.} \textbf{34}, 10243 (2001).
-
-\bibitem{Arnold} V. I. Arnold, \textit{Dynamics, Statistics and Projective
-Geometry of Galois Fields\/} (Cambridge University Press, Cambridge,
-2011).
-
-\bibitem{Turing37} A. M. Turing, \textit{Proceedings of the London
-Mathematical Society} Series 2, \textbf{42}, 230 (1937). Errata appeared
-in Series 2, \textbf{43} 544 (1937).
-
-\bibitem{Minsky67} M. Minsky, \textit{Computation: Finite and Infinite
-Machines} (Prentice-Hall, Englewood Cliffs, 1967). See chapter 9,
-``The Computable Real Numbers.''
-
-\bibitem{Chaitin} G. J. Chaitin, \textit{Thinking about Gödel and
-Turing} (World Scientific, Singapore, 2007).
-
-\bibitem{Feynman} R. P. Feynman, \textit{Int. J. Theor. Phys.} \textbf{21},
-467 (1982).
-
-\bibitem{Landauer} R. Landauer, \textit{Physics Letters A\/} \textbf{217},
-188 (1996).
-
-\bibitem{SchuWest2010} B. Schumacher and M. D. Westmoreland, \textit{Found.
-Phys. \/} \textbf{42}, 918 (2012).
-
-\bibitem{James2011} R. P. James, G. Ortiz, and A. Sabry, \texttt{http://arxiv.org/abs/1101.3764}.
-
-\bibitem{HOSW2011} A. J. Hanson, G. Ortiz, A. Sabry, and J. Willcock,
-\texttt{http://arxiv.org/abs/1104.1630}.
-
-\bibitem{Berger} M. Berger and B. Gostiaux, \textit{Differential
-Geometry: Manifolds, Curves, and Surfaces\/} (Springer-Verlag, New
-York, 1988).
-
-\bibitem{numtheory.ref-1} G. H. Hardy and E. M. Wright, \textit{An
-Introduction to the Theory of Numbers\/} (Oxford University Press,
-Oxford, 2006).
-
-\bibitem{GT.ref-1} I. Stewart, \textit{Galois theory\/} (Chapman
-and Hall/CRC, Boca Raton, 2004). \Comment{
-
-\bibitem{WB.ref} Wildberger N J 2005 \textit{Divine Proportions:
-Rational Trigonometry to Universal Geometry} (Sydney: Wild Egg Books)
-
-\bibitem{OT} Ovsienko V and Tabachnikov S 2005 \textit{Projective
-Differential Geometry Old and New} (Cambridge: Cambridge University
-Press)
-
-\bibitem{VY} Veblen O and J. W. Young J W 1946 \textit{Projective
-Geometry Vol. 2} (Blaisdell Publishing Company), pp 55??7
-
-\bibitem{Ztransform} Campello de Souza R M, de Oliveira H M and Silva
-D 2002 The Z Transform over Finite Fields \textit{International Telecommunications
-Symposium, ITS 2002, Brazil} }
-
-\bibitem{Barnum2003} H. Barnum, E. Knill, G. Ortiz, and L. Viola,
-\textit{Phys. Rev. A} \textbf{68}, 032308 (2003).
-
-\bibitem{Barnum2004} H. Barnum, E. Knill, G. Ortiz, R. Somma, and
-L. Viola, \textit{Phys. Rev. Lett.} \textbf{92}, 107902 (2004). 
-\end{comment}
 
@@
 in general, whether this version of discrete quantum computing actually
-enables the rapid solution of NP-complete problems
-
-.%
-\begin{comment}
-
-\section{Discrete Quantum Theory and Computing (I)}
-
-Our second model called discrete quantum theory (I) considers only
-finite fields of order $p^{2}$, with the prime $p$ of the form $4\ell+3$
-($\ell$ a non-negative integer) \cite{geometry2013,DQT2014}. In
-this model, an irreducible state is a vector in $\mathbb{F}_{p^{2}}^{2^{n}}$,
-and can be reduced to a point in the discrete complex projective space~$\mathbb{DCP}^{2^{n}-1}$.
-Among these irreducible states, the product states and entangled states
-can not only be identified as in CQT but also be counted for different
-$p$. Although the state space is a natural discrete analog to CQT,
-this model still only predicts whether a measurement result is possible
-or impossible, because it is not possible to define an inner product
-in the usual sense due to the modular arithmetic~\cite{grove2002classical}.
-Under suitable conditions, we can have deterministic quantum algorithms
-such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
-and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
-but this still leads to excessive computational power for the unstructured
-database search problem for certain database sizes.
-\end{comment}
+enables the rapid solution of NP-complete problems.
 

### 2018-03-17 dissertation.tex
dissertation.lyx Before install LyX 2.3.0

@@
 \todo{Further explain $\sigma_{\mu}^{j}$ used as a quantum circuit,
-control not, the Deutsch quantum black box~\cite{NCbook}, and maybe
+control not, the Deutsch quantum black box~\cite{544199}, and maybe
 Deutsch Algorithm...}
@@
 variants that exclude ``supernatural'' algorithms such as the one
-presented above. Our first such plausible framework~\cite{powerdqc}
+presented above. Our first such plausible framework~\cite{HOSW2011}
 is based on complexifiable finite fields. To incorporate complex numbers

### 2018-03-18 dissertation.tex
dissertation.lyx "3.4.1 Complexified Finite Fields" Updating...

@@
 \newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
-\newcommand{\fnorm}[1]{\mathsf{N}(#1)}
+\newcommand{\fnorm}[1]{\mathsf{N}\left({#1}\right)}
 
@@
 is \emph{irreducible} (has no solution) over a prime field $\ff{p}$
-with $p$ odd if and only if $p$ is of the form~$4\ell+3$, with
+with $p$ odd if and only if $p$ is of the form $4\ell+3$, with
 $\ell$ a non-negative integer. In other words, $x^{2}+1=0$ is irreducible
-over $\ff{3},\ff{7},\ff{11},\ff{19},\ldots$. We achieve our goal
-by observing that any field in this family is extensible to a field~$\ff{p^{2}}$
-whose elements can be viewed as discrete complex numbers with the
-real and imaginary parts in~$\ff{p}$. In the field~$\ff{p^{2}}$,
-the Frobenius automorphism of an element $\alpha$ (defined as $\alpha^{p}$)
-represents the usual definition of complex conjugation~\cite{fieldexample}.
-
-In a complexified finite field $\Fpp$, the Frobenius automorphism
-that maps $\alpha\in\Fpp$ to $\alpha^{p}\in\Fpp$ acts like complex
-conjugation. For example, in $\Fppx{3}$, we have $(2+i)^{3}=8+12i-6-i=2+11i$
-which, in the field, is equal to $2-i$ since $11\equiv-1\pmod{3}$.
+over $\ff{3}$, $\ff{7}$, $\ff{11}$, $\ff{19}$, \ldots{}. We achieve
+our goal by observing that any field in this family is extensible
+to a field~$\ff{p^{2}}$ whose elements can be viewed as discrete
+complex numbers with the real and imaginary parts in~$\ff{p}$. In
+a complexified finite field $\Fpp$, the Frobenius automorphism that
+maps $\alpha\in\Fpp$ to $\alpha^{p}\in\Fpp$ acts like complex conjugation
+\cite{Artin1991,grove2002classical,DummitFoote2004}. For example,
+in $\Fppx{3}$, we have $\left(2+\rmi\right)^{3}=8+12\rmi-6-\rmi=2+11\rmi$
+which, in the field, is equal to $2-\rmi$ since $11\equiv-1\pmod{3}$.
 
@@
 \begin{equation}
-\fnorm{\alpha=a+ib}=a^{2}+b^{2}\ .\label{fieldnorm.eq}
+\fnorm{\alpha=a+\rmi b}=a^{2}+b^{2}\,.\label{fieldnorm.eq}
 \end{equation}

### 2018-03-19 dissertation.tex
dissertation.lyx "3.4 Discrete Quantum Theory (I)" Updating...

@@
 \theoremstyle{definition}
-\newtheorem{definition}{}[section]
+\newtheorem{definition}{Definition}[section]
 
@@
 is based on complexifiable finite fields. To incorporate complex numbers
-for quantum amplitudes, we exploit the fact that the polynomial $x^{2}+1=0$
-is \emph{irreducible} (has no solution) over a prime field $\ff{p}$
-with $p$ odd if and only if $p$ is of the form $4\ell+3$, with
-$\ell$ a non-negative integer. In other words, $x^{2}+1=0$ is irreducible
-over $\ff{3}$, $\ff{7}$, $\ff{11}$, $\ff{19}$, \ldots{}. We achieve
-our goal by observing that any field in this family is extensible
-to a field~$\ff{p^{2}}$ whose elements can be viewed as discrete
-complex numbers with the real and imaginary parts in~$\ff{p}$. In
-a complexified finite field $\Fpp$, the Frobenius automorphism that
-maps $\alpha\in\Fpp$ to $\alpha^{p}\in\Fpp$ acts like complex conjugation
-\cite{Artin1991,grove2002classical,DummitFoote2004}. For example,
-in $\Fppx{3}$, we have $\left(2+\rmi\right)^{3}=8+12\rmi-6-\rmi=2+11\rmi$
+for quantum amplitudes, we exploit the fact that the polynomial $x^{2}+1$
+is \emph{irreducible} ($x^{2}+1=0$ has no solution) over a prime
+field $\ff{p}$ with $p$ odd if and only if $p$ is of the form $4\ell+3$,
+with $\ell$ a non-negative integer \cite{Artin1991,DummitFoote2004}.
+For example, given any $x\in\ff{3}=\left\{ 0,\pm1\right\} $, when
+$x=0$, we have $x^{2}+1=0^{2}+1=1$; when $x=\pm1$, we have $x^{2}+1=\left(\pm1\right)^{2}+1=1$.
+Therefore, $x^{2}+1$ is irreducible over $\ff{3}$. In contrast,
+over $\ff{5}$, $2^{2}+1=0$ so that $x^{2}+1$ is reducible.
+
+We achieve our goal by observing that any field $\ff{p}$ with $p=4\ell+3$
+is extensible to a field~$\ff{p^{2}}$ whose elements can be viewed
+as discrete complex numbers with the real and imaginary parts in~$\ff{p}$.
+In a complexified finite field $\Fpp$, the Frobenius automorphism
+that maps $\alpha\in\Fpp$ to $\alpha^{p}\in\Fpp$ acts like complex
+conjugation \cite{Artin1991,grove2002classical,DummitFoote2004}.
+For example, in $\Fppx{3}$, we have $\left(2+\rmi\right)^{3}=8+12\rmi-6-\rmi=2+11\rmi$
 which, in the field, is equal to $2-\rmi$ since $11\equiv-1\pmod{3}$.
 
-We define the \emph{field norm} $\fnorm{\cdot}$ as the map from $(a+ib)\in\Fpp$
+We define the \emph{field norm} $\fnorm{\cdot}$ as the map from $a+\rmi b\in\Fpp$
 to $a^{2}+b^{2}\in\Fp$, 
 \begin{equation}
-\fnorm{\alpha=a+\rmi b}=a^{2}+b^{2}\,.\label{fieldnorm.eq}
+\fnorm{a+\rmi b}=a^{2}+b^{2}\,.\label{fieldnorm.eq}
 \end{equation}
@@
 a complex number, and satisfying the following properties: 
-\begin{itemize}
-\item[A.] $\ip{\Phi}{\Psi}$ is the complex conjugate of $\ip{\Psi}{\Phi}$; 
-\item[B.] $\ip{\Phi}{\Psi}$ is conjugate linear in its first argument and
-linear in its second argument; 
-\item[C.] $\ip{\Psi}{\Psi}$ is always non-negative and is equal to~0 only
+\begin{enumerate}[label=(\Alph{enumi})]
+\item $\ip{\Phi}{\Psi}$ is the complex conjugate of $\ip{\Psi}{\Phi}$; 
+\item $\ip{\Phi}{\Psi}$ is conjugate linear in its first argument and linear
+in its second argument; 
+\item $\ip{\Psi}{\Psi}$ is always non-negative and is equal to~0 only
 if $\ket{\Psi}$ is the zero vector. 
-\end{itemize}
+\end{enumerate}
 It turns out that a vector space defined over a finite field cannot
@@
 
-We are interested in the $n$-qubit vector space ${\cal H}$ of dimension
-$D=2^{n}$ defined over the complexified field $\Fpp$. Let $\ket{\Psi}=(\alpha_{0}~\alpha_{1}~\ldots~\alpha_{D-1})^{T}$
-and $\ket{\Phi}=(\beta_{0}~\beta_{1}~\ldots~\beta_{D-1})^{T}$ represent
-vectors in ${\cal H}$, with numbers $\alpha_{i}$ and $\beta_{i}$
-drawn from $\Fpp$, and where $(\cdot)^{T}$ is the transpose.
+We are interested in the vector space ${\cal H}$ of dimension $D$
+defined over the complexified field $\Fpp$. Let $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$
+and $\ket{\Phi}=\begin{pmatrix}\beta_{0} & \beta_{1} & \ldots & \beta_{D-1}\end{pmatrix}^{T}$
+represent vectors in ${\cal H}$, with numbers $\alpha_{i}$ and $\beta_{i}$
+drawn from $\Fpp$, and where $\left(\cdot\right)^{T}$ is the transpose.
 
@@
 \begin{equation}
-\ip{\Phi}{\Psi}=\sum_{i=0}^{D-1}~\beta_{i}^{p}~\alpha_{i}^{\;}\ .
+\ip{\Phi}{\Psi}=\sum_{i=0}^{D-1}\beta_{i}^{p}\alpha_{i}\,.
 \end{equation}
@@
 
-For any vector $\ket{\Psi}=(\alpha_{0}~\alpha_{1}~\ldots~\alpha_{D-1})^{T}$,
-the Hermitian dot product $\ip{\Psi}{\Psi}$ is equal to $\sum_{i=0}^{D-1}~\fnorm{\alpha_{i}}$,
+For any vector $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$,
+the Hermitian dot product $\ip{\Psi}{\Psi}$ is equal to $\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}$,
 which is the sum of the field norms for the complex coefficients.
@@
 \begin{equation}
-\fnorm{\ket{\Psi}}=\ip{\Psi}{\Psi}=\sum_{i=0}^{D-1}~\fnorm{\alpha_{i}}\ .\label{fnormD.eq}
+\fnorm{\ket{\Psi}}=\ip{\Psi}{\Psi}=\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}\,.\label{fnormD.eq}
 \end{equation}

### 2018-03-21 dissertation.tex
dissertation.lyx "3.4 Discrete Quantum Theory (I)" Updating...

@@
 \begin{enumerate}[label=(\Alph{enumi})]
-\item $\ip{\Phi}{\Psi}$ is the complex conjugate of $\ip{\Psi}{\Phi}$; 
-\item $\ip{\Phi}{\Psi}$ is conjugate linear in its first argument and linear
-in its second argument; 
-\item $\ip{\Psi}{\Psi}$ is always non-negative and is equal to~0 only
-if $\ket{\Psi}$ is the zero vector. 
+\item \label{enu:inner-product-complex-conjugate}$\ip{\Phi}{\Psi}$ is
+the complex conjugate of $\ip{\Psi}{\Phi}$; 
+\item \label{enu:inner-product-linear}$\ip{\Phi}{\Psi}$ is conjugate linear
+in its first argument and linear in its second argument; 
+\item \label{enu:inner-product-positive-definite}$\ip{\Psi}{\Psi}$ is
+always non-negative and is equal to~0 only if $\ket{\Psi}$ is the
+zero vector. 
 \end{enumerate}
@@
 \begin{definition}[Hermitian dot product] Given vectors $\ket{\Phi}$
-and $\ket{\Psi}\in{\cal H}$, the Hermitian dot product of these vectors
-is: 
+and $\ket{\Psi}\in{\cal H}$, it can be shown~\cite{grove2002classical}
+the Hermitian dot product is always reducible to the form 
 \begin{equation}
@@
 are said to be orthogonal if $\ip{\Phi}{\Psi}=0$. This product satisfies
-conditions A and B for inner products but violates condition C since
-in every finite field there always exists a non-zero vector $\ket{\Psi}$
-such that $\ip{\Psi}{\Psi}=0$. The reason is that addition in finite
-fields eventually ``wraps around'' (because of their cyclic or modular
-structure), allowing the sum of non-zero elements to be zero. The
-fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$ decreases
-with the order $p$.
+conditions \ref{enu:inner-product-complex-conjugate} and \ref{enu:inner-product-linear}
+for inner products but violates condition \ref{enu:inner-product-positive-definite}
+since in every finite field there always exists a non-zero vector
+$\ket{\Psi}$ such that $\ip{\Psi}{\Psi}=0$. The reason is that addition
+in finite fields eventually ``wraps around'' (because of their cyclic
+or modular structure), allowing the sum of non-zero elements to be
+zero. The fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$
+decreases with the order $p$.
 
@@
 The field norm of a vector can vanish for non-vanishing vectors.
+
+\section{Irreducible Discrete $D$-dimensional States: Generalized Discrete
+Bloch Sphere\label{DQCnqubitBloch.sec}}
+
+In the one-qubit state with coefficients in $\Fpp$, the discrete
+analog of the Bloch sphere is constructed by exact analogy to the
+continuous case: we first require that the coefficients of the single
+qubit basis obey 
+\begin{equation}
+\|\psi_{1}\|^{2}=|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=1\label{DQA2.eq}
+\end{equation}
+in the discrete field. In \ref{appU.sec}, we show that there are
+$p(p^{2}-1)$ such values.\todo{{Check reference...}} Given this
+requirement, which is similar in form to the conservation of probability,
+but not as useful due to the lack of orderable probability values,
+we can immediately conclude that the discrete analog of the Hopf fibration
+is again 
+\begin{eqnarray}
+X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
+Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{DQA6.eq}\\
+Z & = & \left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
+\end{eqnarray}
+but now with all computations in $\pmod{p}$. At this point one simply
+writes down all possible discrete values for the complex numbers $\left(\alpha_{0},\alpha_{1}\right)$
+satisfying Eq.~(\ref{DQA2.eq}) and enumerates those that project
+to the same value of $\{X,Y,Z\}$. This equivalence class is the discrete
+analog of the circle in the complex plane that was eliminated in the
+continuous case. In \ref{appH.sec}, we show that $p+1$ discrete
+values of $\{\alpha_{0},\alpha_{1}\}$ with unit norm map to the same
+point under the Hopf map \Eq{DQA6.eq}; we may think of these as
+discrete circles or projective lines of equivalent, physically indistinguishable,
+complex phase. The surviving $p(p-1)$ values of $\{\alpha_{0},\alpha_{1}\}$
+correspond to irreducible physical states of the discrete single qubit
+system. %% Several examples are shown in Figure \ref{bloch.fig}. %%Thus,
+for example, choosing the underlying field to be $\Fppx{3}$, there
+are exactly 6 single-qubit state vectors to populate the Bloch sphere;
+the four equivalent phase-multiples mapping to each of the six points
+on the $\Fppx{3}$ Bloch sphere are collapsed and regarded as physically
+indistinguishable. In Figure \ref{bloch.fig}, we plot the irreducible
+states on the Bloch sphere for $p=3$, $7$, and $11$. Note that
+the Cartesian lengths of the real vectors corresponding to the points
+on the Bloch sphere vary considerably due to the nature of discrete
+fields; we have artificially normalized them to a ``continuous world''
+unit radius sphere for conceptual clarity.
+
+\begin{figure}[htb]
+%\vspace{-0.2in}  %% \includegraphics[width=0.9\columnwidth]{./Bloch_sphere.pdf}%%\includegraphics[width=2.0\columnwidth]{./picA.png}%%\includegraphics[width=2.0\columnwidth]{./picB.png}
+
+\begin{centering}
+\hspace*{-0.5cm}\includegraphics[width=1.1\columnwidth]{\string"../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/picC\string".png}
+%%\includegraphics[width=0.5\textwidth]{./picAB.eps}\vspace{-0.2in}
+ %% adjust blank space?
+\par\end{centering}
+\caption{Schematically normalized plots of the elements of the discrete Bloch
+sphere, the irreducible single-qubit (two-dimensional) state vectors
+with unit norm over the field $\Fpp$. We show the results for $p=3$,
+$7$, and $11$. For example, in $\Fppx{3}$, there are 24 vectors
+of unit norm, but only the 6 inequivalent classes appear in the plot.
+The $p+1=4$ equivalent vectors in each class differ only by a complex
+discrete phase.}
+\label{bloch.fig} 
+\end{figure}
+
+\subsection{Counting states on the $n$-qubit Bloch sphere}
+
+We have the unique opportunity in the finite-field approach to quantum
+computing to precisely identify and enumerate the physical states.
+In the conventional theory, as we have seen, we employ a generalized
+Hopf fibration on the normalized states to project out a circle of
+phase-equivalent states, yielding the generalized Bloch sphere.
+
+In the introduction to this section, we sketched the counting of the
+irreducible single-qubit discrete states. To count the number of inequivalent
+discrete states for the general $n$-qubit case with coefficients
+in $\Fpp$, we first must find the set of unit-norm states, and then
+determine the equivalence classes of unit-norm states under discrete
+phase transformations; we can then enumerate the list of states on
+the discrete generalized Bloch sphere. By executing computer searches
+of these spaces, we discovered an hypothesis for a closed-form solution
+for the counting of the states, and were then able to find a rigorous
+inductive proof of the enumeration, which is presented in the Appendix.
+
+This process of describing the discrete $n$-qubit irreducible states
+can again be understood geometrically by following the discrete analog
+of the Hopf fibration. First, we construct the discrete version of
+the quadratic unit-length form that automatically annihilates the
+distinction among states differing only by a discrete phase, 
+\begin{eqnarray}
+\hspace*{-0.5cm}\Hat{a}=(|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots)\ ,
+\end{eqnarray}
+where 
+\begin{eqnarray}
+\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
+\end{eqnarray}
+{}From \ref{appH.sec}, we know that $p+1$ elements of this discrete
+$\Sphere{2\times2^{n}-1}$ structure map to the \textit{same point\/}
+in $\Hat{a}$. Each set of $(p+1)$ redundant points is, geometrically
+speaking, the \textit{discrete Hopf fibration circle\/} living above
+each \textit{irreducible\/} point of the $n$-qubit state description.
+These $p+1$ points are interpretable as the $p$ finite points plus
+the single point at infinity of the projective discrete line (see,
+e.g., \cite{Arnold}).
+
+The next part of this argument is the determination of the unit-norm
+states, effectively the space of allowed discrete partitions of unity;
+we cannot exactly call these ``probability-conserving'' sectors
+of the state coefficients since we do not have a well defined notion
+of probability, but we do have a well-defined notion of partition
+of unity. The tally of unit-norm states is $p^{2^{n}-1}(p^{2^{n}}-1)$
+(see \ref{appU.sec}) compared to the total number $p^{2\times2^{n}}$
+of possible complex integer state vectors that could be chosen. This
+unit-norm state structure is the discrete analog of $\Sphere{2\times2^{n}-1}$.
+
+Finally, we repeat the last step of the $n$-qubit continuous Hopf
+fibration process for discrete $n$-qubit states, eliminating the
+discrete set of $p+1$ equivalent points that map to the same point
+$\Hat{a}$ on the generalized $n$-qubit Bloch sphere. Dividing the
+tally $p^{2^{n}-1}(p^{2^{n}}-1)$ of unit norm states by the $p+1$
+elements of each phase-equivalent discrete circle, we find 
+\[
+\frac{p^{2^{n}-1}(p^{2^{n}}-1)}{p+1}=p^{2^{n}-1}(p-1)\,\prod_{k=1}^{n-1}(p^{2^{k}}+1)
+\]
+as the total count of unique irreducible states in a discrete $n$-qubit
+configuration (see \ref{appI.sec}). The resulting object is precisely
+the discrete version of $\CP{D-1}$, which we might call a \textit{discrete
+complex projective space\/} or $\DCP{D-1}$, where $D=2^{n}$ as
+usual.
+
+\Comment{
+
+\subsection{Counting states on the $n$-qubit Bloch sphere}
+
+Although we do not have a rigorous proof for the counting of discrete
+unit-norm states and the number of irreducible unit-norm states in
+the discrete generalized Bloch sphere for $n$-qubit states with coefficients
+in $\Fpp$, we have run extensive computer searches of the state features
+for a range of compatible primes $p$ and number of qubits $n$. From
+these experimental investigations, we have induced a closed-form solution
+for the counting that agrees for every possible combination of parameters
+that can be computed in reasonable time (the computational complexity
+becomes intractable very quickly).
+
+For $n$-qubit discrete states with coefficients in $\Fpp$, our calculation
+begins with an enumeration of all possible $2^{n}$-tuples of state
+coefficients in $\Fpp$; then the moduli-squared of these tuples are
+summed and compared to unity in $(\mbox{mod}~p)$. Those that survive
+are accumulated in a list of allowed discrete partitions of unity;
+we cannot exactly call these ``probability-conserving'' sectors
+of the state coefficients since we do not have a well defined notion
+of probability, but we do have a well-defined notion of partition
+of unity. The heuristic number that results for the tally of unit-norm
+states is $p^{2^{n}-1}(p^{2^{n}}-1)$, compared to the total number
+$p^{2\times2^{n}}$ of possible complex integer state vectors that
+could be chosen. This unit-norm state structure is now the discrete
+analog of $\Sphere{2\times2^{n}-1}$.
+
+Finally, we construct the discrete version of the quadratic unit-length
+form that automatically annihilates the distinction among states differing
+only by a discrete phase, 
+\begin{eqnarray}
+\hspace*{-0.5cm}\Hat{a}=\{|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\}\ ,
+\end{eqnarray}
+where 
+\begin{eqnarray}
+\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
+\end{eqnarray}
+Computing all the elements of the discrete $\Sphere{2\times2^{n}-1}$
+structure that map to the \textit{same point\/} in $\Hat{a}$, we
+find a $(p+1)$-fold redundancy, exactly as for the one-qubit case;
+each set of $(p+1)$ redundant points is, geometrically speaking,
+the \textit{discrete Hopf fibration circle\/} (see, e.g., Arnold
+\cite{Arnold}) living above each \textit{irreducible\/} point of
+the $n$-qubit state description.
+
+In summary, when the $n$-qubit continuous Hopf fibration process
+is repeated for the discrete analog of $n$-qubit states, we find
+that that analog of a phase ``circle'' is a discrete set $p+1$
+equivalent points that map to the same point $\Hat{a}$ on the generalized
+$n$-qubit Bloch sphere, and therefore there are a total of $p^{2^{n}-1}(p^{2^{n}}-1)/(p+1)$
+unique irreducible states in a discrete $n$-qubit configuration.
+The resulting object is precisely the discrete version of $\CP{D-1}$,
+which we might call a \textit{discrete complex projective space\/}
+or $\DCP{D-1}$. }
 

### 2018-03-22 dissertation.tex
dissertation.lyx Convert back to using my own document class...

@@
 
-\author{{Yu-Tsung Tai}}
+\author{Yu-Tsung Tai}
 
@@
 
-\acknowledgements{The acknowledgments are designed to recognize
+\begin{acknowledgments}The acknowledgments are designed to recognize
 people or agencies to whom you feel grateful for any academic, technical,
@@
 of your committee here, as well as institutions that provided funding,
-your typist, or anyone else who helped.} \acknowledgementspage
-
-%\preface{}
-% \prefacepage
-
-\abstract{Our primary research interest is to build a quantum computing
-model characterizing realistic quantum computers. While most of the
-quantum computing models based on uncomputable numbers, that is, the
-continuum of real numbers, most of the classical computers in our
-daily life are digital instead of analog computers. This highlight
-the necessity to investigate discrete models for quantum theory and
-computing. Specifically, we start from replacing the continuum of
-complex numbers by the discrete finite fields. Although we have fruitful
-results on their geometric implications and computing powers, their
-probability models are still not completely satisfactory. To address
-this issue, we further exploited quantum interval-valued probability,
-and proved an imprecise version of foundational results such as the
-Gleason and Kochen-Specker theorems.} \abstractpage
-
+your typist, or anyone else who helped.\end{acknowledgments}
+\begin{abstract}
+Our primary research interest is to build a quantum computing model
+characterizing realistic quantum computers. While most of the quantum
+computing models based on uncomputable numbers, that is, the continuum
+of real numbers, most of the classical computers in our daily life
+are digital instead of analog computers. This highlight the necessity
+to investigate discrete models for quantum theory and computing. Specifically,
+we start from replacing the continuum of complex numbers by the discrete
+finite fields. Although we have fruitful results on their geometric
+implications and computing powers, their probability models are still
+not completely satisfactory. To address this issue, we further exploited
+quantum interval-valued probability, and proved an imprecise version
+of foundational results such as the Gleason and Kochen-Specker theorems.
+\end{abstract}
 \tableofcontents{}
@@
 in the discrete field. In \ref{appU.sec}, we show that there are
-$p(p^{2}-1)$ such values.\todo{{Check reference...}} Given this
-requirement, which is similar in form to the conservation of probability,
-but not as useful due to the lack of orderable probability values,
-we can immediately conclude that the discrete analog of the Hopf fibration
+$p(p^{2}-1)$ such values.\todo{Check reference...} Given this requirement,
+which is similar in form to the conservation of probability, but not
+as useful due to the lack of orderable probability values, we can
+immediately conclude that the discrete analog of the Hopf fibration
 is again 
@@
 
-\Comment{
-
-\subsection{Counting states on the $n$-qubit Bloch sphere}
-
-Although we do not have a rigorous proof for the counting of discrete
-unit-norm states and the number of irreducible unit-norm states in
-the discrete generalized Bloch sphere for $n$-qubit states with coefficients
-in $\Fpp$, we have run extensive computer searches of the state features
-for a range of compatible primes $p$ and number of qubits $n$. From
-these experimental investigations, we have induced a closed-form solution
-for the counting that agrees for every possible combination of parameters
-that can be computed in reasonable time (the computational complexity
-becomes intractable very quickly).
-
-For $n$-qubit discrete states with coefficients in $\Fpp$, our calculation
-begins with an enumeration of all possible $2^{n}$-tuples of state
-coefficients in $\Fpp$; then the moduli-squared of these tuples are
-summed and compared to unity in $(\mbox{mod}~p)$. Those that survive
-are accumulated in a list of allowed discrete partitions of unity;
-we cannot exactly call these ``probability-conserving'' sectors
-of the state coefficients since we do not have a well defined notion
-of probability, but we do have a well-defined notion of partition
-of unity. The heuristic number that results for the tally of unit-norm
-states is $p^{2^{n}-1}(p^{2^{n}}-1)$, compared to the total number
-$p^{2\times2^{n}}$ of possible complex integer state vectors that
-could be chosen. This unit-norm state structure is now the discrete
-analog of $\Sphere{2\times2^{n}-1}$.
-
-Finally, we construct the discrete version of the quadratic unit-length
-form that automatically annihilates the distinction among states differing
-only by a discrete phase, 
-\begin{eqnarray}
-\hspace*{-0.5cm}\Hat{a}=\{|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\}\ ,
-\end{eqnarray}
-where 
-\begin{eqnarray}
-\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
-\end{eqnarray}
-Computing all the elements of the discrete $\Sphere{2\times2^{n}-1}$
-structure that map to the \textit{same point\/} in $\Hat{a}$, we
-find a $(p+1)$-fold redundancy, exactly as for the one-qubit case;
-each set of $(p+1)$ redundant points is, geometrically speaking,
-the \textit{discrete Hopf fibration circle\/} (see, e.g., Arnold
-\cite{Arnold}) living above each \textit{irreducible\/} point of
-the $n$-qubit state description.
-
-In summary, when the $n$-qubit continuous Hopf fibration process
-is repeated for the discrete analog of $n$-qubit states, we find
-that that analog of a phase ``circle'' is a discrete set $p+1$
-equivalent points that map to the same point $\Hat{a}$ on the generalized
-$n$-qubit Bloch sphere, and therefore there are a total of $p^{2^{n}-1}(p^{2^{n}}-1)/(p+1)$
-unique irreducible states in a discrete $n$-qubit configuration.
-The resulting object is precisely the discrete version of $\CP{D-1}$,
-which we might call a \textit{discrete complex projective space\/}
-or $\DCP{D-1}$. }
-
 \section{Discrete Quantum Computing (I)\label{discretequantumcomputingI}}

### 2018-03-23 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex \NewDocumentCommand{\newInterval}{o o o}{...} Added...
revised_prop_letter_ajhs.tex preamble updated...
prop.bib @Misc{HKSS1999} @Unpublished{HKSS1999apsrev4} Added...
revised_prop_letter_ajhs.tex \section{Experimental Data and \texorpdfstring{$\delta$}{delta}-determinism} Fix typos...

@@
 \newcommand{\pmeas}{\ensuremath{\mu}}
-\newcommand{\imposs}{{\text{\wesa{impossible}}}}
-\newcommand{\likely}{{\text{\wesa{likely}}}}
-\newcommand{\unlikely}{{\text{\wesa{unlikely}}}}
-\newcommand{\necess}{{\text{\wesa{certain}}}}
-\newcommand{\unknown}{{\text{\wesa{unknown}}}}
-\newcommand{\midd}{{\text{\wesa{middle}}}}
+
+\NewDocumentCommand{\newInterval}{o o o o}{
+ % \newcommand{#1}{\text{\wesa{{#2}}}}
+ \newcommand{#1}{\ensuremath{\left[{#3}\right]}}
+ % \newcommand{#1}{\ensuremath{I\left({#4}\right)}}
+}
+\newInterval[\imposs][impossible][0,0][0]
+\newInterval[\likely][likely][\tfrac{1}{2},1][\tfrac{1}{2},1]
+\newInterval[\unlikely][unlikely][0,\tfrac{1}{2}][0,\tfrac{1}{2}]
+\newInterval[\necess][certain][1,1][1]
+\newInterval[\unknown][unknown][0,1][0,1]
+\newInterval[\midd][middle][\tfrac{1}{4},\tfrac{3}{4}][\tfrac{1}{4},\tfrac{3}{4}]
+
 \newcommand{\fket}[1]{{|#1\rangle}}
@@
 \NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
+\NewDocumentEnvironment{oldText}{m}{\clearpage{}#1{The following is old text.}}{#1{The old text ends here.}}
+\NewDocumentEnvironment{newText}{m}{\columnbreak{}#1{The following is new text.}}{#1{The new text ends here.}}
 
@@
 \end{table*}
-It is Meyer's great insight to realize that the Kochen-Specker theorem can be nullified 
-by replacing the field of the reals by rational numbers.  In other
-words, Meyer exclusively attributes finite-precision errors to the
-description of the states defined in a general Hilbert space. The
-response of Mermin, argues against Meyer's interpretation but accepts
+It is Meyer's great insight to realize that the Kochen-Specker theorem
+can be nullified by replacing the field of the reals by rational numbers.
+In other words, Meyer exclusively attributes finite-precision errors
+to the description of the states defined in a general Hilbert space.
+The response of Mermin argues against Meyer's interpretation but accepts
 his framework. More generally, there have been responses that argue
 that the effect of finite-precision measurements on the Kochen-Specker
-theorem requires a different approach altogether (see for example Ax
-and Kochen's communication cited by Cabello~\cite{Cabello2002}). Our
-approach is agnostic about attributing elements of reality to the
-state function (as Meyer did). We simply attribute lack of certainty
-to the uncertain results obtained through the use of a measuring
-instrument. Thus, the parameter~$\delta$ in our framework reflects
-insufficient knowledge of the experimenter, which could be due to a
-variety of reasons related to imperfections of devices. For example, a
-typical question that an experimenter may not be able to answer
-accurately would be ``did an electron land in the left half or the
-right half of the screen?''  There are cases in which the electron
-would land too close to the middle of the screen for the experimenter
-to be able to determine with certainty that it was left or right of
-the center. We simply record this imprecision in the probability we
-assign to events, and use the axioms of probability theory to argue
-that a sharp transition occurs when the imprecision reaches a certain
-value.
+theorem requires a different approach altogether (see for example
+Ax and Kochen's communication cited by Cabello~\cite{Cabello2002}).
+Our approach is agnostic about attributing elements of reality to
+the state function (as Meyer did). We simply attribute lack of certainty
+to the uncertain results obtained through the use of a measuring instrument.
+Thus, the parameter~$\delta$ in our framework reflects insufficient
+knowledge of the experimenter, which could be due to a variety of
+reasons related to imperfections of devices. For example, a typical
+question that an experimenter may not be able to answer accurately
+would be ``did an electron land in the left half or the right half
+of the screen?'' There are cases in which the electron would land
+too close to the middle of the screen for the experimenter to be able
+to determine with certainty that it was left or right of the center.
+We simply record this imprecision in the probability we assign to
+events, and use the axioms of probability theory to argue that a sharp
+transition occurs when the imprecision reaches a certain value.
 
@@
 To see this idea in the context of a quantum experiment, consider
-a three-dimensional Hilbert space with
-one-dimensional projectors~$P_{\rho}$, two-dimensional projectors
-$P_{\rho}+P_{\sigma}$, and an experiment that is experiment repeated $12$
-times. By the Kochen-Specker theorem, it is impossible to build a probability
-measure that maps every projection to either $0=\frac{0}{12}$ or
-$1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
+a three-dimensional Hilbert space with one-dimensional projectors~$P_{\rho}$,
+two-dimensional projectors $P_{\rho}+P_{\sigma}$, and an experiment
+that repeated $12$ times. By the Kochen-Specker theorem, it is impossible
+to build a probability measure that maps every projection to either
+$0=\frac{0}{12}$ or $1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
 defined in Table~\ref{tab:probability-measures} is not a QIVPM.
@@
 
-\input{revised_prop_letter_ajhs.bbl}
-% \bibliography{prop}
+% \input{revised_prop_letter_ajhs.bbl}
+\bibliography{prop}
 \end{document}

### 2018-03-23 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex \section{The Born Rule and Gleason's Theorem} Add new texts...

@@
 \NewDocumentCommand{\newInterval}{o o o o}{
- % \newcommand{#1}{\text{\wesa{{#2}}}}
- \newcommand{#1}{\ensuremath{\left[{#3}\right]}}
+ \newcommand{#1}{\text{\wesa{{#2}}}}
+ % \newcommand{#1}{\ensuremath{\left[{#3}\right]}}
  % \newcommand{#1}{\ensuremath{I\left({#4}\right)}}
@@
 \NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
-\NewDocumentEnvironment{oldText}{m}{\clearpage{}#1{The following is old text.}}{#1{The old text ends here.}}
-\NewDocumentEnvironment{newText}{m}{\columnbreak{}#1{The following is new text.}}{#1{The new text ends here.}}
+\NewDocumentEnvironment{compare}{}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
+\NewDocumentEnvironment{oldText}{m}{#1{The following is old text.}\noindent\begin{minipage}[t]{1\columnwidth}}{#1{The old text end here.}\end{minipage}\newpage}
+\NewDocumentEnvironment{newText}{m}{\noindent\begin{minipage}[t]{1\columnwidth}#1{The following is new text.}}{\end{minipage}#1{The new text end here.}}
 
@@
 cannot reveal the underlying state is not surprising. Under certain
-conditions, we can however guarantee that the uncertainty in
-measurements is consistent with \emph{some} non-empty collection of
-quantum states. Furthermore, we can relate the uncertainty in
-measurements to the volume of quantum states such that, in the limit
-of infinitely precise measurements, the volume of states collapses to
-a single state.
-
-To that end, we construct a family of QIVPMs parameterized by
-\emph{blurring} functions $f:\left[0,1\right]\rightarrow\mathscr{I}$ that
-formalize how the real-valued probabilities are mapped to
-intervals. We also introduce a notion of norm that quantifies the
-distance between (pure or mixed) states.  The norm of a pure
-state $\rho=\proj{\psi}$ is defined as usual by
-$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
-given any Hermitian operator~$A$, we consider the usual operator norm
-$\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert
-  =1}\left\Vert A\ket{\psi}\right\Vert $, which is also known as the
-$2$-norm or the spectral
-norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
-Then, a finite-precision extension of Gleason's theorem can be stated as
-follows.
+conditions, we can however guarantee that the uncertainty in measurements
+is consistent with \emph{some} non-empty collection of quantum states.
+Furthermore, we can relate the uncertainty in measurements to the
+volume of quantum states such that, in the limit of infinitely precise
+measurements, the volume of states collapses to a single state.
+
+\begin{compare}
+\begin{oldText}{\yutsung}
+To that end, we construct a family of QIVPMs parameterized by \emph{blurring}
+functions $f:\left[0,1\right]\rightarrow\mathscr{I}$ that formalize
+how the real-valued probabilities are mapped to intervals. We also
+introduce a notion of norm that quantifies the distance between (pure
+or mixed) states. The norm of a pure state $\rho=\proj{\psi}$ is
+defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
+Similarly, given any Hermitian operator~$A$, we consider the usual
+operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
+which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+Then, a finite-precision extension of Gleason's theorem can be stated
+as follows.
 
@@
 
-\begin{thm}[Finite-Precision Extension of the Gleason
-  Theorem]\label{thm:Finite-precision-Gleason}Let $f$ be a blurring
-  function and let $f \circ \muB_{\rho}$ be a QIVPM, where
-  $\muB_{\rho}$ is the probability measure induced by the
-  Born rule for a given state~$\rho$. Let $\alpha$ be the maximum
-  length of intervals in its image. If a state $\rho'$ is consistent
-  with $f\circ\muB_{\rho}$ on all events, i.e.,
-  $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
-  then the norm of their difference is bounded by $\alpha$, i.e.,
-  $\left\Vert \rho-\rho'\right\Vert \le \alpha$.\end{thm}
-
-The proof proceeds as follows. Given a state~$\rho'$ consistent with
-$f\circ\muB_{\rho}$, we have
-$\muB_{\rho'}\left(\proj{\psi}\right)\in
-f\left(\muB_{\rho}\left(\proj{\psi}\right)\right)$ for any
-one-dimensional projector $P=\proj{\psi}$. Since the maximum length of
-the intervals in $\mathscr{I}$ is $\alpha$, it is also the upper bound
-of the difference:
+\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
+$f$ be a blurring function and let $f\circ\muB_{\rho}$ be a QIVPM,
+where $\muB_{\rho}$ is the probability measure induced by the Born
+rule for a given state~$\rho$. Let $\alpha$ be the maximum length
+of intervals in its image. If a state $\rho'$ is consistent with
+$f\circ\muB_{\rho}$ on all events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
+then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
+\end{oldText}
+
+\begin{newText}{\yutsung}
+To that end, we construct a family of QIVPMs parameterized by \emph{blurring}
+functions. A blurring function $f:\left[0,1\right]\rightarrow\mathscr{I}$
+maps every real-valued probability $x\in\left[0,1\right]$ to a set
+of intervals $f\left(x\right)=\left[\ell,r\right]$ containing $x$,
+where $\left[0,1\right]$ denotes the set of real-valued probabilities
+which should not be considered as the interval-valued probability
+$\unknown$. We also introduce a notion of norm that quantifies the
+distance between (pure or mixed) states. The norm of a pure state
+$\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
+Similarly, given any Hermitian operator~$A$, we consider the usual
+operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
+which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+In fact, for any such matrix, including the density matrix~$\rho$,
+the norm is the maximum absolute value of its eigenvalue. Then, a
+finite-precision extension of Gleason's theorem can be stated as follows.
+
+% the composited function~$\ultramodular\circ\mu$ satisfies the constraints
+% for IVPMs naturally no matter in classical or quantum case. Conversely,
+% if $\ultramodular\circ\mu$ is always a IVPM, then the function~$\ultramodular$
+% is ultramodular. In other words, $\ultramodular$ is ultramodular
+% is a necessary and sufficient condition for $\ultramodular\circ\mu$
+% is always a IVPM as we next show.
+
+% When we generalized quantum probability measures to QIVPMs, we changed
+% the range from the unit interval $\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
+% This replacement suggests to find a function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
+% to replace a real-valued probability $\mu\left(P\right)$ by an interval-valued 
+% one $\ultramodular\left(\mu\left(P\right)\right)$. In other words,
+% compositing $\ultramodular$ with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+% produces a function $\ultramodular\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\ultramodular}{\rightarrow}\mathscr{I}$
+% with the same domain and range as a QIVPM. In order to guarantee $\ultramodular\circ\mu$
+% always a QIVPM, we consider the following homomorphism-like properties
+% for~$\ultramodular$.
+
+\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason-1}Let
+$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a blurring function
+and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
+probability measure induced by the Born rule for a given state~$\rho$.
+Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
+If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
+events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
+then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
+\end{newText}
+\end{compare}
+
+The proof proceeds as follows. Given a state~$\rho'$ consistent
+with $f\circ\muB_{\rho}$, we have $\muB_{\rho'}\left(\proj{\psi}\right)\in f\left(\muB_{\rho}\left(\proj{\psi}\right)\right)$
+for any one-dimensional projector $P=\proj{\psi}$. Since the maximum
+length of the intervals in $\mathscr{I}$ is $\alpha$, it is also
+the upper bound of the difference: 
 \[
-\left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le \alpha\,.
+\left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le\alpha\,.
 \]
@@
 and equal to $\left\Vert \rho-\rho'\right\Vert $~\cite{GolubVanLoan1996,Foucart2012}.
-Hence, $\left\Vert \rho-\rho'\right\Vert \le \alpha$.
+Hence, $\left\Vert \rho-\rho'\right\Vert \le\alpha$.
 

### 2018-03-24 revised_prop_letter_ajhs.tex
revision with appendix integrated

@@
 }
-\newInterval[\imposs][impossible][0,0][0]
-\newInterval[\likely][likely][\tfrac{1}{2},1][\tfrac{1}{2},1]
-\newInterval[\unlikely][unlikely][0,\tfrac{1}{2}][0,\tfrac{1}{2}]
-\newInterval[\necess][certain][1,1][1]
-\newInterval[\unknown][unknown][0,1][0,1]
+%% \newInterval[\imposs][impossible][0,0][0]
+%% \newInterval[\likely][likely][\tfrac{1}{2},1][\tfrac{1}{2},1]
+%% \newInterval[\unlikely][unlikely][0,\tfrac{1}{2}][0,\tfrac{1}{2}]
+%% \newInterval[\necess][certain][1,1][1]
+%% \newInterval[\unknown][unknown][0,1][0,1]
 \newInterval[\midd][middle][\tfrac{1}{4},\tfrac{3}{4}][\tfrac{1}{4},\tfrac{3}{4}]
+
+\newcommand{\imposs}{\textbf{\textsf{F}}}
+\newcommand{\necess}{\textbf{\textsf{T}}}
+\newcommand{\unknown}{\textbf{\textsf{U}}}
 
@@
 conventional quantum-mechanical probability measures to include the
-effect of imperfect measurements. 
-There are long-standing debates in the foundations of quantum
-mechanics regarding the tension between finite precision measurement
-and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of
-a theory that is contextual depends upon whether compatible sets of
+effect of imperfect measurements.  There are long-standing debates in
+the foundations of quantum mechanics regarding the tension between
+finite precision measurement and
+contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of a
+theory that is contextual depends upon whether compatible sets of
 observables are measured together or separately; a non-contextual
 theory gives the same results in either case.  A classic example of
-the varying opinions on the impact of imprecision is the disagreement
-between Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999}
-on whether finite-precision measurements invalidate the spirit of the
-Kochen-Specker
-theorem~\cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}.
-The Kochen-Specker theorem is in essence a mathematical statement
-about contextuality, asserting that in a Hilbert space of dimension
-$d \ge 3$, it is impossible to associate determinate probabilities,
-$\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
-way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = \mathbb{1}$, then
-$\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
-determinate probabilities $0$ or~$1$ to the measurement outcomes when
-the Hilbert space is defined over the field of rational numbers,
-therefore nullifying the theorem~\cite{PhysRevLett.83.3751}.
-However, Mermin then argued that measurement outcomes must depend
-smoothly on slight changes in the experimental configuration, leading
-him to assert that the impact of Meyer's negative result is
-``unsupportable'' on physical grounds~\cite{Mermin1999}.  The debate
-on whether contextuality is consistent with experimental outcomes
-continues to be an active topic of
+the varying opinions on the impact of imprecision is the claim by
+Meyer~\cite{PhysRevLett.83.3751} that finite-precision measurements
+invalidate the spirit of the Kochen-Specker theorem. This claim was
+countered in the same year by Havlicek et al. ~\cite{HKSS1999apsrev4}
+and Mermin~\cite{Mermin1999} and the debate continues to be an active
+topic of
 research~\cite{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+
+The Kochen-Specker
+theorem~\cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}
+is in essence a mathematical statement about contextuality, asserting
+that in a Hilbert space of dimension $d \ge 3$, it is impossible to
+associate determinate probabilities, $\mu(P_i)= 0$ or $1$, with every
+projection operator~$P_i$, in such a way that, if a set of commuting
+$P_i$ satisfies $\sum_i P_i = \mathbb{1}$, then $\sum_i \mu(P_i) = 1$.
+Meyer showed that one {\it can\/} assign determinate probabilities $0$
+or~$1$ to the measurement outcomes when the Hilbert space is defined
+over the field of rational numbers, therefore nullifying the
+theorem~\cite{PhysRevLett.83.3751}.  However, Mermin then argued that
+measurement outcomes must depend smoothly on slight changes in the
+experimental configuration, leading him to assert that the impact of
+Meyer's negative result is ``unsupportable'' on physical
+grounds~\cite{Mermin1999}.
 
@@
 
-%% ajh "begin" doubled, replace here; two missing commas
-We start our investigation with the concept of $\delta$-determinism,
+To start our investigation, we note that Meyer attributes
+finite-precision errors \emph{exclusively} to the description of the
+states defined in a general Hilbert space. Mermin's response argues
+against Meyer's interpretation but accepts his framework. Others,
+however, have argued that the effect of finite-precision measurements
+on the Kochen-Specker theorem requires a different approach altogether
+(see for example Ax and Kochen's communication cited by
+Cabello~\cite{Cabello2002}). Here, we propose such a new approach.
+
+Our approach introduces the concept of $\delta$-determinism,
 where~$\delta$ quantifies the effect of finite-precision uncertainties
-on measurement outcomes. We recast the Kochen-Specker theorem using
+on measurement outcomes.  Our parameter $\delta$ is not necessarily
+related to the description of states; we are agnostic about
+attributing elements of reality to the state function. Instead, we
+attribute lack of certainty to the uncertain results obtained through
+the use of a measuring instrument.  Thus, the parameter~$\delta$ in
+our framework reflects insufficient knowledge of the experimenter,
+which could be due to a variety of reasons related to imperfections of
+devices. For example, a typical question that an experimenter may not
+be able to answer accurately would be ``did an electron land in the
+left half or the right half of the screen?''  There are cases in which
+the electron would land too close to the middle of the screen for the
+experimenter to be able to determine with certainty that it was left
+or right of the center.  We simply record this imprecision by
+generalizing the probabilities assigned to events to intervals of
+uncertainties.
+
+%% and use the axioms of probability theory to argue that a sharp
+%% transition occurs when the imprecision reaches a certain value.
+
+We then recast the Kochen-Specker theorem using
 $\delta$-determinism to quantify the effects of finite precision and
@@
 to 1 we note a transition from contextuality to non-contextuality. For
-a \emph{non-vanishing} range of $\delta$, quantum-mechanical
+a \emph{non-vanishing} range of~$\delta$, quantum-mechanical
 contextuality continues to hold, maintaining the Kochen-Specker
@@
 be irreconcilable aspects of contextuality.
-
-%The quantum-mechanical requirement for contextuality
-%continues to hold, thus maintaining the Kochen-Specker result for a
-%\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
-%  fixed value} of $\delta$, there is a sharp transition, parallel in
-%its consequences to, say, a phase transition, to
-%\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
-%% simulated by a non-contextual hidden variable theory.
-%% , turning the
-%% system effectively from a quantum system into a classical system. 
-% that is, quantum mechanics suddenly fails to hold, and all variables
-% can be specified simultaneously, turning the theory effectively into a
-% classical theory that can be specified consistently by hidden
-% variables.
-% \yutsung{The part after ``that is''
-%   looks strange.
-% \begin{enumerate}
-% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
-% quantum mechanics can be simulated by a non-contextual deterministic hidden
-% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
-% doesn't make a lot sense.
-% \item The question is whether there exist a QIVPM means ``a classical theory
-% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
-% I need to check whether it qualities as a classical probabilistic hidden variable
-% theory\ldots(?)
-% \end{enumerate}
-% }
-%These results provide a new insight into the Meyer-Mermin debate by
-%presenting a theory in which there is a \emph{parameter} interpolating
-%between what appeared previously to be irreconcilable aspects %interpretations
-%of contextuality.
-% ajh- above: I think "interpretations" is not quite right -> "aspects"?
 
@@
 
+\subsection{Finite-Precision Extension of the Kochen-Specker Theorem}
+
 The first step in our formalization is to introduce a family of QIVPMs
@@
 We can summarize and illustrate the above arguments using
-Fig.~\ref{fignoname}. An additional perspective on the physical
-interpretation of the theorem is in the appendix.
+Fig.~\ref{fignoname}.
 
@@
 
+\subsection{Experimental Data and \texorpdfstring{$\delta$}{delta}-determinism}
+
+\begin{table*}
+\caption{\label{tab:probability-measures}Possible probability measures on
+a Hilbert space of dimension~$d=3$, where $\bar{\mu}_{2}'$ and
+$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
+and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
+by $P$.}
+\centering{}%
+\begin{tabular}{cccccc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{0}\left(P\right)$ & $\bar{\mu}_{1}\left(P\right)$ & $\bar{\mu}_{2}\left(P\right)$ & $\bar{\mu}_{2}'\left(P\right)$ & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors  & $\left[0,0\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left[0,\tfrac{1}{3}\right]$ & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$ & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors  & $\left[1,1\right]$ & $\left[\tfrac{3}{4},1\right]$ & $\left[\tfrac{2}{3},1\right]$ & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$ & $\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+In an experimental setup, $\delta$ is calculated as follows. To
+determine the probability of any event, we typically repeat an
+experiment $n$ times and count the number of times we witness the
+event. This assumes that for each run of the experiment we can
+determine, using our apparatus, whether the event occurred or
+not. Assume an event has an ideal mathematical probability of $0$, and
+we repeat the experiment $100$ times. In a perfect world we should be
+able to refute the event $100$ times and calculate that the
+probability is $0$. We might also observe the event $2$ times and
+refute it $98$ times and therefore calculate the probability to be
+$0.02$. Note that this situation assumes perfect measurement
+conditions and remains within the context of conventional
+(real-valued) probability theory. The question we focus on is what
+happens if we are only able to refute it $97$ times and are
+\emph{uncertain} $3$ times? This is quite common in actual
+experiments. Mathematically we can model this idea by stating that the
+probability of the event is in the range $\left[0,0.03\right]$ which
+says that the probability of the event could be $0$, $0.01$, $0.02$,
+or $0.03$ as each the three uncertain records could either be evidence
+for the event or against it. We just cannot nail it down given the
+current experimental results and therefore represent the evidence as a
+($\delta=$)$0.03$-deterministic probability measure. The interesting
+observation is that the axioms of probability theory (like additivity
+and convexity) impose enough constraints on the structure of
+interval-valued quantum probability measures to make them robust in
+the face of small non-vanishing $\delta$'s.
+
+To see this idea in the context of a quantum experiment, consider
+a three-dimensional Hilbert space with one-dimensional projectors~$P_{\rho}$,
+two-dimensional projectors $P_{\rho}+P_{\sigma}$, and an experiment
+that repeated $12$ times. By the Kochen-Specker theorem, it is impossible
+to build a probability measure that maps every projection to either
+$0=\frac{0}{12}$ or $1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
+defined in Table~\ref{tab:probability-measures} is not a QIVPM.
+
+Now consider what happens if $\frac{1}{4}$ of the data for \emph{every}
+one-dimensional projector is uncertain. A potential account of this
+degradation is to assign to each event $P$ the entire range of possibilities
+$\bar{\mu}_{1}(P)$ as defined in Table~\ref{tab:probability-measures}.
+This measure is not a valid QIVPM because it does not satisfy
+the convexity condition: for any two orthogonal one-dimensional events
+$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$,
+but $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
+which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$.
+Interestingly, it is impossible to find any probability measure that
+would be consistent with these observations, as the interval $\left[\tfrac{3}{4},1\right]$
+is completely disjoint from the interval $\left[0,\tfrac{1}{2}\right]$
+and no amount of shifting of assumptions regarding the precise outcome
+of the uncertain observations could change that disjointness. However,
+as shown next, a sharp transition occurs when $\delta=\tfrac{1}{3}$.
+
+When the proportion of uncertain data reaches $\frac{1}{3}$, the probability measure
+that assigns to each event the entire range of possibilities is
+$\bar{\mu}_{2}$ defined in Table~\ref{tab:probability-measures}.
+This is also not a valid probability measure by the same
+argument as above. However, in this case $\bar{\mu}_{2}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
+and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{2}\left(P_{0}\right)+\bar{\mu}_{2}\left(P_{1}\right)$
+have a \emph{common point}. Hence, by assuming that the uncertain data for
+one-dimensional projectors always support the associated event, while
+those for two-dimensional projectors always refute the event, we can
+find the probability measure~$\bar{\mu}_{2}'$ that can verified to be a
+valid QIVPM and is consistent with the experimental data.
+
+A similar situation happens when more than $\frac{1}{3}$ of data
+is uncertain. In particular, if half of the data is uncertain, the probability
+measure~$\bar{\mu}_{3}$ that assigns to each event the entire range of possibilities
+is already a QIVPM.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{compare}
-\begin{oldText}{\yutsung}
-To that end, we construct a family of QIVPMs parameterized by \emph{blurring}
-functions $f:\left[0,1\right]\rightarrow\mathscr{I}$ that formalize
-how the real-valued probabilities are mapped to intervals. We also
-introduce a notion of norm that quantifies the distance between (pure
-or mixed) states. The norm of a pure state $\rho=\proj{\psi}$ is
-defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
-Similarly, given any Hermitian operator~$A$, we consider the usual
-operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
-which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
-Then, a finite-precision extension of Gleason's theorem can be stated
-as follows.
-
-% the composited function~$\ultramodular\circ\mu$ satisfies the constraints
-% for IVPMs naturally no matter in classical or quantum case. Conversely,
-% if $\ultramodular\circ\mu$ is always a IVPM, then the function~$\ultramodular$
-% is ultramodular. In other words, $\ultramodular$ is ultramodular
-% is a necessary and sufficient condition for $\ultramodular\circ\mu$
-% is always a IVPM as we next show.
-
-% When we generalized quantum probability measures to QIVPMs, we changed
-% the range from the unit interval $\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
-% This replacement suggests to find a function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
-% to replace a real-valued probability $\mu\left(P\right)$ by an interval-valued 
-% one $\ultramodular\left(\mu\left(P\right)\right)$. In other words,
-% compositing $\ultramodular$ with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
-% produces a function $\ultramodular\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\ultramodular}{\rightarrow}\mathscr{I}$
-% with the same domain and range as a QIVPM. In order to guarantee $\ultramodular\circ\mu$
-% always a QIVPM, we consider the following homomorphism-like properties
-% for~$\ultramodular$.
-
-\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
-$f$ be a blurring function and let $f\circ\muB_{\rho}$ be a QIVPM,
-where $\muB_{\rho}$ is the probability measure induced by the Born
-rule for a given state~$\rho$. Let $\alpha$ be the maximum length
-of intervals in its image. If a state $\rho'$ is consistent with
-$f\circ\muB_{\rho}$ on all events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
-then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
-\end{oldText}
-
-\begin{newText}{\yutsung}
 To that end, we construct a family of QIVPMs parameterized by \emph{blurring}
@@
 which should not be considered as the interval-valued probability
-$\unknown$. We also introduce a notion of norm that quantifies the
+$\unknown$. We also need a notion of norm to quantify the
 distance between (pure or mixed) states. The norm of a pure state
 $\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
-Similarly, given any Hermitian operator~$A$, we consider the usual
+In addition, given any Hermitian operator~$A$, we consider the usual
 operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
@@
 finite-precision extension of Gleason's theorem can be stated as follows.
-
-% the composited function~$\ultramodular\circ\mu$ satisfies the constraints
-% for IVPMs naturally no matter in classical or quantum case. Conversely,
-% if $\ultramodular\circ\mu$ is always a IVPM, then the function~$\ultramodular$
-% is ultramodular. In other words, $\ultramodular$ is ultramodular
-% is a necessary and sufficient condition for $\ultramodular\circ\mu$
-% is always a IVPM as we next show.
-
-% When we generalized quantum probability measures to QIVPMs, we changed
-% the range from the unit interval $\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
-% This replacement suggests to find a function $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
-% to replace a real-valued probability $\mu\left(P\right)$ by an interval-valued 
-% one $\ultramodular\left(\mu\left(P\right)\right)$. In other words,
-% compositing $\ultramodular$ with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
-% produces a function $\ultramodular\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\ultramodular}{\rightarrow}\mathscr{I}$
-% with the same domain and range as a QIVPM. In order to guarantee $\ultramodular\circ\mu$
-% always a QIVPM, we consider the following homomorphism-like properties
-% for~$\ultramodular$.
 
@@
 then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
-\end{newText}
-\end{compare}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix*
-\section{Experimental Data and \texorpdfstring{$\delta$}{delta}-determinism}
-
-\begin{table*}
-\caption{\label{tab:probability-measures}Possible probability measures on
-a Hilbert space of dimension~$d=3$, where $\bar{\mu}_{2}'$ and
-$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
-and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
-by $P$.}
-\centering{}%
-\begin{tabular}{cccccc}
-\toprule 
-\addlinespace
-$P$  & $\bar{\mu}_{0}\left(P\right)$ & $\bar{\mu}_{1}\left(P\right)$ & $\bar{\mu}_{2}\left(P\right)$ & $\bar{\mu}_{2}'\left(P\right)$ & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-All one-dimensional projectors  & $\left[0,0\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left[0,\tfrac{1}{3}\right]$ & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$ & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
-\midrule 
-\addlinespace
-All two-dimensional projectors  & $\left[1,1\right]$ & $\left[\tfrac{3}{4},1\right]$ & $\left[\tfrac{2}{3},1\right]$ & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$ & $\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-It is Meyer's great insight to realize that the Kochen-Specker theorem
-can be nullified by replacing the field of the reals by rational numbers.
-In other words, Meyer exclusively attributes finite-precision errors
-to the description of the states defined in a general Hilbert space.
-The response of Mermin argues against Meyer's interpretation but accepts
-his framework. More generally, there have been responses that argue
-that the effect of finite-precision measurements on the Kochen-Specker
-theorem requires a different approach altogether (see for example
-Ax and Kochen's communication cited by Cabello~\cite{Cabello2002}).
-Our approach is agnostic about attributing elements of reality to
-the state function (as Meyer did). We simply attribute lack of certainty
-to the uncertain results obtained through the use of a measuring instrument.
-Thus, the parameter~$\delta$ in our framework reflects insufficient
-knowledge of the experimenter, which could be due to a variety of
-reasons related to imperfections of devices. For example, a typical
-question that an experimenter may not be able to answer accurately
-would be ``did an electron land in the left half or the right half
-of the screen?'' There are cases in which the electron would land
-too close to the middle of the screen for the experimenter to be able
-to determine with certainty that it was left or right of the center.
-We simply record this imprecision in the probability we assign to
-events, and use the axioms of probability theory to argue that a sharp
-transition occurs when the imprecision reaches a certain value.
-
-In an experimental setup, $\delta$ is calculated as follows. To
-determine the probability of any event, we typically repeat an
-experiment $n$ times and count the number of times we witness the
-event. This assumes that for each run of the experiment we can
-determine, using our apparatus, whether the event occurred or
-not. Assume an event has an ideal mathematical probability of $0$, and
-we repeat the experiment $100$ times. In a perfect world we should be
-able to refute the event $100$ times and calculate that the
-probability is $0$. We might also observe the event $2$ times and
-refute it $98$ times and therefore calculate the probability to be
-$0.02$. Note that this situation assumes perfect measurement
-conditions and remains within the context of conventional
-(real-valued) probability theory. The question we focus on is what
-happens if we are only able to refute it $97$ times and are
-\emph{uncertain} $3$ times? This is quite common in actual
-experiments. Mathematically we can model this idea by stating that the
-probability of the event is in the range $\left[0,0.03\right]$ which
-says that the probability of the event could be $0$, $0.01$, $0.02$,
-or $0.03$ as each the three uncertain records could either be evidence
-for the event or against it. We just cannot nail it down given the
-current experimental results and therefore represent the evidence as a
-($\delta=$)$0.03$-deterministic probability measure. The interesting
-observation is that the axioms of probability theory (like additivity
-and convexity) impose enough constraints on the structure of
-interval-valued quantum probability measures to make them robust in
-the face of small non-vanishing $\delta$'s.
-
-To see this idea in the context of a quantum experiment, consider
-a three-dimensional Hilbert space with one-dimensional projectors~$P_{\rho}$,
-two-dimensional projectors $P_{\rho}+P_{\sigma}$, and an experiment
-that repeated $12$ times. By the Kochen-Specker theorem, it is impossible
-to build a probability measure that maps every projection to either
-$0=\frac{0}{12}$ or $1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
-defined in Table~\ref{tab:probability-measures} is not a QIVPM.
-
-Now consider what happens if $\frac{1}{4}$ of the data for \emph{every}
-one-dimensional projector is uncertain. A potential account of this
-degradation is to assign to each event $P$ the entire range of possibilities
-$\bar{\mu}_{1}(P)$ as defined in Table~\ref{tab:probability-measures}.
-This measure is not a valid QIVPM because it does not satisfy
-the convexity condition: for any two orthogonal one-dimensional events
-$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$,
-but $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
-which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$.
-Interestingly, it is impossible to find any probability measure that
-would be consistent with these observations, as the interval $\left[\tfrac{3}{4},1\right]$
-is completely disjoint from the interval $\left[0,\tfrac{1}{2}\right]$
-and no amount of shifting of assumptions regarding the precise outcome
-of the uncertain observations could change that disjointness. However,
-as shown next, a sharp transition occurs when $\delta=\tfrac{1}{3}$.
-
-When the proportion of uncertain data reaches $\frac{1}{3}$, the probability measure
-that assigns to each event the entire range of possibilities is
-$\bar{\mu}_{2}$ defined in Table~\ref{tab:probability-measures}.
-This is also not a valid probability measure by the same
-argument as above. However, in this case $\bar{\mu}_{2}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
-and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{2}\left(P_{0}\right)+\bar{\mu}_{2}\left(P_{1}\right)$
-have a \emph{common point}. Hence, by assuming that the uncertain data for
-one-dimensional projectors always support the associated event, while
-those for two-dimensional projectors always refute the event, we can
-find the probability measure~$\bar{\mu}_{2}'$ that can verified to be a
-valid QIVPM and is consistent with the experimental data.
-
-A similar situation happens when more than $\frac{1}{3}$ of data
-is uncertain. In particular, if half of the data is uncertain, the probability
-measure~$\bar{\mu}_{3}$ that assigns to each event the entire range of possibilities
-is already a QIVPM.
 

### 2018-03-24 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Updated by Gerardo...

@@
 Meyer's negative result is ``unsupportable'' on physical
-grounds~\cite{Mermin1999}.
-
-The question of how to address this controversy, and the effect of 
+grounds~\cite{Mermin1999}.  The question of how to address this controversy, and the effect of 
 finite precision on measurements in general, is therefore 
@@
 resources available for the realistic accuracy of an actual
-measurement?   In this paper, we extend our previous work on the
+measurement?
+
+In this paper, we extend our previous work on the
 foundations of computability in quantum physics by exploring the
@@
 
-To start our investigation, we note that Meyer attributes
+To put our investigation in perspective, we note that Meyer attributes
 finite-precision errors \emph{exclusively} to the description of the
 states defined in a general Hilbert space. Mermin's response argues
-against Meyer's interpretation but accepts his framework. Others,
+against Meyer's interpretation but, indeed,  accepts his framework. Others,
 however, have argued that the effect of finite-precision measurements
@@
 
-Our approach introduces the concept of $\delta$-determinism,
+Our approach, based on QIPVMs, introduces the concept of $\delta$-determinism,
 where~$\delta$ quantifies the effect of finite-precision uncertainties
@@
 
+\subsection{Experimental Data and \texorpdfstring{$\delta$}{delta}-determinism}
+
+\begin{table*}
+\caption{\label{tab:probability-measures}Possible probability measures on
+a Hilbert space of dimension~$d=3$, where $\bar{\mu}_{2}'$ and
+$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
+and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
+by $P$.}
+\centering{}%
+\begin{tabular}{cccccc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{0}\left(P\right)$ & $\bar{\mu}_{1}\left(P\right)$ & $\bar{\mu}_{2}\left(P\right)$ & $\bar{\mu}_{2}'\left(P\right)$ & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+All one-dimensional projectors  & $\left[0,0\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left[0,\tfrac{1}{3}\right]$ & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$ & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
+\midrule 
+\addlinespace
+All two-dimensional projectors  & $\left[1,1\right]$ & $\left[\tfrac{3}{4},1\right]$ & $\left[\tfrac{2}{3},1\right]$ & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$ & $\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
 We have thus quantified one important aspect of uncertainty in quantum
@@
 % requires every quantum framework to be truly probabilistic.
-
-\subsection{Experimental Data and \texorpdfstring{$\delta$}{delta}-determinism}
-
-\begin{table*}
-\caption{\label{tab:probability-measures}Possible probability measures on
-a Hilbert space of dimension~$d=3$, where $\bar{\mu}_{2}'$ and
-$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
-and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
-by $P$.}
-\centering{}%
-\begin{tabular}{cccccc}
-\toprule 
-\addlinespace
-$P$  & $\bar{\mu}_{0}\left(P\right)$ & $\bar{\mu}_{1}\left(P\right)$ & $\bar{\mu}_{2}\left(P\right)$ & $\bar{\mu}_{2}'\left(P\right)$ & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-All one-dimensional projectors  & $\left[0,0\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left[0,\tfrac{1}{3}\right]$ & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$ & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
-\midrule 
-\addlinespace
-All two-dimensional projectors  & $\left[1,1\right]$ & $\left[\tfrac{3}{4},1\right]$ & $\left[\tfrac{2}{3},1\right]$ & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$ & $\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
 

### 2018-03-25 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fix some typos...

@@
 \newcommand{\pmeas}{\ensuremath{\mu}}
-
-\NewDocumentCommand{\newInterval}{o o o o}{
- \newcommand{#1}{\text{\wesa{{#2}}}}
- % \newcommand{#1}{\ensuremath{\left[{#3}\right]}}
- % \newcommand{#1}{\ensuremath{I\left({#4}\right)}}
-}
-%% \newInterval[\imposs][impossible][0,0][0]
-%% \newInterval[\likely][likely][\tfrac{1}{2},1][\tfrac{1}{2},1]
-%% \newInterval[\unlikely][unlikely][0,\tfrac{1}{2}][0,\tfrac{1}{2}]
-%% \newInterval[\necess][certain][1,1][1]
-%% \newInterval[\unknown][unknown][0,1][0,1]
-\newInterval[\midd][middle][\tfrac{1}{4},\tfrac{3}{4}][\tfrac{1}{4},\tfrac{3}{4}]
 
@@
 topic of
-research~\cite{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+research~\cite{Kent1999,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 
@@
 
-\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason-1}Let
+\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
 $f:\left[0,1\right]\rightarrow\mathscr{I}$ be a blurring function

### 2018-03-25 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fixed a typo...

@@
 invalidate the spirit of the Kochen-Specker theorem. This claim was
-countered in the same year by Havlicek et al. ~\cite{HKSS1999apsrev4}
+countered in the same year by Havlicek et al.~\cite{HKSS1999apsrev4}
 and Mermin~\cite{Mermin1999} and the debate continues to be an active

### 2018-03-25 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fix a typo...

@@
 
-Our approach, based on QIPVMs, introduces the concept of $\delta$-determinism,
+Our approach, based on QIVPMs, introduces the concept of $\delta$-determinism,
 where~$\delta$ quantifies the effect of finite-precision uncertainties

### 2018-03-26 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fix typos...

@@
 
-\newcommand{\imposs}{\textbf{\textsf{F}}}
-\newcommand{\necess}{\textbf{\textsf{T}}}
-\newcommand{\unknown}{\textbf{\textsf{U}}}
+\newcommand{\interval}[1]{{\normalfont\textsf{\textbf{#1}}}}
+\newcommand{\imposs}{\interval{F}}
+\newcommand{\necess}{\interval{T}}
+\newcommand{\unknown}{\interval{U}}
 
@@
 measurement, which is its statistical nature as reflected in the
-application of the Born rule determining the probability of a given
-measurement outcome~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}.
-Here, Gleason's theorem establishes that there is no alternative to
+application of the Born rule \cite{Born1983bibTeX,Mermin2007,Jaeger2007} determining the probability of a given
+measurement outcome.
+Here, Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum} establishes that there is no alternative to
 the Born rule by demonstrating, using reasonable continuity arguments
@@
 state $\rho$ consistent with the statistical predictions computed from
-the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+the Born rule.
 Our question then concerns what happens when infinite precision cannot

### 2018-03-26 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex After meet with Andy, but not completely updated what we discussed...

@@
 \NewDocumentEnvironment{compare}{}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
-\NewDocumentEnvironment{oldText}{m}{#1{The following is old text.}\noindent\begin{minipage}[t]{1\columnwidth}}{#1{The old text end here.}\end{minipage}\newpage}
-\NewDocumentEnvironment{newText}{m}{\noindent\begin{minipage}[t]{1\columnwidth}#1{The following is new text.}}{\end{minipage}#1{The new text end here.}}
+\NewDocumentEnvironment{oldText}{m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is old text.}}{#1{The old text end here.}\end{minipage}\newpage}
+\NewDocumentEnvironment{newText}{m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is new text.}}{#1{The new text end here.}\end{minipage}}
 
@@
 or right of the center.  We simply record this imprecision by
-generalizing the probabilities assigned to events to intervals of
+generalizing the probabilities assigned to events to intervals reflecting the
 uncertainties.
@@
 
-We will start by reviewing IVPMs in the classical setting and then
+We will start by reviewing classical IVPMs and then
 propose our quantum generalization. In the classical setting, there
@@
 interval can be interpreted as a conventional probability. We also
-include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
-refer to the probability interval for impossible events and events
-that are certain. We can write this, respectively, as
+include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals that
+refer, respectively, to the probability interval for impossible events and
+for events that are certain. We can write the latter as
 $\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$
@@
 are disjoint; the naïve addition of intervals would give
-$\mu\left(E\cup\overline{E}\right)=[0.9,1.1]$ which is not a valid probability
+$\mu\left(E\cup\overline{E}\right)=[0.9,1.1]$, which is not a valid probability
 interval. Moreover the event $E\cup\overline{E}$ is the
@@
 the probability assignment for
-$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is therefore:
+$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is taken to be:
 \begin{equation}
@@
   [xr,x\ell] & \textrm{for }x\le0\,.
-  \end{cases}
+  \end{cases}\label{eq:interval-times}
   \end{eqnarray}
@@
 \end{definition}
+
+\begin{compare}
+\begin{oldText}{\andy}
 \noindent The first three constraints,
@@
 aspects of both classical IVPMs and quantum probability measures. 
-
+\end{oldText}
+\begin{newText}{\andy}
+\noindent The first three constraints,
+Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
+corresponding ones for classical IVPMs.  {\color{blue}Note that the possibility of negative
+intervals appearing in Eq.~(\ref{eq:interval-times})
+is a natural consequence of the minus sign appearing in
+Eq.~(\ref{eq:complement}).}  With the understanding that
+the union of classical sets $E_1\cup E_2$ is replaced by
+$P_0+P_1-P_0P_1$ in the case of quantum projection
+operators~\cite{Griffiths2003}, the last condition,
+Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
+direct counterpart of the convexity condition of
+Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
+aspects of both classical IVPMs and quantum probability measures.
+\end{newText}
+\end{compare}
+
+\begin{compare}
+\begin{oldText}{\andy}
 Our definition of QIVPMs is consistent with classical IVPMs in the
@@
 forthcoming thesis by the first author~\cite{TaiThesis2018}. A
-consequence of this fact is that known properties of classical IVPMs
+consequence {\color{blue}of this fact} is that known properties of classical IVPMs
 directly hold for QIVPMs when one restricts to mutually commuting
@@
 $\muB_{\rho}\left(P\right)$ to QIVPMs
-$\bar{\mu}\left(P\right)$. However, if the set of events is mutually
+$\bar{\mu}\left(P\right)$. However, if {\color{blue}the set of events is} mutually
 commuting, the situation reverts to the classical case in which
 probabilities always determine at least one state.
+\end{oldText}
+\begin{newText}{\andy}
+Our definition of QIVPMs is consistent with classical IVPMs in the
+sense that a restriction of QIVPMs to mutually commuting events,
+$\eventsC$, recovers the definition of classical
+IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
+forthcoming thesis by the first author~\cite{TaiThesis2018}. A
+consequence is that known properties of classical IVPMs
+directly hold for QIVPMs when one restricts to mutually commuting
+events, $\eventsC$. In particular, in the classical world, it is
+\emph{impossible} for experiments to result in probabilities that are
+inconsistent with \emph{some} state of the system under consideration,
+i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
+  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
+  proves that a classical IVPM always contains at least one state that
+  is consistent with every event.}. Interestingly, as we show in
+Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
+probabilities associated with some events to be inconsistent with
+\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
+in that case, one cannot guarantee non-empty cores for finite-precision
+attempts at proving Gleason's theorem by extending the Born measure
+$\muB_{\rho}\left(P\right)$ to QIVPMs
+$\bar{\mu}\left(P\right)$. However, if {\color{blue}we restrict ourselves to the set
+$\eventsC$ of} mutually
+commuting, the situation reverts to the classical case in which
+probabilities always determine at least one state.
+\end{newText}
+\end{compare}
 
 We now give the necessary technical definitions to prove this
-non-empty core property. We say a QIVPM $\bar{\mu}$ is
-\emph{consistent} with a state $\rho$ and a projector~$P$ if the
+non-empty core property.
+\begin{definition}[Consistency] We say a QIVPM $\bar{\mu}$
+is \emph{consistent} with a state $\rho$ and a projector~$P$ if the
 interval $\bar{\mu}(P)$ contains the exact probability calculated by
@@
   \muB_{\rho}\left(P\right) = \Tr\left(\rho
-  P\right)\in\bar{\mu}\left(P\right)\ .
+  P\right)\in\bar{\mu}\left(P\right)\ .\label{eq:consistent}
   \end{equation}
 In contrast with classical probability spaces, there is \emph{no
-guarantee} that there exists a unique state $\rho$ consistent with a QIVPM.
+guarantee} that there exists a unique state $\rho$ that satisfies
+Eq.~(\ref{eq:consistent}) and therefor is consistent with a QIVPM.
+\end{definition}
 
@@
 $\events'$ as a \emph{subspace} of a set of events if $\events$ if
-$\events'$ contains  $\mathbb{0}$ and $\mathbb{1}$ and is closed under
-complements, sums, and products.  In particular, for any
+$\events'$ contains the projector $\mathbb{0}$ and $\mathbb{1}$ and is closed
+under complements, sums, and products.  In particular, for any
 projector~$P\in\events'$, we have
@@
 two-dimensional projectors $P_{\rho}+P_{\sigma}$, and an experiment
-that repeated $12$ times. By the Kochen-Specker theorem, it is impossible
+that is repeated $12$ times. By the Kochen-Specker theorem, it is impossible
 to build a probability measure that maps every projection to either

### 2018-03-27 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Updated what Andy and I discussed...

@@
 
+% https://tex.stackexchange.com/questions/303018/minipage-reset-indent-how-can-i-set-again-to-standard
+\edef\docIndent{\the\parindent}
+\edef\docParskip{\the\parskip}
+\NewDocumentEnvironment{docParinfo}{}{%
+ \edef\currentIndent{\the\parindent}
+ \edef\currentParskip{\the\parskip}
+ \setlength{\parindent}{\docIndent}%
+ \setlength{\parskip}{\docParskip}
+}{
+ \setlength{\parindent}{\currentIndent}%
+ \setlength{\parskip}{\currentParskip}
+}
 \newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
@@
 \NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
-\NewDocumentEnvironment{compare}{}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
-\NewDocumentEnvironment{oldText}{m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is old text.}}{#1{The old text end here.}\end{minipage}\newpage}
-\NewDocumentEnvironment{newText}{m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is new text.}}{#1{The new text end here.}\end{minipage}}
+\newenvironment{compare}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
+\newenvironment{compareNextpage}{\clearpage}{\begin{widetext}\end{widetext}}
+\NewDocumentEnvironment{compareText}{m m}{\begin{minipage}[b]{1\columnwidth}#1{The following is #2 text.}\begin{docParinfo}}{\end{docParinfo}#1{The #2 text end here.}\end{minipage}}
+\newenvironment{oldText}[1]{\begin{compareText}{#1}{old}}{\end{compareText}\newpage}
+\newenvironment{newText}[1]{\begin{compareText}{#1}{new}}{\end{compareText}}
 
@@
 probabilities always determine at least one state.
+
+We now give the necessary technical definitions to prove this
+non-empty core property. {\color{blue}We say a QIVPM $\bar{\mu}$ is
+\emph{consistent} with a state $\rho$ and a projector~$P$ if the
+interval $\bar{\mu}(P)$ contains the exact probability calculated by
+the Born rule~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
+  \begin{equation}
+  \muB_{\rho}\left(P\right) = \Tr\left(\rho
+  P\right)\in\bar{\mu}\left(P\right)\ .
+  \end{equation}
+In contrast with classical probability spaces, there is \emph{no
+guarantee} that there exists a unique state $\rho$ consistent with a QIVPM.}
+
+We next refine the concept of consistency by introducing the idea of
+a ``core'' set of states relative to subspaces. First, we define
+$\events'$ as a \emph{subspace} of a set of events if $\events$ if
+$\events'$ contains  $\mathbb{0}$ and $\mathbb{1}$ and is closed under
+complements, sums, and products.  In particular, for any
+projector~$P\in\events'$, we have
+$\mathbb{1}-P\in\events'$ and for each pair of commuting
+projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
+$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$.
 \end{oldText}
@@
 probabilities always determine at least one state.
-\end{newText}
-\end{compare}
 
@@
 non-empty core property.
-\begin{definition}[Consistency] We say a QIVPM $\bar{\mu}$
-is \emph{consistent} with a state $\rho$ and a projector~$P$ if the
+{\color{blue}\begin{definition}[Consistency] We say a QIVPM $\bar{\mu}$ is
+\emph{consistent} with a state $\rho$ and a projector~$P$ if the
 interval $\bar{\mu}(P)$ contains the exact probability calculated by
@@
 Eq.~(\ref{eq:consistent}) and therefor is consistent with a QIVPM.
-\end{definition}
+\end{definition}}
 
@@
 $\events'$ as a \emph{subspace} of a set of events if $\events$ if
-$\events'$ contains the projector $\mathbb{0}$ and $\mathbb{1}$ and is closed
-under complements, sums, and products.  In particular, for any
+$\events'$ contains {\color{blue}the projector} $\mathbb{0}$ and $\mathbb{1}$ and is closed under
+complements, sums, and products.  In particular, for any
 projector~$P\in\events'$, we have
@@
 $P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$.
+\end{newText}
+\end{compare}
 
@@
 
+\begin{compareNextpage}
+\begin{oldText}{\andy}
 Now let us consider relaxing $\mathscr{I}$
@@
 As the intervals in the image of a QIVPM become less and less sharp,
-we expect more and more states to be consistent with it. Indeed, in
+we expect more and more states to be consistent with it. {\color{blue}Indeed, in
 the limit, the intervals become \imposs, \necess, and $\unknown=\left[0,1\right]$,  and
 every state is consistent with an assignment that states that its
-projections are unknown. There is however a subtlety: as shown in the
+projections are unknown.} There is however a subtlety: as shown in the
 theorem below, it is possible for an arbitrary assignment of intervals to projectors
 to be globally inconsistent.
+\end{oldText}
+\begin{newText}{\andy}
+Now let us consider relaxing $\mathscr{I}$
+to a countable set of finite-width intervals.
+As the intervals in the image of a QIVPM become less and less sharp,
+we expect more and more states to be consistent with it. {\color{blue}In
+the limit of minimal sharpness, all states~$\rho$
+are consistent with the following QIVPM
+\begin{equation}
+\bar{\mu}\left(P\right)=\begin{cases}
+\imposs\,, & \textrm{ if }P=\mathbb{0}\:;\\
+\necess\,, & \textrm{ if }P=\mathbb{1}\:;\\
+\unknown=\left[0,1\right]\,, & \textrm{ otherwise.}
+\end{cases}
+\end{equation}
+mapping nearly all
+projections to the unknown interval.} There is however a subtlety: as shown in the
+theorem below, it is possible for an arbitrary assignment of intervals to projectors
+to be globally inconsistent.
+\end{newText}
+\end{compareNextpage}
 

### 2018-03-27 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex After meeting with Gerardo, but not completely updated what we discussed...

--- 2018-03-26 revised_prop_letter_ajhs.tex
@@
 
+% https://tex.stackexchange.com/questions/303018/minipage-reset-indent-how-can-i-set-again-to-standard
+\edef\docIndent{\the\parindent}
+\edef\docParskip{\the\parskip}
+\newenvironment{docParinfo}{%
+ \edef\currentIndent{\the\parindent}
+ \edef\currentParskip{\the\parskip}
+ \setlength{\parindent}{\docIndent}%
+ \setlength{\parskip}{\docParskip}
+}{
+ \setlength{\parindent}{\currentIndent}%
+ \setlength{\parskip}{\currentParskip}
+}
 \newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
@@
 
-\begin{compare}
-\begin{oldText}{\andy}
-Our definition of QIVPMs is consistent with classical IVPMs in the
-sense that a restriction of QIVPMs to mutually commuting events,
-$\eventsC$, recovers the definition of classical
-IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
-forthcoming thesis by the first author~\cite{TaiThesis2018}. A
-consequence {\color{blue}of this fact} is that known properties of classical IVPMs
-directly hold for QIVPMs when one restricts to mutually commuting
-events, $\eventsC$. In particular, in the classical world, it is
-\emph{impossible} for experiments to result in probabilities that are
-inconsistent with \emph{some} state of the system under consideration,
-i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
-  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
-  proves that a classical IVPM always contains at least one state that
-  is consistent with every event.}. Interestingly, as we show in
-Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
-probabilities associated with some events to be inconsistent with
-\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
-in that case, one cannot guarantee non-empty cores for finite-precision
-attempts at proving Gleason's theorem by extending the Born measure
-$\muB_{\rho}\left(P\right)$ to QIVPMs
-$\bar{\mu}\left(P\right)$. However, if {\color{blue}the set of events is} mutually
-commuting, the situation reverts to the classical case in which
-probabilities always determine at least one state.
-\end{oldText}
-\begin{newText}{\andy}
 Our definition of QIVPMs is consistent with classical IVPMs in the
@@
 $\muB_{\rho}\left(P\right)$ to QIVPMs
-$\bar{\mu}\left(P\right)$. However, if {\color{blue}we restrict ourselves to the set
-$\eventsC$ of} mutually
+$\bar{\mu}\left(P\right)$. However, if we restrict ourselves to the set
+$\eventsC$ of mutually
 commuting, the situation reverts to the classical case in which
 probabilities always determine at least one state.
-\end{newText}
-\end{compare}
 
@@
 non-empty core property.
-\begin{definition}[Consistency] We say a QIVPM $\bar{\mu}$
-is \emph{consistent} with a state $\rho$ and a projector~$P$ if the
+\begin{compare}
+\begin{oldText}{\gerardo}
+\begin{definition}[Consistency] We say a QIVPM $\bar{\mu}$ is
+\emph{consistent} with a state $\rho$ and a projector~$P$ if the
 interval $\bar{\mu}(P)$ contains the exact probability calculated by
@@
 \end{definition}
+\end{oldText}
+\begin{newText}{\gerardo}
+\begin{definition}[Consistency] We say a QIVPM $\bar{\mu}$ is
+\emph{consistent} with a state $\rho$ and a projector~$P$ if the
+interval $\bar{\mu}(P)$ contains the exact probability calculated by
+the Born rule~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
+  \begin{equation}
+  \muB_{\rho}\left(P\right) = \Tr\left(\rho
+  P\right)\in\bar{\mu}\left(P\right)\ .\label{eq:consistent}
+  \end{equation}
+In contrast with classical probability spaces, there is \emph{no
+guarantee} that there exists a unique state $\rho$ that satisfies
+Eq.~(\ref{eq:consistent}) and therefor{\color{OliveGreen}e} is consistent with a QIVPM.
+\end{definition}
+\end{newText}
+\end{compare}
 
@@
 $\events'$ as a \emph{subspace} of a set of events if $\events$ if
-$\events'$ contains the projector $\mathbb{0}$ and $\mathbb{1}$ and is closed
-under complements, sums, and products.  In particular, for any
+$\events'$ contains the projector $\mathbb{0}$ and $\mathbb{1}$ and is closed under
+complements, sums, and products.  In particular, for any
 projector~$P\in\events'$, we have
@@
 As the intervals in the image of a QIVPM become less and less sharp,
-we expect more and more states to be consistent with it. Indeed, in
-the limit, the intervals become \imposs, \necess, and $\unknown=\left[0,1\right]$,  and
-every state is consistent with an assignment that states that its
-projections are unknown. There is however a subtlety: as shown in the
+we expect more and more states to be consistent with it. In
+the limit of minimal sharpness, all states~$\rho$
+are consistent with the following QIVPM
+\begin{equation}
+\bar{\mu}\left(P\right)=\begin{cases}
+\imposs\,, & \textrm{ if }P=\mathbb{0}\:;\\
+\necess\,, & \textrm{ if }P=\mathbb{1}\:;\\
+\unknown=\left[0,1\right]\,, & \textrm{ otherwise.}
+\end{cases}
+\end{equation}
+mapping nearly all
+projections to the unknown interval. There is however a subtlety: as shown in the
 theorem below, it is possible for an arbitrary assignment of intervals to projectors

### 2018-03-27 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Updated what Gerardo and I discussed...

@@
 \newenvironment{compareNextpage}{\clearpage}{\begin{widetext}\end{widetext}}
-\NewDocumentEnvironment{compareText}{m m}{\begin{minipage}[b]{1\columnwidth}#1{The following is #2 text.}\begin{docParinfo}}{\end{docParinfo}#1{The #2 text end here.}\end{minipage}}
+\NewDocumentEnvironment{compareText}{m m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is #2 text.}\begin{docParinfo}}{\end{docParinfo}#1{The #2 text end here.}\end{minipage}}
 \newenvironment{oldText}[1]{\begin{compareText}{#1}{old}}{\end{compareText}\newpage}
@@
 Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
-corresponding ones for classical IVPMs.  With the understanding that
+corresponding ones for classical IVPMs.  {\color{blue}Note that the possibility of negative
+intervals appearing in Eq.~(\ref{eq:interval-times})
+is a natural consequence of the minus sign appearing in
+Eq.~(\ref{eq:complement}).}  With the understanding that
 the union of classical sets $E_1\cup E_2$ is replaced by
@@
 \end{oldText}
-\begin{newText}{\andy}
+\begin{newText}{\yutsung}
 \noindent The first three constraints,
 Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
-corresponding ones for classical IVPMs.  {\color{blue}Note that the possibility of negative
-intervals appearing in Eq.~(\ref{eq:interval-times})
-is a natural consequence of the minus sign appearing in
+corresponding ones for classical IVPMs.  {\color{purple}Note that we need to
+consider $x\le0$ case in Eq.~(\ref{eq:interval-times}) because of the minus sign
+appearing in
 Eq.~(\ref{eq:complement}).}  With the understanding that
@@
 
-To that end, we construct a family of QIVPMs parameterized by \emph{blurring}
-functions. A blurring function $f:\left[0,1\right]\rightarrow\mathscr{I}$
+\begin{compare}
+\begin{oldText}{\andy}
+To that end, we construct a family of QIVPMs parameterized by {\color{blue}\emph{blurring}
+functions. A blurring function} $f:\left[0,1\right]\rightarrow\mathscr{I}$
 maps every real-valued probability $x\in\left[0,1\right]$ to a set
@@
 finite-precision extension of Gleason's theorem can be stated as follows.
-
+\end{oldText}
+\begin{newText}{\andy}
+To that end, we construct a family of QIVPMs parameterized by {\color{blue}\emph{interval}
+maps. A interval map} $f:\left[0,1\right]\rightarrow\mathscr{I}$
+maps every real-valued probability $x\in\left[0,1\right]$ to a set
+of intervals $f\left(x\right)=\left[\ell,r\right]$ containing $x$,
+where $\left[0,1\right]$ denotes the set of real-valued probabilities
+which should not be considered as the interval-valued probability
+$\unknown$. We also need a notion of norm to quantify the
+distance between (pure or mixed) states. The norm of a pure state
+$\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
+In addition, given any Hermitian operator~$A$, we consider the usual
+operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
+which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+In fact, for any such matrix, including the density matrix~$\rho$,
+the norm is the maximum absolute value of its eigenvalue. Then, a
+finite-precision extension of Gleason's theorem can be stated as follows.
+\end{newText}
+\end{compare}
+
+\begin{compareNextpage}
+\begin{oldText}{\andy}
 \begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
-$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a blurring function
+$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a {\color{blue}blurring function}
 and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
@@
 then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
+\end{oldText}
+\begin{newText}{\andy}
+\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
+$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a {\color{blue}interval map}
+and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
+probability measure induced by the Born rule for a given state~$\rho$.
+Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
+If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
+events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
+then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
+\end{newText}
+\end{compareNextpage}
 
@@
 
-%% ajh: no abbreviations as first words of sentences.
+\begin{compare}
+\begin{oldText}{\andy}
 Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
@@
 the sense that it only applies to the particular class of QIVPMs
-constructed by composing a blurring function with a conventional
+constructed by composing a {\color{blue}blurring function} with a conventional
 quantum probability measure. QIVPMs constructed in this manner have
@@
 
-A blurring function is called \emph{ultramodular} if it satisfies
+A {\color{blue}blurring function} is called \emph{ultramodular} if it satisfies
 the following properties.
@@
   a collection of intervals $\mathscr{I}$ including $\imposs$ and
-  $\necess$, a blurring function
+  $\necess$, a {\color{blue}blurring function}
   $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
@@
 defines a valid QIVPM. Conversely, if for every quantum probability
-measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the blurring
-function~$f$ is an ultramodular function. Formally, we have the following
+measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the {\color{blue}blurring
+function}~$f$ is an ultramodular function. Formally, we have the following
 result.
+\end{oldText}
+\begin{newText}{\andy}
+Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
+theorem in the sense that it accounts for a larger class of probability measures that includes
+the conventional one as a limit. The theorem is however ``special'' in
+the sense that it only applies to the particular class of QIVPMs
+constructed by composing a {\color{blue}interval map} with a conventional
+quantum probability measure. QIVPMs constructed in this manner have
+some peculiar properties that we examine next.
+
+A {\color{blue}interval map} is called \emph{ultramodular} if it satisfies
+the following properties.
+
+\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
+  a collection of intervals $\mathscr{I}$ including $\imposs$ and
+  $\necess$, a {\color{blue}interval map}
+  $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
+  ultramodular if:
+\begin{subequations}\label{eq:iota-constraints}
+\begin{eqnarray}
+ &  & \ultramodular(0)=\imposs\,,\\
+ &  & \ultramodular(1)=\necess\,,\\
+ &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
+\end{eqnarray}
+\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$, and
+$x_{2}\in\left[0,1\right]$ such that
+$y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have:
+\begin{equation}
+\ultramodular\left(y\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
+\end{equation}
+\end{definition}
+
+\noindent The first three constraints,
+Eqs.~(\ref{eq:iota-constraints}), are the direct counterpart of the
+corresponding QIVPM constraints, Eqs.~(\ref{eq:QIVPM-constraints});
+the last condition, Eq.~(\ref{eq:iota-Inclusion}), is the direct
+counterpart of the convexity conditions,
+Eq.~(\ref{eq:classicalconvex}) and
+(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+\cite{Choquet1954,Shapley1971,NgMoYeh1997,MarinacciMontrucchio2005}. Therefore,
+these conditions guarantee that, for any conventional quantum
+probability measure $\mu$, the composition $\ultramodular \circ \mu$
+defines a valid QIVPM. Conversely, if for every quantum probability
+measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the {\color{blue}interval
+map}~$f$ is an ultramodular function. Formally, we have the following
+result.
+\end{newText}
+\end{compare}
 
@@
 a classical IVPM for the same reason as in the quantum case.
-%% ajh: sentence "This can be done..." is somehow garbled, tried to
-%% fix.  $\eventsC$ is by DEFINITION a commuting subspace, so the
-%% original sentence does not seem to have any meaning.  Are there
-%% MORE mutually commuting projectors in $\eventsC$?  It would seem
-%% that there are no others, so this is all confusing, as that would
-%% make this sentence completely vacuous.
-
-% In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
-% there is always a state consistent with any composite QIVPM
-% $\ultramodular\circ\muB_{\rho}$.  Moreover, the collection
-% of states consistent with $\ultramodular\circ\muB_{\rho}$
-% gets closer and closer to~$\rho$ as the intervals get narrower and
-% narrower. Eventually, the collection of states collapses to the
-% singleton set~$\left\{ \rho\right\} $ as the intervals become the
-% infinitely precise intervals~$\mathscr{I}_{\infty}$. To precisely
-% state this result, we introduce the norm of pure states and
-% operators. The norm of a pure state~$\ket{\psi}$ is defined as usual
-% $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
-% given any Hermitian operator~$A$, we consider the usual operator norm
-% $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert
-%   =1}\left\Vert A\ket{\psi}\right\Vert $, which is also known as the
-% $2$-norm or the spectral
-% norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
-% Then, a version of Gleason's theorem can be stated as follow.
-
+
+\begin{compare}
+\begin{oldText}{\andy}
 In other words, essential properties of QIVPMs constructed using
-blurring functions can be gleaned from the properties of
+{\color{blue}blurring function}s can be gleaned from the properties of
 ultramodular functions. The following is a most interesting property
 in our setting. 
+\end{oldText}
+\begin{newText}{\andy}
+In other words, essential properties of QIVPMs constructed using
+{\color{blue}interval map}s can be gleaned from the properties of
+ultramodular functions. The following is a most interesting property
+in our setting. 
+\end{newText}
+\end{compare}
 
@@
 
+\begin{compare}
+\begin{oldText}{\andy}
 To summarize, a conventional quantum probability measure has an
-uncountable range $[0,1]$. A QIVPM constructed by blurring such a
+uncountable range $[0,1]$. A QIVPM constructed by {\color{blue}blurring} such a
 conventional quantum probability measure must also have an uncountable
@@
 the resources and precision of the particular experiment. 
-%\gerardo{We need to explain physically what it means?}
-% The essential reason for getting an uncountable number of intervals is
-% the convexity condition we imposed on QIVPMs. This condition is widely
-% used in the classical setting but it is possible that it should be
-% modified or weakened in the quantum case. If we take this approach and 
-% % Even if $\ultramodular$ has to be ultramodular to guarantee
-% % $\ultramodular\circ\mu$ a QIVPM, the composited function
-% % $\ultramodular\circ\mu$ may still be a QIVPM when $\ultramodular$ is
-% % not ultramodular. In this case, the composited function
-% % $\ultramodular\circ\mu$ could map to non-trivial finite number of
-% % intervals. For example, we can 
-% weaken the convexity condition, Eq.~(\ref{eq:iota-Inclusion}), we can
-% recover QIVPMs that only require countable and even finite collections
-% of intervals. Formally, we weaken the convexity condition to the
-% following additive condition: for any numbers $x_{0}$ and
-% $x_{1}\in\left[0,1\right]$, their sum $x_{0}+x_{1}\in\left[0,1\right]$
-% implies
-% \begin{equation}
-% \ultramodular\left(x_{0}+x_{1}\right)\subseteq\ultramodular\left(x_{0}\right)+\ultramodular\left(x_{1}\right)\,.\label{eq:iota-add}
-% \end{equation}
-% Then, given a three-dimensional Hilbert space, if $\ultramodular$
-% satisfies Eqs.~(\ref{eq:iota-constraints}) and
-% Eq.~(\ref{eq:iota-add}), then $\ultramodular\circ\mu$ is a
-% QIVPM~\cite{TaiThesis2018}.  For example, consider an orthonormal
-% basis $\{\ket{0},\ket{1},\ket{2}\}$, two states
-% $\rho_{0}=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
-% and
-% $\rho_{1}=\frac{7}{24}\proj{0}+\frac{1}{3}\proj{1}+\frac{3}{8}\proj{2}$,
-% and a set of intervals:
-% \begin{equation}
-% \begin{aligned}\mathscr{I}_{2}={} & \left\{ \imposs,\left[0,\tfrac{1}{4}\right],\left[0,{\textstyle \tfrac{1}{2}}\right],\left[\tfrac{1}{4},\tfrac{3}{4}\right],\right.\\
-%  & \left.\left[\tfrac{1}{2},1\right],\left[\tfrac{3}{4},1\right],\necess\right\} \,.
-% \end{aligned}
-% \end{equation}
-% Since the interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$
-% defined in Table~\ref{tab:I_2} satisfies Eqs.~(\ref{eq:iota-constraints})
-% and Eq.~(\ref{eq:iota-add})~\cite{TaiThesis2018}, $\ultramodular_{2}\circ\muB_{\rho_{0}}$
-% and $\ultramodular_{2}\circ\muB_{\rho_{1}}$ are both
-% QIVPMs.
-% \begin{table}
-% \caption{\label{tab:I_2}A interval-valued function~$\ultramodular_{2}:\left[0,1\right]\rightarrow\mathscr{I}_{2}$.}
-
-% \hfill{}%
-% \begin{minipage}[t]{2.5cm}%
-% \begin{center}
-% \begin{tabular}{cc}
-% \toprule 
-% \addlinespace
-% $x$ & $\ultramodular_{2}\left(x\right)$\tabularnewline\addlinespace
-% \midrule
-% \midrule 
-% \addlinespace
-% $x=0$ & $\imposs$\tabularnewline\addlinespace
-% \midrule 
-% \addlinespace
-% $0<x\le\tfrac{1}{8}$ & $\left[0,\tfrac{1}{4}\right]$\tabularnewline\addlinespace
-% \midrule 
-% \addlinespace
-% $\tfrac{1}{8}<x<\tfrac{3}{8}$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$\tabularnewline\addlinespace
-% \midrule 
-% \addlinespace
-% $\tfrac{3}{8}\le x\le\tfrac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
-% \bottomrule
-% \end{tabular}
-% \par\end{center}%
-% \end{minipage}\hfill{}%
-% \begin{minipage}[t]{2.5cm}%
-% \begin{center}
-% \begin{tabular}{cc}
-% \toprule 
-% \addlinespace
-% $x$ & $\ultramodular_{2}\left(x\right)$\tabularnewline\addlinespace
-% \midrule
-% \midrule 
-% \addlinespace
-% $\tfrac{5}{8}<x<\tfrac{7}{8}$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline\addlinespace
-% \midrule 
-% \addlinespace
-% $\tfrac{7}{8}\le x<1$ & $\left[\tfrac{3}{4},1\right]$\tabularnewline\addlinespace
-% \midrule 
-% \addlinespace
-% $x=1$ & $\necess$\tabularnewline\addlinespace
-% \bottomrule
-% \end{tabular}
-% \par\end{center}%
-% \end{minipage}\hfill{}
-% \end{table}
-% Given any one-dimensional projector $\proj{\psi}$, we have $\muB_{\rho_{0}}\left(\proj{\psi}\right)=\frac{1}{3}$
-% so that $\ultramodular_{2}\left(\muB_{\rho_{0}}\left(\proj{\psi}\right)\right)=\left[0,{\textstyle \tfrac{1}{2}}\right]$.
-% On the other hand, 
-% \begin{eqnarray*}
-% \muB_{\rho_{1}}\left(\proj{\psi}\right) & = & \tfrac{7}{24}\left|\ip{\psi}{0}\right|^{2}+\tfrac{1}{3}\left|\ip{\psi}{1}\right|^{2}+\tfrac{3}{8}\left|\ip{\psi}{2}\right|^{2}
-% \end{eqnarray*}
-% is bounded between $\frac{7}{24}$ and $\frac{3}{8}$. Therefore,
-% $\muB_{\rho_{1}}\left(\proj{\psi}\right)\in\ultramodular_{2}\left(\muB_{\rho_{0}}\left(\proj{\psi}\right)\right)$.
-% According to the complement condition, Eq.~(\ref{eq:complement}), we
-% also have
-% $\muB_{\rho_{1}}\left(P\right)\in\ultramodular_{2}\left(\muB_{\rho_{0}}\left(P\right)\right)$
-% for any two-dimensional projector~$P$. Hence,
-% $\rho_{1}\in\coreBorn\left(\ultramodular_{2}\circ\muB_{\rho_{0}},\events\right)$,
-% and Thm.~\ref{thm:Finite-precision-Gleason} asserts that
-% $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is less than or equal to the
-% maximum length of intervals $\frac{1}{2}$.  This is true because the
-% exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
-% $\frac{1}{24}$.
+\end{oldText}
+\begin{newText}{\andy}
+To summarize, a conventional quantum probability measure has an
+uncountable range $[0,1]$. A QIVPM constructed by {\color{blue}?????} such a
+conventional quantum probability measure must also have an uncountable
+range of intervals. Of course, any particular QIVPM, or any particular
+experiment, will use a fixed collection of intervals appropriate for
+the resources and precision of the particular experiment. 
+\end{newText}
+\end{compare}
 

### 2018-03-28 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex \newenvironment{oldText}[1]{\begin{compareText}{#1}{old}}{\end{compareText}\newpage}
revised_prop_letter_ajhs.tex The version before meeting with Andy...

@@
 \NewDocumentEnvironment{compareText}{m m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is #2 text.}\begin{docParinfo}}{\end{docParinfo}#1{The #2 text end here.}\end{minipage}}
-\newenvironment{oldText}[1]{\begin{compareText}{#1}{old}}{\end{compareText}\newpage}
+\newenvironment{oldText}[1]{\begin{compareText}{#1}{old}}{\end{compareText}\penalty-10000}
 \newenvironment{newText}[1]{\begin{compareText}{#1}{new}}{\end{compareText}}
@@
 corresponding ones for classical IVPMs.  {\color{purple}Note that we need to
-consider $x\le0$ case in Eq.~(\ref{eq:interval-times}) because of the minus sign
-appearing in
+consider $x\le0$ case in Eq.~(\ref{eq:interval-times}) because the minus sign
+appears in
 Eq.~(\ref{eq:complement}).}  With the understanding that
@@
 $\bar{\mu}\left(P\right)$. However, if we restrict ourselves to the set
-$\eventsC$ of mutually
-commuting, the situation reverts to the classical case in which
+$\eventsC$ of mutually commuting, \yutsung{Since ``mutually commuting'' is the
+object of the proposition ``of'', is ``mutually commuting'' a noun?}
+the situation reverts to the classical case in which
 probabilities always determine at least one state.
@@
 
+\begin{compare}
+\begin{oldText}{\yutsung}
 We next refine the concept of consistency by introducing the idea of
 a ``core'' set of states relative to subspaces. First, we define
-$\events'$ as a \emph{subspace} of a set of events if $\events$ if
+$\events'$ as a \emph{subspace} of a set of events {\color{purple}if} $\events$ if
 $\events'$ contains the projector $\mathbb{0}$ and $\mathbb{1}$ and is closed under
@@
 $P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$.
+\end{oldText}
+\begin{newText}{\yutsung}
+We next refine the concept of consistency by introducing the idea of
+a ``core'' set of states relative to subspaces. First, we define
+$\events'$ as a \emph{subspace} of a set of events~$\events$ if
+$\events'$ contains the projector $\mathbb{0}$ and $\mathbb{1}$ and is closed under
+complements, sums, and products.  In particular, for any
+projector~$P\in\events'$, we have
+$\mathbb{1}-P\in\events'$ and for each pair of commuting
+projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
+$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$.
+\end{newText}
+\end{compare}
 
@@
 finite-precision extension of Gleason's theorem can be stated as follows.
+
+\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
+$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a {\color{blue}blurring function}
+and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
+probability measure induced by the Born rule for a given state~$\rho$.
+Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
+If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
+events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
+then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
 \end{oldText}
@@
 finite-precision extension of Gleason's theorem can be stated as follows.
-\end{newText}
-\end{compare}
-
-\begin{compareNextpage}
-\begin{oldText}{\andy}
-\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
-$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a {\color{blue}blurring function}
-and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
-probability measure induced by the Born rule for a given state~$\rho$.
-Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
-If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
-events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
-then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
-\end{oldText}
-\begin{newText}{\andy}
+
 \begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
@@
 \end{newText}
-\end{compareNextpage}
+\end{compare}
 
@@
 
-\begin{compare}
-\begin{oldText}{\andy}
 To summarize, a conventional quantum probability measure has an
-uncountable range $[0,1]$. A QIVPM constructed by {\color{blue}blurring} such a
+uncountable range $[0,1]$. A QIVPM constructed by blurring \yutsung{Should we
+change this ``blurring''?} such a
 conventional quantum probability measure must also have an uncountable
@@
 the resources and precision of the particular experiment.
-\end{oldText}
-\begin{newText}{\andy}
-To summarize, a conventional quantum probability measure has an
-uncountable range $[0,1]$. A QIVPM constructed by {\color{blue}?????} such a
-conventional quantum probability measure must also have an uncountable
-range of intervals. Of course, any particular QIVPM, or any particular
-experiment, will use a fixed collection of intervals appropriate for
-the resources and precision of the particular experiment. 
-\end{newText}
-\end{compare}
 

### 2018-03-29 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex After meeting with Andy and Amr, but not completely updated what we discussed...

--- 2018-03-27 revised_prop_letter_ajhs.tex
@@
 
-\begin{compare}
-\begin{oldText}{\andy}
 \noindent The first three constraints,
 Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
-corresponding ones for classical IVPMs.  {\color{blue}Note that the possibility of negative
-intervals appearing in Eq.~(\ref{eq:interval-times})
-is a natural consequence of the minus sign appearing in
-Eq.~(\ref{eq:complement}).}  With the understanding that
+corresponding ones for classical IVPMs.  {\color{red}Note that the minus sign
+appears in Eq.~(\ref{eq:complement}) is accommodated by the $x\le0$ case in
+Eq.~(\ref{eq:interval-times}).}  With the understanding that
 the union of classical sets $E_1\cup E_2$ is replaced by
@@
 aspects of both classical IVPMs and quantum probability measures.
-\end{oldText}
-\begin{newText}{\yutsung}
-\noindent The first three constraints,
-Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
-corresponding ones for classical IVPMs.  {\color{purple}Note that we need to
-consider $x\le0$ case in Eq.~(\ref{eq:interval-times}) because of the minus sign
-appearing in
-Eq.~(\ref{eq:complement}).}  With the understanding that
-the union of classical sets $E_1\cup E_2$ is replaced by
-$P_0+P_1-P_0P_1$ in the case of quantum projection
-operators~\cite{Griffiths2003}, the last condition,
-Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
-direct counterpart of the convexity condition of
-Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
-aspects of both classical IVPMs and quantum probability measures.
-\end{newText}
-\end{compare}
 
@@
 $\bar{\mu}\left(P\right)$. However, if we restrict ourselves to the set
-$\eventsC$ of mutually
-commuting, the situation reverts to the classical case in which
+$\eventsC$ of mutually commuting {\color{red} events}, 
+the situation reverts to the classical case in which
 probabilities always determine at least one state.
@@
 non-empty core property.
-\begin{compare}
-\begin{oldText}{\gerardo}
-\begin{definition}[Consistency] We say a QIVPM $\bar{\mu}$ is
-\emph{consistent} with a state $\rho$ and a projector~$P$ if the
-interval $\bar{\mu}(P)$ contains the exact probability calculated by
-the Born rule~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
-  \begin{equation}
-  \muB_{\rho}\left(P\right) = \Tr\left(\rho
-  P\right)\in\bar{\mu}\left(P\right)\ .\label{eq:consistent}
-  \end{equation}
-In contrast with classical probability spaces, there is \emph{no
-guarantee} that there exists a unique state $\rho$ that satisfies
-Eq.~(\ref{eq:consistent}) and therefor is consistent with a QIVPM.
-\end{definition}
-\end{oldText}
-\begin{newText}{\gerardo}
-\begin{definition}[Consistency] We say a QIVPM $\bar{\mu}$ is
+\begin{definition}[Consistency]\label{def:Consistency} We say a QIVPM
+$\bar{\mu}$ is
 \emph{consistent} with a state $\rho$ and a projector~$P$ if the
@@
 \end{definition}
-\end{newText}
-\end{compare}
 
@@
 a ``core'' set of states relative to subspaces. First, we define
-$\events'$ as a \emph{subspace} of a set of events if $\events$ if
-$\events'$ contains the projector $\mathbb{0}$ and $\mathbb{1}$ and is closed under
+$\events'$ as a \emph{subspace} of a set of events~$\events$ if
+$\events'$ contains the projector{\color{red}s} $\mathbb{0}$ and $\mathbb{1}$ and is closed under
 complements, sums, and products.  In particular, for any
@@
 
-\begin{definition}[The core of a probability measure] The \emph{core}
+\begin{definition}[The core of a probability measure]\label{def:core} The
+\emph{core}
 $\coreBorn\left(\bar{\mu},\events'\right)$ of a probability measure 
@@
 
-The proof, detailed in the forthcoming thesis~\cite{TaiThesis2018}, proceeds as
+{\color{red}An outline of}The proof, detailed in the forthcoming
+thesis~\cite{TaiThesis2018}, proceeds as
 follows. From a subspace $\eventsC$ of mutually commuting events, one
@@
 state $\rho$ is also the unique state consistent with any possible
-probability measure. In order to re-examine these results in our
+probability measure.
+
+\subsection{\color{red}Finite-Precision Extension of Gleason's Theorem}
+
+In order to re-examine these results in our
 framework, we first reformulate Gleason's theorem in QIVPMs using
@@
 mapping nearly all
-projections to the unknown interval. There is however a subtlety: as shown in the
-theorem below, it is possible for an arbitrary assignment of intervals to projectors
+projections to the {\color{red}\emph{unknown}} interval. There is however a
+subtlety: as shown in
+the theorem below, it is possible for an arbitrary assignment of intervals to projectors
 to be globally inconsistent.
@@
 To prove this theorem, we need to construct a QIVPM on some Hilbert
-space, and verify that there are no states that are consistent with it
+space, and verify that there are no states that are consistent {\color{red}(see
+Defs.~\ref{def:Consistency} and \ref{def:core})} with it
 on all possible events. Assume a Hilbert space of dimension $d=3$ with
@@
 $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
-$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
+$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and {\color{red}assign}
 \begin{equation}
@@
 If this is true, then $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all~$j$. The last equation never holds, proving the theorem.
-%%ajh: garbled argument starting at 'Since we assumed', tried to fix.
+for all~$j$. {\color{red}Since any vector can be decomposed in terms of the
+linearly independent basis $\left\{\ket{0},\ket{\ps},\ket{\ps'}\right\}$, all
+$\ket{\phi_{j}}$ are perpendicular to any vector in the Hilbert space, and so
+are not valid non-empty states, violating the assumption
+$\ip{\phi_{j}}{\phi_{j}}=1$, and thus the theorem is proved.}
 
@@
 
-\begin{compare}
-\begin{oldText}{\andy}
-To that end, we construct a family of QIVPMs parameterized by {\color{blue}\emph{blurring}
-functions. A blurring function} $f:\left[0,1\right]\rightarrow\mathscr{I}$
+To that end, we {\color{red}introduce the conept of \emph{interval maps} which
+we can use to construct a consistent family of QIVPM.}
+A{\color{red}n} interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$
 maps every real-valued probability $x\in\left[0,1\right]$ to a set
@@
 where $\left[0,1\right]$ denotes the set of real-valued probabilities
-which should not be considered as the interval-valued probability
-$\unknown$. We also need a notion of norm to quantify the
+{\color{red}this is unrelated to the interval-valued probability
+$\unknown$.} We also need a notion of {\color{red}\emph{norm}} to quantify the
 distance between (pure or mixed) states. The norm of a pure state
 $\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
-In addition, given any Hermitian operator~$A$, we consider the usual
+{\color{red} For any given Hermitian operator~$A$, we choose}
 operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
@@
 In fact, for any such matrix, including the density matrix~$\rho$,
-the norm is the maximum absolute value of its eigenvalue. Then, a
-finite-precision extension of Gleason's theorem can be stated as follows.
-\end{oldText}
-\begin{newText}{\andy}
-To that end, we construct a family of QIVPMs parameterized by {\color{blue}\emph{interval}
-maps. A interval map} $f:\left[0,1\right]\rightarrow\mathscr{I}$
-maps every real-valued probability $x\in\left[0,1\right]$ to a set
-of intervals $f\left(x\right)=\left[\ell,r\right]$ containing $x$,
-where $\left[0,1\right]$ denotes the set of real-valued probabilities
-which should not be considered as the interval-valued probability
-$\unknown$. We also need a notion of norm to quantify the
-distance between (pure or mixed) states. The norm of a pure state
-$\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
-In addition, given any Hermitian operator~$A$, we consider the usual
-operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
-which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
-In fact, for any such matrix, including the density matrix~$\rho$,
-the norm is the maximum absolute value of its eigenvalue. Then, a
-finite-precision extension of Gleason's theorem can be stated as follows.
-\end{newText}
-\end{compare}
-
-\begin{compareNextpage}
-\begin{oldText}{\andy}
+th{\color{red}is norm is the eigenvalue with maximum absolute value}. Then, a
+finite-precision extension of Gleason's theorem can be stated as
+follows{\color{red}:}
+
 \begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
-$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a {\color{blue}blurring function}
-and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
+$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a{\color{red}n} interval map
+and let {\color{red}the composition} $f\circ\muB_{\rho}$ be a QIVPM, where
+$\muB_{\rho}$ is the
 probability measure induced by the Born rule for a given state~$\rho$.
@@
 then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
-\end{oldText}
-\begin{newText}{\andy}
-\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
-$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a {\color{blue}interval map}
-and let $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$ is the
-probability measure induced by the Born rule for a given state~$\rho$.
-Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
-If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
-events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
-then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
-\end{newText}
-\end{compareNextpage}
 
@@
 
-\begin{compare}
-\begin{oldText}{\andy}
+\subsection{\color{red}Ultramodular Functions}
+
 Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
@@
 the sense that it only applies to the particular class of QIVPMs
-constructed by composing a {\color{blue}blurring function} with a conventional
+constructed by composing a{\color{blue}n} interval map with a conventional
 quantum probability measure. QIVPMs constructed in this manner have
@@
 
-A {\color{blue}blurring function} is called \emph{ultramodular} if it satisfies
+A{\color{blue}n} interval map is called \emph{ultramodular} if it satisfies
 the following properties.
@@
   a collection of intervals $\mathscr{I}$ including $\imposs$ and
-  $\necess$, a {\color{blue}blurring function}
+  $\necess$, a{\color{blue}n} interval map
   $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
@@
 counterpart of the convexity conditions,
-Eq.~(\ref{eq:classicalconvex}) and
-(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
-\cite{Choquet1954,Shapley1971,NgMoYeh1997,MarinacciMontrucchio2005}. Therefore,
-these conditions guarantee that, for any conventional quantum
-probability measure $\mu$, the composition $\ultramodular \circ \mu$
-defines a valid QIVPM. Conversely, if for every quantum probability
-measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the {\color{blue}blurring
-function}~$f$ is an ultramodular function. Formally, we have the following
-result.
-\end{oldText}
-\begin{newText}{\andy}
-Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
-theorem in the sense that it accounts for a larger class of probability measures that includes
-the conventional one as a limit. The theorem is however ``special'' in
-the sense that it only applies to the particular class of QIVPMs
-constructed by composing a {\color{blue}interval map} with a conventional
-quantum probability measure. QIVPMs constructed in this manner have
-some peculiar properties that we examine next.
-
-A {\color{blue}interval map} is called \emph{ultramodular} if it satisfies
-the following properties.
-
-\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
-  a collection of intervals $\mathscr{I}$ including $\imposs$ and
-  $\necess$, a {\color{blue}interval map}
-  $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
-  ultramodular if:
-\begin{subequations}\label{eq:iota-constraints}
-\begin{eqnarray}
- &  & \ultramodular(0)=\imposs\,,\\
- &  & \ultramodular(1)=\necess\,,\\
- &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
-\end{eqnarray}
-\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$, and
-$x_{2}\in\left[0,1\right]$ such that
-$y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have:
-\begin{equation}
-\ultramodular\left(y\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
-\end{equation}
-\end{definition}
-
-\noindent The first three constraints,
-Eqs.~(\ref{eq:iota-constraints}), are the direct counterpart of the
-corresponding QIVPM constraints, Eqs.~(\ref{eq:QIVPM-constraints});
-the last condition, Eq.~(\ref{eq:iota-Inclusion}), is the direct
-counterpart of the convexity conditions,
-Eq.~(\ref{eq:classicalconvex}) and
+Eq{\color{red}s}.~(\ref{eq:classicalconvex}) and
 (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
@@
 map}~$f$ is an ultramodular function. Formally, we have the following
-result.
-\end{newText}
-\end{compare}
+result{\color{red}:}
 
@@
 
-\begin{compare}
-\begin{oldText}{\andy}
 In other words, essential properties of QIVPMs constructed using
-{\color{blue}blurring function}s can be gleaned from the properties of
+interval maps can be gleaned from the properties of
 ultramodular functions. The following is a most interesting property
-in our setting. 
-\end{oldText}
-\begin{newText}{\andy}
-In other words, essential properties of QIVPMs constructed using
-{\color{blue}interval map}s can be gleaned from the properties of
-ultramodular functions. The following is a most interesting property
-in our setting. 
-\end{newText}
-\end{compare}
+in our setting{\color{red}:}
 
@@
 
-\begin{compare}
-\begin{oldText}{\andy}
 To summarize, a conventional quantum probability measure has an
-uncountable range $[0,1]$. A QIVPM constructed by {\color{blue}blurring} such a
+uncountable range $[0,1]$. A QIVPM constructed by blurring such a
 conventional quantum probability measure must also have an uncountable
@@
 the resources and precision of the particular experiment.
-\end{oldText}
-\begin{newText}{\andy}
-To summarize, a conventional quantum probability measure has an
-uncountable range $[0,1]$. A QIVPM constructed by {\color{blue}?????} such a
-conventional quantum probability measure must also have an uncountable
-range of intervals. Of course, any particular QIVPM, or any particular
-experiment, will use a fixed collection of intervals appropriate for
-the resources and precision of the particular experiment. 
-\end{newText}
-\end{compare}
+
+\andy{no ending? What was the point of the section?}
 

### 2018-03-29 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Eliminating pdfLaTeX warning...
revised_prop_letter_ajhs.tex Updated what Andy, Amr, and I discussed...

@@
 guarantee} that there exists a unique state $\rho$ that satisfies
-Eq.~(\ref{eq:consistent}) and therefor{\color{OliveGreen}e} is consistent with a QIVPM.
+Eq.~(\ref{eq:consistent}) and therefore is consistent with a QIVPM.
 \end{definition}
@@
 
-{\color{red}An outline of}The proof, detailed in the forthcoming
+{\color{red}An outline of t}he proof, detailed in the forthcoming
 thesis~\cite{TaiThesis2018}, proceeds as
@@
 
-\subsection{\color{red}Finite-Precision Extension of Gleason's Theorem}
+{\color{red}\subsection{Finite-Precision Extension of Gleason's Theorem}}
 
@@
 
-\subsection{\color{red}Ultramodular Functions}
+{\color{red}\subsection{Ultramodular Functions}}
 
@@
 the sense that it only applies to the particular class of QIVPMs
-constructed by composing a{\color{blue}n} interval map with a conventional
+constructed by composing a{\color{red}n} interval map with a conventional
 quantum probability measure. QIVPMs constructed in this manner have
@@
 
-A{\color{blue}n} interval map is called \emph{ultramodular} if it satisfies
+A{\color{red}n} interval map is called \emph{ultramodular} if it satisfies
 the following properties.
@@
   a collection of intervals $\mathscr{I}$ including $\imposs$ and
-  $\necess$, a{\color{blue}n} interval map
+  $\necess$, a{\color{red}n} interval map
   $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
@@
 defines a valid QIVPM. Conversely, if for every quantum probability
-measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the {\color{blue}interval
+measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the {\color{red}interval
 map}~$f$ is an ultramodular function. Formally, we have the following
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\color{red}\begin{acknowledgments}
+The authors would like to thank the anonymous reviewers for their helpful and
+constructive comments that greatly contributed to improving the final version of the paper.
+\end{acknowledgments}}
 

### 2018-03-29 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Adding more comments...

@@
   To verify the convexity condition of a QIVPM
-  $\mu : \events \rightarrow \mathscr{I}$, it is sufficient to check
+  ${\color{red}\bar{\mu}} : \events \rightarrow \mathscr{I}$, it is sufficient to check
   that:
@@
 $\ip{\phi_{j}}{\phi_{j}}=1$, and thus the theorem is proved.}
+\yutsung{The new text seems not very smooth. How about the following?}
+If this is true, then $\ip{0}{\phi_{j}}=\ip{\ps}{\phi_{j}}=\ip{\ps'}{\phi_{j}}=0$
+for all~$j$. This follows that
+\begin{subequations}
+\begin{eqnarray}
+ &  & \ip{1}{\phi_{j}}=\sqrt{2}\ip{\ps}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,,\\
+ &  & \ip{2}{\phi_{j}}=\sqrt{2}\ip{\ps'}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,,
+\end{eqnarray}
+\end{subequations}
+so
+that$\ket{\phi_{j}}=\ket{0}\ip{0}{\phi_{j}}+\ket{1}\ip{1}{\phi_{j}}+\ket{2}\ip{2}{\phi_{j}}=0$.
+This violates the fact that $\ket{\phi_{j}}$ is a normalized state, and thus the
+theorem is proved.
+\yutsung{End of the suggested text.}
 
@@
 \andy{no ending? What was the point of the section?}
+\yutsung{Begin of comments}
+Can this relate it to the following theorem:
+\begin{thm}Any ($\rho \rightarrow \rho$)-computable function~$f$ mapping between
+continuums, like unit interval $[0,1]$, is continuous
+\cite{Ziegler2007,weihrauch2012computable}.\end{thm}
+The idea is that when we mapping between continuums, only continuous functions
+could be approximated, and discontinuous functions might be too wild to be approximated...
+However, I don't know how to fit this idea with other part of the paper...
+\yutsung{End of comments}
 

### 2018-03-29 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex \section{The Born Rule and Gleason's Theorem} Passed again...

--- 2018-03-29 revised_prop_letter_ajhs.tex
@@
 $\ip{\phi_{j}}{\phi_{j}}=1$, and thus the theorem is proved.}
+\yutsung{The above new text seems not very smooth. How about the following?}
+\noindent If this is true, then $\ip{0}{\phi_{j}}=\ip{\ps}{\phi_{j}}=\ip{\ps'}{\phi_{j}}=0$
+for all~$j$. This follows that
+\begin{subequations}
+\begin{eqnarray}
+ &  & \ip{1}{\phi_{j}}=\sqrt{2}\ip{\ps}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,,\\
+ &  & \ip{2}{\phi_{j}}=\sqrt{2}\ip{\ps'}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,.
+\end{eqnarray}
+\end{subequations}
+The above equation implies
+$\ket{\phi_{j}}=\ket{0}\ip{0}{\phi_{j}}+\ket{1}\ip{1}{\phi_{j}}+\ket{2}\ip{2}{\phi_{j}}=0$,
+violating the assumption that $\ket{\phi_{j}}$ is a normalized state, and thus the
+theorem is proved.
+\yutsung{End of the suggested text.}
 
@@
 where $\left[0,1\right]$ denotes the set of real-valued probabilities
-{\color{red}this is unrelated to the interval-valued probability
-$\unknown$.} We also need a notion of {\color{red}\emph{norm}} to quantify the
+{\color{red}(this is unrelated to the interval-valued probability
+$\unknown$).} \yutsung{How about change to ``(this should not be confused with
+the interval-valued probability $\unknown$)''?}
+We also need a notion of {\color{red}\emph{norm}} to quantify the
 distance between (pure or mixed) states. The norm of a pure state
@@
 defines a valid QIVPM. Conversely, if for every quantum probability
-measure $\mu$, it is the case that if $f \circ \mu$ is a QIVPM, then the {\color{red}interval
-map}~$f$ is an ultramodular function. Formally, we have the following
+measure $\mu$, it is the case {\color{red}that $f \circ \mu$ is a QIVPM, then
+the interval map}~$f$ is an ultramodular function. Formally, we have the following
 result{\color{red}:}
@@
 \]
-The induced map using the Born rule and blurred by $\ultramodular$,
+The induced map using the Born rule and blurred\yutsung{A ``blurred'' here.} by $\ultramodular$,
 $\ultramodular\circ\muB_{\rho}$, fails to satisfy
@@
 interval maps can be gleaned from the properties of
-ultramodular functions. The following is a most interesting property
+ultramodular functions. The following is a most\yutsung{``a most''?} interesting property
 in our setting{\color{red}:}
@@
 $\left(0,1\right)$~\cite{MarinacciMontrucchio2005}.  Therefore,
-either $\ultramodular$ maps every number in $\left[0,1\right]$ to the
+either $\ultramodular$ maps every number in {\color{red}$\left(0,1\right)$} to the
 same interval, or the number of intervals to which $\ultramodular$ maps
@@
 \andy{no ending? What was the point of the section?}
+\yutsung{Begin of comments}
+Thm.~\ref{thm:convex-uncountable} proved
+$\ultramodularL:\left[0,1\right]\rightarrow\left[0,1\right]$ is continuous, and
+$\mathscr{I}$ contains uncountably many intervals. In the sense of ``achieving
+computable theory of quantum mechanics'', this fact may relate the following
+Thm.~\ref{thm:rho2rho-continuous} \cite{Ziegler2007,weihrauch2012computable}
+whose idea is that when we mapping between continuums, only continuous functions
+could be (computably-)approximated, while discontinuous functions might be too
+wild to be approximated.
+
+The relation between ``achieving computable theory''
+and ``finite precision measurement'' is more vague, but ``finite precision
+measurement'' might be one of the reasons why analog computers could not be as
+power as the theoratical prediction\ldots
+
+\begin{definition}
+Call $x\in\mathbb{R}$ Cauchy-computable if there exists a Turing-machine to
+generate two rational sequences $\left(q_{n}\right)_{n\in\mathbb{N}}$ and
+$\left(\epsilon_{n}\right)_{n\in\mathbb{N}}$ with
+$\left|x-q_{n}\right|\le\epsilon_{n}\rightarrow 0$.
+\end{definition}
+
+\begin{definition}
+We call $f:\mathbb{R}\rightarrow\mathbb{R}$ ($\rho\rightarrow\rho$)-computable
+if some Turing machine can, upon input of $x$ (by means of fast converging
+rational approximations $\left(q_{n}\right)_{n\in\mathbb{N}}$ with
+$\epsilon_{n}=2^{-n}$), output (fast convergent rational approximations
+$\left(p_{n}\right)_{n\in\mathbb{N}}$ to) $y=f\left(x\right)$.
+\end{definition}
+
+\begin{thm}\label{thm:rho2rho-continuous}
+If $f:\left[0,1\right]\rightarrow\mathbb{R}$ is
+($\rho\rightarrow\rho$)-computable, then $f$ is continuous.
+\end{thm}
+\yutsung{End of comments}
 

### 2018-03-29 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex \subsection{Ultramodular Functions} Fix a typo...

@@
 measurement'' might be one of the reasons why analog computers could not be as
-power as the theoratical prediction\ldots
+power as the theoretical prediction\ldots
 

### 2018-03-30 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Keep passing...

@@
 In contrast with classical probability spaces, there is \emph{no
-guarantee} that there exists a unique state $\rho$ that satisfies
+guarantee} that there exists {\color{red}a state} $\rho$ that satisfies
 Eq.~(\ref{eq:consistent}) and therefore is consistent with a QIVPM.
@@
 a ``core'' set of states relative to subspaces. First, we define
-$\events'$ as a \emph{subspace} of a set of events~$\events$ if
+$\events'$ as a \emph{subspace} of a set of {\color{red}events~$\events$} if
 $\events'$ contains the projector{\color{red}s} $\mathbb{0}$ and $\mathbb{1}$ and is closed under
@@
   observable with spectral decomposition
-  $\Sigma_{i=1}^d \lambda_iP_i$. Let $\events'$ be the minimal
+  ${\color{red}\sum}_{i=1}^d \lambda_iP_i$. Let $\events'$ be the minimal
   subspace of events containing all the projectors $P_i$ in the
@@
 Kochen-Specker to experimental, and hence finite-precision, quantum
-measurements~\cite{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+measurements~{\color{red}\cite{PhysRevLett.83.3751,HKSS1999apsrev4,Mermin1999,Kent1999,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}}.
 Specifically, the original Kochen-Specker theorem is formulated using

### 2018-03-30 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex \subsection{Finite-Precision Extension of the Kochen-Specker Theorem} Keep passing...

@@
 because, by Eq.~(\ref{eq:necess}), we have
-$\bar{\mu}(\Sigma_{j=0}^{d-1}{\proj{\psi_j}})=\necess$ and by
+$\bar{\mu}{\color{red}\left(\sum_{j=0}^{d-1}{\proj{\psi_j}}\right)}=\necess$ and by
 inductively applying
@@
   Theorem] \label{thm:Kochen-Specker} Given a Hilbert space $\Hilb$ of
-  dimension $d\ge3$, there is no 0-deterministic measure~$\bar{\mu}$
+  dimension $d\ge3$, there is no {\color{red}$0$}-deterministic measure~$\bar{\mu}$
   mapping every event to either $\imposs$ or $\necess$.

### 2018-03-30 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Update macro a little bit...

@@
 \NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
-\newenvironment{compare}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
-\newenvironment{compareNextpage}{\clearpage}{\begin{widetext}\end{widetext}}
-\NewDocumentEnvironment{compareText}{m m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is #2 text.}\begin{docParinfo}}{\end{docParinfo}#1{The #2 text end here.}\end{minipage}}
-\newenvironment{oldText}[1]{\begin{compareText}{#1}{old}}{\end{compareText}\penalty-10000}
-\newenvironment{newText}[1]{\begin{compareText}{#1}{new}}{\end{compareText}}
+\NewDocumentEnvironment{compare}{m}{\begin{widetext}#1{The following left column should be replaced by the right column.}\end{widetext}}{\begin{widetext}#1{End of replacement.}\end{widetext}}
+\newenvironment{compareText}{\noindent\begin{minipage}[b]{1\columnwidth}\begin{docParinfo}}{\end{docParinfo}\end{minipage}}
+\newenvironment{oldText}{\begin{compareText}}{\end{compareText}\penalty-10000}
+\newenvironment{newText}{\begin{compareText}}{\end{compareText}}
 

### 2018-03-30 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex \subsection{Finite-Precision Extension of the Kochen-Specker Theorem} Passed...

@@
   $\delta < \frac{1}{3}$, we can construct a $0$-deterministic QIVPM
-  $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
+  $\bar{\mu}^{\color{red}D}:\events\rightarrow\left\{
     \imposs,\necess\right\}$ defined as follows:
 \begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
+\bar{\mu}^{\color{red}D}\left(P\right)=\begin{cases}
 \imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
@@
 \noindent The most important part of the proof is to verify the convexity
-condition for $\bar{\mu}^{\textrm{D}}$. By Lemma~\ref{lemma:verify-convexity}, it is sufficient
+condition for $\bar{\mu}^{\color{red}D}$. By Lemma~\ref{lemma:verify-convexity}, it is sufficient
 to verify the following equation for orthogonal projectors $P_{0}$
@@
 \begin{equation}
-\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,, \label{eq:QuantumInterval-valuedProbability-Equal}
+\bar{\mu}^{\color{red}D}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\color{red}D}\left(P_{0}\right)+\bar{\mu}^{\color{red}D}\left(P_{1}\right)\,, \label{eq:QuantumInterval-valuedProbability-Equal}
 \end{equation}
@@
 
-When one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
-is $\necess$, say $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\imposs$
-and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\necess$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
+When one of $\bar{\mu}^{\color{red}D}\left(P_{0}\right)$ and $\bar{\mu}^{\color{red}D}\left(P_{1}\right)$
+is $\necess$, say $\bar{\mu}^{\color{red}D}\left(P_{0}\right)=\imposs$
+and $\bar{\mu}^{\color{red}D}\left(P_{1}\right)=\necess$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
 and $\bar{\mu}\left(P_{1}\right)\subseteq\left[1-\delta,1\right]$ which
@@
 $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
-which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)$ is also
+which implies $\bar{\mu}^{\color{red}D}\left(P_{0}+P_{1}\right)$ is also
 $\necess$, thus satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
@@
 When both
-$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
+$\bar{\mu}^{\color{red}D}\left(P_{0}\right)$ and $\bar{\mu}^{\color{red}D}\left(P_{1}\right)$
 are $\imposs$, we have both $\bar{\mu}\left(P_{0}\right)$ and
@@
 $\left[0,\delta\right]$, which implies
-$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$, and hence
+$\bar{\mu}^{\color{red}D}\left(P_{0}+P_{1}\right)=\imposs$, and hence
 also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) is again satisfied.
@@
 determine the probability of any event, we typically repeat an
-experiment $n$ times and count the number of times we witness the
+experiment {\color{red}$m$} times and count the number of times we witness the
 event. This assumes that for each run of the experiment we can

### 2018-03-31 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fix suggestion from Andy...

@@
 corresponding ones for classical IVPMs.  {\color{red}Note that the minus sign
-appears in Eq.~(\ref{eq:complement}) is accommodated by the $x\le0$ case in
+appearing in Eq.~(\ref{eq:complement}) is accommodated by the $x\le0$ case in
 Eq.~(\ref{eq:interval-times}).}  With the understanding that
@@
 intervals, not just ``almost definite intervals.'' The proof requires
-two simple lemmas which we present first.
+two simple lemmas {\color{red}that} we present first.
 
@@
 $\muB_{\rho}(\proj{0})=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
-If this is true, then $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
-for all~$j$. {\color{red}Since any vector can be decomposed in terms of the
-linearly independent basis $\left\{\ket{0},\ket{\ps},\ket{\ps'}\right\}$, all
-$\ket{\phi_{j}}$ are perpendicular to any vector in the Hilbert space, and so
-are not valid non-empty states, violating the assumption
-$\ip{\phi_{j}}{\phi_{j}}=1$, and thus the theorem is proved.}
-\yutsung{The above new text seems not very smooth. How about the following?}
-\noindent If this is true, then $\ip{0}{\phi_{j}}=\ip{\ps}{\phi_{j}}=\ip{\ps'}{\phi_{j}}=0$
-for all~$j$. This follows that
+If this is true, then {\color{red}$\ip{0}{\phi_{j}}=\ip{\ps}{\phi_{j}}=\ip{\ps'}{\phi_{j}}=0$
+for all~$j$, and thus
 \begin{subequations}
@@
 \end{subequations}
-The above equation implies
+The above equations imply
 $\ket{\phi_{j}}=\ket{0}\ip{0}{\phi_{j}}+\ket{1}\ip{1}{\phi_{j}}+\ket{2}\ip{2}{\phi_{j}}=0$,
 violating the assumption that $\ket{\phi_{j}}$ is a normalized state, and thus the
-theorem is proved.
-\yutsung{End of the suggested text.}
+theorem is proved.}
 
@@
 
-To that end, we {\color{red}introduce the conept of \emph{interval maps} which
-we can use to construct a consistent family of QIVPM.}
+To that end, we {\color{red}introduce the concept of \emph{interval maps}, which
+we can use to construct a consistent family of QIVPMs.}
 A{\color{red}n} interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$
@@
 where $\left[0,1\right]$ denotes the set of real-valued probabilities
-{\color{red}(this is unrelated to the interval-valued probability
-$\unknown$).} \yutsung{How about change to ``(this should not be confused with
-the interval-valued probability $\unknown$)''?}
+{\color{red}(this should not be confused with
+the interval-valued probability $\unknown$)}.
 We also need a notion of {\color{red}\emph{norm}} to quantify the
@@
 $\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
-{\color{red} For any given Hermitian operator~$A$, we choose}
+{\color{red} For any given Hermitian operator~$A$, we choose the}
 operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
@@
 A{\color{red}n} interval map is called \emph{ultramodular} if it satisfies
-the following properties.
+the following properties{\color{red}:}
 
@@
 \]
-The induced map using the Born rule and blurred\yutsung{A ``blurred'' here.} by $\ultramodular$,
-$\ultramodular\circ\muB_{\rho}$, fails to satisfy
+The induced map {\color{red}$\ultramodular\circ\muB_{\rho}$ constructed using the Born rule and
+blurred by $\ultramodular$ fails} to satisfy
 Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
@@
 interval maps can be gleaned from the properties of
-ultramodular functions. The following is a most\yutsung{``a most''?} interesting property
+ultramodular functions. The following is a most interesting property
 in our setting{\color{red}:}
@@
 
+\begin{comment}
 \andy{no ending? What was the point of the section?}
@@
 \yutsung{End of comments}
+\end{comment}
 
@@
 
-% \input{revised_prop_letter_ajhs.bbl}
+\input{revised_prop_letter_ajhs.bbl}
+\begin{comment}
 \bibliography{prop}
+\end{comment}
 \end{document}

### 2018-04-01 dissertation.tex
revised_prop_letter_ajhs.tex Fix a typo...
dissertation.lyx Updated for fitting iuphd class b532d3f3c02cf73f4424393d40c2cfa65b0eb468
dissertation.lyx Fix the order of co-chairs...

@@
 %data for Acceptance Page
-\committeeMember{Amr A. Sabry, PhD} \committeeMember{Dylan Paul
-Thurston, PhD} \committeeMember{Gerardo Ortiz, PhD} \committeeMember{Andrew
+\committeeMember{Amr A. Sabry, PhD} \committeeMember{Gerardo
+Ortiz, PhD} \committeeMember{Dylan Paul Thurston, PhD} \committeeMember{Andrew
 J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{Defense
@@
 \tableofcontents{}
-
-\todo{The page of Bibliography is not correct?}
 
@@
 
-\chapter{Quantum Interval-Valued Probability}
+\chapter{Toward a Quantum Measurement Theory with Error: Quantum Interval-Valued
+Probability}
 
@@
 
-\addcontentsline{toc}{chapter}{Bibliography} %
+\addcontentsBibliography %
 \begin{comment}

### 2018-04-01 dissertation.tex
dissertation.tex Acknowledgments Updating...

@@
 
-\begin{acknowledgments}The acknowledgments are designed to recognize
-people or agencies to whom you feel grateful for any academic, technical,
-financial, or personal aid in the preparation of your thesis or dissertation;
-as a matter of courtesy, you would ordinarily mention the members
-of your committee here, as well as institutions that provided funding,
-your typist, or anyone else who helped.\end{acknowledgments}
+\begin{acknowledgments}Thank Prof. Andrew J. Hanson, Prof. Gerardo
+Ortiz, and Prof. Amr A. Sabry for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
+with me. They becomes the main part of my thesis, especially most
+of Chapter~\ref{chap:DQT=000026DQC} is based on ``Geometry of discrete
+quantum computing''~\cite{geometry2013} and ``Discrete quantum
+theories''~\cite{DQT2014}; most of Chapter~\ref{chap:DQT=000026DQC}
+is based on ``Quantum Interval-Valued Probability: Contextuality
+and the Born Rule'' \cite{THOS2017}. Together with Prof. Dylan Paul
+Thurston and Prof. Shouhong Wang, thank you for getting together to
+understand what I did and passing my dissertation proposal Spring
+2017. Also, you passed my Computer Science qualified exam Spring 2016.
+Especially, my survey of real computation inspires me the comparison
+of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
+Thank Prof. Lawrence Moss for inviting me to presented my results
+in the interdisciplinary logic seminar and SICE theory seminar, co-chairing
+my Tier 3 committee, and drawing my attention on Prof. Abramsky's
+paper~\cite{Abramsky2012}, which inspired me to merge quantum probability
+with discrete quantum theories. Thanks John Gardiner for inspiring
+discussion on the difficulties merging quantum probability with discrete
+quantum theories~\cite{Gardiner2014}. An improved work consists
+of Sec.~\ref{sec:Toward-IVPM} \end{acknowledgments}
 \begin{abstract}
@@
 
-\chapter{Introduction}
+\chapter{Introduction\label{chap:Introduction}}
 
@@
 
-\chapter{Quantum Theories and Computing over Finite Fields}
+\chapter{Quantum Theories and Computing over Finite Fields\label{chap:DQT=000026DQC}}
 
@@
 
-\section{Irreducible Discrete $D$-dimensional States: Generalized Discrete
+\subsection{Irreducible Discrete $D$-dimensional States: Generalized Discrete
 Bloch Sphere\label{DQCnqubitBloch.sec}}
@@
 
-\section{Toward Discrete Quantum Probability}
+\section{Toward Discrete Quantum Probability\label{sec:Toward-IVPM}}
 
@@
 \chapter{Toward a Quantum Measurement Theory with Error: Quantum Interval-Valued
-Probability}
+Probability\label{chap:QIVPM}}
 

### 2018-04-02 dissertation.tex
dissertation.lyx acknowledgments Updates...

@@
 
-\begin{acknowledgments}Thank Prof. Andrew J. Hanson, Prof. Gerardo
-Ortiz, and Prof. Amr A. Sabry for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
+\begin{acknowledgments}Thank Prof. Andrew Hanson, Prof. Gerardo Ortiz,
+and Prof. Amr Sabry for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
 with me. They becomes the main part of my thesis, especially most
@@
 is based on ``Quantum Interval-Valued Probability: Contextuality
-and the Born Rule'' \cite{THOS2017}. Together with Prof. Dylan Paul
-Thurston and Prof. Shouhong Wang, thank you for getting together to
-understand what I did and passing my dissertation proposal Spring
-2017. Also, you passed my Computer Science qualified exam Spring 2016.
-Especially, my survey of real computation inspires me the comparison
+and the Born Rule'' \cite{THOS2017}. Together with Prof. Dylan Thurston
+and Prof. Shouhong Wang, thank you for getting together to understand
+what I did and passing my dissertation proposal Spring 2017. Also,
+thank Prof. Dylan Thurston for serving in my advisory committee and
+my Tier 3 committee, with other advisory committee members passing
+my Computer Science qualifying exam Spring 2016. Especially, my survey
+of real computation in the qualifying exam inspires me the comparison
 of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
@@
 in the interdisciplinary logic seminar and SICE theory seminar, co-chairing
-my Tier 3 committee, and drawing my attention on Prof. Abramsky's
-paper~\cite{Abramsky2012}, which inspired me to merge quantum probability
-with discrete quantum theories. Thanks John Gardiner for inspiring
-discussion on the difficulties merging quantum probability with discrete
-quantum theories~\cite{Gardiner2014}. An improved work consists
-of Sec.~\ref{sec:Toward-IVPM} \end{acknowledgments}
+my Tier 3 committee, writing an assessment letter for me, and drawing
+my attention on Prof. Abramsky's paper~\cite{Abramsky2012}, which
+inspired me to merge quantum probability with discrete quantum theories.
+Thanks John Gardiner for inspiring discussion on the difficulties
+merging quantum probability with discrete quantum theories~\cite{Gardiner2014}.
+An improved work consists of Sec.~\ref{sec:Toward-IVPM} \end{acknowledgments}
 \begin{abstract}

### 2018-04-02 dissertation.tex
dissertation.lyx acknowledgments Updates...

@@
 
-\begin{acknowledgments}Thank Prof. Andrew Hanson, Prof. Gerardo Ortiz,
-and Prof. Amr Sabry for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
-with me. They becomes the main part of my thesis, especially most
-of Chapter~\ref{chap:DQT=000026DQC} is based on ``Geometry of discrete
-quantum computing''~\cite{geometry2013} and ``Discrete quantum
-theories''~\cite{DQT2014}; most of Chapter~\ref{chap:DQT=000026DQC}
-is based on ``Quantum Interval-Valued Probability: Contextuality
-and the Born Rule'' \cite{THOS2017}. Together with Prof. Dylan Thurston
-and Prof. Shouhong Wang, thank you for getting together to understand
-what I did and passing my dissertation proposal Spring 2017. Also,
-thank Prof. Dylan Thurston for serving in my advisory committee and
-my Tier 3 committee, with other advisory committee members passing
-my Computer Science qualifying exam Spring 2016. Especially, my survey
-of real computation in the qualifying exam inspires me the comparison
-of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
-Thank Prof. Lawrence Moss for inviting me to presented my results
-in the interdisciplinary logic seminar and SICE theory seminar, co-chairing
-my Tier 3 committee, writing an assessment letter for me, and drawing
-my attention on Prof. Abramsky's paper~\cite{Abramsky2012}, which
-inspired me to merge quantum probability with discrete quantum theories.
-Thanks John Gardiner for inspiring discussion on the difficulties
-merging quantum probability with discrete quantum theories~\cite{Gardiner2014}.
-An improved work consists of Sec.~\ref{sec:Toward-IVPM} \end{acknowledgments}
+\begin{acknowledgments}Thank Prof. Gerardo Ortiz, Prof. Amr Sabry,
+and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
+with me, and enormous other things. These papers become the main part
+of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
+is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
+and ``Discrete quantum theories'' (DQT)~\cite{DQT2014}; most of
+Chapter~\ref{chap:DQT=000026DQC} is based on ``Quantum Interval-Valued
+Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2017}.
+Together with Prof. Dylan Thurston and Prof. Shouhong Wang, thank
+you for getting together to understand what I did and passing my dissertation
+proposal Spring 2017. Also, thank Prof. Dylan Thurston for serving
+in my advisory committee and my Tier 3 committee, with other advisory
+committee members passing my Computer Science qualifying exam Spring
+2016. Especially, my survey of real computation in the qualifying
+exam inspires me the comparison of quantum computer and analog computer
+in Chapter~\ref{chap:Introduction}. Thank Prof. Lawrence Moss for
+inviting me to present our results in the interdisciplinary logic
+seminar and SICE theory seminar, co-chairing my Tier 3 committee,
+writing an assessment letter for me, and drawing my attention on Prof.
+Abramsky's paper~\cite{Abramsky2012}, which inspired me to merge
+quantum probability with discrete quantum theories. Thank John Gardiner
+for inspiring discussion on the difficulties merging them~\cite{Gardiner2014}.
+These results are improved and motivated the transition from DQT to
+QIVPM in Sec.~\ref{sec:Toward-IVPM}. Thank Prof. Tom Lewis for helping
+me organize the unpublished deterministic quantum algorithms in the
+term paper for SLST-T501 Academic Writing course. Thank Instructor
+Traci Nagle\end{acknowledgments}
 \begin{abstract}

### 2018-04-03 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Updated according to Andy's suggestion...

@@
 Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
-corresponding ones for classical IVPMs.  {\color{red}Note that the minus sign
+corresponding ones for classical IVPMs.  Note that the minus sign
 appearing in Eq.~(\ref{eq:complement}) is accommodated by the $x\le0$ case in
-Eq.~(\ref{eq:interval-times}).}  With the understanding that
+Eq.~(\ref{eq:interval-times}).  With the understanding that
 the union of classical sets $E_1\cup E_2$ is replaced by
@@
 $\bar{\mu}\left(P\right)$. However, if we restrict ourselves to the set
-$\eventsC$ of mutually commuting {\color{red} events}, 
+$\eventsC$ of mutually commuting events, 
 the situation reverts to the classical case in which
@@
 In contrast with classical probability spaces, there is \emph{no
-guarantee} that there exists {\color{red}a state} $\rho$ that satisfies
+guarantee} that there exists a state $\rho$ that satisfies
 Eq.~(\ref{eq:consistent}) and therefore is consistent with a QIVPM.
@@
 a ``core'' set of states relative to subspaces. First, we define
-$\events'$ as a \emph{subspace} of a set of {\color{red}events~$\events$} if
-$\events'$ contains the projector{\color{red}s} $\mathbb{0}$ and $\mathbb{1}$ and is closed under
+$\events'$ as a \emph{subspace} of a set of events~$\events$ if
+$\events'$ contains the projectors $\mathbb{0}$ and $\mathbb{1}$ and is closed under
 complements, sums, and products.  In particular, for any
@@
 
-{\color{red}An outline of t}he proof, detailed in the forthcoming
+An outline of the proof, detailed in the forthcoming
 thesis~\cite{TaiThesis2018}, proceeds as
@@
   observable with spectral decomposition
-  ${\color{red}\sum}_{i=1}^d \lambda_iP_i$. Let $\events'$ be the minimal
+  $\sum_{i=1}^d \lambda_iP_i$. Let $\events'$ be the minimal
   subspace of events containing all the projectors $P_i$ in the
@@
 Kochen-Specker to experimental, and hence finite-precision, quantum
-measurements~{\color{red}\cite{PhysRevLett.83.3751,HKSS1999apsrev4,Mermin1999,Kent1999,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}}.
+measurements~\cite{PhysRevLett.83.3751,HKSS1999apsrev4,Mermin1999,Kent1999,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
 Specifically, the original Kochen-Specker theorem is formulated using
@@
 because, by Eq.~(\ref{eq:necess}), we have
-$\bar{\mu}{\color{red}\left(\sum_{j=0}^{d-1}{\proj{\psi_j}}\right)}=\necess$ and by
+$\bar{\mu}\left(\sum_{j=0}^{d-1}{\proj{\psi_j}}\right)=\necess$ and by
 inductively applying
@@
   Theorem] \label{thm:Kochen-Specker} Given a Hilbert space $\Hilb$ of
-  dimension $d\ge3$, there is no {\color{red}$0$}-deterministic measure~$\bar{\mu}$
+  dimension $d\ge3$, there is no $0$-deterministic measure~$\bar{\mu}$
   mapping every event to either $\imposs$ or $\necess$.
@@
 intervals, not just ``almost definite intervals.'' The proof requires
-two simple lemmas {\color{red}that} we present first.
+two simple lemmas that we present first.
 
@@
   To verify the convexity condition of a QIVPM
-  ${\color{red}\bar{\mu}} : \events \rightarrow \mathscr{I}$, it is sufficient to check
+  $\bar{\mu} : \events \rightarrow \mathscr{I}$, it is sufficient to check
   that:
@@
   $\delta < \frac{1}{3}$, we can construct a $0$-deterministic QIVPM
-  $\bar{\mu}^{\color{red}D}:\events\rightarrow\left\{
+  $\bar{\mu}^{D}:\events\rightarrow\left\{
     \imposs,\necess\right\}$ defined as follows:
 \begin{equation}
-\bar{\mu}^{\color{red}D}\left(P\right)=\begin{cases}
+\bar{\mu}^{D}\left(P\right)=\begin{cases}
 \imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
@@
 \noindent The most important part of the proof is to verify the convexity
-condition for $\bar{\mu}^{\color{red}D}$. By Lemma~\ref{lemma:verify-convexity}, it is sufficient
+condition for $\bar{\mu}^{D}$. By Lemma~\ref{lemma:verify-convexity}, it is sufficient
 to verify the following equation for orthogonal projectors $P_{0}$
@@
 \begin{equation}
-\bar{\mu}^{\color{red}D}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\color{red}D}\left(P_{0}\right)+\bar{\mu}^{\color{red}D}\left(P_{1}\right)\,, \label{eq:QuantumInterval-valuedProbability-Equal}
+\bar{\mu}^{D}\left(P_{0}+P_{1}\right)=\bar{\mu}^{D}\left(P_{0}\right)+\bar{\mu}^{D}\left(P_{1}\right)\,, \label{eq:QuantumInterval-valuedProbability-Equal}
 \end{equation}
@@
 
-When one of $\bar{\mu}^{\color{red}D}\left(P_{0}\right)$ and $\bar{\mu}^{\color{red}D}\left(P_{1}\right)$
-is $\necess$, say $\bar{\mu}^{\color{red}D}\left(P_{0}\right)=\imposs$
-and $\bar{\mu}^{\color{red}D}\left(P_{1}\right)=\necess$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
+When one of $\bar{\mu}^{D}\left(P_{0}\right)$ and $\bar{\mu}^{D}\left(P_{1}\right)$
+is $\necess$, say $\bar{\mu}^{D}\left(P_{0}\right)=\imposs$
+and $\bar{\mu}^{D}\left(P_{1}\right)=\necess$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
 and $\bar{\mu}\left(P_{1}\right)\subseteq\left[1-\delta,1\right]$ which
@@
 $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
-which implies $\bar{\mu}^{\color{red}D}\left(P_{0}+P_{1}\right)$ is also
+which implies $\bar{\mu}^{D}\left(P_{0}+P_{1}\right)$ is also
 $\necess$, thus satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
@@
 When both
-$\bar{\mu}^{\color{red}D}\left(P_{0}\right)$ and $\bar{\mu}^{\color{red}D}\left(P_{1}\right)$
+$\bar{\mu}^{D}\left(P_{0}\right)$ and $\bar{\mu}^{D}\left(P_{1}\right)$
 are $\imposs$, we have both $\bar{\mu}\left(P_{0}\right)$ and
@@
 $\left[0,\delta\right]$, which implies
-$\bar{\mu}^{\color{red}D}\left(P_{0}+P_{1}\right)=\imposs$, and hence
+$\bar{\mu}^{D}\left(P_{0}+P_{1}\right)=\imposs$, and hence
 also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) is again satisfied.
@@
 determine the probability of any event, we typically repeat an
-experiment {\color{red}$m$} times and count the number of times we witness the
+experiment $m$ times and count the number of times we witness the
 event. This assumes that for each run of the experiment we can
@@
 
-{\color{red}\subsection{Finite-Precision Extension of Gleason's Theorem}}
+\subsection{Finite-Precision Extension of Gleason's Theorem}
 
@@
 \bar{\mu}\left(P\right)=\begin{cases}
-\imposs\,, & \textrm{ if }P=\mathbb{0}\:;\\
-\necess\,, & \textrm{ if }P=\mathbb{1}\:;\\
-\unknown=\left[0,1\right]\,, & \textrm{ otherwise.}
+\imposs & \textrm{ if }P=\mathbb{0}\\
+\necess & \textrm{ if }P=\mathbb{1}\\
+\unknown=\left[0,1\right] & \textrm{ otherwise}
 \end{cases}
@@
 mapping nearly all
-projections to the {\color{red}\emph{unknown}} interval. There is however a
+projections to the \emph{unknown} interval. There is however a
 subtlety: as shown in
@@
 To prove this theorem, we need to construct a QIVPM on some Hilbert
-space, and verify that there are no states that are consistent {\color{red}(see
-Defs.~\ref{def:Consistency} and \ref{def:core})} with it
+space, and verify that there are no states that are consistent (see
+Defs.~\ref{def:Consistency} and \ref{def:core}) with it
 on all possible events. Assume a Hilbert space of dimension $d=3$ with
@@
 $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
-$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and {\color{red}assign}
+$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and assign
 \begin{equation}
@@
 $\muB_{\rho}(\proj{0})=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
-If this is true, then {\color{red}$\ip{0}{\phi_{j}}=\ip{\ps}{\phi_{j}}=\ip{\ps'}{\phi_{j}}=0$
+If this is true, then $\ip{0}{\phi_{j}}=\ip{\ps}{\phi_{j}}=\ip{\ps'}{\phi_{j}}=0$
 for all~$j$, and thus
@@
 violating the assumption that $\ket{\phi_{j}}$ is a normalized state, and thus the
-theorem is proved.}
+theorem is proved.
 
@@
 
-To that end, we {\color{red}introduce the concept of \emph{interval maps}, which
-we can use to construct a consistent family of QIVPMs.}
-A{\color{red}n} interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$
+To that end, we introduce the concept of \emph{interval maps}, which
+we can use to construct a consistent family of QIVPMs.
+An interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$
 maps every real-valued probability $x\in\left[0,1\right]$ to a set
@@
 where $\left[0,1\right]$ denotes the set of real-valued probabilities
-{\color{red}(this should not be confused with
-the interval-valued probability $\unknown$)}.
-We also need a notion of {\color{red}\emph{norm}} to quantify the
+(this should not be confused with
+the interval-valued probability $\unknown$).
+We also need a notion of \emph{norm} to quantify the
 distance between (pure or mixed) states. The norm of a pure state
 $\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
-{\color{red} For any given Hermitian operator~$A$, we choose the}
+For any given Hermitian operator~$A$, we choose the
 operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
@@
 In fact, for any such matrix, including the density matrix~$\rho$,
-th{\color{red}is norm is the eigenvalue with maximum absolute value}. Then, a
+this norm is the eigenvalue with maximum absolute value. Then, a
 finite-precision extension of Gleason's theorem can be stated as
-follows{\color{red}:}
+follows:
 
 \begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
-$f:\left[0,1\right]\rightarrow\mathscr{I}$ be a{\color{red}n} interval map
-and let {\color{red}the composition} $f\circ\muB_{\rho}$ be a QIVPM, where
+$f:\left[0,1\right]\rightarrow\mathscr{I}$ be an interval map
+and let the composition $f\circ\muB_{\rho}$ be a QIVPM, where
 $\muB_{\rho}$ is the
@@
 
-{\color{red}\subsection{Ultramodular Functions}}
+\subsection{Ultramodular Functions}
 
@@
 the sense that it only applies to the particular class of QIVPMs
-constructed by composing a{\color{red}n} interval map with a conventional
+constructed by composing an interval map with a conventional
 quantum probability measure. QIVPMs constructed in this manner have
@@
 
-A{\color{red}n} interval map is called \emph{ultramodular} if it satisfies
-the following properties{\color{red}:}
+An interval map is called \emph{ultramodular} if it satisfies
+the following properties:
 
@@
   a collection of intervals $\mathscr{I}$ including $\imposs$ and
-  $\necess$, a{\color{red}n} interval map
+  $\necess$, an interval map
   $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$ is called
@@
 counterpart of the convexity conditions,
-Eq{\color{red}s}.~(\ref{eq:classicalconvex}) and
+Eqs.~(\ref{eq:classicalconvex}) and
 (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
@@
 defines a valid QIVPM. Conversely, if for every quantum probability
-measure $\mu$, it is the case {\color{red}that $f \circ \mu$ is a QIVPM, then
-the interval map}~$f$ is an ultramodular function. Formally, we have the following
-result{\color{red}:}
+measure $\mu$, it is the case that $f \circ \mu$ is a QIVPM, then
+the interval map~$f$ is an ultramodular function. Formally, we have the following
+result:
 
@@
 \]
-The induced map {\color{red}$\ultramodular\circ\muB_{\rho}$ constructed using the Born rule and
-blurred by $\ultramodular$ fails} to satisfy
+The induced map $\ultramodular\circ\muB_{\rho}$ constructed using the Born rule and
+blurred by $\ultramodular$ fails to satisfy
 Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
@@
 ultramodular functions. The following is a most interesting property
-in our setting{\color{red}:}
+in our setting:
 
@@
 $\left(0,1\right)$~\cite{MarinacciMontrucchio2005}.  Therefore,
-either $\ultramodular$ maps every number in {\color{red}$\left(0,1\right)$} to the
+either $\ultramodular$ maps every number in $\left(0,1\right)$ to the
 same interval, or the number of intervals to which $\ultramodular$ maps
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\color{red}\begin{acknowledgments}
+\section*{Acknowledgments}
+
+\begin{acknowledgments}
 The authors would like to thank the anonymous reviewers for their helpful and
 constructive comments that greatly contributed to improving the final version of the paper.
-\end{acknowledgments}}
+\end{acknowledgments}
 

### 2018-04-03 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Updated according to Andy's suggestion...

@@
 \end{cases}
-\end{equation}
+\end{equation}%
 mapping nearly all
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgments}
+\section*{ACKNOWLEDGMENTS}
 
 \begin{acknowledgments}
-The authors would like to thank the anonymous reviewers for their helpful and
-constructive comments that greatly contributed to improving the final version of the paper.
+We gratefully acknowledge helpful comments from the anonymous reviewer that
+greatly contributed to improving the final version of the paper.
 \end{acknowledgments}

### 2018-04-05 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Final version?

@@
   \end{equation}
-In contrast with classical probability spaces, there is \emph{no
+In contrast with classical probability spaces~\cite{Note1}, there is \emph{no
 guarantee} that there exists a state $\rho$ that satisfies
@@
 \bar{\mu}^{D}\left(P\right)=\begin{cases}
-\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
-\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
+\imposs & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
+\necess & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
 \end{cases}
@@
 the limit of minimal sharpness, all states~$\rho$
-are consistent with the following QIVPM
+are consistent with the QIVPM
 \begin{equation}
 \bar{\mu}\left(P\right)=\begin{cases}
-\imposs & \textrm{ if }P=\mathbb{0}\\
-\necess & \textrm{ if }P=\mathbb{1}\\
+\imposs & \textrm{ if }P=\mathbb{0}\,;\\
+\necess & \textrm{ if }P=\mathbb{1}\,;\\
 \unknown=\left[0,1\right] & \textrm{ otherwise}
@@
 mapping nearly all
-projections to the \emph{unknown} interval. There is however a
+projections to the \emph{unknown} interval~\unknown. There is however a
 subtlety: as shown in

### 2018-04-05 dissertation.tex
dissertation.lyx Updating...
dissertation.lyx update frontmatter...

@@
 %data for Copyright Page
-% \cryear{2018}
-% \copyrightpage
-
-% \dedication{}
-% \dedicationpage
+\cryear{2018}
+\copyrightpage
+
+\begin{dedication}I would like to dedicate my thesis to my parents,
+Cheng-Tien Tai and Feng-Ming Chang. Thank for your support during
+my Ph.D. study. \end{dedication}
 
@@
 exam inspires me the comparison of quantum computer and analog computer
-in Chapter~\ref{chap:Introduction}. Thank Prof. Lawrence Moss for
-inviting me to present our results in the interdisciplinary logic
-seminar and SICE theory seminar, co-chairing my Tier 3 committee,
+in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
+also contains the motivation in my application for Rethinking Foundations
+of Physics 2017 workshop reviewed by Prof. Amr Sabry. Thank Prof.
+Lawrence Moss for inviting me to present our results in the interdisciplinary
+logic seminar and SICE theory seminar, co-chairing my Tier 3 committee,
 writing an assessment letter for me, and drawing my attention on Prof.
@@
 me organize the unpublished deterministic quantum algorithms in the
-term paper for SLST-T501 Academic Writing course. Thank Instructor
-Traci Nagle\end{acknowledgments}
+term paper for SLST-T501 Academic Writing course as presented in Sec.~\ref{discretequantumtheoryI}.
+Thank Traci Nagle for going through the literature review about finite
+precision measurement and contextuality discussed for CSCI-Y790 Writing
+and Editing course as presented in Sec.~\ref{sec:Quantum-Contextuality}.
+
+Thank Elizabeth ``Betsy'' Merceron and Kexin Chen for helping me
+pass TEPAIC exam. \end{acknowledgments}
 \begin{abstract}
@@
 
-\section{Quantum Contextuality}
+\section{Quantum Contextuality\label{sec:Quantum-Contextuality}}
 

### 2018-04-05 dissertation.tex
CV_thesis.pdf Updating...

@@
 %data for Acceptance Page
-\committeeMember{Amr A. Sabry, PhD} \committeeMember{Gerardo
+\committeeMember{Amr A. Sabry , PhD} \committeeMember{Gerardo
 Ortiz, PhD} \committeeMember{Dylan Paul Thurston, PhD} \committeeMember{Andrew
@@
 \begin{dedication}I would like to dedicate my thesis to my parents,
-Cheng-Tien Tai and Feng-Ming Chang. Thank for your support during
-my Ph.D. study. \end{dedication}
+Cheng-Tien Tai  and Feng-Ming Chang. Thanks for encouraging me to
+study abroad and all your support during my Ph.D. study. \end{dedication}
 
@@
 Thank Elizabeth ``Betsy'' Merceron and Kexin Chen for helping me
-pass TEPAIC exam. \end{acknowledgments}
+pass TEPAIC exam.
+
+Finally, thank Jin-Ru Yang for handling my hand and leading me here,
+and hope I could be with you to wherever place until the death separating
+us apart eventually.\end{acknowledgments}
 \begin{abstract}

### 2018-04-06 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Update ZIP code...

@@
 \affiliation{Department of Computer Science, Indiana University, Bloomington,
-Indiana 47405, USA}
+Indiana 47408, USA}
 
@@
 \affiliation{Department of Informatics, Indiana University, Bloomington,
-Indiana 47405, USA}
+Indiana 47408, USA}
 

### 2018-04-06 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 
-Before diving into quantum computing, it is instructive to review
-two kinds of classical computers: digital and analog. Although discrete
-digital computers could be modeled by various computational models,
-including Turing machines~\cite{Turing_1937}, these models are essentially
-the same by the (strong) Church-Turing thesis \cite{Church_1936,Turing_1937,Kleene_1943}.
-Moreover, any Turing-computable function could be carried out by a
-digital computer as long as it has enough resources~\cite{Piccinini2015}.
-In contrast, there are various idealized real computation models \cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
-Although these models are usually more powerful than discrete Turing
-machines, their computational powers might not be realized by realistic
-analog chips and computers, and the realized analog computational
-devices are mostly chips embedded in our digital computers to communicate
-with non-computational analog devices~\cite{Camenzind2005}. Currently
-most of the quantum computing models based on the continuum of real
-numbers. Similar to the development classical computers, the computational
-power of realistic quantum computers might not be the same as predicted
-by current quantum computing models. When developing realistic quantum
-computers or estimating the computational powers of realistic quantum
-computers, it might also be helpful to study discrete quantum computing
-models.
-
-Despite the history of computation, when replacing the continuum of
-complex and real numbers by the discrete finite fields and finite
-number of intervals, we show how a number of subtle properties of
-quantum computing can be teased apart, step by step, as we explore
-the implications of \emph{discrete quantum theories} in a systematic
-fashion. In particular, on different discrete quantum theories, we
-will present how geometrical structure of states and quantum probability
-could be, and how these mathematical structures affect the power of
-discrete quantum computing.
+This marriage of quantum mechanics and computer science first envisioned
+and popularized by Feynman has created an awkward, but opportune,
+moment. The embarrassing dilemma was concisely described by Aaronson
+with the following three statements \cite{AaronsonArkhipov2011,BFRDARW2013}:
+\begin{enumerate}[label=(\roman{enumi})]
+\item \label{enu:Textbook-quantum-mechanics}Textbook quantum mechanics
+is correct. 
+\item \label{enu:no-efficient-classical-factoring}There does not exist
+an efficient classical factoring algorithm. 
+\item \label{enu:extended-Church-Turing-Thesis}The extended Church-Turing
+thesis — that probabilistic Turing machines can efficiently simulate
+any physically realizable model of computation — is correct \cite{BernsteinVazirani1997,Kaye2007}. 
+\end{enumerate}
+There is overwhelming evidence to support each of these statements.
+The theoretical framework of quantum mechanics \ref{enu:Textbook-quantum-mechanics}
+has withstood decades of experimental confirmation. Entire industries
+are founded on the assumption \ref{enu:no-efficient-classical-factoring}
+that algorithms like RSA are secure and they also have withstood years
+of attempted attacks \cite{boneh1999twenty,wiki:RSAFactoring}. Finally
+the entire field of complexity theory in computer science which has
+also withstood years of field testing rests, in essence, on assumption
+\ref{enu:extended-Church-Turing-Thesis} \cite{Aaronson2005,Piccinini2015}.
+And yet at least one of these three statements \emph{must be false}!
+Indeed if there is a corresponding efficient classical factoring algorithm,
+then we concede \ref{enu:no-efficient-classical-factoring}. If it
+is correct Shor's efficient factoring algorithm is realizable, and
+we can prove there is no efficient classical factoring algorithm,
+we concede \ref{enu:extended-Church-Turing-Thesis}. Otherwise, if
+we cannot implement Shor's algorithm no matter how hard we try, textbook
+quantum mechanics, i.e., \ref{enu:Textbook-quantum-mechanics} may
+need to be improved by a better theory. It is unlikely that there
+will be a simple resolution to this awkward situation. It is more
+likely that the resolution will emerge from deep and careful analyses
+of the foundations of each field.
+
+analog computing and probabilistic computing
+
+In common practice, randomized algorithms are approximated using a
+pseudorandom number generator in place of a true source of random
+bits; such an implementation may deviate from the expected theoretical
+behavior~\cite{wiki:RandomizedAlgorithm}.
 

### 2018-04-09 dissertation.tex
CV_thesis.pdf Fix typos...
dissertation.lyx acknowledgments Updates...

@@
 
+Thank Hao-Chun Lee and Hsien-Ching Kao for discussing what I did in
+the prospective of a general Ph.D. in Physics, and working later in
+more computational industry.
+
 Finally, thank Jin-Ru Yang for handling my hand and leading me here,
@@
 
-In common practice, randomized algorithms are approximated using a
-pseudorandom number generator in place of a true source of random
-bits; such an implementation may deviate from the expected theoretical
-behavior~\cite{wiki:RandomizedAlgorithm}.
-
 \chapter{Conventional Quantum Theory}

### 2018-04-09 dissertation.tex
dissertation.lyx Chapter 1 Introduction Updating...

@@
 
-analog computing and probabilistic computing
+When we check the compatibility between quantum mechanics and computer
+science, we found their fundamental assumptions are different. On
+one hand, quantum mechanics is based on infinitely precise real and
+complex numbers. On the other hand, current computers perform discrete
+computation most of the time, except some analog chips communicating
+with physical world~\cite{Camenzind2005}. While analog chips in
+theory could manipulate infinitely precise real numbers, their computability
+in practice is far weaker than the prediction of real computation
+\cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
+One of the reason behind this gap is that our measurement precision
+is always finite, and the same reason might also limit the computability
+of a realistic quantum computer. To understand these problems, we
+tried two different approaches. We first tried to build discrete quantum
+theories and computing by considering quantum theories and computing
+over finite fields in Chapter~\ref{chap:DQT=000026DQC}. We then
+tried to incorporate the idea of finite precision measurement with
+quantum theories in Chapter~\ref{chap:QIVPM}.
 

### 2018-04-10 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

--- 2018-04-09 dissertation.tex
@@
 \begin{acknowledgments}Thank Prof. Gerardo Ortiz, Prof. Amr Sabry,
-and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
+and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
 with me, and enormous other things. These papers become the main part
@@
 Chapter~\ref{chap:DQT=000026DQC} is based on ``Quantum Interval-Valued
-Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2017}.
+Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2018}.
 Together with Prof. Dylan Thurston and Prof. Shouhong Wang, thank
@@
 
-analog computing and probabilistic computing
+When we check the compatibility between quantum mechanics and computer
+science, we found their fundamental assumptions are different. On
+one hand, the quantum theory is based on infinitely precise real and
+complex numbers. Although its predicting ability to quantum phenomenon
+is limited by measurement precision, it can well describe the physical
+reality together with error analysis. On the other hand, current computers
+perform digital computation most of the time, except some analog chips
+communicating with physical world~\cite{Camenzind2005}. While the
+computability of digital parts is faithfully characterized by its
+theoretical model, the Turing machine~\cite{Turing_1937}, the computability
+of analog chips in reality is far weaker than the theoretical prediction
+of real computation \cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
+One of the reason behind this gap is that our measurement precision
+is always finite, and some of the difference cannot be compensated
+by error analysis technique. All these problems for classical computation
+could potentially apply to quantum computation. To address these issues,
+we tried to develop two different types of quantum theories and computing.
+Since classical discrete computing model faithfully represents digital
+computers, we first tried to build discrete quantum theories and computing
+by considering quantum theories and computing over finite fields in
+Chapter~\ref{chap:DQT=000026DQC}. In order to , We then tried to
+incorporate the idea of finite precision measurement with quantum
+theories in Chapter~\ref{chap:QIVPM}.
 

### 2018-04-11 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 one hand, the quantum theory is based on infinitely precise real and
-complex numbers. Although its predicting ability to quantum phenomenon
-is limited by measurement precision, it can well describe the physical
-reality together with error analysis. On the other hand, current computers
-perform digital computation most of the time, except some analog chips
-communicating with physical world~\cite{Camenzind2005}. While the
-computability of digital parts is faithfully characterized by its
-theoretical model, the Turing machine~\cite{Turing_1937}, the computability
-of analog chips in reality is far weaker than the theoretical prediction
-of real computation \cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
-One of the reason behind this gap is that our measurement precision
-is always finite, and some of the difference cannot be compensated
-by error analysis technique. All these problems for classical computation
-could potentially apply to quantum computation. To address these issues,
-we tried to develop two different types of quantum theories and computing.
-Since classical discrete computing model faithfully represents digital
-computers, we first tried to build discrete quantum theories and computing
-by considering quantum theories and computing over finite fields in
-Chapter~\ref{chap:DQT=000026DQC}. In order to , We then tried to
-incorporate the idea of finite precision measurement with quantum
-theories in Chapter~\ref{chap:QIVPM}.
-
-\chapter{Conventional Quantum Theory}
+complex numbers. Its prediction could fit the physical reality by
+utilizing error analysis technique although these prediction cannot
+be completely faithful because of the measurement precision. On the
+other hand, current computers mostly perform digital computation,
+except some analog chips communicating with physical world~\cite{Camenzind2005}.
+While the computability of digital parts is faithfully characterized
+by its theoretical model, the Turing machine~\cite{Turing_1937},
+the computability of analog chips in reality is far weaker than the
+theoretical prediction of real computation \cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
+One of the reason behind this gap is also due to measurement precision,
+and some of their computability difference cannot be compensated by
+error analysis technique. All these problems for classical computation
+could potentially apply to quantum computation. Because we are agnostic
+about whether the physical reality is ultimately discrete or continuous,
+we tried to develop two different types of quantum theories and computing
+models to address these issues. Since the discrete classical computing
+model faithfully represents digital computers, we first tried to build
+discrete quantum theories and computing by considering quantum theories
+and computing over finite fields in Chapter~\ref{chap:DQT=000026DQC}.
+Since error analysis technique cannot always compensate the inevitable
+problem of measurement precision, we then incorporate the idea of
+finite precision measurement into the quantum theory in Chapter~\ref{chap:QIVPM},
+and hope it could describe the physical reality and computability
+more faithful.
+
+\chapter{Conventional Quantum Theory and Computing}
 

### 2018-04-12 dissertation.tex
dissertation.lyx Frontmatter Updating...

@@
 Cheng-Tien Tai  and Feng-Ming Chang. Thanks for encouraging me to
-study abroad and all your support during my Ph.D. study. \end{dedication}
+study abroad and all your support during my Ph.D. study. \todo{Find
+a way to include my parent's Chinese name. If I can find a way, also
+include Amr's Arabic name.}\end{dedication}
 
@@
 and ``Discrete quantum theories'' (DQT)~\cite{DQT2014}; most of
-Chapter~\ref{chap:DQT=000026DQC} is based on ``Quantum Interval-Valued
+Chapter~\ref{chap:QIVPM} is based on ``Quantum Interval-Valued
 Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2018}.
@@
 
-Finally, thank Jin-Ru Yang for handling my hand and leading me here,
+Finally, thank Jin-Ru Yang for holding my hand and leading me here,
 and hope I could be with you to wherever place until the death separating

### 2018-04-12 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Added...

--- 2018-04-10 dissertation.tex
@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[twoside]{iuphd}
+\documentclass[english]{article}
 \usepackage[T1,T2A]{fontenc}
 \usepackage[utf8]{inputenc}
-\setcounter{secnumdepth}{3}
-\setcounter{tocdepth}{3}
 \usepackage{verbatim}
-\usepackage{mathrsfs}
-\usepackage{enumitem}
-\usepackage{pdfpages}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage[all]{xy}
 
 \makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-\newlength{\lyxlabelwidth}      % auxiliary length
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
@@
 \ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
-\DeclareUnicodeCharacter{0229}{\c{e}}
-\DeclareUnicodeCharacter{00A0}{~}
-\usepackage{mmap}
-\usepackage{comment}
-\usepackage{framed}
-\usepackage[braket,qm]{qcircuit}
-\usepackage{mathrsfs}
-\usepackage{setspace}
-\usepackage{dsfont}
 
-\usepackage[all]{xy}
-\newcommand{\xyR}[1]{\xymatrixrowsep={#1}}
-\newcommand{\xyC}[1]{\xymatrixcolsep={#1}}
-
-%\usepackage[basic]{complexity}
-\newcommand{\lang}[1]{{\ensuremath{\mathsf{#1}}}}
-\newcommand{\newlang}[2]{\newcommand{#1}{\lang{#2}}}
-\newlang{\usat}{UNIQUE-SAT}
-
-\usepackage{amsthm}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\newcommand{\muB}{\ensuremath{\mu^{B}}}
-\newcommand{\events}{\ensuremath{\mathcal{E}}}
-\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
-\newcommand{\gmult}{*}
-\newcommand{\Fpx}[1]{\mathbb{F}_{{#1}}}
-\newcommand{\Fp}{\Fpx{p}}
-\newcommand{\Fppx}[1]{\Fpx{{#1}^2}}
-\newcommand{\Fpp}{\Fppx{p}}
-\newcommand{\Fq}{\Fpx{q}}
-\newcommand{\ff}[1]{\Fpx{#1}}
-\newcommand{\ffzx}[2]{\Fpx{#1}^{{#2}\;*}}
-\newcommand{\ffx}[2]{\Fpx{#1}^{{#2}}}
-\newcommand{\ffzd}[1]{\ffzx{#1}{d}}
-\newcommand{\ffd}[1]{\ffx{#1}{d}}
-\newcommand{\VVec}[1]{\vec{\bf #1}}
-\newcommand{\mathReal}{\mathbb{R}}
-\newcommand{\mathComplex}{\mathbb{C}}
-\newcommand{\braket}[2]{\ip{#1}{#2}}
-\newcommand{\todo}[1]{\textbf{TODO.~#1}}
-\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
-\newcommand{\Sphere}[1]{\mathbf{S}^{#1}}
-\newcommand{\R}{\mathReal}
-\newcommand{\rme}{\mathrm{e}}
-\newcommand{\rmi}{\mathrm{i}}
-\newcommand{\CP}[1]{\mathComplex\mathbf{P}^{#1}}  % Complex projective space
-\newcommand{\DCP}[1]{\mathbf{D}\mathComplex\mathbf{P}^{#1}} % Discrete complex projective
-\def\fh{\mathfrak{h}}
-\newcommand{\uf}{U_{\!f}}
-\newcommand{\scalarPlus}{+}
-\newcommand{\boolt}{\textsf{Bool}} 
-\newcommand{\bfalse}{\texttt{\textbf{false}}}
-\newcommand{\btrue}{\texttt{\textbf{true}}}
-\newcommand{\dotprod}{dot product}
-\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
-\newcommand{\fnorm}[1]{\mathsf{N}\left({#1}\right)}
-
-\department{Department of Mathematics}
-\department{Department of Computer Science}
-
-\@ifundefined{showcaptionsetup}{}{%
- \PassOptionsToPackage{caption=false}{subfig}}
-\usepackage{subfig}
 \makeatother
 
+\usepackage{babel}
 \begin{document}
-%data for Title Page
 
-\title{Discrete Quantum Theories and Computing}
-
-\author{Yu-Tsung Tai}
-
-\date{\today}
+\title{Publicity Outreach for ``Quantum interval-valued probability: Contextuality
+and the Born rule''}
 
 \maketitle
-%data for Acceptance Page
-\committeeMember{Amr A. Sabry , PhD} \committeeMember{Gerardo
-Ortiz, PhD} \committeeMember{Dylan Paul Thurston, PhD} \committeeMember{Andrew
-J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{Defense
-Date} \acceptancepage
+Randomness is used in cryptography, randomized algorithms, and gambling...
+etc. However, it is impossible to test randomness directly~\cite{Shi2015}.
+While some people believed quantumness implies randomness, to prove
+randomness of quantum theory is to prove that quantum theory cannot
+be simulated by any deterministic hidden variable theory. Although
+the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}
+theorems exclude non-local and non-contextuality deterministic hidden
+variable theories.
 
-%data for Copyright Page
-\cryear{2018}
-\copyrightpage
-
-\begin{dedication}I would like to dedicate my thesis to my parents,
-Cheng-Tien Tai  and Feng-Ming Chang. Thanks for encouraging me to
-study abroad and all your support during my Ph.D. study. \end{dedication}
-
-\begin{acknowledgments}Thank Prof. Gerardo Ortiz, Prof. Amr Sabry,
-and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
-with me, and enormous other things. These papers become the main part
-of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
-is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
-and ``Discrete quantum theories'' (DQT)~\cite{DQT2014}; most of
-Chapter~\ref{chap:DQT=000026DQC} is based on ``Quantum Interval-Valued
-Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2018}.
-Together with Prof. Dylan Thurston and Prof. Shouhong Wang, thank
-you for getting together to understand what I did and passing my dissertation
-proposal Spring 2017. Also, thank Prof. Dylan Thurston for serving
-in my advisory committee and my Tier 3 committee, with other advisory
-committee members passing my Computer Science qualifying exam Spring
-2016. Especially, my survey of real computation in the qualifying
-exam inspires me the comparison of quantum computer and analog computer
-in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
-also contains the motivation in my application for Rethinking Foundations
-of Physics 2017 workshop reviewed by Prof. Amr Sabry. Thank Prof.
-Lawrence Moss for inviting me to present our results in the interdisciplinary
-logic seminar and SICE theory seminar, co-chairing my Tier 3 committee,
-writing an assessment letter for me, and drawing my attention on Prof.
-Abramsky's paper~\cite{Abramsky2012}, which inspired me to merge
-quantum probability with discrete quantum theories. Thank John Gardiner
-for inspiring discussion on the difficulties merging them~\cite{Gardiner2014}.
-These results are improved and motivated the transition from DQT to
-QIVPM in Sec.~\ref{sec:Toward-IVPM}. Thank Prof. Tom Lewis for helping
-me organize the unpublished deterministic quantum algorithms in the
-term paper for SLST-T501 Academic Writing course as presented in Sec.~\ref{discretequantumtheoryI}.
-Thank Traci Nagle for going through the literature review about finite
-precision measurement and contextuality discussed for CSCI-Y790 Writing
-and Editing course as presented in Sec.~\ref{sec:Quantum-Contextuality}.
-
-Thank Elizabeth ``Betsy'' Merceron and Kexin Chen for helping me
-pass TEPAIC exam.
-
-Thank Hao-Chun Lee and Hsien-Ching Kao for discussing what I did in
-the prospective of a general Ph.D. in Physics, and working later in
-more computational industry.
-
-Finally, thank Jin-Ru Yang for handling my hand and leading me here,
-and hope I could be with you to wherever place until the death separating
-us apart eventually.\end{acknowledgments}
-\begin{abstract}
-Our primary research interest is to build a quantum computing model
-characterizing realistic quantum computers. While most of the quantum
-computing models based on uncomputable numbers, that is, the continuum
-of real numbers, most of the classical computers in our daily life
-are digital instead of analog computers. This highlight the necessity
-to investigate discrete models for quantum theory and computing. Specifically,
-we start from replacing the continuum of complex numbers by the discrete
-finite fields. Although we have fruitful results on their geometric
-implications and computing powers, their probability models are still
-not completely satisfactory. To address this issue, we further exploited
-quantum interval-valued probability, and proved an imprecise version
-of foundational results such as the Gleason and Kochen-Specker theorems.
-\end{abstract}
-\tableofcontents{}
-
-\chapter{Introduction\label{chap:Introduction}}
-
-This marriage of quantum mechanics and computer science first envisioned
-and popularized by Feynman has created an awkward, but opportune,
-moment. The embarrassing dilemma was concisely described by Aaronson
-with the following three statements \cite{AaronsonArkhipov2011,BFRDARW2013}:
-\begin{enumerate}[label=(\roman{enumi})]
-\item \label{enu:Textbook-quantum-mechanics}Textbook quantum mechanics
-is correct. 
-\item \label{enu:no-efficient-classical-factoring}There does not exist
-an efficient classical factoring algorithm. 
-\item \label{enu:extended-Church-Turing-Thesis}The extended Church-Turing
-thesis — that probabilistic Turing machines can efficiently simulate
-any physically realizable model of computation — is correct \cite{BernsteinVazirani1997,Kaye2007}. 
-\end{enumerate}
-There is overwhelming evidence to support each of these statements.
-The theoretical framework of quantum mechanics \ref{enu:Textbook-quantum-mechanics}
-has withstood decades of experimental confirmation. Entire industries
-are founded on the assumption \ref{enu:no-efficient-classical-factoring}
-that algorithms like RSA are secure and they also have withstood years
-of attempted attacks \cite{boneh1999twenty,wiki:RSAFactoring}. Finally
-the entire field of complexity theory in computer science which has
-also withstood years of field testing rests, in essence, on assumption
-\ref{enu:extended-Church-Turing-Thesis} \cite{Aaronson2005,Piccinini2015}.
-And yet at least one of these three statements \emph{must be false}!
-Indeed if there is a corresponding efficient classical factoring algorithm,
-then we concede \ref{enu:no-efficient-classical-factoring}. If it
-is correct Shor's efficient factoring algorithm is realizable, and
-we can prove there is no efficient classical factoring algorithm,
-we concede \ref{enu:extended-Church-Turing-Thesis}. Otherwise, if
-we cannot implement Shor's algorithm no matter how hard we try, textbook
-quantum mechanics, i.e., \ref{enu:Textbook-quantum-mechanics} may
-need to be improved by a better theory. It is unlikely that there
-will be a simple resolution to this awkward situation. It is more
-likely that the resolution will emerge from deep and careful analyses
-of the foundations of each field.
-
-When we check the compatibility between quantum mechanics and computer
-science, we found their fundamental assumptions are different. On
-one hand, the quantum theory is based on infinitely precise real and
-complex numbers. Although its predicting ability to quantum phenomenon
-is limited by measurement precision, it can well describe the physical
-reality together with error analysis. On the other hand, current computers
-perform digital computation most of the time, except some analog chips
-communicating with physical world~\cite{Camenzind2005}. While the
-computability of digital parts is faithfully characterized by its
-theoretical model, the Turing machine~\cite{Turing_1937}, the computability
-of analog chips in reality is far weaker than the theoretical prediction
-of real computation \cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
-One of the reason behind this gap is that our measurement precision
-is always finite, and some of the difference cannot be compensated
-by error analysis technique. All these problems for classical computation
-could potentially apply to quantum computation. To address these issues,
-we tried to develop two different types of quantum theories and computing.
-Since classical discrete computing model faithfully represents digital
-computers, we first tried to build discrete quantum theories and computing
-by considering quantum theories and computing over finite fields in
-Chapter~\ref{chap:DQT=000026DQC}. In order to , We then tried to
-incorporate the idea of finite precision measurement with quantum
-theories in Chapter~\ref{chap:QIVPM}.
-
-\chapter{Conventional Quantum Theory}
-
-The part of conventional quantum theory (CQT) used by quantum circuit
-model is described by the following:
-\begin{enumerate}[label=(\roman{enumi})]
-\item \label{enu:-orthonormal-basis}$D$ orthonormal basis vectors for
-a Hilbert space of dimension~$D$, 
-\item \label{enu:probability-amplitude}the normalized $D$ complex probability
-amplitude coefficients describing the contribution of each basis vector, 
-\item \label{enu:unitary-matrix}a set of probability-conserving unitary
-matrix operators that suffice to describe all required state transformations
-of a quantum circuit, 
-\item \label{enu:measurement-framework}and a measurement framework. 
-\end{enumerate}
-In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the discrete geometric
-issues raised by the properties \ref{enu:-orthonormal-basis} and
-\ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:Quantum-Circuit-Model},
-we address the property~\ref{enu:unitary-matrix} by describing product
-and entangled $n$-qubit states and unitary matrices in quantum circuit
-model. In Sec.~\ref{sec:fuzzy}, we introduce the important issues
-of \ref{enu:measurement-framework} and the foundations of quantum
-probability space.
-
-\section{Geometrical Structure of States\label{CQC1qubitBloch.sec}}
-
-There are many things that are assumed in CQT, such as the absence
-of zero norm states for non-zero vectors, and the decomposition of
-complex amplitudes into a pair of ordinary real numbers. One also
-typically assumes the existence of a $D$-dimensional Hilbert space
-with an orthonormal basis, allowing us to write \textit{pure} states
-in general as Hilbert space vectors with an Hermitian inner product:
-\begin{eqnarray}
-\ket{\Psi} & = & \sum_{i=0}^{D-1}\alpha_{i}\ket{i}\,.
-\end{eqnarray}
-Here $\alpha_{i}\in\mathComplex$ are complex probability amplitudes,
-$\VVec{\alpha}\in\mathComplex^{D}$, and the $\{\ket{i}\}$ is an
-orthonormal basis of states obeying $\braket{i}{k}=\delta_{ik}$.
-
-The meaning of this is that any state $\ket{\Phi}=\sum_{i=0}^{D-1}\beta_{i}\ket{i}$
-can be projected onto another state $\ket{\Psi}$ by writing 
-\begin{eqnarray}
-\braket{\Phi}{\Psi} & = & \sum_{i=0}^{D-1}\beta_{i}^{*}\alpha_{i}\,,
-\end{eqnarray}
-thus quantifying the proximity of the two states. (Here $^{*}$ denotes
-complex conjugation.) This is one of many properties we take for granted
-in continuum quantum mechanics that challenge us in defining a discrete
-quantum geometry. To facilitate the transition to DQT carried out
-in later sections, we concern ourselves first with the properties
-of the simplest possible abstract state object in CQT, the single
-qubit state.
-
-\subsection{Two-dimensional Hilbert Space}
-
-A state in a two-dimensional Hilbert space, known as a qubit, already
-provides access to a wealth of geometric information and context.
-When we write the single qubit state as $\ket{\psi_{1}}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$,
-a convenience for computing probability and relative state properties
-is the normalization condition 
-\begin{equation}
-\left\Vert \psi_{1}\right\Vert ^{2}=\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=\alpha_{0}^{*}\alpha_{0}+\alpha_{1}^{*}\alpha_{1}=1\,,\label{A2.eq}
-\end{equation}
-which identifies $\alpha_{0}$ and $\alpha_{1}\in\mathbb{C}$ as probability
-amplitudes and implies the conservation of probability in the closed
-world spanned by $\left\{ \ket{0},\ket{1}\right\} $. Note that we
-distinguish for future use the \textit{norm}~$\left\Vert \cdot\right\Vert $
-of a vector from the \textit{modulus}~$\left|\cdot\right|$ of a
-complex number. Continuing, we see that if we want only the irreducible
-state descriptions, we must supplement the process of computing \Eq{A2.eq}
-by finding a way to remove the distinction between states that differ
-only by an overall phase transformation $\rme^{\rmi\theta}$, that
-is, $\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$ and $\rme^{\rmi\theta}\alpha_{0}\ket{0}+\rme^{\rmi\theta}\alpha_{1}\ket{1}$
-are representing the same physical state. This can be accomplished
-by the Hopf fibration \cite{Artin1991,Hatcher2001,MosseriDandoloff2001,Hanson2006,Bengtsson2007,wiki:HopfFibration},
-which can be written down as follows: let $\alpha_{0}=x_{0}+\rmi y_{0}$
-and $\alpha_{1}=x_{1}+\rmi y_{1}$. Then \Eq{A2.eq} becomes the
-condition that the four real variables describing a qubit denote a
-point on the three-sphere $\Sphere{3}$ (a 3-manifold) embedded in
-$\R^{4}$: 
-\begin{equation}
-{x_{0}}^{2}+{y_{0}}^{2}+{x_{1}}^{2}+{y_{1}}^{2}=1\,.\label{A5.eq}
-\end{equation}
-
-We can reduce 3 degrees of freedom in \Eq{A5.eq} to 2 degrees of
-freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
-out by the circle $\Sphere{1}$''). The standard form of this maps
-(``the Hopf fibration'') is 
-\begin{eqnarray}
-X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
-Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{eq:HopfFibration}\\
-Z & = & \left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
-\end{eqnarray}
-By denoting the three-dimensional vector~$\left(X,Y,Z\right)$ as
-$\Hat{a}$, \Eq{A5.eq} implies these transformed coordinates obeying
-\begin{equation}
-\left\Vert \Hat{a}\right\Vert ^{2}=X^{2}+Y^{2}+Z^{2}=\left(\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}\right)^{2}=1\label{A7.eq}
-\end{equation}
-and therefore have only two remaining degrees of freedom describing
-all possible distinct one-qubit quantum states. In Fig.~\ref{hopfFibers.fig},
-we illustrate schematically the family of circles \textit{each one
-of which is collapsed to a point}~$\left(\phi,\psi\right)$ on the
-surface $X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
-
-\begin{figure}[tb]
-\hfill{}\subfloat[]{\centering{}\includegraphics[width=0.48\columnwidth]{hopfS2}}\hfill{}\subfloat[]{\begin{centering}
-\includegraphics[width=0.48\columnwidth]{hopfFibers}
-\par\end{centering}
-}\hfill{} \caption{(a) The two-sphere~$\Sphere{2}$ represented by \Eq{A7.eq}, which
-is the irreducible space of one-qubit states, along with a representative
-set of points on the sphere. Each single point on the sphere in (a)
-corresponding to a circle in (b), and a whole family of circles (the
-paths of $\rme^{\rmi\theta}$) on the three-sphere~$\Sphere{3}$
-represents the Hopf fibration, Eq.~(\ref{eq:HopfFibration}). Although
-$\Sphere{3}$ cannot be directly embedded in $\R^{3}$, three-sphere~$\Sphere{3}$
-can be regarded as attaching two three-dimensional ball on two sides
-of two-sphere~$\Sphere{2}$. In this way, each circle in $\Sphere{3}$
-can be represented as a circle in the three-dimensional ball as shown
-in (b). Moreover, points in (a) are color coded corresponding to circles
-in (b), e.g., one pole contains the red elliptical circle that would
-become an infinite-radius circle by a slightly different way to represent
-$\Sphere{3}$ in $\R^{3}$, and the opposite pole corresponds to the
-large perfectly round red circle at the equator.}
-\label{hopfFibers.fig} 
-\end{figure}
-
-The resulting manifold is the two-sphere $\Sphere{2}$ (a 2-manifold)
-embedded in $\R^{3}$. If we choose one of many possible coordinate
-systems describing $\Sphere{3}$ via \Eq{A5.eq} such as 
-\begin{equation}
-\left(x_{0},y_{0},x_{1},y_{1}\right)=\left(\cos\left(\theta+\phi\right)\cos\psi,\,\sin\left(\theta+\phi\right)\cos\psi,\,\cos\left(\theta-\phi\right)\sin\psi,\,\sin\left(\theta-\phi\right)\sin\psi\right)\,,\label{A8a.eq}
-\end{equation}
-where %% $0\leq \theta \leq 2 \pi$,  $-\pi \leq \phi \leq  \pi$, 
-$0\leq\psi\leq\frac{\pi}{2}$, with $0\leq\theta+\phi<2\pi$ and $0\leq\theta-\phi<2\pi$,
-we see that 
-\begin{equation}
-\left(X,Y,Z\right)=\left(\cos\left(2\phi\right)\sin\left(2\psi\right),\,\sin\left(2\phi\right)\sin\left(2\psi\right),\,\cos\left(2\psi\right)\right)\,.\label{A8b.eq}
-\end{equation}
-Thus the one-qubit state is independent of $\theta$, and we can choose
-$\theta=\phi$ without loss of generality, reducing the form of the
-unique one-qubit states to $\ket{\psi_{1}}=\rme^{2\rmi\phi}\cos\psi\ket{0}+\sin\psi\ket{1}$,
-and an irreducible state can be represented as a point on a sphere
-called the Bloch sphere, as shown in Fig.~\ref{blochSphere.fig}(a).
-
-\begin{figure}[tb]
-\begin{centering}
-\hfill{}\subfloat[]{\centering{}\includegraphics[width=0.47\columnwidth]{blochSphere}}\hfill{}\subfloat[]{\begin{centering}
-\includegraphics[width=0.47\columnwidth]{blochSphereArc}
-\par\end{centering}
-}\hfill{}
-\par\end{centering}
-\caption{(a) The conventional Bloch sphere with a unique state represented
-by the point at the red sphere. (b) The geodesic shortest-distance
-arc connecting two one-qubit quantum states.}
-\label{blochSphere.fig} 
-\end{figure}
-
-Thus the geometry of a single qubit reduces to transformations among
-points on $\Sphere{2}$, which can be parametrized in an infinite
-one-parameter family of transformations, one of which is the geodesic
-or minimal-length transformation. Explicitly, given two one-qubit
-states denoted by points $\Hat{a}$ and $\Hat{b}$ on $\Sphere{2}$,
-the shortest rotation carrying $\Hat{a}$ to $\Hat{b}$ is the SLERP
-(spherical linear interpolation) \cite{Shoemake:1985:ARQ:325334.325242,wiki:Slerp}
-\begin{equation}
-S\left(\Hat{a},\Hat{b},t\right)=\Hat{a}\,\frac{\sin((1-t)\omega)}{\sin\omega}\,+\,\Hat{b}\,\frac{\sin(t\omega)}{\sin\omega}\,,\label{slerp.eq}
-\end{equation}
-where $\Hat{a}\cdot\Hat{b}=\cos\omega$. Figure \ref{blochSphere.fig}(b)
-illustrates the path traced by a SLERP between two irreducible one-qubit
-states on the Bloch sphere. Because states in CQC are defined by infinite
-precision real numbers, it is not possible, even in principle, to
-make an exact state transition as implied by Fig.~\ref{blochSphere.fig}(b).
-In practice, one has to be content with approximate, typically exponentially
-expensive, transitions from state to state.
-
-\subsection{$D$-dimensional Hilbert Space}
-
-The irreducible states in a $D$-dimensional Hilbert space are encoded
-in a similar family of geometric structures known technically as the
-complex projective space $\CP{D-1}$. We obtain these structures starting
-with the $D$ initially unnormalized complex coefficients of the $D$-dimensional
-basis $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$. We then follow
-the analog of the two-dimensional procedure: Conservation of probability
-requires that the norm of the vector $\VVec{\alpha}$ be normalized
-to unity: 
-\begin{equation}
-\braket{\Psi}{\Psi}=\|\VVec{\alpha}\|^{2}=\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=1\,.\label{probEq1.eq}
-\end{equation}
-Thus the initial equation for the geometry of a quantum state describes
-a \textit{topological sphere~}$\Sphere{2D-1}$ embedded in $\mathReal^{2D}$.
-To see this, remember that we can write the real and imaginary parts
-of $\alpha_{i}$ as $\alpha_{i}=x_{i}+\rmi y_{i}$, so 
-\begin{equation}
-\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=\sum_{i=0}^{D-1}{x_{i}}^{2}+{y_{i}}^{2}=1
-\end{equation}
-describes the locus of a $2D$-dimensional real unit vector in $\mathReal^{2D}$,
-which is by definition $\Sphere{2D-1}$, the $(2D-1)$-sphere.
-
-This $\Sphere{2D-1}$ in turn is ambiguous up to the usual overall
-phase, inducing an $\Sphere{1}$ symmetry action, and identifying
-$\Sphere{2D-1}$ as an $\Sphere{1}$ bundle, whose base space is the
-$(D-1)$-complex-dimensional projective space $\CP{D-1}$. There are
-thus $2D-2$ irreducible real degrees of freedom ($D-1$ complex degrees
-of freedom) for a quantum state with a $D$-dimensional basis, $\set{\ket{i}}{i=0,\ldots,D-1}$.
-
-In summary, the full space of a $D$-dimensional quantum state, including
-its overall phase defining its relationship to other quantum states,
-is the topological space $\Sphere{2D-1}$. For an isolated system,
-the overall phase is not measurable, and eliminating the phase dependence
-in turn corresponds to identifying $\Sphere{2D-1}$ as a circle bundle
-over the base space $\CP{D-1}$, and therefore $\CP{D-1}$ defines
-the $2D-2$ intrinsic, irreducible, degrees of freedom of the isolated
-$D$-dimensional state's dynamics. In mathematical notation, this
-would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$\todo{Citation?}.
-For $D=2$, the single qubit, we have $2-1=1$, and the base space
-of the circle bundle is $\CP{1}=\Sphere{2}$, the usual Bloch sphere.
-Note that only for $D=2$ is this actually a sphere-like geometry
-due to an accident of low-dimensional topology.
-
-\subsection{Explicit generalization of the Hopf fibration construction}
-
-For a two-dimensional system, we could easily solve the problem of
-reducing the full unit-norm space to its irreducible components $\Hat{a}=\left(X,Y,Z\right)$
-characterizing the Bloch sphere. We have just argued that essentially
-the same process is possible for $D$-dimensional system: in the abstract
-argument, we simply identify the family of coefficients $\left\{ \alpha_{i}\right\} $
-as being the same if they differ only by an overall phase $\rme^{\rmi\theta}$.
-However, in practice this is not a construction that is easy to realize
-in a practical computation. We now outline an explicit algorithm for
-accomplishing the reduction to the irreducible $D$-dimensional state
-space $\CP{D-1}$; this construction will turn out to be useful for
-the validation of our discrete results to follow below.
-
-Given a normalized pure state $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$,
-a natural quantity characterizing an $D$-dimensional system is its
-\textit{density matrix}, $\rho=\op{\Psi}{\Psi}$, or 
-\begin{equation}
-\rho=\begin{pmatrix}|\alpha_{0}|^{2} & \alpha_{0}\alpha_{1}^{*} & \cdots & \alpha_{0}\alpha_{D-1}^{*}\\
-\alpha_{1}\alpha_{0}^{*} & |\alpha_{1}|^{2} & \cdots & \alpha_{1}\alpha_{D-1}^{*}\\
-\vdots & \vdots & \ddots & \vdots\\
-\alpha_{D-1}\alpha_{0}^{*} & \cdots & \alpha_{D-1}\alpha_{D-2}^{*} & |\alpha_{D-1}|^{2}
-\end{pmatrix}\,.\label{nqDensity.eq}
-\end{equation}
-We can now use the complex generalization of the classical Veronese
-coordinate system for projective geometry to remove the overall phase
-ambiguity $\rme^{\rmi\theta}$ from the $D$-dimensional states. If
-we take a particular weighting of the elements of the density matrix~$\rho$,
-we can construct a \textit{unit vector} of real dimension $D^{2}$
-with the form: 
-\begin{equation}
-\Hat{a}=\left(|\alpha_{i}|^{2},\ldots,\sqrt{2}\,\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\,\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\right)\,,\label{nqCoords.eq}
-\end{equation}
-where 
-\begin{equation}
-\Hat{a}\cdot\Hat{a}=\sum_{i=0}^{D-1}\left(\left|\alpha_{i}\right|^{2}\right)^{2}+\sum_{i=0}^{D-1}\sum_{\substack{j=0\\
-j\ne i
-}
-}^{D-1}\left(\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}+\left(\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)\left(\sum_{j=0}^{D-1}\left|\alpha_{j}\right|^{2}\right)=1\,.
-\end{equation}
-This construction gives an explicit embedding of the $\left(D-1\right)$-dimensional
-complex, or $\left(2D-2\right)$-dimensional real, object in a real
-space of dimension $D^{2}$. However, this is somewhat subtle because
-the vector is of unit length, so technically the embedding space is
-a sphere of dimension $D^{2}-1$ embedded in $\R^{D^{2}}$. For example,
-the two-dimensional irreducible states could be represented in a four-dimensional
-embedding, but the magnitude of every coordinate would be one; furthermore,
-the object embedded in the resulting $\Sphere{3}$ is indeed $\Sphere{2}$
-because we can fix one complex coordinate to be unity, and let one
-vary, giving a total of two irreducible dimensions. In fact one must
-choose \textit{two} coordinate patches, one covering one pole of $\Sphere{2}$
-with coordinates $\alpha_{0}=1+\rmi0$ and $\alpha_{1}=x_{1}+\rmi y_{1}$,
-and the other patch covering the other pole of $\Sphere{2}$ with
-coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=1+\rmi0$.
-\todo{Explain the last part more clear or add a picture.}
-
-We finally see that the irreducible $D$-dimensional state space $\CP{D-1}$
-is described by $D$ projectively equivalent coordinates, one of which
-can always be scaled out to leave $(D-1)$ actual (complex) degrees
-of freedom. We must choose, in turn, $D$ different local sets of
-complex variables defined by taking the value $\alpha_{k}=1$, with
-$k=0,\ldots,D-1$, and allowing the remaining $D-1$ complex (or $2D-2$
-real) variables to run free. No single set of coordinates will work,
-since the submanifold including $\alpha_{k}=0$ is undefined and another
-coordinate system must be chosen to cover that coordinate patch. This
-is a standard feature of the topology of non-trivial manifolds such
-as $\CP{D-1}$ (see any textbook on geometry~\cite{Berger_1988}).
-
-\section{Quantum Circuit Model\label{sec:Quantum-Circuit-Model}}
-
-\begin{comment}
-An $n$-qubit pure state in the conventional quantum theory (CQT)
-is represented as a vector in the $2^{n}$-dimensional Hilbert space.
-If we eliminate all symmetries, an irreducible state is actually a
-point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
-also known as the complex projective space~$\CP{2^{n}-1}$ \cite{Hatcher2001,Bengtsson2007}.
-These irreducible quantum states can also be classified as product
-states and entangled states, and the latter one plays the essential
-role for pure-state algorithms \cite{Mermin2007,Jaeger2007}.
-\end{comment}
-It has been 36 years since Feynman~\cite{Feynman1982Simulating}
-proposed the idea about quantum computation. Although there are many
-models for quantum computing, the circuit model is still one of the
-most widespread models~\cite{544199} no matter whether in theoretical
-study or in building a real quantum computer. Information in a quantum
-circuit is stored in qubits. Each qubit is a two-dimensional quantum
-system. For a two-qubit system, if the first and second qubit are
-described as the state~$\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$
-and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}$, the state of
-the whole system is their tensor product 
-\begin{equation}
-\begin{aligned} & \ket{\psi}\ket{\phi}=\ket{\psi}\otimes\ket{\phi}=\left(\alpha_{0}\ket{0}+\alpha_{1}\ket{1}\right)\otimes\left(\beta_{0}\ket{0}+\beta_{1}\ket{1}\right)\\
-={} & \alpha_{0}\beta_{0}\ket{0}\otimes\ket{0}+\alpha_{0}\beta_{1}\ket{0}\otimes\ket{1}+\alpha_{1}\beta_{0}\ket{1}\otimes\ket{0}+\alpha_{1}\beta_{1}\ket{1}\otimes\ket{1}\\
-={} & \alpha_{0}\beta_{0}\ket{0}\ket{0}+\alpha_{0}\beta_{1}\ket{0}\ket{1}+\alpha_{1}\beta_{0}\ket{1}\ket{0}+\alpha_{1}\beta_{1}\ket{1}\ket{1}
-\end{aligned}
-\end{equation}
-in the four-dimensional Hilbert space. For a $n$-qubit system, if
-we describe the $j$-th qubit as the state~$\ket{\psi_{j}}$, the
-state of the whole system is tensor product of all subsystems 
-\begin{equation}
-\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}=\ket{\psi_{1}}\cdots\ket{\psi_{j}}\cdots\ket{\psi_{n}}
-\end{equation}
-in the Hilbert space of dimension $D=2^{n}$. However, not all quantum
-system can be expressed as the tensor product of its subsystems. This
-kind of system is called entangled, and will be described in the next
-section.\todo{This paragraph need to be polished.}
-
-\subsection{The geometry of entanglement}
-
-\todo{Need to define (partial) trace and mixed state before this
-subsection...}
-
-Entanglement may be regarded as one of the main characteristics distinguishing
-quantum from classical mechanics. Entanglement involves quantum correlations
-such that the measurement outcomes in one subsystem are related to
-the measurement outcomes in another one. Within the standard framework,
-given a quantum system composed of $n$ qubit subsystems, a pure state
-of the total system $\ket{\Psi}$ is said to be entangled if it cannot
-be written as a product of states of each subsystem. That is, a state
-$\ket{\Psi}$ is entangled if $\ket{\Psi}\ne\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$,
-where $\ket{\psi_{j}}$ refers to an arbitrary state of the $j$-th
-qubit, and $\otimes$ represents the tensor product. This is equivalent
-to saying that if one calculates the reduced density operator $\rho_{j}$
-of the $j$-th subsystem by tracing out all the other subsystems,
-$\rho_{j}=\Tr_{\{1,\cdots,j-1,j+1,\cdots,n\}}\left(\rho\right)$,
-with $j=1,\cdots,n$ and $\rho=\op{\Psi}{\Psi}$, the normalized state~$\ket{\Psi}$
-is entangled if and only if at least one subsystem state is \textit{mixed};
-i.e., $\Tr_{j}\left(\rho_{j}^{2}\right)<1$. For example, consider
-\begin{equation}
-\rho_{j}=\frac{1}{2}\left(\sigma_{0}+\sum\limits _{\mu=x,y,z}\expval{\sigma_{\mu}^{j}}\sigma_{\mu}^{j}\right)\,,
-\end{equation}
-where $\sigma_{\mu}^{j}$, $\mu=x,y,z$, are the Pauli operators acting
-on the $j$-th spin~\cite{544199}, 
-\begin{equation}
-\sigma_{\mu}^{j}=\overbrace{\sigma_{0}\otimes\cdots\otimes\sigma_{0}\otimes\underbrace{\sigma_{\mu}}_{j^{\textrm{th}}\textrm{ factors}}\otimes\sigma_{0}\otimes\cdots\otimes\sigma_{0}}^{n\textrm{ factors}}\,,\label{pauli3}
-\end{equation}
-with 
-\begin{align}
-\sigma_{0} & =\left(\begin{array}{cc}
-1 & 0\\
-0 & 1
-\end{array}\right)\,, & \sigma_{x} & =\left(\begin{array}{cc}
-0 & 1\\
-1 & 0
-\end{array}\right)\,, & \sigma_{y} & =\left(\begin{array}{cc}
-0 & -\rmi\\
-\rmi & 0
-\end{array}\right)\,, & \sigma_{z} & =\left(\begin{array}{cc}
-1 & 0\\
-0 & -1
-\end{array}\right)\,,
-\end{align}
-and $\expval{\sigma_{\mu}^{j}}=\melem{\Psi}{\sigma_{\mu}^{j}}{\Psi}$
-denotes the corresponding expectation value. The vectors 
-\begin{equation}
-{\bf X}_{j}=\left(\expval{\sigma_{x}^{j}},\expval{\sigma_{y}^{j}},\expval{\sigma_{y}^{j}}\right)\in\mathbb{R}^{3}
-\end{equation}
-allow a geometric representation of each reduced state in $\mathbb{R}^{3}$,
-satisfying $0\le\left\Vert {\bf X}_{j}\right\Vert \le1$. Since $\Tr_{j}\left(\rho_{j}^{2}\right)=\frac{1}{2}\left(1+\left\Vert {\bf X}_{j}\right\Vert ^{2}\right)$,
-the state $\ket{\Psi}$ is entangled if $\left\Vert {\bf X}_{j}\right\Vert <1$
-for at least one $j$, represented by a point \emph{inside} the corresponding
-local Bloch sphere. One may therefore consider $\ket{\Psi}$ to be
-maximally entangled if $\left\Vert {\bf X}_{j}\right\Vert =0$ for
-all $j$. On the other hand, the state $\ket{\Psi}$ is unentangled
-(i.e., a product state) if $\left\Vert {\bf X}_{j}\right\Vert =1$
-for all $j$, corresponding to points lying on the surface of the
-Bloch sphere.
-
-A natural geometric measure of multipartite entanglement is obtained
-by defining the \emph{purity of a state relative to a set of observables}
-\cite{BKOV2003,BKOSV2004}. If the set is chosen to be the set of
-\emph{all local observables}, i.e., corresponding to each of the subsystems
-that compose the actual system, one recovers the standard notion of
-entanglement for multipartite systems. For example, if the system
-consists of $n$ qubits, we obtain a measure of conventional entanglement
-by calculating the purity relative to the set $\fh=\left\{ \sigma_{x}^{1},\sigma_{y}^{1},\sigma_{z}^{1},\ldots,\sigma_{x}^{n},\sigma_{y}^{n},\sigma_{z}^{n}\right\} $,
-\begin{align}
-P_{\fh} & =\frac{1}{n}\sum\limits _{j=1}^{n}\sum\limits _{\mu=x,y,z}\expval{\sigma_{\mu}^{j}}^{2}\,, & 0\leq P_{\fh}\leq1\,.\label{purityMeasure.eq}
-\end{align}
-Since $\fh$ is a semi-simple Lie algebra, its generalized unentangled
-states are the generalized coherent states obtained by applying any
-group operation to a reference state such as $\ket{\overline{0}}=\ket{0}\otimes\cdots\otimes\ket{0}$.
-For the algebra $\fh$ of local observables, such group operations
-are simply local rotations on each qubit. In other words, the group
-orbit describing the generalized coherent states of $\fh$ comprises
-all the product states of the form $\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{n}}$,
-which have maximum purity (i.e., $P_{\fh}=1$). Other states such
-as the Greenberger-Horne-Zeilinger state $\ket{\Psi}=\ket{\mathsf{GHZ}_{n}}=\frac{1}{\sqrt{2}}\left(\ket{0}\otimes\cdots\otimes\ket{0}+\ket{1}\otimes\cdots\otimes\ket{1}\right)$
-are (maximally) entangled relative to the set of local observables
-(i.e., $P_{\fh}=0$).
-
-Different entanglement measures are obtained when a set $\fh$ different
-from the local observables is chosen. An obvious example, in particular,
-is given by the set of all observables. In this case, the purity takes
-its maximum value independently of the pure quantum state \cite{BKOV2003,BKOSV2004},
-expressing the fact that any state is a generalized coherent state
-of the Lie algebra of all observables.
-
-\subsection{Quantum Circuits\label{subsec:Quantum-Circuits}}
-
-\todo{Further explain $\sigma_{\mu}^{j}$ used as a quantum circuit,
-control not, the Deutsch quantum black box~\cite{544199}, and maybe
-Deutsch Algorithm...}
-
-\section{Quantum Probability\label{sec:fuzzy}}
-
-Given a pure state~$\ket{\phi}$, when we measure an observable represented
-by an Hermitian matrix~$\mathbf{O}$, the measurement result is one
-of the eigenvalues of $\mathbf{O}$. The probability of getting a
-particular eigenvalue~$\lambda$ is $\melem{\phi}{P}{\phi}$, where
-$P$ is the projection operator onto the eigenspace of $\lambda$.
-This rule of computing the probability is called the Born rule \cite{Born1983,Mermin2007,Jaeger2007},
-which is used when we want to extract information from a quantum computer.
-For any mixed state~$\rho$, the generalized Born rule induces a
-conventional quantum probability measure $\muB_{\rho}:\events\rightarrow[0,1]$,
-where $\events$ is the set of all projection operators on a given
-Hilbert space. Conversely, any quantum probability measure $\mu:\events\rightarrow[0,1]$
-can be induced from a mixed state $\rho$ in the Hilbert space of
-dimension $d\ge3$ according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
-In another word, this state $\rho$ is the unique state consistent
-with any given quantum probability measure.
-
-\section{Quantum Contextuality\label{sec:Quantum-Contextuality}}
-
-\todo{Explain enough background knowledge to support the discussion
-about contextuality in the end of Sec.~\ref{modalquantum}. I have
-typed some literature review in writing course, but I need to decide
-whether it could be used or not before finish Sec.~\ref{sec:fuzzy}.}
-
-\chapter{Quantum Theories and Computing over Finite Fields\label{chap:DQT=000026DQC}}
-
-\section{Fundamentals of Finite Fields\label{sec:background}}
-
-\subsection{Background}
-
-A field~$\mathbb{F}$ is an algebraic structure consisting of a set
-of elements equipped with the operations of addition, subtraction,
-multiplication, and division \cite{fieldtheory.ref,numtheory.ref}.
-Fields may contain an infinite or a finite number of elements. The
-rational~$\mathbb{Q}$, real~$\mathbb{R}$, and complex numbers~$\mathbb{C}$
-are examples of infinite fields, while the set $\mathbb{F}_{3}=\{0,1,2\}$,
-under multiplication and addition modulo $3$, is an example of a
-finite field.
-
-There are two distinguished elements in a field, the addition identity
-$0$, and the multiplication identity $1$. Given the field~$\mathbb{F}$,
-the closed operations of addition, ``$+$,'' and multiplication,
-``$\gmult$,'' satisfy the following set of axioms: 
-\begin{enumerate}
-\item $\mathbb{F}$ is an Abelian group under the addition operation~$+$
-(additive group); 
-\item The multiplication operation~$\gmult$ is associative and commutative.
-The field has a multiplicative identity and the property that every
-nonzero element has a multiplicative inverse; 
-\item Distributive laws: For all $a,b,c\in\mathbb{F}$ 
-\begin{eqnarray}
-a\gmult(b+c) & = & a\gmult b+a\gmult c\,,\\
-(b+c)\gmult a & = & b\gmult a+c\gmult a\,.
-\end{eqnarray}
-\end{enumerate}
-\noindent From now on, unless specified, we will omit the symbol~$\gmult$
-whenever we multiply two elements of a field.
-
-Finite fields of $q$ elements, $\Fq=\{0,\ldots,q-1\}$, will play
-a special role in this work. A simple explicit example is $\mathbb{F}_{3}$
-with the following addition and multiplication tables: 
-\begin{align*}
-\begin{array}{c|ccc}
-+ & 0 & 1 & 2\\[0.1in]
-\hline 0 & 0 & 1 & 2\\
-1 & 1 & 2 & 0\\
-2 & 2 & 0 & 1
-\end{array} &  & \begin{array}{c|ccc}
-\gmult & 0 & 1 & 2\\[0.1in]
-\hline 0 & 0 & 0 & 0\\
-1 & 0 & 1 & 2\\
-2 & 0 & 2 & 1
-\end{array}
-\end{align*}
-
-\subsection{Cyclic Properties of Finite Fields}
-
-The characteristic of a field is the least positive integer~$m$
-such that $m=1+1+1+\cdots+1=0$, and if no such $m$ exists we say
-that the field has characteristic zero (which is the case for $\mathbb{R}$
-for example). It turns out that if the characteristic is non-zero,
-it must be a prime~$p$. For every prime~$p$ and positive integer~$r$
-there is a finite field~$\Fpx{p^{r}}$ of size $q=p^{r}$ and characteristic~$p$,
-which is unique up to field isomorphism \cite{Artin1991,DummitFoote2004}.
-The exponent $r$ is known as the \emph{degree} of the field over
-its prime subfield\footnote{ Fields $\ff{q}$ where $q$ is a power of a prime $p$, i.e., $q=p^{r}$,
-are known as Galois fields.}~\cite{GT.ref}. If the characteristic $p$ is an arbitrary prime
-number, we call the field \emph{unrestricted}.
-
-For every $a\in\Fq$, $a\neq0$, then $a^{q-1}=1$, implying the Frobenius
-endomorphism (also a consequence of Fermat's little theorem) $a^{q}=a$,
-which in turn permits us to write the multiplicative inverse of any
-non-zero element in the field as $a^{-1}=a^{q-2}$, since $a^{q-2}a=a^{q-1}=1$.
-Every subfield of the field~$\Fq$, of size $q=p^{r}$, has $p^{r'}$
-elements with some $r'$ dividing $r$, and for a given $r'$ it is
-unique.
-
-\section{Modal Quantum Theory\label{modalquantum}}
-
-Recently, Schumacher and Westmoreland~\cite{Schumacher2012-SCHMQT,SchumacherWestmoreland2010}
-and Chang et al.~\cite{doi:10.1142/S0217984913500644,1751-8121-47-40-405304}
-defined versions of quantum theory over \textit{unrestricted} finite
-fields, which they call modal quantum theories (MQT) or Galois field
-quantum theories. Such theories retain several key quantum characteristics
-including notions of superposition, interference, entanglement, and
-mixed states, along with time evolution using invertible linear operators,
-complementarity of incompatible observables, exclusion of local hidden
-variable theories, impossibility of cloning quantum states, and the
-presence of natural counterparts of quantum information protocols
-such as superdense coding and teleportation. These modal theories
-are obtained by collapsing the Hilbert space structure over the field
-of complex numbers to that of a vector space over an \emph{unrestricted}
-finite field. In the resulting structure, all non-zero vectors represent
-valid quantum states, and the evolution of a closed quantum system
-is described by \emph{arbitrary} invertible linear maps.
-
-Specifically, consider a one-qubit system with basis vectors $\ket{0}$
-and~$\ket{1}$. In conventional quantum theory, there exists an infinite
-number of states for a qubit of the form $\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$,
-with $\alpha_{0}$ and $\alpha_{1}$ elements of the underlying field
-of complex numbers subject to the normalization condition $|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=1$.
-Moving to a finite field immediately limits the set of possible states
-as the coefficients~$\alpha_{0}$ and~$\alpha_{1}$ are now drawn
-from a finite set. In particular, in the field $\ff{2}=\{0,1\}$ of
-booleans, there are exactly four possible vectors: the zero vector,
-the vector~$\ket{0}$, the vector $\ket{1}$, and the vector $\ket{0}+\ket{1}=\ket{+}$.
-Since the zero vector is considered non-physical, a one-qubit system
-can be in one of only three states. The dynamics of these one-qubit
-states is realized by any invertible linear map, i.e., by any linear
-map that is guaranteed never to produce the zero vector from a valid
-state. There are exactly $6$ such maps, and their matrix representation
-with respect to the standard basis are:
-\begin{subequations}\label{eq:MQT-dynamics}
-\begin{align}
-\sigma_{0} & =\begin{pmatrix}1 & 0\\
-0 & 1
-\end{pmatrix}\,, & S & =\begin{pmatrix}1 & 0\\
-1 & 1
-\end{pmatrix}\,, &  & \begin{pmatrix}0 & 1\\
-1 & 1
-\end{pmatrix}\,,\\
-\sigma_{x} & =\begin{pmatrix}0 & 1\\
-1 & 0
-\end{pmatrix}\,, & S^{\dagger} & =\begin{pmatrix}1 & 1\\
-0 & 1
-\end{pmatrix}\,, &  & \begin{pmatrix}1 & 1\\
-1 & 0
-\end{pmatrix}\,.
-\end{align}
-\end{subequations}
-
-For example, 
-\begin{align}
-S\ket{0} & =\begin{pmatrix}1 & 0\\
-1 & 1
-\end{pmatrix}\begin{pmatrix}1\\
-0
-\end{pmatrix}=\begin{pmatrix}1\\
-1
-\end{pmatrix}=\ket{+}\,, & S\ket{+} & =\begin{pmatrix}1 & 0\\
-1 & 1
-\end{pmatrix}\begin{pmatrix}1\\
-1
-\end{pmatrix}=\begin{pmatrix}1\\
-0
-\end{pmatrix}=\ket{0}\,.\label{eq:MQT-dynamics-apply}
-\end{align}
-This set of maps is clearly quite impoverished compared to the full
-set of one-qubit unitary maps in conventional quantum theory. In particular,
-it does not include the Hadamard transformation. However, this set
-also includes non-unitary maps such as $S$ and $S^{\dagger}$ that
-are not allowed in conventional quantum computation.
-
-Measurement in the standard basis is fairly straightforward: measuring
-$\ket{0}$ or $\ket{1}$ deterministically produces the same state
-while measuring $\ket{+}$ nondeterministically produces $\ket{0}$
-or $\ket{1}$ with no assigned probability distribution. When measuring
-an arbitrary state~$\ket{\phi}\in\left\{ \ket{0},\ket{1},\ket{+}\right\} $
-in other bases $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} $,
-we first represents $\ket{\phi}$ as the linear combination of the
-basis vectors $\beta_{0}\ket{\psi_{0}}+\beta_{1}\ket{\psi_{1}}$,
-where $\beta_{0}$ and $\beta_{1}$ are elements in the field~$\ff{2}$.
-If $\beta_{i}$ is zero, measuring $\ket{\phi}$ is impossible to
-produce $\ket{\psi_{i}}$; otherwise, measuring $\ket{\phi}$ is possible
-to produce $\ket{\psi_{i}}$. Since only possibility and impossibility
-is predicted by the theory, modal quantum theories are named after
-these “modal” concepts.
-
-Notice that the measurement process is complicated by the fact that
-the possibility to produce a basis vector~$\ket{\psi_{i}}$ depending
-on the measurement basis. For example, measuring $\ket{+}$ is possible
-to produce $\ket{0}$ in the standard basis $\left\{ \ket{0},\ket{1}\right\} $
-but is impossible to produce $\ket{0}$ in another basis $\left\{ \ket{+},\ket{0}\right\} $.
-In contrast, when measuring a state~$\ket{\phi}$ in CQT, the probability
-to produce a basis vector~$\ket{\psi_{i}}$ is completely determined
-by $\ket{\psi_{i}}$ and $\ket{\phi}$ no matter $\ket{\psi_{i}}$
-is in which measurement basis. This phenomena of the measurement basis
-dependence in CQT only exists when discussing quantum contextuality.
-Despite this kind of ``supercontextuality'' of MQT, its computational
-model, modal quantum computing (MQC), having ``supernatural'' computational
-power is also far from conventional quantum computing as we will describe
-next.
-
-\section{Modal Quantum Computing\label{modalquantumcomputing}}
-
-To understand the computational implications of the modal quantum
-theory defined over the field $\ff{2}$ of booleans, we developed
-a quantum computing model and established its correspondence to a
-classical model of logical programming with a feature that has quantum-like
-behavior~\cite{finiteQC}. In a conventional logic program, answers
-produced by different execution paths are collected in a sequence
-with \emph{no} interference. However, in this modal quantum computing
-model over $\ff{2}$, these answers may interfere destructively with
-one another.
-
-Our computations with this ``toy'' modal quantum theory showed that
-it possesses ``supernatural'' computational power. For example,
-one can solve a black box version of the \usat\ problem~\cite{usat}
-in a way that outperforms conventional quantum computing. The classical
-\usat\ problem (also known as $\lang{USAT}$ or $\lang{UNAMBIGUOUS-SAT}$\todo{Add
-citation about where these two names come from.}) is the problem
-of deciding whether a given boolean formula has a satisfying assignment,
-assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
-This problem is, in a precise sense~\cite{Valiant198685}, just as
-hard as the general satisfiability problem and hence all problems
-in the~NP complexity class. Our black-box version of the \usat\ problem
-replaces the boolean formula with an arbitrary black box. Solutions
-to this generalized problem can be used to solve an unstructured database
-search of size $N$ using $O\left(\log N\right)$ black box evaluations
-by binary search on the database. This algorithm then outperforms
-the known asymptotic bound $O\left(\sqrt{N}\right)$ for unstructured
-database search in conventional quantum computing.
-
-\begin{figure}[t]
-\[
-\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \gate{~S^{\dagger}~} & \ctrl{3} & \gate{~S^{\dagger}~} & \multimeasureD{3}{\text{measure}}\\
-\lstick{x_{1}=\ket{0}} & \multigate{2}{\otimes S} & \ghost{\uf} & \multigate{2}{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
-\lstick{\ldots} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
-\lstick{x_{n}=\ket{0}} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}
-}
-\]
-\caption{\label{fig:alg}Circuit for black box \usat\ in modal quantum theory
-over the field $\ff{2}$. For further notation see text.}
-\end{figure}
-
-We can prove the unreasonable power of the arbitrary-function \usat\ starting
-with a classical function $f:\boolt^{n}\rightarrow\boolt$ that takes
-$n$ bits and returns at most one \btrue\ result. To build a quantum
-algorithm, $f$ is first represented as the Deutsch quantum black
-box~$\uf$ with \cite{Deutsch1985,544199} 
-\begin{equation}
-\uf\ket{y}\ket{\overline{x}}=\begin{cases}
-\ket{y}\ket{\overline{x}}\,, & \textrm{if }f\left(\overline{x}\right)=\bfalse\,;\\
-\ket{\mathsf{not}\left(y\right)}\ket{\overline{x}}\,, & \textrm{if }f\left(\overline{x}\right)=\btrue\,,
-\end{cases}
-\end{equation}
-where $\overline{x}$ denotes a sequence $x_{1},x_{2},\ldots,x_{n}$
-of $n$ bits and $0$ and $1$ are identified as $\bfalse$ and $\btrue$,
-respectively. Then, we can give an algorithm (see Fig.~\ref{fig:alg})
-taking as input such a classical function that decides, deterministically
-and in a constant number of black box evaluations, whether $f$ is
-satisfiable or not:
-
-\paragraph*{Case I: $f$ is unsatisfiable; the measurement deterministically
-produces $\ket{0}\ket{\overline{0}}$.}
-
-\todo{This part use $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$
-while previous parts use $\ket{\Psi}=\ket{\psi_{1}}\cdots\ket{\psi_{j}}\cdots\ket{\psi_{n}}$.
-Moreover, bar is heavily used in QIVPM discussion later, so maybe
-not using bar here????}The state is initialized to $\ket{0}\ket{\overline{0}}$,
-with $\ket{\overline{0}}=\ket{0}\ket{0}\cdots\ket{0}$, i.e., the
-tensor product of $n$ $\ket{0}$ states. As Eq.~(\ref{eq:MQT-dynamics-apply}),
-applying the map $S$ to each qubit in the second component of the
-state produces $\ket{0}\ket{\overline{+}}$ where $\ket{\overline{+}}$
-denotes the sequence $\ket{+}\ldots\ket{+}$ of length $n$. Applying
-$\uf$ to the entire state has no effect since $U_{f}$ is the identity
-when $f$ is unsatisfiable. Applying $S$ to each qubit in the second
-component of the state produces $\ket{0}\ket{\overline{0}}$. Applying
-$S^{\dagger}$ to the first component leaves the state unchanged.
-As the first component of the state is $0$, applying the map $\sigma_{0}$
-(which is the identity) leaves the state unchanged.\todo{Control-not
-need to be defined and explained in Sec.~\ref{subsec:Quantum-Circuits}}
-Applying $S^{\dagger}$ to the first component leaves the state unchanged.
-Measuring the state will deterministically produce $\ket{0}\ket{\overline{0}}$.
-
-\paragraph*{Case II: $f$ is satisfiable; the measurement produces some state
-other than $\ket{0}\ket{\overline{0}}$.}
-
-Assume the function $f$ is satisfiable at some input $a_{1},a_{2},\ldots,a_{n}$
-denoted $\overline{a}$, and where $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$.
-In the second step, the state becomes $\ket{0}\ket{\overline{+}}$
-as above. We can write this state as $\ket{0}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
-Applying $U_{f}$ produces $\ket{1}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
-We can rewrite this state as $\ket{+}\ket{\overline{a}}+\Sigma_{\overline{x}}\ket{0}\ket{\overline{x}}=\ket{+}\ket{\overline{a}}+\ket{0}\ket{\overline{+}}$,
-where the summation is now over all vectors (notice that $\ket{0}\ket{\overline{a}}+\ket{0}\ket{\overline{a}}$
-is the zero vector). Applying $S$ to each qubit in the second component
-produces $\ket{+}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
-Applying $S^{\dagger}$ to the first component produces: $\ket{1}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
-Applying control-not gate, which applying $\sigma_{0}$ or $\sigma_{x}$
-on the second component depending on the first component of the state,
-and produces 
-\begin{equation}
-\ket{1}\left(\sigma_{x}\ket{\overline{S(a)}}\right)+\ket{0}\left(\sigma_{0}\ket{\overline{0}}\right)=\ket{1}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}\,.
-\end{equation}
-Applying $S^{\dagger}$ to the first component produces $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$.
-For the measurement of $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$
-to be guaranteed to never be $\ket{0}\ket{\overline{0}}$, we need
-to verify that $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}$
-has one occurrence $\ket{0}\ket{\overline{0}}$. \todo{The following
-need to be rewritten.}This can be easily proved as follows. Since
-each $a_{i}$ is either 0 or 1, then each $S(a_{i})$ is either $+$
-or $1$, and hence each $\mathsf{not}\left(S(a_{i})\right)$ is either~$+$
-or~$0$. The result follows since any state with a combination of
-$+$ and $0$, when expressed in the standard basis, would consist
-of a superposition containing the state $\ket{0\ldots}$.
-
-\begin{comment}
-
-\section{Modal Quantum Theory and Computing}
-
-Our first discrete model replaces the complex numbers by a unrestricted
-finite field~$\mathbb{F}_{q}$ \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
-In this model, an $n$-qubit state is a non-zero vector in $\mathbb{F}_{q}^{2^{n}}$.
-When we measure a given state~$\ket{\phi}$, an observable is replaced
-by a basis~$\mathcal{B}$ of $\mathbb{F}_{q}^{2^{n}}$. Since $\ket{\phi}$
-can be represented by the summation across a unique subset~$\mathcal{S}$
-of the basis~$\mathcal{B}$, whether it is possible or impossible
-to measure a basis vector~$\ket{i}$ depends on whether $\ket{i}$
-is in $\mathcal{S}$ or not. Because this model only predicts whether
-a result is possible or impossible, it is called the modal quantum
-theory. Its computational model, called the modal quantum computing,
-is far from conventional quantum computing. Although modal quantum
-computing can express simple algorithms such as quantum teleportation
-\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
-it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
-This quantum theory is, however, also so powerful that it can be used
-to solve an unstructured database search of size $N$ using $O(\log(N))$
-steps, which outperforms the known asymptotic bound $O(\sqrt{N})$
-in conventional quantum computing \cite{Grover:1996:FQM:237814.237866,BennettBernsteinBrassardVazirani1997,Mermin2007,Jaeger2007}.
-\end{comment}
-
-\section{Discrete Quantum Theory (I)\label{discretequantumtheoryI}}
-
-\subsection{Complexified Finite Fields}
-
-Our next objective is to develop more realistic discrete quantum theory
-variants that exclude ``supernatural'' algorithms such as the one
-presented above. Our first such plausible framework~\cite{HOSW2011}
-is based on complexifiable finite fields. To incorporate complex numbers
-for quantum amplitudes, we exploit the fact that the polynomial $x^{2}+1$
-is \emph{irreducible} ($x^{2}+1=0$ has no solution) over a prime
-field $\ff{p}$ with $p$ odd if and only if $p$ is of the form $4\ell+3$,
-with $\ell$ a non-negative integer \cite{Artin1991,DummitFoote2004}.
-For example, given any $x\in\ff{3}=\left\{ 0,\pm1\right\} $, when
-$x=0$, we have $x^{2}+1=0^{2}+1=1$; when $x=\pm1$, we have $x^{2}+1=\left(\pm1\right)^{2}+1=1$.
-Therefore, $x^{2}+1$ is irreducible over $\ff{3}$. In contrast,
-over $\ff{5}$, $2^{2}+1=0$ so that $x^{2}+1$ is reducible.
-
-We achieve our goal by observing that any field $\ff{p}$ with $p=4\ell+3$
-is extensible to a field~$\ff{p^{2}}$ whose elements can be viewed
-as discrete complex numbers with the real and imaginary parts in~$\ff{p}$.
-In a complexified finite field $\Fpp$, the Frobenius automorphism
-that maps $\alpha\in\Fpp$ to $\alpha^{p}\in\Fpp$ acts like complex
-conjugation \cite{Artin1991,grove2002classical,DummitFoote2004}.
-For example, in $\Fppx{3}$, we have $\left(2+\rmi\right)^{3}=8+12\rmi-6-\rmi=2+11\rmi$
-which, in the field, is equal to $2-\rmi$ since $11\equiv-1\pmod{3}$.
-
-We define the \emph{field norm} $\fnorm{\cdot}$ as the map from $a+\rmi b\in\Fpp$
-to $a^{2}+b^{2}\in\Fp$, 
-\begin{equation}
-\fnorm{a+\rmi b}=a^{2}+b^{2}\,.\label{fieldnorm.eq}
-\end{equation}
-We avoid the square root in the discrete field framework because,
-unlike the continuous case, the square root does not always exist.
-
-\subsection{Vector Spaces}
-
-In this section we want to build a theory of discrete vector spaces
-that approximates as closely as possible the features of conventional
-quantum theory. Such a structure would ideally consist of the following:
-(i) a vector space over the field of complex numbers, and (ii) an
-inner product $\ip{\Phi}{\Psi}$ associating to each pair of vectors
-a complex number, and satisfying the following properties: 
-\begin{enumerate}[label=(\Alph{enumi})]
-\item \label{enu:inner-product-complex-conjugate}$\ip{\Phi}{\Psi}$ is
-the complex conjugate of $\ip{\Psi}{\Phi}$; 
-\item \label{enu:inner-product-linear}$\ip{\Phi}{\Psi}$ is conjugate linear
-in its first argument and linear in its second argument; 
-\item \label{enu:inner-product-positive-definite}$\ip{\Psi}{\Psi}$ is
-always non-negative and is equal to~0 only if $\ket{\Psi}$ is the
-zero vector. 
-\end{enumerate}
-It turns out that a vector space defined over a finite field cannot
-have an inner product satisfying the properties above. However, we
-will introduce an Hermitian ``dot product'' satisfying some of those
-properties.
-
-We are interested in the vector space ${\cal H}$ of dimension $D$
-defined over the complexified field $\Fpp$. Let $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$
-and $\ket{\Phi}=\begin{pmatrix}\beta_{0} & \beta_{1} & \ldots & \beta_{D-1}\end{pmatrix}^{T}$
-represent vectors in ${\cal H}$, with numbers $\alpha_{i}$ and $\beta_{i}$
-drawn from $\Fpp$, and where $\left(\cdot\right)^{T}$ is the transpose.
-
-\begin{definition}[Hermitian dot product] Given vectors $\ket{\Phi}$
-and $\ket{\Psi}\in{\cal H}$, it can be shown~\cite{grove2002classical}
-the Hermitian dot product is always reducible to the form 
-\begin{equation}
-\ip{\Phi}{\Psi}=\sum_{i=0}^{D-1}\beta_{i}^{p}\alpha_{i}\,.
-\end{equation}
-\end{definition} Two vectors $\ket{\Phi}$ and $\ket{\Psi}\in{\cal H}$
-are said to be orthogonal if $\ip{\Phi}{\Psi}=0$. This product satisfies
-conditions \ref{enu:inner-product-complex-conjugate} and \ref{enu:inner-product-linear}
-for inner products but violates condition \ref{enu:inner-product-positive-definite}
-since in every finite field there always exists a non-zero vector
-$\ket{\Psi}$ such that $\ip{\Psi}{\Psi}=0$. The reason is that addition
-in finite fields eventually ``wraps around'' (because of their cyclic
-or modular structure), allowing the sum of non-zero elements to be
-zero. The fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$
-decreases with the order $p$.
-
-For any vector $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$,
-the Hermitian dot product $\ip{\Psi}{\Psi}$ is equal to $\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}$,
-which is the sum of the field norms for the complex coefficients.
-For convenience, we now extend the field norm to include vector arguments
-by defining 
-\begin{equation}
-\fnorm{\ket{\Psi}}=\ip{\Psi}{\Psi}=\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}\,.\label{fnormD.eq}
-\end{equation}
-The field norm of a vector can vanish for non-vanishing vectors.
-
-\subsection{Irreducible Discrete $D$-dimensional States: Generalized Discrete
-Bloch Sphere\label{DQCnqubitBloch.sec}}
-
-In the one-qubit state with coefficients in $\Fpp$, the discrete
-analog of the Bloch sphere is constructed by exact analogy to the
-continuous case: we first require that the coefficients of the single
-qubit basis obey 
-\begin{equation}
-\|\psi_{1}\|^{2}=|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=1\label{DQA2.eq}
-\end{equation}
-in the discrete field. In \ref{appU.sec}, we show that there are
-$p(p^{2}-1)$ such values.\todo{Check reference...} Given this requirement,
-which is similar in form to the conservation of probability, but not
-as useful due to the lack of orderable probability values, we can
-immediately conclude that the discrete analog of the Hopf fibration
-is again 
-\begin{eqnarray}
-X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
-Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{DQA6.eq}\\
-Z & = & \left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
-\end{eqnarray}
-but now with all computations in $\pmod{p}$. At this point one simply
-writes down all possible discrete values for the complex numbers $\left(\alpha_{0},\alpha_{1}\right)$
-satisfying Eq.~(\ref{DQA2.eq}) and enumerates those that project
-to the same value of $\{X,Y,Z\}$. This equivalence class is the discrete
-analog of the circle in the complex plane that was eliminated in the
-continuous case. In \ref{appH.sec}, we show that $p+1$ discrete
-values of $\{\alpha_{0},\alpha_{1}\}$ with unit norm map to the same
-point under the Hopf map \Eq{DQA6.eq}; we may think of these as
-discrete circles or projective lines of equivalent, physically indistinguishable,
-complex phase. The surviving $p(p-1)$ values of $\{\alpha_{0},\alpha_{1}\}$
-correspond to irreducible physical states of the discrete single qubit
-system. %% Several examples are shown in Figure \ref{bloch.fig}. %%Thus,
-for example, choosing the underlying field to be $\Fppx{3}$, there
-are exactly 6 single-qubit state vectors to populate the Bloch sphere;
-the four equivalent phase-multiples mapping to each of the six points
-on the $\Fppx{3}$ Bloch sphere are collapsed and regarded as physically
-indistinguishable. In Figure \ref{bloch.fig}, we plot the irreducible
-states on the Bloch sphere for $p=3$, $7$, and $11$. Note that
-the Cartesian lengths of the real vectors corresponding to the points
-on the Bloch sphere vary considerably due to the nature of discrete
-fields; we have artificially normalized them to a ``continuous world''
-unit radius sphere for conceptual clarity.
-
-\begin{figure}[htb]
-%\vspace{-0.2in}  %% \includegraphics[width=0.9\columnwidth]{./Bloch_sphere.pdf}%%\includegraphics[width=2.0\columnwidth]{./picA.png}%%\includegraphics[width=2.0\columnwidth]{./picB.png}
-
-\begin{centering}
-\hspace*{-0.5cm}\includegraphics[width=1.1\columnwidth]{\string"../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/picC\string".png}
-%%\includegraphics[width=0.5\textwidth]{./picAB.eps}\vspace{-0.2in}
- %% adjust blank space?
-\par\end{centering}
-\caption{Schematically normalized plots of the elements of the discrete Bloch
-sphere, the irreducible single-qubit (two-dimensional) state vectors
-with unit norm over the field $\Fpp$. We show the results for $p=3$,
-$7$, and $11$. For example, in $\Fppx{3}$, there are 24 vectors
-of unit norm, but only the 6 inequivalent classes appear in the plot.
-The $p+1=4$ equivalent vectors in each class differ only by a complex
-discrete phase.}
-\label{bloch.fig} 
-\end{figure}
-
-\subsection{Counting states on the $n$-qubit Bloch sphere}
-
-We have the unique opportunity in the finite-field approach to quantum
-computing to precisely identify and enumerate the physical states.
-In the conventional theory, as we have seen, we employ a generalized
-Hopf fibration on the normalized states to project out a circle of
-phase-equivalent states, yielding the generalized Bloch sphere.
-
-In the introduction to this section, we sketched the counting of the
-irreducible single-qubit discrete states. To count the number of inequivalent
-discrete states for the general $n$-qubit case with coefficients
-in $\Fpp$, we first must find the set of unit-norm states, and then
-determine the equivalence classes of unit-norm states under discrete
-phase transformations; we can then enumerate the list of states on
-the discrete generalized Bloch sphere. By executing computer searches
-of these spaces, we discovered an hypothesis for a closed-form solution
-for the counting of the states, and were then able to find a rigorous
-inductive proof of the enumeration, which is presented in the Appendix.
-
-This process of describing the discrete $n$-qubit irreducible states
-can again be understood geometrically by following the discrete analog
-of the Hopf fibration. First, we construct the discrete version of
-the quadratic unit-length form that automatically annihilates the
-distinction among states differing only by a discrete phase, 
-\begin{eqnarray}
-\hspace*{-0.5cm}\Hat{a}=(|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots)\ ,
-\end{eqnarray}
-where 
-\begin{eqnarray}
-\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
-\end{eqnarray}
-{}From \ref{appH.sec}, we know that $p+1$ elements of this discrete
-$\Sphere{2\times2^{n}-1}$ structure map to the \textit{same point\/}
-in $\Hat{a}$. Each set of $(p+1)$ redundant points is, geometrically
-speaking, the \textit{discrete Hopf fibration circle\/} living above
-each \textit{irreducible\/} point of the $n$-qubit state description.
-These $p+1$ points are interpretable as the $p$ finite points plus
-the single point at infinity of the projective discrete line (see,
-e.g., \cite{Arnold}).
-
-The next part of this argument is the determination of the unit-norm
-states, effectively the space of allowed discrete partitions of unity;
-we cannot exactly call these ``probability-conserving'' sectors
-of the state coefficients since we do not have a well defined notion
-of probability, but we do have a well-defined notion of partition
-of unity. The tally of unit-norm states is $p^{2^{n}-1}(p^{2^{n}}-1)$
-(see \ref{appU.sec}) compared to the total number $p^{2\times2^{n}}$
-of possible complex integer state vectors that could be chosen. This
-unit-norm state structure is the discrete analog of $\Sphere{2\times2^{n}-1}$.
-
-Finally, we repeat the last step of the $n$-qubit continuous Hopf
-fibration process for discrete $n$-qubit states, eliminating the
-discrete set of $p+1$ equivalent points that map to the same point
-$\Hat{a}$ on the generalized $n$-qubit Bloch sphere. Dividing the
-tally $p^{2^{n}-1}(p^{2^{n}}-1)$ of unit norm states by the $p+1$
-elements of each phase-equivalent discrete circle, we find 
-\[
-\frac{p^{2^{n}-1}(p^{2^{n}}-1)}{p+1}=p^{2^{n}-1}(p-1)\,\prod_{k=1}^{n-1}(p^{2^{k}}+1)
-\]
-as the total count of unique irreducible states in a discrete $n$-qubit
-configuration (see \ref{appI.sec}). The resulting object is precisely
-the discrete version of $\CP{D-1}$, which we might call a \textit{discrete
-complex projective space\/} or $\DCP{D-1}$, where $D=2^{n}$ as
-usual.
-
-\section{Discrete Quantum Computing (I)\label{discretequantumcomputingI}}
-
-Given a complexified finite field $\ff{p^{2}}$ and its Hermitian
-\dotprod\
-(Eq.~\eqref{innerprod}) much of the structure of conventional quantum
-computing can be recovered. For example, the smallest field~$\ff{3^{2}}$
-is already rich enough to express the standard Deutsch-Jozsa~\cite{NCbook}
-algorithm, which requires only normalized versions of vectors or matrices
-with the scalars $0$, $1$, and $-1$. Similarly, other deterministic
-quantum algorithms (algorithms for which we may determine the outcome
-with certainty), such as Simon's and Bernstein-Vazirani, perform as
-desired~\cite{simon}. Algorithms such as Grover's search will not
-work in the usual way because we lack (the notion of) ordered angles
-and probability in general.
-
-\begin{figure}[t]
-\[
-\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \qw & \multimeasureD{3}{\text{measure}}\\
-\lstick{x_{1}=\ket{0}} & \multigate{2}{H} & \ghost{\uf} & \multigate{2}{H} & \ghost{\text{measure}}\\
-\lstick{\ldots} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}\\
-\lstick{x_{n}=\ket{0}} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}
-}
-\]
-\caption[]{Circuit for black box \usat\ in discrete quantum computing.}
-\label{fig:dbsearch} 
-\end{figure}
-
-It is possible, in some situations, to exploit the cyclic behavior
-of the field to creatively cancel probability amplitudes and solve
-problems with what again appears to be ``supernatural'' efficiency.
-We illustrate this behavior with the algorithm in Fig.~\ref{fig:dbsearch},
-which is a variant of the one in Fig.~\ref{fig:alg}. Unlike the
-modal quantum theory algorithm, the new algorithm does not always
-succeed deterministically using a constant number of black box evaluations.
-We can, however, show that supernatural behavior occurs if the characteristic
-$p$ of the field divides $2^{N}-1$. For a database of fixed size
-$N$, matching the conditions becomes less likely as the size of the
-field increases. Nevertheless, for a \textit{given\/} field, it is
-always possible to expand any database with dummy records to satisfy
-the divisibility property. Physically, we are taking advantage of
-additional interference processes that happen because of the possibility
-of ``wrapping around'' due to modular arithmetic. We do not know,
-in general, whether this version of discrete quantum computing actually
-enables the rapid solution of NP-complete problems.
-
-\section{Discrete Quantum Theory and Computing (II)}
-
-Our third model, discrete quantum theory (II)~\cite{DQT2014}, restricts
-states in some local region of $\mathbb{F}_{p^{2}}^{2^{n}}$. Within
-a local region, a notion of inner product and probability could be
-recovered. Its discrete quantum computing can be further applied to
-the deterministic Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007}
-and the probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
-
-\section{Toward Discrete Quantum Probability\label{sec:Toward-IVPM}}
-
-When people tried to define quantum probability over finite fields,
-people tended to treat the original Born rule as an axiom, and tried
-to modify it to get a discrete Born rule \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644,DQT2014,Ellerman2016a}.
-However, any modified Born rule could hardly work on the whole vector
-space, since there is no inner product on the whole vector space over
-finite fields. Instead of treating the Born rule as an axiom, the
-Born rule can actually be deduced from a set of abstract definitions
-and axioms according to Gleason's theorem. Although we might hope
-to deduce a discrete Born rule directly from a similar set of definitions
-and axioms, no discrete Born rule satisfies certain properties motivated
-by Gleason's theorem with infinitely precise real-number probability~\cite{Gardiner2014}.
-Since the state spaces are now discrete and finite, this suggests
-us to consider a discrete Born rule mapping to finite number of intervals
-called interval-valued probability~\cite{JamisonLodwick2004,THOS2017}.
-To adopting the idea of interval-valued probability step-by-step,
-before attempting to study quantum interval-valued probability over
-finite fields, we will first review the classical interval-valued
-probability, and extend it with the conventional quantum theory.
-
-\chapter{Toward a Quantum Measurement Theory with Error: Quantum Interval-Valued
-Probability\label{chap:QIVPM}}
-
-\section{Classical Interval-Valued Probability}
-
-In the classical setting, there are several proposals for ``imprecise
-probabilities'' \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
-Although these proposals differ in some details, they all share the
-fact that the probability $\bar{\mu}(E)$ of an event~$E$ is generalized
-from a single \emph{real number} to an \emph{interval}~$[l,r]$,
-where~$l$ intuitively corresponds to the strength of evidence for
-the event~$E$ and~$1-r$ corresponds to the strength of evidence
-against the same event. Given a sample space~$\Omega$ and a set
-of intervals~$\mathscr{I}$, similar to a classical probability measure
-$\mu:2^{\Omega}\rightarrow\left[0,1\right]$, a classical interval-valued
-probability measure (IVPM) $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
-needs to satisfy some coherent axioms. By satisfying the convexity
-axiom \cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
-Shapley proved that there is always a classical probability measure
-consistent with the classical IVPM~$\bar{\mu}$ \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
-Given any random variable, its expectation value with respect to classical
-probability measures consistent with~$\bar{\mu}$ is consistent with
-its Choquet integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-with respect to $\bar{\mu}$ \cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
-
-\section{Quantum Interval-Valued Probability}
-
-The quantum extension, quantum interval-valued probability measure
-(QIVPM) $\bar{\mu}:\events\rightarrow\mathscr{I}$, is a generalization
-of both classical IVPMs $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
-and conventional quantum probability measures $\mu:\events\rightarrow[0,1]$
-\cite{THOS2017}, because QIVPMs reduce to classical IVPMs when the
-space of quantum events $\events$ is restricted to mutually commuting
-events, and reduces to conventional quantum probability measures when
-mapping to infinitely precise uncountable intervals $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
-While Shapley and Gleason both proved there must be a ``state''
-consistent with any given QIVPM in the reduced cases, in general there
-exists a QIVPM such that no state is consistent with it. However,
-we found a class of QIVPMs such that all QIVPMs in this class are
-consistent with a non-empty ``ball'' of quantum states whose radius
-is defined by the maximal length of the intervals, and recovers the
-original Gleason theorem asymptotically. Similarly, the conventional
-quantum expectation value and the classical Choquet integral are together
-generalized to the quantum interval-valued expectation value. This
-is used to prove an imprecise Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-which suggests a possible resolution of the Meyer-Mermin debate on
-the impact of finite-precision measurement on the Kochen-Specker theorem
-\cite{PhysRevLett.83.3751,Mermin1999}.
-
-\chapter{Further Questions}
-
-When people proved the original Gleason theorem, people usually exploited
-the geometrical structure of real 3-dimensional Hilbert space \cite{gleason1957,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
-Since our finite-precision extension of the Gleason theorem only applies
-on a class of QIVPMs, we might want to ask how to modify these geometrical
-arguments to have a Gleason-type theorem for general QIVPMs. We will
-further study the tensor product structure among QIVPMs which is essential
-for defining product and entangled states, and serves the basis to
-discuss quantum nonlocality~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-and quantum computing with QIVPMs. Finally, we want to improve the
-discrete quantum theories to consider QIVPMs over finite fields in
-future research.
-
-\addcontentsBibliography %
 \begin{comment}
@@
 \printbibliography
-
-% http://latex.org/forum/viewtopic.php?t=7312
-% http://latex.org/forum/viewtopic.php?t=17956
-\addtocontents{toc}{\contentsline{chapter}{Curriculum Vitae}{}}
-\includepdf[pages=-]{CV_thesis} 
 \end{document}

### 2018-04-12 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 etc. However, it is impossible to test randomness directly~\cite{Shi2015}.
-While some people believed quantumness implies randomness, to prove
-randomness of quantum theory is to prove that quantum theory cannot
-be simulated by any deterministic hidden variable theory. Although
+While some people believed quantumness implies randomness~\cite{Shi2015,Yuan2017},
+the randomness of quantum theory cannot be established if we can simulate
+quantum theory by a deterministic hidden variable theory. Although
 the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
 and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}
-theorems exclude non-local and non-contextuality deterministic hidden
-variable theories.
+theorems exclude any non-local and non-contextuality deterministic
+hidden variable theory. However, any physical measurement can only
+be done with finite precision, and Meyer~\cite{PhysRevLett.83.3751}
+claimed that finite-precision measurements invalidate the spirit of
+the Kochen-Specker theorem. In this investigation~\cite{THOS2018},
+we employ an interval-valued framework to establish bounds on the
+validity of the Kochen-Specker theorem in realistic experimental environments.
+In another word, when physical measurements are precise enough, the
+Kochen-Specker theorem remains valid, i.e., quantum theory should
+not be simulated a non-contextuality deterministic hidden variable
+theory. Hence, our results provide additional trust of the randomness
+of quantum theory.
 

### 2018-04-13 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 Randomness is used in cryptography, randomized algorithms, and gambling...
-etc. However, it is impossible to test randomness directly~\cite{Shi2015}.
-While some people believed quantumness implies randomness~\cite{Shi2015,Yuan2017},
+etc.~\cite{PironioAcinMassarEtAl2010,MillerShi2016} However, it
+is impossible to test randomness directly~\cite{Shi2015}. While
+some people believed quantumness implies randomness~\cite{Shi2015,MillerShi2016,Yuan2017},
 the randomness of quantum theory cannot be established if we can simulate

### 2018-04-14 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 is impossible to test randomness directly~\cite{Shi2015}. While
-some people believed quantumness implies randomness~\cite{Shi2015,MillerShi2016,Yuan2017},
+some people believed quantumness implies randomness~\cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
 the randomness of quantum theory cannot be established if we can simulate

### 2018-04-14 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

--- 2018-04-12 revised_prop_letter_publicity.tex
@@
 Randomness is used in cryptography, randomized algorithms, and gambling...
-etc. However, it is impossible to test randomness directly~\cite{Shi2015}.
-While some people believed quantumness implies randomness~\cite{Shi2015,Yuan2017},
-the randomness of quantum theory cannot be established if we can simulate
-quantum theory by a deterministic hidden variable theory. Although
+etc. \cite{PironioAcinMassarEtAl2010,MillerShi2016} However, it is
+impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
+While some people believed quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
+the quantum theory might even be deterministic if it can be simulated
+by a deterministic hidden variable model~\cite{EPR1935}. Although
 the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}
+and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
 theorems exclude any non-local and non-contextuality deterministic
-hidden variable theory. However, any physical measurement can only
+hidden variable model. However, any physical measurement can only
 be done with finite precision, and Meyer~\cite{PhysRevLett.83.3751}
@@
 not be simulated a non-contextuality deterministic hidden variable
-theory. Hence, our results provide additional trust of the randomness
+model. Hence, our results provide additional trust of the randomness
 of quantum theory.

### 2018-04-14 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating....

@@
 theorems exclude any non-local and non-contextuality deterministic
-hidden variable model. However, any physical measurement can only
-be done with finite precision, and Meyer~\cite{PhysRevLett.83.3751}
-claimed that finite-precision measurements invalidate the spirit of
-the Kochen-Specker theorem. In this investigation~\cite{THOS2018},
-we employ an interval-valued framework to establish bounds on the
-validity of the Kochen-Specker theorem in realistic experimental environments.
+hidden variable model, any physical measurement can only be done with
+finite precision, and Meyer~\cite{PhysRevLett.83.3751} claimed that
+finite-precision measurements invalidate the spirit of the Kochen-Specker
+theorem, i.e., quantum theory with finite-precision measurements might
+be non-contextual. In our investigation~\cite{THOS2018}, we employ
+an interval-valued framework to establish bounds on the validity of
+the Kochen-Specker theorem in realistic experimental environments.
 In another word, when physical measurements are precise enough, the
-Kochen-Specker theorem remains valid, i.e., quantum theory should
-not be simulated a non-contextuality deterministic hidden variable
-model. Hence, our results provide additional trust of the randomness
+Kochen-Specker theorem remains valid, i.e., quantum theory remains
+contextual. Hence, our results provide additional trust of the randomness
 of quantum theory.

### 2018-04-15 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 by a deterministic hidden variable model~\cite{EPR1935}. Although
-the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-theorems exclude any non-local and non-contextuality deterministic
-hidden variable model, any physical measurement can only be done with
-finite precision, and Meyer~\cite{PhysRevLett.83.3751} claimed that
-finite-precision measurements invalidate the spirit of the Kochen-Specker
-theorem, i.e., quantum theory with finite-precision measurements might
-be non-contextual. In our investigation~\cite{THOS2018}, we employ
-an interval-valued framework to establish bounds on the validity of
-the Kochen-Specker theorem in realistic experimental environments.
-In another word, when physical measurements are precise enough, the
-Kochen-Specker theorem remains valid, i.e., quantum theory remains
-contextual. Hence, our results provide additional trust of the randomness
-of quantum theory.
+the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum} and
+Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
+theorems respectively exclude any non-local and non-contextuality
+deterministic hidden variable model, Meyer claimed that finite-precision
+measurements invalidate the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751},
+i.e., quantum theory with finite-precision measurements might be non-contextual.
+In our investigation~\cite{THOS2018}, we employ an interval-valued
+framework to establish bounds on the validity of the Kochen-Specker
+theorem in realistic experimental environments. In another word, when
+physical measurements are precise enough, the Kochen-Specker theorem
+remains valid, i.e., quantum theory remains contextual. Hence, our
+results provide additional trust of the randomness of quantum theory.
 

### 2018-04-15 dissertation.tex
prop.bib @Misc{THOS2017} updated to eliminating the version...

@@
 \begin{acknowledgments}Thank Prof. Gerardo Ortiz, Prof. Amr Sabry,
-and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
+and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
 with me, and enormous other things. These papers become the main part
@@
 Chapter~\ref{chap:QIVPM} is based on ``Quantum Interval-Valued
-Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2018}.
+Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2017}.
 Together with Prof. Dylan Thurston and Prof. Shouhong Wang, thank
@@
 
-\section{Quantum Contextuality\label{sec:Quantum-Contextuality}}
+\section{Hidden Variable Model and Quantum Contextuality\label{sec:Quantum-Contextuality}}
 

### 2018-04-15 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 \maketitle
-Randomness is used in cryptography, randomized algorithms, and gambling...
-etc. \cite{PironioAcinMassarEtAl2010,MillerShi2016} However, it is
-impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
+Randomness is used in cryptography, randomized algorithms, and gambling
+\cite{PironioAcinMassarEtAl2010,MillerShi2016}...\ etc. However,
+it is impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
 While some people believed quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
@@
 i.e., quantum theory with finite-precision measurements might be non-contextual.
-In our investigation~\cite{THOS2018}, we employ an interval-valued
+In our investigation~\cite{THOS2017}, we employ an interval-valued
 framework to establish bounds on the validity of the Kochen-Specker

### 2018-04-15 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
-theorems respectively exclude any non-local and non-contextuality
-deterministic hidden variable model, Meyer claimed that finite-precision
-measurements invalidate the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751},
+theorems respectively exclude any local and non-contextuality hidden
+variable model, Meyer claimed that finite-precision measurements invalidate
+the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751},
 i.e., quantum theory with finite-precision measurements might be non-contextual.
@@
 physical measurements are precise enough, the Kochen-Specker theorem
-remains valid, i.e., quantum theory remains contextual. Hence, our
-results provide additional trust of the randomness of quantum theory.
+remains valid, quantum theory remains contextual, and our results
+provide additional trust of the randomness of quantum theory.
 

### 2018-04-15 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 While some people believed quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
-the quantum theory might even be deterministic if it can be simulated
+the quantum theory might even be deterministic if it could be simulated
 by a deterministic hidden variable model~\cite{EPR1935}. Although
@@
 theorems respectively exclude any local and non-contextuality hidden
-variable model, Meyer claimed that finite-precision measurements invalidate
-the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751},
-i.e., quantum theory with finite-precision measurements might be non-contextual.
+variable model for any Hilbert space of dimension $d\ge3$, Meyer
+claimed that finite-precision measurements invalidate the spirit of
+the Kochen-Specker theorem~\cite{PhysRevLett.83.3751}, i.e., quantum
+theory with finite-precision measurements might be non-contextual.
 In our investigation~\cite{THOS2017}, we employ an interval-valued
@@
 theorem in realistic experimental environments. In another word, when
-physical measurements are precise enough, the Kochen-Specker theorem
-remains valid, quantum theory remains contextual, and our results
-provide additional trust of the randomness of quantum theory.
+measurements are precise enough, quantum-mechanical contextuality
+continues to hold, maintaining the Kochen-Specker result, and our
+results provide additional trust of the randomness of quantum theory.
 

### 2018-04-16 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 it is impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
-While some people believed quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
+While some people believe quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
 the quantum theory might even be deterministic if it could be simulated

### 2018-04-16 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 claimed that finite-precision measurements invalidate the spirit of
-the Kochen-Specker theorem~\cite{PhysRevLett.83.3751}, i.e., quantum
-theory with finite-precision measurements might be non-contextual.
-In our investigation~\cite{THOS2017}, we employ an interval-valued
-framework to establish bounds on the validity of the Kochen-Specker
-theorem in realistic experimental environments. In another word, when
-measurements are precise enough, quantum-mechanical contextuality
-continues to hold, maintaining the Kochen-Specker result, and our
-results provide additional trust of the randomness of quantum theory.
+the Kochen-Specker theorem~\cite{PhysRevLett.83.3751}. In our investigation~\cite{THOS2017},
+we employ an interval-valued framework to establish bounds on the
+validity of the Kochen-Specker theorem in realistic experimental environments.
+In another word, when measurements are precise enough, quantum-mechanical
+contextuality continues to hold, maintaining the Kochen-Specker result,
+and our results provide additional trust of the randomness of quantum
+theory.
 

### 2018-04-17 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
-%% LyX 2.2.3 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
-\documentclass[english]{article}
+\documentclass{article}
 \usepackage[T1,T2A]{fontenc}
@@
 
-\usepackage{babel}
+\usepackage[french,main=english]{babel}
 \begin{document}
@@
 by a deterministic hidden variable model~\cite{EPR1935}. Although
-the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum} and
-Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
-theorems respectively exclude any local and non-contextuality hidden
-variable model for any Hilbert space of dimension $d\ge3$, Meyer
-claimed that finite-precision measurements invalidate the spirit of
-the Kochen-Specker theorem~\cite{PhysRevLett.83.3751}. In our investigation~\cite{THOS2017},
-we employ an interval-valued framework to establish bounds on the
-validity of the Kochen-Specker theorem in realistic experimental environments.
-In another word, when measurements are precise enough, quantum-mechanical
-contextuality continues to hold, maintaining the Kochen-Specker result,
-and our results provide additional trust of the randomness of quantum
-theory.
+the Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
+theorem exclude any non-contextuality hidden variable model for any
+Hilbert space of dimension $d\ge3$, Meyer claimed that finite-precision
+measurements invalidate the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751}.
+This claim was countered in the same year by Havlicek et al.~\cite{HKSS1999}
+and Mermin~\cite{Mermin1999} and the debate continues to be an active
+topic of research \cite{Kent1999,SimonBruknerZeilinger2001,Cabello2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+In our investigation~\cite{THOS2017}, we employ an interval-valued
+framework to establish bounds on the validity of the Kochen-Specker
+theorem in realistic experimental environments. In another word, when
+measurements are precise enough, quantum-mechanical contextuality
+continues to hold, the Kochen-Specker theorem maintains, and our results
+provide additional trust of the randomness of quantum theory.
 

### 2018-04-19 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

@@
 \maketitle
-Randomness is used in cryptography, randomized algorithms, and gambling
-\cite{PironioAcinMassarEtAl2010,MillerShi2016}...\ etc. However,
-it is impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
-While some people believe quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
-the quantum theory might even be deterministic if it could be simulated
-by a deterministic hidden variable model~\cite{EPR1935}. Although
-the Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
-theorem exclude any non-contextuality hidden variable model for any
-Hilbert space of dimension $d\ge3$, Meyer claimed that finite-precision
-measurements invalidate the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751}.
-This claim was countered in the same year by Havlicek et al.~\cite{HKSS1999}
-and Mermin~\cite{Mermin1999} and the debate continues to be an active
-topic of research \cite{Kent1999,SimonBruknerZeilinger2001,Cabello2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
-In our investigation~\cite{THOS2017}, we employ an interval-valued
-framework to establish bounds on the validity of the Kochen-Specker
-theorem in realistic experimental environments. In another word, when
-measurements are precise enough, quantum-mechanical contextuality
-continues to hold, the Kochen-Specker theorem maintains, and our results
-provide additional trust of the randomness of quantum theory.
+Randomness is exploited in cryptography, algorithmic complexity, and
+gambling. While quantum physics is associated to randomness, it could
+be causally deterministic if it were simulated by a classical non-contextual
+hidden-variable model. The Kochen-Specker theorem excludes such models.
+However, its main tenet has been questioned because finite-precision
+measurements, i.e. errors in preparation or observation, might invalidate
+its spirit. Our work, by introducing an interval-valued probabilistic
+framework, establishes bounds on the validity of the Kochen-Specker
+theorem in realistic, i.e., error-non-free, experimental environments.
+The conclusion is that a quantum theory of measurement that includes
+errors in the probability outcomes can still provide a valid test
+of contextuality, as long as the error is bounded by a finite amount.
 

### 2018-04-21 dissertation.tex
Keep updating...

@@
-%% LyX 2.2.3 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
@@
 \item \label{enu:extended-Church-Turing-Thesis}The extended Church-Turing
-thesis — that probabilistic Turing machines can efficiently simulate
-any physically realizable model of computation — is correct \cite{BernsteinVazirani1997,Kaye2007}. 
+thesis --- that probabilistic Turing machines can efficiently simulate
+any physically realizable model of computation --- is correct \cite{BernsteinVazirani1997,Kaye2007}. 
 \end{enumerate}
@@
 the Hermitian dot product $\ip{\Psi}{\Psi}$ is equal to $\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}$,
-which is the sum of the field norms for the complex coefficients.
+which is the sum of the field norms for the complex coefficients~\cite{wiki:FieldNorm}.
 For convenience, we now extend the field norm to include vector arguments

### 2018-04-21 revised_prop_letter_publicity.tex
Keep updating...

@@
 \maketitle
-Randomness is exploited in cryptography, algorithmic complexity, and
-gambling. While quantum physics is associated to randomness, it could
-be causally deterministic if it were simulated by a classical non-contextual
-hidden-variable model. The Kochen-Specker theorem excludes such models.
-However, its main tenet has been questioned because finite-precision
-measurements, i.e. errors in preparation or observation, might invalidate
-its spirit. Our work, by introducing an interval-valued probabilistic
-framework, establishes bounds on the validity of the Kochen-Specker
-theorem in realistic, i.e., error-non-free, experimental environments.
-The conclusion is that a quantum theory of measurement that includes
-errors in the probability outcomes can still provide a valid test
-of contextuality, as long as the error is bounded by a finite amount.
+Since randomness is exploited in cryptography, algorithmic complexity,
+and gambling, people are always seeking reliable random sources. Quantum
+physics could provide a reliable random source since it is widely
+believed that the results of quantum measurements have no way to be
+predicted deterministically. More precisely, this fact, called the
+Kochen-Specker theorem, states that quantum physics cannot be simulated
+by a classical non-contextual hidden-variable model. However, its
+main tenet has been questioned because finite-precision measurements,
+i.e., errors in preparation or observation, might invalidate its spirit.
+Our work, by introducing an interval-valued probabilistic framework,
+establishes bounds on the validity of the Kochen-Specker theorem in
+realistic, i.e., error-non-free, experimental environments. The conclusion
+is that a quantum theory of measurement that includes errors in the
+probability outcomes can still be contextuality, as long as the error
+is bounded by a finite amount. This also provides additional trust
+of the randomness of quantum random sources.
 

### 2018-04-24 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updated by me...

@@
 physics could provide a reliable random source since it is widely
-believed that the results of quantum measurements have no way to be
-predicted deterministically. More precisely, this fact, called the
-Kochen-Specker theorem, states that quantum physics cannot be simulated
-by a classical non-contextual hidden-variable model. However, its
-main tenet has been questioned because finite-precision measurements,
-i.e., errors in preparation or observation, might invalidate its spirit.
-Our work, by introducing an interval-valued probabilistic framework,
-establishes bounds on the validity of the Kochen-Specker theorem in
-realistic, i.e., error-non-free, experimental environments. The conclusion
-is that a quantum theory of measurement that includes errors in the
-probability outcomes can still be contextuality, as long as the error
-is bounded by a finite amount. This also provides additional trust
-of the randomness of quantum random sources.
+believed that the results of quantum measurements cannot be predicted
+deterministically. More precisely, this fact, called the Kochen-Specker
+theorem, states that quantum physics cannot be simulated by a classical
+non-contextual hidden-variable model. However, its main tenet has
+been questioned because its spirit might be invalidated by finite-precision
+measurements, i.e., errors in preparation or observation. Our work,
+by introducing an interval-valued probabilistic framework, establishes
+bounds on the validity of the Kochen-Specker theorem in realistic,
+i.e., error-non-free, experimental environments. We found that a quantum
+theory of measurement that includes errors in the probability outcomes
+can still be contextual, as long as the error is bounded by a finite
+amount. This conclusion also provides additional trust of the randomness
+of quantum random sources.
 

### 2018-04-24 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updated by Gerardo...

@@
 Since randomness is exploited in cryptography, algorithmic complexity,
-and gambling, people are always seeking reliable random sources. Quantum
-physics could provide a reliable random source since it is widely
-believed that the results of quantum measurements cannot be predicted
-deterministically. More precisely, this fact, called the Kochen-Specker
-theorem, states that quantum physics cannot be simulated by a classical
-non-contextual hidden-variable model. However, its main tenet has
-been questioned because its spirit might be invalidated by finite-precision
-measurements, i.e., errors in preparation or observation. Our work,
-by introducing an interval-valued probabilistic framework, establishes
-bounds on the validity of the Kochen-Specker theorem in realistic,
-i.e., error-non-free, experimental environments. We found that a quantum
-theory of measurement that includes errors in the probability outcomes
-can still be contextual, as long as the error is bounded by a finite
-amount. This conclusion also provides additional trust of the randomness
-of quantum random sources.
+and gambling, it is desirable to have a reliable source of random
+numbers. Quantum physics could provide such a source since the result
+of a quantum measurement cannot be predicted in a deterministic manner
+and, according to the Kochen and Specker theorem, these measurement
+outcomes cannot be simulated by a classical non-contextual hidden-variable
+model. However, this main tenet has been questioned because of finite-precision
+inaccuracies, i.e., errors in preparation or observation of the measured
+system. Our work, by introducing an interval-valued probabilistic
+framework, establishes bounds on the validity of the Kochen-Specker
+theorem in realistic, i.e., error-non-free, experimental environments.
+We found that a quantum theory of measurement that includes errors
+in the probability outcomes can still be contextual, as long as the
+error is bounded by a finite amount. This conclusion provides additional
+confidence on quantum sources of randomness.
 

### 2018-04-25 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.lyx Clean up according to the changes suggesting to PRA...

@@
 Our definition of QIVPMs is consistent with classical IVPMs in the
-sense that a restriction of QIVPMs to mutually commuting events,
-$\eventsC$, recovers the definition of classical
-IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
-forthcoming thesis by the first author~\cite{TaiThesis2018}. A
-consequence is that known properties of classical IVPMs
-directly hold for QIVPMs when one restricts to mutually commuting
-events, $\eventsC$. In particular, in the classical world, it is
-\emph{impossible} for experiments to result in probabilities that are
-inconsistent with \emph{some} state of the system under consideration,
-i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
-  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
+sense that a restriction of QIVPMs to mutually commuting events, $\eventsC$,
+recovers the definition of classical IVPMs~\citep{JamisonLodwick2004}.
+The proof of this fact is included in the forthcoming thesis by the
+first author~\citep{TaiThesis2018}. A consequence is that known
+properties of classical IVPMs directly hold for QIVPMs when one restricts
+to mutually commuting events, $\eventsC$. In particular, in the classical
+world, it is \emph{impossible} for experiments to result in probabilities
+that are inconsistent with \emph{every} state of the system under
+consideration, i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by Shapley~\citep{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
 proves that a classical IVPM always contains at least one state that
-  is consistent with every event.}. Interestingly, as we show in
-Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
-probabilities associated with some events to be inconsistent with
-\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
-in that case, one cannot guarantee non-empty cores for finite-precision
-attempts at proving Gleason's theorem by extending the Born measure
-$\muB_{\rho}\left(P\right)$ to QIVPMs
-$\bar{\mu}\left(P\right)$. However, if we restrict ourselves to the set
-$\eventsC$ of mutually commuting events, 
-the situation reverts to the classical case in which
-probabilities always determine at least one state.
+is consistent with every event.}. Interestingly, as we show in Sec.~\ref{sec:Gleason}, it is possible
+in the quantum world for the probabilities associated with some events
+to be inconsistent with \emph{any} quantum state, i.e., for the QIVPM
+to have an empty core; in that case, one cannot guarantee non-empty
+cores for finite-precision attempts at proving Gleason's theorem by
+extending the Born measure $\muB_{\rho}\left(P\right)$ to QIVPMs
+$\bar{\mu}\left(P\right)$. However, if we restrict ourselves to the
+set $\eventsC$ of mutually commuting events, the situation reverts
+to the classical case in which probabilities always determine at least
+one state.
 
@@
 Our framework allows us to generalize the above theorem to state that
-for small enough $\delta$, it is impossible to have
-$\delta$-deterministic QIVPMs.
-
-We next prove a main result of this paper which is a stronger
-statement of contextuality that includes the effects of
-finite-precision.  Every QIVPM must map some events to truly uncertain
-intervals, not just ``almost definite intervals.'' The proof requires
-two simple lemmas that we present first.
-
-The first lemma shows a simpler way to prove the convexity
-condition. Recall that the convexity condition for a QIVPM
-$\bar{\mu} : \events \rightarrow \mathscr{I}$ states that for each pair of
-\emph{commuting} projectors~$P$ and~$P'$ with $PP'=P'P$, the following
-equation holds:
+for small enough $\delta$, it is impossible to have $\delta$-deterministic
+QIVPMs, which is a stronger statement of contextuality that includes
+the effects of finite-precision. Every QIVPM must map some events
+to truly uncertain intervals, not just ``almost definite intervals.''
+The proof requires two simple lemmas that we present first.
+
+The first lemma shows a simpler way to prove the convexity condition.
+Recall that the convexity condition for a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
+states that for each pair of \emph{commuting} projectors~$P_{0}$
+and~$P_{1}$ with $P_{0}P_{1}=P_{1}P_{0}$, the following equation
+holds: 
 \begin{equation}
-\bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(P'\right)\,.
+\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
 \end{equation}
 
-\begin{lemma}\label{lemma:verify-convexity}
-  To verify the convexity condition of a QIVPM
-  $\bar{\mu} : \events \rightarrow \mathscr{I}$, it is sufficient to check
-  that:
+\begin{lemma}\label{lemma:verify-convexity} To verify the convexity
+condition of a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, it
+is sufficient to check that: 
 \begin{equation}
-\bar{\mu}\left(P_{0}+P_{1}\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{amr}
+\bar{\mu}\left(P'+P''\right)=\bar{\mu}\left(P'\right)+\bar{\mu}\left(P''\right)\label{amr}
 \end{equation}
- for all orthogonal projectors $P_{0}$ and~$P_{1}$.
-\end{lemma}
-\noindent The proof follows the outline of the proof of the classical
-inclusion-exclusion principle. From the commuting projectors $P$ and
-$P'$, we construct the following three orthogonal projectors: $PP'$,
-$P(\mathbb{1}-P')$, and $(\mathbb{1}-P)P'$. Then we proceed as
-follows:
+for all orthogonal projectors $P'$ and~$P''$. \end{lemma} The
+proof follows the outline of the proof of the classical inclusion-exclusion
+principle. From the commuting projectors $P_{0}$ and $P_{1}$, we
+construct the following three orthogonal projectors: $P_{0}P_{1}$,
+$P_{0}\left(\mathbb{1}-P_{1}\right)$, and $\left(\mathbb{1}-P_{0}\right)P_{1}$.
+Then we proceed as follows:
 \begin{widetext}
+\noindent 
 \begin{equation*} 
 \begin{aligned} 
-\noalign{$\bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right)$}
-\qquad\qquad=~~&\bar{\mu}\left(PP'+P(\mathbb{1}-P')+P'-PP'\right)+\bar{\mu}\left(PP'\right) 
-  & (\mbox{because } P = PP' + P - PP') \\
-=~~& \bar{\mu}\left(P(\mathbb{1}-P')+P'\right)+\bar{\mu}\left(PP'\right) \\
-=~~& \bar{\mu}\left(P(\mathbb{1}-P')+PP'+(\mathbb{1}-P)P'\right)+\bar{\mu}\left(PP'\right) 
-      & (\mbox{because } P' = PP' + P' - PP') \\
-=~~& \bar{\mu}(P(\mathbb{1}-P'))+\bar{\mu}(PP')+\bar{\mu}((\mathbb{1}-P)P')+
-    \bar{\mu}\left(PP'\right) & (\mbox{using Eq.~(\ref{amr}) twice}) \\
-=~~& \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') & (\mbox{using Eq.~(\ref{amr}) twice}) \\
-=~~& \bar{\mu}(P) + \bar{\mu}(P')
+\noalign{$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)$} 
+\qquad\qquad=~~&\bar{\mu}\left(P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
+ & (\mbox{because } P_{0} = P_{0}P_{1} + P_{0} - P_{0}P_{1}) \\ 
+=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) \\ 
+=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
+     & (\mbox{because } P_{1} = P_{0}P_{1} + P_{1} - P_{0}P_{1}) \\ 
+=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1}))+\bar{\mu}(P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1})+ 
+   \bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
+=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1}+P_{0}P_{1}) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
+=~~& \bar{\mu}(P_{0}) + \bar{\mu}(P_{1}) 
 \end{aligned} 
@@
 
-The next lemma relates $\delta$-deterministic QIVPMs with $\delta <
-\frac{1}{3}$ to 0-deterministic QIVPMs.
-
-\begin{lemma}\label{lemma:delta2zero} 
-  From any $\delta$-deterministic
-  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ with
-  $\delta < \frac{1}{3}$, we can construct a $0$-deterministic QIVPM
-  $\bar{\mu}^{D}:\events\rightarrow\left\{
-    \imposs,\necess\right\}$ defined as follows:
+\noindent The next lemma relates $\delta$-deterministic QIVPMs with
+$\delta<\frac{1}{3}$ to 0-deterministic QIVPMs.
+
+\begin{lemma}\label{lemma:delta2zero} From any $\delta$-deterministic
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<\frac{1}{3}$,
+we can construct a $0$-deterministic QIVPM $\bar{\mu}^{D}:\events\rightarrow\left\{ \imposs,\necess\right\} $
+defined as follows: 
 \begin{equation}
@@
 \end{equation}
-\end{lemma}
-\noindent The most important part of the proof is to verify the convexity
-condition for $\bar{\mu}^{D}$. By Lemma~\ref{lemma:verify-convexity}, it is sufficient
-to verify the following equation for orthogonal projectors $P_{0}$
-and~$P_{1}$,
+\end{lemma} The most important part of the proof is to verify the
+convexity condition for $\bar{\mu}^{D}$. By Lemma~\ref{lemma:verify-convexity},
+it is sufficient to verify the following equation for orthogonal projectors
+$P'$ and~$P''$, 
 \begin{equation}
-\bar{\mu}^{D}\left(P_{0}+P_{1}\right)=\bar{\mu}^{D}\left(P_{0}\right)+\bar{\mu}^{D}\left(P_{1}\right)\,, \label{eq:QuantumInterval-valuedProbability-Equal}
+\bar{\mu}^{D}\left(P'+P''\right)=\bar{\mu}^{D}\left(P'\right)+\bar{\mu}^{D}\left(P''\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
 \end{equation}
-for two conditions, which we now examine in detail.
-
-When one of $\bar{\mu}^{D}\left(P_{0}\right)$ and $\bar{\mu}^{D}\left(P_{1}\right)$
-is $\necess$, say $\bar{\mu}^{D}\left(P_{0}\right)=\imposs$
-and $\bar{\mu}^{D}\left(P_{1}\right)=\necess$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
-and $\bar{\mu}\left(P_{1}\right)\subseteq\left[1-\delta,1\right]$ which
-implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1+\delta\right]$.
-Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of $\left[0,1\right]$,
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
-which implies $\bar{\mu}^{D}\left(P_{0}+P_{1}\right)$ is also
-$\necess$, thus satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
-
-When both
-$\bar{\mu}^{D}\left(P_{0}\right)$ and $\bar{\mu}^{D}\left(P_{1}\right)$
-are $\imposs$, we have both $\bar{\mu}\left(P_{0}\right)$ and
-$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
-implies
-$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
+for two cases, which we now examine in detail.
+
+\noindent When one of $\bar{\mu}^{D}\left(P'\right)$ and $\bar{\mu}^{D}\left(P''\right)$
+is $\necess$, say $\bar{\mu}^{D}\left(P'\right)=\imposs$ and $\bar{\mu}^{D}\left(P''\right)=\necess$,
+we have $\bar{\mu}\left(P'\right)\subseteq\left[0,\delta\right]$
+and $\bar{\mu}\left(P''\right)\subseteq\left[1-\delta,1\right]$ which
+implies $\bar{\mu}\left(P'+P''\right)\subseteq\left[1-\delta,1+\delta\right]$.
+Since $\bar{\mu}\left(P'+P''\right)$ is a subset of $\left[0,1\right]$,
+$\bar{\mu}\left(P'+P''\right)$ must be a subset of $\left[1-\delta,1\right]$,
+which implies $\bar{\mu}^{D}\left(P'+P''\right)$ is also $\necess$,
+thus satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
+
+When both $\bar{\mu}^{D}\left(P'\right)$ and $\bar{\mu}^{D}\left(P''\right)$
+are $\imposs$, we have both $\bar{\mu}\left(P'\right)$ and $\bar{\mu}\left(P''\right)\subseteq\left[0,\delta\right]$
+which implies $\bar{\mu}\left(P'+P''\right)\subseteq\left[0,2\delta\right]$.
 Since we assume $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
-$\left[1-\delta,1\right]$ are disjoint, which implies
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ and $\left[1-\delta,1\right]$ are
-disjoint. Together with the fact that
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either
-$\left[0,\delta\right]$ or $\left[1-\delta,1\right]$,
-$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
-$\left[0,\delta\right]$, which implies
-$\bar{\mu}^{D}\left(P_{0}+P_{1}\right)=\imposs$, and hence
-also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}) is again satisfied.
+$\left[1-\delta,1\right]$ are disjoint, which implies $\bar{\mu}\left(P'+P''\right)$
+and $\left[1-\delta,1\right]$ are disjoint. Together with the fact
+that $\bar{\mu}\left(P'+P''\right)$ is a subset of either $\left[0,\delta\right]$
+or $\left[1-\delta,1\right]$, $\bar{\mu}\left(P'+P''\right)$ must
+be a subset of $\left[0,\delta\right]$, which implies $\bar{\mu}^{D}\left(P'+P''\right)=\imposs$,
+and hence also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal})
+is again satisfied.
 
@@
 
-The bound $\delta < \frac{1}{3}$ is tight as it is possible to
-construct a $\frac{1}{3}$-deterministic QIVPM
-$\bar{\mu}:\events\rightarrow\mathscr{I}$. For example, consider a
-three-dimensional Hilbert space~$\Hilb$ with orthonormal basis
-$\left\{\ket{0},\ket{1},\ket{2}\right\}$ and a state
-$\rho=\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$.
-Let $P$ be an operator projecting onto an $n$-dimensional subspace
-of~$\Hilb$, where $n \leq 3$. It is straightforward to check that
-$\muB_{\rho}\left(P\right)=\frac{n}{3}$. Therefore,
-$\bar{\mu}\left(P\right)=\left[\muB_{\rho}\left(P\right),\muB_{\rho}\left(P\right)\right]$
-is a valid $\frac{1}{3}$-deterministic QIVPM.
-
-When $\delta \geq \frac{1}{3}$, i.e, when the uncertainty in
-measurements becomes so large, it becomes possible to map every
-observable to some (quite inaccurate) probability interval, thus
-invalidating the Kochen-Specker theorem.
-
-We can summarize and illustrate the above arguments using
-Fig.~\ref{fignoname}.
+\begin{table}
+\caption{\label{tab:probability-measures}Possible probability measures on
+a Hilbert space of dimension~$d=3$, where $\bar{\mu}_{2}'$ and
+$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
+and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
+by $P$.}
+\centering{}%
+\begin{tabular}{cccccc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{0}\left(P\right)$  & $\bar{\mu}_{1}\left(P\right)$  & $\bar{\mu}_{2}\left(P\right)$  & $\bar{\mu}_{2}'\left(P\right)$  & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+All one-dimensional\tabularnewline
+projectors\tabularnewline
+\end{tabular} & $\left[0,0\right]$  & $\left[0,\tfrac{1}{4}\right]$  & $\left[0,\tfrac{1}{3}\right]$  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+All two-dimensional\tabularnewline
+projectors\tabularnewline
+\end{tabular} & $\left[1,1\right]$  & $\left[\tfrac{3}{4},1\right]$  & $\left[\tfrac{2}{3},1\right]$  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$  & $\left[\tfrac{1}{2},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$  & $\necess$  & $\necess$  & $\necess$  & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+The bound $\delta<\frac{1}{3}$ is tight as it is possible to construct
+a $\frac{1}{3}$-deterministic QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$.
+For example, $\bar{\mu}_{2}'$ defined in Table~\ref{tab:probability-measures}
+is a valid $\frac{1}{3}$-deterministic QIVPM. When $\delta\geq\frac{1}{3}$,
+i.e, when the uncertainty in measurements becomes so large, it becomes
+possible to map every observable to some (quite inaccurate) probability
+interval, thus invalidating the Kochen-Specker theorem. We can summarize
+and illustrate the above arguments using Fig.~\ref{fignoname}.
 
@@
 \subsection{Experimental Data and \texorpdfstring{$\delta$}{delta}-determinism}
-
-\begin{table*}
-\caption{\label{tab:probability-measures}Possible probability measures on
-a Hilbert space of dimension~$d=3$, where $\bar{\mu}_{2}'$ and
-$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
-and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
-by $P$.}
-\centering{}%
-\begin{tabular}{cccccc}
-\toprule 
-\addlinespace
-$P$  & $\bar{\mu}_{0}\left(P\right)$ & $\bar{\mu}_{1}\left(P\right)$ & $\bar{\mu}_{2}\left(P\right)$ & $\bar{\mu}_{2}'\left(P\right)$ & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
-\midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-All one-dimensional projectors  & $\left[0,0\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left[0,\tfrac{1}{3}\right]$ & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$ & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
-\midrule 
-\addlinespace
-All two-dimensional projectors  & $\left[1,1\right]$ & $\left[\tfrac{3}{4},1\right]$ & $\left[\tfrac{2}{3},1\right]$ & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$ & $\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
 

### 2018-04-26 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.lyx "A. Finite-Precision Extension of Gleason's Theorem" Updating...

@@
 To that end, we introduce the concept of \emph{interval maps}, which
-we can use to construct a consistent family of QIVPMs.
-An interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$
-maps every real-valued probability $x\in\left[0,1\right]$ to a set
-of intervals $f\left(x\right)=\left[\ell,r\right]$ containing $x$,
-where $\left[0,1\right]$ denotes the set of real-valued probabilities
-(this should not be confused with
-the interval-valued probability $\unknown$).
-We also need a notion of \emph{norm} to quantify the
-distance between (pure or mixed) states. The norm of a pure state
-$\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
-For any given Hermitian operator~$A$, we choose the
-operator norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
-which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+we can use to construct a consistent family of QIVPMs. An interval
+map $f:\left[0,1\right]\rightarrow\mathscr{I}$ maps every real-valued
+probability $x\in\left[0,1\right]$ to a set of intervals $f\left(x\right)=\left[\ell,r\right]$
+containing $x$, where $\left[0,1\right]$ denotes the set of real-valued
+probabilities (this should not be confused with the interval-valued
+probability $\unknown$). We also need a notion of \emph{norm} to
+quantify the distance between (pure or mixed) states. The norm of
+a pure state $\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
+For any given Hermitian operator~$A$, we choose the operator norm
+$\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
+which is also known as the $2$-norm or the spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
 In fact, for any such matrix, including the density matrix~$\rho$,
-this norm is the eigenvalue with maximum absolute value. Then, a
-finite-precision extension of Gleason's theorem can be stated as
+this norm is the maximum absolute value of its eigenvalues. Then,
+a finite-precision extension of Gleason's theorem can be stated as
 follows:

### 2018-05-16 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Published version except for the policy issue...

@@
 is a valid $\frac{1}{3}$-deterministic QIVPM. When $\delta\geq\frac{1}{3}$,
-i.e, when the uncertainty in measurements becomes so large, it becomes
+i.e, when the uncertainty in measurements becomes too large, it becomes
 possible to map every observable to some (quite inaccurate) probability
@@
 
-As is the case for conventional, infinitely-precise, quantum
+As in the case for conventional, infinitely-precise, quantum
 probability measures, the theorem is only applicable to dimensions
@@
 any ultramodular function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$,
-either $\mathscr{I}=\mathscr{I}_{0}$ as defined in Eq.~(\ref{eq:3-value-intervals}) or
+either $\mathscr{I}=\mathscr{I}_{0}$ as defined in Eq.~(\ref{eq:3-value-intervals}), or
 $\mathscr{I}$ contains uncountably many intervals.\end{thm}

### 2018-08-04 dissertation.tex
dissertation.tex Exported from dissertation.lyx...

--- 2018-04-15 dissertation.tex
@@
-%% LyX 2.2.3 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
-\documentclass[twoside]{iuphd}
-\usepackage[T1,T2A]{fontenc}
-\usepackage[utf8]{inputenc}
+\documentclass[11pt,twoside]{iuphd}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{fontspec}
+\setmainfont[Mapping=tex-text]{Times New Roman}
 \setcounter{secnumdepth}{3}
@@
 \usepackage{verbatim}
+\usepackage{booktabs}
 \usepackage{mathrsfs}
@@
 \usepackage{pdfpages}
-\usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{graphicx}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+\providecommand{\LyX}{L\kern-.1667em\lower.25em\hbox{Y}\kern-.125emX\@}
+%% Because html converters don't know tabularnewline
+\providecommand{\tabularnewline}{\\}
 %% A simple dot to overcome graphicx limitations
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\usepackage[ backend=biber]{biblatex}
-\addbibresource{prop.bib}
-\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
-\DeclareUnicodeCharacter{0229}{\c{e}}
-\DeclareUnicodeCharacter{00A0}{~}
 \usepackage{mmap}
@@
 \usepackage{framed}
-\usepackage[braket,qm]{qcircuit}
 \usepackage{mathrsfs}
@@
 \usepackage{dsfont}
+\usepackage{xeCJK}
+\setCJKmainfont{新細明體}
+\usepackage{unicode-math}
 
@@
 %\usepackage[basic]{complexity}
-\newcommand{\lang}[1]{{\ensuremath{\mathsf{#1}}}}
+\newcommand{\lang}[1]{{\ensuremath{\textsf{#1}}}}
 \newcommand{\newlang}[2]{\newcommand{#1}{\lang{#2}}}
 \newlang{\usat}{UNIQUE-SAT}
+\newcommand{\ComplexityFont}[1]{%
+{\ensuremath{\textsf{#1}}}%extra {} makes everyone happy.
+}
+\newcommand{\NP}{\ComplexityFont{NP}}
 
 \usepackage{amsthm}
+\theoremstyle{plain}
+\newtheorem{prop}{Proposition}[chapter]
+\newtheorem{thm}{Theorem}[chapter]
+\newtheorem{lemma}{Lemma}[chapter]
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\newcommand{\muB}{\ensuremath{\mu^{B}}}
+\newtheorem{definition}{Definition}[chapter]
+\newtheorem*{method}{Method}
+
+\usepackage[braket,qm]{qcircuit}
+\newcommand{\proj}[1]{\op{#1}{#1}}
+
+\newcommand{\muB}{\ensuremath{\mu^{\mathrm{B}}}}
+\newcommand{\muC}{\ensuremath{\mu^{\mathrm{C}}}}
+\newcommand{\muF}{\ensuremath{\mu^{\mathrm{F}}}}
+\newcommand{\barmuD}{\ensuremath{\bar{\mu}^{\mathrm{D}}}}
 \newcommand{\events}{\ensuremath{\mathcal{E}}}
+\newcommand{\eventsC}{\ensuremath{\events_{C}}}
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
@@
 \newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
-\newcommand{\fnorm}[1]{\mathsf{N}\left({#1}\right)}
+\newcommand{\Psibar}{\overline{\Psi}}
+\newcommand{\cardp}[2]{#1 \, \slash\!\! \slash \, #2}
+\def\round{\mathop{\rm round}\nolimits}
+\newcommand{\ps}{\texttt{+}}
+\newcommand{\ms}{\texttt{-}}
+\newcommand{\Hilb}{\mathcal{H}}
+\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
+\def\C{{\mathbb{C}}}
+\newcommand{\ultramodular}{\mathcal{M}}
+\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{L{#1}}}}
+\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{R{#1}}}}
+
+\newcommand{\interval}[1]{{\normalfont\textsf{\textbf{#1}}}}
+\newcommand{\imposs}{\interval{F}}
+\newcommand{\necess}{\interval{T}}
+\newcommand{\unknown}{\interval{U}}
+
+\usepackage{xparse}
+\NewDocumentCommand{\fnorm}{s m}{\mathsf{N}\IfBooleanT{#1}{^{-1}}\left({#2}\right)}
+
+\usepackage{refcount}
+% https://tex.stackexchange.com/questions/16866/how-can-i-use-footnotemark-with-a-ref-argument
 
@@
 
+\usepackage{polyglossia}
+\setdefaultlanguage[variant=american]{english}
+\setotherlanguage{arabic}
+\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
+\addbibresource{prop.bib}
 \begin{document}
@@
 
-\author{Yu-Tsung Tai}
+\author{Yu-Tsung Tai\\
+(戴淯琮)}
 
@@
 %data for Acceptance Page
-\committeeMember{Amr A. Sabry , PhD} \committeeMember{Gerardo
+\committeeMember{Amr Sabry (\textarabic{عمرو صبري}), PhD} \committeeMember{Gerardo
 Ortiz, PhD} \committeeMember{Dylan Paul Thurston, PhD} \committeeMember{Andrew
-J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{Defense
+J. Hanson, PhD} \committeeMember{Shouhong Wang (汪守宏), PhD} \defensedate{Defense
 Date} \acceptancepage
@@
 \begin{dedication}I would like to dedicate my thesis to my parents,
-Cheng-Tien Tai  and Feng-Ming Chang. Thanks for encouraging me to
-study abroad and all your support during my Ph.D. study. \todo{Find
-a way to include my parent's Chinese name. If I can find a way, also
-include Amr's Arabic name.}\end{dedication}
-
-\begin{acknowledgments}Thank Prof. Gerardo Ortiz, Prof. Amr Sabry,
-and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
-with me, and enormous other things. These papers become the main part
-of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
-is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
-and ``Discrete quantum theories'' (DQT)~\cite{DQT2014}; most of
-Chapter~\ref{chap:QIVPM} is based on ``Quantum Interval-Valued
-Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2017}.
-Together with Prof. Dylan Thurston and Prof. Shouhong Wang, thank
-you for getting together to understand what I did and passing my dissertation
-proposal Spring 2017. Also, thank Prof. Dylan Thurston for serving
-in my advisory committee and my Tier 3 committee, with other advisory
-committee members passing my Computer Science qualifying exam Spring
-2016. Especially, my survey of real computation in the qualifying
-exam inspires me the comparison of quantum computer and analog computer
-in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
-also contains the motivation in my application for Rethinking Foundations
-of Physics 2017 workshop reviewed by Prof. Amr Sabry. Thank Prof.
-Lawrence Moss for inviting me to present our results in the interdisciplinary
-logic seminar and SICE theory seminar, co-chairing my Tier 3 committee,
-writing an assessment letter for me, and drawing my attention on Prof.
-Abramsky's paper~\cite{Abramsky2012}, which inspired me to merge
-quantum probability with discrete quantum theories. Thank John Gardiner
-for inspiring discussion on the difficulties merging them~\cite{Gardiner2014}.
-These results are improved and motivated the transition from DQT to
-QIVPM in Sec.~\ref{sec:Toward-IVPM}. Thank Prof. Tom Lewis for helping
-me organize the unpublished deterministic quantum algorithms in the
-term paper for SLST-T501 Academic Writing course as presented in Sec.~\ref{discretequantumtheoryI}.
-Thank Traci Nagle for going through the literature review about finite
-precision measurement and contextuality discussed for CSCI-Y790 Writing
-and Editing course as presented in Sec.~\ref{sec:Quantum-Contextuality}.
-
-Thank Elizabeth ``Betsy'' Merceron and Kexin Chen for helping me
-pass TEPAIC exam.
-
-Thank Hao-Chun Lee and Hsien-Ching Kao for discussing what I did in
-the prospective of a general Ph.D. in Physics, and working later in
-more computational industry.
-
-Finally, thank Jin-Ru Yang for holding my hand and leading me here,
-and hope I could be with you to wherever place until the death separating
-us apart eventually.\end{acknowledgments}
+Cheng-Tien Tai (戴振沺) and Feng-Ming Chang (張鳳鳴). Thanks for encouraging
+me to study abroad and all your support during my Ph.D. study.\end{dedication}
+
+\begin{acknowledgments}I want to thank Prof.~Gerardo Ortiz, Prof.~Amr
+Sabry (\textarabic{عمرو صبري}), and Prof.~Andrew Hanson for publishing
+three papers \cite{geometry2013,DQT2014,THOS2018} with me, and enormous
+other things. These papers become the main part of my thesis, especially
+most of Chapter~\ref{chap:DQT=000026DQC} is based on “Geometry
+of discrete quantum computing”~\cite{geometry2013} and “Discrete
+quantum theories” (DQT)~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
+is based on “Quantum Interval-Valued Probability: Contextuality
+and the Born Rule” (QIVPM) \cite{THOS2018}. Together with Prof.~Dylan
+Thurston and Prof.~Shouhong Wang (汪守宏), I want to thank you for getting
+together to understand what I did and passing my dissertation proposal
+Spring 2017. I also thank Prof. Dylan Thurston for serving in my advisory
+committee and my Tier 3 committee, with other advisory committee members
+passing my Computer Science qualifying exam Spring 2016. Especially,
+my survey of real computation in the qualifying exam inspired me the
+comparison of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
+Chapter~\ref{chap:Introduction} also contains the motivation in
+my application for Rethinking Foundations of Physics 2017 workshop
+reviewed by Prof. Amr Sabry (\textarabic{عمرو صبري}). I want to thank
+Prof. Lawrence Moss for inviting me to present our results in the
+interdisciplinary logic seminar and theory seminar in Computer Science,
+co-chairing my Tier 3 committee, writing an assessment letter for
+me, and drawing my attention on Prof.~Abramsky's paper~\cite{Abramsky2012},
+which inspired me to merge quantum probability with discrete quantum
+theories. And I thank John Gardiner for inspiring discussion on the
+difficulties merging them~\cite{Gardiner2014}. These results are
+improved and motivated the transition from DQT to QIVPM in Sec.~\ref{sec:Toward-IVPM}.
+I also thank Prof.~Tom Lewis for helping me organize the unpublished
+deterministic quantum algorithms in the term paper for SLST-T501 Academic
+Writing course as presented in Sec.~\ref{discretequantumtheoryI}.
+I want to thank Traci Nagle for going through the literature review
+about finite precision measurement and contextuality discussed for
+CSCI-Y790 Writing and Editing course as presented in Sec.~\ref{sec:Quantum-Contextuality}.
+I also thank Elizabeth “Betsy” Merceron and Kexin “Casey”
+Chen (谌可心) for teaching me English in general so that others can understand
+me more easily.
+
+\todo{Type a table for acknowledgment so that I would have to write
+“I thank” so many times here?}Many people in both department
+of Mathematics and Computer Science need to do something more to make
+my double-major works smoothly. I need to thank all of them, especially
+directors of graduate study in Mathematics, especially Prof. Christopher
+Judge and Prof. Matthias Weber; directors of Ph.D. study in Computer
+Science, especially Prof. Yuqing Melanie Wu (吴愈青) and Prof. Funda
+Ergun.
+
+Thank Kin Wai Chan for suggesting me the correct direction for Propsition~\ref{appH.sec},
+Prof. 朱樺 for drawing my attention on Prof. Wan's book~\cite{Wan2006},
+and Weihua Liu (刘伟华) for remaining me analysts call the right side
+of the IVPM outer measure.
+
+Thank Meng-Wei Chen (陳孟瑋) as my best friend and roommate in Bloomington.
+Thank Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
+what I did in the prospective of a general Ph.D. in Physics, and working
+later in more computational industry.
+
+Finally, thank Jin-Ru Yang (楊謹如) for everything could not be written
+here.\end{acknowledgments}
+
+\begin{preface}
+\begin{itemize}
+\item The latest version of this thesis is in GitHub:
+\[
+\hspace{-4em}\textrm{https://github.com/yuttai/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/blob/master/dissertation.pdf}
+\]
+\item Its source code is typeset using \LyX ~\cite{LyX} in:
+\[
+\hspace{-4em}\textrm{https://github.com/yuttai/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/blob/master/dissertation.lyx}
+\]
+\item Any comments can be left in the Issue part of the GitHub Repository:
+\[
+\hspace{-4em}\textrm{https://github.com/yuttai/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/issues}
+\]
+\end{itemize}
+\end{preface}
 \begin{abstract}
@@
 
-This marriage of quantum mechanics and computer science first envisioned
+The marriage of quantum mechanics and computer science first envisioned
 and popularized by Feynman has created an awkward, but opportune,
-moment. The embarrassing dilemma was concisely described by Aaronson
-with the following three statements \cite{AaronsonArkhipov2011,BFRDARW2013}:
+moment. This embarrassing dilemma was concisely summarized by Prof.~Aaronson
+that one of the the following three statements is false \cite{AaronsonArkhipov2011,BFRDARW2013}:
 \begin{enumerate}[label=(\roman{enumi})]
@@
 thesis — that probabilistic Turing machines can efficiently simulate
-any physically realizable model of computation — is correct \cite{BernsteinVazirani1997,Kaye2007}. 
+any physically realizable model of computation — is correct \cites{Bernstein:1993:QCT:167088.167097}{Kaye2007}. 
 \end{enumerate}
@@
 then we concede \ref{enu:no-efficient-classical-factoring}. If it
-is correct Shor's efficient factoring algorithm is realizable, and
-we can prove there is no efficient classical factoring algorithm,
-we concede \ref{enu:extended-Church-Turing-Thesis}. Otherwise, if
-we cannot implement Shor's algorithm no matter how hard we try, textbook
-quantum mechanics, i.e., \ref{enu:Textbook-quantum-mechanics} may
-need to be improved by a better theory. It is unlikely that there
+is correct that Shor's efficient factoring algorithm is realizable,
+and we can prove there is no efficient classical factoring algorithm,
+then we concede \ref{enu:extended-Church-Turing-Thesis}. Otherwise,
+if we cannot implement Shor's algorithm no matter how hard we try,
+textbook quantum mechanics, i.e., \ref{enu:Textbook-quantum-mechanics}
+may need to be improved by a better theory. It is unlikely that there
 will be a simple resolution to this awkward situation. It is more
@@
 issues raised by the properties \ref{enu:-orthonormal-basis} and
-\ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:Quantum-Circuit-Model},
+\ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:fuzzy},
+we introduce the important issues of \ref{enu:measurement-framework}
+and the foundations of quantum probability space. In Sec.~\ref{sec:Quantum-Circuit-Model},
 we address the property~\ref{enu:unitary-matrix} by describing product
 and entangled $n$-qubit states and unitary matrices in quantum circuit
-model. In Sec.~\ref{sec:fuzzy}, we introduce the important issues
-of \ref{enu:measurement-framework} and the foundations of quantum
-probability space.
+model.
 
@@
 
-\subsection{Two-dimensional Hilbert Space}
+\subsection{Two-dimensional Hilbert Space\label{subsec:Two-dimensional-Hilbert-Space}}
 
@@
 We can reduce 3 degrees of freedom in \Eq{A5.eq} to 2 degrees of
-freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
-out by the circle $\Sphere{1}$''). The standard form of this maps
-(``the Hopf fibration'') is 
+freedom by effectively removing $\rme^{\rmi\theta}$ (“fibering
+out by the circle $\Sphere{1}$”). The standard form of this maps
+(“the Hopf fibration”) is 
 \begin{eqnarray}
@@
 \begin{equation}
-\braket{\Psi}{\Psi}=\|\VVec{\alpha}\|^{2}=\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=1\,.\label{probEq1.eq}
+\braket{\Psi}{\Psi}=\left\Vert \VVec{\alpha}\right\Vert ^{2}=\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=1\,.\label{probEq1.eq}
 \end{equation}
@@
 
-\subsection{Explicit generalization of the Hopf fibration construction}
+\subsection{Explicit generalization of the Hopf fibration construction\label{subsec:Explicit-generalization-of}}
 
@@
 where 
-\begin{equation}
+\[
 \Hat{a}\cdot\Hat{a}=\sum_{i=0}^{D-1}\left(\left|\alpha_{i}\right|^{2}\right)^{2}+\sum_{i=0}^{D-1}\sum_{\substack{j=0\\
@@
 }^{D-1}\left(\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}+\left(\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)\left(\sum_{j=0}^{D-1}\left|\alpha_{j}\right|^{2}\right)=1\,.
-\end{equation}
+\]
 This construction gives an explicit embedding of the $\left(D-1\right)$-dimensional
@@
 
-\section{Quantum Circuit Model\label{sec:Quantum-Circuit-Model}}
+\section{Quantum Probability\label{sec:fuzzy}}
+
+A \emph{probability space} is a mathematical abstraction specifying
+the necessary conditions for reasoning coherently about collections
+of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
+In the quantum case, the events of interest are specified by \emph{projection
+operators} $P$ satisfying the condition $P^{2}=P$. These include
+the empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
+projectors of the form $\proj{\Phi}$ where $\ket{\Phi}$ is a pure
+quantum state (an element of a Hilbert space $\mathcal{H}$), sums
+of \emph{orthogonal} projectors~$P_{0}$ and~$P_{1}$ with $P_{0}P_{1}=\mathbb{0}$,
+and products of \emph{commuting} projectors $P_{0}$ and~$P_{1}$
+with $P_{0}P_{1}=P_{1}P_{0}$. In a quantum probability space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
+each event~$P_{i}$ is mapped to a probability~$\mu\left(P_{i}\right)$
+using a probability measure $\mu:\events\rightarrow\left[0,1\right]$,
+where $\events$ is the set of all events, (i.e., projectors on a
+given Hilbert space), subject to the following constraints: $\mu\left(\mathbb{0}\right)=0$,
+$\mu\left(\mathbb{1}\right)=1$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$,
+and for each pair of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
+\begin{equation}
+\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
+\end{equation}
+Given a Hilbert space $\mathcal{H}$ of dimension $D$ and a probability
+assignment for every projector $P$, we can define the expectation
+value of an observable~$\mathbf{O}$ having spectral decomposition
+$\mathbf{O}=\sum_{i=1}^{D}\lambda_{i}P_{i}$, with eigenvalues $\lambda_{i}\in\mathbb{R}$,
+as \cite{544199,Jaeger2007}: 
+\begin{equation}
+\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{D}\lambda_{i}\mu\left(P_{i}\right)\,,\label{eq:quantum-expectation}
+\end{equation}
+where the subscript $\mu$ might be omitted if it is clear according
+to the context.
+
+A conventional quantum probability measure can easily be constructed
+using the Born rule if one knows the current pure unnormalized quantum
+state $\ket{\Phi}\in\mathcal{H}$; then the Born rule induces a probability
+measure $\muB_{\Phi}$ defined as 
+\begin{equation}
+\muB_{\Phi}(P)=\frac{\melem{\Phi}{P}{\Phi}}{\ip{\Phi}{\Phi}}\,.\label{eq:Born}
+\end{equation}
+If $\ket{\Phi}$ is normalized, Eq.~(\ref{eq:Born}) could be simplified
+as $\muB_{\Phi}(P)=\melem{\Phi}{P}{\Phi}$. For mixed states $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$,
+where $\ket{\Phi_{j}}\in\mathcal{H}$ are normalized, $q_{j}>0$,
+and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule induces a
+probability measure $\muB_{\rho}$ defined as $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)$
+\cites{Born1983}{Mermin2007}{Jaeger2007}.
+
+As an example, consider a three-dimensional Hilbert space with orthonormal
+basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $ and an observable
+$\mathbf{O}$ with spectral decomposition $\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
+i.e., the $i$th eigenvalue $\lambda_{i}=i$ and the $i$th eigenprojector
+$P_{i}=\proj{i-1}$. Two fragments of valid probability measures~$\mu_{1}$
+and $\mu_{2}$ that can be associated with this space are defined
+in Table~\ref{tab:quantum-probability-measure}. By the Born rule,
+the first probability measure corresponds to the quantum system being
+in the pure state $\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and the second
+corresponds to the quantum system being in the state $\frac{\proj{0}+\proj{2}}{2}$.
+The expectation values of the observable $\mathbf{O}$, $\expval{\mathbf{O}}_{\mu_{1,2}}$,
+are $1.5$ in the first case and $2$ in the second.
+\begin{table}
+\noindent \begin{centering}
+\caption{\label{tab:quantum-probability-measure}Two fragments of valid probability
+measures~$\mu_{1}$ and $\mu_{2}$.}
+\par\end{centering}
+\noindent \centering{}%
+\begin{tabular}{ccccccccccc}
+\toprule 
+\addlinespace
+$\ket{\Psi}$ & $\ket{0}$ & $\ket{1}$ & $\ket{2}$ & $\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\rmi\ket{2}}{\sqrt{2}}$ & \ldots\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+$\mu_{1}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $0$ & $1$  & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & \ldots\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$\mu_{2}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $0$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & \ldots\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}
+\end{table}
+
+\subsection{Gleason's Theorem and the properties of the Born rule\label{subsec:Gleason's-Theorem-and}}
+
+A conventional quantum probability measure can be easily constructed
+from a state $\rho$ according to the Born rule; conversely, this
+is the only way to obtain a conventional quantum probability measure
+according to Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
+
+\begin{thm}[Gleason's theorem]\label{cor:Gleason's}In a Hilbert
+space $\Hilb$ of dimension $D\geq3$, given a quantum probability
+measure $\mu:\events\rightarrow\left[0,1\right]$, there exists a
+unique mixed state~$\rho$ such that $\mu=\muB_{\rho}$.\end{thm}
+
+When $D=2$, there are some non-Born quantum probability measures.
+In particular, some non-Born quantum probability measures mapping
+every event to either $0$ or $1$. This kind of probability measure
+is called a non-contextual hidden variable model, and will be discussed
+in Sec.~\ref{sec:Quantum-Contextuality}.
+
+Although Gleason's theorem associates every quantum probability measure~$\mu$
+to a mixed state~$\rho$, it is not obvious how to find $\rho$ for
+a given $\mu$. While hard in general, this task can be done easily
+if $\mu$ satisfies $\mu\left(P\right)=1$ for some projection~$P$
+when the dimension $D\geq3$. According to Gleason's theorem, there
+exists a unique mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$
+such that 
+\begin{equation}
+1=\mu\left(P\right)=\muB_{\rho}\left(P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)=\sum_{j=1}^{N}q_{j}\melem{\Phi_{j}}{P}{\Phi_{j}}\,.
+\end{equation}
+Together with the fact that $0\le\melem{\Phi_{j}}{P}{\Phi_{j}}\le1$,
+$q_{j}>0$, and $\sum_{j=1}^{N}q_{j}=1$, we must conclude that $\melem{\Phi_{j}}{P}{\Phi_{j}}=1$
+for all~$j$, and thus $P\ket{\Phi_{j}}=\ket{\Phi_{j}}$. Hence,
+\begin{equation}
+P\rho=\sum_{j=1}^{N}q_{j}P\proj{\Phi_{j}}=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}=\rho\,.
+\end{equation}
+Conversely, $P\rho=\rho$ also implies $\muB_{\rho}\left(P\right)=1$
+because the trace of any mixed state is $1$. The whole idea can then
+be summarized as the following proposition.
+
+\begin{prop}\label{prop:Born-probability-one}$\muB_{\rho}\left(P\right)=1$
+if and only if $P\rho=\rho$.\end{prop}
+
+The final property is that the Born rule is basis independent~\cite{peres1995quantum,544199}:
+\todo{Update the basis independent part with more details...}
+
+\begin{prop}\label{prop:Born-unitary-invariant}$\muB_{U\rho U^{\dagger}}\left(UPU^{\dagger}\right)=\muB_{\rho}\left(P\right)$,
+where $U$ is any unitary map.\end{prop}
+
+In Sec.~\ref{sec:Toward-IVPM}, we will use an analog of Gleason's
+theorem and these two properties to deduce that there is no “sensible”
+real-valued Born rule over finite fields.
+
+\subsection{Fuzzy Measurements}
+
+The quantum probability postulates assume a mathematical idealization
+in which quantum states and measurements are both infinitely precise,
+i.e., \textit{sharp}. In an actual experimental setup with an ensemble
+of quantum states that would ideally be identical, but are not actually
+identically prepared, with imperfections and inaccuracies in measuring
+devices, an experimenter might not be able to determine that the probability
+of an event $P$ is precisely $0.5$. To address this issue, we investigate
+the cardinal probability in Sec.~\ref{discretequantumtheoryIIb}
+and the interval-valued probability in Chapter~\ref{chap:QIVPM}.
+
+The quantum expectation value can also used to decide whether a state
+is entangled or not for multipartite systems as we describe in the
+following section.
+
+\section{The geometry of entanglement}
 
@@
 \end{comment}
-It has been 36 years since Feynman~\cite{Feynman1982Simulating}
-proposed the idea about quantum computation. Although there are many
-models for quantum computing, the circuit model is still one of the
-most widespread models~\cite{544199} no matter whether in theoretical
-study or in building a real quantum computer. Information in a quantum
-circuit is stored in qubits. Each qubit is a two-dimensional quantum
-system. For a two-qubit system, if the first and second qubit are
-described as the state~$\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$
-and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}$, the state of
-the whole system is their tensor product 
-\begin{equation}
-\begin{aligned} & \ket{\psi}\ket{\phi}=\ket{\psi}\otimes\ket{\phi}=\left(\alpha_{0}\ket{0}+\alpha_{1}\ket{1}\right)\otimes\left(\beta_{0}\ket{0}+\beta_{1}\ket{1}\right)\\
-={} & \alpha_{0}\beta_{0}\ket{0}\otimes\ket{0}+\alpha_{0}\beta_{1}\ket{0}\otimes\ket{1}+\alpha_{1}\beta_{0}\ket{1}\otimes\ket{0}+\alpha_{1}\beta_{1}\ket{1}\otimes\ket{1}\\
-={} & \alpha_{0}\beta_{0}\ket{0}\ket{0}+\alpha_{0}\beta_{1}\ket{0}\ket{1}+\alpha_{1}\beta_{0}\ket{1}\ket{0}+\alpha_{1}\beta_{1}\ket{1}\ket{1}
-\end{aligned}
-\end{equation}
-in the four-dimensional Hilbert space. For a $n$-qubit system, if
-we describe the $j$-th qubit as the state~$\ket{\psi_{j}}$, the
-state of the whole system is tensor product of all subsystems 
-\begin{equation}
-\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}=\ket{\psi_{1}}\cdots\ket{\psi_{j}}\cdots\ket{\psi_{n}}
-\end{equation}
-in the Hilbert space of dimension $D=2^{n}$. However, not all quantum
-system can be expressed as the tensor product of its subsystems. This
-kind of system is called entangled, and will be described in the next
-section.\todo{This paragraph need to be polished.}
-
-\subsection{The geometry of entanglement}
-
-\todo{Need to define (partial) trace and mixed state before this
-subsection...}
 
@@
 such that the measurement outcomes in one subsystem are related to
-the measurement outcomes in another one. Within the standard framework,
-given a quantum system composed of $n$ qubit subsystems, a pure state
-of the total system $\ket{\Psi}$ is said to be entangled if it cannot
-be written as a product of states of each subsystem. That is, a state
-$\ket{\Psi}$ is entangled if $\ket{\Psi}\ne\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$,
+the measurement outcomes in another one. To discuss entanglement,
+we consider a $D$-dimensional quantum system composed of $n$-qubit
+subsystems, i.e., $D=2^{n}$. A pure state of the total system $\ket{\Psi}$
+is said to be entangled if it cannot be written as a product of states
+of each subsystem \cites{peres1995quantum}{544199}{Jaeger2007}. That
+is, a state $\ket{\Psi}$ is entangled if $\ket{\Psi}\ne\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$,
 where $\ket{\psi_{j}}$ refers to an arbitrary state of the $j$-th
 qubit, and $\otimes$ represents the tensor product. This is equivalent
-to saying that if one calculates the reduced density operator $\rho_{j}$
+to saying that if one calculates the reduced density operator~$\rho_{j}$
 of the $j$-th subsystem by tracing out all the other subsystems,
-$\rho_{j}=\Tr_{\{1,\cdots,j-1,j+1,\cdots,n\}}\left(\rho\right)$,
+\begin{equation}
+\rho_{j}=\Tr_{\left\{ 1,\cdots,j-1,j+1,\cdots,n\right\} }\left(\rho\right)\,,\label{eq:partialTrace}
+\end{equation}
 with $j=1,\cdots,n$ and $\rho=\op{\Psi}{\Psi}$, the normalized state~$\ket{\Psi}$
-is entangled if and only if at least one subsystem state is \textit{mixed};
-i.e., $\Tr_{j}\left(\rho_{j}^{2}\right)<1$. For example, consider
-\begin{equation}
-\rho_{j}=\frac{1}{2}\left(\sigma_{0}+\sum\limits _{\mu=x,y,z}\expval{\sigma_{\mu}^{j}}\sigma_{\mu}^{j}\right)\,,
-\end{equation}
-where $\sigma_{\mu}^{j}$, $\mu=x,y,z$, are the Pauli operators acting
-on the $j$-th spin~\cite{544199}, 
-\begin{equation}
-\sigma_{\mu}^{j}=\overbrace{\sigma_{0}\otimes\cdots\otimes\sigma_{0}\otimes\underbrace{\sigma_{\mu}}_{j^{\textrm{th}}\textrm{ factors}}\otimes\sigma_{0}\otimes\cdots\otimes\sigma_{0}}^{n\textrm{ factors}}\,,\label{pauli3}
-\end{equation}
-with 
+is entangled if and only if at least one subsystem state is \textit{mixed},
+i.e., $\Tr_{j}\left(\rho_{j}^{2}\right)<1$ \cites{544199}{Jaeger2007}.\NewDocumentCommand{\jthSubsystem}{m O{} m}{{#1}_{#2}^{#3}}
+
+The reduced density operator could be expressed explicitly by the
+expectation value of the Pauli operators. Therefore, we can decide
+whether a system is entangled or not by examining these expectation
+values. Let $\jthSubsystem{\sigma}[\eta]{j}$ be the Pauli operators
+acting on the $j$-th spin~\cite{544199},
+\begin{equation}
+\jthSubsystem{\sigma}[\eta]{j}=\overbrace{\sigma_{0}\otimes\cdots\otimes\sigma_{0}\otimes\underbrace{\sigma_{\eta}}_{j^{\textrm{th}}\textrm{ factors}}\otimes\sigma_{0}\otimes\cdots\otimes\sigma_{0}}^{n\textrm{ factors}}\,,\label{pauli3}
+\end{equation}
+and $\expval{\jthSubsystem{\sigma}[\eta]{j}}$ be the corresponding
+expectation value, $\expval{\jthSubsystem{\sigma}[\eta]{j}}=\melem{\Psi}{\jthSubsystem{\sigma}[\eta]{j}}{\Psi}$,
+where $\eta=x$, $y$, and $z$, and
+\begin{subequations}
 \begin{align}
-\sigma_{0} & =\left(\begin{array}{cc}
-1 & 0\\
-0 & 1
-\end{array}\right)\,, & \sigma_{x} & =\left(\begin{array}{cc}
-0 & 1\\
-1 & 0
-\end{array}\right)\,, & \sigma_{y} & =\left(\begin{array}{cc}
-0 & -\rmi\\
-\rmi & 0
-\end{array}\right)\,, & \sigma_{z} & =\left(\begin{array}{cc}
-1 & 0\\
-0 & -1
-\end{array}\right)\,,
+\sigma_{0} & =\op{0}{0}+\op{1}{1}\,, & \sigma_{x} & =\op{1}{0}+\op{0}{1}\,,\\
+\sigma_{y} & =\rmi\op{1}{0}-\rmi\op{0}{1}\,, & \sigma_{z} & =\op{0}{0}-\op{1}{1}\,.
 \end{align}
-and $\expval{\sigma_{\mu}^{j}}=\melem{\Psi}{\sigma_{\mu}^{j}}{\Psi}$
-denotes the corresponding expectation value. The vectors 
-\begin{equation}
-{\bf X}_{j}=\left(\expval{\sigma_{x}^{j}},\expval{\sigma_{y}^{j}},\expval{\sigma_{y}^{j}}\right)\in\mathbb{R}^{3}
-\end{equation}
-allow a geometric representation of each reduced state in $\mathbb{R}^{3}$,
+\end{subequations}
+For example, given a normalized two-qubit system $\ket{\Psi}=\alpha_{00}\ket{00}+\alpha_{01}\ket{01}+\alpha_{10}\ket{10}+\alpha_{11}\ket{11}$,
+some of its expectation values are
+\begin{equation}
+\begin{aligned}\expval{\jthSubsystem{\sigma}[0]{1}} & =\left|\alpha_{00}\right|^{2}+\left|\alpha_{01}\right|^{2}+\left|\alpha_{10}\right|^{2}+\left|\alpha_{11}\right|^{2}=1\,,\\
+\expval{\jthSubsystem{\sigma}[x]{1}} & =\alpha_{00}\alpha_{10}^{*}+\alpha_{01}\alpha_{11}^{*}+\alpha_{10}\alpha_{00}^{*}+\alpha_{11}\alpha_{01}^{*}\,,\\
+\expval{\jthSubsystem{\sigma}[y]{1}} & =-\alpha_{00}\alpha_{10}^{*}\rmi-\alpha_{01}\alpha_{11}^{*}\rmi+\alpha_{10}\alpha_{00}^{*}\rmi+\alpha_{11}\alpha_{01}^{*}\rmi\,,\\
+\expval{\jthSubsystem{\sigma}[z]{1}} & =\left|\alpha_{00}\right|^{2}+\left|\alpha_{01}\right|^{2}-\left|\alpha_{10}\right|^{2}-\left|\alpha_{11}\right|^{2}\,.
+\end{aligned}
+\end{equation}
+Then, the reduced density operator~$\rho_{1}$ can be expressed by
+these expectation values as following:
+\begin{equation}
+\begin{aligned}\rho_{1}= & \Tr_{\left\{ 2\right\} }\left(\op{\Psi}{\Psi}\right)\\
+= & \left(\left|\alpha_{00}\right|^{2}+\left|\alpha_{01}\right|^{2}\right)\op{0}{0}+\left(\alpha_{00}\alpha_{10}^{*}+\alpha_{01}\alpha_{11}^{*}\right)\op{0}{1}\\
+ & +\left(\alpha_{10}\alpha_{00}^{*}+\alpha_{11}\alpha_{01}^{*}\right)\op{1}{0}+\left(\left|\alpha_{10}\right|^{2}+\left|\alpha_{11}\right|^{2}\right)\op{1}{1}\\
+= & \frac{\expval{\jthSubsystem{\sigma}[0]{1}}\sigma_{0}+\expval{\jthSubsystem{\sigma}[x]{1}}\sigma_{x}+\expval{\jthSubsystem{\sigma}[y]{1}}\sigma_{y}+\expval{\jthSubsystem{\sigma}[z]{1}}\sigma_{z}}{2}\,.
+\end{aligned}
+\end{equation}
+In general\todo{Ask Gerardo why?}, the reduced density operator~$\rho_{j}$
+of the $j$-th subsystem can always be expressed as
+\begin{equation}
+\rho_{j}=\frac{1}{2}\sum\limits _{\eta=0,x,y,z}\expval{\jthSubsystem{\sigma}[\eta]{j}}\sigma_{\eta}\,,\label{eq:reducedDensityOperator}
+\end{equation}
+and its coefficients can be summarized as the vector
+\begin{equation}
+{\bf X}_{j}=\left(\expval{\jthSubsystem{\sigma}[x]{j}},\expval{\jthSubsystem{\sigma}[y]{j}},\expval{\jthSubsystem{\sigma}[z]{j}}\right)\in\mathbb{R}^{3}\label{eq:geometricRepresentationState}
+\end{equation}
+that allows a geometric representation of each reduced state in $\mathbb{R}^{3}$,
 satisfying $0\le\left\Vert {\bf X}_{j}\right\Vert \le1$. Since $\Tr_{j}\left(\rho_{j}^{2}\right)=\frac{1}{2}\left(1+\left\Vert {\bf X}_{j}\right\Vert ^{2}\right)$,
@@
 for at least one $j$, represented by a point \emph{inside} the corresponding
-local Bloch sphere. One may therefore consider $\ket{\Psi}$ to be
-maximally entangled if $\left\Vert {\bf X}_{j}\right\Vert =0$ for
-all $j$. On the other hand, the state $\ket{\Psi}$ is unentangled
+local Bloch sphere embedded in $\mathbb{R}^{3}$. One may therefore
+consider $\ket{\Psi}$ to be maximally entangled if $\left\Vert {\bf X}_{j}\right\Vert =0$
+for all $j$. On the other hand, the state $\ket{\Psi}$ is unentangled
 (i.e., a product state) if $\left\Vert {\bf X}_{j}\right\Vert =1$
 for all $j$, corresponding to points lying on the surface of the
-Bloch sphere.
+Bloch spheres.
 
@@
 consists of $n$ qubits, we obtain a measure of conventional entanglement
-by calculating the purity relative to the set $\fh=\left\{ \sigma_{x}^{1},\sigma_{y}^{1},\sigma_{z}^{1},\ldots,\sigma_{x}^{n},\sigma_{y}^{n},\sigma_{z}^{n}\right\} $,
-\begin{align}
-P_{\fh} & =\frac{1}{n}\sum\limits _{j=1}^{n}\sum\limits _{\mu=x,y,z}\expval{\sigma_{\mu}^{j}}^{2}\,, & 0\leq P_{\fh}\leq1\,.\label{purityMeasure.eq}
-\end{align}
-Since $\fh$ is a semi-simple Lie algebra, its generalized unentangled
-states are the generalized coherent states obtained by applying any
-group operation to a reference state such as $\ket{\overline{0}}=\ket{0}\otimes\cdots\otimes\ket{0}$.
-For the algebra $\fh$ of local observables, such group operations
-are simply local rotations on each qubit. In other words, the group
-orbit describing the generalized coherent states of $\fh$ comprises
-all the product states of the form $\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{n}}$,
-which have maximum purity (i.e., $P_{\fh}=1$). Other states such
-as the Greenberger-Horne-Zeilinger state $\ket{\Psi}=\ket{\mathsf{GHZ}_{n}}=\frac{1}{\sqrt{2}}\left(\ket{0}\otimes\cdots\otimes\ket{0}+\ket{1}\otimes\cdots\otimes\ket{1}\right)$
+by calculating the purity relative to the semi-simple Lie algebra~$\fh$
+spanned by $\left\{ \jthSubsystem{\sigma}[x]{1},\jthSubsystem{\sigma}[y]{1},\jthSubsystem{\sigma}[z]{1},\ldots,\jthSubsystem{\sigma}[x]{n},\jthSubsystem{\sigma}[y]{n},\jthSubsystem{\sigma}[z]{n}\right\} $,
+\begin{equation}
+P_{\fh}=\frac{1}{n}\sum\limits _{j=1}^{n}\sum\limits _{\eta=x,y,z}\expval{\jthSubsystem{\sigma}[\eta]{j}}^{2}=\frac{1}{n}\sum\limits _{j=1}^{n}\left\Vert {\bf X}_{j}\right\Vert ^{2}\,.\label{purityMeasure.eq}
+\end{equation}
+Since the norm of the geometric representation state $\left\Vert {\bf X}_{j}\right\Vert $
+defined in Eq.~(\ref{eq:geometricRepresentationState}) is between
+$0$ and $1$, we have $0\leq P_{\fh}\leq1$, where $\frac{1}{n}$
+in Eq.~(\ref{purityMeasure.eq}) is just a normalization factor.
+All the product states of the form $\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{n}}$,
+have maximum purity (i.e., $P_{\fh}=1$). Other states such as the
+Greenberger-Horne-Zeilinger state $\ket{\Psi}=\ket{\mathsf{GHZ}_{n}}=\frac{1}{\sqrt{2}}\left(\ket{0}\otimes\cdots\otimes\ket{0}+\ket{1}\otimes\cdots\otimes\ket{1}\right)$
 are (maximally) entangled relative to the set of local observables
@@
 
-Different entanglement measures are obtained when a set $\fh$ different
-from the local observables is chosen. An obvious example, in particular,
-is given by the set of all observables. In this case, the purity takes
-its maximum value independently of the pure quantum state \cite{BKOV2003,BKOSV2004},
-expressing the fact that any state is a generalized coherent state
-of the Lie algebra of all observables.
-
-\subsection{Quantum Circuits\label{subsec:Quantum-Circuits}}
-
-\todo{Further explain $\sigma_{\mu}^{j}$ used as a quantum circuit,
-control not, the Deutsch quantum black box~\cite{544199}, and maybe
-Deutsch Algorithm...}
-
-\section{Quantum Probability\label{sec:fuzzy}}
-
-Given a pure state~$\ket{\phi}$, when we measure an observable represented
-by an Hermitian matrix~$\mathbf{O}$, the measurement result is one
-of the eigenvalues of $\mathbf{O}$. The probability of getting a
-particular eigenvalue~$\lambda$ is $\melem{\phi}{P}{\phi}$, where
-$P$ is the projection operator onto the eigenspace of $\lambda$.
-This rule of computing the probability is called the Born rule \cite{Born1983,Mermin2007,Jaeger2007},
-which is used when we want to extract information from a quantum computer.
-For any mixed state~$\rho$, the generalized Born rule induces a
-conventional quantum probability measure $\muB_{\rho}:\events\rightarrow[0,1]$,
-where $\events$ is the set of all projection operators on a given
-Hilbert space. Conversely, any quantum probability measure $\mu:\events\rightarrow[0,1]$
-can be induced from a mixed state $\rho$ in the Hilbert space of
-dimension $d\ge3$ according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
-In another word, this state $\rho$ is the unique state consistent
-with any given quantum probability measure.
+Different entanglement measures are obtained when an algebra~$\fh$
+different from the local observables is chosen. An obvious example,
+in particular, is given by the set of all observables. In this case,
+the purity takes its maximum value independently of the pure quantum
+state \cite{BKOV2003,BKOSV2004}, expressing the fact that any state
+is a generalized coherent state of the Lie algebra of all observables.
 
@@
 of elements equipped with the operations of addition, subtraction,
-multiplication, and division \cite{fieldtheory.ref,numtheory.ref}.
+multiplication, and division \cites{DummitFoote2004}{fieldtheory.ref}{numtheory.ref}.
 Fields may contain an infinite or a finite number of elements. The
@@
 $0$, and the multiplication identity $1$. Given the field~$\mathbb{F}$,
-the closed operations of addition, ``$+$,'' and multiplication,
-``$\gmult$,'' satisfy the following set of axioms: 
+the closed operations of addition, “$+$,” and multiplication,
+“$\gmult$,” satisfy the following set of axioms: 
 \begin{enumerate}
@@
 \item Distributive laws: For all $a,b,c\in\mathbb{F}$ 
-\begin{eqnarray}
-a\gmult(b+c) & = & a\gmult b+a\gmult c\,,\\
-(b+c)\gmult a & = & b\gmult a+c\gmult a\,.
-\end{eqnarray}
+\begin{align}
+a\gmult(b+c) & =a\gmult b+a\gmult c\,, & (b+c)\gmult a & =b\gmult a+c\gmult a\,.
+\end{align}
 \end{enumerate}
@@
 dependence in CQT only exists when discussing quantum contextuality.
-Despite this kind of ``supercontextuality'' of MQT, its computational
-model, modal quantum computing (MQC), having ``supernatural'' computational
-power is also far from conventional quantum computing as we will describe
-next.
+Despite this kind of “supercontextuality” of MQT, its computational
+model, modal quantum computing (MQC), having “supernatural”
+computational power is also far from conventional quantum computing
+as we will describe next.
 
@@
 
-Our computations with this ``toy'' modal quantum theory showed that
-it possesses ``supernatural'' computational power. For example,
+Our computations with this “toy” modal quantum theory showed
+that it possesses “supernatural” computational power. For example,
 one can solve a black box version of the \usat\ problem~\cite{usat}
@@
 hard as the general satisfiability problem and hence all problems
-in the~NP complexity class. Our black-box version of the \usat\ problem
+in the $\NP$ complexity class. Our black-box version of the \usat\ problem
 replaces the boolean formula with an arbitrary black box. Solutions
@@
 \begin{equation}
-\uf\ket{y}\ket{\overline{x}}=\begin{cases}
-\ket{y}\ket{\overline{x}}\,, & \textrm{if }f\left(\overline{x}\right)=\bfalse\,;\\
-\ket{\mathsf{not}\left(y\right)}\ket{\overline{x}}\,, & \textrm{if }f\left(\overline{x}\right)=\btrue\,,
-\end{cases}
+\uf\ket{y}\ket{\overline{x}}=\ket{y\oplus f\left(\overline{x}\right)}\ket{\overline{x}}=\begin{cases}
+\ket{y}\ket{\overline{x}} & \textrm{if }f\left(\overline{x}\right)=\bfalse\,;\\
+\ket{\mathsf{not}\left(y\right)}\ket{\overline{x}} & \textrm{if }f\left(\overline{x}\right)=\btrue\,,
+\end{cases}\label{eq:DeutschBox}
 \end{equation}
 where $\overline{x}$ denotes a sequence $x_{1},x_{2},\ldots,x_{n}$
-of $n$ bits and $0$ and $1$ are identified as $\bfalse$ and $\btrue$,
-respectively. Then, we can give an algorithm (see Fig.~\ref{fig:alg})
-taking as input such a classical function that decides, deterministically
-and in a constant number of black box evaluations, whether $f$ is
-satisfiable or not:
+of $n$ bits, $\oplus$ is exclusive disjunction, and $0$ and $1$
+are identified as $\bfalse$ and $\btrue$, respectively. Then, we
+can give an algorithm (see Fig.~\ref{fig:alg}) taking as input such
+a classical function that decides, deterministically and in a constant
+number of black box evaluations, whether $f$ is satisfiable or not:
 
@@
 In this model, an $n$-qubit state is a non-zero vector in $\mathbb{F}_{q}^{2^{n}}$.
-When we measure a given state~$\ket{\phi}$, an observable is replaced
-by a basis~$\mathcal{B}$ of $\mathbb{F}_{q}^{2^{n}}$. Since $\ket{\phi}$
+When we measure a given state~$\ket{\Phi}$, an observable is replaced
+by a basis~$\mathcal{B}$ of $\mathbb{F}_{q}^{2^{n}}$. Since $\ket{\Phi}$
 can be represented by the summation across a unique subset~$\mathcal{S}$
@@
 
-\subsection{Complexified Finite Fields}
+\subsection{\label{subsec:Complexified-Finite-Fields}Complexified Finite Fields}
 
 Our next objective is to develop more realistic discrete quantum theory
-variants that exclude ``supernatural'' algorithms such as the one
-presented above. Our first such plausible framework~\cite{HOSW2011}
+variants that exclude “supernatural” algorithms such as the
+one presented above. Our first such plausible framework~\cite{HOSW2011}
 is based on complexifiable finite fields. To incorporate complex numbers
@@
 field $\ff{p}$ with $p$ odd if and only if $p$ is of the form $4\ell+3$,
-with $\ell$ a non-negative integer \cite{Artin1991,DummitFoote2004}.
-For example, given any $x\in\ff{3}=\left\{ 0,\pm1\right\} $, when
-$x=0$, we have $x^{2}+1=0^{2}+1=1$; when $x=\pm1$, we have $x^{2}+1=\left(\pm1\right)^{2}+1=1$.
-Therefore, $x^{2}+1$ is irreducible over $\ff{3}$. In contrast,
-over $\ff{5}$, $2^{2}+1=0$ so that $x^{2}+1$ is reducible.
-
-We achieve our goal by observing that any field $\ff{p}$ with $p=4\ell+3$
-is extensible to a field~$\ff{p^{2}}$ whose elements can be viewed
-as discrete complex numbers with the real and imaginary parts in~$\ff{p}$.
-In a complexified finite field $\Fpp$, the Frobenius automorphism
-that maps $\alpha\in\Fpp$ to $\alpha^{p}\in\Fpp$ acts like complex
-conjugation \cite{Artin1991,grove2002classical,DummitFoote2004}.
-For example, in $\Fppx{3}$, we have $\left(2+\rmi\right)^{3}=8+12\rmi-6-\rmi=2+11\rmi$
-which, in the field, is equal to $2-\rmi$ since $11\equiv-1\pmod{3}$.
-
-We define the \emph{field norm} $\fnorm{\cdot}$ as the map from $a+\rmi b\in\Fpp$
-to $a^{2}+b^{2}\in\Fp$, 
-\begin{equation}
-\fnorm{a+\rmi b}=a^{2}+b^{2}\,.\label{fieldnorm.eq}
-\end{equation}
-We avoid the square root in the discrete field framework because,
-unlike the continuous case, the square root does not always exist.
-
-\subsection{Vector Spaces}
+with $\ell$ a non-negative integer \cite{Artin1991,DummitFoote2004,numtheory.ref}.
+For example, when $p=3$, $x$ could be $0$ or $\pm1$. Since $0^{2}+1\ne0$
+and $\left(\pm1\right)^{2}+1\ne0$, none of the element in $\ff{3}$
+solves $x^{2}+1=0$, and $x^{2}+1$ is irreducible over $\ff{3}$.
+In contrast, $2^{2}+1=0$ over $\ff{5}$ so that $x^{2}+1$ is reducible.
+
+Since $x^{2}+1=0$ has no solution in any field $\ff{p}$ with $p=4\ell+3$,
+we can extend $\ff{p}$ to a field~$\ff{p^{2}}$ whose elements can
+be viewed as discrete complex numbers with the real and imaginary
+parts in~$\ff{p}$. Therefore, every element in $\ff{p^{2}}$ can
+be expressed as $a+b\rmi$ with $a,b\in\ff{p}$, and a $\ff{p^{2}}$
+is called a complexified finite field. Since the multiplicative group
+of any finite field is cyclic~\cite{Artin1991}, there is a generator
+$g\in\ff{p^{2}}$ such that every non-zero element $a+b\rmi$ can
+also be represented as the power of a generator, i.e., $a+b\rmi=g^{j}$
+for some $j$. For example, $1-\rmi$ is a generator in $\Fppx{3}$
+means a particular element $1+\rmi\in\Fppx{3}$ can be expressed as
+$1+\rmi=1-3\rmi-3+\rmi=\left(1-\rmi\right)^{3}$. All possible choices
+of generators in $\ff{3^{2}}$ is listed in Table~\ref{tab:Generators-in-F9}.
+\begin{table}
+\caption{\label{tab:Generators-in-F9}Generators in $\ff{3^{2}}$}
+
+\centering{}%
+\begin{tabular}{ccccccccc}
+\toprule 
+\addlinespace
+$j$ & $0$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+$\left(1+\rmi\right)^{j}$ & $1$ & $1+\rmi$ & $-\rmi$ & $1-\rmi$ & $-1$ & $-1-\rmi$ & $\rmi$ & $-1+\rmi$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$\left(1-\rmi\right)^{j}$ & $1$ & $1-\rmi$ & $\rmi$ & $1+\rmi$ & $-1$ & $-1+\rmi$ & $-\rmi$ & $-1-\rmi$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$\left(-1+\rmi\right)^{j}$ & $1$ & $-1+\rmi$ & $\rmi$ & $-1-\rmi$ & $-1$ & $1-\rmi$ & $-\rmi$ & $1+\rmi$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$\left(-1-\rmi\right)^{j}$ & $1$ & $-1-\rmi$ & $-\rmi$ & $-1+\rmi$ & $-1$ & $1+\rmi$ & $\rmi$ & $1-\rmi$\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}
+\end{table}
+
+In Table~\ref{tab:Generators-in-F9}, one can notice that $\left(a+b\rmi\right)^{3}=a-b\rmi$.
+In general, the $p$-th power $\left(a+b\rmi\right)^{p}=a-b\rmi$
+is called the \emph{Frobenius automorphism} acts like complex conjugation
+$\left(a+b\rmi\right)^{*}=a-b\rmi$ \cite{Artin1991,grove2002classical,DummitFoote2004}.
+Then, we define the \emph{field norm} $\fnorm{\cdot}:\Fpp\rightarrow\Fp$
+as an element $a+\rmi b$ multiplying its complex conjugation $\left(a+b\rmi\right)^{*}$~\cite{wiki:FieldNorm},
+\begin{equation}
+\fnorm{a+\rmi b}=\left(a+b\rmi\right)\left(a+b\rmi\right)^{*}=\left(a+b\rmi\right)^{p+1}=a^{2}+b^{2}\,,\label{fieldnorm.eq}
+\end{equation}
+where the square root in the usual definition of norm is avoided because,
+unlike the continuous case, the square root does not always exist,
+and the field norm of an element $\fnorm{\cdot}$ should be the direct
+counterpart of the norm-squared $\left|\cdot\right|^{2}$ in the conventional
+quantum theory. For example, the field norm of every generator~$g$
+in Table~\ref{tab:Generators-in-F9} is the same number $\fnorm{g}=g^{3+1}=-1$.
+In fact, these four generators are the only elements in $\ff{3^{2}}$
+whose field norm is $-1\in\ff{3}$. Generally, given any $c\in\Fp$,
+let $\fnorm*{\left\{ c\right\} }$ denote the set of element whose
+field norm is $c$, i.e., $\fnorm*{\left\{ c\right\} }=\set{\alpha\in\Fpp}{\fnorm{\alpha}=c}$.
+The set $\fnorm*{\left\{ c\right\} }$ is the discrete analog of phase-equivalence
+under the modulus-preserving transformation $z\rightarrow\rme^{\rmi\phi}z$,
+and the number of its elements is characterized by the following proposition.
+
+\begin{prop}\label{appH.sec}Given any $c\in\Fp$, the number of
+elements in $\fnorm*{\left\{ c\right\} }$ is $p+1$, i.e., there
+are always $p+1$ elements in $\Fpp$ whose field norm is $c$.\end{prop}
+
+\begin{proof}To prove Proposition~\ref{appH.sec}, we start by proving
+$\fnorm*{\left\{ c\right\} }$ is non-empty. Consider a special case
+of the field norm $\fnorm{.}$, namely the real quadratic map $Q\left(e\right)=e^{2}$
+taking an arbitrary element $e\in\Fp$ to its square in the field.
+Since $\left(\pm1\right)^{2}=1$, the image of $Q\left(e\right)$
+has only $\frac{p+1}{2}$ elements in $\Fp$, including the zero element.
+We let $A$ be the image of the map $Q\left(e\right)$ in $\Fp$,
+and note that the set $A_{c}$ resulting from displacing an element
+$x=b^{2}$ of $A$ to $c-x=c-b^{2}$ with $c\in\Fp$ also has $\frac{p+1}{2}$
+elements because the result is simply a cyclic shift of element labels.
+We now observe that for any non-zero $c\in\Fp$, the sum of the elements
+in two sets $A$ and $A_{c}$ is $\frac{p+1}{2}+\frac{p+1}{2}=p+1$,
+which is greater than the size $p$ of $\Fp$, and so there must be
+at least one common element such that $a^{2}=c-b^{2}$. Thus every
+element $c\in\Fp$ is the field norm of some element $\alpha=a+b\rmi\in\Fpp$
+such that $\fnorm{\alpha}=a^{2}+b^{2}=c$, and $\fnorm*{\left\{ c\right\} }$
+is non-empty.
+
+We then want to show for all non-zero $c\in\Fp$, the size of $\fnorm*{\left\{ c\right\} }$
+is always the same. Given a particular non-zero $c_{0}\in\Fp$ and
+$\alpha_{0}\in\Fpp$ with $\fnorm{\alpha_{0}}=c_{0}$, consider the
+map $f\left(\alpha\right)=\alpha_{0}\alpha$. When $\fnorm{\alpha}=1$,
+we have~\cite{DummitFoote2004} 
+\begin{equation}
+\fnorm{f\left(\alpha\right)}=\fnorm{\alpha_{0}\alpha}=\fnorm{\alpha_{0}}\fnorm{\alpha}=c_{0}
+\end{equation}
+so that $f\left(\alpha\right)\in\fnorm*{\left\{ c_{0}\right\} }$.
+Since $\fnorm{a+b\rmi}=0$ only for $a=b=0$, $\alpha_{0}$ is non-zero,
+and $f$ is actually a bijection between $\fnorm*{\left\{ 1\right\} }$
+and $\fnorm*{\left\{ c_{0}\right\} }$. This means the number of elements
+in $\fnorm*{\left\{ 1\right\} }$ and $\fnorm*{\left\{ c_{0}\right\} }$
+are the same. Because $c_{0}$ can be any non-zero element, the number
+of elements in the equivalence classes $\fnorm*{\left\{ c\right\} }$
+is always the same.
+
+We can now compute the size of the equivalence class of complex unit-modulus
+phases corresponding to the Hopf fibration circle. \todo{Explain
+the Hopf fibration circle here... ?} Since $\Fpp$ has $p^{2}-1$
+non-zero values, and the map $\fnorm{\alpha}$ distributes these equally
+across the domain of $p-1$ non-zero elements $c\in\Fp$, there are
+$\frac{p^{2}-1}{p-1}=p+1$ (non-zero) domain elements in $\Fpp$ for
+each (non-zero) image element in $\Fp$. We illustrate this graphically
+in Figure~\ref{proof1.fig}. Thus the Hopf circle always has size
+$p+1$, corresponding essentially to a discrete projective line, and
+that is the size of each equivalence class of the map $\fnorm{\alpha}$
+for non-vanishing $\alpha$, including in particular the map to the
+unit norm value $c=1\in\Fp$.
+\begin{figure}
+\noindent \centering{}\includegraphics[width=3.6in]{Fpp2Fp}\caption{Sketch of the map from $\Fpp$ to $\Fp$ using $\fnorm{\alpha}$,
+showing the decomposition of $\Fpp$ into the zero element $\left(0,0\right)$
+and the $p^{2}-1=\left(p+1\right)\left(p-1\right)$ non-zero elements
+that map onto the $p-1$ non-zero elements of $\Fp$ with multiplicity
+$p+1$.}
+\label{proof1.fig}
+\end{figure}
+\end{proof}
+
+\subsection{Vector Spaces\label{subsec:Vector-Spaces}}
 
@@
 have an inner product satisfying the properties above. However, we
-will introduce an Hermitian ``dot product'' satisfying some of those
-properties.
-
-We are interested in the vector space ${\cal H}$ of dimension $D$
-defined over the complexified field $\Fpp$. Let $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$
+will introduce an Hermitian “dot product” satisfying some of
+those properties.
+
+We are interested in the vector space $\mathcal{H}$ of dimension
+$D$ defined over the complexified field $\Fpp$. Let $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$
 and $\ket{\Phi}=\begin{pmatrix}\beta_{0} & \beta_{1} & \ldots & \beta_{D-1}\end{pmatrix}^{T}$
-represent vectors in ${\cal H}$, with numbers $\alpha_{i}$ and $\beta_{i}$
-drawn from $\Fpp$, and where $\left(\cdot\right)^{T}$ is the transpose.
+represent vectors in $\mathcal{H}$, with numbers $\alpha_{i}$ and
+$\beta_{i}$ drawn from $\Fpp$, and where $\left(\cdot\right)^{T}$
+is the transpose.
 
 \begin{definition}[Hermitian dot product] Given vectors $\ket{\Phi}$
-and $\ket{\Psi}\in{\cal H}$, it can be shown~\cite{grove2002classical}
+and $\ket{\Psi}\in\mathcal{H}$, it can be shown~\cite{grove2002classical,Wan2006}
 the Hermitian dot product is always reducible to the form 
 \begin{equation}
-\ip{\Phi}{\Psi}=\sum_{i=0}^{D-1}\beta_{i}^{p}\alpha_{i}\,.
-\end{equation}
-\end{definition} Two vectors $\ket{\Phi}$ and $\ket{\Psi}\in{\cal H}$
+\ip{\Phi}{\Psi}=\sum_{i=0}^{D-1}\beta_{i}^{p}\alpha_{i}\,.\label{innerprod}
+\end{equation}
+\end{definition} Two vectors $\ket{\Phi}$ and $\ket{\Psi}\in\mathcal{H}$
 are said to be orthogonal if $\ip{\Phi}{\Psi}=0$. This product satisfies
@@
 $\ket{\Psi}$ such that $\ip{\Psi}{\Psi}=0$. The reason is that addition
-in finite fields eventually ``wraps around'' (because of their cyclic
-or modular structure), allowing the sum of non-zero elements to be
-zero. The fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$
+in finite fields eventually “wraps around” (because of their
+cyclic or modular structure), allowing the sum of non-zero elements
+to be zero. The fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$
 decreases with the order $p$.
@@
 \end{equation}
-The field norm of a vector can vanish for non-vanishing vectors.
+
+Although the field norm of a vector can vanish for non-vanishing vectors,
+if a vector $\ket{\Psi}$ has a non-vanishing field norm~$c$, then
+$\ket{\Psi}$ can be normalized by utilizing its field norm. Recalled
+in Sec.~\ref{subsec:Complexified-Finite-Fields}, we defined $\fnorm*{\left\{ c\right\} }$
+to be the set of element whose field norm is $c$. Given any $\alpha\in\fnorm*{\left\{ c\right\} }$,
+the field norm of $\frac{\ket{\Psi}}{\alpha}$ is
+\begin{equation}
+\fnorm{\frac{\ket{\Psi}}{\alpha}}=\frac{\fnorm{\ket{\Psi}}}{\fnorm{\alpha}}=\frac{c}{c}=1\,,
+\end{equation}
+i.e., $\frac{\ket{\Psi}}{\alpha}$ is normalized. However, since the
+size of $\fnorm*{\left\{ c\right\} }$ is $p+1$, we cannot identify
+a “unique” way to normalize any given vector.
+
+Actually, the similar problem has already happened in conventional
+quantum theory. For example, assume we want to normalize $\ket{\Psi}=\ket{0}+\ket{1}$.
+Its inner product with itself is $\ip{\Psi}{\Psi}=2$. Since $\left(\pm\sqrt{2}\right)^{2}=2$,
+both $\frac{\ket{\Psi}}{\sqrt{2}}$ and $\frac{\ket{\Psi}}{-\sqrt{2}}$
+are normalized and representing the same state as $\ket{\Psi}$. In
+this case, we systematically choose the state divided by the positive
+square root as “the” normalized vector of $\ket{\Psi}$ in conventional
+quantum theory, and the positive square root function is called the
+\emph{principal} branch of $\sqrt{w}$~\cite{GAMELIN2003}. In discrete
+case, we can also systematically choose the \emph{principal inverse
+field norm} by utilizing a generator $g\in\Fpp$ discussed in Sec.~\ref{subsec:Complexified-Finite-Fields}.
+Because $g$ is a generator, any non-zero element $c\in\ff{p}\backslash\left\{ 0\right\} $
+can be expressed as $g^{\left(p+1\right)k}$ where $k$ is an integer
+and $0\le k<p-1$, so we can define the principal inverse field norm
+$\fnorm*{g^{\left(p+1\right)k}}$ as $g^{k}$. For example, the inverse
+field norm over $\ff{3^{2}}$ with respect to the generator $1-\rmi$
+is shown in Table~\ref{tab:Inverse-field-norm}. Given the non-normalized
+state $\ket{\Psi}=\ket{0}+\ket{1}$, since its field norm is $\fnorm{\ket{\Psi}}=\fnorm{1}+\fnorm{1}=-1$,
+it can be normalized as
+\begin{equation}
+\frac{\ket{\Psi}}{\fnorm*{-1}}=\frac{\ket{0}+\ket{1}}{1-\rmi}=\left(1+\rmi\right)\ket{0}+\left(1+\rmi\right)\ket{1}\,.
+\end{equation}
+\begin{table}
+\caption{\label{tab:Inverse-field-norm}Inverse field norm over $\ff{3^{2}}$
+with respect to the generator $1-\rmi$}
+
+\centering{}%
+\begin{tabular}{cccc}
+\toprule 
+\addlinespace
+$c=g^{\left(p+1\right)k}$ & $\left(p+1\right)k$ & $k$ & $\fnorm*{g^{\left(p+1\right)k}}=g^{k}$\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+$-1$ & $4$ & $1$ & $1-\rmi$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$1$ & $0$ & $0$ & $1$\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}
+\end{table}
 
@@
 \begin{equation}
-\|\psi_{1}\|^{2}=|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=1\label{DQA2.eq}
-\end{equation}
-in the discrete field. In \ref{appU.sec}, we show that there are
-$p(p^{2}-1)$ such values.\todo{Check reference...} Given this requirement,
-which is similar in form to the conservation of probability, but not
-as useful due to the lack of orderable probability values, we can
-immediately conclude that the discrete analog of the Hopf fibration
-is again 
+\fnorm{\ket{\psi_{1}}}=\fnorm{\alpha_{0}}+\fnorm{\alpha_{1}}=1\label{DQA2.eq}
+\end{equation}
+in the discrete field. We show that there are $p\left(p^{2}-1\right)$
+such values later in the general theorem, Proposition~\ref{appU.sec}.
+Given this requirement, which is similar in form to the conservation
+of probability, but not as useful due to the lack of orderable probability
+values, we can immediately conclude that the discrete analog of the
+Hopf fibration is again 
 \begin{eqnarray}
@@
 Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{DQA6.eq}\\
-Z & = & \left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
+Z & = & \fnorm{\alpha_{0}}-\fnorm{\alpha_{1}}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
 \end{eqnarray}
-but now with all computations in $\pmod{p}$. At this point one simply
-writes down all possible discrete values for the complex numbers $\left(\alpha_{0},\alpha_{1}\right)$
-satisfying Eq.~(\ref{DQA2.eq}) and enumerates those that project
-to the same value of $\{X,Y,Z\}$. This equivalence class is the discrete
-analog of the circle in the complex plane that was eliminated in the
-continuous case. In \ref{appH.sec}, we show that $p+1$ discrete
-values of $\{\alpha_{0},\alpha_{1}\}$ with unit norm map to the same
-point under the Hopf map \Eq{DQA6.eq}; we may think of these as
-discrete circles or projective lines of equivalent, physically indistinguishable,
-complex phase. The surviving $p(p-1)$ values of $\{\alpha_{0},\alpha_{1}\}$
-correspond to irreducible physical states of the discrete single qubit
-system. %% Several examples are shown in Figure \ref{bloch.fig}. %%Thus,
-for example, choosing the underlying field to be $\Fppx{3}$, there
-are exactly 6 single-qubit state vectors to populate the Bloch sphere;
-the four equivalent phase-multiples mapping to each of the six points
-on the $\Fppx{3}$ Bloch sphere are collapsed and regarded as physically
-indistinguishable. In Figure \ref{bloch.fig}, we plot the irreducible
+but now with all computations in\hspace{0bp}$\pmod{p}$. At this
+point one simply writes down all possible discrete values for the
+complex numbers $\left(\alpha_{0},\alpha_{1}\right)$ satisfying Eq.~(\ref{DQA2.eq})
+and enumerates those that project to the same value of $\left(X,Y,Z\right)$.
+This equivalence class is the discrete analog of the circle in the
+complex plane that was eliminated in the continuous case. In Proposition~\ref{appH.sec},
+we show that $p+1$ discrete values of $\left(\alpha_{0},\alpha_{1}\right)$
+with unit norm map to the same point under the Hopf map \Eq{DQA6.eq}\todo{Does
+Proposition~\ref{appH.sec} really show this?}; we may think of
+these as discrete circles or projective lines of equivalent, physically
+indistinguishable, complex phase. The surviving $p\left(p-1\right)$
+values of $\left(\alpha_{0},\alpha_{1}\right)$ correspond to irreducible
+physical states of the discrete single qubit system. Thus, for example,
+choosing the underlying field to be $\Fppx{3}$, there are exactly
+6 single-qubit state vectors to populate the Bloch sphere; the four
+equivalent phase-multiples mapping to each of the six points on the
+$\Fppx{3}$ Bloch sphere are collapsed and regarded as physically
+indistinguishable. In Figure~\ref{bloch.fig}, we plot the irreducible
 states on the Bloch sphere for $p=3$, $7$, and $11$. Note that
@@
 on the Bloch sphere vary considerably due to the nature of discrete
-fields; we have artificially normalized them to a ``continuous world''
+fields; we have artificially normalized them to a “continuous world”
 unit radius sphere for conceptual clarity.
-
-\begin{figure}[htb]
-%\vspace{-0.2in}  %% \includegraphics[width=0.9\columnwidth]{./Bloch_sphere.pdf}%%\includegraphics[width=2.0\columnwidth]{./picA.png}%%\includegraphics[width=2.0\columnwidth]{./picB.png}
-
-\begin{centering}
-\hspace*{-0.5cm}\includegraphics[width=1.1\columnwidth]{\string"../../../Public/Documents/StudyInIUB/Computer Science/201209-12.M800/Manuscripts/picC\string".png}
-%%\includegraphics[width=0.5\textwidth]{./picAB.eps}\vspace{-0.2in}
- %% adjust blank space?
+\begin{figure}
+\noindent \begin{centering}
+\includegraphics[viewport=200bp 0bp 1800bp 600bp,width=1.1\columnwidth]{picC}
 \par\end{centering}
@@
 
-\subsection{Counting states on the $n$-qubit Bloch sphere}
+\subsubsection{Counting states on the discrete Bloch sphere}
 
@@
 computing to precisely identify and enumerate the physical states.
-In the conventional theory, as we have seen, we employ a generalized
-Hopf fibration on the normalized states to project out a circle of
-phase-equivalent states, yielding the generalized Bloch sphere.
-
-In the introduction to this section, we sketched the counting of the
-irreducible single-qubit discrete states. To count the number of inequivalent
-discrete states for the general $n$-qubit case with coefficients
-in $\Fpp$, we first must find the set of unit-norm states, and then
-determine the equivalence classes of unit-norm states under discrete
-phase transformations; we can then enumerate the list of states on
-the discrete generalized Bloch sphere. By executing computer searches
-of these spaces, we discovered an hypothesis for a closed-form solution
-for the counting of the states, and were then able to find a rigorous
-inductive proof of the enumeration, which is presented in the Appendix.
-
-This process of describing the discrete $n$-qubit irreducible states
-can again be understood geometrically by following the discrete analog
-of the Hopf fibration. First, we construct the discrete version of
-the quadratic unit-length form that automatically annihilates the
+In the conventional theory, as we have seen in Sec.~\ref{subsec:Explicit-generalization-of},
+we employ a generalized Hopf fibration on the normalized states to
+project out a circle of phase-equivalent states, yielding the generalized
+Bloch sphere.
+
+In the introduction to this subsection, we sketched the counting of
+the irreducible single-qubit discrete states. To count the number
+of inequivalent discrete states for the general $n$-qubit case with
+coefficients in $\Fpp$, we first must find the set of unit-norm states,
+and then determine the equivalence classes of unit-norm states under
+discrete phase transformations; we can then enumerate the list of
+states on the discrete generalized Bloch sphere. By executing computer
+searches of these spaces, we discovered an hypothesis for a closed-form
+solution for the counting of the states, and find a rigorous proof
+of the enumeration.
+
+This process of describing the discrete $D$-dimensional irreducible
+states can again be understood geometrically by following the discrete
+analog of the Hopf fibration. First, we construct the discrete version
+of the quadratic unit-length form that automatically annihilates the
 distinction among states differing only by a discrete phase, 
-\begin{eqnarray}
-\hspace*{-0.5cm}\Hat{a}=(|\alpha_{i}|^{2},...,\sqrt{2}\ \mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\ \mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots)\ ,
-\end{eqnarray}
+\begin{equation}
+\Hat{a}=\left(\fnorm{\alpha_{i}},\ldots,\sqrt{2}\,\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\,\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\right)\,,
+\end{equation}
 where 
-\begin{eqnarray}
-\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)^{2}=1\ .
-\end{eqnarray}
-{}From \ref{appH.sec}, we know that $p+1$ elements of this discrete
-$\Sphere{2\times2^{n}-1}$ structure map to the \textit{same point\/}
-in $\Hat{a}$. Each set of $(p+1)$ redundant points is, geometrically
-speaking, the \textit{discrete Hopf fibration circle\/} living above
-each \textit{irreducible\/} point of the $n$-qubit state description.
-These $p+1$ points are interpretable as the $p$ finite points plus
-the single point at infinity of the projective discrete line (see,
-e.g., \cite{Arnold}).
+\begin{equation}
+\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}\right)^{2}=1\,.
+\end{equation}
+From Proposition~\ref{appH.sec}, we know that $p+1$ elements of
+this discrete $\Sphere{2D-1}$ structure map to the \textit{same point\/}
+in $\Hat{a}$\todo{Does Proposition~\ref{appH.sec} really show
+this?}. Each set of $p+1$ redundant points is, geometrically speaking,
+the \textit{discrete Hopf fibration circle\/} living above each \textit{irreducible\/}
+point of the $D$-dimensional state description. These $p+1$ points
+are interpretable as the $p$ finite points plus the single point
+at infinity of the projective discrete line (see, e.g., \cite{arnold_2010}).
 
@@
 states, effectively the space of allowed discrete partitions of unity;
-we cannot exactly call these ``probability-conserving'' sectors
+we cannot exactly call these “probability-conserving” sectors
 of the state coefficients since we do not have a well defined notion
 of probability, but we do have a well-defined notion of partition
-of unity. The tally of unit-norm states is $p^{2^{n}-1}(p^{2^{n}}-1)$
-(see \ref{appU.sec}) compared to the total number $p^{2\times2^{n}}$
-of possible complex integer state vectors that could be chosen. This
-unit-norm state structure is the discrete analog of $\Sphere{2\times2^{n}-1}$.
-
-Finally, we repeat the last step of the $n$-qubit continuous Hopf
-fibration process for discrete $n$-qubit states, eliminating the
-discrete set of $p+1$ equivalent points that map to the same point
-$\Hat{a}$ on the generalized $n$-qubit Bloch sphere. Dividing the
-tally $p^{2^{n}-1}(p^{2^{n}}-1)$ of unit norm states by the $p+1$
-elements of each phase-equivalent discrete circle, we find 
+of unity. Compared to the total number $p^{2D}$ of possible complex
+integer state vectors that could be chosen, the number of unit-norm
+states is given by the following proposition. This unit-norm state
+structure is the discrete analog of $\Sphere{2D-1}$.
+
+\begin{prop}\label{appU.sec}The number of unit-norm states described
+by a $D$-dimensional vector $\left(\alpha_{0},\ldots,\alpha_{D-1}\right)$
+with coefficients $\alpha_{i}\in\Fpp$ is $p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)$.\end{prop}
+
+\begin{proof}Proposition~11.27 in Grove~\cite{grove2002classical}
+provides the count of the zero-norm states $\zeta\left(D,p\right)=p^{D-1}\left(p^{D}+\left(-1\right)^{D}\left(p-1\right)\right)$.
+Since there are $p^{2}$ elements $\alpha\in\Fpp$, we must have $\left(p^{2}\right)^{D}=p^{2D}$
+possible values of a $D$-dimensional vector $\left(\alpha_{0},\ldots,\alpha_{D-1}\right)$.
+There are $p^{2}-1$ non-zero values of $\alpha\in\Fpp$, and we showed
+in Proposition~\ref{appH.sec} that $\fnorm{\alpha}$ maps exactly
+$p+1$ values in that set to each of the $p-1$ non-zero values in
+$\Fp$. Therefore, the \textit{unit-norm case\/} has a count of domain
+elements that is $\frac{1}{p-1}$ of the total number of non-zero-norm
+cases, 
+\begin{equation}
+\frac{p^{2D}-\zeta\left(D,p\right)}{p-1}=\frac{p^{2D}-p^{2D-1}-\left(-1\right)^{D}p^{D-1}\left(p-1\right)}{p-1}=p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)\,.\label{unitnorm.eq}
+\end{equation}
+\end{proof}
+
+Finally, we repeat the last step of the $D$-dimensional continuous
+Hopf fibration process for discrete $D$-dimensional states, eliminating
+the discrete set of $p+1$ equivalent points that map to the same
+point $\Hat{a}$ on the generalized Bloch sphere. Dividing the tally
+$p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)$ of unit norm states
+by the $p+1$ elements of each phase-equivalent discrete circle, we
+find
+\begin{equation}
+\frac{p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)}{p+1}\label{eq:numberOfIrreducibleStates}
+\end{equation}
+as the total count of unique irreducible states in a discrete $D$-dimensional
+configuration. The resulting object is precisely the discrete version
+of $\CP{D-1}$, which we might call a \textit{discrete complex projective
+space\/} or $\DCP{D-1}$.
+
+\subsection{Geometry of Entangled States}
+
+To discuss entanglement, we consider a $D$-dimensional quantum system
+composed of $n$-qubit subsystems, i.e., $D=2^{n}$ as usual. Without
+regard to uniqueness, an $n$-qubit state with discrete complex coefficients
+in $\Fpp$ will have the total possible space of coefficients with
+dimension $p^{2\times2^{n}}$ (including the null state). Imposing
+the condition of a length-one norm in $\Fp$, this number is reduced
+to $p^{2^{n}-1}\left(p^{2^{n}}-1\right)$. The ratio of all the states
+to the unit-norm states is asymptotically $p$: 
+\begin{equation}
+\frac{p^{2^{n}+1}}{p^{2^{n}}-1}\rightarrow p\,,
+\end{equation}
+so there are roughly $p$ sets of coefficients, for any number of
+qubits $n$, that are discarded for each retained unit-length state
+vector. A factor of $p+1$ more states are discarded in forming the
+discrete Bloch sphere of irreducible states. Selected plots of the
+full space compared to both the unit-norm space and the irreducible
+space for a selection of complexified finite fields are shown in Figure
+\ref{statePlot3Unit.fig} for 1, 2, 3, and 4 qubits.
+\begin{figure}[htb]
+\begin{centering}
+\includegraphics[width=1\columnwidth]{statePlot3} 
+\par\end{centering}
+\caption{Logarithmic plot of the number of discrete unnormalized states (top,
+in red), vs the number of normalized discrete states (middle, in blue),
+vs the irreducible states (bottom, in green) for the first 6 $\Fpp$-compatible
+primes, ($3$, $7$, $11$, $19$, $23$, $31$), for the number of
+qubits $1$, $2$, $3$, and $4$. }
+\label{statePlot3Unit.fig} 
+\end{figure}
+
+\subsubsection{Unentangled vs Entangled Discrete States}
+
+For a given $p$ and the corresponding complexified field $\Fpp$,
+the $n$-qubit discrete quantum states with coefficients in $\Fpp$
+can be classified by their degree of entanglement to a level of precision
+that is unavailable in the continuous theory. We look first at the
+unentangled $n$-qubit states, which are direct product states of
+the form 
+\begin{equation}
+\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}\,.\label{dqcNqUntg.eq}
+\end{equation}
+Without regard to normalization, there are $\left(p^{4}\right)^{n}$
+possible unentangled states out of the total of $p^{2\times2^{n}}$
+states noted above. When we normalize the individual product states
+to unit norm, the norm of the entire $n$-qubit state becomes the
+product of those unit norms, and is automatically normalized to one.
+We have already seen that each single-qubit normalized state in the
+tensor product \Eq{dqcNqUntg.eq} has precisely $p\left(p-1\right)$
+irreducible components due to $D=2$ case in Eq.~(\ref{eq:numberOfIrreducibleStates}).
+
+\subsubsection{Completely Unentangled States and the Discrete Bloch Sphere}
+
+In effect, the irreducible states for unentangled $n$-qubit configurations
+reduce to a single Bloch sphere for each one-qubit component $\ket{\psi_{j}}$,
+and thus the whole set of states is defined by an $n$-tuple of discrete
+Bloch sphere coordinates. Since each Bloch sphere in $\Fpp$ has $p\left(p-1\right)$
+distinct irreducible components, we have 
+\begin{equation}
+\mbox{{\bf Count of Unentangled States}}=p^{n}\left(p-1\right)^{n}\,.\label{eq:CountUnentangledStates}
+\end{equation}
+
+According to Eq.~(\ref{eq:numberOfIrreducibleStates}), we know that
+the total number of irreducible states (points in the generalized
+$\DCP{2^{n}-1}$ Bloch sphere) for an $n$-qubit state is $\frac{p^{2^{n}-1}\left(p^{2^{n}}-1\right)}{p+1}$,
+and so the number of states containing some measure of entanglement
+is 
+\begin{equation}
+\mbox{{\bf Count of Entangled States}}=\frac{p^{2^{n}-1}\left(p^{2^{n}}-1\right)}{p+1}-p^{n}\left(p-1\right)^{n}\,.
+\end{equation}
+Therefore a very small fraction of the unit norm states are unentangled.
+
+\subsubsection{Maximal entanglement}
+
+Equation~(\ref{purityMeasure.eq}) for $P_{\fh}$ includes a normalization
+factor~$\frac{1}{n}$. In the discrete case, this normalization factor
+is undefined when $p\mid n$. Equation~(\ref{purityMeasure.eq})
+also includes a summation of $n$ terms. In the discrete case, certainly
+when $p\mid n$ but also in other cases, this summation may vanish
+in the field even if the individual summands are non-zero. These anomalies
+are irrelevant for the classification of unentangled states as this
+computation is performed by directly checking the possibility of direct
+decomposition into product states, disregarding equation~(\ref{purityMeasure.eq}).
+
+For maximally entangled states, the purity calculation in conventional
+quantum mechanics using equation~(\ref{purityMeasure.eq}) produces
+0. Given the above observations, in a discrete field, equation~(\ref{purityMeasure.eq})
+may be undefined or may report a purity of 0 even for partially entangled
+states. For example, the normalized 5-qubit state $\ket{\Psi}=\left(1-\rmi\right)\left(\ket{00}+\ket{11}\right)\otimes\ket{000}$
+has $P_{\fh}=0$ for $p=3$, and is not maximally entangled because
+only the first two qubits are entangled. In the discrete case, we
+therefore check for maximally entangled states using the following
+equations~\cite{Gardiner2014}, 
+\begin{equation}
+\forall j,\forall\eta\in\left\{ x,y,z\right\} ,\expval{\jthSubsystem{\sigma}[\eta]{j}}^{2}=0\textrm{ ,}\label{eq:john}
+\end{equation}
+which avoids the normalization factor and simply checks that each
+summand is 0.
+
+We now implement these procedures to enumerate the maximally entangled
+states for the specific cases for $n=2,3$ and compare these to the
+counts for product states. We have verified explicitly in Eq.~(\ref{eq:CountUnentangledStates})
+that the numbers of unit-norm product states for $n=2$, $p=\{3,7,11,19,\ldots\}$
+are 
+\begin{equation}
+(p+1)p^{2}(p-1)^{2}=\{144,14\,112,145\,200,2339\,280,\ldots\}\,,
+\end{equation}
+and for general $n$, $(p+1)p^{n}(p-1)^{n}$. The irreducible state
+counts are reduced by $(p+1)$, giving 
+\begin{equation}
+p^{2}(p-1)^{2}=\{36,1764,12\,100,116\,964,\ldots\}\,,
+\end{equation}
+and in general for $n$-qubits, there are $p^{n}\left(p-1\right)^{n}$
+instances of pure product states.
+
+Performing the computation using equation (\ref{eq:john}), we find
+the numbers of maximally entangled states for two qubits to be 
+\begin{equation}
+p\left(p^{2}-1\right)\left(p+1\right)=\left\{ 96,2688,15\,840,136\,800,\ldots\right\} \,.
+\end{equation}
+The irreducible state counts for maximal entanglement are reduced
+by $\left(p+1\right)$, giving, for $n=2$, 
+\begin{equation}
+p\left(p^{2}-1\right)=\left\{ 24,336,1320,6840,\ldots\right\} \,.
+\end{equation}
+For three qubits, there are $p^{3}\left(p^{4}-1\right)\left(p+1\right)$
+(total) and $p^{3}\left(p^{4}-1\right)$ (irreducible) instances of
+pure maximally entangled states, while the general formula for 4-qubit
+states remains unclear.
+
+Therefore, the ratio of maximally entangled to product states is 
+\begin{equation}
+\frac{\textbf{Max entangled}}{\textbf{Product}}=\frac{p+1}{p\left(p-1\right)}\textrm{ and }\frac{\left(p^{2}+1\right)\left(p+1\right)}{\left(p-1\right)^{2}}
+\end{equation}
+for $n=2$ and $3$, respectively.
+
+\section{Discrete Quantum Computing (I)\label{discretequantumcomputingI}}
+
+Given a complexified finite field $\ff{p^{2}}$ and its Hermitian
+\dotprod\  (Eq.~\eqref{innerprod}) much of the structure of conventional
+quantum computing can be recovered. For example, the smallest field~$\ff{3^{2}}$
+is already rich enough to express the standard Deutsch-Jozsa algorithm
+\cite{DeutschJozsa1992,544199,Jaeger2007}, which requires only normalized
+versions of vectors or matrices with the scalars $0$, $1$, and $-1$.
+Similarly, other deterministic quantum algorithms (algorithms for
+which we may determine the outcome with certainty), such as Simon's
+\cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007} and Bernstein-Vazirani
+\cite{Bernstein:1993:QCT:167088.167097,Mermin2007}, perform as desired.
+In the following subsection, we will present the discrete Deutsch
+algorithm as an example. However, this quantum computing model is
+still different from the conventional one. On one hand, algorithms
+such as Grover's search \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}
+will not work in the usual way because we lack (the notion of) ordered
+angles and probability in general. On the other hand, this computational
+model still leads to excessive computational power for the unstructured
+database search problem for certain database sizes.\todo{Gil Kalai
+thought it would be interested if we can so Simon's algorithm in DQC(I).
+Since I need to re-type everything, let's postpone this idea for a
+while...}
+
+\subsection{Discrete Deutsch algorithm}
+
+Although having no realistic application, the Deutsch algorithm is
+the first quantum algorithm which outperforms any possible classical
+algorithm for the Deutsch problem \cite{Deutsch1985,544199,Mermin2007}.
+The Deutsch problem is to decide whether a function $f:\boolt\rightarrow\boolt$
+is constant or balanced. As listed in Table~\ref{tab:Possible-f},
+we have only $4$ different $f$: $2$ of them are constant while
+another $2$ are balanced. Similar to our $\usat$ algorithm in Sec.~\ref{modalquantumcomputing},
+we start by representing $f$ as a Deutsch black box $U_{f}$ in the
+middle of the quantum circuit, Figure~\ref{fig:Quantum-Circuit-Deutsch}.
+To explain why this circuit solves the Deutsch problem, we then compute
+the state in each step explicitly, and express the Dirac bracket notation
+with its matrix representation in the computational basis $\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $
+parallelly.
+\begin{table}
+\noindent \centering{}\caption{\label{tab:Possible-f}Possible $f$ for Deutsch black box $U_{f}$}
+\begin{tabular}{ccccc}
+\toprule 
+\addlinespace
+Input & $f_{1}$ & $f_{2}$ & $f_{3}$ & $f_{4}$\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+$\bfalse$ & $\bfalse$ & $\bfalse$ & $\btrue$ & $\btrue$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$\btrue$ & $\bfalse$ & $\btrue$ & $\bfalse$ & $\btrue$\tabularnewline\addlinespace
+\addlinespace
+\midrule 
+\addlinespace
+constant or balanced? & constant & balanced & balanced & constant\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}
+\end{table}
+\todo{We typeset $U_{f}$ either directly or use macro \textbackslash uf,
+but the definition of \textbackslash uf has a negative space between
+$U$ and $f$ which is different from U\_\{f\}... I need to understand
+whether the negative space is necessary or not, or whether the negative
+space has any semantic meaning...}
+\begin{figure}[t]
+\noindent \centering{}
 \[
-\frac{p^{2^{n}-1}(p^{2^{n}}-1)}{p+1}=p^{2^{n}-1}(p-1)\,\prod_{k=1}^{n-1}(p^{2^{k}}+1)
+\begin{array}{c}
+\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{ & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd]\\
+\lstick{\ket{1}} & \qw & \gate{H} & \qw & \multigate{1}{\uf} & \qw & \gate{H^{\dagger}} & \qw & \multimeasureD{1}{\text{measure}}\\
+\lstick{\ket{0}} & \qw & \gate{H} & \qw & \ghost{\uf} & \qw & \gate{H^{\dagger}} & \qw & \ghost{\text{measure}}\\
+ & \push{\ket{\Phi_{1}}} &  & \push{\ket{\Phi_{2}}} &  & \push{\ket{\Phi_{3}}} &  & \push{\ket{\Phi_{4}}}
+}
+\end{array}
 \]
-as the total count of unique irreducible states in a discrete $n$-qubit
-configuration (see \ref{appI.sec}). The resulting object is precisely
-the discrete version of $\CP{D-1}$, which we might call a \textit{discrete
-complex projective space\/} or $\DCP{D-1}$, where $D=2^{n}$ as
-usual.
-
-\section{Discrete Quantum Computing (I)\label{discretequantumcomputingI}}
-
-Given a complexified finite field $\ff{p^{2}}$ and its Hermitian
-\dotprod\
-(Eq.~\eqref{innerprod}) much of the structure of conventional quantum
-computing can be recovered. For example, the smallest field~$\ff{3^{2}}$
-is already rich enough to express the standard Deutsch-Jozsa~\cite{NCbook}
-algorithm, which requires only normalized versions of vectors or matrices
-with the scalars $0$, $1$, and $-1$. Similarly, other deterministic
-quantum algorithms (algorithms for which we may determine the outcome
-with certainty), such as Simon's and Bernstein-Vazirani, perform as
-desired~\cite{simon}. Algorithms such as Grover's search will not
-work in the usual way because we lack (the notion of) ordered angles
-and probability in general.
+\caption{\label{fig:Quantum-Circuit-Deutsch}Quantum Circuit for Deutsch Algorithm.}
+\end{figure}
+
+First, a 2-qubit pure state is initialized to $\ket{\Phi_{1}}=\ket{1}\ket{0}=\left(\begin{smallmatrix}0\\
+1
+\end{smallmatrix}\right)\otimes\left(\begin{smallmatrix}1\\
+0
+\end{smallmatrix}\right)$.
+
+Second, on both initialized qubits, we apply the Hadamard matrix $H=\frac{1}{\alpha}\left(\begin{smallmatrix}1 & 1\\
+1 & -1
+\end{smallmatrix}\right)$ over $\Fpp$, where $\alpha=\fnorm*{2}$ is the principal inverse
+field norm which is used to replace the square root $\sqrt{2}$ in
+the conventional Hadamard matrix $\frac{1}{\sqrt{2}}\left(\begin{smallmatrix}1 & 1\\
+1 & -1
+\end{smallmatrix}\right)$ as discussed in Sec.~\ref{subsec:Vector-Spaces}. The second step
+produces
+\[
+\ket{\Phi_{2}}=\left(H\otimes H\right)\ket{\Phi_{1}}=\left[\frac{1}{\alpha}\begin{pmatrix}1 & 1\\
+1 & -1
+\end{pmatrix}\begin{pmatrix}0\\
+1
+\end{pmatrix}\right]\otimes\left[\frac{1}{\alpha}\begin{pmatrix}1 & 1\\
+1 & -1
+\end{pmatrix}\begin{pmatrix}1\\
+0
+\end{pmatrix}\right]=\ket{-}\ket{+}\,,
+\]
+where
+\begin{align}
+\ket{+} & =\frac{1}{\alpha}\begin{pmatrix}1\\
+1
+\end{pmatrix}=\frac{\ket{0}+\ket{1}}{\alpha}\,, & \ket{-} & =\frac{1}{\alpha}\begin{pmatrix}1\\
+-1
+\end{pmatrix}=\frac{\ket{0}-\ket{1}}{\alpha}\,.
+\end{align}
+
+Third, the Deutsch black box~$U_{f}$ is applied to the state $\ket{\Phi_{2}}$.
+According to Eq.~(\ref{eq:DeutschBox}), these Deutsch black box
+will be used to apply exclusive disjunction on the first qubit, where
+we respectively identify $\bfalse$ and $\btrue$ as $0$ and $1$
+as usual. Since our first qubit is $\ket{-}$, the value $f\left(x\right)$
+could be moved outside as a phase no matter $f\left(x\right)$ is
+$\bfalse$ or $\btrue$:
+\begin{equation}
+\begin{aligned}U_{f}\ket{-}\ket{x} & =\tfrac{1}{\alpha}\left[\ket{0\oplus f\left(x\right)}\ket{x}-\ket{1\oplus f\left(x\right)}\ket{x}\right]\\
+ & =\begin{cases}
+\frac{1}{\alpha}\left[\ket{0}\ket{x}-\ket{1}\ket{x}\right] & \textrm{if }f\left(x\right)=\bfalse=0\,;\\
+\frac{1}{\alpha}\left[\ket{1}\ket{x}-\ket{0}\ket{x}\right] & \textrm{if }f\left(x\right)=\btrue=1
+\end{cases}\\
+ & =\left(-1\right)^{f\left(x\right)}\ket{-}\ket{x}\,.
+\end{aligned}
+\end{equation}
+Then, $\ket{\Phi_{3}}$ can be evaluated as follow:
+\begin{equation}
+\begin{aligned}\ket{\Phi_{3}} & =U_{f}\ket{-}\ket{+}=\tfrac{1}{\alpha}\left[U_{f}\ket{-}\ket{0}+U_{f}\ket{-}\ket{1}\right]\\
+ & =\tfrac{1}{\alpha}\left[\left(-1\right)^{f\left(0\right)}\ket{-}\ket{0}+\left(-1\right)^{f\left(1\right)}\ket{-}\ket{1}\right]\\
+ & =\begin{cases}
+\left(-1\right)^{f\left(0\right)}\ket{-}\ket{+} & \textrm{if }f\left(0\right)=f\left(1\right)\,;\\
+\left(-1\right)^{f\left(0\right)}\ket{-}\ket{-} & \textrm{if }f\left(0\right)\ne f\left(1\right)\,.
+\end{cases}
+\end{aligned}
+\end{equation}
+
+Finally, $\ket{\Phi_{4}}$ can then be obtained by applying the Hermitian
+conjugate of Hadamard matrix $H^{\dagger}=\frac{1}{\alpha^{*}}\left(\begin{smallmatrix}1 & 1\\
+1 & -1
+\end{smallmatrix}\right)$ on both qubits. If $f\left(0\right)=f\left(1\right)$, i.e., $f$
+is constant, we have 
+\[
+\ket{\Phi_{4}}=\left(-1\right)^{f\left(0\right)}\left[\dfrac{1}{\alpha^{*}}\begin{pmatrix}1 & 1\\
+1 & -1
+\end{pmatrix}\frac{1}{\alpha}\begin{pmatrix}1\\
+-1
+\end{pmatrix}\right]\otimes\left[\dfrac{1}{\alpha^{*}}\begin{pmatrix}1 & 1\\
+1 & -1
+\end{pmatrix}\frac{1}{\alpha}\begin{pmatrix}1\\
+1
+\end{pmatrix}\right]=\left(-1\right)^{f\left(0\right)}\ket{1}\ket{0}\,;
+\]
+if $f\left(0\right)\ne f\left(1\right)$, i.e., $f$ is balanced,
+we have 
+\[
+\ket{\Phi_{4}}=\left(-1\right)^{f\left(0\right)}\left[\dfrac{1}{\alpha^{*}}\begin{pmatrix}1 & 1\\
+1 & -1
+\end{pmatrix}\frac{1}{\alpha}\begin{pmatrix}1\\
+-1
+\end{pmatrix}\right]\otimes\left[\dfrac{1}{\alpha^{*}}\begin{pmatrix}1 & 1\\
+1 & -1
+\end{pmatrix}\frac{1}{\alpha}\begin{pmatrix}1\\
+-1
+\end{pmatrix}\right]=\left(-1\right)^{f\left(0\right)}\ket{1}\ket{1}\,.
+\]
+Hence, we can decide whether $f$ is constant or balanced by measuring
+$\ket{\Phi_{4}}$ in the computational basis.
+
+\subsection{Partial \usat\ Algorithm}
 
 \begin{figure}[t]
+\centering{}
 \[
 \xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \qw & \multimeasureD{3}{\text{measure}}\\
-\lstick{x_{1}=\ket{0}} & \multigate{2}{H} & \ghost{\uf} & \multigate{2}{H} & \ghost{\text{measure}}\\
-\lstick{\ldots} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}\\
-\lstick{x_{n}=\ket{0}} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}
+\lstick{x_{1}=\ket{0}} & \multigate{2}{\otimes H} & \ghost{\uf} & \multigate{2}{\otimes H^{\dagger}} & \ghost{\text{measure}}\\
+\lstick{\ldots} & \ghost{\otimes H} & \ghost{\uf} & \ghost{\otimes H^{\dagger}} & \ghost{\text{measure}}\\
+\lstick{x_{n}=\ket{0}} & \ghost{\otimes H} & \ghost{\uf} & \ghost{\otimes H^{\dagger}} & \ghost{\text{measure}}
 }
 \]
-\caption[]{Circuit for black box \usat\ in discrete quantum computing.}
-\label{fig:dbsearch} 
+\caption{\label{fig:dbsearch}Circuit for black box \usat\ in discrete quantum
+computing.}
 \end{figure}
-
 It is possible, in some situations, to exploit the cyclic behavior
 of the field to creatively cancel probability amplitudes and solve
-problems with what again appears to be ``supernatural'' efficiency.
+problems with what again appears to be “supernatural” efficiency.
 We illustrate this behavior with the algorithm in Fig.~\ref{fig:dbsearch},
 which is a variant of the one in Fig.~\ref{fig:alg}. Unlike the
-modal quantum theory algorithm, the new algorithm does not always
-succeed deterministically using a constant number of black box evaluations.
+modal quantum algorithm, the new algorithm does not always succeed
+deterministically using a constant number of black box evaluations.
 We can, however, show that supernatural behavior occurs if the characteristic
@@
 additional interference processes that happen because of the possibility
-of ``wrapping around'' due to modular arithmetic. We do not know,
+of “wrapping around” due to modular arithmetic. We do not know,
 in general, whether this version of discrete quantum computing actually
-enables the rapid solution of NP-complete problems.
-
-\section{Discrete Quantum Theory and Computing (II)}
-
-Our third model, discrete quantum theory (II)~\cite{DQT2014}, restricts
-states in some local region of $\mathbb{F}_{p^{2}}^{2^{n}}$. Within
-a local region, a notion of inner product and probability could be
-recovered. Its discrete quantum computing can be further applied to
-the deterministic Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007}
-and the probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
-
-\section{Toward Discrete Quantum Probability\label{sec:Toward-IVPM}}
-
-When people tried to define quantum probability over finite fields,
-people tended to treat the original Born rule as an axiom, and tried
-to modify it to get a discrete Born rule \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644,DQT2014,Ellerman2016a}.
-However, any modified Born rule could hardly work on the whole vector
-space, since there is no inner product on the whole vector space over
-finite fields. Instead of treating the Born rule as an axiom, the
-Born rule can actually be deduced from a set of abstract definitions
-and axioms according to Gleason's theorem. Although we might hope
-to deduce a discrete Born rule directly from a similar set of definitions
-and axioms, no discrete Born rule satisfies certain properties motivated
-by Gleason's theorem with infinitely precise real-number probability~\cite{Gardiner2014}.
-Since the state spaces are now discrete and finite, this suggests
-us to consider a discrete Born rule mapping to finite number of intervals
-called interval-valued probability~\cite{JamisonLodwick2004,THOS2017}.
+enables the rapid solution of $\NP$-complete problems.
+
+\section{Discrete Quantum Theory (II): Inner Product Space}
+
+\label{discretequantumtheoryIIa}
+
+We next discuss an approach using finite complexifiable fields that
+conditionally resolves the inner product condition~\ref{enu:inner-product-positive-definite}
+discussed in Sec.~\ref{subsec:Vector-Spaces}, which is violated
+by the theory just presented. A possible path is suggested by the
+work of Reisler and Smith~\cite{ReislerSmith1969}. The general idea
+is that while the cyclic properties of arithmetic in finite fields
+make it impossible to \emph{globally} obtain the desired properties
+of the conventional Hilbert space inner product, it \textit{is} possible
+to recover them \emph{locally}, thereby restoring, with some restrictions,
+all the usual properties of the inner product needed for conventional
+quantum mechanics and conventional quantum computing. As the size
+of the discrete field becomes large, the size of the locally valid
+computational framework grows as well, leading to the \emph{effective
+emergence of conventional quantum theory}. We next briefly outline
+such a context for local orderable subspaces of a finite field, and
+introduce an improvement on the original method~\cite{ReislerSmith1969}
+suggested by recent number theory resources~\cite{Sloane2005}.
+
+Let us first note that the range of the quadratic map, $\set{x^{2}\bmod p}{x\in\ff{p}}$,
+is always one-half of the non-zero elements of $\ff{p}$, and is the
+set of elements with square roots in the field. This is the set of
+\emph{quadratic residues}, and the complementary set (the other half
+of the non-zero field elements) is the set of \emph{quadratic non-residues}.
+For example, in $\ff{7}$, the elements $\left\{ 1,2,4\right\} $
+are considered positive as they have the square roots $\left\{ 1,3,2\right\} $
+respectively; the remaining elements $\left\{ 3,5,6\right\} $ do
+not have square roots in the field. What is interesting is that if
+we have an uninterrupted sequence of numbers that are all quadratic
+residues, then we can define a \textit{transitive order}, with $a>c$
+if $a>b$ and $b>c$, provided $a-b$, $b-c$, and $a-c$ are all
+quadratic residues.\todo{Should we remove the quadratic residue part?
+Since we never use take the square roots of numbers in order range
+later, whether they are the quadratic residues or not doesn't really
+matter...}
+
+As a concrete example, consider a finite field in which the sequential
+elements $0$, $1$, $2$, $3$, \ldots , and $k-1$ are all quadratic
+residues (including $0$). Then any sequence of odd length~$k$ and
+centered around an arbitrary $x\in\ff{p}$, i.e., $S_{x}\left(k\right)=x-\frac{k-1}{2}$,
+\ldots , $x-2$, $x-1$, $x$, $x+1$, $x+2$, \ldots , $x+\frac{k-1}{2}$,
+is \textit{transitively ordered}. Indeed, we have $\left(x+1\right)-x=1$
+which is a quadratic residue and hence $x+1>x$. Similarly, $x-\left(x-1\right)=1$
+and hence $x>x-1$. Also $\left(x+1\right)-\left(x-1\right)=2$ which
+is a quadratic residue and hence $x+1>x-1$. Clearly this process
+may be continued to show that the sequence $S_{x}\left(k\right)$
+is transitively ordered. We can construct examples using the sequence
+A000229 in the encyclopedia of integer sequences \cite{Sloane2005}\footnote{For computational purposes, this sequence is preferable to the one
+proposed by Reisler and Smith~\cite{ReislerSmith1969} because it
+produces smaller primes. Their work showed that a sufficient condition
+on finite fields to produce sequences of quadratic residues is to
+further constrain the underlying prime numbers to be of the form $8\prod_{i=1}^{m}q_{i}-1$,
+where $q_{i}$ is the $i$th odd prime. While all such primes are
+of the form $4\ell+3$, the set is severely restricted to astronomical
+numbers because the first few such primes are $7$, $23$, $839$,
+$9239$, $2042039$, \ldots}. The $n$th element of that sequence (which must be prime) is the
+least number such that the $n$th prime is the \emph{least} quadratic
+non-residue for the given element. The first few elements of this
+sequence are listed in the top row of Table~\ref{pseq}. The next
+row lists the number $k$ of transitively ordered consecutive elements
+in that field, and $\pi\left(k\right)$ in the bottom row is the prime
+counting function (the number of primes up to $k$).
+\begin{table}
+\noindent \centering{}%
+\begin{tabular}{cccccccccccc}
+\toprule 
+\addlinespace
+$p$ & $3$ & $7$ & $23$ & $71$ & $311$ & $479$ & $1559$ & $5711$ & $10559$ & $18191$ & \ldots\tabularnewline\addlinespace
+\addlinespace
+\midrule 
+\addlinespace
+$k$ & ${\bf 2}$ & ${\bf 3}$ & ${\bf 5}$ & ${\bf 7}$ & ${\bf 11}$ & ${\bf 13}$ & ${\bf 17}$ & ${\bf 19}$ & ${\bf 23}$ & ${\bf 29}$ & \ldots\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+$\pi\left(k\right)$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ & $8$ & $9$ & $10$ & \ldots\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}\caption{\label{pseq}Number $k$ of transitively ordered elements for a given
+field $\ff{p}$.}
+\end{table}
+
+As an example, consider the field $\ff{23}$. Looking at the squares
+of the numbers $\ff{23}=\left\{ 0,\ldots,22\right\} $ modulo 23,
+we find the $2$-centered uninterrupted sequence $S_{2}\left(5\right)=\left\{ 0,1,2,3,4\right\} $,
+followed by $5$, which is both the smallest quadratic non-residue
+and the size of the uninterrupted sequence of quadratic residues (including
+$0$) of interest. In particular, it is possible to construct a total
+order for the elements $S_{0}\left(5\right)=\left\{ -2,-1,0,1,2\right\} $
+in the fields $\ff{23}$, $\ff{71}$, $\ff{311}$, etc., but not in
+the smaller fields $\ff{3}$ and $\ff{7}$.
+
+Given a $D$-dimensional vector space over $\ff{p^{2}}$ where~$p$
+is one of the primes above, it is possible to define a \emph{region}
+over which an inner product and norm can be identified. Let the length
+of the sequence of quadratic residues be $k$. The region of interest
+includes all vectors $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$,
+for which $D<p-\frac{k-1}{2}$ and each $\alpha_{i}$ satisfies 
+\begin{equation}
+D\,\fnorm{\alpha_{i}}=D\,\left(a_{i}^{2}+b_{i}^{2}\right)\leq\frac{k-1}{2}\,,\label{eq:region}
+\end{equation}
+with $a_{i}$ and $b_{i}$ drawn from the set $S_{0}\left(k\right)$.
+Consider, for example, $\ff{311^{2}}$ ($p=311$, $k=11$). We find
+that we can trade off the dimension $D$ of the vector space against
+the range of probability amplitudes available for each $\alpha_{i}$
+in Table~\ref{table_allowed}.
+\begin{table}
+\noindent \centering{}%
+\begin{tabular}{ll}
+\toprule 
+\addlinespace
+ & allowed probability amplitudes $F^{D}\left(k\right)$ \tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+$D=1$  & $F^{1}\left(11\right)=\left\{ 0,\pm1,\pm2,\pm\rmi,\pm2\rmi,(\pm1\pm\rmi),(\pm1\pm2\rmi),(\pm2\pm\rmi)\right\} $\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$D=2$  & $F^{2}\left(11\right)=\left\{ 0,\pm1,\pm\rmi,(\pm1\pm\rmi)\right\} $ \tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$D=3$  & $F^{3}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$D=4$  & $F^{4}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$D=5$  & $F^{5}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$D\geq6$  & $F^{D}\left(11\right)=\left\{ 0\right\} $ \tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}\caption{\label{table_allowed}Allowed probability amplitudes for different
+vector space dimensions $D$ and $k=11$.}
+\end{table}
+
+We can now verify, by using Table~\ref{table_allowed}, that for
+any vector $\ket{\Psi}$ in the selected region the value of $\ip{\Psi}{\Psi}$
+is $\geq0$ and vanishes precisely when $\ket{\Psi}$ is the zero
+vector. Thus, in the selected region, condition~\ref{enu:inner-product-positive-definite}
+is established. Although the set of vectors defined over that region
+is not closed under addition, and hence the set is not a vector subspace,
+we can still have a theory by restricting our computations. In other
+words, \emph{as long as our computation remains within the selected
+region}, we may pretend to have an inner product space. The salient
+properties of conventional quantum mechanics emerge, but the price
+to be paid is that the state space is no longer a vector space. This
+is basically a rigorous formulation of Schwinger's intuition (See,
+in particular, Chapter 1, Section 1.16. in \cite{schwinger2001quantum}).
+
+Readers with backgrounds in computer science or numerical analysis
+will notice, significantly, that this model for discrete quantum computing
+is reminiscent of practical computing with a classic microprocessor
+having only integer arithmetic and a limited word length. We cannot
+perform a division having a fractional result at all, since there
+are no fractional representations; we do have the basic constants
+zero and one, as well as positive and negative numbers, but multiplications
+or additions producing results outside the integer range wrap around
+modulo the word length and typically yield nonsense. This implies
+that, for the local discrete model, we must accept an operational
+world view that \textit{has no awareness of the value of $p$}, and
+depends on having set up in advance an environment with a field size,
+analogous to the word size of a microprocessor, that happily processes
+\textit{any} calculation we are prepared to perform. This is the key
+step, though it may seem strange because we are accustomed to arithmetic
+with real numbers: we list the calculations that must be performed
+in our theory, discover an \textit{adequate size of the processor
+word} — implying a possibly ridiculously large value of $p$ chosen
+as described above — and from that point on, we calculate necessarily
+valid values within that processor, never referring in any way to
+$p$ itself in the sequel.
+
+\section{Discrete Quantum Theory (II): Cardinal Probability}
+
+\label{discretequantumtheoryIIb}
+
+The final issue that must be addressed in the discrete theory put
+forward in Section~\ref{discretequantumtheoryIIa} concerns measurement.
+To recap, within the theory, states are $D$-dimensional vectors with
+complex discrete-valued amplitudes drawn from a totally-ordered range,
+$F^{D}(k)$, in the underlying finite field. These states possess,
+by construction, having field norms in the non-negative integers,
+all in the ordered range of Eq.~\eqref{eq:region}, and hence potentially
+produce probabilities that can be ordered. Our point is that, although
+the mathematical framework of conventional quantum mechanics relies
+on infinite precision probabilities, it is impossible in practice
+to measure exact equality of real numbers — we can only achieve an
+approximation within measurement accuracy. Significantly, when we
+use finite fields, this measurement accuracy will be encoded in the
+size of the finite field used for measurements.
+
+Given a $D$-dimensional Hilbert space in conventional quantum theory,
+although we can measure the probability for every eigenprojector of
+an observable as discussed in Sec.~\ref{sec:fuzzy}, our previous
+quantum circuits in Figures~\ref{fig:alg}, \ref{fig:Quantum-Circuit-Deutsch},
+and \ref{fig:dbsearch} always measure in the computational basis
+$\left\{ \ket{0},\ldots,\ket{i},\ldots,\ket{D-1}\right\} $. Indeed,
+it is sufficient to only consider measuring in the computational basis
+because measuring in another basis is the same as applying a quantum
+gate and measuring in the computational basis. In this situation,
+the Born rule for pure states, Eq.~(\ref{eq:Born}), can be simplified
+as
+\begin{equation}
+\muB_{\Psi}\left(\proj{i}\right)\equiv\muB_{\Psi}\left(i\right)=\frac{\ip{\Psi}{i}\ip{i}{\Psi}}{\ip{\Psi}{\Psi}}=\frac{\left|\ip{i}{\Psi}\right|^{2}}{\ip{\Psi}{\Psi}}=\frac{\left|\alpha_{i}\right|^{2}}{\ip{\Psi}{\Psi}}\,,\label{eq:Born-ComputationalBasis}
+\end{equation}
+where $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$
+is an unnormalized state. Hereafter, we will simplify by calling $\muB_{\Psi}\left(i\right)$
+the probability of measuring $\ket{i}$.
+
+Although division is not an allowed operation for the elements in
+the an ordered region, following the standard procedure to define
+a conventional fraction as a pair of integers \cites{Artin1991}{DummitFoote2004}{hottbook2013}{Wolfram2016},
+we could define a \emph{cardinal probability} as a pair of order-region
+elements as well:
+\begin{equation}
+\muC_{\Psi}\left(i\right)=\cardp{\fnorm{\ip{i}{\Psi}}}{\fnorm{\ket{\Psi}}}=\cardp{\fnorm{\alpha_{i}}}{\fnorm{\ket{\Psi}}}\,,\label{eq:cardinalProbability}
+\end{equation}
+where every probability amplitude $\alpha_{i}\in F^{D}\left(k\right)$
+so that both $\fnorm{\alpha_{i}}$ and $\fnorm{\ket{\Psi}}$ are within
+the order range $S_{0}\left(k\right)$, and $\muC_{\Psi}\left(i\right)$
+is called the cardinal probability of measuring $\ket{i}$. For example,
+let $p=311$, $k=11$, and $D=2$. The permitted range is $S_{0}\left(11\right)=\left\{ -5,\ldots,-1,0,1,\ldots,5\right\} $,
+given the dimension $D=2$, the allowed probability amplitude coefficients
+are $F^{2}\left(11\right)=\left\{ 0,\pm1,\pm\rmi,\left(\pm1\pm\rmi\right)\right\} $
+(see Table \ref{table_allowed}). Now the cardinal probabilities of
+several representative one-qubit states are listed in Table~\ref{f11-proj.fig}.
+\begin{table}
+\noindent \centering{}%
+\begin{tabular}{cccccc}
+\toprule 
+\addlinespace
+$\ket{\Psi}$ & $\fnorm{\ip{0}{\Psi}}$ & $\fnorm{\ip{1}{\Psi}}$ & $\fnorm{\ket{\Psi}}$ & $\muC_{\Psi}\left(0\right)$ & $\muC_{\Psi}\left(1\right)$\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+$1\ket{0}$ & $1$ & $0$ & $1$ & $\cardp{1}{1}$ & $\cardp{0}{1}$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$1\ket{0}+1\ket{1}$ & $1$ & $1$ & $2$ & $\cardp{1}{2}$ & $\cardp{1}{2}$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$1\ket{0}+(1+\rmi)\ket{1}$ & $1$ & $2$ & $3$ & $\cardp{1}{3}$ & $\cardp{2}{3}$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$(1-\rmi)\ket{0}+(1+\rmi)\ket{1}$ & $2$ & $2$ & $4$ & $\cardp{2}{4}$ & $\cardp{2}{4}$\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}\caption{\label{f11-proj.fig}Field norms and probabilities for one-qubit states
+$\ket{\Psi}$ in $F^{2}\left(11\right)$.}
+\end{table}
+
+When measuring cardinal probabilities, \textit{inequalities} can be
+preserved with appropriate resources (in the form of a sufficiently
+large choice of the field), while \textit{equalities} cannot be guaranteed
+in the theory, and in fact can be represented as \textit{inequalities
+of any order}. That is, given two cardinal probabilities $\cardp{\fnorm{\alpha_{i}}}{\fnorm{\ket{\Psi}}}$
+and $\cardp{\fnorm{\alpha_{j}}}{\fnorm{\ket{\Psi}}}$ with the same
+“denominator”, $\fnorm{\alpha_{i}}>\fnorm{\alpha_{j}}$ physically
+means it is more likely to measure $\ket{i}$ than $\ket{j}$ if we
+have enough resource; $\fnorm{\alpha_{i}}=\fnorm{\alpha_{j}}$ means
+the experimental results might not always favor $\ket{i}$ or $\ket{j}$
+no matter how much resource we use. The same principle can also apply
+to two cardinal probabilities with the different “denominator”.
+The details of the comparison can easily formulated by following the
+standard procedure \cites{Artin1991}{DummitFoote2004}{hottbook2013}{Wolfram2016}
+and will left as an exercise for the readers.
+
+\section{Discrete Quantum Computing (II)}
+
+\label{discretequantumcomputingII}
+
+We now examine two particularly important types of examples within
+the discrete theory of the previous section: the first is the deterministic
+Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,544199,Jaeger2007},
+which determines the balanced or unbalanced nature of an unknown function
+with a single measurement step ($O\left(1\right)$), and the second
+is the (normally) probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007},
+determining the result of an unstructured search in $O\left(\sqrt{N}\right)$
+time. In the following, we use $k$ to denote the upper bound of the
+ordered range of integers needed to perform a given calculation; this
+in turn is assumed to be implemented using a choice of a finite prime
+number $p$ that supports calculation in the range of~$k$.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Discrete Deutsch-Jozsa Algorithm: Deterministic}
+
+To examine the Deutsch-Jozsa algorithm in the discrete theory of the
+previous section, we assume we are given a classical function $f:\boolt^{n}\rightarrow\boolt$,
+and are told that $f$ is either constant or balanced \cite{DeutschJozsa1992,544199,Jaeger2007}.
+The algorithm is expressed in a space of dimension $D=2^{n+1}$: it
+begins with the $n+1$ qubit state $\ket{1}\ket{\overline{0}}$ where
+the overline denotes a sequence of length~$n$. A straightforward
+calculation~\cite{544199} shows that the final state is\footnote{Note that the algorithm in reference~\cite{544199} makes use of
+the Hadamard matrix. We have eliminated the factor $\frac{1}{\sqrt{2}}$
+to ensure that all quantities are expressed in terms of integers.
+Also notice that the positioning of the initial qubit state $\ket{1}$
+is reversed from~\cite{544199}. }\todo{A little bit more explanation?}
+\begin{equation}
+\sum_{\overline{z}\in\left\{ 0,1\right\} ^{n}}\sum_{\overline{x}\in\left\{ 0,1\right\} ^{n}}\left(-1\right)^{f\left(\overline{x}\right)+\overline{x}\cdot\overline{z}}\left(\ket{0}\ket{\overline{z}}-\ket{1}\ket{\overline{z}}\right)\,,
+\end{equation}
+and that its field norm is $2^{n+1}$.\todo{Verify?} To make sure
+that the algorithm works properly, we note that all the probability
+amplitudes involved in the calculation are in the range $-2^{n}$,
+\ldots , $2^{n}$ and therefore, by Eq.~\eqref{eq:region}, we get
+the following constraint on the size of the ordered region in the
+finite field: 
+\begin{eqnarray}
+2^{n+1}\left(2^{n}\right)^{2}\leq\frac{k-1}{2} & \Leftrightarrow & k\geq2^{3n+2}+1\,.
+\end{eqnarray}
+
+Now we need to choose a prime number $p$ that supports calculation
+in the range of $k$. Assume that $k$ is the least prime satisfying
+$k\geq2^{3n+2}+1$, and let $p$ be the $\pi\left(k\right)$th element
+of the sequence A000229~\cite{Sloane2005}. We argue that no prime
+less than this value of $p$ can support calculation in the ordered
+range of $k$, and that this $p$ is sufficient to support such calculation.
+In particular, since $k$ is the least quadratic non-residue of $p$,
+every number less than $k$ is a quadratic residue, and thus $0$,
+$1$, $2$, $3$, \ldots , $2^{3n+2}$ are all quadratic residues.
+Hence the numbers $-2^{n}$, \ldots , $2^{n}$ are all inside the
+ordered range $S_{0}\left(k\right)$. On the other hand, if we choose
+any prime smaller than $p$, there is a quadratic non-residue smaller
+than $k$, and we also know that the least quadratic non-residue is
+a prime \cite{numtheory.ref}. Thus, there is a quadratic non-residue
+in $0$, $1$, $2$, $3$, \ldots , $2^{3n+2}$, and therefore, for
+this smaller $p$, there would be a number in $-2^{n}$, \ldots ,
+$2^{n}$ that is not in the ordered range $S_{0}\left(k\right)$.
+
+When $f$ is constant, the cardinal probability of measuring $\ket{0}\ket{\overline{0}}$
+or $\ket{1}\ket{\overline{0}}$ is $\cardp{\left(2^{n}\right)^{2}+\left(2^{n}\right)^{2}=2^{2n+1}}{2^{2n+1}}$;
+i.e., the cardinal probability of measuring any other state is $\cardp{0}{2^{2n+1}}$.
+When $f$ is balanced, the cardinal probability of measuring $\ket{0}\ket{\overline{0}}$
+or $\ket{1}\ket{\overline{0}}$ is $\cardp{0}{2^{2n+1}}$. Therefore,
+if we find that the post-measurement state is either $\ket{0}\ket{\overline{0}}$
+or $\ket{1}\ket{\overline{0}}$, we know $f$ is constant; otherwise,
+$f$ is balanced.
+
+For a single qubit Deutsch problem, the probability amplitudes are
+between $-2$ and $2$, and the dimension $D=2^{1+1}=4$, so we want
+to have 
+\begin{equation}
+k\geq2^{3\cdot1+2}+1=2^{5}+1=33\,.
+\end{equation}
+The least prime satisfying the above condition is $k=37$, and thus
+$\pi\left(37\right)=12$ and $p=422231$, as shown in the extended
+elements Table \ref{table_long}. 
+\begin{table}
+\noindent \centering{}%
+\begin{tabular}{cccccccccc}
+\toprule 
+\addlinespace
+$p$ & \ldots{} & $422231$ & \ldots{} & $196265095009$ & \ldots{} &  & \ldots{} &  & \ldots\tabularnewline\addlinespace
+\addlinespace
+\midrule 
+\addlinespace
+$k$ & \ldots{} & ${\bf 37}$ & \ldots{} & ${\bf 131}$ & \ldots{} & ${\bf 257}$ & \ldots{} & ${\bf 32771}$ & \ldots\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+$\pi\left(k\right)$ & \ldots{} & $12$ & \ldots{} & $32$ & \ldots{} & $55$ & \ldots{} & $3513$ & \ldots\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}\caption{\label{table_long}Extension of transitively ordered elements.}
+\end{table}
+
+For the $2$-qubit Deutsch-Jozsa, the computation is already quite
+challenging. Now the probability amplitudes are between $-4$ and
+$4$, and the dimension $D=2^{2+1}=8$, so we need 
+\begin{equation}
+k\geq2^{3\cdot2+2}+1=2^{8}+1=257\,.
+\end{equation}
+Because $257$ is a prime, we can pick $k=257$ and $\pi\left(257\right)=55$.
+The actual value of $p$ is already outside the range of the published
+sequence A000229.
+
+These examples illustrate that the value of $p$ plays an essential
+role: its size grows with the numerical range of the intermediate
+and final results of the algorithms being implemented. Therefore,
+we naturally recover a deterministic measure of the intrinsic resources
+required for a given level of complexity; this measure is normally
+completely hidden in computations with real numbers, and explicitly
+exposing it is one of the significant achievements of our discrete
+field analysis of quantum computation. This solves the conundrum that
+the conventional Deutsch-Jozsa algorithm mysteriously continues to
+work for larger and larger input functions without any apparent increase
+in resources. Our analysis of this problem reveals that as the size
+of the input increases, it is necessary to increase the size of $p$
+and hence the size of the underlying available numeric coefficients.
+This observation does not fully explain the power of quantum computing
+over classical computing, but at least it explains that some of the
+power of quantum computing depends on increasingly larger precision
+in the underlying field of numbers.
+
+\subsection{Discrete Grover Search: Nondeterministic}
+
+As an example of how to apply our cardinal probability framework to
+a nondeterministic algorithm, we consider discrete Grover's algorithm
+searching an unstructured database of size $N=2^{n}$ \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
+Let $f:\boolt^{n}\rightarrow\boolt$ be the function we want to search.
+To simplify our discussion, we will only consider 
+\begin{equation}
+f\left(\overline{x}\right)=\begin{cases}
+1\,, & \textrm{if }\overline{x}=\overline{0}\,;\\
+0\,, & \textrm{if }\overline{x}\ne\overline{0}\,,
+\end{cases}
+\end{equation}
+where we identify $\bfalse$ and $\btrue$ as $0$ and $1$ as usual,
+and $\overline{0}=\left(0,\ldots,0\right)$.
+
+To solve Grover's problem, we represent the search states as $n$-qubit
+states as usual. However, instead of the Deutsch black box~$U_{f}$,
+$f$ is represented as the $N\times N$ “phase rotation” matrix
+\begin{equation}
+R=\begin{pmatrix}-1 & 0 & 0 & \ldots & 0\\
+0 & 1 & 0 & \ldots & 0\\
+0 & 0 & 1 & \ldots & 0\\
+\vdots & \vdots & \vdots & \ddots & \vdots\\
+0 & 0 & 0 & \ldots & 1
+\end{pmatrix}\,,
+\end{equation}
+where the “marked” element is in the first position. Beside
+$R$, we also need the $N\times N$ “diffusion” matrix
+\begin{equation}
+\Delta=\begin{pmatrix}1-\frac{N}{2} & 1 & 1 & \ldots & 1\\
+1 & 1-\frac{N}{2} & 1 & \ldots & 1\\
+1 & 1 & 1-\frac{N}{2} & \ldots & 1\\
+\vdots & \vdots & \vdots & \ddots & \vdots\\
+1 & 1 & 1 & \ldots & 1-\frac{N}{2}
+\end{pmatrix}\,,
+\end{equation}
+where we have eliminated, in matrix~$\Delta$, the scaling factor
+$\frac{2}{N}$ to enforce the requirement that all matrix coefficients
+in our framework are integer-valued. By applying the transformation
+$\Delta R$ repeatedly 
+\begin{equation}
+j=\round\left(\frac{\pi}{4\arccos\sqrt{1-\frac{1}{N}}}-\frac{1}{2}\right)\approx\round\left(\frac{\pi}{4}\sqrt{N}\right)
+\end{equation}
+times, we can find the target element~$\overline{0}$. In our context,
+we also need to choose a prime number that is large enough to ensure
+that all the numbers that occur during the calculation and after measurement
+are within the transitively-ordered subrange.
+
+Let's walk through the state in each iteration to make sure the algorithm
+works. Because the probability amplitudes of $\ket{\overline{x}}$
+are all the same for $\overline{x}\neq\overline{0}$, we can let $a_{l}$
+be the probability amplitude of $\ket{\overline{0}}$, with $b_{l}$
+the probability amplitude of each of the other possibilities, which
+are all the same, after the operators $\Delta R$ is applied $l$
+times. Beginning at $l=0$ with the information-less state, the normalization
+scaled to integer values as usual, the state after $l$th iteration
+can written as\todo{Verify the computation??}
+\begin{equation}
+\begin{pmatrix}a_{l}\\
+b_{l}\\
+\vdots\\
+b_{l}
+\end{pmatrix}=\left(\Delta R\right)^{l}\begin{pmatrix}1\\
+1\\
+\vdots\\
+1
+\end{pmatrix}=\Delta R\begin{pmatrix}a_{l-1}\\
+b_{l-1}\\
+\vdots\\
+b_{l-1}
+\end{pmatrix}\,.
+\end{equation}
+We can solve the above iteration by the following recurrence relation
+for the successive coefficients:
+\begin{subequations}
+\begin{align}
+a_{0} & =1\,, & a_{l+1} & =\left(\frac{N}{2}-1\right)a_{l}+\left(N-1\right)b_{l}\,,\\
+b_{0} & =1\,, & b_{l+1} & =\left(-1\right)a_{l}+\left(\frac{N}{2}-1\right)b_{l}\,.
+\end{align}
+\end{subequations}
+We also know $\left|a_{j}\right|>\left|b_{j}\right|$, so we can estimate
+an upper bound for the maximum cardinal probability as $\max\fnorm{a_{j}}\leq2\left(\frac{N}{2}\right)^{2j+1}$.
+By applying Eq.~\eqref{eq:region} with $D=N=2^{n}$, we can estimate~$k$
+using $k\geq8\left(\frac{N}{2}\right)^{2j+2}+1$. We can then pick
+a prime $k$, and choose the $\pi\left(k\right)$th prime in the sequence
+represented by Table~\ref{pseq} guaranteeing that every number we
+need for the computation is within the transitively ordered range
+$F^{D}\left(k\right)$.
+
+For the $2$-qubit Grover search, we have $N=D=4$ and $j=1$, with
+the maximum cardinal probability 
+\begin{equation}
+\max\fnorm{a_{j}}\leq2\left(\frac{4}{2}\right)^{2+1}=16\,,
+\end{equation}
+so we need 
+\begin{equation}
+k\geq8\left(\frac{4}{2}\right)^{2\cdot1+2}+1=8\cdot2^{4}+1=129\,.
+\end{equation}
+The least prime $k$ satisfying the above condition is $k=131$, and
+so $\pi\left(131\right)=32$ and $p=196265095009$.
+
+When $p=196265095009$, we assume that $f\left(\overline{x}\right)=1$
+if and only if $\ket{\overline{x}}=\ket{0}\!\ket{0}$, and so the
+final state is $\begin{pmatrix}4 & 0 & \ldots & 0\end{pmatrix}^{T}$
+with the field norm of $16$. Then, the cardinal probability of obtaining
+$\ket{0}\!\ket{0}$ as the post-measurement state is $\cardp{16}{16}$,
+and it is $\cardp{0}{16}$ for the rest of the states.
+
+For the $3$-qubit Grover search, we have $N=D=8$ and $j=2$, with
+an upper bound $\max\fnorm{a_{j}}\leq2\left(\frac{8}{2}\right)^{4+1}=2048$
+on the cardinal probability. Thus 
+\begin{equation}
+k\ge8\left(\frac{8}{2}\right)^{6}+1=32769\,.
+\end{equation}
+The nearest prime greater than this number is $32771$, so we can
+pick $k=32771$ and $\pi\left(32771\right)=3513$, and so if we use
+the $3513$th prime, we can implement Grover's algorithm for a database
+of size $8$.
+
+Continuing with the $3$-qubit Grover example, we show how the cardinal
+probabilities evolve to single out the target state. First, assume
+that $f\left(\overline{x}\right)=1$ if and only if $\ket{\overline{x}}=\ket{0}\!\ket{0}\!\ket{0}$.
+The initial information-less $8$-dimensional state vector evolves
+under the application of $\Delta R$ as follows:\todo{Change the
+whole paragraph to a table?}
+\begin{equation}
+\begin{pmatrix}1\\
+1\\
+\vdots\\
+1
+\end{pmatrix}\rightarrow\begin{pmatrix}10\\
+2\\
+\vdots\\
+2
+\end{pmatrix}\rightarrow\begin{pmatrix}44\\
+-4\\
+\vdots\\
+-4
+\end{pmatrix}\,.
+\end{equation}
+These states have differing field norm so we cannot compare their
+cardinal probability directly. Since states differ by only scalar
+multiplication representing the same state, if we multiply the first
+and second states by $16$ and $4$, respectively, their field norms
+become the same value of $2048$. The now-consistently-normalized
+states become 
+\begin{equation}
+\begin{pmatrix}16\\
+16\\
+\vdots\\
+16
+\end{pmatrix}\rightarrow\begin{pmatrix}40\\
+8\\
+\vdots\\
+8
+\end{pmatrix}\rightarrow\begin{pmatrix}44\\
+-4\\
+\vdots\\
+-4
+\end{pmatrix}\,.
+\end{equation}
+Therefore, the cardinal probabilities of measuring $\ket{0}\!\ket{0}\!\ket{0}$
+in each state are 
+\begin{align}
+\cardp{256}{2048} &  & \cardp{1600}{2048} &  & \cardp{1936}{2048} & ,
+\end{align}
+while the cardinal probabilities of measuring the other states become
+\begin{align}
+\cardp{256}{2048} &  & \cardp{64}{2048} &  & \cardp{16}{2048} & .
+\end{align}
+We may thus conclude that the cardinal probability of measuring the
+satisfying assignment of $f$ increases as we apply the diffusion
+$\Delta$ and phase rotation $R$ matrices repeatedly.
+
+Clearly, the required size of $k$ increases systematically with the
+problem size, and the corresponding size of the required prime number
+$p$ defining the discrete field increases in the fashion illustrated
+in Tables~\ref{pseq} and~\ref{table_long}.
+
+\section{Quantum Probability Measures over Finite Fields\label{sec:Toward-IVPM}}
+
+The cardinal probability over finite fields defined in Eq.~(\ref{eq:cardinalProbability})
+is based on the conventional Born rule, Eq.~(\ref{eq:Born-ComputationalBasis}).
+Although they are valid inside an ordered region, some quantum algorithms,
+like Shor's~\cite{Shor1999,Mermin2007,Jaeger2007}, don't localize
+their numbers in a small region. Moreover, we still haven't found
+how to manipulate the resulting cardinal probabilities, and hence
+have little idea how to define the mixed states and expectation values.
+To overcome these issues, we try a different approach to define a
+“conventional” probability over finite fields axiomatically.
+
+Recall Gleason's theorem in Sec.~\ref{subsec:Gleason's-Theorem-and}
+states that every quantum probability measure is induced by the Born
+rule in a Hilbert space $\Hilb$ of dimension $D\geq3$. To find a
+Born rule over finite fields, we could follow the steps in Sec.~\ref{sec:fuzzy}
+to define events and probability measures, and see whether we could
+have a Gleason-like theorem which induces a correspondence between
+states and probability measures qualified as a discrete Born rule.
+
+\begin{definition}[Quantum Probability Measures over Finite Fields]\label{def:QPMFF}Given
+a vector space $\mathcal{H}$ of dimension $D$ over the complexified
+field $\Fpp$, the set of events $\events_{p^{2}}$ are recursively
+defined as follows: 
+\begin{itemize}
+\item $\mathbb{0}$ and $\mathbb{1}\in\events_{p^{2}}$.
+\item If $\ket{\Psi}$ is a unit-norm state in $\mathcal{H}$, i.e., $\ket{\Psi}\in\mathcal{H}$
+with $\ip{\Psi}{\Psi}=\fnorm{\ket{\Psi}}=1$, then the projector of
+the form $\proj{\Psi}\in\events_{p^{2}}$.
+\item For each pair of \emph{orthogonal} events $P_{0}\in\events_{p^{2}}$
+and $P_{1}\in\events_{p^{2}}$, i.e., $P_{0}P_{1}=\mathbb{0}$, their
+sum is $P_{0}+P_{1}$ is an event, i.e., $P_{0}+P_{1}\in\events_{p^{2}}$.
+\end{itemize}
+Then we take a quantum probability measure over finite field (QPMFF)
+$\mu:\events_{p^{2}}\rightarrow\left[0,1\right]$ to be an assignment
+of a probability to each event (projection operator~$P$) subject
+to $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$, and satisfying for
+each pair of \emph{orthogonal} events $P_{0}$ and $P_{1}$, $\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)$.\end{definition}
+
+There are some correspondence qualified as “the discrete Born rule”
+when $p=D=3$. However, when $D=3$ and $p=7$, we have numerical
+verified that the unique QPMFF $\mu:\events_{7^{2}}\rightarrow\left[0,1\right]$
+is
+\begin{equation}
+\mu\left(P\right)=\begin{cases}
+0 & \textrm{if }P=\mathbb{0}\,;\\
+\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimensional projector;}\\
+\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimensional projector;}\\
+1 & \textrm{if }P=\mathbb{1}\,.
+\end{cases}
+\end{equation}
+Since we don't have enough QPMFF to correspond even pure states in
+the vector space~$\ff{7^{2}}^{3}$, there is no discrete Born rule
+in this case. In general, we conjecture that QPMFF is always unique
+for $D\ge3$ except $D=p=3$.
+
+Although we couldn't prove there is no discrete Born rule by investigating
+QPMFF alone, we could prove there is no “sensible” Born rule
+which also satisfies an analog of Proposition~\ref{prop:Born-probability-one}
+and \ref{prop:Born-unitary-invariant}.\todo{Notice that the notation
+here and previous is a little bit different because we dealt with
+mixed states previously, but pure states here. Besides, should we
+explain the physical meaning of these propositions?}
+
+\begin{thm}\label{thm:NotGleasonDQT-group}For $D\ge3$ except $p=D=3$,
+there is no “sensible” Born rule $\muF$ parametrized by unit-norm
+states~$\ket{\Phi}$ in $\mathcal{H}$ such that $\muF_{\Phi}$ is
+a QPMFF;
+\begin{equation}
+\muF_{\Phi}\left(P\right)=1\label{eq:zero}
+\end{equation}
+ if and only if $P\ket{\Phi}=\ket{\Phi}$; and 
+\begin{equation}
+\muF_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muF_{\Phi}\left(P\right)\,,\label{eq:basis-independent}
+\end{equation}
+where $U$ is any unitary map.\end{thm}
+
+\begin{proof}\footnote{This proof assume $p\ge7$, and there is a simpler proof for $D\ge4$
+applying to $p=3$ case~\cite{Gardiner2014}.}Assume such a map $\muF$ satisfying all properties exists, we will
+use the listed properties to build a contradiction. Consider the computational
+basis $\left\{ \ket{0},\ket{1},\ket{2},\ldots\right\} $, and the
+projectors formed by these vectors, $P_{0}=\proj{0}$, $P_{1}=\proj{1}$,
+and $P_{2}=\proj{2}$. Since $p\ge7$, $1+1+1$ is not $0$ in $\ff{p^{2}}$,
+and has the principal inverse field norm $\gamma=\fnorm*{3}$ as defined
+in Sec.~\ref{subsec:Vector-Spaces}. The unit-norm state $\ket{\oplus}=\frac{1}{\gamma}\left[\ket{0}+\ket{1}+\ket{2}\right]$
+can then be used as a parameter of $\muF$, and induces a QPMFF $\muF_{\oplus}$.
+To compute the probability values of $\muF_{\oplus}$, we want to
+utilize Eq.~(\ref{eq:basis-independent}) by letting $U_{i}$ be
+the unitary map that permutes the basis vectors $\ket{0}$ and $\ket{i}$
+and acts as the identity for the rest for $i=1$ and $2$. Note that
+$\ket{\oplus}$ is invariant under $U_{i}$ so we have $\muF_{\oplus}\left(P_{0}\right)=\muF_{U_{i}\ket{\oplus}}\left(U_{i}P_{0}U_{i}^{\dagger}\right)=\muF_{\oplus}\left(P_{i}\right)$
+by Eq.~(\ref{eq:basis-independent}). Let $P'=P_{0}+P_{1}+P_{2}$.
+Since $P'\ket{\oplus}=\ket{\oplus}$, Eq.~(\ref{eq:zero}) implies
+\begin{equation}
+1=\muF_{\oplus}\left(P'\right)=\muF_{\oplus}\left(P_{0}\right)+\muF_{\oplus}\left(P_{1}\right)+\muF_{\oplus}\left(P_{2}\right)=3\muF_{\oplus}\left(P_{0}\right)\,,
+\end{equation}
+and thus for $i=0$, $1$, and $2$, we always have $\muF_{\oplus}\left(P_{i}\right)=\frac{1}{3}$.
+
+Similar to the previous paragraph, we now compute the QPMFF induced
+by $\ket{\Phi'}=U'\ket{\oplus}=\frac{2\alpha}{\gamma}\ket{0}+\frac{1}{\gamma}\ket{2}$,
+where $\alpha=\fnorm*{\frac{1}{2}}\in\ff{p^{2}}$ and
+\begin{equation}
+U'=\begin{pmatrix}\alpha & \alpha & 0\\
+-\alpha & \alpha & 0\\
+0 & 0 & 1
+\end{pmatrix}\,.
+\end{equation}
+Since $\ket{2}$ is invariant under $U'$, Eq.~(\ref{eq:basis-independent})
+implies $\muF_{\oplus}\left(P_{2}\right)=Hilbert\muF_{U'\ket{\oplus}}\left(U'P_{2}U'^{\dagger}\right)=\muF_{\Phi'}\left(P_{2}\right)$.
+Also, Eq.~(\ref{eq:zero}) implies $1=\muF_{\Phi'}\left(P_{0}+P_{2}\right)=\muF_{\Phi'}\left(P_{0}\right)+\muF_{\Phi'}\left(P_{2}\right)$.
+By moving $\muF_{\Phi'}\left(P_{0}\right)$ to the left-hand side
+of the equation, we have 
+\begin{equation}
+\muF_{\Phi'}\left(P_{0}\right)=1-\muF_{\Phi'}\left(P_{2}\right)=1-\muF_{\oplus}\left(P_{2}\right)=1-\tfrac{1}{3}=\tfrac{2}{3}\,.\label{eq:prob23}
+\end{equation}
+
+Iterating the similar process with $\ket{\Phi''}=U''\ket{\Phi'}=\frac{2\alpha}{\gamma}\left(\ket{0}+\ket{1}\right)+\frac{\beta}{\gamma}\ket{2}$,
+where $\beta=\fnorm*{-1}\in\ff{p^{2}}$ and
+\begin{equation}
+U''=\begin{pmatrix}1 & 0 & 0\\
+0 & \beta^{*} & 2\alpha\\
+0 & 2\alpha^{*} & \beta
+\end{pmatrix}\,.
+\end{equation}
+Because $\ket{\Phi''}$ is invariant under $U_{1}$, invoking Eq.~(\ref{eq:basis-independent})
+in $\muF_{\Phi''}\left(P_{1}\right)=\muF_{U_{1}\ket{\Phi''}}\left(U_{1}P_{1}U_{1}^{\dagger}\right)=\muF_{\Phi''}\left(P_{0}\right)$,
+we know $\muF_{\Phi''}\left(P_{1}\right)$ and $\muF_{\Phi''}\left(P_{0}\right)$
+are same. Actually, they are both equal to $\tfrac{2}{3}$ because
+$\muF_{\Phi''}\left(P_{0}\right)=\muF_{U''\ket{\Phi'}}\left(U''P_{0}U''^{\dagger}\right)=\muF_{\Phi'}\left(P_{0}\right)=\tfrac{2}{3}$
+by Eqs.~(\ref{eq:basis-independent}) and (\ref{eq:prob23}). Since
+$P'\ket{\Phi''}=\ket{\Phi''}$, Eq.~(\ref{eq:zero}) implies
+\begin{equation}
+1=\muF_{\Phi''}\left(P'\right)=\muF_{\Phi''}\left(P_{0}\right)+\muF_{\Phi''}\left(P_{1}\right)+\muF_{\Phi''}\left(P_{2}\right)=\tfrac{2}{3}+\tfrac{2}{3}+\muF_{\Phi''}\left(P_{2}\right)>\tfrac{4}{3}\,.
+\end{equation}
+This is inconsistent with the requirement that the probabilities for
+orthogonal outcomes add up to $1$, and build a contradiction.\end{proof}
+
+The reason why there is no “sensible” Born rule might be that
+the state spaces are now discrete and finite, but we still consider
+mapping probability assignments to infinitely precise values in the
+unit interval $\left[0,1\right]$. To overcome this issue, we want
+to consider a discrete Born rule mapping to finite number of intervals
+called interval-valued probability~\cite{JamisonLodwick2004,THOS2018}.
 To adopting the idea of interval-valued probability step-by-step,
@@
 finite fields, we will first review the classical interval-valued
-probability, and extend it with the conventional quantum theory.
+probability, and extend it with the conventional quantum theory in
+the next chapter.
 
@@
 
-\section{Classical Interval-Valued Probability}
-
-In the classical setting, there are several proposals for ``imprecise
-probabilities'' \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+\section{Intervals of Uncertainty\label{sec:Interval-Uncertainty}}
+
+\subsection{Definitions of Classical and Quantum IVPMs}
+
+We will start by reviewing classical IVPMs and then propose our quantum
+generalization. In the classical setting, there are several proposals
+for “imprecise probabilities”~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
 Although these proposals differ in some details, they all share the
-fact that the probability $\bar{\mu}(E)$ of an event~$E$ is generalized
-from a single \emph{real number} to an \emph{interval}~$[l,r]$,
-where~$l$ intuitively corresponds to the strength of evidence for
-the event~$E$ and~$1-r$ corresponds to the strength of evidence
-against the same event. Given a sample space~$\Omega$ and a set
-of intervals~$\mathscr{I}$, similar to a classical probability measure
-$\mu:2^{\Omega}\rightarrow\left[0,1\right]$, a classical interval-valued
-probability measure (IVPM) $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
-needs to satisfy some coherent axioms. By satisfying the convexity
-axiom \cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
-Shapley proved that there is always a classical probability measure
-consistent with the classical IVPM~$\bar{\mu}$ \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
-Given any random variable, its expectation value with respect to classical
-probability measures consistent with~$\bar{\mu}$ is consistent with
-its Choquet integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-with respect to $\bar{\mu}$ \cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
-
-\section{Quantum Interval-Valued Probability}
-
-The quantum extension, quantum interval-valued probability measure
-(QIVPM) $\bar{\mu}:\events\rightarrow\mathscr{I}$, is a generalization
-of both classical IVPMs $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
-and conventional quantum probability measures $\mu:\events\rightarrow[0,1]$
-\cite{THOS2017}, because QIVPMs reduce to classical IVPMs when the
-space of quantum events $\events$ is restricted to mutually commuting
-events, and reduces to conventional quantum probability measures when
-mapping to infinitely precise uncountable intervals $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
-While Shapley and Gleason both proved there must be a ``state''
-consistent with any given QIVPM in the reduced cases, in general there
-exists a QIVPM such that no state is consistent with it. However,
-we found a class of QIVPMs such that all QIVPMs in this class are
-consistent with a non-empty ``ball'' of quantum states whose radius
-is defined by the maximal length of the intervals, and recovers the
-original Gleason theorem asymptotically. Similarly, the conventional
-quantum expectation value and the classical Choquet integral are together
-generalized to the quantum interval-valued expectation value. This
-is used to prove an imprecise Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-which suggests a possible resolution of the Meyer-Mermin debate on
-the impact of finite-precision measurement on the Kochen-Specker theorem
-\cite{PhysRevLett.83.3751,Mermin1999}.
+fact that the probability $\mu(E)$ of an event~$E$ is generalized
+from a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
+where~$\ell$ intuitively corresponds to the strength of evidence
+for the event~$E$ and~$1-r$ corresponds to the strength of evidence
+against the same event. Under some additional assumptions, this interval
+could be interpreted as the Gaussian width of a probability distribution.
+
+We next introduce probability axioms for IVPMs. First, for each interval
+$[\ell,r]$ we have the natural constraint $0\leq\ell\leq r\leq1$
+that guarantees that every element of the interval can be interpreted
+as a conventional probability. We also include $\imposs=[0,0]$ and
+$\necess=[1,1]$ as limiting intervals that refer, respectively, to
+the probability interval for impossible events and for events that
+are certain. We can write the latter as $\mu(\emptyset)=\imposs$
+and $\mu(\Omega)=\necess$, where $\emptyset$ is the empty set and
+$\Omega$ is the event covering the entire sample space. For each
+interval $[\ell,r]$, we also need the dual interval $[1-r,1-\ell]$
+so that if one interval refers to the probability of an event~$E$,
+the dual refers to the probability of the event's complement $\overline{E}$.
+For example, if we discover as a result of an experiment that $\mu(E)=[0.2,0.3]$
+for some event~$E$, we may conclude that $\mu\left(\overline{E}\right)=[0.7,0.8]$
+for the complementary event~$\overline{E}$. In addition to these
+simple conditions, there are some subtle conditions on how intervals
+are combined, which we discuss next.
+
+Let $E_{0}$ and $E_{1}$ be two disjoint events with probabilities
+$\mu(E_{0})=[\ell_{0},r_{0}]$ and $\mu(E_{1})=[\ell_{1},r_{1}]$.
+A first attempt at calculating the probability of the combined event
+that \emph{either} $E_{0}$ or $E_{1}$ occurs might be $\mu(E_{0}\cup E_{1})=[\ell_{0}+\ell_{1},r_{0}+r_{1}]$.
+In some cases, this is indeed a sensible definition. For example,
+if $\mu(E_{0})=[0.1,0.2]$ and $\mu(E_{1})=[0.3,0.4]$ we get $\mu(E_{0}\cup E_{1})=[0.4,0.6]$.
+But consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
+$\mu\left(\overline{E}\right)=[0.7,0.8]$. The two events $E$ and
+$\overline{E}$ are disjoint; the naïve addition of intervals would
+give $\mu\left(E\cup\overline{E}\right)=[0.9,1.1]$, which is not
+a valid probability interval. Moreover the event $E\cup\overline{E}$
+is the entire space; its probability interval should be $\necess$
+which is sharper than $[0.9,1.1]$. The problem is that the two intervals
+are correlated: there is more information in the combined event than
+in each event separately so the combined event should be mapped to
+a sharper interval. In our example, even though the “true” probability
+of $E$ can be anywhere in the range $[0.2,0.3]$ and the “true”
+probability of~$\overline{E}$ can be anywhere in the range $[0.7,0.8]$,
+the values are not independent. Any value of $\mu(E)\leq0.25$ will
+force $\mu\left(\overline{E}\right)\geq0.75$. To account for such
+subtleties, the axioms of interval-valued probability do not use a
+strict equality for the combination of disjoint events. The correct
+constraint enforcing coherence of the probability assignment for $E_{0}\cup E_{1}$
+when $E_{0}$ and $E_{1}$ are disjoint is taken to be: 
+\begin{equation}
+\mu(E_{0}\cup E_{1})\subseteq[\ell_{0}+\ell_{1},r_{0}+r_{1}]\,.\label{eq:disjoint}
+\end{equation}
+Note that for any event $E$ with $\mu(E)=[\ell,r]$, we always have
+$\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E)\cup\mu\left(\overline{E}\right)$.
+%% Parallel arguments
+%% can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
+%% essential new information seems to be introduced.
+
+When combining non-disjoint events, there is a further subtlety whose
+resolution will give us the final general condition for IVPMs. For
+events $E_{0}$ and~$E_{1}$, not necessarily disjoint, we have:
+\begin{equation}
+\mu(E_{0}\cup E_{1})+\mu(E_{0}\cap E_{1})\subseteq\mu(E_{0})+\mu(E_{1})\,,\label{eq:classicalconvex}
+\end{equation}
+which is a generalization of the classical inclusion-exclusion principle
+that uses $\subseteq$ instead of $=$ for the same reason as before.
+The new condition, known as \emph{convexity}~\cites{Shapley1971}{GilboaSchmeidler1994}{NgMoYeh1997Chinese}{Marinacci1999}{MarinacciMontrucchio2005}{Grabisch2016},
+reduces to the previously motivated Eq.~(\ref{eq:disjoint}) when
+the events are disjoint, i.e., when $\mu(E_{0}\cap E_{1})=0$.
+
+Previous discussions can be summarized as the following definition~\cite{JamisonLodwick2004}.
+
+\begin{definition}[IVPM]Assume a collection of intervals $\mathscr{I}$
+including $\imposs$ and $\necess$ with addition and scalar multiplication
+defined as follows: \begin{subequations}\label{eq:interval-operations}
+\begin{eqnarray}
+ &  & [\ell_{0},r_{0}]+[\ell_{1},r_{1}]=[\ell_{0}+\ell_{1},r_{0}+r_{1}]\textrm{ and}\\
+ &  & x[\ell,r]=\begin{cases}
+[x\ell,xr] & \textrm{for }x\ge0\,;\\{}
+[xr,x\ell] & \textrm{for }x\le0\,.
+\end{cases}\label{eq:interval-times}
+\end{eqnarray}
+\end{subequations} Given a finite sample space~$\Omega$, and its
+power set~$2^{\Omega}$ as the classical event space, a classical
+IVPM~$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$ is a function
+subject to the following constraints:\begin{subequations}\label{eq:CIVPM-constraints}
+\begin{eqnarray}
+ &  & \bar{\mu}(\emptyset)=\imposs\,,\\
+ &  & \bar{\mu}(\Omega)=\necess\,,\label{eq:CIVPM-necess}\\
+ &  & \bar{\mu}\left(\overline{E}\right)=\necess-\bar{\mu}\left(E\right)\,,\label{eq:CIVPM-complement}
+\end{eqnarray}
+\end{subequations} and satisfying the convexity condition, Eq.~(\ref{eq:classicalconvex}),
+for each pair of events~$E_{0}$ and~$E_{1}$.\end{definition}
+
+\noindent Note that the minus sign appearing in Eq.~(\ref{eq:CIVPM-complement})
+is accommodated by the $x\le0$ case in Eq.~(\ref{eq:interval-times}).
+
+We now have the necessary ingredients to define the quantum extension,
+QIVPMs, as a generalization of both classical IVPMs and conventional
+quantum probability measures in Sec.~\ref{sec:fuzzy}. We will show
+that QIVPMs reduce to classical IVPMs when the space of quantum events
+$\events$ is restricted to mutually commuting events $\eventsC$,
+i.e., to compatible events that can be measured simultaneously. In
+Sec.~\ref{sec:Gleason} we will discuss the connection between QIVPMs
+and conventional quantum probability measures in detail.
+
+\begin{definition}[QIVPM]\label{def:QIVPM}we take a QIVPM~$\bar{\mu}$
+to be an assignment of an interval to each event (projection operator~$P$)
+subject to the following constraints: 
+\begin{align}
+\bar{\mu}(\mathbb{0}) & =\imposs\,, & \bar{\mu}(\mathbb{1}) & =\necess\,, & \bar{\mu}\left(\mathbb{1}-P\right) & =\necess-\bar{\mu}\left(P\right)\,,\label{eq:QIVPM-constraints}
+\end{align}
+and satisfying for each pair of \emph{commuting} projectors~$P_{0}$
+and~$P_{1}$ with $P_{0}P_{1}=P_{1}P_{0}$, 
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.\label{eq:QuantumInterval-valuedProbability-Inclusion}
+\end{equation}
+\end{definition}
+
+\noindent The first three constraints, Eqs.~(\ref{eq:QIVPM-constraints}),
+are the direct counterpart of the corresponding ones for classical
+IVPMs. With the understanding that the union of classical sets $E_{0}\cup E_{1}$
+is replaced by $P_{0}+P_{1}-P_{0}P_{1}$ in the case of quantum projection
+operators~\cite{Griffiths2003}, the last condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+is a direct counterpart of the convexity condition of Eq.~(\ref{eq:classicalconvex}).
+Thus our definition of QIVPMs merges aspects of both classical IVPMs
+and quantum probability measures.
+
+\subsection{Relations between Classical and Quantum IVPMs}
+
+Our definition of QIVPMs is consistent with classical IVPMs in the
+sense that a restriction of QIVPMs to mutually commuting events, $\eventsC$,
+recovers the definition of classical IVPMs.  Before we prove the
+correspondence between between classical and quantum IVPMs, we some
+necessary technical definitions and lemmas are required. First, we
+define $\events'$ as a \emph{subspace} of a set of events~$\events$
+if $\events'$ contains the projectors $\mathbb{0}$ and $\mathbb{1}$
+and is closed under complements, sums, and products. In particular,
+for any projector $P\in\events'$, we have $\mathbb{1}-P\in\events'$
+and for each pair of commuting projectors $P_{0}\in\events'$ and
+$P_{1}\in\events'$, we have $P_{0}P_{1}$ and $P_{0}+P_{1}-P_{0}P_{1}\in\events'$.
+
+\begin{thm}\label{thm:sub-event-space}Consider a Hilbert space~$\Hilb$
+and a mutually commuting sub-event space $\eventsC\subseteq\events$.
+Since $\events'$ is a set of mutually commuting projections, they
+can be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
+Let $\eventsC'$ be the set of all projectors generated by $\Omega$,
+i.e., $\eventsC'=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
+where $\sum_{P\in\emptyset}P=\mathbb{0}$. Then, 
+\begin{enumerate}
+\item $\eventsC'$ is commuting and satisfying $\eventsC\subseteq\eventsC'\subseteq\events$.
+\item The function $\upsilon:2^{\Omega}\rightarrow\eventsC'$ defined by
+$\upsilon\left(E\right)=\sum_{\ket{j}\in E}\proj{j}$ is a bijection
+and preserving the structure of between $2^{\Omega}$ and $\eventsC'$.
+More specifically, we have
+\begin{align}
+\upsilon\left(\emptyset\right) & =\mathbb{0}\,, & \upsilon\left(\Omega\right) & =\mathbb{1}\,, & \upsilon\left(\overline{E}\right) & =\mathbb{1}-\upsilon\left(E\right)\,,
+\end{align}
+and for each pair of set $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$,
+we have
+\begin{align}
+\upsilon\left(E_{0}\cap E_{1}\right) & =\upsilon\left(E_{0}\right)\upsilon\left(E_{1}\right)\,, & \upsilon\left(E_{0}\cup E_{1}\right) & =\upsilon\left(E_{0}\right)+\upsilon\left(E_{1}\right)-\upsilon\left(E_{0}\right)\upsilon\left(E_{1}\right)\,.
+\end{align}
+\item Since $\upsilon$ is a bijection, its inverse function $\tau=\upsilon^{-1}:\eventsC'\rightarrow2^{\Omega}$
+is also a bijection and preserving the structure of between $\eventsC'$
+and $2^{\Omega}$.
+\item Given any QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, we can
+define the classical IVPM $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
+by $\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(\upsilon\left(E\right)\right)=\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)$
+such that the restriction of $\bar{\mu}$ on $\eventsC'$ is just
+$\bar{\mu}^{\Omega}$ concatenating with $\tau$, i.e., $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$
+for any $P\in\eventsC'$.
+\end{enumerate}
+\end{thm}
+
+\todo{Actually, $\bar{\mu}^{\Omega}$ looks like the pullback of
+$\bar{\mu}$ by $\upsilon$~\cite{wiki:Pullback}. However, $\eventsC$
+and $2^{\Omega}$ are not categories, and $\upsilon$ is not preserving
+algebraic or analytical properties... So I don't know whether people
+call this “pullback” or not.}
+
+\subsection{States Consistent with Quantum IVPMs}
+
+A consequence is that known properties of classical IVPMs directly
+hold for QIVPMs when one restricts to mutually commuting events, $\eventsC$.
+In particular, in the classical world, it is \emph{impossible} for
+experiments to result in probabilities that are inconsistent with
+\emph{every} state of the system under consideration, i.e., all IVPMs
+must have a non-empty “core”\footnote{\label{fn:A-result-by-Shapley}A result by Shapley~\cites{Shapley1971}{GilboaSchmeidler1994}{NgMoYeh1997Chinese}{Grabisch2016}
+proves that a classical IVPM always contains at least one state that
+is consistent with every event.}. Interestingly, as we show in Sec.~\ref{sec:Gleason}, it is possible
+in the quantum world for the probabilities associated with some events
+to be inconsistent with \emph{any} quantum state, i.e., for the QIVPM
+to have an empty core; in that case, one cannot guarantee non-empty
+cores for finite-precision attempts at proving Gleason's theorem by
+extending the Born measure $\muB_{\rho}\left(P\right)$ to QIVPMs
+$\bar{\mu}\left(P\right)$. However, if we restrict ourselves to the
+set $\eventsC$ of mutually commuting events, the situation reverts
+to the classical case in which probabilities always determine at least
+one state.
+
+We now give the necessary technical definitions to prove this non-empty
+core property.
+
+\begin{definition}[Consistency]\label{def:Consistency} We say
+a QIVPM $\bar{\mu}$ is \emph{consistent} with a state $\rho$ and
+a projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
+probability calculated by the Born rule \cites{Born1983}{Mermin2007}{Jaeger2007},
+i.e., 
+\begin{equation}
+\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)\in\bar{\mu}\left(P\right)\,.\label{eq:consistent}
+\end{equation}
+In contrast with classical probability spaces\footnotemark[\getrefnumber{fn:A-result-by-Shapley}],
+there is \emph{no guarantee} that there exists a state $\rho$ that
+satisfies Eq.~(\ref{eq:consistent}) and therefore is consistent
+with a QIVPM. \end{definition}
+
+We next refine the concept of consistency by introducing the idea
+of a “core” set of states relative to subspaces.
+
+\begin{definition}[The core of a probability measure]\label{def:core}
+The \emph{core} $\coreBorn\left(\bar{\mu},\events'\right)$ of a probability
+measure $\bar{\mu}$ relative to a subspace of events $\events'$
+is the collection of all states $\rho$ that are \emph{consistent}
+with $\bar{\mu}$ on every projector in $\events'$, that is 
+\begin{equation}
+\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)}\,.\label{eq:hbar}
+\end{equation}
+\end{definition}
+
+We are now in position to state and prove that, for the special case
+of commuting events, a QIVPM will always have a non-empty core.
+
+\begin{thm}[Non-empty Core for Compatible Measurements] \label{thm:Shapley}
+For every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
+subspace of events~$\eventsC\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\eventsC\right)\ne\emptyset$.
+\end{thm}
+
+An outline of the proof, detailed in the forthcoming thesis~\cite{TaiThesis2018},
+proceeds as follows. From a subspace $\eventsC$ of mutually commuting
+events, one can construct a partial orthonormal basis by diagonalization,
+and complete this to a full orthonormal basis $\overline{\eventsC}$.
+We can then build a bijection between the QIVPM on the set of projectors
+associated with this basis and the set of classical events corresponding
+to this basis. Using this correspondence together with the classical
+result by Shapley~\cites{Shapley1971}{GilboaSchmeidler1994}{NgMoYeh1997Chinese}{Grabisch2016},
+we can establish that for the special case of commuting events, a
+QIVPM will always have a non-empty core.
+
+\subsection{Classical Choquet integrals and Expectation Values of Observables}
+
+We conclude this section with a generalization of expectation values
+of observables in the context of QIVPMs. In conventional quantum mechanics
+the expectation value of an observable as defined in Eq.~\eqref{eq:quantum-expectation}
+is a unique real number. The generalization to QIVPMs implies that
+this expectation value will itself become bounded by an interval.
+
+\begin{definition}[Expectation Value of Observables over QIVPMs]
+Let $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space
+of dimension $D$ with event space~$\events$; and $\mathbf{O}$
+an observable with spectral decomposition $\sum_{i=1}^{D}\lambda_{i}P_{i}$.
+Let $\events'$ be the minimal subspace of events containing all the
+projectors $P_{i}$ in the spectral decomposition of $\mathbf{O}$
+and define: 
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,.\label{eq:quantum-interval-expectation-core}
+\end{equation}
+\end{definition}
+
+\noindent Intuitively the expectation value of an observable relative
+to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
+themselves lie between the minimum and maximum bounds of the probability
+intervals associated with each state~$\rho$ that is consistent with~$\bar{\mu}$
+on every projector in the spectral decomposition of the observable.
+If $\bar{\mu}$ is a conventional (Born) probability measure induced
+by a state $\rho$, then the Born rule probability induced by every
+state in $\coreBorn\left(\bar{\mu},\events'\right)$ will be $\muB_{\rho}$
+and the interval collapses to a point, thus reducing the definition
+to that of Eq.~(\ref{eq:quantum-expectation})~\cite{TaiThesis2018}.
+% For example, we can extend one of the fragments of valid probability
+% measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
+% to a QIVPM~$\bar{\mu}_{3}$:
+% \begin{equation}
+% \begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
+% \bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
+% \end{aligned}
+% \label{eq:Born-QIVPM}
+% \end{equation}
+% For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
+% the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
+% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\muB_{\proj{\ps}}$.
+% Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
+% which is an interval, but not between $0$ and $1$ because it is
+% not a probability of an event. 
+We also note that, when restricted to commuting projectors, Eq.~(\ref{eq:quantum-interval-expectation-core})
+is consistent with the classical notion of the \emph{Choquet integral}~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+which is used to calculate the expectation value of random variables
+as a weighted average~\cite{TaiThesis2018}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{The Kochen-Specker Theorem and Contextuality}
+
+\label{sec:Kochen-Specker}
+
+Our generalization of quantum probability measures to QIVPMs allows
+us to strengthen the scope of one of the fundamental theorems of quantum
+physics: the Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}.
+Our finite-precision extension of that theorem will suggest a resolution
+to the debate initiated by Meyer and Mermin on the relevance of the
+Kochen-Specker to experimental, and hence finite-precision, quantum
+measurements \cites{PhysRevLett.83.3751}{HKSS1999}{Mermin1999}{Kent1999}{SimonBruknerZeilinger2001}{Cabello2002}{Larsson2002}{Appleby2002}{BarrettKent2004}{Appleby_2005}{Spekkens2005}{GuehneKleinmannCabelloEtAl2010}{MazurekPuseyKunjwalEtAl2016}.
+Specifically, the original Kochen-Specker theorem is formulated using
+a model quantum mechanical system that has \emph{definite values at
+all times}~\cite{Held2016}, i.e., its observables have infinitely
+precise values at all times. Our interval-valued probability framework
+will allow us to state, and prove, a stronger version of the theorem
+that holds even if the observables have values that are only definite
+up to some precision specified by a parameter $\delta$. Our approach
+provides a quantitative realization of Mermin's intuition~\cite{Mermin1999}: 
+\begin{quote}
+\ldots although the outcomes deduced from such imperfect measurements
+will occasionally differ dramatically from those allowed in the ideal
+case, if the misalignment is very slight, the statistical distribution
+of outcomes will differ only slightly from the ideal case. 
+\end{quote}
+
+\subsection{Finite-Precision Extension of the Kochen-Specker Theorem}
+
+The first step in our formalization is to introduce a family of QIVPMs
+parameterized by an uncertainty~$\delta$, which we call $\delta$-deterministic
+QIVPMs.
+
+\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
+A QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is $\delta$-deterministic
+if, for every event $P\in\events$, we have that either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
+or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}
+
+% \begin{table}
+%   \noindent \centering{}\caption{\label{tab:classical-IVPMs}Example 
+%     QIVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ on
+%     commuting events $P$.}
+% \begin{tabular}{cccc}
+% \toprule 
+% \addlinespace
+% $P$ & $\bar{\mu}_{A}(P)$ & $\bar{\mu}_{B}(P)$ & $\bar{\mu}_{C}(P)$\tabularnewline\addlinespace
+% \midrule
+% \midrule 
+% \addlinespace
+% $\mathbb{0}$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $\proj{0}$ & $\necess$ & $\left[\frac{2}{3},1\right]$ & $\left[\frac{2}{3},\frac{2}{3}\right]$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $\proj{1}$ & $\imposs$ & $\left[0,\frac{1}{3}\right]$ & $\left[\frac{1}{3},\frac{1}{3}\right]$\tabularnewline\addlinespace
+% \midrule 
+% \addlinespace
+% $\mathbb{1}$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
+% \bottomrule
+% \end{tabular}
+% \yutsung{$\bar{\mu}_{A}$ is neither a QIVPM nor a restriction of a QIVPM
+% according to the current definition. Need to fix this example or fix the definition.}
+% \end{table}
+
+\noindent This definition puts no restrictions on the set of intervals
+itself, only on which intervals are assigned to events. When $\delta=0$,
+every event must be assigned a probability either in $\imposs$ or
+in $\necess$, i.e., every event is completely determined with certainty.
+As $\delta$ gets larger, the QIVPM allows for more indeterminate
+behavior. % For example, $\bar{\mu}_{A}$ defined in
+% Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
+% $\imposs\subseteq\left[0,0\right]$ and
+% $\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
+% ~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
+% $\bar{\mu}_{A}$ represents tossing a double-headed coin. When $\delta$
+% is increased to $\frac{1}{3}$, both $\bar{\mu}_{B}$ and
+% $\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
+% $\bar{\mu}_{A}$ is still not $\frac{1}{3}$-deterministic because
+% $\bar{\mu}_{A}(\proj{0})=\bar{\mu}_{A}(\proj{1})=\unknown=[0,1]$, but
+% both $\unknown\subseteq\left[0,\frac{1}{3}\right]$ and
+% $\unknown\subseteq\left[1-\frac{1}{3},1\right]$ are false.  Finally,
+% when $\delta=1$, because every interval is a subset of $\unknown$,
+% every QIVPM is $1$-deterministic. In particular, the non-informative
+% QIVPM~$\bar{\mu}_{A}$ is 1-deterministic.
+% %% and the Born QIVPM~$\bar{\mu}_{3}$ defined in
+% %% Eq.~(\ref{eq:Born-QIVPM}) are both $1$-deterministic.
+
+The expectation value of an observable $\mathbf{O}$ in a Hilbert
+space ${\cal H}$ of dimension $D$ relative to a 0-deterministic
+QIVPM is fully determinate and is equal to one of the eigenvalues
+$\lambda_{i}$ of that observable. To see this, note that given an
+orthonormal basis $\Omega=\{\ket{\psi_{0}},\ket{\psi_{1}},\ldots,\ket{\psi_{D-1}}\}$,
+a 0-deterministic QIVPM must map exactly one of the projectors $\proj{\psi_{i}}$
+to $\necess$ and all others to $\imposs$. This is because, by Eq.~(\ref{eq:necess}),
+we have $\bar{\mu}\left(\sum_{j=0}^{D-1}{\proj{\psi_{j}}}\right)=\necess$
+and by inductively applying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+we must have one of the $\bar{\mu}(\proj{\psi_{i}})=\necess$ and
+all others mapped to $\imposs$. Given any state~$\rho$ that is
+consistent with this QIVPM on all the projectors in $\Omega$, we
+have by Eq.~(\ref{eq:hbar}) that $\muB_{\rho}$ must also map exactly
+one of the projectors in $\Omega$ to 1 and all others to 0. If an
+observable has a spectral decomposition along~$\Omega$ then, by
+Eq.~(\ref{eq:quantum-expectation}), its expectation value relative
+to~$\muB_{\rho}$ is the eigenvalue $\lambda_{i}$ whose projector
+is mapped to 1. It therefore follows, by Eq.~(\ref{eq:quantum-interval-expectation-core}),
+that the expectation value relative to the 0-deterministic~${\bar{\mu}}$
+is fully determinate and lies in the interval $[\lambda_{i},\lambda_{i}]$.
+
+We can now proceed with the main technical result of this section.
+We first observe that the original Kochen-Specker theorem is a statement
+regarding the non-existence of a $0$-deterministic QIVPM, and generalize
+to a corresponding statement about $\delta$-deterministic QIVPMs.
+
+\begin{thm}[0-Deterministic Variant of the Kochen-Specker Theorem]
+\label{thm:Kochen-Specker} Given a Hilbert space $\Hilb$ of dimension
+$D\ge3$, there is no $0$-deterministic measure~$\bar{\mu}$ mapping
+every event to either $\imposs$ or $\necess$. \end{thm}
+
+\noindent To explain why this result is equivalent to the original
+Kochen-Specker theorem and to prove it at the same time, we proceed
+by assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive the same
+contradiction as the original Kochen-Specker theorem. Instead of adapting
+the more complicated proof for $D=3$, the counterexample presented
+below uses the simpler proof for a Hilbert space of dimension $D=4$
+and is constructed as follows.
+
+We consider a two spin-$\frac{1}{2}$ Hilbert space $\Hilb=\Hilb_{1}\otimes\Hilb_{2}$
+of dimension $D=4$. We use the same nine observables $\mathbf{O}_{ij}$
+with $i$ and $j$ ranging over $\{0,1,2\}$ from the Mermin-Peres
+“magic square” used to prove the Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
+
+{\renewcommand{\arraystretch}{2}% 
+\begin{center} 
+\begin{tabular}{r|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|} 
+$\mathbf{O}_{ij}$~ & $j=0$ & $j=1$ & $j=2$ \\ 
+\hline  
+$i=0~$ & $\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline 
+\hline  
+$i=1~$ & $\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline 
+\hline  
+$i=2~$ & $\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline 
+\hline  
+\end{tabular}
+\par\end{center} 
+}
+
+\noindent The observables are constructed using the Pauli matrices
+$\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\} $ whose
+eigenvalues are all either~$1$ or $-1$ \cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
+They are arranged such that in each row and column, \emph{except the
+column $j=2$}, every observable is the product of the other two.
+In the $j=2$ column, we have instead that $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
+Now assume a 0-deterministic QIVPM~${\bar{\mu}}$; the expectation
+values of the observables in each row relative to this 0-deterministic
+QIVPM are fully determinate and must lie in either the interval $[1,1]$
+or the interval $[-1,-1]$ depending on which eigenvalue is the one
+whose associated projector is certain. Since the product of any two
+observables in a row is equal to the third, there must be an even
+number of occurrences of the interval $[-1,-1]$ in each row and hence
+in the entire table~\cite{TaiThesis2018}. However, looking at the
+expectation values of the observables in each column, there must be
+an even number of occurrences of the interval $[-1,-1]$ in the first
+two columns and an odd number in the $j=2$ column and hence in the
+entire table~\cite{TaiThesis2018}. The contradiction implies the
+non-existence of the assumed 0-deterministic QIVPM. %% We therefore prove a stronger statement of contextuality that 
+%% includes the effects of finite-precision.
+
+% \begin{table*}
+% \caption{\label{tab:Mermin-Peres-Computation}Compute the expectation value
+% of of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$, $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$,
+% and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ relative to a 0-deterministic
+% QIVPM~$\bar{\mu}$. During the computation, whenever $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
+% $\muB_{\rho}\left(P_{1}\right)$ and $\muB_{\rho}\left(P_{2}\right)$
+% must be the value list in the table. Therefore, $\expval{\mathbf{O}}_{\bar{\mu}}$
+% is a singleton set.}
+% \begin{tabular}{|c|c|c|c|c|c|c|c|}
+% \hline 
+% Observable~$\mathbf{O}$ & Spectral Decomposition~$1\cdot P_{1}-1\cdot P_{2}$ & $\bar{\mu}\left(P_{1}\right)$ & $\bar{\mu}\left(P_{2}\right)$ & $\muB_{\rho}\left(P_{1}\right)$ & $\muB_{\rho}\left(P_{2}\right)$ & $\expval{\mathbf{O}}_{\muB_{\rho}}$ & $\expval{\mathbf{O}}_{\bar{\mu}}$\tabularnewline
+% \hline 
+% \hline 
+% $\ensuremath{\mathbb{1}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{2}\right)-1\cdot\left(\proj{1}+\proj{3}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
+% \hline 
+% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$ & $1\cdot\left(\proj{0}+\proj{1}\right)-1\cdot\left(\proj{2}+\proj{3}\right)$ & $\necess$ & $\imposs$ & $1$ & $0$ & $1\cdot1-1\cdot0=1$ & $\left\{ 1\right\} $\tabularnewline
+% \hline 
+% $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{3}\right)-1\cdot\left(\proj{1}+\proj{2}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
+% \hline 
+% \end{tabular}
+% \end{table*}
+% \yutsung{In order to understand the expectation value of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$,
+% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$, and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$
+% relative to a 0-deterministic QIVPM~$\bar{\mu}$, we first diagonalize
+% these observables by the computational basis~$\Omega=\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $,
+% where $\ket{0}=\ket{0}\otimes\ket{0}$, $\ket{1}=\ket{0}\otimes\ket{1}$,
+% $\ket{2}=\ket{1}\otimes\ket{0}$, and $\ket{3}=\ket{1}\otimes\ket{1}$.
+% Since $\bar{\mu}$ is 0-deterministic, there is a unique $\ket{k_{0}}\in\Omega$
+% such that $\bar{\mu}\left(\proj{k_{0}}\right)=\necess$ and $\bar{\mu}\left(\proj{k}\right)=\imposs$
+% for $k\ne k_{0}$~\cite{TaiThesis2018}. Without loss of generality,
+% assume $k_{0}=1$, the expectation values can be computed step-by-step
+% in Table~\ref{tab:Mermin-Peres-Computation}. They are singleton
+% sets whose only element is the eigenvalue of the observable. By adopting
+% an intuitive product rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $
+% for singleton sets, these expectation values also satisfy the property~$\expval{\ensuremath{\mathbb{1}\otimes\sigma_{z}}}_{\bar{\mu}}\cdot\expval{\ensuremath{\sigma_{z}\otimes\mathbb{1}}}_{\bar{\mu}}=\expval{\ensuremath{\sigma_{z}\otimes\sigma_{z}}}_{\bar{\mu}}$
+% since $\left(\ensuremath{\mathbb{1}\otimes\sigma_{z}}\right)\cdot\left(\ensuremath{\sigma_{z}\otimes\mathbb{1}}\right)=\left(\ensuremath{\sigma_{z}\otimes\sigma_{z}}\right)$.}
+
+% A 0-deterministic QIVPM~$\bar{\mu}$ has an important property
+% regarding to the expectation values of a family of $M$ commuting
+% observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ relative to
+% $\bar{\mu}$. Since $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
+% commutes, they can be diagonalized by a common orthonormal
+% basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.  Since
+% $\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ and a unique
+% quantum probability measure~$\mu$ exists such that
+% $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $ and
+% $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$;
+% $\mu\left(\proj{k}\right)=1$ if and only if
+% $k=k_{0}$~\cite{TaiThesis2018}.  If we denote the product
+% observables~$\prod_{j=1}^{M}\mathbf{O}_{j}$ as
+% $\overline{\mathbf{O}}$, the expectation values of the
+% observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$ and
+% $\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
+% singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
+% and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Both
+% $\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$ and
+% $\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product of the
+% eigenvalues corresponding to the pure state~$\ket{k_{0}}$ for each
+% observable~$\mathbf{O}_{j}$. By adopting an intuitive product
+% rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{
+%   x_{0}x_{1}\right\} $, we have the following property:
+% \begin{equation}
+% \prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbF{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
+% \end{equation}
+
+Our framework allows us to generalize the above theorem to state that
+for small enough $\delta$, it is impossible to have $\delta$-deterministic
+QIVPMs, which is a stronger statement of contextuality that includes
+the effects of finite-precision. Every QIVPM must map some events
+to truly uncertain intervals, not just “almost definite intervals.”
+The proof requires two simple lemmas that we present first.
+
+The first lemma shows a simpler way to prove the convexity condition.
+Recall that the convexity condition for a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
+states that for each pair of \emph{commuting} projectors~$P_{0}$
+and~$P_{1}$ with $P_{0}P_{1}=P_{1}P_{0}$, the following equation
+holds: 
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
+\end{equation}
+
+\begin{lemma}\label{lemma:verify-convexity} To verify the convexity
+condition of a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, it
+is sufficient to check that: 
+\begin{equation}
+\bar{\mu}\left(P'+P''\right)=\bar{\mu}\left(P'\right)+\bar{\mu}\left(P''\right)\label{amr}
+\end{equation}
+for all orthogonal projectors $P'$ and~$P''$. \end{lemma} The
+proof follows the outline of the proof of the classical inclusion-exclusion
+principle. From the commuting projectors $P_{0}$ and $P_{1}$, we
+construct the following three orthogonal projectors: $P_{0}P_{1}$,
+$P_{0}\left(\mathbb{1}-P_{1}\right)$, and $\left(\mathbb{1}-P_{0}\right)P_{1}$.
+Then we proceed as follows:
+
+\noindent 
+\begin{equation*} 
+\begin{aligned} 
+\noalign{$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)$} 
+\qquad\qquad=~~&\bar{\mu}\left(P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
+ & (\mbox{because } P_{0} = P_{0}P_{1} + P_{0} - P_{0}P_{1}) \\ 
+=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) \\ 
+=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
+     & (\mbox{because } P_{1} = P_{0}P_{1} + P_{1} - P_{0}P_{1}) \\ 
+=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1}))+\bar{\mu}(P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1})+ 
+   \bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
+=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1}+P_{0}P_{1}) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
+=~~& \bar{\mu}(P_{0}) + \bar{\mu}(P_{1}) 
+\end{aligned} 
+\end{equation*}
+
+\noindent The next lemma relates $\delta$-deterministic QIVPMs with
+$\delta<\frac{1}{3}$ to 0-deterministic QIVPMs.
+
+\begin{lemma}\label{lemma:delta2zero} From any $\delta$-deterministic
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<\frac{1}{3}$,
+we can construct a $0$-deterministic QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
+defined as follows: 
+\begin{equation}
+\barmuD\left(P\right)=\begin{cases}
+\imposs & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
+\necess & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
+\end{cases}
+\end{equation}
+\end{lemma} The most important part of the proof is to verify the
+convexity condition for $\barmuD$. By Lemma~\ref{lemma:verify-convexity},
+it is sufficient to verify the following equation for orthogonal projectors
+$P'$ and~$P''$, 
+\begin{equation}
+\barmuD\left(P'+P''\right)=\barmuD\left(P'\right)+\barmuD\left(P''\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
+\end{equation}
+for two cases, which we now examine in detail.
+
+\noindent When one of $\barmuD\left(P'\right)$ and $\barmuD\left(P''\right)$
+is $\necess$, say $\barmuD\left(P'\right)=\imposs$ and $\barmuD\left(P''\right)=\necess$,
+we have $\bar{\mu}\left(P'\right)\subseteq\left[0,\delta\right]$
+and $\bar{\mu}\left(P''\right)\subseteq\left[1-\delta,1\right]$ which
+implies $\bar{\mu}\left(P'+P''\right)\subseteq\left[1-\delta,1+\delta\right]$.
+Since $\bar{\mu}\left(P'+P''\right)$ is a subset of $\left[0,1\right]$,
+$\bar{\mu}\left(P'+P''\right)$ must be a subset of $\left[1-\delta,1\right]$,
+which implies $\barmuD\left(P'+P''\right)$ is also $\necess$, thus
+satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
+
+When both $\barmuD\left(P'\right)$ and $\barmuD\left(P''\right)$
+are $\imposs$, we have both $\bar{\mu}\left(P'\right)$ and $\bar{\mu}\left(P''\right)\subseteq\left[0,\delta\right]$
+which implies $\bar{\mu}\left(P'+P''\right)\subseteq\left[0,2\delta\right]$.
+Since we assume $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
+$\left[1-\delta,1\right]$ are disjoint, which implies $\bar{\mu}\left(P'+P''\right)$
+and $\left[1-\delta,1\right]$ are disjoint. Together with the fact
+that $\bar{\mu}\left(P'+P''\right)$ is a subset of either $\left[0,\delta\right]$
+or $\left[1-\delta,1\right]$, $\bar{\mu}\left(P'+P''\right)$ must
+be a subset of $\left[0,\delta\right]$, which implies $\barmuD\left(P'+P''\right)=\imposs$,
+and hence also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal})
+is again satisfied.
+
+\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
+\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of
+dimension~$D\ge3$, there is no $\delta$-deterministic QIVPM for
+$\delta<\frac{1}{3}$.\end{thm} The proof is by contradiction: Suppose
+there is a $\delta$-deterministic QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
+By Lemma~\ref{lemma:delta2zero}, we can construct a 0-deterministic
+QIVPM; however, by Thm.~\ref{thm:Kochen-Specker}, such 0-deterministic
+QIVPMs do not exist.
+
+\begin{table}
+\caption{\label{tab:probability-measures}Possible probability measures on
+a Hilbert space of dimension~$D=3$, where $\bar{\mu}_{2}'$ and
+$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
+and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
+by $P$.}
+\centering{}%
+\begin{tabular}{cccccc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}_{0}\left(P\right)$  & $\bar{\mu}_{1}\left(P\right)$  & $\bar{\mu}_{2}\left(P\right)$  & $\bar{\mu}_{2}'\left(P\right)$  & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+All one-dimensional\tabularnewline
+projectors\tabularnewline
+\end{tabular} & $\left[0,0\right]$  & $\left[0,\tfrac{1}{4}\right]$  & $\left[0,\tfrac{1}{3}\right]$  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
+\midrule 
+\addlinespace
+\begin{tabular}{c}
+All two-dimensional\tabularnewline
+projectors\tabularnewline
+\end{tabular} & $\left[1,1\right]$  & $\left[\tfrac{3}{4},1\right]$  & $\left[\tfrac{2}{3},1\right]$  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$  & $\left[\tfrac{1}{2},1\right]$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$  & $\necess$  & $\necess$  & $\necess$  & $\necess$  & $\necess$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+The bound $\delta<\frac{1}{3}$ is tight as it is possible to construct
+a $\frac{1}{3}$-deterministic QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$.
+For example, $\bar{\mu}_{2}'$ defined in Table~\ref{tab:probability-measures}
+is a valid $\frac{1}{3}$-deterministic QIVPM. When $\delta\geq\frac{1}{3}$,
+i.e, when the uncertainty in measurements becomes so large, it becomes
+possible to map every observable to some (quite inaccurate) probability
+interval, thus invalidating the Kochen-Specker theorem. We can summarize
+and illustrate the above arguments using Fig.~\ref{fignoname}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[scale=0.5]{prop_letter_ajhs_referee_response_nb} 
+\par\end{centering}
+\caption{The region to the left of the vertical line at $\delta=\frac{1}{3}$
+is where we assume small measurement degradation; in that region our
+extension of the KS theorem definitely demonstrates contextuality
+(\textsf{C}). In the region to the right, the degradation of the data
+is large and our extension of the KS theorem no longer refutes other
+explanations for the experimental data.}
+\label{fignoname} 
+\end{figure}
+
+As is the case for conventional, infinitely-precise, quantum probability
+measures, the theorem is only applicable to dimensions $D\geq3$.
+Indeed when the Hilbert space has dimension 2, it is straightforward
+to construct a 0-deterministic QIVPM as follows. Consider a non-contextual
+hidden variable model for $D=2$ (e.g., as proposed by Bell or Kochen-Specker~\cite{BELL_1966,kochenspecker1967}).
+Such a two-dimensional model assigns definite values to all observables
+at all times, and hence assigns a \emph{determinate} probability (0
+or 1) to each event. This probability measure directly induces a 0-deterministic
+QIVPM by changing 0 to $\imposs$ and 1 to $\necess$. It follows
+that every 0-deterministic QIVPM is $\delta$-deterministic.
+
+\subsection{Experimental Data and $\delta$-determinism}
+
+We have thus quantified one important aspect of uncertainty in quantum
+mechanics—the effect of the imprecise nature of devices—which is a
+novel addition to the theory of measurement. Indeed, as Heisenberg
+emphasized in his famous microscope example~\cite{Heisenberg1983},
+the conventional theory of measurement states that it is impossible
+to precisely measure any property of a system without disturbing it
+somewhat. Thus, there are fundamental limits to what one can measure
+and these limits have traditionally been attributed to complementarity.
+Our imprecision represents an \emph{additional} source of indeterminacy
+beyond the inherent probabilistic nature of quantum mechanics.
+
+In an experimental setup, $\delta$ is calculated as follows. To determine
+the probability of any event, we typically repeat an experiment $m$
+times and count the number of times we witness the event. This assumes
+that for each run of the experiment we can determine, using our apparatus,
+whether the event occurred or not. Assume an event has an ideal mathematical
+probability of $0$, and we repeat the experiment $100$ times. In
+a perfect world we should be able to refute the event $100$ times
+and calculate that the probability is $0$. We might also observe
+the event $2$ times and refute it $98$ times and therefore calculate
+the probability to be $0.02$. Note that this situation assumes perfect
+measurement conditions and remains within the context of conventional
+(real-valued) probability theory. The question we focus on is what
+happens if we are only able to refute it $97$ times and are \emph{uncertain}
+$3$ times? This is quite common in actual experiments. Mathematically
+we can model this idea by stating that the probability of the event
+is in the range $\left[0,0.03\right]$ which says that the probability
+of the event could be $0$, $0.01$, $0.02$, or $0.03$ as each the
+three uncertain records could either be evidence for the event or
+against it. We just cannot nail it down given the current experimental
+results and therefore represent the evidence as a ($\delta=$)$0.03$-deterministic
+probability measure. The interesting observation is that the axioms
+of probability theory (like additivity and convexity) impose enough
+constraints on the structure of interval-valued quantum probability
+measures to make them robust in the face of small non-vanishing $\delta$'s.
+
+To see this idea in the context of a quantum experiment, consider
+a three-dimensional Hilbert space with one-dimensional projectors~$P_{\rho}$,
+two-dimensional projectors $P_{\rho}+P_{\sigma}$, and an experiment
+that is repeated $12$ times. By the Kochen-Specker theorem, it is
+impossible to build a probability measure that maps every projection
+to either $0=\frac{0}{12}$ or $1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
+defined in Table~\ref{tab:probability-measures} is not a QIVPM.
+
+Now consider what happens if $\frac{1}{4}$ of the data for \emph{every}
+one-dimensional projector is uncertain. A potential account of this
+degradation is to assign to each event $P$ the entire range of possibilities
+$\bar{\mu}_{1}(P)$ as defined in Table~\ref{tab:probability-measures}.
+This measure is not a valid QIVPM because it does not satisfy the
+convexity condition: for any two orthogonal one-dimensional events
+$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$,
+but $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
+which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$.
+Interestingly, it is impossible to find any probability measure that
+would be consistent with these observations, as the interval $\left[\tfrac{3}{4},1\right]$
+is completely disjoint from the interval $\left[0,\tfrac{1}{2}\right]$
+and no amount of shifting of assumptions regarding the precise outcome
+of the uncertain observations could change that disjointness. However,
+as shown next, a sharp transition occurs when $\delta=\tfrac{1}{3}$.
+
+When the proportion of uncertain data reaches $\frac{1}{3}$, the
+probability measure that assigns to each event the entire range of
+possibilities is $\bar{\mu}_{2}$ defined in Table~\ref{tab:probability-measures}.
+This is also not a valid probability measure by the same argument
+as above. However, in this case $\bar{\mu}_{2}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
+and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{2}\left(P_{0}\right)+\bar{\mu}_{2}\left(P_{1}\right)$
+have a \emph{common point}. Hence, by assuming that the uncertain
+data for one-dimensional projectors always support the associated
+event, while those for two-dimensional projectors always refute the
+event, we can find the probability measure~$\bar{\mu}_{2}'$ that
+can verified to be a valid QIVPM and is consistent with the experimental
+data.
+
+A similar situation happens when more than $\frac{1}{3}$ of data
+is uncertain. In particular, if half of the data is uncertain, the
+probability measure~$\bar{\mu}_{3}$ that assigns to each event the
+entire range of possibilities is already a QIVPM.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{The Born Rule and Gleason's Theorem}
+
+\label{sec:Gleason}
+
+A conventional quantum probability measure can be easily constructed
+from a state $\rho$ according to the Born rule \cites{Born1983}{Mermin2007}{Jaeger2007}.
+According to Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum},
+this state $\rho$ is also the unique state consistent with any possible
+probability measure.
+
+\subsection{Finite-Precision Extension of Gleason's Theorem}
+
+In order to re-examine these results in our framework, we first reformulate
+Gleason's theorem in QIVPMs using infinitely precise uncountable intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:
+
+\begin{thm}[$\mathscr{I}_{\infty}$ Variant of the Gleason Theorem]\label{cor:Gleason's-1}In
+a Hilbert space $\Hilb$ of dimension $D\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
+the state $\rho$ consistent with~$\bar{\mu}$ on every projector
+is unique, i.e., there exists a unique state~$\rho$ such that $\coreBorn\left(\bar{\mu},\events\right)=\{\rho\}$.
+\end{thm}
+
+Now let us consider relaxing $\mathscr{I}$ to a countable set of
+finite-width intervals. As the intervals in the image of a QIVPM become
+less and less sharp, we expect more and more states to be consistent
+with it. In the limit of minimal sharpness, all states~$\rho$ are
+consistent with the QIVPM 
+\begin{equation}
+\bar{\mu}\left(P\right)=\begin{cases}
+\imposs & \textrm{ if }P=\mathbb{0}\,;\\
+\necess & \textrm{ if }P=\mathbb{1}\,;\\
+\unknown=\left[0,1\right] & \textrm{ otherwise}
+\end{cases}
+\end{equation}
+mapping nearly all projections to the \emph{unknown} interval~\unknown.
+There is however a subtlety: as shown in the theorem below, it is
+possible for an arbitrary assignment of intervals to projectors to
+be globally inconsistent.
+
+% \noindent For general QIVPMs mapping to imprecise intervals, we also
+% want to seek a simple rule to construct them, and to understand which
+% states are consistent with them. However, if measurement intervals are
+% too imprecise, the state consistent with the results of measurements
+% on some projectors might contradict the state induced by some other
+% projectors. Indeed we can formally prove that, in general, there may
+% be \emph{no} state consistent with some arbitrary QIVPM.
+
+\begin{thm}[Empty Cores Exist for General QIVPMs]\label{thm:Non-extensible-of-Gleason's}There
+exists a Hilbert space ${\cal H}$ and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
+%% ajh: fixed garbled statement, add ${\cal H}$
+
+To prove this theorem, we need to construct a QIVPM on some Hilbert
+space, and verify that there are no states that are consistent (see
+Defs.~\ref{def:Consistency} and \ref{def:core}) with it on all
+possible events. Assume a Hilbert space of dimension $D=3$ with orthonormal
+basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
+$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and assign 
+\begin{equation}
+\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
+\end{equation}
+The map~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined in
+Table~\ref{tab:non-Born-QIVPM} can be verified to be a QIVPM~\cite{TaiThesis2018}.
+\begin{table}
+\caption{\label{tab:non-Born-QIVPM}QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+on a Hilbert space of dimension~$D=3$. Events are listed in the
+column labeled by $P$.}
+
+\begin{tabular}{cc}
+\toprule 
+\addlinespace
+$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+\midrule
+\midrule 
+\addlinespace
+$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$  & $\imposs$\tabularnewline
+\midrule 
+\addlinespace
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, $\mathbb{1}-\proj{\ps'}$  & $\necess$\tabularnewline
+\midrule 
+\addlinespace
+All other projectors  & $\unknown$\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+
+Next we will prove by contradiction that $\coreBorn\left(\bar{\mu},\events\right)$
+is the empty set. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
+where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since we assumed the
+core $\coreBorn\left(\bar{\mu},\events\right)$ is non-empty, so $\muB_{\rho}(P)\in\bar{\mu}(P)$,
+and Table~\ref{tab:non-Born-QIVPM} tells us that $\bar{\mu}(\proj{0})=\imposs=[0,0]$,
+we must conclude that $\muB_{\rho}(\proj{0})=0\in[0,0]$, and similarly
+for $\proj{\ps}$ and $\proj{\ps'}$. If this is true, then $\ip{0}{\phi_{j}}=\ip{\ps}{\phi_{j}}=\ip{\ps'}{\phi_{j}}=0$
+for all~$j$, and thus \begin{subequations} 
+\begin{eqnarray}
+ &  & \ip{1}{\phi_{j}}=\sqrt{2}\ip{\ps}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,,\\
+ &  & \ip{2}{\phi_{j}}=\sqrt{2}\ip{\ps'}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,.
+\end{eqnarray}
+\end{subequations} The above equations imply $\ket{\phi_{j}}=\ket{0}\ip{0}{\phi_{j}}+\ket{1}\ip{1}{\phi_{j}}+\ket{2}\ip{2}{\phi_{j}}=0$,
+violating the assumption that $\ket{\phi_{j}}$ is a normalized state,
+and thus the theorem is proved.
+
+The fact that a collection of poor measurements on a quantum system
+cannot reveal the underlying state is not surprising. Under certain
+conditions, we can however guarantee that the uncertainty in measurements
+is consistent with \emph{some} non-empty collection of quantum states.
+Furthermore, we can relate the uncertainty in measurements to the
+volume of quantum states such that, in the limit of infinitely precise
+measurements, the volume of states collapses to a single state.
+
+To that end, we introduce the concept of \emph{interval maps}, which
+we can use to construct a consistent family of QIVPMs. An interval
+map $f:\left[0,1\right]\rightarrow\mathscr{I}$ maps every real-valued
+probability $x\in\left[0,1\right]$ to a set of intervals $f\left(x\right)=\left[\ell,r\right]$
+containing $x$, where $\left[0,1\right]$ denotes the set of real-valued
+probabilities (this should not be confused with the interval-valued
+probability $\unknown$). We also need a notion of \emph{norm} to
+quantify the distance between (pure or mixed) states. The norm of
+a pure state $\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
+For any given Hermitian operator~$A$, we choose the operator norm
+$\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
+which is also known as the $2$-norm or the spectral norm~\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
+In fact, for any such matrix, including the density matrix~$\rho$,
+this norm is the maximum absolute value of its eigenvalues. Then,
+a finite-precision extension of Gleason's theorem can be stated as
+follows:
+
+\begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
+$f:\left[0,1\right]\rightarrow\mathscr{I}$ be an interval map and
+let the composition $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$
+is the probability measure induced by the Born rule for a given state~$\rho$.
+Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
+If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
+events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
+then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
+
+The proof proceeds as follows. Given a state~$\rho'$ consistent
+with $f\circ\muB_{\rho}$, we have $\muB_{\rho'}\left(\proj{\psi}\right)\in f\left(\muB_{\rho}\left(\proj{\psi}\right)\right)$
+for any one-dimensional projector $P=\proj{\psi}$. Since the maximum
+length of the intervals in $\mathscr{I}$ is $\alpha$, it is also
+the upper bound of the difference: 
+\[
+\left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le\alpha\,.
+\]
+Since $\rho-\rho'$ is Hermitian, $\max_{\left\Vert \psi\right\Vert =1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
+is the maximum absolute value of the eigenvalues of $\rho-\rho'$~\cite{544199},
+and equal to $\left\Vert \rho-\rho'\right\Vert $~\cite{GolubVanLoan1996,Foucart2012}.
+Hence, $\left\Vert \rho-\rho'\right\Vert \le\alpha$.
+
+\subsection{Ultramodular Functions}
+
+Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
+theorem in the sense that it accounts for a larger class of probability
+measures that includes the conventional one as a limit. The theorem
+is however “special” in the sense that it only applies to the
+particular class of QIVPMs constructed by composing an interval map
+with a conventional quantum probability measure. QIVPMs constructed
+in this manner have some peculiar properties that we examine next.
+
+An interval map is called \emph{ultramodular} if it satisfies the
+following properties:
+
+\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
+a collection of intervals $\mathscr{I}$ including $\imposs$ and
+$\necess$, an interval map $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
+is called ultramodular if: \begin{subequations}\label{eq:iota-constraints}
+\begin{eqnarray}
+ &  & \ultramodular(0)=\imposs\,,\\
+ &  & \ultramodular(1)=\necess\,,\\
+ &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
+\end{eqnarray}
+\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$,
+and $x_{2}\in\left[0,1\right]$ such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
+we have: 
+\begin{equation}
+\ultramodular\left(y\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
+\end{equation}
+\end{definition}
+
+\noindent The first three constraints, Eqs.~(\ref{eq:iota-constraints}),
+are the direct counterpart of the corresponding QIVPM constraints,
+Eqs.~(\ref{eq:QIVPM-constraints}); the last condition, Eq.~(\ref{eq:iota-Inclusion}),
+is the direct counterpart of the convexity conditions, Eqs.~(\ref{eq:classicalconvex})
+and (\ref{eq:QuantumInterval-valuedProbability-Inclusion}) \cites{Choquet1954}{Shapley1971}{NgMoYeh1997Chinese}{MarinacciMontrucchio2005}.
+Therefore, these conditions guarantee that, for any conventional quantum
+probability measure $\mu$, the composition $\ultramodular\circ\mu$
+defines a valid QIVPM. Conversely, if for every quantum probability
+measure $\mu$, it is the case that $f\circ\mu$ is a QIVPM, then
+the interval map~$f$ is an ultramodular function. Formally, we have
+the following result:
+
+\begin{thm}[Equivalence of Ultramodular Functions and IVPMs]\label{thm:iota-statements}The
+following three statements are equivalent: \begin{enumerate}
+
+\item \label{enu:iota-subject-to}A function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
+is ultramodular.
+
+\item \label{enu:iota-mu-CIVPM}The composite function~$\ultramodular\circ\mu:\eventsC\rightarrow\mathscr{I}$
+is a classical IVPM for all classical probability measures~$\mu:\eventsC\rightarrow\left[0,1\right]$.
+
+\item \label{enu:iota-mu-QIVPM}The composite function~$\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$
+is a QIVPM for all quantum probability measures~$\mu:\events\rightarrow\left[0,1\right]$.
+\end{enumerate} \end{thm}
+
+Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
+and~\ref{enu:iota-mu-QIVPM} as we have outlined above. Conversely,
+for the quantum case, we want to show that if $\ultramodular$ is
+not ultramodular, then for some quantum probability measure $\mu$,
+the composite $\ultramodular\circ\mu$ might not be a QIVPM. Suppose
+there are three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but they don't
+satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the state: 
+\[
+\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-y\right)\proj{3}\,.
+\]
+The induced map $\ultramodular\circ\muB_{\rho}$ constructed using
+the Born rule and blurred by $\ultramodular$ fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. In
+other words, this induced map fails to be a QIVPM. For the classical
+case, if $\ultramodular$ is not ultramodular, we also want to find
+a classical probability measure $\mu:\eventsC\rightarrow\left[0,1\right]$
+such that $\ultramodular\circ\mu$ is not a classical IVPM. This can
+be done by restricting our previous quantum probability measure $\muB_{\rho}$
+to the space of events $\eventsC$ generated by the mutually commuting
+projectors $\proj{0}$, $\proj{1}$, $\proj{2}$, and $\proj{3}$.
+The restricted function $\mu=\muB_{\rho}|_{\eventsC}$ is then a classical
+probability measure, and the induced map $\ultramodular\circ\mu$
+fails to be a classical IVPM for the same reason as in the quantum
+case.
+
+In other words, essential properties of QIVPMs constructed using interval
+maps can be gleaned from the properties of ultramodular functions.
+The following is a most interesting property in our setting:
+
+\begin{thm}[Range of Ultramodular Functions]\label{thm:convex-uncountable}For
+any ultramodular function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$,
+either $\mathscr{I}=\mathscr{I}_{0}$ as defined in Eq.~(\ref{eq:3-value-intervals})
+or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
+
+Since $\ultramodular$ maps to intervals, we can decompose it into
+two functions: its left-end and right-end, where $\left[\ultramodularL\left(x\right),\ultramodularR\left(x\right)\right]=\ultramodular\left(x\right)$.
+By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\ultramodularL:\left[0,1\right]\rightarrow\left[0,1\right]$
+is Wright-convex~\cite{Wright1954,RobertsVarberg1973,PecaricTong1992},
+i.e., 
+\[
+\ultramodularL\left(y\right)+\ultramodularL\left(x_{2}\right)\ge\ultramodularL\left(x_{0}+x_{2}\right)+\ultramodularL\left(x_{1}+x_{2}\right)
+\]
+for three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+with $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$. Together with the
+fact that $\ultramodularL$ maps to a bounded interval $\left[0,1\right]$,
+the left-end function~$\ultramodularL$ must be continuous on the
+unit open interval $\left(0,1\right)$~\cite{MarinacciMontrucchio2005}.
+Therefore, either $\ultramodular$ maps every number in $\left(0,1\right)$
+to the same interval, or the number of intervals to which $\ultramodular$
+maps must be uncountable.
+
+To summarize, a conventional quantum probability measure has an uncountable
+range $[0,1]$. A QIVPM constructed by blurring such a conventional
+quantum probability measure must also have an uncountable range of
+intervals. Of course, any particular QIVPM, or any particular experiment,
+will use a fixed collection of intervals appropriate for the resources
+and precision of the particular experiment.
 
@@
 \begin{comment}
- \bibliographystyle{plain}
-\bibliography{prop}
+ \printbibliography
 \end{comment}

### 2018-11-09 dissertation.tex
dissertation.lyx Updated according to Prof. Hanson's suggestion...

@@
-%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\usepackage{mmap}
+\usepackage{csquotes}
 \usepackage{comment}
@@
 \usepackage{xeCJK}
-\setCJKmainfont{新細明體}
-\usepackage{unicode-math}
+\setCJKmainfont{SimSun}
 
@@
 \newtheorem{lemma}{Lemma}[chapter]
+\newtheorem{case}{Case}
 \theoremstyle{definition}
 \newtheorem{definition}{Definition}[chapter]
+\newtheorem{question}{Question}[chapter]
 \newtheorem*{method}{Method}
+\newtheorem{example}{Example}[chapter]
 
@@
 
-\newcommand{\muB}{\ensuremath{\mu^{\mathrm{B}}}}
-\newcommand{\muC}{\ensuremath{\mu^{\mathrm{C}}}}
-\newcommand{\muF}{\ensuremath{\mu^{\mathrm{F}}}}
-\newcommand{\barmuD}{\ensuremath{\bar{\mu}^{\mathrm{D}}}}
-\newcommand{\events}{\ensuremath{\mathcal{E}}}
-\newcommand{\eventsC}{\ensuremath{\events_{C}}}
+\usepackage{unicode-math}
+\RequirePackage{ifthen}
+\@ifpackageloaded{unicode-math}{}{
+ \newcommand{\symbf}{\mathbf}
+ \newcommand{\symrm}{\mathrm}
+ \newcommand{\symcal}{\mathcal}
+ \newcommand{\symbb}{\mathbb}
+}
+\newcommand{\muB}{\ensuremath{\mu^{\symrm{B}}}}
+\newcommand{\muC}{\ensuremath{\mu^{\symrm{C}}}}
+\newcommand{\muF}{\ensuremath{\mu^{\symrm{F}}}}
+\newcommand{\symrmL}{\ensuremath{\symrm{L}}}
+\newcommand{\symrmR}{\ensuremath{\symrm{R}}}
+\newcommand{\mul}[1][]{\ensuremath{\mu^{\symrmL{#1}}}}
+\newcommand{\mur}[1][]{\ensuremath{\mu^{\symrmR{#1}}}}
+\newcommand{\barmuD}{\ensuremath{\bar{\mu}^{\symrm{D}}}}
+\newcommand{\events}{\ensuremath{\symcal{E}}}
+\newcommand{\eventsC}{\ensuremath{\events_{\symrm{C}}}}
 \newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
 \newcommand{\gmult}{*}
-\newcommand{\Fpx}[1]{\mathbb{F}_{{#1}}}
+\newcommand{\Fpx}[1]{\symbb{F}_{{#1}}}
 \newcommand{\Fp}{\Fpx{p}}
@@
 \newcommand{\ffd}[1]{\ffx{#1}{d}}
-\newcommand{\VVec}[1]{\vec{\bf #1}}
-\newcommand{\mathReal}{\mathbb{R}}
-\newcommand{\mathComplex}{\mathbb{C}}
+\newcommand{\VVec}[1]{\vec{\symbf{#1}}}
+\newcommand{\mathReal}{\symbb{R}}
+\newcommand{\mathComplex}{\symbb{C}}
 \newcommand{\braket}[2]{\ip{#1}{#2}}
@@
 \newcommand{\Eq}[1]{Eq.~(\ref{#1})}
-\newcommand{\Sphere}[1]{\mathbf{S}^{#1}}
+\newcommand{\Sphere}[1]{\symbf{S}^{#1}}
 \newcommand{\R}{\mathReal}
-\newcommand{\rme}{\mathrm{e}}
-\newcommand{\rmi}{\mathrm{i}}
-\newcommand{\CP}[1]{\mathComplex\mathbf{P}^{#1}}  % Complex projective space
-\newcommand{\DCP}[1]{\mathbf{D}\mathComplex\mathbf{P}^{#1}} % Discrete complex projective
+\newcommand{\rme}{\symrm{e}}
+\newcommand{\rmi}{\symrm{i}}
+\newcommand{\rmd}{\symrm{d}}
+\newcommand{\CP}[1]{\mathComplex\symbf{P}^{#1}} % Complex projective space
+\newcommand{\DCP}[1]{\symbf{D}\mathComplex\symbf{P}^{#1}} % Discrete complex projective
 \def\fh{\mathfrak{h}}
@@
 \newcommand{\ms}{\texttt{-}}
-\newcommand{\Hilb}{\mathcal{H}}
+\newcommand{\Hilb}{\symcal{H}}
 \newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
-\def\C{{\mathbb{C}}}
-\newcommand{\ultramodular}{\mathcal{M}}
+\def\C{{\symbb{C}}}
+\newcommand{\ultramodular}{\symcal{M}}
 \newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{L{#1}}}}
 \newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{R{#1}}}}
+\newcommand{\pmeas}{\ensuremath{\mu}}
+\newcommand{\nb}{\nolinebreak[3] }
 
@@
 \department{Department of Computer Science}
+
+\usepackage{datetime2}
+\usepackage{datetime2-calc}
+\monthGranted{\DTMmonthname{\month}}
+\yearGranted{\the\year}
+
+\usepackage{tabularx}
 
@@
 \begin{document}
-%data for Title Page
-
 \title{Discrete Quantum Theories and Computing}
-
-\author{Yu-Tsung Tai\\
-(戴淯琮)}
-
-\date{\today}
+\author{Tai, Yu-Tsung}
 
@@
 %data for Acceptance Page
-\committeeMember{Amr Sabry (\textarabic{عمرو صبري}), PhD} \committeeMember{Gerardo
-Ortiz, PhD} \committeeMember{Dylan Paul Thurston, PhD} \committeeMember{Andrew
-J. Hanson, PhD} \committeeMember{Shouhong Wang (汪守宏), PhD} \defensedate{Defense
-Date} \acceptancepage
+\committeeMember{Amr A. Sabry, PhD} \committeeMember{Dylan Paul
+Thurston, PhD} \committeeMember{Gerardo Ortiz, PhD} \committeeMember{Andrew
+J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{November
+29, 2018} \acceptancepage
 
 %data for Copyright Page
-\cryear{2018}
 \copyrightpage
 
-\begin{dedication}I would like to dedicate my thesis to my parents,
-Cheng-Tien Tai (戴振沺) and Feng-Ming Chang (張鳳鳴). Thanks for encouraging
-me to study abroad and all your support during my Ph.D. study.\end{dedication}
-
-\begin{acknowledgments}I want to thank Prof.~Gerardo Ortiz, Prof.~Amr
-Sabry (\textarabic{عمرو صبري}), and Prof.~Andrew Hanson for publishing
-three papers \cite{geometry2013,DQT2014,THOS2018} with me, and enormous
-other things. These papers become the main part of my thesis, especially
-most of Chapter~\ref{chap:DQT=000026DQC} is based on “Geometry
-of discrete quantum computing”~\cite{geometry2013} and “Discrete
-quantum theories” (DQT)~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
-is based on “Quantum Interval-Valued Probability: Contextuality
-and the Born Rule” (QIVPM) \cite{THOS2018}. Together with Prof.~Dylan
-Thurston and Prof.~Shouhong Wang (汪守宏), I want to thank you for getting
-together to understand what I did and passing my dissertation proposal
-Spring 2017. I also thank Prof. Dylan Thurston for serving in my advisory
-committee and my Tier 3 committee, with other advisory committee members
-passing my Computer Science qualifying exam Spring 2016. Especially,
-my survey of real computation in the qualifying exam inspired me the
-comparison of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
+\begin{dedication}To my parents, Cheng-Tien Tai (戴振沺) and Feng-Ming
+Chang (張鳳鳴).\end{dedication}
+
+\begin{acknowledgments*}\todo{Confirm people to be acknowledged
+like the way being acknowledged... }I want to thank Prof.~Gerardo
+Ortiz, Prof.~Amr Sabry (\textarabic{عمرو صبري}), and Prof.~Andrew
+Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
+with me, and enormous other things. These papers become the main part
+of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
+is based on “Geometry of discrete quantum computing”~\cite{geometry2013}
+and “Discrete quantum theories” (DQT)~\cite{DQT2014}; most
+of Chapter~\ref{chap:QIVPM} is based on “Quantum Interval-Valued
+Probability: Contextuality and the Born Rule” (QIVPM) \cite{THOS2018}.
+Together with Prof.~Dylan Thurston and Prof.~Shouhong Wang (汪守宏),
+I want to thank you for getting together to understand what I did
+and passing my dissertation proposal Spring 2017. I also thank Prof.
+Dylan Thurston for serving in my advisory committee and my Tier 3
+committee, with other advisory committee members passing my Computer
+Science qualifying exam Spring 2016. Especially, my survey of real
+computation in the qualifying exam inspired me the comparison of quantum
+computer and analog computer in Chapter~\ref{chap:Introduction}.
 Chapter~\ref{chap:Introduction} also contains the motivation in
 my application for Rethinking Foundations of Physics 2017 workshop
-reviewed by Prof. Amr Sabry (\textarabic{عمرو صبري}). I want to thank
-Prof. Lawrence Moss for inviting me to present our results in the
-interdisciplinary logic seminar and theory seminar in Computer Science,
-co-chairing my Tier 3 committee, writing an assessment letter for
-me, and drawing my attention on Prof.~Abramsky's paper~\cite{Abramsky2012},
+reviewed by Prof. Amr Sabry (\textarabic{عمرو صبري}). I want
+to thank Prof. Lawrence Moss for inviting me to present our results
+in the interdisciplinary logic seminar and theory seminar in Computer
+Science, co-chairing my Tier 3 committee, writing an assessment letter
+for me, and drawing my attention on Prof.~Abramsky's paper~\cite{Abramsky2012},
 which inspired me to merge quantum probability with discrete quantum
@@
 deterministic quantum algorithms in the term paper for SLST-T501 Academic
-Writing course as presented in Sec.~\ref{discretequantumtheoryI}.
+Writing course as presented in Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
 I want to thank Traci Nagle for going through the literature review
@@
 \todo{Type a table for acknowledgment so that I would have to write
-“I thank” so many times here?}Many people in both department
+“I thank” so many times here? }Many people in both department
 of Mathematics and Computer Science need to do something more to make
@@
 Finally, thank Jin-Ru Yang (楊謹如) for everything could not be written
-here.\end{acknowledgments}
-
-\begin{preface}
+here.\end{acknowledgments*}
+
+\begin{preface*}
 \begin{itemize}
 \item The latest version of this thesis is in GitHub:
-\[
-\hspace{-4em}\textrm{https://github.com/yuttai/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/blob/master/dissertation.pdf}
-\]
+\begin{verbatim}
+https://git.io/fxbuG
+\end{verbatim}
 \item Its source code is typeset using \LyX ~\cite{LyX} in:
-\[
-\hspace{-4em}\textrm{https://github.com/yuttai/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/blob/master/dissertation.lyx}
-\]
+\begin{verbatim}
+https://git.io/fxbuE
+\end{verbatim}
 \item Any comments can be left in the Issue part of the GitHub Repository:
-\[
-\hspace{-4em}\textrm{https://github.com/yuttai/Contextuality-and-Nonlocality-in-Discrete-Quantum-Theory/issues}
-\]
+\begin{verbatim}
+https://git.io/fxbug
+\end{verbatim}
 \end{itemize}
-\end{preface}
-\begin{abstract}
-Our primary research interest is to build a quantum computing model
-characterizing realistic quantum computers. While most of the quantum
-computing models based on uncomputable numbers, that is, the continuum
-of real numbers, most of the classical computers in our daily life
-are digital instead of analog computers. This highlight the necessity
-to investigate discrete models for quantum theory and computing. Specifically,
-we start from replacing the continuum of complex numbers by the discrete
-finite fields. Although we have fruitful results on their geometric
-implications and computing powers, their probability models are still
-not completely satisfactory. To address this issue, we further exploited
-quantum interval-valued probability, and proved an imprecise version
-of foundational results such as the Gleason and Kochen-Specker theorems.
-\end{abstract}
+\end{preface*}
+
+\begin{abstract*}Most of the quantum computing models are based on
+the continuum of real numbers, despite the fact that classical digital
+computers faithfully realize the prediction of discrete computational
+models, while analog computers in reality are far weaker than the
+theoretical prediction of continuous computational models. Since one
+of the important factors of this gap is the measurement precision,
+we hope to build a more faithful model by investigating discrete quantum
+computing models and incorporating the idea of finite precision measurement
+into the quantum theory.
+
+We first replace the continuum of complex numbers by discrete finite
+fields in the quantum theory. The simplest theory, defined over unrestricted
+finite fields, is so weak that it cannot express Deutsch’s algorithm.
+This quantum theory is, however, also so powerful that it can be used
+to solve the $\usat$ problem, which is as hard as a general $\NP$-complete
+problem. The second framework employs only finite fields with no solution
+to $x^{2}+1=0$, and thus permits an elegant complex representation
+of the extended field by adjoining $\rmi=\sqrt{-1}$. Because the
+states of a discrete $n$-qubit system are in principle enumerable,
+we can count the number of states, and determine the proportions of
+entangled and unentangled states. Although this improved framework
+allows the probabilistic Grover search algorithm in a local region,
+we haven't found sensible correspondences between quantum probability
+measures and the whole state space in general.
+
+To search a sensible correspondence and to incorporate the idea of
+finite precision measurement at the same time, we shift our attention
+to consider quantum interval-valued probability measures (IVPMs).
+This interval-valued framework not only provides a natural generalization
+of both classical IVPMs and conventional quantum probability measures,
+but also establishes bounds on the validity of the Kochen-Specker
+and Gleason theorems in realistic experimental environments.\end{abstract*}
+
 \tableofcontents{}
@@
 When we check the compatibility between quantum mechanics and computer
-science, we found their fundamental assumptions are different. On
-one hand, the quantum theory is based on infinitely precise real and
-complex numbers. Its prediction could fit the physical reality by
-utilizing error analysis technique although these prediction cannot
-be completely faithful because of the measurement precision. On the
-other hand, current computers mostly perform digital computation,
-except some analog chips communicating with physical world~\cite{Camenzind2005}.
-While the computability of digital parts is faithfully characterized
-by its theoretical model, the Turing machine~\cite{Turing_1937},
-the computability of analog chips in reality is far weaker than the
-theoretical prediction of real computation \cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
-One of the reason behind this gap is also due to measurement precision,
-and some of their computability difference cannot be compensated by
-error analysis technique. All these problems for classical computation
-could potentially apply to quantum computation. Because we are agnostic
-about whether the physical reality is ultimately discrete or continuous,
-we tried to develop two different types of quantum theories and computing
-models to address these issues. Since the discrete classical computing
-model faithfully represents digital computers, we first tried to build
-discrete quantum theories and computing by considering quantum theories
-and computing over finite fields in Chapter~\ref{chap:DQT=000026DQC}.
+science, we found one of the biggest difference is that the success
+of digital computers is based on discrete computation while quantum
+physics is usually based on the continuum of real and complex numbers.
+This suggests whether the computational model is discrete or continuous
+may be another important factor parallel to \todo{Find a phrase better
+than “parallel to”. }whether the model is classical or quantum.
+\todo{Add discussion about randomness, like: “Another big difference
+is that randomness in quantum computing is inherited from its underlying
+quantum physics while randomness in probabilistic Turing machine is
+an addition feature acquired by adding random bits to a Turing machine.”
+}Although building a realistic quantum computer is an ongoing project~\cite{Shieber2018},
+reviewing the challenge posed by classical discrete and continuous
+models might provide what we are facing when moving on to the quantum
+world.
+
+There was a long history that human believe they can compute with
+the continuum of real numbers. If the length of a line segment represents
+a real number, Euclid thought he could use an unmarked ruler and a
+compass to compute the real numbers about 300 B.C~\cite{MCC2006}.
+After logarithm was discovered, a slide rule, also known as a slipstick,
+is used to compute multiplication, division, and more complex operations
+as a mechanical analog computer~\cite{wiki:SlideRule}. Although
+more and more complex analog computers, like integrators \cite{wiki:Integrator,wiki:ChargeAmplifier},
+is used, there is still a gap between the computation preformed in
+an analog computer and the idealized operations among real numbers.
+One problem is that the quality computed by an analog computer might
+actually be quantized. For example, charge amplifier is believed to
+produce the integrated value of the input current~\cite{wiki:ChargeAmplifier}
+although the input charge must actually be an integer multiple of
+the elementary charge~\cite{wiki:ElementaryCharge}. Even for the
+qualities which doesn't known to be quantized, the observed computational
+power of an analog computer might still be weaker than the theoretical
+prediction because the precision of an analog computer is limited
+generally three or four significant figures~\cite{wiki:AnalogComputer}.
+For example, Blum, Cucker, Shub, and Smale modeled their machine to
+allow the operations of deciding whether a number is greater or equal
+to zero over real numbers and whether a number is exactly zero over
+complex numbers \cites{BSS1989}{Ziegler2007}{blum2012complexity}.
+Since no physical analog computer could branch in these operations
+based on a few significant figures, the theoretical prediction of
+Blum-Cucker-Shub-Smale (BCSS) machine cannot fully apply on physical
+devices.
+
+Being aware that symbols within a computation should not differ to
+an arbitrarily small extent~\cite{Turing_1937}, Turing defined his
+machine with only finite number of symbols and configurations. One
+of the benefit of discrete computation is that it can be reliably
+repeated with exact equivalence. Therefore, any digital computer can
+faithfully simulate a Turing machine limited only by the available
+memory and time.
+
+\begin{table}
+\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical computational
+models and their physical realizations}
+\begin{tabularx}{\linewidth}{ccX}
+\toprule 
+\addlinespace
+ & Model & Physical Realization\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+Continuum & BCSS machine & The precision of an analog computer was limited so that an analog computer may not reproduce the theoretical prediction reliably.\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+Discrete & Turing machine & A digital computer can be reliably repeated with exact equivalence.\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabularx}
+\end{table}
+The situations for classical computation is summarized in Table~\ref{tab:Comparison},
+and similar situations could potentially be applied to quantum computation.
+\todo{Introduction cleaning up until here. }Similar to classical
+analog computers manipulating, say, the position of substance, the
+most widely used model of quantum computing, the quantum circuit model,
+manipulates the probability amplitudes to do the computation. \todo{Play
+with some cloud quantum computers to see if I can find more support
+evidence. }Because we are agnostic about whether probability amplitude
+is quantized or can really be valued in the continuum of complex numbers,
+we tried to develop two different types of models: the quantum theories
+and computing over finite fields are discrete models, and the quantum
+interval-valued probability measures incorporate the idea of measurement
+precision into the quantum theory. To distinguish the modified quantum
+theories from the usual ones, the usual ones will be called the ‘conventional
+quantum theory’ where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ‘actual,’ ‘standard,’
+and ‘ordinary’ quantum theory.}.
+
+Since conventional probability amplitude is in the field of complex
+numbers, and the field structure is essential to compute the probability
+from some probability amplitudes, we in Chapter~\ref{chap:DQT=000026DQC}
+tried to build discrete quantum theories and computing by considering
+them over finite fields.
+
 Since error analysis technique cannot always compensate the inevitable
@@
 
-\chapter{Conventional Quantum Theory and Computing}
+\chapter{Conventional Quantum Theory\label{chap:Conventional-Quantum-Theory}}
 
@@
 we introduce the important issues of \ref{enu:measurement-framework}
-and the foundations of quantum probability space. In Sec.~\ref{sec:Quantum-Circuit-Model},
-we address the property~\ref{enu:unitary-matrix} by describing product
-and entangled $n$-qubit states and unitary matrices in quantum circuit
-model.
+and the foundations of quantum probability space. The observables
+and expectation values defined in Sec.~\ref{sec:fuzzy} will be used
+to understand the geometry of entangled states in Sec.~\ref{sec:The-geometry-of}.
+The property~\ref{enu:unitary-matrix} directly related to quantum
+circuit will be introduced later in Chapter~\ref{chap:DQT=000026DQC}
+when we dive into quantum algorithms.
 
@@
 \end{figure}
-
 The resulting manifold is the two-sphere $\Sphere{2}$ (a 2-manifold)
@@
 \end{figure}
-
 Thus the geometry of a single qubit reduces to transformations among
@@
 $D$-dimensional state's dynamics. In mathematical notation, this
-would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$\todo{Citation?}.
-For $D=2$, the single qubit, we have $2-1=1$, and the base space
-of the circle bundle is $\CP{1}=\Sphere{2}$, the usual Bloch sphere.
-Note that only for $D=2$ is this actually a sphere-like geometry
-due to an accident of low-dimensional topology.
+would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$.
+\todo{Citation? }For $D=2$, the single qubit, we have $2-1=1$,
+and the base space of the circle bundle is $\CP{1}=\Sphere{2}$, the
+usual Bloch sphere. Note that only for $D=2$ is this actually a sphere-like
+geometry due to an accident of low-dimensional topology.
 
@@
 of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
+Given a finite sample space~$\Omega$, and its power set $2^{\Omega}$
+as the classical event space, a classical probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+is a function subject to the following constraints: $\mu\left(\emptyset\right)=0$,
+$\mu\left(\Omega\right)=1$, $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
+and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
+for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
+
 In the quantum case, the events of interest are specified by \emph{projection
@@
 where $\events$ is the set of all events, (i.e., projectors on a
-given Hilbert space), subject to the following constraints: $\mu\left(\mathbb{0}\right)=0$,
-$\mu\left(\mathbb{1}\right)=1$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$,
+given Hilbert space), subject to the following constraints:
+\begin{align}
+\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability}
+\end{align}
 and for each pair of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
@@
 value of an observable~$\mathbf{O}$ having spectral decomposition
-$\mathbf{O}=\sum_{i=1}^{D}\lambda_{i}P_{i}$, with eigenvalues $\lambda_{i}\in\mathbb{R}$,
+$\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$, with eigenvalues $\lambda_{i}\in\mathbb{R}$,
 as \cite{544199,Jaeger2007}: 
 \begin{equation}
-\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{D}\lambda_{i}\mu\left(P_{i}\right)\,,\label{eq:quantum-expectation}
+\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(P_{i}\right)\,,\label{eq:quantum-expectation}
 \end{equation}
@@
 and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule induces a
-probability measure $\muB_{\rho}$ defined as $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)$
-\cites{Born1983}{Mermin2007}{Jaeger2007}.
+probability measure $\muB_{\rho}$ defined as \cites{Born1983}{Mermin2007}{Jaeger2007}
+\begin{equation}
+\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)\,.\label{eq:mixed-Born}
+\end{equation}
 
@@
 
-When $D=2$, there are some non-Born quantum probability measures.
-In particular, some non-Born quantum probability measures mapping
-every event to either $0$ or $1$. This kind of probability measure
-is called a non-contextual hidden variable model, and will be discussed
-in Sec.~\ref{sec:Quantum-Contextuality}.
+Although the Born rule is widely be considered a postulate of quantum
+theory, it could be derived from a smaller set of abstract definitions
+and axioms according to Gleason's theorem~\cite{peres1995quantum}.
+Since the Born rule linking the probability amplitudes and probability
+might not hold naively when probability amplitudes is in finite fields
+or the probability becomes an interval. Considering a Gleason-like
+theorem is an appealing method to search a rule computing probability
+in all these cases.
 
@@
 
-\subsection{Fuzzy Measurements}
+\subsection{Issues about Measurements and Contextuality}
 
@@
 
+\todo{Add discussions about contextuality...}
+
+When $D=2$, there are some non-Born quantum probability measures.
+In particular, some non-Born quantum probability measures mapping
+every event to either $0$ or $1$. This kind of probability measure
+is called a non-contextual hidden variable model, and will be discussed
+in Sec.~\ref{sec:Quantum-Contextuality}.
+
 The quantum expectation value can also used to decide whether a state
@@
 
-\section{The geometry of entanglement}
+\section{The geometry of entanglement\label{sec:The-geometry-of}}
 
@@
 \end{equation}
-In general\todo{Ask Gerardo why?}, the reduced density operator~$\rho_{j}$
+In general, \todo{Ask Gerardo why? }the reduced density operator~$\rho_{j}$
 of the $j$-th subsystem can always be expressed as
@@
 
-\section{Hidden Variable Model and Quantum Contextuality\label{sec:Quantum-Contextuality}}
-
-\todo{Explain enough background knowledge to support the discussion
-about contextuality in the end of Sec.~\ref{modalquantum}. I have
-typed some literature review in writing course, but I need to decide
-whether it could be used or not before finish Sec.~\ref{sec:fuzzy}.}
-
 \chapter{Quantum Theories and Computing over Finite Fields\label{chap:DQT=000026DQC}}
+
+\todo{Add some introductory text...}
 
@@
 in a way that outperforms conventional quantum computing. The classical
-\usat\ problem (also known as $\lang{USAT}$ or $\lang{UNAMBIGUOUS-SAT}$\todo{Add
-citation about where these two names come from.}) is the problem
-of deciding whether a given boolean formula has a satisfying assignment,
-assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
+\usat\ problem (also known as $\lang{USAT}$ or $\lang{UNAMBIGUOUS-SAT}$)
+\todo{Add citation about where these two names come from. }is the
+problem of deciding whether a given boolean formula has a satisfying
+assignment, assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
 This problem is, in a precise sense~\cite{Valiant198685}, just as
@@
 \end{figure}
-
 We can prove the unreasonable power of the arbitrary-function \usat\ starting
@@
 
-\paragraph*{Case I: $f$ is unsatisfiable; the measurement deterministically
-produces $\ket{0}\ket{\overline{0}}$.}
-
-\todo{This part use $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$
+\begin{case}$f$ is unsatisfiable; the measurement deterministically
+produces $\ket{0}\ket{\overline{0}}$.\end{case}
+
+\begin{proof}\todo{This part use $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$
 while previous parts use $\ket{\Psi}=\ket{\psi_{1}}\cdots\ket{\psi_{j}}\cdots\ket{\psi_{n}}$.
 Moreover, bar is heavily used in QIVPM discussion later, so maybe
-not using bar here????}The state is initialized to $\ket{0}\ket{\overline{0}}$,
+not using bar here???? }The state is initialized to $\ket{0}\ket{\overline{0}}$,
 with $\ket{\overline{0}}=\ket{0}\ket{0}\cdots\ket{0}$, i.e., the
@@
 As the first component of the state is $0$, applying the map $\sigma_{0}$
-(which is the identity) leaves the state unchanged.\todo{Control-not
-need to be defined and explained in Sec.~\ref{subsec:Quantum-Circuits}}
-Applying $S^{\dagger}$ to the first component leaves the state unchanged.
-Measuring the state will deterministically produce $\ket{0}\ket{\overline{0}}$.
-
-\paragraph*{Case II: $f$ is satisfiable; the measurement produces some state
-other than $\ket{0}\ket{\overline{0}}$.}
-
-Assume the function $f$ is satisfiable at some input $a_{1},a_{2},\ldots,a_{n}$
-denoted $\overline{a}$, and where $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$.
+(which is the identity) leaves the state unchanged. \todo{Control-not
+need to be defined and explained in Sec.~\ref{subsec:Quantum-Circuits}
+}Applying $S^{\dagger}$ to the first component leaves the state
+unchanged. Measuring the state will deterministically produce $\ket{0}\ket{\overline{0}}$.\end{proof}
+
+\begin{case}$f$ is satisfiable; the measurement produces some state
+other than $\ket{0}\ket{\overline{0}}$.\end{case}
+
+\begin{proof}Assume the function $f$ is satisfiable at some input
+$a_{1},a_{2},\ldots,a_{n}$ denoted $\overline{a}$, and where $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$.
 In the second step, the state becomes $\ket{0}\ket{\overline{+}}$
@@
 has one occurrence $\ket{0}\ket{\overline{0}}$. \todo{The following
-need to be rewritten.}This can be easily proved as follows. Since
+need to be rewritten. }This can be easily proved as follows. Since
 each $a_{i}$ is either 0 or 1, then each $S(a_{i})$ is either $+$
@@
 $+$ and $0$, when expressed in the standard basis, would consist
-of a superposition containing the state $\ket{0\ldots}$.
-
+of a superposition containing the state $\ket{0\ldots}$.\end{proof}%
 \begin{comment}
@@
 \end{table}
-
 In Table~\ref{tab:Generators-in-F9}, one can notice that $\left(a+b\rmi\right)^{3}=a-b\rmi$.
@@
 phases corresponding to the Hopf fibration circle. \todo{Explain
-the Hopf fibration circle here... ?} Since $\Fpp$ has $p^{2}-1$
+the Hopf fibration circle here... ? }Since $\Fpp$ has $p^{2}-1$
 non-zero values, and the map $\fnorm{\alpha}$ distributes these equally
@@
 
-\subsection{Irreducible Discrete $D$-dimensional States: Generalized Discrete
-Bloch Sphere\label{DQCnqubitBloch.sec}}
+\section{Discrete Quantum Theory (I): Irreducible Discrete $D$-dimensional
+States\label{DQCnqubitBloch.sec}}
 
@@
 we show that $p+1$ discrete values of $\left(\alpha_{0},\alpha_{1}\right)$
-with unit norm map to the same point under the Hopf map \Eq{DQA6.eq}\todo{Does
-Proposition~\ref{appH.sec} really show this?}; we may think of
-these as discrete circles or projective lines of equivalent, physically
-indistinguishable, complex phase. The surviving $p\left(p-1\right)$
+with unit norm map to the same point under the Hopf map \Eq{DQA6.eq};
+\todo{Does Proposition~\ref{appH.sec} really show this? }we may
+think of these as discrete circles or projective lines of equivalent,
+physically indistinguishable, complex phase. The surviving $p\left(p-1\right)$
 values of $\left(\alpha_{0},\alpha_{1}\right)$ correspond to irreducible
@@
 
-\subsubsection{Counting states on the discrete Bloch sphere}
+\subsection{Counting states on the discrete Bloch sphere}
 
@@
 this discrete $\Sphere{2D-1}$ structure map to the \textit{same point\/}
-in $\Hat{a}$\todo{Does Proposition~\ref{appH.sec} really show
-this?}. Each set of $p+1$ redundant points is, geometrically speaking,
+in $\Hat{a}$. \todo{Does Proposition~\ref{appH.sec} really show
+this? }Each set of $p+1$ redundant points is, geometrically speaking,
 the \textit{discrete Hopf fibration circle\/} living above each \textit{irreducible\/}
@@
 
-\subsection{Geometry of Entangled States}
+\section{Discrete Quantum Theory (I): Geometry of Entangled States}
 
@@
 
-\subsubsection{Unentangled vs Entangled Discrete States}
+\subsection{Unentangled vs Entangled Discrete States}
 
@@
 
-\subsubsection{Completely Unentangled States and the Discrete Bloch Sphere}
+\subsection{Completely Unentangled States and the Discrete Bloch Sphere}
 
@@
 
-\subsubsection{Maximal entanglement}
+\subsection{Maximal entanglement}
 
@@
 model still leads to excessive computational power for the unstructured
-database search problem for certain database sizes.\todo{Gil Kalai
-thought it would be interested if we can so Simon's algorithm in DQC(I).
-Since I need to re-type everything, let's postpone this idea for a
-while...}
-
-\subsection{Discrete Deutsch algorithm}
+database search problem for certain database sizes. \todo{Prof.~Gil~Kalai
+thought it would be interested if we can do Simon's algorithm in DQC(I),
+but I don't know when I could organize my unreadable draft to a readable
+one...}
+
+\subsection{Discrete Deutsch algorithm\label{subsec:Discrete-Deutsch-algorithm}}
 
@@
 whether the negative space is necessary or not, or whether the negative
-space has any semantic meaning...}
+space has any semantic meaning... }
 \begin{figure}[t]
@@
 \end{figure}
-
 First, a 2-qubit pure state is initialized to $\ket{\Phi_{1}}=\ket{1}\ket{0}=\left(\begin{smallmatrix}0\\
@@
 
-\section{Discrete Quantum Theory (II): Inner Product Space}
-
-\label{discretequantumtheoryIIa}
+\section{Discrete Quantum Theory (II)}
+
+\subsection{Inner Product Space\label{discretequantumtheoryIIa}}
 
@@
 if $a>b$ and $b>c$, provided $a-b$, $b-c$, and $a-c$ are all
-quadratic residues.\todo{Should we remove the quadratic residue part?
-Since we never use take the square roots of numbers in order range
-later, whether they are the quadratic residues or not doesn't really
-matter...}
+quadratic residues. \todo{Should we remove the quadratic residue
+part? Since we never use take the square roots of numbers in order
+range later, whether they are the quadratic residues or not doesn't
+really matter...}
 
@@
 \begin{table}
-\noindent \centering{}%
+\noindent \centering{}\caption{\label{pseq}Number $k$ of transitively ordered elements for a given
+field $\ff{p}$.}
 \begin{tabular}{cccccccccccc}
@@
 \addlinespace
-\end{tabular}\caption{\label{pseq}Number $k$ of transitively ordered elements for a given
-field $\ff{p}$.}
+\end{tabular}
 \end{table}
-
 As an example, consider the field $\ff{23}$. Looking at the squares
@@
 \begin{table}
-\noindent \centering{}%
+\noindent \centering{}\caption{\label{table_allowed}Allowed probability amplitudes for different
+vector space dimensions $D$ and $k=11$.}
 \begin{tabular}{ll}
@@
 \addlinespace
-\end{tabular}\caption{\label{table_allowed}Allowed probability amplitudes for different
-vector space dimensions $D$ and $k=11$.}
+\end{tabular}
 \end{table}
-
 We can now verify, by using Table~\ref{table_allowed}, that for
@@
 
-\section{Discrete Quantum Theory (II): Cardinal Probability}
-
-\label{discretequantumtheoryIIb}
+\subsection{Cardinal Probability\label{discretequantumtheoryIIb}}
 
@@
 \begin{table}
-\noindent \centering{}%
+\noindent \centering{}\caption{\label{f11-proj.fig}Field norms and probabilities for one-qubit states
+$\ket{\Psi}$ in $F^{2}\left(11\right)$.}
 \begin{tabular}{cccccc}
@@
 \addlinespace
-\end{tabular}\caption{\label{f11-proj.fig}Field norms and probabilities for one-qubit states
-$\ket{\Psi}$ in $F^{2}\left(11\right)$.}
+\end{tabular}
 \end{table}
-
 When measuring cardinal probabilities, \textit{inequalities} can be
@@
 Also notice that the positioning of the initial qubit state $\ket{1}$
-is reversed from~\cite{544199}. }\todo{A little bit more explanation?}
+is reversed from~\cite{544199}. } \todo{A little bit more explanation?}
 \begin{equation}
@@
 \end{equation}
-and that its field norm is $2^{n+1}$.\todo{Verify?} To make sure
+and that its field norm is $2^{n+1}$. \todo{Verify. }To make sure
 that the algorithm works properly, we note that all the probability
@@
 \begin{table}
-\noindent \centering{}%
+\noindent \centering{}\caption{\label{table_long}Extension of transitively ordered elements.}
 \begin{tabular}{cccccccccc}
@@
 \addlinespace
-\end{tabular}\caption{\label{table_long}Extension of transitively ordered elements.}
+\end{tabular}
 \end{table}
-
 For the $2$-qubit Deutsch-Jozsa, the computation is already quite
@@
 scaled to integer values as usual, the state after $l$th iteration
-can written as\todo{Verify the computation??}
+can written as \todo{Verify the computation??}
 \begin{equation}
@@
 The initial information-less $8$-dimensional state vector evolves
-under the application of $\Delta R$ as follows:\todo{Change the
+under the application of $\Delta R$ as follows: \todo{Change the
 whole paragraph to a table?}
@@
 like Shor's~\cite{Shor1999,Mermin2007,Jaeger2007}, don't localize
-their numbers in a small region. Moreover, we still haven't found
-how to manipulate the resulting cardinal probabilities, and hence
-have little idea how to define the mixed states and expectation values.
+their computation in a small region. Moreover, since we haven't found
+a way to manipulate the resulting cardinal probabilities, we have
+little idea how to define the mixed states and expectation values.
 To overcome these issues, we try a different approach to define a
@@
 Recall Gleason's theorem in Sec.~\ref{subsec:Gleason's-Theorem-and}
-states that every quantum probability measure is induced by the Born
-rule in a Hilbert space $\Hilb$ of dimension $D\geq3$. To find a
-Born rule over finite fields, we could follow the steps in Sec.~\ref{sec:fuzzy}
-to define events and probability measures, and see whether we could
-have a Gleason-like theorem which induces a correspondence between
-states and probability measures qualified as a discrete Born rule.
+states that every quantum probability measure is induced a mixed state
+in a Hilbert space $\Hilb$ of dimension $D\geq3$ according to the
+Born rule. To find a Born rule over finite fields, we could follow
+the steps in Sec.~\ref{sec:fuzzy} to define events and probability
+measures, and see whether we could have a Gleason-like theorem which
+induces a correspondence between states and probability measures qualified
+as a discrete Born rule.
 
@@
 a vector space $\mathcal{H}$ of dimension $D$ over the complexified
-field $\Fpp$, the set of events $\events_{p^{2}}$ are recursively
+field $\Fpp$, the set of events $\events_{p^{2}}$ is recursively
 defined as follows: 
@@
 \end{itemize}
-Then we take a quantum probability measure over finite field (QPMFF)
-$\mu:\events_{p^{2}}\rightarrow\left[0,1\right]$ to be an assignment
-of a probability to each event (projection operator~$P$) subject
+Then a quantum probability measure over finite field (QPMFF) $\mu:\events_{p^{2}}\rightarrow\left[0,1\right]$
+assigns a probability to each event (projection operator~$P$) subject
 to $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$, and satisfying for
@@
 
-There are some correspondence qualified as “the discrete Born rule”
-when $p=D=3$. However, when $D=3$ and $p=7$, we have numerical
-verified that the unique QPMFF $\mu:\events_{7^{2}}\rightarrow\left[0,1\right]$
+After defining a QPMFF~$\mu$, we would like to follow the idea of
+Gleason's theorem to see whether we might trace back from $\mu$ to
+a pure or mixed state, and summarize this correspondence as a discrete
+Born rule. When $p=D=3$, there are indeed some correspondence between
+QPMFFs and states. However, when $D=3$ and $p=7$, we have numerical
+verified that the only QPMFF $\mu:\events_{7^{2}}\rightarrow\left[0,1\right]$
 is
@@
 \end{equation}
-Since we don't have enough QPMFF to correspond even pure states in
-the vector space~$\ff{7^{2}}^{3}$, there is no discrete Born rule
-in this case. In general, we conjecture that QPMFF is always unique
-for $D\ge3$ except $D=p=3$.
+As we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}), the
+number of unique irreducible pure states in $\ff{7^{2}}^{3}$ is 
+\begin{equation}
+\frac{7^{3-1}\left(7^{3}-\left(-1\right)^{3}\right)}{7+1}=2107\label{eq:numberOfIrreducibleStates-7-3}
+\end{equation}
+which is much more then one, the number of QPMFF. Since we don't have
+enough QPMFF to correspond even pure states, there is no discrete
+Born rule in this case. In general, we conjecture that QPMFF is always
+unique for $D\ge3$ except $D=p=3$.
 
 Although we couldn't prove there is no discrete Born rule by investigating
-QPMFF alone, we could prove there is no “sensible” Born rule
+QPMFFs alone, we could prove there is no “sensible” Born rule
 which also satisfies an analog of Proposition~\ref{prop:Born-probability-one}
-and \ref{prop:Born-unitary-invariant}.\todo{Notice that the notation
+and \ref{prop:Born-unitary-invariant}. \todo{Notice that the notation
 here and previous is a little bit different because we dealt with
@@
 Since $\ket{2}$ is invariant under $U'$, Eq.~(\ref{eq:basis-independent})
-implies $\muF_{\oplus}\left(P_{2}\right)=Hilbert\muF_{U'\ket{\oplus}}\left(U'P_{2}U'^{\dagger}\right)=\muF_{\Phi'}\left(P_{2}\right)$.
-Also, Eq.~(\ref{eq:zero}) implies $1=\muF_{\Phi'}\left(P_{0}+P_{2}\right)=\muF_{\Phi'}\left(P_{0}\right)+\muF_{\Phi'}\left(P_{2}\right)$.
-By moving $\muF_{\Phi'}\left(P_{0}\right)$ to the left-hand side
+implies $\muF_{\oplus}\left(P_{2}\right)=\muF_{U'\ket{\oplus}}\left(U'P_{2}U'^{\dagger}\right)=\muF_{\Phi'}\left(P_{2}\right)$.
+Also, Eq.~(\ref{eq:zero}) implies $\muF_{\Phi'}\left(P_{0}\right)+\muF_{\Phi'}\left(P_{2}\right)=\muF_{\Phi'}\left(P_{0}+P_{2}\right)=1$.
+By moving $\muF_{\Phi'}\left(P_{2}\right)$ to the right-hand side
 of the equation, we have 
@@
 
+\todo{Add some introductory text...}
+
 \section{Intervals of Uncertainty\label{sec:Interval-Uncertainty}}
 
-\subsection{Definitions of Classical and Quantum IVPMs}
+\subsection{Definitions of Classical and Quantum IVPMs\label{subsec:Definitions-of-IVPMs}}
 
@@
 Note that for any event $E$ with $\mu(E)=[\ell,r]$, we always have
-$\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E)\cup\mu\left(\overline{E}\right)$.
+\begin{equation}
+\mu(\Omega)=\necess\subseteq[\ell,r]+[1-r,1-\ell]=\mu(E)+\mu\left(\overline{E}\right)\,.\label{eq:necess-subset}
+\end{equation}
 %% Parallel arguments
@@
 
-\begin{definition}[QIVPM]\label{def:QIVPM}we take a QIVPM~$\bar{\mu}$
+\begin{definition}[QIVPM]\label{def:QIVPM}We take a QIVPM~$\bar{\mu}$
 to be an assignment of an interval to each event (projection operator~$P$)
 subject to the following constraints: 
-\begin{align}
-\bar{\mu}(\mathbb{0}) & =\imposs\,, & \bar{\mu}(\mathbb{1}) & =\necess\,, & \bar{\mu}\left(\mathbb{1}-P\right) & =\necess-\bar{\mu}\left(P\right)\,,\label{eq:QIVPM-constraints}
-\end{align}
+\begin{subequations}\label{eq:QIVPM-constraints}
+\begin{eqnarray}
+ &  & \bar{\mu}(\mathbb{0})=\imposs\,,\\
+ &  & \bar{\mu}(\mathbb{1})=\necess\,,\label{eq:QIVPM-necess}\\
+ &  & \bar{\mu}\left(\mathbb{1}-P\right)=\necess-\bar{\mu}\left(P\right)\,,\label{eq:QIVPM-complement}
+\end{eqnarray}
+\end{subequations}
 and satisfying for each pair of \emph{commuting} projectors~$P_{0}$
@@
 are the direct counterpart of the corresponding ones for classical
-IVPMs. With the understanding that the union of classical sets $E_{0}\cup E_{1}$
-is replaced by $P_{0}+P_{1}-P_{0}P_{1}$ in the case of quantum projection
-operators~\cite{Griffiths2003}, the last condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+IVPMs, Eqs.~(\ref{eq:CIVPM-constraints}). With the understanding
+that the union of classical sets $E_{0}\cup E_{1}$ is replaced by
+$P_{0}+P_{1}-P_{0}P_{1}$ in the case of quantum projection operators~\cite{Griffiths2003},
+the last condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
 is a direct counterpart of the convexity condition of Eq.~(\ref{eq:classicalconvex}).
@@
 
-\subsection{Relations between Classical and Quantum IVPMs}
+\subsection{States Consistent with Classical and Quantum IVPMs\label{subsec:States-Consistent-with-IVPMs}}
 
@@
 sense that a restriction of QIVPMs to mutually commuting events, $\eventsC$,
-recovers the definition of classical IVPMs.  Before we prove the
-correspondence between between classical and quantum IVPMs, we some
-necessary technical definitions and lemmas are required. First, we
-define $\events'$ as a \emph{subspace} of a set of events~$\events$
-if $\events'$ contains the projectors $\mathbb{0}$ and $\mathbb{1}$
-and is closed under complements, sums, and products. In particular,
-for any projector $P\in\events'$, we have $\mathbb{1}-P\in\events'$
-and for each pair of commuting projectors $P_{0}\in\events'$ and
-$P_{1}\in\events'$, we have $P_{0}P_{1}$ and $P_{0}+P_{1}-P_{0}P_{1}\in\events'$.
-
-\begin{thm}\label{thm:sub-event-space}Consider a Hilbert space~$\Hilb$
-and a mutually commuting sub-event space $\eventsC\subseteq\events$.
-Since $\events'$ is a set of mutually commuting projections, they
-can be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
-Let $\eventsC'$ be the set of all projectors generated by $\Omega$,
-i.e., $\eventsC'=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
-where $\sum_{P\in\emptyset}P=\mathbb{0}$. Then, 
-\begin{enumerate}
-\item $\eventsC'$ is commuting and satisfying $\eventsC\subseteq\eventsC'\subseteq\events$.
-\item The function $\upsilon:2^{\Omega}\rightarrow\eventsC'$ defined by
-$\upsilon\left(E\right)=\sum_{\ket{j}\in E}\proj{j}$ is a bijection
-and preserving the structure of between $2^{\Omega}$ and $\eventsC'$.
-More specifically, we have
+recovers the definition of classical IVPMs.  To see this, note that
+the commuting projectors in $\eventsC$ can be diagonalized by a common
+orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $.
+Since $\Omega$ is a finite set, it can be the sample space of a classical
+probability space with the classical event space $2^{\Omega}$. Because
+a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$ and a classical
+IVPM $\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ only differ on
+their domains, if we can find a function $\varphi:2^{\Omega}\rightarrow\events$
+preserving the structure, we can pullback~\cite{wiki:Pullback} any
+QIVPM~$\bar{\mu}$ to $\varphi^{*}\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+such that $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
+for any $E\subseteq\Omega$ and $\varphi^{*}\bar{\mu}$ should be
+a classical IVPM.
+
+We now explicitly define $\varphi$. First, $\events'$ is called
+a \emph{subspace} of the set of events~$\events$ if $\events'$
+contains the projectors $\mathbb{0}$ and $\mathbb{1}$ and is closed
+under complements, sums, and products. In particular, for any projector
+$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for each pair
+of commuting projectors $P_{0}\in\events'$ and $P_{1}\in\events'$,
+we have $P_{0}P_{1}$ and $P_{0}+P_{1}-P_{0}P_{1}\in\events'$. Given
+a mutually commuting subspace~$\eventsC$ whose elements are diagonalizable
+by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
+we define the function $\varphi:2^{\Omega}\rightarrow\events$ maps
+any set~$E$ to the sum of the projectors formed by elements in $E$,
+i.e., 
+\begin{equation}
+\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\,.\label{eq:pullback-function}
+\end{equation}
+If we follow the convention $\varphi\left(\emptyset\right)=\mathbb{0}$,
+this function $\varphi$ naturally sends the set operations to the
+corresponding projector operations: $\varphi\left(\Omega\right)=\mathbb{1}$,
+$\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$,
+and
 \begin{align}
-\upsilon\left(\emptyset\right) & =\mathbb{0}\,, & \upsilon\left(\Omega\right) & =\mathbb{1}\,, & \upsilon\left(\overline{E}\right) & =\mathbb{1}-\upsilon\left(E\right)\,,
+\varphi\left(E_{0}\cap E_{1}\right) & =\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,, & \varphi\left(E_{0}\cup E_{1}\right) & =\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\label{eq:pullback-properties}
 \end{align}
-and for each pair of set $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$,
+for each pair of set $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
+Therefore, given a QIVPM~$\bar{\mu}$, the function $\varphi^{*}\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+defined by precomposition $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
+is the pullback of $\bar{\mu}$ by $\varphi$, and is a classical
+IVPM naturally. Moreover, if $\mu:\events\rightarrow\left[0,1\right]$
+is a quantum probability measure satisfying Eqs.~(\ref{eq:QuantumProbability})
+and (\ref{eq:QuantumProbability-Addition}), the pullback of $\mu$,
+$\varphi^{*}\mu:2^{\Omega}\rightarrow\left[0,1\right]$, can also
+be defined by precomposition $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$,
+and is a classical probability measure as well.
+
+Since we can pullback a QIVPM to a classical one, known properties
+of classical IVPMs directly hold for QIVPMs when one restricts to
+mutually commuting events~$\eventsC$, and one of them is \emph{core}.
+Recall in Sec.~\ref{subsec:Definitions-of-IVPMs}, given a classical
+IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$ and an event $E\subseteq\Omega$
+such that $\bar{\mu}\left(E\right)=\left[0.2,0.3\right]$ and $\bar{\mu}\left(\overline{E}\right)=\left[0.7,0.8\right]$,
+we discussed the “true” probabilities, $\mu\left(E\right)$
+and $\mu\left(\overline{E}\right)$, can be anywhere in the range
+$\left[0.2,0.3\right]$ and $\left[0.7,0.8\right]$, respectively,
+as long as they satisfy $\mu\left(E\right)+\mu\left(\overline{E}\right)=1$.
+These “true” probabilities can actually be summarized as a probability
+measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$ satisfying 
+\begin{align}
+\mu\left(E\right) & \in\left[0.2,0.3\right]=\bar{\mu}\left(E\right)\,, & \mu\left(\overline{E}\right) & \in\left[0.7,0.8\right]=\bar{\mu}\left(\overline{E}\right)\,.
+\end{align}
+Together with the trivial fact
+\begin{align}
+\mu\left(\emptyset\right) & =0\in\imposs=\bar{\mu}\left(\emptyset\right)\,, & \mu\left(\Omega\right) & =1\in\necess=\bar{\mu}\left(\Omega\right)\,,
+\end{align}
+we conclude the “true” probability of each event belongs to
+the interval probability of the corresponding event. This conclusion
+gives the following definition of core.
+
+\begin{definition}[Classical Consistency and Core]\label{def:Consistency-classical}
+We say an IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$ is \emph{consistent}
+with a probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+on a event~$E\subseteq\Omega$ if the interval $\bar{\mu}(E)$ contains
+the precise probability calculated by $\mu$, i.e., $\mu\left(E\right)\in\bar{\mu}\left(E\right)$.
+The \emph{core} of a IVPM~$\bar{\mu}$, $\mathrm{core}\left(\bar{\mu}\right)$,
+is the collection of all probability measures~$\mu$ that are \emph{consistent}
+with $\bar{\mu}$ on every event, that is,
+\begin{equation}
+\mathrm{core}\left(\bar{\mu}\right)=\set{\mu:2^{\Omega}\rightarrow\left[0,1\right]}{\forall E\subseteq\Omega,~\mu\left(E\right)\in\bar{\mu}\left(E\right)}\,.\label{eq:hbar-classical}
+\end{equation}
+\end{definition}
+
+One fundamental question of these imprecise interval-valued probabilities
+is whether they \emph{always} have underlying precise probabilities.
+A positive answer is given by the following theorem.
+
+\begin{thm}[Shapley \cites{Shapley1971}{GilboaSchmeidler1994}{NgMoYeh1997Chinese}{Grabisch2016}]\label{thm:Shapley-classical}Every
+classical IVPM has a non-empty core.\end{thm}
+
+Although it is \emph{impossible} in the classical world to have an
+empty core, it is possible in the quantum world for the imprecise
+probabilities associated with some events to be inconsistent with
+\emph{any} quantum state, i.e., a QIVPM might have an empty core as
+we will show in Sec.~\ref{sec:Gleason}. In that case, one cannot
+guarantee non-empty cores for finite-precision attempts at proving
+Gleason's theorem by extending the Born measure $\muB_{\rho}\left(P\right)$
+to QIVPMs $\bar{\mu}\left(P\right)$. However, if we restrict ourselves
+to the set $\eventsC$ of mutually commuting events, the situation
+reverts to the classical case in which probabilities always determine
+at least one state.
+
+We now give the necessary technical definition and lemma to prove
+this non-empty core property.
+
+\begin{definition}[Quantum Consistency and Core]\label{def:Consistency}
+We say a QIVPM $\bar{\mu}$ is \emph{consistent} with a state $\rho$
+on a projector~$P$ if the interval $\bar{\mu}(P)$ contains the
+exact probability calculated by the Born rule \cites{Born1983}{Mermin2007}{Jaeger2007},
+i.e., 
+\begin{equation}
+\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)\in\bar{\mu}\left(P\right)\,.\label{eq:consistent}
+\end{equation}
+The \emph{core} $\coreBorn\left(\bar{\mu},\events'\right)$ of $\bar{\mu}$
+relative to a subspace of events $\events'$ is the collection of
+all states $\rho$ that are \emph{consistent} with $\bar{\mu}$ on
+every projector in $\events'$, that is, 
+\begin{equation}
+\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)}\,.\label{eq:hbar}
+\end{equation}
+\end{definition}
+
+In contrast with the classical Thm.~\ref{thm:Shapley-classical},
+there is \emph{no guarantee} that there exists a state $\rho$ that
+satisfies Eq.~(\ref{eq:hbar}) and therefore is in the core of a
+QIVPM. However, for the special case of commuting events, since the
+classical core corresponds to the quantum one by the following lemma,
+there will be a quantum theorem naturally corresponding to classical
+Thm.~\ref{thm:Shapley-classical}.
+
+\begin{lemma}\label{lemma:density-matrix-pullback}Consider a QIVPM
+$\bar{\mu}:\events\rightarrow\mathscr{I}$ and a commuting subspace
+of events $\eventsC$ diagonalizable by a common orthonormal basis
+$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with the
+function $\varphi:2^{\Omega}\rightarrow\events$ defined by Eq.~(\ref{eq:pullback-function}).
+For any classical probability measure~$\mu$ consistent with the
+pullback of $\bar{\mu}$, i.e., $\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)$,
+there is a density matrix~$\rho$ consistent with $\bar{\mu}$ relative
+to $\eventsC$, $\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)$,
+such that the pullback of $\muB_{\rho}$ is $\mu$ in the following
+sense:
+\begin{equation}
+\left(\varphi^{*}\muB_{\rho}\right)\left(E\right)=\muB_{\rho}\left(\varphi\left(E\right)\right)=\mu\left(E\right)\label{eq:density-matrix-pullback}
+\end{equation}
+for all $E\subseteq\Omega$.\end{lemma}
+
+\begin{proof}Consider $\rho=\sum_{j=0}^{D-1}\mu\left(\left\{ \ket{j}\right\} \right)\proj{j}$
+which is a density matrix because $\rho$ is a positive operator and
+has trace equal to one~\cite{544199}:
+\begin{equation}
+\Tr\left(\rho\right)=\sum_{j=0}^{D-1}\mu\left(\left\{ \ket{j}\right\} \right)\Tr\left(\proj{j}\right)=\sum_{j=0}^{D-1}\mu\left(\left\{ \ket{j}\right\} \right)=1\,.
+\end{equation}
+Then, Eq.~(\ref{eq:density-matrix-pullback}) can be inductive proved
+on $E$. By Eq.~(\ref{eq:pullback-function}) and the generalized
+Born rule, Eq.~(\ref{eq:mixed-Born}), we have the base case
+\begin{equation}
+\muB_{\rho}\left(\varphi\left(\left\{ \ket{i}\right\} \right)\right)=\muB_{\rho}\left(\proj{i}\right)=\sum_{j=0}^{D-1}\mu\left(\left\{ \ket{j}\right\} \right)\muB_{\ket{j}}\left(\proj{i}\right)=\mu\left(\left\{ \ket{i}\right\} \right)
+\end{equation}
+for all $i$. By Eq.~(\ref{eq:pullback-properties}) and the induction
+hypothesis $\muB_{\rho}\left(\varphi\left(E\right)\right)=\mu\left(E\right)$,
+the inductive case is also valid:
+\begin{equation}
+\muB_{\rho}\left(\varphi\left(E\cup\left\{ \ket{i}\right\} \right)\right)=\muB_{\rho}\left(\varphi\left(E\right)\right)+\muB_{\rho}\left(\varphi\left(\left\{ \ket{i}\right\} \right)\right)=\mu\left(E\right)+\mu\left(\left\{ \ket{i}\right\} \right)=\mu\left(E\cup\left\{ \ket{i}\right\} \right)
+\end{equation}
+for all $i\notin E$. After we inductively proved $\varphi^{*}\muB_{\rho}=\mu$,
+we can finally prove $\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)$.
+Since $\mu$ is consistent with the pullback of $\bar{\mu}$, $\varphi^{*}\bar{\mu}$,
 we have 
-\begin{align}
-\upsilon\left(E_{0}\cap E_{1}\right) & =\upsilon\left(E_{0}\right)\upsilon\left(E_{1}\right)\,, & \upsilon\left(E_{0}\cup E_{1}\right) & =\upsilon\left(E_{0}\right)+\upsilon\left(E_{1}\right)-\upsilon\left(E_{0}\right)\upsilon\left(E_{1}\right)\,.
-\end{align}
-\item Since $\upsilon$ is a bijection, its inverse function $\tau=\upsilon^{-1}:\eventsC'\rightarrow2^{\Omega}$
-is also a bijection and preserving the structure of between $\eventsC'$
-and $2^{\Omega}$.
-\item Given any QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, we can
-define the classical IVPM $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
-by $\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(\upsilon\left(E\right)\right)=\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)$
-such that the restriction of $\bar{\mu}$ on $\eventsC'$ is just
-$\bar{\mu}^{\Omega}$ concatenating with $\tau$, i.e., $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$
-for any $P\in\eventsC'$.
-\end{enumerate}
-\end{thm}
-
-\todo{Actually, $\bar{\mu}^{\Omega}$ looks like the pullback of
-$\bar{\mu}$ by $\upsilon$~\cite{wiki:Pullback}. However, $\eventsC$
-and $2^{\Omega}$ are not categories, and $\upsilon$ is not preserving
-algebraic or analytical properties... So I don't know whether people
-call this “pullback” or not.}
-
-\subsection{States Consistent with Quantum IVPMs}
-
-A consequence is that known properties of classical IVPMs directly
-hold for QIVPMs when one restricts to mutually commuting events, $\eventsC$.
-In particular, in the classical world, it is \emph{impossible} for
-experiments to result in probabilities that are inconsistent with
-\emph{every} state of the system under consideration, i.e., all IVPMs
-must have a non-empty “core”\footnote{\label{fn:A-result-by-Shapley}A result by Shapley~\cites{Shapley1971}{GilboaSchmeidler1994}{NgMoYeh1997Chinese}{Grabisch2016}
-proves that a classical IVPM always contains at least one state that
-is consistent with every event.}. Interestingly, as we show in Sec.~\ref{sec:Gleason}, it is possible
-in the quantum world for the probabilities associated with some events
-to be inconsistent with \emph{any} quantum state, i.e., for the QIVPM
-to have an empty core; in that case, one cannot guarantee non-empty
-cores for finite-precision attempts at proving Gleason's theorem by
-extending the Born measure $\muB_{\rho}\left(P\right)$ to QIVPMs
-$\bar{\mu}\left(P\right)$. However, if we restrict ourselves to the
-set $\eventsC$ of mutually commuting events, the situation reverts
-to the classical case in which probabilities always determine at least
-one state.
-
-We now give the necessary technical definitions to prove this non-empty
-core property.
-
-\begin{definition}[Consistency]\label{def:Consistency} We say
-a QIVPM $\bar{\mu}$ is \emph{consistent} with a state $\rho$ and
-a projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
-probability calculated by the Born rule \cites{Born1983}{Mermin2007}{Jaeger2007},
-i.e., 
-\begin{equation}
-\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)\in\bar{\mu}\left(P\right)\,.\label{eq:consistent}
-\end{equation}
-In contrast with classical probability spaces\footnotemark[\getrefnumber{fn:A-result-by-Shapley}],
-there is \emph{no guarantee} that there exists a state $\rho$ that
-satisfies Eq.~(\ref{eq:consistent}) and therefore is consistent
-with a QIVPM. \end{definition}
-
-We next refine the concept of consistency by introducing the idea
-of a “core” set of states relative to subspaces.
-
-\begin{definition}[The core of a probability measure]\label{def:core}
-The \emph{core} $\coreBorn\left(\bar{\mu},\events'\right)$ of a probability
-measure $\bar{\mu}$ relative to a subspace of events $\events'$
-is the collection of all states $\rho$ that are \emph{consistent}
-with $\bar{\mu}$ on every projector in $\events'$, that is 
-\begin{equation}
-\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)}\,.\label{eq:hbar}
-\end{equation}
-\end{definition}
-
-We are now in position to state and prove that, for the special case
-of commuting events, a QIVPM will always have a non-empty core.
-
-\begin{thm}[Non-empty Core for Compatible Measurements] \label{thm:Shapley}
-For every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
-subspace of events~$\eventsC\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\eventsC\right)\ne\emptyset$.
-\end{thm}
-
-An outline of the proof, detailed in the forthcoming thesis~\cite{TaiThesis2018},
-proceeds as follows. From a subspace $\eventsC$ of mutually commuting
-events, one can construct a partial orthonormal basis by diagonalization,
-and complete this to a full orthonormal basis $\overline{\eventsC}$.
-We can then build a bijection between the QIVPM on the set of projectors
-associated with this basis and the set of classical events corresponding
-to this basis. Using this correspondence together with the classical
-result by Shapley~\cites{Shapley1971}{GilboaSchmeidler1994}{NgMoYeh1997Chinese}{Grabisch2016},
-we can establish that for the special case of commuting events, a
-QIVPM will always have a non-empty core.
+\begin{equation}
+\muB_{\rho}\left(\varphi\left(E\right)\right)=\mu\left(E\right)\in\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)\,.
+\end{equation}
+Together with the fact that the image of $\varphi$ contains $\eventsC$,
+we have $\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)$ for
+all $P\in\eventsC$, i.e., $\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)$.\end{proof}
+
+Then, the quantum version of Thm.~\ref{thm:Shapley-classical} is
+a natural consequence of the previous lemma.
+
+\begin{thm}[Non-empty Core for Compatible Measurements]\label{thm:Shapley}For
+every QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
+of events $\eventsC\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\eventsC\right)\ne\emptyset$.\end{thm}
+
+\begin{proof}Since $\eventsC$ is a set of mutually commuting projections,
+they can be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $.
+We can then follow Eq.~(\ref{eq:pullback-function}) to define $\varphi:2^{\Omega}\rightarrow\events$
+such that the pullback of $\bar{\mu}$ by $\varphi$, $\varphi^{*}\bar{\mu}$,
+is a classical IVPM. By Thm.~\ref{thm:Shapley-classical}, there
+is a classical probability measure $\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$
+consistent with $\varphi^{*}\bar{\mu}$, and thus there must be a
+density matrix $\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)$
+satisfying $\varphi^{*}\muB_{\rho}=\pmeas$ according to Lemma~\ref{lemma:density-matrix-pullback}.\end{proof}
 
@@
 We conclude this section with a generalization of expectation values
-of observables in the context of QIVPMs. In conventional quantum mechanics
+of observables in the context of QIVPMs. In conventional quantum mechanics,
 the expectation value of an observable as defined in Eq.~\eqref{eq:quantum-expectation}
 is a unique real number. The generalization to QIVPMs implies that
-this expectation value will itself become bounded by an interval.
-
-\begin{definition}[Expectation Value of Observables over QIVPMs]
-Let $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space
-of dimension $D$ with event space~$\events$; and $\mathbf{O}$
-an observable with spectral decomposition $\sum_{i=1}^{D}\lambda_{i}P_{i}$.
-Let $\events'$ be the minimal subspace of events containing all the
-projectors $P_{i}$ in the spectral decomposition of $\mathbf{O}$
-and define: 
-\begin{equation}
-\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,.\label{eq:quantum-interval-expectation-core}
-\end{equation}
+this expectation value should be bounded by an interval. We will start
+from the classical notion of the \emph{Choquet integral} which is
+used to calculate the expectation value of random variables as a weighted
+average \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}. Then,
+we will generalize this notation from classical IVPMs to QIVPMs, and
+prove this generalization consistent with our intuition. For example,
+if $\bar{\mu}$ is a conventional (Born) probability measure induced
+by a state $\rho$, then the interval expectation value collapses
+to a point, thus reducing the interval expectation value to the conventional
+definition of Eq.~(\ref{eq:quantum-expectation}). We will also show
+the expectation value of an observable relative to a QIVPM $\bar{\mu}$
+lies between two possible outcomes, which themselves lie between the
+minimum and maximum bounds of the probability intervals associated
+with each state~$\rho$ that is consistent with~$\bar{\mu}$ on
+every projector in the spectral decomposition of the observable.
+
+Similar to how we pull back classical ideas to the quantum world in
+Secs.~\ref{subsec:Definitions-of-IVPMs} and \ref{subsec:States-Consistent-with-IVPMs},
+we start from defining the classical expectation value relative to
+IVPMs. Consider a classical IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+and an event $E\subseteq\Omega$ such that 
+\begin{align}
+\bar{\mu}\left(E\right) & =\left[0.2,0.3\right]\,, & \bar{\mu}\left(\overline{E}\right) & =\left[0.7,0.8\right]\,,\label{eq:IVPM_example}
+\end{align}
+and a random variable $X:\Omega\rightarrow\mathbb{R}$ defined by
+\begin{equation}
+X\left(\omega\right)=\begin{cases}
+1 & \textrm{if }\omega\in E\,;\\
+2 & \textrm{if }\omega\notin E\,.
+\end{cases}\label{eq:random_variable_example}
+\end{equation}
+As we have discussed, the “true” probability is a probability
+measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$ consistent with
+$\bar{\mu}$ on every event. On one extreme case, $\mu\left(E\right)=0.2$,
+the expectation value of $X$ relative to $\mu$ is 
+\begin{equation}
+1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.2+2\cdot0.8=1.8\,.
+\end{equation}
+On the other extreme case, $\mu\left(E\right)=0.3$, the expectation
+value of $X$ relative to $\mu$ is
+\begin{equation}
+1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.3+2\cdot0.7=1.7\,.
+\end{equation}
+In another word, as long as $\mu$ is in the core of $\bar{\mu}$,
+the expectation value of $X$ belongs to $\left[1.7,1.8\right]$ which
+should be the expectation value of $X$ with respect to $\bar{\mu}$.
+
+\todo{See if we could delete from here to Thm.~\ref{thm:Rosenmuller},
+and make Thm.~\ref{thm:Rosenmuller} the definition of classical
+expectation value. Then, delete Def.~\ref{def:expectation-values-QIVPM}
+and make Eq.~(\ref{eq:interval-expectation-value-between-classical-quantum})
+the definition of quantum expectation value. After that, see if everything
+can be preceded smoothly in this way...}
+
+Although it is intuitive to define the expectation value as the minimum
+and maximum bounds of the probability intervals associated with each
+probability measure in the core of~$\bar{\mu}$, the core of a general
+IVPM is hard to be described and computed. Fortunately, the above
+description is equivalent to the well-known Choquet integral \cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016},
+which can be computed step-by-step like a weighted average.
+
+\begin{definition}[Classical Expectation Values]\label{def:Choquet}Consider
+a classical sample space~$\Omega$ with a random variable $X:\Omega\rightarrow\mathbb{R}$.
+Since we only consider finite sample space, $X$ can always be decomposed
+into the sum of step functions~$\mathbf{1}_{E}$ defined by
+\begin{equation}
+\mathbf{1}_{E}\left(\omega\right)=\begin{cases}
+1 & \textrm{if }\omega\in E\,;\\
+0 & \textrm{if }\omega\notin E\,.
+\end{cases}
+\end{equation}
+For our convenience to define the Choquet integral later, we order
+these step functions by their coefficients from the smallest to the
+largest, and express $X$ as follow: 
+\begin{equation}
+X=x_{N^{-}}^{-}\mathbf{1}_{E_{N^{-}}^{-}}+\cdots+x_{1}^{-}\mathbf{1}_{E_{1}^{-}}+x_{1}^{+}\mathbf{1}_{E_{1}^{+}}+\cdots+x_{N^{+}}^{+}\mathbf{1}_{E_{N^{+}}^{+}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\mathbf{1}_{E_{i}^{s}}\,,\label{eq:classical-decomposition}
+\end{equation}
+where $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
+are all disjoint and $x_{N^{-}}^{-}<\cdots<x_{1}^{-}<0\le x_{1}^{+}<\cdots<x_{N^{+}}^{+}$.
+Then, the expectation values of $X$ relative to real-valued and interval-valued
+probability measures can be defined like weighted averages as follow.
+\begin{itemize}
+\item Given a classical probability measure $\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$,
+the expectation value of $X$ relative to $\mu$ is an average of~$x_{i}^{s}$
+with the weight being the measure of their step functions $\pmeas\left(E_{i}^{s}\right)$,
+i.e., 
+\begin{equation}
+\int X\rmd\pmeas=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\pmeas\left(E_{i}^{s}\right)\,.\label{eq:expectation}
+\end{equation}
+\item Consider a classical IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$.
+The expectation value of $X$ relative to $\bar{\mu}$ still looks
+like a weighted average of~$x_{i}^{s}$, where $s$ is either $+$
+or $-$, but this time the “weights” are not just the measure
+of their step functions $\pmeas\left(E_{i}^{s}\right)$. Instead,
+by computing the accumulative sets $E_{i\uparrow}^{s}=\bigcup_{j\ge i}E_{j}^{s}$
+and their interval-valued probabilities $\bar{\mu}\left(E_{i\uparrow}^{s}\right)$,
+the “weights” are the differences of the both-end of the interval
+probabilities, $\Delta\mu^{t}\left(E_{i\uparrow}^{s}\right)=\mu^{t}\left(E_{i\uparrow}^{s}\right)-\mu^{t}\left(E_{\left(i+1\right)\uparrow}^{s}\right)$,
+where $\mu^{t}\left(E_{i\uparrow}^{s}\right)$ is either the left-end
+$\mul\left(E_{i\uparrow}^{s}\right)$ or right-end $\mur\left(E_{i\uparrow}^{s}\right)$
+of $\bar{\mu}\left(E_{i\uparrow}^{s}\right)$, that is, $\bar{\mu}\left(E_{i\uparrow}^{s}\right)=\left[\mul\left(E_{i\uparrow}^{s}\right),\mur\left(E_{i\uparrow}^{s}\right)\right]$.
+Then, the Choquet integral of $X$ relative to $\bar{\mu}$ is averaging
+$x_{i}^{s}$ with the given “weights,”
+\begin{equation}
+\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i\uparrow}^{s}\right),\Delta\mur\left(E_{i\uparrow}^{s}\right)\right]\,.\label{eq:interval-expectation}
+\end{equation}
+\end{itemize}
 \end{definition}
 
-\noindent Intuitively the expectation value of an observable relative
-to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
-themselves lie between the minimum and maximum bounds of the probability
-intervals associated with each state~$\rho$ that is consistent with~$\bar{\mu}$
-on every projector in the spectral decomposition of the observable.
-If $\bar{\mu}$ is a conventional (Born) probability measure induced
-by a state $\rho$, then the Born rule probability induced by every
-state in $\coreBorn\left(\bar{\mu},\events'\right)$ will be $\muB_{\rho}$
-and the interval collapses to a point, thus reducing the definition
-to that of Eq.~(\ref{eq:quantum-expectation})~\cite{TaiThesis2018}.
-% For example, we can extend one of the fragments of valid probability
-% measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
-% to a QIVPM~$\bar{\mu}_{3}$:
-% \begin{equation}
-% \begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
-% \bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
-% \end{aligned}
-% \label{eq:Born-QIVPM}
-% \end{equation}
-% For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
-% the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
-% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\muB_{\proj{\ps}}$.
-% Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
-% which is an interval, but not between $0$ and $1$ because it is
-% not a probability of an event. 
-We also note that, when restricted to commuting projectors, Eq.~(\ref{eq:quantum-interval-expectation-core})
-is consistent with the classical notion of the \emph{Choquet integral}~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-which is used to calculate the expectation value of random variables
-as a weighted average~\cite{TaiThesis2018}.
+Suppose $\bar{\mu}$ is just a real-valued probability measure~$\pmeas$,
+i.e., $\bar{\mu}\left(E\right)=\left[\pmeas\left(E\right),\pmeas\left(E\right)\right]$
+for all $E$. Since the “weights” in Eq.~(\ref{eq:interval-expectation})
+are the difference on the probability of the accumulative sets, they
+have the same magnitude as ones in Eq.~(\ref{eq:expectation}), and
+the right-hand side of Eq.~(\ref{eq:interval-expectation}) can be
+easily simplified to the right-hand side of Eq.~(\ref{eq:expectation})
+as follow.
+\begin{eqnarray*}
+\int X\rmd\bar{\mu} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\pmeas\left(E_{i\uparrow}^{s}\right),\Delta\pmeas\left(E_{i\uparrow}^{s}\right)\right]\\
+ & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right),\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right)\right]\\
+ & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right),\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right)\right]\\
+ & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right),\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right)\right]\\
+ & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i}^{s}\right),\mu\left(E_{i}^{s}\right)\right]=\left[\int X\rmd\mu,\int X\rmd\mu\right]
+\end{eqnarray*}
+
+The Choquet integral defined in Eq.~(\ref{eq:interval-expectation})
+is consistent with not only Eq.~(\ref{eq:expectation}) but also
+our previous intuition. For example, if $\bar{\mu}$ and $X$ defined
+in Eqs.~(\ref{eq:IVPM_example}) and (\ref{eq:random_variable_example})
+have an intuitive expectation interval $\left[1.7,1.8\right]$, their
+Choquet integral $\int X\rmd\bar{\mu}$ should give the same interval
+$\left[1.7,1.8\right]$. To verify our idea, we first represent $X$
+as the sum $1\cdot\mathbf{1}_{E}+2\cdot\mathbf{1}_{\overline{E}}$.
+Since the coefficients are all positive, we have $N^{-}=0$, $N^{+}=2$,
+$x_{1}^{+}=1$, $E_{1}^{+}=E$, $x_{2}^{+}=2$, and $E_{2}^{+}=\overline{E}$
+as listed in Table~\ref{table:Choquet}. 
+\begin{table}
+\noindent \centering{}\caption{\label{table:Choquet}This table lists the immediate values to compute
+the Choquet integral $\int X\rmd\bar{\mu}$ according to Def.~\ref{def:Choquet}.}
+\begin{tabular}{cccccccc}
+\toprule 
+\addlinespace
+$i$ & $x_{i}^{+}$ & $E_{i}^{+}$ & $E_{i\uparrow}^{+}$ & $\mul\left(E_{i\uparrow}^{+}\right)$ & $\Delta\mul\left(E_{i\uparrow}^{+}\right)$ & $\mur\left(E_{i\uparrow}^{+}\right)$ & $\Delta\mur\left(E_{i\uparrow}^{+}\right)$\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+$1$ & $1$ & $E$ & $\Omega$ & $1$ & $0.3$ & $1$ & $0.2$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$2$ & $2$ & $\overline{E}$ & $\overline{E}$ & $0.7$ & $0.7$ & $0.8$ & $0.8$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$3$ &  &  & $\emptyset$ & $0$ &  & $0$ & \tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}
+\end{table}
+Step-by-step we compute the accumulative sets~$E_{i\uparrow}^{+}$,
+their measures $\mu^{t}\left(E_{i\uparrow}^{+}\right)$, and their
+differences $\Delta\mu^{t}\left(E_{i\uparrow}^{s}\right)$. These
+values can then be plugged into Eq.~(\ref{eq:interval-expectation})
+giving the Choquet integral 
+\begin{equation}
+\begin{aligned}\int X\rmd\bar{\mu} & =x_{1}^{+}\left[\Delta\mul\left(E_{1\uparrow}^{+}\right),\Delta\mur\left(E_{1\uparrow}^{+}\right)\right]+x_{2}^{+}\left[\Delta\mul\left(E_{2\uparrow}^{+}\right),\Delta\mur\left(E_{2\uparrow}^{+}\right)\right]\\
+ & =1\cdot\left[0.3,0.2\right]+2\cdot\left[0.7,0.8\right]=\left[1.7,1.8\right]\,.
+\end{aligned}
+\end{equation}
+In general, the Choquet integral is always equal to the minimum and
+maximum of expectation values relative to probability measures in
+the core according to the following theorem \cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
+
+\begin{thm}\label{thm:Rosenmuller}For every classical IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+and any random variable $X:\Omega\rightarrow\mathbb{R}$, we have
+\begin{equation}
+\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.\label{eq:Rosenmuller}
+\end{equation}
+\end{thm}
+
+After we defined the expectation values of random variables relative
+to classical IVPMs, we can parallelly define the expectation values
+of observables relative to QIVPMs as follow.
+
+\begin{definition}[Expectation Values relative to QIVPMs]\label{def:expectation-values-QIVPM}Since
+we want to define the expectation value of observables relative to
+QIVPMs parallel to classical definition~\ref{def:Choquet}, we order
+the eigenvalues of an observable~$\mathbf{O}$ in the spectral decomposition
+from the smallest to the largest as well
+\begin{equation}
+\mathbf{O}=\lambda_{N^{-}}^{-}P_{N^{-}}^{-}+\cdots+\lambda_{1}^{-}P_{1}^{-}+\lambda_{1}^{+}P_{1}^{+}+\cdots+\lambda_{N^{+}}^{+}P_{N^{+}}^{+}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition-distinct}
+\end{equation}
+where $\lambda_{N^{-}}^{-}<\cdots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\cdots<\lambda_{N^{+}}^{+}$
+and each $P_{i}^{s}$ is the projector onto the eigenspace of distinct
+eigenvalue~$\lambda_{i}^{s}$. Consider a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
+with its left-end and right-end denoted by $\mul:\events\rightarrow\left[0,1\right]$
+and $\mur:\events\rightarrow\left[0,1\right]$, respectively, i.e.,
+$\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$.
+Let $s$ be either $+$ or $-$ in the superscript in the following
+discussion. We denote $P_{i\uparrow}^{s}$ as the accumulative projectors
+on the sub-index $i$, i.e., $P_{i\uparrow}^{s}=\sum_{j\ge i}P_{j}^{s}$,
+and $\Delta\mu^{t}\left(P_{i\uparrow}^{s}\right)$ as the difference
+of the measure of these accumulative projectors, i.e., $\Delta\mu^{t}\left(P_{i\uparrow}^{s}\right)=\mu^{t}\left(P_{i\uparrow}^{s}\right)-\mu^{t}\left(P_{\left(i+1\right)\uparrow}^{s}\right)$,
+where $t\in\left\{ \symrmL,\symrmR\right\} $. Then, the expectation
+values of $\mathbf{O}$ relative to $\bar{\mu}$ is
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i\uparrow}^{s}\right),\Delta\mur\left(P_{i\uparrow}^{s}\right)\right]\,,\label{eq:interval-expectation-quantum}
+\end{equation}
+which looks like a weighted average of the difference of the measure
+of these accumulative projectors.\end{definition}
+
+Parallel to the similarity between Eqs.~(\ref{eq:expectation}) and
+(\ref{eq:interval-expectation}), Eq.~(\ref{eq:interval-expectation-quantum})
+can be simplified to Eq.~(\ref{eq:quantum-expectation}) if $\bar{\mu}$
+is essentially real-valued.
+
+\begin{thm}\label{lemma:expectation-singleton}Given a quantum probability
+measure $\mu:\events\rightarrow\left[0,1\right]$ satisfying Eqs.~(\ref{eq:QuantumProbability})
+and (\ref{eq:QuantumProbability-Addition}), if we define a QIVPM
+$\bar{\mu}:\events\rightarrow\mathscr{I}$ by $\bar{\mu}\left(P\right)=\left[\mu\left(P\right),\mu\left(P\right)\right]$
+for all projectors~$P$, then the expectation value of any observable~$\mathbf{O}$
+relative to $\bar{\mu}$, $\expval{\mathbf{O}}_{\bar{\mu}}$, is just
+$\left[\expval{\mathbf{O}}_{\mu},\expval{\mathbf{O}}_{\mu}\right]$.\end{thm}
+
+We then want to show the expectation value relative to a QIVPM generalizes
+the one relative to a classical IVPM by proving a quantum version
+of Thm.~\ref{thm:Rosenmuller}. Although we previously only pull
+back probability measures, this time we also need to pull back observables.
+
+\begin{definition}[Pullback of Observables]\label{def:observable2random-variable}Consider
+an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
+$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ so that
+$\mathbf{O}$ has spectral decomposition $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\proj{i}$.
+If we follow Eq.~(\ref{eq:pullback-function}) to define $\varphi:2^{\Omega}\rightarrow\events$,
+then the pullback of $\mathbf{O}$ by $\varphi$ is a random variable
+$\varphi^{*}\mathbf{O}:\Omega\rightarrow\mathbb{R}$ defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$.\end{definition}
+
+While both observables and probability measures can be pulled back
+from quantum to classical, these pullbacks keep the expectation value
+invariant.
+
+\begin{lemma}\label{lemma:expectation-value-between-classical-quantum}Consider
+an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
+$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with $\varphi:2^{\Omega}\rightarrow\events$
+defined by Eq.~(\ref{eq:pullback-function}).
+\begin{itemize}
+\item Given a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$,
+the expectation value of $\mathbf{O}$ relative to $\mu$ is exactly
+the expectation value of the pullback of $\mathbf{O}$ relative to
+the pullback of $\mu$, i.e., 
+\begin{equation}
+\expval{\mathbf{O}}_{\mu}=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)\,.\label{eq:real-expectation-value-between-classical-quantum}
+\end{equation}
+\item Given a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, the expectation
+value of $\mathbf{O}$ relative to $\bar{\mu}$ is exactly the expectation
+value of the pullback of $\mathbf{O}$ relative to the pullback of
+$\bar{\mu}$, i.e., 
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\bar{\mu}\right)\,.\label{eq:interval-expectation-value-between-classical-quantum}
+\end{equation}
+\end{itemize}
+\end{lemma}
+
+\begin{proof}[Proof of Eq.~(\ref{eq:real-expectation-value-between-classical-quantum})]By
+Eq.~(\ref{eq:quantum-expectation}), we have
+\[
+\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\proj{i}\right)=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\varphi\left(\left\{ \ket{i}\right\} \right)\right)=\sum_{i=0}^{D-1}\lambda_{i}\left(\varphi^{*}\mu\right)\left(\left\{ \ket{i}\right\} \right)=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)\,.
+\]
+\end{proof}
+
+\begin{proof}[Proof of Eq.~(\ref{eq:interval-expectation-value-between-classical-quantum})]Consider
+to express the observable~$\mathbf{O}$ in the spectral decomposition
+specialized to compute the expectation value relative to a QIVPM,
+$\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}$,
+where $\lambda_{N^{-}}^{-}<\cdots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\cdots<\lambda_{N^{+}}^{+}$
+and each $P_{i}^{s}$ is the projector onto the eigenspace of distinct
+eigenvalue~$\lambda_{i}^{s}$. Since $\mathbf{O}$ can be diagonalized
+by an orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
+each $P_{i}^{s}$ can be expressed as the sum of some projectors formed
+by the elements in $\Omega$, i.e., there is a subset $E_{i}^{s}\subseteq\Omega$
+such that $P_{i}^{s}=\sum_{\ket{j}\in E_{i}^{s}}\proj{j}=\varphi\left(E_{i}^{s}\right)$.
+To compute the expectation values, we want to not only map $E_{i}^{s}$
+to $P_{i}^{s}$ but also map the other ingredients of the expectation
+values, including the accumulative sets or projectors, their measures,
+and their differences:
+\begin{subequations}
+\begin{eqnarray}
+ &  & P_{i\uparrow}^{s}=\sum_{j\ge i}P_{j}^{s}=\sum_{j\ge i}\sum_{\ket{k}\in E_{j}^{s}}\proj{k}=\sum_{\ket{k}\in\bigcup_{j\ge i}E_{j}^{s}}\proj{k}=\varphi\left(\bigcup_{j\ge i}E_{j}^{s}\right)=\varphi\left(E_{i\uparrow}^{s}\right)\,,\nonumber \\
+ &  & \mu^{t}\left(P_{i\uparrow}^{s}\right)=\mu^{t}\left(\varphi\left(E_{i\uparrow}^{s}\right)\right)=\left(\varphi^{*}\mu^{t}\right)\left(E_{i\uparrow}^{s}\right)\,,\label{eq:pullback-real-measures}\\
+ &  & \begin{aligned}\Delta\mu^{t}\left(P_{i\uparrow}^{s}\right) & =\mu^{t}\left(P_{i\uparrow}^{s}\right)-\mu^{t}\left(P_{\left(i+1\right)\uparrow}^{s}\right)=\left(\varphi^{*}\mu^{t}\right)\left(E_{i\uparrow}^{s}\right)-\left(\varphi^{*}\mu^{t}\right)\left(E_{\left(i+1\right)\uparrow}^{s}\right)\\
+ & =\Delta\left(\varphi^{*}\mu^{t}\right)\left(E_{i\uparrow}^{s}\right)\,,
+\end{aligned}
+\label{eq:pullback-differences}
+\end{eqnarray}
+\end{subequations}
+where $t\in\left\{ \symrmL,\symrmR\right\} $ and $\left[\mul\left(P\right),\mur\left(P\right)\right]=\bar{\mu}\left(P\right)$
+as in Defs.~\ref{def:Choquet} and \ref{def:expectation-values-QIVPM}.
+Notice that Eq.~(\ref{eq:pullback-real-measures}) and (\ref{eq:pullback-differences})
+were simplified to the pullback of $\mul$ and $\mur$ which can be
+combined into the pullback of $\bar{\mu}$ as follows: 
+\begin{equation}
+\begin{aligned}\left[\left(\varphi^{*}\mul\right)\left(E\right),\left(\varphi^{*}\mur\right)\left(E\right)\right] & =\left[\mul\left(\varphi\left(E\right)\right),\mur\left(\varphi\left(E\right)\right)\right]=\bar{\mu}\left(\varphi\left(E\right)\right)\\
+ & =\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\left[\left(\varphi^{*}\bar{\mu}\right)^{\symrmL}\left(E\right),\left(\varphi^{*}\bar{\mu}\right)^{\symrmR}\left(E\right)\right]
+\end{aligned}
+\label{eq:pullback-interval-measures}
+\end{equation}
+for all $E\subseteq\Omega$.
+
+To compute the expectation value, we also need to know the the pullback
+of $\mathbf{O}$. Since $\mathbf{O}$ can be expressed as the sum
+of one-dimensional projectors 
+\begin{equation}
+\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\sum_{\ket{j}\in E_{i}^{s}}\proj{j}\,,
+\end{equation}
+the pullback of $\mathbf{O}$ should be
+\begin{equation}
+\varphi^{*}\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\sum_{\ket{j}\in E_{i}^{s}}\mathbf{1}_{\left\{ \ket{j}\right\} }=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{E_{i}^{s}}\label{eq:pullback-observables}
+\end{equation}
+according to Def.~\ref{def:observable2random-variable}. Then, the
+expectation value can be computed by spelling the definitions and
+applying Eqs.~(\ref{eq:pullback-differences}), (\ref{eq:pullback-interval-measures}),
+and (\ref{eq:pullback-observables})
+\begin{equation}
+\begin{aligned}\expval{\mathbf{O}}_{\bar{\mu}} & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i\uparrow}^{s}\right),\Delta\mur\left(P_{i\uparrow}^{s}\right)\right]\\
+ & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\left(\varphi^{*}\mul\right)\left(E_{i\uparrow}^{s}\right),\Delta\left(\varphi^{*}\mur\right)\left(E_{i\uparrow}^{s}\right)\right]\\
+ & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\left(\varphi^{*}\bar{\mu}\right)^{\symrmL}\left(E_{i\uparrow}^{s}\right),\Delta\left(\varphi^{*}\bar{\mu}\right)^{\symrmR}\left(E_{i\uparrow}^{s}\right)\right]\\
+ & =\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\bar{\mu}\right)\,.
+\end{aligned}
+\end{equation}
+\end{proof}
+
+After we have required lemmas, we are in a good position to prove
+a quantum analog of Thm.~\ref{thm:Rosenmuller}. However, since Lemma~\ref{lemma:density-matrix-pullback}
+hasn't established enough correspondence between classical and quantum
+cores, this theorem is weaker than its classical counterpart.
+
+\begin{thm}\label{thm:quantum-Rosenmuller}Consider an observable~$\mathbf{O}$
+diagonalizable by an orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $
+and a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$.
+\begin{itemize}
+\item Express $\mathbf{O}$ in the spectral decomposition specialized to
+compute the expectation value relative to a QIVPM, $\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}$,
+where $\lambda_{N^{-}}^{-}<\cdots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\cdots<\lambda_{N^{+}}^{+}$
+and each $P_{i}^{s}$ is the projector onto the eigenspace of distinct
+eigenvalue~$\lambda_{i}^{s}$. Given any commuting subspace of events
+$\eventsC$ containing all projectors $P_{i}^{s}$, we have
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}\subseteq\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,.\label{eq:quantum-interval-expectation-core}
+\end{equation}
+\item Let $\events_{\Omega}$ be the set of projectors generated from $\Omega$,
+$\set{\varphi\left(E\right)}{E\subseteq\Omega}$, we have
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,.\label{eq:quantum-interval-expectation-core-equal}
+\end{equation}
+\end{itemize}
+\todo{Can we find a example where Eq.~(\ref{eq:quantum-interval-expectation-core})
+is a proper inclusion? Or prove the two sides in Eq.~(\ref{eq:quantum-interval-expectation-core})
+are always equal? Also, see if the proof can be simplified if we prove
+Eqs.~(\ref{eq:quantum-interval-expectation-core}) and (\ref{eq:quantum-interval-expectation-core-equal})
+separately...}\end{thm}
+
+\begin{proof}By Eq.~(\ref{eq:interval-expectation-value-between-classical-quantum})
+and Thm.~\ref{thm:Rosenmuller}, we have
+
+\begin{equation}
+\expval{\mathbf{O}}_{\bar{\mu}}=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\bar{\mu}\right)=\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\,,
+\end{equation}
+where $\varphi:2^{\Omega}\rightarrow\events$ is defined by Eq.~(\ref{eq:pullback-function}).
+Hence, to prove Eq.~(\ref{eq:quantum-interval-expectation-core}),
+it is sufficient to prove
+\begin{equation}
+\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\subseteq\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,.\label{eq:quantum-interval-expectation-core-1}
+\end{equation}
+Since $\events_{\Omega}$ contains all projectors $P_{i}^{s}$ no
+matter how $\Omega$ is picked, $\events_{\Omega}$ is one of the
+possible choice of $\eventsC$. Thus, if Eq.~(\ref{eq:quantum-interval-expectation-core-1})
+is true, and we can also prove
+\begin{equation}
+\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\supseteq\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,,\label{eq:quantum-interval-expectation-core-supseteq}
+\end{equation}
+we then have Eq.~(\ref{eq:quantum-interval-expectation-core-equal}).
+
+\paragraph*{Proof of Eq.~(\ref{eq:quantum-interval-expectation-core-1})}
+
+According to Lemma~\ref{lemma:density-matrix-pullback}, for all
+$\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)$, there is
+a density matrix $\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)$
+such that $\mu=\varphi^{*}\muB_{\rho}$. Together with the properties
+of extremum and Eq.~(\ref{eq:real-expectation-value-between-classical-quantum}),
+we have 
+\begin{eqnarray}
+ &  & \min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\ge\min_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\muB_{\rho}\right)=\min_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\,,\\
+ &  & \max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\le\max_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\muB_{\rho}\right)=\max_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\,,
+\end{eqnarray}
+which implies Eq.~(\ref{eq:quantum-interval-expectation-core-1}).
+
+\paragraph*{Proof of Eq.~(\ref{eq:quantum-interval-expectation-core-supseteq})}
+
+Given a density matrix $\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)$,
+it must satisfy $\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)$
+for all $P\in\events_{\Omega}$. Since $\varphi\left(E\right)\in\events_{\Omega}$
+for all $E\subseteq\Omega$, we have 
+\begin{equation}
+\left(\varphi^{*}\muB_{\rho}\right)\left(E\right)=\muB_{\rho}\left(\varphi\left(E\right)\right)\in\bar{\mu}\left(\varphi\left(E\right)\right)=\left(\varphi^{*}\bar{\mu}\right)\left(E\right)\,,
+\end{equation}
+i.e., $\varphi^{*}\muB_{\rho}\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)$.
+
+Together with the properties of extremum and Eq.~(\ref{eq:real-expectation-value-between-classical-quantum}),
+the previous paragraph implies 
+\begin{eqnarray}
+ &  & \min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\le\min_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\muB_{\rho}\right)=\min_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\,,\\
+ &  & \max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\ge\max_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\muB_{\rho}\right)=\max_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\,,
+\end{eqnarray}
+which then implies Eq.~(\ref{eq:quantum-interval-expectation-core-supseteq}).\end{proof}
 
@@
 every event must be assigned a probability either in $\imposs$ or
-in $\necess$, i.e., every event is completely determined with certainty.
-As $\delta$ gets larger, the QIVPM allows for more indeterminate
-behavior. % For example, $\bar{\mu}_{A}$ defined in
+in $\necess$, i.e., whether every event is happened is completely
+determined with certainty. As $\delta$ gets larger, the QIVPM allows
+for more indeterminate behavior. % For example, $\bar{\mu}_{A}$ defined in
 % Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
@@
 $\lambda_{i}$ of that observable. To see this, note that given an
-orthonormal basis $\Omega=\{\ket{\psi_{0}},\ket{\psi_{1}},\ldots,\ket{\psi_{D-1}}\}$,
-a 0-deterministic QIVPM must map exactly one of the projectors $\proj{\psi_{i}}$
-to $\necess$ and all others to $\imposs$. This is because, by Eq.~(\ref{eq:necess}),
-we have $\bar{\mu}\left(\sum_{j=0}^{D-1}{\proj{\psi_{j}}}\right)=\necess$
+orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
+a 0-deterministic QIVPM must map exactly one of the projectors $\proj{i}$
+to $\necess$ and all others to $\imposs$. This is because, by Eq.~(\ref{eq:QIVPM-necess}),
+we have $\bar{\mu}\left(\sum_{j=0}^{D-1}{\proj{j}}\right)=\necess$
 and by inductively applying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
-we must have one of the $\bar{\mu}(\proj{\psi_{i}})=\necess$ and
-all others mapped to $\imposs$. Given any state~$\rho$ that is
-consistent with this QIVPM on all the projectors in $\Omega$, we
-have by Eq.~(\ref{eq:hbar}) that $\muB_{\rho}$ must also map exactly
-one of the projectors in $\Omega$ to 1 and all others to 0. If an
-observable has a spectral decomposition along~$\Omega$ then, by
-Eq.~(\ref{eq:quantum-expectation}), its expectation value relative
-to~$\muB_{\rho}$ is the eigenvalue $\lambda_{i}$ whose projector
-is mapped to 1. It therefore follows, by Eq.~(\ref{eq:quantum-interval-expectation-core}),
-that the expectation value relative to the 0-deterministic~${\bar{\mu}}$
-is fully determinate and lies in the interval $[\lambda_{i},\lambda_{i}]$.
+we must have one of the $\bar{\mu}\left(\proj{i}\right)=\necess$
+and all others mapped to $\imposs$. This unique projector mapping
+to $\necess$ will be denoted by $\proj{\necess}$. Given any state~$\rho$
+that is consistent with $\bar{\mu}$ on all the projectors in $\Omega$,
+we have by Eq.~(\ref{eq:consistent}) that $\muB_{\rho}$ must also
+map $\proj{\necess}$ to 1 and all other projectors formed by elements
+in $\Omega$ to 0. If an observable has a spectral decomposition along~$\Omega$
+then, by Eq.~(\ref{eq:quantum-expectation}), its expectation value
+relative to~$\muB_{\rho}$ is the eigenvalue $\lambda_{\necess}$
+whose projector is $\proj{\necess}$. It therefore follows, by Eq.~(\ref{eq:quantum-interval-expectation-core-equal}),
+that the expectation value relative to the 0-deterministic~$\bar{\mu}$
+is fully determinate and lies in the interval $[\lambda_{\necess},\lambda_{\necess}]$.
+
+Given a Hilbert space ${\cal H}$ of dimension $D$, the expectation
+value of the product of a sequence of commuting observables $\left\{ \mathbf{O}_{j}\right\} $
+relative to the 0-deterministic QIVPM~$\bar{\mu}$ is the product
+of the expectation value of individual $\mathbf{O}_{j}$. Since $\left\{ \mathbf{O}_{j}\right\} $
+is a sequence of commuting observables, they can be diagonalized by
+a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $
+with spectral decompositions 
+\begin{equation}
+\mathbf{O}_{j}=\sum_{i=0}^{D-1}\lambda_{j,i}\proj{i}\,.\label{eq:spectral-decomposition}
+\end{equation}
+Because of the orthogonality of $\Omega$, the product of Eqs.~(\ref{eq:spectral-decomposition})
+can also be simplified as a spectral decomposition $\prod_{j}\mathbf{O}_{j}=\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,i}\proj{i}$.
+According to our discussion in the previous paragraph, there is a
+unique projector such that $\bar{\mu}\left(\proj{\necess}\right)=\necess$,
+and the expectation values relative to $\bar{\mu}$ are their eigenvalues
+of $\proj{\necess}$, i.e., $\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\left[\lambda_{j,\necess},\lambda_{j,\necess}\right]$
+and
+\begin{equation}
+\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}=\left[\prod_{j}\lambda_{j,\necess},\prod_{j}\lambda_{j,\necess}\right]=\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
+\end{equation}
+with the understanding that the product of the singleton sets, $\prod_{j}\left[\lambda_{j,\necess},\lambda_{j,\necess}\right]$,
+is defined to be the product of their elements, $\left[\prod_{j}\lambda_{j,\necess},\prod_{j}\lambda_{j,\necess}\right]$.
 
@@
 
-We consider a two spin-$\frac{1}{2}$ Hilbert space $\Hilb=\Hilb_{1}\otimes\Hilb_{2}$
+\begin{proof}[Proof of Thm.~\ref{thm:Kochen-Specker}]We consider
+a two spin-$\frac{1}{2}$ Hilbert space $\Hilb=\Hilb_{1}\otimes\Hilb_{2}$
 of dimension $D=4$. We use the same nine observables $\mathbf{O}_{ij}$
@@
 whose associated projector is certain. Since the product of any two
-observables in a row is equal to the third, there must be an even
-number of occurrences of the interval $[-1,-1]$ in each row and hence
-in the entire table~\cite{TaiThesis2018}. However, looking at the
-expectation values of the observables in each column, there must be
-an even number of occurrences of the interval $[-1,-1]$ in the first
-two columns and an odd number in the $j=2$ column and hence in the
-entire table~\cite{TaiThesis2018}. The contradiction implies the
-non-existence of the assumed 0-deterministic QIVPM. %% We therefore prove a stronger statement of contextuality that 
+observables in a row is equal to the third, the product of any two
+their expectation values in a row is also equal to the third by Eq.~(\ref{eq:Kochen-Specker-Rules}),
+and there must be an even number of occurrences of the interval $[-1,-1]$
+in each row and hence in the entire table. However, looking at the
+expectation values of the observables in each column, by the same
+reason, there must be an even number of occurrences of the interval
+$[-1,-1]$ in the first two columns and an odd number in the $j=2$
+column and hence in the entire table. The contradiction implies the
+non-existence of the assumed 0-deterministic QIVPM.\end{proof}%% We therefore prove a stronger statement of contextuality that 
 %% includes the effects of finite-precision.
@@
 \end{equation}
-for all orthogonal projectors $P'$ and~$P''$. \end{lemma} The
-proof follows the outline of the proof of the classical inclusion-exclusion
-principle. From the commuting projectors $P_{0}$ and $P_{1}$, we
-construct the following three orthogonal projectors: $P_{0}P_{1}$,
-$P_{0}\left(\mathbb{1}-P_{1}\right)$, and $\left(\mathbb{1}-P_{0}\right)P_{1}$.
+for all orthogonal projectors $P'$ and~$P''$. \end{lemma}
+
+\begin{proof}The proof follows the outline of the proof of the classical
+inclusion-exclusion principle. From the commuting projectors $P_{0}$
+and $P_{1}$, we construct the following three orthogonal projectors:
+$P_{0}P_{1}$, $P_{0}\left(\mathbb{1}-P_{1}\right)$, and $\left(\mathbb{1}-P_{0}\right)P_{1}$.
 Then we proceed as follows:
@@
 \qquad\qquad=~~&\bar{\mu}\left(P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
- & (\mbox{because } P_{0} = P_{0}P_{1} + P_{0} - P_{0}P_{1}) \\ 
+ & (\mbox{because } P_{0} = P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})) \\ 
 =~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) \\ 
 =~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
-     & (\mbox{because } P_{1} = P_{0}P_{1} + P_{1} - P_{0}P_{1}) \\ 
+     & (\mbox{because } P_{1} = P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}) \\ 
 =~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1}))+\bar{\mu}(P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1})+ 
@@
 \end{equation*}
+\end{proof}
 
@@
 \end{equation}
-\end{lemma} The most important part of the proof is to verify the
+\end{lemma}
+
+\begin{proof}The most important part of the proof is to verify the
 convexity condition for $\barmuD$. By Lemma~\ref{lemma:verify-convexity},
@@
 
-\noindent When one of $\barmuD\left(P'\right)$ and $\barmuD\left(P''\right)$
+When one of $\barmuD\left(P'\right)$ and $\barmuD\left(P''\right)$
 is $\necess$, say $\barmuD\left(P'\right)=\imposs$ and $\barmuD\left(P''\right)=\necess$,
@@
 which implies $\bar{\mu}\left(P'+P''\right)\subseteq\left[0,2\delta\right]$.
-Since we assume $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
-$\left[1-\delta,1\right]$ are disjoint, which implies $\bar{\mu}\left(P'+P''\right)$
+Since we assume $\delta<\frac{1}{3}$, the intervals $\left[0,2\delta\right]$
+and $\left[1-\delta,1\right]$ are disjoint, which implies $\bar{\mu}\left(P'+P''\right)$
 and $\left[1-\delta,1\right]$ are disjoint. Together with the fact
@@
 and hence also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal})
-is again satisfied.
+is again satisfied.\end{proof}
 
@@
 dimension~$D\ge3$, there is no $\delta$-deterministic QIVPM for
-$\delta<\frac{1}{3}$.\end{thm} The proof is by contradiction: Suppose
-there is a $\delta$-deterministic QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
-By Lemma~\ref{lemma:delta2zero}, we can construct a 0-deterministic
-QIVPM; however, by Thm.~\ref{thm:Kochen-Specker}, such 0-deterministic
-QIVPMs do not exist.
+$\delta<\frac{1}{3}$.\end{thm}
+
+\begin{proof}[Proof by Contradiction] Suppose there is a $\delta$-deterministic
+QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. By Lemma~\ref{lemma:delta2zero},
+we can construct a 0-deterministic QIVPM; however, by Thm.~\ref{thm:Kochen-Specker},
+such 0-deterministic QIVPMs do not exist.\end{proof}
 
 \begin{table}
-\caption{\label{tab:probability-measures}Possible probability measures on
+\noindent \centering{}\caption{\label{tab:probability-measures}Possible probability measures on
 a Hilbert space of dimension~$D=3$, where $\bar{\mu}_{2}'$ and
@@
 by $P$.}
-\centering{}%
 \begin{tabular}{cccccc}
@@
 \addlinespace
-$P$  & $\bar{\mu}_{0}\left(P\right)$  & $\bar{\mu}_{1}\left(P\right)$  & $\bar{\mu}_{2}\left(P\right)$  & $\bar{\mu}_{2}'\left(P\right)$  & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
+$P$  & $\bar{\mu}_{0}\left(P\right)$  & $\bar{\mu}_{1}\left(P\right)$  & $\bar{\mu}_{2}\left(P\right)$  & $\bar{\mu}_{2}'\left(P\right)$  & $\bar{\mu}_{3}\left(P\right)$\tabularnewline\addlinespace
 \midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-\begin{tabular}{c}
-All one-dimensional\tabularnewline
-projectors\tabularnewline
-\end{tabular} & $\left[0,0\right]$  & $\left[0,\tfrac{1}{4}\right]$  & $\left[0,\tfrac{1}{3}\right]$  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
-\midrule 
-\addlinespace
-\begin{tabular}{c}
-All two-dimensional\tabularnewline
-projectors\tabularnewline
-\end{tabular} & $\left[1,1\right]$  & $\left[\tfrac{3}{4},1\right]$  & $\left[\tfrac{2}{3},1\right]$  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$  & $\left[\tfrac{1}{2},1\right]$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$  & $\necess$  & $\necess$  & $\necess$  & $\necess$  & $\necess$\tabularnewline
+\addlinespace
+\addlinespace
+$\mathbb{0}$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+All one-dimensional projectors & $\left[0,0\right]$  & $\left[0,\tfrac{1}{4}\right]$  & $\left[0,\tfrac{1}{3}\right]$  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+All two-dimensional projectors & $\left[1,1\right]$  & $\left[\tfrac{3}{4},1\right]$  & $\left[\tfrac{2}{3},1\right]$  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$  & $\left[\tfrac{1}{2},1\right]$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$\mathbb{1}$  & $\necess$  & $\necess$  & $\necess$  & $\necess$  & $\necess$\tabularnewline\addlinespace
 \bottomrule
+\addlinespace
 \end{tabular}
@@
 \end{figure}
-
 As is the case for conventional, infinitely-precise, quantum probability
@@
 
+Similar to how we proved Thm.~\ref{cor:Kochen-Specker-IVPM}, we
+need other two lemmas to simplify the proof of the convexity condition.
+
+\begin{lemma}\label{thm:convex-3}Given a Hilbert space~$\Hilb$
+of dimension~$3$, to verify $\bar{\mu}:\events\rightarrow\mathscr{I}$
+is a QIVPM, it is sufficient to check Eqs.~(\ref{eq:QIVPM-constraints})
+and 
+\begin{equation}
+\bar{\mu}\left(P'+P''\right)\subseteq\bar{\mu}\left(P'\right)+\bar{\mu}\left(P''\right)\label{amr-1}
+\end{equation}
+for each pair of orthogonal projectors $P'$ and~$P''$.\end{lemma}
+
+\begin{proof}The most important part of the proof is to verify the
+convexity condition for $\bar{\mu}$. Given a pair of commuting projectors
+$P_{0}$ and $P_{1}$ on a three-dimensional Hilbert space, they can
+be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+Consider the function $\varphi:2^{\Omega}\rightarrow\events$ defined
+in Eq.~(\ref{eq:pullback-function}), there are two set of basis
+vectors $E_{0}$ and $E_{1}\subseteq\Omega$, such that $\varphi\left(E_{0}\right)=P_{0}$
+and $\varphi\left(E_{1}\right)=P_{1}$. Since $E_{0}$ and $E_{1}$
+are both subsets of a three-element set, their relation has only three
+possibilities. The first possibility is that one of them is a subset
+of the other one, $E_{0}\subseteq E_{1}$ or $E_{1}\subseteq E_{0}$.
+The second possibility is that they are disjoint, $E_{0}\cap E_{1}=\emptyset$.
+If neither of the previous possibilities is true, i.e., they have
+some intersections, but not a subset relation, then all of $E_{0}\cap E_{1}$,
+$E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$ are non-empties.
+Together with the fact that $\Omega$ has only three elements, they
+are all singleton sets.
+\begin{itemize}
+\item When one of them is a subset of the other one, say $E_{0}\subseteq E_{1}$,
+we have $P_{0}P_{1}=\varphi\left(E_{0}\cap E_{1}\right)=P_{0}$ and
+$P_{0}+P_{1}-P_{0}P_{1}=P_{1}$. Thus,
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\bar{\mu}\left(P_{1}\right)+\bar{\mu}\left(P_{0}\right)\,.
+\end{equation}
+\item When $E_{0}\cap E_{1}=\emptyset$, we have $P_{0}P_{1}=\varphi\left(E_{0}\cap E_{1}\right)=\mathbb{0}$
+and 
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion-3}
+\end{equation}
+by Eq.~(\ref{amr-1}).
+\item When $E_{0}\cap E_{1}$, $E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$
+are all singleton sets, say $E_{0}\backslash E_{1}=\left\{ \ket{0}\right\} $,
+$E_{1}\backslash E_{0}=\left\{ \ket{1}\right\} $, and $E_{0}\cap E_{1}=\left\{ \ket{2}\right\} $,
+proving an equivalent condition for the convexity condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
+is easier than proving Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
+directly. Since one minus an interval maps this interval to its mirror
+image, and reflection preserves the subset relations, the convexity
+condition holds if and only if
+\begin{equation}
+\necess-\bar{\mu}\left(P_{0}P_{1}\right)+\necess-\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)\subseteq\necess-\bar{\mu}\left(P_{0}\right)+\necess-\bar{\mu}\left(P_{1}\right)
+\end{equation}
+which is equivalent to
+\begin{equation}
+\bar{\mu}\left(\mathbb{1}-P_{0}P_{1}\right)+\bar{\mu}\left(\mathbb{1}-\left(P_{0}+P_{1}-P_{0}P_{1}\right)\right)\subseteq\bar{\mu}\left(\mathbb{1}-P_{0}\right)+\bar{\mu}\left(\mathbb{1}-P_{1}\right)
+\end{equation}
+because of Eq.~(\ref{eq:QIVPM-complement}). The last equation holds
+because we can apply Eq.~(\ref{amr-1}) on the following chain of
+equations:
+\begin{equation}
+\begin{aligned} & \bar{\mu}\left(\mathbb{1}-P_{0}P_{1}\right)+\bar{\mu}\left(\mathbb{1}-\left(P_{0}+P_{1}-P_{0}P_{1}\right)\right)=\bar{\mu}\left(\proj{0}+\proj{1}\right)+\bar{\mu}\left(\mathbb{0}\right)\\
+\subseteq{} & \bar{\mu}\left(\proj{0}\right)+\bar{\mu}\left(\proj{1}\right)=\bar{\mu}\left(\mathbb{1}-P_{0}\right)+\bar{\mu}\left(\mathbb{1}-P_{1}\right)\,.
+\end{aligned}
+\end{equation}
+\end{itemize}
+Since the convexity condition holds for all three possibilities, $\bar{\mu}$
+is a QIVPM.\end{proof}
+
+\begin{lemma}\label{thm:convex-3-1}Given a Hilbert space~$\Hilb$
+of dimension~$3$, to verify $\bar{\mu}:\events\rightarrow\mathscr{I}$
+is a QIVPM, it is sufficient to check Eqs.~(\ref{eq:QIVPM-constraints})
+and 
+\begin{equation}
+\bar{\mu}\left(\proj{\psi'}+\proj{\psi''}\right)\subseteq\bar{\mu}\left(\proj{\psi'}\right)+\bar{\mu}\left(\proj{\psi''}\right)\label{amr-3}
+\end{equation}
+for each pair of orthogonal states $\ket{\psi'}$ and $\ket{\psi''}$.\end{lemma}
+
+\begin{proof}Since any projectors can be expressed as the sum of
+orthogonal one-dimensional projectors, Eq.~(\ref{amr-3}) implies
+Eq.~(\ref{amr-1}) by induction, and this lemma holds because of
+Lemma~\ref{thm:convex-3}.\end{proof}
+
+After we proved the lemmas, we can state and prove the theorem.
+
 \begin{thm}[Empty Cores Exist for General QIVPMs]\label{thm:Non-extensible-of-Gleason's}There
-exists a Hilbert space ${\cal H}$ and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+exists a Hilbert space $\Hilb$ and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
 such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
@@
 
-To prove this theorem, we need to construct a QIVPM on some Hilbert
-space, and verify that there are no states that are consistent (see
-Defs.~\ref{def:Consistency} and \ref{def:core}) with it on all
-possible events. Assume a Hilbert space of dimension $D=3$ with orthonormal
-basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
-$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and assign 
+\begin{proof}To prove this theorem, we need to construct a QIVPM
+on some Hilbert space, and verify that there are no states that are
+consistent (see Def.~\ref{def:Consistency}) with it on all possible
+events. Assume a Hilbert space of dimension $D=3$ with orthonormal
+basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$,
+$\ket{\ps'}=\frac{\ket{0}+\ket{2}}{\sqrt{2}}$, and assign 
 \begin{equation}
@@
 \end{equation}
-The map~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined in
-Table~\ref{tab:non-Born-QIVPM} can be verified to be a QIVPM~\cite{TaiThesis2018}.
+Consider the map $\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
+in Table~\ref{tab:non-Born-QIVPM}. We want to prove $\bar{\mu}$
+is a QIVPM. Since it is easy to verify $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}),
+by Lemma~\ref{thm:convex-3-1}, it is sufficient to verify for each
+pair of orthogonal states $\ket{\psi'}$ and $\ket{\psi''}$ 
+\begin{equation}
+\bar{\mu}\left(\proj{\psi'}+\proj{\psi''}\right)\subseteq\bar{\mu}\left(\proj{\psi'}\right)+\bar{\mu}\left(\proj{\psi''}\right)\,.\label{amr-2}
+\end{equation}
+Since $\ket{0}$, $\ket{\ps}$, and $\ket{\ps'}$ are not orthogonal
+to each other, at least one of $\bar{\mu}\left(\proj{\psi'}\right)$
+and $\bar{\mu}\left(\proj{\psi''}\right)$ is unknown~$\unknown$,
+which implies $\unknown\subseteq\bar{\mu}\left(\proj{\psi'}\right)+\bar{\mu}\left(\proj{\psi''}\right)$.
+Together with the fact that every interval in $\mathscr{I}_{0}$ is
+a subset of $\unknown$, Eq.~(\ref{amr-2}) holds, and $\bar{\mu}$
+is a QIVPM.
+
 \begin{table}
-\caption{\label{tab:non-Born-QIVPM}QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+\noindent \centering{}\caption{\label{tab:non-Born-QIVPM}QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
 on a Hilbert space of dimension~$D=3$. Events are listed in the
 column labeled by $P$.}
-
 \begin{tabular}{cc}
@@
 \addlinespace
-$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
+$P$  & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
 \midrule
-\midrule 
-\addlinespace
-$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$  & $\imposs$\tabularnewline
-\midrule 
-\addlinespace
-$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, $\mathbb{1}-\proj{\ps'}$  & $\necess$\tabularnewline
-\midrule 
-\addlinespace
-All other projectors  & $\unknown$\tabularnewline
+\addlinespace
+\addlinespace
+$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$  & $\imposs$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, $\mathbb{1}-\proj{\ps'}$  & $\necess$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+All other projectors  & $\unknown$\tabularnewline\addlinespace
 \bottomrule
+\addlinespace
 \end{tabular}
 \end{table}
-
 Next we will prove by contradiction that $\coreBorn\left(\bar{\mu},\events\right)$
@@
 for $\proj{\ps}$ and $\proj{\ps'}$. If this is true, then $\ip{0}{\phi_{j}}=\ip{\ps}{\phi_{j}}=\ip{\ps'}{\phi_{j}}=0$
-for all~$j$, and thus \begin{subequations} 
-\begin{eqnarray}
- &  & \ip{1}{\phi_{j}}=\sqrt{2}\ip{\ps}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,,\\
- &  & \ip{2}{\phi_{j}}=\sqrt{2}\ip{\ps'}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,.
-\end{eqnarray}
-\end{subequations} The above equations imply $\ket{\phi_{j}}=\ket{0}\ip{0}{\phi_{j}}+\ket{1}\ip{1}{\phi_{j}}+\ket{2}\ip{2}{\phi_{j}}=0$,
+for all~$j$, and thus 
+\begin{align}
+\ip{1}{\phi_{j}}=\sqrt{2}\ip{\ps}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,, &  & \ip{2}{\phi_{j}}=\sqrt{2}\ip{\ps'}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,.
+\end{align}
+The above equations imply $\ket{\phi_{j}}=\ket{0}\ip{0}{\phi_{j}}+\ket{1}\ip{1}{\phi_{j}}+\ket{2}\ip{2}{\phi_{j}}=0$,
 violating the assumption that $\ket{\phi_{j}}$ is a normalized state,
-and thus the theorem is proved.
+and thus the theorem is proved.\end{proof}
 
@@
 a finite-precision extension of Gleason's theorem can be stated as
-follows:
+follows.
 
@@
 
-The proof proceeds as follows. Given a state~$\rho'$ consistent
-with $f\circ\muB_{\rho}$, we have $\muB_{\rho'}\left(\proj{\psi}\right)\in f\left(\muB_{\rho}\left(\proj{\psi}\right)\right)$
+\begin{proof}Given a state~$\rho'$ consistent with $f\circ\muB_{\rho}$,
+we have $\muB_{\rho'}\left(\proj{\psi}\right)\in f\left(\muB_{\rho}\left(\proj{\psi}\right)\right)$
 for any one-dimensional projector $P=\proj{\psi}$. Since the maximum
@@
 the upper bound of the difference: 
-\[
+\begin{equation}
 \left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le\alpha\,.
-\]
+\end{equation}
 Since $\rho-\rho'$ is Hermitian, $\max_{\left\Vert \psi\right\Vert =1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
@@
 and equal to $\left\Vert \rho-\rho'\right\Vert $~\cite{GolubVanLoan1996,Foucart2012}.
-Hence, $\left\Vert \rho-\rho'\right\Vert \le\alpha$.
+Hence, $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{proof}
 
@@
 An interval map is called \emph{ultramodular} if it satisfies the
-following properties:
+following properties.
 
@@
 $\necess$, an interval map $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
-is called ultramodular if: \begin{subequations}\label{eq:iota-constraints}
-\begin{eqnarray}
- &  & \ultramodular(0)=\imposs\,,\\
- &  & \ultramodular(1)=\necess\,,\\
- &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,
-\end{eqnarray}
-\end{subequations}and for any three numbers~$x_{0}$, $x_{1}$,
-and $x_{2}\in\left[0,1\right]$ such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
-we have: 
+is called ultramodular if: 
+\begin{align}
+\ultramodular(0)=\imposs\,, &  & \ultramodular(1)=\necess\,, &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,\label{eq:iota-constraints}
+\end{align}
+and for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
+such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have: 
 \begin{equation}
@@
 
-\item \label{enu:iota-mu-CIVPM}The composite function~$\ultramodular\circ\mu:\eventsC\rightarrow\mathscr{I}$
-is a classical IVPM for all classical probability measures~$\mu:\eventsC\rightarrow\left[0,1\right]$.
-
-\item \label{enu:iota-mu-QIVPM}The composite function~$\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$
-is a QIVPM for all quantum probability measures~$\mu:\events\rightarrow\left[0,1\right]$.
+\item \label{enu:iota-mu-CIVPM}The composite function $\ultramodular\circ\mu:2^{\Omega}\rightarrow\mathscr{I}$
+is a classical IVPM for all classical probability measures $\mu:2^{\Omega}\rightarrow\left[0,1\right]$.
+
+\item \label{enu:iota-mu-QIVPM}The composite function $\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$
+is a QIVPM for all quantum probability measures $\mu:\events\rightarrow\left[0,1\right]$.
 \end{enumerate} \end{thm}
 
-Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
+\begin{proof}Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
 and~\ref{enu:iota-mu-QIVPM} as we have outlined above. Conversely,
@@
 satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the state: 
-\[
+\begin{equation}
 \rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-y\right)\proj{3}\,.
-\]
+\end{equation}
 The induced map $\ultramodular\circ\muB_{\rho}$ constructed using
@@
 when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. In
-other words, this induced map fails to be a QIVPM. For the classical
-case, if $\ultramodular$ is not ultramodular, we also want to find
-a classical probability measure $\mu:\eventsC\rightarrow\left[0,1\right]$
-such that $\ultramodular\circ\mu$ is not a classical IVPM. This can
-be done by restricting our previous quantum probability measure $\muB_{\rho}$
-to the space of events $\eventsC$ generated by the mutually commuting
-projectors $\proj{0}$, $\proj{1}$, $\proj{2}$, and $\proj{3}$.
-The restricted function $\mu=\muB_{\rho}|_{\eventsC}$ is then a classical
-probability measure, and the induced map $\ultramodular\circ\mu$
-fails to be a classical IVPM for the same reason as in the quantum
-case.
+other words, this induced map fails to be a QIVPM.
+
+For the classical case, if $\ultramodular$ is not ultramodular, we
+also want to find a classical probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+such that $\ultramodular\circ\mu$ is not a classical IVPM. Consider
+an orthonormal basis $\Omega$ containing $\ket{0}$, $\ket{1}$,
+$\ket{2}$, $\ket{3}$, \ldots , and $\ket{D-1}$, and $\varphi:2^{\Omega}\rightarrow\events$
+defined by Eq.~(\ref{eq:pullback-function}). Notice that the pullback
+of our previous quantum probability measure $\muB_{\rho}$, $\varphi^{*}\muB_{\rho}$,
+is a classical probability measure. If we pick $\mu$ as $\varphi^{*}\muB_{\rho}$,
+then the induced map $\ultramodular\circ\mu$ fails to be a classical
+IVPM for the same reason as in the quantum case.\end{proof}
 
@@
 maps can be gleaned from the properties of ultramodular functions.
-The following is a most interesting property in our setting:
+The following is a most interesting property in our setting.
 
@@
 
-Since $\ultramodular$ maps to intervals, we can decompose it into
-two functions: its left-end and right-end, where $\left[\ultramodularL\left(x\right),\ultramodularR\left(x\right)\right]=\ultramodular\left(x\right)$.
+\begin{proof}Since $\ultramodular$ maps to intervals, we can decompose
+it into two functions: its left-end and right-end, where $\left[\ultramodularL\left(x\right),\ultramodularR\left(x\right)\right]=\ultramodular\left(x\right)$.
 By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\ultramodularL:\left[0,1\right]\rightarrow\left[0,1\right]$
@@
 i.e., 
-\[
+\begin{equation}
 \ultramodularL\left(y\right)+\ultramodularL\left(x_{2}\right)\ge\ultramodularL\left(x_{0}+x_{2}\right)+\ultramodularL\left(x_{1}+x_{2}\right)
-\]
+\end{equation}
 for three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
@@
 to the same interval, or the number of intervals to which $\ultramodular$
-maps must be uncountable.
+maps must be uncountable.\end{proof}
 
@@
 
-\chapter{Further Questions}
-
-When people proved the original Gleason theorem, people usually exploited
-the geometrical structure of real 3-dimensional Hilbert space \cite{gleason1957,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
-Since our finite-precision extension of the Gleason theorem only applies
-on a class of QIVPMs, we might want to ask how to modify these geometrical
-arguments to have a Gleason-type theorem for general QIVPMs. We will
-further study the tensor product structure among QIVPMs which is essential
-for defining product and entangled states, and serves the basis to
-discuss quantum nonlocality~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-and quantum computing with QIVPMs. Finally, we want to improve the
-discrete quantum theories to consider QIVPMs over finite fields in
-future research.
-
-\addcontentsBibliography %
+\chapter{Further Discussion}
+
+\todo{Further discussion clean up until here.} Almost all QIVPMs
+in Chapter~\ref{chap:QIVPM} are closely related to quantum probability
+measures. For example, given a $\delta$-deterministic QIVPM, Lemma~\ref{lemma:delta2zero}
+provides a way to derive a $0$-deterministic QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
+which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+satisfying $\mu\left(P\right)$ is either $0$ or $1$. Moreover,
+an interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$ in Sec.~\ref{sec:Gleason}
+provides an systemic way to derive QIVPMs from quantum probability
+measures.
+
+the only QIVPM unrelated to quantum probability measures is defined
+in Table~\ref{tab:non-Born-QIVPM}, and is ill-behaved as having
+an empty core.
+
+On one hand, classical IVPMs could be studied directly without deriving
+from or to classical probability measures.
+
+On the other hand, to state the original Gleason theorem, we don't
+need to know a state a priori, and use this state to derive a quantum
+probability measures and further a QIVPM. Therefore, it would be desirable
+if we could answer the following variant of Gleason theorem which
+
+whether shirking the maximum length of intervals alone could provide
+a well-behaved QIVPMs. More precisely, we have the following question.
+
+\begin{question}In a Hilbert space $\Hilb$ of dimension $D\geq3$,
+given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, $\alpha$
+be the maximum length of intervals in $\mathscr{I}$, is there an
+$\varepsilon\in\left(0,1\right)$ such that $\alpha<\varepsilon$
+implies $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
+
+\clearpageAddContentsChapter{Bibliography} %
 \begin{comment}
@@
 
-% http://latex.org/forum/viewtopic.php?t=7312
-% http://latex.org/forum/viewtopic.php?t=17956
-\addtocontents{toc}{\contentsline{chapter}{Curriculum Vitae}{}}
+\addContentsChapterWithoutPagenumber{Curriculum Vitae}
+
 \includepdf[pages=-]{CV_thesis} 

### 2018-11-11 dissertation.tex
dissertation.tex Exported from dissertation.lyx

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{amssymb}
@@
 Given a finite sample space~$\Omega$, and its power set $2^{\Omega}$
-as the classical event space, a classical probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+as the classical event space, a classical probability measure $\mu$
+describe how likely every event~$E$ could happen by mapping $E$
+to a number $\mu\left(E\right)\in\left[0,1\right]$.
+
 is a function subject to the following constraints: $\mu\left(\emptyset\right)=0$,
@@
 
-\todo{Further discussion clean up until here.} Almost all QIVPMs
-in Chapter~\ref{chap:QIVPM} are closely related to quantum probability
-measures. For example, given a $\delta$-deterministic QIVPM, Lemma~\ref{lemma:delta2zero}
-provides a way to derive a $0$-deterministic QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
+Almost all QIVPMs in Chapter~\ref{chap:QIVPM} are closely related
+to quantum probability measures. For example, given a $\delta$-deterministic
+QIVPM, Lemma~\ref{lemma:delta2zero} provides a way to derive a $0$-deterministic
+QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
 which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$

### 2018-11-12 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating, and then put TODOs so that I can wrap up and send to Andy...

@@
 of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
-Given a finite sample space~$\Omega$, and its power set $2^{\Omega}$
-as the classical event space, a classical probability measure $\mu$
-describe how likely every event~$E$ could happen by mapping $E$
-to a number $\mu\left(E\right)\in\left[0,1\right]$.
-
-is a function subject to the following constraints: $\mu\left(\emptyset\right)=0$,
-$\mu\left(\Omega\right)=1$, $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
-and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
+Given a finite sample space~$\Omega$ representing all possible outcomes,
+and its power set $2^{\Omega}$ as the classical event space, a classical
+probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
+specifying how likely one of the outcome~$\omega\in E$ actually
+happens. To maintain the coherence, we want $\mu$ subject to the
+following constraints: $\mu\left(\emptyset\right)=0$, $\mu\left(\Omega\right)=1$,
+$\mu\left(\overline{E}\right)=1-\mu\left(E\right)$, and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
 for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
@@
 with $P_{0}P_{1}=P_{1}P_{0}$. In a quantum probability space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
+the set of all events is the set of all projectors on a given Hilbert
+space denoted by $\events$. After the measurement, if the system
+transits to a state $\ket{\Phi}$ and we call an event $P\in\events$
+happen when .
+
 each event~$P_{i}$ is mapped to a probability~$\mu\left(P_{i}\right)$
-using a probability measure $\mu:\events\rightarrow\left[0,1\right]$,
-where $\events$ is the set of all events, (i.e., projectors on a
-given Hilbert space), subject to the following constraints:
+using a probability measure $\mu:\events\rightarrow\left[0,1\right]$
+subject to the following constraints:
 \begin{align}

### 2018-11-13 dissertation.tex
dissertation.lyx Adding TODOs

@@
 probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
-specifying how likely one of the outcome~$\omega\in E$ actually
-happens. To maintain the coherence, we want $\mu$ subject to the
-following constraints: $\mu\left(\emptyset\right)=0$, $\mu\left(\Omega\right)=1$,
+specifying how likely one of the outcome in $E$ actually happens.
+To maintain the coherence, we want $\mu$ subject to the following
+constraints: $\mu\left(\emptyset\right)=0$, $\mu\left(\Omega\right)=1$,
 $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$, and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
@@
 the set of all events is the set of all projectors on a given Hilbert
-space denoted by $\events$. After the measurement, if the system
-transits to a state $\ket{\Phi}$ and we call an event $P\in\events$
-happen when .
-
+space denoted by $\events$. \todo{Use the same idea as the classical
+probability measure to explain the meaning of $\mu\left(P\right)$.}
 each event~$P_{i}$ is mapped to a probability~$\mu\left(P_{i}\right)$
@@
 
-A conventional quantum probability measure can easily be constructed
-using the Born rule if one knows the current pure unnormalized quantum
-state $\ket{\Phi}\in\mathcal{H}$; then the Born rule induces a probability
-measure $\muB_{\Phi}$ defined as 
+\todo{Rewrite the beginng of this paragraph to explain the meaning
+of the Born rule... Maybe move Gleason's Theorem here?} A conventional
+quantum probability measure can easily be constructed using the Born
+rule if one knows the current pure unnormalized quantum state $\ket{\Phi}\in\mathcal{H}$;
+then the Born rule induces a probability measure $\muB_{\Phi}$ defined
+as 
 \begin{equation}
@@
 
+\todo{Make the meaning of Gleason's Theorem more clear? So that we
+can explain the motivation of the question in Chapter~\ref{chap:Further-Discussion}}
 A conventional quantum probability measure can be easily constructed
@@
 Kochen-Specker to experimental, and hence finite-precision, quantum
-measurements \cites{PhysRevLett.83.3751}{HKSS1999}{Mermin1999}{Kent1999}{SimonBruknerZeilinger2001}{Cabello2002}{Larsson2002}{Appleby2002}{BarrettKent2004}{Appleby_2005}{Spekkens2005}{GuehneKleinmannCabelloEtAl2010}{MazurekPuseyKunjwalEtAl2016}.
-Specifically, the original Kochen-Specker theorem is formulated using
-a model quantum mechanical system that has \emph{definite values at
-all times}~\cite{Held2016}, i.e., its observables have infinitely
-precise values at all times. Our interval-valued probability framework
-will allow us to state, and prove, a stronger version of the theorem
-that holds even if the observables have values that are only definite
-up to some precision specified by a parameter $\delta$. Our approach
-provides a quantitative realization of Mermin's intuition~\cite{Mermin1999}: 
+measurements . Specifically, the original Kochen-Specker theorem
+is formulated using a model quantum mechanical system that has \emph{definite
+values at all times}~\cite{Held2016}, i.e., its observables have
+infinitely precise values at all times. Our interval-valued probability
+framework will allow us to state, and prove, a stronger version of
+the theorem that holds even if the observables have values that are
+only definite up to some precision specified by a parameter $\delta$.
+Our approach provides a quantitative realization of Mermin's intuition~\cite{Mermin1999}: 
 \begin{quote}
@@
 
-\chapter{Further Discussion}
-
-Almost all QIVPMs in Chapter~\ref{chap:QIVPM} are closely related
-to quantum probability measures. For example, given a $\delta$-deterministic
-QIVPM, Lemma~\ref{lemma:delta2zero} provides a way to derive a $0$-deterministic
-QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
+\chapter{Further Discussion\label{chap:Further-Discussion}}
+
+\todo{After updating Sec.~\ref{sec:fuzzy}, update this chapter
+by starting from the meaning of Gleason's Theorem.} Almost all QIVPMs
+in Chapter~\ref{chap:QIVPM} are closely related to quantum probability
+measures. For example, given a $\delta$-deterministic QIVPM, Lemma~\ref{lemma:delta2zero}
+provides a way to derive a $0$-deterministic QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
 which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$

### 2018-11-14 dissertation.tex
dissertation.tex Exported from dissertation.lyx...

@@
 Kochen-Specker to experimental, and hence finite-precision, quantum
-measurements . Specifically, the original Kochen-Specker theorem
-is formulated using a model quantum mechanical system that has \emph{definite
-values at all times}~\cite{Held2016}, i.e., its observables have
-infinitely precise values at all times. Our interval-valued probability
-framework will allow us to state, and prove, a stronger version of
-the theorem that holds even if the observables have values that are
-only definite up to some precision specified by a parameter $\delta$.
-Our approach provides a quantitative realization of Mermin's intuition~\cite{Mermin1999}: 
+measurements \cite{PhysRevLett.83.3751,HKSS1999,Mermin1999,Kent1999,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
+Specifically, the original Kochen-Specker theorem is formulated using
+a model quantum mechanical system that has \emph{definite values at
+all times}~\cite{Held2016}, i.e., its observables have infinitely
+precise values at all times. Our interval-valued probability framework
+will allow us to state, and prove, a stronger version of the theorem
+that holds even if the observables have values that are only definite
+up to some precision specified by a parameter $\delta$. Our approach
+provides a quantitative realization of Mermin's intuition~\cite{Mermin1999}: 
 \begin{quote}

### 2018-11-14 dissertation.tex
dissertation.lyx Global replace \cites by \cite

@@
 \usepackage{amsmath}
-\usepackage{amsthm}
 \usepackage{amssymb}
@@
 thesis — that probabilistic Turing machines can efficiently simulate
-any physically realizable model of computation — is correct \cites{Bernstein:1993:QCT:167088.167097}{Kaye2007}. 
+any physically realizable model of computation — is correct \cite{Bernstein:1993:QCT:167088.167097,Kaye2007}. 
 \end{enumerate}
@@
 to zero over real numbers and whether a number is exactly zero over
-complex numbers \cites{BSS1989}{Ziegler2007}{blum2012complexity}.
-Since no physical analog computer could branch in these operations
-based on a few significant figures, the theoretical prediction of
-Blum-Cucker-Shub-Smale (BCSS) machine cannot fully apply on physical
-devices.
+complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}. Since
+no physical analog computer could branch in these operations based
+on a few significant figures, the theoretical prediction of Blum-Cucker-Shub-Smale
+(BCSS) machine cannot fully apply on physical devices.
 
@@
 the necessary conditions for reasoning coherently about collections
-of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
+of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
 Given a finite sample space~$\Omega$ representing all possible outcomes,
@@
 space denoted by $\events$. \todo{Use the same idea as the classical
-probability measure to explain the meaning of $\mu\left(P\right)$.}
-each event~$P_{i}$ is mapped to a probability~$\mu\left(P_{i}\right)$
-using a probability measure $\mu:\events\rightarrow\left[0,1\right]$
-subject to the following constraints:
+probability measure to explain the meaning of $\mu\left(P\right)$.
+Maybe move the structure preserving function $\varphi:2^{\Omega}\rightarrow\events$
+defined in Eq.~\ref{eq:pullback-function} here.} each event~$P_{i}$
+is mapped to a probability~$\mu\left(P_{i}\right)$ using a probability
+measure $\mu:\events\rightarrow\left[0,1\right]$ subject to the following
+constraints:
 \begin{align}
@@
 and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule induces a
-probability measure $\muB_{\rho}$ defined as \cites{Born1983}{Mermin2007}{Jaeger2007}
+probability measure $\muB_{\rho}$ defined as \cite{Born1983,Mermin2007,Jaeger2007}
 \begin{equation}
@@
 is said to be entangled if it cannot be written as a product of states
-of each subsystem \cites{peres1995quantum}{544199}{Jaeger2007}. That
+of each subsystem \cite{peres1995quantum,544199,Jaeger2007}. That
 is, a state $\ket{\Psi}$ is entangled if $\ket{\Psi}\ne\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$,
@@
 is entangled if and only if at least one subsystem state is \textit{mixed},
-i.e., $\Tr_{j}\left(\rho_{j}^{2}\right)<1$ \cites{544199}{Jaeger2007}.\NewDocumentCommand{\jthSubsystem}{m O{} m}{{#1}_{#2}^{#3}}
+i.e., $\Tr_{j}\left(\rho_{j}^{2}\right)<1$ \cite{544199,Jaeger2007}.\NewDocumentCommand{\jthSubsystem}{m O{} m}{{#1}_{#2}^{#3}}
 
@@
 of elements equipped with the operations of addition, subtraction,
-multiplication, and division \cites{DummitFoote2004}{fieldtheory.ref}{numtheory.ref}.
+multiplication, and division \cite{DummitFoote2004,fieldtheory.ref,numtheory.ref}.
 Fields may contain an infinite or a finite number of elements. The
@@
 the an ordered region, following the standard procedure to define
-a conventional fraction as a pair of integers \cites{Artin1991}{DummitFoote2004}{hottbook2013}{Wolfram2016},
+a conventional fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
 we could define a \emph{cardinal probability} as a pair of order-region
@@
 The details of the comparison can easily formulated by following the
-standard procedure \cites{Artin1991}{DummitFoote2004}{hottbook2013}{Wolfram2016}
+standard procedure \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016}
 and will left as an exercise for the readers.
@@
 that uses $\subseteq$ instead of $=$ for the same reason as before.
-The new condition, known as \emph{convexity}~\cites{Shapley1971}{GilboaSchmeidler1994}{NgMoYeh1997Chinese}{Marinacci1999}{MarinacciMontrucchio2005}{Grabisch2016},
+The new condition, known as \emph{convexity} \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997Chinese,Marinacci1999,MarinacciMontrucchio2005,Grabisch2016},
 reduces to the previously motivated Eq.~(\ref{eq:disjoint}) when
@@
 
-\begin{thm}[Shapley \cites{Shapley1971}{GilboaSchmeidler1994}{NgMoYeh1997Chinese}{Grabisch2016}]\label{thm:Shapley-classical}Every
+\begin{thm}[Shapley \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997Chinese,Grabisch2016}]\label{thm:Shapley-classical}Every
 classical IVPM has a non-empty core.\end{thm}
@@
 on a projector~$P$ if the interval $\bar{\mu}(P)$ contains the
-exact probability calculated by the Born rule \cites{Born1983}{Mermin2007}{Jaeger2007},
+exact probability calculated by the Born rule \cite{Born1983,Mermin2007,Jaeger2007},
 i.e., 
@@
 A conventional quantum probability measure can be easily constructed
-from a state $\rho$ according to the Born rule \cites{Born1983}{Mermin2007}{Jaeger2007}.
+from a state $\rho$ according to the Born rule \cite{Born1983,Mermin2007,Jaeger2007}.
 According to Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum},
@@
 is the direct counterpart of the convexity conditions, Eqs.~(\ref{eq:classicalconvex})
-and (\ref{eq:QuantumInterval-valuedProbability-Inclusion}) \cites{Choquet1954}{Shapley1971}{NgMoYeh1997Chinese}{MarinacciMontrucchio2005}.
+and (\ref{eq:QuantumInterval-valuedProbability-Inclusion}) \cite{Choquet1954,Shapley1971,NgMoYeh1997Chinese,MarinacciMontrucchio2005}.
 Therefore, these conditions guarantee that, for any conventional quantum

### 2018-11-14 dissertation.tex
dissertation.lyx "2.2.1 Gleason's Theorem and the properties of the Born rule" Updating...

@@
 \todo{Make the meaning of Gleason's Theorem more clear? So that we
-can explain the motivation of the question in Chapter~\ref{chap:Further-Discussion}}
+can explain the motivation of the question in Chapter~\ref{chap:Further-Discussion}.}
 A conventional quantum probability measure can be easily constructed

### 2018-11-18 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 To maintain the coherence, we want $\mu$ subject to the following
-constraints: $\mu\left(\emptyset\right)=0$, $\mu\left(\Omega\right)=1$,
-$\mu\left(\overline{E}\right)=1-\mu\left(E\right)$, and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
-for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
+constraints. When $E$ contains no outcome, $E$ is the least likely
+to happen, i.e., $\mu\left(\emptyset\right)=0$. When $E$ contains
+all outcomes, $E$ is the most likely to happen, i.e., $\mu\left(\Omega\right)=1$.
+If we know the likelihood of an event, $\mu\left(E\right)$, it is
+natural to assume the likelihood of the event’s complement is just
+the opposite of $\mu\left(E\right)$, i.e., $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$.
+For each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$,
+the likelihood of the union event is additive, $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$.
+
+The previous abstraction
 

### 2018-11-19 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
-Given a finite sample space~$\Omega$ representing all possible outcomes,
-and its power set $2^{\Omega}$ as the classical event space, a classical
-probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
-specifying how likely one of the outcome in $E$ actually happens.
-To maintain the coherence, we want $\mu$ subject to the following
-constraints. When $E$ contains no outcome, $E$ is the least likely
-to happen, i.e., $\mu\left(\emptyset\right)=0$. When $E$ contains
-all outcomes, $E$ is the most likely to happen, i.e., $\mu\left(\Omega\right)=1$.
-If we know the likelihood of an event, $\mu\left(E\right)$, it is
-natural to assume the likelihood of the event’s complement is just
-the opposite of $\mu\left(E\right)$, i.e., $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$.
+Given a finite sample space~$\Omega$ representing all possible outcomes
+of a process, and its power set $2^{\Omega}$ as the classical event
+space, a classical probability measure~$\mu$ maps an event~$E$
+to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
+likely one of the outcome in $E$ actually happens. To maintain the
+coherence, we want $\mu$ subject to the following constraints. When
+$E$ contains no outcome, $E$ is the least likely to happen, i.e.,
+$\mu\left(\emptyset\right)=0$. When $E$ contains all outcomes, $E$
+is the most likely to happen, i.e., $\mu\left(\Omega\right)=1$. If
+we know the likelihood of an event, $\mu\left(E\right)$, it is natural
+to assume the likelihood of the event’s complement is just the opposite
+of $\mu\left(E\right)$, i.e., $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$.
 For each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$,
@@
 
-The previous abstraction
+Since the previous abstraction disregards the underlying process generating
+the outcomes, this process might be a quantum measurement. Let us
+prepare a beam of a kind of spin~$1$ particles. In principle, we
+can preform a Stern-Gerlach type experiment to splits the beam according
+to the eigenvalues of the observable $\mathbf{O}_{0}=0\,\proj{0}+1\,\proj{1}+2\,\proj{2}$
+\cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
+If we only send one particle instead of a beam, it could be in three
+possible states after the experiment, i.e., the outcome of this process
+is $\Omega_{0}=\left\{ \ket{0},\ket{1},\ket{2}\right\} $. All possible
+events are $\emptyset$, $\left\{ \ket{0}\right\} $, $\left\{ \ket{1}\right\} $,
+$\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
+$\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
+and $\Omega$. Given any particle, it specifies the likelihood of
+each event $\mu_{0}\left(E\right)$, and the function $\mu_{0}:2^{\Omega}\rightarrow\left[0,1\right]$
+is a probability measure satisfying the conditions listed in previous
+paragraph.
+
+The different of the quantum world is that the probability of previous
+experiment is correlated to the other experiment if we use the same
+particle, but change the beam splitter. Consider a beam splitter corresponding
+to the observable $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
+where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
+The outcome of this process is $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $.
+All possible events are $\emptyset$, $\left\{ \ket{\ps}\right\} $,
+$\left\{ \ket{\ms}\right\} $, $\left\{ \ket{2}\right\} $, $\left\{ \ket{\ps},\ket{\ms}\right\} $,
+$\left\{ \ket{\ps},\ket{2}\right\} $, $\left\{ \ket{\ms},\ket{2}\right\} $,
+and $\Omega_{1}$. When we can formulate the likelihood of each event
+as another probability measure $\mu_{1}:2^{\Omega}\rightarrow\left[0,1\right]$,
+we found the likelihood of the same event of these two experiments
+are the same if we use the same particle, i.e., $\mu_{0}\left(\emptyset\right)=\mu_{1}\left(\emptyset\right)$
+and $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
+
+Since the probability is always the same if the particle and the event
+are the same no matter which beam splitter is actually used. It is
+more natural to define the set of quantum event~$\events$ as all
+possible events using different beam splitters. Since we are focus
+on the probability instead of outcome, and the probabilities of events
+$\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
+are always the same, it is reasonable to identify them as the same
+event.
+
+, and consider the quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+as a function assigning the likelihood to every quantum event
 

### 2018-11-19 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

--- 2018-11-14 dissertation.tex
@@
 of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
-Given a finite sample space~$\Omega$ representing all possible outcomes,
-and its power set $2^{\Omega}$ as the classical event space, a classical
-probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
-specifying how likely one of the outcome in $E$ actually happens.
-To maintain the coherence, we want $\mu$ subject to the following
-constraints: $\mu\left(\emptyset\right)=0$, $\mu\left(\Omega\right)=1$,
-$\mu\left(\overline{E}\right)=1-\mu\left(E\right)$, and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
+Given a finite sample space~$\Omega$ representing all possible outcomes
+of a process, and its power set $2^{\Omega}$ as the classical event
+space, a classical probability measure~$\mu$ maps an event~$E$
+to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
+likely one of the outcome in $E$ actually happens. To maintain the
+coherence, we want $\mu$ subject to the following constraints: $\mu\left(\emptyset\right)=0$,
+$\mu\left(\Omega\right)=1$, $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
+and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
 for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
+
+Since the previous abstraction disregards the process generating the
+outcomes, this process might be a quantum experiment. Let us prepare
+a beam of one kind of spin~$1$ particles. In principle, we can preform
+a Stern-Gerlach type experiment to splits the beam according to the
+eigenvalues of the observable $\mathbf{O}_{0}=0\,\proj{0}+1\,\proj{1}+2\,\proj{2}$
+\cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
+If we only send one particle instead of a beam, the state after the
+experiment could be $\ket{0}$, $\ket{1}$, or $\ket{2}$. In another
+word, the outcome of this process is $\Omega_{0}=\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
+and all possible events are $\emptyset$, $\left\{ \ket{0}\right\} $,
+$\left\{ \ket{1}\right\} $, $\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
+$\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
+and $\Omega_{0}$. Sending any particular particle specifies the likelihood
+of each event $\mu_{0}\left(E\right)$, and the function $\mu_{0}:2^{\Omega}\rightarrow\left[0,1\right]$
+is a classical probability measure.
+
+One special feature of quantum experiments is that the probabilities
+in different experiments are correlated. Consider another experiment
+similar to the previous one. This experiment send exactly the same
+particle, but we use a beam splitter corresponding to the observable
+$\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$, where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$
+and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$. The outcome of
+this process is $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $,
+and all possible events are $\emptyset$, $\left\{ \ket{\ps}\right\} $,
+$\left\{ \ket{\ms}\right\} $, $\left\{ \ket{2}\right\} $, $\left\{ \ket{\ps},\ket{\ms}\right\} $,
+$\left\{ \ket{\ps},\ket{2}\right\} $, $\left\{ \ket{\ms},\ket{2}\right\} $,
+and $\Omega_{1}$. When we formulate the likelihood of each event
+as another probability measure $\mu_{1}:2^{\Omega}\rightarrow\left[0,1\right]$,
+the likelihood of the same event of these two experiments are experimentally
+found to be the same, i.e., $\mu_{0}\left(\emptyset\right)=\mu_{1}\left(\emptyset\right)$
+and $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
+In general, when the particle and the event are the same, so does
+their probability.
+
+Since the probability induced by the different beam splitters are
+correlated, it is more natural to define the set of quantum event~$\events$
+as all possible events using different beam splitters. Since we are
+focus on the probability instead of outcome, and the probabilities
+of events $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
+are always the same, it is reasonable to identify them as the same
+event.
+
+, and consider the quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+as a function assigning the likelihood to every quantum event
 

### 2018-11-20 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

--- 2018-11-18 dissertation.tex
@@
 of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
-Given a finite sample space~$\Omega$ representing all possible outcomes,
-and its power set $2^{\Omega}$ as the classical event space, a classical
-probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
-specifying how likely one of the outcome in $E$ actually happens.
-To maintain the coherence, we want $\mu$ subject to the following
-constraints. When $E$ contains no outcome, $E$ is the least likely
-to happen, i.e., $\mu\left(\emptyset\right)=0$. When $E$ contains
-all outcomes, $E$ is the most likely to happen, i.e., $\mu\left(\Omega\right)=1$.
-If we know the likelihood of an event, $\mu\left(E\right)$, it is
-natural to assume the likelihood of the event’s complement is just
-the opposite of $\mu\left(E\right)$, i.e., $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$.
-For each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$,
-the likelihood of the union event is additive, $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$.
-
-The previous abstraction
+Given a finite sample space~$\Omega$ representing all possible outcomes
+of a process, and its power set $2^{\Omega}$ as the classical event
+space, a classical probability measure~$\mu$ maps an event~$E$
+to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
+likely one of the outcome in $E$ actually happens. To maintain the
+coherence, $\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
+$\mu\left(\Omega\right)=1$, $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
+and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
+for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
+
+Since the previous abstraction doesn't specify how to generate the
+outcomes, the generating process could well be a quantum experiment.
+Let us prepare a beam of one kind of spin~$1$ particles with basis
+vectors $\ket{0}$, $\ket{1}$, and $\ket{2}$. In principle, this
+beam can be split by a Stern-Gerlach type experiment according to
+the eigenvalues of the observable $\mathbf{O}_{0}=0\,\proj{0}+1\,\proj{1}+2\,\proj{2}$,
+and the states corresponding to the split beam are $\ket{0}$, $\ket{1}$,
+and $\ket{2}$ \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
+Instead of a beam, if only one particle is sent to the beam splitter,
+the state after the experiment is one of $\ket{0}$, $\ket{1}$, and
+$\ket{2}$, and each state has a probability. In the language of our
+previous abstraction, the set of outcomes is $\Omega_{0}=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+All possible events are $\emptyset$, $\left\{ \ket{0}\right\} $,
+$\left\{ \ket{1}\right\} $, $\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
+$\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
+and $\Omega_{0}$. This experiment defines a classical probability
+measure $\mu_{0}:2^{\Omega_{0}}\rightarrow\left[0,1\right]$.
+
+One special feature of quantum experiments is that the probabilities
+in different experiments are correlated. Consider another experiment
+similar to the previous one. While this experiment send exactly the
+same particle, we use a beam splitter corresponding to the observable
+$\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$, where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$
+and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$. The outcome of
+this experiment is $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $,
+and it defines another probability measure $\mu_{1}:2^{\Omega_{1}}\rightarrow\left[0,1\right]$.
+Although $\mu_{0}$ and $\mu_{1}$ are different probability measures,
+the probability of the same event are experimentally found to be the
+same, i.e., $\mu_{0}\left(\emptyset\right)=\mu_{1}\left(\emptyset\right)$
+and $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
+In general, when the particle and the event are the same, so does
+their probability no matter how we set up the beam splitters.
+
+Since the probability induced by the different beam splitters are
+correlated, it is more natural to define the set of quantum event~$\events$
+as the union of all possible event spaces using different beam splitters.
+Since we are focus on the probability instead of outcome, and the
+probabilities of events $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
+are always the same, it is reasonable to identify them as the same
+event. To simplify the notation, given any classical event $E\subseteq\Omega$,
+its corresponding quantum event is defined by 
+\begin{equation}
+\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\,.\label{eq:pullback-function}
+\end{equation}
+Following this definition, it is easy to check that not only 
+\begin{equation}
+\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)
+\end{equation}
+but every classical event mapping the same projector must also have
+the same probability. If we follow the convention $\varphi\left(\emptyset\right)=\mathbb{0}$,
+this function $\varphi$ naturally sends the set operations to the
+corresponding projector operations: $\varphi\left(\Omega\right)=\mathbb{1}$,
+$\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
+For each pair of set $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$,
+\begin{align}
+\varphi\left(E_{0}\cap E_{1}\right) & =\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,, & \varphi\left(E_{0}\cup E_{1}\right) & =\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,.\label{eq:pullback-properties}
+\end{align}
+If $E_{0}$ and $E_{1}$ are disjoint, then $\varphi\left(E_{0}\right)$
+and $\varphi\left(E_{1}\right)$ are orthogonal, where two projectors
+$P_{0}$ and $P_{1}$ are called \emph{orthogonal} if $P_{0}P_{1}=\mathbb{0}$.
+
+, and consider the quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+as a function assigning the likelihood to every quantum event
 
@@
 we define the function $\varphi:2^{\Omega}\rightarrow\events$ maps
-any set~$E$ to the sum of the projectors formed by elements in $E$,
-i.e., 
-\begin{equation}
-\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\,.\label{eq:pullback-function}
-\end{equation}
-If we follow the convention $\varphi\left(\emptyset\right)=\mathbb{0}$,
-this function $\varphi$ naturally sends the set operations to the
-corresponding projector operations: $\varphi\left(\Omega\right)=\mathbb{1}$,
-$\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$,
-and
-\begin{align}
-\varphi\left(E_{0}\cap E_{1}\right) & =\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,, & \varphi\left(E_{0}\cup E_{1}\right) & =\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\label{eq:pullback-properties}
-\end{align}
-for each pair of set $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
-Therefore, given a QIVPM~$\bar{\mu}$, the function $\varphi^{*}\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+any set~$E$ to the sum of the projectors formed by elements in $E$
+as in Eq.~(\ref{eq:pullback-function}). \todo{Review this part
+because Eq.~(\ref{eq:pullback-function}) is moved to Sec.~\ref{sec:fuzzy}.
+}Therefore, given a QIVPM~$\bar{\mu}$, the function $\varphi^{*}\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
 defined by precomposition $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$

### 2018-11-20 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 coherence, $\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
-$\mu\left(\Omega\right)=1$, $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
-and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
+$\mu\left(\Omega\right)=1$, and $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
+where $\overline{E}$ is the complement of $E$.  Moreover, $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
 for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
 
-Since the previous abstraction doesn't specify how to generate the
-outcomes, the generating process could well be a quantum experiment.
-Let us prepare a beam of one kind of spin~$1$ particles with basis
-vectors $\ket{0}$, $\ket{1}$, and $\ket{2}$. In principle, this
-beam can be split by a Stern-Gerlach type experiment according to
-the eigenvalues of the observable $\mathbf{O}_{0}=0\,\proj{0}+1\,\proj{1}+2\,\proj{2}$,
-and the states corresponding to the split beam are $\ket{0}$, $\ket{1}$,
+Since the previous abstraction doesn't specify the process to generate
+the outcomes, this process could well be a quantum experiment. Let
+us prepare a beam of one kind of spin~$1$ particles with basis vectors
+$\ket{0}$, $\ket{1}$, and $\ket{2}$. In principle, this beam can
+be split by a Stern-Gerlach type experiment according to the eigenvalues
+of the observable $\mathbf{O}_{0}=0\,\proj{0}+1\,\proj{1}+2\,\proj{2}$,
+and the states corresponding to the split beams are $\ket{0}$, $\ket{1}$,
 and $\ket{2}$ \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
-Instead of a beam, if only one particle is sent to the beam splitter,
-the state after the experiment is one of $\ket{0}$, $\ket{1}$, and
-$\ket{2}$, and each state has a probability. In the language of our
-previous abstraction, the set of outcomes is $\Omega_{0}=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-All possible events are $\emptyset$, $\left\{ \ket{0}\right\} $,
-$\left\{ \ket{1}\right\} $, $\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
+Instead of sending a beam, if only one particle is sent to the beam
+splitter, the state after the experiment is one of $\ket{0}$, $\ket{1}$,
+and $\ket{2}$, and there is a probability for each post-experimental
+state. In the language of our abstraction, the set of outcomes is
+$\Omega_{0}=\left\{ \ket{0},\ket{1},\ket{2}\right\} $. All possible
+events are $\emptyset$, $\left\{ \ket{0}\right\} $, $\left\{ \ket{1}\right\} $,
+$\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
 $\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
-and $\Omega_{0}$. This experiment defines a classical probability
+and $\Omega_{0}$. And this experiment defines a classical probability
 measure $\mu_{0}:2^{\Omega_{0}}\rightarrow\left[0,1\right]$.
@@
 in different experiments are correlated. Consider another experiment
-similar to the previous one. While this experiment send exactly the
-same particle, we use a beam splitter corresponding to the observable
-$\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$, where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$
-and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$. The outcome of
-this experiment is $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $,
-and it defines another probability measure $\mu_{1}:2^{\Omega_{1}}\rightarrow\left[0,1\right]$.
-Although $\mu_{0}$ and $\mu_{1}$ are different probability measures,
-the probability of the same event are experimentally found to be the
-same, i.e., $\mu_{0}\left(\emptyset\right)=\mu_{1}\left(\emptyset\right)$
+similar to the previous one. While sending exactly the same particle,
+we use a different beam splitter corresponding to the observable $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
+where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
+Now the sample space is $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $,
+and another probability measure $\mu_{1}:2^{\Omega_{1}}\rightarrow\left[0,1\right]$
+is defined. Although the sample spaces and the probability measures
+are different, these two experiments may produce the same outcome
+state. Moreover, the probability of the same event in different experiments
+are experimentally found to be the same, i.e., $\mu_{0}\left(\emptyset\right)=\mu_{1}\left(\emptyset\right)$
 and $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
-In general, when the particle and the event are the same, so does
-their probability no matter how we set up the beam splitters.
+In general, as long as sending the same particle, the probability
+of the same event in different experiments are always the same. This
+fact is equivalent to the fact that commuting observables could be
+measured simultaneous, and the latter fact is essential to define
+contextuality which will be explained later.
 
 Since the probability induced by the different beam splitters are
-correlated, it is more natural to define the set of quantum event~$\events$
-as the union of all possible event spaces using different beam splitters.
-Since we are focus on the probability instead of outcome, and the
-probabilities of events $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
-are always the same, it is reasonable to identify them as the same
-event. To simplify the notation, given any classical event $E\subseteq\Omega$,
-its corresponding quantum event is defined by 
-\begin{equation}
-\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\,.\label{eq:pullback-function}
-\end{equation}
-Following this definition, it is easy to check that not only 
-\begin{equation}
-\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)
-\end{equation}
-but every classical event mapping the same projector must also have
-the same probability. If we follow the convention $\varphi\left(\emptyset\right)=\mathbb{0}$,
-this function $\varphi$ naturally sends the set operations to the
-corresponding projector operations: $\varphi\left(\Omega\right)=\mathbb{1}$,
-$\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
-For each pair of set $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$,
+correlated, it is more natural to define the set of quantum events~$\events$
+as the union of all possible event spaces using different beam splitters
+on a given Hilbert space. Because we are focus on the probability
+instead of outcome, and the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
+and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, it
+is reasonable to identify them as the same event. By observing the
+projectors generated by these two events are the same
+\begin{equation}
+\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}\,,
+\end{equation}
+we define the projector generated by any classical event~$E$ as
+its quantum event 
+\begin{equation}
+\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events\,.\label{eq:pullback-function}
+\end{equation}
+If we follow the convention $\varphi\left(\emptyset\right)=\mathbb{0}$,
+not only the same projector must have the same probability, but this
+function $\varphi$ also naturally sends the set structure to the
+corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
+and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
+Given a sample space $\Omega$ and a pair of event $E_{0}\subseteq\Omega$
+and $E_{1}\subseteq\Omega$, their corresponding quantum events $\varphi\left(E_{0}\right)$
+and $\varphi\left(E_{1}\right)$ are commuting and vice versa, where
+two projectors $P_{0}$ and~$P_{1}$ are \emph{commuting} if $P_{0}P_{1}=P_{1}P_{0}$.
+Moreover, $E_{0}$ and $E_{1}$ also satisfy the following properties:
 \begin{align}
@@
 If $E_{0}$ and $E_{1}$ are disjoint, then $\varphi\left(E_{0}\right)$
-and $\varphi\left(E_{1}\right)$ are orthogonal, where two projectors
-$P_{0}$ and $P_{1}$ are called \emph{orthogonal} if $P_{0}P_{1}=\mathbb{0}$.
-
-, and consider the quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
-as a function assigning the likelihood to every quantum event
-
-In the quantum case, the events of interest are specified by \emph{projection
-operators} $P$ satisfying the condition $P^{2}=P$. These include
-the empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
-projectors of the form $\proj{\Phi}$ where $\ket{\Phi}$ is a pure
-quantum state (an element of a Hilbert space $\mathcal{H}$), sums
-of \emph{orthogonal} projectors~$P_{0}$ and~$P_{1}$ with $P_{0}P_{1}=\mathbb{0}$,
-and products of \emph{commuting} projectors $P_{0}$ and~$P_{1}$
-with $P_{0}P_{1}=P_{1}P_{0}$. In a quantum probability space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
-the set of all events is the set of all projectors on a given Hilbert
-space denoted by $\events$. \todo{Use the same idea as the classical
-probability measure to explain the meaning of $\mu\left(P\right)$.
-Maybe move the structure preserving function $\varphi:2^{\Omega}\rightarrow\events$
-defined in Eq.~\ref{eq:pullback-function} here.} each event~$P_{i}$
-is mapped to a probability~$\mu\left(P_{i}\right)$ using a probability
-measure $\mu:\events\rightarrow\left[0,1\right]$ subject to the following
-constraints:
+and $\varphi\left(E_{1}\right)$ are orthogonal and vice versa, where
+two projectors $P_{0}$ and $P_{1}$ are called \emph{orthogonal}
+if $P_{0}P_{1}=\mathbb{0}$.
+
+After we define the set of all events~$\events$ as the set of all
+projectors on a given Hilbert space, a quantum probability space can
+be defined by $\events$ together with a probability measure $\mu:\events\rightarrow\left[0,1\right]$
+subject to the following constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
 \begin{align}
@@
 
-\todo{Rewrite the beginng of this paragraph to explain the meaning
+\todo{Rewrite the beginning of this paragraph to explain the meaning
 of the Born rule... Maybe move Gleason's Theorem here?} A conventional

### 2018-11-20 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 
+\subsection{Classical and Quantum Probability Spaces}
+
 A \emph{probability space} is a mathematical abstraction specifying
@@
 $\mu\left(\Omega\right)=1$, and $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
-where $\overline{E}$ is the complement of $E$.  Moreover, $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
+where $\overline{E}$ is the complement of $E$.  Moreover, we require
+$\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
 for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
@@
 are different, these two experiments may produce the same outcome
-state. Moreover, the probability of the same event in different experiments
-are experimentally found to be the same, i.e., $\mu_{0}\left(\emptyset\right)=\mu_{1}\left(\emptyset\right)$
-and $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
+state~$\ket{2}$, and the probability of the common event $\left\{ \ket{2}\right\} $
+is experimentally found to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
 In general, as long as sending the same particle, the probability
@@
 fact is equivalent to the fact that commuting observables could be
-measured simultaneous, and the latter fact is essential to define
+measured simultaneously, and the latter fact is essential to define
 contextuality which will be explained later.
@@
 correlated, it is more natural to define the set of quantum events~$\events$
-as the union of all possible event spaces using different beam splitters
-on a given Hilbert space. Because we are focus on the probability
-instead of outcome, and the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
-and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, it
-is reasonable to identify them as the same event. By observing the
-projectors generated by these two events are the same
+as the union of all possible event spaces using different beam splitters.
+Because we are focus on the probability instead of outcome, and the
+probabilities of events $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
+are always the same, it is reasonable to identify them as the same
+event. By observing the projectors generated by these two events are
+the same
 \begin{equation}
@@
 If we follow the convention $\varphi\left(\emptyset\right)=\mathbb{0}$,
-not only the same projector must have the same probability, but this
-function $\varphi$ also naturally sends the set structure to the
-corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
+not only the events mapping to the same projector must have the same
+probability, but this function $\varphi$ also naturally sends the
+set structure to the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
 and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
@@
 two projectors $P_{0}$ and~$P_{1}$ are \emph{commuting} if $P_{0}P_{1}=P_{1}P_{0}$.
-Moreover, $E_{0}$ and $E_{1}$ also satisfy the following properties:
+Moreover, the events $E_{0}$ and $E_{1}$ in the same sample space
+also satisfy the following properties: 
 \begin{align}
@@
 
-After we define the set of all events~$\events$ as the set of all
-projectors on a given Hilbert space, a quantum probability space can
-be defined by $\events$ together with a probability measure $\mu:\events\rightarrow\left[0,1\right]$
-subject to the following constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
+After we define the set of all quantum events~$\events$ as the set
+of all projectors on a given Hilbert space, a quantum probability
+space can be defined by $\events$ together with a quantum probability
+measure $\mu:\events\rightarrow\left[0,1\right]$ subject to the corresponding
+constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
 \begin{align}
@@
 \end{align}
-and for each pair of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
+and for each pair of orthogonal projectors $P_{0}$ and $P_{1}$:
 \begin{equation}
@@
 \end{equation}
+By defining in this way, given any orthonormal basis~$\Omega$, the
+restricted function $\varphi:2^{\Omega}\rightarrow\events$ can pull
+$\mu$ back to a classical probability measure $\varphi^{*}\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+by precomposition $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$.
+
 Given a Hilbert space $\mathcal{H}$ of dimension $D$ and a probability
@@
 where the subscript $\mu$ might be omitted if it is clear according
-to the context.
+to the context. This definition is also consistent with the classical
+expectation values because we can pullback an observable to a classical
+random variable, and the expectation values are invariant.
+
+\begin{definition}[Pullback of Observables]\label{def:observable2random-variable}Consider
+an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
+$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ so that
+$\mathbf{O}$ has spectral decomposition $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\proj{i}$.
+If we restrict $\varphi$ on the classical event space~$2^{\Omega}$
+and consider $\varphi:2^{\Omega}\rightarrow\events$, then the pullback
+of $\mathbf{O}$ by $\varphi$ is a random variable $\varphi^{*}\mathbf{O}:\Omega\rightarrow\mathbb{R}$
+defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$.\end{definition}
+
+\begin{lemma}\label{lemma:real-expectation-value-between-classical-quantum}Consider
+an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
+$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with $\varphi:2^{\Omega}\rightarrow\events$
+defined by Eq.~(\ref{eq:pullback-function}). Given a quantum probability
+measure $\mu:\events\rightarrow\left[0,1\right]$, the expectation
+value of $\mathbf{O}$ relative to $\mu$ is exactly the expectation
+value of the pullback of $\mathbf{O}$ relative to the pullback of
+$\mu$, i.e., 
+\begin{equation}
+\expval{\mathbf{O}}_{\mu}=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)\,.\label{eq:real-expectation-value-between-classical-quantum}
+\end{equation}
+\end{lemma}
+
+\begin{proof}By Eq.~(\ref{eq:quantum-expectation}), we have
+\[
+\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\proj{i}\right)=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\varphi\left(\left\{ \ket{i}\right\} \right)\right)=\sum_{i=0}^{D-1}\lambda_{i}\left(\varphi^{*}\mu\right)\left(\left\{ \ket{i}\right\} \right)=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)\,.
+\]
+\end{proof}
+
+\subsection{The Born Rule and Gleason's Theorem\label{subsec:Gleason's-Theorem-and}}
 
@@
 \end{table}
-
-\subsection{Gleason's Theorem and the properties of the Born rule\label{subsec:Gleason's-Theorem-and}}
-
 \todo{Make the meaning of Gleason's Theorem more clear? So that we
@@
 
-\subsection{Issues about Measurements and Contextuality}
+\subsection{The Kochen-Specker Theorem and Contextuality}
 
@@
 is the pullback of $\bar{\mu}$ by $\varphi$, and is a classical
-IVPM naturally. Moreover, if $\mu:\events\rightarrow\left[0,1\right]$
-is a quantum probability measure satisfying Eqs.~(\ref{eq:QuantumProbability})
-and (\ref{eq:QuantumProbability-Addition}), the pullback of $\mu$,
-$\varphi^{*}\mu:2^{\Omega}\rightarrow\left[0,1\right]$, can also
-be defined by precomposition $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$,
-and is a classical probability measure as well.
+IVPM naturally.
 
@@
 the one relative to a classical IVPM by proving a quantum version
-of Thm.~\ref{thm:Rosenmuller}. Although we previously only pull
-back probability measures, this time we also need to pull back observables.
-
-\begin{definition}[Pullback of Observables]\label{def:observable2random-variable}Consider
-an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
-$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ so that
-$\mathbf{O}$ has spectral decomposition $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\proj{i}$.
-If we follow Eq.~(\ref{eq:pullback-function}) to define $\varphi:2^{\Omega}\rightarrow\events$,
-then the pullback of $\mathbf{O}$ by $\varphi$ is a random variable
-$\varphi^{*}\mathbf{O}:\Omega\rightarrow\mathbb{R}$ defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$.\end{definition}
-
-While both observables and probability measures can be pulled back
-from quantum to classical, these pullbacks keep the expectation value
-invariant.
+of Thm.~\ref{thm:Rosenmuller}. \todo{Review this part because Def.~\ref{def:observable2random-variable}
+is moved to Sec.~\ref{sec:fuzzy}. }While both observables and IVPMs
+can be pulled back from quantum to classical, these pullbacks keep
+the expectation value invariant.
 
@@
 $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with $\varphi:2^{\Omega}\rightarrow\events$
-defined by Eq.~(\ref{eq:pullback-function}).
-\begin{itemize}
-\item Given a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$,
-the expectation value of $\mathbf{O}$ relative to $\mu$ is exactly
-the expectation value of the pullback of $\mathbf{O}$ relative to
-the pullback of $\mu$, i.e., 
-\begin{equation}
-\expval{\mathbf{O}}_{\mu}=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)\,.\label{eq:real-expectation-value-between-classical-quantum}
-\end{equation}
-\item Given a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, the expectation
-value of $\mathbf{O}$ relative to $\bar{\mu}$ is exactly the expectation
-value of the pullback of $\mathbf{O}$ relative to the pullback of
-$\bar{\mu}$, i.e., 
+defined by Eq.~(\ref{eq:pullback-function}). Given a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$,
+the expectation value of $\mathbf{O}$ relative to $\bar{\mu}$ is
+exactly the expectation value of the pullback of $\mathbf{O}$ relative
+to the pullback of $\bar{\mu}$, i.e., 
 \begin{equation}
@@
 \end{equation}
-\end{itemize}
 \end{lemma}
 
-\begin{proof}[Proof of Eq.~(\ref{eq:real-expectation-value-between-classical-quantum})]By
-Eq.~(\ref{eq:quantum-expectation}), we have
-\[
-\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\proj{i}\right)=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\varphi\left(\left\{ \ket{i}\right\} \right)\right)=\sum_{i=0}^{D-1}\lambda_{i}\left(\varphi^{*}\mu\right)\left(\left\{ \ket{i}\right\} \right)=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)\,.
-\]
-\end{proof}
-
-\begin{proof}[Proof of Eq.~(\ref{eq:interval-expectation-value-between-classical-quantum})]Consider
-to express the observable~$\mathbf{O}$ in the spectral decomposition
-specialized to compute the expectation value relative to a QIVPM,
-$\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}$,
+\begin{proof}Consider to express the observable~$\mathbf{O}$ in
+the spectral decomposition specialized to compute the expectation
+value relative to a QIVPM, $\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}$,
 where $\lambda_{N^{-}}^{-}<\cdots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\cdots<\lambda_{N^{+}}^{+}$

### 2018-11-21 dissertation.tex
dissertation.lyx "2.2.1 Classical and Quantum Probability Spaces" Updating...

@@
 state~$\ket{2}$, and the probability of the common event $\left\{ \ket{2}\right\} $
-is experimentally found to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
+is believed to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
 In general, as long as sending the same particle, the probability
@@
 Since the probability induced by the different beam splitters are
-correlated, it is more natural to define the set of quantum events~$\events$
+correlated, it is more natural to define one quantum event space~$\events$
+containing all possible event spaces using different beam splitters.
+However, a simple union of all event spaces will contain duplicate
+information. For example, if we take the complement on the both sides
+of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
+we will have
+\begin{equation}
+\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
+\end{equation}
+that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
+and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same as
+well. To simplify our discussion, it might be desirable to identify
+two classical events $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
+as one quantum event. Fortunately, the projectors generated by these
+two events are the same, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$.
+Thus, given a classical event~$E$, we may define its corresponding
+quantum event $\varphi\left(E\right)$ as the projector generated
+by $E$,
+\begin{equation}
+\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
+\end{equation}
+with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$. Then,
+a quantum event space $\events$is the set of all projectors on a
+given Hilbert space.
+
+It is easy to check that defining quantum
+
+we not only want to consider all possible events with different beam
+splitters as a whole, but also want to
+
+Because the projectors generated by these two events are the same,
+i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$,
+
+if we want to consider all possible events with different beam splitters
+as a whole, it might be easier to define a quantum
+
+we could simplify our discussion by mapping a classical event~$E$
+
+To simplify our discussion on quantum probability, it would be better
+to identify $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
+as the same event. Fortunately, the projectors generated by these
+two events are the same, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$.
+So does
+
+Because we are focus on the probability instead of outcome,
+
+Since the probability induced by the different beam splitters are
+correlated, it is more natural to define the set of quantum events
 as the union of all possible event spaces using different beam splitters.
-Because we are focus on the probability instead of outcome, and the
-probabilities of events $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
-are always the same, it is reasonable to identify them as the same
-event. By observing the projectors generated by these two events are
-the same
-\begin{equation}
-\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}\,,
-\end{equation}
+Because we are focus on the probability instead of outcome, and ,
+it is reasonable to identify them as the same event. By observing
+the projectors generated by these two events are the same, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$,
 we define the projector generated by any classical event~$E$ as
 its quantum event
-\begin{equation}
-\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events\,.\label{eq:pullback-function}
-\end{equation}
-If we follow the convention $\varphi\left(\emptyset\right)=\mathbb{0}$,
-not only the events mapping to the same projector must have the same
-probability, but this function $\varphi$ also naturally sends the
-set structure to the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
-and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
+
+It is easy to verify that , not only the events mapping to the same
+projector must have the same probability, but this function $\varphi$
+also naturally sends the set structure to the corresponding projector
+structure: $\varphi\left(\Omega\right)=\mathbb{1}$ and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
 Given a sample space $\Omega$ and a pair of event $E_{0}\subseteq\Omega$

### 2018-11-21 dissertation.tex
dissertation.lyx "2.2.1 Classical and Quantum Probability Spaces" Updating...

--- 2018-11-20 dissertation.tex
@@
 \newtheorem{example}{Example}[chapter]
+\newtheorem{postulate}{Postulate}[chapter]
 
@@
 where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
-Now the sample space is $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $,
-and another probability measure $\mu_{1}:2^{\Omega_{1}}\rightarrow\left[0,1\right]$
-is defined. Although the sample spaces and the probability measures
-are different, these two experiments may produce the same outcome
-state~$\ket{2}$, and the probability of the common event $\left\{ \ket{2}\right\} $
-is experimentally found to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
-In general, as long as sending the same particle, the probability
-of the same event in different experiments are always the same. This
-fact is equivalent to the fact that commuting observables could be
-measured simultaneously, and the latter fact is essential to define
-contextuality which will be explained later.
+Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
+and the probability measure $\mu_{1}:2^{\Omega_{1}}\rightarrow\left[0,1\right]$
+defined by this experiment is different from the previous one, these
+two experiments may produce the same post-experimental state~$\ket{2}$,
+and the probability of the common event $\left\{ \ket{2}\right\} $
+is believed to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
+The general situation can be summarized as the following postulate.
+
+\begin{postulate}Given two quantum experiments, their post-experimental
+states are two orthonormal bases, and $E$ is a event for both of
+the experiments. Assume we send the same particle into these two experiments,
+then the probability of $E$ in these two experiments are the same.\end{postulate}
+
+\noindent This postulate is actually equivalent to the fact that commuting
+observables could be measured simultaneously. The latter fact is essential
+to define contextuality which will be explained later.
 
 Since the probability induced by the different beam splitters are
-correlated, it is more natural to define the set of quantum events~$\events$
-as the union of all possible event spaces using different beam splitters.
-Because we are focus on the probability instead of outcome, and the
-probabilities of events $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
-are always the same, it is reasonable to identify them as the same
-event. By observing the projectors generated by these two events are
-the same
-\begin{equation}
-\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}\,,
-\end{equation}
-we define the projector generated by any classical event~$E$ as
-its quantum event 
-\begin{equation}
-\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events\,.\label{eq:pullback-function}
-\end{equation}
-If we follow the convention $\varphi\left(\emptyset\right)=\mathbb{0}$,
-not only the events mapping to the same projector must have the same
-probability, but this function $\varphi$ also naturally sends the
-set structure to the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
+correlated, it is more natural to define one quantum event space~$\events$
+containing all possible classical event spaces using different beam
+splitters. However, simply taking the union of all event spaces is
+bad because two events might appear different but representing the
+same situation. For example, if we take the complement on the both
+sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
+we will have
+\begin{equation}
+\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
+\end{equation}
+that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
+and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same. To
+simplify our discussion, we want to identify two classical events
+$\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
+as the same quantum event. Since the projectors generated by these
+two events are equal as operators, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$,
+given any classical event~$E$, we can follow the same idea to define
+the quantum event corresponding to $E$ as the projector generated
+by $E$
+\begin{equation}
+\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
+\end{equation}
+with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, and
+a quantum event space~$\events$ is the set of all projectors on
+a given Hilbert space. This definition is really capture our intuition
+because of the following lemma.
+
+\begin{lemma}Given two quantum experiments, their post-experimental
+states are two orthonormal bases $\Omega$ and $\Omega'$, and $E\subseteq\Omega$
+and $E'\subseteq\Omega'$ are two events with $\varphi\left(E\right)=\varphi\left(E'\right)$.
+Assume we send the same particle into these two experiments, then
+the probability of $E$ is the same as the probability of $E'$.\end{lemma}
+
+\begin{proof}This lemma is obvious if we consider the third orthonormal
+bases $\Omega''=E\cup\left(\Omega'\backslash E'\right)$ and induction
+on the basis vectors.\end{proof}
+
+\noindent Moreover, this function $\varphi$ also naturally sends
+the set structure to the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
 and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.

### 2018-11-21 dissertation.tex
dissertation.lyx "Chapter 2 Conventional Quantum Theory" Updating...

@@
 a Hilbert space of dimension~$D$, 
-\item \label{enu:probability-amplitude}the normalized $D$ complex probability
-amplitude coefficients describing the contribution of each basis vector, 
+\item \label{enu:probability-amplitude}$D$ complex probability amplitude
+coefficients describing the contribution of each basis vector, 
 \item \label{enu:unitary-matrix}a set of probability-conserving unitary
@@
 \end{enumerate}
-In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the discrete geometric
-issues raised by the properties \ref{enu:-orthonormal-basis} and
-\ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:fuzzy},
-we introduce the important issues of \ref{enu:measurement-framework}
-and the foundations of quantum probability space. The observables
-and expectation values defined in Sec.~\ref{sec:fuzzy} will be used
-to understand the geometry of entangled states in Sec.~\ref{sec:The-geometry-of}.
-The property~\ref{enu:unitary-matrix} directly related to quantum
-circuit will be introduced later in Chapter~\ref{chap:DQT=000026DQC}
+In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the geometric issues
+raised by the properties \ref{enu:-orthonormal-basis} and \ref{enu:probability-amplitude}
+given above for CQT. In Sec.~\ref{sec:fuzzy}, we introduce the important
+issues of \ref{enu:measurement-framework} and the foundations of
+quantum probability space. The observables and expectation values
+defined in Sec.~\ref{sec:fuzzy} will be used to understand the geometry
+of entangled states in Sec.~\ref{sec:The-geometry-of}. The property~\ref{enu:unitary-matrix}
+directly related to quantum circuit will be introduced later in Chapter~\ref{chap:DQT=000026DQC}
 when we dive into quantum algorithms.
@@
 in general as Hilbert space vectors with an Hermitian inner product:
-\begin{eqnarray}
-\ket{\Psi} & = & \sum_{i=0}^{D-1}\alpha_{i}\ket{i}\,.
-\end{eqnarray}
+\begin{equation}
+\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}\,.
+\end{equation}
 Here $\alpha_{i}\in\mathComplex$ are complex probability amplitudes,
@@
 can be projected onto another state $\ket{\Psi}$ by writing 
-\begin{eqnarray}
-\braket{\Phi}{\Psi} & = & \sum_{i=0}^{D-1}\beta_{i}^{*}\alpha_{i}\,,
-\end{eqnarray}
+\begin{equation}
+\braket{\Phi}{\Psi}=\sum_{i=0}^{D-1}\beta_{i}^{*}\alpha_{i}\,,
+\end{equation}
 thus quantifying the proximity of the two states. (Here $^{*}$ denotes
@@
 \begin{eqnarray}
-X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
-Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{eq:HopfFibration}\\
-Z & = & \left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
+ &  & X=2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
+ &  & Y=2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{eq:HopfFibration}\\
+ &  & Z=\left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
 \end{eqnarray}
@@
 
+After introducing quantum probability measures, we might follow the
+convention to introduce the Born rule which is the only way to construct
+quantum probability measures in CQT. However, since the variants of
+quantum probability measures in Sec.~\ref{sec:Toward-IVPM} and Chapter~\ref{chap:QIVPM}
+could not be constructed by the Born rule easily, it is instructive
+to search for a Born rule here, and we will actually find the unique
+one.
+
+Although quantum probability measures constructed by gluing classical
+probability measures in the previous section looks complex, it could
+actually be constructed by operators according to Gleason's theorem.
+
+\begin{thm}[Gleason's theorem]\label{cor:Gleason's}In a Hilbert
+space $\Hilb$ of dimension $D\geq3$, given a quantum probability
+measure $\mu:\events\rightarrow\left[0,1\right]$, there exists a
+unique mixed state~$\rho$ such that $\mu\left(P\right)=\Tr\left(\rho P\right)$
+for any $D$-dimensional projector~$P$.\end{thm}
+
+\noindent In another word, when sending a particle to a Stern-Gerlach
+type experiment, we will get a quantum probability measure of the
+form $\Tr\left(\rho P\right)$ for some operator~$\rho$.
+
+Recall in Sec.~\ref{CQC1qubitBloch.sec}, the status of our system
+can be characterized by
+
 \todo{Rewrite the beginning of this paragraph to explain the meaning
@@
 according to Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-
-\begin{thm}[Gleason's theorem]\label{cor:Gleason's}In a Hilbert
-space $\Hilb$ of dimension $D\geq3$, given a quantum probability
-measure $\mu:\events\rightarrow\left[0,1\right]$, there exists a
-unique mixed state~$\rho$ such that $\mu=\muB_{\rho}$.\end{thm}
 

### 2018-11-22 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 given any classical event~$E$, we can follow the same idea to define
-the quantum event corresponding to $E$ as the projector generated
-by $E$
+its quantum event as the projector generated by $E$
 \begin{equation}
@@
 \end{equation}
-with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, and
-a quantum event space~$\events$ is the set of all projectors on
-a given Hilbert space. This definition is really capture our intuition
-because of the following lemma.
+with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$. This
+function $\varphi$ well glues all classical event spaces into one
+quantum event space~$\events$, the set of all projectors on a given
+Hilbert space, because of the following lemma.
 
@@
 
-\noindent In another word, when sending a particle to a Stern-Gerlach
-type experiment, we will get a quantum probability measure of the
-form $\Tr\left(\rho P\right)$ for some operator~$\rho$.
-
-Recall in Sec.~\ref{CQC1qubitBloch.sec}, the status of our system
-can be characterized by
+Although Gleason's theorem can correspond every quantum probability
+measure to a unique mixed state~$\rho$, it doesn't explain whether
+this state $\rho$ characterizing the state of particle sending to
+a Stern-Gerlach type experiment. For example, a variant of quantum
+probability measure has only one instance defined in Eq.~\ref{eq:QPMFF37}.
+This instance predicts all outcomes to be equally probable which intuitively
+corresponds to the mixed state $\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
+in its space. However, ignoring the input state and always predicting
+equally probable is not a sensible quantum theory.
+
+Let $\ket{\Phi}$ characterize the state of particle sending to a
+Stern-Gerlach type experiment, and $\muB_{\Phi}$ be the corresponding
+quantum probability measure of the resulting events.
+
+To find a sensible correspondences between quantum probability measures
+and the input states,
+
+\noindent , when sending a particle to a Stern-Gerlach type experiment,
+we will get a quantum probability measure of the form $\Tr\left(\rho P\right)$
+for some operator~$\rho$.
+
+Recall in Sec.~\ref{CQC1qubitBloch.sec}, the state of the particle
+can be characterized by a pure state $\ket{\Psi}\in\Hilb$ or more
+generally a mixed state~$\rho'$. Although the function $\Tr\left(\rho P\right)$
+is parametrized by
 
@@
 1 & \textrm{if }P=\mathbb{1}\,.
-\end{cases}
+\end{cases}\label{eq:QPMFF37}
 \end{equation}

### 2018-11-22 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 \newtheorem{case}{Case}
+\newtheorem{corollary}{Corollary}[chapter]
+
 \theoremstyle{definition}
@@
 fields in the quantum theory. The simplest theory, defined over unrestricted
-finite fields, is so weak that it cannot express Deutsch’s algorithm.
+finite fields, is so weak that it cannot express Deutsch's algorithm.
 This quantum theory is, however, also so powerful that it can be used
@@
 be split by a Stern-Gerlach type experiment according to the eigenvalues
-of the observable $\mathbf{O}_{0}=0\,\proj{0}+1\,\proj{1}+2\,\proj{2}$,
+of the observable $\mathbf{O}_{0}$ with with spectral decomposition
+\begin{equation}
+\mathbf{O}_{0}=0\,\proj{0}+1\,\proj{1}+2\,\proj{2}\,,\label{eq:observable}
+\end{equation}
 and the states corresponding to the split beams are $\ket{0}$, $\ket{1}$,
@@
 similar to the previous one. While sending exactly the same particle,
-we use a different beam splitter corresponding to the observable $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
-where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
+we use a different beam splitter corresponding to the observable $\mathbf{O}_{1}$
+with spectral decomposition $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
+where 
+\begin{align}
+\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}\,, &  & \ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.\label{eq:psms}
+\end{align}
 Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
@@
 
-\subsection{The Born Rule and Gleason's Theorem\label{subsec:Gleason's-Theorem-and}}
+\subsection{Gleason's Theorem and The Born Rule\label{subsec:Gleason's-Theorem-and}}
 
 After introducing quantum probability measures, we might follow the
-convention to introduce the Born rule which is the only way to construct
-quantum probability measures in CQT. However, since the variants of
-quantum probability measures in Sec.~\ref{sec:Toward-IVPM} and Chapter~\ref{chap:QIVPM}
-could not be constructed by the Born rule easily, it is instructive
-to search for a Born rule here, and we will actually find the unique
-one.
-
-Although quantum probability measures constructed by gluing classical
-probability measures in the previous section looks complex, it could
-actually be constructed by operators according to Gleason's theorem.
+convention to introduce the Born rule which is the only way corresponding
+a state to construct quantum probability measures in CQT. However,
+since the variants of quantum probability measures in Sec.~\ref{sec:Toward-IVPM}
+and Chapter~\ref{chap:QIVPM} could not be constructed by the Born
+rule easily, it is instructive to search for a Born rule here, and
+we will actually find the unique one.
+
+Although quantum probability measures constructed by gluing together
+the classical ones looks complex, they could all be induced by operators
+according to Gleason's theorem.
 
@@
 this state $\rho$ characterizing the state of particle sending to
-a Stern-Gerlach type experiment. For example, a variant of quantum
-probability measure has only one instance defined in Eq.~\ref{eq:QPMFF37}.
-This instance predicts all outcomes to be equally probable which intuitively
-corresponds to the mixed state $\frac{1}{3}\proj{0}+\frac{1}{3}\proj{1}+\frac{1}{3}\proj{2}$
-in its space. However, ignoring the input state and always predicting
-equally probable is not a sensible quantum theory.
-
-Let $\ket{\Phi}$ characterize the state of particle sending to a
-Stern-Gerlach type experiment, and $\muB_{\Phi}$ be the corresponding
-quantum probability measure of the resulting events.
-
-To find a sensible correspondences between quantum probability measures
-and the input states,
-
-\noindent , when sending a particle to a Stern-Gerlach type experiment,
-we will get a quantum probability measure of the form $\Tr\left(\rho P\right)$
-for some operator~$\rho$.
-
-Recall in Sec.~\ref{CQC1qubitBloch.sec}, the state of the particle
-can be characterized by a pure state $\ket{\Psi}\in\Hilb$ or more
-generally a mixed state~$\rho'$. Although the function $\Tr\left(\rho P\right)$
-is parametrized by
-
-\todo{Rewrite the beginning of this paragraph to explain the meaning
-of the Born rule... Maybe move Gleason's Theorem here?} A conventional
-quantum probability measure can easily be constructed using the Born
-rule if one knows the current pure unnormalized quantum state $\ket{\Phi}\in\mathcal{H}$;
-then the Born rule induces a probability measure $\muB_{\Phi}$ defined
-as 
-\begin{equation}
-\muB_{\Phi}(P)=\frac{\melem{\Phi}{P}{\Phi}}{\ip{\Phi}{\Phi}}\,.\label{eq:Born}
-\end{equation}
-If $\ket{\Phi}$ is normalized, Eq.~(\ref{eq:Born}) could be simplified
+a Stern-Gerlach type experiment. For example, in contrast with CQT,
+if a quantum theory always ignore the input state and predict the
+experimental outcomes are equally probable, even if this quantum theory
+maps every input state to a quantum probability measure, it is still
+not very sensible.
+
+Let a pure unnormalized state $\ket{\Phi}\in\mathcal{H}$ characterize
+the particle sending to a Stern-Gerlach type experiment, and $\muB_{\Phi}$
+be the corresponding quantum probability measure of the resulting
+events. To define a sensible correspondence, we hope that if the state~$\ket{\Phi}$
+is one of the outcome of a quantum event~$P$, i.e., $P\ket{\Phi}=\ket{\Phi}$,
+then the event~$P$ always happens, $\muB_{\Phi}\left(P\right)=1$
+and vice versa. Moreover, since the physical phenomena exists and
+should be the same no matter how we describe them, the probability
+of an event should be invariant despite how we choose the basis. Because
+changing to another basis is the same as applying an unitary map~$U$,
+we should have$\muF_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muF_{\Phi}\left(P\right)$.
+It is easy to check the correspondence satisfying the conditions in
+this paragraph is unique, 
+\begin{equation}
+\muB_{\Phi}(P)=\frac{\melem{\Phi}{P}{\Phi}}{\ip{\Phi}{\Phi}}\label{eq:Born}
+\end{equation}
+and called the Born rule \cite{Born1983,Mermin2007,Jaeger2007}. If
+$\ket{\Phi}$ is normalized, Eq.~(\ref{eq:Born}) could be simplified
 as $\muB_{\Phi}(P)=\melem{\Phi}{P}{\Phi}$. For mixed states $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$,
@@
 and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule induces a
-probability measure $\muB_{\rho}$ defined as \cite{Born1983,Mermin2007,Jaeger2007}
+probability measure $\muB_{\rho}$ defined as 
 \begin{equation}
@@
 basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $ and an observable
-$\mathbf{O}$ with spectral decomposition $\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
-i.e., the $i$th eigenvalue $\lambda_{i}=i$ and the $i$th eigenprojector
-$P_{i}=\proj{i-1}$. Two fragments of valid probability measures~$\mu_{1}$
-and $\mu_{2}$ that can be associated with this space are defined
-in Table~\ref{tab:quantum-probability-measure}. By the Born rule,
-the first probability measure corresponds to the quantum system being
-in the pure state $\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and the second
-corresponds to the quantum system being in the state $\frac{\proj{0}+\proj{2}}{2}$.
-The expectation values of the observable $\mathbf{O}$, $\expval{\mathbf{O}}_{\mu_{1,2}}$,
-are $1.5$ in the first case and $2$ in the second.
+$\mathbf{O}_{0}$ defined in Eq.~(\ref{eq:observable}). Two fragments
+of valid probability measures~$\mu_{1}$ and $\mu_{2}$ that can
+be associated with this space are defined in Table~\ref{tab:quantum-probability-measure}.
+By the Born rule, the first probability measure corresponds to the
+quantum system being in the pure state $\ket{\ps}$ defined in Eq.~(\ref{eq:psms})
+and the second corresponds to the quantum system being in the state
+$\frac{\proj{0}+\proj{2}}{2}$. The expectation values of the observable
+$\mathbf{O}$, $\expval{\mathbf{O}}_{\mu_{1,2}}$, are $1.5$ in the
+first case and $2$ in the second.
 \begin{table}
@@
 \end{table}
-\todo{Make the meaning of Gleason's Theorem more clear? So that we
-can explain the motivation of the question in Chapter~\ref{chap:Further-Discussion}.}
-A conventional quantum probability measure can be easily constructed
-from a state $\rho$ according to the Born rule; conversely, this
-is the only way to obtain a conventional quantum probability measure
-according to Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
-
-Although the Born rule is widely be considered a postulate of quantum
-theory, it could be derived from a smaller set of abstract definitions
-and axioms according to Gleason's theorem~\cite{peres1995quantum}.
-Since the Born rule linking the probability amplitudes and probability
-might not hold naively when probability amplitudes is in finite fields
-or the probability becomes an interval. Considering a Gleason-like
-theorem is an appealing method to search a rule computing probability
-in all these cases.
-
-Although Gleason's theorem associates every quantum probability measure~$\mu$
-to a mixed state~$\rho$, it is not obvious how to find $\rho$ for
-a given $\mu$. While hard in general, this task can be done easily
-if $\mu$ satisfies $\mu\left(P\right)=1$ for some projection~$P$
-when the dimension $D\geq3$. According to Gleason's theorem, there
-exists a unique mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$
-such that 
-\begin{equation}
-1=\mu\left(P\right)=\muB_{\rho}\left(P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)=\sum_{j=1}^{N}q_{j}\melem{\Phi_{j}}{P}{\Phi_{j}}\,.
-\end{equation}
-Together with the fact that $0\le\melem{\Phi_{j}}{P}{\Phi_{j}}\le1$,
-$q_{j}>0$, and $\sum_{j=1}^{N}q_{j}=1$, we must conclude that $\melem{\Phi_{j}}{P}{\Phi_{j}}=1$
-for all~$j$, and thus $P\ket{\Phi_{j}}=\ket{\Phi_{j}}$. Hence,
-\begin{equation}
-P\rho=\sum_{j=1}^{N}q_{j}P\proj{\Phi_{j}}=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}=\rho\,.
-\end{equation}
-Conversely, $P\rho=\rho$ also implies $\muB_{\rho}\left(P\right)=1$
-because the trace of any mixed state is $1$. The whole idea can then
-be summarized as the following proposition.
-
-\begin{prop}\label{prop:Born-probability-one}$\muB_{\rho}\left(P\right)=1$
-if and only if $P\rho=\rho$.\end{prop}
-
-The final property is that the Born rule is basis independent~\cite{peres1995quantum,544199}:
-\todo{Update the basis independent part with more details...}
-
-\begin{prop}\label{prop:Born-unitary-invariant}$\muB_{U\rho U^{\dagger}}\left(UPU^{\dagger}\right)=\muB_{\rho}\left(P\right)$,
-where $U$ is any unitary map.\end{prop}
-
-In Sec.~\ref{sec:Toward-IVPM}, we will use an analog of Gleason's
-theorem and these two properties to deduce that there is no “sensible”
-real-valued Born rule over finite fields.
 

### 2018-11-23 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 observables could be measured simultaneously. The latter fact is essential
-to define contextuality which will be explained later.
+to define contextuality which will be explained later in Sec.~\ref{sec:Kochen-Specker}.
 
@@
 $\mathbf{O}$, $\expval{\mathbf{O}}_{\mu_{1,2}}$, are $1.5$ in the
-first case and $2$ in the second.
+first case and $2$ in the second. The quantum expectation value can
+also used to decide whether a state is entangled or not for multipartite
+systems as we describe in the following section.
 \begin{table}
@@
 \end{table}
-
-\subsection{The Kochen-Specker Theorem and Contextuality}
-
-The quantum probability postulates assume a mathematical idealization
-in which quantum states and measurements are both infinitely precise,
-i.e., \textit{sharp}. In an actual experimental setup with an ensemble
-of quantum states that would ideally be identical, but are not actually
-identically prepared, with imperfections and inaccuracies in measuring
-devices, an experimenter might not be able to determine that the probability
-of an event $P$ is precisely $0.5$. To address this issue, we investigate
-the cardinal probability in Sec.~\ref{discretequantumtheoryIIb}
-and the interval-valued probability in Chapter~\ref{chap:QIVPM}.
-
-\todo{Add discussions about contextuality...}
-
-When $D=2$, there are some non-Born quantum probability measures.
-In particular, some non-Born quantum probability measures mapping
-every event to either $0$ or $1$. This kind of probability measure
-is called a non-contextual hidden variable model, and will be discussed
-in Sec.~\ref{sec:Quantum-Contextuality}.
-
-The quantum expectation value can also used to decide whether a state
-is entangled or not for multipartite systems as we describe in the
-following section.
 

### 2018-11-23 dissertation.tex
dissertation.lyx "Chapter 5 Further Discussion" Commented out...

@@
 will use a fixed collection of intervals appropriate for the resources
-and precision of the particular experiment.
-
-\chapter{Further Discussion\label{chap:Further-Discussion}}
-
-\todo{After updating Sec.~\ref{sec:fuzzy}, update this chapter
-by starting from the meaning of Gleason's Theorem.} Almost all QIVPMs
-in Chapter~\ref{chap:QIVPM} are closely related to quantum probability
-measures. For example, given a $\delta$-deterministic QIVPM, Lemma~\ref{lemma:delta2zero}
-provides a way to derive a $0$-deterministic QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
-which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
-satisfying $\mu\left(P\right)$ is either $0$ or $1$. Moreover,
-an interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$ in Sec.~\ref{sec:Gleason}
-provides an systemic way to derive QIVPMs from quantum probability
-measures.
-
-the only QIVPM unrelated to quantum probability measures is defined
-in Table~\ref{tab:non-Born-QIVPM}, and is ill-behaved as having
-an empty core.
-
-On one hand, classical IVPMs could be studied directly without deriving
-from or to classical probability measures.
-
-On the other hand, to state the original Gleason theorem, we don't
-need to know a state a priori, and use this state to derive a quantum
-probability measures and further a QIVPM. Therefore, it would be desirable
-if we could answer the following variant of Gleason theorem which
-
-whether shirking the maximum length of intervals alone could provide
-a well-behaved QIVPMs. More precisely, we have the following question.
-
-\begin{question}In a Hilbert space $\Hilb$ of dimension $D\geq3$,
-given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, $\alpha$
-be the maximum length of intervals in $\mathscr{I}$, is there an
-$\varepsilon\in\left(0,1\right)$ such that $\alpha<\varepsilon$
-implies $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
+and precision of the particular experiment.\todo{Update the further
+discussion chapter according to an updated Sec.~\ref{sec:fuzzy}.}
 

### 2018-11-23 dissertation.tex
dissertation.lyx "Chapter 2 Conventional Quantum Theory" Updating...

@@
 issues of \ref{enu:measurement-framework} and the foundations of
-quantum probability space. The observables and expectation values
-defined in Sec.~\ref{sec:fuzzy} will be used to understand the geometry
-of entangled states in Sec.~\ref{sec:The-geometry-of}. The property~\ref{enu:unitary-matrix}
-directly related to quantum circuit will be introduced later in Chapter~\ref{chap:DQT=000026DQC}
+quantum probability space. The expectation values defined in Sec.~\ref{sec:fuzzy}
+will be used to understand the geometry of entangled states in Sec.~\ref{sec:The-geometry-of}.
+The property~\ref{enu:unitary-matrix} directly related to quantum
+circuits will be introduced later in Chapter~\ref{chap:DQT=000026DQC}
 when we dive into quantum algorithms.
@@
 to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
-likely one of the outcome in $E$ actually happens. To maintain the
-coherence, $\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
+likely one of the outcome in $E$ will actually happen. To maintain
+the coherence, $\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
 $\mu\left(\Omega\right)=1$, and $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
@@
 the outcomes, this process could well be a quantum experiment. Let
-us prepare a beam of one kind of spin~$1$ particles with basis vectors
-$\ket{0}$, $\ket{1}$, and $\ket{2}$. In principle, this beam can
-be split by a Stern-Gerlach type experiment according to the eigenvalues
-of the observable $\mathbf{O}_{0}$ with with spectral decomposition
+us prepare a beam of one kind of spin~$1$ particles whose state
+can be characterized by a vector in three-dimensional Hilbert space
+with basis vectors $\ket{0}$, $\ket{1}$, and $\ket{2}$. In principle,
+this beam can be split by a Stern-Gerlach type experiment according
+to the eigenvalues of the observable $\mathbf{O}_{0}$ with spectral
+decomposition 
 \begin{equation}
@@
 and $\ket{2}$ \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
-Instead of sending a beam, if only one particle is sent to the beam
-splitter, the state after the experiment is one of $\ket{0}$, $\ket{1}$,
-and $\ket{2}$, and there is a probability for each post-experimental
-state. In the language of our abstraction, the set of outcomes is
-$\Omega_{0}=\left\{ \ket{0},\ket{1},\ket{2}\right\} $. All possible
-events are $\emptyset$, $\left\{ \ket{0}\right\} $, $\left\{ \ket{1}\right\} $,
-$\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
+Instead of sending a beam of particles, if only one particle is sent
+to the beam splitter, the state of the particle after the experiment
+is one of $\ket{0}$, $\ket{1}$, and $\ket{2}$, and there is a probability
+to get each post-experimental state. In the language of our abstraction,
+the set of outcomes is $\Omega_{0}=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+All possible events are $\emptyset$, $\left\{ \ket{0}\right\} $,
+$\left\{ \ket{1}\right\} $, $\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
 $\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
@@
 in different experiments are correlated. Consider another experiment
-similar to the previous one. While sending exactly the same particle,
-we use a different beam splitter corresponding to the observable $\mathbf{O}_{1}$
+sending exactly the same particle as the previous one, but using a
+different beam splitter corresponding to the observable $\mathbf{O}_{1}$
 with spectral decomposition $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
@@
 is believed to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
-The general situation can be summarized as the following postulate.
-
-\begin{postulate}Given two quantum experiments, their post-experimental
-states are two orthonormal bases, and $E$ is a event for both of
-the experiments. Assume we send the same particle into these two experiments,
-then the probability of $E$ in these two experiments are the same.\end{postulate}
-
-\noindent This postulate is actually equivalent to the fact that commuting
-observables could be measured simultaneously. The latter fact is essential
-to define contextuality which will be explained later in Sec.~\ref{sec:Kochen-Specker}.
+In general, as long as sending the same particle, the probability
+of the same event in different experiments should always be the same.
+This fact is equivalent to the fact that commuting observables could
+be measured simultaneously which is essential to define contextuality
+and will be explained in Sec.~\ref{sec:Kochen-Specker}.
 
@@
 splitters. However, simply taking the union of all event spaces is
-bad because two events might appear different but representing the
-same situation. For example, if we take the complement on the both
-sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
+a bad idea because two events might appear different but representing
+the same situation. For example, if we take the complement on the
+both sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
 we will have
@@
 that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
-and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same. To
-simplify our discussion, we want to identify two classical events
-$\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
-as the same quantum event. Since the projectors generated by these
-two events are equal as operators, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$,
-given any classical event~$E$, we can follow the same idea to define
-its quantum event as the projector generated by $E$
+and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
+should be identified as the same quantum event to simplify our discussion.
+Since the projectors generated by these two events are equal as operators,
+i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$, given any classical
+event~$E$, we can follow the same idea to define its quantum event
+as the projector generated by $E$
 \begin{equation}
@@
 quantum event space~$\events$, the set of all projectors on a given
-Hilbert space, because of the following lemma.
-
-\begin{lemma}Given two quantum experiments, their post-experimental
-states are two orthonormal bases $\Omega$ and $\Omega'$, and $E\subseteq\Omega$
-and $E'\subseteq\Omega'$ are two events with $\varphi\left(E\right)=\varphi\left(E'\right)$.
-Assume we send the same particle into these two experiments, then
-the probability of $E$ is the same as the probability of $E'$.\end{lemma}
-
-\begin{proof}This lemma is obvious if we consider the third orthonormal
-bases $\Omega''=E\cup\left(\Omega'\backslash E'\right)$ and induction
-on the basis vectors.\end{proof}
-
-\noindent Moreover, this function $\varphi$ also naturally sends
-the set structure to the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
+Hilbert space, because it is easy to inductively prove that if two
+classical events~$E$ and $E'$ corresponding to the same quantum
+event, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$, then
+the probability of $E$ is the same as the probability of $E'$.
+
+Moreover, this function $\varphi$ also naturally sends the set structure
+to the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
 and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.

### 2018-11-24 dissertation.tex
dissertation.lyx "2.2.1 Classical and Quantum Probability Spaces" Updating...

@@
 and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
-should be identified as the same quantum event to simplify our discussion.
-Since the projectors generated by these two events are equal as operators,
-i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$, given any classical
-event~$E$, we can follow the same idea to define its quantum event
-as the projector generated by $E$
+these events should be identified as the same quantum event to simplify
+our discussion. This can be achieved by mapping a classical event~$E$
+to the projector generated by $E$
 \begin{equation}
@@
 \end{equation}
-with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$. This
-function $\varphi$ well glues all classical event spaces into one
-quantum event space~$\events$, the set of all projectors on a given
-Hilbert space, because it is easy to inductively prove that if two
-classical events~$E$ and $E'$ corresponding to the same quantum
-event, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$, then
-the probability of $E$ is the same as the probability of $E'$.
+with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$ because
+\begin{equation}
+\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,.
+\end{equation}
+In general, if two classical events~$E$ and $E'$ mapped the same
+projector, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$,
+then the probability of $E$ is the same as the probability of $E'$.
+the function $\varphi$ well glues all classical event spaces into
+one quantum event space~$\events$.
 

### 2018-11-25 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 
-\subsection{Classical and Quantum Probability Spaces}
-
 A \emph{probability space} is a mathematical abstraction specifying
@@
 of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
+Although they can be used to describe an individual quantum experiment,
+to describe a family of quantum experiments, we would like to glue
+the corresponding family of classical probability space together to
+define a quantum probability space. The glued quantum probability
+space is well-behaved since not only we can define the expectation
+values, but the quantum probability measure define on the whole space
+can be simply induced by the Born rule according to Gleason's theorem
+\cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+
+\subsection{Classical and Quantum Probability Spaces}
+
 Given a finite sample space~$\Omega$ representing all possible outcomes
@@
 then the probability of $E$ is the same as the probability of $E'$.
-the function $\varphi$ well glues all classical event spaces into
-one quantum event space~$\events$.
-
-Moreover, this function $\varphi$ also naturally sends the set structure
-to the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
+Because of these good properties, the projector $\varphi\left(E\right)$
+is called the quantum event corresponding to $E$, and the set of
+all projectors on a given Hilbert space is called a quantum event
+space~$\events$.
+
+This function $\varphi$ also naturally sends the set structure to
+the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
 and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
-Given a sample space $\Omega$ and a pair of event $E_{0}\subseteq\Omega$
-and $E_{1}\subseteq\Omega$, their corresponding quantum events $\varphi\left(E_{0}\right)$
-and $\varphi\left(E_{1}\right)$ are commuting and vice versa, where
-two projectors $P_{0}$ and~$P_{1}$ are \emph{commuting} if $P_{0}P_{1}=P_{1}P_{0}$.
-Moreover, the events $E_{0}$ and $E_{1}$ in the same sample space
-also satisfy the following properties: 
+Given two \emph{commuting} projectors $P_{0}$ and~$P_{1}$, there
+exists a sample space $\Omega$ and a pair of event $E_{0}\subseteq\Omega$
+and $E_{1}\subseteq\Omega$ such that $P_{0}=\varphi\left(E_{0}\right)$
+and $P_{1}=\varphi\left(E_{1}\right)$. Conversely, given a pair of
+event $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$, their corresponding
+quantum events $\varphi\left(E_{0}\right)$ and $\varphi\left(E_{1}\right)$
+are commuting and satisfying the following properties: 
 \begin{align}
@@
 \end{align}
-If $E_{0}$ and $E_{1}$ are disjoint, then $\varphi\left(E_{0}\right)$
-and $\varphi\left(E_{1}\right)$ are orthogonal and vice versa, where
-two projectors $P_{0}$ and $P_{1}$ are called \emph{orthogonal}
-if $P_{0}P_{1}=\mathbb{0}$.
-
-After we define the set of all quantum events~$\events$ as the set
-of all projectors on a given Hilbert space, a quantum probability
-space can be defined by $\events$ together with a quantum probability
-measure $\mu:\events\rightarrow\left[0,1\right]$ subject to the corresponding
-constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
+Moreover, $E_{0}$ and $E_{1}$ are disjoint if and only if $\varphi\left(E_{0}\right)$
+and $\varphi\left(E_{1}\right)$ are orthogonal, where two projectors
+$P_{0}$ and $P_{1}$ are called \emph{orthogonal} if $P_{0}P_{1}=\mathbb{0}$.
+
+Then, a quantum probability space can be defined by a quantum event
+space~$\events$ together with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+subject to the corresponding constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
 \begin{align}

### 2018-11-25 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 to describe a family of quantum experiments, we would like to glue
-the corresponding family of classical probability space together to
-define a quantum probability space. The glued quantum probability
-space is well-behaved since not only we can define the expectation
-values, but the quantum probability measure define on the whole space
-can be simply induced by the Born rule according to Gleason's theorem
-\cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+their probability spaces together to define a quantum probability
+space. The glued quantum probability space is well-behaved since not
+only we can define the expectation values, but the quantum probability
+measure define on the whole space can be simply induced by the Born
+rule according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
 
@@
 to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
-likely one of the outcome in $E$ will actually happen. To maintain
+likely one of the outcomes in $E$ will actually happen. To maintain
 the coherence, $\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
@@
 with spectral decomposition $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
-where 
-\begin{align}
-\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}\,, &  & \ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.\label{eq:psms}
-\end{align}
+where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
 Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
@@
 \end{equation}
-In general, if two classical events~$E$ and $E'$ mapped the same
-projector, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$,
+In general, if two classical events~$E$ and $E'$ are mapped to
+the same projector, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$,
 then the probability of $E$ is the same as the probability of $E'$.
-Because of these good properties, the projector $\varphi\left(E\right)$
-is called the quantum event corresponding to $E$, and the set of
-all projectors on a given Hilbert space is called a quantum event
-space~$\events$.
-
-This function $\varphi$ also naturally sends the set structure to
-the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
-and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
+Therefore, for any classical event~$E$, its corresponding quantum
+event is defined to be the projector $\varphi\left(E\right)$, and
+the set of all projectors on a given Hilbert space is called a quantum
+event space~$\events$.
+
+This function $\varphi$ not only respects the probability of events
+but also naturally sends the set structure to the corresponding projector
+structure: $\varphi\left(\Omega\right)=\mathbb{1}$ and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
 Given two \emph{commuting} projectors $P_{0}$ and~$P_{1}$, there
-exists a sample space $\Omega$ and a pair of event $E_{0}\subseteq\Omega$
+exists a sample space $\Omega$ and a pair of events $E_{0}\subseteq\Omega$
 and $E_{1}\subseteq\Omega$ such that $P_{0}=\varphi\left(E_{0}\right)$
 and $P_{1}=\varphi\left(E_{1}\right)$. Conversely, given a pair of
-event $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$, their corresponding
-quantum events $\varphi\left(E_{0}\right)$ and $\varphi\left(E_{1}\right)$
-are commuting and satisfying the following properties: 
+events $E_{0}$ and $E_{1}$ in the same sample space~$\Omega$,
+their corresponding quantum events $\varphi\left(E_{0}\right)$ and
+$\varphi\left(E_{1}\right)$ are commuting and satisfying the following
+properties: 
 \begin{align}
@@
 \end{equation}
-By defining in this way, given any orthonormal basis~$\Omega$, the
-restricted function $\varphi:2^{\Omega}\rightarrow\events$ can pull
-$\mu$ back to a classical probability measure $\varphi^{*}\mu:2^{\Omega}\rightarrow\left[0,1\right]$
-by precomposition $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$.
+Because $\varphi$ respects the probability of events, if we restrict
+$\varphi$ on an event space $2^{\Omega}$, the function $\varphi^{*}\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+defined by precomposition $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$
+is a classical probability measure and called the pullback of $\mu$
+by $\varphi:2^{\Omega}\rightarrow\events$.
 
@@
 convention to introduce the Born rule which is the only way corresponding
-a state to construct quantum probability measures in CQT. However,
-since the variants of quantum probability measures in Sec.~\ref{sec:Toward-IVPM}
+a state to a quantum probability measure in CQT. However, since the
+variants of quantum probability measures in Sec.~\ref{sec:Toward-IVPM}
 and Chapter~\ref{chap:QIVPM} could not be constructed by the Born
-rule easily, it is instructive to search for a Born rule here, and
-we will actually find the unique one.
-
-Although quantum probability measures constructed by gluing together
-the classical ones looks complex, they could all be induced by operators
+rule easily, searching for a Born rule step-by-step here might provide
+a idea what we should do in Sec.~\ref{sec:Toward-IVPM} and Chapter~\ref{chap:QIVPM}.
+While the situations will become more delicate in the later sections,
+we will fortunately find the unique Born rule in CQT here.
+
+Although a quantum probability measure constructed by gluing together
+the classical ones looks complex, it could be induced by an operator
 according to Gleason's theorem.
@@
 Although Gleason's theorem can correspond every quantum probability
-measure to a unique mixed state~$\rho$, it doesn't explain whether
-this state $\rho$ characterizing the state of particle sending to
-a Stern-Gerlach type experiment. For example, in contrast with CQT,
-if a quantum theory always ignore the input state and predict the
-experimental outcomes are equally probable, even if this quantum theory
-maps every input state to a quantum probability measure, it is still
-not very sensible.
+measure~$\mu$ to a unique mixed state~$\rho$, if we follow the
+Stern-Gerlach type experiment interpretation in previous section,
+we can find Gleason's theorem doesn't specify whether this state $\rho$
+characterizing the state of particle sending to the quantum experiment.
+For example, in contrast with CQT, a quantum theory could basically
+ignore the input state and predict the experimental outcomes are equally
+probable~\cite{doi:10.1142/S0217984913500644,1751-8121-47-40-405304}.
+Even if a version of Bell's inequality could be proved in this quantum
+theory, its prediction might be different from the prediction of CQT
+enough that it is easily distinguish them experimentally.
 
@@
 events. To define a sensible correspondence, we hope that if the state~$\ket{\Phi}$
-is one of the outcome of a quantum event~$P$, i.e., $P\ket{\Phi}=\ket{\Phi}$,
+is one of the outcomes of a quantum event~$P$, i.e., $P\ket{\Phi}=\ket{\Phi}$,
 then the event~$P$ always happens, $\muB_{\Phi}\left(P\right)=1$
@@
 changing to another basis is the same as applying an unitary map~$U$,
-we should have$\muF_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muF_{\Phi}\left(P\right)$.
-It is easy to check the correspondence satisfying the conditions in
-this paragraph is unique, 
+we should have $\muF_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muF_{\Phi}\left(P\right)$.
+It is easy to check that the correspondence satisfying the conditions
+in this paragraph is unique, 
 \begin{equation}
@@
 By the Born rule, the first probability measure corresponds to the
-quantum system being in the pure state $\ket{\ps}$ defined in Eq.~(\ref{eq:psms})
+quantum system being in the pure state $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$
 and the second corresponds to the quantum system being in the state

### 2018-11-26 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 of a process, and its power set $2^{\Omega}$ as the classical event
-space, a classical probability measure~$\mu$ maps an event~$E$
+space, a classical probability measure~$\mu$ maps every event~$E$
 to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
@@
 our discussion. This can be achieved by mapping a classical event~$E$
-to the projector generated by $E$
+to the projector generated by $E$,
 \begin{equation}
@@
 \end{equation}
-with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$ because
+with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, because
 \begin{equation}
@@
 Given two \emph{commuting} projectors $P_{0}$ and~$P_{1}$, there
-exists a sample space $\Omega$ and a pair of events $E_{0}\subseteq\Omega$
-and $E_{1}\subseteq\Omega$ such that $P_{0}=\varphi\left(E_{0}\right)$
-and $P_{1}=\varphi\left(E_{1}\right)$. Conversely, given a pair of
-events $E_{0}$ and $E_{1}$ in the same sample space~$\Omega$,
-their corresponding quantum events $\varphi\left(E_{0}\right)$ and
-$\varphi\left(E_{1}\right)$ are commuting and satisfying the following
-properties: 
+exists a pair of events $E_{0}$ and $E_{1}$ in the same sample space~$\Omega$
+such that $P_{0}=\varphi\left(E_{0}\right)$ and $P_{1}=\varphi\left(E_{1}\right)$.
+Conversely, given a pair of events $E_{0}$ and $E_{1}$ in the same
+sample space~$\Omega$, their corresponding quantum events $\varphi\left(E_{0}\right)$
+and $\varphi\left(E_{1}\right)$ are commuting and satisfying the
+following properties: 
 \begin{align}
@@
 
-Then, a quantum probability space can be defined by a quantum event
+Then, a quantum probability space can be defined as a quantum event
 space~$\events$ together with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
@@
 Because $\varphi$ respects the probability of events, if we restrict
-$\varphi$ on an event space $2^{\Omega}$, the function $\varphi^{*}\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+the domain of $\varphi$ on an classical event space $2^{\Omega}$,
+the function $\varphi^{*}\mu:2^{\Omega}\rightarrow\left[0,1\right]$
 defined by precomposition $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$
@@
 rule easily, searching for a Born rule step-by-step here might provide
-a idea what we should do in Sec.~\ref{sec:Toward-IVPM} and Chapter~\ref{chap:QIVPM}.
-While the situations will become more delicate in the later sections,
-we will fortunately find the unique Born rule in CQT here.
+a better idea what we should do in Sec.~\ref{sec:Toward-IVPM} and
+Chapter~\ref{chap:QIVPM}. While the situations will become more
+delicate in the later sections, we will fortunately find the unique
+Born rule in CQT here.
 
@@
 measure $\mu:\events\rightarrow\left[0,1\right]$, there exists a
-unique mixed state~$\rho$ such that $\mu\left(P\right)=\Tr\left(\rho P\right)$
-for any $D$-dimensional projector~$P$.\end{thm}
-
-Although Gleason's theorem can correspond every quantum probability
-measure~$\mu$ to a unique mixed state~$\rho$, if we follow the
-Stern-Gerlach type experiment interpretation in previous section,
-we can find Gleason's theorem doesn't specify whether this state $\rho$
-characterizing the state of particle sending to the quantum experiment.
-For example, in contrast with CQT, a quantum theory could basically
-ignore the input state and predict the experimental outcomes are equally
-probable~\cite{doi:10.1142/S0217984913500644,1751-8121-47-40-405304}.
-Even if a version of Bell's inequality could be proved in this quantum
-theory, its prediction might be different from the prediction of CQT
-enough that it is easily distinguish them experimentally.
+unique mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such
+that $\mu\left(P\right)=\Tr\left(\rho P\right)$ for any $D$-dimensional
+projector~$P$, where $\ket{\Phi_{j}}\in\mathcal{H}$ are normalized,
+$q_{j}>0$, and $\sum_{j=1}^{N}q_{j}=1$.\end{thm}
+
+To understand Gleason's theorem, we can follow the Stern-Gerlach type
+experiment interpretation in the previous section. Although Gleason's
+theorem correspond every quantum probability measure~$\mu$ to a
+unique mixed state~$\rho$, it doesn't specify whether this state
+$\rho$ characterizing the state of particle sending to the quantum
+experiment. Consider an extreme example: a quantum theory could ignore
+the input state and predict the experimental outcomes are always equally
+probable. Even if these predictions form a quantum probability measure,
+this kind of prediction is so different from the prediction of CQT
+that they can be easily distinguished experimentally.
 
@@
 events. To define a sensible correspondence, we hope that if the state~$\ket{\Phi}$
-is one of the outcomes of a quantum event~$P$, i.e., $P\ket{\Phi}=\ket{\Phi}$,
-then the event~$P$ always happens, $\muB_{\Phi}\left(P\right)=1$
-and vice versa. Moreover, since the physical phenomena exists and
-should be the same no matter how we describe them, the probability
-of an event should be invariant despite how we choose the basis. Because
+is one of the outcomes of a quantum event~$P$, $P\ket{\Phi}=\ket{\Phi}$,
+then the event~$P$ always happens, $\muB_{\Phi}\left(P\right)=1$,
+and vice versa. Moreover, since the physical phenomena exist and should
+be the same no matter how we describe them, the probability of an
+event should be invariant despite how we choose the basis. Because
 changing to another basis is the same as applying an unitary map~$U$,
@@
 $\ket{\Phi}$ is normalized, Eq.~(\ref{eq:Born}) could be simplified
-as $\muB_{\Phi}(P)=\melem{\Phi}{P}{\Phi}$. For mixed states $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$,
-where $\ket{\Phi_{j}}\in\mathcal{H}$ are normalized, $q_{j}>0$,
-and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule induces a
-probability measure $\muB_{\rho}$ defined as 
-\begin{equation}
-\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)\,.\label{eq:mixed-Born}
-\end{equation}
+as $\muB_{\Phi}(P)=\melem{\Phi}{P}{\Phi}$. Since a mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$
+is a weighted average of projectors $\proj{\Phi_{j}}$ with weights
+$q_{j}>0$ and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule
+of $\rho$, $\muB_{\rho}\left(P\right)$, is also a weighted average
+of $\muB_{\Phi_{j}}\left(P\right)$, 
+\begin{equation}
+\muB_{\rho}\left(P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)=\Tr\left(\rho P\right)\,,\label{eq:mixed-Born}
+\end{equation}
+which is also a quantum probability measure and consistent with Gleason's
+theorem.
 

### 2018-11-26 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

@@
 of a process, and its power set $2^{\Omega}$ as the classical event
-space, a classical probability measure~$\mu$ maps every event~$E$
+space, a classical probability measure~$\mu$ maps every event $E\subseteq\Omega$
 to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
@@
 these events should be identified as the same quantum event to simplify
-our discussion. This can be achieved by mapping a classical event~$E$
-to the projector generated by $E$,
+our discussion. This identification can be achieved by mapping a classical
+event~$E$ to the projector generated by $E$,
 \begin{equation}
@@
 with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, because
+$\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)$ is equal to
+$\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)$ as operators,
 \begin{equation}
@@
 delicate in the later sections, we will fortunately find the unique
-Born rule in CQT here.
-
-Although a quantum probability measure constructed by gluing together
-the classical ones looks complex, it could be induced by an operator
-according to Gleason's theorem.
+Born rule for CQT here.
+
+Although the quantum probability measure constructed by gluing together
+classical ones looks complex, it could be induced by an operator according
+to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
 
@@
 
-To understand Gleason's theorem, we can follow the Stern-Gerlach type
-experiment interpretation in the previous section. Although Gleason's
-theorem correspond every quantum probability measure~$\mu$ to a
-unique mixed state~$\rho$, it doesn't specify whether this state
-$\rho$ characterizing the state of particle sending to the quantum
-experiment. Consider an extreme example: a quantum theory could ignore
-the input state and predict the experimental outcomes are always equally
-probable. Even if these predictions form a quantum probability measure,
-this kind of prediction is so different from the prediction of CQT
-that they can be easily distinguished experimentally.
+If we follow the discussion of Stern-Gerlach type experiments in the
+previous section to interpret Gleason's theorem, we can find Gleason's
+theorem doesn't specify whether its unique mixed state~$\rho$ characterizes
+the state of particle sending to the quantum experiment or not. Consider
+an extreme example: a quantum theory could ignore the input state
+and predict the experimental outcomes are always equally probable.
+Even if these predictions form a quantum probability measure, this
+kind of prediction is so different from the prediction of CQT that
+they can be easily distinguished experimentally.
 
@@
 the particle sending to a Stern-Gerlach type experiment, and $\muB_{\Phi}$
-be the corresponding quantum probability measure of the resulting
-events. To define a sensible correspondence, we hope that if the state~$\ket{\Phi}$
-is one of the outcomes of a quantum event~$P$, $P\ket{\Phi}=\ket{\Phi}$,
+be the quantum probability measure of the resulting events sensibly
+corresponding to $\ket{\Phi}$. For a correspondence $\ket{\Phi}\mapsto\muB_{\Phi}$
+to be sensible, we hope that if the state~$\ket{\Phi}$ is one of
+the outcomes of a quantum event~$P$, $P\ket{\Phi}=\ket{\Phi}$,
 then the event~$P$ always happens, $\muB_{\Phi}\left(P\right)=1$,
@@
 As an example, consider a three-dimensional Hilbert space with orthonormal
-basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $ and an observable
+basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $ and the observable
 $\mathbf{O}_{0}$ defined in Eq.~(\ref{eq:observable}). Two fragments

### 2018-11-26 dissertation.tex
dissertation.lyx "2.2.2 Gleason's Theorem and The Born Rule" Fix typos...

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[11pt,twoside]{iuphd}
+\documentclass[11pt,twoside,english]{iuphd}
 \usepackage{amsmath}
@@
 \setdefaultlanguage[variant=american]{english}
-\setotherlanguage{arabic}
 \usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
@@
 like the way being acknowledged... }I want to thank Prof.~Gerardo
-Ortiz, Prof.~Amr Sabry (\textarabic{عمرو صبري}), and Prof.~Andrew
-Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
-with me, and enormous other things. These papers become the main part
-of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
-is based on “Geometry of discrete quantum computing”~\cite{geometry2013}
-and “Discrete quantum theories” (DQT)~\cite{DQT2014}; most
-of Chapter~\ref{chap:QIVPM} is based on “Quantum Interval-Valued
-Probability: Contextuality and the Born Rule” (QIVPM) \cite{THOS2018}.
-Together with Prof.~Dylan Thurston and Prof.~Shouhong Wang (汪守宏),
-I want to thank you for getting together to understand what I did
-and passing my dissertation proposal Spring 2017. I also thank Prof.
-Dylan Thurston for serving in my advisory committee and my Tier 3
-committee, with other advisory committee members passing my Computer
-Science qualifying exam Spring 2016. Especially, my survey of real
-computation in the qualifying exam inspired me the comparison of quantum
-computer and analog computer in Chapter~\ref{chap:Introduction}.
+Ortiz, Prof.~Amr Sabry, and Prof.~Andrew Hanson for publishing
+three papers \cite{geometry2013,DQT2014,THOS2018} with me, and enormous
+other things. These papers become the main part of my thesis, especially
+most of Chapter~\ref{chap:DQT=000026DQC} is based on “Geometry
+of discrete quantum computing”~\cite{geometry2013} and “Discrete
+quantum theories” (DQT)~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
+is based on “Quantum Interval-Valued Probability: Contextuality
+and the Born Rule” (QIVPM) \cite{THOS2018}. Together with Prof.~Dylan
+Thurston and Prof.~Shouhong Wang (汪守宏), I want to thank you for getting
+together to understand what I did and passing my dissertation proposal
+Spring 2017. I also thank Prof. Dylan Thurston for serving in my advisory
+committee and my Tier 3 committee, with other advisory committee members
+passing my Computer Science qualifying exam Spring 2016. Especially,
+my survey of real computation in the qualifying exam inspired me the
+comparison of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
 Chapter~\ref{chap:Introduction} also contains the motivation in
 my application for Rethinking Foundations of Physics 2017 workshop
-reviewed by Prof. Amr Sabry (\textarabic{عمرو صبري}). I want
-to thank Prof. Lawrence Moss for inviting me to present our results
-in the interdisciplinary logic seminar and theory seminar in Computer
-Science, co-chairing my Tier 3 committee, writing an assessment letter
-for me, and drawing my attention on Prof.~Abramsky's paper~\cite{Abramsky2012},
-which inspired me to merge quantum probability with discrete quantum
-theories. And I thank John Gardiner for inspiring discussion on the
-difficulties merging them~\cite{Gardiner2014}. These results are
-improved and motivated the transition from DQT to QIVPM in Sec.~\ref{sec:Toward-IVPM}.
+reviewed by Prof. Amr Sabry. I want to thank Prof. Lawrence Moss
+for inviting me to present our results in the interdisciplinary logic
+seminar and theory seminar in Computer Science, co-chairing my Tier
+3 committee, writing an assessment letter for me, and drawing my attention
+on Prof.~Abramsky's paper~\cite{Abramsky2012}, which inspired me
+to merge quantum probability with discrete quantum theories. And I
+thank John Gardiner for inspiring discussion on the difficulties merging
+them~\cite{Gardiner2014}. These results are improved and motivated
+the transition from DQT to QIVPM in Sec.~\ref{sec:Toward-IVPM}.
 I also thank Prof.~Tom Lewis for helping me organize the unpublished
@@
 changing to another basis is the same as applying an unitary map~$U$,
-we should have $\muF_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muF_{\Phi}\left(P\right)$.
-It is easy to check that the correspondence satisfying the conditions
-in this paragraph is unique, 
+we should have $\muB_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muB_{\Phi}\left(P\right)$.
+It is easy to check that the correspondence satisfying these conditions
+is unique, 
 \begin{equation}

### 2018-11-29 dissertation.tex
dissertation.lyx "2.2.1 Classical and Quantum Probability Spaces" Added a TODO...

@@
 of $\mathbf{O}$ by $\varphi$ is a random variable $\varphi^{*}\mathbf{O}:\Omega\rightarrow\mathbb{R}$
-defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$.\end{definition}
+defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$.
+\todo{Put the definition of indicator function!}\end{definition}
 

### 2018-11-30 dissertation.tex
dissertation.lyx Put TODOs get from defense...

@@
 
-\begin{abstract*}Most of the quantum computing models are based on
-the continuum of real numbers, despite the fact that classical digital
-computers faithfully realize the prediction of discrete computational
-models, while analog computers in reality are far weaker than the
-theoretical prediction of continuous computational models. Since one
-of the important factors of this gap is the measurement precision,
-we hope to build a more faithful model by investigating discrete quantum
-computing models and incorporating the idea of finite precision measurement
-into the quantum theory.
+\begin{abstract*}\todo{Rewrite the abstract so that the committee
+can sign it. Prof. Thurston: “To address the same issue, the thesis
+contains four different theories each have different pros and cons.
+The abstract should said them seperately and explicitly.” }Most
+of the quantum computing models are based on the continuum of real
+numbers, despite the fact that classical digital computers faithfully
+realize the prediction of discrete computational models, while analog
+computers in reality are far weaker than the theoretical prediction
+of continuous computational models. Since one of the important factors
+of this gap is the measurement precision, we hope to build a more
+faithful model by investigating discrete quantum computing models
+and incorporating the idea of finite precision measurement into the
+quantum theory.
 
@@
 
-The marriage of quantum mechanics and computer science first envisioned
-and popularized by Feynman has created an awkward, but opportune,
-moment. This embarrassing dilemma was concisely summarized by Prof.~Aaronson
-that one of the the following three statements is false \cite{AaronsonArkhipov2011,BFRDARW2013}:
+\todo{Write a story so that physicists will also be interested in
+this thesis. For example, quantum simulation problem and how to apply
+these to other physicists work (say two more pages?). Check our previous
+papers. Explicitly say what question we wan to solve. In particular,
+merging quantum mechanics and computer science is too broad for a
+thesis. }The marriage of quantum mechanics and computer science first
+envisioned and popularized by Feynman has created an awkward, but
+opportune, moment. This embarrassing dilemma was concisely summarized
+by Prof.~Aaronson that one of the the following three statements
+is false \cite{AaronsonArkhipov2011,BFRDARW2013}:
 \begin{enumerate}[label=(\roman{enumi})]
@@
 \noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical computational
-models and their physical realizations}
+models and their physical realizations \todo{Update this table to
+include }}
 \begin{tabularx}{\linewidth}{ccX}
@@
 the set of all projectors on a given Hilbert space is called a quantum
-event space~$\events$.
+event space~$\events$. \todo{Check the citation of this part. Did
+von Neumann really think about this when he use projectors to formulate
+quantum theory?}
 
@@
 but I don't know when I could organize my unreadable draft to a readable
-one...}
+one... Moreover, Prof.~Ortiz wants to check Shor's algorithm in DQC(I).}
 
@@
 verified that the only QPMFF $\mu:\events_{7^{2}}\rightarrow\left[0,1\right]$
-is
+is \todo{Equal probable.}
 \begin{equation}
@@
 will use a fixed collection of intervals appropriate for the resources
-and precision of the particular experiment.\todo{Update the further
-discussion chapter according to an updated Sec.~\ref{sec:fuzzy}.}
+and precision of the particular experiment.\todo{Add a two-page conclusion
+chapter which could include further discussion, but it can be only
+a few sentences? }\todo{Discrete Schrödinger equation? And its relation
+with Grover's algorithm?}
 

### 2018-12-01 dissertation.tex
dissertation.lyx Add some TODOs for new ideas...

@@
 precision into the quantum theory. To distinguish the modified quantum
-theories from the usual ones, the usual ones will be called the ‘conventional
-quantum theory’ where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ‘actual,’ ‘standard,’
-and ‘ordinary’ quantum theory.}.
+theories from the usual ones, the usual ones will be called the “conventional
+quantum theory” where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes “actual,”
+“standard,” and “ordinary” quantum theory.}.
 
@@
 expectation values because we can pullback an observable to a classical
-random variable, and the expectation values are invariant.
+random variable, and the expectation values are invariant.\todo{Add
+interpretation!}
 
@@
 are same. Actually, they are both equal to $\tfrac{2}{3}$ because
-$\muF_{\Phi''}\left(P_{0}\right)=\muF_{U''\ket{\Phi'}}\left(U''P_{0}U''^{\dagger}\right)=\muF_{\Phi'}\left(P_{0}\right)=\tfrac{2}{3}$
+$\muF_{\Phi''}\left(P_{0}\right)=\muF_{U''\ket{\Phi'}}\left(U''P_{0}U''\right)=\muF_{\Phi'}\left(P_{0}\right)=\tfrac{2}{3}$
 by Eqs.~(\ref{eq:basis-independent}) and (\ref{eq:prob23}). Since
@@
 a few sentences? }\todo{Discrete Schrödinger equation? And its relation
-with Grover's algorithm?}
+with Grover's algorithm? }\todo{Notice that in differential geometry,
+Killing–Hopf theorem asserts that having positive constant curvature
+guarantees a manifold is essentially a sphere, but say little things
+even if the curvature has only small deviation from constant. Since
+a quantum probability measure is glued by classical probability measures,
+like a manifold. When their relations are exact, Gleason's theorem
+asserts that a quantum probability measure can essentially induced
+by the Born rule, but they can be wild when we move on to interval-valued
+situation! }
 

### 2018-12-01 dissertation.tex
dissertation.lyx Global replace the quotation marks “ ” by `` '' so that the LaTeX can be displayed correctly in ASCII...

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[11pt,twoside,english]{iuphd}
+\documentclass[11pt,twoside]{iuphd}
 \usepackage{amsmath}
@@
 \setdefaultlanguage[variant=american]{english}
+\setotherlanguage{arabic}
 \usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
@@
 like the way being acknowledged... }I want to thank Prof.~Gerardo
-Ortiz, Prof.~Amr Sabry, and Prof.~Andrew Hanson for publishing
-three papers \cite{geometry2013,DQT2014,THOS2018} with me, and enormous
-other things. These papers become the main part of my thesis, especially
-most of Chapter~\ref{chap:DQT=000026DQC} is based on “Geometry
-of discrete quantum computing”~\cite{geometry2013} and “Discrete
-quantum theories” (DQT)~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
-is based on “Quantum Interval-Valued Probability: Contextuality
-and the Born Rule” (QIVPM) \cite{THOS2018}. Together with Prof.~Dylan
-Thurston and Prof.~Shouhong Wang (汪守宏), I want to thank you for getting
-together to understand what I did and passing my dissertation proposal
-Spring 2017. I also thank Prof. Dylan Thurston for serving in my advisory
-committee and my Tier 3 committee, with other advisory committee members
-passing my Computer Science qualifying exam Spring 2016. Especially,
-my survey of real computation in the qualifying exam inspired me the
-comparison of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
+Ortiz, Prof.~Amr Sabry (\textarabic{عمرو صبري}), and Prof.~Andrew
+Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
+with me, and enormous other things. These papers become the main part
+of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
+is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
+and ``Discrete quantum theories'' (DQT)~\cite{DQT2014}; most of
+Chapter~\ref{chap:QIVPM} is based on ``Quantum Interval-Valued
+Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2018}.
+Together with Prof.~Dylan Thurston and Prof.~Shouhong Wang (汪守宏),
+I want to thank you for getting together to understand what I did
+and passing my dissertation proposal Spring 2017. I also thank Prof.
+Dylan Thurston for serving in my advisory committee and my Tier 3
+committee, with other advisory committee members passing my Computer
+Science qualifying exam Spring 2016. Especially, my survey of real
+computation in the qualifying exam inspired me the comparison of quantum
+computer and analog computer in Chapter~\ref{chap:Introduction}.
 Chapter~\ref{chap:Introduction} also contains the motivation in
 my application for Rethinking Foundations of Physics 2017 workshop
-reviewed by Prof. Amr Sabry. I want to thank Prof. Lawrence Moss
-for inviting me to present our results in the interdisciplinary logic
-seminar and theory seminar in Computer Science, co-chairing my Tier
-3 committee, writing an assessment letter for me, and drawing my attention
-on Prof.~Abramsky's paper~\cite{Abramsky2012}, which inspired me
-to merge quantum probability with discrete quantum theories. And I
-thank John Gardiner for inspiring discussion on the difficulties merging
-them~\cite{Gardiner2014}. These results are improved and motivated
-the transition from DQT to QIVPM in Sec.~\ref{sec:Toward-IVPM}.
+reviewed by Prof. Amr Sabry (\textarabic{عمرو صبري}). I want
+to thank Prof. Lawrence Moss for inviting me to present our results
+in the interdisciplinary logic seminar and theory seminar in Computer
+Science, co-chairing my Tier 3 committee, writing an assessment letter
+for me, and drawing my attention on Prof.~Abramsky's paper~\cite{Abramsky2012},
+which inspired me to merge quantum probability with discrete quantum
+theories. And I thank John Gardiner for inspiring discussion on the
+difficulties merging them~\cite{Gardiner2014}. These results are
+improved and motivated the transition from DQT to QIVPM in Sec.~\ref{sec:Toward-IVPM}.
 I also thank Prof.~Tom Lewis for helping me organize the unpublished
@@
 CSCI-Y790 Writing and Editing course as presented in Sec.~\ref{sec:Quantum-Contextuality}.
-I also thank Elizabeth “Betsy” Merceron and Kexin “Casey”
+I also thank Elizabeth ``Betsy'' Merceron and Kexin ``Casey''
 Chen (谌可心) for teaching me English in general so that others can understand
@@
 \todo{Type a table for acknowledgment so that I would have to write
-“I thank” so many times here? }Many people in both department
+``I thank'' so many times here? }Many people in both department
 of Mathematics and Computer Science need to do something more to make
@@
 \begin{abstract*}\todo{Rewrite the abstract so that the committee
-can sign it. Prof. Thurston: “To address the same issue, the thesis
+can sign it. Prof. Thurston: ``To address the same issue, the thesis
 contains four different theories each have different pros and cons.
-The abstract should said them seperately and explicitly.” }Most
+The abstract should said them seperately and explicitly.'' }Most
 of the quantum computing models are based on the continuum of real
@@
 may be another important factor parallel to \todo{Find a phrase better
-than “parallel to”. }whether the model is classical or quantum.
-\todo{Add discussion about randomness, like: “Another big difference
+than ``parallel to''. }whether the model is classical or quantum.
+\todo{Add discussion about randomness, like: ``Another big difference
 is that randomness in quantum computing is inherited from its underlying
 quantum physics while randomness in probabilistic Turing machine is
-an addition feature acquired by adding random bits to a Turing machine.”
+an addition feature acquired by adding random bits to a Turing machine.''
 }Although building a realistic quantum computer is an ongoing project~\cite{Shieber2018},
@@
 precision into the quantum theory. To distinguish the modified quantum
-theories from the usual ones, the usual ones will be called the “conventional
-quantum theory” where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes “actual,”
-“standard,” and “ordinary” quantum theory.}.
+theories from the usual ones, the usual ones will be called the ``conventional
+quantum theory'' where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+and ``ordinary'' quantum theory.}.
 
@@
 We can reduce 3 degrees of freedom in \Eq{A5.eq} to 2 degrees of
-freedom by effectively removing $\rme^{\rmi\theta}$ (“fibering
-out by the circle $\Sphere{1}$”). The standard form of this maps
-(“the Hopf fibration”) is 
+freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
+out by the circle $\Sphere{1}$''). The standard form of this maps
+(``the Hopf fibration'') is 
 \begin{eqnarray}
@@
 $0$, and the multiplication identity $1$. Given the field~$\mathbb{F}$,
-the closed operations of addition, “$+$,” and multiplication,
-“$\gmult$,” satisfy the following set of axioms: 
+the closed operations of addition, ``$+$,'' and multiplication,
+``$\gmult$,'' satisfy the following set of axioms: 
 \begin{enumerate}
@@
 is predicted by the theory, modal quantum theories are named after
-these “modal” concepts.
+these ``modal'' concepts.
 
@@
 dependence in CQT only exists when discussing quantum contextuality.
-Despite this kind of “supercontextuality” of MQT, its computational
-model, modal quantum computing (MQC), having “supernatural”
-computational power is also far from conventional quantum computing
-as we will describe next.
+Despite this kind of ``supercontextuality'' of MQT, its computational
+model, modal quantum computing (MQC), having ``supernatural'' computational
+power is also far from conventional quantum computing as we will describe
+next.
 
@@
 
-Our computations with this “toy” modal quantum theory showed
-that it possesses “supernatural” computational power. For example,
+Our computations with this ``toy'' modal quantum theory showed that
+it possesses ``supernatural'' computational power. For example,
 one can solve a black box version of the \usat\ problem~\cite{usat}
@@
 Our next objective is to develop more realistic discrete quantum theory
-variants that exclude “supernatural” algorithms such as the
-one presented above. Our first such plausible framework~\cite{HOSW2011}
+variants that exclude ``supernatural'' algorithms such as the one
+presented above. Our first such plausible framework~\cite{HOSW2011}
 is based on complexifiable finite fields. To incorporate complex numbers
@@
 have an inner product satisfying the properties above. However, we
-will introduce an Hermitian “dot product” satisfying some of
-those properties.
+will introduce an Hermitian ``dot product'' satisfying some of those
+properties.
 
@@
 $\ket{\Psi}$ such that $\ip{\Psi}{\Psi}=0$. The reason is that addition
-in finite fields eventually “wraps around” (because of their
-cyclic or modular structure), allowing the sum of non-zero elements
-to be zero. The fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$
+in finite fields eventually ``wraps around'' (because of their cyclic
+or modular structure), allowing the sum of non-zero elements to be
+zero. The fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$
 decreases with the order $p$.
@@
 size of $\fnorm*{\left\{ c\right\} }$ is $p+1$, we cannot identify
-a “unique” way to normalize any given vector.
+a ``unique'' way to normalize any given vector.
 
@@
 this case, we systematically choose the state divided by the positive
-square root as “the” normalized vector of $\ket{\Psi}$ in conventional
+square root as ``the'' normalized vector of $\ket{\Psi}$ in conventional
 quantum theory, and the positive square root function is called the
@@
 on the Bloch sphere vary considerably due to the nature of discrete
-fields; we have artificially normalized them to a “continuous world”
+fields; we have artificially normalized them to a ``continuous world''
 unit radius sphere for conceptual clarity.
@@
 states, effectively the space of allowed discrete partitions of unity;
-we cannot exactly call these “probability-conserving” sectors
+we cannot exactly call these ``probability-conserving'' sectors
 of the state coefficients since we do not have a well defined notion
@@
 of the field to creatively cancel probability amplitudes and solve
-problems with what again appears to be “supernatural” efficiency.
+problems with what again appears to be ``supernatural'' efficiency.
 We illustrate this behavior with the algorithm in Fig.~\ref{fig:dbsearch},
@@
 additional interference processes that happen because of the possibility
-of “wrapping around” due to modular arithmetic. We do not know,
+of ``wrapping around'' due to modular arithmetic. We do not know,
 in general, whether this version of discrete quantum computing actually
@@
 and $\cardp{\fnorm{\alpha_{j}}}{\fnorm{\ket{\Psi}}}$ with the same
-“denominator”, $\fnorm{\alpha_{i}}>\fnorm{\alpha_{j}}$ physically
+``denominator'', $\fnorm{\alpha_{i}}>\fnorm{\alpha_{j}}$ physically
 means it is more likely to measure $\ket{i}$ than $\ket{j}$ if we
@@
 no matter how much resource we use. The same principle can also apply
-to two cardinal probabilities with the different “denominator”.
+to two cardinal probabilities with the different ``denominator''.
 The details of the comparison can easily formulated by following the
@@
 states as usual. However, instead of the Deutsch black box~$U_{f}$,
-$f$ is represented as the $N\times N$ “phase rotation” matrix
+$f$ is represented as the $N\times N$ ``phase rotation'' matrix
 \begin{equation}
@@
 \end{equation}
-where the “marked” element is in the first position. Beside
-$R$, we also need the $N\times N$ “diffusion” matrix
+where the ``marked'' element is in the first position. Beside $R$,
+we also need the $N\times N$ ``diffusion'' matrix
 \begin{equation}
@@
 To overcome these issues, we try a different approach to define a
-“conventional” probability over finite fields axiomatically.
+``conventional'' probability over finite fields axiomatically.
 
@@
 Although we couldn't prove there is no discrete Born rule by investigating
-QPMFFs alone, we could prove there is no “sensible” Born rule
+QPMFFs alone, we could prove there is no ``sensible'' Born rule
 which also satisfies an analog of Proposition~\ref{prop:Born-probability-one}
@@
 \begin{thm}\label{thm:NotGleasonDQT-group}For $D\ge3$ except $p=D=3$,
-there is no “sensible” Born rule $\muF$ parametrized by unit-norm
+there is no ``sensible'' Born rule $\muF$ parametrized by unit-norm
 states~$\ket{\Phi}$ in $\mathcal{H}$ such that $\muF_{\Phi}$ is
@@
 
-The reason why there is no “sensible” Born rule might be that
+The reason why there is no ``sensible'' Born rule might be that
 the state spaces are now discrete and finite, but we still consider
@@
 generalization. In the classical setting, there are several proposals
-for “imprecise probabilities”~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+for ``imprecise probabilities''~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
 Although these proposals differ in some details, they all share the
@@
 in each event separately so the combined event should be mapped to
-a sharper interval. In our example, even though the “true” probability
-of $E$ can be anywhere in the range $[0.2,0.3]$ and the “true”
+a sharper interval. In our example, even though the ``true'' probability
+of $E$ can be anywhere in the range $[0.2,0.3]$ and the ``true''
 probability of~$\overline{E}$ can be anywhere in the range $[0.7,0.8]$,
@@
 such that $\bar{\mu}\left(E\right)=\left[0.2,0.3\right]$ and $\bar{\mu}\left(\overline{E}\right)=\left[0.7,0.8\right]$,
-we discussed the “true” probabilities, $\mu\left(E\right)$
-and $\mu\left(\overline{E}\right)$, can be anywhere in the range
-$\left[0.2,0.3\right]$ and $\left[0.7,0.8\right]$, respectively,
-as long as they satisfy $\mu\left(E\right)+\mu\left(\overline{E}\right)=1$.
-These “true” probabilities can actually be summarized as a probability
-measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$ satisfying 
+we discussed the ``true'' probabilities, $\mu\left(E\right)$ and
+$\mu\left(\overline{E}\right)$, can be anywhere in the range $\left[0.2,0.3\right]$
+and $\left[0.7,0.8\right]$, respectively, as long as they satisfy
+$\mu\left(E\right)+\mu\left(\overline{E}\right)=1$. These ``true''
+probabilities can actually be summarized as a probability measure
+$\mu:2^{\Omega}\rightarrow\left[0,1\right]$ satisfying 
 \begin{align}
@@
 \end{align}
-we conclude the “true” probability of each event belongs to
-the interval probability of the corresponding event. This conclusion
-gives the following definition of core.
+we conclude the ``true'' probability of each event belongs to the
+interval probability of the corresponding event. This conclusion gives
+the following definition of core.
 
@@
 \end{equation}
-As we have discussed, the “true” probability is a probability
+As we have discussed, the ``true'' probability is a probability
 measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$ consistent with
@@
 like a weighted average of~$x_{i}^{s}$, where $s$ is either $+$
-or $-$, but this time the “weights” are not just the measure
+or $-$, but this time the ``weights'' are not just the measure
 of their step functions $\pmeas\left(E_{i}^{s}\right)$. Instead,
@@
 and their interval-valued probabilities $\bar{\mu}\left(E_{i\uparrow}^{s}\right)$,
-the “weights” are the differences of the both-end of the interval
+the ``weights'' are the differences of the both-end of the interval
 probabilities, $\Delta\mu^{t}\left(E_{i\uparrow}^{s}\right)=\mu^{t}\left(E_{i\uparrow}^{s}\right)-\mu^{t}\left(E_{\left(i+1\right)\uparrow}^{s}\right)$,
@@
 Then, the Choquet integral of $X$ relative to $\bar{\mu}$ is averaging
-$x_{i}^{s}$ with the given “weights,”
+$x_{i}^{s}$ with the given ``weights,''
 \begin{equation}
@@
 i.e., $\bar{\mu}\left(E\right)=\left[\pmeas\left(E\right),\pmeas\left(E\right)\right]$
-for all $E$. Since the “weights” in Eq.~(\ref{eq:interval-expectation})
+for all $E$. Since the ``weights'' in Eq.~(\ref{eq:interval-expectation})
 are the difference on the probability of the accumulative sets, they
@@
 with $i$ and $j$ ranging over $\{0,1,2\}$ from the Mermin-Peres
-“magic square” used to prove the Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
+``magic square'' used to prove the Kochen-Specker theorem~\cite{Mermin1990Simple,peres1995quantum,Griffiths2003}:
 
@@
 the effects of finite-precision. Every QIVPM must map some events
-to truly uncertain intervals, not just “almost definite intervals.”
+to truly uncertain intervals, not just ``almost definite intervals.''
 The proof requires two simple lemmas that we present first.
@@
 measures that includes the conventional one as a limit. The theorem
-is however “special” in the sense that it only applies to the
+is however ``special'' in the sense that it only applies to the
 particular class of QIVPMs constructed by composing an interval map

### 2018-12-01 abstract-ajh1.tex
From: Hanson, Andrew J. <hansona@indiana.edu> Sent: Thursday, November 29, 2018 13:24 To: Tai, Yu-Tsung <yuttai@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: CV...abstract edits...

Corrections - A. Hanson  29 Nov 2018

\begin{abstract*}

Most quantum computing models are based on
the continuum of real numbers, while classical digital
computers faithfully realize only discrete computational
models.   Analog computers appear to be an option, but in reality are
far weaker than would be needed for computational models requiring
real numbers.   One approach to resolving this conflict is to
find consistent mathematical ways to limit measurement precision
to computable contexts that do not require incomputable real numbers.
Our goal is to build a more philosophically consistent models by
investigating discrete quantum computing using finite number systems, 
and, alternatively, by incorporating finite precision measurement
using intervals into quantum theory.

We begin by replacing the continuum of complex numbers by discrete
finite fields in quantum theory. The simplest theory, defined over
unrestricted finite fields, is so weak that it cannot express
Deutsch's algorithm, but, paradoxcially, is also so powerful that it
can be used to solve the $\usat$ problem, which is as hard as a
general $\NP$-complete problem.  Our second framework employs only
finite fields over prime numbers of the form $4n+3$, which possess no
solutions to $x^{2}+1=0$, and thus permit an elegant complex
representation of the finite field by adjoining
$\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit system
are in principle enumerable, we can count the number of states, and
determine the proportions of entangled and unentangled
states. Although this improved framework can be used to implement the
probabilistic Grover search algorithm in a local region, we haven't
found a consistent way to treat quantum probability measures
in general.

Finally, we shift our attention
to consider quantum interval-valued probability measures (IVPMs),
which potentially embody both finite precision measurement and
a sensible correspondence to standard quantum probability.
This interval-valued framework not only provides a natural generalization
of both classical IVPMs and conventional quantum probability measures,
but also establishes bounds on the validity of the Kochen-Specker
and Gleason theorems in realistic experimental environments.

\end{abstract*}

### 2018-12-01 dissertation.tex
From: Hanson, Andrew J. <hansona@indiana.edu> Sent: Thursday, November 29, 2018 13:24 To: Tai, Yu-Tsung <yuttai@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: CV...abstract edits...

@@
 contains four different theories each have different pros and cons.
-The abstract should said them seperately and explicitly.'' }Most
-of the quantum computing models are based on the continuum of real
-numbers, despite the fact that classical digital computers faithfully
-realize the prediction of discrete computational models, while analog
-computers in reality are far weaker than the theoretical prediction
-of continuous computational models. Since one of the important factors
-of this gap is the measurement precision, we hope to build a more
-faithful model by investigating discrete quantum computing models
-and incorporating the idea of finite precision measurement into the
+The abstract should said them separately and explicitly.'' }
+
+Most quantum computing models are based on the continuum of real numbers,
+while classical digital computers faithfully realize only discrete
+computational models. Analog computers appear to be an option, but
+in reality are far weaker than would be needed for computational models
+requiring real numbers. One approach to resolving this conflict is
+to find consistent mathematical ways to limit measurement precision
+to computable contexts that do not require incomputable real numbers.
+Our goal is to build a more philosophically consistent models by investigating
+discrete quantum computing using finite number systems, and, alternatively,
+by incorporating finite precision measurement using intervals into
 quantum theory.
 
-We first replace the continuum of complex numbers by discrete finite
-fields in the quantum theory. The simplest theory, defined over unrestricted
-finite fields, is so weak that it cannot express Deutsch's algorithm.
-This quantum theory is, however, also so powerful that it can be used
-to solve the $\usat$ problem, which is as hard as a general $\NP$-complete
-problem. The second framework employs only finite fields with no solution
-to $x^{2}+1=0$, and thus permits an elegant complex representation
-of the extended field by adjoining $\rmi=\sqrt{-1}$. Because the
-states of a discrete $n$-qubit system are in principle enumerable,
-we can count the number of states, and determine the proportions of
-entangled and unentangled states. Although this improved framework
-allows the probabilistic Grover search algorithm in a local region,
-we haven't found sensible correspondences between quantum probability
-measures and the whole state space in general.
-
-To search a sensible correspondence and to incorporate the idea of
-finite precision measurement at the same time, we shift our attention
-to consider quantum interval-valued probability measures (IVPMs).
-This interval-valued framework not only provides a natural generalization
-of both classical IVPMs and conventional quantum probability measures,
-but also establishes bounds on the validity of the Kochen-Specker
+We begin by replacing the continuum of complex numbers by discrete
+finite fields in quantum theory. The simplest theory, defined over
+unrestricted finite fields, is so weak that it cannot express Deutsch's
+algorithm, but, paradoxically, is also so powerful that it can be
+used to solve the $\usat$ problem, which is as hard as a general
+$\NP$-complete problem. Our second framework employs only finite
+fields over prime numbers of the form $4n+3$, which possess no solutions
+to $x^{2}+1=0$, and thus permit an elegant complex representation
+of the finite field by adjoining $\rmi=\sqrt{-1}$. Because the states
+of a discrete $n$-qubit system are in principle enumerable, we can
+count the number of states, and determine the proportions of entangled
+and unentangled states. Although this improved framework can be used
+to implement the probabilistic Grover search algorithm in a local
+region, we haven't found a consistent way to treat quantum probability
+measures in general.
+
+Finally, we shift our attention to consider quantum interval-valued
+probability measures (IVPMs), which potentially embody both finite
+precision measurement and a sensible correspondence to standard quantum
+probability. This interval-valued framework not only provides a natural
+generalization of both classical IVPMs and conventional quantum probability
+measures, but also establishes bounds on the validity of the Kochen-Specker
 and Gleason theorems in realistic experimental environments.\end{abstract*}

### 2018-12-01 abstract-ajh1.tex
From: Hanson, Andrew J. <hansona@indiana.edu> Sent: Thursday, November 29, 2018 13:34 To: Tai, Yu-Tsung <yuttai@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: abstract: better last paragraph

@@
-Corrections - A. Hanson  29 Nov 2018
+Yu-Tsun Tai's abstract:
+   Some possible edits - A. Hanson  29 Nov 2018
 
@@
 of both classical IVPMs and conventional quantum probability measures,
-but also establishes bounds on the validity of the Kochen-Specker
+but also allows us to establish bounds on the validity of the Kochen-Specker
 and Gleason theorems in realistic experimental environments.

### 2018-12-01 dissertation.tex
From: Hanson, Andrew J. <hansona@indiana.edu> Sent: Thursday, November 29, 2018 13:34 To: Tai, Yu-Tsung <yuttai@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: abstract: better last paragraph

@@
 generalization of both classical IVPMs and conventional quantum probability
-measures, but also establishes bounds on the validity of the Kochen-Specker
-and Gleason theorems in realistic experimental environments.\end{abstract*}
+measures, but also allows us to establish bounds on the validity of
+the Kochen-Specker and Gleason theorems in realistic experimental
+environments.\end{abstract*}
 

### 2018-12-02 dissertation.tex
dissertation.lyx Abstract Updating...

@@
 to computable contexts that do not require incomputable real numbers.
-Our goal is to build a more philosophically consistent models by investigating
-discrete quantum computing using finite number systems, and, alternatively,
-by incorporating finite precision measurement using intervals into
-quantum theory.
+\todo{I don't understand the previous two sentences... Maybe simplify...
+}Our goal is to build a more philosophically consistent models by
+investigating discrete quantum computing using finite number systems,
+and, alternatively, by incorporating finite precision measurement
+using intervals into quantum theory.
 
@@
 finite fields in quantum theory. The simplest theory, defined over
-unrestricted finite fields, is so weak that it cannot express Deutsch's
-algorithm, but, paradoxically, is also so powerful that it can be
-used to solve the $\usat$ problem, which is as hard as a general
-$\NP$-complete problem. Our second framework employs only finite
-fields over prime numbers of the form $4n+3$, which possess no solutions
-to $x^{2}+1=0$, and thus permit an elegant complex representation
-of the finite field by adjoining $\rmi=\sqrt{-1}$. Because the states
-of a discrete $n$-qubit system are in principle enumerable, we can
-count the number of states, and determine the proportions of entangled
-and unentangled states. Although this improved framework can be used
-to implement the probabilistic Grover search algorithm in a local
-region, we haven't found a consistent way to treat quantum probability
+unrestricted finite fields, is so weak that it only predict whether
+the measure result is possible or impossible. Its computational model
+is also weak that it cannot express Deutsch's algorithm, but, paradoxically,
+is also so powerful that it can be used to solve the $\usat$ problem,
+which is as hard as a general $\NP$-complete problem.
+
+Our second framework employs only finite fields over prime numbers
+of the form $4\ell+3$, which possess no solutions to $x^{2}+1=0$,
+and thus permit an elegant complex representation of the finite field
+by adjoining $\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit
+system are in principle enumerable, we can count the number of states,
+and determine the proportions of entangled and unentangled states.
+We tried define its measurement process in three different approaches.
+For the model only predicting possible or impossible, we have solutions
+to deterministic quantum algorithms such as Deutsch's algorithm, but
+unnaturally strong computational power may still occur. In an improved
+model, the probability of measurement results could be predicted locally.
+
+the probabilistic Grover search algorithm can be implemented in a
+local region, we haven't found a consistent way to treat quantum probability
 measures in general.
@@
 
-\tableofcontents{}
+\tableofcontents{}\todo{Reorganize the chapters and sections to
+fit the new abstract.}
 

### 2018-12-02 dissertation.tex
dissertation.lyx Abstract Updating...

@@
 
-\begin{abstract*}\todo{Rewrite the abstract so that the committee
-can sign it. Prof. Thurston: ``To address the same issue, the thesis
-contains four different theories each have different pros and cons.
-The abstract should said them separately and explicitly.'' }
-
-Most quantum computing models are based on the continuum of real numbers,
-while classical digital computers faithfully realize only discrete
-computational models. Analog computers appear to be an option, but
-in reality are far weaker than would be needed for computational models
-requiring real numbers. One approach to resolving this conflict is
-to find consistent mathematical ways to limit measurement precision
-to computable contexts that do not require incomputable real numbers.
-\todo{I don't understand the previous two sentences... Maybe simplify...
-}Our goal is to build a more philosophically consistent models by
-investigating discrete quantum computing using finite number systems,
-and, alternatively, by incorporating finite precision measurement
+\begin{abstract*}Most quantum computing models are based on the continuum
+of real numbers, while classical digital computers faithfully realize
+only discrete computational models. Analog computers appear to be
+an option, but in reality are far weaker than would be needed for
+computational models requiring real numbers. One approach to resolving
+this conflict is to find consistent mathematical ways to limit measurement
+precision to computable contexts that do not require incomputable
+real numbers. Our goal is to build a more philosophically consistent
+models by investigating discrete quantum computing using finite number
+systems, and, alternatively, by incorporating finite precision measurement
 using intervals into quantum theory.
@@
 unnaturally strong computational power may still occur. In an improved
-model, the probability of measurement results could be predicted locally.
-
-the probabilistic Grover search algorithm can be implemented in a
-local region, we haven't found a consistent way to treat quantum probability
-measures in general.
+model, the cardinal probability of measurement results could be predicted
+locally. In the local ordered region, the unnaturally computational
+power is ruled out and the probabilistic Grover search algorithm can
+be implemented. However, lacking arithmetic operations on cardinal
+probabilities, expectation values cannot be defined easily. Since
+arithmetic operations works with conventional probability measures,
+we consider quantum probability measures over finite fields, but we
+haven't found a consistent way to treat them in general.
 
@@
 
-\tableofcontents{}\todo{Reorganize the chapters and sections to
-fit the new abstract.}
+\tableofcontents{}\todo{Split Chapter~\ref{chap:DQT=000026DQC}
+into ``Quantum Theories and Computing over Unrestricted Finite Fields''
+and ``Quantum Theories and Computing over $\ff{p^{2}}$'' two chapters.
+}
 
@@
 like Shor's~\cite{Shor1999,Mermin2007,Jaeger2007}, don't localize
-their computation in a small region. Moreover, since we haven't found
-a way to manipulate the resulting cardinal probabilities, we have
-little idea how to define the mixed states and expectation values.
-To overcome these issues, we try a different approach to define a
-``conventional'' probability over finite fields axiomatically.
+their computation in a small region. \todo{Remove the discussion
+of Shor's algorithm if I cannot verify it on DQT(I) on time. }Moreover,
+since we haven't found a way to manipulate the resulting cardinal
+probabilities, we have little idea how to define the mixed states
+and expectation values. To overcome these issues, we try a different
+approach to define a ``conventional'' probability over finite fields
+axiomatically.
 

### 2018-12-02 dissertation.tex
dissertation.lyx Abstract updating...

@@
 finite fields in quantum theory. The simplest theory, defined over
-unrestricted finite fields, is so weak that it only predict whether
-the measure result is possible or impossible. Its computational model
-is also weak that it cannot express Deutsch's algorithm, but, paradoxically,
-is also so powerful that it can be used to solve the $\usat$ problem,
-which is as hard as a general $\NP$-complete problem.
+unrestricted finite fields, is so weak that it cannot express Deutsch's
+algorithm, but, paradoxically, is also so powerful that it can be
+used to solve the $\usat$ problem, which is as hard as a general
+$\NP$-complete problem.
 
@@
 and determine the proportions of entangled and unentangled states.
-We tried define its measurement process in three different approaches.
-For the model only predicting possible or impossible, we have solutions
-to deterministic quantum algorithms such as Deutsch's algorithm, but
-unnaturally strong computational power may still occur. In an improved
-model, the cardinal probability of measurement results could be predicted
-locally. In the local ordered region, the unnaturally computational
-power is ruled out and the probabilistic Grover search algorithm can
-be implemented. However, lacking arithmetic operations on cardinal
-probabilities, expectation values cannot be defined easily. Since
-arithmetic operations works with conventional probability measures,
-we consider quantum probability measures over finite fields, but we
-haven't found a consistent way to treat them in general.
+Depending on how we model the measurement process, this improved framework
+can be used to implement deterministic Deutsch's algorithm and the
+probabilistic Grover search algorithm in a local region, but we still
+haven't found a consistent way to treat quantum probability measures
+in general.
 

### 2018-12-03 dissertation.tex
dissertation.lyx Preface updating...
dissertation.lyx Split Chapter 3 into two chapters...

--- 2018-12-02 dissertation.tex
@@
 \newlength{\lyxlabelwidth}      % auxiliary length 
+\providecommand*{\code}[1]{\texttt{#1}}
 
@@
 \begin{itemize}
-\item The latest version of this thesis is in GitHub:
-\begin{verbatim}
-https://git.io/fxbuG
-\end{verbatim}
-\item Its source code is typeset using \LyX ~\cite{LyX} in:
-\begin{verbatim}
-https://git.io/fxbuE
-\end{verbatim}
+\item The latest version of this thesis is in GitHub: \code{https://git.io/fxbuG}
+\item Its source code is typeset using \LyX ~\cite{LyX} in: \code{https://git.io/fxbuE}
 \item Any comments can be left in the Issue part of the GitHub Repository:
-\begin{verbatim}
-https://git.io/fxbug
-\end{verbatim}
+\code{https://git.io/fxbug}
 \end{itemize}
@@
 
-\tableofcontents{}\todo{Split Chapter~\ref{chap:DQT=000026DQC}
-into ``Quantum Theories and Computing over Unrestricted Finite Fields''
-and ``Quantum Theories and Computing over $\ff{p^{2}}$'' two chapters.
-}
+\tableofcontents{}
 
@@
 these to other physicists work (say two more pages?). Check our previous
-papers. Explicitly say what question we wan to solve. In particular,
+papers. Explicitly say what question we want to solve. In particular,
 merging quantum mechanics and computer science is too broad for a
-thesis. }The marriage of quantum mechanics and computer science first
-envisioned and popularized by Feynman has created an awkward, but
-opportune, moment. This embarrassing dilemma was concisely summarized
-by Prof.~Aaronson that one of the the following three statements
-is false \cite{AaronsonArkhipov2011,BFRDARW2013}:
+thesis. }
+
+The marriage of quantum mechanics and computer science first envisioned
+and popularized by Feynman has created an awkward, but opportune,
+moment. This embarrassing dilemma was concisely summarized by Prof.~Aaronson
+that one of the the following three statements is false \cite{AaronsonArkhipov2011,BFRDARW2013}:
 \begin{enumerate}[label=(\roman{enumi})]
@@
 \noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical computational
-models and their physical realizations \todo{Update this table to
-include }}
+models and their physical realizations\todo{Put the third row in
+the middle alignment.}}
 \begin{tabularx}{\linewidth}{ccX}
@@
 \addlinespace
- & Model & Physical Realization\tabularnewline\addlinespace
+ & Discrete & Continuum\tabularnewline\addlinespace
 \midrule
 \addlinespace
-\addlinespace
-Continuum & BCSS machine & The precision of an analog computer was limited so that an analog computer may not reproduce the theoretical prediction reliably.\tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-Discrete & Turing machine & A digital computer can be reliably repeated with exact equivalence.\tabularnewline\addlinespace
+\midrule
+\addlinespace
+Theoretical  Model & Turing machine & BCSS machine\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Physical Realization & Digital Computer & Analog Computer\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+How the models realize? & Reliably & Not Reliably:
+\begin{itemize}
+\item The quality might be quantized.
+\item The precision of an analog computer is low.
+\end{itemize}\tabularnewline\addlinespace
 \bottomrule
@@
 
-Since conventional probability amplitude is in the field of complex
-numbers, and the field structure is essential to compute the probability
-from some probability amplitudes, we in Chapter~\ref{chap:DQT=000026DQC}
-tried to build discrete quantum theories and computing by considering
-them over finite fields.
+\todo{Beginning of Merge Left}Since conventional probability amplitude
+is in the field of complex numbers, and the field structure is essential
+to compute the probability from some probability amplitudes, we in
+Chapter~\ref{chap:DQT=000026DQC} tried to build discrete quantum
+theories and computing by considering them over finite fields.
 
@@
 and hope it could describe the physical reality and computability
-more faithful.
+more faithful.\todo{End of Merge Left}
+
+\todo{Beginning of Merge Right}We begin by replacing the continuum
+of complex numbers by discrete finite fields in quantum theory. The
+simplest theory, defined over unrestricted finite fields, is so weak
+that it only predict whether the measure result is possible or impossible.
+Its computational model is also weak that it cannot express Deutsch's
+algorithm, but, paradoxically, is also so powerful that it can be
+used to solve the $\usat$ problem, which is as hard as a general
+$\NP$-complete problem.
+
+Our second framework employs only finite fields over prime numbers
+of the form $4\ell+3$, which possess no solutions to $x^{2}+1=0$,
+and thus permit an elegant complex representation of the finite field
+by adjoining $\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit
+system are in principle enumerable, we can count the number of states,
+and determine the proportions of entangled and unentangled states.
+We tried define its measurement process in three different approaches.
+For the model only predicting possible or impossible, we have solutions
+to deterministic quantum algorithms such as Deutsch's algorithm, but
+unnaturally strong computational power may still occur. In an improved
+model, the cardinal probability of measurement results could be predicted
+locally. In the local ordered region, the unnaturally computational
+power is ruled out and the probabilistic Grover search algorithm can
+be implemented. However, lacking arithmetic operations on cardinal
+probabilities, expectation values cannot be defined easily. Since
+arithmetic operations works with conventional probability measures,
+we consider quantum probability measures over finite fields, but we
+haven't found a consistent way to treat them in general.
+
+Finally, we shift our attention to consider quantum interval-valued
+probability measures (IVPMs), which potentially embody both finite
+precision measurement and a sensible correspondence to standard quantum
+probability. This interval-valued framework not only provides a natural
+generalization of both classical IVPMs and conventional quantum probability
+measures, but also allows us to establish bounds on the validity of
+the Kochen-Specker and Gleason theorems in realistic experimental
+environments.\todo{End of Merge Right}
 
@@
 
-\chapter{Quantum Theories and Computing over Finite Fields\label{chap:DQT=000026DQC}}
+\chapter{Quantum Theories and Computing over Unrestricted Finite Fields}
 
@@
 \end{comment}
+
+\chapter{Quantum Theories and Computing over Complexified Finite Fields\label{chap:DQT=000026DQC}}
 

### 2018-12-04 dissertation.tex
prop.bib @InBook{Gisin2017} Added...

@@
 generally three or four significant figures~\cite{wiki:AnalogComputer}.
-For example, Blum, Cucker, Shub, and Smale modeled their machine to
-allow the operations of deciding whether a number is greater or equal
-to zero over real numbers and whether a number is exactly zero over
-complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}. Since
-no physical analog computer could branch in these operations based
-on a few significant figures, the theoretical prediction of Blum-Cucker-Shub-Smale
-(BCSS) machine cannot fully apply on physical devices.
+\todo{See if we can cite this paper~\cite{Gisin2017} for finite
+precision measurement. }For example, Blum, Cucker, Shub, and Smale
+modeled their machine to allow the operations of deciding whether
+a number is greater or equal to zero over real numbers and whether
+a number is exactly zero over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
+Since no physical analog computer could branch in these operations
+based on a few significant figures, the theoretical prediction of
+Blum-Cucker-Shub-Smale (BCSS) machine cannot fully apply on physical
+devices.
 

### 2018-12-04 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Add a table to summarize the results...

--- 2018-12-03 dissertation.tex
@@
 \usepackage{verbatim}
+\usepackage{rotfloat}
 \usepackage{booktabs}
@@
 
+\todo{Maybe start with this kind of sentence “We want a more faithful
+quantum theory not only because the current quantum theory don't take
+into account of the measurement precision, but also because its computational
+model doesn't fit the current development of computer science.”
+}\todo{See if we can cite this paper~\cite{Gisin2017} for finite
+precision measurement. }
+
+\todo{新的大綱：主旨：probability amplitude到底是離散還是連續的？
+\begin{itemize}
+\item Some quantities are obvious discrete, but how to model other quantities
+which we don't know?
+\begin{itemize}
+\item 一尺之槌，日取其半，萬世不竭。
+\item Zeno 追龜的故事
+\item $\sqrt{2}$是無理數謀殺案(物理量？)
+\item Euclid?(物理量？)
+\end{itemize}
+當我們的儀器不足以分辨出最小單位時，假設沒有最小單位很合理，而且可以很好的解釋我們觀察到的現象。
+\item 很多大家本來相信是連續的物理量最後被證明是離散的：
+\begin{itemize}
+\item “一尺之槌，日取其半，萬世不竭。”是錯的。
+\item 光電效應
+\item 角動量(角度？)
+\end{itemize}
+\end{itemize}
+}
+
 The marriage of quantum mechanics and computer science first envisioned
@@
 and ``ordinary'' quantum theory.}.
-
+\begin{sidewaystable}
+\caption{Comparison among our models}
+
+\centering{}%
+\begin{tabular}{ccccccc}
+\toprule 
+\addlinespace
+ & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\midrule 
+\addlinespace
+ & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+States Space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Local Region\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+in $\Fpp^{D}$\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Prediction\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+of Events\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Real-Valued\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Probability\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Possible or\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Impossible\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Possible or\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Impossible\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Cardinal\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Probability\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Real-Valued\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Probability, but no\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+sensible Born rule\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Interval-Valued\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Probability\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular}\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Expectation\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Values\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Defined &  &  & Undefined &  & Defined\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\midrule 
+\addlinespace
+ &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Hadamard\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Transformation\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Included & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+May not be\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Included\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Included & Included &  & \tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Solve\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+$\usat$\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Efficiently\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Unlikely & Yes & Partially & No &  & \tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Grover Search\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Algorithm\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Yes &  &  & Yes &  & \tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}
+\end{sidewaystable}
 \todo{Beginning of Merge Left}Since conventional probability amplitude
@@
 
-\section{Discrete Quantum Theory (I): Geometry of Entangled States}
+\section{Discrete Quantum Theory (I): Geometry of Entangled States\label{sec:Geometry-of-Entangled-States}}
 
@@
 
-\section{Discrete Quantum Theory (II)}
+\section{Discrete Quantum Theory (II)\label{sec:Discrete-Quantum-Theory-(II)}}
 

### 2018-12-05 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 
+In conventional quantum theory and computation, the probability amplitudes
+are modeled by the continuum of complex numbers. This kind of model
+doesn't take into account that human doesn't have the ability to distinguish
+quantities differing only by an arbitrarily small extent. One possibility
+is that the probability amplitudes in quantum theories are quantized.
+This leads us to consider quantum theories and computing over finite
+fields. Even if the probability amplitudes are actually continuous,
+since human has no ability to distinguish the probability computed
+by these probability amplitudes, it may be desirable to incorporate
+the idea of measurement precision into the quantum theory, and consider
+quantum interval-valued probability.
+\begin{sidewaystable}
+\caption{Comparison among our models, where the upper half of the table lists
+their quantum mechanical definitions and properties, and the lower
+half of the table lists their computational power.}
+
+\centering{}%
+\begin{tabular}{ccccccc}
+\toprule 
+\addlinespace
+ & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\midrule 
+\addlinespace
+ & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+States Space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Local Region\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+in $\Fpp^{D}$\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Prediction\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+of Events\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Real-Valued\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Probability\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Possible or\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Impossible\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Possible or\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Impossible\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Cardinal\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Probability\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Real-Valued\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Probability, but no\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+sensible Born rule\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Interval-Valued\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Probability\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular}\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Expectation\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Value\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Defined &  &  & Undefined &  & Defined\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\midrule 
+\addlinespace
+ &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Hadamard\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Transformation\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Included & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+May not be\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Included\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Included & Included &  & \tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Solve\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+$\usat$\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Efficiently\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Grover Search\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Algorithm\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Yes &  &  & Yes &  & \tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}
+\end{sidewaystable}
+\todo{Introduction Cleaned up until here.}
+
 \todo{Write a story so that physicists will also be interested in
@@
 and ``ordinary'' quantum theory.}.
-\begin{sidewaystable}
-\caption{Comparison among our models}
-
-\centering{}%
-\begin{tabular}{ccccccc}
-\toprule 
-\addlinespace
- & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
-\midrule
-\addlinespace
-\midrule 
-\addlinespace
- & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
-\midrule
-\addlinespace
-\addlinespace
-States Space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Local Region\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-in $\Fpp^{D}$\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Prediction\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-of Events\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Real-Valued\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Probability\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Possible or\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Impossible\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Possible or\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Impossible\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Cardinal\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Probability\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Real-Valued\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Probability, but no\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-sensible Born rule\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Interval-Valued\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Probability\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular}\tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Expectation\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Values\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Defined &  &  & Undefined &  & Defined\tabularnewline\addlinespace
-\midrule
-\addlinespace
-\midrule 
-\addlinespace
- &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
-\midrule
-\addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Hadamard\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Transformation\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Included & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-May not be\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Included\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Included & Included &  & \tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Solve\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-$\usat$\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Efficiently\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Unlikely & Yes & Partially & No &  & \tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Grover Search\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Algorithm\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Yes &  &  & Yes &  & \tabularnewline\addlinespace
-\bottomrule
-\addlinespace
-\end{tabular}
-\end{sidewaystable}
+
 \todo{Beginning of Merge Left}Since conventional probability amplitude

### 2018-12-05 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Add more comments...

@@
 
-In conventional quantum theory and computation, the probability amplitudes
-are modeled by the continuum of complex numbers. This kind of model
-doesn't take into account that human doesn't have the ability to distinguish
-quantities differing only by an arbitrarily small extent. One possibility
-is that the probability amplitudes in quantum theories are quantized.
-This leads us to consider quantum theories and computing over finite
-fields. Even if the probability amplitudes are actually continuous,
-since human has no ability to distinguish the probability computed
-by these probability amplitudes, it may be desirable to incorporate
-the idea of measurement precision into the quantum theory, and consider
-quantum interval-valued probability.
+In conventional quantum theory and computation, the probability amplitudes\todo{We
+haven't said the probability amplitudes in the first paragraph in
+our previous papers. I may need to replace it by a term which is not
+that technical? } are modeled by the continuum of complex numbers.
+This kind of model doesn't take into account that human doesn't have
+the ability to distinguish quantities differing only by an arbitrarily
+small extent~\cite{Turing_1937,Gisin2017}. One possibility is that
+the probability amplitudes in quantum theories are quantized. This
+leads us to consider quantum theories and computing over finite fields.
+Even if the probability amplitudes are actually continuous, since
+human has no ability to distinguish the probability computed by these
+probability amplitudes, it may be desirable to incorporate the idea
+of measurement precision into the quantum theory, and consider quantum
+interval-valued probability.
 \begin{sidewaystable}

### 2018-12-12 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

--- 2018-12-05 dissertation.tex
@@
 
-In conventional quantum theory and computation, the probability amplitudes
-are modeled by the continuum of complex numbers. This kind of model
-doesn't take into account that human doesn't have the ability to distinguish
-quantities differing only by an arbitrarily small extent. One possibility
-is that the probability amplitudes in quantum theories are quantized.
-This leads us to consider quantum theories and computing over finite
-fields. Even if the probability amplitudes are actually continuous,
-since human has no ability to distinguish the probability computed
-by these probability amplitudes, it may be desirable to incorporate
-the idea of measurement precision into the quantum theory, and consider
-quantum interval-valued probability.
+Since we as human cannot distinguish quantities differing only by
+an arbitrarily small extent \cite{Turing_1937,Gisin2017}, modeling
+quantum mechanics and computation over the continuum of complex numbers
+may not capture our ability of predicting quantum phenomenon and the
+power of quantum computation. Being agnostic about whether the reality
+is ultimately discrete or continuous, we considered two types of models
+to incorporate the limitation of distinguishability. By assuming the
+quantum states are quantized and distinguishable, instead of the conventional
+theory over the continuum of complex numbers, we considered the quantum
+theories and computing over finite fields. Shifting our attention
+from the reality to the limitation of distinguishability itself, the
+second model incorporate the finite precision measurement into the
+quantum theory called quantum interval-valued probability measures.
+
+Even before quantum mechanics is discovered, human tried to characterize
+the physical quantities and controlled the quantities and operations
+to simulate and predict unknown quantities. Discrete quantities can
+be easily characterized by whole numbers~\cite{ParkerBaldridge2004}.
+Even if the proportion of whole numbers are fractions but not whole
+numbers, the operation among fractions can be considered as the operation
+among whole numbers after we find the common denominator, and the
+resulting numbers faithfully represent the quantities they represent.
+In general, discrete computation can be reliably repeated with exact
+equivalence, and any digital computer can faithfully simulate a Turing
+machine limited only by the available memory and time~\cite{Turing_1937}.
+
+The non-apparently discrete quantities and their operations confused
+many cultures from the very beginning. An ancient Chinese philosopher
+Chuang-tzu (庄子) has expressed ``If a one-foot-long stick is cut into
+halves every day, the cutting will never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
 \begin{sidewaystable}

### 2018-12-12 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

--- 2018-12-05 dissertation.tex
@@
 
-In conventional quantum theory and computation, the probability amplitudes
-are modeled by the continuum of complex numbers. This kind of model
-doesn't take into account that human doesn't have the ability to distinguish
-quantities differing only by an arbitrarily small extent. One possibility
-is that the probability amplitudes in quantum theories are quantized.
-This leads us to consider quantum theories and computing over finite
-fields. Even if the probability amplitudes are actually continuous,
-since human has no ability to distinguish the probability computed
-by these probability amplitudes, it may be desirable to incorporate
-the idea of measurement precision into the quantum theory, and consider
-quantum interval-valued probability.
+Since we as human cannot distinguish quantities differing only by
+an arbitrarily small extent \cite{Turing_1937,Gisin2017}, quantum
+mechanics and computation based on the continuum of complex numbers
+may not capture our ability of predicting quantum phenomenon and the
+power of quantum computation. Being agnostic about whether the reality
+is ultimately discrete or continuous, we considered two types of models
+to incorporate our limitation of distinguishability. By assuming the
+quantum states are quantized and distinguishable, the continuum of
+complex numbers is replaced by finite fields which serves as the basis
+of the first type of our quantum theories and computing. We then shift
+our attention from the reality to the limitation of distinguishability
+itself, incorporate the finite precision measurement into our model,
+and consider quantum interval-valued probability measures.
+
+Even before quantum mechanics is discovered, human tried to characterize
+the physical quantities and manipulate them to simulate and predict
+unknown quantities. Discrete quantities can be easily characterized
+by whole numbers~\cite{ParkerBaldridge2004}. Even if the proportion
+of whole numbers are fractions, the operation among fractions can
+be considered as the operation among whole numbers after we find the
+common denominator, and the resulting numbers faithfully predicts
+the corresponding quantities. In general, discrete computation can
+be reliably repeated with exact equivalence, and any digital computer
+can faithfully simulate a Turing machine limited only by the available
+memory and time~\cite{Turing_1937}.
+
+In contrast, the non-apparently discrete quantities confused many
+cultures from the very beginning. Some people, including Greek mathematicians
+in the school of Pythagoras, tried to apply their discrete idea into
+their model, and believed even the mathematical models must be ultimately
+discrete. In legend, they murdered Hippasus because he found there
+is no minimum unit between a side of a square and its diagonal. Comparing
+to admit that the length of a square's diagonal is not a physical
+quantity or there is no square physically, working with a mathematical
+model without minimum unit seems more appealing, and their corresponding
+physical quantities are also assumed to be continuous. An ancient
+Chinese philosopher Chuang-tzu (庄子) expressed this belief as ``If
+a one-foot-long stick is cut into halves every day, the cutting will
+never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
+Later, these continuous quantities becomes the basic component of
+analog computers. After logarithm was discovered, a slide rule, also
+known as a slipstick, is used to compute multiplication, division,
+and more complex operations as a mechanical analog computer~\cite{wiki:SlideRule}.
+Charge amplifiers is used to build integrators \cite{wiki:Integrator,wiki:ChargeAmplifier}.
+
 \begin{sidewaystable}

### 2018-12-12 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 is ultimately discrete or continuous, we considered two types of models
-to incorporate our limitation of distinguishability. By assuming the
-quantum states are quantized and distinguishable, the continuum of
-complex numbers is replaced by finite fields which serves as the basis
-of the first type of our quantum theories and computing. We then shift
-our attention from the reality to the limitation of distinguishability
-itself, incorporate the finite precision measurement into our model,
-and consider quantum interval-valued probability measures.
+to incorporate our limitation of distinguishability into quantum theories.
+By assuming the quantum states are ultimately quantized and distinguishable,
+the first type of our quantum theories replaces the complex numbers
+by discrete finite fields. We then shift our attention to focus on
+the limitation of distinguishability itself, incorporate the finite
+precision measurement into our model, and consider quantum interval-valued
+probability measures.
 
@@
 by whole numbers~\cite{ParkerBaldridge2004}. Even if the proportion
-of whole numbers are fractions, the operation among fractions can
-be considered as the operation among whole numbers after we find the
-common denominator, and the resulting numbers faithfully predicts
-the corresponding quantities. In general, discrete computation can
-be reliably repeated with exact equivalence, and any digital computer
+of whole numbers are fractions, the operations among fractions is
+essentially the same as those among whole numbers over the common
+denominator, and the computational results faithfully represent the
+corresponding quantities. In general, discrete computation can be
+reliably repeated with exact equivalence, and any digital computer
 can faithfully simulate a Turing machine limited only by the available
@@
 In contrast, the non-apparently discrete quantities confused many
-cultures from the very beginning. Some people, including Greek mathematicians
-in the school of Pythagoras, tried to apply their discrete idea into
-their model, and believed even the mathematical models must be ultimately
-discrete. In legend, they murdered Hippasus because he found there
-is no minimum unit between a side of a square and its diagonal. Comparing
-to admit that the length of a square's diagonal is not a physical
-quantity or there is no square physically, working with a mathematical
-model without minimum unit seems more appealing, and their corresponding
-physical quantities are also assumed to be continuous. An ancient
-Chinese philosopher Chuang-tzu (庄子) expressed this belief as ``If
-a one-foot-long stick is cut into halves every day, the cutting will
-never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
+cultures since very beginning. For example, Greek mathematicians in
+the school of Pythagoras tried to apply their discrete idea into their
+model, and believed every mathematical model must be ultimately discrete.
+They believed so much that they in legend murdered Hippasus because
+he found there is no minimum unit between a side of a square and its
+diagonal. Comparing the idea that the length of a square's diagonal
+is not a physical quantity or there is no square physically, working
+with a mathematical model without minimum unit seems more appealing,
+and their corresponding physical quantities are also assumed to be
+continuous. An ancient Chinese philosopher Chuang-tzu (庄子) expressed
+this belief as ``If a one-foot-long stick is cut into halves every
+day, the cutting will never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
 Later, these continuous quantities becomes the basic component of
@@
 \noalign{\vskip\doublerulesep}
-Prediction\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-of Events\tabularnewline[\doublerulesep]
+Likelihood of\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Events is\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Predicted by\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-\end{tabular} & Defined &  &  & Undefined &  & Defined\tabularnewline\addlinespace
+\end{tabular} & Defined & Undefined & Undefined & Undefined &  & Defined\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+Contextuality & Yes & Supercontextuality &  &  &  & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Yes when Measurement\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+Precise Enough\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular}\tabularnewline\addlinespace
 \midrule

### 2018-12-13 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 \setotherlanguage{arabic}
+\setotherlanguage{turkish}
 \usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
@@
 Judge and Prof. Matthias Weber; directors of Ph.D. study in Computer
-Science, especially Prof. Yuqing Melanie Wu (吴愈青) and Prof. Funda
-Ergun.
-
-Thank Kin Wai Chan for suggesting me the correct direction for Propsition~\ref{appH.sec},
+Science, especially Prof. Yuqing Melanie Wu (吴愈青) and Prof. \textturkish{Funda
+Ergun}.
+
+Thank Kin Wai Chan for suggesting me the correct direction for Proposition~\ref{appH.sec},
 Prof. 朱樺 for drawing my attention on Prof. Wan's book~\cite{Wan2006},
@@
 
-Even before quantum mechanics is discovered, human tried to characterize
-the physical quantities and manipulate them to simulate and predict
-unknown quantities. Discrete quantities can be easily characterized
-by whole numbers~\cite{ParkerBaldridge2004}. Even if the proportion
-of whole numbers are fractions, the operations among fractions is
-essentially the same as those among whole numbers over the common
-denominator, and the computational results faithfully represent the
-corresponding quantities. In general, discrete computation can be
-reliably repeated with exact equivalence, and any digital computer
+After first suggesting by Richard Feynman and 40 years theoretical
+developments~\cite{Feynman1982Simulating}, IBM, Rigetti, Google,
+Microsoft, and many other companies start to build realistic quantum
+computers to simulate chemical molecules for drug development and
+to improving the classical algorithms like artificial and machine
+learning \cite{Shieber2018,Kahn2019}. Before we dive into the issue
+between our limitation of distinguishability and quantum theories
+and computing, it is instructive to review how classical physical
+quantities are characterized and computed.
+
+Discrete quantities can be easily characterized by whole numbers~\cite{ParkerBaldridge2004}.
+Even if the proportion of whole numbers are fractions, the operations
+among fractions is essentially the same as those among whole numbers
+over the common denominator, and the computational results faithfully
+represent the corresponding quantities. In general, discrete computation
+can be reliably repeated with exact equivalence, and any digital computer
 can faithfully simulate a Turing machine limited only by the available
@@
 \addlinespace
-States Space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & %
+States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & %
 \begin{tabular}{c}
 \noalign{\vskip\doublerulesep}
-Local Region\tabularnewline[\doublerulesep]
+Local region\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Likelihood of\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Events is\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Predicted by\tabularnewline[\doublerulesep]
+Likelihood\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+of events is\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+predicted by\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Real-Valued\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Probability\tabularnewline[\doublerulesep]
+Real-valued\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+probability\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Impossible\tabularnewline[\doublerulesep]
+impossible\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Probability\tabularnewline[\doublerulesep]
+probability\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Real-Valued\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Probability, but no\tabularnewline[\doublerulesep]
+Real-valued\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+probability, but no\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Interval-Valued\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Probability\tabularnewline[\doublerulesep]
+Interval-valued\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+probability\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Value\tabularnewline[\doublerulesep]
+value\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Yes when Measurement\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Precise Enough\tabularnewline[\doublerulesep]
+Yes when measuring\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+precise enough\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Transformation\tabularnewline[\doublerulesep]
+transformation\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Included\tabularnewline[\doublerulesep]
+included\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Efficiently\tabularnewline[\doublerulesep]
+efficiently\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}
@@
 \noalign{\vskip\doublerulesep}
-Grover Search\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-Algorithm\tabularnewline[\doublerulesep]
+Grover search\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+algorithm\tabularnewline[\doublerulesep]
 \noalign{\vskip\doublerulesep}

### 2018-12-13 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 \setotherlanguage{arabic}
+\setotherlanguage{italian}
 \setotherlanguage{turkish}
@@
 power of quantum computation. Being agnostic about whether the reality
-is ultimately discrete or continuous, we considered two types of models
-to incorporate our limitation of distinguishability into quantum theories.
-By assuming the quantum states are ultimately quantized and distinguishable,
-the first type of our quantum theories replaces the complex numbers
-by discrete finite fields. We then shift our attention to focus on
-the limitation of distinguishability itself, incorporate the finite
-precision measurement into our model, and consider quantum interval-valued
-probability measures.
-
-After first suggesting by Richard Feynman and 40 years theoretical
-developments~\cite{Feynman1982Simulating}, IBM, Rigetti, Google,
-Microsoft, and many other companies start to build realistic quantum
-computers to simulate chemical molecules for drug development and
-to improving the classical algorithms like artificial and machine
-learning \cite{Shieber2018,Kahn2019}. Before we dive into the issue
-between our limitation of distinguishability and quantum theories
-and computing, it is instructive to review how classical physical
-quantities are characterized and computed.
+is ultimately discrete or continuous, we considered two types of quantum
+models to incorporate our limitation of distinguishability. By assuming
+the quantum states are ultimately quantized and distinguishable, our
+first type of quantum theories replaces the complex numbers by discrete
+finite fields. We then focus on the limitation of distinguishability
+itself, incorporate the finite precision measurement into our model,
+and consider quantum interval-valued probability measures.
+
+After first suggesting by Richard Feynman 40 years ago~\cite{Feynman1982Simulating},
+IBM, \textitalian{Rigetti}, Google, Microsoft, and many other companies
+and countries start to build realistic quantum computers \cite{Shieber2018,Kahn2019},
+and seek more efficient ways to simulate chemical molecules and to
+break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}. Despite
+how we compute these two tasks, we can notice they require us to compute
+two different types of quantities. While RSA requires discrete computation,
+it is beyond our ability to distinguish whether the quantities required
+by simulating molecules are discrete or not. Before discussing the
+quantities characterizing and computing with quantum mechanics, it
+is instructive to review how classical physical quantities are characterized
+and computed.
 

### 2018-12-13 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 Since we as human cannot distinguish quantities differing only by
-an arbitrarily small extent \cite{Turing_1937,Gisin2017}, quantum
-mechanics and computation based on the continuum of complex numbers
-may not capture our ability of predicting quantum phenomenon and the
-power of quantum computation. Being agnostic about whether the reality
-is ultimately discrete or continuous, we considered two types of quantum
+an arbitrarily small extent \cite{Turing_1937,Gisin2017}, the quantum
+mechanical model based on the continuum of complex numbers may not
+capture our ability of predicting quantum phenomenon and the power
+of quantum computation. Being agnostic about whether the reality is
+ultimately discrete or continuous, we considered two types of quantum
 models to incorporate our limitation of distinguishability. By assuming
@@
 IBM, \textitalian{Rigetti}, Google, Microsoft, and many other companies
-and countries start to build realistic quantum computers \cite{Shieber2018,Kahn2019},
-and seek more efficient ways to simulate chemical molecules and to
-break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}. Despite
-how we compute these two tasks, we can notice they require us to compute
-two different types of quantities. While RSA requires discrete computation,
-it is beyond our ability to distinguish whether the quantities required
-by simulating molecules are discrete or not. Before discussing the
-quantities characterizing and computing with quantum mechanics, it
-is instructive to review how classical physical quantities are characterized
-and computed.
+and countries start to build realistic quantum computers recently
+\cite{Shieber2018,Kahn2019}, and seek more efficient ways to simulate
+chemical molecules and to break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}.
+No matter whether we use classical or quantum computers to solve these
+two tasks, we notice that they require two different types of quantities.
+The quantities required by RSA are discrete, and it is beyond our
+ability to distinguish whether the quantities required by simulating
+molecules are discrete or not. Before we dive into the discussion
+of these quantities in quantum computation, it is instructive to review
+how classical quantities are characterized and computed.
 
@@
 Even if the proportion of whole numbers are fractions, the operations
-among fractions is essentially the same as those among whole numbers
-over the common denominator, and the computational results faithfully
-represent the corresponding quantities. In general, discrete computation
-can be reliably repeated with exact equivalence, and any digital computer
+among fractions are essentially the same as those among whole numbers
+over the common denominator. In general, discrete computation can
+be reliably repeated with exact equivalence, and any digital computer
 can faithfully simulate a Turing machine limited only by the available
@@
 In contrast, the non-apparently discrete quantities confused many
-cultures since very beginning. For example, Greek mathematicians in
-the school of Pythagoras tried to apply their discrete idea into their
-model, and believed every mathematical model must be ultimately discrete.
-They believed so much that they in legend murdered Hippasus because
-he found there is no minimum unit between a side of a square and its
+cultures since very beginning. On one hand, the ancient Chinese philosopher
+Chuang-tzu (庄子) didn't believe these quantities have a minimum unit,
+and expressed ``If a one-foot-long stick is cut into halves every
+day, the cutting will never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
+On the other hand, Greek mathematicians in the school of Pythagoras
+believed every mathematical model must be ultimately discrete. They
+believed so much that they in legend murdered Hippasus because he
+found there is no minimum unit between a side of a square and its
 diagonal. Comparing the idea that the length of a square's diagonal
 is not a physical quantity or there is no square physically, working
-with a mathematical model without minimum unit seems more appealing,
-and their corresponding physical quantities are also assumed to be
-continuous. An ancient Chinese philosopher Chuang-tzu (庄子) expressed
-this belief as ``If a one-foot-long stick is cut into halves every
-day, the cutting will never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
-Later, these continuous quantities becomes the basic component of
-analog computers. After logarithm was discovered, a slide rule, also
-known as a slipstick, is used to compute multiplication, division,
-and more complex operations as a mechanical analog computer~\cite{wiki:SlideRule}.
-Charge amplifiers is used to build integrators \cite{wiki:Integrator,wiki:ChargeAmplifier}.
+with a mathematical model without minimum unit seems more appealing.
+Since the mathematical model is continuous, their corresponding physical
+quantities are also assumed to be continuous. Later, these continuous
+quantities becomes the basic component of analog computers. After
+logarithm was discovered, a slide rule, also known as a slipstick,
+is used to compute multiplication, division, and more complex operations
+as a mechanical analog computer~\cite{wiki:SlideRule}. Charge amplifiers
+is used to build electrical analog computers and compute the integration
+in calculus \cite{wiki:Integrator,wiki:ChargeAmplifier}.
 

### 2018-12-14 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 capture our ability of predicting quantum phenomenon and the power
-of quantum computation. Being agnostic about whether the reality is
-ultimately discrete or continuous, we considered two types of quantum
-models to incorporate our limitation of distinguishability. By assuming
-the quantum states are ultimately quantized and distinguishable, our
-first type of quantum theories replaces the complex numbers by discrete
-finite fields. We then focus on the limitation of distinguishability
-itself, incorporate the finite precision measurement into our model,
-and consider quantum interval-valued probability measures.
-
-After first suggesting by Richard Feynman 40 years ago~\cite{Feynman1982Simulating},
+of realistic quantum computers. To incorporate our limitation of distinguishability,
+but agnostic about whether the reality is ultimately discrete or continuous,
+we considered two types of quantum models. By assuming the quantum
+states are ultimately discrete and distinguishable, our first type
+of quantum theories replaces the complex numbers by finite fields.
+We then focus on the limitation of distinguishability itself, incorporate
+the finite precision measurement into our model, and consider quantum
+interval-valued probability measures.
+
+After first suggested by Richard Feynman 40 years ago~\cite{Feynman1982Simulating},
 IBM, \textitalian{Rigetti}, Google, Microsoft, and many other companies
@@
 No matter whether we use classical or quantum computers to solve these
-two tasks, we notice that they require two different types of quantities.
-The quantities required by RSA are discrete, and it is beyond our
+two tasks, they require two different types of quantities. The question
+and answer of RSA are both discrete integers, but it is beyond our
 ability to distinguish whether the quantities required by simulating
@@
 
-Discrete quantities can be easily characterized by whole numbers~\cite{ParkerBaldridge2004}.
-Even if the proportion of whole numbers are fractions, the operations
-among fractions are essentially the same as those among whole numbers
-over the common denominator. In general, discrete computation can
-be reliably repeated with exact equivalence, and any digital computer
-can faithfully simulate a Turing machine limited only by the available
-memory and time~\cite{Turing_1937}.
+Discrete quantities can be easily characterized by integers~\cite{ParkerBaldridge2004}.
+Even if the proportion of integers are fractions, the operations among
+fractions are essentially the same as those among integers over the
+common denominator. In general, discrete computation can be reliably
+repeated with exact equivalence, and any digital computer can faithfully
+simulate a Turing machine limited only by the available memory and
+time~\cite{Turing_1937}.
 
 In contrast, the non-apparently discrete quantities confused many
-cultures since very beginning. On one hand, the ancient Chinese philosopher
+cultures since very beginning. For example, the ancient Chinese philosopher
 Chuang-tzu (庄子) didn't believe these quantities have a minimum unit,
@@
 day, the cutting will never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
-On the other hand, Greek mathematicians in the school of Pythagoras
-believed every mathematical model must be ultimately discrete. They
-believed so much that they in legend murdered Hippasus because he
-found there is no minimum unit between a side of a square and its
-diagonal. Comparing the idea that the length of a square's diagonal
-is not a physical quantity or there is no square physically, working
-with a mathematical model without minimum unit seems more appealing.
-Since the mathematical model is continuous, their corresponding physical
-quantities are also assumed to be continuous. Later, these continuous
-quantities becomes the basic component of analog computers. After
-logarithm was discovered, a slide rule, also known as a slipstick,
-is used to compute multiplication, division, and more complex operations
-as a mechanical analog computer~\cite{wiki:SlideRule}. Charge amplifiers
-is used to build electrical analog computers and compute the integration
-in calculus \cite{wiki:Integrator,wiki:ChargeAmplifier}.
+As another example, Greek mathematicians in the school of Pythagoras
+believed every mathematical model must be ultimately discrete, and
+they in legend murdered Hippasus because he proved there is no minimum
+unit between a side of a square and its diagonal. Comparing the idea
+that the length of a square's diagonal is not a physical quantity
+or there is no square physically, working with a mathematical model
+without minimum unit seems more appealing. Since the mathematical
+model is continuous, their corresponding physical quantities are naturally
+assumed to be continuous. Later, these continuous quantities becomes
+the basic component of analog computers. After logarithm was discovered,
+a slide rule, also known as a slipstick, is used to compute multiplication,
+division, and more complex operations as a mechanical analog computer~\cite{wiki:SlideRule}.
+Charge amplifiers are used to build electrical analog computers and
+compute the integration in calculus \cite{wiki:Integrator,wiki:ChargeAmplifier}.
+
+Although assuming physical quantities is as continuous as their mathematical
+models are convenience, the physical quantities discussed in previous
+paragraph are not simply real numbers. Chuang-tzu's stick are made
+by molecules and cannot be cut in halves endlessly. The input charge
+of an integrator an must actually be an integer multiple of the elementary
+charge. A prefect square cannot be draw physically. It is beyond our
+ability to decide whether a prefect square exists in the space because
+whether space itself is ultimately discrete or continuous is still
+an solved question. Even if it exists, human have no ability to distinguish
+them from an almost prefect square differing only by an arbitrarily
+small extent. Similar situation applying to the length of a slide
+rule, it is beyond our ability to decide whether its length is ultimately
+discrete or continuous. Even if it is continuous, there is no way
+to identify which real number represents the length of a slide rule.
+As the results, even if analog computers really store real numbers,
+they cannot be read, write, and use to its exact value to branch the
+computation. The opposite of the last condition sometimes is assumed
+by real computational models. For example, Blum, Cucker, Shub, and
+Smale modeled their BCSS machine to allow the operations of deciding
+whether a number is greater or equal to zero over real numbers and
+whether a number is exactly zero over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
+Therefore, the computational power of analog computers is far weaker
+than their theoretical prediction.
+
+\begin{table}
+\caption{\label{tab:Comparison}Comparison between the classical quantities
+and their mathematical models}
+
+\centering{}%
+\begin{tabular}{cccc}
+\toprule 
+\addlinespace
+Physical quantities & Discrete & %
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Discrete with\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+extreme small unit\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & We don't know\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+Computational devices & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+\begin{tabular}{c}
+\noalign{\vskip\doublerulesep}
+Mathematical\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\noalign{\vskip\doublerulesep}
+representation\tabularnewline[\doublerulesep]
+\noalign{\vskip\doublerulesep}
+\end{tabular} & Integers & Real numbers & Real numbers\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+Computational model  & Turing machine & BCSS machine & BCSS machine\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+How the models realize? & Reliably & Not reliably & Not reliably\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}
+\end{table}
+The situations for classical quantities and the computational power
+above them are summarized in Table~\ref{tab:Comparison}, and similar
+situations could potentially be applied to quantum mechanics and computation.
+The physical quantity manipulated by the quantum circuit model, the
+most widely used model of quantum computing, is the probability amplitudes
+of states. \todo{Introduction Cleaned up until here. }Because we
+are agnostic about whether probability amplitude is quantized or can
+really be valued in the continuum of complex numbers, we tried to
+develop two different types of models: the quantum theories and computing
+over finite fields are discrete models, and the quantum interval-valued
+probability measures incorporate the idea of measurement precision
+into the quantum theory. To distinguish the modified quantum theories
+from the usual ones, the usual ones will be called the ``conventional
+quantum theory'' where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+and ``ordinary'' quantum theory.}.
 
@@
 \addlinespace
-\addlinespace
-Contextuality & Yes & Supercontextuality &  &  &  & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Yes when measuring\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-precise enough\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular}\tabularnewline\addlinespace
-\midrule
-\addlinespace
 \midrule 
@@
 \end{sidewaystable}
-\todo{Introduction Cleaned up until here.}
-
-\todo{Write a story so that physicists will also be interested in
-this thesis. For example, quantum simulation problem and how to apply
-these to other physicists work (say two more pages?). Check our previous
-papers. Explicitly say what question we want to solve. In particular,
-merging quantum mechanics and computer science is too broad for a
-thesis. }
-
-\todo{Maybe start with this kind of sentence “We want a more faithful
-quantum theory not only because the current quantum theory don't take
-into account of the measurement precision, but also because its computational
-model doesn't fit the current development of computer science.”
-}\todo{See if we can cite this paper~\cite{Gisin2017} for finite
-precision measurement. }
-
-\todo{新的大綱：主旨：probability amplitude到底是離散還是連續的？
-\begin{itemize}
-\item Some quantities are obvious discrete, but how to model other quantities
-which we don't know?
-\begin{itemize}
-\item 一尺之槌，日取其半，萬世不竭。
-\item Zeno 追龜的故事
-\item $\sqrt{2}$是無理數謀殺案(物理量？)
-\item Euclid?(物理量？)
-\end{itemize}
-當我們的儀器不足以分辨出最小單位時，假設沒有最小單位很合理，而且可以很好的解釋我們觀察到的現象。
-\item 很多大家本來相信是連續的物理量最後被證明是離散的：
-\begin{itemize}
-\item “一尺之槌，日取其半，萬世不竭。”是錯的。
-\item 光電效應
-\item 角動量(角度？)
-\end{itemize}
-\end{itemize}
-}
-
-The marriage of quantum mechanics and computer science first envisioned
-and popularized by Feynman has created an awkward, but opportune,
-moment. This embarrassing dilemma was concisely summarized by Prof.~Aaronson
-that one of the the following three statements is false \cite{AaronsonArkhipov2011,BFRDARW2013}:
-\begin{enumerate}[label=(\roman{enumi})]
-\item \label{enu:Textbook-quantum-mechanics}Textbook quantum mechanics
-is correct. 
-\item \label{enu:no-efficient-classical-factoring}There does not exist
-an efficient classical factoring algorithm. 
-\item \label{enu:extended-Church-Turing-Thesis}The extended Church-Turing
-thesis — that probabilistic Turing machines can efficiently simulate
-any physically realizable model of computation — is correct \cite{Bernstein:1993:QCT:167088.167097,Kaye2007}. 
-\end{enumerate}
-There is overwhelming evidence to support each of these statements.
-The theoretical framework of quantum mechanics \ref{enu:Textbook-quantum-mechanics}
-has withstood decades of experimental confirmation. Entire industries
-are founded on the assumption \ref{enu:no-efficient-classical-factoring}
-that algorithms like RSA are secure and they also have withstood years
-of attempted attacks \cite{boneh1999twenty,wiki:RSAFactoring}. Finally
-the entire field of complexity theory in computer science which has
-also withstood years of field testing rests, in essence, on assumption
-\ref{enu:extended-Church-Turing-Thesis} \cite{Aaronson2005,Piccinini2015}.
-And yet at least one of these three statements \emph{must be false}!
-Indeed if there is a corresponding efficient classical factoring algorithm,
-then we concede \ref{enu:no-efficient-classical-factoring}. If it
-is correct that Shor's efficient factoring algorithm is realizable,
-and we can prove there is no efficient classical factoring algorithm,
-then we concede \ref{enu:extended-Church-Turing-Thesis}. Otherwise,
-if we cannot implement Shor's algorithm no matter how hard we try,
-textbook quantum mechanics, i.e., \ref{enu:Textbook-quantum-mechanics}
-may need to be improved by a better theory. It is unlikely that there
-will be a simple resolution to this awkward situation. It is more
-likely that the resolution will emerge from deep and careful analyses
-of the foundations of each field.
-
-When we check the compatibility between quantum mechanics and computer
-science, we found one of the biggest difference is that the success
-of digital computers is based on discrete computation while quantum
-physics is usually based on the continuum of real and complex numbers.
-This suggests whether the computational model is discrete or continuous
-may be another important factor parallel to \todo{Find a phrase better
-than ``parallel to''. }whether the model is classical or quantum.
-\todo{Add discussion about randomness, like: ``Another big difference
-is that randomness in quantum computing is inherited from its underlying
-quantum physics while randomness in probabilistic Turing machine is
-an addition feature acquired by adding random bits to a Turing machine.''
-}Although building a realistic quantum computer is an ongoing project~\cite{Shieber2018},
-reviewing the challenge posed by classical discrete and continuous
-models might provide what we are facing when moving on to the quantum
-world.
-
-There was a long history that human believe they can compute with
-the continuum of real numbers. If the length of a line segment represents
-a real number, Euclid thought he could use an unmarked ruler and a
-compass to compute the real numbers about 300 B.C~\cite{MCC2006}.
-After logarithm was discovered, a slide rule, also known as a slipstick,
-is used to compute multiplication, division, and more complex operations
-as a mechanical analog computer~\cite{wiki:SlideRule}. Although
-more and more complex analog computers, like integrators \cite{wiki:Integrator,wiki:ChargeAmplifier},
-is used, there is still a gap between the computation preformed in
-an analog computer and the idealized operations among real numbers.
-One problem is that the quality computed by an analog computer might
-actually be quantized. For example, charge amplifier is believed to
-produce the integrated value of the input current~\cite{wiki:ChargeAmplifier}
-although the input charge must actually be an integer multiple of
-the elementary charge~\cite{wiki:ElementaryCharge}. Even for the
-qualities which doesn't known to be quantized, the observed computational
-power of an analog computer might still be weaker than the theoretical
-prediction because the precision of an analog computer is limited
-generally three or four significant figures~\cite{wiki:AnalogComputer}.
-For example, Blum, Cucker, Shub, and Smale modeled their machine to
-allow the operations of deciding whether a number is greater or equal
-to zero over real numbers and whether a number is exactly zero over
-complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}. Since
-no physical analog computer could branch in these operations based
-on a few significant figures, the theoretical prediction of Blum-Cucker-Shub-Smale
-(BCSS) machine cannot fully apply on physical devices.
-
-Being aware that symbols within a computation should not differ to
-an arbitrarily small extent~\cite{Turing_1937}, Turing defined his
-machine with only finite number of symbols and configurations. One
-of the benefit of discrete computation is that it can be reliably
-repeated with exact equivalence. Therefore, any digital computer can
-faithfully simulate a Turing machine limited only by the available
-memory and time.
-
-\begin{table}
-\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical computational
-models and their physical realizations\todo{Put the third row in
-the middle alignment.}}
-\begin{tabularx}{\linewidth}{ccX}
-\toprule 
-\addlinespace
- & Discrete & Continuum\tabularnewline\addlinespace
-\midrule
-\addlinespace
-\midrule
-\addlinespace
-Theoretical  Model & Turing machine & BCSS machine\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-Physical Realization & Digital Computer & Analog Computer\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-How the models realize? & Reliably & Not Reliably:
-\begin{itemize}
-\item The quality might be quantized.
-\item The precision of an analog computer is low.
-\end{itemize}\tabularnewline\addlinespace
-\bottomrule
-\addlinespace
-\end{tabularx}
-\end{table}
-The situations for classical computation is summarized in Table~\ref{tab:Comparison},
-and similar situations could potentially be applied to quantum computation.
-\todo{Introduction cleaning up until here. }Similar to classical
-analog computers manipulating, say, the position of substance, the
-most widely used model of quantum computing, the quantum circuit model,
-manipulates the probability amplitudes to do the computation. \todo{Play
-with some cloud quantum computers to see if I can find more support
-evidence. }Because we are agnostic about whether probability amplitude
-is quantized or can really be valued in the continuum of complex numbers,
-we tried to develop two different types of models: the quantum theories
-and computing over finite fields are discrete models, and the quantum
-interval-valued probability measures incorporate the idea of measurement
-precision into the quantum theory. To distinguish the modified quantum
-theories from the usual ones, the usual ones will be called the ``conventional
-quantum theory'' where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
-and ``ordinary'' quantum theory.}.
-
 \todo{Beginning of Merge Left}Since conventional probability amplitude

### 2018-12-16 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 \usepackage{tabularx}
+\newcolumntype{Y}{>{\centering\doublespacing\arraybackslash}X}
 
@@
 Since we as human cannot distinguish quantities differing only by
-an arbitrarily small extent \cite{Turing_1937,Gisin2017}, the quantum
-mechanical model based on the continuum of complex numbers may not
-capture our ability of predicting quantum phenomenon and the power
-of realistic quantum computers. To incorporate our limitation of distinguishability,
-but agnostic about whether the reality is ultimately discrete or continuous,
-we considered two types of quantum models. By assuming the quantum
-states are ultimately discrete and distinguishable, our first type
-of quantum theories replaces the complex numbers by finite fields.
-We then focus on the limitation of distinguishability itself, incorporate
-the finite precision measurement into our model, and consider quantum
-interval-valued probability measures.
+an arbitrarily small extent \cite{Turing_1937,Gisin2017}, we want
+to incorporate this limitation into our quantum mechanical model to
+better capture our ability of predicting quantum phenomenon and the
+power of realistic quantum computers. Since we are agnostic about
+whether the reality is ultimately discrete or continuous, we considered
+two types of quantum models. By assuming the quantum states are ultimately
+discrete and distinguishable, our first type of quantum theories replaces
+the complex numbers by finite fields. We then focus on the limitation
+of distinguishability itself, incorporate the finite precision measurement
+into our model, and consider quantum interval-valued probability measures.
 
@@
 chemical molecules and to break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}.
-No matter whether we use classical or quantum computers to solve these
-two tasks, they require two different types of quantities. The question
-and answer of RSA are both discrete integers, but it is beyond our
-ability to distinguish whether the quantities required by simulating
-molecules are discrete or not. Before we dive into the discussion
-of these quantities in quantum computation, it is instructive to review
+No matter how, classical or quantum, to attack these two tasks, they
+require two different types of quantities. On one hand, the question
+and answer of RSA are both discrete integers. On the other hand, even
+if the quantities describing molecules are considered as continuous,
+we want to argue that it is beyond our ability to decide these quantities,
+including the coordinate of the wave functions, are ultimately discrete
+or continuous. To better understand this issue without struggling
+with their meaning in the quantum theory, it is instructive to review
 how classical quantities are characterized and computed.
@@
 model is continuous, their corresponding physical quantities are naturally
-assumed to be continuous. Later, these continuous quantities becomes
+assumed to be continuous. Later, these continuous quantities become
 the basic component of analog computers. After logarithm was discovered,
@@
 
-Although assuming physical quantities is as continuous as their mathematical
-models are convenience, the physical quantities discussed in previous
-paragraph are not simply real numbers. Chuang-tzu's stick are made
-by molecules and cannot be cut in halves endlessly. The input charge
-of an integrator an must actually be an integer multiple of the elementary
-charge. A prefect square cannot be draw physically. It is beyond our
-ability to decide whether a prefect square exists in the space because
-whether space itself is ultimately discrete or continuous is still
-an solved question. Even if it exists, human have no ability to distinguish
-them from an almost prefect square differing only by an arbitrarily
-small extent. Similar situation applying to the length of a slide
-rule, it is beyond our ability to decide whether its length is ultimately
-discrete or continuous. Even if it is continuous, there is no way
-to identify which real number represents the length of a slide rule.
+Although it is convenient to assume physical quantities is as continuous
+as their mathematical models, the physical quantities discussed in
+previous paragraph may not simply represented by real numbers. Chuang-tzu's
+stick are made by molecules and cannot be cut in halves endlessly.
+The input charge of an integrator must actually be an integer multiple
+of the elementary charge. A prefect square cannot be draw physically.
+Even we don't draw it, but merely asking whether it exists in the
+space is still beyond our ability to answer because whether the space
+itself is ultimately discrete or continuous is still an unsolved question.
+Even if it exists, it cannot be distinguished by human from an almost
+prefect square differing only by an arbitrarily small extent. Similar
+situation applying to the length of a slide rule, it is beyond our
+ability to decide whether its length is ultimately discrete or continuous.
+Even if it is continuous, identifying which real number represents
+its length requires infinite precision, but the precision in reality
+is limited generally three or four significant figures~\cite{wiki:AnalogComputer}.
 As the results, even if analog computers really store real numbers,
 they cannot be read, write, and use to its exact value to branch the
-computation. The opposite of the last condition sometimes is assumed
+computation. The opposite of the last condition is sometimes assumed
 by real computational models. For example, Blum, Cucker, Shub, and
@@
 
-\begin{table}
+\begin{sidewaystable}
 \caption{\label{tab:Comparison}Comparison between the classical quantities
-and their mathematical models}
-
-\centering{}%
-\begin{tabular}{cccc}
+and their mathematical models. \todo{Add the quantum case, and center
+entries vertically.}}
+
+\centering{}\centering{}%
+\begin{tabularx}{\linewidth}{YcYY}
 \toprule 
 \addlinespace
-Physical quantities & Discrete & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Discrete with\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-extreme small unit\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & We don't know\tabularnewline\addlinespace
+Physical quantities & Discrete & Discrete with extreme small unit & Continuous?\tabularnewline\addlinespace
 \addlinespace
@@
 Computational devices & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
+\addlinespace
 \midrule
 \addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Mathematical\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-representation\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Integers & Real numbers & Real numbers\tabularnewline\addlinespace
+Mathematical representation & Integers & Real numbers & Real numbers\tabularnewline\addlinespace
 \addlinespace
@@
 Computational model  & Turing machine & BCSS machine & BCSS machine\tabularnewline\addlinespace
+\addlinespace
 \midrule
 \addlinespace
-\addlinespace
-How the models realize? & Reliably & Not reliably & Not reliably\tabularnewline\addlinespace
+How the models realize? & Reliably & 
+Not reliably, but could be represented by a faithful discrete model when the minimum unit could be manipulated with a better technology. & 
+Not reliably, because precision can never be high enough. \tabularnewline\addlinespace
 \bottomrule
 \addlinespace
-\end{tabular}
-\end{table}
+\end{tabularx}
+\end{sidewaystable}
 The situations for classical quantities and the computational power
@@
 
-\centering{}%
-\begin{tabular}{ccccccc}
+\begin{tabularx}{\linewidth}{YYYYYYY}
 \toprule 
@@
  & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
+\addlinespace
 \midrule
-\addlinespace
 \midrule 
@@
  & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
+\addlinespace
 \midrule
 \addlinespace
-\addlinespace
-States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Local region\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-in $\Fpp^{D}$\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Likelihood\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-of events is\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-predicted by\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Real-valued\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-probability\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Possible or\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-impossible\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Possible or\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-impossible\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Cardinal\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-probability\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Real-valued\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-probability, but no\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-sensible Born rule\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Interval-valued\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-probability\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular}\tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Expectation\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-value\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Defined & Undefined & Undefined & Undefined &  & Defined\tabularnewline\addlinespace
+States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
 \addlinespace
@@
 \addlinespace
+Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Expectation value & Defined & Undefined & Undefined & Undefined &  & Defined\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\midrule 
+\addlinespace
  &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
+\addlinespace
 \midrule
 \addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Hadamard\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-transformation\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Included & %
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-May not be\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-included\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Included & Included &  & \tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Solve\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-$\usat$\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-efficiently\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-\begin{tabular}{c}
-\noalign{\vskip\doublerulesep}
-Grover search\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\noalign{\vskip\doublerulesep}
-algorithm\tabularnewline[\doublerulesep]
-\noalign{\vskip\doublerulesep}
-\end{tabular} & Yes &  &  & Yes &  & \tabularnewline\addlinespace
+Hadamard transformation & Included & May not be included & Included & Included &  & \tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Solve $\usat$ efficiently & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline\addlinespace
 \bottomrule
 \addlinespace
-\end{tabular}
+\end{tabularx}
 \end{sidewaystable}

### 2018-12-17 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 chemical molecules and to break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}.
-No matter how, classical or quantum, to attack these two tasks, they
+No matter how to, classical or quantum, attack these two tasks, they
 require two different types of quantities. On one hand, the question
 and answer of RSA are both discrete integers. On the other hand, even
-if the quantities describing molecules are considered as continuous,
-we want to argue that it is beyond our ability to decide these quantities,
-including the coordinate of the wave functions, are ultimately discrete
-or continuous. To better understand this issue without struggling
-with their meaning in the quantum theory, it is instructive to review
-how classical quantities are characterized and computed.
+if the quantities describing molecules, like their positions, are
+considered as continuous, we want to argue that it is beyond our ability
+to decide whether these quantities are ultimately discrete or continuous.
+To better understand this issue without struggling with the quantum
+theory, it is instructive to review how classical quantities are characterized
+and computed.
 
@@
 without minimum unit seems more appealing. Since the mathematical
-model is continuous, their corresponding physical quantities are naturally
-assumed to be continuous. Later, these continuous quantities become
-the basic component of analog computers. After logarithm was discovered,
-a slide rule, also known as a slipstick, is used to compute multiplication,
-division, and more complex operations as a mechanical analog computer~\cite{wiki:SlideRule}.
-Charge amplifiers are used to build electrical analog computers and
-compute the integration in calculus \cite{wiki:Integrator,wiki:ChargeAmplifier}.
+models are continuous, their corresponding physical quantities are
+naturally assumed to be continuous. Later, these continuous quantities
+become the basic component of analog computers. After logarithm was
+discovered, a slide rule, also known as a slipstick, is used to compute
+multiplication, division, and more complex operations as a mechanical
+analog computer~\cite{wiki:SlideRule}. Charge amplifiers are used
+to build electrical analog computers and compute the integration in
+calculus \cite{wiki:Integrator,wiki:ChargeAmplifier}.
 
@@
 as their mathematical models, the physical quantities discussed in
-previous paragraph may not simply represented by real numbers. Chuang-tzu's
-stick are made by molecules and cannot be cut in halves endlessly.
-The input charge of an integrator must actually be an integer multiple
-of the elementary charge. A prefect square cannot be draw physically.
-Even we don't draw it, but merely asking whether it exists in the
-space is still beyond our ability to answer because whether the space
-itself is ultimately discrete or continuous is still an unsolved question.
-Even if it exists, it cannot be distinguished by human from an almost
-prefect square differing only by an arbitrarily small extent. Similar
-situation applying to the length of a slide rule, it is beyond our
-ability to decide whether its length is ultimately discrete or continuous.
-Even if it is continuous, identifying which real number represents
+the previous paragraph should not simply represented by real numbers.
+Chuang-tzu's stick are made by molecules and cannot be cut in halves
+endlessly. The input charge of an integrator must actually be an integer
+multiple of the elementary charge. A prefect square cannot be draw
+physically. Even we don't draw it, but merely asking whether it exists
+in the space is still beyond our ability to answer because whether
+the space itself is ultimately discrete or continuous is still an
+unsolved question. Even if a prefect square exists physically, we
+cannot decide whether it is really a prefect square or an almost prefect
+one differing only by an arbitrarily small extent. Similar situation
+applying to the length of a slide rule, it is beyond our ability to
+decide whether its length is ultimately discrete or continuous. Even
+if its length is continuous, identifying which real number represents
 its length requires infinite precision, but the precision in reality
@@
 As the results, even if analog computers really store real numbers,
-they cannot be read, write, and use to its exact value to branch the
-computation. The opposite of the last condition is sometimes assumed
-by real computational models. For example, Blum, Cucker, Shub, and
-Smale modeled their BCSS machine to allow the operations of deciding
+they cannot be read, written, and used to branch the computation based
+on their exact values. The opposite of the last statement is sometimes
+assumed by real computational models. For example, Blum, Cucker, Shub,
+and Smale modeled their BCSS machine to allow the operations of deciding
 whether a number is greater or equal to zero over real numbers and
@@
 Therefore, the computational power of analog computers is far weaker
-than their theoretical prediction.
+than the prediction based on this kind of theoretical models.
 
@@
 \caption{\label{tab:Comparison}Comparison between the classical quantities
-and their mathematical models. \todo{Add the quantum case, and center
-entries vertically.}}
+and their mathematical models with their inspired quantum models.
+\todo{Center entries vertically.}}
 
 \centering{}\centering{}%
-\begin{tabularx}{\linewidth}{YcYY}
+\begin{tabularx}{\linewidth}{ccYY}
 \toprule 
@@
 How the models realize? & Reliably & 
-Not reliably, but could be represented by a faithful discrete model when the minimum unit could be manipulated with a better technology. & 
+Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computation model by a better discrete model. & 
 Not reliably, because precision can never be high enough. \tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Inspired quantum models &  & Quantum Theories and Computing over Finite Fields & Quantum Interval-Valued Probability Measures (QIVPM)\tabularnewline\addlinespace
+\addlinespace
 \bottomrule
-\addlinespace
 \end{tabularx}
@@
 The situations for classical quantities and the computational power
-above them are summarized in Table~\ref{tab:Comparison}, and similar
-situations could potentially be applied to quantum mechanics and computation.
-The physical quantity manipulated by the quantum circuit model, the
-most widely used model of quantum computing, is the probability amplitudes
-of states. \todo{Introduction Cleaned up until here. }Because we
-are agnostic about whether probability amplitude is quantized or can
-really be valued in the continuum of complex numbers, we tried to
-develop two different types of models: the quantum theories and computing
-over finite fields are discrete models, and the quantum interval-valued
-probability measures incorporate the idea of measurement precision
-into the quantum theory. To distinguish the modified quantum theories
-from the usual ones, the usual ones will be called the ``conventional
-quantum theory'' where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+above them are summarized in Table~\ref{tab:Comparison} with their
+inspired quantum models. The physical quantity manipulated by the
+quantum circuit model, the most widely used model of quantum computing,
+is the probability amplitudes of states. \todo{Introduction Cleaned
+up until here. }Because we are agnostic about whether probability
+amplitude is quantized or can really be valued in the continuum of
+complex numbers, we tried to develop two different types of models:
+the quantum theories and computing over finite fields are discrete
+models, and the quantum interval-valued probability measures incorporate
+the idea of measurement precision into the quantum theory. To distinguish
+the modified quantum theories from the usual ones, the usual ones
+will be called the ``conventional quantum theory'' where necessary
+and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
 and ``ordinary'' quantum theory.}.
@@
 Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline\addlinespace
+\addlinespace
 \bottomrule
-\addlinespace
 \end{tabularx}

### 2018-12-18 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 and answer of RSA are both discrete integers. On the other hand, even
-if the quantities describing molecules, like their positions, are
-considered as continuous, we want to argue that it is beyond our ability
-to decide whether these quantities are ultimately discrete or continuous.
-To better understand this issue without struggling with the quantum
-theory, it is instructive to review how classical quantities are characterized
-and computed.
+if the quantities describing molecules, like the domain of their position
+wave functions or the probability amplitudes of a wave function, are
+considered as continuous, we want to argue that these quantities might
+later be discovered as discrete. Even if they are ultimately continuous,
+this fact may never be proved and the exact value of these quantities
+may never be pinned down. To better understand this issue without
+struggling with the quantum theory, it is instructive to review how
+classical quantities are characterized and computed.
 
@@
 Although it is convenient to assume physical quantities is as continuous
-as their mathematical models, the physical quantities discussed in
-the previous paragraph should not simply represented by real numbers.
-Chuang-tzu's stick are made by molecules and cannot be cut in halves
-endlessly. The input charge of an integrator must actually be an integer
-multiple of the elementary charge. A prefect square cannot be draw
-physically. Even we don't draw it, but merely asking whether it exists
-in the space is still beyond our ability to answer because whether
-the space itself is ultimately discrete or continuous is still an
-unsolved question. Even if a prefect square exists physically, we
-cannot decide whether it is really a prefect square or an almost prefect
-one differing only by an arbitrarily small extent. Similar situation
-applying to the length of a slide rule, it is beyond our ability to
-decide whether its length is ultimately discrete or continuous. Even
-if its length is continuous, identifying which real number represents
-its length requires infinite precision, but the precision in reality
-is limited generally three or four significant figures~\cite{wiki:AnalogComputer}.
-As the results, even if analog computers really store real numbers,
-they cannot be read, written, and used to branch the computation based
-on their exact values. The opposite of the last statement is sometimes
-assumed by real computational models. For example, Blum, Cucker, Shub,
-and Smale modeled their BCSS machine to allow the operations of deciding
-whether a number is greater or equal to zero over real numbers and
-whether a number is exactly zero over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
+as their mathematical models, each physical quantity discussed in
+the previous paragraph could not have a simple one-to-one correspondence
+with a real number. Chuang-tzu's stick are made by molecules and cannot
+be cut in halves endlessly. The input charge of an integrator must
+actually be an integer multiple of the elementary charge. A prefect
+square cannot be draw physically. Even we don't draw it, but merely
+asking whether it exists in the space is still beyond our ability
+to answer because whether the space itself is ultimately discrete
+or continuous is still an unsolved question. Even if a prefect square
+exists physically, we may not able to decide whether the “square”
+we discussed is really prefect or almost prefect differing only by
+an arbitrarily small extent. Similar situation applying to the length
+of a slide rule, it is beyond our ability to decide whether its length
+is ultimately discrete or continuous. Even if its length is continuous,
+identifying which real number represents its length requires infinite
+precision, but the precision in reality is limited generally three
+or four significant figures~\cite{wiki:AnalogComputer}. As the results,
+even if analog computers really store real numbers, they cannot be
+precisely read, written, and used to branch the computation. The opposite
+of the last statement is sometimes assumed by real computational models.
+For example, Blum, Cucker, Shub, and Smale modeled their BCSS machine
+to allow the operations of deciding whether a number is greater or
+equal to zero over real numbers and whether a number is exactly zero
+over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
 Therefore, the computational power of analog computers is far weaker
@@
 above them are summarized in Table~\ref{tab:Comparison} with their
-inspired quantum models. The physical quantity manipulated by the
+inspired quantum models. Similar to classical analog computers, the
 quantum circuit model, the most widely used model of quantum computing,
-is the probability amplitudes of states. \todo{Introduction Cleaned
-up until here. }Because we are agnostic about whether probability
-amplitude is quantized or can really be valued in the continuum of
-complex numbers, we tried to develop two different types of models:
-the quantum theories and computing over finite fields are discrete
-models, and the quantum interval-valued probability measures incorporate
-the idea of measurement precision into the quantum theory. To distinguish
+manipulates a quantity which is not discrete apparently: the probability
+amplitudes of quantum states, and it is reasonable to expect the similar
+consistence between classical classical quantities and their mathematical
+representation applies to the quantum case as well. To distinguish
 the modified quantum theories from the usual ones, the usual ones
@@
 and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
-and ``ordinary'' quantum theory.}.
-
-\begin{sidewaystable}
-\caption{Comparison among our models, where the upper half of the table lists
-their quantum mechanical definitions and properties, and the lower
-half of the table lists their computational power.}
-
-\begin{tabularx}{\linewidth}{YYYYYYY}
-\toprule 
-\addlinespace
- & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\midrule 
-\addlinespace
- & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-Expectation value & Defined & Undefined & Undefined & Undefined &  & Defined\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\midrule 
-\addlinespace
- &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-Hadamard transformation & Included & May not be included & Included & Included &  & \tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-Solve $\usat$ efficiently & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline\addlinespace
-\addlinespace
-\bottomrule
-\end{tabularx}
-\end{sidewaystable}
+and ``ordinary'' quantum theory.} On one hand, to address the assumption that the probability amplitudes
+are ultimately discrete, we consider the quantum theories and computing
+over finite fields because the conventional quantum theory is based
+on the field of complex numbers, and it is essential to have a field
+structure underlying a quantum theory. On the other hand, if the probability
+amplitudes are contiuous, we want to incorporate the idea of measurement
+precision into the quantum theory and consider the quantum interval-valued
+probability measures.
+
+\todo{Introduction Cleaned up until here. }Because we are agnostic
+about whether probability amplitude is quantized or can really be
+valued in the continuum of complex numbers, we tried to develop two
+different types of models: the quantum theories and computing over
+finite fields are discrete models, and the quantum interval-valued
+probability measures incorporate the idea of measurement precision
+into the quantum theory. .
+
 \todo{Beginning of Merge Left}Since conventional probability amplitude
@@
 environments.\todo{End of Merge Right}
+
+\begin{sidewaystable}
+\caption{Comparison among our models, where the upper half of the table lists
+their quantum mechanical definitions and properties, and the lower
+half of the table lists their computational power.}
+
+\begin{tabularx}{\linewidth}{YYYYYYY}
+\toprule 
+\addlinespace
+ & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Expectation value & Defined & Undefined & Undefined & Undefined &  & Defined\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Hadamard transformation & Included & May not be included & Included & Included &  & \tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Solve $\usat$ efficiently & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline\addlinespace
+\addlinespace
+\bottomrule
+\end{tabularx}
+\end{sidewaystable}
 

### 2018-12-20 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 No matter how to, classical or quantum, attack these two tasks, they
-require two different types of quantities. On one hand, the question
-and answer of RSA are both discrete integers. On the other hand, even
-if the quantities describing molecules, like the domain of their position
-wave functions or the probability amplitudes of a wave function, are
-considered as continuous, we want to argue that these quantities might
-later be discovered as discrete. Even if they are ultimately continuous,
+require two different types of quantities. On one hand, a question
+and its answer of RSA are both discrete integers. On the other hand,
+even if the quantities describing molecules, like the domain of their
+position wave functions or the probability amplitudes of a wave function,
+are considered as continuous, we want to argue that these quantities
+might later be discovered as discrete. Even if they were not discrete,
 this fact may never be proved and the exact value of these quantities
@@
 square cannot be draw physically. Even we don't draw it, but merely
-asking whether it exists in the space is still beyond our ability
-to answer because whether the space itself is ultimately discrete
-or continuous is still an unsolved question. Even if a prefect square
-exists physically, we may not able to decide whether the “square”
+ask whether it exists in the space. This question is still beyond
+our ability to answer because whether the space itself is ultimately
+discrete or continuous is still an unsolved question. Even if a prefect
+square exists physically, we may not able to decide whether the “square”
 we discussed is really prefect or almost prefect differing only by
@@
 How the models realize? & Reliably & 
-Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computation model by a better discrete model. & 
+Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computational power by a better discrete model. & 
 Not reliably, because precision can never be high enough. \tabularnewline\addlinespace
@@
 \end{sidewaystable}
-The situations for classical quantities and the computational power
-above them are summarized in Table~\ref{tab:Comparison} with their
-inspired quantum models. Similar to classical analog computers, the
-quantum circuit model, the most widely used model of quantum computing,
-manipulates a quantity which is not discrete apparently: the probability
-amplitudes of quantum states, and it is reasonable to expect the similar
-consistence between classical classical quantities and their mathematical
-representation applies to the quantum case as well. To distinguish
-the modified quantum theories from the usual ones, the usual ones
-will be called the ``conventional quantum theory'' where necessary
-and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
-and ``ordinary'' quantum theory.} On one hand, to address the assumption that the probability amplitudes
-are ultimately discrete, we consider the quantum theories and computing
-over finite fields because the conventional quantum theory is based
-on the field of complex numbers, and it is essential to have a field
-structure underlying a quantum theory. On the other hand, if the probability
-amplitudes are contiuous, we want to incorporate the idea of measurement
-precision into the quantum theory and consider the quantum interval-valued
-probability measures.
+The situations for classical quantities, the computational power above
+them, and their inspired quantum models are summarized in Table~\ref{tab:Comparison}.
+Similar to classical analog computers, the quantum circuit model,
+the most widely used model of quantum computing, manipulates quantities
+which are not discrete apparently: the probability amplitudes of quantum
+states. It is reasonable to expect the similar inconsistency between
+classical classical quantities and their mathematical representation
+applies to the quantum case as well. To address this issue, we will
+start from the ``conventional quantum theory'' reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+and ``ordinary'' quantum theory.}, where the probability amplitudes are in the field of complex numbers.
+On one hand, if the probability amplitudes are assumed to be ultimately
+discrete, we replace the field of complex numbers by discrete finite
+fields and consider the quantum theories and computing over finite
+fields. On the other hand, if the probability amplitudes are never
+quantized no matter how hard we try, we still should not be able to
+access their exactly values. This inaccessibility is essentially the
+same as the measurement precision should only be finite, which will
+be incorporated into the quantum theory by our quantum interval-valued
+probability measures (QIVPM) framework.
 

### 2018-12-21 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 and its answer of RSA are both discrete integers. On the other hand,
-even if the quantities describing molecules, like the domain of their
-position wave functions or the probability amplitudes of a wave function,
-are considered as continuous, we want to argue that these quantities
-might later be discovered as discrete. Even if they were not discrete,
-this fact may never be proved and the exact value of these quantities
-may never be pinned down. To better understand this issue without
-struggling with the quantum theory, it is instructive to review how
-classical quantities are characterized and computed.
+molecules are described by quantities including the domain of their
+position wave functions or the probability amplitudes of a wave function.
+Even if these quantities look like continuous, we want to argue that
+these quantities might later be discovered to be discrete. Even if
+they were not discrete, this fact may never be proved and the exact
+value of these quantities may never be pinned down. To better understand
+this issue without struggling with the quantum theory, it is instructive
+to review how classical quantities are characterized and computed.
 
@@
 discrete or continuous is still an unsolved question. Even if a prefect
-square exists physically, we may not able to decide whether the “square”
+square exists physically, we may not able to decide whether the ``square''
 we discussed is really prefect or almost prefect differing only by
@@
 over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
-Therefore, the computational power of analog computers is far weaker
-than the prediction based on this kind of theoretical models.
+Hence, even if the inputs of an analog computer and a BCSS machine
+are close to each other, their computational results might be completely
+different, like the butterfly effect, and may not be compensated by
+error analysis techniques. Therefore, the computational power of analog
+computers is far weaker than the prediction based on this kind of
+theoretical models.
 
@@
 \caption{\label{tab:Comparison}Comparison between the classical quantities
-and their mathematical models with their inspired quantum models.
-\todo{Center entries vertically.}}
+and their mathematical models with the inspired quantum models. \todo{Center
+entries vertically.}}
 
@@
 Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computational power by a better discrete model. & 
-Not reliably, because precision can never be high enough. \tabularnewline\addlinespace
+Not reliably, because precision can never be high enough, and the difference between their computational power might not be compensated by error analysis techniques. \tabularnewline\addlinespace
 \addlinespace
@@
 \end{sidewaystable}
-The situations for classical quantities, the computational power above
-them, and their inspired quantum models are summarized in Table~\ref{tab:Comparison}.
-Similar to classical analog computers, the quantum circuit model,
-the most widely used model of quantum computing, manipulates quantities
-which are not discrete apparently: the probability amplitudes of quantum
-states. It is reasonable to expect the similar inconsistency between
-classical classical quantities and their mathematical representation
-applies to the quantum case as well. To address this issue, we will
-start from the ``conventional quantum theory'' reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+The situations for classical quantities and the computational power
+above them are summarized in Table~\ref{tab:Comparison}, and the
+two possibilities dealing with real-valued models inspires us two
+types of quantum models. Similar to classical analog computers, the
+quantum circuit model, the most widely used model of quantum computing,
+manipulates quantities which are not discrete apparently: the probability
+amplitudes of quantum states. To address the similar inconsistency,
+we first review the ``conventional quantum theory'' in Chapter~\ref{chap:Conventional-Quantum-Theory}\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
 and ``ordinary'' quantum theory.}, where the probability amplitudes are in the field of complex numbers.
-On one hand, if the probability amplitudes are assumed to be ultimately
-discrete, we replace the field of complex numbers by discrete finite
-fields and consider the quantum theories and computing over finite
-fields. On the other hand, if the probability amplitudes are never
-quantized no matter how hard we try, we still should not be able to
-access their exactly values. This inaccessibility is essentially the
-same as the measurement precision should only be finite, which will
-be incorporated into the quantum theory by our quantum interval-valued
-probability measures (QIVPM) framework.
-
-\todo{Introduction Cleaned up until here. }Because we are agnostic
-about whether probability amplitude is quantized or can really be
-valued in the continuum of complex numbers, we tried to develop two
-different types of models: the quantum theories and computing over
-finite fields are discrete models, and the quantum interval-valued
-probability measures incorporate the idea of measurement precision
-into the quantum theory. .
-
-\todo{Beginning of Merge Left}Since conventional probability amplitude
-is in the field of complex numbers, and the field structure is essential
-to compute the probability from some probability amplitudes, we in
-Chapter~\ref{chap:DQT=000026DQC} tried to build discrete quantum
-theories and computing by considering them over finite fields.
-
-Since error analysis technique cannot always compensate the inevitable
-problem of measurement precision, we then incorporate the idea of
-finite precision measurement into the quantum theory in Chapter~\ref{chap:QIVPM},
-and hope it could describe the physical reality and computability
-more faithful.\todo{End of Merge Left}
-
-\todo{Beginning of Merge Right}We begin by replacing the continuum
-of complex numbers by discrete finite fields in quantum theory. The
-simplest theory, defined over unrestricted finite fields, is so weak
-that it only predict whether the measure result is possible or impossible.
-Its computational model is also weak that it cannot express Deutsch's
-algorithm, but, paradoxically, is also so powerful that it can be
-used to solve the $\usat$ problem, which is as hard as a general
-$\NP$-complete problem.
+If the probability amplitudes are assumed to be ultimately discrete,
+we replace the field of complex numbers by discrete finite fields
+and consider the quantum theories and computing over finite fields.
+Another possibilities could be that the probability amplitudes are
+never quantized no matter how hard we try, and we could never access
+their exactly values. Notice that the probability amplitudes can never
+be accessed directly in an experiment, the accessible properties of
+a quantum system is its measurement results and the probability of
+an event. Hence, to incorporate the finite precision measurement into
+the quantum theory, we consider a framework called quantum interval-valued
+probability measures (QIVPM).
+
+\begin{comment}
+Our first discrete model replaces the complex numbers by a unrestricted
+finite field~$\mathbb{F}_{q}$ \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
+In this model, an $n$-qubit state is a non-zero vector in $\mathbb{F}_{q}^{2^{n}}$.
+When we measure a given state~$\ket{\Phi}$, an observable is replaced
+by a basis~$\mathcal{B}$ of $\mathbb{F}_{q}^{2^{n}}$. Since $\ket{\Phi}$
+can be represented by the summation across a unique subset~$\mathcal{S}$
+of the basis~$\mathcal{B}$, whether it is possible or impossible
+to measure a basis vector~$\ket{i}$ depends on whether $\ket{i}$
+is in $\mathcal{S}$ or not. Because this model only predicts whether
+a result is possible or impossible, it is called the modal quantum
+theory. Its computational model, called the modal quantum computing,
+is far from conventional quantum computing. Although modal quantum
+computing can express simple algorithms such as quantum teleportation
+\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
+it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
+This quantum theory is, however, also so powerful that it can be used
+to solve an unstructured database search of size $N$ using $O(\log(N))$
+steps, which outperforms the known asymptotic bound $O(\sqrt{N})$
+in conventional quantum computing \cite{Grover:1996:FQM:237814.237866,BennettBernsteinBrassardVazirani1997,Mermin2007,Jaeger2007}.
+\end{comment}
+When replacing the continuum of complex numbers by discrete finite
+fields, we first doesn't restrict our quantum theory and computing
+over which finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
+\cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
+This theory is called modal quantum theory because it is so weak that
+it only predict whether the measure result is possible or impossible,
+and even the expectation value of an observable is not able to be
+defined. Although a version of quantum theory defined over a two-valued
+field can express simple algorithms such as quantum teleportation
+\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
+it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
+This quantum theory is, however, also so powerful that it can be used
+to solve the $\usat$ problem, which is as hard as a general $\NP$-complete
+problem.
+
+\todo{Introduction Cleaned up until here. }Next, in Sec.~\ref{discretequantumtheoryI}
+to \ref{sec:Geometry-of-Entangled-States}, we improve on this by
+showing that for finite fields of order $p^{2}$, with the prime $p$
+of the form $4\ell+3$ ($\ell$ a non-negative integer), the complex
+numbers have extremely compelling and natural discrete analogs that
+permit a great many of the standard requirements of quantum computing
+to be preserved. Under suitable conditions, we have amplitude-based
+partitions of unity, unitary transformations, and entanglement, as
+well as solutions to deterministic quantum algorithms such as the
+algorithms of Deutsch, Simon, and Bernstein-Vazirani, though still
+with some bothersome shortcomings. Because of the modular nature of
+arithmetic in the finite complex field, it is not possible to define
+an inner product in the usual sense, and we show in Sec.~\ref{subsec:Partial-Algorithm}
+that this leads to excessive computational power for the unstructured
+database search problem for certain database sizes.
 
@@
 the Kochen-Specker and Gleason theorems in realistic experimental
-environments.\todo{End of Merge Right}
+environments.
 
@@
 \addlinespace
-Hadamard transformation & Included & May not be included & Included & Included &  & \tabularnewline\addlinespace
+Deutsch's algorithm & Yes & Maybe no & Yes & Yes &  & \tabularnewline\addlinespace
 \addlinespace
@@
 
-\chapter{Quantum Theories and Computing over Unrestricted Finite Fields}
-
-\todo{Add some introductory text...}
+\chapter{Quantum Theories and Computing over Unrestricted Finite Fields\label{chap:Unrestricted-Finite-Fields}}
 
@@
 $+$ and $0$, when expressed in the standard basis, would consist
-of a superposition containing the state $\ket{0\ldots}$.\end{proof}%
-\begin{comment}
-
-\section{Modal Quantum Theory and Computing}
-
-Our first discrete model replaces the complex numbers by a unrestricted
-finite field~$\mathbb{F}_{q}$ \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
-In this model, an $n$-qubit state is a non-zero vector in $\mathbb{F}_{q}^{2^{n}}$.
-When we measure a given state~$\ket{\Phi}$, an observable is replaced
-by a basis~$\mathcal{B}$ of $\mathbb{F}_{q}^{2^{n}}$. Since $\ket{\Phi}$
-can be represented by the summation across a unique subset~$\mathcal{S}$
-of the basis~$\mathcal{B}$, whether it is possible or impossible
-to measure a basis vector~$\ket{i}$ depends on whether $\ket{i}$
-is in $\mathcal{S}$ or not. Because this model only predicts whether
-a result is possible or impossible, it is called the modal quantum
-theory. Its computational model, called the modal quantum computing,
-is far from conventional quantum computing. Although modal quantum
-computing can express simple algorithms such as quantum teleportation
-\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
-it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
-This quantum theory is, however, also so powerful that it can be used
-to solve an unstructured database search of size $N$ using $O(\log(N))$
-steps, which outperforms the known asymptotic bound $O(\sqrt{N})$
-in conventional quantum computing \cite{Grover:1996:FQM:237814.237866,BennettBernsteinBrassardVazirani1997,Mermin2007,Jaeger2007}.
-\end{comment}
+of a superposition containing the state $\ket{0\ldots}$.\end{proof}
 
@@
 
-\subsection{Partial \usat\ Algorithm}
+\subsection{Partial \usat\ Algorithm\label{subsec:Partial-Algorithm}}
 

### 2018-12-22 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 Even if these quantities look like continuous, we want to argue that
-these quantities might later be discovered to be discrete. Even if
-they were not discrete, this fact may never be proved and the exact
-value of these quantities may never be pinned down. To better understand
-this issue without struggling with the quantum theory, it is instructive
-to review how classical quantities are characterized and computed.
+either these quantities might later be discovered to be discrete,
+or the exact value of these continuous quantities may never be pinned
+down. To better understand this issue without struggling with the
+quantum theory, it is instructive to review how classical quantities
+are characterized and computed.
 
@@
 over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
-Hence, even if the inputs of an analog computer and a BCSS machine
-are close to each other, their computational results might be completely
-different, like the butterfly effect, and may not be compensated by
-error analysis techniques. Therefore, the computational power of analog
-computers is far weaker than the prediction based on this kind of
-theoretical models.
+Hence, when the quantities used to branch the computation is closed
+to zero, the branch chosen by a BCSS machine cannot reliably predict
+the branch chosen by an analog computer. Since two branches of computations
+may not have any relations, the later computational path may be completely
+different like the butterfly effect, and this kind of difference cannot
+be compensated by error analysis techniques easily. Therefore, the
+computational power of analog computers might be far weaker than the
+prediction based on this kind of theoretical models.
 
@@
 amplitudes of quantum states. To address the similar inconsistency,
-we first review the ``conventional quantum theory'' in Chapter~\ref{chap:Conventional-Quantum-Theory}\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
-and ``ordinary'' quantum theory.}, where the probability amplitudes are in the field of complex numbers.
-If the probability amplitudes are assumed to be ultimately discrete,
-we replace the field of complex numbers by discrete finite fields
-and consider the quantum theories and computing over finite fields.
-Another possibilities could be that the probability amplitudes are
-never quantized no matter how hard we try, and we could never access
-their exactly values. Notice that the probability amplitudes can never
-be accessed directly in an experiment, the accessible properties of
-a quantum system is its measurement results and the probability of
-an event. Hence, to incorporate the finite precision measurement into
-the quantum theory, we consider a framework called quantum interval-valued
-probability measures (QIVPM).
+we first review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+and ``ordinary'' quantum theory.} in Chapter~\ref{chap:Conventional-Quantum-Theory}, where the probability
+amplitudes are in the field of complex numbers. If the probability
+amplitudes are assumed to be ultimately discrete, we replace the field
+of complex numbers by discrete finite fields and consider the quantum
+theories and computing over finite fields. Another possibilities could
+be that the probability amplitudes are never quantized no matter how
+hard we try, and we could never access their exactly values. Notice
+that the probability amplitudes can never be accessed directly in
+an experiment, the accessible properties of a quantum system is its
+measurement results and the probability of an event. Hence, to incorporate
+the finite precision measurement into the quantum theory, we consider
+a framework called quantum interval-valued probability measures (QIVPM).
 

### 2018-12-25 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
-%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.3.2-1 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
@@
 \providecommand{\LyX}{L\kern-.1667em\lower.25em\hbox{Y}\kern-.125emX\@}
+\let\@@LyX\LyX
+\def\LyX{\@ensure@LTR{\@@LyX}}
 %% Because html converters don't know tabularnewline
@@
 molecules are described by quantities including the domain of their
-position wave functions or the probability amplitudes of a wave function.
+position wave functions and the probability amplitudes of a wave function.
 Even if these quantities look like continuous, we want to argue that
@@
 to zero, the branch chosen by a BCSS machine cannot reliably predict
-the branch chosen by an analog computer. Since two branches of computations
-may not have any relations, the later computational path may be completely
-different like the butterfly effect, and this kind of difference cannot
-be compensated by error analysis techniques easily. Therefore, the
-computational power of analog computers might be far weaker than the
-prediction based on this kind of theoretical models.
+the branch chosen by a realistic analog computer. Since two branches
+of computations may not have any relations, the following computational
+path may be completely different like the butterfly effect, and this
+kind of difference cannot be compensated by error analysis techniques
+easily. Therefore, the computational power of analog computers might
+be far weaker than the prediction based on this kind of theoretical
+models. \todo{Maybe extended to consider probabilistic model? }
 
@@
 The situations for classical quantities and the computational power
-above them are summarized in Table~\ref{tab:Comparison}, and the
-two possibilities dealing with real-valued models inspires us two
-types of quantum models. Similar to classical analog computers, the
-quantum circuit model, the most widely used model of quantum computing,
-manipulates quantities which are not discrete apparently: the probability
-amplitudes of quantum states. To address the similar inconsistency,
-we first review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+above them are summarized in Table~\ref{tab:Comparison}, and two
+possibilities dealing with real-valued models inspires us two types
+of quantum models. Similar to classical analog computers, the quantum
+circuit model, the most widely used model of quantum computing, manipulates
+quantities which are not discrete apparently: the probability amplitudes
+of quantum states. To address the similar inconsistency, we first
+review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
 and ``ordinary'' quantum theory.} in Chapter~\ref{chap:Conventional-Quantum-Theory}, where the probability
@@
 \end{figure}
+
 The resulting manifold is the two-sphere $\Sphere{2}$ (a 2-manifold)
@@
 \end{figure}
+
 Thus the geometry of a single qubit reduces to transformations among
@@
 \end{figure}
+
 We can prove the unreasonable power of the arbitrary-function \usat\ starting
@@
 \end{table}
+
 In Table~\ref{tab:Generators-in-F9}, one can notice that $\left(a+b\rmi\right)^{3}=a-b\rmi$.
@@
 \end{figure}
+
 First, a 2-qubit pure state is initialized to $\ket{\Phi_{1}}=\ket{1}\ket{0}=\left(\begin{smallmatrix}0\\
@@
 \end{table}
+
 As an example, consider the field $\ff{23}$. Looking at the squares
@@
 \end{table}
+
 We can now verify, by using Table~\ref{table_allowed}, that for
@@
 \end{table}
+
 When measuring cardinal probabilities, \textit{inequalities} can be
@@
 \end{table}
+
 For the $2$-qubit Deutsch-Jozsa, the computation is already quite
@@
 \end{figure}
+
 As is the case for conventional, infinitely-precise, quantum probability

### 2018-12-26 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 molecules are described by quantities including the domain of their
-position wave functions and the probability amplitudes of a wave function.
-Even if these quantities look like continuous, we want to argue that
-either these quantities might later be discovered to be discrete,
-or the exact value of these continuous quantities may never be pinned
-down. To better understand this issue without struggling with the
-quantum theory, it is instructive to review how classical quantities
-are characterized and computed.
+position wave functions and the probability amplitudes of these wave
+functions, which look like continuous at first sight. However, we
+want to argue that either these quantities might later be discovered
+to be discrete, or the exact values of these continuous quantities
+may never be pinned down. Hence, modeling quantum computing based
+on the exact values of continuous quantities cannot really describe
+the computational power of a realistic quantum computer. To better
+understand this issue without struggling with the quantum theory,
+it is instructive to review how classical quantities are characterized
+and computed.
 
@@
 the branch chosen by a realistic analog computer. Since two branches
-of computations may not have any relations, the following computational
-path may be completely different like the butterfly effect, and this
-kind of difference cannot be compensated by error analysis techniques
-easily. Therefore, the computational power of analog computers might
-be far weaker than the prediction based on this kind of theoretical
-models. \todo{Maybe extended to consider probabilistic model? }
+of computations may not have any relations, the follow-up computational
+paths may be significantly different, and may not be compensated by
+error analysis techniques easily like the butterfly effect. Therefore,
+the computational power of analog computers might be far weaker than
+the prediction based on this kind of theoretical models. \todo{Maybe
+extended to consider probabilistic model? }
 

### 2018-12-28 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 position wave functions and the probability amplitudes of these wave
-functions, which look like continuous at first sight. However, we
-want to argue that either these quantities might later be discovered
-to be discrete, or the exact values of these continuous quantities
-may never be pinned down. Hence, modeling quantum computing based
-on the exact values of continuous quantities cannot really describe
+functions, which look like continuous at first sight. Indeed, either
+these quantities might later be discovered to be discrete, or their
+exact values may never be pinned down. Hence, modeling quantum computing
+based on the exact values of continuous quantities cannot really describe
 the computational power of a realistic quantum computer. To better
@@
 of computations may not have any relations, the follow-up computational
-paths may be significantly different, and may not be compensated by
-error analysis techniques easily like the butterfly effect. Therefore,
-the computational power of analog computers might be far weaker than
-the prediction based on this kind of theoretical models. \todo{Maybe
-extended to consider probabilistic model? }
+paths may be significantly different. These difference may not be
+compensated by error analysis techniques easily like the butterfly
+effect. Therefore, the computational power of analog computers might
+be far weaker than the prediction based on this kind of theoretical
+models.%
+\begin{comment}
+\todo{Maybe extended to consider probabilistic model? }
+\end{comment}
 
@@
 \caption{\label{tab:Comparison}Comparison between the classical quantities
-and their mathematical models with the inspired quantum models. \todo{Center
-entries vertically.}}
+and their mathematical models with the inspired quantum models.}
 
@@
 \end{sidewaystable}
+\begin{comment}
+Given a pure state~$\ket{\Phi}$, when we measure an observable represented
+by an Hermitian matrix~$\mathbf{O}$, the measurement result is one
+of the eigenvalues of $\mathbf{O}$. The probability of getting a
+particular eigenvalue~$\lambda$ is $\melem{\Phi}{P}{\Phi}$, where
+$P$ is the projection operator onto the eigenspace of $\lambda$.
+This rule of computing the probability is called the Born rule \cite{Born1983,Mermin2007,Jaeger2007},
+which is used when we want to extract information from a quantum computer.
+For any mixed state~$\rho$, the generalized Born rule induces a
+conventional quantum probability measure $\muB_{\rho}:\events\rightarrow[0,1]$,
+where $\events$ is the set of all projection operators on a given
+Hilbert space. Conversely, any quantum probability measure $\mu:\events\rightarrow[0,1]$
+can be induced from a mixed state $\rho$ in the Hilbert space of
+dimension $D\ge3$ according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+In another word, this state $\rho$ is the unique state consistent
+with any given quantum probability measure.
+\end{comment}
+\begin{comment}
+An $n$-qubit pure state in the conventional quantum theory (CQT)
+is represented as a vector in the $2^{n}$-dimensional Hilbert space.
+If we eliminate all symmetries, an irreducible state is actually a
+point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
+also known as the complex projective space~$\CP{2^{n}-1}$ \cite{Hatcher2001,Bengtsson2007}.
+These irreducible quantum states can also be classified as product
+states and entangled states, and the latter one plays the essential
+role for pure-state algorithms \cite{Mermin2007,Jaeger2007}.
+\end{comment}
 The situations for classical quantities and the computational power
-above them are summarized in Table~\ref{tab:Comparison}, and two
-possibilities dealing with real-valued models inspires us two types
-of quantum models. Similar to classical analog computers, the quantum
-circuit model, the most widely used model of quantum computing, manipulates
-quantities which are not discrete apparently: the probability amplitudes
-of quantum states. To address the similar inconsistency, we first
-review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+above them are summarized in Table~\ref{tab:Comparison}, and the
+two possibilities dealing with real-valued models inspires us two
+types of quantum models. Similar to classical analog computers, the
+quantum circuit model, the most widely used model of quantum computing,
+manipulates quantities which are not discrete apparently: the probability
+amplitudes of quantum states. To address the similar inconsistency,
+we first review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
 and ``ordinary'' quantum theory.} in Chapter~\ref{chap:Conventional-Quantum-Theory}, where the probability
@@
 of complex numbers by discrete finite fields and consider the quantum
-theories and computing over finite fields. Another possibilities could
-be that the probability amplitudes are never quantized no matter how
-hard we try, and we could never access their exactly values. Notice
-that the probability amplitudes can never be accessed directly in
-an experiment, the accessible properties of a quantum system is its
-measurement results and the probability of an event. Hence, to incorporate
-the finite precision measurement into the quantum theory, we consider
-a framework called quantum interval-valued probability measures (QIVPM).
+theories and computing over finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
+and \ref{chap:DQT=000026DQC}. Another possibilities could be that
+the probability amplitudes would never be quantized no matter how
+hard we try, but we could never access their exactly values as well.
+Notice that the probability amplitudes can never be accessed directly
+in an experiment, the accessible properties of a quantum system is
+its measurement results and the probability of an event. Hence, to
+incorporate the finite precision measurement into the quantum theory,
+we consider a framework called quantum interval-valued probability
+measures (QIVPM) in Chapter~\ref{chap:QIVPM}.
 
@@
 When replacing the continuum of complex numbers by discrete finite
-fields, we first doesn't restrict our quantum theory and computing
-over which finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
+fields, we first doesn't restrict the chosen finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
 \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
-This theory is called modal quantum theory because it is so weak that
-it only predict whether the measure result is possible or impossible,
-and even the expectation value of an observable is not able to be
-defined. Although a version of quantum theory defined over a two-valued
-field can express simple algorithms such as quantum teleportation
-\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
+This theory is called modal quantum theory because it can only predict
+whether a measure result is possible or impossible, but not its probability.
+Although a version of quantum theory defined over a two-valued field
+can express simple algorithms such as quantum teleportation \cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
 it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
 This quantum theory is, however, also so powerful that it can be used
-to solve the $\usat$ problem, which is as hard as a general $\NP$-complete
-problem.
-
+to solve the $\usat$ problem~\cite{Papadimitriou1993}, which is
+as hard as a general $\NP$-complete problem~\cite{Valiant198685}.
+
+\begin{comment}
+Our second model called discrete quantum theory (I) considers only
+finite fields of order $p^{2}$, with the prime $p$ of the form $4\ell+3$
+($\ell$ a non-negative integer) \cite{geometry2013,DQT2014}. In
+this model, an irreducible state is a vector in $\mathbb{F}_{p^{2}}^{2^{n}}$,
+and can be reduced to a point in the discrete complex projective space~$\mathbb{DCP}^{2^{n}-1}$.
+Among these irreducible states, the product states and entangled states
+can not only be identified as in CQT but also be counted for different
+$p$. Although the state space is a natural discrete analog to CQT,
+this model still only predicts whether a measurement result is possible
+or impossible, because it is not possible to define an inner product
+in the usual sense due to the modular arithmetic~\cite{grove2002classical}.
+Under suitable conditions, we can have deterministic quantum algorithms
+such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
+and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
+but this still leads to excessive computational power for the unstructured
+database search problem for certain database sizes.
+\end{comment}
 \todo{Introduction Cleaned up until here. }Next, in Sec.~\ref{discretequantumtheoryI}
@@
 well as solutions to deterministic quantum algorithms such as the
-algorithms of Deutsch, Simon, and Bernstein-Vazirani, though still
-with some bothersome shortcomings. Because of the modular nature of
-arithmetic in the finite complex field, it is not possible to define
-an inner product in the usual sense, and we show in Sec.~\ref{subsec:Partial-Algorithm}
+algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
+and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
+though still with some bothersome shortcomings. Because of the modular
+nature of arithmetic in the finite complex field, it is not possible
+to define an inner product in the usual sense, and we show in Sec.~\ref{subsec:Partial-Algorithm}
 that this leads to excessive computational power for the unstructured
@@
 
+\begin{comment}
+Our third model, discrete quantum theory (II)~\cite{DQT2014}, restricts
+states in some local region of $\mathbb{F}_{p^{2}}^{2^{n}}$. Within
+a local region, a notion of inner product and probability could be
+recovered. Its discrete quantum computing can be further applied to
+the deterministic Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007}
+and the probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
+\end{comment}
 Finally, we shift our attention to consider quantum interval-valued
@@
 \section{The geometry of entanglement\label{sec:The-geometry-of}}
-
-\begin{comment}
-An $n$-qubit pure state in the conventional quantum theory (CQT)
-is represented as a vector in the $2^{n}$-dimensional Hilbert space.
-If we eliminate all symmetries, an irreducible state is actually a
-point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
-also known as the complex projective space~$\CP{2^{n}-1}$ \cite{Hatcher2001,Bengtsson2007}.
-These irreducible quantum states can also be classified as product
-states and entangled states, and the latter one plays the essential
-role for pure-state algorithms \cite{Mermin2007,Jaeger2007}.
-\end{comment}
 

### 2018-12-29 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

--- 2018-12-26 dissertation.tex
@@
 position wave functions and the probability amplitudes of these wave
-functions, which look like continuous at first sight. However, we
-want to argue that either these quantities might later be discovered
-to be discrete, or the exact values of these continuous quantities
-may never be pinned down. Hence, modeling quantum computing based
-on the exact values of continuous quantities cannot really describe
+functions, which look like continuous at first sight. However, either
+these quantities might later be discovered to be discrete, or their
+exact values may never be pinned down. Hence, modeling quantum computing
+based on the exact values of continuous quantities cannot really describe
 the computational power of a realistic quantum computer. To better
@@
 of computations may not have any relations, the follow-up computational
-paths may be significantly different, and may not be compensated by
-error analysis techniques easily like the butterfly effect. Therefore,
-the computational power of analog computers might be far weaker than
-the prediction based on this kind of theoretical models. \todo{Maybe
-extended to consider probabilistic model? }
+paths may be significantly different, and these difference may not
+be compensated by error analysis techniques easily like the butterfly
+effect. Therefore, the computational power of analog computers might
+be far weaker than the prediction based on this kind of theoretical
+models.%
+\begin{comment}
+\todo{Maybe extended to consider probabilistic model? }
+\end{comment}
 
@@
 Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computational power by a better discrete model. & 
-Not reliably, because precision can never be high enough, and the difference between their computational power might not be compensated by error analysis techniques. \tabularnewline\addlinespace
+Not reliably, because precision can never be high enough, and the difference between their computational power might not be able compensated by error analysis techniques. \tabularnewline\addlinespace
 \addlinespace
@@
 The situations for classical quantities and the computational power
-above them are summarized in Table~\ref{tab:Comparison}, and two
-possibilities dealing with real-valued models inspires us two types
-of quantum models. Similar to classical analog computers, the quantum
-circuit model, the most widely used model of quantum computing, manipulates
-quantities which are not discrete apparently: the probability amplitudes
-of quantum states. To address the similar inconsistency, we first
-review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+above them are summarized in Table~\ref{tab:Comparison}, and the
+two possibilities dealing with real-valued models inspires us two
+types of quantum models. Similar to classical analog computers, the
+quantum circuit model, the most widely used model of quantum computing,
+manipulates quantities which are not discrete apparently: the probability
+amplitudes of quantum states. To address the similar inconsistency,
+we first review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
 and ``ordinary'' quantum theory.} in Chapter~\ref{chap:Conventional-Quantum-Theory}, where the probability
@@
 of complex numbers by discrete finite fields and consider the quantum
-theories and computing over finite fields. Another possibilities could
-be that the probability amplitudes are never quantized no matter how
-hard we try, and we could never access their exactly values. Notice
-that the probability amplitudes can never be accessed directly in
-an experiment, the accessible properties of a quantum system is its
-measurement results and the probability of an event. Hence, to incorporate
-the finite precision measurement into the quantum theory, we consider
-a framework called quantum interval-valued probability measures (QIVPM).
-
+theories and computing over finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
+and \ref{chap:DQT=000026DQC}. Another possibilities could be that
+the probability amplitudes would never be quantized no matter how
+hard we try. Notice that the probability amplitudes can never be accessed
+directly in an experiment, the accessible properties of a quantum
+system is its measurement results and the probability of an event.
+Hence, to incorporate the finite precision measurement into the quantum
+theory, we consider a framework called quantum interval-valued probability
+measures (QIVPM) in Chapter~\ref{chap:QIVPM}.
+
+\begin{comment}
+After a review of finite fields in Section~\ref{sec:background},
+we proceed with a sequence of finite-field approaches that lead more
+and more closely to the properties of conventional quantum computing.
+\end{comment}
+\begin{comment}
+An $n$-qubit pure state in the conventional quantum theory (CQT)
+is represented as a vector in the $2^{n}$-dimensional Hilbert space.
+If we eliminate all symmetries, an irreducible state is actually a
+point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
+also known as the complex projective space~$\CP{2^{n}-1}$ \cite{Hatcher2001,Bengtsson2007}.
+These irreducible quantum states can also be classified as product
+states and entangled states, and the latter one plays the essential
+role for pure-state algorithms \cite{Mermin2007,Jaeger2007}.
+
+Given a pure state~$\ket{\Phi}$, when we measure an observable represented
+by an Hermitian matrix~$\mathbf{O}$, the measurement result is one
+of the eigenvalues of $\mathbf{O}$. The probability of getting a
+particular eigenvalue~$\lambda$ is $\melem{\Phi}{P}{\Phi}$, where
+$P$ is the projection operator onto the eigenspace of $\lambda$.
+This rule of computing the probability is called the Born rule \cite{Born1983,Mermin2007,Jaeger2007},
+which is used when we want to extract information from a quantum computer.
+For any mixed state~$\rho$, the generalized Born rule induces a
+conventional quantum probability measure $\muB_{\rho}:\events\rightarrow[0,1]$,
+where $\events$ is the set of all projection operators on a given
+Hilbert space. Conversely, any quantum probability measure $\mu:\events\rightarrow[0,1]$
+can be induced from a mixed state $\rho$ in the Hilbert space of
+dimension $D\ge3$ according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+In another word, this state $\rho$ is the unique state consistent
+with any given quantum probability measure.
+\end{comment}
+The review of CQT in Chapter~\ref{chap:Conventional-Quantum-Theory}
+starts from the geometrical structure of states in Sec.~\ref{CQC1qubitBloch.sec},
+where a pure state is represented as a vector in the Hilbert space,
+and an irreducible state is actually a point in the projective Hilbert
+space \cite{MosseriDandoloff2001,Jaeger2007} also known as the complex
+projective space \cite{Hatcher2001,Bengtsson2007}. In Sec.~\ref{sec:fuzzy},
+we will construct a quantum probability space based on classical probability
+space, apply Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}
+to recover the Born rule \cite{Born1983,Mermin2007,Jaeger2007}, and
+define the expectation value of an observable. These expectation values
+will be used to defined purity which provides an easy way to decide
+whether a state is entangled or not and to defined the maximum entangled
+states.
+
+\begin{comment}
+In Section~\ref{modalquantum}, we examine previously-introduced
+quantum theories defined over unrestricted finite fields and show
+in Section~\ref{modalquantumcomputing} that this approach leads
+to theories with such bizarre powers that they are probably unphysical.
+Although a version of quantum theory defined over a two-valued field
+can express simple algorithms such as quantum teleportation, it is
+so weak that it cannot express Deutsch's algorithm. This quantum theory
+is, however, also so powerful that it can be used to solve an unstructured
+database search of size $N$ using $O(\log(N))$ steps, which outperforms
+the known asymptotic bound $O(\sqrt{N})$ in conventional quantum
+computing.
+\end{comment}
 \begin{comment}
@@
 When replacing the continuum of complex numbers by discrete finite
-fields, we first doesn't restrict our quantum theory and computing
-over which finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
+fields, we first doesn't restrict the chosen finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
 \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
-This theory is called modal quantum theory because it is so weak that
-it only predict whether the measure result is possible or impossible,
-and even the expectation value of an observable is not able to be
-defined. Although a version of quantum theory defined over a two-valued
-field can express simple algorithms such as quantum teleportation
-\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
+This theory is called modal quantum theory because it can only predict
+whether a measure result is possible or impossible, but not its probability.
+Although a version of quantum theory defined over the two-valued field
+can express simple algorithms such as quantum teleportation \cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
 it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
 This quantum theory is, however, also so powerful that it can be used
-to solve the $\usat$ problem, which is as hard as a general $\NP$-complete
-problem.
-
-\todo{Introduction Cleaned up until here. }Next, in Sec.~\ref{discretequantumtheoryI}
-to \ref{sec:Geometry-of-Entangled-States}, we improve on this by
-showing that for finite fields of order $p^{2}$, with the prime $p$
-of the form $4\ell+3$ ($\ell$ a non-negative integer), the complex
-numbers have extremely compelling and natural discrete analogs that
-permit a great many of the standard requirements of quantum computing
+to solve the $\usat$ problem~\cite{Papadimitriou1993}, which is
+as hard as a general $\NP$-complete problem~\cite{Valiant198685}.
+
+\begin{comment}
+Next, in Section \ref{discretequantumtheoryI}, we improve on this
+by showing that for finite fields of order $p^{2}$, with the prime
+$p$ of the form $4\ell+3$ ($\ell$ a non-negative integer), the
+complex numbers have extremely compelling and natural discrete analogs
+that permit a great many of the standard requirements of quantum computing
 to be preserved. Under suitable conditions, we have amplitude-based
@@
 well as solutions to deterministic quantum algorithms such as the
-algorithms of Deutsch, Simon, and Bernstein-Vazirani, though still
-with some bothersome shortcomings. Because of the modular nature of
-arithmetic in the finite complex field, it is not possible to define
-an inner product in the usual sense, and we show in Sec.~\ref{subsec:Partial-Algorithm}
+algorithms of Deutsch, Simon, and Bernstein-Vazirani~\cite{NCbook,Mermin},
+though still with some bothersome shortcomings. Because of the modular
+nature of arithmetic in the finite complex field, it is not possible
+to define an inner product in the usual sense, and we show in Section~\ref{discretequantumcomputingI}
+that this leads to excessive computational power for the unstructured
+database search problem for certain database sizes.
+\end{comment}
+\begin{comment}
+Our second model called discrete quantum theory (I) considers only
+finite fields of order $p^{2}$, with the prime $p$ of the form $4\ell+3$
+($\ell$ a non-negative integer) \cite{geometry2013,DQT2014}. In
+this model, an irreducible state is a vector in $\mathbb{F}_{p^{2}}^{2^{n}}$,
+and can be reduced to a point in the discrete complex projective space~$\mathbb{DCP}^{2^{n}-1}$.
+Among these irreducible states, the product states and entangled states
+can not only be identified as in CQT but also be counted for different
+$p$. Although the state space is a natural discrete analog to CQT,
+this model still only predicts whether a measurement result is possible
+or impossible, because it is not possible to define an inner product
+in the usual sense due to the modular arithmetic~\cite{grove2002classical}.
+Under suitable conditions, we can have deterministic quantum algorithms
+such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
+and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
+but this still leads to excessive computational power for the unstructured
+database search problem for certain database sizes.
+\end{comment}
+Next, in Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States},
+we improve on this by showing that for finite fields of order $p^{2}$,
+$\Fpp$, with the prime $p$ of the form $4\ell+3$ ($\ell$ a non-negative
+integer), the complex numbers have extremely compelling and natural
+discrete analogs that permit a great many of the standard requirements
+of quantum computing to be preserved. In this model, the states of
+a discrete $d$-dimensional system is a vector in the $d$-dimensional
+vector space over $\Fpp$. \todo{Introduction Cleaned up until here.
+} Because the states of a discrete $n$-qubit system are in principle
+enumerable, we can count the number of states, and determine the proportions
+of entangled and unentangled states. Under suitable conditions, we
+have amplitude-based partitions of unity, unitary transformations,
+and entanglement, as well as solutions to deterministic quantum algorithms
+such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
+and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
+though still with some bothersome shortcomings. Because of the modular
+nature of arithmetic in the finite complex field, it is not possible
+to define an inner product in the usual sense, and we show in Sec.~\ref{subsec:Partial-Algorithm}
 that this leads to excessive computational power for the unstructured
@@
 
+\begin{comment}
+We are led, in Sections~\ref{discretequantumtheoryIIa} and~\ref{discretequantumtheoryIIb},
+to develop a framework with further restrictions on~$p$ that \emph{locally\/}
+recovers the structure and expected properties of conventional quantum
+theory. Section~\ref{discretequantumtheoryIIa} locally recovers
+the inner product space and Section~\ref{discretequantumtheoryIIb}
+locally recovers a notion of probability. The development in both
+sections exploits the fact that longer sequences of \textit{ordered\/}
+numbers appear in the quadratic residues (numbers with square-roots
+in the field) as the size of the field increases. Discrete quantum
+computations whose calculations are confined to numbers in this ordered
+sequence resemble conventional quantum computations. The size of the
+field $p$ plays an important role in describing the resources needed
+for the computation as larger problem sizes require a larger field
+size to represent all intermediate numerical values. A significant
+feature of our framework is that the resources needed for the measurement
+process can be separated from the resources needed by the evolution
+of the system being modeled. This interplay between the resources
+used by the system under study and the resources used for the observation
+process is a significant concept that is nonexistent in conventional
+quantum computing and is exposed by our careful accounting of resources.
+
+We note that the conventional mathematical framework based on the
+real numbers allows one to distinguish states whose measurement outcomes
+differ by infinitesimally small probabilities, e.g., $10^{-100}$
+vs.~$0$. In the proposed framework of discrete quantum computing,
+the finite size of the field implies a maximum precision for measurement:
+a ``small'' field represents limited resources with which it becomes
+impossible to distinguish states whose measurement outcomes differ
+by an amount less than the resolution afforded by the field. It is
+possible, however, to discriminate between such states at the cost
+of moving to a larger field, i.e., by investing more resources in
+the measurement process. We formalize this approach to measurement
+using the novel notion of \textit{cardinal probability\/}, with numerical
+labels corresponding to ``more probable, the same, or less probable,''
+rather than a percentage-based likelihood measure. In cardinal probability,
+relative outcomes are associated with intervals of ambiguity that
+get smaller and more precise as the size of the field increases.
+
+Finally, in Section~\ref{discretequantumcomputingII}, we apply our
+discrete quantum theory to the study of two representative algorithms,
+the deterministic Deutsch-Jozsa algorithm and the probabilistic Grover
+algorithm~\cite{NCbook,Mermin}. The first algorithm highlights the
+role played by the size of the field $p$ in determining the actual
+resources required for computation as the number of input bits $n$
+increases, a concept nonexistent in conventional quantum computing.
+The second algorithm highlights, in addition, the dependence of the
+precision of measurement (via cardinal probabilities) on the size
+of the field, another nonexistent concept in conventional quantum
+computing.
+\end{comment}
+\begin{comment}
+Our third model, discrete quantum theory (II)~\cite{DQT2014}, restricts
+states in some local region of $\mathbb{F}_{p^{2}}^{2^{n}}$. Within
+a local region, a notion of inner product and probability could be
+recovered. Its discrete quantum computing can be further applied to
+the deterministic Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007}
+and the probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
+\end{comment}
 Finally, we shift our attention to consider quantum interval-valued
@@
 \addlinespace
-Expectation value & Defined & Undefined & Undefined & Undefined &  & Defined\tabularnewline\addlinespace
+Expectation value & Defined & Undefined & Formally defined & Undefined &  & Defined\tabularnewline\addlinespace
 \addlinespace
@@
 \item \label{enu:inner-product-positive-definite}$\ip{\Psi}{\Psi}$ is
-always non-negative and is equal to~0 only if $\ket{\Psi}$ is the
-zero vector. 
+always non-negative and is equal to $0$ only if $\ket{\Psi}$ is
+the zero vector. 
 \end{enumerate}
@@
 \end{equation}
-\end{definition} Two vectors $\ket{\Phi}$ and $\ket{\Psi}\in\mathcal{H}$
-are said to be orthogonal if $\ip{\Phi}{\Psi}=0$. This product satisfies
-conditions \ref{enu:inner-product-complex-conjugate} and \ref{enu:inner-product-linear}
+If we use $\bra{\Phi}$ to represent the dual vector of $\ket{\Phi}$,
+i.e., the conjugate transport of $\ket{\Phi}$, then the matrix multiplication
+of $\bra{\Phi}$ and $\ket{\Phi}$ results a $1\times1$ matrix whose
+only entry is their Hermitian dot product $\ip{\Phi}{\Psi}$.\end{definition}
+
+Two vectors $\ket{\Phi}$ and $\ket{\Psi}\in\mathcal{H}$ are said
+to be orthogonal if $\ip{\Phi}{\Psi}=0$. This product satisfies conditions
+\ref{enu:inner-product-complex-conjugate} and \ref{enu:inner-product-linear}
 for inner products but violates condition \ref{enu:inner-product-positive-definite}
@@
 which avoids the normalization factor and simply checks that each
-summand is 0.
+summand is 0, where $\expval{\jthSubsystem{\sigma}[\eta]{j}}$ is
+defined as $\melem{\Psi}{\jthSubsystem{\sigma}[\eta]{j}}{\Psi}$.
 

### 2018-12-30 dissertation.tex
dissertation.lyx  "Chapter 1 Introduction" Updating...

@@
 over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
-Hence, when the quantities used to branch the computation is closed
-to zero, the branch chosen by a BCSS machine cannot reliably predict
+Hence, when the quantities used to branch the computation closes to
+zero, the branch chosen by a BCSS machine cannot reliably predict
 the branch chosen by a realistic analog computer. Since two branches
@@
 \addlinespace
-Physical quantities & Discrete & Discrete with extreme small unit & Continuous?\tabularnewline\addlinespace
+Physical quantities & Discrete & Discrete with extreme small unit & Continuous, but unlikely to verify they really are\tabularnewline\addlinespace
 \addlinespace
@@
 Hence, to incorporate the finite precision measurement into the quantum
-theory, we consider a framework called quantum interval-valued probability
+theory, we assume the probability of an event
+
+, and consider a framework called quantum interval-valued probability
 measures (QIVPM) in Chapter~\ref{chap:QIVPM}.

### 2018-12-31 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 of computations may not have any relations, the follow-up computational
-paths may be significantly different, and these difference may not
-be compensated by error analysis techniques easily like the butterfly
+paths may be significantly different, and these difference is unlikely
+to be compensated by error analysis techniques easily like the butterfly
 effect. Therefore, the computational power of analog computers might
@@
 \addlinespace
-Physical quantities & Discrete & Discrete with extreme small unit & Continuous, but unlikely to verify they really are\tabularnewline\addlinespace
+Physical quantities & Discrete & Discrete with extreme small unit & Continuous, or no evidence to support they are discrete\tabularnewline\addlinespace
 \addlinespace
@@
 amplitudes of quantum states. To address the similar inconsistency,
-we first review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+we first review the ``conventional quantum theory'' (CQT)\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
 and ``ordinary'' quantum theory.} in Chapter~\ref{chap:Conventional-Quantum-Theory}, where the probability
@@
 the probability amplitudes would never be quantized no matter how
-hard we try. Notice that the probability amplitudes can never be accessed
-directly in an experiment, the accessible properties of a quantum
-system is its measurement results and the probability of an event.
-Hence, to incorporate the finite precision measurement into the quantum
-theory, we assume the probability of an event
-
-, and consider a framework called quantum interval-valued probability
-measures (QIVPM) in Chapter~\ref{chap:QIVPM}.
+hard we try. Notice that the probability amplitudes is unlikely to
+be accessed directly while the probability of an event can be deduced
+after a series of experiments. To achieve a coherent formulation of
+finite-resource quantum mechanics, we extend classical interval-valued
+probability measures to quantum domain, and consider quantum interval-valued
+probability measures (QIVPM) in Chapter~\ref{chap:QIVPM}.
 
@@
 \end{comment}
-The review of CQT in Chapter~\ref{chap:Conventional-Quantum-Theory}
-starts from the geometrical structure of states in Sec.~\ref{CQC1qubitBloch.sec},
+The geometrical structure of states in CQT is first reviewed in Sec.~\ref{CQC1qubitBloch.sec},
 where a pure state is represented as a vector in the Hilbert space,
@@
 define the expectation value of an observable. These expectation values
-will be used to defined purity which provides an easy way to decide
-whether a state is entangled or not and to defined the maximum entangled
-states.
+in Sec.~\ref{sec:The-geometry-of} will be used to defined purity
+which provides an easy way to decide whether a state is entangled
+or not and to defined the maximum entangled states.
 
@@
 \end{comment}
-When replacing the continuum of complex numbers by discrete finite
-fields, we first doesn't restrict the chosen finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
-\cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
-This theory is called modal quantum theory because it can only predict
-whether a measure result is possible or impossible, but not its probability.
+In Chapter~\ref{chap:Unrestricted-Finite-Fields}, we examine previously-introduced
+quantum theories defined over unrestricted finite fields \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
+It is called modal quantum theory because it can only predict whether
+a measure result is possible or impossible, but not its probability.
 Although a version of quantum theory defined over the two-valued field
@@
 \end{comment}
-Next, in Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States},
+In Sec.~\ref{discretequantumtheoryI} to \ref{discretequantumcomputingI},
 we improve on this by showing that for finite fields of order $p^{2}$,
@@
 a discrete $d$-dimensional system is a vector in the $d$-dimensional
-vector space over $\Fpp$. \todo{Introduction Cleaned up until here.
-} Because the states of a discrete $n$-qubit system are in principle
-enumerable, we can count the number of states, and determine the proportions
-of entangled and unentangled states. Under suitable conditions, we
-have amplitude-based partitions of unity, unitary transformations,
-and entanglement, as well as solutions to deterministic quantum algorithms
-such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
+vector space over $\Fpp$, and can be reduced to a point in the discrete
+complex projective space. Among these irreducible states, the product
+states and entangled states can not only be identified as in CQT but
+also be counted for different $p$. Although the state space is a
+natural discrete analog to CQT, this model still only predicts whether
+a measurement result is possible or impossible, because it is not
+possible to define an inner product in the usual sense due to the
+modular arithmetic~\cite{grove2002classical}. Under suitable conditions,
+we can have deterministic quantum algorithms such as the algorithms
+of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
 and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
-though still with some bothersome shortcomings. Because of the modular
-nature of arithmetic in the finite complex field, it is not possible
-to define an inner product in the usual sense, and we show in Sec.~\ref{subsec:Partial-Algorithm}
-that this leads to excessive computational power for the unstructured
-database search problem for certain database sizes.
-
-Our second framework employs only finite fields over prime numbers
-of the form $4\ell+3$, which possess no solutions to $x^{2}+1=0$,
-and thus permit an elegant complex representation of the finite field
-by adjoining $\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit
-system are in principle enumerable, we can count the number of states,
-and determine the proportions of entangled and unentangled states.
-We tried define its measurement process in three different approaches.
-For the model only predicting possible or impossible, we have solutions
-to deterministic quantum algorithms such as Deutsch's algorithm, but
-unnaturally strong computational power may still occur. In an improved
-model, the cardinal probability of measurement results could be predicted
-locally. In the local ordered region, the unnaturally computational
-power is ruled out and the probabilistic Grover search algorithm can
-be implemented. However, lacking arithmetic operations on cardinal
-probabilities, expectation values cannot be defined easily. Since
-arithmetic operations works with conventional probability measures,
-we consider quantum probability measures over finite fields, but we
-haven't found a consistent way to treat them in general.
+but this still leads to excessive computational power for partially
+solving the $\usat$ problem.
 
@@
 and the probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
+\end{comment}
+Since many important quantum algorithms are probabilistic, we want
+to find a notion of probability for quantum theory over finite fields.
+The cardinal probability is defined in Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
+by restricting states in some local region of the vector spaces. Within
+a local region, a notion of inner product and probability could be
+recovered. In Sec.~\ref{discretequantumcomputingII}, this discrete
+quantum theory is applied on two representative algorithms, the deterministic
+Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007} and the
+probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
+\begin{comment}
+When people tried to define quantum probability over finite fields,
+people tended to treat the original Born rule as an axiom, and tried
+to modify it to get a discrete Born rule \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644,DQT2014,Ellerman2016a}.
+However, any modified Born rule could hardly work on the whole vector
+space, since there is no inner product on the whole vector space over
+finite fields. Instead of treating the Born rule as an axiom, the
+Born rule can actually be deduced from a set of abstract definitions
+and axioms according to Gleason's theorem. Although we might hope
+to deduce a discrete Born rule directly from a similar set of definitions
+and axioms, no discrete Born rule satisfies certain properties motivated
+by Gleason's theorem with infinitely precise real-number probability~\cite{Gardiner2014}.
+Since the state spaces are now discrete and finite, this suggests
+us to consider a discrete Born rule mapping to finite number of intervals
+called interval-valued probability~\cite{JamisonLodwick2004,THOS2017}.
+To adopting the idea of interval-valued probability step-by-step,
+before attempting to study quantum interval-valued probability over
+finite fields, we will first review the classical interval-valued
+probability, and extend it with the conventional quantum theory.
+\end{comment}
+Despite the great success of cardinal probabilities, lacking arithmetic
+operations on them provides some difficulties to define expectation
+values. By attempting to define expectation values, we consider quantum
+probability measures over finite fields (QPMFF) in Sec.~\ref{sec:Toward-IVPM}.
+However, we cannot find a discrete Born rule to satisfy the Gleason-like
+conditions. \todo{Introduction Cleaned up until here. }
+
+\begin{comment}
+
+\section{Classical Interval-Valued Probability}
+
+In the classical setting, there are several proposals for ``imprecise
+probabilities'' \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+Although these proposals differ in some details, they all share the
+fact that the probability $\bar{\mu}(E)$ of an event~$E$ is generalized
+from a single \emph{real number} to an \emph{interval}~$[l,r]$,
+where~$l$ intuitively corresponds to the strength of evidence for
+the event~$E$ and~$1-r$ corresponds to the strength of evidence
+against the same event. Given a sample space~$\Omega$ and a set
+of intervals~$\mathscr{I}$, similar to a classical probability measure
+$\mu:2^{\Omega}\rightarrow\left[0,1\right]$, a classical interval-valued
+probability measure (IVPM) $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+needs to satisfy some coherent axioms. By satisfying the convexity
+axiom \cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
+Shapley proved that there is always a classical probability measure
+consistent with the classical IVPM~$\bar{\mu}$ \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
+Given any random variable, its expectation value with respect to classical
+probability measures consistent with~$\bar{\mu}$ is consistent with
+its Choquet integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
+with respect to $\bar{\mu}$ \cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
+
+\section{Quantum Interval-Valued Probability}
+
+The quantum extension, quantum interval-valued probability measure
+(QIVPM) $\bar{\mu}:\events\rightarrow\mathscr{I}$, is a generalization
+of both classical IVPMs $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+and conventional quantum probability measures $\mu:\events\rightarrow[0,1]$
+\cite{THOS2017}, because QIVPMs reduce to classical IVPMs when the
+space of quantum events $\events$ is restricted to mutually commuting
+events, and reduces to conventional quantum probability measures when
+mapping to infinitely precise uncountable intervals $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
+While Shapley and Gleason both proved there must be a ``state''
+consistent with any given QIVPM in the reduced cases, in general there
+exists a QIVPM such that no state is consistent with it. However,
+we found a class of QIVPMs such that all QIVPMs in this class are
+consistent with a non-empty ``ball'' of quantum states whose radius
+is defined by the maximal length of the intervals, and recovers the
+original Gleason theorem asymptotically. Similarly, the conventional
+quantum expectation value and the classical Choquet integral are together
+generalized to the quantum interval-valued expectation value. This
+is used to prove an imprecise Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+which suggests a possible resolution of the Meyer-Mermin debate on
+the impact of finite-precision measurement on the Kochen-Specker theorem
+\cite{PhysRevLett.83.3751,Mermin1999}.
 \end{comment}

### 2019-01-01 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 \addlinespace
-Inspired quantum models &  & Quantum Theories and Computing over Finite Fields & Quantum Interval-Valued Probability Measures (QIVPM)\tabularnewline\addlinespace
+Inspired quantum models &  & Quantum theories and computing over finite fields & Quantum interval-valued probability measures (QIVPM)\tabularnewline\addlinespace
 \addlinespace
@@
 theories and computing over finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
-and \ref{chap:DQT=000026DQC}. Another possibilities could be that
-the probability amplitudes would never be quantized no matter how
-hard we try. Notice that the probability amplitudes is unlikely to
-be accessed directly while the probability of an event can be deduced
-after a series of experiments. To achieve a coherent formulation of
-finite-resource quantum mechanics, we extend classical interval-valued
-probability measures to quantum domain, and consider quantum interval-valued
-probability measures (QIVPM) in Chapter~\ref{chap:QIVPM}.
+and \ref{chap:DQT=000026DQC}. Alternatively, that the probability
+amplitudes could never be quantized no matter how hard we try. Notice
+that the probability amplitudes is unlikely to be accessed directly
+while the probability of an event can be easily deduced after a series
+of experiments. To achieve a coherent formulation of finite-resource
+quantum mechanics, we extend classical interval-valued probability
+measures to quantum domain, and consider quantum interval-valued probability
+measures (QIVPM) in Chapter~\ref{chap:QIVPM}.
 
@@
 we will construct a quantum probability space based on classical probability
-space, apply Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}
+spaces, apply Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}
 to recover the Born rule \cite{Born1983,Mermin2007,Jaeger2007}, and
 define the expectation value of an observable. These expectation values
-in Sec.~\ref{sec:The-geometry-of} will be used to defined purity
+will be used in Sec.~\ref{sec:The-geometry-of} to defined purity
 which provides an easy way to decide whether a state is entangled
@@
 quantum theories defined over unrestricted finite fields \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
-It is called modal quantum theory because it can only predict whether
+We call it the modal quantum theory because it can only predict whether
 a measure result is possible or impossible, but not its probability.
 Although a version of quantum theory defined over the two-valued field
-can express simple algorithms such as quantum teleportation \cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
-it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
+can express simple algorithms such as quantum teleportation \cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007,Schumacher2012-SCHMQT},
+it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007,DQT2014}.
 This quantum theory is, however, also so powerful that it can be used
@@
 complex projective space. Among these irreducible states, the product
-states and entangled states can not only be identified as in CQT but
-also be counted for different $p$. Although the state space is a
-natural discrete analog to CQT, this model still only predicts whether
-a measurement result is possible or impossible, because it is not
-possible to define an inner product in the usual sense due to the
-modular arithmetic~\cite{grove2002classical}. Under suitable conditions,
-we can have deterministic quantum algorithms such as the algorithms
-of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
+states and entangled states could not only be identified as in CQT
+but also be counted for different $p$. Despite this model's similarity
+to CQT, it still only predicts whether a measurement result is possible
+or impossible, because it is not possible to define an inner product
+in the usual sense due to the modular arithmetic~\cite{grove2002classical}.
+Under suitable conditions, we can have deterministic quantum algorithms
+such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
 and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
@@
 to find a notion of probability for quantum theory over finite fields.
-The cardinal probability is defined in Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
-by restricting states in some local region of the vector spaces. Within
+The cardinal probability defined in Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
+restricts states in some local region of the vector spaces. Within
 a local region, a notion of inner product and probability could be
@@
 \end{comment}
-Despite the great success of cardinal probabilities, lacking arithmetic
-operations on them provides some difficulties to define expectation
-values. By attempting to define expectation values, we consider quantum
-probability measures over finite fields (QPMFF) in Sec.~\ref{sec:Toward-IVPM}.
-However, we cannot find a discrete Born rule to satisfy the Gleason-like
-conditions. \todo{Introduction Cleaned up until here. }
+Despite the great success of cardinal probabilities, it is difficulty
+to define their arithmetic operations and expectation values. Since
+these could be defined easily with real-valued probability measures
+in CQT, we attempt to consider quantum probability measures over finite
+fields (QPMFF) in Sec.~\ref{sec:Toward-IVPM}. In contrast to CQT,
+our Gleason-like conditions over finite fields cannot deduce a discrete
+Born rule in general. This impossible result suggests us that the
+discrete and finite state spaces might not compatible with infinitely
+precise real-valued probability. Thus, no matter whether the probability
+amplitudes are ultimately discrete or not,
+
+it might be more natural to consider a discrete Born rule mapping
+to finite number of intervals, and we will start the discussion in
+Chapter~\ref{chap:QIVPM}.
 
 \begin{comment}
-
-\section{Classical Interval-Valued Probability}
-
 In the classical setting, there are several proposals for ``imprecise
@@
 with respect to $\bar{\mu}$ \cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
-
-\section{Quantum Interval-Valued Probability}
 
@@
 \end{comment}
+\begin{comment}
+We present a mathematical framework based on quantum interval-valued
+probability measures to study the effect of experimental imperfections
+and finite precision measurements on defining aspects of quantum mechanics
+such as contextuality and the Born rule. While foundational results
+such as the Kochen-Specker and Gleason theorems are valid in the context
+of infinite precision, they fail to hold in general in a world with
+limited resources. Here we employ an interval-valued framework to
+establish bounds on the validity of those theorems in realistic experimental
+environments. In this way, not only can we quantify the idea of finite-precision
+measurement within our theory, but we can also suggest a possible
+resolution of the Meyer-Mermin debate on the impact of finite-precision
+measurement on the Kochen-Specker theorem.
+\end{comment}
+Sec.~\ref{sec:Interval-Uncertainty} starts from reviewing how to
+formulate classical ``imprecise probabilities'' \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}
+as interval-valued probability measures (IVPMs). Given a classical
+IVPM, its core is the set of the real-valued probability measures
+consistent with it \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997Chinese,Grabisch2016},
+and the expectation value is \todo{Introduction Cleaned up until
+here. }
+
 Finally, we shift our attention to consider quantum interval-valued
@@
 \addlinespace
-Solve $\usat$ efficiently & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
+Efficiently solve $\usat$ & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
 \addlinespace

### 2019-01-02 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 amplitudes are in the field of complex numbers. If the probability
-amplitudes are assumed to be ultimately discrete, we replace the field
-of complex numbers by discrete finite fields and consider the quantum
-theories and computing over finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
-and \ref{chap:DQT=000026DQC}. Alternatively, that the probability
-amplitudes could never be quantized no matter how hard we try. Notice
-that the probability amplitudes is unlikely to be accessed directly
-while the probability of an event can be easily deduced after a series
-of experiments. To achieve a coherent formulation of finite-resource
-quantum mechanics, we extend classical interval-valued probability
-measures to quantum domain, and consider quantum interval-valued probability
-measures (QIVPM) in Chapter~\ref{chap:QIVPM}.
+amplitudes are assumed to be ultimately discrete, since their field
+structure is essential to construct a quantum theory, we might assume
+they are elements in discrete finite fields and build the quantum
+theories and computing upon these finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
+and \ref{chap:DQT=000026DQC}. Alternatively, the probability amplitudes
+might never be found quantized. However, instead of considering the
+precision of probability amplitudes, it is better to consider the
+precision of their inducing probabilities because the probability
+amplitudes is unlikely to be accessed directly while the probability
+of an event can be deduced after a series of experiments. Therefore,
+we extend the idea of ``imprecise probabilities'' into quantum domain,
+and consider quantum interval-valued probability measures (QIVPM)
+in Chapter~\ref{chap:QIVPM}.
 

### 2019-01-03 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 and \ref{chap:DQT=000026DQC}. Alternatively, the probability amplitudes
-might never be found quantized. However, instead of considering the
-precision of probability amplitudes, it is better to consider the
-precision of their inducing probabilities because the probability
+might never be found quantized so that we should try another approach
+to take into account the precision of quantities. However, instead
+of the precision of probability amplitudes, it is better to consider
+the precision of their inducing probabilities because the probability
 amplitudes is unlikely to be accessed directly while the probability
-of an event can be deduced after a series of experiments. Therefore,
-we extend the idea of ``imprecise probabilities'' into quantum domain,
-and consider quantum interval-valued probability measures (QIVPM)
-in Chapter~\ref{chap:QIVPM}.
+of an event can be deduced after a series of experiments. Moreover,
+the idea of ``imprecise probabilities'' have well-studied classically
+\cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+In Chapter~\ref{chap:QIVPM}, they will be extended it to quantum
+domain, and define quantum interval-valued probability measures (QIVPM)
+.
 
@@
 The geometrical structure of states in CQT is first reviewed in Sec.~\ref{CQC1qubitBloch.sec},
-where a pure state is represented as a vector in the Hilbert space,
-and an irreducible state is actually a point in the projective Hilbert
-space \cite{MosseriDandoloff2001,Jaeger2007} also known as the complex
+where a pure state is represented as a vector in a Hilbert space,
+and an irreducible state is actually a point in a projective Hilbert
+space \cite{MosseriDandoloff2001,Jaeger2007} also known as a complex
 projective space \cite{Hatcher2001,Bengtsson2007}. In Sec.~\ref{sec:fuzzy},
@@
 to recover the Born rule \cite{Born1983,Mermin2007,Jaeger2007}, and
-define the expectation value of an observable. These expectation values
-will be used in Sec.~\ref{sec:The-geometry-of} to defined purity
+define the expectation value of an observable. The expectation value
+will then be used in Sec.~\ref{sec:The-geometry-of} to defined purity
 which provides an easy way to decide whether a state is entangled
@@
 quantum theories defined over unrestricted finite fields \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
-We call it the modal quantum theory because it can only predict whether
-a measure result is possible or impossible, but not its probability.
+It is called the modal quantum theory because it can only predict
+whether a measure result is possible or impossible, but not its probability.
 Although a version of quantum theory defined over the two-valued field
@@
 This quantum theory is, however, also so powerful that it can be used
-to solve the $\usat$ problem~\cite{Papadimitriou1993}, which is
-as hard as a general $\NP$-complete problem~\cite{Valiant198685}.
+to efficiently solve the $\usat$ problem~\cite{Papadimitriou1993},
+which is as hard as a general $\NP$-complete problem~\cite{Valiant198685}.
 
@@
 but this still leads to excessive computational power for partially
-solving the $\usat$ problem.
+solving the $\usat$ problem efficiently.
 
@@
 Since many important quantum algorithms are probabilistic, we want
-to find a notion of probability for quantum theory over finite fields.
+to find a notion of probability for quantum theories over finite fields.
 The cardinal probability defined in Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
-restricts states in some local region of the vector spaces. Within
+restricts states in some local regions of the vector spaces. Within
 a local region, a notion of inner product and probability could be
@@
 \end{comment}
-Despite the great success of cardinal probabilities, it is difficulty
+Despite the great success of cardinal probabilities, it is difficult
 to define their arithmetic operations and expectation values. Since
-these could be defined easily with real-valued probability measures
-in CQT, we attempt to consider quantum probability measures over finite
-fields (QPMFF) in Sec.~\ref{sec:Toward-IVPM}. In contrast to CQT,
-our Gleason-like conditions over finite fields cannot deduce a discrete
-Born rule in general. This impossible result suggests us that the
-discrete and finite state spaces might not compatible with infinitely
-precise real-valued probability. Thus, no matter whether the probability
-amplitudes are ultimately discrete or not,
+these could be defined easily with real-valued probabilities in CQT,
+we attempt to consider quantum probability measures over finite fields
+(QPMFF) in Sec.~\ref{sec:Toward-IVPM}. In contrast to CQT, our Gleason-like
+conditions over finite fields cannot deduce a discrete Born rule in
+general. This impossible result suggests us that the discrete and
+finite state spaces might not compatible with infinitely precise real-valued
+probability. Thus, no matter whether the probability amplitudes are
+ultimately discrete or not,
 

### 2019-01-04 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 amplitudes are in the field of complex numbers. If the probability
-amplitudes are assumed to be ultimately discrete, since their field
-structure is essential to construct a quantum theory, we might assume
-they are elements in discrete finite fields and build the quantum
-theories and computing upon these finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
+amplitudes are assumed to be ultimately discrete, we need to replace
+the field of complex numbers by some discrete structures. Finite fields
+is chosen because CQT is built upon the operations among the probability
+amplitudes, and the probability amplitudes have the required operations
+since the complex numbers form a field. The quantum theories and computing
+built upon finite fields are discussed in Chapter~\ref{chap:Unrestricted-Finite-Fields}
 and \ref{chap:DQT=000026DQC}. Alternatively, the probability amplitudes
-might never be found quantized so that we should try another approach
-to take into account the precision of quantities. However, instead
+might never be found quantized. In this situation, a better model
+could take into account the precision of quantities. However, instead
 of the precision of probability amplitudes, it is better to consider
-the precision of their inducing probabilities because the probability
-amplitudes is unlikely to be accessed directly while the probability
-of an event can be deduced after a series of experiments. Moreover,
-the idea of ``imprecise probabilities'' have well-studied classically
-\cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+the precision of their inducing probabilities because the idea of
+``imprecise probabilities'' have well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
 In Chapter~\ref{chap:QIVPM}, they will be extended it to quantum
-domain, and define quantum interval-valued probability measures (QIVPM)
-.
+domain, and define quantum interval-valued probability measures (QIVPM).
 
@@
 define the expectation value of an observable. The expectation value
-will then be used in Sec.~\ref{sec:The-geometry-of} to defined purity
+will then be used in Sec.~\ref{sec:The-geometry-of} to define purity
 which provides an easy way to decide whether a state is entangled
-or not and to defined the maximum entangled states.
+or not and to define the maximum entangled states.
 
@@
 integer), the complex numbers have extremely compelling and natural
-discrete analogs that permit a great many of the standard requirements
-of quantum computing to be preserved. In this model, the states of
-a discrete $d$-dimensional system is a vector in the $d$-dimensional
-vector space over $\Fpp$, and can be reduced to a point in the discrete
-complex projective space. Among these irreducible states, the product
-states and entangled states could not only be identified as in CQT
-but also be counted for different $p$. Despite this model's similarity
-to CQT, it still only predicts whether a measurement result is possible
-or impossible, because it is not possible to define an inner product
-in the usual sense due to the modular arithmetic~\cite{grove2002classical}.
-Under suitable conditions, we can have deterministic quantum algorithms
-such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
+discrete analogs that preserve a great many of the standard requirements
+of quantum computing. In this model, the states of a discrete $d$-dimensional
+system is a vector in the $d$-dimensional vector space over $\Fpp$,
+and can be reduced to a point in the discrete complex projective space.
+Among these irreducible states, the product states and entangled states
+could not only be identified as in CQT but also be counted for different
+$p$. Despite this model's similarity to CQT, it still only predicts
+whether a measurement result is possible or impossible, because it
+is not possible to define an inner product in the usual sense due
+to the modular arithmetic~\cite{grove2002classical}. Under suitable
+conditions, we can have deterministic quantum algorithms such as the
+algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
 and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
@@
 The cardinal probability defined in Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
-restricts states in some local regions of the vector spaces. Within
-a local region, a notion of inner product and probability could be
-recovered. In Sec.~\ref{discretequantumcomputingII}, this discrete
-quantum theory is applied on two representative algorithms, the deterministic
-Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007} and the
-probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
+restricts states in some local regions of the vector spaces, where
+a notion of inner product and probability could be recovered. In Sec.~\ref{discretequantumcomputingII},
+this discrete quantum theory is applied on two representative algorithms,
+the deterministic Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007}
+and the probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
 \begin{comment}
@@
 these could be defined easily with real-valued probabilities in CQT,
-we attempt to consider quantum probability measures over finite fields
-(QPMFF) in Sec.~\ref{sec:Toward-IVPM}. In contrast to CQT, our Gleason-like
-conditions over finite fields cannot deduce a discrete Born rule in
-general. This impossible result suggests us that the discrete and
-finite state spaces might not compatible with infinitely precise real-valued
-probability. Thus, no matter whether the probability amplitudes are
-ultimately discrete or not,
-
-it might be more natural to consider a discrete Born rule mapping
-to finite number of intervals, and we will start the discussion in
-Chapter~\ref{chap:QIVPM}.
+we attempt to consider real-valued quantum probability measures over
+finite fields (QPMFF) in Sec.~\ref{sec:Toward-IVPM}. In contrast
+to CQT, our Gleason-like conditions over finite fields cannot deduce
+a discrete Born rule in general. This impossible result suggests us
+that the discrete and finite state spaces might not be compatible
+with infinitely precise real-valued probability. Thus, no matter whether
+the probability amplitudes are ultimately discrete or continuous,
+we should study imprecise quantum probabilities formulated by quantum
+interval-valued probability measures.
 
@@
 consistent with it \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997Chinese,Grabisch2016},
-and the expectation value is \todo{Introduction Cleaned up until
-here. }
-
-Finally, we shift our attention to consider quantum interval-valued
-probability measures (IVPMs), which potentially embody both finite
-precision measurement and a sensible correspondence to standard quantum
-probability. This interval-valued framework not only provides a natural
-generalization of both classical IVPMs and conventional quantum probability
-measures, but also allows us to establish bounds on the validity of
-the Kochen-Specker and Gleason theorems in realistic experimental
-environments.
+and the expectation value with respect to it is just classical Choquet
+integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}. When
+we extend classical IVPMs to QIVPMs, these known properties of classical
+IVPMs all have their natural correspondence for QIVPMs. In Sec.~\ref{sec:Kochen-Specker},
+their expectation values will play a role in proving the Kochen-Specker
+theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+for ``almost'' certain QIVPMs. In Sec.~\ref{sec:Gleason}, we are
+able to show that, while a QIVPM incorporating the effects of finite
+precision might not be consistent with Gleason's unique state~$\rho$
+on all projectors defined on a Hilbert space~$\Hilb$ of dimension
+$d\ge3$, there is a mathematically precise sense in which one recovers
+the original Gleason theorem asymptotically. Specifically, it is possible
+to construct a class of QIVPMs representing bounded resources that
+is parameterized by the size of the intervals.
 
 \begin{sidewaystable}
-\caption{Comparison among our models, where the upper half of the table lists
-their quantum mechanical definitions and properties, and the lower
-half of the table lists their computational power.}
+\caption{\label{tab:organization}Comparison among our models, where the upper
+half of the table lists their quantum mechanical definitions and properties,
+and the lower half of the table lists their computational power.}
 
@@
 \end{sidewaystable}
+The organization of this thesis is summarized in Table~\ref{tab:organization},
+and we present our conclusions in final Chapter~\ref{chap:Conclusion}.
 
@@
 we will generalize this notation from classical IVPMs to QIVPMs, and
-prove this generalization consistent with our intuition. For example,
-if $\bar{\mu}$ is a conventional (Born) probability measure induced
-by a state $\rho$, then the interval expectation value collapses
+prove the generalized definition consistent with our intuition. For
+example, if $\bar{\mu}$ is a conventional (Born) probability measure
+induced by a state $\rho$, then the interval expectation value collapses
 to a point, thus reducing the interval expectation value to the conventional
@@
 will use a fixed collection of intervals appropriate for the resources
-and precision of the particular experiment.\todo{Add a two-page conclusion
-chapter which could include further discussion, but it can be only
-a few sentences? }\todo{Discrete Schrödinger equation? And its relation
-with Grover's algorithm? }\todo{Notice that in differential geometry,
-Killing–Hopf theorem asserts that having positive constant curvature
-guarantees a manifold is essentially a sphere, but say little things
-even if the curvature has only small deviation from constant. Since
-a quantum probability measure is glued by classical probability measures,
-like a manifold. When their relations are exact, Gleason's theorem
-asserts that a quantum probability measure can essentially induced
-by the Born rule, but they can be wild when we move on to interval-valued
-situation! }
+and precision of the particular experiment.
+
+\chapter{Conclusion\label{chap:Conclusion}}
+
+\todo{Add a two-page conclusion chapter which could include further
+discussion, but it can be only a few sentences? }\todo{Discrete
+Schrödinger equation? And its relation with Grover's algorithm? }\todo{Notice
+that in differential geometry, Killing–Hopf theorem asserts that having
+positive constant curvature guarantees a manifold is essentially a
+sphere, but say little things even if the curvature has only small
+deviation from constant. Since a quantum probability measure is glued
+by classical probability measures, like a manifold. When their relations
+are exact, Gleason's theorem asserts that a quantum probability measure
+can essentially induced by the Born rule, but they can be wild when
+we move on to interval-valued situation! }
 

### 2019-01-04 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 amplitudes are in the field of complex numbers. If the probability
-amplitudes are assumed to be ultimately discrete, we need to replace
-the field of complex numbers by some discrete structures. Finite fields
-is chosen because CQT is built upon the operations among the probability
-amplitudes, and the probability amplitudes have the required operations
-since the complex numbers form a field. The quantum theories and computing
-built upon finite fields are discussed in Chapter~\ref{chap:Unrestricted-Finite-Fields}
-and \ref{chap:DQT=000026DQC}. Alternatively, the probability amplitudes
-might never be found quantized. In this situation, a better model
-could take into account the precision of quantities. However, instead
-of the precision of probability amplitudes, it is better to consider
-the precision of their inducing probabilities because the idea of
-``imprecise probabilities'' have well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
-In Chapter~\ref{chap:QIVPM}, they will be extended it to quantum
-domain, and define quantum interval-valued probability measures (QIVPM).
+amplitudes are assumed to be ultimately discrete, we choose to replace
+the field of complex numbers by discrete finite fields as discussed
+in Chapter~\ref{chap:Unrestricted-Finite-Fields} and \ref{chap:DQT=000026DQC}
+for two reasons. On one hand, CQT is built upon the operations among
+the probability amplitudes, and the probability amplitudes have the
+required operations since the complex numbers form a field. On the
+other hand, finite fields could be based to define the fraction-like
+cardinal probability which could provide extremely small units when
+the size of the field is extremely large. Alternatively, the probability
+amplitudes might never be found quantized. In this situation, a better
+model could take into account the precision of quantities. However,
+instead of the precision of probability amplitudes, it is better to
+consider the precision of their inducing probabilities because the
+idea of ``imprecise probabilities'' have well-studied classically
+\cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+\todo{Make sure whether quantum computers can branch its computation
+based on its probability amplitudes or measured probabilities? If
+they can only branch on measured probabilities, it will provide another
+reason why we want to study the precision of the induced probabilities...
+}In Chapter~\ref{chap:QIVPM}, this idea will be extended to quantum
+domain as quantum interval-valued probability measures (QIVPM).
 
@@
 will then be used in Sec.~\ref{sec:The-geometry-of} to define purity
-which provides an easy way to decide whether a state is entangled
-or not and to define the maximum entangled states.
+which provides an easy entanglement test.
 
@@
 discrete analogs that preserve a great many of the standard requirements
-of quantum computing. In this model, the states of a discrete $d$-dimensional
+of quantum computing. In this model, the state of a discrete $d$-dimensional
 system is a vector in the $d$-dimensional vector space over $\Fpp$,
@@
 to define their arithmetic operations and expectation values. Since
-these could be defined easily with real-valued probabilities in CQT,
+they could be defined easily with real-valued probabilities in CQT,
 we attempt to consider real-valued quantum probability measures over
@@
 integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}. When
-we extend classical IVPMs to QIVPMs, these known properties of classical
-IVPMs all have their natural correspondence for QIVPMs. In Sec.~\ref{sec:Kochen-Specker},
+we extend classical IVPMs to QIVPMs, these known properties have their
+natural correspondence for QIVPMs. In Sec.~\ref{sec:Kochen-Specker},
 their expectation values will play a role in proving the Kochen-Specker
 theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-for ``almost'' certain QIVPMs. In Sec.~\ref{sec:Gleason}, we are
-able to show that, while a QIVPM incorporating the effects of finite
-precision might not be consistent with Gleason's unique state~$\rho$
-on all projectors defined on a Hilbert space~$\Hilb$ of dimension
-$d\ge3$, there is a mathematically precise sense in which one recovers
-the original Gleason theorem asymptotically. Specifically, it is possible
-to construct a class of QIVPMs representing bounded resources that
-is parameterized by the size of the intervals.
+for ``almost'' certain QIVPMs, and establish bounds on its validity
+in realistic experimental environments. In Sec.~\ref{sec:Gleason},
+we are able to show that, while a QIVPM incorporating the effects
+of finite precision might not be consistent with Gleason's unique
+state~$\rho$ on all projectors defined on a Hilbert space~$\Hilb$
+of dimension $d\ge3$, there is a mathematically precise sense in
+which one recovers the original Gleason theorem asymptotically. Specifically,
+it is possible to construct a class of QIVPMs representing bounded
+resources that is parameterized by the size of the intervals.
 

### 2019-01-06 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 we first review the ``conventional quantum theory'' (CQT)\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
-and ``ordinary'' quantum theory.} in Chapter~\ref{chap:Conventional-Quantum-Theory}, where the probability
-amplitudes are in the field of complex numbers. If the probability
-amplitudes are assumed to be ultimately discrete, we choose to replace
-the field of complex numbers by discrete finite fields as discussed
-in Chapter~\ref{chap:Unrestricted-Finite-Fields} and \ref{chap:DQT=000026DQC}
-for two reasons. On one hand, CQT is built upon the operations among
-the probability amplitudes, and the probability amplitudes have the
-required operations since the complex numbers form a field. On the
-other hand, finite fields could be based to define the fraction-like
+and ``ordinary'' quantum theory.}, where the probability amplitudes are in the field of complex numbers.
+If the probability amplitudes are assumed to be ultimately discrete,
+we choose to replace the field of complex numbers by discrete finite
+fields for two reasons. On one hand, CQT is built upon the operations
+among the probability amplitudes, and the probability amplitudes have
+the required operations since the complex numbers form a field. On
+the other hand, finite fields will be based to define the fraction-like
 cardinal probability which could provide extremely small units when
@@
 model could take into account the precision of quantities. However,
-instead of the precision of probability amplitudes, it is better to
-consider the precision of their inducing probabilities because the
-idea of ``imprecise probabilities'' have well-studied classically
+comparing to the precision of probability amplitudes, it is easier
+to consider the precision of their inducing probabilities because
+the idea of ``imprecise probabilities'' have well-studied classically
 \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
-\todo{Make sure whether quantum computers can branch its computation
-based on its probability amplitudes or measured probabilities? If
-they can only branch on measured probabilities, it will provide another
-reason why we want to study the precision of the induced probabilities...
-}In Chapter~\ref{chap:QIVPM}, this idea will be extended to quantum
-domain as quantum interval-valued probability measures (QIVPM).
+\todo{Make sure whether realistic quantum computers branch their
+computation based on its probability amplitudes or measured probabilities?
+If they can only branch on measured probabilities, it will provide
+another reason why we want to study the precision of the induced probabilities...
+}This idea will be extended to quantum domain as quantum interval-valued
+probability measures (QIVPM).
 
@@
 and the expectation value with respect to it is just classical Choquet
-integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}. When
-we extend classical IVPMs to QIVPMs, these known properties have their
-natural correspondence for QIVPMs. In Sec.~\ref{sec:Kochen-Specker},
-their expectation values will play a role in proving the Kochen-Specker
-theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-for ``almost'' certain QIVPMs, and establish bounds on its validity
-in realistic experimental environments. In Sec.~\ref{sec:Gleason},
-we are able to show that, while a QIVPM incorporating the effects
-of finite precision might not be consistent with Gleason's unique
-state~$\rho$ on all projectors defined on a Hilbert space~$\Hilb$
-of dimension $d\ge3$, there is a mathematically precise sense in
-which one recovers the original Gleason theorem asymptotically. Specifically,
-it is possible to construct a class of QIVPMs representing bounded
-resources that is parameterized by the size of the intervals.
+integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}. These
+classical properties can naturally be extended for QIVPMs when we
+extend classical IVPMs to QIVPMs. In Sec.~\ref{sec:Kochen-Specker},
+we utilize the previous defined expectation values while proving the
+finite precision variants of the Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
+and establish bounds on its validity in realistic experimental environments.
+In Sec.~\ref{sec:Gleason}, we are able to show that, while a QIVPM
+incorporating the effects of finite precision might not be consistent
+with Gleason's unique state~$\rho$ on all projectors defined on
+a Hilbert space~$\Hilb$ of dimension $d\ge3$, there is a mathematically
+precise sense in which one recovers the original Gleason theorem asymptotically.
+Specifically, it is possible to construct a class of QIVPMs representing
+bounded resources that is parameterized by the size of the intervals.
 

### 2019-01-06 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 two possibilities dealing with real-valued models inspires us two
-types of quantum models. Similar to classical analog computers, the
-quantum circuit model, the most widely used model of quantum computing,
-manipulates quantities which are not discrete apparently: the probability
-amplitudes of quantum states. To address the similar inconsistency,
-we first review the ``conventional quantum theory'' (CQT)\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+types of quantum models. Similar to classical analog computers, quantum
+circuit model, the most widely used model of quantum computing, manipulates
+quantities which are not discrete apparently: the probability amplitudes
+of quantum states. To address the similar inconsistency, we first
+review the ``conventional quantum theory'' (CQT)\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
 and ``ordinary'' quantum theory.}, where the probability amplitudes are in the field of complex numbers.
@@
 the required operations since the complex numbers form a field. On
-the other hand, finite fields will be based to define the fraction-like
-cardinal probability which could provide extremely small units when
-the size of the field is extremely large. Alternatively, the probability
-amplitudes might never be found quantized. In this situation, a better
-model could take into account the precision of quantities. However,
+the other hand, based on finite fields, we will define the fraction-like
+cardinal probability which has extremely small units when the size
+of the field is extremely large. Alternatively, even if the probability
+amplitudes might never be found quantized, taking into account the
+precision of quantities could still result in a better model. However,
 comparing to the precision of probability amplitudes, it is easier
@@
 \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
-\todo{Make sure whether realistic quantum computers branch their
-computation based on its probability amplitudes or measured probabilities?
-If they can only branch on measured probabilities, it will provide
-another reason why we want to study the precision of the induced probabilities...
-}This idea will be extended to quantum domain as quantum interval-valued
-probability measures (QIVPM).
+\todo{Make sure whether realistic quantum computers could branch
+their computation based on their probability amplitudes or measured
+probabilities? If they can only branch on their measured probabilities,
+it will provide another reason why we want to study the precision
+of the induced probabilities... }This idea will be extended to quantum
+domain as quantum interval-valued probability measures (QIVPM).
 

### 2019-01-07 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 above them are summarized in Table~\ref{tab:Comparison}, and the
-two possibilities dealing with real-valued models inspires us two
-types of quantum models. Similar to classical analog computers, quantum
-circuit model, the most widely used model of quantum computing, manipulates
-quantities which are not discrete apparently: the probability amplitudes
-of quantum states. To address the similar inconsistency, we first
-review the ``conventional quantum theory'' (CQT)\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+two classical possibilities inspires us two types of quantum models.
+Similar to its classical counterparts, quantum circuit model, the
+most widely used model of quantum computing, manipulates quantities
+which are not discrete apparently: the probability amplitudes of quantum
+states. To address the similar inconsistency, we first review the
+``conventional quantum theory'' (CQT)\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
 and ``ordinary'' quantum theory.}, where the probability amplitudes are in the field of complex numbers.
@@
 it will provide another reason why we want to study the precision
-of the induced probabilities... }This idea will be extended to quantum
+of the inducing probabilities... }This idea will be extended to quantum
 domain as quantum interval-valued probability measures (QIVPM).

### 2019-01-07 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

@@
 \centering{}\centering{}%
-\begin{tabularx}{\linewidth}{ccYY}
+\begin{tabularx}{\linewidth}{YcYY}
 \toprule 
 \addlinespace
-Physical quantities & Discrete & Discrete with extreme small unit & Continuous, or no evidence to support they are discrete\tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-Computational devices & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
+Physical quantity & Discrete & Discrete with extreme small units & Continuous, or no evidence to support they are discrete\tabularnewline\addlinespace
+\addlinespace
+\addlinespace
+Computational device & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
 \addlinespace
@@
 \addlinespace
-Mathematical representation & Integers & Real numbers & Real numbers\tabularnewline\addlinespace
+Mathematical representation & Integer & Real number & Real number\tabularnewline\addlinespace
 \addlinespace
@@
 \addlinespace
-How the models realize? & Reliably & 
+How does the theorical model predict the behavior of the Physical device? & 
+Reliably & 
 Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computational power by a better discrete model. & 
@@
 \addlinespace
-Inspired quantum models &  & Quantum theories and computing over finite fields & Quantum interval-valued probability measures (QIVPM)\tabularnewline\addlinespace
+Inspired quantum model &  & Quantum theories and computing over finite fields & Quantum interval-valued probability measures (QIVPM)\tabularnewline\addlinespace
 \addlinespace
@@
 The situations for classical quantities and the computational power
-above them are summarized in Table~\ref{tab:Comparison}, and the
-two classical possibilities inspires us two types of quantum models.
-Similar to its classical counterparts, quantum circuit model, the
-most widely used model of quantum computing, manipulates quantities
+above them are summarized in Table~\ref{tab:Comparison}, and two
+possibilities for classical quantities inspires two types of quantum
+models. Similar to its classical counterparts, quantum circuit model,
+the most widely used model of quantum computing, manipulates quantities
 which are not discrete apparently: the probability amplitudes of quantum

### 2019-01-08 dissertation.tex
dissertation.lyx "Chapter 6 Further Discussion" Updating...

@@
 bounded resources that is parameterized by the size of the intervals.
+We then demonstrate that all QIVPMs in this class are consistent with
+a non-empty “ball” of quantum states whose radius is defined
+by the maximal length of the intervals characterizing the uncertainties.
+As the size of the intervals goes to zero, this ball of quantum states
+converges to a point representing the unique state consistent with
+the Born rule and Gleason's theorem.
 
@@
 The organization of this thesis is summarized in Table~\ref{tab:organization},
-and we present our conclusions in final Chapter~\ref{chap:Conclusion}.
+and the further extended questions are in final Chapter~\ref{chap:Further-Discussion}.
 
@@
 
+\chapter{Further Discussion\label{chap:Further-Discussion}}
+
+As we discussed in previous section, the finite-precision extension
+of the Gleason theorem, Thm.~\ref{thm:Finite-precision-Gleason},
+only applies on a class of QIVPMs inducing by composting interval
+maps $f:\left[0,1\right]\rightarrow\mathscr{I}$ and quantum probability
+measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$.
+
+\begin{comment}
+ Almost all QIVPMs in Chapter~\ref{chap:QIVPM} are closely related
+to quantum probability measures. For example, given a $\delta$-deterministic
+QIVPM, Lemma~\ref{lemma:delta2zero} provides a way to derive a $0$-deterministic
+QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
+which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+satisfying $\mu\left(P\right)$ is either $0$ or $1$. Moreover,
+an interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$ in Sec.~\ref{sec:Gleason}
+provides an systemic way to derive QIVPMs from quantum probability
+measures.
+
+the only QIVPM unrelated to quantum probability measures is defined
+in Table~\ref{tab:non-Born-QIVPM}, and is ill-behaved as having
+an empty core.
+
+On one hand, classical IVPMs could be studied directly without deriving
+from or to classical probability measures.
+
+On the other hand, to state the original Gleason theorem, we don't
+need to know a state a priori, and use this state to derive a quantum
+probability measures and further a QIVPM. Therefore, it would be desirable
+if we could answer the following variant of Gleason theorem which
+
+whether shirking the maximum length of intervals alone could provide
+a well-behaved QIVPMs. More precisely, we have the following question.
+
+\begin{question}In a Hilbert space $\Hilb$ of dimension $D\geq3$,
+given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, $\alpha$
+be the maximum length of intervals in $\mathscr{I}$, is there an
+$\varepsilon\in\left(0,1\right)$ such that $\alpha<\varepsilon$
+implies $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
+\end{comment}
+\begin{comment}
+
 \chapter{Conclusion\label{chap:Conclusion}}
@@
 we move on to interval-valued situation! }
+\end{comment}
 

### 2019-01-09 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" and "Chapter 6 Further Discussion" Updating...

@@
 The organization of this thesis is summarized in Table~\ref{tab:organization},
-and the further extended questions are in final Chapter~\ref{chap:Further-Discussion}.
+and finally Chapter~\ref{chap:Further-Discussion} contains the further
+extended questions.
 
@@
 
-As we discussed in previous section, the finite-precision extension
+\begin{comment}
+When people proved the original Gleason theorem, people usually exploited
+the geometrical structure of real 3-dimensional Hilbert space \cite{gleason1957,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+Since our finite-precision extension of the Gleason theorem only applies
+on a class of QIVPMs, we might want to ask how to modify these geometrical
+arguments to have a Gleason-type theorem for general QIVPMs. We will
+further study the tensor product structure among QIVPMs which is essential
+for defining product and entangled states, and serves the basis to
+discuss quantum nonlocality~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
+and quantum computing with QIVPMs. Finally, we want to improve the
+discrete quantum theories to consider QIVPMs over finite fields in
+future research.
+\end{comment}
+As we discussed in the previous section, the finite-precision extension
 of the Gleason theorem, Thm.~\ref{thm:Finite-precision-Gleason},
-only applies on a class of QIVPMs inducing by composting interval
-maps $f:\left[0,1\right]\rightarrow\mathscr{I}$ and quantum probability
-measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$.
-
-\begin{comment}
- Almost all QIVPMs in Chapter~\ref{chap:QIVPM} are closely related
-to quantum probability measures. For example, given a $\delta$-deterministic
-QIVPM, Lemma~\ref{lemma:delta2zero} provides a way to derive a $0$-deterministic
-QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
-which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
-satisfying $\mu\left(P\right)$ is either $0$ or $1$. Moreover,
-an interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$ in Sec.~\ref{sec:Gleason}
-provides an systemic way to derive QIVPMs from quantum probability
-measures.
-
-the only QIVPM unrelated to quantum probability measures is defined
-in Table~\ref{tab:non-Born-QIVPM}, and is ill-behaved as having
-an empty core.
-
-On one hand, classical IVPMs could be studied directly without deriving
-from or to classical probability measures.
-
-On the other hand, to state the original Gleason theorem, we don't
-need to know a state a priori, and use this state to derive a quantum
-probability measures and further a QIVPM. Therefore, it would be desirable
-if we could answer the following variant of Gleason theorem which
-
-whether shirking the maximum length of intervals alone could provide
-a well-behaved QIVPMs. More precisely, we have the following question.
+only applies on the QIVPMs composted by interval maps $f:\left[0,1\right]\rightarrow\mathscr{I}$
+and quantum probability measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$,
+where the maximum length of intervals in $\mathscr{I}$ is an important
+. In this case, the states consistent with the composition $f\circ\muB_{\rho}$
+is bounded by . While the QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
+is not in this class, it is too wild to have a non-empty core, and
+the maximum length of its intervals $\mathscr{I}_{0}$ is $1$, the
+longest length of all possible intervals. This suggests us to ask
+if we shirk the maximum length of intervals alone, whether this ill-behaved
+QIVPMs disappears. More precisely, we have the following question.
 
 \begin{question}In a Hilbert space $\Hilb$ of dimension $D\geq3$,
-given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, $\alpha$
+given a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, $\alpha$
 be the maximum length of intervals in $\mathscr{I}$, is there an
-$\varepsilon\in\left(0,1\right)$ such that $\alpha<\varepsilon$
-implies $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
-\end{comment}
+$\varepsilon>0$ such that $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$
+for $\alpha<\varepsilon$.\end{question}
+
+\noindent %
 \begin{comment}

### 2019-01-10 dissertation.tex
dissertation.lyx Preface and "Chapter 6 Further Discussion" Updating...

@@
 \item Its source code is typeset using \LyX ~\cite{LyX} in: \code{https://git.io/fxbuE}
+and the exported \LaTeX{} is in \code{https://git.io/fhZBW}.
 \item Any comments can be left in the Issue part of the GitHub Repository:
@@
 \end{itemize}
+Following explains how to compile the PDF from the source:
+\begin{enumerate}
+\item Clone the document class \code{https://github.com/yuttai/iuphd} in
+a location where the system can find.
+\item Run \code{xelatex dissertation.tex}.
+\item Run \code{biber dissertation}.
+\item Run \code{xelatex dissertation.tex} several times until all the references
+are resolved.
+\end{enumerate}
 \end{preface*}
@@
 and quantum probability measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$,
-where the maximum length of intervals in $\mathscr{I}$ is an important
-. In this case, the states consistent with the composition $f\circ\muB_{\rho}$
-is bounded by . While the QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
-is not in this class, it is too wild to have a non-empty core, and
-the maximum length of its intervals $\mathscr{I}_{0}$ is $1$, the
-longest length of all possible intervals. This suggests us to ask
-if we shirk the maximum length of intervals alone, whether this ill-behaved
-QIVPMs disappears. More precisely, we have the following question.
+and the states consistent with the composition $f\circ\muB_{\rho}$
+converges to $\rho$ as the maximum length of intervals in $\mathscr{I}$
+shrinking to $0$. In contrast, the wildest QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
+is not in this class and the maximum length of its intervals $\mathscr{I}_{0}$
+is $1$, the longest length of all possible intervals. This doesn't
+rule out the possibility that shirking the maximum length of intervals
+itself could result QIVPMs with non-empty cores. More precisely, we
+have the following question.
 
@@
 \end{comment}
+To understand how difficult this question could be,
 

### 2019-01-11 dissertation.tex
dissertation.lyx "Preface" and "Chapter 6 Further Discussion" Updating...

--- 2019-01-09 dissertation.tex
@@
 \newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{R{#1}}}}
+\newcommand{\frameL}[1][]{\ensuremath{f^{L{#1}}}}
+\newcommand{\frameR}[1][]{\ensuremath{f^{R{#1}}}}
 \newcommand{\pmeas}{\ensuremath{\mu}}
@@
 \begin{itemize}
-\item The latest version of this thesis is in GitHub: \code{https://git.io/fxbuG}
-\item Its source code is typeset using \LyX ~\cite{LyX} in: \code{https://git.io/fxbuE}
-\item Any comments can be left in the Issue part of the GitHub Repository:
-\code{https://git.io/fxbug}
+\item The latest PDF version of this thesis is in GitHub: \code{https://git.io/fxbuG}.
+\item Its source code is typeset using \LyX ~\cite{LyX} in \code{https://git.io/fxbuE}
+and the exported \LaTeX{} file is in \code{https://git.io/fhZBW}.
+\item Any comments can be left in the Issue part of the GitHub repository:
+\code{https://git.io/fxbug}.
 \end{itemize}
-\end{preface*}
+Following explains how to compile the PDF from the \LaTeX{} source:
+\begin{enumerate}
+\item \label{enu:Clone-the-git}Clone the git repository of this thesis
+\code{https://git.io/fhZP5} into your local directory and the thesis
+document class \code{https://github.com/yuttai/iuphd} in a location
+where the system can find.
+\item In the local directory of this thesis, run \code{xelatex dissertation.tex}.
+\item Run \code{biber dissertation}.
+\item Run \code{xelatex dissertation.tex} several times until all the references
+are resolved.
+\end{enumerate}
+The previous steps only tested in Microsoft Windows. Please report
+me if there is any difficulty compile it in the other system. Besides,
+to compile the PDF file from \LyX{} source, just finish step~\ref{enu:Clone-the-git}
+and click the toolbar button \includegraphics[width=1em]{buffer-view}.\end{preface*}
 
@@
 
-\subsection{Ultramodular Functions}
+\subsection{Ultramodular Functions\label{subsec:Ultramodular-Functions}}
 
@@
 only applies on the QIVPMs composted by interval maps $f:\left[0,1\right]\rightarrow\mathscr{I}$
-and quantum probability measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$,
-where the maximum length of intervals in $\mathscr{I}$ is an important
-. In this case, the states consistent with the composition $f\circ\muB_{\rho}$
-is bounded by . While the QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
-is not in this class, it is too wild to have a non-empty core, and
-the maximum length of its intervals $\mathscr{I}_{0}$ is $1$, the
-longest length of all possible intervals. This suggests us to ask
-if we shirk the maximum length of intervals alone, whether this ill-behaved
-QIVPMs disappears. More precisely, we have the following question.
+and quantum probability measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$;
+the states consistent with the composition $f\circ\muB_{\rho}$ converges
+to $\rho$ as the maximum length of intervals in $\mathscr{I}$ shrinking
+to $0$. In contrast, the wildest QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
+maps to $\mathscr{I}_{0}$ whose intervals' maximum length is $1$,
+the longest possible length. This provides another possibility that
+shirking the maximum length of intervals itself could result QIVPMs
+with non-empty cores. More precisely, we have the following question.
 
 \begin{question}In a Hilbert space $\Hilb$ of dimension $D\geq3$,
-given a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, $\alpha$
-be the maximum length of intervals in $\mathscr{I}$, is there an
-$\varepsilon>0$ such that $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$
+given a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\alpha$
+being the maximum length of intervals in $\mathscr{I}$, is there
+an $\varepsilon>0$ such that $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$
 for $\alpha<\varepsilon$.\end{question}
 
-\noindent %
 \begin{comment}
@@
 \end{comment}
+To better understand this question, we start from the dimension $D=3$.
+This case is simpler than the general situation because any two-dimensional
+projectors can be expressed as the complement of a one-dimensional
+projector, $\mathbb{1}-\ket{\psi}$. Together with Eq.~\ref{eq:QIVPM-complement},
+the interval-valued probability of any two-dimensional projectors,
+$\bar{\mu}\left(\mathbb{1}-\ket{\psi}\right)$, can also be expressed
+as the complement of the latter, $\necess-\bar{\mu}\left(\ket{\psi}\right)$.
+Since the one-dimensional projectors are one-to-one corresponding
+to the irreducible states in the complex projective space $\CP{2}$
+as discussed in Sec.~\ref{subsec:Explicit-generalization-of}, QIVPMs
+$\bar{\mu}:\events\rightarrow\mathscr{I}$ are one-to-one corresponding
+to interval-valued frame functions $\bar{f}:\CP{2}\rightarrow\mathscr{I}$
+according to the following lemma.
+
+\begin{lemma}\label{thm:interval-valued-frame-function}Given a QIVPM
+$\bar{\mu}:\events\rightarrow\mathscr{I}$, the function $\bar{f}:\CP{2}\rightarrow\mathscr{I}$
+by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$
+are called an interval-valued frame function, and satisfies
+\begin{equation}
+\left[1,1\right]-\bar{f}\left(\ket{\psi_{0}}\right)\subseteq\bar{f}\left(\ket{\psi_{1}}\right)+\bar{f}\left(\ket{\psi_{2}}\right)\label{eq:interval-valued-frame-function}
+\end{equation}
+for any orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
+Conversely, if a function $\bar{f}:\CP{2}\rightarrow\mathscr{I}$
+satisfies Eq.~\ref{eq:interval-valued-frame-function}, $\bar{f}$
+must be an interval-valued frame function.\end{lemma}
+
+\begin{proof}This lemma is the direct consequence of Lemma~\ref{thm:convex-3-1}.\end{proof}
+
+Similar to the ultramodular functions in Sec.~\ref{subsec:Ultramodular-Functions},
+we can also decompose an interval-valued frame function into its left-end
+and right-end, where $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]=\bar{f}\left(\ket{\psi}\right)$.
+Then, Eq.~\ref{eq:interval-valued-frame-function} can be rephrased
+as
+\begin{equation}
+\left[1,1\right]-\bar{f}\left(\ket{\psi_{0}}\right)\subseteq\bar{f}\left(\ket{\psi_{1}}\right)+\bar{f}\left(\ket{\psi_{2}}\right)\label{eq:two-ends-frame-function}
+\end{equation}
 

### 2019-01-12 dissertation.tex
dissertation.lyx "Preface" and "Chapter 6 Further Discussion" Updating...

--- 2019-01-09 dissertation.tex
@@
 \begin{itemize}
-\item The latest version of this thesis is in GitHub: \code{https://git.io/fxbuG}
-\item Its source code is typeset using \LyX ~\cite{LyX} in: \code{https://git.io/fxbuE}
-\item Any comments can be left in the Issue part of the GitHub Repository:
-\code{https://git.io/fxbug}
+\item The latest PDF version of this thesis is in GitHub: \code{https://git.io/fxbuG}.
+\item Its source code is typeset using \LyX ~\cite{LyX} in \code{https://git.io/fxbuE}
+and the exported \LaTeX{} file is in \code{https://git.io/fhZBW}.
+\item Any comments can be left in the Issue part of the GitHub repository:
+\code{https://git.io/fxbug}.
 \end{itemize}
-\end{preface*}
+Following explains how to compile the PDF from the \LaTeX{} source:
+\begin{enumerate}
+\item \label{enu:Clone-the-git}Clone the git repository of this thesis
+\code{https://git.io/fhZP5} into your local directory and the thesis
+document class \code{https://github.com/yuttai/iuphd} in a location
+where the system can find.
+\item In the local directory of this thesis, run \code{xelatex dissertation.tex}.
+\item Run \code{biber dissertation}.
+\item Run \code{xelatex dissertation.tex} several times until all the references
+are resolved.
+\end{enumerate}
+The previous steps only tested in Microsoft Windows. Please report
+me if there is any difficulty to compile it. Besides, to compile a
+PDF file from the \LyX{} source, just finish step~\ref{enu:Clone-the-git}
+and click the toolbar button \includegraphics[width=1em]{buffer-view}.\end{preface*}
 
@@
 of the Gleason theorem, Thm.~\ref{thm:Finite-precision-Gleason},
-only applies on the QIVPMs composted by interval maps $f:\left[0,1\right]\rightarrow\mathscr{I}$
-and quantum probability measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$,
-where the maximum length of intervals in $\mathscr{I}$ is an important
-. In this case, the states consistent with the composition $f\circ\muB_{\rho}$
-is bounded by . While the QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
-is not in this class, it is too wild to have a non-empty core, and
-the maximum length of its intervals $\mathscr{I}_{0}$ is $1$, the
-longest length of all possible intervals. This suggests us to ask
-if we shirk the maximum length of intervals alone, whether this ill-behaved
-QIVPMs disappears. More precisely, we have the following question.
-
-\begin{question}In a Hilbert space $\Hilb$ of dimension $D\geq3$,
-given a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, $\alpha$
-be the maximum length of intervals in $\mathscr{I}$, is there an
-$\varepsilon>0$ such that $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$
-for $\alpha<\varepsilon$.\end{question}
-
-\noindent %
+only applies on the QIVPMs composed by interval maps $f:\left[0,1\right]\rightarrow\mathscr{I}$
+and quantum probability measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$:
+the states consistent with the composition $f\circ\muB_{\rho}$ converges
+to $\rho$ as the maximum length of intervals in $\mathscr{I}$ shrinking
+to $0$. In contrast, the wildest QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
+maps to $\mathscr{I}_{0}$ whose intervals' maximum length is $1$,
+the longest possible length. This provides another possibility that
+shirking the maximum length of intervals itself could result the QIVPMs
+mapping to these intervals having non-empty cores. More precisely,
+we have the following question.
+
+\begin{question}\label{question:approximation-Gleason}Given a Hilbert
+space $\Hilb$ of dimension $D\geq3$, is there an $\varepsilon>0$
+such that for all QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
+satisfying the maximum length of intervals in $\mathscr{I}$ less
+than $\varepsilon$, $\bar{\mu}$ must have an non-empty core, i.e.,
+$\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
+
 \begin{comment}
@@
 \end{comment}
+To better understand this question, consider the $D=3$ situation
+which is largely simplified by the fact that any two-dimensional projectors
+can be expressed as the complement of a one-dimensional projector,
+and by Eq.~(\ref{eq:QIVPM-complement}) so does their interval-valued
+probabilities, i.e., $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\necess-\bar{\mu}\left(\proj{\psi}\right)$.
+Hence, a QIVPM is completely determined by its values on the one-dimensional
+projectors which are one-to-one corresponding to the irreducible states,
+and these irreducible states are encoded in the complex projective
+space $\CP{2}$ as discussed in Sec.~\ref{subsec:Explicit-generalization-of}.
+To further simplify the question, for any state $\ket{\psi}\in\CP{2}$,
+we can decompose interval-valued probabilities on these states into
+its left-end and right-end, where $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]=\bar{\mu}\left(\proj{\psi}\right)$.
+According to Lemma~\ref{thm:convex-3-1}, $\bar{\mu}:\events\rightarrow\mathscr{I}$
+is a QIVPM if and only if the pair of functions $\frameL:\CP{2}\rightarrow\left[0,1\right]$
+and $\frameR:\CP{2}\rightarrow\left[0,1\right]$ satisfying the following
+interval-inclusion
+\begin{equation}
+\left[1,1\right]-\left[\frameL\left(\ket{\psi_{0}}\right),\frameR\left(\ket{\psi_{0}}\right)\right]\subseteq\left[\frameL\left(\ket{\psi_{1}}\right),\frameR\left(\ket{\psi_{1}}\right)\right]+\left[\frameL\left(\ket{\psi_{2}}\right),\frameR\left(\ket{\psi_{2}}\right)\right]\label{eq:interval-valued-frame-function}
+\end{equation}
+for any orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
+This interval-inclusion can be rephrased as a long inequality
+\begin{equation}
+\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)\le1-\frameR\left(\ket{\psi_{0}}\right)\le1-\frameL\left(\ket{\psi_{0}}\right)\le\frameR\left(\ket{\psi_{1}}\right)+\frameR\left(\ket{\psi_{2}}\right)\,.
+\end{equation}
+Since the maximum length of intervals in $\mathscr{I}$ is less than
+$\varepsilon$, $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]\in\mathscr{I}$
+implies $\frameR\left(\ket{\psi}\right)-\frameL\left(\ket{\psi}\right)<\varepsilon$.
+Then, the largest term in the previous inequality $\frameR\left(\ket{\psi_{1}}\right)+\frameR\left(\ket{\psi_{2}}\right)$
+is bounded by $\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)+2\varepsilon$.
+In another word, the left-end function satisfies the following inequalities
+\begin{subequations}
+\begin{eqnarray}
+ &  & \frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)\le1-\frameL\left(\ket{\psi_{0}}\right)\le\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)+2\varepsilon\,.\\
+ & \Leftrightarrow & 1-2\varepsilon\le\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)\le1\,.\label{eq:left-end-frame-function}
+\end{eqnarray}
+\end{subequations}
+In this language, Gleason's theorem basically states that when $\varepsilon=0$,
+given any function $\frameL:\CP{2}\rightarrow\left[0,1\right]$ satisfying
+Eq.~(\ref{eq:left-end-frame-function}), there exists a unique mixed
+state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such that 
+\begin{equation}
+\frameL\left(\ket{\psi}\right)=\melem{\psi}{\rho}{\psi}\label{eq:Gleason-for-CP2}
+\end{equation}
+for any $D$-dimensional projector~$P$, where $\ket{\Phi_{j}}\in\mathcal{H}$
+are normalized, $q_{j}>0$, and $\sum_{j=1}^{N}q_{j}=1$. Our Question~\ref{question:approximation-Gleason}
+ask what $\frameL$ would look like with a positive $\varepsilon$.
+
+With different settings, whether there is an approximate version of
+Gleason's theorem in general was asked by Sam Sanders in constructivenews~\cite{Sanders2013},
+and there is no clear answer for his question as far as I understand.
+To have an idea how hard this question could be, recall in Sec.~\ref{sec:fuzzy}
+we state that a quantum probability space is glued by a family of
+classical probability spaces. This is similar to the situation that
+a manifold is glued by many local coordinates. When the curvature
+of each small piece is ``exactly'' the same and positive, Killing-Hopf
+theorem asserts this manifold is a sphere, but little can we say even
+if the curvature has only small deviation from constant. Similar situation
+might happen when approximating Gleason's theorem. Since the sum of
+$\frameL$ on each local classical probability space is ``exactly''
+the same and equal to $1$, Gleason's theorem can assert $\frameL$
+can be expressed as Eq.~\ref{eq:Gleason-for-CP2}. However, when
+each local classical probability space becomes imprecise, a general
+$\frameL$ might be as wild as we can image, and we might say little
+about its global property.
 

### 2019-01-13 dissertation.tex
dissertation.lyx Preface, 5.3.1 Finite-Precision Extension of Gleason's Theorem, and Chapter 6 Further Discussion Updating...

@@
 \end{enumerate}
-The previous steps only tested in Microsoft Windows. Please report
-me if there is any difficulty to compile it. Besides, to compile a
-PDF file from the \LyX{} source, just finish step~\ref{enu:Clone-the-git}
-and click the toolbar button \includegraphics[width=1em]{buffer-view}.\end{preface*}
+The previous steps only tested in Microsoft Windows with MiK\TeX ~2.9.
+Please report me if there is any difficulty to compile it. Besides,
+to compile a PDF file from the \LyX{} source, just finish step~\ref{enu:Clone-the-git},
+open \code{dissertation.lyx} in \LyX , and click the toolbar button
+\includegraphics[width=1em]{buffer-view}.\end{preface*}
 
@@
 probabilities (this should not be confused with the interval-valued
-probability $\unknown$). We also need a notion of \emph{norm} to
-quantify the distance between (pure or mixed) states. The norm of
-a pure state $\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
+probability $\unknown$). Let $\left|\mathscr{I}\right|$ be the maximum
+length of intervals in $\mathscr{I}$. We also need a notion of \emph{norm}
+to quantify the distance between (pure or mixed) states. The norm
+of a pure state $\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
 For any given Hermitian operator~$A$, we choose the operator norm
@@
 is the probability measure induced by the Born rule for a given state~$\rho$.
-Let $\alpha$ be the maximum length of intervals in $\mathscr{I}$.
 If a state $\rho'$ is consistent with $f\circ\muB_{\rho}$ on all
 events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
-then the norm of their difference is bounded by $\alpha$, i.e., $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{thm}
+then the norm of their difference is bounded by $\left|\mathscr{I}\right|$,
+i.e., $\left\Vert \rho-\rho'\right\Vert \le\left|\mathscr{I}\right|$.\end{thm}
 
@@
 for any one-dimensional projector $P=\proj{\psi}$. Since the maximum
-length of the intervals in $\mathscr{I}$ is $\alpha$, it is also
-the upper bound of the difference: 
-\begin{equation}
-\left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le\alpha\,.
+length of the intervals in $\mathscr{I}$ is $\left|\mathscr{I}\right|$,
+it is also the upper bound of the difference: 
+\begin{equation}
+\left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le\left|\mathscr{I}\right|\,.
 \end{equation}
@@
 and equal to $\left\Vert \rho-\rho'\right\Vert $~\cite{GolubVanLoan1996,Foucart2012}.
-Hence, $\left\Vert \rho-\rho'\right\Vert \le\alpha$.\end{proof}
+Hence, $\left\Vert \rho-\rho'\right\Vert \le\left|\mathscr{I}\right|$.\end{proof}
 
@@
 \chapter{Further Discussion\label{chap:Further-Discussion}}
+
+\section{Gleason's Theorem for General QIVPMs}
 
@@
 \end{comment}
-As we discussed in the previous section, the finite-precision extension
-of the Gleason theorem, Thm.~\ref{thm:Finite-precision-Gleason},
-only applies on the QIVPMs composed by interval maps $f:\left[0,1\right]\rightarrow\mathscr{I}$
-and quantum probability measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$:
-the states consistent with the composition $f\circ\muB_{\rho}$ converges
-to $\rho$ as the maximum length of intervals in $\mathscr{I}$ shrinking
-to $0$. In contrast, the wildest QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
-maps to $\mathscr{I}_{0}$ whose intervals' maximum length is $1$,
-the longest possible length. This provides another possibility that
-shirking the maximum length of intervals itself could result the QIVPMs
-mapping to these intervals having non-empty cores. More precisely,
-we have the following question.
+Recall in previous section, we denote the maximum length of intervals
+in $\mathscr{I}$ as $\left|\mathscr{I}\right|$. The finite-precision
+extension of the Gleason theorem, Thm.~\ref{thm:Finite-precision-Gleason},
+only applies on the QIVPMs of the form $f\circ\muB_{\rho}$ and states
+that as $\left|\mathscr{I}\right|$ shrinks to $0$, the composition
+$f\circ\muB_{\rho}$ would be better in the sense that the states
+consistent with the composition $f\circ\muB_{\rho}$ converges to
+$\rho$. In contrast, the wildest QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
+has the range~$\mathscr{I}_{0}$ with $\left|\mathscr{I}_{0}\right|=1$,
+the longest possible length. This suggests that shrinking the length
+$\left|\mathscr{I}\right|$ might regularize QIVPMs mapping to $\mathscr{I}$
+as the following question.
 
@@
 such that for all QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
-satisfying the maximum length of intervals in $\mathscr{I}$ less
-than $\varepsilon$, $\bar{\mu}$ must have an non-empty core, i.e.,
-$\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
+satisfying $\left|\mathscr{I}\right|<\varepsilon$, $\bar{\mu}$ must
+have an non-empty core, i.e., $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
 
@@
 \end{comment}
-To better understand this question, consider the $D=3$ situation
-which is largely simplified by the fact that any two-dimensional projectors
-can be expressed as the complement of a one-dimensional projector,
-and by Eq.~(\ref{eq:QIVPM-complement}) so does their interval-valued
-probabilities, i.e., $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\necess-\bar{\mu}\left(\proj{\psi}\right)$.
+To better understand this question, consider the $D=3$ situation,
+where any two-dimensional projectors can be expressed as the complement
+of a one-dimensional projector, and by Eq.~(\ref{eq:QIVPM-complement})
+so does their interval-valued probabilities, i.e., $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\necess-\bar{\mu}\left(\proj{\psi}\right)$.
 Hence, a QIVPM is completely determined by its values on the one-dimensional
@@
 To further simplify the question, for any state $\ket{\psi}\in\CP{2}$,
-we can decompose interval-valued probabilities on these states into
-its left-end and right-end, where $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]=\bar{\mu}\left(\proj{\psi}\right)$.
+we can decompose the interval-valued probabilities on its projectors
+$\proj{\psi}$ into the left-end and right-end on $\ket{\psi}$, i.e.,
+$\bar{\mu}\left(\proj{\psi}\right)=\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]$.
 According to Lemma~\ref{thm:convex-3-1}, $\bar{\mu}:\events\rightarrow\mathscr{I}$
@@
 \end{equation}
-Since the maximum length of intervals in $\mathscr{I}$ is less than
-$\varepsilon$, $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]\in\mathscr{I}$
-implies $\frameR\left(\ket{\psi}\right)-\frameL\left(\ket{\psi}\right)<\varepsilon$.
-Then, the largest term in the previous inequality $\frameR\left(\ket{\psi_{1}}\right)+\frameR\left(\ket{\psi_{2}}\right)$
+Since $\left|\mathscr{I}\right|<\varepsilon$, the length of every
+interval $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]$
+is bounded by $\varepsilon$ as well, which implies the largest term
+in the previous inequality $\frameR\left(\ket{\psi_{1}}\right)+\frameR\left(\ket{\psi_{2}}\right)$
 is bounded by $\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)+2\varepsilon$.
@@
 \end{equation}
-for any $D$-dimensional projector~$P$, where $\ket{\Phi_{j}}\in\mathcal{H}$
+for any state $\ket{\psi}\in\CP{2}$, where $\ket{\Phi_{j}}\in\mathcal{H}$
 are normalized, $q_{j}>0$, and $\sum_{j=1}^{N}q_{j}=1$. Our Question~\ref{question:approximation-Gleason}
-ask what $\frameL$ would look like with a positive $\varepsilon$.
+then ask what $\frameL$ would look like with a positive $\varepsilon$.
 
@@
 classical probability spaces. This is similar to the situation that
-a manifold is glued by many local coordinates. When the curvature
-of each small piece is ``exactly'' the same and positive, Killing-Hopf
+a manifold is glued by many local coordinates. When each small piece
+has \emph{exactly} the same and positive curvature, the Killing-Hopf
 theorem asserts this manifold is a sphere, but little can we say even
@@
 might happen when approximating Gleason's theorem. Since the sum of
-$\frameL$ on each local classical probability space is ``exactly''
-the same and equal to $1$, Gleason's theorem can assert $\frameL$
-can be expressed as Eq.~\ref{eq:Gleason-for-CP2}. However, when
-each local classical probability space becomes imprecise, a general
-$\frameL$ might be as wild as we can image, and we might say little
-about its global property.
+$\frameL$ on each ``local'' classical probability space, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$,
+is \emph{exactly} the same and equal to $1$, Gleason's theorem can
+assert $\frameL$ can be expressed as Eq.~(\ref{eq:Gleason-for-CP2}).
+However, when each local classical probability space becomes imprecise,
+a general $\frameL$ might be as wild as we can imagine, and we might
+say little about its global property.
+
+\section{And Beyond\ldots}
 

### 2019-01-13 dissertation.tex
dissertation.lyx Global replace $\left|\mathscr{I}\right|$ by $\left\Vert \mathscr{I}\right\Vert $...

@@
 probabilities (this should not be confused with the interval-valued
-probability $\unknown$). Let $\left|\mathscr{I}\right|$ be the maximum
-length of intervals in $\mathscr{I}$. We also need a notion of \emph{norm}
-to quantify the distance between (pure or mixed) states. The norm
-of a pure state $\rho=\proj{\psi}$ is defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
+probability $\unknown$). We also need a notion of \emph{norm} to
+quantify the uncertainty in measurements and the distance between
+(pure or mixed) states. The norm of a collection of intervals $\mathscr{I}$,
+$\left\Vert \mathscr{I}\right\Vert $, is defined by the maximum length
+of intervals in it. The norm of a pure state $\rho=\proj{\psi}$ is
+defined as usual by $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.
 For any given Hermitian operator~$A$, we choose the operator norm
@@
 events, i.e., $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
-then the norm of their difference is bounded by $\left|\mathscr{I}\right|$,
-i.e., $\left\Vert \rho-\rho'\right\Vert \le\left|\mathscr{I}\right|$.\end{thm}
+then the norm of their difference is bounded by $\left\Vert \mathscr{I}\right\Vert $,
+i.e., $\left\Vert \rho-\rho'\right\Vert \le\left\Vert \mathscr{I}\right\Vert $.\end{thm}
 
@@
 for any one-dimensional projector $P=\proj{\psi}$. Since the maximum
-length of the intervals in $\mathscr{I}$ is $\left|\mathscr{I}\right|$,
+length of the intervals in $\mathscr{I}$ is $\left\Vert \mathscr{I}\right\Vert $,
 it is also the upper bound of the difference: 
 \begin{equation}
-\left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le\left|\mathscr{I}\right|\,.
+\left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le\left\Vert \mathscr{I}\right\Vert \,.
 \end{equation}
@@
 and equal to $\left\Vert \rho-\rho'\right\Vert $~\cite{GolubVanLoan1996,Foucart2012}.
-Hence, $\left\Vert \rho-\rho'\right\Vert \le\left|\mathscr{I}\right|$.\end{proof}
+Hence, $\left\Vert \rho-\rho'\right\Vert \le\left\Vert \mathscr{I}\right\Vert $.\end{proof}
 
@@
 Recall in previous section, we denote the maximum length of intervals
-in $\mathscr{I}$ as $\left|\mathscr{I}\right|$. The finite-precision
+in $\mathscr{I}$ as $\left\Vert \mathscr{I}\right\Vert $. The finite-precision
 extension of the Gleason theorem, Thm.~\ref{thm:Finite-precision-Gleason},
 only applies on the QIVPMs of the form $f\circ\muB_{\rho}$ and states
-that as $\left|\mathscr{I}\right|$ shrinks to $0$, the composition
-$f\circ\muB_{\rho}$ would be better in the sense that the states
-consistent with the composition $f\circ\muB_{\rho}$ converges to
-$\rho$. In contrast, the wildest QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
-has the range~$\mathscr{I}_{0}$ with $\left|\mathscr{I}_{0}\right|=1$,
+that as $\left\Vert \mathscr{I}\right\Vert $ shrinks to $0$, the
+composition $f\circ\muB_{\rho}$ would be better in the sense that
+the states consistent with the composition $f\circ\muB_{\rho}$ converges
+to $\rho$. In contrast, the wildest QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
+has the range~$\mathscr{I}_{0}$ with $\left\Vert \mathscr{I}_{0}\right\Vert =1$,
 the longest possible length. This suggests that shrinking the length
-$\left|\mathscr{I}\right|$ might regularize QIVPMs mapping to $\mathscr{I}$
-as the following question.
+$\left\Vert \mathscr{I}\right\Vert $ might regularize QIVPMs mapping
+to $\mathscr{I}$ as the following question.
 
@@
 such that for all QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
-satisfying $\left|\mathscr{I}\right|<\varepsilon$, $\bar{\mu}$ must
-have an non-empty core, i.e., $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
+satisfying $\left\Vert \mathscr{I}\right\Vert <\varepsilon$, $\bar{\mu}$
+must have an non-empty core, i.e., $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
 
@@
 \end{equation}
-Since $\left|\mathscr{I}\right|<\varepsilon$, the length of every
-interval $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]$
+Since $\left\Vert \mathscr{I}\right\Vert <\varepsilon$, the length
+of every interval $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]$
 is bounded by $\varepsilon$ as well, which implies the largest term

### 2019-01-14 dissertation.tex
dissertation.lyx "Chapter 6 Further Discussion" Updating...

@@
 \end{comment}
-Recall in previous section, we denote the maximum length of intervals
-in $\mathscr{I}$ as $\left\Vert \mathscr{I}\right\Vert $. The finite-precision
-extension of the Gleason theorem, Thm.~\ref{thm:Finite-precision-Gleason},
-only applies on the QIVPMs of the form $f\circ\muB_{\rho}$ and states
-that as $\left\Vert \mathscr{I}\right\Vert $ shrinks to $0$, the
-composition $f\circ\muB_{\rho}$ would be better in the sense that
-the states consistent with the composition $f\circ\muB_{\rho}$ converges
-to $\rho$. In contrast, the wildest QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
-has the range~$\mathscr{I}_{0}$ with $\left\Vert \mathscr{I}_{0}\right\Vert =1$,
-the longest possible length. This suggests that shrinking the length
-$\left\Vert \mathscr{I}\right\Vert $ might regularize QIVPMs mapping
-to $\mathscr{I}$ as the following question.
+As we discussed in the previous section, Thm.~\ref{thm:Finite-precision-Gleason}
+only applies to the QIVPMs constructed by composing an interval map~$f$
+with a conventional quantum probability measure~$\muB_{\rho}$, and
+the states consistent with the composition $f\circ\muB_{\rho}$ collapses
+to a single state as the maximum length of intervals in $\mathscr{I}$,
+$\left\Vert \mathscr{I}\right\Vert $, shrinks to $0$. In contrast,
+the globally inconsistent QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
+has the minimal sharp range~$\mathscr{I}_{0}$ with $\left\Vert \mathscr{I}_{0}\right\Vert =1$.
+This suggests that even for general QIVPMs, shrinking the length $\left\Vert \mathscr{I}\right\Vert $
+might help to regularize them. In another word, if $\left\Vert \mathscr{I}\right\Vert $
+is shorter than a number, all QIVPMs map to $\mathscr{I}$ might have
+an non-empty core.
 
@@
 such that for all QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
-satisfying $\left\Vert \mathscr{I}\right\Vert <\varepsilon$, $\bar{\mu}$
+satisfying $\left\Vert \mathscr{I}\right\Vert \le\varepsilon$, $\bar{\mu}$
 must have an non-empty core, i.e., $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
@@
 space $\CP{2}$ as discussed in Sec.~\ref{subsec:Explicit-generalization-of}.
-To further simplify the question, for any state $\ket{\psi}\in\CP{2}$,
-we can decompose the interval-valued probabilities on its projectors
-$\proj{\psi}$ into the left-end and right-end on $\ket{\psi}$, i.e.,
-$\bar{\mu}\left(\proj{\psi}\right)=\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]$.
-According to Lemma~\ref{thm:convex-3-1}, $\bar{\mu}:\events\rightarrow\mathscr{I}$
-is a QIVPM if and only if the pair of functions $\frameL:\CP{2}\rightarrow\left[0,1\right]$
-and $\frameR:\CP{2}\rightarrow\left[0,1\right]$ satisfying the following
+Therefore, to study a QIVPM~$\bar{\mu}$, we can just study a pair
+of functions $\frameL:\CP{2}\rightarrow\left[0,1\right]$ and $\frameR:\CP{2}\rightarrow\left[0,1\right]$
+defined by $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]=\bar{\mu}\left(\proj{\psi}\right)$
+for $\ket{\psi}\in\CP{2}$. According to Lemma~\ref{thm:convex-3-1},
+$\bar{\mu}:\events\rightarrow\mathscr{I}$ is a QIVPM if and only
+if Eqs.~(\ref{eq:QIVPM-constraints}) and
+\begin{equation}
+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)+\bar{\mu}\left(\proj{\psi_{2}}\right)\label{eq:interval-valued-inclusion}
+\end{equation}
+holds for any orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
+By applying Eq.~(\ref{eq:QIVPM-complement}) on the left-hand side,
+Eq.~(\ref{eq:interval-valued-inclusion}) is equivalent to the following
 interval-inclusion
-\begin{equation}
-\left[1,1\right]-\left[\frameL\left(\ket{\psi_{0}}\right),\frameR\left(\ket{\psi_{0}}\right)\right]\subseteq\left[\frameL\left(\ket{\psi_{1}}\right),\frameR\left(\ket{\psi_{1}}\right)\right]+\left[\frameL\left(\ket{\psi_{2}}\right),\frameR\left(\ket{\psi_{2}}\right)\right]\label{eq:interval-valued-frame-function}
-\end{equation}
-for any orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
+\begin{eqnarray}
+ &  & \necess-\left[\frameL\left(\ket{\psi_{0}}\right),\frameR\left(\ket{\psi_{0}}\right)\right]\subseteq\left[\frameL\left(\ket{\psi_{1}}\right),\frameR\left(\ket{\psi_{1}}\right)\right]+\left[\frameL\left(\ket{\psi_{2}}\right),\frameR\left(\ket{\psi_{2}}\right)\right]\label{eq:interval-valued-frame-function}\\
+ & \Leftrightarrow & \left[1-\frameR\left(\ket{\psi_{0}}\right),1-\frameL\left(\ket{\psi_{0}}\right)\right]\subseteq\left[\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right),\frameR\left(\ket{\psi_{1}}\right)+\frameR\left(\ket{\psi_{2}}\right)\right]\,.\nonumber
+\end{eqnarray}
 This interval-inclusion can be rephrased as a long inequality
@@
 \end{equation}
-Since $\left\Vert \mathscr{I}\right\Vert <\varepsilon$, the length
+Since $\left\Vert \mathscr{I}\right\Vert \le\varepsilon$, the length
 of every interval $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]$
@@
 is bounded by $\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)+2\varepsilon$.
-In another word, the left-end function satisfies the following inequalities
+In another word, the left-end function~$\frameL$ satisfies the following
+inequalities
 \begin{subequations}
@@
 Eq.~(\ref{eq:left-end-frame-function}), there exists a unique mixed
-state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such that 
+state~$\rho$ such that 
 \begin{equation}
@@
 \end{equation}
-for any state $\ket{\psi}\in\CP{2}$, where $\ket{\Phi_{j}}\in\mathcal{H}$
-are normalized, $q_{j}>0$, and $\sum_{j=1}^{N}q_{j}=1$. Our Question~\ref{question:approximation-Gleason}
+for any state $\ket{\psi}\in\CP{2}$. Our Question~\ref{question:approximation-Gleason}
 then ask what $\frameL$ would look like with a positive $\varepsilon$.
@@
 With different settings, whether there is an approximate version of
-Gleason's theorem in general was asked by Sam Sanders in constructivenews~\cite{Sanders2013},
-and there is no clear answer for his question as far as I understand.
-To have an idea how hard this question could be, recall in Sec.~\ref{sec:fuzzy}
-we state that a quantum probability space is glued by a family of
-classical probability spaces. This is similar to the situation that
-a manifold is glued by many local coordinates. When each small piece
-has \emph{exactly} the same and positive curvature, the Killing-Hopf
-theorem asserts this manifold is a sphere, but little can we say even
-if the curvature has only small deviation from constant. Similar situation
-might happen when approximating Gleason's theorem. Since the sum of
-$\frameL$ on each ``local'' classical probability space, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$,
-is \emph{exactly} the same and equal to $1$, Gleason's theorem can
-assert $\frameL$ can be expressed as Eq.~(\ref{eq:Gleason-for-CP2}).
-However, when each local classical probability space becomes imprecise,
-a general $\frameL$ might be as wild as we can imagine, and we might
-say little about its global property.
+Gleason's theorem was asked by Sam Sanders in constructivenews on
+2013~\cite{Sanders2013}, and there is no clear answer for his question
+as far as I understand. To have an idea how hard this question could
+be, recall in Sec.~\ref{sec:fuzzy} we state that a quantum probability
+space is glued by a family of classical probability spaces. This is
+similar to the situation that a manifold is glued by many local coordinates.
+When each small piece has \emph{exactly} the same and positive curvature,
+the Killing-Hopf theorem asserts this manifold is a sphere, but little
+can we say even if the curvature has only small deviation from constant.
+Similar situation might happen when approximating Gleason's theorem.
+When the sum of $\frameL$ on each ``local'' classical probability
+space, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$, is \emph{exactly}
+the same and equal to $1$, Gleason's theorem can assert $\frameL$
+can be expressed as Eq.~(\ref{eq:Gleason-for-CP2}). However, when
+each local classical probability space becomes imprecise, a general
+$\frameL$ might be as wild as we can imagine, and we might need to
+know a little bit more, like the function is of the form $f\circ\muB_{\rho}$,
+to deduce its global property.
 
 \section{And Beyond\ldots}
+
+After we build the quantum interval-valued probability models, we
+might think how powerful a quantum computer could be based on this
+model. Since the conventional quantum circuit model manipulates the
+probability amplitudes of quantum states, to build a quantum computing
+model above QIVPMs, we might either consider evolving the states in
+the core of a QIVPM, or find a way to evolve QIVPMs directly. Both
+strategies are not straightforward. As we proved in Thm.~\ref{thm:Non-extensible-of-Gleason's},
+a QIVPM might have an empty core which cannot be evolved over time.
+If we want to evolve and compute QIVPMs directly, we need to get the
+QIVPM of the whole system from the QIVPM for each subsystem or qubit.
+However, there is no straightforward way to define the tensor product
+among QIVPMs because we cannot summarize a probability measure into
+a state as we did in conventional quantum theory.
 

### 2019-01-16 dissertation.tex
dissertation.lyx "5.3.1 Finite-Precision Extension of Gleason's Theorem" and "Chapter 6 Further Discussion" Updating...

@@
 (pure or mixed) states. The norm of a collection of intervals $\mathscr{I}$,
-$\left\Vert \mathscr{I}\right\Vert $, is defined by the maximum length
+$\left\Vert \mathscr{I}\right\Vert $, is defined as the maximum length
 of intervals in it. The norm of a pure state $\rho=\proj{\psi}$ is
@@
 As we discussed in the previous section, Thm.~\ref{thm:Finite-precision-Gleason}
-only applies to the QIVPMs constructed by composing an interval map~$f$
-with a conventional quantum probability measure~$\muB_{\rho}$, and
-the states consistent with the composition $f\circ\muB_{\rho}$ collapses
-to a single state as the maximum length of intervals in $\mathscr{I}$,
-$\left\Vert \mathscr{I}\right\Vert $, shrinks to $0$. In contrast,
-the globally inconsistent QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
-has the minimal sharp range~$\mathscr{I}_{0}$ with $\left\Vert \mathscr{I}_{0}\right\Vert =1$.
-This suggests that even for general QIVPMs, shrinking the length $\left\Vert \mathscr{I}\right\Vert $
-might help to regularize them. In another word, if $\left\Vert \mathscr{I}\right\Vert $
+only applies to the QIVPMs constructed by composing an interval map
+with a conventional quantum probability measure, and the states consistent
+with the composite QIVPM collapses to a single state as the maximum
+length of intervals in $\mathscr{I}$, $\left\Vert \mathscr{I}\right\Vert $,
+shrinks to $0$. In contrast, the globally inconsistent QIVPM defined
+in Table~\ref{tab:non-Born-QIVPM} has the least sharp range~$\mathscr{I}_{0}$
+with $\left\Vert \mathscr{I}_{0}\right\Vert =1$. This suggests a
+possibility that shrinking the length $\left\Vert \mathscr{I}\right\Vert $
+might help to regularize general QIVPMs, and when $\left\Vert \mathscr{I}\right\Vert $
 is shorter than a number, all QIVPMs map to $\mathscr{I}$ might have
-an non-empty core.
+non-empty cores.
 
@@
 of a one-dimensional projector, and by Eq.~(\ref{eq:QIVPM-complement})
-so does their interval-valued probabilities, i.e., $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\necess-\bar{\mu}\left(\proj{\psi}\right)$.
+so does their interval-valued probabilities, i.e., 
+\begin{equation}
+\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\necess-\bar{\mu}\left(\proj{\psi}\right)\,.\label{eq:QIVPM-complement-states}
+\end{equation}
 Hence, a QIVPM is completely determined by its values on the one-dimensional
@@
 defined by $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]=\bar{\mu}\left(\proj{\psi}\right)$
-for $\ket{\psi}\in\CP{2}$. According to Lemma~\ref{thm:convex-3-1},
+for any irreducible state $\ket{\psi}\in\CP{2}$. According to Lemma~\ref{thm:convex-3-1},
 $\bar{\mu}:\events\rightarrow\mathscr{I}$ is a QIVPM if and only
-if Eqs.~(\ref{eq:QIVPM-constraints}) and
+if $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}) and
 \begin{equation}
@@
 \end{equation}
-holds for any orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
-By applying Eq.~(\ref{eq:QIVPM-complement}) on the left-hand side,
+for all orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
+By applying $\proj{\psi_{1}}+\proj{\psi_{2}}=\mathbb{1}-\proj{\psi_{0}}$
+and Eq.~(\ref{eq:QIVPM-complement-states}) on the left-hand side,
 Eq.~(\ref{eq:interval-valued-inclusion}) is equivalent to the following
@@
 space, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$, is \emph{exactly}
-the same and equal to $1$, Gleason's theorem can assert $\frameL$
+the same and equal to $1$, Gleason's theorem assert that $\frameL$
 can be expressed as Eq.~(\ref{eq:Gleason-for-CP2}). However, when
@@
 $\frameL$ might be as wild as we can imagine, and we might need to
-know a little bit more, like the function is of the form $f\circ\muB_{\rho}$,
-to deduce its global property.
+know a little bit more, like its QIVPM is a composite function, to
+deduce its global property.
 
@@
 probability amplitudes of quantum states, to build a quantum computing
-model above QIVPMs, we might either consider evolving the states in
-the core of a QIVPM, or find a way to evolve QIVPMs directly. Both
-strategies are not straightforward. As we proved in Thm.~\ref{thm:Non-extensible-of-Gleason's},
-a QIVPM might have an empty core which cannot be evolved over time.
-If we want to evolve and compute QIVPMs directly, we need to get the
-QIVPM of the whole system from the QIVPM for each subsystem or qubit.
-However, there is no straightforward way to define the tensor product
-among QIVPMs because we cannot summarize a probability measure into
-a state as we did in conventional quantum theory.
+model above QIVPMs, we might consider either manipulating the states
+in the core of a QIVPM, or finding a way to manipulate QIVPMs directly.
+However, both strategies are not straightforward. As we proved in
+Thm.~\ref{thm:Non-extensible-of-Gleason's}, a QIVPM might have an
+empty core which cannot be evolved over time. If we want to manipulate
+and compute QIVPMs directly for multi-qubit algorithms, we need to
+glue the QIVPM for each qubit or subsystem together to get the QIVPM
+of the whole system, and this is not straightforward either.
+
+A successful interval-valued theory might be further extended to the
+quantum theory over finite fields, and consider the following quantum
+interval-valued probability measures over finite fields.
+
+\begin{definition}[Quantum Interval-valued Probability Measures
+over Finite Fields]\label{def:QIVPMFF}Given a vector space~$\mathcal{H}$
+of dimension~$D$ over the complexified field~$\Fpp$, the set of
+events~$\events_{p^{2}}$ is defined as in Def.~\ref{def:QPMFF},
+and $\mathscr{I}$ is a collection of intervals. Then, a quantum interval-valued
+probability measure over finite field $\bar{\mu}:\events_{p^{2}}\rightarrow\mathscr{I}$
+assigns a probability to each event (projection operator~$P$) subject
+to $\bar{\mu}(\mathbb{0})=\imposs$, $\bar{\mu}(\mathbb{1})=\necess$,
+$\bar{\mu}\left(\mathbb{1}-P\right)=\necess-\bar{\mu}\left(P\right)$,
+and satisfying for each pair of \emph{commuting} projectors~$P_{0}$
+and~$P_{1}$ with $P_{0}P_{1}=P_{1}P_{0}$, 
+\begin{equation}
+\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.\label{eq:QuantumInterval-valuedProbability-Inclusion-Finite-Field}
+\end{equation}
+\end{definition}
+
+\noindent Understanding the properties of these probability measures
+and whether we could define any ``sensible'' Born upon them will
+be the next natural extension for seeking a computable quantum theory.
 

### 2019-01-18 dissertation.tex
dissertation.lyx Acknowledgments and "Chapter 6 Further Discussion" Updating...

@@
 my application for Rethinking Foundations of Physics 2017 workshop
-reviewed by Prof. Amr Sabry (\textarabic{عمرو صبري}). I want
+reviewed by Prof. Amr Sabry(\textarabic{عمرو صبري}). I want
 to thank Prof. Lawrence Moss for inviting me to present our results
@@
 directors of graduate study in Mathematics, especially Prof. Christopher
-Judge and Prof. Matthias Weber; directors of Ph.D. study in Computer
+Judge and Prof. Matthias Weber; directors of PhD. study in Computer
 Science, especially Prof. Yuqing Melanie Wu (吴愈青) and Prof. \textturkish{Funda
@@
 
-Thank Meng-Wei Chen (陳孟瑋) as my best friend and roommate in Bloomington.
-Thank Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
-what I did in the prospective of a general Ph.D. in Physics, and working
+Thank all my friends for your supports, including:
+
+\begin{itemize}
+
+\item Meng-Wei Chen (陳孟瑋) as my roommate, AT\&T family plan member,
+and emergency contact for all kinds of emergency and non-emergency
+situations.
+
+\item My other AT\&T family plan members, especially Kexin ``Casey''
+Chen (谌可心), Yao-yu Chih (池耀宇), Xinyi ``Diana'' Gong (龚欣怡), and Nanxi
+``Nancy'' Zhang (张楠茜), for you always pay our telephone bill on
+time so that......................\todo{Maybe I don't have to thank
+them as AT\&T family plan members, but I should thank some of them
+for support and sharing information...}
+
+\item My other roommates,
+
+\item Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
+what I did in the prospective of a general PhD. in Physics, and working
 later in more computational industry.
+
+\end{itemize}
 
@@
 possibility that shrinking the length $\left\Vert \mathscr{I}\right\Vert $
-might help to regularize general QIVPMs, and when $\left\Vert \mathscr{I}\right\Vert $
-is shorter than a number, all QIVPMs map to $\mathscr{I}$ might have
-non-empty cores.
+might help to regularize general QIVPMs, and it is natural to ask
+whether there is a short enough length~$\varepsilon$ such that QIVPMs
+mapping to intervals shorter than $\varepsilon$ always have non-empty
+cores.
 
@@
 satisfying $\left\Vert \mathscr{I}\right\Vert \le\varepsilon$, $\bar{\mu}$
-must have an non-empty core, i.e., $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}
+must have an non-empty core, i.e., $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$
+?\end{question}
 
@@
 and these irreducible states are encoded in the complex projective
-space $\CP{2}$ as discussed in Sec.~\ref{subsec:Explicit-generalization-of}.
+space $\CP{2}$ as we discussed in Sec.~\ref{subsec:Explicit-generalization-of}.
 Therefore, to study a QIVPM~$\bar{\mu}$, we can just study a pair
@@
 \begin{equation}
-\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)+\bar{\mu}\left(\proj{\psi_{2}}\right)\label{eq:interval-valued-inclusion}
-\end{equation}
-for all orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
-By applying $\proj{\psi_{1}}+\proj{\psi_{2}}=\mathbb{1}-\proj{\psi_{0}}$
-and Eq.~(\ref{eq:QIVPM-complement-states}) on the left-hand side,
-Eq.~(\ref{eq:interval-valued-inclusion}) is equivalent to the following
-interval-inclusion
+\bar{\mu}\left(\mathbb{1}-\proj{\psi_{0}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)+\bar{\mu}\left(\proj{\psi_{2}}\right)\label{eq:interval-valued-inclusion}
+\end{equation}
+for all orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$
+because $\proj{\psi_{1}}+\proj{\psi_{2}}=\mathbb{1}-\proj{\psi_{0}}$.
+By applying Eq.~(\ref{eq:QIVPM-complement-states}) on the left-hand
+side, Eq.~(\ref{eq:interval-valued-inclusion}) is equivalent to
+the following interval-inclusion
 \begin{eqnarray}
@@
 can we say even if the curvature has only small deviation from constant.
-Similar situation might happen when approximating Gleason's theorem.
-When the sum of $\frameL$ on each ``local'' classical probability
-space, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$, is \emph{exactly}
-the same and equal to $1$, Gleason's theorem assert that $\frameL$
-can be expressed as Eq.~(\ref{eq:Gleason-for-CP2}). However, when
-each local classical probability space becomes imprecise, a general
-$\frameL$ might be as wild as we can imagine, and we might need to
-know a little bit more, like its QIVPM is a composite function, to
-deduce its global property.
+Similar situation might happen when approximating Gleason's theorem,
+but this time the whole space is glued by ``local'' classical probability
+space defined by each orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
+When the sum of $\frameL$, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$,
+is \emph{exactly} the same and equal to $1$, Gleason's theorem assert
+that $\frameL$ can be expressed as Eq.~(\ref{eq:Gleason-for-CP2}).
+However, when each local classical probability space becomes imprecise,
+a general $\frameL$ might be as wild as we can imagine, and we might
+need to know a little bit more, like its QIVPM is a composite function,
+to deduce its global property.
 
@@
 
-After we build the quantum interval-valued probability models, we
-might think how powerful a quantum computer could be based on this
+After we build the quantum interval-valued probability model, we might
+want to know how powerful a quantum computer could be based on this
 model. Since the conventional quantum circuit model manipulates the
-probability amplitudes of quantum states, to build a quantum computing
-model above QIVPMs, we might consider either manipulating the states
-in the core of a QIVPM, or finding a way to manipulate QIVPMs directly.
-However, both strategies are not straightforward. As we proved in
-Thm.~\ref{thm:Non-extensible-of-Gleason's}, a QIVPM might have an
-empty core which cannot be evolved over time. If we want to manipulate
-and compute QIVPMs directly for multi-qubit algorithms, we need to
-glue the QIVPM for each qubit or subsystem together to get the QIVPM
-of the whole system, and this is not straightforward either.
+probability amplitudes instead of the measured probability, a quantum
+computing model above QIVPMs might either need to manipulate the states
+in the core of a QIVPM, or find a way to manipulate QIVPMs directly.
+However, both strategies are not straightforward. On one hand, a QIVPM
+might have an empty core which cannot be evolved over time as we proved
+in Thm.~\ref{thm:Non-extensible-of-Gleason's}. On the other hand,
+if we want to manipulate and compute QIVPMs directly for multi-qubit
+algorithms, we need to glue the QIVPM for each qubit or subsystem
+together to get the QIVPM of the whole system, and this is not straightforward
+either.
 
 A successful interval-valued theory might be further extended to the
-quantum theory over finite fields, and consider the following quantum
-interval-valued probability measures over finite fields.
+quantum theory over finite fields as follow.
 
 \begin{definition}[Quantum Interval-valued Probability Measures
-over Finite Fields]\label{def:QIVPMFF}Given a vector space~$\mathcal{H}$
-of dimension~$D$ over the complexified field~$\Fpp$, the set of
-events~$\events_{p^{2}}$ is defined as in Def.~\ref{def:QPMFF},
-and $\mathscr{I}$ is a collection of intervals. Then, a quantum interval-valued
+over Finite Fields]\label{def:QIVPMFF}Consider a vector space~$\mathcal{H}$
+of dimension~$D$ over the complexified field~$\Fpp$, its set of
+events~$\events_{p^{2}}$ as defined in Def.~\ref{def:QPMFF}, and
+a collection of intervals~$\mathscr{I}$. A quantum interval-valued
 probability measure over finite field $\bar{\mu}:\events_{p^{2}}\rightarrow\mathscr{I}$
-assigns a probability to each event (projection operator~$P$) subject
-to $\bar{\mu}(\mathbb{0})=\imposs$, $\bar{\mu}(\mathbb{1})=\necess$,
-$\bar{\mu}\left(\mathbb{1}-P\right)=\necess-\bar{\mu}\left(P\right)$,
+assigns an interval to each event~$P$ subject to $\bar{\mu}(\mathbb{0})=\imposs$,
+$\bar{\mu}(\mathbb{1})=\necess$, $\bar{\mu}\left(\mathbb{1}-P\right)=\necess-\bar{\mu}\left(P\right)$,
 and satisfying for each pair of \emph{commuting} projectors~$P_{0}$
@@
 \noindent Understanding the properties of these probability measures
-and whether we could define any ``sensible'' Born upon them will
-be the next natural extension for seeking a computable quantum theory.
+and whether we could define a ``sensible'' Born upon them combine
+two approaches for dealing with the continuous quantities used in
+the conventional quantum theory, and will be the next natural extension
+for our discrete quantum theories and computing.
 

### 2019-01-19 dissertation.tex
dissertation.lyx Update according to the suggestion from Spellchecker and Check TeX...

@@
-%% LyX 2.3.2-1 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.3.2-2 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
@@
 \begin{acknowledgments*}\todo{Confirm people to be acknowledged
-like the way being acknowledged... }I want to thank Prof.~Gerardo
+like the way being acknowledged\ldots{} }I want to thank Prof.~Gerardo
 Ortiz, Prof.~Amr Sabry (\textarabic{عمرو صبري}), and Prof.~Andrew
@@
 Chapter~\ref{chap:QIVPM} is based on ``Quantum Interval-Valued
-Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2018}.
+Probability: Contextuality and the Born Rule'' (QIVPM)~\cite{THOS2018}.
 Together with Prof.~Dylan Thurston and Prof.~Shouhong Wang (汪守宏),
 I want to thank you for getting together to understand what I did
-and passing my dissertation proposal Spring 2017. I also thank Prof.
-Dylan Thurston for serving in my advisory committee and my Tier 3
-committee, with other advisory committee members passing my Computer
-Science qualifying exam Spring 2016. Especially, my survey of real
-computation in the qualifying exam inspired me the comparison of quantum
-computer and analog computer in Chapter~\ref{chap:Introduction}.
-Chapter~\ref{chap:Introduction} also contains the motivation in
-my application for Rethinking Foundations of Physics 2017 workshop
-reviewed by Prof. Amr Sabry(\textarabic{عمرو صبري}). I want
-to thank Prof. Lawrence Moss for inviting me to present our results
-in the interdisciplinary logic seminar and theory seminar in Computer
-Science, co-chairing my Tier 3 committee, writing an assessment letter
-for me, and drawing my attention on Prof.~Abramsky's paper~\cite{Abramsky2012},
+and passing my dissertation proposal Spring 2017. I also thank Prof.\ Dylan
+Thurston for serving in my advisory committee and my Tier 3 committee,
+with other advisory committee members passing my Computer Science
+qualifying exam Spring 2016. Especially, my survey of real computation
+in the qualifying exam inspired me the comparison of quantum computer
+and analog computer in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
+also contains the motivation in my application for Rethinking Foundations
+of Physics 2017 workshop reviewed by Prof.\ Amr Sabry~(\textarabic{عمرو صبري}).
+I want to thank Prof.\ Lawrence Moss for inviting me to present our
+results in the interdisciplinary logic seminar and theory seminar
+in Computer Science, co-chairing my Tier 3 committee, writing an assessment
+letter for me, and drawing my attention on Prof.~Abramsky's paper~\cite{Abramsky2012},
 which inspired me to merge quantum probability with discrete quantum
@@
 my double-major works smoothly. I need to thank all of them, especially
-directors of graduate study in Mathematics, especially Prof. Christopher
-Judge and Prof. Matthias Weber; directors of PhD. study in Computer
-Science, especially Prof. Yuqing Melanie Wu (吴愈青) and Prof. \textturkish{Funda
+directors of graduate study in Mathematics, especially Prof.\ Christopher
+Judge and Prof.\ Matthias Weber; directors of PhD. study in Computer
+Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
 Ergun}.
@@
 Thank Kin Wai Chan for suggesting me the correct direction for Proposition~\ref{appH.sec},
-Prof. 朱樺 for drawing my attention on Prof. Wan's book~\cite{Wan2006},
+Prof.\ 朱樺 for drawing my attention on Prof.\ Wan's book~\cite{Wan2006},
 and Weihua Liu (刘伟华) for remaining me analysts call the right side
@@
 ``Nancy'' Zhang (张楠茜), for you always pay our telephone bill on
-time so that......................\todo{Maybe I don't have to thank
-them as AT\&T family plan members, but I should thank some of them
-for support and sharing information...}
+time so that\ldots\ldots\todo{Maybe I don't have to thank them
+as AT\&T family plan members, but I should thank some of them for
+support and sharing information\ldots}
 
@@
 \item The latest PDF version of this thesis is in GitHub: \code{https://git.io/fxbuG}.
-\item Its source code is typeset using \LyX ~\cite{LyX} in \code{https://git.io/fxbuE}
+\item Its source code is typeset using \LyX{} \cite{LyX} in \code{https://git.io/fxbuE}
 and the exported \LaTeX{} file is in \code{https://git.io/fhZBW}.
@@
 \end{enumerate}
-The previous steps only tested in Microsoft Windows with MiK\TeX ~2.9.
-Please report me if there is any difficulty to compile it. Besides,
+The previous steps only tested in Microsoft Windows with MiK\TeX{}
+2.9. Please report me if there is any difficulty to compile it. Besides,
 to compile a PDF file from the \LyX{} source, just finish step~\ref{enu:Clone-the-git},
@@
 it will provide another reason why we want to study the precision
-of the inducing probabilities... }This idea will be extended to quantum
-domain as quantum interval-valued probability measures (QIVPM).
+of the inducing probabilities\ldots{} }This idea will be extended
+to quantum domain as quantum interval-valued probability measures
+(QIVPM).
 
@@
 in Section~\ref{modalquantumcomputing} that this approach leads
-to theories with such bizarre powers that they are probably unphysical.
+to theories with such bizarre powers that they are probably nonphysical.
 Although a version of quantum theory defined over a two-valued field
@@
 \end{comment}
-In Sec.~\ref{discretequantumtheoryI} to \ref{discretequantumcomputingI},
+In Sec.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI},
 we improve on this by showing that for finite fields of order $p^{2}$,
@@
 \addlinespace
- & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
+ & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to~\ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
 \addlinespace
@@
 In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the geometric issues
-raised by the properties \ref{enu:-orthonormal-basis} and \ref{enu:probability-amplitude}
-given above for CQT. In Sec.~\ref{sec:fuzzy}, we introduce the important
-issues of \ref{enu:measurement-framework} and the foundations of
-quantum probability space. The expectation values defined in Sec.~\ref{sec:fuzzy}
+raised by the properties~\ref{enu:-orthonormal-basis} and~\ref{enu:probability-amplitude}
+given above for CQT\@. In Sec.~\ref{sec:fuzzy}, we introduce the
+important issues of~\ref{enu:measurement-framework} and the foundations
+of quantum probability space. The expectation values defined in Sec.~\ref{sec:fuzzy}
 will be used to understand the geometry of entangled states in Sec.~\ref{sec:The-geometry-of}.
@@
 \par\end{centering}
-}\hfill{} \caption{(a) The two-sphere~$\Sphere{2}$ represented by \Eq{A7.eq}, which
+}\hfill{} \label{hopfFibers.fig}\caption{(a) The two-sphere~$\Sphere{2}$ represented by \Eq{A7.eq}, which
 is the irreducible space of one-qubit states, along with a representative
@@
 large perfectly round red circle at the equator.}
-\label{hopfFibers.fig} 
 \end{figure}
@@
 and an irreducible state can be represented as a point on a sphere
-called the Bloch sphere, as shown in Fig.~\ref{blochSphere.fig}(a).
+called the Bloch sphere, as shown in Fig.~\ref{blochSphere.fig}~(a).
 
@@
 \par\end{centering}
-\caption{(a) The conventional Bloch sphere with a unique state represented
+\label{blochSphere.fig}\caption{(a) The conventional Bloch sphere with a unique state represented
 by the point at the red sphere. (b) The geodesic shortest-distance
 arc connecting two one-qubit quantum states.}
-\label{blochSphere.fig} 
 \end{figure}
@@
 \end{equation}
-where $\Hat{a}\cdot\Hat{b}=\cos\omega$. Figure \ref{blochSphere.fig}(b)
+where $\Hat{a}\cdot\Hat{b}=\cos\omega$. Figure~\ref{blochSphere.fig}~(b)
 illustrates the path traced by a SLERP between two irreducible one-qubit
@@
 precision real numbers, it is not possible, even in principle, to
-make an exact state transition as implied by Fig.~\ref{blochSphere.fig}(b).
+make an exact state transition as implied by Fig.~\ref{blochSphere.fig}~(b).
 In practice, one has to be content with approximate, typically exponentially
@@
 convention to introduce the Born rule which is the only way corresponding
-a state to a quantum probability measure in CQT. However, since the
-variants of quantum probability measures in Sec.~\ref{sec:Toward-IVPM}
+a state to a quantum probability measure in CQT\@. However, since
+the variants of quantum probability measures in Sec.~\ref{sec:Toward-IVPM}
 and Chapter~\ref{chap:QIVPM} could not be constructed by the Born
@@
 \begin{equation}
-\rho_{j}=\Tr_{\left\{ 1,\cdots,j-1,j+1,\cdots,n\right\} }\left(\rho\right)\,,\label{eq:partialTrace}
-\end{equation}
-with $j=1,\cdots,n$ and $\rho=\op{\Psi}{\Psi}$, the normalized state~$\ket{\Psi}$
+\rho_{j}=\Tr_{\left\{ 1,\ldots,j-1,j+1,\ldots,n\right\} }\left(\rho\right)\,,\label{eq:partialTrace}
+\end{equation}
+with $j=1,\ldots,n$ and $\rho=\op{\Psi}{\Psi}$, the normalized state~$\ket{\Psi}$
 is entangled if and only if at least one subsystem state is \textit{mixed},
@@
 phases corresponding to the Hopf fibration circle. \todo{Explain
-the Hopf fibration circle here... ? }Since $\Fpp$ has $p^{2}-1$
+the Hopf fibration circle here\ldots ? }Since $\Fpp$ has $p^{2}-1$
 non-zero values, and the map $\fnorm{\alpha}$ distributes these equally
@@
 \begin{figure}
-\noindent \centering{}\includegraphics[width=3.6in]{Fpp2Fp}\caption{Sketch of the map from $\Fpp$ to $\Fp$ using $\fnorm{\alpha}$,
+\noindent \centering{}\includegraphics[width=3.6in]{Fpp2Fp}\label{proof1.fig}\caption{Sketch of the map from $\Fpp$ to $\Fp$ using $\fnorm{\alpha}$,
 showing the decomposition of $\Fpp$ into the zero element $\left(0,0\right)$
@@
 $p+1$.}
-\label{proof1.fig}
 \end{figure}
@@
 We are interested in the vector space $\mathcal{H}$ of dimension
-$D$ defined over the complexified field $\Fpp$. Let $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$
-and $\ket{\Phi}=\begin{pmatrix}\beta_{0} & \beta_{1} & \ldots & \beta_{D-1}\end{pmatrix}^{T}$
+$D$ defined over the complexified field $\Fpp$. Let $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \cdots & \alpha_{D-1}\end{pmatrix}^{T}$
+and $\ket{\Phi}=\begin{pmatrix}\beta_{0} & \beta_{1} & \cdots & \beta_{D-1}\end{pmatrix}^{T}$
 represent vectors in $\mathcal{H}$, with numbers $\alpha_{i}$ and
@@
 Two vectors $\ket{\Phi}$ and $\ket{\Psi}\in\mathcal{H}$ are said
-to be orthogonal if $\ip{\Phi}{\Psi}=0$. This product satisfies conditions
-\ref{enu:inner-product-complex-conjugate} and \ref{enu:inner-product-linear}
-for inner products but violates condition \ref{enu:inner-product-positive-definite}
-since in every finite field there always exists a non-zero vector
-$\ket{\Psi}$ such that $\ip{\Psi}{\Psi}=0$. The reason is that addition
-in finite fields eventually ``wraps around'' (because of their cyclic
-or modular structure), allowing the sum of non-zero elements to be
-zero. The fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$
-decreases with the order $p$.
-
-For any vector $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$,
+to be orthogonal if $\ip{\Phi}{\Psi}=0$. This product satisfies conditions~\ref{enu:inner-product-complex-conjugate}
+and~\ref{enu:inner-product-linear} for inner products but violates
+condition~\ref{enu:inner-product-positive-definite} since in every
+finite field there always exists a non-zero vector $\ket{\Psi}$ such
+that $\ip{\Psi}{\Psi}=0$. The reason is that addition in finite fields
+eventually ``wraps around'' (because of their cyclic or modular
+structure), allowing the sum of non-zero elements to be zero. The
+fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$ decreases
+with the order $p$.
+
+For any vector $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \cdots & \alpha_{D-1}\end{pmatrix}^{T}$,
 the Hermitian dot product $\ip{\Psi}{\Psi}$ is equal to $\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}$,
@@
 \par\end{centering}
-\caption{Schematically normalized plots of the elements of the discrete Bloch
+\label{bloch.fig}\caption{Schematically normalized plots of the elements of the discrete Bloch
 sphere, the irreducible single-qubit (two-dimensional) state vectors
@@
 discrete phase.}
-\label{bloch.fig} 
 \end{figure}
@@
 From Proposition~\ref{appH.sec}, we know that $p+1$ elements of
-this discrete $\Sphere{2D-1}$ structure map to the \textit{same point\/}
+this discrete $\Sphere{2D-1}$ structure map to the \textit{same point}
 in $\Hat{a}$. \todo{Does Proposition~\ref{appH.sec} really show
 this? }Each set of $p+1$ redundant points is, geometrically speaking,
-the \textit{discrete Hopf fibration circle\/} living above each \textit{irreducible\/}
+the \textit{discrete Hopf fibration circle} living above each \textit{irreducible}
 point of the $D$-dimensional state description. These $p+1$ points
 are interpretable as the $p$ finite points plus the single point
-at infinity of the projective discrete line (see, e.g., \cite{arnold_2010}).
+at infinity of the projective discrete line (see, e.g.,~\cite{arnold_2010}).
 
@@
 $p+1$ values in that set to each of the $p-1$ non-zero values in
-$\Fp$. Therefore, the \textit{unit-norm case\/} has a count of domain
+$\Fp$. Therefore, the \textit{unit-norm case} has a count of domain
 elements that is $\frac{1}{p-1}$ of the total number of non-zero-norm
@@
 of $\CP{D-1}$, which we might call a \textit{discrete complex projective
-space\/} or $\DCP{D-1}$.
+space} or $\DCP{D-1}$.
 
@@
 full space compared to both the unit-norm space and the irreducible
-space for a selection of complexified finite fields are shown in Figure
-\ref{statePlot3Unit.fig} for 1, 2, 3, and 4 qubits.
+space for a selection of complexified finite fields are shown in Figure~\ref{statePlot3Unit.fig}
+for 1, 2, 3, and 4 qubits.
 \begin{figure}[htb]
@@
 \par\end{centering}
-\caption{Logarithmic plot of the number of discrete unnormalized states (top,
+\label{statePlot3Unit.fig}\caption{Logarithmic plot of the number of discrete unnormalized states (top,
 in red), vs the number of normalized discrete states (middle, in blue),
@@
 qubits $1$, $2$, $3$, and $4$. }
-\label{statePlot3Unit.fig} 
 \end{figure}
@@
 database search problem for certain database sizes. \todo{Prof.~Gil~Kalai
-thought it would be interested if we can do Simon's algorithm in DQC(I),
+thought it would be interested if we can do Simon's algorithm in DQC~(I),
 but I don't know when I could organize my unreadable draft to a readable
-one... Moreover, Prof.~Ortiz wants to check Shor's algorithm in DQC(I).}
+one\ldots{} Moreover, Prof.~Ortiz wants to check Shor's algorithm
+in DQC~(I).}
 
@@
 but the definition of \textbackslash uf has a negative space between
-$U$ and $f$ which is different from U\_\{f\}... I need to understand
+$U$ and $f$ which is different from U\_\{f\}\ldots{} I need to understand
 whether the negative space is necessary or not, or whether the negative
-space has any semantic meaning... }
+space has any semantic meaning\ldots{} }
 \begin{figure}[t]
@@
 $N$, matching the conditions becomes less likely as the size of the
-field increases. Nevertheless, for a \textit{given\/} field, it is
-always possible to expand any database with dummy records to satisfy
-the divisibility property. Physically, we are taking advantage of
-additional interference processes that happen because of the possibility
-of ``wrapping around'' due to modular arithmetic. We do not know,
-in general, whether this version of discrete quantum computing actually
-enables the rapid solution of $\NP$-complete problems.
+field increases. Nevertheless, for a \textit{given} field, it is always
+possible to expand any database with dummy records to satisfy the
+divisibility property. Physically, we are taking advantage of additional
+interference processes that happen because of the possibility of ``wrapping
+around'' due to modular arithmetic. We do not know, in general, whether
+this version of discrete quantum computing actually enables the rapid
+solution of $\NP$-complete problems.
 
@@
 range later, whether they are the quadratic residues or not doesn't
-really matter...}
+really matter\ldots}
 
@@
 is transitively ordered. We can construct examples using the sequence
-A000229 in the encyclopedia of integer sequences \cite{Sloane2005}\footnote{For computational purposes, this sequence is preferable to the one
+A000229 in the encyclopedia of integer sequences~\cite{Sloane2005}\footnote{For computational purposes, this sequence is preferable to the one
 proposed by Reisler and Smith~\cite{ReislerSmith1969} because it
@@
 of the sequence of quadratic residues be $k$. The region of interest
-includes all vectors $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$,
+includes all vectors $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \cdots & \alpha_{D-1}\end{pmatrix}^{T}$,
 for which $D<p-\frac{k-1}{2}$ and each $\alpha_{i}$ satisfies 
@@
 is basically a rigorous formulation of Schwinger's intuition (See,
-in particular, Chapter 1, Section 1.16. in \cite{schwinger2001quantum}).
+in particular, Chapter~1, Section~1.16. in \cite{schwinger2001quantum}).
 
@@
 quantum circuits in Figures~\ref{fig:alg}, \ref{fig:Quantum-Circuit-Deutsch},
-and \ref{fig:dbsearch} always measure in the computational basis
+and~\ref{fig:dbsearch} always measure in the computational basis
 $\left\{ \ket{0},\ldots,\ket{i},\ldots,\ket{D-1}\right\} $. Indeed,
@@
 \end{equation}
-where $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \ldots & \alpha_{D-1}\end{pmatrix}^{T}$
+where $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \cdots & \alpha_{D-1}\end{pmatrix}^{T}$
 is an unnormalized state. Hereafter, we will simplify by calling $\muB_{\Psi}\left(i\right)$
@@
 are $F^{2}\left(11\right)=\left\{ 0,\pm1,\pm\rmi,\left(\pm1\pm\rmi\right)\right\} $
-(see Table \ref{table_allowed}). Now the cardinal probabilities of
-several representative one-qubit states are listed in Table~\ref{f11-proj.fig}.
+(see Table~\ref{table_allowed}). Now the cardinal probabilities
+of several representative one-qubit states are listed in Table~\ref{f11-proj.fig}.
 \begin{table}
@@
 
-\section{Discrete Quantum Computing (II)}
-
-\label{discretequantumcomputingII}
+\section{Discrete Quantum Computing (II)\label{discretequantumcomputingII}}
 
@@
 than $k$, and we also know that the least quadratic non-residue is
-a prime \cite{numtheory.ref}. Thus, there is a quadratic non-residue
+a prime~\cite{numtheory.ref}. Thus, there is a quadratic non-residue
 in $0$, $1$, $2$, $3$, \ldots , $2^{3n+2}$, and therefore, for
@@
 $\pi\left(37\right)=12$ and $p=422231$, as shown in the extended
-elements Table \ref{table_long}. 
+elements Table~\ref{table_long}. 
 \begin{table}
@@
 \begin{equation}
-R=\begin{pmatrix}-1 & 0 & 0 & \ldots & 0\\
-0 & 1 & 0 & \ldots & 0\\
-0 & 0 & 1 & \ldots & 0\\
+R=\begin{pmatrix}-1 & 0 & 0 & \cdots & 0\\
+0 & 1 & 0 & \cdots & 0\\
+0 & 0 & 1 & \cdots & 0\\
 \vdots & \vdots & \vdots & \ddots & \vdots\\
-0 & 0 & 0 & \ldots & 1
+0 & 0 & 0 & \cdots & 1
 \end{pmatrix}\,,
@@
 \begin{equation}
-\Delta=\begin{pmatrix}1-\frac{N}{2} & 1 & 1 & \ldots & 1\\
-1 & 1-\frac{N}{2} & 1 & \ldots & 1\\
-1 & 1 & 1-\frac{N}{2} & \ldots & 1\\
+\Delta=\begin{pmatrix}1-\frac{N}{2} & 1 & 1 & \cdots & 1\\
+1 & 1-\frac{N}{2} & 1 & \cdots & 1\\
+1 & 1 & 1-\frac{N}{2} & \cdots & 1\\
 \vdots & \vdots & \vdots & \ddots & \vdots\\
-1 & 1 & 1 & \ldots & 1-\frac{N}{2}
+1 & 1 & 1 & \cdots & 1-\frac{N}{2}
 \end{pmatrix}\,,
@@
 if and only if $\ket{\overline{x}}=\ket{0}\!\ket{0}$, and so the
-final state is $\begin{pmatrix}4 & 0 & \ldots & 0\end{pmatrix}^{T}$
+final state is $\begin{pmatrix}4 & 0 & \cdots & 0\end{pmatrix}^{T}$
 with the field norm of $16$. Then, the cardinal probability of obtaining
@@
 their computation in a small region. \todo{Remove the discussion
-of Shor's algorithm if I cannot verify it on DQT(I) on time. }Moreover,
+of Shor's algorithm if I cannot verify it on DQT~(I) on time. }Moreover,
 since we haven't found a way to manipulate the resulting cardinal
@@
 \end{equation}
-which is much more then one, the number of QPMFF. Since we don't have
-enough QPMFF to correspond even pure states, there is no discrete
+which is much more then one, the number of QPMFF\@. Since we don't
+have enough QPMFF to correspond even pure states, there is no discrete
 Born rule in this case. In general, we conjecture that QPMFF is always
@@
 which also satisfies an analog of Proposition~\ref{prop:Born-probability-one}
-and \ref{prop:Born-unitary-invariant}. \todo{Notice that the notation
+and~\ref{prop:Born-unitary-invariant}. \todo{Notice that the notation
 here and previous is a little bit different because we dealt with
@@
 
-\todo{Add some introductory text...}
+\todo{Add some introductory text\ldots}
 
@@
 for any $E\subseteq\Omega$ and $\varphi^{*}\bar{\mu}$ should be
-a classical IVPM.
+a classical IVPM\@.
 
@@
 satisfies Eq.~(\ref{eq:hbar}) and therefore is in the core of a
-QIVPM. However, for the special case of commuting events, since the
-classical core corresponds to the quantum one by the following lemma,
-there will be a quantum theorem naturally corresponding to classical
-Thm.~\ref{thm:Shapley-classical}.
+QIVPM\@. However, for the special case of commuting events, since
+the classical core corresponds to the quantum one by the following
+lemma, there will be a quantum theorem naturally corresponding to
+classical Thm.~\ref{thm:Shapley-classical}.
 
@@
 such that the pullback of $\bar{\mu}$ by $\varphi$, $\varphi^{*}\bar{\mu}$,
-is a classical IVPM. By Thm.~\ref{thm:Shapley-classical}, there
+is a classical IVPM\@. By Thm.~\ref{thm:Shapley-classical}, there
 is a classical probability measure $\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$
@@
 Similar to how we pull back classical ideas to the quantum world in
-Secs.~\ref{subsec:Definitions-of-IVPMs} and \ref{subsec:States-Consistent-with-IVPMs},
+Secs.~\ref{subsec:Definitions-of-IVPMs} and~\ref{subsec:States-Consistent-with-IVPMs},
 we start from defining the classical expectation value relative to
@@
 the definition of quantum expectation value. After that, see if everything
-can be preceded smoothly in this way...}
+can be preceded smoothly in this way\ldots}
 
@@
 where $t\in\left\{ \symrmL,\symrmR\right\} $ and $\left[\mul\left(P\right),\mur\left(P\right)\right]=\bar{\mu}\left(P\right)$
-as in Defs.~\ref{def:Choquet} and \ref{def:expectation-values-QIVPM}.
-Notice that Eq.~(\ref{eq:pullback-real-measures}) and (\ref{eq:pullback-differences})
+as in Defs.~\ref{def:Choquet} and~\ref{def:expectation-values-QIVPM}.
+Notice that Eq.~(\ref{eq:pullback-real-measures}) and~(\ref{eq:pullback-differences})
 were simplified to the pullback of $\mul$ and $\mur$ which can be
@@
 Eqs.~(\ref{eq:quantum-interval-expectation-core}) and (\ref{eq:quantum-interval-expectation-core-equal})
-separately...}\end{thm}
+separately\ldots}\end{thm}
 
@@
 
-\section{The Kochen-Specker Theorem and Contextuality}
-
-\label{sec:Kochen-Specker}
+\section{The Kochen-Specker Theorem and Contextuality\label{sec:Kochen-Specker}}
 
@@
 
-\begin{thm}[0-Deterministic Variant of the Kochen-Specker Theorem]
-\label{thm:Kochen-Specker} Given a Hilbert space $\Hilb$ of dimension
-$D\ge3$, there is no $0$-deterministic measure~$\bar{\mu}$ mapping
-every event to either $\imposs$ or $\necess$. \end{thm}
+\begin{thm}[0-Deterministic Variant of the Kochen-Specker Theorem]\label{thm:Kochen-Specker}Given
+a Hilbert space $\Hilb$ of dimension $D\ge3$, there is no $0$-deterministic
+measure~$\bar{\mu}$ mapping every event to either $\imposs$ or
+$\necess$. \end{thm}
 
@@
 \begin{tabular}{r|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|} 
-$\mathbf{O}_{ij}$~ & $j=0$ & $j=1$ & $j=2$ \\ 
+$\mathbf{O}_{ij}$ & $j=0$ & $j=1$ & $j=2$ \\ 
 \hline  
@@
 $\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\} $ whose
-eigenvalues are all either~$1$ or $-1$ \cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
+eigenvalues are all either~$1$ or~$-1$ \cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
 They are arranged such that in each row and column, \emph{except the
@@
 
-\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]
-\label{cor:Kochen-Specker-IVPM} Given a Hilbert space $\Hilb$ of
-dimension~$D\ge3$, there is no $\delta$-deterministic QIVPM for
-$\delta<\frac{1}{3}$.\end{thm}
+\begin{thm}[Finite-precision Extension of the Kochen-Specker Theorem]\label{cor:Kochen-Specker-IVPM}Given
+a Hilbert space $\Hilb$ of dimension~$D\ge3$, there is no $\delta$-deterministic
+QIVPM for $\delta<\frac{1}{3}$.\end{thm}
 
@@
 For example, $\bar{\mu}_{2}'$ defined in Table~\ref{tab:probability-measures}
-is a valid $\frac{1}{3}$-deterministic QIVPM. When $\delta\geq\frac{1}{3}$,
+is a valid $\frac{1}{3}$-deterministic QIVPM\@. When $\delta\geq\frac{1}{3}$,
 i.e, when the uncertainty in measurements becomes so large, it becomes
@@
 \par\end{centering}
-\caption{The region to the left of the vertical line at $\delta=\frac{1}{3}$
+\caption{\label{fignoname}The region to the left of the vertical line at $\delta=\frac{1}{3}$
 is where we assume small measurement degradation; in that region our
@@
 explanations for the experimental data.}
-\label{fignoname} 
 \end{figure}
@@
 to either $0=\frac{0}{12}$ or $1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
-defined in Table~\ref{tab:probability-measures} is not a QIVPM.
+defined in Table~\ref{tab:probability-measures} is not a QIVPM\@.
 
@@
 probability measure~$\bar{\mu}_{3}$ that assigns to each event the
-entire range of possibilities is already a QIVPM.
+entire range of possibilities is already a QIVPM\@.
 
@@
 
-\section{The Born Rule and Gleason's Theorem}
-
-\label{sec:Gleason}
+\section{The Born Rule and Gleason's Theorem\label{sec:Gleason}}
 
@@
 in Table~\ref{tab:non-Born-QIVPM}. We want to prove $\bar{\mu}$
-is a QIVPM. Since it is easy to verify $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}),
+is a QIVPM\@. Since it is easy to verify $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}),
 by Lemma~\ref{thm:convex-3-1}, it is sufficient to verify for each
@@
 a subset of $\unknown$, Eq.~(\ref{amr-2}) holds, and $\bar{\mu}$
-is a QIVPM.
+is a QIVPM\@.
 
@@
 is the direct counterpart of the convexity conditions, Eqs.~(\ref{eq:classicalconvex})
-and (\ref{eq:QuantumInterval-valuedProbability-Inclusion}) \cite{Choquet1954,Shapley1971,NgMoYeh1997Chinese,MarinacciMontrucchio2005}.
+and~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) \cite{Choquet1954,Shapley1971,NgMoYeh1997Chinese,MarinacciMontrucchio2005}.
 Therefore, these conditions guarantee that, for any conventional quantum
 probability measure $\mu$, the composition $\ultramodular\circ\mu$
-defines a valid QIVPM. Conversely, if for every quantum probability
+defines a valid QIVPM\@. Conversely, if for every quantum probability
 measure $\mu$, it is the case that $f\circ\mu$ is a QIVPM, then
@@
 
-\item \label{enu:iota-subject-to}A function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
+\item\label{enu:iota-subject-to}A function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
 is ultramodular.
 
-\item \label{enu:iota-mu-CIVPM}The composite function $\ultramodular\circ\mu:2^{\Omega}\rightarrow\mathscr{I}$
+\item\label{enu:iota-mu-CIVPM}The composite function $\ultramodular\circ\mu:2^{\Omega}\rightarrow\mathscr{I}$
 is a classical IVPM for all classical probability measures $\mu:2^{\Omega}\rightarrow\left[0,1\right]$.
 
-\item \label{enu:iota-mu-QIVPM}The composite function $\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$
+\item\label{enu:iota-mu-QIVPM}The composite function $\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$
 is a QIVPM for all quantum probability measures $\mu:\events\rightarrow\left[0,1\right]$.
@@
 
-\begin{proof}Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
+\begin{proof}Statement~\ref{enu:iota-subject-to} implies~\ref{enu:iota-mu-CIVPM}
 and~\ref{enu:iota-mu-QIVPM} as we have outlined above. Conversely,
@@
 not ultramodular, then for some quantum probability measure $\mu$,
-the composite $\ultramodular\circ\mu$ might not be a QIVPM. Suppose
+the composite $\ultramodular\circ\mu$ might not be a QIVPM\@. Suppose
 there are three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
@@
 when $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. In
-other words, this induced map fails to be a QIVPM.
+other words, this induced map fails to be a QIVPM\@.
 
@@
 also want to find a classical probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
-such that $\ultramodular\circ\mu$ is not a classical IVPM. Consider
+such that $\ultramodular\circ\mu$ is not a classical IVPM\@. Consider
 an orthonormal basis $\Omega$ containing $\ket{0}$, $\ket{1}$,
@@
 discussion, but it can be only a few sentences? }\todo{Discrete
-Schrödinger equation? And its relation with Grover's algorithm? }\todo{Notice
+\textgerman[variant=german,spelling=new,babelshorthands=true]{Schrödinger}
+equation? And its relation with Grover's algorithm? }\todo{Notice
 that in differential geometry, Killing–Hopf theorem asserts that having

### 2019-01-20 dissertation.tex
dissertation.lyx Exported to HTML, and use Microsoft Word to grammar check...

@@
 \newcommand{\nb}{\nolinebreak[3] }
+\NewDocumentCommand{\jthSubsystem}{m O{} m}{{#1}_{#2}^{#3}}
 
@@
 \item Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
-what I did in the prospective of a general PhD. in Physics, and working
+what I did in the prospective of a general PhD. in Physics and working
 later in more computational industry.
@@
 be cut in halves endlessly. The input charge of an integrator must
-actually be an integer multiple of the elementary charge. A prefect
-square cannot be draw physically. Even we don't draw it, but merely
-ask whether it exists in the space. This question is still beyond
-our ability to answer because whether the space itself is ultimately
-discrete or continuous is still an unsolved question. Even if a prefect
-square exists physically, we may not able to decide whether the ``square''
+be an integer multiple of the elementary charge. A prefect square
+cannot be draw physically. Even we don't draw it, but merely ask whether
+it exists in the space. This question is still beyond our ability
+to answer because whether the space itself is ultimately discrete
+or continuous is still an unsolved question. Even if a prefect square
+exists physically, we may not able to decide whether the ``square''
 we discussed is really prefect or almost prefect differing only by
@@
 of computations may not have any relations, the follow-up computational
-paths may be significantly different, and these difference is unlikely
+paths may be significantly different, and this difference is unlikely
 to be compensated by error analysis techniques easily like the butterfly
@@
 possibilities for classical quantities inspires two types of quantum
-models. Similar to its classical counterparts, quantum circuit model,
-the most widely used model of quantum computing, manipulates quantities
+models. Like its classical counterparts, quantum circuit model, the
+most widely used model of quantum computing, manipulates quantities
 which are not discrete apparently: the probability amplitudes of quantum
@@
 of the field is extremely large. Alternatively, even if the probability
-amplitudes might never be found quantized, taking into account the
-precision of quantities could still result in a better model. However,
-comparing to the precision of probability amplitudes, it is easier
-to consider the precision of their inducing probabilities because
-the idea of ``imprecise probabilities'' have well-studied classically
-\cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+amplitudes might never be found quantized, considering the precision
+of quantities could still result in a better model. However, comparing
+to the precision of probability amplitudes, it is easier to consider
+the precision of their inducing probabilities because the idea of
+``imprecise probabilities'' have well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
 \todo{Make sure whether realistic quantum computers could branch
@@
 finite fields. Instead of treating the Born rule as an axiom, the
-Born rule can actually be deduced from a set of abstract definitions
-and axioms according to Gleason's theorem. Although we might hope
-to deduce a discrete Born rule directly from a similar set of definitions
-and axioms, no discrete Born rule satisfies certain properties motivated
+Born rule can be deduced from a set of abstract definitions and axioms
+according to Gleason's theorem. Although we might hope to deduce a
+discrete Born rule directly from a similar set of definitions and
+axioms, no discrete Born rule satisfies certain properties motivated
 by Gleason's theorem with infinitely precise real-number probability~\cite{Gardiner2014}.
@@
 finite fields, we will first review the classical interval-valued
-probability, and extend it with the conventional quantum theory.
+probability and extend it with the conventional quantum theory.
 \end{comment}
@@
 against the same event. Given a sample space~$\Omega$ and a set
-of intervals~$\mathscr{I}$, similar to a classical probability measure
+of intervals~$\mathscr{I}$, like a classical probability measure
 $\mu:2^{\Omega}\rightarrow\left[0,1\right]$, a classical interval-valued
@@
 consistent with a non-empty ``ball'' of quantum states whose radius
-is defined by the maximal length of the intervals, and recovers the
+is defined by the maximal length of the intervals and recovers the
 original Gleason theorem asymptotically. Similarly, the conventional
@@
 make an exact state transition as implied by Fig.~\ref{blochSphere.fig}~(b).
-In practice, one has to be content with approximate, typically exponentially
+In practice, one must be content with approximate, typically exponentially
 expensive, transitions from state to state.
@@
 coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=1+\rmi0$.
-\todo{Explain the last part more clear or add a picture.}
+\todo{Explain the last part clearer or add a picture.}
 
@@
 to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
-likely one of the outcomes in $E$ will actually happen. To maintain
-the coherence, $\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
+likely one of the outcomes in $E$ will happen. To maintain the coherence,
+$\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
 $\mu\left(\Omega\right)=1$, and $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
@@
 in different experiments are correlated. Consider another experiment
-sending exactly the same particle as the previous one, but using a
+sending exactly the same particle as the previous one but using a
 different beam splitter corresponding to the observable $\mathbf{O}_{1}$
@@
 event space~$\events$. \todo{Check the citation of this part. Did
-von Neumann really think about this when he use projectors to formulate
+von Neumann really think about this when he uses projectors to formulate
 quantum theory?}
@@
 first case and $2$ in the second. The quantum expectation value can
-also used to decide whether a state is entangled or not for multipartite
+also use to decide whether a state is entangled or not for multipartite
 systems as we describe in the following section.
@@
 is entangled if and only if at least one subsystem state is \textit{mixed},
-i.e., $\Tr_{j}\left(\rho_{j}^{2}\right)<1$ \cite{544199,Jaeger2007}.\NewDocumentCommand{\jthSubsystem}{m O{} m}{{#1}_{#2}^{#3}}
+i.e., $\Tr_{j}\left(\rho_{j}^{2}\right)<1$ \cite{544199,Jaeger2007}.
 
@@
 Different entanglement measures are obtained when an algebra~$\fh$
-different from the local observables is chosen. An obvious example,
-in particular, is given by the set of all observables. In this case,
-the purity takes its maximum value independently of the pure quantum
-state \cite{BKOV2003,BKOSV2004}, expressing the fact that any state
-is a generalized coherent state of the Lie algebra of all observables.
+different from the local observables is chosen. An obvious example
+is given by the set of all observables. In this case, the purity takes
+its maximum value independently of the pure quantum state \cite{BKOV2003,BKOSV2004},
+expressing the fact that any state is a generalized coherent state
+of the Lie algebra of all observables.
 
@@
 from a finite set. In particular, in the field $\ff{2}=\{0,1\}$ of
-booleans, there are exactly four possible vectors: the zero vector,
+Booleans, there are exactly four possible vectors: the zero vector,
 the vector~$\ket{0}$, the vector $\ket{1}$, and the vector $\ket{0}+\ket{1}=\ket{+}$.
@@
 
-Measurement in the standard basis is fairly straightforward: measuring
-$\ket{0}$ or $\ket{1}$ deterministically produces the same state
-while measuring $\ket{+}$ nondeterministically produces $\ket{0}$
-or $\ket{1}$ with no assigned probability distribution. When measuring
-an arbitrary state~$\ket{\phi}\in\left\{ \ket{0},\ket{1},\ket{+}\right\} $
-in other bases $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} $,
-we first represents $\ket{\phi}$ as the linear combination of the
-basis vectors $\beta_{0}\ket{\psi_{0}}+\beta_{1}\ket{\psi_{1}}$,
-where $\beta_{0}$ and $\beta_{1}$ are elements in the field~$\ff{2}$.
+Measurement in the standard basis is straightforward: measuring $\ket{0}$
+or $\ket{1}$ deterministically produces the same state while measuring
+$\ket{+}$ nondeterministically produces $\ket{0}$ or $\ket{1}$
+with no assigned probability distribution. When measuring an arbitrary
+state~$\ket{\phi}\in\left\{ \ket{0},\ket{1},\ket{+}\right\} $ in
+other bases $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} $, we
+first represent $\ket{\phi}$ as the linear combination of the basis
+vectors $\beta_{0}\ket{\psi_{0}}+\beta_{1}\ket{\psi_{1}}$, where
+$\beta_{0}$ and $\beta_{1}$ are elements in the field~$\ff{2}$.
 If $\beta_{i}$ is zero, measuring $\ket{\phi}$ is impossible to
@@
 To understand the computational implications of the modal quantum
-theory defined over the field $\ff{2}$ of booleans, we developed
+theory defined over the field $\ff{2}$ of Booleans, we developed
 a quantum computing model and established its correspondence to a
@@
 \todo{Add citation about where these two names come from. }is the
-problem of deciding whether a given boolean formula has a satisfying
+problem of deciding whether a given Boolean formula has a satisfying
 assignment, assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
@@
 in the $\NP$ complexity class. Our black-box version of the \usat\ problem
-replaces the boolean formula with an arbitrary black box. Solutions
+replaces the Boolean formula with an arbitrary black box. Solutions
 to this generalized problem can be used to solve an unstructured database
@@
 for some $j$. For example, $1-\rmi$ is a generator in $\Fppx{3}$
-means a particular element $1+\rmi\in\Fppx{3}$ can be expressed as
-$1+\rmi=1-3\rmi-3+\rmi=\left(1-\rmi\right)^{3}$. All possible choices
-of generators in $\ff{3^{2}}$ is listed in Table~\ref{tab:Generators-in-F9}.
+so another element $1+\rmi\in\Fppx{3}$ can be expressed as $1+\rmi=1-3\rmi-3+\rmi=\left(1-\rmi\right)^{3}$.
+All possible choices of generators in $\ff{3^{2}}$ is listed in Table~\ref{tab:Generators-in-F9}.
 \begin{table}
@@
 whose field norm is $-1\in\ff{3}$. Generally, given any $c\in\Fp$,
-let $\fnorm*{\left\{ c\right\} }$ denote the set of element whose
+let $\fnorm*{\left\{ c\right\} }$ denote the set of elements whose
 field norm is $c$, i.e., $\fnorm*{\left\{ c\right\} }=\set{\alpha\in\Fpp}{\fnorm{\alpha}=c}$.
@@
 Since $\fnorm{a+b\rmi}=0$ only for $a=b=0$, $\alpha_{0}$ is non-zero,
-and $f$ is actually a bijection between $\fnorm*{\left\{ 1\right\} }$
-and $\fnorm*{\left\{ c_{0}\right\} }$. This means the number of elements
+and $f$ is a bijection between $\fnorm*{\left\{ 1\right\} }$ and
+$\fnorm*{\left\{ c_{0}\right\} }$. This means the number of elements
 in $\fnorm*{\left\{ 1\right\} }$ and $\fnorm*{\left\{ c_{0}\right\} }$
@@
 that is the size of each equivalence class of the map $\fnorm{\alpha}$
-for non-vanishing $\alpha$, including in particular the map to the
-unit norm value $c=1\in\Fp$.
+for non-vanishing $\alpha$, including the map to the unit norm value
+$c=1\in\Fp$.
 \begin{figure}
@@
 in Sec.~\ref{subsec:Complexified-Finite-Fields}, we defined $\fnorm*{\left\{ c\right\} }$
-to be the set of element whose field norm is $c$. Given any $\alpha\in\fnorm*{\left\{ c\right\} }$,
+to be the set of elements whose field norm is $c$. Given any $\alpha\in\fnorm*{\left\{ c\right\} }$,
 the field norm of $\frac{\ket{\Psi}}{\alpha}$ is
@@
 
-Actually, the similar problem has already happened in conventional
-quantum theory. For example, assume we want to normalize $\ket{\Psi}=\ket{0}+\ket{1}$.
+The similar problem has already happened in conventional quantum theory.
+For example, assume we want to normalize $\ket{\Psi}=\ket{0}+\ket{1}$.
 Its inner product with itself is $\ip{\Psi}{\Psi}=2$. Since $\left(\pm\sqrt{2}\right)^{2}=2$,
@@
 searches of these spaces, we discovered an hypothesis for a closed-form
-solution for the counting of the states, and find a rigorous proof
+solution for the counting of the states and find a rigorous proof
 of the enumeration.
@@
 we cannot exactly call these ``probability-conserving'' sectors
-of the state coefficients since we do not have a well defined notion
+of the state coefficients since we do not have a well-defined notion
 of probability, but we do have a well-defined notion of partition
@@
 to unit norm, the norm of the entire $n$-qubit state becomes the
-product of those unit norms, and is automatically normalized to one.
+product of those unit norms and is automatically normalized to one.
 We have already seen that each single-qubit normalized state in the
@@
 is basically a rigorous formulation of Schwinger's intuition (See,
-in particular, Chapter~1, Section~1.16. in \cite{schwinger2001quantum}).
+Chapter~1, Section~1.16. in \cite{schwinger2001quantum}).
 
@@
 range of $k$, and that this $p$ is sufficient to support such calculation.
-In particular, since $k$ is the least quadratic non-residue of $p$,
-every number less than $k$ is a quadratic residue, and thus $0$,
-$1$, $2$, $3$, \ldots , $2^{3n+2}$ are all quadratic residues.
-Hence the numbers $-2^{n}$, \ldots , $2^{n}$ are all inside the
-ordered range $S_{0}\left(k\right)$. On the other hand, if we choose
-any prime smaller than $p$, there is a quadratic non-residue smaller
-than $k$, and we also know that the least quadratic non-residue is
-a prime~\cite{numtheory.ref}. Thus, there is a quadratic non-residue
-in $0$, $1$, $2$, $3$, \ldots , $2^{3n+2}$, and therefore, for
-this smaller $p$, there would be a number in $-2^{n}$, \ldots ,
-$2^{n}$ that is not in the ordered range $S_{0}\left(k\right)$.
+Since $k$ is the least quadratic non-residue of $p$, every number
+less than $k$ is a quadratic residue, and thus $0$, $1$, $2$,
+$3$, \ldots , $2^{3n+2}$ are all quadratic residues. Hence the numbers
+$-2^{n}$, \ldots , $2^{n}$ are all inside the ordered range $S_{0}\left(k\right)$.
+On the other hand, if we choose any prime smaller than $p$, there
+is a quadratic non-residue smaller than $k$, and we also know that
+the least quadratic non-residue is a prime~\cite{numtheory.ref}.
+Thus, there is a quadratic non-residue in $0$, $1$, $2$, $3$,
+\ldots , $2^{3n+2}$, and therefore, for this smaller $p$, there
+would be a number in $-2^{n}$, \ldots , $2^{n}$ that is not in the
+ordered range $S_{0}\left(k\right)$.
 
@@
 times. Beginning at $l=0$ with the information-less state, the normalization
-scaled to integer values as usual, the state after $l$th iteration
-can written as \todo{Verify the computation??}
+scaled to integer values as usual, the state after $l$-th iteration
+can be written as \todo{Verify the computation??}
 \begin{equation}
@@
 the steps in Sec.~\ref{sec:fuzzy} to define events and probability
-measures, and see whether we could have a Gleason-like theorem which
+measures and see whether we could have a Gleason-like theorem which
 induces a correspondence between states and probability measures qualified
@@
 Gleason's theorem to see whether we might trace back from $\mu$ to
-a pure or mixed state, and summarize this correspondence as a discrete
+a pure or mixed state and summarize this correspondence as a discrete
 Born rule. When $p=D=3$, there are indeed some correspondence between
@@
 \end{equation}
-which is much more then one, the number of QPMFF\@. Since we don't
+which is much more than one, the number of QPMFF\@. Since we don't
 have enough QPMFF to correspond even pure states, there is no discrete
@@
 
-\begin{proof}\footnote{This proof assume $p\ge7$, and there is a simpler proof for $D\ge4$
+\begin{proof}\footnote{This proof assumes $p\ge7$, and there is a simpler proof for $D\ge4$
 applying to $p=3$ case~\cite{Gardiner2014}.}Assume such a map $\muF$ satisfying all properties exists, we will
@@
 
-Similar to the previous paragraph, we now compute the QPMFF induced
-by $\ket{\Phi'}=U'\ket{\oplus}=\frac{2\alpha}{\gamma}\ket{0}+\frac{1}{\gamma}\ket{2}$,
+Like the previous paragraph, we now compute the QPMFF induced by $\ket{\Phi'}=U'\ket{\oplus}=\frac{2\alpha}{\gamma}\ket{0}+\frac{1}{\gamma}\ket{2}$,
 where $\alpha=\fnorm*{\frac{1}{2}}\in\ff{p^{2}}$ and
@@
 we know $\muF_{\Phi''}\left(P_{1}\right)$ and $\muF_{\Phi''}\left(P_{0}\right)$
-are same. Actually, they are both equal to $\tfrac{2}{3}$ because
-$\muF_{\Phi''}\left(P_{0}\right)=\muF_{U''\ket{\Phi'}}\left(U''P_{0}U''\right)=\muF_{\Phi'}\left(P_{0}\right)=\tfrac{2}{3}$
+are same. They are both equal to $\tfrac{2}{3}$ because $\muF_{\Phi''}\left(P_{0}\right)=\muF_{U''\ket{\Phi'}}\left(U''P_{0}U''\right)=\muF_{\Phi'}\left(P_{0}\right)=\tfrac{2}{3}$
 by Eqs.~(\ref{eq:basis-independent}) and (\ref{eq:prob23}). Since
@@
 finite fields, we will first review the classical interval-valued
-probability, and extend it with the conventional quantum theory in
+probability and extend it with the conventional quantum theory in
 the next chapter.
@@
 $\mu\left(E\right)+\mu\left(\overline{E}\right)=1$. These ``true''
-probabilities can actually be summarized as a probability measure
-$\mu:2^{\Omega}\rightarrow\left[0,1\right]$ satisfying 
+probabilities can be summarized as a probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+satisfying 
 \begin{align}
@@
 with a probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
-on a event~$E\subseteq\Omega$ if the interval $\bar{\mu}(E)$ contains
+on an event~$E\subseteq\Omega$ if the interval $\bar{\mu}(E)$ contains
 the precise probability calculated by $\mu$, i.e., $\mu\left(E\right)\in\bar{\mu}\left(E\right)$.
@@
 average \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}. Then,
-we will generalize this notation from classical IVPMs to QIVPMs, and
+we will generalize this notation from classical IVPMs to QIVPMs and
 prove the generalized definition consistent with our intuition. For
@@
 
-Similar to how we pull back classical ideas to the quantum world in
-Secs.~\ref{subsec:Definitions-of-IVPMs} and~\ref{subsec:States-Consistent-with-IVPMs},
-we start from defining the classical expectation value relative to
-IVPMs. Consider a classical IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
-and an event $E\subseteq\Omega$ such that 
+Like how we pull back classical ideas to the quantum world in Secs.~\ref{subsec:Definitions-of-IVPMs}
+and~\ref{subsec:States-Consistent-with-IVPMs}, we start from defining
+the classical expectation value relative to IVPMs. Consider a classical
+IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$ and an event $E\subseteq\Omega$
+such that 
 \begin{align}
@@
 \end{equation}
-In another word, as long as $\mu$ is in the core of $\bar{\mu}$,
-the expectation value of $X$ belongs to $\left[1.7,1.8\right]$ which
-should be the expectation value of $X$ with respect to $\bar{\mu}$.
+In another word, if $\mu$ is in the core of $\bar{\mu}$, the expectation
+value of $X$ belongs to $\left[1.7,1.8\right]$ which should be the
+expectation value of $X$ with respect to $\bar{\mu}$.
 
@@
 
-\begin{proof}Consider to express the observable~$\mathbf{O}$ in
+\begin{proof}Consider expressing the observable~$\mathbf{O}$ in
 the spectral decomposition specialized to compute the expectation
@@
 
-To compute the expectation value, we also need to know the the pullback
+To compute the expectation value, we also need to know the pullback
 of $\mathbf{O}$. Since $\mathbf{O}$ can be expressed as the sum
@@
 \end{itemize}
-\todo{Can we find a example where Eq.~(\ref{eq:quantum-interval-expectation-core})
+\todo{Can we find an example where Eq.~(\ref{eq:quantum-interval-expectation-core})
 is a proper inclusion? Or prove the two sides in Eq.~(\ref{eq:quantum-interval-expectation-core})
@@
 matter how $\Omega$ is picked, $\events_{\Omega}$ is one of the
-possible choice of $\eventsC$. Thus, if Eq.~(\ref{eq:quantum-interval-expectation-core-1})
+possible choices of $\eventsC$. Thus, if Eq.~(\ref{eq:quantum-interval-expectation-core-1})
 is true, and we can also prove
@@
 Specifically, the original Kochen-Specker theorem is formulated using
-a model quantum mechanical system that has \emph{definite values at
-all times}~\cite{Held2016}, i.e., its observables have infinitely
-precise values at all times. Our interval-valued probability framework
-will allow us to state, and prove, a stronger version of the theorem
-that holds even if the observables have values that are only definite
-up to some precision specified by a parameter $\delta$. Our approach
-provides a quantitative realization of Mermin's intuition~\cite{Mermin1999}: 
+a model quantum mechanical system that \emph{always has definite values}~\cite{Held2016},
+i.e., its observables have infinitely precise values at all times.
+Our interval-valued probability framework will allow us to state,
+and prove, a stronger version of the theorem that holds even if the
+observables have values that are only definite up to some precision
+specified by a parameter $\delta$. Our approach provides a quantitative
+realization of Mermin's intuition~\cite{Mermin1999}: 
 \begin{quote}
@@
 We first observe that the original Kochen-Specker theorem is a statement
-regarding the non-existence of a $0$-deterministic QIVPM, and generalize
+regarding the non-existence of a $0$-deterministic QIVPM and generalize
 to a corresponding statement about $\delta$-deterministic QIVPMs.
@@
 is a valid $\frac{1}{3}$-deterministic QIVPM\@. When $\delta\geq\frac{1}{3}$,
-i.e, when the uncertainty in measurements becomes so large, it becomes
+i.e., when the uncertainty in measurements becomes so large, it becomes
 possible to map every observable to some (quite inaccurate) probability
@@
 is where we assume small measurement degradation; in that region our
-extension of the KS theorem definitely demonstrates contextuality
-(\textsf{C}). In the region to the right, the degradation of the data
-is large and our extension of the KS theorem no longer refutes other
-explanations for the experimental data.}
+extension of the KS theorem demonstrates contextuality (\textsf{C}).
+In the region to the right, the degradation of the data is large,
+and our extension of the KS theorem no longer refutes other explanations
+for the experimental data.}
 \end{figure}
@@
 hidden variable model for $D=2$ (e.g., as proposed by Bell or Kochen-Specker~\cite{BELL_1966,kochenspecker1967}).
-Such a two-dimensional model assigns definite values to all observables
-at all times, and hence assigns a \emph{determinate} probability (0
+Such a two-dimensional model always assigns definite values to all
+observables, and hence assigns a \emph{determinate} probability (0
 or 1) to each event. This probability measure directly induces a 0-deterministic
@@
 event, we can find the probability measure~$\bar{\mu}_{2}'$ that
-can verified to be a valid QIVPM and is consistent with the experimental
+can be verified as a valid QIVPM and is consistent with the experimental
 data.
@@
 
-Similar to how we proved Thm.~\ref{cor:Kochen-Specker-IVPM}, we
-need other two lemmas to simplify the proof of the convexity condition.
+Like how we proved Thm.~\ref{cor:Kochen-Specker-IVPM}, we need other
+two lemmas to simplify the proof of the convexity condition.
 
@@
 If neither of the previous possibilities is true, i.e., they have
-some intersections, but not a subset relation, then all of $E_{0}\cap E_{1}$,
-$E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$ are non-empties.
+some intersections, but not a subset relation, then $E_{0}\cap E_{1}$,
+$E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$ are all non-empties.
 Together with the fact that $\Omega$ has only three elements, they
@@
 \end{table}
-Next we will prove by contradiction that $\coreBorn\left(\bar{\mu},\events\right)$
+Next, we will prove by contradiction that $\coreBorn\left(\bar{\mu},\events\right)$
 is the empty set. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
@@
 \textgerman[variant=german,spelling=new,babelshorthands=true]{Schrödinger}
-equation? And its relation with Grover's algorithm? }\todo{Notice
+equation? And its relationship with Grover's algorithm? }\todo{Notice
 that in differential geometry, Killing–Hopf theorem asserts that having
@@
 space is glued by a family of classical probability spaces. This is
-similar to the situation that a manifold is glued by many local coordinates.
+like the situation that a manifold is glued by many local coordinates.
 When each small piece has \emph{exactly} the same and positive curvature,
@@
 When the sum of $\frameL$, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$,
-is \emph{exactly} the same and equal to $1$, Gleason's theorem assert
+is \emph{exactly} the same and equal to $1$, Gleason's theorem asserts
 that $\frameL$ can be expressed as Eq.~(\ref{eq:Gleason-for-CP2}).
@@
 computing model above QIVPMs might either need to manipulate the states
-in the core of a QIVPM, or find a way to manipulate QIVPMs directly.
+in the core of a QIVPM or find a way to manipulate QIVPMs directly.
 However, both strategies are not straightforward. On one hand, a QIVPM
@@
 two approaches for dealing with the continuous quantities used in
-the conventional quantum theory, and will be the next natural extension
+the conventional quantum theory and will be the next natural extension
 for our discrete quantum theories and computing.

### 2019-01-21 dissertation.tex
dissertation.lyx Expert to plain text and grammar checked by LanguageTool with too many false positive alert...

@@
 ``Nancy'' Zhang (张楠茜), for you always pay our telephone bill on
-time so that\ldots\ldots\todo{Maybe I don't have to thank them
+time so that\ldots\ldots\todo{ Maybe I don't have to thank them
 as AT\&T family plan members, but I should thank some of them for
@@
 be an integer multiple of the elementary charge. A prefect square
-cannot be draw physically. Even we don't draw it, but merely ask whether
-it exists in the space. This question is still beyond our ability
-to answer because whether the space itself is ultimately discrete
+cannot be drawn physically. Even we don't draw it, but merely ask
+whether it exists in the space. This question is still beyond our
+ability to answer because whether the space itself is ultimately discrete
 or continuous is still an unsolved question. Even if a prefect square
@@
 \begin{comment}
-Our first discrete model replaces the complex numbers by a unrestricted
+Our first discrete model replaces the complex numbers by an unrestricted
 finite field~$\mathbb{F}_{q}$ \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
@@
 freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
-out by the circle $\Sphere{1}$''). The standard form of this maps
+out by the circle $\Sphere{1}$''). The standard form of these maps
 (``the Hopf fibration'') is 
@@
 \end{equation}
-Thus the one-qubit state is independent of $\theta$, and we can choose
-$\theta=\phi$ without loss of generality, reducing the form of the
-unique one-qubit states to $\ket{\psi_{1}}=\rme^{2\rmi\phi}\cos\psi\ket{0}+\sin\psi\ket{1}$,
+Thus, the one-qubit state is independent of $\theta$, and we can
+choose $\theta=\phi$ without loss of generality, reducing the form
+of the unique one-qubit states to $\ket{\psi_{1}}=\rme^{2\rmi\phi}\cos\psi\ket{0}+\sin\psi\ket{1}$,
 and an irreducible state can be represented as a point on a sphere
@@
 
-Thus the geometry of a single qubit reduces to transformations among
+Thus, the geometry of a single qubit reduces to transformations among
 points on $\Sphere{2}$, which can be parametrized in an infinite
@@
 \end{equation}
-Thus the initial equation for the geometry of a quantum state describes
+Thus, the initial equation for the geometry of a quantum state describes
 a \textit{topological sphere~}$\Sphere{2D-1}$ embedded in $\mathReal^{2D}$.
@@
 Because $\varphi$ respects the probability of events, if we restrict
-the domain of $\varphi$ on an classical event space $2^{\Omega}$,
+the domain of $\varphi$ on a classical event space $2^{\Omega}$,
 the function $\varphi^{*}\mu:2^{\Omega}\rightarrow\left[0,1\right]$
@@
 which is greater than the size $p$ of $\Fp$, and so there must be
-at least one common element such that $a^{2}=c-b^{2}$. Thus every
+at least one common element such that $a^{2}=c-b^{2}$. Thus, every
 element $c\in\Fp$ is the field norm of some element $\alpha=a+b\rmi\in\Fpp$
@@
 each (non-zero) image element in $\Fp$. We illustrate this graphically
-in Figure~\ref{proof1.fig}. Thus the Hopf circle always has size
+in Figure~\ref{proof1.fig}. Thus, the Hopf circle always has size
 $p+1$, corresponding essentially to a discrete projective line, and
@@
 \end{equation}
-Therefore a very small fraction of the unit norm states are unentangled.
+Therefore, a very small fraction of the unit norm states are unentangled.
 
@@
 Although division is not an allowed operation for the elements in
-the an ordered region, following the standard procedure to define
-a conventional fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
+an ordered region, following the standard procedure to define a conventional
+fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
 we could define a \emph{cardinal probability} as a pair of order-region
@@
 to two cardinal probabilities with the different ``denominator''.
-The details of the comparison can easily formulated by following the
-standard procedure \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016}
-and will left as an exercise for the readers.
+The details of the comparison can be easily formulated by following
+the standard procedure \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016}
+and will leave as an exercise for the readers.
 
@@
 to ensure that all quantities are expressed in terms of integers.
-Also notice that the positioning of the initial qubit state $\ket{1}$
-is reversed from~\cite{544199}. } \todo{A little bit more explanation?}
+Also, notice that the positioning of the initial qubit state $\ket{1}$
+is reversed from~\cite{544199}. } \todo{A bit more explanation?}
 \begin{equation}
@@
 less than $k$ is a quadratic residue, and thus $0$, $1$, $2$,
-$3$, \ldots , $2^{3n+2}$ are all quadratic residues. Hence the numbers
-$-2^{n}$, \ldots , $2^{n}$ are all inside the ordered range $S_{0}\left(k\right)$.
-On the other hand, if we choose any prime smaller than $p$, there
-is a quadratic non-residue smaller than $k$, and we also know that
-the least quadratic non-residue is a prime~\cite{numtheory.ref}.
+$3$, \ldots , $2^{3n+2}$ are all quadratic residues. Hence, the
+numbers $-2^{n}$, \ldots , $2^{n}$ are all inside the ordered range
+$S_{0}\left(k\right)$. On the other hand, if we choose any prime
+smaller than $p$, there is a quadratic non-residue smaller than $k$,
+and we also know that the least quadratic non-residue is a prime~\cite{numtheory.ref}.
 Thus, there is a quadratic non-residue in $0$, $1$, $2$, $3$,
@@
 \end{equation}
-These states have differing field norm so we cannot compare their
+These states have differing field norm, so we cannot compare their
 cardinal probability directly. Since states differ by only scalar
@@
 and $P_{1}\in\events_{p^{2}}$, i.e., $P_{0}P_{1}=\mathbb{0}$, their
-sum is $P_{0}+P_{1}$ is an event, i.e., $P_{0}+P_{1}\in\events_{p^{2}}$.
+sum $P_{0}+P_{1}$ is an event, i.e., $P_{0}+P_{1}\in\events_{p^{2}}$.
 \end{itemize}
@@
 and acts as the identity for the rest for $i=1$ and $2$. Note that
-$\ket{\oplus}$ is invariant under $U_{i}$ so we have $\muF_{\oplus}\left(P_{0}\right)=\muF_{U_{i}\ket{\oplus}}\left(U_{i}P_{0}U_{i}^{\dagger}\right)=\muF_{\oplus}\left(P_{i}\right)$
+$\ket{\oplus}$ is invariant under $U_{i}$, so we have $\muF_{\oplus}\left(P_{0}\right)=\muF_{U_{i}\ket{\oplus}}\left(U_{i}P_{0}U_{i}^{\dagger}\right)=\muF_{\oplus}\left(P_{i}\right)$
 by Eq.~(\ref{eq:basis-independent}). Let $P'=P_{0}+P_{1}+P_{2}$.
@@
 give $\mu\left(E\cup\overline{E}\right)=[0.9,1.1]$, which is not
-a valid probability interval. Moreover the event $E\cup\overline{E}$
+a valid probability interval. Moreover, the event $E\cup\overline{E}$
 is the entire space; its probability interval should be $\necess$
@@
 is a direct counterpart of the convexity condition of Eq.~(\ref{eq:classicalconvex}).
-Thus our definition of QIVPMs merges aspects of both classical IVPMs
+Thus, our definition of QIVPMs merges aspects of both classical IVPMs
 and quantum probability measures.
@@
 measures, the theorem is only applicable to dimensions $D\geq3$.
-Indeed when the Hilbert space has dimension 2, it is straightforward
+Indeed, when the Hilbert space has dimension 2, it is straightforward
 to construct a 0-deterministic QIVPM as follows. Consider a non-contextual
@@
 are exact, Gleason's theorem asserts that a quantum probability measure
-can essentially induced by the Born rule, but they can be wild when
-we move on to interval-valued situation! }
+can be essentially induced by the Born rule, but they can be wild
+when we move on to interval-valued situation! }
 \end{comment}

### 2019-01-21 dissertation.tex
dissertation.lyx Exported to HTML and grammar checked by Grammarly.

@@
 with other advisory committee members passing my Computer Science
-qualifying exam Spring 2016. Especially, my survey of real computation
+qualifying exam in Spring 2016. Especially, my survey of real computation
 in the qualifying exam inspired me the comparison of quantum computer
@@
 Writing course as presented in Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
-I want to thank Traci Nagle for going through the literature review
-about finite precision measurement and contextuality discussed for
-CSCI-Y790 Writing and Editing course as presented in Sec.~\ref{sec:Quantum-Contextuality}.
-I also thank Elizabeth ``Betsy'' Merceron and Kexin ``Casey''
-Chen (谌可心) for teaching me English in general so that others can understand
-me more easily.
+I also thank Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin
+``Casey'' Chen (谌可心) for teaching me English in general so that
+others can understand me more easily.
 
 \todo{Type a table for acknowledgment so that I would have to write
-``I thank'' so many times here? }Many people in both department
+``I thank'' so many times here? }Many people in both departments
 of Mathematics and Computer Science need to do something more to make
@@
 directors of graduate study in Mathematics, especially Prof.\ Christopher
-Judge and Prof.\ Matthias Weber; directors of PhD. study in Computer
+Judge and Prof.\ Matthias Weber; directors of Ph.D. study in Computer
 Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
@@
 
-Thank all my friends for your supports, including:
+Thank all my friends for your support, including:
 
@@
 \item Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
-what I did in the prospective of a general PhD. in Physics and working
+what I did in the perspective of a general PhD. in Physics and working
 later in more computational industry.
@@
 precision to computable contexts that do not require incomputable
-real numbers. Our goal is to build a more philosophically consistent
+real numbers. Our goal is to build more philosophically consistent
 models by investigating discrete quantum computing using finite number
@@
 generalization of both classical IVPMs and conventional quantum probability
-measures, but also allows us to establish bounds on the validity of
+measures but also allows us to establish bounds on the validity of
 the Kochen-Specker and Gleason theorems in realistic experimental
@@
 
-Since we as human cannot distinguish quantities differing only by
-an arbitrarily small extent \cite{Turing_1937,Gisin2017}, we want
-to incorporate this limitation into our quantum mechanical model to
-better capture our ability of predicting quantum phenomenon and the
-power of realistic quantum computers. Since we are agnostic about
-whether the reality is ultimately discrete or continuous, we considered
-two types of quantum models. By assuming the quantum states are ultimately
-discrete and distinguishable, our first type of quantum theories replaces
-the complex numbers by finite fields. We then focus on the limitation
-of distinguishability itself, incorporate the finite precision measurement
-into our model, and consider quantum interval-valued probability measures.
+Since a human cannot distinguish quantities differing only by an arbitrarily
+small extent \cite{Turing_1937,Gisin2017}, we want to incorporate
+this limitation into our quantum mechanical model to better capture
+our ability to predict quantum phenomenon and the power of realistic
+quantum computers. Since we are agnostic about whether the reality
+is ultimately discrete or continuous, we considered two types of quantum
+models. By assuming the quantum states are ultimately discrete and
+distinguishable, our first type of quantum theories replaces the complex
+numbers by finite fields. We then focus on the limitation of distinguishability
+itself, incorporate the finite precision measurement into our model,
+and consider quantum interval-valued probability measures.
 
@@
 and countries start to build realistic quantum computers recently
-\cite{Shieber2018,Kahn2019}, and seek more efficient ways to simulate
+\cite{Shieber2018,Kahn2019} and seek more efficient ways to simulate
 chemical molecules and to break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}.
@@
 In contrast, the non-apparently discrete quantities confused many
-cultures since very beginning. For example, the ancient Chinese philosopher
-Chuang-tzu (庄子) didn't believe these quantities have a minimum unit,
-and expressed ``If a one-foot-long stick is cut into halves every
-day, the cutting will never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
+cultures since the very beginning. For example, the ancient Chinese
+philosopher Chuang-tzu (庄子) didn't believe these quantities have a
+minimum unit and expressed ``If a one-foot-long stick is cut into
+halves every day, the cutting will never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
 As another example, Greek mathematicians in the school of Pythagoras
@@
 the previous paragraph could not have a simple one-to-one correspondence
-with a real number. Chuang-tzu's stick are made by molecules and cannot
+with a real number. Chuang-tzu's stick is made by molecules and cannot
 be cut in halves endlessly. The input charge of an integrator must
-be an integer multiple of the elementary charge. A prefect square
+be an integer multiple of the elementary charge. A perfect square
 cannot be drawn physically. Even we don't draw it, but merely ask
 whether it exists in the space. This question is still beyond our
-ability to answer because whether the space itself is ultimately discrete
-or continuous is still an unsolved question. Even if a prefect square
+ability to answer because whether space itself is ultimately discrete
+or continuous is still an unsolved question. Even if a perfect square
 exists physically, we may not able to decide whether the ``square''
-we discussed is really prefect or almost prefect differing only by
+we discussed is really perfect or almost perfect differing only by
 an arbitrarily small extent. Similar situation applying to the length
@@
 identifying which real number represents its length requires infinite
-precision, but the precision in reality is limited generally three
+precision, but the precision, in reality, is limited generally three
 or four significant figures~\cite{wiki:AnalogComputer}. As the results,
@@
 the precision of their inducing probabilities because the idea of
-``imprecise probabilities'' have well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+``imprecise probabilities'' has well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
 \todo{Make sure whether realistic quantum computers could branch
@@
 of the inducing probabilities\ldots{} }This idea will be extended
-to quantum domain as quantum interval-valued probability measures
+to the quantum domain as quantum interval-valued probability measures
 (QIVPM).
@@
 Given a pure state~$\ket{\Phi}$, when we measure an observable represented
-by an Hermitian matrix~$\mathbf{O}$, the measurement result is one
+by a Hermitian matrix~$\mathbf{O}$, the measurement result is one
 of the eigenvalues of $\mathbf{O}$. The probability of getting a
@@
 dimension $D\ge3$ according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
-In another word, this state $\rho$ is the unique state consistent
-with any given quantum probability measure.
+In other word, this state $\rho$ is the unique state consistent with
+any given quantum probability measure.
 \end{comment}
@@
 \begin{comment}
-Our first discrete model replaces the complex numbers by an unrestricted
+Our first discrete model replaces the complex numbers with an unrestricted
 finite field~$\mathbb{F}_{q}$ \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
@@
 It is called the modal quantum theory because it can only predict
-whether a measure result is possible or impossible, but not its probability.
-Although a version of quantum theory defined over the two-valued field
-can express simple algorithms such as quantum teleportation \cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007,Schumacher2012-SCHMQT},
+whether a measurement result is possible or impossible, but not its
+probability. Although a version of a quantum theory defined over the
+two-valued field can express simple algorithms such as quantum teleportation
+\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007,Schumacher2012-SCHMQT},
 it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007,DQT2014}.
@@
 of quantum computing. In this model, the state of a discrete $d$-dimensional
-system is a vector in the $d$-dimensional vector space over $\Fpp$,
+system is a vector in the $d$-dimensional vector space over $\Fpp$
 and can be reduced to a point in the discrete complex projective space.
@@
 $p$. Despite this model's similarity to CQT, it still only predicts
-whether a measurement result is possible or impossible, because it
+whether a measurement result is possible or impossible because it
 is not possible to define an inner product in the usual sense due
@@
 a notion of inner product and probability could be recovered. In Sec.~\ref{discretequantumcomputingII},
-this discrete quantum theory is applied on two representative algorithms,
+this discrete quantum theory is applied to two representative algorithms,
 the deterministic Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007}
@@
 When people tried to define quantum probability over finite fields,
-people tended to treat the original Born rule as an axiom, and tried
+people tended to treat the original Born rule as an axiom and tried
 to modify it to get a discrete Born rule \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644,DQT2014,Ellerman2016a}.
@@
 Since the state spaces are now discrete and finite, this suggests
-us to consider a discrete Born rule mapping to finite number of intervals
-called interval-valued probability~\cite{JamisonLodwick2004,THOS2017}.
+us to consider a discrete Born rule mapping to a finite number of
+intervals called interval-valued probability~\cite{JamisonLodwick2004,THOS2017}.
 To adopting the idea of interval-valued probability step-by-step,
@@
 to CQT, our Gleason-like conditions over finite fields cannot deduce
-a discrete Born rule in general. This impossible result suggests us
-that the discrete and finite state spaces might not be compatible
-with infinitely precise real-valued probability. Thus, no matter whether
+a discrete Born rule in general. This impossible result suggests that
+the discrete and finite state spaces might not be compatible with
+infinitely precise real-valued probability. Thus, no matter whether
 the probability amplitudes are ultimately discrete or continuous,
@@
 where~$l$ intuitively corresponds to the strength of evidence for
-the event~$E$ and~$1-r$ corresponds to the strength of evidence
+the event~$E$ and~$1-r$ corresponds to the strength of the evidence
 against the same event. Given a sample space~$\Omega$ and a set
@@
 space of quantum events $\events$ is restricted to mutually commuting
-events, and reduces to conventional quantum probability measures when
+events and reduce to conventional quantum probability measures when
 mapping to infinitely precise uncountable intervals $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
 While Shapley and Gleason both proved there must be a ``state''
-consistent with any given QIVPM in the reduced cases, in general there
-exists a QIVPM such that no state is consistent with it. However,
+consistent with any given QIVPM in the reduced cases, in general,
+there exists a QIVPM such that no state is consistent with it. However,
 we found a class of QIVPMs such that all QIVPMs in this class are
@@
 extend classical IVPMs to QIVPMs. In Sec.~\ref{sec:Kochen-Specker},
-we utilize the previous defined expectation values while proving the
-finite precision variants of the Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
+we utilize the previously defined expectation values while proving
+the finite precision variants of the Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
 and establish bounds on its validity in realistic experimental environments.
@@
 The organization of this thesis is summarized in Table~\ref{tab:organization},
-and finally Chapter~\ref{chap:Further-Discussion} contains the further
+and finally, Chapter~\ref{chap:Further-Discussion} contains further
 extended questions.
@@
 
-The part of conventional quantum theory (CQT) used by quantum circuit
-model is described by the following:
+The part of the conventional quantum theory (CQT) used by quantum
+circuit model is described by the following:
 \begin{enumerate}[label=(\roman{enumi})]
@@
 with an orthonormal basis, allowing us to write \textit{pure} states
-in general as Hilbert space vectors with an Hermitian inner product:
+in general as Hilbert space vectors with a Hermitian inner product:
 \begin{equation}
@@
 $\Sphere{3}$ cannot be directly embedded in $\R^{3}$, three-sphere~$\Sphere{3}$
-can be regarded as attaching two three-dimensional ball on two sides
+can be regarded as attaching two three-dimensional balls on two sides
 of two-sphere~$\Sphere{2}$. In this way, each circle in $\Sphere{3}$
 can be represented as a circle in the three-dimensional ball as shown
-in (b). Moreover, points in (a) are color coded corresponding to circles
+in (b). Moreover, points in (a) are color-coded corresponding to circles
 in (b), e.g., one pole contains the red elliptical circle that would
@@
 Thus, the one-qubit state is independent of $\theta$, and we can
-choose $\theta=\phi$ without loss of generality, reducing the form
+choose $\theta=\phi$ without loss of generality, reducing the formula
 of the unique one-qubit states to $\ket{\psi_{1}}=\rme^{2\rmi\phi}\cos\psi\ket{0}+\sin\psi\ket{1}$,
@@
 
-This $\Sphere{2D-1}$ in turn is ambiguous up to the usual overall
-phase, inducing an $\Sphere{1}$ symmetry action, and identifying
-$\Sphere{2D-1}$ as an $\Sphere{1}$ bundle, whose base space is the
-$(D-1)$-complex-dimensional projective space $\CP{D-1}$. There are
-thus $2D-2$ irreducible real degrees of freedom ($D-1$ complex degrees
-of freedom) for a quantum state with a $D$-dimensional basis, $\set{\ket{i}}{i=0,\ldots,D-1}$.
+This $\Sphere{2D-1}$ is ambiguous up to the usual overall phase,
+inducing an $\Sphere{1}$ symmetry action, and identifying $\Sphere{2D-1}$
+as an $\Sphere{1}$ bundle, whose base space is the $(D-1)$-complex-dimensional
+projective space $\CP{D-1}$. There are thus $2D-2$ irreducible real
+degrees of freedom ($D-1$ complex degrees of freedom) for a quantum
+state with a $D$-dimensional basis, $\set{\ket{i}}{i=0,\ldots,D-1}$.
 
@@
 the overall phase is not measurable, and eliminating the phase dependence
-in turn corresponds to identifying $\Sphere{2D-1}$ as a circle bundle
-over the base space $\CP{D-1}$, and therefore $\CP{D-1}$ defines
-the $2D-2$ intrinsic, irreducible, degrees of freedom of the isolated
+corresponds to identifying $\Sphere{2D-1}$ as a circle bundle over
+the base space $\CP{D-1}$, and therefore $\CP{D-1}$ defines the
+$2D-2$ intrinsic, irreducible, degrees of freedom of the isolated
 $D$-dimensional state's dynamics. In mathematical notation, this
@@
 as being the same if they differ only by an overall phase $\rme^{\rmi\theta}$.
-However, in practice this is not a construction that is easy to realize
+However, in practice, this is not a construction that is easy to realize
 in a practical computation. We now outline an explicit algorithm for
@@
 Given a normalized pure state $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$,
-a natural quantity characterizing an $D$-dimensional system is its
+a natural quantity characterizing a $D$-dimensional system is its
 \textit{density matrix}, $\rho=\op{\Psi}{\Psi}$, or 
@@
 because we can fix one complex coordinate to be unity, and let one
-vary, giving a total of two irreducible dimensions. In fact one must
+vary, giving a total of two irreducible dimensions. In fact, one must
 choose \textit{two} coordinate patches, one covering one pole of $\Sphere{2}$
@@
 only we can define the expectation values, but the quantum probability
-measure define on the whole space can be simply induced by the Born
+measure defined on the whole space can be simply induced by the Born
 rule according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
@@
 a bad idea because two events might appear different but representing
-the same situation. For example, if we take the complement on the
-both sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
+the same situation. For example, if we take the complement on both
+sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
 we will have
@@
 von Neumann really think about this when he uses projectors to formulate
-quantum theory?}
+the quantum theory?}
 
@@
 expectation values because we can pullback an observable to a classical
-random variable, and the expectation values are invariant.\todo{Add
-interpretation!}
+random variable, and the expectation values are invariant.\todo{
+Add interpretation!}
 
@@
 rule easily, searching for a Born rule step-by-step here might provide
-a better idea what we should do in Sec.~\ref{sec:Toward-IVPM} and
-Chapter~\ref{chap:QIVPM}. While the situations will become more
-delicate in the later sections, we will fortunately find the unique
+a better idea of what we should do in Sec.~\ref{sec:Toward-IVPM}
+and Chapter~\ref{chap:QIVPM}. While the situations will become more
+delicate in the later sections, we will, fortunately, find the unique
 Born rule for CQT here.
@@
 event should be invariant despite how we choose the basis. Because
-changing to another basis is the same as applying an unitary map~$U$,
+changing to another basis is the same as applying a unitary map~$U$,
 we should have $\muB_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muB_{\Phi}\left(P\right)$.
@@
 for at least one $j$, represented by a point \emph{inside} the corresponding
-local Bloch sphere embedded in $\mathbb{R}^{3}$. One may therefore
+local Bloch sphere embedded in $\mathbb{R}^{3}$. One may, therefore,
 consider $\ket{\Psi}$ to be maximally entangled if $\left\Vert {\bf X}_{j}\right\Vert =0$
@@
 map that is guaranteed never to produce the zero vector from a valid
-state. There are exactly $6$ such maps, and their matrix representation
+state. There are exactly $6$ such maps, and their matrix representations
 with respect to the standard basis are:
@@
 \]
-\caption{\label{fig:alg}Circuit for black box \usat\ in modal quantum theory
-over the field $\ff{2}$. For further notation see text.}
+\caption{\label{fig:alg}Circuit for the black box \usat\ in modal quantum
+theory over the field $\ff{2}$. For further notation see text.}
 \end{figure}
@@
 while previous parts use $\ket{\Psi}=\ket{\psi_{1}}\cdots\ket{\psi_{j}}\cdots\ket{\psi_{n}}$.
-Moreover, bar is heavily used in QIVPM discussion later, so maybe
-not using bar here???? }The state is initialized to $\ket{0}\ket{\overline{0}}$,
+Moreover, the ``bar'' is heavily used in QIVPM discussion later,
+so maybe not using bar here???? }The state is initialized to $\ket{0}\ket{\overline{0}}$,
 with $\ket{\overline{0}}=\ket{0}\ket{0}\cdots\ket{0}$, i.e., the
@@
 (which is the identity) leaves the state unchanged. \todo{Control-not
-need to be defined and explained in Sec.~\ref{subsec:Quantum-Circuits}
+needs to be defined and explained in Sec.~\ref{subsec:Quantum-Circuits}
 }Applying $S^{\dagger}$ to the first component leaves the state
@@
 so another element $1+\rmi\in\Fppx{3}$ can be expressed as $1+\rmi=1-3\rmi-3+\rmi=\left(1-\rmi\right)^{3}$.
-All possible choices of generators in $\ff{3^{2}}$ is listed in Table~\ref{tab:Generators-in-F9}.
+All possible choices of generators in $\ff{3^{2}}$ are listed in
+Table~\ref{tab:Generators-in-F9}.
 \begin{table}
@@
 \end{equation}
-where the square root in the usual definition of norm is avoided because,
-unlike the continuous case, the square root does not always exist,
-and the field norm of an element $\fnorm{\cdot}$ should be the direct
-counterpart of the norm-squared $\left|\cdot\right|^{2}$ in the conventional
-quantum theory. For example, the field norm of every generator~$g$
-in Table~\ref{tab:Generators-in-F9} is the same number $\fnorm{g}=g^{3+1}=-1$.
-In fact, these four generators are the only elements in $\ff{3^{2}}$
-whose field norm is $-1\in\ff{3}$. Generally, given any $c\in\Fp$,
-let $\fnorm*{\left\{ c\right\} }$ denote the set of elements whose
-field norm is $c$, i.e., $\fnorm*{\left\{ c\right\} }=\set{\alpha\in\Fpp}{\fnorm{\alpha}=c}$.
+where the square root in the usual definition of the norm is avoided
+because, unlike the continuous case, the square root does not always
+exist, and the field norm of an element $\fnorm{\cdot}$ should be
+the direct counterpart of the norm-squared $\left|\cdot\right|^{2}$
+in the conventional quantum theory. For example, the field norm of
+every generator~$g$ in Table~\ref{tab:Generators-in-F9} is the
+same number $\fnorm{g}=g^{3+1}=-1$. In fact, these four generators
+are the only elements in $\ff{3^{2}}$ whose field norm is $-1\in\ff{3}$.
+Generally, given any $c\in\Fp$, let $\fnorm*{\left\{ c\right\} }$
+denote the set of elements whose field norm is $c$, i.e., $\fnorm*{\left\{ c\right\} }=\set{\alpha\in\Fpp}{\fnorm{\alpha}=c}$.
 The set $\fnorm*{\left\{ c\right\} }$ is the discrete analog of phase-equivalence
@@
 in $\fnorm*{\left\{ 1\right\} }$ and $\fnorm*{\left\{ c_{0}\right\} }$
-are the same. Because $c_{0}$ can be any non-zero element, the number
+is the same. Because $c_{0}$ can be any non-zero element, the number
 of elements in the equivalence classes $\fnorm*{\left\{ c\right\} }$
@@
 each (non-zero) image element in $\Fp$. We illustrate this graphically
-in Figure~\ref{proof1.fig}. Thus, the Hopf circle always has size
-$p+1$, corresponding essentially to a discrete projective line, and
-that is the size of each equivalence class of the map $\fnorm{\alpha}$
+in Figure~\ref{proof1.fig}. Thus, the Hopf circle always has the
+size $p+1$, corresponding essentially to a discrete projective line,
+and that is the size of each equivalence class of the map $\fnorm{\alpha}$
 for non-vanishing $\alpha$, including the map to the unit norm value
@@
 
-In this section we want to build a theory of discrete vector spaces
-that approximates as closely as possible the features of conventional
+In this section, we want to build a theory of discrete vector spaces
+that approximates as closely as possible the features of the conventional
 quantum theory. Such a structure would ideally consist of the following:
@@
 have an inner product satisfying the properties above. However, we
-will introduce an Hermitian ``dot product'' satisfying some of those
+will introduce a Hermitian ``dot product'' satisfying some of those
 properties.
@@
 quantum theory, and the positive square root function is called the
-\emph{principal} branch of $\sqrt{w}$~\cite{GAMELIN2003}. In discrete
-case, we can also systematically choose the \emph{principal inverse
-field norm} by utilizing a generator $g\in\Fpp$ discussed in Sec.~\ref{subsec:Complexified-Finite-Fields}.
-Because $g$ is a generator, any non-zero element $c\in\ff{p}\backslash\left\{ 0\right\} $
+\emph{principal} branch of $\sqrt{w}$~\cite{GAMELIN2003}. In the
+discrete case, we can also systematically choose the \emph{principal
+inverse field norm} by utilizing a generator $g\in\Fpp$ discussed
+in Sec.~\ref{subsec:Complexified-Finite-Fields}. Because $g$ is
+a generator, any non-zero element $c\in\ff{p}\backslash\left\{ 0\right\} $
 can be expressed as $g^{\left(p+1\right)k}$ where $k$ is an integer
@@
 but now with all computations in\hspace{0bp}$\pmod{p}$. At this
-point one simply writes down all possible discrete values for the
+point, one simply writes down all possible discrete values for the
 complex numbers $\left(\alpha_{0},\alpha_{1}\right)$ satisfying Eq.~(\ref{DQA2.eq})
@@
 states on the discrete generalized Bloch sphere. By executing computer
-searches of these spaces, we discovered an hypothesis for a closed-form
+searches of these spaces, we discovered a hypothesis for a closed-form
 solution for the counting of the states and find a rigorous proof
@@
 of the state coefficients since we do not have a well-defined notion
-of probability, but we do have a well-defined notion of partition
+of probability, but we do have a well-defined notion of the partition
 of unity. Compared to the total number $p^{2D}$ of possible complex
@@
 \end{equation}
-and in general for $n$-qubits, there are $p^{n}\left(p-1\right)^{n}$
+and in general, for $n$-qubits, there are $p^{n}\left(p-1\right)^{n}$
 instances of pure product states.
@@
 database search problem for certain database sizes. \todo{Prof.~Gil~Kalai
-thought it would be interested if we can do Simon's algorithm in DQC~(I),
-but I don't know when I could organize my unreadable draft to a readable
-one\ldots{} Moreover, Prof.~Ortiz wants to check Shor's algorithm
-in DQC~(I).}
+thought it would be interesting if we can do Simon's algorithm in
+DQC~(I), but I don't know when I could organize my unreadable draft
+to a readable one\ldots{} Moreover, Prof.~Ortiz wants to check Shor's
+algorithm in DQC~(I).}
 
@@
 To explain why this circuit solves the Deutsch problem, we then compute
-the state in each step explicitly, and express the Dirac bracket notation
+the state in each step explicitly and express the Dirac bracket notation
 with its matrix representation in the computational basis $\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $
@@
 \]
-\caption{\label{fig:dbsearch}Circuit for black box \usat\ in discrete quantum
-computing.}
+\caption{\label{fig:dbsearch}Circuit for the black box \usat\ in discrete
+quantum computing.}
 \end{figure}
@@
 emergence of conventional quantum theory}. We next briefly outline
-such a context for local orderable subspaces of a finite field, and
+such a context for local orderable subspaces of a finite field and
 introduce an improvement on the original method~\cite{ReislerSmith1969}
@@
 which is a quadratic residue and hence $x+1>x$. Similarly, $x-\left(x-1\right)=1$
-and hence $x>x-1$. Also $\left(x+1\right)-\left(x-1\right)=2$ which
-is a quadratic residue and hence $x+1>x-1$. Clearly this process
+and hence $x>x-1$. Also, $\left(x+1\right)-\left(x-1\right)=2$ which
+is a quadratic residue and hence $x+1>x-1$. Clearly, this process
 may be continued to show that the sequence $S_{x}\left(k\right)$
@@
 having only integer arithmetic and a limited word length. We cannot
-perform a division having a fractional result at all, since there
-are no fractional representations; we do have the basic constants
-zero and one, as well as positive and negative numbers, but multiplications
-or additions producing results outside the integer range wrap around
+perform a division having a fractional result at all since there are
+no fractional representations; we do have the basic constants zero
+and one, as well as positive and negative numbers, but multiplications
+or additions producing results outside the integer range wrap-around
 modulo the word length and typically yield nonsense. This implies
@@
 
-Although division is not an allowed operation for the elements in
-an ordered region, following the standard procedure to define a conventional
-fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
+Although the division is not an allowed operation for the elements
+in an ordered region, following the standard procedure to define a
+conventional fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
 we could define a \emph{cardinal probability} as a pair of order-region
@@
 large choice of the field), while \textit{equalities} cannot be guaranteed
-in the theory, and in fact can be represented as \textit{inequalities
+in the theory, and in fact, can be represented as \textit{inequalities
 of any order}. That is, given two cardinal probabilities $\cardp{\fnorm{\alpha_{i}}}{\fnorm{\ket{\Psi}}}$
@@
 the experimental results might not always favor $\ket{i}$ or $\ket{j}$
-no matter how much resource we use. The same principle can also apply
+no matter how many resources we use. The same principle can also apply
 to two cardinal probabilities with the different ``denominator''.
@@
 To examine the Deutsch-Jozsa algorithm in the discrete theory of the
-previous section, we assume we are given a classical function $f:\boolt^{n}\rightarrow\boolt$,
+previous section, we assume we are given a classical function $f:\boolt^{n}\rightarrow\boolt$
 and are told that $f$ is either constant or balanced \cite{DeutschJozsa1992,544199,Jaeger2007}.
@@
 less than this value of $p$ can support calculation in the ordered
-range of $k$, and that this $p$ is sufficient to support such calculation.
+range of $k$ and that this $p$ is sufficient to support such calculation.
 Since $k$ is the least quadratic non-residue of $p$, every number
@@
 \end{itemize}
-Then a quantum probability measure over finite field (QPMFF) $\mu:\events_{p^{2}}\rightarrow\left[0,1\right]$
+Then a quantum probability measure over a finite field (QPMFF) $\mu:\events_{p^{2}}\rightarrow\left[0,1\right]$
 assigns a probability to each event (projection operator~$P$) subject
@@
 a pure or mixed state and summarize this correspondence as a discrete
-Born rule. When $p=D=3$, there are indeed some correspondence between
-QPMFFs and states. However, when $D=3$ and $p=7$, we have numerical
+Born rule. When $p=D=3$, there is indeed some correspondence between
+QPMFFs and states. However, when $D=3$ and $p=7$, we have numerically
 verified that the only QPMFF $\mu:\events_{7^{2}}\rightarrow\left[0,1\right]$
@@
 in Sec.~\ref{subsec:Vector-Spaces}. The unit-norm state $\ket{\oplus}=\frac{1}{\gamma}\left[\ket{0}+\ket{1}+\ket{2}\right]$
-can then be used as a parameter of $\muF$, and induces a QPMFF $\muF_{\oplus}$.
+can then be used as a parameter of $\muF$ and induces a QPMFF $\muF_{\oplus}$.
 To compute the probability values of $\muF_{\oplus}$, we want to
@@
 unit interval $\left[0,1\right]$. To overcome this issue, we want
-to consider a discrete Born rule mapping to finite number of intervals
+to consider a discrete Born rule mapping to a finite number of intervals
 called interval-valued probability~\cite{JamisonLodwick2004,THOS2018}.
@@
 where~$\ell$ intuitively corresponds to the strength of evidence
-for the event~$E$ and~$1-r$ corresponds to the strength of evidence
-against the same event. Under some additional assumptions, this interval
-could be interpreted as the Gaussian width of a probability distribution.
+for the event~$E$ and~$1-r$ corresponds to the strength of the
+evidence against the same event. Under some additional assumptions,
+this interval could be interpreted as the Gaussian width of a probability
+distribution.
 
@@
 defined by precomposition $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
-is the pullback of $\bar{\mu}$ by $\varphi$, and is a classical
-IVPM naturally.
-
-Since we can pullback a QIVPM to a classical one, known properties
+is the pullback of $\bar{\mu}$ by $\varphi$ and is a classical IVPM
+naturally.
+
+Since we can pull back a QIVPM to a classical one, known properties
 of classical IVPMs directly hold for QIVPMs when one restricts to
@@
 the precise probability calculated by $\mu$, i.e., $\mu\left(E\right)\in\bar{\mu}\left(E\right)$.
-The \emph{core} of a IVPM~$\bar{\mu}$, $\mathrm{core}\left(\bar{\mu}\right)$,
+The \emph{core} of an IVPM~$\bar{\mu}$, $\mathrm{core}\left(\bar{\mu}\right)$,
 is the collection of all probability measures~$\mu$ that are \emph{consistent}
@@
 \end{equation}
-In another word, if $\mu$ is in the core of $\bar{\mu}$, the expectation
+In other word, if $\mu$ is in the core of $\bar{\mu}$, the expectation
 value of $X$ belongs to $\left[1.7,1.8\right]$ which should be the
@@
 Then, the expectation values of $X$ relative to real-valued and interval-valued
-probability measures can be defined like weighted averages as follow.
+probability measures can be defined as weighted averages as follow.
 \begin{itemize}
@@
 where $t\in\left\{ \symrmL,\symrmR\right\} $. Then, the expectation
-values of $\mathbf{O}$ relative to $\bar{\mu}$ is
+value of $\mathbf{O}$ relative to $\bar{\mu}$ is
 \begin{equation}
@@
 i.e., its observables have infinitely precise values at all times.
-Our interval-valued probability framework will allow us to state,
-and prove, a stronger version of the theorem that holds even if the
-observables have values that are only definite up to some precision
-specified by a parameter $\delta$. Our approach provides a quantitative
-realization of Mermin's intuition~\cite{Mermin1999}: 
+Our interval-valued probability framework will allow us to state and
+prove, a stronger version of the theorem that holds even if the observables
+have values that are only definite up to some precision specified
+by a parameter $\delta$. Our approach provides a quantitative realization
+of Mermin's intuition~\cite{Mermin1999}: 
 \begin{quote}
@@
 every event must be assigned a probability either in $\imposs$ or
-in $\necess$, i.e., whether every event is happened is completely
-determined with certainty. As $\delta$ gets larger, the QIVPM allows
-for more indeterminate behavior. % For example, $\bar{\mu}_{A}$ defined in
+in $\necess$, i.e., whether every event happens is completely determined
+with certainty. As $\delta$ gets larger, the QIVPM allows for more
+indeterminate behavior. % For example, $\bar{\mu}_{A}$ defined in
 % Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
@@
 \caption{\label{fignoname}The region to the left of the vertical line at $\delta=\frac{1}{3}$
-is where we assume small measurement degradation; in that region our
-extension of the KS theorem demonstrates contextuality (\textsf{C}).
+is where we assume small measurement degradation; in that region,
+our extension of the KS theorem demonstrates contextuality (\textsf{C}).
 In the region to the right, the degradation of the data is large,
@@
 Such a two-dimensional model always assigns definite values to all
-observables, and hence assigns a \emph{determinate} probability (0
+observables and hence assigns a \emph{determinate} probability (0
 or 1) to each event. This probability measure directly induces a 0-deterministic
@@
 probability of $0$, and we repeat the experiment $100$ times. In
-a perfect world we should be able to refute the event $100$ times
+a perfect world, we should be able to refute the event $100$ times
 and calculate that the probability is $0$. We might also observe
@@
 This is also not a valid probability measure by the same argument
-as above. However, in this case $\bar{\mu}_{2}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
+as above. However, in this case, $\bar{\mu}_{2}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
 and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{2}\left(P_{0}\right)+\bar{\mu}_{2}\left(P_{1}\right)$
@@
 \begin{proof}To prove this theorem, we need to construct a QIVPM
-on some Hilbert space, and verify that there are no states that are
+on some Hilbert space and verify that there are no states that are
 consistent (see Def.~\ref{def:Consistency}) with it on all possible
@@
 and~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) \cite{Choquet1954,Shapley1971,NgMoYeh1997Chinese,MarinacciMontrucchio2005}.
-Therefore, these conditions guarantee that, for any conventional quantum
+Therefore, these conditions guarantee that for any conventional quantum
 probability measure $\mu$, the composition $\ultramodular\circ\mu$
@@
 
-In other words, essential properties of QIVPMs constructed using interval
-maps can be gleaned from the properties of ultramodular functions.
-The following is a most interesting property in our setting.
+In other words, the essential properties of QIVPMs constructed using
+interval maps can be gleaned from the properties of ultramodular functions.
+The following is the most interesting property in our setting.
 
@@
 further study the tensor product structure among QIVPMs which is essential
-for defining product and entangled states, and serves the basis to
+for defining product and entangled states and serves the basis to
 discuss quantum nonlocality~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
@@
 satisfying $\left\Vert \mathscr{I}\right\Vert \le\varepsilon$, $\bar{\mu}$
-must have an non-empty core, i.e., $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$
+must have a non-empty core, i.e., $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$
 ?\end{question}
@@
 positive constant curvature guarantees a manifold is essentially a
-sphere, but say little things even if the curvature has only small
+sphere, but say little things even if the curvature has an only small
 deviation from constant. Since a quantum probability measure is glued
@@
 can be essentially induced by the Born rule, but they can be wild
-when we move on to interval-valued situation! }
+when we move on to the interval-valued situation! }
 \end{comment}
@@
 is bounded by $\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)+2\varepsilon$.
-In another word, the left-end function~$\frameL$ satisfies the following
+In other word, the left-end function~$\frameL$ satisfies the following
 inequalities
@@
 2013~\cite{Sanders2013}, and there is no clear answer for his question
-as far as I understand. To have an idea how hard this question could
-be, recall in Sec.~\ref{sec:fuzzy} we state that a quantum probability
-space is glued by a family of classical probability spaces. This is
-like the situation that a manifold is glued by many local coordinates.
-When each small piece has \emph{exactly} the same and positive curvature,
-the Killing-Hopf theorem asserts this manifold is a sphere, but little
-can we say even if the curvature has only small deviation from constant.
-Similar situation might happen when approximating Gleason's theorem,
-but this time the whole space is glued by ``local'' classical probability
-space defined by each orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
-When the sum of $\frameL$, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$,
-is \emph{exactly} the same and equal to $1$, Gleason's theorem asserts
+as far as I understand. To have an idea of how hard this question
+could be, recall in Sec.~\ref{sec:fuzzy} we state that a quantum
+probability space is glued by a family of classical probability spaces.
+This is like the situation that a manifold is glued by many local
+coordinates. When each small piece has \emph{exactly} the same and
+positive curvature, the Killing-Hopf theorem asserts this manifold
+is a sphere, but little can we say even if the curvature has an only
+small deviation from constant. A similar situation might happen when
+approximating Gleason's theorem, but this time the whole space is
+glued by ``local'' classical probability space defined by each orthonormal
+basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$. When the sum of
+$\frameL$, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$, is
+\emph{exactly} the same and equal to $1$, Gleason's theorem asserts
 that $\frameL$ can be expressed as Eq.~(\ref{eq:Gleason-for-CP2}).

### 2019-01-22 dissertation.tex
dissertation.lyx Replace all $:$ by $\colon$ because LaTeX assumes a $:$ in mathmode means division, and we should use $\colon$ to define a function. Thanks for "Online Grammar Checker for TeX files" ( http://mccabedj.ucc.asn.au/checktex.html ) for point this out...

@@
 For any mixed state~$\rho$, the generalized Born rule induces a
-conventional quantum probability measure $\muB_{\rho}:\events\rightarrow[0,1]$,
+conventional quantum probability measure $\muB_{\rho}\colon\events\rightarrow[0,1]$,
 where $\events$ is the set of all projection operators on a given
-Hilbert space. Conversely, any quantum probability measure $\mu:\events\rightarrow[0,1]$
+Hilbert space. Conversely, any quantum probability measure $\mu\colon\events\rightarrow[0,1]$
 can be induced from a mixed state $\rho$ in the Hilbert space of
@@
 of intervals~$\mathscr{I}$, like a classical probability measure
-$\mu:2^{\Omega}\rightarrow\left[0,1\right]$, a classical interval-valued
-probability measure (IVPM) $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+$\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$, a classical interval-valued
+probability measure (IVPM) $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
 needs to satisfy some coherent axioms. By satisfying the convexity
@@
 The quantum extension, quantum interval-valued probability measure
-(QIVPM) $\bar{\mu}:\events\rightarrow\mathscr{I}$, is a generalization
-of both classical IVPMs $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
-and conventional quantum probability measures $\mu:\events\rightarrow[0,1]$
+(QIVPM) $\bar{\mu}\colon\events\rightarrow\mathscr{I}$, is a generalization
+of both classical IVPMs $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
+and conventional quantum probability measures $\mu\colon\events\rightarrow[0,1]$
 \cite{THOS2017}, because QIVPMs reduce to classical IVPMs when the
@@
 and $\Omega_{0}$. And this experiment defines a classical probability
-measure $\mu_{0}:2^{\Omega_{0}}\rightarrow\left[0,1\right]$.
+measure $\mu_{0}\colon2^{\Omega_{0}}\rightarrow\left[0,1\right]$.
 
@@
 Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
-and the probability measure $\mu_{1}:2^{\Omega_{1}}\rightarrow\left[0,1\right]$
+and the probability measure $\mu_{1}\colon2^{\Omega_{1}}\rightarrow\left[0,1\right]$
 defined by this experiment is different from the previous one, these
@@
 Then, a quantum probability space can be defined as a quantum event
-space~$\events$ together with a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
+space~$\events$ together with a quantum probability measure $\mu\colon\events\rightarrow\left[0,1\right]$
 subject to the corresponding constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
@@
 the domain of $\varphi$ on a classical event space $2^{\Omega}$,
-the function $\varphi^{*}\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+the function $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
 defined by precomposition $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$
 is a classical probability measure and called the pullback of $\mu$
-by $\varphi:2^{\Omega}\rightarrow\events$.
+by $\varphi\colon2^{\Omega}\rightarrow\events$.
 
@@
 If we restrict $\varphi$ on the classical event space~$2^{\Omega}$
-and consider $\varphi:2^{\Omega}\rightarrow\events$, then the pullback
-of $\mathbf{O}$ by $\varphi$ is a random variable $\varphi^{*}\mathbf{O}:\Omega\rightarrow\mathbb{R}$
+and consider $\varphi\colon2^{\Omega}\rightarrow\events$, then the
+pullback of $\mathbf{O}$ by $\varphi$ is a random variable $\varphi^{*}\mathbf{O}\colon\Omega\rightarrow\mathbb{R}$
 defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$.
@@
 an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
-$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with $\varphi:2^{\Omega}\rightarrow\events$
+$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with $\varphi\colon2^{\Omega}\rightarrow\events$
 defined by Eq.~(\ref{eq:pullback-function}). Given a quantum probability
-measure $\mu:\events\rightarrow\left[0,1\right]$, the expectation
+measure $\mu\colon\events\rightarrow\left[0,1\right]$, the expectation
 value of $\mathbf{O}$ relative to $\mu$ is exactly the expectation
@@
 space $\Hilb$ of dimension $D\geq3$, given a quantum probability
-measure $\mu:\events\rightarrow\left[0,1\right]$, there exists a
-unique mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such
+measure $\mu\colon\events\rightarrow\left[0,1\right]$, there exists
+a unique mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such
 that $\mu\left(P\right)=\Tr\left(\rho P\right)$ for any $D$-dimensional
@@
 We can prove the unreasonable power of the arbitrary-function \usat\ starting
-with a classical function $f:\boolt^{n}\rightarrow\boolt$ that takes
-$n$ bits and returns at most one \btrue\ result. To build a quantum
-algorithm, $f$ is first represented as the Deutsch quantum black
-box~$\uf$ with \cite{Deutsch1985,544199} 
+with a classical function $f\colon\boolt^{n}\rightarrow\boolt$ that
+takes $n$ bits and returns at most one \btrue\ result. To build
+a quantum algorithm, $f$ is first represented as the Deutsch quantum
+black box~$\uf$ with \cite{Deutsch1985,544199} 
 \begin{equation}
@@
 $\left(a+b\rmi\right)^{*}=a-b\rmi$ \cite{Artin1991,grove2002classical,DummitFoote2004}.
-Then, we define the \emph{field norm} $\fnorm{\cdot}:\Fpp\rightarrow\Fp$
+Then, we define the \emph{field norm} $\fnorm{\cdot}\colon\Fpp\rightarrow\Fp$
 as an element $a+\rmi b$ multiplying its complex conjugation $\left(a+b\rmi\right)^{*}$~\cite{wiki:FieldNorm},
@@
 algorithm for the Deutsch problem \cite{Deutsch1985,544199,Mermin2007}.
-The Deutsch problem is to decide whether a function $f:\boolt\rightarrow\boolt$
+The Deutsch problem is to decide whether a function $f\colon\boolt\rightarrow\boolt$
 is constant or balanced. As listed in Table~\ref{tab:Possible-f},
@@
 To examine the Deutsch-Jozsa algorithm in the discrete theory of the
-previous section, we assume we are given a classical function $f:\boolt^{n}\rightarrow\boolt$
+previous section, we assume we are given a classical function $f\colon\boolt^{n}\rightarrow\boolt$
 and are told that $f$ is either constant or balanced \cite{DeutschJozsa1992,544199,Jaeger2007}.
@@
 searching an unstructured database of size $N=2^{n}$ \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
-Let $f:\boolt^{n}\rightarrow\boolt$ be the function we want to search.
-To simplify our discussion, we will only consider 
+Let $f\colon\boolt^{n}\rightarrow\boolt$ be the function we want
+to search. To simplify our discussion, we will only consider 
 \begin{equation}
@@
 \end{itemize}
-Then a quantum probability measure over a finite field (QPMFF) $\mu:\events_{p^{2}}\rightarrow\left[0,1\right]$
+Then a quantum probability measure over a finite field (QPMFF) $\mu\colon\events_{p^{2}}\rightarrow\left[0,1\right]$
 assigns a probability to each event (projection operator~$P$) subject
@@
 QPMFFs and states. However, when $D=3$ and $p=7$, we have numerically
-verified that the only QPMFF $\mu:\events_{7^{2}}\rightarrow\left[0,1\right]$
+verified that the only QPMFF $\mu\colon\events_{7^{2}}\rightarrow\left[0,1\right]$
 is \todo{Equal probable.}
@@
 power set~$2^{\Omega}$ as the classical event space, a classical
-IVPM~$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$ is a function
+IVPM~$\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ is a function
 subject to the following constraints:\begin{subequations}\label{eq:CIVPM-constraints}
@@
 probability space with the classical event space $2^{\Omega}$. Because
-a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$ and a classical
-IVPM $\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ only differ on
-their domains, if we can find a function $\varphi:2^{\Omega}\rightarrow\events$
+a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$ and a classical
+IVPM $\bar{\mu}'\colon2^{\Omega}\rightarrow\mathscr{I}$ only differ
+on their domains, if we can find a function $\varphi\colon2^{\Omega}\rightarrow\events$
 preserving the structure, we can pullback~\cite{wiki:Pullback} any
-QIVPM~$\bar{\mu}$ to $\varphi^{*}\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+QIVPM~$\bar{\mu}$ to $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
 such that $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
@@
 by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
-we define the function $\varphi:2^{\Omega}\rightarrow\events$ maps
-any set~$E$ to the sum of the projectors formed by elements in $E$
-as in Eq.~(\ref{eq:pullback-function}). \todo{Review this part
-because Eq.~(\ref{eq:pullback-function}) is moved to Sec.~\ref{sec:fuzzy}.
-}Therefore, given a QIVPM~$\bar{\mu}$, the function $\varphi^{*}\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
+we define the function $\varphi\colon2^{\Omega}\rightarrow\events$
+maps any set~$E$ to the sum of the projectors formed by elements
+in $E$ as in Eq.~(\ref{eq:pullback-function}). \todo{Review this
+part because Eq.~(\ref{eq:pullback-function}) is moved to Sec.~\ref{sec:fuzzy}.
+}Therefore, given a QIVPM~$\bar{\mu}$, the function $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
 defined by precomposition $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
@@
 Recall in Sec.~\ref{subsec:Definitions-of-IVPMs}, given a classical
-IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$ and an event $E\subseteq\Omega$
-such that $\bar{\mu}\left(E\right)=\left[0.2,0.3\right]$ and $\bar{\mu}\left(\overline{E}\right)=\left[0.7,0.8\right]$,
-we discussed the ``true'' probabilities, $\mu\left(E\right)$ and
-$\mu\left(\overline{E}\right)$, can be anywhere in the range $\left[0.2,0.3\right]$
-and $\left[0.7,0.8\right]$, respectively, as long as they satisfy
-$\mu\left(E\right)+\mu\left(\overline{E}\right)=1$. These ``true''
-probabilities can be summarized as a probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
-satisfying 
+IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ and an event
+$E\subseteq\Omega$ such that $\bar{\mu}\left(E\right)=\left[0.2,0.3\right]$
+and $\bar{\mu}\left(\overline{E}\right)=\left[0.7,0.8\right]$, we
+discussed the ``true'' probabilities, $\mu\left(E\right)$ and $\mu\left(\overline{E}\right)$,
+can be anywhere in the range $\left[0.2,0.3\right]$ and $\left[0.7,0.8\right]$,
+respectively, as long as they satisfy $\mu\left(E\right)+\mu\left(\overline{E}\right)=1$.
+These ``true'' probabilities can be summarized as a probability
+measure $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$ satisfying
 \begin{align}
@@
 \begin{definition}[Classical Consistency and Core]\label{def:Consistency-classical}
-We say an IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$ is \emph{consistent}
-with a probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+We say an IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
+is \emph{consistent} with a probability measure $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
 on an event~$E\subseteq\Omega$ if the interval $\bar{\mu}(E)$ contains
@@
 \begin{equation}
-\mathrm{core}\left(\bar{\mu}\right)=\set{\mu:2^{\Omega}\rightarrow\left[0,1\right]}{\forall E\subseteq\Omega,~\mu\left(E\right)\in\bar{\mu}\left(E\right)}\,.\label{eq:hbar-classical}
+\mathrm{core}\left(\bar{\mu}\right)=\set{\mu\colon2^{\Omega}\rightarrow\left[0,1\right]}{\forall E\subseteq\Omega,~\mu\left(E\right)\in\bar{\mu}\left(E\right)}\,.\label{eq:hbar-classical}
 \end{equation}
@@
 \begin{lemma}\label{lemma:density-matrix-pullback}Consider a QIVPM
-$\bar{\mu}:\events\rightarrow\mathscr{I}$ and a commuting subspace
+$\bar{\mu}\colon\events\rightarrow\mathscr{I}$ and a commuting subspace
 of events $\eventsC$ diagonalizable by a common orthonormal basis
 $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with the
-function $\varphi:2^{\Omega}\rightarrow\events$ defined by Eq.~(\ref{eq:pullback-function}).
+function $\varphi\colon2^{\Omega}\rightarrow\events$ defined by Eq.~(\ref{eq:pullback-function}).
 For any classical probability measure~$\mu$ consistent with the
@@
 \begin{thm}[Non-empty Core for Compatible Measurements]\label{thm:Shapley}For
-every QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
-of events $\eventsC\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\eventsC\right)\ne\emptyset$.\end{thm}
+every QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$, if a
+subspace of events $\eventsC\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\eventsC\right)\ne\emptyset$.\end{thm}
 
@@
 they can be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $.
-We can then follow Eq.~(\ref{eq:pullback-function}) to define $\varphi:2^{\Omega}\rightarrow\events$
+We can then follow Eq.~(\ref{eq:pullback-function}) to define $\varphi\colon2^{\Omega}\rightarrow\events$
 such that the pullback of $\bar{\mu}$ by $\varphi$, $\varphi^{*}\bar{\mu}$,
 is a classical IVPM\@. By Thm.~\ref{thm:Shapley-classical}, there
-is a classical probability measure $\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$
+is a classical probability measure $\pmeas\colon2^{\Omega}\rightarrow\left[0,1\right]$
 consistent with $\varphi^{*}\bar{\mu}$, and thus there must be a
@@
 the classical expectation value relative to IVPMs. Consider a classical
-IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$ and an event $E\subseteq\Omega$
-such that 
+IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ and an event
+$E\subseteq\Omega$ such that 
 \begin{align}
@@
 \end{align}
-and a random variable $X:\Omega\rightarrow\mathbb{R}$ defined by
+and a random variable $X\colon\Omega\rightarrow\mathbb{R}$ defined
+by
 \begin{equation}
@@
 As we have discussed, the ``true'' probability is a probability
-measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$ consistent with
-$\bar{\mu}$ on every event. On one extreme case, $\mu\left(E\right)=0.2$,
+measure $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$ consistent
+with $\bar{\mu}$ on every event. On one extreme case, $\mu\left(E\right)=0.2$,
 the expectation value of $X$ relative to $\mu$ is 
@@
 \begin{definition}[Classical Expectation Values]\label{def:Choquet}Consider
-a classical sample space~$\Omega$ with a random variable $X:\Omega\rightarrow\mathbb{R}$.
+a classical sample space~$\Omega$ with a random variable $X\colon\Omega\rightarrow\mathbb{R}$.
 Since we only consider finite sample space, $X$ can always be decomposed
@@
 \begin{itemize}
-\item Given a classical probability measure $\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$,
+\item Given a classical probability measure $\pmeas\colon2^{\Omega}\rightarrow\left[0,1\right]$,
 the expectation value of $X$ relative to $\mu$ is an average of~$x_{i}^{s}$
@@
 \end{equation}
-\item Consider a classical IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$.
+\item Consider a classical IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$.
 The expectation value of $X$ relative to $\bar{\mu}$ still looks
@@
 
-\begin{thm}\label{thm:Rosenmuller}For every classical IVPM $\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
-and any random variable $X:\Omega\rightarrow\mathbb{R}$, we have
+\begin{thm}\label{thm:Rosenmuller}For every classical IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
+and any random variable $X\colon\Omega\rightarrow\mathbb{R}$, we
+have
 \begin{equation}
@@
 and each $P_{i}^{s}$ is the projector onto the eigenspace of distinct
-eigenvalue~$\lambda_{i}^{s}$. Consider a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
-with its left-end and right-end denoted by $\mul:\events\rightarrow\left[0,1\right]$
-and $\mur:\events\rightarrow\left[0,1\right]$, respectively, i.e.,
-$\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$.
+eigenvalue~$\lambda_{i}^{s}$. Consider a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
+with its left-end and right-end denoted by $\mul\colon\events\rightarrow\left[0,1\right]$
+and $\mur\colon\events\rightarrow\left[0,1\right]$, respectively,
+i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$.
 Let $s$ be either $+$ or $-$ in the superscript in the following
@@
 \begin{thm}\label{lemma:expectation-singleton}Given a quantum probability
-measure $\mu:\events\rightarrow\left[0,1\right]$ satisfying Eqs.~(\ref{eq:QuantumProbability})
-and (\ref{eq:QuantumProbability-Addition}), if we define a QIVPM
-$\bar{\mu}:\events\rightarrow\mathscr{I}$ by $\bar{\mu}\left(P\right)=\left[\mu\left(P\right),\mu\left(P\right)\right]$
+measure $\mu\colon\events\rightarrow\left[0,1\right]$ satisfying
+Eqs.~(\ref{eq:QuantumProbability}) and (\ref{eq:QuantumProbability-Addition}),
+if we define a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
+by $\bar{\mu}\left(P\right)=\left[\mu\left(P\right),\mu\left(P\right)\right]$
 for all projectors~$P$, then the expectation value of any observable~$\mathbf{O}$
@@
 an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
-$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with $\varphi:2^{\Omega}\rightarrow\events$
-defined by Eq.~(\ref{eq:pullback-function}). Given a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$,
+$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with $\varphi\colon2^{\Omega}\rightarrow\events$
+defined by Eq.~(\ref{eq:pullback-function}). Given a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$,
 the expectation value of $\mathbf{O}$ relative to $\bar{\mu}$ is
@@
 diagonalizable by an orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $
-and a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$.
+and a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$.
 \begin{itemize}
@@
 \end{equation}
-where $\varphi:2^{\Omega}\rightarrow\events$ is defined by Eq.~(\ref{eq:pullback-function}).
+where $\varphi\colon2^{\Omega}\rightarrow\events$ is defined by Eq.~(\ref{eq:pullback-function}).
 Hence, to prove Eq.~(\ref{eq:quantum-interval-expectation-core}),
@@
 \begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
-A QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is $\delta$-deterministic
+A QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}$ is $\delta$-deterministic
 if, for every event $P\in\events$, we have that either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
@@
 The first lemma shows a simpler way to prove the convexity condition.
-Recall that the convexity condition for a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
+Recall that the convexity condition for a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
 states that for each pair of \emph{commuting} projectors~$P_{0}$
@@
 \begin{lemma}\label{lemma:verify-convexity} To verify the convexity
-condition of a QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$, it
-is sufficient to check that: 
+condition of a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$,
+it is sufficient to check that: 
 \begin{equation}
@@
 \begin{lemma}\label{lemma:delta2zero} From any $\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<\frac{1}{3}$,
-we can construct a $0$-deterministic QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
+QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}$ with $\delta<\frac{1}{3}$,
+we can construct a $0$-deterministic QIVPM $\barmuD\colon\events\rightarrow\left\{ \imposs,\necess\right\} $
 defined as follows: 
@@
 \begin{proof}[Proof by Contradiction] Suppose there is a $\delta$-deterministic
-QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. By Lemma~\ref{lemma:delta2zero},
+QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}$. By Lemma~\ref{lemma:delta2zero},
 we can construct a 0-deterministic QIVPM; however, by Thm.~\ref{thm:Kochen-Specker},
@@
 The bound $\delta<\frac{1}{3}$ is tight as it is possible to construct
-a $\frac{1}{3}$-deterministic QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$.
+a $\frac{1}{3}$-deterministic QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$.
 For example, $\bar{\mu}_{2}'$ defined in Table~\ref{tab:probability-measures}
@@
 \begin{thm}[$\mathscr{I}_{\infty}$ Variant of the Gleason Theorem]\label{cor:Gleason's-1}In
-a Hilbert space $\Hilb$ of dimension $D\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
+a Hilbert space $\Hilb$ of dimension $D\geq3$, given a QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}_{\infty}$,
 the state $\rho$ consistent with~$\bar{\mu}$ on every projector
@@
 \begin{lemma}\label{thm:convex-3}Given a Hilbert space~$\Hilb$
-of dimension~$3$, to verify $\bar{\mu}:\events\rightarrow\mathscr{I}$
+of dimension~$3$, to verify $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
 is a QIVPM, it is sufficient to check Eqs.~(\ref{eq:QIVPM-constraints})
@@
 be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
-Consider the function $\varphi:2^{\Omega}\rightarrow\events$ defined
-in Eq.~(\ref{eq:pullback-function}), there are two set of basis
-vectors $E_{0}$ and $E_{1}\subseteq\Omega$, such that $\varphi\left(E_{0}\right)=P_{0}$
+Consider the function $\varphi\colon2^{\Omega}\rightarrow\events$
+defined in Eq.~(\ref{eq:pullback-function}), there are two set of
+basis vectors $E_{0}$ and $E_{1}\subseteq\Omega$, such that $\varphi\left(E_{0}\right)=P_{0}$
 and $\varphi\left(E_{1}\right)=P_{1}$. Since $E_{0}$ and $E_{1}$
@@
 \begin{lemma}\label{thm:convex-3-1}Given a Hilbert space~$\Hilb$
-of dimension~$3$, to verify $\bar{\mu}:\events\rightarrow\mathscr{I}$
+of dimension~$3$, to verify $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
 is a QIVPM, it is sufficient to check Eqs.~(\ref{eq:QIVPM-constraints})
@@
 \begin{thm}[Empty Cores Exist for General QIVPMs]\label{thm:Non-extensible-of-Gleason's}There
-exists a Hilbert space $\Hilb$ and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
+exists a Hilbert space $\Hilb$ and a QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}$
 such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
@@
 \end{equation}
-Consider the map $\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
-in Table~\ref{tab:non-Born-QIVPM}. We want to prove $\bar{\mu}$
+Consider the map $\bar{\mu}\colon\events\rightarrow\mathscr{I}_{0}$
+defined in Table~\ref{tab:non-Born-QIVPM}. We want to prove $\bar{\mu}$
 is a QIVPM\@. Since it is easy to verify $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}),
@@
 \begin{table}
-\noindent \centering{}\caption{\label{tab:non-Born-QIVPM}QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
+\noindent \centering{}\caption{\label{tab:non-Born-QIVPM}QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}_{0}$
 on a Hilbert space of dimension~$D=3$. Events are listed in the
@@
 we can use to construct a consistent family of QIVPMs. An interval
-map $f:\left[0,1\right]\rightarrow\mathscr{I}$ maps every real-valued
+map $f\colon\left[0,1\right]\rightarrow\mathscr{I}$ maps every real-valued
 probability $x\in\left[0,1\right]$ to a set of intervals $f\left(x\right)=\left[\ell,r\right]$
@@
 \begin{thm}[Finite-Precision Extension of the Gleason Theorem]\label{thm:Finite-precision-Gleason}Let
-$f:\left[0,1\right]\rightarrow\mathscr{I}$ be an interval map and
-let the composition $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$
+$f\colon\left[0,1\right]\rightarrow\mathscr{I}$ be an interval map
+and let the composition $f\circ\muB_{\rho}$ be a QIVPM, where $\muB_{\rho}$
 is the probability measure induced by the Born rule for a given state~$\rho$.
@@
 a collection of intervals $\mathscr{I}$ including $\imposs$ and
-$\necess$, an interval map $\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
+$\necess$, an interval map $\ultramodular\colon\left[0,1\right]\rightarrow\mathscr{I}$
 is called ultramodular if: 
@@
 
-\item\label{enu:iota-subject-to}A function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$
+\item\label{enu:iota-subject-to}A function~$\ultramodular\colon\left[0,1\right]\rightarrow\mathscr{I}$
 is ultramodular.
 
-\item\label{enu:iota-mu-CIVPM}The composite function $\ultramodular\circ\mu:2^{\Omega}\rightarrow\mathscr{I}$
-is a classical IVPM for all classical probability measures $\mu:2^{\Omega}\rightarrow\left[0,1\right]$.
-
-\item\label{enu:iota-mu-QIVPM}The composite function $\ultramodular\circ\mu:\events\rightarrow\mathscr{I}$
-is a QIVPM for all quantum probability measures $\mu:\events\rightarrow\left[0,1\right]$.
+\item\label{enu:iota-mu-CIVPM}The composite function $\ultramodular\circ\mu\colon2^{\Omega}\rightarrow\mathscr{I}$
+is a classical IVPM for all classical probability measures $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$.
+
+\item\label{enu:iota-mu-QIVPM}The composite function $\ultramodular\circ\mu\colon\events\rightarrow\mathscr{I}$
+is a QIVPM for all quantum probability measures $\mu\colon\events\rightarrow\left[0,1\right]$.
 \end{enumerate} \end{thm}
@@
 For the classical case, if $\ultramodular$ is not ultramodular, we
-also want to find a classical probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
+also want to find a classical probability measure $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
 such that $\ultramodular\circ\mu$ is not a classical IVPM\@. Consider
 an orthonormal basis $\Omega$ containing $\ket{0}$, $\ket{1}$,
-$\ket{2}$, $\ket{3}$, \ldots , and $\ket{D-1}$, and $\varphi:2^{\Omega}\rightarrow\events$
+$\ket{2}$, $\ket{3}$, \ldots , and $\ket{D-1}$, and $\varphi\colon2^{\Omega}\rightarrow\events$
 defined by Eq.~(\ref{eq:pullback-function}). Notice that the pullback
@@
 \begin{thm}[Range of Ultramodular Functions]\label{thm:convex-uncountable}For
-any ultramodular function~$\ultramodular:\left[0,1\right]\rightarrow\mathscr{I}$,
+any ultramodular function~$\ultramodular\colon\left[0,1\right]\rightarrow\mathscr{I}$,
 either $\mathscr{I}=\mathscr{I}_{0}$ as defined in Eq.~(\ref{eq:3-value-intervals})
@@
 it into two functions: its left-end and right-end, where $\left[\ultramodularL\left(x\right),\ultramodularR\left(x\right)\right]=\ultramodular\left(x\right)$.
-By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\ultramodularL:\left[0,1\right]\rightarrow\left[0,1\right]$
+By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\ultramodularL\colon\left[0,1\right]\rightarrow\left[0,1\right]$
 is Wright-convex~\cite{Wright1954,RobertsVarberg1973,PecaricTong1992},
@@
 space $\Hilb$ of dimension $D\geq3$, is there an $\varepsilon>0$
-such that for all QIVPM $\bar{\mu}:\events\rightarrow\mathscr{I}$
+such that for all QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
 satisfying $\left\Vert \mathscr{I}\right\Vert \le\varepsilon$, $\bar{\mu}$
@@
 Therefore, to study a QIVPM~$\bar{\mu}$, we can just study a pair
-of functions $\frameL:\CP{2}\rightarrow\left[0,1\right]$ and $\frameR:\CP{2}\rightarrow\left[0,1\right]$
-defined by $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]=\bar{\mu}\left(\proj{\psi}\right)$
+of functions $\frameL\colon\CP{2}\rightarrow\left[0,1\right]$ and
+$\frameR\colon\CP{2}\rightarrow\left[0,1\right]$ defined by $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]=\bar{\mu}\left(\proj{\psi}\right)$
 for any irreducible state $\ket{\psi}\in\CP{2}$. According to Lemma~\ref{thm:convex-3-1},
-$\bar{\mu}:\events\rightarrow\mathscr{I}$ is a QIVPM if and only
-if $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}) and
+$\bar{\mu}\colon\events\rightarrow\mathscr{I}$ is a QIVPM if and
+only if $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints})
+and
 \begin{equation}
@@
 In this language, Gleason's theorem basically states that when $\varepsilon=0$,
-given any function $\frameL:\CP{2}\rightarrow\left[0,1\right]$ satisfying
-Eq.~(\ref{eq:left-end-frame-function}), there exists a unique mixed
-state~$\rho$ such that 
+given any function $\frameL\colon\CP{2}\rightarrow\left[0,1\right]$
+satisfying Eq.~(\ref{eq:left-end-frame-function}), there exists
+a unique mixed state~$\rho$ such that 
 \begin{equation}
@@
 a collection of intervals~$\mathscr{I}$. A quantum interval-valued
-probability measure over finite field $\bar{\mu}:\events_{p^{2}}\rightarrow\mathscr{I}$
+probability measure over finite field $\bar{\mu}\colon\events_{p^{2}}\rightarrow\mathscr{I}$
 assigns an interval to each event~$P$ subject to $\bar{\mu}(\mathbb{0})=\imposs$,

### 2019-01-22 dissertation.tex
dissertation.lyx Updated according to the suggestion from "Online Grammar Checker for TeX files" (http://mccabedj.ucc.asn.au/checktex.html)...

@@
 \par\end{centering}
-}\hfill{} \label{hopfFibers.fig}\caption{(a) The two-sphere~$\Sphere{2}$ represented by \Eq{A7.eq}, which
+}\hfill{}\label{hopfFibers.fig}\caption{(a) The two-sphere~$\Sphere{2}$ represented by \Eq{A7.eq}, which
 is the irreducible space of one-qubit states, along with a representative
@@
 
-\subsection{Gleason's Theorem and The Born Rule\label{subsec:Gleason's-Theorem-and}}
+\subsection{Gleason's Theorem and the Born Rule\label{subsec:Gleason's-Theorem-and}}
 
@@
 not have square roots in the field. What is interesting is that if
-we have an uninterrupted sequence of numbers that are all quadratic
+we have a uninterrupted sequence of numbers that are all quadratic
 residues, then we can define a \textit{transitive order}, with $a>c$
@@
 further constrain the underlying prime numbers to be of the form $8\prod_{i=1}^{m}q_{i}-1$,
-where $q_{i}$ is the $i$th odd prime. While all such primes are
+where $q_{i}$ is the $i$-th odd prime. While all such primes are
 of the form $4\ell+3$, the set is severely restricted to astronomical
 numbers because the first few such primes are $7$, $23$, $839$,
-$9239$, $2042039$, \ldots}. The $n$th element of that sequence (which must be prime) is the
-least number such that the $n$th prime is the \emph{least} quadratic
+$9239$, $2042039$, \ldots}. The $n$-th element of that sequence (which must be prime) is the
+least number such that the $n$-th prime is the \emph{least} quadratic
 non-residue for the given element. The first few elements of this
@@
 in the range of $k$. Assume that $k$ is the least prime satisfying
-$k\geq2^{3n+2}+1$, and let $p$ be the $\pi\left(k\right)$th element
+$k\geq2^{3n+2}+1$, and let $p$ be the $\pi\left(k\right)$-th element
 of the sequence A000229~\cite{Sloane2005}. We argue that no prime
@@
 using $k\geq8\left(\frac{N}{2}\right)^{2j+2}+1$. We can then pick
-a prime $k$, and choose the $\pi\left(k\right)$th prime in the sequence
-represented by Table~\ref{pseq} guaranteeing that every number we
-need for the computation is within the transitively ordered range
-$F^{D}\left(k\right)$.
+a prime $k$, and choose the $\pi\left(k\right)$-th prime in the
+sequence represented by Table~\ref{pseq} guaranteeing that every
+number we need for the computation is within the transitively ordered
+range $F^{D}\left(k\right)$.
 
@@
 pick $k=32771$ and $\pi\left(32771\right)=3513$, and so if we use
-the $3513$th prime, we can implement Grover's algorithm for a database
+the $3513$-th prime, we can implement Grover's algorithm for a database
 of size $8$.

### 2019-01-22 dissertation.tex
dissertation.lyx "Chapter 6 Further Discussion" and CV Updated...

@@
 whether there is a short enough length~$\varepsilon$ such that QIVPMs
-mapping to intervals shorter than $\varepsilon$ always have non-empty
+mapping to intervals bounded by $\varepsilon$ always have non-empty
 cores.
@@
 \begin{eqnarray}
- &  & \frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)\le1-\frameL\left(\ket{\psi_{0}}\right)\le\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)+2\varepsilon\,.\\
+ &  & \frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)\le1-\frameL\left(\ket{\psi_{0}}\right)\le\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)+2\varepsilon\\
  & \Leftrightarrow & 1-2\varepsilon\le\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)\le1\,.\label{eq:left-end-frame-function}
@@
 for any state $\ket{\psi}\in\CP{2}$. Our Question~\ref{question:approximation-Gleason}
-then ask what $\frameL$ would look like with a positive $\varepsilon$.
+then ask how $\frameL$ would look like with a positive $\varepsilon$.
 
@@
 probability space is glued by a family of classical probability spaces.
-This is like the situation that a manifold is glued by many local
-coordinates. When each small piece has \emph{exactly} the same and
-positive curvature, the Killing-Hopf theorem asserts this manifold
-is a sphere, but little can we say even if the curvature has an only
-small deviation from constant. A similar situation might happen when
-approximating Gleason's theorem, but this time the whole space is
-glued by ``local'' classical probability space defined by each orthonormal
-basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$. When the sum of
-$\frameL$, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$, is
-\emph{exactly} the same and equal to $1$, Gleason's theorem asserts
+\todo{Check the differential geometry analog with Andy, since I don't
+really understand the differential geometry\ldots{} }This is like
+the situation that a manifold is glued by many local coordinates.
+When each small piece has \emph{exactly} the same and positive curvature,
+the Killing-Hopf theorem asserts this manifold is a sphere, but little
+can we say even if the curvature has a small deviation from constant.
+A similar situation might happen when approximating Gleason's theorem,
+but this time the whole space is glued by ``local'' classical probability
+space defined by each orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
+When the sum of $\frameL$, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$,
+is \emph{exactly} the same and equal to $1$, Gleason's theorem asserts
 that $\frameL$ can be expressed as Eq.~(\ref{eq:Gleason-for-CP2}).
@@
 model. Since the conventional quantum circuit model manipulates the
-probability amplitudes instead of the measured probability, a quantum
-computing model above QIVPMs might either need to manipulate the states
-in the core of a QIVPM or find a way to manipulate QIVPMs directly.
-However, both strategies are not straightforward. On one hand, a QIVPM
-might have an empty core which cannot be evolved over time as we proved
-in Thm.~\ref{thm:Non-extensible-of-Gleason's}. On the other hand,
-if we want to manipulate and compute QIVPMs directly for multi-qubit
-algorithms, we need to glue the QIVPM for each qubit or subsystem
-together to get the QIVPM of the whole system, and this is not straightforward
-either.
+probability amplitudes instead of the measured probability, either
+a quantum computing model above QIVPMs needs to manipulate the states
+in the core of a QIVPM, or we need to find a way to manipulate QIVPMs
+directly. However, both strategies are not straightforward. On one
+hand, as we proved in Thm.~\ref{thm:Non-extensible-of-Gleason's},
+a QIVPM might have an empty core which cannot be evolved over time.
+On the other hand, if we want to manipulate and compute QIVPMs directly
+for multi-qubit algorithms, we need to glue the QIVPM for each qubit
+or subsystem together to get the QIVPM of the whole system, and this
+is not straightforward either.
 
@@
 $\bar{\mu}(\mathbb{1})=\necess$, $\bar{\mu}\left(\mathbb{1}-P\right)=\necess-\bar{\mu}\left(P\right)$,
-and satisfying for each pair of \emph{commuting} projectors~$P_{0}$
+and satisfying for each pair of \emph{commuting} events~$P_{0}$
 and~$P_{1}$ with $P_{0}P_{1}=P_{1}P_{0}$, 

### 2019-01-25 dissertation.tex
dissertation.lyx "Chapter 6 Further Discussion", "Chapter 1 Introduction", and Acknowledgments Updating...

@@
 
-\begin{acknowledgments*}\todo{Confirm people to be acknowledged
-like the way being acknowledged\ldots{} }I want to thank Prof.~Gerardo
-Ortiz, Prof.~Amr Sabry (\textarabic{عمرو صبري}), and Prof.~Andrew
-Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
+\chapter*{Survey of the acknowledgments in theses}
+
+I found the sentences in my Acknowledgments almost always contains
+“thank”, and looks boring. To improve my Acknowledgments, I
+briefly read the Acknowledgments in other theses \cite{Chih2013,Sun2015,Lee2013}.
+
+\begin{acknowledgments*}
+
+\todo{Confirm people to be acknowledged like the way being acknowledged\ldots{}
+}I want to thank Prof.~Gerardo Ortiz, Prof.~Amr Sabry (\textarabic{عمرو صبري}),
+and Prof.~Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
 with me, and enormous other things. These papers become the main part
@@
 is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
-and ``Discrete quantum theories'' (DQT)~\cite{DQT2014}; most of
-Chapter~\ref{chap:QIVPM} is based on ``Quantum Interval-Valued
-Probability: Contextuality and the Born Rule'' (QIVPM)~\cite{THOS2018}.
-Together with Prof.~Dylan Thurston and Prof.~Shouhong Wang (汪守宏),
-I want to thank you for getting together to understand what I did
-and passing my dissertation proposal Spring 2017. I also thank Prof.\ Dylan
-Thurston for serving in my advisory committee and my Tier 3 committee,
-with other advisory committee members passing my Computer Science
-qualifying exam in Spring 2016. Especially, my survey of real computation
-in the qualifying exam inspired me the comparison of quantum computer
-and analog computer in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
+and ``Discrete quantum theories''~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
+is based on ``Quantum Interval-Valued Probability: Contextuality
+and the Born Rule''~\cite{THOS2018}. Together with Prof.~Dylan
+Thurston and Prof.~Shouhong Wang (汪守宏), I want to thank you for getting
+together to understand what I did and passing my dissertation proposal
+Spring 2017 and defense Fall 2018. Also thank Prof.\ Dylan Thurston
+for serving in my advisory committee and my Tier 3 committee, with
+other advisory committee members passing my Computer Science qualifying
+exam Spring 2016. Especially, my survey of real computation in the
+qualifying exam inspired me the comparison of quantum computer and
+analog computer in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
 also contains the motivation in my application for Rethinking Foundations
@@
 in Computer Science, co-chairing my Tier 3 committee, writing an assessment
-letter for me, and drawing my attention on Prof.~Abramsky's paper~\cite{Abramsky2012},
+letter for me, and drawing my attention on Prof.\ Abramsky's paper~\cite{Abramsky2012},
 which inspired me to merge quantum probability with discrete quantum
@@
 
-Since a human cannot distinguish quantities differing only by an arbitrarily
-small extent \cite{Turing_1937,Gisin2017}, we want to incorporate
-this limitation into our quantum mechanical model to better capture
-our ability to predict quantum phenomenon and the power of realistic
-quantum computers. Since we are agnostic about whether the reality
-is ultimately discrete or continuous, we considered two types of quantum
-models. By assuming the quantum states are ultimately discrete and
-distinguishable, our first type of quantum theories replaces the complex
-numbers by finite fields. We then focus on the limitation of distinguishability
-itself, incorporate the finite precision measurement into our model,
-and consider quantum interval-valued probability measures.
+Since no human being can distinguish quantities differing only by
+an arbitrarily small extent \cite{Turing_1937,Gisin2017}, we want
+to incorporate this limitation into our quantum mechanical model to
+better capture our ability to predict quantum phenomenon and the power
+of realistic quantum computers. Since we are agnostic about whether
+the reality is ultimately discrete or continuous, we consider two
+types of quantum models. By assuming the quantum states are ultimately
+discrete and distinguishable, our first type of quantum theories replaces
+the complex numbers by finite fields. We then focus on the limitation
+of distinguishability itself, incorporate the finite precision measurement
+into our model, and consider quantum interval-valued probability measures.
 
@@
 identifying which real number represents its length requires infinite
-precision, but the precision, in reality, is limited generally three
+precision, but the precision in reality is limited generally three
 or four significant figures~\cite{wiki:AnalogComputer}. As the results,
@@
 to be compensated by error analysis techniques easily like the butterfly
-effect. Therefore, the computational power of analog computers might
-be far weaker than the prediction based on this kind of theoretical
-models.%
+effect. Therefore, it is is unlikely to utilize the realistic analog
+computers to achieve the computational power predicted by this kind
+of theoretical models.%
 \begin{comment}
@@
 \addlinespace
-How does the theorical model predict the behavior of the Physical device? & 
+How does the theorical model predict the behavior of the physical device? & 
 Reliably & 
-Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computational power by a better discrete model. & 
+Not reliably, but after we have better technology to manipulate the minimum units, we can more reliably predict the physical phenomenon and their computational power by a better discrete model. & 
 Not reliably, because precision can never be high enough, and the difference between their computational power might not be able compensated by error analysis techniques. \tabularnewline\addlinespace
@@
 which are not discrete apparently: the probability amplitudes of quantum
-states. To address the similar inconsistency, we first review the
-``conventional quantum theory'' (CQT)\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
-and ``ordinary'' quantum theory.}, where the probability amplitudes are in the field of complex numbers.
-If the probability amplitudes are assumed to be ultimately discrete,
+states, which are assumed in the field of complex numbers in the ``conventional
+quantum theory'' (CQT)\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+and ``ordinary'' quantum theory.}. If the probability amplitudes are assumed to be ultimately discrete,
 we choose to replace the field of complex numbers by discrete finite
@@
 whether a measurement result is possible or impossible, but not its
-probability. Although a version of a quantum theory defined over the
+probability. Although a version of quantum theory defined over the
 two-valued field can express simple algorithms such as quantum teleportation
@@
 $\Fpp$, with the prime $p$ of the form $4\ell+3$ ($\ell$ a non-negative
-integer), the complex numbers have extremely compelling and natural
+integer), the complex numbers then have extremely compelling and natural
 discrete analogs that preserve a great many of the standard requirements
-of quantum computing. In this model, the state of a discrete $d$-dimensional
-system is a vector in the $d$-dimensional vector space over $\Fpp$
+of quantum computing. In this model, the state of a discrete $D$-dimensional
+system is a vector in the $D$-dimensional vector space over $\Fpp$
 and can be reduced to a point in the discrete complex projective space.
@@
 could not only be identified as in CQT but also be counted for different
-$p$. Despite this model's similarity to CQT, it still only predicts
-whether a measurement result is possible or impossible because it
-is not possible to define an inner product in the usual sense due
-to the modular arithmetic~\cite{grove2002classical}. Under suitable
-conditions, we can have deterministic quantum algorithms such as the
-algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
+$p$. Despite the similarity between this model and CQT, it still
+only predicts whether a measurement result is possible or impossible
+because it is not possible to define an inner product in the usual
+sense due to the modular arithmetic~\cite{grove2002classical}. Under
+suitable conditions, we can have deterministic quantum algorithms
+such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
 and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
@@
 extend classical IVPMs to QIVPMs. In Sec.~\ref{sec:Kochen-Specker},
-we utilize the previously defined expectation values while proving
-the finite precision variants of the Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
+we utilize the expectation values while proving the finite precision
+variants of the Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
 and establish bounds on its validity in realistic experimental environments.
@@
 with Gleason's unique state~$\rho$ on all projectors defined on
-a Hilbert space~$\Hilb$ of dimension $d\ge3$, there is a mathematically
-precise sense in which one recovers the original Gleason theorem asymptotically.
-Specifically, it is possible to construct a class of QIVPMs representing
-bounded resources that is parameterized by the size of the intervals.
-We then demonstrate that all QIVPMs in this class are consistent with
-a non-empty “ball” of quantum states whose radius is defined
-by the maximal length of the intervals characterizing the uncertainties.
-As the size of the intervals goes to zero, this ball of quantum states
-converges to a point representing the unique state consistent with
-the Born rule and Gleason's theorem.
+a Hilbert space~$\Hilb$ of dimension $D\ge3$, it is possible to
+construct a class of QIVPMs representing bounded resources that is
+parameterized by the size of the intervals, and the original Gleason
+theorem could be recovered for this class of QIVPMs asymptotically.
 
@@
 and finally, Chapter~\ref{chap:Further-Discussion} contains further
-extended questions.
+extended questions, especially, briefly explaining why it might be
+hard to recover Gleason's theorem for general QIVPMs.
 
@@
 whether there is a short enough length~$\varepsilon$ such that QIVPMs
-mapping to intervals bounded by $\varepsilon$ always have non-empty
+mapping to intervals not longer than $\varepsilon$ always have non-empty
 cores.
@@
 model. Since the conventional quantum circuit model manipulates the
-probability amplitudes instead of the measured probability, either
-a quantum computing model above QIVPMs needs to manipulate the states
-in the core of a QIVPM, or we need to find a way to manipulate QIVPMs
-directly. However, both strategies are not straightforward. On one
-hand, as we proved in Thm.~\ref{thm:Non-extensible-of-Gleason's},
+probability amplitudes instead of the measured probabilities, either
+a quantum computing model above QIVPMs needs to simultaneously manipulate
+all states in the core of a QIVPM, or we need to find a way to manipulate
+a QIVPM directly. However, both strategies are not straightforward.
+On one hand, as we proved in Thm.~\ref{thm:Non-extensible-of-Gleason's},
 a QIVPM might have an empty core which cannot be evolved over time.
@@
 A successful interval-valued theory might be further extended to the
-quantum theory over finite fields as follow.
+quantum theory over finite fields based on the following definition.
 

### 2019-01-25 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" and Acknowledgments Updating...

@@
 
+\begin{comment}
+
 \chapter*{Survey of the acknowledgments in theses}
@@
 “thank”, and looks boring. To improve my Acknowledgments, I
-briefly read the Acknowledgments in other theses \cite{Chih2013,Sun2015,Lee2013}.
-
-\begin{acknowledgments*}
-
+briefly read the Acknowledgments in other theses \cite{Chih2013,Sun2015,Lee2013,Chen2016,sabry1995formal}.
+\end{comment}
+\begin{acknowledgments*}%
+\begin{comment}
 \todo{Confirm people to be acknowledged like the way being acknowledged\ldots{}
-}I want to thank Prof.~Gerardo Ortiz, Prof.~Amr Sabry (\textarabic{عمرو صبري}),
+}
+\end{comment}
+I want to thank Prof.~Gerardo Ortiz, Prof.~Amr Sabry (\textarabic{عمرو صبري}),
 and Prof.~Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
@@
 and the Born Rule''~\cite{THOS2018}. Together with Prof.~Dylan
-Thurston and Prof.~Shouhong Wang (汪守宏), I want to thank you for getting
-together to understand what I did and passing my dissertation proposal
-Spring 2017 and defense Fall 2018. Also thank Prof.\ Dylan Thurston
-for serving in my advisory committee and my Tier 3 committee, with
-other advisory committee members passing my Computer Science qualifying
-exam Spring 2016. Especially, my survey of real computation in the
-qualifying exam inspired me the comparison of quantum computer and
-analog computer in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
+Thurston and Prof.~Shouhong Wang (汪守宏), they getting together to
+understand my dissertation proposal and dissertation, and all the
+suggestions are extremely helpful, where the proposal provides the
+framework of the dissertation. Some proposed questions are solved
+in Chapter~\ref{chap:QIVPM}, and some of the remaining questions
+is explained in Chapter~\ref{chap:Further-Discussion}. \todo{Acknowledgments
+cleaned up until here. }Also thank Prof.\ Dylan Thurston for serving
+in my advisory committee and my Tier 3 committee, with other advisory
+committee members passing my Computer Science qualifying exam Spring
+2016. Especially, my survey of real computation in the qualifying
+exam inspired me the comparison of quantum computer and analog computer
+in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
 also contains the motivation in my application for Rethinking Foundations
@@
 to be compensated by error analysis techniques easily like the butterfly
-effect. Therefore, it is is unlikely to utilize the realistic analog
-computers to achieve the computational power predicted by this kind
+effect. Therefore, we might not be able to utilize the realistic analog
+computers to acquire the computational power predicted by this kind
 of theoretical models.%
@@
 ``imprecise probabilities'' has well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+\begin{comment}
 \todo{Make sure whether realistic quantum computers could branch
@@
 it will provide another reason why we want to study the precision
-of the inducing probabilities\ldots{} }This idea will be extended
-to the quantum domain as quantum interval-valued probability measures
-(QIVPM).
+of the inducing probabilities\ldots{} }
+\end{comment}
+This idea will be extended to the quantum domain as quantum interval-valued
+probability measures (QIVPM).
 

### 2019-01-25 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" and Acknowledgments Updating...

@@
 with me, and enormous other things. These papers become the main part
-of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
+of my thesis, especially most of Chapter~\ref{chap:Conventional-Quantum-Theory},
+\ref{chap:Unrestricted-Finite-Fields}, and~\ref{chap:DQT=000026DQC}
 is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
@@
 and the Born Rule''~\cite{THOS2018}. Together with Prof.~Dylan
-Thurston and Prof.~Shouhong Wang (汪守宏), they getting together to
-understand my dissertation proposal and dissertation, and all the
-suggestions are extremely helpful, where the proposal provides the
-framework of the dissertation. Some proposed questions are solved
-in Chapter~\ref{chap:QIVPM}, and some of the remaining questions
-is explained in Chapter~\ref{chap:Further-Discussion}. \todo{Acknowledgments
-cleaned up until here. }Also thank Prof.\ Dylan Thurston for serving
-in my advisory committee and my Tier 3 committee, with other advisory
-committee members passing my Computer Science qualifying exam Spring
-2016. Especially, my survey of real computation in the qualifying
-exam inspired me the comparison of quantum computer and analog computer
-in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
-also contains the motivation in my application for Rethinking Foundations
-of Physics 2017 workshop reviewed by Prof.\ Amr Sabry~(\textarabic{عمرو صبري}).
-I want to thank Prof.\ Lawrence Moss for inviting me to present our
+Thurston and Prof.~Shouhong Wang (汪守宏), you provide helpful suggestions
+for my dissertation proposal and dissertation itself, where the proposal
+provides the framework of the dissertation. Some proposed questions
+are solved in Chapter~\ref{chap:QIVPM}, and some of the remaining
+questions are explained in Chapter~\ref{chap:Further-Discussion}.
+While being completely rewritten, the idea of Chapter~\ref{chap:Introduction}
+comes from my application for Rethinking Foundations of Physics 2017
+workshop reviewed by Prof.\ Amr Sabry~(\textarabic{عمرو صبري})
+and my survey of real computation in my Computer Science qualifying
+exam with my advisory committee, Prof.~Amr Sabry(\textarabic{عمرو صبري}),
+Prof.~Gerardo Ortiz, and Prof.~Andrew Hanson, and Prof.\ Dylan
+Thurston. My study for Tier 3 exam, which is part of the qualifying
+exam for Mathematics, is also helpful when I start to export the work
+of quantum computing, and \todo{Acknowledgments cleaned up until
+here. }Also thank Prof.\ Dylan Thurston for serving in my advisory
+committee and my Tier 3 committee, with other advisory committee members
+passing my Computer Science qualifying exam Spring 2016. Especially,
+my survey of real computation in the qualifying exam inspired me the
+comparison of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
+Chapter~\ref{chap:Introduction} also contains the motivation in
+my application for Rethinking Foundations of Physics 2017 workshop
+reviewed by Prof.\ Amr Sabry~(\textarabic{عمرو صبري}). I
+want to thank Prof.\ Lawrence Moss for inviting me to present our
 results in the interdisciplinary logic seminar and theory seminar
@@
 to be compensated by error analysis techniques easily like the butterfly
-effect. Therefore, we might not be able to utilize the realistic analog
-computers to acquire the computational power predicted by this kind
+effect. Therefore, we might not be able to utilize a realistic analog
+computer to acquire the computational power predicted by this kind
 of theoretical models.%
@@
 \end{comment}
-This idea will be extended to the quantum domain as quantum interval-valued
+This idea will be extended to quantum domain as quantum interval-valued
 probability measures (QIVPM).

### 2019-01-26 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" and Acknowledgments Updating...

--- 2019-01-25 dissertation.tex
@@
 \usepackage{tabularx}
+\renewcommand{\tabularxcolumn}[1]{m{#1}}
 \newcolumntype{Y}{>{\centering\doublespacing\arraybackslash}X}
+\newcolumntype{M}[1]{>{\centering\doublespacing\arraybackslash}m{\widthof{#1}}}
 
@@
 “thank”, and looks boring. To improve my Acknowledgments, I
-briefly read the Acknowledgments in other theses \cite{Chih2013,Sun2015,Lee2013}.
-
+briefly read the Acknowledgments in other theses \cite{Chih2013,Sun2015,Lee2013,Chen2016,sabry1995formal}.
+\end{comment}
 \begin{acknowledgments*}
-
-\todo{Confirm people to be acknowledged like the way being acknowledged\ldots{}
-}I want to thank Prof.~Gerardo Ortiz, Prof.~Amr Sabry (\textarabic{عمرو صبري}),
-and Prof.~Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
-with me, and enormous other things. These papers become the main part
-of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
-is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
-and ``Discrete quantum theories''~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
-is based on ``Quantum Interval-Valued Probability: Contextuality
-and the Born Rule''~\cite{THOS2018}. Together with Prof.~Dylan
-Thurston and Prof.~Shouhong Wang (汪守宏), I want to thank you for getting
-together to understand what I did and passing my dissertation proposal
-Spring 2017 and defense Fall 2018. Also thank Prof.\ Dylan Thurston
-for serving in my advisory committee and my Tier 3 committee, with
-other advisory committee members passing my Computer Science qualifying
-exam Spring 2016. Especially, my survey of real computation in the
-qualifying exam inspired me the comparison of quantum computer and
-analog computer in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
-also contains the motivation in my application for Rethinking Foundations
-of Physics 2017 workshop reviewed by Prof.\ Amr Sabry~(\textarabic{عمرو صبري}).
-I want to thank Prof.\ Lawrence Moss for inviting me to present our
-results in the interdisciplinary logic seminar and theory seminar
-in Computer Science, co-chairing my Tier 3 committee, writing an assessment
-letter for me, and drawing my attention on Prof.\ Abramsky's paper~\cite{Abramsky2012},
-which inspired me to merge quantum probability with discrete quantum
-theories. And I thank John Gardiner for inspiring discussion on the
-difficulties merging them~\cite{Gardiner2014}. These results are
-improved and motivated the transition from DQT to QIVPM in Sec.~\ref{sec:Toward-IVPM}.
-I also thank Prof.~Tom Lewis for helping me organize the unpublished
-deterministic quantum algorithms in the term paper for SLST-T501 Academic
-Writing course as presented in Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
-I also thank Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin
-``Casey'' Chen (谌可心) for teaching me English in general so that
-others can understand me more easily.
-
-\todo{Type a table for acknowledgment so that I would have to write
-``I thank'' so many times here? }Many people in both departments
-of Mathematics and Computer Science need to do something more to make
-my double-major works smoothly. I need to thank all of them, especially
-directors of graduate study in Mathematics, especially Prof.\ Christopher
-Judge and Prof.\ Matthias Weber; directors of Ph.D. study in Computer
-Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
-Ergun}.
-
-Thank Kin Wai Chan for suggesting me the correct direction for Proposition~\ref{appH.sec},
-Prof.\ 朱樺 for drawing my attention on Prof.\ Wan's book~\cite{Wan2006},
-and Weihua Liu (刘伟华) for remaining me analysts call the right side
-of the IVPM outer measure.
+\begin{sidewaystable}
+\noindent \begin{centering}
+\caption{\label{tab:acknowledgments}I want to thank the professors co-authored
+with me, suggested me as a committee member, and taught me, and the
+collaboration or supervised works or studies become the basis of or
+inspire this dissertation.}
+\par\end{centering}
+\noindent \centering{}\noindent \centering{}%
+\begin{tabularx}{\linewidth}{M{MATH-M781}M{Co-author}M{(\textarabic{عمرو صبري})}M{Co-author}M{Thurston}M{Shouhong}M{Lawrence}Y}
+\toprule 
+\addlinespace
+Committee or course & Gerardo Ortiz & Amr\nolinebreak[3] A.
+Sabry\linebreak[3] (\textarabic{عمرو صبري}) & Andrew\nolinebreak[3] J.
+Hanson & Dylan\nolinebreak[3] Paul Thurston & Shouhong Wang\linebreak[3] (汪守宏) & Lawrence\nolinebreak[3] S.\linebreak[2] Moss & Relation with the dissertation\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\midrule 
+\addlinespace
+ & Co-author & Co-author & Co-author &  &  &  & Most of Chapters~\ref{chap:Conventional-Quantum-Theory}, \ref{chap:Unrestricted-Finite-Fields},
+and~\ref{chap:DQT=000026DQC} is based on \cite{geometry2013} and \cite{DQT2014}; most of Chapter~\ref{chap:QIVPM} is
+based on \cite{THOS2018}.\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Research committee & Co-chair & Co-chair & Member & Co-chair & Member &  & Some questions in the dissertation proposal are answered in Chapter~\ref{chap:QIVPM},
+and some of the remaining ones are explained in Chapter~\ref{chap:Further-Discussion}.\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+ &  & Suggested &  &  &  &  & The application for Rethinking Foundations of Physics 2017 workshop
+inspires Chapter~\ref{chap:Introduction}.\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Advisory committee & Member & Member & Member & Member &  &  & The survey of real computation in the Computer Science qualifying
+exam (chaired by Prof.\ Sabry) inspires Chapter~\ref{chap:Introduction}.\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+PHYS-P700 & Instructor &  &  &  &  &  & The textbook~\cite{Mermin2007} is
+cited in Chapters~\ref{chap:Introduction}, \ref{chap:Conventional-Quantum-Theory},
+\ref{chap:DQT=000026DQC}, and~\ref{chap:QIVPM}.\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+MATH-M781 &  &  &  &  &  & Instructor & The presented paper~\cite{Abramsky2012} is cited in Sec.~\ref{subsec:Classical-and-Quantum}.\tabularnewline\addlinespace
+\addlinespace
+\midrule
+\addlinespace
+Tier 3 committee & Co-chair & Co-chair &  & Member &  & Co-chair & Two of
+the assigned papers in the Tier 3 exam, \cite{Schumacher2012-SCHMQT}
+and \cite{doi:10.1142/S0217984913500644},
+are cited in Sec.~\ref{modalquantum}.\tabularnewline\addlinespace
+\addlinespace
+\bottomrule
+\end{tabularx}
+\end{sidewaystable}
+I want to thanks all my professors co-authored with me, suggested
+me as a committee members, and taught me which become the bases or
+inspired any part of my dissertation as listed in Table~\ref{tab:acknowledgments}.
+Especially, Prof.\ Gerardo Ortiz, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري}),
+and Prof.\ Andrew J. Hanson meet me weekly for the pass few years,
+read and tried to understand what I typed which sometimes even myself
+cannot understand, taught me how to organize them in ``English''
+so that general audience might be interested and have some chance
+to understand, and encourage me to participate seminars, workshops,
+and conferences. Prof.\ Lawrence Moss invited me to present our results
+in the interdisciplinary logic seminar and theory seminar in Computer
+Science and wrote an assessment letter for me. Although not directly
+related to this dissertation, the knot theory studied with Prof.\ Dylan
+Paul Thurston and the quantum interpretation discussed with Prof.\ Shouhong
+Wang (汪守宏) also broadened my understanding on quantum theory and computing.
+I would like express my appreciation to all of these.
+
+Besides of Table~\ref{tab:acknowledgments}, I have some inspiring
+discussion with John Gardiner about quantum probability measures over
+finite fields~\cite{Gardiner2014}, and his results are improved
+and motivated the transition from DQT to QIVPM in Sec.~\ref{sec:Toward-IVPM}.
+Also, some unpublished computation for deterministic quantum algorithms
+is organized in the term paper for SLST-T501 Academic Writing course.
+I want to thank Prof.\ Tom Lewis for proof-reading them, and they
+become the bases of Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
+Besides of Prof.\ Tom Lewis, my other English teachers, especially
+Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
+Chen (谌可心), taught me a lot on expressing myself in English as well.
+Others who help me indirectly on the content of dissertation including
+Kin Wai Chan, Prof.\ 朱樺, Weihua Liu (刘伟华), 劉鈺平, Meng-Wei Chen
+(陳孟瑋), \ldots , etc. This could be listed on and on, and I still
+thank you even if your name is not listed here.\todo{Acknowledgments
+cleaned up until here. }
+
+Many people in both departments of Mathematics and Computer Science
+need to do something more to make my double-major works smoothly.
+I need to thank all of them, especially directors of graduate study
+in Mathematics, especially Prof.\ Christopher Judge and Prof.\ Matthias
+Weber; directors of Ph.D. study in Computer Science, especially Prof.\ Yuqing
+Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda Ergun}.
 
@@
 \item My other AT\&T family plan members, especially Kexin ``Casey''
-Chen (谌可心), Yao-yu Chih (池耀宇), Xinyi ``Diana'' Gong (龚欣怡), and Nanxi
-``Nancy'' Zhang (张楠茜), for you always pay our telephone bill on
-time so that\ldots\ldots\todo{ Maybe I don't have to thank them
-as AT\&T family plan members, but I should thank some of them for
-support and sharing information\ldots}
+Chen (谌可心), Yao-yu Chih (池耀宇), and Xinyi ``Diana'' Gong (龚欣怡), for
+you always pay our telephone bill on time so that\ldots\ldots\todo{
+Maybe I don't have to thank them as AT\&T family plan members, but
+I should thank some of them for support and sharing information\ldots}
 
@@
 to be compensated by error analysis techniques easily like the butterfly
-effect. Therefore, it is is unlikely to utilize the realistic analog
-computers to achieve the computational power predicted by this kind
+effect. Therefore, we might not be able to utilize a realistic analog
+computer to acquire the computational power predicted by this kind
 of theoretical models.%
@@
 the precision of their inducing probabilities because the idea of
-``imprecise probabilities'' has well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+``imprecise probability'' has well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+\begin{comment}
 \todo{Make sure whether realistic quantum computers could branch
@@
 it will provide another reason why we want to study the precision
-of the inducing probabilities\ldots{} }This idea will be extended
-to the quantum domain as quantum interval-valued probability measures
-(QIVPM).
+of the inducing probabilities\ldots{} }
+\end{comment}
+This idea will be extended to quantum domain as quantum interval-valued
+probability measure (QIVPM).
 
@@
 
-\subsection{Classical and Quantum Probability Spaces}
+\subsection{Classical and Quantum Probability Spaces\label{subsec:Classical-and-Quantum}}
 

### 2019-01-29 dissertation.tex
dissertation.lyx Acknowledgments Updating...

@@
 \setotherlanguage{arabic}
+\setotherlanguage{german}
 \setotherlanguage{italian}
@@
  & Co-author & Co-author & Co-author &  &  &  & Most of Chapters~\ref{chap:Conventional-Quantum-Theory}, \ref{chap:Unrestricted-Finite-Fields},
-and~\ref{chap:DQT=000026DQC} is based on \cite{geometry2013} and \cite{DQT2014}; most of Chapter~\ref{chap:QIVPM} is
-based on \cite{THOS2018}.\tabularnewline\addlinespace
+and~\ref{chap:DQT=000026DQC} is based on~\cite{geometry2013} and~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM} is
+based on~\cite{THOS2018}.\tabularnewline\addlinespace
 \addlinespace
@@
 \addlinespace
- &  & Suggested &  &  &  &  & The application for Rethinking Foundations of Physics 2017 workshop
+ &  & Supervisor &  &  &  &  & The application for Rethinking Foundations of Physics 2017 workshop
 inspires Chapter~\ref{chap:Introduction}.\tabularnewline\addlinespace
@@
 the assigned papers in the Tier 3 exam, \cite{Schumacher2012-SCHMQT}
-and \cite{doi:10.1142/S0217984913500644},
+and~\cite{doi:10.1142/S0217984913500644},
 are cited in Sec.~\ref{modalquantum}.\tabularnewline\addlinespace
@@
 I want to thanks all my professors co-authored with me, suggested
-me as a committee members, and taught me which become the bases or
-inspired any part of my dissertation as listed in Table~\ref{tab:acknowledgments}.
-Especially, Prof.\ Gerardo Ortiz, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري}),
-and Prof.\ Andrew J. Hanson meet me weekly for the pass few years,
-read and tried to understand what I typed which sometimes even myself
-cannot understand, taught me how to organize them in ``English''
-so that general audience might be interested and have some chance
-to understand, and encourage me to participate seminars, workshops,
-and conferences. Prof.\ Lawrence Moss invited me to present our results
-in the interdisciplinary logic seminar and theory seminar in Computer
-Science and wrote an assessment letter for me. Although not directly
-related to this dissertation, the knot theory studied with Prof.\ Dylan
-Paul Thurston and the quantum interpretation discussed with Prof.\ Shouhong
-Wang (汪守宏) also broadened my understanding on quantum theory and computing.
-I would like express my appreciation to all of these.
-
-Besides of Table~\ref{tab:acknowledgments}, I have some inspiring
-discussion with John Gardiner about quantum probability measures over
-finite fields~\cite{Gardiner2014}, and his results are improved
-and motivated the transition from DQT to QIVPM in Sec.~\ref{sec:Toward-IVPM}.
-Also, some unpublished computation for deterministic quantum algorithms
+me as a committee members, and taught me so that our work or studies
+became the bases or inspired any part of my dissertation as listed
+in Table~\ref{tab:acknowledgments}. Especially, Prof.\ Andrew J.
+Hanson, Prof.\ Gerardo Ortiz, and Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
+meet me weekly for the pass few years, read and tried to understand
+what I typed which sometimes even myself cannot understand, taught
+me how to organize them in ``English'' so that general audience
+might be interested and have some chance to understand, and encouraged
+me to participate seminars, workshops, and conferences. Prof.\ Lawrence
+Moss invited me to present our results in the interdisciplinary logic
+seminar and theory seminar in Computer Science and wrote an assessment
+letter for me. Although not directly related to this dissertation,
+the \textgerman[variant=german,spelling=new,babelshorthands=true]{Weil}
+conjecture on Grassmannians studied with Prof.\ Dylan Paul Thurston
+and the quantum interpretation discussed with Prof.\ Shouhong Wang
+(汪守宏) also broadened my understanding on discrete and conventional
+quantum theories. I would like express my appreciation to all of these.
+
+To have the current the content of the dissertation, I would also
+like to thank John Gardiner for some inspiring discussion about quantum
+probability measures over finite fields~\cite{Gardiner2014}. His
+results were improved and motivated the transition from DQT to QIVPM
+in Sec.~\ref{sec:Toward-IVPM}. Also, the unpublished computation
+for the discrete Deutsch algorithm \cite{Deutsch1985,544199,Mermin2007}
 is organized in the term paper for SLST-T501 Academic Writing course.
@@
 Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
-Chen (谌可心), taught me a lot on expressing myself in English as well.
-Others who help me indirectly on the content of dissertation including
-Kin Wai Chan, Prof.\ 朱樺, Weihua Liu (刘伟华), 劉鈺平, Meng-Wei Chen
-(陳孟瑋), \ldots , etc. This could be listed on and on, and I still
-thank you even if your name is not listed here.\todo{Acknowledgments
+Chen (谌可心), taught me a lot on how to communicate in English as well.
+Others who help me indirectly on the content of the dissertation including
+Kin Wai Chan, Prof.\ Huah Chu (朱樺), Weihua Liu (刘伟华), Caren Liu
+(劉鈺平), Meng-Wei Chen (陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen
+(陳昭宏)\ldots , etc. This could be listed on and on. I still thank
+you even if your name is not listed here, and sorry for my bad memory.\todo{Acknowledgments
 cleaned up until here. }

### 2019-01-29 dissertation.tex
dissertation.lyx Acknowledgments Updating according to Amr's suggestion...

@@
 \addlinespace
- &  & Supervisor &  &  &  &  & The application for Rethinking Foundations of Physics 2017 workshop
+ &  & Supervisor &  &  &  &  & The application for ``Rethinking Foundations of Physics'' 2017 workshop
 inspires Chapter~\ref{chap:Introduction}.\tabularnewline\addlinespace
@@
 (陳昭宏)\ldots , etc. This could be listed on and on. I still thank
-you even if your name is not listed here, and sorry for my bad memory.\todo{Acknowledgments
-cleaned up until here. }
-
-Many people in both departments of Mathematics and Computer Science
-need to do something more to make my double-major works smoothly.
-I need to thank all of them, especially directors of graduate study
-in Mathematics, especially Prof.\ Christopher Judge and Prof.\ Matthias
-Weber; directors of Ph.D. study in Computer Science, especially Prof.\ Yuqing
-Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda Ergun}.
+you even if your name is not listed here, and sorry for my bad memory.
+
+Many people in both the departments of Mathematics and Computer Science
+have done everything to make my double-major smooth. \todo{Acknowledgments
+cleaned up until here. }I need to thank all of them, especially directors
+of graduate study in Mathematics, especially Prof.\ Christopher Judge
+and Prof.\ Matthias Weber; directors of Ph.D. study in Computer Science,
+especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
+Ergun}.
 
@@
 \item Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
-what I did in the perspective of a general PhD. in Physics and working
+what I did from the perspective of a general PhD. in Physics and working
 later in more computational industry.
@@
 
-Finally, thank Jin-Ru Yang (楊謹如) for everything could not be written
-here.\end{acknowledgments*}
+Finally, I thank Jin-Ru Yang (楊謹如) for everything that could not be
+written here.\end{acknowledgments*}
 

### 2019-01-30 dissertation.tex
dissertation.lyx Resolving TODOs before "5.1.2 States Consistent with Classical and Quantum IVPMs"...

@@
 would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$.
-\todo{Citation? }For $D=2$, the single qubit, we have $2-1=1$,
-and the base space of the circle bundle is $\CP{1}=\Sphere{2}$, the
-usual Bloch sphere. Note that only for $D=2$ is this actually a sphere-like
-geometry due to an accident of low-dimensional topology.
+\begin{comment}
+\todo{Citation? }
+\end{comment}
+For $D=2$, the single qubit, we have $2-1=1$, and the base space
+of the circle bundle is $\CP{1}=\Sphere{2}$, the usual Bloch sphere.
+Note that only for $D=2$ is this actually a sphere-like geometry
+due to an accident of low-dimensional topology.
 
@@
 coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=1+\rmi0$.
+\begin{comment}
 \todo{Explain the last part clearer or add a picture.}
+\end{comment}
 
@@
 the set of all projectors on a given Hilbert space is called a quantum
-event space~$\events$. \todo{Check the citation of this part. Did
-von Neumann really think about this when he uses projectors to formulate
-the quantum theory?}
+event space~$\events$. %
+\begin{comment}
+\todo{Check the citation of this part. Did von Neumann really think
+about this when he uses projectors to formulate the quantum theory?}
+\end{comment}
 
@@
 expectation values because we can pullback an observable to a classical
-random variable, and the expectation values are invariant.\todo{
-Add interpretation!}
+random variable, and the expectation values are invariant.%
+\begin{comment}
+\todo{ Add interpretation!}
+\end{comment}
 
@@
 pullback of $\mathbf{O}$ by $\varphi$ is a random variable $\varphi^{*}\mathbf{O}\colon\Omega\rightarrow\mathbb{R}$
-defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$.
-\todo{Put the definition of indicator function!}\end{definition}
+defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$,
+where $\mathbf{1}_{E}$ is the indicator function defined by
+\begin{equation}
+\mathbf{1}_{E}\left(\omega\right)=\begin{cases}
+1 & \textrm{if }\omega\in E\,;\\
+0 & \textrm{if }\omega\notin E\,.
+\end{cases}
+\end{equation}
+\begin{comment}
+\todo{Put the definition of indicator function!}
+\end{comment}
+\end{definition}
 
@@
 \end{equation}
-In general, \todo{Ask Gerardo why? }the reduced density operator~$\rho_{j}$
-of the $j$-th subsystem can always be expressed as
+In general, %
+\begin{comment}
+\todo{Ask Gerardo why? }
+\end{comment}
+the reduced density operator~$\rho_{j}$ of the $j$-th subsystem
+can always be expressed as
 \begin{equation}
@@
 \usat\ problem (also known as $\lang{USAT}$ or $\lang{UNAMBIGUOUS-SAT}$)
-\todo{Add citation about where these two names come from. }is the
-problem of deciding whether a given Boolean formula has a satisfying
+\begin{comment}
+\todo{Add citation about where these two names come from. }
+\end{comment}
+is the problem of deciding whether a given Boolean formula has a satisfying
 assignment, assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
@@
 
-\begin{proof}\todo{This part use $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$
+\begin{proof}%
+\begin{comment}
+\todo{This part use $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$
 while previous parts use $\ket{\Psi}=\ket{\psi_{1}}\cdots\ket{\psi_{j}}\cdots\ket{\psi_{n}}$.
 Moreover, the ``bar'' is heavily used in QIVPM discussion later,
-so maybe not using bar here???? }The state is initialized to $\ket{0}\ket{\overline{0}}$,
-with $\ket{\overline{0}}=\ket{0}\ket{0}\cdots\ket{0}$, i.e., the
-tensor product of $n$ $\ket{0}$ states. As Eq.~(\ref{eq:MQT-dynamics-apply}),
+so maybe not using bar here???? }
+\end{comment}
+The state is initialized to $\ket{0}\ket{\overline{0}}$, with $\ket{\overline{0}}=\ket{0}\ket{0}\cdots\ket{0}$,
+i.e., the tensor product of $n$ $\ket{0}$ states. As Eq.~(\ref{eq:MQT-dynamics-apply}),
 applying the map $S$ to each qubit in the second component of the
@@
 As the first component of the state is $0$, applying the map $\sigma_{0}$
-(which is the identity) leaves the state unchanged. \todo{Control-not
-needs to be defined and explained in Sec.~\ref{subsec:Quantum-Circuits}
-}Applying $S^{\dagger}$ to the first component leaves the state
-unchanged. Measuring the state will deterministically produce $\ket{0}\ket{\overline{0}}$.\end{proof}
+(which is the identity) leaves the state unchanged. %
+\begin{comment}
+\todo{Control-not needs to be defined and explained in Sec.~\ref{subsec:Quantum-Circuits}
+}
+\end{comment}
+Applying $S^{\dagger}$ to the first component leaves the state unchanged.
+Measuring the state will deterministically produce $\ket{0}\ket{\overline{0}}$.\end{proof}
 
@@
 to verify that $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}$
-has one occurrence $\ket{0}\ket{\overline{0}}$. \todo{The following
-need to be rewritten. }This can be easily proved as follows. Since
-each $a_{i}$ is either 0 or 1, then each $S(a_{i})$ is either $+$
-or $1$, and hence each $\mathsf{not}\left(S(a_{i})\right)$ is either~$+$
-or~$0$. The result follows since any state with a combination of
-$+$ and $0$, when expressed in the standard basis, would consist
-of a superposition containing the state $\ket{0\ldots}$.\end{proof}
+has one occurrence $\ket{0}\ket{\overline{0}}$. %
+\begin{comment}
+\todo{The following need to be rewritten. }
+\end{comment}
+This can be easily proved as follows. Since each $a_{i}$ is either
+0 or 1, then each $S(a_{i})$ is either $+$ or $1$, and hence each
+$\mathsf{not}\left(S(a_{i})\right)$ is either~$+$ or~$0$. The
+result follows since any state with a combination of $+$ and $0$,
+when expressed in the standard basis, would consist of a superposition
+containing the state $\ket{0\ldots}$.\end{proof}
 
@@
 We can now compute the size of the equivalence class of complex unit-modulus
-phases corresponding to the Hopf fibration circle. \todo{Explain
-the Hopf fibration circle here\ldots ? }Since $\Fpp$ has $p^{2}-1$
-non-zero values, and the map $\fnorm{\alpha}$ distributes these equally
-across the domain of $p-1$ non-zero elements $c\in\Fp$, there are
-$\frac{p^{2}-1}{p-1}=p+1$ (non-zero) domain elements in $\Fpp$ for
-each (non-zero) image element in $\Fp$. We illustrate this graphically
-in Figure~\ref{proof1.fig}. Thus, the Hopf circle always has the
-size $p+1$, corresponding essentially to a discrete projective line,
-and that is the size of each equivalence class of the map $\fnorm{\alpha}$
-for non-vanishing $\alpha$, including the map to the unit norm value
-$c=1\in\Fp$.
+phases corresponding to the Hopf fibration circle. %
+\begin{comment}
+\todo{Explain the Hopf fibration circle here\ldots ? }
+\end{comment}
+Since $\Fpp$ has $p^{2}-1$ non-zero values, and the map $\fnorm{\alpha}$
+distributes these equally across the domain of $p-1$ non-zero elements
+$c\in\Fp$, there are $\frac{p^{2}-1}{p-1}=p+1$ (non-zero) domain
+elements in $\Fpp$ for each (non-zero) image element in $\Fp$. We
+illustrate this graphically in Figure~\ref{proof1.fig}. Thus, the
+Hopf circle always has the size $p+1$, corresponding essentially
+to a discrete projective line, and that is the size of each equivalence
+class of the map $\fnorm{\alpha}$ for non-vanishing $\alpha$, including
+the map to the unit norm value $c=1\in\Fp$.
 \begin{figure}
@@
 with unit norm map to the same point under the Hopf map \Eq{DQA6.eq};
-\todo{Does Proposition~\ref{appH.sec} really show this? }we may
-think of these as discrete circles or projective lines of equivalent,
+\begin{comment}
+\todo{Does Proposition~\ref{appH.sec} really show this? }
+\end{comment}
+we may think of these as discrete circles or projective lines of equivalent,
 physically indistinguishable, complex phase. The surviving $p\left(p-1\right)$
@@
 this discrete $\Sphere{2D-1}$ structure map to the \textit{same point}
-in $\Hat{a}$. \todo{Does Proposition~\ref{appH.sec} really show
-this? }Each set of $p+1$ redundant points is, geometrically speaking,
-the \textit{discrete Hopf fibration circle} living above each \textit{irreducible}
+in $\Hat{a}$. %
+\begin{comment}
+\todo{Does Proposition~\ref{appH.sec} really show this? }
+\end{comment}
+Each set of $p+1$ redundant points is, geometrically speaking, the
+\textit{discrete Hopf fibration circle} living above each \textit{irreducible}
 point of the $D$-dimensional state description. These $p+1$ points
@@
 model still leads to excessive computational power for the unstructured
-database search problem for certain database sizes. \todo{Prof.~Gil~Kalai
-thought it would be interesting if we can do Simon's algorithm in
-DQC~(I), but I don't know when I could organize my unreadable draft
-to a readable one\ldots{} Moreover, Prof.~Ortiz wants to check Shor's
-algorithm in DQC~(I).}
+database search problem for certain database sizes. %
+\begin{comment}
+\todo{Prof.~Gil~Kalai thought it would be interesting if we can
+do Simon's algorithm in DQC~(I), but I don't know when I could organize
+my unreadable draft to a readable one\ldots{} Moreover, Prof.~Ortiz
+wants to check Shor's algorithm in DQC~(I).}
+\end{comment}
 
@@
 \end{table}
+\begin{comment}
 \todo{We typeset $U_{f}$ either directly or use macro \textbackslash uf,
@@
 space has any semantic meaning\ldots{} }
+\end{comment}
 \begin{figure}[t]
@@
 if $a>b$ and $b>c$, provided $a-b$, $b-c$, and $a-c$ are all
-quadratic residues. \todo{Should we remove the quadratic residue
-part? Since we never use take the square roots of numbers in order
-range later, whether they are the quadratic residues or not doesn't
-really matter\ldots}
+quadratic residues. %
+\begin{comment}
+\todo{Should we remove the quadratic residue part? Since we never
+use take the square roots of numbers in order range later, whether
+they are the quadratic residues or not doesn't really matter\ldots}
+\end{comment}
 
@@
 Also, notice that the positioning of the initial qubit state $\ket{1}$
-is reversed from~\cite{544199}. } \todo{A bit more explanation?}
+is reversed from~\cite{544199}. } %
+\begin{comment}
+\todo{A bit more explanation?}
+\end{comment}
 \begin{equation}
@@
 \end{equation}
-and that its field norm is $2^{n+1}$. \todo{Verify. }To make sure
-that the algorithm works properly, we note that all the probability
-amplitudes involved in the calculation are in the range $-2^{n}$,
-\ldots , $2^{n}$ and therefore, by Eq.~\eqref{eq:region}, we get
-the following constraint on the size of the ordered region in the
-finite field: 
+and that its field norm is $2^{n+1}$. %
+\begin{comment}
+\todo{Verify. }
+\end{comment}
+To make sure that the algorithm works properly, we note that all the
+probability amplitudes involved in the calculation are in the range
+$-2^{n}$, \ldots , $2^{n}$ and therefore, by Eq.~\eqref{eq:region},
+we get the following constraint on the size of the ordered region
+in the finite field: 
 \begin{eqnarray}
@@
 scaled to integer values as usual, the state after $l$-th iteration
-can be written as \todo{Verify the computation??}
+can be written as %
+\begin{comment}
+\todo{Verify the computation??}
+\end{comment}
 \begin{equation}
@@
 The initial information-less $8$-dimensional state vector evolves
-under the application of $\Delta R$ as follows: \todo{Change the
-whole paragraph to a table?}
+under the application of $\Delta R$ as follows: %
+\begin{comment}
+\todo{Change the whole paragraph to a table?}
+\end{comment}
 \begin{equation}
@@
 is based on the conventional Born rule, Eq.~(\ref{eq:Born-ComputationalBasis}).
+\begin{comment}
 Although they are valid inside an ordered region, some quantum algorithms,
@@
 of Shor's algorithm if I cannot verify it on DQT~(I) on time. }Moreover, 
-since we haven't found a way to manipulate the resulting cardinal
+\end{comment}
+Since we haven't found a way to manipulate the resulting cardinal
 probabilities, we have little idea how to define the mixed states
@@
 verified that the only QPMFF $\mu\colon\events_{7^{2}}\rightarrow\left[0,1\right]$
-is \todo{Equal probable.}
+is %
+\begin{comment}
+\todo{Equal probable.}
+\end{comment}
 \begin{equation}
@@
 which also satisfies an analog of Proposition~\ref{prop:Born-probability-one}
-and~\ref{prop:Born-unitary-invariant}. \todo{Notice that the notation
-here and previous is a little bit different because we dealt with
-mixed states previously, but pure states here. Besides, should we
-explain the physical meaning of these propositions?}
+and~\ref{prop:Born-unitary-invariant}. %
+\begin{comment}
+\todo{Notice that the notation here and previous is a little bit
+different because we dealt with mixed states previously, but pure
+states here. Besides, should we explain the physical meaning of these
+propositions?}
+\end{comment}
 
@@
 
+\begin{comment}
 \todo{Add some introductory text\ldots}
+\end{comment}
 
@@
 Since we only consider finite sample space, $X$ can always be decomposed
-into the sum of step functions~$\mathbf{1}_{E}$ defined by
-\begin{equation}
-\mathbf{1}_{E}\left(\omega\right)=\begin{cases}
-1 & \textrm{if }\omega\in E\,;\\
-0 & \textrm{if }\omega\notin E\,.
-\end{cases}
-\end{equation}
+into the sum of step functions~$\mathbf{1}_{E}$ defined in Def.~\ref{def:observable2random-variable}.
 For our convenience to define the Choquet integral later, we order

### 2019-01-30 dissertation.tex
dissertation.lyx Fix the location of figure labels...

@@
 \par\end{centering}
-}\hfill{}\label{hopfFibers.fig}\caption{(a) The two-sphere~$\Sphere{2}$ represented by \Eq{A7.eq}, which
-is the irreducible space of one-qubit states, along with a representative
-set of points on the sphere. Each single point on the sphere in (a)
-corresponding to a circle in (b), and a whole family of circles (the
-paths of $\rme^{\rmi\theta}$) on the three-sphere~$\Sphere{3}$
-represents the Hopf fibration, Eq.~(\ref{eq:HopfFibration}). Although
-$\Sphere{3}$ cannot be directly embedded in $\R^{3}$, three-sphere~$\Sphere{3}$
+}\hfill{}\caption{\label{hopfFibers.fig}(a) The two-sphere~$\Sphere{2}$ represented
+by \Eq{A7.eq}, which is the irreducible space of one-qubit states,
+along with a representative set of points on the sphere. Each single
+point on the sphere in (a) corresponding to a circle in (b), and a
+whole family of circles (the paths of $\rme^{\rmi\theta}$) on the
+three-sphere~$\Sphere{3}$ represents the Hopf fibration, Eq.~(\ref{eq:HopfFibration}).
+Although $\Sphere{3}$ cannot be directly embedded in $\R^{3}$, three-sphere~$\Sphere{3}$
 can be regarded as attaching two three-dimensional balls on two sides
@@
 \par\end{centering}
-\label{blochSphere.fig}\caption{(a) The conventional Bloch sphere with a unique state represented
-by the point at the red sphere. (b) The geodesic shortest-distance
-arc connecting two one-qubit quantum states.}
+\caption{\label{blochSphere.fig}(a) The conventional Bloch sphere with a unique
+state represented by the point at the red sphere. (b) The geodesic
+shortest-distance arc connecting two one-qubit quantum states.}
 \end{figure}
@@
 \begin{figure}
-\noindent \centering{}\includegraphics[width=3.6in]{Fpp2Fp}\label{proof1.fig}\caption{Sketch of the map from $\Fpp$ to $\Fp$ using $\fnorm{\alpha}$,
-showing the decomposition of $\Fpp$ into the zero element $\left(0,0\right)$
-and the $p^{2}-1=\left(p+1\right)\left(p-1\right)$ non-zero elements
-that map onto the $p-1$ non-zero elements of $\Fp$ with multiplicity
-$p+1$.}
+\noindent \centering{}\includegraphics[width=3.6in]{Fpp2Fp}\caption{\label{proof1.fig}Sketch of the map from $\Fpp$ to $\Fp$ using
+$\fnorm{\alpha}$, showing the decomposition of $\Fpp$ into the zero
+element $\left(0,0\right)$ and the $p^{2}-1=\left(p+1\right)\left(p-1\right)$
+non-zero elements that map onto the $p-1$ non-zero elements of $\Fp$
+with multiplicity $p+1$.}
 \end{figure}
@@
 \par\end{centering}
-\label{bloch.fig}\caption{Schematically normalized plots of the elements of the discrete Bloch
-sphere, the irreducible single-qubit (two-dimensional) state vectors
-with unit norm over the field $\Fpp$. We show the results for $p=3$,
-$7$, and $11$. For example, in $\Fppx{3}$, there are 24 vectors
-of unit norm, but only the 6 inequivalent classes appear in the plot.
-The $p+1=4$ equivalent vectors in each class differ only by a complex
-discrete phase.}
+\caption{\label{bloch.fig}Schematically normalized plots of the elements of
+the discrete Bloch sphere, the irreducible single-qubit (two-dimensional)
+state vectors with unit norm over the field $\Fpp$. We show the results
+for $p=3$, $7$, and $11$. For example, in $\Fppx{3}$, there are
+24 vectors of unit norm, but only the 6 inequivalent classes appear
+in the plot. The $p+1=4$ equivalent vectors in each class differ
+only by a complex discrete phase.}
 \end{figure}
@@
 \par\end{centering}
-\label{statePlot3Unit.fig}\caption{Logarithmic plot of the number of discrete unnormalized states (top,
-in red), vs the number of normalized discrete states (middle, in blue),
-vs the irreducible states (bottom, in green) for the first 6 $\Fpp$-compatible
-primes, ($3$, $7$, $11$, $19$, $23$, $31$), for the number of
-qubits $1$, $2$, $3$, and $4$. }
+\caption{\label{statePlot3Unit.fig}Logarithmic plot of the number of discrete
+unnormalized states (top, in red), vs the number of normalized discrete
+states (middle, in blue), vs the irreducible states (bottom, in green)
+for the first 6 $\Fpp$-compatible primes, ($3$, $7$, $11$, $19$,
+$23$, $31$), for the number of qubits $1$, $2$, $3$, and $4$. }
 \end{figure}

### 2019-01-30 dissertation.tex
dissertation.lyx "5.1.2 States Consistent with Classical and Quantum IVPMs" Updated...

@@
 but also naturally sends the set structure to the corresponding projector
-structure: $\varphi\left(\Omega\right)=\mathbb{1}$ and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
+structure:
+\begin{align}
+\varphi\left(\Omega\right) & =\mathbb{1}\,, & \varphi\left(\overline{E}\right) & =\mathbb{1}-\varphi\left(E\right)\,.\label{eq:pullback-properties-basic}
+\end{align}
 Given two \emph{commuting} projectors $P_{0}$ and~$P_{1}$, there
@@
 the function $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
-defined by precomposition $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$
+defined by precomposition 
+\begin{equation}
+\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)\label{eq:classical-pullback}
+\end{equation}
 is a classical probability measure and called the pullback of $\mu$
@@
 sense that a restriction of QIVPMs to mutually commuting events, $\eventsC$,
-recovers the definition of classical IVPMs.  To see this, note that
-the commuting projectors in $\eventsC$ can be diagonalized by a common
-orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $.
-Since $\Omega$ is a finite set, it can be the sample space of a classical
-probability space with the classical event space $2^{\Omega}$. Because
-a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$ and a classical
-IVPM $\bar{\mu}'\colon2^{\Omega}\rightarrow\mathscr{I}$ only differ
-on their domains, if we can find a function $\varphi\colon2^{\Omega}\rightarrow\events$
-preserving the structure, we can pullback~\cite{wiki:Pullback} any
-QIVPM~$\bar{\mu}$ to $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
-such that $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
-for any $E\subseteq\Omega$ and $\varphi^{*}\bar{\mu}$ should be
-a classical IVPM\@.
-
-We now explicitly define $\varphi$. First, $\events'$ is called
-a \emph{subspace} of the set of events~$\events$ if $\events'$
-contains the projectors $\mathbb{0}$ and $\mathbb{1}$ and is closed
-under complements, sums, and products. In particular, for any projector
-$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for each pair
-of commuting projectors $P_{0}\in\events'$ and $P_{1}\in\events'$,
-we have $P_{0}P_{1}$ and $P_{0}+P_{1}-P_{0}P_{1}\in\events'$. Given
-a mutually commuting subspace~$\eventsC$ whose elements are diagonalizable
-by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
-we define the function $\varphi\colon2^{\Omega}\rightarrow\events$
-maps any set~$E$ to the sum of the projectors formed by elements
-in $E$ as in Eq.~(\ref{eq:pullback-function}). \todo{Review this
-part because Eq.~(\ref{eq:pullback-function}) is moved to Sec.~\ref{sec:fuzzy}.
-}Therefore, given a QIVPM~$\bar{\mu}$, the function $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
+recovers the definition of classical IVPMs.  To see this, first,
+$\events'$ is called a \emph{subspace} of the set of events~$\events$
+if $\events'$ contains the projectors $\mathbb{0}$ and $\mathbb{1}$
+and is closed under complements, sums, and products. In particular,
+for any projector $P\in\events'$, we have $\mathbb{1}-P\in\events'$
+and for each pair of commuting projectors $P_{0}\in\events'$ and
+$P_{1}\in\events'$, we have $P_{0}P_{1}$ and $P_{0}+P_{1}-P_{0}P_{1}\in\events'$.
+Given a mutually commuting subspace~$\eventsC$ whose elements are
+diagonalizable by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
+the function $\varphi\colon2^{\Omega}\rightarrow\eventsC$ defined
+in in Eq.~(\ref{eq:pullback-function}) maps any set~$E$ to the
+sum of the projectors formed by elements in $E$, and preserve all
+operations used to defined classical and quantum IVPMs as in Eqs.~(\ref{eq:pullback-properties-basic})
+and~(\ref{eq:pullback-properties}). According to the same reason
+as the classical counterpart, Eq.~(\ref{eq:classical-pullback}),
+given a QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}$, the
+function $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
 defined by precomposition $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$

### 2019-01-30 dissertation.tex
dissertation.lyx "5.1.3 Classical Choquet integrals and Expectation Values of Observables" Updating...

@@
 
+\begin{comment}
 \todo{See if we could delete from here to Thm.~\ref{thm:Rosenmuller},
@@
 can be preceded smoothly in this way\ldots}
-
+\end{comment}
 Although it is intuitive to define the expectation value as the minimum
@@
 as follow.
-\begin{eqnarray*}
-\int X\rmd\bar{\mu} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\pmeas\left(E_{i\uparrow}^{s}\right),\Delta\pmeas\left(E_{i\uparrow}^{s}\right)\right]\\
- & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right),\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right)\right]\\
- & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right),\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right)\right]\\
- & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right),\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right)\right]\\
- & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i}^{s}\right),\mu\left(E_{i}^{s}\right)\right]=\left[\int X\rmd\mu,\int X\rmd\mu\right]
-\end{eqnarray*}
+\begin{equation}
+\begin{aligned}\int X\rmd\bar{\mu} & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\pmeas\left(E_{i\uparrow}^{s}\right),\Delta\pmeas\left(E_{i\uparrow}^{s}\right)\right]\\
+ & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right),\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right)\right]\\
+ & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right),\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right)\right]\\
+ & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right),\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right)\right]\\
+ & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i}^{s}\right),\mu\left(E_{i}^{s}\right)\right]=\left[\int X\rmd\mu,\int X\rmd\mu\right]
+\end{aligned}
+\label{eq:classical-real-interval-Choquet}
+\end{equation}
 
@@
 After we defined the expectation values of random variables relative
-to classical IVPMs, we can parallelly define the expectation values
-of observables relative to QIVPMs as follow.
+to classical IVPMs, we can merge this definition with the expectation
+values to quantum probability measures, Eq.~(\ref{eq:quantum-expectation}),
+and define the expectation values of observables relative to QIVPMs
+as follow.
 
@@
 
-Parallel to the similarity between Eqs.~(\ref{eq:expectation}) and
-(\ref{eq:interval-expectation}), Eq.~(\ref{eq:interval-expectation-quantum})
-can be simplified to Eq.~(\ref{eq:quantum-expectation}) if $\bar{\mu}$
-is essentially real-valued.
-
-\begin{thm}\label{lemma:expectation-singleton}Given a quantum probability
-measure $\mu\colon\events\rightarrow\left[0,1\right]$ satisfying
-Eqs.~(\ref{eq:QuantumProbability}) and (\ref{eq:QuantumProbability-Addition}),
-if we define a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
-by $\bar{\mu}\left(P\right)=\left[\mu\left(P\right),\mu\left(P\right)\right]$
-for all projectors~$P$, then the expectation value of any observable~$\mathbf{O}$
-relative to $\bar{\mu}$, $\expval{\mathbf{O}}_{\bar{\mu}}$, is just
-$\left[\expval{\mathbf{O}}_{\mu},\expval{\mathbf{O}}_{\mu}\right]$.\end{thm}
-
-We then want to show the expectation value relative to a QIVPM generalizes
-the one relative to a classical IVPM by proving a quantum version
-of Thm.~\ref{thm:Rosenmuller}. \todo{Review this part because Def.~\ref{def:observable2random-variable}
-is moved to Sec.~\ref{sec:fuzzy}. }While both observables and IVPMs
-can be pulled back from quantum to classical, these pullbacks keep
-the expectation value invariant.
+Recall Lemma~\ref{lemma:real-expectation-value-between-classical-quantum}
+proved real expectation values are invariant when pulling back observables
+and probability measures. The following lemma shows interval expectation
+values are invariant under pullback as well.
 
@@
 
-After we have required lemmas, we are in a good position to prove
-a quantum analog of Thm.~\ref{thm:Rosenmuller}. However, since Lemma~\ref{lemma:density-matrix-pullback}
+Since Def.~\ref{def:expectation-values-QIVPM} is an extension of
+both quantum real expectation value and classical interval expectation
+value, not only the property of quantum real expectation value could
+be extended to the previous lemma, but the properties of classical
+interval expectation value, like Eq.~(\ref{eq:classical-real-interval-Choquet})
+and Thm.~\ref{thm:Rosenmuller}, could be extended to quantum interval
+expectation value as well. In particular, Eq.~(\ref{eq:classical-real-interval-Choquet})
+can be extended to the following lemma.
+
+\begin{thm}\label{lemma:expectation-singleton}Given a quantum probability
+measure $\mu\colon\events\rightarrow\left[0,1\right]$ satisfying
+Eqs.~(\ref{eq:QuantumProbability}) and (\ref{eq:QuantumProbability-Addition}),
+if we define a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
+by $\bar{\mu}\left(P\right)=\left[\mu\left(P\right),\mu\left(P\right)\right]$
+for all projectors~$P$, then the expectation value of any observable~$\mathbf{O}$
+relative to $\bar{\mu}$, $\expval{\mathbf{O}}_{\bar{\mu}}$, is just
+$\left[\expval{\mathbf{O}}_{\mu},\expval{\mathbf{O}}_{\mu}\right]$.\end{thm}
+
+We then want to show the expectation value relative to a QIVPM generalizes
+the one relative to a classical IVPM by proving a quantum version
+of Thm.~\ref{thm:Rosenmuller}. However, since Lemma~\ref{lemma:density-matrix-pullback}
 hasn't established enough correspondence between classical and quantum
@@
 \end{itemize}
+\begin{comment}
 \todo{Can we find an example where Eq.~(\ref{eq:quantum-interval-expectation-core})
@@
 Eqs.~(\ref{eq:quantum-interval-expectation-core}) and (\ref{eq:quantum-interval-expectation-core-equal})
-separately\ldots}\end{thm}
+separately\ldots}
+\end{comment}
+\end{thm}
 

### 2019-02-01 dissertation.tex
dissertation.lyx Review until "5.1.3 Classical Choquet integrals and Expectation Values of Observables", but I suddenly afraid the definition of expectation value of classical IVPM might be wrong... Need to check...

@@
 
-The part of the conventional quantum theory (CQT) used by quantum
-circuit model is described by the following:
+The part of conventional quantum theory (CQT) used by quantum circuit
+model is described by the following:
 \begin{enumerate}[label=(\roman{enumi})]
@@
 The property~\ref{enu:unitary-matrix} directly related to quantum
-circuits will be introduced later in Chapter~\ref{chap:DQT=000026DQC}
-when we dive into quantum algorithms.
+circuits will be introduced later in Chapters~\ref{chap:Unrestricted-Finite-Fields}
+and~\ref{chap:DQT=000026DQC} when we dive into quantum algorithms.
 
@@
 as being the same if they differ only by an overall phase $\rme^{\rmi\theta}$.
-However, in practice, this is not a construction that is easy to realize
+However in practice, this is not a construction that is easy to realize
 in a practical computation. We now outline an explicit algorithm for
@@
 the two-dimensional irreducible states could be represented in a four-dimensional
-embedding, but the magnitude of every coordinate would be one; furthermore,
+embedding, but the magnitude of every coordinate would be one. Furthermore,
 the object embedded in the resulting $\Sphere{3}$ is indeed $\Sphere{2}$
@@
 and the probability of the common event $\left\{ \ket{2}\right\} $
-is believed to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
+is believed to be the same, i.e., 
+\begin{equation}
+\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)\,.\label{eq:mu0-equal-mu1}
+\end{equation}
 In general, as long as sending the same particle, the probability
@@
 the same situation. For example, if we take the complement on both
-sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
-we will have
+sides of Eq.~(\ref{eq:mu0-equal-mu1}), we will have
 \begin{equation}
@@
 
-\begin{proof}By Eq.~(\ref{eq:quantum-expectation}), we have
+\begin{proof}By Eqs.~(\ref{eq:quantum-expectation}), (\ref{eq:pullback-function}),
+and (\ref{eq:classical-pullback}), we have
 \[
@@
 the variants of quantum probability measures in Sec.~\ref{sec:Toward-IVPM}
-and Chapter~\ref{chap:QIVPM} could not be constructed by the Born
-rule easily, searching for a Born rule step-by-step here might provide
-a better idea of what we should do in Sec.~\ref{sec:Toward-IVPM}
+and Chapter~\ref{chap:QIVPM} could not be constructed by a ``Born
+rule'' easily, searching for a Born rule step-by-step here might
+provide a better idea of what we should do in Sec.~\ref{sec:Toward-IVPM}
 and Chapter~\ref{chap:QIVPM}. While the situations will become more
-delicate in the later sections, we will, fortunately, find the unique
+delicate in the later sections, we will fortunately find the unique
 Born rule for CQT here.
@@
 the outcomes of a quantum event~$P$, $P\ket{\Phi}=\ket{\Phi}$,
-then the event~$P$ always happens, $\muB_{\Phi}\left(P\right)=1$,
+then the event~$P$ always happens, 
+\begin{equation}
+\muB_{\Phi}\left(P\right)=1\,,\label{eq:Born-probability-one}
+\end{equation}
 and vice versa. Moreover, since the physical phenomena exist and should
@@
 changing to another basis is the same as applying a unitary map~$U$,
-we should have $\muB_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muB_{\Phi}\left(P\right)$.
+we should have 
+\begin{equation}
+\muB_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muB_{\Phi}\left(P\right)\,.\label{eq:Born-unitary-invariant}
+\end{equation}
 It is easy to check that the correspondence satisfying these conditions
@@
 first case and $2$ in the second. The quantum expectation value can
-also use to decide whether a state is entangled or not for multipartite
+also be used to decide whether a state is entangled or not for multipartite
 systems as we describe in the following section.
@@
 for at least one $j$, represented by a point \emph{inside} the corresponding
-local Bloch sphere embedded in $\mathbb{R}^{3}$. One may, therefore,
+local Bloch sphere embedded in $\mathbb{R}^{3}$. Therefore, one may
 consider $\ket{\Psi}$ to be maximally entangled if $\left\Vert {\bf X}_{j}\right\Vert =0$
@@
 but now with all computations in\hspace{0bp}$\pmod{p}$. At this
-point, one simply writes down all possible discrete values for the
-complex numbers $\left(\alpha_{0},\alpha_{1}\right)$ satisfying Eq.~(\ref{DQA2.eq})
-and enumerates those that project to the same value of $\left(X,Y,Z\right)$.
-This equivalence class is the discrete analog of the circle in the
-complex plane that was eliminated in the continuous case. In Proposition~\ref{appH.sec},
-we show that $p+1$ discrete values of $\left(\alpha_{0},\alpha_{1}\right)$
-with unit norm map to the same point under the Hopf map \Eq{DQA6.eq};
+point, one can simply write down all possible discrete values for
+the complex numbers $\left(\alpha_{0},\alpha_{1}\right)$ satisfying
+Eq.~(\ref{DQA2.eq}) and enumerate those that project to the same
+value of $\left(X,Y,Z\right)$. This equivalence class is the discrete
+analog of the circle in the complex plane that was eliminated in the
+continuous case. In Proposition~\ref{appH.sec}, we show that $p+1$
+discrete values of $\left(\alpha_{0},\alpha_{1}\right)$ with unit
+norm map to the same point under the Hopf map \Eq{DQA6.eq}; %
 \begin{comment}
@@
 \end{equation}
-and in general, for $n$-qubits, there are $p^{n}\left(p-1\right)^{n}$
+and in general for $n$-qubits, there are $p^{n}\left(p-1\right)^{n}$
 instances of pure product states.
@@
 To explain why this circuit solves the Deutsch problem, we then compute
-the state in each step explicitly and express the Dirac bracket notation
-with its matrix representation in the computational basis $\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $
-parallelly. 
+the state in each step explicitly and express them in the Dirac bracket
+notation and its matrix representation in the computational basis
+$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $. 
 \begin{table}
-\noindent \centering{}\caption{\label{tab:Possible-f}Possible $f$ for Deutsch black box $U_{f}$}
+\noindent \centering{}\caption{\label{tab:Possible-f}All Possible $f\colon\boolt\rightarrow\boolt$.}
 \begin{tabular}{ccccc}
@@
 \addlinespace
-Input & $f_{1}$ & $f_{2}$ & $f_{3}$ & $f_{4}$\tabularnewline\addlinespace
+$x$ & $f_{1}\left(x\right)$ & $f_{2}\left(x\right)$ & $f_{3}\left(x\right)$ & $f_{4}\left(x\right)$\tabularnewline\addlinespace
 \midrule
@@
 \]
-\caption{\label{fig:Quantum-Circuit-Deutsch}Quantum Circuit for Deutsch Algorithm.}
+\caption{\label{fig:Quantum-Circuit-Deutsch}Quantum Circuit for the Deutsch
+Algorithm.}
 \end{figure}
@@
 of the non-zero field elements) is the set of \emph{quadratic non-residues}.
-For example, in $\ff{7}$, the elements $\left\{ 1,2,4\right\} $
-are considered positive as they have the square roots $\left\{ 1,3,2\right\} $
+For example in $\ff{7}$, the elements $\left\{ 1,2,4\right\} $ are
+considered positive as they have the square roots $\left\{ 1,3,2\right\} $
 respectively; the remaining elements $\left\{ 3,5,6\right\} $ do
@@
 $\left\{ \ket{0},\ldots,\ket{i},\ldots,\ket{D-1}\right\} $. Indeed,
-it is sufficient to only consider measuring in the computational basis
-because measuring in another basis is the same as applying a quantum
-gate and measuring in the computational basis. In this situation,
-the Born rule for pure states, Eq.~(\ref{eq:Born}), can be simplified
-as
+it is sufficient to only consider measuring a quantum circuit in the
+computational basis because measuring in another basis is the same
+as applying a quantum gate and measuring in the computational basis.
+In this situation, the Born rule for pure states, Eq.~(\ref{eq:Born}),
+can be simplified as
 \begin{equation}
@@
 where $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \cdots & \alpha_{D-1}\end{pmatrix}^{T}$
-is an unnormalized state. Hereafter, we will simplify by calling $\muB_{\Psi}\left(i\right)$
+is an unnormalized state. Hereafter, we will simply call $\muB_{\Psi}\left(i\right)$
 the probability of measuring $\ket{i}$.
 
-Although the division is not an allowed operation for the elements
-in an ordered region, following the standard procedure to define a
-conventional fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
+Although division is not an allowed operation for the elements in
+an ordered region, following the standard procedure to define a conventional
+fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
 we could define a \emph{cardinal probability} as a pair of order-region
@@
 
-The cardinal probability over finite fields defined in Eq.~(\ref{eq:cardinalProbability})
-is based on the conventional Born rule, Eq.~(\ref{eq:Born-ComputationalBasis}).
+Although cardinal probabilities can be ordered as discussed in \ref{discretequantumtheoryIIb},
+it is still unclear how to define their arithmetic operations, which
+is required to further define the mixed states and expectation values.
+Notice that the cardinal probability over finite fields defined in
+Eq.~(\ref{eq:cardinalProbability}) is based on the conventional
+Born rule, Eq.~(\ref{eq:Born-ComputationalBasis}) which could be
+derived axiomatically according to Gleason's theorem as in Sec.~\ref{subsec:Gleason's-Theorem-and}.
 \begin{comment}
@@
 \end{comment}
-Since we haven't found a way to manipulate the resulting cardinal
-probabilities, we have little idea how to define the mixed states
-and expectation values. To overcome these issues, we try a different
-approach to define a ``conventional'' probability over finite fields
-axiomatically.
-
-Recall Gleason's theorem in Sec.~\ref{subsec:Gleason's-Theorem-and}
-states that every quantum probability measure is induced a mixed state
-in a Hilbert space $\Hilb$ of dimension $D\geq3$ according to the
-Born rule. To find a Born rule over finite fields, we could follow
-the steps in Sec.~\ref{sec:fuzzy} to define events and probability
-measures and see whether we could have a Gleason-like theorem which
-induces a correspondence between states and probability measures qualified
-as a discrete Born rule.
+To overcome these issues, we want to follow the steps in Sec.~\ref{sec:fuzzy}
+to define events and probability measures, and see whether we could
+have a Gleason-like theorem which induces a correspondence between
+states and probability measures qualified as a discrete Born rule.
 
@@
 QPMFFs alone, we could prove there is no ``sensible'' Born rule
-which also satisfies an analog of Proposition~\ref{prop:Born-probability-one}
-and~\ref{prop:Born-unitary-invariant}. %
+which also satisfies an analog of Eqs.~(\ref{eq:Born-probability-one})
+and~(\ref{eq:Born-unitary-invariant}). %
 \begin{comment}
@@
 
-Like the previous paragraph, we now compute the QPMFF induced by $\ket{\Phi'}=U'\ket{\oplus}=\frac{2\alpha}{\gamma}\ket{0}+\frac{1}{\gamma}\ket{2}$,
+Following the similar computation to the previous paragraph, we now
+compute the probabilities induced by $\ket{\Phi'}=U'\ket{\oplus}=\frac{2\alpha}{\gamma}\ket{0}+\frac{1}{\gamma}\ket{2}$,
 where $\alpha=\fnorm*{\frac{1}{2}}\in\ff{p^{2}}$ and
@@
 Our definition of QIVPMs is consistent with classical IVPMs in the
-sense that a restriction of QIVPMs to mutually commuting events, $\eventsC$,
-recovers the definition of classical IVPMs.  To see this, first,
-$\events'$ is called a \emph{subspace} of the set of events~$\events$
-if $\events'$ contains the projectors $\mathbb{0}$ and $\mathbb{1}$
-and is closed under complements, sums, and products. In particular,
-for any projector $P\in\events'$, we have $\mathbb{1}-P\in\events'$
-and for each pair of commuting projectors $P_{0}\in\events'$ and
-$P_{1}\in\events'$, we have $P_{0}P_{1}$ and $P_{0}+P_{1}-P_{0}P_{1}\in\events'$.
-Given a mutually commuting subspace~$\eventsC$ whose elements are
-diagonalizable by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
-the function $\varphi\colon2^{\Omega}\rightarrow\eventsC$ defined
-in in Eq.~(\ref{eq:pullback-function}) maps any set~$E$ to the
-sum of the projectors formed by elements in $E$, and preserve all
-operations used to defined classical and quantum IVPMs as in Eqs.~(\ref{eq:pullback-properties-basic})
+sense that a restriction of QIVPMs to mutually commuting subspace
+of events, $\eventsC$, recovers the definition of classical IVPMs.
+ To see this, we first define the idea of subspace of events. $\events'$
+is called a \emph{subspace} of the set of events~$\events$ if $\events'$
+contains the projectors $\mathbb{0}$ and $\mathbb{1}$ and is closed
+under complements, sums, and products. In particular, for any projector
+$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for each pair
+of commuting projectors $P_{0}\in\events'$ and $P_{1}\in\events'$,
+we have $P_{0}P_{1}$ and $P_{0}+P_{1}-P_{0}P_{1}\in\events'$. Given
+a mutually commuting subspace~$\eventsC$ whose elements are diagonalizable
+by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
+the function $\varphi\colon2^{\Omega}\rightarrow\events$ defined
+in Eq.~(\ref{eq:pullback-function}) maps any set~$E$ to the sum
+of the projectors formed by elements in $E$, and preserve all operations
+used to defined classical and quantum IVPMs as in Eqs.~(\ref{eq:pullback-properties-basic})
 and~(\ref{eq:pullback-properties}). According to the same reason
@@
 respectively, as long as they satisfy $\mu\left(E\right)+\mu\left(\overline{E}\right)=1$.
-These ``true'' probabilities can be summarized as a probability
+These ``true'' probabilities can be represented as a probability
 measure $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$ satisfying
@@
 to $\eventsC$, $\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)$,
-such that the pullback of $\muB_{\rho}$ is $\mu$ in the following
-sense:
+such that the pullback of $\muB_{\rho}$ is $\mu$, i.e.,
 \begin{equation}
@@
 
-Like how we pull back classical ideas to the quantum world in Secs.~\ref{subsec:Definitions-of-IVPMs}
+Like how we pulled back classical ideas to the quantum world in Secs.~\ref{subsec:Definitions-of-IVPMs}
 and~\ref{subsec:States-Consistent-with-IVPMs}, we start from defining
@@
 easily simplified to the right-hand side of Eq.~(\ref{eq:expectation})
-as follow.
-\begin{equation}
-\begin{aligned}\int X\rmd\bar{\mu} & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\pmeas\left(E_{i\uparrow}^{s}\right),\Delta\pmeas\left(E_{i\uparrow}^{s}\right)\right]\\
- & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right),\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right)\right]\\
- & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right),\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right)\right]\\
- & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right),\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right)\right]\\
- & =\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i}^{s}\right),\mu\left(E_{i}^{s}\right)\right]=\left[\int X\rmd\mu,\int X\rmd\mu\right]
+as follow:
+\begin{equation}
+\begin{aligned} & \int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\pmeas\left(E_{i\uparrow}^{s}\right),\Delta\pmeas\left(E_{i\uparrow}^{s}\right)\right]\\
+={} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right),\mu\left(E_{i\uparrow}^{s}\right)-\mu\left(E_{\left(i+1\right)\uparrow}^{s}\right)\right]\\
+={} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right),\mu\left(\bigcup_{j\ge i}E_{j}^{s}\right)-\mu\left(\bigcup_{j\ge i+1}E_{j}^{s}\right)\right]\\
+={} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right),\sum_{j\ge i}\mu\left(E_{j}^{s}\right)-\sum_{j\ge i+1}\mu\left(E_{j}^{s}\right)\right]\\
+={} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\mu\left(E_{i}^{s}\right),\mu\left(E_{i}^{s}\right)\right]=\left[\int X\rmd\mu,\int X\rmd\mu\right]\,.
 \end{aligned}

### 2019-02-01 dissertation.tex
dissertation.lyx Follow the following webpage to fix line breaking for inline math... https://tex.stackexchange.com/questions/19094/allowing-line-break-at-in-inline-math-mode-breaks-citations/19100#19100

@@
 
+% https://tex.stackexchange.com/questions/19094/allowing-line-break-at-in-inline-math-mode-breaks-citations/19100#19100
+\AtBeginDocument{%
+  \mathchardef\mathcomma\mathcode`\,
+  \mathcode`\,="8000 
+}
+{\catcode`,=\active
+  \gdef,{\mathcomma\nolinebreak[3]}
+}
+
 \@ifundefined{showcaptionsetup}{}{%
@@
 an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
-$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ so that
-$\mathbf{O}$ has spectral decomposition $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\proj{i}$.
+$\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$ so that $\mathbf{O}$
+has spectral decomposition $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\proj{i}$.
 If we restrict $\varphi$ on the classical event space~$2^{\Omega}$
@@
 an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
-$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with $\varphi\colon2^{\Omega}\rightarrow\events$
+$\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$ with $\varphi\colon2^{\Omega}\rightarrow\events$
 defined by Eq.~(\ref{eq:pullback-function}). Given a quantum probability
@@
 by calculating the purity relative to the semi-simple Lie algebra~$\fh$
-spanned by $\left\{ \jthSubsystem{\sigma}[x]{1},\jthSubsystem{\sigma}[y]{1},\jthSubsystem{\sigma}[z]{1},\ldots,\jthSubsystem{\sigma}[x]{n},\jthSubsystem{\sigma}[y]{n},\jthSubsystem{\sigma}[z]{n}\right\} $,
+spanned by $\{\jthSubsystem{\sigma}[x]{1},\jthSubsystem{\sigma}[y]{1},\jthSubsystem{\sigma}[z]{1},\ldots,\jthSubsystem{\sigma}[x]{n},\jthSubsystem{\sigma}[y]{n},\jthSubsystem{\sigma}[z]{n}\}$,
 \begin{equation}
@@
 \begin{prop}\label{appU.sec}The number of unit-norm states described
-by a $D$-dimensional vector $\left(\alpha_{0},\ldots,\alpha_{D-1}\right)$
-with coefficients $\alpha_{i}\in\Fpp$ is $p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)$.\end{prop}
+by a $D$-dimensional vector $(\alpha_{0},\ldots,\alpha_{D-1})$ with
+coefficients $\alpha_{i}\in\Fpp$ is $p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)$.\end{prop}
 
@@
 Since there are $p^{2}$ elements $\alpha\in\Fpp$, we must have $\left(p^{2}\right)^{D}=p^{2D}$
-possible values of a $D$-dimensional vector $\left(\alpha_{0},\ldots,\alpha_{D-1}\right)$.
+possible values of a $D$-dimensional vector $(\alpha_{0},\ldots,\alpha_{D-1})$.
 There are $p^{2}-1$ non-zero values of $\alpha\in\Fpp$, and we showed
@@
 As an example, consider the field $\ff{23}$. Looking at the squares
-of the numbers $\ff{23}=\left\{ 0,\ldots,22\right\} $ modulo 23,
-we find the $2$-centered uninterrupted sequence $S_{2}\left(5\right)=\left\{ 0,1,2,3,4\right\} $,
+of the numbers $\ff{23}=\{0,\ldots,22\}$ modulo 23, we find the $2$-centered
+uninterrupted sequence $S_{2}\left(5\right)=\left\{ 0,1,2,3,4\right\} $,
 followed by $5$, which is both the smallest quadratic non-residue
@@
 and~\ref{fig:dbsearch} always measure in the computational basis
-$\left\{ \ket{0},\ldots,\ket{i},\ldots,\ket{D-1}\right\} $. Indeed,
-it is sufficient to only consider measuring a quantum circuit in the
-computational basis because measuring in another basis is the same
-as applying a quantum gate and measuring in the computational basis.
-In this situation, the Born rule for pure states, Eq.~(\ref{eq:Born}),
-can be simplified as
+$\{\ket{0},\ldots,\ket{i},\ldots,\ket{D-1}\}$. Indeed, it is sufficient
+to only consider measuring a quantum circuit in the computational
+basis because measuring in another basis is the same as applying a
+quantum gate and measuring in the computational basis. In this situation,
+the Born rule for pure states, Eq.~(\ref{eq:Born}), can be simplified
+as
 \begin{equation}
@@
 is called the cardinal probability of measuring $\ket{i}$. For example,
-let $p=311$, $k=11$, and $D=2$. The permitted range is $S_{0}\left(11\right)=\left\{ -5,\ldots,-1,0,1,\ldots,5\right\} $,
+let $p=311$, $k=11$, and $D=2$. The permitted range is $S_{0}\left(11\right)=\{-5,\ldots,-1,0,1,\ldots,5\}$,
 given the dimension $D=2$, the allowed probability amplitude coefficients
@@
 where we identify $\bfalse$ and $\btrue$ as $0$ and $1$ as usual,
-and $\overline{0}=\left(0,\ldots,0\right)$.
+and $\overline{0}=(0,\ldots,0)$.
 
@@
 use the listed properties to build a contradiction. Consider the computational
-basis $\left\{ \ket{0},\ket{1},\ket{2},\ldots\right\} $, and the
-projectors formed by these vectors, $P_{0}=\proj{0}$, $P_{1}=\proj{1}$,
-and $P_{2}=\proj{2}$. Since $p\ge7$, $1+1+1$ is not $0$ in $\ff{p^{2}}$,
-and has the principal inverse field norm $\gamma=\fnorm*{3}$ as defined
-in Sec.~\ref{subsec:Vector-Spaces}. The unit-norm state $\ket{\oplus}=\frac{1}{\gamma}\left[\ket{0}+\ket{1}+\ket{2}\right]$
+basis $\{\ket{0},\ket{1},\ket{2},\ldots\}$, and the projectors formed
+by these vectors, $P_{0}=\proj{0}$, $P_{1}=\proj{1}$, and $P_{2}=\proj{2}$.
+Since $p\ge7$, $1+1+1$ is not $0$ in $\ff{p^{2}}$, and has the
+principal inverse field norm $\gamma=\fnorm*{3}$ as defined in Sec.~\ref{subsec:Vector-Spaces}.
+The unit-norm state $\ket{\oplus}=\frac{1}{\gamma}\left[\ket{0}+\ket{1}+\ket{2}\right]$
 can then be used as a parameter of $\muF$ and induces a QPMFF $\muF_{\oplus}$.
@@
 a mutually commuting subspace~$\eventsC$ whose elements are diagonalizable
-by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
+by a common orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$,
 the function $\varphi\colon2^{\Omega}\rightarrow\events$ defined
@@
 of events $\eventsC$ diagonalizable by a common orthonormal basis
-$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with the
-function $\varphi\colon2^{\Omega}\rightarrow\events$ defined by Eq.~(\ref{eq:pullback-function}).
-For any classical probability measure~$\mu$ consistent with the
-pullback of $\bar{\mu}$, i.e., $\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)$,
-there is a density matrix~$\rho$ consistent with $\bar{\mu}$ relative
-to $\eventsC$, $\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)$,
-such that the pullback of $\muB_{\rho}$ is $\mu$, i.e.,
+$\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$ with the function $\varphi\colon2^{\Omega}\rightarrow\events$
+defined by Eq.~(\ref{eq:pullback-function}). For any classical probability
+measure~$\mu$ consistent with the pullback of $\bar{\mu}$, i.e.,
+$\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)$, there is
+a density matrix~$\rho$ consistent with $\bar{\mu}$ relative to
+$\eventsC$, $\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)$, such
+that the pullback of $\muB_{\rho}$ is $\mu$, i.e.,
 \begin{equation}
@@
 \begin{proof}Since $\eventsC$ is a set of mutually commuting projections,
-they can be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $.
+they can be diagonalized by a common orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$.
 We can then follow Eq.~(\ref{eq:pullback-function}) to define $\varphi\colon2^{\Omega}\rightarrow\events$
@@
 an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
-$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ with $\varphi\colon2^{\Omega}\rightarrow\events$
+$\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$ with $\varphi\colon2^{\Omega}\rightarrow\events$
 defined by Eq.~(\ref{eq:pullback-function}). Given a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$,
@@
 eigenvalue~$\lambda_{i}^{s}$. Since $\mathbf{O}$ can be diagonalized
-by an orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
+by an orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$,
 each $P_{i}^{s}$ can be expressed as the sum of some projectors formed
@@
 \begin{thm}\label{thm:quantum-Rosenmuller}Consider an observable~$\mathbf{O}$
-diagonalizable by an orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $
+diagonalizable by an orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$
 and a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$.
@@
 $\lambda_{i}$ of that observable. To see this, note that given an
-orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $,
+orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$,
 a 0-deterministic QIVPM must map exactly one of the projectors $\proj{i}$
@@
 is a sequence of commuting observables, they can be diagonalized by
-a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $
+a common orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$
 with spectral decompositions 

### 2019-02-02 dissertation.tex
dissertation.lyx "Chapter 5 Toward a Quantum Measurement Theory with Error: Quantum Interval-Valued Probability" Reviewed...

@@
 as in Defs.~\ref{def:Choquet} and~\ref{def:expectation-values-QIVPM}.
-Notice that Eq.~(\ref{eq:pullback-real-measures}) and~(\ref{eq:pullback-differences})
-were simplified to the pullback of $\mul$ and $\mur$ which can be
-combined into the pullback of $\bar{\mu}$ as follows: 
+Notice that right-most side of Eq.~(\ref{eq:pullback-real-measures})
+and~(\ref{eq:pullback-differences}) are actually the pullback of
+$\mul$ and $\mur$ which can be combined into the pullback of $\bar{\mu}$
+as follows: 
 \begin{equation}
@@
 expectation value as well. In particular, Eq.~(\ref{eq:classical-real-interval-Choquet})
-can be extended to the following lemma.
+can be extended to the following theorem.
 
@@
 
-We then want to show the expectation value relative to a QIVPM generalizes
-the one relative to a classical IVPM by proving a quantum version
-of Thm.~\ref{thm:Rosenmuller}. However, since Lemma~\ref{lemma:density-matrix-pullback}
-hasn't established enough correspondence between classical and quantum
-cores, this theorem is weaker than its classical counterpart.
+Although we can faithfully extend Eq.~(\ref{eq:classical-real-interval-Choquet})
+to Thm.~\ref{lemma:expectation-singleton}, this theorem is weaker
+than its classical counterpart, Thm.~\ref{thm:Rosenmuller} because
+Lemma~\ref{lemma:density-matrix-pullback} hasn't established enough
+correspondence between classical and quantum cores.
 
@@
 possible choices of $\eventsC$. Thus, if Eq.~(\ref{eq:quantum-interval-expectation-core-1})
-is true, and we can also prove
-\begin{equation}
-\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\supseteq\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,,\label{eq:quantum-interval-expectation-core-supseteq}
-\end{equation}
-we then have Eq.~(\ref{eq:quantum-interval-expectation-core-equal}).
+is true, to prove Eq.~(\ref{eq:quantum-interval-expectation-core-equal}),
+it is sufficient to verify 
+\begin{equation}
+\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\supseteq\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,.\label{eq:quantum-interval-expectation-core-supseteq}
+\end{equation}
 
@@
 mapping nearly all projections to the \emph{unknown} interval~\unknown.
-There is however a subtlety: as shown in the theorem below, it is
-possible for an arbitrary assignment of intervals to projectors to
-be globally inconsistent.
-
-% \noindent For general QIVPMs mapping to imprecise intervals, we also
+There is however a subtlety: as we will show in Thm.~\ref{thm:Non-extensible-of-Gleason's}
+later, it is possible for an arbitrary assignment of intervals to
+projectors to be globally inconsistent, % \noindent For general QIVPMs mapping to imprecise intervals, we also
 % want to seek a simple rule to construct them, and to understand which
@@
 % be \emph{no} state consistent with some arbitrary QIVPM.
-
-Like how we proved Thm.~\ref{cor:Kochen-Specker-IVPM}, we need other
-two lemmas to simplify the proof of the convexity condition.
+but before proving Thm.~\ref{thm:Non-extensible-of-Gleason's}, we
+need other two lemmas to simplify the proof of the convexity condition
+again.
 
@@
 If neither of the previous possibilities is true, i.e., they have
-some intersections, but not a subset relation, then $E_{0}\cap E_{1}$,
+some intersections, but no subset relation, then $E_{0}\cap E_{1}$,
 $E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$ are all non-empties.
 Together with the fact that $\Omega$ has only three elements, they
-are all singleton sets.
+are all singleton sets. These three possibilities are going to be
+discussed as follow.
 \begin{itemize}
@@
 
-After we proved the lemmas, we can state and prove the theorem.
+After we proved the lemmas, we can state and prove the theorem that
+some assignment of intervals to projectors can be globally inconsistent..
 
@@
 is a QIVPM\@. Since it is easy to verify $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}),
-by Lemma~\ref{thm:convex-3-1}, it is sufficient to verify for each
-pair of orthogonal states $\ket{\psi'}$ and $\ket{\psi''}$ 
-\begin{equation}
-\bar{\mu}\left(\proj{\psi'}+\proj{\psi''}\right)\subseteq\bar{\mu}\left(\proj{\psi'}\right)+\bar{\mu}\left(\proj{\psi''}\right)\,.\label{amr-2}
-\end{equation}
+it is sufficient by Lemma~\ref{thm:convex-3-1} to verify 
+\begin{equation}
+\bar{\mu}\left(\proj{\psi'}+\proj{\psi''}\right)\subseteq\bar{\mu}\left(\proj{\psi'}\right)+\bar{\mu}\left(\proj{\psi''}\right)\label{amr-2}
+\end{equation}
+for each pair of orthogonal states $\ket{\psi'}$ and $\ket{\psi''}$.
 Since $\ket{0}$, $\ket{\ps}$, and $\ket{\ps'}$ are not orthogonal
@@
 $\necess$, an interval map $\ultramodular\colon\left[0,1\right]\rightarrow\mathscr{I}$
-is called ultramodular if: 
+is called ultramodular if
 \begin{align}
@@
 and for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
-such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have: 
+such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have
 \begin{equation}
@@
 such that $\ultramodular\circ\mu$ is not a classical IVPM\@. Consider
-an orthonormal basis $\Omega$ containing $\ket{0}$, $\ket{1}$,
-$\ket{2}$, $\ket{3}$, \ldots , and $\ket{D-1}$, and $\varphi\colon2^{\Omega}\rightarrow\events$
-defined by Eq.~(\ref{eq:pullback-function}). Notice that the pullback
-of our previous quantum probability measure $\muB_{\rho}$, $\varphi^{*}\muB_{\rho}$,
-is a classical probability measure. If we pick $\mu$ as $\varphi^{*}\muB_{\rho}$,
-then the induced map $\ultramodular\circ\mu$ fails to be a classical
-IVPM for the same reason as in the quantum case.\end{proof}
+an orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$
+and $\varphi\colon2^{\Omega}\rightarrow\events$ defined by Eq.~(\ref{eq:pullback-function}).
+Notice that the pullback of our previous quantum probability measure
+$\muB_{\rho}$, $\varphi^{*}\muB_{\rho}$, is a classical probability
+measure. If we pick $\mu$ as $\varphi^{*}\muB_{\rho}$, then the
+induced map $\ultramodular\circ\mu$ fails to be a classical IVPM
+for the same reason as in the quantum case.\end{proof}
 

### 2019-02-04 dissertation.tex
dissertation.lyx Acknowledgments Adding a table...

@@
 
+% https://wiki.lyx.org/LyX/Tables#tabularx
+%% Hack by Heiko Oberdiek (on de.comp.text.tex)
 \usepackage{tabularx}
+
+%% Redefine the standard table
+\let\ORIGtabular\tabular
+\let\ORIGendtabular\endtabular
+\let\ORIGtabularx\tabularx
+\renewcommand*{\tabularx}{%
+  \def\tabular{%
+    \let\endtabular\ORIGendtabular
+    \ORIGtabular
+  }%
+  \ORIGtabularx
+}
+
 \renewcommand{\tabularxcolumn}[1]{m{#1}}
@@
 \noindent \begin{centering}
-\caption{\label{tab:acknowledgments}I want to thank the professors co-authored
-with me, suggested me as a committee member, and taught me, and the
-collaboration or supervised works or studies become the basis of or
-inspire this dissertation.}
+\caption{\label{tab:committee}I want to thank the professors co-authored with
+me, suggested me as a committee member, and taught me, and the collaboration
+or supervised works or studies become the basis of or inspire this
+dissertation.}
 \par\end{centering}
@@
 \end{sidewaystable}
-I want to thanks all my professors co-authored with me, suggested
-me as a committee members, and taught me so that our work or studies
-became the bases or inspired any part of my dissertation as listed
-in Table~\ref{tab:acknowledgments}. Especially, Prof.\ Andrew J.
-Hanson, Prof.\ Gerardo Ortiz, and Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
+I want to thanks the professors served in all my committees. These
+professors advised me as committee members and taught me while we
+wrote papers together and when I took their courses. Most of my dissertation
+is either based on these papers or inspired by the studies supervised
+by them as listed in Table~\ref{tab:committee}. Especially, Prof.\ Andrew
+J. Hanson, Prof.\ Gerardo Ortiz, and Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
 meet me weekly for the pass few years, read and tried to understand
@@
 
+\begin{sidewaystable}
+\noindent \begin{centering}
+\caption{\label{tab:teacher}The knowledge I learned from teachers in other
+courses help me consolidate this dissertation, where IUB stands for
+Indiana University Bloomington and NTU stands for National Taiwan
+University.}
+\par\end{centering}
+%% ERT block 1 (before LyX tabular)
+\renewcommand{\tabular}{\tabularx{\linewidth}}
+\renewcommand{\endtabular}{\endtabularx} 
+\begin{tabular}{ccM{MATH-M522}M{English~for~International~Graduate~Students:}Y}
+\toprule 
+\addlinespace
+Instructor & School & Course & Title & Relation with the dissertation\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\midrule 
+\addlinespace
+Tom Lewis & IUB & SLST-T501 & English for International Graduate Students:\linebreak[3] Academic
+Writing & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
+paper.\tabularnewline\addlinespace
+\addlinespace
+\midrule 
+\addlinespace
+Michael A. Mandell & IUB & MATH-M522 & Topology II & The textbook~\cite{Hatcher2001} is cited in Chapters~\ref{chap:Introduction}
+and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline\addlinespace
+\addlinespace
+\midrule 
+\addlinespace
+Steven Myers & IUB & CSCI-B502 & Computational Complexity & The textbook~\cite{AroraBarak2009} is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline\addlinespace
+\addlinespace
+\midrule 
+\addlinespace
+Valery Lunts & IUB & MATH-M501 & Survey of Algebra & The textbook~\cite{DummitFoote2004} is cited in Sec.~\ref{sec:background},
+\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
+\addlinespace
+\midrule 
+\addlinespace
+Huah Chu (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & Algebra(I)\linebreak[3] Algebra(II) & The textbook~\cite{Artin1991} is cited in Sec.~\ref{CQC1qubitBloch.sec},
+\ref{sec:background}, \ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
+\midrule
+\addlinespace
+\addlinespace
+Jin-Tzu Chen (陳金次) & NTU & 201~31300 & Functions of a Complex Variable & The textbook~\cite{GAMELIN2003} is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline\addlinespace
+\bottomrule
+\addlinespace
+\end{tabular}% ERT block 2 (after LyX tabular)
+\renewcommand{\tabular}{\ORIGtabular}
+\renewcommand{\endtabular}{\ORIGendtabular} 
+\end{sidewaystable}
 To have the current the content of the dissertation, I would also
@@
 results were improved and motivated the transition from DQT to QIVPM
-in Sec.~\ref{sec:Toward-IVPM}. Also, the unpublished computation
-for the discrete Deutsch algorithm \cite{Deutsch1985,544199,Mermin2007}
-is organized in the term paper for SLST-T501 Academic Writing course.
-I want to thank Prof.\ Tom Lewis for proof-reading them, and they
-become the bases of Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
+in Sec.~\ref{sec:Toward-IVPM}. Besides of my committee members,
+the knowledge I learned from teachers in other courses help me consolidate
+this dissertation as listed in Table~\ref{tab:teacher}.
+
 Besides of Prof.\ Tom Lewis, my other English teachers, especially
@@
 Others who help me indirectly on the content of the dissertation including
-Kin Wai Chan, Prof.\ Huah Chu (朱樺), Weihua Liu (刘伟华), Caren Liu
-(劉鈺平), Meng-Wei Chen (陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen
-(陳昭宏)\ldots , etc. This could be listed on and on. I still thank
-you even if your name is not listed here, and sorry for my bad memory.
+Kin Wai Chan, Weihua Liu (刘伟华), Caren Liu (劉鈺平), Meng-Wei Chen
+(陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen (陳昭宏)\ldots , etc. This
+could be listed on and on. I still thank you even if your name is
+not listed here, and sorry for my bad memory.
 
@@
 in a way that outperforms conventional quantum computing. The classical
-\usat\ problem (also known as $\lang{USAT}$ or $\lang{UNAMBIGUOUS-SAT}$)
+\usat\ problem (also known as $\lang{USAT}$~\cite{AroraBarak2009}
+or $\lang{UNAMBIGUOUS-SAT}$) %
 \begin{comment}

### 2019-02-05 dissertation.tex
dissertation.lyx ACKNOWLEDGMENTS Updates, and commit before adjust the spacing in document class...

@@
 \caption{\label{tab:committee}I want to thank the professors co-authored with
-me, suggested me as a committee member, and taught me, and the collaboration
+me, suggested me as a committee member, and taught me; the collaboration
 or supervised works or studies become the basis of or inspire this
@@
 \midrule
-\addlinespace
 \midrule 
@@
 paper.\tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 Steven Myers & IUB & CSCI-B502 & Computational Complexity & The textbook~\cite{AroraBarak2009} is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 \ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 \addlinespace
-\addlinespace
 Jin-Tzu Chen (陳金次) & NTU & 201~31300 & Functions of a Complex Variable & The textbook~\cite{GAMELIN2003} is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline\addlinespace
 \bottomrule
-\addlinespace
 \end{tabular}% ERT block 2 (after LyX tabular)
@@
 the knowledge I learned from teachers in other courses help me consolidate
-this dissertation as listed in Table~\ref{tab:teacher}.
-
-Besides of Prof.\ Tom Lewis, my other English teachers, especially
-Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
-Chen (谌可心), taught me a lot on how to communicate in English as well.
+this dissertation as listed in Table~\ref{tab:teacher}. Although
+not directly relating to the dissertation, I have to thank for your
+teaching to make me more mature and easier to communicate with others,
+especially my English teachers, Traci Nagle, Elizabeth ``Betsy''
+Merceron, and Kexin ``Casey'' Chen (谌可心).
+
+Many people in both the departments of Mathematics and Computer Science
+have done everything to make my double-major smooth. \todo{Acknowledgments
+cleaned up until here. }I need to thank all of them, especially directors
+of graduate study in Mathematics, especially Prof.\ Christopher Judge,
+Prof.\ Matthias Weber, and Prof.\ Michael A.\ Mandell; directors
+of Ph.D. study in Computer Science, especially Prof.\ Yuqing Melanie
+Wu (吴愈青) and Prof.\ \textturkish{Funda Ergun}.
+
 Others who help me indirectly on the content of the dissertation including
@@
 not listed here, and sorry for my bad memory.
-
-Many people in both the departments of Mathematics and Computer Science
-have done everything to make my double-major smooth. \todo{Acknowledgments
-cleaned up until here. }I need to thank all of them, especially directors
-of graduate study in Mathematics, especially Prof.\ Christopher Judge
-and Prof.\ Matthias Weber; directors of Ph.D. study in Computer Science,
-especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
-Ergun}.
 

### 2019-02-06 dissertation.tex
dissertation.lyx Fixing the space in tables...

@@
 \begin{sidewaystable}
-\noindent \begin{centering}
-\caption{\label{tab:committee}I want to thank the professors co-authored with
+\noindent \centering{}\caption{\label{tab:committee}I want to thank the professors co-authored with
 me, suggested me as a committee member, and taught me; the collaboration
@@
 dissertation.}
-\par\end{centering}
-\noindent \centering{}\noindent \centering{}%
-\begin{tabularx}{\linewidth}{M{MATH-M781}M{Co-author}M{(\textarabic{عمرو صبري})}M{Co-author}M{Thurston}M{Shouhong}M{Lawrence}Y}
+%% ERT block 1 (before LyX tabular)
+\renewcommand{\tabular}{\tabularx{\linewidth}}
+\renewcommand{\endtabular}{\endtabularx} 
+\begin{tabular}{M{MATH-M781}M{Co-author}M{(\textarabic{عمرو~صبري})}M{Co-author}M{Thurston}M{Shouhong}M{Lawrence}Y}
 \toprule 
@@
 Hanson & Dylan\nolinebreak[3] Paul Thurston & Shouhong Wang\linebreak[3] (汪守宏) & Lawrence\nolinebreak[3] S.\linebreak[2] Moss & Relation with the dissertation\tabularnewline\addlinespace
-\addlinespace
 \midrule
@@
 \addlinespace
- & Co-author & Co-author & Co-author &  &  &  & Most of Chapters~\ref{chap:Conventional-Quantum-Theory}, \ref{chap:Unrestricted-Finite-Fields},
-and~\ref{chap:DQT=000026DQC} is based on~\cite{geometry2013} and~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM} is
-based on~\cite{THOS2018}.\tabularnewline\addlinespace
-\addlinespace
+ & Co-author & Co-author & Co-author &  &  &  & Most of Chapters~\ref{chap:Conventional-Quantum-Theory}, \ref{chap:Unrestricted-Finite-Fields},and~\ref{chap:DQT=000026DQC}
+is based on~\cite{geometry2013} and~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
+is based on~\cite{THOS2018}.\tabularnewline\addlinespace
 \midrule 
 \addlinespace
-Research committee & Co-chair & Co-chair & Member & Co-chair & Member &  & Some questions in the dissertation proposal are answered in Chapter~\ref{chap:QIVPM},
-and some of the remaining ones are explained in Chapter~\ref{chap:Further-Discussion}.\tabularnewline\addlinespace
-\addlinespace
+Research committee & Co-chair & Co-chair & Member & Co-chair & Member &  & Some questions in the dissertation proposal are answered in Chapter~\ref{chap:QIVPM},and
+some of the remaining ones are explained in Chapter~\ref{chap:Further-Discussion}.\tabularnewline\addlinespace
 \midrule 
@@
 inspires Chapter~\ref{chap:Introduction}.\tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 exam (chaired by Prof.\ Sabry) inspires Chapter~\ref{chap:Introduction}.\tabularnewline\addlinespace
-\addlinespace
 \midrule 
 \addlinespace
-PHYS-P700 & Instructor &  &  &  &  &  & The textbook~\cite{Mermin2007} is
-cited in Chapters~\ref{chap:Introduction}, \ref{chap:Conventional-Quantum-Theory},
+PHYS-P700 & Instructor &  &  &  &  &  & The textbook~\cite{Mermin2007} of \emph{Quantum Computation and Information}
+is cited in Chapters~\ref{chap:Introduction}, \ref{chap:Conventional-Quantum-Theory},
 \ref{chap:DQT=000026DQC}, and~\ref{chap:QIVPM}.\tabularnewline\addlinespace
-\addlinespace
 \midrule 
 \addlinespace
-MATH-M781 &  &  &  &  &  & Instructor & The presented paper~\cite{Abramsky2012} is cited in Sec.~\ref{subsec:Classical-and-Quantum}.\tabularnewline\addlinespace
-\addlinespace
+CSCI-B629 &  & Instructor &  &  &  &  & The textbook~\cite{hottbook2013} of \emph{Homotopy Type Theory}
+is cited in Sec.~\ref{discretequantumtheoryIIb}.\tabularnewline\addlinespace
 \midrule
 \addlinespace
-Tier 3 committee & Co-chair & Co-chair &  & Member &  & Co-chair & Two of
-the assigned papers in the Tier 3 exam, \cite{Schumacher2012-SCHMQT}
-and~\cite{doi:10.1142/S0217984913500644},
+Tier 3 committee & Co-chair & Co-chair &  & Member &  & Co-chair & Two of the assigned papers in the Tier 3 exam \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644}
 are cited in Sec.~\ref{modalquantum}.\tabularnewline\addlinespace
-\addlinespace
+\midrule
+\addlinespace
+MATH-M781 &  &  &  &  &  & Instructor & The presented paper~\cite{Abramsky2012} of \emph{Coalgebra} is
+cited in Sec.~\ref{subsec:Classical-and-Quantum}.\tabularnewline\addlinespace
 \bottomrule
-\end{tabularx}
+\end{tabular}% ERT block 2 (after LyX tabular)
+\renewcommand{\tabular}{\ORIGtabular}
+\renewcommand{\endtabular}{\ORIGendtabular} 
 \end{sidewaystable}
@@
 
-\begin{sidewaystable}
-\noindent \begin{centering}
-\caption{\label{tab:teacher}The knowledge I learned from teachers in other
-courses help me consolidate this dissertation, where IUB stands for
-Indiana University Bloomington and NTU stands for National Taiwan
-University.}
-\par\end{centering}
-%% ERT block 1 (before LyX tabular)
-\renewcommand{\tabular}{\tabularx{\linewidth}}
-\renewcommand{\endtabular}{\endtabularx} 
-\begin{tabular}{ccM{MATH-M522}M{English~for~International~Graduate~Students:}Y}
-\toprule 
-\addlinespace
-Instructor & School & Course & Title & Relation with the dissertation\tabularnewline\addlinespace
-\midrule
-\midrule 
-\addlinespace
-Tom Lewis & IUB & SLST-T501 & English for International Graduate Students:\linebreak[3] Academic
-Writing & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
-paper.\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-Michael A. Mandell & IUB & MATH-M522 & Topology II & The textbook~\cite{Hatcher2001} is cited in Chapters~\ref{chap:Introduction}
-and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-Steven Myers & IUB & CSCI-B502 & Computational Complexity & The textbook~\cite{AroraBarak2009} is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-Valery Lunts & IUB & MATH-M501 & Survey of Algebra & The textbook~\cite{DummitFoote2004} is cited in Sec.~\ref{sec:background},
-\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-Huah Chu (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & Algebra(I)\linebreak[3] Algebra(II) & The textbook~\cite{Artin1991} is cited in Sec.~\ref{CQC1qubitBloch.sec},
-\ref{sec:background}, \ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
-\midrule
-\addlinespace
-Jin-Tzu Chen (陳金次) & NTU & 201~31300 & Functions of a Complex Variable & The textbook~\cite{GAMELIN2003} is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}% ERT block 2 (after LyX tabular)
-\renewcommand{\tabular}{\ORIGtabular}
-\renewcommand{\endtabular}{\ORIGendtabular} 
-\end{sidewaystable}
 To have the current the content of the dissertation, I would also
@@
 Merceron, and Kexin ``Casey'' Chen (谌可心).
+\begin{table}[t]
+\noindent \begin{centering}
+\caption{\label{tab:teacher}The knowledge I learned from teachers in other
+courses help me consolidate this dissertation, where IUB stands for
+Indiana University Bloomington and NTU stands for National Taiwan
+University.}
+\par\end{centering}
+%% ERT block 1 (before LyX tabular)
+\renewcommand{\tabular}{\tabularx{\linewidth}}
+\renewcommand{\endtabular}{\endtabularx} 
+\begin{tabular}{M{Jin-Tzu~Chen}cM{MATH-M522}Y}
+\toprule 
+\addlinespace
+Instructor & School & Course & Relation with the dissertation\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
+Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
+paper of \emph{Academic Writing}.\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
+in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
+is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
+is cited in Sec.~\ref{sec:background}, \ref{discretequantumtheoryI},
+and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
+is cited in Sec.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
+\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
+\midrule
+\addlinespace
+Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
+is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline\addlinespace
+\bottomrule
+\end{tabular}% ERT block 2 (after LyX tabular)
+\renewcommand{\tabular}{\ORIGtabular}
+\renewcommand{\endtabular}{\ORIGendtabular} 
+\end{table}
 
@@
 and their mathematical models with the inspired quantum models.}
-
-\centering{}\centering{}%
-\begin{tabularx}{\linewidth}{YcYY}
+%% ERT block 1 (before LyX tabular)
+\renewcommand{\tabular}{\tabularx{\linewidth}}
+\renewcommand{\endtabular}{\endtabularx} 
+\begin{tabular}{YcYY}
 \toprule 
@@
 Physical quantity & Discrete & Discrete with extreme small units & Continuous, or no evidence to support they are discrete\tabularnewline\addlinespace
-\addlinespace
+\midrule 
 \addlinespace
 Computational device & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
-\addlinespace
 \midrule
+\midrule 
 \addlinespace
 Mathematical representation & Integer & Real number & Real number\tabularnewline\addlinespace
-\addlinespace
+\midrule 
 \addlinespace
 Computational model & Turing machine & BCSS machine & BCSS machine\tabularnewline\addlinespace
-\addlinespace
 \midrule
-\addlinespace
-How does the theorical model predict the behavior of the physical device? & 
-Reliably & 
-Not reliably, but after we have better technology to manipulate the minimum units, we can more reliably predict the physical phenomenon and their computational power by a better discrete model. & 
-Not reliably, because precision can never be high enough, and the difference between their computational power might not be able compensated by error analysis techniques. \tabularnewline\addlinespace
-\addlinespace
 \midrule 
 \addlinespace
+How does the theoretical model predict the behavior of the physical
+device? & Reliably & Not reliably, but after we have better technology to manipulate the
+minimum units, we can more reliably predict the physical phenomenon
+and their computational power by a better discrete model. & Not reliably, because precision can never be high enough, and the
+difference between their computational power might not be able compensated
+by error analysis techniques.\tabularnewline\addlinespace
+\midrule 
+\addlinespace
 Inspired quantum model &  & Quantum theories and computing over finite fields & Quantum interval-valued probability measures (QIVPM)\tabularnewline\addlinespace
-\addlinespace
 \bottomrule
-\end{tabularx}
+\end{tabular}% ERT block 2 (after LyX tabular)
+\renewcommand{\tabular}{\ORIGtabular}
+\renewcommand{\endtabular}{\ORIGendtabular} 
 \end{sidewaystable}
@@
 
-\begin{tabularx}{\linewidth}{YYYYYYY}
+%% ERT block 1 (before LyX tabular)
+\renewcommand{\tabular}{\tabularx{\linewidth}}
+\renewcommand{\endtabular}{\endtabularx} 
+\begin{tabular}{YYYYYYY}
 \toprule 
@@
  & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
-\addlinespace
 \midrule
@@
 \addlinespace
- & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to~\ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline\addlinespace
-\addlinespace
-\midrule
-\addlinespace
-Expectation value & Defined & Undefined & Formally defined & Undefined &  & Defined\tabularnewline\addlinespace
-\addlinespace
+ & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
 \midrule
@@
 \addlinespace
+States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline\addlinespace
+\midrule 
+\addlinespace
+Expectation value & Defined & Undefined & Formally defined & Undefined &  & Defined\tabularnewline\addlinespace
+\midrule
+\midrule 
+\addlinespace
  &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 Deutsch's algorithm & Yes & Maybe no & Yes & Yes &  & \tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 Efficiently solve $\usat$ & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline\addlinespace
-\addlinespace
 \bottomrule
-\end{tabularx}
+\end{tabular}% ERT block 2 (after LyX tabular)
+\renewcommand{\tabular}{\ORIGtabular}
+\renewcommand{\endtabular}{\ORIGendtabular} 
 \end{sidewaystable}
@@
 \addlinespace
-\addlinespace
 $\mu_{1}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $0$ & $1$  & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & \ldots\tabularnewline\addlinespace
-\addlinespace
 \addlinespace
@@
 \bottomrule
-\addlinespace
 \end{tabular}
@@
 \addlinespace
-\addlinespace
 $\left(1+\rmi\right)^{j}$ & $1$ & $1+\rmi$ & $-\rmi$ & $1-\rmi$ & $-1$ & $-1-\rmi$ & $\rmi$ & $-1+\rmi$\tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $\left(1-\rmi\right)^{j}$ & $1$ & $1-\rmi$ & $\rmi$ & $1+\rmi$ & $-1$ & $-1+\rmi$ & $-\rmi$ & $-1-\rmi$\tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $\left(-1+\rmi\right)^{j}$ & $1$ & $-1+\rmi$ & $\rmi$ & $-1-\rmi$ & $-1$ & $1-\rmi$ & $-\rmi$ & $1+\rmi$\tabularnewline\addlinespace
-\addlinespace
 \addlinespace
@@
 \addlinespace
-\addlinespace
 $-1$ & $4$ & $1$ & $1-\rmi$\tabularnewline\addlinespace
-\addlinespace
 \addlinespace
@@
 \addlinespace
-\addlinespace
 $\bfalse$ & $\bfalse$ & $\bfalse$ & $\btrue$ & $\btrue$\tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $\btrue$ & $\bfalse$ & $\btrue$ & $\bfalse$ & $\btrue$\tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 $p$ & $3$ & $7$ & $23$ & $71$ & $311$ & $479$ & $1559$ & $5711$ & $10559$ & $18191$ & \ldots\tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 \addlinespace
-\addlinespace
 $\pi\left(k\right)$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ & $8$ & $9$ & $10$ & \ldots\tabularnewline\addlinespace
 \bottomrule
-\addlinespace
 \end{tabular}
@@
 \addlinespace
-\addlinespace
 $D=1$  & $F^{1}\left(11\right)=\left\{ 0,\pm1,\pm2,\pm\rmi,\pm2\rmi,(\pm1\pm\rmi),(\pm1\pm2\rmi),(\pm2\pm\rmi)\right\} $\tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $D=2$  & $F^{2}\left(11\right)=\left\{ 0,\pm1,\pm\rmi,(\pm1\pm\rmi)\right\} $ \tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $D=3$  & $F^{3}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $D=4$  & $F^{4}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $D=5$  & $F^{5}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline\addlinespace
 \addlinespace
-\addlinespace
-$D\geq6$  & $F^{D}\left(11\right)=\left\{ 0\right\} $ \tabularnewline\addlinespace
+$D\geq6$  & $F^{D}\left(11\right)=\left\{ 0\right\} $\tabularnewline\addlinespace
 \bottomrule
-\addlinespace
 \end{tabular}
@@
 \addlinespace
-\addlinespace
 $1\ket{0}$ & $1$ & $0$ & $1$ & $\cardp{1}{1}$ & $\cardp{0}{1}$\tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $1\ket{0}+1\ket{1}$ & $1$ & $1$ & $2$ & $\cardp{1}{2}$ & $\cardp{1}{2}$\tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $1\ket{0}+(1+\rmi)\ket{1}$ & $1$ & $2$ & $3$ & $\cardp{1}{3}$ & $\cardp{2}{3}$\tabularnewline\addlinespace
-\addlinespace
 \addlinespace
@@
 $p$ & \ldots{} & $422231$ & \ldots{} & $196265095009$ & \ldots{} &  & \ldots{} &  & \ldots\tabularnewline\addlinespace
-\addlinespace
 \midrule 
@@
 \addlinespace
-\addlinespace
 $\pi\left(k\right)$ & \ldots{} & $12$ & \ldots{} & $32$ & \ldots{} & $55$ & \ldots{} & $3513$ & \ldots\tabularnewline\addlinespace
 \bottomrule
-\addlinespace
 \end{tabular}
@@
 \addlinespace
-\addlinespace
 $1$ & $1$ & $E$ & $\Omega$ & $1$ & $0.3$ & $1$ & $0.2$\tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 $2$ & $2$ & $\overline{E}$ & $\overline{E}$ & $0.7$ & $0.7$ & $0.8$ & $0.8$\tabularnewline\addlinespace
-\addlinespace
 \addlinespace
@@
 \addlinespace
-\addlinespace
 $\mathbb{0}$ & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 All one-dimensional projectors & $\left[0,0\right]$  & $\left[0,\tfrac{1}{4}\right]$  & $\left[0,\tfrac{1}{3}\right]$  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline\addlinespace
 \addlinespace
-\addlinespace
 All two-dimensional projectors & $\left[1,1\right]$  & $\left[\tfrac{3}{4},1\right]$  & $\left[\tfrac{2}{3},1\right]$  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$  & $\left[\tfrac{1}{2},1\right]$\tabularnewline\addlinespace
-\addlinespace
 \addlinespace

### 2019-02-06 dissertation.tex
dissertation.lyx Fix space and place of floats...

@@
 \usepackage{graphicx}
+\usepackage{setspace}
 \usepackage[all]{xy}
@@
 
+\usepackage[font=doublespacing]{caption}
+
 \@ifundefined{showcaptionsetup}{}{%
@@
 \begin{sidewaystable}
+\begin{doublespace}
 \noindent \centering{}\caption{\label{tab:committee}I want to thank the professors co-authored with
@@
 \toprule 
-\addlinespace
 Committee or course & Gerardo Ortiz & Amr\nolinebreak[3] A.
 Sabry\linebreak[3] (\textarabic{عمرو صبري}) & Andrew\nolinebreak[3] J.
-Hanson & Dylan\nolinebreak[3] Paul Thurston & Shouhong Wang\linebreak[3] (汪守宏) & Lawrence\nolinebreak[3] S.\linebreak[2] Moss & Relation with the dissertation\tabularnewline\addlinespace
+Hanson & Dylan\nolinebreak[3] Paul Thurston & Shouhong Wang\linebreak[3] (汪守宏) & Lawrence\nolinebreak[3] S.\linebreak[2] Moss & Relation with the dissertation\tabularnewline
 \midrule
 \midrule 
-\addlinespace
  & Co-author & Co-author & Co-author &  &  &  & Most of Chapters~\ref{chap:Conventional-Quantum-Theory}, \ref{chap:Unrestricted-Finite-Fields},and~\ref{chap:DQT=000026DQC}
 is based on~\cite{geometry2013} and~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
-is based on~\cite{THOS2018}.\tabularnewline\addlinespace
+is based on~\cite{THOS2018}.\tabularnewline
 \midrule 
-\addlinespace
 Research committee & Co-chair & Co-chair & Member & Co-chair & Member &  & Some questions in the dissertation proposal are answered in Chapter~\ref{chap:QIVPM},and
-some of the remaining ones are explained in Chapter~\ref{chap:Further-Discussion}.\tabularnewline\addlinespace
+some of the remaining ones are explained in Chapter~\ref{chap:Further-Discussion}.\tabularnewline
 \midrule 
-\addlinespace
  &  & Supervisor &  &  &  &  & The application for ``Rethinking Foundations of Physics'' 2017 workshop
-inspires Chapter~\ref{chap:Introduction}.\tabularnewline\addlinespace
+inspires Chapter~\ref{chap:Introduction}.\tabularnewline
 \midrule 
-\addlinespace
 Advisory committee & Member & Member & Member & Member &  &  & The survey of real computation in the Computer Science qualifying
-exam (chaired by Prof.\ Sabry) inspires Chapter~\ref{chap:Introduction}.\tabularnewline\addlinespace
+exam (chaired by Prof.\ Sabry) inspires Chapter~\ref{chap:Introduction}.\tabularnewline
 \midrule 
-\addlinespace
 PHYS-P700 & Instructor &  &  &  &  &  & The textbook~\cite{Mermin2007} of \emph{Quantum Computation and Information}
 is cited in Chapters~\ref{chap:Introduction}, \ref{chap:Conventional-Quantum-Theory},
-\ref{chap:DQT=000026DQC}, and~\ref{chap:QIVPM}.\tabularnewline\addlinespace
+\ref{chap:DQT=000026DQC}, and~\ref{chap:QIVPM}.\tabularnewline
 \midrule 
-\addlinespace
 CSCI-B629 &  & Instructor &  &  &  &  & The textbook~\cite{hottbook2013} of \emph{Homotopy Type Theory}
-is cited in Sec.~\ref{discretequantumtheoryIIb}.\tabularnewline\addlinespace
+is cited in Sec.~\ref{discretequantumtheoryIIb}.\tabularnewline
 \midrule
-\addlinespace
 Tier 3 committee & Co-chair & Co-chair &  & Member &  & Co-chair & Two of the assigned papers in the Tier 3 exam \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644}
-are cited in Sec.~\ref{modalquantum}.\tabularnewline\addlinespace
+are cited in Sec.~\ref{modalquantum}.\tabularnewline
 \midrule
-\addlinespace
 MATH-M781 &  &  &  &  &  & Instructor & The presented paper~\cite{Abramsky2012} of \emph{Coalgebra} is
-cited in Sec.~\ref{subsec:Classical-and-Quantum}.\tabularnewline\addlinespace
+cited in Sec.~\ref{subsec:Classical-and-Quantum}.\tabularnewline
 \bottomrule
@@
 \renewcommand{\endtabular}{\ORIGendtabular} 
+\end{doublespace}
 \end{sidewaystable}
@@
 \begin{table}[t]
-\noindent \begin{centering}
-\caption{\label{tab:teacher}The knowledge I learned from teachers in other
+\begin{doublespace}
+\noindent \centering{}\caption{\label{tab:teacher}The knowledge I learned from teachers in other
 courses help me consolidate this dissertation, where IUB stands for
@@
 University.}
-\par\end{centering}
 %% ERT block 1 (before LyX tabular)
@@
 \toprule 
-\addlinespace
-Instructor & School & Course & Relation with the dissertation\tabularnewline\addlinespace
+Instructor & School & Course & Relation with the dissertation\tabularnewline
 \midrule
 \midrule 
-\addlinespace
 Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
-paper of \emph{Academic Writing}.\tabularnewline\addlinespace
+paper of \emph{Academic Writing}.\tabularnewline
 \midrule 
-\addlinespace
 Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
-in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline\addlinespace
+in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
 \midrule 
-\addlinespace
 Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
-is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline\addlinespace
+is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
 \midrule 
-\addlinespace
 Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
 is cited in Sec.~\ref{sec:background}, \ref{discretequantumtheoryI},
-and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
+and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
 \midrule 
-\addlinespace
 Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
 is cited in Sec.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
-\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
+\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
 \midrule
-\addlinespace
 Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
-is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline\addlinespace
+is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
 \bottomrule
@@
 \renewcommand{\endtabular}{\ORIGendtabular} 
+\end{doublespace}
 \end{table}
@@
 \begin{sidewaystable}
-\caption{\label{tab:Comparison}Comparison between the classical quantities
+\begin{doublespace}
+\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical quantities
 and their mathematical models with the inspired quantum models.}
@@
 \toprule 
-\addlinespace
-Physical quantity & Discrete & Discrete with extreme small units & Continuous, or no evidence to support they are discrete\tabularnewline\addlinespace
+Physical quantity & Discrete & Discrete with extreme small units & Continuous, or no evidence to support they are discrete\tabularnewline
 \midrule 
-\addlinespace
-Computational device & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
+Computational device & Digital computer & Analog computer & Analog computer\tabularnewline
 \midrule
 \midrule 
-\addlinespace
-Mathematical representation & Integer & Real number & Real number\tabularnewline\addlinespace
+Mathematical representation & Integer & Real number & Real number\tabularnewline
 \midrule 
-\addlinespace
-Computational model & Turing machine & BCSS machine & BCSS machine\tabularnewline\addlinespace
+Computational model & Turing machine & BCSS machine & BCSS machine\tabularnewline
 \midrule
 \midrule 
-\addlinespace
 How does the theoretical model predict the behavior of the physical
@@
 difference between their computational power might not be able compensated
-by error analysis techniques.\tabularnewline\addlinespace
+by error analysis techniques.\tabularnewline
 \midrule 
-\addlinespace
-Inspired quantum model &  & Quantum theories and computing over finite fields & Quantum interval-valued probability measures (QIVPM)\tabularnewline\addlinespace
+Inspired quantum model &  & Quantum theories and computing over finite fields & Quantum interval-valued probability measures (QIVPM)\tabularnewline
 \bottomrule
@@
 \begin{sidewaystable}
-\caption{\label{tab:organization}Comparison among our models, where the upper
+\begin{doublespace}
+\noindent \centering{}\caption{\label{tab:organization}Comparison among our models, where the upper
 half of the table lists their quantum mechanical definitions and properties,
 and the lower half of the table lists their computational power.}
-
 %% ERT block 1 (before LyX tabular)
@@
 \toprule 
-\addlinespace
- & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
+ & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline
 \midrule
 \midrule 
-\addlinespace
- & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
+ & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline
+\midrule 
+States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline
+\midrule 
+Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline
+\midrule 
+Expectation value & Defined & Undefined & Formally defined & Undefined &  & Defined\tabularnewline
 \midrule
 \midrule 
-\addlinespace
-States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
+ &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline
 \midrule 
-\addlinespace
-Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline\addlinespace
+Deutsch's algorithm & Yes & Maybe no & Yes & Yes &  & \tabularnewline
 \midrule 
-\addlinespace
-Expectation value & Defined & Undefined & Formally defined & Undefined &  & Defined\tabularnewline\addlinespace
+Efficiently solve $\usat$ & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline
 \midrule 
-\midrule 
-\addlinespace
- &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
-\midrule 
-\addlinespace
-Deutsch's algorithm & Yes & Maybe no & Yes & Yes &  & \tabularnewline\addlinespace
-\midrule 
-\addlinespace
-Efficiently solve $\usat$ & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace
-\midrule 
-\addlinespace
-Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline\addlinespace
+Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline
 \bottomrule
@@
 
-We can reduce 3 degrees of freedom in \Eq{A5.eq} to 2 degrees of
-freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
-out by the circle $\Sphere{1}$''). The standard form of these maps
-(``the Hopf fibration'') is 
-\begin{eqnarray}
- &  & X=2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
- &  & Y=2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{eq:HopfFibration}\\
- &  & Z=\left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
-\end{eqnarray}
-By denoting the three-dimensional vector~$\left(X,Y,Z\right)$ as
-$\Hat{a}$, \Eq{A5.eq} implies these transformed coordinates obeying
-\begin{equation}
-\left\Vert \Hat{a}\right\Vert ^{2}=X^{2}+Y^{2}+Z^{2}=\left(\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}\right)^{2}=1\label{A7.eq}
-\end{equation}
-and therefore have only two remaining degrees of freedom describing
-all possible distinct one-qubit quantum states. In Fig.~\ref{hopfFibers.fig},
-we illustrate schematically the family of circles \textit{each one
-of which is collapsed to a point}~$\left(\phi,\psi\right)$ on the
-surface $X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
-
-\begin{figure}[tb]
+\begin{figure}[!b]
 \hfill{}\subfloat[]{\centering{}\includegraphics[width=0.48\columnwidth]{hopfS2}}\hfill{}\subfloat[]{\begin{centering}
@@
 \end{figure}
-
-The resulting manifold is the two-sphere $\Sphere{2}$ (a 2-manifold)
-embedded in $\R^{3}$. If we choose one of many possible coordinate
-systems describing $\Sphere{3}$ via \Eq{A5.eq} such as 
-\begin{equation}
-\left(x_{0},y_{0},x_{1},y_{1}\right)=\left(\cos\left(\theta+\phi\right)\cos\psi,\,\sin\left(\theta+\phi\right)\cos\psi,\,\cos\left(\theta-\phi\right)\sin\psi,\,\sin\left(\theta-\phi\right)\sin\psi\right)\,,\label{A8a.eq}
-\end{equation}
-where %% $0\leq \theta \leq 2 \pi$,  $-\pi \leq \phi \leq  \pi$, 
-$0\leq\psi\leq\frac{\pi}{2}$, with $0\leq\theta+\phi<2\pi$ and $0\leq\theta-\phi<2\pi$,
-we see that 
-\begin{equation}
-\left(X,Y,Z\right)=\left(\cos\left(2\phi\right)\sin\left(2\psi\right),\,\sin\left(2\phi\right)\sin\left(2\psi\right),\,\cos\left(2\psi\right)\right)\,.\label{A8b.eq}
-\end{equation}
-Thus, the one-qubit state is independent of $\theta$, and we can
-choose $\theta=\phi$ without loss of generality, reducing the formula
-of the unique one-qubit states to $\ket{\psi_{1}}=\rme^{2\rmi\phi}\cos\psi\ket{0}+\sin\psi\ket{1}$,
-and an irreducible state can be represented as a point on a sphere
-called the Bloch sphere, as shown in Fig.~\ref{blochSphere.fig}~(a).
-
-\begin{figure}[tb]
+We can reduce 3 degrees of freedom in \Eq{A5.eq} to 2 degrees of
+freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
+out by the circle $\Sphere{1}$''). The standard form of these maps
+(``the Hopf fibration'') is 
+\begin{eqnarray}
+ &  & X=2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
+ &  & Y=2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{eq:HopfFibration}\\
+ &  & Z=\left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
+\end{eqnarray}
+By denoting the three-dimensional vector~$\left(X,Y,Z\right)$ as
+$\Hat{a}$, \Eq{A5.eq} implies these transformed coordinates obeying
+\begin{equation}
+\left\Vert \Hat{a}\right\Vert ^{2}=X^{2}+Y^{2}+Z^{2}=\left(\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}\right)^{2}=1\label{A7.eq}
+\end{equation}
+and therefore have only two remaining degrees of freedom describing
+all possible distinct one-qubit quantum states. In Fig.~\ref{hopfFibers.fig},
+we illustrate schematically the family of circles \textit{each one
+of which is collapsed to a point}~$\left(\phi,\psi\right)$ on the
+surface $X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
+
+\begin{figure}[!b]
 \begin{centering}
@@
 \end{figure}
+The resulting manifold is the two-sphere $\Sphere{2}$ (a 2-manifold)
+embedded in $\R^{3}$. If we choose one of many possible coordinate
+systems describing $\Sphere{3}$ via \Eq{A5.eq} such as 
+\begin{equation}
+\left(x_{0},y_{0},x_{1},y_{1}\right)=\left(\cos\left(\theta+\phi\right)\cos\psi,\,\sin\left(\theta+\phi\right)\cos\psi,\,\cos\left(\theta-\phi\right)\sin\psi,\,\sin\left(\theta-\phi\right)\sin\psi\right)\,,\label{A8a.eq}
+\end{equation}
+where %% $0\leq \theta \leq 2 \pi$,  $-\pi \leq \phi \leq  \pi$, 
+$0\leq\psi\leq\frac{\pi}{2}$, with $0\leq\theta+\phi<2\pi$ and $0\leq\theta-\phi<2\pi$,
+we see that 
+\begin{equation}
+\left(X,Y,Z\right)=\left(\cos\left(2\phi\right)\sin\left(2\psi\right),\,\sin\left(2\phi\right)\sin\left(2\psi\right),\,\cos\left(2\psi\right)\right)\,.\label{A8b.eq}
+\end{equation}
+Thus, the one-qubit state is independent of $\theta$, and we can
+choose $\theta=\phi$ without loss of generality, reducing the formula
+of the unique one-qubit states to $\ket{\psi_{1}}=\rme^{2\rmi\phi}\cos\psi\ket{0}+\sin\psi\ket{1}$,
+and an irreducible state can be represented as a point on a sphere
+called the Bloch sphere, as shown in Fig.~\ref{blochSphere.fig}~(a).
 
@@
 \begin{table}
-\noindent \begin{centering}
-\caption{\label{tab:quantum-probability-measure}Two fragments of valid probability
+\begin{doublespace}
+\noindent \centering{}\caption{\label{tab:quantum-probability-measure}Two fragments of valid probability
 measures~$\mu_{1}$ and $\mu_{2}$.}
-\par\end{centering}
-\noindent \centering{}%
 \begin{tabular}{ccccccccccc}
 \toprule 
-\addlinespace
-$\ket{\Psi}$ & $\ket{0}$ & $\ket{1}$ & $\ket{2}$ & $\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\rmi\ket{2}}{\sqrt{2}}$ & \ldots\tabularnewline\addlinespace
+$\ket{\Psi}$ & $\ket{0}$ & $\ket{1}$ & $\ket{2}$ & $\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\rmi\ket{2}}{\sqrt{2}}$ & $\cdots$\tabularnewline
 \midrule
-\addlinespace
-$\mu_{1}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $0$ & $1$  & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & \ldots\tabularnewline\addlinespace
-\addlinespace
-$\mu_{2}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $0$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & \ldots\tabularnewline\addlinespace
+$\mu_{1}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $0$ & $1$  & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\cdots$\tabularnewline
+$\mu_{2}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $0$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\cdots$\tabularnewline
 \bottomrule
 \end{tabular}
+\end{doublespace}
 \end{table}
@@
 
-\begin{figure}[t]
+\begin{figure}[b]
 \[
@@
 \begin{table}
-\caption{\label{tab:Generators-in-F9}Generators in $\ff{3^{2}}$}
-
-\centering{}%
+\begin{doublespace}
+\noindent \centering{}\caption{\label{tab:Generators-in-F9}Generators in $\ff{3^{2}}$}
 \begin{tabular}{ccccccccc}
 \toprule 
-\addlinespace
-$j$ & $0$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$\tabularnewline\addlinespace
+$j$ & $0$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$\tabularnewline
 \midrule
-\addlinespace
-$\left(1+\rmi\right)^{j}$ & $1$ & $1+\rmi$ & $-\rmi$ & $1-\rmi$ & $-1$ & $-1-\rmi$ & $\rmi$ & $-1+\rmi$\tabularnewline\addlinespace
-\addlinespace
-$\left(1-\rmi\right)^{j}$ & $1$ & $1-\rmi$ & $\rmi$ & $1+\rmi$ & $-1$ & $-1+\rmi$ & $-\rmi$ & $-1-\rmi$\tabularnewline\addlinespace
-\addlinespace
-$\left(-1+\rmi\right)^{j}$ & $1$ & $-1+\rmi$ & $\rmi$ & $-1-\rmi$ & $-1$ & $1-\rmi$ & $-\rmi$ & $1+\rmi$\tabularnewline\addlinespace
-\addlinespace
-$\left(-1-\rmi\right)^{j}$ & $1$ & $-1-\rmi$ & $-\rmi$ & $-1+\rmi$ & $-1$ & $1+\rmi$ & $\rmi$ & $1-\rmi$\tabularnewline\addlinespace
+$\left(1+\rmi\right)^{j}$ & $1$ & $1+\rmi$ & $-\rmi$ & $1-\rmi$ & $-1$ & $-1-\rmi$ & $\rmi$ & $-1+\rmi$\tabularnewline
+$\left(1-\rmi\right)^{j}$ & $1$ & $1-\rmi$ & $\rmi$ & $1+\rmi$ & $-1$ & $-1+\rmi$ & $-\rmi$ & $-1-\rmi$\tabularnewline
+$\left(-1+\rmi\right)^{j}$ & $1$ & $-1+\rmi$ & $\rmi$ & $-1-\rmi$ & $-1$ & $1-\rmi$ & $-\rmi$ & $1+\rmi$\tabularnewline
+$\left(-1-\rmi\right)^{j}$ & $1$ & $-1-\rmi$ & $-\rmi$ & $-1+\rmi$ & $-1$ & $1+\rmi$ & $\rmi$ & $1-\rmi$\tabularnewline
 \bottomrule
 \end{tabular}
+\end{doublespace}
 \end{table}
@@
 
+\begin{figure}[!b]
+\noindent \centering{}\includegraphics[width=3.6in]{Fpp2Fp}\caption{\label{proof1.fig}Sketch of the map from $\Fpp$ to $\Fp$ using
+$\fnorm{\alpha}$, showing the decomposition of $\Fpp$ into the zero
+element $\left(0,0\right)$ and the $p^{2}-1=\left(p+1\right)\left(p-1\right)$
+non-zero elements that map onto the $p-1$ non-zero elements of $\Fp$
+with multiplicity $p+1$.}
+\end{figure}
 We can now compute the size of the equivalence class of complex unit-modulus
@@
 class of the map $\fnorm{\alpha}$ for non-vanishing $\alpha$, including
-the map to the unit norm value $c=1\in\Fp$.
-\begin{figure}
-\noindent \centering{}\includegraphics[width=3.6in]{Fpp2Fp}\caption{\label{proof1.fig}Sketch of the map from $\Fpp$ to $\Fp$ using
-$\fnorm{\alpha}$, showing the decomposition of $\Fpp$ into the zero
-element $\left(0,0\right)$ and the $p^{2}-1=\left(p+1\right)\left(p-1\right)$
-non-zero elements that map onto the $p-1$ non-zero elements of $\Fp$
-with multiplicity $p+1$.}
-\end{figure}
-\end{proof}
+the map to the unit norm value $c=1\in\Fp$.\end{proof}
 
@@
 \begin{table}
-\caption{\label{tab:Inverse-field-norm}Inverse field norm over $\ff{3^{2}}$
+\begin{doublespace}
+\noindent \centering{}\caption{\label{tab:Inverse-field-norm}Inverse field norm over $\ff{3^{2}}$
 with respect to the generator $1-\rmi$}
-
-\centering{}%
 \begin{tabular}{cccc}
 \toprule 
-\addlinespace
-$c=g^{\left(p+1\right)k}$ & $\left(p+1\right)k$ & $k$ & $\fnorm*{g^{\left(p+1\right)k}}=g^{k}$\tabularnewline\addlinespace
+$c=g^{\left(p+1\right)k}$ & $\left(p+1\right)k$ & $k$ & $\fnorm*{g^{\left(p+1\right)k}}=g^{k}$\tabularnewline
 \midrule
-\addlinespace
-$-1$ & $4$ & $1$ & $1-\rmi$\tabularnewline\addlinespace
-\addlinespace
-$1$ & $0$ & $0$ & $1$\tabularnewline\addlinespace
+$-1$ & $4$ & $1$ & $1-\rmi$\tabularnewline
+$1$ & $0$ & $0$ & $1$\tabularnewline
 \bottomrule
 \end{tabular}
+\end{doublespace}
 \end{table}
@@
 
+\begin{figure}[!b]
+\noindent \begin{centering}
+\includegraphics[viewport=200bp 0bp 1800bp 600bp,width=1.1\columnwidth]{picC}
+\par\end{centering}
+\caption{\label{bloch.fig}Schematically normalized plots of the elements of
+the discrete Bloch sphere, the irreducible single-qubit (two-dimensional)
+state vectors with unit norm over the field $\Fpp$. We show the results
+for $p=3$, $7$, and $11$. For example, in $\Fppx{3}$, there are
+24 vectors of unit norm, but only the 6 inequivalent classes appear
+in the plot. The $p+1=4$ equivalent vectors in each class differ
+only by a complex discrete phase.}
+\end{figure}
 In the one-qubit state with coefficients in $\Fpp$, the discrete
@@
 unit radius sphere for conceptual clarity.
-\begin{figure}
-\noindent \begin{centering}
-\includegraphics[viewport=200bp 0bp 1800bp 600bp,width=1.1\columnwidth]{picC}
-\par\end{centering}
-\caption{\label{bloch.fig}Schematically normalized plots of the elements of
-the discrete Bloch sphere, the irreducible single-qubit (two-dimensional)
-state vectors with unit norm over the field $\Fpp$. We show the results
-for $p=3$, $7$, and $11$. For example, in $\Fppx{3}$, there are
-24 vectors of unit norm, but only the 6 inequivalent classes appear
-in the plot. The $p+1=4$ equivalent vectors in each class differ
-only by a complex discrete phase.}
-\end{figure}
 
@@
 
+\begin{figure}[!b]
+\begin{centering}
+\includegraphics[width=1\columnwidth]{statePlot3}
+\par\end{centering}
+\caption{\label{statePlot3Unit.fig}Logarithmic plot of the number of discrete
+unnormalized states (top, in red), vs the number of normalized discrete
+states (middle, in blue), vs the irreducible states (bottom, in green)
+for the first 6 $\Fpp$-compatible primes, ($3$, $7$, $11$, $19$,
+$23$, $31$), for the number of qubits $1$, $2$, $3$, and $4$.}
+\end{figure}
 To discuss entanglement, we consider a $D$-dimensional quantum system
@@
 for 1, 2, 3, and 4 qubits.
-\begin{figure}[htb]
-\begin{centering}
-\includegraphics[width=1\columnwidth]{statePlot3} 
-\par\end{centering}
-\caption{\label{statePlot3Unit.fig}Logarithmic plot of the number of discrete
-unnormalized states (top, in red), vs the number of normalized discrete
-states (middle, in blue), vs the irreducible states (bottom, in green)
-for the first 6 $\Fpp$-compatible primes, ($3$, $7$, $11$, $19$,
-$23$, $31$), for the number of qubits $1$, $2$, $3$, and $4$. }
-\end{figure}
 
@@
 
+\begin{table}
+\begin{doublespace}
+\noindent \centering{}\caption{\label{tab:Possible-f}All Possible $f\colon\boolt\rightarrow\boolt$.}
+\begin{tabular}{ccccc}
+\toprule 
+$x$ & $f_{1}\left(x\right)$ & $f_{2}\left(x\right)$ & $f_{3}\left(x\right)$ & $f_{4}\left(x\right)$\tabularnewline
+\midrule
+$\bfalse$ & $\bfalse$ & $\bfalse$ & $\btrue$ & $\btrue$\tabularnewline
+$\btrue$ & $\bfalse$ & $\btrue$ & $\bfalse$ & $\btrue$\tabularnewline
+\midrule 
+constant or balanced? & constant & balanced & balanced & constant\tabularnewline
+\bottomrule
+\end{tabular}
+\end{doublespace}
+\end{table}
+\begin{comment}
+\todo{We typeset $U_{f}$ either directly or use macro \textbackslash uf,
+but the definition of \textbackslash uf has a negative space between
+$U$ and $f$ which is different from U\_\{f\}\ldots{} I need to understand
+whether the negative space is necessary or not, or whether the negative
+space has any semantic meaning\ldots{} }
+\end{comment}
+\begin{figure}[!b]
+\noindent \centering{}
+\[
+\begin{array}{c}
+\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{ & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd]\\
+\lstick{\ket{1}} & \qw & \gate{H} & \qw & \multigate{1}{\uf} & \qw & \gate{H^{\dagger}} & \qw & \multimeasureD{1}{\text{measure}}\\
+\lstick{\ket{0}} & \qw & \gate{H} & \qw & \ghost{\uf} & \qw & \gate{H^{\dagger}} & \qw & \ghost{\text{measure}}\\
+ & \push{\ket{\Phi_{1}}} &  & \push{\ket{\Phi_{2}}} &  & \push{\ket{\Phi_{3}}} &  & \push{\ket{\Phi_{4}}}
+}
+\end{array}
+\]
+\caption{\label{fig:Quantum-Circuit-Deutsch}Quantum Circuit for the Deutsch
+Algorithm.}
+\end{figure}
 Although having no realistic application, the Deutsch algorithm is
@@
 $\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $.
-\begin{table}
-\noindent \centering{}\caption{\label{tab:Possible-f}All Possible $f\colon\boolt\rightarrow\boolt$.}
-\begin{tabular}{ccccc}
-\toprule 
-\addlinespace
-$x$ & $f_{1}\left(x\right)$ & $f_{2}\left(x\right)$ & $f_{3}\left(x\right)$ & $f_{4}\left(x\right)$\tabularnewline\addlinespace
-\midrule
-\addlinespace
-$\bfalse$ & $\bfalse$ & $\bfalse$ & $\btrue$ & $\btrue$\tabularnewline\addlinespace
-\addlinespace
-$\btrue$ & $\bfalse$ & $\btrue$ & $\bfalse$ & $\btrue$\tabularnewline\addlinespace
-\midrule 
-\addlinespace
-constant or balanced? & constant & balanced & balanced & constant\tabularnewline\addlinespace
-\bottomrule
-\end{tabular}
-\end{table}
-\begin{comment}
-\todo{We typeset $U_{f}$ either directly or use macro \textbackslash uf,
-but the definition of \textbackslash uf has a negative space between
-$U$ and $f$ which is different from U\_\{f\}\ldots{} I need to understand
-whether the negative space is necessary or not, or whether the negative
-space has any semantic meaning\ldots{} }
-\end{comment}
-\begin{figure}[t]
-\noindent \centering{}
-\[
-\begin{array}{c}
-\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{ & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd]\\
-\lstick{\ket{1}} & \qw & \gate{H} & \qw & \multigate{1}{\uf} & \qw & \gate{H^{\dagger}} & \qw & \multimeasureD{1}{\text{measure}}\\
-\lstick{\ket{0}} & \qw & \gate{H} & \qw & \ghost{\uf} & \qw & \gate{H^{\dagger}} & \qw & \ghost{\text{measure}}\\
- & \push{\ket{\Phi_{1}}} &  & \push{\ket{\Phi_{2}}} &  & \push{\ket{\Phi_{3}}} &  & \push{\ket{\Phi_{4}}}
-}
-\end{array}
-\]
-\caption{\label{fig:Quantum-Circuit-Deutsch}Quantum Circuit for the Deutsch
-Algorithm.}
-\end{figure}
 
@@
 
-\begin{figure}[t]
+\begin{figure}[!b]
 \centering{}
@@
 \begin{table}
+\begin{doublespace}
 \noindent \centering{}\caption{\label{pseq}Number $k$ of transitively ordered elements for a given
@@
 \toprule 
-\addlinespace
-$p$ & $3$ & $7$ & $23$ & $71$ & $311$ & $479$ & $1559$ & $5711$ & $10559$ & $18191$ & \ldots\tabularnewline\addlinespace
+$p$ & $3$ & $7$ & $23$ & $71$ & $311$ & $479$ & $1559$ & $5711$ & $10559$ & $18191$ & $\cdots$\tabularnewline
 \midrule 
-\addlinespace
-$k$ & ${\bf 2}$ & ${\bf 3}$ & ${\bf 5}$ & ${\bf 7}$ & ${\bf 11}$ & ${\bf 13}$ & ${\bf 17}$ & ${\bf 19}$ & ${\bf 23}$ & ${\bf 29}$ & \ldots\tabularnewline\addlinespace
+$k$ & ${\bf 2}$ & ${\bf 3}$ & ${\bf 5}$ & ${\bf 7}$ & ${\bf 11}$ & ${\bf 13}$ & ${\bf 17}$ & ${\bf 19}$ & ${\bf 23}$ & ${\bf 29}$ & $\cdots$\tabularnewline
 \midrule
-\addlinespace
-$\pi\left(k\right)$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ & $8$ & $9$ & $10$ & \ldots\tabularnewline\addlinespace
+$\pi\left(k\right)$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ & $8$ & $9$ & $10$ & $\cdots$\tabularnewline
 \bottomrule
 \end{tabular}
+\end{doublespace}
 \end{table}
@@
 \begin{table}
+\begin{doublespace}
 \noindent \centering{}\caption{\label{table_allowed}Allowed probability amplitudes for different
@@
 \toprule 
-\addlinespace
- & allowed probability amplitudes $F^{D}\left(k\right)$ \tabularnewline\addlinespace
+ & allowed probability amplitudes $F^{D}\left(k\right)$ \tabularnewline
 \midrule
-\addlinespace
-$D=1$  & $F^{1}\left(11\right)=\left\{ 0,\pm1,\pm2,\pm\rmi,\pm2\rmi,(\pm1\pm\rmi),(\pm1\pm2\rmi),(\pm2\pm\rmi)\right\} $\tabularnewline\addlinespace
-\addlinespace
-$D=2$  & $F^{2}\left(11\right)=\left\{ 0,\pm1,\pm\rmi,(\pm1\pm\rmi)\right\} $ \tabularnewline\addlinespace
-\addlinespace
-$D=3$  & $F^{3}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline\addlinespace
-\addlinespace
-$D=4$  & $F^{4}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline\addlinespace
-\addlinespace
-$D=5$  & $F^{5}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline\addlinespace
-\addlinespace
-$D\geq6$  & $F^{D}\left(11\right)=\left\{ 0\right\} $\tabularnewline\addlinespace
+$D=1$  & $F^{1}\left(11\right)=\left\{ 0,\pm1,\pm2,\pm\rmi,\pm2\rmi,(\pm1\pm\rmi),(\pm1\pm2\rmi),(\pm2\pm\rmi)\right\} $\tabularnewline
+$D=2$  & $F^{2}\left(11\right)=\left\{ 0,\pm1,\pm\rmi,(\pm1\pm\rmi)\right\} $ \tabularnewline
+$D=3$  & $F^{3}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline
+$D=4$  & $F^{4}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline
+$D=5$  & $F^{5}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline
+$D\geq6$  & $F^{D}\left(11\right)=\left\{ 0\right\} $\tabularnewline
 \bottomrule
 \end{tabular}
+\end{doublespace}
 \end{table}
@@
 \begin{table}
+\begin{doublespace}
 \noindent \centering{}\caption{\label{f11-proj.fig}Field norms and probabilities for one-qubit states
@@
 \toprule 
-\addlinespace
-$\ket{\Psi}$ & $\fnorm{\ip{0}{\Psi}}$ & $\fnorm{\ip{1}{\Psi}}$ & $\fnorm{\ket{\Psi}}$ & $\muC_{\Psi}\left(0\right)$ & $\muC_{\Psi}\left(1\right)$\tabularnewline\addlinespace
+$\ket{\Psi}$ & $\fnorm{\ip{0}{\Psi}}$ & $\fnorm{\ip{1}{\Psi}}$ & $\fnorm{\ket{\Psi}}$ & $\muC_{\Psi}\left(0\right)$ & $\muC_{\Psi}\left(1\right)$\tabularnewline
 \midrule
-\addlinespace
-$1\ket{0}$ & $1$ & $0$ & $1$ & $\cardp{1}{1}$ & $\cardp{0}{1}$\tabularnewline\addlinespace
-\addlinespace
-$1\ket{0}+1\ket{1}$ & $1$ & $1$ & $2$ & $\cardp{1}{2}$ & $\cardp{1}{2}$\tabularnewline\addlinespace
-\addlinespace
-$1\ket{0}+(1+\rmi)\ket{1}$ & $1$ & $2$ & $3$ & $\cardp{1}{3}$ & $\cardp{2}{3}$\tabularnewline\addlinespace
-\addlinespace
-$(1-\rmi)\ket{0}+(1+\rmi)\ket{1}$ & $2$ & $2$ & $4$ & $\cardp{2}{4}$ & $\cardp{2}{4}$\tabularnewline\addlinespace
+$1\ket{0}$ & $1$ & $0$ & $1$ & $\cardp{1}{1}$ & $\cardp{0}{1}$\tabularnewline
+$1\ket{0}+1\ket{1}$ & $1$ & $1$ & $2$ & $\cardp{1}{2}$ & $\cardp{1}{2}$\tabularnewline
+$1\ket{0}+(1+\rmi)\ket{1}$ & $1$ & $2$ & $3$ & $\cardp{1}{3}$ & $\cardp{2}{3}$\tabularnewline
+$(1-\rmi)\ket{0}+(1+\rmi)\ket{1}$ & $2$ & $2$ & $4$ & $\cardp{2}{4}$ & $\cardp{2}{4}$\tabularnewline
 \bottomrule
 \end{tabular}
+\end{doublespace}
 \end{table}
@@
 \begin{table}
+\begin{doublespace}
 \noindent \centering{}\caption{\label{table_long}Extension of transitively ordered elements.}
@@
 \toprule 
-\addlinespace
-$p$ & \ldots{} & $422231$ & \ldots{} & $196265095009$ & \ldots{} &  & \ldots{} &  & \ldots\tabularnewline\addlinespace
+$p$ & $\cdots$ & $422231$ & $\cdots$ & $196265095009$ & $\cdots$ &  & $\cdots$ &  & $\cdots$\tabularnewline
 \midrule 
-\addlinespace
-$k$ & \ldots{} & ${\bf 37}$ & \ldots{} & ${\bf 131}$ & \ldots{} & ${\bf 257}$ & \ldots{} & ${\bf 32771}$ & \ldots\tabularnewline\addlinespace
+$k$ & $\cdots$ & ${\bf 37}$ & $\cdots$ & ${\bf 131}$ & $\cdots$ & ${\bf 257}$ & $\cdots$ & ${\bf 32771}$ & $\cdots$\tabularnewline
 \midrule
-\addlinespace
-$\pi\left(k\right)$ & \ldots{} & $12$ & \ldots{} & $32$ & \ldots{} & $55$ & \ldots{} & $3513$ & \ldots\tabularnewline\addlinespace
+$\pi\left(k\right)$ & $\cdots$ & $12$ & $\cdots$ & $32$ & $\cdots$ & $55$ & $\cdots$ & $3513$ & $\cdots$\tabularnewline
 \bottomrule
 \end{tabular}
+\end{doublespace}
 \end{table}
@@
 \begin{table}
+\begin{doublespace}
 \noindent \centering{}\caption{\label{table:Choquet}This table lists the immediate values to compute
@@
 \toprule 
-\addlinespace
-$i$ & $x_{i}^{+}$ & $E_{i}^{+}$ & $E_{i\uparrow}^{+}$ & $\mul\left(E_{i\uparrow}^{+}\right)$ & $\Delta\mul\left(E_{i\uparrow}^{+}\right)$ & $\mur\left(E_{i\uparrow}^{+}\right)$ & $\Delta\mur\left(E_{i\uparrow}^{+}\right)$\tabularnewline\addlinespace
+$i$ & $x_{i}^{+}$ & $E_{i}^{+}$ & $E_{i\uparrow}^{+}$ & $\mul\left(E_{i\uparrow}^{+}\right)$ & $\Delta\mul\left(E_{i\uparrow}^{+}\right)$ & $\mur\left(E_{i\uparrow}^{+}\right)$ & $\Delta\mur\left(E_{i\uparrow}^{+}\right)$\tabularnewline
 \midrule
-\addlinespace
-$1$ & $1$ & $E$ & $\Omega$ & $1$ & $0.3$ & $1$ & $0.2$\tabularnewline\addlinespace
-\addlinespace
-$2$ & $2$ & $\overline{E}$ & $\overline{E}$ & $0.7$ & $0.7$ & $0.8$ & $0.8$\tabularnewline\addlinespace
-\addlinespace
-$3$ &  &  & $\emptyset$ & $0$ &  & $0$ & \tabularnewline\addlinespace
+$1$ & $1$ & $E$ & $\Omega$ & $1$ & $0.3$ & $1$ & $0.2$\tabularnewline
+$2$ & $2$ & $\overline{E}$ & $\overline{E}$ & $0.7$ & $0.7$ & $0.8$ & $0.8$\tabularnewline
+$3$ &  &  & $\emptyset$ & $0$ &  & $0$ & \tabularnewline
 \bottomrule
 \end{tabular}
+\end{doublespace}
 \end{table}
@@
 \begin{table}
+\begin{doublespace}
 \noindent \centering{}\caption{\label{tab:probability-measures}Possible probability measures on
@@
 \toprule 
-\addlinespace
-$P$ & $\bar{\mu}_{0}\left(P\right)$  & $\bar{\mu}_{1}\left(P\right)$  & $\bar{\mu}_{2}\left(P\right)$  & $\bar{\mu}_{2}'\left(P\right)$  & $\bar{\mu}_{3}\left(P\right)$\tabularnewline\addlinespace
+$P$ & $\bar{\mu}_{0}\left(P\right)$  & $\bar{\mu}_{1}\left(P\right)$  & $\bar{\mu}_{2}\left(P\right)$  & $\bar{\mu}_{2}'\left(P\right)$  & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
 \midrule
-\addlinespace
-$\mathbb{0}$ & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline\addlinespace
-\addlinespace
-All one-dimensional projectors & $\left[0,0\right]$  & $\left[0,\tfrac{1}{4}\right]$  & $\left[0,\tfrac{1}{3}\right]$  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline\addlinespace
-\addlinespace
-All two-dimensional projectors & $\left[1,1\right]$  & $\left[\tfrac{3}{4},1\right]$  & $\left[\tfrac{2}{3},1\right]$  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$  & $\left[\tfrac{1}{2},1\right]$\tabularnewline\addlinespace
-\addlinespace
-$\mathbb{1}$ & $\necess$  & $\necess$  & $\necess$  & $\necess$  & $\necess$\tabularnewline\addlinespace
+$\mathbb{0}$ & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline
+All one-dimensional projectors & $\left[0,0\right]$  & $\left[0,\tfrac{1}{4}\right]$  & $\left[0,\tfrac{1}{3}\right]$  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
+All two-dimensional projectors & $\left[1,1\right]$  & $\left[\tfrac{3}{4},1\right]$  & $\left[\tfrac{2}{3},1\right]$  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$  & $\left[\tfrac{1}{2},1\right]$\tabularnewline
+$\mathbb{1}$ & $\necess$  & $\necess$  & $\necess$  & $\necess$  & $\necess$\tabularnewline
 \bottomrule
 \end{tabular}
+\end{doublespace}
 \end{table}
-The bound $\delta<\frac{1}{3}$ is tight as it is possible to construct
-a $\frac{1}{3}$-deterministic QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$.
-For example, $\bar{\mu}_{2}'$ defined in Table~\ref{tab:probability-measures}
-is a valid $\frac{1}{3}$-deterministic QIVPM\@. When $\delta\geq\frac{1}{3}$,
-i.e., when the uncertainty in measurements becomes so large, it becomes
-possible to map every observable to some (quite inaccurate) probability
-interval, thus invalidating the Kochen-Specker theorem. We can summarize
-and illustrate the above arguments using Fig.~\ref{fignoname}.
-
-\begin{figure}
+\begin{figure}[!b]
 \begin{centering}
@@
 \end{figure}
+The bound $\delta<\frac{1}{3}$ is tight as it is possible to construct
+a $\frac{1}{3}$-deterministic QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$.
+For example, $\bar{\mu}_{2}'$ defined in Table~\ref{tab:probability-measures}
+is a valid $\frac{1}{3}$-deterministic QIVPM\@. When $\delta\geq\frac{1}{3}$,
+i.e., when the uncertainty in measurements becomes so large, it becomes
+possible to map every observable to some (quite inaccurate) probability
+interval, thus invalidating the Kochen-Specker theorem. We can summarize
+and illustrate the above arguments using Fig.~\ref{fignoname}.
 
@@
 \begin{table}
+\begin{doublespace}
 \noindent \centering{}\caption{\label{tab:non-Born-QIVPM}QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}_{0}$
@@
 \toprule 
-\addlinespace
-$P$  & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
+$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
 \midrule
-\addlinespace
-\addlinespace
-$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$  & $\imposs$\tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, $\mathbb{1}-\proj{\ps'}$  & $\necess$\tabularnewline\addlinespace
-\addlinespace
-\addlinespace
-All other projectors  & $\unknown$\tabularnewline\addlinespace
+$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$  & $\imposs$\tabularnewline
+$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, $\mathbb{1}-\proj{\ps'}$  & $\necess$\tabularnewline
+All other projectors  & $\unknown$\tabularnewline
 \bottomrule
-\addlinespace
 \end{tabular}
+\end{doublespace}
 \end{table}

### 2019-02-09 dissertation.tex
dissertation.lyx Acknowledgments Updates...

@@
 \begin{doublespace}
-\noindent \centering{}\caption{\label{tab:committee}I want to thank the professors co-authored with
-me, suggested me as a committee member, and taught me; the collaboration
-or supervised works or studies become the basis of or inspire this
-dissertation.}
+\noindent \centering{}\caption{\label{tab:committee}The professors served in all my committees.}
 %% ERT block 1 (before LyX tabular)
@@
 \midrule 
- & Co-author & Co-author & Co-author &  &  &  & Most of Chapters~\ref{chap:Conventional-Quantum-Theory}, \ref{chap:Unrestricted-Finite-Fields},and~\ref{chap:DQT=000026DQC}
-is based on~\cite{geometry2013} and~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
-is based on~\cite{THOS2018}.\tabularnewline
+ & Co-author & Co-author & Co-author &  &  &  & Most of Chapters~\ref{chap:Conventional-Quantum-Theory}, \ref{chap:Unrestricted-Finite-Fields},
+and~\ref{chap:DQT=000026DQC} is based on~\cite{geometry2013} and~\cite{DQT2014};
+most of Chapter~\ref{chap:QIVPM} is based on~\cite{THOS2018}.\tabularnewline
 \midrule 
-Research committee & Co-chair & Co-chair & Member & Co-chair & Member &  & Some questions in the dissertation proposal are answered in Chapter~\ref{chap:QIVPM},and
-some of the remaining ones are explained in Chapter~\ref{chap:Further-Discussion}.\tabularnewline
+Research committee & Co-chair & Co-chair & Member & Co-chair & Member &  & Some questions in the dissertation proposal are answered in Chapter~\ref{chap:QIVPM},
+and some of the remaining ones are explained in Chapter~\ref{chap:Further-Discussion}.\tabularnewline
 \midrule 
@@
 \midrule
-Tier 3 committee & Co-chair & Co-chair &  & Member &  & Co-chair & Two of the assigned papers in the Tier 3 exam \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644}
-are cited in Sec.~\ref{modalquantum}.\tabularnewline
+Tier 3 committee & Co-chair & Co-chair &  & Member &  & Co-chair & Two of the assigned papers \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644}
+in the Tier 3 exam~\cite{Mathematics2018} are cited in Sec.~\ref{modalquantum}.\tabularnewline
 \midrule
@@
 probability measures over finite fields~\cite{Gardiner2014}. His
-results were improved and motivated the transition from DQT to QIVPM
-in Sec.~\ref{sec:Toward-IVPM}. Besides of my committee members,
-the knowledge I learned from teachers in other courses help me consolidate
+research supervised by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
+and~\ref{sec:Toward-IVPM}. Besides of my committee members, the
+knowledge I learned from teachers in other courses help me consolidate
 this dissertation as listed in Table~\ref{tab:teacher}. Although
@@
 
-Many people in both the departments of Mathematics and Computer Science
-have done everything to make my double-major smooth. \todo{Acknowledgments
-cleaned up until here. }I need to thank all of them, especially directors
-of graduate study in Mathematics, especially Prof.\ Christopher Judge,
-Prof.\ Matthias Weber, and Prof.\ Michael A.\ Mandell; directors
-of Ph.D. study in Computer Science, especially Prof.\ Yuqing Melanie
-Wu (吴愈青) and Prof.\ \textturkish{Funda Ergun}.
+Many people have done everything to make my double-major smooth and
+to financially support me during my Ph.D. study. I need to thank all
+of them, and the complete list of the support according to the employment
+and award is listed in my Curriculum Vitae at the end of the dissertation.
+Most importantly Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
+helped me deal with the rules, supervised my reading courses for writing
+our papers, and financially support me as a research assistant and
+associate. In the department of Mathematics, I need to thank the graduate
+services assistant, Kate Forrest, and the directors of graduate study
+in Mathematics, especially Prof.\ Christopher Judge, Prof.\ Matthias
+Weber, and Prof.\ Michael A.\ Mandell. In the department of Computer
+Science, I want to thank the graduate student office; the director
+of AI/UI assignments, Charles Pope; the directors of Ph.D. study in
+Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
+Ergun}; the infrastructure and technology group (ITG). In particular,
+I don't know how much computational power I consumed to count the
+states in Sec.~\ref{subsec:Maximal-entanglement}. These computational
+power not only came from the Linux systems in Computer Science but
+also came from the Big Red II administrated by the University Information
+Technology Services (UITS). Also, I have checked out a stack of books
+from the Indiana University Libraries. While the books are not in
+the collection, I occasionally requested them via the Interlibrary
+Loan service, submitted the Purchase Recommendation Form to suggested
+IU libraries to buy them.\todo{Acknowledgments cleaned up until here.
+}
+
+Except the financial support via employment and award, I have also
+support by my family, especially my father Cheng-Tien Tai (戴振沺).
 
@@
 
-\subsection{Maximal entanglement}
+\subsection{Maximal entanglement\label{subsec:Maximal-entanglement}}
 
@@
 (total) and $p^{3}\left(p^{4}-1\right)$ (irreducible) instances of
-pure maximally entangled states, while the general formula for 4-qubit
-states remains unclear.
+pure maximally entangled states. For four-qubits and $p=3$, there
+are $2195538048$ instances of pure maximally entangled states, while
+the general formula for four-qubit states remains unclear.
 

### 2019-02-11 dissertation.tex
dissertation.lyx Acknowledgments Updates...

@@
 research supervised by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
-and~\ref{sec:Toward-IVPM}. Besides of my committee members, the
-knowledge I learned from teachers in other courses help me consolidate
-this dissertation as listed in Table~\ref{tab:teacher}. Although
-not directly relating to the dissertation, I have to thank for your
-teaching to make me more mature and easier to communicate with others,
-especially my English teachers, Traci Nagle, Elizabeth ``Betsy''
-Merceron, and Kexin ``Casey'' Chen (谌可心).
+and~\ref{sec:Toward-IVPM}. Besides of my committee members, what
+I learned from the teachers in other courses also helped me consolidate
+this dissertation as listed in Table~\ref{tab:teacher}. Even if
+what taught by my other teachers are not directly related to this
+dissertation, I have to thank for your teaching to make me more mature
+and easier to communicate with others, especially my English teachers,
+Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
+Chen (谌可心).
 \begin{table}[t]
 \begin{doublespace}
-\noindent \centering{}\caption{\label{tab:teacher}The knowledge I learned from teachers in other
-courses help me consolidate this dissertation, where IUB stands for
-Indiana University Bloomington and NTU stands for National Taiwan
-University.}
+\noindent \centering{}\caption{\label{tab:teacher}Other courses I took which is relevant to this
+dissertation, where IUB stands for Indiana University Bloomington
+and NTU stands for National Taiwan University.}
 %% ERT block 1 (before LyX tabular)
@@
 and award is listed in my Curriculum Vitae at the end of the dissertation.
-Most importantly Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
+Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
 helped me deal with the rules, supervised my reading courses for writing
@@
 Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
-Ergun}; the infrastructure and technology group (ITG). In particular,
+Ergun}; and the infrastructure and technology group (ITG). In particular,
 I don't know how much computational power I consumed to count the
@@
 also came from the Big Red II administrated by the University Information
-Technology Services (UITS). Also, I have checked out a stack of books
-from the Indiana University Libraries. While the books are not in
-the collection, I occasionally requested them via the Interlibrary
-Loan service, submitted the Purchase Recommendation Form to suggested
-IU libraries to buy them.\todo{Acknowledgments cleaned up until here.
+Technology Services (UITS). The Indiana University Libraries was also
+extremely helpful during my dissertation research. Except for a stack
+of books I checked out directly, while the books are not in their
+collection, I occasionally requested them via the Interlibrary Loan
+service, submitted the Purchase Recommendation Form to suggested IU
+libraries to buy them.\todo{Acknowledgments cleaned up until here.
 }
@@
 Except the financial support via employment and award, I have also
-support by my family, especially my father Cheng-Tien Tai (戴振沺).
-
-Others who help me indirectly on the content of the dissertation including
-Kin Wai Chan, Weihua Liu (刘伟华), Caren Liu (劉鈺平), Meng-Wei Chen
-(陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen (陳昭宏)\ldots , etc. This
-could be listed on and on. I still thank you even if your name is
-not listed here, and sorry for my bad memory.
-
-Thank all my friends for your support, including:
+support by my family, especially my father Cheng-Tien Tai (戴振沺). He
+always thinks one-step ahead and cares about my future more than I
+do. Discussion with other family members and friends also helped me
+to compose this dissertation or to do research in general. In particular,
+I want to thank Prof.~Daniel Leivant, Prof.~Paul Purdom, Weihua
+Liu (刘伟华), and classifies others as the following:\footnote{I only provide the Chinese name for some of them since I only know
+their Chinese names and there is no unique way to alphabetize Chinese
+into English. Hence, if I randomly choose a way to alphabetize their
+name, it might just be a random string which might not be their English
+name when they really want to use an English name. For the reader
+who don't know Chinese, their names should be able to be copied directly
+since the output of \XeLaTeX should be encoded in the Unicode.}
 
@@
 
-\item Meng-Wei Chen (陳孟瑋) as my roommate, AT\&T family plan member,
-and emergency contact for all kinds of emergency and non-emergency
-situations.
+\item The Ph.D. students in Mathematics, including, Kin Wai Chan,
+ChunHsien Lu (呂俊賢), Cong Zhou (周蔥), Junyan Xu (许俊彦), Zhipeng Lu (路志鹏),
+Robert Rose, Neal Coleman, Dami Lee, Ruiyu Yang (杨瑞雨), Yingwei Li
+(李盈伟), Yu-Yuan Chen (陳裕元)\ldots{} etc.
+
+\item My other family members, including, my mother Feng-Ming Chang
+(張鳳鳴), my grandmother 戴許玉婷, my sister Sih-Sian Tai (戴司嫻), my cousins
+Caren Liu (劉鈺平) and Kiwi Liu (劉子綺), \ldots{} etc.
+
+\item My official and nonofficial roommates, including Meng-Wei Chen
+(陳孟瑋), Yu ``Larry'' Chen (陈煜), Jing-Han Liou (劉經翰), Shu-Ling Wang
+(王舒齡), and Wan-Ling ``Wynnie'' Chang (張婉鈴).
+
+\item My classmates in NTU, including, Hao-Chun Lee (李浩君), Hsien-Ching
+Kao (高憲慶), 鄭維,
+
+\item My building mates, including Chao-Hong Chen (陳昭宏)
 
@@
 
-\item Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
-what I did from the perspective of a general PhD. in Physics and working
-later in more computational industry.
+\item Hao-Chun Lee (李浩君) and for discussing what I did from the perspective
+of a general PhD. in Physics and working later in more computational
+industry.
 
@@
 
-Finally, I thank Jin-Ru Yang (楊謹如) for everything that could not be
-written here.\end{acknowledgments*}
+\ldots , etc. This could be listed on and on. I still thank you even
+if your name is not listed here, and sorry for my bad memory.
+
+Finally, I want to thank Blue Coat system for providing K9 Web Protection
+to block distractive websites to keep me focus, and Jin-Ru Yang (楊謹如)
+for keeping the password and helping me control myself in general.\end{acknowledgments*}
 

### 2019-02-13 dissertation.tex
dissertation.lyx Before send Acknowledgments to grammar-checkers...

@@
 \usepackage{dsfont}
-\usepackage{xeCJK}
-\setCJKmainfont{SimSun}
+\usepackage[AutoFallBack=true]{xeCJK}
+\setCJKmainfont[FallBack=Batang]{SimSun}
+% \usepackage{xeCJK}
+% \setCJKmainfont{SimSun}
 
@@
 \setotherlanguage{arabic}
+\setotherlanguage{bahasai}
+\setotherlanguage{basque}
+\setotherlanguage{french}
 \setotherlanguage{german}
 \setotherlanguage{italian}
+\setotherlanguage{portuges}
 \setotherlanguage{turkish}
+\setotherlanguage{vietnamese}
 \usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
@@
 
-To have the current the content of the dissertation, I would also
-like to thank John Gardiner for some inspiring discussion about quantum
+To have the current content of the dissertation, I would also like
+to thank John Gardiner for some inspiring discussion about quantum
 probability measures over finite fields~\cite{Gardiner2014}. His
@@
 collection, I occasionally requested them via the Interlibrary Loan
-service, submitted the Purchase Recommendation Form to suggested IU
-libraries to buy them.\todo{Acknowledgments cleaned up until here.
-}
+service, recommended IU libraries to purchase them.
 
@@
 to compose this dissertation or to do research in general. In particular,
-I want to thank Prof.~Daniel Leivant, Prof.~Paul Purdom, Weihua
-Liu (刘伟华), and classifies others as the following:\footnote{I only provide the Chinese name for some of them since I only know
-their Chinese names and there is no unique way to alphabetize Chinese
-into English. Hence, if I randomly choose a way to alphabetize their
-name, it might just be a random string which might not be their English
-name when they really want to use an English name. For the reader
-who don't know Chinese, their names should be able to be copied directly
-since the output of \XeLaTeX should be encoded in the Unicode.}
+I want to thank following people which haven't been listed previously:\footnote{I only provide the Chinese name for some of them for three reasons.
+First, I might only know their Chinese names. Second, there is no
+unique way to translate a Chinese name to English, and I am not familiar
+with any of them. Third, all these methods translate infinitely different
+Chinese names to the same English name so we loss some precision or
+information if we only record their English name.}
 
@@
 
-\item The Ph.D. students in Mathematics, including, Kin Wai Chan,
+\item The Ph.D. students in Mathematics, including Kin Wai Chan,
 ChunHsien Lu (呂俊賢), Cong Zhou (周蔥), Junyan Xu (许俊彦), Zhipeng Lu (路志鹏),
 Robert Rose, Neal Coleman, Dami Lee, Ruiyu Yang (杨瑞雨), Yingwei Li
-(李盈伟), Yu-Yuan Chen (陳裕元)\ldots{} etc.
+(李盈伟), Yu-Yuan Chen (陳裕元), Jan-Li Lin (林展立), Ping Zhong, Chen Xu (徐晨),
+Yiqiu Mao (茅一遒), Yu-Min Chung (鍾佑民), Shizhuo Zhang (张诗卓), Max Yining
+Zhang (张忆宁), \textturkish{Ata Tuncer}, Hongming Nie (聂洪明), Sandeep
+Bhupatiraju, Peng Wang, Guanglu Zhu (祝广路), Sailaja Gajula, Xuqiang
+Qin (秦绪强), and \textvietnamese{Phuong Nguyen}, \ldots , etc.
+
+\item Other members in Mathematics, including Weihua Liu (刘伟华),
+Yinan ``Christina'' Wu (武怡楠), Cheng ``Freddie'' Shi (史程), Shabnam
+Kavousian, and Tyler Bennett (班天瑞), \ldots , etc.
+
+\item My officemates, especially, Inhak Hwang\ (황인학), Jiecao
+Chen (陈洁操), Erfan Sadeqi~Azer, Chao ``Alan'' Tao (陶超), Haoyu Zhang
+(张皓宇), Yadi Wei (魏雅廸), BoLi Fang (方博立), Yuan Xie (谢缘), and Mrinmoy
+Maity, \ldots , etc.
+
+\item My other friends have office in Lindley or \textportuges{Luddy}
+Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-chieh
+Shan (單中杰), Chao-Hong Chen (陳昭宏), Robert Rose, \textbasque{Bibrak
+Chandio}, Yuxiang Jiang (蒋宇翔), Pei-Ying Chen (陳珮瑩), Prof.~Qin Zhang
+(张勤), Kaitlyn Owens, Praveen Narayanan, Liang Chen (陈亮), \textfrench{Ambrose
+Bonnaire-Sergeant}, Ali Varamesh, Larry ``LP'' \textfrench{Ailes},
+and Min-Chin Lin (林旻瑾), \ldots , etc.
 
@@
 (張鳳鳴), my grandmother 戴許玉婷, my sister Sih-Sian Tai (戴司嫻), my cousins
-Caren Liu (劉鈺平) and Kiwi Liu (劉子綺), \ldots{} etc.
+Caren Liu (劉鈺平), and Kiwi Liu (劉子綺), \ldots , etc.
 
 \item My official and nonofficial roommates, including Meng-Wei Chen
-(陳孟瑋), Yu ``Larry'' Chen (陈煜), Jing-Han Liou (劉經翰), Shu-Ling Wang
-(王舒齡), and Wan-Ling ``Wynnie'' Chang (張婉鈴).
-
-\item My classmates in NTU, including, Hao-Chun Lee (李浩君), Hsien-Ching
-Kao (高憲慶), 鄭維,
-
-\item My building mates, including Chao-Hong Chen (陳昭宏)
-
-\item My other AT\&T family plan members, especially Kexin ``Casey''
-Chen (谌可心), Yao-yu Chih (池耀宇), and Xinyi ``Diana'' Gong (龚欣怡), for
-you always pay our telephone bill on time so that\ldots\ldots\todo{
-Maybe I don't have to thank them as AT\&T family plan members, but
-I should thank some of them for support and sharing information\ldots}
-
-\item My other roommates,
-
-\item Hao-Chun Lee (李浩君) and for discussing what I did from the perspective
-of a general PhD. in Physics and working later in more computational
-industry.
+(陳孟瑋), Yu ``Larry'' Chen (陈煜), Kenshin Reita (禮田謙信), Jing-Han Liou
+(劉經翰), Shu-Ling Wang (王舒齡), and Wan-Ling ``Wynnie'' Chang (張婉鈴).
+
+\item My classmates or friends in NTU, including Hao-Chun Lee (李浩君),
+Hsien-Ching Kao (高憲慶), Wei Cheng (鄭維), Chin-Yi Lin (林金毅), Chun-Ting
+Chen (陳俊廷), and Prof.~Chenying Huang (黃貞穎), \ldots , etc.
+
+\item My friends lived in the Tulip Tree Apartments, including Chao-Hong
+Chen (陳昭宏), Tsaiyi Wu (吳采奕), Cheng ``Freddie'' Shi (史程), Ossama
+Abdel~Gawwad, and Cathryn ``Cathy'' Creger-Chambers, \textbahasai{Sary
+Silvhiany}, Shaozhuan Li (李绍颛), and Chenwei Zhang (张晨薇), Shu-Nan ``Nancy''
+Chang (張舒涵), and Ching-Chi ``Victoria'' Chang (張靖琪), \ldots , etc.
+
+\item My AT\&T family plan members, especially Meng-Wei Chen (陳孟瑋),
+Yao-yu Chih (池耀宇), and Xinyi ``Diana'' Gong (龚欣怡), \ldots , etc.
+
+\item Other friends, including Yu-Jung Lin (林宇容), Winnie Lou (何慧芳),
+Yi-Rong Yang (楊宜蓉), Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
+Davis Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding (丁颖), Hung-Chun
+Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超), Prof.~Jyh-Chyi
+Gong (龔治齊), and 江靜宜, \ldots , etc.
 
@@
 
-\ldots , etc. This could be listed on and on. I still thank you even
-if your name is not listed here, and sorry for my bad memory.
+\noindent This list could be on and on and never ends. If you have
+help me in any form or provide any helpful information during my Ph.D.
+study, but I forget to list you or your unit here. Please forgive
+my bad memory.
 

### 2019-02-13 dissertation.tex
dissertation.lyx Grammar-checked by "Online Grammar Checker for TeX files"...

@@
 
+\newcommand{\PhD}{Ph.D.\ }
+
 \@ifundefined{showcaptionsetup}{}{%
@@
 %data for Acceptance Page
-\committeeMember{Amr A. Sabry, PhD} \committeeMember{Dylan Paul
-Thurston, PhD} \committeeMember{Gerardo Ortiz, PhD} \committeeMember{Andrew
-J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{November
+\committeeMember{Amr A. Sabry, \PhD} \committeeMember{Dylan
+Paul Thurston, \PhD} \committeeMember{Gerardo Ortiz, \PhD} \committeeMember{Andrew
+J. Hanson, \PhD} \committeeMember{Shouhong Wang, \PhD} \defensedate{November
 29, 2018} \acceptancepage
@@
 Many people have done everything to make my double-major smooth and
-to financially support me during my Ph.D. study. I need to thank all
+to financially support me during my \PhD study. I need to thank all
 of them, and the complete list of the support according to the employment
@@
 Science, I want to thank the graduate student office; the director
-of AI/UI assignments, Charles Pope; the directors of Ph.D. study in
+of AI/UI assignments, Charles Pope; the directors of \PhD study in
 Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
-Ergun}; and the infrastructure and technology group (ITG). In particular,
+Ergun}; and the infrastructure and technology group (ITG). Particularly,
 I don't know how much computational power I consumed to count the
@@
 
-\item The Ph.D. students in Mathematics, including Kin Wai Chan,
+\item The \PhD students in Mathematics, including Kin Wai Chan,
 ChunHsien Lu (呂俊賢), Cong Zhou (周蔥), Junyan Xu (许俊彦), Zhipeng Lu (路志鹏),
@@
 \noindent This list could be on and on and never ends. If you have
-help me in any form or provide any helpful information during my Ph.D.
+help me in any form or provide any helpful information during my \PhD
 study, but I forget to list you or your unit here. Please forgive
@@
 minimum unit and expressed ``If a one-foot-long stick is cut into
-halves every day, the cutting will never come to an end''\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}.
+halves every day, the cutting will never come to an end''.\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}
 As another example, Greek mathematicians in the school of Pythagoras
@@
 states, which are assumed in the field of complex numbers in the ``conventional
-quantum theory'' (CQT)\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
-and ``ordinary'' quantum theory.}. If the probability amplitudes are assumed to be ultimately discrete,
+quantum theory'' (CQT).\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
+and ``ordinary'' quantum theory.} If the probability amplitudes are assumed to be ultimately discrete,
 we choose to replace the field of complex numbers by discrete finite
@@
 basis $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$. We then follow
-the analog of the two-dimensional procedure: Conservation of probability
+the analog of the two-dimensional procedure: conservation of probability
 requires that the norm of the vector $\VVec{\alpha}$ be normalized
@@
 \item $\mathbb{F}$ is an Abelian group under the addition operation~$+$
-(additive group);
+(additive group).
 \item The multiplication operation~$\gmult$ is associative and commutative.
 The field has a multiplicative identity and the property that every
-nonzero element has a multiplicative inverse;
-\item Distributive laws: For all $a,b,c\in\mathbb{F}$ 
+nonzero element has a multiplicative inverse.
+\item Distributive laws: for all $a,b,c\in\mathbb{F}$, 
 \begin{align}
@@
 The exponent $r$ is known as the \emph{degree} of the field over
-its prime subfield\footnote{ Fields $\ff{q}$ where $q$ is a power of a prime $p$, i.e., $q=p^{r}$,
-are known as Galois fields.}~\cite{GT.ref}. If the characteristic $p$ is an arbitrary prime
-number, we call the field \emph{unrestricted}.
+its prime subfield~\cite{GT.ref}.\footnote{Fields $\ff{q}$ where $q$ is a power of a prime $p$, i.e., $q=p^{r}$,
+are known as Galois fields.} If the characteristic $p$ is an arbitrary prime number, we call
+the field \emph{unrestricted}.
 
@@
 by $\ket{\psi_{i}}$ and $\ket{\phi}$ no matter $\ket{\psi_{i}}$
-is in which measurement basis. This phenomena of the measurement basis
-dependence in CQT only exists when discussing quantum contextuality.
-Despite this kind of ``supercontextuality'' of MQT, its computational
-model, modal quantum computing (MQC), having ``supernatural'' computational
-power is also far from conventional quantum computing as we will describe
-next.
+is in which measurement basis. Only when we want to simulate the prediction
+of CQT by a classical hidden variable theory, these kind of prediction
+must depend on the measurement bases which is called quantum contextuality.
+The measurement process itself in MQT depending on the bases demonstrates
+that MQT is more contextual than CQT. Despite this kind of ``supercontextuality''
+of MQT, its computational model, modal quantum computing (MQC), having
+``supernatural'' computational power is also far from conventional
+quantum computing as we will describe next.
 
@@
 when $f$ is unsatisfiable. Applying $S$ to each qubit in the second
-component of the state produces $\ket{0}\ket{\overline{0}}$. Applying
-$S^{\dagger}$ to the first component leaves the state unchanged.
+component of the state produces $\ket{0}\ket{\overline{0}}$, and
+applying $S^{\dagger}$ to the first component leaves the state unchanged.
 As the first component of the state is $0$, applying the map $\sigma_{0}$
@@
 the complex conjugate of $\ip{\Psi}{\Phi}$;
-\item \label{enu:inner-product-linear}$\ip{\Phi}{\Psi}$ is conjugate linear
+\item \label{enu:inner-product-linear}$\ip{\Phi}{\Psi}$ is conjugate-linear
 in its first argument and linear in its second argument;
@@
 is transitively ordered. We can construct examples using the sequence
-A000229 in the encyclopedia of integer sequences~\cite{Sloane2005}\footnote{For computational purposes, this sequence is preferable to the one
+A000229 in the encyclopedia of integer sequences~\cite{Sloane2005}.\footnote{For computational purposes, this sequence is preferable to the one
 proposed by Reisler and Smith~\cite{ReislerSmith1969} because it
@@
 numbers because the first few such primes are $7$, $23$, $839$,
-$9239$, $2042039$, \ldots}. The $n$-th element of that sequence (which must be prime) is the
+$9239$, $2042039$, \ldots} The $n$-th element of that sequence (which must be prime) is the
 least number such that the $n$-th prime is the \emph{least} quadratic
@@
 is basically a rigorous formulation of Schwinger's intuition (See,
-Chapter~1, Section~1.16. in \cite{schwinger2001quantum}).
+Chapter~1, Section~1.16 in \cite{schwinger2001quantum}).
 
@@
 To examine the Deutsch-Jozsa algorithm in the discrete theory of the
-previous section, we assume we are given a classical function $f\colon\boolt^{n}\rightarrow\boolt$
+previous section, assume we are given a classical function $f\colon\boolt^{n}\rightarrow\boolt$
 and are told that $f$ is either constant or balanced \cite{DeutschJozsa1992,544199,Jaeger2007}.
@@
 \begin{comment}
-\todo{Notice that the notation here and previous is a little bit
-different because we dealt with mixed states previously, but pure
-states here. Besides, should we explain the physical meaning of these
-propositions?}
+\todo{Notice that the notation here and previous is a bit different
+because we dealt with mixed states previously, but pure states here.
+Besides, should we explain the physical meaning of these propositions?}
 \end{comment}
@@
 Then, the expectation values of $X$ relative to real-valued and interval-valued
-probability measures can be defined as weighted averages as follow.
+probability measures can be defined as weighted averages as follows.
 \begin{itemize}
@@
 are the difference on the probability of the accumulative sets, they
-have the same magnitude as ones in Eq.~(\ref{eq:expectation}), and
-the right-hand side of Eq.~(\ref{eq:interval-expectation}) can be
-easily simplified to the right-hand side of Eq.~(\ref{eq:expectation})
+have the same magnitude as the ones in Eq.~(\ref{eq:expectation}),
+and the right-hand side of Eq.~(\ref{eq:interval-expectation}) can
+be easily simplified to the right-hand side of Eq.~(\ref{eq:expectation})
 as follow:
@@
 % \caption{\label{tab:Mermin-Peres-Computation}Compute the expectation value
-% of of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$, $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$,
+% of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$, $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$,
 % and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ relative to a 0-deterministic
@@
 Consider the function $\varphi\colon2^{\Omega}\rightarrow\events$
-defined in Eq.~(\ref{eq:pullback-function}), there are two set of
-basis vectors $E_{0}$ and $E_{1}\subseteq\Omega$, such that $\varphi\left(E_{0}\right)=P_{0}$
+defined in Eq.~(\ref{eq:pullback-function}), there are two sets
+of basis vectors $E_{0}$ and $E_{1}\subseteq\Omega$, such that $\varphi\left(E_{0}\right)=P_{0}$
 and $\varphi\left(E_{1}\right)=P_{1}$. Since $E_{0}$ and $E_{1}$
@@
 are all singleton sets. These three possibilities are going to be
-discussed as follow.
+discussed as follows.
 \begin{itemize}
@@
 equation? And its relationship with Grover's algorithm? }\todo{Notice
-that in differential geometry, Killing–Hopf theorem asserts that having
-positive constant curvature guarantees a manifold is essentially a
-sphere, but say little things even if the curvature has an only small
-deviation from constant. Since a quantum probability measure is glued
-by classical probability measures, like a manifold. When their relations
-are exact, Gleason's theorem asserts that a quantum probability measure
-can be essentially induced by the Born rule, but they can be wild
-when we move on to the interval-valued situation! }
+that in differential geometry, the Killing-Hopf theorem asserts that
+having positive constant curvature guarantees a manifold is essentially
+a sphere, but say little things even if the curvature has an only
+small deviation from constant. Since a quantum probability measure
+is glued by classical probability measures, like a manifold. When
+their relations are exact, Gleason's theorem asserts that a quantum
+probability measure can be essentially induced by the Born rule, but
+they can be wild when we move on to the interval-valued situation!
+}
 \end{comment}
@@
 a general $\frameL$ might be as wild as we can imagine, and we might
-need to know a little bit more, like its QIVPM is a composite function,
-to deduce its global property.
+need to know a bit more, like its QIVPM is a composite function, to
+deduce its global property.
 

### 2019-02-13 dissertation.tex
dissertation.lyx Grammar-checked by Grammarly and Microsoft Word...

@@
 I found the sentences in my Acknowledgments almost always contains
-“thank”, and looks boring. To improve my Acknowledgments, I
-briefly read the Acknowledgments in other theses \cite{Chih2013,Sun2015,Lee2013,Chen2016,sabry1995formal}.
+“thank” and looks boring. To improve my Acknowledgments, I briefly
+read the Acknowledgments in other theses \cite{Chih2013,Sun2015,Lee2013,Chen2016,sabry1995formal}.
 \end{comment}
@@
 \end{sidewaystable}
-I want to thanks the professors served in all my committees. These
+I want to thank the professors served in all my committees. These
 professors advised me as committee members and taught me while we
@@
 J. Hanson, Prof.\ Gerardo Ortiz, and Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
-meet me weekly for the pass few years, read and tried to understand
+meet me weekly for the past few years, read and tried to understand
 what I typed which sometimes even myself cannot understand, taught
@@
 (汪守宏) also broadened my understanding on discrete and conventional
-quantum theories. I would like express my appreciation to all of these.
+quantum theories. I would like to express my appreciation to all of
+these.
 
@@
 what taught by my other teachers are not directly related to this
-dissertation, I have to thank for your teaching to make me more mature
+dissertation, I must thank for your teaching to make me more mature
 and easier to communicate with others, especially my English teachers,
@@
 Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
-is cited in Sec.~\ref{sec:background}, \ref{discretequantumtheoryI},
+is cited in Secs.~\ref{sec:background}, \ref{discretequantumtheoryI},
 and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
@@
 Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
-is cited in Sec.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
+is cited in Secs.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
 \ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
@@
 
-Many people have done everything to make my double-major smooth and
-to financially support me during my \PhD study. I need to thank all
-of them, and the complete list of the support according to the employment
-and award is listed in my Curriculum Vitae at the end of the dissertation.
-Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
+Many people have done everything to make my double-major smooth. Moreover,
+
+and to financially or specially support me during my \PhD study.
+A comprehensive list is in my Curriculum Vitae at the end of the dissertation.
+I need to thank all of them. Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
 helped me deal with the rules, supervised my reading courses for writing
@@
 I don't know how much computational power I consumed to count the
-states in Sec.~\ref{subsec:Maximal-entanglement}. These computational
+states in Sec.~\ref{subsec:Maximal-entanglement}. This computational
 power not only came from the Linux systems in Computer Science but
-also came from the Big Red II administrated by the University Information
-Technology Services (UITS). The Indiana University Libraries was also
+also came from the Big Red II administrated by University Information
+Technology Services (UITS). Indiana University Libraries was also
 extremely helpful during my dissertation research. Except for a stack
@@
 
-Except the financial support via employment and award, I have also
-support by my family, especially my father Cheng-Tien Tai (戴振沺). He
-always thinks one-step ahead and cares about my future more than I
-do. Discussion with other family members and friends also helped me
-to compose this dissertation or to do research in general. In particular,
+Except for the financial support via employment and award, I have
+also supported by my family, especially my father Cheng-Tien Tai (戴振沺).
+He always thinks one-step ahead and cares about my future more than
+I do. Discussion with other family members and friends also helped
+me to compose this dissertation or to do research in general, and
 I want to thank following people which haven't been listed previously:\footnote{I only provide the Chinese name for some of them for three reasons.
@@
 with any of them. Third, all these methods translate infinitely different
-Chinese names to the same English name so we loss some precision or
-information if we only record their English name.}
+Chinese names to the same English name, so we lose some precision
+or information if we only record their English name.}
 
@@
 \item My other friends have office in Lindley or \textportuges{Luddy}
-Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-chieh
+Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-Chieh
 Shan (單中杰), Chao-Hong Chen (陳昭宏), Robert Rose, \textbasque{Bibrak
@@
 \noindent This list could be on and on and never ends. If you have
-help me in any form or provide any helpful information during my \PhD
-study, but I forget to list you or your unit here. Please forgive
+helped me in any form or provide any helpful information during my
+\PhD study, but I forget to list you or your unit here. Please forgive
 my bad memory.
@@
 These irreducible quantum states can also be classified as product
-states and entangled states, and the latter one plays the essential
+states and entangled states, and the latter one plays an essential
 role for pure-state algorithms \cite{Mermin2007,Jaeger2007}.
@@
 dimension $D\ge3$ according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
-In other word, this state $\rho$ is the unique state consistent with
-any given quantum probability measure.
+In other words, this state $\rho$ is the unique state consistent
+with any given quantum probability measure.
 \end{comment}
@@
 \end{figure}
-We can reduce 3 degrees of freedom in \Eq{A5.eq} to 2 degrees of
-freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
+We can reduce 3 degrees of freedom in Eq.~(\ref{A5.eq}) to 2 degrees
+of freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
 out by the circle $\Sphere{1}$''). The standard form of these maps
@@
 By denoting the three-dimensional vector~$\left(X,Y,Z\right)$ as
-$\Hat{a}$, \Eq{A5.eq} implies these transformed coordinates obeying
+$\Hat{a}$, Eq.~(\ref{A5.eq}) implies these transformed coordinates
+obeying 
 \begin{equation}
@@
 embedded in $\R^{3}$. If we choose one of many possible coordinate
-systems describing $\Sphere{3}$ via \Eq{A5.eq} such as 
+systems describing $\Sphere{3}$ via Eq.~(\ref{A5.eq}) such as 
 \begin{equation}
@@
 by $\ket{\psi_{i}}$ and $\ket{\phi}$ no matter $\ket{\psi_{i}}$
-is in which measurement basis. Only when we want to simulate the prediction
-of CQT by a classical hidden variable theory, these kind of prediction
-must depend on the measurement bases which is called quantum contextuality.
+is in which measurement basis. The measurement bases only matters
+we want to simulate the prediction of CQT by a classical hidden variable
+theory. In this situation, the hidden variable theory is called \emph{contextual}.
 The measurement process itself in MQT depending on the bases demonstrates
@@
 qubits $n$, that are discarded for each retained unit-length state
-vector. A factor of $p+1$ more states are discarded in forming the
+vector. A factor of $p+1$ more states is discarded in forming the
 discrete Bloch sphere of irreducible states. Selected plots of the
@@
 We have already seen that each single-qubit normalized state in the
-tensor product \Eq{dqcNqUntg.eq} has precisely $p\left(p-1\right)$
+tensor product Eq.~(\ref{dqcNqUntg.eq}) has precisely $p\left(p-1\right)$
 irreducible components due to $D=2$ case in Eq.~(\ref{eq:numberOfIrreducibleStates}).
@@
 \end{equation}
-Therefore, a very small fraction of the unit norm states are unentangled.
+Therefore, a very small fraction of the unit norm states is unentangled.
 
@@
 not have square roots in the field. What is interesting is that if
-we have a uninterrupted sequence of numbers that are all quadratic
+we have an uninterrupted sequence of numbers that are all quadratic
 residues, then we can define a \textit{transitive order}, with $a>c$
@@
 no matter how many resources we use. The same principle can also apply
-to two cardinal probabilities with the different ``denominator''.
-The details of the comparison can be easily formulated by following
-the standard procedure \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016}
+to two cardinal probabilities with different ``denominator''. The
+details of the comparison can be easily formulated by following the
+standard procedure \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016}
 and will leave as an exercise for the readers.
@@
 force $\mu\left(\overline{E}\right)\geq0.75$. To account for such
-subtleties, the axioms of interval-valued probability do not use a
-strict equality for the combination of disjoint events. The correct
-constraint enforcing coherence of the probability assignment for $E_{0}\cup E_{1}$
+subtleties, the axioms of interval-valued probability do not use strict
+equality for the combination of disjoint events. The correct constraint
+enforcing coherence of the probability assignment for $E_{0}\cup E_{1}$
 when $E_{0}$ and $E_{1}$ are disjoint is taken to be: 
@@
 of events, $\eventsC$, recovers the definition of classical IVPMs.
- To see this, we first define the idea of subspace of events. $\events'$
-is called a \emph{subspace} of the set of events~$\events$ if $\events'$
+ To see this, we first define a subspace of events. $\events'$ is
+called a \emph{subspace} of the set of events~$\events$ if $\events'$
 contains the projectors $\mathbb{0}$ and $\mathbb{1}$ and is closed
@@
 of the projectors formed by elements in $E$, and preserve all operations
-used to defined classical and quantum IVPMs as in Eqs.~(\ref{eq:pullback-properties-basic})
+used to define classical and quantum IVPMs as in Eqs.~(\ref{eq:pullback-properties-basic})
 and~(\ref{eq:pullback-properties}). According to the same reason
@@
 \end{equation}
-In other word, if $\mu$ is in the core of $\bar{\mu}$, the expectation
+In other words, if $\mu$ is in the core of $\bar{\mu}$, the expectation
 value of $X$ belongs to $\left[1.7,1.8\right]$ which should be the
@@
 but before proving Thm.~\ref{thm:Non-extensible-of-Gleason's}, we
-need other two lemmas to simplify the proof of the convexity condition
+need the other two lemmas to simplify the proof of the convexity condition
 again.
@@
 After we proved the lemmas, we can state and prove the theorem that
-some assignment of intervals to projectors can be globally inconsistent..
+some assignment of intervals to projectors can be globally inconsistent.
 
@@
 is bounded by $\frameL\left(\ket{\psi_{1}}\right)+\frameL\left(\ket{\psi_{2}}\right)+2\varepsilon$.
-In other word, the left-end function~$\frameL$ satisfies the following
+In other words, the left-end function~$\frameL$ satisfies the following
 inequalities

### 2019-02-13 dissertation.tex
dissertation.lyx Acknowledgments Updates...

@@
 \end{table}
-
-Many people have done everything to make my double-major smooth. Moreover,
-
-and to financially or specially support me during my \PhD study.
-A comprehensive list is in my Curriculum Vitae at the end of the dissertation.
-I need to thank all of them. Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
+Many people have done everything to make my double-major smooth. I
+need to thank all of their supports, financially or providing some
+experience, as listed in my Curriculum Vitae at the end of the dissertation.
+Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
 helped me deal with the rules, supervised my reading courses for writing

### 2019-02-16 dissertation.tex
dissertation.lyx Acknowledgments Reviewed...

--- 2019-02-13 dissertation.tex
@@
 \midrule 
- &  & Supervisor &  &  &  &  & The application for ``Rethinking Foundations of Physics'' 2017 workshop
-inspires Chapter~\ref{chap:Introduction}.\tabularnewline
+ &  & Supervisor &  &  &  &  & The application for \emph{Rethinking Foundations of Physics} 2017
+workshop inspires Chapter~\ref{chap:Introduction}.\tabularnewline
 \midrule 
@@
 Tier 3 committee & Co-chair & Co-chair &  & Member &  & Co-chair & Two of the assigned papers \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644}
-in the Tier 3 exam~\cite{Mathematics2018} are cited in Sec.~\ref{modalquantum}.\tabularnewline
+in the Tier 3 exam~\cite{Mathematics2018} are cited in Chapters~\ref{chap:Introduction}
+and~\ref{chap:Unrestricted-Finite-Fields}.\tabularnewline
 \midrule
@@
 the \textgerman[variant=german,spelling=new,babelshorthands=true]{Weil}
-conjecture on Grassmannians studied with Prof.\ Dylan Paul Thurston
-and the quantum interpretation discussed with Prof.\ Shouhong Wang
-(汪守宏) also broadened my understanding on discrete and conventional
-quantum theories. I would like to express my appreciation to all of
-these.
-
-To have the current content of the dissertation, I would also like
-to thank John Gardiner for some inspiring discussion about quantum
-probability measures over finite fields~\cite{Gardiner2014}. His
-research supervised by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
+conjecture~\cite{hartshorne1977algebraic} on Grassmannians studied
+with Prof.\ Dylan Paul Thurston and the quantum interpretation discussed
+with Prof.\ Shouhong Wang (汪守宏) also broadened my understanding on
+discrete and conventional quantum theories. I would like to express
+my appreciation to all of these.
+
+To have the current content of dissertation, I would also like to
+thank John Gardiner for some inspiring discussion about quantum probability
+measures over finite fields~\cite{Gardiner2014}. His research supervised
+by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
 and~\ref{sec:Toward-IVPM}. Besides of my committee members, what
 I learned from the teachers in other courses also helped me consolidate
-this dissertation as listed in Table~\ref{tab:teacher}. Even if
-what taught by my other teachers are not directly related to this
-dissertation, I must thank for your teaching to make me more mature
-and easier to communicate with others, especially my English teachers,
-Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
+this dissertation as listed in Table~\ref{tab:teacher}. Learning
+other materials also made me more mature and easier to communicate
+with others. I need to thank those who taught me, especially my English
+teachers, Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
 Chen (谌可心).
-\begin{table}[t]
+
+\begin{table}[!t]
 \begin{doublespace}
@@
 \renewcommand{\endtabular}{\endtabularx} 
-\begin{tabular}{M{Jin-Tzu~Chen}cM{MATH-M522}Y}
+\begin{tabular}{M{Chou~(周謀鴻)}cM{MATH-M522}Y}
 \toprule 
@@
 is cited in Secs.~\ref{sec:background}, \ref{discretequantumtheoryI},
-and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
+and~\ref{discretequantumtheoryIIb}.\tabularnewline
 \midrule 
 Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
-is cited in Secs.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
-\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
+is cited in Secs.~\ref{subsec:Two-dimensional-Hilbert-Space}, \ref{subsec:Cyclic-Properties-of},
+\ref{subsec:Complexified-Finite-Fields}, and~\ref{discretequantumtheoryIIb}.\tabularnewline
 \midrule 
@@
 is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
+\midrule
+Mo-Hong\linebreak[3] Chou (周謀鴻) & NTU & 221~U4290 & The textbook~\cite{GolubVanLoan1996} of \emph{Introduction to Computational Linear Algebra}
+is cited in Sec.~\ref{subsec:Finite-Precision-Extension-of}.\tabularnewline
 \bottomrule
@@
 collection, I occasionally requested them via the Interlibrary Loan
-service, recommended IU libraries to purchase them.
+service or recommended IU libraries to purchase them.
 
@@
 I do. Discussion with other family members and friends also helped
-me to compose this dissertation or to do research in general, and
-I want to thank following people which haven't been listed previously:\footnote{I only provide the Chinese name for some of them for three reasons.
-First, I might only know their Chinese names. Second, there is no
-unique way to translate a Chinese name to English, and I am not familiar
-with any of them. Third, all these methods translate infinitely different
-Chinese names to the same English name, so we lose some precision
-or information if we only record their English name.}
+me to compose this dissertation, to do research, or to live better
+in general, and I want to thank the following people which haven't
+been listed previously:\footnote{For some of them, I only provide their Chinese names for two reason.
+First, I might only know their Chinese names. Second, there are many
+ways to translate a name to English, but I don't know which one they
+choose.}
 
@@
 
-\item My other friends have office in Lindley or \textportuges{Luddy}
+\item My other friends having an office in Lindley or \textportuges{Luddy}
 Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-Chieh
 Shan (單中杰), Chao-Hong Chen (陳昭宏), Robert Rose, \textbasque{Bibrak
-Chandio}, Yuxiang Jiang (蒋宇翔), Pei-Ying Chen (陳珮瑩), Prof.~Qin Zhang
-(张勤), Kaitlyn Owens, Praveen Narayanan, Liang Chen (陈亮), \textfrench{Ambrose
-Bonnaire-Sergeant}, Ali Varamesh, Larry ``LP'' \textfrench{Ailes},
-and Min-Chin Lin (林旻瑾), \ldots , etc.
-
-\item My other family members, including, my mother Feng-Ming Chang
-(張鳳鳴), my grandmother 戴許玉婷, my sister Sih-Sian Tai (戴司嫻), my cousins
-Caren Liu (劉鈺平), and Kiwi Liu (劉子綺), \ldots , etc.
-
-\item My official and nonofficial roommates, including Meng-Wei Chen
-(陳孟瑋), Yu ``Larry'' Chen (陈煜), Kenshin Reita (禮田謙信), Jing-Han Liou
-(劉經翰), Shu-Ling Wang (王舒齡), and Wan-Ling ``Wynnie'' Chang (張婉鈴).
+Chandio}, Yuxiang Jiang (蒋宇翔), Lei Wang (王磊), Diyue Bu (卜廸悦), Pei-Ying
+Chen (陳珮瑩), Prof.~Qin Zhang (张勤), Kaitlyn Owens, Praveen Narayanan,
+Liang Chen (陈亮), \textfrench{Ambrose Bonnaire-Sergeant}, Ali Varamesh,
+Larry ``LP'' \textfrench{Ailes}, and Min-Chin Lin (林旻瑾), \ldots ,
+etc.
+
+\item My other family members, including my mother Feng-Ming Chang
+(張鳳鳴), my grandmothers 戴許玉婷 and 張林枝, my sister Sih-Sian Tai (戴司嫻),
+my cousins especially Caren Liu (劉鈺平) and Kiwi Liu (劉子綺), and my
+aunts and uncles, \ldots , etc.
+
+\item My roommates, including Meng-Wei Chen (陳孟瑋), Yu ``Larry''
+Chen (陈煜), Kenshin Reita (禮田謙信), and Jing-Han Liou (劉經翰).
 
@@
 
-\item My friends lived in the Tulip Tree Apartments, including Chao-Hong
+\item My friends living in the Tulip Tree Apartments, including Chao-Hong
 Chen (陳昭宏), Tsaiyi Wu (吳采奕), Cheng ``Freddie'' Shi (史程), Ossama
 Abdel~Gawwad, and Cathryn ``Cathy'' Creger-Chambers, \textbahasai{Sary
-Silvhiany}, Shaozhuan Li (李绍颛), and Chenwei Zhang (张晨薇), Shu-Nan ``Nancy''
+Silvhiany}, Shaozhuan Li (李绍颛), Chenwei Zhang (张晨薇), Shu-Nan ``Nancy''
 Chang (張舒涵), and Ching-Chi ``Victoria'' Chang (張靖琪), \ldots , etc.
@@
 
-\item Other friends, including Yu-Jung Lin (林宇容), Winnie Lou (何慧芳),
-Yi-Rong Yang (楊宜蓉), Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
+\item Other friends, including Shu-Ling Wang (王舒齡), Wan-Ling ``Wynnie''
+Chang (張婉鈴), Yu-Jung Lin (林宇容), Winnie Lou (何慧芳), Yi-Rong Yang (楊宜蓉),
+Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
 Davis Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding (丁颖), Hung-Chun
@@
 
-Finally, I want to thank Blue Coat system for providing K9 Web Protection
-to block distractive websites to keep me focus, and Jin-Ru Yang (楊謹如)
-for keeping the password and helping me control myself in general.\end{acknowledgments*}
+Finally, I want to thank K9 Web Protection for blocking distractive
+websites to keep me focus, and Jin-Ru Yang (楊謹如) for keeping the password
+and helping me control myself in general.\end{acknowledgments*}
 
@@
 
-\subsection{Cyclic Properties of Finite Fields}
+\subsection{Cyclic Properties of Finite Fields\label{subsec:Cyclic-Properties-of}}
 
@@
 
-\subsection{Finite-Precision Extension of Gleason's Theorem}
+\subsection{Finite-Precision Extension of Gleason's Theorem\label{subsec:Finite-Precision-Extension-of}}
 

### 2019-02-17 dissertation.tex
dissertation.lyx Chapters 1, 2, and 3 Reviewed...

@@
 \midrule 
-States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in $\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline
+States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in~$\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline
 \midrule 
@@
 splitters. However, simply taking the union of all event spaces is
-a bad idea because two events might appear different but representing
+a bad idea because two events might appear different but represent
 the same situation. For example, if we take the complement on both
@@
 $0$, and the multiplication identity $1$. Given the field~$\mathbb{F}$,
-the closed operations of addition, ``$+$,'' and multiplication,
-``$\gmult$,'' satisfy the following set of axioms:
+the closed operations of addition~$+$, and multiplication~$\gmult$,
+satisfy the following set of axioms:
 \begin{enumerate}
@@
 by $\ket{\psi_{i}}$ and $\ket{\phi}$ no matter $\ket{\psi_{i}}$
-is in which measurement basis. The measurement bases only matters
-we want to simulate the prediction of CQT by a classical hidden variable
-theory. In this situation, the hidden variable theory is called \emph{contextual}.
-The measurement process itself in MQT depending on the bases demonstrates
-that MQT is more contextual than CQT. Despite this kind of ``supercontextuality''
-of MQT, its computational model, modal quantum computing (MQC), having
-``supernatural'' computational power is also far from conventional
-quantum computing as we will describe next.
+is in which measurement basis. The measurement bases play some roles
+only when we want to simulate the prediction of CQT by a classical
+hidden variable theory. If the prediction of a hidden variable theory
+depending on the measurement bases, this hidden variable theory is
+called \emph{contextual}. The measurement process itself in MQT depending
+on the bases demonstrates that MQT is more contextual than CQT. Despite
+this kind of ``supercontextuality'' of MQT, its computational model,
+modal quantum computing (MQC), having ``supernatural'' computational
+power is also far from conventional quantum computing as we will describe
+next.
 
@@
 In general, the $p$-th power $\left(a+b\rmi\right)^{p}=a-b\rmi$
-is called the \emph{Frobenius automorphism} acts like complex conjugation
-$\left(a+b\rmi\right)^{*}=a-b\rmi$ \cite{Artin1991,grove2002classical,DummitFoote2004}.
+is called the \emph{Frobenius automorphism} and acts like complex
+conjugation $\left(a+b\rmi\right)^{*}=a-b\rmi$ \cite{Artin1991,grove2002classical,DummitFoote2004}.
 Then, we define the \emph{field norm} $\fnorm{\cdot}\colon\Fpp\rightarrow\Fp$

### 2019-02-19 dissertation.tex
dissertation.lyx Acknowledgments Updates...

@@
 Chandio}, Yuxiang Jiang (蒋宇翔), Lei Wang (王磊), Diyue Bu (卜廸悦), Pei-Ying
-Chen (陳珮瑩), Prof.~Qin Zhang (张勤), Kaitlyn Owens, Praveen Narayanan,
-Liang Chen (陈亮), \textfrench{Ambrose Bonnaire-Sergeant}, Ali Varamesh,
-Larry ``LP'' \textfrench{Ailes}, and Min-Chin Lin (林旻瑾), \ldots ,
-etc.
+Chen (陳珮瑩), Prof.~Qin Zhang (张勤), Praveen Narayanan, Liang Chen (陈亮),
+\textfrench{Ambrose Bonnaire-Sergeant}, Ali Varamesh, Min-Chin Lin
+(林旻瑾), and Career Services in the School of Informatics, Computing,
+and Engineering, \ldots , etc.
 

### 2019-02-20 dissertation.tex
dissertation.lyx Secs. 4.1, 4.2, and 4.3 Reviewed...

@@
 
-\begin{figure}[!b]
-\noindent \begin{centering}
-\includegraphics[viewport=200bp 0bp 1800bp 600bp,width=1.1\columnwidth]{picC}
-\par\end{centering}
-\caption{\label{bloch.fig}Schematically normalized plots of the elements of
-the discrete Bloch sphere, the irreducible single-qubit (two-dimensional)
-state vectors with unit norm over the field $\Fpp$. We show the results
-for $p=3$, $7$, and $11$. For example, in $\Fppx{3}$, there are
-24 vectors of unit norm, but only the 6 inequivalent classes appear
-in the plot. The $p+1=4$ equivalent vectors in each class differ
-only by a complex discrete phase.}
-\end{figure}
 In the one-qubit state with coefficients in $\Fpp$, the discrete
@@
 Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{DQA6.eq}\\
-Z & = & \fnorm{\alpha_{0}}-\fnorm{\alpha_{1}}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
+Z & = & \fnorm{\alpha_{0}}-\fnorm{\alpha_{1}}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,,\nonumber 
 \end{eqnarray}
@@
 unit radius sphere for conceptual clarity.
+\begin{figure}[!b]
+\noindent \begin{centering}
+\includegraphics[viewport=200bp 0bp 1800bp 600bp,width=1.1\columnwidth]{picC}
+\par\end{centering}
+\caption{\label{bloch.fig}Schematically normalized plots of the elements of
+the discrete Bloch sphere, the irreducible single-qubit (two-dimensional)
+state vectors with unit norm over the field $\Fpp$. We show the results
+for $p=3$, $7$, and $11$. For example, in $\Fppx{3}$, there are
+24 vectors of unit norm, but only the 6 inequivalent classes appear
+in the plot. The $p+1=4$ equivalent vectors in each class differ
+only by a complex discrete phase.}
+\end{figure}
 

### 2019-02-20 dissertation.tex
dissertation.lyx "6.1 Gleason's Theorem for General QIVPMs" Remove the last TODO... CV_thesis.pdf Remove "(expect)"...

@@
 
-\section{Discrete Quantum Theory (I): Irreducible Discrete $D$-dimensional
-States\label{DQCnqubitBloch.sec}}
+\section{Irreducible Discrete $D$-dimensional States\label{DQCnqubitBloch.sec}}
 
@@
 
-\section{Discrete Quantum Theory (I): Geometry of Entangled States\label{sec:Geometry-of-Entangled-States}}
-
+\section{Geometry of Entangled States\label{sec:Geometry-of-Entangled-States}}
+
+To discuss entanglement, we consider a $D$-dimensional quantum system
+composed of $n$-qubit subsystems, i.e., $D=2^{n}$ as usual. Without
+regard to uniqueness, an $n$-qubit state with discrete complex coefficients
+in $\Fpp$ will have the total possible space of coefficients with
+dimension $p^{2\times2^{n}}$ (including the null state). Imposing
+the condition of a length-one norm in $\Fp$, this number is reduced
+to $p^{2^{n}-1}\left(p^{2^{n}}-1\right)$. The ratio of all the states
+to the unit-norm states is asymptotically $p$: 
+\begin{equation}
+\frac{p^{2^{n}+1}}{p^{2^{n}}-1}\rightarrow p\,,
+\end{equation}
+so there are roughly $p$ sets of coefficients, for any number of
+qubits $n$, that are discarded for each retained unit-length state
+vector. A factor of $p+1$ more states is discarded in forming the
+discrete Bloch sphere of irreducible states. Selected plots of the
+full space compared to both the unit-norm space and the irreducible
+space for a selection of complexified finite fields are shown in Figure~\ref{statePlot3Unit.fig}
+for 1, 2, 3, and 4 qubits.
 \begin{figure}[!b]
@@
 \end{figure}
-To discuss entanglement, we consider a $D$-dimensional quantum system
-composed of $n$-qubit subsystems, i.e., $D=2^{n}$ as usual. Without
-regard to uniqueness, an $n$-qubit state with discrete complex coefficients
-in $\Fpp$ will have the total possible space of coefficients with
-dimension $p^{2\times2^{n}}$ (including the null state). Imposing
-the condition of a length-one norm in $\Fp$, this number is reduced
-to $p^{2^{n}-1}\left(p^{2^{n}}-1\right)$. The ratio of all the states
-to the unit-norm states is asymptotically $p$: 
-\begin{equation}
-\frac{p^{2^{n}+1}}{p^{2^{n}}-1}\rightarrow p\,,
-\end{equation}
-so there are roughly $p$ sets of coefficients, for any number of
-qubits $n$, that are discarded for each retained unit-length state
-vector. A factor of $p+1$ more states is discarded in forming the
-discrete Bloch sphere of irreducible states. Selected plots of the
-full space compared to both the unit-norm space and the irreducible
-space for a selection of complexified finite fields are shown in Figure~\ref{statePlot3Unit.fig}
-for 1, 2, 3, and 4 qubits.
 
@@
 probability space is glued by a family of classical probability spaces.
-\todo{Check the differential geometry analog with Andy, since I don't
-really understand the differential geometry\ldots{} }This is like
-the situation that a manifold is glued by many local coordinates.
-When each small piece has \emph{exactly} the same and positive curvature,
-the Killing-Hopf theorem asserts this manifold is a sphere, but little
-can we say even if the curvature has a small deviation from constant.
-A similar situation might happen when approximating Gleason's theorem,
-but this time the whole space is glued by ``local'' classical probability
-space defined by each orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
+This is like the situation that a manifold is glued by many local
+coordinates. When each small piece has \emph{exactly} the same and
+positive curvature, the Killing-Hopf theorem asserts this manifold
+is a sphere, but little can we say even if the curvature has a small
+deviation from constant. A similar situation might happen when approximating
+Gleason's theorem, but this time the whole space is glued by ``local''
+classical probability space defined by each orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
 When the sum of $\frameL$, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$,

### 2019-02-21 dissertation.tex
dissertation.lyx Secs. 4.4, 4.5, and 4.6 Reviewed...

@@
 our papers, and financially support me as a research assistant and
-associate. In the department of Mathematics, I need to thank the graduate
-services assistant, Kate Forrest, and the directors of graduate study
-in Mathematics, especially Prof.\ Christopher Judge, Prof.\ Matthias
-Weber, and Prof.\ Michael A.\ Mandell. In the department of Computer
-Science, I want to thank the graduate student office; the director
-of AI/UI assignments, Charles Pope; the directors of \PhD study in
-Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
-Ergun}; and the infrastructure and technology group (ITG). Particularly,
+associate. In the department of Mathematics, I need to thank the directors
+of graduate study in Mathematics, especially Prof.\ Christopher Judge,
+Prof.\ Matthias Weber, and Prof.\ Michael A.\ Mandell; and the
+graduate services assistant, Kate Forrest. In the department of Computer
+Science, I want to thank the directors of \PhD study in Computer
+Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
+Ergun}; the graduate student office; the director of AI/UI assignments,
+Charles Pope; and the infrastructure and technology group (ITG). Particularly,
 I don't know how much computational power I consumed to count the
@@
 \end{comment}
+Although having no realistic application, the Deutsch algorithm is
+the first quantum algorithm which outperforms any possible classical
+algorithm for the Deutsch problem \cite{Deutsch1985,544199,Mermin2007}.
+The Deutsch problem is to decide whether a function $f\colon\boolt\rightarrow\boolt$
+is constant or balanced. As listed in Table~\ref{tab:Possible-f},
+we have only $4$ different $f$: $2$ of them are constant while
+another $2$ are balanced. Similar to our $\usat$ algorithm in Sec.~\ref{modalquantumcomputing},
+we start by representing $f$ as a Deutsch black box $U_{f}$ in the
+middle of the quantum circuit, Figure~\ref{fig:Quantum-Circuit-Deutsch}.
+To explain why this circuit solves the Deutsch problem, we then compute
+the state in each step explicitly and express them in the Dirac bracket
+notation and its matrix representation in the computational basis
+$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $.
 \begin{figure}[!b]
@@
 \end{figure}
-Although having no realistic application, the Deutsch algorithm is
-the first quantum algorithm which outperforms any possible classical
-algorithm for the Deutsch problem \cite{Deutsch1985,544199,Mermin2007}.
-The Deutsch problem is to decide whether a function $f\colon\boolt\rightarrow\boolt$
-is constant or balanced. As listed in Table~\ref{tab:Possible-f},
-we have only $4$ different $f$: $2$ of them are constant while
-another $2$ are balanced. Similar to our $\usat$ algorithm in Sec.~\ref{modalquantumcomputing},
-we start by representing $f$ as a Deutsch black box $U_{f}$ in the
-middle of the quantum circuit, Figure~\ref{fig:Quantum-Circuit-Deutsch}.
-To explain why this circuit solves the Deutsch problem, we then compute
-the state in each step explicitly and express them in the Dirac bracket
-notation and its matrix representation in the computational basis
-$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $.
 
@@
 of the numbers $\ff{23}=\{0,\ldots,22\}$ modulo 23, we find the $2$-centered
-uninterrupted sequence $S_{2}\left(5\right)=\left\{ 0,1,2,3,4\right\} $,
-followed by $5$, which is both the smallest quadratic non-residue
-and the size of the uninterrupted sequence of quadratic residues (including
+uninterrupted sequence $S_{2}\left(5\right)=\{0,1,2,3,4\}$, followed
+by $5$, which is both the smallest quadratic non-residue and the
+size of the uninterrupted sequence of quadratic residues (including
 $0$) of interest. In particular, it is possible to construct a total
-order for the elements $S_{0}\left(5\right)=\left\{ -2,-1,0,1,2\right\} $
-in the fields $\ff{23}$, $\ff{71}$, $\ff{311}$, etc., but not in
-the smaller fields $\ff{3}$ and $\ff{7}$.
+order for the elements $S_{0}\left(5\right)=\{-2,-1,0,1,2\}$ in the
+fields $\ff{23}$, $\ff{71}$, $\ff{311}$, etc., but not in the smaller
+fields $\ff{3}$ and $\ff{7}$.
 
@@
 given the dimension $D=2$, the allowed probability amplitude coefficients
-are $F^{2}\left(11\right)=\left\{ 0,\pm1,\pm\rmi,\left(\pm1\pm\rmi\right)\right\} $
+are $F^{2}\left(11\right)=\{0,\pm1,\pm\rmi,\left(\pm1\pm\rmi\right)\}$
 (see Table~\ref{table_allowed}). Now the cardinal probabilities
@@
 are all the same, after the operators $\Delta R$ is applied $l$
-times. Beginning at $l=0$ with the information-less state, the normalization
-scaled to integer values as usual, the state after $l$-th iteration
-can be written as %
+times. Beginning at $l=0$ with the information-less state and the
+normalization scaled to integer values as usual, the state after $l$-th
+iteration can be written as %
 \begin{comment}

### 2019-02-22 dissertation.tex
dissertation.lyx Sec. 4.7 Reviewed...

@@
 
-Although cardinal probabilities can be ordered as discussed in \ref{discretequantumtheoryIIb},
+Although cardinal probabilities can be ordered as discussed in Sec.~\ref{discretequantumtheoryIIb},
 it is still unclear how to define their arithmetic operations, which
@@
 Eq.~(\ref{eq:cardinalProbability}) is based on the conventional
-Born rule, Eq.~(\ref{eq:Born-ComputationalBasis}) which could be
+Born rule, Eq.~(\ref{eq:Born-ComputationalBasis}), which could be
 derived axiomatically according to Gleason's theorem as in Sec.~\ref{subsec:Gleason's-Theorem-and}.
@@
 QPMFFs and states. However, when $D=3$ and $p=7$, we have numerically
-verified that the only QPMFF $\mu\colon\events_{7^{2}}\rightarrow\left[0,1\right]$
-is %
-\begin{comment}
-\todo{Equal probable.}
-\end{comment}
+verified that the unique QPMFF $\mu\colon\events_{7^{2}}\rightarrow\left[0,1\right]$
+is the equal probable one
 \begin{equation}
@@
 \end{equation}
-As we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}), the
-number of unique irreducible pure states in $\ff{7^{2}}^{3}$ is 
+However, the irreducible pure states in $\ff{7^{2}}^{3}$ is not unique.
+Indeed, there are 
 \begin{equation}
@@
 \end{equation}
-which is much more than one, the number of QPMFF\@. Since we don't
-have enough QPMFF to correspond even pure states, there is no discrete
-Born rule in this case. In general, we conjecture that QPMFF is always
-unique for $D\ge3$ except $D=p=3$.
+irreducible pure states in $\ff{7^{2}}^{3}$ as we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}).
+Since we don't have enough QPMFF to correspond even pure states, there
+is no discrete Born rule in this case. In general, we conjecture that
+QPMFF is always unique for $D\ge3$ except $D=p=3$.
 
@@
 
-Following the similar computation to the previous paragraph, we now
+Following the computation similar to the previous paragraph, we now
 compute the probabilities induced by $\ket{\Phi'}=U'\ket{\oplus}=\frac{2\alpha}{\gamma}\ket{0}+\frac{1}{\gamma}\ket{2}$,

### 2019-02-22 dissertation.tex
dissertation.lyx Secs. 5.1.1, 5.1.2, and partial 5.1.3 Reviewed...

@@
 sense that a restriction of QIVPMs to mutually commuting subspace
-of events, $\eventsC$, recovers the definition of classical IVPMs.
- To see this, we first define a subspace of events. $\events'$ is
+of events~$\eventsC$ recovers the definition of classical IVPMs.
+ To see this, we first define a subspace of events: $\events'$ is
 called a \emph{subspace} of the set of events~$\events$ if $\events'$
@@
 $E\subseteq\Omega$ such that $\bar{\mu}\left(E\right)=\left[0.2,0.3\right]$
-and $\bar{\mu}\left(\overline{E}\right)=\left[0.7,0.8\right]$, we
-discussed the ``true'' probabilities, $\mu\left(E\right)$ and $\mu\left(\overline{E}\right)$,
+and $\bar{\mu}\left(E\right)=\left[0.7,0.8\right]$, we discussed
+the ``true'' probabilities, $\mu\left(E\right)$ and $\mu\left(\overline{E}\right)$,
 can be anywhere in the range $\left[0.2,0.3\right]$ and $\left[0.7,0.8\right]$,
-respectively, as long as they satisfy $\mu\left(E\right)+\mu\left(\overline{E}\right)=1$.
-These ``true'' probabilities can be represented as a probability
-measure $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$ satisfying
+respectively, as long as they satisfy 
+\begin{equation}
+\mu\left(E\right)+\mu\left(\overline{E}\right)=1\,.\label{eq:total-probability}
+\end{equation}
+Eq.~(\ref{eq:total-probability}) guarantees the function mapping
+an event to its ``true'' probabilities, $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$,
+is a probability measure. Requiring the ``true'' probability of
+each event should be in the range spanned by the interval-valued probability
+of the same event, i.e., 
 \begin{align}
-\mu\left(E\right) & \in\left[0.2,0.3\right]=\bar{\mu}\left(E\right)\,, & \mu\left(\overline{E}\right) & \in\left[0.7,0.8\right]=\bar{\mu}\left(\overline{E}\right)\,.
-\end{align}
-Together with the trivial fact
-\begin{align}
+\mu\left(E\right) & \in\left[0.2,0.3\right]=\bar{\mu}\left(E\right)\,, & \mu\left(\overline{E}\right) & \in\left[0.7,0.8\right]=\bar{\mu}\left(\overline{E}\right)\,,\\
 \mu\left(\emptyset\right) & =0\in\imposs=\bar{\mu}\left(\emptyset\right)\,, & \mu\left(\Omega\right) & =1\in\necess=\bar{\mu}\left(\Omega\right)\,,
 \end{align}
-we conclude the ``true'' probability of each event belongs to the
-interval probability of the corresponding event. This conclusion gives
-the following definition of core.
+gives the following definition of core.
 
@@
 \begin{equation}
-1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.2+2\cdot0.8=1.8\,.
+\int X\rmd\pmeas=1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.2+2\cdot0.8=1.8\,.
 \end{equation}
@@
 \begin{equation}
-1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.3+2\cdot0.7=1.7\,.
+\int X\rmd\pmeas=1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.3+2\cdot0.7=1.7\,.
 \end{equation}
 In other words, if $\mu$ is in the core of $\bar{\mu}$, the expectation
-value of $X$ belongs to $\left[1.7,1.8\right]$ which should be the
-expectation value of $X$ with respect to $\bar{\mu}$.
+value of $X$ relative to $\mu$, $\int X\rmd\pmeas$, belongs to
+$\left[1.7,1.8\right]$ which should be the expectation value of $X$
+relative to $\bar{\mu}$.
 

### 2019-02-22 dissertation.tex
dissertation.lyx "4.6.2 Discrete Grover Search: Nondeterministic" Replaced $\Delta$ by $V$ to avoid conflicting of symbols...

@@
 \begin{equation}
-\Delta=\begin{pmatrix}1-\frac{N}{2} & 1 & 1 & \cdots & 1\\
+V=\begin{pmatrix}1-\frac{N}{2} & 1 & 1 & \cdots & 1\\
 1 & 1-\frac{N}{2} & 1 & \cdots & 1\\
@@
 \end{equation}
-where we have eliminated, in matrix~$\Delta$, the scaling factor
-$\frac{2}{N}$ to enforce the requirement that all matrix coefficients
-in our framework are integer-valued. By applying the transformation
-$\Delta R$ repeatedly 
+where we have eliminated, in matrix~$V$, the scaling factor $\frac{2}{N}$
+to enforce the requirement that all matrix coefficients in our framework
+are integer-valued. By applying the transformation $VR$ repeatedly
 \begin{equation}
@@
 the probability amplitude of each of the other possibilities, which
-are all the same, after the operators $\Delta R$ is applied $l$
-times. Beginning at $l=0$ with the information-less state and the
-normalization scaled to integer values as usual, the state after $l$-th
-iteration can be written as %
+are all the same, after the operators $VR$ is applied $l$ times.
+Beginning at $l=0$ with the information-less state and the normalization
+scaled to integer values as usual, the state after $l$-th iteration
+can be written as %
 \begin{comment}
@@
 b_{l}
-\end{pmatrix}=\left(\Delta R\right)^{l}\begin{pmatrix}1\\
+\end{pmatrix}=\left(VR\right)^{l}\begin{pmatrix}1\\
 1\\
@@
 1
-\end{pmatrix}=\Delta R\begin{pmatrix}a_{l-1}\\
+\end{pmatrix}=VR\begin{pmatrix}a_{l-1}\\
 b_{l-1}\\
@@
 The initial information-less $8$-dimensional state vector evolves
-under the application of $\Delta R$ as follows: %
+under the application of $VR$ as follows: %
 \begin{comment}
@@
 We may thus conclude that the cardinal probability of measuring the
-satisfying assignment of $f$ increases as we apply the diffusion
-$\Delta$ and phase rotation $R$ matrices repeatedly.
+satisfying assignment of $f$ increases as we apply the diffusion~$V$
+and phase rotation~$R$ matrices repeatedly.
 

### 2019-02-27 dissertation.tex
dissertation.lyx Acknowledgments Updates...

@@
 Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超), Prof.~Jyh-Chyi
-Gong (龔治齊), and 江靜宜, \ldots , etc.
+Gong (龔治齊), 江靜宜, and the office of International Services\ldots ,
+etc.
 

### 2019-03-24 dissertation.tex
CV.docm Add the URL for HackerRank...
dissertation.lyx Updating according to Amr's suggestion... Pending: $\mathcal$, sort reference, and write a conclusion...

@@
 \end{sidewaystable}
-I want to thank the professors served in all my committees. These
+I want to thank the professors who served in all my committees. These
 professors advised me as committee members and taught me while we
@@
 to incorporate this limitation into our quantum mechanical model to
-better capture our ability to predict quantum phenomenon and the power
+better capture our ability to predict quantum phenomena and the power
 of realistic quantum computers. Since we are agnostic about whether
@@
 the complex numbers by finite fields. We then focus on the limitation
-of distinguishability itself, incorporate the finite precision measurement
+of distinguishability itself, incorporate finite precision measurements
 into our model, and consider quantum interval-valued probability measures.
@@
 IBM, \textitalian{Rigetti}, Google, Microsoft, and many other companies
-and countries start to build realistic quantum computers recently
-\cite{Shieber2018,Kahn2019} and seek more efficient ways to simulate
-chemical molecules and to break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}.
+and countries have started to build realistic quantum computers recently
+\cite{Shieber2018,Kahn2019} seeking more efficient ways to simulate
+chemical molecules and breaking RSA \cite{boneh1999twenty,wiki:RSAFactoring}.
 No matter how to, classical or quantum, attack these two tasks, they
@@
 naturally assumed to be continuous. Later, these continuous quantities
-become the basic component of analog computers. After logarithm was
-discovered, a slide rule, also known as a slipstick, is used to compute
+became the basic component of analog computers. After logarithms were
+discovered, a slide rule, also known as a slipstick, was used to compute
 multiplication, division, and more complex operations as a mechanical
 analog computer~\cite{wiki:SlideRule}. Charge amplifiers are used
-to build electrical analog computers and compute the integration in
-calculus \cite{wiki:Integrator,wiki:ChargeAmplifier}.
-
-Although it is convenient to assume physical quantities is as continuous
+to build electrical analog computers and compute integration in calculus
+\cite{wiki:Integrator,wiki:ChargeAmplifier}.
+
+Although it is convenient to assume physical quantities are as continuous
 as their mathematical models, each physical quantity discussed in
@@
 identifying which real number represents its length requires infinite
-precision, but the precision in reality is limited generally three
+precision, but the precision in reality is limited generally to three
 or four significant figures~\cite{wiki:AnalogComputer}. As the results,
@@
 the precision of their inducing probabilities because the idea of
-``imprecise probability'' has well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
+``imprecise probability'' is well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
 \begin{comment}
@@
 
-The part of conventional quantum theory (CQT) used by quantum circuit
-model is described by the following:
+The part of conventional quantum theory (CQT) used by the quantum
+circuit model is described by the following:
 \begin{enumerate}[label=(\roman{enumi})]
@@
 After introducing quantum probability measures, we might follow the
-convention to introduce the Born rule which is the only way corresponding
+convention to introduce the Born rule which is the only way to relate
 a state to a quantum probability measure in CQT\@. However, since
@@
 hidden variable theory. If the prediction of a hidden variable theory
-depending on the measurement bases, this hidden variable theory is
-called \emph{contextual}. The measurement process itself in MQT depending
+depends on the measurement bases, this hidden variable theory is called
+\emph{contextual}. The measurement process itself in MQT depending
 on the bases demonstrates that MQT is more contextual than CQT. Despite
@@
 Applying $S^{\dagger}$ to the first component produces: $\ket{1}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
-Applying control-not gate, which applying $\sigma_{0}$ or $\sigma_{x}$
+Applying control-not gate, which applies $\sigma_{0}$ or $\sigma_{x}$
 on the second component depending on the first component of the state,
@@
 searches of these spaces, we discovered a hypothesis for a closed-form
-solution for the counting of the states and find a rigorous proof
+solution for the counting of the states and found a rigorous proof
 of the enumeration.
@@
 \begin{equation}
-(p+1)p^{2}(p-1)^{2}=\{144,14\,112,145\,200,2339\,280,\ldots\}\,,
+(p+1)p^{2}(p-1)^{2}=\{144,14112,145200,2339280,\ldots\}\,,
 \end{equation}
@@
 \begin{equation}
-p^{2}(p-1)^{2}=\{36,1764,12\,100,116\,964,\ldots\}\,,
+p^{2}(p-1)^{2}=\{36,1764,12100,116964,\ldots\}\,,
 \end{equation}
@@
 \begin{equation}
-p\left(p^{2}-1\right)\left(p+1\right)=\left\{ 96,2688,15\,840,136\,800,\ldots\right\} \,.
+p\left(p^{2}-1\right)\left(p+1\right)=\left\{ 96,2688,15840,136800,\ldots\right\} \,.
 \end{equation}
@@
 means it is more likely to measure $\ket{i}$ than $\ket{j}$ if we
-have enough resource; $\fnorm{\alpha_{i}}=\fnorm{\alpha_{j}}$ means
+have enough resources; $\fnorm{\alpha_{i}}=\fnorm{\alpha_{j}}$ means
 the experimental results might not always favor $\ket{i}$ or $\ket{j}$
 no matter how many resources we use. The same principle can also apply
-to two cardinal probabilities with different ``denominator''. The
+to two cardinal probabilities with different ``denominators''. The
 details of the comparison can be easily formulated by following the
-standard procedure \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016}
-and will leave as an exercise for the readers.
+standard procedure \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016}.
 
@@
 Our definition of QIVPMs is consistent with classical IVPMs in the
-sense that a restriction of QIVPMs to mutually commuting subspace
+sense that a restriction of QIVPMs to mutually commuting subspaces
 of events~$\eventsC$ recovers the definition of classical IVPMs.
@@
 in Eq.~(\ref{eq:pullback-function}) maps any set~$E$ to the sum
-of the projectors formed by elements in $E$, and preserve all operations
+of the projectors formed by elements in $E$, and preserves all operations
 used to define classical and quantum IVPMs as in Eqs.~(\ref{eq:pullback-properties-basic})
@@
 of classical IVPMs directly hold for QIVPMs when one restricts to
-mutually commuting events~$\eventsC$, and one of them is \emph{core}.
-Recall in Sec.~\ref{subsec:Definitions-of-IVPMs}, given a classical
-IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ and an event
-$E\subseteq\Omega$ such that $\bar{\mu}\left(E\right)=\left[0.2,0.3\right]$
+mutually commuting events~$\eventsC$, and one of them is having
+a \emph{core}. Recall in Sec.~\ref{subsec:Definitions-of-IVPMs},
+given a classical IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
+and an event $E\subseteq\Omega$ such that $\bar{\mu}\left(E\right)=\left[0.2,0.3\right]$
 and $\bar{\mu}\left(E\right)=\left[0.7,0.8\right]$, we discussed
@@
 \end{equation}
-Then, Eq.~(\ref{eq:density-matrix-pullback}) can be inductive proved
+Then, Eq.~(\ref{eq:density-matrix-pullback}) can be proved by induction
 on $E$. By Eq.~(\ref{eq:pullback-function}) and the generalized
@@
 a classical sample space~$\Omega$ with a random variable $X\colon\Omega\rightarrow\mathbb{R}$.
-Since we only consider finite sample space, $X$ can always be decomposed
+Since we only consider finite sample spaces, $X$ can always be decomposed
 into the sum of step functions~$\mathbf{1}_{E}$ defined in Def.~\ref{def:observable2random-variable}.
-For our convenience to define the Choquet integral later, we order
-these step functions by their coefficients from the smallest to the
-largest, and express $X$ as follow: 
+For conveniences to define the Choquet integral later, we order these
+step functions by their coefficients from the smallest to the largest,
+and express $X$ as follow: 
 \begin{equation}
@@
 of their step functions $\pmeas\left(E_{i}^{s}\right)$. Instead,
-by computing the accumulative sets $E_{i\uparrow}^{s}=\bigcup_{j\ge i}E_{j}^{s}$
+by computing the cumulative sets $E_{i\uparrow}^{s}=\bigcup_{j\ge i}E_{j}^{s}$
 and their interval-valued probabilities $\bar{\mu}\left(E_{i\uparrow}^{s}\right)$,
@@
 for all $E$. Since the ``weights'' in Eq.~(\ref{eq:interval-expectation})
-are the difference on the probability of the accumulative sets, they
+are the difference on the probability of the cumulative sets, they
 have the same magnitude as the ones in Eq.~(\ref{eq:expectation}),
@@
 \end{table}
-Step-by-step we compute the accumulative sets~$E_{i\uparrow}^{+}$,
+Step-by-step we compute the cumulative sets~$E_{i\uparrow}^{+}$,
 their measures $\mu^{t}\left(E_{i\uparrow}^{+}\right)$, and their
@@
 and each $P_{i}^{s}$ is the projector onto the eigenspace of distinct
-eigenvalue~$\lambda_{i}^{s}$. Consider a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
+eigenvalues~$\lambda_{i}^{s}$. Consider a QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$
 with its left-end and right-end denoted by $\mul\colon\events\rightarrow\left[0,1\right]$
@@
 Let $s$ be either $+$ or $-$ in the superscript in the following
-discussion. We denote $P_{i\uparrow}^{s}$ as the accumulative projectors
+discussion. We denote $P_{i\uparrow}^{s}$ as the cumulative projectors
 on the sub-index $i$, i.e., $P_{i\uparrow}^{s}=\sum_{j\ge i}P_{j}^{s}$,
 and $\Delta\mu^{t}\left(P_{i\uparrow}^{s}\right)$ as the difference
-of the measure of these accumulative projectors, i.e., $\Delta\mu^{t}\left(P_{i\uparrow}^{s}\right)=\mu^{t}\left(P_{i\uparrow}^{s}\right)-\mu^{t}\left(P_{\left(i+1\right)\uparrow}^{s}\right)$,
+of the measure of these cumulative projectors, i.e., $\Delta\mu^{t}\left(P_{i\uparrow}^{s}\right)=\mu^{t}\left(P_{i\uparrow}^{s}\right)-\mu^{t}\left(P_{\left(i+1\right)\uparrow}^{s}\right)$,
 where $t\in\left\{ \symrmL,\symrmR\right\} $. Then, the expectation
@@
 which looks like a weighted average of the difference of the measure
-of these accumulative projectors.\end{definition}
+of these cumulative projectors.\end{definition}
 
@@
 to $P_{i}^{s}$ but also map the other ingredients of the expectation
-values, including the accumulative sets or projectors, their measures,
+values, including the cumulative sets or projectors, their measures,
 and their differences:
@@
 as in Defs.~\ref{def:Choquet} and~\ref{def:expectation-values-QIVPM}.
-Notice that right-most side of Eq.~(\ref{eq:pullback-real-measures})
+Notice that the right-most sides of Eq.~(\ref{eq:pullback-real-measures})
 and~(\ref{eq:pullback-differences}) are actually the pullback of
@@
 Since Def.~\ref{def:expectation-values-QIVPM} is an extension of
-both quantum real expectation value and classical interval expectation
-value, not only the property of quantum real expectation value could
+both quantum real expectation values and classical interval expectation
+values, not only the property of quantum real expectation values could
 be extended to the previous lemma, but the properties of classical
-interval expectation value, like Eq.~(\ref{eq:classical-real-interval-Choquet})
+interval expectation values, like Eq.~(\ref{eq:classical-real-interval-Choquet})
 and Thm.~\ref{thm:Rosenmuller}, could be extended to quantum interval
-expectation value as well. In particular, Eq.~(\ref{eq:classical-real-interval-Choquet})
+expectation values as well. In particular, Eq.~(\ref{eq:classical-real-interval-Choquet})
 can be extended to the following theorem.
@@
 observables in a row is equal to the third, the product of any two
-their expectation values in a row is also equal to the third by Eq.~(\ref{eq:Kochen-Specker-Rules}),
+expectation values in a row is also equal to the third by Eq.~(\ref{eq:Kochen-Specker-Rules}),
 and there must be an even number of occurrences of the interval $[-1,-1]$
@@
 some intersections, but no subset relation, then $E_{0}\cap E_{1}$,
-$E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$ are all non-empties.
+$E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$ are all non-empty.
 Together with the fact that $\Omega$ has only three elements, they
@@
 with a conventional quantum probability measure, and the states consistent
-with the composite QIVPM collapses to a single state as the maximum
+with the composite QIVPM collapse to a single state as the maximum
 length of intervals in $\mathscr{I}$, $\left\Vert \mathscr{I}\right\Vert $,
@@
 With different settings, whether there is an approximate version of
-Gleason's theorem was asked by Sam Sanders in constructivenews on
-2013~\cite{Sanders2013}, and there is no clear answer for his question
-as far as I understand. To have an idea of how hard this question
-could be, recall in Sec.~\ref{sec:fuzzy} we state that a quantum
-probability space is glued by a family of classical probability spaces.
-This is like the situation that a manifold is glued by many local
-coordinates. When each small piece has \emph{exactly} the same and
-positive curvature, the Killing-Hopf theorem asserts this manifold
-is a sphere, but little can we say even if the curvature has a small
-deviation from constant. A similar situation might happen when approximating
-Gleason's theorem, but this time the whole space is glued by ``local''
-classical probability space defined by each orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
+Gleason's theorem was asked by Sam Sanders in \emph{constructivenews}
+on 2013~\cite{Sanders2013}, and there is no clear answer for his
+question. To have an idea of how hard this question could be, recall
+in Sec.~\ref{sec:fuzzy} we state that a quantum probability space
+is glued by a family of classical probability spaces. This is like
+the situation that a manifold is glued by many local coordinates.
+When each small piece has \emph{exactly} the same and positive curvature,
+the Killing-Hopf theorem asserts this manifold is a sphere, but little
+can we say even if the curvature has a small deviation from constant.
+A similar situation might happen when approximating Gleason's theorem,
+but this time the whole space is glued by ``local'' classical probability
+space defined by each orthonormal basis $\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$.
 When the sum of $\frameL$, $\sum_{i=0}^{2}\frameL\left(\ket{\psi_{i}}\right)$,
@@
 \noindent Understanding the properties of these probability measures
-and whether we could define a ``sensible'' Born upon them combine
+and whether we could define a ``sensible'' Born rule upon them combines
 two approaches for dealing with the continuous quantities used in
@@
 
-\clearpageAddContentsChapter{Bibliography} %
+\chapter{Conclusion}
+
+\clearpageAddContents{chapter}{Bibliography} %
 \begin{comment}

### 2019-03-25 dissertation.tex
dissertation.lyx Bibliography Sorted...

@@
 \setotherlanguage{vietnamese}
-\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
+\usepackage[style=numeric-comp,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
 \addbibresource{prop.bib}
@@
 
-\chapter{Further Discussion\label{chap:Further-Discussion}}
+\chapter{Conclusion and Further Discussion\label{chap:Further-Discussion}}
+
+\section{Conclusion}
+
+Before what we can do further based on this thesis, let's summarize
+what we have done previously.\todo{Keep writing\ldots}
 
@@
 
-\chapter{Conclusion}
-
 \clearpageAddContents{chapter}{Bibliography} %

### 2019-03-25 dissertation.tex
dissertation.lyx Global replace ${\cal H}$ to $\Hilb$...

@@
 The expectation value of an observable $\mathbf{O}$ in a Hilbert
-space ${\cal H}$ of dimension $D$ relative to a 0-deterministic
-QIVPM is fully determinate and is equal to one of the eigenvalues
-$\lambda_{i}$ of that observable. To see this, note that given an
-orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$,
-a 0-deterministic QIVPM must map exactly one of the projectors $\proj{i}$
-to $\necess$ and all others to $\imposs$. This is because, by Eq.~(\ref{eq:QIVPM-necess}),
+space $\Hilb$ of dimension $D$ relative to a 0-deterministic QIVPM
+is fully determinate and is equal to one of the eigenvalues $\lambda_{i}$
+of that observable. To see this, note that given an orthonormal basis
+$\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$, a 0-deterministic
+QIVPM must map exactly one of the projectors $\proj{i}$ to $\necess$
+and all others to $\imposs$. This is because, by Eq.~(\ref{eq:QIVPM-necess}),
 we have $\bar{\mu}\left(\sum_{j=0}^{D-1}{\proj{j}}\right)=\necess$
@@
 
-Given a Hilbert space ${\cal H}$ of dimension $D$, the expectation
+Given a Hilbert space $\Hilb$ of dimension $D$, the expectation
 value of the product of a sequence of commuting observables $\left\{ \mathbf{O}_{j}\right\} $
@@
 such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
-%% ajh: fixed garbled statement, add ${\cal H}$
+%% ajh: fixed garbled statement, add $$
 

### 2019-03-28 dissertation.tex
dissertation.lyx "6.1 Conclusion" Updating...

@@
 Before what we can do further based on this thesis, let's summarize
-what we have done previously.\todo{Keep writing\ldots}
+what we have done previously. In Chapter~\ref{chap:Conventional-Quantum-Theory},
+we reviewed what was established in CQT. In particular, Sec.~\ref{CQC1qubitBloch.sec}
+studied the geometrical structure of quantum states to prepare replacing
+the conventional projective Hilbert space~$\CP{D-1}$ by its discrete
+analog in Chapter~\ref{chap:Unrestricted-Finite-Fields} and~\ref{chap:DQT=000026DQC}.
+Since the replacing state spaces are discrete, after \todo{Keep writing\ldots}
 

### 2019-03-29 dissertation.tex
dissertation.lyx "6.1 Conclusion" Updating...

--- 2019-03-25 dissertation.tex
@@
 Before what we can do further based on this thesis, let's summarize
-what we have done previously.\todo{Keep writing\ldots}
+what we have done previously. In Chapter~\ref{chap:Conventional-Quantum-Theory},
+we reviewed what was established in CQT. In particular, Sec.~\ref{CQC1qubitBloch.sec}
+studied the geometrical structure of quantum states to prepare replacing
+the conventional Hilbert space~$\mathComplex^{D}$ or projective
+Hilbert space~$\CP{D-1}$ by its discrete analog in Chapter~\ref{chap:Unrestricted-Finite-Fields}
+and~\ref{chap:DQT=000026DQC}. Since the replaced state spaces are
+discrete, the quantum computation model could be built upon them naturally.
+In Chapter~\ref{chap:Unrestricted-Finite-Fields}, the field of complex
+numbers~$\mathComplex$ is replaced by unrestricted finite fields~$\Fq$,
+and a valid pure state can be represented as any non-zero vector in
+$\Fq^{D}$ and a measure scheme could be defined which only predicts
+whether an measurement result is possible or not. \todo{Keep writing\ldots}
 

### 2019-04-04 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

@@
 
-\section{Conclusion}
-
-Before what we can do further based on this thesis, let's summarize
-what we have done previously. In Chapter~\ref{chap:Conventional-Quantum-Theory},
+\section{Summary}
+
+Since conventional quantum theory is defined over the continuum of
+complex numbers which cannot be identified with unbounded resources,
+it is natural to explore alternative versions of quantum theory incorporate
+our limitation of distinguishability. Examining the computational
+and physical consequences of such frameworks can yield new insights
+into the power and capacity of quantum computing. We have described
+two types of discrete quantum theories: quantum theories and computing
+over finite fields and quantum interval-valued probability measures.
+
+The theories over finite fields starting with unrestricted discrete
+fields (modal theories), then advancing to a more reasonable framework
+based on complexifiable discrete fields (discrete quantum theory I),
+which not only supports unnaturally efficient deterministic quantum
+algorithms but also lacks the ability to .
+
+\todo{Clean up until here\ldots}
+
+....
+
+Before discussing the further extension, let's summarize what we have
+done previously. In Chapter~\ref{chap:Conventional-Quantum-Theory},
 we reviewed what was established in CQT. In particular, Sec.~\ref{CQC1qubitBloch.sec}
@@
 Hilbert space~$\CP{D-1}$ by its discrete analog in Chapter~\ref{chap:Unrestricted-Finite-Fields}
-and~\ref{chap:DQT=000026DQC}. Since the replaced state spaces are
-discrete, the quantum computation model could be built upon them naturally.
-In Chapter~\ref{chap:Unrestricted-Finite-Fields}, the field of complex
-numbers~$\mathComplex$ is replaced by unrestricted finite fields~$\Fq$,
-and a valid pure state can be represented as any non-zero vector in
-$\Fq^{D}$ and a measure scheme could be defined which only predicts
+and~\ref{chap:DQT=000026DQC}. In Chapter~\ref{chap:Unrestricted-Finite-Fields},
+the field of complex numbers~$\mathComplex$ is replaced by unrestricted
+finite fields~$\Fq$. Although this modal theory is
+
+, and a valid pure state can be represented as any non-zero vector
+in $\Fq^{D}$ and a measure scheme could be defined which only predicts
 whether an measurement result is possible or not. \todo{Keep writing\ldots}

### 2019-04-06 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

@@
 Since conventional quantum theory is defined over the continuum of
-complex numbers which cannot be identified with unbounded resources,
-it is natural to explore alternative versions of quantum theory incorporate
-our limitation of distinguishability. Examining the computational
+complex numbers, but each complex number can only be identified with
+unbounded resources, it is natural to explore alternative versions
+of quantum theory incorporate our limitation of distinguishability.
+Two types of discrete quantum theories have been described in this
+thesis: quantum theories and computing over finite fields and quantum
+interval-valued probability measures. Examining the computational
 and physical consequences of such frameworks can yield new insights
-into the power and capacity of quantum computing. We have described
-two types of discrete quantum theories: quantum theories and computing
-over finite fields and quantum interval-valued probability measures.
+into not only the subtle properties of conventional quantum theory
+but also the power and capacity of quantum computing.
 

### 2019-04-06 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

@@
 
-Since conventional quantum theory is defined over the continuum of
-complex numbers, but each complex number can only be identified with
-unbounded resources, it is natural to explore alternative versions
-of quantum theory incorporate our limitation of distinguishability.
-Two types of discrete quantum theories have been described in this
-thesis: quantum theories and computing over finite fields and quantum
-interval-valued probability measures. Examining the computational
-and physical consequences of such frameworks can yield new insights
-into not only the subtle properties of conventional quantum theory
-but also the power and capacity of quantum computing.
+Conventional quantum theory is defined over the continuum of complex
+numbers, but each complex number can only be identified with unbounded
+resources. To explore alternative versions of quantum theory incorporating
+our limitation of distinguishability, two types of discrete quantum
+theories have been described in this thesis: quantum theories and
+computing over finite fields and quantum interval-valued probability
+measures. Examining the computational and physical consequences of
+such frameworks can yield new insights into not only the subtle properties
+of conventional quantum theory but also the power and capacity of
+quantum computing.
 
@@
 based on complexifiable discrete fields (discrete quantum theory I),
-which not only supports unnaturally efficient deterministic quantum
-algorithms but also lacks the ability to .
+which lacks a notion of probability and supports unnaturally efficient
+deterministic quantum algorithms. A still more plausible discrete
+theory (discrete quantum theory II) is proposed, where conventional
+quantum computing and conventional quantum theory emerge in a local
+sense.
 

### 2019-04-07 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

@@
 Conventional quantum theory is defined over the continuum of complex
-numbers, but each complex number can only be identified with unbounded
-resources. To explore alternative versions of quantum theory incorporating
-our limitation of distinguishability, two types of discrete quantum
-theories have been described in this thesis: quantum theories and
-computing over finite fields and quantum interval-valued probability
+numbers, but we cannot distinguish two arbitrary complex numbers without
+unbounded resources. To explore alternative versions of quantum theory
+incorporating our limitation of distinguishability, two types of discrete
+quantum theories have been described in this thesis: quantum theories
+and computing over finite fields and quantum interval-valued probability
 measures. Examining the computational and physical consequences of
@@
 theory (discrete quantum theory II) is proposed, where conventional
-quantum computing and conventional quantum theory emerge in a local
-sense.
+quantum theory and computing emerge in a local sense. However, since
 

### 2019-04-16 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

@@
 
-The theories over finite fields starting with unrestricted discrete
-fields (modal theories), then advancing to a more reasonable framework
-based on complexifiable discrete fields (discrete quantum theory I),
+The theories over finite fields started with unrestricted discrete
+fields (Chapter~\ref{chap:Unrestricted-Finite-Fields}), then advanced
+to a more reasonable framework based on complexifiable discrete fields
+(Sec.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
 which lacks a notion of probability and supports unnaturally efficient
 deterministic quantum algorithms. A still more plausible discrete
-theory (discrete quantum theory II) is proposed, where conventional
-quantum theory and computing emerge in a local sense. However, since
-
-\todo{Clean up until here\ldots}
+theory with cardinal probabilities is proposed (Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
+and~\ref{discretequantumcomputingII}), where conventional quantum
+theory and computing emerge in a local sense, but lacking arithmetic
+operations among cardinal probabilities still posed difficulty to
+define expectation values. One attempt to address this issue was to
+switch to an axiomatic approach and following Gleason's theorem to
+deduce a Born rule over finite fields (Sec.~\ref{sec:Toward-IVPM}).
+However, quantum theories over finite fields looked unlikely to compatible
+with infinitely precise real-valued probability; we thus extended
+the classical imprecise interval-valued probability to quantum domain,
+and defined quantum interval-valued probability measures (QIVPMs).
+
+\begin{figure}[b]
+\centering{}$\xymatrix{\textrm{Classical Probability Measure}\ar[d]\ar[r] & \textrm{Quantum Probability Measure}\ar[d]\\
+\textrm{Classical IVPM}\ar[r] & \textrm{QIVPM}
+}
+$\caption{\label{fig:commutative-diagrams}Quantum IVPMs inherited from both
+quantum probability measures and classical IVPMs. Since Quantum IVPMs
+inherited from classical probability measures in two different paths,
+it is natural to ask whether this diagram commutes.}
+\end{figure}
+As a natural extension of both convention quantum probability measures
+and classical interval-valued probability measures (IVPMs) illustrated
+in Fig.~\ref{fig:commutative-diagrams}, QIVPMs inherited definitions
+and properties from the both sides. While the core and expectation
+values of QIVPMs can be pulled back to the classical cases and consistent
+with those of quantum probability measures in the infinitely precise
+limit (Sec.~\ref{sec:Interval-Uncertainty}), foundational concepts
+in quantum mechanics, such as the Kochen-Specker and Gleason theorems,
+extended to QIVPMs in subtle ways. \todo{Clean up until here\ldots}
+
+Similar to gluing a family of classical probability spaces together
+to form a conventional quantum probability space (Sec.~\ref{sec:fuzzy}),
+a family of classical IVPMs can be glued to get a quantum IVPM. Although
+most of structures above classical IVPMs can be extended to the quantum
+case (Sec.~\ref{sec:Interval-Uncertainty}), .
 

### 2019-04-17 dissertation.tex
dissertation.lyx "Chapter 6 Conclusion and Further Discussion" Updating...

--- 2019-04-06 dissertation.tex
@@
 
-Conventional quantum theory is defined over the continuum of complex
-numbers, but each complex number can only be identified with unbounded
+Conventional quantum theory is based on the continuum of complex numbers,
+but we cannot distinguish two arbitrary complex numbers without unbounded
 resources. To explore alternative versions of quantum theory incorporating
 our limitation of distinguishability, two types of discrete quantum
-theories have been described in this thesis: quantum theories and
-computing over finite fields and quantum interval-valued probability
-measures. Examining the computational and physical consequences of
-such frameworks can yield new insights into not only the subtle properties
-of conventional quantum theory but also the power and capacity of
-quantum computing.
-
-The theories over finite fields starting with unrestricted discrete
-fields (modal theories), then advancing to a more reasonable framework
-based on complexifiable discrete fields (discrete quantum theory I),
-which lacks a notion of probability and supports unnaturally efficient
+theories were described: \emph{quantum theories and computing over
+finite fields} and \emph{quantum interval-valued probability measures
+(QIVPMs)}. Examining the computational and physical consequences of
+such frameworks could yield new insights into not only the subtle
+properties of conventional quantum theory but also the power and capacity
+of quantum computing.
+
+The theories over finite fields started with unrestricted discrete
+fields (Chapter~\ref{chap:Unrestricted-Finite-Fields}), then advanced
+to a more reasonable framework based on complexifiable discrete fields
+(Sec.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
+which lacked a notion of probability and supported unnaturally efficient
 deterministic quantum algorithms. A still more plausible discrete
-theory (discrete quantum theory II) is proposed, where conventional
-quantum computing and conventional quantum theory emerge in a local
-sense.
-
-\todo{Clean up until here\ldots}
-
-....
-
-Before discussing the further extension, let's summarize what we have
-done previously. In Chapter~\ref{chap:Conventional-Quantum-Theory},
-we reviewed what was established in CQT. In particular, Sec.~\ref{CQC1qubitBloch.sec}
-studied the geometrical structure of quantum states to prepare replacing
-the conventional Hilbert space~$\mathComplex^{D}$ or projective
-Hilbert space~$\CP{D-1}$ by its discrete analog in Chapter~\ref{chap:Unrestricted-Finite-Fields}
-and~\ref{chap:DQT=000026DQC}. In Chapter~\ref{chap:Unrestricted-Finite-Fields},
-the field of complex numbers~$\mathComplex$ is replaced by unrestricted
-finite fields~$\Fq$. Although this modal theory is
-
-, and a valid pure state can be represented as any non-zero vector
-in $\Fq^{D}$ and a measure scheme could be defined which only predicts
-whether an measurement result is possible or not. \todo{Keep writing\ldots}
+theory with cardinal probabilities was proposed (Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
+and~\ref{discretequantumcomputingII}), where conventional quantum
+theory and computing emerged in a local sense, but lacking arithmetic
+operations among cardinal probabilities still posed difficulty to
+define expectation values. Since the axiomatic approach looked unlikely
+to provide ``sensible'' real-valued probability measures over finite
+fields (Sec.~\ref{sec:Toward-IVPM}), we shifted our attention to
+directly embed our limitation of distinguishability into the theory
+to define QIVPM.
+
+\begin{figure}[b]
+\centering{}$\xymatrix{\textrm{Classical Probability Measure}\ar[d]_{\textrm{blur probability}}\ar[r]^{\textrm{glue events}} & \textrm{Quantum Probability Measure}\ar[d]^{\textrm{blur probability}}\\
+\textrm{Classical IVPM}\ar[r]_{\textrm{glue events}} & \textrm{QIVPM}
+}
+$\caption{\label{fig:commutative-diagrams}QIVPMs inherited from both quantum
+probability measures and classical IVPMs.\todo{The first arrow is
+too short!}}
+\end{figure}
+As a natural extension of both convention quantum probability measures
+and classical interval-valued probability measures (IVPMs) illustrated
+in Fig.~\ref{fig:commutative-diagrams}, QIVPMs inherited definitions
+and properties from the both sides. While the expectation values of
+QIVPMs could be pulled back to the classical cases and consistent
+with those of quantum probability measures in the infinitely precise
+limit (Sec.~\ref{sec:Interval-Uncertainty}), foundational concepts
+in quantum mechanics, such as the Kochen-Specker and Gleason theorems,
+extended to QIVPMs in subtle ways. By carefully specifying experimental
+uncertainties, we established rigorous bounds on the validity of the
+Kochen-Specker theorem (Sec.~\ref{sec:Kochen-Specker}). While there
+is a QIVPM not consistent with Gleason's unique state~$\rho$ on
+all projectors, we constructed a class of QIVPMs for which the original
+Gleason theorem could be recovered asymptotically (Sec.~\ref{sec:Gleason}).
+
+In the following further discussion, we will briefly explain why we
+can only recover Gleason's on a class of QIVPM, the possibility to
+further build a computational model over QIVPMs, and the possibility
+to combine two approaches to consider quantum interval-valued probability
+measures over finite fields.
 
@@
 \end{comment}
-As we discussed in the previous section, Thm.~\ref{thm:Finite-precision-Gleason}
+As we discussed in Sec.~\ref{sec:Gleason}, Thm.~\ref{thm:Finite-precision-Gleason}
 only applies to the QIVPMs constructed by composing an interval map

### 2019-04-21 dissertation.tex
dissertation.lyx "Chapter 6 Conclusion and Further Discussion" Updating...

@@
 \begin{comment}
-\todo{Maybe extended to consider probabilistic model? }
+\todo{Maybe extended to consider probabilistic model? For BCSS machine,
+maybe using the idea of BPP to define the complexity class is more
+reasonable than P or NP?}
 \end{comment}
@@
 (QIVPMs)}. Examining the computational and physical consequences of
-such frameworks could yield new insights into not only the subtle
-properties of conventional quantum theory but also the power and capacity
-of quantum computing.
+such frameworks can yield new insights into not only the subtle properties
+of conventional quantum theory but also the power and capacity of
+quantum computing.
 
@@
 to a more reasonable framework based on complexifiable discrete fields
-(Sec.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
-which lacked a notion of probability and supported unnaturally efficient
+(Secs.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
+which lacks a notion of probability and supports unnaturally efficient
 deterministic quantum algorithms. A still more plausible discrete
-theory with cardinal probabilities was proposed (Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
+theory with cardinal probabilities was proposed (Secs.~\ref{sec:Discrete-Quantum-Theory-(II)}
 and~\ref{discretequantumcomputingII}), where conventional quantum
-theory and computing emerged in a local sense, but lacking arithmetic
+theory and computing emerge in a local sense, but lacking arithmetic
 operations among cardinal probabilities still posed difficulty to
 define expectation values. Since the axiomatic approach looked unlikely
-to provide ``sensible'' real-valued probability measures over finite
-fields (Sec.~\ref{sec:Toward-IVPM}), we shifted our attention to
-directly embed our limitation of distinguishability into the theory
-to define QIVPM.
+to provide sensible real-valued probability measures over finite fields
+(Sec.~\ref{sec:Toward-IVPM}), we shifted our attention to directly
+embed our limitation of distinguishability into the theory to define
+QIVPM.
 
 \begin{figure}[b]
-\centering{}$\xymatrix{\textrm{Classical Probability Measure}\ar[d]_{\textrm{blur probability}}\ar[r]^{\textrm{glue events}} & \textrm{Quantum Probability Measure}\ar[d]^{\textrm{blur probability}}\\
-\textrm{Classical IVPM}\ar[r]_{\textrm{glue events}} & \textrm{QIVPM}
+\centering{}$\xymatrix{\textrm{Classical Probability Measure}\ar[d]_{\textrm{blur probability}}\ar[rr]^{\textrm{glue events}} &  & \textrm{Quantum Probability Measure}\ar[d]^{\textrm{blur probability}}\\
+\textrm{Classical IVPM}\ar[rr]_{\textrm{glue events}} &  & \textrm{QIVPM}
 }
-$\caption{\label{fig:commutative-diagrams}QIVPMs inherited from both quantum
-probability measures and classical IVPMs.\todo{The first arrow is
-too short!}}
+$\caption{\label{fig:commutative-diagrams}QIVPMs inherit from both quantum
+probability measures and classical IVPMs.}
 \end{figure}
-As a natural extension of both convention quantum probability measures
+As a natural extension of both conventional quantum probability measures
 and classical interval-valued probability measures (IVPMs) illustrated
-in Fig.~\ref{fig:commutative-diagrams}, QIVPMs inherited definitions
+in Fig.~\ref{fig:commutative-diagrams}, QIVPMs inherit definitions
 and properties from the both sides. While the expectation values of
-QIVPMs could be pulled back to the classical cases and consistent
-with those of quantum probability measures in the infinitely precise
-limit (Sec.~\ref{sec:Interval-Uncertainty}), foundational concepts
-in quantum mechanics, such as the Kochen-Specker and Gleason theorems,
+QIVPMs can be pulled back to the classical cases and consistent with
+those of quantum probability measures in the infinitely precise limit
+(Sec.~\ref{sec:Interval-Uncertainty}), foundational concepts in
+quantum mechanics, such as the Kochen-Specker and Gleason theorems,
 extended to QIVPMs in subtle ways. By carefully specifying experimental
@@
 In the following further discussion, we will briefly explain why we
-can only recover Gleason's on a class of QIVPM, the possibility to
+only recovered Gleason's on a class of QIVPMs, the possibility to
 further build a computational model over QIVPMs, and the possibility
-to combine two approaches to consider quantum interval-valued probability
+combining both approaches to consider quantum interval-valued probability
 measures over finite fields.
@@
 of functions $\frameL\colon\CP{2}\rightarrow\left[0,1\right]$ and
-$\frameR\colon\CP{2}\rightarrow\left[0,1\right]$ defined by $\left[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)\right]=\bar{\mu}\left(\proj{\psi}\right)$
+$\frameR\colon\CP{2}\rightarrow\left[0,1\right]$ defined by $[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)]=\bar{\mu}\left(\proj{\psi}\right)$
 for any irreducible state $\ket{\psi}\in\CP{2}$. According to Lemma~\ref{thm:convex-3-1},
@@
 
-A successful interval-valued theory might be further extended to the
-quantum theory over finite fields based on the following definition.
+A successful interval-valued theory might be further extended over
+finite fields based on the following definition.
 

### 2019-04-22 dissertation.tex
dissertation.lyx Replaced URLs from \code to \url...

@@
 \usepackage{mathrsfs}
+\usepackage{url}
 \usepackage{enumitem}
@@
 \begin{itemize}
-\item The latest PDF version of this thesis is in GitHub: \code{https://git.io/fxbuG}.
-\item Its source code is typeset using \LyX{} \cite{LyX} in \code{https://git.io/fxbuE}
-and the exported \LaTeX{} file is in \code{https://git.io/fhZBW}.
+\item The latest PDF version of this thesis is in GitHub: \url{https://git.io/fxbuG}.
+\item Its source code is typeset using \LyX{} \cite{LyX} in \url{https://git.io/fxbuE}
+and the exported \LaTeX{} file is in \url{https://git.io/fhZBW}.
 \item Any comments can be left in the Issue part of the GitHub repository:
-\code{https://git.io/fxbug}.
+\url{https://git.io/fxbug}.
 \end{itemize}
@@
 \item \label{enu:Clone-the-git}Clone the git repository of this thesis
-\code{https://git.io/fhZP5} into your local directory and the thesis
-document class \code{https://github.com/yuttai/iuphd} in a location
+\url{https://git.io/fhZP5} into your local directory and the thesis
+document class \url{https://github.com/yuttai/iuphd} in a location
 where the system can find.
@@
 power set~$2^{\Omega}$ as the classical event space, a classical
-IVPM~$\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ is a function
+IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ is a function
 subject to the following constraints:\begin{subequations}\label{eq:CIVPM-constraints}
@@
 Then we proceed as follows:
-
+\begin{align*}
+ & \bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
+={} & \bar{\mu}\left(P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{because }P_{0}=P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1}))\\
+={} & \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
+={} & \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{because }P_{1}=P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1})\\
+={} & \bar{\mu}(P_{0}(\mathbb{1}-P_{1}))+\bar{\mu}(P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1})+\bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{using Eq.~(\ref{amr}) twice})\\
+={} & \bar{\mu}(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1}+P_{0}P_{1}) & (\mbox{using Eq.~(\ref{amr}) twice})\\
+={} & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})
+\end{align*}
+\begin{comment}
 \noindent 
@@
 \end{equation*}
+\end{comment}
 \end{proof}
@@
 or $\left[1-\delta,1\right]$, $\bar{\mu}\left(P'+P''\right)$ must
-be a subset of $\left[0,\delta\right]$, which implies $\barmuD\left(P'+P''\right)=\imposs$,
+be a subset of $\left[0,\delta\right]$, which implies $\barmuD(P'+P'')=\imposs$,
 and hence also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal})

### 2019-04-22 dissertation.tex
dissertation.lyx Global replace "-dimensional" by "-dimen\-sional"

@@
 \newcommand{\PhD}{Ph.D.\ }
+
+% \hyphenation{$D$=dimen-sional}
 
@@
 An $n$-qubit pure state in the conventional quantum theory (CQT)
-is represented as a vector in the $2^{n}$-dimensional Hilbert space.
-If we eliminate all symmetries, an irreducible state is actually a
-point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
+is represented as a vector in the $2^{n}$-dimen\-sional Hilbert
+space. If we eliminate all symmetries, an irreducible state is actually
+a point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
 also known as the complex projective space~$\CP{2^{n}-1}$ \cite{Hatcher2001,Bengtsson2007}.
@@
 discrete analogs that preserve a great many of the standard requirements
-of quantum computing. In this model, the state of a discrete $D$-dimensional
-system is a vector in the $D$-dimensional vector space over $\Fpp$
+of quantum computing. In this model, the state of a discrete $D$-dimen\-sional
+system is a vector in the $D$-dimen\-sional vector space over $\Fpp$
 and can be reduced to a point in the discrete complex projective space.
@@
 complex amplitudes into a pair of ordinary real numbers. One also
-typically assumes the existence of a $D$-dimensional Hilbert space
+typically assumes the existence of a $D$-dimen\-sional Hilbert space
 with an orthonormal basis, allowing us to write \textit{pure} states
@@
 
-\subsection{Two-dimensional Hilbert Space\label{subsec:Two-dimensional-Hilbert-Space}}
-
-A state in a two-dimensional Hilbert space, known as a qubit, already
+\subsection{Two-dimen\-sional Hilbert Space\label{subsec:Two-dimensional-Hilbert-Space}}
+
+A state in a two-dimen\-sional Hilbert space, known as a qubit, already
 provides access to a wealth of geometric information and context.
@@
 Although $\Sphere{3}$ cannot be directly embedded in $\R^{3}$, three-sphere~$\Sphere{3}$
-can be regarded as attaching two three-dimensional balls on two sides
-of two-sphere~$\Sphere{2}$. In this way, each circle in $\Sphere{3}$
-can be represented as a circle in the three-dimensional ball as shown
-in (b). Moreover, points in (a) are color-coded corresponding to circles
-in (b), e.g., one pole contains the red elliptical circle that would
-become an infinite-radius circle by a slightly different way to represent
-$\Sphere{3}$ in $\R^{3}$, and the opposite pole corresponds to the
-large perfectly round red circle at the equator.}
+can be regarded as attaching two three-dimen\-sional balls on two
+sides of two-sphere~$\Sphere{2}$. In this way, each circle in $\Sphere{3}$
+can be represented as a circle in the three-dimen\-sional ball as
+shown in (b). Moreover, points in (a) are color-coded corresponding
+to circles in (b), e.g., one pole contains the red elliptical circle
+that would become an infinite-radius circle by a slightly different
+way to represent $\Sphere{3}$ in $\R^{3}$, and the opposite pole
+corresponds to the large perfectly round red circle at the equator.}
 \end{figure}
@@
 \end{eqnarray}
-By denoting the three-dimensional vector~$\left(X,Y,Z\right)$ as
-$\Hat{a}$, Eq.~(\ref{A5.eq}) implies these transformed coordinates
+By denoting the three-dimen\-sional vector~$\left(X,Y,Z\right)$
+as $\Hat{a}$, Eq.~(\ref{A5.eq}) implies these transformed coordinates
 obeying 
@@
 
-\subsection{$D$-dimensional Hilbert Space}
-
-The irreducible states in a $D$-dimensional Hilbert space are encoded
-in a similar family of geometric structures known technically as the
-complex projective space $\CP{D-1}$. We obtain these structures starting
-with the $D$ initially unnormalized complex coefficients of the $D$-dimensional
-basis $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$. We then follow
-the analog of the two-dimensional procedure: conservation of probability
-requires that the norm of the vector $\VVec{\alpha}$ be normalized
-to unity: 
+\subsection{$D$-dimen\-sional Hilbert Space}
+
+The irreducible states in a $D$-dimen\-sional Hilbert space are
+encoded in a similar family of geometric structures known technically
+as the complex projective space $\CP{D-1}$. We obtain these structures
+starting with the $D$ initially unnormalized complex coefficients
+of the $D$-dimen\-sional basis $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$.
+We then follow the analog of the two-dimen\-sional procedure: conservation
+of probability requires that the norm of the vector $\VVec{\alpha}$
+be normalized to unity: 
 \begin{equation}
@@
 \end{equation}
-describes the locus of a $2D$-dimensional real unit vector in $\mathReal^{2D}$,
-which is by definition $\Sphere{2D-1}$, the $(2D-1)$-sphere.
+describes the locus of a $2D$-dimen\-sional real unit vector in
+$\mathReal^{2D}$, which is by definition $\Sphere{2D-1}$, the $(2D-1)$-sphere.
 
@@
 inducing an $\Sphere{1}$ symmetry action, and identifying $\Sphere{2D-1}$
-as an $\Sphere{1}$ bundle, whose base space is the $(D-1)$-complex-dimensional
+as an $\Sphere{1}$ bundle, whose base space is the $(D-1)$-complex-dimen\-sional
 projective space $\CP{D-1}$. There are thus $2D-2$ irreducible real
 degrees of freedom ($D-1$ complex degrees of freedom) for a quantum
-state with a $D$-dimensional basis, $\set{\ket{i}}{i=0,\ldots,D-1}$.
-
-In summary, the full space of a $D$-dimensional quantum state, including
-its overall phase defining its relationship to other quantum states,
-is the topological space $\Sphere{2D-1}$. For an isolated system,
-the overall phase is not measurable, and eliminating the phase dependence
-corresponds to identifying $\Sphere{2D-1}$ as a circle bundle over
-the base space $\CP{D-1}$, and therefore $\CP{D-1}$ defines the
-$2D-2$ intrinsic, irreducible, degrees of freedom of the isolated
-$D$-dimensional state's dynamics. In mathematical notation, this
-would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$.
+state with a $D$-dimen\-sional basis, $\set{\ket{i}}{i=0,\ldots,D-1}$.
+
+In summary, the full space of a $D$-dimen\-sional quantum state,
+including its overall phase defining its relationship to other quantum
+states, is the topological space $\Sphere{2D-1}$. For an isolated
+system, the overall phase is not measurable, and eliminating the phase
+dependence corresponds to identifying $\Sphere{2D-1}$ as a circle
+bundle over the base space $\CP{D-1}$, and therefore $\CP{D-1}$
+defines the $2D-2$ intrinsic, irreducible, degrees of freedom of
+the isolated $D$-dimen\-sional state's dynamics. In mathematical
+notation, this would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$.
 \begin{comment}
@@
 Note that only for $D=2$ is this actually a sphere-like geometry
-due to an accident of low-dimensional topology.
+due to an accident of low-dimen\-sional topology.
 
@@
 
-For a two-dimensional system, we could easily solve the problem of
-reducing the full unit-norm space to its irreducible components $\Hat{a}=\left(X,Y,Z\right)$
-characterizing the Bloch sphere. We have just argued that essentially
-the same process is possible for $D$-dimensional system: in the abstract
-argument, we simply identify the family of coefficients $\left\{ \alpha_{i}\right\} $
-as being the same if they differ only by an overall phase $\rme^{\rmi\theta}$.
+For a two-dimen\-sional system, we could easily solve the problem
+of reducing the full unit-norm space to its irreducible components
+$\Hat{a}=\left(X,Y,Z\right)$ characterizing the Bloch sphere. We
+have just argued that essentially the same process is possible for
+$D$-dimen\-sional system: in the abstract argument, we simply identify
+the family of coefficients $\left\{ \alpha_{i}\right\} $ as being
+the same if they differ only by an overall phase $\rme^{\rmi\theta}$.
 However in practice, this is not a construction that is easy to realize
 in a practical computation. We now outline an explicit algorithm for
-accomplishing the reduction to the irreducible $D$-dimensional state
-space $\CP{D-1}$; this construction will turn out to be useful for
-the validation of our discrete results to follow below.
+accomplishing the reduction to the irreducible $D$-dimen\-sional
+state space $\CP{D-1}$; this construction will turn out to be useful
+for the validation of our discrete results to follow below.
 
 Given a normalized pure state $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$,
-a natural quantity characterizing a $D$-dimensional system is its
-\textit{density matrix}, $\rho=\op{\Psi}{\Psi}$, or 
+a natural quantity characterizing a $D$-dimen\-sional system is
+its \textit{density matrix}, $\rho=\op{\Psi}{\Psi}$, or 
 \begin{equation}
@@
 coordinate system for projective geometry to remove the overall phase
-ambiguity $\rme^{\rmi\theta}$ from the $D$-dimensional states. If
-we take a particular weighting of the elements of the density matrix~$\rho$,
+ambiguity $\rme^{\rmi\theta}$ from the $D$-dimen\-sional states.
+If we take a particular weighting of the elements of the density matrix~$\rho$,
 we can construct a \textit{unit vector} of real dimension $D^{2}$
@@
 \]
-This construction gives an explicit embedding of the $\left(D-1\right)$-dimensional
-complex, or $\left(2D-2\right)$-dimensional real, object in a real
-space of dimension $D^{2}$. However, this is somewhat subtle because
-the vector is of unit length, so technically the embedding space is
-a sphere of dimension $D^{2}-1$ embedded in $\R^{D^{2}}$. For example,
-the two-dimensional irreducible states could be represented in a four-dimensional
-embedding, but the magnitude of every coordinate would be one. Furthermore,
-the object embedded in the resulting $\Sphere{3}$ is indeed $\Sphere{2}$
-because we can fix one complex coordinate to be unity, and let one
-vary, giving a total of two irreducible dimensions. In fact, one must
-choose \textit{two} coordinate patches, one covering one pole of $\Sphere{2}$
-with coordinates $\alpha_{0}=1+\rmi0$ and $\alpha_{1}=x_{1}+\rmi y_{1}$,
-and the other patch covering the other pole of $\Sphere{2}$ with
-coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=1+\rmi0$.
+This construction gives an explicit embedding of the $\left(D-1\right)$-dimen\-sional
+complex, or $\left(2D-2\right)$-dimen\-sional real, object in a
+real space of dimension $D^{2}$. However, this is somewhat subtle
+because the vector is of unit length, so technically the embedding
+space is a sphere of dimension $D^{2}-1$ embedded in $\R^{D^{2}}$.
+For example, the two-dimen\-sional irreducible states could be represented
+in a four-dimen\-sional embedding, but the magnitude of every coordinate
+would be one. Furthermore, the object embedded in the resulting $\Sphere{3}$
+is indeed $\Sphere{2}$ because we can fix one complex coordinate
+to be unity, and let one vary, giving a total of two irreducible dimensions.
+In fact, one must choose \textit{two} coordinate patches, one covering
+one pole of $\Sphere{2}$ with coordinates $\alpha_{0}=1+\rmi0$ and
+$\alpha_{1}=x_{1}+\rmi y_{1}$, and the other patch covering the other
+pole of $\Sphere{2}$ with coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$
+and $\alpha_{1}=1+\rmi0$. %
 \begin{comment}
@@
 
-We finally see that the irreducible $D$-dimensional state space $\CP{D-1}$
-is described by $D$ projectively equivalent coordinates, one of which
-can always be scaled out to leave $(D-1)$ actual (complex) degrees
-of freedom. We must choose, in turn, $D$ different local sets of
-complex variables defined by taking the value $\alpha_{k}=1$, with
-$k=0,\ldots,D-1$, and allowing the remaining $D-1$ complex (or $2D-2$
-real) variables to run free. No single set of coordinates will work,
-since the submanifold including $\alpha_{k}=0$ is undefined and another
-coordinate system must be chosen to cover that coordinate patch. This
-is a standard feature of the topology of non-trivial manifolds such
-as $\CP{D-1}$ (see any textbook on geometry~\cite{Berger_1988}).
+We finally see that the irreducible $D$-dimen\-sional state space
+$\CP{D-1}$ is described by $D$ projectively equivalent coordinates,
+one of which can always be scaled out to leave $(D-1)$ actual (complex)
+degrees of freedom. We must choose, in turn, $D$ different local
+sets of complex variables defined by taking the value $\alpha_{k}=1$,
+with $k=0,\ldots,D-1$, and allowing the remaining $D-1$ complex
+(or $2D-2$ real) variables to run free. No single set of coordinates
+will work, since the submanifold including $\alpha_{k}=0$ is undefined
+and another coordinate system must be chosen to cover that coordinate
+patch. This is a standard feature of the topology of non-trivial manifolds
+such as $\CP{D-1}$ (see any textbook on geometry~\cite{Berger_1988}).
 
@@
 us prepare a beam of one kind of spin~$1$ particles whose state
-can be characterized by a vector in three-dimensional Hilbert space
+can be characterized by a vector in three-dimen\-sional Hilbert space
 with basis vectors $\ket{0}$, $\ket{1}$, and $\ket{2}$. In principle,
@@
 a unique mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such
-that $\mu\left(P\right)=\Tr\left(\rho P\right)$ for any $D$-dimensional
+that $\mu\left(P\right)=\Tr\left(\rho P\right)$ for any $D$-dimen\-sional
 projector~$P$, where $\ket{\Phi_{j}}\in\mathcal{H}$ are normalized,
@@
 
-As an example, consider a three-dimensional Hilbert space with orthonormal
-basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $ and the observable
-$\mathbf{O}_{0}$ defined in Eq.~(\ref{eq:observable}). Two fragments
-of valid probability measures~$\mu_{1}$ and $\mu_{2}$ that can
-be associated with this space are defined in Table~\ref{tab:quantum-probability-measure}.
+As an example, consider a three-dimen\-sional Hilbert space with
+orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $ and
+the observable $\mathbf{O}_{0}$ defined in Eq.~(\ref{eq:observable}).
+Two fragments of valid probability measures~$\mu_{1}$ and $\mu_{2}$
+that can be associated with this space are defined in Table~\ref{tab:quantum-probability-measure}.
 By the Born rule, the first probability measure corresponds to the
@@
 the measurement outcomes in another one. To discuss entanglement,
-we consider a $D$-dimensional quantum system composed of $n$-qubit
+we consider a $D$-dimen\-sional quantum system composed of $n$-qubit
 subsystems, i.e., $D=2^{n}$. A pure state of the total system $\ket{\Psi}$
@@
 
-\section{Irreducible Discrete $D$-dimensional States\label{DQCnqubitBloch.sec}}
+\section{Irreducible Discrete $D$-dimen\-sional States\label{DQCnqubitBloch.sec}}
 
@@
 \caption{\label{bloch.fig}Schematically normalized plots of the elements of
-the discrete Bloch sphere, the irreducible single-qubit (two-dimensional)
+the discrete Bloch sphere, the irreducible single-qubit (two-dimen\-sional)
 state vectors with unit norm over the field $\Fpp$. We show the results
@@
 
-This process of describing the discrete $D$-dimensional irreducible
+This process of describing the discrete $D$-dimen\-sional irreducible
 states can again be understood geometrically by following the discrete
@@
 \textit{discrete Hopf fibration circle} living above each \textit{irreducible}
-point of the $D$-dimensional state description. These $p+1$ points
+point of the $D$-dimen\-sional state description. These $p+1$ points
 are interpretable as the $p$ finite points plus the single point
@@
 \begin{prop}\label{appU.sec}The number of unit-norm states described
-by a $D$-dimensional vector $(\alpha_{0},\ldots,\alpha_{D-1})$ with
-coefficients $\alpha_{i}\in\Fpp$ is $p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)$.\end{prop}
+by a $D$-dimen\-sional vector $(\alpha_{0},\ldots,\alpha_{D-1})$
+with coefficients $\alpha_{i}\in\Fpp$ is $p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)$.\end{prop}
 
@@
 Since there are $p^{2}$ elements $\alpha\in\Fpp$, we must have $\left(p^{2}\right)^{D}=p^{2D}$
-possible values of a $D$-dimensional vector $(\alpha_{0},\ldots,\alpha_{D-1})$.
+possible values of a $D$-dimen\-sional vector $(\alpha_{0},\ldots,\alpha_{D-1})$.
 There are $p^{2}-1$ non-zero values of $\alpha\in\Fpp$, and we showed
@@
 
-Finally, we repeat the last step of the $D$-dimensional continuous
-Hopf fibration process for discrete $D$-dimensional states, eliminating
+Finally, we repeat the last step of the $D$-dimen\-sional continuous
+Hopf fibration process for discrete $D$-dimen\-sional states, eliminating
 the discrete set of $p+1$ equivalent points that map to the same
@@
 \end{equation}
-as the total count of unique irreducible states in a discrete $D$-dimensional
+as the total count of unique irreducible states in a discrete $D$-dimen\-sional
 configuration. The resulting object is precisely the discrete version
@@
 
-To discuss entanglement, we consider a $D$-dimensional quantum system
-composed of $n$-qubit subsystems, i.e., $D=2^{n}$ as usual. Without
-regard to uniqueness, an $n$-qubit state with discrete complex coefficients
-in $\Fpp$ will have the total possible space of coefficients with
-dimension $p^{2\times2^{n}}$ (including the null state). Imposing
+To discuss entanglement, we consider a $D$-dimen\-sional quantum
+system composed of $n$-qubit subsystems, i.e., $D=2^{n}$ as usual.
+Without regard to uniqueness, an $n$-qubit state with discrete complex
+coefficients in $\Fpp$ will have the total possible space of coefficients
+with dimension $p^{2\times2^{n}}$ (including the null state). Imposing
 the condition of a length-one norm in $\Fp$, this number is reduced
@@
 
-Given a $D$-dimensional vector space over $\ff{p^{2}}$ where~$p$
+Given a $D$-dimen\-sional vector space over $\ff{p^{2}}$ where~$p$
 is one of the primes above, it is possible to define a \emph{region}
@@
 forward in Section~\ref{discretequantumtheoryIIa} concerns measurement.
-To recap, within the theory, states are $D$-dimensional vectors with
-complex discrete-valued amplitudes drawn from a totally-ordered range,
-$F^{D}(k)$, in the underlying finite field. These states possess,
+To recap, within the theory, states are $D$-dimen\-sional vectors
+with complex discrete-valued amplitudes drawn from a totally-ordered
+range, $F^{D}(k)$, in the underlying finite field. These states possess,
 by construction, having field norms in the non-negative integers,
@@
 
-Given a $D$-dimensional Hilbert space in conventional quantum theory,
-although we can measure the probability for every eigenprojector of
-an observable as discussed in Sec.~\ref{sec:fuzzy}, our previous
+Given a $D$-dimen\-sional Hilbert space in conventional quantum
+theory, although we can measure the probability for every eigenprojector
+of an observable as discussed in Sec.~\ref{sec:fuzzy}, our previous
 quantum circuits in Figures~\ref{fig:alg}, \ref{fig:Quantum-Circuit-Deutsch},
@@
 that $f\left(\overline{x}\right)=1$ if and only if $\ket{\overline{x}}=\ket{0}\!\ket{0}\!\ket{0}$.
-The initial information-less $8$-dimensional state vector evolves
+The initial information-less $8$-dimen\-sional state vector evolves
 under the application of $VR$ as follows: %
@@
 0 & \textrm{if }P=\mathbb{0}\,;\\
-\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimensional projector;}\\
-\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimensional projector;}\\
+\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimen\-sional projector;}\\
+\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimen\-sional projector;}\\
 1 & \textrm{if }P=\mathbb{1}\,.
@@
 of $\mathbf{O}$. Since $\mathbf{O}$ can be expressed as the sum
-of one-dimensional projectors 
+of one-dimen\-sional projectors 
 \begin{equation}
@@
 $\mathbb{0}$ & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline
-All one-dimensional projectors & $\left[0,0\right]$  & $\left[0,\tfrac{1}{4}\right]$  & $\left[0,\tfrac{1}{3}\right]$  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
-All two-dimensional projectors & $\left[1,1\right]$  & $\left[\tfrac{3}{4},1\right]$  & $\left[\tfrac{2}{3},1\right]$  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$  & $\left[\tfrac{1}{2},1\right]$\tabularnewline
+All one-dimen\-sional projectors & $\left[0,0\right]$  & $\left[0,\tfrac{1}{4}\right]$  & $\left[0,\tfrac{1}{3}\right]$  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
+All two-dimen\-sional projectors & $\left[1,1\right]$  & $\left[\tfrac{3}{4},1\right]$  & $\left[\tfrac{2}{3},1\right]$  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$  & $\left[\tfrac{1}{2},1\right]$\tabularnewline
 $\mathbb{1}$ & $\necess$  & $\necess$  & $\necess$  & $\necess$  & $\necess$\tabularnewline
@@
 hidden variable model for $D=2$ (e.g., as proposed by Bell or Kochen-Specker~\cite{BELL_1966,kochenspecker1967}).
-Such a two-dimensional model always assigns definite values to all
-observables and hence assigns a \emph{determinate} probability (0
-or 1) to each event. This probability measure directly induces a 0-deterministic
-QIVPM by changing 0 to $\imposs$ and 1 to $\necess$. It follows
-that every 0-deterministic QIVPM is $\delta$-deterministic.
+Such a two-dimen\-sional model always assigns definite values to
+all observables and hence assigns a \emph{determinate} probability
+(0 or 1) to each event. This probability measure directly induces
+a 0-deterministic QIVPM by changing 0 to $\imposs$ and 1 to $\necess$.
+It follows that every 0-deterministic QIVPM is $\delta$-deterministic.
 
@@
 To see this idea in the context of a quantum experiment, consider
-a three-dimensional Hilbert space with one-dimensional projectors~$P_{\rho}$,
-two-dimensional projectors $P_{\rho}+P_{\sigma}$, and an experiment
+a three-dimen\-sional Hilbert space with one-dimen\-sional projectors~$P_{\rho}$,
+two-dimen\-sional projectors $P_{\rho}+P_{\sigma}$, and an experiment
 that is repeated $12$ times. By the Kochen-Specker theorem, it is
@@
 Now consider what happens if $\frac{1}{4}$ of the data for \emph{every}
-one-dimensional projector is uncertain. A potential account of this
-degradation is to assign to each event $P$ the entire range of possibilities
-$\bar{\mu}_{1}(P)$ as defined in Table~\ref{tab:probability-measures}.
+one-dimen\-sional projector is uncertain. A potential account of
+this degradation is to assign to each event $P$ the entire range
+of possibilities $\bar{\mu}_{1}(P)$ as defined in Table~\ref{tab:probability-measures}.
 This measure is not a valid QIVPM because it does not satisfy the
-convexity condition: for any two orthogonal one-dimensional events
+convexity condition: for any two orthogonal one-dimen\-sional events
 $P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$,
@@
 have a \emph{common point}. Hence, by assuming that the uncertain
-data for one-dimensional projectors always support the associated
-event, while those for two-dimensional projectors always refute the
-event, we can find the probability measure~$\bar{\mu}_{2}'$ that
-can be verified as a valid QIVPM and is consistent with the experimental
+data for one-dimen\-sional projectors always support the associated
+event, while those for two-dimen\-sional projectors always refute
+the event, we can find the probability measure~$\bar{\mu}_{2}'$
+that can be verified as a valid QIVPM and is consistent with the experimental
 data.
@@
 convexity condition for $\bar{\mu}$. Given a pair of commuting projectors
-$P_{0}$ and $P_{1}$ on a three-dimensional Hilbert space, they can
-be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+$P_{0}$ and $P_{1}$ on a three-dimen\-sional Hilbert space, they
+can be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
 Consider the function $\varphi\colon2^{\Omega}\rightarrow\events$
@@
 \begin{proof}Since any projectors can be expressed as the sum of
-orthogonal one-dimensional projectors, Eq.~(\ref{amr-3}) implies
+orthogonal one-dimen\-sional projectors, Eq.~(\ref{amr-3}) implies
 Eq.~(\ref{amr-1}) by induction, and this lemma holds because of
@@
 we have $\muB_{\rho'}\left(\proj{\psi}\right)\in f\left(\muB_{\rho}\left(\proj{\psi}\right)\right)$
-for any one-dimensional projector $P=\proj{\psi}$. Since the maximum
+for any one-dimen\-sional projector $P=\proj{\psi}$. Since the maximum
 length of the intervals in $\mathscr{I}$ is $\left\Vert \mathscr{I}\right\Vert $,
@@
 When people proved the original Gleason theorem, people usually exploited
-the geometrical structure of real 3-dimensional Hilbert space \cite{gleason1957,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+the geometrical structure of real 3-dimen\-sional Hilbert space \cite{gleason1957,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
 Since our finite-precision extension of the Gleason theorem only applies
@@
 To better understand this question, consider the $D=3$ situation,
-where any two-dimensional projectors can be expressed as the complement
-of a one-dimensional projector, and by Eq.~(\ref{eq:QIVPM-complement})
+where any two-dimen\-sional projectors can be expressed as the complement
+of a one-dimen\-sional projector, and by Eq.~(\ref{eq:QIVPM-complement})
 so does their interval-valued probabilities, i.e., 
@@
 \end{equation}
-Hence, a QIVPM is completely determined by its values on the one-dimensional
+Hence, a QIVPM is completely determined by its values on the one-dimen\-sional
 projectors which are one-to-one corresponding to the irreducible states,

### 2019-04-22 dissertation.tex
dissertation.lyx Fixing Overfull by adding breaking points...

@@
 to get each post-experimental state. In the language of our abstraction,
-the set of outcomes is $\Omega_{0}=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+the set of outcomes is $\Omega_{0}=\{\ket{0},\ket{1},\ket{2}\}$.
 All possible events are $\emptyset$, $\left\{ \ket{0}\right\} $,
@@
 As an example, consider a three-dimen\-sional Hilbert space with
-orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $ and
-the observable $\mathbf{O}_{0}$ defined in Eq.~(\ref{eq:observable}).
-Two fragments of valid probability measures~$\mu_{1}$ and $\mu_{2}$
-that can be associated with this space are defined in Table~\ref{tab:quantum-probability-measure}.
+orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and the observable
+$\mathbf{O}_{0}$ defined in Eq.~(\ref{eq:observable}). Two fragments
+of valid probability measures~$\mu_{1}$ and $\mu_{2}$ that can
+be associated with this space are defined in Table~\ref{tab:quantum-probability-measure}.
 By the Born rule, the first probability measure corresponds to the
@@
 \begin{proof}The most important part of the proof is to verify the
-convexity condition for $\barmuD$. By Lemma~\ref{lemma:verify-convexity},
+convexity condition for $\barmuD$. By Lemma\nolinebreak[3] \ref{lemma:verify-convexity},
 it is sufficient to verify the following equation for orthogonal projectors
@@
 $P_{0}$ and $P_{1}$ on a three-dimen\-sional Hilbert space, they
-can be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
+can be diagonalized by a common orthonormal basis $\Omega=\{\ket{0},\ket{1},\ket{2}\}$.
 Consider the function $\varphi\colon2^{\Omega}\rightarrow\events$
@@
 events. Assume a Hilbert space of dimension $D=3$ with orthonormal
-basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$,
+basis $\{\ket{0},\ket{1},\ket{2}\}$, let $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$,
 $\ket{\ps'}=\frac{\ket{0}+\ket{2}}{\sqrt{2}}$, and assign 

### 2019-04-26 dissertation.tex
dissertation.lyx Adding protected space between URL and period...

@@
 \begin{itemize}
-\item The latest PDF version of this thesis is in GitHub: \url{https://git.io/fxbuG}.
+\item The latest PDF version of this thesis is in GitHub: \url{https://git.io/fxbuG}~.
 \item Its source code is typeset using \LyX{} \cite{LyX} in \url{https://git.io/fxbuE}
-and the exported \LaTeX{} file is in \url{https://git.io/fhZBW}.
+and the exported \LaTeX{} file is in \url{https://git.io/fhZBW}~.
 \item Any comments can be left in the Issue part of the GitHub repository:
-\url{https://git.io/fxbug}.
+\url{https://git.io/fxbug}~.
 \end{itemize}
@@
 where the system can find.
-\item In the local directory of this thesis, run \code{xelatex dissertation.tex}.
-\item Run \code{biber dissertation}.
+\item In the local directory of this thesis, run \code{xelatex dissertation.tex}~.
+\item Run \code{biber dissertation}~.
 \item Run \code{xelatex dissertation.tex} several times until all the references
@@
 0 & \textrm{if }P=\mathbb{0}\,;\\
-\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimen\-sional projector;}\\
-\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimen\-sional projector;}\\
+\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimen­sional projector;}\\
+\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimen­sional projector;}\\
 1 & \textrm{if }P=\mathbb{1}\,.

### 2019-04-27 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

@@
 0 & \textrm{if }P=\mathbb{0}\,;\\
-\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimen­sional projector;}\\
-\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimen­sional projector;}\\
+\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimensional projector;}\\
+\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimensional projector;}\\
 1 & \textrm{if }P=\mathbb{1}\,.
@@
 finite fields} and \emph{quantum interval-valued probability measures
-(QIVPMs)}. Examining the computational and physical consequences of
+(QIVPMs)}. Examining the physical and computational consequences of
 such frameworks can yield new insights into not only the subtle properties
@@
 (Secs.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
-which lacks a notion of probability and supports unnaturally efficient
-deterministic quantum algorithms. A still more plausible discrete
-theory with cardinal probabilities was proposed (Secs.~\ref{sec:Discrete-Quantum-Theory-(II)}
+but both of them lack a notion of probability and support unnaturally
+efficient deterministic quantum algorithms. A still more plausible
+discrete theory with cardinal probabilities was proposed (Secs.~\ref{sec:Discrete-Quantum-Theory-(II)}
 and~\ref{discretequantumcomputingII}), where conventional quantum
@@
 in Fig.~\ref{fig:commutative-diagrams}, QIVPMs inherit definitions
-and properties from the both sides. While the expectation values of
-QIVPMs can be pulled back to the classical cases and consistent with
-those of quantum probability measures in the infinitely precise limit
-(Sec.~\ref{sec:Interval-Uncertainty}), foundational concepts in
-quantum mechanics, such as the Kochen-Specker and Gleason theorems,
+and properties from the both frameworks. While the expectation values
+of QIVPMs can be pulled back to the classical ones and consistent
+with those of quantum probability measures in the infinitely precise
+limit (Sec.~\ref{sec:Interval-Uncertainty}), foundational concepts
+in quantum mechanics, such as the Kochen-Specker and Gleason theorems,
 extended to QIVPMs in subtle ways. By carefully specifying experimental
@@
 In the following further discussion, we will briefly explain why we
-only recovered Gleason's on a class of QIVPMs, the possibility to
-further build a computational model over QIVPMs, and the possibility
-combining both approaches to consider quantum interval-valued probability
-measures over finite fields.
+only recovered Gleason's theorem on a class of QIVPMs, the possibility
+to further build a computational model over QIVPMs, and the possibility
+combining both approaches to consider QIVPMs over finite fields.
 

### 2019-04-29 dissertation.tex
dissertation.lyx Acknowledgments, Preface, "4.7 Quantum Probability Measures over Finite Fields", and "Chapter 6 Conclusion and Further Discussion" Fix small things...

@@
 Abdel~Gawwad, and Cathryn ``Cathy'' Creger-Chambers, \textbahasai{Sary
-Silvhiany}, Shaozhuan Li (李绍颛), Chenwei Zhang (张晨薇), Shu-Nan ``Nancy''
+Silvhiany}, Shaozhuan Li (李绍颛), Chenwei Zhang (张晨薇), Shu-Han ``Nancy''
 Chang (張舒涵), and Ching-Chi ``Victoria'' Chang (張靖琪), \ldots , etc.
@@
 \item My AT\&T family plan members, especially Meng-Wei Chen (陳孟瑋),
-Yao-yu Chih (池耀宇), and Xinyi ``Diana'' Gong (龚欣怡), \ldots , etc.
-
-\item Other friends, including Shu-Ling Wang (王舒齡), Wan-Ling ``Wynnie''
+Yao-Yu Chih (池耀宇), and Xinyi ``Diana'' Gong (龚欣怡), \ldots , etc.
+
+\item Other friends, including Shu-Ling Wang (王舒齡), Wanling ``Wynnie''
 Chang (張婉鈴), Yu-Jung Lin (林宇容), Winnie Lou (何慧芳), Yi-Rong Yang (楊宜蓉),
 Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
-Davis Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding (丁颖), Hung-Chun
-Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超), Prof.~Jyh-Chyi
-Gong (龔治齊), 江靜宜, and the office of International Services\ldots ,
+Peng Chou ``Davis'' Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding
+(丁颖), Hung-Chun Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超),
+Prof.~Jyh-Chyi Gong (龔治齊), 江靜宜, and the office of International Services\ldots ,
 etc.
@@
 \end{itemize}
-Following explains how to compile the PDF from the \LaTeX{} source:
+The following explains how to compile the PDF file from the \LaTeX{}
+source:
 \begin{enumerate}
@@
 \end{equation}
-However, the irreducible pure states in $\ff{7^{2}}^{3}$ is not unique.
-Indeed, there are 
+In contrast, the irreducible pure states in $\ff{7^{2}}^{3}$ is not
+unique. As we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}),
+there are 
 \begin{equation}
@@
 \end{equation}
-irreducible pure states in $\ff{7^{2}}^{3}$ as we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}).
-Since we don't have enough QPMFF to correspond even pure states, there
-is no discrete Born rule in this case. In general, we conjecture that
-QPMFF is always unique for $D\ge3$ except $D=p=3$.
+irreducible pure states in $\ff{7^{2}}^{3}$. Since we don't have
+enough QPMFF to correspond even pure states, there is no discrete
+Born rule in this case. In general, we conjecture that QPMFF is always
+unique for $D\ge3$ except $D=p=3$.
 
@@
 (QIVPMs)}. Examining the physical and computational consequences of
-such frameworks can yield new insights into not only the subtle properties
-of conventional quantum theory but also the power and capacity of
-quantum computing.
+such frameworks could yield new insights into not only the subtle
+properties of conventional quantum theory but also the power and capacity
+of quantum computing.
 
@@
 and properties from the both frameworks. While the expectation values
-of QIVPMs can be pulled back to the classical ones and consistent
-with those of quantum probability measures in the infinitely precise
-limit (Sec.~\ref{sec:Interval-Uncertainty}), foundational concepts
-in quantum mechanics, such as the Kochen-Specker and Gleason theorems,
-extended to QIVPMs in subtle ways. By carefully specifying experimental
-uncertainties, we established rigorous bounds on the validity of the
-Kochen-Specker theorem (Sec.~\ref{sec:Kochen-Specker}). While there
-is a QIVPM not consistent with Gleason's unique state~$\rho$ on
-all projectors, we constructed a class of QIVPMs for which the original
-Gleason theorem could be recovered asymptotically (Sec.~\ref{sec:Gleason}).
+with respect to QIVPMs can be pulled back to the classical ones and
+consistent with those with respect to quantum probability measures
+in the infinitely precise limit (Sec.~\ref{sec:Interval-Uncertainty}),
+foundational concepts in quantum mechanics, such as the Kochen-Specker
+and Gleason theorems, extended to QIVPMs in subtle ways. By carefully
+specifying experimental uncertainties, we established rigorous bounds
+on the validity of the Kochen-Specker theorem (Sec.~\ref{sec:Kochen-Specker}).
+While there is a QIVPM not consistent with Gleason's unique state~$\rho$
+on all projectors, we constructed a class of QIVPMs for which the
+original Gleason theorem could be recovered asymptotically (Sec.~\ref{sec:Gleason}).
 
@@
 space $\CP{2}$ as we discussed in Sec.~\ref{subsec:Explicit-generalization-of}.
-Therefore, to study a QIVPM~$\bar{\mu}$, we can just study a pair
-of functions $\frameL\colon\CP{2}\rightarrow\left[0,1\right]$ and
-$\frameR\colon\CP{2}\rightarrow\left[0,1\right]$ defined by $[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)]=\bar{\mu}\left(\proj{\psi}\right)$
+Therefore, to study a QIVPM~$\bar{\mu}$, we just need to study a
+pair of functions $\frameL\colon\CP{2}\rightarrow\left[0,1\right]$
+and $\frameR\colon\CP{2}\rightarrow\left[0,1\right]$ defined by $[\frameL\left(\ket{\psi}\right),\frameR\left(\ket{\psi}\right)]=\bar{\mu}\left(\proj{\psi}\right)$
 for any irreducible state $\ket{\psi}\in\CP{2}$. According to Lemma~\ref{thm:convex-3-1},

### 2019-04-29 dissertation.tex
dissertation.lyx Acknowledgments and "6.1 Summary" Fix small things...

@@
 Hsien-Ching Kao (高憲慶), Wei Cheng (鄭維), Chin-Yi Lin (林金毅), Chun-Ting
-Chen (陳俊廷), and Prof.~Chenying Huang (黃貞穎), \ldots , etc.
+Chen (陳俊廷), and Prof.~Chen-Ying Huang (黃貞穎), \ldots , etc.
 
@@
 The theories over finite fields started with unrestricted discrete
-fields (Chapter~\ref{chap:Unrestricted-Finite-Fields}), then advanced
-to a more reasonable framework based on complexifiable discrete fields
-(Secs.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
+fields (Chapter~\ref{chap:Unrestricted-Finite-Fields}) and then
+advanced to a more reasonable framework based on complexifiable discrete
+fields (Secs.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
 but both of them lack a notion of probability and support unnaturally

### 2019-05-12 dissertation.tex
dissertation.lyx Acknowledgments and CV updated; Copyright Page removed...

@@
 %data for Copyright Page
-\copyrightpage
+%\copyrightpage
 
@@
 in general, and I want to thank the following people which haven't
-been listed previously:\footnote{For some of them, I only provide their Chinese names for two reason.
+been listed previously:\footnote{For some of them, I only provide their Chinese names for two reasons.
 First, I might only know their Chinese names. Second, there are many

### 2019-05-15 dissertation.tex
dissertation.lyx Updating graduating month... CV_thesis.pdf Updating graduating month...
dissertation.lyx Revert any change of abstract and acceptance page back to the signed version.

@@
 \usepackage{datetime2-calc}
-\monthGranted{\DTMmonthname{\month}}
+\monthGranted{June}%\DTMmonthname{\month}}
 \yearGranted{\the\year}
@@
 %data for Acceptance Page
-\committeeMember{Amr A. Sabry, \PhD} \committeeMember{Dylan
-Paul Thurston, \PhD} \committeeMember{Gerardo Ortiz, \PhD} \committeeMember{Andrew
-J. Hanson, \PhD} \committeeMember{Shouhong Wang, \PhD} \defensedate{November
+\committeeMember{Amr A. Sabry, PhD} \committeeMember{Dylan Paul
+Thurston, PhD} \committeeMember{Gerardo Ortiz, PhD} \committeeMember{Andrew
+J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{November
 29, 2018} \acceptancepage
@@
 precision to computable contexts that do not require incomputable
-real numbers. Our goal is to build more philosophically consistent
+real numbers. Our goal is to build a more philosophically consistent
 models by investigating discrete quantum computing using finite number
@@
 generalization of both classical IVPMs and conventional quantum probability
-measures but also allows us to establish bounds on the validity of
+measures, but also allows us to establish bounds on the validity of
 the Kochen-Specker and Gleason theorems in realistic experimental

### 2019-05-23 dissertation.tex
- We do not recommend using alternating page margins as this can cause problems if you opt to print the final version. We recommend changing your margins to one inch on all four sides. This margin space is satisfactory for ProQuest publications. You are not required to make this change but we highly recommend it.
- On the title page, list your name as "Yu-Tsung Tai" (rather than "Tai, Yu-Tsung"

- On the abstract page, list your name as "Yu-Tsung Tai" (rather than "Tai, Yu-Tsung"
- Your table of contents is currently in a font with all capital letters. Please change this to a font with the sta

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[11pt,twoside]{iuphd}
+\documentclass[11pt]{iuphd}
 \usepackage{amsmath}
@@
 \title{Discrete Quantum Theories and Computing}
-\author{Tai, Yu-Tsung}
+\author{Yu-Tsung Tai}
 
@@
 
-\subsection{Explicit generalization of the Hopf fibration construction\label{subsec:Explicit-generalization-of}}
+\subsection{Explicit Generalization of the Hopf Fibration Construction\label{subsec:Explicit-generalization-of}}
 
@@
 
-\section{The geometry of entanglement\label{sec:The-geometry-of}}
+\section{The Geometry of Entanglement\label{sec:The-geometry-of}}
 
@@
 
-\subsection{Counting states on the discrete Bloch sphere}
+\subsection{Counting States on the Discrete Bloch Sphere}
 
@@
 
-\subsection{Maximal entanglement\label{subsec:Maximal-entanglement}}
+\subsection{Maximal Entanglement\label{subsec:Maximal-entanglement}}
 
@@
 
-\subsection{Discrete Deutsch algorithm\label{subsec:Discrete-Deutsch-algorithm}}
+\subsection{Discrete Deutsch Algorithm\label{subsec:Discrete-Deutsch-algorithm}}
 
@@
 
-\subsection{Classical Choquet integrals and Expectation Values of Observables}
+\subsection{Classical Choquet Integrals and Expectation Values of Observables}
 

### 2019-05-30 dissertation.tex
- All four sides of each page of your submission must have, at a minimum, a one inch margin. The following pages definitely have content extending into one or more margins and need to be corrected but you should check every page to make sure the margin space is correct: v, 36.
- Remove the physically present horizontal line(s) denoting section breaks from the CV. The CV needs to meet the same formatting requirements as the rest of your submission; section break lines are not permitted in dissertations.
- All four sides of each page of your submission must have, at a minimum, a one inch margin.

@@
 \begin{sidewaystable}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{tab:committee}The professors served in all my committees.}
-%% ERT block 1 (before LyX tabular)
+\noindent \centering{}{\small{}\caption{\label{tab:committee}The professors served in all my committees.}
+}%% ERT block 1 (before LyX tabular)
 \renewcommand{\tabular}{\tabularx{\linewidth}}
 \renewcommand{\endtabular}{\endtabularx} 
-\begin{tabular}{M{MATH-M781}M{Co-author}M{(\textarabic{عمرو~صبري})}M{Co-author}M{Thurston}M{Shouhong}M{Lawrence}Y}
+{\small{}}%
+\begin{tabular}{M{\small{}MATH-M781}M{\small{}Co-author}M{\small{}(\textarabic{عمرو~صبري})}M{\small{}Co-author}M{\small{}Thurston}M{\small{}Shouhong}M{\small{}Lawrence}Y}
 \toprule 
-Committee or course & Gerardo Ortiz & Amr\nolinebreak[3] A.
-Sabry\linebreak[3] (\textarabic{عمرو صبري}) & Andrew\nolinebreak[3] J.
-Hanson & Dylan\nolinebreak[3] Paul Thurston & Shouhong Wang\linebreak[3] (汪守宏) & Lawrence\nolinebreak[3] S.\linebreak[2] Moss & Relation with the dissertation\tabularnewline
+{\small{}Committee or course} & {\small{}Gerardo Ortiz} & {\small{}Amr\nolinebreak[3] A. Sabry\linebreak[3] (}\textarabic{{\small{}عمرو
+صبري}}{\small{})} & {\small{}Andrew\nolinebreak[3] J.
+Hanson} & {\small{}Dylan\nolinebreak[3] Paul Thurston} & {\small{}Shouhong Wang\linebreak[3] (}{\small{}汪守宏}{\small{})} & {\small{}Lawrence\nolinebreak[3] S.\linebreak[2] Moss} & {\small{}Relation with the dissertation}\tabularnewline
 \midrule
 \midrule 
- & Co-author & Co-author & Co-author &  &  &  & Most of Chapters~\ref{chap:Conventional-Quantum-Theory}, \ref{chap:Unrestricted-Finite-Fields},
-and~\ref{chap:DQT=000026DQC} is based on~\cite{geometry2013} and~\cite{DQT2014};
-most of Chapter~\ref{chap:QIVPM} is based on~\cite{THOS2018}.\tabularnewline
+ & {\small{}Co-author} & {\small{}Co-author} & {\small{}Co-author} &  &  &  & {\small{}Most of Chapters~\ref{chap:Conventional-Quantum-Theory},
+\ref{chap:Unrestricted-Finite-Fields}, and~\ref{chap:DQT=000026DQC}
+is based on~\cite{geometry2013} and~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM}
+is based on~\cite{THOS2018}.}\tabularnewline
 \midrule 
-Research committee & Co-chair & Co-chair & Member & Co-chair & Member &  & Some questions in the dissertation proposal are answered in Chapter~\ref{chap:QIVPM},
-and some of the remaining ones are explained in Chapter~\ref{chap:Further-Discussion}.\tabularnewline
+{\small{}Research committee} & {\small{}Co-chair} & {\small{}Co-chair} & {\small{}Member} & {\small{}Co-chair} & {\small{}Member} &  & {\small{}Some questions in the dissertation proposal are answered
+in Chapter~\ref{chap:QIVPM}, and some of the remaining ones are
+explained in Chapter~\ref{chap:Further-Discussion}.}\tabularnewline
 \midrule 
- &  & Supervisor &  &  &  &  & The application for \emph{Rethinking Foundations of Physics} 2017
-workshop inspires Chapter~\ref{chap:Introduction}.\tabularnewline
+ &  & {\small{}Supervisor} &  &  &  &  & {\small{}The application for \emph{{\small{}Rethinking Foundations of Physics}}
+2017 workshop inspires Chapter~\ref{chap:Introduction}.}\tabularnewline
 \midrule 
-Advisory committee & Member & Member & Member & Member &  &  & The survey of real computation in the Computer Science qualifying
-exam (chaired by Prof.\ Sabry) inspires Chapter~\ref{chap:Introduction}.\tabularnewline
+{\small{}Advisory committee} & {\small{}Member} & {\small{}Member} & {\small{}Member} & {\small{}Member} &  &  & {\small{}The survey of real computation in the Computer Science qualifying
+exam (chaired by Prof.\ Sabry) inspires Chapter~\ref{chap:Introduction}.}\tabularnewline
 \midrule 
-PHYS-P700 & Instructor &  &  &  &  &  & The textbook~\cite{Mermin2007} of \emph{Quantum Computation and Information}
+{\small{}PHYS-P700} & {\small{}Instructor} &  &  &  &  &  & {\small{}The textbook~\cite{Mermin2007} of \emph{{\small{}Quantum Computation and Information}}
 is cited in Chapters~\ref{chap:Introduction}, \ref{chap:Conventional-Quantum-Theory},
-\ref{chap:DQT=000026DQC}, and~\ref{chap:QIVPM}.\tabularnewline
+\ref{chap:DQT=000026DQC}, and~\ref{chap:QIVPM}.}\tabularnewline
 \midrule 
-CSCI-B629 &  & Instructor &  &  &  &  & The textbook~\cite{hottbook2013} of \emph{Homotopy Type Theory}
-is cited in Sec.~\ref{discretequantumtheoryIIb}.\tabularnewline
+{\small{}CSCI-B629} &  & {\small{}Instructor} &  &  &  &  & {\small{}The textbook~\cite{hottbook2013} of \emph{{\small{}Homotopy Type Theory}}
+is cited in Sec.~\ref{discretequantumtheoryIIb}.}\tabularnewline
 \midrule
-Tier 3 committee & Co-chair & Co-chair &  & Member &  & Co-chair & Two of the assigned papers \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644}
+{\small{}Tier 3 committee} & {\small{}Co-chair} & {\small{}Co-chair} &  & {\small{}Member} &  & {\small{}Co-chair} & {\small{}Two of the assigned papers \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644}
 in the Tier 3 exam~\cite{Mathematics2018} are cited in Chapters~\ref{chap:Introduction}
-and~\ref{chap:Unrestricted-Finite-Fields}.\tabularnewline
+and~\ref{chap:Unrestricted-Finite-Fields}.}\tabularnewline
 \midrule
-MATH-M781 &  &  &  &  &  & Instructor & The presented paper~\cite{Abramsky2012} of \emph{Coalgebra} is
-cited in Sec.~\ref{subsec:Classical-and-Quantum}.\tabularnewline
+{\small{}MATH-M781} &  &  &  &  &  & {\small{}Instructor} & {\small{}The presented paper~\cite{Abramsky2012} of \emph{{\small{}Coalgebra}}
+is cited in Sec.~\ref{subsec:Classical-and-Quantum}.}\tabularnewline
 \bottomrule
@@
 \renewcommand{\endtabular}{\ORIGendtabular} 
-\end{doublespace}
 \end{sidewaystable}
@@
 \noindent \begin{centering}
-\includegraphics[viewport=200bp 0bp 1800bp 600bp,width=1.1\columnwidth]{picC}
+\includegraphics[viewport=200bp 0bp 1800bp 600bp,width=0.9\columnwidth]{picC}
 \par\end{centering}

### 2022-04-09 pullback.tex
pullback.lyx change the main compiler from XeTeX to pdfLaTeX...

--- 2019-05-23 dissertation.tex
@@
-%% LyX 2.3.2-2 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.3.6.1 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
-\documentclass[11pt]{iuphd}
+\documentclass[11pt,english]{article}
+\usepackage[T1,T2A]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{verbatim}
+\usepackage{booktabs}
+\usepackage{mathrsfs}
+\usepackage{enumitem}
 \usepackage{amsmath}
 \usepackage{amssymb}
-\usepackage{fontspec}
-\setmainfont[Mapping=tex-text]{Times New Roman}
-\setcounter{secnumdepth}{3}
-\setcounter{tocdepth}{3}
-\usepackage{verbatim}
+\usepackage{graphicx}
 \usepackage{rotfloat}
-\usepackage{booktabs}
-\usepackage{mathrsfs}
-\usepackage{url}
-\usepackage{enumitem}
-\usepackage{pdfpages}
-\usepackage{graphicx}
 \usepackage{setspace}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-\providecommand{\LyX}{L\kern-.1667em\lower.25em\hbox{Y}\kern-.125emX\@}
-\let\@@LyX\LyX
-\def\LyX{\@ensure@LTR{\@@LyX}}
 %% Because html converters don't know tabularnewline
 \providecommand{\tabularnewline}{\\}
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
 
@@
 \newlength{\lyxlabelwidth}      % auxiliary length
-\providecommand*{\code}[1]{\texttt{#1}}
 
@@
 \usepackage{dsfont}
-\usepackage[AutoFallBack=true]{xeCJK}
-\setCJKmainfont[FallBack=Batang]{SimSun}
+%\usepackage[AutoFallBack=true]{xeCJK}
+%\setCJKmainfont[FallBack=Batang]{SimSun}
 % \usepackage{xeCJK}
@@
 %\usepackage[basic]{complexity}
-\newcommand{\lang}[1]{{\ensuremath{\textsf{#1}}}}
-\newcommand{\newlang}[2]{\newcommand{#1}{\lang{#2}}}
-\newlang{\usat}{UNIQUE-SAT}
+%\newcommand{\lang}[1]{{\ensuremath{\textsf{#1}}}}
+%\newcommand{\newlang}[2]{\newcommand{#1}{\lang{#2}}}
+%\newlang{\usat}{UNIQUE-SAT}
 \newcommand{\ComplexityFont}[1]{%
@@
 \theoremstyle{plain}
-\newtheorem{prop}{Proposition}[chapter]
-\newtheorem{thm}{Theorem}[chapter]
-\newtheorem{lemma}{Lemma}[chapter]
+\newtheorem{prop}{Proposition}%[chapter]
+\newtheorem{thm}{Theorem}%[chapter]
+\newtheorem{lemma}{Lemma}%[chapter]
 \newtheorem{case}{Case}
-\newtheorem{corollary}{Corollary}[chapter]
+\newtheorem{corollary}{Corollary}%[chapter]
 
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}[chapter]
-\newtheorem{question}{Question}[chapter]
+\newtheorem{definition}{Definition}%[chapter]
+\newtheorem{question}{Question}%[chapter]
 \newtheorem*{method}{Method}
-\newtheorem{example}{Example}[chapter]
-\newtheorem{postulate}{Postulate}[chapter]
+\newtheorem{example}{Example}%[chapter]
+\newtheorem{postulate}{Postulate}%[chapter]
 
@@
 
-\usepackage{unicode-math}
+%\usepackage{unicode-math}
 \RequirePackage{ifthen}
@@
 
-\department{Department of Mathematics}
-\department{Department of Computer Science}
+%\department{Department of Mathematics}
+%\department{Department of Computer Science}
 
@@
 \usepackage{datetime2-calc}
-\monthGranted{June}%\DTMmonthname{\month}}
-\yearGranted{\the\year}
+%\monthGranted{June}%\DTMmonthname{\month}}
+%\yearGranted{\the\year}
 
@@
 \renewcommand{\tabularxcolumn}[1]{m{#1}}
-\newcolumntype{Y}{>{\centering\doublespacing\arraybackslash}X}
-\newcolumntype{M}[1]{>{\centering\doublespacing\arraybackslash}m{\widthof{#1}}}
+\newcolumntype{Y}{>{\centering\arraybackslash}X}
+\newcolumntype{M}[1]{>{\centering\arraybackslash}m{\widthof{#1}}}
 
@@
 
-\@ifundefined{showcaptionsetup}{}{%
- \PassOptionsToPackage{caption=false}{subfig}}
-\usepackage{subfig}
 \makeatother
 
-\usepackage{polyglossia}
-\setdefaultlanguage[variant=american]{english}
-\setotherlanguage{arabic}
-\setotherlanguage{bahasai}
-\setotherlanguage{basque}
-\setotherlanguage{french}
-\setotherlanguage{german}
-\setotherlanguage{italian}
-\setotherlanguage{portuges}
-\setotherlanguage{turkish}
-\setotherlanguage{vietnamese}
+\usepackage{babel}
 \usepackage[style=numeric-comp,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
@@
 \begin{document}
-\title{Discrete Quantum Theories and Computing}
-\author{Yu-Tsung Tai}
+\title{Classical probability measures as pullback of quantum probability
+measures?}
 
 \maketitle
-%data for Acceptance Page
-\committeeMember{Amr A. Sabry, PhD} \committeeMember{Dylan Paul
-Thurston, PhD} \committeeMember{Gerardo Ortiz, PhD} \committeeMember{Andrew
-J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{November
-29, 2018} \acceptancepage
-
-%data for Copyright Page
-%\copyrightpage
-
-\begin{dedication}To my parents, Cheng-Tien Tai (戴振沺) and Feng-Ming
-Chang (張鳳鳴).\end{dedication}
-
-\begin{comment}
-
-\chapter*{Survey of the acknowledgments in theses}
-
-I found the sentences in my Acknowledgments almost always contains
-“thank” and looks boring. To improve my Acknowledgments, I briefly
-read the Acknowledgments in other theses \cite{Chih2013,Sun2015,Lee2013,Chen2016,sabry1995formal}.
-\end{comment}
-\begin{acknowledgments*}
+As discussed in Sec.~\ref{subsec:Classical-and-Quantum}, the quantum
+probability spaces could be thought as a big space glued by ``local''
+classical probability space defined by each orthonormal basis~$\Omega$
+according to the map $\varphi:2^{\Omega}\rightarrow\events$ defined
+in Eq.~(\ref{eq:pullback-function}) which sends a classical event
+$E\in2^{\Omega}$ to a quantum event $\varphi\left(E\right)\in\events$.
+Then, for any quantum probability measure $\mu\colon\events\rightarrow\left[0,1\right]$,
+the function $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)\colon2^{\Omega}\rightarrow\left[0,1\right]$
+defined by precomposition is a classical probability measure. Since
+that ``precomposition'' is called ``pullback'' in differential
+geometry~\cite{wiki:Pullback}\footnote{Whether this kind of ``pullback'' is categorical will need further
+investigate.}, we will use their notation and write the precomposition $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)$
+as $\lambda E.\left(\varphi^{*}\mu\right)\left(E\right)$, i.e., $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$,
+and $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$ the
+pullback of $\mu$ by $\varphi$, and summarize how ``pullback''
+preserves their structures in Table~\ref{tab:Comparison}. 
 \begin{sidewaystable}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{tab:committee}The professors served in all my committees.}
+\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical and quantum
+measurement processes with real-valued probability for finite dimensional
+cases}
 %% ERT block 1 (before LyX tabular)
@@
 \renewcommand{\endtabular}{\endtabularx} 
-\begin{tabular}{M{MATH-M781}M{Co-author}M{(\textarabic{عمرو~صبري})}M{Co-author}M{Thurston}M{Shouhong}M{Lawrence}Y}
+\begin{tabular}{YYYY}
 \toprule 
-Committee or course & Gerardo Ortiz & Amr\nolinebreak[3] A.
-Sabry\linebreak[3] (\textarabic{عمرو صبري}) & Andrew\nolinebreak[3] J.
-Hanson & Dylan\nolinebreak[3] Paul Thurston & Shouhong Wang\linebreak[3] (汪守宏) & Lawrence\nolinebreak[3] S.\linebreak[2] Moss & Relation with the dissertation\tabularnewline
+Name & Classical & Quantum & How does the structure preserve?\tabularnewline
 \midrule
 \midrule 
- & Co-author & Co-author & Co-author &  &  &  & Most of Chapters~\ref{chap:Conventional-Quantum-Theory}, \ref{chap:Unrestricted-Finite-Fields},
-and~\ref{chap:DQT=000026DQC} is based on~\cite{geometry2013} and~\cite{DQT2014};
-most of Chapter~\ref{chap:QIVPM} is based on~\cite{THOS2018}.\tabularnewline
+Event & $E\in2^{\Omega}$ & $\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events$ & Eqs.~(\ref{eq:pullback-properties-basic}) and (\ref{eq:pullback-properties})\tabularnewline
 \midrule 
-Research committee & Co-chair & Co-chair & Member & Co-chair & Member &  & Some questions in the dissertation proposal are answered in Chapter~\ref{chap:QIVPM},
-and some of the remaining ones are explained in Chapter~\ref{chap:Further-Discussion}.\tabularnewline
+Probability measure & $\begin{array}{cccc}
+\varphi^{*}\mu\colon & 2^{\Omega} & \rightarrow & \left[0,1\right]\\
+ & E & \mapsto & \mu\left(\varphi\left(E\right)\right)
+\end{array}$ & $\begin{array}{cccc}
+\mu\colon & \events & \rightarrow & \left[0,1\right]\\
+ & P & \mapsto & \mu\left(P\right)
+\end{array}$ & Eqs.~(\ref{eq:QuantumProbability}) and (\ref{eq:QuantumProbability-Addition})\tabularnewline
 \midrule
- &  & Supervisor &  &  &  &  & The application for \emph{Rethinking Foundations of Physics} 2017
-workshop inspires Chapter~\ref{chap:Introduction}.\tabularnewline
 \midrule 
-Advisory committee & Member & Member & Member & Member &  &  & The survey of real computation in the Computer Science qualifying
-exam (chaired by Prof.\ Sabry) inspires Chapter~\ref{chap:Introduction}.\tabularnewline
+Possible measured values & $\lambda_{i}\in\mathbb{R}$ & $\lambda_{i}\in\mathbb{R}$ & Equal\tabularnewline
 \midrule 
-PHYS-P700 & Instructor &  &  &  &  &  & The textbook~\cite{Mermin2007} of \emph{Quantum Computation and Information}
-is cited in Chapters~\ref{chap:Introduction}, \ref{chap:Conventional-Quantum-Theory},
-\ref{chap:DQT=000026DQC}, and~\ref{chap:QIVPM}.\tabularnewline
+The event to measure $\lambda_{i}$ & $E_{i}\in2^{\Omega}$ & $\varphi\left(E_{i}\right)\in\events$ & Mapped by $\varphi$\tabularnewline
 \midrule 
-CSCI-B629 &  & Instructor &  &  &  &  & The textbook~\cite{hottbook2013} of \emph{Homotopy Type Theory}
-is cited in Sec.~\ref{discretequantumtheoryIIb}.\tabularnewline
+The probability that the measured value is $\lambda_{i}$ & $\left(\varphi^{*}\mu\right)\left(E_{i}\right)=\mu\left(\varphi\left(E_{i}\right)\right)\in\left[0,1\right]$ & $\mu\left(\varphi\left(E_{i}\right)\right)\in\left[0,1\right]$ & Equal\tabularnewline
 \midrule 
-Tier 3 committee & Co-chair & Co-chair &  & Member &  & Co-chair & Two of the assigned papers \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644}
-in the Tier 3 exam~\cite{Mathematics2018} are cited in Chapters~\ref{chap:Introduction}
-and~\ref{chap:Unrestricted-Finite-Fields}.\tabularnewline
+Summarize the measurement process as & random variable $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{E_{i}}$ & observable $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\varphi\left(E_{i}\right)$ & \tabularnewline
 \midrule 
-MATH-M781 &  &  &  &  &  & Instructor & The presented paper~\cite{Abramsky2012} of \emph{Coalgebra} is
-cited in Sec.~\ref{subsec:Classical-and-Quantum}.\tabularnewline
+Expectation value & $\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)=\sum_{i=0}^{D-1}\lambda_{i}\left(\varphi^{*}\mu\right)\left(E_{i}\right)$ & $\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\varphi\left(E_{i}\right)\right)$ & Equal, and proved in Lemma~\ref{lemma:real-expectation-value-between-classical-quantum}\tabularnewline
+\midrule
+\midrule 
+Probability measure could be simplified as & probability mass function $m:\Omega\rightarrow[0,1]$ such that $\left(\varphi^{*}\mu\right)(E)=\sum_{\omega\in E}m(\omega)$ & mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such that $\mu\left(P\right)=\Tr\left(\rho P\right)$ & \tabularnewline
+\midrule 
+ & Need a notation for $\varphi^{*}\mu\mapsto m$ to keep going & Need a notation for $\mu\mapsto\rho$ to keep going & We may draw commuting diagram (?) here\tabularnewline
+\midrule 
+The probability that the measured value is $\lambda_{i}$ &  &  & \tabularnewline
+\midrule 
+Expectation value &  &  & \tabularnewline
+\midrule
+\midrule 
+Post-measurement state &  &  & \tabularnewline
 \bottomrule
@@
 \renewcommand{\endtabular}{\ORIGendtabular} 
-\end{doublespace}
 \end{sidewaystable}
-I want to thank the professors who served in all my committees. These
-professors advised me as committee members and taught me while we
-wrote papers together and when I took their courses. Most of my dissertation
-is either based on these papers or inspired by the studies supervised
-by them as listed in Table~\ref{tab:committee}. Especially, Prof.\ Andrew
-J. Hanson, Prof.\ Gerardo Ortiz, and Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
-meet me weekly for the past few years, read and tried to understand
-what I typed which sometimes even myself cannot understand, taught
-me how to organize them in ``English'' so that general audience
-might be interested and have some chance to understand, and encouraged
-me to participate seminars, workshops, and conferences. Prof.\ Lawrence
-Moss invited me to present our results in the interdisciplinary logic
-seminar and theory seminar in Computer Science and wrote an assessment
-letter for me. Although not directly related to this dissertation,
-the \textgerman[variant=german,spelling=new,babelshorthands=true]{Weil}
-conjecture~\cite{hartshorne1977algebraic} on Grassmannians studied
-with Prof.\ Dylan Paul Thurston and the quantum interpretation discussed
-with Prof.\ Shouhong Wang (汪守宏) also broadened my understanding on
-discrete and conventional quantum theories. I would like to express
-my appreciation to all of these.
-
-To have the current content of dissertation, I would also like to
-thank John Gardiner for some inspiring discussion about quantum probability
-measures over finite fields~\cite{Gardiner2014}. His research supervised
-by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
-and~\ref{sec:Toward-IVPM}. Besides of my committee members, what
-I learned from the teachers in other courses also helped me consolidate
-this dissertation as listed in Table~\ref{tab:teacher}. Learning
-other materials also made me more mature and easier to communicate
-with others. I need to thank those who taught me, especially my English
-teachers, Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
-Chen (谌可心).
-
-\begin{table}[!t]
-\begin{doublespace}
-\noindent \centering{}\caption{\label{tab:teacher}Other courses I took which is relevant to this
-dissertation, where IUB stands for Indiana University Bloomington
-and NTU stands for National Taiwan University.}
+We can then extend this table to compare between the classical and
+quantum measurement processes to get real numbers. It is clear that
+each step of the measurement process is exactly equal or just mapped
+by $\varphi$ except we summarize classical measurement process as
+random variable, but summarize quantum measurement process as an observable.
+Notice that after we fix an orthonormal basis~$\Omega$, $\varphi$
+is actually an invertible map so that given an observable $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$,
+we can define an unique random variable $\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\varphi^{-1}\left(P_{i}\right)}$
+corresponding to $\mathbf{O}$. Therefore, we call this random variable
+as the pullback of $\mathbf{O}$ by $\varphi$, and denoted by $\varphi^{*}\mathbf{O}$.\footnote{We might also choose the other way around so that each random variable
+has a push forward observable. This is better in the sense that we
+don't have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be
+different for different orthonormal basis, but every theorem for IVPMs
+starts from the quantum part with an observable, so we need the ambiguous
+$\varphi^{*}\mathbf{O}$ for each different orthonormal basis anyway.} According to Gleason's theorem, the table could be extended to simplify
+the formula computing expectation values and the the post-measurement-state
+postulates after we define a notation to send probability measures
+to states and the other way around.
+
+By following the same process, Sec.~\ref{sec:Interval-Uncertainty}
+showed the corresponding results for interval-valued probability.
+For any QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$, the
+function $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
+defined by $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
+is a classical IVPM.
+\begin{sidewaystable}
+\noindent \centering{}\caption{\label{tab:Comparison-interval}Comparison between the classical and
+quantum measurement processes with interval-valued probability for
+finite dimensional cases}
 %% ERT block 1 (before LyX tabular)
@@
 \renewcommand{\endtabular}{\endtabularx} 
-\begin{tabular}{M{Chou~(周謀鴻)}cM{MATH-M522}Y}
+\begin{tabular}{YYYY}
 \toprule 
-Instructor & School & Course & Relation with the dissertation\tabularnewline
+Name & Classical & Quantum & How does the structure preserve?\tabularnewline
 \midrule
 \midrule 
-Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
-paper of \emph{Academic Writing}.\tabularnewline
-\midrule 
-Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
-in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
-\midrule 
-Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
-is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
-\midrule 
-Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
-is cited in Secs.~\ref{sec:background}, \ref{discretequantumtheoryI},
-and~\ref{discretequantumtheoryIIb}.\tabularnewline
-\midrule 
-Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
-is cited in Secs.~\ref{subsec:Two-dimensional-Hilbert-Space}, \ref{subsec:Cyclic-Properties-of},
-\ref{subsec:Complexified-Finite-Fields}, and~\ref{discretequantumtheoryIIb}.\tabularnewline
-\midrule 
-Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
-is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
-\midrule
-Mo-Hong\linebreak[3] Chou (周謀鴻) & NTU & 221~U4290 & The textbook~\cite{GolubVanLoan1996} of \emph{Introduction to Computational Linear Algebra}
-is cited in Sec.~\ref{subsec:Finite-Precision-Extension-of}.\tabularnewline
+Probability measure & $\begin{array}{cccc}
+\varphi^{*}\bar{\mu}\colon & 2^{\Omega} & \rightarrow & \mathscr{I}\\
+ & E & \mapsto & \bar{\mu}\left(\varphi\left(E\right)\right)
+\end{array}$ & $\begin{array}{cccc}
+\bar{\mu}\colon & \events & \rightarrow & \mathscr{I}\\
+ & E & \mapsto & \bar{\mu}\left(E\right)
+\end{array}$ & \tabularnewline
 \bottomrule
@@
 \renewcommand{\endtabular}{\ORIGendtabular} 
-\end{doublespace}
-\end{table}
-Many people have done everything to make my double-major smooth. I
-need to thank all of their supports, financially or providing some
-experience, as listed in my Curriculum Vitae at the end of the dissertation.
-Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
-helped me deal with the rules, supervised my reading courses for writing
-our papers, and financially support me as a research assistant and
-associate. In the department of Mathematics, I need to thank the directors
-of graduate study in Mathematics, especially Prof.\ Christopher Judge,
-Prof.\ Matthias Weber, and Prof.\ Michael A.\ Mandell; and the
-graduate services assistant, Kate Forrest. In the department of Computer
-Science, I want to thank the directors of \PhD study in Computer
-Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
-Ergun}; the graduate student office; the director of AI/UI assignments,
-Charles Pope; and the infrastructure and technology group (ITG). Particularly,
-I don't know how much computational power I consumed to count the
-states in Sec.~\ref{subsec:Maximal-entanglement}. This computational
-power not only came from the Linux systems in Computer Science but
-also came from the Big Red II administrated by University Information
-Technology Services (UITS). Indiana University Libraries was also
-extremely helpful during my dissertation research. Except for a stack
-of books I checked out directly, while the books are not in their
-collection, I occasionally requested them via the Interlibrary Loan
-service or recommended IU libraries to purchase them.
-
-Except for the financial support via employment and award, I have
-also supported by my family, especially my father Cheng-Tien Tai (戴振沺).
-He always thinks one-step ahead and cares about my future more than
-I do. Discussion with other family members and friends also helped
-me to compose this dissertation, to do research, or to live better
-in general, and I want to thank the following people which haven't
-been listed previously:\footnote{For some of them, I only provide their Chinese names for two reasons.
-First, I might only know their Chinese names. Second, there are many
-ways to translate a name to English, but I don't know which one they
-choose.}
-
-\begin{itemize}
-
-\item The \PhD students in Mathematics, including Kin Wai Chan,
-ChunHsien Lu (呂俊賢), Cong Zhou (周蔥), Junyan Xu (许俊彦), Zhipeng Lu (路志鹏),
-Robert Rose, Neal Coleman, Dami Lee, Ruiyu Yang (杨瑞雨), Yingwei Li
-(李盈伟), Yu-Yuan Chen (陳裕元), Jan-Li Lin (林展立), Ping Zhong, Chen Xu (徐晨),
-Yiqiu Mao (茅一遒), Yu-Min Chung (鍾佑民), Shizhuo Zhang (张诗卓), Max Yining
-Zhang (张忆宁), \textturkish{Ata Tuncer}, Hongming Nie (聂洪明), Sandeep
-Bhupatiraju, Peng Wang, Guanglu Zhu (祝广路), Sailaja Gajula, Xuqiang
-Qin (秦绪强), and \textvietnamese{Phuong Nguyen}, \ldots , etc.
-
-\item Other members in Mathematics, including Weihua Liu (刘伟华),
-Yinan ``Christina'' Wu (武怡楠), Cheng ``Freddie'' Shi (史程), Shabnam
-Kavousian, and Tyler Bennett (班天瑞), \ldots , etc.
-
-\item My officemates, especially, Inhak Hwang\ (황인학), Jiecao
-Chen (陈洁操), Erfan Sadeqi~Azer, Chao ``Alan'' Tao (陶超), Haoyu Zhang
-(张皓宇), Yadi Wei (魏雅廸), BoLi Fang (方博立), Yuan Xie (谢缘), and Mrinmoy
-Maity, \ldots , etc.
-
-\item My other friends having an office in Lindley or \textportuges{Luddy}
-Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-Chieh
-Shan (單中杰), Chao-Hong Chen (陳昭宏), Robert Rose, \textbasque{Bibrak
-Chandio}, Yuxiang Jiang (蒋宇翔), Lei Wang (王磊), Diyue Bu (卜廸悦), Pei-Ying
-Chen (陳珮瑩), Prof.~Qin Zhang (张勤), Praveen Narayanan, Liang Chen (陈亮),
-\textfrench{Ambrose Bonnaire-Sergeant}, Ali Varamesh, Min-Chin Lin
-(林旻瑾), and Career Services in the School of Informatics, Computing,
-and Engineering, \ldots , etc.
-
-\item My other family members, including my mother Feng-Ming Chang
-(張鳳鳴), my grandmothers 戴許玉婷 and 張林枝, my sister Sih-Sian Tai (戴司嫻),
-my cousins especially Caren Liu (劉鈺平) and Kiwi Liu (劉子綺), and my
-aunts and uncles, \ldots , etc.
-
-\item My roommates, including Meng-Wei Chen (陳孟瑋), Yu ``Larry''
-Chen (陈煜), Kenshin Reita (禮田謙信), and Jing-Han Liou (劉經翰).
-
-\item My classmates or friends in NTU, including Hao-Chun Lee (李浩君),
-Hsien-Ching Kao (高憲慶), Wei Cheng (鄭維), Chin-Yi Lin (林金毅), Chun-Ting
-Chen (陳俊廷), and Prof.~Chen-Ying Huang (黃貞穎), \ldots , etc.
-
-\item My friends living in the Tulip Tree Apartments, including Chao-Hong
-Chen (陳昭宏), Tsaiyi Wu (吳采奕), Cheng ``Freddie'' Shi (史程), Ossama
-Abdel~Gawwad, and Cathryn ``Cathy'' Creger-Chambers, \textbahasai{Sary
-Silvhiany}, Shaozhuan Li (李绍颛), Chenwei Zhang (张晨薇), Shu-Han ``Nancy''
-Chang (張舒涵), and Ching-Chi ``Victoria'' Chang (張靖琪), \ldots , etc.
-
-\item My AT\&T family plan members, especially Meng-Wei Chen (陳孟瑋),
-Yao-Yu Chih (池耀宇), and Xinyi ``Diana'' Gong (龚欣怡), \ldots , etc.
-
-\item Other friends, including Shu-Ling Wang (王舒齡), Wanling ``Wynnie''
-Chang (張婉鈴), Yu-Jung Lin (林宇容), Winnie Lou (何慧芳), Yi-Rong Yang (楊宜蓉),
-Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
-Peng Chou ``Davis'' Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding
-(丁颖), Hung-Chun Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超),
-Prof.~Jyh-Chyi Gong (龔治齊), 江靜宜, and the office of International Services\ldots ,
-etc.
-
-\end{itemize}
-
-\noindent This list could be on and on and never ends. If you have
-helped me in any form or provide any helpful information during my
-\PhD study, but I forget to list you or your unit here. Please forgive
-my bad memory.
-
-Finally, I want to thank K9 Web Protection for blocking distractive
-websites to keep me focus, and Jin-Ru Yang (楊謹如) for keeping the password
-and helping me control myself in general.\end{acknowledgments*}
-
-\begin{preface*}
-\begin{itemize}
-\item The latest PDF version of this thesis is in GitHub: \url{https://git.io/fxbuG}~.
-\item Its source code is typeset using \LyX{} \cite{LyX} in \url{https://git.io/fxbuE}
-and the exported \LaTeX{} file is in \url{https://git.io/fhZBW}~.
-\item Any comments can be left in the Issue part of the GitHub repository:
-\url{https://git.io/fxbug}~.
-\end{itemize}
-The following explains how to compile the PDF file from the \LaTeX{}
-source:
-\begin{enumerate}
-\item \label{enu:Clone-the-git}Clone the git repository of this thesis
-\url{https://git.io/fhZP5} into your local directory and the thesis
-document class \url{https://github.com/yuttai/iuphd} in a location
-where the system can find.
-\item In the local directory of this thesis, run \code{xelatex dissertation.tex}~.
-\item Run \code{biber dissertation}~.
-\item Run \code{xelatex dissertation.tex} several times until all the references
-are resolved.
-\end{enumerate}
-The previous steps only tested in Microsoft Windows with MiK\TeX{}
-2.9. Please report me if there is any difficulty to compile it. Besides,
-to compile a PDF file from the \LyX{} source, just finish step~\ref{enu:Clone-the-git},
-open \code{dissertation.lyx} in \LyX , and click the toolbar button
-\includegraphics[width=1em]{buffer-view}.\end{preface*}
-
-\begin{abstract*}Most quantum computing models are based on the continuum
-of real numbers, while classical digital computers faithfully realize
-only discrete computational models. Analog computers appear to be
-an option, but in reality are far weaker than would be needed for
-computational models requiring real numbers. One approach to resolving
-this conflict is to find consistent mathematical ways to limit measurement
-precision to computable contexts that do not require incomputable
-real numbers. Our goal is to build a more philosophically consistent
-models by investigating discrete quantum computing using finite number
-systems, and, alternatively, by incorporating finite precision measurement
-using intervals into quantum theory.
-
-We begin by replacing the continuum of complex numbers by discrete
-finite fields in quantum theory. The simplest theory, defined over
-unrestricted finite fields, is so weak that it cannot express Deutsch's
-algorithm, but, paradoxically, is also so powerful that it can be
-used to solve the $\usat$ problem, which is as hard as a general
-$\NP$-complete problem.
-
-Our second framework employs only finite fields over prime numbers
-of the form $4\ell+3$, which possess no solutions to $x^{2}+1=0$,
-and thus permit an elegant complex representation of the finite field
-by adjoining $\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit
-system are in principle enumerable, we can count the number of states,
-and determine the proportions of entangled and unentangled states.
-Depending on how we model the measurement process, this improved framework
-can be used to implement deterministic Deutsch's algorithm and the
-probabilistic Grover search algorithm in a local region, but we still
-haven't found a consistent way to treat quantum probability measures
-in general.
-
-Finally, we shift our attention to consider quantum interval-valued
-probability measures (IVPMs), which potentially embody both finite
-precision measurement and a sensible correspondence to standard quantum
-probability. This interval-valued framework not only provides a natural
-generalization of both classical IVPMs and conventional quantum probability
-measures, but also allows us to establish bounds on the validity of
-the Kochen-Specker and Gleason theorems in realistic experimental
-environments.\end{abstract*}
-
-\tableofcontents{}
-
-\chapter{Introduction\label{chap:Introduction}}
-
-Since no human being can distinguish quantities differing only by
-an arbitrarily small extent \cite{Turing_1937,Gisin2017}, we want
-to incorporate this limitation into our quantum mechanical model to
-better capture our ability to predict quantum phenomena and the power
-of realistic quantum computers. Since we are agnostic about whether
-the reality is ultimately discrete or continuous, we consider two
-types of quantum models. By assuming the quantum states are ultimately
-discrete and distinguishable, our first type of quantum theories replaces
-the complex numbers by finite fields. We then focus on the limitation
-of distinguishability itself, incorporate finite precision measurements
-into our model, and consider quantum interval-valued probability measures.
-
-After first suggested by Richard Feynman 40 years ago~\cite{Feynman1982Simulating},
-IBM, \textitalian{Rigetti}, Google, Microsoft, and many other companies
-and countries have started to build realistic quantum computers recently
-\cite{Shieber2018,Kahn2019} seeking more efficient ways to simulate
-chemical molecules and breaking RSA \cite{boneh1999twenty,wiki:RSAFactoring}.
-No matter how to, classical or quantum, attack these two tasks, they
-require two different types of quantities. On one hand, a question
-and its answer of RSA are both discrete integers. On the other hand,
-molecules are described by quantities including the domain of their
-position wave functions and the probability amplitudes of these wave
-functions, which look like continuous at first sight. However, either
-these quantities might later be discovered to be discrete, or their
-exact values may never be pinned down. Hence, modeling quantum computing
-based on the exact values of continuous quantities cannot really describe
-the computational power of a realistic quantum computer. To better
-understand this issue without struggling with the quantum theory,
-it is instructive to review how classical quantities are characterized
-and computed.
-
-Discrete quantities can be easily characterized by integers~\cite{ParkerBaldridge2004}.
-Even if the proportion of integers are fractions, the operations among
-fractions are essentially the same as those among integers over the
-common denominator. In general, discrete computation can be reliably
-repeated with exact equivalence, and any digital computer can faithfully
-simulate a Turing machine limited only by the available memory and
-time~\cite{Turing_1937}.
-
-In contrast, the non-apparently discrete quantities confused many
-cultures since the very beginning. For example, the ancient Chinese
-philosopher Chuang-tzu (庄子) didn't believe these quantities have a
-minimum unit and expressed ``If a one-foot-long stick is cut into
-halves every day, the cutting will never come to an end''.\footnote{``一尺之棰，日取其半，萬世不竭。'' in Chinese \cite{Zhuangzi1999,Liu2018}.}
-As another example, Greek mathematicians in the school of Pythagoras
-believed every mathematical model must be ultimately discrete, and
-they in legend murdered Hippasus because he proved there is no minimum
-unit between a side of a square and its diagonal. Comparing the idea
-that the length of a square's diagonal is not a physical quantity
-or there is no square physically, working with a mathematical model
-without minimum unit seems more appealing. Since the mathematical
-models are continuous, their corresponding physical quantities are
-naturally assumed to be continuous. Later, these continuous quantities
-became the basic component of analog computers. After logarithms were
-discovered, a slide rule, also known as a slipstick, was used to compute
-multiplication, division, and more complex operations as a mechanical
-analog computer~\cite{wiki:SlideRule}. Charge amplifiers are used
-to build electrical analog computers and compute integration in calculus
-\cite{wiki:Integrator,wiki:ChargeAmplifier}.
-
-Although it is convenient to assume physical quantities are as continuous
-as their mathematical models, each physical quantity discussed in
-the previous paragraph could not have a simple one-to-one correspondence
-with a real number. Chuang-tzu's stick is made by molecules and cannot
-be cut in halves endlessly. The input charge of an integrator must
-be an integer multiple of the elementary charge. A perfect square
-cannot be drawn physically. Even we don't draw it, but merely ask
-whether it exists in the space. This question is still beyond our
-ability to answer because whether space itself is ultimately discrete
-or continuous is still an unsolved question. Even if a perfect square
-exists physically, we may not able to decide whether the ``square''
-we discussed is really perfect or almost perfect differing only by
-an arbitrarily small extent. Similar situation applying to the length
-of a slide rule, it is beyond our ability to decide whether its length
-is ultimately discrete or continuous. Even if its length is continuous,
-identifying which real number represents its length requires infinite
-precision, but the precision in reality is limited generally to three
-or four significant figures~\cite{wiki:AnalogComputer}. As the results,
-even if analog computers really store real numbers, they cannot be
-precisely read, written, and used to branch the computation. The opposite
-of the last statement is sometimes assumed by real computational models.
-For example, Blum, Cucker, Shub, and Smale modeled their BCSS machine
-to allow the operations of deciding whether a number is greater or
-equal to zero over real numbers and whether a number is exactly zero
-over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
-Hence, when the quantities used to branch the computation closes to
-zero, the branch chosen by a BCSS machine cannot reliably predict
-the branch chosen by a realistic analog computer. Since two branches
-of computations may not have any relations, the follow-up computational
-paths may be significantly different, and this difference is unlikely
-to be compensated by error analysis techniques easily like the butterfly
-effect. Therefore, we might not be able to utilize a realistic analog
-computer to acquire the computational power predicted by this kind
-of theoretical models.%
-\begin{comment}
-\todo{Maybe extended to consider probabilistic model? For BCSS machine,
-maybe using the idea of BPP to define the complexity class is more
-reasonable than P or NP?}
-\end{comment}
-
-\begin{sidewaystable}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical quantities
-and their mathematical models with the inspired quantum models.}
-%% ERT block 1 (before LyX tabular)
-\renewcommand{\tabular}{\tabularx{\linewidth}}
-\renewcommand{\endtabular}{\endtabularx} 
-\begin{tabular}{YcYY}
-\toprule 
-Physical quantity & Discrete & Discrete with extreme small units & Continuous, or no evidence to support they are discrete\tabularnewline
-\midrule 
-Computational device & Digital computer & Analog computer & Analog computer\tabularnewline
-\midrule
-\midrule 
-Mathematical representation & Integer & Real number & Real number\tabularnewline
-\midrule 
-Computational model & Turing machine & BCSS machine & BCSS machine\tabularnewline
-\midrule
-\midrule 
-How does the theoretical model predict the behavior of the physical
-device? & Reliably & Not reliably, but after we have better technology to manipulate the
-minimum units, we can more reliably predict the physical phenomenon
-and their computational power by a better discrete model. & Not reliably, because precision can never be high enough, and the
-difference between their computational power might not be able compensated
-by error analysis techniques.\tabularnewline
-\midrule 
-Inspired quantum model &  & Quantum theories and computing over finite fields & Quantum interval-valued probability measures (QIVPM)\tabularnewline
-\bottomrule
-\end{tabular}% ERT block 2 (after LyX tabular)
-\renewcommand{\tabular}{\ORIGtabular}
-\renewcommand{\endtabular}{\ORIGendtabular} 
-\end{doublespace}
 \end{sidewaystable}
-The situations for classical quantities and the computational power
-above them are summarized in Table~\ref{tab:Comparison}, and two
-possibilities for classical quantities inspires two types of quantum
-models. Like its classical counterparts, quantum circuit model, the
-most widely used model of quantum computing, manipulates quantities
-which are not discrete apparently: the probability amplitudes of quantum
-states, which are assumed in the field of complex numbers in the ``conventional
-quantum theory'' (CQT).\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
-and ``ordinary'' quantum theory.} If the probability amplitudes are assumed to be ultimately discrete,
-we choose to replace the field of complex numbers by discrete finite
-fields for two reasons. On one hand, CQT is built upon the operations
-among the probability amplitudes, and the probability amplitudes have
-the required operations since the complex numbers form a field. On
-the other hand, based on finite fields, we will define the fraction-like
-cardinal probability which has extremely small units when the size
-of the field is extremely large. Alternatively, even if the probability
-amplitudes might never be found quantized, considering the precision
-of quantities could still result in a better model. However, comparing
-to the precision of probability amplitudes, it is easier to consider
-the precision of their inducing probabilities because the idea of
-``imprecise probability'' is well-studied classically \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
-\begin{comment}
-\todo{Make sure whether realistic quantum computers could branch
-their computation based on their probability amplitudes or measured
-probabilities? If they can only branch on their measured probabilities,
-it will provide another reason why we want to study the precision
-of the inducing probabilities\ldots{} }
-\end{comment}
-This idea will be extended to quantum domain as quantum interval-valued
-probability measure (QIVPM).
-
-\begin{comment}
-After a review of finite fields in Section~\ref{sec:background},
-we proceed with a sequence of finite-field approaches that lead more
-and more closely to the properties of conventional quantum computing.
-\end{comment}
-\begin{comment}
-An $n$-qubit pure state in the conventional quantum theory (CQT)
-is represented as a vector in the $2^{n}$-dimen\-sional Hilbert
-space. If we eliminate all symmetries, an irreducible state is actually
-a point in the projective Hilbert space \cite{MosseriDandoloff2001,Jaeger2007}
-also known as the complex projective space~$\CP{2^{n}-1}$ \cite{Hatcher2001,Bengtsson2007}.
-These irreducible quantum states can also be classified as product
-states and entangled states, and the latter one plays an essential
-role for pure-state algorithms \cite{Mermin2007,Jaeger2007}.
-
-Given a pure state~$\ket{\Phi}$, when we measure an observable represented
-by a Hermitian matrix~$\mathbf{O}$, the measurement result is one
-of the eigenvalues of $\mathbf{O}$. The probability of getting a
-particular eigenvalue~$\lambda$ is $\melem{\Phi}{P}{\Phi}$, where
-$P$ is the projection operator onto the eigenspace of $\lambda$.
-This rule of computing the probability is called the Born rule \cite{Born1983,Mermin2007,Jaeger2007},
-which is used when we want to extract information from a quantum computer.
-For any mixed state~$\rho$, the generalized Born rule induces a
-conventional quantum probability measure $\muB_{\rho}\colon\events\rightarrow[0,1]$,
-where $\events$ is the set of all projection operators on a given
-Hilbert space. Conversely, any quantum probability measure $\mu\colon\events\rightarrow[0,1]$
-can be induced from a mixed state $\rho$ in the Hilbert space of
-dimension $D\ge3$ according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
-In other words, this state $\rho$ is the unique state consistent
-with any given quantum probability measure.
-\end{comment}
-The geometrical structure of states in CQT is first reviewed in Sec.~\ref{CQC1qubitBloch.sec},
-where a pure state is represented as a vector in a Hilbert space,
-and an irreducible state is actually a point in a projective Hilbert
-space \cite{MosseriDandoloff2001,Jaeger2007} also known as a complex
-projective space \cite{Hatcher2001,Bengtsson2007}. In Sec.~\ref{sec:fuzzy},
-we will construct a quantum probability space based on classical probability
-spaces, apply Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}
-to recover the Born rule \cite{Born1983,Mermin2007,Jaeger2007}, and
-define the expectation value of an observable. The expectation value
-will then be used in Sec.~\ref{sec:The-geometry-of} to define purity
-which provides an easy entanglement test.
-
-\begin{comment}
-In Section~\ref{modalquantum}, we examine previously-introduced
-quantum theories defined over unrestricted finite fields and show
-in Section~\ref{modalquantumcomputing} that this approach leads
-to theories with such bizarre powers that they are probably nonphysical.
-Although a version of quantum theory defined over a two-valued field
-can express simple algorithms such as quantum teleportation, it is
-so weak that it cannot express Deutsch's algorithm. This quantum theory
-is, however, also so powerful that it can be used to solve an unstructured
-database search of size $N$ using $O(\log(N))$ steps, which outperforms
-the known asymptotic bound $O(\sqrt{N})$ in conventional quantum
-computing.
-\end{comment}
-\begin{comment}
-Our first discrete model replaces the complex numbers with an unrestricted
-finite field~$\mathbb{F}_{q}$ \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
-In this model, an $n$-qubit state is a non-zero vector in $\mathbb{F}_{q}^{2^{n}}$.
-When we measure a given state~$\ket{\Phi}$, an observable is replaced
-by a basis~$\mathcal{B}$ of $\mathbb{F}_{q}^{2^{n}}$. Since $\ket{\Phi}$
-can be represented by the summation across a unique subset~$\mathcal{S}$
-of the basis~$\mathcal{B}$, whether it is possible or impossible
-to measure a basis vector~$\ket{i}$ depends on whether $\ket{i}$
-is in $\mathcal{S}$ or not. Because this model only predicts whether
-a result is possible or impossible, it is called the modal quantum
-theory. Its computational model, called the modal quantum computing,
-is far from conventional quantum computing. Although modal quantum
-computing can express simple algorithms such as quantum teleportation
-\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007},
-it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007}.
-This quantum theory is, however, also so powerful that it can be used
-to solve an unstructured database search of size $N$ using $O(\log(N))$
-steps, which outperforms the known asymptotic bound $O(\sqrt{N})$
-in conventional quantum computing \cite{Grover:1996:FQM:237814.237866,BennettBernsteinBrassardVazirani1997,Mermin2007,Jaeger2007}.
-\end{comment}
-In Chapter~\ref{chap:Unrestricted-Finite-Fields}, we examine previously-introduced
-quantum theories defined over unrestricted finite fields \cite{Schumacher2012-SCHMQT,DQT2014,SchumacherWestmoreland2010}.
-It is called the modal quantum theory because it can only predict
-whether a measurement result is possible or impossible, but not its
-probability. Although a version of quantum theory defined over the
-two-valued field can express simple algorithms such as quantum teleportation
-\cite{BennettBrassardEtAl1993,peres1995quantum,Mermin2007,Jaeger2007,Schumacher2012-SCHMQT},
-it is so weak that it cannot express Deutsch's algorithm \cite{Deutsch1985,Mermin2007,DQT2014}.
-This quantum theory is, however, also so powerful that it can be used
-to efficiently solve the $\usat$ problem~\cite{Papadimitriou1993},
-which is as hard as a general $\NP$-complete problem~\cite{Valiant198685}.
-
-\begin{comment}
-Next, in Section \ref{discretequantumtheoryI}, we improve on this
-by showing that for finite fields of order $p^{2}$, with the prime
-$p$ of the form $4\ell+3$ ($\ell$ a non-negative integer), the
-complex numbers have extremely compelling and natural discrete analogs
-that permit a great many of the standard requirements of quantum computing
-to be preserved. Under suitable conditions, we have amplitude-based
-partitions of unity, unitary transformations, and entanglement, as
-well as solutions to deterministic quantum algorithms such as the
-algorithms of Deutsch, Simon, and Bernstein-Vazirani~\cite{NCbook,Mermin},
-though still with some bothersome shortcomings. Because of the modular
-nature of arithmetic in the finite complex field, it is not possible
-to define an inner product in the usual sense, and we show in Section~\ref{discretequantumcomputingI}
-that this leads to excessive computational power for the unstructured
-database search problem for certain database sizes.
-\end{comment}
-\begin{comment}
-Our second model called discrete quantum theory (I) considers only
-finite fields of order $p^{2}$, with the prime $p$ of the form $4\ell+3$
-($\ell$ a non-negative integer) \cite{geometry2013,DQT2014}. In
-this model, an irreducible state is a vector in $\mathbb{F}_{p^{2}}^{2^{n}}$,
-and can be reduced to a point in the discrete complex projective space~$\mathbb{DCP}^{2^{n}-1}$.
-Among these irreducible states, the product states and entangled states
-can not only be identified as in CQT but also be counted for different
-$p$. Although the state space is a natural discrete analog to CQT,
-this model still only predicts whether a measurement result is possible
-or impossible, because it is not possible to define an inner product
-in the usual sense due to the modular arithmetic~\cite{grove2002classical}.
-Under suitable conditions, we can have deterministic quantum algorithms
-such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
-and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
-but this still leads to excessive computational power for the unstructured
-database search problem for certain database sizes.
-\end{comment}
-In Sec.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI},
-we improve on this by showing that for finite fields of order $p^{2}$,
-$\Fpp$, with the prime $p$ of the form $4\ell+3$ ($\ell$ a non-negative
-integer), the complex numbers then have extremely compelling and natural
-discrete analogs that preserve a great many of the standard requirements
-of quantum computing. In this model, the state of a discrete $D$-dimen\-sional
-system is a vector in the $D$-dimen\-sional vector space over $\Fpp$
-and can be reduced to a point in the discrete complex projective space.
-Among these irreducible states, the product states and entangled states
-could not only be identified as in CQT but also be counted for different
-$p$. Despite the similarity between this model and CQT, it still
-only predicts whether a measurement result is possible or impossible
-because it is not possible to define an inner product in the usual
-sense due to the modular arithmetic~\cite{grove2002classical}. Under
-suitable conditions, we can have deterministic quantum algorithms
-such as the algorithms of Deutsch, Simon \cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007},
-and Bernstein-Vazirani \cite{Bernstein:1993:QCT:167088.167097,Mermin2007},
-but this still leads to excessive computational power for partially
-solving the $\usat$ problem efficiently.
-
-\begin{comment}
-We are led, in Sections~\ref{discretequantumtheoryIIa} and~\ref{discretequantumtheoryIIb},
-to develop a framework with further restrictions on~$p$ that \emph{locally\/}
-recovers the structure and expected properties of conventional quantum
-theory. Section~\ref{discretequantumtheoryIIa} locally recovers
-the inner product space and Section~\ref{discretequantumtheoryIIb}
-locally recovers a notion of probability. The development in both
-sections exploits the fact that longer sequences of \textit{ordered\/}
-numbers appear in the quadratic residues (numbers with square-roots
-in the field) as the size of the field increases. Discrete quantum
-computations whose calculations are confined to numbers in this ordered
-sequence resemble conventional quantum computations. The size of the
-field $p$ plays an important role in describing the resources needed
-for the computation as larger problem sizes require a larger field
-size to represent all intermediate numerical values. A significant
-feature of our framework is that the resources needed for the measurement
-process can be separated from the resources needed by the evolution
-of the system being modeled. This interplay between the resources
-used by the system under study and the resources used for the observation
-process is a significant concept that is nonexistent in conventional
-quantum computing and is exposed by our careful accounting of resources.
-
-We note that the conventional mathematical framework based on the
-real numbers allows one to distinguish states whose measurement outcomes
-differ by infinitesimally small probabilities, e.g., $10^{-100}$
-vs.~$0$. In the proposed framework of discrete quantum computing,
-the finite size of the field implies a maximum precision for measurement:
-a ``small'' field represents limited resources with which it becomes
-impossible to distinguish states whose measurement outcomes differ
-by an amount less than the resolution afforded by the field. It is
-possible, however, to discriminate between such states at the cost
-of moving to a larger field, i.e., by investing more resources in
-the measurement process. We formalize this approach to measurement
-using the novel notion of \textit{cardinal probability\/}, with numerical
-labels corresponding to ``more probable, the same, or less probable,''
-rather than a percentage-based likelihood measure. In cardinal probability,
-relative outcomes are associated with intervals of ambiguity that
-get smaller and more precise as the size of the field increases.
-
-Finally, in Section~\ref{discretequantumcomputingII}, we apply our
-discrete quantum theory to the study of two representative algorithms,
-the deterministic Deutsch-Jozsa algorithm and the probabilistic Grover
-algorithm~\cite{NCbook,Mermin}. The first algorithm highlights the
-role played by the size of the field $p$ in determining the actual
-resources required for computation as the number of input bits $n$
-increases, a concept nonexistent in conventional quantum computing.
-The second algorithm highlights, in addition, the dependence of the
-precision of measurement (via cardinal probabilities) on the size
-of the field, another nonexistent concept in conventional quantum
-computing.
-\end{comment}
-\begin{comment}
-Our third model, discrete quantum theory (II)~\cite{DQT2014}, restricts
-states in some local region of $\mathbb{F}_{p^{2}}^{2^{n}}$. Within
-a local region, a notion of inner product and probability could be
-recovered. Its discrete quantum computing can be further applied to
-the deterministic Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007}
-and the probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
-\end{comment}
-Since many important quantum algorithms are probabilistic, we want
-to find a notion of probability for quantum theories over finite fields.
-The cardinal probability defined in Sec.~\ref{sec:Discrete-Quantum-Theory-(II)}
-restricts states in some local regions of the vector spaces, where
-a notion of inner product and probability could be recovered. In Sec.~\ref{discretequantumcomputingII},
-this discrete quantum theory is applied to two representative algorithms,
-the deterministic Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,Jaeger2007}
-and the probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
-\begin{comment}
-When people tried to define quantum probability over finite fields,
-people tended to treat the original Born rule as an axiom and tried
-to modify it to get a discrete Born rule \cite{Schumacher2012-SCHMQT,doi:10.1142/S0217984913500644,DQT2014,Ellerman2016a}.
-However, any modified Born rule could hardly work on the whole vector
-space, since there is no inner product on the whole vector space over
-finite fields. Instead of treating the Born rule as an axiom, the
-Born rule can be deduced from a set of abstract definitions and axioms
-according to Gleason's theorem. Although we might hope to deduce a
-discrete Born rule directly from a similar set of definitions and
-axioms, no discrete Born rule satisfies certain properties motivated
-by Gleason's theorem with infinitely precise real-number probability~\cite{Gardiner2014}.
-Since the state spaces are now discrete and finite, this suggests
-us to consider a discrete Born rule mapping to a finite number of
-intervals called interval-valued probability~\cite{JamisonLodwick2004,THOS2017}.
-To adopting the idea of interval-valued probability step-by-step,
-before attempting to study quantum interval-valued probability over
-finite fields, we will first review the classical interval-valued
-probability and extend it with the conventional quantum theory.
-\end{comment}
-Despite the great success of cardinal probabilities, it is difficult
-to define their arithmetic operations and expectation values. Since
-they could be defined easily with real-valued probabilities in CQT,
-we attempt to consider real-valued quantum probability measures over
-finite fields (QPMFF) in Sec.~\ref{sec:Toward-IVPM}. In contrast
-to CQT, our Gleason-like conditions over finite fields cannot deduce
-a discrete Born rule in general. This impossible result suggests that
-the discrete and finite state spaces might not be compatible with
-infinitely precise real-valued probability. Thus, no matter whether
-the probability amplitudes are ultimately discrete or continuous,
-we should study imprecise quantum probabilities formulated by quantum
-interval-valued probability measures.
-
-\begin{comment}
-In the classical setting, there are several proposals for ``imprecise
-probabilities'' \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
-Although these proposals differ in some details, they all share the
-fact that the probability $\bar{\mu}(E)$ of an event~$E$ is generalized
-from a single \emph{real number} to an \emph{interval}~$[l,r]$,
-where~$l$ intuitively corresponds to the strength of evidence for
-the event~$E$ and~$1-r$ corresponds to the strength of the evidence
-against the same event. Given a sample space~$\Omega$ and a set
-of intervals~$\mathscr{I}$, like a classical probability measure
-$\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$, a classical interval-valued
-probability measure (IVPM) $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
-needs to satisfy some coherent axioms. By satisfying the convexity
-axiom \cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
-Shapley proved that there is always a classical probability measure
-consistent with the classical IVPM~$\bar{\mu}$ \cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.
-Given any random variable, its expectation value with respect to classical
-probability measures consistent with~$\bar{\mu}$ is consistent with
-its Choquet integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
-with respect to $\bar{\mu}$ \cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
-
-The quantum extension, quantum interval-valued probability measure
-(QIVPM) $\bar{\mu}\colon\events\rightarrow\mathscr{I}$, is a generalization
-of both classical IVPMs $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
-and conventional quantum probability measures $\mu\colon\events\rightarrow[0,1]$
-\cite{THOS2017}, because QIVPMs reduce to classical IVPMs when the
-space of quantum events $\events$ is restricted to mutually commuting
-events and reduce to conventional quantum probability measures when
-mapping to infinitely precise uncountable intervals $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
-While Shapley and Gleason both proved there must be a ``state''
-consistent with any given QIVPM in the reduced cases, in general,
-there exists a QIVPM such that no state is consistent with it. However,
-we found a class of QIVPMs such that all QIVPMs in this class are
-consistent with a non-empty ``ball'' of quantum states whose radius
-is defined by the maximal length of the intervals and recovers the
-original Gleason theorem asymptotically. Similarly, the conventional
-quantum expectation value and the classical Choquet integral are together
-generalized to the quantum interval-valued expectation value. This
-is used to prove an imprecise Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
-which suggests a possible resolution of the Meyer-Mermin debate on
-the impact of finite-precision measurement on the Kochen-Specker theorem
-\cite{PhysRevLett.83.3751,Mermin1999}.
-\end{comment}
-\begin{comment}
-We present a mathematical framework based on quantum interval-valued
-probability measures to study the effect of experimental imperfections
-and finite precision measurements on defining aspects of quantum mechanics
-such as contextuality and the Born rule. While foundational results
-such as the Kochen-Specker and Gleason theorems are valid in the context
-of infinite precision, they fail to hold in general in a world with
-limited resources. Here we employ an interval-valued framework to
-establish bounds on the validity of those theorems in realistic experimental
-environments. In this way, not only can we quantify the idea of finite-precision
-measurement within our theory, but we can also suggest a possible
-resolution of the Meyer-Mermin debate on the impact of finite-precision
-measurement on the Kochen-Specker theorem.
-\end{comment}
-Sec.~\ref{sec:Interval-Uncertainty} starts from reviewing how to
-formulate classical ``imprecise probabilities'' \cite{Shafer1976,GilboaSchmeidler1994,Marinacci1999,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}
-as interval-valued probability measures (IVPMs). Given a classical
-IVPM, its core is the set of the real-valued probability measures
-consistent with it \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997Chinese,Grabisch2016},
-and the expectation value with respect to it is just classical Choquet
-integral \cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}. These
-classical properties can naturally be extended for QIVPMs when we
-extend classical IVPMs to QIVPMs. In Sec.~\ref{sec:Kochen-Specker},
-we utilize the expectation values while proving the finite precision
-variants of the Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
-and establish bounds on its validity in realistic experimental environments.
-In Sec.~\ref{sec:Gleason}, we are able to show that, while a QIVPM
-incorporating the effects of finite precision might not be consistent
-with Gleason's unique state~$\rho$ on all projectors defined on
-a Hilbert space~$\Hilb$ of dimension $D\ge3$, it is possible to
-construct a class of QIVPMs representing bounded resources that is
-parameterized by the size of the intervals, and the original Gleason
-theorem could be recovered for this class of QIVPMs asymptotically.
-
-\begin{sidewaystable}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{tab:organization}Comparison among our models, where the upper
-half of the table lists their quantum mechanical definitions and properties,
-and the lower half of the table lists their computational power.}
-%% ERT block 1 (before LyX tabular)
-\renewcommand{\tabular}{\tabularx{\linewidth}}
-\renewcommand{\endtabular}{\endtabularx} 
-\begin{tabular}{YYYYYYY}
-\toprule 
- & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline
-\midrule
-\midrule 
- & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline
-\midrule 
-States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & Local region in~$\Fpp^{D}$ & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline
-\midrule 
-Likelihood of events is predicted by & Real-valued probability & Possible or impossible & Possible or impossible & Cardinal probability & Real-valued probability, but no sensible Born rule & Interval-valued probability\tabularnewline
-\midrule 
-Expectation value & Defined & Undefined & Formally defined & Undefined &  & Defined\tabularnewline
-\midrule
-\midrule 
- &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline
-\midrule 
-Deutsch's algorithm & Yes & Maybe no & Yes & Yes &  & \tabularnewline
-\midrule 
-Efficiently solve $\usat$ & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline
-\midrule 
-Grover search algorithm & Yes &  &  & Yes &  & \tabularnewline
-\bottomrule
-\end{tabular}% ERT block 2 (after LyX tabular)
-\renewcommand{\tabular}{\ORIGtabular}
-\renewcommand{\endtabular}{\ORIGendtabular} 
-\end{doublespace}
-\end{sidewaystable}
-The organization of this thesis is summarized in Table~\ref{tab:organization},
-and finally, Chapter~\ref{chap:Further-Discussion} contains further
-extended questions, especially, briefly explaining why it might be
-hard to recover Gleason's theorem for general QIVPMs.
-
-\chapter{Conventional Quantum Theory\label{chap:Conventional-Quantum-Theory}}
-
-The part of conventional quantum theory (CQT) used by the quantum
-circuit model is described by the following:
-\begin{enumerate}[label=(\roman{enumi})]
-\item \label{enu:-orthonormal-basis}$D$ orthonormal basis vectors for
-a Hilbert space of dimension~$D$,
-\item \label{enu:probability-amplitude}$D$ complex probability amplitude
-coefficients describing the contribution of each basis vector,
-\item \label{enu:unitary-matrix}a set of probability-conserving unitary
-matrix operators that suffice to describe all required state transformations
-of a quantum circuit,
-\item \label{enu:measurement-framework}and a measurement framework.
-\end{enumerate}
-In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the geometric issues
-raised by the properties~\ref{enu:-orthonormal-basis} and~\ref{enu:probability-amplitude}
-given above for CQT\@. In Sec.~\ref{sec:fuzzy}, we introduce the
-important issues of~\ref{enu:measurement-framework} and the foundations
-of quantum probability space. The expectation values defined in Sec.~\ref{sec:fuzzy}
-will be used to understand the geometry of entangled states in Sec.~\ref{sec:The-geometry-of}.
-The property~\ref{enu:unitary-matrix} directly related to quantum
-circuits will be introduced later in Chapters~\ref{chap:Unrestricted-Finite-Fields}
-and~\ref{chap:DQT=000026DQC} when we dive into quantum algorithms.
-
-\section{Geometrical Structure of States\label{CQC1qubitBloch.sec}}
-
-There are many things that are assumed in CQT, such as the absence
-of zero norm states for non-zero vectors, and the decomposition of
-complex amplitudes into a pair of ordinary real numbers. One also
-typically assumes the existence of a $D$-dimen\-sional Hilbert space
-with an orthonormal basis, allowing us to write \textit{pure} states
-in general as Hilbert space vectors with a Hermitian inner product:
-\begin{equation}
-\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}\,.
-\end{equation}
-Here $\alpha_{i}\in\mathComplex$ are complex probability amplitudes,
-$\VVec{\alpha}\in\mathComplex^{D}$, and the $\{\ket{i}\}$ is an
-orthonormal basis of states obeying $\braket{i}{k}=\delta_{ik}$.
-
-The meaning of this is that any state $\ket{\Phi}=\sum_{i=0}^{D-1}\beta_{i}\ket{i}$
-can be projected onto another state $\ket{\Psi}$ by writing 
-\begin{equation}
-\braket{\Phi}{\Psi}=\sum_{i=0}^{D-1}\beta_{i}^{*}\alpha_{i}\,,
-\end{equation}
-thus quantifying the proximity of the two states. (Here $^{*}$ denotes
-complex conjugation.) This is one of many properties we take for granted
-in continuum quantum mechanics that challenge us in defining a discrete
-quantum geometry. To facilitate the transition to DQT carried out
-in later sections, we concern ourselves first with the properties
-of the simplest possible abstract state object in CQT, the single
-qubit state.
-
-\subsection{Two-dimen\-sional Hilbert Space\label{subsec:Two-dimensional-Hilbert-Space}}
-
-A state in a two-dimen\-sional Hilbert space, known as a qubit, already
-provides access to a wealth of geometric information and context.
-When we write the single qubit state as $\ket{\psi_{1}}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$,
-a convenience for computing probability and relative state properties
-is the normalization condition 
-\begin{equation}
-\left\Vert \psi_{1}\right\Vert ^{2}=\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=\alpha_{0}^{*}\alpha_{0}+\alpha_{1}^{*}\alpha_{1}=1\,,\label{A2.eq}
-\end{equation}
-which identifies $\alpha_{0}$ and $\alpha_{1}\in\mathbb{C}$ as probability
-amplitudes and implies the conservation of probability in the closed
-world spanned by $\left\{ \ket{0},\ket{1}\right\} $. Note that we
-distinguish for future use the \textit{norm}~$\left\Vert \cdot\right\Vert $
-of a vector from the \textit{modulus}~$\left|\cdot\right|$ of a
-complex number. Continuing, we see that if we want only the irreducible
-state descriptions, we must supplement the process of computing \Eq{A2.eq}
-by finding a way to remove the distinction between states that differ
-only by an overall phase transformation $\rme^{\rmi\theta}$, that
-is, $\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$ and $\rme^{\rmi\theta}\alpha_{0}\ket{0}+\rme^{\rmi\theta}\alpha_{1}\ket{1}$
-are representing the same physical state. This can be accomplished
-by the Hopf fibration \cite{Artin1991,Hatcher2001,MosseriDandoloff2001,Hanson2006,Bengtsson2007,wiki:HopfFibration},
-which can be written down as follows: let $\alpha_{0}=x_{0}+\rmi y_{0}$
-and $\alpha_{1}=x_{1}+\rmi y_{1}$. Then \Eq{A2.eq} becomes the
-condition that the four real variables describing a qubit denote a
-point on the three-sphere $\Sphere{3}$ (a 3-manifold) embedded in
-$\R^{4}$: 
-\begin{equation}
-{x_{0}}^{2}+{y_{0}}^{2}+{x_{1}}^{2}+{y_{1}}^{2}=1\,.\label{A5.eq}
-\end{equation}
-
-\begin{figure}[!b]
-\hfill{}\subfloat[]{\centering{}\includegraphics[width=0.48\columnwidth]{hopfS2}}\hfill{}\subfloat[]{\begin{centering}
-\includegraphics[width=0.48\columnwidth]{hopfFibers}
-\par\end{centering}
-}\hfill{}\caption{\label{hopfFibers.fig}(a) The two-sphere~$\Sphere{2}$ represented
-by \Eq{A7.eq}, which is the irreducible space of one-qubit states,
-along with a representative set of points on the sphere. Each single
-point on the sphere in (a) corresponding to a circle in (b), and a
-whole family of circles (the paths of $\rme^{\rmi\theta}$) on the
-three-sphere~$\Sphere{3}$ represents the Hopf fibration, Eq.~(\ref{eq:HopfFibration}).
-Although $\Sphere{3}$ cannot be directly embedded in $\R^{3}$, three-sphere~$\Sphere{3}$
-can be regarded as attaching two three-dimen\-sional balls on two
-sides of two-sphere~$\Sphere{2}$. In this way, each circle in $\Sphere{3}$
-can be represented as a circle in the three-dimen\-sional ball as
-shown in (b). Moreover, points in (a) are color-coded corresponding
-to circles in (b), e.g., one pole contains the red elliptical circle
-that would become an infinite-radius circle by a slightly different
-way to represent $\Sphere{3}$ in $\R^{3}$, and the opposite pole
-corresponds to the large perfectly round red circle at the equator.}
-\end{figure}
-We can reduce 3 degrees of freedom in Eq.~(\ref{A5.eq}) to 2 degrees
-of freedom by effectively removing $\rme^{\rmi\theta}$ (``fibering
-out by the circle $\Sphere{1}$''). The standard form of these maps
-(``the Hopf fibration'') is 
-\begin{eqnarray}
- &  & X=2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
- &  & Y=2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{eq:HopfFibration}\\
- &  & Z=\left|\alpha_{0}\right|^{2}-\left|\alpha_{1}\right|^{2}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,.\nonumber 
-\end{eqnarray}
-By denoting the three-dimen\-sional vector~$\left(X,Y,Z\right)$
-as $\Hat{a}$, Eq.~(\ref{A5.eq}) implies these transformed coordinates
-obeying 
-\begin{equation}
-\left\Vert \Hat{a}\right\Vert ^{2}=X^{2}+Y^{2}+Z^{2}=\left(\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}\right)^{2}=1\label{A7.eq}
-\end{equation}
-and therefore have only two remaining degrees of freedom describing
-all possible distinct one-qubit quantum states. In Fig.~\ref{hopfFibers.fig},
-we illustrate schematically the family of circles \textit{each one
-of which is collapsed to a point}~$\left(\phi,\psi\right)$ on the
-surface $X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
-
-\begin{figure}[!b]
-\begin{centering}
-\hfill{}\subfloat[]{\centering{}\includegraphics[width=0.47\columnwidth]{blochSphere}}\hfill{}\subfloat[]{\begin{centering}
-\includegraphics[width=0.47\columnwidth]{blochSphereArc}
-\par\end{centering}
-}\hfill{}
-\par\end{centering}
-\caption{\label{blochSphere.fig}(a) The conventional Bloch sphere with a unique
-state represented by the point at the red sphere. (b) The geodesic
-shortest-distance arc connecting two one-qubit quantum states.}
-\end{figure}
-The resulting manifold is the two-sphere $\Sphere{2}$ (a 2-manifold)
-embedded in $\R^{3}$. If we choose one of many possible coordinate
-systems describing $\Sphere{3}$ via Eq.~(\ref{A5.eq}) such as 
-\begin{equation}
-\left(x_{0},y_{0},x_{1},y_{1}\right)=\left(\cos\left(\theta+\phi\right)\cos\psi,\,\sin\left(\theta+\phi\right)\cos\psi,\,\cos\left(\theta-\phi\right)\sin\psi,\,\sin\left(\theta-\phi\right)\sin\psi\right)\,,\label{A8a.eq}
-\end{equation}
-where %% $0\leq \theta \leq 2 \pi$,  $-\pi \leq \phi \leq  \pi$, 
-$0\leq\psi\leq\frac{\pi}{2}$, with $0\leq\theta+\phi<2\pi$ and $0\leq\theta-\phi<2\pi$,
-we see that 
-\begin{equation}
-\left(X,Y,Z\right)=\left(\cos\left(2\phi\right)\sin\left(2\psi\right),\,\sin\left(2\phi\right)\sin\left(2\psi\right),\,\cos\left(2\psi\right)\right)\,.\label{A8b.eq}
-\end{equation}
-Thus, the one-qubit state is independent of $\theta$, and we can
-choose $\theta=\phi$ without loss of generality, reducing the formula
-of the unique one-qubit states to $\ket{\psi_{1}}=\rme^{2\rmi\phi}\cos\psi\ket{0}+\sin\psi\ket{1}$,
-and an irreducible state can be represented as a point on a sphere
-called the Bloch sphere, as shown in Fig.~\ref{blochSphere.fig}~(a).
-
-Thus, the geometry of a single qubit reduces to transformations among
-points on $\Sphere{2}$, which can be parametrized in an infinite
-one-parameter family of transformations, one of which is the geodesic
-or minimal-length transformation. Explicitly, given two one-qubit
-states denoted by points $\Hat{a}$ and $\Hat{b}$ on $\Sphere{2}$,
-the shortest rotation carrying $\Hat{a}$ to $\Hat{b}$ is the SLERP
-(spherical linear interpolation) \cite{Shoemake:1985:ARQ:325334.325242,wiki:Slerp}
-\begin{equation}
-S\left(\Hat{a},\Hat{b},t\right)=\Hat{a}\,\frac{\sin((1-t)\omega)}{\sin\omega}\,+\,\Hat{b}\,\frac{\sin(t\omega)}{\sin\omega}\,,\label{slerp.eq}
-\end{equation}
-where $\Hat{a}\cdot\Hat{b}=\cos\omega$. Figure~\ref{blochSphere.fig}~(b)
-illustrates the path traced by a SLERP between two irreducible one-qubit
-states on the Bloch sphere. Because states in CQC are defined by infinite
-precision real numbers, it is not possible, even in principle, to
-make an exact state transition as implied by Fig.~\ref{blochSphere.fig}~(b).
-In practice, one must be content with approximate, typically exponentially
-expensive, transitions from state to state.
-
-\subsection{$D$-dimen\-sional Hilbert Space}
-
-The irreducible states in a $D$-dimen\-sional Hilbert space are
-encoded in a similar family of geometric structures known technically
-as the complex projective space $\CP{D-1}$. We obtain these structures
-starting with the $D$ initially unnormalized complex coefficients
-of the $D$-dimen\-sional basis $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$.
-We then follow the analog of the two-dimen\-sional procedure: conservation
-of probability requires that the norm of the vector $\VVec{\alpha}$
-be normalized to unity: 
-\begin{equation}
-\braket{\Psi}{\Psi}=\left\Vert \VVec{\alpha}\right\Vert ^{2}=\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=1\,.\label{probEq1.eq}
-\end{equation}
-Thus, the initial equation for the geometry of a quantum state describes
-a \textit{topological sphere~}$\Sphere{2D-1}$ embedded in $\mathReal^{2D}$.
-To see this, remember that we can write the real and imaginary parts
-of $\alpha_{i}$ as $\alpha_{i}=x_{i}+\rmi y_{i}$, so 
-\begin{equation}
-\sum_{i=0}^{D-1}|\alpha_{i}|^{2}=\sum_{i=0}^{D-1}{x_{i}}^{2}+{y_{i}}^{2}=1
-\end{equation}
-describes the locus of a $2D$-dimen\-sional real unit vector in
-$\mathReal^{2D}$, which is by definition $\Sphere{2D-1}$, the $(2D-1)$-sphere.
-
-This $\Sphere{2D-1}$ is ambiguous up to the usual overall phase,
-inducing an $\Sphere{1}$ symmetry action, and identifying $\Sphere{2D-1}$
-as an $\Sphere{1}$ bundle, whose base space is the $(D-1)$-complex-dimen\-sional
-projective space $\CP{D-1}$. There are thus $2D-2$ irreducible real
-degrees of freedom ($D-1$ complex degrees of freedom) for a quantum
-state with a $D$-dimen\-sional basis, $\set{\ket{i}}{i=0,\ldots,D-1}$.
-
-In summary, the full space of a $D$-dimen\-sional quantum state,
-including its overall phase defining its relationship to other quantum
-states, is the topological space $\Sphere{2D-1}$. For an isolated
-system, the overall phase is not measurable, and eliminating the phase
-dependence corresponds to identifying $\Sphere{2D-1}$ as a circle
-bundle over the base space $\CP{D-1}$, and therefore $\CP{D-1}$
-defines the $2D-2$ intrinsic, irreducible, degrees of freedom of
-the isolated $D$-dimen\-sional state's dynamics. In mathematical
-notation, this would be written $\Sphere{1}\hookrightarrow\Sphere{2D-1}\rightarrow\CP{D-1}$.
-\begin{comment}
-\todo{Citation? }
-\end{comment}
-For $D=2$, the single qubit, we have $2-1=1$, and the base space
-of the circle bundle is $\CP{1}=\Sphere{2}$, the usual Bloch sphere.
-Note that only for $D=2$ is this actually a sphere-like geometry
-due to an accident of low-dimen\-sional topology.
-
-\subsection{Explicit Generalization of the Hopf Fibration Construction\label{subsec:Explicit-generalization-of}}
-
-For a two-dimen\-sional system, we could easily solve the problem
-of reducing the full unit-norm space to its irreducible components
-$\Hat{a}=\left(X,Y,Z\right)$ characterizing the Bloch sphere. We
-have just argued that essentially the same process is possible for
-$D$-dimen\-sional system: in the abstract argument, we simply identify
-the family of coefficients $\left\{ \alpha_{i}\right\} $ as being
-the same if they differ only by an overall phase $\rme^{\rmi\theta}$.
-However in practice, this is not a construction that is easy to realize
-in a practical computation. We now outline an explicit algorithm for
-accomplishing the reduction to the irreducible $D$-dimen\-sional
-state space $\CP{D-1}$; this construction will turn out to be useful
-for the validation of our discrete results to follow below.
-
-Given a normalized pure state $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$,
-a natural quantity characterizing a $D$-dimen\-sional system is
-its \textit{density matrix}, $\rho=\op{\Psi}{\Psi}$, or 
-\begin{equation}
-\rho=\begin{pmatrix}|\alpha_{0}|^{2} & \alpha_{0}\alpha_{1}^{*} & \cdots & \alpha_{0}\alpha_{D-1}^{*}\\
-\alpha_{1}\alpha_{0}^{*} & |\alpha_{1}|^{2} & \cdots & \alpha_{1}\alpha_{D-1}^{*}\\
-\vdots & \vdots & \ddots & \vdots\\
-\alpha_{D-1}\alpha_{0}^{*} & \cdots & \alpha_{D-1}\alpha_{D-2}^{*} & |\alpha_{D-1}|^{2}
-\end{pmatrix}\,.\label{nqDensity.eq}
-\end{equation}
-We can now use the complex generalization of the classical Veronese
-coordinate system for projective geometry to remove the overall phase
-ambiguity $\rme^{\rmi\theta}$ from the $D$-dimen\-sional states.
-If we take a particular weighting of the elements of the density matrix~$\rho$,
-we can construct a \textit{unit vector} of real dimension $D^{2}$
-with the form: 
-\begin{equation}
-\Hat{a}=\left(|\alpha_{i}|^{2},\ldots,\sqrt{2}\,\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\,\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\right)\,,\label{nqCoords.eq}
-\end{equation}
-where 
-\[
-\Hat{a}\cdot\Hat{a}=\sum_{i=0}^{D-1}\left(\left|\alpha_{i}\right|^{2}\right)^{2}+\sum_{i=0}^{D-1}\sum_{\substack{j=0\\
-j\ne i
-}
-}^{D-1}\left(\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}+\left(\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)\left(\sum_{j=0}^{D-1}\left|\alpha_{j}\right|^{2}\right)=1\,.
-\]
-This construction gives an explicit embedding of the $\left(D-1\right)$-dimen\-sional
-complex, or $\left(2D-2\right)$-dimen\-sional real, object in a
-real space of dimension $D^{2}$. However, this is somewhat subtle
-because the vector is of unit length, so technically the embedding
-space is a sphere of dimension $D^{2}-1$ embedded in $\R^{D^{2}}$.
-For example, the two-dimen\-sional irreducible states could be represented
-in a four-dimen\-sional embedding, but the magnitude of every coordinate
-would be one. Furthermore, the object embedded in the resulting $\Sphere{3}$
-is indeed $\Sphere{2}$ because we can fix one complex coordinate
-to be unity, and let one vary, giving a total of two irreducible dimensions.
-In fact, one must choose \textit{two} coordinate patches, one covering
-one pole of $\Sphere{2}$ with coordinates $\alpha_{0}=1+\rmi0$ and
-$\alpha_{1}=x_{1}+\rmi y_{1}$, and the other patch covering the other
-pole of $\Sphere{2}$ with coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$
-and $\alpha_{1}=1+\rmi0$. %
-\begin{comment}
-\todo{Explain the last part clearer or add a picture.}
-\end{comment}
-
-We finally see that the irreducible $D$-dimen\-sional state space
-$\CP{D-1}$ is described by $D$ projectively equivalent coordinates,
-one of which can always be scaled out to leave $(D-1)$ actual (complex)
-degrees of freedom. We must choose, in turn, $D$ different local
-sets of complex variables defined by taking the value $\alpha_{k}=1$,
-with $k=0,\ldots,D-1$, and allowing the remaining $D-1$ complex
-(or $2D-2$ real) variables to run free. No single set of coordinates
-will work, since the submanifold including $\alpha_{k}=0$ is undefined
-and another coordinate system must be chosen to cover that coordinate
-patch. This is a standard feature of the topology of non-trivial manifolds
-such as $\CP{D-1}$ (see any textbook on geometry~\cite{Berger_1988}).
 
@@
 the set of all projectors on a given Hilbert space is called a quantum
-event space~$\events$. %
-\begin{comment}
-\todo{Check the citation of this part. Did von Neumann really think
-about this when he uses projectors to formulate the quantum theory?}
-\end{comment}
+event space~$\events$.
 
@@
 expectation values because we can pullback an observable to a classical
-random variable, and the expectation values are invariant.%
-\begin{comment}
-\todo{ Add interpretation!}
-\end{comment}
+random variable, and the expectation values are invariant.
 
@@
 \end{equation}
-\begin{comment}
-\todo{Put the definition of indicator function!}
-\end{comment}
 \end{definition}
@@
 \end{table}
-
-\section{The Geometry of Entanglement\label{sec:The-geometry-of}}
-
-Entanglement may be regarded as one of the main characteristics distinguishing
-quantum from classical mechanics. Entanglement involves quantum correlations
-such that the measurement outcomes in one subsystem are related to
-the measurement outcomes in another one. To discuss entanglement,
-we consider a $D$-dimen\-sional quantum system composed of $n$-qubit
-subsystems, i.e., $D=2^{n}$. A pure state of the total system $\ket{\Psi}$
-is said to be entangled if it cannot be written as a product of states
-of each subsystem \cite{peres1995quantum,544199,Jaeger2007}. That
-is, a state $\ket{\Psi}$ is entangled if $\ket{\Psi}\ne\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}$,
-where $\ket{\psi_{j}}$ refers to an arbitrary state of the $j$-th
-qubit, and $\otimes$ represents the tensor product. This is equivalent
-to saying that if one calculates the reduced density operator~$\rho_{j}$
-of the $j$-th subsystem by tracing out all the other subsystems,
-\begin{equation}
-\rho_{j}=\Tr_{\left\{ 1,\ldots,j-1,j+1,\ldots,n\right\} }\left(\rho\right)\,,\label{eq:partialTrace}
-\end{equation}
-with $j=1,\ldots,n$ and $\rho=\op{\Psi}{\Psi}$, the normalized state~$\ket{\Psi}$
-is entangled if and only if at least one subsystem state is \textit{mixed},
-i.e., $\Tr_{j}\left(\rho_{j}^{2}\right)<1$ \cite{544199,Jaeger2007}.
-
-The reduced density operator could be expressed explicitly by the
-expectation value of the Pauli operators. Therefore, we can decide
-whether a system is entangled or not by examining these expectation
-values. Let $\jthSubsystem{\sigma}[\eta]{j}$ be the Pauli operators
-acting on the $j$-th spin~\cite{544199},
-\begin{equation}
-\jthSubsystem{\sigma}[\eta]{j}=\overbrace{\sigma_{0}\otimes\cdots\otimes\sigma_{0}\otimes\underbrace{\sigma_{\eta}}_{j^{\textrm{th}}\textrm{ factors}}\otimes\sigma_{0}\otimes\cdots\otimes\sigma_{0}}^{n\textrm{ factors}}\,,\label{pauli3}
-\end{equation}
-and $\expval{\jthSubsystem{\sigma}[\eta]{j}}$ be the corresponding
-expectation value, $\expval{\jthSubsystem{\sigma}[\eta]{j}}=\melem{\Psi}{\jthSubsystem{\sigma}[\eta]{j}}{\Psi}$,
-where $\eta=x$, $y$, and $z$, and
-\begin{subequations}
-\begin{align}
-\sigma_{0} & =\op{0}{0}+\op{1}{1}\,, & \sigma_{x} & =\op{1}{0}+\op{0}{1}\,,\\
-\sigma_{y} & =\rmi\op{1}{0}-\rmi\op{0}{1}\,, & \sigma_{z} & =\op{0}{0}-\op{1}{1}\,.
-\end{align}
-\end{subequations}
-For example, given a normalized two-qubit system $\ket{\Psi}=\alpha_{00}\ket{00}+\alpha_{01}\ket{01}+\alpha_{10}\ket{10}+\alpha_{11}\ket{11}$,
-some of its expectation values are
-\begin{equation}
-\begin{aligned}\expval{\jthSubsystem{\sigma}[0]{1}} & =\left|\alpha_{00}\right|^{2}+\left|\alpha_{01}\right|^{2}+\left|\alpha_{10}\right|^{2}+\left|\alpha_{11}\right|^{2}=1\,,\\
-\expval{\jthSubsystem{\sigma}[x]{1}} & =\alpha_{00}\alpha_{10}^{*}+\alpha_{01}\alpha_{11}^{*}+\alpha_{10}\alpha_{00}^{*}+\alpha_{11}\alpha_{01}^{*}\,,\\
-\expval{\jthSubsystem{\sigma}[y]{1}} & =-\alpha_{00}\alpha_{10}^{*}\rmi-\alpha_{01}\alpha_{11}^{*}\rmi+\alpha_{10}\alpha_{00}^{*}\rmi+\alpha_{11}\alpha_{01}^{*}\rmi\,,\\
-\expval{\jthSubsystem{\sigma}[z]{1}} & =\left|\alpha_{00}\right|^{2}+\left|\alpha_{01}\right|^{2}-\left|\alpha_{10}\right|^{2}-\left|\alpha_{11}\right|^{2}\,.
-\end{aligned}
-\end{equation}
-Then, the reduced density operator~$\rho_{1}$ can be expressed by
-these expectation values as following:
-\begin{equation}
-\begin{aligned}\rho_{1}= & \Tr_{\left\{ 2\right\} }\left(\op{\Psi}{\Psi}\right)\\
-= & \left(\left|\alpha_{00}\right|^{2}+\left|\alpha_{01}\right|^{2}\right)\op{0}{0}+\left(\alpha_{00}\alpha_{10}^{*}+\alpha_{01}\alpha_{11}^{*}\right)\op{0}{1}\\
- & +\left(\alpha_{10}\alpha_{00}^{*}+\alpha_{11}\alpha_{01}^{*}\right)\op{1}{0}+\left(\left|\alpha_{10}\right|^{2}+\left|\alpha_{11}\right|^{2}\right)\op{1}{1}\\
-= & \frac{\expval{\jthSubsystem{\sigma}[0]{1}}\sigma_{0}+\expval{\jthSubsystem{\sigma}[x]{1}}\sigma_{x}+\expval{\jthSubsystem{\sigma}[y]{1}}\sigma_{y}+\expval{\jthSubsystem{\sigma}[z]{1}}\sigma_{z}}{2}\,.
-\end{aligned}
-\end{equation}
-In general, %
-\begin{comment}
-\todo{Ask Gerardo why? }
-\end{comment}
-the reduced density operator~$\rho_{j}$ of the $j$-th subsystem
-can always be expressed as
-\begin{equation}
-\rho_{j}=\frac{1}{2}\sum\limits _{\eta=0,x,y,z}\expval{\jthSubsystem{\sigma}[\eta]{j}}\sigma_{\eta}\,,\label{eq:reducedDensityOperator}
-\end{equation}
-and its coefficients can be summarized as the vector
-\begin{equation}
-{\bf X}_{j}=\left(\expval{\jthSubsystem{\sigma}[x]{j}},\expval{\jthSubsystem{\sigma}[y]{j}},\expval{\jthSubsystem{\sigma}[z]{j}}\right)\in\mathbb{R}^{3}\label{eq:geometricRepresentationState}
-\end{equation}
-that allows a geometric representation of each reduced state in $\mathbb{R}^{3}$,
-satisfying $0\le\left\Vert {\bf X}_{j}\right\Vert \le1$. Since $\Tr_{j}\left(\rho_{j}^{2}\right)=\frac{1}{2}\left(1+\left\Vert {\bf X}_{j}\right\Vert ^{2}\right)$,
-the state $\ket{\Psi}$ is entangled if $\left\Vert {\bf X}_{j}\right\Vert <1$
-for at least one $j$, represented by a point \emph{inside} the corresponding
-local Bloch sphere embedded in $\mathbb{R}^{3}$. Therefore, one may
-consider $\ket{\Psi}$ to be maximally entangled if $\left\Vert {\bf X}_{j}\right\Vert =0$
-for all $j$. On the other hand, the state $\ket{\Psi}$ is unentangled
-(i.e., a product state) if $\left\Vert {\bf X}_{j}\right\Vert =1$
-for all $j$, corresponding to points lying on the surface of the
-Bloch spheres.
-
-A natural geometric measure of multipartite entanglement is obtained
-by defining the \emph{purity of a state relative to a set of observables}
-\cite{BKOV2003,BKOSV2004}. If the set is chosen to be the set of
-\emph{all local observables}, i.e., corresponding to each of the subsystems
-that compose the actual system, one recovers the standard notion of
-entanglement for multipartite systems. For example, if the system
-consists of $n$ qubits, we obtain a measure of conventional entanglement
-by calculating the purity relative to the semi-simple Lie algebra~$\fh$
-spanned by $\{\jthSubsystem{\sigma}[x]{1},\jthSubsystem{\sigma}[y]{1},\jthSubsystem{\sigma}[z]{1},\ldots,\jthSubsystem{\sigma}[x]{n},\jthSubsystem{\sigma}[y]{n},\jthSubsystem{\sigma}[z]{n}\}$,
-\begin{equation}
-P_{\fh}=\frac{1}{n}\sum\limits _{j=1}^{n}\sum\limits _{\eta=x,y,z}\expval{\jthSubsystem{\sigma}[\eta]{j}}^{2}=\frac{1}{n}\sum\limits _{j=1}^{n}\left\Vert {\bf X}_{j}\right\Vert ^{2}\,.\label{purityMeasure.eq}
-\end{equation}
-Since the norm of the geometric representation state $\left\Vert {\bf X}_{j}\right\Vert $
-defined in Eq.~(\ref{eq:geometricRepresentationState}) is between
-$0$ and $1$, we have $0\leq P_{\fh}\leq1$, where $\frac{1}{n}$
-in Eq.~(\ref{purityMeasure.eq}) is just a normalization factor.
-All the product states of the form $\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{n}}$,
-have maximum purity (i.e., $P_{\fh}=1$). Other states such as the
-Greenberger-Horne-Zeilinger state $\ket{\Psi}=\ket{\mathsf{GHZ}_{n}}=\frac{1}{\sqrt{2}}\left(\ket{0}\otimes\cdots\otimes\ket{0}+\ket{1}\otimes\cdots\otimes\ket{1}\right)$
-are (maximally) entangled relative to the set of local observables
-(i.e., $P_{\fh}=0$).
-
-Different entanglement measures are obtained when an algebra~$\fh$
-different from the local observables is chosen. An obvious example
-is given by the set of all observables. In this case, the purity takes
-its maximum value independently of the pure quantum state \cite{BKOV2003,BKOSV2004},
-expressing the fact that any state is a generalized coherent state
-of the Lie algebra of all observables.
-
-\chapter{Quantum Theories and Computing over Unrestricted Finite Fields\label{chap:Unrestricted-Finite-Fields}}
-
-\section{Fundamentals of Finite Fields\label{sec:background}}
-
-\subsection{Background}
-
-A field~$\mathbb{F}$ is an algebraic structure consisting of a set
-of elements equipped with the operations of addition, subtraction,
-multiplication, and division \cite{DummitFoote2004,fieldtheory.ref,numtheory.ref}.
-Fields may contain an infinite or a finite number of elements. The
-rational~$\mathbb{Q}$, real~$\mathbb{R}$, and complex numbers~$\mathbb{C}$
-are examples of infinite fields, while the set $\mathbb{F}_{3}=\{0,1,2\}$,
-under multiplication and addition modulo $3$, is an example of a
-finite field.
-
-There are two distinguished elements in a field, the addition identity
-$0$, and the multiplication identity $1$. Given the field~$\mathbb{F}$,
-the closed operations of addition~$+$, and multiplication~$\gmult$,
-satisfy the following set of axioms:
-\begin{enumerate}
-\item $\mathbb{F}$ is an Abelian group under the addition operation~$+$
-(additive group).
-\item The multiplication operation~$\gmult$ is associative and commutative.
-The field has a multiplicative identity and the property that every
-nonzero element has a multiplicative inverse.
-\item Distributive laws: for all $a,b,c\in\mathbb{F}$, 
-\begin{align}
-a\gmult(b+c) & =a\gmult b+a\gmult c\,, & (b+c)\gmult a & =b\gmult a+c\gmult a\,.
-\end{align}
-\end{enumerate}
-\noindent From now on, unless specified, we will omit the symbol~$\gmult$
-whenever we multiply two elements of a field.
-
-Finite fields of $q$ elements, $\Fq=\{0,\ldots,q-1\}$, will play
-a special role in this work. A simple explicit example is $\mathbb{F}_{3}$
-with the following addition and multiplication tables: 
-\begin{align*}
-\begin{array}{c|ccc}
-+ & 0 & 1 & 2\\[0.1in]
-\hline 0 & 0 & 1 & 2\\
-1 & 1 & 2 & 0\\
-2 & 2 & 0 & 1
-\end{array} &  & \begin{array}{c|ccc}
-\gmult & 0 & 1 & 2\\[0.1in]
-\hline 0 & 0 & 0 & 0\\
-1 & 0 & 1 & 2\\
-2 & 0 & 2 & 1
-\end{array}
-\end{align*}
-
-\subsection{Cyclic Properties of Finite Fields\label{subsec:Cyclic-Properties-of}}
-
-The characteristic of a field is the least positive integer~$m$
-such that $m=1+1+1+\cdots+1=0$, and if no such $m$ exists we say
-that the field has characteristic zero (which is the case for $\mathbb{R}$
-for example). It turns out that if the characteristic is non-zero,
-it must be a prime~$p$. For every prime~$p$ and positive integer~$r$
-there is a finite field~$\Fpx{p^{r}}$ of size $q=p^{r}$ and characteristic~$p$,
-which is unique up to field isomorphism \cite{Artin1991,DummitFoote2004}.
-The exponent $r$ is known as the \emph{degree} of the field over
-its prime subfield~\cite{GT.ref}.\footnote{Fields $\ff{q}$ where $q$ is a power of a prime $p$, i.e., $q=p^{r}$,
-are known as Galois fields.} If the characteristic $p$ is an arbitrary prime number, we call
-the field \emph{unrestricted}.
-
-For every $a\in\Fq$, $a\neq0$, then $a^{q-1}=1$, implying the Frobenius
-endomorphism (also a consequence of Fermat's little theorem) $a^{q}=a$,
-which in turn permits us to write the multiplicative inverse of any
-non-zero element in the field as $a^{-1}=a^{q-2}$, since $a^{q-2}a=a^{q-1}=1$.
-Every subfield of the field~$\Fq$, of size $q=p^{r}$, has $p^{r'}$
-elements with some $r'$ dividing $r$, and for a given $r'$ it is
-unique.
-
-\section{Modal Quantum Theory\label{modalquantum}}
-
-Recently, Schumacher and Westmoreland~\cite{Schumacher2012-SCHMQT,SchumacherWestmoreland2010}
-and Chang et al.~\cite{doi:10.1142/S0217984913500644,1751-8121-47-40-405304}
-defined versions of quantum theory over \textit{unrestricted} finite
-fields, which they call modal quantum theories (MQT) or Galois field
-quantum theories. Such theories retain several key quantum characteristics
-including notions of superposition, interference, entanglement, and
-mixed states, along with time evolution using invertible linear operators,
-complementarity of incompatible observables, exclusion of local hidden
-variable theories, impossibility of cloning quantum states, and the
-presence of natural counterparts of quantum information protocols
-such as superdense coding and teleportation. These modal theories
-are obtained by collapsing the Hilbert space structure over the field
-of complex numbers to that of a vector space over an \emph{unrestricted}
-finite field. In the resulting structure, all non-zero vectors represent
-valid quantum states, and the evolution of a closed quantum system
-is described by \emph{arbitrary} invertible linear maps.
-
-Specifically, consider a one-qubit system with basis vectors $\ket{0}$
-and~$\ket{1}$. In conventional quantum theory, there exists an infinite
-number of states for a qubit of the form $\alpha_{0}\ket{0}+\alpha_{1}\ket{1}$,
-with $\alpha_{0}$ and $\alpha_{1}$ elements of the underlying field
-of complex numbers subject to the normalization condition $|\alpha_{0}|^{2}+|\alpha_{1}|^{2}=1$.
-Moving to a finite field immediately limits the set of possible states
-as the coefficients~$\alpha_{0}$ and~$\alpha_{1}$ are now drawn
-from a finite set. In particular, in the field $\ff{2}=\{0,1\}$ of
-Booleans, there are exactly four possible vectors: the zero vector,
-the vector~$\ket{0}$, the vector $\ket{1}$, and the vector $\ket{0}+\ket{1}=\ket{+}$.
-Since the zero vector is considered non-physical, a one-qubit system
-can be in one of only three states. The dynamics of these one-qubit
-states is realized by any invertible linear map, i.e., by any linear
-map that is guaranteed never to produce the zero vector from a valid
-state. There are exactly $6$ such maps, and their matrix representations
-with respect to the standard basis are:
-\begin{subequations}\label{eq:MQT-dynamics}
-\begin{align}
-\sigma_{0} & =\begin{pmatrix}1 & 0\\
-0 & 1
-\end{pmatrix}\,, & S & =\begin{pmatrix}1 & 0\\
-1 & 1
-\end{pmatrix}\,, &  & \begin{pmatrix}0 & 1\\
-1 & 1
-\end{pmatrix}\,,\\
-\sigma_{x} & =\begin{pmatrix}0 & 1\\
-1 & 0
-\end{pmatrix}\,, & S^{\dagger} & =\begin{pmatrix}1 & 1\\
-0 & 1
-\end{pmatrix}\,, &  & \begin{pmatrix}1 & 1\\
-1 & 0
-\end{pmatrix}\,.
-\end{align}
-\end{subequations}
-
-For example, 
-\begin{align}
-S\ket{0} & =\begin{pmatrix}1 & 0\\
-1 & 1
-\end{pmatrix}\begin{pmatrix}1\\
-0
-\end{pmatrix}=\begin{pmatrix}1\\
-1
-\end{pmatrix}=\ket{+}\,, & S\ket{+} & =\begin{pmatrix}1 & 0\\
-1 & 1
-\end{pmatrix}\begin{pmatrix}1\\
-1
-\end{pmatrix}=\begin{pmatrix}1\\
-0
-\end{pmatrix}=\ket{0}\,.\label{eq:MQT-dynamics-apply}
-\end{align}
-This set of maps is clearly quite impoverished compared to the full
-set of one-qubit unitary maps in conventional quantum theory. In particular,
-it does not include the Hadamard transformation. However, this set
-also includes non-unitary maps such as $S$ and $S^{\dagger}$ that
-are not allowed in conventional quantum computation.
-
-Measurement in the standard basis is straightforward: measuring $\ket{0}$
-or $\ket{1}$ deterministically produces the same state while measuring
-$\ket{+}$ nondeterministically produces $\ket{0}$ or $\ket{1}$
-with no assigned probability distribution. When measuring an arbitrary
-state~$\ket{\phi}\in\left\{ \ket{0},\ket{1},\ket{+}\right\} $ in
-other bases $\left\{ \ket{\psi_{0}},\ket{\psi_{1}}\right\} $, we
-first represent $\ket{\phi}$ as the linear combination of the basis
-vectors $\beta_{0}\ket{\psi_{0}}+\beta_{1}\ket{\psi_{1}}$, where
-$\beta_{0}$ and $\beta_{1}$ are elements in the field~$\ff{2}$.
-If $\beta_{i}$ is zero, measuring $\ket{\phi}$ is impossible to
-produce $\ket{\psi_{i}}$; otherwise, measuring $\ket{\phi}$ is possible
-to produce $\ket{\psi_{i}}$. Since only possibility and impossibility
-is predicted by the theory, modal quantum theories are named after
-these ``modal'' concepts.
-
-Notice that the measurement process is complicated by the fact that
-the possibility to produce a basis vector~$\ket{\psi_{i}}$ depending
-on the measurement basis. For example, measuring $\ket{+}$ is possible
-to produce $\ket{0}$ in the standard basis $\left\{ \ket{0},\ket{1}\right\} $
-but is impossible to produce $\ket{0}$ in another basis $\left\{ \ket{+},\ket{0}\right\} $.
-In contrast, when measuring a state~$\ket{\phi}$ in CQT, the probability
-to produce a basis vector~$\ket{\psi_{i}}$ is completely determined
-by $\ket{\psi_{i}}$ and $\ket{\phi}$ no matter $\ket{\psi_{i}}$
-is in which measurement basis. The measurement bases play some roles
-only when we want to simulate the prediction of CQT by a classical
-hidden variable theory. If the prediction of a hidden variable theory
-depends on the measurement bases, this hidden variable theory is called
-\emph{contextual}. The measurement process itself in MQT depending
-on the bases demonstrates that MQT is more contextual than CQT. Despite
-this kind of ``supercontextuality'' of MQT, its computational model,
-modal quantum computing (MQC), having ``supernatural'' computational
-power is also far from conventional quantum computing as we will describe
-next.
-
-\section{Modal Quantum Computing\label{modalquantumcomputing}}
-
-To understand the computational implications of the modal quantum
-theory defined over the field $\ff{2}$ of Booleans, we developed
-a quantum computing model and established its correspondence to a
-classical model of logical programming with a feature that has quantum-like
-behavior~\cite{finiteQC}. In a conventional logic program, answers
-produced by different execution paths are collected in a sequence
-with \emph{no} interference. However, in this modal quantum computing
-model over $\ff{2}$, these answers may interfere destructively with
-one another.
-
-Our computations with this ``toy'' modal quantum theory showed that
-it possesses ``supernatural'' computational power. For example,
-one can solve a black box version of the \usat\ problem~\cite{usat}
-in a way that outperforms conventional quantum computing. The classical
-\usat\ problem (also known as $\lang{USAT}$~\cite{AroraBarak2009}
-or $\lang{UNAMBIGUOUS-SAT}$) %
-\begin{comment}
-\todo{Add citation about where these two names come from. }
-\end{comment}
-is the problem of deciding whether a given Boolean formula has a satisfying
-assignment, assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
-This problem is, in a precise sense~\cite{Valiant198685}, just as
-hard as the general satisfiability problem and hence all problems
-in the $\NP$ complexity class. Our black-box version of the \usat\ problem
-replaces the Boolean formula with an arbitrary black box. Solutions
-to this generalized problem can be used to solve an unstructured database
-search of size $N$ using $O\left(\log N\right)$ black box evaluations
-by binary search on the database. This algorithm then outperforms
-the known asymptotic bound $O\left(\sqrt{N}\right)$ for unstructured
-database search in conventional quantum computing.
-
-\begin{figure}[b]
-\[
-\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \gate{~S^{\dagger}~} & \ctrl{3} & \gate{~S^{\dagger}~} & \multimeasureD{3}{\text{measure}}\\
-\lstick{x_{1}=\ket{0}} & \multigate{2}{\otimes S} & \ghost{\uf} & \multigate{2}{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
-\lstick{\ldots} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
-\lstick{x_{n}=\ket{0}} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}
-}
-\]
-\caption{\label{fig:alg}Circuit for the black box \usat\ in modal quantum
-theory over the field $\ff{2}$. For further notation see text.}
-\end{figure}
-We can prove the unreasonable power of the arbitrary-function \usat\ starting
-with a classical function $f\colon\boolt^{n}\rightarrow\boolt$ that
-takes $n$ bits and returns at most one \btrue\ result. To build
-a quantum algorithm, $f$ is first represented as the Deutsch quantum
-black box~$\uf$ with \cite{Deutsch1985,544199} 
-\begin{equation}
-\uf\ket{y}\ket{\overline{x}}=\ket{y\oplus f\left(\overline{x}\right)}\ket{\overline{x}}=\begin{cases}
-\ket{y}\ket{\overline{x}} & \textrm{if }f\left(\overline{x}\right)=\bfalse\,;\\
-\ket{\mathsf{not}\left(y\right)}\ket{\overline{x}} & \textrm{if }f\left(\overline{x}\right)=\btrue\,,
-\end{cases}\label{eq:DeutschBox}
-\end{equation}
-where $\overline{x}$ denotes a sequence $x_{1},x_{2},\ldots,x_{n}$
-of $n$ bits, $\oplus$ is exclusive disjunction, and $0$ and $1$
-are identified as $\bfalse$ and $\btrue$, respectively. Then, we
-can give an algorithm (see Fig.~\ref{fig:alg}) taking as input such
-a classical function that decides, deterministically and in a constant
-number of black box evaluations, whether $f$ is satisfiable or not:
-
-\begin{case}$f$ is unsatisfiable; the measurement deterministically
-produces $\ket{0}\ket{\overline{0}}$.\end{case}
-
-\begin{proof}%
-\begin{comment}
-\todo{This part use $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$
-while previous parts use $\ket{\Psi}=\ket{\psi_{1}}\cdots\ket{\psi_{j}}\cdots\ket{\psi_{n}}$.
-Moreover, the ``bar'' is heavily used in QIVPM discussion later,
-so maybe not using bar here???? }
-\end{comment}
-The state is initialized to $\ket{0}\ket{\overline{0}}$, with $\ket{\overline{0}}=\ket{0}\ket{0}\cdots\ket{0}$,
-i.e., the tensor product of $n$ $\ket{0}$ states. As Eq.~(\ref{eq:MQT-dynamics-apply}),
-applying the map $S$ to each qubit in the second component of the
-state produces $\ket{0}\ket{\overline{+}}$ where $\ket{\overline{+}}$
-denotes the sequence $\ket{+}\ldots\ket{+}$ of length $n$. Applying
-$\uf$ to the entire state has no effect since $U_{f}$ is the identity
-when $f$ is unsatisfiable. Applying $S$ to each qubit in the second
-component of the state produces $\ket{0}\ket{\overline{0}}$, and
-applying $S^{\dagger}$ to the first component leaves the state unchanged.
-As the first component of the state is $0$, applying the map $\sigma_{0}$
-(which is the identity) leaves the state unchanged. %
-\begin{comment}
-\todo{Control-not needs to be defined and explained in Sec.~\ref{subsec:Quantum-Circuits}
-}
-\end{comment}
-Applying $S^{\dagger}$ to the first component leaves the state unchanged.
-Measuring the state will deterministically produce $\ket{0}\ket{\overline{0}}$.\end{proof}
-
-\begin{case}$f$ is satisfiable; the measurement produces some state
-other than $\ket{0}\ket{\overline{0}}$.\end{case}
-
-\begin{proof}Assume the function $f$ is satisfiable at some input
-$a_{1},a_{2},\ldots,a_{n}$ denoted $\overline{a}$, and where $\ket{\overline{a}}=\ket{a_{1}}\ldots\ket{a_{n}}$.
-In the second step, the state becomes $\ket{0}\ket{\overline{+}}$
-as above. We can write this state as $\ket{0}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
-Applying $U_{f}$ produces $\ket{1}\ket{\overline{a}}+\Sigma_{\overline{x}\neq\overline{a}}\ket{0}\ket{\overline{x}}$.
-We can rewrite this state as $\ket{+}\ket{\overline{a}}+\Sigma_{\overline{x}}\ket{0}\ket{\overline{x}}=\ket{+}\ket{\overline{a}}+\ket{0}\ket{\overline{+}}$,
-where the summation is now over all vectors (notice that $\ket{0}\ket{\overline{a}}+\ket{0}\ket{\overline{a}}$
-is the zero vector). Applying $S$ to each qubit in the second component
-produces $\ket{+}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
-Applying $S^{\dagger}$ to the first component produces: $\ket{1}\ket{\overline{S(a)}}+\ket{0}\ket{\overline{0}}$.
-Applying control-not gate, which applies $\sigma_{0}$ or $\sigma_{x}$
-on the second component depending on the first component of the state,
-and produces 
-\begin{equation}
-\ket{1}\left(\sigma_{x}\ket{\overline{S(a)}}\right)+\ket{0}\left(\sigma_{0}\ket{\overline{0}}\right)=\ket{1}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}\,.
-\end{equation}
-Applying $S^{\dagger}$ to the first component produces $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$.
-For the measurement of $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}+\ket{0}\ket{\overline{0}}$
-to be guaranteed to never be $\ket{0}\ket{\overline{0}}$, we need
-to verify that $\ket{+}\ket{\overline{\mathsf{not}\left(S(a)\right)}}$
-has one occurrence $\ket{0}\ket{\overline{0}}$. %
-\begin{comment}
-\todo{The following need to be rewritten. }
-\end{comment}
-This can be easily proved as follows. Since each $a_{i}$ is either
-0 or 1, then each $S(a_{i})$ is either $+$ or $1$, and hence each
-$\mathsf{not}\left(S(a_{i})\right)$ is either~$+$ or~$0$. The
-result follows since any state with a combination of $+$ and $0$,
-when expressed in the standard basis, would consist of a superposition
-containing the state $\ket{0\ldots}$.\end{proof}
-
-\chapter{Quantum Theories and Computing over Complexified Finite Fields\label{chap:DQT=000026DQC}}
-
-\section{Discrete Quantum Theory (I)\label{discretequantumtheoryI}}
-
-\subsection{\label{subsec:Complexified-Finite-Fields}Complexified Finite Fields}
-
-Our next objective is to develop more realistic discrete quantum theory
-variants that exclude ``supernatural'' algorithms such as the one
-presented above. Our first such plausible framework~\cite{HOSW2011}
-is based on complexifiable finite fields. To incorporate complex numbers
-for quantum amplitudes, we exploit the fact that the polynomial $x^{2}+1$
-is \emph{irreducible} ($x^{2}+1=0$ has no solution) over a prime
-field $\ff{p}$ with $p$ odd if and only if $p$ is of the form $4\ell+3$,
-with $\ell$ a non-negative integer \cite{Artin1991,DummitFoote2004,numtheory.ref}.
-For example, when $p=3$, $x$ could be $0$ or $\pm1$. Since $0^{2}+1\ne0$
-and $\left(\pm1\right)^{2}+1\ne0$, none of the element in $\ff{3}$
-solves $x^{2}+1=0$, and $x^{2}+1$ is irreducible over $\ff{3}$.
-In contrast, $2^{2}+1=0$ over $\ff{5}$ so that $x^{2}+1$ is reducible.
-
-Since $x^{2}+1=0$ has no solution in any field $\ff{p}$ with $p=4\ell+3$,
-we can extend $\ff{p}$ to a field~$\ff{p^{2}}$ whose elements can
-be viewed as discrete complex numbers with the real and imaginary
-parts in~$\ff{p}$. Therefore, every element in $\ff{p^{2}}$ can
-be expressed as $a+b\rmi$ with $a,b\in\ff{p}$, and a $\ff{p^{2}}$
-is called a complexified finite field. Since the multiplicative group
-of any finite field is cyclic~\cite{Artin1991}, there is a generator
-$g\in\ff{p^{2}}$ such that every non-zero element $a+b\rmi$ can
-also be represented as the power of a generator, i.e., $a+b\rmi=g^{j}$
-for some $j$. For example, $1-\rmi$ is a generator in $\Fppx{3}$
-so another element $1+\rmi\in\Fppx{3}$ can be expressed as $1+\rmi=1-3\rmi-3+\rmi=\left(1-\rmi\right)^{3}$.
-All possible choices of generators in $\ff{3^{2}}$ are listed in
-Table~\ref{tab:Generators-in-F9}.
-\begin{table}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{tab:Generators-in-F9}Generators in $\ff{3^{2}}$}
-\begin{tabular}{ccccccccc}
-\toprule 
-$j$ & $0$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$\tabularnewline
-\midrule
-$\left(1+\rmi\right)^{j}$ & $1$ & $1+\rmi$ & $-\rmi$ & $1-\rmi$ & $-1$ & $-1-\rmi$ & $\rmi$ & $-1+\rmi$\tabularnewline
-$\left(1-\rmi\right)^{j}$ & $1$ & $1-\rmi$ & $\rmi$ & $1+\rmi$ & $-1$ & $-1+\rmi$ & $-\rmi$ & $-1-\rmi$\tabularnewline
-$\left(-1+\rmi\right)^{j}$ & $1$ & $-1+\rmi$ & $\rmi$ & $-1-\rmi$ & $-1$ & $1-\rmi$ & $-\rmi$ & $1+\rmi$\tabularnewline
-$\left(-1-\rmi\right)^{j}$ & $1$ & $-1-\rmi$ & $-\rmi$ & $-1+\rmi$ & $-1$ & $1+\rmi$ & $\rmi$ & $1-\rmi$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{doublespace}
-\end{table}
-
-In Table~\ref{tab:Generators-in-F9}, one can notice that $\left(a+b\rmi\right)^{3}=a-b\rmi$.
-In general, the $p$-th power $\left(a+b\rmi\right)^{p}=a-b\rmi$
-is called the \emph{Frobenius automorphism} and acts like complex
-conjugation $\left(a+b\rmi\right)^{*}=a-b\rmi$ \cite{Artin1991,grove2002classical,DummitFoote2004}.
-Then, we define the \emph{field norm} $\fnorm{\cdot}\colon\Fpp\rightarrow\Fp$
-as an element $a+\rmi b$ multiplying its complex conjugation $\left(a+b\rmi\right)^{*}$~\cite{wiki:FieldNorm},
-\begin{equation}
-\fnorm{a+\rmi b}=\left(a+b\rmi\right)\left(a+b\rmi\right)^{*}=\left(a+b\rmi\right)^{p+1}=a^{2}+b^{2}\,,\label{fieldnorm.eq}
-\end{equation}
-where the square root in the usual definition of the norm is avoided
-because, unlike the continuous case, the square root does not always
-exist, and the field norm of an element $\fnorm{\cdot}$ should be
-the direct counterpart of the norm-squared $\left|\cdot\right|^{2}$
-in the conventional quantum theory. For example, the field norm of
-every generator~$g$ in Table~\ref{tab:Generators-in-F9} is the
-same number $\fnorm{g}=g^{3+1}=-1$. In fact, these four generators
-are the only elements in $\ff{3^{2}}$ whose field norm is $-1\in\ff{3}$.
-Generally, given any $c\in\Fp$, let $\fnorm*{\left\{ c\right\} }$
-denote the set of elements whose field norm is $c$, i.e., $\fnorm*{\left\{ c\right\} }=\set{\alpha\in\Fpp}{\fnorm{\alpha}=c}$.
-The set $\fnorm*{\left\{ c\right\} }$ is the discrete analog of phase-equivalence
-under the modulus-preserving transformation $z\rightarrow\rme^{\rmi\phi}z$,
-and the number of its elements is characterized by the following proposition.
-
-\begin{prop}\label{appH.sec}Given any $c\in\Fp$, the number of
-elements in $\fnorm*{\left\{ c\right\} }$ is $p+1$, i.e., there
-are always $p+1$ elements in $\Fpp$ whose field norm is $c$.\end{prop}
-
-\begin{proof}To prove Proposition~\ref{appH.sec}, we start by proving
-$\fnorm*{\left\{ c\right\} }$ is non-empty. Consider a special case
-of the field norm $\fnorm{.}$, namely the real quadratic map $Q\left(e\right)=e^{2}$
-taking an arbitrary element $e\in\Fp$ to its square in the field.
-Since $\left(\pm1\right)^{2}=1$, the image of $Q\left(e\right)$
-has only $\frac{p+1}{2}$ elements in $\Fp$, including the zero element.
-We let $A$ be the image of the map $Q\left(e\right)$ in $\Fp$,
-and note that the set $A_{c}$ resulting from displacing an element
-$x=b^{2}$ of $A$ to $c-x=c-b^{2}$ with $c\in\Fp$ also has $\frac{p+1}{2}$
-elements because the result is simply a cyclic shift of element labels.
-We now observe that for any non-zero $c\in\Fp$, the sum of the elements
-in two sets $A$ and $A_{c}$ is $\frac{p+1}{2}+\frac{p+1}{2}=p+1$,
-which is greater than the size $p$ of $\Fp$, and so there must be
-at least one common element such that $a^{2}=c-b^{2}$. Thus, every
-element $c\in\Fp$ is the field norm of some element $\alpha=a+b\rmi\in\Fpp$
-such that $\fnorm{\alpha}=a^{2}+b^{2}=c$, and $\fnorm*{\left\{ c\right\} }$
-is non-empty.
-
-We then want to show for all non-zero $c\in\Fp$, the size of $\fnorm*{\left\{ c\right\} }$
-is always the same. Given a particular non-zero $c_{0}\in\Fp$ and
-$\alpha_{0}\in\Fpp$ with $\fnorm{\alpha_{0}}=c_{0}$, consider the
-map $f\left(\alpha\right)=\alpha_{0}\alpha$. When $\fnorm{\alpha}=1$,
-we have~\cite{DummitFoote2004} 
-\begin{equation}
-\fnorm{f\left(\alpha\right)}=\fnorm{\alpha_{0}\alpha}=\fnorm{\alpha_{0}}\fnorm{\alpha}=c_{0}
-\end{equation}
-so that $f\left(\alpha\right)\in\fnorm*{\left\{ c_{0}\right\} }$.
-Since $\fnorm{a+b\rmi}=0$ only for $a=b=0$, $\alpha_{0}$ is non-zero,
-and $f$ is a bijection between $\fnorm*{\left\{ 1\right\} }$ and
-$\fnorm*{\left\{ c_{0}\right\} }$. This means the number of elements
-in $\fnorm*{\left\{ 1\right\} }$ and $\fnorm*{\left\{ c_{0}\right\} }$
-is the same. Because $c_{0}$ can be any non-zero element, the number
-of elements in the equivalence classes $\fnorm*{\left\{ c\right\} }$
-is always the same.
-
-\begin{figure}[!b]
-\noindent \centering{}\includegraphics[width=3.6in]{Fpp2Fp}\caption{\label{proof1.fig}Sketch of the map from $\Fpp$ to $\Fp$ using
-$\fnorm{\alpha}$, showing the decomposition of $\Fpp$ into the zero
-element $\left(0,0\right)$ and the $p^{2}-1=\left(p+1\right)\left(p-1\right)$
-non-zero elements that map onto the $p-1$ non-zero elements of $\Fp$
-with multiplicity $p+1$.}
-\end{figure}
-We can now compute the size of the equivalence class of complex unit-modulus
-phases corresponding to the Hopf fibration circle. %
-\begin{comment}
-\todo{Explain the Hopf fibration circle here\ldots ? }
-\end{comment}
-Since $\Fpp$ has $p^{2}-1$ non-zero values, and the map $\fnorm{\alpha}$
-distributes these equally across the domain of $p-1$ non-zero elements
-$c\in\Fp$, there are $\frac{p^{2}-1}{p-1}=p+1$ (non-zero) domain
-elements in $\Fpp$ for each (non-zero) image element in $\Fp$. We
-illustrate this graphically in Figure~\ref{proof1.fig}. Thus, the
-Hopf circle always has the size $p+1$, corresponding essentially
-to a discrete projective line, and that is the size of each equivalence
-class of the map $\fnorm{\alpha}$ for non-vanishing $\alpha$, including
-the map to the unit norm value $c=1\in\Fp$.\end{proof}
-
-\subsection{Vector Spaces\label{subsec:Vector-Spaces}}
-
-In this section, we want to build a theory of discrete vector spaces
-that approximates as closely as possible the features of the conventional
-quantum theory. Such a structure would ideally consist of the following:
-(i) a vector space over the field of complex numbers, and (ii) an
-inner product $\ip{\Phi}{\Psi}$ associating to each pair of vectors
-a complex number, and satisfying the following properties:
-\begin{enumerate}[label=(\Alph{enumi})]
-\item \label{enu:inner-product-complex-conjugate}$\ip{\Phi}{\Psi}$ is
-the complex conjugate of $\ip{\Psi}{\Phi}$;
-\item \label{enu:inner-product-linear}$\ip{\Phi}{\Psi}$ is conjugate-linear
-in its first argument and linear in its second argument;
-\item \label{enu:inner-product-positive-definite}$\ip{\Psi}{\Psi}$ is
-always non-negative and is equal to $0$ only if $\ket{\Psi}$ is
-the zero vector.
-\end{enumerate}
-It turns out that a vector space defined over a finite field cannot
-have an inner product satisfying the properties above. However, we
-will introduce a Hermitian ``dot product'' satisfying some of those
-properties.
-
-We are interested in the vector space $\mathcal{H}$ of dimension
-$D$ defined over the complexified field $\Fpp$. Let $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \cdots & \alpha_{D-1}\end{pmatrix}^{T}$
-and $\ket{\Phi}=\begin{pmatrix}\beta_{0} & \beta_{1} & \cdots & \beta_{D-1}\end{pmatrix}^{T}$
-represent vectors in $\mathcal{H}$, with numbers $\alpha_{i}$ and
-$\beta_{i}$ drawn from $\Fpp$, and where $\left(\cdot\right)^{T}$
-is the transpose.
-
-\begin{definition}[Hermitian dot product] Given vectors $\ket{\Phi}$
-and $\ket{\Psi}\in\mathcal{H}$, it can be shown~\cite{grove2002classical,Wan2006}
-the Hermitian dot product is always reducible to the form 
-\begin{equation}
-\ip{\Phi}{\Psi}=\sum_{i=0}^{D-1}\beta_{i}^{p}\alpha_{i}\,.\label{innerprod}
-\end{equation}
-If we use $\bra{\Phi}$ to represent the dual vector of $\ket{\Phi}$,
-i.e., the conjugate transport of $\ket{\Phi}$, then the matrix multiplication
-of $\bra{\Phi}$ and $\ket{\Phi}$ results a $1\times1$ matrix whose
-only entry is their Hermitian dot product $\ip{\Phi}{\Psi}$.\end{definition}
-
-Two vectors $\ket{\Phi}$ and $\ket{\Psi}\in\mathcal{H}$ are said
-to be orthogonal if $\ip{\Phi}{\Psi}=0$. This product satisfies conditions~\ref{enu:inner-product-complex-conjugate}
-and~\ref{enu:inner-product-linear} for inner products but violates
-condition~\ref{enu:inner-product-positive-definite} since in every
-finite field there always exists a non-zero vector $\ket{\Psi}$ such
-that $\ip{\Psi}{\Psi}=0$. The reason is that addition in finite fields
-eventually ``wraps around'' (because of their cyclic or modular
-structure), allowing the sum of non-zero elements to be zero. The
-fraction of non-zero vectors satisfying $\ip{\Psi}{\Psi}=0$ decreases
-with the order $p$.
-
-For any vector $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \cdots & \alpha_{D-1}\end{pmatrix}^{T}$,
-the Hermitian dot product $\ip{\Psi}{\Psi}$ is equal to $\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}$,
-which is the sum of the field norms for the complex coefficients.
-For convenience, we now extend the field norm to include vector arguments
-by defining 
-\begin{equation}
-\fnorm{\ket{\Psi}}=\ip{\Psi}{\Psi}=\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}\,.\label{fnormD.eq}
-\end{equation}
-
-Although the field norm of a vector can vanish for non-vanishing vectors,
-if a vector $\ket{\Psi}$ has a non-vanishing field norm~$c$, then
-$\ket{\Psi}$ can be normalized by utilizing its field norm. Recalled
-in Sec.~\ref{subsec:Complexified-Finite-Fields}, we defined $\fnorm*{\left\{ c\right\} }$
-to be the set of elements whose field norm is $c$. Given any $\alpha\in\fnorm*{\left\{ c\right\} }$,
-the field norm of $\frac{\ket{\Psi}}{\alpha}$ is
-\begin{equation}
-\fnorm{\frac{\ket{\Psi}}{\alpha}}=\frac{\fnorm{\ket{\Psi}}}{\fnorm{\alpha}}=\frac{c}{c}=1\,,
-\end{equation}
-i.e., $\frac{\ket{\Psi}}{\alpha}$ is normalized. However, since the
-size of $\fnorm*{\left\{ c\right\} }$ is $p+1$, we cannot identify
-a ``unique'' way to normalize any given vector.
-
-The similar problem has already happened in conventional quantum theory.
-For example, assume we want to normalize $\ket{\Psi}=\ket{0}+\ket{1}$.
-Its inner product with itself is $\ip{\Psi}{\Psi}=2$. Since $\left(\pm\sqrt{2}\right)^{2}=2$,
-both $\frac{\ket{\Psi}}{\sqrt{2}}$ and $\frac{\ket{\Psi}}{-\sqrt{2}}$
-are normalized and representing the same state as $\ket{\Psi}$. In
-this case, we systematically choose the state divided by the positive
-square root as ``the'' normalized vector of $\ket{\Psi}$ in conventional
-quantum theory, and the positive square root function is called the
-\emph{principal} branch of $\sqrt{w}$~\cite{GAMELIN2003}. In the
-discrete case, we can also systematically choose the \emph{principal
-inverse field norm} by utilizing a generator $g\in\Fpp$ discussed
-in Sec.~\ref{subsec:Complexified-Finite-Fields}. Because $g$ is
-a generator, any non-zero element $c\in\ff{p}\backslash\left\{ 0\right\} $
-can be expressed as $g^{\left(p+1\right)k}$ where $k$ is an integer
-and $0\le k<p-1$, so we can define the principal inverse field norm
-$\fnorm*{g^{\left(p+1\right)k}}$ as $g^{k}$. For example, the inverse
-field norm over $\ff{3^{2}}$ with respect to the generator $1-\rmi$
-is shown in Table~\ref{tab:Inverse-field-norm}. Given the non-normalized
-state $\ket{\Psi}=\ket{0}+\ket{1}$, since its field norm is $\fnorm{\ket{\Psi}}=\fnorm{1}+\fnorm{1}=-1$,
-it can be normalized as
-\begin{equation}
-\frac{\ket{\Psi}}{\fnorm*{-1}}=\frac{\ket{0}+\ket{1}}{1-\rmi}=\left(1+\rmi\right)\ket{0}+\left(1+\rmi\right)\ket{1}\,.
-\end{equation}
-\begin{table}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{tab:Inverse-field-norm}Inverse field norm over $\ff{3^{2}}$
-with respect to the generator $1-\rmi$}
-\begin{tabular}{cccc}
-\toprule 
-$c=g^{\left(p+1\right)k}$ & $\left(p+1\right)k$ & $k$ & $\fnorm*{g^{\left(p+1\right)k}}=g^{k}$\tabularnewline
-\midrule
-$-1$ & $4$ & $1$ & $1-\rmi$\tabularnewline
-$1$ & $0$ & $0$ & $1$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{doublespace}
-\end{table}
-
-\section{Irreducible Discrete $D$-dimen\-sional States\label{DQCnqubitBloch.sec}}
-
-In the one-qubit state with coefficients in $\Fpp$, the discrete
-analog of the Bloch sphere is constructed by exact analogy to the
-continuous case: we first require that the coefficients of the single
-qubit basis obey 
-\begin{equation}
-\fnorm{\ket{\psi_{1}}}=\fnorm{\alpha_{0}}+\fnorm{\alpha_{1}}=1\label{DQA2.eq}
-\end{equation}
-in the discrete field. We show that there are $p\left(p^{2}-1\right)$
-such values later in the general theorem, Proposition~\ref{appU.sec}.
-Given this requirement, which is similar in form to the conservation
-of probability, but not as useful due to the lack of orderable probability
-values, we can immediately conclude that the discrete analog of the
-Hopf fibration is again 
-\begin{eqnarray}
-X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
-Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\label{DQA6.eq}\\
-Z & = & \fnorm{\alpha_{0}}-\fnorm{\alpha_{1}}={x_{0}}^{2}+{y_{0}}^{2}-{x_{1}}^{2}-{y_{1}}^{2}\,,\nonumber 
-\end{eqnarray}
-but now with all computations in\hspace{0bp}$\pmod{p}$. At this
-point, one can simply write down all possible discrete values for
-the complex numbers $\left(\alpha_{0},\alpha_{1}\right)$ satisfying
-Eq.~(\ref{DQA2.eq}) and enumerate those that project to the same
-value of $\left(X,Y,Z\right)$. This equivalence class is the discrete
-analog of the circle in the complex plane that was eliminated in the
-continuous case. In Proposition~\ref{appH.sec}, we show that $p+1$
-discrete values of $\left(\alpha_{0},\alpha_{1}\right)$ with unit
-norm map to the same point under the Hopf map \Eq{DQA6.eq}; %
-\begin{comment}
-\todo{Does Proposition~\ref{appH.sec} really show this? }
-\end{comment}
-we may think of these as discrete circles or projective lines of equivalent,
-physically indistinguishable, complex phase. The surviving $p\left(p-1\right)$
-values of $\left(\alpha_{0},\alpha_{1}\right)$ correspond to irreducible
-physical states of the discrete single qubit system. Thus, for example,
-choosing the underlying field to be $\Fppx{3}$, there are exactly
-6 single-qubit state vectors to populate the Bloch sphere; the four
-equivalent phase-multiples mapping to each of the six points on the
-$\Fppx{3}$ Bloch sphere are collapsed and regarded as physically
-indistinguishable. In Figure~\ref{bloch.fig}, we plot the irreducible
-states on the Bloch sphere for $p=3$, $7$, and $11$. Note that
-the Cartesian lengths of the real vectors corresponding to the points
-on the Bloch sphere vary considerably due to the nature of discrete
-fields; we have artificially normalized them to a ``continuous world''
-unit radius sphere for conceptual clarity.
-\begin{figure}[!b]
-\noindent \begin{centering}
-\includegraphics[viewport=200bp 0bp 1800bp 600bp,width=1.1\columnwidth]{picC}
-\par\end{centering}
-\caption{\label{bloch.fig}Schematically normalized plots of the elements of
-the discrete Bloch sphere, the irreducible single-qubit (two-dimen\-sional)
-state vectors with unit norm over the field $\Fpp$. We show the results
-for $p=3$, $7$, and $11$. For example, in $\Fppx{3}$, there are
-24 vectors of unit norm, but only the 6 inequivalent classes appear
-in the plot. The $p+1=4$ equivalent vectors in each class differ
-only by a complex discrete phase.}
-\end{figure}
-
-\subsection{Counting States on the Discrete Bloch Sphere}
-
-We have the unique opportunity in the finite-field approach to quantum
-computing to precisely identify and enumerate the physical states.
-In the conventional theory, as we have seen in Sec.~\ref{subsec:Explicit-generalization-of},
-we employ a generalized Hopf fibration on the normalized states to
-project out a circle of phase-equivalent states, yielding the generalized
-Bloch sphere.
-
-In the introduction to this subsection, we sketched the counting of
-the irreducible single-qubit discrete states. To count the number
-of inequivalent discrete states for the general $n$-qubit case with
-coefficients in $\Fpp$, we first must find the set of unit-norm states,
-and then determine the equivalence classes of unit-norm states under
-discrete phase transformations; we can then enumerate the list of
-states on the discrete generalized Bloch sphere. By executing computer
-searches of these spaces, we discovered a hypothesis for a closed-form
-solution for the counting of the states and found a rigorous proof
-of the enumeration.
-
-This process of describing the discrete $D$-dimen\-sional irreducible
-states can again be understood geometrically by following the discrete
-analog of the Hopf fibration. First, we construct the discrete version
-of the quadratic unit-length form that automatically annihilates the
-distinction among states differing only by a discrete phase, 
-\begin{equation}
-\Hat{a}=\left(\fnorm{\alpha_{i}},\ldots,\sqrt{2}\,\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\,\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\right)\,,
-\end{equation}
-where 
-\begin{equation}
-\Hat{a}\cdot\Hat{a}=\left(\sum_{i=0}^{D-1}\fnorm{\alpha_{i}}\right)^{2}=1\,.
-\end{equation}
-From Proposition~\ref{appH.sec}, we know that $p+1$ elements of
-this discrete $\Sphere{2D-1}$ structure map to the \textit{same point}
-in $\Hat{a}$. %
-\begin{comment}
-\todo{Does Proposition~\ref{appH.sec} really show this? }
-\end{comment}
-Each set of $p+1$ redundant points is, geometrically speaking, the
-\textit{discrete Hopf fibration circle} living above each \textit{irreducible}
-point of the $D$-dimen\-sional state description. These $p+1$ points
-are interpretable as the $p$ finite points plus the single point
-at infinity of the projective discrete line (see, e.g.,~\cite{arnold_2010}).
-
-The next part of this argument is the determination of the unit-norm
-states, effectively the space of allowed discrete partitions of unity;
-we cannot exactly call these ``probability-conserving'' sectors
-of the state coefficients since we do not have a well-defined notion
-of probability, but we do have a well-defined notion of the partition
-of unity. Compared to the total number $p^{2D}$ of possible complex
-integer state vectors that could be chosen, the number of unit-norm
-states is given by the following proposition. This unit-norm state
-structure is the discrete analog of $\Sphere{2D-1}$.
-
-\begin{prop}\label{appU.sec}The number of unit-norm states described
-by a $D$-dimen\-sional vector $(\alpha_{0},\ldots,\alpha_{D-1})$
-with coefficients $\alpha_{i}\in\Fpp$ is $p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)$.\end{prop}
-
-\begin{proof}Proposition~11.27 in Grove~\cite{grove2002classical}
-provides the count of the zero-norm states $\zeta\left(D,p\right)=p^{D-1}\left(p^{D}+\left(-1\right)^{D}\left(p-1\right)\right)$.
-Since there are $p^{2}$ elements $\alpha\in\Fpp$, we must have $\left(p^{2}\right)^{D}=p^{2D}$
-possible values of a $D$-dimen\-sional vector $(\alpha_{0},\ldots,\alpha_{D-1})$.
-There are $p^{2}-1$ non-zero values of $\alpha\in\Fpp$, and we showed
-in Proposition~\ref{appH.sec} that $\fnorm{\alpha}$ maps exactly
-$p+1$ values in that set to each of the $p-1$ non-zero values in
-$\Fp$. Therefore, the \textit{unit-norm case} has a count of domain
-elements that is $\frac{1}{p-1}$ of the total number of non-zero-norm
-cases, 
-\begin{equation}
-\frac{p^{2D}-\zeta\left(D,p\right)}{p-1}=\frac{p^{2D}-p^{2D-1}-\left(-1\right)^{D}p^{D-1}\left(p-1\right)}{p-1}=p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)\,.\label{unitnorm.eq}
-\end{equation}
-\end{proof}
-
-Finally, we repeat the last step of the $D$-dimen\-sional continuous
-Hopf fibration process for discrete $D$-dimen\-sional states, eliminating
-the discrete set of $p+1$ equivalent points that map to the same
-point $\Hat{a}$ on the generalized Bloch sphere. Dividing the tally
-$p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)$ of unit norm states
-by the $p+1$ elements of each phase-equivalent discrete circle, we
-find
-\begin{equation}
-\frac{p^{D-1}\left(p^{D}-\left(-1\right)^{D}\right)}{p+1}\label{eq:numberOfIrreducibleStates}
-\end{equation}
-as the total count of unique irreducible states in a discrete $D$-dimen\-sional
-configuration. The resulting object is precisely the discrete version
-of $\CP{D-1}$, which we might call a \textit{discrete complex projective
-space} or $\DCP{D-1}$.
-
-\section{Geometry of Entangled States\label{sec:Geometry-of-Entangled-States}}
-
-To discuss entanglement, we consider a $D$-dimen\-sional quantum
-system composed of $n$-qubit subsystems, i.e., $D=2^{n}$ as usual.
-Without regard to uniqueness, an $n$-qubit state with discrete complex
-coefficients in $\Fpp$ will have the total possible space of coefficients
-with dimension $p^{2\times2^{n}}$ (including the null state). Imposing
-the condition of a length-one norm in $\Fp$, this number is reduced
-to $p^{2^{n}-1}\left(p^{2^{n}}-1\right)$. The ratio of all the states
-to the unit-norm states is asymptotically $p$: 
-\begin{equation}
-\frac{p^{2^{n}+1}}{p^{2^{n}}-1}\rightarrow p\,,
-\end{equation}
-so there are roughly $p$ sets of coefficients, for any number of
-qubits $n$, that are discarded for each retained unit-length state
-vector. A factor of $p+1$ more states is discarded in forming the
-discrete Bloch sphere of irreducible states. Selected plots of the
-full space compared to both the unit-norm space and the irreducible
-space for a selection of complexified finite fields are shown in Figure~\ref{statePlot3Unit.fig}
-for 1, 2, 3, and 4 qubits.
-\begin{figure}[!b]
-\begin{centering}
-\includegraphics[width=1\columnwidth]{statePlot3}
-\par\end{centering}
-\caption{\label{statePlot3Unit.fig}Logarithmic plot of the number of discrete
-unnormalized states (top, in red), vs the number of normalized discrete
-states (middle, in blue), vs the irreducible states (bottom, in green)
-for the first 6 $\Fpp$-compatible primes, ($3$, $7$, $11$, $19$,
-$23$, $31$), for the number of qubits $1$, $2$, $3$, and $4$.}
-\end{figure}
-
-\subsection{Unentangled vs Entangled Discrete States}
-
-For a given $p$ and the corresponding complexified field $\Fpp$,
-the $n$-qubit discrete quantum states with coefficients in $\Fpp$
-can be classified by their degree of entanglement to a level of precision
-that is unavailable in the continuous theory. We look first at the
-unentangled $n$-qubit states, which are direct product states of
-the form 
-\begin{equation}
-\ket{\Psi}=\ket{\psi_{1}}\otimes\cdots\otimes\ket{\psi_{j}}\otimes\cdots\otimes\ket{\psi_{n}}\,.\label{dqcNqUntg.eq}
-\end{equation}
-Without regard to normalization, there are $\left(p^{4}\right)^{n}$
-possible unentangled states out of the total of $p^{2\times2^{n}}$
-states noted above. When we normalize the individual product states
-to unit norm, the norm of the entire $n$-qubit state becomes the
-product of those unit norms and is automatically normalized to one.
-We have already seen that each single-qubit normalized state in the
-tensor product Eq.~(\ref{dqcNqUntg.eq}) has precisely $p\left(p-1\right)$
-irreducible components due to $D=2$ case in Eq.~(\ref{eq:numberOfIrreducibleStates}).
-
-\subsection{Completely Unentangled States and the Discrete Bloch Sphere}
-
-In effect, the irreducible states for unentangled $n$-qubit configurations
-reduce to a single Bloch sphere for each one-qubit component $\ket{\psi_{j}}$,
-and thus the whole set of states is defined by an $n$-tuple of discrete
-Bloch sphere coordinates. Since each Bloch sphere in $\Fpp$ has $p\left(p-1\right)$
-distinct irreducible components, we have 
-\begin{equation}
-\mbox{{\bf Count of Unentangled States}}=p^{n}\left(p-1\right)^{n}\,.\label{eq:CountUnentangledStates}
-\end{equation}
-
-According to Eq.~(\ref{eq:numberOfIrreducibleStates}), we know that
-the total number of irreducible states (points in the generalized
-$\DCP{2^{n}-1}$ Bloch sphere) for an $n$-qubit state is $\frac{p^{2^{n}-1}\left(p^{2^{n}}-1\right)}{p+1}$,
-and so the number of states containing some measure of entanglement
-is 
-\begin{equation}
-\mbox{{\bf Count of Entangled States}}=\frac{p^{2^{n}-1}\left(p^{2^{n}}-1\right)}{p+1}-p^{n}\left(p-1\right)^{n}\,.
-\end{equation}
-Therefore, a very small fraction of the unit norm states is unentangled.
-
-\subsection{Maximal Entanglement\label{subsec:Maximal-entanglement}}
-
-Equation~(\ref{purityMeasure.eq}) for $P_{\fh}$ includes a normalization
-factor~$\frac{1}{n}$. In the discrete case, this normalization factor
-is undefined when $p\mid n$. Equation~(\ref{purityMeasure.eq})
-also includes a summation of $n$ terms. In the discrete case, certainly
-when $p\mid n$ but also in other cases, this summation may vanish
-in the field even if the individual summands are non-zero. These anomalies
-are irrelevant for the classification of unentangled states as this
-computation is performed by directly checking the possibility of direct
-decomposition into product states, disregarding equation~(\ref{purityMeasure.eq}).
-
-For maximally entangled states, the purity calculation in conventional
-quantum mechanics using equation~(\ref{purityMeasure.eq}) produces
-0. Given the above observations, in a discrete field, equation~(\ref{purityMeasure.eq})
-may be undefined or may report a purity of 0 even for partially entangled
-states. For example, the normalized 5-qubit state $\ket{\Psi}=\left(1-\rmi\right)\left(\ket{00}+\ket{11}\right)\otimes\ket{000}$
-has $P_{\fh}=0$ for $p=3$, and is not maximally entangled because
-only the first two qubits are entangled. In the discrete case, we
-therefore check for maximally entangled states using the following
-equations~\cite{Gardiner2014}, 
-\begin{equation}
-\forall j,\forall\eta\in\left\{ x,y,z\right\} ,\expval{\jthSubsystem{\sigma}[\eta]{j}}^{2}=0\textrm{ ,}\label{eq:john}
-\end{equation}
-which avoids the normalization factor and simply checks that each
-summand is 0, where $\expval{\jthSubsystem{\sigma}[\eta]{j}}$ is
-defined as $\melem{\Psi}{\jthSubsystem{\sigma}[\eta]{j}}{\Psi}$.
-
-We now implement these procedures to enumerate the maximally entangled
-states for the specific cases for $n=2,3$ and compare these to the
-counts for product states. We have verified explicitly in Eq.~(\ref{eq:CountUnentangledStates})
-that the numbers of unit-norm product states for $n=2$, $p=\{3,7,11,19,\ldots\}$
-are 
-\begin{equation}
-(p+1)p^{2}(p-1)^{2}=\{144,14112,145200,2339280,\ldots\}\,,
-\end{equation}
-and for general $n$, $(p+1)p^{n}(p-1)^{n}$. The irreducible state
-counts are reduced by $(p+1)$, giving 
-\begin{equation}
-p^{2}(p-1)^{2}=\{36,1764,12100,116964,\ldots\}\,,
-\end{equation}
-and in general for $n$-qubits, there are $p^{n}\left(p-1\right)^{n}$
-instances of pure product states.
-
-Performing the computation using equation (\ref{eq:john}), we find
-the numbers of maximally entangled states for two qubits to be 
-\begin{equation}
-p\left(p^{2}-1\right)\left(p+1\right)=\left\{ 96,2688,15840,136800,\ldots\right\} \,.
-\end{equation}
-The irreducible state counts for maximal entanglement are reduced
-by $\left(p+1\right)$, giving, for $n=2$, 
-\begin{equation}
-p\left(p^{2}-1\right)=\left\{ 24,336,1320,6840,\ldots\right\} \,.
-\end{equation}
-For three qubits, there are $p^{3}\left(p^{4}-1\right)\left(p+1\right)$
-(total) and $p^{3}\left(p^{4}-1\right)$ (irreducible) instances of
-pure maximally entangled states. For four-qubits and $p=3$, there
-are $2195538048$ instances of pure maximally entangled states, while
-the general formula for four-qubit states remains unclear.
-
-Therefore, the ratio of maximally entangled to product states is 
-\begin{equation}
-\frac{\textbf{Max entangled}}{\textbf{Product}}=\frac{p+1}{p\left(p-1\right)}\textrm{ and }\frac{\left(p^{2}+1\right)\left(p+1\right)}{\left(p-1\right)^{2}}
-\end{equation}
-for $n=2$ and $3$, respectively.
-
-\section{Discrete Quantum Computing (I)\label{discretequantumcomputingI}}
-
-Given a complexified finite field $\ff{p^{2}}$ and its Hermitian
-\dotprod\  (Eq.~\eqref{innerprod}) much of the structure of conventional
-quantum computing can be recovered. For example, the smallest field~$\ff{3^{2}}$
-is already rich enough to express the standard Deutsch-Jozsa algorithm
-\cite{DeutschJozsa1992,544199,Jaeger2007}, which requires only normalized
-versions of vectors or matrices with the scalars $0$, $1$, and $-1$.
-Similarly, other deterministic quantum algorithms (algorithms for
-which we may determine the outcome with certainty), such as Simon's
-\cite{Simon:1994:PQC:1398518.1399019,Mermin2007,Jaeger2007} and Bernstein-Vazirani
-\cite{Bernstein:1993:QCT:167088.167097,Mermin2007}, perform as desired.
-In the following subsection, we will present the discrete Deutsch
-algorithm as an example. However, this quantum computing model is
-still different from the conventional one. On one hand, algorithms
-such as Grover's search \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}
-will not work in the usual way because we lack (the notion of) ordered
-angles and probability in general. On the other hand, this computational
-model still leads to excessive computational power for the unstructured
-database search problem for certain database sizes. %
-\begin{comment}
-\todo{Prof.~Gil~Kalai thought it would be interesting if we can
-do Simon's algorithm in DQC~(I), but I don't know when I could organize
-my unreadable draft to a readable one\ldots{} Moreover, Prof.~Ortiz
-wants to check Shor's algorithm in DQC~(I).}
-\end{comment}
-
-\subsection{Discrete Deutsch Algorithm\label{subsec:Discrete-Deutsch-algorithm}}
-
-\begin{table}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{tab:Possible-f}All Possible $f\colon\boolt\rightarrow\boolt$.}
-\begin{tabular}{ccccc}
-\toprule 
-$x$ & $f_{1}\left(x\right)$ & $f_{2}\left(x\right)$ & $f_{3}\left(x\right)$ & $f_{4}\left(x\right)$\tabularnewline
-\midrule
-$\bfalse$ & $\bfalse$ & $\bfalse$ & $\btrue$ & $\btrue$\tabularnewline
-$\btrue$ & $\bfalse$ & $\btrue$ & $\bfalse$ & $\btrue$\tabularnewline
-\midrule 
-constant or balanced? & constant & balanced & balanced & constant\tabularnewline
-\bottomrule
-\end{tabular}
-\end{doublespace}
-\end{table}
-\begin{comment}
-\todo{We typeset $U_{f}$ either directly or use macro \textbackslash uf,
-but the definition of \textbackslash uf has a negative space between
-$U$ and $f$ which is different from U\_\{f\}\ldots{} I need to understand
-whether the negative space is necessary or not, or whether the negative
-space has any semantic meaning\ldots{} }
-\end{comment}
-Although having no realistic application, the Deutsch algorithm is
-the first quantum algorithm which outperforms any possible classical
-algorithm for the Deutsch problem \cite{Deutsch1985,544199,Mermin2007}.
-The Deutsch problem is to decide whether a function $f\colon\boolt\rightarrow\boolt$
-is constant or balanced. As listed in Table~\ref{tab:Possible-f},
-we have only $4$ different $f$: $2$ of them are constant while
-another $2$ are balanced. Similar to our $\usat$ algorithm in Sec.~\ref{modalquantumcomputing},
-we start by representing $f$ as a Deutsch black box $U_{f}$ in the
-middle of the quantum circuit, Figure~\ref{fig:Quantum-Circuit-Deutsch}.
-To explain why this circuit solves the Deutsch problem, we then compute
-the state in each step explicitly and express them in the Dirac bracket
-notation and its matrix representation in the computational basis
-$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $.
-\begin{figure}[!b]
-\noindent \centering{}
-\[
-\begin{array}{c}
-\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{ & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd]\\
-\lstick{\ket{1}} & \qw & \gate{H} & \qw & \multigate{1}{\uf} & \qw & \gate{H^{\dagger}} & \qw & \multimeasureD{1}{\text{measure}}\\
-\lstick{\ket{0}} & \qw & \gate{H} & \qw & \ghost{\uf} & \qw & \gate{H^{\dagger}} & \qw & \ghost{\text{measure}}\\
- & \push{\ket{\Phi_{1}}} &  & \push{\ket{\Phi_{2}}} &  & \push{\ket{\Phi_{3}}} &  & \push{\ket{\Phi_{4}}}
-}
-\end{array}
-\]
-\caption{\label{fig:Quantum-Circuit-Deutsch}Quantum Circuit for the Deutsch
-Algorithm.}
-\end{figure}
-
-First, a 2-qubit pure state is initialized to $\ket{\Phi_{1}}=\ket{1}\ket{0}=\left(\begin{smallmatrix}0\\
-1
-\end{smallmatrix}\right)\otimes\left(\begin{smallmatrix}1\\
-0
-\end{smallmatrix}\right)$.
-
-Second, on both initialized qubits, we apply the Hadamard matrix $H=\frac{1}{\alpha}\left(\begin{smallmatrix}1 & 1\\
-1 & -1
-\end{smallmatrix}\right)$ over $\Fpp$, where $\alpha=\fnorm*{2}$ is the principal inverse
-field norm which is used to replace the square root $\sqrt{2}$ in
-the conventional Hadamard matrix $\frac{1}{\sqrt{2}}\left(\begin{smallmatrix}1 & 1\\
-1 & -1
-\end{smallmatrix}\right)$ as discussed in Sec.~\ref{subsec:Vector-Spaces}. The second step
-produces
-\[
-\ket{\Phi_{2}}=\left(H\otimes H\right)\ket{\Phi_{1}}=\left[\frac{1}{\alpha}\begin{pmatrix}1 & 1\\
-1 & -1
-\end{pmatrix}\begin{pmatrix}0\\
-1
-\end{pmatrix}\right]\otimes\left[\frac{1}{\alpha}\begin{pmatrix}1 & 1\\
-1 & -1
-\end{pmatrix}\begin{pmatrix}1\\
-0
-\end{pmatrix}\right]=\ket{-}\ket{+}\,,
-\]
-where
-\begin{align}
-\ket{+} & =\frac{1}{\alpha}\begin{pmatrix}1\\
-1
-\end{pmatrix}=\frac{\ket{0}+\ket{1}}{\alpha}\,, & \ket{-} & =\frac{1}{\alpha}\begin{pmatrix}1\\
--1
-\end{pmatrix}=\frac{\ket{0}-\ket{1}}{\alpha}\,.
-\end{align}
-
-Third, the Deutsch black box~$U_{f}$ is applied to the state $\ket{\Phi_{2}}$.
-According to Eq.~(\ref{eq:DeutschBox}), these Deutsch black box
-will be used to apply exclusive disjunction on the first qubit, where
-we respectively identify $\bfalse$ and $\btrue$ as $0$ and $1$
-as usual. Since our first qubit is $\ket{-}$, the value $f\left(x\right)$
-could be moved outside as a phase no matter $f\left(x\right)$ is
-$\bfalse$ or $\btrue$:
-\begin{equation}
-\begin{aligned}U_{f}\ket{-}\ket{x} & =\tfrac{1}{\alpha}\left[\ket{0\oplus f\left(x\right)}\ket{x}-\ket{1\oplus f\left(x\right)}\ket{x}\right]\\
- & =\begin{cases}
-\frac{1}{\alpha}\left[\ket{0}\ket{x}-\ket{1}\ket{x}\right] & \textrm{if }f\left(x\right)=\bfalse=0\,;\\
-\frac{1}{\alpha}\left[\ket{1}\ket{x}-\ket{0}\ket{x}\right] & \textrm{if }f\left(x\right)=\btrue=1
-\end{cases}\\
- & =\left(-1\right)^{f\left(x\right)}\ket{-}\ket{x}\,.
-\end{aligned}
-\end{equation}
-Then, $\ket{\Phi_{3}}$ can be evaluated as follow:
-\begin{equation}
-\begin{aligned}\ket{\Phi_{3}} & =U_{f}\ket{-}\ket{+}=\tfrac{1}{\alpha}\left[U_{f}\ket{-}\ket{0}+U_{f}\ket{-}\ket{1}\right]\\
- & =\tfrac{1}{\alpha}\left[\left(-1\right)^{f\left(0\right)}\ket{-}\ket{0}+\left(-1\right)^{f\left(1\right)}\ket{-}\ket{1}\right]\\
- & =\begin{cases}
-\left(-1\right)^{f\left(0\right)}\ket{-}\ket{+} & \textrm{if }f\left(0\right)=f\left(1\right)\,;\\
-\left(-1\right)^{f\left(0\right)}\ket{-}\ket{-} & \textrm{if }f\left(0\right)\ne f\left(1\right)\,.
-\end{cases}
-\end{aligned}
-\end{equation}
-
-Finally, $\ket{\Phi_{4}}$ can then be obtained by applying the Hermitian
-conjugate of Hadamard matrix $H^{\dagger}=\frac{1}{\alpha^{*}}\left(\begin{smallmatrix}1 & 1\\
-1 & -1
-\end{smallmatrix}\right)$ on both qubits. If $f\left(0\right)=f\left(1\right)$, i.e., $f$
-is constant, we have 
-\[
-\ket{\Phi_{4}}=\left(-1\right)^{f\left(0\right)}\left[\dfrac{1}{\alpha^{*}}\begin{pmatrix}1 & 1\\
-1 & -1
-\end{pmatrix}\frac{1}{\alpha}\begin{pmatrix}1\\
--1
-\end{pmatrix}\right]\otimes\left[\dfrac{1}{\alpha^{*}}\begin{pmatrix}1 & 1\\
-1 & -1
-\end{pmatrix}\frac{1}{\alpha}\begin{pmatrix}1\\
-1
-\end{pmatrix}\right]=\left(-1\right)^{f\left(0\right)}\ket{1}\ket{0}\,;
-\]
-if $f\left(0\right)\ne f\left(1\right)$, i.e., $f$ is balanced,
-we have 
-\[
-\ket{\Phi_{4}}=\left(-1\right)^{f\left(0\right)}\left[\dfrac{1}{\alpha^{*}}\begin{pmatrix}1 & 1\\
-1 & -1
-\end{pmatrix}\frac{1}{\alpha}\begin{pmatrix}1\\
--1
-\end{pmatrix}\right]\otimes\left[\dfrac{1}{\alpha^{*}}\begin{pmatrix}1 & 1\\
-1 & -1
-\end{pmatrix}\frac{1}{\alpha}\begin{pmatrix}1\\
--1
-\end{pmatrix}\right]=\left(-1\right)^{f\left(0\right)}\ket{1}\ket{1}\,.
-\]
-Hence, we can decide whether $f$ is constant or balanced by measuring
-$\ket{\Phi_{4}}$ in the computational basis.
-
-\subsection{Partial \usat\ Algorithm\label{subsec:Partial-Algorithm}}
-
-\begin{figure}[!b]
-\centering{}
-\[
-\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \qw & \multimeasureD{3}{\text{measure}}\\
-\lstick{x_{1}=\ket{0}} & \multigate{2}{\otimes H} & \ghost{\uf} & \multigate{2}{\otimes H^{\dagger}} & \ghost{\text{measure}}\\
-\lstick{\ldots} & \ghost{\otimes H} & \ghost{\uf} & \ghost{\otimes H^{\dagger}} & \ghost{\text{measure}}\\
-\lstick{x_{n}=\ket{0}} & \ghost{\otimes H} & \ghost{\uf} & \ghost{\otimes H^{\dagger}} & \ghost{\text{measure}}
-}
-\]
-\caption{\label{fig:dbsearch}Circuit for the black box \usat\ in discrete
-quantum computing.}
-\end{figure}
-It is possible, in some situations, to exploit the cyclic behavior
-of the field to creatively cancel probability amplitudes and solve
-problems with what again appears to be ``supernatural'' efficiency.
-We illustrate this behavior with the algorithm in Fig.~\ref{fig:dbsearch},
-which is a variant of the one in Fig.~\ref{fig:alg}. Unlike the
-modal quantum algorithm, the new algorithm does not always succeed
-deterministically using a constant number of black box evaluations.
-We can, however, show that supernatural behavior occurs if the characteristic
-$p$ of the field divides $2^{N}-1$. For a database of fixed size
-$N$, matching the conditions becomes less likely as the size of the
-field increases. Nevertheless, for a \textit{given} field, it is always
-possible to expand any database with dummy records to satisfy the
-divisibility property. Physically, we are taking advantage of additional
-interference processes that happen because of the possibility of ``wrapping
-around'' due to modular arithmetic. We do not know, in general, whether
-this version of discrete quantum computing actually enables the rapid
-solution of $\NP$-complete problems.
-
-\section{Discrete Quantum Theory (II)\label{sec:Discrete-Quantum-Theory-(II)}}
-
-\subsection{Inner Product Space\label{discretequantumtheoryIIa}}
-
-We next discuss an approach using finite complexifiable fields that
-conditionally resolves the inner product condition~\ref{enu:inner-product-positive-definite}
-discussed in Sec.~\ref{subsec:Vector-Spaces}, which is violated
-by the theory just presented. A possible path is suggested by the
-work of Reisler and Smith~\cite{ReislerSmith1969}. The general idea
-is that while the cyclic properties of arithmetic in finite fields
-make it impossible to \emph{globally} obtain the desired properties
-of the conventional Hilbert space inner product, it \textit{is} possible
-to recover them \emph{locally}, thereby restoring, with some restrictions,
-all the usual properties of the inner product needed for conventional
-quantum mechanics and conventional quantum computing. As the size
-of the discrete field becomes large, the size of the locally valid
-computational framework grows as well, leading to the \emph{effective
-emergence of conventional quantum theory}. We next briefly outline
-such a context for local orderable subspaces of a finite field and
-introduce an improvement on the original method~\cite{ReislerSmith1969}
-suggested by recent number theory resources~\cite{Sloane2005}.
-
-Let us first note that the range of the quadratic map, $\set{x^{2}\bmod p}{x\in\ff{p}}$,
-is always one-half of the non-zero elements of $\ff{p}$, and is the
-set of elements with square roots in the field. This is the set of
-\emph{quadratic residues}, and the complementary set (the other half
-of the non-zero field elements) is the set of \emph{quadratic non-residues}.
-For example in $\ff{7}$, the elements $\left\{ 1,2,4\right\} $ are
-considered positive as they have the square roots $\left\{ 1,3,2\right\} $
-respectively; the remaining elements $\left\{ 3,5,6\right\} $ do
-not have square roots in the field. What is interesting is that if
-we have an uninterrupted sequence of numbers that are all quadratic
-residues, then we can define a \textit{transitive order}, with $a>c$
-if $a>b$ and $b>c$, provided $a-b$, $b-c$, and $a-c$ are all
-quadratic residues. %
-\begin{comment}
-\todo{Should we remove the quadratic residue part? Since we never
-use take the square roots of numbers in order range later, whether
-they are the quadratic residues or not doesn't really matter\ldots}
-\end{comment}
-
-As a concrete example, consider a finite field in which the sequential
-elements $0$, $1$, $2$, $3$, \ldots , and $k-1$ are all quadratic
-residues (including $0$). Then any sequence of odd length~$k$ and
-centered around an arbitrary $x\in\ff{p}$, i.e., $S_{x}\left(k\right)=x-\frac{k-1}{2}$,
-\ldots , $x-2$, $x-1$, $x$, $x+1$, $x+2$, \ldots , $x+\frac{k-1}{2}$,
-is \textit{transitively ordered}. Indeed, we have $\left(x+1\right)-x=1$
-which is a quadratic residue and hence $x+1>x$. Similarly, $x-\left(x-1\right)=1$
-and hence $x>x-1$. Also, $\left(x+1\right)-\left(x-1\right)=2$ which
-is a quadratic residue and hence $x+1>x-1$. Clearly, this process
-may be continued to show that the sequence $S_{x}\left(k\right)$
-is transitively ordered. We can construct examples using the sequence
-A000229 in the encyclopedia of integer sequences~\cite{Sloane2005}.\footnote{For computational purposes, this sequence is preferable to the one
-proposed by Reisler and Smith~\cite{ReislerSmith1969} because it
-produces smaller primes. Their work showed that a sufficient condition
-on finite fields to produce sequences of quadratic residues is to
-further constrain the underlying prime numbers to be of the form $8\prod_{i=1}^{m}q_{i}-1$,
-where $q_{i}$ is the $i$-th odd prime. While all such primes are
-of the form $4\ell+3$, the set is severely restricted to astronomical
-numbers because the first few such primes are $7$, $23$, $839$,
-$9239$, $2042039$, \ldots} The $n$-th element of that sequence (which must be prime) is the
-least number such that the $n$-th prime is the \emph{least} quadratic
-non-residue for the given element. The first few elements of this
-sequence are listed in the top row of Table~\ref{pseq}. The next
-row lists the number $k$ of transitively ordered consecutive elements
-in that field, and $\pi\left(k\right)$ in the bottom row is the prime
-counting function (the number of primes up to $k$).
-\begin{table}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{pseq}Number $k$ of transitively ordered elements for a given
-field $\ff{p}$.}
-\begin{tabular}{cccccccccccc}
-\toprule 
-$p$ & $3$ & $7$ & $23$ & $71$ & $311$ & $479$ & $1559$ & $5711$ & $10559$ & $18191$ & $\cdots$\tabularnewline
-\midrule 
-$k$ & ${\bf 2}$ & ${\bf 3}$ & ${\bf 5}$ & ${\bf 7}$ & ${\bf 11}$ & ${\bf 13}$ & ${\bf 17}$ & ${\bf 19}$ & ${\bf 23}$ & ${\bf 29}$ & $\cdots$\tabularnewline
-\midrule
-$\pi\left(k\right)$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ & $8$ & $9$ & $10$ & $\cdots$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{doublespace}
-\end{table}
-
-As an example, consider the field $\ff{23}$. Looking at the squares
-of the numbers $\ff{23}=\{0,\ldots,22\}$ modulo 23, we find the $2$-centered
-uninterrupted sequence $S_{2}\left(5\right)=\{0,1,2,3,4\}$, followed
-by $5$, which is both the smallest quadratic non-residue and the
-size of the uninterrupted sequence of quadratic residues (including
-$0$) of interest. In particular, it is possible to construct a total
-order for the elements $S_{0}\left(5\right)=\{-2,-1,0,1,2\}$ in the
-fields $\ff{23}$, $\ff{71}$, $\ff{311}$, etc., but not in the smaller
-fields $\ff{3}$ and $\ff{7}$.
-
-Given a $D$-dimen\-sional vector space over $\ff{p^{2}}$ where~$p$
-is one of the primes above, it is possible to define a \emph{region}
-over which an inner product and norm can be identified. Let the length
-of the sequence of quadratic residues be $k$. The region of interest
-includes all vectors $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \cdots & \alpha_{D-1}\end{pmatrix}^{T}$,
-for which $D<p-\frac{k-1}{2}$ and each $\alpha_{i}$ satisfies 
-\begin{equation}
-D\,\fnorm{\alpha_{i}}=D\,\left(a_{i}^{2}+b_{i}^{2}\right)\leq\frac{k-1}{2}\,,\label{eq:region}
-\end{equation}
-with $a_{i}$ and $b_{i}$ drawn from the set $S_{0}\left(k\right)$.
-Consider, for example, $\ff{311^{2}}$ ($p=311$, $k=11$). We find
-that we can trade off the dimension $D$ of the vector space against
-the range of probability amplitudes available for each $\alpha_{i}$
-in Table~\ref{table_allowed}.
-\begin{table}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{table_allowed}Allowed probability amplitudes for different
-vector space dimensions $D$ and $k=11$.}
-\begin{tabular}{ll}
-\toprule 
- & allowed probability amplitudes $F^{D}\left(k\right)$ \tabularnewline
-\midrule
-$D=1$  & $F^{1}\left(11\right)=\left\{ 0,\pm1,\pm2,\pm\rmi,\pm2\rmi,(\pm1\pm\rmi),(\pm1\pm2\rmi),(\pm2\pm\rmi)\right\} $\tabularnewline
-$D=2$  & $F^{2}\left(11\right)=\left\{ 0,\pm1,\pm\rmi,(\pm1\pm\rmi)\right\} $ \tabularnewline
-$D=3$  & $F^{3}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline
-$D=4$  & $F^{4}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline
-$D=5$  & $F^{5}\left(11\right)=\left\{ 0,\pm1,\pm\rmi\right\} $ \tabularnewline
-$D\geq6$  & $F^{D}\left(11\right)=\left\{ 0\right\} $\tabularnewline
-\bottomrule
-\end{tabular}
-\end{doublespace}
-\end{table}
-
-We can now verify, by using Table~\ref{table_allowed}, that for
-any vector $\ket{\Psi}$ in the selected region the value of $\ip{\Psi}{\Psi}$
-is $\geq0$ and vanishes precisely when $\ket{\Psi}$ is the zero
-vector. Thus, in the selected region, condition~\ref{enu:inner-product-positive-definite}
-is established. Although the set of vectors defined over that region
-is not closed under addition, and hence the set is not a vector subspace,
-we can still have a theory by restricting our computations. In other
-words, \emph{as long as our computation remains within the selected
-region}, we may pretend to have an inner product space. The salient
-properties of conventional quantum mechanics emerge, but the price
-to be paid is that the state space is no longer a vector space. This
-is basically a rigorous formulation of Schwinger's intuition (See,
-Chapter~1, Section~1.16 in \cite{schwinger2001quantum}).
-
-Readers with backgrounds in computer science or numerical analysis
-will notice, significantly, that this model for discrete quantum computing
-is reminiscent of practical computing with a classic microprocessor
-having only integer arithmetic and a limited word length. We cannot
-perform a division having a fractional result at all since there are
-no fractional representations; we do have the basic constants zero
-and one, as well as positive and negative numbers, but multiplications
-or additions producing results outside the integer range wrap-around
-modulo the word length and typically yield nonsense. This implies
-that, for the local discrete model, we must accept an operational
-world view that \textit{has no awareness of the value of $p$}, and
-depends on having set up in advance an environment with a field size,
-analogous to the word size of a microprocessor, that happily processes
-\textit{any} calculation we are prepared to perform. This is the key
-step, though it may seem strange because we are accustomed to arithmetic
-with real numbers: we list the calculations that must be performed
-in our theory, discover an \textit{adequate size of the processor
-word} — implying a possibly ridiculously large value of $p$ chosen
-as described above — and from that point on, we calculate necessarily
-valid values within that processor, never referring in any way to
-$p$ itself in the sequel.
-
-\subsection{Cardinal Probability\label{discretequantumtheoryIIb}}
-
-The final issue that must be addressed in the discrete theory put
-forward in Section~\ref{discretequantumtheoryIIa} concerns measurement.
-To recap, within the theory, states are $D$-dimen\-sional vectors
-with complex discrete-valued amplitudes drawn from a totally-ordered
-range, $F^{D}(k)$, in the underlying finite field. These states possess,
-by construction, having field norms in the non-negative integers,
-all in the ordered range of Eq.~\eqref{eq:region}, and hence potentially
-produce probabilities that can be ordered. Our point is that, although
-the mathematical framework of conventional quantum mechanics relies
-on infinite precision probabilities, it is impossible in practice
-to measure exact equality of real numbers — we can only achieve an
-approximation within measurement accuracy. Significantly, when we
-use finite fields, this measurement accuracy will be encoded in the
-size of the finite field used for measurements.
-
-Given a $D$-dimen\-sional Hilbert space in conventional quantum
-theory, although we can measure the probability for every eigenprojector
-of an observable as discussed in Sec.~\ref{sec:fuzzy}, our previous
-quantum circuits in Figures~\ref{fig:alg}, \ref{fig:Quantum-Circuit-Deutsch},
-and~\ref{fig:dbsearch} always measure in the computational basis
-$\{\ket{0},\ldots,\ket{i},\ldots,\ket{D-1}\}$. Indeed, it is sufficient
-to only consider measuring a quantum circuit in the computational
-basis because measuring in another basis is the same as applying a
-quantum gate and measuring in the computational basis. In this situation,
-the Born rule for pure states, Eq.~(\ref{eq:Born}), can be simplified
-as
-\begin{equation}
-\muB_{\Psi}\left(\proj{i}\right)\equiv\muB_{\Psi}\left(i\right)=\frac{\ip{\Psi}{i}\ip{i}{\Psi}}{\ip{\Psi}{\Psi}}=\frac{\left|\ip{i}{\Psi}\right|^{2}}{\ip{\Psi}{\Psi}}=\frac{\left|\alpha_{i}\right|^{2}}{\ip{\Psi}{\Psi}}\,,\label{eq:Born-ComputationalBasis}
-\end{equation}
-where $\ket{\Psi}=\begin{pmatrix}\alpha_{0} & \alpha_{1} & \cdots & \alpha_{D-1}\end{pmatrix}^{T}$
-is an unnormalized state. Hereafter, we will simply call $\muB_{\Psi}\left(i\right)$
-the probability of measuring $\ket{i}$.
-
-Although division is not an allowed operation for the elements in
-an ordered region, following the standard procedure to define a conventional
-fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
-we could define a \emph{cardinal probability} as a pair of order-region
-elements as well:
-\begin{equation}
-\muC_{\Psi}\left(i\right)=\cardp{\fnorm{\ip{i}{\Psi}}}{\fnorm{\ket{\Psi}}}=\cardp{\fnorm{\alpha_{i}}}{\fnorm{\ket{\Psi}}}\,,\label{eq:cardinalProbability}
-\end{equation}
-where every probability amplitude $\alpha_{i}\in F^{D}\left(k\right)$
-so that both $\fnorm{\alpha_{i}}$ and $\fnorm{\ket{\Psi}}$ are within
-the order range $S_{0}\left(k\right)$, and $\muC_{\Psi}\left(i\right)$
-is called the cardinal probability of measuring $\ket{i}$. For example,
-let $p=311$, $k=11$, and $D=2$. The permitted range is $S_{0}\left(11\right)=\{-5,\ldots,-1,0,1,\ldots,5\}$,
-given the dimension $D=2$, the allowed probability amplitude coefficients
-are $F^{2}\left(11\right)=\{0,\pm1,\pm\rmi,\left(\pm1\pm\rmi\right)\}$
-(see Table~\ref{table_allowed}). Now the cardinal probabilities
-of several representative one-qubit states are listed in Table~\ref{f11-proj.fig}.
-\begin{table}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{f11-proj.fig}Field norms and probabilities for one-qubit states
-$\ket{\Psi}$ in $F^{2}\left(11\right)$.}
-\begin{tabular}{cccccc}
-\toprule 
-$\ket{\Psi}$ & $\fnorm{\ip{0}{\Psi}}$ & $\fnorm{\ip{1}{\Psi}}$ & $\fnorm{\ket{\Psi}}$ & $\muC_{\Psi}\left(0\right)$ & $\muC_{\Psi}\left(1\right)$\tabularnewline
-\midrule
-$1\ket{0}$ & $1$ & $0$ & $1$ & $\cardp{1}{1}$ & $\cardp{0}{1}$\tabularnewline
-$1\ket{0}+1\ket{1}$ & $1$ & $1$ & $2$ & $\cardp{1}{2}$ & $\cardp{1}{2}$\tabularnewline
-$1\ket{0}+(1+\rmi)\ket{1}$ & $1$ & $2$ & $3$ & $\cardp{1}{3}$ & $\cardp{2}{3}$\tabularnewline
-$(1-\rmi)\ket{0}+(1+\rmi)\ket{1}$ & $2$ & $2$ & $4$ & $\cardp{2}{4}$ & $\cardp{2}{4}$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{doublespace}
-\end{table}
-
-When measuring cardinal probabilities, \textit{inequalities} can be
-preserved with appropriate resources (in the form of a sufficiently
-large choice of the field), while \textit{equalities} cannot be guaranteed
-in the theory, and in fact, can be represented as \textit{inequalities
-of any order}. That is, given two cardinal probabilities $\cardp{\fnorm{\alpha_{i}}}{\fnorm{\ket{\Psi}}}$
-and $\cardp{\fnorm{\alpha_{j}}}{\fnorm{\ket{\Psi}}}$ with the same
-``denominator'', $\fnorm{\alpha_{i}}>\fnorm{\alpha_{j}}$ physically
-means it is more likely to measure $\ket{i}$ than $\ket{j}$ if we
-have enough resources; $\fnorm{\alpha_{i}}=\fnorm{\alpha_{j}}$ means
-the experimental results might not always favor $\ket{i}$ or $\ket{j}$
-no matter how many resources we use. The same principle can also apply
-to two cardinal probabilities with different ``denominators''. The
-details of the comparison can be easily formulated by following the
-standard procedure \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016}.
-
-\section{Discrete Quantum Computing (II)\label{discretequantumcomputingII}}
-
-We now examine two particularly important types of examples within
-the discrete theory of the previous section: the first is the deterministic
-Deutsch-Jozsa algorithm \cite{DeutschJozsa1992,544199,Jaeger2007},
-which determines the balanced or unbalanced nature of an unknown function
-with a single measurement step ($O\left(1\right)$), and the second
-is the (normally) probabilistic Grover algorithm \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007},
-determining the result of an unstructured search in $O\left(\sqrt{N}\right)$
-time. In the following, we use $k$ to denote the upper bound of the
-ordered range of integers needed to perform a given calculation; this
-in turn is assumed to be implemented using a choice of a finite prime
-number $p$ that supports calculation in the range of~$k$.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Discrete Deutsch-Jozsa Algorithm: Deterministic}
-
-To examine the Deutsch-Jozsa algorithm in the discrete theory of the
-previous section, assume we are given a classical function $f\colon\boolt^{n}\rightarrow\boolt$
-and are told that $f$ is either constant or balanced \cite{DeutschJozsa1992,544199,Jaeger2007}.
-The algorithm is expressed in a space of dimension $D=2^{n+1}$: it
-begins with the $n+1$ qubit state $\ket{1}\ket{\overline{0}}$ where
-the overline denotes a sequence of length~$n$. A straightforward
-calculation~\cite{544199} shows that the final state is\footnote{Note that the algorithm in reference~\cite{544199} makes use of
-the Hadamard matrix. We have eliminated the factor $\frac{1}{\sqrt{2}}$
-to ensure that all quantities are expressed in terms of integers.
-Also, notice that the positioning of the initial qubit state $\ket{1}$
-is reversed from~\cite{544199}. } %
-\begin{comment}
-\todo{A bit more explanation?}
-\end{comment}
-\begin{equation}
-\sum_{\overline{z}\in\left\{ 0,1\right\} ^{n}}\sum_{\overline{x}\in\left\{ 0,1\right\} ^{n}}\left(-1\right)^{f\left(\overline{x}\right)+\overline{x}\cdot\overline{z}}\left(\ket{0}\ket{\overline{z}}-\ket{1}\ket{\overline{z}}\right)\,,
-\end{equation}
-and that its field norm is $2^{n+1}$. %
-\begin{comment}
-\todo{Verify. }
-\end{comment}
-To make sure that the algorithm works properly, we note that all the
-probability amplitudes involved in the calculation are in the range
-$-2^{n}$, \ldots , $2^{n}$ and therefore, by Eq.~\eqref{eq:region},
-we get the following constraint on the size of the ordered region
-in the finite field: 
-\begin{eqnarray}
-2^{n+1}\left(2^{n}\right)^{2}\leq\frac{k-1}{2} & \Leftrightarrow & k\geq2^{3n+2}+1\,.
-\end{eqnarray}
-
-Now we need to choose a prime number $p$ that supports calculation
-in the range of $k$. Assume that $k$ is the least prime satisfying
-$k\geq2^{3n+2}+1$, and let $p$ be the $\pi\left(k\right)$-th element
-of the sequence A000229~\cite{Sloane2005}. We argue that no prime
-less than this value of $p$ can support calculation in the ordered
-range of $k$ and that this $p$ is sufficient to support such calculation.
-Since $k$ is the least quadratic non-residue of $p$, every number
-less than $k$ is a quadratic residue, and thus $0$, $1$, $2$,
-$3$, \ldots , $2^{3n+2}$ are all quadratic residues. Hence, the
-numbers $-2^{n}$, \ldots , $2^{n}$ are all inside the ordered range
-$S_{0}\left(k\right)$. On the other hand, if we choose any prime
-smaller than $p$, there is a quadratic non-residue smaller than $k$,
-and we also know that the least quadratic non-residue is a prime~\cite{numtheory.ref}.
-Thus, there is a quadratic non-residue in $0$, $1$, $2$, $3$,
-\ldots , $2^{3n+2}$, and therefore, for this smaller $p$, there
-would be a number in $-2^{n}$, \ldots , $2^{n}$ that is not in the
-ordered range $S_{0}\left(k\right)$.
-
-When $f$ is constant, the cardinal probability of measuring $\ket{0}\ket{\overline{0}}$
-or $\ket{1}\ket{\overline{0}}$ is $\cardp{\left(2^{n}\right)^{2}+\left(2^{n}\right)^{2}=2^{2n+1}}{2^{2n+1}}$;
-i.e., the cardinal probability of measuring any other state is $\cardp{0}{2^{2n+1}}$.
-When $f$ is balanced, the cardinal probability of measuring $\ket{0}\ket{\overline{0}}$
-or $\ket{1}\ket{\overline{0}}$ is $\cardp{0}{2^{2n+1}}$. Therefore,
-if we find that the post-measurement state is either $\ket{0}\ket{\overline{0}}$
-or $\ket{1}\ket{\overline{0}}$, we know $f$ is constant; otherwise,
-$f$ is balanced.
-
-For a single qubit Deutsch problem, the probability amplitudes are
-between $-2$ and $2$, and the dimension $D=2^{1+1}=4$, so we want
-to have 
-\begin{equation}
-k\geq2^{3\cdot1+2}+1=2^{5}+1=33\,.
-\end{equation}
-The least prime satisfying the above condition is $k=37$, and thus
-$\pi\left(37\right)=12$ and $p=422231$, as shown in the extended
-elements Table~\ref{table_long}. 
-\begin{table}
-\begin{doublespace}
-\noindent \centering{}\caption{\label{table_long}Extension of transitively ordered elements.}
-\begin{tabular}{cccccccccc}
-\toprule 
-$p$ & $\cdots$ & $422231$ & $\cdots$ & $196265095009$ & $\cdots$ &  & $\cdots$ &  & $\cdots$\tabularnewline
-\midrule 
-$k$ & $\cdots$ & ${\bf 37}$ & $\cdots$ & ${\bf 131}$ & $\cdots$ & ${\bf 257}$ & $\cdots$ & ${\bf 32771}$ & $\cdots$\tabularnewline
-\midrule
-$\pi\left(k\right)$ & $\cdots$ & $12$ & $\cdots$ & $32$ & $\cdots$ & $55$ & $\cdots$ & $3513$ & $\cdots$\tabularnewline
-\bottomrule
-\end{tabular}
-\end{doublespace}
-\end{table}
-
-For the $2$-qubit Deutsch-Jozsa, the computation is already quite
-challenging. Now the probability amplitudes are between $-4$ and
-$4$, and the dimension $D=2^{2+1}=8$, so we need 
-\begin{equation}
-k\geq2^{3\cdot2+2}+1=2^{8}+1=257\,.
-\end{equation}
-Because $257$ is a prime, we can pick $k=257$ and $\pi\left(257\right)=55$.
-The actual value of $p$ is already outside the range of the published
-sequence A000229.
-
-These examples illustrate that the value of $p$ plays an essential
-role: its size grows with the numerical range of the intermediate
-and final results of the algorithms being implemented. Therefore,
-we naturally recover a deterministic measure of the intrinsic resources
-required for a given level of complexity; this measure is normally
-completely hidden in computations with real numbers, and explicitly
-exposing it is one of the significant achievements of our discrete
-field analysis of quantum computation. This solves the conundrum that
-the conventional Deutsch-Jozsa algorithm mysteriously continues to
-work for larger and larger input functions without any apparent increase
-in resources. Our analysis of this problem reveals that as the size
-of the input increases, it is necessary to increase the size of $p$
-and hence the size of the underlying available numeric coefficients.
-This observation does not fully explain the power of quantum computing
-over classical computing, but at least it explains that some of the
-power of quantum computing depends on increasingly larger precision
-in the underlying field of numbers.
-
-\subsection{Discrete Grover Search: Nondeterministic}
-
-As an example of how to apply our cardinal probability framework to
-a nondeterministic algorithm, we consider discrete Grover's algorithm
-searching an unstructured database of size $N=2^{n}$ \cite{Grover:1996:FQM:237814.237866,Mermin2007,Jaeger2007}.
-Let $f\colon\boolt^{n}\rightarrow\boolt$ be the function we want
-to search. To simplify our discussion, we will only consider 
-\begin{equation}
-f\left(\overline{x}\right)=\begin{cases}
-1\,, & \textrm{if }\overline{x}=\overline{0}\,;\\
-0\,, & \textrm{if }\overline{x}\ne\overline{0}\,,
-\end{cases}
-\end{equation}
-where we identify $\bfalse$ and $\btrue$ as $0$ and $1$ as usual,
-and $\overline{0}=(0,\ldots,0)$.
-
-To solve Grover's problem, we represent the search states as $n$-qubit
-states as usual. However, instead of the Deutsch black box~$U_{f}$,
-$f$ is represented as the $N\times N$ ``phase rotation'' matrix
-\begin{equation}
-R=\begin{pmatrix}-1 & 0 & 0 & \cdots & 0\\
-0 & 1 & 0 & \cdots & 0\\
-0 & 0 & 1 & \cdots & 0\\
-\vdots & \vdots & \vdots & \ddots & \vdots\\
-0 & 0 & 0 & \cdots & 1
-\end{pmatrix}\,,
-\end{equation}
-where the ``marked'' element is in the first position. Beside $R$,
-we also need the $N\times N$ ``diffusion'' matrix
-\begin{equation}
-V=\begin{pmatrix}1-\frac{N}{2} & 1 & 1 & \cdots & 1\\
-1 & 1-\frac{N}{2} & 1 & \cdots & 1\\
-1 & 1 & 1-\frac{N}{2} & \cdots & 1\\
-\vdots & \vdots & \vdots & \ddots & \vdots\\
-1 & 1 & 1 & \cdots & 1-\frac{N}{2}
-\end{pmatrix}\,,
-\end{equation}
-where we have eliminated, in matrix~$V$, the scaling factor $\frac{2}{N}$
-to enforce the requirement that all matrix coefficients in our framework
-are integer-valued. By applying the transformation $VR$ repeatedly
-\begin{equation}
-j=\round\left(\frac{\pi}{4\arccos\sqrt{1-\frac{1}{N}}}-\frac{1}{2}\right)\approx\round\left(\frac{\pi}{4}\sqrt{N}\right)
-\end{equation}
-times, we can find the target element~$\overline{0}$. In our context,
-we also need to choose a prime number that is large enough to ensure
-that all the numbers that occur during the calculation and after measurement
-are within the transitively-ordered subrange.
-
-Let's walk through the state in each iteration to make sure the algorithm
-works. Because the probability amplitudes of $\ket{\overline{x}}$
-are all the same for $\overline{x}\neq\overline{0}$, we can let $a_{l}$
-be the probability amplitude of $\ket{\overline{0}}$, with $b_{l}$
-the probability amplitude of each of the other possibilities, which
-are all the same, after the operators $VR$ is applied $l$ times.
-Beginning at $l=0$ with the information-less state and the normalization
-scaled to integer values as usual, the state after $l$-th iteration
-can be written as %
-\begin{comment}
-\todo{Verify the computation??}
-\end{comment}
-\begin{equation}
-\begin{pmatrix}a_{l}\\
-b_{l}\\
-\vdots\\
-b_{l}
-\end{pmatrix}=\left(VR\right)^{l}\begin{pmatrix}1\\
-1\\
-\vdots\\
-1
-\end{pmatrix}=VR\begin{pmatrix}a_{l-1}\\
-b_{l-1}\\
-\vdots\\
-b_{l-1}
-\end{pmatrix}\,.
-\end{equation}
-We can solve the above iteration by the following recurrence relation
-for the successive coefficients:
-\begin{subequations}
-\begin{align}
-a_{0} & =1\,, & a_{l+1} & =\left(\frac{N}{2}-1\right)a_{l}+\left(N-1\right)b_{l}\,,\\
-b_{0} & =1\,, & b_{l+1} & =\left(-1\right)a_{l}+\left(\frac{N}{2}-1\right)b_{l}\,.
-\end{align}
-\end{subequations}
-We also know $\left|a_{j}\right|>\left|b_{j}\right|$, so we can estimate
-an upper bound for the maximum cardinal probability as $\max\fnorm{a_{j}}\leq2\left(\frac{N}{2}\right)^{2j+1}$.
-By applying Eq.~\eqref{eq:region} with $D=N=2^{n}$, we can estimate~$k$
-using $k\geq8\left(\frac{N}{2}\right)^{2j+2}+1$. We can then pick
-a prime $k$, and choose the $\pi\left(k\right)$-th prime in the
-sequence represented by Table~\ref{pseq} guaranteeing that every
-number we need for the computation is within the transitively ordered
-range $F^{D}\left(k\right)$.
-
-For the $2$-qubit Grover search, we have $N=D=4$ and $j=1$, with
-the maximum cardinal probability 
-\begin{equation}
-\max\fnorm{a_{j}}\leq2\left(\frac{4}{2}\right)^{2+1}=16\,,
-\end{equation}
-so we need 
-\begin{equation}
-k\geq8\left(\frac{4}{2}\right)^{2\cdot1+2}+1=8\cdot2^{4}+1=129\,.
-\end{equation}
-The least prime $k$ satisfying the above condition is $k=131$, and
-so $\pi\left(131\right)=32$ and $p=196265095009$.
-
-When $p=196265095009$, we assume that $f\left(\overline{x}\right)=1$
-if and only if $\ket{\overline{x}}=\ket{0}\!\ket{0}$, and so the
-final state is $\begin{pmatrix}4 & 0 & \cdots & 0\end{pmatrix}^{T}$
-with the field norm of $16$. Then, the cardinal probability of obtaining
-$\ket{0}\!\ket{0}$ as the post-measurement state is $\cardp{16}{16}$,
-and it is $\cardp{0}{16}$ for the rest of the states.
-
-For the $3$-qubit Grover search, we have $N=D=8$ and $j=2$, with
-an upper bound $\max\fnorm{a_{j}}\leq2\left(\frac{8}{2}\right)^{4+1}=2048$
-on the cardinal probability. Thus 
-\begin{equation}
-k\ge8\left(\frac{8}{2}\right)^{6}+1=32769\,.
-\end{equation}
-The nearest prime greater than this number is $32771$, so we can
-pick $k=32771$ and $\pi\left(32771\right)=3513$, and so if we use
-the $3513$-th prime, we can implement Grover's algorithm for a database
-of size $8$.
-
-Continuing with the $3$-qubit Grover example, we show how the cardinal
-probabilities evolve to single out the target state. First, assume
-that $f\left(\overline{x}\right)=1$ if and only if $\ket{\overline{x}}=\ket{0}\!\ket{0}\!\ket{0}$.
-The initial information-less $8$-dimen\-sional state vector evolves
-under the application of $VR$ as follows: %
-\begin{comment}
-\todo{Change the whole paragraph to a table?}
-\end{comment}
-\begin{equation}
-\begin{pmatrix}1\\
-1\\
-\vdots\\
-1
-\end{pmatrix}\rightarrow\begin{pmatrix}10\\
-2\\
-\vdots\\
-2
-\end{pmatrix}\rightarrow\begin{pmatrix}44\\
--4\\
-\vdots\\
--4
-\end{pmatrix}\,.
-\end{equation}
-These states have differing field norm, so we cannot compare their
-cardinal probability directly. Since states differ by only scalar
-multiplication representing the same state, if we multiply the first
-and second states by $16$ and $4$, respectively, their field norms
-become the same value of $2048$. The now-consistently-normalized
-states become 
-\begin{equation}
-\begin{pmatrix}16\\
-16\\
-\vdots\\
-16
-\end{pmatrix}\rightarrow\begin{pmatrix}40\\
-8\\
-\vdots\\
-8
-\end{pmatrix}\rightarrow\begin{pmatrix}44\\
--4\\
-\vdots\\
--4
-\end{pmatrix}\,.
-\end{equation}
-Therefore, the cardinal probabilities of measuring $\ket{0}\!\ket{0}\!\ket{0}$
-in each state are 
-\begin{align}
-\cardp{256}{2048} &  & \cardp{1600}{2048} &  & \cardp{1936}{2048} & ,
-\end{align}
-while the cardinal probabilities of measuring the other states become
-\begin{align}
-\cardp{256}{2048} &  & \cardp{64}{2048} &  & \cardp{16}{2048} & .
-\end{align}
-We may thus conclude that the cardinal probability of measuring the
-satisfying assignment of $f$ increases as we apply the diffusion~$V$
-and phase rotation~$R$ matrices repeatedly.
-
-Clearly, the required size of $k$ increases systematically with the
-problem size, and the corresponding size of the required prime number
-$p$ defining the discrete field increases in the fashion illustrated
-in Tables~\ref{pseq} and~\ref{table_long}.
-
-\section{Quantum Probability Measures over Finite Fields\label{sec:Toward-IVPM}}
-
-Although cardinal probabilities can be ordered as discussed in Sec.~\ref{discretequantumtheoryIIb},
-it is still unclear how to define their arithmetic operations, which
-is required to further define the mixed states and expectation values.
-Notice that the cardinal probability over finite fields defined in
-Eq.~(\ref{eq:cardinalProbability}) is based on the conventional
-Born rule, Eq.~(\ref{eq:Born-ComputationalBasis}), which could be
-derived axiomatically according to Gleason's theorem as in Sec.~\ref{subsec:Gleason's-Theorem-and}.
-\begin{comment}
-Although they are valid inside an ordered region, some quantum algorithms,
-like Shor's~\cite{Shor1999,Mermin2007,Jaeger2007}, don't localize
-their computation in a small region. \todo{Remove the discussion
-of Shor's algorithm if I cannot verify it on DQT~(I) on time. }Moreover, 
-\end{comment}
-To overcome these issues, we want to follow the steps in Sec.~\ref{sec:fuzzy}
-to define events and probability measures, and see whether we could
-have a Gleason-like theorem which induces a correspondence between
-states and probability measures qualified as a discrete Born rule.
-
-\begin{definition}[Quantum Probability Measures over Finite Fields]\label{def:QPMFF}Given
-a vector space $\mathcal{H}$ of dimension $D$ over the complexified
-field $\Fpp$, the set of events $\events_{p^{2}}$ is recursively
-defined as follows:
-\begin{itemize}
-\item $\mathbb{0}$ and $\mathbb{1}\in\events_{p^{2}}$.
-\item If $\ket{\Psi}$ is a unit-norm state in $\mathcal{H}$, i.e., $\ket{\Psi}\in\mathcal{H}$
-with $\ip{\Psi}{\Psi}=\fnorm{\ket{\Psi}}=1$, then the projector of
-the form $\proj{\Psi}\in\events_{p^{2}}$.
-\item For each pair of \emph{orthogonal} events $P_{0}\in\events_{p^{2}}$
-and $P_{1}\in\events_{p^{2}}$, i.e., $P_{0}P_{1}=\mathbb{0}$, their
-sum $P_{0}+P_{1}$ is an event, i.e., $P_{0}+P_{1}\in\events_{p^{2}}$.
-\end{itemize}
-Then a quantum probability measure over a finite field (QPMFF) $\mu\colon\events_{p^{2}}\rightarrow\left[0,1\right]$
-assigns a probability to each event (projection operator~$P$) subject
-to $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$, and satisfying for
-each pair of \emph{orthogonal} events $P_{0}$ and $P_{1}$, $\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)$.\end{definition}
-
-After defining a QPMFF~$\mu$, we would like to follow the idea of
-Gleason's theorem to see whether we might trace back from $\mu$ to
-a pure or mixed state and summarize this correspondence as a discrete
-Born rule. When $p=D=3$, there is indeed some correspondence between
-QPMFFs and states. However, when $D=3$ and $p=7$, we have numerically
-verified that the unique QPMFF $\mu\colon\events_{7^{2}}\rightarrow\left[0,1\right]$
-is the equal probable one
-\begin{equation}
-\mu\left(P\right)=\begin{cases}
-0 & \textrm{if }P=\mathbb{0}\,;\\
-\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimensional projector;}\\
-\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimensional projector;}\\
-1 & \textrm{if }P=\mathbb{1}\,.
-\end{cases}\label{eq:QPMFF37}
-\end{equation}
-In contrast, the irreducible pure states in $\ff{7^{2}}^{3}$ is not
-unique. As we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}),
-there are 
-\begin{equation}
-\frac{7^{3-1}\left(7^{3}-\left(-1\right)^{3}\right)}{7+1}=2107\label{eq:numberOfIrreducibleStates-7-3}
-\end{equation}
-irreducible pure states in $\ff{7^{2}}^{3}$. Since we don't have
-enough QPMFF to correspond even pure states, there is no discrete
-Born rule in this case. In general, we conjecture that QPMFF is always
-unique for $D\ge3$ except $D=p=3$.
-
-Although we couldn't prove there is no discrete Born rule by investigating
-QPMFFs alone, we could prove there is no ``sensible'' Born rule
-which also satisfies an analog of Eqs.~(\ref{eq:Born-probability-one})
-and~(\ref{eq:Born-unitary-invariant}). %
-\begin{comment}
-\todo{Notice that the notation here and previous is a bit different
-because we dealt with mixed states previously, but pure states here.
-Besides, should we explain the physical meaning of these propositions?}
-\end{comment}
-
-\begin{thm}\label{thm:NotGleasonDQT-group}For $D\ge3$ except $p=D=3$,
-there is no ``sensible'' Born rule $\muF$ parametrized by unit-norm
-states~$\ket{\Phi}$ in $\mathcal{H}$ such that $\muF_{\Phi}$ is
-a QPMFF;
-\begin{equation}
-\muF_{\Phi}\left(P\right)=1\label{eq:zero}
-\end{equation}
- if and only if $P\ket{\Phi}=\ket{\Phi}$; and 
-\begin{equation}
-\muF_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muF_{\Phi}\left(P\right)\,,\label{eq:basis-independent}
-\end{equation}
-where $U$ is any unitary map.\end{thm}
-
-\begin{proof}\footnote{This proof assumes $p\ge7$, and there is a simpler proof for $D\ge4$
-applying to $p=3$ case~\cite{Gardiner2014}.}Assume such a map $\muF$ satisfying all properties exists, we will
-use the listed properties to build a contradiction. Consider the computational
-basis $\{\ket{0},\ket{1},\ket{2},\ldots\}$, and the projectors formed
-by these vectors, $P_{0}=\proj{0}$, $P_{1}=\proj{1}$, and $P_{2}=\proj{2}$.
-Since $p\ge7$, $1+1+1$ is not $0$ in $\ff{p^{2}}$, and has the
-principal inverse field norm $\gamma=\fnorm*{3}$ as defined in Sec.~\ref{subsec:Vector-Spaces}.
-The unit-norm state $\ket{\oplus}=\frac{1}{\gamma}\left[\ket{0}+\ket{1}+\ket{2}\right]$
-can then be used as a parameter of $\muF$ and induces a QPMFF $\muF_{\oplus}$.
-To compute the probability values of $\muF_{\oplus}$, we want to
-utilize Eq.~(\ref{eq:basis-independent}) by letting $U_{i}$ be
-the unitary map that permutes the basis vectors $\ket{0}$ and $\ket{i}$
-and acts as the identity for the rest for $i=1$ and $2$. Note that
-$\ket{\oplus}$ is invariant under $U_{i}$, so we have $\muF_{\oplus}\left(P_{0}\right)=\muF_{U_{i}\ket{\oplus}}\left(U_{i}P_{0}U_{i}^{\dagger}\right)=\muF_{\oplus}\left(P_{i}\right)$
-by Eq.~(\ref{eq:basis-independent}). Let $P'=P_{0}+P_{1}+P_{2}$.
-Since $P'\ket{\oplus}=\ket{\oplus}$, Eq.~(\ref{eq:zero}) implies
-\begin{equation}
-1=\muF_{\oplus}\left(P'\right)=\muF_{\oplus}\left(P_{0}\right)+\muF_{\oplus}\left(P_{1}\right)+\muF_{\oplus}\left(P_{2}\right)=3\muF_{\oplus}\left(P_{0}\right)\,,
-\end{equation}
-and thus for $i=0$, $1$, and $2$, we always have $\muF_{\oplus}\left(P_{i}\right)=\frac{1}{3}$.
-
-Following the computation similar to the previous paragraph, we now
-compute the probabilities induced by $\ket{\Phi'}=U'\ket{\oplus}=\frac{2\alpha}{\gamma}\ket{0}+\frac{1}{\gamma}\ket{2}$,
-where $\alpha=\fnorm*{\frac{1}{2}}\in\ff{p^{2}}$ and
-\begin{equation}
-U'=\begin{pmatrix}\alpha & \alpha & 0\\
--\alpha & \alpha & 0\\
-0 & 0 & 1
-\end{pmatrix}\,.
-\end{equation}
-Since $\ket{2}$ is invariant under $U'$, Eq.~(\ref{eq:basis-independent})
-implies $\muF_{\oplus}\left(P_{2}\right)=\muF_{U'\ket{\oplus}}\left(U'P_{2}U'^{\dagger}\right)=\muF_{\Phi'}\left(P_{2}\right)$.
-Also, Eq.~(\ref{eq:zero}) implies $\muF_{\Phi'}\left(P_{0}\right)+\muF_{\Phi'}\left(P_{2}\right)=\muF_{\Phi'}\left(P_{0}+P_{2}\right)=1$.
-By moving $\muF_{\Phi'}\left(P_{2}\right)$ to the right-hand side
-of the equation, we have 
-\begin{equation}
-\muF_{\Phi'}\left(P_{0}\right)=1-\muF_{\Phi'}\left(P_{2}\right)=1-\muF_{\oplus}\left(P_{2}\right)=1-\tfrac{1}{3}=\tfrac{2}{3}\,.\label{eq:prob23}
-\end{equation}
-
-Iterating the similar process with $\ket{\Phi''}=U''\ket{\Phi'}=\frac{2\alpha}{\gamma}\left(\ket{0}+\ket{1}\right)+\frac{\beta}{\gamma}\ket{2}$,
-where $\beta=\fnorm*{-1}\in\ff{p^{2}}$ and
-\begin{equation}
-U''=\begin{pmatrix}1 & 0 & 0\\
-0 & \beta^{*} & 2\alpha\\
-0 & 2\alpha^{*} & \beta
-\end{pmatrix}\,.
-\end{equation}
-Because $\ket{\Phi''}$ is invariant under $U_{1}$, invoking Eq.~(\ref{eq:basis-independent})
-in $\muF_{\Phi''}\left(P_{1}\right)=\muF_{U_{1}\ket{\Phi''}}\left(U_{1}P_{1}U_{1}^{\dagger}\right)=\muF_{\Phi''}\left(P_{0}\right)$,
-we know $\muF_{\Phi''}\left(P_{1}\right)$ and $\muF_{\Phi''}\left(P_{0}\right)$
-are same. They are both equal to $\tfrac{2}{3}$ because $\muF_{\Phi''}\left(P_{0}\right)=\muF_{U''\ket{\Phi'}}\left(U''P_{0}U''\right)=\muF_{\Phi'}\left(P_{0}\right)=\tfrac{2}{3}$
-by Eqs.~(\ref{eq:basis-independent}) and (\ref{eq:prob23}). Since
-$P'\ket{\Phi''}=\ket{\Phi''}$, Eq.~(\ref{eq:zero}) implies
-\begin{equation}
-1=\muF_{\Phi''}\left(P'\right)=\muF_{\Phi''}\left(P_{0}\right)+\muF_{\Phi''}\left(P_{1}\right)+\muF_{\Phi''}\left(P_{2}\right)=\tfrac{2}{3}+\tfrac{2}{3}+\muF_{\Phi''}\left(P_{2}\right)>\tfrac{4}{3}\,.
-\end{equation}
-This is inconsistent with the requirement that the probabilities for
-orthogonal outcomes add up to $1$, and build a contradiction.\end{proof}
-
-The reason why there is no ``sensible'' Born rule might be that
-the state spaces are now discrete and finite, but we still consider
-mapping probability assignments to infinitely precise values in the
-unit interval $\left[0,1\right]$. To overcome this issue, we want
-to consider a discrete Born rule mapping to a finite number of intervals
-called interval-valued probability~\cite{JamisonLodwick2004,THOS2018}.
-To adopting the idea of interval-valued probability step-by-step,
-before attempting to study quantum interval-valued probability over
-finite fields, we will first review the classical interval-valued
-probability and extend it with the conventional quantum theory in
-the next chapter.
-
-\chapter{Toward a Quantum Measurement Theory with Error: Quantum Interval-Valued
-Probability\label{chap:QIVPM}}
 
@@
 \end{align*}
-\begin{comment}
-\noindent 
-\begin{equation*} 
-\begin{aligned} 
-\noalign{$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)$} 
-\qquad\qquad=~~&\bar{\mu}\left(P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
- & (\mbox{because } P_{0} = P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})) \\ 
-=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) \\ 
-=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
-     & (\mbox{because } P_{1} = P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}) \\ 
-=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1}))+\bar{\mu}(P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1})+ 
-   \bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
-=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1}+P_{0}P_{1}) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
-=~~& \bar{\mu}(P_{0}) + \bar{\mu}(P_{1}) 
-\end{aligned} 
-\end{equation*}
-\end{comment}
 \end{proof}
@@
 We have thus quantified one important aspect of uncertainty in quantum
-mechanics—the effect of the imprecise nature of devices—which is a
-novel addition to the theory of measurement. Indeed, as Heisenberg
+mechanics---the effect of the imprecise nature of devices---which
+is a novel addition to the theory of measurement. Indeed, as Heisenberg
 emphasized in his famous microscope example~\cite{Heisenberg1983},
@@
 
-\chapter{Conclusion and Further Discussion\label{chap:Further-Discussion}}
-
 \section{Summary}
@@
 \begin{comment}
-
-\chapter{Conclusion\label{chap:Conclusion}}
-
-\todo{Add a two-page conclusion chapter which could include further
-discussion, but it can be only a few sentences? }\todo{Discrete
-\textgerman[variant=german,spelling=new,babelshorthands=true]{Schrödinger}
-equation? And its relationship with Grover's algorithm? }\todo{Notice
-that in differential geometry, the Killing-Hopf theorem asserts that
-having positive constant curvature guarantees a manifold is essentially
-a sphere, but say little things even if the curvature has an only
-small deviation from constant. Since a quantum probability measure
-is glued by classical probability measures, like a manifold. When
-their relations are exact, Gleason's theorem asserts that a quantum
-probability measure can be essentially induced by the Born rule, but
-they can be wild when we move on to the interval-valued situation!
-}
+\todo{Discrete \foreignlanguage{ngerman}{Schrödinger} equation? And
+its relationship with Grover's algorithm? }\todo{Notice that in
+differential geometry, the Killing-Hopf theorem asserts that having
+positive constant curvature guarantees a manifold is essentially a
+sphere, but say little things even if the curvature has an only small
+deviation from constant. Since a quantum probability measure is glued
+by classical probability measures, like a manifold. When their relations
+are exact, Gleason's theorem asserts that a quantum probability measure
+can be essentially induced by the Born rule, but they can be wild
+when we move on to the interval-valued situation! }
 \end{comment}
@@
 
-\clearpageAddContents{chapter}{Bibliography} %
 \begin{comment}
@@
 \printbibliography
-
-\addContentsChapterWithoutPagenumber{Curriculum Vitae}
-
-\includepdf[pages=-]{CV_thesis}
 \end{document}

### 2022-04-10 pullback.tex
pullback.lyx Updated to reduce compile error because of the Chinese characters...

@@
 \newcommand{\nb}{\nolinebreak[3] }
-\NewDocumentCommand{\jthSubsystem}{m O{} m}{{#1}_{#2}^{#3}}
+%\NewDocumentCommand{\jthSubsystem}{m O{} m}{{#1}_{#2}^{#3}}
 
@@
 \usepackage{xparse}
-\NewDocumentCommand{\fnorm}{s m}{\mathsf{N}\IfBooleanT{#1}{^{-1}}\left({#2}\right)}
+%\NewDocumentCommand{\fnorm}{s m}{\mathsf{N}\IfBooleanT{#1}{^{-1}}\left({#2}\right)}
 
@@
 
-\usepackage[font=doublespacing]{caption}
+%\usepackage[font=doublespacing]{caption}
+\usepackage{caption}
 
@@
 \usepackage{babel}
-\usepackage[style=numeric-comp,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
+\usepackage[style=numeric-comp,backend=bibtex,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
 \addbibresource{prop.bib}
@@
 as $\lambda E.\left(\varphi^{*}\mu\right)\left(E\right)$, i.e., $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$,
-and $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$ the
-pullback of $\mu$ by $\varphi$, and summarize how ``pullback''
+call $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
+the pullback of $\mu$ by $\varphi$, and summarize how ``pullback''
 preserves their structures in Table~\ref{tab:Comparison}. 
@@
 that uses $\subseteq$ instead of $=$ for the same reason as before.
-The new condition, known as \emph{convexity} \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997Chinese,Marinacci1999,MarinacciMontrucchio2005,Grabisch2016},
+The new condition, known as \emph{convexity} \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,MarinacciMontrucchio2005,Grabisch2016},
 reduces to the previously motivated Eq.~(\ref{eq:disjoint}) when
@@
 
-\begin{thm}[Shapley \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997Chinese,Grabisch2016}]\label{thm:Shapley-classical}Every
+\begin{thm}[Shapley \cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}]\label{thm:Shapley-classical}Every
 classical IVPM has a non-empty core.\end{thm}
@@
 is the direct counterpart of the convexity conditions, Eqs.~(\ref{eq:classicalconvex})
-and~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) \cite{Choquet1954,Shapley1971,NgMoYeh1997Chinese,MarinacciMontrucchio2005}.
+and~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) \cite{Choquet1954,Shapley1971,NgMoYeh1997,MarinacciMontrucchio2005}.
 Therefore, these conditions guarantee that for any conventional quantum

### 2022-04-11 pullback.tex
pullback.lyx Comment out \usepackage{datetime2-calc} to compile in Overleaf...
Keep comment out \usepackage{datetime2} to compile in Overleaf...
pullback.lyx Add "\usepackage{unicode-math}" back to typeset correctly...

@@
 \usepackage[T1,T2A]{fontenc}
-\usepackage[utf8]{inputenc}
 \usepackage{verbatim}
@@
 
-%\usepackage{unicode-math}
+\usepackage{unicode-math}
 \RequirePackage{ifthen}
@@
 
-\usepackage{datetime2}
-\usepackage{datetime2-calc}
+%\usepackage{datetime2}
+%\usepackage{datetime2-calc}
 %\monthGranted{June}%\DTMmonthname{\month}}
@@
 the function $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)\colon2^{\Omega}\rightarrow\left[0,1\right]$
-defined by precomposition is a classical probability measure. Since
-that ``precomposition'' is called ``pullback'' in differential
+defined by precomposition is a classical probability measure because
+\begin{align}
+\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability-1}
+\end{align}
+. Since that ``precomposition'' is called ``pullback'' in differential
 geometry~\cite{wiki:Pullback}\footnote{Whether this kind of ``pullback'' is categorical will need further
@@
  & P & \mapsto & \mu\left(P\right)
-\end{array}$ & Eqs.~(\ref{eq:QuantumProbability}) and (\ref{eq:QuantumProbability-Addition})\tabularnewline
+\end{array}$ & \tabularnewline
 \midrule
@@
 $\mu\left(\overline{E}\right)=[0.7,0.8]$. The two events $E$ and
-$\overline{E}$ are disjoint; the naïve addition of intervals would
-give $\mu\left(E\cup\overline{E}\right)=[0.9,1.1]$, which is not
-a valid probability interval. Moreover, the event $E\cup\overline{E}$
+$\overline{E}$ are disjoint; the na\"{\i}ve addition of intervals
+would give $\mu\left(E\cup\overline{E}\right)=[0.9,1.1]$, which is
+not a valid probability interval. Moreover, the event $E\cup\overline{E}$
 is the entire space; its probability interval should be $\necess$
@@
 \begin{comment}
-\todo{Discrete \foreignlanguage{ngerman}{Schrödinger} equation? And
-its relationship with Grover's algorithm? }\todo{Notice that in
-differential geometry, the Killing-Hopf theorem asserts that having
+\todo{Discrete \foreignlanguage{ngerman}{Schr\"{o}dinger} equation?
+And its relationship with Grover's algorithm? }\todo{Notice that
+in differential geometry, the Killing-Hopf theorem asserts that having
 positive constant curvature guarantees a manifold is essentially a

### 2022-04-11 pullback.tex
pullback.tex Exported from pullback.lyx...

@@
 defined by precomposition is a classical probability measure because
-\begin{align}
-\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability-1}
-\end{align}
-. Since that ``precomposition'' is called ``pullback'' in differential
+\begin{subequations}\label{eq:CPM-constraints}
+\begin{eqnarray}
+ &  & \mu\left(\varphi(\Omega)\right)=\mu\left(\mathbb{1}\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1\,,\label{eq:CPM-necess}\\
+ &  & \mu\left(\varphi\left(\overline{E}\right)\right)=\mu\left(\mathbb{1}-\varphi\left(E\right)\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1-\mu\left(\varphi\left(E\right)\right)\,,\label{eq:CPM-complement}\\
+ &  & \mu\left(\varphi(\emptyset)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-complement})}}{=}1-\mu\left(\varphi\left(\Omega\right)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-necess})}}{=}0\,,\label{eq:CPM-imposs}
+\end{eqnarray}
+\end{subequations}
+and for each pair of disjoin $E_{0}$ and $E_{1}$: 
+\begin{equation}
+\begin{aligned} & \mu\left(\varphi\left(E_{0}\cup E_{1}\right)\right)\\
+\overset{\textrm{Eq.~(\ref{eq:pullback-properties})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(\emptyset\right)\right)\\
+\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\left(\mathbb{1}-\mathbb{1}\right)\right)\\
+\overset{\textrm{Eq.~(\ref{eq:QuantumProbability-Addition})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)\right)+\mu\left(\varphi\left(E_{1}\right)\right)\,.
+\end{aligned}
+\label{eq:Probability-Addition}
+\end{equation}
+Since that ``precomposition'' is called ``pullback'' in differential
 geometry~\cite{wiki:Pullback}\footnote{Whether this kind of ``pullback'' is categorical will need further
@@
 \midrule 
-Event & $E\in2^{\Omega}$ & $\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events$ & Eqs.~(\ref{eq:pullback-properties-basic}) and (\ref{eq:pullback-properties})\tabularnewline
+Event & $E\in2^{\Omega}$ & $\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events$ & Eqs.~(\ref{eq:pullback-properties-basic}) and~(\ref{eq:pullback-properties})\tabularnewline
 \midrule 
@@
  & P & \mapsto & \mu\left(P\right)
-\end{array}$ & \tabularnewline
+\end{array}$ & Eqs.~(\ref{eq:CPM-constraints}) and~(\ref{eq:Probability-Addition})\tabularnewline
 \midrule

### 2022-04-13 pullback.tex
pullback.lyx Update here and there...

@@
 the function $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)\colon2^{\Omega}\rightarrow\left[0,1\right]$
-defined by precomposition is a classical probability measure because
+defined by precomposition is a classical probability measure\footnote{\begin{proof}
 \begin{subequations}\label{eq:CPM-constraints}
 \begin{eqnarray}
- &  & \mu\left(\varphi(\Omega)\right)=\mu\left(\mathbb{1}\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1\,,\label{eq:CPM-necess}\\
- &  & \mu\left(\varphi\left(\overline{E}\right)\right)=\mu\left(\mathbb{1}-\varphi\left(E\right)\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1-\mu\left(\varphi\left(E\right)\right)\,,\label{eq:CPM-complement}\\
+ &  & \mu\left(\varphi(\Omega)\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mu\left(\mathbb{1}\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1\,,\label{eq:CPM-necess}\\
+ &  & \mu\left(\varphi\left(\overline{E}\right)\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mu\left(\mathbb{1}-\varphi\left(E\right)\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1-\mu\left(\varphi\left(E\right)\right)\,,\label{eq:CPM-complement}\\
  &  & \mu\left(\varphi(\emptyset)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-complement})}}{=}1-\mu\left(\varphi\left(\Omega\right)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-necess})}}{=}0\,,\label{eq:CPM-imposs}
@@
 \end{subequations}
-and for each pair of disjoin $E_{0}$ and $E_{1}$: 
+and for each pair of disjoint $E_{0}$ and $E_{1}$, we have 
+\[
+\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties})}}{=}\varphi\left(\emptyset\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mathbb{0}\,,
+\]
+i.e., $\varphi\left(E_{0}\right)$ and $\varphi\left(E_{1}\right)$
+are orthogonal, and then: 
 \begin{equation}
@@
 \overset{\textrm{Eq.~(\ref{eq:pullback-properties})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(\emptyset\right)\right)\\
-\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\left(\mathbb{1}-\mathbb{1}\right)\right)\\
+\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)\right)\\
 \overset{\textrm{Eq.~(\ref{eq:QuantumProbability-Addition})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)\right)+\mu\left(\varphi\left(E_{1}\right)\right)\,.
@@
 \end{equation}
-Since that ``precomposition'' is called ``pullback'' in differential
+\end{proof}}. Since that ``precomposition'' is called ``pullback'' in differential
 geometry~\cite{wiki:Pullback}\footnote{Whether this kind of ``pullback'' is categorical will need further
-investigate.}, we will use their notation and write the precomposition $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)$
+investigate.}, we will use their notation, write the precomposition $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)$
 as $\lambda E.\left(\varphi^{*}\mu\right)\left(E\right)$, i.e., $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$,
@@
 \midrule 
-Probability measure could be simplified as & probability mass function $m:\Omega\rightarrow[0,1]$ such that $\left(\varphi^{*}\mu\right)(E)=\sum_{\omega\in E}m(\omega)$ & mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such that $\mu\left(P\right)=\Tr\left(\rho P\right)$ & \tabularnewline
+Probability measure could be simplified as & probability mass function $m:\Omega\rightarrow[0,1]$ such that $\left(\varphi^{*}\mu\right)\left(E\right)=\sum_{\omega\in E}m\left(\omega\right)$ & mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such that $\mu\left(P\right)=\Tr\left(\rho P\right)$ & \tabularnewline
 \midrule 
- & Need a notation for $\varphi^{*}\mu\mapsto m$ to keep going & Need a notation for $\mu\mapsto\rho$ to keep going & We may draw commuting diagram (?) here\tabularnewline
+ & Need a notation for $\varphi^{*}\mu\mapsto m$ to keep going & Need a notation for $\mu\mapsto\rho$ to keep going & We may draw commuting diagram here?\tabularnewline
 \midrule 
@@
 by $\varphi$ except we summarize classical measurement process as
-random variable, but summarize quantum measurement process as an observable.
+random variable, but summarize quantum measurement process as observable.
 Notice that after we fix an orthonormal basis~$\Omega$, $\varphi$
@@
 as the pullback of $\mathbf{O}$ by $\varphi$, and denoted by $\varphi^{*}\mathbf{O}$.\footnote{We might also choose the other way around so that each random variable
-has a push forward observable. This is better in the sense that we
-don't have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be
-different for different orthonormal basis, but every theorem for IVPMs
-starts from the quantum part with an observable, so we need the ambiguous
-$\varphi^{*}\mathbf{O}$ for each different orthonormal basis anyway.} According to Gleason's theorem, the table could be extended to simplify
+has a push forward observable. This is better in a sense that we don't
+have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be different
+for different orthonormal bases, but every theorem for IVPMs starts
+from the quantum part with an observable, so we need the notation
+$\varphi^{*}\mathbf{O}$ and fixing an orthonormal basis to disambiguate
+$\varphi^{*}\mathbf{O}$ anyway.} According to Gleason's theorem, the table could be extended to simplify
 the formula computing expectation values and the the post-measurement-state

### 2022-04-22 pullback.tex
pullback.lyx Commit a successful compiled lyx file for debugging...

@@
 \usepackage{booktabs}
+\usepackage{textcomp}
 \usepackage{mathrsfs}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
+  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}
+
 %% Because html converters don't know tabularnewline
@@
 \maketitle
-As discussed in Sec.~\ref{subsec:Classical-and-Quantum}, the quantum
-probability spaces could be thought as a big space glued by ``local''
-classical probability space defined by each orthonormal basis~$\Omega$
-according to the map $\varphi:2^{\Omega}\rightarrow\events$ defined
-in Eq.~(\ref{eq:pullback-function}) which sends a classical event
-$E\in2^{\Omega}$ to a quantum event $\varphi\left(E\right)\in\events$.
-Then, for any quantum probability measure $\mu\colon\events\rightarrow\left[0,1\right]$,
-the function $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)\colon2^{\Omega}\rightarrow\left[0,1\right]$
-defined by precomposition is a classical probability measure\footnote{\begin{proof}
+It is clear that each step of the measurement process is exactly equal
+or just mapped by $\varphi$ except we summarize classical measurement
+process as random variable, but summarize quantum measurement process
+as observable. Notice that after we fix an orthonormal basis~$\Omega$,
+$\varphi$ is actually an invertible map so that given an observable
+$\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$, we can define an unique
+random variable $\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\varphi^{-1}\left(P_{i}\right)}$
+corresponding to $\mathbf{O}$. Therefore, we call this random variable
+as the pullback of $\mathbf{O}$ by $\varphi$, and denoted by $\varphi^{*}\mathbf{O}$.\footnote{We might also choose the other way around so that each random variable
+has a push forward observable. This is better in a sense that we don't
+have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be different
+for different orthonormal bases, but every theorem for IVPMs starts
+from the quantum part with an observable, so we need the notation
+$\varphi^{*}\mathbf{O}$ and fixing an orthonormal basis to disambiguate
+$\varphi^{*}\mathbf{O}$ anyway.} According to Gleason's theorem, the table could be extended to simplify
+the formula computing expectation values and the the post-measurement-state
+postulates after we define a notation to send probability measures
+to states and the other way around.
+
+By following the same process, Sec.~\ref{sec:Interval-Uncertainty}
+showed the corresponding results for interval-valued probability.
+For any QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$, the
+function $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
+defined by $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
+is a classical IVPM.
+\begin{sidewaystable}
+\noindent \centering{}\caption{\label{tab:Comparison-interval}Comparison between the classical and
+quantum measurement processes with interval-valued probability for
+finite dimensional cases}
+%% ERT block 1 (before LyX tabular)
+\renewcommand{\tabular}{\tabularx{\linewidth}}
+\renewcommand{\endtabular}{\endtabularx} 
+\begin{tabular}{YYYY}
+\toprule 
+Name & Classical & Quantum & How does the structure preserve?\tabularnewline
+\midrule
+\midrule 
+Probability measure & $\begin{array}{cccc}
+\varphi^{*}\bar{\mu}\colon & 2^{\Omega} & \rightarrow & \mathscr{I}\\
+ & E & \mapsto & \bar{\mu}\left(\varphi\left(E\right)\right)
+\end{array}$ & $\begin{array}{cccc}
+\bar{\mu}\colon & \events & \rightarrow & \mathscr{I}\\
+ & E & \mapsto & \bar{\mu}\left(E\right)
+\end{array}$ & \tabularnewline
+\bottomrule
+\end{tabular}% ERT block 2 (after LyX tabular)
+\renewcommand{\tabular}{\ORIGtabular}
+\renewcommand{\endtabular}{\ORIGendtabular} 
+\end{sidewaystable}
+
+\section{Quantum Probability\label{sec:fuzzy}}
+
+A \emph{probability space} is a mathematical abstraction specifying
+the necessary conditions for reasoning coherently about collections
+of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
+Although they can be used to describe an individual quantum experiment,
+to describe a family of quantum experiments, we would like to glue
+their probability spaces together to define a quantum probability
+space. The glued quantum probability space is well-behaved since not
+only we can define the expectation values, but the quantum probability
+measure defined on the whole space can be simply induced by the Born
+rule according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
+
+\subsection{Classical Probability Space\label{subsec:Classical-and-Quantum}}
+
+Given a finite sample space~$\Omega$ representing all possible outcomes
+of a process, and its power set $2^{\Omega}$ as the classical event
+space, a classical probability measure~$\mu$ maps every event $E\subseteq\Omega$
+to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
+likely one of the outcomes in $E$ will happen. To maintain the coherence,
+$\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
+$\mu\left(\Omega\right)=1$, and $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
+where $\overline{E}$ is the complement of $E$.  Moreover, we require
+$\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
+for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
+
+Since the previous abstraction doesn't specify the process to generate
+the outcomes, this process could well be a quantum experiment. Let
+us prepare a beam of one kind of spin~$1$ particles, and split it
+by an inhomogeneous magnetic field along the $z$-axis as a well-known
+Stern-Gerlach type experiment \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
+This beam will be split into three beams, and we will call the outcome
+beams bent up as $\ket{0}$, bent down as $\ket{1}$, and not-bent
+as $\ket{2}$. Instead of sending a beam of particles, if only one
+particle is sent to the beam splitter, we will only get one of the
+outcomes $\ket{0}$, $\ket{1}$, and $\ket{2}$, and there is a probability
+to get each outcome. In the language of our abstraction, the set of
+outcomes is $\Omega_{0}=\{\ket{0},\ket{1},\ket{2}\}$. All possible
+events are $\emptyset$, $\left\{ \ket{0}\right\} $, $\left\{ \ket{1}\right\} $,
+$\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
+$\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
+and $\Omega_{0}$. Each time we perform this experiment, it induces
+a classical probability measure $\mu_{0}\colon2^{\Omega_{0}}\rightarrow\left[0,1\right]$.
+Moreover, if we prepare the particles in the ``same'' way as the
+particle inducing $\mu_{0}$, they will induce the same classical
+probability measure $\mu_{0}$.
+
+One special feature of quantum experiments is that the probabilities
+in different experiments are correlated. Consider another experiment
+sending the ``same'' particle as the previous one, but we rotate
+the inhomogeneous magnetic field $90\lyxmathsym{\textdegree}$ and
+now along the $x$-axis. This time we call the outcome beams bent
+left as $\ket{\ps}$, bent right as $\ket{\ms}$, and not-bent still
+as $\ket{2}$. Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
+and the probability measure $\mu_{1}\colon2^{\Omega_{1}}\rightarrow\left[0,1\right]$
+defined by this experiment is different from the previous one, they
+all produce a not-bent outcome~$\ket{2}$, and the probability of
+the common event $\left\{ \ket{2}\right\} $ is believed to be the
+same, i.e., 
+\begin{equation}
+\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)\,.\label{eq:mu0-equal-mu1}
+\end{equation}
+
+Since we may rotate the inhomogeneous magnetic field any degree~$\theta$,
+it is nature to represent the two bent outcomes as $\sin\theta\ket{0}+\cos\theta\ket{1}$
+and $\cos\theta\ket{0}-\sin\theta\ket{1}$. Then, $\ket{\ps}$ and
+$\ket{\ms}$ can be represented as $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$
+and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$. Conventionally
+\cite{peres1995quantum}, we will then postulate any normalized complex
+vector spanned by $\ket{0}$, $\ket{1}$, and $\ket{2}$ could be
+a measurement outcome, any orthonormal basis form a sample space,
+and sending a particle to this orthonormal basis inducing a classical
+probability measure. In general, as long as sending the same particle,
+the probability of the same event in different experiments should
+always be the same, i.e., giving two induced classical probability
+measures $\mu'\colon2^{\Omega'}\rightarrow\left[0,1\right]$ and $\mu''\colon2^{\Omega''}\rightarrow\left[0,1\right]$,
+the probabilities of getting $E\subseteq\Omega'\cap\Omega''$ are
+the same
+\begin{equation}
+\mu'\left(E\right)=\mu''\left(E\right)\,.\label{eq:mu-equal-same-event}
+\end{equation}
+\footnote{This fact is equivalent to the fact that commuting observables could
+be measured simultaneously which is essential to define contextuality
+and will be explained in Sec.~\ref{sec:Kochen-Specker}... Or maybe
+there is a gap between outcomes in a few types of experiments and
+every normalized vector in a Hilbert space could be an outcome, but
+inducing latter from axioms seems a bit too much here\ldots}
+
+\subsection{Quantum Probability Space}
+
+Since the probability induced by the different beam splitters are
+correlated, it is more natural to define one quantum event space~$\events$
+containing all possible classical event spaces using different beam
+splitters. However, simply taking the union of all event spaces is
+a bad idea because two events might appear different but represent
+the same situation. For example, if we take the complement on both
+sides of Eq.~(\ref{eq:mu0-equal-mu1}), we will have
+\begin{equation}
+\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
+\end{equation}
+that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
+and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
+these events should be identified as the same quantum event to simplify
+our discussion. This identification can be achieved by mapping a classical
+event~$E$ to the projector generated by $E$,\footnote{Should we prove whether there is no other way to identify?}
+\begin{equation}
+\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
+\end{equation}
+with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, because
+$\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)$ is equal to
+$\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)$ as operators,
+\begin{equation}
+\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,.
+\end{equation}
+
+In general, this function $\varphi$ naturally sends the set structure
+to the corresponding projector structure:
+\begin{align}
+\varphi\left(\Omega\right) & =\mathbb{1}\,, & \varphi\left(\overline{E}\right) & =\mathbb{1}-\varphi\left(E\right)\,.\label{eq:pullback-properties-basic}
+\end{align}
+Given two \emph{commuting} projectors $P_{0}$ and~$P_{1}$, there
+exists a pair of events $E_{0}$ and $E_{1}$ in the same sample space~$\Omega$
+such that $P_{0}=\varphi\left(E_{0}\right)$ and $P_{1}=\varphi\left(E_{1}\right)$.
+Conversely, given a pair of events $E_{0}$ and $E_{1}$ in the same
+sample space~$\Omega$, their corresponding quantum events $\varphi\left(E_{0}\right)$
+and $\varphi\left(E_{1}\right)$ are commuting and satisfying the
+following properties: 
+\begin{align}
+\varphi\left(E_{0}\cap E_{1}\right) & =\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,, & \varphi\left(E_{0}\cup E_{1}\right) & =\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,.\label{eq:pullback-properties}
+\end{align}
+Moreover, $E_{0}$ and $E_{1}$ are disjoint if and only if $\varphi\left(E_{0}\right)$
+and $\varphi\left(E_{1}\right)$ are orthogonal, where two projectors
+$P_{0}$ and $P_{1}$ are called \emph{orthogonal} if $P_{0}P_{1}=\mathbb{0}$.
+Because the structure is preserved by $\varphi$, so does the probability
+of events.
+
+\begin{lemma}Consider two classical events $E'\subseteq\Omega'$
+and $E''\subseteq\Omega''$ are mapped to the same projector, i.e.,
+$\varphi\left(E'\right)=\varphi\left(E''\right)$. Even if their experimental
+outcomes $\Omega'$ and $\Omega''$ may be different, when sending
+the ``same'' particle to these two experiments, and inducing two
+classical probability measures $\mu'\colon2^{\Omega'}\rightarrow\left[0,1\right]$
+and $\mu''\colon2^{\Omega''}\rightarrow\left[0,1\right]$, the probability
+of getting $E'$ is the same as the probability of getting $E''$,
+i.e., $\mu'\left(E'\right)=\mu''\left(E''\right)$.\end{lemma}
+
+\begin{proof}Consider the outcomes in the complement event of $E''$,
+$\Omega''\backslash E''$. Because $\varphi\left(E'\right)=\varphi\left(E''\right)$,
+every outcomes in $\Omega''\backslash E''$ is orthogonal to $E'$,
+and $\Omega'''=E'\cup\left(\Omega''\backslash E''\right)$ is an orthonormal
+basis. Consider its inducing classical probability measure $\mu'''\colon2^{\Omega'''}\rightarrow\left[0,1\right]$,
+we have
+\[
+\mu'\left(E'\right)\overset{\textrm{Eq.~(\ref{eq:mu-equal-same-event})}}{=}\mu'''\left(E'\right)=1-\mu'''\left(\Omega''\backslash E''\right)\overset{\textrm{Eq.~(\ref{eq:mu-equal-same-event})}}{=}1-\mu''\left(\Omega''\backslash E''\right)=\mu''\left(E''\right)\,.
+\]
+\end{proof}
+
+Therefore, for any classical event~$E$, its corresponding quantum
+event is defined to be the projector $\varphi\left(E\right)$, and
+the set of all projectors on a given Hilbert space is called a quantum
+event space~$\events$. Then, a quantum probability space can be
+defined as a quantum event space~$\events$ together with a quantum
+probability measure $\mu\colon\events\rightarrow\left[0,1\right]$
+subject to the corresponding constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
+\begin{align}
+\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability}
+\end{align}
+and for each pair of orthogonal projectors $P_{0}$ and $P_{1}$:
+\begin{equation}
+\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
+\end{equation}
+Because $\varphi$ respects the structure of events, it also respects
+probability measures according to precomposition.
+
+\begin{lemma}If we restrict the domain of $\varphi$ on a classical
+event space $2^{\Omega}$, the function $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
+defined by precomposition 
+\begin{equation}
+\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)\label{eq:classical-pullback}
+\end{equation}
+is a classical probability measure.\end{lemma}
+
+\begin{proof}
 \begin{subequations}\label{eq:CPM-constraints}
@@
 \end{equation}
-\end{proof}}. Since that ``precomposition'' is called ``pullback'' in differential
-geometry~\cite{wiki:Pullback}\footnote{Whether this kind of ``pullback'' is categorical will need further
-investigate.}, we will use their notation, write the precomposition $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)$
-as $\lambda E.\left(\varphi^{*}\mu\right)\left(E\right)$, i.e., $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$,
-call $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
+\end{proof}
+
+We denote the precomposition as $\varphi^{*}\mu$, because that ``precomposition''
+is called ``pullback'' in differential geometry and they use this
+notation~\cite{wiki:Pullback}\footnote{Whether this kind of ``pullback'' is categorical will need further
+investigate.}, and we will also follow their convention to call $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
 the pullback of $\mu$ by $\varphi$, and summarize how ``pullback''
@@
 \end{sidewaystable}
-We can then extend this table to compare between the classical and
-quantum measurement processes to get real numbers. It is clear that
-each step of the measurement process is exactly equal or just mapped
-by $\varphi$ except we summarize classical measurement process as
-random variable, but summarize quantum measurement process as observable.
-Notice that after we fix an orthonormal basis~$\Omega$, $\varphi$
-is actually an invertible map so that given an observable $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$,
-we can define an unique random variable $\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\varphi^{-1}\left(P_{i}\right)}$
-corresponding to $\mathbf{O}$. Therefore, we call this random variable
-as the pullback of $\mathbf{O}$ by $\varphi$, and denoted by $\varphi^{*}\mathbf{O}$.\footnote{We might also choose the other way around so that each random variable
-has a push forward observable. This is better in a sense that we don't
-have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be different
-for different orthonormal bases, but every theorem for IVPMs starts
-from the quantum part with an observable, so we need the notation
-$\varphi^{*}\mathbf{O}$ and fixing an orthonormal basis to disambiguate
-$\varphi^{*}\mathbf{O}$ anyway.} According to Gleason's theorem, the table could be extended to simplify
-the formula computing expectation values and the the post-measurement-state
-postulates after we define a notation to send probability measures
-to states and the other way around.
-
-By following the same process, Sec.~\ref{sec:Interval-Uncertainty}
-showed the corresponding results for interval-valued probability.
-For any QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$, the
-function $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
-defined by $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
-is a classical IVPM.
-\begin{sidewaystable}
-\noindent \centering{}\caption{\label{tab:Comparison-interval}Comparison between the classical and
-quantum measurement processes with interval-valued probability for
-finite dimensional cases}
-%% ERT block 1 (before LyX tabular)
-\renewcommand{\tabular}{\tabularx{\linewidth}}
-\renewcommand{\endtabular}{\endtabularx} 
-\begin{tabular}{YYYY}
-\toprule 
-Name & Classical & Quantum & How does the structure preserve?\tabularnewline
-\midrule
-\midrule 
-Probability measure & $\begin{array}{cccc}
-\varphi^{*}\bar{\mu}\colon & 2^{\Omega} & \rightarrow & \mathscr{I}\\
- & E & \mapsto & \bar{\mu}\left(\varphi\left(E\right)\right)
-\end{array}$ & $\begin{array}{cccc}
-\bar{\mu}\colon & \events & \rightarrow & \mathscr{I}\\
- & E & \mapsto & \bar{\mu}\left(E\right)
-\end{array}$ & \tabularnewline
-\bottomrule
-\end{tabular}% ERT block 2 (after LyX tabular)
-\renewcommand{\tabular}{\ORIGtabular}
-\renewcommand{\endtabular}{\ORIGendtabular} 
-\end{sidewaystable}
-
-\section{Quantum Probability\label{sec:fuzzy}}
-
-A \emph{probability space} is a mathematical abstraction specifying
-the necessary conditions for reasoning coherently about collections
-of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
-Although they can be used to describe an individual quantum experiment,
-to describe a family of quantum experiments, we would like to glue
-their probability spaces together to define a quantum probability
-space. The glued quantum probability space is well-behaved since not
-only we can define the expectation values, but the quantum probability
-measure defined on the whole space can be simply induced by the Born
-rule according to Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
-
-\subsection{Classical and Quantum Probability Spaces\label{subsec:Classical-and-Quantum}}
-
-Given a finite sample space~$\Omega$ representing all possible outcomes
-of a process, and its power set $2^{\Omega}$ as the classical event
-space, a classical probability measure~$\mu$ maps every event $E\subseteq\Omega$
-to a number $\mu\left(E\right)\in\left[0,1\right]$ specifying how
-likely one of the outcomes in $E$ will happen. To maintain the coherence,
-$\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
-$\mu\left(\Omega\right)=1$, and $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
-where $\overline{E}$ is the complement of $E$.  Moreover, we require
-$\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
-for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
-
-Since the previous abstraction doesn't specify the process to generate
-the outcomes, this process could well be a quantum experiment. Let
-us prepare a beam of one kind of spin~$1$ particles whose state
-can be characterized by a vector in three-dimen\-sional Hilbert space
-with basis vectors $\ket{0}$, $\ket{1}$, and $\ket{2}$. In principle,
-this beam can be split by a Stern-Gerlach type experiment according
-to the eigenvalues of the observable $\mathbf{O}_{0}$ with spectral
-decomposition 
-\begin{equation}
-\mathbf{O}_{0}=0\,\proj{0}+1\,\proj{1}+2\,\proj{2}\,,\label{eq:observable}
-\end{equation}
-and the states corresponding to the split beams are $\ket{0}$, $\ket{1}$,
-and $\ket{2}$ \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
-Instead of sending a beam of particles, if only one particle is sent
-to the beam splitter, the state of the particle after the experiment
-is one of $\ket{0}$, $\ket{1}$, and $\ket{2}$, and there is a probability
-to get each post-experimental state. In the language of our abstraction,
-the set of outcomes is $\Omega_{0}=\{\ket{0},\ket{1},\ket{2}\}$.
-All possible events are $\emptyset$, $\left\{ \ket{0}\right\} $,
-$\left\{ \ket{1}\right\} $, $\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
-$\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
-and $\Omega_{0}$. And this experiment defines a classical probability
-measure $\mu_{0}\colon2^{\Omega_{0}}\rightarrow\left[0,1\right]$.
-
-One special feature of quantum experiments is that the probabilities
-in different experiments are correlated. Consider another experiment
-sending exactly the same particle as the previous one but using a
-different beam splitter corresponding to the observable $\mathbf{O}_{1}$
-with spectral decomposition $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
-where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
-Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
-and the probability measure $\mu_{1}\colon2^{\Omega_{1}}\rightarrow\left[0,1\right]$
-defined by this experiment is different from the previous one, these
-two experiments may produce the same post-experimental state~$\ket{2}$,
-and the probability of the common event $\left\{ \ket{2}\right\} $
-is believed to be the same, i.e., 
-\begin{equation}
-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)\,.\label{eq:mu0-equal-mu1}
-\end{equation}
-In general, as long as sending the same particle, the probability
-of the same event in different experiments should always be the same.
-This fact is equivalent to the fact that commuting observables could
-be measured simultaneously which is essential to define contextuality
-and will be explained in Sec.~\ref{sec:Kochen-Specker}.
-
-Since the probability induced by the different beam splitters are
-correlated, it is more natural to define one quantum event space~$\events$
-containing all possible classical event spaces using different beam
-splitters. However, simply taking the union of all event spaces is
-a bad idea because two events might appear different but represent
-the same situation. For example, if we take the complement on both
-sides of Eq.~(\ref{eq:mu0-equal-mu1}), we will have
-\begin{equation}
-\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
-\end{equation}
-that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
-and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
-these events should be identified as the same quantum event to simplify
-our discussion. This identification can be achieved by mapping a classical
-event~$E$ to the projector generated by $E$,
-\begin{equation}
-\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
-\end{equation}
-with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, because
-$\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)$ is equal to
-$\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)$ as operators,
-\begin{equation}
-\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,.
-\end{equation}
-In general, if two classical events~$E$ and $E'$ are mapped to
-the same projector, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$,
-then the probability of $E$ is the same as the probability of $E'$.
-Therefore, for any classical event~$E$, its corresponding quantum
-event is defined to be the projector $\varphi\left(E\right)$, and
-the set of all projectors on a given Hilbert space is called a quantum
-event space~$\events$.
-
-This function $\varphi$ not only respects the probability of events
-but also naturally sends the set structure to the corresponding projector
-structure:
-\begin{align}
-\varphi\left(\Omega\right) & =\mathbb{1}\,, & \varphi\left(\overline{E}\right) & =\mathbb{1}-\varphi\left(E\right)\,.\label{eq:pullback-properties-basic}
-\end{align}
-Given two \emph{commuting} projectors $P_{0}$ and~$P_{1}$, there
-exists a pair of events $E_{0}$ and $E_{1}$ in the same sample space~$\Omega$
-such that $P_{0}=\varphi\left(E_{0}\right)$ and $P_{1}=\varphi\left(E_{1}\right)$.
-Conversely, given a pair of events $E_{0}$ and $E_{1}$ in the same
-sample space~$\Omega$, their corresponding quantum events $\varphi\left(E_{0}\right)$
-and $\varphi\left(E_{1}\right)$ are commuting and satisfying the
-following properties: 
-\begin{align}
-\varphi\left(E_{0}\cap E_{1}\right) & =\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,, & \varphi\left(E_{0}\cup E_{1}\right) & =\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,.\label{eq:pullback-properties}
-\end{align}
-Moreover, $E_{0}$ and $E_{1}$ are disjoint if and only if $\varphi\left(E_{0}\right)$
-and $\varphi\left(E_{1}\right)$ are orthogonal, where two projectors
-$P_{0}$ and $P_{1}$ are called \emph{orthogonal} if $P_{0}P_{1}=\mathbb{0}$.
-
-Then, a quantum probability space can be defined as a quantum event
-space~$\events$ together with a quantum probability measure $\mu\colon\events\rightarrow\left[0,1\right]$
-subject to the corresponding constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
-\begin{align}
-\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability}
-\end{align}
-and for each pair of orthogonal projectors $P_{0}$ and $P_{1}$:
-\begin{equation}
-\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
-\end{equation}
-Because $\varphi$ respects the probability of events, if we restrict
-the domain of $\varphi$ on a classical event space $2^{\Omega}$,
-the function $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
-defined by precomposition 
-\begin{equation}
-\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)\label{eq:classical-pullback}
-\end{equation}
-is a classical probability measure and called the pullback of $\mu$
-by $\varphi\colon2^{\Omega}\rightarrow\events$.
-
+
+\subsection{Measurement Process and Expectation Values}
+
+We can then extend Table~\ref{tab:Comparison} to compare between
+the classical and quantum measurement processes to get real numbers.
 Given a Hilbert space $\mathcal{H}$ of dimension $D$ and a probability

### 2022-05-02 pullback.tex
中文摘要.lyx Copied from dissertation.lyx as required by 中興大學人工智慧學程...

@@
 \maketitle
-It is clear that each step of the measurement process is exactly equal
-or just mapped by $\varphi$ except we summarize classical measurement
-process as random variable, but summarize quantum measurement process
-as observable. Notice that after we fix an orthonormal basis~$\Omega$,
-$\varphi$ is actually an invertible map so that given an observable
-$\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$, we can define an unique
-random variable $\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\varphi^{-1}\left(P_{i}\right)}$
-corresponding to $\mathbf{O}$. Therefore, we call this random variable
-as the pullback of $\mathbf{O}$ by $\varphi$, and denoted by $\varphi^{*}\mathbf{O}$.\footnote{We might also choose the other way around so that each random variable
-has a push forward observable. This is better in a sense that we don't
-have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be different
-for different orthonormal bases, but every theorem for IVPMs starts
-from the quantum part with an observable, so we need the notation
-$\varphi^{*}\mathbf{O}$ and fixing an orthonormal basis to disambiguate
-$\varphi^{*}\mathbf{O}$ anyway.} According to Gleason's theorem, the table could be extended to simplify
-the formula computing expectation values and the the post-measurement-state
-postulates after we define a notation to send probability measures
-to states and the other way around.
-
-By following the same process, Sec.~\ref{sec:Interval-Uncertainty}
-showed the corresponding results for interval-valued probability.
-For any QIVPM $\bar{\mu}\colon\events\rightarrow\mathscr{I}$, the
-function $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
-defined by $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
-is a classical IVPM.
-\begin{sidewaystable}
-\noindent \centering{}\caption{\label{tab:Comparison-interval}Comparison between the classical and
-quantum measurement processes with interval-valued probability for
-finite dimensional cases}
-%% ERT block 1 (before LyX tabular)
-\renewcommand{\tabular}{\tabularx{\linewidth}}
-\renewcommand{\endtabular}{\endtabularx} 
-\begin{tabular}{YYYY}
-\toprule 
-Name & Classical & Quantum & How does the structure preserve?\tabularnewline
-\midrule
-\midrule 
-Probability measure & $\begin{array}{cccc}
-\varphi^{*}\bar{\mu}\colon & 2^{\Omega} & \rightarrow & \mathscr{I}\\
- & E & \mapsto & \bar{\mu}\left(\varphi\left(E\right)\right)
-\end{array}$ & $\begin{array}{cccc}
-\bar{\mu}\colon & \events & \rightarrow & \mathscr{I}\\
- & E & \mapsto & \bar{\mu}\left(E\right)
-\end{array}$ & \tabularnewline
-\bottomrule
-\end{tabular}% ERT block 2 (after LyX tabular)
-\renewcommand{\tabular}{\ORIGtabular}
-\renewcommand{\endtabular}{\ORIGendtabular} 
-\end{sidewaystable}
 
@@
 $\mu$ is subject to the following constraints: $\mu\left(\emptyset\right)=0$,
-$\mu\left(\Omega\right)=1$, and $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
-where $\overline{E}$ is the complement of $E$.  Moreover, we require
-$\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
+$\mu\left(\Omega\right)=1$, and $\mu\left(\Omega\backslash E\right)=\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
+where $\Omega\backslash E$ is the complement of $E$, and we may
+simply write $\overline{E}$ if the sample space~$\Omega$ is clear
+from the context.  Moreover, we require $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
 for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
@@
 and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$. Conventionally
-\cite{peres1995quantum}, we will then postulate any normalized complex
-vector spanned by $\ket{0}$, $\ket{1}$, and $\ket{2}$ could be
-a measurement outcome, any orthonormal basis form a sample space,
-and sending a particle to this orthonormal basis inducing a classical
-probability measure. In general, as long as sending the same particle,
-the probability of the same event in different experiments should
-always be the same, i.e., giving two induced classical probability
+\cite{peres1995quantum,schwinger2001quantum}, we will then postulate
+any normalized complex vector spanned by $\ket{0}$, $\ket{1}$, and
+$\ket{2}$ could be a measurement outcome, any orthonormal basis form
+a sample space, and sending a particle to this orthonormal basis inducing
+a classical probability measure. In general, as long as sending the
+same particle, the probability of the same event in different experiments
+should always be the same, i.e., giving two induced classical probability
 measures $\mu'\colon2^{\Omega'}\rightarrow\left[0,1\right]$ and $\mu''\colon2^{\Omega''}\rightarrow\left[0,1\right]$,

### 2022-05-03 pullback.tex
pullback.lyx The version attached "On Wed, May 4, 2022 at 4:43 AM Yu-Tsung Tai <yuttai@alumni.iu.edu>"

@@
 where $\Omega\backslash E$ is the complement of $E$, and we may
-simply write $\overline{E}$ if the sample space~$\Omega$ is clear
-from the context.  Moreover, we require $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
+simply write $\Omega\backslash E$ as $\overline{E}$ if the sample
+space~$\Omega$ is clear from the context.  Moreover, we require
+$\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
 for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
@@
 by an inhomogeneous magnetic field along the $z$-axis as a well-known
-Stern-Gerlach type experiment \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
+Stern-Gerlach type experiment \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum,schwinger2001quantum}.
 This beam will be split into three beams, and we will call the outcome

### 2022-05-10 pullback.tex
pullback.lyx Global replace the subindex of the probability spaces along axes...

@@
 to get each outcome. In the language of our abstraction, the set of
-outcomes is $\Omega_{0}=\{\ket{0},\ket{1},\ket{2}\}$. All possible
+outcomes is $\Omega_{z}=\{\ket{0},\ket{1},\ket{2}\}$. All possible
 events are $\emptyset$, $\left\{ \ket{0}\right\} $, $\left\{ \ket{1}\right\} $,
@@
 $\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
-and $\Omega_{0}$. Each time we perform this experiment, it induces
-a classical probability measure $\mu_{0}\colon2^{\Omega_{0}}\rightarrow\left[0,1\right]$.
+and $\Omega_{z}$. Each time we perform this experiment, it induces
+a classical probability measure $\mu_{z}\colon2^{\Omega_{z}}\rightarrow\left[0,1\right]$.
 Moreover, if we prepare the particles in the ``same'' way as the
-particle inducing $\mu_{0}$, they will induce the same classical
-probability measure $\mu_{0}$.
+particle inducing $\mu_{z}$, they will induce the same classical
+probability measure $\mu_{z}$.
 
@@
 left as $\ket{\ps}$, bent right as $\ket{\ms}$, and not-bent still
-as $\ket{2}$. Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
-and the probability measure $\mu_{1}\colon2^{\Omega_{1}}\rightarrow\left[0,1\right]$
+as $\ket{2}$. Although the sample space $\Omega_{x}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
+and the probability measure $\mu_{x}\colon2^{\Omega_{x}}\rightarrow\left[0,1\right]$
 defined by this experiment is different from the previous one, they
@@
 \begin{equation}
-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)\,.\label{eq:mu0-equal-mu1}
+\mu_{z}\left(\left\{ \ket{2}\right\} \right)=\mu_{x}\left(\left\{ \ket{2}\right\} \right)\,.\label{eq:mu0-equal-mu1}
 \end{equation}
@@
 \begin{equation}
-\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
+\mu_{z}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{z}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{x}\left(\left\{ \ket{2}\right\} \right)=\mu_{x}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
 \end{equation}

### 2022-05-12 pullback.tex
pullback.lyx On Fri, May 13, 2022 at 4:10 AM Yu-Tsung Tai <yuttai@alumni.iu.edu>

@@
 
+\subsection{The Source of Probability and Contextuality}
+
+One of reason why we need probability is because we don't know the
+detail to generate the outcomes. For example, a number might be deterministically
+generated by a random number generator, but looks random for whom
+don't know the seed and the algorithm. One might calculate whether
+a flipped coin will be head up or tail up, but flipping coin looks
+like a random process for whom don't know the initial condition. Whether
+the randomness of a quantum process is also due to lack of knowledge
+was asked by Einstein, Podolsky, and Rosen (EPR)~\cite{EPR1935,peres1995quantum,544199,Mermin2007}.
+In the language of our previous examples, they guess there might be
+some unknown physical laws such that if we know the initial condition
+of the particle we could predict with certain that one of the outcomes
+$\omega_{z}\in\Omega_{z}$ will happen.
+
+EPR's question apparently looks hard, but could be explained if we
+assume the predictions among these processes are correlated and consider
+more experimental processes. To simplify the later discussion, we
+will represent the certain outcome $\omega_{z}$ as its characteristic
+function $\chi_{z}:\Omega_{z}\rightarrow\left\{ 0,1\right\} $ defined
+by
+\begin{equation}
+\chi_{z}\left(\omega\right)=\begin{cases}
+1 & \textrm{if }\omega=\omega_{z}\,;\\
+0 & \textrm{if }\omega\ne\omega_{z}\,,
+\end{cases}
+\end{equation}
+and we will represent the hypothetical certain prediction of experiment
+$\mu_{x}$ as another characteristic function $\chi_{x}:\Omega_{x}\rightarrow\left\{ 0,1\right\} $.
+Notice that Eq.~(\ref{eq:mu0-equal-mu1}) states the probability
+of event $\left\{ \ket{2}\right\} $ should be the same no matter
+which process to generate the outcomes. We may generalize this idea
+to assume the characteristic functions of the common outcomes to be
+the same, i.e., 
+\begin{equation}
+\chi_{z}\left(\ket{2}\right)=\chi_{x}\left(\ket{2}\right)\,.\label{eq:equality-among-chi}
+\end{equation}
+
+\subsection{Quantum Probability Space}
+
 Since we may rotate the inhomogeneous magnetic field any degree~$\theta$,
@@
 inducing latter from axioms seems a bit too much here\ldots}
-
-\subsection{Quantum Probability Space}
 

### 2022-05-21 pullback.tex
pullback.lyx Attached On Sun, May 22, 2022 at 5:10 AM Yu-Tsung Tai <yuttai@alumni.iu.edu>

@@
 don't know the seed and the algorithm. One might calculate whether
-a flipped coin will be head up or tail up, but flipping coin looks
-like a random process for whom don't know the initial condition. Whether
-the randomness of a quantum process is also due to lack of knowledge
-was asked by Einstein, Podolsky, and Rosen (EPR)~\cite{EPR1935,peres1995quantum,544199,Mermin2007}.
-In the language of our previous examples, they guess there might be
-some unknown physical laws such that if we know the initial condition
-of the particle we could predict with certain that one of the outcomes
+a flipped coin will be head up or tail up according to its initial
+condition, but flipping coin looks like a random process for whom
+don't know that. Whether the randomness of a quantum process is also
+due to lack of knowledge was asked by Einstein, Podolsky, and Rosen
+(EPR)~\cite{EPR1935,peres1995quantum,544199,Mermin2007}. In the
+language of our previous examples, they guess there might be some
+unknown physical laws such that if we know the initial condition of
+the particle we could predict with certain that one of the outcomes
 $\omega_{z}\in\Omega_{z}$ will happen.
@@
 assume the predictions among these processes are correlated and consider
-more experimental processes. To simplify the later discussion, we
-will represent the certain outcome $\omega_{z}$ as its characteristic
-function $\chi_{z}:\Omega_{z}\rightarrow\left\{ 0,1\right\} $ defined
-by
+more experimental processes. To simplify the discussion, we will represent
+the certain outcome $\omega_{z}$ as its characteristic function $\chi_{z}:\Omega_{z}\rightarrow\left\{ 0,1\right\} $
+defined by
 \begin{equation}
@@
 $\mu_{x}$ as another characteristic function $\chi_{x}:\Omega_{x}\rightarrow\left\{ 0,1\right\} $.
-Notice that Eq.~(\ref{eq:mu0-equal-mu1}) states the probability
-of event $\left\{ \ket{2}\right\} $ should be the same no matter
-which process to generate the outcomes. We may generalize this idea
-to assume the characteristic functions of the common outcomes to be
-the same, i.e., 
-\begin{equation}
-\chi_{z}\left(\ket{2}\right)=\chi_{x}\left(\ket{2}\right)\,.\label{eq:equality-among-chi}
-\end{equation}
+To have an idea how these characteristic functions could be correlated,
+we find their probabilities of event $\left\{ \ket{2}\right\} $ are
+the same no matter which process generates it as in Eq.~(\ref{eq:mu0-equal-mu1}).
+We may generalize this idea to assume that the characteristic functions
+satisfying a similar condition,
+\begin{equation}
+\chi_{z}\left(\ket{2}\right)=\chi_{x}\left(\ket{2}\right)\,,\label{eq:equality-among-chi}
+\end{equation}
+i.e., whether the hypothetical certain prediction is either $\ket{2}$
+or not $\ket{2}$ are the same for two experiments $\mu_{z}$ and
+$\mu_{x}$\footnote{To justify this assumption, we might need to assume that if we factor
+an experiment as the composition of partial experiments~\cite{peres1995quantum},
+the certain outcome of the original experiment is also the composition
+of the certain outcome of the partial experiments... etc. However,
+this kind of assumption is not as obvious as other assumptions we
+discussed in Sec.~\ref{subsec:Classical-and-Quantum}.}.
+
+Since the common part of characteristic functions are the same, it
+might be easier to glue these characteristic functions together and
+consider $\chi:\Omega_{z}\cup\Omega_{x}\rightarrow\left\{ 0,1\right\} $
+defined by
+\begin{equation}
+\chi\left(\omega\right)=\begin{cases}
+\chi_{z}\left(\omega\right) & \textrm{if }\omega\in\Omega_{z}\,;\\
+\chi_{x}\left(\omega\right) & \textrm{if }\omega\in\Omega_{x}\backslash\Omega_{z}\,.
+\end{cases}
+\end{equation}
+$\chi$ is the natural generalization of $\chi_{z}$ and $\chi_{x}$
+because if we restrict the function $\chi$ in a smaller domain $\Omega_{z}$,
+the resulting function $\chi\restriction_{\Omega_{z}}$ is exactly
+the same as $\chi_{z}$. Also, $\chi\restriction_{\Omega_{x}}=\chi_{x}$.
+
+We could further extend this idea to consider more experiments with
+different set of outcomes $\left\{ \Omega_{i}\right\} _{i=1}^{M}$.
+If we could predict with certain that one of the outcomes $\omega_{i}\in\Omega_{i}$
+will happen for every experiment, there is a characteristic function
+$\chi:\bigcup_{i=1}^{M}\Omega_{i}\rightarrow\left\{ 0,1\right\} $
+such that 
+\begin{equation}
+\sum_{\omega\in\Omega_{i}}\chi\left(\omega\right)=1\label{eq:characteristic_one}
+\end{equation}
+ for every set of outcomes $\Omega_{i}$. In contrast, if there is
+no characteristic function $\chi:\bigcup_{i=1}^{M}\Omega_{i}\rightarrow\left\{ 0,1\right\} $
+satisfying Eq.~(\ref{eq:characteristic_one}), then there is no certain
+prediction consistent with the outcomes $\left\{ \Omega_{i}\right\} _{i=1}^{M}$
+of all the experiments.
+
+After considering multiple experiments, we observe that the original
+Kochen-Specker theorem asserts that the characteristic function doesn't
+exists when we consider enough experiments.\footnote{Then we may put the 20-vector proof of the Kochen-Specker theorem
+here if we want...}
 

### 2022-10-29 pullback.tex
pullback.lyx Added some unreadable things... Comment out and commit whatever currently have so far...

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[11pt,english]{article}
+\documentclass[11pt,ngerman,english]{article}
 \usepackage[T1,T2A]{fontenc}
@@
 \usepackage{babel}
-\usepackage[style=numeric-comp,backend=bibtex,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
+\usepackage[style=numeric-comp,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
 \addbibresource{prop.bib}
@@
 
+\section{Introduction}
+
+The means by which quantum computing\footnote{We use the phrase \textquotedblleft conventional quantum theory\textquotedblright{}
+where necessary to distinguish the usual quantum theory and quantum
+computing paradigm using (continuous) complex numbers from discrete
+quantum theory. Alternative terminology in the literature includes
+\textquotedblleft actual,\textquotedblright{} \textquotedblleft standard,\textquotedblright{}
+and \textquotedblleft ordinary\textquotedblright{} quantum theory. } extends the capacity of classical computing frameworks deeply involves
+both the laws of physics and the mathematical principles of computation.
+Richard Feynman and \foreignlanguage{ngerman}{Rolf Landauer} \cite{Feynman1982Simulating,Landauer1996188},
+among others, have strongly advocated the careful study of quantum
+computation to understand its mechanisms and the source of its computational
+features. To tease apart a number of subtle properties of quantum
+computing, we previously replaced complex continuous numbers by finite
+fields to study how uncomputable numbers affect quantum theory \cite{geometry2013,DQT2014},
+and replaced real-valued probability measures by interval-valued probability
+measures to study the effect of experimental imperfections and finite
+precision measurements~\cite{THOS2018}. This time we try to decompose
+a quantum probability space as a family of classical probability spaces
+to see which part of quantum probability space has a classical counterpart,
+to have a unified notation for classical and quantum probability for
+this part, and to separate ``quantum-ness'' from the classical part
+in a quantum probability description.\footnote{We might also put ``equivalence principle'' as one of the motivation.
+Equivalence principle, gravitational and inertial forces are indistinguishable,
+is the foundation to build relativity, and we are stating that in
+some situation classical and quantum random process are indistinguishable...}
+
 \section{Quantum Probability\label{sec:fuzzy}}
@@
 of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
-Although they can be used to describe an individual quantum experiment,
-to describe a family of quantum experiments, we would like to glue
-their probability spaces together to define a quantum probability
+Since this abstraction doesn't specify the process to generate the
+outcomes, we could use the same abstraction to describe both classical
+and quantum processes, including tossing a coin and one Stern-Gerlach
+type experiment \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum,schwinger2001quantum}.
+
+Although a quantum process could be described by a probability space,
+the probability spaces describing a family of quantum experiments
+might contain some redundant information which could be used to glue
+these probability spaces together to define a quantum probability
 space. The glued quantum probability space is well-behaved since not
@@
 for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.
+
+\footnote{Should find a ``simple'' example comparing the classical and quantum
+process... Maybe Stern-Gerlach experiment with classical particle?}
 
